### 2023-07-15 Notes.tex
Notes

%(query-replace-regexp "\\\\sqsubseteq^{sh}_{\\([^}]*\\)}" "\\\\shiftpre[\\1]")
% --- LNCS ---'
\documentclass{llncs}

\usepackage{hyperref}
\usepackage[textsize=tiny]{todonotes}
\usepackage{etex}

\usepackage[all]{xy}
\SelectTips{cm}{}
% derivations and labels
\usepackage{proof}
\newcommand{\lab}[1]{\ensuremath{\mathsf{{#1}}}}
\newcommand{\slab}[1]{\ensuremath{\scriptstyle{\mathsf{{#1}}}}}

% ``boxed'' \infer command
\newcommand{\binfer}[3][]{
  \mbox{\infer[#1]{#2}{#3}}}

% Command for labels on the left side of the rule
%       \inferL{<name>}{<post>}{<pre>}
% generates:
%             <pre>
%      <name> ------
%             <post>
%
\newlength{\myheight}
\newcommand{\inferL}[3]
  {\settoheight{\myheight}{\mbox{${#2}$}}
   \raisebox{\myheight}{{#1}}
   \makebox[1mm]{}
   \mbox{\infer{#2}{#3}}
}

\usepackage{amssymb,graphicx,epsfig,color}
%\usepackage[scriptsize]{subfigure}
\usepackage{subcaption}
\usepackage{wrapfig}

% re-stating 
%\usepackage{thm-restate}

% showing labels
%\usepackage[inline]{showlabels}

\usepackage{pgf}
\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri,fit,positioning}
\tikzstyle{node}=[circle, draw=black, minimum size=1mm]
\tikzstyle{trans}=[font=\scriptsize]
\tikzstyle{lab}=[font=\small]

\newcommand{\pgfBox}{
  \begin{pgfonlayer}{background} 
    \fill[blue!2,thick,draw=black!50,rounded corners,inner sep=3mm] ([xshift=-1.5pt,yshift=-1.5pt]current bounding box.south west) rectangle ([xshift=1.5pt,yshift=1.5pt]current bounding box.north east);
  \end{pgfonlayer}
}

\newcommand{\Rrel}[1]   {\stackrel{{#1}}{\Longrightarrow}}
\newcommand{\oa}{\overline a}
\newcommand{\ob}{\overline b}
\newcommand{\oc}{\overline c}
\newcommand{\od}{\overline d}
\newcommand{\nil}{{\tt 0}}
\newcommand{\rec}{\emph{rec}}
\newcommand{\fn}[1]{{\mathtt{fn}}(#1)}
%\usepackage{latexsym}
\usepackage{stmaryrd}
\def\encodep#1{\llfloor#1\rrfloor}

\newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}

\newcommand{\dpo}{\textsc{dpo}}

% base classes of categories for adhesive and quasi adhesive case
\newcommand{\bAdh}{\ensuremath{\mathbb{B}}}
\newcommand{\bQAdh}{\ensuremath{\mathbb{QB}}}

%from pawel
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
%2 righe tolte da Fabio
\usepackage{amssymb}
%\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{xspace}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage{float}
\usepackage{fancybox}

%%%%%%%% MATHEMATICAL NOTATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%symbol for natural numbers
\newcommand{\nat}{\ensuremath{\mathbb{N}}}

% finite subset
\newcommand{\sfin}{\ensuremath{\subseteq_{\mathit{fin}}}}

% flattening of a multiset
\newcommand{\flt}[1]{\ensuremath{[\![{#1}]\!]}}

% compact elements
\newcommand{\compact}[1]{\ensuremath{\mathop{\mathsf{K}({#1})}}}

% principal ideal
\newcommand{\principal}[1]{\ensuremath{\mathop{\downarrow\!{#1}}}}

% ideal completion
\newcommand{\ideal}[1]{\ensuremath{\mathsf{Idl}({#1})}}

% complete prime elements
\newcommand{\pr}[1]{\ensuremath{\mathop{\mathit{pr}({#1})}}}
\newcommand{\wpr}[1]{\ensuremath{\mathop{\mathit{wpr}({#1})}}}

% irreducible elements
\newcommand{\ir}[1]{\ensuremath{\mathop{\mathit{ir}({#1})}}}

% difference of irreducible elements
\newcommand{\diff}[2]{\ensuremath{\delta({#1},{#2})}}

% immediate precedence

% abbreviation for event structure
% \newcommand{\esabbr}{event structure}
\newcommand{\esabbr}{\textsc{es}}
\newcommand{\esnabbr}{\textsc{esnb}}
\newcommand{\esnmabbr}{\textsc{esn}}
\newcommand{\eseqabbr}{\textsc{epes}}

% predecessor of an irreducible
\newcommand{\pred}[1]{\ensuremath{\mathit{p}({#1})}}

% irreducible elements in es domains
\newcommand{\esir}[2]{\ensuremath{\langle{#1}, {#2}\rangle}}

% equivalence classes [of irreducibles]
\newcommand{\eqclass}[2][]{\ensuremath{[{#2}]_{\scriptscriptstyle {#1}}}}
% union of the equivalence classes of the elements in a set
\newcommand{\eqclasscup}[2]{\ensuremath{{#2}_{\scriptscriptstyle {#1}}}}

\newcommand{\eqclassir}[1]{\ensuremath{\eqclass[\leftrightarrow^*]{#1}}}

% quotient of set wrt a relation
\newcommand{\quotient}[2]{\ensuremath{{#1}_{\scriptscriptstyle {#2}}}}

% category of event structures 
\newcommand{\es}{\ensuremath{\mathsf{ES}}}
% category of stable event structures 
\newcommand{\ses}{\ensuremath{\mathsf{sES}}}
% category of prime event structures 
\newcommand{\pes}{\ensuremath{\mathsf{pES}}}
% category of prime event structures with equivalence
\newcommand{\epes}{\ensuremath{\mathsf{epES}}}

% category of connected event structures 
\newcommand{\ces}{\ensuremath{\mathsf{cES}}}

% category of weak prime algebraic domains domains 
\newcommand{\WDom}{\ensuremath{\mathsf{wDom}}}
% category of domains
\newcommand{\Dom}{\ensuremath{\mathsf{Dom}}}
% category of prime algebraic domains
\newcommand{\PDom}{\ensuremath{\mathsf{pDom}}}

%%%%% NON BINARY CONFLICT

% category of event structures 
\newcommand{\esn}{\ensuremath{\mathsf{ES_{nb}}}}
% category of stable event structures 
\newcommand{\sesn}{\ensuremath{\mathsf{sES_n}}}

% category of connected event structures 
\newcommand{\cesn}{\ensuremath{\mathsf{cES_{nb}}}}

% category of prime event structures 
\newcommand{\pesn}{\ensuremath{\mathsf{pES_n}}}

% category of fusion domains 
\newcommand{\WDomb}{\ensuremath{\mathsf{wDom_b}}}
% category of domains
\newcommand{\Domb}{\ensuremath{\mathsf{Dom_b}}}
% category of prime algebraic domains
\newcommand{\PDomb}{\ensuremath{\mathsf{pDom_b}}}

%%%%% END NON BINARY CONFLICT

% slice category
\newcommand{\slice}[2]{\ensuremath{({#1} \downarrow {#2})}}

% event structure for a domain
\newcommand{\zev}[0]{\ensuremath{\mathcal{E}}}
\newcommand{\ev}[1]{\ensuremath{\zev({#1})}}

% from general to connected event structures
\newcommand{\zconnes}[0]{\ensuremath{\mathcal{C}}}
\newcommand{\connes}[1]{\ensuremath{\zconnes({#1})}}
% and inclusion
\newcommand{\zinces}[0]{\ensuremath{\mathcal{I}}}
\newcommand{\inces}[1]{\ensuremath{\zinces({#1})}}

% stable version
\newcommand{\zsev}[0]{\ensuremath{\mathcal{E}_S}}
\newcommand{\sev}[1]{\ensuremath{\zsev({#1})}}

% with equivalence
\newcommand{\zeveq}[0]{\ensuremath{\mathcal{E}_{eq}}}
\newcommand{\eveq}[1]{\ensuremath{\zeveq({#1})}}

% es with equivalence to es and vice
\newcommand{\zfuse}[0]{\ensuremath{\mathcal{M}}}
\newcommand{\fuse}[1]{\ensuremath{\zfuse({#1})}}
\newcommand{\zunf}[0]{\ensuremath{\zunf}}
\newcommand{\unf}[1]{\ensuremath{\mathcal{U}({#1})}}

% Winskel/Droste version
\newcommand{\zevwd}[0]{\ensuremath{\mathcal{E}_{wd}}}
\newcommand{\evwd}[1]{\ensuremath{\zevwd({#1})}}

% configurations of an event structure
\newcommand{\conf}[1]{\ensuremath{\mathit{Conf}({#1})}}
% finite configurations
\newcommand{\conff}[1]{\ensuremath{\mathit{Conf_F}({#1})}}

% product of the sets of minimal enablinsg
\newcommand{\pmin}[1]{\ensuremath{U_{#1}}}

% connectectedness of minimal enablinsg
\newcommand{\conn}[1]{\ensuremath{\stackrel{#1}{\frown}}}

% domain for an event structure or graph grammar
\newcommand{\zdom}[0]{\ensuremath{\mathcal{D}}}
\newcommand{\dom}[1]{\ensuremath{\zdom({#1})}}

\newcommand{\zdomeq}[0]{\ensuremath{\mathcal{D}_{eq}}}
\newcommand{\domeq}[1]{\ensuremath{\zdomeq({#1})}}

% partial order for a graph grammar
\newcommand{\poset}[1]{\ensuremath{\mathcal{P}({#1})}}

% stable version
\newcommand{\pdom}[1]{\ensuremath{\mathcal{D}_S({#1})}}
\newcommand{\ppdom}[0]{\ensuremath{\mathcal{D}_S}}

% powerset
\newcommand{\Pow}[1]{\ensuremath{\mathbf{2}^{#1}}}

% powerset of finite subsets
\newcommand{\Powfin}[1]{\ensuremath{\mathbf{2}_\mathit{fin}^{#1}}}

% powerset of subsets of cardinality <= 1
\newcommand{\Powone}[1]{\ensuremath{\mathbf{2}_1^{#1}}}

% integer interval
\newcommand{\interval}[2][1]{\ensuremath{[{#1},{#2}]}}

% domain interval
\newcommand{\dint}[2]{\ensuremath{[{#1},{#2}]}}

% set of intervals
\newcommand{\IntSet}[1]{\ensuremath{\mathop{\mathit{Int}({#1})}}}

% intervals to irreducibles and vice
\newcommand{\inir}{\ensuremath{\mathop{\mathit{\zeta}}}}
\newcommand{\irin}{\ensuremath{\mathop{\mathit{\iota}}}}

% permutations
\newcommand{\perm}{\sigma}

% causes
\newcommand{\causes}[1]{\ensuremath{\lfloor {#1})}}

%%% GRAPH GRAMMARS

\newcommand{\Abs}[1]{\ensuremath{\mathsf{Abs}({#1})}}
\newcommand{\tr}[1]{\ensuremath{\mathsf{Tr}({#1})}}
% fusion safe traces
\newcommand{\trs}[1]{\ensuremath{\mathsf{Tr}_s({#1})}}
%\newcommand{\graph}{\ensuremath{\mathsf{Graph}}}
\newcommand{\tgraph}[1]{\ensuremath{\mathsf{Graph}_{#1}}}
\newcommand{\can}[1]{\ensuremath{\mathsf{C}({#1})}}
% source and target of a derivation
\newcommand{\source}[1]{\ensuremath{\mathsf{s}({#1})}}
\newcommand{\target}[1]{\ensuremath{\mathsf{t}({#1})}}
\newcommand{\col}[1]{\ensuremath{\mathsf{col}({#1})}}

% left decorated trace
\newcommand{\ltrace}[1]{\ensuremath{\langle {#1}\rangle_c}}

\newcommand{\bx}[1]{\phantom{\big(}#1{\phantom{\big)}}}
\newcommand{\bxx}[1]{\,#1\,}
\newcommand{\cycl}[1]{\ensuremath{\mbox{\textcircled{\scriptsize{$#1$}}}}}
\renewcommand{\iff}{\ensuremath{\Leftrightarrow}}

%%% NEW

\usepackage{xparse}

% inversions
\newcommand{\inv}[1]{\ensuremath{inv}({#1})}

% direct shift
\newcommand{\shiftdir}[1][]{\ensuremath{\mathrel{{\rightsquigarrow}^{\mathit{sh}}_{#1}}}}

% shift preorder
\newcommand{\shiftpre}[1][]{\ensuremath{\mathrel{{\sqsubseteq}^{\mathit{sh}}_{#1}}}}

% shift equivalence
\newcommand{\shifteq}[1][]{\ensuremath{\mathrel{{\equiv}^\mathit{sh}_{#1}}}}

% transp{source}[target]: if target not specified source+1
\NewDocumentCommand{\transp}{m o}{%
  \ensuremath{({#1},%
  \IfNoValueTF{#2}%
    {{#1}+1}%
    {#2}%
    )}
}

\NewDocumentCommand{\mycommand}{o}{%
  % <code>
  \IfNoValueTF{#1}
    {code when no optional argument is passed}
    {code when the optional argument #1 is present}%
  % <code>
}
% interchange
\newcommand{\IC}[1]{\ensuremath{\mathit{IC}({#1})}}

\title{Ideas}

\begin{document}
\maketitle

\subsection*{Shift equivalence for non-right linear}

Sequential independence is a key ingredient in the concurrency theory of DPO graph transformation, since it states when consecutive rewriting steps can be switched, thus 
identifying them as causally unrelated. The associated theory of shift equivalence on rewriting sequences is well-understood for linear rules, including its 
connection with standard models for concurrent systems such as event structures. 
%
This is not so for rules that are only left-linear, i.e., such that
their right-hand side may merge graph items.

In particular, if one just take the definition with general
interchange pairs, undesidered things might happen. In particular one
can have shift-equivalent derivations where the permutation is the
identity but which are non isomorphic (e.g., in GraphShift, page 1-2
$\rho_1 \shifteq \rho_3$, but $\rho_1 \equiv^{a} \rho_3$.

We want a notion of shift-equivalence which ensures some properties
which are indispensable to allow to interpret derivations up-to shift
as equivalent concurrent computations which differ only for the fact
that independent steps have been moved around. When moving around steps, we should not loose track of the identity of the steps: this is essential to be able to have an event structure semantics with a clearly defined notion of event.

Hence we assume to deal
with a notion of shift-equivalence between derivations of the kind
$\rho \shifteq_\sigma \rho'$ where $\rho, \rho'$ consist of $n$
rewriting steps, $\sigma: \interval{n} \to \interval{n}$ is a
permutation (the idea being that $\rho$ is obtained from $\rho'$
pemutating the steps according to $\sigma$) with the following
properties:

\begin{itemize}
\item \textbf{Property 0}. Shift equivalence is an equivalence, in particular it is symmetric. I.e., if  $\rho \shifteq_\sigma \rho'$ then $\rho' \shifteq_{\sigma^{-1}} \rho$;

\item \textbf{Property 1}. Derivations which are shift-equivalent via the
  identity permutation are isomorphic: if $\rho \shifteq \rho'$ then
  $\rho \equiv^a \rho'$;

\item \textbf{Property 2}. Shift equivalence between adjacent rewriting steps
  is a property of the steps, invariant for permutation according to
  shift, i.e., if two steps are independent in some derivation $\rho$
  and we can prove that $\rho$ is shift-equivalent to some $\rho'$
  where the same steps are again consecutive, but possibly in a
  different position, then the steps are again independent, and also
  the converse holds. Formally, if $\rho \shifteq_\sigma \rho'$ with
  $\rho, \rho'$ consist of $n$ rewriting steps and for some
  $i \in \interval{n-1}$, $\sigma(i)+1 = \sigma(i+1)$, the the steps
  $i, i+1$ in $\rho$ are shift-independent iff $\sigma(i)$ and
  $\sigma(i)+1$ are so in $\rho'$.
\end{itemize}

\textbf{Question.} Taking the standard shift, with generic interchange pair, a a counterexample to property 1, is the one mentioned above.  Do we have a counterexample to property 2? Not clear to me.

The above discussion should lead to

\begin{enumerate}
\item The conditions proposed by Andrea for a good notion of shift (in
  the draft, GraphShift, Def. 3, cond (1)-(5), with the addition of
  Lemma 12).

  \textbf{Questions}: Can we reduce the set of axioms? Do we need something else relating abstraction equivalence (iso of derivation) and shift? Relation with symmetries?

\item For left-linear rules, the proposed notion of shift equivalence
  requires: uniqueness of the interchange pair and symmetry. Show that
  this satisfies the above

\item Apparently, the satisfaction of the properties above has not
  been explicitly observed for the case of linear rules. If so, it is
  worth to remark it.

\item Does the theory above apply to other cases. E.g., if one wants a
  proper notion of causality (avoiding or-causality) a possibility
  seems to be to restrict the applicability condition for rules, to
  prevent fusions to act on already merged items (see section V.D in
  the arxiv). By the way, note that the satisfaction of the conditions
  on shift depends not only on the notion of shift, but also on the
  notion of rewriting. In this case we expect to have a prime event
  structure (bit this has to do with the second part of the work).

\end{enumerate}

\subsection*{Event structures for non-right linear}

Ideally, one would like to be able to work with an abstract notion of
shift-equivalence and just using its properties as singled out in the
previous part derive a weak prime domain or connected event structure
for it. This is probably difficult, but one might need to add some
futher properties to be proved for the specific notion of shift at
hand.

For this part, relevant material is section V of Arxiv. We use abstraction equivalence (iso of derivations) $\equiv^{a}$ (def. 36), shift-equivalence $\shifteq_\sigma$ (Def. 38, traking the permutation) and their join $\equiv^c_\sigma$.

For linear rules on graphs it is known that two derivations are
related by $\rho \equiv^c_\sigma \rho'$ iff $\sigma$ is a consistent
permutation (def. 40, arxiv). Rough;y the idea is to take the colimit
and consider the rewriting steps over the colimit to deduce
dependencies. This was used in many places in the proofs, but for
left-linear rules the proof does not go through (only the implication
``if $\rho \equiv^c_\sigma \rho'$ then $\sigma$ is a consistent
permutation'' (Lemma 17(1)) seems to hold as the original proof do not
to rely on linearity, this should be double-checked, but the converse
is false). In general, the hope is to get rid of using consistent
permutation and use instead more asbtract properties of
shift-equivalence as discussed in the first part.

The general idea is to show that considering derivations are arrows from the source to the target graph, then the slice from the initial graph $\slice{[G_s]}{\tr{\mathcal{G}}}$ should be a pre-order, whose ideal completion is a weak prime domain.

Relevant technical lemma in Arxiv are:

\begin{itemize}

\item
  \textbf{Lemma 17}. Points (2) and (3) should be hopefully consequences of the general properties of shift in the previous part and they play a role in proving that $\slice{[G_s]}{\tr{\mathcal{G}}}$ is a pre-order (Prop. 14)

\item
  \textbf{Lemma 19}.
  (1) says that if $\psi; \psi_1 \equiv^c_\sigma \psi'; \psi_1'$ and the permutation $\sigma$ sends $n$ steps of $\psi_1$ to $\psi'$ then such steps are not in $\psi$ and they will need to be in every $\phi_2$ such that $\psi; \phi_2 \equiv^c_\sigma \psi'; \phi_2'$. In particular there is $\phi_2$ consisting of exactly $n$ steps which allows for commutation. This allows essentially to deduce existence of minimal upper bounds, al with the same length. 
  Then (2) shows that all minimal upper bounds are isomorphic, so that we have a sup.

  Again, the hope is to obtain this from the abstract properties of
  shift.

\item \textbf{Proposition 15} shows that $\ideal{\poset{\mathcal{G}}}$
  is a domain, i.e., algebraic finitary (see Def. 6), while
  \textbf{Theorem 6} prove that it is weak prime.

  Here I think that the proofs are draft modifications of the original ones, changed after discovering the property on consistent permutation to be wrong. But they are drafty, to be redone maybe keeping some ideas.

\subsection*{Event structures for non-right linear, but jointly mono matches}

This is the idea in Section V.D. As mentioned above, ideally, if the proof in the previous part were based just on abstract properties of shift, one could hope of proving that shift in this context has the right properties, deduce that the construction produces a weak prime domain.

Then, one could observe that in this specific context actually all weak primes are primes an thus deduce that this provides a prime algebraic domain/pes semantics of fusion.

\end{itemize}

\end{document}

\keywords{Shift equivalence, non-linear rules, DPO rewriting.}

\section{Introduction}
\label{se:graphs}

Shortly, shift equivalence can be defined as the smallest equivalence relation on derivations, i.e. sequences of rewriting steps,
that can be obtained by the iterated switch of sequentially 
independent steps. A crucial observation, which represented our starting point, is that the notion of sequential independence traditionally
adopted for linear graph transfomation systems is not adequate when we
allow rules to be non-right linear, i.e., in the presence of
fusions. Consider the rules in Fig.~\ref{fi:rules}, typed over the type graph $T$,
where numbers are used to represent the mappings from the interface to the left- and
right-hand sides.

\begin{figure}
  \input{Figure/rules.tex}

\caption{The type graph  and the rules of the grammar of the example.}
\label{fi:rules}
\end{figure}

Now, let us consider an initial graph with a single node. We can then obtain
the derivation $\rho_1 = \delta_1; \delta_2; \delta_3$ in Fig.~\ref{fi:der1}, where $\delta_2$ and $\delta_3$ are
sequential independent according to the standard notion.

\begin{figure}
  \input{Figure/der1.tex}
\caption{The derivation $\rho_1$.}
\label{fi:der1}
\end{figure}

We can exchange the applications of $p_2$ and $p_3$, thus getting the
derivation $\rho_2 = \delta_1; \delta_3'; \delta_2'$ in
Figure~\ref{fi:der2}. Now, one can exchange again $p_3$ and $p_2$,
reaching the derivation $\rho_3 = \delta_1; \delta_2'; \delta_3$ in
Figure~\ref{fi:der3}, where in $\delta_2'$ production $p_2$ uses the
node of the start graph and thus ``does not depend'' on $p_1$.

\begin{figure}[t]
  \input{Figure/der2.tex}
\caption{The derivation $\rho_2$.}
\label{fi:der2}
\end{figure}

\begin{figure}[t]
  \input{Figure/der3.tex}
\caption{The derivation $\rho_3$.}
\label{fi:der3}
\end{figure}

The fact that if we switch two steps and then switch them back, we obtain a derivation that is not equivalent to the original one has unpleasant consequences. For instance, if we restrict $\rho_1'$ and $\rho_3'$ to the first two steps, we get non-equivalent derivations $\delta_1;\delta_2 \not\shifteq \delta_1;\delta_2'$, but $\rho_1 \shifteq[\sigma] \rho_3$, with $\sigma$ mapping $\delta_1$ to $\delta_1$ and $\delta_2$ to $\delta_2'$.
%
The lack of such closure with respect to composition does not allow to obtain a causal semantics for graph transformation systems.
More precisely, it does  not allow to associate an event structure to a derivation.
%
Thus, the notion of sequential independence has to be refined. The point is that in the associated shift equivalence we want to forget who made the fusion, 
but we should not forget (as it happens in the example) that some fusions occurred.

% In Andrea's counterexample (same as above, but $p_2$ produces an item that is consumed by $p_3$, thus forcing $p_3$ to happen last), if we construct the domain we have:
% \begin{center}
%   \includegraphics[scale=.7]{dom.pdf}
% \end{center}
% which is a weak prime domain (actually a prime domain) but it does not capture the proper semantics (e.g., $p_2'$ and $p_3$ are the same event!).

Shift equivalence is made stricter by asking that two steps are
sequentially independent if the result of their switch is uniquely
determined. Intuitively, when there are several way of performing the
exchange, it means that the first step has executed some fusions that
the second step is using in an essential way, hence they should not
considered independent. Formally, this boils down to require that 
in the definition of sequential independence the interchange pair is unique.

The paper builds on this intuition: it introduces this stricter notion of sequential independence
(Section~xxx) and prove that the associated theory of shift equivalence on derivations is 
well-behaved with respect to the concatenation of rewriting steps (Section~xxx).
Finally, it outlines how the relationship with event structure works, wrapping up the paper
with comparison with related woks and hinting at further direction of research (Section~xxx).

\section{Preliminaries [to be redone]}

\begin{figure}[t]
   \input{Figure/basic_independence}
\caption{Sequential independence for
  $\rho = G \Rrel{p_1/m_1} H \Rrel{p_2/m_2} M$.}
\label{fi:strongseq}
\end{figure}

\begin{definition}[sequential independence]
  \label{de:seq-ind}
  Consider a derivation $G \Rrel{p_1/m_1} H \Rrel{p_2/m_2} M$ as in
  Fig.~\ref{fi:strongseq}. Then, its components are \emph{sequentially
    independent} if there exists a unique \emph{independence pair} among
  them, i.e., two graph morphisms $i_1: R_1 \rightarrow D_2$ and
  $i_2: L_2 \rightarrow D_1$ such that $l_2^* \circ i_1 = m_{R_1}$,
  $r_1^* \circ i_2 = m_{L_2}$.
\end{definition}

Observe that this notion reduces to the usual one for linear rules. In
fact when $r_1^*$ and $l_2^*$ are mono the uniqueness requirement is
trivially satisfied. Instead, for left-injective rules $i_1$ is still
unique, but $i_2$ might be not (as it happens, e.g., in the example
before).\todo{Say more about the example}

Observe that the notion is not symmetric: if
$\rho = G \Rrel{p_1/m_1} H \Rrel{p_2/m_2} M$ is sequential independent
and we switch it, we could obtain a pair which is not because it fails
to satisfy uniqueness of the independence pair (this happens, e.g., in
our example, where $\delta_2;\delta_3$ is sequential independent, but
$\delta_3';\delta_2'$ is not). The idea is to define shift equivalence
as $\rho \equiv_{sh} \rho'$ when \emph{each of the two} can be
obtained from the other by exchanging sequential independent
derivations. More precisely, we have a shift relation, which is used
for defining the equivalence as in Fig.~\ref{fi:ind}. It could be
better to have a slightly less elegant but more direct
definition. Write $\rho \shiftdir[\transp{i}] \rho'$ when
$\rho = \rho_1; \rho_2; \rho_3$ and $\rho' = \rho_1; \rho_2', \rho_3$
with $|\rho_1| = i-1$, $|\rho_2|=2$ and $\rho_2' \in
\IC{\rho_2}$. Then we write $\rho \shiftpre[\perm] \rho'$ if
$\rho = \rho_0 \shiftdir[\perm_1] \rho_1 \ldots \shiftdir[\perm_n ]
\rho'$ with $\perm = \perm_1; \ldots; \perm_n$ for some $n \geq 0$
(with the convention that for $n=0$ we get the identity).

The restricted notion of sequential independence ensures that the interchange operator produces a result that is unique up to abstraction equivalence.

\begin{lemma}[IC is unique]
  \label{le:unique-IC} 
  Let $\rho$ be a derivation such that $|\rho|=2$. If $\rho$ is
  sequential independent, let us write
  $\IC{\rho} = \{ \rho' \mid \rho \shiftdir \rho'\}$. Then for
  all $\rho', \rho'' \in \IC{\rho}$ we have $\rho' \equiv
  \rho''$. Moreover, if $\rho$ is sequential independent then for all
  $\rho' \in \IC{\rho}$, if $\rho'$ is sequential independent and
  $\rho'' \in \IC{\rho'}$, we have $\rho \equiv \rho''$.
\end{lemma}

\begin{figure}[t]
  \input{Figure/independence}
  \caption{Independence.}
  \label{fi:independence}
\end{figure}

It is convenient (at the beginning, at least) to work with shift
on derivations where the source and target graph is concrete and the
middle can be taken up to iso. I think that everything can be then
easily transferred to ctc-equivalence. We say that $\rho$ and $\rho'$
are abstract shift-equivalent and write $\rho \sim \rho'$.

A crucial observation is that independence can be defined also for non-contiguous steps.

\begin{definition}[independence]
  Let $\delta_1;\rho;\delta_n$ be a derivation as in
  Fig.~\ref{fi:independence}, where $\delta_1$ and $\delta_n$ are
  direct derivations and $\rho$ is a generic, possibly empty
  derivation. We say that $\delta_1$ and $\delta_n$ are independent if
  there is a unique independence pair $i_{n,1}$ and $i_{1,n}$
  satisfying the expected commutation, where $C$ is the colimit of the
  bottom line (excluding $G_1, G_{n+1}$).
\end{definition}

The fact that the notion of independence makes sense is proved by the following lemma, showing that the notion is preserved by the shift relation.

\begin{lemma}[independence is global]
  \label{le:seq-ind-glob1}
  The notion of independence for contiguous derivation steps
  coincides with sequential independence.

  Moreover, independence is invariant under the shift-relation, i.e.,
  \begin{itemize}

  \item if $\delta_1;\rho;\delta_2$ and $\rho \shiftpre \delta'$ then
    in $\delta_1;\rho;\delta_2$ the steps $\delta_1$, $\delta_2$ are
    independent iff they are in $\delta_1;\delta';\delta_2$.

  \item if $\delta_1;\rho;\delta';\delta_2$ and
    $\delta_2'; \delta'' \in \IC{\delta';\delta_2}$ then in
    $\delta_1;\rho;\delta';\delta_2$ the steps $\delta_1$ and $\delta_2$ are
    independent iff they are in $\delta_1;\rho;\delta_2'$.

  \item same as before, but with shift on the left.
  \end{itemize}
\end{lemma}

\begin{proof}
  To be done. The fact that sequential independence coincides with
  independence for contiguous derivations is easy. The fact that it coincides when derivations are not contiguous is false (the approach based on defining independence for non-contiguous derivation is not working, but the results should be true ...)
\end{proof}

A \emph{permutation} on $\interval{n}$ is a bijection
$\perm : \interval{n} \to \interval{n}$. We call it a
\emph{transposition} when there are $i, j \in \interval{n}$,
$i \neq j$ such that $\sigma(i)=j$, $\sigma(j) = i$ and
$\sigma(k) = k$ otherwise. Such a transposition is normally denoted as
$\transp{i}[j]$. Whenever $j = i+1$ we call it an \emph{adjacent
  transposition}.

Given a permutation $\perm$ on $\interval{n}$, the set of inversions
of $\perm$ is
$\inv{\perm} = \{ (i,j) \mid i,j \in \interval{n-1}\ \land\ i<j\
\land\ \perm(i) > \perm(j) \}$. Clearly, $\perm$ is the identity iff
$\inv{\perm}=0$.

Now, if $\perm \neq id$ there is at least an inversion of the kind
$(i,i+1)$.  Then we have that $\perm = \transp{i}; \perm'$
with $|\inv{\perm'}| = |\inv{\perm}| -1$. Hence we can inductively
express $\perm$ as a (minimal length) composition of adjacent
transpositions.

\begin{lemma}[on permutations]
  \label{le:perm}
  Let $\perm$, $\perm'$ be permutations on $\interval{n}$ and
  $\perm = \upsilon_1; \perm'; \upsilon_2$ where $\upsilon_1$ and $\upsilon_2$
  are transpositions with $\upsilon_1 = \transp{i}[j]$ and
  $\upsilon_2 = \transp{\perm'(i)}[\perm'(j)]$. Then $\sigma =
  \sigma'$.

  Moreover, let $\upsilon_1, \upsilon_2$ be adjacent
  transpositions and $\sigma' = \upsilon_1; \ldots, \upsilon_m$ a
  minimal length decomposition of $\sigma'$ in terms of adjacent
  transpositions (that thus operate on inversions). Then, for all
  $h \in \interval{m}$ with $\upsilon_h = \transp{l}[l+1]$ there exists
  $k \in \interval{m}$ such that
  $\upsilon_k = \transp{\upsilon_{1,h-1}^{-1};v_1;
    \upsilon_{1,k-1}(l)}[\upsilon_{1,h-1}^{-1};v_1; \upsilon_{1,k-1}(l+1)]$.
\end{lemma}

\begin{proof}
  The first part is easy. The second is a consequence of the fact that
  the minimal decomposition in terms of adjacent transpositions is
  essentially unique, in the sense that it consists of exchanges of
  all the inversions. To be formalised.
\end{proof}

In words, the lemma above says that if a permutation is decomposed as $\sigma = \upsilon_1; \sigma'; \upsilon_2$ with $\sigma' = \upsilon_1'; \ldots, \upsilon_n'$, where $\upsilon_1$ and $\upsilon_2$ performs a switch and its reverse, and the inner decomposition is minimal, then we can strip the first and last switch and get a decomposition of the same permutation that performs the same switches but possibly in a different order.

\begin{lemma}[no need of useless shifts]
  \label{le:no-useless-shifts}
  Let $\rho$, $\rho'$ be direct derivations and assume
  $\rho \shiftpre[\sigma] \rho'$. Then
  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots \shiftdir[\upsilon_n ]
  \rho'$ where $\sigma = \upsilon_1; \ldots; \upsilon_n$ and $\upsilon_j \in \inv{\upsilon_{j,n}}$ for $j \in \{1, \ldots,n\}$.
\end{lemma}

\begin{proof}
  Let $\rho \shiftpre[\perm] \rho'$. This means that
  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots \shiftdir[\upsilon_n ]
  \rho'$ with $\perm = \upsilon_1; \ldots; \upsilon_n$ for some $n \geq 0$.

  We show that if some $\upsilon_j$ does not act on an inversion, i.e.,
  $\upsilon_j \not\in \inv{\sigma_{j,n}}$ then we can shorten the
  proof of $\rho \shiftpre[\sigma] \rho'$ of two steps. This will
  allow us to conclude that we can reduce it to a proof only acting
  on inversions, as desired.

  The key observation is that, if
  $\upsilon_j \not\in \inv{\sigma_{j,n}}$ then, intuitively, the ``same
  exchange'' must be performed in the reverse direction by some
  $\upsilon_h$ ($h>j$).  Formally, if $\upsilon_j = \transp{i}$ and
  $(i,i+1)\not\in\inv{\upsilon_{i,n}}$ then there exists $h>j$ such that
  $\upsilon_{j,h-1}(i) = \upsilon_{j,h-1}(i+1)+1$ and
  $\upsilon_h = \transp{\upsilon_{j,h-1}(i+1)}$. Among all the pairs
  $j, h$ of this kind, take one with minimal $h-i$. This means that in
  the middle all transpositions are inversions of $\upsilon_{i+1,h-1}$.

  By Lemma~\ref{le:perm}, $\upsilon_i$ and $\upsilon_h$ can be
  stripped, i.e., $\upsilon_{i,h} = \upsilon_{i+1,h-1}$. Moreover,
  again by Lemma~\ref{le:perm},
  $\upsilon_{i+1}, \ldots, \upsilon_{h-1}$ perform exchanges that were
  already done in the original proof, and thus, since independence is
  invariant under shift equivalence, as expressed by
  Lemma~\ref{le:seq-ind-glob1} they are allowed. Moreover, since by
  Lemma~\ref{le:unique-IC} the result of switching is uniquely
  determined (up to iso), the resulting derivation is the same as
  before, hence we can strip $\upsilon_{i}$ and $\upsilon_{h}$,
  and conclude.
\end{proof}

Then we can prove that whenever $\rho \shiftpre[\perm] \rho'$, each
decomposition of $\perm$ in terms of inversions leads to a valid
derivation of $\rho'$ from $\rho$.

\begin{lemma}[independence is global/2]
  \label{le:seq-ind-glob2}
  Let $\rho$, $\rho'$ be direct derivations. Let
  $\rho \shiftpre[\perm] \rho'$, with $\perm \neq id$ and let
  $\perm = \transp{i}; \perm'$ where $(i,i+1) \in \inv{\perm}$. Then
  there exists $\rho''$ such that
  $\rho \shiftpre[\transp{i}] \rho'' \shiftpre[\perm']
  \rho'$.
\end{lemma}

\begin{proof}
  Let
  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots
  \shiftdir[\upsilon_n] \rho'$ where $\sigma = \upsilon_1; \ldots; \upsilon_n$ and $\upsilon_j \in \inv{\upsilon_{j,n}}$ for $j \in \{1, \ldots,n\}$, be the decomposition
  provided by Lemma~\ref{le:no-useless-shifts}.

  We know that steps corresponding to $i$ and $i+1$ are exchanged at
  some point, namely there is $j$ such that
  $\upsilon_j =
  \transp{\upsilon_{1,j-1}(i)}[\upsilon_{1,j-1}(i+1)]$. By
  Lemma~\ref{le:seq-ind-glob1} the steps $i$ and $i+1$ are independent
  already at the beginning and thus we can exchange them first.
  More precisely, 
  \begin{center}
    $\rho \shiftdir_{\transp{i}} \rho'' \shiftdir_{\upsilon_{1,j-1}}
    \rho_j \shiftdir_{\upsilon_{j+1,n}} \rho'$.
  \end{center}
  This can be proved by induction on $j$.
\end{proof}

\begin{lemma}[more on shift]
  \label{le:more-shift}
  if $\rho_1;\rho_1' \shiftpre[\perm | \perm'] \rho_2; \rho_2'$,
  with $|\rho_1| = |\rho_2|$ and
  $\sigma : \interval{|\rho_1|-1]} \to \interval{|\rho_2|-1]}$ then
  $\rho_1 \shiftpre[\perm] \rho_2$ and
  $\rho_1' \shiftpre[\perm'] \rho_2'$.
\end{lemma}

\begin{proof}
  The results follows by the fact that, from
  Lemma~\ref{le:no-useless-shifts}, we derive that
  \begin{center} 
    $\rho_1;\rho_1' \shiftdir[ \upsilon_1 \mid id_{[1..|\rho_1'|]}]
    \ldots \shiftdir[ \upsilon_h \mid id_{[1..|\rho_1'|]}] \rho_2;
    \rho_1' \shiftdir[ id_{[1..|\rho_1|]} \mid \upsilon_1'] \ldots
    \shiftdir[ id_{[1..|\rho_1|]} \mid \upsilon_k'] \rho_2; \rho_2'$
  \end{center}
  where $\upsilon_1; \ldots; \upsilon_h$ is a decomposition of $\perm$
  in terms of inversions and, similarly,
  $\upsilon_1'; \ldots; \upsilon_k'$ is a decomposition of
  $\perm'$. Then
  $\rho_1 \shiftdir[\upsilon_1] \ldots \shiftdir[\upsilon_h] \rho_2$
  and analogously
  $\rho_1' \shiftdir[\upsilon_1'] \ldots \shiftdir[\upsilon_k']
  \rho_2'$, which leads to the desired conclusion.
\end{proof}

\todo[inline]{Note that above we assume that $\rho_1$ and $\rho_1'$ ends in the same graph. To be formalised.}

\begin{lemma}[uniqueness of permutation]
  if $\rho \shiftpre[\perm_1] \rho'$ and
  $\rho \shiftpre[\perm_2] \rho'$ then $\perm_1 = \perm_2$. In
  particular, if $\rho_1 \shiftpre[\perm_1] \rho_1$ then $\perm_1 = id$.
\end{lemma}

\begin{proof}
  We proceed by induction on the length of the derivations
  $\ell=|\rho|=|\rho'|$ and by an inner induction on the number of
  inversions in $\sigma_1$. When $\ell = 0$, the result is
  trivial. Let us assume $\ell>0$ and let $i_1 = \sigma_1^{-1}(1)$,
  $i_2 = \sigma_2^{-1}(1)$. Let
  $L_1' \stackrel{l_1'}{\leftarrow} K_1' \stackrel{r_1'}{\rightarrow}
  R_1')$ be the rule used by the first production in $\rho'$.
  By Lemma 17(1) in the paper [the implication
  that holds] $\sigma_1$ and $\sigma_2$ are consistent permutations of
  $\rho$ into $\rho'$.
  %
  Since they are consuming, it is easy to see that
  $i_1=\sigma_1^{-1}(1)$ is uniquely determined by the (equivalence
  class) of an item in the initial graph consumed by $L_1'$ and the
  same applies to $i_2=\sigma_2^{-1}(1)$, hence we conclude that
  $i_1=i_2$.

  Now, if $i_1=i_2=1$, then $\sigma_j = \transp{1}[1] \mid \sigma_j'$
  for $j \in \{1,2\}$ and $\rho = \delta; \rho_1$,
  $\rho' = \delta; \rho_1'$ where $\delta$ is the first direct
  derivation, and $\rho_1 \shiftpre[\perm_j'] \rho_1'$ for
  $j \in \{1,2\}$. Since $|\rho_1| = \ell-1$ we conclude by inductive
  hypothesis that $\sigma_1'=\sigma_2'$ and thus $\sigma_1=\sigma_2$,
  as desired.

  If instead $i_1=i_2=i>1$, since $\transp{i_1-1}[i_1]$ is an inversion for both
   $\sigma_1$ and $\sigma_2$, by Lemma~\ref{le:seq-ind-glob2} we can
  perform such a shift first, obtaining
  \begin{center}
    $\rho \shiftdir[{\transp{i-1}[i]}] \rho_1
    \shiftpre[{\transp{i-1}[i];\sigma_1}] \rho'$
    %
    \quad and \quad
    %
    $\rho \shiftdir[{\transp{i-1}[i]}] \rho_1
    \shiftpre[{\transp{i-1}[i];\sigma_2}] \rho'$
  \end{center}
  Since ${\transp{i-1}[i];\sigma_1}$ has an inversion less than
  $\sigma_1$ we conclude by inductive hypothesis that
  ${\transp{i-1}[i];\sigma_1} ={\transp{i-1}[i];\sigma_2}$, whence
  $\sigma_1=\sigma_2$.
\end{proof}

Note that the above works also with the liberal definition of
sequential independence.

\begin{lemma}[Lemma 17(2) in the paper]
  if $\rho;\rho_1 \shiftpre[\perm] \rho; \rho_2$ then
  $\perm = id_{[1..|\rho|]} \mid \perm'$ and
  $\rho_1 \shiftpre[\perm'] \rho_2$.
\end{lemma}

\begin{proof}[skecth]
  Productions are `uniquely identified by the items they consume,
  hence productions in $\rho$ are necessarily mapped to themselves,
  i.e., $\perm = id_{[1..|\rho|]} \mid \perm'$. Then we conclude
  $\rho_1 \shiftpre[\perm'] \rho_2$ by Lemma~\ref{le:more-shift}.
\end{proof}

\begin{lemma}[Lemma 20 in the paper]
  \label{le:prop-c}
  Let $\psi$ and $\psi'$ be decorated derivations. Then the following hold:
  \begin{enumerate}
  \item
    \label{le:prop-c:1}
    Let $\psi_1, \psi_1'$ be such
    that $\psi;\psi_1 \equiv^c_{\perm} \psi';\psi_1'$ and let
    $n = | \{ j \in \interval[|\psi|]{|\psi;\psi_1|-1} \mid \perm(j)
    < |\psi'| \}|$. Then for all $\phi_2, \phi_2'$ such that
    $\psi;\phi_2 \equiv^c \psi';\phi_2'$ it holds $|\phi_2| \geq n$
    and there are $\psi_2, \psi_2',\psi_3$ such that

    \begin{itemize}
    \item $\psi;\psi_1 \equiv^c \psi;\psi_2;\psi_3$
    \item $\psi;\psi_2 \equiv^c \psi';\psi_2'$

    \item $|\psi_2| = n$

    \end{itemize}

  \item
    \label{le:prop-c:2}
    Let $\psi_1, \psi_1'$, $\psi_2, \psi_2'$ be such that
    $\psi;\psi_1 \equiv^c_{\perm_1} \psi';\psi_1'$ and
    $\psi;\psi_2 \equiv^c_{\perm_2} \psi';\psi_2'$ with $\psi_1, \psi_2$
    of minimal length. Then $\psi_1 \equiv^c_\perm \psi_2 \cdot \nu$,
    where $\nu : \target{\psi_2} \to \target{\psi_2}$ is some graph isomorphism and
    $\perm(j) = \perm_2^{-1}(\perm_1(j + |\psi|))-|\psi|$ for
    $j \in \interval[0]{|\psi_1|-1}$.    
  \end{enumerate}
\end{lemma}

\begin{proof}[sketch]  
  Point ~\ref{le:prop-c:1}: The proof should be similar to the one we have already, basing the rearrangement on Lemma~\ref{le:seq-ind-glob2}. Roughly we get $\psi;\psi_1 \equiv^c \psi_a;\psi_b;\psi_{2};\psi_{3}$ and
  $\psi';\psi_1' \equiv^c \psi_a';\psi_b';\psi_{2}';\psi_{3}'$
  with
  \begin{center}
    $\psi_a;\psi_b;\psi_{2};\psi_{3}
    \equiv^c_{\perm_a|\perm_{b2}|\perm_2}
    \psi_a';\psi_b';\psi_{2}';\psi_{3}'$
  \end{center}
  with $\perm_a$ over $\interval{|\psi_a|-1}$, $\perm_{b2}$ over
  $\interval{|\psi_b;\psi_{2}|-1}$ ``mapping $\psi_b$ to $\psi_{2}'$
  and $\psi_b'$ to $\psi_{2}$'', $\perm_3$ over
  $\interval{|\psi_2|-1}$.  We deduce by Lemma~\ref{le:more-shift}
  that $\psi_a \equiv^c_{\perm_a} \psi_a'$,
  $\psi_b;\psi_{2} \equiv^c_{\perm_{b2}} \psi_b';\psi_{2}'$ and
  $\psi_{3} \equiv^c_{\perm_3} \psi_{3}'$.

  Now, for all $\phi_2, \phi_2'$ such that
  $\psi;\phi_2 \equiv^c \psi';\phi_2'$ we can perform the same
  splitting and this leads to the conclusion that $|\phi| \geq n$ and
  also it can be expressed as $\psi_2;\phi_2'$, that should subsume
  also the second point.
  %
\qed
\end{proof}

% \paragraph{Note.} This does not solve the problem raised by Andrea's counterexample that still applies.

Another idea could be to try to use the inductive characterisation in Figure~\ref{fi:ind} (but I do not see how to mange the transitive rule).

\begin{figure}
  \begin{center}
    \small
  \[
    \inferL{\slab{(SH-id)}}
    {\rho \shiftpre[id] \rho}
    {}
    % 
    \hspace{0.9cm}
    % 
    \inferL{\slab{(SH-exch)}}
    {\rho \shiftpre[{\transp{1}[2]}] \rho'}
    {\rho = \upsilon_1;\upsilon_2 & \rho' \in \IC{\rho}}
  \]

  \[
    \inferL{\slab{(SH-comp)}}
    {\rho_1 ; \rho_2  \shiftpre[\upsilon_1 \mid \upsilon_2] \rho'_1 ;
      \rho'_2}
    {\rho_1 \shiftpre[\upsilon_1] \rho'_1, \ \rho_2 \shiftpre[\upsilon_2] 
      \rho'_2,\ \tau(\rho_1) = \perm(\rho_2)}
  \]

  \[
    % 
    % \inferL{\slab{(SH-sym)}}
    % {\rho' \shiftpre[\perm^{-1}] \rho}
    % {\rho \shiftpre[\perm] \rho'}
    % % 
    % \hspace{0.3cm}
    % 
    \inferL{\slab{(SH-tr)}}
    {\rho \shiftpre[\perm'\circ \perm] \rho''}
    {\rho \shiftpre[\perm] \rho',\ \rho' \shiftpre[\perm'], \rho''}
    %
    \hspace{0.3cm}
    \inferL{\slab{(SH-eq)}}
    {\rho' \shifteq[\perm] \rho}
    {\rho \shiftpre[\perm] \rho' & \rho' \shiftpre[\perm^{-1}] \rho}
  \]

%  \noindent
%  for $\perm_1 \mid \perm_2$ the pairing of two permutations,
%  and similarly $\sqsubseteq^c_{\perm}$ is defined inductively by

  \[
    \inferL{\slab{(C-abs)}}
    {\psi \equiv^c_{id} \psi'} 
    {\psi \equiv^{a} \psi'} 
    % 
    \hspace{0.3cm}
    % 
    \inferL{\slab{(C-sh)}}
    {\langle \alpha, \rho, \omega \rangle \equiv^c_{\perm} \langle \alpha, \rho', \omega \rangle} 
    {\rho \shifteq[\perm] \rho'}
    % 
    \hspace{0.3cm}
    % 
    \inferL{\slab{(C-tr)}}
    {\psi \equiv^c_{\perm' \circ \perm} \psi''}
    {
      {\psi \equiv^c_{\perm} \psi'} & 
      {\psi' \equiv^c_{\perm'} \psi''}
    }
  \]
\end{center}
\caption{Inductive definition of $\shiftpre$ and $\equiv^c$, for $\perm_1 \mid \perm_2$ the pairing of two permutations.}
\label{fi:ind}
\end{figure}

% \paragraph{Consistent $5$-tuple}. The alternative is to try to amend the notion of consistent $5$-tuple by adding some dependencies between productions and asking that they are ``preserved'' by the mapping. With the new definition I fear that it could be difficult distinguishing between dependencies arising from fusions and other, hence one should try to capture all dependencies, that will concretise in a deterministic event structure. Concretely, given $\rho = p_1 p_2 \ldots p_n$ it could be mapped to $E(\rho) = \langle \{ 1, \ldots, n\}, \vdash\rangle$ where $X \vdash i$ if there exists $\rho \equiv_\perm \rho'$ such that for all $j \in X$ it holds $j < \perm(i)$.

\section{Proving invariance of independence with respect to shift}
\newcommand{\si}{\ensuremath{\mathrel{\langle \mbox{\textsc{si}}\rangle}}}

This is the way I (AC) propose to organize the proof that sequential independence is invariant with respect to shift. I copy and update some results of the previous part. Not everything is formalized completely.

The structure of the proof should be applicable to any notion of \emph{sequential independence} for which we can prove the following facts:

\begin{definition}[conditions on sequential independence]
\label{def:si-conditions}
\begin{enumerate}
\item \label{cond:CR} Sequential independent steps can be switched. If two consecutive steps $\delta_i$ and $\delta_{i+1}$ of a derivation $\rho$ are SI (sequential independent, written $\delta_i \si \delta_{i+1}$), then there is a constructive way to obtain a derivation $\rho'$ differing from $\rho$ only for steps $\delta'_i$ and $\delta'_{i+1}$, such that $rule(\delta_i) = rule(\delta'_{i+1})$ and $rule(\delta_{i+1}) = rule(\delta'_{i})$. In this case we write $\rho \shiftdir[i] \rho'$.

\item  \label{cond:CRdet} Switching is deterministic up to iso. If $\delta_i \si \delta_{i+1}$ in $\rho$ and $\rho \shiftdir[i] \rho'$, $\rho \shiftdir[i] \rho''$, then $\rho' \equiv \rho''$.

\item \label{cond:si-symm} Sequential independence is preserved by immediate switch. If $\delta_i \si \delta_{i+1}$ in $\rho$ and $\rho \shiftdir[i] \rho'$, then $\delta'_i \si \delta'_{i+1}$ in $\rho'$.

\item  \label{cond:si-si-iso} Switch is reversible. If $\rho \shiftdir[i] \rho'$ then $\rho' \shiftdir[i] \rho$.

\item As a consequence of the previous points, if $\rho \shiftdir[i] \rho'$ and $\rho' \shiftdir[i] \rho''$ then $\rho \equiv \rho''$.

\end{enumerate}
\end{definition}
%Given a derivation $\rho = \delta_1; \ldots ; \delta_i ; \delta_{i+1}; \ldots; \delta_n$, if $\delta_i \si \delta_{i+1}$, then
\todo[inline]{I think that all conditions are satisfied by the standard definition of SI in DPO with linear rules and by our stronger notion of SI (uniqueness of the two mediating morphism \textbf{and} same property of the switched steps) in DPO with possibly non-right-linear rules. }

\begin{proposition}[$\si$ satisfies all the conditions...]
Let's call the relation of Def.~\ref{de:seq-ind} \emph{weak sequential independence}. Then it satisfies conditions \ref{cond:CR} and \ref{cond:CRdet} of Definition~\ref{def:si-conditions} (by the classical Church-Rosser Theorem and uniqueness of the mediating morphisms), but not the remaining ones.

Let \emph{sequential independence} be defined as follows: $\delta_i \si \delta_{i+1}$ in $\rho$ iff they are weak sequential independent, and if $\rho'$ is obtained by $\rho$ switching  $\delta_i$ and $\delta_{i+1}$ (which is possible by condition \ref{cond:CR} and deterministic up to iso by condition \ref{cond:CRdet}) then $\delta'_i$ and $\delta'_{i+1}$ are weak sequential independent in $\rho'$.

 Then $\si$ satisfies all the conditions of Definition~\ref{def:si-conditions}.
 \end{proposition}

\begin{proof}
Conditions  \ref{cond:CR} and \ref{cond:CRdet} already hold for weak sequential independence. Condition \ref{cond:si-symm} holds by definition. \textbf{Condition \ref{cond:si-si-iso} should be proved explicitly, I fear...}
\end{proof}

\begin{definition}[Invariance under shift]
\label{def:invariance} 
A binary relation $R$ on consecutive steps of derivations is \emph{invariant under shift equivalence up to $n$} if whenever  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots \shiftdir[\upsilon_k] \rho'$ with  $\perm = \upsilon_1; \ldots; \upsilon_k$ and $k \leq n$ (thus $\rho \shifteq[\perm] \rho'$ with a proof made of at most  $n$ switches of steps) and $\perm(i+1) = \perm(i) + 1$, then $\delta_i \mathrel{R} \delta_{i+1}$ in $\rho$ if and only if $\delta'_{\perm(i)} \mathrel{R} \delta'_{\perm(i+1)}$ in $\rho'$. Relation $R$  is \emph{invariant under shift equivalence}, tout-court, if it is so up to any $n$.

In words, two consecutive steps are related by $R$ in a derivation iff they are related by $R$ in any shift-equivalent derivation in which they are again consecutive.

%$\delta_i \mathrel{R} \delta_{i+1}$ in $\rho$, $\rho \shifteq[\perm] \rho'$, and $\perm(i+1) = \perm(i) + 1$, then $\delta'_{\perm(i)} \mathrel{R} \delta'_{\perm(i+1)}$ in $\rho'$.

\end{definition}

\todo[inline]{The following is Lemma~\ref{le:no-useless-shifts} with a bound $n$ on the length of the proof that two derivations are shift equivalent. Also, it uses as assumption the fact that \si is invariant w.r.t.~shift up to $n-1$: the fact that $n-1$ is sufficient is exploited later in the proof of the main result. I think that it works, because the assumption is used only at the end, when the two reverse transpositions were already stripped, thus the length is $n-2$.}
\begin{lemma}[no need of useless shifts]
  \label{le:no-useless-shifts-bounded}
  Given an integer $n$, let us assume that $\si$ is invariant under shift up to $n-1$.  Let $\rho$, $\rho'$ be direct derivations such that  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots \shiftdir[\upsilon_k] \rho'$ with $k \leq n$, and 
  let $\sigma = \upsilon_1; \ldots; \upsilon_k$.
   Then
  $\rho = \rho_0 \shiftdir[\upsilon'_1] \rho_1 \ldots \shiftdir[\upsilon'_h ]
  \rho'$ where $\sigma = \upsilon'_1; \ldots; \upsilon'_h$, $h \leq k$ and $\upsilon'_j \in \inv{\upsilon'_{j,h}}$ for $j \in \{1, \ldots,h\}$. 
  %\todo{I understand that $\upsilon'_{j,h} = \upsilon'_j; \ldots; \upsilon'_h$}
\end{lemma}

\begin{proof}
  Let 
  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots \shiftdir[\upsilon_k ]
  \rho'$.
  %
  We show that if some $\upsilon_j$ does not act on an inversion, i.e.,
  $\upsilon_j \not\in \inv{\upsilon_{j,k}}$ then we can shorten the
  proof of $\rho \shifteq[\sigma] \rho'$ of two steps. This 
  allow us to conclude that we can reduce the original proof to one which is not longer and only acting
  on inversions, as desired.

  The key observation is that, if
  $\upsilon_j \not\in \inv{\sigma_{j,k}}$ then, intuitively, the ``same
  exchange'' must be performed in the reverse direction by some
  $\upsilon_s$, with $s>j$.  Formally, if $\upsilon_j = \transp{i}$ and
  $(i,i+1)\not\in\inv{\upsilon_{i,k}}$ then there exists $s>j$ such that
  $\upsilon_{j,s-1}(i) = \upsilon_{j,s-1}(i+1)+1$ and
  $\upsilon_s = \transp{\upsilon_{j,s-1}(i+1)}$. Among all the pairs
  $j, s$ of this kind, take one with minimal $s-j$. This means that in
  the middle all transpositions are inversions of $\upsilon_{j+1,s-1}$.

  By Lemma~\ref{le:perm}, $\upsilon_j$ and $\upsilon_s$ can be
  stripped, i.e., $\upsilon_{j,s} = \upsilon_{j+1,s-1}$. Moreover,
  again by Lemma~\ref{le:perm},
  $\upsilon_{i+1}, \ldots, \upsilon_{s-1}$ perform exchanges that were
  already done in the original proof, and thus, since independence is
  invariant under shift equivalence up to $n-1$, they are allowed. 
  Moreover, since by condition \ref{cond:CRdet} of Definition~\ref{def:si-conditions} the result of switching is uniquely
  determined (up to iso), the resulting derivation is the same as
  before, hence we can strip $\upsilon_{j}$ and $\upsilon_{s}$,
  and conclude.
\end{proof}

\todo[inline]{The next one is Lemma~\ref{le:seq-ind-glob2}, again bounded w.r.t.~ the length of the proof of shift equivalence. \textbf{Note:} It is not used in the following.}

Then we can prove that whenever $\rho \shifteq[\perm] \rho'$, each
decomposition of $\perm$ in terms of inversions leads to a valid
valid proof of the shift equivalence  of $\rho$ and $\rho$.

\begin{lemma}[independence is global/2]
  \label{le:seq-ind-glob2-new}
 Given an integer $n$, let us assume that $\si$ is invariant under shift up to $n$.  Let $\rho$, $\rho'$ be direct derivations such that $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots
  \shiftdir[\upsilon_k] \rho'$, with $0 < k \leq n$,  
   $\sigma = \upsilon_1; \ldots; \upsilon_k$  and  $\upsilon_j \in \inv{\upsilon_{j,k}}$ for $j \in \{1, \ldots,k\}$. 
  Let
  $\perm = \transp{i}; \perm'$ where $(i,i+1) \in \inv{\perm}$. Then
  there exists $\rho''$ such that
  $\rho \shifteq[\transp{i}] \rho'' \shifteq[\perm']
  \rho'$.
\end{lemma}

\begin{proof}
%  Let
%  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots
%  \shiftdir[\upsilon_n] \rho'$ where $\sigma = \upsilon_1; \ldots; \upsilon_n$ and $\upsilon_j \in \inv{\upsilon_{j,n}}$ for $j \in \{1, \ldots,n\}$, be the decomposition
%  provided by Lemma~\ref{le:no-useless-shifts}.
 % 
  We know that steps corresponding to $i$ and $i+1$ are exchanged at
  some point, namely there is $j$ such that
  $\upsilon_j =
  \transp{\upsilon_{1,j-1}(i)}[\upsilon_{1,j-1}(i+1)]$. Since $\si$ is invariant up to $n$, the steps $i$ and $i+1$ are independent
  already at the beginning and thus we can exchange them first.
  More precisely, 
  \begin{center}
    $\rho \shiftdir_{\transp{i}} \rho'' \shiftdir_{\upsilon_{1,j-1}}
    \rho_j \shiftdir_{\upsilon_{j+1,k}} \rho'$.
  \end{center}
  This can be proved by induction on $j$.
\end{proof}

The following main lemma needs a proof.

\begin{lemma}[Invariance of $\si$ under immediate shift]
\label{le:invariance-immediate}
\begin{enumerate}
%\item Let $\rho = \delta_1 ; \delta_2 ; \delta_3 $ with $\delta_2 \si \delta_3$, suppose that $\rho \shiftdir[(2,3)] \rho' = \delta_1 ; \delta'_3 ; \delta'_2$,  that $\delta_1 \si \delta'_3$ in $\rho'$, and that $\rho' \shiftdir[(1,2)] \rho'' =  \delta''_3 ; \delta'_1 ; \delta'_2$. 
%Then $\delta_1 \si \delta_2$ in $\rho$ if and only if  $\delta'_1 \si \delta'_2$ in $\rho''$.

\item Let $\rho = \delta_1 ; \delta_2 ; \delta_3 $ be a derivation such that $\rho \shiftdir[(2,3)] \rho'  \shiftdir[(1,2)] \rho''$,  with $\delta_2 \si \delta_3$ in $\rho$, $\rho' = \delta_1 ; \delta'_3 ; \delta'_2$,   $\delta_1 \si \delta'_3$ in $\rho'$, and that $\rho'' =  \delta''_3 ; \delta'_1 ; \delta'_2$. 
Then $\delta_1 \si \delta_2$ in $\rho$ if and only if  $\delta'_1 \si \delta'_2$ in $\rho''$.

The situation can be represented as in the following diagram, where each transposition is performed, downwards, only if the two starting steps are sequential independent. The proposition states that the steps \cycl{1} are sequential independent if and only if so are the steps \cycl{2}. For brevity, we abbreviate this statement to $SI(\cycl{1}) \iff SI(\cycl{2})$.

%\center{\xymatrix@C=2pc@R=1pc{
% \rho  \ar@{~>}[d]^{sh}_{(2,3)}  \ar@{}[r]|{=} & \rho_1 \ar@{-}[d] \ar@{}[r]|{;} & \delta_1 \ar@{-}[d]  \ar@{}[r]|{;} & \delta_2 \ar@{-}[dr]  \ar@{}[r]|{;} & \delta_3 \ar@{-}[dl]  \ar@{}[r]|{;} &\rho_2 \ar@{-}[d] \\
%\rho'  \ar@{~>}[d]^{sh}_{(1,2)}  \ar@{}[r]|{=} &  \rho_1 \ar@{-}[d]  \ar@{}[r]|{;} & \delta_1 \ar@{-}[dr]  \ar@{}[r]|{;} & \delta'_3 \ar@{-}[dl]  \ar@{}[r]|{;} & \delta'_2 \ar@{-}[d]  \ar@{}[r]|{;} &\rho_2 \ar@{-}[d] \\
%\rho''  \ar@{}[r]|{=} &   \rho_1 \ar@{}[r]|{;} & \delta''_3 \ar@{}[r]|{;} & \delta'_1 \ar@{}[r]|{;} & \delta'_2 \ar@{}[r]|{;} &\rho_2\\
%}}

$$\xymatrix@C=2pc@R=1pc{
 \rho  \ar@{~>}[d]^{sh}_{(2,3)}  \ar@{}[r]|{=} &  \delta_1 \ar@{-}[d]  \ar@{}[r]|{;}  \ar@{-}@/^3ex/[r]|{\cycl{1}} & \delta_2 \ar@{-}[dr]  \ar@{}[r]|{;} & \delta_3 \ar@{-}[dl] \\
\rho'  \ar@{~>}[d]^{sh}_{(1,2)}  \ar@{}[r]|{=} &   \delta_1 \ar@{-}[dr]  \ar@{}[r]|{;} & \delta'_3 \ar@{-}[dl]  \ar@{}[r]|{;} & \delta'_2 \ar@{-}[d]\\
\rho''  \ar@{}[r]|{=} &    \delta''_3 \ar@{}[r]|{;} & \delta'_1 \ar@{-}@/_3ex/[r]|{\cycl{2}} \ar@{}[r]|{;} & \delta'_2  \\
}$$

\item  Also a symmetric statement holds, for which we show only the graphical representation. Again, we show that $SI(\cycl{1}) \iff SI(\cycl{2})$.
% the steps \cycl{1} are sequential independent if and only if so are the steps \cycl{2}.

$$\xymatrix@C=2pc@R=1pc{
 \rho  \ar@{~>}[d]^{sh}_{(1,2)}  \ar@{}[r]|{=} &
   \delta_1 \ar@{-}[dr]  \ar@{}[r]|{;}  &
    \delta_2 \ar@{-}[dl]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
    \delta_3 \ar@{-}[d] \\
\rho'  \ar@{~>}[d]^{sh}_{(2,3)}  \ar@{}[r]|{=} &
   \delta'_2 \ar@{-}[d]  \ar@{}[r]|{;} &
    \delta'_1 \ar@{-}[dr]  \ar@{}[r]|{;} &
     \delta_3 \ar@{-}[dl]\\
\rho''  \ar@{}[r]|{=} & 
   \delta'_2 \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
    \delta'_3  \ar@{}[r]|{;} &
     \delta''_1  \\
}$$

%
%Symmetrically, let $\rho = \rho_1 ; \delta_1 ; \delta_2 ; \delta_3 ; \rho_2$ with $\delta_1 \si \delta_2$ in $\rho$, suppose that $\rho \shiftdir[(1,2)] \rho' = \rho_1 ; \delta'_2 ; \delta'_1 ; \delta_3 ;\rho_2$,  that $\delta'_1 \si \delta_3$ in $\rho'$, and that $\rho' \shiftdir[(2,3)] \rho'' = \rho_1 ; \delta'_2 ; \delta'_3 ; \delta''_1 ;\rho_2$. 
%Then $\delta_2 \si \delta_3$ in $\rho$ if and only if  $\delta'_2 \si \delta'_3$ in $\rho''$. 
\end{enumerate}
%\begin{enumerate}
%\item Let $\rho = \rho_1 ; \delta_1 ; \delta_2 ; \delta_3 ; \rho_2$ with $\delta_2 \si \delta_3$ in $\rho$, suppose that $\rho \shiftdir[(2,3)] \rho' = \rho_1 ; \delta_1 ; \delta'_3 ; \delta'_2 ;\rho_2$,  that $\delta_1 \si \delta'_3$ in $\rho'$, and that $\rho' \shiftdir[(1,2)] \rho'' = \rho_1 ; \delta''_3 ; \delta'_1 ; \delta'_2 ;\rho_2$. 
%Then $\delta_1 \si \delta_2$ in $\rho$ if and only if  $\delta'_1 \si \delta'_2$ in $\rho''$. 
%
%The following A graphical representation The situation can 
%\item  Symmetrically, let $\rho = \rho_1 ; \delta_1 ; \delta_2 ; \delta_3 ; \rho_2$ with $\delta_1 \si \delta_2$ in $\rho$, suppose that $\rho \shiftdir[(1,2)] \rho' = \rho_1 ; \delta'_2 ; \delta'_1 ; \delta_3 ;\rho_2$,  that $\delta'_1 \si \delta_3$ in $\rho'$, and that $\rho' \shiftdir[(2,3)] \rho'' = \rho_1 ; \delta'_2 ; \delta'_3 ; \delta''_1 ;\rho_2$. 
%Then $\delta_2 \si \delta_3$ in $\rho$ if and only if  $\delta'_2 \si \delta'_3$ in $\rho''$. 
%\end{enumerate}
\end{lemma}
\begin{proof}
\textbf{To be done...}

\end{proof}

We are now able to state and prove the main result.

\begin{theorem}[Invariance of $\si$]
Relation $\si$ is invariant under shift equivalence, as for Definition~\ref{def:invariance}.
\end{theorem}

\begin{proof}
Let $\rho \shifteq[\perm] \rho'$ be two shift equivalent derivations and let $1 \leq i <  |\rho|$ such that $\perm(i+1) = \perm(i) + 1$. We have to show that $\delta_i \si \delta_{i+1}$ in $\rho$  iff  $\delta_{\perm(i)} \si \delta_{\perm(i+1)}$ in $\rho'$.

Since $\rho \shifteq[\perm] \rho'$, we have $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots \shiftdir[\upsilon_n] \rho'$, with $\sigma = \upsilon_1; \ldots; \upsilon_n$. We proceed by induction on $n$. If $n = 0$, then $\perm = id$ and the statement trivially holds. Now we assume that the statement holds for each $k \leq n$, and  we show that it holds for $n+1$. Let  $\sigma'$ be defined as $\sigma' =  \upsilon_1; \ldots; \upsilon_n$, thus  $\sigma = \sigma' ; \upsilon_{n+1}$.  We proceed by case analysis on the last adjacent transposition $\upsilon_{n+1} = (z, z+1)$.

\begin{description} 
\item [{[$z+1 < \sigma'(i)$ or $\sigma'(i+1) < z$]}] In this case the last transposition does not affect the steps $\delta^n_{\sigma'(i)}$ and $\delta^n_{\sigma'(i+1)}$  of $\rho_n$, as depicted here:

$$\xymatrix@C=2pc@R=2pc{
 \rho  \ar@{~>}[d]^{sh}^(.9){*} \ar@{}[r]|{=} &
   \cdots   \ar@{}[r]|{;}  &
    \delta_i \ar@{--}@/_2ex/[d]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
    \delta_{i+1} \ar@{--}@/^1ex/[d]  \ar@{}[r]|{;}  & \cdots\\
\rho_n  \ar@{~>}[d]^{sh}_{\upsilon_{n+1}}  \ar@{}[r]|{=} &
   \cdots   \ar@{}[r]|{;}  &
    \delta^n_{\sigma'(i)} \ar@{-}[d]  \ar@{}[r]|{;}  \ar@{-}@/_3ex/[r]|{\cycl{3}}  &
   \delta^n_{\sigma'(i+1)} \ar@{-}[d]  \ar@{}[r]|{;} &
    \cdots\\
\rho'  \ar@{}[r]|{=} & 
    \cdots   \ar@{}[r]|{;}  &
     \delta'_{\sigma(i)} \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
    \delta'_{\sigma(i+1)}  \ar@{}[r]|{;} &
     \cdots  \\
}$$

\todo[inline]{But is it obvious that if two steps keep their position the remain shift-equivalent? Maybe this is another condition...}

Therefore clearly $SI(\cycl{2}) \iff SI(\cycl{3})$. Furthermore $SI(\cycl{1}) \iff SI(\cycl{3})$  by induction hypothesis, because $\rho  \stackrel{sh\ *}{\rightsquigarrow} \rho_n$  has length $n$, and thus we conclude $SI(\cycl{1}) \iff SI(\cycl{2})$.

\item  [{[$z = \sigma'(i+1)$ and $\sigma'(i) = z+1$]}]  In this case the last transposition switches the steps $\delta^n_{\sigma'(i+1)}$ and $\delta^n_{\sigma'(i)}$  of $\rho_n$, as depicted here:

$$\xymatrix@C=2pc@R=2pc{
 \rho  \ar@{~>}[d]^{sh}^(.9){*} \ar@{}[r]|{=} &
   \cdots   \ar@{}[r]|{;}  &
    \delta_i \ar@{--}[dr]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
    \delta_{i+1} \ar@{--}[dl]  \ar@{}[r]|{;}  & \cdots\\
\rho_n  \ar@{~>}[d]^{sh}_{\upsilon_{n+1}}  \ar@{}[r]|{=} &
   \cdots   \ar@{}[r]|{;}  &
    \delta^n_{\sigma'(i+1)} \ar@{-}[dr]  \ar@{}[r]|{;}  \ar@{-}@/^2ex/[r]|{\cycl{3}}  &
   \delta^n_{\sigma'(i)} \ar@{-}[dl]  \ar@{}[r]|{;} &
    \cdots\\
\rho'  \ar@{}[r]|{=} & 
    \cdots   \ar@{}[r]|{;}  &
     \delta'_{\sigma(i)} \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
    \delta'_{\sigma(i+1)}  \ar@{}[r]|{;} &
     \cdots  \\
}$$

Clearly we have $SI(\cycl{3})$ because the two steps are switched, and thus also $SI(\cycl{2})$ by  conditions  \ref{cond:si-symm} and \ref{cond:si-si-iso} of Definition~\ref{def:si-conditions}. Furthermore, as evident from the drawing the steps $\delta_i$ and $\delta_{i+1}$ of $\rho$ must have been switched by a transposition $\upsilon_j = (v, v+1)$ with $1 \leq j \leq n$.  Therefore we have that steps $\delta^{j-1}_v$ and $\delta^{j-1}_{v+1}$  are sequential independent in $\rho^{j-1}$, and by induction hypothesis  (because $j \leq n$) we infer $SI(\cycl{1})$, allowing us to conclude that $SI(\cycl{1}) \iff SI(\cycl{2})$.

\item  [{[$z+1 = \sigma'(i+1)$, thus $z = \sigma(i+1)$]}]

% and $z =\sigma'(v) for $v \gt i+1
In this case the transposition $\upsilon_{n+1}$ affects one of the steps \cycl{2} but not both, as summarized in the drawing.
$$\xymatrix@C=2pc@R=2pc{
 \rho  \ar@{~>}[d]^{sh}^(.9){*} \ar@{}[r]|{=} &
   \cdots   \ar@{}[r]|{;}  &
    \delta_i \ar@{--}@/_2ex/[d]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
    \delta_{i+1} \ar@{--}@/^1ex/[dr]  \ar@{}[r]|{;}  & \cdots\\
\rho_n  \ar@{~>}[d]^{sh}_{\upsilon_{n+1}}  \ar@{}[r]|{=} &
   \cdots   \ar@{}[r]|{;}  &
    \delta^n_{\sigma'(i)} \ar@{-}[d]  \ar@{}[r]|{;}   &
   \delta^n_z \ar@{-}[dr]  \ar@{}[r]|{;} &
   \delta^n_{\sigma'(i+1)} \ar@{-}[dl]  \ar@{}[r]|{;} &
    \cdots\\
\rho'  \ar@{}[r]|{=} & 
    \cdots   \ar@{}[r]|{;}  &
     \delta'_{\sigma(i)} \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
    \delta'_{\sigma(i+1)}  \ar@{}[r]|{;} &
    \delta'_{z+1}  \ar@{}[r]|{;} &
     \cdots  \\
}$$

There are two subcases, depending on whether step $\delta_z^n$ originates from a step in $\rho$ after $\delta_{i+1}$ or before $\delta_i$. In the first case we have:  
$$\xymatrix@C=2pc@R=2pc{
 \rho  \ar@{~>}[d]^{sh}^(.9){*} \ar@{}[r]|{=} &
   \cdots   \ar@{}[r]|{;}  &
    \delta_i \ar@{--}@/_2ex/[d]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
   \delta_{i+1}  \ar@{--}@/^1ex/[dr]  \ar@{}[r]|{\cdots}  &
    \delta_{{\sigma'}^{-1}(z)} \ar@{--}@/_1ex/[dl]  \ar@{}[r]|{;}  & \cdots\\
\rho_n  \ar@{~>}[d]^{sh}_{\upsilon_{n+1}}  \ar@{}[r]|{=} &
   \cdots   \ar@{}[r]|{;}  &
    \delta^n_{\sigma'(i)} \ar@{-}[d]  \ar@{}[r]|{;}   &
   \delta^n_z \ar@{-}[dr]  \ar@{}[r]|{;} &
   \delta^n_{\sigma'(i+1)} \ar@{-}[dl]  \ar@{}[r]|{;} &
    \cdots\\
\rho'  \ar@{}[r]|{=} & 
    \cdots   \ar@{}[r]|{;}  &
     \delta'_{\sigma(i)} \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
    \delta'_{\sigma(i+1)}  \ar@{}[r]|{;} &
    \delta'_{z+1}  \ar@{}[r]|{;} &
     \cdots  \\
}$$

As evident form the drawing, in this case there are certainly some useless transpositions. Thus by Lemma~\ref{le:no-useless-shifts-bounded} (used on proofs of length at most $n+1$, with the induction hypothesis up to length $n$) there exists an equivalent proof of $\rho \shifteq[\perm] \rho'$  of length at most $n-1$, thus we can conclude by inductive hypothesis.

The second case is depicted as follows:

$$\xymatrix@C=2pc@R=2pc{
 \rho  \ar@{~>}[d]^{sh}^(.9){*} \ar@{}[r]|{=} &
   \delta_{{\sigma'}^{-1}}(z)  \ar@{--}@/^1ex/[drr]   \ar@{}[r]|{\cdots}  &
    \delta_i \ar@{--}@/_2ex/[d]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
    \delta_{i+1} \ar@{--}@/^1ex/[dr]  \ar@{}[r]|{;}  & \cdots\\
\rho_n  \ar@{~>}[d]^{sh}_{\upsilon_{n+1}}  \ar@{}[r]|{=} &
   \cdots   \ar@{}[r]|{;}  &
    \delta^n_{\sigma'(i)} \ar@{-}[d]  \ar@{}[r]|{;}   &
   \delta^n_z \ar@{-}[dr]  \ar@{}[r]|{;} &
   \delta^n_{\sigma'(i+1)} \ar@{-}[dl]  \ar@{}[r]|{;} &
    \cdots\\
\rho'  \ar@{}[r]|{=} & 
    \cdots   \ar@{}[r]|{;}  &
     \delta'_{\sigma(i)} \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
    \delta'_{\sigma(i+1)}  \ar@{}[r]|{;} &
    \delta'_{z+1}  \ar@{}[r]|{;} &
     \cdots  \\
}$$

We see that two steps from which $\delta^n_{\sigma'(i)}$ and $\delta^n_z$ originate were switched by a transposition $\upsilon_j$ with $1 \leq j \leq n$ therefore by induction hypothesis we infer that  $\delta^n_{\sigma'(i)}$ and $\delta^n_z$ are sequentially independent. Thus we can modify the proof as follows, switching such steps twice:

$$\xymatrix@C=2pc@R=2pc{
 \rho  \ar@{~>}[d]^{sh}^(.9){*} \ar@{}[r]|{=} &
   \delta_{{\sigma'}^{-1}}(z)  \ar@{--}@/^1ex/[drr]   \ar@{}[r]|{\cdots}  &
    \delta_i \ar@{--}@/_2ex/[d]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
    \delta_{i+1} \ar@{--}@/^1ex/[dr]  \ar@{}[r]|{;}  & \cdots\\
\rho_n  \ar@{~>}[d]^{sh}_{\upsilon_{n+1}}  \ar@{}[r]|{=} &
   \cdots   \ar@{}[r]|{;}  &
    \delta^n_{\sigma'(i)} \ar@{-}[dr]  \ar@{}[r]|{;}   &
   \delta^n_z \ar@{-}[dl]  \ar@{}[r]|{;} &
   \delta^n_{\sigma'(i+1)} \ar@{-}[d]  \ar@{}[r]|{;} &
    \cdots\\
  \rho_{n+1}  \ar@{~>}[d]^{sh}_{\upsilon_{n+2}}  \ar@{}[r]|{=} &
   \cdots   \ar@{}[r]|{;}  &
    \delta^{n+1}_{z-1} \ar@{-}[dr]  \ar@{}[r]|{;}   &
   \delta^{n+1}_{\sigma'(i)+1}  \ar@{-}[dl]  \ar@{}[r]|{;}   \ar@{-}@/^3ex/[r]|{\cycl{3}} &
   \delta^{n+1}_{\sigma'(i+1)} \ar@{-}[d]  \ar@{}[r]|{;} &
    \cdots\\
    \rho_{n+2}  \ar@{~>}[d]^{sh}_{\upsilon_{n+3}}  \ar@{}[r]|{=} &
   \cdots   \ar@{}[r]|{;}  &
    \delta^{n+2}_{\sigma'(i)} \ar@{-}[d]  \ar@{}[r]|{;}   &
   \delta^{n+2}_z \ar@{-}[dr]  \ar@{}[r]|{;} &
   \delta^{n+2}_{\sigma'(i+1)} \ar@{-}[dl]  \ar@{}[r]|{;} &
    \cdots\\  
\rho'  \ar@{}[r]|{=} & 
    \cdots   \ar@{}[r]|{;}  &
     \delta'_{\sigma(i)} \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
    \delta'_{\sigma(i+1)}  \ar@{}[r]|{;} &
    \delta'_{z+1}  \ar@{}[r]|{;} &
     \cdots  \\
}$$

Now we can conclude observing that $SI(\cycl{2}) \iff SI(\cycl{3})$ by point 2 of Lemma~\ref{le:invariance-immediate}, and that $SI(\cycl{1}) \iff SI(\cycl{3})$ can be proved by applying the first subcase of this step of the proof.

\todo[inline]{Lemma~\ref{le:invariance-immediate} considera solo derivazioni di lunghezza 3. Anche qui serve un lemma che garantisce che vale anche in un contesto piu' ampio.}

\item   [{[$z = \sigma'(i)$, thus $z+1 = \sigma(i)$]}]  
This case is completely symmetrical to the previous one, exploiting in the last subcase point 1 of Lemma~\ref{le:invariance-immediate}.

\end{description}

\end{proof}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2023-07-15 GraphShift/GraphShift.tex
added directory

--- 2023-07-15 Notes.tex
@@
 
-\title{Ideas}
+\title{On graphs and shift}
 
@@
 
-\subsection*{Shift equivalence for non-right linear}
-
-Sequential independence is a key ingredient in the concurrency theory of DPO graph transformation, since it states when consecutive rewriting steps can be switched, thus 
-identifying them as causally unrelated. The associated theory of shift equivalence on rewriting sequences is well-understood for linear rules, including its 
-connection with standard models for concurrent systems such as event structures. 
-%
-This is not so for rules that are only left-linear, i.e., such that
-their right-hand side may merge graph items.
-
-In particular, if one just take the definition with general
-interchange pairs, undesidered things might happen. In particular one
-can have shift-equivalent derivations where the permutation is the
-identity but which are non isomorphic (e.g., in GraphShift, page 1-2
-$\rho_1 \shifteq \rho_3$, but $\rho_1 \equiv^{a} \rho_3$.
-
-We want a notion of shift-equivalence which ensures some properties
-which are indispensable to allow to interpret derivations up-to shift
-as equivalent concurrent computations which differ only for the fact
-that independent steps have been moved around.
-When moving around steps, we should not loose track of the identity of the steps: this is essential to be able to have an event structure semantics with a clearly defined notion of event.
-
-Hence we assume to deal
-with a notion of shift-equivalence between derivations of the kind
-$\rho \shifteq_\sigma \rho'$ where $\rho, \rho'$ consist of $n$
-rewriting steps, $\sigma: \interval{n} \to \interval{n}$ is a
-permutation (the idea being that $\rho$ is obtained from $\rho'$
-pemutating the steps according to $\sigma$) with the following
-properties:
-
-\begin{itemize}
-\item \textbf{Property 0}. Shift equivalence is an equivalence, in particular it is symmetric. I.e., if  $\rho \shifteq_\sigma \rho'$ then $\rho' \shifteq_{\sigma^{-1}} \rho$;
-
-\item \textbf{Property 1}. Derivations which are shift-equivalent via the
-  identity permutation are isomorphic: if $\rho \shifteq \rho'$ then
-  $\rho \equiv^a \rho'$;
-
-\item \textbf{Property 2}. Shift equivalence between adjacent rewriting steps
-  is a property of the steps, invariant for permutation according to
-  shift, i.e., if two steps are independent in some derivation $\rho$
-  and we can prove that $\rho$ is shift-equivalent to some $\rho'$
-  where the same steps are again consecutive, but possibly in a
-  different position, then the steps are again independent, and also
-  the converse holds. Formally, if $\rho \shifteq_\sigma \rho'$ with
-  $\rho, \rho'$ consist of $n$ rewriting steps and for some
-  $i \in \interval{n-1}$, $\sigma(i)+1 = \sigma(i+1)$, the the steps
-  $i, i+1$ in $\rho$ are shift-independent iff $\sigma(i)$ and
-  $\sigma(i)+1$ are so in $\rho'$.
-\end{itemize}
-
-\textbf{Question.} Taking the standard shift, with generic interchange pair, a a counterexample to property 1, is the one mentioned above.  Do we have a counterexample to property 2? Not clear to me.
-
-The above discussion should lead to
-
-\begin{enumerate}
-\item The conditions proposed by Andrea for a good notion of shift (in
-  the draft, GraphShift, Def. 3, cond (1)-(5), with the addition of
-  Lemma 12).
-
-  \textbf{Questions}: Can we reduce the set of axioms? Do we need something else relating abstraction equivalence (iso of derivation) and shift? Relation with symmetries?
-
-\item For left-linear rules, the proposed notion of shift equivalence
-  requires: uniqueness of the interchange pair and symmetry. Show that
-  this satisfies the above
-
-\item Apparently, the satisfaction of the properties above has not
-  been explicitly observed for the case of linear rules. If so, it is
-  worth to remark it.
-
-\item Does the theory above apply to other cases. E.g., if one wants a
-  proper notion of causality (avoiding or-causality) a possibility
-  seems to be to restrict the applicability condition for rules, to
-  prevent fusions to act on already merged items (see section V.D in
-  the arxiv). By the way, note that the satisfaction of the conditions
-  on shift depends not only on the notion of shift, but also on the
-  notion of rewriting. In this case we expect to have a prime event
-  structure (bit this has to do with the second part of the work).
-
-\end{enumerate}
-
-\subsection*{Event structures for non-right linear}
-
-Ideally, one would like to be able to work with an abstract notion of
-shift-equivalence and just using its properties as singled out in the
-previous part derive a weak prime domain or connected event structure
-for it. This is probably difficult, but one might need to add some
-futher properties to be proved for the specific notion of shift at
-hand.
-
-For this part, relevant material is section V of Arxiv.
-We use abstraction equivalence (iso of derivations) $\equiv^{a}$ (def.
-36), shift-equivalence $\shifteq_\sigma$ (Def.
-38, traking the permutation) and their join $\equiv^c_\sigma$.
-
-For linear rules on graphs it is known that two derivations are
-related by $\rho \equiv^c_\sigma \rho'$ iff $\sigma$ is a consistent
-permutation (def. 40, arxiv). Rough;y the idea is to take the colimit
-and consider the rewriting steps over the colimit to deduce
-dependencies. This was used in many places in the proofs, but for
-left-linear rules the proof does not go through (only the implication
-``if $\rho \equiv^c_\sigma \rho'$ then $\sigma$ is a consistent
-permutation'' (Lemma 17(1)) seems to hold as the original proof do not
-to rely on linearity, this should be double-checked, but the converse
-is false). In general, the hope is to get rid of using consistent
-permutation and use instead more asbtract properties of
-shift-equivalence as discussed in the first part.
-
-The general idea is to show that considering derivations are arrows from the source to the target graph, then the slice from the initial graph $\slice{[G_s]}{\tr{\mathcal{G}}}$ should be a pre-order, whose ideal completion is a weak prime domain.
-
-Relevant technical lemma in Arxiv are:
-
-\begin{itemize}
-
-\item
-  \textbf{Lemma 17}.
-Points (2) and (3) should be hopefully consequences of the general properties of shift in the previous part and they play a role in proving that $\slice{[G_s]}{\tr{\mathcal{G}}}$ is a pre-order (Prop.
-14)
-
-\item
-  \textbf{Lemma 19}.
-  (1) says that if $\psi; \psi_1 \equiv^c_\sigma \psi'; \psi_1'$ and the permutation $\sigma$ sends $n$ steps of $\psi_1$ to $\psi'$ then such steps are not in $\psi$ and they will need to be in every $\phi_2$ such that $\psi; \phi_2 \equiv^c_\sigma \psi'; \phi_2'$.
-In particular there is $\phi_2$ consisting of exactly $n$ steps which allows for commutation.
-This allows essentially to deduce existence of minimal upper bounds, al with the same length.
-  Then (2) shows that all minimal upper bounds are isomorphic, so that we have a sup.
-
-  Again, the hope is to obtain this from the abstract properties of
-  shift.
-
-\item \textbf{Proposition 15} shows that $\ideal{\poset{\mathcal{G}}}$
-  is a domain, i.e., algebraic finitary (see Def. 6), while
-  \textbf{Theorem 6} prove that it is weak prime.
-
-  Here I think that the proofs are draft modifications of the original ones, changed after discovering the property on consistent permutation to be wrong.
-But they are drafty, to be redone maybe keeping some ideas.
-
-\subsection*{Event structures for non-right linear, but jointly mono matches}
-
-This is the idea in Section V.D.
-As mentioned above, ideally, if the proof in the previous part were based just on abstract properties of shift, one could hope of proving that shift in this context has the right properties, deduce that the construction produces a weak prime domain.
-
-Then, one could observe that in this specific context actually all weak primes are primes an thus deduce that this provides a prime algebraic domain/pes semantics of fusion.
-
-\end{itemize}
-
-\end{document}
-
-\keywords{Shift equivalence, non-linear rules, DPO rewriting.}
-
-\section{Introduction}
+\section{Domain and event structure semantics for graph rewriting}
 \label{se:graphs}
-
-Shortly, shift equivalence can be defined as the smallest equivalence relation on derivations, i.e. sequences of rewriting steps,
-that can be obtained by the iterated switch of sequentially 
-independent steps. A crucial observation, which represented our starting point, is that the notion of sequential independence traditionally
-adopted for linear graph transfomation systems is not adequate when we
-allow rules to be non-right linear, i.e., in the presence of
-fusions. Consider the rules in Fig.~\ref{fi:rules}, typed over the type graph $T$,
-where numbers are used to represent the mappings from the interface to the left- and
-right-hand sides.
 
@@
 
-Now, let us consider an initial graph with a single node. We can then obtain
-the derivation $\rho_1 = \delta_1; \delta_2; \delta_3$ in Fig.~\ref{fi:der1}, where $\delta_2$ and $\delta_3$ are
+A crucial observation is that the notion of shift equivalence normally
+adopted for linear graph rewriting systems is not adequate when we
+allow rules to be non-right linear, i.e., in the presence of
+fusions. Consider the rewriting system in Fig.~\ref{fi:rules},
+where numbers are used to represent the mappings from the interface to the left- and
+right-hand sides.
+%
+Then, starting from an initial graph with a single node, we can obtain
+the derivation $\rho = \delta_1; \delta_2; \delta_3$ in Fig.~\ref{fi:der1}, where $\delta_2$ and $\delta_3$ are
 sequential independent according to the standard notion.
@@
 
-The fact that if we switch two steps and then switch them back, we obtain a derivation that is not equivalent to the original one has unpleasant consequences.
+The fact that if we shift two steps and then switch them back, we can obtain a derivation that is not equivalent to the original one has unpleasant consequences.
 For instance, if we restrict $\rho_1'$ and $\rho_3'$ to the first two steps, we get non-equivalent derivations $\delta_1;\delta_2 \not\shifteq \delta_1;\delta_2'$, but $\rho_1 \shifteq[\sigma] \rho_3$, with $\sigma$ mapping $\delta_1$ to $\delta_1$ and $\delta_2$ to $\delta_2'$.
-%
-The lack of such closure with respect to composition does not allow to obtain a causal semantics for graph transformation systems.
-More precisely, it does  not allow to associate an event structure to a derivation.
-%
-Thus, the notion of sequential independence has to be refined. The point is that in the associated shift equivalence we want to forget who made the fusion, 
-but we should not forget (as it happens in the example) that some fusions occurred.
+
+The notion of shift equivalence has to be refined: the point is that we want to forget who made the fusion, but we should not forget (as it happens in the example) that some fusions occurred.
 
@@
 Shift equivalence is made stricter by asking that two steps are
-sequentially independent if the result of their switch is uniquely
+shiftable only when the result of the shift is uniquely
 determined. Intuitively, when there are several way of performing the
-exchange, it means that the first step has executed some fusions that
+exchange, it means that the first step has performed some fusions that
 the second step is using in an essential way, hence they should not
-considered independent. Formally, this boils down to require that 
-in the definition of sequential independence the interchange pair is unique.
-
-The paper builds on this intuition: it introduces this stricter notion of sequential independence
-(Section~xxx) and prove that the associated theory of shift equivalence on derivations is 
-well-behaved with respect to the concatenation of rewriting steps (Section~xxx).
-Finally, it outlines how the relationship with event structure works, wrapping up the paper
-with comparison with related woks and hinting at further direction of research (Section~xxx).
-
-\section{Preliminaries [to be redone]}
+considered independent. Formally, in the definition of sequential
+independence (Fig.~\ref{fi:strongseq}) we ask that the independence pair $\langle i_1, i_2\rangle$ is unique.
 
@@
   independence for contiguous derivations is easy.
-The fact that it coincides when derivations are not contiguous is false (the approach based on defining independence for non-contiguous derivation is not working, but the results should be true ...)
 \end{proof}
@@
   transpositions (that thus operate on inversions). Then, for all
-  $h \in \interval{m}$ with $\upsilon_h = \transp{l}[l+1]$ there exists
+  $h \in \interval{m}$ with $\upsilon_h = \transp{l}[m]$ there exists
   $k \in \interval{m}$ such that
   $\upsilon_k = \transp{\upsilon_{1,h-1}^{-1};v_1;
-    \upsilon_{1,k-1}(l)}[\upsilon_{1,h-1}^{-1};v_1; \upsilon_{1,k-1}(l+1)]$.
+    \upsilon_{1,k-1}(l)}[\upsilon_{1,h-1}^{-1};v_1; \upsilon_{1,k-1}(m)]$.
 \end{lemma}

### 2023-07-15 GraphShift/icgt2023.tex
added directory

--- 2023-07-15 Notes.tex
@@
 
-\title{Ideas}
+\title{On shift equivalence for non-linear rules\thanks{Research partially supported by the MIUR PRIN 2017FTXR7S ``IT-MaTTerS''.}
+}
+
+\author{Paolo Baldan\inst{1}, Andrea Corradini\inst{2}, Fabio Gadducci\inst{2}
+} 
+	\institute{Department of Mathematics, University of Padua, Italy \\
+		\email{baldan@math.unipd.it}
+		\and Department of Computer Science, University of Pisa, Italy \\
+		\email{\{andrea.corradini, fabio.gadducci\}@unipi.it}
+		}
+
+\titlerunning{On shift equivalence for non-linear rules}
+\authorrunning{Baldan, Corradini, and Gadducci, and Santini}
 
@@
 
-\subsection*{Shift equivalence for non-right linear}
-
+\begin{abstract}
 Sequential independence is a key ingredient in the concurrency theory of DPO graph transformation, since it states when consecutive rewriting steps can be switched, thus 
@@
 %
-This is not so for rules that are only left-linear, i.e., such that
-their right-hand side may merge graph items.
-
-In particular, if one just take the definition with general
-interchange pairs, undesidered things might happen. In particular one
-can have shift-equivalent derivations where the permutation is the
-identity but which are non isomorphic (e.g., in GraphShift, page 1-2
-$\rho_1 \shifteq \rho_3$, but $\rho_1 \equiv^{a} \rho_3$.
-
-We want a notion of shift-equivalence which ensures some properties
-which are indispensable to allow to interpret derivations up-to shift
-as equivalent concurrent computations which differ only for the fact
-that independent steps have been moved around.
-When moving around steps, we should not loose track of the identity of the steps: this is essential to be able to have an event structure semantics with a clearly defined notion of event.
-
-Hence we assume to deal
-with a notion of shift-equivalence between derivations of the kind
-$\rho \shifteq_\sigma \rho'$ where $\rho, \rho'$ consist of $n$
-rewriting steps, $\sigma: \interval{n} \to \interval{n}$ is a
-permutation (the idea being that $\rho$ is obtained from $\rho'$
-pemutating the steps according to $\sigma$) with the following
-properties:
-
-\begin{itemize}
-\item \textbf{Property 0}. Shift equivalence is an equivalence, in particular it is symmetric. I.e., if  $\rho \shifteq_\sigma \rho'$ then $\rho' \shifteq_{\sigma^{-1}} \rho$;
-
-\item \textbf{Property 1}. Derivations which are shift-equivalent via the
-  identity permutation are isomorphic: if $\rho \shifteq \rho'$ then
-  $\rho \equiv^a \rho'$;
-
-\item \textbf{Property 2}. Shift equivalence between adjacent rewriting steps
-  is a property of the steps, invariant for permutation according to
-  shift, i.e., if two steps are independent in some derivation $\rho$
-  and we can prove that $\rho$ is shift-equivalent to some $\rho'$
-  where the same steps are again consecutive, but possibly in a
-  different position, then the steps are again independent, and also
-  the converse holds. Formally, if $\rho \shifteq_\sigma \rho'$ with
-  $\rho, \rho'$ consist of $n$ rewriting steps and for some
-  $i \in \interval{n-1}$, $\sigma(i)+1 = \sigma(i+1)$, the the steps
-  $i, i+1$ in $\rho$ are shift-independent iff $\sigma(i)$ and
-  $\sigma(i)+1$ are so in $\rho'$.
-\end{itemize}
-
-\textbf{Question.} Taking the standard shift, with generic interchange pair, a a counterexample to property 1, is the one mentioned above.  Do we have a counterexample to property 2? Not clear to me.
-
-The above discussion should lead to
-
-\begin{enumerate}
-\item The conditions proposed by Andrea for a good notion of shift (in
-  the draft, GraphShift, Def. 3, cond (1)-(5), with the addition of
-  Lemma 12).
-
-  \textbf{Questions}: Can we reduce the set of axioms? Do we need something else relating abstraction equivalence (iso of derivation) and shift? Relation with symmetries?
-
-\item For left-linear rules, the proposed notion of shift equivalence
-  requires: uniqueness of the interchange pair and symmetry. Show that
-  this satisfies the above
-
-\item Apparently, the satisfaction of the properties above has not
-  been explicitly observed for the case of linear rules. If so, it is
-  worth to remark it.
-
-\item Does the theory above apply to other cases. E.g., if one wants a
-  proper notion of causality (avoiding or-causality) a possibility
-  seems to be to restrict the applicability condition for rules, to
-  prevent fusions to act on already merged items (see section V.D in
-  the arxiv). By the way, note that the satisfaction of the conditions
-  on shift depends not only on the notion of shift, but also on the
-  notion of rewriting. In this case we expect to have a prime event
-  structure (bit this has to do with the second part of the work).
-
-\end{enumerate}
-
-\subsection*{Event structures for non-right linear}
-
-Ideally, one would like to be able to work with an abstract notion of
-shift-equivalence and just using its properties as singled out in the
-previous part derive a weak prime domain or connected event structure
-for it. This is probably difficult, but one might need to add some
-futher properties to be proved for the specific notion of shift at
-hand.
-
-For this part, relevant material is section V of Arxiv.
-We use abstraction equivalence (iso of derivations) $\equiv^{a}$ (def.
-36), shift-equivalence $\shifteq_\sigma$ (Def.
-38, traking the permutation) and their join $\equiv^c_\sigma$.
-
-For linear rules on graphs it is known that two derivations are
-related by $\rho \equiv^c_\sigma \rho'$ iff $\sigma$ is a consistent
-permutation (def. 40, arxiv). Rough;y the idea is to take the colimit
-and consider the rewriting steps over the colimit to deduce
-dependencies. This was used in many places in the proofs, but for
-left-linear rules the proof does not go through (only the implication
-``if $\rho \equiv^c_\sigma \rho'$ then $\sigma$ is a consistent
-permutation'' (Lemma 17(1)) seems to hold as the original proof do not
-to rely on linearity, this should be double-checked, but the converse
-is false). In general, the hope is to get rid of using consistent
-permutation and use instead more asbtract properties of
-shift-equivalence as discussed in the first part.
-
-The general idea is to show that considering derivations are arrows from the source to the target graph, then the slice from the initial graph $\slice{[G_s]}{\tr{\mathcal{G}}}$ should be a pre-order, whose ideal completion is a weak prime domain.
-
-Relevant technical lemma in Arxiv are:
-
-\begin{itemize}
-
-\item
-  \textbf{Lemma 17}.
-Points (2) and (3) should be hopefully consequences of the general properties of shift in the previous part and they play a role in proving that $\slice{[G_s]}{\tr{\mathcal{G}}}$ is a pre-order (Prop.
-14)
-
-\item
-  \textbf{Lemma 19}.
-  (1) says that if $\psi; \psi_1 \equiv^c_\sigma \psi'; \psi_1'$ and the permutation $\sigma$ sends $n$ steps of $\psi_1$ to $\psi'$ then such steps are not in $\psi$ and they will need to be in every $\phi_2$ such that $\psi; \phi_2 \equiv^c_\sigma \psi'; \phi_2'$.
-In particular there is $\phi_2$ consisting of exactly $n$ steps which allows for commutation.
-This allows essentially to deduce existence of minimal upper bounds, al with the same length.
-  Then (2) shows that all minimal upper bounds are isomorphic, so that we have a sup.
-
-  Again, the hope is to obtain this from the abstract properties of
-  shift.
-
-\item \textbf{Proposition 15} shows that $\ideal{\poset{\mathcal{G}}}$
-  is a domain, i.e., algebraic finitary (see Def. 6), while
-  \textbf{Theorem 6} prove that it is weak prime.
-
-  Here I think that the proofs are draft modifications of the original ones, changed after discovering the property on consistent permutation to be wrong.
-But they are drafty, to be redone maybe keeping some ideas.
-
-\subsection*{Event structures for non-right linear, but jointly mono matches}
-
-This is the idea in Section V.D.
-As mentioned above, ideally, if the proof in the previous part were based just on abstract properties of shift, one could hope of proving that shift in this context has the right properties, deduce that the construction produces a weak prime domain.
-
-Then, one could observe that in this specific context actually all weak primes are primes an thus deduce that this provides a prime algebraic domain/pes semantics of fusion.
-
-\end{itemize}
-
-\end{document}
+This is not so for rules that are only left-linear, i.e., such that their right-hand side may merge graph items. More precisely, the correspondence with
+event structures fails, since merging may hinder the causal dependency between rewriting steps.
+%
+We argue that a stricter notion of sequential independence is needed for such rules, and we prove that our proposal is well-behaved with respect to the concatenation of
+rewriting steps.
+\end{abstract}
+
+%We extend Soft Concurrent Constraint languages with the possibility to manage both local (and global) knowledge of agents.
+Being constraints defined as soft, the underlying system of preferences consists in an ordered monoid where it is possible to natively represent partially ordered and bipolar (i.e., positive/negative) preferences.
+Such a formalism further generalise the previous literature, while it also grants  a \emph{polynomial}  representation of soft constraints that can be exploited in  several applications.
+Variables, which support constraints, can either be private to a single agent, or in common with all of them, thus allowing  for different levels of visibility.
+We provide labelled and unlabelled reduction semantics and their correspondence, together with a labelled bisimulation equivalence.
 
@@
 
-The fact that if we switch two steps and then switch them back, we obtain a derivation that is not equivalent to the original one has unpleasant consequences.
+The fact that if we switch two steps and then switch them back, we may obtain a derivation that is not coincident with the original one has unpleasant consequences.
 For instance, if we restrict $\rho_1'$ and $\rho_3'$ to the first two steps, we get non-equivalent derivations $\delta_1;\delta_2 \not\shifteq \delta_1;\delta_2'$, but $\rho_1 \shifteq[\sigma] \rho_3$, with $\sigma$ mapping $\delta_1$ to $\delta_1$ and $\delta_2$ to $\delta_2'$.
 %
-The lack of such closure with respect to composition does not allow to obtain a causal semantics for graph transformation systems.
+Such a behaviour with respect to composition does not allow to obtain a causal semantics for graph transformation systems.
 More precisely, it does  not allow to associate an event structure to a derivation.
@@
 
+\bibliographystyle{splncs04}
+%\bibliographystyle{plainurl}
+\bibliography{Unstable}
+
 \end{document}

### 2023-07-16 Related/GraphShift.tex
some related stuff

--- 2023-07-15 GraphShift/icgt2023.tex
@@
 
-%We extend Soft Concurrent Constraint languages with the possibility to manage both local (and global) knowledge of agents.
-Being constraints defined as soft, the underlying system of preferences consists in an ordered monoid where it is possible to natively represent partially ordered and bipolar (i.e., positive/negative) preferences.
-Such a formalism further generalise the previous literature, while it also grants  a \emph{polynomial}  representation of soft constraints that can be exploited in  several applications.
-Variables, which support constraints, can either be private to a single agent, or in common with all of them, thus allowing  for different levels of visibility.
-We provide labelled and unlabelled reduction semantics and their correspondence, together with a labelled bisimulation equivalence.
-
 \keywords{Shift equivalence, non-linear rules, DPO rewriting.}
@@
 
-The fact that if we switch two steps and then switch them back, we may obtain a derivation that is not coincident with the original one has unpleasant consequences.
+The fact that if we switch two steps and then switch them back, we obtain a derivation that is not equivalent to the original one has unpleasant consequences.
 For instance, if we restrict $\rho_1'$ and $\rho_3'$ to the first two steps, we get non-equivalent derivations $\delta_1;\delta_2 \not\shifteq \delta_1;\delta_2'$, but $\rho_1 \shifteq[\sigma] \rho_3$, with $\sigma$ mapping $\delta_1$ to $\delta_1$ and $\delta_2$ to $\delta_2'$.
 %
-Such a behaviour with respect to composition does not allow to obtain a causal semantics for graph transformation systems.
+The lack of such closure with respect to composition does not allow to obtain a causal semantics for graph transformation systems.
 More precisely, it does  not allow to associate an event structure to a derivation.
@@
   independence for contiguous derivations is easy.
+The fact that it coincides when derivations are not contiguous is false (the approach based on defining independence for non-contiguous derivation is not working, but the results should be true ...)
 \end{proof}
@@
   transpositions (that thus operate on inversions). Then, for all
-  $h \in \interval{m}$ with $\upsilon_h = \transp{l}[m]$ there exists
+  $h \in \interval{m}$ with $\upsilon_h = \transp{l}[l+1]$ there exists
   $k \in \interval{m}$ such that
   $\upsilon_k = \transp{\upsilon_{1,h-1}^{-1};v_1;
-    \upsilon_{1,k-1}(l)}[\upsilon_{1,h-1}^{-1};v_1; \upsilon_{1,k-1}(m)]$.
+    \upsilon_{1,k-1}(l)}[\upsilon_{1,h-1}^{-1};v_1; \upsilon_{1,k-1}(l+1)]$.
 \end{lemma}
@@
 
-\bibliographystyle{splncs04}
-%\bibliographystyle{plainurl}
-\bibliography{Unstable}
-
 \end{document}

### 2023-07-16 Related/UnstableFull.tex
some related stuff

% (query-replace-regexp "\\\\begin{\\([^}]*\\)}\\[\\([^]]*\\)\\]{\\([^}]*\\)}{\\([^}]*\\)}" "\\\\begin{\\3}[\\2]")
\documentclass[conference]{IEEEtran}
 \pdfoutput=1 
%

%
%

 \usepackage{cite}
 \usepackage[standard]{ntheorem}
 %
 %
 %
 %
 %
\renewenvironment{proof}{\begin{IEEEproof}}{\end{IEEEproof}}
%

%
\newif\ifconf
\conftrue
\conffalse

%
\ifconf
  \newcommand{\short}[1]{#1}
  \newcommand{\full}[1]{}
  \usepackage{environ}
  \NewEnviron{killcontents}{}
  \let\proof\killcontents
  \let\endproof\endkillcontents
\else
  \newcommand{\short}[1]{}
  \newcommand{\full}[1]{{#1}}
\fi

%
\newif\iffinal
\finaltrue
%

%
%
%
%
%
%
%

%
%

\usepackage{etex}

\usepackage{hyperref}
\usepackage[textsize=tiny%
\iffinal
,disable%
\fi
]{todonotes}

\iffinal
\else
%
\setlength{\marginparwidth}{1.3cm}
\fi

%
\usepackage{proof}
\newcommand{\lab}[1]{\ensuremath{\mathsf{{#1}}}}
\newcommand{\slab}[1]{\ensuremath{\scriptstyle{\mathsf{{#1}}}}}

% name for transitivity of intechangeabilty on consistent irreducibles
\newcommand{\wi}{{interchangeable}}

% 
\newcommand{\binfer}[3][]{
  \mbox{\infer[#1]{#2}{#3}}}

%
%
%
%
%
%
%
\newlength{\myheight}
\newcommand{\inferL}[3]
  {\settoheight{\myheight}{\mbox{${#2}$}}
   \raisebox{\myheight}{{#1}}
   \makebox[1mm]{}
   \mbox{\infer{#2}{#3}}
}

\usepackage{amssymb,graphicx,epsfig,color}
%
\usepackage{subcaption}
\usepackage[arrow,matrix,frame,curve,cmtip,color]{xy}
\newdir{  >}{*{}!/-.9em/\dir{>}}
\newdir{ >}{*{}!/-.4em/\dir{>}}
\usepackage{wrapfig}

%
%

%
%

\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows,backgrounds,patterns}
\tikzstyle{node}=[circle, draw=black, minimum size=1mm]
\tikzstyle{trans}=[font=\scriptsize]
\tikzstyle{lab}=[font=\small]

\usepackage{tikz-cd}

\newcommand{\pgfBox}{
  \begin{pgfonlayer}{background} 
    \fill[blue!2,thick,draw=black!50,rounded corners,inner sep=3mm] ([xshift=-1.5pt]current bounding box.south west) rectangle ([xshift=1.5pt]current bounding box.north east);
  \end{pgfonlayer}
}

\newcommand{\bx}[1]{\phantom{\big(}#1{\phantom{\big)}}} %

\newcommand{\Rrel}[1]   {\stackrel{{#1}}{\Longrightarrow}}
\newcommand{\oa}{\overline a}
\newcommand{\ob}{\overline b}
\newcommand{\oc}{\overline c}
\newcommand{\od}{\overline d}
\newcommand{\nil}{{\tt 0}}
\newcommand{\rec}{\emph{rec}}
\newcommand{\fn}[1]{{\mathtt{fn}}(#1)}
%
\usepackage{stmaryrd}
\def\encodep#1{\llfloor#1\rrfloor}

\newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}

\newcommand{\dpo}{\textsc{dpo}}

%
\newcommand{\bAdh}{\ensuremath{\mathbb{B}}}
\newcommand{\bQAdh}{\ensuremath{\mathbb{QB}}}

%
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
%
%
%
\usepackage{enumerate}
\usepackage{xspace}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage{float}
\usepackage{fancybox}

%

%
\newcommand{\nat}{\ensuremath{\mathbb{N}}}

%
\newcommand{\sfin}{\ensuremath{\subseteq_{\mathit{fin}}}}

%
\newcommand{\flt}[1]{\ensuremath{[\![{#1}]\!]}}

%
\newcommand{\compact}[1]{\ensuremath{\mathop{\mathsf{K}({#1})}}}

%
\newcommand{\principal}[1]{\ensuremath{\mathop{\downarrow\!{#1}}}}

%
\newcommand{\ideal}[1]{\ensuremath{\mathsf{Idl}({#1})}}

%
\newcommand{\pr}[1]{\ensuremath{\mathop{\mathit{pr}({#1})}}}
\newcommand{\wpr}[1]{\ensuremath{\mathop{\mathit{wpr}({#1})}}}

%
\newcommand{\ir}[1]{\ensuremath{\mathop{\mathit{ir}({#1})}}}

%
\newcommand{\diff}[2]{\ensuremath{\delta({#1},{#2})}}

%

%
%
\newcommand{\esabbr}{\textsc{es}}
\newcommand{\esnabbr}{\textsc{esnb}}
\newcommand{\esnmabbr}{\textsc{esn}}
\newcommand{\eseqabbr}{\textsc{epes}}

%
\newcommand{\pred}[1]{\ensuremath{\mathit{p}({#1})}}

%
\newcommand{\esir}[2]{\ensuremath{\langle{#1}, {#2}\rangle}}

%
\newcommand{\eqclass}[2][]{\ensuremath{[{#2}]_{\scriptscriptstyle {#1}}}}
%
\newcommand{\eqclasscup}[2]{\ensuremath{{#2}_{\scriptscriptstyle {#1}}}}

\newcommand{\eqclassir}[1]{\ensuremath{\eqclass[\leftrightarrow^*]{#1}}}

%
\newcommand{\quotient}[2]{\ensuremath{{#1}_{\scriptscriptstyle {#2}}}}

%
\newcommand{\es}{\ensuremath{\mathsf{ES}}}
%
\newcommand{\ses}{\ensuremath{\mathsf{sES}}}
%
\newcommand{\pes}{\ensuremath{\mathsf{pES}}}
%
\newcommand{\epes}{\ensuremath{\mathsf{epES}}}

%
\newcommand{\ces}{\ensuremath{\mathsf{cES}}}

%
\newcommand{\WDom}{\ensuremath{\mathsf{wDom}}}
%
\newcommand{\Dom}{\ensuremath{\mathsf{Dom}}}
%
\newcommand{\PDom}{\ensuremath{\mathsf{pDom}}}

%

%
\newcommand{\esn}{\ensuremath{\mathsf{ES_{nb}}}}
%
\newcommand{\sesn}{\ensuremath{\mathsf{sES_n}}}

%
\newcommand{\cesn}{\ensuremath{\mathsf{cES_{nb}}}}

%
\newcommand{\pesn}{\ensuremath{\mathsf{pES_n}}}

%
\newcommand{\WDomb}{\ensuremath{\mathsf{wDom_b}}}
%
\newcommand{\Domb}{\ensuremath{\mathsf{Dom_b}}}
%
\newcommand{\PDomb}{\ensuremath{\mathsf{pDom_b}}}

%

%
\newcommand{\slice}[2]{\ensuremath{({#1} \downarrow {#2})}}

%
\newcommand{\zev}[0]{\ensuremath{\mathcal{E}}}
\newcommand{\ev}[1]{\ensuremath{\zev({#1})}}

%
\newcommand{\zconnes}[0]{\ensuremath{\mathcal{C}}}
\newcommand{\connes}[1]{\ensuremath{\zconnes({#1})}}
%
\newcommand{\zinces}[0]{\ensuremath{\mathcal{I}}}
\newcommand{\inces}[1]{\ensuremath{\zinces({#1})}}

%
\newcommand{\zsev}[0]{\ensuremath{\mathcal{E}_S}}
\newcommand{\sev}[1]{\ensuremath{\zsev({#1})}}

%
\newcommand{\zeveq}[0]{\ensuremath{\mathcal{E}_{eq}}}
\newcommand{\eveq}[1]{\ensuremath{\zeveq({#1})}}

%
\newcommand{\zfuse}[0]{\ensuremath{\mathcal{M}}}
\newcommand{\fuse}[1]{\ensuremath{\zfuse({#1})}}
\newcommand{\zunf}[0]{\ensuremath{\zunf}}
\newcommand{\unf}[1]{\ensuremath{\mathcal{U}({#1})}}

%
\newcommand{\zevwd}[0]{\ensuremath{\mathcal{E}_{wd}}}
\newcommand{\evwd}[1]{\ensuremath{\zevwd({#1})}}

%
\newcommand{\conf}[1]{\ensuremath{\mathit{Conf}({#1})}}
%
\newcommand{\conff}[1]{\ensuremath{\mathit{Conf_F}({#1})}}

%
\newcommand{\pmin}[1]{\ensuremath{U_{#1}}}

%
\newcommand{\conn}[1]{\ensuremath{\stackrel{#1}{\frown}}}

%
\newcommand{\zdom}[0]{\ensuremath{\mathcal{D}}}
\newcommand{\dom}[1]{\ensuremath{\zdom({#1})}}

\newcommand{\zdomeq}[0]{\ensuremath{\mathcal{D}_{eq}}}
\newcommand{\domeq}[1]{\ensuremath{\zdomeq({#1})}}

%
\newcommand{\poset}[1]{\ensuremath{\mathcal{P}({#1})}}

%
\newcommand{\pdom}[1]{\ensuremath{\mathcal{D}_S({#1})}}
\newcommand{\ppdom}[0]{\ensuremath{\mathcal{D}_S}}

%
\newcommand{\Pow}[1]{\ensuremath{\mathbf{2}^{#1}}}

%
\newcommand{\Powfin}[1]{\ensuremath{\mathbf{2}_\mathit{fin}^{#1}}}

%
\newcommand{\Powone}[1]{\ensuremath{\mathbf{2}_1^{#1}}}

%
\newcommand{\interval}[2][1]{\ensuremath{[{#1},{#2}]}}

%
\newcommand{\dint}[2]{\ensuremath{[{#1},{#2}]}}

%
\newcommand{\IntSet}[1]{\ensuremath{\mathop{\mathit{Int}({#1})}}}

%
\newcommand{\inir}{\ensuremath{\mathop{\mathit{\zeta}}}}
\newcommand{\irin}{\ensuremath{\mathop{\mathit{\iota}}}}

%
\newcommand{\perm}{\sigma}

% causes
\newcommand\twoheaddownarrow{\mathrel{\raisebox{0.8\depth}{\rotatebox{270}{$\twoheadrightarrow$}}}}
\newcommand{\scauses}[1]{\ensuremath{\twoheaddownarrow\!\!{#1}\,}}
\newcommand{\causes}[1]{\ensuremath{\,\downarrow\!\!{#1}}}

% saturation
\newcommand{\sat}[1]{\ensuremath{\tilde{#1}}}

\newcommand{\Abs}[1]{\ensuremath{\mathsf{Abs}({#1})}}
\newcommand{\tr}[1]{\ensuremath{\mathsf{Tr}({#1})}}
%
\newcommand{\trs}[1]{\ensuremath{\mathsf{Tr}_s({#1})}}
\newcommand{\graph}{\ensuremath{\mathsf{Graph}}}
\newcommand{\tgraph}[1]{\ensuremath{\mathsf{Graph}_{#1}}}
\newcommand{\can}[1]{\ensuremath{\mathsf{C}({#1})}}
%
\newcommand{\source}[1]{\ensuremath{\mathsf{s}({#1})}}
\newcommand{\target}[1]{\ensuremath{\mathsf{t}({#1})}}
\newcommand{\col}[1]{\ensuremath{\mathsf{col}({#1})}}

%
\newcommand{\ltrace}[1]{\ensuremath{\langle {#1}\rangle_c}}

\title{Domains and Event Structures for Fusions}
\author{\IEEEauthorblockN{Paolo Baldan}\IEEEauthorblockA{University of Padova}\IEEEauthorblockN{Andrea Corradini, Fabio Gadducci}\IEEEauthorblockA{University of Pisa}}

\begin{document}

\maketitle

\begin{abstract}
  Stable event structures, and their duality with prime algebraic domains
  arising as partial orders of configurations, are a landmark
  of concurrency theory, providing a clear characterisation of
  causality in computations.
  % 
  They have been used for defining a concurrent semantics of several
  formalisms, from Petri nets to (linear) graph rewriting systems,
  which in turn lay at the basis of many visual modelling frameworks.
  % 
  Stability however is restrictive when dealing with formalisms
  with ``fusion'', i.e., where a computational step can not only consume
  and produce but also merge parts of the state. This happens, e.g.,
  for graph rewriting systems with non-linear rules, which are needed
  to cover some relevant applications (such as the graphical encoding
  of calculi with name passing).
  %
  Guided by the need of capturing the semantics of formalisms with
  fusion we leave aside stability and we characterise, as a natural
  generalisation of prime algebraic domains, a class of domains,
  referred to as weak prime domains.
  %
  % We characterise, as a natural generalisation of prime algebraic
  % domains, a class of domains {(called weak-prime)} that is
  % well-suited to model the semantics of formalisms with fusions.
  %, whose definition relies on a weakened notion of primality.  
  We then identify a corresponding class of event structures, that we call 
  connected event structures, via a duality result formalised as an equivalence
  of categories.
  %
  We show that connected event structures are exactly the class of
  event structures that arise as the semantics of non-linear graph
  rewriting systems.
  % 
  Interestingly, the category of general unstable event structures
  coreflects into our category of {weak prime} domains, so that our
  result provides a characterisation of the partial orders of
  configurations of such event structures.

  \begin{IEEEkeywords}
    Event structures, fusions, graph rewriting, process calculi.
  \end{IEEEkeywords}
\end{abstract}

\section{Introduction}

For a long time stable/prime event structures and their duality with
prime algebraic domains have been considered one of the landmarks of
concurrency theory, providing a clear characterisation of causality in
software systems. They have been used to provide a concurrent
semantics to a wide range of foundational formalisms, from Petri
nets~\cite{NPW:PNES} to linear graph rewriting
systems~\cite{Handbook,Bal:PhD,Sch:RRSG} and process
calculi~\cite{Win:ESSCCS,VY:TESLP,BMM:ESSNC}. They are one of the
standard tools for the formal treatment of (true, i.e.,
non-interleaving) concurrency. See, e.g.,~\cite{Winskel11} for a
reasoned survey on the use of such causal models. Recently, they have
been used in the study of concurrency in weak memory
models~\cite{PS:CSRA,JR:OTRES,CV:GTARES} and for process mining and
differencing~\cite{DG:PMRES}.

In order to endow a chosen formalism with an event structure
semantics, a standard construction consists in viewing the class of
computations as a partial order. An element of the order is some sort
of configuration, i.e., an execution trace up to an equivalence that
identifies traces differing only for the order of independent steps
(e.g., interchange law~\cite{Mes92} in term rewriting, shift
equivalence~\cite{CMREHL:AAGT} in graph rewriting or permutation
equivalence~\cite{JJL80} in $\lambda$-calculus),
% and thus which should be indistinguishable when interpreted as
%concurrent computations
and the order relates two computations when
the latter is an extension of the former.
%
Events are then identified with configurations consisting
of a maximal computation step (e.g., a transition of a CCS process or
a firing for a Petri net) with all its causes.
%
As a simple example, consider the CCS process $a.c \mid b$. 
The corresponding transition system is depicted in Fig.~\ref{fi:ccs-ts}. We can identify the states of the computation with the sets of actions executed and obtain the partial order depicted in Fig.~\ref{fi:ccs-domain}.
%
The fact that each {computation step}  in a configuration has a uniquely determined
set of causes, a property that for event structures is called
\emph{stability}, allows one to characterise such elements, order
theoretically, as the prime elements: if they are included in a join
they must be included in one of the elements that are joined.
%
{For example}, in Fig.~\ref{fi:ccs-domain}, the events correspond to configurations $\{a\}$ (transition $a$ with
empty set of causes), $\{a,c\}$ (transition $c$ caused by $a$) and
$\{b\}$ (transition $b$ with empty set of causes).
%
Each element of the partial order of configurations can be
reconstructed uniquely as the join of the primes under it, so that the partial
order is prime algebraic.
%
This duality between event structures and domains of configurations 
can be nicely formalised in terms of an equivalence between the
categories of prime event structures and prime algebraic 
domains~\cite{NPW:PNES,Win:ES}.

\begin{figure}
  \subcaptionbox{
    \label{fi:ccs-ts}
  }{
    \begin{tikzpicture}[node distance=5mm, >=stealth',x=17mm,y=5mm]
      \node at (1,0) (s)  {$a.c \mid b$};
      \node at (0,1) (a)  {$c \mid b$};
      \node at (2,1) (c)  {$a.c \mid 0$};
      \node at (-1,2) (ab) {$0 \mid b$};
      \node at (1,2) (ac) {$c \mid 0$};
      \node at (0,3) (abc) {$0 \mid 0$};
      \draw [->] (s) -- (a);
      \draw [->] (s) -- (c);
      \draw [->] (a) -- (ab);
      \draw [->] (a) -- (ac);
      \draw [->] (c) -- (ac);
      \draw [->] (ab) -- (abc);
      \draw [->] (ac) -- (abc);
    \end{tikzpicture}
  }
  \subcaptionbox{
    \label{fi:ccs-domain}
  }{
    \begin{tikzpicture}[node distance=5mm, >=stealth',x=17mm,y=5mm]
      \node at (1,0) (s)  {$\emptyset$};
      \node at (0,1) (a)  {$\{a\}$};
      \node at (2,1) (c)  {$\{b\}$};
      \node at (-1,2) (ab) {$\{a,c\}$};
      \node at (1,2) (ac) {$\{a,b\}$};
      \node at (0,3) (abc) {$\{a,b,c\}$};
      \draw [->] (s) -- (a);
      \draw [->] (s) -- (c);
      \draw [->] (a) -- (ab);
      \draw [->] (a) -- (ac);
      \draw [->] (c) -- (ac);
      \draw [->] (ab) -- (abc);
      \draw [->] (ac) -- (abc);
    \end{tikzpicture}
  }
  \caption{The (a) transition system and (b) domain of configurations
    of the process $a.c \mid b$.}
  \label{fi:ccs}
\end{figure}

The set up described so far fails when moving to formalisms where a
computational step can merge parts of the state. This happens, e.g.,
in nominal calculi where, as a result of name passing,
the received name is identified with a local one at the
receiver~\cite{CVY:ESSPE,Gad07} or in the modelling of bonding in biological/chemical processes~\cite{PUY:MBPE}.
%
Whenever we think of the state of the system as some kind of graph
with the dynamics described by graph rewriting, this means that rewriting rules
are non-linear (more precisely, in the jargon of the double pushout
approach~\cite{Ehr:TIAA}, left-linear but possibly not right-linear).
%
% These are indeed the kind of rules that arise in some
% encodings of process calculi~\cite{Gad07} or when modelling some
% biological processes~\cite{xxx}.
%
In general terms, the point is that, in the presence of fusions, the
same event can be enabled by different minimal sets of events, thus
preventing the identification of a proper notion of causality.

\begin{figure}[h!]
  \begin{center}
  \subcaptionbox{The start graph $G_s$ and the rules $p_y$ ($y \in \{ a, b\}$) and $p_c$.
    \label{fi:running-gg}
  }{
    %%% START GRAPH
    \begin{tikzpicture}[node distance=6mm, >=stealth',baseline=(current bounding box.center)]
      %
      \node at (0,0) [node, label=below:$c$] (nc) {} 
      edge [in=160, out=130, loop]  node [lab,above] {$\bar{b}$} ()
      edge [in=105, out=75, loop]  node [lab,above] {$\bar{a}$} ()
      edge [in=50, out=20, loop]  node [lab,above] {$\mathit{in}$} ();
      %
      \node at (1,0) [node, label=below:$\nu$] (nu) {} 
      edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
      % 
      \pgfBox
    \end{tikzpicture}
    %
    \
    \hfill
    \
    %
    %%% RULES 
    %
    % RULES Pa and Pb
    %
    \begin{tikzpicture}[node distance=3mm, baseline=(current bounding box.center)]
      \node (l) {
      \begin{tikzpicture}[node distance=8mm, >=stealth']
      %
      \node at (0,0) [node, label=below:$c$] (nc) {} 
      edge [in=105, out=75, loop]  node [lab,above] {$\bar{y}$} ();
      %
      \node at (.5,0) [node, label=below:$\nu$] (nu) {} 
      edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
      %
      \pgfBox
      \end{tikzpicture} 
    };
    \node  [right=of l] (r) {
      \begin{tikzpicture}[node distance=8mm, >=stealth']
        \node at (0,0) [node, label=below:${c,\nu}$] (nc) {} 
        edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
        % 
        \pgfBox
      \end{tikzpicture}
    };
    \path (l) edge[->] node[trans, above] {$p_y$} (r);
    \end{tikzpicture}
    %
    \
    \hfill
    \
    %
    %%% RULE Px    
    %
    \begin{tikzpicture}[node distance=3mm, baseline=(current bounding box.center)]
      \node (l) {
      \begin{tikzpicture}[node distance=8mm, >=stealth']
        \node at (0,0) [node, label=below:${c,\nu}$] (nc) {} 
        edge [in=160, out=130, loop]  node [lab,above] {$\mathit{in}$} ()
        edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
        %
        \pgfBox
      \end{tikzpicture} 
    };
    \node  [right=of l] (r) {
      \begin{tikzpicture}[node distance=8mm, >=stealth']
        \node at (0,0) [node, label=below:${c,\nu}$] (nc) {} 
        edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
        % 
        \pgfBox
      \end{tikzpicture}
    };
    \path (l) edge[->] node[trans, above] {$p_c$} (r);
  \end{tikzpicture}  
  }
  \end{center}
  %   
  %%%% REWRITES
  %
  \begin{center}
  \subcaptionbox{The possible rewrites.
    \label{fi:running-rewriting}
  }
  {
    \begin{tikzpicture}[node distance=5mm, >=stealth']
      \node (Gs) {$G_s$};
      %
      %
      % Ga
      %
      \node [yshift=1.2cm, right=of Gs] (Ga) {
        \begin{tikzpicture}[node distance=8mm, >=stealth']
          %           
          \node  [node, label=below:${c,v}$] (nc) {} 
          edge [in=160, out=130, loop]  node [lab,above] {$\bar{a}$} ()
          edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ()
          edge [in=50, out=20, loop]  node [lab,above] {$\mathit{in}$} ();
          % 
          \pgfBox
        \end{tikzpicture}
      };
      \node [lab, xshift=-2mm, yshift=4mm] at (Ga.west) {$G_a$};
      %
      %
      % Gb
      %
      \node [yshift=-1.2cm, right=of Gs] (Gb) {
        \begin{tikzpicture}[node distance=8mm, >=stealth']
          % 
          \node at (0,0) [node, label=below:${c,v}$] (nc) {} 
          edge [in=160, out=130, loop]  node [lab,above] {$\bar{b}$} ()
          edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ()
          edge [in=50, out=20, loop]  node [lab,above] {$\mathit{in}$} ();
          % 
          \pgfBox
        \end{tikzpicture}
      };
     \node [lab, xshift=-2mm, yshift=-4mm] at (Gb.west) {$G_b$};
     %
     %
     % Gab
     %
      \node [yshift=-1.2cm, right=of Ga] (Gab) {
        \begin{tikzpicture}[node distance=8mm, >=stealth']
          % 
          \node at (0,0) [node, label=below:${c,\nu}$] (nc) {} 
          edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ()
          edge [in=50, out=20, loop]  node [lab,above] {$\mathit{in}$} ();
          % 
          \pgfBox
        \end{tikzpicture}
      };
      \node [lab, xshift=-2mm, yshift=0mm] at (Gab.west) {{$G_{ab}$}};
%      \node [lab, xshift=2mm, yshift=-3mm] at (Gab.north east) {$G_{ab}$};
      %
      %
      % Gac
      %
      \node [yshift=1.2cm, right=of Gab] (Gac) {
        \begin{tikzpicture}[node distance=8mm, >=stealth']
          % 
          \node at (0,0) [node, label=below:${c,\nu}$] (nc) {} 
          edge [in=160, out=130, loop]  node [lab,above] {$\bar{a}$} ()
          edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
          % 
          \pgfBox
        \end{tikzpicture}
      };
      \node [lab, xshift=-2mm, yshift=4mm] at (Gac.west) {$G_{ac}$};
      %
      %
      % Gbc
      %
      \node [yshift=-1.2cm, right=of Gab] (Gbc) {
        \begin{tikzpicture}[node distance=8mm, >=stealth']
          % 
          \node at (0,0) [node, label=below:${c,\nu}$] (nc) {} 
          edge [in=160, out=130, loop]  node [lab,above] {$\bar{b}$} ()
          edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
          % 
          \pgfBox
        \end{tikzpicture}
      };
      \node [lab, xshift=-2mm, yshift=-4mm] at (Gbc.west) {$G_{bc}$};
      %
      %
      % Gc
      %
      \node [yshift=-1.2cm, right=of Gac] (Gc) {
        \begin{tikzpicture}[node distance=8mm, >=stealth']
          %  
          \node at (0,0) [node, label=below:${c,\nu}$] (nc) {} 
          edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
          % 
          \pgfBox
        \end{tikzpicture}
      };
      \node [lab, xshift=0mm, yshift=2mm] at (Gc.north) {$G_{c}$};

      \path (Gs) edge [->] node[trans,pos=0.3,below] {$p_a$} (Gb)
                 edge [->] node[trans,pos=0.3,above] {$p_b$} (Ga);
      \path (Ga) edge [->] node[trans,pos=0.6,above] {$p_a$} (Gab) 
                 edge [->] node[trans,above] {$p_c$} (Gac);
      \path (Gb) edge [->] node[trans,below] {$p_b$} (Gab) 
                 edge [->] node[trans,below] {$p_c$} (Gbc);
      \path (Gab) edge[->] node[trans,pos=0.15,above] {$p_c$} (Gc);
      \path (Gac) edge[->] node[trans,above] {$p_a$} (Gc);
      \path (Gbc) edge[->] node[trans,below] {$p_b$} (Gc);
    \end{tikzpicture}
  }
  %
  \end{center}
  %
  %%% CONFIGURATIONS
  %  
  \begin{center}
  \subcaptionbox{The domain of configurations.
    \label{fi:running-configurations}
  }
  {  
    \begin{tikzpicture}[node distance=5mm, >=stealth',x=23mm,y=6mm]
      \node at (1,0) (Gs)  {$\emptyset$};
      \node at (0,1) (Ga)  {$\{a\}$};
      \node at (2,1) (Gb)  {$\{b\}$};
      \node at (1,2.1) (Gab) {$\{a,b\}$};
      \node at (0,2.7) (Gac)  {$\{a,c\}$};
      \node at (2,2.7) (Gbc)  {$\{b,c\}$};
      \node at (1,4) (Gc)  {$\{a,b,c\}$};
      \draw [->] (Gs) -- (Ga);
      \draw [->] (Gs) -- (Gb);
      \draw [->] (Ga) -- (Gab);
      \draw [->] (Gb) -- (Gab);
      \draw [->] (Ga) -- (Gac);
      \draw [->] (Gb) -- (Gbc);
      \draw [->] (Gac) -- (Gc);
      \draw [->] (Gbc) -- (Gc);
      \draw [->] (Gab) -- (Gc);
    \end{tikzpicture}
    % 
    }
  \end{center}
  \caption{A graph rewriting system with fusions.}
  \label{fi:running}
\end{figure}

\begin{figure}
{\begin{center}
{
    \begin{tikzpicture}[node distance=2mm, >=stealth']
       \node (Gs) {$(\nu c)(\bar{a}(c) \mid \bar{b}(c) \mid
c())$};
        \node [yshift=1.2cm, right=-9mm of Gs] (Ga) {$\bar{a}(c) \mid
c()$};
        \node [yshift=-1.2cm, right=-9mmof Gs] (Gb) {$\bar{b}(c) \mid
c()$};
 	\node [yshift=-1.2cm, right=of Ga] (Gab) {$c()$}; 
        \node [yshift=1.2cm, right=of Gab] (Gac) {$\bar{a}(c)$};      %
      \node [yshift=-1.2cm, right=of Gab] (Gbc) {$\bar{b}(c)$};      %
     \node [yshift=-1.2cm, right=of Gac] (Gc) {$0$};    
     %   
      \path (Gs) edge [->] node[trans,pos=0.1,below] {$\bar{a}(c)$} (Gb)
                 edge [->] node[trans,pos=0.1,above] {$\bar{b}(c)$} (Ga);
      \path (Ga) edge [->] node[trans,pos=0.7,xshift=0.2cm, above] {$\bar{a}(c)$} (Gab) 
                 edge [->] node[trans,above] {$c()$} (Gac);
      \path (Gb) edge [->] node[trans,pos=0.7, xshift=0.2cm, below] {$\bar{b}(c)$} (Gab) 
                 edge [->] node[trans,below] {$c()$} (Gbc);
      \path (Gab) edge[->] node[trans,pos=0.5,above] {$c()$} (Gc);
      \path (Gac) edge[->] node[trans,pos=0.7, xshift=0.2cm, above] {$\bar{a}(c)$} (Gc);
      \path (Gbc) edge[->] node[trans,pos=0.7, xshift=0.2cm, below] {$\bar{b}(c)$} (Gc);
    \end{tikzpicture}
  }
  %
  \end{center}
  }
\caption{The possible transitions of the $\pi$-calculus process $(\nu c)(\bar{a}(c) \mid \bar{b}(c) \mid c())$.}
  \label{fi:pi}
\end{figure}

As an example, consider the graph rewriting system in
Fig.~\ref{fi:running}.
%
The start graph $G_s$ and the rewriting rules $p_a$, $p_b$, and $p_c$
are reported in Fig.~\ref{fi:running-gg}.  Observe that rules $p_y$,
where $y$ can be either $a$ or $b$, delete edge $\bar{y}$ and merge
nodes $c$ and $\nu$. The possible rewrites are depicted in
Fig.~\ref{fi:running-rewriting}. For instance, applying $p_a$ to $G_s$
we get the graph $G_b$. Now, $p_b$ can still be applied to $G_b$
matching its left-hand side non-injectively, thus getting graph
$G_{ab}$. Similarly, we can apply first $p_b$ and then $p_a$,
obtaining again $G_{ab}$. Observe that at least one between $p_a$ 
and $p_b$ must be applied to enable $p_c$, since the latter rule requires 
nodes $c$ and $\nu$ to be merged.
%%
%The graph rewriting system is a (simplified) representation of the
%$\pi$-calculus process $(\nu c)(\bar{a}(c) \mid \bar{b}(c) \mid
%c())$. Rules $p_y$, for $y \in \{a,b\}$, represent the execution of
%$\bar{y}(c)$ that outputs on channel $y$ the restricted name $c$. The
%first rule that is executed extrudes name $c$, while the second is just a standard
%output. Only after the extrusion, the name $c$ is available outside
%the scope and the input prefix $c()$ can be consumed.
%
{Note also} that in a situation where all the three rules $p_a$, $p_b$, and
$p_c$ are applied, since $p_a$ and $p_b$ are independent,
it is not possible to define a proper notion of causality. We only
know that at least one between $p_a$ and $p_b$ must be applied  
before $p_c$.
%
The corresponding domain of configurations, reported in
Fig.~\ref{fi:running-configurations}, is naturally derived from the
possible rewrites in Fig.~\ref{fi:running-rewriting}. 
% AC: Tolto, discusso bene piu' avanti. 
%{It is easy to check that 
%this domain is not prime because, for example, element $\{a,c\}$ is not prime (it is included in the join of $\{a,b\}$ and $\{b,c\}$, but it is not included in either of the two) and thus it is not equal to the join of the primes under it.} 
%Observe, that for later reference we denoted by $x$ the event corresponding to the application of $p_x$ (for $x \in \{ a, b, c \}$).

The graph rewriting system of Fig.~\ref{fi:running-gg} is a (simplified) representation of the
$\pi$-calculus process $(\nu c)(\bar{a}(c) \mid \bar{b}(c) \mid
c())$. Rules $p_y$, for $y \in \{a,b\}$, represent the execution of
$\bar{y}(c)$ that outputs on channel $y$ the restricted name $c$. The
first rule that is executed extrudes name $c$, while the second is just a standard
output. The name $c$ is available outside the scope only after the extrusion, and 
after that the input prefix $c()$ can be consumed. {Figure~\ref{fi:pi} shows the possible transitions of the process, which correspond one-to-one to the possible rewrites of  Fig.~\ref{fi:running-rewriting}.}

The impossibility of modelling these situations with stable
event structures 
% with binary causality 
is well-known (see,
e.g.,~\cite{Win:ES} for a general discussion,~\cite{Handbook} for
graph rewriting systems or~\cite{CVY:ESSPE} for the $\pi$-calculus). One has
to drop the stability requirement and replace causality
by an enabling relation $\vdash$. More precisely, in the specific case 
we would have
$\emptyset \vdash a$, $\emptyset \vdash b$, $\{ a \} \vdash c$,
$\{ b \} \vdash c$.

% In these situations, sequential independence can still be defined as
% for linear rules, but it does not induce a ``traditional'' notion of
% causality in the sense that causality is not captured by a partial
% order.

\medskip

The questions that we try to answer is: what can be retained of the
duality between events structures and domains, when 
dealing with formalisms with fusions? Which are the properties of 
the domain of computations that arise in this setting? What are the 
event structure counterparts?

The domain of configurations of the example suggests that in this
context an event is still a computation that cannot be decomposed
as the join of other computations. Hence, in order theoretical terms,
it is an irreducible.
%
However, % in absence of fusions, stability ensures that an event in a
% configuration has a uniquely determined history, hence if
% $i \sqsubseteq \bigsqcup_j x_j$, then $i \sqsubseteq x_j$ for some
% $j$, namely $i$ is a prime. In words, if $i$ is included in the join
% of some configurations, it must be included in one of the components.
%
% Instead,
due to unstability, irreducibles are not {necessarily} primes: two different
irreducibles can {represent the same computation step with different minimal enablings}, 
%be different minimal enablings of the same event, 
in
a way that an irreducible can be included in a computation that is the
join of two computations without being included in any of the two. For
instance, in the example above, $\{ a, c \}$ is an irreducible,
corresponding to the execution of $c$ enabled by $a$, and it is
included in $\{ a \} \sqcup \{ b, c \} = \{ a, b , c \}$,
%i.e., $\{ p_a, p_c \} \subseteq \{ p_a, p_b , p_c \}$, 
although neither
$\{ a, c \} \subseteq \{ a \}$ nor
$\{ a, c \} \subseteq \{ b , c \}$.
%
Uniqueness of decomposition of an element in terms of (downward closed sets of) irreducibles
also fails, e.g.,
$\{a,b,c\} = \{a\} \sqcup \{b\} \sqcup \{a,c\} = \{a\} \sqcup \{b\} \sqcup
\{b,c\}$: the irreducibles $\{a,c\}$ and $\{b,c\}$ can be used
interchangeably in the decomposition of $\{a,b,c\}$.

Building on the previous observation, we introduce an equivalence on irreducibles
identifying those that can be used interchangeably in the
decompositions of an element (intuitively, different minimal enablings
of the same {computation step}). This is used to define a weaker notion of primality
(up to interchangeability) that allows us to characterise the class of domains
suited for modelling the semantics of formalisms with fusions {as}
the class of weak prime algebraic domains.

Given a weak prime algebraic domain, a corresponding event structure
can be obtained by taking as events the set of irreducibles,
quotiented under the (transitive closure of the) interchangeability
relation. The resulting class of event structures is a (mild)
restriction of the general event structures in~\cite{Win:ES}
that we call connected event structures. Categorically, we get an
equivalence between the category of weak prime algebraic domains and
the one of connected event structures, generalising the equivalence
between prime algebraic domains and prime event structures.

We also show that, in the same way as prime algebraic domains/prime
event structures are exactly what is needed for Petri nets/linear graph 
rewriting systems, weak prime
algebraic domains/connected event structures are exactly what is needed
for non-linear graph rewriting systems: each rewriting system maps to
a connected event structure and conversely each connected event structure
arises as the semantics of some rewriting system. This supports the
adequateness of weak prime algebraic domains and connected event
structures as semantics structures for formalisms with fusions.

Interestingly, we can also show that the category of general
event structures~\cite{Win:ES} coreflects into our category of weak
prime algebraic domains. Therefore our notion of weak prime algebraic
domain can be seen as a novel characterisation of the partial order of
configurations of such event structures that is alternative to those
based on intervals in~\cite{Winskel:phd,Dro:ESD}.  It represents a
natural generalisation of the one for prime event structures, with
irreducibles (instead of primes) having a tight connection with
events. The correspondence is established, at a categorical level, as a
coreflection of categories:
%something that, 
to the best of our knowledge, this {has} not been done before in the literature.

As mentioned above, weak prime domains, corresponding to possibly
unstable event structures, satisfy the same conditions as prime
domains, corresponding to stable event structures, up to an
equivalence on irreducibles. This suggests the possibility of viewing
unstable event structures as stable ones up to an equivalence on
events.
%
We show how this can be formalised  with a set up closely
related to the framework of prime event structures with equivalence 
recently devised in~\cite{win2017,VismeW19}.
% , further establishing a correspondence between unstable event
% structures and stable ones with equivalence.

Event structures and their domains have been also studied in relation
with automata with concurrency~\cite{Dro:CAD,DK:ACRS}, 
a form of automata endowed with a concurrency relation on transitions 
(local to each state).
%
On a similar line, the transition graphs of prime event structures
have been given a characterisation in terms of local axioms
in~\cite{PU:RMC}, answering a question posed in~\cite{SNW:MFCTC}.
%
Recently, in connection with the abstract theory of rewriting and
concurrent games, a slightly different but equivalent characterisation
has been rediscovered in~\cite{Mel:hab}, where prime event structures
are shown to correspond exactly to a suitable class of
asynchronous graphs.
%
Roughly, an asynchronous graph is a transition system where some
squares are declared to commute, meaning that the coinitial edges of
the square are concurrent and each one can follow the
other. Asynchronous graphs correspond to prime event structures that
satisfy the cube axiom, consisting of two parts: the forward
and the backward cube axioms, the latter often referred to as the
stability axiom. We show that asynchronous graphs that verify only the
forward part of the cube axiom are exactly the transition systems of
weak prime domains.

The rest of the paper is structured as follows. In
Section~\ref{se:background} we recall the basics of (prime) event
structures and their correspondence with prime algebraic domains.  In
Section~\ref{se:fes} we introduce weak prime algebraic domains and
connected event structures, and we characterise their relation
categorically.  
% In Section~\ref{ss:pes-equiv} we present a characterisation of our
% proposal in terms of a formalism reminiscent of prime event
% structures with equivalence.
%
In Section~\ref{se:characterisations}
we present a characterisation of our proposal 
in terms of a formalism reminiscent of prime event structures with equivalence of~\cite{win2017,VismeW19}.
% 
We also discuss and formalise the relation of our work with alternative  characterisations of the domains of event structures  based on intervals and on asynchronous graphs. 
%
In Section~\ref{se:graphs} we show the intimate connection between
weak prime algebraic domains (or equivalently, connected event
structures) and non-linear graph rewriting systems.
%
Finally, in Section~\ref{se:conc} we wrap up the main contributions of
the paper and we sketch further advances and some connections with
related works.

The paper is rounded up with an appendix extending our characterisation results
to event structures with non-binary conflict~\cite{Dro:ESD}. We also discuss the relation with a  proposal based on labelled event structures for
modelling the concurrent computations of name passing process
calculi~\cite{CVY:ESSPE}.

This is a revised and extended  version of the conference paper~\cite{BCG:DESF}.

\section{Background: Domains and Event Structures}
\label{se:background}

In this section we review the basics of event structures, as introduced
in~\cite{Win:ES}, and their duality with partial orders.

\subsection{Event Structures}
\label{ss:es}

For the sake of presentation, 
we focus on event structures with binary conflict.
%
Most results can be easily rephrased for event structures with
non-binary conflict expressed by means of a consistency predicate
(This is explicitly discussed in Appendix~\ref{app:consistency}).
%
Given a set $X$ we denote by
$\Pow{X}$ and $\Powfin{X}$ the powerset and the set of finite subsets
of $X$, respectively. For $m,n \in \mathbb{N}$, we denote by
$\interval[m]{n}$ the set $\{ m, m+1, \ldots, n\}$.

\begin{definition}[event structure]
  \label{de:es}
  An \emph{event structure} ({\esabbr} for short) is a tuple
  $\langle E, \vdash, \# \rangle$ such that
  \begin{itemize}
  \item $E$ is a set of events;
  \item ${\vdash} \subseteq \Powfin{E} \times E$ is the \emph{enabling}
    relation, satisfying $X \vdash e$ and $X \subseteq Y$
    implies $Y \vdash e$;
  \item $\# \subseteq E \times E$ is the conflict relation.
  \end{itemize}
  A subset $X \subseteq E$ is \emph{consistent} if $\neg (e \# e')$
  for all $e, e' \in X$.
  %The event structure $\mathsf{E}$ is \emph{stable}
  %if whenever $X\vdash e$, $Y \vdash e$, and $X \cup Y \cup \{e\}$ is
  %consistent then $X \cap Y \vdash e$.
  %\marginpar{old story :-)}
\end{definition}

An {\esabbr} $\langle E, \vdash, \# \rangle$ is often
denoted simply by $E$.  Computations are captured by the notion of
configuration.

\begin{definition}[configuration, live {event structure}]
  Let $\langle E, \vdash, \# \rangle$ be an {\esabbr}. A
  \emph{configuration} of $E$ is a consistent subset $C \subseteq E$
  that is \emph{secured}, i.e., such that for all $e \in C$ there are
  $e_1, \ldots, e_n \in C$ with $e_n =e$ such that
  $\{ e_1, \ldots, e_{k-1} \} \vdash e_k$ for all $k \in \interval{n}$
  (in particular, $\emptyset \vdash e_1$). The set of configurations
  of an {\esabbr} $E$ is denoted by $\conf{E}$ and the subset of
  \emph{finite} configurations by $\conff{E}$.
  %
  % An {\esabbr} is \emph{live} if conflict is irreflexive (i.e., for
  % all $e \in E$ we have $\neg (e \# e)$) and \emph{saturated}, i.e.,
  % for all $e, e' \in E$, if there is no $C \in \conf{E}$ such that
  % $\{e,e'\} \subseteq C$ then $e \# e'$.
  % 
  % 
  An {\esabbr} is \emph{live} if conflict is 
 \emph{saturated}, i.e., for all
  $e, e' \in E$, if there is no $C \in \conf{E}$ such that
  $\{e,e'\} \subseteq C$ then $e \# e'$, and moreover
  for all $e \in E$ it holds $\neg (e \# e)$.
\end{definition}

\begin{remark}
  In live {\esabbr}, the fact that conflict is saturated corresponds
  to inheritance of conflict in prime event structures. Moreover, the
  absence of self-conflicts implies that each event appears in some
  configuration (intuitively, it is executable). In the rest of the
  paper, we restrict to live {\esabbr}, hence the qualification
  ``live'' is omitted.
\end{remark}

In this setting, two events are \emph{concurrent} when they are consistent
and enabled by the same configuration.

Since the enabling predicate is over finite sets of events, we can
consider minimal sets of events enabling a given one.

\begin{definition}[minimal enabling]
  \label{de:minimimal-enabling}
  Let $\langle E, \vdash, \# \rangle$ be an {\esabbr}. Given a
  configuration $C \in \conf{{E}}$ and an event $e \in E$ we write
  $C \vdash_0 e$ and call it a \emph{minimal enabling} for $e$, when
  $C \cup \{ e \} \in \conf{E}$ (hence $C \cup \{ e \}$ consistent and
  $C \vdash e$), and for any other configuration $C' \subseteq C$, if
  $C' \vdash e$ then $C' = C$.
\end{definition}

The classes of stable and prime {\esabbr} represent our starting point and 
play an important role in the paper.

\begin{definition}[stable and prime {event structures}]
  \label{de:stable-prime-es}
  An {\esabbr} $\langle E, \vdash, \# \rangle$ is \emph{stable}
  if $X\vdash e$, $Y \vdash e$, and $X \cup Y \cup \{e\}$ consistent
  imply $X \cap Y \vdash e$.  It is \emph{prime} if $X\vdash e$ and
  $Y \vdash e$ imply $X \cap Y \vdash e$.
\end{definition}
%\marginpar{detto prima}

For stable {\esabbr}, given a configuration $C$ and an event $e \in C$,
there is a unique minimal configuration $C' \subseteq C$ such that
$C' \vdash_0 e$.  The set $C'$ can be seen as the set of causes of
the event $e$ in the configuration $C$. This gives a well-defined notion of
causality that is local to each configuration. In a prime {\esabbr}, for any event $e$
there is a unique minimal enabling $C \vdash_0 e$, thus providing a
global notion of causality.
%
In general, in possibly unstable {\esabbr}, due to the presence of consistent
\emph{or-enablings}, there might be distinct minimal enablings in the
same configuration.

\begin{example}
  \label{ex:event-structure}
  A simple example of unstable {\esabbr} is the one associated with
  the running example discussed in the introduction (see
  Fig.~\ref{fi:running}). The set of events is $\{ a, b, c \}$, the
  conflict relation $\#$ is the empty one and the minimal enablings
  are $\emptyset \vdash_0 a$, $\emptyset \vdash_0 b$,
  $\{ a\} \vdash_0 c$, and $\{ b\} \vdash_0 c$. Thus, event $c$ has
  two minimal enablings and these are consistent, hence
  $ \{ a, b \} \vdash c$.  The corresponding configurations are
  reported in Fig.~\ref{fi:running-configurations}.
\end{example}

The class of {\esabbr} can be turned into a category.

\begin{definition}[category of {event structures}]
  \label{de:es-morphism}
  A morphism of {\esabbr} $f : {E}_1 \to {E}_2$
  is a partial function $f : E_1 \to E_2$ such that for all
  $C_1 \in \conf{E_1}$ and $e_1, e_1' \in E_1$ with $f(e_1)$, $f(e_1')$ defined
  \begin{itemize}
  \item if $f(e_1) \# f(e_1')$ then $e_1 \# e_1'$;
  \item if $f(e_1) = f(e_1')$ then  $e_1 = e_1'$ or $e_1 \# e_1'$;
  \item if $C_1 \vdash_1 e_1$ then $f(C_1) \vdash_2 f(e_1)$.
  \end{itemize}
  We denote by $\es$ the category of {\esabbr} and their
  morphisms and by $\ses$ and $\pes$, respectively, the full subcategories of stable and prime {\esabbr}.
\end{definition}

\subsection{Domains}
\label{ss:domains}

A preordered or partially ordered set $\langle D, \sqsubseteq \rangle$
is often denoted simply as $D$, omitting the (pre)order
relation.  We denote by
$\preceq$ the immediate predecessor relation, i.e., for $x, y \in D$, 
we write $x \preceq y$ whenever
$x \sqsubseteq y$ and for all $z \in D$ if
$x \sqsubseteq z \sqsubseteq y$ then $z \in \{x,y\}$.
%
A subset $X \subseteq D$ is \emph{consistent}
if it has an upper bound $d \in D$  (i.e., $x \sqsubseteq d$ for all $x \in X$),
while it is \emph{pairwise consistent} if
every two elements subset 
of $X$ is consistent.
%
A subset $X \subseteq D$ is \emph{directed} if $X \neq \emptyset$ and
every pair of elements in $X$ has an upper bound in $X$. We say that
$D$ is \emph{complete} if every directed subset has a least upper
bound in $D$.

A subset $X \subseteq D$ is an \emph{ideal} if it is directed and
downward closed.
%
Given an element $x \in D$, we write $\principal{x}$ to
denote the \emph{principal ideal} $\{ y \in D \mid y \sqsubseteq x \}$ generated by $x$.
Given a partial order $D$, its \emph{ideal completion}, denoted by $\ideal{D}$, is the
set of ideals of $D$,  ordered by subset inclusion.
%Observe that any directed set is also finitely
%consistent.
%
The \emph{least upper bound} and the \emph{greatest lower bound} of a
subset $X \subseteq D$ (if they exist) are denoted by $\bigsqcup X$
and $\bigsqcap X$, respectively.

\begin{definition}[domains]
  \label{c-de:domain}
  A partial order $D$ is \emph{coherent} if for all
  pairwise  consistent $X \subseteq D$ the least
  upper bound $\bigsqcup X$ exists. 
  %
  An element $d \in D$ is \emph{compact} if for all directed
  $X \subseteq D$, $d \sqsubseteq \bigsqcup X$ implies
  $d \sqsubseteq x$ for some $x \in X$. The set of compact
  elements of $D$ is denoted by $\compact{D}$.
  % 
  A coherent partial order $D$ is \emph{algebraic}
  % \emph{$\omega$-algebraic} if $\compact{D}$ is denumerable and 
  if for every $x \in D$ we have
  $x = \bigsqcup (\principal{x} \cap \compact{D})$.  We say that $D$
  is \emph{finitary} if for every element $a \in \compact{D}$ the set
  $\principal{a}$ is finite.
  %
  We refer to 
  % $\omega$-
  algebraic finitary coherent partially ordered sets as
  \emph{domains}.
\end{definition}

Note that every domain has a bottom element (indeed $\bot = \bigsqcup \emptyset$), and that
in a domain all non-empty subsets have a meet. In fact, if
$\emptyset \neq X \subseteq D$, then $\bigsqcap X = \bigsqcup L(X)$
where $L(X) = \{ y \mid \forall x \in X.\, y \sqsubseteq x\}$ is the
set of lowerbounds of $X$, which is pairwise consistent since it is
dominated by any $x \in X$. And it is easy to see that finite joins of 
compact elements are compact.
%\todo{PB: Non lo inserirei, ma ecco l'argomento: $x, y \in \compact{D}$ and $Z$ directed and  $x \sqcup y \sqsubseteq \bigsqcup Z$ then $x \sqsubseteq \bigsqcup Z$, hence $x \sqsubseteq z_x$ for some $z_x \in Z$. For similar reasons $y \sqsubseteq z_y$ for some $z_y \in Z$. Since $Z$ is directed there is $z \in Z$ such that $z_x, z_y \sqsubseteq Z$, hence $x \sqcup x \sqsubseteq z$.}

For a domain $D$ we can think of its elements as ``pieces of
information'' expressing the states of evolution of a process. Compact
elements represent states that are reached after a finite number of
steps.  Thus algebraicity essentially says that infinite
computations can be approximated with arbitrary precision by finite
ones. More formally, when $D$ is algebraic, it is determined by
$\compact{D}$, i.e., $D \simeq \ideal{\compact{D}}$.

For an {\esabbr}, the configurations ordered by subset inclusion form
a domain. When the {\esabbr} is stable, if a minimal
enabling is included in the join of different configurations, then it is necessarily included in one of the configurations. In
order-theoretic terms, minimal enablings are prime elements, and thus
they represent the building blocks of computations.

\begin{definition}[primes and prime algebraicity] Let $D$ be a domain.
  A \emph{complete prime} is an element $p \in D$
  % \compact{D}$ %$p \neq \bot$, such
  such that for any pairwise consistent $X \subseteq D$, if
  $p \sqsubseteq \bigsqcup X$ then $p \sqsubseteq x$ for some
  $x \in X$.
  % 
  The set of complete prime elements of $D$ is denoted by $\pr{D}$. 
  % , the set %
  % $\principal{d} \cap \pr{D}$ of primes of $D$ below $d$ is denoted
  % $\pr{d}$.
  %
  The domain $D$ is \emph{prime algebraic} (or simply \emph{prime}) 
  if for all $x \in D$ we have
  $x = \bigsqcup (\principal{x} \cap \pr{D})$.
\end{definition}

Prime domains can be also characterised as coherent finitary distributive complete partial orders~\cite{Win:ES}.
%
Note that complete primes are compact (since each directed set is pairwise
consistent). Since we will only use complete primes, the qualification ``complete'' will be omitted.

Prime domains are the domain
theoretical counterpart of stable and prime {\esabbr}.
%
For a stable {\esabbr} $\langle E, \#, \vdash \rangle$, the
partial order $\langle \conf{{E}}, \subseteq \rangle$ is
a prime  domain, denoted $\pdom{{E}}$. Conversely,
given a prime  domain $D$, the triple
$\langle \pr{D}, \#, \vdash \rangle$, where $p \# p'$ if $\{ p, p' \}$
is not consistent and $X \vdash p$ when
$(\principal{p} \cap \pr{D}) \setminus \{ p \} \subseteq X$,
%$\{ p' \in \pr{D} \mid p' \sqsubseteq p \} \subseteq X$ 
is a prime {\esabbr}, denoted $\sev{D}$.

This correspondence can be elegantly formulated at the categorical
level~\cite{Win:ES}.
%
We recall the notion of domain morphism.

\begin{definition}[category of prime domains]
  \label{de:pdomain-category}
  Let $D_1$, $D_2$ be prime domains. A morphism
  $f : D_1 \to D_2$ is a total function such that
  for all consistent $X_1 \subseteq D_1$ and
  $d_1, d_1' \in D_1$
  \begin{enumerate}
  \item if $d_1 \preceq d_1'$ then $f(d_1) \preceq f(d_1')$;
  \item $f(\bigsqcup X_1) = \bigsqcup f(X_1)$;
  \item if $X_1 \neq \emptyset$ then
    $f(\bigsqcap X_1) = \bigsqcap f(X_1)$;
  \end{enumerate}
  %
  We denote by $\PDom$ the category of prime domains and
  their morphisms.
\end{definition}

The correspondence is then captured by the result below.

\begin{theorem}[duality]
  \label{th:duality}
  There are functors $\ppdom : \ses \to \PDom$ and
  $\zsev : \PDom \to \ses$ establishing a coreflection. It restricts
  to an equivalence of categories between $\PDom$ and $\pes$.
\end{theorem}

\section{Weak Prime Domains and Connected Event Structures}
\label{se:fes}

In this section we show that, relaxing the stability assumption, we
can generalise the duality result described in the previous
section, linking suitably defined classes of domains and 
{\esabbr}. These can be proven to properly capture the
semantics of computational formalisms with fusions.

\subsection{Weak Prime Algebraic Domains}
\label{ss:weakdomains}

We show that domains arising in absence of stability can be
characterised by resorting to a weakened notion of prime element. 
We start recalling the notion of irreducible element.

\begin{definition}[irreducibles]
  Let $D$ be a domain. A \emph{complete irreducible} of $D$ is an
  element $x \in D$ such that, for any pairwise consistent
  $X \subseteq D$, if $x = \bigsqcup X$ then $x \in X$.  The set of
  complete irreducibles of $D$ is denoted by $\ir{D}$ and, for
  $d \in D$, we define $\ir{d} = \principal{d} \cap \ir{D}$.
\end{definition}

Observe that complete irreducibles in a domain are compact. In fact,
if $i$ is a complete irreducible, by algebraicity,
$i = \bigsqcup \principal{i} \cap \compact{D}$ whence
$i \in \principal{i} \cap \compact{D}$. Conversely, we have the following.

\begin{lemma}[irreducibility and compactness]
  \label{le:comp-irr}
  Let $D$ be a domain. If $d \in \compact{D}$ then $d$ is a complete
  irreducible iff for all $x, y \in D$, consistent,
  $d = x \sqcup y$ implies $d = x$ or $d=y$.
\end{lemma}

\begin{proof}
  Let $d \in \compact{D}$. Assume that for all $x, y \in D$, consistent,
  $d = x \sqcup y$ implies $d = x$ or $d=y$.
  %
  Assume that $d = \bigsqcup X$ for some pairwise consistent $X$. It
  is easy to see that $X' = \{ \bigsqcup Y \mid Y \in \Powfin{X} \}$
  is directed and {moreover} $\bigsqcup X' = \bigsqcup X = d$. Since $d$
  is compact, there is $x' \in X'$ such that $d \sqsubseteq x'$, hence
  $d = x'$. By definition of $X'$, this means that there exists
  $Y \in \Powfin{X}$ such that $d = \bigsqcup Y$. {Now, using the hypothesis,
  an inductive reasoning} allows us to conclude that
  $d \in Y \subseteq X$, as desired.

  The converse implication is trivial: if $d \in \ir{D}$ and
  $d \sqsubseteq x \sqcup y$ then, by definition of complete
  irreducible, $d \in \{x,y\}$, i.e., either $d=x$ or $d=y$, as
  desired.
\end{proof}

Since in this paper we will refer only to complete irreducibles, the qualification ``complete'' will be omitted.

%Note that $\bot$ is not irreducible (since
%$\bot = \bigsqcup \emptyset$) while any prime is.

Irreducibles in domains have a simple characterisation.

\begin{lemma}[unique predecessor for irreducibles]
  \label{le:unique-pred}
  Let $D$ be a domain and $i \in D$. Then $i \in \ir{D}$ 
  iff it has a unique immediate predecessor.
\end{lemma}

\begin{proof}
  Assume that $i \in D$ has a unique immediate predecessor
  $d \prec i$, and let $X \subseteq D$ be pairwise consistent and
  such that $ i = \bigsqcup X$. Hence for any $x \in X$ we have
  $x \sqsubseteq i$. Assume by contradiction that $i \not\in X$. This
  implies that for all elements $x \in X$ we have $x \sqsubseteq d$, and therefore
  $i= \bigsqcup X \sqsubseteq d \prec i$, which is a contradiction.
  Hence it must be $i \in X$, which means that $i$ is irreducible.

  Vice versa, let $i$ be irreducible and let $d_1, d_2 \prec i$ be
  immediate predecessors. Since $D$ is a domain and $\{ d_1, d_2 \}$
  is consistent, we can take $d = d_1 \sqcup d_2$ and we know
  $d_1 \sqsubseteq  d \sqsubseteq i$. Since $i$ is irreducible it cannot be
  $d = i$, therefore $d = d_1$ and thus $d_1 = d_2$. Thus we conclude that
  $i$ has a unique immediate predecessor.
\end{proof}

The unique predecessor of an irreducible will play an important role, hence we introduce a notation.

\begin{definition}[immediate predecessor]
  Let $D$ be a domain and $i \in \ir{D}$. We denote by $\pred{i}$ the
  (unique) immediate predecessor of $i$.
\end{definition}

We next observe that any domain is actually irreducible algebraic, namely it can be generated by the irreducibles.

\begin{proposition}[domains are irreducible algebraic]
  \label{pr:domains-irr-alg}
  Let $D$ be a domain. Then for any $d \in D$ it holds
  $d = \bigsqcup \ir{d}$.
  % $x = \bigsqcup (\principal{x} \cap \ir{D})$.
\end{proposition}

\begin{proof}
  We first prove that for any compact element $d \in \compact{D}$ it
  holds that $d = \bigsqcup (\principal{d} \cap \ir{D})$. 
  %
  The thesis then immediately follows from algebraicity of $D$. Since
  $D$ is a domain, $\principal{d}$ is finite, hence we can proceed by
  induction on $|\principal{d}|$. When $|\principal{d}| = 1$, we have
  that $d = \bot$, hence $\principal{d} \cap \ir{D} = \emptyset$ and
  indeed $\bot = \bigsqcup \emptyset$. When $|\principal{d}| = k > 1$
  consider the immediate predecessors of $d$ and denote them
  $d_1, \ldots, d_n \prec d$. Since $D$ is a domain and
  $\{ d_1, \ldots, d_n \}$ is consistent, there exists
  $\bigsqcup \{ d_1, \ldots, d_n \} = d'$ and
  $d_i \sqsubseteq d' \sqsubseteq d$. There are two cases
  \begin{itemize}
  \item $d' = d_i$, for all $i \in \interval{n}$,
    i.e., $d$ has a unique immediate predecessor, hence it is an
    irreducible and thus clearly $d = \bigsqcup (\principal{d} \cap \ir{D})$ or
  \item $d = d' = \bigsqcup \{ d_1, \ldots, d_n \}$. Since, in turn,
    by inductive hypothesis $d_i = \bigsqcup (\principal{d_i} \cap \ir{D})$ 
    and $\principal{d} \cap \ir{D}= \bigcup_{i=1}^n (\principal{d_i} \cap \ir{D})$,
    we immediately get the thesis.
  \end{itemize}
\end{proof}

We next observe that every prime is an irreducible and, if $D$ is a
prime domain, then also the converse holds, i.e., irreducibles
coincide with primes.

\begin{proposition}[irreducibles vs. primes]
  \label{pr:irr-prime-alg}
  Let $D$ be a domain. Then $\pr{D} \subseteq \ir{D}$. Moreover, $D$ is a
  prime domain iff $\pr{D} = \ir{D}$.
\end{proposition}

\begin{proof}
  Let $D$ be a domain. We show that $\pr{D} \subseteq \ir{D}$. Let
  $d \in \pr{D}$. Assume that $d = \bigsqcup X$ for some pairwise
  consistent set $X$. By primality, since $d \sqsubseteq \bigsqcup X$
  there must be $x \in X$ such that $d \sqsubseteq x$. We have also
  $x \sqsubseteq \bigsqcup X = d$ and thus $d=x \in X$.

    \medskip

    For the second part, let us assume that $D$ is a prime domain. We have to prove that $\pr{D} = \ir{D}$. We already know that $\pr{D} \subseteq \ir{D}$.
  %
  For the converse inclusion, let $i \in \ir{D}$. By
  prime algebraicity $i =\bigsqcup (\principal{i} \cap
  \pr{D})$. Since $i$ is irreducible, there exists
  $p \in \principal{i} \cap \pr{D}$ such that $i = p$, hence $i$ is
  a prime.

  Vice versa, if $D$ is a domain, by Proposition~\ref{pr:domains-irr-alg} we
  know that $D$ is irreducible algebraic. Hence, if $\pr{D} = \ir{D}$,
  we immediately conclude that $D$ is prime.
\end{proof}

Quite intuitively, in the domain of configurations of an {\esabbr} the
irreducibles are minimal enablings of events. For instance, in the
domain depicted in Fig.~\ref{fi:running-configurations} the
irreducibles are $\{a\}$, $\{b\}$, $\{ a, c \}$, and $\{ b, c \}$.
%
For stable {\esabbr}, the domain is prime and thus, as observed
above, irreducibles coincide with primes. This fails in unstable {\esabbr},
as we can see in our running example: while $\{a\}$ and
$\{b\}$ are primes, the two minimal enablings of $c$, namely
$\{ a, c \}$ and $\{ b, c \}$, are not. In fact,
$\{ a, c \} \subseteq \{ a \} \sqcup \{ b, c\}$, but neither
$\{ a, c \} \subseteq \{ a \}$ nor $\{ a, c\} \subseteq \{ b, c\}$.

%  event structures, then
% the presence of an event $e$ in a configuration implies that the
% minimal enabling is included in the configuration. Therefore if $d$
% represents event $e$ with its minimal enabling, from
% $d \sqsubseteq \bigsqcup X$, i.e., if $d$ is in some computation
% arising as the join of some subcomputations, we deduce that it occurs
% in some subcomputation. Instead, in connected event structures, 
% An irreducible $d$ representing event $e$ with one of its possible
% enablings could occur even if $d$ is not in any subcomputation, but
% rather we find an element $d'$ corresponding to $e$ with a different
% minimal history. For instance, in
% Figure~\ref{fi:running-configurations}, we have
% $\{ b, c \} \subseteq \bigcup \{ \{ a, c\}, \{ b\} \}$.  As mentioned
% before, events with their minimal enablings are irreducibles, h
%
The key observation is that in general an event corresponds to a class of
irreducibles, like $\{ a,c\}$ and $\{ b, c\}$ in our
example. Additionally, two irreducibles corresponding to the same
event can be used, to a certain extent, interchangeably for building
the same configuration. For instance,
$\{ a, b, c \} = \{a, b \} \sqcup \{ a, c \} = \{a, b \} \sqcup \{ b, c
\}$.
%
We next formalise this intuition, i.e., we interpret
irreducibles in a domain as minimal enablings of some event and we
identify classes of irreducibles corresponding to the same event.

We start by observing that, in a prime domain, any element admits a unique decomposition in terms of downward closed sets of irreducibles (or, equivalently, of primes).

\begin{lemma}[unique decomposition in prime domains]
  \label{le:unique-decomposition}
  Let $D$ be a prime domain and let $X, X' \subseteq \ir{D}$ be
  downward closed sets of irreducibles.
  If $\bigsqcup X = \bigsqcup X'$ then $X=X'$.
\end{lemma}

\begin{proof}
  % 
  Let $X, X' \subseteq \ir{D}$ be downward closed sets of irreducibles
  such that $\bigsqcup X = \bigsqcup X'$.  Take any $i' \in X'$. Then
  $i' \sqsubseteq \bigsqcup X$. Since the domain is prime
  algebraic, and thus $i'$ is prime, there must exist $i \in X$ such
  that $i' \sqsubseteq i$ and thus $i' \in X$.  Therefore
  $X' \subseteq X$. By symmetry also the converse inclusion holds,
  whence equality.
\end{proof}

% introducing a notion of decomposition.

% \begin{definition}[decomposition]
%   Let $D$ be a domain and $x \in D$.  A \emph{decomposition} of
%   $x$ is a downward closed set $X \subseteq \ir{D}$ such that
%   $x = \bigsqcup X$.
%   %
%   % It is called \emph{minimal} if it is minimal w.r.t. subset
%   % inclusion.
% \end{definition}

The result above no longer holds in domains arising in the presence
of fusions.  For instance, in the domain in
Fig.~\ref{fi:running-configurations},
$X = \{ \{a\}, \{b\}, \{a,c\} \}$, $X'= \{ \{a\}, \{b\}, \{b,c\} \}$
and $X''= \{ \{a\}, \{b\}, \{b,c\}, \{a,c\} \}$ are all decompositions
for $\{a,b,c\}$.
%
The idea is to identify irreducibles
that can be used interchangeably in a decomposition.

% The interchangeability relation will be especially meaningful on
% irreducibles but it is convenient to define the notion on general
% compact elements.

\begin{definition}[interchangeability]
  \label{de:interchangeable}
  Let $D$ be a domain and $i, i' \in \ir{D}$. We write
  $i \leftrightarrow i'$ if $\{i, i'\}$ consistent and for all
  $X \subseteq \ir{D}$ such that $X \cup \{ i \}$ and
  $ X \cup \{ i' \}$ are downward closed and consistent we have
  $\bigsqcup (X \cup \{ i \}) = \bigsqcup (X \cup \{ i' \})$.
  % \ICrem{``and for some such $X$ it holds
  %   $\bigsqcup X \neq \bigsqcup (X \cup \{ i \})$.''}
\end{definition}

In words, $i \leftrightarrow i'$ means that $i$ and $i'$ produce the
same effect when added to a decomposition that already includes their
predecessors.
% \ICrem{``and there is at least one situation in which the addition
%   of $i$ and $i'$ produces some effect.''}
%
Hence, intuitively, $i$ and $i'$ correspond to the execution of the
same event with different and consistent enablings.

% \begin{remark}[internal note, just to remember]
%   One could think that equivalence on irreducibles could be defined as
%   $i \leftrightarrow i'$ iff there exists $d, d' \in D$, $d \prec d'$ such that
%   $d' = d \sqcup i = d \sqcup i'$.

%   Note that this is not the same: consider, e.g.,
%   \[
%     \xymatrix@R=3mm{
%       {} & {} & {d'} \ar@{-}[d] \ar@{-}[ddll] \ar@{-}[ddrr] & {} & {} \\
%       {} & {} & {d''} \ar@{-}[dl] \ar@{-}[dr] & {}  & {} \\
%       {i} \ar@{-}[drr] & {d} \ar@{-}[dr] & {} & {i''} \ar@{-}[dl] & {i'} \ar@{-}[dll] \\
%       {} &  {} & {\bot} & {} & {}
%     }
%   \]

% \end{remark}

%\ICrem{Clearly, interchangeable irreducibles need to be consistent.}

We first observe that distinct irreducibles related by the
interchangeability relation are necessarily incomparable.

\begin{lemma}[$\leftrightarrow$ vs $\sqsubseteq$]
  \label{le:inter-ord}
  Let $D$ be a domain and let $i, i' \in \ir{D}$.
  If $i \leftrightarrow i'$ and $i \sqsubseteq i'$ then $i=i'$.
\end{lemma}

\begin{proof}
  % The fist part is obvious, since by definition there must exist
  % $X \subseteq \ir{D}$ such that $X \cup \{ i \}$ and
  % $X \cup \{ i' \}$ downward closed, and
  % $\bigsqcup (X \cup \{ i \}) = \bigsqcup (X \cup \{ i'
  % \})$. Therefore
  % $i, i' \sqsubseteq \bigsqcup (X \cup \{ i \}) = \bigsqcup (X \cup \{
  % i' \})$ and thus $i, i'$ are consistent.

  % For the second part, 
  Let $i \leftrightarrow i'$ and $i \sqsubseteq i'$. 
  % Since $\{i, i'\}$ is consistent, $i \leftrightarrow i$. 
  If $i \neq i'$ and we let
  $X = \ir{\pred{i'}}$, it turns out that $X \cup \{i\} = X$ and
  $X \cup \{i'\}$ are consistent and downward closed. Moreover
  $\bigsqcup X \cup \{i\} = \bigsqcup X = \pred{i'} \neq \bigsqcup X
  \cup \{i'\} = i'$, contradicting $i \leftrightarrow i'$.
\end{proof}

We next give some characterisations of interchangeability.
% on irreducibles.

\begin{lemma}[characterising $\leftrightarrow$]
  \label{le:eq-char}
  Let $D$ be a domain and $i, i' \in \ir{D}$.  Then the
  following are equivalent
  \begin{enumerate}
  \item 
    \label{le:eq-char:1}
    $i \leftrightarrow i'$;

  % \item 
  %   \label{le:eq-char:2}
  %   for all $X \subseteq \ir{D}$ such that
  %   $X \cup \{ i \}$ and $ X \cup \{ i' \}$ are downward closed and
  %   consistent, $\bigsqcup (X \cup \{ i \}) = \bigsqcup (X \cup \{ i' \})$;

  \item 
    \label{le:eq-char:3}
    $\{i, i'\}$ consistent and for all $d \in \compact{D}$
    if $\pred{i}, \pred{i'} \sqsubseteq d$ then
    $d \sqcup i = d \sqcup i'$;
    % \ICrem{and for some such $d$ it holds
    % $d \neq  d \sqcup i$;}

  \item 
    \label{le:eq-char:4}
    $\{i, i'\}$ consistent and $i \sqcup \pred{i'} = \pred{i} \sqcup i'$.
  \end{enumerate}
\end{lemma}

\begin{proof}
  % (\ref{le:eq-char:1} $\leftrightarrow$ \ref{le:eq-char:2})
  % % 
  % The direction (\ref{le:eq-char:1} $\to$ \ref{le:eq-char:2}) follows
  % by observing that if $X \subseteq \ir{D}$ is a downward closed set
  % of irreducibles then also $\principal{X}$ is a downward closed set
  % of compact elements and it has the same sup. For the converse
  % (\ref{le:eq-char:2} $\to$ \ref{le:eq-char:1}), observe that dually
  % if $X \subseteq \compact{D}$ is a downward closed set of compacts
  % then also $X \cap \ir{D}$ is a downward closed set of irreducibles
  % and it has the same sup, since domains are irreducible algebraic
  % (Proposition~\ref{pr:domains-irr-alg}).

  % Additionally, we need to note that if $i \neq i'$ then $i, i'$ are
  % uncomparable. Assume by contradiction that $i \sqsubseteq i'$. Since
  % $i \neq i'$, necessarily $i \sqsubseteq \pred{i'}$. Hence, if we let
  % $Y = \ir{i'} \setminus \{i'\}$ we have $i \in Y$. Therefore it should
  % be
  % $i' = \bigsqcup (Y \cup \{ i' \}) = \bigsqcup (Y \cup \{
  % i \}) = \bigsqcup Y  = p(i')$, which is a contradiction.

  % \bigskip

  (\ref{le:eq-char:1} $\to$ \ref{le:eq-char:3})
  %
  Assume that $i \leftrightarrow i'$. By definition, $\{i, i'\}$ is
  consistent. Let $d \in \compact{D}$ be such that
  $\pred{i}, \pred{i'} \sqsubseteq d$. If we let $X = \ir{d}$ we have
  that $\ir{i} \setminus \{i\} \subseteq X$ and similarly
  $\ir{i'} \setminus \{i'\} \subseteq X$.  This implies that
  $X \cup \{ i \}$ and $X \cup \{ i' \}$ are downward closed and
  consistent. Hence
  $d \sqcup i = \bigsqcup X \sqcup i = \bigsqcup (X \cup \{ i \}) =
  \bigsqcup (X \cup \{ i' \}) = \bigsqcup X \sqcup i' = d \sqcup i'$.

  % \ICrem{Finally, if we consider the set $X \subseteq \ir{D}$ required by
  % the definition of interchangeability, such that
  % $\bigsqcup X \neq \bigsqcup (X \cup \{ i \}) = \bigsqcup (X \cup \{
  % i' \})$ and define $d = \bigsqcup X$, we obtain
  % $d \neq \bigsqcup (X \cup \{ i \}) = \bigsqcup X \sqcup i = d \sqcup
  % i$, as desired.}

  \bigskip

  (\ref{le:eq-char:3} $\to$ \ref{le:eq-char:4})
  %
  Assume (\ref{le:eq-char:3}). Let $p = \pred{i} \sqcup \pred{i'}$,
  which is in $\compact{D}$ since
  $\pred{i}, \pred{i'} \in \compact{D}$. Clearly,
  $\pred{i}, \pred{i'} \sqsubseteq p$.
  %
  Therefore
  $i \sqcup \pred{i'} = i \sqcup \pred{i} \sqcup \pred{i'} = i \sqcup
  p = p \sqcup i' = \pred{i} \sqcup \pred{i'} \sqcup i' = \pred{i}
  \sqcup i'$.

  % \ICrem{Moreover, $p = \pred{i} \sqcup \pred{i'} \neq \pred{i'} \sqcup i$,
  % otherwise for any $d \in \compact{D}$ such that
  % $\pred{i}, \pred{i'} \sqsubseteq d$, we would have
  % $d \sqcup i = d \sqcup \pred{i'} \sqcup i = d \sqcup
  % \pred{i} \sqcup \pred{i'} = d$, contradicting the second part of
  % condition (\ref{le:eq-char:3}).}

  \bigskip

  (\ref{le:eq-char:4} $\to$ \ref{le:eq-char:1}) Assume
  (\ref{le:eq-char:4}).  Let $X \subseteq \ir{D}$
  be such that $X \cup \{ i\}$ and $X \cup \{ i'\}$ are downward
  closed and consistent sets of irreducibles. This implies that
  $\ir{\pred{i}} \subseteq X$ and similarly
  $\ir{\pred{i'}} \subseteq X$.  Hence, if we let
  $P = \ir{\pred{i}} \cup \ir{\pred{i'}}$, we have
  \begin{center}
    $P  \subseteq X$ \quad and \quad $\bigsqcup P = \pred{i} \sqcup \pred{i'}$.
  \end{center}
  Therefore
  \begin{center}
    $
    \begin{array}{ll}
      \bigsqcup (X \cup \{ i \}) =\\
      \quad = (\bigsqcup X \setminus P) \sqcup \bigsqcup P \sqcup i =\\
      \quad = (\bigsqcup X \setminus P) \sqcup \pred{i} \sqcup \pred{i'} \sqcup i =\\
      \quad = (\bigsqcup X \setminus P) \sqcup i \sqcup \pred{i'} =\\
      \quad = (\bigsqcup X \setminus P) \sqcup \pred{i} \sqcup i' =\\
      \quad = (\bigsqcup X \setminus P) \sqcup \pred{i} \sqcup \pred{i'}  \sqcup i' =\\
      \quad = (\bigsqcup X \setminus P) \sqcup \bigsqcup P \sqcup i' =\\
      \quad = \bigsqcup (X \cup \{ i' \})
    \end{array}
    $
  \end{center}
  %
  % \ICrem{Moreover, if we take $X = \ir{\pred{i}} \cup \ir{\pred{i'}}$ then
  % $X \cup \{i\}$ and $X \cup \{i'\}$ are downward closed and
  % consistent. Moreover,
  % $\bigsqcup X = \pred{i} \sqcup \pred{i'} \neq \pred{i} \sqcup i' =
  % \sqcup (X \cup \{i'\})$, as desired.}
\end{proof}

The interchangeability relation is clearly reflexive and symmetric, but not
transitive in general: in the domain of Fig.~\ref{fi:not-trans}, using the characterisation in Lemma~\ref{le:eq-char}(\ref{le:eq-char:4}) one can easily see that
$i \leftrightarrow i_1$ and $i_1 \leftrightarrow i'$ but not
$i \leftrightarrow i'$, simply because
$\{i, i'\}$ is not consistent.
%
More interestingly, in the domain of Fig.~\ref{fi:not-trans-cons}, we have $i \leftrightarrow i_1$, $i_1 \leftrightarrow i_2$, $i_2 \leftrightarrow i'$, hence $i \leftrightarrow^* i'$. However, despite the fact that $\{i, i'\}$ is consistent, it does not hold $i \leftrightarrow i'$, since $\pred{i} \sqcup i' \neq i \sqcup \pred{i'}$. 
%
This shows that the intuition that
interchangeable irreducibles correspond to the execution of the
same event with different and consistent enablings is still not properly captured. Since $i$ and $i'$ represent the execution of the same event and they are consistent, one would expect that they are interchangeable.

% renamed:
% i_1 -> i,   i_2 -> i_1,   i_3 -> i'
\begin{figure}
  \begin{center}
    \begin{tikzpicture}[node distance=5mm, >=stealth',x=20mm,y=8mm, scale=.8]
      \node[lab] at (2,-0.4) (bot)  {$\bot$};

      \node[lab] at (0,0.8) (pi1)  {$\pred{i}$};
      \node[lab] at (2,0.8) (pi2)  {$\pred{i_1}$};
      \node[lab] at (4,0.8) (pi3)  {$\pred{i'}$};

      \node[lab] at (0,1.9) (i1)   {$i$};
      \node[lab] at (1,1.7) (pi12) {$\bullet$};
      \node[lab] at (2,1.9) (i2)   {$i_1$};
      \node[lab] at (3,1.7) (pi23) {$\bullet$};
      \node[lab] at (4,1.9) (i3)   {$i'$};

      \node[lab] at (1,2.7) (i12) {$\bullet$};
      \node[lab] at (3,2.7) (i23) {$\bullet$};

      %\node[lab] at (2,3.3) (top)  {$\top$};

      \draw [->]  (bot)  -- (pi1);
      \draw [->]  (bot)  -- (pi2);
      \draw [->]  (bot)  -- (pi3);

      \draw [->]  (pi1)  -- (i1);
      \draw [->]  (pi1)  -- (pi12);
      \draw [->]  (pi2)  -- (i2);
      \draw [->]  (pi2)  -- (pi12);
      \draw [->]  (pi2)  -- (pi23);
      \draw [->]  (pi3)  -- (i3);
      \draw [->]  (pi3)  -- (pi23);

      \draw [->]  (i1)  -- (i12);
      \draw [->]  (i2)  -- (i12);
      \draw [->]  (pi12)  -- (i12);
      \draw [->]  (i2)  -- (i23);
      \draw [->]  (i3)  -- (i23);

      \draw [->]  (pi12)  -- (i12);
      \draw [->]  (pi23)  -- (i23);
      %\draw [->]  (i12)   -- (top);
      %\draw [->]  (i23)   -- (top);
    \end{tikzpicture}
  \end{center}

\caption{Interchangeability need not be transitive.}
\label{fi:not-trans}
\end{figure}

% renamed:
% i_1 -> i
% i_2 -> i_1
% i_3 -> i_2
% i_4 -> i'

\begin{figure}
  \begin{center}
    \begin{tikzpicture}[node distance=5mm, >=stealth',x=20mm,y=12mm, scale=.7]     
      \node[lab] at (3,0) (bot)  {$\bot$};

      \node[lab] at (0,0.8) (pi1)  {$\pred{i}$};
      \node[lab] at (2,0.8) (pi2)  {$\pred{i_1}$};
      \node[lab] at (4,0.8) (pi3)  {$\pred{i_2}$};
      \node[lab] at (6,0.8) (pi4)  {$\pred{i'}$};

      \node[lab] at (0,1.9) (i1)   {$i$};
      \node[lab] at (1,1.4) (pi12) {$\pred{i} \sqcup \pred{i_1}$};
      \node[lab] at (2,1.9) (i2)   {$i_1$};
      \node[lab] at (3,1.4) (pi23) {$\pred{i_1} \sqcup \pred{i_2}$};
      \node[lab] at (4,1.9) (i3)   {$i_2$};
      \node[lab] at (5,1.4) (pi34) {$\pred{i_2} \sqcup \pred{i'}$};
      \node[lab] at (6,1.9) (i4)   {$i'$};

      \node[lab] at (1,2.9) (i12) {$i \sqcup i_1$};
      \node[lab] at (3,2.7) (i23) {$i_1 \sqcup i_2$};
      \node[lab] at (5,2.9) (i34) {$i_2 \sqcup i'$};

      \node[lab] at (2,4)   (pi141) {$i \sqcup \pred{i'}$};
      \node[lab] at (4,4)   (pi144) {$\pred{i}  \sqcup i'$};

      \node[lab] at (3,3.2) (pi14)  {$\pred{i} \sqcup \pred{i'}$};

      \node[lab] at (3,4.5) (i14)  {$i \sqcup i'$};

      \draw [->]  (bot)  -- (pi1);
      \draw [->]  (bot)  -- (pi2);
      \draw [->]  (bot)  -- (pi3);
      \draw [->]  (bot)  -- (pi4);

      \draw [->]  (pi1)  -- (i1);
      \draw [->]  (pi1)  -- (pi12);
      \draw [->]  (pi2)  -- (i2);
      \draw [->]  (pi2)  -- (pi12);
      \draw [->]  (pi2)  -- (pi23);
      \draw [->]  (pi3)  -- (i3);
      \draw [->]  (pi3)  -- (pi23);
      \draw [->]  (pi3)  -- (pi34);
      \draw [->]  (pi4)  -- (i4);
      \draw [->]  (pi4)  -- (pi34);

      \draw [->]  (i1)  -- (i12);
      \draw [->]  (i2)  -- (i12);
      \draw [->]  (pi12)  -- (i12);
      \draw [->]  (i2)  -- (i23);
      \draw [->]  (i3)  -- (i23);
      \draw [->]  (i3)  -- (i34);
      \draw [->]  (i4)  -- (i34);

      \draw [->]  (pi12)  -- (i12);
      \draw [->]  (pi23)  -- (i23);
      \draw [->]  (pi34)  -- (i34);

      \draw [-,color=white,line width=1.5mm]  (pi1)  to [bend left=17] (pi14);	
      \draw [->]  (pi1)  to [bend left=17] (pi14);
      \draw [-,color=white,line width=1.5mm]   (pi4)  to [bend right=17] (pi14);
      \draw [->]   (pi4)  to [bend right=17] (pi14);
      \draw [->]  (pi14)   -- (pi141);
      \draw [->]  (pi14)   -- (pi144);
      \draw [->]  (pi144)   -- (i14);
      \draw [->]  (pi141)   -- (i14);
      \draw [->] (i1)   to [bend left=17]  (pi141);
      \draw [->]  (i4)   to [bend right=17]  (pi144);
    \end{tikzpicture}
  \end{center}

\caption{A domain which is not {\wi} , since Definition~\ref{de:well-interchange}(\ref{de:well-interchange:1}) is violated.}
\label{fi:not-trans-cons}
\end{figure}

% renamed:
% i_1 -> i'
% i_2 -> i
% i_3 -> j
% i_4 -> j'
\begin{figure}
  \begin{center}
    \begin{tikzpicture}[node distance=5mm, >=stealth',x=20mm,y=12mm, scale=.7]     
      \node[lab] at (3,0) (bot)  {$\bot$};

      \node[lab] at (0,0.8) (pi1)  {$\pred{i'}$};
      \node[lab] at (2,0.8) (pi2)  {$\pred{i}$};
      \node[lab] at (4,0.8) (pi3)  {$\pred{j}$};
      \node[lab] at (6,0.8) (pi4)  {$\pred{j'}$};

      \node[lab] at (0,1.9) (i1)   {$i'$};
      \node[lab] at (1,1.4) (pi12) {$\pred{i'} \sqcup \pred{i}$};
      \node[lab] at (2,1.9) (i2)   {$i$};
      \node[lab] at (3,1.4) (pi23) {$\pred{i} \sqcup \pred{j}$};
      \node[lab] at (4,1.9) (i3)   {$j$};
      \node[lab] at (5,1.4) (pi34) {$\pred{j} \sqcup \pred{j'}$};
      \node[lab] at (6,1.9) (i4)   {$j'$};

      \node[lab] at (1,2.9) (i12) {$i' \sqcup i$};
      \node[lab] at (2.5,2.6) (i2p3) {$i \sqcup \pred{j}$};
      \node[lab] at (3.5,2.6) (i3p2) {$j \sqcup \pred{i}$};
      \node[lab] at (5,2.9) (i34) {$j \sqcup j'$};

      \node[lab] at (2,4)   (pi141) {$i' \sqcup \pred{j'}$};
      \node[lab] at (4,4)   (pi144) {$\pred{i'}  \sqcup j'$};

      \node[lab] at (3,3.2) (pi14)  {$\pred{i'} \sqcup \pred{j'}$};

      \node[lab] at (3,4.5) (i14)  {$i' \sqcup j'$};

      \draw [->]  (bot)  -- (pi1);
      \draw [->]  (bot)  -- (pi2);
      \draw [->]  (bot)  -- (pi3);
      \draw [->]  (bot)  -- (pi4);

      \draw [->]  (pi1)  -- (i1);
      \draw [->]  (pi1)  -- (pi12);
      \draw [->]  (pi2)  -- (i2);
      \draw [->]  (pi2)  -- (pi12);
      \draw [->]  (pi2)  -- (pi23);
      \draw [->]  (pi3)  -- (i3);
      \draw [->]  (pi3)  -- (pi23);
      \draw [->]  (pi3)  -- (pi34);
      \draw [->]  (pi4)  -- (i4);
      \draw [->]  (pi4)  -- (pi34);

      \draw [->]  (i1)  -- (i12);
      \draw [->]  (i2)  -- (i12);
      \draw [->]  (pi12)  -- (i12);
      \draw [->]  (i2)  -- (i2p3); 
      \draw [->]  (i3)  -- (i3p2);
      \draw [->]  (i3)  -- (i34);
      \draw [->]  (i4)  -- (i34);

      \draw [->]  (pi12)  -- (i12);
      \draw [->]  (pi23)  -- (i2p3);
      \draw [->]  (pi23)  -- (i3p2);
      \draw [->]  (pi34)  -- (i34);

      \draw [-,color=white,line width=1.5mm]  (pi1)  to [bend left=17] (pi14);	
      \draw [->]  (pi1)  to [bend left=17] (pi14);
      \draw [-,color=white,line width=1.5mm]   (pi4)  to [bend right=17] (pi14);
      \draw [->]   (pi4)  to [bend right=17] (pi14);
      \draw [->]  (pi14)   -- (pi141);
      \draw [->]  (pi14)   -- (pi144);
      \draw [->]  (pi144)   -- (i14);
      \draw [->]  (pi141)   -- (i14);
      \draw [->] (i1)   to [bend left=17]  (pi141);
      \draw [->]  (i4)   to [bend right=17]  (pi144);
    \end{tikzpicture}
  \end{center}

\caption{A domain which is not {\wi}, since Definition~\ref{de:well-interchange}(\ref{de:well-interchange:2}) is violated.}
\label{fi:not-trans-cons-bis}
\end{figure}

The next definition formalises two additional properties that a domain must enjoy to provide $\leftrightarrow$ the intended meaning.

\begin{definition}[{\wi} domain]
  \label{de:well-interchange}
  Let $D$ be a domain.
  %
  We say that $D$ is \emph{\wi} when
  \begin{enumerate}
  \item
    \label{de:well-interchange:1}
    for all $i,i' \in \ir{D}$, if $\{\pred{i}, \pred{i'}\}$ consistent
    and $i \leftrightarrow^* i'$ then $i \leftrightarrow i'$;

  \item
    \label{de:well-interchange:2} for all $i,i',j, j' \in \ir{D}$, if
    $i \leftrightarrow^* i'$, $j \leftrightarrow^* j'$,  and $\{i', j'\}$,
    $\{\pred{i}, j\}$,
    $\{\pred{j}, i\}$ consistent then $\{i, j\}$ consistent.
  \end{enumerate}
\end{definition}

Property (\ref{de:well-interchange:1}) is motivated by the discussion above. It intuitively asks that whenever $i$ and $i'$ represents the execution of the same event and they are consistent, then they are interchangeable. Property (\ref{de:well-interchange:2}) can
be read as follows: if $i, i'$ and $j, j'$ represent the same events
and $i', j'$ are consistent, the only source of inconsistency
between $i$ and $j$ is in their enablings. In other words, either $i$ and $j$ are consistent or it must be that $\pred{i}$ is inconsistent with $j$, or $i$ is inconsistent with $\pred{j}$.  A situation in which this property fails is illustrated in Fig.~\ref{fi:not-trans-cons-bis}.

We now introduce weak primes: they weaken the property
of prime elements, requiring that it holds up to
interchangeability.

\begin{definition}[weak prime]
  \label{de:weak-prime}
  Let $D$ be a domain. A \emph{weak prime} of $D$ is an element
  $i \in \ir{D}$ such that for all pairwise consistent
  $X \subseteq D$, if $i \sqsubseteq \bigsqcup X$ then there exist
  $i' \in \ir{D}$ and $d \in X$ such that $i \leftrightarrow i'$ and
  $i' \sqsubseteq d$. We denote by $\wpr{D}$ the set of weak primes of
  $D$.
\end{definition}

Clearly, since interchangeability is reflexive, any prime is a weak
prime. Moreover, in prime domains interchangeability turns out to be
the identity and thus also the converse holds.

\begin{lemma}[weak primes in prime domains]
  \label{le:interchange-id-pad}
  Let $D$ be a prime domain. Then $\leftrightarrow$ is the
  identity and $\wpr{D} = \pr{D}$.
\end{lemma}

\begin{proof}
  Let $i, i' \in \ir{D}$ be such that $i \leftrightarrow i'$.

  If $i$ and $i'$ are comparable, i.e., $i \sqsubseteq i'$ or
  $i' \sqsubseteq i$, by Lemma~\ref{le:inter-ord} we deduce
  $i = i'$ and we are done.

  Otherwise,
  let
  $X = (\ir{i} \setminus \{i\}) \cup (\ir{i'} \setminus \{i'\})$.
  % \todo{AC: better $X = \ir{\pred{i}} \cup \ir{\pred{i'}}$? PB':
  % Preferisco la versione attuale, mi pare renda pie' evidente
  % $i, i' \not\in X$ usato dopo.}
  Note that $X \cup \{ i \}$ and $X \cup \{ i' \}$ are consistent,
  since, by definition of $\leftrightarrow$, $i$ and $i'$ are so.
  %
  Moreover $X \cup \{ i \}$ and $X \cup \{ i' \}$ are downward closed,
  and thus, from $i \leftrightarrow i'$, we deduce
  $\bigsqcup(X \cup \{ i \})= \bigsqcup(X \cup \{ i' \})$.  Since $D$
  is prime, by Lemma~\ref{le:unique-decomposition}, this
  implies that $X \cup \{ i \} = X \cup \{ i' \}$.
  %
  Since $i$ and $i'$ are uncomparable,
  $i, i' \not\in X$ and we
  conclude $i=i'$.
\end{proof}

We argue that the domain of configurations arising in the presence of
fusions can be characterised domain-theoretically as {\wi} domains
  where all irreducibles are weak primes, i.e., that the domain is
algebraic with respect to weak primes.

\begin{definition}[weak prime algebraic domains]
  \label{de:fusion-domain-new}
  Let $D$ be an {\wi} domain.  It is \emph{weak prime algebraic} (or simply
  \emph{weak prime}) if for all $d \in D$ it holds
  $d = \bigsqcup (\principal{d} \cap \wpr{D})$.
\end{definition}

Observe that weak prime domains are assumed to be interchangeable. This hypothesis will actually play a role only when relating weak prime domains and event structures in Section~\ref{ss:domain-to-es}. However, in order to simplify the presentation we preferred to assume it since the beginning.

% We next provide an alternative characterisation of weak prime domain based
% on irreducibles. As a first step, we observe that weak primes are
% necessarily irreducibles.

% \begin{lemma}[weak primes are irreducibles]
%   Let $D$ be a domain and $d \in \compact{D}$ a weak prime. Then $d \in \ir{D}$.
% \end{lemma}

% \begin{proof}
%   Assume that $d = \bigsqcup X$ for some $X \subseteq
%   \compact{D}$.
%   Since $d$ is a weak prime there exists $d' \leftrightarrow d$ and
%   $x \in X$ such that $d' \sqsubseteq x$. Hence
%   $d' \sqsubseteq x \sqsubseteq \bigsqcup X = d$, from which, by
%   definition of $\leftrightarrow$, we derive $d=x=d'$. Hence $d$ is an
%   irreducible.
%   %
%   % \qed
% \end{proof}

In the same way as prime domains are domains where all
irreducibles are primes (see Proposition~\ref{pr:irr-prime-alg}), we
can provide a characterisation of weak prime domains in terms of
coincidence between irreducibles and weak primes.

\begin{proposition}[weak prime domains, again]
  \label{pr:fusion-domains}
  Let $D$ be an {\wi} domain.
  It is weak prime iff  all irreducibles are weak primes.
\end{proposition}

\begin{proof}
  Let $D$ be an {\wi} domain. We know, by
  Lemma~\ref{pr:domains-irr-alg}, that $D$ is irreducible
  algebraic. If all irreducibles are weak primes, then clearly $D$ is
  also weak prime algebraic. Conversely, if it is weak prime
  algebraic, then for any irreducible $i \in \ir{D}$, we have that
  $i = \bigsqcup (\principal{i} \cap \wpr{D})$. Since $i$ is
  irreducible, this implies
  $i \in \principal{i} \cap \wpr{D} \subseteq \wpr{D}$, as desired.
\end{proof}

A domain is often built as the ideal completion of its compact
elements. We next provide a characterisation of domains and weak prime
domains based on the generators.

\begin{lemma}[weak prime domains from generators]
\label{le:generators}
  Let $(P,\sqsubseteq)$ be a finitary partial order such that 
 for all $d, d', d'' \in P$, if
  $\{ d, d', d''\}$ is pairwise consistent then $d \sqcup d'$ exists
  and is consistent with $d''$. Then $\ideal{P}$ is a domain with
  $\compact{\ideal{P}} = \{ \principal{d} \mid d \in P \} \simeq P$.

  Additionally, let $P$ be {\wi} and for all $i \in \ir{P}$,
  $d, d' \in P$ consistent, if $i \sqsubseteq d \sqcup d'$ then there
  is $i' \in \ir{P}$, $i \leftrightarrow i'$ such that
  $i' \sqsubseteq d$ or $i' \sqsubseteq d'$. Then $\ideal{P}$ is a
  weak prime domain.
\end{lemma}

\begin{proof}
  Let $(P,\sqsubseteq)$ be a 
  finitary partial order such that for all $d, d', d' \in P'$,
  if $\{ d, d', d''\}$ is pairwise consistent then
  $d \sqcup d'$ exists and is consistent with $d''$.

  The fact that $\ideal{P}$ is a
  % $\omega$-algebraic 
  complete algebraic finitary
  partial order with
  $\compact{\ideal{P}} = \{ \principal{d} \mid d \in P \} \simeq P$ is
  a standard result. 
  %
  Moreover, let $X \subseteq \ideal{P}$ pairwise consistent. Consider
  $A = \bigcup \{ I \mid I \in X\}$. Observe that for any finite
  $Y \subseteq A$ there exists $\bigsqcup Y$ in $P$. In fact, let
  $Y = \{ y_1, \ldots, y_n \}$. This means that there are
  $I_1, \ldots, I_n$ such that $y_i \in I_i$ for each
  $i \in \interval{n}$. Since $X$ is pairwise consistent in
  $\ideal{P}$, we deduce that $Y$ is pairwise consistent in $P$.
  Since $y_1, y_2$ are consistent and both are consistent with
  $y_3, \ldots, y_n$, by {hypothesis} there exists $y_1 \sqcup y_2$ and it is
  consistent with $y_3, \ldots, y_n$, i.e.,
  $\{ y_1 \sqcup y_2, y_3, \ldots, y_n \}$ is again pairwise
  consistent. Iterating the reasoning we get the existence of
  $y_1 \sqcup y_2 \sqcup \ldots \sqcup y_n = \bigsqcup Y$, as desired.
  %
  Now, if we define
  $I' = \{ \bigsqcup Y \mid Y \subseteq_{\mathit{fin}} A \}$, then
  $I'$ is an ideal and $I' = \bigsqcup X$.

  \bigskip

  Let us consider the second part. It is easy to see that
  $\ir{\ideal{P}} = \{ \principal{i} \mid i \in \ir{P} \}$.
  %
  Moreover, for $i, i' \in \ir{P}$ we have $i \leftrightarrow i'$
  in $P$ if and only if 
  $\principal{i} \leftrightarrow \principal{i'}$ in $\ideal{P}$.
  %
  This immediately implies that $\ideal{P}$ is {\wi}, because so is
  $P$ by assumption.

  We need to show that, under the hypotheses, if
  $I \in \ir{\ideal{P}}$ and $X \subseteq \ideal{P}$ pairwise
  consistent and $I \subseteq \bigsqcup X$ then there exists
  $I' \leftrightarrow I$ and $A \in X$ such that $I' \subseteq
  A$. Thus let $I = \principal{i}$ for some $i \in \ir{P}$. The fact
  that
  $I = \principal{i} \subseteq \bigsqcup X = \bigsqcup \{
  \principal{d} \mid d \in \bigcup X \}$, since $\principal{i}$ is
  finite, means that
  $\principal{i} \subseteq \principal{d_1} \cup \ldots \cup
  \principal{d_n}$ for some finite subset
  $\{ d_1, \ldots, d_n \} \subseteq \bigcup X$ and thus
  $i \sqsubseteq \bigsqcup \{ d_1, \ldots, d_n \}$. Since
  $i \sqsubseteq d_1 \sqcup \bigsqcup \{ d_2, \ldots, d_n\}$, by the
  hypothesis there is $i_1 \leftrightarrow i$ such that
  $i_1 \sqsubseteq d_1$ or
  $i_1 \sqsubseteq \bigsqcup \{ d_2, \ldots, d_n\} = d_2 \sqcup
  \bigsqcup \{ d_3, \ldots, d_n\}$.
  %
  In the second case, again by the hypotheses, there are two
  possibilities. The first is that there is $i_2 \leftrightarrow i_1$,
  such that $i_2 \sqsubseteq d_2$. Note that, since $\pred{i}$ and
  $\pred{i_2}$ are clearly consistent (they are dominated by
  $\bigsqcup \{ d_1, \ldots, d_n \}$), by property
  (\ref{de:well-interchange:1}) of well-interchangeability
  (Definition~\ref{de:well-interchange}), we get
  $i_2 \leftrightarrow i$.
  % 
  The second possibility is that
  ${i_2} \sqsubseteq \bigsqcup \{ d_3, \ldots, d_n\}$, and we can iterate the reasoning. 
  In the end, we get the existence of some
  $i' \leftrightarrow i$ and $j \in \interval{n}$ such that
  $i' \sqsubseteq d_j$. Recalling that $d_j \in \bigcup X$, there is
  ${A} \in X$ such that $d_j \in {A}$, hence
  $\principal{{i'}} \subseteq \principal{d_j} \subseteq
  {A}$. Since $i \leftrightarrow {i'}$ in $P$ implies
    $\principal{i} \leftrightarrow \principal{{i'}}$ in $\ideal{P}$,
    we conclude.
\end{proof}

We finally introduce a category of weak prime domains by defining a notion of morphism.

\begin{definition}[category of weak prime domains]
  \label{de:domain-category}
  Let $D_1$, $D_2$ be weak prime domains.
  A  weak prime domain morphism $f : D_1 \to D_2$ is a total function such that
  for all consistent $X_1 \subseteq D_1$ and $d_1, d_1' \in D_1$
  \begin{enumerate}
  \item if $d_1 \preceq d_1'$ then $f(d_1) \preceq f(d_1')$;
  \item $f(\bigsqcup X_1) = \bigsqcup f(X_1)$;
  \item if $d_1, d_1'$ consistent and
    $d_1 \sqcap d_1' \preceq d_1$ then
    $f(d_1 \sqcap d_1') = f(d_1) \sqcap f(d_1')$;
  \end{enumerate}
  We denote by $\WDom$ the category of weak prime domains
  and their morphisms.
\end{definition}

Compared with the notion of morphism for prime domains in
Definition~\ref{de:pdomain-category} (from~\cite{Win:ES}), we still
require the preservation of $\preceq$ and $\sqcup$ of consistent sets
(conditions (1) and (2)). However, the third condition, i.e.,
preservation of $\sqcap$, is weakened to preservation in some
cases. General preservation of meets is indeed not expected in the
presence of fusions. Consider, e.g., the {\esabbr} in
Example~\ref{ex:event-structure}. Take another {\esabbr} $E' = \{c \}$
with $\emptyset \vdash c$ and the morphism $f : E \to E'$ that forgets
$a$ and $b$, i.e., $f(c) = c$ and $f(a)$, $f(b)$ undefined.
%
Then $f(\{a,c\}) \sqcap f(\{b,c\}) = \{c\} \sqcap \{c\} = \{ c \} \neq
f(\{a,c\} \sqcap \{b,c\}) = f(\emptyset) = \emptyset$. 
%
Intuitively, the condition $d_1 \sqcap d_1' \prec d_1$ means that
$d_1'$ includes the computation modelled by $d_1$ apart from a final
step, hence $d_1 \sqcap d_1'$ coincides with $d_1$ when such step is
removed. Since domain morphisms preserve immediate precedence (i.e.,
single steps), also $f(d_1)$ differs from $f(d_1')$ for the
execution of a final step and the meet $f(d_1) \sqcap f(d_1')$ is
$f(d_1)$ without such step, and thus it coincides with
$f(d_1 \sqcap d_1')$.

In general we only have
\begin{center}
  $f(\bigsqcap X_1) \sqsubseteq \bigsqcap f(X_1)$
\end{center}
% 
In fact, for all $x_1 \in X_1$, we have
$\bigsqcap X_1 \sqsubseteq x_1$, hence
$f(\bigsqcap X_1) \sqsubseteq f(x_1)$ and thus
$f(\bigsqcap X_1) \sqsubseteq \bigsqcap f(X_1)$.
%
Still, when restricted to prime domains, also the converse inequality
holds and our notion of morphism boils down to the original one, i.e.,
the full subcategory of $\WDom$ having prime domains as objects is
$\PDom$.

\begin{theorem}[$\PDom$ as a subcategory of $\WDom$]
    \label{th:PdomFullSub}
  The category of prime domains $\PDom$ is the full
  subcategory of $\WDom$ having prime domains as objects.
\end{theorem}

\begin{proof}
  We just need to show that weak prime domain morphisms preserve meets
  on prime domains, i.e., that if $D_1$, $D_2$ are prime domains and
  $f : D_1 \to D_2$ is a weak prime domain morphism then
  $f(\bigsqcap X_1) = \bigsqcap f(X_1)$ for all $X_1 \subseteq D_1$
  pairwise consistent.

  We first show that for $d_1, d_1' \in \compact{D_1}$, consistent, it
  holds that $f(d_1 \sqcap d_1') = f(d_1) \sqcap f(d_1')$. We proceed
  by induction on $k = |\principal{d_1} \cap \pr{D}|$.

  When $k=0$ we have $d_1 = \bot$. Since $f$ preserves joins, we have
  that
  $f(\bot) = f(\bigsqcup \emptyset) = \bigsqcup f(\emptyset) =
  \bigsqcup \emptyset = \bot$.  Hence
  \begin{center}
    $f(d_1 \sqcap d_1') = f(\bot \sqcap d_1') = f(\bot)= \bot = \bot \sqcap
    f(d_1') = f(\bot) \sqcap f(d_1') = f(d_1) \sqcap f(d_1')$.
  \end{center}

  Suppose now $k > 0$. We distinguish two subcases. If $d_1$ is not
  prime then, recalling that in a prime domain, primes and
  irreducibles coincide, $d_1$ is not irreducible and thus
  $d_1 = e_1 \sqcup f_1$ with $d_1 \neq e_1, f_1 \neq \bot$. It is
  immediate to see that $|\principal{e_1} \cap \pr{D}| < k$ and
  $|\principal{f_1} \cap \pr{D}| < k$. Moreover, since any prime
  algebraic domain is distributive we have
  $d_1 \sqcap d_1' = (e_1 \sqcup f_1) \sqcap d_1' = (e_1 \sqcap d_1')
  \sqcup (f_1 \sqcap d_1')$. Summing up
  \begin{align*}
    & f(d_1 \sqcap d_1') = \\[1mm]
    % 
    & \quad =f((e_1 \sqcap d_1') \sqcup (f_1 \sqcap d_1'))\\
    & \qquad \mbox{[Preservation of $\sqcup$]}\\[1mm]
    % 
    & \quad =f(e_1 \sqcap d_1') \sqcup f(f_1 \sqcap d_1')\\
    & \qquad \mbox{[Inductive hypothesis]}\\[1mm]
    % 
    & \quad =(f(e_1) \sqcap f(d_1')) \sqcup (f(f_1) \sqcap f(d_1'))\\
    & \qquad \mbox{[Distributivity]}\\[1mm]
    % 
    & \quad =(f(e_1) \sqcup f(f_1)) \sqcap f(d_1')\\
    & \qquad \mbox{[Preservation of $\sqcup$]}\\[1mm]
    % 
    & \quad =f(e_1 \sqcup f_1) \sqcap f(d_1') =\\[1mm]
    % 
    & \quad =f(d_1) \sqcap f(d_1')
  \end{align*}

  If instead $d_1$ is prime then note that if $d_1 \sqsubseteq d_1'$
  the thesis is immediate: by monotonicity
  $f(d_1) \sqsubseteq f(d_1')$. Thus
  $f(d_1 \sqcap d_1') = f(d_1) = f(d_1)\sqcap f(d_1')$ as
  desired. Therefore, let us assume that $d_1 \not\sqsubseteq
  d_1'$.
  In this case $d_1 \sqcap d_1' = \pred{d_1} \sqcap d_1'$, since the set
  of lower bounds of $\{ d_1, d_1'\}$ and of $\{ \pred{d_1}, d_1' \}$ is
  the same. Observe that
  \begin{equation}
    \label{eq:pad1}
    \pred{d_1} = d_1 \sqcap (\pred{d_1} \sqcup d_1')
  \end{equation}
  In fact, the join exists since $d_1$, $d_1'$ are consistent. Moreover, by distributivity,
  $d_1 \sqcap (\pred{d_1} \sqcup d_1') = (d_1 \sqcap \pred{d_1})
  \sqcup (d_1 \sqcap d_1') = \pred{d_1} \sqcup (\pred{d_1} \sqcap
  d_1') = \pred{d_1}$.

  Therefore
  \begin{align*}
    & f(d_1 \sqcap d_1') =\\[1mm]
    % 
    & \quad = f(\pred{d_1} \sqcap d_1')\\
    & \qquad \mbox{[Inductive hypothesis]}\\[1mm]
    % 
    & \quad =f(\pred{d_1}) \sqcap f(d_1')\\
    & \qquad \mbox{[Using~(\ref{eq:pad1})]}\\[1mm]
    % 
    & \quad = f(d_1 \sqcap (\pred{d_1} \sqcup d_1')) \sqcap f(d_1')\\
    & \qquad \mbox{[By Definition~\ref{de:domain-category}(3)]}\\[1mm]
    % 
    & \quad = f(d_1) \sqcap f(\pred{d_1} \sqcup d_1')) \sqcap f(d_1')\\
    & \qquad \mbox{[Preservation of $\sqcup$]}\\[1mm]
    % 
    & \quad = f(d_1) \sqcap f(d_1')
  \end{align*}
  as desired. This extends to the meet of finite sets of compact elements, by
  associativity of $\sqcap$, and to 
  infinite sets of compacts by observing that, given an infinite set
  $X$, by finitariness we can identify a finite subset $F \subseteq X$
  such that $\bigsqcap X = \bigsqcap F$.
  %
  The last assertion can be proved by induction on
  $k = \min \{ |\principal{d}| : d \in X \}$. In fact, let $d \in X$
  be an element such that $|\principal{d}| = k$. If {$k=1$} then
  $d = \bot$ and thus $\bigsqcap X = \bot = \bigsqcap \{ d \}$, as
  desired. If {$k >1$}, then we distinguish two possibilities. If for
  all $d' \in X$ it holds $d \sqcap d' = d$ then
  $\bigsqcap X = d = \bigsqcap \{d\}$. If instead, there is $d' \in X$
  such that $d \sqcap d' \sqsubset d$ then recall that the meet of
  compact elements is compact and consider
  $X' = X \cup \{ d \sqcap d' \}$. We have that
  $\bigsqcap X = \bigsqcap X'$. Moreover
  $|\principal{d \sqcap d'}| < k$, hence we can apply the inductive
  hypothesis to $X'$ and get a finite subset $F' \subseteq X'$ such
  that $\bigsqcap X' = \bigsqcap F'$. We conclude observing that
  $\bigsqcap X = \bigsqcap X' = \bigsqcap F' = \bigsqcap ((F'
  \setminus \{d \sqcap d'\}) \cup \{ d, d'\})$. Therefore we can take
  $F = (F' \setminus \{d \sqcap d'\}) \cup \{ d, d'\}$ and we
  conclude.
\end{proof}

%\subsection{Connected Event Structures}
\subsection{{From Event Structures to Weak Prime Domains}}
\label{ss:es-to-domain}

We show that the set of configurations of an {\esabbr}, ordered by
subset inclusion, is a weak prime domain where the compact elements
are the finite configurations.
%More precisely, since
%configurations are finite sets, they represent the compact elements of
%the domain, which is obtained by ideal completion. 
Moreover, the
correspondence can be lifted to a functor. We also identify a subclass
of {\esabbr} that we call \emph{connected {\esabbr}} and that are the exact counterpart of
weak prime domains (in the same way as prime {\esabbr} correspond to prime
algebraic domains).

\begin{definition}[configurations of an {event structure}, ordered]
  Let ${E}$ be an {\esabbr}. We define
  $\dom{{E}} = \langle \conf{{E}}, \subseteq \rangle$.
  Given an {\esabbr} morphism $f : {E}_1 \to {E}_2$, its image
  $\dom{f} : \dom{{E}_1} \to \dom{{E}_2}$ is defined as
  $\dom{f}(C_1) =   \{ f(e_1) \mid e_1 \in C_1 \}$.
  %\bigcup_{e_1 \in C_1} f(e_1)$.
\end{definition}

We need some technical facts, collected in the following lemma.
Recall that in the setting of unstable {\esabbr} we can have distinct
consistent minimal enablings for an event. The following notation will be useful.

\begin{definition}[connected enablings]
  Let $E$ be an {\esabbr}, $C, C' \in \conf{E}$ and $e \in E$.
  % 
  When $C \vdash_0 e$, $C' \vdash_0 e$, and $C \cup C' \cup \{ e \}$
  is consistent, we write $C \conn{e} C'$. We denote by $\conn{e}^*$ the
  transitive closure of the relation $\conn{e}$.
\end{definition}

Note that, whenever $C \vdash_0 e$ and $C' \vdash_0 e$, requiring 
$C \cup C' \cup \{ e \}$ consistent amounts to require  $C \cup C'$ 
consistent, since conflict is binary.

\begin{lemma}[properties of the domain of configurations]
  \label{le:es-to-fusion-domain}
  Let $\langle E, \vdash, Con \rangle$ be an {\esabbr}.
  % and $\dom{E}$ the corresponding domain. 
  Then
  \begin{enumerate}

  \item 
    \label{le:es-to-fusion-domain:1}
    $\dom{{E}}$ is a domain,
    $\compact{\dom{{E}}} = \conff{{E}}$, join is union and
    $C \prec C'$ iff {$C' = C \cup \{ e \}$
    for some $e \in E \setminus C$};

  \item
    \label{le:es-to-fusion-domain:2}
    $C \in \conf{{E}}$ is irreducible iff $C = C' \cup \{ e \}$ and
    $C' \vdash_0 e$; in this case we denote $C$ as $\esir{C'}{e}$;

  \item 
    \label{le:es-to-fusion-domain:3}
    for $C \in \conf{{E}}$, we have
    $\ir{C} = \{ \esir{C'}{e'} \mid e' \in C\ \land\ C' \subseteq C\
    \land\ C' \vdash_0 e' \}$; moreover $\pred{\esir{C'}{e'}} = C'$;

  \item 
    \label{le:es-to-fusion-domain:4}
%    for $I_1, I_2 \in \ir{\dom{{E}}}$, we have
%    $I_1 \leftrightarrow I_2$ iff $I_1 = \esir{C_1}{e}$,
%    $I_2 = \esir{C_2}{e}$, and $C_1 \conn{e} C_2$.
%
    for $\esir{C_1}{e_1}, \esir{C_2}{e_2} \in \ir{\dom{{E}}}$, we have
    $\esir{C_1}{e_1} \leftrightarrow \esir{C_2}{e_2}$ iff $e = e_1 = e_2$
    and $C_1 \conn{e} C_2$;

  \item
    \label{le:es-to-fusion-domain:5}
    $\dom{E}$ is {\wi}.

  \end{enumerate}
\end{lemma}

\begin{proof}
  \begin{enumerate}
  \item
    %
    We first observe that, given a pairwise consistent set of
    configurations $X \subseteq \conf{E}$, the join is the union
    $\bigsqcup X = \bigcup X$. The fact that $\bigcup X$ is a
    configuration, i.e., that it is consistent and secured immediately
    follows from the fact that each $C \in X$ is.

    Let $C \in \conf{E}$ be a configuration.  For every event $e \in E$,
    since $C$ is secured, we can consider a set
    $C_e = \{ e_1, \ldots, e_n \} \subseteq C$ such that $e_n =e$ and
    $\{ e_1, \ldots, e_{k-1} \} \vdash e_k$ for all
    $k \in \interval{n}$. It is immediate to see that
    $C_e \in \conff{E}$ and clearly $C = \bigsqcup_{e \in C} C_e$.

    From the above it is almost immediate to conclude that the
    compact elements of $\dom{{E}}$ are the finite configurations
    $\compact{\dom{E}} =\conff{E}$ and that $\dom{{E}}$ is algebraic.
    %
    Moreover, $\dom{E}$ is finitary, since the number of subsets of a
    finite configurations is clearly finite. Hence $\dom{{E}}$ is a
    domain.

    Concerning immediate precedence, let $C, C' \in \conff{E}$. If
    $C' = C \cup \{ e \}$ with $e \not\in C$ then clearly
    $C \prec C'$, since the order is subset inclusion. Conversely,
      if $C \prec C'$ by definition $C \subseteq C'$ and it must be
      $|C' \setminus C| = 1$. In fact, $C \subseteq C'$ and
      $C \neq C'$, hence $C' \setminus C \neq \emptyset$. Let
    $e, e' \in C' \setminus C$. Let us prove that $e=e'$. Since $C'$
    is secured there is a set of events
    $D = \{ e_1, \ldots, e_n \} \subseteq C'$, such that $e_n = e$ and
    $\{ e_1, \ldots, e_{k-1} \} \vdash e_k$ for all
    $k \in \interval{n}$. Now, if $e' \not\in D$, observe that
    $C \cup D$ is a configuration and $C \subset C \cup D \subset C'$,
    contradicting $C \prec C'$.
%
    Assume that, instead, $e' \in D$. If $e' = e_k$ for $k< n$ we would
    have that $D' = \{ e_1, \ldots, e_k \}$ is a configuration and we
    could replace $D$ by $D'$ in the contradiction above. Hence it
    must be $e =e'$, as desired.

    \medskip

  \item Let $C \in \conf{{E}}$ be a configuration and assume
    that $C = C' \cup \{ e \}$ with $C' \vdash_0 e$. Then $C$ is a finite configuration, and thus a compact element. Moreover, if
    $C = C_1 \cup C_2$ for $C_1, C_2 \in \conf{{E}}$, 
    then $e$ must occur either in $C_1$ or in
    $C_2$. If $e \in C_1$, since $C_1$ is secured,
    there exists $C_1' \subseteq C_1 \setminus \{ e \}$ such that
    $C_1' \vdash e$. Hence, by monotonicity of enabling,
    $C_1 \setminus \{ e \} \vdash e$. Since $C' \vdash_0 e$ and
    $C_1 \setminus \{ e \} \subseteq C'$ it follows that
    $C_1 \setminus \{ e \} = C'$ and thus $C_1 = C$.
    %
    Therefore, by Lemma~\ref{le:comp-irr}, $C$ is an irreducible.

    Vice versa, let $C \in \conf{{E}}$ be an irreducible. It is
    compact, hence finite. Hence we can consider a secured execution
    % \begin{quote}
    $\langle e_1, \ldots, e_{n} \rangle$
    % \end{quote}
    of configuration $C$. Note that for any $k \in \interval{n-1}$ it
    must be $\{ e_1, \ldots, e_{k-1} \} \not\vdash e_n$.
    % 
    Otherwise, if it were $\{ e_1, \ldots, e_{k-1} \} \vdash e_n$ for
    some $k \in \interval{n-1}$, we would have that $C' = \{
    e_1, \ldots, e_{k}, e_n \}$ and $C'' = \{ e_1, \ldots, e_{n-1} \}$
    are two proper subconfigurations of $C$ such that $C = C'
    \cup C''$, violating the fact that $C$ is irreducible. But this
    means exactly that $\{ e_1, \ldots, e_{n-1} \} \vdash_0 e_n$, as
    desired.

  \medskip

\item Immediate.

  \medskip

% \item In order to prove that $D$ is irreducible algebraic, we show any
%   compact elements, namely, any configuration $C \in \conf{D}$ is the
%   sup of the irreducible in $\ir{C}$. Since any element $x$ is
%   the sup of $\compact{x}$ this implies the thesis.

%   Hence we have to show that for any configuration $C \in \conf{D}$,
%   it holds that $C = \bigcup \ir{C}$. This follows immediately from
%   the observation that for any event $e \in C$ there is at least one
%   irreducible (notice that for PES there is exactly one prime!)
%   $I= \esir{C'}{e} \in \ir{C}$. In order to see this,
%   consider a secured execution of $C$
%   \begin{quote}
%     $e_1, \ldots, e_n$
%   \end{quote}
%   and assume that $e= e_k$. Hence $C_k = \{ e_1, \ldots, e_{k-1} \}$
%   is a configuration and $C_k \vdash e_k$. Therefore there is a
%   (possibly not unique) minimal subset $C_k'$ of $C_k$ being a
%   configuration and enabling $e_k$, i.e., $C_k' \vdash_0 e_k$. Then
%   $I = \esir{C_k'}{e} \in \ir{C}$.

%   \medskip

\item Let $I_j = \esir{C_j}{e_j} \in \ir{\dom{{E}}}$ for
  $j \in \{1,2\}$ be irreducibles. Assume $I_1 \leftrightarrow I_2$.
  By Lemma~\ref{le:eq-char}(\ref{le:eq-char:4}), observing that
  $\pred{I_j} = C_j$, we must have $I_1 \cup C_2 = C_1 \cup I_2$,
  namely $C_1 \cup \{e_1\} \cup C_2 = C_1 \cup C_2 \cup \{ e_2\}$,
  from which we conclude that it must be $e_1 = e_2$, i.e., as desired
  $I_j = \esir{C_j}{e}$, where $e = e_1 = e_2$ for $j \in \{ 1,2 \}$.
  Additionally, $I_1$ and $I_2$ are consistent, by definition of
  $\leftrightarrow$,
  % \ICrem{Lemma~\ref{le:inter-cons-ord}}
  meaning that $C_1 \conn{e} C_2$.

  For the converse, consider two irreducibles $I_1 = \esir{C_1}{e}$
  and $I_2 = \esir{C_2}{e}$, such that $C_1 \conn{e} C_2$. Hence
  $C_1 \vdash_0 e$, $C_2 \vdash_0 e$ and
  $C = C_1 \cup C_2 \cup \{ e \}$ is consistent. Since
  $I_1, I_2 \subseteq C$, they are consistent in
  $\dom{{E}}$. Moreover, $\pred{I_1} = C_1$, $\pred{I_2} = C_2$
  and $I_1 \cup C_2 = I_2 \cup C_1 = C$.
  %\ICrem{$\neq C_1 \cup C_2$.}
  Hence by
  Lemma~\ref{le:eq-char}(\ref{le:eq-char:4}) we have
  $I_1 \leftrightarrow I_2$, as desired.

\item 
  %
  We have to show that $\dom{E}$ satisfies the conditions of Definition~\ref{de:well-interchange}. Concerning condition (\ref{de:well-interchange:1}), let
  $I_1 = \esir{C_1}{e_1}$ and $I_2 = \esir{C_2}{e_2}$ such that
  $I_1 \leftrightarrow^* I_2$ and $\pred{I_1}=C_1, \pred{I_2}=C_2$ consistent. From
  $I_1 \leftrightarrow^* I_2$, by the above result, we deduce $e_1 = e_2$.
  %
  Since, $C_1, C_2$ consistent, we deduce $C_1 \conn{e} C_2$ and thus,
  again by the same result, $I_1 \leftrightarrow I_2$.

  As for Condition~(\ref{de:well-interchange:2}), consider the
  irreducibles $I$, $I'$, $J$ and $J'$ such that
  $I \leftrightarrow^* I'$, $J \leftrightarrow^* J'$, and
  $\{I', J'\}$, $\{\pred{I}, J\}$ and $\{\pred{J}, I\}$
  consistent. From $I \leftrightarrow^* I'$ and
  $J \leftrightarrow^* J'$ we deduce that $I = \esir{C}{e}$,
  $I' = \esir{C'}{e}$, $J = \esir{D}{f}$ and $J' =
  \esir{D'}{f}$. Moreover, we have $\pred{I}=C$ and $\pred{J}=D$,
  hence the hypotheses say $\{C, J\}$ and $\{D, I\}$ consistent. From
  the consistency of $\{I', J'\}$ we deduce that $\{e,f\}$
  consistent. Therefore we have that $I = \esir{C}{e}$ and
  $J = \esir{D}{f}$ are consistent.
\end{enumerate}
\end{proof}

Concerning point 1, observe that the meet in the domain of
configurations is
$C \sqcap C' = \bigcup \{ C'' \in \conf{{E}} \mid C'' \subseteq C\
\land\ C'' \subseteq C'\}$, which is usually smaller than the
intersection. For instance, in Fig.~\ref{fi:running},
$\{a,c\} \sqcap \{b, c\} = \emptyset \neq \{c\}$.
%
Point 2 says that irreducibles are configurations of the form
$C \cup \{ e \}$ that admits a secured execution in which the event
$e$ appears as the last one and cannot be switched with any other. In
other words, irreducibles are minimal enablings of events.
%
Point 3 characterises the irreducibles in a configuration.  According
to point 4, two irreducibles are interchangeable when they are
different minimal enablings for the same event.

\begin{proposition}[{the domain of configurations is weak prime}]
  \label{pr:es-to-dom}
  Let ${E}$ be an {\esabbr}.
  % = \langle E, \vdash, Con \rangle$ be an {\esabbr}. 
  Then $\dom{{E}}$
  is a weak prime domain. Moreover, given two {\esabbr} $E_1$ and $E_2$, and  a morphism
  $f : {E}_1 \to {E}_2$, its image
  $\dom{f} : \dom{{E}_1} \to \dom{{E}_2}$ is a weak prime domain morphism.
\end{proposition}

\begin{proof}
  We know that
  $\dom{{E}}$ is a domain
  (Lemma~\ref{le:es-to-fusion-domain}(\ref{le:es-to-fusion-domain:1}))
  and that it is {\wi}
  (Lemma~\ref{le:es-to-fusion-domain}(\ref{le:es-to-fusion-domain:5})).
%  
%  we know that
%  $\dom{{E}}$ is a domain \IC{and by
%    \todo{AC: 4 -> 5 se si modifica il lemma} Lemma~\ref{le:es-to-fusion-domain}(\ref{le:es-to-fusion-domain:4}),
%    it is {\wi}.}
  %
  % Moreover, interchangeability is history consistent. In fact,
  % let
  % $I = \esir{C}{e}, I' = \esir{C'}{e'}, I''=
  % \esir{C''}{e''}$ be irreducibles such that $I \leftrightarrow I'$,
  % $I \leftrightarrow I''$ and $I' \subseteq I''$. By
  % Lemma~\ref{le:es-to-fusion-domain}(\ref{le:es-to-fusion-domain:4}),
  % $e=e'$ and $e= e''$, hence
  % $e'=e''$. Moreover, $C' \subseteq C''$. Since $C' \vdash_0 e'$ and
  % $C'' \vdash_0 e'' = e'$, we conclude $C'=C''$ and thus $I' = I''$,
  % as desired.

  In order to show that $\dom{{E}}$ is a weak prime domain, we
  exploit the characterisation in Proposition~\ref{pr:fusion-domains},
  i.e., we prove that all irreducibles are weak primes.
  %
  Consider an irreducible $I$, which by
  Lemma~\ref{le:es-to-fusion-domain}(\ref{le:es-to-fusion-domain:2})
  is of the shape $I = \esir{C}{e}$ with $C \vdash_0 e$, and suppose that
  $I \subseteq \bigsqcup X$ for some
  $X \subseteq \dom{{E}}$.
  %
  In particular, this means that $e \in \bigsqcup X$ and thus there is
  $C' \in X$ such that $e \in C'$.  In turn, we can consider a minimal
  enabling of $e$ in $C'$, i.e., a minimal $C'' \subseteq C'$ such
  that $C'' \vdash_0 e$, and we have that $I'' = \esir{C''}{e}$ is an
  irreducible $I'' \subseteq C'$. Since $I$ and $I''$ are consistent,
  as they are both included in $\bigsqcup X$, then $C \conn{e} C''$
  and by
  Lemma~\ref{le:es-to-fusion-domain}(\ref{le:es-to-fusion-domain:4})
  $I \leftrightarrow I''$.

  \bigskip

  We next prove that given an {\esabbr} morphism
  $f : {E}_1 \to {E}_2$, its image
  $\dom{f} : \dom{{E}_1} \to \dom{{E}_2}$ is a weak prime
  domain morphism.
  %
  \begin{itemize}
  \item $C_1 \preceq C_1'$ implies $\dom{f}(C_1) \preceq \dom{f}(C_1')$\\  
    Since $\dom{f}(C_i) = \{ f(d_i) \mid d_i \in C_i \}$ and by
    Lemma~\ref{le:es-to-fusion-domain}(\ref{le:es-to-fusion-domain:1})
    $C_1 \preceq C_1'$ iff $C_1' = C_1 \cup \{ e_1 \}$ for some event
    $e_1$, the result
    follows immediately.\\

  \item for $X_1 \subseteq \dom{{E}_1}$ consistent, $\dom{f}(\bigsqcup X_1) = \bigsqcup \dom{f}(X_1)$\\
    %
    Since $\dom{f}$ takes the image as set and $\bigsqcup$ on
    consistent sets is union, the result follows.\\

  \item for $C_1, C_1' \in \dom{{E}_1}$ consistent such that
    $C_1 \sqcap C_1' \prec C_1$ it holds
    $f(C_1 \sqcap C_1') = f(C_1) \sqcap f(C_1')$\\
    % 
    Since $C_1 \sqcap C_1' \prec C_1$, by
      Lemma~\ref{le:es-to-fusion-domain}(\ref{le:es-to-fusion-domain:1})
      we have that $C_ 1 = (C_1 \sqcap C_1') \cup \{ e_1 \}$ for some
      $e_1 \not\in C_1 \sqcap C_1'$.
    %
    Clearly $e_1 \not\in C_1'$, otherwise we would have $C_1 \subseteq C_1'$
    and thus $C_1 \sqcap C_1' = C_1$. Therefore in this case, the meet
    coincides with intersection,
    $C_1 \sqcap C_1' = C_1 \cap C_1' = C_1 \setminus \{ e_1 \}$.
    %
    Since for the events in $C_1 \cup C_1'$, by definition of event
    structure morphism, $f$ is injective, we have that
    $f(C_1) \cap f(C_1') = f(C_1 \cap C_1')$.
    % 
    As a general fact,
    $f(C_1) \sqcap f(C_1') \subseteq f(C_1) \cap f(C_1')$. Therefore,
    putting things together, we conclude
    \begin{center}
      $f(C_1) \sqcap f(C_1') \subseteq f(C_1) \cap f(C_1') = f(C_1
      \cap C_1') = f(C_1 \sqcap C_1')$
    \end{center}
    The converse inequality holds in any domain (as observed after
    Definition~\ref{de:domain-category}) and thus the result follows.
  \end{itemize}
\end{proof}

A special role is played by the subclass of \emph{connected} {\esabbr}
which will be shown to be exact counterpart of weak prime domains.

\begin{definition}[connected {event structure}]
  \label{de:connected-es}
  An {\esabbr} is \emph{connected} if whenever
  $C \vdash_0 e$ and $C' \vdash_0 e$ then $C \conn{e}^* C'$.  We
  denote by $\ces$ the full subcategory of $\es$ having connected {\esabbr}
  as objects.
\end{definition}

In words, different minimal enablings for the same event must be
pairwise connected by a chain of consistency. Equivalently, for each
event $e$ the set of minimal enablings, say
$M_e = \{ C \mid C \vdash_0 e \}$, endowed with the relation
$\conn{e}$ is a connected graph. Intuitively, as discussed in more
detail below, if $M_e$ were not connected, then we could split event
$e$ into different instances, one for each connected component,
without changing the associated domain.

For instance, the {\esabbr} in
Example~\ref{ex:event-structure} is a connected {\esabbr}. Only event $c$ has
two minimal enablings $\{ a \} \vdash_0 c$ and $\{ b \} \vdash_0 c$
and obviously $\{ a \} \conn{c} \{ b \}$.
% hence it is a connected {\esabbr}.
%
Clearly, prime {\esabbr} are also connected {\esabbr}. More precisely, we have the following.

% \begin{proposition}[connectedness, stability, primality]
\begin{proposition}[{primality = stability + connectedness}]
  \label{le:constapri}
  Let ${E}$ be an {\esabbr}. Then $E$ is prime iff it is stable and connected.
\end{proposition}

\begin{proof}
  The fact that a prime {\esabbr} is stable and connected follows immediately
  from the definitions. Conversely, let ${E}$ be a stable and
  connected {\esabbr}. We show that $E$ is prime, i.e., each $e \in E$ has a
  unique minimal enabling. Let $C, C' \in \conf{E}$ be minimal
  enablings for $e$, i.e., $C \vdash_0 e$ and $C' \vdash_0 e$. Since
  $E$ is connected $C \conn{e}^* C'$. Let
  $C \conn{e} C_1 \conn{e} \ldots \conn{e} C_n \conn{e} C'$. Then
  by stability we get that $C=C_1=\ldots = C_n =C'$. 
\end{proof}

The defining property of connected {\esabbr} allows one to recognise that two
minimal enablings are relative to the same event by only looking at
the partially ordered structure and thus, as we will see, from the
domain of configurations of a connected {\esabbr} we can recover an {\esabbr}
isomorphic to the original one and vice versa (see Theorem~\ref{th:es-dom-equivalence}). 
In general, this is not possible.
%
For instance, consider the {\esabbr} ${E}'$ with events
$E' = \{ a, b, c \}$, and where $a \# b$ and the minimal enablings are
again $\emptyset \vdash_0 a$, $\emptyset \vdash_0 b$,
$\{ a\} \vdash_0 c$, and $\{ b\} \vdash_0 c$. Namely, event $c$ has two
minimal enablings, but differently from what happens in the
running example, these are not consistent, hence
$ \{ a, b \} \not\vdash c$. The resulting domain of configurations is depicted on
the left of Fig.~\ref{fi:non-fusion}. Intuitively, it is not possible
to recognise that $\{ a,c\}$ and $\{ b, c \}$ are different minimal enablings
of the same event. In fact, we would get an isomorphic
domain of configurations by considering the {\esabbr} ${E}''$ with events
$E'' = \{ a, b, c_1, c_2 \}$ such that $a \# b$ and the minimal enablings
are again $\emptyset \vdash_0 a$, $\emptyset \vdash_0 b$,
$\{ a\} \vdash_0 c_1$, and $\{ b\} \vdash_0 c_2$.

\begin{figure}
  \hfill
  \begin{tikzpicture}[node distance=5mm, >=stealth',x=10mm,y=6mm]
    \node at (1,0) (Gs)  {$\emptyset$};
    \node at (0,1) (Ga)  {$\{a\}$};
    \node at (2,1) (Gb)  {$\{b\}$};
    \node at (0,2.7) (Gac)  {$\{a,c\}$};
    \node at (2,2.7) (Gbc)  {$\{b,c\}$};
    \draw [->] (Gs) -- (Ga);
    \draw [->] (Gs) -- (Gb);
    \draw [->] (Ga) -- (Gac);
    \draw [->] (Gb) -- (Gbc);
  \end{tikzpicture}
  \hfill
  \begin{tikzpicture}[node distance=5mm, >=stealth',x=10mm,y=6mm]
    \node at (1,0) (Gs)  {$\emptyset$};
    \node at (0,1) (Ga)  {$\{a\}$};
    \node at (2,1) (Gb)  {$\{b\}$};
    \node at (0,2.7) (Gac)  {$\{a,c_1\}$};
    \node at (2,2.7) (Gbc)  {$\{b,c_2\}$};
    \draw [->] (Gs) -- (Ga);
    \draw [->] (Gs) -- (Gb);
    \draw [->] (Ga) -- (Gac);
    \draw [->] (Gb) -- (Gbc);
  \end{tikzpicture}
  \hfill$\mbox{}$
  \caption{Non-connected {\esabbr} do not uniquely determine a domain.}
  \label{fi:non-fusion}
\end{figure}

%\subsection{Interchangeability, irreducibles and immediate precedence}
%\subsection{From Domains to Event Structures}
\subsection{From {Weak Prime Domains} to {Connected} Event Structures}
\label{ss:domain-to-es}
We show how to get an {\esabbr} from a weak prime domain. As {anticipated},
events are equivalence classes of irreducibles, where the equivalence
is (the transitive closure of) interchangeability.

In order to properly relate domains to the corresponding {\esabbr} we need to prove some properties of irreducibles and of the interchangeability relation in weak prime domains.

% \ICrem{We already observed that the interchangeability relation in
% general is not transitive. We show that in weak prime domains it is transitive on consistent
% irreducibles. 
% %
% We start with a simple
% technical lemma.

% \begin{lemma}[{irreducibles related by $\leftrightarrow^2$ are uncomparable}]
%   \label{le:not-eq-below} 
%   Let $D$ be a domain and
%   $i, i', i'' \in \ir{D}$.  If $i' \leftrightarrow i$,
%   $i \leftrightarrow i''$, and $i' \sqsubseteq i''$ then $i' = i''$.
% \end{lemma}

% \begin{proof} 
%   Assume $i' \leftrightarrow i$, $i \leftrightarrow i''$, and
%   $i' \sqsubseteq i''$ and suppose by {contradiction} that $i' \neq i''$,
%   hence $i' \sqsubseteq \pred{i''}$.  Then we have
%   \begin{quote} 
%     $
%     \begin{array}{lll}
%       i \sqcup \pred{i''} & \sqsubseteq  (i \sqcup \pred{i'}) \sqcup \pred{i''} & \\[1mm]
%       % 
%         & = (\pred{i} \sqcup i') \sqcup \pred{i''} &  \hfill \mbox{[By $i \leftrightarrow i'$  and Lemma~\ref{le:eq-char}(\ref{le:eq-char:4})]}\\[1mm]
%         % 
%         & \sqsubseteq \pred{i} \sqcup \pred{i''} &  \hfill \mbox{[Since $i' \sqsubseteq \pred{i''}$]}\\[1mm]
%     \end{array}$
% %\begin{array}{lll}
% %      i & \sqsubseteq  i \sqcup \pred{i'} & \\[1mm]
% %      % 
% %        & = \pred{i} \sqcup i' &  \hfill \mbox{[By $i \leftrightarrow i'$  and Lemma~\ref{le:eq-char}(\ref{le:eq-char:4})]}\\[1mm]
% %        % 
% %        & \sqsubseteq \pred{i} \sqcup \pred{i''} &  \hfill \mbox{[Since $i' \sqsubseteq \pred{i''}$]}\\[1mm]
% %    \end{array}$
%   \end{quote}
% %  Therefore
% %  $\pred{i} \sqcup \pred{i''} \sqsubseteq i \sqcup \pred{i''}
% %  \sqsubseteq \pred{i} \sqcup \pred{i''} \sqcup \pred{i''} = \pred{i}
% %  \sqcup \pred{i''}$.
% {Since obviously $\pred{i} \sqcup \pred{i''} \sqsubseteq i \sqcup \pred{i''} $, we deduce
%   $i \sqcup \pred{i''} = \pred{i} \sqcup \pred{i''}$, which by
%   Lemma~\ref{le:eq-char}(\ref{le:eq-char:4}) contradicts
%   $i \leftrightarrow i''$.}
%   %
%   \qed
% \end{proof}

% \begin{lemma}[$\leftrightarrow$ transitive on consistent irreducibles]
%   \label{le:transitive}
%   Let $D$ be a weak prime domain and
%   $i, i', i'' \in \ir{D}$ such that $i \leftrightarrow i'$,
%   $i \leftrightarrow i''$, and $i', i''$ consistent. Then
%   $i' \leftrightarrow i''$.
% \end{lemma}

% \begin{proof}
%   Since $i \leftrightarrow i'$ and $i \leftrightarrow i''$, by
%   definition of $\eftrightarrow$,
%   % \ICrem{Lemma~\ref{le:inter-cons-ord}}
%   $i, i'$ and $i, i''$ are
%   consistent and, by Lemma~\ref{le:eq-char}(\ref{le:eq-char:4}),
%   $\pred{i} \sqcup i' = i \sqcup \pred{i'}$ and
%   $\pred{i} \sqcup i'' = i \sqcup \pred{i''}$.  Moreover $i', i''$ is
%   consistent by hypothesis and thus, by coherence, the set $\{i, i', i''\}$ is
%   consistent.

%   Therefore
%   $i' \sqsubseteq \pred{i} \sqcup i' \sqcup \pred{i''} = i \sqcup
%   \pred{i'} \sqcup \pred{i''} = \pred{i} \sqcup \pred{i'} \sqcup i''$.
%   Since $D$ is a weak prime domain, irreducibles are weak primes and
%   there must exist $i'_1 \leftrightarrow i'$ such that either
%   $i'_1 \sqsubseteq \pred{i}$ or ${i'_1} \sqsubseteq \pred{i'}$ or
%   $i'_1 \sqsubseteq i''$. The first possibility
%   $i'_1 \sqsubseteq \pred{i} \sqsubset i$, recalling that
%   $i_1' \leftrightarrow i'$ and $i' \leftrightarrow i$, contradicts
%   Lemma~\ref{le:not-eq-below}, while the second one
%   $i'_1 \sqsubseteq \pred{i'} \sqsubset i'$ contradicts
%   Lemma~\ref{le:inter-ord}.
% %
% % non funge...
% %{Therefore it must be $i'_1 \sqsubseteq i''$, which by Lemma~\ref{le:unique-pred} means that either $i'_1 = i''$ or $i'_1 \sqsubseteq \pred{i''}$. 
% %But  if $i'_1 \sqsubseteq \pred{i''}$, by
% %  Lemma~\ref{le:eq-char}(\ref{le:eq-char:3}) (since $i' \leftrightarrow i'_1$)  we would have $i' \sqcup  \pred{i'} \sqcup \pred{i''} = i'_1  \sqcup \pred{i'} \sqcup \pred{i''} = \pred{i'} \sqcup \pred{i''}$, 
% % and thus $i' \sqsubseteq \pred{i''} \sqsubset i''$, contradicting Lemma~\ref{le:not-eq-below}. Thus we have $i'_1 = i''$, which means that $i' \leftrightarrow i''$, as desired.}
%   %
%   Therefore it must be $i'_1 \sqsubseteq i''$. We also note that it
%   cannot be $i'_1 \sqsubseteq \pred{i''}$, and therefore, by
%   Lemma~\ref{le:unique-pred}, $i'' = i'_1\leftrightarrow i''$,  as desired.
%    In fact, if $i'_1 \sqsubseteq \pred{i''}$, by
%   Lemma~\ref{le:eq-char}(\ref{le:eq-char:3}) we would have
%   \begin{center}
%     $
%     \begin{array}{lll}
%       i' \sqcup \pred{i} \sqcup \pred{i'} \sqcup \pred{i''} & = 
%       & i'_1 \sqcup \pred{i} \sqcup \pred{i'} \sqcup \pred{i''}\\
%       & = & \pred{i} \sqcup \pred{i'} \sqcup \pred{i''}
%     \end{array}
%     $
%   \end{center}
%   In turn, the above equality could be used to prove that
%   \begin{center}
%     $
%     \begin{array}{lll}
%         i & \sqsubseteq & i \sqcup \pred{i} \sqcup \pred{i'} \sqcup
%                            \pred{i''}\\
%            & = & i' \sqcup \pred{i} \sqcup \pred{i'} \sqcup \pred{i''}\\
%            & = & \pred{i} \sqcup \pred{i'} \sqcup \pred{i''}
%     \end{array}
%     $
%   \end{center}
%   Again, by the fact that $D$ is a weak prime domain, there should exist
%   $i_1 \leftrightarrow i$ such that $i_1 \sqsubseteq \pred{i}$ or
%   $i_1 \sqsubseteq \pred{i'}$ or $i_1 \sqsubseteq \pred{i''}$. Note
%   that $i_1 \sqsubseteq \pred{i} \sqsubset i$ contradicts
%   Lemma~\ref{le:inter-ord}. Moreover, recalling that
%   $i \leftrightarrow i'$ and $i \leftrightarrow i_1$,
%   $i_1 \sqsubseteq \pred{i'} \sqsubset i'$ contradicts
%   Lemma~\ref{le:not-eq-below}. The same applies to the case
%   $i_1 \sqsubseteq \pred{i''} \sqsubset i''$. Hence we conclude.
%   %
%   \qed
% \end{proof}
% }

Domains are irreducible algebraic
(see Proposition~\ref{pr:domains-irr-alg}), hence any element is
determined by the irreducibles under it. The difference between two
elements is thus somehow captured by the irreducibles that are under
one element and not under the other.
%
This motivates the following definition.
% %
% In order to have a succint notation, for domain $D$ and $d \in D$ we
% denote the set $\principal{d} \cap \ir{D}$ of irreducibles of $D$
% below $d$ by $\ir{d}$.

\begin{definition}[irreducible difference]
  Let $D$ be a domain and $d, d' \in \compact{D}$ such that
  $d \sqsubseteq d'$. Then we define
  $\diff{d'}{d} = \ir{d'} \setminus \ir{d}$.
\end{definition}

The immediate precedence relation intuitively relates domain elements
corresponding to configurations that differ for the
execution of a single event.
%
In order to formalise this fact we first need a preliminary technical lemma.

\begin{lemma}[immediate precedence and irreducibles/1]
  \label{le:prec-irr-a}
  Let $D$ be a weak prime domain, $d \in \compact{D}$, and $i \in \ir{D}$
  such that $d$, $i$ are consistent and $\pred{i} \sqsubseteq d$. Then
  \begin{enumerate}
  \item 
    \label{le:prec-irr-a:1}
    for all $i' \in \diff{d \sqcup i}{d}$ minimal, it holds
    $i \leftrightarrow i'$;
  \item 
    \label{le:prec-irr-a:2}
    $d \preceq d \sqcup i$.
  \end{enumerate}
\end{lemma}

\begin{proof}
  \begin{enumerate}
  \item Clearly, if $d = d \sqcup i$ {then $\diff{d \sqcup i}{d} = \emptyset$ and 
  % , hence
   % $\ir{d \sqcup i} = \ir{d}$ and 
   the property trivially
    holds.} Assume $d \neq d \sqcup i$ and take
    $i' \in \diff{d \sqcup i}{d}$ minimal. Note that minimality
    implies that $\pred{i'} \sqsubseteq d$. In fact, for all
    {$i_1' \in \ir{\pred{i'}}$} we have
    $i_1' \sqsubset i' \sqsubseteq d \sqcup i$. Hence
    $i_1' \sqsubseteq d$, otherwise ${i_1'} \in \diff{d \sqcup i}{d}$,
    violating minimality of $i'$. Therefore
    $\pred{i'} = \bigsqcup \ir{\pred{i'}} \sqsubseteq d$.

    Now, from $i' \sqsubseteq d \sqcup i$, since $D$ is a weak prime
    domain and thus irreducibles are weak primes, there must be
    $i'' \in \ir{D}$, $i'' \leftrightarrow i'$ such that
    $i'' \sqsubseteq d$ or $i'' \sqsubseteq i$. We first note that it
    cannot be $i'' \sqsubseteq d$, otherwise
    $d = d \sqcup i'' = d \sqcup i'$, the last equality motivated by
    Lemma~\ref{le:eq-char}(\ref{le:eq-char:3}), {which implies that 
    $i' \sqsubseteq d$,} contradicting the hypothesis. 
    {Hence it must be $i'' \sqsubseteq i$, 
    which by Lemma~\ref{le:unique-pred} means that either $i'' = i$ or $i'' \sqsubseteq \pred{i}$. Since $\pred{i} \sqsubseteq d$ by hypothesis, the latter 
    case would contradict $i'' \not \sqsubseteq d$, hence $i'' = i$ which means
    that $i' \leftrightarrow i$, as desired.}

%   Hence it must be
%    $i'' \sqsubseteq i \sqsubseteq i \sqcup d$. Therefore
%    $i'' \in \diff{d \sqcup i}{d}$ and this, in turn, by the minimality
%    of $i$ in $\diff{d \sqcup i}{d}$, implies $i = i''$, hence
%    $i = i'' \leftrightarrow i'$, as desired.

  \item {Let us assume  that $d \not = d \sqcup i$ (otherwise the property is trivial), and} consider $d'$ such that $d \prec d' \sqsubseteq d \sqcup i$:
   we prove that $d' = d \sqcup i$. Since $d \prec d'$, hence
    $d \neq d'$, we know that $\diff{d'}{d}$ is not empty. Take a
    minimal $i' \in \diff{d'}{d}$. Thus $i'$ is minimal also in
    $\diff{d \sqcup i}{d}$, and thus, by point~(\ref{le:prec-irr-a:1}),
    $i \leftrightarrow i'$. By minimality of $i'$ we deduce also that
    $\pred{i'} \sqsubseteq d$. Since also $\pred{i} \sqsubseteq d$ by
    hypothesis, using Lemma~\ref{le:eq-char}(\ref{le:eq-char:3}), we have
    $d \sqcup i = d \sqcup i'$.  Observing that
    $d \sqcup i' \sqsubseteq d' \sqsubseteq d \sqcup i$ we conclude
    that $d' = d \sqcup i$, as desired.
  \end{enumerate}

\end{proof}

We can now  show that whenever $d \prec d'$ the
irreducible difference of $d'$ and $d$ consists of a set of
irreducibles which are pairwise interchangeble, hence, intuitively corresponding to the same event.

\begin{lemma}[immediate precedence and irreducibles/2]
  \label{le:prec-irr-b}
  Let $D$ be a weak prime domain and $d, d' \in D$ such that $d \preceq d'$.
  Then for all $i,i' \in \diff{d'}{d}$ 
  \begin{enumerate}
  \item  
    \label{le:prec-irr-b:1}
    $d' = d \sqcup i$;

  \item  
    \label{le:prec-irr-b:1bis}
    if $i \sqsubseteq i'$ then $i=i'$;

  % \item  
  %   \label{le:prec-irr-b:2}
  %   there is no $i'' \in \ir{d}$ such that $i \leftrightarrow i''$;

  \item  
    \label{le:prec-irr-b:3}
    $i \leftrightarrow i'$.
  \end{enumerate}
\end{lemma}

\begin{proof}
If $ d = d'$ all properties hold trivially.
\begin{enumerate}
\item[\ref{le:prec-irr-b:1})] Let $i \in \diff{d'}{d}$. Then
  $d \sqsubseteq d \sqcup i \sqsubseteq d'$. It follows that either
  $d \sqcup i = d$ or $d \sqcup i = d'$. The first possibility can be
  excluded for the fact that it would imply $i \sqsubseteq d$, while we
  know that $i \not\in \ir{d}$. Hence we get the thesis.

\item[\ref{le:prec-irr-b:1bis})] Let $i, i' \in \diff{d'}{d}$, with
  $i \sqsubseteq i'$. Let us first assume $i$ minimal  in
  $\diff{d'}{d}$, hence $\pred{i} \sqsubseteq d$. Then
  $i' \sqsubseteq d' = d \sqcup i$. Since $i'$ is a weak prime, there
  exists $i'' \in \ir{D}$ such that {$i' \leftrightarrow i''$} 
  and either $i'' \sqsubseteq i$ or $i'' \sqsubseteq d$. The second
  possibility is excluded. In fact, if $i'' \sqsubseteq d$, then we
  would have $\pred{i}, \pred{i''} \sqsubseteq d$ and thus, by
  Lemma~\ref{le:eq-char}(\ref{le:eq-char:3}),
  $d' = d \sqcup i = d \sqcup i'' = d$, contradicting $d \neq
  d'$. Hence it must be $i'' \sqsubseteq i$. Since
  $i \sqsubseteq i'$, by transitivity $i'' \sqsubseteq i'$ and since
  {$i' \leftrightarrow i''$}, 
%  by Lemma~\ref{le:transitive},
%  $i' \leftrightarrow^* i''$, then, 
  by Lemma~\ref{le:inter-ord},  $i''=i'$ and thus $i''=i=i'$.

  If instead, $i$ is not minimal in $\diff{d'}{d}$, take
  $i_1 \sqsubseteq i$ minimal. By the argument above, we have that
  $i_1 \leftrightarrow i'$, and thus, by Lemma~\ref{le:inter-ord},
  $i_1=i'$. Recalling that $i_1 \sqsubseteq i \sqsubseteq i'$ we
  conclude $i=i'$, as desired.

  % NON PIU' USATO
  % \item[\ref{le:prec-irr-b:2})] Let $i \in \diff{d'}{d}$. Note that
  %   by (\ref{le:prec-irr-b:1bis}) element $i$ is minimal in
  %   $\diff{d'}{d}$. Therefore
  %   $\pred{i} \sqsubseteq d$.  If there were $i'' \in \ir{d}$ such
  %   that $i \leftrightarrow i''$ then, since also
  %   $\pred{i''} \sqsubseteq d$, by
  %   Lemma~\ref{le:eq-char}(\ref{le:eq-char:3}) we would get
  %   $d = d \sqcup i'' = d \sqcup i = d'$, the last equality
  %   following from point (1). But this contradicts the hypothesis
  %   that $d \prec d'$.

\item[\ref{le:prec-irr-b:3})] Let $i, i' \in \diff{d'}{d}$ be
  irreducibles. By (\ref{le:prec-irr-b:1}) we have $d' = d \sqcup i$,
  hence $i' \in \diff{d \sqcup i}{d}$. By (\ref{le:prec-irr-b:1bis})
  $i'$ is minimal in $\diff{d \sqcup i}{d}$. Therefore, by
  Lemma~\ref{le:prec-irr-a}(\ref{le:prec-irr-a:1}), we conclude
  $i \leftrightarrow i'$ .
\end{enumerate}
\end{proof}

We next show another technical result, i.e., that chains of immediate
precedence are generated in essentially a unique way by sequences of
irreducibles. Given a domain $D$ and an irreducible $i \in \ir{D}$, we
denote by $\eqclassir{i}$ the corresponding equivalence class. For
$X \subseteq \ir{D}$ we define
$\eqclassir{X} = \{ \eqclassir{i} \mid i \in X \}$.

\begin{lemma}[chains of immediate precedence]
  \label{le:chains}
  Let $D$ be a weak prime domain, $d \in \compact{D}$ and
  $\ir{d} = \{ i_1, \ldots, i_n \}$ such that the sequence
  $i_1, \ldots, i_n$ is compatible with the order (i.e., for all
  $h, k$ if $i_h \sqsubseteq i_k$ then $h \leq k$). If we let
  $d_k = \bigsqcup_{h = 1}^k i_h$ for $k \in \{ 1, \ldots, n\}$ we
  have
  \begin{center}
    $\bot = d_0 \preceq  d_1 \preceq \ldots \preceq d_n =d$
  \end{center}

  Vice versa, given a chain
  $\bot = d_0\prec d_1\prec \ldots\prec d_n$ and taking
  $i_h \in \diff{d_h}{d_{h-1}}$ for
  $h \in \{ 1, \ldots, n\}$ we have
  \begin{center}
    $d_n = \bigsqcup_{h=1}^n i_h$ \ \ and \ \
    $\forall i \in \ir{d_n}.\ \exists h \in \interval{n}.\ i
    \leftrightarrow i_h$.
  \end{center}
  Therefore
  $\eqclassir{\{i_1, \ldots, i_n \}} = \eqclassir{\ir{d_n}}$.
\end{lemma}

\begin{proof}
  For the first part, observe that for $k \in \{ 1, \ldots, n\}$ we have that
  \begin{center}
    $\pred{i_k} \sqsubseteq d_{k-1}$
  \end{center}
  In fact, recalling that $\ir{i_k} \subseteq \ir{d}$, we have that
  irreducibles in $\ir{\pred{i_k}} = \ir{i_k} \setminus \{ i_k \}$, which are
  smaller than $i_k$, must occur before in the list hence
  \begin{center}
    $\ir{\pred{i_k}} = \ir{i_k} \setminus \{ i_k \} \subseteq \{ i_1, \ldots,
    i_{k-1}\}$.
  \end{center}
  Therefore
  $\pred{i_k} = \bigsqcup \ir{\pred{i_k}} \sqsubseteq \bigsqcup \{ i_1,
  \ldots, i_{k-1}\} = d_{k-1}$. Thus we use
  Lemma~\ref{le:prec-irr-a}(\ref{le:prec-irr-a:2}) to infer
  $d_{k-1} \preceq d_{k-1} \sqcup i_k = d_k$.

  \bigskip

  For the second part, we proceed by induction on $n$.

  \begin{itemize}
  \item ($n=0$) Note that $d_0 = \bigsqcup \emptyset = \bot$ and
    $\ir{\bot} = \emptyset$, hence the thesis trivially holds.

  \item ($n>0$) By induction hypothesis
    \begin{center}
      $d_{n-1} = \bigsqcup_{h=1}^{n-1} i_h$ \ \ and \ \
    $\forall i \in \ir{d_{n-1}}.\ \exists h \in \interval{n-1}.\ i
    \leftrightarrow i_h$.
    \end{center}

    Since by construction $i_n \in \diff{d_n}{d_{n-1}}$,
    by Lemma~\ref{le:prec-irr-b}(\ref{le:prec-irr-b:1}) we deduce
    \begin{center}
      $d_n = i_n \sqcup d_{n-1} = {\bigsqcup_{h=1}^{n} i_h}$
      %\bigsqcup (\{i_n\} \cup \ir{d_{n-1}})$.
    \end{center}

    Moreover, for all $i \in \diff{d_n}{d_{n-1}}$, we have $i
    \sqsubseteq d_n = i_n \sqcup
    d_{n-1}$. By definition of weak prime domain, there exists $i'
    \leftrightarrow i$ such that $i' \sqsubseteq d_{n-1}$ or $i'
    \sqsubseteq i_n$. In the first case, since $i' \sqsubseteq
    d_{n-1}$, by the inductive hypothesis there is $h \in
    \interval{n-1}$ such that $i' \leftrightarrow i_h$. Since $i
    \leftrightarrow i' \leftrightarrow i_h$, and $i, i_h \sqsubseteq
    d_n$ are consistent, by using the fact that
      $D$ is {\wi} we deduce $i \leftrightarrow
  i_h$, as desired. If, instead, we are in the second case, namely $i'
  \sqsubseteq
  i_n$, by Lemma~\ref{le:prec-irr-b}(\ref{le:prec-irr-b:1bis}) it
  follows that $i_n = i' \leftrightarrow i$, as desired.
  \end{itemize}
\end{proof}

In a prime domain, an element admits a unique decomposition in
terms of primes (see Lemma~\ref{le:unique-decomposition}). Here the
same holds for irreducibles but only up to interchangeability. 
% Given a domain $D$ and an irreducible $i \in \ir{D}$, we denote by
% $\eqclassir{i}$ the corresponding equivalence class. For
% $X \subseteq \ir{D}$ we define
% $\eqclassir{X} = \{ \eqclassir{i} \mid i \in X \}$.

\begin{proposition}[unique decomposition up to $\leftrightarrow$]
  \label{pr:unique-dec}
  Let $D$ be a weak prime domain, let $d \in \compact{D}$, and let
  $X \subseteq D$ be a downward closed and consistent set such that
  $\eqclassir{X} \subseteq \eqclassir{\ir{d}}$. Then $d = \bigsqcup X$
  iff $\eqclassir{X} = \eqclassir{\ir{d}}$.
\end{proposition}

\begin{proof}
  ($\Rightarrow$) Let $d = \bigsqcup X$. By hypothesis
  $\eqclassir{X} \subseteq \eqclassir{\ir{d}}$. Hence we only need to
  prove that $\eqclassir{\ir{d}} \subseteq \eqclassir{X}$. Let $i \in
  \ir{d}$. Hence $i \sqsubseteq d = \bigsqcup X$. By definition of
  weak prime domain, this implies that there exists
  $i' \leftrightarrow i$ and $x \in X$ such that $i' \sqsubseteq
  x$. Since $X$ is downward closed, necessarily $i' \in X$ and thus
  $\eqclassir{i} \in \eqclassir{X}$, as desired.

  \bigskip

  ($\Leftarrow$) Let $\eqclassir{X} = \eqclassir{\ir{d}}$. We can
  prove that $\bigsqcup X = d$ by induction on
  $k(X) = |(\ir{d} \setminus X) \cup (X \setminus \ir{d}|$. If $k(X)=0$ then $X = \ir{d}$ and thus, by
  Proposition~\ref{pr:domains-irr-alg}, we conclude that
  $d = \bigsqcup X$.
  %
  If $k(X) > 0$ we distinguish two subcases.
  \begin{itemize}
  \item First assume
  $\ir{d} \setminus X \neq \emptyset$. Then take a minimal element
  $i \in \ir{d} \setminus X$. Therefore $X' = X \cup \{ i \}$ is
  downward closed and, by minimality of $i$, we have
  $\pred{i} \sqsubseteq \bigsqcup X$. Since
  $\eqclassir{X} = \eqclassir{\ir{d}}$, there is $i' \in X$ such that
  $i \leftrightarrow^* i'$ and thus, since
  $\pred{i}, \pred{i'} \sqsubseteq \bigsqcup X$ are consistent and $D$
  is {\wi}, $i \leftrightarrow i'$.  
  %
  Therefore
  \begin{equation}
    \label{eq:irr-b}
    \bigsqcup X' = \bigsqcup X \cup \{ i \} = \bigsqcup X \cup \{ i' \}
    = \bigsqcup X.
  \end{equation}

  Since $\eqclassir{X'} =  \eqclassir{X}  =  \eqclassir{\ir{d}}$ and
  $|\ir{d} \setminus X'| = |\ir{d} \setminus X| -1$, we have
  $k(X') < k(X)$, and thus by inductive hypothesis $\bigsqcup X' =
  d$. Hence, using (\ref{eq:irr-b}), we get $\bigsqcup X = d$, as
  desired.

\item If instead $\ir{d} \setminus X = \emptyset$, i.e.,
  $\ir{d} \subseteq X$, since $k(X)>0$, it must be
  $X \setminus \ir{d} \neq \emptyset$. Consider a maximal element
  $i \in X \setminus \ir{d}$, and let $X' = X \setminus \{i\}$. Clearly, $X'$ is downward closed because so are $X$ and $\ir{d}$.  Since
  $\eqclassir{X} = \eqclassir{\ir{d}}$, there is
  $i' \in \ir{d} \subseteq X$ such that $i \leftrightarrow^* i'$. Since $X$ is consistent and $D$ is {\wi}, $i \leftrightarrow i'$. Therefore
    \begin{equation}
    \label{eq:irr-c}
    \bigsqcup X = \bigsqcup X' \cup \{ i \} = \bigsqcup X' \cup \{ i' \}
    = \bigsqcup X'.
  \end{equation}
  Since by construction $k(X') = k(X)-1$, the inductive hypothesis
  gives us $\bigsqcup X'=d$. Hence, using (\ref{eq:irr-c}), we get
  $\bigsqcup X = d$, as desired.
  \end{itemize}
\end{proof}

We explicitly observe that, by the above result, whenever $X = \eqclassir{\ir{d}}$ for some $d \in \compact{D}$ then $d$ is uniquely determined by $X$.

We now have all the tools needed for mapping our domains to an {\esabbr}.

\begin{definition}[{event structure} for a weak prime domain]
\label{de:esfusdom}
  Let $D$ be a weak prime domain. The {\esabbr}
  $\ev{D} = \langle E, \#, \vdash \rangle$ is defined as
  follows
  \begin{itemize}

  \item $E = \eqclassir{\ir{D}}$;

  \item $e \# e'$ if there is no $d \in \compact{D}$ such that
    $e, e' \in \eqclassir{\ir{d}}$;

  \item $X \vdash e$ if there is $i \in e$ such that
    $\eqclassir{\ir{i} \setminus \{ i \}} \subseteq X$.

  \end{itemize}

  Given a morphism $f : D_1 \to D_2$, its image
  $\ev{f} : \ev{D_1} \to \ev{D_2}$ is defined  for
  $\eqclassir{i_1} \in {E_1}$ as 
  %
  $\ev{f}(\eqclassir{i_1})= \eqclassir{i_2}$,
  where $i_2 \in \diff{f(i_1)}{f(\pred{i_1})}$, and
  $\ev{f}(\eqclassir{i_1})$ is undefined if $f(\pred{i_1}) = f(i_1)$.
\end{definition}

The events in $\ev{D}$ are equivalence classes of irreducibles. Two events $e$, $e'$ are consistent (not in conflict) when there is some compact element $d$ such that $e, e' \in \eqclassir{\ir{d}}$. Spelled out, this means that there are irreducibles $i \in e$ and $i' \in e'$ such that $i, i' \sqsubseteq d$, i.e., there are minimal enablings of the events $e$ and $e'$ in the same configuration. Finally, an event $e$ is enabled by a set $X$ when $X$ includes, up to intechangeability, all the predecessors of $e$.

Note that the definition above is well-given: in particular, there is no
ambiguity in the definition of the image of a morphism, since by
Lemma~\ref{le:prec-irr-b}(\ref{le:prec-irr-b:3}) we easily conclude
that for all $i_2, i_2' \in \diff{f(i_1)}{f(\pred{i_1})}$, it
holds $i_2 \leftrightarrow i_2'$ (this is argued in detail in the proof of Lemma~\ref{le:domain-to-es-wd}).

In the following we often use a technical lemma that holds in any domain.

\begin{lemma}
  \label{le:inf}
  Let $D$ be a domain and $a, b, c \in D$ such that
  $c \sqsubseteq a$ and $c \preceq b$. Then
  either $b \sqsubseteq a$ or $c = a \sqcap b$.
\end{lemma}

\begin{proof}
  Recall that in a domain the meet of non-empty  sets
  exists. Since $c$ is a lower bound for $a$ and $b$, necessarily
  $c \sqsubseteq a\sqcap b \sqsubseteq b$. If it were
  $c \neq a\sqcap b$ then we would have $a \sqcap b = b$, hence
  $b \sqsubseteq a$, as desired.
\end{proof}

\begin{lemma}[{from weak prime domains to event structures}]
  \label{le:domain-to-es-wd}
  Let  $D$ be a weak prime domain. Then $\ev{D}$ is an {\esabbr}. Moreover, given two weak prime domains $D_1$, $D_2$ and a
  morphism $f : D_1 \to D_2$, its image
  $\ev{f} : \ev{D_1} \to \ev{D_2}$ is an {\esabbr} morphism.
\end{lemma}

\begin{proof}
  %

  % \begin{itemize}

  % \item $X \in Con$ and $Y \subseteq X$ implies $Y \in Con$\\[1mm]
  %   %
  %   This is obvious. In fact if $X \in Con$, by definition $X
  %   \subseteq \eqclassir{\ir{d}}$
  %   for some $d \in \compact{D}$. Hence if we take
  %   $Y \subseteq X$, we have
  %   $Y \subseteq X \subseteq \eqclassir{\ir{d}}$ hence
  %   we conclude that $Y \in Con$.

  We first show that $\ev{D}$ is a live {\esabbr}. In fact, it is an
  {\esabbr}: if $X \vdash e$ and $X \subseteq Y$ then
  $Y \vdash e$. In fact, by definition, if $X \vdash e$ then there
  exists $i \in e$ such that
  $\eqclassir{\ir{i} \setminus \{i\}} \subseteq X$. Hence if
  $X \subseteq Y$ it immediately follows that $Y \vdash e$.
  %
  Moreover $\ev{D}$ is live. The fact that conflict is saturated
  follows immediately by the definition of conflict and the
  characterisation of configurations provided later in
  Lemma~\ref{le:comp-conf}. Conflict is irreflexive since for any
  $e \in \ev{D}$, if $e = \eqclassir{i}$ then
  $e \in \eqclassir{\ir{i}}$, which is a configuration again by
  Lemma~\ref{le:comp-conf}.\footnote{This forward reference is only
    useful to simplify the structure of the presentation and to avoid
    breaking the statement in two parts, but it
    introduces no cyclic dependency.}

  \bigskip

  Given a morphism $f : D_1 \to D_2$, its image
  $\ev{f} : \ev{D_1} \to \ev{D_2}$ is defined for
  $\eqclassir{i_1} \in {E_1}$ as
  %
  $\ev{f}(\eqclassir{i_1})= \eqclassir{i_2}$,
  where $i_2 \in \diff{f(i_1)}{f(\pred{i_1})}$, and
  $\ev{f}(\eqclassir{i_1})$ is undefined if $f(\pred{i_1}) = f(i_1)$.
  %
  First observe that $\ev{f}(\eqclassir{i_1})$ does
  not depend on the choice of the representative. In fact, let
  $i_2, i_2' \in \diff{f(i_1)}{f(\pred{i_1})}$.  Since
  $\pred{i_1} \prec i_1$, by definition of domain morphism,
  $f(\pred{i_1}) \prec f(i_1)$. Thus, by
  Lemma~\ref{le:prec-irr-b}(\ref{le:prec-irr-b:3}),
  $i_2 \leftrightarrow i_2'$.

  We next show that $\ev{f}$ is an {\esabbr} morphism.
  %
  \begin{itemize}
  \item If $\ev{f}(e_1) \# \ev{f}(e_1')$ then $e_1 \# e_1'$.\\
    %
    We prove the contronominal, namely if $e_1,e_1'$ consistent
    then $\ev{f}(e_1),\ev{f}(e_1')$ consistent.

    The fact that $e_1, e_1'$ consistent means that there exists
    $d_1 \in \compact{D_1}$ such that
    $e_1, e_1' \in \eqclassir{\ir{d_1}}$. We show that
    $\ev{f}(e_1), \ev{f}(e_1') \in \eqclassir{\ir{f(d_1)}}$ (note
    that $f(d_1)$ is a compact, since $f$ is a domain morphism).

    Let us show, for instance, that
    $\ev{f}(e_1) \in \eqclassir{\ir{f(d_1)}}$. The fact that
    $e_1 \in \eqclassir{\ir{d_1}}$ means that $e_1 = \eqclassir{i_1}$
    for some $i_1 \sqsubseteq d_1$. By definition
    $\ev{f}(e_1) = \eqclassir{i_2}$, where
    $i_2 \in \diff{f(i_1)}{f(\pred{i_1})}$ (since $\ev{f}(e_1)$ is
    defined the irreducible difference cannot be empty). Now, since
    $i_1 \sqsubseteq d_1$ we have that $f(i_1) \sqsubseteq f(d_1)$,
    whence $i_2 \sqsubseteq f(i_1) \sqsubseteq f(d_1)$ and
    $\ev{f}(\eqclassir{i_1}) = \eqclassir{i_2} \in
    \eqclassir{\ir{f(d_1)}}$, as desired.

  \item If $\ev{f}(e_1) = \ev{f}(e_1')$ and $e_1 \neq e_1'$ 
    then $e_1 \# e_1'$.\\
    %
    We prove the contronominal, namely if $e_1, e_1'$ consistent and
    $\ev{f}(e_1) = \ev{f}(e_1')$ then $e_1=e_1'$.

    Assume $e_1, e_1'$ consistent and $\ev{f}(e_1) = \ev{f}(e_1')$. By
    the first condition and the definition of conflict, there must be $d_1 \in \compact{D_1}$ such
    that $e_1, e_1' \in \eqclassir{\ir{d_1}}$, namely
    $e_1=\eqclassir{i_1}$ and ${e_1'}=\eqclassir{i_1'}$ with
    $i_1, i_1' \sqsubseteq d_1$.

    Moreover, $\ev{f}(\eqclassir{i_1}) = \eqclassir{i_2}$ and
    $\ev{f}(\eqclassir{i_1'}) = \eqclassir{i_2'}$ where $i_2$ and
    $i_2'$ are in $\diff{f(i_1)}{f(\pred{i_1})}$ and
    $\diff{f(i_1')}{f(\pred{i_1'})}$, respectively, and
    $\eqclassir{i_2} = \eqclassir{i_2'}$, which means
    $i_2 \leftrightarrow^* i_2'$, and in turn, being $i_2$ and $i_2'$
    consistent, by the fact that $D$ is {\wi},
    implies
    $i_2 \leftrightarrow i_2'$.

    We distinguish two cases.

    \begin{enumerate}[A.]
    \item If $i_1$ and $i_1'$ are comparable, e.g.,
      if $i_1 \sqsubseteq i_1'$, then $i_1 = i_1'$ and we are
      done. In fact, otherwise, if $i_1 \neq i_1'$ we have
      $\pred{i_1} \prec i_1 \sqsubseteq \pred{i_1'} \prec i_1'$.  By
      monotonicity of $f$ we have
      $f(\pred{i_1}) \prec f(i_1) \sqsubseteq f(\pred{i_1'}) \prec
      f(i_1')$
      (where strict inequalities $\prec$  are motivated by the 
      definition of $\ev{f}$, since
      both $\ev{f}(\eqclassir{i_1})$ and $\ev{f}(\eqclassir{i_1'})$
      are defined).
      % 
      Now notice that
      $\pred{i_2} \sqsubseteq i_2 \sqsubseteq f(i_1) \sqsubseteq
      f(\pred{i_1'})$. Moreover,
      $i_2' \in \diff{f(i_1')}{f(\pred{i_1'})}$, therefore
      $\pred{i_2'} \sqsubseteq i_2' \sqsubseteq f(\pred{i_1'})$.
      Hence, using the fact that $i_2 \leftrightarrow i_2'$, by
      Lemma~\ref{le:eq-char}(\ref{le:eq-char:3}) we have
      \begin{center}
        $f(\pred{i_1'}) = f(\pred{i_1'}) \sqcup i_2 = f(\pred{i_1'})
        \sqcup i_2' = f(i_1')$
      \end{center}
      contradicting  the fact that $f(\pred{i_1'}) \prec f(i_1')$.

      \smallskip

    \item Assume now that $i_1$ and $i_1'$ are uncomparable{: we show that this leads to a contradiction.}   Let 
      $p = \pred{i_1} \sqcup \pred{i_1'}$. We can also assume
      $i_1, i_1' \not\sqsubseteq p$. In fact, otherwise, e.g., if
      $i_1 \sqsubseteq p$, then, by the defining property of weak
      prime domains, we derive the existence of
      $i_1'' \leftrightarrow i_1$ such that
      $i_1'' \sqsubseteq \pred{i_1}$ or
      $i_1'' \sqsubseteq \pred{i'_1}$. The first possibility can be
      excluded because it would imply $i_1'' \sqsubseteq i_1$. Hence,
      since $i_1'' \leftrightarrow i_1$, by
      Lemma~\ref{le:inter-ord}, we would get $i_1=i_1''$,
      contradicting $i_1'' \sqsubseteq \pred{i_1}$. Then it should be
      $i_1'' \sqsubseteq \pred{i_1'} \sqsubseteq i_1'$. Therefore, if
      we take $i_1''$ as representative of the equivalence class we
      are back to case A above.

      Using the fact that $i_1, i_1' \not\sqsubseteq p$ and
      $\pred{i_1}, \pred{i_1'} \sqsubseteq p$, by
      Lemma~\ref{le:prec-irr-a}(\ref{le:prec-irr-a:2}) we deduce that
      $p \prec p \sqcup i_1$ and $p \prec p \sqcup i_1'$.
      % Moreover
      % $[p, p \sqcup i_1] \sim [\pred{i_1}, i_1]$.  In fact,
      % $p \sqcap i_1 = \pred{i_1}$ by Lemma~\ref{le:inf}, and
      % $p \sqcup i_1 = p \sqcup i_1$. Similarly,
      % $[p, p \sqcup i_1'] \sim [\pred{i_1}, i_1']$.
      %
      Hence $f(p) \prec f(p \sqcup i_1)$ with strict inequality again
      motivated by the definition of $\ev{f}$, since
      $\ev{f}(\eqclassir{i_1})$ is defined.

      By Lemma~\ref{le:prec-irr-b}(\ref{le:prec-irr-b:1}), since
      $i_2 \in \diff{f(i_1)}{f(\pred{i_1})}$ and
      $i_2' \in \diff{f(i_1')}{f(\pred{i_1'})}$, we have
      \begin{equation}
        \label{eq:adding}
        f(\pred{i_1}) \sqcup i_2 = f(i_1) 
        \qquad f(\pred{i_1'}) \sqcup i_2' = f(i_1')
      \end{equation}

      Now, observe that
      \begin{center}
      $\begin{array}{lll}
         f(p \sqcup i_1)  =  \\
         = f(\pred{i_1} \sqcup \pred{i_1'} \sqcup i_1)\\
         % 
         =  f(\pred{i_1'} \sqcup i_1)\\
         % 
         =  f(\pred{i_1'}) \sqcup f(i_1) 
      & \mbox{[preservation of $\sqcup$]}\\
      % 
         =  f(\pred{i_1'}) \sqcup f(\pred{i_1}) \sqcup i_2 
      & \mbox{[by~(\ref{eq:adding})]}\\
      % 
         =   f(\pred{i_1'}) \sqcup f(\pred{i_1}) \sqcup i_2' 
      & \mbox{[by Lemma~\ref{le:eq-char}(\ref{le:eq-char:3}),} \\
         & \mbox{\ since $i_2 \leftrightarrow i_2'$]}\\
      % 
                          =  f(i_1') \sqcup f(\pred{i_1}) 
         & \mbox{[by~(\ref{eq:adding})]}\\
         % 
                          =  f(\pred{i_1} \sqcup i_1')
         & \mbox{[preservation of $\sqcup$]}\\
         %
                          =  f(\pred{i_1} \sqcup \pred{i_1'} \sqcup  i_1')\\
         %
                          =  f(p \sqcup  i_1')\\
       \end{array}
       $
     \end{center}
     Since $p \prec p \sqcup i_1$ and $p \prec p \sqcup i_1'$, by
     Lemma~\ref{le:inf}, we have
     $(p \sqcup i_1) \sqcap (p \sqcup i_1') = p$.
     %
     Therefore, on the one hand
     $f((p \sqcup i_1) \sqcap (p \sqcup i_1')) = f(p)$. On the other
     hand, since the meet is an immediate predecessor, by definition
     of weak domain morphism (Definition~\ref{de:domain-category}), it
     is preserved:
     $f((p \sqcup i_1) \sqcap (p \sqcup i_1')) = f(p \sqcup i_1)
     \sqcap f(p \sqcup i_1') = f(p \sqcup i_1) = f(p \sqcup i_1')$.
     Putting things together,
     $f(p) = f(p \sqcup i_1) = f(p \sqcup i_1')$, contradicting  the
     fact that $f(p) \prec f(p \sqcup i_1)$.
   \end{enumerate}

   \item if $C_1 \vdash_1 \eqclassir{i_1}$ and
     $\ev{f}(\eqclassir{i_1})$ is defined then
     $\ev{f}(C_1) \vdash_2 \ev{f}(\eqclassir{i_1})$

     Recall that $C_1 \vdash_1 \eqclassir{i_1}$ means that 
     $\eqclassir{\ir{i_1'} \setminus \{ i_1'\}} =
     \eqclassir{\ir{\pred{i_1'}}} \subseteq C_1$ for some
     $i_1' \leftrightarrow i_1$.

     By definition, $\ev{f}(\eqclassir{i_1}) = \eqclassir{i_2}$ where
     $i_2 \in \diff{f(i_1')}{f(\pred{i_1'})}$. We show that
     $\ev{f}(C_1) \vdash_2 \eqclassir{i_2}$, namely that
     \begin{equation}
       \label{eq:new}
       \eqclassir{\ir{i_2}\setminus \{ i_2\} } =
       \eqclassir{\ir{\pred{i_2}}} \subseteq \ev{f}(C_1)
     \end{equation}
     Observe that since $i_2 \in \diff{f(i_1')}{f(\pred{i_1'})} $ and
     distinct elements in $\diff{f(i_1')}{f(\pred{i_1'})}$ are
       incomparable by
       Lemma~\ref{le:prec-irr-b}(\ref{le:prec-irr-b:1bis}), it holds
       $\pred{i_2} \sqsubseteq f(\pred{i_1'})$. Therefore, we have
     \begin{center}
       $\ir{\pred{i_2}} \subseteq \ir{f(\pred{i_1'})}$
     \end{center}
     Hence, in order to conclude~(\ref{eq:new}), it suffices to show that
     \begin{equation}
       \label{eq:obj}
       \eqclassir{\ir{f(\pred{i_1'})}} \subseteq \ev{f}(C_1)
     \end{equation}

     In order to reach this result, first note that, by
     Lemma~\ref{le:chains}, if
     $\ir{\pred{i_1'}} = \{ j_1^1, \ldots, j_1^n \}$ is a sequence of
     irreducibles compatible with the order, we can obtain a
     $\preceq$-chain
     \begin{center}
       $\bot = d_1^0 \preceq d_1^1 \preceq \ldots \preceq d_1^n =
       \pred{i_1'} \prec i_1'$
     \end{center}
     We can extract a strictly increasing subsequence
     \begin{center}
       $\bot = d_1'^0 \prec d_1'^1 \prec \ldots \prec d_1'^m =
       \pred{i_1'} \prec i_1'$
     \end{center}
     and, if we take irreducibles $j_1'^1, \ldots, j_1'^m$ in
     $\diff{d_1'^{i}}{d_1'^{i-1}}$, again by Lemma~\ref{le:chains} we
     know that
     \begin{equation}
       \label{eq:chain}
       \eqclassir{\ir{\pred{i_1'}}} = \eqclassir{\{j_1'^1, \ldots,
         j_1'^m\}}
     \end{equation}

     Since $f$ is a domain morphism, it preserves $\preceq$, namely
     \begin{center}
       $\bot = f(d_1'^0) \preceq f(d_1'^1) \preceq \ldots \preceq f(d_1'^m) =
       f(\pred{i_1'}) \prec f(i_1')$
     \end{center}
     where the last inequality is strict since
     $\ev{f}(\eqclassir{i_1'}) = \eqclassir{i_2}$ is
     defined. Moreover, whenever $f(d_1'^{h-1}) \prec f(d_1'^h)$, then
     $\ev{f}(\eqclassir{j_1'^h}) = \eqclassir{\ell_2^h}$ where $\ell_2^h$
     is any irreducible in $\diff{f(d_1'^h)}{f(d_1'^{h-1})}$, otherwise
     $\ev{f}(\eqclassir{j_1'^h})$ is undefined.

     Once more by Lemma~\ref{le:chains} we know that
     \begin{center}
       $\eqclassir{\ir{f(\pred{i_1'})}} = \eqclassir{\{\ell_2^1, \ldots,
         \ell_2^m\}} = \ev{f}(\eqclassir{\{j_1'^1, \ldots, j_1'^m\}})$,
     \end{center}
     % \todo{Some $\ell_2^i$ are undefined, find a good notation} 
     thus, using (\ref{eq:chain})
     \begin{equation}
       \label{eq:chain1}
       \eqclassir{\ir{f(\pred{i_1'})}} =
       \ev{f}(\eqclassir{\ir{\pred{i_1'}}}).
     \end{equation}
     Hence, recalling that, by hypothesis,
     $\eqclassir{\ir{\pred{i_1'}}} \subseteq C_1$, we conclude the desired
     inclusion~(\ref{eq:obj}).
  \end{itemize}
\end{proof}

Since in a prime domain irreducibles coincide with
primes (Proposition~\ref{pr:irr-prime-alg}), $\leftrightarrow$ is the
identity (Lemma~\ref{le:interchange-id-pad}) and $\diff{d'}{d}$ is a
singleton when $d \prec d'$, the construction above produces the prime
{\esabbr} $\pes(D)$ as defined in Section~\ref{se:background}.

Given a weak prime domain $D$, the finite configurations of the {\esabbr}
$\ev{D}$ exactly correspond to the elements in
$\compact{D}$. Moreover, in such {\esabbr} we have a minimal enabling
$C \vdash_0 e$ when there is an irreducible in $e$ (recall that events
are equivalence classes of irreducibles) such that $C$ contains all and only
(the equivalence classes of) its predecessors.

\begin{lemma}[compacts vs. configurations]
  \label{le:comp-conf}
  Let $D$ be a weak prime domain and $C \subseteq \ev{D}$ a finite set
  of events.  Then $C$ is a configuration in the {\esabbr} $\ev{D}$
  iff there exists a unique $d \in \compact{D}$ such that $C =
  \eqclassir{\ir{d}}$. Moreover, for any $e \in \ev{D}$ we have that
  $C \vdash_0 e$ iff $C = \eqclassir{\ir{i} \setminus \{ i \}}$ for
  some $i \in e$.
\end{lemma}

\begin{proof}
  The left to right implication {of the first part} follows by proving that, given a
  configuration $C \in \conff{\ev{D}}$, there exists
  $X \subseteq \ir{D}$ downward closed and consistent such that
  $\eqclassir{X} = C$. Hence, if we let $d = \bigsqcup X$, by
  Proposition~\ref{pr:unique-dec}, we have that
  $C = \eqclassir{X} = \eqclassir{\ir{d}}$. Moreover, $d$ is uniquely
  determined, since, by the same proposition we have that for any
  other $X'$ such that $\eqclassir{X'} = C$, since
  $\eqclassir{X'} = C = \eqclassir{X} = \eqclassir{\ir{d}}$,
  necessarily $d = \bigsqcup X'$.

  Let us thus prove the existence of $X \subseteq \ir{D}$ consistent
  and downward closed such that $\eqclassir{X} = C$.  
  %
  We proceed by induction on the cardinality of $C$.

  % know that $C$ is consistent, i.e., for all $e, e' \in C$ it
  % holds $\neg (e \# e')$. This means that $e = \eqclassir{i}$,
  % $e' = \eqclassir{i'}$ and $d \in \compact{D}$ such
  % that $i, i' \sqsubseteq d$. Since $D$ is coherent this implies
  % that there exists $d \in \compact{D}$ such that for all
  % $e = \eqclassir{i} \in C$, it holds $i \sqsubseteq d$, i.e.,
  % $C \subseteq \eqclassir{\ir{d}}$.

  % We can define
  % $X = \{ j \in \ir{d} \mid \eqclassir{j} \in C \}$.
  % %
  % The set $X$ is clearly consistent and $\eqclassir{X} = C$. The fact
  % that it is downward closed can be proved by induction on the
  % cardinality of $C$, as follows
  \begin{itemize}
  \item if $|C| = 0$, namely $C = \emptyset$ then we can take $X= \emptyset$,
    and trivially conclude.

  \item if $|C|>0$, since $C$ is secured, there is
    $\eqclassir{i} \in C$ such that
    $C' = C \setminus \{ \eqclassir{i} \} \vdash \eqclassir{i}$.\
    %
    By inductive hypothesis there is $X' \subseteq \ir{D}$, downward
    closed and consistent such that $\eqclassir{X'} = C'$.
    %
%     We can
%     assume without loss of generality that $i \in X$.  Observe that
%     \begin{center}
% %      $X' = X \setminus \{ i \} = \{ j \in \ir{D} \mid \eqclassir{j} \in C'\ \land\
% %      j \sqsubseteq d \}$
%       $X' = X \setminus \{ i \} = {\{ j \in \ir{d} \mid \eqclassir{j} \in C' \}}$
%     \end{center}
%     hence, by inductive hypothesis, $X'$ is {downward} closed.

    The fact that
    $C' = C \setminus \{ \eqclassir{i} \} \vdash \eqclassir{i}$ means
    that for some $i' \in \ir{D}$ such that $i' \leftrightarrow^* i$, it holds
    $\eqclassir{\ir{i'} \setminus \{i'\}} = \eqclassir{\ir{\pred{i'}}}
    \subseteq C'$.
    %
    Therefore, there is $X'' \subseteq X'$ such that
    $\eqclassir{X''} = \eqclassir{\ir{\pred{i}}}$ and thus, by
    Proposition~\ref{pr:unique-dec},
    $\pred{i'} \sqsubseteq \bigsqcup X'$.
    %
    We can assume, without loss of generality that
    $\ir{\pred{i'}} \subseteq X'$. If not, we can replace $X'$ by
    $X' \cup \ir{\pred{i'}}$. By the consideration above, it is
    consistent and it has the same join of $X'$.

    Now, an induction on the cardinality $k$ of
    $X' \setminus \ir{\pred{i'}}$ allows us to show that $\{i', j\}$
    consistent for all $j \in X'$. If $k=0$ then
    $X' \setminus \ir{\pred{i'}} =\emptyset$ and the thesis is
    trivial. Otherwise, consider $j' \in X' \setminus \ir{\pred{i'}}$
    maximal and $X'' = X' \setminus \{j'\}$. Since
    $|X' \setminus \ir{\pred{i'}}|=k-1$, by inductive hypothesis, for
    all $j \in X''$, we have $\{j,i'\}$ consistent. Now, since
    $j, \pred{i} \sqsubseteq \bigsqcup X'$, we have that
    $\{j, \pred{i}\}$ is consistent. Moreover, since
    $\ir{j'} \setminus\{j'\} = \ir{\pred{j'}} \subseteq X''$, we have
    that $\{i, \pred{j'}\}$ is consistent.

    Finally, recalling that, since $C$ is
    consistent, we have that
    $\neg (\eqclassir{j'} \# \eqclassir{i'})$, i.e., there is
    $d \in \compact{D}$ such that
    $\{ \eqclassir{j'}, \eqclassir{i'} \} \subseteq
    \eqclassir{\ir{d}}$. More explicitly, this means that there are
    $j'', i'' \in \ir{D}$ such that $j'' \leftrightarrow^* j'$,
    $i'' \leftrightarrow^* i'$ and $j', i''$ consistent.
    %
    Since $D$ is {\wi}, by condition (\ref{de:well-interchange:2}) of
    Definition~\ref{de:well-interchange}, we conlcude $j', i'$
    consistent.

    We can thus conclude that $X = X' \cup \{ i' \}$ is consistent,
    and downward closed since
    $\ir{\pred{i'}} \subseteq X'$. Hence we conclude.
  \end{itemize}

  \bigskip

  For the converse, let $C = \eqclassir{\ir{d}}$. Let
  $\bot = d_0 \prec d_1 \prec \ldots d_{n-1} \prec d_n = d$ be a chain
  of immediate precedence and for each $h \in \{1, \ldots, n\}$ take
  $i_h \in \diff{d_h}{d_{h-1}}$. By Lemma~\ref{le:chains},
  $d = \bigsqcup \{ i_1, \ldots, i_n\}$ and
  $\eqclassir{\ir{d}} = \eqclassir{\{ i_1, \ldots, i_n\}}$. Moreover,
  for all $h \in \{1, \ldots, n\}$, we have
  $\eqclassir{\ir{i_h} \setminus \{ i_h \}} \subseteq
  \eqclassir{\ir{d_{h-1}}}$, hence
  $\eqclassir{\ir{d_{h-1}}} \vdash \eqclassir{i_h}$. Therefore $C$ is
  secured. Moreover, it is clearly consistent and thus
  $C \in \conf{\ev{D}}$.

  \bigskip

  The second part follows immediately by Definition~\ref{de:esfusdom}.
\end{proof}

Given the lemma above, it is now possible to state how weak prime 
domains relate to connected {\esabbr}.

\begin{proposition}[{from weak prime domains to connected ES}]
  \label{pr:domain-to-fes}
  Let  $D$ be a weak prime domain. Then $\ev{D}$ is a connected {\esabbr}.
\end{proposition}

\begin{proof}
  We have to show that
  if $X \vdash_0 e$ and $X' \vdash_0 e$, then $X \conn{e}^* X'$.  Note
  that, by Lemma~\ref{le:comp-conf}, 
  % era \ref{le:minimal}  
  from $X \vdash_0 e$ and
  $X' \vdash_0 e$, we deduce that there exists $i, i' \in e$ such that
  $\eqclassir{\ir{i} \setminus \{i\}} = X$ and
  $\eqclassir{\ir{i'} \setminus \{i'\}} = X'$. Since $i, i' \in e$ we
  deduce that $i \leftrightarrow^* i'$, namely
  $i = i_0 \leftrightarrow i_1 \leftrightarrow \ldots \leftrightarrow
  i_n = i'$. We proceed by induction on $n$. The base case $n=0$ is
  trivial. If $n >0$ then from
  $i \leftrightarrow i_1 \leftrightarrow^* i'$ we have that
  $i_1 \in e$ and, if we let
  $X_1 = \eqclassir{\ir{i_1} \setminus \{i_1\}}$, then
  $X_1 \vdash_0 e$. By inductive hypothesis, we know that
  $X_1 \conn{e}^* X'$. Moreover, since $i \leftrightarrow i_1$,
  % \ICrem{, by Lemma~\ref{le:inter-cons-ord}}
  the irreducibles $i$ and $i_1$ are consistent. Hence, by definition
  of conflict in $\ev{D}$, also $X \cup X_1 \cup \{e\}$ is consistent
  and hence $X \conn{e} X_1$. Therefore $X \conn{e}^* X'$, as desired.
\end{proof}

\subsection{Relating Categories of Models}
\label{ss:relating-cats}
We show that, at a categorical level, the constructions taking a weak prime domain to an
{\esabbr} and an {\esabbr} to a domain (the domain of its configurations) establish
a coreflection between the corresponding categories.
%
This becomes an equivalence when it is restricted to the full subcategory of connected {\esabbr}.

\begin{theorem}[coreflection of $\es$ and $\WDom$]
 \label{th:es-dom-equivalence}
 The functors $\zdom : \es \to \WDom$ and $\zev: \WDom \to \es$ form
 a coreflection $\zev \dashv \zdom$.  It restricts to an equivalence between $\WDom$ and
 $\ces$.
\end{theorem}

\begin{proof}
  Let ${E}$ be an {\esabbr}. Recall that the corresponding domain of
  configurations is
  $\dom{{E}} = \langle \conf{{E}}, \subseteq \rangle$.  Then,
  $\ev{\dom{{E}}} = \langle E', \#', \vdash'\rangle$, where the set of
  events $E'$ is defined as
  \begin{center}
    $E' = \eqclassir{\ir{\dom{{E}}}} = \{ \eqclassir{\esir{C}{e}} \mid C
    \vdash_0 e \}$
  \end{center}

  By
  Lemma~\ref{le:es-to-fusion-domain}(\ref{le:es-to-fusion-domain:4}),
  the equivalence class of an irreducible $\esir{C}{e}$ consists of
  all minimal enablings of event $e$ which are connected. Therefore we
  can define a morphism, which is the counit of the adjunction, as follows:
  \begin{center}
    $\begin{array}{lccc}
       \theta_{{E}} : & \ev{\dom{{E}}} &  \to & {E}\\
                             & \eqclassir{\esir{C}{e}}
                             % \esir{C}{e} 
                             & \mapsto & e
     \end{array}
     $
  \end{center}
  %
  Observe that $\theta_{{E}}$ is surjective. In fact ${E}$ is live and
  thus any event $e \in E$ has at least a minimal enabling
  $C \vdash_0 e$. If we let $I = \esir{C}{e}$, then
  $\eqclassir{I} \in \ev{\dom{{E}}}$ and $\theta_{{E}}(\eqclassir{I}) = e$.
  % \todo{Probably better to extract the definition and properties of
  %  the unit and counit}
  %
  The mapping $\theta_E$ is clearly
  a  morphism of event structures. In fact, observe that
  \begin{itemize}

  \item For 
  % \todo{AC: scambiati primo e secondo punto di questa dimostrazione, per coerenza con Def.~\ref{de:es-morphism}.} 
  $I_1, I_2 \in \ir{\dom{{E}}}$, if
    $\theta_{{E}}(\eqclassir{I_1}) \#
    \theta_{{E}}(\eqclassir{I_2})$
    then $\eqclassir{I_1} \#' \eqclassir{I_2}$.\\
    %
    Let $I_1 = \esir{C_1}{e_1}$ and $I_2 = \esir{C_2}{e_2}$. If
    $\theta_{{E}}(\eqclassir{I_1}) = e_1 \# e_2 =
    \theta_{{E}}(\eqclassir{I_2})$, then there cannot be any
    configuration $C \in \conf{{E}}$ such that $I_1, I_2 \subseteq
    C$. Hence, by definition of conflict in $\ev{\dom{{E}}}$, we have
    $\eqclassir{I_1} \#' \eqclassir{I_2}$.

  \smallskip

  \item For  $I_1, I_2 \in \ir{\dom{{E}}}$, with
    $\eqclassir{I_1} \neq \eqclassir{I_2}$, we have that
    $\theta_{{E}}(\eqclassir{I_1}) =
    \theta_{{E}}(\eqclassir{I_2})$
    implies $\eqclassir{I_1} \#' \eqclassir{I_2}$.

    In fact, by
    Lemma~\ref{le:es-to-fusion-domain}(\ref{le:es-to-fusion-domain:2}),
    the irreducibles $I_1$ and $I_2$ are of the kind
    $I_1 = \esir{C_1}{e_1}$ and $I_2 = \esir{C_2}{e_2}$. We show that
    if $\eqclassir{I_1}$ and $\eqclassir{I_2}$ are consistent and
    $\theta_{{E}}(\eqclassir{I_1}) = \theta_{{E}}(\eqclassir{I_2})$
    then $\eqclassir{I_1} = \eqclassir{I_2}$.

    Assume
    $\theta_{{E}}(\eqclassir{I_1}) =
    \theta_{{E}}(\eqclassir{I_2})$,
    hence $e_1=e_2$. Since $\eqclassir{I_1}$ and
    $\eqclassir{I_2}$ are consistent, there exists
    $k \in \compact{\dom{{E}}}$ such that
    $\eqclassir{I_1}, \eqclassir{I_2} \in \eqclassir{\ir{k}}$.  
    Compacts in $\dom{{E}}$ are finite configurations, hence the condition
    amounts to the existence of $C \in \conff{{E}}$ such that
    $\eqclassir{I_1}, \eqclassir{I_2} \in \eqclassir{\ir{C}}$, i.e.,
    there  are $I_1', I_2'$ with $I_i \leftrightarrow^* I_i'$ for
    $i \in \{ 1,2\}$, such that $I_1', I_2' \subseteq C$. Since the
    choice of the representatives is irrelevant, we can assume
    that $I_1 = I_1'$ and $I_2 = I_2'$. Summing up, $I_1$ and $I_2$
    are consistent minimal enablings of the same event, hence by
    Lemma~\ref{le:es-to-fusion-domain}(\ref{le:es-to-fusion-domain:4}), $I_1 \leftrightarrow I_2$,
    i.e., $\eqclassir{I_1} = \eqclassir{I_2}$, as desired.

    \smallskip

  \item
    %
    For the enabling relation, we have to show that if
    $X \vdash' \eqclassir{\esir{C}{e}}$ then
    $\theta_E(X) \vdash \theta(\eqclassir{\esir{C}{e}}) = e$.
    %
    Assume $X \vdash' \eqclassir{\esir{C}{e}}$. According to the
    definition of the functor ${\ensuremath{\mathcal{E}}}$, this means
    that there exists
    $i \in \eqclassir{\esir{C}{e}}$ such that
    ${\eqclassir{\ir{i} \setminus \{i \}} \subseteq X}$.
    % $\eqclassir{\ir{\esir{C}{e}} \setminus \{ \esir{C}{e} \}} \subseteq
    % X$.
    Let such $i \in \eqclassir{\esir{C}{e}}$ be $i = \esir{C'}{e}$
    with $C' \vdash_0 {e}$. We have
    \begin{center}
      $\ir{\esir{C'}{e}} \setminus \{ \esir{C'}{e} \} = \ir{C'} = \{
      \eqclassir{\esir{ C''}{ e''}} \mid \esir{ C''}{ e''} \subseteq C'\}$.
    \end{center}    
    %
    Therefore from
    $\eqclassir{\ir{\esir{C'}{e'}} \setminus \{ \esir{C'}{e'} \}} \subseteq X$
    we deduce
    \begin{center}
      $\theta_E(\eqclassir{\ir{\esir{C'}{e'}} \setminus \{ \esir{C'}{e'} \}}) = C' \subseteq \theta_E(X)$.
    \end{center}
    Since $C' \vdash_0 e$, by monotonicity of enabling, we conclude
    $\theta_E(X) \vdash e$, as desired.
  \end{itemize}

  We prove the naturality of $\theta$ by showing that the
  diagram below commutes.
  \begin{center}
    \begin{tikzcd}[column sep=large]
      \ev{\dom{{E}_1}} 
      \arrow[d, below, "\ev{\dom{f}}" left]
      \arrow[r, "\theta_{{E}_1}"]
      & {{E}_1} \arrow[d, "f"]\\
      %
      \ev{\dom{{E}_2}} 
      \arrow[r, "\theta_{{E}_2}" below]
      &
      {{E}_2}
    \end{tikzcd}
  \end{center}
  %
  Consider $\eqclassir{\esir{C_1}{e_1}} \in \ev{\dom{{E}_1}}$.
  Recall that $\ev{\dom{f}}(\eqclassir{\esir{C_1}{e_1}})$ is computed
  by considering the image of the irreducible
  $\esir{C_1}{e_1}$ and of its predecessor, namely
  \begin{center}
    $\dom{f}(C_1) = f(C_1)$ and $\dom{f}(\esir{C_1}{e_1}) = f(C_1 \cup\{e_1\})$
  \end{center}
  If $f(e_1)$ is defined, then $f(C_1) \prec f(C_1 \cup\{e_1\})$ and
  $\ev{\dom{f}}(\eqclassir{\esir{C_1}{e_1}}) = f(e_1)$, otherwise
  $\ev{\dom{f}}(\eqclassir{\esir{C_1}{e_1}})$ is undefined. This means
  that in all cases, as desired
  \begin{center}
    $\ev{\dom{f}}(\eqclassir{\esir{C_1}{e_1}}) = f(e_1) =
    f(\theta_{{E}_1}(\eqclassir{\esir{C_1}{e_1}}))$.
  \end{center}

  \bigskip

  Vice versa, let $D$ be a weak prime domain. Recall from Definition~\ref{de:esfusdom} that 
  $\ev{D} = \langle E, \#, \vdash \rangle$ is defined as:
  \begin{itemize}
  \item $E =  \eqclassir{\ir{D}}$
  \item $e \# e'$ if there is no $d \in \compact{D}$ such that
    $e, e' \in \eqclassir{\ir{d}}$;
  \item $X \vdash e$ if there exists $i \in e$ such that
    $\eqclassir{\ir{i} \setminus \{ i \}} \subseteq X$.
  \end{itemize}
  and consider $\dom{\ev{D}}$.  Elements of $\compact{\dom{\ev{D}}}$
  are configurations of $C \in \conff{\ev{D}}$.  
  % XXXX
  We can define the {unit} of the adjunction as
  \begin{center}
    $\begin{array}{lccc}
       \eta_{D} : & \compact{D} &  \to & \compact{\dom{\ev{D}}}\\
                  & d & \mapsto & \eqclassir{\ir{d}}
     \end{array}
     $
  \end{center}
  Observe that it is well defined, since by Lemma~\ref{le:comp-conf},
  $\eqclassir{\ir{d}}$ is a finite configuration of $\ev{D}$ and thus
  a compact element in $\compact{\dom{\ev{D}}}$.  The function is
  clearly monotone and bijective with inverse
  $\eta_D^{-1} : \compact{\dom{\ev{D}}} \to \compact{D}$ defined, for
  $C \in \compact{\dom{\ev{D}}} = \conff{\ev{D}}$ by letting
  $\eta_D^{-1}(C) = d$, where $d$ is the unique element, given by
  Lemma~\ref{le:comp-conf}, such that $C = \eqclassir{\ir{d}}$.
  %
  By
  algebraicity of the domains, this function thus uniquely extends to
  an isomorphism $\eta_D : D \to \dom{\ev{D}}$.

  Finally, we prove the naturality of $\eta_D$. It is convenient to
  prove the naturality of the inverse, i.e., to show that the diagram
  below commutes.
  \begin{center}
    \begin{tikzcd}[column sep=large]
      \dom{\ev{D_1}}
      \arrow[d, "\dom{\ev{f}}" left]
      \arrow[r, "\eta_{D_1}^{-1}"]
      &
      D_1
      \arrow[d, "f"]\\
      %
      %
      \dom{\ev{D_2}}
      \arrow[r, "\eta_{D_2}^{-1}"]
      &
      D_2
    \end{tikzcd}
  \end{center}

  Let $C_1 \in \compact{\dom{\ev{D_1}}}$, namely
  $C_1 \in \conff{\ev{D_1}}$, and let $\eta_{D_1}^{-1}(C_1) = d_1$ be the
  element such that $C_1 = \eqclassir{\ir{d_1}}$.

  The construction offered by Lemma~\ref{le:chains} provides a chain
  \begin{center}
    ${d^0_1} = \bot \prec d_1^1 \prec d_1^2 \prec \ldots \prec d_1^n = d_1$
  \end{center}
  and, by the same lemma, if we take an irreducible $i_1^h \in
  \diff{d_1^h}{d_1^{h-1}}$ for $1 \leq h \leq n$ we have that
  $C_1 = \eqclassir{\ir{d_1}} = \eqclassir{\{i_1^1, \ldots, i_1^n \}}$.
  Therefore the image
  \begin{center}
    $\dom{\ev{f}}(C_1) = \{ \ev{f}(\eqclassir{j_1}) \mid
    \eqclassir{j_1} \in C_1 \} = \{ \ev{f}(\eqclassir{i_1^h}) \mid h
    \in \interval{n}\}$
  \end{center}
  is the set of equivalence classes of irreducibles
  $i_2^1, \ldots, i_2^k$ corresponding to 
  \begin{center}
    $f(d_1^0) = \bot \prec f(d_1^1) \prec f(d_1^2) \prec \ldots \prec
    f(d_1^n) = f(d_1)$
  \end{center}
  namely $i_2^j \in \diff{f(d_1^j)}{f(d_1^{j-1})}$, and,
  again, by Lemma~\ref{le:chains},
  $\eqclassir{\{i_2^1, \ldots, i_2^k\}} = \eqclassir{\ir{f(d_1)}}$.
  Summing up
  \begin{center}
    $\eta_{D_2}^{-1}(\dom{\ev{f}}(C_1)) = \eta_{D_2}^{-1}(\{ \eqclassir{i_2^h}
    \mid 1 \leq h \leq k \} \}) = f(d_1) = f(\eta_{D_1}^{-1}(C_1))$
  \end{center}
  as desired.
%\end{proof}

%\begin{corollary}[equivalence]
%  \label{co:es-dom-equivalence}
%  The above coreflection restricts to an equivalence between $\WDom$ and $\ces$.
%\end{corollary}
%
%\begin{proof}
  We finally show that the above coreflection restricts to an
  equivalence between $\WDom$ and $\ces$.
  %
  For this, just observe that, in the proof above, when ${E}$ is a connected
  {\esabbr}, then the morphism $\theta_{E}$ defined as
  \begin{center}
    $\begin{array}{lccc}
       \theta_{{E}} : & \ev{\dom{{E}}} &  \to & {E}\\
                             & \eqclassir{\esir{C}{e}} & \mapsto & e
     \end{array}
     $
  \end{center}
  is an isomorphism. We already know that
  it is surjective. We next show that it is also injective. In fact, if
  $\theta_{{E}}(\eqclassir{I}) =
  \theta_{{E}}(\eqclassir{I'})$
  then $I$ and $I'$ are minimal enablings of the same event, i.e.,
  $I = \eqclassir{\esir{C}{e}}$ and $I' = \eqclassir{\esir{C'}{e}}$. Since
  ${E}$ is a weak prime domain, $C \conn{e}^* C'$ and thus, by
  Lemma~\ref{le:es-to-fusion-domain}(\ref{le:es-to-fusion-domain:4}), $I \leftrightarrow^* I'$,
  i.e., $\eqclassir{I} =\eqclassir{I'}$.
  % 
  Proving that also the inverse is an {\esabbr} morphism is immediate, by
  exploiting the fact that the {\esabbr} is live.
\end{proof}

The above result indirectly provides a way of turning a general
{\esabbr} into a connected {\esabbr}.

\begin{corollary}[from general to connected {\esabbr}]
  The functors $\zconnes : \es \to \ces$ defined by
  $\zconnes = \zev \circ \zdom$ and the inclusion
  $\zinces : \ces \to \es$ form a coreflection.
\end{corollary}

\begin{proof}
  Immediate consequence of Theorem~\ref{th:es-dom-equivalence}.
\end{proof}

Explicitly, for any event structure $E$ the corresponding connected {\esabbr} 
$\zconnes(E) = \langle E', \vdash', \#' \rangle$ is defined as follows. 
The set of events is $E' = \{ \eqclass[\sim]{\esir{C}{e}} \mid C \vdash_0 e \}$, 
where $\sim$ is the least equivalence such that $\esir{C}{e} \sim \esir{C'}{e}$ 
if $\esir{C}{e}$ and $\esir{C'}{e}$ are consistent. 
%
Moreover $\eqclass[\sim]{\esir{C}{e}} \#' \eqclass[\sim]{\esir{C'}{e'}}$ if for all 
$\esir{C_1}{e} \sim \esir{C}{e}$ and $\esir{C_1'}{e'} \sim \esir{C'}{e'}$ the 
minimal enablings $\esir{C_1}{e}$ and $\esir{C_1'}{e_1'}$ are not consistent. 
Finally, for $X \subseteq E'$, $X \vdash' \eqclass[\sim]{\esir{C}{e}}$ if there 
exists $\esir{C'}{e} \sim \esir{C}{e}$ such that 
$C' \subseteq \{ e'' \mid \eqclass[\sim]{\esir{C''}{e''}} \in X\}$.

\begin{figure}
\subcaptionbox{
  \label{fi:summary-diag}
}{
  \begin{tikzcd}[row sep=small,ampersand replacement=\&]      
  \&
  {}
  \&
  \PDom \arrow[dd, hook]
  \arrow[dl, shift right=1.2ex]
  \arrow[dll, bend right=20, shift right=2ex]
  \\
  % 
  \ses \arrow[dd, hook]
  \arrow[urr, bend left=20, sloped, "\bot"]
  \&
  \pes \arrow[dd, hook]
  \arrow[l, hook]
  \arrow[ur, shift right=1.2ex, sloped, near end, "\sim"]
  \&
  {}\\
  %
  {}
  \&
  {}
  \&
  \WDom
  \arrow[dl, shift right=1.2ex]
  \arrow[dll, bend right=20, shift right=2ex]\\
  % 
  \es
  \arrow[urr, bend left=20, sloped, "\bot"]
  \&
  \ces
  \arrow[l, hook]
  \arrow[ur, shift right=1.2ex, sloped, near end, "\sim"]
  \&
  {}
\end{tikzcd}
}
\subcaptionbox{
  \label{fi:summary-pict}
}{
\begin{tikzpicture}[x=8mm,y=10mm]
  \def\esel{(0,1)  ellipse [x radius=2, y radius=4]}
  \def\cesel{[black, pattern=north west lines, pattern color=gray] (0,0) ellipse [x radius=1.5, y radius=2.2]}
  \def\sesel{[black, pattern=north east lines, pattern color=gray](0,2) ellipse [x radius=1.5, y radius=2.2]}

 \def\wdomel {(6,0) ellipse [x radius=1.5, y radius=2.5]}
 \def\pdomel {[fill=gray!10] (6,2) ellipse [x radius=1.5, y radius=2.5]}

 \begin{scope}
   \clip (6,0) ellipse [x radius=1.5, y radius=2.5];
   \draw (6,2) ellipse [x radius=1.5, y radius=2.5];
 \end{scope}
 \begin{scope}
   \clip (6,2) ellipse [x radius=1.5, y radius=2.5];
   \draw [fill=gray!10] (6,0) ellipse [x radius=1.5, y radius=2.5];      
 \end{scope}

  \draw \esel;
  \draw \cesel;
  \draw \sesel;
  \draw \wdomel;
 % \draw \pdomel;

  \node [rectangle, rounded corners, fill=white] (ses) at (0,2.7)   {$\ses$};
  \node [rectangle, rounded corners, fill=white] (pes) at (0, 1)   {$\pes$};
  \node [rectangle, rounded corners, fill=white] (ces) at (0,-0.7)  {$\ces$};
  \node [rectangle, rounded corners, fill=white] (es)  at (0,-2.5)  {$\es$};

  \node (pesh) at (0,1.8)  {\phantom{$xx$}};
  \node (cesl) at (0,-1.5)  {\phantom{$xx$}};

  \node (seq)   at (3,2)    {$\top$};
  \node (pdomh) at (6,2)    {\phantom{$x$}};
  \node (pdoml) at (6,1.4)  {\phantom{$xxxx$}};

  \node [rectangle, rounded corners, fill=white] (pdom) at  (6,0.8)   {$\PDom$};
  \node (sadj)  at (3,1.2)   {$\sim$};
  \node (wdom)  at (6,-0.9)  {$\WDom$};
  \node (weq)   at (3,-1.2)  {$\sim$};
  \node (wdomh)  at (6,-1.5)  {\phantom{$xxxx$}};
  \node (wadj)  at (3,-1.9)  {$\bot$};
  \node (wdoml) at (6,-2.1)  {\phantom{$x$}};

  \draw [->] (ses) --  (pdomh);
  \draw [->] (pes) --  (pdom);
  \draw [->] (pdoml) -- (pesh);

  \draw [->] (ces) --  (wdom);
  \draw [->] (es)  --  (wdoml);
  \draw [->] (wdomh) -- (cesl);  
\end{tikzpicture}
}

\caption{A summary of the relations among classes of {\esabbr} and domains.}
\label{fi:summary}
\end{figure}

An overall picture of the results discussed up to now can be found in Fig.~\ref{fi:summary}. The arrows from classes of event structures to domains are restrictions of the functor $\dom{\cdot}$, while the converse arrows are restrictions of the functor  $\ev{\cdot}$. The Venn diagram stresses the fact that prime {\esabbr} are exactly the {\esabbr} which are stable and connected (see Lemma~\ref{le:constapri}) showing how the notion of connectedness naturally emerges in the framework.

\section{Related Characterisations}
\label{se:characterisations}

In this section we present a characterisation of our proposal in terms
of a formalism reminiscent of the prime event structures with
equivalence of~\cite{win2017,VismeW19}. Moreover, we discuss and
formalise the relation of our work with alternative characterisations
of the domains of (prime) event structures proposed in the literature,
based on intervals and on asynchronous graphs.

\subsection{Prime Event Structures with Equivalence}
\label{ss:pes-equiv}

The previous sections showed that the domains of configurations of
unstable {\esabbr} are weak prime domains, i.e., they satisfy the same
conditions as those of prime domains but only up to the equivalence
induced by interchangeability.
%
Symmetrically, this suggests the possibility of viewing unstable
{\esabbr} as stable ones up to some equivalence on events.
%
In this section we consider a formalisation for such a view,
leading to a set up that is closely related to the framework devised
in~\cite{win2017,VismeW19},
which we also call \emph{prime event structures with equivalence}
for the space of this article, since no confusion can arise.
% , further establishing a correspondence between
% unstable {\esabbr} and stable {\esabbr} with equivalence.

In Section~\ref{ss:es} we mentioned that in prime {\esabbr} a global
notion of causality can be used in place of the enabling. We next
recall the formal definition. We also introduce a notation for direct
(i.e., non-inherited) conflict that will play a role later.

\begin{definition}[causality/direct conflict in prime {event
    structures}]
  Let $P = \langle E, \vdash, \# \rangle$ be a prime {\esabbr}.  Given
  an event $e \in E$, the unique $C \in \conf{P}$ such that
  $C \vdash_0 e$ is called the set of \emph{strict causes} of $e$ and
  denoted by $\scauses{e}$, while the set of causes is
  $\causes{e} = \scauses{e} \cup \{e\}$. The \emph{strict causality
    relation} $<$ is defined by $e' < e$ if $e' \in\, \scauses{e}$,
  and, as usual, we denote by $\leq$ the reflexive closure of $<$. We
  say that $e, e' \in E$ are in \emph{direct conflict}, written
  $e \#_d e'$, when $e \# e'$ and $\scauses{e} \cup \{e'\}$,
  $\scauses{e'} \cup \{e\}$ are consistent.
\end{definition}

We next introduce our notion of prime {\esabbr} with
equivalence. Given a prime {\esabbr} $P$ with an equivalence over the
set of events ${\sim}\subseteq E \times E$, we say that a subset
$X \subseteq E$ is \emph{$\sim$-saturated} if for all $e \in X$ and
$e' \in E$, if $e \sim e'$ and $\scauses{e'} \subseteq X$  then
$e' \in X$. Since the intersection of saturated sets is saturated, given a set $X$ we can always consider the smallest saturated superset of $X$, called the  \emph{saturation} of $X$ and denoted $\sat{X}$.

\begin{definition}[prime {event structures} with equivalence]
  \label{de:pes-eq}
  A \emph{prime {\esabbr} with equivalence} ({\eseqabbr} for short) is
  a pair $\langle P, \sim \rangle$ where
  $P = \langle E, \vdash, \# \rangle$ is a prime {\esabbr} and $\sim$
  is an equivalence on $E$ such that for all $e, e', e_1, e_1' \in E$
  \begin{enumerate}

  \item
    \label{de:pes-eq:1}
    if
    $\eqclass[\sim]{\causes{e}} \subseteq \eqclass[\sim]{\causes{e'}}$
    then $e \leq e'$; if in addition $e \sim e'$ then $e=e'$;

  \item
    \label{de:pes-eq:2}
    if $e \sim e'$ and $\scauses{e} \cup \scauses{e'}$ consistent then
    $\neg (e \# e')$.

  \item
    \label{de:pes-eq:3}
    if $e \sim e'$, $e_1 \sim e_1'$, and $e \#_d e_1$ then $e' \# e_1'$.
  \end{enumerate}
  We say that $\langle P, \sim \rangle$ is {\emph{connected}}
  if ${\sim} = (\sim \setminus \#)^*$. A morphism of {\eseqabbr}
  $f : \langle P_1, \sim_1 \rangle \to \langle P_{{2}}, \sim_2 \rangle$ is
  an {\esabbr} morphism $f : P_1 \to P_2$ such that for all
  $e_1, e_1' \in P_1$, $e_1 \sim_1 e_1'$ iff
  %~\todo{We need iff for having the quotient to unstable es functorial}
  $f(e_1) \sim_2 f(e_1')$. We denote by $\epes$ the corresponding
  category.
\end{definition}

An {\esabbr} with equivalence is thus just an {\esabbr} equipped with
an equivalence on events. Condition (\ref{de:pes-eq:1}) essentially
says that an event is determined by the equivalence classes of events
in its causal history. In particular, as a consequence, if
$\scauses{e} \subseteq\, \scauses{e'}$ and $e \sim e'$ then $e=e'$,
which intuitively means that distinct equivalent events must
correspond to different enablings of the same event. Moreover, it
implies that the set $\causes{e}$ is $\sim$-saturated and thus it is a
configuration (see Definition~\ref{de:epes-conf} and
Lemma~\ref{le:hist-conf}).
%
Conditions (\ref{de:pes-eq:2}) and (\ref{de:pes-eq:3}) essentially say that equivalent events can have different conflicts only for the fact that their minimal enablings have different conflicts.
%
Connectedness 
amounts to the fact that equivalent events must be connected by a 
chain of equivalences going through consistent events. 
%
We next introduce a notion of configuration.

%In the sequel we write
%$\eqclasscup{\sim}{X}$ for the equivalence closure of the set $X$,
%i.e., $\bigcup \{ \eqclass[\sim]{x} \mid x \in X \}$.

\begin{definition}[configurations]
  \label{de:epes-conf}
  Let $\langle P, \sim \rangle$ be an {\eseqabbr}. Then
  $\conf{\langle P, \sim \rangle} = \{ C \mid C \in \conf{P}\ \land\
  C\mbox{ $\sim$-saturated}\}$.
\end{definition}

In words, a configuration of a prime {\esabbr} with equivalence is a
configuration $C$ of the underlying event structure, where all events
enabled in $C$ that are equivalent to some event already in $C$ are also in
$C$. Thus equivalent events may have different minimal enablings,
but whenever a configuration contains the causes of two equivalent
events, their executions cannot be taken apart.

\begin{lemma}[histories are configurations]
  \label{le:hist-conf}
  Let $\langle P, \sim \rangle$ be a {\eseqabbr}. For all $e \in E$,
  $\causes{e}$ is a configuration.
\end{lemma}

\begin{proof}
  Let $e \in E$ be any event. We have to show that
  $\causes{e}$ is saturated. If there are
  $e' \in \causes{e}$ and $e'' \sim e'$ such that
  $\scauses{e''} \subseteq \causes{e}$ then
  $\eqclass[\sim]{\causes{e''}} \subseteq
  \eqclass[\sim]{\causes{e}}$ and hence, by condition (\ref{de:pes-eq:1}) in
  Definition~\ref{de:pes-eq}, $e'' \leq e$ which means
  $e'' \in \causes{e}$.
\end{proof}

As an example, the connected {\esabbr} of our running example (see
Fig.~\ref{fi:running}), corresponds to the prime {\esabbr} with
equivalence in {Fig.~\ref{fi:running-pes-equivalence:a}}, where we have two
distinct copies of event $c$, namely $c_a \sim c_b$, corresponding to
the possibile minimal enablings. Graphically, causality is represented
by a straight directed line. The corresponding domain of configurations is depicted in {Fig.~\ref{fi:running-pes-equivalence:b}}. Note that $C=\{ a, b, c_a\}$ is not a configuration despite the fact that it is {downward} closed, since it is not $\sim$-saturated: event $c_b$ is missing, but its causes {$\{b\}$} are in $C$.% and $c_b \sim c_a \in C$.

\begin{figure}[h!]
  \begin{center}
  \subcaptionbox{
  %{A prime {\esabbr} with equivalence}
    \label{fi:running-pes-equivalence:a}
  }{
    \begin{tikzpicture}[node distance=5mm, >=stealth',x=10mm,y=6mm]
      \node at (1,0) (Gs)  {};
      \node at (0,1) (Ga)  {$a$};
      \node at (2,1) (Gb)  {$b$};
      \node at (1,2.1) (Gab) {};
      \node at (0,2.7) (Gac)  {$c_a$};
      \node at (1,2.7) (sim)  {$\sim$};
      \node at (2,2.7) (Gbc)  {$c_b$};
      \node at (1,4) (Gc)  {};
      \draw [->] (Ga) -- (Gac);
      \draw [->] (Gb) -- (Gbc);
    \end{tikzpicture}
  }
  %
  \hspace{15mm}
  %
  %%% CONFIGURATIONS
  %  
  \subcaptionbox{
  %The domain of configurations.
    \label{fi:running-pes-equivalence:b}
  }
  {  
    \begin{tikzpicture}[node distance=5mm, >=stealth',x=23mm,y=6mm]
      \node at (1,0) (Gs)  {$\emptyset$};
      \node at (0,1) (Ga)  {$\{a\}$};
      \node at (2,1) (Gb)  {$\{b\}$};
      \node at (1,2.1) (Gab) {$\{a,b\}$};
      \node at (0,2.7) (Gac)  {$\{a,c_a\}$};
      \node at (2,2.7) (Gbc)  {$\{b,c_b\}$};
      \node at (1,4) (Gc)  {$\{a,b,c_a,c_b\}$};
      \draw [->] (Gs) -- (Ga);
      \draw [->] (Gs) -- (Gb);
      \draw [->] (Ga) -- (Gab);
      \draw [->] (Gb) -- (Gab);
      \draw [->] (Ga) -- (Gac);
      \draw [->] (Gb) -- (Gbc);
      \draw [->] (Gac) -- (Gc);
      \draw [->] (Gbc) -- (Gc);
      \draw [->] (Gab) -- (Gc);
    \end{tikzpicture}
    % 
    }
  \end{center}
  \caption{A prime {\esabbr} with equivalence and its domain of configurations.}
  \label{fi:running-pes-equivalence}
\end{figure}

Our definition of {\eseqabbr} is similar to that
in~\cite{win2017,VismeW19}.
%
Concerning {configurations}, while~\cite{win2017,VismeW19} identifies unambiguous
configurations where there is a unique representative for each
equivalence class, here instead we saturate including \emph{all}
equivalent events that are not in conflict.

We finally observe that the constructions above can be ``translated'' 
into constructions that relate directly {\eseqabbr} and weak prime domains.
%
%More precisely, for a weak prime domain $D$ we have  prime {\esabbr} with equivalence
%$\langle \langle \ir{D}, \#, \vdash \rangle, \leftrightarrow^*
%\rangle$ with conflict and enabling defined by%
%\begin{itemize}
%\item $i_1 \# i_2$ if $\{ i_1, i_2\}$ is not consistent;
%\item $X \vdash i$ if
%  $\{ i' \in \ir{D} \mid i' \sqsubset i \} \subseteq X$. %\ \land\ i \neq  i' \}$.
%\end{itemize}
%% 
%Conversely, given a prime {\esabbr} with equivalence $\langle P, \sim \rangle$,
%the configurations ordered by inclusion, i.e., $\langle \conf{\langle P, \sim \rangle}, \subseteq \rangle$,
%form a weak
%prime domain.
%
%The configurations of a {\eseqabbr}. ordered by subset inclusion can
%be shown to form a weak prime domain and, conversely, a weak prime
%domain
%$D$ can be naturally mapped to a prime {\esabbr} with equivalence by
%taking irreducibles as events.

\begin{proposition}[weak prime domain for {\eseqabbr}]
  \label{pr:wpd-eseq}
  Let $\langle P, \sim \rangle$ be a {\eseqabbr}. Then
  $\domeq{\langle P, \sim \rangle} = \langle  \conf{\langle P, \sim \rangle}, \subseteq \rangle$ 
  is a weak prime domain.
  % 
  Conversely, if $D$ is a weak prime domain then
  $\eveq{D} = \langle \langle \ir{D}, \#, \vdash \rangle,
  \leftrightarrow^* \rangle$ with conflict and enabling defined by
  \begin{itemize}
  \item $i_1 \# i_2$ if $\{ i_1, i_2\}$ not consistent;
  \item $X \vdash i$ if
    $X \supseteq \ir{i}\setminus\{i\}$.
  \end{itemize}
  is an {\eseqabbr}.
\end{proposition}

\begin{proof}
  Let $\langle P, \sim \rangle$ be a {\eseqabbr}.
  %
  Then it is easy to see that the irreducibles of
  $\domeq{\langle P, \sim \rangle}$ are the minimal enablings
  $\causes{e}$ for $e \in E$.
  %
  Moreover, given a set of pairwise consistent configurations
  $X \subseteq \conf{\langle P, \sim \rangle}$, the join $\bigsqcup X$
  is the saturation of their union.
  %
  Interchangeability is given by
  $\causes{e} \leftrightarrow \causes{e'}$
  if $e \sim e'$ and $\neg (e \# e')$.
  %
  Using these fact it is almost immediate to conclude that
    $\domeq{\langle P, \sim \rangle}$ is a weak prime domain. Let us
    first observe that $\domeq{\langle P, \sim \rangle}$ is
    {\wi} (Definition~\ref{de:well-interchange}):
    \begin{itemize}
    \item Condition (\ref{de:well-interchange:1}) requires that for
      all $e, e' \in P$ if $\causes{e} \leftrightarrow^* \causes{e'}$
      and $\scauses{e} \cup \scauses{e'}$ consistent then
      $\causes{e} \leftrightarrow \causes{e'}$. Observe that
      $\causes{e} \leftrightarrow^* \causes{e'}$ implies $e \sim
      e'$. Moreover, by condition (\ref{de:pes-eq:2}) in
      Definition~\ref{de:pes-eq}, $\scauses{e} \cup \scauses{e'}$
      consistent implies $\neg (e \# e')$. Hence we conclude
      $\causes{e} \leftrightarrow \causes{e'}$.

    \item Condition~(\ref{de:well-interchange:2}) is an easy
      consequence of condition~(\ref{de:pes-eq:3}) of
      Definition~\ref{de:pes-eq}. In fact, let
      $e, e', e_1, e_1' \in E$ such that
      $\causes{e} \leftrightarrow^* \causes{e'}$,
      $\causes{e_1} \leftrightarrow^* \causes{e_1'}$, i.e.,
      $e \sim e'$ and $e_1 \sim e_1'$. Assume moreover that the sets
      $\{ \causes{e'}, \causes{e_1'}\}$,
      $\{ \causes{e}, \scauses{e_1}\}$,
      $\{ \scauses{e}, \causes{e_1}\}$ are consistent, meaning that $\causes{e'} \cup \causes{e_1'}$, $\causes{e} \cup \scauses{e_1}$, 
      $\scauses{e} \cup \causes{e_1}$ are so. From the consistency of $\causes{e'} \cup \causes{e_1'}$ we have $\neg (e' \# e_1')$. Moreover, the consistency of $\causes{e} \cup \scauses{e_1}$, 
      $\scauses{e} \cup \causes{e_1}$ implies that if $e \# e_1$ then the conflict would be direct and  this would violate condition~(\ref{de:pes-eq:3}) of
      Definition~\ref{de:pes-eq}. Hence we must have $\neg (e \# e_1)$, i.e., $\{  \causes{e}, \causes{e_1}\}$ consistent, as desired.
    \end{itemize}

    Finally, we show that all irreducibles are weak prime. Let $e \in P$, consider the irreducible $\causes{e}$ and a consistent set of configurations $X \subseteq \conf{\langle P, \sim \rangle}$. Assume that $\causes{e} \subseteq \bigsqcup X$. This means that $e$ is in the saturation of $\bigcup X$, which in turn means that there is $C \in X$ and $e' \in C$, whence $\causes{e'} \subseteq C$, such that $e' \sim e$. Since $e, e' \in  \bigsqcup X$, they are consistent, hence $\causes{e} \leftrightarrow \causes{e'}$. Summing up $\causes{e'} \subseteq C$ and $e \sim e'$, as desired.

  Conversely, let $D$ be a weak  prime domain. Observe that the causal
  order  in $\eveq{D}$  is  the  restriction of  the  domain order  to
  irreducibles. Condition (\ref{de:pes-eq:1}) in Definition~\ref{de:pes-eq} is an immediate consequence of Proposition~\ref{pr:unique-dec}.

    Condition (\ref{de:pes-eq:2}) is immediately implied by condition
    (\ref{de:well-interchange:1}) in the definition of {\wi} domain
    (Definition~\ref{de:well-interchange}).

    Concerning condition (\ref{de:pes-eq:3}), observe that it becomes:
    for $i, i', i_1, i_1' \in \ir{D}$, if $i \leftrightarrow^* i'$,
    $i_1 \leftrightarrow^* i_1'$, $i, i_1$ not consistent and
    $i', i_1'$ consistent then either $\ir{\pred{i}} \cup \{i_1\}$ or
    $\ir{\pred{i_1}} \cup \{i\}$ not consistent. In turn this is
    easily seen to be equivalent to condition
    (\ref{de:well-interchange:2}) in the definition of {\wi} domain
    (Definition~\ref{de:well-interchange}).
% Moreover, in order
  % to see that  for a given $i  \in \ir{D}$ the set  of causes, namely
  % $\ir{i}$,      is      $\leftrightarrow$-saturated,     just      use
  % Lemma~\ref{le:eq-char}(\ref{le:eq-char:4}).
  % %
  % Explicitly, let $i_1 \in \ir{i}$ and let $i_1' \leftrightarrow i_1$
  % with $\ir{i_1'} \setminus \{i_1'\} \subseteq \ir{i}$. We have to
  % show that $i_1' \in \ir{i}$. From
  % $\ir{i_1'} \setminus \{i_1'\} \subseteq \ir{i}$ we deduce that
  % $\pred{i_1'} \sqsubseteq i$. Moreover, since
  % $i_1' \leftrightarrow i_1$, by
  % Lemma~\ref{le:eq-char}(\ref{le:eq-char:4}), we have
  % $i_1' \sqcup \pred{i_1} = i_1 \sqcup \pred{i_1'} \sqsubseteq i$,
  % hence $i_1' \sqsubseteq i$ and thus $i_1' \in \ir{i}$, as desired.
\end{proof}

The correspondence above can be translated to an analogous
correspondence between {\eseqabbr} and unstable {\esabbr}. It is
however impossible to make such correspondence functorial essentially for
the same reason why~\cite{win2017,VismeW19} resorts to a pseudo-adjunction. 
We try to enucleate the problem by showing a correspondence between
(unstable) event structures and {\eseqabbr}.

\begin{definition}[from {\esabbr} to {\eseqabbr} and back]
  Let $\langle P, \sim \rangle$ be an {\eseqabbr}, where
  $P = \langle E, \vdash, \# \rangle$. The corresponding {\esabbr} is
  $\fuse{\langle P, \sim\rangle} = \langle \quotient{E}{\sim},
  \quotient{\vdash}{\sim}, \quotient{\#}{\sim} \rangle$, with
  $\quotient{\vdash}{\sim}$ and $\quotient{\#}{\sim}$ defined by
  \begin{itemize}
  \item $\eqclass[\sim]{X} \quotient{\vdash}{\sim} \eqclass[\sim]{e}$ when $X \vdash e$;
  \item $\eqclass[\sim]{e} \quotient{\#}{\sim} \eqclass[\sim]{e'}$ 
           when $e_1 \# e_1'$ for all $e_1 \in \eqclass[\sim]{e}$ and $e_1' \in \eqclass[\sim]{e'}$.
  \end{itemize}
  Conversely, given an {\esabbr} $P = \langle E, \vdash, \# \rangle$ the
  corresponding {\eseqabbr} is $\unf{P} = \langle Q, \sim \rangle$, with
  $Q = \langle E', \vdash', \#' \rangle$ defined by
  \begin{itemize}
  \item
    $E' = \{ \esir{C}{e} \mid C \in \conf{E}\ \land\ e\in E\ \land\ C
    \vdash_0 e \}$;
    % 
  \item $X \vdash' \esir{C}{e}$ if
    $C \subseteq \bigcup \{ C' \cup \{e'\} \mid \langle C', e' \rangle
    \in X\} $;
    % 
  \item $\esir{C}{e} \#' \esir{C'}{e'}$ if
    $C \cup C' \cup \{e, e'\}$ is not consistent.
  \end{itemize}
  and the equivalence is defined by $\esir{C}{e} \sim \esir{C'}{e}$ for all $C, C'$ such that $C \vdash_0 e$ and $C' \vdash_0 e$.
\end{definition}

We can easily show, exploiting Proposition~\ref{pr:wpd-eseq},
that the constructions above produce well-defined structures and map
connected structures to connected structures.
%
Moreover, the two constructions are inverse of each other.

\begin{proposition}
  \label{pr:epes-inverse}
  Let $\langle P, \sim \rangle$ be an {\eseqabbr}.
  % with $P = \langle E, \vdash, \# \rangle$. 
  Then $\langle P, \sim \rangle$ and
  $\unf{\fuse{\langle P, \sim\rangle}}$ are isomorphic. Dually, 
  let $P = \langle E, \vdash, \# \rangle$ be an
  {\esabbr}. Then
  $\fuse{\unf{P}}$ and $P$ are isomorphic.
\end{proposition}

\begin{proof}
  Let $\langle P, \sim \rangle$ be an {\eseqabbr}.
  Recall that events in
  $\unf{\fuse{\langle P, \sim\rangle}}$ are minimal
  enablings in $\fuse{\langle P, \sim\rangle}$.
  %
  By definitions of $\fuse{\langle P, \sim\rangle}$, for all $e \in P$
  we have
  $\eqclass[\sim]{X} \vdash_{\fuse{\langle P, \sim\rangle}}
  \eqclass[\sim]{e}$ when $X \vdash e$. Therefore
  $\eqclass[\sim]{\scauses{e}} \vdash_{\fuse{\langle P, \sim\rangle}}
  \eqclass[\sim]{e}$, and this enabling is minimal since, by
  Definition~\ref{de:pes-eq}(\ref{de:pes-eq:1}), whenever $e' \sim e$
  and $\eqclassir{\scauses{e'}} \subseteq \eqclassir{\scauses{e}}$ we
  have $e=e'$. And, again relying on the definition of enabling, one
  sees that all minimal enablings are of this shape.
  %
  Therefore we can define
  $c : \langle P, \sim \rangle \to \unf{\fuse{\langle P,
      \sim\rangle}}$ by
  $c(e) =
  \esir{\eqclass[\sim]{\scauses{e}}}{\eqclass[\sim]{e}}$.
  % 
  By the previous arguments it is a bijection and it can be shown $c$
  to be an isomorphism of {\eseqabbr}.

  \smallskip

  Conversely, let $\langle E, \vdash, \# \rangle$ be an an
  {\esabbr}.
  %
  According to the definition, events in $\unf{E}$ are minimal
  enablings $\esir{C}{e}$ in $E$, and they are equivalent when they are minimal
  enablings of the same event.
  %
  Then events in $\fuse{\unf{E}}$ are just equivalence classes of events in $\unf{E}$. Therefore we can define $u : E \to \fuse{\unf{E}}$ by
  $u(e) = \{ \esir{C}{e} \mid C \in \conf{E}\ \land\ C \vdash_0 e \}$. It is
  immediate to see that it is a bijection and 
  an isomorphism of {\esabbr}.
\end{proof}

Observe that the construction from {\eseqabbr} to {\esabbr} can be
easily turned into a functor $\zfuse : \epes \to \es$. In fact, given a
morphism
$f : \langle P_1, \sim_1 \rangle \to \langle P_2, \sim_2\rangle$ we
can let $\fuse{f}(\eqclass[\sim_1]{e_1}) = \eqclass[\sim_2]{f(e_1)}$.

Instead, making the converse construction from {\esabbr} to
{\eseqabbr} functorial is problematic. In fact, consider the {\esabbr} of the running example
$E = \{ a, b, c \}$, with $\emptyset \vdash_0 a$,
$\emptyset \vdash_0 b$ and $\{ a, b \} \vdash_0 c$ and the
{\esabbr} with events $E' = \{ a', b', c' \}$ with
$\emptyset \vdash_0 a'$, $\emptyset \vdash_0 b'$ and
$\{ a' \} \vdash_0 c'$ and $\{ b' \} \vdash_0 c'$ and the morphism
$f : E \to E'$ with $f(x) = x'$ for $x \in \{ a, b, c\}$. Then
$\unf{E} = \{ \esir{\emptyset}{a}, \esir{\emptyset}{b},
\esir{\{a, b\}}{c} \}$ and
$\unf{E'} = \{ \esir{\emptyset}{a'}, \esir{\emptyset}{b'},
\esir{\{a'\}}{c'}, \esir{\{b'\}}{c'} \}$. Observe that, while clearly
$\unf{f}(\esir{\emptyset}{a}) = \esir{\emptyset}{a'}$ and
$\unf{f}(\esir{\emptyset}{b}) = \esir{\emptyset}{b'}$, when we come
to $\unf{f}(\esir{\{a,b\}}{c})$ we can define it as one of the
two equivalent events $\esir{\{a'\}}{c'}$ and $\esir{\{b'\}}{c'}$.

The solution offered by~\cite{win2017,VismeW19} is to move towards 
pseudo-functors,
i.e., considering two {\eseqabbr} morphisms $g, g' : P_1 \to P_2$ equivalent
%, written $f \sim f'$ 
if $g(e_1) \sim_2 g'(e_1)$ for all $e_1\in P_1$ and requiring that functors 
are defined only up-to morphism equivalence. 
%
Indeed, it is easy to see that the two possible choices for $f$ above lead to
equivalent morphisms.

% \begin{definition}[from domains to {\eseqabbr} and back]
%   Let $D$ be a weak prime domain. Then we define
%   $\eveq{D} = \langle \langle \ir{D}, \#, \vdash \rangle,
%   \leftrightarrow^* \rangle$ with conflict and enabling defined by
%   \begin{itemize}
%   \item $i_1 \# i_2$ if $\{ i_1, i_2\}$ not consistent;
%   \item $X \vdash i$ if
%     $X \subseteq \{ i' \in \ir{D} \mid i' \sqsubseteq i\ \land\ i \neq
%     i' \}$.
%   \end{itemize}

%   Conversely, for any {\eseqabbr} $\langle P, \sim \rangle$, we
%   define
%   $\domeq{E} = \langle \{ C \mid C \in \conf{\langle P,
%     \sim \rangle} \}, \subseteq \rangle$.
% \end{definition}

%  Given a domain morphism $f : D_1 \to D_2$ we define
%   $\eveq{f} : \eveq{D_1} \to \eveq{D_2}$ by $\eveq{f}(i_1) = i_2$ with
%   $i_2 \in \diff{\pred{f(i_1)}}{f(i_1)}$.\todo{This is not well
%     defined, only up to equivalence ... same problem as in
%     winskel. Need to work in enriched setting? See below}
%  Given
%   $f : \langle P_1, \sim_1 \rangle \to \langle P_2, \sim_2
%   \rangle$ we define
%   $\domeq{f} : \domeq{P_1, \sim_1 \rangle} \to \domeq{P_2, \sim_2
%     \rangle}$ by $f(C_1)= \{ f(e) \mid e \in C_1 \}$.\todo{Not completely clear that this  is a configuration}

% Note that the definition of $\eveq{}$ as a functor as above is problematic. Consider for instance the domains below: the prime $d$ on the left could be mapped either to the prime $d'$ or to the prime $d''$ on the right.

% \begin{center}
%   \begin{tikzpicture}[node distance=5mm, baseline=(current bounding box.center)]
%     \node  (D1) {
%       \begin{tikzpicture}[node distance=5mm, >=stealth',x=10mm,y=4mm]
%         \node at (1,0) (s)  {$\bot$};
%         \node at (0,1) (a)  {$a$};
%         \node at (2,1) (b)  {$b$};
%         \node at (1,2) (c) {$c$};
%         \node at (1,4) (d) {$d$};

%         \draw [-] (s) -- (a);
%         \draw [-] (s) -- (b);
%         \draw [-] (a) -- (c);
%         \draw [-] (b) -- (c);
%         \draw [-] (c) -- (d);
%         % 
%         \pgfBox
%       \end{tikzpicture}
%     };
%     \node (D2) [right=of D1] {
%       \begin{tikzpicture}[node distance=5mm, >=stealth',x=10mm,y=4mm]
%         \node at (1,0) (s)  {$\bot$};
%         \node at (0,1) (a)  {$a$};
%         \node at (2,1) (b)  {$b$};
%         \node at (1,2) (c) {$c$};
%         \node at (0,3) (d') {$d'$};
%         \node at (1,4) (d) {$d$};
%         \node at (2,3) (d'') {$d''$};

%         \draw [-] (s) -- (a);
%         \draw [-] (s) -- (b);
%         \draw [-] (a) -- (c);
%         \draw [-] (b) -- (c);
%         \draw [-] (c) -- (d);
%         \draw [-] (a) -- (d');
%         \draw [-] (c) -- (d);
%         \draw [-] (b) -- (d'');
%         \draw [-] (d') -- (d);
%         \draw [-] (d'') -- (d);
%         % 
%         \pgfBox
%       \end{tikzpicture}

%       };
%       \path (D1) edge[->] node[trans, above] {} (D2);
%     \end{tikzpicture}
%   \end{center}

% One can show that
% \begin{itemize}
% \item $\domeq{\eveq{D}}$ is isomorphic to $D$; this should give a
%   coreflection (but in an enriched setting)

% \item if $\langle P, \sim \rangle$ is connected, then $\eveq{\domeq{\langle P, \sim \rangle}}$ (and this is an equivalence, (but in an enriched setting;

% \item through the coreflection/equivlence between (connected) es and domains, we have a correspondence between unstable es and pes with equivalence.
% \end{itemize}

\subsection{Relation with Interval Based Characterisations}
\label{ss:intervals}

The correspondence between event structures and domains has been often
studied in the literature by relying on the notion of
interval~\cite{Winskel:phd,NPW:PNES,Win:ES,Dro:ESD}.
% We next discuss the
% relation with our approach.

\begin{definition}[interval]
  \label{de:interval}
  Let $D$ be a domain. An \emph{interval} is a pair $\dint{d}{d'}$ of
  elements of $D$ such that $d \prec d'$. The set of intervals of $D$
  is denoted by $\IntSet{D}$.
  %
  Given two intervals $\dint{c}{c'}, \dint{d}{d'} \in \IntSet{D}$ we define
  \begin{center}
    $\dint{c}{c'} \leq \dint{d}{d'}$ \quad if $(c = c' \sqcap d)\ \wedge \ (c'
    \sqcup d = d')$, 
  \end{center}
  and we let $\sim$ be the equivalence obtained as the
  symmetric and transitive closure of $\leq$.
\end{definition}
%
It can be shown that $\leq$ is a partial order on intervals and thus $\sim$
is indeed an equivalence. An interval represents a pair of elements
differing only for a ``quantum'' of information, intuitively the
execution of an event. The equivalence $\sim$ is intended to identify
intervals corresponding to the execution of the same event in diffent states.
%
Indeed, in~\cite{NPW:PNES} it is shown that for prime domains there is a
bijective correspondence between $\sim$-classes of intervals and
complete primes.
%
In weak prime domains we can establish a similar correspondence, with $\leftrightarrow^*$-classes of irreducibles 
playing the role of the primes.

\begin{lemma}[intervals vs. irreducibles]
  \label{le:int-vs-irr}
  Let $D$ be a weak prime domain. Define $\inir : \quotient{\IntSet{D}}{\sim} \to \quotient{\ir{D}}{\leftrightarrow^*}$ by
  \begin{center}
    $\inir(\dint{d}{d'}_\sim) = \eqclassir{i}$,
  \end{center}
  where $i$ is any element in $\diff{d'}{d}$. Then $\inir$ is a bijection, whose inverse is  $\irin :  \quotient{\ir{D}}{\leftrightarrow^*} \to \quotient{\IntSet{D}}{\sim}$
  defined by
  \begin{center}
    $\irin(\eqclassir{i}) = \dint{\pred{i}}{i}_\sim$.
  \end{center}
\end{lemma}

\begin{proof}
  We first observe that $\inir$ is well-defined, i.e., if
  $\dint{c}{c'} \sim \dint{d}{d'}$ are equivalent intervals then for
  all $i \in \diff{c'}{c}$, $i' \in \diff{d'}{d}$ it holds
  $i \leftrightarrow i'$. This follows by noting that if
  $\dint{c}{c'} \leq \dint{d}{d'}$, $i \in \diff{c'}{c}$ and
  $i' \in \diff{d'}{d}$ then $i \leftrightarrow i'$.
  %
  In order to prove the last assertion, observe that since
  $i \in \ir{c'}$ we have $i \sqsubseteq c' \sqsubseteq d'$, thus
  $i \in \ir{d'}$.  Moreover, $i \not\in \ir{d}$, otherwise, by
  $i \sqsubseteq d$, $i \sqsubseteq c'$ and $c = d \sqcap c'$, we
  would get $i \sqsubseteq c$, contradicting the assumption that
  $i \in \diff{c'}{c}$. Hence $i \in \diff{d'}{d}$ and by
  Lemma~\ref{le:prec-irr-b}(\ref{le:prec-irr-b:3}) we conclude.

  Also the converse map $\irin$ is well-defined. This follows from the
  observation that for all irreducibles $i, i' \in \ir{D}$ if
  $i \leftrightarrow i'$ then
  $\dint{\pred{i}}{i}, \dint{\pred{i'}}{i'} \leq \dint{\pred{i} \sqcup
    \pred{i'}}{i \sqcup i'}$ and thus
  $\dint{\pred{i}}{i} \sim \dint{\pred{i'}}{i'}$. Let us prove, for
  instance, that
  \begin{center}
    $\dint{\pred{i}}{i} \leq \dint{\pred{i} \sqcup \pred{i'}}{i \sqcup
      i'}$.
  \end{center}
  Since $i \leftrightarrow i'$, surely
  $\pred{i} \sqsubseteq \pred{i} \sqcup \pred{i'}$ and
  $\pred{i} \prec i$, hence by Lemma~\ref{le:inf}, we deduce
  $i \sqsubseteq \pred{i} \sqcup \pred{i'}$ or
  $\pred{i} = i \sqcap (\pred{i} \sqcup \pred{i'})$. The first
  possibility, $i \sqsubseteq \pred{i} \sqcup \pred{i'}$, by the fact
  that $i$ is irreducible leads to $i \sqsubseteq \pred{i'}$ (since
  $i \sqsubseteq \pred{i}$ is clearly false). Thus
  $i \sqcup \pred{i'} = \pred{i'} \prec i' \sqsubseteq \pred{i} \sqcup
  i'$, that, by Lemma~\ref{le:eq-char}(\ref{le:eq-char:4}),
  contradicts $i \leftrightarrow i'$.
  %
  Hence the second possibility must hold, i.e.,
  $\pred{i} = i \sqcap (\pred{i} \sqcup \pred{i'})$. Moreover, again
  by Lemma~\ref{le:eq-char}(\ref{le:eq-char:4}), we have
  $i \sqcup (\pred{i} \sqcup \pred{i'}) = i \sqcup i'$. Hence
  $\dint{\pred{i}}{i} \leq \dint{\pred{i} \sqcup \pred{i'}}{i \sqcup
    i'}$ as desired.

  \bigskip

  The two maps are inverse each other.
  \begin{itemize}
  \item If $\dint{d}{d'} \in \IntSet{D}$ and $i \in \diff{d'}{d}$ then
    $\dint{d}{d'} \sim \dint{\pred{i}}{i}$.\\
    %
    Observe that $d \sqcup i = d'$ by
    Lemma~\ref{le:prec-irr-b}(\ref{le:prec-irr-b:1}). Moreover, in
    order to show that $d \sqcap i = \pred{i}$, note that, since
    $i \in \diff{d'}{d}$ and, by
    Lemma~\ref{le:prec-irr-b}(\ref{le:prec-irr-b:1bis}), the set
    $\diff{d'}{d}$ is flat, we have that $\pred{i} \sqsubseteq d$.
    Moreover $\pred{i} \prec i$, therefore by Lemma~\ref{le:inf},
    $\pred{i} = d \sqcap i$, as desired.

  \item If $i \in \ir{D}$ and $i' \in \dint{\pred{i}}{i}$ then
    $i \leftrightarrow i'$.\\
    %
    Just observe that $i \in \dint{\pred{i}}{i}$ and then use
    Lemma~\ref{le:prec-irr-b}(\ref{le:prec-irr-b:3}).
  \end{itemize}

\end{proof}

In ~\cite{Winskel:phd,Dro:ESD} the domain of
configurations of general event structures with binary conflict is characterised in terms of intervals. It is shown (see, e.g.,~\cite[Theorem 3.3.3]{Winskel:phd}), that given a an event structure with binary conflict, the domain of configuration is an 
% ($\omega$-)
algebraic complete partial order where the
following axioms hold

\begin{description}
\item[(F)] for all $d \in \compact{D}$ the set $\principal{d}$ is finite;

\item[(C)] for all $x, y, z \in \compact{D}$, if $x \prec y$,
  $x \prec z$, $\{y, z\}$ consistent, and $y \neq z$ then there exists
  $y \sqcup z$ and $y \prec y \sqcup z$ and $z \prec y \sqcup z$;

\item[(R)] for all intervals $\dint{x}{y}$, $\dint{x}{z}$ if
  $\dint{x}{y} \sim \dint{x}{z}$ then $y=z$;

% \item[(Q)] for all $x, y, z \in \compact{D}$, if $y \sqsupseteq x \prec z$ and
%   $y, z$ not consistent there exists a unique $t \sqsubseteq y$ such
%   that $x \prec t$ and $t, z$ not consistent

\item[(V)] for all $x,x',y,y',x'',y'' \in \compact{D}$ if
  $\dint{x}{x'} \sim \dint{y}{y'}$, $\dint{x}{x''} \sim \dint{y}{y''}$, and $\{x',x''\}$
  consistent then $y',y''$ consistent.
\end{description}

% \begin{remark}
%   Given a domain morphism $f : D_1 \to D_2$ and an interval
%   $\dint{d_1}{d_1'}$, since morphisms are $\preceq$-preserving, either
%   $f(d_1) = f(d_1')$ or $f(d_1) \prec f(d_1')$ and thus
%   $\dint{f(d_1)}{f(d_1')}$ is an interval.
% \end{remark}

Conversely, in~\cite{Dro:ESD} an explicit construction of the {\esabbr} corresponding to
a domain is provided. Given
$d \in \compact{D}$, let
$s(d) = \{ \dint{c}{c'}_{\sim} \mid c' \sqsubseteq d \}$.

\begin{definition}[{event structure} from a domain~\cite{Dro:ESD}]
  \label{de:evwd}
  Given a domain $D$ satisfying the axioms (F), (C), (R), (V), the
  corresponding {\esabbr} with binary conflict is defined as
  $\evwd{D} = (E, \#, \vdash)$ where
  \begin{itemize}

  \item
    $E = \quotient{\IntSet{D}}{\sim}$;
  \item $\dint{c}{c'}_\sim \# \dint{d}{d'}_\sim$ if for all
    $\dint{c_1}{c_1'}$, $\dint{d_1}{d_1'}$ such that
    $\dint{c_1}{c_1'} \sim \dint{c}{c'}$ and
    $\dint{d_1}{d_1'} \sim \dint{d}{d'}$ the set $\{c_1',d_1'\}$ is
    not consistent;

  \item 
    % 
    for $X \subseteq E$, $X \vdash \dint{c}{c'}_\sim$ if
    $s(c_1) \subseteq X$ for some interval
    $\dint{c_1}{c_1'} \sim \dint{c}{c'}$.
  \end{itemize}
\end{definition}

The above construction produces an event structure with binary conflict that is mapped back to the original domain (see, e.g.,~\cite[Corollary 2.10]{Dro:ESD}).

\begin{theorem}
  \label{th:evwd}
  Let $D$ be a domain satisfying axioms (F), (C), (R), (V). Then
  $\dom{\evwd{D}}$ is isomorphic to $D$.
\end{theorem}

We can build on the above results to show that the domains satisfying
axioms (F), (C), (R) and (V) are exactly the weak prime domains.

\begin{proposition}[weak prime domains and intervals]
  Let $D$ be a domain. Then $D$ is a weak prime domain iff $D$
  satisfies axioms (F), (C), (R) and (V).
\end{proposition}

\begin{proof}
  Let $D$ be a domain satisfying axioms (F), (C), (R) and (V).  By
  Theorem~\ref{th:evwd}, $\dom{\evwd{D}} \simeq D$. Since, by
  Proposition~\ref{pr:es-to-dom}, the set of configurations of any
  event structure forms a weak prime domain, we conclude that $D$ is
  weak prime.

  For the converse, let $D$ be a weak prime domain. By
  Theorem~\ref{th:es-dom-equivalence}, we have that
  $\dom{\ev{D}} \simeq D$ and thus, since by~\cite{Winskel:phd,Dro:ESD},
  the domain of configuration of an event structure with binary
  conflict satisfies axioms (F), (C), (R) and (V), we conclude.
\end{proof}

Moreover, relying on Lemma~\ref{le:int-vs-irr}, we can
show that the event structures associated with a domain
in~\cite{Dro:ESD} (Definition~\ref{de:evwd}) and in our work (Definition~\ref{de:esfusdom})
coincide.

\begin{proposition}
  \label{pr:es-int}
  Let $D$ be a weak prime domain. Then $\ev{D}$ and $\evwd{D}$ are isomorphic.
\end{proposition}

\begin{proof}
  By Lemma~\ref{le:int-vs-irr}, the function
  $\inir : \quotient{\IntSet{D}}{\sim} \to \quotient{\ir{D}}{\leftrightarrow^*}$ is a
  bijection. Note that $\quotient{\IntSet{D}}{\sim}$ and
  $\quotient{\ir{D}}{\leftrightarrow^*}$ are the sets of events respectively of
  $\ev{D}$ and $\evwd{D}$. We next show that $\inir$ is an isomorphism
  of event structures.

  \medskip

  Let $e_1, e_2$ be events in $\evwd{D}$. We show that $e_1 \# e_2$
  iff $\inir(e_1) \# \inir(e_2)$.

  If $\neg (e_1 \# e_2)$, from Definition~\ref{de:evwd}, we get that
  there exist $\dint{c_1}{c_1'} \in e_1$ and
  $\dint{c_2}{c_2'} \in e_2$ such that $\{ c_1', c_2' \}$ is
  consistent. Let $d \in D$ be an upper bound, i.e.,
  $c_1', c_2' \sqsubseteq d$. Now, $\inir(e_j) = \eqclassir{i_j}$ for
  $i_j \in \diff{c_j}{c_j'}$, for $j \in \{1,2\}$. Clearly,
  $i_1, i_2 \in \ir{d}$ whence
  $\eqclassir{i_1}, \eqclassir{i_2} \subseteq \eqclassir{\ir{d}}$ and
  thus, according to Definition~\ref{de:esfusdom}, we have
  $\neg (\eqclassir{i_1} \# \eqclassir{i_2})$, as desired.
  %
  The argument can be reversed to prove that if
  $\neg( \inir(e_1) \# \inir(e_2) )$ then $\neg (e_1 \# e_2)$.

  \medskip

  Concerning the enabling relation, we show that $X \vdash e$ in
  $\evwd{D}$ iff $\inir(X) \vdash \inir(e)$ in $\ev{D}$.
  %
  Assume that $X \vdash e$ in $\evwd{D}$. This means that there exists
  $\dint{c}{c'} \in e$ such that
  $s(c) = \{ \dint{d}{d'}_{\sim} \mid d' \sqsubseteq c \} \subseteq
  X$.
  %
  Now, recall that $\inir(e) = \eqclassir{i}$ with
  $i \in \diff{c'}{c}$.
  %
  In order to show that $\inir(X) \vdash \inir(e)$, according to
  Definition~\ref{de:esfusdom}, we prove that
  $\eqclassir{\ir{i} \setminus \{ i\}} \subseteq \inir(X)$.
  %
  Let $j \in \ir{i} \setminus \{ i \}$. Clearly
  $j \in \diff{j}{\pred{j}}$ and thus
  $\eqclassir{j} = \inir(\dint{\pred{j}}{j}_{\sim})$.
  %
  Moreover, by
  Lemma~\ref{le:prec-irr-b}(\ref{le:prec-irr-b:1bis}) the set
  $\diff{c'}{c}$ is flat and thus, since $j \sqsubset i$
  necessarily $j \not\in \diff{c'}{c}$. Since
  $j \in \ir{c'}$ we conclude that $j \in \ir{c}$, namely
  $j \sqsubseteq c$.
  %
  This implies that $\dint{\pred{j}}{j}_{\sim} \in s(c)$ and thus
  \begin{center}
    $
    \begin{array}{lll}
      \eqclassir{j} & = \inir(\dint{\pred{j}}{j}_{\sim}) & \\
      & \subseteq \inir(s(c)) & \\
      & \subseteq \inir(X) & \mbox{[since $s(c) \subseteq X$]}
    \end{array}
    $
  \end{center}
  We thus conclude that
  $\eqclassir{\ir{i} \setminus \{ i\}} \subseteq \inir(X)$ as desired.

  Also in this case, the argument can be easily reversed to prove the
  converse implication.
\end{proof}

The paper by Droste~\cite{Dro:ESD} considers also the case of event
structures with a general consistency relation (rather than a binary
conflict). The correspondence with our approach can be extended to this setting, as further detailed in Appendix~\ref{app:consistency}.

\subsection{Relation with Asynchronous Graphs}
\label{ss:async-graphs}

A characterisation  of prime {\esabbr} in terms of their transition
graph has been given in~\cite{PU:RMC}. A slightly different, yet
equivalent formalisation has been rediscovered in~\cite{Mel:hab}, in the
context of the work on the abstract theory of rewriting and concurrent
games.
%
Here we show that an analogous characterisation can be obtained for (connected)
event structures. For our development we refer to the formalisation in~\cite{Mel:hab}.
%
Given a graph $G = \langle N, U, s, t \rangle$, a sequence of edges
$w = u_1; \ldots; u_n \in U^*$ is a path whenever each edge has a
target that coincide with the source of the subsequent edge, i.e., for
all $i \in \interval{n-1}$, $t(u_i) = s(u_{i+1})$.
%
Let us denote by $P_2(G)$ the set of paths of length $2$, i.e.,
$P_2(G) = \{ u_1; u_2 \mid u_1, u_2 \in E \}$. Note that two paths of
length 2 with the same source and target can be seen as a ``square''
in the graph. An asynchronous graph is then a transition system where
some squares are declared to commute.

\begin{definition}[asynchronous graph]
  \label{de:async-graph}
  An \emph{asynchronous graph} 
  %\todo{AC: Melli\`es li definisce come grafi con ``tuiles'', che sono i generatori dell'equivalenza. Siamo sicuri che gli assiomi sull'equivalenza siano equivalenti a quelli sulle tiles?} 
  is a tuple
  $A = \langle G, n_0, \simeq \rangle$ where
  $G = \langle N, U, s, t \rangle$ is a directed graph,
  $n_0 \in N$ is the origin and
  ${\simeq} \subseteq P_2(G) \times P_2(G)$ is an equivalence
  relation
  % \todo{Not an equivalence in Mellies, but then used as an equivalence}
  on coinitial and cofinal paths of length $2$ (i.e., if
  $u_1;u_2 \simeq v_1;v_2$ then $s(u_1)=s(v_1)$ and $t(u_2)=t(v_2)$)
  such that the following axioms hold (in pictures, all squares
  depicted are assumed to commute)
  \begin{enumerate}
  % \item if $u_1;u_2 \simeq v_1;v_2$ then $v_1;v_2 \simeq u_1;u_2$
  %   \begin{center}
  %     \begin{tikzpicture}[node distance=6mm, >=stealth',baseline=(current bounding box.center), x=12mm, y=6mm]
  %       % 
  %       \node at (1,2) (T) {$\bullet$};    
  %       \node at (0,1) (L) {$\bullet$};
  %       \node at (2,1) (R) {$\bullet$};
  %       \node at (1,0) (B) {$\bullet$};    
  %       \path (B) edge[->] node[trans, below] {$u_1$} (L);
  %       \path (B) edge[->] node[trans, below] {$v_1$} (R);
  %       \path (L) edge[->] node[trans, above] {$u_2$} (T);
  %       \path (R) edge[->] node[trans, above] {$v_2$} (T);
  %       % 
  %       \pgfBox
  %     \end{tikzpicture}
  %     $\Leftrightarrow$
  %     \begin{tikzpicture}[node distance=6mm, >=stealth',baseline=(current bounding box.center), x=12mm, y=6mm]
  %       % 
  %       \node at (1,2) (T) {$\bullet$};    
  %       \node at (0,1) (L) {$\bullet$};
  %       \node at (2,1) (R) {$\bullet$};
  %       \node at (1,0) (B) {$\bullet$};    
  %       \path (B) edge[->] node[trans, below] {$v_1$} (L);
  %       \path (B) edge[->] node[trans, below] {$u_1$} (R);
  %       \path (L) edge[->] node[trans, above] {$v_2$} (T);
  %       \path (R) edge[->] node[trans, above] {$u_2$} (T);
  %       % 
  %       \pgfBox
  %     \end{tikzpicture}
  %   \end{center}

  \item if $u_1;u_2 \simeq v_1;v_2$ and $u_2 \neq v_2$ then $u_1 \neq v_1$;
    \label{de:async-graph:1}
    \begin{center}
      \begin{tikzpicture}[node distance=6mm, >=stealth',baseline=(current bounding box.center), x=12mm, y=6mm]
            % 
        \node at (1,2) (T) {$\bullet$};    
        \node at (0,1) (L) {$\bullet$};
        \node at (2,1) (R) {$\bullet$};
        \node at (1,0) (B) {$\bullet$};    
        \path (B) edge[->] node[trans, below] {$u_1$} (L);
        \path (B) edge[->] node[trans, below] {$v_1$} (R);
        \path (L) edge[->] node[trans, above] {$u_2$} (T);
        \path (R) edge[->] node[trans, above] {$v_2$} (T);
        % 
        \pgfBox
      \end{tikzpicture}
    \end{center}

  \item if $u;u_1 \simeq v_1;v_2$ and $u;u_1' \simeq v_1';v_2'$ then
    ($u_1=u_1'$ iff $v_1=v_1'$);
    \label{de:async-graph:2}
    \begin{center}
      \begin{tikzpicture}[node distance=6mm, >=stealth',baseline=(current bounding box.center), x=12mm, y=6mm]
        % 
        \node at (1,2) (T) {$\bullet$};    
        \node at (0,1) (L) {$\bullet$};
        \node at (2,1) (R) {$\bullet$};
        \node at (1,0) (B) {$\bullet$};    
        \path (B) edge[->] node[trans, below] {$u$} (L);
        \path (B) edge[->] node[trans, below] {$v_1$} (R);
        \path (L) edge[->] node[trans, above] {$u_1$} (T);
        \path (R) edge[->] node[trans, above] {$v_2$} (T);
        % 
        \pgfBox
      \end{tikzpicture}
      and 
      \begin{tikzpicture}[node distance=6mm, >=stealth',baseline=(current bounding box.center), x=12mm, y=6mm]
        % 
        \node at (1,2) (T) {$\bullet$};
        \node at (0,1) (L) {$\bullet$};
        \node at (2,1) (R) {$\bullet$};
        \node at (1,0) (B) {$\bullet$};    
        \path (B) edge[->] node[trans, below] {$u$} (L);
        \path (B) edge[->] node[trans, below] {$v_1'$} (R);
        \path (L) edge[->] node[trans, above] {$u_1'$} (T);
        \path (R) edge[->] node[trans, above] {$v_2'$} (T);
        % 
        \pgfBox
      \end{tikzpicture}
    \end{center}

  \item Cube 
  %\todo{AC: \`E implicito qui e sopra che ogni tile disegnata \`e nella relazione di equivalenza. Va detto? Melli\`es ci mette dentro il simbolo. PB: aggiunto}
    \label{de:async-graph:3}
    \begin{center}
      \begin{tikzpicture}[node distance=6mm, >=stealth',baseline=(current bounding box.center), x=12mm, y=7mm]
        % 
        \node at (1,3) (T) {$\bullet$};
        \node at (0,2) (TL) {$\bullet$};
        \node at (2,2) (TR) {$\bullet$};
        \node at (1,1) (C) {$\bullet$};    
        \node at (0,1) (L) {$\bullet$};
        \node at (2,1) (R) {$\bullet$};
        \node at (1,0) (B) {$\bullet$};    
        \path (B) edge[->] node[trans, below] {$u_1$} (L);
        \path (B) edge[->] node[trans, below] {$v_1$} (R);
        \path (C) edge[->] node[trans, above] {} (TL);
        \path (C) edge[->] node[trans, above] {} (TR);
        \path (L) edge[->] node[trans, left] {$u_2$} (TL);
        \path (R) edge[->] node[trans, right] {$v_2$} (TR);
        \path (TL) edge[->] node[trans, above] {$u_3$} (T);
        \path (TR) edge[->] node[trans, above] {$v_3$} (T);
        \path (B) edge[->] node[trans] {} (C);

        % 
        \pgfBox
      \end{tikzpicture}
      %
      $
      \begin{array}{c}
        \stackrel{(a)}{\Rightarrow}\\
        \stackrel{(b)}{\Leftarrow}
      \end{array}
      $        
      % 
      \begin{tikzpicture}[node distance=6mm, >=stealth',baseline=(current bounding box.center), x=12mm, y=7mm]
        % 
        \node at (1,3) (T) {$\bullet$};
        \node at (0,2) (TL) {$\bullet$};
        \node at (2,2) (TR) {$\bullet$};
        \node at (1,2) (C) {$\bullet$};    
        \node at (0,1) (L) {$\bullet$};
        \node at (2,1) (R) {$\bullet$};
        \node at (1,0) (B) {$\bullet$};    
        \path (B) edge[->] node[trans, below] {$u_1$} (L);
        \path (B) edge[->] node[trans, below] {$v_1$} (R);
        \path (L) edge[->] node[trans, above] {} (C);
        \path (R) edge[->] node[trans, above] {} (C);
        \path (L) edge[->] node[trans, left] {$u_2$} (TL);
        \path (R) edge[->] node[trans, right] {$v_2$} (TR);
        \path (TL) edge[->] node[trans, above] {$u_3$} (T);
        \path (TR) edge[->] node[trans, above] {$v_3$} (T);
        \path (C) edge[->] node[trans] {} (T);

        % 
        \pgfBox
      \end{tikzpicture}
    \end{center}

  \item Coherence axiom
    \label{de:async-graph:4}
      \begin{center}
      \begin{tikzpicture}[node distance=6mm, >=stealth',baseline=(current bounding box.center), x=12mm, y=7mm]
        %
        \node at (1,3) (NIL) {$ $};
        \node at (1,2) (CT) {$\bullet$};
        \node at (0,2) (TL) {$\bullet$};
        \node at (2,2) (TR) {$\bullet$};
        \node at (1,1) (C) {$\bullet$};    
        \node at (0,1) (L) {$\bullet$};
        \node at (2,1) (R) {$\bullet$};
        \node at (1,0) (B) {$\bullet$};    
        \path (B) edge[->] node[trans, below] {$u_1$} (L);
        \path (B) edge[->] node[trans, below] {$v_1$} (R);
        \path (C) edge[->] node[trans, above] {} (TL);
        \path (C) edge[->] node[trans, above] {} (TR);
        \path (L) edge[->] node[trans, left] {$u_2$} (TL);
        \path (R) edge[->] node[trans, right] {$v_2$} (TR);
        \path (L) edge[->] node[trans, above] {} (CT);
        \path (R) edge[->] node[trans, above] {} (CT);
        \path (B) edge[->] node[trans] {} (C);

        % 
        \pgfBox
      \end{tikzpicture}
      %
      $\Rightarrow$
      %
      \begin{tikzpicture}[node distance=6mm, >=stealth',baseline=(current bounding box.center), x=12mm, y=7mm]
        %
        \node at (1,3) (T) {$\bullet$};
        \node at (0,2) (TL) {$\bullet$};
        \node at (2,2) (TR) {$\bullet$};
        \node at (1,2) (C) {$\bullet$};    
        \node at (0,1) (L) {$\bullet$};
        \node at (2,1) (R) {$\bullet$};
        \node at (1,0) (B) {$\bullet$};    
        \path (B) edge[->] node[trans, below] {$u_1$} (L);
        \path (B) edge[->] node[trans, below] {$v_1$} (R);
        \path (L) edge[->] node[trans, above] {} (C);
        \path (R) edge[->] node[trans, above] {} (C);
        \path (L) edge[->] node[trans, left] {$u_2$} (TL);
        \path (R) edge[->] node[trans, right] {$v_2$} (TR);
        \path (TL) edge[->] node[trans, above] {} (T);
        \path (TR) edge[->] node[trans, above] {} (T);
        \path (C) edge[->] node[trans] {} (T);

        % 
        \pgfBox
      \end{tikzpicture}
    \end{center}

  \end{enumerate}
\end{definition}

Given an asynchronous graph, we denote by the same symbol $\simeq$ the
extension of the equivalence to all paths by contextual closure, i.e.,
$w_1;w;w_2 \simeq w_1;w';w_2$ for all $w_1, w_2, w, w' \in U^*$ with $w \simeq w'$.
%
The equivalence
classes of paths from the origin can be ordered by prefix, leading to
a partial order $P(A)$.
%
Then it can be shown that the partial orders of finite configurations
of prime {\esabbr} exactly correspond to asynchronous graphs such
that all cofinal paths from the origin are %\todo{AC: sarebbe bello vedere un semplice esempio per fissare le idee.} 
equivalent.

\begin{definition}[prime asynchronous graph]
  An asynchronous graph 
  $A = \langle G, n_0, \simeq \rangle$ is called  \emph{prime} if 
  all cofinal paths from the origin $n_0$ are equivalent.
\end{definition}

It can be seen that the requirement of having all cofinal paths equivalent amounts to that of having all {coinitial and cofinal} paths of length $2$ (squares) equivalent. This is indeed how the condition is formalised in~\cite{PU:RMC}.

\begin{theorem}[asynchronous graphs/prime {\esabbr}~\cite{Mel:hab}]
  \label{th:async-pes}
  Let $A$ be a prime asynchronous graph. The ideal completion
  $\ideal{P(A)}$ is a prime domain. Conversely, each
  prime domain is isomorphic to $\ideal{P(A)}$ for some prime
  asynchronous graph $A$.
\end{theorem}

%\todo[inline]{AC: Quanto affermato in questo paragrafo mi sembra importante. O si sviluppa formalmente, oppure lo si lascia come un claim dicendo magari gi\`a qui che \`e ``future work''.\\
 %PB: Ho chiesto a  Mellies che conferma che si tratta di un errore, intendi ci vorrebbe un controesempio?\\
% AC: No, ma che ne dici di una footnote che dice che in una personal communication Mellies era d'accordo?\\
%PB: Ho provato a rifrasare, ma non riesco a scriverlo in un modo che mi convinca.}
With respect to~\cite{Mel:hab},
we added the coherence
axiom~(\ref{de:async-graph:4}) in the definition of
asynchronous graph, which
is going to be pivotal in our later characterisation of weak prime domains (Proposition~\ref{pr:was-ces}). This is actually necessary already for having a correspondence with
prime domains and {\esabbr}.\footnote{In a personal communication, Paul Andr\'ee Melli\`es agreed that condition (4) is necessary for the correctness of Theorem 3 of Section 2.6 of~\cite{Mel:hab},
rephrased here as Theorem~\ref{th:async-pes}.
% In the absence of such axiom a correspondence still holds,
% yet it is with prime {\esabbr} with non-binary conflict (see~\ref{app:consistency}).
}

The correspondence established by Theorem~\ref{th:async-pes}
generalises to connected {\esabbr} and what we call weak
asynchronous graphs, i.e., asynchronous graphs where only the forward
part of the cube axiom holds, while the converse implication (indeed
sometimes referred to as stability axiom) may fail.

\begin{definition}[weak asynchronous graphs]
  A \emph{weak asynchronous graph} is defined as in
  Definition~\ref{de:async-graph}, but omitting the stability
  axiom~(\ref{de:async-graph:3}a). It is called \emph{weak prime} if
  additionally all cofinal paths from the origin are equivalent.
\end{definition}

Then we can prove that weak prime domains are exactly the partial
orders generated by weak prime asynchronous graphs (which in turn
correspond to connected {\esabbr}).

\begin{proposition}[weak asynchronous graphs and  domains]
  \label{pr:was-ces}
  Let $A$ be a weak prime asynchronous graph. The ideal completion
  $\ideal{P(A)}$ is a weak prime domain. Conversely, each weak
  prime domain is isomorphic to $\ideal{P(A)}$ for some weak prime
  asynchronous graph $A$.
\end{proposition}

\begin{proof}
  First observe that in a weak asynchronous graph
  $A = \langle G, n_0, \simeq \rangle$ with
  $G = \langle N, U, s, t \rangle$ such that all the {cofinal} paths from the
  origin are equivalent we have that all the squares are commuting. Thus
  axioms~(\ref{de:async-graph:1}) and ~(\ref{de:async-graph:2}) imply that the graph
  is simple, that there are at most two different paths of length $2$ with
  the same source and target, and that there is at most one way of
  closing a square.

  % The correspondence then follows easily by observing that the
  % domain
  % axioms (F),(C) in Subsection~\ref{ss:intervals} closely correspond
  % to
  % Definition~\ref{de:async-graph}(\ref{de:async-graph:1}-\ref{de:async-graph:2})
  % and the domain axiom (R) is essentially
  % Definition~\ref{de:async-graph}(\ref{de:async-graph:3}).

  Now, let $D$ be a weak prime domain and consider the subset of compact
  elements $\compact{D}$. It can be seen as an (acyclic) graph by taking compact
  elements as nodes and intervals as edges, with source and target
  functions being the obvious ones $s(\dint{c}{c'}{)} = c$ and
  $t(\dint{c}{c'}) = c'$.
  %
  Then taking $\emptyset$ as origin and letting all the squares commute,
  we get a weak asynchronous graph where all the paths are equivalent.
  %
  In detail, as observed above, axiom~(\ref{de:async-graph:1}) follows
  from the fact that the graph is simple. 
  %In fact, if
  %$u_1;u_2 \simeq v_1;v_2$ and $u_2 \neq v_2$ then $u_1 \neq v_1$; but
  %$u_1=v_1$ and $u_2 \neq v_2$ the edges $u_2$ and $v_2$ would be
  %parallel edges.
  %
  Axiom (\ref{de:async-graph:2}) says that there are at most two
  paths of length $2$ between the same source and target. Assume that this
  is not the case, i.e., $\compact{D}$ contains a substructure as below, with $y_1, y_2, y_3$ pairwise distinct.
  \begin{center}
    \begin{tikzpicture}[node distance=6mm, >=stealth',baseline=(current bounding box.center), x=12mm, y=8mm]
      % 
      \node at (1,2) (z) {$z$};
      \node at (0,1) (y1) {$y_1$};    
      \node at (1,1) (y2) {$y_2$};
      \node at (2,1) (y3) {$y_3$};
      \node at (1,0) (x) {$x$};    
      \path (x) edge[->] (y1);
      \path (x) edge[->] (y2);
      \path (x) edge[->] (y3);
      \path (y1) edge[->] (z);
      \path (y2) edge[->] (z);
      \path (y3) edge[->] (z);
    \end{tikzpicture}
  \end{center}
  Then we would have that $y_1$ is an irreducible which is not a weak
  prime. In fact $y_1 \sqsubseteq y_2 \sqcup y_3$, but it is not the
  case that either $y_1 \leftrightarrow y_2$ or $y_1 \leftrightarrow y_3$.

  Axiom (\ref{de:async-graph:3}a) follows from bounded completeness
  and the fact that if $x \prec y_1$ and $x \prec y_2$, with
  $y_1 \neq y_2$ then $y_1 \prec y_1 \sqcup y_2$ and
  $y_2 \prec y_1 \sqcup y_2$.

  Axiom (\ref{de:async-graph:4}) is an immediate
  consequence of coherence.

  Finally, we have to prove that all the paths from $\emptyset$ to the
  same target are equivalent. We prove more generally that all
  coinitial and cofinal paths are equivalent. First 
  %\todo{AC: chi garantisce che paths coiniziali e cofinali abbiano la stessa lunghezza? PB: aggiunto rif. al lemma, e c'era un pb di notazione} 
  notice that given
  two paths $w = y_1 \ldots y_n$ and $w' = y_1' \ldots y_m'$ with
  $y_1=y_1'$ and $y_n=y_m'$ then  $n=m=|\eqclassir{\ir{y_n}} \setminus \eqclassir{\ir{y_1}}|$, by Lemma~\ref{le:chains}. We prove
  by induction on $n=m$ that the two paths are equivalent. The base
  cases $n=1$ and $n=2$ are obvious.
  In the inductive case, consider
  $z = y_2 \sqcup y_2'$.
  \begin{center}
    \begin{tikzpicture}[node distance=6mm, >=stealth',baseline=(current bounding box.center), x=18mm, y=7mm]
      % 
      \node at (1,4) (T) {$y_n=y_n'$};
      \node at (0,2.5) (TL) {$y_3$};
      \node at (2,2.5) (TR) {$y_3'$};
      \node at (1,2) (C) {$z$};    
      \node at (0,1) (L) {$y_2$};
      \node at (2,1) (R) {$y_2'$};
      \node at (1,0) (B) {$y_1=y_1'$};    
      \path (B) edge[->]  (L);
      \path (B) edge[->]  (R);
      \path (L) edge[->]  (C);
      \path (R) edge[->]  (C);
      \path (L) edge[->]  (TL);
      \path (R) edge[->]  (TR);
      \path (TL) edge[->, dotted, bend left]  (T);
      \path (TR) edge[->, dotted, bend right]  (T);
      \path (C) edge[->, dotted] (T);
     \end{tikzpicture}
  \end{center}

  Then, as already observed, $y_2 \prec z$ and
  $y_2' \prec z$. Then
  \begin{equation}
    \label{eq:equiv}
    y_1 y_2 z \simeq y_1' y_2' z
  \end{equation}
  Moreover, since $z \sqsubseteq y_n=y_n'$ there is a path
  $y_2 z \ldots y_n$ of length $n-1$ in a way that we can apply the
  inductive hypothesis to prove that
  $y_2 y_3 \ldots y_n \simeq y_2 z \ldots y_n$.  Similarly, on the
  left side, we get $y_2' y_3' \ldots y_n \simeq y_2' z \ldots
  y_n'$. Therefore, together with (\ref{eq:equiv}), we conclude that
  $w= y_1 y_2 y_3 \ldots y_n \simeq y_1 y_2 z \ldots y_n \simeq y_1'
  y_2' z \ldots y_n' \simeq y_1' y_2' y_3' \ldots y_n' = w'$.

  \bigskip

  Conversely, let $A = \langle G, n_0, \simeq \rangle$ where
  $G = \langle N, U, s, t \rangle$ is a weak asynchronous graph such that
  all the paths from the origin are equivalent. Then, in particular, all
  the squares are commuting and, by axiom~(\ref{de:async-graph:1}), the
  graph is simple, i.e., we can think of edges as a relation on
  nodes.
  This allows us to view $A$ as a concurrent automata
  $(Q,\Sigma, T, (\parallel_q)_{q \in Q})$ in the sense
  of~\cite{Dro:CAD} as follows. Define an equivalence on edges by
  $u \equiv u'$ if there are $v, v' \in U$ such that $u v \sim v'u'$
  (namely, $u, u'$ are the opposite edges of a square). Then take
  nodes as states $Q = N$, equivalence classes of edges as labels
  $\Sigma = \quotient{U}{\equiv}$, transition relation
  $T = \{ (s(u), u, t(u)) \mid u \in U \}$ and local concurrency given
  by $\eqclass[\equiv]{u} \parallel_n \eqclass[\equiv]{v}$ when $u, v$ are such that
  $s(u)=s(v)=n$ and there are $u', v' \in E$ such that $uu' \sim v v'$.
  %
  The fact that $\parallel_n$ is well-defined uses in an essential way
  axioms~(\ref{de:async-graph:3}a) and~(\ref{de:async-graph:4}).  Then an immediate adaptation
  of~\cite[Theorem 10]{Dro:CAD} to asynchronous graphs shows that
  $P(A)$ is a domain that satisfies axioms (F), (C), and (R) in
  Subsection~\ref{ss:intervals}. Finally, observe that axiom (V) is a
  ``global'' version of the axiom (\ref{de:async-graph:1}). The fact
  that the latter implies the former can be proved by exploiting the
  fact that each bounded subset of $P(A)$ is a semimodular lattice~\cite[Theorem 3.1]{DK:ACRS}. 
  Hence $D$ is a weak prime domain.
\end{proof}

\section{Domain and event structure semantics for graph rewriting}
\label{se:graphs}

In this section we consider graph rewriting systems where rules are
left-linear but possibly not right-linear and thus, as an effect of a
rewriting step, some items can be merged. We argue that weak prime
domains and connected {\esabbr} are the right tool for providing a
concurrent semantics to this class of rewriting systems. More
precisely, in Subsection~\ref{ss:back-graph} we review the basics of
graph rewriting and we generalise the notion of independence between
rule applications to graph rewriting with left-linear rules.  Then in
Subsections~\ref{ss:graph-dom} and \ref{ss:es-graph} we show that the
domain associated with a graph rewriting system by a generalisation of
a classical construction is a weak prime domain and vice versa that
each connected {\esabbr} and thus each weak prime domain arise as the
semantics of some graph rewriting system. Finally, in
Subsection~\ref{ss:prime-gg} we show how a prime event structure
semantics for a graph rewriting system can be recovered by imposing
suitable restriction on rule application.

\subsection{Graph rewriting and concatenable traces}
\label{ss:back-graph}

We first review the basic definitions about graph rewriting in the double-pushout approach~\cite{Ehr:TIAA}.
%
We recall graph grammars and then introduce a notion of trace, which provides a representation of a sequence of 
rewriting steps that abstracts from the order of independent rewrites. This requires an original generalisation of the notion of independence between rewriting steps to the case of left-linear rules.
%
Traces are then turned into a category 
$\tr{\mathcal{G}}$ of concatenable derivation traces~\cite{CELMR:ESSG}.

%\newpage

\begin{definition}
A \emph{(directed) graph} is a tuple
$G = \langle N, E, s, t \rangle$, where $N$ and $E$ are 
% finite 
sets of
nodes and edges, and $s, t: E \rightarrow N$ are the source and target
functions.  The components of a graph $G$ are often denoted by
$N_G$, $E_G$, $s_G$, $t_G$.  A \emph{graph morphism}
$f: G \rightarrow H$ is a pair of functions
$\langle f_N: N_G \rightarrow N_H, f_E: E_G \rightarrow E_H\rangle$ such
that $f_N \circ s = s' \circ f_E$ and $f_N \circ t = t' \circ f_E$.
%; it is an isomorphism if both $f_N$ and $f_E$ are bijections.
We denote by $\graph$ the category of graphs and graph morphisms
%

\end{definition}

An \emph{abstract graph} $[G]$ is an isomorphism class of
graphs.
%, i.e., $[G] = \{H \mid H \simeq G\}$. 
%%  An \emph{automorphism}
%% of $G$ is an isomorphism $h : G \to G$
We work with typed graphs, i.e., graphs which are
``labelled'' over some fixed graph. Formally, given a graph $T$, the category of
\emph{graphs typed over $T$}, as introduced in~\cite{CMR:GP}, is the
slice category $\slice{\graph}{T}$, also denoted $\tgraph{T}$.

\begin{definition} [graph grammar]
  A \emph{($T$-typed graph) rule} is a span
  $(L \stackrel{l}{\leftarrow} K \stackrel{r}{\rightarrow} R)$ in
  $\tgraph{T}$ where $l$ is mono and not epi.
  % 
  The typed graphs $L$, $K$, and $R$ are called the \emph{left-hand side},
  the \emph{interface}, and the \emph{right-hand side} of the rule, respectively. 
  % 
  A \emph{($T$-typed) graph grammar} is a tuple
  $\mathcal{G} = \langle T, G_s, P, \pi \rangle$, where $G_s$ is the
  \emph{start (typed) graph}, $P$ is a 
  % finite 
  set of \emph{rule names}, and
  $\pi$ maps each rule name in $P$ into a rule.
\end{definition}
%
Sometimes we write
$p:(L \stackrel{l}{\leftarrow} K \stackrel{r}{\rightarrow} R)$ for
%$\pi(p) = (L \stackrel{l}{\leftarrow} K \stackrel{r}{\rightarrow} R)$.
%
denoting the rule $\pi(p)$.  When clear from the context we omit the
word ``typed'' and the typing morphisms.  Note that we consider only
\emph{consuming} grammars, i.e., grammars where for every rule
$\pi(p)$
%$p:(L \stackrel{l}{\leftarrow} K \stackrel{r}{\rightarrow} R)$,
the morphism $l$ is not epi.  
% This corresponds to the requirement on
% non-empty preconditions for Petri nets.
%
Also note that rules are, by default, \emph{left-linear}, i.e., the morphism
$l$ is mono. When also the morphism $r$ is mono, the rule is called
\emph{right-linear}.

An example of graph grammar has been discussed in the introduction
(see Fig.~\ref{fi:running-gg}). The type graph was left implicit: it
can be found in the top part of Fig.~\ref{fi:rules-grammars}. The
typing morphisms for the start graph and the rules are implicitly
represented by the labelling. Also observe that for the rules only the
left-hand side $L$ and the right-hand side $R$ were reported. The same
rules with the interface graph explicitly represented are in
Fig.~\ref{fi:rules-grammars}.

\begin{figure}

  \begin{center}
    %%% TYPE GRAPH
    \subcaptionbox*{$T$}{
        \begin{tikzpicture}[node distance=8mm, >=stealth']
          % 
          \node at (0,0) [node, label=below:${c,v}$] (nc) {} 
          edge [in=200, out=170, loop]  node [lab,above] {$\bar{a}$} ()
          edge [in=150, out=120, loop]  node [lab,above] {$\bar{b}$} ()
          edge [in=95, out=65, loop]  node [lab,above] {$\bar{\nu}$} ()
          edge [in=30, out=0, loop]  node [lab,above] {$\mathit{in}$} ();
          % 
          \pgfBox
        \end{tikzpicture}
      }\\
    %%% RULES 
    %
    \hspace{-4mm}
    \subcaptionbox*{$p_y$ ($y \in \{a,b\}$)}{
    % RULES Pa and Pb
    %
    \begin{tikzpicture}[node distance=2mm, baseline=(current bounding box.center)]
      \node (l) {
      \begin{tikzpicture}[node distance=8mm, >=stealth']
      %
      \node at (0,0) [node, label=below:$c$] (nc) {} 
      edge [in=105, out=75, loop]  node [lab,above] {$\bar{y}$} ();
      %
      \node at (.5,0) [node, label=below:$\nu$] (nu) {} 
      edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
      %
      \pgfBox
      \end{tikzpicture} 
    };
    \node [right=of l] (k) {
      \begin{tikzpicture}[node distance=8mm, >=stealth']
      %
      \node at (0,0) [node, label=below:$c$] (nc) {};
      %
      \node at (.5,0) [node, label=below:$\nu$] (nu) {} 
      edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
      %
      \pgfBox
      \end{tikzpicture} 
    };
    \node  [right=of k] (r) {
      \begin{tikzpicture}[node distance=8mm, >=stealth']
        \node at (0,0) [node, label=below:${c,\nu}$] (nc) {} 
        edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
        % 
        \pgfBox
      \end{tikzpicture}
    };
    \path (k) edge[->] node[trans, above] {} (l);
    \path (k) edge[->] node[trans, above] {} (r);
    \end{tikzpicture}
    }
    \ \hfill\ 
    \subcaptionbox*{$p_c$}{
    %
    %%% RULE Px    
    %
    \begin{tikzpicture}[node distance=2mm, baseline=(current bounding box.center)]
      \node (l) {
      \begin{tikzpicture}[node distance=8mm, >=stealth']
        \node at (0,0) [node, label=below:${c,\nu}$] (nc) {} 
        edge [in=160, out=130, loop]  node [lab,above] {$\mathit{in}$} ()
        edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
        %
        \pgfBox
      \end{tikzpicture} 
    };
    \node [right=of l] (k) {
      \begin{tikzpicture}[node distance=8mm, >=stealth']
        \node at (0,0) [node, label=below:${c,\nu}$] (nc) {} 
         edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
        %
        \pgfBox
      \end{tikzpicture} 
    };
    \node  [right=of k] (r) {
      \begin{tikzpicture}[node distance=8mm, >=stealth']
        \node at (0,0) [node, label=below:${c,\nu}$] (nc) {} 
        edge [in=105, out=75, loop]  node [lab,above] {$\bar{\nu}$} ();
        % 
        \pgfBox
      \end{tikzpicture}
    };
    \path (k) edge[->] node[trans, above] {} (l);
    \path (k) edge[->] node[trans, above] {} (r);
  \end{tikzpicture}  
  }
  % 
\end{center}
\caption{The type graph  and the rules of the grammar in Fig.~\ref{fi:running-gg}.}
\label{fi:rules-grammars}
\end{figure}

%We assume that the reader is familiar with the categorical constructions 
%of pushout and pushout complement, which are the formal basis of the 
%definition of direct derivation (see \cite{Ehr:TIAA,CMREHL:AAGT}).

\begin{figure}[t]
\[
\xymatrix@R=4mm{ 
  {L} \ar[d]_{m^L} & {K} \ar[l]_{l} \ar[r]^{r} 
  \ar[d]^{m^K} & {R} \ar[d]^{m^R}\\
  {G} & {D} \ar[l]^{l^*} \ar[r]_{r^*} & {H} }
\]
\caption{A direct derivation.}
\label{fi:deriv}
\end{figure}

\begin{definition}[direct derivation]
  \label{de:direct derivation}
  Let $G$ be a typed graph,
  let $p : (L \stackrel{l}{\leftarrow} K \stackrel{r}{\rightarrow} R)$
  be a rule, and let $m^L$ be a \emph{match}, i.e., a typed graph
  morphism $m^L: L \rightarrow G$.  A \emph{direct derivation}
  $\delta$ from $G$ to $H$ via $p$ (based on $m^L$) is a diagram as in
  Fig.~\ref{fi:deriv}, where both squares are required to be pushouts in
  $\tgraph{T}$.
  %
  We write $\delta : G \Rrel{p/m} H$, where $m = \langle
  m^L, m^K, m^R\rangle$, or simply $\delta : G \Rrel{p} H$.
\end{definition}

%In this case, $D$ is called the \emph{context} graph.
% 
Since pushouts are defined only up to isomorphism, given isomorphisms
$\kappa : G' \to G$ and $\nu : H \to H'$, also $G' \Rrel{p/m'} H$
with $m' = \langle \kappa^{-1} \circ m^L, m^K, m^R \rangle$ and
$G \Rrel{p/m''} H'$ with $m'' = \langle  m^L, m^K, \nu \circ m^R \rangle$  are direct derivations, 
denoted by $\kappa \cdot \delta$ and $\delta \cdot \nu$, respectively.
%To have an informal understanding of the notion of direct derivation,
%one can think of the pushout, for instance in the left square of
%the figure above, as the gluing of $L$ and $D$, obtained
%by identifying the images of the interface $K$ via $l$ and $k$. With
%this interpretation,
%
Informally, the rewriting step removes (the image
of) the left-hand side from $G$ and replaces it by (the
image of) the right-hand side $R$. The interface $K$ (the common part 
of $L$ and $R$) specifies what is preserved.
%
For example, the transitions in Fig.~\ref{fi:running-rewriting} are
all direct derivations.
%
When rules are not right-linear, some items in the (image of the) interface are merged. This happens, e.g., for  $p_a$ and $p_b$.

\begin{definition}[derivations]
  \label{de:derivations}
  Let $\mathcal{G} = \langle T, G_s, P, \pi \rangle$ be a graph
  grammar. A \emph{derivation}
  $\rho: G_0 \Rrel{}^{*}_{\mathcal{G}} G_n$ over ${\mathcal{G}}$ is a
  (possibly empty) sequence of direct derivations
  $\{G_{i-1} \Rrel{p_{i}} G_i\}_{i \in \interval{n}}$ where
  $p_i \in P$ for $i \in \interval{n}$.  The graphs $G_0$ and $G_n$
  are called the \emph{source} and the \emph{target} of $\rho$, and
  denoted by $\source{\rho}$ and $\target{\rho}$, respectively. The
  \emph{length} of $\rho$ is $|\rho| = n$.
  The derivation is called {\em
    proper} if $|\rho| > 0$.
  % If $|\rho|=0$ then $\rho$ called the
  % \emph{identity derivation} on $G_0$. 
  Given two derivations $\rho$
  and $\rho'$ such that $\target{\rho} = \source{\rho'}$, their
  sequential composition
  $\rho\,;\,\rho': \source{\rho} \Rrel{}^{*} \target{\rho'}$ is
  defined in the obvious way.
\end{definition}

%When the grammar is clear from the context, the subscript
%$\mathcal{G}$ is omitted and we write simply $\rho: G_0 \Rrel{}^{*} G_n$.  
When irrelevant/clear from the context, the subscript
$\mathcal{G}$ is omitted.  
If
$\rho : G \Rrel{}^{*} H$ is a proper derivation 
% $|\rho| > 0$ 
and
$\kappa : G' \to G$, $\nu : H \to H'$ are graph isomorphisms, then
$\kappa \cdot \rho : G' \Rrel{}^{*} H$ and
$\rho \cdot \nu : G \Rrel{}^{*} H'$ are defined as expected.

In the double pushout approach to graph rewriting, it is natural to
consider graphs and derivations up to isomorphism.
%
However some structure must be imposed on the start and end graphs
of an abstract derivation in order to have a meaningful notion of
sequential composition.
%
In fact, isomorphic graphs are, in general, related by several
isomorphisms, while in order to concatenate derivations keeping track
of the flow of causality one must specify how the items of the source
and target isomorphic graphs should be identified.
%
We follow~\cite{Handbook}, inspired by the theory of
Petri nets~\cite{DMM:AANCP}: we choose for each class of isomorphic
typed graphs a specific graph, named the \emph{canonical graph}, and we
decorate the source and target graphs of a derivation with
isomorphisms from the corresponding canonical graphs to such
graphs.
%  In such a way we are allowed to distinguish
% ``equivalent''\footnote{With ``equivalent'' we mean here two items
%   related by an automorphism of the graph, that are, in absence of
%   further informations, indistinguishable.} elements in the starting
% and ending graphs of derivations and we can safely define their
% sequential composition.

Let $\mathsf{C}$ denote the operation that associates with each ($T$-typed)
graph its \emph{canonical graph}, thus satisfying $\can{G} \simeq G$
and if $G \simeq G'$ then $\can{G} = \can{G'}$.
% The construction of the canonical graph can be performed by adapting
% to our slightly different framework the ideas of \cite{MW:DG}.
%
%and a similar technique can be used to single out a class of standard
%isomorphisms in the sense of \cite{CELMR:NSRG,CELMR:AGDD}. Working
%with finite graphs the constructions are effective.

\begin{definition}[decorated derivation]
  A \emph{decorated derivation} $\psi : G_0 \Rrel{}^* G_n$ is a
  triple $\langle \alpha, \rho, \omega \rangle$, where $\rho : G_0 \Rrel{}^*
  G_n$ is a derivation and $\alpha: \can{G_0} \to G_0$, $\omega: \can{G_n} \to
  G_n$ are isomorphisms. 
  We define $\source{\psi} = \can{\source{\rho}}$, $\target{\psi} =
  \can{\target{\rho}}$ and $|\psi| =|\rho|$.
  % The  derivation is called {\em proper} if $|\psi| > 0$.
\end{definition}

%The sequential composition of two decorated derivations $\psi$ and
%$\psi'$ such that $\target{\psi} \simeq \source{\psi'}$
%is defined by considering the derivations obtained from $\psi$ and
%$\psi'$, respectively, ending at and starting from $\can{\target{\psi}} =
%\can{\source{\psi'}}$, and concatenating them in the obvious way.

\begin{definition}[sequential composition]
\label{def:seq_com_decorated}
  Let $\psi = \langle \alpha, \rho, \omega \rangle$, $\psi' = \langle \alpha',
  \rho', \omega' \rangle$ be decorated derivations such that
  $\target{\psi} = \source{\psi'}$. Their \emph{sequential
  composition} $\psi ; \psi'$ is defined, if $\psi$ and
  $\psi'$ are proper, as 
  %\begin{center}
    $\langle \alpha, (\rho \cdot \omega^{-1}); (\alpha' \cdot \rho'), \omega' \rangle$.
  %\end{center}
  Otherwise, if $|\psi|=0$ then $\psi ; \psi' =
  \langle \alpha' \circ \omega^{-1} \circ \alpha, \rho', \omega' \rangle$, and similarly,
  if $|\psi'| = 0$ then $\psi ; \psi' =
  \langle \alpha, \rho, \omega \circ {\alpha'}^{-1} \circ \omega' \rangle$.
\end{definition}

We next define an abstraction equivalence that identifies derivations that differ
only in representation details.
%  As for  $\equiv^{sh}$ and
% $\equiv^{c}$, introduced in the following, such equivalence is
% a reformulation, in our setting, of the equivalences defined in
% \cite{CELMR:ESSG}.

\begin{definition}[abstraction equivalence]
  \label{de:der-equiv1}
  Let $\psi = \langle \alpha, \rho, \omega \rangle$, $\psi' = \langle \alpha',
  \rho', \omega' \rangle$ be decorated derivations with $\rho: G_0
  \Rrel{}^{*} G_n$ and $\rho': G'_0 \Rrel{}^{*} G'_{n'}$
  (whose $i^{th}$ step is depicted in the lower rows of
  Fig.~\ref{fi:der-iso}).  They are \emph{abstraction equivalent}, 
  written  $\psi \equiv^{a} \psi'$, 
  if  $n = n'$,  $p_{i} = p_{i}'$ for all $i \in \interval{n}$,
  and there exists a family of isomorphisms
  $\{\theta_{X_i}: X_i \rightarrow X'_i \mid X \in \{G, D\},$
  $i \in \interval{n} \} \cup\{\theta_{G_0}\}$
  between corresponding graphs in the two derivations such that
  %\begin{enumerate}
  (1)
    the isomorphisms relating the source and target
    commute with the decorations, i.e., $\theta_{G_0} \circ \alpha = \alpha'$
    and $\theta_{G_n} \circ \omega = \omega'$; and
  (2) 
    the resulting diagram (whose $i^{th}$ step is represented in
    Fig.~\ref{fi:der-iso}) commutes.
  %\end{enumerate}
  %

  %  \noindent
\end{definition}

  Equivalence classes of decorated derivations 
  with respect to $\equiv^{a}$ 
  are called \emph{abstract derivations} and 
  denoted by
  $[\psi]_{a}$, where $\psi$ is an element of the class.

\begin{figure}
\vspace{-1.1cm}

\[
\scalebox{.8}{
\xymatrix@R=1.4mm@C=2mm{ 
  & & & {p_i:} & {L_i} \ar[ddddl]|/-6mm/{\bx{m_i^L}} \ar[ddr]|{\bx{m_i'^L}} & & {K_i}
  \ar[ll]_{l_i} \ar[rr]^{r_i} \ar[ddddl]|/-6mm/{\bx{m_i^K}} \ar[ddr]|{\bx{m_i'^K}} & &
  {R_i} \ar[ddddl]|/-6mm/{\bx{m_i^R}} \ar[ddr]|{\bx{m_i'^R}}& & & &\\
  & & & & & & & & & & &\\  
  & & & {G_0'} & & {G_{i-1}'} & &
  {D_i'} \ar[ll]|{\bx{l_i'^*}} \ar[rr]|{\bx{r_i'^*}} & & {G_{i}'} & & {G_n'} &\\
  {\can{G_0}} \ar[urrr]^{\alpha'} \ar[dr]_{\alpha}  & & & & & & & & & & & &
  {\can{G_n}} \ar[ul]_{\omega'} \ar[dlll]^{\omega} \\
  & {G_0} \ar[uurr]|{\theta_{G_0}} &  & {G_{i-1}} \ar[uurr]|{\theta_{G_{i-1}}} & &
  {D_i} \ar[ll]^{l_i^*} \ar[rr]_{r_i^*} \ar[uurr]|{\theta_{D_i}} & &
  G_{i} \ar[uurr]|{\theta_{G_{i}}} & & {G_n} \ar[uurr]|{\theta_{G_n}} & & }
}
\]

\caption{Abstraction equivalence of decorated derivations.}
\label{fi:der-iso}
\end{figure}

%\noindent
%Notice that two derivations are abstraction equivalent, not only if they
%have the same length and apply the same rules in the same order,
%but also if, in a sense, rules are applied to ``corresponding''
%items (conditions 1 and 2).
%It is possible to prove that if $\psi \equiv^{a} \psi'$
%and $\psi_1 \equiv^{a} \psi_1'$ then, if defined, $\psi; \psi_1
%\equiv^{a} \psi'; \psi_1'$. Therefore sequential composition of
%decorated derivations lifts to composition of abstract derivations.

%\begin{definition}[category of abstract derivations]
%  \label{de:abs-cat}
%  The \emph{category of abstract derivations} of a grammar ${\mathcal{G}}$,
%  denoted by \Abs{\mathcal{G}}, has abstract graphs as
%  objects, and abstract derivations as arrows.  In particular, if
%  $\psi: G \Rrel{}^{*} H$, then $[\psi]_{a}$ is an
%  arrow from $[G]$ to $[H]$. The identity arrow on $[G]$ is the
%  abs-equivalence class of an identity derivation $\langle i, G, i
%  \rangle$, where $i : \can{G} \to G$ is any isomorphism, and
%  the composition of arrows $[\psi]_{a}: [G] \rightarrow [H]$ and
%  $[\psi']_{a}: [H] \rightarrow [X]$ is defined as
%  $[\psi\,;\,\psi']_{a}: [G] \rightarrow [X]$.
%  
%\end{definition}

From a concurrent perspective, also derivations that only differ for
the order in which two independent direct derivations are applied
should not be distinguished. This is classically formalised by a
notion of sequential independence between rewrites inducing the
so-called shift equivalence on derivations. When working with rules
which are only left-linear, we need to refine the notion of
independence as discussed below.

\begin{definition}[sequential independence]
  \label{de:seq-ind}
  Consider a derivation $G \Rrel{p_1/m_1} H \Rrel{p_2/m_2} M$ as in
  Fig.~\ref{fi:strongseq}. Then, its components are \emph{weakly sequentially
    independent} if there exists an \emph{independence pair} among
  them, i.e., two graph morphisms $i_1: R_1 \rightarrow D_2$ and
  $i_2: L_2 \rightarrow D_1$ such that $l_2^* \circ i_1 = m_{R_1}$,
  $r_1^* \circ i_2 = m_{L_2}$.
  %
  They are \emph{sequentially
    independent} if the independence pair is unique.
\end{definition}

Intuitively, when the independence pair is not unique, we can think
that the first rewrite has performed some fusions that the second
rewrite is using in an essential way. Hence the steps should not
considered independent.
%
Note that when dealing with linear rules, the independence pair, if it exists,
is always unique. Hence the two notions independence coincide and
reduce to the classical one in~\cite{CMREHL:AAGT}.

\begin{figure}[t]
\[
\def\objectstyle{\scriptstyle}\def\labelstyle{\scriptstyle}
\xymatrix@C=0.7mm@R=7mm{
  {L_1} \ar[d]_{m_{L_1}}
        & & {K_1} \ar[ll]_{l_1} \ar[rr]^{r_1} \ar[d]|{m_{K_1}}
        & & {R_1} \ar[drrr]|{m_{R_1}}  \ar@(r,ul)@{.>}|(.75){i_1}[drrrrrrrr]
        & & & & & &
    %
  {L_2}\ar[dlll]|{m_{L_2}} \ar@(l,ur)@{.>}|(.75){i_2}[dllllllll]
        & & {K_2} \ar[ll]_{l_2} \ar[rr]^{r_2} \ar[d]|{m_{K_2}}
        & & {R_2} \ar[d]^{m_{R_2}} \\
    %
    %
    {G}
     & & {D_1} \ar[ll]^{l^*_1} \ar[rrrrr]_{r^*_1}
     & & & &  & {H} & &
     & & & {D_2} \ar[lllll]^{l^*_2} \ar[rr]_{r^*_2}
     & & {M}  }
%\hspace{-1cm}
%\includegraphics{figure/processo}
\]
\caption{Sequential independence for
  $\rho = G \Rrel{p_1/m_1} H \Rrel{p_2/m_2} M$.}
\label{fi:strongseq}
\end{figure}

\begin{proposition}[interchange operator]
  \label{pr:interchangeEG}
  Let $\rho = {G} \Rrel{p_1/m_1} {H} \Rrel{p_2/m_2} {M}$ be a
  derivation whose components are sequentially independent via
  an independence pair $\xi$.
  % 
  Then, a derivation $IC_\xi(\rho) = {G} \Rrel{p_2/m^*_2}
  {H^*} \Rrel{p_1/m^*_1} {M}$ can be uniquely constructed.
  %
  The interchange is called \emph{proper} when it produces a
  derivation that is again sequentially independent.
  % sen, such
  % that its components are sequentially independent via a canonical
  % independence pair $\xi^*$.
\end{proposition}

We explicitly observe that the result of the interchange of two
sequentially independent rewrites is still weak sequentially
independent, but, differently from what happens for linear rules, it
could fail to be sequentially independent due to non-uniqueness of the
independence pair. This motivates the notion of proper interchange.

The interchange operator is used to introduce a notion of shift
equivalence~\cite{CMREHL:AAGT}, identifying (as for the analogous
permutation equivalence of $\lambda$-calculus) those derivations which
differ only for the scheduling of independent steps. Due to the fact
that the interchange of a sequential independence derivation is not
necessarily sequential independent some care must be put for making the
relation symmetric.

\begin{definition}[shift equivalence]
  \label{de:shift-equivalence}
  The derivations $\rho$ and $\rho'$ are \emph{shift equivalent},
  written $\rho \equiv^{sh} \rho'$, if $\rho'$ can be obtained from
  $\rho$ by repeated proper interchanges of pairs of
  sequentially independent rewrite steps.
\end{definition}
%
If we are
interested in the way $\rho'$ is obtained from $\rho$, we write
$\rho \equiv^{sh}_\perm \rho'$, for
$\perm : \interval{n} \to \interval{n}$ the associated permutation.
%
It is easy to see that, due to the requirement that interchanges are proper, the relation $\equiv^{sh}$ is indeed symmetric.

For instance, in Fig.~\ref{fi:running-rewriting} it is easy to see
that the derivation $G_s \Rrel{p_a} G_b \Rrel{p_b} G_{ab}$
consists of sequentially independent direct derivations. It is shift
equivalent to $G_s \Rrel{p_b} G_a \Rrel{p_a} G_{ab}$,
via the permutation $\perm = \{(1,2),(2,1)\}$.

Two decorated derivations are said to be shift equivalent when the
underlying derivations are, i.e.,
$\langle \alpha, \rho, \omega \rangle \equiv^{sh} \langle \alpha,
\rho', \omega \rangle$ if $\rho \equiv^{sh} \rho'$. Then the
equivalence of interest arises by joining abstraction and shift equivalence.

\begin{definition}[concatenable traces]
  We denote by $\equiv^c$ the equivalence on decorated derivations
  arising as the transitive closure of the union of the relations
  $\equiv^{a}$ and $\equiv^{sh}$.
%
  Equivalence classes of decorated derivations with respect to
  $\equiv^c$ are denoted as $[\psi]_c$ and are called
  \emph{concatenable (derivation) traces}.
\end{definition}
%
We will sometimes annotate $\equiv^c$ with the permutation relating
the equivalent permutations. Formally, $\equiv^c_\sigma$ can be
defined inductively as: if $\psi \equiv^{a} \psi'$ then
$\psi \equiv^c_{id} \psi'$ , if $\psi \equiv^{sh}_{\sigma} \psi'$ then
$\psi \equiv^c_{\sigma} \psi'$, and if
$\psi \equiv^{c}_{\sigma} \psi'$ and
$\psi' \equiv^{c}_{\sigma'} \psi''$ then
$\psi \equiv^{c}_{\sigma' \circ \sigma} \psi''$.

{ %AC  \full ***

Several proofs concerning concatenable traces exploit a 
property of equivalence $\equiv^c$ presented in \cite[Sec. 3.5]{Handbook}, 
that we summarize and adapt here to our framework.

If $\psi$ and $\psi'$ are decorated derivations, then a \emph{consistent permutation}
between their steps relates two direct derivations if they consume
and produce the same items, up to an isomorphism that is consistent with the decorations.

% $\psi \equiv^c \psi'$ if and only if 
%they have the same length (say $n$) and  there is a permutation $\perm:
%\interval{n} \to \interval{n}$ relating their direct derivations  that is 
%\emph{consistent}, i.e.~related direct derivations use the same rules and 
%consume/produce essentially the same items (nodes or edges) of corresponding graphs. 
%
%Essentially, a consistent permutation relates two direct derivations if they consume
%and produce the same items, up to an isomorphism that is consistent with the decorations.

%The formal definition is based on the notion of \emph{consistent five-tuple} Def. 3.5.1 of \cite{Handbook}, 
%and the  
%
%
%
%$|\psi| = |\psi'| \stackrel{\mathit{def}}{=} n$ and there is a permutation $\perm:
%\interval{n} \to \interval{n}$ which is \emph{consistent}, that is:

\begin{definition}[consistent permutation]
\label{de:consistent_permutation}
%\begin{definition}[consistent function between decorated derivations]
%Given a decorated derivation  $\psi = \langle \alpha, \rho, \omega \rangle:  G_0 \Rrel{}^* G_n$, 
%let $\col{\psi}$ be the colimit of the corresponding diagram in category $\tgraph{T}$.
%A \emph{consistent function} $\perm$ from $\psi$ to $\psi'$ is a function $f: \interval{|\psi|} \to \interval{|\psi'|}$

Given a decorated derivation  $\psi = \langle \alpha, \rho, \omega \rangle:  G_0 \Rrel{}^* G_n$, 
we denote by $\col{\psi}$ the colimit of the corresponding diagram in category $\tgraph{T}$, and by $in^X_{\col{\psi}}$
the injection of $X$ into the colimit, for any graph $X$ in $\rho$.
Given two such decorated derivations $\psi$ and $\psi'$ of equal length $n$, 
a \emph{consistent permutation} $\perm$ from $\psi$ to $\psi'$ is a permutation
$\perm$ on $\interval{n}$ such that
\begin{enumerate}
\item there exists an isomorphism $\xi: \col{\psi} \to \col{\psi'}$;
\item for each $i \in \interval{n}$ the direct derivations $\delta_i$ of $\psi$ and $\delta_{\perm(i)}$ of $\psi'$
use the same rule;

\item for each $i \in \interval{n}$, let  $p : (L \stackrel{l}{\leftarrow} K \stackrel{r}{\rightarrow} R)$ be the
rule used by direct derivations $\delta_i: G_{i-1} \Rrel{p/m} G_{i}$ and
$\delta'_{\perm(i)}: G'_{\perm(i)-1} \Rrel{p/m'} G'_{\perm(i)}$; then 
\begin{itemize}
\item$\xi \circ in^{G_{i-1}}_{\col{\psi}} \circ m^L =
  in^{G_{\perm(i)-1}}_{\col{\psi'}} \circ m'^L$, and 
  \item $\xi \circ in^{G_{i}}_{\col{\psi}} \circ m^R =
  in^{G_{\perm(i)}}_{\col{\psi'}} \circ m'^R$;
%l_i^* \circ m_i^* = l_i'^* \circ m_i'^*$.
\end{itemize}

\item {[$\alpha$-consistency]} $\xi \circ in^{G_0}_{\col{\phi}} \circ \alpha = in^{G'_0}_{\col{\phi'}} \circ \alpha'$;

\item {[$\omega$-consistency]}  $\xi \circ in^{G_n}_{\col{\phi}} \circ \omega = in^{G'_n}_{\col{\phi'}} \circ \omega'$;

%\item for each $i \in \interval{n}$, let  $p : (L \stackrel{l}{\leftarrow} K \stackrel{r}{\rightarrow} R)$ be the 
%rule used by direct derivations $\delta_i: G_{i-1} \Rrel{p/m} G_i$ and 
%$\delta'_{\perm(i)}: G'_{\perm(i)-1} \Rrel{p/m'} G'_\perm(i)$; then for each item $x$ consumed by $p$ 
%(i.e., $x \in L \setminus l(K)$), it  holds
%$\xi (in^{G_{i-1}}_{\col{\psi}}(m^L(x))) = in^{G'_{\perm(i)-1}}_{\col{\psi'}}({m'}^L(x))$;
%
%\item the same conditions holds for items created by $p$, i.e., for each $x \in R \setminus r(K)$ it 
%holds $\xi (in^{G_{i}}_{\col{\psi}}(m^R(x))) = in^{G'_{\perm(i)}}_{\col{\psi'}}({m'}^R(x))$.

\end{enumerate}
A permutation $\perm$ from $\psi$ to $\psi'$ is called \emph{left-consistent} if it satisfies 
conditions (1)-(4), but possibly not $\omega$-consistency.
It is easy to show, by induction on the length of derivations, that the isomorphism 
$\xi: \col{\psi} \to \col{\psi'}$ is uniquely determined by conditions (2)-(4), if it exists. 
%Essentially, a consistent permutation relates two direct derivations if they consume
%and produce the same items, up to an isomorphism that is consistent with the decorations.
%steps of two decorated derivations
%they have the same length (say $n$) and  there is a permutation $\perm:
%\interval{n} \to \interval{n}$ relating their direct derivations  that is 
%\emph{consistent}, i.e.~related direct derivations use the same rules and 
%consume/produce essentially the same items (nodes or edges) of corresponding graphs

\end{definition}

In the case of linear rules the existence of a consistent permutation
is a characterisation of equivalence $\equiv^c$. Here, it just
provides a necessary condition.

\begin{lemma}
\label{le:consistent_permutations}
Let $\psi$, $\psi'$ be decorated derivations. 
\begin{enumerate}
\item if $\psi \equiv^c_\sigma \psi'$ then
$|\psi| = |\psi'|$ and $\perm$ is a consistent permutation on 
$\interval{|\psi|}$ between them. We write  $\psi \equiv^{c}_\perm \psi'$ in this case.
%relating direct derivations of $\psi$ and $\psi'$. 
\item If $\psi; \psi_1  \equiv^{c}_\perm \psi'; \psi'_1$ and $\psi  \equiv^{c}_{\perm_0} \psi'$, 
then $\perm_0$ is the restriction of $\perm$ to $\interval{|\psi|}$. In this case it also holds
$\psi_1  \equiv^{c}_{\perm_1} \psi'_1$, with $\perm_1(i) = \perm(i + |\psi|) -  |\psi|$.
\item
If $\psi \equiv^{c} \psi'$, then there is a unique consistent permutation $\perm$ such that 
$\psi \equiv^{c}_\perm \psi'$.
\end{enumerate}
\end{lemma}
} %AC

\begin{proof}{[sketch]}
\begin{enumerate}
\item This holds by  \cite[Thm. 3.5.3]{Handbook}. Just note that the proof of this direction does not use linearity of rules. 
%Statement (2) follows from  \cite[Lemma 3.6.10]{Handbook}, because we assumed rules to be consuming.
%Actually the proof of this last result uses linearity of rules, but it can be generalized to the present setting
%by observing that every direct derivation that deletes an item is sequentially dependent of (must follow)
%any direct derivation that merges that item with others, and symmetrically every direct derivation that
%creates an item must precede any direct derivation that merges that item with others.

\item Suppose by absurd that  $j$ be the smallest index in $\interval{|\psi|}$ such that 
$\perm(j) \not =  \perm_0(j)$. Let  $p : (L \stackrel{l}{\leftarrow} K \stackrel{r}{\rightarrow} R)$ be the 
rule used in $\delta_j$ and let 
$x \in L \setminus{l(K)}$ be an item consumed by it, which exists because all rules are consuming. 
By Definition~\ref{de:consistent_permutation} we deduce that both direct derivations $\delta'_{\perm(j)}$
and $\delta'_{\perm_0(j)}$ of $\psi';\psi'_1$ use the same rule $p$ (say, with matches $m'$ and $m''$), 
and that 
%From $\psi_1  \equiv^{c}_{\perm_1} \psi'_1$ we know that 
%and that $in^{G'_{\perm_1(j)-1}}_{\col{\psi'}}({m'}^L(x))
%= in^{G'_{\perm_2(j)-1}}_{\col{\psi'}}({m''}^L(x))$, i.e., 
the items ${m'}^L(x) \in G'_{\perm(j)-1}$ and 
${m''}^L(x) \in G'_{\perm_0(j)-1}$ which are consumed by $\delta'_{\perm(j)}$ and $\delta'_{\perm_0(j)}$, 
respectively, are identified in the colimit $\col{\psi';\psi'_1}$ (actually, from $\psi  \equiv^{c}_{\perm_0} \psi'$
we know that there is a morphism $G'_{\perm_0(j)-1} \to \col{\psi'}$, but we can compose it with 
the obvious -- not necessarily injective -- morphism  $\col{\psi'} \to  \col{\psi';\psi'_1}$).
 But given the shape of the derivation diagram determined
by the left-linearity of rules, and the 
properties of colimits in $\graph$, this is not possible, because there is no undirected path of morphisms 
relating the images of element $x \in L$ in  $G'_{\perm(j)-1}$ and $G'_{\perm_0(j)-1}$ respectively.
Therefore $\perm$ and $\perm_0$ must coincide on $\interval{|\psi|}$.

For the second part, by the fact just proved clearly $\perm_1$ is a
well-defined permutation on $\interval{|\psi_1|}$. Then the fact that
$\psi_1 \equiv^{c}_{\perm_1} \psi'_1$ is almost immediate. Only
commutation of the source decorations is not obvious, but it follows
from commutation of the target for $\psi \equiv^{c}_{\perm_0} \psi'$
and Definition~\ref{def:seq_com_decorated}.

\item Direct consequence of the previous point, considering zero-length decorated derivations $\psi_1$ and $\psi_1'$.
\end{enumerate}
%For statement (2) we sketch the proof following that of \cite[Lemma 3.6.10]{Handbook}, which exploits linearity 
%of rules. Suppose by absurd that there are two different consistent permutations $\perm_1, \perm_2$  from $\psi$ to $\psi'$, 
%and let $j$ be the smallest index in $\interval{|\psi|}$ such that, w.l.o.g., $\perm_1(j) < \perm_2(j)$. 
%Let  $p : (L \stackrel{l}{\leftarrow} K \stackrel{r}{\rightarrow} R)$ be the rule used in $\delta_i$ and let 
%$x \in L \setminus{l(K)}$ be an item consumed by it, which exists because all rules are consuming. 
%
%By Definition~\ref{de:consistent_permutation} we deduce that both direct derivations $\delta'_{\perm_1(j)}$
%and $\delta'_{\perm_2(j)}$ of $\psi'$ use the same rule $p$ (say, with matches $m'$ and $m''$),
%and that $in^{G'_{\perm_1(j)-1}}_{\col{\psi'}}({m'}^L(x))
%= in^{G'_{\perm_2(j)-1}}_{\col{\psi'}}({m''}^L(x))$, i.e., the items ${m'}^L(x) \in G'_{\perm_1(j)-1}$ and 
%${m''}^L(x) \in G'_{\perm_2(j)-1}$ which are consumed by $\delta'_{\perm_1(j)}$ and $\delta'_{\perm_2(j)}$, 
%respectively, and identified in the colimit $\col{\psi'}$. But given the shape of the derivation diagram determined
%by the left-linearity of rules, and the 
%properties of colimits in $\graph$, this is not possible, because there is no undirected path of morphisms 
%relating the images of element $x \in L$ in  $G'_{\perm_1(j)-1}$ and $G'_{\perm_2(j)-1}$ respectively.
\end{proof}

The sequential composition of decorated derivations lifts to
composition of derivation traces so that we can consider the
corresponding category.

\begin{definition}[category of concatenable traces]
  \label{de:abs-shift-cat}
   Let $\mathcal{G}$ be a graph grammar.
   The \emph{category of concatenable traces} of 
  $\mathcal{G}$, denoted by \tr{\mathcal{G}}, has abstract graphs as
  objects and concatenable traces as arrows.
%  In particular, if $\psi: G
%  \Rightarrow^{*}_{\mathcal{G}} H$, then $[\psi]_c$ is an arrow from $[G]$
%  to $[H]$. The identity arrow on $[G]$ is the ctc-equivalence class
%  of the identity derivation $\langle i, G, i \rangle$, where $i :
%  \can{G} \to G$ is any isomorphism.
%  and the composition of arrows $[\psi]_c: [G] \rightarrow [H]$ and
%  $[\psi']_c: [H] \rightarrow [X]$ is defined as $[\psi\,;\,\psi']_c:
%  [G] \rightarrow [X]$.
\end{definition}

%In the sequel we will often write $\mathbf{\psi} : G \to G'$ to refer to the corresponding trace $[\psi]_c : [G] \to [G']$.\todo{P:: vedere se fa casino}

\subsection{A weak prime domain for a grammar}
\label{ss:graph-dom}

For a grammar $\mathcal{G}$ we obtain a partially ordered representation of its derivations
starting from the initial graph by considering the concatenable traces ordered 
by prefix. 
%
Formally, as done in~\cite{Handbook,Bal:PhD} for linear
grammars, we consider the category
$\slice{[G_s]}{\tr{\mathcal{G}}}$, which, by definition of sequential
composition between traces, is easily shown to be a preorder.

\begin{proposition}
  Let $\mathcal{G}$ be a graph grammar. Then the category
  $\slice{[G_s]}{\tr{\mathcal{G}}}$ is a preorder.
\end{proposition}

\begin{proof}
  Let $[\psi] : [G_s] \to [G]$, $[\psi'] : [G_s] \to [G']$ be
  concatenable traces and let
  $[\psi_1], [\psi_2] : [\psi] \to [\psi']$ be arrows in the slice
  category. Spelled out, this means that $\psi_1, \psi_2: G \to G'$
  are such that $\psi; \psi_1 \equiv^c \psi; \psi_2 \equiv^c
  \psi'$. By point (2) of Lemma~\ref{le:consistent_permutations}, 
  using the fact that $\psi \equiv^c \psi$ we can conclude
  that $\psi_1 \equiv^c \psi_2$, as desired. 
%    
%   Spelled out, this means that $\psi_1, \psi_2: G \to G'$
%  are such that $\psi; \psi_1 \equiv^c \psi; \psi_2 \equiv^c
%  \psi'$. Using the fact that $\psi \equiv^c \psi$ we can conclude
%  that $\psi_1 \equiv^c \psi_2$, as desired. This follows
%  from~\cite[Lemma 3.6.4]{Handbook}, whose proof does not rely on
%  rule linearity and thus holds also in our setting.\todo{Vedere se
%    si puo' eliminare la dipendenza}
 \end{proof}

Explicitly, elements of the preorder are concatenable traces
$[\psi]_c : [G_s] \to [G]$ and, for $[\psi']_c : [G_s] \to [G']$, we
have $[\psi]_c \sqsubseteq [\psi']_c$ if there is $\psi'' : G \to G'$
such that $\psi ; \psi'' \equiv^c \psi'$.
%
Note that, given two concatenable traces $[\psi]_c : [G_s] \to [G]$
and $[\psi']_c : [G_s] \to [G']$, if
$[\psi]_c \sqsubseteq [\psi']_c \sqsubseteq [\psi]_c$ then $\psi$ can be
obtained from $\psi'$  by composing it with a zero-length
trace. Hence the elements of the partial order induced by
$\slice{[G_s]}{\tr{\mathcal{G}}}$ intuitively consist of classes of
concatenable traces whose decorated derivations  are
related by an isomorphism that has to be consistent with
the decoration of the source.
%
Once applied to the grammar in Fig.~\ref{fi:running-gg}, this
construction produces a domain isomorphic to that in
Fig.~\ref{fi:running-configurations}.

\begin{lemma}
\label{le:partial_order_gg}
  Let $\mathcal{G}$ be a graph grammar. The partial order induced by
  $\slice{[G_s]}{\tr{\mathcal{G}}}$, denoted $\poset{\mathcal{G}}$,
  has as elements
  $\ltrace{\psi} = \{ [\psi \cdot \nu]_c \mid \nu : \target{\psi}
  \stackrel{\sim}{\to} \target{\psi} \}$ and
  $\ltrace{\psi} \sqsubseteq \ltrace{\psi'}$ if
  $\psi;\psi'' \equiv^c \psi'$ for some decorated derivation $\psi''$.
%
%\textbf{old version}\\
%Let $\mathcal{G}$ be a graph grammar. The partial order induced by
%  $\slice{[G_s]}{\tr{\mathcal{G}}}$, denoted $\poset{\mathcal{G}}$,
%  has as elements
%  $\ltrace{\psi} = \{ \psi \cdot \nu \mid \nu : \target{\psi}
%  \stackrel{\sim}{\to} \target{\psi} \}$ and
%  $\ltrace{\psi} \sqsubseteq \ltrace{\psi'}$ if
%  $\psi;\psi'' \equiv^c \psi'$ for some concatenable trace $\psi''$.
%  
\end{lemma}

\begin{proof}
  Immediate.
\end{proof}

% \full{ %AC
% \begin{lemma}
% \label{le:traces_left_consistent}
% Let $\mathcal{G}$ be a graph grammar and $\ltrace{\psi} \in \poset{\mathcal{G}}$. If $[\psi']_c, [\psi'']_c
% \in \ltrace{\psi}$ then there is a left-consistent permutation  
% from $\psi'$ to  $\psi''$.
% \end{lemma}
% }%AC
% \begin{proof}
%   Immediate.
% \end{proof}

The domain of interest is then obtained by ideal completion of
$\poset{\mathcal{G}}$, with (the principal ideals generated by) the elements in
$\poset{\mathcal{G}}$ as compact elements.
%
In order to give a proof for this, we need a preliminary technical lemma that
essentially proves the existence and provides the shape of the least 
upper bounds in the domain of traces.

\begin{lemma}[properties of $\equiv^c$]
  \label{le:prop-c}
  Let $\psi$ and $\psi'$ be decorated derivations. Then the following hold:
  \begin{enumerate}
  \item
    \label{le:prop-c:1}
    Let $\psi_1, \psi_1'$ be such
    that $\psi;\psi_1 \equiv^c_{\perm} \psi';\psi_1'$ and let
    $n = | \{ j \in \interval[|\psi|]{|\psi;\psi_1|-1} \mid \perm(j)
    < |\psi'| \}|$. Then for all $\phi_2, \phi_2'$ such that
    $\psi;\phi_2 \equiv^c \psi';\phi_2'$ it holds $|\phi_2| \geq n$
    and there are $\psi_2, \psi_2',\psi_3$ such that

    \begin{itemize}
    \item $\psi;\psi_1 \equiv^c \psi;\psi_2;\psi_3$
    \item $\psi;\psi_2 \equiv^c \psi';\psi_2'$

    \item $|\psi_2| = n$

    \end{itemize}

  \item
    \label{le:prop-c:2}
    Let $\psi_1, \psi_1'$, $\psi_2, \psi_2'$ be such that
    $\psi;\psi_1 \equiv^c_{\perm_1} \psi';\psi_1'$ and
    $\psi;\psi_2 \equiv^c_{\perm_2} \psi';\psi_2'$ with $\psi_1, \psi_2$
    of minimal length. Then $\psi_1 \equiv^c_\perm \psi_2 \cdot \nu$,
    where $\nu : \target{\psi_2} \to \target{\psi_2}$ is some graph isomorphism and
    $\perm(j) = \perm_2^{-1}(\perm_1(j + |\psi|))-|\psi|$ for
    $j \in \interval[0]{|\psi_1|-1}$.    
  \end{enumerate}
\end{lemma}

\begin{proof}
\begin{enumerate}
\item 
  %\label{le:prop-c:1}
  We first observe that if $\psi, \psi'$ are derivation traces and
  $\psi_1, \psi_1'$ are such that
  $\psi;\psi_1 \equiv^c_{\perm} \psi';\psi_1'$, with $|\psi| = k$, $|\psi'|=k'$, $|\psi;\psi_1| = |\psi';\psi_1'|=h$ then there is
  a $\phi_1$ such that
  $\psi;\psi_1 \equiv^c \psi;\phi_1 \equiv^c_{\perm_1} \psi';\psi_1'$
  and
  \begin{center}
    for $i, j \in \interval[|\psi|]{h-1}$, $i \leq j$ implies
     $\perm_1(i) \leq \perm_1(j)$. \hfill{(\dag)}
  \end{center}

  In order to prove this, we can proceed by induction on the number of
  inversions
  $x = |\{ (i, j) \in \interval[|\psi|]{h - 1} \mid i \leq
  j\ \land\ \perm(i) > \perm(j) \}|$, i.e., on the number of pairs
  $(i,j)$ in the interval of interest that do not respect the
  monotonicity condition. When $x=0$ the thesis immediately
  holds. Assume that $x > 0$. Then there are certainly indices
  $j \in \interval[|\psi|]{h-2}$ such that
  $\perm(j) > \perm(j+1)$. Among these, take the index $i$ such that
  $\perm(i+1)$ is minimal. Then it can be shown that direct derivations at 
  position $i$ and
  $i+1$ in $\psi_1$ are sequentially independent,  and thus they can be switched, i.e., there
  is $\phi_2$ such that
  $\psi; \phi_2 \equiv^c_{id[i \mapsto i+1, i+1 \mapsto i]} \psi;
  \psi_1$. Therefore
  $\psi; \phi_2 \equiv^c_{\perm \circ id[i \mapsto i+1, i+1 \mapsto
    i]} \psi'; \psi_1'$. This reduces the number of inversions and thus
  the inductive hypothesis allows us to conclude.
  % \begin{quote}
  %   $\perm'(j) = \left\{
  %     \begin{array}{ll}
  %       j          & \mbox{if $j <\perm(i+1)$ or $j > \perm(i)$}\\
  %       j+1        & \mbox{if $\perm(i+1) \leq j < \perm(i)$}\\
  %       \perm(i+1)   & \mbox{if $j = \perm(i)$}
  %     \end{array}
  %   \right.
  %   $
  % \end{quote}

  In the same way, we can prove that there is
  a $\phi'_1$ such that
  $\psi;\phi_1 \equiv_{\perm_2}^c \psi';\phi'_1 \equiv^c \psi';\psi_1'$
  and
  \begin{center}
    for $i, j \in \interval[|\psi'|]{h\!-\!1}$, if $i \leq j$ then
     $\perm^{-1}_2(i) \leq \perm^{-1}_2(j)$ {(\ddag)}
  \end{center}

  Putting conditions (\dag) and (\ddag) together we derive that
  $\psi;\psi_1 \equiv^c \psi;\phi_1\equiv^c_{\perm'} = \psi';\phi'_1
  \equiv^c \psi';\psi'_1$.  Now let $y \in\interval[|\psi|]{h-1}$ be
  the largest index such that $\perm'(y) < |\psi'|$ (or $y= |\psi|$ if
  it does not exist), let $l_3 = h - y$ and consider decorated
  derivations $\psi_2, \psi_3, \psi_2',\psi_3'$ such that
  $|\psi_3| = |\psi'_3| = l_3$ and
  $ \psi;\psi_2;\psi_3 = \psi;\phi_1 \equiv^c_{\perm'} \psi';\phi'_1 =
  \psi';\psi'_2;\psi'_3$.  By construction we obtain that
  $|\psi_2| = n$ and that $\perm'$ restricts to a permutation
  $\perm'_2$ on $\interval[0]{|\psi;\psi_2|-1}$. Commutation with the
  target decoration can be obtained, if necessary, by changing the
  $\omega$ decoration of $\psi_2$, affecting only the $\alpha$
  decoration of $\psi_3$. Thus
  % by Lemma~\ref{le:consistent_permutations}(1)
  we conclude that
  $\psi;\psi_2 \equiv^c \psi';\psi_2'$.

  Finally, notice that by the definition of $y$ and the properties of $\perm'$, 
  it follows that $\perm'(j) < |\psi'|$ for all $j \in
  \interval[|\psi|]{|\psi;\psi_2|-1}$ and $\perm'(j) \geq |\psi'|$ for all $j \in \interval[|\psi;\psi_2|]{h-1}$. 
  That is, the direct derivations in $\psi_2$ match 
  all direct derivations of $\psi'$ that are not matched in $\psi$. This implies that 
  there cannot exist a derivation $\phi_2$ shorter than $n$ such that 
  $\psi;\phi_2 \equiv^c \psi';\phi_2'$ for some $\phi_2'$.

\item 
%The proof is by induction on $k = |\psi|$. 
%
%  If $k = 0$, then by point (\ref{le:prop-c:1}) we have
%  $|\psi_1'| = |\psi_2'| = 0$, i.e., $\psi_1'$ and $\psi_2'$ are
%  symmetries. Therefore
%  $\psi;\psi_1;{\psi_1'}^{-1} \equiv^c_{\perm_1} \psi'
%  \equiv^c_{\perm^{-1}_2} \psi;\psi_2;{\psi_2'}^{-1}$, whence the
%  thesis.
%
%
%  If $k>0$, let $\psi = \psi_0;\delta$. Then, by inductive hypothesis
%  we get that $\delta; \psi_1 \equiv^c_\perm \delta;\psi_2 \cdot \nu$,
%  where $\nu : \target{\psi_2} \to \target{\psi_2}$ is some iso and
%  $\perm(j) = \perm_2^{-1}(\perm_1(j))$ for
%  $j \in \interval{|\psi_1|+1}$.
%  %
%  To conclude we just need to show that $\perm(1) = 1$, [looks ok, but
%  HOW CAN WE SHOW IT?]
%
%
%  [BOZZA ALTERNATIVA]
  Let $n = |\psi|$ and $m = |\psi_1| = |\psi_2|$, which must have the same length.
  By the last part of the proof of the previous point,
  since 
  %$\psi;\psi_1 \equiv^c_{\perm_1} \psi';\psi_1'$ and 
  both $\psi_1$ and $\psi_2$ are of 
  minimal length, we have that for all $j \in
  \interval[n]{n+m-1}$ it holds  $\perm_1(j) < |\psi'|$ and $\perm_2(j) < |\psi'|$.
%  [This can be proved formally as follows. Let $j'$ be the maximal
%  index such that $\perm_1(j') > |\psi'|$. Then $\delta_{j'}$ is sequential
%  independent of all the following direct derivations in $\psi_1$, and can
%  be shifted to the end of $\psi_1$. Correspondingly, direct derivation
%  $\delta_{i_1(j')}$ of $\psi_1'$ is sequentially independent of all the
%  following direct derivations of $\psi_1'$, and can be moved to the end
%  of $\psi_1'$. Thus we can delete these two direct derivations obtaining
%  a shorter $\hat{\psi_1}$, which is absurd.]
%
%  Similarly, we have that  for all $j \in
%  \interval[|\psi|]{|\psi;\psi_2|}$ it holds  $\perm_2(j) \in
%  \interval{|\psi'|}$. 
Furthermore, $\perm_1(\interval[n]{n+m-1}) = \perm_2(\interval[n]{n+m-1})$, 
because both $\psi_1$ and  $\psi_2$ consist of direct derivation that match 
those of $\psi'$ which are not matched in $\psi$.

Thus 
%for all $j \in \interval[n]{n+m-1}$
%  we have $\perm_2^{-1}(\perm_1(j)) \in \interval[n]{n+m-1}$, and 
$\perm(j) = \perm_2^{-1}(\perm_1(j + |\psi|))-|\psi|$ is a
well-defined permutation on $\interval[0]{|\psi_1|-1}$ from $\psi_1$
to $\psi_2$. It is easy to see that the only condition that can be
violated for concluding $\psi_1 \equiv^c_\sigma \psi_2$ is commutation
of the target decorations. This can be reestablished by post-composing
$\psi_2$ with a graph isomorphism.
  %
  % Conditions (1)-(3) of Definition~\ref{de:consistent_permutation}
  % are guaranteed by the corresponding properties of $\perm_1$ and
  % $\perm_2$, and
  % $\alpha$-consistency holds because both $\psi_1$ to $\psi_2$ start
  % from the same
  % graph ($\target{\psi}$). Therefore $\perm$ is a left-consistent
  % permutation from $\psi_1$ to $\psi_2$.
  % From the fact that $\psi_1$ and $\psi_2$ apply identical
  % productions
  % to corresponding items we can infer that the final graphs are
  % isomorphic, but not necessarily
  % that $\perm$ is $\omega$-consistent.
\end{enumerate}
\end{proof}

Relying on the results above we can easily prove that the ideal
completion of the partial order of traces is a domain.

\begin{proposition}[domain of traces] 
  \label{pr:domain-gg} 
  Let $\mathcal{G}$ be a graph grammar. Then
  $\dom{\mathcal{G}} =  \ideal{\poset{\mathcal{G}}}$
  % \ideal{\slice{[G_s]}{\tr{\mathcal{G}}}}$ 
  is a
  domain.
\end{proposition}

\begin{proof}
  By Lemma~\ref{le:generators}
  % ~\ref{le:prop-c}(\ref{le:prop-c:2}),
  it is sufficient to prove 
  % (1) that
  % $\poset{\mathcal{G}}$ is denumerable,
  (1) that
  $\principal{\ltrace{\psi}}$ is finite for every $\ltrace{\psi} \in
  \poset{\mathcal{G}}$, and (2) that if $\{\ltrace{\psi_1},
  \ltrace{\psi_2},
  \ltrace{\psi_3}\}$ is pairwise consistent then $\ltrace{\psi_1}
  \sqcup
  \ltrace{\psi_2}$ exists and is consistent with $\ltrace{\psi_3}$.

  % The partial order $\dom{\mathcal{G}}$ can be obtained by completion
  % of $\poset{\mathcal{G}}$, i.e.,
  % $\dom{\mathcal{G}} = \ideal{\poset{\mathcal{G}}}$.

  \begin{enumerate}
  % \item Denumerability follows from the finiteness of graphs and of
  %   the set of rules of a grammar, and by the fact that derivations
  %   are taken up to abstraction isomorphism.

  \item Let $\ltrace{\psi'} \sqsubseteq \ltrace{\psi}$. By
    Lemma~\ref{le:partial_order_gg}
    % and by Lemma~\ref{le:consistent_permutations}(1)
    we know that
    $\psi';\psi'' \equiv^c_{\perm} \psi$ for some decorated derivation
    $\psi''$ and a
    % consistent
    permutation $\perm$.  Now suppose that
    $\psi'_1$ and $\psi'_2$ are decorated derivations such that
    $\psi'_1;\psi''_1 \equiv^c_{\perm_1} \psi$ and
    $\psi'_2;\psi''_2 \equiv^c_{\perm_2} \psi$ for some $\psi''_1$,
    $\psi''_2$, and that
    $\perm_1(\interval[0]{|\psi'_1|}) =
    \perm_2(\interval[0]{|\psi'_2|}) \subseteq
    \interval[0]{|\psi|}$. Then $\perm_2^{-1}\circ \perm_1$ is a
    permutation on $\interval[0]{|\psi'_1|}$ from $\psi'_1$ to
    $\psi'_2$ witnessing $\psi'_1 \equiv^c_{\perm_2^{-1}\circ \perm_1} \psi'_2; \nu$ for some isomorphism $\nu$. 
    % which satisfies conditions (1)-(4) of
    % Definition~\ref{de:consistent_permutation}.
    Therefore
    % by  Lemma~\ref{le:traces_left_consistent}
    $\ltrace{\psi'_1} = \ltrace{\psi'_2}$.  As a consequence, the
    cardinality of $\principal{\ltrace{\psi}}$ is bound by
    $2^{|\psi|}$.

    % The image
    % $\perm(\interval[0]{|\psi'|} \subseteq \interval[0]{|\psi|}$ is
    % invariant for elements of $\ltrace{\psi'}$, and any such subset
    % of $\interval[0]{|\psi|}$ uniquely determine a trace
    % 
    % for any $\ltrace{\psi}$ in $\poset{\mathcal{G}}$ the set
    % $\{ \ltrace{\psi'} \mid \ltrace{\psi'} \sqsubseteq \ltrace{\psi}
    % \}$ is finite;

  \item Given two consistent elements $\ltrace{\psi_1}$ and
    $\ltrace{\psi_2}$ of $\poset{\mathcal{G}}$, there exists
    $\ltrace{\psi} = \ltrace{\psi_1} \sqcup \ltrace{\psi_2}$, where
    $\psi$ is the minimal common extension of $\psi_1$ and $\psi_2$,
    provided by Lemma~\ref{le:prop-c}(\ref{le:prop-c:1}). Uniqueness
    of $\ltrace{\psi}$ follows by
    Lemma~\ref{le:prop-c}(\ref{le:prop-c:2})
    % and~\ref{le:traces_left_consistent} 
    because minimal common are essentially unique (up to $\equiv^c$
    and right-composition with isomorphisms).  Suppose further that
    $\ltrace{\psi_3}$ is compatible with both $\ltrace{\psi_1}$ and
    $\ltrace{\psi_2}$: we have to show that it is compatible with
    $\ltrace{\psi}$.  Let
    $\ltrace{\psi'} = \ltrace{\psi_2} \sqcup \ltrace{\psi_3}$. Then
    there exist $\phi_1$, $\phi$ and $\phi'$ such that
    $\psi_1 ; \phi_1 \equiv^c_{\perm_1} \psi_2 ; \phi \equiv^c_{\perm}
    \psi$ and $\psi_2 ; \phi' \equiv^c_{\perm'} \psi'$ for suitable
    % consistent
    permutations $\perm_1$, $\perm$ and $\perm'$.

    We conclude by showing that either $\ltrace{\psi}$ and $\ltrace{\psi'}$ 
    are compatible, or $\ltrace{\psi_1} \sqcup  \ltrace{\psi_3}$ and $\ltrace{\psi'}$
    are compatible, both of which are equivalent and imply the thesis. We proceed by 
    induction on $k = |\psi_1|+|\psi_3|$.  If
    $|\psi_1|=0$, i.e.~$\psi_1$ is a zero-length decorated derivation, hence,
    by Lemma~\ref{le:prop-c}, also $\phi$ is so and thus
    $\ltrace{\psi} = \ltrace{\psi_2}$, and the latter is compatible
    with $\ltrace{\psi'}$. If $|\psi_3|=0$ we conclude analogously.  
    If $k>0$, let $\delta$ be the last
     derivation step in $\psi_1$, i.e.,
    $\psi_1 = \psi_1'; \delta$. If $\sigma_1(|\psi_1|-1) < |\psi_2|$,
    namely if step $\delta$ is already in $\psi_2$, then by
    Lemma~\ref{le:prop-c} we get that
    $\ltrace{\psi} = \ltrace{\psi_1'} \sqcup \ltrace{\psi_2}$. Since
    $|\psi_1'| < k$ we conclude by inductive hypothesis
    that $\psi$ and $\psi'$ are compatible. If instead,
    $\sigma_1(|\psi_1|-1) \geq |\psi_2|$ then, again by Lemma~\ref{le:prop-c},
    we can write $\psi$ as
    $\psi \equiv^c_{\sigma''} \psi_2; \phi''; \delta'$, where
    $\ltrace{\psi_2; \phi''} = \ltrace{\psi_1'} \sqcup
    \ltrace{\psi_2}$ and $\sigma''(|\psi_1|-1) = |\psi|-1$, i.e., $\delta$
    is mapped to $\delta'$. Hence, by inductive hypothesis
    $\psi_2; \phi''$ and $\psi'$ are compatible.
    %

    Now, since $\ltrace{\psi_1}$ and  $\ltrace{\psi_3}$ are compatible (thus
    $\psi_1;\phi'_1 \equiv^c_{\perm_3} \psi_3;\phi'_3$ for suitable derivations 
    $\phi'_1, \phi'_3$ and permutation $\perm_3$), either step $\delta$ is 
    already in $\psi_3$ (thus $\perm_3(|\psi_1|-1) < |\psi_3|)$, or it isn't, and 
    $\perm_3(|\psi_1|-1) \geq |\psi_3|$. In the first case $\delta$ is related to 
    a step in $\psi'$, and it follows that $\ltrace{\psi'} \sqcup  \ltrace{\psi_2; \phi''} = 
    \ltrace{\psi'} \sqcup  \ltrace{\psi_2; \phi'';\delta'}$ and we conclude. 
    If instead $\delta$ is not a step in $\psi_3$,  we can write $\psi_3;\phi'_3$ as
     $\psi_3;\phi''_3;\delta''$, where step $\delta''$ matches step $\delta$ of $\psi_1$.
     By inductive hypothesis we have that $\psi_3;\phi''_3$ and $\psi'$ are compatible, 
     and we get $\ltrace{\psi_3;\phi''_3} \sqcup \ltrace{\psi'} = 
     \ltrace{\psi_2;\phi''} \sqcup \ltrace{\psi'}$. Since both steps $\delta'$ and $\delta''$ are 
     related by suitable
     % consistent
     permutations to step $\delta$ of $\psi_1$, we 
     can extend uniformly the two derivations preserving consistency,  obtaining
      $\ltrace{\psi_3;\phi''_3;\delta''} \sqcup \ltrace{\psi'} = 
     \ltrace{\psi_2;\phi'';\delta'} \sqcup \ltrace{\psi'} =  \ltrace{\psi} \sqcup \ltrace{\psi'}$, as desired.

%    
%    Now, if $\psi \equiv^c \psi_2; \phi'';\delta'$ and
%    $\psi' \equiv^c \psi_2 ; \phi'$ are not compatible, it must be that $\delta'$ consumes
%    an item that is also consumed by some direct derivation in
%    $\phi'$. However, this is not possible, since the direct
%    derivation in $\phi'$ are the same as in $\psi_3$, which is
%    compatible with $\psi_1$ by hypothesis. Hence we conclude.
%    %
\todo{A: provato ad aggiustare....}
    \todo{P: il finale \`e tirato, ma al momento non vedo come fare
      meglio}  \end{enumerate}
\end{proof}

We can show that $\dom{\mathcal{G}}$ is a weak prime domain. The proof relies on the fact that irreducibles
are (the principal ideals of) elements of the form $\ltrace{\epsilon}$, where
$\epsilon = \psi; \delta$ is a decorated derivation such that its last
direct derivation $\delta$ cannot be shifted back, i.e., minimal
traces enabling some direct derivation. These are called
\emph{pre-events} in~\cite{Handbook,Bal:PhD}, where graph
grammars are linear and thus, consistently with Lemma~\ref{pr:irr-prime-alg}, such
elements provide the primes of the domain. Two irreducibles
$\ltrace{\epsilon}$ and $\ltrace{\epsilon'}$ are interchangeable when
they are different minimal traces for the same direct derivation.

\begin{theorem}[weak prime domains from graph grammars]
  \label{th:fusion-domain-for-gg}
  Let $\mathcal{G}$ be a graph grammar. Then
  $\dom{\mathcal{G}}$ is a weak prime domain.
\end{theorem}

\begin{proof}
  We know by Proposition~\ref{pr:domain-gg} that $\dom{\mathcal{G}}$
  is a domain. Hence, recalling Definition~\ref{de:fusion-domain-new},
  we have to show that $\dom{\mathcal{G}}$ is weak prime
  algebraic.

  We will exploit the characterisation in
  Lemma~\ref{le:generators}. First provide a characterisation of
  irreducibles and of the interchangeability relation among them. As
  usual, we confuse compact elements of $\dom{\mathcal{G}}$ with the
  corresponding generators in $\poset{\mathcal{G}}$.

  \medskip

  As mentioned above, irreducibles in $\dom{\mathcal{G}}$ are, in the
  terminology of~\cite{Handbook,Bal:PhD}, \emph{pre-events}, namely
  elements of the form $\ltrace{\epsilon}$, where
  $\epsilon = \psi; \delta$ is a decorated derivation such that its
  last direct derivation $\delta$ cannot be switched back. Formally,
  $\ltrace{\epsilon}$ is a pre-event if letting $n = |\epsilon|$ then
  for all $\epsilon = \psi; \delta \equiv^c_\perm \psi'$ it holds
  $\perm(n) = n$.

  In fact, assume that
  $\ltrace{\epsilon} = \ltrace{\psi_1} \sqcup \ltrace{\psi_2}$, and
  let
  $\epsilon  \equiv^c_\perm \psi_1 ; \psi_1' \equiv^c_{\perm'} \psi_2;
  \psi_2'$ for suitable $\psi_1', \psi_2'$ of minimal length. 
  %
  Since $\epsilon$ is a pre-event, we have that if
  $n = |\psi; \delta| = |\psi_1 ; \psi_1'| = |\psi_2 ; \psi_2'|$, then
  $\perm'(n) = n$. This implies that $|\psi_1'| = 0$ (and thus
  $\ltrace{\epsilon} = \ltrace{\psi_1}$) or $|\psi_2'| = 0$ (and thus
  $\ltrace{\epsilon} = \ltrace{\psi_2}$),
  as desired.

   \medskip

   Two irreducibles $\ltrace{\epsilon}$ and $\ltrace{\epsilon'}$ are
   interchangeable iff the corresponding traces are compatible and
   whenever $\epsilon; \psi_1 \equiv^c_{\perm} \epsilon' ; \psi_1'$
   with $\psi_1, \psi_1'$ of minimal length (thus
   $\ltrace{\epsilon; \psi_1} = \ltrace{\epsilon'; \psi'_1} =
   \ltrace{\epsilon} \sqcup \ltrace{\epsilon'}$), then
   $\perm(|\epsilon|) = |\epsilon'|$.

   In fact, assume that $\ltrace{\epsilon} = \ltrace{\psi; \delta}$
   and $\ltrace{\epsilon'} = \ltrace{\psi';\delta'}$ are
   interchangeable, and
   $\epsilon; \psi_1 \equiv^c_{\perm} \epsilon' ; \psi_1'$ with
   $\psi_1, \psi_1'$ of minimal length. By the proof of
   Lemma~\ref{le:prop-c}(\ref{le:prop-c:1})
%  . Hence they are
%  consistent and we can take their join
%  $\epsilon \sqcup \epsilon' = \epsilon ; \psi_1 \equiv^c_{\perm}
   we have that $\perm$ maps steps in $\psi_1$ to
   $\epsilon'$ and, analogously, $\perm^{-1}$ maps steps in
   $\psi_1'$ to $\epsilon$ (formally, $\perm(j) < |\epsilon'|$ for $j
   \geq |\epsilon|$ and, dually, if $\perm(j) \geq
   |\epsilon'|$ then $j <
   |\epsilon|$). By Lemma~\ref{le:eq-char}(\ref{le:eq-char:4}) we have
   that $\ltrace{\epsilon} \sqcup \ltrace{\epsilon'} = \ltrace{\psi}
   \sqcup \ltrace{\epsilon'} = \ltrace{\epsilon} \sqcup
   \ltrace{\psi'}$. Hence we can view the previous equivalence of
   decorated derivations as $\psi; (\delta ; \psi_1) \equiv^c_{\perm}
   (\psi'; \delta') ;\psi_1'$, with $\delta ; \psi_1$ and
   $\psi_1'$ of minimal length. This means that
   $\perm$ maps steps in $\delta;\psi_1$ to
   $\epsilon'$ and, with a dual argument, steps in
   $\delta';\psi_1'$ to
   $\epsilon$. Putting all this together we get that necessarily
   $\perm(|\epsilon|) = |\epsilon'|$, as desired.

   For the converse, assume that
   $\ltrace{\epsilon}$,
   $\ltrace{\epsilon'}$ are compatible, that $\ltrace{\psi} =
   \ltrace{\epsilon} \sqcup \ltrace{\epsilon'}$, and that $\psi
   \equiv^c \epsilon; \psi_1 \equiv^c_{\perm} \epsilon' ;
   \psi_1'$ where $\perm(|\epsilon|) =
   |\epsilon'|$. Then, reverting the reasoning above, we get that
   $\ltrace{\psi} \sqcup \ltrace{\epsilon'} = \ltrace{\epsilon} \sqcup
   \ltrace{\psi'}$, and thus we conclude that $\ltrace{\epsilon},
   \ltrace{\epsilon'}$ are interchangeable by
   Lemma~\ref{le:eq-char}(\ref{le:eq-char:4}).

  \medskip

  We conclude that $\dom{\mathcal{G}}$ is a weak prime domain, relying on
  Lemma~\ref{le:generators}. Let $\ltrace{\epsilon}$ with
  $\epsilon = \psi; \delta$ be an irreducible, and
  $\ltrace{\epsilon} \sqsubseteq \ltrace{\psi_1} \sqcup
  \ltrace{\psi_2}$.
  %
  Let $\psi_1'$ and $\psi_2'$ be decorated derivations of minimal
  length such that
  $\epsilon;\psi \equiv^c_\perm \psi_1;\psi_1' \equiv^c_{\perm_1}
  \psi_2;\psi_2'$ for some $\psi$. If
  $\perm(|\epsilon|) \in \interval[0]{|\psi_1|-1}$ then consider
  $\phi_1$ such that
  $\psi_1;\psi_1' \equiv^c_{\perm'} \phi_1; \psi_1'$ and
  $\perm'(\perm(|\epsilon|))$ is minimal. Then $\ltrace{\phi_1}$ is an
  irreducible, $\ltrace{\phi_1}$ and $\ltrace{\epsilon}$ are
  interchangeable, and clearly
  $\ltrace{\phi_1} \sqsubseteq \ltrace{\psi_1}$. If instead
  $\perm(|\epsilon|) \geq |\psi_1|$ we have that
  $\perm_1(\perm(|\epsilon|)) < |\psi_2|$, and we can conclude, in the
  same way, the existence of
  $\ltrace{\phi_2} \sqsubseteq {\ltrace{\psi_2}}$ irreducible and
  interchangeable with $\ltrace{\epsilon}$.
\end{proof}

% ALTERNATIVE APPROACH: Define directly the event structure, as done in
% the cited paper, and prove that it is a connected {\esabbr} (not really much
% different, I guess the first approach is simpler):

% \begin{itemize}
% \item events are equivalence classes of pre-events up to interchangeability (see above)

% \item derivations which contain an event $\epsilon$ are $Der([\epsilon]) = \{ \delta \mid \exists \delta_\epsilon \in [\epsilon].\ \exists \delta'.\ \delta_\epsilon; \delta' = \delta \}$
% \item $Der(X) = \bigcap_{[\epsilon] \in X} Der([\epsilon])$
% \item consistency is $Con(X)$ when $Der(X) \neq \emptyset$

% \item say that $\delta \prec \delta'$ when $\delta' = \delta; s$ where
%   $s$ is a direct derivation;

% \item enabling is $X \vdash [\epsilon]$ when for any $\delta$ minimal in
%   $Der(X)$ there exists $\delta_\epsilon \in [\epsilon]$ such that
%   $\delta \prec \delta_\epsilon$
% \end{itemize}

Note that when the rules are right-linear the domain and {\esabbr} semantics
specialises to the usual prime event structure semantics
(see~\cite{Handbook,Bal:PhD,Sch:RRSG}), since the construction of the
domain in the present paper is formally the same as
in~\cite{Handbook}.

\subsection{Any connected {\esabbr} is generated by some grammar}
\label{ss:es-graph}

By Theorem~\ref{th:fusion-domain-for-gg}, given a graph grammar
$\mathcal{G}$ the domain $\dom{\mathcal{G}}$ is weak prime.
We next show that also the converse holds, i.e., any connected
{\esabbr} (and thus any weak prime domain) is generated by a suitable graph
grammar.
%
This shows that weak prime domains and connected {\esabbr} are
precisely what is needed to capture the concurrent semantics of
non-linear graph grammars, and thus strengthen our claim that they
represent the right structure for modelling formalisms with fusions.

\smallskip

\noindent
\textbf{Construction (graph grammar for a connected {\esabbr})} 
%
Let $\langle E, \#, \vdash \rangle$ be a 
% finite 
connected {\esabbr}. 
%
The grammar $\mathcal{G}_{E} = \langle T, P, \pi, G_s \rangle$ is
defined as follows.

First, for every element $e \in E$, we define the following graphs, which are
then used as basic building blocks
\begin{itemize}
\item $I_e$ and $S_e$ as shown in Fig.~\ref{fi:any-fes}(\subref{fi:any-fes-ie}) and Fig.~\ref{fi:any-fes}(\subref{fi:any-fes-Se});

\item let $\pmin{e}$ denote the set-theoretical product of the minimal enablings of
  $e$, i.e., $\pmin{e} = \Pi \{ X \subseteq E \mid X \vdash_0 e
  \}$; for every tuple $u \in \pmin{e}$ we define the graph $L_{u,e}$ as in
  Fig.~\ref{fi:any-fes}(\subref{fi:any-fes-Lue}).
\end{itemize}
Moreover, for every pair of events $e, e' \in E$ such that $e \# e'$,
we define a graph $C_{e,e'}$ as in
Fig.~\ref{fi:any-fes}(\subref{fi:any-fes-C}).

The set of productions is $P = E$, i.e., we add a rule for every event $e \in E$, and we define such rule in a way that
\begin{itemize}

\item it deletes $I_e$ and  $C_{e,e'}$ for each $e' \in E$ such that $e \# e'$.
\item it preserves the graph $S_e \cup \bigcup_{u \in U_e} L_{u,e}$

\item for all $e' \in E$, for all graphs $L_{u,e'}$ such that
  $e$ occurs in $u$, it merges the corresponding nodes and that of $S_{e'}$ into one.

\end{itemize}
The graph $S_e \cup \bigcup_{u \in U_e} L_{u,e}$ arises from $S_e$ and
$L_{u,e}$, $u \in \pmin{e}$ by merging all the nodes (we use $\bigcup$
and $\biguplus$ to denote union and disjoint union, respectively, with
a meaning illustrated in Fig.~\ref{fi:any-fes}(\subref{fi:any-fes-U})
and Fig.~\ref{fi:any-fes}(\subref{fi:any-fes-Uplus}).) Hence, there is a match for the
rule $e$ only if $S_e$ and all $L_{u,e}$ for $u \in \pmin{e}$ have been merged
and this happens if and only if at least one minimal enabling of $e$
has been entirely executed.  The deletion of the graphs $C_{e,e'}$ establishes the
needed conflicts. The rule is consuming since it deletes the node of graph
$I_e$.
%
\full{
Formally, the rule for $e$ has as left-hand side the graph
\[
  I_e \cup 
  (\bigcup_{\substack{e' \in E\\ e\#e'}} C_{e,e'}) \cup
  (\bigcup_{e' \in E} (S_{e'} \uplus \biguplus_{\substack{\ u'\in\pmin{e'}\\e \in u'}} L_{u',e'})) 
  \cup (S_e \cup \bigcup_{u \in \pmin{e}} L_{u,e}) 
\]
while the right-hand side is
\[
  (S_e \cup \bigcup_{u \in \pmin{e}} L_{u,e}) 
  \cup
  (\bigcup_{e' \in E} (S_{e'} \cup \bigcup_{\substack{\ u'\in\pmin{e'}\\e \in u'}} L_{u',e'}))
\]
}
%
The rule is schematised in
Fig.~\ref{fi:any-fes}(\subref{fi:any-fes-rule}), where it is intended
that $e$ occurs in $u_j^1, \ldots, u_j^{n_j}$ for $u_j^i \in U_{e_j}$,
$i \in \interval{n_j}$, $j \in \interval{k}$. Moreover
$e_1', \ldots, e_h'$ are the events in conflict with $e$ and, finally,
$U_e = \{ u_1, \ldots, u_n \}$.

The start graph is just the disjoint union of all the basic graphs
introduced above
\[
  G_s = (\bigcup_{e\#e'} C_{e,e'}) \cup
  \bigcup_{e \in E}  (I_e \cup S_e \uplus \biguplus_{u \in U_e} L_{u,e})
\]

\full{
Then the type graph is
\[
  T = (\bigcup_{e\#e'} C_{e,e'}) \cup
  \bigcup_{e \in E}  (I_e \cup S_e \cup \bigcup_{u \in U_e} L_{u,e})
\]
}
\smallskip

Note that the interfaces of the rules are not given explicitly. They
can be deduced from the left and right-hand side, and the
labelling. The same applies to the type graph.

% The requirement that ${E}$ has a finite set of events ensures that
% the associated graph grammar has a finite set of rules, and acts on
% finite graphs.
%
It is not difficult to show that the grammar
$\mathcal{G}_{E}$ generates exactly the {\esabbr} ${E}$. 
%The only technical restriction is the 
%requirement that the set of events is finite.

\begin{theorem}[connected ES from graph grammars]
  Let $\langle E, \#, \vdash \rangle$ be a 
  % finite 
  connected {\esabbr}.  Then,
  ${E}$ and $\ev{\dom{\mathcal{G}_{E}}}$ are isomorphic.
\end{theorem}

\begin{proof}
  First observe that any rule in $\mathcal{G}_{E}$ is executed at
  most once in a derivation since it consumes an item (the node of graph
  $I_e$) that is generated by no other rule. If we consider
  $\dom{\mathcal{G}_{E}}$, then the irreducibles are minimal
  $\ltrace{\epsilon}$ with $\epsilon = \psi; \delta$.
  %
  By the shape of rule $e$, the derivation $\psi$ must contain
  the occurrences of a minimal set of rules such that the graphs
  $S_e$ and $L_{u,e}$ for $u \in U_e $ are merged along the common node.
  % 
  By construction, in order to merge all such graphs, if we denote by
  $X_\psi$ the set of rules applied in $\psi$, it must be
  $X_\psi \supseteq C$ for some $C \in \conff{E}$ such that
  $C \vdash_0 e$. Therefore by minimality we conclude that
  $X_\psi \vdash_0 e$. Relying on this observation, a routine
  induction on the $|C|$ shows that minimal enablings $C \vdash_0 e$
  in $E$ are in one to one correspondence with irreducibles
  $\ltrace{\epsilon}$ in $\dom{\mathcal{G}_{E}}$. Recalling, that, in
  turn, irreducibles in $\dom{E}$ are again minimal enablings, i.e.,
  $\esir{C}{e}$ with $C \in\conff{E}$ such that $C \vdash_0 e$ we
  obtain a bijection between irreducibles in $\dom{\mathcal{G}_{E}}$
  and $\dom{E}$.

  The fact that the correspondence preserves and reflects the order
  is, again, almost immediate by construction. In fact, consider two
  irreducibles $\ltrace{\epsilon}$ and $\ltrace{\epsilon'}$ in
  $\dom{\mathcal{G}_{E}}$ and the corresponding irreducibles
  $\esir{C}{e}$ and $\esir{C'}{e'}$ in $\dom{E}$. If
  $\esir{C}{e} \subseteq \esir{C'}{e'}$, take
  $X = \esir{C'}{e'} \setminus \esir{C}{e}$. Then $\epsilon$ can be
  extended with the rules corresponding to the events in $X$, thus
  showing the existence of a derivation $\psi$ such that
  $\epsilon; \psi \equiv^c \epsilon'$. In fact, if this were not
  possible, there would be an event $e'' \in X$ such that the
  corresponding rule compete for deleting some item of the start graph
  with a rule $e_1$ in $\epsilon$, hence $e_1 \in \esir{C}{e}$. By
  construction, the only possibility is that the common item is
  $C_{e'',e_1}$. But this would mean that $e'' \# e_1$. This
  contradicts the fact that $\{ e_1, e''\} \subseteq \esir{C'}{e'}$.
  %
  The converse, i.e., the fact that if
  $\ltrace{\epsilon} \sqsubseteq \ltrace{\epsilon'}$ then
  $\esir{C}{e} \subseteq \esir{C'}{e'}$ is immediate.

  Recalling that domains are irreducible algebraic
  (Proposition~\ref{pr:domains-irr-alg}), we conclude that
  $\dom{\mathcal{G}_{E}}$ and $\dom{E}$ are isomorphic. 
  Since $E$ is connected {\esabbr}, by
  Theorem~\ref{th:es-dom-equivalence}, $E \simeq \ev{\dom{E}}$ and thus
  $\ev{\dom{\mathcal{G}_{E}}}$ and $E$ are isomorphic, as desired.
\end{proof}

\begin{figure}
  \hfill
  \mbox{}
  %
  \subcaptionbox{$I_{e}$\label{fi:any-fes-ie}}{
    \begin{tikzpicture}[node distance=10mm, >=stealth',x=8mm]
      % 
      \node at (0,0) [node, label=below:${i_e}$] (ie) {}
      node[above] {};
      % 
      \pgfBox
    \end{tikzpicture}
  }
  %
   \hfill
  %
  \subcaptionbox{$S_e$\label{fi:any-fes-Se}}[10mm]
  {
    \begin{tikzpicture}[node distance=10mm, >=stealth',x=8mm]
      % 
      \node at (0,0) [node, label=below:$e$] (ne0) {} edge [in=105, out=75,loop]  node [above] {$e$} ();
      % 
      \pgfBox
    \end{tikzpicture}
  }
  %
 \hfill
  %
  \subcaptionbox{$L_{u,e}$\label{fi:any-fes-Lue}}[12mm]
  {
    \begin{tikzpicture}[node distance=10mm, >=stealth',x=8mm]
      \node at (1,0) [node, label=below:$e$] (ne1) {} edge [in=105, out=75,loop]  node [above] {$u$} ();
      % 
      \pgfBox
    \end{tikzpicture}
  }
  %
  \hfill
  %
  \subcaptionbox{$C_{e, e'}$\label{fi:any-fes-C}}{
    \begin{tikzpicture}[node distance=10mm, >=stealth',x=8mm]
      % 
      \node at (0,0) [node, label=below:${e \# e'}$] (ne0) {}
      node[above] {};
      % 
      \pgfBox
    \end{tikzpicture}
  }
  %
  \mbox{}
  \hfill\\[4mm]
  %
  \subcaptionbox{rule $e$\label{fi:any-fes-rule}}{
    \begin{tikzpicture}
      \node (l) {
        \begin{tikzpicture}[node distance=10mm, >=stealth',x=8mm]
          %
          \node at (0,2) [node, lab, label=below:$i_e$] (ie) {}; 
          % 
          \node at (1,2) [node, lab, label=below:\scriptsize $e \# e_1'$] (c1) {}; 
          \node at (2,2) [node, lab, label=below:\scriptsize $e \# e_h'$] (cn) {}; 
          \draw[dotted] (c1) -- (cn); 
          % 
          %
          \node at (3.5,2) [node, label=below:$e$] (ne0) {}
          edge [in=195, out=165, loop] node [below] (lu1)  {$e$} ()        
          edge [in=150, out=120, loop] node [above] (lu1)  {$u_1$} ()
          edge [in=60, out=30, loop]  node [above]  (lun)  {$u_n$} ();
          % 
          \draw[dotted] (lu1) -- (lun);           
          %
          %
          \node at (0,0) [node, label=below:{$e_1$}] (n1e0) {}  edge [in=105, out=75,loop]  node [above] {$e_1$} ();
          \node at (0.7,0) [node, label=below:{$e_1$}] (n1e1) {}  edge [in=105, out=75,loop]  node [above] {$u_1^1$} ();
          \node at (1.5,0) [node, label=below:{$e_1$}] (n1e2) {} edge [in=105, out=75,loop]  node [above] {$u_1^{n_1}$} ();
          % 
          \draw[dotted] (n1e1) -- (n1e2); 
          % 
          \node at (2.5,0) [node, label=below:{$e_k$}] (nke0) {}  edge [in=105, out=75,loop]  node [above] {$e_k$} ();
          \node at (3.2,0) [node, label=below:{$e_k$}] (nke1) {}  edge [in=105, out=75,loop]  node [above] {$u_k^1$} ();
          \node at (4.0,0) [node, label=below:{$e_k$}] (nke2) {} edge [in=105, out=75,loop]  node [above] {$u_k^{n_k}$} ();
          % 
          \draw[dotted] (nke1) -- (nke2); 
          % 
          \pgfBox
        \end{tikzpicture}
      };
      %
      \node  [right=of l] (r) {
        \begin{tikzpicture}[node distance=10mm, >=stealth',x=8mm]
          %
          \node at (3,2) [node, label=below:$e$] (ne0) {}
          edge [in=195, out=165, loop] node [below] (lu1)  {$e$} ()        
          edge [in=150, out=120, loop] node [above] (lu1)  {$u_1$} ()
          edge [in=60, out=30, loop]  node [above]  (lun)  {$u_n$} ();
          % 
          \draw[dotted] (lu1) -- (lun);           
          %
          % 
          \node at (1,0) [node, label=below:$e_1$] (ne0) {} 
          edge [in=195, out=165, loop] node [below] (lu1)  {$e_1$} ()
          edge [in=150, out=120, loop] node [above] (lu1)  {$u_1^1$} ()
          edge [in=60, out=30, loop]  node [above]  (lun)  {$u_1^{n_1}$} ();
          % 
          \draw[dotted] (lu1) -- (lun); 
          %
          \node at (3,0) [node, label=below:$e_k$] (ne0) {}
          edge [in=195, out=165, loop] node [below] (lu1)  {$e_k$} ()
          edge [in=150, out=120, loop] node [above] (lu1)  {$u_k^1$} ()
          edge [in=60, out=30, loop]  node [above]  (lun)  {$u_k^{n_k}$} ();
          % 
          \pgfBox
        \end{tikzpicture}
      };
      \path (l) edge[->] node[trans, above] {$e$} (r);
    \end{tikzpicture}
  }\\[4mm]
  \mbox{} \hfill
  \subcaptionbox{$S_e \uplus L_{u_1,e} \uplus L_{u_2,e}$\label{fi:any-fes-U}}
  [35mm]
  {
    \begin{tikzpicture}[node distance=10mm, >=stealth',x=8mm]
      % 
      \node at (0,0) [node, label=below:$e$] (ne0) {} 
      edge [in=105, out=75,loop]  node [above] {$e$} ();;
      % 
      \node at (1,0) [node, label=below:$e$] (ne1) {} 
      edge [in=105, out=75,loop]  node [above] {$u_1$} ();
      % 
      \node at (2,0) [node, label=below:$e$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$u_2$} ();
      % 
      \pgfBox
    \end{tikzpicture}
  }
  %
  \hfill
  %
  \subcaptionbox{$S_e \cup  L_{u_1,e} \cup L_{u_2,e}$\label{fi:any-fes-Uplus}}
  [30mm]
  {
    \begin{tikzpicture}[node distance=10mm, >=stealth',x=8mm]
      % 
      \node at (0,0) [node, label=below:$e$] (ne0) {}
      edge [in=195, out=165, loop] node [below] (lu1)  {$e$} ()    
      edge [in=130, out=100, loop]  node [above] {$u_1$} ()
      edge [in=80, out=50, loop]  node [above] {$u_2$} ();
      % 
      \pgfBox
    \end{tikzpicture}
  }
  \hfill
  \mbox{}
  %
  \caption{Some graphs illustrating the construction of $\mathcal{G}_E$.}
  \label{fi:any-fes}
\end{figure}

\begin{example}
  \label{ex:final}
  Consider the running example {\esabbr}, from
  Example~\ref{ex:event-structure}, with set of events
  $\{ a, b, c \}$, empty conflict relation and the minimal enablings by
  $\{a\} \vdash_0 c$ and $\{b\} \vdash_0 c$. The associated grammar is
  depicted in Fig.~\ref{fi:any-fes-a}.

  As a further example, consider an {\esabbr} $E_1$ with events
  $\{ a, b, c, d, e \}$. The conflict relation $\#$ is given by
  $e \# d$ and minimal enablings $\emptyset \vdash_0 a$,
  $\emptyset \vdash_0 b$, $\emptyset \vdash_0 c$, $\emptyset \vdash_0 e$,
  $\{a, b\} \vdash_0 d$ and $\{c\} \vdash_0 d$. The grammar is in
  Fig.~\ref{fi:any-fes-b}.
\end{example}

\begin{figure}
  %
  \subcaptionbox*{$T$}{
    \begin{tikzpicture}[node distance=10mm, >=stealth',x=6.2mm]
      \node at (0,1) [node, label=below:${a}$] (na) {} edge [in=105, out=75,loop]  node [above] {$a$} ();
      % 
      \node at (1,1) [node, label=below:${b}$] (nb) {} edge [in=105, out=75,loop]  node [above] {$b$} ();
      %
      \node at (2.2,1) [node, label=below:${c}$] (nc) {} edge [in=160, out=130, loop]  node [above] {$c$} ()
      edge [in=50, out=20, loop]  node [above] {$(a,b)$} ();
      % 
      \node at (0,0) [node, label=below:$i_{a}$] (ia) {};
      \node at (1,0) [node, label=below:$i_{b}$] (ib) {};
      \node at (2,0) [node, label=below:$i_{c}$] (ic) {};
      \pgfBox
    \end{tikzpicture}
  }
  %
  \hspace{10mm}
  %
  \subcaptionbox*{$G_s$}{
    \begin{tikzpicture}[node distance=10mm, >=stealth',x=6.2mm]
      % 
      \node at (0,1) [node, label=below:$a$] (ne0) {} edge [in=105, out=75,loop]  node [lab,above] {$a$} ();
      % 
      \node at (1,1) [node, label=below:$b$] (ne1) {} edge [in=105, out=75,loop]  node [above] {$b$} ();
      % 
      \node at (2,1) [node, label=below:$c$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$c$} ();
      %
      \node at (3,1) [node, label=below:$c$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$(a,b)$} ();
      % 
      \node at (0,0) [node, label=below:$i_{a}$] (ia) {};
      \node at (1,0) [node, label=below:$i_{b}$] (ib) {};
      \node at (2,0) [node, label=below:$i_{c}$] (ic) {};
      \pgfBox
      \pgfBox
    \end{tikzpicture}  }
  %
  \\[2mm]
  %
  \subcaptionbox*{}{    
    \begin{tikzpicture}[node distance=6.2mm]
      \node (l) {
      \begin{tikzpicture}[node distance=10mm, >=stealth',x=6.2mm]
        %
        \node at (0,0) [node, label=below:$i_{a}$] (ia) {};
        % 
        \node at (1,0) [node, label=below:$a$] (ne0) {} edge [in=105, out=75,loop]  node [above] {$a$} ();
        % 
        \node at (2,0) [node, label=below:$c$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$c$} ();
        % 
        \node at (3,0) [node, label=below:$c$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$(a,b)$} ();
        %
        \pgfBox
      \end{tikzpicture} 
    };
    \node  [right=of l] (r) {
      \begin{tikzpicture}[node distance=10mm, >=stealth',x=6.2mm]
        \node at (0,0) [node, label=below:$a$] (ne0) {} edge [in=105, out=75,loop]  node [above] {$a$} ();
        % 
        \node at (1.5,0) [node, label=below:${c}$] (nc) {} edge [in=160, out=130, loop]  node [above] {$c$} ()
        edge [in=50, out=20, loop]  node [above] {$(a,b)$} ();
        % 
        \pgfBox
      \end{tikzpicture}
    };
    \path (l) edge[->] node[trans, above] {$a$} (r);
    \end{tikzpicture}
  }
  %
  \\
  %
  \subcaptionbox*{}{    
    \begin{tikzpicture}[node distance=6.2mm]
      \node (l) {
      \begin{tikzpicture}[node distance=10mm, >=stealth',x=6.2mm]
        %
        \node at (0,0) [node, label=below:$i_{b}$] (ib) {};
        % 
        \node at (1,0) [node, label=below:$b$] (ne0) {} edge [in=105, out=75,loop]  node [above] {$b$} ();
        % 
        \node at (2,0) [node, label=below:$c$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$c$} ();
        % 
        \node at (3,0) [node, label=below:$c$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$(a,b)$} ();
        %
        \pgfBox
      \end{tikzpicture} 
    };
    \node  [right=of l] (r) {
      \begin{tikzpicture}[node distance=10mm, >=stealth',x=6.2mm]
        \node at (0,0) [node, label=below:$b$] (ne0) {} edge [in=105, out=75,loop]  node [above] {$b$} ();
        % 
        \node at (1.5,0) [node, label=below:${c}$] (nc) {} edge [in=160, out=130, loop]  node [above] {$c$} ()
        edge [in=50, out=20, loop]  node [above] {$(a,b)$} ();
        % 
        \pgfBox
      \end{tikzpicture}
    };
    \path (l) edge[->] node[trans, above] {$b$} (r);
    \end{tikzpicture}
  }
  %
  \hfill
  %
  \subcaptionbox*{}{    
    \begin{tikzpicture}[node distance=6.2mm]
      \node (l) {
      \begin{tikzpicture}[node distance=10mm, >=stealth',x=6.2mm]
        \node at (0,0) [node, label=below:$i_{c}$] (ic) {};
        %
        \node at (1,0) [node, label=below:${c}$] (nc) {} 
        edge [in=160, out=130, loop]  node [above] {$c$} ()
        edge [in=50, out=20, loop]  node [above] {$(a,b)$} ();
        %
        \pgfBox
      \end{tikzpicture} 
    };
    \node  [right=of l] (r) {
      \begin{tikzpicture}[node distance=10mm, >=stealth',x=6.2mm]
        \node at (0,0) [node, label=below:${c}$] (nc) {} 
        edge [in=160, out=130, loop]  node [above] {$c$} ()
        edge [in=50, out=20, loop]  node [above] {$(a,b)$} ();
        %
        \pgfBox
      \end{tikzpicture}
    };
   \path (l) edge[->] node[trans, above] {$c$} (r);
    \end{tikzpicture}
  }
  \caption{The grammar associated to our running example.}
  \label{fi:any-fes-a}
\end{figure}

\begin{figure}
  \subcaptionbox*{$T$}{
    \begin{tikzpicture}[node distance=10mm, >=stealth']
      \node at (0,0) [node, label=below:${a}$] (na) {} edge [in=105, out=75,loop]  node [above] {$a$} ();
      % 
      \node at (1,0) [node, label=below:${b}$] (nb) {} edge [in=105, out=75,loop]  node [above] {$b$} ();
      %
      \node at (2,0) [node, label=below:${c}$] (nc) {} edge [in=105, out=75,loop]  node [above] {$c$} ();
      %
      \node at (3,0) [node, label=below:${d}$] (nc) {} edge [in=180, out=150, loop]  node [above] {$d$} ()
      edge [in=70, out=110, loop]  node [above] {$(a,c)$} ()
      edge [in=30, out=0, loop]  node [above right=0mm and -3.5mm] {$(b,c)$} ();
      % 
      \node at (4.2,0) [node, label=below:${e}$] (ne) {} edge [in=105, out=75,loop]  node [above] {$e$} ();
      %
      \node at (5,0) [node, label=below:$d\#e$] (de) {};
      \pgfBox
    \end{tikzpicture}
  }
  %
  \\[2mm]
  %
  \subcaptionbox*{$G_s$}{
    \begin{tikzpicture}[node distance=10mm, >=stealth',x=6.2mm]
      \node at (0,1) [node, label=below:${a}$] (na) {} edge [in=105, out=75,loop]  node [above] {$a$} ();
      % 
      \node at (1,1) [node, label=below:${b}$] (nb) {} edge [in=105, out=75,loop]  node [above] {$b$} ();
      %
      \node at (2,1) [node, label=below:${c}$] (nc) {} edge [in=105, out=75,loop]  node [above] {$c$} ();
      %
      \node at (3,1) [node, label=below:${d}$] (nd) {} edge [in=105, out=75,loop]  node [above] {$d$} ();
      %
      \node at (3.9,1) [node, label=below:${d}$] (nd1) {} edge [in=105, out=75,loop]  node [above] {$(a,c)$} ();
      % 
      \node at (5.1,1) [node, label=below:${d}$] (nd2) {} edge [in=105, out=75,loop]  node [above] {$(b,c)$} ();
      % 
      \node at (6,1) [node, label=below:${e}$] (ne) {} edge [in=105, out=75,loop]  node [above] {$e$} ();
      %
      \node at (7,1) [node, label=below:$d\#e$] (de) {};
      %
      % 
      \node at (0,0) [node, label=below:$i_{a}$] (ia) {};
      \node at (1,0) [node, label=below:$i_{b}$] (ib) {};
      \node at (2,0) [node, label=below:$i_{c}$] (ic) {};
      \node at (3,0) [node, label=below:$i_{d}$] (ic) {};
      \node at (4,0) [node, label=below:$i_{e}$] (ic) {};
      %
      \pgfBox
    \end{tikzpicture}
  }
  %
  \\[2mm]
  %
  \subcaptionbox*{}{    
    \begin{tikzpicture}[node distance=6.2mm]
      \node (l) {
      \begin{tikzpicture}[node distance=10mm, >=stealth',x=6.2mm]
        %
        \node at (0,0) [node, label=below:$i_{a}$] (ia) {};
        % 
        \node at (1,0) [node, label=below:$a$] (ne0) {} edge [in=105, out=75,loop]  node [above] {$a$} ();
        % 
        \node at (2,0) [node, label=below:$d$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$d$} ();
        % 
        \node at (3,0) [node, label=below:$d$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$(a,c)$} ();
        %
        \pgfBox
      \end{tikzpicture} 
    };
    \node  [right=of l] (r) {
      \begin{tikzpicture}[node distance=10mm, >=stealth',x=6.2mm]
        \node at (0,0) [node, label=below:$a$] (ne0) {} 
        edge [in=105, out=75,loop]  node [above] {$a$} ();
        % 
        \node at (1.5,0) [node, label=below:${d}$] (nc) {} 
        edge [in=160, out=130, loop]  node [above] {$d$} ()
        edge [in=50, out=20, loop]  node [above] {$(a,c)$} ();
        % 
        \pgfBox
      \end{tikzpicture}
    };
   \path (l) edge[->] node[trans, above] {$a$} (r);
    \end{tikzpicture}
  }
  %
  \hfill
  %
  \subcaptionbox*{}{    
    \begin{tikzpicture}[node distance=6.2mm]
      \node (l) {
      \begin{tikzpicture}[node distance=10mm, >=stealth',x=6.2mm]
        % 
        %
        \node at (0,0) [node, label=below:$i_{b}$] (ib) {};
        % 
        \node at (1,0) [node, label=below:$b$] (ne0) {} edge [in=105, out=75,loop]  node [above] {$b$} ();
        % 
        \node at (2,0) [node, label=below:$d$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$d$} ();
        % 
        \node at (3,0) [node, label=below:$d$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$(b,c)$} ();
        %
        \pgfBox
      \end{tikzpicture} 
    };
    \node  [right=of l] (r) {
      \begin{tikzpicture}[node distance=10mm, >=stealth',x=6.2mm]
        % 
        \node at (0,0) [node, label=below:$b$] (ne0) {} 
        edge [in=105, out=75,loop]  node [above] {$b$} ();
        %
        \node at (1.5,0) [node, label=below:${d}$] (nc) {}
        edge [in=160, out=130, loop]  node [above] {$d$} ()
        edge [in=50, out=20, loop]  node [above] {$(b,c)$} ();
        % 
        \pgfBox
      \end{tikzpicture}
    };
   \path (l) edge[->] node[trans, above] {$b$} (r);
    \end{tikzpicture}
  }
  %
  \hfill
  %
  \subcaptionbox*{}{    
  %
    \begin{tikzpicture}[node distance=6.2mm]
      \node (l) {
      \begin{tikzpicture}[node distance=10mm, >=stealth', x=6mm]
        % 
        %
        \node at (0,0) [node, label=below:$i_{c}$] (ic) {};
        % 
        \node at (1,0) [node, label=below:$c$] (ne0) {} edge [in=105, out=75,loop]  node [above] {$c$} ();
        % 
        \node at (2,0) [node, label=below:$d$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$d$} ();
        % 
        \node at (3,0) [node, label=below:$d$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$(a,c)$} ();       
        % 
        \node at (4.5,0) [node, label=below:$d$] (ne2) {} edge [in=105, out=75,loop]  node [above] {$(b,c)$} ();
        %
        \pgfBox
      \end{tikzpicture} 
    };
    \node  [right=of l] (r) {
      \begin{tikzpicture}[node distance=10mm, >=stealth']
        % 
        \node at (0,0) [node, label=below:$c$] (ne0) {} edge [in=105, out=75,loop]  node [above] {$c$} ();
        %
        \node at (1,0) [node, label=below:${d}$] (nc) {} edge [in=180, out=150, loop]  node [above] {$d$} ()
        edge [in=70, out=110, loop]  node [above] {$(a,c)$} ()
        edge [in=30, out=0, loop]  node [above right=0mm and -3.5mm] {$(b,c)$} ();
        % 
        \pgfBox
      \end{tikzpicture}
    };
   \path (l) edge[->] node[trans, above] {$c$} (r);
    \end{tikzpicture}
  }
  \hfill
  %
  \subcaptionbox*{}{    
    \begin{tikzpicture}[node distance=6.2mm]
      \node (l) {
      \begin{tikzpicture}[node distance=10mm, >=stealth']
        \node at (0,0) [node, label=below:$i_{d}$] (id) {};
        % 
        \node at (1,0) [node, label=below:${d}$] (nc) {} edge [in=180, out=150, loop]  node [above] {$d$} ()
        edge [in=70, out=110, loop]  node [above] {$(a,c)$} ()
        edge [in=30, out=0, loop]  node [above right=0mm and -3.5mm] {$(b,c)$} ();
        % 
        \node at (2.1,0) [node, label=below:$d\#e$] (de) {};
        % 
        \pgfBox
      \end{tikzpicture}       
      }; 
      \node  [right=of l] (r) {
      \begin{tikzpicture}[node distance=10mm, >=stealth']
        \node at (0,0) [node, label=below:${d}$] (nc) {} edge [in=180, out=150, loop]  node [above] {$d$} ()
        edge [in=70, out=110, loop]  node [above] {$(a,c)$} ()
        edge [in=30, out=0, loop]  node [above right=0mm and -3.5mm] {$(b,c)$} ();
        % 
        \pgfBox
      \end{tikzpicture}
    };
   \path (l) edge[->] node[trans, above] {$d$} (r);
    \end{tikzpicture}
  }
  %
  \subcaptionbox*{}{    
    \begin{tikzpicture}[node distance=6.2mm]
      \node (l) {
      \begin{tikzpicture}[node distance=10mm, >=stealth', x=6mm]
        \node at (0,0) [node, label=below:$i_{e}$] (ie) {};
        % 
        \node at (1,0) [node, label=below:${e}$] (e) {} 
        edge [in=75, out=105, loop] node [above] {$e$} ();
        % 
        \node at (2.1,0) [node, label=below:$d\#e$] (de) {};
        % 
        \pgfBox
      \end{tikzpicture}       
      }; 
      \node  [right=of l] (r) {
      \begin{tikzpicture}[node distance=10mm, >=stealth']
        \node at (0,0) [node, label=below:${e}$] (e) {} 
        edge [in=75, out=105, loop] node [above] {$e$} ();
        % 
        \pgfBox
      \end{tikzpicture}
    };
   \path (l) edge[->] node[trans, above] {$e$} (r);
    \end{tikzpicture}
  }
  \caption{The grammar for the {\esabbr} in example~\ref{ex:final}.}
  \label{fi:any-fes-b}
\end{figure}

\subsection{A prime {\esabbr} semantics for grammars with fusions}
\label{ss:prime-gg}

A possibility for recovering a notion of causality based on prime
{\esabbr} also for graph grammars with fusions is to
introduce suitable restrictions on the concurrent applicability of
rules.
%
Indeed, the lack of stability arises essentially from
considering as concurrent those fusions which act on common items.
Preventing fusions to act on already merged items, one may lose some
concurrency, yet gaining a definite notion of causality.
%
Technically, a prime {\esabbr} can be obtained for left-linear
rewriting systems by restricting the applicability condition: the
match must be such that the pair $\langle l; m^L, r \rangle$ of
Fig.~\ref{fi:deriv} is jointly mono. This essentially means that items
which have been already fused, should not be fused again.

Formally, this means changing the applicability condition, restricting
to fusion safe derivations.

\begin{figure}[t]
\[
\xymatrix@R=6mm{ 
  {L} \ar[d]_{m^L} & {K} \ar[l]_{l} \ar[r]^{r} 
  \ar[d]^{m^K} & {R} \ar[d]^{m^R}\\
  {G} & {D} \ar[l]^{l^*} \ar[r]_{r^*} & {H} }
\]
\caption{A direct derivation.}
\label{fi:deriv-jointly}
\end{figure}

\begin{definition}[fusion safe (direct) derivation]
  A \emph{fusion safe} direct derivation is a direct derivation as in
  Fig.~\ref{fi:deriv-jointly} where $\langle l; m^L, r \rangle$ is
  jointly mono. A derivation is fusion safe if it consists of a
  sequence of fusion safe direct derivations.
\end{definition}

Consider our running example in Fig.~\ref{fi:running}.
Clearly, the derivations labelled $p_a$ and $p_b$ starting from 
$G_s$ are now in conflict, since e.g. the application of $p_a$ 
forbids the application of $p_b$ to $G_a$, since the 
derivation would not be anymore jointly mono.
%
We thus end up in the situation presented by the configurations
in Fig.~\ref{fi:non-fusion}, 
hence the applications of $p_c$ to $G_a$ and $G_b$ respectively 
must be considered as different events.

The notion of sequential independence remains unchanged. Note that the interchange operator (see Proposition~\ref{pr:interchangeEG}) 
applied to sequential independent derivations that are fusion safe produces a new pair of fusion safe 
derivations. \todo{to be proved}
%
Then we can consider concatenable fusion safe traces, that form a subcategory of the category of traces.

\begin{definition}[fusion safe traces]
  \label{de:abs-shift-cat-2}
  Let $\mathcal{G}$ be a graph grammar.  The \emph{category of
    concatenable fusion safe traces} of $\mathcal{G}$, denoted by
  \trs{\mathcal{G}}, has abstract graphs as objects and concatenable
  fusion safe traces as arrows.
\end{definition}

The construction of Theorem~\ref{th:fusion-domain-for-gg} recasted on
fusion safe traces now produces a prime domain (hence a
prime {\esabbr}).

\begin{theorem}[prime domain structure for graph grammars]
  Let $\mathcal{G}$ be a graph grammar. Then
  $\ideal{\slice{[G_s]}{\trs{\mathcal{G}}}}$ is a prime domain.
\end{theorem}

\begin{proof}
  The proof is the same as for
  Theorem~\ref{th:fusion-domain-for-gg}. We already know that the
  domain is weak prime, hence, by Proposition~\ref{pr:fusion-domains},
  all irreducibles are weak primes.  Additionally, interchangeability,
  as characterised in the proof of the mentioned theorem, is the
  identity.

  \todo[inline]{Sketchy argument, to be be made more precise.}

  In fact, given two irreducibles $\ltrace{\epsilon_i}$ with
  $\epsilon_i = \psi_i; \delta_i$ for $i \in \{1,2\}$ such that
  $\ltrace{\epsilon_1} \leftrightarrow \ltrace{\epsilon_2}$, by
  interchangeability
  $\ltrace{\psi_1} \sqcup \ltrace{\epsilon_2} =
  \ltrace{\epsilon_1} \sqcup \ltrace{\psi_2}$. Let such join be
  $\ltrace{\psi_1; \delta_1; \psi_1'} = \ltrace{\psi_2; \delta_2;
    \psi_2'}$ for suitable $\psi_1', \psi_2'$. This means that
  $\psi_1; \delta_1; \psi_1' \equiv^c_\sigma \psi_2; \delta_2;
  \psi_2'$ for a suitable permutation $\sigma$, with
  $\sigma(|\epsilon_1|) = \sigma(|\epsilon_2|)$. There are two
  possibilities. If $|\psi_1| = |\psi_2|$ and $\sigma$ restricts to a
  permutation of $\interval{|\psi_1|}$, then $\psi_1 \equiv^c \psi_2$
  and we conclude. Otherwise a step in $\psi_2$ is not mapped
  to $\psi_1$ or viceversa. Assume, without loss of generality, that
  there is $i \in \interval{|\psi_1|}$ such that
  $\sigma(i) > |\psi_2|$. This means that the $i$-th step in $\psi_1$
  is performed in $\psi_2'$. Since such step is performed after
  $\delta_2$, it cannot generate items consumed by $\delta_1$. Hence
  it must merge items that are merged by a different step in
  $\psi_2$. But this contradicts its fusion safety.

  \smallskip

  Hence all weak primes are primes and we
  conclude.
\end{proof}

% Parallel independence, instead should be changed as follows.

% \begin{figure}[t]
% \[
% \def\objectstyle{\scriptstyle}\def\labelstyle{\scriptstyle}
% \xymatrix@C=1mm@R=8mm{
%   {R_1} \ar[d]_{m_{R_1}}
%         & & {K_1} \ar[ll]_{r_1} \ar[rr]^{l_1} \ar[d]|{m_{K_1}}
%         & & {L_1} \ar[drrr]|{m_{L_1}}  \ar@(r,ul)@{.>}[drrrrrrrr]|{i_1}
%         & & & & & &
%     %
%   {L_2}\ar[dlll]|{m_{L_2}} \ar@(l,ur)@{.>}[dllllllll]|{i_2}
%         & & {K_2} \ar[ll]_{l_2} \ar[rr]^{r_2} \ar[d]|{m_{K_2}}
%         & & {R_2} \ar[d]^{m_{R_2}} \\
%     %
%     %
%     {H_1}
%      & & {D_1} \ar[ll]^{r^*_1} \ar[rrrrr]_{l^*_1}
%      & & & &  & {G} & &
%      & & & {D_2} \ar[lllll]^{l^*_2} \ar[rr]_{r^*_2}
%      & & {H_2}  }
% \]
% \caption{Parallel independence for $p_1/m_1\colon G \Rrel{ } H_1$ and $p_2/m_2\colon G\Rrel{ } H_2$.} 
% \label{fi:par}
% \end{figure}

% \begin{definition}[parallel independence]
%   \label{de:parInd}
%   Let $p_1$, $p_2$ be rules and $p_1/m_1\colon G \Rrel{ }H_1$,
%   $p_2/m_2\colon G \Rrel{ } H_2$ direct derivations as in
%   Fig.~\ref{fi:par}.  They are called \emph{parallel independent} if
%   there exist arrows $i_1\colon L_1 \rightarrow D_2$ and $i_2\colon
%   L_2 \rightarrow D_1$ such that $l_2^* \circ i_1 = m_{L_1}$ and
%   $l_1^* \circ i_2 = m_{L_2}$.
%   %
%   % These derivations are called \emph{parallel independent} if there
%   % exists an \emph{independence pair} among them, i.e., two arrows
%   % $i_1\colon L_1 \rightarrow D_2$ and $i_2\colon L_2 \rightarrow D_1$ such
%   % that $l_2^* \circ i_1 = m_{L_2}$ and $l_1^* \circ i_2 = m_{L_1}$.

%   Fusion safe parallel independence is defined by asking additionally
%   that the pairs $\langle l_1;i_1,r_2^*, r_1 \rangle$ and dually
%   $\langle l_2;i_2,r_1^*, r_2 \rangle$ are jointly mono (one
%   suffices?).
% \end{definition}

% Intuitively, fusion safe parallel independent rules do not merge the
% same items, so once sequentialised they do not violate the fact that
% items should not be merged twice.

% Probably the notion of parallel independence is not really relevant here as one can simply prove the following.

\section{Conclusions and Related Work}
\label{se:conc}

In the paper we provided a characterisation of a class of domains,
referred to as weak prime algebraic domains, which is appropriate for
describing the concurrent semantics of those formalisms where a
computational step can merge parts of the state. We show a
categorical equivalence between weak prime algebraic domains and a
suitably defined class of connected event structures. We also prove
that the category of general event structures coreflects into
the category of weak prime algebraic domains.

The appropriateness of
the class of weak prime domains is witnessed by the results 
that show that weak prime algebraic domains
are precisely those arising from left-linear graph rewriting systems,
i.e., those systems where rules besides generating and deleting can
also merge graph items.
%
Furthermore, we show how to recover 
a prime event structures semantics also for rule-based
formalisms with fusions by introducing suitable restrictions on the
concurrent applicability of rules.

We have shown that the  
characterisations of prime domains and event structures in terms of intervals 
and asynchronous graphs naturally extend to weak prime domains. 
The characterisation of weak prime domains in terms of the interchangeability 
equivalence on irreducibles naturally suggest a presentation in terms of prime 
event structures endowed with an equivalence relation, allowing us to establish 
a link with the work in~\cite{win2017,VismeW19}.
%
%Indeed, the lack of stability seems to arise essentially from
%considering as concurrent those fusions that act on common items.
%Preventing fusions to act on already merged items, one  lose some
%concurrency, yet gaining a definite notion of causality.
%
%Technically, a prime event structure can be obtained for left-linear
%grammars by restricting the applicability condition: the match must be
%such that the pair $\langle l; m^L, r \rangle$ of Fig.~\ref{fi:deriv} is 
%jointly mono. This essentially means that those items that have been
%already fused, should not be fused again.
%%
%This is indeed the intuition behind the proposal advanced in~\cite{BaldanGM06}.

Technically, the starting point for our proposal is the relaxation of the stability
condition for event structures. As already noted by Winskel
in~\cite{Win:ESSCCS} ``[t]he stability axiom would go if one wished to
model processes which had an event which could be caused in several
compatible ways [\ldots]; then I expect complete irreducibles would
play a similar role to complete primes here''.  Indeed, the
correspondence between irreducibles and weak primes, which
exploits the
notion of interchangeability, is the ingenious step that allows us to
obtain a smooth extension of the classical duality between
prime event structures and prime algebraic domains.

The coreflection between the category of general unstable event structures 
(with binary conflict)
and the one of weak prime algebraic domains says that the latter are
exactly the partial orders of configurations of the former. 
%general unstable event structures 
Such class of domains has been
studied originally in~\cite{Winskel:phd} where, generalising the work
on concrete domains and sequentiality~\cite{KP:CD}, a characterisation
is given in terms of a set of axioms expressing properties of prime
intervals.
%
%We consider our simple characterisation of this class of domains,
%where weak primes intuitively account for events in a computation,
%as a valuable contribution of the paper.
%
In our paper we also provide an in depth comparison with these  results,
based on the observation that, roughly speaking, weak primes correspond to executions 
of events with their minimal enablings, while intervals can be seen as executions of 
events in a generic configuration.
%
A comparison is also drawn with the more recent notions of asynchronous graph~\cite{Mel:hab}, 
an alternative representation of prime algebraic domains based on the notion of path equivalence,
which we generalise in order to account for weak prime ones.
%

% \subsection{An {\esabbr} semantics for the $\pi$-calculus}

The need of resorting to unstable {\esabbr} for modelling the
concurrent computations of name passing process calculi has been
observed by several authors. In particular, in~\cite{CVY:ESSPE} an
{\esabbr} semantics for the $\pi$-calculus is defined by relying on
 {\esabbr} \emph{with names}, %which labelled unstable
%{\esabbr} ({\esnmabbr} for short), 
namely labelled {\esabbr} tailored for modelling
parallel extrusions. An event can have various minimal enablings but
with the constraint that distinct minimal enablings can differ only for one
event (intuitively, the extruder).
%
{\esabbr} with names are not connected {\esabbr} since they can have 
non-connected minimal enablings (roughly, because identical events in 
disconnected minimal enablings can be identified via the labelling).
% 
Nevertheless, a connected {\esabbr} semantics could be obtained by
transforming {\esabbr} with names through the coreflection in the
paper: More details are reported 
in Appendix~\ref{app:pi}.

% Concerning the appropriateness of the class of weak prime domains,
% length and readability concerns suggested us to move to a different paper
% the results preliminarily reported in~\cite{BaldanCG17} and further refined 
% in~\cite{BCG:DESF-tr} showing that weak prime algebraic domains
% are precisely those arising from graph rewriting systems 
% where rules 
% %besides generating and deleting 
% can also merge graph items, a paradigmatic example of formalism with fusion.
% %
% Indeed, we prove there that, in the same way as prime algebraic domains/prime
% event structures are exactly what is needed for Petri nets/linear graph 
% rewriting systems, weak prime
% algebraic domains/connected event structures are exactly what is needed
% for left-linear graph rewriting systems: each rewriting system maps to
% a connected event structure and conversely each connected event structure
% arises as the semantics of some rewriting system. This supports the
% adequateness of weak prime algebraic domains and connected event
% structures as semantics structures for formalisms with fusions, hinted at 
% in the present paper with a few examples.

We believe that our results cover a long road in establishing weak prime domains and 
connected event structures as a foundational concept in the event-based semantics for 
concurrent computational systems.
%
Our next step will be to look at possible more general formalisms. 
In particular, the paper~\cite{GP:CSESPN} studies a characterisation 
of the partial order of configurations for a variety of classes of event
structures in terms of axiomatisability of the associated
propositional theories. Even if the focus in the present paper is 
on event structures that generalise Winskel's ones, we believe that
our work can provide interesting suggestions for
further development.

%%
%Furthermore, we show how to recover 
%%a notion of causality based on 
%a prime event structures semantics also for rule-based
%formalisms with fusions by introducing suitable restrictions on the
%concurrent applicability of rules.

\smallskip

\paragraph*{Acknowledgements}
We are grateful to the anonymous referees of the conference version of
the paper for their insightful comments and suggestions. We are also indebted to Paul-Andr\`e Melli\'es for insightful discussions on the relation between event structures and asynchronous graphs.

\bibliography{Unstable}

\bibliographystyle{IEEEtran}

\appendix

\subsection{Event Structures with Non-Binary Conflict}
\label{app:consistency}

In the literature also {\esabbr} with non-binary conflict have been considered, 
where the binary conflict relation is replaced by a consistency predicate~\cite{Dro:ESD}. 
It is noteworthy that the duality results of Section~\ref{se:fes} easily adapt to this case.

\begin{definition}[{\esabbr} with non-binary conflict]
  An {\esabbr} \emph{with non-binary conflict} ({\esnabbr} for
  short) is a tuple $\langle E, \vdash, Con \rangle$ such
  that
  \begin{itemize}
  \item $E$ is a set of events
  \item $Con \subseteq \mathbf{2}^E_{fin}$ is the consistency
    predicate, satisfying $X \in Con$ and $Y \subseteq X$ implies $Y
    \in Con$
  \item $\vdash\ \subseteq Con \times E$ is the \emph{enabling}
    relation, satisfying $X \vdash e$ and $X \subseteq Y \in Con$
    implies $Y \vdash e$.
  \end{itemize}
  The {\esnabbr} ${E}$ is \emph{stable} if $X\vdash e$,
  $Y \vdash e$, and $X \cup Y \cup \{e\} \in Con$ imply
  $X \cap Y \vdash e$.
\end{definition}

A configuration $C \subseteq E$ is just a set such that
it is secured and all its finite subsets are consistent.
%
The notion of live {\esnabbr} is easily adapted to take into account
non-binary conflicts and also in this case we will implicitly assume
all {\esnabbr} to be live.

\begin{definition}[live {\esnabbr}]
  An {\esnabbr} ${E}$ is \emph{live} if for all
  $X \in Con$ there is $C \in \conf{E}$ such that
  $X \subseteq C$ and moreover
  for all $e \in E$ we have $\{ e \} \in  Con$.
  %\todo{Double check. Please.}
\end{definition}

The notion of the category of {\esnabbr} is adapted accordingly.

\begin{definition}[category of event structures]
  \label{a-de:es-morphism}
  A morphism of {\esnabbr} $f : {E}_1 \to {E}_2$ is a partial
  function $f : E_1 \to E_2$ such that
  for all $X_1 \subseteq E_1$ and $e_1, e_1' \in E_1$ with $f(e_1)$, $f(e_1')$ defined
  \begin{itemize}
  \item if $X_1 \in Con_1$ then $f(X_1) \in Con_2$;
  \item if $\{ e_1, e_1' \} \in Con_1$ and $f(e_1) = f(e_1')$ then $e_1 = e_1'$;
  \item if $X_1 \vdash_1 e_1$ then 
  $f(X_1) \vdash_2 f(e_1)$.
  \end{itemize}
  We denote by $\esn$ the category of {\esnabbr} and {\esnabbr} morphisms,
  and by $\cesn$ its full subcategory having connected {\esnabbr} as objects (the definition of conectedness remains unchanged).
\end{definition}

In the definition of domains (Definition~\ref{c-de:domain}), the
existence of joins is now required only for consistent subsets,
instead of being required for pairwise consistent.

\begin{definition}[b-domains]
  \label{de:domain}
  A \emph{bounded complete domain (b-domain)} is an algebraic
  % $\omega$-algebraic
  finitary partial order where all consistent subsets $X \subseteq D$
  admit a least upper bound $\bigsqcup X$.
  %
  B-domain morphisms are as in Definition~\ref{de:domain-category}. 
  %
  We denote by $\Domb$ the corresponding category.
\end{definition}

% Note that any domain is a b-domain.
% %
% However, Lemma~\ref{le:transitive} that shows a form of transitivity for
% interchangeability ceases to hold in the current formulation: an
% counterexample is found in Fig.~\ref{fi:not-eq}.
% Still, it suffices 
% to strengthen the hypotheses by asking that $i, i', i''$ are consistent 
% and the proof goes through again.
%
The definition of weak prime algebraicity remains formally the same, 
but the underlying partial order is required to be a b-domain.

% \begin{figure}
%   \begin{center}
%     \begin{tikzcd}%[column sep=large]
%        {} & {} & {\bullet} & {} & {}\\
%        % 
%        {} & {\bullet} \ar[ur] & {} & {\bullet} \ar[ul] & {}\\
%        % 
%        {} & {} & {p_1 \sqcup p_3} \ar[ur] \ar[ul] & {} & {}\\
%        % 
%        {} & {i_1 \sqcup i_2} & {} & {i_2 \sqcup i_3} & {}\\
%        % 
%        {i_1} \ar[uuur] \ar[ur] & {p_1 \sqcup p_2} \ar[u] & {i_2} \ar[ul] \ar[ur] & {p_2 \sqcup p_3} \ar[u] & {i_3} \ar[uuul] \ar[ul]\\
%        % 
%        {p_1} \ar[u] \ar[uuurr, bend right=47] \ar[ur] & {} & {p_2} \ar[u] \ar[ul] \ar[ur] & {} & {p_3} \ar[u] \ar[uuull, bend left=47] \ar[ul]\\
%        % 
%        {} & {} & {\bot} \ar[urr] \ar[u] \ar[ull] & {} & {}   
%      \end{tikzcd}
%    \end{center}
%    \caption{A counterexample to Lemma~\ref{le:transitive}: a weak
%      prime algebraic b-domain where $i_1 \leftrightarrow i_2$,
%      $i_2 \leftrightarrow i_3$, and $i_1, i_3$ are consistent but
%      $i_1 \not\leftrightarrow i_3$.}
% \label{fi:not-eq}
% \end{figure}

\begin{definition}[weak prime algebraic b-domain]
  \label{a-de:fusion-domain-new}
  A \emph{weak prime algebraic b-domain} (or simply \emph{weak prime
    b-domain}) is a {\wi} b-domain $D$ such that for all $d \in D$ it
  holds $d = \bigsqcup (\principal{d} \cap \wpr{D})$. We denote by
  $\WDomb$ the corresponding category.
\end{definition}

The proof of the fact that, given an {\esnabbr} ${E}$, the partial order of
configurations $\dom{{E}} = \langle \conf{{E}}, \subseteq \rangle$ is
a weak prime b-domain, is unchanged. The same holds for the fact that
if $f : E_1 \to E_2$ is an {\esnabbr} morphism then
$\dom{f} : \dom{{E}_1} \to \dom{{E}_2}$ is a weak prime b-domain
morphism.

Vice versa the {\esnabbr} associated with a
weak prime b-domain is defined as follows.

\begin{definition}[{\esnabbr} for a weak prime b-domain]
  \label{a-de:es-for-dom}
  Let $D$ be a weak prime b-domain. The {\esnabbr} 
  $\ev{D} = \langle E, Con, \vdash \rangle$ is defined as
  follows
  \begin{itemize}

  \item $E = \eqclassir{\ir{D}}$;

  \item
    $Con = \{ X \mid \exists d \in \compact{D}.\ X \subseteq
    \eqclassir{\ir{d}} \}$;

  \item $X \vdash e$ if there exists $i \in e$ such that
    $\eqclassir{\ir{i} \setminus \{ i \}} \subseteq X$.

  \end{itemize}

%  Given a morphism $f : D_1 \to D_2$, its image
%  $\ev{f} : \ev{D_1} \to \ev{D_2}$ is defined as follows: for
%  $\eqclassir{i_1} \in E$, if $f(\pred{i_1}) = f(i_1)$, then
%  $\ev{f}(\eqclassir{i_1}) = \bot$, else 
%  $\ev{f}(\eqclassir{i_1})= \eqclassir{i_2}$, where
%  $i_2 \in \diff{f(i_1)}{f(\pred{i_1})}$.
 %\todo{PB: qui e altrove, $\bot$ come indefinito forse fa casino}
% aggiustato come nella def. 17
Given a morphism $f : D_1 \to D_2$, its image
$\ev{f} : \ev{D_1} \to \ev{D_2}$ is defined for
$\eqclassir{i_1} \in E$ as
$\ev{f}(\eqclassir{i_1}) = \eqclassir{i_2}$, where
 $i_2 \in \diff{f(i_1)}{f(\pred{i_1})}$,
and $\ev{f}(\eqclassir{i_1})$ is undefined if
$f(\pred{i_1}) = f(i_1)$.
\end{definition}

% In the proof of Proposition~\ref{pr:es-to-dom} we need to prove
% that, $\leftrightarrow$ is an equivalence on consistent
% irreducibles. This immediately follows from
% Lemma~\ref{le:es-to-fusion-domain}(\ref{le:es-to-fusion-domain:4}).

We then get a result corresponding to Theorem~\ref{th:duality} for {\esabbr}
with non-binary conflict and  weak prime b-domains.

\begin{theorem}[corecflection of $\esn$ and $\WDomb$]
 \label{th:es-dom-equivalence-non-binary}
 The functors $\zdom : \esn \to \WDomb$ and $\zev : \WDomb \to \esn$
 form a coreflection.  It restricts to an equivalence between $\WDomb$
 and $\cesn$.
 %\todo{PB: verificare i nomi, funtori stesso nome, ok?}
\end{theorem}

Concerning the interval-based characterisation in
Section~\ref{ss:intervals}, we recall that the paper by
Droste~\cite{Dro:ESD} considers also the case of event structures with
a general consistency relation (rather than a binary conflict) and
shows that the corresponding domains can be characterised as
% $\omega$-
algebraic complete partial orders where
axioms (F), (C) of Section~\ref{ss:intervals} and, additionally, (I) below hold.

\begin{description}
\item[(I)] for all $x,x',y,y' \in \compact{D}$ if $\dint{x}{x'} \sim \dint{y}{y'}$
  and $x \sqsubseteq x'$ then $y \sqsubseteq y'$.
\end{description}

The definition of the {\esabbr} $\evwd{D}$ associated with a domain $D$
(Definition~\ref{de:evwd}) can be easily adapted to the non-binary
case. The only thing that changes is the definition of
consistency: a set $X \subseteq E$ is consistent if for all $e \in X$
there exists a representative $\dint{c_e}{c_e'} \in e$ such that
$\{ c_e \mid e \in X \}$ is bounded in $D$.
%
Then the correspondence with our approach established in
Section~\ref{ss:intervals} easily extends to this setting: algebraic
complete partial orders where axioms (F), (C) and (I) hold are exactly
the weak prime b-domains and the obvious rephrasing of
Proposition~\ref{pr:es-int} continue to hold.

Also the connection with asynchronous graphs in
Section~\ref{ss:async-graphs} can be adapted easily. Unsurprisingly,
Proposition~\ref{pr:was-ces} holds for connected {\esabbr} with
non-binary conflict if we modify the definition of asynchronous graph
(Definition~\ref{de:async-graph}) by omitting the coherence
axiom~(\ref{de:async-graph:4}).

%
%
%\item Winskel's {\esabbr} with symmetries~\cite{Win:ECS} (where events are
%  equated under a suitable symmetry ... check)
%\end{itemize}

\subsection{An Event Structure Semantics for the $\pi$-calculus}
\label{app:pi}

%\todo{Not in final version}

The need of resorting to unstable {\esabbr} for modelling the
concurrent computations of name passing process calculi has been
observed by several authors. In particular, in~\cite{CVY:ESSPE} an
{\esabbr} semantics for the pi-calculus is defined by relying on
so-called {\esabbr} \emph{with names} ({\esnmabbr} for short), namely
{\esabbr} that are tailored for parallel extrusions: labelled unstable
{\esabbr} with the constraint that two minimal enablings can differ
only for one event (intuitively, the extruder).

% In the paper, the authors use event structures with names. 
Given a global set of names $\mathcal{N}$, {\esabbr} \emph{with names}
({\esnmabbr} for short) are triples $(E, X, \lambda)$ where $E$ is a
prime {\esabbr}, $X \subseteq \mathcal{N}$ is a set of names
(intuitively, the names that are restricted), and
$\lambda : E \to \{ x(y), \bar{x}(y) \}$ is a function mapping each event
to either an input or an output prefix.

A configuration $C$ is a configuration of the underlying prime
{\esabbr} such that there exists a maximal $e \in C$
%~\todo{In the paper it is not asked that $e$ is maximal, but it is a typo}
satisfying
\begin{itemize}
\item $C \setminus \{ e \}$ is a configuration;
\item if $\lambda(e) = x(y)$ or $\lambda(e) = \bar{x}(y)$ with
  $x \in X$ then there exists $e' \in C \setminus \{e\}$ such that
  $\lambda(e') = \bar{z}(x)$.
\end{itemize}

The latter requirement above boils down to ensuring that if the name were 
restricted, it has been extruded before.
% 
Thus, {\esnmabbr} are unstable {\esabbr} with the additional constraint 
that two minimal enablings can differ only for one event (the extruder!):
namely, if $X_1 \vdash_0 e$ and $X_2 \vdash_0 e$ then
$X_1 \cap X_2 = X_1 \setminus \{ e_1 \} = X_2 \setminus \{ e_2 \}$
for suitable $e_1, e_2$.

Note that, {\esnmabbr} are not connected {\esabbr} since they can have 
non-connected minimal enablings (roughly, because identical events in 
disconnected minimal enablings are identified via the labelling).
% 
Consider e.g. $E = \{ \bar{a}(x), \bar{b}(x), x(y) \}$, with
$\bar{a}(x) \# \bar{b}(x)$, and $X=\{x\}$. Then the
configurations are $\emptyset$, $\{\bar{a}(x)\}$, $\{\bar{b}(x)\}$,
$\{\bar{a}(x), x(y)\}$, and $\{\bar{b}(x), x(y)\}$, hence $x(y)$ has two
non-connected minimal enablings. 
% 
% \todo{AC: Questa frase \`e un po' troppo informale. Togliere?}
% Nevertheless, we could get to a connected {\esabbr} through
% a suitable adjunction.

\end{document}

%
%
%
%

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2023-07-16 GraphShift/Figure/basic_independence.tex

\begin{center}
  \begin{tikzcd}[column sep=small, row sep=normal]
    {L_1} \ar[d, "m_{L_1}" swap]
    &
    {K_1} \ar[l, "l_1" swap] \ar[r, "r_1"] \ar[d, "m_{K_1}" description]
    &
    {R_1} \ar[dr, "m_{R_1}" description]  \ar[drrr, dotted, bend left=16, "i_1" description, pos=0.75]
    & &
    % 
    {L_2}\ar[dl, "m_{L_2}" description] \ar[dlll, dotted, bend right=16, "i_2" description, pos=0.75]
    &
    {K_2} \ar[l, "l_2" swap] \ar[r, "r_2"] \ar[d, "m_{K_2}" description]
    &
    {R_2} \ar[d, "m_{R_2}"] \\
    % 
    % 
    {G}
    &
    {D_1} \ar[l, "l^*_1"] \ar[rr, "r^*_1" swap]
    & {} &
    {H}
    & {} &
    {D_2} \ar[ll, "l^*_2"] \ar[r, "r^*_2" swap]
    &
    {M}  
  \end{tikzcd}
\end{center}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: ../GraphShift.tex
%%% End:

### 2023-07-16 Notes.tex
try
some related stuff

@@
   prevent fusions to act on already merged items (see section V.D in
-  the arxiv). By the way, note that the satisfaction of the conditions
+  UnstableFull). By the way, note that the satisfaction of the conditions
   on shift depends not only on the notion of shift, but also on the
@@
 
-For this part, relevant material is section V of Arxiv.
+For this part, relevant material is section V of UnstableFull.
 We use abstraction equivalence (iso of derivations) $\equiv^{a}$ (def.
@@
 related by $\rho \equiv^c_\sigma \rho'$ iff $\sigma$ is a consistent
-permutation (def. 40, arxiv). Rough;y the idea is to take the colimit
+permutation (def. 40, UnstableFull). Rough;y the idea is to take the colimit
 and consider the rewriting steps over the colimit to deduce
@@
 
-Relevant technical lemma in Arxiv are:
+Relevant technical lemma in UnstableFull are:
 

### 2023-07-16 Notes.tex
minima

@@
 
-We want a notion of shift-equivalence which ensures some properties
+We want a notion of shift-equivalence that ensures some properties
 which are indispensable to allow to interpret derivations up-to shift
@@
 that independent steps have been moved around.
-When moving around steps, we should not loose track of the identity of the steps: this is essential to be able to have an event structure semantics with a clearly defined notion of event.
+When moving around steps, we should not lose track of the identity of the steps: this is essential to be able to have an event structure semantics with a clearly defined notion of event.
 
@@
 
-\textbf{Question.} Taking the standard shift, with generic interchange pair, a a counterexample to property 1, is the one mentioned above.  Do we have a counterexample to property 2? Not clear to me.
+\textbf{Question.} Taking the standard shift with generic interchange pair, a counterexample to Property 1 is the one mentioned above.  Do we have a counterexample to Property 2? Not clear to me.
 
@@
 
-  \textbf{Questions}: Can we reduce the set of axioms? Do we need something else relating abstraction equivalence (iso of derivation) and shift? Relation with symmetries?
+  \textbf{Questions}: Can we reduce the set of axioms? Do we need something else relating abstraction equivalence (iso of derivations) and shift? Relation with symmetries?
 
@@
   notion of rewriting. In this case we expect to have a prime event
-  structure (bit this has to do with the second part of the work).
+  structure (but this has to do with the second part of the work).
 
@@
 shift-equivalence and just using its properties as singled out in the
-previous part derive a weak prime domain or connected event structure
+previous part to derive a weak prime domain or connected event structure
 for it. This is probably difficult, but one might need to add some
@@
 For this part, relevant material is section V of UnstableFull.
-We use abstraction equivalence (iso of derivations) $\equiv^{a}$ (def.
+We use abstraction equivalence (iso of derivations) $\equiv^{a}$ (Def.
 36), shift-equivalence $\shifteq_\sigma$ (Def.
@@
 related by $\rho \equiv^c_\sigma \rho'$ iff $\sigma$ is a consistent
-permutation (def. 40, UnstableFull). Rough;y the idea is to take the colimit
+permutation (Def. 40, UnstableFull). Roughly the idea is to take the colimit
 and consider the rewriting steps over the colimit to deduce
@@
 is false). In general, the hope is to get rid of using consistent
-permutation and use instead more asbtract properties of
+permutations and use instead more abstract properties of
 shift-equivalence as discussed in the first part.
@@
 In particular there is $\phi_2$ consisting of exactly $n$ steps which allows for commutation.
-This allows essentially to deduce existence of minimal upper bounds, al with the same length.
+This allows essentially to deduce existence of minimal upper bounds, all with the same length.
   Then (2) shows that all minimal upper bounds are isomorphic, so that we have a sup.
@@
 
-  Here I think that the proofs are draft modifications of the original ones, changed after discovering the property on consistent permutation to be wrong.
+  Here I think that the proofs are draft modifications of the original ones, changed after discovering the property on consistent permutations to be wrong.
 But they are drafty, to be redone maybe keeping some ideas.

### 2023-07-17 Notes.tex
typo

@@
 identity but which are non isomorphic (e.g., in GraphShift, page 1-2
-$\rho_1 \shifteq \rho_3$, but $\rho_1 \equiv^{a} \rho_3$.
+$\rho_1 \shifteq \rho_3$, but $\rho_1 \not\equiv^{a} \rho_3$.
 

### 2023-07-17 Notes.tex
typo

--- 2023-07-16 Notes.tex
@@
 
-Sequential independence is a key ingredient in the concurrency theory of DPO graph transformation, since it states when consecutive rewriting steps can be switched, thus 
-identifying them as causally unrelated. The associated theory of shift equivalence on rewriting sequences is well-understood for linear rules, including its 
-connection with standard models for concurrent systems such as event structures. 
+Sequential independence is a key ingredient in the concurrency theory
+of DPO graph transformation, since it states when consecutive
+rewriting steps can be switched, thus identifying them as causally
+unrelated. The associated theory of shift equivalence on rewriting
+sequences is well-understood for linear rules, including its
+connection with standard models for concurrent systems such as event
+structures.
 %
@@
 identity but which are non isomorphic (e.g., in GraphShift, page 1-2
-$\rho_1 \shifteq \rho_3$, but $\rho_1 \equiv^{a} \rho_3$.
+$\rho_1 \shifteq \rho_3$, but $\rho_1 \not\equiv^{a} \rho_3$).
 
@@
 as equivalent concurrent computations which differ only for the fact
-that independent steps have been moved around.
-When moving around steps, we should not lose track of the identity of the steps: this is essential to be able to have an event structure semantics with a clearly defined notion of event.
+that independent steps have switched. When moving around steps, we
+should not lose track of the identity of the steps: this is essential
+to be able to have an event structure semantics with a clearly defined
+notion of event.
 
-Hence we assume to deal
-with a notion of shift-equivalence between derivations of the kind
-$\rho \shifteq_\sigma \rho'$ where $\rho, \rho'$ consist of $n$
-rewriting steps, $\sigma: \interval{n} \to \interval{n}$ is a
-permutation (the idea being that $\rho$ is obtained from $\rho'$
-pemutating the steps according to $\sigma$) with the following
-properties:
+Hence we assume to deal with a notion of shift-equivalence between
+derivations of the kind $\rho \shifteq_\sigma \rho'$ where
+$\rho, \rho'$ consist of $n$ rewriting steps,
+$\sigma: \interval{n} \to \interval{n}$ is a permutation (the idea
+being that $\rho$ is obtained from $\rho'$ permutating the steps
+according to $\sigma$) with - at least - the following properties:
 
 \begin{itemize}
-\item \textbf{Property 0}. Shift equivalence is an equivalence, in particular it is symmetric. I.e., if  $\rho \shifteq_\sigma \rho'$ then $\rho' \shifteq_{\sigma^{-1}} \rho$;
+\item \textbf{Property 0}. Shift-equivalence is an equivalence! In
+  particular it is symmetric. I.e., if $\rho \shifteq_\sigma \rho'$
+  then $\rho' \shifteq_{\sigma^{-1}} \rho$;
 
@@
 
-\textbf{Question.} Taking the standard shift with generic interchange pair, a counterexample to Property 1 is the one mentioned above.  Do we have a counterexample to Property 2? Not clear to me.
+\textbf{Question.} Taking the standard shift with generic interchange
+pair, in the case of non-linear rules a counterexample to Property 1
+is the one mentioned above.  Do we have a counterexample to Property
+2? Not clear to me.
 
@@
 
-  \textbf{Questions}: Can we reduce the set of axioms? Do we need something else relating abstraction equivalence (iso of derivations) and shift? Relation with symmetries?
+  \textbf{Questions}: Can we reduce the set of axioms? Do we need
+  something else relating abstraction equivalence (iso of derivations)
+  and shift? Relation with symmetries?
 
-\item For left-linear rules, the proposed notion of shift equivalence
-  requires: uniqueness of the interchange pair and symmetry. Show that
+\item For left-linear rules, the notion of shift equivalence should
+  require: uniqueness of the interchange pair and symmetry. Show that
   this satisfies the above
@@
 \item Apparently, the satisfaction of the properties above has not
-  been explicitly observed for the case of linear rules. If so, it is
-  worth to remark it.
+  been explicitly observed, not even for the case of linear rules. If
+  so, it is worth to remark it.
 
@@
   prevent fusions to act on already merged items (see section V.D in
-  UnstableFull). By the way, note that the satisfaction of the conditions
-  on shift depends not only on the notion of shift, but also on the
-  notion of rewriting. In this case we expect to have a prime event
-  structure (but this has to do with the second part of the work).
+  UnstableFull). Incidentally, note that the satisfaction of the
+  conditions on shift depends not only on the notion of shift, but
+  also on the notion of rewriting.
+
+  In this specific case we expect to have a prime event structure (but
+  this has to do with the second part of the work).
 
@@
 for it. This is probably difficult, but one might need to add some
-futher properties to be proved for the specific notion of shift at
+further properties to be proved for the specific notion of shift at
 hand.
@@
 36), shift-equivalence $\shifteq_\sigma$ (Def.
-38, traking the permutation) and their join $\equiv^c_\sigma$.
+38, tracking the permutation) and their join $\equiv^c_\sigma$.
 
@@
 to rely on linearity, this should be double-checked, but the converse
-is false). In general, the hope is to get rid of using consistent
+is false).
+
+In general, the hope could be to get rid of using consistent
 permutations and use instead more abstract properties of
-shift-equivalence as discussed in the first part.
+shift-equivalence as discussed in the first part. However, I think
+that using the valid implication (``if $\rho \equiv^c_\sigma \rho'$
+then $\sigma$ is a consistent permutation'') can be quite useful to track the identity of rewriting steps, as they can be identified with the items consumed in the colimit.
 
-The general idea is to show that considering derivations are arrows from the source to the target graph, then the slice from the initial graph $\slice{[G_s]}{\tr{\mathcal{G}}}$ should be a pre-order, whose ideal completion is a weak prime domain.
+The general idea for getting a domain is to show that considering derivations are arrows from the source to the target graph, then the slice from the initial graph $\slice{[G_s]}{\tr{\mathcal{G}}}$ should be a pre-order, whose ideal completion is a weak prime domain.
 
@@
 
-\keywords{Shift equivalence, non-linear rules, DPO rewriting.}
-
-\section{Introduction}
-\label{se:graphs}
-
-Shortly, shift equivalence can be defined as the smallest equivalence relation on derivations, i.e. sequences of rewriting steps,
-that can be obtained by the iterated switch of sequentially 
-independent steps. A crucial observation, which represented our starting point, is that the notion of sequential independence traditionally
-adopted for linear graph transfomation systems is not adequate when we
-allow rules to be non-right linear, i.e., in the presence of
-fusions. Consider the rules in Fig.~\ref{fi:rules}, typed over the type graph $T$,
-where numbers are used to represent the mappings from the interface to the left- and
-right-hand sides.
-
-\begin{figure}
-  \input{Figure/rules.tex}
-
-\caption{The type graph  and the rules of the grammar of the example.}
-\label{fi:rules}
-\end{figure}
-
-Now, let us consider an initial graph with a single node. We can then obtain
-the derivation $\rho_1 = \delta_1; \delta_2; \delta_3$ in Fig.~\ref{fi:der1}, where $\delta_2$ and $\delta_3$ are
-sequential independent according to the standard notion.
-
-\begin{figure}
-  \input{Figure/der1.tex}
-\caption{The derivation $\rho_1$.}
-\label{fi:der1}
-\end{figure}
-
-We can exchange the applications of $p_2$ and $p_3$, thus getting the
-derivation $\rho_2 = \delta_1; \delta_3'; \delta_2'$ in
-Figure~\ref{fi:der2}. Now, one can exchange again $p_3$ and $p_2$,
-reaching the derivation $\rho_3 = \delta_1; \delta_2'; \delta_3$ in
-Figure~\ref{fi:der3}, where in $\delta_2'$ production $p_2$ uses the
-node of the start graph and thus ``does not depend'' on $p_1$.
-
-\begin{figure}[t]
-  \input{Figure/der2.tex}
-\caption{The derivation $\rho_2$.}
-\label{fi:der2}
-\end{figure}
-
-\begin{figure}[t]
-  \input{Figure/der3.tex}
-\caption{The derivation $\rho_3$.}
-\label{fi:der3}
-\end{figure}
-
-The fact that if we switch two steps and then switch them back, we obtain a derivation that is not equivalent to the original one has unpleasant consequences.
-For instance, if we restrict $\rho_1'$ and $\rho_3'$ to the first two steps, we get non-equivalent derivations $\delta_1;\delta_2 \not\shifteq \delta_1;\delta_2'$, but $\rho_1 \shifteq[\sigma] \rho_3$, with $\sigma$ mapping $\delta_1$ to $\delta_1$ and $\delta_2$ to $\delta_2'$.
-%
-The lack of such closure with respect to composition does not allow to obtain a causal semantics for graph transformation systems.
-More precisely, it does  not allow to associate an event structure to a derivation.
-%
-Thus, the notion of sequential independence has to be refined. The point is that in the associated shift equivalence we want to forget who made the fusion, 
-but we should not forget (as it happens in the example) that some fusions occurred.
-
-% In Andrea's counterexample (same as above, but $p_2$ produces an item that is consumed by $p_3$, thus forcing $p_3$ to happen last), if we construct the domain we have:
-% \begin{center}
-%   \includegraphics[scale=.7]{dom.pdf}
-% \end{center}
-% which is a weak prime domain (actually a prime domain) but it does not capture the proper semantics (e.g., $p_2'$ and $p_3$ are the same event!).
-
-Shift equivalence is made stricter by asking that two steps are
-sequentially independent if the result of their switch is uniquely
-determined. Intuitively, when there are several way of performing the
-exchange, it means that the first step has executed some fusions that
-the second step is using in an essential way, hence they should not
-considered independent. Formally, this boils down to require that 
-in the definition of sequential independence the interchange pair is unique.
-
-The paper builds on this intuition: it introduces this stricter notion of sequential independence
-(Section~xxx) and prove that the associated theory of shift equivalence on derivations is 
-well-behaved with respect to the concatenation of rewriting steps (Section~xxx).
-Finally, it outlines how the relationship with event structure works, wrapping up the paper
-with comparison with related woks and hinting at further direction of research (Section~xxx).
-
-\section{Preliminaries [to be redone]}
-
-\begin{figure}[t]
-   \input{Figure/basic_independence}
-\caption{Sequential independence for
-  $\rho = G \Rrel{p_1/m_1} H \Rrel{p_2/m_2} M$.}
-\label{fi:strongseq}
-\end{figure}
-
-\begin{definition}[sequential independence]
-  \label{de:seq-ind}
-  Consider a derivation $G \Rrel{p_1/m_1} H \Rrel{p_2/m_2} M$ as in
-  Fig.~\ref{fi:strongseq}. Then, its components are \emph{sequentially
-    independent} if there exists a unique \emph{independence pair} among
-  them, i.e., two graph morphisms $i_1: R_1 \rightarrow D_2$ and
-  $i_2: L_2 \rightarrow D_1$ such that $l_2^* \circ i_1 = m_{R_1}$,
-  $r_1^* \circ i_2 = m_{L_2}$.
-\end{definition}
-
-Observe that this notion reduces to the usual one for linear rules. In
-fact when $r_1^*$ and $l_2^*$ are mono the uniqueness requirement is
-trivially satisfied. Instead, for left-injective rules $i_1$ is still
-unique, but $i_2$ might be not (as it happens, e.g., in the example
-before).\todo{Say more about the example}
-
-Observe that the notion is not symmetric: if
-$\rho = G \Rrel{p_1/m_1} H \Rrel{p_2/m_2} M$ is sequential independent
-and we switch it, we could obtain a pair which is not because it fails
-to satisfy uniqueness of the independence pair (this happens, e.g., in
-our example, where $\delta_2;\delta_3$ is sequential independent, but
-$\delta_3';\delta_2'$ is not). The idea is to define shift equivalence
-as $\rho \equiv_{sh} \rho'$ when \emph{each of the two} can be
-obtained from the other by exchanging sequential independent
-derivations. More precisely, we have a shift relation, which is used
-for defining the equivalence as in Fig.~\ref{fi:ind}. It could be
-better to have a slightly less elegant but more direct
-definition. Write $\rho \shiftdir[\transp{i}] \rho'$ when
-$\rho = \rho_1; \rho_2; \rho_3$ and $\rho' = \rho_1; \rho_2', \rho_3$
-with $|\rho_1| = i-1$, $|\rho_2|=2$ and $\rho_2' \in
-\IC{\rho_2}$. Then we write $\rho \shiftpre[\perm] \rho'$ if
-$\rho = \rho_0 \shiftdir[\perm_1] \rho_1 \ldots \shiftdir[\perm_n ]
-\rho'$ with $\perm = \perm_1; \ldots; \perm_n$ for some $n \geq 0$
-(with the convention that for $n=0$ we get the identity).
-
-The restricted notion of sequential independence ensures that the interchange operator produces a result that is unique up to abstraction equivalence.
-
-\begin{lemma}[IC is unique]
-  \label{le:unique-IC} 
-  Let $\rho$ be a derivation such that $|\rho|=2$. If $\rho$ is
-  sequential independent, let us write
-  $\IC{\rho} = \{ \rho' \mid \rho \shiftdir \rho'\}$. Then for
-  all $\rho', \rho'' \in \IC{\rho}$ we have $\rho' \equiv
-  \rho''$. Moreover, if $\rho$ is sequential independent then for all
-  $\rho' \in \IC{\rho}$, if $\rho'$ is sequential independent and
-  $\rho'' \in \IC{\rho'}$, we have $\rho \equiv \rho''$.
-\end{lemma}
-
-\begin{figure}[t]
-  \input{Figure/independence}
-  \caption{Independence.}
-  \label{fi:independence}
-\end{figure}
-
-It is convenient (at the beginning, at least) to work with shift
-on derivations where the source and target graph is concrete and the
-middle can be taken up to iso. I think that everything can be then
-easily transferred to ctc-equivalence. We say that $\rho$ and $\rho'$
-are abstract shift-equivalent and write $\rho \sim \rho'$.
-
-A crucial observation is that independence can be defined also for non-contiguous steps.
-
-\begin{definition}[independence]
-  Let $\delta_1;\rho;\delta_n$ be a derivation as in
-  Fig.~\ref{fi:independence}, where $\delta_1$ and $\delta_n$ are
-  direct derivations and $\rho$ is a generic, possibly empty
-  derivation. We say that $\delta_1$ and $\delta_n$ are independent if
-  there is a unique independence pair $i_{n,1}$ and $i_{1,n}$
-  satisfying the expected commutation, where $C$ is the colimit of the
-  bottom line (excluding $G_1, G_{n+1}$).
-\end{definition}
-
-The fact that the notion of independence makes sense is proved by the following lemma, showing that the notion is preserved by the shift relation.
-
-\begin{lemma}[independence is global]
-  \label{le:seq-ind-glob1}
-  The notion of independence for contiguous derivation steps
-  coincides with sequential independence.
-
-  Moreover, independence is invariant under the shift-relation, i.e.,
-  \begin{itemize}
-
-  \item if $\delta_1;\rho;\delta_2$ and $\rho \shiftpre \delta'$ then
-    in $\delta_1;\rho;\delta_2$ the steps $\delta_1$, $\delta_2$ are
-    independent iff they are in $\delta_1;\delta';\delta_2$.
-
-  \item if $\delta_1;\rho;\delta';\delta_2$ and
-    $\delta_2'; \delta'' \in \IC{\delta';\delta_2}$ then in
-    $\delta_1;\rho;\delta';\delta_2$ the steps $\delta_1$ and $\delta_2$ are
-    independent iff they are in $\delta_1;\rho;\delta_2'$.
-
-  \item same as before, but with shift on the left.
-  \end{itemize}
-\end{lemma}
-
-\begin{proof}
-  To be done. The fact that sequential independence coincides with
-  independence for contiguous derivations is easy.
-The fact that it coincides when derivations are not contiguous is false (the approach based on defining independence for non-contiguous derivation is not working, but the results should be true ...)
-\end{proof}
-
-A \emph{permutation} on $\interval{n}$ is a bijection
-$\perm : \interval{n} \to \interval{n}$. We call it a
-\emph{transposition} when there are $i, j \in \interval{n}$,
-$i \neq j$ such that $\sigma(i)=j$, $\sigma(j) = i$ and
-$\sigma(k) = k$ otherwise. Such a transposition is normally denoted as
-$\transp{i}[j]$. Whenever $j = i+1$ we call it an \emph{adjacent
-  transposition}.
-
-Given a permutation $\perm$ on $\interval{n}$, the set of inversions
-of $\perm$ is
-$\inv{\perm} = \{ (i,j) \mid i,j \in \interval{n-1}\ \land\ i<j\
-\land\ \perm(i) > \perm(j) \}$. Clearly, $\perm$ is the identity iff
-$\inv{\perm}=0$.
-
-Now, if $\perm \neq id$ there is at least an inversion of the kind
-$(i,i+1)$.  Then we have that $\perm = \transp{i}; \perm'$
-with $|\inv{\perm'}| = |\inv{\perm}| -1$. Hence we can inductively
-express $\perm$ as a (minimal length) composition of adjacent
-transpositions.
-
-\begin{lemma}[on permutations]
-  \label{le:perm}
-  Let $\perm$, $\perm'$ be permutations on $\interval{n}$ and
-  $\perm = \upsilon_1; \perm'; \upsilon_2$ where $\upsilon_1$ and $\upsilon_2$
-  are transpositions with $\upsilon_1 = \transp{i}[j]$ and
-  $\upsilon_2 = \transp{\perm'(i)}[\perm'(j)]$. Then $\sigma =
-  \sigma'$.
-
-  Moreover, let $\upsilon_1, \upsilon_2$ be adjacent
-  transpositions and $\sigma' = \upsilon_1; \ldots, \upsilon_m$ a
-  minimal length decomposition of $\sigma'$ in terms of adjacent
-  transpositions (that thus operate on inversions). Then, for all
-  $h \in \interval{m}$ with $\upsilon_h = \transp{l}[l+1]$ there exists
-  $k \in \interval{m}$ such that
-  $\upsilon_k = \transp{\upsilon_{1,h-1}^{-1};v_1;
-    \upsilon_{1,k-1}(l)}[\upsilon_{1,h-1}^{-1};v_1; \upsilon_{1,k-1}(l+1)]$.
-\end{lemma}
-
-\begin{proof}
-  The first part is easy. The second is a consequence of the fact that
-  the minimal decomposition in terms of adjacent transpositions is
-  essentially unique, in the sense that it consists of exchanges of
-  all the inversions. To be formalised.
-\end{proof}
-
-In words, the lemma above says that if a permutation is decomposed as $\sigma = \upsilon_1; \sigma'; \upsilon_2$ with $\sigma' = \upsilon_1'; \ldots, \upsilon_n'$, where $\upsilon_1$ and $\upsilon_2$ performs a switch and its reverse, and the inner decomposition is minimal, then we can strip the first and last switch and get a decomposition of the same permutation that performs the same switches but possibly in a different order.
-
-\begin{lemma}[no need of useless shifts]
-  \label{le:no-useless-shifts}
-  Let $\rho$, $\rho'$ be direct derivations and assume
-  $\rho \shiftpre[\sigma] \rho'$. Then
-  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots \shiftdir[\upsilon_n ]
-  \rho'$ where $\sigma = \upsilon_1; \ldots; \upsilon_n$ and $\upsilon_j \in \inv{\upsilon_{j,n}}$ for $j \in \{1, \ldots,n\}$.
-\end{lemma}
-
-\begin{proof}
-  Let $\rho \shiftpre[\perm] \rho'$. This means that
-  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots \shiftdir[\upsilon_n ]
-  \rho'$ with $\perm = \upsilon_1; \ldots; \upsilon_n$ for some $n \geq 0$.
-
-  We show that if some $\upsilon_j$ does not act on an inversion, i.e.,
-  $\upsilon_j \not\in \inv{\sigma_{j,n}}$ then we can shorten the
-  proof of $\rho \shiftpre[\sigma] \rho'$ of two steps. This will
-  allow us to conclude that we can reduce it to a proof only acting
-  on inversions, as desired.
-
-  The key observation is that, if
-  $\upsilon_j \not\in \inv{\sigma_{j,n}}$ then, intuitively, the ``same
-  exchange'' must be performed in the reverse direction by some
-  $\upsilon_h$ ($h>j$).  Formally, if $\upsilon_j = \transp{i}$ and
-  $(i,i+1)\not\in\inv{\upsilon_{i,n}}$ then there exists $h>j$ such that
-  $\upsilon_{j,h-1}(i) = \upsilon_{j,h-1}(i+1)+1$ and
-  $\upsilon_h = \transp{\upsilon_{j,h-1}(i+1)}$. Among all the pairs
-  $j, h$ of this kind, take one with minimal $h-i$. This means that in
-  the middle all transpositions are inversions of $\upsilon_{i+1,h-1}$.
-
-  By Lemma~\ref{le:perm}, $\upsilon_i$ and $\upsilon_h$ can be
-  stripped, i.e., $\upsilon_{i,h} = \upsilon_{i+1,h-1}$. Moreover,
-  again by Lemma~\ref{le:perm},
-  $\upsilon_{i+1}, \ldots, \upsilon_{h-1}$ perform exchanges that were
-  already done in the original proof, and thus, since independence is
-  invariant under shift equivalence, as expressed by
-  Lemma~\ref{le:seq-ind-glob1} they are allowed. Moreover, since by
-  Lemma~\ref{le:unique-IC} the result of switching is uniquely
-  determined (up to iso), the resulting derivation is the same as
-  before, hence we can strip $\upsilon_{i}$ and $\upsilon_{h}$,
-  and conclude.
-\end{proof}
-
-Then we can prove that whenever $\rho \shiftpre[\perm] \rho'$, each
-decomposition of $\perm$ in terms of inversions leads to a valid
-derivation of $\rho'$ from $\rho$.
-
-\begin{lemma}[independence is global/2]
-  \label{le:seq-ind-glob2}
-  Let $\rho$, $\rho'$ be direct derivations. Let
-  $\rho \shiftpre[\perm] \rho'$, with $\perm \neq id$ and let
-  $\perm = \transp{i}; \perm'$ where $(i,i+1) \in \inv{\perm}$. Then
-  there exists $\rho''$ such that
-  $\rho \shiftpre[\transp{i}] \rho'' \shiftpre[\perm']
-  \rho'$.
-\end{lemma}
-
-\begin{proof}
-  Let
-  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots
-  \shiftdir[\upsilon_n] \rho'$ where $\sigma = \upsilon_1; \ldots; \upsilon_n$ and $\upsilon_j \in \inv{\upsilon_{j,n}}$ for $j \in \{1, \ldots,n\}$, be the decomposition
-  provided by Lemma~\ref{le:no-useless-shifts}.
-
-  We know that steps corresponding to $i$ and $i+1$ are exchanged at
-  some point, namely there is $j$ such that
-  $\upsilon_j =
-  \transp{\upsilon_{1,j-1}(i)}[\upsilon_{1,j-1}(i+1)]$. By
-  Lemma~\ref{le:seq-ind-glob1} the steps $i$ and $i+1$ are independent
-  already at the beginning and thus we can exchange them first.
-  More precisely, 
-  \begin{center}
-    $\rho \shiftdir_{\transp{i}} \rho'' \shiftdir_{\upsilon_{1,j-1}}
-    \rho_j \shiftdir_{\upsilon_{j+1,n}} \rho'$.
-  \end{center}
-  This can be proved by induction on $j$.
-\end{proof}
-
-\begin{lemma}[more on shift]
-  \label{le:more-shift}
-  if $\rho_1;\rho_1' \shiftpre[\perm | \perm'] \rho_2; \rho_2'$,
-  with $|\rho_1| = |\rho_2|$ and
-  $\sigma : \interval{|\rho_1|-1]} \to \interval{|\rho_2|-1]}$ then
-  $\rho_1 \shiftpre[\perm] \rho_2$ and
-  $\rho_1' \shiftpre[\perm'] \rho_2'$.
-\end{lemma}
-
-\begin{proof}
-  The results follows by the fact that, from
-  Lemma~\ref{le:no-useless-shifts}, we derive that
-  \begin{center} 
-    $\rho_1;\rho_1' \shiftdir[ \upsilon_1 \mid id_{[1..|\rho_1'|]}]
-    \ldots \shiftdir[ \upsilon_h \mid id_{[1..|\rho_1'|]}] \rho_2;
-    \rho_1' \shiftdir[ id_{[1..|\rho_1|]} \mid \upsilon_1'] \ldots
-    \shiftdir[ id_{[1..|\rho_1|]} \mid \upsilon_k'] \rho_2; \rho_2'$
-  \end{center}
-  where $\upsilon_1; \ldots; \upsilon_h$ is a decomposition of $\perm$
-  in terms of inversions and, similarly,
-  $\upsilon_1'; \ldots; \upsilon_k'$ is a decomposition of
-  $\perm'$. Then
-  $\rho_1 \shiftdir[\upsilon_1] \ldots \shiftdir[\upsilon_h] \rho_2$
-  and analogously
-  $\rho_1' \shiftdir[\upsilon_1'] \ldots \shiftdir[\upsilon_k']
-  \rho_2'$, which leads to the desired conclusion.
-\end{proof}
-
-\todo[inline]{Note that above we assume that $\rho_1$ and $\rho_1'$ ends in the same graph. To be formalised.}
-
-\begin{lemma}[uniqueness of permutation]
-  if $\rho \shiftpre[\perm_1] \rho'$ and
-  $\rho \shiftpre[\perm_2] \rho'$ then $\perm_1 = \perm_2$. In
-  particular, if $\rho_1 \shiftpre[\perm_1] \rho_1$ then $\perm_1 = id$.
-\end{lemma}
-
-\begin{proof}
-  We proceed by induction on the length of the derivations
-  $\ell=|\rho|=|\rho'|$ and by an inner induction on the number of
-  inversions in $\sigma_1$. When $\ell = 0$, the result is
-  trivial. Let us assume $\ell>0$ and let $i_1 = \sigma_1^{-1}(1)$,
-  $i_2 = \sigma_2^{-1}(1)$. Let
-  $L_1' \stackrel{l_1'}{\leftarrow} K_1' \stackrel{r_1'}{\rightarrow}
-  R_1')$ be the rule used by the first production in $\rho'$.
-  By Lemma 17(1) in the paper [the implication
-  that holds] $\sigma_1$ and $\sigma_2$ are consistent permutations of
-  $\rho$ into $\rho'$.
-  %
-  Since they are consuming, it is easy to see that
-  $i_1=\sigma_1^{-1}(1)$ is uniquely determined by the (equivalence
-  class) of an item in the initial graph consumed by $L_1'$ and the
-  same applies to $i_2=\sigma_2^{-1}(1)$, hence we conclude that
-  $i_1=i_2$.
-
-  Now, if $i_1=i_2=1$, then $\sigma_j = \transp{1}[1] \mid \sigma_j'$
-  for $j \in \{1,2\}$ and $\rho = \delta; \rho_1$,
-  $\rho' = \delta; \rho_1'$ where $\delta$ is the first direct
-  derivation, and $\rho_1 \shiftpre[\perm_j'] \rho_1'$ for
-  $j \in \{1,2\}$. Since $|\rho_1| = \ell-1$ we conclude by inductive
-  hypothesis that $\sigma_1'=\sigma_2'$ and thus $\sigma_1=\sigma_2$,
-  as desired.
-
-  If instead $i_1=i_2=i>1$, since $\transp{i_1-1}[i_1]$ is an inversion for both
-   $\sigma_1$ and $\sigma_2$, by Lemma~\ref{le:seq-ind-glob2} we can
-  perform such a shift first, obtaining
-  \begin{center}
-    $\rho \shiftdir[{\transp{i-1}[i]}] \rho_1
-    \shiftpre[{\transp{i-1}[i];\sigma_1}] \rho'$
-    %
-    \quad and \quad
-    %
-    $\rho \shiftdir[{\transp{i-1}[i]}] \rho_1
-    \shiftpre[{\transp{i-1}[i];\sigma_2}] \rho'$
-  \end{center}
-  Since ${\transp{i-1}[i];\sigma_1}$ has an inversion less than
-  $\sigma_1$ we conclude by inductive hypothesis that
-  ${\transp{i-1}[i];\sigma_1} ={\transp{i-1}[i];\sigma_2}$, whence
-  $\sigma_1=\sigma_2$.
-\end{proof}
-
-Note that the above works also with the liberal definition of
-sequential independence.
-
-\begin{lemma}[Lemma 17(2) in the paper]
-  if $\rho;\rho_1 \shiftpre[\perm] \rho; \rho_2$ then
-  $\perm = id_{[1..|\rho|]} \mid \perm'$ and
-  $\rho_1 \shiftpre[\perm'] \rho_2$.
-\end{lemma}
-
-\begin{proof}[skecth]
-  Productions are `uniquely identified by the items they consume,
-  hence productions in $\rho$ are necessarily mapped to themselves,
-  i.e., $\perm = id_{[1..|\rho|]} \mid \perm'$. Then we conclude
-  $\rho_1 \shiftpre[\perm'] \rho_2$ by Lemma~\ref{le:more-shift}.
-\end{proof}
-
-\begin{lemma}[Lemma 20 in the paper]
-  \label{le:prop-c}
-  Let $\psi$ and $\psi'$ be decorated derivations. Then the following hold:
-  \begin{enumerate}
-  \item
-    \label{le:prop-c:1}
-    Let $\psi_1, \psi_1'$ be such
-    that $\psi;\psi_1 \equiv^c_{\perm} \psi';\psi_1'$ and let
-    $n = | \{ j \in \interval[|\psi|]{|\psi;\psi_1|-1} \mid \perm(j)
-    < |\psi'| \}|$. Then for all $\phi_2, \phi_2'$ such that
-    $\psi;\phi_2 \equiv^c \psi';\phi_2'$ it holds $|\phi_2| \geq n$
-    and there are $\psi_2, \psi_2',\psi_3$ such that
-
-    \begin{itemize}
-    \item $\psi;\psi_1 \equiv^c \psi;\psi_2;\psi_3$
-    \item $\psi;\psi_2 \equiv^c \psi';\psi_2'$
-
-    \item $|\psi_2| = n$
-
-    \end{itemize}
-
-  \item
-    \label{le:prop-c:2}
-    Let $\psi_1, \psi_1'$, $\psi_2, \psi_2'$ be such that
-    $\psi;\psi_1 \equiv^c_{\perm_1} \psi';\psi_1'$ and
-    $\psi;\psi_2 \equiv^c_{\perm_2} \psi';\psi_2'$ with $\psi_1, \psi_2$
-    of minimal length. Then $\psi_1 \equiv^c_\perm \psi_2 \cdot \nu$,
-    where $\nu : \target{\psi_2} \to \target{\psi_2}$ is some graph isomorphism and
-    $\perm(j) = \perm_2^{-1}(\perm_1(j + |\psi|))-|\psi|$ for
-    $j \in \interval[0]{|\psi_1|-1}$.    
-  \end{enumerate}
-\end{lemma}
-
-\begin{proof}[sketch]  
-  Point ~\ref{le:prop-c:1}: The proof should be similar to the one we have already, basing the rearrangement on Lemma~\ref{le:seq-ind-glob2}.
-Roughly we get $\psi;\psi_1 \equiv^c \psi_a;\psi_b;\psi_{2};\psi_{3}$ and
-  $\psi';\psi_1' \equiv^c \psi_a';\psi_b';\psi_{2}';\psi_{3}'$
-  with
-  \begin{center}
-    $\psi_a;\psi_b;\psi_{2};\psi_{3}
-    \equiv^c_{\perm_a|\perm_{b2}|\perm_2}
-    \psi_a';\psi_b';\psi_{2}';\psi_{3}'$
-  \end{center}
-  with $\perm_a$ over $\interval{|\psi_a|-1}$, $\perm_{b2}$ over
-  $\interval{|\psi_b;\psi_{2}|-1}$ ``mapping $\psi_b$ to $\psi_{2}'$
-  and $\psi_b'$ to $\psi_{2}$'', $\perm_3$ over
-  $\interval{|\psi_2|-1}$.  We deduce by Lemma~\ref{le:more-shift}
-  that $\psi_a \equiv^c_{\perm_a} \psi_a'$,
-  $\psi_b;\psi_{2} \equiv^c_{\perm_{b2}} \psi_b';\psi_{2}'$ and
-  $\psi_{3} \equiv^c_{\perm_3} \psi_{3}'$.
-
-  Now, for all $\phi_2, \phi_2'$ such that
-  $\psi;\phi_2 \equiv^c \psi';\phi_2'$ we can perform the same
-  splitting and this leads to the conclusion that $|\phi| \geq n$ and
-  also it can be expressed as $\psi_2;\phi_2'$, that should subsume
-  also the second point.
-  %
-\qed
-\end{proof}
-
-% \paragraph{Note.} This does not solve the problem raised by Andrea's counterexample that still applies.
-
-Another idea could be to try to use the inductive characterisation in Figure~\ref{fi:ind} (but I do not see how to mange the transitive rule).
-
-\begin{figure}
-  \begin{center}
-    \small
-  \[
-    \inferL{\slab{(SH-id)}}
-    {\rho \shiftpre[id] \rho}
-    {}
-    % 
-    \hspace{0.9cm}
-    % 
-    \inferL{\slab{(SH-exch)}}
-    {\rho \shiftpre[{\transp{1}[2]}] \rho'}
-    {\rho = \upsilon_1;\upsilon_2 & \rho' \in \IC{\rho}}
-  \]
-
-  \[
-    \inferL{\slab{(SH-comp)}}
-    {\rho_1 ; \rho_2  \shiftpre[\upsilon_1 \mid \upsilon_2] \rho'_1 ;
-      \rho'_2}
-    {\rho_1 \shiftpre[\upsilon_1] \rho'_1, \ \rho_2 \shiftpre[\upsilon_2] 
-      \rho'_2,\ \tau(\rho_1) = \perm(\rho_2)}
-  \]
-
-  \[
-    % 
-    % \inferL{\slab{(SH-sym)}}
-    % {\rho' \shiftpre[\perm^{-1}] \rho}
-    % {\rho \shiftpre[\perm] \rho'}
-    % % 
-    % \hspace{0.3cm}
-    % 
-    \inferL{\slab{(SH-tr)}}
-    {\rho \shiftpre[\perm'\circ \perm] \rho''}
-    {\rho \shiftpre[\perm] \rho',\ \rho' \shiftpre[\perm'], \rho''}
-    %
-    \hspace{0.3cm}
-    \inferL{\slab{(SH-eq)}}
-    {\rho' \shifteq[\perm] \rho}
-    {\rho \shiftpre[\perm] \rho' & \rho' \shiftpre[\perm^{-1}] \rho}
-  \]
-
-%  \noindent
-%  for $\perm_1 \mid \perm_2$ the pairing of two permutations,
-%  and similarly $\sqsubseteq^c_{\perm}$ is defined inductively by
-
-  \[
-    \inferL{\slab{(C-abs)}}
-    {\psi \equiv^c_{id} \psi'} 
-    {\psi \equiv^{a} \psi'} 
-    % 
-    \hspace{0.3cm}
-    % 
-    \inferL{\slab{(C-sh)}}
-    {\langle \alpha, \rho, \omega \rangle \equiv^c_{\perm} \langle \alpha, \rho', \omega \rangle} 
-    {\rho \shifteq[\perm] \rho'}
-    % 
-    \hspace{0.3cm}
-    % 
-    \inferL{\slab{(C-tr)}}
-    {\psi \equiv^c_{\perm' \circ \perm} \psi''}
-    {
-      {\psi \equiv^c_{\perm} \psi'} & 
-      {\psi' \equiv^c_{\perm'} \psi''}
-    }
-  \]
-\end{center}
-\caption{Inductive definition of $\shiftpre$ and $\equiv^c$, for $\perm_1 \mid \perm_2$ the pairing of two permutations.}
-\label{fi:ind}
-\end{figure}
-
-% \paragraph{Consistent $5$-tuple}.
-The alternative is to try to amend the notion of consistent $5$-tuple by adding some dependencies between productions and asking that they are ``preserved'' by the mapping.
-With the new definition I fear that it could be difficult distinguishing between dependencies arising from fusions and other, hence one should try to capture all dependencies, that will concretise in a deterministic event structure.
-Concretely, given $\rho = p_1 p_2 \ldots p_n$ it could be mapped to $E(\rho) = \langle \{ 1, \ldots, n\}, \vdash\rangle$ where $X \vdash i$ if there exists $\rho \equiv_\perm \rho'$ such that for all $j \in X$ it holds $j < \perm(i)$.
-
-\section{Proving invariance of independence with respect to shift}
-\newcommand{\si}{\ensuremath{\mathrel{\langle \mbox{\textsc{si}}\rangle}}}
-
-This is the way I (AC) propose to organize the proof that sequential independence is invariant with respect to shift.
-I copy and update some results of the previous part.
-Not everything is formalized completely.
-
-The structure of the proof should be applicable to any notion of \emph{sequential independence} for which we can prove the following facts:
-
-\begin{definition}[conditions on sequential independence]
-\label{def:si-conditions}
-\begin{enumerate}
-\item \label{cond:CR} Sequential independent steps can be switched.
-If two consecutive steps $\delta_i$ and $\delta_{i+1}$ of a derivation $\rho$ are SI (sequential independent, written $\delta_i \si \delta_{i+1}$), then there is a constructive way to obtain a derivation $\rho'$ differing from $\rho$ only for steps $\delta'_i$ and $\delta'_{i+1}$, such that $rule(\delta_i) = rule(\delta'_{i+1})$ and $rule(\delta_{i+1}) = rule(\delta'_{i})$.
-In this case we write $\rho \shiftdir[i] \rho'$.
-
-\item  \label{cond:CRdet} Switching is deterministic up to iso. If $\delta_i \si \delta_{i+1}$ in $\rho$ and $\rho \shiftdir[i] \rho'$, $\rho \shiftdir[i] \rho''$, then $\rho' \equiv \rho''$.
-
-\item \label{cond:si-symm} Sequential independence is preserved by immediate switch.
-If $\delta_i \si \delta_{i+1}$ in $\rho$ and $\rho \shiftdir[i] \rho'$, then $\delta'_i \si \delta'_{i+1}$ in $\rho'$.
-
-\item  \label{cond:si-si-iso} Switch is reversible. If $\rho \shiftdir[i] \rho'$ then $\rho' \shiftdir[i] \rho$.
-
-\item As a consequence of the previous points, if $\rho \shiftdir[i] \rho'$ and $\rho' \shiftdir[i] \rho''$ then $\rho \equiv \rho''$.
-
-\end{enumerate}
-\end{definition}
-%Given a derivation $\rho = \delta_1; \ldots ; \delta_i ; \delta_{i+1}; \ldots; \delta_n$, if $\delta_i \si \delta_{i+1}$, then
-\todo[inline]{I think that all conditions are satisfied by the standard definition of SI in DPO with linear rules and by our stronger notion of SI (uniqueness of the two mediating morphism \textbf{and} same property of the switched steps) in DPO with possibly non-right-linear rules.
-}
-
-\begin{proposition}[$\si$ satisfies all the conditions...]
-Let's call the relation of Def.~\ref{de:seq-ind} \emph{weak sequential independence}.
-Then it satisfies conditions \ref{cond:CR} and \ref{cond:CRdet} of Definition~\ref{def:si-conditions} (by the classical Church-Rosser Theorem and uniqueness of the mediating morphisms), but not the remaining ones.
-
-Let \emph{sequential independence} be defined as follows: $\delta_i \si \delta_{i+1}$ in $\rho$ iff they are weak sequential independent, and if $\rho'$ is obtained by $\rho$ switching  $\delta_i$ and $\delta_{i+1}$ (which is possible by condition \ref{cond:CR} and deterministic up to iso by condition \ref{cond:CRdet}) then $\delta'_i$ and $\delta'_{i+1}$ are weak sequential independent in $\rho'$.
-
- Then $\si$ satisfies all the conditions of Definition~\ref{def:si-conditions}.
- \end{proposition}
-
-\begin{proof}
-Conditions  \ref{cond:CR} and \ref{cond:CRdet} already hold for weak sequential independence.
-Condition \ref{cond:si-symm} holds by definition.
-\textbf{Condition \ref{cond:si-si-iso} should be proved explicitly, I fear...}
-\end{proof}
-
-\begin{definition}[Invariance under shift]
-\label{def:invariance} 
-A binary relation $R$ on consecutive steps of derivations is \emph{invariant under shift equivalence up to $n$} if whenever  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots \shiftdir[\upsilon_k] \rho'$ with  $\perm = \upsilon_1; \ldots; \upsilon_k$ and $k \leq n$ (thus $\rho \shifteq[\perm] \rho'$ with a proof made of at most  $n$ switches of steps) and $\perm(i+1) = \perm(i) + 1$, then $\delta_i \mathrel{R} \delta_{i+1}$ in $\rho$ if and only if $\delta'_{\perm(i)} \mathrel{R} \delta'_{\perm(i+1)}$ in $\rho'$.
-Relation $R$  is \emph{invariant under shift equivalence}, tout-court, if it is so up to any $n$.
-
-In words, two consecutive steps are related by $R$ in a derivation iff they are related by $R$ in any shift-equivalent derivation in which they are again consecutive.
-
-%$\delta_i \mathrel{R} \delta_{i+1}$ in $\rho$, $\rho \shifteq[\perm] \rho'$, and $\perm(i+1) = \perm(i) + 1$, then $\delta'_{\perm(i)} \mathrel{R} \delta'_{\perm(i+1)}$ in $\rho'$.
-
-\end{definition}
-
-\todo[inline]{The following is Lemma~\ref{le:no-useless-shifts} with a bound $n$ on the length of the proof that two derivations are shift equivalent.
-Also, it uses as assumption the fact that \si is invariant w.r.t.~shift up to $n-1$: the fact that $n-1$ is sufficient is exploited later in the proof of the main result.
-I think that it works, because the assumption is used only at the end, when the two reverse transpositions were already stripped, thus the length is $n-2$.}
-\begin{lemma}[no need of useless shifts]
-  \label{le:no-useless-shifts-bounded}
-  Given an integer $n$, let us assume that $\si$ is invariant under shift up to $n-1$.
-Let $\rho$, $\rho'$ be direct derivations such that  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots \shiftdir[\upsilon_k] \rho'$ with $k \leq n$, and
-  let $\sigma = \upsilon_1; \ldots; \upsilon_k$.
-   Then
-  $\rho = \rho_0 \shiftdir[\upsilon'_1] \rho_1 \ldots \shiftdir[\upsilon'_h ]
-  \rho'$ where $\sigma = \upsilon'_1; \ldots; \upsilon'_h$, $h \leq k$ and $\upsilon'_j \in \inv{\upsilon'_{j,h}}$ for $j \in \{1, \ldots,h\}$. 
-  %\todo{I understand that $\upsilon'_{j,h} = \upsilon'_j; \ldots; \upsilon'_h$}
-\end{lemma}
-
-\begin{proof}
-  Let 
-  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots \shiftdir[\upsilon_k ]
-  \rho'$.
-  %
-  We show that if some $\upsilon_j$ does not act on an inversion, i.e.,
-  $\upsilon_j \not\in \inv{\upsilon_{j,k}}$ then we can shorten the
-  proof of $\rho \shifteq[\sigma] \rho'$ of two steps. This 
-  allow us to conclude that we can reduce the original proof to one which is not longer and only acting
-  on inversions, as desired.
-
-  The key observation is that, if
-  $\upsilon_j \not\in \inv{\sigma_{j,k}}$ then, intuitively, the ``same
-  exchange'' must be performed in the reverse direction by some
-  $\upsilon_s$, with $s>j$.  Formally, if $\upsilon_j = \transp{i}$ and
-  $(i,i+1)\not\in\inv{\upsilon_{i,k}}$ then there exists $s>j$ such that
-  $\upsilon_{j,s-1}(i) = \upsilon_{j,s-1}(i+1)+1$ and
-  $\upsilon_s = \transp{\upsilon_{j,s-1}(i+1)}$. Among all the pairs
-  $j, s$ of this kind, take one with minimal $s-j$. This means that in
-  the middle all transpositions are inversions of $\upsilon_{j+1,s-1}$.
-
-  By Lemma~\ref{le:perm}, $\upsilon_j$ and $\upsilon_s$ can be
-  stripped, i.e., $\upsilon_{j,s} = \upsilon_{j+1,s-1}$. Moreover,
-  again by Lemma~\ref{le:perm},
-  $\upsilon_{i+1}, \ldots, \upsilon_{s-1}$ perform exchanges that were
-  already done in the original proof, and thus, since independence is
-  invariant under shift equivalence up to $n-1$, they are allowed. 
-  Moreover, since by condition \ref{cond:CRdet} of Definition~\ref{def:si-conditions} the result of switching is uniquely
-  determined (up to iso), the resulting derivation is the same as
-  before, hence we can strip $\upsilon_{j}$ and $\upsilon_{s}$,
-  and conclude.
-\end{proof}
-
-\todo[inline]{The next one is Lemma~\ref{le:seq-ind-glob2}, again bounded w.r.t.~ the length of the proof of shift equivalence. \textbf{Note:} It is not used in the following.}
-
-Then we can prove that whenever $\rho \shifteq[\perm] \rho'$, each
-decomposition of $\perm$ in terms of inversions leads to a valid
-valid proof of the shift equivalence  of $\rho$ and $\rho$.
-
-\begin{lemma}[independence is global/2]
-  \label{le:seq-ind-glob2-new}
- Given an integer $n$, let us assume that $\si$ is invariant under shift up to $n$.  Let $\rho$, $\rho'$ be direct derivations such that $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots
-  \shiftdir[\upsilon_k] \rho'$, with $0 < k \leq n$,  
-   $\sigma = \upsilon_1; \ldots; \upsilon_k$  and  $\upsilon_j \in \inv{\upsilon_{j,k}}$ for $j \in \{1, \ldots,k\}$. 
-  Let
-  $\perm = \transp{i}; \perm'$ where $(i,i+1) \in \inv{\perm}$. Then
-  there exists $\rho''$ such that
-  $\rho \shifteq[\transp{i}] \rho'' \shifteq[\perm']
-  \rho'$.
-\end{lemma}
-
-\begin{proof}
-%  Let
-%  $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots
-%  \shiftdir[\upsilon_n] \rho'$ where $\sigma = \upsilon_1; \ldots; \upsilon_n$ and $\upsilon_j \in \inv{\upsilon_{j,n}}$ for $j \in \{1, \ldots,n\}$, be the decomposition
-%  provided by Lemma~\ref{le:no-useless-shifts}.
- % 
-  We know that steps corresponding to $i$ and $i+1$ are exchanged at
-  some point, namely there is $j$ such that
-  $\upsilon_j =
-  \transp{\upsilon_{1,j-1}(i)}[\upsilon_{1,j-1}(i+1)]$. Since $\si$ is invariant up to $n$, the steps $i$ and $i+1$ are independent
-  already at the beginning and thus we can exchange them first.
-  More precisely, 
-  \begin{center}
-    $\rho \shiftdir_{\transp{i}} \rho'' \shiftdir_{\upsilon_{1,j-1}}
-    \rho_j \shiftdir_{\upsilon_{j+1,k}} \rho'$.
-  \end{center}
-  This can be proved by induction on $j$.
-\end{proof}
-
-The following main lemma needs a proof.
-
-\begin{lemma}[Invariance of $\si$ under immediate shift]
-\label{le:invariance-immediate}
-\begin{enumerate}
-%\item Let $\rho = \delta_1 ; \delta_2 ; \delta_3 $ with $\delta_2 \si \delta_3$, suppose that $\rho \shiftdir[(2,3)] \rho' = \delta_1 ; \delta'_3 ; \delta'_2$,  that $\delta_1 \si \delta'_3$ in $\rho'$, and that $\rho' \shiftdir[(1,2)] \rho'' =  \delta''_3 ; \delta'_1 ; \delta'_2$.
-%Then $\delta_1 \si \delta_2$ in $\rho$ if and only if  $\delta'_1 \si \delta'_2$ in $\rho''$.
-
-\item Let $\rho = \delta_1 ; \delta_2 ; \delta_3 $ be a derivation such that $\rho \shiftdir[(2,3)] \rho'  \shiftdir[(1,2)] \rho''$,  with $\delta_2 \si \delta_3$ in $\rho$, $\rho' = \delta_1 ; \delta'_3 ; \delta'_2$,   $\delta_1 \si \delta'_3$ in $\rho'$, and that $\rho'' =  \delta''_3 ; \delta'_1 ; \delta'_2$.
-Then $\delta_1 \si \delta_2$ in $\rho$ if and only if  $\delta'_1 \si \delta'_2$ in $\rho''$.
-
-The situation can be represented as in the following diagram, where each transposition is performed, downwards, only if the two starting steps are sequential independent.
-The proposition states that the steps \cycl{1} are sequential independent if and only if so are the steps \cycl{2}.
-For brevity, we abbreviate this statement to $SI(\cycl{1}) \iff SI(\cycl{2})$.
-
-%\center{\xymatrix@C=2pc@R=1pc{
-% \rho  \ar@{~>}[d]^{sh}_{(2,3)}  \ar@{}[r]|{=} & \rho_1 \ar@{-}[d] \ar@{}[r]|{;} & \delta_1 \ar@{-}[d]  \ar@{}[r]|{;} & \delta_2 \ar@{-}[dr]  \ar@{}[r]|{;} & \delta_3 \ar@{-}[dl]  \ar@{}[r]|{;} &\rho_2 \ar@{-}[d] \\
-%\rho'  \ar@{~>}[d]^{sh}_{(1,2)}  \ar@{}[r]|{=} &  \rho_1 \ar@{-}[d]  \ar@{}[r]|{;} & \delta_1 \ar@{-}[dr]  \ar@{}[r]|{;} & \delta'_3 \ar@{-}[dl]  \ar@{}[r]|{;} & \delta'_2 \ar@{-}[d]  \ar@{}[r]|{;} &\rho_2 \ar@{-}[d] \\
-%\rho''  \ar@{}[r]|{=} &   \rho_1 \ar@{}[r]|{;} & \delta''_3 \ar@{}[r]|{;} & \delta'_1 \ar@{}[r]|{;} & \delta'_2 \ar@{}[r]|{;} &\rho_2\\
-%}}
-
-$$\xymatrix@C=2pc@R=1pc{
- \rho  \ar@{~>}[d]^{sh}_{(2,3)}  \ar@{}[r]|{=} &  \delta_1 \ar@{-}[d]  \ar@{}[r]|{;}  \ar@{-}@/^3ex/[r]|{\cycl{1}} & \delta_2 \ar@{-}[dr]  \ar@{}[r]|{;} & \delta_3 \ar@{-}[dl] \\
-\rho'  \ar@{~>}[d]^{sh}_{(1,2)}  \ar@{}[r]|{=} &   \delta_1 \ar@{-}[dr]  \ar@{}[r]|{;} & \delta'_3 \ar@{-}[dl]  \ar@{}[r]|{;} & \delta'_2 \ar@{-}[d]\\
-\rho''  \ar@{}[r]|{=} &    \delta''_3 \ar@{}[r]|{;} & \delta'_1 \ar@{-}@/_3ex/[r]|{\cycl{2}} \ar@{}[r]|{;} & \delta'_2  \\
-}$$
-
-\item  Also a symmetric statement holds, for which we show only the graphical representation. Again, we show that $SI(\cycl{1}) \iff SI(\cycl{2})$.
-% the steps \cycl{1} are sequential independent if and only if so are the steps \cycl{2}.
-
-$$\xymatrix@C=2pc@R=1pc{
- \rho  \ar@{~>}[d]^{sh}_{(1,2)}  \ar@{}[r]|{=} &
-   \delta_1 \ar@{-}[dr]  \ar@{}[r]|{;}  &
-    \delta_2 \ar@{-}[dl]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
-    \delta_3 \ar@{-}[d] \\
-\rho'  \ar@{~>}[d]^{sh}_{(2,3)}  \ar@{}[r]|{=} &
-   \delta'_2 \ar@{-}[d]  \ar@{}[r]|{;} &
-    \delta'_1 \ar@{-}[dr]  \ar@{}[r]|{;} &
-     \delta_3 \ar@{-}[dl]\\
-\rho''  \ar@{}[r]|{=} & 
-   \delta'_2 \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
-    \delta'_3  \ar@{}[r]|{;} &
-     \delta''_1  \\
-}$$
-
-%
-%Symmetrically, let $\rho = \rho_1 ; \delta_1 ; \delta_2 ; \delta_3 ; \rho_2$ with $\delta_1 \si \delta_2$ in $\rho$, suppose that $\rho \shiftdir[(1,2)] \rho' = \rho_1 ; \delta'_2 ; \delta'_1 ; \delta_3 ;\rho_2$,  that $\delta'_1 \si \delta_3$ in $\rho'$, and that $\rho' \shiftdir[(2,3)] \rho'' = \rho_1 ; \delta'_2 ; \delta'_3 ; \delta''_1 ;\rho_2$.
-%Then $\delta_2 \si \delta_3$ in $\rho$ if and only if  $\delta'_2 \si \delta'_3$ in $\rho''$. 
-\end{enumerate}
-%\begin{enumerate}
-%\item Let $\rho = \rho_1 ; \delta_1 ; \delta_2 ; \delta_3 ; \rho_2$ with $\delta_2 \si \delta_3$ in $\rho$, suppose that $\rho \shiftdir[(2,3)] \rho' = \rho_1 ; \delta_1 ; \delta'_3 ; \delta'_2 ;\rho_2$,  that $\delta_1 \si \delta'_3$ in $\rho'$, and that $\rho' \shiftdir[(1,2)] \rho'' = \rho_1 ; \delta''_3 ; \delta'_1 ; \delta'_2 ;\rho_2$.
-%Then $\delta_1 \si \delta_2$ in $\rho$ if and only if  $\delta'_1 \si \delta'_2$ in $\rho''$. 
-%
-%The following A graphical representation The situation can 
-%\item  Symmetrically, let $\rho = \rho_1 ; \delta_1 ; \delta_2 ; \delta_3 ; \rho_2$ with $\delta_1 \si \delta_2$ in $\rho$, suppose that $\rho \shiftdir[(1,2)] \rho' = \rho_1 ; \delta'_2 ; \delta'_1 ; \delta_3 ;\rho_2$,  that $\delta'_1 \si \delta_3$ in $\rho'$, and that $\rho' \shiftdir[(2,3)] \rho'' = \rho_1 ; \delta'_2 ; \delta'_3 ; \delta''_1 ;\rho_2$.
-%Then $\delta_2 \si \delta_3$ in $\rho$ if and only if  $\delta'_2 \si \delta'_3$ in $\rho''$. 
-%\end{enumerate}
-\end{lemma}
-\begin{proof}
-\textbf{To be done...}
-
-\end{proof}
-
-We are now able to state and prove the main result.
-
-\begin{theorem}[Invariance of $\si$]
-Relation $\si$ is invariant under shift equivalence, as for Definition~\ref{def:invariance}.
-\end{theorem}
-
-\begin{proof}
-Let $\rho \shifteq[\perm] \rho'$ be two shift equivalent derivations and let $1 \leq i <  |\rho|$ such that $\perm(i+1) = \perm(i) + 1$.
-We have to show that $\delta_i \si \delta_{i+1}$ in $\rho$  iff  $\delta_{\perm(i)} \si \delta_{\perm(i+1)}$ in $\rho'$.
-
-Since $\rho \shifteq[\perm] \rho'$, we have $\rho = \rho_0 \shiftdir[\upsilon_1] \rho_1 \ldots \shiftdir[\upsilon_n] \rho'$, with $\sigma = \upsilon_1; \ldots; \upsilon_n$.
-We proceed by induction on $n$.
-If $n = 0$, then $\perm = id$ and the statement trivially holds.
-Now we assume that the statement holds for each $k \leq n$, and  we show that it holds for $n+1$.
-Let  $\sigma'$ be defined as $\sigma' =  \upsilon_1; \ldots; \upsilon_n$, thus  $\sigma = \sigma' ; \upsilon_{n+1}$.
-We proceed by case analysis on the last adjacent transposition $\upsilon_{n+1} = (z, z+1)$.
-
-\begin{description} 
-\item [{[$z+1 < \sigma'(i)$ or $\sigma'(i+1) < z$]}] In this case the last transposition does not affect the steps $\delta^n_{\sigma'(i)}$ and $\delta^n_{\sigma'(i+1)}$  of $\rho_n$, as depicted here:
-
-$$\xymatrix@C=2pc@R=2pc{
- \rho  \ar@{~>}[d]^{sh}^(.9){*} \ar@{}[r]|{=} &
-   \cdots   \ar@{}[r]|{;}  &
-    \delta_i \ar@{--}@/_2ex/[d]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
-    \delta_{i+1} \ar@{--}@/^1ex/[d]  \ar@{}[r]|{;}  & \cdots\\
-\rho_n  \ar@{~>}[d]^{sh}_{\upsilon_{n+1}}  \ar@{}[r]|{=} &
-   \cdots   \ar@{}[r]|{;}  &
-    \delta^n_{\sigma'(i)} \ar@{-}[d]  \ar@{}[r]|{;}  \ar@{-}@/_3ex/[r]|{\cycl{3}}  &
-   \delta^n_{\sigma'(i+1)} \ar@{-}[d]  \ar@{}[r]|{;} &
-    \cdots\\
-\rho'  \ar@{}[r]|{=} & 
-    \cdots   \ar@{}[r]|{;}  &
-     \delta'_{\sigma(i)} \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
-    \delta'_{\sigma(i+1)}  \ar@{}[r]|{;} &
-     \cdots  \\
-}$$
-
-\todo[inline]{But is it obvious that if two steps keep their position the remain shift-equivalent? Maybe this is another condition...}
-
-Therefore clearly $SI(\cycl{2}) \iff SI(\cycl{3})$.
-Furthermore $SI(\cycl{1}) \iff SI(\cycl{3})$  by induction hypothesis, because $\rho  \stackrel{sh\ *}{\rightsquigarrow} \rho_n$  has length $n$, and thus we conclude $SI(\cycl{1}) \iff SI(\cycl{2})$.
-
-\item  [{[$z = \sigma'(i+1)$ and $\sigma'(i) = z+1$]}]  In this case the last transposition switches the steps $\delta^n_{\sigma'(i+1)}$ and $\delta^n_{\sigma'(i)}$  of $\rho_n$, as depicted here:
-
-$$\xymatrix@C=2pc@R=2pc{
- \rho  \ar@{~>}[d]^{sh}^(.9){*} \ar@{}[r]|{=} &
-   \cdots   \ar@{}[r]|{;}  &
-    \delta_i \ar@{--}[dr]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
-    \delta_{i+1} \ar@{--}[dl]  \ar@{}[r]|{;}  & \cdots\\
-\rho_n  \ar@{~>}[d]^{sh}_{\upsilon_{n+1}}  \ar@{}[r]|{=} &
-   \cdots   \ar@{}[r]|{;}  &
-    \delta^n_{\sigma'(i+1)} \ar@{-}[dr]  \ar@{}[r]|{;}  \ar@{-}@/^2ex/[r]|{\cycl{3}}  &
-   \delta^n_{\sigma'(i)} \ar@{-}[dl]  \ar@{}[r]|{;} &
-    \cdots\\
-\rho'  \ar@{}[r]|{=} & 
-    \cdots   \ar@{}[r]|{;}  &
-     \delta'_{\sigma(i)} \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
-    \delta'_{\sigma(i+1)}  \ar@{}[r]|{;} &
-     \cdots  \\
-}$$
-
-Clearly we have $SI(\cycl{3})$ because the two steps are switched, and thus also $SI(\cycl{2})$ by  conditions  \ref{cond:si-symm} and \ref{cond:si-si-iso} of Definition~\ref{def:si-conditions}.
-Furthermore, as evident from the drawing the steps $\delta_i$ and $\delta_{i+1}$ of $\rho$ must have been switched by a transposition $\upsilon_j = (v, v+1)$ with $1 \leq j \leq n$.
-Therefore we have that steps $\delta^{j-1}_v$ and $\delta^{j-1}_{v+1}$  are sequential independent in $\rho^{j-1}$, and by induction hypothesis  (because $j \leq n$) we infer $SI(\cycl{1})$, allowing us to conclude that $SI(\cycl{1}) \iff SI(\cycl{2})$.
-
-\item  [{[$z+1 = \sigma'(i+1)$, thus $z = \sigma(i+1)$]}]
-
-% and $z =\sigma'(v) for $v \gt i+1
-In this case the transposition $\upsilon_{n+1}$ affects one of the steps \cycl{2} but not both, as summarized in the drawing.
-$$\xymatrix@C=2pc@R=2pc{
- \rho  \ar@{~>}[d]^{sh}^(.9){*} \ar@{}[r]|{=} &
-   \cdots   \ar@{}[r]|{;}  &
-    \delta_i \ar@{--}@/_2ex/[d]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
-    \delta_{i+1} \ar@{--}@/^1ex/[dr]  \ar@{}[r]|{;}  & \cdots\\
-\rho_n  \ar@{~>}[d]^{sh}_{\upsilon_{n+1}}  \ar@{}[r]|{=} &
-   \cdots   \ar@{}[r]|{;}  &
-    \delta^n_{\sigma'(i)} \ar@{-}[d]  \ar@{}[r]|{;}   &
-   \delta^n_z \ar@{-}[dr]  \ar@{}[r]|{;} &
-   \delta^n_{\sigma'(i+1)} \ar@{-}[dl]  \ar@{}[r]|{;} &
-    \cdots\\
-\rho'  \ar@{}[r]|{=} & 
-    \cdots   \ar@{}[r]|{;}  &
-     \delta'_{\sigma(i)} \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
-    \delta'_{\sigma(i+1)}  \ar@{}[r]|{;} &
-    \delta'_{z+1}  \ar@{}[r]|{;} &
-     \cdots  \\
-}$$
-
-There are two subcases, depending on whether step $\delta_z^n$ originates from a step in $\rho$ after $\delta_{i+1}$ or before $\delta_i$. In the first case we have:  
-$$\xymatrix@C=2pc@R=2pc{
- \rho  \ar@{~>}[d]^{sh}^(.9){*} \ar@{}[r]|{=} &
-   \cdots   \ar@{}[r]|{;}  &
-    \delta_i \ar@{--}@/_2ex/[d]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
-   \delta_{i+1}  \ar@{--}@/^1ex/[dr]  \ar@{}[r]|{\cdots}  &
-    \delta_{{\sigma'}^{-1}(z)} \ar@{--}@/_1ex/[dl]  \ar@{}[r]|{;}  & \cdots\\
-\rho_n  \ar@{~>}[d]^{sh}_{\upsilon_{n+1}}  \ar@{}[r]|{=} &
-   \cdots   \ar@{}[r]|{;}  &
-    \delta^n_{\sigma'(i)} \ar@{-}[d]  \ar@{}[r]|{;}   &
-   \delta^n_z \ar@{-}[dr]  \ar@{}[r]|{;} &
-   \delta^n_{\sigma'(i+1)} \ar@{-}[dl]  \ar@{}[r]|{;} &
-    \cdots\\
-\rho'  \ar@{}[r]|{=} & 
-    \cdots   \ar@{}[r]|{;}  &
-     \delta'_{\sigma(i)} \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
-    \delta'_{\sigma(i+1)}  \ar@{}[r]|{;} &
-    \delta'_{z+1}  \ar@{}[r]|{;} &
-     \cdots  \\
-}$$
-
-As evident form the drawing, in this case there are certainly some useless transpositions.
-Thus by Lemma~\ref{le:no-useless-shifts-bounded} (used on proofs of length at most $n+1$, with the induction hypothesis up to length $n$) there exists an equivalent proof of $\rho \shifteq[\perm] \rho'$  of length at most $n-1$, thus we can conclude by inductive hypothesis.
-
-The second case is depicted as follows:
-
-$$\xymatrix@C=2pc@R=2pc{
- \rho  \ar@{~>}[d]^{sh}^(.9){*} \ar@{}[r]|{=} &
-   \delta_{{\sigma'}^{-1}}(z)  \ar@{--}@/^1ex/[drr]   \ar@{}[r]|{\cdots}  &
-    \delta_i \ar@{--}@/_2ex/[d]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
-    \delta_{i+1} \ar@{--}@/^1ex/[dr]  \ar@{}[r]|{;}  & \cdots\\
-\rho_n  \ar@{~>}[d]^{sh}_{\upsilon_{n+1}}  \ar@{}[r]|{=} &
-   \cdots   \ar@{}[r]|{;}  &
-    \delta^n_{\sigma'(i)} \ar@{-}[d]  \ar@{}[r]|{;}   &
-   \delta^n_z \ar@{-}[dr]  \ar@{}[r]|{;} &
-   \delta^n_{\sigma'(i+1)} \ar@{-}[dl]  \ar@{}[r]|{;} &
-    \cdots\\
-\rho'  \ar@{}[r]|{=} & 
-    \cdots   \ar@{}[r]|{;}  &
-     \delta'_{\sigma(i)} \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
-    \delta'_{\sigma(i+1)}  \ar@{}[r]|{;} &
-    \delta'_{z+1}  \ar@{}[r]|{;} &
-     \cdots  \\
-}$$
-
-We see that two steps from which $\delta^n_{\sigma'(i)}$ and $\delta^n_z$ originate were switched by a transposition $\upsilon_j$ with $1 \leq j \leq n$ therefore by induction hypothesis we infer that  $\delta^n_{\sigma'(i)}$ and $\delta^n_z$ are sequentially independent.
-Thus we can modify the proof as follows, switching such steps twice:
-
-$$\xymatrix@C=2pc@R=2pc{
- \rho  \ar@{~>}[d]^{sh}^(.9){*} \ar@{}[r]|{=} &
-   \delta_{{\sigma'}^{-1}}(z)  \ar@{--}@/^1ex/[drr]   \ar@{}[r]|{\cdots}  &
-    \delta_i \ar@{--}@/_2ex/[d]  \ar@{}[r]|{;} \ar@{-}@/^3ex/[r]|{\cycl{1}} &
-    \delta_{i+1} \ar@{--}@/^1ex/[dr]  \ar@{}[r]|{;}  & \cdots\\
-\rho_n  \ar@{~>}[d]^{sh}_{\upsilon_{n+1}}  \ar@{}[r]|{=} &
-   \cdots   \ar@{}[r]|{;}  &
-    \delta^n_{\sigma'(i)} \ar@{-}[dr]  \ar@{}[r]|{;}   &
-   \delta^n_z \ar@{-}[dl]  \ar@{}[r]|{;} &
-   \delta^n_{\sigma'(i+1)} \ar@{-}[d]  \ar@{}[r]|{;} &
-    \cdots\\
-  \rho_{n+1}  \ar@{~>}[d]^{sh}_{\upsilon_{n+2}}  \ar@{}[r]|{=} &
-   \cdots   \ar@{}[r]|{;}  &
-    \delta^{n+1}_{z-1} \ar@{-}[dr]  \ar@{}[r]|{;}   &
-   \delta^{n+1}_{\sigma'(i)+1}  \ar@{-}[dl]  \ar@{}[r]|{;}   \ar@{-}@/^3ex/[r]|{\cycl{3}} &
-   \delta^{n+1}_{\sigma'(i+1)} \ar@{-}[d]  \ar@{}[r]|{;} &
-    \cdots\\
-    \rho_{n+2}  \ar@{~>}[d]^{sh}_{\upsilon_{n+3}}  \ar@{}[r]|{=} &
-   \cdots   \ar@{}[r]|{;}  &
-    \delta^{n+2}_{\sigma'(i)} \ar@{-}[d]  \ar@{}[r]|{;}   &
-   \delta^{n+2}_z \ar@{-}[dr]  \ar@{}[r]|{;} &
-   \delta^{n+2}_{\sigma'(i+1)} \ar@{-}[dl]  \ar@{}[r]|{;} &
-    \cdots\\  
-\rho'  \ar@{}[r]|{=} & 
-    \cdots   \ar@{}[r]|{;}  &
-     \delta'_{\sigma(i)} \ar@{}[r]|{;} \ar@{-}@/_3ex/[r]|{\cycl{2}} &
-    \delta'_{\sigma(i+1)}  \ar@{}[r]|{;} &
-    \delta'_{z+1}  \ar@{}[r]|{;} &
-     \cdots  \\
-}$$
-
-Now we can conclude observing that $SI(\cycl{2}) \iff SI(\cycl{3})$ by point 2 of Lemma~\ref{le:invariance-immediate}, and that $SI(\cycl{1}) \iff SI(\cycl{3})$ can be proved by applying the first subcase of this step of the proof.
-
-\todo[inline]{Lemma~\ref{le:invariance-immediate} considera solo derivazioni di lunghezza 3. Anche qui serve un lemma che garantisce che vale anche in un contesto piu' ampio.}
-
-\item   [{[$z = \sigma'(i)$, thus $z+1 = \sigma(i)$]}]  
-This case is completely symmetrical to the previous one, exploiting in the last subcase point 1 of Lemma~\ref{le:invariance-immediate}.
-
-\end{description}
-
-\end{proof}
-
-\end{document}
-
 %%% Local Variables:

### 2023-09-12 fusione.tex
filler

 %(query-replace-regexp "\\\\sqsubseteq^{sh}_{\\([^}]*\\)}" "\\\\shiftpre[\\1]")
% --- LNCS ---'
\documentclass{llncs}

\usepackage{hyperref}
\usepackage[textsize=tiny]{todonotes}
\usepackage{etex}

\usepackage[all]{xy}
\SelectTips{cm}{}
% derivations and labels
\usepackage{proof}
\newcommand{\lab}[1]{\ensuremath{\mathsf{{#1}}}}
\newcommand{\slab}[1]{\ensuremath{\scriptstyle{\mathsf{{#1}}}}}

% ``boxed'' \infer command
\newcommand{\binfer}[3][]{
  \mbox{\infer[#1]{#2}{#3}}}

% Command for labels on the left side of the rule
%       \inferL{<name>}{<post>}{<pre>}
% generates:
%             <pre>
%      <name> ------
%             <post>
%
\newlength{\myheight}
\newcommand{\inferL}[3]
  {\settoheight{\myheight}{\mbox{${#2}$}}
   \raisebox{\myheight}{{#1}}
   \makebox[1mm]{}
   \mbox{\infer{#2}{#3}}
}

\usepackage{amssymb,graphicx,epsfig,color}
%\usepackage[scriptsize]{subfigure}
\usepackage{subcaption}
\usepackage{wrapfig}

% re-stating 
%\usepackage{thm-restate}

% showing labels
%\usepackage[inline]{showlabels}

\usepackage{pgf}
\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri,fit,positioning}
\tikzstyle{node}=[circle, draw=black, minimum size=1mm]
\tikzstyle{trans}=[font=\scriptsize]
\tikzstyle{lab}=[font=\small]

\newcommand{\pgfBox}{
  \begin{pgfonlayer}{background} 
    \fill[blue!2,thick,draw=black!50,rounded corners,inner sep=3mm] ([xshift=-1.5pt,yshift=-1.5pt]current bounding box.south west) rectangle ([xshift=1.5pt,yshift=1.5pt]current bounding box.north east);
  \end{pgfonlayer}
}

\newcommand{\Rrel}[1]   {\stackrel{{#1}}{\Longrightarrow}}
\newcommand{\oa}{\overline a}
\newcommand{\ob}{\overline b}
\newcommand{\oc}{\overline c}
\newcommand{\od}{\overline d}
\newcommand{\nil}{{\tt 0}}
\newcommand{\rec}{\emph{rec}}
\newcommand{\fn}[1]{{\mathtt{fn}}(#1)}
%\usepackage{latexsym}
\usepackage{stmaryrd}
\def\encodep#1{\llfloor#1\rrfloor}

\newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}

\newcommand{\dpo}{\textsc{dpo}}

% base classes of categories for adhesive and quasi adhesive case
\newcommand{\bAdh}{\ensuremath{\mathbb{B}}}
\newcommand{\bQAdh}{\ensuremath{\mathbb{QB}}}

%from pawel
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
%2 righe tolte da Fabio
\usepackage{amssymb}
%\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{xspace}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage{float}
\usepackage{fancybox}

\usepackage{cleveref}

\spnewtheorem*{notation}{Notation}{\bfseries}{\rmfamily}

%%%%%%%% MATHEMATICAL NOTATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%symbol for natural numbers
\newcommand{\nat}{\ensuremath{\mathbb{N}}}

% finite subset
\newcommand{\sfin}{\ensuremath{\subseteq_{\mathit{fin}}}}

% flattening of a multiset
\newcommand{\flt}[1]{\ensuremath{[\![{#1}]\!]}}

% compact elements
\newcommand{\compact}[1]{\ensuremath{\mathop{\mathsf{K}({#1})}}}

% principal ideal
\newcommand{\principal}[1]{\ensuremath{\mathop{\downarrow\!{#1}}}}

% ideal completion
\newcommand{\ideal}[1]{\ensuremath{\mathsf{Idl}({#1})}}

% complete prime elements
\newcommand{\pr}[1]{\ensuremath{\mathop{\mathit{pr}({#1})}}}
\newcommand{\wpr}[1]{\ensuremath{\mathop{\mathit{wpr}({#1})}}}

% irreducible elements
\newcommand{\ir}[1]{\ensuremath{\mathop{\mathit{ir}({#1})}}}

% difference of irreducible elements
\newcommand{\diff}[2]{\ensuremath{\delta({#1},{#2})}}

% immediate precedence

% abbreviation for event structure
% \newcommand{\esabbr}{event structure}
\newcommand{\esabbr}{\textsc{es}}
\newcommand{\esnabbr}{\textsc{esnb}}
\newcommand{\esnmabbr}{\textsc{esn}}
\newcommand{\eseqabbr}{\textsc{epes}}

% predecessor of an irreducible
\newcommand{\pred}[1]{\ensuremath{\mathit{p}({#1})}}

% irreducible elements in es domains
\newcommand{\esir}[2]{\ensuremath{\langle{#1}, {#2}\rangle}}

% equivalence classes [of irreducibles]
\newcommand{\eqclass}[2][]{\ensuremath{[{#2}]_{\scriptscriptstyle {#1}}}}
% union of the equivalence classes of the elements in a set
\newcommand{\eqclasscup}[2]{\ensuremath{{#2}_{\scriptscriptstyle {#1}}}}

\newcommand{\eqclassir}[1]{\ensuremath{\eqclass[\leftrightarrow^*]{#1}}}

% quotient of set wrt a relation
\newcommand{\quotient}[2]{\ensuremath{{#1}_{\scriptscriptstyle {#2}}}}

% category of event structures 
\newcommand{\es}{\ensuremath{\mathsf{ES}}}
% category of stable event structures 
\newcommand{\ses}{\ensuremath{\mathsf{sES}}}
% category of prime event structures 
\newcommand{\pes}{\ensuremath{\mathsf{pES}}}
% category of prime event structures with equivalence
\newcommand{\epes}{\ensuremath{\mathsf{epES}}}

% category of connected event structures 
\newcommand{\ces}{\ensuremath{\mathsf{cES}}}

% category of weak prime algebraic domains domains 
\newcommand{\WDom}{\ensuremath{\mathsf{wDom}}}
% category of domains
\newcommand{\Dom}{\ensuremath{\mathsf{Dom}}}
% category of prime algebraic domains
\newcommand{\PDom}{\ensuremath{\mathsf{pDom}}}

%%%%% NON BINARY CONFLICT

% category of event structures 
\newcommand{\esn}{\ensuremath{\mathsf{ES_{nb}}}}
% category of stable event structures 
\newcommand{\sesn}{\ensuremath{\mathsf{sES_n}}}

% category of connected event structures 
\newcommand{\cesn}{\ensuremath{\mathsf{cES_{nb}}}}

% category of prime event structures 
\newcommand{\pesn}{\ensuremath{\mathsf{pES_n}}}

% category of fusion domains 
\newcommand{\WDomb}{\ensuremath{\mathsf{wDom_b}}}
% category of domains
\newcommand{\Domb}{\ensuremath{\mathsf{Dom_b}}}
% category of prime algebraic domains
\newcommand{\PDomb}{\ensuremath{\mathsf{pDom_b}}}

%%%%% END NON BINARY CONFLICT

% slice category
\newcommand{\slice}[2]{\ensuremath{({#1} \downarrow {#2})}}

% event structure for a domain
\newcommand{\zev}[0]{\ensuremath{\mathcal{E}}}
\newcommand{\ev}[1]{\ensuremath{\zev({#1})}}

% from general to connected event structures
\newcommand{\zconnes}[0]{\ensuremath{\mathcal{C}}}
\newcommand{\connes}[1]{\ensuremath{\zconnes({#1})}}
% and inclusion
\newcommand{\zinces}[0]{\ensuremath{\mathcal{I}}}
\newcommand{\inces}[1]{\ensuremath{\zinces({#1})}}

% stable version
\newcommand{\zsev}[0]{\ensuremath{\mathcal{E}_S}}
\newcommand{\sev}[1]{\ensuremath{\zsev({#1})}}

% with equivalence
\newcommand{\zeveq}[0]{\ensuremath{\mathcal{E}_{eq}}}
\newcommand{\eveq}[1]{\ensuremath{\zeveq({#1})}}

% es with equivalence to es and vice
\newcommand{\zfuse}[0]{\ensuremath{\mathcal{M}}}
\newcommand{\fuse}[1]{\ensuremath{\zfuse({#1})}}
\newcommand{\zunf}[0]{\ensuremath{\zunf}}
\newcommand{\unf}[1]{\ensuremath{\mathcal{U}({#1})}}

% Winskel/Droste version
\newcommand{\zevwd}[0]{\ensuremath{\mathcal{E}_{wd}}}
\newcommand{\evwd}[1]{\ensuremath{\zevwd({#1})}}

% configurations of an event structure
\newcommand{\conf}[1]{\ensuremath{\mathit{Conf}({#1})}}
% finite configurations
\newcommand{\conff}[1]{\ensuremath{\mathit{Conf_F}({#1})}}

% product of the sets of minimal enablinsg
\newcommand{\pmin}[1]{\ensuremath{U_{#1}}}

% connectectedness of minimal enablinsg
\newcommand{\conn}[1]{\ensuremath{\stackrel{#1}{\frown}}}

% domain for an event structure or graph grammar
\newcommand{\zdom}[0]{\ensuremath{\mathcal{D}}}
\newcommand{\dom}[1]{\ensuremath{\zdom({#1})}}

\newcommand{\zdomeq}[0]{\ensuremath{\mathcal{D}_{eq}}}
\newcommand{\domeq}[1]{\ensuremath{\zdomeq({#1})}}

% partial order for a graph grammar
\newcommand{\poset}[1]{\ensuremath{\mathcal{P}({#1})}}

% stable version
\newcommand{\pdom}[1]{\ensuremath{\mathcal{D}_S({#1})}}
\newcommand{\ppdom}[0]{\ensuremath{\mathcal{D}_S}}

% powerset
\newcommand{\Pow}[1]{\ensuremath{\mathbf{2}^{#1}}}

% powerset of finite subsets
\newcommand{\Powfin}[1]{\ensuremath{\mathbf{2}_\mathit{fin}^{#1}}}

% powerset of subsets of cardinality <= 1
\newcommand{\Powone}[1]{\ensuremath{\mathbf{2}_1^{#1}}}

% integer interval
\newcommand{\interval}[2][1]{\ensuremath{[{#1},{#2}]}}

% domain interval
\newcommand{\dint}[2]{\ensuremath{[{#1},{#2}]}}

% set of intervals
\newcommand{\IntSet}[1]{\ensuremath{\mathop{\mathit{Int}({#1})}}}

% intervals to irreducibles and vice
\newcommand{\inir}{\ensuremath{\mathop{\mathit{\zeta}}}}
\newcommand{\irin}{\ensuremath{\mathop{\mathit{\iota}}}}

% permutations
\newcommand{\perm}{\sigma}

% causes
\newcommand{\causes}[1]{\ensuremath{\lfloor {#1})}}

%%% GRAPH GRAMMARS

\newcommand{\Abs}[1]{\ensuremath{\mathsf{Abs}({#1})}}
\newcommand{\tr}[1]{\ensuremath{\mathsf{Tr}({#1})}}
% fusion safe traces
\newcommand{\trs}[1]{\ensuremath{\mathsf{Tr}_s({#1})}}
%\newcommand{\graph}{\ensuremath{\mathsf{Graph}}}
\newcommand{\tgraph}[1]{\ensuremath{\mathsf{Graph}_{#1}}}
\newcommand{\can}[1]{\ensuremath{\mathsf{C}({#1})}}
% source and target of a derivation
\newcommand{\source}[1]{\ensuremath{\mathsf{s}({#1})}}
\newcommand{\target}[1]{\ensuremath{\mathsf{t}({#1})}}
\newcommand{\col}[1]{\ensuremath{\mathsf{col}({#1})}}

% left decorated trace
\newcommand{\ltrace}[1]{\ensuremath{\langle {#1}\rangle_c}}

\newcommand{\bx}[1]{\phantom{\big(}#1{\phantom{\big)}}}
\newcommand{\bxx}[1]{\,#1\,}
\newcommand{\cycl}[1]{\ensuremath{\mbox{\textcircled{\scriptsize{$#1$}}}}}
\renewcommand{\iff}{\ensuremath{\Leftrightarrow}}

%%%%GENERAL CATEGORICAL NOTATION

%identità
\newcommand{\id}[1]{\mathsf{id}_{#1}}
%codominio
\newcommand{\cod}[1]{\mathsf{cod}({#1})}
	%Variabili categorie
\def\A{\textbf {\textup{A}}}
\def\B{\textbf {\textup{B}}}
\def\C{\textbf {\textup{C}}}
\def\D{\textbf {\textup{D}}}
\def\X{\textbf {\textup{X}}}
\def\Y{\textbf {\textup{Y}}}
\renewcommand{\P}{\textbf {\textup{P}}}

%\derivazioni

\newcommand{\dder}[1]{\mathscr{#1}}
\newcommand{\sder}[2]{I(\mathscr{#1}, \mathscr{#2})}
\newcommand{\der}[1]{\underline{\dder{#1}}}
\def\dpo{\mathsf{C}^{\X}_R}
\def\gpo{\mathsf{G}^{\X}_R}
\def\dpi{[\mathsf{C}]^{\X}_R}
\def\gpi{[\mathsf{G}]^{\X}_R}

\newcommand{\ider}[1]{\mathscr{I}_{#1}}

%categorie
\def\Set{\textbf {\textup{Set}}}

%comma
\newcommand{\comma}[2]{#1\hspace{1pt} {\downarrow}\hspace{1pt} #2}
\newcommand{\cma}[2]{\mathcal{#1}\hspace{1pt} {\downarrow}\hspace{1pt} \mathcal{#2}}

%derivazioni
\newcommand{\lpro}{\langle \hspace{-1.85pt}[}
\newcommand{\rpro}{]\hspace{-1.85pt}\rangle}
\newcommand{\tpro}[1]{\lpro \der{#1}\rpro}
\newcommand{\lgt}[0]{\mathsf{length}}

%%% NEW

\usepackage{xparse}

% inversions
\newcommand{\inv}[1]{\ensuremath{inv}({#1})}

% direct shift
\newcommand{\shiftdir}[1][]{\ensuremath{\mathrel{{\rightsquigarrow}^{\mathit{sh}}_{#1}}}}

% shift preorder
\newcommand{\shiftpre}[1][]{\ensuremath{\mathrel{{\sqsubseteq}^{\mathit{sh}}_{#1}}}}

% shift equivalence
\newcommand{\shifteq}[1][]{\ensuremath{\mathrel{{\equiv}^\mathit{sh}_{#1}}}}

% transp{source}[target]: if target not specified source+1
\NewDocumentCommand{\transp}{m o}{%
  \ensuremath{({#1},%
  \IfNoValueTF{#2}%
    {{#1}+1}%
    {#2}%
    )}
}

\NewDocumentCommand{\mycommand}{o}{%
  % <code>
  \IfNoValueTF{#1}
    {code when no optional argument is passed}
    {code when the optional argument #1 is present}%
  % <code>
}
% interchange
\newcommand{\IC}[1]{\ensuremath{\mathit{IC}({#1})}}

\title{Fusion}

\begin{document}
\maketitle

\begin{abstract}
\todo{	A VERY NICE ABSTRACT}
\end{abstract}

\section{Introduction}

\todo{A VERY NICE INTRODUCTION}

\section{$\mathcal{M}$-adhesive categories}

This first section is devoted to recall the definition and the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2006weak,lack2005adhesive}.

\begin{notation} 
We stipulate here some notational conventions which will be used throughout this paper.

Given a category $\X$ we will not distinguish notationally between $\X$ and its class of objects: so that ``$X\in \X$'' means that $X$ belongs to the class of objects of $\X$.

If $1$ is a terminal object in a category $\X$,  the unique arrow $X\to 1$ from another object $X$ will be denoted by $!_X$. Similarly, if $0$ is initial in $\X$ then $?_X$ will denote the unique arrow $0\to X$. When $\X$ is $\Set$ and $1$ is a singleton, $\delta_x$ will denote the arrow $1\to X$ with value $x\in X$.

Finally, we will use the following notation for some special classes of arrows of a category $\X$:
\begin{itemize}
	\item $\mathcal{A}(\X)$ will denote the class of all arrows of $\X$;
	\item $\mathcal{M}(\X)$ will denote the class of all monos of $\X$;
	\item $\mathcal{R}(\X)$ will denote the class of all regular monos of $\X$.
\end{itemize}
\end{notation}

\subsection{The Van Kampen condition}
The key property that $\mathcal{M}$-adhesive categories enjoy is given by  the so-called \emph{Van Kampen condition} \cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive}. We will recall it and examine some of its consequences.

\begin{definition} \index{Van Kampen square} \index{pushout!- square} \index{pushout!Van Kampen -|see{Van Kampen square}}Let $\X$ be a category  and consider the two diagrams below
	\[\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{f}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{g} &&D&&C \ar[rr]_{g} & & D}\]
	We say that the left square is a \emph{Van Kampen square} if:
	\begin{enumerate}
		\item it is a pushout square;
		\item whenever the right cube has pullbacks as back and left faces, then its top face is a pushout if and only if the front and right faces are pullbacks.
	\end{enumerate}

	Pushout squares which enjoy the ``if'' half of this condition are called \emph{stable}.
\end{definition}

\begin{example}\label{ex:iso}
	In any category $\X$, a square as the one below on the left, in which $m$ is an isomorphism, is Van Kampen. Notice that, in this situation, $n$ must be an isomorphism too.
		\[\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{f}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{g} &&D&&C \ar[rr]_{g} & & D}\]

	Take a cube as the one above and suppose that its back faces are pullbacks. In particular we know that also $m'$ is an isomorphism.

	\smallskip \noindent 
	$(\Rightarrow)$ Suppose that the top face is a pushout, thus $n'$ is an isomorphism and the right square is a pullback. The thesis for the front face follows at once since $m', n', m$ and $m$ are isomorphisms and the back face a pullback.

	\smallskip \noindent 
	$(\Leftarrow)$ If all the vertical faces are pullbacks, then $m'$ and $n'$ are isomorphisms and this entails at once that the top face is a pushout.
\end{example}

Before proceeding further, we recall this classical result about pullbacks.

\begin{lemma}\label{lem:pb1}
	Let $\X$ be a category, and consider the following diagram 	in which the right square is a pullback.
	\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
	Then the whole rectangle is a pullback if and only if the left square is one.
\end{lemma}

The previous result can be dualised to get an analogous lemma for pushouts.

\begin{lemma}\label{lem:po1}
	Let $\X$ be a category, and consider the following diagram 	in which the left square is a pushout.
	\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
	Then the whole rectangle is a pushout if and only if the right square is one.
\end{lemma}

The following proposition establishes a key property of Van Kampen squares with a mono as a side: they are not only pushouts, but also pullbacks.
\begin{proposition}\label{prop:pbpo} Let $m\colon A\to C$ be a monomorphism in a category $\X$. Then every Van Kampen square
	\[\xymatrix{A\ar[r]^{g} \ar[d]_{m} & B \ar[d]^{n} \\ C \ar[r]_{f}  & D}\]
	is also a pullback square and $n$ is a monomorphism.
\end{proposition}
\begin{proof} Take the following cube:
	\[\xymatrix@C=13pt@R=13pt{&A\ar[dd]|\hole_(.65){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_{\id{B}} \\ A  \ar[dd]_{m}\ar[rr]^(.65){g} & & B \ar[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{f} & & D}\]
	By construction the top face of the cube is a pushout and the back one a pullback. The left face is a pullback because $m$ is mono. Thus the Van Kampen property yields that the front and the right faces are pullbacks and the thesis follows. \qed 
\end{proof}

The previous proposition, in turn, allows us to establish the following results.
\begin{lemma}\label{lem:varie} Let $m:X\to Y$ be a monomorphism in a category $\X$ and suppose that the left square below is Van Kampen, while all the vertical faces in the right cube are pullbacks.
		\[\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{f}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{g} &&D&&C \ar[rr]_{g} & & D}\]
Supppose, moreover that $d:D'\to D$ is mono, then $d\leq n$ if and only if $c \leq m$.
\end{lemma}
\begin{remark}
	Recall that, given two monos $m:M\to X$ and $n:N\to X$ with the same codomain, $m\leq n$ means that there exists a, necessarily unique, $k:M\to N$ fitting in the triangle below:
	\[\xymatrix{M\ar@{.>}[rr]^{k}  \ar[dr]_{m}&& N \ar[dl]^{n}\\ & X}\]
	Notice that, if $m\leq n$ and $n\leq m$, then the arrow $k:M\to N$ is an isomorphism.  
\end{remark}
\begin{remark}
	Notice that, since $d$ is a mono and the front face a pullback, then $c$ is a monomorphism too.
\end{remark}

\begin{proof}
	$(\Rightarrow)$ By hypothesis there exists $k:D'\to B$ such that $n\circ k = d$. By \Cref{prop:pbpo}, the bottom face of the cube is a pullback, thus there exists a unique $h:C'\to A$ as in the diagram below. 
	In particular, this implies the thesis.
		\[\xymatrix@C=40pt{C'  \ar@{.>}[dr]^{h}\ar[r]^{g'} \ar@/_.3cm/[ddr]_{c}& D' \ar@/_.3cm/[ddr]|(.45)\hole_(.7){d}\ar@/^.3cm/[dr]^{k}\\ & A \ar[d]_{m} \ar[r]^{f} & B \ar[d]^{n} \\ & C \ar[r]_g & D}\]

	\smallskip \noindent 
	$(\Leftarrow)$ Let $h:C\to A$ be such that $c=m\circ h$. By the Van Kampen property the top face of the given cube is a pushout. Thus the dotted $k:D'\to B$ in the following diagram exists.
		\[\xymatrix@C=40pt{A' \ar@/^.3cm/[ddr]^(.8){a} \ar[d]_{m'} \ar[r]^{f'} & B' \ar[d]^{n'} \ar@/^.3cm/[ddr]^{b} \\  C' \ar@/_.3cm/[dr]_{h} \ar[r]_{g'}|(.7)\hole & D' \ar@{.>}[dr]^{k}\\ &A \ar[r]_f& B }\]
	The thesis now follows at once. \qed 
\end{proof}

\subsection{$\mathcal{M}$-adhesivity}

In this section we will define the notion of $\mathcal{M}, \mathcal{N}$-adhesivity and explore some of the consequence of such a property. Let us start fixing some terminology.

\begin{definition}\
	Let $\mathcal{M}$  be a class of arrows of a category $\X$. We say that  $\mathcal{M}$ is
	\begin{itemize}
		\item 
		\emph{stable under pushouts (pullbacks)} if for every pushout (pullbacks) square 
		\[\xymatrix{A\ar[r]^f  \ar[d]_{m}& B \ar[d]^n \\ C \ar[r]_g & D}\]
		if $m \in \mathcal{M}$ ($n\in \mathcal{M}$) then $n \in \mathcal{M}$ ($m \in \mathcal{M}$);
		\item \emph{closed under composition} if $g, f\in \mathcal{M}$ implies $g\circ f\in \mathcal{M}$ whenever $g$ and $f$ are composable;
		\item \emph{closed under decomposition} if $g\circ f\in \mathcal{M}$ and $g\in \mathcal{M}$ implies $f\in \mathcal{M}$.
	\end{itemize}
\end{definition}

\begin{remark}Clearly, ``decomposition'' corresponds to ``left cancellation'', but we prefer to stick to the name commonly used in literature.
\end{remark}

We are now ready to give the definition of $\mathcal{M}$-adhesive category	
\begin{definition}[\cite{azzi2019essence,heindel2009category}]
	Let $\X$ be a category and consider a subclass $\mathcal{M}$ of the class $\mathcal{M}(\X)$ of monomorphisms such that:
	\begin{enumerate}
		\item $\mathcal{M}$ contains all isomorphisms and is closed under composition;
		\item $\mathcal{M}$ is stable under pullbacks and pushouts.
	\end{enumerate}
	We say that $\X$ is \emph{$\mathcal{M}$-adhesive} if
	\begin{enumerate}
		\item for every $m\colon X\to Y$ in $\mathcal{M}$ and $g\colon Z\to Y$, a pullback square
		\[\xymatrix{P\ar[r]^p \ar[d]_{n}& X \ar[d]^{m}\\ Z \ar[r]_g& Y}\]
		exists, such pullbacks will be called \emph{$\mathcal{M}$-pullbacks};
		\item for every $m\colon X\to Y$ in $\mathcal{M}$ and $n\colon X\to Z$, a pushout square
		\[\xymatrix{X \ar[r]^n \ar[d]_{m}& Z \ar[d]^{q}\\ Y\ar[r]_p &Q}\]
		exists, such pushouts  will be called \emph{$\mathcal{M}$-pushouts}; 
		\item  $\mathcal{M}$-pushouts are Van Kampen squares.
	\end{enumerate}
\end{definition}

\begin{remark}\label{rem:diff}Our notion of $\mathcal{M}$-adhesivity is slightly different from the one of \cite{azzi2019essence}: in that paper, $\mathcal{M}$ is assumed to be only stable under pullbacks. Notice, however, that if $\mathcal{M}$ contains all split monos, then stability under pushouts can be deduced from the other axioms \cite[Prop.~$5.1.21$]{castelnovo2023thesis}.
\end{remark}

\begin{remark}\label{rem:salva} 
	\emph{Adhesivity} and \emph{quasiadhesivity} as defined in \cite{lack2005adhesive,garner2012axioms}  coincide with  $\mathcal{A}(\X) $-adhesivity and $\mathcal{R}(\X)$-adhesivity, respectively. 
\end{remark}

A first result we can prove regards closure under decomposition of $\mathcal{M}$.

\begin{proposition}\label{prop:deco}Let  $\mathcal{M}$ be a class of monomorphisms containing all isomorphisms and stable under pullbacks. For every arrow $f: X\to Y$ and monomorphism $m: Y\to Z$, if $m\circ f \in\mathcal{M}$ then $f\in \mathcal{M}$.
\end{proposition}
\begin{proof}Take the diagram
	\[\xymatrix{X \ar[d]_{\id{X}}\ar[r]^{f}& Y \ar[r]^{\id{Y}}  \ar[d]_{\id{Y}}& Y \ar[d]^{m}\\
		X \ar[r]_{f}& Y \ar[r]_{m} & Z}\]
	Since $m$ is mono the right square is a pullback, the thesis now follows from \Cref{lem:pb1}.
\end{proof}
\begin{corollary}\label{cor:deco}
	In every $\mathcal{M}$-adhesive category $\X$, the class $\mathcal{M}$ is closed under decomposition.
\end{corollary}

Another result which can be immediately established, with the aid of \Cref{prop:pbpo}, is the following one.
\begin{proposition}\label{prop:pbpoad}
	Let $\X$ be an $\mathcal{M}$-adhesive category. Then $\mathcal{M}$-pushouts are also pullback squares.
\end{proposition}

From \Cref{prop:pbpoad}, in turn, we can derive the following corollaries.
\begin{corollary}\label{cor:rego}
	In a $\mathcal{M}$-adhesive category $\X$, every $m\in\mathcal{M}$ is a regular mono.
\end{corollary}
\begin{proof}
Let $m$ be an element of $\mathcal{M}$ and consider its pushout along itself.
\[\xymatrix{X\ar[r]^m \ar[d]_m& Y\ar[d]^{f}\\Y \ar[r]_g & Z}\]
By \Cref{prop:pbpoad} this square is a pullback, proving that $m$ is the equalizer of the arrows $f,g\colon Y\rightrightarrows Z$. \qed 
\end{proof}

The following result now follows at once noticing that a regular monomorphism which is also epic is automatically an isomorphism.

\begin{corollary}\label{prop:bal}
If $\X$ is an $\mathcal{M}$-adhesive categories, then every epimorphisms in $\mathcal{M}$ is an isomorphisms. In particular, every adhesive category $\X$ is \emph{balanced}: if a morphism is monic and epic, then it is an isomorphism.
\end{corollary}

$\mathcal{M}$-adhesivity is well-behaved with respect to the comma construction \cite{mac2013categories}, as shown by the following theorem.
\begin{theorem}[\cite{CastelnovoGM22,ehrig2006fundamentals}]\label{lem:comma}
	Let $\A$ and $\B$ be respectively an $\mathcal{M}$-adhesive and an $\mathcal{M}'$-adhesive category. Let also $L:\A\rightarrow \C$ be a functor that preserves $\mathcal{M}, \mathcal{N}$-pushouts, and  $R:\B\rightarrow \C$ be a functor which preserves pullbacks.Then $\comma{L}{R}$ is $\cma{M}{M'}$-adhesive, where 
	\[
	\cma{M}{M}':=\{(h,k)\in \mathcal{A}(\comma{L}{R}) \mid h\in \mathcal{M}, k\in \mathcal{M}'\}\]
\end{theorem}

In particular, we can apply this result  to slices over a given object.

\begin{corollary}\label{cor:slice}
	Let  $X$ be an object of an $\mathcal{M}$-adhesive category $\X$. Then  $\X/X$ is $\mathcal{M}/X$-adhesive, where
	\[\mathcal{M}/X:=\{m\in  \mathcal{A}(\X/X) \mid m\in \mathcal{M} \}\]
\end{corollary}

\todo{ESEMPI}
We can list various examples of $\mathcal{M}$-adhesive categories (see \cite{castelnovo2023thesis,CastelnovoGM22,lack2006toposes}).

\begin{example}Topos, ipergrafi e grafi
\end{example}

\begin{example}GRAFI GERARCHICI
\end{example}

\begin{example}term graph
\end{example}

We end this section proving two properties of $\mathcal{M}$-adhesive categories:  $\mathcal{M}$-pushout-pullback decomposition and uniqueness of pushouts complements.

\begin{lemma}[$\mathcal{M}$-pushout-pullback decomposition]\label{lem:popb} Let $\X$ be an $\mathcal{M}$-adhesive category  and suppose that, in the diagram below, the whole rectangle is a pushout and the right square a pullback.
\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
	Then the following statements hold true:
	\begin{enumerate}
\item if $a$ belongs to $\mathcal{M}$ and $k$ is a monomorphism,  then both squares are pushouts and pullbacks;
\item if $f$ and $k $ are in  $\mathcal{M}$, then both squares are pushouts and pullbacks.
	\end{enumerate}
\end{lemma}
\begin{proof}
\begin{enumerate}
	\item 	We can begin noticing that $c$ is an element of $\mathcal{M}$ because it is the pushout of $a$. Moreover, $b$, being the pullback of $c$, is in $\mathcal{M}$ too. Now, the whole rectangle is a $\mathcal{M}$-pushout, thus, by \Cref{prop:pbpoad}, it is a pullback and so its left half is a pullback, by \Cref{prop:pbpo}. Moreover, $g$, being the pullback of a monomorphism, is monic too.

	Putting together these observations, we can build the cube below, in which all the vertical faces are pullbacks.
	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y \ar[rrr]|(.67)\hole^{b} \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
	The bottom face is a Van Kampen square and so its top one is a pushout. The thesis now follows from \Cref{lem:po1}.
	\item By hypothesis, $g$ is the pullback of an arrow in $\mathcal{M}$, thus belongs to it. But then $g\circ f\in \mathcal{M}$ too  and the whole rectangle is a $\mathcal{M}$-pushout. Therefore, by \Cref{prop:pbpoad} a pullback, so that its left half is a pullback too, by \Cref{prop:pbpo}. Moreover $k\circ h$ is in $\mathcal{M}$ as the pushout of $g\circ f$ and, by \Cref{cor:deco}, we also know that $h\in \mathcal{M}$.

	Using again \Cref{lem:po1}, it is enough to show that the left half of the original rectangle is a pushout. We can build the same cube of the previous point:
	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y \ar[rrr]|(.67)\hole^{b} \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
	Its vertical faces are all pullbacks, those the top one is a pushout and we can conclude. \qed 
\end{enumerate}
\end{proof}

Let us turn our attention to pushout complements.

\begin{definition}
Let $f:X\to Y$ and $g:Y\to Z$ ba two composable arrows in a category $\X$. A \emph{pushout complement} for the pair $(f,g)$ is a pair $(h,k)$ with $h:X\to W$ and $k:W\to Z$ such that the square below commutes and it is a pushout.
\[\xymatrix{X \ar[r]^{f} \ar[d]_{h}& Y \ar[d]^{g} \\ W \ar[r]_{k}& Z}\]
\end{definition}

\begin{example}
	In a generic category $\X$, pushout complements may not exist: in the  the category of $\Set$ the arrows $?_{2}:\emptyset \to 2$ and $!_2:2\to 1$ do not have a pushout complement.

	Moreover, composable arrows $f:X\to Y$ and $g:Y\to Z$ may have  pushout complements which are non-isomorphic: for instance, in $\Set$ the two squares below are both pushouts.

	\[\xymatrix{2 \ar[r]^{!_2} \ar[d]_{\id{2}}& 1 \ar[d]^{\id{1}} & 2 \ar[r]^{!_2} \ar[d]_{!_2}& 1 \ar[d]^{\id{1}}\\ 2 \ar[r]_{!_2}& 1 & 1 \ar[r]_{\id{1}}& 1}\]
\end{example}

Working in an $\mathcal{M}$-adhesive category we can amend the second defect.

\begin{lemma}[Uniqueness of pushouts complements]\label{lem:pocomp}
Let $\X$ be a $\mathcal{M}$-adhesive category. Given $m:X\to Y$ in $\mathcal{M}$ and $n:Y\to Z$, let $(h_1, k_1)$ and $(h_2, k_2)$ be pushout complements of $m$  and $n$ and $W_1=\cod{h_1}$, $W_2=\cod{h_2}$. Then there exists a unique isomorphism $f:W_1\to W_2$ making the following diagram commutative.
\[\xymatrix{&X \ar[r]^{m} \ar[d]_{h_1} \ar@/_.3cm/[ddl]_{h_2}& Y \ar[d]^{n} \\ &W_1 \ar@{.>}[dl]^{f} \ar[r]_{k_1} & Z \\ W_2 \ar@/_.3cm/[urr]_{k_2}}\]

\end{lemma}
\begin{proof}
	$k_1$ and $k_2$, being the pushout of $m$, are elements of $\mathcal{M}$ and thus are monomorphisms. In particular, $k_2$ is a monomorphism and this  entails at once the uniqueness of $f$.  Moreover, notice that the squares
	\[\xymatrix{X \ar[r]^{m} \ar[d]_{h_1}& Y \ar[d]^{n}& X \ar[d]_{h_2}\ar[r]^{m} & Y \ar[d]^{n}\\ W_1 \ar[r]_{k_1} & Z & W_2 \ar[r]_{k_2}& Z}\]
	are $\mathcal{M}$-pushouts and thus Van Kampen.

To prove the existence of the wanted $f$, we can start observing that $k_1$ and $k_2$, being the pushout of $m$, are elements of $\mathcal{M}$, so that we can consider the pullback square
	\[\xymatrix{P\ar[r]^{p_1}  \ar[d]_{p_2}& W_1 \ar[d]^{k_1}\\ W_2 \ar[r]_{k_2} & Z}\]
	Since $k_1\circ h_1=k_2\circ h_2$, there exists a unique $g: X\to P$ such that
	\[p_1\circ g=h_1 \qquad p_2\circ g = h_2\]
	We can then build the cubes
	\[\xymatrix@C=13pt@R=13pt{&X\ar[dd]|\hole_(.65){\id{X}}\ar[rr]^{g} \ar[dl]_{\id{X}} && P \ar[dd]^{p_1} \ar[dl]_{p_2} & &X\ar[dd]|\hole_(.65){\id{X}}\ar[rr]^{g} \ar[dl]_{\id{X}} && P \ar[dd]^{p_2} \ar[dl]_{p_1}\\ X  \ar[dd]_{m}\ar[rr]^(.65){h_2} & & W_2 \ar[dd]_(.3){k_2}& &  X  \ar[dd]_{m}\ar[rr]^(.65){h_1} & & W_1 \ar[dd]_(.3){k_1}\\&X\ar[rr]|\hole^(.65){h_1} \ar[dl]^{m} && W_1 \ar[dl]^{k_1} & &X\ar[rr]|\hole^(.65){h_2} \ar[dl]^{m} && W_2 \ar[dl]^{k_2}\\Y \ar[rr]_{n} & & Z & &Y \ar[rr]_{n} & & Z}\]

	Now, in both cubes the front and left faces are pullbacks, thus, by \Cref{lem:pb1}, their back face is a pullback too. Since $m\leq m$, \Cref{lem:varie} now entails that $k_1\leq k_2$ and $k_2\leq k_1$. Thus there exists an isomorphism $f:W_1\circ W_2$ such that $k_1=k_2\circ f$. To see that $h_2=f\circ h_1$, we can compute:
	\begin{align*}
		k_2\circ f \circ h_1 & = k_1\circ h_1\\&= n\circ m\\&= k_2\circ h_2
	\end{align*}
	The claim now follows since $k_2$ is a monomoprhism. \qed 
\end{proof}

\section{Double pushout rewriting and derivations}
\todo{A VERY NICE INTRODUCTION}

\subsection{Left-linear DPO-rewriting systems}
We are now going to study rewriting systems in $\mathcal{M}, \mathcal{N}$-adhesive categories.

\begin{definition}[\cite{habel2012mathcal,heindel2009category}]
	Let $\X$ be a $\mathcal{M}$-adhesive category, a  \emph{left $\mathcal{M}$-linear} rule $\rho$ is a pair $(l,r)$ of arrows with the same domain, such that $l$ belongs to $\mathcal{M}$.  The rule $\rho$ is said to be \emph{$\mathcal{M}$-linear} if $r\in \mathcal{M}$ too. A rule $\rho$ is said to be \emph{consuming} if $l$ is not an isomorphism. We will represent a rule $\rho$ as a span 
	\[\xymatrix{L & K\ar[l]_{l} \ar[r]^{r} & R}\]
$L$ is the \emph{left-hand side}, $R$ is the \emph{right-hand side} and $K$ the \emph{glueing object}.

A \emph{left-linear DPO-rewriting system} is a pair $(\X, R)$ where $\X$ is a $\mathcal{M}$-adhesive category and $R$ is a set of left $\mathcal{M}$-linear rules. Given  two objects $G$ and $H$ and a rule $\rho=(l,r)$ in $R$, a \emph{direct derivation $\mathscr{D}$ from $G$ to $H$ via $\rho$}, is a diagram as the one below, in which both squares are pushouts. 
	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
	The arrow $n$ is called the \emph{match} of the derivation, while $h$ is its \emph{back-match}.
	We will denote a direct derivation $\dder{D}$ between $G$ and $H$ as $\dder{D}:G\Mapsto H$.
\end{definition}

\begin{remark}\todo{perché regole non consumanti non vanno bene}
\end{remark}

\begin{example}\todo{
esempi di	derivazione}
\end{example}

$\mathcal{M}$-adhesivity of $\X$ guarantess the essential uniqueness of the result obtained rewriting an object, as shown by the next proposition.

\begin{proposition}\label{prop:unique} Let $\X$  be a $\mathcal{M}$-adhesive category. Suppose that the two direct derivations $\mathscr{D}$ and $\mathscr{D'}$ below, with the same match and applying the same left $\mathcal{M}$-linear rule $\rho$ are given.
	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L \ar[d]_{n}& K \ar[d]^{k'}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & G & \ar[l]^{f'} D' \ar[r]_{g'}& H'}\]
Then there exist isomorphisms $t:D\to D'$ and $s:H\to H'$ as in the following diagram.
	\[\xymatrix@C=30pt@R=10pt{ &&&R\ar[dddr]^{h'} \ar[dddl]_{h}|(.67)\hole\\&&K \ar[dl]_{l} \ar[ur]^{r}\ar[dddr]^{k'} \ar[dddl]_{k}\\&L \ar[dddl]_{n}\\&&H \ar@{.>}[rr]^{s} && H'\\ & D \ar[ur]^{g} \ar@{.>}[rr]^{t} \ar[dl]_{f}&& D' \ar[ur]_{g'}\ar@/^.3cm/[dlll]^{f'}\\ G}\]
\end{proposition}
\begin{proof}
	By construction, the pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$ and $n$. Thus, the existence of the isomorphism $t:D\to D'$ follows from \Cref{lem:pocomp}. Now, computing we have
	\begin{align*}
		g'\circ t \circ k &= g' \circ k'\\&=h'\circ r
	\end{align*}
	Hence, we have the dotted $s:H\to H'$. To see that $s$ is an isomorphism, consider the diagram 
	\[\xymatrix{K  \ar@/^.4cm/[rr]^{k'}\ar[d]_{r} \ar[r]_{k}& \ar[r]_{t} D \ar[d]^{g}& D' \ar[d]^{g'}\\ R \ar@/_.4cm/[rr]_{h'} \ar[r]^{h}& H \ar[r]^{s}& H'}\]
	By hypothesis the whole rectangle and its left half are pushouts, therefore, by \Cref{lem:po1} its right square is a pushout too. The claim now follows from the fact that the pushout of an isomorphism is an isomorphism. \qed
\end{proof}

If we look to direct derivations as transitions, it is natural to consider them as edges in a direct graph. Taking as vertices objects or isomorphism classes of objects led us to the following definitions \cite{heindel2009category,mellies2005axiomatic}.

\begin{definition}
	Let $(\X, R)$ be a left-linear DPO-rewrityng system, with $\X$ $\mathcal{M}$-adhesive. The \emph{DPO-derivation graph} of $(\X, R)$ is the (large)  directed graph $\gpo$ having as vertices the objects of $\X$ and in which an edge between $G$ and $H$ is a direct derivation $\dder{D}:G\Mapsto H$.	A \emph{derivation} $\der{D}$ between two objects $G$ and $H$ is a path between them in $\gpo$.
\end{definition}

\begin{remark}
	If $\X$ is not a small category , then $\gpo$ has a proper class of vertices.
\end{remark}

	We can spell out more explicitly what  a derivation $\dder{D}$ between $G$ and $H$ is.  $\dder{D}$ is a, possibly empty, sequence $\{\dder{D}_i\}_{i=0}^n$ of direct derivations such that:
	\begin{enumerate}
		\item for every index $i$, $\dder{D}_i$ is a direct derivation $G_i \Mapsto G_{i+1}$;
		\item $G_0=G$ and $G_{n+1}=H$.
	\end{enumerate}

	We will call the number $n+1$ the \emph{length} of the derivation, denoted by $\lgt(\der{D})$. We will also say that an empty derivation has length $0$.

	Moreover,  if $\mathcal{D}_i$ is an application of the rule $\rho_i\in R$, then we can define an associated sequence of rule as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.

\begin{notation}Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ be a derivation. We will depict the $i^\text{th}$ element $\dder{D}_i$ of $\der{D}$ as in the following diagram.  
	\[\xymatrix{L_i \ar[d]_{m_i}& K_i \ar[d]^{k_i}\ar[l]_{l_i} \ar[r]^{r_i} & R_i \ar[d]^{h_i} \\G_{i} & \ar[l]^{f_{i}} D_{i} \ar[r]_{g_{i}}& G_{i+1} }\]
	Notice that, in particular, if $\der{D}:G\to H$, then $G_0=G$ and $G_{n+1}=H$. When $\der{D}$ has length $1$ we will suppress the indexes. In such case, we will also identify $\der{D}$ with its only element. 
\end{notation}

\begin{example}\todo{esempi di derivazione}
\end{example}

\begin{remark}
Derivations, being paths in a graph, can be concatenate: given $\der{D}=\{\dder{D}\}_{i=0}^n$ between $G$ and $H$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^m$, their \emph{concatenation} $\der{D}\cdot\der{D}'$ is the derivation $\{\dder{E}_i\}_{i=0}^{m+n+1}$ in which
\[\dder{E}_i:=\begin{cases}
	\dder{D}_i & i \leq n\\
	\dder{D}'_{i-(n+1)} & n< i 
\end{cases}\]	
\end{remark}

We are often interested in an object of $\X$ only up to isomorphism. It is then useful to consider a version of $\gpo$ in which vertices are classes of isomorphism of object of $\X$. However, in order to do so, we have also to identify direct derivations up to coherent isomorphisms. We are thus lead to the following definition.

\begin{definition}
	Let $\dder{D}:G\Mapsto H$ and $\dder{D}':G'\Mapsto H'$ be two direct derivations given by the following two diagrams
	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L \ar[d]_{n'}& K \ar[d]^{k'}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & G' & \ar[l]^{f'} D' \ar[r]_{g'}& H'}\]
	An \emph{abstraction equivalence} $\phi:\dder{D}\to \dder{D}'$ is a triple $(\phi_1, \phi_2, \phi_3)$ of isomorphism fitting in the diagram below.
	\[\xymatrix@C=40pt@R=10pt{ &&&R\ar[dddr]^{h'} \ar[dddl]_{h}|(.67)\hole\\&&K \ar[dl]_{l} \ar[ur]^{r}\ar[dddr]^{k'} \ar[dddl]_{k}|(.67)\hole\\&L\ar[dddr]^(.4){n'} \ar[dddl]_(.4){n}\\&&H \ar[rr]^{\phi_3} && H'\\ & D \ar[ur]_(.7){g} \ar[rr]^{\phi_2} \ar[dl]_{f}&& D' \ar[ur]_{g'}\ar[dl]^{f'}\\ G \ar[rr]_{\phi_1} && G'}\]

Given two derivations $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ such that $\dder{D}_i:G_i\Mapsto G_{i+1}$ and $\dder{D}'_i:G'_i\Mapsto G'_{i+1}$., we will say that $\der{D}$ and $\der{D}'$ are \emph{abstraction equivalent}, if  $r(\der{D})=r(\der{D'})$  and there exists a family $\{\phi^i\}_{i=0}^n$ of abstraction equivalences $\phi^i:\dder{D}_i\to \dder{D}'_i$ such, for every index $i$, $\phi^i_3=\phi^{i+1}_1$.

	In such situation we will say that $\der{D}$ and $\der{D}'$ are \emph{abstraction equivalent}. We will use $\equiv^a$ to denote the resulting equivalence relation, while $[\der{D}]_a$ will denote the equivalence class of $\der{D}$. 
\end{definition}
\begin{remark}
	We can restate \Cref{prop:unique}: it asserts that, given two direct derivations $\dder{D}$ and $\dder{D'}$ with the same match, there exists an abstract equivalence between them whose first component is an identity.
\end{remark}

\begin{definition}
	Let $(\X, R)$ be a left-linear DPO-rewrityng system, with $\X$ an $\mathcal{M}$-adhesive category. The  graph $\gpi$ is the (large)  directed graph having as vertices isomorphism classes of objects of $\X$ and in which an edge between $[G]$ and $[H]$ is the equivalence class $[\der{D}]_a$ of derivation $\der{D}$ between $G$ and $H$.	
\end{definition}

\subsection{Consistent permutations}

Given a left-linear DPO-rewriting system $(\X, R)$,  a derivation $\der{D}$  determines a diagram $\Delta(\der{D})$ in $\X$. We can then wonder if such a diagram has a colimit. Clealry if $\der{D}$ is the empty derivation then a colimit for $\Delta(\der{D})$ amount to an initial object in $\X$. If $\der{D}$ is non-empty we can use the following result.

\begin{lemma}\cite{heindel2009category}
	Let $\X$ be an $\mathcal{M}, \mathcal{N}$-adhesive category and $(\X, R)$ a left-linear DPO-rewriting system over it. Then for every non-empty derivation $\der{D}:G\to H$, the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belong to $\mathcal{M}$.
\end{lemma}
\begin{proof}
	We proceed by induction.
	\begin{enumerate}
		\item Suppose that $n=0$ so that $\der{D}$ consists only of the following direct derivation
		\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G & \ar[l]^{f} D \ar[r]_{g}& H }\]
		then $f\in \mathcal{M}$ so that we can consider its pushout along $g$ to get a diagram
		\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G \ar@/_.2cm/[dr]_{q}& \ar[l]^{f} D \ar[r]_{g}& H  \ar@/^.2cm/[dl]^{p}\\ & P}\]
		Let $(C, \{c_X\}_{X\in \Delta(\der{D})})$ be another cocone, in particular we have
		\begin{align*}
			c_H\circ g & = c_D \\&= c_G\circ f
		\end{align*}
		Hence, there exists a unique $c:P\to C$ such that 
		\[c\circ q= c_G \qquad c\circ p =c_H\]
		Now, $f$ is in $\mathcal{M}$ as it is the pushout of $l$, hence $p$ is in $\mathcal{M}$ too and this gives us the thesis. 
		\item Let $\der{D}$ be $\{\dder{D}_i\}_{i=0}^n$ and suppose that $n\geq 1$. Let also $\der{D}'$ be $\{\dder{D}_i\}^{n-1}_{i=0}$ and $\rho_n=(l_n, r_n)$ be the rule applied in $\dder{D}_n$. The pushout of $l_n$ is the arrow $f_n:D_n\to G_n$ is in $\mathcal{M}$ and, by inductive hypothesis, $\iota_{G_{n}}:G_{n}\to \lpro \der{D}'\rpro$ is in $\mathcal{M}$ too. Thus, we can consider the diagram below, having a pushout as its lower half.
		\[\xymatrix{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar[l]_{l_{n}} \ar[r]^{r_{n}} & R_{n} \ar[d]^{h_n} \\G_{n} \ar[d]_{\iota_{G_{n}}}& \ar[l]^{f_n} D_n \ar[r]_{g_n}& H  \ar[d]^{q}\\ \lpro \der{D}' \ar[rr]_{p}\rpro && P}\] 
		Notice that, as in the point above, the arrow $q:H\to P$ is the pushout of an element in $\mathcal{M}$, therefore it is enough to show that the diagram so constructed provides a colimiting cocone for $\Delta(\der{D})$.

		Let $(C, \{c_X\}_{X\in \Delta(\der{D})})$ be a cocone, since $\Delta(\der{D}')$ is a subdiagram of $\Delta(\der{D})$, we get another cocone $(c, \{c_X\}_{X\in \Delta(\der{D}')})$ which induces an arrow $c':\lpro \der{D}' \rpro \to C$ such that
		\begin{align*}
			c'\circ \iota_{G_n} \circ f_n &=c_{G_n} \circ f_n\\&= c_{D_n}\\&= c_{H}\circ g_n
		\end{align*}
		Therefore the arrows $c'$ and $c_H$ induce a morphism $c:P\to C$ and the thesis now follows at once.
		\qed 
	\end{enumerate}
\end{proof}

So equipped, we can introduce the notion of \emph{consistent permutation}.

\begin{definition}
	Let $\X$ be an $\mathcal{M}$-adhesive category and consider a left-linear DPO-rewriting system $(\X, R)$ on it.  Take two non-empty derivations $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with the same length with their associated sequences of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$. A permutation $\sigma:n+1\to n+1$  is called a \emph{consistent permutation} between $\der{D}$ and $\der{D}'$, if for every $i\in n+1$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists an isomorphism $\phi:\tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
\[\xymatrix{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi} \\G'_{\sigma(i)} \ar[rr]_{\iota_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
\end{definition}

\begin{remark}
The commutativity of the two rectangles above, is equivalent to the commutativity of the following bigger diagram.		
\[\xymatrix@C=40pt@R=10pt{ &&&R_{i}\ar[dddr]^{h'_i} \ar[dddl]_{h_i}|(.67)\hole\\&&K_i \ar[dl]_{l_i} \ar[ur]^{r}\ar[dddr]^{k'_i} \ar[dddl]_{k_i}|(.67)\hole\\&L_i\ar[dddr]_(.6){m'_i} \ar[dddl]_{m_i}\\&&G_{i+1}  \ar@/^.3cm/[dddl]|(.35)\hole^(.7){\iota_{G_{i+1}}}&& G'_{\sigma(i)+1}\ar@/^.3cm/[dddl]^{\iota_{G'_{\sigma(i)+1}}}\\ & D_i \ar[dd]_{\iota_{D_i}}\ar[ur]^(.6){g_i}  \ar[dl]_{f_i}&& D'_\sigma(i) \ar[dd]^{\iota_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_{f'_{\sigma(i)}}\\ G_i \ar@/_.3cm/[dr]_{\iota_{G_i}} && G'_{\sigma(i)}\ar@/_.3cm/[dr]^{\iota_{G'_{\sigma(i)}}}\\& \tpro{D} \ar[rr]_{\xi}&& \lpro \der{D}' \rpro}\]

Indeed,  to prove the commutativity of the central pentagon we can compute to get:
\begin{align*}
	\xi \circ \iota_{D_i}\circ k_i&=\xi \circ \iota_{G_{i}} \circ f_i\\&= \xi \circ \iota_{G_{i}}\circ m_i \circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ m'_i\circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ f'_{\sigma(i)}\circ k'_i\\&=\iota_{D'_\sigma(i)}\circ k_i'
\end{align*}
\end{remark}

\begin{example} Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ be two abstraction equivalent non-empty derivations. Then the identity permutation $\id{n+1}$ is a consistent permuation between them. In such a case $\xi$ is simply the isomorphism induced by the $\{\phi^i\}_{i=0}^n$.
\end{example}

\begin{example}\todo{esempi di cose equivalenti}
\end{example}

\begin{lemma}\label{lem:unique}\todo{Questo è il punto 2 di Lemma 17}
	contenuto...
\end{lemma}
\begin{proof}
	contenuto...
\end{proof}

\begin{corollary}\label{cor:unique}
	contenuto...
\end{corollary}

\section{Switch equivalence and traces}
\todo{A VERY NICE INTRO}

\subsection{Sequentially independend ndependent and switchable derivations}
\todo{A VERY NICE INTRO}

\begin{definition}  Let $(\X, R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category. Let also $\dder{D}:G\Mapsto H$ and $\dder{D'}:H\Mapsto T$ be the two direct derivations depicted below.

\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]

An \emph{independence pair} between $\dder{D}$ and $\dder{D'}$, is a pair of  arrows $i_1:R\to D'$ and $i_2:L'\to D$ such that the following diagram commutes.

\[\xymatrix@C=12pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
We will say that $\dder{D}$ and $\dder{D'}$ are \emph{weakly sequentially independent} if an independence pair exists. If such independence pair is unique we will say that $\dder{D}$ and $\dder{D'}$ are \emph{sequentially independent}.
\end{definition}

\begin{example}
	\todo{sequential independence}
\end{example}
\begin{example}
	\todo{sequential independence che serva anche per es successivo}
\end{example}

\begin{remark} Let $(i_1, i_2)$ and $(j_1, j_2)$ be independence pairs for the direct derivations $\dder{D}$ and $\dder{D'}$. Notice that, by definition, we have
	\begin{align*}f'\circ i_1&=h\\&=f'\circ j_1
	\end{align*}
	On the other hand, 
	 $f':D'\to H$ is  the pushout of $l':K'\to L'$ and so it is in $\mathcal{M}$, implying $j_1=i_1$.

	 On the other hand, if the rules $\rho$ applied in $\dder{D}$ is linear, then $g:D\to H$ is in $\mathcal{M}$, hence, from the equation
	 \begin{align*}
	 g\circ i_2&=h \\&= g\circ j_2
	 \end{align*}
we can deduce that $i_2=j_2$, too.

Summing up, it all the rules of $(\X, R)$ are linear, then sequential independence and weak sequential independence coincide. 
\end{remark}

When working with linear rewriting systems, (weakly) sequential independent direct derivations can be switched, producing two new (weakly) sequential independent direct derivations between the same objects \cite[Thm.~$7.7$]{lack2005adhesive} . This is no more the case if the rules are only left-linear, as shown by the next example.

\begin{example}
	\todo{pensare ad un esempio in cui l'indipendenza non basta (o farsi venire in mente una dimostrazione della prop. 13 della versione su arxiv)}
\end{example}

To fix this problem, we adapt the notion of \emph{canonical filler} from \cite{heindel2009category}.

\begin{definition}
Let $(\X, R)$ be a left-linear DPO-rewriting system with $\X$ $\mathcal{M}$-adhesive. Let also $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ be the two derivations depicted below.
\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
Since $f'$ is in $\mathcal{M}$, we can moreover consider a pullback square
\[\xymatrix{P \ar[r]^{p} \ar[d]_{p'}& D\ar[d]^{g} \\ D' \ar[r]_{f'} & H}\]

A \emph{filler} $\dder{D}$ and $\dder{D}'$ is  given by a pair of arrows $u:K\to P$ and $u':K'\to P$ satisfying the following conditions
\begin{enumerate}
	\item $p\circ u = k$, $p'\circ u' = k'$ and there exists a pushout square
\[\xymatrix{K' \ar[r]^{r'} \ar[d]_{u'}& R'\ar@{.>}[d]^{j} \\ P \ar@{.>}[r]_{q'} & Q'}\]
	\item  there exist arrows $i_1:R\to D'$, $i_2:L'\to D$ satisfying $f'\circ i_1=h$, $g\circ i_2=n'$ and such that the following squares are pushouts
\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar@{.>}[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar@{.>}[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
\end{enumerate}

We will say that $\dder{D}$ and $\dder{D}'$ are \emph{switchable} if a filler between them exists. If such a filler is unique, we will say that $\dder{D}$ and $\dder{D}'$ are \emph{properly switchable}. We will use the notation $\dder{D}\updownarrow \dder{D'}$ to mean that $\dder{D}$ and $\dder{D}'$ are switchable, while $\dder{D}\Updownarrow \dder{D'}$ will denote that they are properly so.
\end{definition}

\begin{remark}\label{rem:obv}Notice that if $\dder{D}$ and $\dder{D}'$ are switchable, then they are weakly sequentially independent: indeed, if a filler between them exists, then $(i_1, i_2)$ is an independence pair.
\end{remark}

\begin{remark}\label{rem:deco} Let $\dder{D}$ and $\dder{D'}$ be two switchable direct derivations. Then the existence of a filler allows us to build the solid part of the diagram below.
	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1} \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@{.>}@/_.8cm/[ddrr]_{j'}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar@{.>}[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar@{.>}[ul]_{s} &&Q'\ar@{.>}[ur]^{t}}\]

Let us complete this diagram defining the dotted arrows. We can start noticing that, since $l\in \mathcal{M}$, there exists a pushout square 
	\[\xymatrix{K \ar[r]^{l} \ar[d]_{u}& L\ar@{.>}[d]^{j'} \\ P \ar[r]_{q} & Q}\]
Moreover, the existence of the wanted $s:Q\to G$ and $t:Q'\to T$ follows from the following equalities
\[\begin{split}
f\circ p \circ u &= f\circ k \\&= n\circ l
\end{split} \qquad \begin{split}
g'\circ p'\circ u' &= g'\circ k'\\&=h'\circ r'
\end{split}\]

We can prove some other properties of the arrows appearing in the diagram above.
\begin{itemize}
	\item The three rectangles below are pushouts and their left halves are pushouts too. Therefore, by \Cref{lem:po1}, also their right halves are pushouts.
	\[\xymatrix{K \ar@/^.4cm/[rr]^{u}\ar[d]_{r}\ar[r]_{u} &P\ar[d]^{p'} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{l'}\ar[r]_{u'} &P\ar[d]^{p} \ar[r]_{p'} & D' \ar[d]^{f'}\\  R \ar@/_.4cm/[rr]_{h} \ar[r]^{i_1}&D' \ar[r]^{f'} & H&L' \ar@/_.4cm/[rr]_{n'} \ar[r]^{i_2}&D \ar[r]^{g} & H}\]
	\[ \xymatrix{K \ar@/^.4cm/[rr]^{k}\ar[d]_{l}\ar[r]_{u} &P\ar[d]^{q} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{r'}\ar[r]_{u'} &P\ar[d]^{q'} \ar[r]_{p'} & D' \ar[d]^{g'}\\ L \ar@/_.4cm/[rr]_{n} \ar[r]^{j'}&Q \ar[r]^{s} & G&R' \ar@/_.4cm/[rr]_{h'} \ar[r]^{j}&Q' \ar[r]^{t} & T}\]
\end{itemize}
\end{remark}

Before proceeding further, let us show that, in the linear case, the switchability relation reduces to sequential independence.

\begin{proposition}
	\todo{se il sistema è lineare}
\end{proposition}
\begin{proof}
	contenuto...
\end{proof}

We are now going to justify the choice of the name for the relation $\updownarrow$, showing that two switchable direct derivations $\dder{D}$ and $\dder{D'}$ can be actually switched. Consider the following diagram: the solid part exists by the definition of a filler, while the two new dotted arrows $v:Q\to J$ and $v':Q'\to J$ are obtained  as the pushout of $q:P\to Q$, which is in $\mathcal{M}$ by \Cref{rem:deco}, along $q':P\to Q'$.
	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@/_.8cm/[ddrr]_{j'}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar[ul]_{s}\ar@{.>}[dr]_{v} &&Q'\ar[ur]^{t} \ar@{.>}[dl]^{v'}\\&&&J}\]

	Since, by \Cref{rem:deco}, all the curved rectangles are pushouts, as well as the bottom square, we can state the following definition.
\begin{definition}
	Let $(\X,R)$ be a left-linear DPO-rewriting system and suppose that $\X$ is $\mathcal{M}$-adhesive. Given two switchable direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, we can define other two direct derivations $I_{\dder{D}'}:G\Mapsto J$ and $I_{\dder{D}}:J\Mapsto T$ as follows:
		\[\xymatrix{L' \ar[d]_{f\circ i_2}& \ar[l]_{l'}K'\ar[d]_{q\circ u'} \ar[r]^{r'} & R' \ar[d]_{v'\circ j} & L \ar[d]_{v\circ j'} & \ar[l]_{l}K \ar[d]^{q'\circ u}\ar[r]^{r}& R \ar[d]^{g'\circ i_1}\\
		G &\ar[l]^{s} Q \ar[r]_{v}& J&J & \ar[l]^{v'}Q' \ar[r]_{t} & T}\]
	The \emph{switching} $\sder{D}{D'}$ of $\dder{D}$ and $\dder{D'}$ is the derivation $I_{\dder{D'}} \cdot I_{\dder{D}}$.
\end{definition}

\begin{remark}Notice that $(j, j')$ is an independence pair for $I_{\dder{D}'}$ and $I_{\dder{D}}$. This is wintessed by the following diagram, commutative by construction.
	\[\xymatrix@C=15pt{L' \ar[d]_{f\circ i_2}&& K \ar[d]_{q\circ u'}\ar[ll]_{l'} \ar[r]^{r'} & R' \ar@/^.35cm/[drrr]_(.4){j}|(.285)\hole \ar[dr]|(.28)\hole_{v'\circ j} && L \ar@/_.35cm/[dlll]^(.4){j'} \ar[dl]|(.28)\hole^{v\circ j'}& K \ar[d]^{q'\circ u}\ar[l]_{l} \ar[rr]^{r} && R \ar[d]^{g'\circ i_1}\\G && \ar[ll]^{s} Q \ar[rr]_{v}&& J  && \ar[ll]^{v'} Q' \ar[rr]_{t}&& T}\]
\end{remark}

\begin{example}\todo{controesempio sul fatto che scambiando posso avere debolezza}
\end{example}

\begin{example}\todo{esempio sul perché weakly independence/scambiabilità non basta nel caso non lineare}
\end{example}

\begin{proposition}bla blah 
		unicità del filler implica unicitò degli ind pair
\end{proposition}
\begin{proof}
	contenuto...\qed 
\end{proof}

\begin{definition}Let $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system $(\X, R)$. We will say that $\dder{D}$ and $\dder{D}'$ are \emph{properly interchangeable} if:
	\begin{enumerate}
		\item $\dder{D}$ and $\dder{D}'$ are sequentially independent;
		\item $I_{\dder{D}'}$ and $I_{\dder{D}}$ are sequentially independent too.
	\end{enumerate}

	Take two derivations $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_{i}\}_{i=0}^n$ with the same length and between the same $G_0$ and $G_n$. We say that $\der{D}'$ is \emph{obtained by a switch from $\der{D}$} if there exists an index $j\in n$ such that
	\begin{itemize}
\item 
\item 		
	\end{itemize}

\end{definition}

\begin{lemma}\todo{Punto 1 del Lemma 17}
	contenuto...
\end{lemma}
\begin{proof}
	contenuto...
\end{proof}

\begin{example}\todo{permutazione consistente non implica scambiabilità}
\end{example}

\begin{lemma}
	\todo{lemma 19}
\end{lemma}
\begin{proof}
	contenuto...
\end{proof}

\subsection{Concatenable traces}
\begin{lemma}
	\todo{abstract equivalence and switch }
\end{lemma}
\begin{proof}
	contenuto...
\end{proof}
\begin{definition}
	\todo{tracce}
\end{definition}

\begin{theorem}
	\todo{preordine}
\end{theorem}
\begin{proof}
	contenuto...
\end{proof}

\section{ Domains for DPO-rewriting}

\subsection{weak domains}

\subsection{From adhesive grammars to weak domains}

\section{Conclusions and further work}
\todo{VERY NICE CONCLUSIONS}

\bibliographystyle{plain}
\bibliography{bibliog.bib}

\end{document}

### 2023-09-14 fusione.tex
cose

@@
 \newcommand{\dder}[1]{\mathscr{#1}}
-\newcommand{\sder}[2]{I(\mathscr{#1}, \mathscr{#2})}
+\newcommand{\sder}[2]{S_{u,u'}(\mathscr{#1}, \mathscr{#2})}
 \newcommand{\der}[1]{\underline{\dder{#1}}}
@@
 
-\todo{ESEMPI}
 We can list various examples of $\mathcal{M}$-adhesive categories (see \cite{castelnovo2023thesis,CastelnovoGM22,lack2006toposes}).
 
-\begin{example}Topos, ipergrafi e grafi
-\end{example}
-
-\begin{example}GRAFI GERARCHICI
-\end{example}
-
-\begin{example}term graph
+\begin{example}\todo{Topos, ipergrafi e grafi}
+\end{example}
+
+\begin{example}\todo{GRAFI GERARCHICI}
+\end{example}
+
+\begin{example}\todo{term graph}
 \end{example}
@@
 A \emph{left-linear DPO-rewriting system} is a pair $(\X, R)$ where $\X$ is a $\mathcal{M}$-adhesive category and $R$ is a set of left $\mathcal{M}$-linear rules.
+$(\X, R)$ will be called \emph{linear} if every rule in $R$ is so.
+
 Given  two objects $G$ and $H$ and a rule $\rho=(l,r)$ in $R$, a \emph{direct derivation $\mathscr{D}$ from $G$ to $H$ via $\rho$}, is a diagram as the one below, in which both squares are pushouts. 
@@
 Then there exist isomorphisms $t:D\to D'$ and $s:H\to H'$ as in the following diagram.
-	\[\xymatrix@C=30pt@R=10pt{ &&&R\ar[dddr]^{h'} \ar[dddl]_{h}|(.67)\hole\\&&K \ar[dl]_{l} \ar[ur]^{r}\ar[dddr]^{k'} \ar[dddl]_{k}\\&L \ar[dddl]_{n}\\&&H \ar@{.>}[rr]^{s} && H'\\ & D \ar[ur]^{g} \ar@{.>}[rr]^{t} \ar[dl]_{f}&& D' \ar[ur]_{g'}\ar@/^.3cm/[dlll]^{f'}\\ G}\]
+	\[\xymatrix@C=40pt@R=10pt{ &&&R\ar[dddr]^{h'} \ar[dddl]_{h}|(.67)\hole\\&&K \ar[dl]_{l} \ar[ur]^{r}\ar[dddr]^{k'} \ar[dddl]_{k}\\&L \ar[dddl]_{n}\\&&H \ar@{.>}[rr]^{s} && H'\\ & D \ar[ur]^{g} \ar@{.>}[rr]^{t} \ar[dl]_{f}&& D' \ar[ur]_{g'}\ar@/^.4cm/[dlll]^{f'}\\ G}\]
 \end{proposition}
@@
 \end{definition}
-\begin{remark}
+\begin{remark}\label{rem:res}
 	We can restate \Cref{prop:unique}: it asserts that, given two direct derivations $\dder{D}$ and $\dder{D'}$ with the same match, there exists an abstract equivalence between them whose first component is an identity.
@@
 
-\begin{example}\todo{esempi di cose equivalenti}
+\begin{example}\todo{esempi di cose consistenti utile per \cref{ex:contro}}
 \end{example}
@@
 
-\[\xymatrix@C=12pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
+\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
 We will say that $\dder{D}$ and $\dder{D'}$ are \emph{weakly sequentially independent} if an independence pair exists.
@@
 
-\begin{remark} Let $(i_1, i_2)$ and $(j_1, j_2)$ be independence pairs for the direct derivations $\dder{D}$ and $\dder{D'}$. Notice that, by definition, we have
+\begin{remark}\label{rem:weak} Let $(i_1, i_2)$ and $(j_1, j_2)$ be independence pairs for the direct derivations $\dder{D}$ and $\dder{D'}$. Notice that, by definition, we have
 	\begin{align*}f'\circ i_1&=h\\&=f'\circ j_1
@@
 	 $f':D'\to H$ is  the pushout of $l':K'\to L'$ and so it is in $\mathcal{M}$, implying $j_1=i_1$.
-
-	 On the other hand, if the rules $\rho$ applied in $\dder{D}$ is linear, then $g:D\to H$ is in $\mathcal{M}$, hence, from the equation
+If, moreover, we suppose that the rule $\rho$ applied in $\dder{D}$ is linear, then $g:D\to H$ is in $\mathcal{M}$ too, hence, from the equation
 	 \begin{align*}
@@
 
-Summing up, it all the rules of $(\X, R)$ are linear, then sequential independence and weak sequential independence coincide. 
+Summing up, if $(\X, R)$ is a linear DPO-rewriting system, then sequential independence and weak sequential independence coincide. 
 \end{remark}
@@
 
-\begin{definition}
+\begin{definition}\label{def:filler}
 Let $(\X, R)$ be a left-linear DPO-rewriting system with $\X$ $\mathcal{M}$-adhesive. Let also $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ be the two derivations depicted below.
@@
 
-A \emph{filler} $\dder{D}$ and $\dder{D}'$ is  given by a pair of arrows $u:K\to P$ and $u':K'\to P$ satisfying the following conditions
+A \emph{filler} between $\dder{D}$ and $\dder{D}'$ is  given by a pair of arrows $u:K\to P$ and $u':K'\to P$ satisfying the following conditions
 \begin{enumerate}
 	\item $p\circ u = k$, $p'\circ u' = k'$ and there exists a pushout square
-\[\xymatrix{K' \ar[r]^{r'} \ar[d]_{u'}& R'\ar@{.>}[d]^{j} \\ P \ar@{.>}[r]_{q'} & Q'}\]
+\[\xymatrix{K' \ar[r]^{r'} \ar[d]_{u'}& R'\ar@{.>}[d]^{j'} \\ P \ar@{.>}[r]_{q'} & Q'}\]
 	\item  there exist arrows $i_1:R\to D'$, $i_2:L'\to D$ satisfying $f'\circ i_1=h$, $g\circ i_2=n'$ and such that the following squares are pushouts
@@
 We will say that $\dder{D}$ and $\dder{D}'$ are \emph{switchable} if a filler between them exists.
-If such a filler is unique, we will say that $\dder{D}$ and $\dder{D}'$ are \emph{properly switchable}.
-We will use the notation $\dder{D}\updownarrow \dder{D'}$ to mean that $\dder{D}$ and $\dder{D}'$ are switchable, while $\dder{D}\Updownarrow \dder{D'}$ will denote that they are properly so.
-\end{definition}
+If such a filler is unique, we will say that $\dder{D}$ and $\dder{D}'$ are \emph{uniquely switchable}.
+We will use the notation $\dder{D}\updownarrow \dder{D'}$ to mean that $\dder{D}$ and $\dder{D}'$ are switchable, while $\dder{D}\updownarrow_!
+\dder{D'}$ will denote that they are uniquely so.
+\end{definition}
+
+\begin{remark}\todo{oss su unicità del filler}
+\end{remark}
 
@@
 \begin{remark}\label{rem:deco} Let $\dder{D}$ and $\dder{D'}$ be two switchable direct derivations. Then the existence of a filler allows us to build the solid part of the diagram below.
-	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1} \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@{.>}@/_.8cm/[ddrr]_{j'}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar@{.>}[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar@{.>}[ul]_{s} &&Q'\ar@{.>}[ur]^{t}}\]
+	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole  \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@{.>}@/_.8cm/[ddrr]_{j}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j'}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar@{.>}[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar@{.>}[ul]_{s} &&Q'\ar@{.>}[ur]^{t}}\]
 
 Let us complete this diagram defining the dotted arrows. We can start noticing that, since $l\in \mathcal{M}$, there exists a pushout square 
-	\[\xymatrix{K \ar[r]^{l} \ar[d]_{u}& L\ar@{.>}[d]^{j'} \\ P \ar[r]_{q} & Q}\]
+	\[\xymatrix{K \ar[r]^{l} \ar[d]_{u}& L\ar[d]^{j} \\ P \ar[r]_{q} & Q}\]
 Moreover, the existence of the wanted $s:Q\to G$ and $t:Q'\to T$ follows from the following equalities
@@
 	\item The three rectangles below are pushouts and their left halves are pushouts too. Therefore, by \Cref{lem:po1}, also their right halves are pushouts.
+	\[\xymatrix{K \ar@/^.4cm/[rr]^{u}\ar[d]_{r}\ar[r]_{u} &P\ar[d]^{p'} \ar[r]_{p} & D \ar[d]^{g}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{l'}\ar[r]_{u'} &P\ar[d]^{p} \ar[r]_{p'} & D' \ar[d]^{f'}\\  R \ar@/_.4cm/[rr]_{h} \ar[r]^{i_1}&D' \ar[r]^{f'} & H&L' \ar@/_.4cm/[rr]_{n'} \ar[r]^{i_2}&D \ar[r]^{g} & H}\]
+	\[ \xymatrix{K \ar@/^.4cm/[rr]^{k}\ar[d]_{l}\ar[r]_{u} &P\ar[d]^{q} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{r'}\ar[r]_{u'} &P\ar[d]^{q'} \ar[r]_{p'} & D' \ar[d]^{g'}\\ L \ar@/_.4cm/[rr]_{n} \ar[r]^{j}&Q \ar[r]^{s} & G&R' \ar@/_.4cm/[rr]_{h'} \ar[r]^{j'}&Q' \ar[r]^{t} & T}\]
+\end{itemize}
+\end{remark}
+
+Before proceeding further, let us show that, in the linear case, the switchability relation reduces to sequential independence.
+
+\begin{proposition}Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, R)$ a linear DPO-rewriting system.
+Given two direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, the following are equivalent:
+	\begin{enumerate}
+		\item there exists a filler between $\dder{D}$ and $\dder{D'}$;
+		\item $\dder{D}$ and $\dder{D'}$ are sequentially independent.
+	\end{enumerate}
+ \end{proposition}
+\begin{proof} $(1\Rightarrow 2)$ This follows immediately from \Cref{rem:weak,rem:deco}.
+
+	\smallskip \noindent $(2\Rightarrow 1)$  By hypothesis, we have a diagram
+	\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
+Pulling back $g$ along $f'$, we get another diagram 
+	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@{.>}@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@{.>}@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} && D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar[dl]^{h'}\\&G &&P\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T}\]
+Now, if we compute we get
+\[\begin{split}
+	f'\circ i_1\circ r &= h\circ r \\&= g\circ k
+\end{split}\qquad \begin{split}
+g\circ i_2\circ l' &= n'\circ l'\\&=f'\circ k'
+\end{split}\]
+Therefore the two dotted arrows $u:K\to P$ and $u':K'\to P$ exist. We have to show that they satisfy the two conditions in the definition of a filler. 
+\begin{enumerate}
+	\item  By construction $p\circ u = k$ and $p'\circ u'=k'$. Since $(\X, R)$ is linear, then $r':K'\to R'$ belongs to $\mathcal{M}$, thus it admits a pushout along $u':K'\to P$, as wanted.
+	\item Take the following two rectangles
 \[\xymatrix{K \ar@/^.4cm/[rr]^{u}\ar[d]_{r}\ar[r]_{u} &P\ar[d]^{p'} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{l'}\ar[r]_{u'} &P\ar[d]^{p} \ar[r]_{p'} & D' \ar[d]^{f'}\\  R \ar@/_.4cm/[rr]_{h} \ar[r]^{i_1}&D' \ar[r]^{f'} & H&L' \ar@/_.4cm/[rr]_{n'} \ar[r]^{i_2}&D \ar[r]^{g} & H}\]
-	\[ \xymatrix{K \ar@/^.4cm/[rr]^{k}\ar[d]_{l}\ar[r]_{u} &P\ar[d]^{q} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{r'}\ar[r]_{u'} &P\ar[d]^{q'} \ar[r]_{p'} & D' \ar[d]^{g'}\\ L \ar@/_.4cm/[rr]_{n} \ar[r]^{j'}&Q \ar[r]^{s} & G&R' \ar@/_.4cm/[rr]_{h'} \ar[r]^{j}&Q' \ar[r]^{t} & T}\]
-\end{itemize}
-\end{remark}
-
-Before proceeding further, let us show that, in the linear case, the switchability relation reduces to sequential independence.
+	By hypothesis $r$ and $l'$ are in $\mathcal{M}$, thus $f'$ and $g$ belong to it too. The first point of \Cref{lem:popb}  yields the thesis. \qed 
+\end{enumerate}
+\end{proof}
+
+We are now going to justify the choice of the name for the relation $\updownarrow$, showing that two switchable direct derivations $\dder{D}$ and $\dder{D'}$ can be actually switched.
+Consider the following diagram: the solid part exists by the definition of a filler, while the two new dotted arrows $v:Q\to J$ and $v':Q'\to J$ are obtained  as the pushout of $q:P\to Q$, which is in $\mathcal{M}$ by \Cref{rem:deco}, along $q':P\to Q'$.
+	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@/_.8cm/[ddrr]_{j}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j'}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar[ul]_{s}\ar@{.>}[dr]_{v} &&Q'\ar[ur]^{t} \ar@{.>}[dl]^{v'}\\&&&J}\]
+
+	Since, by \Cref{rem:deco}, all the curved rectangles are pushouts, as well as the bottom square, we can state the following definition.
+\begin{definition}
+	Let $(\X,R)$ be a left-linear DPO-rewriting system and suppose that $\X$ is $\mathcal{M}$-adhesive.
+Given two switchable direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, with a filler $(u,u')$, we can define other two direct derivations $S_{u,u'}(\dder{D}'):G\Mapsto J$ and $S_{u,u'}(\dder{D}):J\Mapsto T$ as follows:
+		\[\xymatrix{L' \ar[d]_{f\circ i_2}& \ar[l]_{l'}K'\ar[d]_{q\circ u'} \ar[r]^{r'} & R' \ar[d]_{v'\circ j'} & L \ar[d]_{v\circ j} & \ar[l]_{l}K \ar[d]^{q'\circ u}\ar[r]^{r}& R \ar[d]^{g'\circ i_1}\\
+		G &\ar[l]^{s} Q \ar[r]_{v}& J&J & \ar[l]^{v'}Q' \ar[r]_{t} & T}\]
+	The \emph{switching} $\sder{D}{D'}$ of $\dder{D}$ and $\dder{D'}$ is the derivation $S_{u,u'}(\dder{D}')\cdot S_{u,u'}(\dder{D})$.
+\end{definition}
+
+\begin{remark}\label{rem:indip}Notice that $(j', j)$ is an independence pair for $I_{\dder{D}'}$ and $I_{\dder{D}}$. This is witnessed by the following diagram, commutative by construction.
+	\[\xymatrix@C=15pt{L' \ar[d]_{f\circ i_2}&& K' \ar[d]_{q\circ u'}\ar[ll]_{l'} \ar[r]^{r'} & R' \ar@/^.35cm/[drrr]_(.4){j'}|(.285)\hole \ar[dr]|(.28)\hole_{v'\circ j'} && L \ar@/_.35cm/[dlll]^(.4){j} \ar[dl]|(.28)\hole^{v\circ j}& K \ar[d]^{q'\circ u}\ar[l]_{l} \ar[rr]^{r} && R \ar[d]^{g'\circ i_1}\\G && \ar[ll]^{s} Q \ar[rr]_{v}&& J  && \ar[ll]^{v'} Q' \ar[rr]_{t}&& T}\]
+\end{remark}
+
+\begin{proposition}\label{prop:fil}Let $(\X, R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
+Then every filler between two direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ is a filler also for $S_{u,u'}(\dder{D'}):G\Mapsto J$ and $S_{u,u'}(\dder{D}): J\Mapsto H$.
+In particular, if $\dder{D}\updownarrow \dder{D}'$, then $S_{u,u'}(\dder{D}')\updownarrow S_{u,u'}(\dder{D})$.
+\end{proposition}
+\begin{proof}By definition of filler, we have two pushout square
+		\[\xymatrix{K \ar[r]^{l} \ar[d]_{u}& L \ar[d]^{j} & K' \ar[r]^{r'} \ar[d]_{u'} & R' \ar[d]^{j'}\\ P \ar[r]_q & Q & P \ar[r]_{q'} & Q'}\]
+		In particular, $q$ is an arrow of $\mathcal{M}$, therefore, by \Cref{prop:pbpoad}, the square below is a pullback.
+		\[\xymatrix{P \ar[r]^{q} \ar[d]_{q'}& Q\ar[d]^{v}\\ Q' \ar[r]_{v'} & J}\]
+		To prove our claim, it is now enough to show that $(u',u)$ is a filler between $S_{u,u'}(\dder{D}')$ and $S_{u, u'}(\dder{D})$.
+		\begin{enumerate}
+			\item As for the first  point of \Cref{def:filler}, the only non obvious part is the existence of a pushout of $u$ along $r$.
+But, since $(u,u')$ is a filler between $\dder{D}$ and $\dder{D'}$, we know that such a pushout exists: it is enough to take the square
+			\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} \\P \ar[r]_{p'}& D'}\]
+			\item For the second point, notice that the arrows $j$ and $j'$ fit in the squares
+	\[\xymatrix{K' \ar[r]^{r'} \ar[d]_{u'}& R' \ar[d]^{j'} &K \ar[r]^{l} \ar[d]_{u}& L\ar[d]^{j} \\P \ar[r]_{q}& Q& P \ar[r]_{q'} & Q'}\]
+			By construction these squares are pushouts and we can conclude.			\qed 
+		\end{enumerate}
+\end{proof}
+
+The previous remark allow us to further switch the direct derivation $S_{u,u'}(\dder{D})$ and $S_{u,u'}(\dder{D}')$.
+The following lemma guarantees us that, in this way, we get back a derivation which is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
+
+\begin{lemma}\label{lem:rev}
+	Let $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system $(\X, R)$ and let $(u,u')$ be a filler between them.
+Then $S_{u',u}(S_{u,u'}(\dder{D}, \dder{D'}))$ is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
+\end{lemma}
+\begin{proof} By \Cref{prop:fil}, $(u', u)$ is a filler between $S_{u,u'}(\dder{D}')$ and $S_{u,u'}(\dder{D})$, thus we have a diagram as the one below.
+		\[\xymatrix{&&R' \ar@/_1cm/[ddrr]_(.35){j'}|(.7)\hole \ar[dr]^{v'\circ j'}&& L \ar@/^1cm/[ddll]^(.35){j}  \ar[dl]_{v\circ j}\\&K'\ar[dr]^{q\circ u'}\ar[dl]_{l'} \ar@/_.8cm/[ddrr]^(.65){u'}\ar[ur]^{r'}&& J && K \ar@/^.8cm/[ddll]_(.65){u}\ar[dl]_{q'\circ u}\ar[lu]_{l} \ar[dr]^{r}\\L' \ar[dr]^{f\circ i_2} \ar@/_.8cm/[ddrr]_{c_2}&& Q \ar[dl]|(.42)\hole_(.64){s}\ar[ur]|(.48)\hole^(.7){v}&&Q' \ar[dr]|(.42)\hole_(.65){t} \ar[ul]|(.48)\hole_(.7){v'}&&R\ar@/^.8cm/[ddll]^{c_1}\ar[dl]_{g'\circ i_1}\\&G &&P\ar[dr]^{e} \ar[dl]_{e'}\ar[ur]^(.4){q'}\ar[ul]_(.4){q}&&T\\&&E' \ar[ul]_{a}\ar[dr]_{w'} &&E\ar[ur]^{b} \ar[dl]^{w}\\&&&F}\]
+
+	Now, to ease the notation, let $S_{u',u}(S_{u,u'}(\dder{D}, \dder{D'}))$ be $\dder{E}_0\cdot \dder{E}_1$, then $\dder{E}_0$ and $\dder{E}_1$ are the direct derivations given by the diagrams
+	\[\xymatrix{L \ar[d]_{s\circ j}& K\ar[l]_{l} \ar[r]^{r} \ar[d]_{e'\circ u} & R \ar[d]_{w\circ c_1} & L' \ar[d]^{w'\circ c_2}& K' \ar[d]^{e\circ u'} \ar[r]^{r'} \ar[l]_{l'}& R' \ar[d]^{t\circ j'}\\G & E' \ar[l]^{a}  \ar[r]_{w'}& F & F & E \ar[l]^{w} \ar[r]_{b} & R}\]
+
+	Notice, moreover, that, since the squares
+	\[\xymatrix{K' \ar[d]_{u'} \ar[r]^{l'}& L' \ar[d]^{c_2} & K \ar[r]^{r}\ar[d]_{u} & R \ar[d]^{c_1}\\ P \ar[r]_{e'} & E' & P\ar[r]_e & E}\]
+	are pushouts, we have isomorphisms  $\phi': D\to E'$, $\phi:D'\to E$ making the following diagrams commutative.
+	\[\xymatrix{K' \ar[d]_{u'} \ar[r]^{l'}& L'\ar[d]^{i_2}  \ar@/^.2cm/[dr]^{c_2} & &K \ar[r]^{r}\ar[d]_{u} & R \ar[d]^{i_1} \ar@/^.2cm/[dr]^{c_1}\\ P \ar@/_.4cm/[rr]_{e'}\ar[r]^{p} & D\ar@{.>}[r]^{\phi'} &E'& P\ar@/_.4cm/[rr]_{e}\ar[r]^{p'} & D'\ar@{.>}[r]^{\phi}& E}\]
+	In particular, we have
+	\[\begin{split}
+		a\circ \phi' \circ i_2&=a \circ c_2\\&=f\circ i_2\\&
+	\end{split}\quad \begin{split}
+	a\circ \phi' \circ p'&=a \circ e'\\&=s\circ q\\&=f\circ p
+	\end{split}\quad \begin{split}
+	b\circ \phi \circ i_1&=b \circ c_1\\&=g'\circ i_1\\&
+	\end{split}\quad \begin{split}
+	b\circ \phi \circ p&=b \circ e\\&=t\circ q'\\&=g'\circ p'
+	\end{split} \]
+	and this shows that 
+	\[a\circ \phi'=f \qquad b\circ \phi = g'\]
+	Now, since $\phi'$ is an isomorphism and by \Cref{prop:pbpoad}, the two halves of the rectangle
+	\[\xymatrix{K\ar[r]^{\id{K}} \ar[d]_{(\phi')^{-1} \circ e' \circ u}&K\ar[d]_{e'\circ u} \ar[r]^{l} & L \ar[d]^{s\circ j} \\D\ar[r]_{\phi'} & E' \ar[r]_{a}&G}\]
+	are pullbacks.
+Thus the whole diagram is a pullback.
+But, by construction $s\circ j =n$ and we have already proved that $a\circ \phi'=f$.
+We then conclude that ther exists an isomorphism $\zeta:K\to K$ which makes the diagram below commutative
+	\[\xymatrix{K \ar@{.>}[r]_{\zeta}\ar@/^.4cm/[rr]^{l}  \ar@/_.5cm/[dr]_{(\phi')^{-1} \circ e' \circ u}& K \ar[r]_{l} \ar[d]_{n} & L \ar[d]^{n} \\ & D \ar[r]_{f} & G}\]
+	The commutativity of the upper triangle entails
+	\[l\circ \zeta=l\]
+	but $l$, being an element of $\mathcal{M}$ is mono, so that $\zeta=\id{K}$. From this, we can conclude that
+	\[e'\circ u = \phi' \circ k\]
+
+	As a next step, notice the existence of $\phi$ and $\phi'$, together with \cref{rem:deco}, entails  the existence of a third isomorphism $\psi:H\to F$ fitting in the diagram below.
+	\[\xymatrix{P  \ar[d]^{p'}\ar@/_.4cm/[dd]_{e}\ar@/^.4cm/[rr]^{e'} \ar[r]_{p} & D \ar[d]^{g} \ar[r]_{\phi'} & E'\ar[d]^{w'}\\D' \ar[d]^{\phi} \ar[r]_{f'} & H\ar@{.>}[r]^{\psi} & F \\E \ar@/_.4cm/[urr]_{w}}\]
+Now, if we compute, we get
+\begin{align*}
+	\psi^{-1}\circ w\circ c_1&=f'\circ \phi^{-1}\circ c_1\\&=f'\circ i_1&=h
+\end{align*}
+	Summing up, we have just build the diagram below.	
+	\[\xymatrix@C=40pt@R=10pt{ &&&R\ar[dddr]^{w\circ c_1} \ar[dddl]_{h}|(.67)\hole\\&&K \ar[dl]_{l} \ar[ur]^{r}\ar[dddr]^{e'\circ u} \ar[dddl]_{k}|(.67)\hole\\&L\ar[dddr]^(.4){s\circ j} \ar[dddl]_(.4){n}\\&&H \ar[rr]^{\psi} && F\\ & D \ar[ur]_(.7){g} \ar[rr]^{\phi'} \ar[dl]_{f}&& E' \ar[ur]_{w'}\ar[dl]^{a}\\ G \ar[rr]_{\id{G}} && G}\]
+
+Next, we already know that
+\[t\circ j'= h' \quad w\circ \phi = \psi \circ f' \quad b\circ \phi = g'\]
+If we compute further, we also get
+\[\begin{split}
+	\psi^{-1}\circ w'\circ c_2 &= g\circ (\phi')^{-1}\circ c_2\\&=g\circ i_2\\&=n'
+\end{split}\qquad \begin{split}
+\phi^{-1}\circ e \circ u'&=p'\circ u'\\&= k'\\&
+\end{split}\]
+These equations allow us to conclude that the following diagram commutes.
+	\[\xymatrix@C=40pt@R=10pt{ &&&R'\ar[dddr]^{t\circ j'} \ar[dddl]_{h'}|(.67)\hole\\&&K' \ar[dl]_{l'} \ar[ur]^{r}\ar[dddr]^{e\circ u'} \ar[dddl]_{k}|(.67)\hole\\&L'\ar[dddr]^(.4){w'\circ c_2} \ar[dddl]_(.4){n'}\\&&T \ar[rr]^{\id{T}} && T\\ & D' \ar[ur]_(.7){g'} \ar[rr]^{\phi} \ar[dl]_{f'}&& E \ar[ur]_{b}\ar[dl]^{w}\\ H \ar[rr]_{\psi} && F}\]
+
+Putting together the two diagrams above we get the thesis. \qed 
+\end{proof}
+
+Our next step is to relate derivations which are equal ``up to switching''.
+
+\begin{definition} Let $(\X, R)$ be a left-linear DPO-rewriting system.
+Given two direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, we say that  $\dder{D}$ and $\dder{D}'$ are \emph{properly interchangeable} if $\dder{D}\updownarrow_!
+\dder{D'}$ and $S_{u,u'}(\dder{D}')\updownarrow_!S_{u,u'}(\dder{D})$, where $(u,u')$ is a filler between $\dder{D}$ and $\dder{D}'$.
+In such a case, we will write $\dder{D}\Updownarrow\dder{D}'$.
+
+Take two derivations $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_{i}\}_{i=0}^n$ with the same length and between the same $G_0$ and $G_n$.
+We say that $\der{D}'$ is \emph{obtained by a proper switch from $\der{D}$} if there exists an index $j < n$ such that
+	\begin{enumerate}
+\item for every $i\notin \{j, j+1\} $, $\dder{D}_i=\dder{D}'_i$;
+\item $\dder{D}_j \Updownarrow \dder{D}_{j+1}$;		
+\item $\dder{D}'_j\cdot \dder{D}'_{j+1} = S_{u,u'}(\dder{D}, \dder{D}')$.
+	\end{enumerate}
+
+	We will also say that $\der{D}$ is \emph{switch equivalent} to $\der{D}'$, if there exists a sequence, $\{\der{D}_i\}_{i=0}^n$ of derivations such that
+	\begin{enumerate}
+		\item $\der{D}_0=\der{D}$ and $\der{D}_n=\der{D}'$;
+		\item for every $i< n$, $\der{D}_{i+1}$ is obtained by a proper switch from $\der{D}_i$.
+	\end{enumerate}
+
+	We will write $\der{D} \equiv^s \der{D}'$ to denote that $\der{D}$ is switch equivalent to $\der{D}'$.
+\end{definition}
+
+\begin{example}
+	\todo{il punto due sopra è necessario}
+\end{example}
 
 \begin{proposition}
-	\todo{se il sistema è lineare}
+	\todo{reversibilità}
 \end{proposition}
@@
 \end{proof}
-
-We are now going to justify the choice of the name for the relation $\updownarrow$, showing that two switchable direct derivations $\dder{D}$ and $\dder{D'}$ can be actually switched.
-Consider the following diagram: the solid part exists by the definition of a filler, while the two new dotted arrows $v:Q\to J$ and $v':Q'\to J$ are obtained  as the pushout of $q:P\to Q$, which is in $\mathcal{M}$ by \Cref{rem:deco}, along $q':P\to Q'$.
-	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@/_.8cm/[ddrr]_{j'}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar[ul]_{s}\ar@{.>}[dr]_{v} &&Q'\ar[ur]^{t} \ar@{.>}[dl]^{v'}\\&&&J}\]
-
-	Since, by \Cref{rem:deco}, all the curved rectangles are pushouts, as well as the bottom square, we can state the following definition.
-\begin{definition}
-	Let $(\X,R)$ be a left-linear DPO-rewriting system and suppose that $\X$ is $\mathcal{M}$-adhesive.
-Given two switchable direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, we can define other two direct derivations $I_{\dder{D}'}:G\Mapsto J$ and $I_{\dder{D}}:J\Mapsto T$ as follows:
-		\[\xymatrix{L' \ar[d]_{f\circ i_2}& \ar[l]_{l'}K'\ar[d]_{q\circ u'} \ar[r]^{r'} & R' \ar[d]_{v'\circ j} & L \ar[d]_{v\circ j'} & \ar[l]_{l}K \ar[d]^{q'\circ u}\ar[r]^{r}& R \ar[d]^{g'\circ i_1}\\
-		G &\ar[l]^{s} Q \ar[r]_{v}& J&J & \ar[l]^{v'}Q' \ar[r]_{t} & T}\]
-	The \emph{switching} $\sder{D}{D'}$ of $\dder{D}$ and $\dder{D'}$ is the derivation $I_{\dder{D'}} \cdot I_{\dder{D}}$.
-\end{definition}
-
-\begin{remark}Notice that $(j, j')$ is an independence pair for $I_{\dder{D}'}$ and $I_{\dder{D}}$. This is wintessed by the following diagram, commutative by construction.
-	\[\xymatrix@C=15pt{L' \ar[d]_{f\circ i_2}&& K \ar[d]_{q\circ u'}\ar[ll]_{l'} \ar[r]^{r'} & R' \ar@/^.35cm/[drrr]_(.4){j}|(.285)\hole \ar[dr]|(.28)\hole_{v'\circ j} && L \ar@/_.35cm/[dlll]^(.4){j'} \ar[dl]|(.28)\hole^{v\circ j'}& K \ar[d]^{q'\circ u}\ar[l]_{l} \ar[rr]^{r} && R \ar[d]^{g'\circ i_1}\\G && \ar[ll]^{s} Q \ar[rr]_{v}&& J  && \ar[ll]^{v'} Q' \ar[rr]_{t}&& T}\]
-\end{remark}
-
-\begin{example}\todo{controesempio sul fatto che scambiando posso avere debolezza}
-\end{example}
-
-\begin{example}\todo{esempio sul perché weakly independence/scambiabilità non basta nel caso non lineare}
-\end{example}
-
-\begin{proposition}bla blah 
-		unicità del filler implica unicitò degli ind pair
-\end{proposition}
-\begin{proof}
-	contenuto...\qed 
-\end{proof}
-
-\begin{definition}Let $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system $(\X, R)$.
-We will say that $\dder{D}$ and $\dder{D}'$ are \emph{properly interchangeable} if:
-	\begin{enumerate}
-		\item $\dder{D}$ and $\dder{D}'$ are sequentially independent;
-		\item $I_{\dder{D}'}$ and $I_{\dder{D}}$ are sequentially independent too.
-	\end{enumerate}
-
-	Take two derivations $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_{i}\}_{i=0}^n$ with the same length and between the same $G_0$ and $G_n$.
-We say that $\der{D}'$ is \emph{obtained by a switch from $\der{D}$} if there exists an index $j\in n$ such that
-	\begin{itemize}
-\item 
-\item 		
-	\end{itemize}
-
-\end{definition}
+\begin{corollary}
+	\todo{ho davver una relazione di equivalenza}
+\end{corollary}
+
+\begin{example}\todo{esempio sul perché weakly independence non è invertibile}
+\end{example}
 
@@
 
-\begin{example}\todo{permutazione consistente non implica scambiabilità}
-\end{example}
+\begin{example}\label{ex:contro}\todo{permutazione consistente non implica scambiabilità}
+\end{example}
+
+Before moving forward, we will prove some other useful properties of the switch equivalence relation.
 

### 2023-09-15 fusione.tex
cose

@@
 
-\title{Fusion}
+\title{Switch equivalence and weak prime domains for fusions}
 
@@
 
-\begin{lemma}\cite{heindel2009category}
-	Let $\X$ be an $\mathcal{M}, \mathcal{N}$-adhesive category and $(\X, R)$ a left-linear DPO-rewriting system over it.
-Then for every non-empty derivation $\der{D}:G\to H$, the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belong to $\mathcal{M}$.
+\begin{lemma}\label{lem:colim}
+	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, R)$ a left-linear DPO-rewriting system over it. The following hold true:
+	\begin{enumerate}
+		\item if $\der{D}$ is a derivation of length one given by the following diagram
+
+		then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists and  fits in the diagram below, wher the bottom face is a pushout;
+		\[\xymatrix{}\]
+		\item 
+		\item  for every non-empty derivation $\der{D}:G\to H$, the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belong to $\mathcal{M}$.
+	\end{enumerate}
+\end{lemma}
+\begin{proof}\begin{enumerate}
+		contenuto...
+	\end{enumerate}
+	contenuto...
+\end{proof}
+
+\begin{lemma}	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, R)$ a left-linear DPO-rewriting system over it.
+ Then
 \end{lemma}
@@
 Take two non-empty derivations $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with the same length with their associated sequences of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$.
-A permutation $\sigma:n+1\to n+1$  is called a \emph{consistent permutation} between $\der{D}$ and $\der{D}'$, if for every $i\in n+1$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists an isomorphism $\phi:\tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
+A permutation $\sigma:n+1\to n+1$  is called a \emph{consistent permutation} between $\der{D}$ and $\der{D}'$, if for every $i\in n+1$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists an isomorphism $\xi:\tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
 \[\xymatrix{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi} \\G'_{\sigma(i)} \ar[rr]_{\iota_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
@@
 	\end{enumerate}
-
-	We will also say that $\der{D}$ is \emph{switch equivalent} to $\der{D}'$, if there exists a sequence, $\{\der{D}_i\}_{i=0}^n$ of derivations such that
+	In such a case, we will write $\der{D}\rightsquigarrow_j \der{D}'$ to denote that $\der{D}'$ is obtained by a proper switch between $\dder{D}_j$ and $\dder{D}_{j+1}$.
+
+	We will say that $\der{D}$ is \emph{switch equivalent} to $\der{D}'$, if there exists a sequence, $\{\der{D}_i\}_{i=0}^n$ of derivations such that
 	\begin{enumerate}
@@
 
-\begin{proposition}
-	\todo{reversibilità}
-\end{proposition}
-\begin{proof}
-	contenuto...
-\end{proof}
-\begin{corollary}
-	\todo{ho davver una relazione di equivalenza}
-\end{corollary}
+We can now prove some properties of switch equivalence.
+\begin{lemma}\todo{Def. 3 della bozza di Andrea }Let $(\X, R)$ be a left-linear DPO-rewriting system. Then the following hold true: 
+	\begin{enumerate}
+		\item 
+		\item 
+		\item 
+		\item 
+	\end{enumerate}
+\end{lemma}
+\begin{proof}\begin{enumerate}
+		\item 
+		\item 
+		\item 
+		\item \qed 
+	\end{enumerate}
+\end{proof}
 
@@
 
-\begin{lemma}\todo{Punto 1 del Lemma 17}
-	contenuto...
+\begin{lemma} Let $(\X, R)$ be a left-linear DPO-rewriting system $(\X, R)$. Then the following hold true
+	\begin{enumerate}
+		\item If $\dder{D}$ and $\dder{D'}$ are two direct derivations such that $\dder{D}\updownarrow \dder{D'}$, then for every filler $(u,u')$ between them, the function
+		\[\tau:2\to2 \qquad x \mapsto \begin{cases}
+			1 & x=0\\
+			0 & x=1
+		\end{cases}\]
+		defines a consistent permutation between $\dder{D}\cdot \dder{D}'$ and $\sder{D}{D'}$;
+		\item if $\der{D}$ and $\der{D}'$ are two switch equivalent derivation, then there exists a consistent permutation between them.
+	\end{enumerate}
 \end{lemma}
 \begin{proof}
-	contenuto...
-\end{proof}
+	\begin{enumerate}
+		\item 
+		\item \qed 
+	\end{enumerate}
+\end{proof}
+ This, together with ???
+\begin{corollary}
+	\todo{unicità}
+\end{corollary}
 
@@
 \end{example}
-
-Before moving forward, we will prove some other useful properties of the switch equivalence relation.
-
-\begin{lemma}
-	\todo{lemma 19}
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
 
@@
 
+Before moving forward, we will prove some other useful properties of the switch equivalence relation.
+
+\begin{lemma}
+	\todo{lemma 19}
+\end{lemma}
+\begin{proof}
+	contenuto...
+\end{proof}
+
 \begin{theorem}

### 2023-09-19 fusione.tex
cose

@@
 \newcommand{\tpro}[1]{\lpro \der{#1}\rpro}
+\newcommand{\tproi}[2]{\lpro \der{#1}_{#2}\rpro}
 \newcommand{\lgt}[0]{\mathsf{length}}
@@
 	\begin{enumerate}
-		\item if $\der{D}$ is a derivation of length one given by the following diagram
-
-		then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists and  fits in the diagram below, wher the bottom face is a pushout;
-		\[\xymatrix{}\]
-		\item 
-		\item  for every non-empty derivation $\der{D}:G\to H$, the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belong to $\mathcal{M}$.
+		\item if $\der{D}$ is a derivation of length one, whose unique element is given by the following diagram
+	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G & \ar[l]^{f} D \ar[r]_{g}& H }\]	
+		then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists and  fits in the diagram below, where the bottom face is a pushout;
+		\[\xymatrix@R=10pt{&K\ar[dd]^{k}\ar[rr]^{r} \ar[dl]_{l} && R \ar[dd]^{h} \\ L  \ar[dd]_{m} \\&D\ar[rr]^{g} \ar[dl]_{f} && H \ar[dl]^{\iota_H} \\G \ar[rr]_{\iota_G} & & \tpro{D}}\]
+		\item  for every non-empty derivation $\der{D}$ from $G$ to $H$, the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belong to $\mathcal{M}$;
+		\item let $\der{D}$ be the concatenation $\der{D}_1\cdot \der{D}_2$ of two derivations $\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^{n_1}$ between $G$ and $H$ and $\der{D}_2=\{\dder{D}_{2,j}\}_{j=0}^{n_2}$ between $H$ and $T$,  then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists too and there is a pushout square
+		\[\xymatrix{H\ar[r]^-{\iota_{2, H}} \ar[d]_-{\iota_{1, H}} & \tproi{D}{2} \ar[d]^{p_2}\\  \tproi{D}{1} \ar[r]_{p_1}& \tpro{D}}\]
+		where $(\tproi{D}{1}, \{\iota_{1, X}\}_{X\in \Delta(\der{D}_1)})$ and $(\tproi{D}{2}, \{\iota_{2, X}\}_{X\in \Delta(\der{D}_2)})$ are the colimiting cocone for $\Delta(\der{D}_1)$ and $\Delta(\der{D}_2)$, respectively.
 	\end{enumerate}
@@
 \begin{proof}\begin{enumerate}
-		contenuto...
-	\end{enumerate}
-	contenuto...
-\end{proof}
-
-\begin{lemma}	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, R)$ a left-linear DPO-rewriting system over it.
- Then
-\end{lemma}
-\begin{proof}
-	We proceed by induction.
-	\begin{enumerate}
-		\item Suppose that $n=0$ so that $\der{D}$ consists only of the following direct derivation
-		\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G & \ar[l]^{f} D \ar[r]_{g}& H }\]
-		then $f\in \mathcal{M}$ so that we can consider its pushout along $g$ to get a diagram
-		\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G \ar@/_.2cm/[dr]_{q}& \ar[l]^{f} D \ar[r]_{g}& H  \ar@/^.2cm/[dl]^{p}\\ & P}\]
-		Let $(C, \{c_X\}_{X\in \Delta(\der{D})})$ be another cocone, in particular we have
+		\item We can start noticing that $f$, being the pushout of $l$ is in $\mathcal{M}$ and thus it admits a pushout along $g$, giving us the diagram 
+		\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G \ar@/_.2cm/[dr]_{q}& \ar[l]^{f} D \ar[r]_{g}& H  \ar@/^.2cm/[dl]^{p}\\ & P}\]
+		Clearly, precomposing $p$ and $q$ with the arrows appearing in $\dder{D}$, we can extend the pushout $(P, p, q)$, to a cocone $(P, \{j_X\}_{X\in \Delta(\der{D})})$ on $\Delta(\der{D})$.
+Let $(C, \{c_X\}_{X\in \Delta(\der{D})})$ be another cocone, for $\Delta(\der{D})$, in particular we have
 		\begin{align*}
@@
 		\end{align*}
-		Hence, there exists a unique $c:P\to C$ such that 
-		\[c\circ q= c_G \qquad c\circ p =c_H\]
-		Now, $f$ is in $\mathcal{M}$ as it is the pushout of $l$, hence $p$ is in $\mathcal{M}$ too and this gives us the thesis. 
+		Hence, there exists a unique $c:P\to C$ such that $c\circ q= c_G$ and $c\circ p =c_H$. But these identities are enough to deduce that $(P, \{j_X\}_{X\in \Delta(\der{D})})$  is colimiting.
+		\item Let us proceed by induction.
+		\begin{itemize}
+			\item  If $n=0$, then the claim follows immediately from point $1$, noticing that $\iota_H$ is the pushout of $f$ and thus an element of $\mathcal{M}$.
 			\item Let $\der{D}$ be $\{\dder{D}_i\}_{i=0}^n$ and suppose that $n\geq 1$.
@@
 			Therefore the arrows $c'$ and $c_H$ induce a morphism $c:P\to C$ and the thesis now follows at once.
-		\qed 
+		\end{itemize}
+		\item  As a first step, notice that $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D}_1)})$ and $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D}_2)})$ are cocone on, respectively, $\Delta(\der{D}_1)$ and $\Delta(\der{D}_2)$.
+Hence, there exist two arrows $p_1:\tproi{D}{1}\to \tpro{D}$, $p_2:\tproi{D}{2}\to \tpro{D}$ such that, for every $X\in  \Delta(\der{D}_1)$ and $Y\in  \Delta(\der{D}_2)$
+		\[p_1\circ \iota_{1, X} = \iota_X \qquad p_2\circ \iota_{2, Y}=\iota_{2,Y}\]
+		In particular, this entails the commutativity of the square
+				\[\xymatrix{H \ar[dr]^{\iota_H} \ar[r]^-{\iota_{2, H}} \ar[d]_-{\iota_{1, H}} & \tproi{D}{2} \ar[d]^{p_2}\\  \tproi{D}{1} \ar[r]_{p_1}& \tpro{D}}\]
+
+	Let us now show that the square above is a pushout. Take two arrows $a:\tproi{D}{1}\to C$, $b:\tproi{D}{2}\to C$ such that
+	\[a\circ \iota_{1, H}=b\circ \iota_{2, H}\]
+	We can use the previous equality to define a cocone $(C, \{c_X\}_{X\in \Delta(\der{D})})$ putting:
+	\[c_X:=\begin{cases}
+		a\circ \iota_{1, X} & X\in \Delta(\der{D}_1)\\
+		b\circ \iota_{2, X} & X\in \Delta(\der{D}_2)
+	\end{cases}\]
+From this, we can deduce at once the existence of a unique $c:\der{D}\to C$ such that 
+\[c\circ \iota_X = c_X\]
+By construction, for every $X\in  \Delta(\der{D}_1)$ and $Y\in  \Delta(\der{D}_2)$ we have
+\[\begin{split}
+	c\circ p_1 \circ \iota_{1,X}&=c\circ \iota_{1, X}\\&=c_X \\&=a\circ \iota_{1,X}\\&=a\circ p_1\circ \iota_{1,X}
+\end{split}\qquad \begin{split}
+	c\circ p_2 \circ \iota_{2,Y}&=c\circ \iota_{2, Y}\\&=c_Y \\&=b\circ \iota_{2,Y}\\&=b\circ p_2\circ \iota_{2,Y}
+\end{split}\]
+Therefore
+\[c\circ p_1=a \qquad c\circ p_2 = b\]
+
+	For uniqueness, suppose that $c':\der{D}\to C$ is such that
+	\[c'\circ p_1=a \qquad c'\circ p_2 = b\]
+Then, for every $X\in \der{D}$ we have
+\begin{align*}
+	c'\circ \iota_X &= \begin{cases}
+	c'\circ p_1\circ \iota_{1, X} & X\in \Delta(\der{D}_1)\\
+	c'\circ p_2\circ \iota_{2, X} & X\in \Delta(\der{D}_2)
+	\end{cases}\\&=\begin{cases}
+a\circ \iota_{1, X} & X\in \Delta(\der{D}_1)\\
+b\circ \iota_{2, X} & X\in \Delta(\der{D}_2)
+	\end{cases}\\&=c_X\\&=c\circ \iota_X
+\end{align*}
+showing that $c'=c$ as wanted.	\qed
 	\end{enumerate}
@@
 
-\subsection{Sequentially independend ndependent and switchable derivations}
+\subsection{Sequentially independendent and switchable derivations}
 \todo{A VERY NICE INTRO}
@@
 
-\begin{proposition}Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, R)$ a linear DPO-rewriting system.
+\begin{proposition}\label{prop:equi}Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, R)$ a linear DPO-rewriting system.
 Given two direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, the following are equivalent:
@@
 
+\begin{remark}\todo{riferminto a \Cref{app:fill}}
+\end{remark}
+
 We are now going to justify the choice of the name for the relation $\updownarrow$, showing that two switchable direct derivations $\dder{D}$ and $\dder{D'}$ can be actually switched.
+
 Consider the following diagram: the solid part exists by the definition of a filler, while the two new dotted arrows $v:Q\to J$ and $v':Q'\to J$ are obtained  as the pushout of $q:P\to Q$, which is in $\mathcal{M}$ by \Cref{rem:deco}, along $q':P\to Q'$.
@@
 \end{proposition}
+\begin{remark}\label{rem:locCR}
+\todo{questo è Church-Rosser}
+\end{remark}
 \begin{proof}By definition of filler, we have two pushout square
@@
 
+\subsection{Proper switchability is global}
+\todo{Tutto}
 \subsection{Concatenable traces}
@@
 
+\appendix
+\section{A note on fillers and sequential independence}\label{app:fill}
+ In \Cref{prop:equi} we proved that, in the linear case, the existence of an indpendence pair between two derivation is equivalent to that of a filler between them.
+This result can be further refined: in a\cite{baldan2011adhesivity} a class  $\mathbb{B}$ of (quasi)adhesive category is defined for which the local Church-Rosser Theorem holds even for left-linear DPO-rewriting system.
+In our language, and given \Cref{prop:fil} and \Cref{rem:locCR}, this amount to prove that, for elements of $\mathbb{B}$, every independence pair induces a filler.
+
+\begin{definition}
+	\todo{classe B e class B+}
+\end{definition}
+
+\begin{example}
+\todo{esempi}
+\end{example}
+
+\begin{example}
+	\todo{esempi}
+\end{example}
+
+\begin{definition}
+	\todo{due proprietà}
+\end{definition}
+
+\begin{proposition}
+	\todo{da B a B+}
+\end{proposition}
+\begin{proof}
+	contenuto... \qed 
+\end{proof}
+\begin{lemma}\todo{due proprietà classe B}
+\end{lemma}
+\begin{proof}
+	\qed 
+\end{proof}
+
+\begin{corollary}
+	\todo{due proprietà classe B+}
+\end{corollary}
+
+\begin{theorem}
+	\todo{filler e classe B+}
+\end{theorem}
+\begin{proof}\qed 
+\end{proof}
+
 \end{document}

### 2023-09-20 fusione.tex
cose

@@
 
+Finally, we can show that stable pushouts enjoy a kind of \emph{pullback-pushout decomposition} property.
+
+\begin{proposition}\label{prop:stab}Let $\X$ be a category  and suppose that, in the diagram below, the whole rectangle is a stable pushout and the right square a pullback.
+	\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
+	If the arrow $k$ is a monomorphism,  then both squares are pushouts.
+\end{proposition}
+
+\begin{proof} We can begin noticinng that $g$, being the pullback of the monomorphism $k$, is monic too. Thus we can build the cube below, in which all the vertical faces are pullbacks.
+	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y  \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
+	By hypothesis the face is a stable pushout and so its top one is a pushout. \Cref{lem:po1} now entails that the right half of the rectangle with which we have started is a pushout too. \qed 
+\end{proof}
+
 \subsection{$\mathcal{M}$-adhesivity}
@@
 	Let $\A$ and $\B$ be respectively an $\mathcal{M}$-adhesive and an $\mathcal{M}'$-adhesive category.
-Let also $L:\A\rightarrow \C$ be a functor that preserves $\mathcal{M}, \mathcal{N}$-pushouts, and  $R:\B\rightarrow \C$ be a functor which preserves pullbacks.Then $\comma{L}{R}$ is $\cma{M}{M'}$-adhesive, where
+Let also $L:\A\rightarrow \C$ be a functor that preserves $\mathcal{M}$-pushouts, and  $R:\B\rightarrow \C$ be a functor which preserves pullbacks.Then $\comma{L}{R}$ is $\cma{M}{M'}$-adhesive, where
 	\[
@@
 
-In particular, we can apply this result  to slices over a given object.
+In particular, we can apply this result to slices over and under a given object.
 
@@
 
+Another categorical construction which preserves adhesivity property is the formation of the category of functors.
+
+\begin{theorem}[\cite{CastelnovoGM22,ehrig2006fundamentals,lack2005adhesive}]\label{thm:functors}
+	contenuto...
+\end{theorem}
+
 We can list various examples of $\mathcal{M}$-adhesive categories (see \cite{castelnovo2023thesis,CastelnovoGM22,lack2006toposes}).
@@
 	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y \ar[rrr]|(.67)\hole^{b} \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
-	The bottom face is a Van Kampen square and so its top one is a pushout. The thesis now follows from \Cref{lem:po1}.
+	The bottom face is a Van Kampen square and so its top one is a pushout. The thesis now follows from \Cref{lem:po1}. This follows at once from \Cref{prop:stab}.
 	\item By hypothesis, $g$ is the pullback of an arrow in $\mathcal{M}$, thus belongs to it.
@@
 
-	Using again \Cref{lem:po1}, it is enough to show that the left half of the original rectangle is a pushout. We can build the same cube of the previous point:
+	Using \Cref{lem:po1}, it is enough to show that the left half of the original rectangle is a pushout. We can build the same cube of the previous point:
 	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y \ar[rrr]|(.67)\hole^{b} \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
@@
 
-\begin{lemma}\label{lem:unique}\todo{Questo è il punto 2 di Lemma 17}
+To proceed further, we have to introduce a notion from general category theory.
+
+\begin{definition}[\cite{borceux1994handbook1,adamek1994locally}]
+Let $\X$ be a category, a \emph{separator}, or \emph{generator}, is an object $S$ such that, for every pair of arrows $f, g:X\rightrightarrows Y$, if \[f\circ s = g\circ s\] for every $s:S\to X$, then $f=g$.
+
+Given a separator $S$, we will say that a morphism $f:X\to Y$,  is an \emph{$S$-surjection} if for every $s:S\to Y$  there exists $s':S\to X$ such that $f\circ s'= s$.
+\end{definition}
+
+\begin{example}
 	contenuto...
+\end{example}
+\begin{example}
+	contenuto...
+\end{example}
+
+\begin{proposition}
+Let $f:X\to Y$ be a morphism in a category $\X$ with a separator $S$, then every $S$-surjection is an epimorphism.
+\end{proposition}
+\begin{proof}
+	Let $f:X\to Y$ be an $S$-surjection, and suppose that there exist two arrows $g, h:Y\rightrightarrows Z$ such that 
+	\[g\circ f = h\circ f\]
+Since $f$ is an $S$-surjection, for every $s:S\to Y$ there exists $s':S\to X$ such that $f\circ s'=s$, so that
+\begin{align*}
+	g\circ s &= g\circ f \circ s'\\&=h\circ f \circ s'\\&= h\circ s
+\end{align*} 
+	The thesis now follows since $S$ is a separator.	 \qed 
+\end{proof}
+\begin{lemma}Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that every rule in $R$ is consuming.
+Given two non-empty derivations $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_{i}\}_{i=0}^n$, if $\X$ has a separator $S$, then there exists at most one consistent permutation between them.
 \end{lemma}
-\begin{proof}
-	contenuto...
+\begin{proof} Consider two permutations $\sigma$ and $\sigma': n+1 \rightrightarrows n+1$
 \end{proof}
@@
 
+\begin{definition}Let $\X$ be a category, we say that $\X$ satisfies
+	\begin{itemize}
+		\item the \emph{mixed decomposition} property if for every diagram
+		\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
+		whose outer boundary is a pushout and in which $k$ is a monomorphisms, 
+		\item the \emph{pushout decomposition} property
+	\end{itemize}
+\end{definition}
+
+\begin{lemma}
+	contenuto...
+\end{lemma}
+\begin{proof}
+	contenuto...\qed 
+\end{proof}
+
+\begin{corollary}
+	contenuto...
+\end{corollary}
+
+The following result shows that the mixed and pushout decomposition properties guarantee that every independence pair gives rise to a filler.
+
+\begin{theorem}
+	\todo{filler e classe B+}
+\end{theorem}
+\begin{proof}\qed 
+\end{proof}
+
+Our next step is to identify sufficient conditions for a category $\X$ to satisfy the mixed and pushout decomposition properties.
+
 \begin{definition}
@@
 \end{example}
-
-\begin{definition}
-	\todo{due proprietà}
-\end{definition}
 
@@
 
-\begin{theorem}
+\begin{corollary}
 	\todo{filler e classe B+}
-\end{theorem}
-\begin{proof}\qed 
-\end{proof}
+\end{corollary}
 

### 2023-09-27 fusione.tex
lemma perm consistente

@@
 \def\A{\textbf {\textup{A}}}
+
+\def\R{\mathsf{R}}
 \def\B{\textbf {\textup{B}}}
@@
 $\mathcal{M}$-adhesivity is well-behaved with respect to  the comma construction \cite{mac2013categories}, as shown by the following theorem.
-\begin{theorem}[\cite{CastelnovoGM22,ehrig2006fundamentals}]\label{lem:comma}
+\begin{theorem}[\cite{CastelnovoGM22,ehrig2006fundamentals,lack2005adhesive}]\label{lem:comma}
 	Let $\A$ and $\B$ be respectively an $\mathcal{M}$-adhesive and an $\mathcal{M}'$-adhesive category.
@@
 \begin{corollary}\label{cor:slice}
-	Let  $X$ be an object of an $\mathcal{M}$-adhesive category $\X$. Then  $\X/X$ is $\mathcal{M}/X$-adhesive, where
-	\[\mathcal{M}/X:=\{m\in  \mathcal{A}(\X/X) \mid m\in \mathcal{M} \}\]
+	Let  $X$ be an object of an $\mathcal{M}$-adhesive category $\X$. Then  $\X/X$ and $X/\X$ are, respectively, is $\mathcal{M}/X$- and $X/\mathcal{M}$-adhesive, where
+	\[\mathcal{M}/X:=\{m\in  \mathcal{A}(\X/X) \mid m\in \mathcal{M} \} \qquad X/\mathcal{M}:=\{m\in  \mathcal{A}(X/\X) \mid m\in \mathcal{M} \}\]
 \end{corollary}
 
-Another categorical construction which preserves adhesivity property is the formation of the category of functors.
+Another categorical construction which preserves $\mathcal{M}$-adhesivity property is the formation of the category of functors.
 
 \begin{theorem}[\cite{CastelnovoGM22,ehrig2006fundamentals,lack2005adhesive}]\label{thm:functors}
-	contenuto...
+If $\X$ is an $\mathcal{M}$-adhesive category, then for every small category $\Y$, the category $\X^\Y$  of functors $\Y\to \X$ is $\mathcal{M}^{\Y}$-adhesive, where
+\[\mathcal{M}^{\Y}:=\{\eta \in \mathcal{A}(\X^\Y) \mid \eta_Y \in \mathcal{M} \text{ for every } Y\in \Y\}\]
 \end{theorem}
@@
 \begin{enumerate}
-	\item 	We can begin noticing that $c$ is an element of $\mathcal{M}$ because it is the pushout of $a$.
-Moreover, $b$, being the pullback of $c$, is in $\mathcal{M}$ too.
-Now, the whole rectangle is a $\mathcal{M}$-pushout, thus, by \Cref{prop:pbpoad}, it is a pullback and so its left half is a pullback, by \Cref{prop:pbpo}.
-Moreover, $g$, being the pullback of a monomorphism, is monic too.
-
-	Putting together these observations, we can build the cube below, in which all the vertical faces are pullbacks.
-	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y \ar[rrr]|(.67)\hole^{b} \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
-	The bottom face is a Van Kampen square and so its top one is a pushout. The thesis now follows from \Cref{lem:po1}. This follows at once from \Cref{prop:stab}.
+	\item By \Cref{prop:stab}, it follows that both squares are pushouts.
+On the other hand, \Cref{prop:pbpoad} entails that the whole rectangle is a pullback, thus the thesis follows from \Cref{lem:pb1}.
 	\item By hypothesis, $g$ is the pullback of an arrow in $\mathcal{M}$, thus belongs to it.
@@
 
-A \emph{left-linear DPO-rewriting system} is a pair $(\X, R)$ where $\X$ is a $\mathcal{M}$-adhesive category and $R$ is a set of left $\mathcal{M}$-linear rules.
-$(\X, R)$ will be called \emph{linear} if every rule in $R$ is so.
+A \emph{left-linear DPO-rewriting system} is a pair $(\X, \R)$ where $\X$ is a $\mathcal{M}$-adhesive category and $R$ is a set of left $\mathcal{M}$-linear rules.
+$(\X, \R)$ will be called \emph{linear} if every rule in $R$ is so.
 
@@
 \begin{definition}
-	Let $(\X, R)$ be a left-linear DPO-rewrityng system, with $\X$ $\mathcal{M}$-adhesive.
-The \emph{DPO-derivation graph} of $(\X, R)$ is the (large)  directed graph $\gpo$ having as vertices the objects of $\X$ and in which an edge between $G$ and $H$ is a direct derivation $\dder{D}:G\Mapsto H$.	A \emph{derivation} $\der{D}$ between two objects $G$ and $H$ is a path between them in $\gpo$.
+	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ $\mathcal{M}$-adhesive.
+The \emph{DPO-derivation graph} of $(\X, \R)$ is the (large)  directed graph $\gpo$ having as vertices the objects of $\X$ and in which an edge between $G$ and $H$ is a direct derivation $\dder{D}:G\Mapsto H$.	A \emph{derivation} $\der{D}$ between two objects $G$ and $H$ is a path between them in $\gpo$.
 \end{definition}
@@
 
+\begin{definition}
+	contenuto...
+\end{definition}
 \begin{remark}
@@
 	In such situation we will say that $\der{D}$ and $\der{D}'$ are \emph{abstraction equivalent}.
-We will use $\equiv^a$ to denote the resulting equivalence relation, while $[\der{D}]_a$ will denote the equivalence class of $\der{D}$.
+We will use $\equiv^a$ to denote the resulting equivalence relation, while $[\der{D}]_a$ will denote the equivalence class of $\der{D}$, called an \emph{abstract derivation}.
 \end{definition}
@@
 \begin{definition}
-	Let $(\X, R)$ be a left-linear DPO-rewrityng system, with $\X$ an $\mathcal{M}$-adhesive category.
+	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ an $\mathcal{M}$-adhesive category.
 The  graph $\gpi$ is the (large)  directed graph having as vertices isomorphism classes of objects of $\X$ and in which an edge between $[G]$ and $[H]$ is the equivalence class $[\der{D}]_a$ of derivation $\der{D}$ between $G$ and $H$.
@@
 
+Concatenation of abstraction equivalence classes of derivations requires a bit of care.  We start with some auxiliary definitions.
+
+\begin{definition} Let $(\X, \R)$ be a left-linear DPO-rewriting system and let also $\phi:G\to G'$ and $\psi:H\to H'$ be two isomorphisms. Given a direct derivation $\dder{D}:G\Mapsto H$
+	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
+we define	$\phi * \dder{D}*\psi : G'\Mapsto H'$ as the direct derivation given by the following diagram.
+	\[\xymatrix{L \ar[d]_{\phi \circ n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{\psi \circ h}\\G' & \ar[l]^{\phi \circ f} D \ar[r]_{\psi \circ g}& H}\]
+
+Moreover, if $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ is a derivation between $G$ and $H$, then we define a derivation $\phi *\der{D} * \psi$ between $G'$ and $H'$ putting
+\[\phi *\der{D} * \psi := \{\phi* \dder{D}_0\}\cdot \{\dder{D}_i\}_{i=1}^{n-1} \cdot \{\dder{D}_n*\psi\}\] 
+\end{definition}
+\begin{remark}
+	By construction $\phi *\der{D} * \psi \equiv^a \der{D}$ for every derivation $\der{D}$. 
+\end{remark}
+\begin{notation}	We will use the notation $\phi *\dder{D}$, $\phi*\der{D}$ and $\dder{D}*\psi$, $\der{D}*\psi$ for the cases in which, respectively, $\psi=\id{H}$ and $\phi=\id{G}$.
+\end{notation}
+
+So equipped we can define the composite of two abstract derivations.
+
+\begin{definition}Let $[\der{D}]_a$ be an abstract derivation between $[G]$ and $[H]$ and $[\der{D}']_a$ one between $[H]$ and $[K]$ and suppose that $\der{D}$ and $\der{D}'$ are derivations between, respectively, $G'$ and $H'$ and between $\hat{H}$ and $K'$.
+We define the  \emph{composite  abstract derivation} $[\der{D}]_a\cdot [\der{D}']_a$ as $[\der{D}*(\psi\circ \phi)  \cdot \der{D}']_a$, where $\phi:H'\to H$ and $\psi:H\to \hat{H}$ are isomorphisms.
+\end{definition}
+\begin{remark} $\der{D}*(\psi\circ \phi)$ is a derivation between $G'$ and $\hat{H}$, thus
+	$[\der{D}*(\psi\circ \phi)  \cdot \der{D}']_a$  is really an abstract derivation between $[G]$ and $[K]$.
+\end{remark}
+\begin{remark}
+	The definition of $[\der{D}]_a\cdot [\der{D}]'_a$ does not depend on the choice of $\phi$ and $\psi$.
+	contenuto...
+\end{remark}
+
+\begin{proposition}
+	contenuto...
+\end{proposition}
+\begin{proof}
+	contenuto... \qed 
+\end{proof}
+\begin{lemma}\label{lem:tec}
+	contenuto...
+\end{lemma}
+\begin{proof}
+	contenuto...\qed 
+\end{proof}
+
+As concatenation of path in a graph is always associative, \Cref{lem:tec} allows us to deduce the following. 
+\begin{corollary}
+	contenuto...
+\end{corollary}
+
+\begin{definition}
+	contenuto...
+\end{definition}
+
+\begin{corollary}
+	contenuto...
+\end{corollary}
+
 \subsection{Consistent permutations}
 
-Given a left-linear DPO-rewriting system $(\X, R)$,  a derivation $\der{D}$  determines a diagram $\Delta(\der{D})$ in $\X$.
+Given a left-linear DPO-rewriting system $(\X, \R)$,  a derivation $\der{D}$  determines a diagram $\Delta(\der{D})$ in $\X$.
 We can then wonder if such a diagram has a colimit.
@@
 \begin{lemma}\label{lem:colim}
-	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, R)$ a left-linear DPO-rewriting system over it. The following hold true:
+	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO-rewriting system over it. The following hold true:
 	\begin{enumerate}
@@
 Thus, we can consider the diagram below, having a pushout as its lower half.
-			\[\xymatrix{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar[l]_{l_{n}} \ar[r]^{r_{n}} & R_{n} \ar[d]^{h_n} \\G_{n} \ar[d]_{\iota_{G_{n}}}& \ar[l]^{f_n} D_n \ar[r]_{g_n}& H  \ar[d]^{q}\\ \lpro \der{D}' \ar[rr]_{p}\rpro && P}\]
+			\[\xymatrix{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar[l]_{l_{n}} \ar[r]^{r_{n}} & R_{n} \ar[d]^{h_n} \\G_{n} \ar[d]_{\iota'_{G_{n}}}& \ar[l]^{f_n} D_n \ar[r]_{g_n}& H  \ar[d]^{q}\\ \lpro \der{D}' \ar[rr]_{p}\rpro && P}\]
 			Notice that, as in the point above, the arrow $q:H\to P$ is the pushout of an element in $\mathcal{M}$, therefore it is enough to show that the diagram so constructed provides a colimiting cocone for $\Delta(\der{D})$.
@@
 \end{proof}
+\iffalse
+
+\begin{corollary}\label{cor:ele}
+	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ be a derivation between $G$ and $H$. Let $j$ be an index strictly less than $n+1$ and consider two arrows $a:T\to G_j$, $b:T\to H$. If
+	\[\iota_H\circ b = \iota_{G_j}\circ t\]
+	then for every $j\leq i \leq n$ there exist an arrow $c_i:T\to D_k $ making the following diagrams commutative
+	\[\xymatrix{&T\ar[dr]^{a} \ar[dl]_{c_j}&&T\ar[d]_{c_i} \ar[r]^-{c_{i-1}} & D_{i-1} \ar[d]^{g_{i-1}}&&T \ar[dr]^{b} \ar[dl]_{c_n}\\D_j \ar[rr]_{f_j} && G_j & D_k \ar[r]_{f_i}& G_i & D_{n} \ar[rr]_{g_n} && H}\]
+	Where the index in the central square is assumed to be sctrictly greater than $j$.
+	\end{corollary}
+
+	\begin{proof}
+		Let us proceed by induction on $n$.
+		\begin{itemize}
+			\item $n=0$. Let $\der{D}$ have as only element the derivation
+\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G & \ar[l]_{f} D \ar[r]^{g}& H }\]
+The hypotheses gives us the following diagram, in which, by the first point of \cref{lem:colim}, the square is a pushout.
+\[\xymatrix{T \ar@/^.2cm/[drr]^{b}  \ar@{.>}[dr]^c \ar@/_.2cm/[ddr]_{a}\\& D \ar[r]^{g} \ar[d]_{f}& H \ar[d]^{\iota_H}\\ &G \ar[r]_{\iota_G} & \tpro{D}}\]
+The square above is an $\mathcal{M}$-pushout, thus by \Cref{prop:pbpoad} it is also a pullback and the thesis follows.
+
+			\item $n>0$.
+Let $\der{D}$ be $\{\dder{D}_{i}\}_{i=0}^n$ and consider $\der{D}':=\{\dder{D}_i\}_{i=0}^{n-1}$.
+By the second point of \Cref{lem:colim} we know that there exists a diagram as the one below, in which the rectangle is a $\mathcal{M}$-pushout.
+					\[\xymatrix{&T \ar@/^.3cm/[drr]^{b}  \ar@/_.2cm/[dl]_{a}  \ar@{.>}[dr]_{c_n}\\G_j \ar@/_.3cm/[dr]_{\iota'_{G_j}} \ar[drrr]|(.34)\hole^(.7){\iota_{G_j}}&G_{n} \ar[d]_{\iota'_{G_{n}}}& \ar[l]^{f_n} D_n \ar[r]_{g_n}& H  \ar[d]^{\iota_H}\\ & \lpro \der{D}' \ar[rr]_{p}\rpro && \tpro{D}}\]
+				By \Cref{prop:pbpoad} the rectangle in the diagram above is a pullback, hence the dotted $c_n:T\to D_n$ exists.
+The thesis now follows applying the inductive hypothesis to $a$ and $ \iota'_{G_n}\circ f_n\circ c_n$.
+\qed
+		\end{itemize}
+\end{proof} 
+\fi
 
@@
 \begin{definition}
-	Let $\X$ be an $\mathcal{M}$-adhesive category and consider a left-linear DPO-rewriting system $(\X, R)$ on it.
+	Let $\X$ be an $\mathcal{M}$-adhesive category and consider a left-linear DPO-rewriting system $(\X, \R)$ on it.
 Take two non-empty derivations $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with the same length with their associated sequences of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$.
@@
 
+\begin{remark}Notice that, by definition, an object $S$ in a category $\X$ is a separator if and only if the representable functor $\X(S,-):\X\to \Set$ is faithful.
+\end{remark}
 \begin{example}
@@
 \end{example}
-
+\begin{example}
+	contenuto...
+\end{example}
+\begin{example}
+	contenuto...
+\end{example}
 \begin{proposition}
@@
 \end{proof}
+
+For our purposes we need to introduce a particular kind of separator.
+\begin{definition} Let $(\X, \R)$ be left linear DPO-rewriting system on an $\mathcal{M}$-adhesive category $\X$.
+We define a class of arrows $\mathcal{R}$ saying that $f:X\to Y $ belongs to it if and only if there exists a rule $(l,r)\in \R$, an arrow $g$ and a pushout square
+	\[\xymatrix{K \ar[r]^{r} \ar[d]_{g}& R \ar[d]^{p}\\ X \ar[r]_{f} & Y}\]
+\end{definition}
+
+\begin{remark}\label{rem:comp} \Cref{lem:po1} entalis that $\mathcal{R}$ is stable under $\mathcal{M}$-pushouts and closed under composition.
+\end{remark}
+
+\begin{proposition}
+	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO-rewriting system over it.
+Then for every non-empty derivation $\der{D}=\{\der{D}\}_{i=0}^n$ between $G$ and $H$, the arrow $\iota_{G}:G\to \tpro{D}$ is in $\mathcal{R}$.
+\end{proposition}
+\begin{proof} We proceed by induction.
+		\begin{itemize}
+		\item $n=0$. Let $\der{D}$ have as only element the derivation
+		\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G & \ar[l]_{f} D \ar[r]^{g}& H }\]
+	 Thus $g$ belongs to $\mathcal{R}$. The thesis now follows immediately since, by \Cref{lem:colim}, the following square is an $\mathcal{M}$-pushout. 
+		\[\xymatrix{& D \ar[r]^{g} \ar[d]_{f}& H \ar[d]^{\iota_H}\\ &G \ar[r]_{\iota_G} & \tpro{D}}\]
+
+		\item $n>0$.
+Define $\der{D}'$ as $\{\dder{D}_i\}_{i=0}^{n-1}$.
+Using \Cref{lem:colim}, we can build the diagram below, in which the bottom rectangle is a $\mathcal{M}$-pushout.			\[\xymatrix{&L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar[l]_{l_{n}} \ar[r]^{r_{n}} & R_{n} \ar[d]^{h_n} \\&G_{n} \ar[d]_{\iota'_{G_{n}}}& \ar[l]^{f_n} D_n \ar[r]_{g_n}& H  \ar[d]^{\iota_H}\\ G\ar[r]^{\iota'_{G}} \ar@/_.4cm/[rrr]_{\iota_{G}}&\lpro \der{D}' \ar[rr]^{p}\rpro && \tpro{D}}\]
+		By inductive hypothesis $\iota'_G$ is in $\mathcal{R}$, while $p$ is in it by construction. The thesis follows from \Cref{rem:comp}. \qed 
+	\end{itemize}
+
+\end{proof}
+\begin{definition}\label{def:sepb} Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.	An \emph{$\mathcal{R}$-separator} for $\X$ is a separator $S$ with the property that, for every pushout square
+	\[\xymatrix{X \ar[r]^{f} \ar[d]_{m}& Z \ar[d]^{q} \\ Y \ar[r]_{p} & P}\]
+	 with $m\in \mathcal{M}$ and $f \in \mathcal{R}$, and for every $s_1, s_2:S\rightrightarrows Y$ such that 
+	$p\circ s_1=p\circ s_2$,	if $s_1\neq s_2$, then there exists $t_1, t_2:S\rightrightarrows X$ such that
+	\[m\circ t_1 = s_1 \quad m\circ t_2=s_2 \quad f\circ t_1=f\circ t_2\]
+\end{definition}
+\begin{remark}
+If $(\X, \R)$ is linear then every separator is an $\mathcal{M}, \mathcal{R}$-separator. Indeed, in such a case every arrow in $\mathcal{R}$ is in $\mathcal{M}$. Thus given a pushout
+\[\xymatrix{X \ar[r]^{f} \ar[d]_{m}& Z \ar[d]^{q} \\ Y \ar[r]_{p} & P}\]
+with $f\in \mathcal{R}$ it follows that $p$ is in $\mathcal{M}$ too. But then $p$ is mono and so the equality
+\[p\circ s_1=p\circ s_2\] 
+entails $s_1=s_2$.
+\end{remark}
+
+\begin{remark} Notice that, since $m$ is assumed to be in $\mathcal{M}$, and thus mono, the arrows $t_1$ and $t$
+\end{remark}
+
+\begin{example}
+	contenuto...
+\end{example}
+\begin{example}
+	contenuto...
+\end{example}
+\begin{example}
+	contenuto...
+\end{example}
+\begin{example}
+	contenuto...
+\end{example}
+
+We can combine \Cref{def:sepb} with \Cref{cor:ele} to get the following.
+
+\begin{proposition}\label{prop:salva}
+	contenuto...
+\end{proposition}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+We are now ready to prove the central result of this section.
+
 \begin{lemma}Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that every rule in $R$ is consuming.
@@
 \end{lemma}
-\begin{proof} Consider two permutations $\sigma$ and $\sigma': n+1 \rightrightarrows n+1$
+\begin{proof} Consider two consistent permutations $\sigma$ and $\sigma': n+1 \rightrightarrows n+1$ and let $\xi, \xi':\tpro{D}\rightrightarrows \tpro{D'}$ be the associated isomorphisms.
+Let also $i\in n+1$ be such that $\sigma(i)\neq \sigma'(i)$ whithout loss of generality we can suppose that $\sigma'(i)<\sigma(i)$.
+Using consistency, we get a diagram
+	\[\xymatrix@C=8pt@R=15pt{ &&&&&R_{i}\ar@/^1.4cm/[dddrrr]^{h'_{\sigma(i)}} \ar@/_1.7cm/[dddlll]_{h'_{\sigma'(i)}}|(.65)\hole|(.83)\hole\ar[ddd]|(.34)\hole^{h_i}|(.82)\hole\\&&&&K_i \ar@/_1.7cm/[dddlll]_{k'_{\sigma'(i)}}|(.67)\hole\ar[dl]_{l_i} \ar[ur]^{r}\ar@/^1.4cm/[dddrrr]^{k'_{\sigma(i)}} \ar[ddd]|(.35)\hole_(.7){k_i}\\&&&L_i\ar@/_1.7cm/[dddlll]_{m'_{\sigma'(i)}}\ar@/^1.4cm/[dddrrr]^(.7){m'_{\sigma(i)}} \ar[ddd]_{m_i}\\&&G'_{\sigma'(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma'(i)+1}}}&&&G_{i+1}  \ar@/^.5cm/[dddl]^{\iota_{G_{i+1}}}&&& G'_{\sigma(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma(i)+1}}}\\ & D_{\sigma'(i)}\ar[ur]^{g'_{\sigma'(i)}}\ar[dl]_(.4){f'_{\sigma'(i)}}\ar[dd]^{\iota_{D'_{\sigma'(i)}}}&&&D_i \ar[dd]^{\iota_{D_i}}\ar[ur]^{g_i}  \ar[dl]_{f_i}&&& D'_\sigma(i) \ar[dd]^{\iota_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_(.4){f'_{\sigma(i)}}\\ G'_{\sigma'(i)}\ar@/_.3cm/[dr]_(.4){\iota_{G_{\sigma'(i)}}}&&&G_i \ar@/_.3cm/[dr]_(.4){\iota_{G_i}} &&& G'_{\sigma(i)}\ar@/_.3cm/[dr]_(.4){\iota_{G'_{\sigma(i)}}}\\&\lpro \der{D}'\rpro &&& \tpro{D} \ar[rrr]_{\xi} \ar[lll]^{\xi'}&&& \lpro \der{D}' \rpro}\]
+
+	Take an arrow $s:S\to L_i$ , then we 
 \end{proof}
@@
 
-\begin{definition}  Let $(\X, R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
+\begin{definition}  Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
 Let also $\dder{D}:G\Mapsto H$ and $\dder{D'}:H\Mapsto T$ be the two direct derivations depicted below.
@@
 
-Summing up, if $(\X, R)$ is a linear DPO-rewriting system, then sequential independence and weak sequential independence coincide. 
+Summing up, if $(\X, \R)$ is a linear DPO-rewriting system, then sequential independence and weak sequential independence coincide. 
 \end{remark}
@@
 \begin{definition}\label{def:filler}
-Let $(\X, R)$ be a left-linear DPO-rewriting system with $\X$ $\mathcal{M}$-adhesive. Let also $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ be the two derivations depicted below.
+Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ $\mathcal{M}$-adhesive. Let also $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ be the two derivations depicted below.
 \[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
@@
 
-\begin{proposition}\label{prop:equi}Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, R)$ a linear DPO-rewriting system.
+\begin{proposition}\label{prop:equi}Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a linear DPO-rewriting system.
 Given two direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, the following are equivalent:
@@
 \begin{enumerate}
-	\item  By construction $p\circ u = k$ and $p'\circ u'=k'$. Since $(\X, R)$ is linear, then $r':K'\to R'$ belongs to $\mathcal{M}$, thus it admits a pushout along $u':K'\to P$, as wanted.
+	\item  By construction $p\circ u = k$ and $p'\circ u'=k'$. Since $(\X, \R)$ is linear, then $r':K'\to R'$ belongs to $\mathcal{M}$, thus it admits a pushout along $u':K'\to P$, as wanted.
 	\item Take the following two rectangles
@@
 
-\begin{proposition}\label{prop:fil}Let $(\X, R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
+\begin{proposition}\label{prop:fil}Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
 Then every filler between two direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ is a filler also for $S_{u,u'}(\dder{D'}):G\Mapsto J$ and $S_{u,u'}(\dder{D}): J\Mapsto H$.
@@
 \begin{lemma}\label{lem:rev}
-	Let $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system $(\X, R)$ and let $(u,u')$ be a filler between them.
+	Let $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system $(\X, \R)$ and let $(u,u')$ be a filler between them.
 Then $S_{u',u}(S_{u,u'}(\dder{D}, \dder{D'}))$ is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
@@
 
-\begin{definition} Let $(\X, R)$ be a left-linear DPO-rewriting system.
+\begin{definition} Let $(\X, \R)$ be a left-linear DPO-rewriting system.
 Given two direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, we say that  $\dder{D}$ and $\dder{D}'$ are \emph{properly interchangeable} if $\dder{D}\updownarrow_!
@@
 We can now prove some properties of switch equivalence.
-\begin{lemma}\todo{Def. 3 della bozza di Andrea }Let $(\X, R)$ be a left-linear DPO-rewriting system. Then the following hold true: 
+\begin{lemma}\todo{Def. 3 della bozza di Andrea }Let $(\X, \R)$ be a left-linear DPO-rewriting system. Then the following hold true: 
 	\begin{enumerate}
@@
 
-\begin{lemma} Let $(\X, R)$ be a left-linear DPO-rewriting system $(\X, R)$. Then the following hold true
+\begin{lemma} Let $(\X, \R)$ be a left-linear DPO-rewriting system $(\X, \R)$. Then the following hold true
 	\begin{enumerate}
@@
 \subsection{Proper switchability is global}
-\todo{Tutto}
+\todo{NO IDEA PER ORA}
 \subsection{Concatenable traces}

### 2023-09-27 fusione.tex
dettagli

@@
 		\[\xymatrix{H\ar[r]^-{\iota_{2, H}} \ar[d]_-{\iota_{1, H}} & \tproi{D}{2} \ar[d]^{p_2}\\  \tproi{D}{1} \ar[r]_{p_1}& \tpro{D}}\]
-		where $(\tproi{D}{1}, \{\iota_{1, X}\}_{X\in \Delta(\der{D}_1)})$ and $(\tproi{D}{2}, \{\iota_{2, X}\}_{X\in \Delta(\der{D}_2)})$ are the colimiting cocone for $\Delta(\der{D}_1)$ and $\Delta(\der{D}_2)$, respectively.
+		where $(\tproi{D}{1}, \{\iota_{1, X}\}_{X\in \Delta(\der{D}_1)})$ and $(\tproi{D}{2}, \{\iota_{2, X}\}_{X\in \Delta(\der{D}_2)})$ are the colimiting cocone for $\Delta(\der{D}_1)$ and $\Delta(\der{D}_2)$, respectively;
+		\item given a non-empty derivation $\der{D}=\{\dder{D}\}_{i=0}^n$ between $G$ and $H$, for every $j\in n+1$ different from $0$ the following diagram is a pushout
+		\[\xymatrix@C=30pt{D_{j} \ar[r]^{g_j}\ar[d]_{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar[dd]^{p_2} \\ G_j \ar[d]_{\iota'_{G_j}}\\ \lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
+		where $\der{\hat{D}}=\{\dder{D}_i\}_{i=j+1}^n$, $\der{D}'=\{\dder{D}_i\}_{i=0}^j$ and $p_1:\lpro\der{D}' \rpro\to \tpro{D}$ and $p_2:\lpro \der{\hat{D}}\rpro \to \tpro{D}$ are the arrows induced by the cocones, $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}')})$ and $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}')})$, respectively.
 	\end{enumerate}
 \end{lemma}
+\begin{remark}\label{rem:zero}
+There is a version of point $4$ of \Cref{lem:colim} for $j=0$ which follows directly from points $1$ and $3$.
+Indeed, $\der{D}=\der{D}_1 \cdot \der{D}_2$ where $\der{D}_1=\{\dder{D}_0\}$ and $\der{D}_2=\{\dder{D}_i\}_{i=1}^n$.
+Then the two halves of the rectangle below are pushouts.
+By \Cref{lem:po1} the whole diagram is then a pushout too.
+	\[\xymatrix@C=30pt{D_{0} \ar[r]^{g_0}\ar[d]_{f_0}& G_{1} \ar[r]^-{\iota_{2,G_{1}}} & \lpro \der{D}_2\rpro \ar[dd]^{p_2} \\ G \ar[d]_{\iota_{1,G}}\\ \lpro \der{D}_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
+\end{remark}
+
 \begin{proof}\begin{enumerate}
@@
 	\end{cases}\]
-From this, we can deduce at once the existence of a unique $c:\der{D}\to C$ such that 
+From this, we can deduce at once the existence of a unique $c:\tpro{D}\to C$ such that 
 \[c\circ \iota_X = c_X\]
@@
 \[\begin{split}
-	c\circ p_1 \circ \iota_{1,X}&=c\circ \iota_{1, X}\\&=c_X \\&=a\circ \iota_{1,X}\\&=a\circ p_1\circ \iota_{1,X}
+	c\circ p_1 \circ \iota_{1,X}&=c\circ \iota_{X}\\&=c_X \\&=a\circ \iota_{1,X}\\&=a\circ p_1\circ \iota_{1,X}
 \end{split}\qquad \begin{split}
-	c\circ p_2 \circ \iota_{2,Y}&=c\circ \iota_{2, Y}\\&=c_Y \\&=b\circ \iota_{2,Y}\\&=b\circ p_2\circ \iota_{2,Y}
+	c\circ p_2 \circ \iota_{2,Y}&=c\circ \iota_{Y}\\&=c_Y \\&=b\circ \iota_{2,Y}\\&=b\circ p_2\circ \iota_{2,Y}
 \end{split}\]
@@
 
-	For uniqueness, suppose that $c':\der{D}\to C$ is such that
+	For uniqueness, suppose that $c':\tpro{D}\to C$ is such that
 	\[c'\circ p_1=a \qquad c'\circ p_2 = b\]
-Then, for every $X\in \der{D}$ we have
+Then, for every $X\in \Delta(\der{D})$ we have
 \begin{align*}
@@
 \end{align*}
-showing that $c'=c$ as wanted.	\qed
-	\end{enumerate}
-\end{proof}
-\iffalse
-
+showing that $c'=c$ as wanted.
+
+\item Let $a:\lpro \der{\hat{D}}\rpro\to C$ , $b:\lpro \der{D}' \rpro\to C$ be two arrows fitting in the diagram 
+	\[\xymatrix{D_{j} \ar[ddrr]^{\iota_{D_j}}\ar[r]^{g_j}\ar[d]_{f_j}& G_{j+1} \ar[r]^{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar@/^.4cm/[dddr]^{a} \ar[dd]^{p_2} \\ G_j \ar[d]_{\iota'_{G_j}}\\ \lpro \der{D}' \rpro \ar@/_.4cm/[rrrd]_{b} \ar[rr]_{p_1}  &&\tpro{D} \ar@{.>}[dr]^{c}\\ &&& C }\]
+
+	We can define a cocone $(C, \{c_X\}_{X\in \Delta(\der{D})})$ putting
+		\[c_X:=\begin{cases}
+		a\circ \hat{\iota}_{ X} & X\in \Delta(\der{\hat{D}})\\
+		b\circ \iota'_{ X} & X\in \Delta(\der{D}')\\
+		b\circ \iota'_{G_j} \circ f_j & X=D_j
+	\end{cases}\]
+	Thus we get a unique arrow $c:\tpro{D}\to C$ such that 
+	\[c\circ \iota_X = c_X\]
+	Now, for every $X\in  \Delta(\der{D}')$ and $Y\in  \Delta(\der{\hat{D}})$ we have
+	\[\begin{split}
+		c\circ p_1 \circ \iota'_{X}&=c\circ \iota_{X}\\&=c_X \\&=b\circ \iota'_{X}\\&=b\circ p_1\circ \iota'_{X}
+	\end{split}\qquad \begin{split}
+		c\circ p_2 \circ \hat{\iota}_{Y}&=c\circ \iota_{Y}\\&=c_Y \\&=a\circ \hat{\iota}_{Y}\\&=a\circ p_2\circ \hat{\iota}_{Y}
+	\end{split}\]
+	so that we can deduce
+	\[c\circ p_1=a \qquad c\circ p_2 = b\]
+
+	To see that such $c$ is unique, suppose that $c':\tpro{D}\to C$ is given such that
+	\[c'\circ p_1=b \qquad c'\circ p_2 = a\]
+	Then, for every $X\in \Delta(\der{D})$ we have
+	\begin{align*}
+		c'\circ \iota_X &= \begin{cases}
+			c'\circ p_1\circ \iota'_{X} & X\in \Delta(\der{D}')\\
+			c'\circ p_2\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
+			c'\circ \iota_{D_j} & X=D_j
+		\end{cases}\\&=\begin{cases}
+		b\circ \iota'_{X} & X\in \Delta(\der{D}')\\
+		a\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
+		c'\circ p_1 \circ \iota'_{G_j} \circ f_j  & X=D_j
+		\end{cases}\\&= \begin{cases}
+		b\circ \iota'_{X} & X\in \Delta(\der{D}')\\
+		a\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
+			b\circ \iota'_{G_j} \circ f_j  & X=D_j
+		\end{cases}\\&=c_X\\&=c\circ \iota_X
+	\end{align*}
+	allowing us to deduce that $c'=c$.	\qed 	
+	\end{enumerate}
+\end{proof}
 \begin{corollary}\label{cor:ele}
-	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ be a derivation between $G$ and $H$. Let $j$ be an index strictly less than $n+1$ and consider two arrows $a:T\to G_j$, $b:T\to H$. If
-	\[\iota_H\circ b = \iota_{G_j}\circ t\]
-	then for every $j\leq i \leq n$ there exist an arrow $c_i:T\to D_k $ making the following diagrams commutative
-	\[\xymatrix{&T\ar[dr]^{a} \ar[dl]_{c_j}&&T\ar[d]_{c_i} \ar[r]^-{c_{i-1}} & D_{i-1} \ar[d]^{g_{i-1}}&&T \ar[dr]^{b} \ar[dl]_{c_n}\\D_j \ar[rr]_{f_j} && G_j & D_k \ar[r]_{f_i}& G_i & D_{n} \ar[rr]_{g_n} && H}\]
-	Where the index in the central square is assumed to be sctrictly greater than $j$.
+	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ be a derivation between $G$ and $H$.
+Let $j$ and $k$ be two indexes less or equal than $n+1$ and suppose that $j< k$.
+Consider two arrows $a:T\to G_j$, $b:T\to G_k$.
+If $\iota_{G_j}\circ a = \iota_{G_k}\circ b$,
+	then  there exist arrow $c:T\to D_j $  such that \[f_j\circ c = a\qquad \iota_{D_j}\circ c =\iota_{G_k}\circ b\]
 	\end{corollary}
+\begin{proof} We split the cases.
+	\begin{itemize}
+		\item $j=0$. Consider $\der{D}_1:=\{\dder{D}_0\}$ and $\der{D}_2:=\{\dder{D}_i\}_{i=1}^n$.  Consider the diagram below in which, by \Cref{rem:zero}, the rectangle on the bottom right is a pushout.
+		\[\xymatrix@C= 40pt{T  \ar@/_.3cm/[dddr]_{a}\ar@{.>}[dr]^{t}\ar[rr]^{b}&& G_k \ar@/^.3cm/[dr]^{\iota_{2, G_k}} \ar@/_.25cm/[dddr]|(.31)\hole_{\iota_{G_k}}\\&D_{0} \ar[r]^{g_0}\ar[d]_{f_0}& G_{1} \ar[r]^-{\iota_{2,G_{1}}} & \lpro \der{D}_2\rpro \ar[dd]^{p_2} \\ &G \ar[drr]^{\iota_G} \ar[d]^{\iota_{1,G}}\\ &\lpro \der{D}_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
+		Since $f_0$ and $\iota_{1,G}$ are in $\mathcal{M}$ the same rectangle is an $\mathcal{M}$-pushout and so, by \Cref{prop:pbpoad} is a pullback and the thesis follows.
+		\item   $j\neq 0$.
+
+		The thesis now followins appealing again to \Cref{prop:pbpoad}. \qed
+	\end{itemize}
+\end{proof}
 
@@
 \end{proof} 
-\fi
-
 So equipped, we can introduce the notion of \emph{consistent permutation}.

### 2023-09-27 fusione.tex
minori

@@
 		Since $f_0$ and $\iota_{1,G}$ are in $\mathcal{M}$ the same rectangle is an $\mathcal{M}$-pushout and so, by \Cref{prop:pbpoad} is a pullback and the thesis follows.
-		\item   $j\neq 0$.
-
-		The thesis now followins appealing again to \Cref{prop:pbpoad}. \qed
+		\item   $j\neq 0$. We proceed as in the point above. Using point $4$ of \Cref{lem:colim} we know that the bottom right rectangle in the diagram above. 
+			\[\xymatrix@C=30pt{T  \ar@/_.3cm/[dddr]_{a}\ar@{.>}[dr]^{t}\ar[rr]^{b}&& G_k \ar@/^.3cm/[dr]^{\iota_{2, G_k}} \ar@/_.25cm/[dddr]|(.31)\hole_{\iota_{G_k}}\\&D_{j} \ar[r]^{g_j}\ar[d]_{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar[dd]^{p_2} \\ &G_j \ar[d]^{\iota'_{G_j}}\\ &\lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
+		Such rectangle is an $\mathcal{M}$-pushout and the thesis follows from \Cref{prop:pbpoad}. \qed
 	\end{itemize}
@@
 
-	\begin{proof}
-		Let us proceed by induction on $n$.
-		\begin{itemize}
-			\item $n=0$. Let $\der{D}$ have as only element the derivation
-\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G & \ar[l]_{f} D \ar[r]^{g}& H }\]
-The hypotheses gives us the following diagram, in which, by the first point of \cref{lem:colim}, the square is a pushout.
-\[\xymatrix{T \ar@/^.2cm/[drr]^{b}  \ar@{.>}[dr]^c \ar@/_.2cm/[ddr]_{a}\\& D \ar[r]^{g} \ar[d]_{f}& H \ar[d]^{\iota_H}\\ &G \ar[r]_{\iota_G} & \tpro{D}}\]
-The square above is an $\mathcal{M}$-pushout, thus by \Cref{prop:pbpoad} it is also a pullback and the thesis follows.
-
-			\item $n>0$.
-Let $\der{D}$ be $\{\dder{D}_{i}\}_{i=0}^n$ and consider $\der{D}':=\{\dder{D}_i\}_{i=0}^{n-1}$.
-By the second point of \Cref{lem:colim} we know that there exists a diagram as the one below, in which the rectangle is a $\mathcal{M}$-pushout.
-					\[\xymatrix{&T \ar@/^.3cm/[drr]^{b}  \ar@/_.2cm/[dl]_{a}  \ar@{.>}[dr]_{c_n}\\G_j \ar@/_.3cm/[dr]_{\iota'_{G_j}} \ar[drrr]|(.34)\hole^(.7){\iota_{G_j}}&G_{n} \ar[d]_{\iota'_{G_{n}}}& \ar[l]^{f_n} D_n \ar[r]_{g_n}& H  \ar[d]^{\iota_H}\\ & \lpro \der{D}' \ar[rr]_{p}\rpro && \tpro{D}}\]
-				By \Cref{prop:pbpoad} the rectangle in the diagram above is a pullback, hence the dotted $c_n:T\to D_n$ exists.
-The thesis now follows applying the inductive hypothesis to $a$ and $ \iota'_{G_n}\circ f_n\circ c_n$.
-\qed
-		\end{itemize}
-\end{proof} 
 So equipped, we can introduce the notion of \emph{consistent permutation}.

### 2023-10-06 fusione.tex
minori

@@
 \def\A{\textbf {\textup{A}}}
+%scheletro
+
+\newcommand{\sk}{\mathsf{sk}_{\X}}
 
@@
 \def\Y{\textbf {\textup{Y}}}
+
+\newcommand{\ske}{\mathsf{sk}(\X)}
 \renewcommand{\P}{\textbf {\textup{P}}}
@@
 
-\begin{remark}\todo{perché regole non consumanti non vanno bene}
-\end{remark}
-
 \begin{example}\todo{
 esempi di	derivazione}
+\end{example}
+
+\begin{example}\label{exa:conc} Let  $\dder{D}:G\Mapsto H$ be the direct derivation 
+		\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
+	If $\phi:G\to G'$ and $\psi:H\to H'$ are two isomorphisms, 	we can consider the direct derivation	$\phi * \dder{D}*\psi : G'\Mapsto H'$ given by the following diagram.
+	\[\xymatrix{L \ar[d]_{\phi \circ n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{\psi \circ h}\\G' & \ar[l]^{\phi \circ f} D \ar[r]_{\psi \circ g}& H}\]
 \end{example}
@@
 If we look to direct derivations as transitions, it is natural to consider them as edges in a direct graph.
-Taking as vertices objects or isomorphism classes of objects led us to the following definitions \cite{heindel2009category,mellies2005axiomatic}.
+Taking objects as vertices objects led us to the following definition \cite{heindel2009category}.
 
@@
 \begin{definition}
-	contenuto...
+	The \emph{DPO-derivation category} of a left-linear DPO-rewriting system $(\X, \R)$ is the free category on $\gpo$.
 \end{definition}
@@
 \end{cases}\]
-\end{remark}
+
+It is immediate to see that the concatenation of two non-empty derivations coincides with their composition in $\dpo$. 
+\end{remark}
+
+ \Cref{exa:conc} allows us to compose derivations with isomorphisms.
+
+\begin{definition} Given a left-linear DPO-rewriting system $(\X, \R)$ and aderivation $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ between $G$ and $H$, the derivation $\phi *\der{D} * \psi$ between $G'$ and $H'$ is defined as
+	\[\phi *\der{D} * \psi := \{\phi* \dder{D}_0*\id{G_1}\}\cdot \{\dder{D}_i\}_{i=1}^{n-1} \cdot \{\id{G_n}*\dder{D}_n*\psi\}\]
+
+\end{definition}
+
+\begin{notation} In the following, we will use the notation $\phi *\dder{D}$, $\phi*\der{D}$ and $\dder{D}*\psi$, $\der{D}*\psi$ for the cases in which, respectively, $\psi=\id{H}$ and $\phi=\id{G}$.
+In particular
+	\[\phi *\der{D} * \psi = \{\phi* \dder{D}_0\}\cdot \{\dder{D}_i\}_{i=1}^{n-1} \cdot \{\dder{D}_n*\psi\}\] 
+\end{notation}
 
@@
 It is then useful to consider a version of $\gpo$ in which vertices are classes of isomorphism of object of $\X$.
-However, in order to do so, we have also to identify direct derivations up to coherent isomorphisms.
-We are thus lead to the following definition.
+In order to do so, some preliminary work is needed.
+
+\begin{definition}\cite{mac2013categories}
+Let $\X$ be a category, we say that  $\X$ is \emph{skeletal} if, for every two objects $X$ and $Y$, the existence of an isomorphism $\phi:X\to Y$ entails $X=Y$.
+A \emph{skeleton} for a category $\X$ is a full subcategory $\ske$ which is skeletal and such that the inclusion functor $\ske\to \X$ is an equivalence.
+\end{definition}
+
+\begin{remark}
+By definition the inclusion $\ske \to \X$ is an equivalence. In particular, this mean that, for every objects $X$ of $\X$ there exists $\pi(X)$ in $\ske$ and an isomorphism $\phi_X: \pi(X) \to X$.
+\end{remark}
+
+\begin{proposition}\label{prop:ske}
+	Every category $\X$ has a skeleton. 
+\end{proposition}
+\begin{proof}
+	For every object $X\in \X$, pick a single representative $\pi(X)$ of its isomorphism class.
+Let $\ske$ be the full subcategory given by these objects.
+By definition $\ske$ is skeletal and the inclusion functor is full, faithful and essentially surjective.\qed
+\end{proof}
+\begin{remark}
+	The proof of \Cref{prop:ske} relies on the axiom of choice for classes.
+	\end{remark}
+\begin{remark}
+	It is possible to proof that every two skeleta of a given category $\X$ are isomorphic (not only equivalent).
+For the remaining of this paper we assume that a skeleton $\ske$ of $\X$ and a functor $\pi:\X\to \ske$ are chosen once and for all.
+\end{remark}
+
+\begin{definition}
+	Let $(\X, \R)$ be a left-linear DPO-rewriting system, a \emph{decorated derivation} between two objects $G$ and $H$ is a triple $(\der{D}, \alpha, \omega)$, where $\der{D}$ is a derivation between $G$ and $H$, and $\alpha:\pi(G)\to G$ and $\omega:\pi(H)\to H$ are isomorphisms.
+\end{definition}
+
+As we are interested in objects only up to isomorphism, so we are interested in (decorated) derivations only up to some notion of coherent isomorphism between them.
 
@@
 
-Given two derivations $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ such that $\dder{D}_i:G_i\Mapsto G_{i+1}$ and $\dder{D}'_i:G'_i\Mapsto G'_{i+1}$., we will say that $\der{D}$ and $\der{D}'$ are \emph{abstraction equivalent}, if  $r(\der{D})=r(\der{D'})$  and there exists a family $\{\phi^i\}_{i=0}^n$ of abstraction equivalences $\phi^i:\dder{D}_i\to \dder{D}'_i$ such, for every index $i$, $\phi^i_3=\phi^{i+1}_1$.
-
-	In such situation we will say that $\der{D}$ and $\der{D}'$ are \emph{abstraction equivalent}.
-We will use $\equiv^a$ to denote the resulting equivalence relation, while $[\der{D}]_a$ will denote the equivalence class of $\der{D}$, called an \emph{abstract derivation}.
-\end{definition}
-\begin{remark}\label{rem:res}
-	We can restate \Cref{prop:unique}: it asserts that, given two direct derivations $\dder{D}$ and $\dder{D'}$ with the same match, there exists an abstract equivalence between them whose first component is an identity.
-\end{remark}
+Given two decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ with  $\der{D}=\{\dder{D}_i\}_{i=0}^n$, $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ such that $\dder{D}_i:G_i\Mapsto G_{i+1}$ and $\dder{D}'_i:G'_i\Mapsto G'_{i+1}$, we will say that $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ are \emph{abstraction equivalent}, if  $r(\der{D})=r(\der{D'})$  and there exists a family $\{\phi^i\}_{i=0}^n$ of abstraction equivalences $\phi^i$ between $\dder{D}_i$ and  $\dder{D}'_i$ such that, for every index $i$, $\phi^i_3=\phi^{i+1}_1$ and  the following diagrams commute.
+\[\xymatrix{&\pi(G_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G_{n+1}) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G_0 \ar[rr]_{\phi^0_0} && G'_0 &G_{n+1} \ar[rr]_{\phi^n_3} && G'_{n+1} } \]
+
+	In such situation we will say that $ (\der{D}, \alpha, \omega)$ and  $(\der{D}', \alpha', \omega')$ are \emph{abstraction equivalent}.
+We will use $\equiv^a$ to denote the resulting equivalence relation, while  $[\der{D}, \alpha, \omega]_a$ will denote the equivalence class of  $(\der{D}, \alpha, \omega)$, called an \emph{abstract decorated derivation}.
+\end{definition}
+\begin{remark}\label{rem:res} \Cref{prop:unique} can be restated as saying that, given two direct derivations $\dder{D}$ and $\dder{D'}$ with the same match, there exists an abstract equivalence between them whose first component is an identity.
+\end{remark}
+
+\begin{definition}
+Let $(\der{D}, \alpha, \omega)$ be a decorated derivation between $G$ and $H$ and $(\der{D}', \alpha', \omega')$ one between $H'$ and $K$.
+If $H$ and $H'$ are isomorphic, so that $\pi(H)=\pi(H')$, we define the  \emph{composite decorated derivation}  $(\der{D}, \alpha, \omega)\cdot (\der{D}', \alpha', \omega')$as $((\der{D}* \omega^{-1}) \cdot ((\alpha')^{-1} *\der{D}'), \alpha, \omega')$.
+\end{definition}
+
+\begin{remark}\label{rem:lgt}
+	contenuto...
+\end{remark}
+
+The next proposition justifies the use of decorations, guaranteeing that concatenation of abstract decorated derivations is weel-defined.
+\begin{proposition}
+	Given a decorated derivation $(\der{D}, \alpha, \omega)$  between $G$ and $H$ and  another one $(\der{E}, \beta, \xi)$ between $E$ and $K$ with $\pi(H)=\pi(E)$.
+If  $(\der{D}', \alpha', \omega')$ and $(\der{E}', \beta', \xi')$ are two other decorated derivations such that
+	$[\der{D}, \alpha, \omega]_a = [\der{D}', \alpha', \omega']_a$ and $[\der{D}, \beta, \xi]_a=[\der{E}', \beta', \xi']_a$, then
+	\[[(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)]_a=[(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')]_a\]
+\end{proposition}
+
+\begin{proof}
+	contenuto...\qed 
+\end{proof}
+
+\begin{definition}
+	contenuto...
+\end{definition}
 
@@
 
-Concatenation of abstraction equivalence classes of derivations requires a bit of care.  We start with some auxiliary definitions.
-
-\begin{definition} Let $(\X, \R)$ be a left-linear DPO-rewriting system and let also $\phi:G\to G'$ and $\psi:H\to H'$ be two isomorphisms. Given a direct derivation $\dder{D}:G\Mapsto H$
-	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
-we define	$\phi * \dder{D}*\psi : G'\Mapsto H'$ as the direct derivation given by the following diagram.
-	\[\xymatrix{L \ar[d]_{\phi \circ n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{\psi \circ h}\\G' & \ar[l]^{\phi \circ f} D \ar[r]_{\psi \circ g}& H}\]
-
-Moreover, if $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ is a derivation between $G$ and $H$, then we define a derivation $\phi *\der{D} * \psi$ between $G'$ and $H'$ putting
-\[\phi *\der{D} * \psi := \{\phi* \dder{D}_0\}\cdot \{\dder{D}_i\}_{i=1}^{n-1} \cdot \{\dder{D}_n*\psi\}\] 
-\end{definition}
 \begin{remark}
-	By construction $\phi *\der{D} * \psi \equiv^a \der{D}$ for every derivation $\der{D}$. 
-\end{remark}
-\begin{notation}	We will use the notation $\phi *\dder{D}$, $\phi*\der{D}$ and $\dder{D}*\psi$, $\der{D}*\psi$ for the cases in which, respectively, $\psi=\id{H}$ and $\phi=\id{G}$.
-\end{notation}
-
-So equipped we can define the composite of two abstract derivations.
-
-\begin{definition}Let $[\der{D}]_a$ be an abstract derivation between $[G]$ and $[H]$ and $[\der{D}']_a$ one between $[H]$ and $[K]$ and suppose that $\der{D}$ and $\der{D}'$ are derivations between, respectively, $G'$ and $H'$ and between $\hat{H}$ and $K'$.
-We define the  \emph{composite  abstract derivation} $[\der{D}]_a\cdot [\der{D}']_a$ as $[\der{D}*(\psi\circ \phi)  \cdot \der{D}']_a$, where $\phi:H'\to H$ and $\psi:H\to \hat{H}$ are isomorphisms.
-\end{definition}
-\begin{remark} $\der{D}*(\psi\circ \phi)$ is a derivation between $G'$ and $\hat{H}$, thus
-	$[\der{D}*(\psi\circ \phi)  \cdot \der{D}']_a$  is really an abstract derivation between $[G]$ and $[K]$.
-\end{remark}
-\begin{remark}
-	The definition of $[\der{D}]_a\cdot [\der{D}]'_a$ does not depend on the choice of $\phi$ and $\psi$.
 	contenuto...
 \end{remark}
-
-\begin{proposition}
-	contenuto...
-\end{proposition}
-\begin{proof}
-	contenuto... \qed 
-\end{proof}
-\begin{lemma}\label{lem:tec}
-	contenuto...
-\end{lemma}
-\begin{proof}
-	contenuto...\qed 
-\end{proof}
-
-As concatenation of path in a graph is always associative, \Cref{lem:tec} allows us to deduce the following. 
-\begin{corollary}
-	contenuto...
-\end{corollary}
-
-\begin{definition}
-	contenuto...
-\end{definition}
-
-\begin{corollary}
-	contenuto...
-\end{corollary}
-
 \subsection{Consistent permutations}
@@
 The commutativity of the two rectangles above, is equivalent to the commutativity of the following bigger diagram.		
-\[\xymatrix@C=40pt@R=10pt{ &&&R_{i}\ar[dddr]^{h'_i} \ar[dddl]_{h_i}|(.67)\hole\\&&K_i \ar[dl]_{l_i} \ar[ur]^{r}\ar[dddr]^{k'_i} \ar[dddl]_{k_i}|(.67)\hole\\&L_i\ar[dddr]_(.6){m'_i} \ar[dddl]_{m_i}\\&&G_{i+1}  \ar@/^.3cm/[dddl]|(.35)\hole^(.7){\iota_{G_{i+1}}}&& G'_{\sigma(i)+1}\ar@/^.3cm/[dddl]^{\iota_{G'_{\sigma(i)+1}}}\\ & D_i \ar[dd]_{\iota_{D_i}}\ar[ur]^(.6){g_i}  \ar[dl]_{f_i}&& D'_\sigma(i) \ar[dd]^{\iota_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_{f'_{\sigma(i)}}\\ G_i \ar@/_.3cm/[dr]_{\iota_{G_i}} && G'_{\sigma(i)}\ar@/_.3cm/[dr]^{\iota_{G'_{\sigma(i)}}}\\& \tpro{D} \ar[rr]_{\xi}&& \lpro \der{D}' \rpro}\]
+\[\xymatrix@C=40pt@R=10pt{ &&&R_{i}\ar[dddr]^{h'_{\sigma(i)}} \ar[dddl]_{h_i}|(.67)\hole\\&&K_i \ar[dl]_{l_i} \ar[ur]^{r}\ar[dddr]^{k'_{\sigma(i)}} \ar[dddl]_{k_i}|(.67)\hole\\&L_i\ar[dddr]_(.6){m'_{\sigma(i)}} \ar[dddl]_{m_i}\\&&G_{i+1}  \ar@/^.3cm/[dddl]|(.35)\hole^(.7){\iota_{G_{i+1}}}&& G'_{\sigma(i)+1}\ar@/^.3cm/[dddl]^{\iota'_{G'_{\sigma(i)+1}}}\\ & D_i \ar[dd]_{\iota_{D_i}}\ar[ur]^(.6){g_i}  \ar[dl]_{f_i}&& D'_\sigma(i) \ar[dd]^{\iota'_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_{f'_{\sigma(i)}}\\ G_i \ar@/_.3cm/[dr]_{\iota_{G_i}} && G'_{\sigma(i)}\ar@/_.3cm/[dr]^{\iota'_{G'_{\sigma(i)}}}\\& \tpro{D} \ar[rr]_{\xi}&& \lpro \der{D}' \rpro}\]
 
@@
 
+\begin{remark}\label{rem:coproj}
+Notice that, in particular, the previous diagram entails
+		\[\xi \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
+\end{remark}
+
 \begin{example} Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ be two abstraction equivalent non-empty derivations.
@@
 \begin{definition}[\cite{borceux1994handbook1,adamek1994locally}]
-Let $\X$ be a category, a \emph{separator}, or \emph{generator}, is an object $S$ such that, for every pair of arrows $f, g:X\rightrightarrows Y$, if \[f\circ s = g\circ s\] for every $s:S\to X$, then $f=g$.
-
-Given a separator $S$, we will say that a morphism $f:X\to Y$,  is an \emph{$S$-surjection} if for every $s:S\to Y$  there exists $s':S\to X$ such that $f\circ s'= s$.
-\end{definition}
-
-\begin{remark}Notice that, by definition, an object $S$ in a category $\X$ is a separator if and only if the representable functor $\X(S,-):\X\to \Set$ is faithful.
-\end{remark}
-\begin{example}
-	contenuto...
-\end{example}
-\begin{example}
-	contenuto...
-\end{example}
-\begin{example}
-	contenuto...
-\end{example}
-\begin{example}
-	contenuto...
-\end{example}
-\begin{proposition}
-Let $f:X\to Y$ be a morphism in a category $\X$ with a separator $S$, then every $S$-surjection is an epimorphism.
-\end{proposition}
-\begin{proof}
-	Let $f:X\to Y$ be an $S$-surjection, and suppose that there exist two arrows $g, h:Y\rightrightarrows Z$ such that 
-	\[g\circ f = h\circ f\]
-Since $f$ is an $S$-surjection, for every $s:S\to Y$ there exists $s':S\to X$ such that $f\circ s'=s$, so that
-\begin{align*}
-	g\circ s &= g\circ f \circ s'\\&=h\circ f \circ s'\\&= h\circ s
-\end{align*} 
-	The thesis now follows since $S$ is a separator.	 \qed 
-\end{proof}
-
-For our purposes we need to introduce a particular kind of separator.
-\begin{definition} Let $(\X, \R)$ be left linear DPO-rewriting system on an $\mathcal{M}$-adhesive category $\X$.
-We define a class of arrows $\mathcal{R}$ saying that $f:X\to Y $ belongs to it if and only if there exists a rule $(l,r)\in \R$, an arrow $g$ and a pushout square
-	\[\xymatrix{K \ar[r]^{r} \ar[d]_{g}& R \ar[d]^{p}\\ X \ar[r]_{f} & Y}\]
-\end{definition}
-
-\begin{remark}\label{rem:comp} \Cref{lem:po1} entalis that $\mathcal{R}$ is stable under $\mathcal{M}$-pushouts and closed under composition.
-\end{remark}
-
-\begin{proposition}
-	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO-rewriting system over it.
-Then for every non-empty derivation $\der{D}=\{\der{D}\}_{i=0}^n$ between $G$ and $H$, the arrow $\iota_{G}:G\to \tpro{D}$ is in $\mathcal{R}$.
-\end{proposition}
-\begin{proof} We proceed by induction.
-		\begin{itemize}
-		\item $n=0$. Let $\der{D}$ have as only element the derivation
-		\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G & \ar[l]_{f} D \ar[r]^{g}& H }\]
-	 Thus $g$ belongs to $\mathcal{R}$. The thesis now follows immediately since, by \Cref{lem:colim}, the following square is an $\mathcal{M}$-pushout. 
-		\[\xymatrix{& D \ar[r]^{g} \ar[d]_{f}& H \ar[d]^{\iota_H}\\ &G \ar[r]_{\iota_G} & \tpro{D}}\]
-
-		\item $n>0$.
-Define $\der{D}'$ as $\{\dder{D}_i\}_{i=0}^{n-1}$.
-Using \Cref{lem:colim}, we can build the diagram below, in which the bottom rectangle is a $\mathcal{M}$-pushout.			\[\xymatrix{&L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar[l]_{l_{n}} \ar[r]^{r_{n}} & R_{n} \ar[d]^{h_n} \\&G_{n} \ar[d]_{\iota'_{G_{n}}}& \ar[l]^{f_n} D_n \ar[r]_{g_n}& H  \ar[d]^{\iota_H}\\ G\ar[r]^{\iota'_{G}} \ar@/_.4cm/[rrr]_{\iota_{G}}&\lpro \der{D}' \ar[rr]^{p}\rpro && \tpro{D}}\]
-		By inductive hypothesis $\iota'_G$ is in $\mathcal{R}$, while $p$ is in it by construction. The thesis follows from \Cref{rem:comp}. \qed 
-	\end{itemize}
-
-\end{proof}
-\begin{definition}\label{def:sepb} Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.	An \emph{$\mathcal{R}$-separator} for $\X$ is a separator $S$ with the property that, for every pushout square
-	\[\xymatrix{X \ar[r]^{f} \ar[d]_{m}& Z \ar[d]^{q} \\ Y \ar[r]_{p} & P}\]
-	 with $m\in \mathcal{M}$ and $f \in \mathcal{R}$, and for every $s_1, s_2:S\rightrightarrows Y$ such that 
-	$p\circ s_1=p\circ s_2$,	if $s_1\neq s_2$, then there exists $t_1, t_2:S\rightrightarrows X$ such that
-	\[m\circ t_1 = s_1 \quad m\circ t_2=s_2 \quad f\circ t_1=f\circ t_2\]
-\end{definition}
-\begin{remark}
-If $(\X, \R)$ is linear then every separator is an $\mathcal{M}, \mathcal{R}$-separator. Indeed, in such a case every arrow in $\mathcal{R}$ is in $\mathcal{M}$. Thus given a pushout
-\[\xymatrix{X \ar[r]^{f} \ar[d]_{m}& Z \ar[d]^{q} \\ Y \ar[r]_{p} & P}\]
-with $f\in \mathcal{R}$ it follows that $p$ is in $\mathcal{M}$ too. But then $p$ is mono and so the equality
-\[p\circ s_1=p\circ s_2\] 
-entails $s_1=s_2$.
-\end{remark}
-
-\begin{remark} Notice that, since $m$ is assumed to be in $\mathcal{M}$, and thus mono, the arrows $t_1$ and $t$
-\end{remark}
-
-\begin{example}
-	contenuto...
-\end{example}
-\begin{example}
-	contenuto...
-\end{example}
-\begin{example}
-	contenuto...
-\end{example}
-\begin{example}
-	contenuto...
-\end{example}
-
-We can combine \Cref{def:sepb} with \Cref{cor:ele} to get the following.
-
-\begin{proposition}\label{prop:salva}
+Let $\X$ be a category, a \emph{separating family},  is a class $\mathcal{S}$ of objects such that, for every pair of arrows $f, g:X\rightrightarrows Y$, if \[f\circ s = g\circ s\] for every $s:S\to X$ with domain $S\in \mathcal{S}$, then $f=g$.
+
+Given a separating family $\mathcal{S}$, we will say that a morphism $f:X\to Y$,  is an \emph{$\mathcal{S}$-surjection} if for every $s:S\to Y$ with domain in $\mathcal{S}$  there exists $s':S\to X$ such that $f\circ s'= s$.
+\end{definition}
+
+\begin{proposition}\label{prop:sep}
 	contenuto...
@@
 
+We can list some examples of separating families.
+
+\begin{example}
+	contenuto...
+\end{example}
+\begin{example}
+	contenuto...
+\end{example}
+\begin{example}
+	contenuto...
+\end{example}
+\begin{example}
+	contenuto...
+\end{example}
+\begin{proposition}
+Let $f:X\to Y$ be a morphism in a category $\X$ with a separating family $\mathcal{S}$, then every $\mathcal{S}$-surjection is an epimorphism.
+\end{proposition}
+\begin{proof}
+	Let $f:X\to Y$ be an $\mathcal{S}$-surjection, and suppose that there exist two arrows $g, h:Y\rightrightarrows Z$ such that 
+	\[g\circ f = h\circ f\]
+Since $f$ is an $\mathcal{S}$-surjection, for every $S\in \mathcal{S}$ and arrow $s:S\to Y$ there exists $s':S\to X$ such that $f\circ s'=s$, so that
+\begin{align*}
+	g\circ s &= g\circ f \circ s'\\&=h\circ f \circ s'\\&= h\circ s
+\end{align*} 
+	The thesis now follows since $\mathcal{S}$ is separating.	 \qed 
+\end{proof}
+
 We are now ready to prove the central result of this section.
@@
 \end{lemma}
-\begin{proof} Consider two consistent permutations $\sigma$ and $\sigma': n+1 \rightrightarrows n+1$ and let $\xi, \xi':\tpro{D}\rightrightarrows \tpro{D'}$ be the associated isomorphisms.
-Let also $i\in n+1$ be such that $\sigma(i)\neq \sigma'(i)$ whithout loss of generality we can suppose that $\sigma'(i)<\sigma(i)$.
-Using consistency, we get a diagram
-	\[\xymatrix@C=8pt@R=15pt{ &&&&&R_{i}\ar@/^1.4cm/[dddrrr]^{h'_{\sigma(i)}} \ar@/_1.7cm/[dddlll]_{h'_{\sigma'(i)}}|(.65)\hole|(.83)\hole\ar[ddd]|(.34)\hole^{h_i}|(.82)\hole\\&&&&K_i \ar@/_1.7cm/[dddlll]_{k'_{\sigma'(i)}}|(.67)\hole\ar[dl]_{l_i} \ar[ur]^{r}\ar@/^1.4cm/[dddrrr]^{k'_{\sigma(i)}} \ar[ddd]|(.35)\hole_(.7){k_i}\\&&&L_i\ar@/_1.7cm/[dddlll]_{m'_{\sigma'(i)}}\ar@/^1.4cm/[dddrrr]^(.7){m'_{\sigma(i)}} \ar[ddd]_{m_i}\\&&G'_{\sigma'(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma'(i)+1}}}&&&G_{i+1}  \ar@/^.5cm/[dddl]^{\iota_{G_{i+1}}}&&& G'_{\sigma(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma(i)+1}}}\\ & D_{\sigma'(i)}\ar[ur]^{g'_{\sigma'(i)}}\ar[dl]_(.4){f'_{\sigma'(i)}}\ar[dd]^{\iota_{D'_{\sigma'(i)}}}&&&D_i \ar[dd]^{\iota_{D_i}}\ar[ur]^{g_i}  \ar[dl]_{f_i}&&& D'_\sigma(i) \ar[dd]^{\iota_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_(.4){f'_{\sigma(i)}}\\ G'_{\sigma'(i)}\ar@/_.3cm/[dr]_(.4){\iota_{G_{\sigma'(i)}}}&&&G_i \ar@/_.3cm/[dr]_(.4){\iota_{G_i}} &&& G'_{\sigma(i)}\ar@/_.3cm/[dr]_(.4){\iota_{G'_{\sigma(i)}}}\\&\lpro \der{D}'\rpro &&& \tpro{D} \ar[rrr]_{\xi} \ar[lll]^{\xi'}&&& \lpro \der{D}' \rpro}\]
+
+\begin{proof} Consider two consistent permutations $\sigma$ and $\sigma': n+1 \rightrightarrows n+1$ and let $\xi, \xi':\tpro{D}\rightrightarrows \tpro{D'}$ be the associated isomorphisms.	\[\xymatrix@C=8pt@R=20pt{ &&&&&R_{i}\ar@/^1.4cm/[dddrrr]^{h'_{\sigma(i)}} \ar@/_1.7cm/[dddlll]_{h'_{\sigma'(i)}}|(.65)\hole|(.83)\hole\ar[ddd]|(.35)\hole^{h_i}|(.805)\hole\\&&&&K_i \ar@/_1.7cm/[dddlll]_{k'_{\sigma'(i)}}|(.67)\hole\ar[dl]_{l_i} \ar[ur]^{r}\ar@/^1.4cm/[dddrrr]^{k'_{\sigma(i)}} \ar[ddd]|(.35)\hole_(.7){k_i}\\&&&L_i\ar@/_1.7cm/[dddlll]_{m'_{\sigma'(i)}}\ar@/^1.4cm/[dddrrr]^(.7){m'_{\sigma(i)}} \ar[ddd]_{m_i}\\&&G'_{\sigma'(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma'(i)+1}}}&&&G_{i+1}  \ar@/^.5cm/[dddl]^{\iota_{G_{i+1}}}&&& G'_{\sigma(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma(i)+1}}}\\ & D'_{\sigma'(i)}\ar[ur]^{g'_{\sigma'(i)}}\ar[dl]_(.35){f'_{\sigma'(i)}}\ar[dd]^{\iota_{D'_{\sigma'(i)}}}&&&D_i \ar[dd]^{\iota_{D_i}}\ar[ur]^{g_i}  \ar[dl]_{f_i}&&& D'_\sigma(i) \ar[dd]^{\iota_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_(.4){f'_{\sigma(i)}}\\ G'_{\sigma'(i)}\ar@/_.3cm/[dr]_(.35){\iota_{G_{\sigma'(i)}}}&&&G_i \ar@/_.3cm/[dr]_(.35){\iota_{G_i}} &&& G'_{\sigma(i)}\ar@/_.3cm/[dr]_(.35){\iota_{G'_{\sigma(i)}}}\\&\lpro \der{D}'\rpro &&& \tpro{D} \ar[rrr]_{\xi} \ar[lll]^{\xi'}&&& \lpro \der{D}' \rpro}\]
+
+Suppose that there exists $j\in n+1$ be such that $\sigma(j)\neq \sigma'(j)$.  Let $k$ be $\sigma^{-1}(\sigma'(i))$, then, in particular $j\neq k$. By \Cref{rem:coproj} we know that
+\begin{align*}
+\iota_{L_{k}}=\xi^{-1} \circ \iota'_{L_{\sigma(k)}}
+\end{align*}We have two cases.
+	\begin{itemize}
+		\item $i< \sigma^{-1}(\sigma'(i))$.
+		\item $\sigma^{-1}(\sigma'(i))<i$.\qed 
+	\end{itemize} 
+\end{proof}
+
+\begin{proof}  whithout loss of generality we can suppose that $\sigma'(i)<\sigma(i)$. Using consistency, we get a diagram
 

### 2023-10-10 fusione.tex
unicità

@@
 \title{Switch equivalence and weak prime domains for fusions}
+\author{Paolo Baldan \and Davide Castelnovo  \and  Andrea Corradini  Fabio Gadducci}
 
@@
 
-	Moreover,  if $\mathcal{D}_i$ is an application of the rule $\rho_i\in R$, then we can define an associated sequence of rule as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.
+	Moreover,  if $\mathcal{D}_i$ is an application of the rule $\rho_i\in R$, then we can define an associated sequence of rules as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.
 
@@
 \begin{definition}
-	The \emph{DPO-derivation category} of a left-linear DPO-rewriting system $(\X, \R)$ is the free category on $\gpo$.
+	The \emph{DPO-derivation category} $\dpo$ of a left-linear DPO-rewriting system $(\X, \R)$ is the free category on $\gpo$.
 \end{definition}
@@
 Given two decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ with  $\der{D}=\{\dder{D}_i\}_{i=0}^n$, $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ such that $\dder{D}_i:G_i\Mapsto G_{i+1}$ and $\dder{D}'_i:G'_i\Mapsto G'_{i+1}$, we will say that $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ are \emph{abstraction equivalent}, if  $r(\der{D})=r(\der{D'})$  and there exists a family $\{\phi^i\}_{i=0}^n$ of abstraction equivalences $\phi^i$ between $\dder{D}_i$ and  $\dder{D}'_i$ such that, for every index $i$, $\phi^i_3=\phi^{i+1}_1$ and  the following diagrams commute.
-\[\xymatrix{&\pi(G_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G_{n+1}) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G_0 \ar[rr]_{\phi^0_0} && G'_0 &G_{n+1} \ar[rr]_{\phi^n_3} && G'_{n+1} } \]
+\[\xymatrix{&\pi(G_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G_{n+1}) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G_0 \ar[rr]_{\phi^0_1} && G'_0 &G_{n+1} \ar[rr]_{\phi^n_3} && G'_{n+1} } \]
 
@@
 Let $(\der{D}, \alpha, \omega)$ be a decorated derivation between $G$ and $H$ and $(\der{D}', \alpha', \omega')$ one between $H'$ and $K$.
-If $H$ and $H'$ are isomorphic, so that $\pi(H)=\pi(H')$, we define the  \emph{composite decorated derivation}  $(\der{D}, \alpha, \omega)\cdot (\der{D}', \alpha', \omega')$as $((\der{D}* \omega^{-1}) \cdot ((\alpha')^{-1} *\der{D}'), \alpha, \omega')$.
+If $H$ and $H'$ are isomorphic, so that $\pi(H)=\pi(H')$, we define the  \emph{composite decorated derivation}  $(\der{D}, \alpha, \omega)\cdot (\der{D}', \alpha', \omega')$ as $((\der{D}* \omega^{-1}) \cdot ((\alpha')^{-1} *\der{D}'), \alpha, \omega')$.
 \end{definition}
@@
 \begin{remark}\label{rem:lgt}
-	contenuto...
+	Given two composable decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$  such that $\der{D}$ and $\der{D}'$ have  length $n$ and $m$, respectively, then $(\der{D}* \omega^{-1}) \cdot ((\alpha')^{-1} *\der{D}')$ has length $n+m$.
 \end{remark}
@@
 \begin{proof}
-	contenuto...\qed 
+	To fix the notation, let $\der{D}$, $\der{D}'$, $\der{E}$ and $\der{E}'$ be given by
+	\[\der{D}=\{\dder{D}_i\}_{i=0}^n \quad \der{D}'=\{\dder{D}'_i\}_{i=0}^n \quad \der{E}=\{\dder{E}_i\}_{i=0}^m \quad \der{E}'=\{\dder{E}'_i\}_{i=0}^m\]
+	Let also $\{\phi^i\}_{i=0}^n$ and $\{\varphi^i\}_{i=0}^m$ be families of abstract equivalences between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ and between $(\der{E}, \beta, \xi)$ and $(\der{E}', \beta', \xi')$, respectively.
+For every $i\in [0, n+m-1]$ define
+	\[\psi^{i}:=\begin{cases}
+		\phi^i & i< n\\
+		(\phi^n_1, \phi^n_2, \id{\pi(H)}) & i=n\\
+		(\id{\pi(E)}, \varphi^{0}_2, \varphi^{0}_3) & i=n+1\\
+		\varphi^{i-n+1} & i>n+1
+	\end{cases}\] 
+Notice suppose that $h_n:R_n\to H, h_n:R_n\to H'$ are the back-matches of $\der{D}_n$ and $\der{D}'_n$ and that the following diagram is given
+	\[\xymatrix@C=40pt@R=10pt{ &&&R_n\ar[dddr]^{h'_n} \ar[dddl]_{h_n}|(.67)\hole\\&&K_n \ar[dl]_{l_n} \ar[ur]^{r_n}\ar[dddr]^{k'_n} \ar[dddl]_{k_n}|(.67)\hole\\&L_n\ar[dddr]^(.4){m'_n} \ar[dddl]_(.4){m_n}\\&&H \ar[rr]^{\phi^n_3} && H'\\ & D_n \ar[ur]_(.7){g_n} \ar[rr]^{\phi^n_2} \ar[dl]_{f_n}&& D'_n \ar[ur]_{g'_n}\ar[dl]^{f'_n}\\ G_{n} \ar[rr]_{\phi^n_1} && G'_n}\]
+Then we have
+\begin{align*} 
+	\id{\pi(H)}\circ \omega^{-1} \circ h_n&=(\omega')^{-1}\circ \phi^n_3 \circ \omega \circ \omega^{-1} \circ h_n\\&=(\omega')^{-1}\circ \phi^n_3  \circ h_n\\&=(\omega')^{-1}  \circ h'_n
+\end{align*} 
+and 
+\begin{align*} \id{\pi(H)}\circ \omega^{-1} \circ g_n  &=(\omega')^{-1}\circ \phi^n_3 \circ \omega \circ \omega^{-1}\circ g_n\\&=(\omega')^{-1}\circ \phi^n_3\circ g'_n\\&=(\omega')^{-1}\circ g'_n\circ \phi^n_2\end{align*}
+Therefore $\psi^n$ is an abstract equivalence between $\dder{D}_n*\omega^{-1}$ and $\dder{D}_n'*(\omega')^{-1}$.
+
+Similarly, if $\hat{m}_0:\hat{L}_0\to E, \hat{m}'_0:L'_0\to E'$ the matches of $\der{E}_0$, $\der{E}'_0$, we can consider the diagram
+\[\xymatrix@C=40pt@R=10pt{ &&&\hat{R}_0\ar[dddr]^{\hat{h}'_0} \ar[dddl]_{\hat{h}_0}|(.67)\hole\\&&\hat{K}_0 \ar[dl]_{\hat{l}_0} \ar[ur]^{\hat{r}_0}\ar[dddr]^{k'_0} \ar[dddl]_{\hat{k}_0}|(.67)\hole\\&\hat{L}_n\ar[dddr]^(.4){\hat{m}'_0} \ar[dddl]_(.4){\hat{m}_0}\\&&\hat{G}_1 \ar[rr]^{\varphi^0_3} && \hat{G}'_1\\ & \hat{D}_0 \ar[ur]_(.7){\hat{g}_0} \ar[rr]^{\varphi^0_2} \ar[dl]_{\hat{f}_0}&& \hat{D}'_0 \ar[ur]_{\hat{g}'_0}\ar[dl]^{\hat{f}'_0}\\ E \ar[rr]_{\varphi^0_1} && E'}\]
+and computing we get
+\begin{align*}
+	\id{\pi(E)}\circ \alpha^{-1} \circ \hat{m}_0&=(\alpha')^{-1}\circ \varphi^0_1 \circ \alpha \circ \alpha^{-1} \circ \hat{m}_0\\&=(\alpha')^{-1}\circ \varphi^0_1  \circ \hat{m}_0\\&=(\alpha')^{-1}\circ \hat{m}'_n
+\end{align*}
+together with
+\begin{align*} \id{\pi(E)}\circ \alpha^{-1}\circ \hat{f}_0  &=(\alpha')^{-1}\circ \varphi^0_1 \circ \alpha \circ \alpha^{-1}\circ \hat{f}_0\\&=(\alpha')^{-1}\circ \varphi^0_1\circ \hat{f}_0\\&=(\alpha')^{-1}\circ \hat{f}'_0\circ \varphi^0_2\end{align*}
+The previous two identities show that $\psi^{n+1}$ is an abstract equivalence between $\dder{E}_0$ and $\dder{E}'_0$. By hypothesis $\pi(H)=\pi(E)$ and, moreover, we have
+	\[\begin{split}
+		\psi^{0}_1\circ \alpha &= \phi^0_1\circ \alpha \\&= \alpha'
+	\end{split}\qquad \begin{split}
+	\psi^{n+m-1}_3\circ \xi &=\varphi^m_3\circ \xi \\&= \xi'
+	\end{split}\]
+Therefore the thesis now follows.	\qed 
 \end{proof}
@@
 \begin{definition}
-	contenuto...
-\end{definition}
-
-\begin{definition}
-	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ an $\mathcal{M}$-adhesive category.
-The  graph $\gpi$ is the (large)  directed graph having as vertices isomorphism classes of objects of $\X$ and in which an edge between $[G]$ and $[H]$ is the equivalence class $[\der{D}]_a$ of derivation $\der{D}$ between $G$ and $H$.
-\end{definition}
-
-\begin{remark}
-	contenuto...
-\end{remark}
+	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ an $\mathcal{M}$-adhesive category. The  category $\dpi$ is defined as follows:
+	\begin{itemize}
+		\item objects are isomorphism classes of objects of $\X$;
+		\item a non-identity arrow $[G]\to [H]$ is an equivalence class $[\der{D}, \alpha, \omega]_a$ of a decorated derivation between $G'$ and $H'$ for some $G'$ and $H'$ such that $\pi(G')=G$ and $\pi(H')=H$;
+		\item composition is concatenation of abstract decorated derivations;
+		\item identities are added formally.
+	\end{itemize}
+\end{definition}
+
 \subsection{Consistent permutations}
@@
 		Since $f_0$ and $\iota_{1,G}$ are in $\mathcal{M}$ the same rectangle is an $\mathcal{M}$-pushout and so, by \Cref{prop:pbpoad} is a pullback and the thesis follows.
-		\item   $j\neq 0$. We proceed as in the point above. Using point $4$ of \Cref{lem:colim} we know that the bottom right rectangle in the diagram above. 
+		\item   $j\neq 0$. We proceed as in the point above. Using point $4$ of \Cref{lem:colim} we know that the bottom right rectangle in the diagram below is a pushout. 
 			\[\xymatrix@C=30pt{T  \ar@/_.3cm/[dddr]_{a}\ar@{.>}[dr]^{t}\ar[rr]^{b}&& G_k \ar@/^.3cm/[dr]^{\iota_{2, G_k}} \ar@/_.25cm/[dddr]|(.31)\hole_{\iota_{G_k}}\\&D_{j} \ar[r]^{g_j}\ar[d]_{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar[dd]^{p_2} \\ &G_j \ar[d]^{\iota'_{G_j}}\\ &\lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
-		Such rectangle is an $\mathcal{M}$-pushout and the thesis follows from \Cref{prop:pbpoad}. \qed
+		Point $2$ of \Cref{lem:colim} entails that $\iota'_{G_j}$ is in $\mathcal{M}$, and so is $f_j$ as it is the pushout of $l_j$.
+Thus the rectangle we are considering is an $\mathcal{M}$-pushout and the thesis follows again from \Cref{prop:pbpoad}.
+\qed
 	\end{itemize}
@@
 
-\begin{definition}
+\begin{definition}\label{def:permcon}
 	Let $\X$ be an $\mathcal{M}$-adhesive category and consider a left-linear DPO-rewriting system $(\X, \R)$ on it.
-Take two non-empty derivations $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with the same length with their associated sequences of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$.
-A permutation $\sigma:n+1\to n+1$  is called a \emph{consistent permutation} between $\der{D}$ and $\der{D}'$, if for every $i\in n+1$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists an isomorphism $\xi:\tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
-\[\xymatrix{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi} \\G'_{\sigma(i)} \ar[rr]_{\iota_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
+Take two non-empty decorated derivations $(\der{D}, \alpha, \omega)$ and  $(\der{D}', \alpha', \omega')$ such that
+	\begin{itemize}
+		\item $\der{D}$ and $\der{D}'$ have the same length;
+		\item if  $\der{D}$  is a derivation between $G$ and $H$ amd $\der{D}'$ one between $G'$ and $H'$, then $G\simeq G'$ and $H\simeq H'$.
+	\end{itemize}
+
+	 	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with assciated squence of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma:[0,n]\to [0,n]$  such that, for every $i\in [0,n]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma:\tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
+	\[\xymatrix{\pi(G)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G \ar[r]^{\iota_{G}} &\tpro{D} \ar[d]^{\xi}&   \pi(H) \ar[r]^{\omega} \ar[d]_{\omega'} & H \ar[r]^{\iota_H} &\tpro{D} \ar[d]^{\xi}\\ G' \ar[rr]_{\iota'_{G'}} & &\lpro \der{D}' \rpro& H' \ar[rr]_{\iota'_{H'}} & &\lpro \der{D}' \rpro}\]
+\[\xymatrix{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
 \end{definition}
@@
 \begin{remark}
-The commutativity of the two rectangles above, is equivalent to the commutativity of the following bigger diagram.		
-\[\xymatrix@C=40pt@R=10pt{ &&&R_{i}\ar[dddr]^{h'_{\sigma(i)}} \ar[dddl]_{h_i}|(.67)\hole\\&&K_i \ar[dl]_{l_i} \ar[ur]^{r}\ar[dddr]^{k'_{\sigma(i)}} \ar[dddl]_{k_i}|(.67)\hole\\&L_i\ar[dddr]_(.6){m'_{\sigma(i)}} \ar[dddl]_{m_i}\\&&G_{i+1}  \ar@/^.3cm/[dddl]|(.35)\hole^(.7){\iota_{G_{i+1}}}&& G'_{\sigma(i)+1}\ar@/^.3cm/[dddl]^{\iota'_{G'_{\sigma(i)+1}}}\\ & D_i \ar[dd]_{\iota_{D_i}}\ar[ur]^(.6){g_i}  \ar[dl]_{f_i}&& D'_\sigma(i) \ar[dd]^{\iota'_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_{f'_{\sigma(i)}}\\ G_i \ar@/_.3cm/[dr]_{\iota_{G_i}} && G'_{\sigma(i)}\ar@/_.3cm/[dr]^{\iota'_{G'_{\sigma(i)}}}\\& \tpro{D} \ar[rr]_{\xi}&& \lpro \der{D}' \rpro}\]
+The commutativity of the last two rectangles in \Cref{def:permcon}, is equivalent to the commutativity of the following bigger diagram.		
+\[\xymatrix@C=40pt@R=10pt{ &&&R_{i}\ar[dddr]^{h'_{\sigma(i)}} \ar[dddl]_{h_i}|(.67)\hole\\&&K_i \ar[dl]_{l_i} \ar[ur]^{r}\ar[dddr]^{k'_{\sigma(i)}} \ar[dddl]_{k_i}|(.67)\hole\\&L_i\ar[dddr]_(.6){m'_{\sigma(i)}} \ar[dddl]_{m_i}\\&&G_{i+1}  \ar@/^.3cm/[dddl]|(.35)\hole^(.7){\iota_{G_{i+1}}}&& G'_{\sigma(i)+1}\ar@/^.3cm/[dddl]^{\iota'_{G'_{\sigma(i)+1}}}\\ & D_i \ar[dd]_{\iota_{D_i}}\ar[ur]^(.6){g_i}  \ar[dl]_{f_i}&& D'_\sigma(i) \ar[dd]^{\iota'_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_{f'_{\sigma(i)}}\\ G_i \ar@/_.3cm/[dr]_{\iota_{G_i}} && G'_{\sigma(i)}\ar@/_.3cm/[dr]^{\iota'_{G'_{\sigma(i)}}}\\& \tpro{D} \ar[rr]_{\xi_\sigma}&& \lpro \der{D}' \rpro}\]
 
@@
 \begin{align*}
-	\xi \circ \iota_{D_i}\circ k_i&=\xi \circ \iota_{G_{i}} \circ f_i\\&= \xi \circ \iota_{G_{i}}\circ m_i \circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ m'_i\circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ f'_{\sigma(i)}\circ k'_i\\&=\iota_{D'_\sigma(i)}\circ k_i'
+	\xi_\sigma \circ \iota_{D_i}\circ k_i&=\xi_\sigma \circ \iota_{G_{i}} \circ f_i\\&= \xi_\sigma \circ \iota_{G_{i}}\circ m_i \circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ m'_i\circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ f'_{\sigma(i)}\circ k'_i\\&=\iota_{D'_\sigma(i)}\circ k_i'
 \end{align*}
@@
 Notice that, in particular, the previous diagram entails
-		\[\xi \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
-\end{remark}
-
-\begin{example} Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ be two abstraction equivalent non-empty derivations.
-Then the identity permutation $\id{n+1}$ is a consistent permuation between them.
-In such a case $\xi$ is simply the isomorphism induced by the $\{\phi^i\}_{i=0}^n$.
+		\[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
+\end{remark}
+
+\begin{remark}\label{rem:comp} Consistent permutations can be composed.
+Indeed, given decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$, if $\sigma$ is a consistent permutation between the first two and $\sigma'$ one between the second and the third, then  we have diagrams
+	\[\xymatrix@C=18pt{ & G \ar[rr]^{\iota_{G}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  H \ar[rr]^{\iota_H} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G' \ar[rr]^{\iota'_{G'}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&\pi(H)\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & H' \ar[rr]^{\iota'_{H'}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}  \ar[rr]_{\hat{\iota}_{\hat{G}}}&& \lpro \hat{\der{D}}\rpro  && \hat{H} \ar[rr]_{\hat{\iota}_{\hat{H}}}&& \lpro \hat{\der{D}} \rpro \\& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_{\sigma'(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\sigma'(\sigma(i))} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}} \rpro	}\]
+	We deduce at once that $\sigma'\circ \sigma$ is a consistent permutation with mediating isomorphism given by $\xi_{\sigma'} \circ \xi_\sigma$.
+\end{remark}
+
+\begin{example} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstraction equivalent non-empty decorated derivations of length $n+1$.
+Then the identity permutation $\id{[0,n]}$ is a consistent permutation between them.
+In such a case $\xi_{\id{[0,n]}}$ is simply the isomorphism induced by any family $\{\phi^i\}_{i=0}^n$ witnessing $(\der{D}, \alpha, \omega)\equiv^a (\der{D}', \alpha', \omega')$.
 \end{example}
@@
 \end{example}
+
+\begin{proposition}\label{prop:uniqu}
+	Let $\sigma,\sigma':[0,n]\rightrightarrows [0,n]$ be two consistent permutations between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.  Then the following hold true:
+	\begin{enumerate}
+	\item $\xi_\sigma \circ \iota_{G_0} = \xi_{\sigma'} \circ \iota_{G_0}$;
+	\item  $\xi_\sigma \circ \iota_{G_i}=\xi_{\sigma'} \circ \iota_{G_i}$ for every index $i\in [0,n]$ such that $\sigma_{|[0,i]}=\sigma'_{|[0,i]}$.
+	\end{enumerate}
+\end{proposition}
+\begin{proof}\begin{enumerate}
+		\item This follows at once noticing that both $\xi_\sigma \circ \iota_{G_0}$ and $\xi_{\sigma'} \circ \iota_{G_0}$ are equal to $\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}$.
+		\item  If $\sigma(0)\neq \sigma'(0)$ there is nothing to show. Otherwise, let $j$ be the maximum of the set
+		\[\{i\in [0,n]\mid \sigma_{|[0,i]}=\sigma'_{|[0,i]}\}\]
+		We proceed by induction on $i\in [0,j]$. 
+		\begin{itemize}
+			\item If $i=0$ the thesis follows from point $1$.
+			\item If $i>0$, we know that there is a pushout square
+			\[\xymatrix{K_{i-1}\ar[r]^{r_{i-1}} \ar[d]_{k_{i-1}}& R_{i-1} \ar[d]^{h_{i-1}}\\ D_{i-1} \ar[r]_{g_{i-1}}& G_i}\] 
+			By \Cref{rem:coproj} we know that
+			\begin{align*}
+				\xi_\sigma \circ \iota_{G_i}\circ h_{i-1}&=  \xi_\sigma\circ \iota_{R_{i-1}}\\&=\iota'_{R_{\sigma(i-1)}}\\&=\iota'_{R_{\sigma'(i-1)}}\\&=\xi_{\sigma'}\circ \iota_{R_{i-1}}\\&=\xi_{\sigma'} \circ \iota_{G_i}\circ h_{i-1}
+			\end{align*}
+			But, by the induction hypothesis we also have
+			\begin{align*}
+				\xi_\sigma \circ \iota_{G_i}\circ g_{i-1}&=\xi_{\sigma}\circ \iota_{D_{i-1}}\\&=\xi_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi_{\sigma'}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi_{\sigma'}\circ \iota_{D_{i-1}} \\&=\xi_{\sigma'}\circ \iota_{G_{i}} \circ g_{i-1}
+			\end{align*}
+			The thesis now follows.			\qed
+		\end{itemize}
+	\end{enumerate}
+\end{proof}
+
+Now, notice that, given a consistent permutation $\sigma$, $\xi_\sigma:\tpro{D}\to \lpro \der{D}'\rpro$, we already know, by \Cref{rem:coproj} that
+\[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
+	Moreover, for $\xi_\sigma \circ \iota_{D_i}$ must be $\xi_\sigma \circ \iota_{G_i}\circ f_i$.
+Thus it is enough to define $\xi_{\sigma} \circ \iota_{G_i}$ for every $i\in [0, n]$.
+But then \Cref{prop:uniqu} entails the following.
+\begin{corollary} Given a consistent permutation $\sigma$ between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, the mediating isomorphism $\xi_\sigma:\tpro{D}\to \lpro \der{D}'\rpro$ is unique.
+\end{corollary}
+
+\begin{proposition}\label{prop:sum}
+\todo{il caso in cui sigma si decomponga come due permu}
+\end{proposition}
+\begin{proof}
+	contenuto...\qed 
+\end{proof}
 
@@
 \end{definition}
-
-\begin{proposition}\label{prop:sep}
-	contenuto...
-\end{proposition}
-\begin{proof}
-	contenuto...
-\end{proof}
 
@@
 
+\begin{lemma} Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that $\X$ has a separator $\mathcal{S}$.
+Consider two consistent permutation $\sigma,\sigma':[0,n]\rightrightarrows [0,n]$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
+Suppose that $\sigma\neq \sigma'$ and let $j$ be the minimum index such that $\sigma(j)\neq \sigma'(j)$.
+Let also $r(\der{D})$ be $\{\rho_i\}_{i=0}^n$.
+Then the following hold true:
+	\begin{enumerate}
+		\item if $j=0$, then the rule $\rho_0$ is not consuming;
+		\item if $j\neq 0$, then the rule $\rho_{j-1}$ is not consuming.
+	\end{enumerate}
+\end{lemma}
+\begin{proof}\begin{enumerate}
+		\item 
+		\item  \qed
+	\end{enumerate}
+\end{proof}
+
+\begin{corollary}\label{cor:unique}
+Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that every rule in $R$ is consuming.
+Given two non-empty derivations $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_{i}\}_{i=0}^n$, if $\X$ has a separator $\mathcal{S}$, then there exists at most one consistent permutation between them.
+\end{corollary}
+
 \begin{lemma}Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that every rule in $R$ is consuming.
@@
 
-\begin{proof} Consider two consistent permutations $\sigma$ and $\sigma': n+1 \rightrightarrows n+1$ and let $\xi, \xi':\tpro{D}\rightrightarrows \tpro{D'}$ be the associated isomorphisms.	\[\xymatrix@C=8pt@R=20pt{ &&&&&R_{i}\ar@/^1.4cm/[dddrrr]^{h'_{\sigma(i)}} \ar@/_1.7cm/[dddlll]_{h'_{\sigma'(i)}}|(.65)\hole|(.83)\hole\ar[ddd]|(.35)\hole^{h_i}|(.805)\hole\\&&&&K_i \ar@/_1.7cm/[dddlll]_{k'_{\sigma'(i)}}|(.67)\hole\ar[dl]_{l_i} \ar[ur]^{r}\ar@/^1.4cm/[dddrrr]^{k'_{\sigma(i)}} \ar[ddd]|(.35)\hole_(.7){k_i}\\&&&L_i\ar@/_1.7cm/[dddlll]_{m'_{\sigma'(i)}}\ar@/^1.4cm/[dddrrr]^(.7){m'_{\sigma(i)}} \ar[ddd]_{m_i}\\&&G'_{\sigma'(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma'(i)+1}}}&&&G_{i+1}  \ar@/^.5cm/[dddl]^{\iota_{G_{i+1}}}&&& G'_{\sigma(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma(i)+1}}}\\ & D'_{\sigma'(i)}\ar[ur]^{g'_{\sigma'(i)}}\ar[dl]_(.35){f'_{\sigma'(i)}}\ar[dd]^{\iota_{D'_{\sigma'(i)}}}&&&D_i \ar[dd]^{\iota_{D_i}}\ar[ur]^{g_i}  \ar[dl]_{f_i}&&& D'_\sigma(i) \ar[dd]^{\iota_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_(.4){f'_{\sigma(i)}}\\ G'_{\sigma'(i)}\ar@/_.3cm/[dr]_(.35){\iota_{G_{\sigma'(i)}}}&&&G_i \ar@/_.3cm/[dr]_(.35){\iota_{G_i}} &&& G'_{\sigma(i)}\ar@/_.3cm/[dr]_(.35){\iota_{G'_{\sigma(i)}}}\\&\lpro \der{D}'\rpro &&& \tpro{D} \ar[rrr]_{\xi} \ar[lll]^{\xi'}&&& \lpro \der{D}' \rpro}\]
+\begin{proof} Consider two consistent permutations $\sigma$ and $\sigma': n+1 \rightrightarrows n+1$ and let $\xi, \xi':\tpro{D}\rightrightarrows \lpro \der{D}' \rpro$ be the associated isomorphisms.	\[\xymatrix@C=8pt@R=20pt{ &&&&&R_{i}\ar@/^1.4cm/[dddrrr]^{h'_{\sigma(i)}} \ar@/_1.7cm/[dddlll]_{h'_{\sigma'(i)}}|(.65)\hole|(.83)\hole\ar[ddd]|(.35)\hole^{h_i}|(.805)\hole\\&&&&K_i \ar@/_1.7cm/[dddlll]_{k'_{\sigma'(i)}}|(.67)\hole\ar[dl]_{l_i} \ar[ur]^{r}\ar@/^1.4cm/[dddrrr]^{k'_{\sigma(i)}} \ar[ddd]|(.35)\hole_(.7){k_i}\\&&&L_i\ar@/_1.7cm/[dddlll]_{m'_{\sigma'(i)}}\ar@/^1.4cm/[dddrrr]^(.7){m'_{\sigma(i)}} \ar[ddd]_{m_i}\\&&G'_{\sigma'(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma'(i)+1}}}&&&G_{i+1}  \ar@/^.5cm/[dddl]^{\iota_{G_{i+1}}}&&& G'_{\sigma(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma(i)+1}}}\\ & D'_{\sigma'(i)}\ar[ur]^{g'_{\sigma'(i)}}\ar[dl]_(.35){f'_{\sigma'(i)}}\ar[dd]^{\iota_{D'_{\sigma'(i)}}}&&&D_i \ar[dd]^{\iota_{D_i}}\ar[ur]^{g_i}  \ar[dl]_{f_i}&&& D'_\sigma(i) \ar[dd]^{\iota_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_(.4){f'_{\sigma(i)}}\\ G'_{\sigma'(i)}\ar@/_.3cm/[dr]_(.35){\iota_{G_{\sigma'(i)}}}&&&G_i \ar@/_.3cm/[dr]_(.35){\iota_{G_i}} &&& G'_{\sigma(i)}\ar@/_.3cm/[dr]_(.35){\iota_{G'_{\sigma(i)}}}\\&\lpro \der{D}'\rpro &&& \tpro{D} \ar[rrr]_{\xi} \ar[lll]^{\xi'}&&& \lpro \der{D}' \rpro}\]
 
@@
 
-\begin{corollary}\label{cor:unique}
+\begin{corollary}
 	contenuto...
@@
 \subsection{Proper switchability is global}
+
+\begin{lemma}
+	contenuto...
+\end{lemma}
+\begin{proof}
+	contenuto... \qed 
+\end{proof}
+
 \todo{NO IDEA PER ORA}

### 2023-10-13 fusione.tex
cose

@@
 		\[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
+\end{remark}
+
+\begin{remark}\label{rem:inversa}
+Let $\sigma:[0,n]\to [0,n]$ be a consistent permutation between $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, then $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$: indeed, it is enough to consider, as mediating isomorphism, the inverse $\xi^{-1}_\sigma$ of $\xi_\sigma$.
 \end{remark}
@@
 
-To proceed further, we have to introduce a notion from general category theory.
-
-\begin{definition}[\cite{borceux1994handbook1,adamek1994locally}]
-Let $\X$ be a category, a \emph{separating family},  is a class $\mathcal{S}$ of objects such that, for every pair of arrows $f, g:X\rightrightarrows Y$, if \[f\circ s = g\circ s\] for every $s:S\to X$ with domain $S\in \mathcal{S}$, then $f=g$.
-
-Given a separating family $\mathcal{S}$, we will say that a morphism $f:X\to Y$,  is an \emph{$\mathcal{S}$-surjection} if for every $s:S\to Y$ with domain in $\mathcal{S}$  there exists $s':S\to X$ such that $f\circ s'= s$.
-\end{definition}
-
-We can list some examples of separating families.
-
-\begin{example}
-	contenuto...
-\end{example}
-\begin{example}
-	contenuto...
-\end{example}
-\begin{example}
-	contenuto...
-\end{example}
-\begin{example}
-	contenuto...
-\end{example}
-\begin{proposition}
-Let $f:X\to Y$ be a morphism in a category $\X$ with a separating family $\mathcal{S}$, then every $\mathcal{S}$-surjection is an epimorphism.
-\end{proposition}
-\begin{proof}
-	Let $f:X\to Y$ be an $\mathcal{S}$-surjection, and suppose that there exist two arrows $g, h:Y\rightrightarrows Z$ such that 
-	\[g\circ f = h\circ f\]
-Since $f$ is an $\mathcal{S}$-surjection, for every $S\in \mathcal{S}$ and arrow $s:S\to Y$ there exists $s':S\to X$ such that $f\circ s'=s$, so that
-\begin{align*}
-	g\circ s &= g\circ f \circ s'\\&=h\circ f \circ s'\\&= h\circ s
-\end{align*} 
-	The thesis now follows since $\mathcal{S}$ is separating.	 \qed 
-\end{proof}
-
 We are now ready to prove the central result of this section.
 
-\begin{lemma} Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that $\X$ has a separator $\mathcal{S}$.
+\begin{lemma} Let $(\X,R)$ be a left-linear DPO-rewriting system.
 Consider two consistent permutation $\sigma,\sigma':[0,n]\rightrightarrows [0,n]$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
@@
 		\item if $j=0$, then the rule $\rho_0$ is not consuming;
-		\item if $j\neq 0$, then the rule $\rho_{j-1}$ is not consuming.
+		\item if $j\neq 0$ then the rule $\rho_{j-1}$ is not consuming.
 	\end{enumerate}
@@
 \begin{proof}\begin{enumerate}
-		\item 
-		\item  \qed
+		\item Let $k$ be $\sigma^{-1}(\sigma'(0))$ and notice that, since $\sigma(0)\neq \sigma'(0)$, then $0< k$.  By  the first point of  \Cref{prop:uniqu} we can consider the diagram
+		\[\xymatrix@C=40pt{& L_0 \ar[d]_{m'_{\sigma'(0)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{0}} \\G_{0} \ar@/_.2cm/[drr]_(.3){\iota_{G_0}}|(.515)\hole \ar[d]_{\iota_{G_0}}& G'_{\sigma'(0)} \ar[d]^{\iota_{G'_{\sigma'(0)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\sigma'}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
+	From \Cref{cor:ele}, we can conclude that there exists $c:L_0\to D_0$ such that $f_0\circ c=m_0$. We thus have the solid part of the commutative diagram below.
+		\[\xymatrix{L_0 \ar@/^.3cm/[drr]^{\id{L_0}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_0 \ar[d]_{k_0}\ar[r]^{l_0}& L_0 \ar[d]^{m_0} \\& D_0 \ar[r]_{f_0} & G_0} \]
+		The internal square is an $\mathcal{M}$-pushout and thus a pullback, by \Cref{prop:pbpoad}, so that we have the existence of the dotted $t:L_0\to K_0$.
+Therefore $\id{L_0}=l_0\circ t$, proving that $l_0$ is an epimorphism.
+The thesis now follows from \Cref{cor:rego}.
+		\item  Let $k$ be $\sigma^{-1}(\sigma'(j-1))$ and notice that $\rho_{j-1}=\rho_k$.
+By definition of $j$, $\sigma_{|[0,j-1]}=\sigma'_{|[0,j-1]}$, thus the second point of \Cref{prop:unique} yields the diagram
+			\[\xymatrix@C=40pt{& L_{j-1} \ar[d]_{m'_{\sigma'(j-1)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{j-1}} \\G_{j-1} \ar@/_.2cm/[drr]_(.3){\iota_{G_{j-1}}}|(.515)\hole \ar[d]_{\iota_{G_{j-1}}}& G'_{\sigma'(j-1)} \ar[d]^{\iota_{G'_{\sigma'(j-1)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\sigma'}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
+			Let $a$ be $\min(j-1, k)$, by \Cref{cor:ele},  there exists $c:L_{j-1}\to D_a$ such that $f_a\circ c=m_a$. As before this yields the solid part of the following diagram
+			\[\xymatrix{L_{j-1} \ar@/^.3cm/[drr]^{\id{L_{j-1}}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_{j-1} \ar[d]_{k_a}\ar[r]^{l_{j-1}}& L_{j-1} \ar[d]^{m_a} \\& D_a \ar[r]_{f_a} & G_a} \]
+			The existence of the dotted $t:L_{j-1}\to K_{j-1}$ follows from  \Cref{prop:pbpoad} and we can conclude. \qed
 	\end{enumerate}
@@
 Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that every rule in $R$ is consuming.
-Given two non-empty derivations $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_{i}\}_{i=0}^n$, if $\X$ has a separator $\mathcal{S}$, then there exists at most one consistent permutation between them.
+For every two non-empty decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, there exists at most one consistent permutation between them.
 \end{corollary}
 
-\begin{lemma}Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that every rule in $R$ is consuming.
-Given two non-empty derivations $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_{i}\}_{i=0}^n$, if $\X$ has a separator $S$, then there exists at most one consistent permutation between them.
-\end{lemma}
-
-\begin{proof} Consider two consistent permutations $\sigma$ and $\sigma': n+1 \rightrightarrows n+1$ and let $\xi, \xi':\tpro{D}\rightrightarrows \lpro \der{D}' \rpro$ be the associated isomorphisms.	\[\xymatrix@C=8pt@R=20pt{ &&&&&R_{i}\ar@/^1.4cm/[dddrrr]^{h'_{\sigma(i)}} \ar@/_1.7cm/[dddlll]_{h'_{\sigma'(i)}}|(.65)\hole|(.83)\hole\ar[ddd]|(.35)\hole^{h_i}|(.805)\hole\\&&&&K_i \ar@/_1.7cm/[dddlll]_{k'_{\sigma'(i)}}|(.67)\hole\ar[dl]_{l_i} \ar[ur]^{r}\ar@/^1.4cm/[dddrrr]^{k'_{\sigma(i)}} \ar[ddd]|(.35)\hole_(.7){k_i}\\&&&L_i\ar@/_1.7cm/[dddlll]_{m'_{\sigma'(i)}}\ar@/^1.4cm/[dddrrr]^(.7){m'_{\sigma(i)}} \ar[ddd]_{m_i}\\&&G'_{\sigma'(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma'(i)+1}}}&&&G_{i+1}  \ar@/^.5cm/[dddl]^{\iota_{G_{i+1}}}&&& G'_{\sigma(i)+1}\ar@/^.5cm/[dddl]^{\iota_{G'_{\sigma(i)+1}}}\\ & D'_{\sigma'(i)}\ar[ur]^{g'_{\sigma'(i)}}\ar[dl]_(.35){f'_{\sigma'(i)}}\ar[dd]^{\iota_{D'_{\sigma'(i)}}}&&&D_i \ar[dd]^{\iota_{D_i}}\ar[ur]^{g_i}  \ar[dl]_{f_i}&&& D'_\sigma(i) \ar[dd]^{\iota_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_(.4){f'_{\sigma(i)}}\\ G'_{\sigma'(i)}\ar@/_.3cm/[dr]_(.35){\iota_{G_{\sigma'(i)}}}&&&G_i \ar@/_.3cm/[dr]_(.35){\iota_{G_i}} &&& G'_{\sigma(i)}\ar@/_.3cm/[dr]_(.35){\iota_{G'_{\sigma(i)}}}\\&\lpro \der{D}'\rpro &&& \tpro{D} \ar[rrr]_{\xi} \ar[lll]^{\xi'}&&& \lpro \der{D}' \rpro}\]
-
-Suppose that there exists $j\in n+1$ be such that $\sigma(j)\neq \sigma'(j)$.  Let $k$ be $\sigma^{-1}(\sigma'(i))$, then, in particular $j\neq k$. By \Cref{rem:coproj} we know that
-\begin{align*}
-\iota_{L_{k}}=\xi^{-1} \circ \iota'_{L_{\sigma(k)}}
-\end{align*}We have two cases.
-	\begin{itemize}
-		\item $i< \sigma^{-1}(\sigma'(i))$.
-		\item $\sigma^{-1}(\sigma'(i))<i$.\qed 
-	\end{itemize} 
-\end{proof}
-
-\begin{proof}  whithout loss of generality we can suppose that $\sigma'(i)<\sigma(i)$. Using consistency, we get a diagram
-
-	Take an arrow $s:S\to L_i$ , then we 
-\end{proof}
-
-\begin{corollary}
-	contenuto...
+\begin{corollary}\label{cor:dec}
+	\todo{prefisso e suffisso}
 \end{corollary}
+\begin{proof}
+	contenuto...\qed 
+\end{proof}
 
@@
 
-\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
+\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
 We will say that $\dder{D}$ and $\dder{D'}$ are \emph{weakly sequentially independent} if an independence pair exists.
@@
 \begin{example}
-	\todo{pensare ad un esempio in cui l'indipendenza non basta (o farsi venire in mente una dimostrazione della prop. 13 della versione su arxiv)}
+	\todo{pensare ad un esempio in cui l'indipendenza non basta }
 \end{example}
@@
 We can prove some other properties of the arrows appearing in the diagram above.
-\begin{itemize}
-	\item The three rectangles below are pushouts and their left halves are pushouts too. Therefore, by \Cref{lem:po1}, also their right halves are pushouts.
+The three rectangles below are pushouts and their left halves are pushouts too.
+Therefore, by \Cref{lem:po1}, also their right halves are pushouts.
 	\[\xymatrix{K \ar@/^.4cm/[rr]^{u}\ar[d]_{r}\ar[r]_{u} &P\ar[d]^{p'} \ar[r]_{p} & D \ar[d]^{g}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{l'}\ar[r]_{u'} &P\ar[d]^{p} \ar[r]_{p'} & D' \ar[d]^{f'}\\  R \ar@/_.4cm/[rr]_{h} \ar[r]^{i_1}&D' \ar[r]^{f'} & H&L' \ar@/_.4cm/[rr]_{n'} \ar[r]^{i_2}&D \ar[r]^{g} & H}\]
 	\[ \xymatrix{K \ar@/^.4cm/[rr]^{k}\ar[d]_{l}\ar[r]_{u} &P\ar[d]^{q} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{r'}\ar[r]_{u'} &P\ar[d]^{q'} \ar[r]_{p'} & D' \ar[d]^{g'}\\ L \ar@/_.4cm/[rr]_{n} \ar[r]^{j}&Q \ar[r]^{s} & G&R' \ar@/_.4cm/[rr]_{h'} \ar[r]^{j'}&Q' \ar[r]^{t} & T}\]
-\end{itemize}
+
+Notice, moreover, that $p, q$ are the pushouts of $l'$ and $l$, respectively, thus they  are elements of $\mathcal{M}$. By \Cref{prop:pbpoad} the squares
+\[\xymatrix{P\ar[r]^{p} \ar[d]_{p'} & D \ar[d]^{g}& P \ar[r]^{p} \ar[d]_{q} &D\ar[d]^{f}\\ D' \ar[r]_{f'} & H & Q \ar[r]_{s}& G}\]
+are pullbacks too.
 \end{remark}
@@
 	Since, by \Cref{rem:deco}, all the curved rectangles are pushouts, as well as the bottom square, we can state the following definition.
-\begin{definition}
+\begin{definition}\label{def:switch}
 	Let $(\X,R)$ be a left-linear DPO-rewriting system and suppose that $\X$ is $\mathcal{M}$-adhesive.
@@
 \subsection{Proper switchability is global}
-
-\begin{lemma}
-	contenuto...
+\todo{intro}
+
+\begin{lemma}[Invariance under immediate shift, 1] Let $(\X,\R)$ be a left-linear DPO-rewriting system consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$.
+If $(v,v')$ is a filler between $\dder{D}_0$ and $\dder{D}_1$, $(u,u')$ one between $\dder{D}_1$ and $\dder{D}_2$ and $\dder{D}_0\updownarrow S_{u,u'}(\dder{D}_2)$ with filler $(w,w')$, then there exists a filler between $S_{w,w'}(\dder{D}_0)$ and $S_{u,u'}(\dder{D}_1)$.
 \end{lemma}
 \begin{proof}
-	contenuto... \qed 
-\end{proof}
-
-\todo{NO IDEA PER ORA}
+By \Cref{def:filler,def:switch}, the fillers $(v,v')$, $(u,u')$ and $(w,w')$ give us the following three diagrams 
+			\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
+			\[\xymatrix{&&R_1 \ar@/_1cm/[ddrr]_(.35){a_1}|(.7)\hole \ar[dr]^{h_1}&& L_2\ar@/^1cm/[ddll]^(.35){a_2}  \ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar[dl]_{l_1} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){u}\ar[ur]^{r_1}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){u'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_1 \ar@/_.8cm/[ddrr]_(.2){b_1}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_1}|(.61)\hole && D_1 \ar[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){b_2}|(.31)\hole|(.81)\hole\ar[dl]_{h_2}\\&G_1 &&P_2\ar[dr]_{d_2} \ar[dl]^{d_1}\ar[ur]^(.4){c_2}\ar[ul]_(.4){c_1}&&G_2\\L_2 \ar@/^.8cm/[uurr]^(.2){a_2} \ar[ur]_(.35){f_1\circ a_2}|(.61)\hole&&Q_2 \ar[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1} &&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar[dl]|(.5)\hole_(.65){x_2} && R_1  \ar[ul]^(.35){g_2\circ a_1}|(.61)\hole\ar@/_.8cm/[uull]_(.2){a_1}\\&K_2 \ar[ur]_{d_1\circ u'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){u'}&&G'_2&& K_1 \ar[ur]_{r_1} \ar[ul]^{d_2\circ u} \ar[dl]^{l_1} \ar@/_.8cm/[uull]^(.65){u}\\&& R_2 \ar[ur]_{\hspace{-5pt}x_2\circ b_2}\ar@/^1cm/[uurr]^(.25){b_2}&& L_1 \ar[ul]^{y_1\circ b_1\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){b_1} |(.69)\hole }\]
+			\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){e_0}|(.7)\hole \ar[dr]^{h_0}&& L_2\ar@/^1cm/[ddll]^(.35){e_1}  \ar[dl]_{f_1\circ a_2}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){w}\ar[ur]^{r_0}&& G_1 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){w'}\ar[dl]_{d_1\circ u'\hspace{-5pt}}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_0 \ar@/_.8cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2 \ar[dr]|(.4)\hole^(.65){y_1} \ar[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.8cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){x_2\circ b_2}\\&G_0 &&P_3\ar[dr]_{n_1} \ar[dl]^{n_0}\ar[ur]^(.4){u_1}\ar[ul]_(.4){u_0}&&G'_2\\L_2 \ar@/^.8cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ e_1}|(.61)\hole&&Q_4 \ar[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0} &&Q_5\ar[ur]|(.4)\hole^(.65){z'_1} \ar[dl]|(.5)\hole_(.65){z_1} && R_0  \ar[ul]^(.35){g_1\circ e_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){e_0}\\&K_2 \ar[ur]_{n_0\circ w'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){w'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{n_1\circ w} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){w}\\&& R_2 \ar[ur]_{\hspace{-4pt}z_1\circ o_1}\ar@/^1cm/[uurr]^(.25){o_1}&& L_0 \ar[ul]^{z'_0\circ o_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){o_0} |(.69)\hole }\]
+
+		To construct a filler between $S_{w,w'}(\dder{D}_0)$ and $S_{u,u'}(\dder{D}_1)$,  we can start pulling back $x_2:Q_3\to G'_2$, which is in $\mathcal{M}$, along $z'_1:Q_5\to G'_2$ along  to get the solid part of the diagram below.
+			\[\xymatrix{&&R_0 \ar@{.>}@/_1cm/[ddrr]_(.25){\alpha_1}|(.7)\hole  \ar[dr]^{\hspace{-4pt}g_1\circ e_0}&& L_1\ar@{.>}@/^1cm/[ddll]^(.25){\alpha_2}  \ar[dl]_{y_1\circ b_1\hspace{-4pt}}\\&K_0\ar[dr]^{n_1\circ w}\ar[dl]_{l_0} \ar@{.>}@/_.8cm/[ddrr]_(.65){\beta}\ar[ur]^{r_0}&& G'_2&& K_1 \ar@{.>}@/^.8cm/[ddll]^(.65){\beta'}\ar[dl]_{d_2\circ u}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar[dr]_{z'_0\circ o_0} && Q_5 \ar[dl]|(.4)\hole_(.6){z_1}\ar[ur]|(.5)\hole^(.7){z'_1}&&Q_3 \ar[dr]|(.4)\hole^(.65){y_2} \ar[ul]|(.5)\hole_(.7){x_2}&&R_1\ar@{.>}@/^.8cm/[ddll]^{\gamma'}\ar[dl]_(.4){g_2\circ a_1}\\&G'_1 &&P_4\ar@{.>}[dr]^{\epsilon'} \ar[ur]^(.4){\delta'}\ar[ul]_(.4){\delta}&&G_2\\&& &&Q_6}\]
+
+		Let us construct the dotted arrows.
+		\begin{itemize}
+		\item Existence of $\beta$. Comsider the arrows $i_0\circ r_0:K_0\to D_1$ and $u_1\circ w:K_0\to Q_2$. Then
+		\begin{align*}
+	f_1\circ i_0\circ r_0&=h_0\circ r_0\\&=g_0\circ k_0\\&=g_0\circ u_0\circ w\\&=x_1\circ u_1\circ w
+		\end{align*}
+		\item Existence of $\beta'$. We proceed as above, this time taking the arrows $i_1\circ l_1:K_1\to D_0$ and $d_1\circ u:K_1\to Q_2$. We get
+		\begin{align*}
+			g_0\circ i_1\circ l_1&=m_1\circ l_1\\&=f_1\circ k_1\\&f_1\circ c_1\circ u\\&=x_1\circ d_1\circ u
+		\end{align*}
+		giving a unique $\underline{\beta}':K_1\to P_3$ fitting in the diagram 
+		\[\xymatrix{K_1 \ar@{.>}[dr]^{\underline{\beta}'} \ar[r]^{l_1} \ar[d]_{u}& L_1 \ar@/^.2cm/[dr]^{i_1}\\ P_2 \ar@/_.2cm/[dr]_{d_1}&P_3 \ar[r]^{u_0} \ar[d]_{u_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar[r]_{x_1} & G_1}\]
+		If we compute we get
+		\begin{align*}
+			z'_1\circ n_1\circ\underline{\beta}'&=y_1\circ u_1\circ \underline{\beta}'\\&=y_1\circ d_1\circ u\\&=x_2\circ d_2\circ u
+		\end{align*}
+		Therefore there is $\beta':K_1\to P_4$ such that
+		\[\xymatrix{K_1 \ar@{.>}[dr]^{\beta'} \ar[r]^{\underline{\beta}'} \ar[d]_{u}& P_3 \ar@/^.2cm/[dr]^{n_1}\\ P_2 \ar@/_.2cm/[dr]_{d_2}&P_4 \ar[r]^{\delta} \ar[d]_{\delta'}& Q_5 \ar[d]^{z'_1}\\ &Q_3\ar[r]_{x_2} & G'_2}\]
+		commutes.
+		\item Existence of $\alpha_1$.
+		\item Existence of $\alpha_2$.
+		\item Existence of $\epsilon'$.
+		\item Existence of $\gamma'$.
+		\end{itemize}
+
+		Finally, we have to show that these data form a filler.
+	\begin{enumerate}
+		\item 
+		\item 
+	\end{enumerate} 
+\end{proof}
+
+\begin{lemma}[Invariance under immediate shift, 2]\todo{nell'altro senso}
+\end{lemma}
+\begin{proof}
+ \todo{fare} \qed 
+\end{proof}
+
+\begin{corollary}
+\todo{passare a $\updownarrow_!$ e $\Updownarrow$}
+\end{corollary}
+
+\todo{ricopiare tutta l'induzione di Andrea}
 \subsection{Concatenable traces}
@@
 \appendix
+\section{On permutations}\label{app:perm}
+\todo{inserire risutati sulle permutazione che abbiamo usato}
+
 \section{A note on fillers and sequential independence}\label{app:fill}

### 2023-10-16 fusione.tex
ind is global

@@
 
-\begin{remark}\label{rem:obv}Notice that if $\dder{D}$ and $\dder{D}'$ are switchable, then they are weakly sequentially independent: indeed, if a filler between them exists, then $(i_1, i_2)$ is an independence pair.
-\end{remark}
-
 \begin{remark}\label{rem:deco} Let $\dder{D}$ and $\dder{D'}$ be two switchable direct derivations. Then the existence of a filler allows us to build the solid part of the diagram below.
@@
 
-Before proceeding further, let us show that, in the linear case, the switchability relation reduces to sequential independence.
-
-\begin{proposition}\label{prop:equi}Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a linear DPO-rewriting system.
-Given two direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, the following are equivalent:
-	\begin{enumerate}
-		\item there exists a filler between $\dder{D}$ and $\dder{D'}$;
-		\item $\dder{D}$ and $\dder{D'}$ are sequentially independent.
-	\end{enumerate}
+Notice that if $\dder{D}$ and $\dder{D}'$ are switchable, then they are weakly sequentially independent: indeed, if a filler between them exists, then $(i_1, i_2)$ is an independence pair.
+
+\begin{definition}We will say that a left-linear DPO-rewriting system  $(\X, \R)$ is \emph{tame} if for every two direct derivations $\dder{D}:H\Mapsto H$, $\dder{D}':H\Mapsto T$ and for every independence pair $(i_1, i_2)$ between them, there exists a filler $(u,u')$ between them such that  the squares below are pushouts.\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
+\end{definition}
+
+\begin{proposition}\label{prop:equi}Every linear DPO-rewriting system. $(\X, \R)$ a linear is tame.
  \end{proposition}
-\begin{proof} $(1\Rightarrow 2)$ This follows immediately from \Cref{rem:weak,rem:deco}.
-
-	\smallskip \noindent $(2\Rightarrow 1)$  By hypothesis, we have a diagram
+\begin{proof} Let $(i_1, i_2)$ be an independence pair between $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$. We have a diagram
 	\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
@@
 
-\begin{lemma}[Invariance under immediate shift, 1] Let $(\X,\R)$ be a left-linear DPO-rewriting system consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$.
+\begin{lemma}Let $(\X,\R)$ be a tame left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
+Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$.
 If $(v,v')$ is a filler between $\dder{D}_0$ and $\dder{D}_1$, $(u,u')$ one between $\dder{D}_1$ and $\dder{D}_2$ and $\dder{D}_0\updownarrow S_{u,u'}(\dder{D}_2)$ with filler $(w,w')$, then there exists a filler between $S_{w,w'}(\dder{D}_0)$ and $S_{u,u'}(\dder{D}_1)$.
@@
 \begin{proof}
-By \Cref{def:filler,def:switch}, the fillers $(v,v')$, $(u,u')$ and $(w,w')$ give us the following three diagrams 
+We can use \Cref{def:filler,def:switch} to get some diagrams.  First of all the filler $(v,v')$ between $\dder{D}_0$ and $\dder{D}_1$ yields
 			\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
-			\[\xymatrix{&&R_1 \ar@/_1cm/[ddrr]_(.35){a_1}|(.7)\hole \ar[dr]^{h_1}&& L_2\ar@/^1cm/[ddll]^(.35){a_2}  \ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar[dl]_{l_1} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){u}\ar[ur]^{r_1}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){u'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_1 \ar@/_.8cm/[ddrr]_(.2){b_1}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_1}|(.61)\hole && D_1 \ar[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){b_2}|(.31)\hole|(.81)\hole\ar[dl]_{h_2}\\&G_1 &&P_2\ar[dr]_{d_2} \ar[dl]^{d_1}\ar[ur]^(.4){c_2}\ar[ul]_(.4){c_1}&&G_2\\L_2 \ar@/^.8cm/[uurr]^(.2){a_2} \ar[ur]_(.35){f_1\circ a_2}|(.61)\hole&&Q_2 \ar[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1} &&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar[dl]|(.5)\hole_(.65){x_2} && R_1  \ar[ul]^(.35){g_2\circ a_1}|(.61)\hole\ar@/_.8cm/[uull]_(.2){a_1}\\&K_2 \ar[ur]_{d_1\circ u'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){u'}&&G'_2&& K_1 \ar[ur]_{r_1} \ar[ul]^{d_2\circ u} \ar[dl]^{l_1} \ar@/_.8cm/[uull]^(.65){u}\\&& R_2 \ar[ur]_{\hspace{-5pt}x_2\circ b_2}\ar@/^1cm/[uurr]^(.25){b_2}&& L_1 \ar[ul]^{y_1\circ b_1\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){b_1} |(.69)\hole }\]
-			\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){e_0}|(.7)\hole \ar[dr]^{h_0}&& L_2\ar@/^1cm/[ddll]^(.35){e_1}  \ar[dl]_{f_1\circ a_2}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){w}\ar[ur]^{r_0}&& G_1 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){w'}\ar[dl]_{d_1\circ u'\hspace{-5pt}}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_0 \ar@/_.8cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2 \ar[dr]|(.4)\hole^(.65){y_1} \ar[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.8cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){x_2\circ b_2}\\&G_0 &&P_3\ar[dr]_{n_1} \ar[dl]^{n_0}\ar[ur]^(.4){u_1}\ar[ul]_(.4){u_0}&&G'_2\\L_2 \ar@/^.8cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ e_1}|(.61)\hole&&Q_4 \ar[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0} &&Q_5\ar[ur]|(.4)\hole^(.65){z'_1} \ar[dl]|(.5)\hole_(.65){z_1} && R_0  \ar[ul]^(.35){g_1\circ e_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){e_0}\\&K_2 \ar[ur]_{n_0\circ w'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){w'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{n_1\circ w} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){w}\\&& R_2 \ar[ur]_{\hspace{-4pt}z_1\circ o_1}\ar@/^1cm/[uurr]^(.25){o_1}&& L_0 \ar[ul]^{z'_0\circ o_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){o_0} |(.69)\hole }\]
-
-		To construct a filler between $S_{w,w'}(\dder{D}_0)$ and $S_{u,u'}(\dder{D}_1)$,  we can start pulling back $x_2:Q_3\to G'_2$, which is in $\mathcal{M}$, along $z'_1:Q_5\to G'_2$ along  to get the solid part of the diagram below.
-			\[\xymatrix{&&R_0 \ar@{.>}@/_1cm/[ddrr]_(.25){\alpha_1}|(.7)\hole  \ar[dr]^{\hspace{-4pt}g_1\circ e_0}&& L_1\ar@{.>}@/^1cm/[ddll]^(.25){\alpha_2}  \ar[dl]_{y_1\circ b_1\hspace{-4pt}}\\&K_0\ar[dr]^{n_1\circ w}\ar[dl]_{l_0} \ar@{.>}@/_.8cm/[ddrr]_(.65){\beta}\ar[ur]^{r_0}&& G'_2&& K_1 \ar@{.>}@/^.8cm/[ddll]^(.65){\beta'}\ar[dl]_{d_2\circ u}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar[dr]_{z'_0\circ o_0} && Q_5 \ar[dl]|(.4)\hole_(.6){z_1}\ar[ur]|(.5)\hole^(.7){z'_1}&&Q_3 \ar[dr]|(.4)\hole^(.65){y_2} \ar[ul]|(.5)\hole_(.7){x_2}&&R_1\ar@{.>}@/^.8cm/[ddll]^{\gamma'}\ar[dl]_(.4){g_2\circ a_1}\\&G'_1 &&P_4\ar@{.>}[dr]^{\epsilon'} \ar[ur]^(.4){\delta'}\ar[ul]_(.4){\delta}&&G_2\\&& &&Q_6}\]
+
+	Secondly, the filler $(u,u')$ between $\dder{D}_1$ and $\dder{D}_2$ gives us another diagram:
+\[
+			\xymatrix{&&R_1 \ar@/_1cm/[ddrr]_(.35){a_1}|(.7)\hole \ar[dr]^{h_1}&& L_2\ar@/^1cm/[ddll]^(.35){a_2}  \ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar[dl]_{l_1} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){u}\ar[ur]^{r_1}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){u'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_1 \ar@/_.8cm/[ddrr]_(.2){b_1}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_1}|(.61)\hole && D_1 \ar[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){b_2}|(.31)\hole|(.81)\hole\ar[dl]_{h_2}\\&G_1 &&P_2\ar[dr]_{d_2} \ar[dl]^{d_1}\ar[ur]^(.4){c_2}\ar[ul]_(.4){c_1}&&G_2\\L_2 \ar@/^.8cm/[uurr]^(.2){a_2} \ar[ur]_(.35){f_1\circ a_2}|(.61)\hole&&Q_2 \ar[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1} &&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar[dl]|(.5)\hole_(.65){x_2} && R_1  \ar[ul]^(.35){g_2\circ a_1}|(.61)\hole\ar@/_.8cm/[uull]_(.2){a_1}\\&K_2 \ar[ur]_{d_1\circ u'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){u'}&&G'_2&& K_1 \ar[ur]_{r_1} \ar[ul]^{d_2\circ u} \ar[dl]^{l_1} \ar@/_.8cm/[uull]^(.65){u}\\&& R_2 \ar[ur]_{\hspace{-5pt}x_2\circ b_2}\ar@/^1cm/[uurr]^(.25){b_2}&& L_1 \ar[ul]^{y_1\circ b_1\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){b_1} |(.69)\hole }\]
+
+	Finally, the filler $(w,w')$ between $\dder{D}_0$ and $S_{u,u'}(\dder{D}_2)$ provides us with:
+			\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){e_0}|(.7)\hole \ar[dr]^{h_0}&& L_2\ar@/^1cm/[ddll]^(.35){e_1}  \ar[dl]_{f_1\circ a_2}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){w}\ar[ur]^{r_0}&& G_1 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){w'}\ar[dl]_{d_1\circ u'\hspace{-5pt}}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_0 \ar@/_.8cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2 \ar[dr]|(.4)\hole^(.65){y_1} \ar[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.8cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){x_2\circ b_2}\\&G_0 &&P_3\ar[dr]_{n_1} \ar[dl]^{n_0}\ar[ur]^(.4){u_1}\ar[ul]_(.4){u_0}&&G'_2\\L_2 \ar@/^.8cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ e_1}|(.61)\hole&&Q_4 \ar[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0} &&Q_5\ar[ur]|(.4)\hole^(.65){z'_1} \ar[dl]|(.5)\hole_(.65){z_1} && R_0  \ar[ul]^(.35){y_1\circ e_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){e_0}\\&K_2 \ar[ur]_{n_0\circ w'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){w'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{n_1\circ w} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){w}\\&& R_2 \ar[ur]_{\hspace{-4pt}z_1\circ o_1}\ar@/^1cm/[uurr]^(.25){o_1}&& L_0 \ar[ul]^{z'_0\circ o_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){o_0} |(.69)\hole }\]
+
+		By tameness of $(\X,\R)$, to construct a filler between $S_{w,w'}(\dder{D}_0)$ and $S_{u,u'}(\dder{D}_1)$, it is enough to construct the two dotted arrows in the diagram below.
+			\[\xymatrix@C=15pt{L_.
+\ar[d]_{z'_0\circ o_0}&& K_0 \ar[d]_{n_1\circ w}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@{.>}@/^.35cm/[drrr]_(.4){\alpha_1}|(.285)\hole \ar[dr]|(.28)\hole_{y_1\circ e_0} && L_1 \ar@{.>}@/_.35cm/[dlll]^(.4){\alpha_2} \ar[dl]|(.28)\hole^{y_1\circ b_1}& K_1 \ar[d]^{d_2\circ u}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ a_1}\\G'_1 && \ar[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2  && \ar[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_2}\]
+
+		Consider the arrows $i_0:R_0\to D_1$ and $e_0:R_0\to Q_2$. An easy computation shows that
+			\begin{align*}
+				f_1\circ i_0&= h_0\\&=x_1\circ e_0
+			\end{align*}
+			entailing the existence of  the dotted $\alpha'_1:R_0\to P_2$ in the diagram
+			\[\xymatrix{R_0 \ar@{.>}[dr]^{\alpha'_1} \ar@/^.3cm/[drr]^{i_0} \ar@/_.3cm/[ddr]_{e_0}\\ &P_2 \ar[r]^{c_2} \ar[d]_{d_1}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
+			If we define $\alpha_1:R_0\to Q_3$ as $d_2\circ \alpha'_1$, then we easily get that 
+		\begin{align*}
+			x_2\circ \alpha_1&=x_2\circ d_2\circ \alpha'_1\\&= y_1\circ d_1\circ \alpha'_1\\&=y_1\circ e_0
+		\end{align*}
+
+		For $\alpha_2$, we proceed similarly. First consider  $i_1:L_1\to D_0$ and $b_1: L_1 \to Q_2$ and notice that
+		\begin{align*}
+			g_0\circ i_1&= m_1 \\&= x_1 \circ b_1
+		\end{align*}
+			implying the existence of $\alpha'_2:L_1\to P_3$ fitting in the fiagram below.
+			\[\xymatrix{L_1 \ar@{.>}[dr]^{\alpha'_2} \ar@/^.3cm/[drr]^{i_1} \ar@/_.3cm/[ddr]_{e_0}\\ &P_2 \ar[r]^{c_2} \ar[d]_{d_1}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
+
+		\iffalse 
+		  we can start pulling back $x_2:Q_3\to G'_2$, which is in $\mathcal{M}$, along $z'_1:Q_5\to G'_2$ along  to get the solid part of the diagram below.
+			\[\xymatrix{&&R_0 \ar@{.>}@/_1cm/[ddrr]_(.25){\alpha_1}|(.7)\hole  \ar[dr]^{\hspace{-4pt}y_1\circ e_0}&& L_1\ar@{.>}@/^1cm/[ddll]^(.25){\alpha_2}  \ar[dl]_{y_1\circ b_1\hspace{-4pt}}\\&K_0\ar[dr]^{n_1\circ w}\ar[dl]_{l_0} \ar@{.>}@/_.8cm/[ddrr]_(.65){\beta}\ar[ur]^{r_0}&& G'_2&& K_1 \ar@{.>}@/^.8cm/[ddll]^(.65){\beta'}\ar[dl]_{d_2\circ u}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar[dr]_{z'_0\circ o_0} && Q_5 \ar[dl]|(.4)\hole_(.6){z_1}\ar[ur]|(.5)\hole^(.7){z'_1}&&Q_3 \ar[dr]|(.4)\hole^(.65){y_2} \ar[ul]|(.5)\hole_(.7){x_2}&&R_1\ar@{.>}@/^.8cm/[ddll]^{\gamma'}\ar[dl]_(.4){g_2\circ a_1}\\&G'_1 &&P_4\ar@{.>}[dr]^{\epsilon'} \ar[ur]^(.4){\delta'}\ar[ul]_(.4){\delta}&&G_2\\&& &&Q_6}\]
 
@@
 		\begin{itemize}
-		\item Existence of $\beta$. Comsider the arrows $i_0\circ r_0:K_0\to D_1$ and $u_1\circ w:K_0\to Q_2$. Then
+		\item Existence of $\beta$. Consider the arrows $i_0\circ r_0:K_0\to D_1$ and $u_1\circ w:K_0\to Q_2$. Then
 		\begin{align*}
@@
 		\end{align*}
+		Therefore there exists a unique $\underline{\beta}:K_0\to P_2$ making the diagram 
+		\[\xymatrix{K_0 \ar@{.>}[dr]^{\underline{\beta}} \ar[r]^{r_0} \ar[d]_{w}& R_0 \ar@/^.2cm/[dr]^{i_0}\\ P_3 \ar@/_.2cm/[dr]_{u_1}&P_2 \ar[r]^{c_1} \ar[d]_{d_1}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
+		commutative. Computing further we also get
+		\begin{align*}
+		x_2\circ d_2\circ \underline{\beta}&=y_1\circ d_1\circ \underline{\beta}\\&=y_1\circ u_1\circ w\\&=z'_1\circ u_1\circ w
+		\end{align*}
+		We conclude that there exists the dotted  $\beta: K_0\to P_4$ depicted in the diagram below.
+		\[\xymatrix{K_0 \ar@{.>}[dr]^{\beta} \ar[r]^{\underline{\beta}} \ar[d]_{w}& P_2 \ar@/^.2cm/[dr]^{d_2}\\ P_3 \ar@/_.2cm/[dr]_{n_1}&P_4 \ar[r]^{\delta'} \ar[d]_{\delta}& Q_3 \ar[d]^{x_2}\\ &Q_5\ar[r]_{z'_1} & G'_2}\]
 		\item Existence of $\beta'$. We proceed as above, this time taking the arrows $i_1\circ l_1:K_1\to D_0$ and $d_1\circ u:K_1\to Q_2$. We get
 		\begin{align*}
-			g_0\circ i_1\circ l_1&=m_1\circ l_1\\&=f_1\circ k_1\\&f_1\circ c_1\circ u\\&=x_1\circ d_1\circ u
+			g_0\circ i_1\circ l_1&=m_1\circ l_1\\&=f_1\circ k_1\\&=f_1\circ c_1\circ u\\&=x_1\circ d_1\circ u
 		\end{align*}
@@
 		commutes.
-		\item Existence of $\alpha_1$.
+		\item Existence of $\alpha_1$. Let us consider the arrows $i_0:R_0\to D_1$ and $e_0:R_0\to Q_2$. An easy computation shows that
+		\begin{align*}
+			f_1\circ i_0&= h_0\\&=x_1\circ e_0
+		\end{align*}
+	entailing the existence of  $\alpha'_1:R_0\to P_2$
+	\[\xymatrix{R_0 \ar@{.>}[dr]^{\alpha'_1} \ar@/^.3cm/[drr]^{i_0} \ar@/_.3cm/[ddr]_{e_0}\\ &P_2 \ar[r]^{c_2} \ar[d]_{d_1}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
+	We can then define $\alpha_1:R_0\to Q_3$ as $d_2\circ \alpha'_1$. Notice that 
+	\begin{align*}
+x_2\circ \alpha_1&=x_2\circ d_2\circ \alpha'_1\\&= y_1\circ d_1\circ \alpha'_1\\&=y_1\circ e_0
+	\end{align*}
+This equality, in turn, implies	
+		\begin{align*}
+x_2\circ \alpha_1\circ r_0&=y_1\circ e_0\circ r_0\\&=y_1\circ  u_1\circ w \\&= z'_1\circ  n_1\circ w \\&= z'_1 \circ \beta \circ \delta \\&= x_2\circ \beta \circ \delta' 
+	\end{align*}
+	Since $x_2$ is mono, because $x_2\in \mathcal{M}$, we conclude that the square below is commutative.
+	\[\xymatrix{K_0 \ar[r]^{r_0} \ar[d]_{\beta}& R_0  \ar[d]^{\alpha_1}\\ P_4 \ar[r]_{\delta'} & Q_3}\]
+
 		\item Existence of $\alpha_2$.
@@
 	\begin{enumerate}
-		\item 
-		\item 
-	\end{enumerate} 
-\end{proof}
-
-\begin{lemma}[Invariance under immediate shift, 2]\todo{nell'altro senso}
+		\item \todo{This follows by definition}
+		\item We have to show that the following two squares are pushouts
+		\[\xymatrix{}\]
+
+		\smallskip
+		For the first one, consider the diagram
+		\[\xymatrix{K_0 \ar[r]^{r_0} \ar[d]_{\beta}& R_0  \ar[d]^{\alpha_1}\\ P_4 \ar[r]_{\delta'} & Q_3\\&& U}\]
+			\[\xymatrix{K_0 \ar[r]^{r_0} \ar[d]_{\beta}& R_0  \ar[d]^{\alpha_1}\\ P_4 \ar[r]_{\delta'} & Q_3}\]
+
+			\[\xymatrix{K_0 \ar[r]^{r_0} \ar[d]_{\beta}& R_0  \ar[d]^{\alpha_1}\\ P_4 \ar[r]_{\delta'} & Q_3}\]
+
+		For the second one
+	\end{enumerate} 
+	\fi  
+\end{proof}
+
+\begin{corollary}
+	\todo{passare a $\updownarrow_!$ e $\Updownarrow$}
+\end{corollary}
+
+\begin{lemma}\todo{nell'altro senso}
 \end{lemma}
@@
 \todo{passare a $\updownarrow_!$ e $\Updownarrow$}
+\end{corollary}
+
+\begin{corollary}[Invariance under shift]
+	contenuto...
 \end{corollary}

### 2023-10-17 fusione.tex
da cancellare: unicità dei filler

@@
 \title{Switch equivalence and weak prime domains for fusions}
-\author{Paolo Baldan \and Davide Castelnovo  \and  Andrea Corradini  Fabio Gadducci}
+\author{Paolo Baldan \and Davide Castelnovo  \and  Andrea Corradini  \and Fabio Gadducci}
 
@@
 
-\section{Switch equivalence and traces}
+\section{Shift equivalence and traces}
 \todo{A VERY NICE INTRO}
@@
 
-\begin{remark}\todo{oss su unicità del filler}
+\begin{remark}A remark on the uniqueness of filler is due.
+Let $\der{D}:\Mapsto H$ and $\der{D}':G\Mapsto T$ be two direct derivations such that $\der{D}\updownarrow_!
+\der{D}'$.
+The uniqueness of the filler between them must be interpreted only up to a choice of a pullback square
+	\[\xymatrix{P \ar[r]^{p} \ar[d]_{p'}& D\ar[d]^{g} \\ D' \ar[r]_{f'} & H}\]
 \end{remark}
@@
 
-\begin{proposition}\label{prop:equi}Every linear DPO-rewriting system. $(\X, \R)$ a linear is tame.
+\begin{remark}\label{rem:unic} Given an independence pair $(i_1, i_2)$ between $\dder{D}$ and $\dder{D}'$, there is at most one filler  such that $(u,u')$ such that 
+	\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
+	are pushouts. Indeed, for every other filler $(v,v')$, it must be that
+	\[\begin{split}
+		p\circ u &=k \\&= p\circ v
+	\end{split}\qquad \begin{split}
+	p\circ u' &= i_2\circ l' \\&= p\circ v'
+	\end{split}\]
+	Since the arrow $p:P\to D$, which is the pullback of $f'$, is in $\mathcal{M}$ we conclude that $(u,u')=(v,v')$.
+\end{remark}
+
+\begin{proposition}\label{prop:filip}
+Let $(\X, \R)$ be a tame left-linear DPO-rewriting system, then, given $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, the following are equivalent:
+\begin{enumerate}
+	\item $\dder{D}$ and $\dder{D}'$ are sequentially independent;
+	\item $\dder{D}\updownarrow_! \dder{D}'$.
+\end{enumerate}
 \end{proposition}
-\begin{proof} Let $(i_1, i_2)$ be an independence pair between $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$. We have a diagram
+\begin{proof} $(1\Rightarrow 2)$ Let $(i_1, i_2)$ be the unique independence pair between $\dder{D}$ and $\dder{D}$'.
+Take a pullback square \[\xymatrix{P \ar[r]^{p} \ar[d]_{p'}& D\ar[d]^{g} \\ D' \ar[r]_{f'} & H}\]
+by tameness we know that there exist a filler $(u,u')$ made by arrows $u:K\to P$ and $u':K'\to P$ fitting in the two pushout squares below. 
+	\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
+	In particular, 	$\der{D}\updownarrow \der{D'}$. On the other hand, if $(v,v')$ with $v:K\to P$ and $v':K'\to P$ is another filler, then there are other  two pushout squares
+	\[\xymatrix{K \ar[r]^{r} \ar[d]_{v}& R \ar[d]^{j_1} &K' \ar[r]^{l'} \ar[d]_{v'}& L'\ar[d]^{j_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
+	such that $f'\circ j_1=h$, $g\circ j_2=n'$. But then $(j_1, j_2)$ is an independence pair and so $j_1=i_1$ and $j_2=i_2$. \Cref{rem:unic} now yields the thesis.
+
+	\smallskip \noindent $(2\Rightarrow 1)$ Let $(u,u')$ be the filler between $\dder{D}$ and $\dder{D}$'.
+Then we get an independence pair $(i_1, i_2)$ pushing out $u$ along $r$ and $u'$ along $l'$, respectively.
+If $(j_1, j_2)$ is another independence pair
+\end{proof}
+
+A source of tame left-linear DPO-rewriting systems is given by the linear ones, as shown by the following proposition.
+
+\begin{proposition}\label{prop:equi}Every linear DPO-rewriting system $(\X, \R)$ is tame.
+ \end{proposition}
+\begin{proof} Suppose that $\X$ is $\mathcal{M}$-adhesive and let $(i_1, i_2)$ be an independence pair between $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$. We have a diagram
 	\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
@@
 
-\begin{lemma}Let $(\X,\R)$ be a tame left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
+\begin{lemma}\label{lem:iig1}Let $(\X,\R)$ be a tame left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
 Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$.
@@
 		\end{align*}
-			implying the existence of $\alpha'_2:L_1\to P_3$ fitting in the fiagram below.
-			\[\xymatrix{L_1 \ar@{.>}[dr]^{\alpha'_2} \ar@/^.3cm/[drr]^{i_1} \ar@/_.3cm/[ddr]_{e_0}\\ &P_2 \ar[r]^{c_2} \ar[d]_{d_1}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
-
-		\iffalse 
-		  we can start pulling back $x_2:Q_3\to G'_2$, which is in $\mathcal{M}$, along $z'_1:Q_5\to G'_2$ along  to get the solid part of the diagram below.
-			\[\xymatrix{&&R_0 \ar@{.>}@/_1cm/[ddrr]_(.25){\alpha_1}|(.7)\hole  \ar[dr]^{\hspace{-4pt}y_1\circ e_0}&& L_1\ar@{.>}@/^1cm/[ddll]^(.25){\alpha_2}  \ar[dl]_{y_1\circ b_1\hspace{-4pt}}\\&K_0\ar[dr]^{n_1\circ w}\ar[dl]_{l_0} \ar@{.>}@/_.8cm/[ddrr]_(.65){\beta}\ar[ur]^{r_0}&& G'_2&& K_1 \ar@{.>}@/^.8cm/[ddll]^(.65){\beta'}\ar[dl]_{d_2\circ u}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar[dr]_{z'_0\circ o_0} && Q_5 \ar[dl]|(.4)\hole_(.6){z_1}\ar[ur]|(.5)\hole^(.7){z'_1}&&Q_3 \ar[dr]|(.4)\hole^(.65){y_2} \ar[ul]|(.5)\hole_(.7){x_2}&&R_1\ar@{.>}@/^.8cm/[ddll]^{\gamma'}\ar[dl]_(.4){g_2\circ a_1}\\&G'_1 &&P_4\ar@{.>}[dr]^{\epsilon'} \ar[ur]^(.4){\delta'}\ar[ul]_(.4){\delta}&&G_2\\&& &&Q_6}\]
-
-		Let us construct the dotted arrows.
-		\begin{itemize}
-		\item Existence of $\beta$. Consider the arrows $i_0\circ r_0:K_0\to D_1$ and $u_1\circ w:K_0\to Q_2$. Then
+			implying the existence of $\alpha'_2:L_1\to P_3$ fitting in the diagram below.
+			\[\xymatrix{L_1 \ar@{.>}[dr]^{\alpha'_2} \ar@/^.3cm/[drr]^{i_1} \ar@/_.3cm/[ddr]_{b_1}\\ &P_3 \ar[r]^{u_0} \ar[d]_{u_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar[r]_{x_1} & G_1}\] 
+			Let $\alpha_2:L_1\to Q_5$ be $n_1\circ \alpha'_2$, then
 			\begin{align*}
-	f_1\circ i_0\circ r_0&=h_0\circ r_0\\&=g_0\circ k_0\\&=g_0\circ u_0\circ w\\&=x_1\circ u_1\circ w
+				z'_1 \circ \alpha_2 & = z'_1 \circ n_1\circ \alpha'_2\\&=y_1\circ u_1\circ \alpha'_2\\&=y_1\circ b_1
 			\end{align*}
-		Therefore there exists a unique $\underline{\beta}:K_0\to P_2$ making the diagram 
-		\[\xymatrix{K_0 \ar@{.>}[dr]^{\underline{\beta}} \ar[r]^{r_0} \ar[d]_{w}& R_0 \ar@/^.2cm/[dr]^{i_0}\\ P_3 \ar@/_.2cm/[dr]_{u_1}&P_2 \ar[r]^{c_1} \ar[d]_{d_1}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
-		commutative. Computing further we also get
-		\begin{align*}
-		x_2\circ d_2\circ \underline{\beta}&=y_1\circ d_1\circ \underline{\beta}\\&=y_1\circ u_1\circ w\\&=z'_1\circ u_1\circ w
-		\end{align*}
-		We conclude that there exists the dotted  $\beta: K_0\to P_4$ depicted in the diagram below.
-		\[\xymatrix{K_0 \ar@{.>}[dr]^{\beta} \ar[r]^{\underline{\beta}} \ar[d]_{w}& P_2 \ar@/^.2cm/[dr]^{d_2}\\ P_3 \ar@/_.2cm/[dr]_{n_1}&P_4 \ar[r]^{\delta'} \ar[d]_{\delta}& Q_3 \ar[d]^{x_2}\\ &Q_5\ar[r]_{z'_1} & G'_2}\]
-		\item Existence of $\beta'$. We proceed as above, this time taking the arrows $i_1\circ l_1:K_1\to D_0$ and $d_1\circ u:K_1\to Q_2$. We get
-		\begin{align*}
-			g_0\circ i_1\circ l_1&=m_1\circ l_1\\&=f_1\circ k_1\\&=f_1\circ c_1\circ u\\&=x_1\circ d_1\circ u
-		\end{align*}
-		giving a unique $\underline{\beta}':K_1\to P_3$ fitting in the diagram 
-		\[\xymatrix{K_1 \ar@{.>}[dr]^{\underline{\beta}'} \ar[r]^{l_1} \ar[d]_{u}& L_1 \ar@/^.2cm/[dr]^{i_1}\\ P_2 \ar@/_.2cm/[dr]_{d_1}&P_3 \ar[r]^{u_0} \ar[d]_{u_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar[r]_{x_1} & G_1}\]
-		If we compute we get
-		\begin{align*}
-			z'_1\circ n_1\circ\underline{\beta}'&=y_1\circ u_1\circ \underline{\beta}'\\&=y_1\circ d_1\circ u\\&=x_2\circ d_2\circ u
-		\end{align*}
-		Therefore there is $\beta':K_1\to P_4$ such that
-		\[\xymatrix{K_1 \ar@{.>}[dr]^{\beta'} \ar[r]^{\underline{\beta}'} \ar[d]_{u}& P_3 \ar@/^.2cm/[dr]^{n_1}\\ P_2 \ar@/_.2cm/[dr]_{d_2}&P_4 \ar[r]^{\delta} \ar[d]_{\delta'}& Q_5 \ar[d]^{z'_1}\\ &Q_3\ar[r]_{x_2} & G'_2}\]
-		commutes.
-		\item Existence of $\alpha_1$. Let us consider the arrows $i_0:R_0\to D_1$ and $e_0:R_0\to Q_2$. An easy computation shows that
-		\begin{align*}
-			f_1\circ i_0&= h_0\\&=x_1\circ e_0
-		\end{align*}
-	entailing the existence of  $\alpha'_1:R_0\to P_2$
-	\[\xymatrix{R_0 \ar@{.>}[dr]^{\alpha'_1} \ar@/^.3cm/[drr]^{i_0} \ar@/_.3cm/[ddr]_{e_0}\\ &P_2 \ar[r]^{c_2} \ar[d]_{d_1}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
-	We can then define $\alpha_1:R_0\to Q_3$ as $d_2\circ \alpha'_1$. Notice that 
-	\begin{align*}
-x_2\circ \alpha_1&=x_2\circ d_2\circ \alpha'_1\\&= y_1\circ d_1\circ \alpha'_1\\&=y_1\circ e_0
-	\end{align*}
-This equality, in turn, implies	
-		\begin{align*}
-x_2\circ \alpha_1\circ r_0&=y_1\circ e_0\circ r_0\\&=y_1\circ  u_1\circ w \\&= z'_1\circ  n_1\circ w \\&= z'_1 \circ \beta \circ \delta \\&= x_2\circ \beta \circ \delta' 
-	\end{align*}
-	Since $x_2$ is mono, because $x_2\in \mathcal{M}$, we conclude that the square below is commutative.
-	\[\xymatrix{K_0 \ar[r]^{r_0} \ar[d]_{\beta}& R_0  \ar[d]^{\alpha_1}\\ P_4 \ar[r]_{\delta'} & Q_3}\]
-
-		\item Existence of $\alpha_2$.
-		\item Existence of $\epsilon'$.
-		\item Existence of $\gamma'$.
-		\end{itemize}
-
-		Finally, we have to show that these data form a filler.
-	\begin{enumerate}
-		\item \todo{This follows by definition}
-		\item We have to show that the following two squares are pushouts
-		\[\xymatrix{}\]
-
-		\smallskip
-		For the first one, consider the diagram
-		\[\xymatrix{K_0 \ar[r]^{r_0} \ar[d]_{\beta}& R_0  \ar[d]^{\alpha_1}\\ P_4 \ar[r]_{\delta'} & Q_3\\&& U}\]
-			\[\xymatrix{K_0 \ar[r]^{r_0} \ar[d]_{\beta}& R_0  \ar[d]^{\alpha_1}\\ P_4 \ar[r]_{\delta'} & Q_3}\]
-
-			\[\xymatrix{K_0 \ar[r]^{r_0} \ar[d]_{\beta}& R_0  \ar[d]^{\alpha_1}\\ P_4 \ar[r]_{\delta'} & Q_3}\]
-
-		For the second one
-	\end{enumerate} 
-	\fi  
+			The thesis now follows. \qed
+\end{proof}
+
+\begin{corollary} Given a tame  left-linear DPO-rewriting system  $(\X,\R)$ with $\X$ an $\mathcal{M}$-adhesive category and a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$, the following are true: 
+	\begin{enumerate}
+		\item suppose that $(u,u')$ and $(w,w')$ are fillers witnessing  $\dder{D}_1\updownarrow_!
+\dder{D}_2$ and $\dder{D}_0\updownarrow_!
+S_{u,u'}(\dder{D}_2)$ respectively, if $\dder{D}_0\updownarrow_!\dder{D}_1$, then $S_{w,w'}(\dder{D}_0)\updownarrow_!S_{u,u'}(\dder{D}_1)$;
+		\item 
+	\end{enumerate}
+\end{corollary}
+\begin{proof}
+	\begin{enumerate}
+		\item Let $(v,v')$ be the unique filler between $\dder{D}_0$ and $\dder{D}_1$.  By \Cref{rem:filip}
+		\item \qed 
+	\end{enumerate}
+\end{proof}
+
+ We need another lemma, similar to \Cref{lem:iig1}.
+\begin{lemma}\label{lem:iig2}\todo{nell'altro senso}
+\end{lemma}
+\begin{proof}
+ \todo{fare} \qed 
 \end{proof}
@@
 
-\begin{lemma}\todo{nell'altro senso}
-\end{lemma}
-\begin{proof}
- \todo{fare} \qed 
-\end{proof}
-
-\begin{corollary}
-\todo{passare a $\updownarrow_!$ e $\Updownarrow$}
-\end{corollary}
-
-\begin{corollary}[Invariance under shift]
+\begin{corollary}[Invariance under immediate shift]\label{cor:ius}
 	contenuto...

### 2023-10-20 fusione.tex
cose

@@
 \newcommand{\dder}[1]{\mathscr{#1}}
-\newcommand{\sder}[2]{S_{u,u'}(\mathscr{#1}, \mathscr{#2})}
+\newcommand{\sder}[2]{S_{i_1,i_2}(\mathscr{#1}, \mathscr{#2})}
 \newcommand{\der}[1]{\underline{\dder{#1}}}
@@
 
-\begin{example}
+\begin{example}\label{ex:difficile}
 	\todo{pensare ad un esempio in cui l'indipendenza non basta }
@@
 \end{enumerate}
-
-We will say that $\dder{D}$ and $\dder{D}'$ are \emph{switchable} if a filler between them exists.
-If such a filler is unique, we will say that $\dder{D}$ and $\dder{D}'$ are \emph{uniquely switchable}.
-We will use the notation $\dder{D}\updownarrow \dder{D'}$ to mean that $\dder{D}$ and $\dder{D}'$ are switchable, while $\dder{D}\updownarrow_!
-\dder{D'}$ will denote that they are uniquely so.
-\end{definition}
-
-\begin{remark}A remark on the uniqueness of filler is due.
-Let $\der{D}:\Mapsto H$ and $\der{D}':G\Mapsto T$ be two direct derivations such that $\der{D}\updownarrow_!
-\der{D}'$.
-The uniqueness of the filler between them must be interpreted only up to a choice of a pullback square
-	\[\xymatrix{P \ar[r]^{p} \ar[d]_{p'}& D\ar[d]^{g} \\ D' \ar[r]_{f'} & H}\]
-\end{remark}
+\end{definition}
 
@@
 
-Notice that if $\dder{D}$ and $\dder{D}'$ are switchable, then they are weakly sequentially independent: indeed, if a filler between them exists, then $(i_1, i_2)$ is an independence pair.
-
-\begin{definition}We will say that a left-linear DPO-rewriting system  $(\X, \R)$ is \emph{tame} if for every two direct derivations $\dder{D}:H\Mapsto H$, $\dder{D}':H\Mapsto T$ and for every independence pair $(i_1, i_2)$ between them, there exists a filler $(u,u')$ between them such that  the squares below are pushouts.\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
-\end{definition}
-
-\begin{remark}\label{rem:unic} Given an independence pair $(i_1, i_2)$ between $\dder{D}$ and $\dder{D}'$, there is at most one filler  such that $(u,u')$ such that 
+Notice that if there is a filler between  $\dder{D}$ and $\dder{D}'$ are switchable, then they are weakly sequentially independent: indeed, if a filler between them exists, then $(i_1, i_2)$ is an independence pair.
+On the other hand, \Cref{ex:difficile} shows that not every independence pair arises in this way.
+
+\begin{definition} Let  $\dder{D}:H\Mapsto H$, $\dder{D}':H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system  $(\X, \R)$.
+An independence pair $(i_1, i_2)$ between $\dder{D}$ and $\dder{D}'$ is \emph{good} if there exists a filler $(u,u')$ between them such that  the squares below are pushouts.\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
+
+We will say that $\dder{D}$ and $\dder{D}'$ are \emph{switchable} if a good independence pair between them exists.
+If such a pair is unique, we will say that $\dder{D}$ and $\dder{D}'$ are \emph{uniquely switchable}.
+We will use the notation $\dder{D}\updownarrow \dder{D'}$ to mean that $\dder{D}$ and $\dder{D}'$ are switchable, while $\dder{D}\updownarrow_!
+\dder{D'}$ will denote that they are uniquely so.
+
+If every independence pair is good we will say that $(\X, \R)$ is \emph{tame}.
+\end{definition}
+
+\begin{remark}\label{rem:unic} Given a good independence pair $(i_1, i_2)$ between $\dder{D}$ and $\dder{D}'$, there is a unique filler  such that $(u,u')$ such that 
 	\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
@@
 
-\begin{proposition}\label{prop:filip}
-Let $(\X, \R)$ be a tame left-linear DPO-rewriting system, then, given $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, the following are equivalent:
-\begin{enumerate}
-	\item $\dder{D}$ and $\dder{D}'$ are sequentially independent;
-	\item $\dder{D}\updownarrow_! \dder{D}'$.
-\end{enumerate}
-\end{proposition}
-\begin{proof} $(1\Rightarrow 2)$ Let $(i_1, i_2)$ be the unique independence pair between $\dder{D}$ and $\dder{D}$'.
-Take a pullback square \[\xymatrix{P \ar[r]^{p} \ar[d]_{p'}& D\ar[d]^{g} \\ D' \ar[r]_{f'} & H}\]
-by tameness we know that there exist a filler $(u,u')$ made by arrows $u:K\to P$ and $u':K'\to P$ fitting in the two pushout squares below. 
-	\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
-	In particular, 	$\der{D}\updownarrow \der{D'}$. On the other hand, if $(v,v')$ with $v:K\to P$ and $v':K'\to P$ is another filler, then there are other  two pushout squares
-	\[\xymatrix{K \ar[r]^{r} \ar[d]_{v}& R \ar[d]^{j_1} &K' \ar[r]^{l'} \ar[d]_{v'}& L'\ar[d]^{j_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
-	such that $f'\circ j_1=h$, $g\circ j_2=n'$. But then $(j_1, j_2)$ is an independence pair and so $j_1=i_1$ and $j_2=i_2$. \Cref{rem:unic} now yields the thesis.
-
-	\smallskip \noindent $(2\Rightarrow 1)$ Let $(u,u')$ be the filler between $\dder{D}$ and $\dder{D}$'.
-Then we get an independence pair $(i_1, i_2)$ pushing out $u$ along $r$ and $u'$ along $l'$, respectively.
-If $(j_1, j_2)$ is another independence pair
-\end{proof}
+\begin{remark}Clearly in a tame left-linear DPO-rewriting system two direct derivations are sequentially independent if and only if they are unquely switchable.
+\end{remark}
 
@@
 
-\begin{remark}\todo{riferminto a \Cref{app:fill}}
+\begin{remark} \cite{baldan2011adhesivity} identifies a large class of (quasi)adhesive categories with the property that every left linear DPO-rewriting system on them is tame.
+We reproduce these results in \Cref{app:fill}.
 \end{remark}
@@
 
-Consider the following diagram: the solid part exists by the definition of a filler, while the two new dotted arrows $v:Q\to J$ and $v':Q'\to J$ are obtained  as the pushout of $q:P\to Q$, which is in $\mathcal{M}$ by \Cref{rem:deco}, along $q':P\to Q'$.
+Let $(i_1, i_2)$ be a good independence pair and consider the following diagram: the solid part exists by the definition of a filler, while the two new dotted arrows $v:Q\to J$ and $v':Q'\to J$ are obtained  as the pushout of $q:P\to Q$, which is in $\mathcal{M}$ by \Cref{rem:deco}, along $q':P\to Q'$.
 	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@/_.8cm/[ddrr]_{j}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j'}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar[ul]_{s}\ar@{.>}[dr]_{v} &&Q'\ar[ur]^{t} \ar@{.>}[dl]^{v'}\\&&&J}\]
@@
 	Let $(\X,R)$ be a left-linear DPO-rewriting system and suppose that $\X$ is $\mathcal{M}$-adhesive.
-Given two switchable direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, with a filler $(u,u')$, we can define other two direct derivations $S_{u,u'}(\dder{D}'):G\Mapsto J$ and $S_{u,u'}(\dder{D}):J\Mapsto T$ as follows:
+Given a good independence pair $(i_1, i_2)$ between $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, if $(u,u')$ is the associate filler, we define other two direct derivations $S_{i_1,i_2}(\dder{D}'):G\Mapsto J$ and $S_{i_1,i_2}(\dder{D}):J\Mapsto T$ as follows:
 		\[\xymatrix{L' \ar[d]_{f\circ i_2}& \ar[l]_{l'}K'\ar[d]_{q\circ u'} \ar[r]^{r'} & R' \ar[d]_{v'\circ j'} & L \ar[d]_{v\circ j} & \ar[l]_{l}K \ar[d]^{q'\circ u}\ar[r]^{r}& R \ar[d]^{g'\circ i_1}\\
 		G &\ar[l]^{s} Q \ar[r]_{v}& J&J & \ar[l]^{v'}Q' \ar[r]_{t} & T}\]
-	The \emph{switching} $\sder{D}{D'}$ of $\dder{D}$ and $\dder{D'}$ is the derivation $S_{u,u'}(\dder{D}')\cdot S_{u,u'}(\dder{D})$.
-\end{definition}
-
-\begin{remark}\label{rem:indip}Notice that $(j', j)$ is an independence pair for $I_{\dder{D}'}$ and $I_{\dder{D}}$. This is witnessed by the following diagram, commutative by construction.
+	The \emph{switching} $\sder{D}{D'}$ of $\dder{D}$ and $\dder{D'}$ is the derivation $S_{i_1,i_2}(\dder{D}')\cdot S_{i_1,i_2}(\dder{D})$.
+\end{definition}
+
+\begin{remark}\label{rem:indip}Notice that $(j', j)$ is an independence pair for $S_{i_1,i_2}(\dder{D}')$ and $S_{i_1,i_2}(\dder{D})$.
+This is witnessed by the following diagram, commutative by construction.
 	\[\xymatrix@C=15pt{L' \ar[d]_{f\circ i_2}&& K' \ar[d]_{q\circ u'}\ar[ll]_{l'} \ar[r]^{r'} & R' \ar@/^.35cm/[drrr]_(.4){j'}|(.285)\hole \ar[dr]|(.28)\hole_{v'\circ j'} && L \ar@/_.35cm/[dlll]^(.4){j} \ar[dl]|(.28)\hole^{v\circ j}& K \ar[d]^{q'\circ u}\ar[l]_{l} \ar[rr]^{r} && R \ar[d]^{g'\circ i_1}\\G && \ar[ll]^{s} Q \ar[rr]_{v}&& J  && \ar[ll]^{v'} Q' \ar[rr]_{t}&& T}\]
@@
 	\[\xymatrix{K' \ar[r]^{r'} \ar[d]_{u'}& R' \ar[d]^{j'} &K \ar[r]^{l} \ar[d]_{u}& L\ar[d]^{j} \\P \ar[r]_{q}& Q& P \ar[r]_{q'} & Q'}\] 
-			By construction these squares are pushouts and we can conclude.			\qed 
-		\end{enumerate}
-\end{proof}
-
-The previous remark allow us to further switch the direct derivation $S_{u,u'}(\dder{D})$ and $S_{u,u'}(\dder{D}')$.
+		\end{enumerate}
+
+By \Cref{rem:indip} we know that $(j,j')$ is an independence pair. The results above now implies that $(j,j')$ is good.
+\end{proof}
+
+The previous remark allow us to further switch the direct derivation $S_{i_1,i_2}(\dder{D})$ and $S_{i_2,i_2}(\dder{D}')$.
 The following lemma guarantees us that, in this way, we get back a derivation which is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
@@
 \begin{lemma}\label{lem:rev}
-	Let $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system $(\X, \R)$ and let $(u,u')$ be a filler between them.
-Then $S_{u',u}(S_{u,u'}(\dder{D}, \dder{D'}))$ is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
+	Let $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system $(\X, \R)$ and let $(i_1,i_2)$ be a good independence pair between them.
+Then $S_{j',j}(S_{i_1,i_2}(\dder{D}, \dder{D'}))$ is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
 \end{lemma}
-\begin{proof} By \Cref{prop:fil}, $(u', u)$ is a filler between $S_{u,u'}(\dder{D}')$ and $S_{u,u'}(\dder{D})$, thus we have a diagram as the one below.
+\begin{proof}Let $(u,u')$ be the filler associated to $(i_1, i_2)$.
+By \Cref{prop:fil}, $(u', u)$ is a filler between $S_{i_1,i_2}(\dder{D}')$ and $S_{i_1,i_2}(\dder{D})$.
+Thus we have a diagram as the one below.
 		\[\xymatrix{&&R' \ar@/_1cm/[ddrr]_(.35){j'}|(.7)\hole \ar[dr]^{v'\circ j'}&& L \ar@/^1cm/[ddll]^(.35){j}  \ar[dl]_{v\circ j}\\&K'\ar[dr]^{q\circ u'}\ar[dl]_{l'} \ar@/_.8cm/[ddrr]^(.65){u'}\ar[ur]^{r'}&& J && K \ar@/^.8cm/[ddll]_(.65){u}\ar[dl]_{q'\circ u}\ar[lu]_{l} \ar[dr]^{r}\\L' \ar[dr]^{f\circ i_2} \ar@/_.8cm/[ddrr]_{c_2}&& Q \ar[dl]|(.42)\hole_(.64){s}\ar[ur]|(.48)\hole^(.7){v}&&Q' \ar[dr]|(.42)\hole_(.65){t} \ar[ul]|(.48)\hole_(.7){v'}&&R\ar@/^.8cm/[ddll]^{c_1}\ar[dl]_{g'\circ i_1}\\&G &&P\ar[dr]^{e} \ar[dl]_{e'}\ar[ur]^(.4){q'}\ar[ul]_(.4){q}&&T\\&&E' \ar[ul]_{a}\ar[dr]_{w'} &&E\ar[ur]^{b} \ar[dl]^{w}\\&&&F}\]
 
-	Now, to ease the notation, let $S_{u',u}(S_{u,u'}(\dder{D}, \dder{D'}))$ be $\dder{E}_0\cdot \dder{E}_1$, then $\dder{E}_0$ and $\dder{E}_1$ are the direct derivations given by the diagrams
+	Now, to ease the notation, let $S_{j',j}(S_{i_1,i_2}(\dder{D}, \dder{D'}))$ be $\dder{E}_0\cdot \dder{E}_1$, then $\dder{E}_0$ and $\dder{E}_1$ are the direct derivations given by the diagrams
 	\[\xymatrix{L \ar[d]_{s\circ j}& K\ar[l]_{l} \ar[r]^{r} \ar[d]_{e'\circ u} & R \ar[d]_{w\circ c_1} & L' \ar[d]^{w'\circ c_2}& K' \ar[d]^{e\circ u'} \ar[r]^{r'} \ar[l]_{l'}& R' \ar[d]^{t\circ j'}\\G & E' \ar[l]^{a}  \ar[r]_{w'}& F & F & E \ar[l]^{w} \ar[r]_{b} & R}\]
@@
 \begin{align*}
-	\psi^{-1}\circ w\circ c_1&=f'\circ \phi^{-1}\circ c_1\\&=f'\circ i_1&=h
+	\psi^{-1}\circ w\circ c_1&=f'\circ \phi^{-1}\circ c_1\\&=f'\circ i_1\\&=h
 \end{align*}
@@
 \begin{definition} Let $(\X, \R)$ be a left-linear DPO-rewriting system.
-Given two direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, we say that  $\dder{D}$ and $\dder{D}'$ are \emph{properly interchangeable} if $\dder{D}\updownarrow_!
-\dder{D'}$ and $S_{u,u'}(\dder{D}')\updownarrow_!S_{u,u'}(\dder{D})$, where $(u,u')$ is a filler between $\dder{D}$ and $\dder{D}'$.
+Given two direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, we say that  $\dder{D}$ and $\dder{D}'$ are \emph{properly switchable} if $\dder{D}\updownarrow_!
+\dder{D'}$ and $S_{i_1,i_2}(\dder{D}')\updownarrow_!S_{i_1,i_2}(\dder{D})$, where $(i_2,i_2)$ is a good independencepair betwwen $\dder{D}$ and $\dder{D}'$.
 In such a case, we will write $\dder{D}\Updownarrow\dder{D}'$.
@@
 \item $\dder{D}_j \Updownarrow \dder{D}_{j+1}$;		
-\item $\dder{D}'_j\cdot \dder{D}'_{j+1} = S_{u,u'}(\dder{D}, \dder{D}')$.
+\item $\dder{D}'_j\cdot \dder{D}'_{j+1} = S_{i_1,i_2}(\dder{D}, \dder{D}')$.
 	\end{enumerate}
@@
 
-\begin{lemma}\label{lem:iig1}Let $(\X,\R)$ be a tame left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
+\begin{lemma}\label{lem:iig1}Let $(\X,\R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
 Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$.
-If $(v,v')$ is a filler between $\dder{D}_0$ and $\dder{D}_1$, $(u,u')$ one between $\dder{D}_1$ and $\dder{D}_2$ and $\dder{D}_0\updownarrow S_{u,u'}(\dder{D}_2)$ with filler $(w,w')$, then there exists a filler between $S_{w,w'}(\dder{D}_0)$ and $S_{u,u'}(\dder{D}_1)$.
+If $(i_0,i_1)$ is a good independence pair between $\dder{D}_0$ and $\dder{D}_1$, $(a_1,a_2)$ one between $\dder{D}_1$ and $\dder{D}_2$ and $\dder{D}_0\updownarrow S_{a_1,a_2}(\dder{D}_2)$ with good independence pair $(e_0,e_1)$, then $S_{e_0,e_1}(\dder{D}_0)$ and $S_{a_1,a_2}(\dder{D}_1)$ are weakly sequentially independent.
 \end{lemma}
-\begin{proof}
-We can use \Cref{def:filler,def:switch} to get some diagrams.  First of all the filler $(v,v')$ between $\dder{D}_0$ and $\dder{D}_1$ yields
+\begin{proof} We can use \Cref{def:filler,def:switch} to get some diagrams.  First of all, let $(v,v')$ be the filler between $\dder{D}_0$ and $\dder{D}_1$ associated to $(i_1, i_2)$, then we have
 			\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
 
-	Secondly, the filler $(u,u')$ between $\dder{D}_1$ and $\dder{D}_2$ gives us another diagram:
+	Secondly, the filler $(u,u')$ induced by $(a_1, a_2)$ between $\dder{D}_1$ and $\dder{D}_2$ yields:
 \[
@@
 
-	Finally, the filler $(w,w')$ between $\dder{D}_0$ and $S_{u,u'}(\dder{D}_2)$ provides us with:
+	Finally, the filler $(w,w')$  between $\dder{D}_0$ and $S_{u,u'}(\dder{D}_2)$ given by $(e_0, e_1)$ provides us with:
 			\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){e_0}|(.7)\hole \ar[dr]^{h_0}&& L_2\ar@/^1cm/[ddll]^(.35){e_1}  \ar[dl]_{f_1\circ a_2}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){w}\ar[ur]^{r_0}&& G_1 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){w'}\ar[dl]_{d_1\circ u'\hspace{-5pt}}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_0 \ar@/_.8cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2 \ar[dr]|(.4)\hole^(.65){y_1} \ar[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.8cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){x_2\circ b_2}\\&G_0 &&P_3\ar[dr]_{n_1} \ar[dl]^{n_0}\ar[ur]^(.4){u_1}\ar[ul]_(.4){u_0}&&G'_2\\L_2 \ar@/^.8cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ e_1}|(.61)\hole&&Q_4 \ar[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0} &&Q_5\ar[ur]|(.4)\hole^(.65){z'_1} \ar[dl]|(.5)\hole_(.65){z_1} && R_0  \ar[ul]^(.35){y_1\circ e_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){e_0}\\&K_2 \ar[ur]_{n_0\circ w'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){w'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{n_1\circ w} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){w}\\&& R_2 \ar[ur]_{\hspace{-4pt}z_1\circ o_1}\ar@/^1cm/[uurr]^(.25){o_1}&& L_0 \ar[ul]^{z'_0\circ o_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){o_0} |(.69)\hole }\]
 
-		By tameness of $(\X,\R)$, to construct a filler between $S_{w,w'}(\dder{D}_0)$ and $S_{u,u'}(\dder{D}_1)$, it is enough to construct the two dotted arrows in the diagram below.
+	We have to construct the two dotted arrows in the diagram below.
 			\[\xymatrix@C=15pt{L_.
@@
 	\begin{enumerate}
-		\item suppose that $(u,u')$ and $(w,w')$ are fillers witnessing  $\dder{D}_1\updownarrow_!
+		\item suppose that $(a_1,a_2)$ and $(e_0,e_1)$ are independence pairs witnessing  $\dder{D}_1\updownarrow_!
 \dder{D}_2$ and $\dder{D}_0\updownarrow_!
-S_{u,u'}(\dder{D}_2)$ respectively, if $\dder{D}_0\updownarrow_!\dder{D}_1$, then $S_{w,w'}(\dder{D}_0)\updownarrow_!S_{u,u'}(\dder{D}_1)$;
+S_{a_1,a_2}(\dder{D}_2)$ respectively, if $\dder{D}_0\updownarrow_!\dder{D}_1$, then $S_{e_0,e_1}(\dder{D}_0)\updownarrow_!S_{a_2,a_2}(\dder{D}_1)$;
 		\item 
@@
 	\begin{enumerate}
-		\item Let $(v,v')$ be the unique filler between $\dder{D}_0$ and $\dder{D}_1$.  By \Cref{rem:filip}
+		\item Let $(i_1,i_2)$ be the unique independence pair between $\dder{D}_0$ and $\dder{D}_1$.
+By tameness and \Cref{lem:iig1} we know that $S_{e_0,e_1}(\dder{D}_0)\updownarrow S_{a_1,a_2}(\dder{D}_1)$.
+Let $(\alpha_1, \alpha_2)$ be the independence pair constructed in the proof of \Cref{lem:iig1}.
+Take another independence pair $(\beta_1, \beta_2)$,  by \Cref{rem:weak} we already know that $\beta_1=\alpha_1$.
+Now, using the same notation as the proof of \Cref{lem:iig1}, we have
+		\[x_2\circ \beta_1 = y_1\circ e_0 \qquad z'_1\circ \beta_2 = y_1\circ b_1\]
+
+		In particular, this implies that there exist $\beta'_1:R_0\to P_2$, $\beta'_2:L_1\to P_3$ as in the diagrams below.
+		\[\xymatrix{R_0 &&& L_1\\ & P_2 & Q_3 && P } \]
+
 		\item \qed 

### 2023-10-25 fusione.tex
unicità

@@
 		\item given a non-empty derivation $\der{D}=\{\dder{D}\}_{i=0}^n$ between $G$ and $H$, for every $j\in n+1$ different from $0$ the following diagram is a pushout
-		\[\xymatrix@C=30pt{D_{j} \ar[r]^{g_j}\ar[d]_{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar[dd]^{p_2} \\ G_j \ar[d]_{\iota'_{G_j}}\\ \lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
+		\[\xymatrix@C=30pt{D_{j} \ar[r]^{g_j}\ar[d]_{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} \ar@/^.3cm/[ddl]^{\iota'_{G_j}} & \lpro \der{\hat{D}}\rpro \ar[dd]^{p_2} \\ G_j \ar[d]_{\iota'_{G_j}}\\ \lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
 		where $\der{\hat{D}}=\{\dder{D}_i\}_{i=j+1}^n$, $\der{D}'=\{\dder{D}_i\}_{i=0}^j$ and $p_1:\lpro\der{D}' \rpro\to \tpro{D}$ and $p_2:\lpro \der{\hat{D}}\rpro \to \tpro{D}$ are the arrows induced by the cocones, $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}')})$ and $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}')})$, respectively.
@@
 Indeed, $\der{D}=\der{D}_1 \cdot \der{D}_2$ where $\der{D}_1=\{\dder{D}_0\}$ and $\der{D}_2=\{\dder{D}_i\}_{i=1}^n$.
-Then the two halves of the rectangle below are pushouts.
+By point $1$ and $3$ of \Cref{lem:colim}, the two halves of the rectangle below are pushouts.
 By \Cref{lem:po1} the whole diagram is then a pushout too.
-	\[\xymatrix@C=30pt{D_{0} \ar[r]^{g_0}\ar[d]_{f_0}& G_{1} \ar[r]^-{\iota_{2,G_{1}}} & \lpro \der{D}_2\rpro \ar[dd]^{p_2} \\ G \ar[d]_{\iota_{1,G}}\\ \lpro \der{D}_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
+	\[\xymatrix@C=30pt{D_{0} \ar[r]^{g_0}\ar[d]_{f_0}& G_{1} \ar[d]^{\iota_{1, G_1}} \ar[r]^-{\iota_{2,G_{1}}} & \lpro \der{D}_2\rpro \ar[d]^{p_2} \\ G \ar[r]_{\iota_{1,G}}& \lpro \der{D}_1 \rpro \ar[r]_{p_1}  &\tpro{D} }\]
+Notice that this entails that the square below is also a pushout. 
+\[\xymatrix@C=25pt{D_0\ar[r]^-{\iota_{2, D_0}}  \ar[d]_{\iota_{1, D_0}}&  \lpro \der{D}_1 \rpro\ar[d]^{p_2}\\ \lpro \der{D}_1 \rpro \ar[r]_{p_1}  &\tpro{D} }\]
 \end{remark}
@@
 		\item $j=0$. Consider $\der{D}_1:=\{\dder{D}_0\}$ and $\der{D}_2:=\{\dder{D}_i\}_{i=1}^n$.  Consider the diagram below in which, by \Cref{rem:zero}, the rectangle on the bottom right is a pushout.
-		\[\xymatrix@C= 40pt{T  \ar@/_.3cm/[dddr]_{a}\ar@{.>}[dr]^{t}\ar[rr]^{b}&& G_k \ar@/^.3cm/[dr]^{\iota_{2, G_k}} \ar@/_.25cm/[dddr]|(.31)\hole_{\iota_{G_k}}\\&D_{0} \ar[r]^{g_0}\ar[d]_{f_0}& G_{1} \ar[r]^-{\iota_{2,G_{1}}} & \lpro \der{D}_2\rpro \ar[dd]^{p_2} \\ &G \ar[drr]^{\iota_G} \ar[d]^{\iota_{1,G}}\\ &\lpro \der{D}_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
+		\[\xymatrix@C= 40pt{T  \ar@/_.6cm/[ddd]_{a}\ar@{.>}[d]^{t}\ar[rr]^{b}&& G_k \ar[d]_{\iota_{2, G_k}} \ar@/^.6cm/[ddd]^{\iota_{G_k}}\\D_{0} \ar[r]^{g_0}\ar[d]^{f_0}& G_{1} \ar[r]^-{\iota_{2,G_{1}}} & \lpro \der{D}_2\rpro \ar[dd]_{p_2} \\ G \ar[drr]^{\iota_G} \ar[d]^{\iota_{1,G}}\\ \lpro \der{D}_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
 		Since $f_0$ and $\iota_{1,G}$ are in $\mathcal{M}$ the same rectangle is an $\mathcal{M}$-pushout and so, by \Cref{prop:pbpoad} is a pullback and the thesis follows.
 		\item   $j\neq 0$. We proceed as in the point above. Using point $4$ of \Cref{lem:colim} we know that the bottom right rectangle in the diagram below is a pushout. 
-			\[\xymatrix@C=30pt{T  \ar@/_.3cm/[dddr]_{a}\ar@{.>}[dr]^{t}\ar[rr]^{b}&& G_k \ar@/^.3cm/[dr]^{\iota_{2, G_k}} \ar@/_.25cm/[dddr]|(.31)\hole_{\iota_{G_k}}\\&D_{j} \ar[r]^{g_j}\ar[d]_{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar[dd]^{p_2} \\ &G_j \ar[d]^{\iota'_{G_j}}\\ &\lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
+			\[\xymatrix@C=30pt{T  \ar@/_.6cm/[ddd]_{a}\ar@{.>}[d]^{t}\ar[rr]^{b}&& G_k \ar[d]_{\iota_{2, G_k}} \ar@/^.6cm/[ddd]^{\iota_{G_k}}\\D_{j} \ar[r]^{g_j}\ar[d]^{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar[dd]_{p_2} \\ G_j \ar[d]^{\iota'_{G_j}} \ar[drr]^{\iota_{G_j}}\\ \lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
 		Point $2$ of \Cref{lem:colim} entails that $\iota'_{G_j}$ is in $\mathcal{M}$, and so is $f_j$ as it is the pushout of $l_j$.
@@
 \begin{remark} \cite{baldan2011adhesivity} identifies a large class of (quasi)adhesive categories with the property that every left linear DPO-rewriting system on them is tame.
-We reproduce these results in \Cref{app:fill}.
+We adapt these results to our context in \Cref{app:fill}.
 \end{remark}
@@
 
+\begin{remark}\label{rem:pbsalva}
+Let $(i_1,i_2)$ be a good independence pair between the derivation $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$.
+Let also $\der{\hat{D}}$ be the derivation consisting only in $S_{i_1,i_2}(\dder{D})$.
+We have a diagram
+\[\xymatrix{P\ar[r]^{q}  \ar[d]_{p}& Q \ar[r]^{v} \ar[d]^{s}& J \ar[r]^{\hat{\iota}_J}& \lpro \der{\hat{D}} \rpro \ar[d]^{\hat{p}}  \\D	\ar[r]_{f} &G \ar[rr]_{\iota_{G}}&& \lpro S_{i_1, i_2}(\dder{D}, \dder{D}')\rpro}\]
+By \Cref{rem:zero,rem:deco}, its two halves are pullbacks and so, by \Cref{lem:pb1} the whole rectangle is a pullback too. Moreover, notice that
+\begin{align*}
+	\hat{\iota}_J\circ v \circ q &= \hat{\iota}_J\circ v'\circ q'\\&= \hat{\iota}_{Q'}\circ q'
+\end{align*}
+which entails that the rectangle below is a pullback too.
+\[\xymatrix{P\ar[r]^{q'}  \ar[d]_{p}& Q' \ar[r]^{\hat{\iota}_{Q'}}& \lpro \der{\hat{D}} \rpro \ar[d]^{\hat{p}}  \\D	\ar[r]_{f} &G \ar[r]_-{\iota_{G}}& \lpro S_{i_1, i_2}(\dder{D}, \dder{D}')\rpro}\]
+\end{remark}
+
 \begin{remark}\label{rem:indip}Notice that $(j', j)$ is an independence pair for $S_{i_1,i_2}(\dder{D}')$ and $S_{i_1,i_2}(\dder{D})$.
@@
 The following lemma guarantees us that, in this way, we get back a derivation which is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
+
+\todo{introdurre decorazione}
 
@@
 	\[\xymatrix{K \ar@{.>}[r]_{\zeta}\ar@/^.4cm/[rr]^{l}  \ar@/_.5cm/[dr]_{(\phi')^{-1} \circ e' \circ u}& K \ar[r]_{l} \ar[d]_{n} & L \ar[d]^{n} \\ & D \ar[r]_{f} & G}\]
-	The commutativity of the upper triangle entails
-	\[l\circ \zeta=l\]
-	but $l$, being an element of $\mathcal{M}$ is mono, so that $\zeta=\id{K}$. From this, we can conclude that
+	The commutativity of the upper triangle entails $l\circ \zeta=l$. Since $l$ is an element of $\mathcal{M}$  we can deduce that. $\zeta=\id{K}$. From this, we conclude that
 	\[e'\circ u = \phi' \circ k\]
 
-	As a next step, notice the existence of $\phi$ and $\phi'$, together with \cref{rem:deco}, entails  the existence of a third isomorphism $\psi:H\to F$ fitting in the diagram below.
+	As a next step, notice the existence of $\phi$ and $\phi'$, together with \Cref{rem:deco}, entails  the existence of a third isomorphism $\psi:H\to F$ fitting in the diagram below.
 	\[\xymatrix{P  \ar[d]^{p'}\ar@/_.4cm/[dd]_{e}\ar@/^.4cm/[rr]^{e'} \ar[r]_{p} & D \ar[d]^{g} \ar[r]_{\phi'} & E'\ar[d]^{w'}\\D' \ar[d]^{\phi} \ar[r]_{f'} & H\ar@{.>}[r]^{\psi} & F \\E \ar@/_.4cm/[urr]_{w}}\]
@@
 
-\begin{lemma} Let $(\X, \R)$ be a left-linear DPO-rewriting system $(\X, \R)$. Then the following hold true
+\begin{lemma}\label{lem:consperm} Let $(\X, \R)$ be a left-linear DPO-rewriting system $(\X, \R)$. Then the following hold true
 	\begin{enumerate}
@@
 
-\begin{corollary} Given a tame  left-linear DPO-rewriting system  $(\X,\R)$ with $\X$ an $\mathcal{M}$-adhesive category and a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$, the following are true: 
+\begin{corollary} Given a tame  left-linear DPO-rewriting system  $(\X,\R)$ with $\X$ an $\mathcal{M}$-adhesive category and a decorated derivation $(\der{D}, \alpha, \omega)$ with $\der{D}=\{\dder{D}_i\}_{i=0}^2$.
+Then the following are true:
 	\begin{enumerate}
@@
 Take another independence pair $(\beta_1, \beta_2)$,  by \Cref{rem:weak} we already know that $\beta_1=\alpha_1$.
-Now, using the same notation as the proof of \Cref{lem:iig1}, we have
-		\[x_2\circ \beta_1 = y_1\circ e_0 \qquad z'_1\circ \beta_2 = y_1\circ b_1\]
-
-		In particular, this implies that there exist $\beta'_1:R_0\to P_2$, $\beta'_2:L_1\to P_3$ as in the diagrams below.
-		\[\xymatrix{R_0 &&& L_1\\ & P_2 & Q_3 && P } \]
+Let also $\der{E}$ be the derivation $S_{e_0, e_1}(S_{a_1, a_2}(\der{D}_2))\cdot S_{e_0, e_1}(\dder{D}_0) \cdot S_{a_1, a_2}(\der{D}_1)$.
+Let $\sigma:[0,2]\to [0,2]$ be the cycle $(0,1,2)$.
+By \Cref{lem:consperm} we know that $\sigma$ is a consistente permutation between $(\der{D}, \alpha, \omega)$ and $(\der{E}, \alpha, \omega)$.
+In particular, we have
+		\begin{align*}
+			\iota_{\der{E}, G_0}\circ f_0\circ  i_1 &=\xi_\sigma \circ 	\iota_{\der{D}, G_0}\circ f_0\circ  i_1 \\&= \xi_\sigma \circ 	\iota_{\der{D}, D_0}\circ  i_1\\ &= \xi_\sigma \circ \iota_{\der{D}, G_1} \circ g_0\circ  i_1 \\&=\xi_\sigma \circ \iota_{\der{D}, G_1}\circ m_1\\ &=  \iota_{\der{E}, G'_2}\circ y_1\circ b_1\\&= \iota_{\der{E}, G'_2}\circ z'_1\circ \beta_2\\&= \iota_{\der{E}, Q_5}\circ \beta_2
+		\end{align*}
+		Using	\Cref{rem:pbsalva} we can deduce the existence of a unique arrow $\beta'_2:L_1\to P_3$ fitting in the diagram below
+		\[\xymatrix{L_1 \\& P_3 & Q_5\\
+		&D_0& \tpro{E}}\]
+		If we further compute, we get
+		\begin{align*}
+			y_1\circ u_1\circ \beta'_2\\&=z'_1\circ n_1\circ \beta'_2=\\&= z'_1\circ \beta_2 \\&=y_1\circ b_1
+		\end{align*}
+		Thus $(u_1\circ \beta'_2, b_2)$ is an independence pair between $S_{a_1, a_2}(\der{D}_2)$ and $S_{a_1, a_2}(\der{D}_1)$ therefore, by hypothesis $u_1\circ \beta'_2=b_1$.
+But this implies that $\beta'_2$ and $\alpha'_2$ are equal, giving us the thesis.
+
+\todo{ripulire le ipotesi: serve scambiabilità propria tra 1 e 2}
 

### 2023-10-26 fusione.tex
cose

@@
 \end{corollary}
+
+\todo{ripulire le ipotesi: serve scambiabilità propria tra 1 e 2}
+\todo{sistemare il fatto che qua utilizziamo derivazioni di 3 passi}
 \begin{proof}
@@
 Let $\sigma:[0,2]\to [0,2]$ be the cycle $(0,1,2)$.
-By \Cref{lem:consperm} we know that $\sigma$ is a consistente permutation between $(\der{D}, \alpha, \omega)$ and $(\der{E}, \alpha, \omega)$.
+By \Cref{lem:consperm} we know that $\sigma$ is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{E}, \alpha, \omega)$.
 In particular, we have
@@
 		Using	\Cref{rem:pbsalva} we can deduce the existence of a unique arrow $\beta'_2:L_1\to P_3$ fitting in the diagram below
-		\[\xymatrix{L_1 \\& P_3 & Q_5\\
-		&D_0& \tpro{E}}\]
+		\[\xymatrix@C=30pt{L_1  \ar@/^.3cm/[drr]^{\beta_2} \ar@/_.3cm/[ddr]_{i_1}\ar@{.>}[dr]^{\beta'_2}\\& P_3 \ar[r]^{n_1}  \ar[d]_{u_0}& Q_5 \ar[d]^{\iota_{\dder{E}, Q_5}}\\
+		&D_0 \ar[r]_{\iota_{\dder{E}, G_0}}& \tpro{E}}\]
 		If we further compute, we get
 		\begin{align*}
-			y_1\circ u_1\circ \beta'_2\\&=z'_1\circ n_1\circ \beta'_2=\\&= z'_1\circ \beta_2 \\&=y_1\circ b_1
+			y_1\circ u_1\circ \beta'_2&=z'_1\circ n_1\circ \beta'_2=\\&= z'_1\circ \beta_2 \\&=y_1\circ b_1
 		\end{align*}
@@
 \todo{ripulire le ipotesi: serve scambiabilità propria tra 1 e 2}
+\todo{sistemare il fatto che qua utilizziamo derivazioni di 3 passi}
 

### 2023-10-27 fusione.tex
pulizia

@@
 % --- LNCS ---'
-\documentclass{llncs}
+\documentclass{article}
 
@@
 \usepackage{amsmath}
-%2 righe tolte da Fabio
+
 \usepackage{amssymb}
-%\usepackage{amsthm}
+\usepackage{amsthm}
 \usepackage{enumerate}
@@
 
-\spnewtheorem*{notation}{Notation}{\bfseries}{\rmfamily}
+%\spnewtheorem*{notation}{Notation}{\bfseries}{\rmfamily}
 
@@
 
+%%%%% Ambienti matematici  %%%%%%
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem*{notation}{Notation}
+\newtheorem{remark}[theorem]{Remark}
+\newtheorem{example}[theorem]{Example}
+
 \title{Switch equivalence and weak prime domains for fusions}
@@
 
+\tableofcontents
 \section{Introduction}
@@
 Thus the Van Kampen property yields that the front and the right faces are pullbacks and the thesis follows.
-\qed
+\qedhere
 \end{proof}
@@
 		\[\xymatrix@C=40pt{A' \ar@/^.3cm/[ddr]^(.8){a} \ar[d]_{m'} \ar[r]^{f'} & B' \ar[d]^{n'} \ar@/^.3cm/[ddr]^{b} \\  C' \ar@/_.3cm/[dr]_{h} \ar[r]_{g'}|(.7)\hole & D' \ar@{.>}[dr]^{k}\\ &A \ar[r]_f& B }\]
-	The thesis now follows at once. \qed 
+	The thesis now follows at once. \qedhere 
 \end{proof}
@@
 	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y  \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
-	By hypothesis the face is a stable pushout and so its top one is a pushout. \Cref{lem:po1} now entails that the right half of the rectangle with which we have started is a pushout too. \qed 
+	By hypothesis the face is a stable pushout and so its top one is a pushout. \Cref{lem:po1} now entails that the right half of the rectangle with which we have started is a pushout too. \qedhere 
 \end{proof}
@@
 \[\xymatrix{X\ar[r]^m \ar[d]_m& Y\ar[d]^{f}\\Y \ar[r]_g & Z}\]
-By \Cref{prop:pbpoad} this square is a pullback, proving that $m$ is the equalizer of the arrows $f,g\colon Y\rightrightarrows Z$. \qed 
+By \Cref{prop:pbpoad} this square is a pullback, proving that $m$ is the equalizer of the arrows $f,g\colon Y\rightrightarrows Z$. \qedhere 
 \end{proof}
@@
 	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y \ar[rrr]|(.67)\hole^{b} \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
-	Its vertical faces are all pullbacks, those the top one is a pushout and we can conclude. \qed 
+	Its vertical faces are all pullbacks, those the top one is a pushout and we can conclude. \qedhere 
 \end{enumerate}
@@
 	\end{align*}
-	The claim now follows since $k_2$ is a monomoprhism. \qed 
+	The claim now follows since $k_2$ is a monomoprhism. \qedhere 
 \end{proof}
@@
 \begin{remark}
-	If $\X$ is not a small category , then $\gpo$ has a proper class of vertices.
-\end{remark}
-
-	We can spell out more explicitly what  a derivation $\dder{D}$ between $G$ and $H$ is.  $\dder{D}$ is a, possibly empty, sequence $\{\dder{D}_i\}_{i=0}^n$ of direct derivations such that:
+We can spell out more explicitly what  a derivation $\dder{D}$ betwee nis.
+An \emph{empty derivation} starting and ending in $G$ is just $G$ itself.
+A \emph{non-empty derivation} $\dder{D}$ is a sequence $\{\dder{D}_i\}_{i=0}^n$ of direct derivations such that:
 \begin{enumerate}
@@
 
-	Moreover,  if $\mathcal{D}_i$ is an application of the rule $\rho_i\in R$, then we can define an associated sequence of rules as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.
+Moreover,  if every $\dder{D}_i$ applies the rule $\rho_i\in R$, then we can define an associated sequence of rules as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.
+\end{remark}
 
@@
 \begin{definition}
-	The \emph{DPO-derivation category} $\dpo$ of a left-linear DPO-rewriting system $(\X, \R)$ is the free category on $\gpo$.
+	The \emph{DPO-derivation category} $\dpo$ of a left-linear DPO-rewriting system $(\X, \R)$ is the category in which arrows between $G$ and $H$ are given by, possibly empty, derivations.
+Composition is concatenation of paths in $\gpo$ and identities are given by empty derivations.
 \end{definition} 	
 \begin{remark}
-Derivations, being paths in a graph, can be concatenate: given $\der{D}=\{\dder{D}\}_{i=0}^n$ between $G$ and $H$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^m$, their \emph{concatenation} $\der{D}\cdot\der{D}'$ is the derivation $\{\dder{E}_i\}_{i=0}^{m+n+1}$ in which
+	More explicitly, given $\der{D}=\{\dder{D}\}_{i=0}^n$ between $G$ and $H$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^m$, their concatenation $\der{D}\cdot\der{D}'$ is the derivation $\{\dder{E}_i\}_{i=0}^{m+n+1}$ in which
 	\[\dder{E}_i:=\begin{cases}
@@
 	\end{cases}\]	
-
-It is immediate to see that the concatenation of two non-empty derivations coincides with their composition in $\dpo$. 
 \end{remark}
@@
 Let $\ske$ be the full subcategory given by these objects.
-By definition $\ske$ is skeletal and the inclusion functor is full, faithful and essentially surjective.\qed
+By definition $\ske$ is skeletal and the inclusion functor is full, faithful and essentially surjective.\qedhere
 \end{proof}
@@
 \end{definition}
+
+\begin{remark}A decorated derivation $(\der{D}, \alpha, \omega)$ with $\der{D}$ empty is just a span
+	\[\xymatrix{G & \pi(G) \ar[r]^{\omega} \ar[l]_{\alpha} & G}\]
+	in which both $\omega$ and $\alpha$ are isomorphisms.
+\end{remark}
 
@@
 	\end{split}\]
-Therefore the thesis now follows.	\qed 
+Therefore the thesis now follows.	\qedhere 
 \end{proof}
@@
 	\end{align*}
-	allowing us to deduce that $c'=c$.	\qed 	
+	allowing us to deduce that $c'=c$. \qedhere 
 	\end{enumerate}
@@
 Thus the rectangle we are considering is an $\mathcal{M}$-pushout and the thesis follows again from \Cref{prop:pbpoad}.
-\qed
+\qedhere
 	\end{itemize}
@@
 \begin{proof}
-	contenuto...\qed 
+	contenuto...\qedhere 
 \end{proof}
@@
 
-\subsection{Sequentially independendent and switchable derivations}
+\subsection{Sequentially independent and switchable derivations}
 \todo{A VERY NICE INTRO}
@@
 \[\xymatrix{K \ar@/^.4cm/[rr]^{u}\ar[d]_{r}\ar[r]_{u} &P\ar[d]^{p'} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{l'}\ar[r]_{u'} &P\ar[d]^{p} \ar[r]_{p'} & D' \ar[d]^{f'}\\  R \ar@/_.4cm/[rr]_{h} \ar[r]^{i_1}&D' \ar[r]^{f'} & H&L' \ar@/_.4cm/[rr]_{n'} \ar[r]^{i_2}&D \ar[r]^{g} & H}\]
-	By hypothesis $r$ and $l'$ are in $\mathcal{M}$, thus $f'$ and $g$ belong to it too. The first point of \Cref{lem:popb}  yields the thesis. \qed 
+	By hypothesis $r$ and $l'$ are in $\mathcal{M}$, thus $f'$ and $g$ belong to it too. The first point of \Cref{lem:popb}  yields the thesis. \qedhere 
 \end{enumerate}
@@
 
-Putting together the two diagrams above we get the thesis. \qed 
+Putting together the two diagrams above we get the thesis. \qedhere 
 \end{proof}
@@
 		\item 
-		\item \qed 
+		\item \qedhere 
 	\end{enumerate}
@@
 
-		\item \qed 
+		\item \qedhere 
 	\end{enumerate}
@@
 \begin{proof}
- \todo{fare} \qed 
+ \todo{fare} \qedhere 
 \end{proof}
@@
 \end{theorem}
-\begin{proof}\qed 
+\begin{proof}\qedhere 
 \end{proof}
@@
 \begin{proof}
-	contenuto... \qed 
+	contenuto... \qedhere 
 \end{proof}
@@
 \begin{proof}
-	\qed 
+	\qedhere 
 \end{proof}

### 2023-10-30 fusione.tex
pulizia

@@
 \newcommand{\od}{\overline d}
-\newcommand{\nil}{{\tt 0}}
 \newcommand{\rec}{\emph{rec}}
@@
 \newcommand{\tproi}[2]{\lpro \der{#1}_{#2}\rpro}
-\newcommand{\lgt}[0]{\mathsf{length}}
+\newcommand{\lgh}[0]{\mathsf{length}}
 
@@
 
-We will call the number $n+1$ the \emph{length} of the derivation, denoted by $\lgt(\der{D})$. We will also say that an empty derivation has length $0$.
+We will call the number $n+1$ the \emph{length} of the derivation, denoted by $\lgh(\der{D})$. We will also say that an empty derivation has length $0$.
 
@@
 
-Given two decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ with  $\der{D}=\{\dder{D}_i\}_{i=0}^n$, $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ such that $\dder{D}_i:G_i\Mapsto G_{i+1}$ and $\dder{D}'_i:G'_i\Mapsto G'_{i+1}$, we will say that $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ are \emph{abstraction equivalent}, if  $r(\der{D})=r(\der{D'})$  and there exists a family $\{\phi^i\}_{i=0}^n$ of abstraction equivalences $\phi^i$ between $\dder{D}_i$ and  $\dder{D}'_i$ such that, for every index $i$, $\phi^i_3=\phi^{i+1}_1$ and  the following diagrams commute.
+We will say that  two decorated derivations$(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ are \emph{abstraction equivalent}, if $\lgh(\der{D})=\lgh(\der{D}')$, $r(\der{D})=r(\der{D'})$, and there exists a family $\{\phi^i\}_{i=0}^{\lgh(\der{D})}$ of abstraction equivalences $\phi^i$ between $\dder{D}_i$ and  $\dder{D}'_i$ such that, for $i\in [0, \lgh(\der{D})]$, $\phi^i_3=\phi^{i+1}_1$ and  the following diagrams commute.
 \[\xymatrix{&\pi(G_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G_{n+1}) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G_0 \ar[rr]_{\phi^0_1} && G'_0 &G_{n+1} \ar[rr]_{\phi^n_3} && G'_{n+1} } \]
 
-	In such situation we will say that $ (\der{D}, \alpha, \omega)$ and  $(\der{D}', \alpha', \omega')$ are \emph{abstraction equivalent}.
-We will use $\equiv^a$ to denote the resulting equivalence relation, while  $[\der{D}, \alpha, \omega]_a$ will denote the equivalence class of  $(\der{D}, \alpha, \omega)$, called an \emph{abstract decorated derivation}.
+We will use $\equiv^a$ to denote the resulting equivalence relation.
+An \emph{abstract decorated derivation}.
+$[\der{D}, \alpha, \omega]_a$ is just the equivalence class of  $(\der{D}, \alpha, \omega)$.
 \end{definition}

### 2023-11-24 fusione.tex
derivazioni e categoria

@@
- %(query-replace-regexp "\\\\sqsubseteq^{sh}_{\\([^}]*\\)}" "\\\\shiftpre[\\1]")
-% --- LNCS ---'
-\documentclass{article}
-
+\documentclass[a4paper]{article}
 \usepackage{hyperref}
 \usepackage[textsize=tiny]{todonotes}
-\usepackage{etex}
+%\usepackage{etex}
 
@@
 }
-
+\usepackage{scalerel}
+\newcommand{\smallmin}{\scaleobj{0.6}{-}}
+\newcommand{\Deltamin}{\Delta^{\hspace{-2pt}\begin{matrix}
+			\smallmin\\
+		\end{matrix}} \hspace{-1pt}}
 \newcommand{\Rrel}[1]   {\stackrel{{#1}}{\Longrightarrow}}
@@
 \newcommand{\tproi}[2]{\lpro \der{#1}_{#2}\rpro}
-\newcommand{\lgh}[0]{\mathsf{length}}
+\newcommand{\lgh}[0]{\mathsf{lg}}
 
@@
 	$(\Rightarrow)$ By hypothesis there exists $k:D'\to B$ such that $n\circ k = d$.
-By \Cref{prop:pbpo}, the bottom face of the cube is a pullback, thus there exists a unique $h:C'\to A$ as in the diagram below.
-	In particular, this implies the thesis.
-		\[\xymatrix@C=40pt{C'  \ar@{.>}[dr]^{h}\ar[r]^{g'} \ar@/_.3cm/[ddr]_{c}& D' \ar@/_.3cm/[ddr]|(.45)\hole_(.7){d}\ar@/^.3cm/[dr]^{k}\\ & A \ar[d]_{m} \ar[r]^{f} & B \ar[d]^{n} \\ & C \ar[r]_g & D}\]
+By \Cref{prop:pbpo}, the bottom face of the cube is a pullback.
+Thus there exists a unique $h:C'\to A$ as in the diagram below, implying the thesis.
+		\[\xymatrix@C=40pt{C'  \ar@{.>}[d]^{h}\ar[r]^{g'} \ar@/_.5cm/[dd]_{c}& D' \ar@/^.5cm/[dd]^{d}\ar[d]_{k}\\ A \ar[d]^{m} \ar[r]^{f} & B \ar[d]_{n} \\  C \ar[r]_g & D}\]
 
@@
 	$(\Leftarrow)$ Let $h:C\to A$ be such that $c=m\circ h$. By the Van Kampen property the top face of the given cube is a pushout. Thus the dotted $k:D'\to B$ in the following diagram exists.
-		\[\xymatrix@C=40pt{A' \ar@/^.3cm/[ddr]^(.8){a} \ar[d]_{m'} \ar[r]^{f'} & B' \ar[d]^{n'} \ar@/^.3cm/[ddr]^{b} \\  C' \ar@/_.3cm/[dr]_{h} \ar[r]_{g'}|(.7)\hole & D' \ar@{.>}[dr]^{k}\\ &A \ar[r]_f& B }\]
+		\[\xymatrix@C=40pt{A' \ar@/_.5cm/[dd]_{a} \ar[d]^{m'} \ar[r]^{f'} & B' \ar[d]_{n'} \ar@/^.5cm/[dd]^{b} \\  C' \ar[d]^{h} \ar[r]_{g'} & D' \ar@{.>}[d]_{k}\\ A \ar[r]_f& B }\]
 	The thesis now follows at once. \qedhere 
@@
 
-Given  two objects $G$ and $H$ and a rule $\rho=(l,r)$ in $R$, a \emph{direct derivation $\mathscr{D}$ from $G$ to $H$ via $\rho$}, is a diagram as the one below, in which both squares are pushouts. 
+Given  two objects $G$ and $H$ and a rule $\rho=(l,r)$ in $\R$, a \emph{direct derivation $\mathscr{D}$ from $G$ to $H$ applying the rule $\rho$}, is a diagram as the one below, in which both squares are pushouts.
 	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
 	The arrow $n$ is called the \emph{match} of the derivation, while $h$ is its \emph{back-match}.
-	We will denote a direct derivation $\dder{D}$ between $G$ and $H$ as $\dder{D}:G\Mapsto H$.
+	We will denote a direct derivation $\dder{D}$ between $G$ and $H$ as $\dder{D}:G\Mapsto H$. W
 \end{definition}
@@
 
-\begin{example}\label{exa:conc} Let  $\dder{D}:G\Mapsto H$ be the direct derivation 
+\begin{remark}\label{exa:conc} Let  $\dder{D}:G\Mapsto H$ be the direct derivation 
 		\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
@@
 	\[\xymatrix{L \ar[d]_{\phi \circ n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{\psi \circ h}\\G' & \ar[l]^{\phi \circ f} D \ar[r]_{\psi \circ g}& H}\]
-\end{example}
+
+	In particular, we will use $\phi*\dder{D}$ and $\dder{D}*\psi$  to denote $\phi*\dder{D}*\id{H}$ and $\id{G}*\dder{D}*\psi$.
+\end{remark}
 
@@
 Then there exist isomorphisms $t:D\to D'$ and $s:H\to H'$ as in the following diagram.
-	\[\xymatrix@C=40pt@R=10pt{ &&&R\ar[dddr]^{h'} \ar[dddl]_{h}|(.67)\hole\\&&K \ar[dl]_{l} \ar[ur]^{r}\ar[dddr]^{k'} \ar[dddl]_{k}\\&L \ar[dddl]_{n}\\&&H \ar@{.>}[rr]^{s} && H'\\ & D \ar[ur]^{g} \ar@{.>}[rr]^{t} \ar[dl]_{f}&& D' \ar[ur]_{g'}\ar@/^.4cm/[dlll]^{f'}\\ G}\]
+\[\xymatrix@C=40pt{&&D' \ar[r]^{g'} \ar@/_.45cm/[dll]_{f'}&H'\\G & L \ar[l]_{n} & K \ar[u]_{k'} \ar[d]^{k}\ar[r]^{r} \ar[l]_{l} &R\ar[u]^{h'} \ar[d]_{h}\\&&D\ar@/^.45cm/[ull]^{f}\ar@/^.4cm/@{.>}[uu]^(.4){t}|\hole \ar[r]_{g}&H\ar@/_.4cm/@{.>}[uu]_{s}}\]
 \end{proposition}
@@
 	\end{align*}
-	Hence, we have the dotted $s:H\to H'$. To see that $s$ is an isomorphism, consider the diagram 
+	Hence, we have the wanted $s:H\to H'$. To see that $s$ is an isomorphism, consider the diagram 
 	\[\xymatrix{K  \ar@/^.4cm/[rr]^{k'}\ar[d]_{r} \ar[r]_{k}& \ar[r]_{t} D \ar[d]^{g}& D' \ar[d]^{g'}\\ R \ar@/_.4cm/[rr]_{h'} \ar[r]^{h}& H \ar[r]^{s}& H'}\]
@@
 The claim now follows from the fact that the pushout of an isomorphism is an isomorphism.
-\qed
 \end{proof}
@@
 \begin{remark}
-We can spell out more explicitly what  a derivation $\dder{D}$ betwee nis.
+We can spell out more explicitly what  a derivation $\dder{D}$ is.
 An \emph{empty derivation} starting and ending in $G$ is just $G$ itself.
@@
 Moreover,  if every $\dder{D}_i$ applies the rule $\rho_i\in R$, then we can define an associated sequence of rules as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.
+\end{remark}
+
+\begin{remark}\label{rem:func}
+	Consider a derivation $\der{D}$ in a left-linear DPO-rewriting system $(\X, \R)$.
+We can take the subcategory $\Delta(\der{D})$ of $\X$ given by the arrows appearing in $\der{D}$.
+This subcategory comes equipped with an inclusion functor $I(\der{D}):\Delta(\der{D})\to \X$.
+Moreover, we can further define $\Deltamin(\der{D})$ as the subcategory of $\Delta(\der{D})$ containing only the bottom row of the derivation.
 \end{remark}
@@
 	\end{cases}\]
+
+Notice, moreover that, $\der{D}\cdot \der{D'}$ is equal to $\der{D}'$ if $\der{D}$ is empty, while it coincides with $\der{D}$ if $\der{D}'$ has length zero.
 \end{remark}
@@
 
-\begin{definition} Given a left-linear DPO-rewriting system $(\X, \R)$ and aderivation $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ between $G$ and $H$, the derivation $\phi *\der{D} * \psi$ between $G'$ and $H'$ is defined as
-	\[\phi *\der{D} * \psi := \{\phi* \dder{D}_0*\id{G_1}\}\cdot \{\dder{D}_i\}_{i=1}^{n-1} \cdot \{\id{G_n}*\dder{D}_n*\psi\}\]
-
-\end{definition}
-
-\begin{notation} In the following, we will use the notation $\phi *\dder{D}$, $\phi*\der{D}$ and $\dder{D}*\psi$, $\der{D}*\psi$ for the cases in which, respectively, $\psi=\id{H}$ and $\phi=\id{G}$.
-In particular
+\begin{definition} Let $(\X, \R)$ be a a left-linear DPO-rewriting system.
+Given a derivation $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ between $G$ and $H$ and isomorphisms $\phi: G\to G'$, $\psi:H\to H'$, the derivations  $\phi*\der{D}$ and $\der{D}*\psi$ are defined as
+	\[\phi *\der{D} := \begin{cases}
+		G' & \lgh(\der{D})=0\\ 
+		\{\phi* \dder{D}_0\}\cdot \{\dder{D}_i\}_{i=1}^{n}  & \lgh(\der{D})\neq 0
+	\end{cases}\] 
+	\[\der{D}*\psi := \begin{cases}
+		H' & \lgh(\der{D})=0\\ 
+		 \{\dder{D}_i\}_{i=0}^{n-1} \cdot \{\dder{D}_n*\psi\} & \lgh(\der{D})\neq 0
+	\end{cases}\]
+
+	Moreover, if $\lgh(\der{D})>0$,  we define the derivation $\phi *\der{D} * \psi$ as
 	\[\phi *\der{D} * \psi = \{\phi* \dder{D}_0\}\cdot \{\dder{D}_i\}_{i=1}^{n-1} \cdot \{\dder{D}_n*\psi\}\] 
-\end{notation}
+\end{definition}
+
+\begin{remark}
+When $\der{D}$ consists only in the direct derivation $\dder{D}$, then $\phi*\der{D}*\psi$ is the derivation of length one whose unique element is $\phi*\dder{D}*\psi$.
+\end{remark}
 
 We are often interested in an object of $\X$ only up to isomorphism.
-It is then useful to consider a version of $\gpo$ in which vertices are classes of isomorphism of object of $\X$.
+It is therefore useful to consider a version of $\gpo$ in which vertices are classes of isomorphism of object of $\X$.
 In order to do so, some preliminary work is needed.
@@
 
-\begin{remark}A decorated derivation $(\der{D}, \alpha, \omega)$ with $\der{D}$ empty is just a span
-	\[\xymatrix{G & \pi(G) \ar[r]^{\omega} \ar[l]_{\alpha} & G}\]
+\begin{example}A decorated derivation $(\der{D}, \alpha, \omega)$ with $\der{D}$ empty is just a span
+	\[\xymatrix{G & \pi(G) \ar[r]^-{\omega} \ar[l]_-{\alpha} & G}\]
 	in which both $\omega$ and $\alpha$ are isomorphisms.
-\end{remark}
+\end{example}
 
 As we are interested in objects only up to isomorphism, so we are interested in (decorated) derivations only up to some notion of coherent isomorphism between them.
-
-\begin{definition}
-	Let $\dder{D}:G\Mapsto H$ and $\dder{D}':G'\Mapsto H'$ be two direct derivations given by the following two diagrams
-	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L \ar[d]_{n'}& K \ar[d]^{k'}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & G' & \ar[l]^{f'} D' \ar[r]_{g'}& H'}\]
-	An \emph{abstraction equivalence} $\phi:\dder{D}\to \dder{D}'$ is a triple $(\phi_1, \phi_2, \phi_3)$ of isomorphism fitting in the diagram below.
-	\[\xymatrix@C=40pt@R=10pt{ &&&R\ar[dddr]^{h'} \ar[dddl]_{h}|(.67)\hole\\&&K \ar[dl]_{l} \ar[ur]^{r}\ar[dddr]^{k'} \ar[dddl]_{k}|(.67)\hole\\&L\ar[dddr]^(.4){n'} \ar[dddl]_(.4){n}\\&&H \ar[rr]^{\phi_3} && H'\\ & D \ar[ur]_(.7){g} \ar[rr]^{\phi_2} \ar[dl]_{f}&& D' \ar[ur]_{g'}\ar[dl]^{f'}\\ G \ar[rr]_{\phi_1} && G'}\]
-
-We will say that  two decorated derivations$(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ are \emph{abstraction equivalent}, if $\lgh(\der{D})=\lgh(\der{D}')$, $r(\der{D})=r(\der{D'})$, and there exists a family $\{\phi^i\}_{i=0}^{\lgh(\der{D})}$ of abstraction equivalences $\phi^i$ between $\dder{D}_i$ and  $\dder{D}'_i$ such that, for $i\in [0, \lgh(\der{D})]$, $\phi^i_3=\phi^{i+1}_1$ and  the following diagrams commute.
-\[\xymatrix{&\pi(G_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G_{n+1}) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G_0 \ar[rr]_{\phi^0_1} && G'_0 &G_{n+1} \ar[rr]_{\phi^n_3} && G'_{n+1} } \]
-
-We will use $\equiv^a$ to denote the resulting equivalence relation.
-An \emph{abstract decorated derivation}.
-$[\der{D}, \alpha, \omega]_a$ is just the equivalence class of  $(\der{D}, \alpha, \omega)$.
-\end{definition}
+This is done with the help of \Cref{rem:func}.
+
+\begin{definition}Let $(\X, \R)$ be a left-linear DPO-rewriting system,  an \emph{abstraction equivalence} between two derivations $\der{D}$ and $\der{D'}$ with the same length and such that $r(\der{D})=r(\der{D}')$, is a family of isomorphisms $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ such that, for every $i\in [0, \lgh(\der{D})]$ the following diagram commutes
+	\[\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i} \ar[l]_{f'}&G'_{i+1}\\  L_i \ar[u]^{n'_i} \ar[d]_{n_i}& K_i \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar[l]_{l_i} &R\ar[u]^{h'_i} \ar[d]_{h_i}\\G_i \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole \ar[r]_{g}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{H_i}}}\]
+
+Given two decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, we say that they are \emph{abstraction equivalent}, if $\lgh(\der{D})=\lgh(\der{D}')$, $r(\der{D})=r(\der{D'})$, and there exists an of abstraction equivalence between $\der{D}$ and  $\der{D}$ such that the triangles below commute.
+\[\xymatrix@C=15pt{&\pi(G_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G_{n+1}) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G_0 \ar[rr]_{\phi_{G_0}} && G'_0 &G_{n+1} \ar[rr]_{\phi_{G_{n+1}}} && G'_{n+1} } \]
+We will use $\equiv^a$ to denote the resulting relation.
+\end{definition}
+
+\begin{remark}\label{rem:equi}
+	It is immediate to see that $\equiv^a$ is an equivalence relation.
+Indeed $(\der{D}, \alpha, \omega)$ is abstract equivalent to itself via the abstract equivalence with the identities as components.
+Furthermore, if  $\{\phi_X\}_{X\in \Deltamin(\der{D})}$  witnesses $(\der{D}, \alpha, \omega)\equiv_a (\der{D}', \alpha', \omega')$, then considering $\{\phi^{-1}_X\}_{X\in \Deltamin(\der{D})}$ shows $(\der{D}', \alpha', \omega)\equiv_a (\der{D}, \alpha, \omega)$.
+Finally, transitivity is assured composing abstract equivalences.
+
+	We will denote by $[\der{D}, \alpha, \omega]_a$ is just the equivalence class of  $(\der{D}, \alpha, \omega)$.
+	 Such equivalence classes will be called  \emph{abstract decorated derivation}.  
+\end{remark}
+
+\begin{remark}\label{rem:empty}
+Let $(\der{D},\alpha, \omega)$ be an empty derivation from an object $G$ and  $(\der{D}',\alpha', \omega')$ a another empty one from $G'$.
+If $(\der{D},\alpha, \omega)\equiv_a(\der{D}',\alpha', \omega')$ then an abstraction equivalence between $\der(D)$ and $\der{D}'$ is just an isomorphism $\phi:G\to G'$, so that $\pi(G)=\pi(G')$.
+Moreover, such isomorphism must fit in the diagrams below.
+\[\xymatrix@C=15pt{&\pi(G) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G\ar[rr]_{\phi} && G' &G \ar[rr]_{\phi} && G' } \]
+In particular, these two triangles imply that
+\begin{align*}
+	\alpha'\circ \alpha^{-1}&=\phi \\&=\omega'\circ \omega^{-1}
+\end{align*}
+\end{remark}
+
 \begin{remark}\label{rem:res} \Cref{prop:unique} can be restated as saying that, given two direct derivations $\dder{D}$ and $\dder{D'}$ with the same match, there exists an abstract equivalence between them whose first component is an identity.
@@
 
-\begin{definition}
+\begin{definition}\label{def:conc}
 Let $(\der{D}, \alpha, \omega)$ be a decorated derivation between $G$ and $H$ and $(\der{D}', \alpha', \omega')$ one between $H'$ and $K$.
-If $H$ and $H'$ are isomorphic, so that $\pi(H)=\pi(H')$, we define the  \emph{composite decorated derivation}  $(\der{D}, \alpha, \omega)\cdot (\der{D}', \alpha', \omega')$ as $((\der{D}* \omega^{-1}) \cdot ((\alpha')^{-1} *\der{D}'), \alpha, \omega')$.
+If $H$ and $H'$ are isomorphic, so that $\pi(H)=\pi(H')$, we define the  \emph{composite decorated derivation} putting
+\[(\der{D}, \alpha, \omega)\cdot (\der{D}', \alpha', \omega'):=\begin{cases}
+(\der{D}', \alpha'\circ \omega^{-1}\circ \alpha, \omega')	&\lgh(\der{D})=0 \\
+	(\der{D}, \alpha, \omega \circ (\alpha')^{-1}\circ \omega')&\lgh(\der{D}')=0 \text{ and } \lgh(\der{D})\neq 0\\
+(\der{D}*\omega^{-1}\cdot \alpha'*\der{D'}, \alpha, \omega')	&\text{otherwise}
+\end{cases}\]
 \end{definition}
@@
 \begin{remark}\label{rem:lgt}
-	Given two composable decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$  such that $\der{D}$ and $\der{D}'$ have  length $n$ and $m$, respectively, then $(\der{D}* \omega^{-1}) \cdot ((\alpha')^{-1} *\der{D}')$ has length $n+m$.
-\end{remark}
+	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ two composable decorated derivations   such that $\lgh(\der{D})=n$ and $\lgh(\der{D}')=m$.	 Then $(\der{D}*\omega^{-1}\cdot \alpha'*\der{D'}, \alpha, \omega')$ has length $n+m$.
+\end{remark}
+\iffalse 
+\begin{proposition}\label{prop:ident}
+Let $(\der{D}, \alpha, \omega)$ be a decorated derivation between $G$ and $H$ and  $(\der{D}',\alpha', \omega')$ be one between $G'$ and $H'$.
+Suppose, moreover that $G'$ and $H$ are isomorphic, so that $\pi(G')=\pi(H)$.
+Then the following hold true.
+\begin{enumerate}
+	\item If $\der{D}$ is the empty derivation, then
+	\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')\equiv_a (\der{D}',\alpha', \omega')\]
+	\item  If $\der{D}'$ is the empty derivation, then
+	\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')\equiv_a (\der{D},\alpha, \omega)\]
+\end{enumerate}
+\end{proposition}
+\begin{proof}
+\begin{enumerate}
+	\item 
+	By \Cref{def:conc}, we have that 
+	\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')= (\der{D}', \alpha'\circ \omega^{-1}\circ \alpha, \omega')\]
+
+	For every $X\in \Deltamin(\der{D'})$ we can define
+	\[\phi_{X}:=\begin{cases}
+		\alpha' \circ \alpha \circ \omega \circ (\alpha')^{-1} & X=G'\\
+		\id{X} & \text{otherwise}
+	\end{cases} \]
+	Now, we can notice that $\phi_{G'_0}$ is the composition $\alpha'\circ (\alpha'\circ \omega^{-1}\circ \alpha)^{-1}$, giving us the triangle
+
+\[\xymatrix@C=15pt{&\pi(G') \ar[dr]^{\alpha'} \ar[dl]_{\alpha'\circ \omega^{-1}\circ \alpha}\\ G'\ar[rr]_{\phi_{G'}} && G'} \]
+To conclude the proof it is now enough to show the commutativity of 
+	\[\xymatrix@C=40pt{G'&D'_0 \ar[r]^{g'_0} \ar[l]_{f'_0}&G'_{1}\\  L'_0 \ar[u]^{n'_0} \ar[d]_{n'_0}& K'_0 \ar[u]^{k'_0} \ar[d]_{k'_0} \ar[r]^{r'_0} \ar[l]_{l'_0} &R'_0\ar[u]^{h'_0} \ar[d]_{h'_0}\\G' \ar@/_.45cm/[uu]_(.35){\phi_{G'}}|\hole&D'_0\ar[l]^{f'_0}\ar@/_.45cm/[uu]_(.35){\id{D'_0}}|\hole \ar[r]_{g'_0}&G'_{1}\ar@/_.45cm/[uu]_{\id{G'_1}}}\]
+
+	\item \qedhere 
+\end{enumerate}
+\end{proof}
+
+\begin{remark}\label{rem:ident}Consider a decorated derivation $(\der{D}, \alpha, \omega)$ between $G$ and $H$ and another one $(\der{D}',\alpha', \omega')$ between $G'$ and $H'$.
+Suppose, moreover that $\pi(G')=\pi(H)$.
+By \Cref{rem:empty}, if $\der{D}$ is the empty derivation, so that $G=H$, then
+	\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')= ((\omega \circ (\alpha')^{-1}) *\der{D}', \alpha, \omega')\]
+
+Furthermore, we can notice that
+\[(\der{D}', \alpha', \omega')\equiv_a ((\omega \circ (\alpha')^{-1}) *\der{D}', \alpha, \omega')\]	
+Indeed, for every $X'\in \Deltamin(\der{D'})$ we can define
+\[\phi_{X'}:=\begin{cases}
+	(\alpha')^{-1} & X'=G'\\
+	\id{X'} & \text{otherwise}
+\end{cases} \]
+
+Similarly, if $\lgh(\der{D}')=0$, implying $G'=H'$, we get
+		\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')=(\der{D}*\omega^{-1}, \alpha, \omega')\]
+
+We can notice, moreover, that 
+\[(\der{D}', \alpha', \omega')\equiv_a ((\omega \circ (\alpha')^{-1}) *\der{D}', \alpha, \omega') \qquad  (\der{D}, \alpha, \omega) \equiv_a (\der{D}*\omega^{-1}, \alpha, \omega')\] 	
+Indeed,  for every $X'\in \Deltamin(\der{D'})$ and $X\in \Deltamin(\der{D})$ we can define
+\[\phi_{X'}:=\begin{cases}
+	(\alpha')^{-1} & X'=G'_{0}\\
+	\id{X'} & \text{otherwise}
+\end{cases} \qquad \phi_{X}:=\begin{cases}
+\id{X} & \text{otherwise}\\
+\omega^{-1} & X=H\\
+\end{cases}\]
+
+first of all notice that the triangles below commute.
+\[\xymatrix@C=15pt{&\pi(G'_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G\ar[rr]_{\phi} && G' &G' \ar[rr]_{\phi} && G' } \]
+
+Furthermore, for every $X\in $ $i\in [0, \lgh(\der{D})]$
+
+\end{remark}
+\fi
 
 The next proposition justifies the use of decorations, guaranteeing that concatenation of abstract decorated derivations is weel-defined.
-\begin{proposition}
+\begin{lemma}
 	Given a decorated derivation $(\der{D}, \alpha, \omega)$  between $G$ and $H$ and  another one $(\der{E}, \beta, \xi)$ between $E$ and $K$ with $\pi(H)=\pi(E)$.
 If  $(\der{D}', \alpha', \omega')$ and $(\der{E}', \beta', \xi')$ are two other decorated derivations such that
-	$[\der{D}, \alpha, \omega]_a = [\der{D}', \alpha', \omega']_a$ and $[\der{D}, \beta, \xi]_a=[\der{E}', \beta', \xi']_a$, then
+	\[[\der{D}, \alpha, \omega]_a = [\der{D}', \alpha', \omega']_a \qquad [\der{D}, \beta, \xi]_a=[\der{E}', \beta', \xi']_a\]
+	Then
 	\[[(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)]_a=[(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')]_a\]
-\end{proposition}
-
-\begin{proof}
-	To fix the notation, let $\der{D}$, $\der{D}'$, $\der{E}$ and $\der{E}'$ be given by
-	\[\der{D}=\{\dder{D}_i\}_{i=0}^n \quad \der{D}'=\{\dder{D}'_i\}_{i=0}^n \quad \der{E}=\{\dder{E}_i\}_{i=0}^m \quad \der{E}'=\{\dder{E}'_i\}_{i=0}^m\]
-	Let also $\{\phi^i\}_{i=0}^n$ and $\{\varphi^i\}_{i=0}^m$ be families of abstract equivalences between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ and between $(\der{E}, \beta, \xi)$ and $(\der{E}', \beta', \xi')$, respectively.
-For every $i\in [0, n+m-1]$ define
-	\[\psi^{i}:=\begin{cases}
-		\phi^i & i< n\\
-		(\phi^n_1, \phi^n_2, \id{\pi(H)}) & i=n\\
-		(\id{\pi(E)}, \varphi^{0}_2, \varphi^{0}_3) & i=n+1\\
-		\varphi^{i-n+1} & i>n+1
-	\end{cases}\] 
-Notice suppose that $h_n:R_n\to H, h_n:R_n\to H'$ are the back-matches of $\der{D}_n$ and $\der{D}'_n$ and that the following diagram is given
-	\[\xymatrix@C=40pt@R=10pt{ &&&R_n\ar[dddr]^{h'_n} \ar[dddl]_{h_n}|(.67)\hole\\&&K_n \ar[dl]_{l_n} \ar[ur]^{r_n}\ar[dddr]^{k'_n} \ar[dddl]_{k_n}|(.67)\hole\\&L_n\ar[dddr]^(.4){m'_n} \ar[dddl]_(.4){m_n}\\&&H \ar[rr]^{\phi^n_3} && H'\\ & D_n \ar[ur]_(.7){g_n} \ar[rr]^{\phi^n_2} \ar[dl]_{f_n}&& D'_n \ar[ur]_{g'_n}\ar[dl]^{f'_n}\\ G_{n} \ar[rr]_{\phi^n_1} && G'_n}\]
-Then we have
-\begin{align*} 
-	\id{\pi(H)}\circ \omega^{-1} \circ h_n&=(\omega')^{-1}\circ \phi^n_3 \circ \omega \circ \omega^{-1} \circ h_n\\&=(\omega')^{-1}\circ \phi^n_3  \circ h_n\\&=(\omega')^{-1}  \circ h'_n
+\end{lemma}
+
+\begin{proof} Take two abstraction equivalences $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ and $\{\varphi_X\}_{X\in \Deltamin(\der{D})}$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ and between $(\der{E}, \beta, \xi)$ and $(\der{E}', \beta', \xi')$, respectively.
+To fix the notation, suppose that goes from $G'$ to $H'$ and $(\der{E}', \beta', \xi')$ from $E'$ to $K'$.
+We have three cases.
+
+\begin{itemize}
+	\item $\lgh(\der{D})=0$. Then, $\lgh(\der{D}')$ is $0$ too. By \Cref{def:conc} we have
+	\begin{align*}
+	(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)&=(\der{E}, \beta\circ \omega^{-1}\circ \alpha, \xi)\\
+		(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')&=(\der{E}', \beta'\circ (\omega')^{-1}\circ \alpha', \xi')
+	\end{align*}
+ Now, notice that $G$ and $H$ must coincide.
+Moreover, by \Cref{rem:empty} we also know that $\pi(G)=\pi(G')$ too.
+The same \Cref{rem:empty} entails that the inner squares of the following diagram are commutative, so that the whole rectangle commutes too.
+ \[\xymatrix@C=35pt{\pi(G) \ar[r]^{\alpha} \ar[d]_{\id{\pi(G)}}& G  \ar[d]_{\phi_G}\ar[r]^-{\omega^{-1}} & \pi(G) \ar[d]_{\id{\pi(G)}} \ar[r]^{\beta}& E \ar[d]^{\varphi_E}\\\pi(G') \ar[r]_{\alpha'}& G' \ar[r]_-{(\omega')^{-1}} & \pi(G') \ar[r]_{\beta'} & E'}\]
+
+ We can  then conclude that $\{\varphi_X\}_{X\in \Deltamin(\der{D})}$ witnesses the fact that $(\der{E}, \beta\circ \omega^{-1}\circ \alpha, \xi)$ is abstraction equivalent to $(\der{E}', \beta'\circ (\omega')^{-1}\circ \alpha', \xi')$.
+
+\item $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})= 0$. As in the point above, we get that also $\der{E}'$  is an empty derivation, thus we have
+\begin{align*}
+	(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)&=(\der{D},  \alpha, \omega \circ \beta^{-1}\circ \xi)\\
+	(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')&=(\der{D}',  \alpha', \omega' \circ (\beta')^{-1}\circ \xi')
+\end{align*}
+In this case we have that $E=K$ and that $\pi(E)=\pi(E')$. From \Cref{rem:empty} we deduce that the diagram below commutes.
+\[\xymatrix@C=35pt{\pi(E) \ar[r]^{\xi} \ar[d]_{\id{\pi(E)}}& E  \ar[d]_{\varphi_E}\ar[r]^-{\beta^{-1}} & \pi(E) \ar[d]_{\id{\pi(E)}} \ar[r]^{\omega}& H \ar[d]^{\phi_H}\\\pi(E') \ar[r]_{\xi'}& E' \ar[r]_-{(\beta')^{-1}} & \pi(E') \ar[r]_{\omega'} & H'}\]
+The thesis now follows at once.
+	\item $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})\neq 0$. In this case we have
+	\begin{align*}
+		(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)&=(\der{D}*\omega^{-1}\cdot \beta*\der{E}, \alpha, \xi)\\
+		(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')&=(\der{D}'*(\omega')^{-1}\cdot \beta'*\der{E'}, \alpha', \xi')
+	\end{align*}
+ To fix the notation, suppose that $\der{D}$, $\der{D}'$, $\der{E}$ and $\der{E}'$ are given by
+	\[\der{D}=\{\dder{D}_i\}_{i=0}^n \quad \der{D}'=\{\dder{D}'_i\}_{i=0}^n \quad \der{E}=\{\dder{E}_i\}_{i=0}^t \quad \der{E}'=\{\dder{E}'_i\}_{i=0}^t\]
+	where $\dder{D}_i$, $\dder{D}'_i$, $\dder{E}_i$ and $\dder{E}'_i$ are given, respectively, by the following four diagrams.
+We can also notice that the rule applied by $\dder{D}_i$ must coincide with the one applpied in $\dder{D}'_i$ and that the same holds for $\dder{E}_i$ and $\dder{E}'_i$.
+	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}, i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}, i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}, i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}, i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}, i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}, i}} \\G_i & D_i \ar[r]_{g_{\der{D},i}} \ar[l]^{f_{\der{D},i}} & G_{i+1} & E_i & F_i\ar[r]_{g_{\der{E},i}} \ar[l]^{f_{\der{E},i}}  & E_{i+1}}\]
+	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}', i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}', i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}', i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}', i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}', i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}', i}} \\G_i & D_i \ar[r]_{g_{\der{D}',i}} \ar[l]^{f_{\der{D}',i}} & G_{i+1} & E_i & F_i\ar[r]_{g_{\der{E}',i}} \ar[l]^{f_{\der{E}',i}}  & E_{i+1}}\]
+
+Now, for every $X\in \Deltamin(\der{D}*\omega^{-1}\cdot \beta*\der{E})$ we can define
+\[\psi_X:=\begin{cases}
+	\phi_X & X\in  \Deltamin(\der{D})\text{ and } X\neq H\\\varphi_X & X\in  \Deltamin(\der{E}) \text{ and } X\neq E\\\id{\pi(H)}& X=\pi(H)\end{cases}\]
+Notice that, since $\psi_G=\phi_G$ and $\psi_K=\varphi_K$ we have at once  the commutativity of the triangles
+\[\xymatrix@C=15pt{&\pi(G) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(K) \ar[dr]^{\xi'} \ar[dl]_{\xi}\\ G\ar[rr]_{\psi_G} && G' &K \ar[rr]_{\psi_K} && K' } \]
+
+To show that $\{\psi_X\}_{\Deltamin(\der{D}*\omega^{-1}\cdot \beta*\der{E})}$ it is now enough to prove the commutativity of the diagrams
+	\[\xymatrix@C=45pt@R=15pt{G'_n&D'_n \ar[r]^-{(\omega')^{-1}\circ g_{\der{D}',n}} \ar@/_.2cm/[dr]_(.6){g_{\der{D}',n}} \ar[l]_{f_{\der{D}',n}}&\pi(H') \\&&H' \ar[u]^{(\omega')^{-1}}\\  L_{\der{D}, n} \ar[uu]^{m_{\der{D}',n}} \ar[dd]_{m_{\der{D},n}}& K_{\der{D}, n} \ar[uu]^{k_{\der{D}',n}} \ar[dd]_{k_{\der{D},n}} \ar[r]^{r_{\der{D},n}} \ar[l]_{l_{\der{D},n}} &R_{\der{D}, n}\ar[u]^{h_{\der{D}',n}} \ar[d]_{h_{\der{D},n}}\\&&H \ar[d]_{\omega^{-1}}\\G_n \ar@/_.7cm/[uuuu]_(.35){\phi_{G_n}}|\hole&D_n\ar[l]^{f_{\der{D},n}}\ar@/_.7cm/[uuuu]_(.35){\phi_{D_n}}|\hole \ar@/^.2cm/[ur]^(.6){g_{\der{D},n}}\ar[r]_{\omega^{-1}\circ g_{\der{D},n}}&\pi(H)\ar@/_.7cm/[uuuu]_{\id{\pi(H)}}\\ \pi(E')&F'_0 \ar[l]_-{(\beta')^{-1}\circ f_{\der{E}',0}} \ar@/^.2cm/[dl]^(.6){f_{\der{E}',0}} \ar[r]^{g_{\der{E}',0}}&E'_1 \\E' \ar[u]_{(\beta')^{-1}}&& \\  L_{\der{E}, 0} \ar[u]_{m_{\der{E}', 0}} \ar[d]^{m_{\der{E}, 0}}& K_{\der{E}, 0} \ar[uu]_{k_{\der{E}', 0}} \ar[dd]^{k_{\der{E}, i}} \ar[r]^{r_{\der{E},0}} \ar[l]_{l_{\der{E},0}} &R_{\der{E}, 0}\ar[uu]_{h_{\der{E}',0}} \ar[dd]^{h_{\der{E},0}}\\E \ar[d]^{\beta^{-1}}&& \\\pi(E) \ar@/^.7cm/[uuuu]^{\id{\pi(E)}}&F_0\ar[l]^{\beta^{-1}\circ f_{\der{E},0}}\ar@/^.7cm/[uuuu]^(.35){\varphi_{F_0}}|\hole \ar@/_.2cm/[ul]_(.6){f_{\der{E},0}}\ar[r]_{g_{\der{E},0}}&E_1\ar@/^.7cm/[uuuu]^(.35){\varphi_{E_1}}|\hole}\]
+
+To see this, in turn, it is enough to show that	the squares
+\[\xymatrix{&R_{\der{D}, n} \ar[d]_{h_{\der{D}, n}}\ar[r]^{h_{\der{D}', n}} & H' \ar[d]^{(\omega')^{-1}} &L_{\der{E}, 0} \ar[d]_{m_{\der{E}, 0}}\ar[r]^{m_{\der{E}', 0}}& E' \ar[d]^{(\beta')^{-1}}\\&H\ar[r]_{\omega^{-1}} &\pi(H)&E \ar[r]_{\beta^{-1}} & \pi(E)\\D_n \ar[rr]^{\phi_{D_n}} \ar[d]_{g_{\der{D}, n}}&&D'_n \ar[d]^{g_{\der{D}', n}}&F_0 \ar[d]_{f_{\der{E}, 0}} \ar[rr]^{\varphi_{F_0}} && F_0' \ar[d]^{f_{\der{E}', 0}}\\H \ar[r]_-{\omega^{-1}} &\pi(H)&H' \ar[l]^-{(\omega')^{-1}}  &E \ar[r]_-{\beta^{-1}} & \pi(E) & E' \ar[l]^-{(\beta')^{-1}}}\]
+are commutative. For the first ones, we have
+	\begin{align*} 
+	\omega^{-1} \circ h_{\der{D}, n}&=\id{\pi(H)}\circ \omega^{-1} \circ h_{\der{D}, n} \\&=(\omega')^{-1}\circ \phi_H \circ \omega \circ \omega^{-1} \circ h_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H  \circ h_{\der{D}, n}\\&=(\omega')^{-1}  \circ h_{\der{D}', n}
 \end{align*} 
 and
-\begin{align*} \id{\pi(H)}\circ \omega^{-1} \circ g_n  &=(\omega')^{-1}\circ \phi^n_3 \circ \omega \circ \omega^{-1}\circ g_n\\&=(\omega')^{-1}\circ \phi^n_3\circ g'_n\\&=(\omega')^{-1}\circ g'_n\circ \phi^n_2\end{align*}
-Therefore $\psi^n$ is an abstract equivalence between $\dder{D}_n*\omega^{-1}$ and $\dder{D}_n'*(\omega')^{-1}$.
-
-Similarly, if $\hat{m}_0:\hat{L}_0\to E, \hat{m}'_0:L'_0\to E'$ the matches of $\der{E}_0$, $\der{E}'_0$, we can consider the diagram
-\[\xymatrix@C=40pt@R=10pt{ &&&\hat{R}_0\ar[dddr]^{\hat{h}'_0} \ar[dddl]_{\hat{h}_0}|(.67)\hole\\&&\hat{K}_0 \ar[dl]_{\hat{l}_0} \ar[ur]^{\hat{r}_0}\ar[dddr]^{k'_0} \ar[dddl]_{\hat{k}_0}|(.67)\hole\\&\hat{L}_n\ar[dddr]^(.4){\hat{m}'_0} \ar[dddl]_(.4){\hat{m}_0}\\&&\hat{G}_1 \ar[rr]^{\varphi^0_3} && \hat{G}'_1\\ & \hat{D}_0 \ar[ur]_(.7){\hat{g}_0} \ar[rr]^{\varphi^0_2} \ar[dl]_{\hat{f}_0}&& \hat{D}'_0 \ar[ur]_{\hat{g}'_0}\ar[dl]^{\hat{f}'_0}\\ E \ar[rr]_{\varphi^0_1} && E'}\]
-and computing we get
-\begin{align*}
-	\id{\pi(E)}\circ \alpha^{-1} \circ \hat{m}_0&=(\alpha')^{-1}\circ \varphi^0_1 \circ \alpha \circ \alpha^{-1} \circ \hat{m}_0\\&=(\alpha')^{-1}\circ \varphi^0_1  \circ \hat{m}_0\\&=(\alpha')^{-1}\circ \hat{m}'_n
-\end{align*}
-together with
-\begin{align*} \id{\pi(E)}\circ \alpha^{-1}\circ \hat{f}_0  &=(\alpha')^{-1}\circ \varphi^0_1 \circ \alpha \circ \alpha^{-1}\circ \hat{f}_0\\&=(\alpha')^{-1}\circ \varphi^0_1\circ \hat{f}_0\\&=(\alpha')^{-1}\circ \hat{f}'_0\circ \varphi^0_2\end{align*}
-The previous two identities show that $\psi^{n+1}$ is an abstract equivalence between $\dder{E}_0$ and $\dder{E}'_0$. By hypothesis $\pi(H)=\pi(E)$ and, moreover, we have
-	\[\begin{split}
-		\psi^{0}_1\circ \alpha &= \phi^0_1\circ \alpha \\&= \alpha'
-	\end{split}\qquad \begin{split}
-	\psi^{n+m-1}_3\circ \xi &=\varphi^m_3\circ \xi \\&= \xi'
-	\end{split}\]
-Therefore the thesis now follows.	\qedhere 
+\begin{align*} 
+	\beta^{-1} \circ m_{\der{E}, 0}&=\id{\pi(E)}\circ \beta^{-1} \circ m_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_{E} \circ \beta \circ \beta^{-1} \circ m_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_{E}  \circ m_{\der{E}, 0}\\&=(\beta')^{-1}  \circ m_{\der{E}', 0}
+\end{align*}
+
+The commutativity of the second row of diagrams follows from
+\begin{align*}
+ \omega^{-1} \circ g_{\der{D}, n}&=\id{\pi(H)}\circ \omega^{-1} \circ g_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H \circ \omega\circ \omega^{-1} \circ g_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H  \circ g_{\der{D}, n}\\&= (\omega')^{-1} \circ g_{\der{D}', n}\circ \phi_{D_n}
+\end{align*}
+and
+\begin{align*}
+	\beta^{-1} \circ f_{\der{E}, 0}&=\id{\pi(E)}\circ \beta^{-1} \circ f_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_E \circ \beta\circ \beta^{-1} \circ f_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_E  \circ f_{\der{E}, 0}\\&= (\beta')^{-1} \circ f_{\der{E}', n}\circ \varphi_{F_0}
+\end{align*}
+ The thesis now follows.	\qedhere 
+\end{itemize}	
 \end{proof}
@@
 		\item objects are isomorphism classes of objects of $\X$;
-		\item a non-identity arrow $[G]\to [H]$ is an equivalence class $[\der{D}, \alpha, \omega]_a$ of a decorated derivation between $G'$ and $H'$ for some $G'$ and $H'$ such that $\pi(G')=G$ and $\pi(H')=H$;
+		\item an arrow $[G]\to [H]$ is an equivalence class $[\der{D}, \alpha, \omega]_a$ of a decorated derivation between $G'$ and $H'$ for some $G'$ and $H'$ such that $\pi(G')=G$ and $\pi(H')=H$;
 		\item composition is concatenation of abstract decorated derivations;
-		\item identities are added formally.
-	\end{itemize}
+		\item the identity on $[G]$ is $[(G, \alpha, \alpha)]_a$, where $\alpha$ is any isomorphism $\pi(G)\to G$.	\end{itemize}
 \end{definition}
@@
 	We have to construct the two dotted arrows in the diagram below.
-			\[\xymatrix@C=15pt{L_.
-\ar[d]_{z'_0\circ o_0}&& K_0 \ar[d]_{n_1\circ w}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@{.>}@/^.35cm/[drrr]_(.4){\alpha_1}|(.285)\hole \ar[dr]|(.28)\hole_{y_1\circ e_0} && L_1 \ar@{.>}@/_.35cm/[dlll]^(.4){\alpha_2} \ar[dl]|(.28)\hole^{y_1\circ b_1}& K_1 \ar[d]^{d_2\circ u}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ a_1}\\G'_1 && \ar[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2  && \ar[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_2}\]
+			\[\xymatrix@C=15pt{L_0 \ar[d]_{z'_0\circ o_0}&& K_0 \ar[d]_{n_1\circ w}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@{.>}@/^.35cm/[drrr]_(.4){\alpha_1}|(.285)\hole \ar[dr]|(.28)\hole_{y_1\circ e_0} && L_1 \ar@{.>}@/_.35cm/[dlll]^(.4){\alpha_2} \ar[dl]|(.28)\hole^{y_1\circ b_1}& K_1 \ar[d]^{d_2\circ u}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ a_1}\\G'_1 && \ar[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2  && \ar[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_2}\]
 
@@
 			\end{align*}
-			The thesis now follows. \qed
+			The thesis now follows.  
 \end{proof}
@@
 
+\section{On rewriting systems on $\Set$.}\label{app:set}
+
 \end{document}

### 2023-12-11 fusione.tex
indep is global + varie

@@
 \usepackage[all]{xy}
+\newdir^{ (}{{}*!/-5pt/@^{(}}
 \SelectTips{cm}{}
@@
 \newcommand{\slab}[1]{\ensuremath{\scriptstyle{\mathsf{{#1}}}}}
+
+%frecce
+\newcommand{\mor}{\mathsf{Mor}}
+\newcommand{\mon}{\mathsf{Mono}}
+\newcommand{\reg}{\mathsf{Reg}}
 
@@
 \def\A{\textbf {\textup{A}}}
-%scheletro
+%mono
+\newcommand{\mto}[0]{\scalebox{1}{$\rightarrowtail$}}
 
@@
 \title{Switch equivalence and weak prime domains for fusions}
-\author{Paolo Baldan \and Davide Castelnovo  \and  Andrea Corradini  \and Fabio Gadducci}
+\author{Paolo Baldan\and Davide Castelnovo\and  Andrea Corradini\and Fabio Gadducci}
 
@@
 
-This first section is devoted to recall the definition and the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2006weak,lack2005adhesive}.
+This first section is devoted to recall the definition and the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive}.
 
@@
 We stipulate here some notational conventions which will be used throughout this paper. 
-
+\begin{itemize}\item 
 	Given a category $\X$ we will not distinguish notationally between $\X$ and its class of objects: so that ``$X\in \X$'' means that $X$ belongs to the class of objects of $\X$.  
-
+	\item 
 	If $1$ is a terminal object in a category $\X$,  the unique arrow $X\to 1$ from another object $X$ will be denoted by $!_X$.
 Similarly, if $0$ is initial in $\X$ then $?_X$ will denote the unique arrow $0\to X$.
-When $\X$ is $\Set$ and $1$ is a singleton, $\delta_x$ will denote the arrow $1\to X$ with value $x\in X$.
-
-Finally, we will use the following notation for some special classes of arrows of a category $\X$:
-\begin{itemize}
-	\item $\mathcal{A}(\X)$ will denote the class of all arrows of $\X$;
-	\item $\mathcal{M}(\X)$ will denote the class of all monos of $\X$;
-	\item $\mathcal{R}(\X)$ will denote the class of all regular monos of $\X$.
+%When $\X$ is $\Set$ and $1$ is a singleton, $\delta_x$ will denote the arrow $1\to X$ with value $x\in X$.
+	\item  $\mor(\X)$, $\mon(\X)$ and $\reg(\X)$ will denote the class of all arrows, monos and regular monos of $\X$, respectively.
+
+	\item Given an integer $n\in \mathbb{Z}$, $[0,n]$ will denote the set
+	\[[0,n]:=\{x\in \mathbb{N}\mid x\leq n\}\]
+	Indeed, if $n<0$, then $[0,n]=\emptyset$.
 \end{itemize}
@@
 
-\subsection{The Van Kampen condition}
+\subsection{The Van Kampen property}
 The key property that $\mathcal{M}$-adhesive categories enjoy is given by  the so-called \emph{Van Kampen condition} \cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive}.
 We will recall it and examine some of its consequences.
-
-\begin{definition} \index{Van Kampen square} \index{pushout!- square} \index{pushout!Van Kampen -|see{Van Kampen square}}Let $\X$ be a category  and consider the two diagrams below
+First of all we need to recall some terminology and facts regarding subclasses of $\mor(\X)$.
+
+\begin{definition}
+	Let $\X$ be a category and $\mathcal{A}$ a  subclass of $\mor(\X)$. We say that  $\mathcal{A}$ is
+	\begin{itemize}
+		\item 
+		\emph{stable under pushouts (pullbacks)} if for every pushout (pullbacks) square 
+		\[\xymatrix{A\ar[r]^f  \ar[d]_{m}& B \ar[d]^n \\ C \ar[r]_g & D}\]
+		if $m \in \mathcal{A}$ ($n\in \mathcal{A}$) then $n \in \mathcal{A}$ ($m \in \mathcal{A}$);
+		\item \emph{closed under composition} if $g, f\in \mathcal{A}$ implies $g\circ f\in \mathcal{A}$ whenever $g$ and $f$ are composable;
+		\item \emph{closed under decomposition} if $g\circ f, g\in \mathcal{A}$ implies $f\in \mathcal{A}$.
+	\end{itemize}
+\end{definition}
+
+\begin{remark}In the previous definition, ``decomposition'' corresponds to ``left cancellation'', but we prefer to stick to the name commonly used in literature (see e.g.~\cite{habel2012mathcal}).
+\end{remark}
+
+So equipped, we can introduce the notion of \emph{$\mathcal{A}$-Van Kampen square}.
+\begin{definition}[Van Kampen property] Let $\X$ be a category  and consider the two diagrams below
 	\[\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{f}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{g} &&D&&C \ar[rr]_{g} & & D}\]
-	We say that the left square is a \emph{Van Kampen square} if:
-	\begin{enumerate}
-		\item it is a pushout square;
-		\item whenever the right cube has pullbacks as back and left faces, then its top face is a pushout if and only if the front and right faces are pullbacks.
-	\end{enumerate}
-
-	Pushout squares which enjoy the ``if'' half of this condition are called \emph{stable}.
-\end{definition}
-
-\begin{example}\label{ex:iso}
-	In any category $\X$, a square as the one below on the left, in which $m$ is an isomorphism, is Van Kampen. Notice that, in this situation, $n$ must be an isomorphism too.
-		\[\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{f}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{g} &&D&&C \ar[rr]_{g} & & D}\]
-
-	Take a cube as the one above and suppose that its back faces are pullbacks. In particular we know that also $m'$ is an isomorphism.
-
-	\smallskip \noindent 
-	$(\Rightarrow)$ Suppose that the top face is a pushout, thus $n'$ is an isomorphism and the right square is a pullback.
-The thesis for the front face follows at once since $m', n', m$ and $m$ are isomorphisms and the back face a pullback.
-
-	\smallskip \noindent 
-	$(\Leftarrow)$ If all the vertical faces are pullbacks, then $m'$ and $n'$ are isomorphisms and this entails at once that the top face is a pushout.
-\end{example}
+
+	Given  a class of arrows $\mathcal{A}\subseteq \mor(\X)$, we say that the left square \emph{has the Van Kampen property relatively to $\mathcal{A}$}, or that it  is a \emph{$\mathcal{A}$-Van Kampen square} if:
+	\begin{enumerate}
+		\item is a pushout square;
+		\item 	whenever the right cube has pullbacks as back and left faces and the vertical arrows belong to $\mathcal{A}$, then its top face is a pushout if and only if the front and right faces are pullbacks.
+	\end{enumerate}
+	Pushout squares which enjoy the ``if'' half of the second point of the condition above are called \emph{$\mathcal{A}$-stable}.
+
+We will call a $\mor(\X)$-Van Kampen ($\mor(\X)$-stable) square simply a \emph{Van Kampen} (\emph{stable}) square.
+\end{definition}
 
@@
 
-The following proposition establishes a key property of Van Kampen squares with a mono as a side: they are not only pushouts, but also pullbacks.
-\begin{proposition}\label{prop:pbpo} Let $m\colon A\to C$ be a monomorphism in a category $\X$. Then every Van Kampen square
+The following proposition establishes a key property of $\mathcal{A}$-Van Kampen squares with a mono as a side: they are not only pushouts, but also pullbacks.
+\begin{proposition}\label{prop:pbpo} Let $\mathcal{A}$ be a class of arrows stable under pushouts and containing all the isomorphisms.
+If $m\colon A\to C$ is mono and belongs to $\mathcal{A}$, then every $\mathcal{A}$-Van Kampen square
 	\[\xymatrix{A\ar[r]^{g} \ar[d]_{m} & B \ar[d]^{n} \\ C \ar[r]_{f}  & D}\]
@@
 \end{proposition}
-\begin{proof} Take the following cube:
+\begin{proof} We can start considering the cube below and noticing that $n$, being the pushout of $m\in \mathcal{M}$, belongs to $\mathcal{A}$ too.
 	\[\xymatrix@C=13pt@R=13pt{&A\ar[dd]|\hole_(.65){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_{\id{B}} \\ A  \ar[dd]_{m}\ar[rr]^(.65){g} & & B \ar[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{f} & & D}\]
@@
 The left face is a pullback because $m$ is mono.
-Thus the Van Kampen property yields that the front and the right faces are pullbacks and the thesis follows.
-\qedhere
+Thus the $\mathcal{A}$-Van Kampen property yields that the front and the right faces are pullbacks.
 \end{proof}
@@
 The previous proposition, in turn, allows us to establish the following results.
-\begin{lemma}\label{lem:varie} Let $m:X\to Y$ be a monomorphism in a category $\X$ and suppose that the left square below is Van Kampen, while all the vertical faces in the right cube are pullbacks.
-		\[\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{f}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{g} &&D&&C \ar[rr]_{g} & & D}\]
-Supppose, moreover that $d:D'\to D$ is mono, then $d\leq n$ if and only if $c \leq m$.
+\begin{lemma}\label{lem:varie}Let $\mathcal{A}$ be a class of arrows stable under pullbacks, pushouts and containing all isomorphisms.
+Suppose that, the left square below is $\mathcal{A}$-Van Kampen, while the vertical faces in the right cube are pullbacks.
+		\[\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{g'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{g}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){f'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){g} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{f} &&D&&C \ar[rr]_{f} & & D}\]
+Supppose, moreover that $m:A\to C$ and $d:D'\to D$ are mono and that $d$ belongs to $\mathcal{A}$. Then $d\leq n$ if and only if $c \leq m$.
 \end{lemma}
+
 \begin{remark}
-	Recall that, given two monos $m:M\to X$ and $n:N\to X$ with the same codomain, $m\leq n$ means that there exists a, necessarily unique, $k:M\to N$ fitting in the triangle below:
-	\[\xymatrix{M\ar@{.>}[rr]^{k}  \ar[dr]_{m}&& N \ar[dl]^{n}\\ & X}\]
+	Recall that, given two monos $m:M\to X$ and $n:N\to X$ with the same codomain, $m\leq n$ means that there exists a, necessarily unique and necessarily mono, $k:M\to N$ fitting in the triangle below:
+	\[\xymatrix{M\ar[rr]^{k}  \ar[dr]_{m}&& N \ar[dl]^{n}\\ & X}\]
 	Notice that, if $m\leq n$ and $n\leq m$, then the arrow $k:M\to N$ is an isomorphism.  
@@
 \begin{remark}
-	Notice that, since $d$ is a mono and the front face a pullback, then $c$ is a monomorphism too.
+	Notice that, since $d$ is a mono and the vertical faces are pullbacks, then $a, b$ and $c$ are monomorphisms too. Moreover, $n$ is mono by \Cref{prop:pbpo}, so that even $m'$ and $n'$ are monos.
 \end{remark}
@@
 Thus there exists a unique $h:C'\to A$ as in the diagram below, implying the thesis.
-		\[\xymatrix@C=40pt{C'  \ar@{.>}[d]^{h}\ar[r]^{g'} \ar@/_.5cm/[dd]_{c}& D' \ar@/^.5cm/[dd]^{d}\ar[d]_{k}\\ A \ar[d]^{m} \ar[r]^{f} & B \ar[d]_{n} \\  C \ar[r]_g & D}\]
+		\[\xymatrix@C=40pt{C'  \ar[d]^{h}\ar[r]^{f'} \ar@/_.5cm/[dd]_{c}& D' \ar@/^.5cm/[dd]^{d}\ar[d]_{k}\\ A \ar[d]^{m} \ar[r]^{g} & B \ar[d]_{n} \\  C \ar[r]_f & D}\]
 
 	\smallskip \noindent 
-	$(\Leftarrow)$ Let $h:C\to A$ be such that $c=m\circ h$. By the Van Kampen property the top face of the given cube is a pushout. Thus the dotted $k:D'\to B$ in the following diagram exists.
-		\[\xymatrix@C=40pt{A' \ar@/_.5cm/[dd]_{a} \ar[d]^{m'} \ar[r]^{f'} & B' \ar[d]_{n'} \ar@/^.5cm/[dd]^{b} \\  C' \ar[d]^{h} \ar[r]_{g'} & D' \ar@{.>}[d]_{k}\\ A \ar[r]_f& B }\]
-	The thesis now follows at once. \qedhere 
-\end{proof}
-
-Finally, we can show that stable pushouts enjoy a kind of \emph{pullback-pushout decomposition} property.
-
-\begin{proposition}\label{prop:stab}Let $\X$ be a category  and suppose that, in the diagram below, the whole rectangle is a stable pushout and the right square a pullback.
+	$(\Leftarrow)$ Let $h:C\to A$ be such that $c=m\circ h$.
+By the $\mathcal{A}$-Van Kampen property the top face of the given cube is a pushout.
+Thus the dotted $k:D'\to B$ in the following diagram exists.
+		\[\xymatrix@C=40pt{A' \ar@/_.5cm/[dd]_{a} \ar[d]^{m'} \ar[r]^{g'} & B' \ar[d]_{n'} \ar@/^.5cm/[dd]^{b} \\  C' \ar[d]^{h} \ar[r]_{f'} & D' \ar@{.>}[d]_{k}\\ A \ar[r]_g& B }\]
+Moreover, by construction we have
+\[\begin{split}
+n\circ k \circ n' &= n\circ b\\&=d\circ n'\\&\\&
+\end{split} \qquad \begin{split}
+n\circ k \circ f' &= n\circ g\circ h\\&=f\circ m\circ h\\&=f\circ c\\&= d\circ f' \end{split}\]
+We can therefore conclude that $n\circ k =d$. \qedhere 
+\end{proof}
+
+Finally, we can show that $\mathcal{A}$-stable pushouts enjoy a kind of \emph{pullback-pushout decomposition} property.
+
+\begin{proposition}\label{prop:stab}Let $\X$ be a category and $\mathcal{A}$ a class of arrows stable under pullbacks.
+Suppose that, in the diagram below, the whole rectangle is an $\mathcal{A}$-stable pushout and the right square a pullback.
 	\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
-	If the arrow $k$ is a monomorphism,  then both squares are pushouts.
+	If the arrow $k$ is in $\mathcal{A}$ and it is a monomorphism,  then both squares are pushouts.
 \end{proposition}
 
-\begin{proof} We can begin noticinng that $g$, being the pullback of the monomorphism $k$, is monic too. Thus we can build the cube below, in which all the vertical faces are pullbacks.
+\begin{proof} We can begin noticing that $g$, being the pullback of $k$, is mono and in $\mathcal{A}$ too.
+Thus we can build the cube below, in which all the vertical faces are pullbacks, entailing that all the vertical arrows are in $\mathcal{A}$.
 	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y  \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
-	By hypothesis the face is a stable pushout and so its top one is a pushout. \Cref{lem:po1} now entails that the right half of the rectangle with which we have started is a pushout too. \qedhere 
+	By hypothesis the face is an $\mathcal{A}$-stable pushout and so its top one is a pushout.
+Using \Cref{lem:po1} we can conclude that the right half of the rectangle with which we have started is a pushout too.
+\qedhere
 \end{proof}
@@
 
-In this section we will define the notion of $\mathcal{M}, \mathcal{N}$-adhesivity and explore some of the consequence of such a property. Let us start fixing some terminology.
-
-\begin{definition}\
-	Let $\mathcal{M}$  be a class of arrows of a category $\X$. We say that  $\mathcal{M}$ is
-	\begin{itemize}
-		\item 
-		\emph{stable under pushouts (pullbacks)} if for every pushout (pullbacks) square 
-		\[\xymatrix{A\ar[r]^f  \ar[d]_{m}& B \ar[d]^n \\ C \ar[r]_g & D}\]
-		if $m \in \mathcal{M}$ ($n\in \mathcal{M}$) then $n \in \mathcal{M}$ ($m \in \mathcal{M}$);
-		\item \emph{closed under composition} if $g, f\in \mathcal{M}$ implies $g\circ f\in \mathcal{M}$ whenever $g$ and $f$ are composable;
-		\item \emph{closed under decomposition} if $g\circ f\in \mathcal{M}$ and $g\in \mathcal{M}$ implies $f\in \mathcal{M}$.
-	\end{itemize}
-\end{definition}
-
-\begin{remark}Clearly, ``decomposition'' corresponds to ``left cancellation'', but we prefer to stick to the name commonly used in literature.
-\end{remark}
-
-We are now ready to give the definition of $\mathcal{M}$-adhesive category	
-\begin{definition}[\cite{azzi2019essence,heindel2009category}]
-	Let $\X$ be a category and consider a subclass $\mathcal{M}$ of the class $\mathcal{M}(\X)$ of monomorphisms such that:
+In this section we will define the notion of $\mathcal{M}$-adhesivity \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,heindel2009category,lack2005adhesive} and explore some of the consequence of such a property.
+
+\begin{definition}[$\mathcal{M}$-adhesive category]
+	Let $\X$ be a category and consider a subclass $\mathcal{M}$ of the class $\mon(\X)$ of monomorphisms such that:
 	\begin{enumerate}
@@
 	\end{enumerate} 
-	We say that $\X$ is \emph{$\mathcal{M}$-adhesive} if
-	\begin{enumerate}
-		\item for every $m\colon X\to Y$ in $\mathcal{M}$ and $g\colon Z\to Y$, a pullback square
-		\[\xymatrix{P\ar[r]^p \ar[d]_{n}& X \ar[d]^{m}\\ Z \ar[r]_g& Y}\]
+	We will use $m\colon X\mto Y$ to denote that an arrow $m:X\to Y$ belongs to $\mathcal{M}$. $\X$ is said to be \emph{$\mathcal{M}$-adhesive} if
+	\begin{enumerate}
+		\item for every $m\colon X\mto Y$ in $\mathcal{M}$ and $g\colon Z\to Y$, a pullback square
+		\[\xymatrix{P\ar[r]^p \ar@{>->}[d]_{n}& X \ar@{>->}[d]^{m}\\ Z \ar[r]_g& Y}\]
 		exists, such pullbacks will be called \emph{$\mathcal{M}$-pullbacks};
-		\item for every $m\colon X\to Y$ in $\mathcal{M}$ and $n\colon X\to Z$, a pushout square
-		\[\xymatrix{X \ar[r]^n \ar[d]_{m}& Z \ar[d]^{q}\\ Y\ar[r]_p &Q}\]
+		\item for every $m\colon X\mto Y$ in $\mathcal{M}$ and $f\colon X\to Z$, a pushout square
+		\[\xymatrix{X \ar[r]^f \ar@{>->}[d]_{m}& Z \ar[d]^{q}\\ Y\ar[r]_p &Q}\]
 		exists, such pushouts  will be called \emph{$\mathcal{M}$-pushouts}; 
-		\item  $\mathcal{M}$-pushouts are Van Kampen squares.
-	\end{enumerate}
-\end{definition}
-
-\begin{remark}\label{rem:diff}Our notion of $\mathcal{M}$-adhesivity is slightly different from the one of \cite{azzi2019essence}: in that paper, $\mathcal{M}$ is assumed to be only stable under pullbacks.
-Notice, however, that if $\mathcal{M}$ contains all split monos, then stability under pushouts can be deduced from the other axioms \cite[Prop.~$5.1.21$]{castelnovo2023thesis}.
+		\item  $\mathcal{M}$-pushouts are $\mathcal{M}$-Van Kampen squares.
+	\end{enumerate}
+
+A category $\X$ is said to be \emph{strictly $\mathcal{M}$-adhesive} if $\mathcal{M}$-pushouts are Van Kampen squares.	
+\end{definition}
+
+\begin{remark}\label{rem:diff}Our notion of $\mathcal{M}$-adhesivity follows \cite{ehrig2012,ehrig2014adhesive} and is different from the one of \cite{azzi2019essence}.
+What is called $\mathcal{M}$-adhesivity in that paper corresponds to our strict $\mathcal{M}$-adhesivity.
+Moreover, in \cite{azzi2019essence} the class $\mathcal{M}$ is assumed to be only stable under pullbacks.
+However, if $\mathcal{M}$ contains all split monos, then stability under pushouts can be deduced from the other axioms \cite[Prop.~$5.1.21$]{castelnovo2023thesis}.
 \end{remark}
@@
 \begin{remark}\label{rem:salva} 
-	\emph{Adhesivity} and \emph{quasiadhesivity} as defined in \cite{lack2005adhesive,garner2012axioms}  coincide with  $\mathcal{A}(\X) $-adhesivity and $\mathcal{R}(\X)$-adhesivity, respectively. 
+	\emph{Adhesivity} and \emph{quasiadhesivity} as defined in \cite{lack2005adhesive,garner2012axioms}  coincide with  strict $\mon(\X) $-adhesivity and strict $\reg(\X)$-adhesivity, respectively. 
 \end{remark}
@@
 
-\begin{proposition}\label{prop:deco}Let  $\mathcal{M}$ be a class of monomorphisms containing all isomorphisms and stable under pullbacks.
-For every arrow $f: X\to Y$ and monomorphism $m: Y\to Z$, if $m\circ f \in\mathcal{M}$ then $f\in \mathcal{M}$.
+\begin{proposition}\label{prop:deco}Let  $\mathcal{A}$ be a class of arrows stable under pullbacks.
+For every arrow $f\colon X\to Y$ and monomorphism $m\colon Y\to Z$, if $m\circ f \in\mathcal{A}$ then $f\in \mathcal{A}$.
 \end{proposition}
@@
 		X \ar[r]_{f}& Y \ar[r]_{m} & Z}\]
-	Since $m$ is mono the right square is a pullback, the thesis now follows from \Cref{lem:pb1}.
+	Since $m$ is mono the right square is a pullback, while the left square is a pullback by construction. By \Cref{lem:pb1} the whole rectangle is a pullback and the thesis follows.
 \end{proof}
@@
 Let $m$ be an element of $\mathcal{M}$ and consider its pushout along itself.
-\[\xymatrix{X\ar[r]^m \ar[d]_m& Y\ar[d]^{f}\\Y \ar[r]_g & Z}\]
+\[\xymatrix{X\ar@{>->}[r]^m \ar@{>->}[d]_m& Y\ar@{>->}[d]^{f}\\Y \ar@{>->}[r]_g & Z}\]
 By \Cref{prop:pbpoad} this square is a pullback, proving that $m$ is the equalizer of the arrows $f,g\colon Y\rightrightarrows Z$. \qedhere 
@@
 $\mathcal{M}$-adhesivity is well-behaved with respect to  the comma construction \cite{mac2013categories}, as shown by the following theorem.
-\begin{theorem}[\cite{CastelnovoGM22,ehrig2006fundamentals,lack2005adhesive}]\label{lem:comma}
+\begin{theorem}[\cite{ehrig2006fundamentals,lack2005adhesive}]\label{lem:comma}
 	Let $\A$ and $\B$ be respectively an $\mathcal{M}$-adhesive and an $\mathcal{M}'$-adhesive category.
@@
 
-\begin{theorem}[\cite{CastelnovoGM22,ehrig2006fundamentals,lack2005adhesive}]\label{thm:functors}
+\begin{theorem}[\cite{ehrig2006fundamentals,lack2005adhesive}]\label{thm:functors}
 If $\X$ is an $\mathcal{M}$-adhesive category, then for every small category $\Y$, the category $\X^\Y$  of functors $\Y\to \X$ is $\mathcal{M}^{\Y}$-adhesive, where
@@
 
+\begin{example}
+	\todo{grafi semplici}
+\end{example}
+
 \begin{example}\todo{GRAFI GERARCHICI}
@@
 \begin{enumerate}
-	\item By \Cref{prop:stab}, it follows that both squares are pushouts.
-On the other hand, \Cref{prop:pbpoad} entails that the whole rectangle is a pullback, thus the thesis follows from \Cref{lem:pb1}.
-	\item By hypothesis, $g$ is the pullback of an arrow in $\mathcal{M}$, thus belongs to it.
+	\item By \Cref{prop:stab}, it follows that both squares are pushouts, thus the thesis follows from \Cref{prop:pbpoad}.
+	\item By hypothesis, $g$ is the pullback of an arrow in $\mathcal{M}$, thus it belongs to it.
 But then $g\circ f\in \mathcal{M}$ too  and the whole rectangle is a $\mathcal{M}$-pushout.
@@
 
-	Using \Cref{lem:po1}, it is enough to show that the left half of the original rectangle is a pushout. We can build the same cube of the previous point:
-	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y \ar[rrr]|(.67)\hole^{b} \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
-	Its vertical faces are all pullbacks, those the top one is a pushout and we can conclude. \qedhere 
+	Using \Cref{lem:po1}, it is enough to show that the left half of the original rectangle is a pushout. We can build the following cube:
+	\[\xymatrix@C=20pt@R=10pt{ & &X\ar@{>->}[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar@{>->}[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar@{>->}[ddd]_{g} \ar[rrr]^{b}&&& B\ar@{>->}[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar@{>->}[dl]_{f}&&& A \ar@{>->}[dl]^{h}\\ & Y \ar[rrr]|(.67)\hole^{b} \ar@{>->}[dl]_{g}&&& B \ar@{>->}[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
+	Its vertical faces are all pullbacks and all the vertical arrows are in $\mathcal{M}$, hence the top face is a pushout and we can conclude. \qedhere 
 \end{enumerate}
@@
 
-\begin{definition}
-Let $f:X\to Y$ and $g:Y\to Z$ ba two composable arrows in a category $\X$.
-A \emph{pushout complement} for the pair $(f,g)$ is a pair $(h,k)$ with $h:X\to W$ and $k:W\to Z$ such that the square below commutes and it is a pushout.
+\begin{definition}[Pushout complement]
+Let $f\colon X\to Y$ and $g\colon Y\to Z$ ba two composable arrows in a category $\X$.
+A \emph{pushout complement} for the pair $(f,g)$ is a pair $(h,k)$ with $h\colon X\to W$ and $k\colon W\to Z$ such that the square below commutes and it is a pushout.
 \[\xymatrix{X \ar[r]^{f} \ar[d]_{h}& Y \ar[d]^{g} \\ W \ar[r]_{k}& Z}\]
@@
 \begin{example}
-	In a generic category $\X$, pushout complements may not exist: in the  the category of $\Set$ the arrows $?_{2}:\emptyset \to 2$ and $!_2:2\to 1$ do not have a pushout complement.
-
-	Moreover, composable arrows $f:X\to Y$ and $g:Y\to Z$ may have  pushout complements which are non-isomorphic: for instance, in $\Set$ the two squares below are both pushouts.
+	In a generic category $\X$, pushout complements may not exist: in $\Set$ the arrows $?_{2}\colon \emptyset \to 2$ and $!_2\colon 2\to 1$ do not have a pushout complement.
+
+	Moreover, composable arrows $f\colon X\to Y$ and $g\colon Y\to Z$ may have  pushout complements which are non-isomorphic: for instance, in $\Set$ the two squares below are both pushouts.
 
@@
 Let $\X$ be a $\mathcal{M}$-adhesive category.
-Given $m:X\to Y$ in $\mathcal{M}$ and $n:Y\to Z$, let $(h_1, k_1)$ and $(h_2, k_2)$ be pushout complements of $m$  and $n$ and $W_1=\cod{h_1}$, $W_2=\cod{h_2}$.
-Then there exists a unique isomorphism $f:W_1\to W_2$ making the following diagram commutative.
-\[\xymatrix{&X \ar[r]^{m} \ar[d]_{h_1} \ar@/_.3cm/[ddl]_{h_2}& Y \ar[d]^{n} \\ &W_1 \ar@{.>}[dl]^{f} \ar[r]_{k_1} & Z \\ W_2 \ar@/_.3cm/[urr]_{k_2}}\]
+Given $m\colon X\mto Y$ in $\mathcal{M}$ and $n\colon Y\to Z$, let $(h_1, k_1)$ and $(h_2, k_2)$ be pushout complements of $m$  and $n$ and $W_1=\cod{h_1}$, $W_2=\cod{h_2}$.
+Then there exists a unique isomorphism $f\colon W_1\to W_2$ making the following diagram commutative.
+\[\xymatrix{&X \ar@{>->}[r]^{m} \ar[d]_{h_1} \ar@/_.3cm/[ddl]_{h_2}& Y \ar[d]^{n} \\ &W_1 \ar@{.>}[dl]^{f} \ar@{>->}[r]_{k_1} & Z \\ W_2 \ar@{>->}@/_.3cm/[urr]_{k_2}}\]
 
 \end{lemma}
-\begin{proof}
-	$k_1$ and $k_2$, being the pushout of $m$, are elements of $\mathcal{M}$ and thus are monomorphisms.
+\begin{proof} By hypothesis
+	$k_1$ and $k_2$, being the pushout of $m$, are elements of $\mathcal{M}$ and therefore are monomorphisms.
 In particular, $k_2$ is a monomorphism and this  entails at once the uniqueness of $f$.
 Moreover, notice that the squares
-	\[\xymatrix{X \ar[r]^{m} \ar[d]_{h_1}& Y \ar[d]^{n}& X \ar[d]_{h_2}\ar[r]^{m} & Y \ar[d]^{n}\\ W_1 \ar[r]_{k_1} & Z & W_2 \ar[r]_{k_2}& Z}\]
-	are $\mathcal{M}$-pushouts and thus Van Kampen.
-
-To prove the existence of the wanted $f$, we can start observing that $k_1$ and $k_2$, being the pushout of $m$, are elements of $\mathcal{M}$, so that we can consider the pullback square
-	\[\xymatrix{P\ar[r]^{p_1}  \ar[d]_{p_2}& W_1 \ar[d]^{k_1}\\ W_2 \ar[r]_{k_2} & Z}\]
-	Since $k_1\circ h_1=k_2\circ h_2$, there exists a unique $g: X\to P$ such that
-	\[p_1\circ g=h_1 \qquad p_2\circ g = h_2\]
+	\[\xymatrix{X \ar@{>->}[r]^{m} \ar[d]_{h_1}& Y \ar[d]^{n}& X \ar[d]_{h_2}\ar@{>->}[r]^{m} & Y \ar[d]^{n}\\ W_1 \ar@{>->}[r]_{k_1} & Z & W_2 \ar@{>->}[r]_{k_2}& Z}\]
+	are $\mathcal{M}$-pushouts and thus $\mathcal{M}$-Van Kampen.
+
+Now, take the $\mathcal{M}$-pullback square
+	\[\xymatrix{P\ar[r]^{p_1}  \ar[d]_{p_2}& W_1 \ar@{>->}[d]^{k_1}\\ W_2 \ar@{>->}[r]_{k_2} & Z}\]
+	Since $k_1\circ h_1=k_2\circ h_2$, there exists a unique $g\colon X\to P$ fitting in
+	\[\xymatrix{X \ar@/^.3cm/[drr]^{h_1} \ar@{.>}[dr]^{g} \ar@/_.3cm/[ddr]_{h_2}\\ &P\ar[r]^{p_1}  \ar[d]_{p_2}& W_1 \ar@{>->}[d]^{k_1}\\ &W_2 \ar@{>->}[r]_{k_2} & Z}\]
 	We can then build the cubes
-	\[\xymatrix@C=13pt@R=13pt{&X\ar[dd]|\hole_(.65){\id{X}}\ar[rr]^{g} \ar[dl]_{\id{X}} && P \ar[dd]^{p_1} \ar[dl]_{p_2} & &X\ar[dd]|\hole_(.65){\id{X}}\ar[rr]^{g} \ar[dl]_{\id{X}} && P \ar[dd]^{p_2} \ar[dl]_{p_1}\\ X  \ar[dd]_{m}\ar[rr]^(.65){h_2} & & W_2 \ar[dd]_(.3){k_2}& &  X  \ar[dd]_{m}\ar[rr]^(.65){h_1} & & W_1 \ar[dd]_(.3){k_1}\\&X\ar[rr]|\hole^(.65){h_1} \ar[dl]^{m} && W_1 \ar[dl]^{k_1} & &X\ar[rr]|\hole^(.65){h_2} \ar[dl]^{m} && W_2 \ar[dl]^{k_2}\\Y \ar[rr]_{n} & & Z & &Y \ar[rr]_{n} & & Z}\]
+	\[\xymatrix@C=13pt@R=13pt{&X\ar[dd]|\hole_(.65){\id{X}}\ar[rr]^{g} \ar[dl]_{\id{X}} && P \ar[dd]^{p_1} \ar[dl]_{p_2} & &X\ar[dd]|\hole_(.65){\id{X}}\ar[rr]^{g} \ar[dl]_{\id{X}} && P \ar[dd]^{p_2} \ar[dl]_{p_1}\\ X  \ar@{>->}[dd]_{m}\ar[rr]^(.65){h_2} & & W_2 \ar@{>->}[dd]_(.3){k_2}& &  X  \ar@{>->}[dd]_{m}\ar[rr]^(.65){h_1} & & W_1 \ar@{>->}[dd]_(.3){k_1}\\&X\ar[rr]|\hole^(.65){h_1} \ar@{>->}[dl]^{m} && W_1 \ar@{>->}[dl]^{k_1} & &X\ar[rr]|\hole^(.65){h_2} \ar@{>->}[dl]^{m} && W_2 \ar@{>->}[dl]^{k_2}\\Y \ar[rr]_{n} & & Z & &Y \ar[rr]_{n} & & Z}\]
 
@@
 Since $m\leq m$, \Cref{lem:varie} now entails that $k_1\leq k_2$ and $k_2\leq k_1$.
-Thus there exists an isomorphism $f:W_1\circ W_2$ such that $k_1=k_2\circ f$.
+Thus there exists an isomorphism $f\colon W_1\to W_2$ such that $k_1=k_2\circ f$.
 To see that $h_2=f\circ h_1$, we can compute:
@@
 	\end{align*}
-	The claim now follows since $k_2$ is a monomoprhism. \qedhere 
-\end{proof}
-
-\section{Double pushout rewriting and derivations}
-\todo{A VERY NICE INTRODUCTION}
+	The claim now follows since $k_2$ is a monomorphism. \qedhere 
+\end{proof}
+
+\section{DPO rewriting and derivations}
+
+$\mathcal{M}$-adhesive categories are the right context in which to perform abstract rewriting using the so-called ``douple pushout approach'' (DPO).
+We will recall the basic definitions and properties of this approach to abstract rewriting.
 
@@
 A \emph{left-linear DPO-rewriting system} is a pair $(\X, \R)$ where $\X$ is a $\mathcal{M}$-adhesive category and $R$ is a set of left $\mathcal{M}$-linear rules.
-$(\X, \R)$ will be called \emph{linear} if every rule in $R$ is so.
+$(\X, \R)$ will be called \emph{linear} if every rule in $R$ is $\mathcal{M}$-linear.
 
@@
 	The arrow $n$ is called the \emph{match} of the derivation, while $h$ is its \emph{back-match}.
-	We will denote a direct derivation $\dder{D}$ between $G$ and $H$ as $\dder{D}:G\Mapsto H$. W
+	We will denote a direct derivation $\dder{D}$ between $G$ and $H$ as $\dder{D}\colon G\Mapsto H$. 
 \end{definition}
@@
 
-\begin{remark}\label{exa:conc} Let  $\dder{D}:G\Mapsto H$ be the direct derivation 
+\begin{remark}\label{exa:conc} Let  $\dder{D}\colon G\Mapsto H$ be the direct derivation 
 		\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
-	If $\phi:G\to G'$ and $\psi:H\to H'$ are two isomorphisms, 	we can consider the direct derivation	$\phi * \dder{D}*\psi : G'\Mapsto H'$ given by the following diagram.
+	If $\phi\colon G\to G'$ and $\psi\colon H\to H'$ are two isomorphisms, 	we can consider the direct derivation	$\phi * \dder{D}*\psi \colon G'\Mapsto H'$ given by the following diagram.
 	\[\xymatrix{L \ar[d]_{\phi \circ n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{\psi \circ h}\\G' & \ar[l]^{\phi \circ f} D \ar[r]_{\psi \circ g}& H}\]
@@
 
-$\mathcal{M}$-adhesivity of $\X$ guarantess the essential uniqueness of the result obtained rewriting an object, as shown by the next proposition.
+$\mathcal{M}$-adhesivity of $\X$ guarantes the essential uniqueness of the result obtained rewriting an object, as shown by the next proposition.
 
@@
 Suppose that the two direct derivations $\mathscr{D}$ and $\mathscr{D'}$ below, with the same match and applying the same left $\mathcal{M}$-linear rule $\rho$ are given.
-	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L \ar[d]_{n}& K \ar[d]^{k'}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & G & \ar[l]^{f'} D' \ar[r]_{g'}& H'}\]
-Then there exist isomorphisms $t:D\to D'$ and $s:H\to H'$ as in the following diagram.
-\[\xymatrix@C=40pt{&&D' \ar[r]^{g'} \ar@/_.45cm/[dll]_{f'}&H'\\G & L \ar[l]_{n} & K \ar[u]_{k'} \ar[d]^{k}\ar[r]^{r} \ar[l]_{l} &R\ar[u]^{h'} \ar[d]_{h}\\&&D\ar@/^.45cm/[ull]^{f}\ar@/^.4cm/@{.>}[uu]^(.4){t}|\hole \ar[r]_{g}&H\ar@/_.4cm/@{.>}[uu]_{s}}\]
+	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L \ar[d]_{m}& K \ar[d]^{k'}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h'}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}& H & G & \ar@{>->}[l]^{f'} D' \ar[r]_{g'}& H'}\]
+Then there exist isomorphisms $t\colon D\to D'$ and $s\colon H\to H'$ as in the following diagram.
+\[\xymatrix@C=40pt{&&D' \ar[r]^{g'} \ar@{>->}@/_.45cm/[dll]_{f'}&H'\\G & L \ar[l]_{m} & K \ar[u]_{k'} \ar[d]^{k}\ar[r]^{r} \ar@{>->}[l]_{l} &R\ar[u]^{h'} \ar[d]_{h}\\&&D\ar@{>->}@/^.45cm/[ull]^{f}\ar@/^.4cm/@{.>}[uu]^(.4){t}|\hole \ar[r]_{g}&H\ar@/_.4cm/@{.>}[uu]_{s}}\]
 \end{proposition}
 \begin{proof}
-	By construction, the pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$ and $n$. Thus, the existence of the isomorphism $t:D\to D'$ follows from \Cref{lem:pocomp}. Now, computing we have
+	By construction, the pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$ and $n$.
+Thus, the existence of the isomorphism $t\colon D\to D'$ follows from \Cref{lem:pocomp}.
+Now, computing we have
 	\begin{align*}
@@
 	\end{align*}
-	Hence, we have the wanted $s:H\to H'$. To see that $s$ is an isomorphism, consider the diagram 
+	Hence, we have the wanted $s\colon H\to H'$. To see that $s$ is an isomorphism, consider the diagram 
 	\[\xymatrix{K  \ar@/^.4cm/[rr]^{k'}\ar[d]_{r} \ar[r]_{k}& \ar[r]_{t} D \ar[d]^{g}& D' \ar[d]^{g'}\\ R \ar@/_.4cm/[rr]_{h'} \ar[r]^{h}& H \ar[r]^{s}& H'}\]
@@
 \begin{definition}
-	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ $\mathcal{M}$-adhesive.
-The \emph{DPO-derivation graph} of $(\X, \R)$ is the (large)  directed graph $\gpo$ having as vertices the objects of $\X$ and in which an edge between $G$ and $H$ is a direct derivation $\dder{D}:G\Mapsto H$.	A \emph{derivation} $\der{D}$ between two objects $G$ and $H$ is a path between them in $\gpo$.
+	Let $(\X, \R)$ be a DPO-rewrityng system, with $\X$ $\mathcal{M}$-adhesive.
+The \emph{DPO-derivation graph} of $(\X, \R)$ is the (large)  directed graph $\gpo$ having as vertices the objects of $\X$ and in which an edge between $G$ and $H$ is a direct derivation $\dder{D}\colon G\Mapsto H$.	A \emph{derivation} $\der{D}$ between two objects $G$ and $H$ is a path between them in $\gpo$.
 \end{definition}
@@
 \begin{remark}\label{rem:func}
-	Consider a derivation $\der{D}$ in a left-linear DPO-rewriting system $(\X, \R)$.
+	Consider a derivation $\der{D}$ in a DPO-rewriting system $(\X, \R)$.
 We can take the subcategory $\Delta(\der{D})$ of $\X$ given by the arrows appearing in $\der{D}$.
-This subcategory comes equipped with an inclusion functor $I(\der{D}):\Delta(\der{D})\to \X$.
+This subcategory comes equipped with an inclusion functor $I(\der{D})\colon \Delta(\der{D})\to \X$.
 Moreover, we can further define $\Deltamin(\der{D})$ as the subcategory of $\Delta(\der{D})$ containing only the bottom row of the derivation.
@@
 	\[\xymatrix{L_i \ar[d]_{m_i}& K_i \ar[d]^{k_i}\ar[l]_{l_i} \ar[r]^{r_i} & R_i \ar[d]^{h_i} \\G_{i} & \ar[l]^{f_{i}} D_{i} \ar[r]_{g_{i}}& G_{i+1} }\]
-	Notice that, in particular, if $\der{D}:G\to H$, then $G_0=G$ and $G_{n+1}=H$.
+	Notice that, in particular, if $\der{D}\colon G\to H$, then $G_0=G$ and $G_{n+1}=H$.
 When $\der{D}$ has length $1$ we will suppress the indexes.
@@
 \begin{definition}
-	The \emph{DPO-derivation category} $\dpo$ of a left-linear DPO-rewriting system $(\X, \R)$ is the category in which arrows between $G$ and $H$ are given by, possibly empty, derivations.
+	The \emph{DPO-derivation category} $\dpo$ of a DPO-rewriting system $(\X, \R)$ is the category in which arrows between $G$ and $H$ are given by, possibly empty, derivations.
 Composition is concatenation of paths in $\gpo$ and identities are given by empty derivations.
@@
 \begin{definition} Let $(\X, \R)$ be a a left-linear DPO-rewriting system.
-Given a derivation $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ between $G$ and $H$ and isomorphisms $\phi: G\to G'$, $\psi:H\to H'$, the derivations  $\phi*\der{D}$ and $\der{D}*\psi$ are defined as
+Given a derivation $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ between $G$ and $H$ and isomorphisms $\phi\colon G\to G'$, $\psi\colon H\to H'$, the derivations  $\phi*\der{D}$ and $\der{D}*\psi$ are defined as
 	\[\phi *\der{D} := \begin{cases}
@@
 \begin{definition}\cite{mac2013categories}
-Let $\X$ be a category, we say that  $\X$ is \emph{skeletal} if, for every two objects $X$ and $Y$, the existence of an isomorphism $\phi:X\to Y$ entails $X=Y$.
+Let $\X$ be a category, we say that  $\X$ is \emph{skeletal} if, for every two objects $X$ and $Y$, the existence of an isomorphism $\phi\colon X\to Y$ entails $X=Y$.
 A \emph{skeleton} for a category $\X$ is a full subcategory $\ske$ which is skeletal and such that the inclusion functor $\ske\to \X$ is an equivalence.
@@
 \begin{remark}
-By definition the inclusion $\ske \to \X$ is an equivalence. In particular, this mean that, for every objects $X$ of $\X$ there exists $\pi(X)$ in $\ske$ and an isomorphism $\phi_X: \pi(X) \to X$.
+By definition the inclusion $\ske \to \X$ is an equivalence.
+In particular, this mean that, for every objects $X$ of $\X$ there exists $\pi(X)$ in $\ske$ and an isomorphism $\phi_X\colon \pi(X) \to X$.
 \end{remark}
@@
 	It is possible to proof that every two skeleta of a given category $\X$ are isomorphic (not only equivalent).
-For the remaining of this paper we assume that a skeleton $\ske$ of $\X$ and a functor $\pi:\X\to \ske$ are chosen once and for all.
+For the remaining of this paper we assume that a skeleton $\ske$ of $\X$ and a functor $\pi\colon \X\to \ske$ are chosen once and for all.
 \end{remark}
@@
 \begin{definition}
-	Let $(\X, \R)$ be a left-linear DPO-rewriting system, a \emph{decorated derivation} between two objects $G$ and $H$ is a triple $(\der{D}, \alpha, \omega)$, where $\der{D}$ is a derivation between $G$ and $H$, and $\alpha:\pi(G)\to G$ and $\omega:\pi(H)\to H$ are isomorphisms.
+	Let $(\X, \R)$ be a DPO-rewriting system, a \emph{decorated derivation} between two objects $G$ and $H$ is a triple $(\der{D}, \alpha, \omega)$, where $\der{D}$ is a derivation between $G$ and $H$, and $\alpha\colon \pi(G)\to G$ and $\omega\colon \pi(H)\to H$ are isomorphisms.
 \end{definition}
@@
 
-\begin{definition}Let $(\X, \R)$ be a left-linear DPO-rewriting system,  an \emph{abstraction equivalence} between two derivations $\der{D}$ and $\der{D'}$ with the same length and such that $r(\der{D})=r(\der{D}')$, is a family of isomorphisms $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ such that, for every $i\in [0, \lgh(\der{D})]$ the following diagram commutes
+\begin{definition}Let $(\X, \R)$ be a DPO-rewriting system,  an \emph{abstraction equivalence} between two derivations $\der{D}$ and $\der{D'}$ with the same length and such that $r(\der{D})=r(\der{D}')$, is a family of isomorphisms $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ such that, for every $i\in [0, \lgh(\der{D})]$ the following diagram commutes
 	\[\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i} \ar[l]_{f'}&G'_{i+1}\\  L_i \ar[u]^{n'_i} \ar[d]_{n_i}& K_i \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar[l]_{l_i} &R\ar[u]^{h'_i} \ar[d]_{h_i}\\G_i \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole \ar[r]_{g}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{H_i}}}\]
@@
 Let $(\der{D},\alpha, \omega)$ be an empty derivation from an object $G$ and  $(\der{D}',\alpha', \omega')$ a another empty one from $G'$.
-If $(\der{D},\alpha, \omega)\equiv_a(\der{D}',\alpha', \omega')$ then an abstraction equivalence between $\der(D)$ and $\der{D}'$ is just an isomorphism $\phi:G\to G'$, so that $\pi(G)=\pi(G')$.
+If $(\der{D},\alpha, \omega)\equiv_a(\der{D}',\alpha', \omega')$ then an abstraction equivalence between $\der(D)$ and $\der{D}'$ is just an isomorphism $\phi\colon G\to G'$, so that $\pi(G)=\pi(G')$.
 Moreover, such isomorphism must fit in the diagrams below.
@@
  \omega^{-1} \circ g_{\der{D}, n}&=\id{\pi(H)}\circ \omega^{-1} \circ g_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H \circ \omega\circ \omega^{-1} \circ g_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H  \circ g_{\der{D}, n}\\&= (\omega')^{-1} \circ g_{\der{D}', n}\circ \phi_{D_n}
-\end{align*}
+r\end{align*}
 and
@@
 \begin{definition}
-	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ an $\mathcal{M}$-adhesive category. The  category $\dpi$ is defined as follows:
+	Let $(\X, \R)$ be a DPO-rewrityng system, with $\X$ an $\mathcal{M}$-adhesive category. The  category $\dpi$ is defined as follows:
 	\begin{itemize}
@@
 		\item composition is concatenation of abstract decorated derivations;
-		\item the identity on $[G]$ is $[(G, \alpha, \alpha)]_a$, where $\alpha$ is any isomorphism $\pi(G)\to G$.	\end{itemize}
+		\item the identity on $[G]$ is $[G, \alpha, \alpha]_a$, where $\alpha$ is any isomorphism $\pi(G)\to G$.	\end{itemize}
 \end{definition}
@@
 
-Given a left-linear DPO-rewriting system $(\X, \R)$,  a derivation $\der{D}$  determines a diagram $\Delta(\der{D})$ in $\X$.
+Given DPO-rewriting system $(\X, \R)$,  we have already noted in \Cref{rem:func} that a derivation $\der{D}$  determines a diagram $\Delta(\der{D})$ in $\X$.
 We can then wonder if such a diagram has a colimit.
-Clealry if $\der{D}$ is the empty derivation then a colimit for $\Delta(\der{D})$ amount to an initial object in $\X$.
-If $\der{D}$ is non-empty we can use the following result.
+Clealry if $\der{D}$ is the empty derivation $G$ then a colimit for $\Delta(\der{D})$ is simply the object $G$.
+More generally, we have the following result.
 
 \begin{lemma}\label{lem:colim}
-	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO-rewriting system over it. The following hold true:
-	\begin{enumerate}
+	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO-rewriting system over it. The following hold true.
+	\begin{enumerate}
+		\item For every derivation $\der{D}=$ of length $n$ and for every $j\in[0,n-1]$, the outer boundary of following diagram is a pushout,
+		\[\xymatrix@C=30pt{D_{j} \ar[r]^{g_j}\ar@{>->}[d]_{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} \ar@{>->}@/^.3cm/[ddl]^{\iota'_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar[dd]^{p_2} \\ G_j \ar[d]_{\iota'_{G_j}}\\ \lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
+		where $\der{D}':=\{\dder{D}_i\}_{i=0}^{j-1}$, $\der{\hat{D}}:=\{\dder{D}_i\}_{i=j+1}^n$ and the two arrows $p_1\colon \lpro\der{D}' \rpro\to \tpro{D}$, $p_2\colon \lpro \der{\hat{D}}\rpro \to \tpro{D}$ are induced by the cocones $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}')})$ and $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}')})$, respectively.
+		\iffalse 
 		\item if $\der{D}$ is a derivation of length one, whose unique element is given by the following diagram
-	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G & \ar[l]^{f} D \ar[r]_{g}& H }\]	
-		then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists and  fits in the diagram below, where the bottom face is a pushout;
-		\[\xymatrix@R=10pt{&K\ar[dd]^{k}\ar[rr]^{r} \ar[dl]_{l} && R \ar[dd]^{h} \\ L  \ar[dd]_{m} \\&D\ar[rr]^{g} \ar[dl]_{f} && H \ar[dl]^{\iota_H} \\G \ar[rr]_{\iota_G} & & \tpro{D}}\]
-		\item  for every non-empty derivation $\der{D}$ from $G$ to $H$, the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belong to $\mathcal{M}$;
-		\item let $\der{D}$ be the concatenation $\der{D}_1\cdot \der{D}_2$ of two derivations $\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^{n_1}$ between $G$ and $H$ and $\der{D}_2=\{\dder{D}_{2,j}\}_{j=0}^{n_2}$ between $H$ and $T$,  then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists too and there is a pushout square
-		\[\xymatrix{H\ar[r]^-{\iota_{2, H}} \ar[d]_-{\iota_{1, H}} & \tproi{D}{2} \ar[d]^{p_2}\\  \tproi{D}{1} \ar[r]_{p_1}& \tpro{D}}\]
-		where $(\tproi{D}{1}, \{\iota_{1, X}\}_{X\in \Delta(\der{D}_1)})$ and $(\tproi{D}{2}, \{\iota_{2, X}\}_{X\in \Delta(\der{D}_2)})$ are the colimiting cocone for $\Delta(\der{D}_1)$ and $\Delta(\der{D}_2)$, respectively;
-		\item given a non-empty derivation $\der{D}=\{\dder{D}\}_{i=0}^n$ between $G$ and $H$, for every $j\in n+1$ different from $0$ the following diagram is a pushout
-		\[\xymatrix@C=30pt{D_{j} \ar[r]^{g_j}\ar[d]_{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} \ar@/^.3cm/[ddl]^{\iota'_{G_j}} & \lpro \der{\hat{D}}\rpro \ar[dd]^{p_2} \\ G_j \ar[d]_{\iota'_{G_j}}\\ \lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
-		where $\der{\hat{D}}=\{\dder{D}_i\}_{i=j+1}^n$, $\der{D}'=\{\dder{D}_i\}_{i=0}^j$ and $p_1:\lpro\der{D}' \rpro\to \tpro{D}$ and $p_2:\lpro \der{\hat{D}}\rpro \to \tpro{D}$ are the arrows induced by the cocones, $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}')})$ and $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}')})$, respectively.
+	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G & \ar@{>->}[l]^{f} D \ar[r]_{g}& H }\]	
+		Then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists, moreover the following square is an $\mathcal{M}$-pushout;
+		\[\xymatrix{ D\ar[r]^{g} \ar@{>->}[d]_{f} & H \ar[d]^{\iota_H} \\G \ar[r]_{\iota_G} &  \tpro{D}}\]
+		\fi
+
+		\item  If $\der{D}$ is a derivation from $G$ to $H$, then the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belongs to $\mathcal{M}$.
+
+		\item Let $\der{D}$ be the concatenation $\der{D}_1\cdot \der{D}_2$ of two derivations $\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^{n_1}$ between $G$ and $H$ and $\der{D}_2=\{\dder{D}_{2,j}\}_{j=0}^{n_2}$ between $H$ and $T$,  then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists too and there is a pushout square
+		\[\xymatrix{H\ar[r]^-{\iota_{2, H}} \ar@{>->}[d]_-{\iota_{1, H}} & \tproi{D}{2} \ar[d]^{p_2}\\  \tproi{D}{1} \ar[r]_{p_1}& \tpro{D}}\]
+		where $(\tproi{D}{1}, \{\iota_{1, X}\}_{X\in \Delta(\der{D}_1)})$ and $(\tproi{D}{2}, \{\iota_{2, X}\}_{X\in \Delta(\der{D}_2)})$ are the colimiting cocone for $\Delta(\der{D}_1)$ and $\Delta(\der{D}_2)$, respectively.
 	\end{enumerate}
 \end{lemma}
+\begin{remark}\label{rem:cof}
+	contenuto...
+\end{remark}
+
 \begin{remark}\label{rem:zero}
@@
 		\end{align*}
-		Hence, there exists a unique $c:P\to C$ such that $c\circ q= c_G$ and $c\circ p =c_H$. But these identities are enough to deduce that $(P, \{j_X\}_{X\in \Delta(\der{D})})$  is colimiting.
+		Hence, there exists a unique $c\colon P\to C$ such that $c\circ q= c_G$ and $c\circ p =c_H$. But these identities are enough to deduce that $(P, \{j_X\}_{X\in \Delta(\der{D})})$  is colimiting.
 		\item Let us proceed by induction.
@@
 Let also $\der{D}'$ be $\{\dder{D}_i\}^{n-1}_{i=0}$ and $\rho_n=(l_n, r_n)$ be the rule applied in $\dder{D}_n$.
-The pushout of $l_n$ is the arrow $f_n:D_n\to G_n$ is in $\mathcal{M}$ and, by inductive hypothesis, $\iota_{G_{n}}:G_{n}\to \lpro \der{D}'\rpro$ is in $\mathcal{M}$ too.
+The pushout of $l_n$ is the arrow $f_n\colon D_n\to G_n$ is in $\mathcal{M}$ and, by inductive hypothesis, $\iota_{G_{n}}\colon G_{n}\to \lpro \der{D}'\rpro$ is in $\mathcal{M}$ too.
 Thus, we can consider the diagram below, having a pushout as its lower half.
 			\[\xymatrix{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar[l]_{l_{n}} \ar[r]^{r_{n}} & R_{n} \ar[d]^{h_n} \\G_{n} \ar[d]_{\iota'_{G_{n}}}& \ar[l]^{f_n} D_n \ar[r]_{g_n}& H  \ar[d]^{q}\\ \lpro \der{D}' \ar[rr]_{p}\rpro && P}\]
-			Notice that, as in the point above, the arrow $q:H\to P$ is the pushout of an element in $\mathcal{M}$, therefore it is enough to show that the diagram so constructed provides a colimiting cocone for $\Delta(\der{D})$.
-
-			Let $(C, \{c_X\}_{X\in \Delta(\der{D})})$ be a cocone, since $\Delta(\der{D}')$ is a subdiagram of $\Delta(\der{D})$, we get another cocone $(c, \{c_X\}_{X\in \Delta(\der{D}')})$ which induces an arrow $c':\lpro \der{D}' \rpro \to C$ such that
+			Notice that, as in the point above, the arrow $q\colon H\to P$ is the pushout of an element in $\mathcal{M}$, therefore it is enough to show that the diagram so constructed provides a colimiting cocone for $\Delta(\der{D})$.
+
+			Let $(C, \{c_X\}_{X\in \Delta(\der{D})})$ be a cocone, since $\Delta(\der{D}')$ is a subdiagram of $\Delta(\der{D})$, we get another cocone $(c, \{c_X\}_{X\in \Delta(\der{D}')})$ which induces an arrow $c'\colon \lpro \der{D}' \rpro \to C$ such that
 			\begin{align*}
@@
 			\end{align*}
-			Therefore the arrows $c'$ and $c_H$ induce a morphism $c:P\to C$ and the thesis now follows at once.
+			Therefore the arrows $c'$ and $c_H$ induce a morphism $c\colon P\to C$ and the thesis now follows at once.
 		\end{itemize}
 		\item  As a first step, notice that $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D}_1)})$ and $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D}_2)})$ are cocone on, respectively, $\Delta(\der{D}_1)$ and $\Delta(\der{D}_2)$.
-Hence, there exist two arrows $p_1:\tproi{D}{1}\to \tpro{D}$, $p_2:\tproi{D}{2}\to \tpro{D}$ such that, for every $X\in  \Delta(\der{D}_1)$ and $Y\in  \Delta(\der{D}_2)$
+Hence, there exist two arrows $p_1\colon \tproi{D}{1}\to \tpro{D}$, $p_2\colon \tproi{D}{2}\to \tpro{D}$ such that, for every $X\in  \Delta(\der{D}_1)$ and $Y\in  \Delta(\der{D}_2)$
 		\[p_1\circ \iota_{1, X} = \iota_X \qquad p_2\circ \iota_{2, Y}=\iota_{2,Y}\]
@@
 
-	Let us now show that the square above is a pushout. Take two arrows $a:\tproi{D}{1}\to C$, $b:\tproi{D}{2}\to C$ such that
+	Let us now show that the square above is a pushout. Take two arrows $a\colon \tproi{D}{1}\to C$, $b\colon \tproi{D}{2}\to C$ such that
 	\[a\circ \iota_{1, H}=b\circ \iota_{2, H}\]
@@
 	\end{cases}\]
-From this, we can deduce at once the existence of a unique $c:\tpro{D}\to C$ such that 
+From this, we can deduce at once the existence of a unique $c\colon \tpro{D}\to C$ such that 
 \[c\circ \iota_X = c_X\]
@@
 
-	For uniqueness, suppose that $c':\tpro{D}\to C$ is such that
+	For uniqueness, suppose that $c'\colon \tpro{D}\to C$ is such that
 	\[c'\circ p_1=a \qquad c'\circ p_2 = b\]
@@
 
-\item Let $a:\lpro \der{\hat{D}}\rpro\to C$ , $b:\lpro \der{D}' \rpro\to C$ be two arrows fitting in the diagram 
+\item Let $a\colon \lpro \der{\hat{D}}\rpro\to C$ , $b\colon \lpro \der{D}' \rpro\to C$ be two arrows fitting in the diagram 
 	\[\xymatrix{D_{j} \ar[ddrr]^{\iota_{D_j}}\ar[r]^{g_j}\ar[d]_{f_j}& G_{j+1} \ar[r]^{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar@/^.4cm/[dddr]^{a} \ar[dd]^{p_2} \\ G_j \ar[d]_{\iota'_{G_j}}\\ \lpro \der{D}' \rpro \ar@/_.4cm/[rrrd]_{b} \ar[rr]_{p_1}  &&\tpro{D} \ar@{.>}[dr]^{c}\\ &&& C }\]
@@
 	\end{cases}\]
-	Thus we get a unique arrow $c:\tpro{D}\to C$ such that 
+	Thus we get a unique arrow $c\colon \tpro{D}\to C$ such that 
 	\[c\circ \iota_X = c_X\]
@@
 
-	To see that such $c$ is unique, suppose that $c':\tpro{D}\to C$ is given such that
+	To see that such $c$ is unique, suppose that $c'\colon \tpro{D}\to C$ is given such that
 	\[c'\circ p_1=b \qquad c'\circ p_2 = a\]
@@
 Let $j$ and $k$ be two indexes less or equal than $n+1$ and suppose that $j< k$.
-Consider two arrows $a:T\to G_j$, $b:T\to G_k$.
+Consider two arrows $a\colon T\to G_j$, $b\colon T\to G_k$.
 If $\iota_{G_j}\circ a = \iota_{G_k}\circ b$,
-	then  there exist arrow $c:T\to D_j $  such that \[f_j\circ c = a\qquad \iota_{D_j}\circ c =\iota_{G_k}\circ b\]
+	then  there exist arrow $c\colon T\to D_j $  such that \[f_j\circ c = a\qquad \iota_{D_j}\circ c =\iota_{G_k}\circ b\]
 	\end{corollary}
@@
 
-	 	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with assciated squence of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma:[0,n]\to [0,n]$  such that, for every $i\in [0,n]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma:\tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
+	 	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with assciated squence of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma\colon [0,n]\to [0,n]$  such that, for every $i\in [0,n]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
 	\[\xymatrix{\pi(G)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G \ar[r]^{\iota_{G}} &\tpro{D} \ar[d]^{\xi}&   \pi(H) \ar[r]^{\omega} \ar[d]_{\omega'} & H \ar[r]^{\iota_H} &\tpro{D} \ar[d]^{\xi}\\ G' \ar[rr]_{\iota'_{G'}} & &\lpro \der{D}' \rpro& H' \ar[rr]_{\iota'_{H'}} & &\lpro \der{D}' \rpro}\]
@@
 \begin{remark}\label{rem:inversa}
-Let $\sigma:[0,n]\to [0,n]$ be a consistent permutation between $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, then $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$: indeed, it is enough to consider, as mediating isomorphism, the inverse $\xi^{-1}_\sigma$ of $\xi_\sigma$.
+Let $\sigma\colon [0,n]\to [0,n]$ be a consistent permutation between $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, then $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$: indeed, it is enough to consider, as mediating isomorphism, the inverse $\xi^{-1}_\sigma$ of $\xi_\sigma$.
 \end{remark}
@@
 \begin{proposition}\label{prop:uniqu}
-	Let $\sigma,\sigma':[0,n]\rightrightarrows [0,n]$ be two consistent permutations between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.  Then the following hold true:
+	Let $\sigma,\sigma'\colon [0,n]\rightrightarrows [0,n]$ be two consistent permutations between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.  Then the following hold true:
 	\begin{enumerate}
@@
 
-Now, notice that, given a consistent permutation $\sigma$, $\xi_\sigma:\tpro{D}\to \lpro \der{D}'\rpro$, we already know, by \Cref{rem:coproj} that
+Now, notice that, given a consistent permutation $\sigma$, $\xi_\sigma\colon \tpro{D}\to \lpro \der{D}'\rpro$, we already know, by \Cref{rem:coproj} that
 \[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
@@
 But then \Cref{prop:uniqu} entails the following.
-\begin{corollary} Given a consistent permutation $\sigma$ between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, the mediating isomorphism $\xi_\sigma:\tpro{D}\to \lpro \der{D}'\rpro$ is unique.
+\begin{corollary} Given a consistent permutation $\sigma$ between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, the mediating isomorphism $\xi_\sigma\colon \tpro{D}\to \lpro \der{D}'\rpro$ is unique.
 \end{corollary}
@@
 \begin{lemma} Let $(\X,R)$ be a left-linear DPO-rewriting system.
-Consider two consistent permutation $\sigma,\sigma':[0,n]\rightrightarrows [0,n]$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
+Consider two consistent permutation $\sigma,\sigma'\colon [0,n]\rightrightarrows [0,n]$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
 Suppose that $\sigma\neq \sigma'$ and let $j$ be the minimum index such that $\sigma(j)\neq \sigma'(j)$.
@@
 		\[\xymatrix@C=40pt{& L_0 \ar[d]_{m'_{\sigma'(0)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{0}} \\G_{0} \ar@/_.2cm/[drr]_(.3){\iota_{G_0}}|(.515)\hole \ar[d]_{\iota_{G_0}}& G'_{\sigma'(0)} \ar[d]^{\iota_{G'_{\sigma'(0)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\sigma'}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
-	From \Cref{cor:ele}, we can conclude that there exists $c:L_0\to D_0$ such that $f_0\circ c=m_0$. We thus have the solid part of the commutative diagram below.
+	From \Cref{cor:ele}, we can conclude that there exists $c\colon L_0\to D_0$ such that $f_0\circ c=m_0$. We thus have the solid part of the commutative diagram below.
 		\[\xymatrix{L_0 \ar@/^.3cm/[drr]^{\id{L_0}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_0 \ar[d]_{k_0}\ar[r]^{l_0}& L_0 \ar[d]^{m_0} \\& D_0 \ar[r]_{f_0} & G_0} \]
-		The internal square is an $\mathcal{M}$-pushout and thus a pullback, by \Cref{prop:pbpoad}, so that we have the existence of the dotted $t:L_0\to K_0$.
+		The internal square is an $\mathcal{M}$-pushout and thus a pullback, by \Cref{prop:pbpoad}, so that we have the existence of the dotted $t\colon L_0\to K_0$.
 Therefore $\id{L_0}=l_0\circ t$, proving that $l_0$ is an epimorphism.
@@
 			\[\xymatrix@C=40pt{& L_{j-1} \ar[d]_{m'_{\sigma'(j-1)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{j-1}} \\G_{j-1} \ar@/_.2cm/[drr]_(.3){\iota_{G_{j-1}}}|(.515)\hole \ar[d]_{\iota_{G_{j-1}}}& G'_{\sigma'(j-1)} \ar[d]^{\iota_{G'_{\sigma'(j-1)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\sigma'}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
-			Let $a$ be $\min(j-1, k)$, by \Cref{cor:ele},  there exists $c:L_{j-1}\to D_a$ such that $f_a\circ c=m_a$. As before this yields the solid part of the following diagram
+			Let $a$ be $\min(j-1, k)$, by \Cref{cor:ele},  there exists $c\colon L_{j-1}\to D_a$ such that $f_a\circ c=m_a$. As before this yields the solid part of the following diagram
 			\[\xymatrix{L_{j-1} \ar@/^.3cm/[drr]^{\id{L_{j-1}}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_{j-1} \ar[d]_{k_a}\ar[r]^{l_{j-1}}& L_{j-1} \ar[d]^{m_a} \\& D_a \ar[r]_{f_a} & G_a} \]
-			The existence of the dotted $t:L_{j-1}\to K_{j-1}$ follows from  \Cref{prop:pbpoad} and we can conclude. \qed
+			The existence of the dotted $t\colon L_{j-1}\to K_{j-1}$ follows from  \Cref{prop:pbpoad} and we can conclude. \qed
 	\end{enumerate}
@@
 \begin{definition}  Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Let also $\dder{D}:G\Mapsto H$ and $\dder{D'}:H\Mapsto T$ be the two direct derivations depicted below.
+Let also $\dder{D}\colon G\Mapsto H$ and $\dder{D'}\colon H\Mapsto T$ be the two direct derivations depicted below.
 
@@
 
-An \emph{independence pair} between $\dder{D}$ and $\dder{D'}$, is a pair of  arrows $i_1:R\to D'$ and $i_2:L'\to D$ such that the following diagram commutes.
+An \emph{independence pair} between $\dder{D}$ and $\dder{D'}$, is a pair of  arrows $i_1\colon R\to D'$ and $i_2\colon L'\to D$ such that the following diagram commutes.
 
@@
 	On the other hand, 
-	 $f':D'\to H$ is  the pushout of $l':K'\to L'$ and so it is in $\mathcal{M}$, implying $j_1=i_1$.
-If, moreover, we suppose that the rule $\rho$ applied in $\dder{D}$ is linear, then $g:D\to H$ is in $\mathcal{M}$ too, hence, from the equation
+	 $f'\colon D'\to H$ is  the pushout of $l'\colon K'\to L'$ and so it is in $\mathcal{M}$, implying $j_1=i_1$.
+If, moreover, we suppose that the rule $\rho$ applied in $\dder{D}$ is linear, then $g\colon D\to H$ is in $\mathcal{M}$ too, hence, from the equation
 	 \begin{align*}
@@
 \begin{definition}\label{def:filler}
-Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ $\mathcal{M}$-adhesive. Let also $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ be the two derivations depicted below.
+Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ $\mathcal{M}$-adhesive. Let also $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$ be the two derivations depicted below.
 \[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
@@
 
-A \emph{filler} between $\dder{D}$ and $\dder{D}'$ is  given by a pair of arrows $u:K\to P$ and $u':K'\to P$ satisfying the following conditions
+A \emph{filler} between $\dder{D}$ and $\dder{D}'$ is  given by a pair of arrows $u\colon K\to P$ and $u'\colon K'\to P$ satisfying the following conditions
 \begin{enumerate}
@@
 \[\xymatrix{K' \ar[r]^{r'} \ar[d]_{u'}& R'\ar@{.>}[d]^{j'} \\ P \ar@{.>}[r]_{q'} & Q'}\]
-	\item  there exist arrows $i_1:R\to D'$, $i_2:L'\to D$ satisfying $f'\circ i_1=h$, $g\circ i_2=n'$ and such that the following squares are pushouts
+	\item  there exist arrows $i_1\colon R\to D'$, $i_2\colon L'\to D$ satisfying $f'\circ i_1=h$, $g\circ i_2=n'$ and such that the following squares are pushouts
 \[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar@{.>}[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar@{.>}[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
@@
 	\[\xymatrix{K \ar[r]^{l} \ar[d]_{u}& L\ar[d]^{j} \\ P \ar[r]_{q} & Q}\]
-	Moreover, the existence of the wanted $s:Q\to G$ and $t:Q'\to T$ follows from the following equalities
+	Moreover, the existence of the wanted $s\colon Q\to G$ and $t\colon Q'\to T$ follows from the following equalities
 	\[\begin{split}
@@
 
-\begin{definition} Let  $\dder{D}:H\Mapsto H$, $\dder{D}':H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system  $(\X, \R)$.
+\begin{definition} Let  $\dder{D}\colon H\Mapsto H$, $\dder{D}'\colon H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system  $(\X, \R)$.
 An independence pair $(i_1, i_2)$ between $\dder{D}$ and $\dder{D}'$ is \emph{good} if there exists a filler $(u,u')$ between them such that  the squares below are pushouts.\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
@@
 	\end{split}\]
-	Since the arrow $p:P\to D$, which is the pullback of $f'$, is in $\mathcal{M}$ we conclude that $(u,u')=(v,v')$.
+	Since the arrow $p\colon P\to D$, which is the pullback of $f'$, is in $\mathcal{M}$ we conclude that $(u,u')=(v,v')$.
 \end{remark}
@@
  \end{proposition}
-\begin{proof} Suppose that $\X$ is $\mathcal{M}$-adhesive and let $(i_1, i_2)$ be an independence pair between $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$. We have a diagram
+\begin{proof} Suppose that $\X$ is $\mathcal{M}$-adhesive and let $(i_1, i_2)$ be an independence pair between $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$. We have a diagram
 	\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
@@
 \end{split}\]
-Therefore the two dotted arrows $u:K\to P$ and $u':K'\to P$ exist. We have to show that they satisfy the two conditions in the definition of a filler. 
-\begin{enumerate}
-	\item  By construction $p\circ u = k$ and $p'\circ u'=k'$. Since $(\X, \R)$ is linear, then $r':K'\to R'$ belongs to $\mathcal{M}$, thus it admits a pushout along $u':K'\to P$, as wanted.
+Therefore the two dotted arrows $u\colon K\to P$ and $u'\colon K'\to P$ exist. We have to show that they satisfy the two conditions in the definition of a filler. 
+\begin{enumerate}
+	\item  By construction $p\circ u = k$ and $p'\circ u'=k'$. Since $(\X, \R)$ is linear, then $r'\colon K'\to R'$ belongs to $\mathcal{M}$, thus it admits a pushout along $u'\colon K'\to P$, as wanted.
 	\item Take the following two rectangles
@@
 
-Let $(i_1, i_2)$ be a good independence pair and consider the following diagram: the solid part exists by the definition of a filler, while the two new dotted arrows $v:Q\to J$ and $v':Q'\to J$ are obtained  as the pushout of $q:P\to Q$, which is in $\mathcal{M}$ by \Cref{rem:deco}, along $q':P\to Q'$.
+Let $(i_1, i_2)$ be a good independence pair and consider the following diagram: the solid part exists by the definition of a filler, while the two new dotted arrows $v\colon Q\to J$ and $v'\colon Q'\to J$ are obtained  as the pushout of $q\colon P\to Q$, which is in $\mathcal{M}$ by \Cref{rem:deco}, along $q'\colon P\to Q'$.
 	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@/_.8cm/[ddrr]_{j}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j'}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar[ul]_{s}\ar@{.>}[dr]_{v} &&Q'\ar[ur]^{t} \ar@{.>}[dl]^{v'}\\&&&J}\]
@@
 	Let $(\X,R)$ be a left-linear DPO-rewriting system and suppose that $\X$ is $\mathcal{M}$-adhesive.
-Given a good independence pair $(i_1, i_2)$ between $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, if $(u,u')$ is the associate filler, we define other two direct derivations $S_{i_1,i_2}(\dder{D}'):G\Mapsto J$ and $S_{i_1,i_2}(\dder{D}):J\Mapsto T$ as follows:
+Given a good independence pair $(i_1, i_2)$ between $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$, if $(u,u')$ is the associate filler, we define other two direct derivations $S_{i_1,i_2}(\dder{D}')\colon G\Mapsto J$ and $S_{i_1,i_2}(\dder{D})\colon J\Mapsto T$ as follows:
 		\[\xymatrix{L' \ar[d]_{f\circ i_2}& \ar[l]_{l'}K'\ar[d]_{q\circ u'} \ar[r]^{r'} & R' \ar[d]_{v'\circ j'} & L \ar[d]_{v\circ j} & \ar[l]_{l}K \ar[d]^{q'\circ u}\ar[r]^{r}& R \ar[d]^{g'\circ i_1}\\
@@
 \begin{remark}\label{rem:pbsalva}
-Let $(i_1,i_2)$ be a good independence pair between the derivation $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$.
+Let $(i_1,i_2)$ be a good independence pair between the derivation $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$.
 Let also $\der{\hat{D}}$ be the derivation consisting only in $S_{i_1,i_2}(\dder{D})$.
@@
 \begin{proposition}\label{prop:fil}Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Then every filler between two direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ is a filler also for $S_{u,u'}(\dder{D'}):G\Mapsto J$ and $S_{u,u'}(\dder{D}): J\Mapsto H$.
+Then every filler between two direct derivations $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$ is a filler also for $S_{u,u'}(\dder{D'})\colon G\Mapsto J$ and $S_{u,u'}(\dder{D})\colon J\Mapsto H$.
 In particular, if $\dder{D}\updownarrow \dder{D}'$, then $S_{u,u'}(\dder{D}')\updownarrow S_{u,u'}(\dder{D})$.
@@
 \begin{lemma}\label{lem:rev}
-	Let $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system $(\X, \R)$ and let $(i_1,i_2)$ be a good independence pair between them.
+	Let $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system $(\X, \R)$ and let $(i_1,i_2)$ be a good independence pair between them.
 Then $S_{j',j}(S_{i_1,i_2}(\dder{D}, \dder{D'}))$ is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
@@
 	\[\xymatrix{K' \ar[d]_{u'} \ar[r]^{l'}& L' \ar[d]^{c_2} & K \ar[r]^{r}\ar[d]_{u} & R \ar[d]^{c_1}\\ P \ar[r]_{e'} & E' & P\ar[r]_e & E}\]
-	are pushouts, we have isomorphisms  $\phi': D\to E'$, $\phi:D'\to E$ making the following diagrams commutative.
+	are pushouts, we have isomorphisms  $\phi'\colon D\to E'$, $\phi\colon D'\to E$ making the following diagrams commutative.
 	\[\xymatrix{K' \ar[d]_{u'} \ar[r]^{l'}& L'\ar[d]^{i_2}  \ar@/^.2cm/[dr]^{c_2} & &K \ar[r]^{r}\ar[d]_{u} & R \ar[d]^{i_1} \ar@/^.2cm/[dr]^{c_1}\\ P \ar@/_.4cm/[rr]_{e'}\ar[r]^{p} & D\ar@{.>}[r]^{\phi'} &E'& P\ar@/_.4cm/[rr]_{e}\ar[r]^{p'} & D'\ar@{.>}[r]^{\phi}& E}\]
@@
 But, by construction $s\circ j =n$ and we have already proved that $a\circ \phi'=f$.
-We then conclude that ther exists an isomorphism $\zeta:K\to K$ which makes the diagram below commutative
+We then conclude that ther exists an isomorphism $\zeta\colon K\to K$ which makes the diagram below commutative
 	\[\xymatrix{K \ar@{.>}[r]_{\zeta}\ar@/^.4cm/[rr]^{l}  \ar@/_.5cm/[dr]_{(\phi')^{-1} \circ e' \circ u}& K \ar[r]_{l} \ar[d]_{n} & L \ar[d]^{n} \\ & D \ar[r]_{f} & G}\]
@@
 
-	As a next step, notice the existence of $\phi$ and $\phi'$, together with \Cref{rem:deco}, entails  the existence of a third isomorphism $\psi:H\to F$ fitting in the diagram below.
+	As a next step, notice the existence of $\phi$ and $\phi'$, together with \Cref{rem:deco}, entails  the existence of a third isomorphism $\psi\colon H\to F$ fitting in the diagram below.
 	\[\xymatrix{P  \ar[d]^{p'}\ar@/_.4cm/[dd]_{e}\ar@/^.4cm/[rr]^{e'} \ar[r]_{p} & D \ar[d]^{g} \ar[r]_{\phi'} & E'\ar[d]^{w'}\\D' \ar[d]^{\phi} \ar[r]_{f'} & H\ar@{.>}[r]^{\psi} & F \\E \ar@/_.4cm/[urr]_{w}}\]
@@
 \begin{definition} Let $(\X, \R)$ be a left-linear DPO-rewriting system.
-Given two direct derivations $\dder{D}:G\Mapsto H$ and $\dder{D}':H\Mapsto T$, we say that  $\dder{D}$ and $\dder{D}'$ are \emph{properly switchable} if $\dder{D}\updownarrow_!
-\dder{D'}$ and $S_{i_1,i_2}(\dder{D}')\updownarrow_!S_{i_1,i_2}(\dder{D})$, where $(i_2,i_2)$ is a good independencepair betwwen $\dder{D}$ and $\dder{D}'$.
+Given two direct derivations $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$, we say that  $\dder{D}$ and $\dder{D}'$ are \emph{properly switchable} if $\dder{D}\updownarrow_!
+\dder{D'}$ and $S_{i_1,i_2}(\dder{D}')\updownarrow_!S_{i_1,i_2}(\dder{D})$, where $(i_2,i_2)$ is a good independence pair betwwen $\dder{D}$ and $\dder{D}'$.
 In such a case, we will write $\dder{D}\Updownarrow\dder{D}'$.
@@
 		\item If $\dder{D}$ and $\dder{D'}$ are two direct derivations such that $\dder{D}\updownarrow \dder{D'}$, then for every filler $(u,u')$ between them, the function
-		\[\tau:2\to2 \qquad x \mapsto \begin{cases}
+		\[\tau\colon 2\to2 \qquad x \mapsto \begin{cases}
 			1 & x=0\\
@@
 
-\subsection{Proper switchability is global}
+\begin{definition}[Very tameness]
+	\todo{very tame}
+\end{definition}
+
+\begin{remark}
+\todo{tutto coincide con tutto}
+\end{remark}
+
+\subsubsection{Graphical rewriting systems}
+\todo{ci sono un sacco di sistemi very tame}
+\subsection{On the globality of $\Updownarrow$}
 \todo{intro}
 
-\begin{lemma}\label{lem:iig1}Let $(\X,\R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$.
-If $(i_0,i_1)$ is a good independence pair between $\dder{D}_0$ and $\dder{D}_1$, $(a_1,a_2)$ one between $\dder{D}_1$ and $\dder{D}_2$ and $\dder{D}_0\updownarrow S_{a_1,a_2}(\dder{D}_2)$ with good independence pair $(e_0,e_1)$, then $S_{e_0,e_1}(\dder{D}_0)$ and $S_{a_1,a_2}(\dder{D}_1)$ are weakly sequentially independent.
+\begin{lemma}[Three steps Lemma]\label{lem:iig1}Let $(\X,\R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
+Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$ and suppose that $(i_0,i_1)$ is a good independence pair between $\dder{D}_0$ and $\dder{D}_1$, $(a_0,a_1)$ one between $\dder{D}_1$ and $\dder{D}_2$ and $(e_0, e_1)$ one between $\dder{D}_0$ and $S_{a_0,a_1}(\dder{D}_2)$.
+Then the following properties hold true.
+	\begin{enumerate}
+		\item $S_{e_0,e_1}(\dder{D}_0)$ and $S_{a_0,a_1}(\dder{D}_1)$ are weakly sequentially independent.
+		\item If $S_{i_0, i_1}(\dder{D}_0)\updownarrow_!
+\dder{D}_2$ with a good independence pair $(\alpha_0, \alpha_1)$, then  $S_{i_0,i_1}(\dder{D}_1)$ and $S_{\alpha_0, \alpha_1}(\dder{D}_2)$ are weakly sequentially independent.
+	\end{enumerate}
+
 \end{lemma}
-\begin{proof} We can use \Cref{def:filler,def:switch} to get some diagrams.  First of all, let $(v,v')$ be the filler between $\dder{D}_0$ and $\dder{D}_1$ associated to $(i_1, i_2)$, then we have
-			\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
-
-	Secondly, the filler $(u,u')$ induced by $(a_1, a_2)$ between $\dder{D}_1$ and $\dder{D}_2$ yields:
+\begin{proof}  As a preliminary step, we are going to use \Cref{def:filler,def:switch} to get some diagrams.
+First of all, let $(v,v')$ be the filler between $\dder{D}_0$ and $\dder{D}_1$ associated to $(i_0, i_1)$, then we have
+	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&H'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
+
+	Secondly, the filler $(u,u')$ induced by $(a_0, a_1)$ between $\dder{D}_1$ and $\dder{D}_2$ yields:
 	\[
-			\xymatrix{&&R_1 \ar@/_1cm/[ddrr]_(.35){a_1}|(.7)\hole \ar[dr]^{h_1}&& L_2\ar@/^1cm/[ddll]^(.35){a_2}  \ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar[dl]_{l_1} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){u}\ar[ur]^{r_1}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){u'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_1 \ar@/_.8cm/[ddrr]_(.2){b_1}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_1}|(.61)\hole && D_1 \ar[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){b_2}|(.31)\hole|(.81)\hole\ar[dl]_{h_2}\\&G_1 &&P_2\ar[dr]_{d_2} \ar[dl]^{d_1}\ar[ur]^(.4){c_2}\ar[ul]_(.4){c_1}&&G_2\\L_2 \ar@/^.8cm/[uurr]^(.2){a_2} \ar[ur]_(.35){f_1\circ a_2}|(.61)\hole&&Q_2 \ar[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1} &&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar[dl]|(.5)\hole_(.65){x_2} && R_1  \ar[ul]^(.35){g_2\circ a_1}|(.61)\hole\ar@/_.8cm/[uull]_(.2){a_1}\\&K_2 \ar[ur]_{d_1\circ u'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){u'}&&G'_2&& K_1 \ar[ur]_{r_1} \ar[ul]^{d_2\circ u} \ar[dl]^{l_1} \ar@/_.8cm/[uull]^(.65){u}\\&& R_2 \ar[ur]_{\hspace{-5pt}x_2\circ b_2}\ar@/^1cm/[uurr]^(.25){b_2}&& L_1 \ar[ul]^{y_1\circ b_1\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){b_1} |(.69)\hole }\]
-
-	Finally, the filler $(w,w')$  between $\dder{D}_0$ and $S_{u,u'}(\dder{D}_2)$ given by $(e_0, e_1)$ provides us with:
-			\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){e_0}|(.7)\hole \ar[dr]^{h_0}&& L_2\ar@/^1cm/[ddll]^(.35){e_1}  \ar[dl]_{f_1\circ a_2}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){w}\ar[ur]^{r_0}&& G_1 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){w'}\ar[dl]_{d_1\circ u'\hspace{-5pt}}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_0 \ar@/_.8cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2 \ar[dr]|(.4)\hole^(.65){y_1} \ar[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.8cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){x_2\circ b_2}\\&G_0 &&P_3\ar[dr]_{n_1} \ar[dl]^{n_0}\ar[ur]^(.4){u_1}\ar[ul]_(.4){u_0}&&G'_2\\L_2 \ar@/^.8cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ e_1}|(.61)\hole&&Q_4 \ar[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0} &&Q_5\ar[ur]|(.4)\hole^(.65){z'_1} \ar[dl]|(.5)\hole_(.65){z_1} && R_0  \ar[ul]^(.35){y_1\circ e_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){e_0}\\&K_2 \ar[ur]_{n_0\circ w'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){w'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{n_1\circ w} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){w}\\&& R_2 \ar[ur]_{\hspace{-4pt}z_1\circ o_1}\ar@/^1cm/[uurr]^(.25){o_1}&& L_0 \ar[ul]^{z'_0\circ o_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){o_0} |(.69)\hole }\]
-
-	We have to construct the two dotted arrows in the diagram below.
-			\[\xymatrix@C=15pt{L_0 \ar[d]_{z'_0\circ o_0}&& K_0 \ar[d]_{n_1\circ w}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@{.>}@/^.35cm/[drrr]_(.4){\alpha_1}|(.285)\hole \ar[dr]|(.28)\hole_{y_1\circ e_0} && L_1 \ar@{.>}@/_.35cm/[dlll]^(.4){\alpha_2} \ar[dl]|(.28)\hole^{y_1\circ b_1}& K_1 \ar[d]^{d_2\circ u}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ a_1}\\G'_1 && \ar[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2  && \ar[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_2}\]
-
-		Consider the arrows $i_0:R_0\to D_1$ and $e_0:R_0\to Q_2$. An easy computation shows that
+	\xymatrix{&&R_1 \ar@/_1cm/[ddrr]_(.35){a_0}|(.7)\hole \ar[dr]^{h_1}&& L_2\ar@/^1cm/[ddll]^(.35){a_1}  \ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar[dl]_{l_1} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){u}\ar[ur]^{r_1}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){u'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_1 \ar@/_.8cm/[ddrr]_(.2){b_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_1}|(.61)\hole && D_1 \ar[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){b_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_2}\\&G_1 &&P_2\ar[dr]_{d_1} \ar[dl]^{d_0}\ar[ur]^(.4){c_1}\ar[ul]_(.4){c_0}&&G_3\\L_2 \ar@/^.8cm/[uurr]^(.2){a_1} \ar[ur]_(.35){f_1\circ a_1}|(.61)\hole&&Q_2 \ar[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1} &&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar[dl]|(.5)\hole_(.65){x_2} && R_1  \ar[ul]^(.35){g_2\circ a_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){a_0}\\&K_2 \ar[ur]_{d_0\circ u'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){u'}&&G'_2&& K_1 \ar[ur]_{r_1} \ar[ul]^{d_1\circ u} \ar[dl]^{l_1} \ar@/_.8cm/[uull]^(.65){u}\\&& R_2 \ar[ur]_{\hspace{-5pt}x_2\circ b_1}\ar@/^1cm/[uurr]^(.25){b_1}&& L_1 \ar[ul]^{y_1\circ b_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){b_0} |(.69)\hole }\]
+
+	Finally, the filler $(w,w')$  between $\dder{D}_0$ and $S_{a_0,a_1}(\dder{D}_2)$ given by $(e_0, e_1)$ provides us with:
+\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){e_0}|(.7)\hole \ar[dr]^{h_0}&& L_2\ar@/^1cm/[ddll]^(.35){e_1}  \ar[dl]_{f_1\circ a_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){w}\ar[ur]^{r_0}&& G_1 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){w'}\ar[dl]_{d_0\circ u'\hspace{-5pt}}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_0 \ar@/_.8cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2 \ar[dr]|(.4)\hole^(.65){y_1} \ar[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.8cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){x_2\circ b_1}\\&G_0 &&P_3\ar[dr]_{n_1} \ar[dl]^{n_0}\ar[ur]^(.4){u_1}\ar[ul]_(.4){u_0}&&G'_2\\L_2 \ar@/^.8cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ e_1}|(.61)\hole&&Q_4 \ar[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0} &&Q_5\ar[ur]|(.4)\hole^(.65){z'_1} \ar[dl]|(.5)\hole_(.65){z_1} && R_0  \ar[ul]^(.35){y_1\circ e_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){e_0}\\&K_2 \ar[ur]_{n_0\circ w'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){w'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{n_1\circ w} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){w}\\&& R_2 \ar[ur]_{\hspace{-4pt}z_1\circ o_1}\ar@/^1cm/[uurr]^(.25){o_1}&& L_0 \ar[ul]^{z'_0\circ o_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){o_0} |(.69)\hole }\]
+So equipped we can turn to the prove of our claims.	
+	\begin{enumerate}
+		\item We have to construct the two dotted arrows in the diagram below.
+			\[\xymatrix@C=15pt{L_0 \ar[d]_{z'_0\circ o_0}&& K_0 \ar[d]_{n_1\circ w}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@{.>}@/^.35cm/[drrr]_(.4){\beta_0}|(.285)\hole \ar[dr]|(.28)\hole_{y_1\circ e_0} && L_1 \ar@{.>}@/_.35cm/[dlll]^(.4){\beta_1} \ar[dl]|(.28)\hole^{y_1\circ b_0}& K_1 \ar[d]^{d_1\circ u}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ a_1}\\G'_1 && \ar[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2  && \ar[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_3}\]
+
+		Consider the arrows $i_0\colon R_0\to D_1$ and $e_0\colon R_0\to Q_2$. An easy computation shows that
 			\begin{align*}
@@
 			\end{align*}
-			entailing the existence of  the dotted $\alpha'_1:R_0\to P_2$ in the diagram
-			\[\xymatrix{R_0 \ar@{.>}[dr]^{\alpha'_1} \ar@/^.3cm/[drr]^{i_0} \ar@/_.3cm/[ddr]_{e_0}\\ &P_2 \ar[r]^{c_2} \ar[d]_{d_1}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
-			If we define $\alpha_1:R_0\to Q_3$ as $d_2\circ \alpha'_1$, then we easily get that 
-		\begin{align*}
-			x_2\circ \alpha_1&=x_2\circ d_2\circ \alpha'_1\\&= y_1\circ d_1\circ \alpha'_1\\&=y_1\circ e_0
-		\end{align*}
-
-		For $\alpha_2$, we proceed similarly. First consider  $i_1:L_1\to D_0$ and $b_1: L_1 \to Q_2$ and notice that
-		\begin{align*}
-			g_0\circ i_1&= m_1 \\&= x_1 \circ b_1
-		\end{align*}
-			implying the existence of $\alpha'_2:L_1\to P_3$ fitting in the diagram below.
-			\[\xymatrix{L_1 \ar@{.>}[dr]^{\alpha'_2} \ar@/^.3cm/[drr]^{i_1} \ar@/_.3cm/[ddr]_{b_1}\\ &P_3 \ar[r]^{u_0} \ar[d]_{u_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar[r]_{x_1} & G_1}\] 
-			Let $\alpha_2:L_1\to Q_5$ be $n_1\circ \alpha'_2$, then
-			\begin{align*}
-				z'_1 \circ \alpha_2 & = z'_1 \circ n_1\circ \alpha'_2\\&=y_1\circ u_1\circ \alpha'_2\\&=y_1\circ b_1
-			\end{align*}
-			The thesis now follows.  
-\end{proof}
-
+			entailing the existence of  the dotted $\beta'_0\colon R_0\to P_2$ in the diagram
+			\[\xymatrix{R_0 \ar@{.>}[dr]^{\beta'_0} \ar@/^.3cm/[drr]^{i_0} \ar@/_.3cm/[ddr]_{e_0}\\ &P_2 \ar[r]^{c_1} \ar[d]_{d_0}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
+			If we define $\beta_0\colon R_0\to Q_3$ as $d_1\circ \beta'_1$, then we easily get that 
+		\begin{align*}
+			x_2\circ \beta_0&=x_2\circ d_2\circ \beta'_0\\&= y_1\circ d_0\circ \beta'_0\\&=y_1\circ e_0
+		\end{align*}
+
+		To define $\beta_1$, we proceed similarly. First consider  $i_1\colon L_1\to D_0$ and $b_0\colon L_1 \to Q_2$ and notice that
+		\begin{align*}
+			g_0\circ i_1&= m_1 \\&= x_1 \circ b_0
+		\end{align*}
+			implying the existence of $\beta'_1\colon L_1\to P_3$ fitting in the diagram below.
+			\[\xymatrix{L_1 \ar@{.>}[dr]^{\beta'_1} \ar@/^.3cm/[drr]^{i_1} \ar@/_.3cm/[ddr]_{b_0}\\ &P_3 \ar[r]^{u_0} \ar[d]_{u_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar[r]_{x_1} & G_1}\] 
+			Let $\beta_1\colon L_1\to Q_5$ be $n_1\circ \beta'_1$, then
+			\begin{align*}
+				z'_1 \circ \beta_1 & = z'_1 \circ n_1\circ \beta'_1\\&=y_1\circ u_1\circ \beta'_1\\&=y_1\circ b_0
+			\end{align*}
+		Therefore, $(\beta_0, \beta_1)$ is the wanted independence pair.
+
+\item  In addition to the three diagram above, we have a fourth one given by the filler $(\varphi_0, \varphi_1)$ associated to $(\alpha_0, \alpha_1)$. 
+\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){\alpha_0}|(.7)\hole \ar[dr]^{g_1\circ i_0}&& L_2\ar@/^1cm/[ddll]^(.35){\alpha_1}  \ar[dl]_{m_2}\\
+&K_0\ar[dr]^{\hspace{-4pt}q_1\circ v}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){\varphi}\ar[ur]^{r_0}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){\varphi'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\
+L_0 \ar@/_.8cm/[ddrr]_(.2){\gamma_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){\hspace{-4pt}t_0\circ j_0}|(.61)\hole && Q_1 \ar[dl]|(.4)\hole_(.65){s_1}\ar[ur]|(.5)\hole^(.7){t_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){\gamma_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){h_2}\\&H'_1 &&P_4\ar[dr]_{\lambda_1} \ar[dl]^{\lambda_0}\ar[ur]^(.4){\zeta_1}\ar[ul]_(.4){\zeta_0}&&G_3\\
+L_2 \ar@/^.8cm/[uurr]^(.2){\alpha_1} \ar[ur]_(.35){s_1\circ \alpha_1}|(.61)\hole&&Q_6 \ar[ul]|(.4)\hole_(.65){\xi_0}\ar[dr]|(.5)\hole^(.65){\xi'_0} &&Q_7\ar[ur]|(.4)\hole^(.65){\xi'_1} \ar[dl]|(.5)\hole_(.65){\xi_1} && R_0  \ar[ul]^(.35){g_2\circ \alpha_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){\alpha_0}\\&K_2 \ar[ur]_{\lambda_0\circ \phi'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){\phi'}&&H'_2&& K_0 \ar[ur]_{r_0} \ar[ul]^{\lambda_1\circ \phi} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){\phi}\\&& R_2 \ar[ur]_{\hspace{-4pt}\xi_1\circ \gamma_1}\ar@/^1cm/[uurr]^(.25){\gamma_1}&& L_0 \ar[ul]^{\xi'_0\circ \gamma_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){\gamma_0} |(.69)\hole }\]
+
+Our aim is to construct the dotted arrow in the following diagram.
+		\[\xymatrix@C=15pt{L_1 \ar[d]_{f_0\circ i_0}&& K_1 \ar[d]_{q_0\circ v'}\ar[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@{.>}@/^.35cm/[drrr]_(.4){\epsilon_0}|(.285)\hole \ar[dr]|(.28)\hole_{s_1\circ j_1} && L_2 \ar@{.>}@/_.35cm/[dlll]^(.4){\epsilon_1} \ar[dl]|(.28)\hole^{s_1\circ \alpha_1}& K_2 \ar[d]^{\lambda_0\circ \phi'}\ar[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]^{\xi_1\circ \gamma_1}\\G_0 && \ar[ll]^{s_0} Q_0 \ar[rr]_{t_0}&& H'_1  && \ar[ll]^{\xi_0} Q_6 \ar[rr]_{\xi'_0}&& H'_2}\]
+
+Let us start considering $j_1\colon R_1\to Q_1$ and $a_0\colon R_1\to D_2$. We have
+\begin{align*}
+	f_2\circ a_0&=h_1\\&=t_1\circ j_1
+\end{align*}
+and thus we get an arrow $\epsilon'_0\colon R_1\to P_4$ which makes the diagram below commutative.
+			\[\xymatrix{R_1 \ar@{.>}[dr]^{\epsilon'_0} \ar@/^.3cm/[drr]^{j_1} \ar@/_.3cm/[ddr]_{a_0}\\ &P_4 \ar[r]^{\zeta_0} \ar[d]_{\zeta_1}& Q_1 \ar[d]^{t_1}\\ &D_2\ar[r]_{f_2} & G_2}\] 
+We can then define $\epsilon_0\colon R_1\to Q_6$ to be $\lambda_0\circ \epsilon'_0$. For such an arrow we have a chain of identities:
+\begin{align*}
+	\xi_0\circ \epsilon_0&=\xi_0\circ \lambda_0\circ \epsilon'_0\\&=s_1\circ \zeta_0 \circ \epsilon'_0\\&=s_1\circ j_1
+\end{align*}
+
+Next, to define $\epsilon_1\colon L_2\to Q_0$ we take $e_1\colon L_2 \to D_0$ and $a_1\colon L_2\to D_1$. By definition we have $	g_0\circ e_1=f_1\circ a_1$, giving us the dotted arrow below
+	\[\xymatrix{L_2 \ar@{.>}[dr]^{\epsilon'_1} \ar@/^.3cm/[drr]^{a_1} \ar@/_.3cm/[ddr]_{e_0}\\ &P_1 \ar[r]^{p_1} \ar[d]_{p_0}& D_1 \ar[d]^{f_1}\\ &D_0\ar[r]_{g_0} & G_1}\] 
+Now, notice that 
+\begin{align*}
+	t_1\circ q_1\circ \epsilon'_1&=g_1\circ p_1\circ \epsilon'_1&=g_1\circ a_1\\&=m_2
+\end{align*}
+Hence $(\alpha_0, q_1\circ \epsilon'_1)$ is an independence pair for $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$.
+By hypothesis $S_{i_0, i_1}(\dder{D}_0)\updownarrow_!
+\dder{D}_2$ and thus $q_1\circ \epsilon'_1$ must coincide with $\alpha_1$.
+Now, let $\epsilon_1\colon L_2\to Q_0$ be $q_0\circ \epsilon'_1$.
+Computing we get
+\begin{align*}
+t_0\circ \epsilon_1&= t_0\circ q_0\circ \epsilon'_1\\&=s_1\circ q_1\circ \epsilon'_1\\&=s_1\circ \alpha_1
+\end{align*}
+Allowing us to conclude that  $S_{i_0,i_1}(\dder{D}_1)\updownarrow S_{\alpha_0, \alpha_1}(\dder{D}_2)$.
+\qedhere 
+			\end{enumerate}
+\end{proof}
+\iffalse 
 \begin{corollary} Given a tame  left-linear DPO-rewriting system  $(\X,\R)$ with $\X$ an $\mathcal{M}$-adhesive category and a decorated derivation $(\der{D}, \alpha, \omega)$ with $\der{D}=\{\dder{D}_i\}_{i=0}^2$.
@@
 Let also $\der{E}$ be the derivation $S_{e_0, e_1}(S_{a_1, a_2}(\der{D}_2))\cdot S_{e_0, e_1}(\dder{D}_0) \cdot S_{a_1, a_2}(\der{D}_1)$.
-Let $\sigma:[0,2]\to [0,2]$ be the cycle $(0,1,2)$.
+Let $\sigma\colon [0,2]\to [0,2]$ be the cycle $(0,1,2)$.
 By \Cref{lem:consperm} we know that $\sigma$ is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{E}, \alpha, \omega)$.
@@
 		\end{align*}
-		Using	\Cref{rem:pbsalva} we can deduce the existence of a unique arrow $\beta'_2:L_1\to P_3$ fitting in the diagram below
+		Using	\Cref{rem:pbsalva} we can deduce the existence of a unique arrow $\beta'_2\colon L_1\to P_3$ fitting in the diagram below
 		\[\xymatrix@C=30pt{L_1  \ar@/^.3cm/[drr]^{\beta_2} \ar@/_.3cm/[ddr]_{i_1}\ar@{.>}[dr]^{\beta'_2}\\& P_3 \ar[r]^{n_1}  \ar[d]_{u_0}& Q_5 \ar[d]^{\iota_{\dder{E}, Q_5}}\\
@@
 
- We need another lemma, similar to \Cref{lem:iig1}.
-\begin{lemma}\label{lem:iig2}\todo{nell'altro senso}
+ \todo{mettere esempio del perché fallisce nell'altra direziome}
+ \todo{anche una breve intro}
+
+\begin{lemma}\label{lem:iig2}Let $(\X,\R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
+For every derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$, if $(i_0,i_1)$ is a good independence pair between $\dder{D}_0$ and $\dder{D}_1$, $(a_1,a_2)$ one between $\dder{D}_1$ and $\dder{D}_2$ and $\dder{D}_0\updownarrow S_{a_1,a_2}(\dder{D}_2)$ with good independence pair $(e_0,e_1)$, then $S_{e_0,e_1}(\dder{D}_0)$ and $S_{a_1,a_2}(\dder{D}_1)$ are weakly sequentially independent.
 \end{lemma}
-\begin{proof}
- \todo{fare} \qedhere 
-\end{proof}
-
-\begin{corollary}
-\todo{passare a $\updownarrow_!$ e $\Updownarrow$}
-\end{corollary}
-
-\begin{corollary}[Invariance under immediate shift]\label{cor:ius}
-	contenuto...
-\end{corollary}
-
-\todo{ricopiare tutta l'induzione di Andrea}
+\begin{proof} As in the proof of \Cref{lem:iig1}, \Cref{def:filler,def:switch} yield to us some diagrams.
+First of all, let $(v,v')$ be the filler between $\dder{D}_0$ and $\dder{D}_1$ associated to $(i_1, i_2)$, then we have
+	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
+
+	Secondly, the filler $(u,u')$ induced by $(a_1, a_2)$ between $\dder{D}_1$ and $\dder{D}_2$ yields:
+	\[
+	\xymatrix{&&R_1 \ar@/_1cm/[ddrr]_(.35){a_1}|(.7)\hole \ar[dr]^{h_1}&& L_2\ar@/^1cm/[ddll]^(.35){a_2}  \ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar[dl]_{l_1} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){u}\ar[ur]^{r_1}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){u'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_1 \ar@/_.8cm/[ddrr]_(.2){b_1}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_1}|(.61)\hole && D_1 \ar[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){b_2}|(.31)\hole|(.81)\hole\ar[dl]_{h_2}\\&G_1 &&P_2\ar[dr]_{d_2} \ar[dl]^{d_1}\ar[ur]^(.4){c_2}\ar[ul]_(.4){c_1}&&G_2\\L_2 \ar@/^.8cm/[uurr]^(.2){a_2} \ar[ur]_(.35){f_1\circ a_2}|(.61)\hole&&Q_2 \ar[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1} &&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar[dl]|(.5)\hole_(.65){x_2} && R_1  \ar[ul]^(.35){g_2\circ a_1}|(.61)\hole\ar@/_.8cm/[uull]_(.2){a_1}\\&K_2 \ar[ur]_{d_1\circ u'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){u'}&&G'_2&& K_1 \ar[ur]_{r_1} \ar[ul]^{d_2\circ u} \ar[dl]^{l_1} \ar@/_.8cm/[uull]^(.65){u}\\&& R_2 \ar[ur]_{\hspace{-5pt}x_2\circ b_2}\ar@/^1cm/[uurr]^(.25){b_2}&& L_1 \ar[ul]^{y_1\circ b_1\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){b_1} |(.69)\hole }\]
+
+	Finally, the filler $(w,w')$  between $\dder{D}_0$ and $S_{u,u'}(\dder{D}_2)$ given by $(e_0, e_1)$ provides us with:
+	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){e_0}|(.7)\hole \ar[dr]^{h_0}&& L_2\ar@/^1cm/[ddll]^(.35){e_1}  \ar[dl]_{f_1\circ a_2}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){w}\ar[ur]^{r_0}&& G_1 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){w'}\ar[dl]_{d_1\circ u'\hspace{-5pt}}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_0 \ar@/_.8cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2 \ar[dr]|(.4)\hole^(.65){y_1} \ar[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.8cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){x_2\circ b_2}\\&G_0 &&P_3\ar[dr]_{n_1} \ar[dl]^{n_0}\ar[ur]^(.4){u_1}\ar[ul]_(.4){u_0}&&G'_2\\L_2 \ar@/^.8cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ e_1}|(.61)\hole&&Q_4 \ar[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0} &&Q_5\ar[ur]|(.4)\hole^(.65){z'_1} \ar[dl]|(.5)\hole_(.65){z_1} && R_0  \ar[ul]^(.35){y_1\circ e_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){e_0}\\&K_2 \ar[ur]_{n_0\circ w'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){w'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{n_1\circ w} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){w}\\&& R_2 \ar[ur]_{\hspace{-4pt}z_1\circ o_1}\ar@/^1cm/[uurr]^(.25){o_1}&& L_0 \ar[ul]^{z'_0\circ o_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){o_0} |(.69)\hole }\]
+
+	We have to construct the two dotted arrows in the diagram below.
+	\[\xymatrix@C=15pt{L_0 \ar[d]_{z'_0\circ o_0}&& K_0 \ar[d]_{n_1\circ w}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@{.>}@/^.35cm/[drrr]_(.4){\alpha_1}|(.285)\hole \ar[dr]|(.28)\hole_{y_1\circ e_0} && L_1 \ar@{.>}@/_.35cm/[dlll]^(.4){\alpha_2} \ar[dl]|(.28)\hole^{y_1\circ b_1}& K_1 \ar[d]^{d_2\circ u}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ a_1}\\G'_1 && \ar[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2  && \ar[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_2}\]
+
+	Consider the arrows $i_0\colon R_0\to D_1$ and $e_0\colon R_0\to Q_2$. An easy computation shows that
+	\begin{align*}
+		f_1\circ i_0&= h_0\\&=x_1\circ e_0
+	\end{align*}
+	entailing the existence of  the dotted $\alpha'_1\colon R_0\to P_2$ in the diagram
+	\[\xymatrix{R_0 \ar@{.>}[dr]^{\alpha'_1} \ar@/^.3cm/[drr]^{i_0} \ar@/_.3cm/[ddr]_{e_0}\\ &P_2 \ar[r]^{c_2} \ar[d]_{d_1}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
+	If we define $\alpha_1\colon R_0\to Q_3$ as $d_2\circ \alpha'_1$, then we easily get that 
+	\begin{align*}
+		x_2\circ \alpha_1&=x_2\circ d_2\circ \alpha'_1\\&= y_1\circ d_1\circ \alpha'_1\\&=y_1\circ e_0
+	\end{align*}
+
+	For $\alpha_2$, we proceed similarly. First consider  $i_1\colon L_1\to D_0$ and $b_1\colon L_1 \to Q_2$ and notice that
+	\begin{align*}
+		g_0\circ i_1&= m_1 \\&= x_1 \circ b_1
+	\end{align*}
+	implying the existence of $\alpha'_2\colon L_1\to P_3$ fitting in the diagram below.
+	\[\xymatrix{L_1 \ar@{.>}[dr]^{\alpha'_2} \ar@/^.3cm/[drr]^{i_1} \ar@/_.3cm/[ddr]_{b_1}\\ &P_3 \ar[r]^{u_0} \ar[d]_{u_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar[r]_{x_1} & G_1}\] 
+	Let $\alpha_2\colon L_1\to Q_5$ be $n_1\circ \alpha'_2$, then
+	\begin{align*}
+		z'_1 \circ \alpha_2 & = z'_1 \circ n_1\circ \alpha'_2\\&=y_1\circ u_1\circ \alpha'_2\\&=y_1\circ b_1
+	\end{align*}
+	The thesis now follows.  
+\end{proof}
+\fi
+
 \subsection{Concatenable traces}
@@
 
-\section{On rewriting systems on $\Set$.}\label{app:set}
+\section{Rewriting systems on $\Set$.}\label{app:set}
+
+\section{Full proof of \Cref{thm:crit}}
 

### 2023-12-12 fusione.tex
pulizia

@@
 \newcommand{\smallmin}{\scaleobj{0.6}{-}}
-\newcommand{\Deltamin}{\Delta^{\hspace{-2pt}\begin{matrix}
-			\smallmin\\
-		\end{matrix}} \hspace{-1pt}}
+\newcommand{\Deltamin}{\Delta^{\hspace{-1pt}\downarrow\hspace{-1pt}}}
 \newcommand{\Rrel}[1]   {\stackrel{{#1}}{\Longrightarrow}}
@@
 The \emph{DPO-derivation graph} of $(\X, \R)$ is the (large)  directed graph $\gpo$ having as vertices the objects of $\X$ and in which an edge between $G$ and $H$ is a direct derivation $\dder{D}\colon G\Mapsto H$.	A \emph{derivation} $\der{D}$ between two objects $G$ and $H$ is a path between them in $\gpo$.
+The \emph{source} and \emph{target} of $\der{D}$ are, respectively, $G$ and $H$.
 \end{definition}
@@
 
+\begin{notation}
+	We will extend the use of the words length, source and target to decorated derivations in the obvious way, forgetting the decorations $\alpha$ and $\omega$.
+\end{notation}
+
 \begin{example}A decorated derivation $(\der{D}, \alpha, \omega)$ with $\der{D}$ empty is just a span
@@
 \begin{definition}Let $(\X, \R)$ be a DPO-rewriting system,  an \emph{abstraction equivalence} between two derivations $\der{D}$ and $\der{D'}$ with the same length and such that $r(\der{D})=r(\der{D}')$, is a family of isomorphisms $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ such that, for every $i\in [0, \lgh(\der{D})]$ the following diagram commutes
-	\[\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i} \ar[l]_{f'}&G'_{i+1}\\  L_i \ar[u]^{n'_i} \ar[d]_{n_i}& K_i \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar[l]_{l_i} &R\ar[u]^{h'_i} \ar[d]_{h_i}\\G_i \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole \ar[r]_{g}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{H_i}}}\]
+	\[\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i} \ar[l]_{f'_i}&G'_{i+1}\\  L_i \ar[u]^{n'_i} \ar[d]_{n_i}& K_i \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar[l]_{l_i} &R\ar[u]^{h'_i} \ar[d]_{h_i}\\G_i \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole \ar[r]_{g_i}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{H_i}}}\]
 
@@
 We can then wonder if such a diagram has a colimit.
-Clealry if $\der{D}$ is the empty derivation $G$ then a colimit for $\Delta(\der{D})$ is simply the object $G$.
+Clearly if $\der{D}$ is the empty derivation $G$ then a colimit for $\Delta(\der{D})$ is simply the object $G$.
 More generally, we have the following result.
@@
 \begin{lemma}\label{lem:colim}
-	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO-rewriting system over it. The following hold true.
-	\begin{enumerate}
-		\item For every derivation $\der{D}=$ of length $n$ and for every $j\in[0,n-1]$, the outer boundary of following diagram is a pushout,
-		\[\xymatrix@C=30pt{D_{j} \ar[r]^{g_j}\ar@{>->}[d]_{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} \ar@{>->}@/^.3cm/[ddl]^{\iota'_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar[dd]^{p_2} \\ G_j \ar[d]_{\iota'_{G_j}}\\ \lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
-		where $\der{D}':=\{\dder{D}_i\}_{i=0}^{j-1}$, $\der{\hat{D}}:=\{\dder{D}_i\}_{i=j+1}^n$ and the two arrows $p_1\colon \lpro\der{D}' \rpro\to \tpro{D}$, $p_2\colon \lpro \der{\hat{D}}\rpro \to \tpro{D}$ are induced by the cocones $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}')})$ and $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}')})$, respectively.
-		\iffalse 
-		\item if $\der{D}$ is a derivation of length one, whose unique element is given by the following diagram
-	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G & \ar@{>->}[l]^{f} D \ar[r]_{g}& H }\]	
-		Then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists, moreover the following square is an $\mathcal{M}$-pushout;
-		\[\xymatrix{ D\ar[r]^{g} \ar@{>->}[d]_{f} & H \ar[d]^{\iota_H} \\G \ar[r]_{\iota_G} &  \tpro{D}}\]
-		\fi
-
+	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO-rewriting system over it. The following properties hold true.
+	\begin{enumerate}
 		\item  If $\der{D}$ is a derivation from $G$ to $H$, then the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belongs to $\mathcal{M}$.
-
 		\item Let $\der{D}$ be the concatenation $\der{D}_1\cdot \der{D}_2$ of two derivations $\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^{n_1}$ between $G$ and $H$ and $\der{D}_2=\{\dder{D}_{2,j}\}_{j=0}^{n_2}$ between $H$ and $T$,  then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists too and there is a pushout square
@@
 \begin{remark}\label{rem:cof}
-	contenuto...
-\end{remark}
-
-\begin{remark}\label{rem:zero}
-There is a version of point $4$ of \Cref{lem:colim} for $j=0$ which follows directly from points $1$ and $3$.
-Indeed, $\der{D}=\der{D}_1 \cdot \der{D}_2$ where $\der{D}_1=\{\dder{D}_0\}$ and $\der{D}_2=\{\dder{D}_i\}_{i=1}^n$.
-By point $1$ and $3$ of \Cref{lem:colim}, the two halves of the rectangle below are pushouts.
-By \Cref{lem:po1} the whole diagram is then a pushout too.
-	\[\xymatrix@C=30pt{D_{0} \ar[r]^{g_0}\ar[d]_{f_0}& G_{1} \ar[d]^{\iota_{1, G_1}} \ar[r]^-{\iota_{2,G_{1}}} & \lpro \der{D}_2\rpro \ar[d]^{p_2} \\ G \ar[r]_{\iota_{1,G}}& \lpro \der{D}_1 \rpro \ar[r]_{p_1}  &\tpro{D} }\]
-Notice that this entails that the square below is also a pushout. 
-\[\xymatrix@C=25pt{D_0\ar[r]^-{\iota_{2, D_0}}  \ar[d]_{\iota_{1, D_0}}&  \lpro \der{D}_1 \rpro\ar[d]^{p_2}\\ \lpro \der{D}_1 \rpro \ar[r]_{p_1}  &\tpro{D} }\]
+Let $I:\Deltamin(\dder{D})\to \Delta(\dder{D})$ be the inclusion functor.
+It is immediate to see that such functor is \emph{final} \cite{mac2013categories}.
+This means that for every functor $F\colon \Delta(\dder{D})\to \Y$ we have:
+\begin{enumerate}
+	\item if  $(C, \{c_X\}_{X\in \Deltamin(\dder{D})})$ is colimiting for $F\circ I$, then there exists a colimiting cocone $(D, \{d_X\}_{X\in \Delta(\dder{D})})$ for $F$;
+	\item $(C, \{c_X\}_{X\in \Deltamin(\dder{D})})$ and $(D, \{d_X\}_{X\in \Delta(\dder{D})})$ are colimiting for, repsectively, $F\circ I$ and $F$, then the canonical arrow $\phi\colon C\to D$ induced by $(D, \{d_X\}_{X\in \Deltamin(\dder{D})})$ is an isomorphism.
+\end{enumerate}
 \end{remark}
@@
 \begin{proof}\begin{enumerate}
-		\item We can start noticing that $f$, being the pushout of $l$ is in $\mathcal{M}$ and thus it admits a pushout along $g$, giving us the diagram 
-		\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G \ar@/_.2cm/[dr]_{q}& \ar[l]^{f} D \ar[r]_{g}& H  \ar@/^.2cm/[dl]^{p}\\ & P}\]
-		Clearly, precomposing $p$ and $q$ with the arrows appearing in $\dder{D}$, we can extend the pushout $(P, p, q)$, to a cocone $(P, \{j_X\}_{X\in \Delta(\der{D})})$ on $\Delta(\der{D})$.
-Let $(C, \{c_X\}_{X\in \Delta(\der{D})})$ be another cocone, for $\Delta(\der{D})$, in particular we have
-		\begin{align*}
-			c_H\circ g & = c_D \\&= c_G\circ f
-		\end{align*}
-		Hence, there exists a unique $c\colon P\to C$ such that $c\circ q= c_G$ and $c\circ p =c_H$. But these identities are enough to deduce that $(P, \{j_X\}_{X\in \Delta(\der{D})})$  is colimiting.
-		\item Let us proceed by induction.
+		\item Let us proceed by induction on the length of $\der{D}$.
 		\begin{itemize}
-			\item  If $n=0$, then the claim follows immediately from point $1$, noticing that $\iota_H$ is the pushout of $f$ and thus an element of $\mathcal{M}$.
-			\item Let $\der{D}$ be $\{\dder{D}_i\}_{i=0}^n$ and suppose that $n\geq 1$.
+			\item  $\lgh(\dder{D})=0$. then the $\tpro{\dder{D}}$ is simply $(G, \{\id{G}\})$ and $\id{G}\in \mathcal{M}$.¸
+			\item $\lgh(\dder{D})=0$. Suppose that $\dder{D}$ has as its single component the derivation
+			\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G& \ar@{>->}[l]^{f} D \ar[r]_{g}& H  \\}\]
+			The arrow $f$ is  the pushout of $l$ and so it is in in $\mathcal{M}$. We can thus consider the $\mathcal{M}$-pushout square
+			\[\xymatrix{D \ar@{>->}[d]_{f} \ar[r]^{g} & H \ar@{>->}[d]^{p} \\G \ar[r]_{q}& P }\]
+			Since $p\in \mathcal{M}$, the thesis follows immediately from \Cref{rem:cof}. 
+			\item $\lgh(\dder{D})\geq 2$.
+Let $\der{D}$ be $\{\dder{D}_i\}_{i=0}^n$ with $n\geq 1$.
 Let also $\der{D}'$ be $\{\dder{D}_i\}^{n-1}_{i=0}$ and $\rho_n=(l_n, r_n)$ be the rule applied in $\dder{D}_n$.
@@
 Thus, we can consider the diagram below, having a pushout as its lower half.
-			\[\xymatrix{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar[l]_{l_{n}} \ar[r]^{r_{n}} & R_{n} \ar[d]^{h_n} \\G_{n} \ar[d]_{\iota'_{G_{n}}}& \ar[l]^{f_n} D_n \ar[r]_{g_n}& H  \ar[d]^{q}\\ \lpro \der{D}' \ar[rr]_{p}\rpro && P}\]
+			\[\xymatrix{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar@{>->}[l]_{l_{n}} \ar[r]^{r_{n}} & R_{n} \ar[d]^{h_n} \\G_{n} \ar@{>->}[d]_{\iota'_{G_{n}}}& \ar@{>->}[l]^{f_n} D_n \ar[r]_{g_n}& H  \ar@{>->}[d]^{q}\\ \lpro \der{D}' \ar[rr]_{p}\rpro && P}\]
 			Notice that, as in the point above, the arrow $q\colon H\to P$ is the pushout of an element in $\mathcal{M}$, therefore it is enough to show that the diagram so constructed provides a colimiting cocone for $\Delta(\der{D})$.
@@
 		\end{itemize}
+
 		\item  As a first step, notice that $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D}_1)})$ and $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D}_2)})$ are cocone on, respectively, $\Delta(\der{D}_1)$ and $\Delta(\der{D}_2)$.
@@
 		In particular, this entails the commutativity of the square
-				\[\xymatrix{H \ar[dr]^{\iota_H} \ar[r]^-{\iota_{2, H}} \ar[d]_-{\iota_{1, H}} & \tproi{D}{2} \ar[d]^{p_2}\\  \tproi{D}{1} \ar[r]_{p_1}& \tpro{D}}\]
+				\[\xymatrix{H \ar[dr]^{\iota_H} \ar[r]^-{\iota_{2, H}} \ar@{>->}[d]_-{\iota_{1, H}} & \tproi{D}{2} \ar[d]^{p_2}\\  \tproi{D}{1} \ar[r]_{p_1}& \tpro{D}}\]
 
@@
 \end{align*}
-showing that $c'=c$ as wanted.
-
-\item Let $a\colon \lpro \der{\hat{D}}\rpro\to C$ , $b\colon \lpro \der{D}' \rpro\to C$ be two arrows fitting in the diagram 
-	\[\xymatrix{D_{j} \ar[ddrr]^{\iota_{D_j}}\ar[r]^{g_j}\ar[d]_{f_j}& G_{j+1} \ar[r]^{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar@/^.4cm/[dddr]^{a} \ar[dd]^{p_2} \\ G_j \ar[d]_{\iota'_{G_j}}\\ \lpro \der{D}' \rpro \ar@/_.4cm/[rrrd]_{b} \ar[rr]_{p_1}  &&\tpro{D} \ar@{.>}[dr]^{c}\\ &&& C }\]
-
-	We can define a cocone $(C, \{c_X\}_{X\in \Delta(\der{D})})$ putting
-		\[c_X:=\begin{cases}
-		a\circ \hat{\iota}_{ X} & X\in \Delta(\der{\hat{D}})\\
-		b\circ \iota'_{ X} & X\in \Delta(\der{D}')\\
-		b\circ \iota'_{G_j} \circ f_j & X=D_j
-	\end{cases}\]
-	Thus we get a unique arrow $c\colon \tpro{D}\to C$ such that 
-	\[c\circ \iota_X = c_X\]
-	Now, for every $X\in  \Delta(\der{D}')$ and $Y\in  \Delta(\der{\hat{D}})$ we have
-	\[\begin{split}
-		c\circ p_1 \circ \iota'_{X}&=c\circ \iota_{X}\\&=c_X \\&=b\circ \iota'_{X}\\&=b\circ p_1\circ \iota'_{X}
-	\end{split}\qquad \begin{split}
-		c\circ p_2 \circ \hat{\iota}_{Y}&=c\circ \iota_{Y}\\&=c_Y \\&=a\circ \hat{\iota}_{Y}\\&=a\circ p_2\circ \hat{\iota}_{Y}
-	\end{split}\]
-	so that we can deduce
-	\[c\circ p_1=a \qquad c\circ p_2 = b\]
-
-	To see that such $c$ is unique, suppose that $c'\colon \tpro{D}\to C$ is given such that
-	\[c'\circ p_1=b \qquad c'\circ p_2 = a\]
-	Then, for every $X\in \Delta(\der{D})$ we have
-	\begin{align*}
-		c'\circ \iota_X &= \begin{cases}
-			c'\circ p_1\circ \iota'_{X} & X\in \Delta(\der{D}')\\
-			c'\circ p_2\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
-			c'\circ \iota_{D_j} & X=D_j
-		\end{cases}\\&=\begin{cases}
-		b\circ \iota'_{X} & X\in \Delta(\der{D}')\\
-		a\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
-		c'\circ p_1 \circ \iota'_{G_j} \circ f_j  & X=D_j
-		\end{cases}\\&= \begin{cases}
-		b\circ \iota'_{X} & X\in \Delta(\der{D}')\\
-		a\circ \hat{\iota}_{X} & X\in \Delta(\der{\hat{D}})\\
-			b\circ \iota'_{G_j} \circ f_j  & X=D_j
-		\end{cases}\\&=c_X\\&=c\circ \iota_X
-	\end{align*}
-	allowing us to deduce that $c'=c$. \qedhere 
-	\end{enumerate}
-\end{proof}
+showing that $c'=c$ as wanted.	 \qedhere 
+	\end{enumerate}
+\end{proof}
+
+\begin{corollary}\label{cor:colim}
+Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ a derivation of length $n+1$ and fix an index $j\in[0,n]$. Define
+\[\der{D}^j_1:=\{\dder{D}_i\}_{i=0}^{j-1} \qquad  \der{D}^j_2=\{\dder{D}_j\} \qquad \der{D}^j_3:=\{\dder{D}_i\}_{i=j+1}^n\]
+with the convention that $\der{D}^0_1$ and $\der{D}^n_3$ are the empty derivation on, respectively, $G_0$ and $G_n$. Then the square below is a pushout and a pullback
+\[\xymatrix@C=30pt{D_{j} \ar[ddrr]^{\iota_{D_j}} \ar[r]^{g_j}\ar@{>->}[d]_{f_j}& G_{j+1} \ar[ddr]^{\iota_{G_{j+1}}} \ar[r]^-{\iota_{3, G_{j+1}}} & \lpro \der{D}^j_3\rpro \ar[dd]^{p_2} \\ G_j\ar[drr]_{\iota_{G_{j}}} \ar@{>->}[d]_{\iota_{1,G_j}}\\ \lpro \der{D}^j_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
+Where the two arrows $p_1\colon \lpro\der{D}^j_1 \rpro\to \tpro{D}$, $p_2\colon \lpro \der{D}^j_3\rpro \to \tpro{D}$ are induced by the cocones $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}^j_1)})$ and $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}^j_3)})$, respectively.
+\end{corollary}
+\begin{remark}
+If $\der{D}$ is empty then $\der{D}^j_1, \der{D}^j_2$ and $\der{D}^j_3$ are empty too.
+\end{remark}
+\begin{proof}
+We can notice that $\der{D}=\der{D}^j_1\cdot \der{D}^j_2 \cdot \der{D}^j_3$.
+By the first and the second point of \Cref{lem:colim} then we get the following diagram, in which all squares are $\mathcal{M}$-pushouts.
+
+\[\xymatrix@C=30pt{D_{j}  \ar[r]^{g_j}\ar@{>->}[d]_{f_j}& G_{j+1}  \ar[r]^-{\iota_{3,G_{j+1}}} \ar[d]_{\iota_{2, G_{j+1}}}  \ar@/^.5cm/[dd]^{\iota_{1,2, G_{j+1}}}& \lpro \der{D}^j_3\rpro \ar[dd]^{p_2} \\ G_j \ar[r]^{\iota_{2, G_j}}\ar@{>->}[d]_{\iota_{1,G_j}} & \lpro \der{D}^j_2\rpro \ar[d]_a\\ \lpro \der{D}^j_1 \rpro \ar@/_.4cm/[rr]_{p_1} \ar[r]^b &\lpro \der{D}^j_1\cdot \der{D}^j_2 \rpro \ar[r]^c&\tpro{D} }\]
+Applying \Cref{lem:po1} twice we get that the whole square is an $\mathcal{M}$-pushout. Then the thesis follows from \Cref{prop:pbpoad}.
+\end{proof}
+
+\begin{remark}\label{rem:zero1} In particular, considering $j=0$ or $j=n$, we get that the following two squares are $\mathcal{M}$-pushouts and, thus, pullbacks.
+	\[\xymatrix{D_0 \ar[r]^-{\iota_{3, D_0}} \ar@{>->}[d]_{f_0}& \lpro \der{D}^0_3 \rpro \ar@{>->}[d]^{p_2} &D_n \ar@{>->}[d]_{\iota_{1, D_n}}\ar[r]^{g_n}& G_n \ar@{>->}[d]^{\iota_{G_n}}\\ G \ar[r]_{\iota_G}& \tpro{D} & \lpro \der{D}^n_1 \rpro \ar[r]_{p_1}  & \tpro{D}}\]
+\end{remark}
+
 \begin{corollary}\label{cor:ele}
@@
 If $\iota_{G_j}\circ a = \iota_{G_k}\circ b$,
-	then  there exist arrow $c\colon T\to D_j $  such that \[f_j\circ c = a\qquad \iota_{D_j}\circ c =\iota_{G_k}\circ b\]
+	then  there exist a unique arrow $c\colon T\to D_j $  such that \[f_j\circ c = a\qquad \iota_{D_j}\circ c =\iota_{G_k}\circ b\]
 	\end{corollary}
-\begin{proof} We split the cases.
-	\begin{itemize}
-		\item $j=0$. Consider $\der{D}_1:=\{\dder{D}_0\}$ and $\der{D}_2:=\{\dder{D}_i\}_{i=1}^n$.  Consider the diagram below in which, by \Cref{rem:zero}, the rectangle on the bottom right is a pushout.
-		\[\xymatrix@C= 40pt{T  \ar@/_.6cm/[ddd]_{a}\ar@{.>}[d]^{t}\ar[rr]^{b}&& G_k \ar[d]_{\iota_{2, G_k}} \ar@/^.6cm/[ddd]^{\iota_{G_k}}\\D_{0} \ar[r]^{g_0}\ar[d]^{f_0}& G_{1} \ar[r]^-{\iota_{2,G_{1}}} & \lpro \der{D}_2\rpro \ar[dd]_{p_2} \\ G \ar[drr]^{\iota_G} \ar[d]^{\iota_{1,G}}\\ \lpro \der{D}_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
-		Since $f_0$ and $\iota_{1,G}$ are in $\mathcal{M}$ the same rectangle is an $\mathcal{M}$-pushout and so, by \Cref{prop:pbpoad} is a pullback and the thesis follows.
-		\item   $j\neq 0$. We proceed as in the point above. Using point $4$ of \Cref{lem:colim} we know that the bottom right rectangle in the diagram below is a pushout. 
-			\[\xymatrix@C=30pt{T  \ar@/_.6cm/[ddd]_{a}\ar@{.>}[d]^{t}\ar[rr]^{b}&& G_k \ar[d]_{\iota_{2, G_k}} \ar@/^.6cm/[ddd]^{\iota_{G_k}}\\D_{j} \ar[r]^{g_j}\ar[d]^{f_j}& G_{j+1} \ar[r]^-{\hat{\iota}_{G_{j+1}}} & \lpro \der{\hat{D}}\rpro \ar[dd]_{p_2} \\ G_j \ar[d]^{\iota'_{G_j}} \ar[drr]^{\iota_{G_j}}\\ \lpro \der{D}' \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
-		Point $2$ of \Cref{lem:colim} entails that $\iota'_{G_j}$ is in $\mathcal{M}$, and so is $f_j$ as it is the pushout of $l_j$.
-Thus the rectangle we are considering is an $\mathcal{M}$-pushout and the thesis follows again from \Cref{prop:pbpoad}.
-\qedhere
-	\end{itemize}
+\begin{proof} Consider the diagram
+			\[\xymatrix@C=34pt{T  \ar@/_.6cm/[dd]_{a}\ar@{.>}[d]^{c}\ar[rr]^{b}&& G_k \ar[d]_{\iota_{3, G_k}} \ar@/^.6cm/[ddd]^{\iota_{G_k}}\\D_{j} \ar[r]^{g_j} \ar[ddrr]^{\iota_{D_j}}\ar@{>->}[d]^{f_j}& G_{j+1} \ar[r]^-{\iota_{3,G_{j+1}}} \ar[ddr]^{\iota_{G_{j+1}}} & \lpro \der{D}^j_3\rpro \ar[dd]_(.6){p_2} \\ G_j \ar@{>->}[d]_{\iota_{1,G_j}} \ar[drr]_{\iota_{G_j}}\\ \lpro \der{D}^j_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
+			Thanks to \Cref{cor:colim} we know that the bottom right rectangle in the diagram above is a pullback and the thesis follows at once.
 \end{proof}
@@
 
-\begin{definition}\label{def:permcon}
+\begin{definition}[Consistent permutation]\label{def:permcon}
 	Let $\X$ be an $\mathcal{M}$-adhesive category and consider a left-linear DPO-rewriting system $(\X, \R)$ on it.
-Take two non-empty decorated derivations $(\der{D}, \alpha, \omega)$ and  $(\der{D}', \alpha', \omega')$ such that
-	\begin{itemize}
-		\item $\der{D}$ and $\der{D}'$ have the same length;
-		\item if  $\der{D}$  is a derivation between $G$ and $H$ amd $\der{D}'$ one between $G'$ and $H'$, then $G\simeq G'$ and $H\simeq H'$.
-	\end{itemize}
-
-	 	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with assciated squence of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma\colon [0,n]\to [0,n]$  such that, for every $i\in [0,n]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
-	\[\xymatrix{\pi(G)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G \ar[r]^{\iota_{G}} &\tpro{D} \ar[d]^{\xi}&   \pi(H) \ar[r]^{\omega} \ar[d]_{\omega'} & H \ar[r]^{\iota_H} &\tpro{D} \ar[d]^{\xi}\\ G' \ar[rr]_{\iota'_{G'}} & &\lpro \der{D}' \rpro& H' \ar[rr]_{\iota'_{H'}} & &\lpro \der{D}' \rpro}\]
+Take two non-empty decorated derivations $(\der{D}, \alpha, \omega)$ and  $(\der{D}', \alpha', \omega')$ with the same length and with isomorphic sources and targets.
+
+	 	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with assciated sequence of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma\colon [0,n]\to [0,n]$  such that, for every $i\in [0,n]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
+	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_\sigma}&   \pi(G_{n+1}) \ar[r]^{\omega} \ar[d]_{\omega'} & G_{n+1} \ar[r]^{\iota_{G_{n+1}}} &\tpro{D} \ar[d]^{\xi_\sigma}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro& G'_{n+1} \ar[rr]_{\iota'_{G'_{n+1}}} & &\lpro \der{D}' \rpro}\]
 \[\xymatrix{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
@@
 The commutativity of the last two rectangles in \Cref{def:permcon}, is equivalent to the commutativity of the following bigger diagram.		
-\[\xymatrix@C=40pt@R=10pt{ &&&R_{i}\ar[dddr]^{h'_{\sigma(i)}} \ar[dddl]_{h_i}|(.67)\hole\\&&K_i \ar[dl]_{l_i} \ar[ur]^{r}\ar[dddr]^{k'_{\sigma(i)}} \ar[dddl]_{k_i}|(.67)\hole\\&L_i\ar[dddr]_(.6){m'_{\sigma(i)}} \ar[dddl]_{m_i}\\&&G_{i+1}  \ar@/^.3cm/[dddl]|(.35)\hole^(.7){\iota_{G_{i+1}}}&& G'_{\sigma(i)+1}\ar@/^.3cm/[dddl]^{\iota'_{G'_{\sigma(i)+1}}}\\ & D_i \ar[dd]_{\iota_{D_i}}\ar[ur]^(.6){g_i}  \ar[dl]_{f_i}&& D'_\sigma(i) \ar[dd]^{\iota'_{D'_\sigma(i)}} \ar[ur]^{g'_{\sigma(i)}}\ar[dl]_{f'_{\sigma(i)}}\\ G_i \ar@/_.3cm/[dr]_{\iota_{G_i}} && G'_{\sigma(i)}\ar@/_.3cm/[dr]^{\iota'_{G'_{\sigma(i)}}}\\& \tpro{D} \ar[rr]_{\xi_\sigma}&& \lpro \der{D}' \rpro}\]
-
-Indeed,  to prove the commutativity of the central pentagon we can compute to get:
+\[\xymatrix@C=40pt{G_i\ar@/^1cm/[rrr]^{\iota_{G_{i}}}&D_i\ar@/^.4cm/[rr]^(.35){\iota_{D_i}} \ar[r]_{g_i} \ar@{>->}[l]^{f_i}&G_{i+1} \ar[r]_{\iota_{G_{i+1}}}&\tpro{D} \ar[dd]^{\xi_\sigma}\\  L_i \ar[u]^{n_i} \ar[d]_{n'_{\sigma(i)}}& K_i \ar[d]^{k'_{\sigma(i)}} \ar[u]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i} &R\ar[u]^{h_i} \ar[d]_{h'_{\sigma(i)}}\\G'_{\sigma(i)}\ar@/_1cm/[rrr]_{\iota'_{G'_{\sigma(i)}}} &D'_{\sigma(i)}\ar@{>->}[l]_{f'_{\sigma(i)}} \ar[r]^{g'_i} \ar@/_.4cm/[rr]_(.35){\iota'_{D'_{\sigma(i)}}}&G'_{\sigma(i)+1} \ar[r]^{\iota'_{G'_{\sigma{i}+1}}}& \lpro\der{D}' \rpro }\]
+This follows at once from the following chain of identities::
 \begin{align*}
@@
 \begin{remark}\label{rem:inversa}
-Let $\sigma\colon [0,n]\to [0,n]$ be a consistent permutation between $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, then $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$: indeed, it is enough to consider, as mediating isomorphism, the inverse $\xi^{-1}_\sigma$ of $\xi_\sigma$.
+Let $\sigma\colon [0,n]\to [0,n]$ be a consistent permutation between $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, then its inverse $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$.
+Indeed, it is enough to consider, as mediating isomorphism, the inverse $\xi^{-1}_\sigma$ of $\xi_\sigma$.
 \end{remark}
@@
 Then the identity permutation $\id{[0,n]}$ is a consistent permutation between them.
-In such a case $\xi_{\id{[0,n]}}$ is simply the isomorphism induced by any family $\{\phi^i\}_{i=0}^n$ witnessing $(\der{D}, \alpha, \omega)\equiv^a (\der{D}', \alpha', \omega')$.
+In such a case $\xi_{\id{[0,n]}}$ is simply the isomorphism induced by any abstraction equivalence $\{\phi_X\}_{X\in \Delta(X)}$.
+
+	If $\der{D}$ and $\der{D}'$ are empty, then the converse also holds: indeed in such a case a mediating isomorphism provides the wanted abstraction equivalence.
 \end{example}
 
-\begin{example}\todo{esempi di cose consistenti utile per \cref{ex:contro}}
+\begin{example}\todo{identità consistente non implica astrazione}
 \end{example}
@@
 			\end{align*}
-			The thesis now follows.			\qed
+			The thesis now follows.			\qedhere
 		\end{itemize}
@@
 
-Now, notice that, given a consistent permutation $\sigma$, $\xi_\sigma\colon \tpro{D}\to \lpro \der{D}'\rpro$, we already know, by \Cref{rem:coproj} that
+Now, notice that, given a consistent permutation $\sigma\colon [0,n]\to[0,n]$, we already know, by \Cref{rem:coproj} that
 \[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
-	Moreover, for $\xi_\sigma \circ \iota_{D_i}$ must be $\xi_\sigma \circ \iota_{G_i}\circ f_i$.
-Thus it is enough to define $\xi_{\sigma} \circ \iota_{G_i}$ for every $i\in [0, n]$.
-But then \Cref{prop:uniqu} entails the following.
-\begin{corollary} Given a consistent permutation $\sigma$ between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, the mediating isomorphism $\xi_\sigma\colon \tpro{D}\to \lpro \der{D}'\rpro$ is unique.
+	Moreover, $\xi_\sigma \circ \iota_{D_i}$ must be $\xi_\sigma \circ \iota_{G_i}\circ f_i$.
+Thus $\xi_\sigma$ is uniquely determined by $\xi_{\sigma} \circ \iota_{G_i}$ for every $i\in [0, n]$.
+In particular,  \Cref{prop:uniqu} entails the following.
+\begin{corollary} For every consistent permutation $\sigma$ between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, the mediating isomorphism $\xi_\sigma\colon \tpro{D}\to \lpro \der{D}'\rpro$ is unique.
 \end{corollary}
 
-\begin{proposition}\label{prop:sum}
-\todo{il caso in cui sigma si decomponga come due permu}
+\begin{proposition}\label{prop:sum} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstract decorated derivations such that
+	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)\]
+If $\sigma_1\colon [0, \lgh(\der{D}_1)-1]\to [0, \lgh(\der{D}_1)-1]$ is a consistent permutation between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$ and $\sigma_2:[0, \lgh(\der{D}_2)-1]\to [0, \lgh(\der{D}_2)-1]$ one between $(\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$, then
+\[\sigma_1+\sigma_2\colon[0, \lgh(\der{D})-1]\to[0, \lgh(\der{D})-1] \qquad n \mapsto \begin{cases}
+	\sigma_1(n) & n < \lgh(\der{D}_1)\\
+	\sigma_2(n-\lgh(\der{D}_1)) &   \lgh(\der{D}_1) \leq n
+\end{cases}\]
+ is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
 \end{proposition}
 \begin{proof}
-	contenuto...\qedhere 
+	\[(\der{D}, \alpha, \omega)\cdot (\der{D}', \alpha', \omega'):=\begin{cases}
+		(\der{D}', \alpha'\circ \omega^{-1}\circ \alpha, \omega')	&\lgh(\der{D})=0 \\
+		(\der{D}, \alpha, \omega \circ (\alpha')^{-1}\circ \omega')&\lgh(\der{D}')=0 \text{ and } \lgh(\der{D})\neq 0\\
+		(\der{D}*\omega^{-1}\cdot \alpha'*\der{D'}, \alpha, \omega')	&\text{otherwise}
+	\end{cases}\]
+
+	Following \Cref{def:conc}, we will split the proof in three cases.
+	\begin{itemize}
+		\item $\lgh(\der{D}_1)=0$. Thus $\lgh(\der{D}'_1)=0$ too  and we have
+		\[(\der{D}, \alpha, \omega)=(\der{D}_2, \alpha_2\circ \omega_1^{-1}\circ \alpha_1, \omega_2) \quad (\der{D}', \alpha', \omega')=(\der{D}'_2, \alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1, \omega'_2)\]
+	Moreover, in this case $\sigma_1+\sigma_2=\sigma_2$. The thesis now follows at once noticing that 
+	\begin{align*}\xi_{\sigma_2}\circ \iota_{G_{2,0}}\circ \alpha_2 \circ \omega_1^{-1}\circ \alpha_1 &=\iota'_{G'_{2,0}} \circ \alpha'_2 \circ \omega^{-1}_1 \circ \alpha_1\\&=\iota'_{G'_{2,0}} \circ \alpha'_2 \circ (\omega'_1)^{-1}\circ \xi_{\id{\emptyset}} \circ \alpha_1\\&=\iota'_{G'_{2,0}} \circ \alpha'_2\circ (\omega'_1)^{-1} \circ \alpha'_1
+	\end{align*}
+
+		\item 
+		\item  \qedhere 
+	\end{itemize}
 \end{proof}
@@
 			\[\xymatrix{L_{j-1} \ar@/^.3cm/[drr]^{\id{L_{j-1}}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_{j-1} \ar[d]_{k_a}\ar[r]^{l_{j-1}}& L_{j-1} \ar[d]^{m_a} \\& D_a \ar[r]_{f_a} & G_a} \]
-			The existence of the dotted $t\colon L_{j-1}\to K_{j-1}$ follows from  \Cref{prop:pbpoad} and we can conclude. \qed
+			The existence of the dotted $t\colon L_{j-1}\to K_{j-1}$ follows from  \Cref{prop:pbpoad} and we can conclude. \qedhere
 	\end{enumerate}
@@
 \end{remark}
+\begin{definition}[Very tameneness]
+	\todo{very tame}
+\end{definition}
+
+\begin{remark}
+	\todo{tutto coincide con tutto}
+\end{remark}
 
@@
 
-\begin{remark}\label{rem:pbsalva}
-Let $(i_1,i_2)$ be a good independence pair between the derivation $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$.
-Let also $\der{\hat{D}}$ be the derivation consisting only in $S_{i_1,i_2}(\dder{D})$.
-We have a diagram
-\[\xymatrix{P\ar[r]^{q}  \ar[d]_{p}& Q \ar[r]^{v} \ar[d]^{s}& J \ar[r]^{\hat{\iota}_J}& \lpro \der{\hat{D}} \rpro \ar[d]^{\hat{p}}  \\D	\ar[r]_{f} &G \ar[rr]_{\iota_{G}}&& \lpro S_{i_1, i_2}(\dder{D}, \dder{D}')\rpro}\]
-By \Cref{rem:zero,rem:deco}, its two halves are pullbacks and so, by \Cref{lem:pb1} the whole rectangle is a pullback too. Moreover, notice that
-\begin{align*}
-	\hat{\iota}_J\circ v \circ q &= \hat{\iota}_J\circ v'\circ q'\\&= \hat{\iota}_{Q'}\circ q'
-\end{align*}
-which entails that the rectangle below is a pullback too.
-\[\xymatrix{P\ar[r]^{q'}  \ar[d]_{p}& Q' \ar[r]^{\hat{\iota}_{Q'}}& \lpro \der{\hat{D}} \rpro \ar[d]^{\hat{p}}  \\D	\ar[r]_{f} &G \ar[r]_-{\iota_{G}}& \lpro S_{i_1, i_2}(\dder{D}, \dder{D}')\rpro}\]
-\end{remark}
-
 \begin{remark}\label{rem:indip}Notice that $(j', j)$ is an independence pair for $S_{i_1,i_2}(\dder{D}')$ and $S_{i_1,i_2}(\dder{D})$.
@@
 
-\begin{proposition}\label{prop:fil}Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
+\begin{theorem}[Local Church-Rosser Theorem]\label{prop:fil}Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
 Then every filler between two direct derivations $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$ is a filler also for $S_{u,u'}(\dder{D'})\colon G\Mapsto J$ and $S_{u,u'}(\dder{D})\colon J\Mapsto H$.
 In particular, if $\dder{D}\updownarrow \dder{D}'$, then $S_{u,u'}(\dder{D}')\updownarrow S_{u,u'}(\dder{D})$.
-\end{proposition}
-\begin{remark}\label{rem:locCR}
-\todo{questo è Church-Rosser}
-\end{remark}
+\end{theorem}
 \begin{proof}By definition of filler, we have two pushout square
@@
 
-\begin{definition}[Very tameness]
-	\todo{very tame}
-\end{definition}
-
-\begin{remark}
-\todo{tutto coincide con tutto}
-\end{remark}
-
-\subsubsection{Graphical rewriting systems}
+\subsubsection{Graphical rewriting systems}\label{subsubsec:graphical}
+
 \todo{ci sono un sacco di sistemi very tame}
@@
 \appendix
-\section{On permutations}\label{app:perm}
-\todo{inserire risutati sulle permutazione che abbiamo usato}
 
@@
 
-\section{Full proof of \Cref{thm:crit}}
+\section{On permutations}\label{app:perm}
+\todo{inserire risutati sulle permutazione che abbiamo usato}
 

### 2023-12-13 fusione.tex
typos

@@
 
-The next proposition justifies the use of decorations, guaranteeing that concatenation of abstract decorated derivations is weel-defined.
+The next proposition justifies the use of decorations, guaranteeing that concatenation of abstract decorated derivations is well-defined.
 \begin{lemma}
@@
 
-\begin{remark}Clearly in a tame left-linear DPO-rewriting system two direct derivations are sequentially independent if and only if they are unquely switchable.
+\begin{remark}
+  Clearly in a tame left-linear DPO-rewriting system two direct derivations are sequentially independent if and only if they are unquely switchable.
 \end{remark}

### 2023-12-15 fusione.tex
cose

--- 2023-12-12 fusione.tex
@@
 		\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
-	If $\phi\colon G\to G'$ and $\psi\colon H\to H'$ are two isomorphisms, 	we can consider the direct derivation	$\phi * \dder{D}*\psi \colon G'\Mapsto H'$ given by the following diagram.
-	\[\xymatrix{L \ar[d]_{\phi \circ n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{\psi \circ h}\\G' & \ar[l]^{\phi \circ f} D \ar[r]_{\psi \circ g}& H}\]
+	If $\phi\colon G'\to G$ and $\psi\colon H\to H'$ are two isomorphisms, 	we can consider the direct derivation	$\phi * \dder{D}*\psi \colon G'\Mapsto H'$ given by the following diagram.
+	\[\xymatrix{L \ar[d]_{\phi^{-1} \circ n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{\psi \circ h}\\G' & \ar[l]^{\phi^{-1} \circ f} D \ar[r]_{\psi \circ g}& H'}\]
 
@@
 
+\begin{example}\label{rem:absequi}
+	Let $\der{D}$ be a derivation with source $G$ and target $H$. Let also $\phi:G'\to G$ and $\psi:H\to H'$ be two isomorphisms. Then for every $X\in \Deltamin(\der{D})$ we can define 
+	\[\varphi_X:=\begin{cases}
+		\phi^{-1} & X=G\\
+		\psi & X=H\\
+		\id{X} & \text{otherwise}
+	\end{cases}\]
+
+It is immediate to see that the family $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ is an abstraction equivalence between $\der{D}$ and $\phi *\der{D}*\psi$.	
+\end{example}
+
 \begin{definition}\label{def:conc}
@@
 The next proposition justifies the use of decorations, guaranteeing that concatenation of abstract decorated derivations is weel-defined.
-\begin{lemma}
+\begin{lemma}\label{lem:conc}
 	Given a decorated derivation $(\der{D}, \alpha, \omega)$  between $G$ and $H$ and  another one $(\der{E}, \beta, \xi)$ between $E$ and $K$ with $\pi(H)=\pi(E)$.
@@
 	\[\der{D}=\{\dder{D}_i\}_{i=0}^n \quad \der{D}'=\{\dder{D}'_i\}_{i=0}^n \quad \der{E}=\{\dder{E}_i\}_{i=0}^t \quad \der{E}'=\{\dder{E}'_i\}_{i=0}^t\]
-	where $\dder{D}_i$, $\dder{D}'_i$, $\dder{E}_i$ and $\dder{E}'_i$ are given, respectively, by the following four diagrams.
-We can also notice that the rule applied by $\dder{D}_i$ must coincide with the one applpied in $\dder{D}'_i$ and that the same holds for $\dder{E}_i$ and $\dder{E}'_i$.
+	Moreover, noticing that the rule applied by $\dder{D}_i$ and the one applied in $\mathcal{E}_i$  must coincide with, respectively, the one applied in $\dder{D}'_i$ and the one applied $\dder{E}'_i$.
+We will also assume that $\dder{D}_i$, $\dder{D}'_i$, $\dder{E}_i$ and $\dder{E}'_i$ are given, respectively, by the following four diagrams.
 	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}, i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}, i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}, i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}, i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}, i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}, i}} \\G_i & D_i \ar[r]_{g_{\der{D},i}} \ar[l]^{f_{\der{D},i}} & G_{i+1} & E_i & F_i\ar[r]_{g_{\der{E},i}} \ar[l]^{f_{\der{E},i}}  & E_{i+1}}\]
-	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}', i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}', i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}', i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}', i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}', i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}', i}} \\G_i & D_i \ar[r]_{g_{\der{D}',i}} \ar[l]^{f_{\der{D}',i}} & G_{i+1} & E_i & F_i\ar[r]_{g_{\der{E}',i}} \ar[l]^{f_{\der{E}',i}}  & E_{i+1}}\]
+	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}', i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}', i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}', i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}', i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}', i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}', i}} \\G'_i & D'_i \ar[r]_{g_{\der{D}',i}} \ar[l]^{f_{\der{D}',i}} & G'_{i+1} & E'_i & F'_i\ar[r]_{g_{\der{E}',i}} \ar[l]^{f_{\der{E}',i}}  & E'_{i+1}}\]
 
@@
 
-To show that $\{\psi_X\}_{\Deltamin(\der{D}*\omega^{-1}\cdot \beta*\der{E})}$ it is now enough to prove the commutativity of the diagrams
+To show that $\{\psi_X\}_{\Deltamin(\der{D}*\omega^{-1}\cdot \beta*\der{E})}$ is an abstraction equivalence, it is now enough to prove the commutativity of the diagrams
 	\[\xymatrix@C=45pt@R=15pt{G'_n&D'_n \ar[r]^-{(\omega')^{-1}\circ g_{\der{D}',n}} \ar@/_.2cm/[dr]_(.6){g_{\der{D}',n}} \ar[l]_{f_{\der{D}',n}}&\pi(H') \\&&H' \ar[u]^{(\omega')^{-1}}\\  L_{\der{D}, n} \ar[uu]^{m_{\der{D}',n}} \ar[dd]_{m_{\der{D},n}}& K_{\der{D}, n} \ar[uu]^{k_{\der{D}',n}} \ar[dd]_{k_{\der{D},n}} \ar[r]^{r_{\der{D},n}} \ar[l]_{l_{\der{D},n}} &R_{\der{D}, n}\ar[u]^{h_{\der{D}',n}} \ar[d]_{h_{\der{D},n}}\\&&H \ar[d]_{\omega^{-1}}\\G_n \ar@/_.7cm/[uuuu]_(.35){\phi_{G_n}}|\hole&D_n\ar[l]^{f_{\der{D},n}}\ar@/_.7cm/[uuuu]_(.35){\phi_{D_n}}|\hole \ar@/^.2cm/[ur]^(.6){g_{\der{D},n}}\ar[r]_{\omega^{-1}\circ g_{\der{D},n}}&\pi(H)\ar@/_.7cm/[uuuu]_{\id{\pi(H)}}\\ \pi(E')&F'_0 \ar[l]_-{(\beta')^{-1}\circ f_{\der{E}',0}} \ar@/^.2cm/[dl]^(.6){f_{\der{E}',0}} \ar[r]^{g_{\der{E}',0}}&E'_1 \\E' \ar[u]_{(\beta')^{-1}}&& \\  L_{\der{E}, 0} \ar[u]_{m_{\der{E}', 0}} \ar[d]^{m_{\der{E}, 0}}& K_{\der{E}, 0} \ar[uu]_{k_{\der{E}', 0}} \ar[dd]^{k_{\der{E}, i}} \ar[r]^{r_{\der{E},0}} \ar[l]_{l_{\der{E},0}} &R_{\der{E}, 0}\ar[uu]_{h_{\der{E}',0}} \ar[dd]^{h_{\der{E},0}}\\E \ar[d]^{\beta^{-1}}&& \\\pi(E) \ar@/^.7cm/[uuuu]^{\id{\pi(E)}}&F_0\ar[l]^{\beta^{-1}\circ f_{\der{E},0}}\ar@/^.7cm/[uuuu]^(.35){\varphi_{F_0}}|\hole \ar@/_.2cm/[ul]_(.6){f_{\der{E},0}}\ar[r]_{g_{\der{E},0}}&E_1\ar@/^.7cm/[uuuu]^(.35){\varphi_{E_1}}|\hole}\]
@@
 	 	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with assciated sequence of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma\colon [0,n]\to [0,n]$  such that, for every $i\in [0,n]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
-	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_\sigma}&   \pi(G_{n+1}) \ar[r]^{\omega} \ar[d]_{\omega'} & G_{n+1} \ar[r]^{\iota_{G_{n+1}}} &\tpro{D} \ar[d]^{\xi_\sigma}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro& G'_{n+1} \ar[rr]_{\iota'_{G'_{n+1}}} & &\lpro \der{D}' \rpro}\]
-\[\xymatrix{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
+	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_\sigma}&   \pi(G_{n+1}) \ar[r]^{\omega} \ar[d]_{\omega'} & G_{n+1} \ar@{>->}[r]^{\iota_{G_{n+1}}} &\tpro{D} \ar[d]^{\xi_\sigma}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro& G'_{n+1} \ar@{>->}[rr]_{\iota'_{G'_{n+1}}} & &\lpro \der{D}' \rpro\\L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
 \end{definition}
@@
 \begin{remark}\label{rem:comp} Consistent permutations can be composed.
-Indeed, given decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$, if $\sigma$ is a consistent permutation between the first two and $\sigma'$ one between the second and the third, then  we have diagrams
-	\[\xymatrix@C=18pt{ & G \ar[rr]^{\iota_{G}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  H \ar[rr]^{\iota_H} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G' \ar[rr]^{\iota'_{G'}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&\pi(H)\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & H' \ar[rr]^{\iota'_{H'}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}  \ar[rr]_{\hat{\iota}_{\hat{G}}}&& \lpro \hat{\der{D}}\rpro  && \hat{H} \ar[rr]_{\hat{\iota}_{\hat{H}}}&& \lpro \hat{\der{D}} \rpro \\& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_{\sigma'(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\sigma'(\sigma(i))} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}} \rpro	}\]
+Indeed, given decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$ all of length $n$, if $\sigma$ is a consistent permutation between the first two and $\sigma'$ one between the second and the third, then  we have diagrams
+	\[\xymatrix@C=18pt{ & G_0 \ar[rr]^{\iota_{G_0}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_{n} \ar@{>->}[rr]^{\iota_{ G_{n}}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G_0) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G'_0 \ar[rr]^{\iota'_{G'_0}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&\pi({ G_{n}})\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & { G'_{n}} \ar@{>->}[rr]^{\iota'_{{ G'_{n}}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_0  \ar[rr]_{\hat{\iota}_{\hat{G}_0}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_n \ar@{>->}[rr]_{\hat{\iota}_{\hat{G}_n}}&& \lpro \hat{\der{D}} \rpro \\& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_{\sigma'(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\sigma'(\sigma(i))} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}} \rpro	}\]
 	We deduce at once that $\sigma'\circ \sigma$ is a consistent permutation with mediating isomorphism given by $\xi_{\sigma'} \circ \xi_\sigma$.
@@
 
-\begin{proposition}\label{prop:sum} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstract decorated derivations such that
-	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)\]
-If $\sigma_1\colon [0, \lgh(\der{D}_1)-1]\to [0, \lgh(\der{D}_1)-1]$ is a consistent permutation between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$ and $\sigma_2:[0, \lgh(\der{D}_2)-1]\to [0, \lgh(\der{D}_2)-1]$ one between $(\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$, then
-\[\sigma_1+\sigma_2\colon[0, \lgh(\der{D})-1]\to[0, \lgh(\der{D})-1] \qquad n \mapsto \begin{cases}
-	\sigma_1(n) & n < \lgh(\der{D}_1)\\
-	\sigma_2(n-\lgh(\der{D}_1)) &   \lgh(\der{D}_1) \leq n
-\end{cases}\]
- is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
-\end{proposition}
-\begin{proof}
-	\[(\der{D}, \alpha, \omega)\cdot (\der{D}', \alpha', \omega'):=\begin{cases}
-		(\der{D}', \alpha'\circ \omega^{-1}\circ \alpha, \omega')	&\lgh(\der{D})=0 \\
-		(\der{D}, \alpha, \omega \circ (\alpha')^{-1}\circ \omega')&\lgh(\der{D}')=0 \text{ and } \lgh(\der{D})\neq 0\\
-		(\der{D}*\omega^{-1}\cdot \alpha'*\der{D'}, \alpha, \omega')	&\text{otherwise}
-	\end{cases}\]
-
-	Following \Cref{def:conc}, we will split the proof in three cases.
-	\begin{itemize}
-		\item $\lgh(\der{D}_1)=0$. Thus $\lgh(\der{D}'_1)=0$ too  and we have
-		\[(\der{D}, \alpha, \omega)=(\der{D}_2, \alpha_2\circ \omega_1^{-1}\circ \alpha_1, \omega_2) \quad (\der{D}', \alpha', \omega')=(\der{D}'_2, \alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1, \omega'_2)\]
-	Moreover, in this case $\sigma_1+\sigma_2=\sigma_2$. The thesis now follows at once noticing that 
-	\begin{align*}\xi_{\sigma_2}\circ \iota_{G_{2,0}}\circ \alpha_2 \circ \omega_1^{-1}\circ \alpha_1 &=\iota'_{G'_{2,0}} \circ \alpha'_2 \circ \omega^{-1}_1 \circ \alpha_1\\&=\iota'_{G'_{2,0}} \circ \alpha'_2 \circ (\omega'_1)^{-1}\circ \xi_{\id{\emptyset}} \circ \alpha_1\\&=\iota'_{G'_{2,0}} \circ \alpha'_2\circ (\omega'_1)^{-1} \circ \alpha'_1
-	\end{align*}
-
-		\item 
-		\item  \qedhere 
-	\end{itemize}
-\end{proof}
-
 We are now ready to prove the central result of this section.
@@
 	From \Cref{cor:ele}, we can conclude that there exists $c\colon L_0\to D_0$ such that $f_0\circ c=m_0$. We thus have the solid part of the commutative diagram below.
-		\[\xymatrix{L_0 \ar@/^.3cm/[drr]^{\id{L_0}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_0 \ar[d]_{k_0}\ar[r]^{l_0}& L_0 \ar[d]^{m_0} \\& D_0 \ar[r]_{f_0} & G_0} \]
+		\[\xymatrix{L_0 \ar@/^.3cm/[drr]^{\id{L_0}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_0 \ar[d]_{k_0}\ar@{>->}[r]^{l_0}& L_0 \ar[d]^{m_0} \\& D_0 \ar@{>->}[r]_{f_0} & G_0} \]
 		The internal square is an $\mathcal{M}$-pushout and thus a pullback, by \Cref{prop:pbpoad}, so that we have the existence of the dotted $t\colon L_0\to K_0$.
@@
 			Let $a$ be $\min(j-1, k)$, by \Cref{cor:ele},  there exists $c\colon L_{j-1}\to D_a$ such that $f_a\circ c=m_a$. As before this yields the solid part of the following diagram
-			\[\xymatrix{L_{j-1} \ar@/^.3cm/[drr]^{\id{L_{j-1}}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_{j-1} \ar[d]_{k_a}\ar[r]^{l_{j-1}}& L_{j-1} \ar[d]^{m_a} \\& D_a \ar[r]_{f_a} & G_a} \]
+			\[\xymatrix{L_{j-1} \ar@/^.3cm/[drr]^{\id{L_{j-1}}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_{j-1} \ar[d]_{k_a}\ar@{>->}[r]^{l_{j-1}}& L_{j-1} \ar[d]^{m_a} \\& D_a \ar@{>->}[r]_{f_a} & G_a} \]
 			The existence of the dotted $t\colon L_{j-1}\to K_{j-1}$ follows from  \Cref{prop:pbpoad} and we can conclude. \qedhere
@@
 
-\begin{corollary}\label{cor:unique}
+\begin{corollary}[Uniqueness of consistent permutation]\label{cor:unique}
 Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that every rule in $R$ is consuming.
@@
 
-\begin{corollary}\label{cor:dec}
+We end this section proving two rather technical result about consistent permutations between composite decorated derivations.
+
+\begin{proposition}\label{prop:sum} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstract decorated derivations such that
+	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)\]
+	If $\sigma\colon [0, \lgh(\der{D}_1)-1]\to [0, \lgh(\der{D}_1)-1]$ is a consistent permutation between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$ and $\tau:[0, \lgh(\der{D}_2)-1]\to [0, \lgh(\der{D}_2)-1]$ one between $(\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$, then
+	\[\sigma+\tau\colon[0, \lgh(\der{D})-1]\to[0, \lgh(\der{D})-1] \qquad n \mapsto \begin{cases}
+		\sigma(n) & n < \lgh(\der{D}_1)\\
+		\tau(n-\lgh(\der{D}_1)) &   \lgh(\der{D}_1) \leq n
+	\end{cases}\]
+	is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
+\end{proposition}
+\begin{proof}
+	Let us start fixing some notation.
+Given $X_1\in \Delta(\der{D}_1)$, $X_2\in \Delta(\der{D}_2)$, $X'_1\in \Delta(\der{D}'_1)$, $X'_2\in \Delta(\der{D}'_2)$, we will denote their coprojections into, respectively, $\lpro \der{D}_1\rpro$, $\lpro \der{D}'_2\rpro$, $\lpro \der{D}'_1\rpro$, $\lpro \der{D}'_2\rpro$ by
+	$\iota_{1, X_1}\colon X_1\to \lpro\der{D}_1\rpro$, $\iota_{1, X_2}\colon X_2\to \lpro\der{D}_1\rpro$, $\iota'_{1, X'_1}\colon X'_1\to \lpro\der{D}'_1\rpro$ and $\iota'_{2, X'_2}\colon X'_2\to \lpro\der{D}_1\rpro$.
+
+	Now that these preliminaries matters have been addressed, we will proceed with the rest of the proof.. We split the proof in three cases.
+	\begin{itemize}
+		\item $\lgh(\der{D}_1)=0$. Thus $\lgh(\der{D}'_1)=0$ too  and we have
+		\begin{align*}
+			(\der{D}, \alpha, \omega)&=(\der{D}_2, \alpha_2\circ \omega_1^{-1}\circ \alpha_1, \omega_2) \\ (\der{D}', \alpha', \omega')&=(\der{D}'_2, \alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1, \omega'_2)
+		\end{align*}
+		Moreover, in this case $\sigma$ must be $\id{\emptyset}$ and $\sigma+\tau$ must be equal to $\tau$. The thesis now follows from the commutativity of the following diagram.
+		\[\xymatrix@C=35pt{& G_{1,0}\ar[dd]^{\xi_{\id{\emptyset}}} \ar[dr]^{\omega^{-1}_1}&&G_{2,0}\ar[r]^-{\iota_{2, G_{2,0}}} & \lpro \der{D}_2\rpro \ar[dd]^{\xi_{\tau}}\\\pi(G_{1,0})  \ar[ur]^{\alpha_1} \ar[dr]_{\alpha'_1}&& \pi(G_{2,0}) \ar[ur]^{\alpha_2} \ar[dr]_{\alpha'_2}\\& G'_{1,0} \ar[ur]_{(\omega'_1)^{-1}}&&G'_{2,0} \ar[r]_-{\iota'_{2, G_{2,0}}}& \lpro \der{D}'_2\rpro}\]
+
+		\item $\lgh(\der{D}_2)=0$.  As before this implies that also $\lgh(\der{D}'_2)$ is $0$.  Applying \Cref{def:conc} we get 
+		\begin{align*}
+			(\der{D}, \alpha, \omega)&=(\der{D}_1, \alpha_1, \omega_1 \circ (\alpha_2)^{-1}\circ \omega_2) \\ (\der{D}', \alpha', \omega')&=(\der{D}'_1, \alpha'_1, \omega'_1 \circ (\alpha'_2)^{-1}\circ \omega'_2)
+		\end{align*}
+		Since $\der{D}_2$ is empty, then $\tau=\id{\emptyset}$ and $\sigma+\tau=\sigma$. Let $n$ be $\lg(\der{D}_1)$, as before the thesis follows from the diagram below.
+		\[\xymatrix@C=35pt{& G_{2,0}\ar[dd]^{\xi_{\id{\emptyset}}} \ar[dr]^{\alpha^{-1}_2}&&G_{1,n}\ar@{>->}[r]^-{\iota_{1, G_{1,n}}} & \lpro \der{D}_2\rpro \ar[dd]^{\xi_{\sigma_1}}\\\pi(G_{2,0})  \ar[ur]^{\omega_2} \ar[dr]_{\omega'_2}&& \pi(G_{1,n}) \ar[ur]^{\omega_1} \ar[dr]_{\omega'_1}\\& G'_{2,0} \ar[ur]_{(\alpha'_1)^{-1}}&&G'_{1,n} \ar@{>->}[r]_-{\iota'_{1, G_{1,n}}}& \lpro \der{D}'_2\rpro}\]
+		\item   $\lgh(\der{D}_1)\neq0$ and $\lgh(\der{D}_2)\neq 0$. Thus $\der{D}'_1$ and $\der{D}'_2$ are non-empty too. In this case we have:
+		\begin{align*}
+			(\der{D}, \alpha, \omega)&=(\der{D}_1*\omega_1^{-1}\cdot \alpha_2*\der{D}_2, \alpha_1, \omega_2)\\
+			(\der{D}', \alpha', \omega')&=(\der{D}'_1*(\omega'_1)^{-1}\cdot \alpha'_2*\der{D}'_2, \alpha'_1, \omega'_2)
+		\end{align*}
+
+		Let us assume that $\der{D}_1$, $\der{D}'_1$, $\der{D}_2$ and $\der{D}'_2$ are given by
+		\[\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^n \quad \der{D}'_1=\{\dder{D}'_{1,i}\}_{i=0}^n \quad \der{D}_2=\{\dder{D}_{2,i}\}_{i=0}^t \quad \der{D}_2'=\{\dder{D}'_{2,i}\}_{i=0}^t\]
+		By definition of consistent permutation, the rule applied by $\dder{D}_{1,i}$ and the one applied in $\dder{D}_{2,i}$  must coincide with, respectively, the one applied in $\dder{D}'_{1,i}$ and the one applied $\dder{D}'_{2,1}$.
+Let $\dder{D}_{1,i}$, $\dder{D}'_{1,i}$, $\dder{D}_{2,i}$ and $\dder{D}'_{2,i}$ be given, by the following four diagrams.
+		\[\xymatrix{L_{1,i} \ar[d]_{m_{1, i}}& K_{1,i} \ar[d]_{k_{1, i}} \ar[r]^{r_{1,i}} \ar@{>->}[l]_{l_{1,i}} & R_{1,i}\ar[d]^{h_{1, i}} &L_{1,i} \ar[d]_{m'_{1, i}}& K_{1,i} \ar[d]_{k'_{1, i}} \ar[r]^{r_{1,i}} \ar@{>->}[l]_{l_{1,i}} & R_{1,i}\ar[d]^{h'_{1, i}} \\G_{1,i} & D_{1,i} \ar[r]_{g_{1,i}} \ar@{>->}[l]^{f_{1,i}} & G_{1,i+1} & G'_{1,i} & D'_{1,i}\ar[r]_{g'_{1,i}} \ar@{>->}[l]^{f'_{1,i}}  & G'_{1,i+1}}\]
+		\[\xymatrix{L_{2,i} \ar[d]_{m_{2, i}}& K_{2,i} \ar[d]_{k_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h_{2, i}} &L_{2,i} \ar[d]_{m'_{2, i}}& K_{2,i} \ar[d]_{k'_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h'_{2, i}} \\G_{2,i} & D_{2,i} \ar[r]_{g_{2,i}} \ar@{>->}[l]^{f_{2,i}} & G_{2,i+1} & G'_{2,i} & D'_{2,i}\ar[r]_{g'_{2,i}} \ar@{>->}[l]^{f'_{2,i}}  & G'_{2,i+1}}\]
+	\end{itemize}
+	Let $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$, $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$, $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$ and $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$ be colimiting cocones.
+Define two other cocones and  $\der{D}'_1*(\omega'_1)^{-1}\cdot \alpha'_2*\der{D}'_2$
+	Using point $2$ of \Cref{lem:colim} we get two pushout squares
+	\[\xymatrix{\pi(H) & }\]
+	Now, notice that $()$ and $bb$ are cocones on ... so that there exists... such that. 
+\end{proof}
+
+\begin{corollary}\label{cor:presuffix}
 	\todo{prefisso e suffisso}
@@
 \begin{proof}
-	contenuto...\qedhere 
+	contenuto...
 \end{proof}

### 2023-12-15 fusione.tex
merge

@@
 
-\begin{example} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstraction equivalent non-empty decorated derivations of length $n+1$.
+\begin{example} RISCRIVERE Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstraction equivalent non-empty decorated derivations of length $n+1$.
 Then the identity permutation $\id{[0,n]}$ is a consistent permutation between them.

### 2023-12-15 fusione.tex

@@
 \end{remark}
-\iffalse 
-\begin{proposition}\label{prop:ident}
-Let $(\der{D}, \alpha, \omega)$ be a decorated derivation between $G$ and $H$ and  $(\der{D}',\alpha', \omega')$ be one between $G'$ and $H'$.
-Suppose, moreover that $G'$ and $H$ are isomorphic, so that $\pi(G')=\pi(H)$.
-Then the following hold true.
-\begin{enumerate}
-	\item If $\der{D}$ is the empty derivation, then
-	\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')\equiv_a (\der{D}',\alpha', \omega')\]
-	\item  If $\der{D}'$ is the empty derivation, then
-	\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')\equiv_a (\der{D},\alpha, \omega)\]
-\end{enumerate}
-\end{proposition}
-\begin{proof}
-\begin{enumerate}
-	\item 
-	By \Cref{def:conc}, we have that 
-	\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')= (\der{D}', \alpha'\circ \omega^{-1}\circ \alpha, \omega')\]
-
-	For every $X\in \Deltamin(\der{D'})$ we can define
-	\[\phi_{X}:=\begin{cases}
-		\alpha' \circ \alpha \circ \omega \circ (\alpha')^{-1} & X=G'\\
-		\id{X} & \text{otherwise}
-	\end{cases} \]
-	Now, we can notice that $\phi_{G'_0}$ is the composition $\alpha'\circ (\alpha'\circ \omega^{-1}\circ \alpha)^{-1}$, giving us the triangle
-
-\[\xymatrix@C=15pt{&\pi(G') \ar[dr]^{\alpha'} \ar[dl]_{\alpha'\circ \omega^{-1}\circ \alpha}\\ G'\ar[rr]_{\phi_{G'}} && G'} \]
-To conclude the proof it is now enough to show the commutativity of 
-	\[\xymatrix@C=40pt{G'&D'_0 \ar[r]^{g'_0} \ar[l]_{f'_0}&G'_{1}\\  L'_0 \ar[u]^{n'_0} \ar[d]_{n'_0}& K'_0 \ar[u]^{k'_0} \ar[d]_{k'_0} \ar[r]^{r'_0} \ar[l]_{l'_0} &R'_0\ar[u]^{h'_0} \ar[d]_{h'_0}\\G' \ar@/_.45cm/[uu]_(.35){\phi_{G'}}|\hole&D'_0\ar[l]^{f'_0}\ar@/_.45cm/[uu]_(.35){\id{D'_0}}|\hole \ar[r]_{g'_0}&G'_{1}\ar@/_.45cm/[uu]_{\id{G'_1}}}\]
-
-	\item \qedhere 
-\end{enumerate}
-\end{proof}
-
-\begin{remark}\label{rem:ident}Consider a decorated derivation $(\der{D}, \alpha, \omega)$ between $G$ and $H$ and another one $(\der{D}',\alpha', \omega')$ between $G'$ and $H'$.
-Suppose, moreover that $\pi(G')=\pi(H)$.
-By \Cref{rem:empty}, if $\der{D}$ is the empty derivation, so that $G=H$, then
-	\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')= ((\omega \circ (\alpha')^{-1}) *\der{D}', \alpha, \omega')\]
-
-Furthermore, we can notice that
-\[(\der{D}', \alpha', \omega')\equiv_a ((\omega \circ (\alpha')^{-1}) *\der{D}', \alpha, \omega')\]	
-Indeed, for every $X'\in \Deltamin(\der{D'})$ we can define
-\[\phi_{X'}:=\begin{cases}
-	(\alpha')^{-1} & X'=G'\\
-	\id{X'} & \text{otherwise}
-\end{cases} \]
-
-Similarly, if $\lgh(\der{D}')=0$, implying $G'=H'$, we get
-		\[(\der{D}, \alpha, \omega)\cdot (\der{D}',\alpha', \omega')=(\der{D}*\omega^{-1}, \alpha, \omega')\]
-
-We can notice, moreover, that 
-\[(\der{D}', \alpha', \omega')\equiv_a ((\omega \circ (\alpha')^{-1}) *\der{D}', \alpha, \omega') \qquad  (\der{D}, \alpha, \omega) \equiv_a (\der{D}*\omega^{-1}, \alpha, \omega')\] 	
-Indeed,  for every $X'\in \Deltamin(\der{D'})$ and $X\in \Deltamin(\der{D})$ we can define
-\[\phi_{X'}:=\begin{cases}
-	(\alpha')^{-1} & X'=G'_{0}\\
-	\id{X'} & \text{otherwise}
-\end{cases} \qquad \phi_{X}:=\begin{cases}
-\id{X} & \text{otherwise}\\
-\omega^{-1} & X=H\\
-\end{cases}\]
-
-first of all notice that the triangles below commute.
-\[\xymatrix@C=15pt{&\pi(G'_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G\ar[rr]_{\phi} && G' &G' \ar[rr]_{\phi} && G' } \]
-
-Furthermore, for every $X\in $ $i\in [0, \lgh(\der{D})]$
-
-\end{remark}
-\fi
-
-The next proposition justifies the use of decorations, guaranteeing that concatenation of abstract decorated derivations is weel-defined.
+
+The next proposition justifies the use of decorations, guaranteeing that concatenation of abstract decorated derivations is well-defined.
 \begin{lemma}\label{lem:conc}

### 2023-12-19 fusione.tex
intro draft

@@
 \todo{A VERY NICE INTRODUCTION}
+
+SOME IDEAS (BADLY WRITTEN, JUST TO START TO PUT IDEAS IN ORDER)
+
+Graph-like structures are used in uncountably many setting for representing the dynamic of software systems: the graph represents the entities in the states and their relations, while rewriting steps, modifying the graph, are used to model events which produce state changes.
+
+Rewriting over graph-like structures is elegantly captured by
+DPO-rewriting over adhesive categories and variants.  This has been
+largely studied for so-called linear rewriting rules. Roughly
+speaking, with linear rules a rewriting step can express the fact that
+some entities in the current state are removed, some other are needed
+for the rewriting step to occur but preserved and some new entities
+are generated.
+
+The computation described by a rewriting system can be naturally
+interpreted as a distributed computation and a notion of independence
+between rewriting steps naturally emerges. When different rules are
+applied at ``distinct'' parts of the state, possibly overlapping on
+preserved items, the rewriting steps can be naturally deemed as
+independent and their application can occur in any order and possibly
+concurrently. This phenomenon is formally captured by the so-called
+Church-Rosser theorem of DPO rewriting. This represent the basis for
+viewing sequences of rewriting in the DPO approach as concurrent
+computations and derive corresponding concurrent semantics. Derivation
+traces can be quotiented by an equivalence relation which identifies
+sequences of rewritings which differs only for the order of
+independent steps, leading to so-called derivation traces. In turn,
+the dependencies this setting can be captured by a classical structure
+in concurrency theory, the so-called prime event structures where
+dependencies are reduced to causality and conflict.
+
+It can be the case that linear rules are not sufficiently expressive for capturing the dynamic of a system.
+This is the case when  a computational step is required not only to consume, preserve and generated, but also ``merge'' parts of the state.
+This happens, e.g., in nominal calculi where, as a result of name passing, the received name is identified with a local one at the receiver, in the modelling of bonding in biological/chemical processes, add EGGS, something about string diagrams?
+
+Technically, describing fusions requires to move from linear to left-linear rewriting rules.
+While left-linear rules have been considered in various instances (mainly for graph rewriting( and some results concerning the corresponding rewriting theory have been put forward, to the best of our knowledge the phenomena arising when rewriting with left-linear rules in the general setting of adhesive categories (which capture most ``applications'') have not been systematically explored.
+
+Here we perform this exploration by observing that a number of basic
+properties of rewriting which play a role in the corresponding
+rewriting and concurrency theory need a deep rethinking for
+left-linear rules and we propose solutions for the problems which
+arise.
+
+Firstly, Church-Rosser theorem does not work out of the box: the independence condition for adhesive categories does not extend smoothly to left-linear rules, i.e., existence of an independence pair does not ensure the possibility of switching two derivation and a refined notion, involving the concept of a so-called filler has to be introduced.
+The problem was identified already in ...
+where a suitable subclass of adhesive categories is identified where independence as induced by a filler coincide with independence as induced by an independence pair.
+
+Having a notion of independence between computation steps sits at the core of the possibility of viewing an execution trace as a concurrent computation.
+This is obtained by considering traces up to an equivalence that identifies traces differing only for the order of independent steps (e.g., interchange law [?] in term rewriting, shift equivalence [?] in graph rewriting or permutation equivalence [?] in lambda-calculus).
+While for linear rewriting systems this works smoothly, for left-linear ones one has to face the problem that if two rewriting steps $r_a r_b$ are independent, if we switch $r_a$ after $r_a$ and then switch it back we can obtain a computation which is not the original one, making the theory of derivation traces inconsistent.
+In order to solve this problem, we work in a subclass of adhesive categories where derivation steps can be switched in an ``essentially unique way''.
+We also identify a large class of adhesive categories, arising as presheaves, where the condition is automatically satisfied.
+[this solves also the previous problem, right;
+
+Additionally, a central property for linear rewriting systems is the fact that independence of two rewriting steps is a global notion, independently of the context in which the rewritings take place.
+This is at the basis of the possibility of capturing the dependencies between rewriting steps in terms of two basic relations, causality and conflict, investigated in ...
+
+This fails for left-linear rules where, as observed in ...
+for graph rewriting, the possibility of merging parts of the state leads to a sort of disjunctive causality, i.e., a rewriting step, say $r_c$ can be enabled by two different rewriting steps $r_a$ and $r_b$, in a way that in a derivation $r_a r_b r_c$ steps $r_b$ and $r_c$ are independent since the presence of $r_a$ in the past is sufficient for enabling $r_a$, while in $r_b r_c r_a$ , the steps $r_b$ and $r_c$ are not independent.
+The paper shows that for left-linear rewriting systems a special form of globality of independence can be recovered.
+
+The concurrent semantics of linear graph rewriting systems over adhesive categories can be captured by prime event structures and prime algebraic domains [extend] [...].
+This is extended to adhesive categories in   [IS THIS IN TOBIAS?]
+
+In [...] it is observed for graph rewriting systems that the presence of fusions, the same event can be enabled by different minimal sets of events, thus preventing the identification of a proper notion of causality and making prime event structures and prime domain inadequate.
+It is argued that the right class of structures capturing the concurrent behaviour in the presence of fusion are connected event structures and weak prime algebraic domains.
+This is worked out for DPO rewriting systems over graphs.
+However the proof relies on a characterisation of independence which fails for non linear rules.
+Here we correct that result and extend it to DPO rewriting over a large class of adhesive categories.
 
@@
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2023-12-28 fusione.tex
permutazioni

--- 2023-12-15 fusione.tex
@@
 %\usepackage{etex}
-
 \usepackage[all]{xy}
-\newdir^{ (}{{}*!/-5pt/@^{(}}
 \SelectTips{cm}{}
@@
 	\end{enumerate} 
-	We will use $m\colon X\mto Y$ to denote that an arrow $m:X\to Y$ belongs to $\mathcal{M}$. $\X$ is said to be \emph{$\mathcal{M}$-adhesive} if
+	We will use $m\colon X\mto Y$ to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$. $\X$ is said to be \emph{$\mathcal{M}$-adhesive} if
 	\begin{enumerate}
@@
 Let $(\der{D},\alpha, \omega)$ be an empty derivation from an object $G$ and  $(\der{D}',\alpha', \omega')$ a another empty one from $G'$.
-If $(\der{D},\alpha, \omega)\equiv_a(\der{D}',\alpha', \omega')$ then an abstraction equivalence between $\der(D)$ and $\der{D}'$ is just an isomorphism $\phi\colon G\to G'$, so that $\pi(G)=\pi(G')$.
+If $(\der{D},\alpha, \omega)\equiv_a(\der{D}',\alpha', \omega')$ then an abstraction equivalence between $\der{D}$ and $\der{D}'$ is just an isomorphism $\phi\colon G\to G'$, so that $\pi(G)=\pi(G')$.
 Moreover, such isomorphism must fit in the diagrams below.
@@
 
-\begin{example}\label{rem:absequi}
-	Let $\der{D}$ be a derivation with source $G$ and target $H$. Let also $\phi:G'\to G$ and $\psi:H\to H'$ be two isomorphisms. Then for every $X\in \Deltamin(\der{D})$ we can define 
+\begin{remark}\label{rem:absequi}
+	Let $\der{D}$ be a derivation with source $G$ and target $H$. Let also $\phi\colon G'\to G$ and $\psi\colon H\to H'$ be two isomorphisms. Then for every $X\in \Deltamin(\der{D})$ we can define 
 	\[\varphi_X:=\begin{cases}
 		\phi^{-1} & X=G\\
+		\id{X} & \text{otherwise}
+	\end{cases} \qquad \varphi'_X:=\begin{cases}
 	\psi & X=H\\
@@
 	\end{cases}\]
-
-It is immediate to see that the family $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ is an abstraction equivalence between $\der{D}$ and $\phi *\der{D}*\psi$.	
-\end{example}
+It is immediate to see that the family $\{\varphi_X\}_{X\in \Deltamin(\der{D})}$ is an abstraction equivalence between $\der{D}$ and $\phi *\der{D}$, while $\{\varphi'_X\}_{X\in \Deltamin(\der{D})}$ is one between $\der{D}$ and $\der{D}*\psi$.
+\end{remark}
 
@@
 		\item Let us proceed by induction on the length of $\der{D}$.
-		\begin{itemize}
-			\item  $\lgh(\dder{D})=0$. then the $\tpro{\dder{D}}$ is simply $(G, \{\id{G}\})$ and $\id{G}\in \mathcal{M}$.¸
-			\item $\lgh(\dder{D})=0$. Suppose that $\dder{D}$ has as its single component the derivation
+
+	\smallskip \noindent $\lgh(\dder{D})=0$. then the $\tpro{\dder{D}}$ is simply $(G, \{\id{G}\})$ and $\id{G}\in \mathcal{M}$.¸
+
+	\smallskip \noindent$\lgh(\dder{D})=1$. Suppose that $\dder{D}$ has as its single component the derivation
 			\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G& \ar@{>->}[l]^{f} D \ar[r]_{g}& H  \\}\]
@@
 			Since $p\in \mathcal{M}$, the thesis follows immediately from \Cref{rem:cof}.
-			\item $\lgh(\dder{D})\geq 2$.
+
+	\smallskip \noindent$\lgh(\dder{D})\geq 2$.
 Let $\der{D}$ be $\{\dder{D}_i\}_{i=0}^n$ with $n\geq 1$.
@@
 			Therefore the arrows $c'$ and $c_H$ induce a morphism $c\colon P\to C$ and the thesis now follows at once.
-		\end{itemize}
 
@@
 \begin{remark}\label{rem:comp} Consistent permutations can be composed.
-Indeed, given decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$ all of length $n$, if $\sigma$ is a consistent permutation between the first two and $\sigma'$ one between the second and the third, then  we have diagrams
-	\[\xymatrix@C=18pt{ & G_0 \ar[rr]^{\iota_{G_0}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_{n} \ar@{>->}[rr]^{\iota_{ G_{n}}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G_0) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G'_0 \ar[rr]^{\iota'_{G'_0}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&\pi({ G_{n}})\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & { G'_{n}} \ar@{>->}[rr]^{\iota'_{{ G'_{n}}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_0  \ar[rr]_{\hat{\iota}_{\hat{G}_0}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_n \ar@{>->}[rr]_{\hat{\iota}_{\hat{G}_n}}&& \lpro \hat{\der{D}} \rpro \\& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_{\sigma'(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\sigma'(\sigma(i))} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}} \rpro	}\]
-	We deduce at once that $\sigma'\circ \sigma$ is a consistent permutation with mediating isomorphism given by $\xi_{\sigma'} \circ \xi_\sigma$.
-\end{remark}
-
-\begin{example} RISCRIVERE Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstraction equivalent non-empty decorated derivations of length $n+1$.
-Then the identity permutation $\id{[0,n]}$ is a consistent permutation between them.
-In such a case $\xi_{\id{[0,n]}}$ is simply the isomorphism induced by any abstraction equivalence $\{\phi_X\}_{X\in \Delta(X)}$.
-
-	If $\der{D}$ and $\der{D}'$ are empty, then the converse also holds: indeed in such a case a mediating isomorphism provides the wanted abstraction equivalence.
+Indeed, given decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$ all of length $n$, if $\sigma$ is a consistent permutation between the first two and $\tau$ one between the second and the third, then  we have diagrams
+	\[\xymatrix@C=18pt{ & G_0 \ar[rr]^{\iota_{G_0}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_{n} \ar@{>->}[rr]^{\iota_{ G_{n}}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G_0) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G'_0 \ar[rr]^{\iota'_{G'_0}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\tau}}&\pi({ G_{n}})\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & { G'_{n}} \ar@{>->}[rr]^{\iota'_{{ G'_{n}}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\tau}}\\ &\hat{G}_0  \ar[rr]_{\hat{\iota}_{\hat{G}_0}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_n \ar@{>->}[rr]_{\hat{\iota}_{\hat{G}_n}}&& \lpro \hat{\der{D}} \rpro \\& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\tau(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\tau}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\tau(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\tau}}\\ &\hat{G}_{\tau(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\tau(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\tau(\sigma(i))} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\tau(\sigma(i))}}}&& \lpro \hat{\der{D}} \rpro	}\]
+	We deduce at once that $\tau\circ \sigma$ is a consistent permutation with mediating isomorphism given by $\xi_{\tau} \circ \xi_\sigma$.
+\end{remark}
+
+\begin{remark} \label{ex:abscons}Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstraction equivalent non-empty decorated derivations of length $n+1$.
+Then the identity permutation $\id{[0,n]}\colon [0,n]\to [0,n]$ is a consistent permutation between them.
+In such a case we can take as $\xi_{\id{[0,n]}}\colon \tpro{D}\to \lpro \der{D}'\rpro$ simply the isomorphism induced by any abstraction equivalence $\{\phi_X\}_{X\in \Delta(X)}$.
+
+Given a decorated derivation $(\der{D}, \alpha, \omega)$ with source $G$ and target $H$ and two isomorphisms, $\phi\colon G'\to G$ $\psi\colon H\to H'$ be two isomorphisms, we know, by \Cref{rem:absequi}, that \[(\der{D}, \alpha, \omega)\equiv_a (\phi*\der{D}, \phi^{-1}\circ \alpha, \omega ) \qquad (\der{D}, \alpha, \omega)\equiv_a (\der{D}*\psi, \alpha, \psi \circ \omega )\]
+In these cases, if $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$, $(\lpro \phi *\der{D} \rpro, \{\iota'_X\}_{X\in \Delta(\der{D})})$ and $(\lpro \der{D}*\psi \rpro, \{\iota'_X\}_{X\in \Delta(\der{D})})$ are colimiting cocones, we can take as mediating isomorphisms, respectively, the unique arrows $\Gamma^{\phi} \colon \tpro{D}\to \lpro \phi*\der{D} \rpro$ and $\Gamma_\psi\colon \tpro{D}\to \lpro \der{D}*\psi \rpro$  such that, for every $X\in \Deltamin(\der{D})$:
+\[\Gamma^\phi \circ \iota_X:=\begin{cases}
+\iota'_{G'}\circ \phi^{-1}  & X=G'\\
+\iota'_X & \text{otherwise}
+\end{cases} \qquad \Gamma_\psi \circ \iota_X:=\begin{cases}
+\hat{\iota}_{H'}\circ \psi  & X=H'\\
+\hat{\iota}_X & \text{otherwise}
+\end{cases}\]
+\end{remark}
+
+\begin{remark}\label{ex:empty}
+	If $\der{D}$ and $\der{D}'$ are empty, then the converse also holds. If $\id{\emptyset}$ is a consistent permutation, then a mediating isomorphism provides an abstraction equivalence.
+\end{remark}
+
+\begin{example}\todo{identità consistente non implica astrazione}Notice that the \Cref{ex:empty} cannot, in general, be generalized to non-empty derivations. A counterexample si the following one.
 \end{example}
 
-\begin{example}\todo{identità consistente non implica astrazione}
-\end{example}
-
 \begin{proposition}\label{prop:uniqu}
-	Let $\sigma,\sigma'\colon [0,n]\rightrightarrows [0,n]$ be two consistent permutations between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.  Then the following hold true:
+	Let $\sigma,\tau\colon [0,n]\rightrightarrows [0,n]$ be two consistent permutations between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.  Then the following hold true:
 	\begin{enumerate}
-	\item $\xi_\sigma \circ \iota_{G_0} = \xi_{\sigma'} \circ \iota_{G_0}$;
-	\item  $\xi_\sigma \circ \iota_{G_i}=\xi_{\sigma'} \circ \iota_{G_i}$ for every index $i\in [0,n]$ such that $\sigma_{|[0,i]}=\sigma'_{|[0,i]}$.
+	\item $\xi_\sigma \circ \iota_{G_0} = \xi_{\tau} \circ \iota_{G_0}$;
+	\item  $\xi_\sigma \circ \iota_{G_i}=\xi_{\tau} \circ \iota_{G_i}$ for every index $i\in [0,n]$ such that $\sigma_{|[0,i]}=\tau_{|[0,i]}$.
 	\end{enumerate}
@@
 \begin{proof}\begin{enumerate}
-		\item This follows at once noticing that both $\xi_\sigma \circ \iota_{G_0}$ and $\xi_{\sigma'} \circ \iota_{G_0}$ are equal to $\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}$.
-		\item  If $\sigma(0)\neq \sigma'(0)$ there is nothing to show. Otherwise, let $j$ be the maximum of the set
-		\[\{i\in [0,n]\mid \sigma_{|[0,i]}=\sigma'_{|[0,i]}\}\]
+		\item This follows at once noticing that both $\xi_\sigma \circ \iota_{G_0}$ and $\xi_{\tau} \circ \iota_{G_0}$ are equal to $\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}$.
+		\item  If $\sigma(0)\neq \tau(0)$ there is nothing to show. Otherwise, let $j$ be the maximum of the set
+		\[\{i\in [0,n]\mid \sigma_{|[0,i]}=\tau_{|[0,i]}\}\]
 		We proceed by induction on $i\in [0,j]$. 
@@
 			\begin{align*}
-				\xi_\sigma \circ \iota_{G_i}\circ h_{i-1}&=  \xi_\sigma\circ \iota_{R_{i-1}}\\&=\iota'_{R_{\sigma(i-1)}}\\&=\iota'_{R_{\sigma'(i-1)}}\\&=\xi_{\sigma'}\circ \iota_{R_{i-1}}\\&=\xi_{\sigma'} \circ \iota_{G_i}\circ h_{i-1}
+				\xi_\sigma \circ \iota_{G_i}\circ h_{i-1}&=  \xi_\sigma\circ \iota_{R_{i-1}}\\&=\iota'_{R_{\sigma(i-1)}}\\&=\iota'_{R_{\tau(i-1)}}\\&=\xi_{\tau}\circ \iota_{R_{i-1}}\\&=\xi_{\tau} \circ \iota_{G_i}\circ h_{i-1}
 			\end{align*}
@@
 			\begin{align*}
-				\xi_\sigma \circ \iota_{G_i}\circ g_{i-1}&=\xi_{\sigma}\circ \iota_{D_{i-1}}\\&=\xi_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi_{\sigma'}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi_{\sigma'}\circ \iota_{D_{i-1}} \\&=\xi_{\sigma'}\circ \iota_{G_{i}} \circ g_{i-1}
+				\xi_\sigma \circ \iota_{G_i}\circ g_{i-1}&=\xi_{\sigma}\circ \iota_{D_{i-1}}\\&=\xi_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi_{\tau}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi_{\tau}\circ \iota_{D_{i-1}} \\&=\xi_{\tau}\circ \iota_{G_{i}} \circ g_{i-1}
 			\end{align*}
@@
 \begin{lemma} Let $(\X,R)$ be a left-linear DPO-rewriting system.
-Consider two consistent permutation $\sigma,\sigma'\colon [0,n]\rightrightarrows [0,n]$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
-Suppose that $\sigma\neq \sigma'$ and let $j$ be the minimum index such that $\sigma(j)\neq \sigma'(j)$.
+Consider two consistent permutation $\sigma,\tau\colon [0,n]\rightrightarrows [0,n]$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
+Suppose that $\sigma\neq \tau$ and let $j$ be the minimum index such that $\sigma(j)\neq \tau(j)$.
 Let also $r(\der{D})$ be $\{\rho_i\}_{i=0}^n$.
@@
 \begin{proof}\begin{enumerate}
-		\item Let $k$ be $\sigma^{-1}(\sigma'(0))$ and notice that, since $\sigma(0)\neq \sigma'(0)$, then $0< k$.  By  the first point of  \Cref{prop:uniqu} we can consider the diagram
-		\[\xymatrix@C=40pt{& L_0 \ar[d]_{m'_{\sigma'(0)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{0}} \\G_{0} \ar@/_.2cm/[drr]_(.3){\iota_{G_0}}|(.515)\hole \ar[d]_{\iota_{G_0}}& G'_{\sigma'(0)} \ar[d]^{\iota_{G'_{\sigma'(0)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\sigma'}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
+		\item Let $k$ be $\sigma^{-1}(\tau(0))$ and notice that, since $\sigma(0)\neq \tau(0)$, then $0< k$.  By  the first point of  \Cref{prop:uniqu} we can consider the diagram
+		\[\xymatrix@C=40pt{& L_0 \ar[d]_{m'_{\tau(0)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{0}} \\G_{0} \ar@/_.2cm/[drr]_(.3){\iota_{G_0}}|(.515)\hole \ar[d]_{\iota_{G_0}}& G'_{\tau(0)} \ar[d]^{\iota_{G'_{\tau(0)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\tau}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
 	From \Cref{cor:ele}, we can conclude that there exists $c\colon L_0\to D_0$ such that $f_0\circ c=m_0$. We thus have the solid part of the commutative diagram below.
@@
 The thesis now follows from \Cref{cor:rego}.
-		\item  Let $k$ be $\sigma^{-1}(\sigma'(j-1))$ and notice that $\rho_{j-1}=\rho_k$.
-By definition of $j$, $\sigma_{|[0,j-1]}=\sigma'_{|[0,j-1]}$, thus the second point of \Cref{prop:unique} yields the diagram
-			\[\xymatrix@C=40pt{& L_{j-1} \ar[d]_{m'_{\sigma'(j-1)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{j-1}} \\G_{j-1} \ar@/_.2cm/[drr]_(.3){\iota_{G_{j-1}}}|(.515)\hole \ar[d]_{\iota_{G_{j-1}}}& G'_{\sigma'(j-1)} \ar[d]^{\iota_{G'_{\sigma'(j-1)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\sigma'}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
+		\item  Let $k$ be $\sigma^{-1}(\tau(j-1))$ and notice that $\rho_{j-1}=\rho_k$.
+By definition of $j$, $\sigma_{|[0,j-1]}=\tau_{|[0,j-1]}$, thus the second point of \Cref{prop:unique} yields the diagram
+			\[\xymatrix@C=40pt{& L_{j-1} \ar[d]_{m'_{\tau(j-1)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{j-1}} \\G_{j-1} \ar@/_.2cm/[drr]_(.3){\iota_{G_{j-1}}}|(.515)\hole \ar[d]_{\iota_{G_{j-1}}}& G'_{\tau(j-1)} \ar[d]^{\iota_{G'_{\tau(j-1)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\tau}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
 			Let $a$ be $\min(j-1, k)$, by \Cref{cor:ele},  there exists $c\colon L_{j-1}\to D_a$ such that $f_a\circ c=m_a$. As before this yields the solid part of the following diagram
@@
 	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)\]
-	If $\sigma\colon [0, \lgh(\der{D}_1)-1]\to [0, \lgh(\der{D}_1)-1]$ is a consistent permutation between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$ and $\tau:[0, \lgh(\der{D}_2)-1]\to [0, \lgh(\der{D}_2)-1]$ one between $(\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$, then
-	\[\sigma+\tau\colon[0, \lgh(\der{D})-1]\to[0, \lgh(\der{D})-1] \qquad n \mapsto \begin{cases}
-		\sigma(n) & n < \lgh(\der{D}_1)\\
-		\tau(n-\lgh(\der{D}_1)) &   \lgh(\der{D}_1) \leq n
+	Given a consistent permutation $\sigma\colon [0, \lgh(\der{D}_1)-1]\to [0, \lgh(\der{D}_1)-1]$ between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$ and another $\tau:[0, \lgh(\der{D}_2)-1]\to [0, \lgh(\der{D}_2)-1]$ between $(\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$, then
+	\[\sigma+\tau\colon[0, \lgh(\der{D})-1]\to[0, \lgh(\der{D})-1] \quad i \mapsto \begin{cases}
+		\sigma(i) & i < \lgh(\der{D}_1)\\
+		\lgh(\der{D}_1)+\tau(i-\lgh(\der{D}_1)) &   i\geq \lgh(\der{D}_1) 
 	\end{cases}\]
@@
 	$\iota_{1, X_1}\colon X_1\to \lpro\der{D}_1\rpro$, $\iota_{1, X_2}\colon X_2\to \lpro\der{D}_1\rpro$, $\iota'_{1, X'_1}\colon X'_1\to \lpro\der{D}'_1\rpro$ and $\iota'_{2, X'_2}\colon X'_2\to \lpro\der{D}_1\rpro$.
+Similarly, given $X\in \Delta(\der{D})$ and $\X'\in \Delta(\der{D}')$ we will use $\iota_X:X\to \tpro{D}$ and $\iota'_{X'}:X'\to \lpro \der{D}' \rpro$ for the coprojections.
 
 	Now that these preliminaries matters have been addressed, we will proceed with the rest of the proof.. We split the proof in three cases.
-	\begin{itemize}
-		\item $\lgh(\der{D}_1)=0$. Thus $\lgh(\der{D}'_1)=0$ too  and we have
+
+	\smallskip \noindent $\lgh(\der{D}_1)=0$. Thus $\lgh(\der{D}'_1)=0$ too  and we have
 		\begin{align*}
@@
 
-		\item $\lgh(\der{D}_2)=0$.  As before this implies that also $\lgh(\der{D}'_2)$ is $0$.  Applying \Cref{def:conc} we get 
+	\smallskip \noindent$\lgh(\der{D}_2)=0$.  As before this implies that also $\lgh(\der{D}'_2)$ is $0$.  Applying \Cref{def:conc} we get 
 		\begin{align*}
@@
 		\[\xymatrix@C=35pt{& G_{2,0}\ar[dd]^{\xi_{\id{\emptyset}}} \ar[dr]^{\alpha^{-1}_2}&&G_{1,n}\ar@{>->}[r]^-{\iota_{1, G_{1,n}}} & \lpro \der{D}_2\rpro \ar[dd]^{\xi_{\sigma_1}}\\\pi(G_{2,0})  \ar[ur]^{\omega_2} \ar[dr]_{\omega'_2}&& \pi(G_{1,n}) \ar[ur]^{\omega_1} \ar[dr]_{\omega'_1}\\& G'_{2,0} \ar[ur]_{(\alpha'_1)^{-1}}&&G'_{1,n} \ar@{>->}[r]_-{\iota'_{1, G_{1,n}}}& \lpro \der{D}'_2\rpro}\]
-		\item   $\lgh(\der{D}_1)\neq0$ and $\lgh(\der{D}_2)\neq 0$. Thus $\der{D}'_1$ and $\der{D}'_2$ are non-empty too. In this case we have:
+
+	\smallskip \noindent $\lgh(\der{D}_1)\neq0$ and $\lgh(\der{D}_2)\neq 0$. Thus $\der{D}'_1$ and $\der{D}'_2$ are non-empty too. In this case we have:
 		\begin{align*}
@@
 		\[\xymatrix{L_{2,i} \ar[d]_{m_{2, i}}& K_{2,i} \ar[d]_{k_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h_{2, i}} &L_{2,i} \ar[d]_{m'_{2, i}}& K_{2,i} \ar[d]_{k'_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h'_{2, i}} \\G_{2,i} & D_{2,i} \ar[r]_{g_{2,i}} \ar@{>->}[l]^{f_{2,i}} & G_{2,i+1} & G'_{2,i} & D'_{2,i}\ar[r]_{g'_{2,i}} \ar@{>->}[l]^{f'_{2,i}}  & G'_{2,i+1}}\]
+
+		%Let $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$, $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$, $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$ and $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$ be colimiting cocones.
+		By the second point of \Cref{lem:colim} and by \Cref{ex:abscons} we get the following diagram, in which the two solid squares are pushouts:
+		\[\xymatrix@C=45pt@R=30pt{\pi(G_{2,0}) \ar@/^.4cm/[rrr]^{\id{\pi(G_{2,0})}}\ar@{>->}[d]_{\iota_{1, G_{1,n+1}} \circ \omega_1}\ar[r]_{\iota_{2, G_{2,0}} \circ \alpha_2}& \lpro \der{D}_2 \rpro \ar@{>->}[d]^{p_2}\ar[r]_{\xi_\tau} & \lpro \der{D}'_2 \rpro \ar@{>->}[d]_{p'_2} &\pi(G'_{2,0}) \ar@{>->}[d]^{\iota'_{1, G'_{1,n+1}} \circ \omega'_1} \ar[l]^{\iota'_{2, G'_{2,0}} \circ \alpha'_2}\\ \lpro \der{D}_1 \rpro \ar@/_.4cm/[rrr]_{\xi_\sigma} \ar[r]^{p_1} & \tpro{D} \ar@{.>}[r]^{\xi_{\sigma+\tau}} & \lpro \der{D}'\rpro & \lpro \der{D}'_1\rpro  \ar[l]_{p'_1}}\]
+
+Moreover, we can pont out that, for every index $i\in [0,n+t+2]$ we have
+
+\[\iota_{G_i}=\begin{cases}p_1\circ \iota_{1, G_{1,i}} & i \leq n\\
+	p_1\circ \iota_{1, G_{1, i}}\circ \omega_1& i=n+1\\
+p_2\circ \iota_{2, G_{2,i-(n+1)}} & i > n+1 
+\end{cases} \qquad \iota'_{G'_i}=\begin{cases}p'_1\circ \iota'_{1, G'_{1,i}} & i \leq n\\
+p'_1\circ \iota'_{1, G'_{1, i}}\circ \omega'_1& i=n+1\\
+p'_2\circ \iota'_{2, G'_{2,i-(n+1)}} & i > n+1 
+\end{cases}\]
+
+Now, on the one hand, the existence of the dotted arrow $\xi_{\sigma+\tau}\colon \tpro{D}\to \lpro \der{D}'\rpro$ in the diagram above follows from the following computation:
+	\begin{align*}
+		p'_1\circ \xi_\sigma \circ \iota_{1, G_{1,n+1}} \circ \omega_1&=p'_1\circ \iota'_{1,G'_{1, n+1}} \circ \omega'_1\\&= p'_2 \circ \iota'_{2, G'_{2,0}} \circ \alpha'_2\\&=p'_2\circ \xi_\tau \circ \iota_{2, G_{2,0}} \circ \alpha_2
+	\end{align*} 
+On the other hand, we can repeat the same computation for $\xi^{-1}_\sigma$ and $\xi^{-1}_\tau$ to get
+\begin{align*}
+	p_1\circ \xi^{-1}_\sigma \circ \iota'_{1, G'_{1,n+1}} \circ \omega'_1&=p_1\circ \iota_{1,G_{1, n+1}} \circ \omega_1\\&= p_2 \circ \iota_{2, G_{2,0}} \circ \alpha_2\\&=p_2\circ \xi^{-1}_\tau \circ \iota'_{2, G'_{2,0}} \circ \alpha'_2
+\end{align*} 
+Hence there exists a $\psi\colon \lpro \der{D}'\rpro \to \tpro{D}$ such that:
+\[\psi \circ p'_1=p_1\circ \xi^{-1}_\sigma \qquad \psi \circ p'_2=p_2\circ \xi^{-1}_\tau\]
+Furthermore, the computations below show that $\psi$ is the inverse of $\xi_\sigma$.
+\[\begin{split}
+	\psi \circ \xi_{\sigma+\tau}\circ  p_1&=\psi \circ p'_1\circ \xi_\sigma \\&=p_1\circ \xi^{-1}_{\sigma}\circ \xi_\sigma\\&=p_1\\\\
+	\xi_{\sigma+\tau}\circ \psi \circ p'_1&=\xi_{\sigma+\tau}\circ p_1\circ \xi^{-1}_\sigma \\&=p'_1\circ \xi_{\sigma}\circ \xi^{-1}_\sigma\\&=p'_1
+\end{split}\qquad \begin{split}
+	\psi \circ \xi_{\sigma+\tau}\circ  p_2&=\psi \circ p'_2\circ \xi_\tau \\&=p_2\circ \xi^{-1}_{\tau}\circ \xi_\tau\\&=p_2\\ \\ 	\xi_{\sigma+\tau}\circ \psi \circ p'_2&=\xi_{\sigma+\tau}\circ p_2\circ \xi^{-1}_\tau \\&=p'_2\circ \xi_{\tau}\circ \xi^{-1}_\tau\\&=p'_2
+\end{split}\]
+To conclude we have to show that $\xi_{\sigma+\tau}$ fits in the diagrams of \Cref{def:permcon}. For the first two diagrams we have:
+\begin{align*}
+	\xi_{\sigma+\tau} \circ \iota_{G_{0}}\circ \alpha&=\xi_{\sigma+\tau} \circ p_1 \circ \iota_{1,G_{1,0}}\circ \alpha_1\\&=p_1'\circ \xi_\sigma \circ  \iota_{1,G_{1,0}} \alpha_1\\&=p'_1\circ \iota'_{1, G'_{1,0}}\circ \alpha'_1\\&=\iota'_{G'_0}\circ \alpha'
+\end{align*} 
+and
+ \begin{align*}
+\xi_{\sigma+\tau} \circ \iota_{G_{n+t+2}}\circ \omega&=\xi_{\sigma+\tau} \circ p_2 \circ \iota_{2,G_{2,t+1}}\circ \omega_2\\&=p'_2\circ \xi_\tau \circ  \iota_{2,G_{2,t+1}} \omega_2\\&=p'_2\circ \iota'_{2, G'_{2,t+1}}\circ \omega'_2\\&=\iota'_{G'_{n+t+2}}\circ \omega'
+\end{align*}
+
+Let $i$ be an index in $[0, n+t+1]$, we proceed splitting the cases.
+\begin{itemize}
+	\item $i$ is in $[0,n]$. Then we have
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_i} \circ m_i &= \xi_{\sigma+\tau} \circ p_1\circ \iota_{1, G_{1,i}}\circ m_{1,i}\\&=p'_1 \circ \xi_\sigma \circ \iota_{1, G_{1,i}}\circ m_{1,i}\\&= p'_1\circ \iota'_{1, G'_{1,\sigma(i)}}\circ m'_{1,\sigma(i)}\\&=\iota'_{G'_{\sigma(i)}}\circ m'_{\sigma(i)}
+	\end{align*}
+	Now, suppose that $i\neq n$, then 
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i &= \xi_{\sigma+\tau} \circ p_1\circ \iota_{1, G_{1,{i+1}}}\circ h_{1,i}\\&=p'_1\circ \xi_\sigma \circ \iota_{1, G_{1,{i+1}}}\circ h_{1,i}\\&= p'_1\circ \iota'_{1, G'_{1,\sigma(i)+1}}\circ h'_{1,\sigma(i)}
+	\end{align*}
+	and we have two subcases. If $\sigma(i)\neq n$, then \[h'_{1, \sigma(i)}=h'_{\sigma(i)} \qquad p'_1\circ \iota'_{1, G'_{1,\sigma(i)+1}}=
+	\iota'_{G'_{\sigma(i)+1}}\] 
+	and we can conclude. Otherwise, we have
+	\begin{align*}p'_1\circ \iota'_{1, G'_{1,n+1}}\circ h'_{1,n}&=p'_1 \circ \iota'_{1,G'_{1,n+1}} \circ \omega'_1\circ (\omega')^{-1}_1 \circ h'_{1,n}\\&=\iota'_{G'_{n+1}}\circ h'_n
+	\end{align*}
+yielding again the wanted equality
+	\[\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i=\iota'_{G'_{\sigma(i)+1}}\circ h'_{\sigma(i)}\]
+	Finally, if $i=n$ we get
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ h_n &= \xi_{\sigma+\tau} \circ \iota_{\pi(G_{1,n+1})} \circ \omega^{-1}_1\circ h_{1,n}\\&= \xi_{\sigma+\tau} \circ p_1\circ \iota_{1, G_{1,n+1}} \circ \omega_1 \circ \omega^{-1}_1 \circ h_{1,n}\\&=p'_1 \circ \xi_\sigma \circ \iota_{1, G_{1,n+1}} \circ h_{1,n}\\&=p'_1\circ \iota'_{1, G_{1,\sigma(n)+1}} \circ h'_{1,\sigma(n)}
+	\end{align*}
+	We have again two cases. If $\sigma(n)\neq n$ then we can conclude at once since 
+	\[h'_{1, \sigma(n)}=h'_{\sigma(n)} \qquad p'_1\circ \iota'_{1, G'_{1,\sigma(n)+1}}=
+	\iota'_{G'_{\sigma(n)+1}}\] 
+	While, if $\sigma(n)=n$, then we can use the identities
+		\[(\omega'_1)^{-1}\circ h'_{1, n}=h'_{n} \qquad p'_1\circ \iota'_{1, G'_{1, n+1}}=
+	\iota'_{G'_{n+1}}\circ (\omega'_1)^{-1}\] 
+	to get
+		\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ h_n &= p'_1\circ \iota'_{1, G_{1,n+1}} \circ h'_{1,n}\\&=\iota'_{G'_{n+1}}\circ (\omega'_1)^{-1}\circ h'_{1,n}\\&=\iota'_{G'_{n+1}} h'_{n}
+	\end{align*}
+	\item $i$ is in $[n+1, n+t+1]$- We proceed  similarly to the point above. First of all we have
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i &= \xi_{\sigma+\tau} \circ p_2\circ \iota_{1, G_{2,i-n}}\circ h_{2,i-(n+1)}\\&=p'_2 \circ \xi_\tau \circ \iota_{2, G_{2,i-n}}\circ h_{2,i-(n+1)}\\&= p'_2\circ \iota'_{2, G'_{2,\tau(i-n)}}\circ h'_{2,\tau(i-(n+1))}\\&=\iota'_{G'_{\tau(i-n)}}\circ h'_{n+1+\tau(i-(n+1))}
+	\end{align*}
+	Next, supposing that $i\neq n+1$:	
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{i}} \circ m_i &= \xi_{\sigma+\tau} \circ p_2\circ \iota_{2, G_{2,i-(n+1)}}\circ m_{2,i-(n+1)}\\&=p'_2\circ \xi_\tau \circ \iota_{2, G_{2,{i-(n+1)}}}\circ m_{2,i-(n+1)}\\&= p'_2\circ \iota'_{2, G'_{2,\tau(i-(n+1))}}\circ m'_{2,\tau(i-(n+1))}
+	\end{align*}
+	and we have again two possibilities.
+If $\tau(i-(n+1))\neq 0$, then the thesis follows from the equalities \[m'_{2, \tau(i-(n+1))}=m'_{(\sigma+\tau)(i)} \qquad p'_2\circ \iota'_{2, G'_{2,\tau(i-(n+1))}}=
+	\iota'_{G'_{(\sigma+\tau)(i)}}\] 
+	Suppose, instead, that $\tau(i-(n+1))= 0$, then we have
+	\begin{align*} p'_2\circ \iota'_{2, G'_{2,0}}\circ m'_{2,0}&=p'_2 \circ \iota'_{2,G'_{2,0}} \circ \alpha'_2 \circ \alpha'^{-1}_2 \circ m'_{2,0}\\&=p'_1\circ \iota'_{1, G'_{1, n+1}}\circ \omega'_1\circ \alpha'^{-1}_2 \circ m'_{2,0}\\&=\iota'_{G'_{n+1}}\circ m'_{n+1}
+	\end{align*}
+allowing us to conclude again.
+
+	We are left with the case $i=n+1$. Let us compute
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= \xi_{\sigma+\tau} \circ \iota_{\pi(G_{2,0})} \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ p_1\circ \iota_{1, G_{1,n+1}} \circ \omega_1 \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ p'_2 \circ \iota'_{2,G'_{2,0}} \circ \alpha'_2 \circ (\alpha'_2)^{-1}\circ m_{2,0} \\&=p'_2 \circ \xi_\tau \circ \iota_{2, G_{2,0}} \circ m_{2,0}\\&=p'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}
+	\end{align*}
+	We have again two cases. If $\tau(0)\neq 0$ then $(\sigma+\tau)(i)\neq n+1$ and we can conclude at once since 
+	\[m'_{2, \tau(0)}=m'_{(\sigma+\tau)(n+1)} \qquad p'_2\circ \iota'_{2, G'_{2,\tau(0)}}=
+	\iota'_{G'_{(\sigma+\tau)(0)}}\] 
+If $\tau(0)=0$, so that  $(\sigma+\tau)(0)= n+1$ we appeal to the equalities
+	\[(\alpha')^{-1}_2\circ m'_{2, 0}=m'_{n+1} \qquad p'_2\circ \iota'_{2, G'_{2, 0}}=
+	\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\] 
+	to get
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= p'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}\\&=	\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\circ m'_{2,0}\\&=\iota'_{G'_{n+1}}\circ  m'_{n+1}
+	\end{align*}
 \end{itemize}
-	Let $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$, $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$, $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$ and $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$ be colimiting cocones.
-Define two other cocones and  $\der{D}'_1*(\omega'_1)^{-1}\cdot \alpha'_2*\der{D}'_2$
-	Using point $2$ of \Cref{lem:colim} we get two pushout squares
-	\[\xymatrix{\pi(H) & }\]
-	Now, notice that $()$ and $bb$ are cocones on ... so that there exists... such that. 
+The thesis now follows at once.	
 \end{proof}
@@
 
-\section{Shift equivalence and traces}
+\section{Switch equivalence and traces}
 \todo{A VERY NICE INTRO}
@@
 \end{proof}
+
+\begin{lemma}
+	\todo{lemma salvavita}
+\end{lemma}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{corollary}
+	contenuto...
+\end{corollary}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{corollary}
+	contenuto...
+\end{corollary}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{corollary}
+	contenuto...
+\end{corollary}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{corollary}[No need for useless shifts]
+	contenuto...
+\end{corollary}
+\begin{proof}
+	contenuto...
+\end{proof}
+
 \iffalse 

### 2024-02-02 icalp/pratendsec2.tex
aggiunto stile

\begin{proof}[Proof of \autoref{thm:prAtEndii}]\phantomsection\label{proof:prAtEndii}We can start considering the cube below and noticing that $n$, being the pushout of $m\in \mathcal {M}$, belongs to $\mathcal {A}$ too. \[\xymatrix @C=13pt@R=13pt{&A\ar [dd]|\hole _(.65){\id {A}}\ar [rr]^{g} \ar [dl]_{\id {A}} && B \ar [dd]^{\id {B}} \ar [dl]_{\id {B}} \\ A \ar [dd]_{m}\ar [rr]^(.65){g} & & B \ar [dd]_(.3){n}\\&A\ar [rr]|\hole ^(.65){g} \ar [dl]^{m} && B \ar [dl]^{n} \\C \ar [rr]_{f} & & D}\] By construction the top face of the cube is a pushout and the back one a pullback. The left face is a pullback because $m$ is mono. Thus the $\mathcal {A}$-Van Kampen property yields that the front and the right faces are pullbacks.\end{proof}
\begin{proof}[Proof of \autoref{thm:prAtEndiv}]\phantomsection\label{proof:prAtEndiv}We can begin noticing that $g$, being the pullback of $k$, is mono and in $\mathcal {A}$ too. Thus we can build the cube below, in which all the vertical faces are pullbacks, entailing that all the vertical arrows are in $\mathcal {A}$. \[\xymatrix @C=20pt@R=10pt{ & &X\ar [dl]_{f} \ar [ddd]^(.333333){\id {X}}|(.666666)\hole \ar [rrr]^{a} &&&A \ar [ddd]^{\id {A}} \ar [dl]^{h}\\& Y\ar [dl]_{\id {Y}} \ar [ddd]|(.333333)\hole _{\id {Y}} &&&B \ar [ddd]^{\id {B}} \ar [dl]_{\id {B}} \\Y \ar [ddd]_{g} \ar [rrr]^{b}&&& B\ar [ddd]^{k}\\&&X \ar [rrr]|(.34)\hole ^{a}|(.67)\hole \ar [dl]_{f}&&& A \ar [dl]^{h}\\ & Y \ar [dl]_{g}&&& B \ar [dl]^{k}\\ Z\ar [rrr]_{c} &&& C}\] By hypothesis the face is an $\mathcal {A}$-stable pushout and so its top one is a pushout. Using \Cref {lem:po1} we can conclude that the right half of the rectangle with which we have started is a pushout too.\end{proof}
\begin{proof}[Proof of \autoref{thm:prAtEndv}]\phantomsection\label{proof:prAtEndv}Take the diagram \[\xymatrix {X \ar [d]_{\id {X}}\ar [r]^{f}& Y \ar [r]^{\id {Y}} \ar [d]_{\id {Y}}& Y \ar [d]^{m}\\ X \ar [r]_{f}& Y \ar [r]_{m} & Z}\] Since $m$ is mono the right square is a pullback, while the left square is a pullback by construction. By \Cref {lem:pb1} the whole rectangle is a pullback and the thesis follows.\end{proof}
\begin{proof}[Proof of \autoref{thm:prAtEndvi}]\phantomsection\label{proof:prAtEndvi}Let $m$ be an element of $\mathcal {M}$ and consider its pushout along itself. \[\xymatrix {X\ar @{>->}[r]^m \ar @{>->}[d]_m& Y\ar @{>->}[d]^{f}\\Y \ar @{>->}[r]_g & Z}\] By \Cref {prop:pbpoad} this square is a pullback, proving that $m$ is the equalizer of the arrows $f,g\colon Y\rightrightarrows Z$.\end{proof}
\begin{proof}[Proof of \autoref{thm:prAtEndx}]\phantomsection\label{proof:prAtEndx}By construction, the pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$ and $n$. Thus, the existence of the isomorphism $t\colon D\to D'$ follows from \Cref {lem:pocomp}. Now, computing we have \[ g'\circ t \circ k= g' \circ k'=h'\circ r\] Hence, we have the wanted $s\colon H\to H'$. To see that $s$ is an isomorphism, consider the diagram \[\xymatrix {K \ar @/^.4cm/[rr]^{k'}\ar [d]_{r} \ar [r]_{k}& \ar [r]_{t} D \ar [d]^{g}& D' \ar [d]^{g'}\\ R \ar @/_.4cm/[rr]_{h'} \ar [r]^{h}& H \ar [r]^{s}& H'}\] By hypothesis the whole rectangle and its left half are pushouts, therefore, by \Cref {lem:po1} its right square is a pushout too. The claim now follows from the fact that the pushout of an isomorphism is an isomorphism.\end{proof}

### 2024-02-03 icalp/fusione-pratendsec2.tex

\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndii}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofii{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndii}]\phantomsection\label{proof:prAtEndii}We can start considering the cube below and noticing that $n$, being the pushout of $m\in \mathcal {M}$, belongs to $\mathcal {A}$ too. \[\xymatrix @C=13pt@R=13pt{&A\ar [dd]|\hole _(.65){\id {A}}\ar [rr]^{g} \ar [dl]_{\id {A}} && B \ar [dd]^{\id {B}} \ar [dl]_{\id {B}} \\ A \ar [dd]_{m}\ar [rr]^(.65){g} & & B \ar [dd]_(.3){n}\\&A\ar [rr]|\hole ^(.65){g} \ar [dl]^{m} && B \ar [dl]^{n} \\C \ar [rr]_{f} & & D}\] By construction the top face of the cube is a pushout and the back one a pullback. The left face is a pullback because $m$ is mono. Thus the $\mathcal {A}$-Van Kampen property yields that the front and the right faces are pullbacks.\end{proof}

\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndiii}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofiii{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndiii}]\phantomsection\label{proof:prAtEndiii}$(\Rightarrow )$ By hypothesis there exists $k:D'\to B$ such that $n\circ k = d$. By \Cref {prop:pbpo}, the bottom face of the cube is a pullback. Thus there exists a unique $h:C'\to A$ as in the diagram below, implying the thesis. \[\xymatrix @C=40pt{C' \ar [d]^{h}\ar [r]^{f'} \ar @/_.5cm/[dd]_{c}& D' \ar @/^.5cm/[dd]^{d}\ar [d]_{k}\\ A \ar [d]^{m} \ar [r]^{g} & B \ar [d]_{n} \\ C \ar [r]_f & D}\] \par \smallskip \noindent $(\Leftarrow )$ Let $h:C\to A$ be such that $c=m\circ h$. By the $\mathcal {A}$-Van Kampen property the top face of the given cube is a pushout. Thus the dotted $k:D'\to B$ in the following diagram exists. \[\xymatrix @C=40pt{A' \ar @/_.5cm/[dd]_{a} \ar [d]^{m'} \ar [r]^{g'} & B' \ar [d]_{n'} \ar @/^.5cm/[dd]^{b} \\ C' \ar [d]^{h} \ar [r]_{f'} & D' \ar @{.>}[d]_{k}\\ A \ar [r]_g& B }\] Moreover, by construction we have \begin {align*} n\circ k \circ n'&= n\circ b=d\circ n'\\ n\circ k \circ f' &= n\circ g\circ h=f\circ m\circ h=f\circ c= d\circ f' \end {align*} We can therefore conclude that $n\circ k =d$.\end{proof}

\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndiv}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofiv{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndiv}]\phantomsection\label{proof:prAtEndiv}We can begin noticing that $g$, being the pullback of $k$, is mono and in $\mathcal {A}$ too. Thus we can build the cube below, in which all the vertical faces are pullbacks, entailing that all the vertical arrows are in $\mathcal {A}$. \[\xymatrix @C=20pt@R=10pt{ & &X\ar [dl]_{f} \ar [ddd]^(.333333){\id {X}}|(.666666)\hole \ar [rrr]^{a} &&&A \ar [ddd]^{\id {A}} \ar [dl]^{h}\\& Y\ar [dl]_{\id {Y}} \ar [ddd]|(.333333)\hole _{\id {Y}} &&&B \ar [ddd]^{\id {B}} \ar [dl]_{\id {B}} \\Y \ar [ddd]_{g} \ar [rrr]^{b}&&& B\ar [ddd]^{k}\\&&X \ar [rrr]|(.34)\hole ^{a}|(.67)\hole \ar [dl]_{f}&&& A \ar [dl]^{h}\\ & Y \ar [dl]_{g}&&& B \ar [dl]^{k}\\ Z\ar [rrr]_{c} &&& C}\] By hypothesis the face is an $\mathcal {A}$-stable pushout and so its top one is a pushout. Using \Cref {lem:po1} we can conclude that the right half of the rectangle with which we have started is a pushout too.\end{proof}

\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndv}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofv{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndv}]\phantomsection\label{proof:prAtEndv}Take the diagram \[\xymatrix {X \ar [d]_{\id {X}}\ar [r]^{f}& Y \ar [r]^{\id {Y}} \ar [d]_{\id {Y}}& Y \ar [d]^{m}\\ X \ar [r]_{f}& Y \ar [r]_{m} & Z}\] Since $m$ is mono the right square is a pullback, while the left square is a pullback by construction. By \Cref {lem:pb1} the whole rectangle is a pullback and the thesis follows.\end{proof}

\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndvi}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofvi{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndvi}]\phantomsection\label{proof:prAtEndvi}Let $m$ be an element of $\mathcal {M}$ and consider its pushout along itself. \[\xymatrix {X\ar @{>->}[r]^m \ar @{>->}[d]_m& Y\ar @{>->}[d]^{f}\\Y \ar @{>->}[r]_g & Z}\] By \Cref {prop:pbpoad} this square is a pullback, proving that $m$ is the equalizer of the arrows $f,g\colon Y\rightrightarrows Z$.\end{proof}

\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndvii}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofvii{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndvii}]\phantomsection\label{proof:prAtEndvii}\begin {enumerate} \item By \Cref {prop:stab}, it follows that both squares are pushouts, thus the thesis follows from \Cref {prop:pbpoad}. \item By hypothesis, $g$ is the pullback of an arrow in $\mathcal {M}$, thus it belongs to it. But then $g\circ f\in \mathcal {M}$ too and the whole rectangle is a $\mathcal {M}$-pushout. Therefore, by \Cref {prop:pbpoad} a pullback, so that its left half is a pullback too, by \Cref {prop:pbpo}. Moreover $k\circ h$ is in $\mathcal {M}$ as the pushout of $g\circ f$ and, by \Cref {cor:deco}, we also know that $h\in \mathcal {M}$. \par Using \Cref {lem:po1}, it is enough to show that the left half of the original rectangle is a pushout. We can build the following cube: \[\xymatrix @C=20pt@R=10pt{ & &X\ar @{>->}[dl]_{f} \ar [ddd]^(.333333){\id {X}}|(.666666)\hole \ar [rrr]^{a} &&&A \ar [ddd]^{\id {A}} \ar @{>->}[dl]^{h}\\& Y\ar [dl]_{\id {Y}} \ar [ddd]|(.333333)\hole _{\id {Y}} &&&B \ar [ddd]^{\id {B}} \ar [dl]_{\id {B}} \\Y \ar @{>->}[ddd]_{g} \ar [rrr]^{b}&&& B\ar @{>->}[ddd]^{k}\\&&X \ar [rrr]|(.34)\hole ^{a}|(.67)\hole \ar @{>->}[dl]_{f}&&& A \ar @{>->}[dl]^{h}\\ & Y \ar [rrr]|(.67)\hole ^{b} \ar @{>->}[dl]_{g}&&& B \ar @{>->}[dl]^{k}\\ Z\ar [rrr]_{c} &&& C}\] Its vertical faces are all pullbacks and all the vertical arrows are in $\mathcal {M}$, hence the top face is a pushout and we can conclude. \qedhere \end {enumerate}\end{proof}

\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndviii}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofviii{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndviii}]\phantomsection\label{proof:prAtEndviii}We start pulling back $n$ along $k$ and then pulling back the resulting arrow along $h$, getting the following two pullbacks square: \[\xymatrix {B \ar @{>->}[d]_{b}\ar @{>->}[r]^{s}& N \ar @{>->}[d]^{n} & A \ar [r]^{r} \ar @{>->}[d]_{a}& B \ar @{>->}[d]^{b}\\Q\ar @{>->}[r]_{k}&Y &M \ar [r]_h&Q\\}\] Notice that \[ f\circ m\circ a=k\circ h\circ a=k\circ b\circ r=n\circ s\circ r\] \par Thus there exists a unique $t\colon A\to P$ as in the diagram \[\xymatrix {A \ar @{>->}[d]_{a} \ar @{.>}[dr]^{t}\ar [r]^{r} &B \ar @{>->}@/^.2cm/[dr]^{s} \\ M \ar @{>->}@/_.2cm/[dr]_{m}&P\ar [r]^{p_1} \ar @{>->}[d]_{p_2}& N \ar @{>->}[d]^{n}\\ &X \ar [r]_{f} & Y}\] We can then consider the cube below, in which the front, right and back faces are pullbacks. \[\xymatrix @C=15pt@R=15pt{&A\ar @{>->}[dd]|\hole _(.65){a}\ar [rr]^{r} \ar [dl]_{t} && B \ar @{>->}[dd]^{b} \ar [dl]_{s} \\ P \ar @{>->}[dd]_{p_2}\ar [rr]^(.7){p_1} & & N \ar @{>->}[dd]_(.3){n}\\&M\ar [rr]|\hole ^(.65){h} \ar @{>->}[dl]^{m} && Q \ar @{>->}[dl]^{k} \\X \ar [rr]_{f} & & Y}\] We can notice that the left square is a pullback too. To see this it is enough to apply \Cref {lem:pb1} to the diagram \[\xymatrix {A \ar @/^.4cm/[rr]^{s\circ r}\ar @{>->}[d]_{a} \ar [r]_{t}& \ar [r]_{p_1} P \ar @{>->}[d]^{p_2}& N \ar [d]^{c}\\ M \ar @/_.4cm/[rr]_{k\circ h}\ar @{>->}[r]^{m}& X \ar [r]^{f}& Y}\] \par The thesis now follows immediately from \Cref {lem:varie}. \qedhere \end{proof}

\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndix}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofix{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndix}]\phantomsection\label{proof:prAtEndix}Consider the two pushout squares \[\xymatrix {M \ar [r]^{h_1}\ar @{>->}[d]_{m}& W_1 \ar @{>->}[d]^{k_1} & M \ar @{>->}[d]_{m} \ar [r]^{h_1}& W_2 \ar @{>->}[d]^{k_2}\\Y\ar [r]_{f}&Z &Y \ar [r]_{f}&Z}\] Since $\mathcal {M}$ is in $\mathcal {M}$, \cref {prop:pbpoad} guarantees that they are both pullbacks. Since $m\leq m$, by \Cref {lem:radj} we get that now entails that $k_1\leq k_2$ and $k_2\leq k_1$. Thus there exists an isomorphism $\phi \colon W_1\to W_2$ such that $k_1=k_2\circ \phi $. To see that $h_2=\phi \circ h_1$, we can compute: \[ k_2\circ \phi \circ h_1 = k_1\circ h_1= n\circ m= k_2\circ h_2\] \par The claim now follows since $k_2$ is a monomorphism.\end{proof}

\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndx}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofx{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndx}]\phantomsection\label{proof:prAtEndx}By construction, the pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$ and $n$. Thus, the existence of the isomorphism $t\colon D\to D'$ follows from \Cref {lem:pocomp}. Now, computing we have \[ g'\circ t \circ k= g' \circ k'=h'\circ r\] Hence, we have the wanted $s\colon H\to H'$. To see that $s$ is an isomorphism, consider the diagram \[\xymatrix {K \ar @/^.4cm/[rr]^{k'}\ar [d]_{r} \ar [r]_{k}& \ar [r]_{t} D \ar [d]^{g}& D' \ar [d]^{g'}\\ R \ar @/_.4cm/[rr]_{h'} \ar [r]^{h}& H \ar [r]^{s}& H'}\] By hypothesis the whole rectangle and its left half are pushouts, therefore, by \Cref {lem:po1} its right square is a pushout too. The claim now follows from the fact that the pushout of an isomorphism is an isomorphism.\end{proof}

### 2024-02-03 icalp/fusione-pratendsec3.tex

\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndxi}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofxi{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndxi}]\phantomsection\label{proof:prAtEndxi}The first point of \Cref {def:switc} is obviously satisfied. The second one follows at once since \[m_{\der {E},0}= f_0\circ i_1 \qquad h_{\der {E},1}= g_{1}\circ i_0\] Finally, the third point holds because we already know that \[m_{\der {E},0}= f_0\circ i_1 \qquad h_{\der {E},1}= g_{1}\circ i_0\]\end{proof}

\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndxii}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofxii{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndxii}]\phantomsection\label{proof:prAtEndxii}aaa\end{proof}

### 2024-02-06 icalp/fusione-pratendsec2.tex
bozza altra versione intro

@@
-\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndii}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofii{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndii}]\phantomsection\label{proof:prAtEndii}We can start considering the cube below and noticing that $n$, being the pushout of $m\in \mathcal {M}$, belongs to $\mathcal {A}$ too.
-\[\xymatrix @C=13pt@R=13pt{&A\ar [dd]|\hole _(.65){\id {A}}\ar [rr]^{g} \ar [dl]_{\id {A}} && B \ar [dd]^{\id {B}} \ar [dl]_{\id {B}} \\ A \ar [dd]_{m}\ar [rr]^(.65){g} & & B \ar [dd]_(.3){n}\\&A\ar [rr]|\hole ^(.65){g} \ar [dl]^{m} && B \ar [dl]^{n} \\C \ar [rr]_{f} & & D}\] By construction the top face of the cube is a pushout and the back one a pullback.
-The left face is a pullback because $m$ is mono.
-Thus the $\mathcal {A}$-Van Kampen property yields that the front and the right faces are pullbacks.\end{proof}
-
-\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndiii}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofiii{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndiii}]\phantomsection\label{proof:prAtEndiii}$(\Rightarrow )$ By hypothesis there exists $k:D'\to B$ such that $n\circ k = d$.
-By \Cref {prop:pbpo}, the bottom face of the cube is a pullback.
-Thus there exists a unique $h:C'\to A$ as in the diagram below, implying the thesis.
-\[\xymatrix @C=40pt{C' \ar [d]^{h}\ar [r]^{f'} \ar @/_.5cm/[dd]_{c}& D' \ar @/^.5cm/[dd]^{d}\ar [d]_{k}\\ A \ar [d]^{m} \ar [r]^{g} & B \ar [d]_{n} \\ C \ar [r]_f & D}\] \par \smallskip \noindent $(\Leftarrow )$ Let $h:C\to A$ be such that $c=m\circ h$.
-By the $\mathcal {A}$-Van Kampen property the top face of the given cube is a pushout.
-Thus the dotted $k:D'\to B$ in the following diagram exists.
-\[\xymatrix @C=40pt{A' \ar @/_.5cm/[dd]_{a} \ar [d]^{m'} \ar [r]^{g'} & B' \ar [d]_{n'} \ar @/^.5cm/[dd]^{b} \\ C' \ar [d]^{h} \ar [r]_{f'} & D' \ar @{.>}[d]_{k}\\ A \ar [r]_g& B }\] Moreover, by construction we have \begin {align*} n\circ k \circ n'&= n\circ b=d\circ n'\\ n\circ k \circ f' &= n\circ g\circ h=f\circ m\circ h=f\circ c= d\circ f' \end {align*} We can therefore conclude that $n\circ k =d$.\end{proof}
-
-\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndiv}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofiv{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndiv}]\phantomsection\label{proof:prAtEndiv}We can begin noticing that $g$, being the pullback of $k$, is mono and in $\mathcal {A}$ too.
-Thus we can build the cube below, in which all the vertical faces are pullbacks, entailing that all the vertical arrows are in $\mathcal {A}$.
-\[\xymatrix @C=20pt@R=10pt{ & &X\ar [dl]_{f} \ar [ddd]^(.333333){\id {X}}|(.666666)\hole \ar [rrr]^{a} &&&A \ar [ddd]^{\id {A}} \ar [dl]^{h}\\& Y\ar [dl]_{\id {Y}} \ar [ddd]|(.333333)\hole _{\id {Y}} &&&B \ar [ddd]^{\id {B}} \ar [dl]_{\id {B}} \\Y \ar [ddd]_{g} \ar [rrr]^{b}&&& B\ar [ddd]^{k}\\&&X \ar [rrr]|(.34)\hole ^{a}|(.67)\hole \ar [dl]_{f}&&& A \ar [dl]^{h}\\ & Y \ar [dl]_{g}&&& B \ar [dl]^{k}\\ Z\ar [rrr]_{c} &&& C}\] By hypothesis the face is an $\mathcal {A}$-stable pushout and so its top one is a pushout.
-Using \Cref {lem:po1} we can conclude that the right half of the rectangle with which we have started is a pushout too.\end{proof}
-
-\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndv}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofv{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndv}]\phantomsection\label{proof:prAtEndv}Take the diagram \[\xymatrix {X \ar [d]_{\id {X}}\ar [r]^{f}& Y \ar [r]^{\id {Y}} \ar [d]_{\id {Y}}& Y \ar [d]^{m}\\ X \ar [r]_{f}& Y \ar [r]_{m} & Z}\] Since $m$ is mono the right square is a pullback, while the left square is a pullback by construction.
-By \Cref {lem:pb1} the whole rectangle is a pullback and the thesis follows.\end{proof}
-
-\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndvi}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofvi{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndvi}]\phantomsection\label{proof:prAtEndvi}Let $m$ be an element of $\mathcal {M}$ and consider its pushout along itself.
-\[\xymatrix {X\ar @{>->}[r]^m \ar @{>->}[d]_m& Y\ar @{>->}[d]^{f}\\Y \ar @{>->}[r]_g & Z}\] By \Cref {prop:pbpoad} this square is a pullback, proving that $m$ is the equalizer of the arrows $f,g\colon Y\rightrightarrows Z$.\end{proof}
-
-\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndvii}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofvii{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndvii}]\phantomsection\label{proof:prAtEndvii}\begin {enumerate} \item By \Cref {prop:stab}, it follows that both squares are pushouts, thus the thesis follows from \Cref {prop:pbpoad}.
-\item By hypothesis, $g$ is the pullback of an arrow in $\mathcal {M}$, thus it belongs to it.
-But then $g\circ f\in \mathcal {M}$ too and the whole rectangle is a $\mathcal {M}$-pushout.
-Therefore, by \Cref {prop:pbpoad} a pullback, so that its left half is a pullback too, by \Cref {prop:pbpo}.
-Moreover $k\circ h$ is in $\mathcal {M}$ as the pushout of $g\circ f$ and, by \Cref {cor:deco}, we also know that $h\in \mathcal {M}$.
-\par Using \Cref {lem:po1}, it is enough to show that the left half of the original rectangle is a pushout.
-We can build the following cube: \[\xymatrix @C=20pt@R=10pt{ & &X\ar @{>->}[dl]_{f} \ar [ddd]^(.333333){\id {X}}|(.666666)\hole \ar [rrr]^{a} &&&A \ar [ddd]^{\id {A}} \ar @{>->}[dl]^{h}\\& Y\ar [dl]_{\id {Y}} \ar [ddd]|(.333333)\hole _{\id {Y}} &&&B \ar [ddd]^{\id {B}} \ar [dl]_{\id {B}} \\Y \ar @{>->}[ddd]_{g} \ar [rrr]^{b}&&& B\ar @{>->}[ddd]^{k}\\&&X \ar [rrr]|(.34)\hole ^{a}|(.67)\hole \ar @{>->}[dl]_{f}&&& A \ar @{>->}[dl]^{h}\\ & Y \ar [rrr]|(.67)\hole ^{b} \ar @{>->}[dl]_{g}&&& B \ar @{>->}[dl]^{k}\\ Z\ar [rrr]_{c} &&& C}\] Its vertical faces are all pullbacks and all the vertical arrows are in $\mathcal {M}$, hence the top face is a pushout and we can conclude.
-\qedhere \end {enumerate}\end{proof}
-
-\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndviii}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofviii{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndviii}]\phantomsection\label{proof:prAtEndviii}We start pulling back $n$ along $k$ and then pulling back the resulting arrow along $h$, getting the following two pullbacks square: \[\xymatrix {B \ar @{>->}[d]_{b}\ar @{>->}[r]^{s}& N \ar @{>->}[d]^{n} & A \ar [r]^{r} \ar @{>->}[d]_{a}& B \ar @{>->}[d]^{b}\\Q\ar @{>->}[r]_{k}&Y &M \ar [r]_h&Q\\}\] Notice that \[ f\circ m\circ a=k\circ h\circ a=k\circ b\circ r=n\circ s\circ r\] \par Thus there exists a unique $t\colon A\to P$ as in the diagram \[\xymatrix {A \ar @{>->}[d]_{a} \ar @{.>}[dr]^{t}\ar [r]^{r} &B \ar @{>->}@/^.2cm/[dr]^{s} \\ M \ar @{>->}@/_.2cm/[dr]_{m}&P\ar [r]^{p_1} \ar @{>->}[d]_{p_2}& N \ar @{>->}[d]^{n}\\ &X \ar [r]_{f} & Y}\] We can then consider the cube below, in which the front, right and back faces are pullbacks.
-\[\xymatrix @C=15pt@R=15pt{&A\ar @{>->}[dd]|\hole _(.65){a}\ar [rr]^{r} \ar [dl]_{t} && B \ar @{>->}[dd]^{b} \ar [dl]_{s} \\ P \ar @{>->}[dd]_{p_2}\ar [rr]^(.7){p_1} & & N \ar @{>->}[dd]_(.3){n}\\&M\ar [rr]|\hole ^(.65){h} \ar @{>->}[dl]^{m} && Q \ar @{>->}[dl]^{k} \\X \ar [rr]_{f} & & Y}\] We can notice that the left square is a pullback too.
-To see this it is enough to apply \Cref {lem:pb1} to the diagram \[\xymatrix {A \ar @/^.4cm/[rr]^{s\circ r}\ar @{>->}[d]_{a} \ar [r]_{t}& \ar [r]_{p_1} P \ar @{>->}[d]^{p_2}& N \ar [d]^{c}\\ M \ar @/_.4cm/[rr]_{k\circ h}\ar @{>->}[r]^{m}& X \ar [r]^{f}& Y}\] \par The thesis now follows immediately from \Cref {lem:varie}.
-\qedhere \end{proof}
-
-\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndix}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofix{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndix}]\phantomsection\label{proof:prAtEndix}Consider the two pushout squares \[\xymatrix {M \ar [r]^{h_1}\ar @{>->}[d]_{m}& W_1 \ar @{>->}[d]^{k_1} & M \ar @{>->}[d]_{m} \ar [r]^{h_1}& W_2 \ar @{>->}[d]^{k_2}\\Y\ar [r]_{f}&Z &Y \ar [r]_{f}&Z}\] Since $\mathcal {M}$ is in $\mathcal {M}$, \cref {prop:pbpoad} guarantees that they are both pullbacks.
-Since $m\leq m$, by \Cref {lem:radj} we get that now entails that $k_1\leq k_2$ and $k_2\leq k_1$.
-Thus there exists an isomorphism $\phi \colon W_1\to W_2$ such that $k_1=k_2\circ \phi $.
-To see that $h_2=\phi \circ h_1$, we can compute: \[ k_2\circ \phi \circ h_1 = k_1\circ h_1= n\circ m= k_2\circ h_2\] \par The claim now follows since $k_2$ is a monomorphism.\end{proof}
-
-\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndx}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofx{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndx}]\phantomsection\label{proof:prAtEndx}By construction, the pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$ and $n$.
-Thus, the existence of the isomorphism $t\colon D\to D'$ follows from \Cref {lem:pocomp}.
-Now, computing we have \[ g'\circ t \circ k= g' \circ k'=h'\circ r\] Hence, we have the wanted $s\colon H\to H'$.
-To see that $s$ is an isomorphism, consider the diagram \[\xymatrix {K \ar @/^.4cm/[rr]^{k'}\ar [d]_{r} \ar [r]_{k}& \ar [r]_{t} D \ar [d]^{g}& D' \ar [d]^{g'}\\ R \ar @/_.4cm/[rr]_{h'} \ar [r]^{h}& H \ar [r]^{s}& H'}\] By hypothesis the whole rectangle and its left half are pushouts, therefore, by \Cref {lem:po1} its right square is a pushout too.
-The claim now follows from the fact that the pushout of an isomorphism is an isomorphism.\end{proof}
+\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndii}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofii{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndii}]\phantomsection\label{proof:prAtEndii}Both pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$ and $n$, thus, \Cref {lem:pocomp} yields an isomorphism $\phi _D\colon D\to D'$.
+Computing we have \[ g'\circ \phi _D \circ k= g' \circ k'=h'\circ r\] \par \noindent \parbox {3cm}{ $\xymatrix {K \ar @/^.4cm/[rr]^{k'}\ar [d]_{r} \ar [r]_{k}& \ar [r]_{\phi _D} D \ar [d]^{g}& D' \ar [d]^{g'}\\ R \ar @/_.4cm/[rr]_{h'} \ar [r]^{h}& H \ar [r]^{\phi _H}& H'}$} \hfill \parbox {10cm}{ \hspace {15pt}Hence, we have another $\phi _H\colon H\to H'$.
+To see that $\phi _H$ is an isomorphism, consider the diagram aside.
+By hypothesis the whole rectangle and its left half are pushouts, therefore, by \Cref {lem:po1} its right square is a pushout too.
+The claim now follows from the fact that the pushout of an isomorphism is an isomorphism.
+\qedhere }\end{proof}

### 2024-02-06 icalp/fusione-pratendsec3.tex
bozza altra versione intro

@@
-\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndxi}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofxi{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndxi}]\phantomsection\label{proof:prAtEndxi}The first point of \Cref {def:switc} is obviously satisfied.
-The second one follows at once since \[m_{\der {E},0}= f_0\circ i_1 \qquad h_{\der {E},1}= g_{1}\circ i_0\] Finally, the third point holds because we already know that \[m_{\der {E},0}= f_0\circ i_1 \qquad h_{\der {E},1}= g_{1}\circ i_0\]\end{proof}
-
-\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndxii}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofxii{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndxii}]\phantomsection\label{proof:prAtEndxii}aaa\end{proof}
+\makeatletter\Hy@SaveLastskip\label{proofsection:prAtEndiii}\ifdefined\pratend@current@sectionlike@label\immediate\write\@auxout{\string\gdef\string\pratend@section@for@proofiii{\pratend@current@sectionlike@label}}\fi\Hy@RestoreLastskip\makeatother\begin{proof}[Proof of \pratendRef{thm:prAtEndiii}]\phantomsection\label{proof:prAtEndiii}Let us begin considering the diagram built in \Cref {rem:deco}: \[\xymatrix {&&R_0 \ar @/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar [dr]^{h_0}&& L_1\ar @/^1cm/[ddll]^(.35){i_1} \ar [dl]_{m_1}\\&K_0\ar [dr]^{k_0}\ar @{>->}[dl]_{l_0} \ar @/_.8cm/[ddrr]^(.65){u_0}\ar [ur]^{r_0}&& G_1 && K_1 \ar @/^.8cm/[ddll]_(.65){u_1}\ar [dl]_{k_1}\ar @{>->}[lu]_{l_1} \ar [dr]^{r_1}\\L_0 \ar [dr]^{m_0} \ar @{>}@/_.8cm/[ddrr]_{j_1}&& D_0 \ar @{>->}[dl]|(.42)\hole _(.64){f_0}\ar [ur]|(.48)\hole ^(.7){g_1}&&D_1 \ar [dr]|(.42)\hole ^(.65){g_1} \ar @{>->}[ul]|(.48)\hole _(.7){f_1}&&R_1\ar @/^.8cm/[ddll]^{j_0}\ar [dl]^{h_1}\\&G_0 &&P\ar [dr]^{q_1} \ar @{>->}[dl]_{q_0}\ar [ur]^(.4){p_1}\ar @{>->}[ul]_(.4){p_0}&&G_2\\&&Q_0 \ar @{>->}@{>->}[ul]_{a_0} \ar @{.>}[dr]_{b_0} &&Q_1\ar [ur]^{b_1} \ar @{>.>}[dl]^{a_1} \\ &&&H_1 }\] Since $q_0\colon P\to Q_0$ is in $\mathcal {M}$, we can take its pushout along $q_1$ to get the dotted arrows $a_1\colon Q_1\to H_1$ and $q_0\colon Q_0\to H_1$.
+But then, since the composite of two pushout squares is a pushout, the diagram below is a derivation.
+\[\xymatrix @C=15pt{L_1 \ar [d]_{f_0 \circ i_1}&& K_1 \ar [d]_{q_0\circ u_1}\ar @{>->}[ll]_{l_1} \ar [r]^{r_1} & R_1 \ar @/^.35cm/[drrr]|(.3)\hole _(.4){j_0} \ar [dr]|(.3)\hole _{a_1\circ j_0} && L_0 \ar @/_.35cm/[dlll]^(.4){j_1} \ar [dl]|(.3)\hole ^{b_0\circ j_1}& K_1 \ar [d]^{q_1\circ u_0}\ar @{>->}[l]_{l_0} \ar [rr]^{r_0} && R_0 \ar [d]^{g_1\circ i_0} \\G_0 && \ar @{>->}[ll]^{a_0} D_0 \ar [rr]_{b_0}&& G_1 && \ar @{>->}[ll]^{a_1} D_1 \ar [rr]_{b_1}&& G_2}\] It is immediate now to see that it is a switch of $\dder {D}_0$ and $\dder {D}_1$ along $(i_0, i_1)$.\end{proof}

### 2024-03-27 icalp/Rebuttal.txt
rebuttal

We thank the reviewer for carefully reading the paper and for their comments. Here are some answers:

REVIEWER 1
We believe that the paper fits into "Algebraic and Categorical Models of Computation" which is one of the topics of ICALP. We did our best to make the paper accessible to people having a basic knowledge of category theory and we inserted a number of examples aimed at communicating the main problems and solution of dealing with non-linear rewriting (which apply to a number of cincrete visual rewriting formalisms like string diagrams [9]). In the preparation of the final version we can put further effort in conveying intuition.\

REVIEWER 2
- "it is unfortunate that you did not find space for describing the class in any detail, but please at least indicate how it compare to the class studied in [6]."

As mentioned in the paper, the class is the natural generalisation of the one in [6] from adhesive to M-adhesive categories. In the final version we can make this more explicit and add some further details.

- Ex. 3.7 does not look quite right. The was not adhesive, wasn't it? It was only iso-adhesive.

The idea here is to provide an example of a M-left linear rewriting systems over an M-adhesive category which is not strong enforcing. Hence left-linear and adheive should read M-left linear and M-adhesive. Omitting the M- prefix which is done also in other parts of the paper here is definitively confusing and we will amend this.

REVIEWER 3

- Is Church-Rosser essentially a consequence of the definition of strong independence pair?

Yes, the idea here was to distill the minimal assumptions needed to make Church-Rosser result work. This is then used to show that for a large class of M-adhesive rewriting systems (the one generalising [6]) this assumptions reduce to the existence of an independence pair.

- well-switching rewriting systems feel overly restrictive and, as such, the development feels slightly preliminary.

Actually, the counterexamples discussed in the paper (ex. 3.14) suggest that out of the class of well-switching rewriting systems no reasonable theory of rewriting can be developed. And, as the reviewer correctly observe, despite the fact that the condition could look restrictive, classes of rewriting systems (Node-merging graphical rewriting systems and E-graphs) which cover many concrete applications in the literature are well-switching.

### 2024-03-27 icalp/Rebuttal.txt
minimi ritocchi al rebuttal

@@
-We thank the reviewer for carefully reading the paper and for their comments. Here are some answers:
+We thank the reviewers for the careful reading of our paper and for their comments. Here are some answers:
 
@@
 We believe that the paper fits into "Algebraic and Categorical Models of Computation" which is one of the topics of ICALP.
-We did our best to make the paper accessible to people having a basic knowledge of category theory and we inserted a number of examples aimed at communicating the main problems and solution of dealing with non-linear rewriting (which apply to a number of cincrete visual rewriting formalisms like string diagrams [9]).
-In the preparation of the final version we can put further effort in conveying intuition.\
+We did our best to make the paper accessible to people having a basic knowledge of category theory and we inserted a number of examples aimed at communicating the main problems and solution of dealing with non-linear rewriting (which apply to a number of concrete visual rewriting formalisms like string diagrams [9]).
+In the preparation of the final version we can put further effort in conveying intuition.
 
@@
 
-As mentioned in the paper, the class is the natural generalisation of the one in [6] from adhesive to M-adhesive categories.
-In the final version we can make this more explicit and add some further details.
+Indeed, the class is the natural generalisation of the one in [6] from adhesive to M-adhesive categories. In the final version we can make this more explicit and add some further details.
 
@@
 The idea here is to provide an example of a M-left linear rewriting systems over an M-adhesive category which is not strong enforcing.
-Hence left-linear and adheive should read M-left linear and M-adhesive.
-Omitting the M- prefix which is done also in other parts of the paper here is definitively confusing and we will amend this.
+Hence left-linear and adhesive should read M-left linear and M-adhesive.
+Omitting the M- prefix here is definitively confusing and we will amend this.
 
@@
 
-Yes, the idea here was to distill the minimal assumptions needed to make Church-Rosser result work.
-This is then used to show that for a large class of M-adhesive rewriting systems (the one generalising [6]) this assumptions reduce to the existence of an independence pair.
+Yes, the idea here was to distill the minimal assumptions needed to make Church-Rosser work.
+This is then used to show that for a large class of M-adhesive rewriting systems (the one generalising [6]) this assumption reduce to the existence of an independence pair.
 
@@
 3.14) suggest that out of the class of well-switching rewriting systems no reasonable theory of rewriting can be developed.
-And, as the reviewer correctly observe, despite the fact that the condition could look restrictive, classes of rewriting systems (Node-merging graphical rewriting systems and E-graphs) which cover many concrete applications in the literature are well-switching.
+And, as the reviewer correctly observes, despite the fact that the condition could look restrictive, classes of rewriting systems (Node-merging graphical rewriting systems and E-graphs) that cover many concrete applications in the literature are well-switching.

### 2024-03-27 icalp/Rebuttal.txt
r2

@@
 
-Indeed, the class is the natural generalisation of the one in [6] from adhesive to M-adhesive categories. In the final version we can make this more explicit and add some further details.
+Indeed, the class is constructed using a generalisation of the methods exploited in [6], adapting them to the more general M-adhesive context.
+In the final version we can make this more explicit and add some further details.
 
@@
 Hence left-linear and adhesive should read M-left linear and M-adhesive.
-Omitting the M- prefix here is definitively confusing and we will amend this.
+Omitting the M- prefix which is done also in other parts of the paper here is definitively confusing and we will amend this.
+It is worth noticing that, having in mind the results of [6] and of our Appendix B, in every category built from Set using the comma construction or taking the category of functors is strong enforcing, thus every example of an independence pair which is not strong, must live in a rather "pathological" category.
 

### 2024-03-28 icalp/Rebuttal.txt
rebuttal

@@
 Omitting the M- prefix which is done also in other parts of the paper here is definitively confusing and we will amend this.
-It is worth noticing that, having in mind the results of [6] and of our Appendix B, in every category built from Set using the comma construction or taking the category of functors is strong enforcing, thus every example of an independence pair which is not strong, must live in a rather "pathological" category.
+It is worth noticing that, having in mind the results of [6] and of our Appendix B, in every category built from Set using the comma construction or taking the category of functors is strong enforcing, thus every example of an independence pair which is not strong, must live in a rather "pathological" example of M-adhesive category.
 

### 2024-03-28 icalp/Rebuttal.txt
Update Rebuttal.txt
typos

@@
 We believe that the paper fits into "Algebraic and Categorical Models of Computation" which is one of the topics of ICALP.
-We did our best to make the paper accessible to people having a basic knowledge of category theory and we inserted a number of examples aimed at communicating the main problems and solution of dealing with non-linear rewriting (which apply to a number of concrete visual rewriting formalisms like string diagrams [9]).
+We did our best to make the paper accessible to people having a basic knowledge of category theory and we inserted a number of examples aimed at communicating the main problems and solutions of dealing with non-linear rewriting (which apply to a number of concrete visual rewriting formalisms like string diagrams [9]).
 In the preparation of the final version we can put further effort in conveying intuition.
@@
 Yes, the idea here was to distill the minimal assumptions needed to make Church-Rosser work.
-This is then used to show that for a large class of M-adhesive rewriting systems (the one generalising [6]) this assumption reduce to the existence of an independence pair.
+This is then used to show that for a large class of M-adhesive rewriting systems (the one generalising [6]) this assumption reduces to the existence of an independence pair.
 

### 2024-03-28 icalp/Rebuttal.txt
rebuttal

@@
 REVIEWER 1
+- Adequate for ICALP?
+
 We believe that the paper fits into "Algebraic and Categorical Models of Computation" which is one of the topics of ICALP.
@@
 REVIEWER 2
-- "it is unfortunate that you did not find space for describing the class in any detail, but please at least indicate how it compare to the class studied in [6]."
+- It is unfortunate that you did not find space for describing the class in any detail, but please at least indicate how it compare to the class studied in [6].
 
@@
 
-- well-switching rewriting systems feel overly restrictive and, as such, the development feels slightly preliminary.
+- Well-switching rewriting systems feel overly restrictive and, as such, the development feels slightly preliminary.
 

### 2024-07-02 concur/submitted/Figure/coffee-rewriting.tex

\begin{center}

  %%% REWRITING 
  % 
  %
  % 
  \begin{tikzpicture}[node distance=4mm, font=\small]
    % graph G0
    \node (G0) {
      \begin{tikzpicture}[node distance=2mm, font=\scriptsize]
        % 
        \node at (0,0.5) {};
        \node at (0,1.5) [node, label=left:$1$] (1) {} ;
        \node at (0,1.0) [node, label=left:$2$] (2) {} ;
        \node at (0,0.5) [node, label=left:$3$] (3) {} ;

        \node at (0.6,1.0) [node, label=right:$4$] (4) {}
        edge [in=45, out=75, loop] node[above] {$\mathit{cf}$} ();

        \draw[->] (1) to[out=350, in=110] node[above]{$m$} (4);
        \draw[->] (2) to node[above, pos=0.4]{$s$} (4);
        \draw[->] (3) to[out=10, in=240] node[below]{$c$} (4);

      %
      \pgfBox
      \end{tikzpicture} 
    };
    \node[below] at (G0.south) {$G_0$};
    % graph G1
    \node [right=of G0] (G1) {
      \begin{tikzpicture}[node distance=2mm, font=\scriptsize]
      % 
        \node at (0,0.5) {};
        \node at (0,0.5) [node, label=left:$3$] (3) {} ;

        \node at (0.6,1.0) [node, label=right:$124$] (124) {}
        edge [in=90, out=130, loop] node[above] {$\mathit{m}$} ()
        edge [in=155, out=185, loop] node[above] {$\mathit{s}$} ()

        edge [in=45, out=75, loop] node[above] {$\mathit{cf}$} ();

        \draw[->] (3) to[out=10, in=240] node[below]{$c$}  (124);

      %
      \pgfBox
      \end{tikzpicture}
    };
    \node[below] at (G1.south) {$G_1$};

    % graph G2
    \node [right=of G1] (G2) {        
      \begin{tikzpicture}[node distance=2mm, font=\scriptsize]
      % 
        \node at (0,0.5) {};

        \node at (0.6,1.0) [node, label=right:$1234$] (1234) {}
        edge [in=210, out=240, loop] node[below] {$\mathit{c}$} ()
        edge [in=90, out=130, loop] node[above] {$\mathit{m}$} ()
        edge [in=155, out=185, loop] node[above] {$\mathit{s}$} ()
        edge [in=45, out=75, loop] node[above] {$\mathit{cf}$} ();

      %
      \pgfBox
    \end{tikzpicture}
    };
    \node[below] at (G2.south) {$G_2$};

    % graph G3
    \node [right=of G2] (G3) {
      \begin{tikzpicture}[node distance=2mm, font=\scriptsize]
      % 
        \node at (0,0.5) {};

        \node at (0.6,1.0) [node, label=right:$1234$] (1234) {}
        edge [in=210, out=240, loop] node[below] {$\mathit{c}$} ()
        edge [in=90, out=130, loop] node[above] {$\mathit{m}$} ()
        edge [in=155, out=185, loop] node[above] {$\mathit{s}$} ()
        % edge [in=2500, out=295, loop] node[above]
        edge [in=280, out=310, loop] node[right] {$\mathit{r}$} ()
        edge [in=45, out=75, loop] node[above] {$\mathit{cf}$} ();

        % 
        \pgfBox
      \end{tikzpicture}
    };
    \node[below] at (G3.south) {$G_3$};

    \path (G0) edge[->] node[trans, above] {$\rho_m$} (G1);
    \path (G1) edge[->] node[trans, above] {$\rho_c$} (G2);
    \path (G2) edge[->] node[trans, above] {$\rho_r$} (G3);    
  \end{tikzpicture}
\end{center}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../fusione"
%%% End:

### 2024-07-02 concur/Figure/coffee-rewriting.tex
coffee new

\begin{center}

  %%% REWRITING 
  % 
  %
  % 
  \begin{tikzpicture}[node distance=4mm, font=\small]
    % graph G0
    \node (G0) {
      \begin{tikzpicture}[node distance=2mm, font=\scriptsize]
        % 
        \node at (0,1.0) [node, label=left:$1$] (1) {}
        edge [in=110, out=140, loop] node[above] {$\mathit{w}$} ()
        edge [in=220, out=250, loop] node[below] {$\mathit{b}$} ();

        \node at (0.7,1.0) [node, label=right:$2$] (2) {}
        edge [in=40, out=70, loop] node[above] {$\mathit{c}$} ();

        \draw[->] (1) to node[above, pos=0.4]{$s$} (2);        
      %
      \pgfBox
      \end{tikzpicture} 
    };
    \node[below] at (G0.south) {$G_0$};
    % graph G1
    \node [right=of G0] (G1) {
      \begin{tikzpicture}[node distance=2mm, font=\scriptsize]
      % 
      \node at (0.6,1.0) [node, label=right:$12$] (12) {}
        edge [in=220, out=250, loop] node[below] {$\mathit{b}$} ()
        edge [in=40, out=70, loop] node[above] {$\mathit{c}$} ()
        edge [in=300, out=330, loop] node[below] {$\mathit{s}$} ();        
      %
      \pgfBox
      \end{tikzpicture}
    };
    \node[below] at (G1.south) {$G_1$};

    % graph G2
    \node [right=of G1] (G2) {        
      \begin{tikzpicture}[node distance=2mm, font=\scriptsize]
      % 
      \node at (0.6,1.0) [node, label=right:$12$] (12) {}
        edge [in=220, out=250, loop] node[below] {$\mathit{b}$} ()
        edge [in=40, out=70, loop] node[above] {$\mathit{c}$} ();
      %
      \pgfBox
    \end{tikzpicture}
    };
    \node[below] at (G2.south) {$G_2$};

    % graph G3
    \node [right=of G2] (G3) {
      \begin{tikzpicture}[node distance=2mm, font=\scriptsize]
      % 
      \node at (0.6,1.0) [node, label=right:$12$] (12) {}
        edge [in=220, out=250, loop] node[below] {$\mathit{b}$} ()
        edge [in=40, out=70, loop] node[above] {$\mathit{cr}$} ();        
        % 
        \pgfBox
      \end{tikzpicture}
    };
    \node[below] at (G3.south) {$G_3$};

    \path (G0) edge[->] node[trans, above] {$\rho_w$} (G1);
    \path (G1) edge[->] node[trans, above] {$\rho_b$} (G2);
    \path (G2) edge[->] node[trans, above] {$\rho_r$} (G3);    
  \end{tikzpicture}
\end{center}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../final"
%%% End:

### 2024-07-02 concur/Figure/coffee-rewriting.tex
minima

@@
         edge [in=220, out=250, loop] node[below] {$\mathit{b}$} ()
-        edge [in=40, out=70, loop] node[above] {$\mathit{cr}$} ();        
+        edge [in=40, out=70, loop] node[above] {$\mathit{r}$} ();        
         % 

### 2024-07-02 concur/Figure/coffee-rewriting.tex

@@
       \node at (0.6,1.0) [node, label=right:$12$] (12) {}
-        edge [in=220, out=250, loop] node[below] {$\mathit{b}$} ()
-        edge [in=40, out=70, loop] node[above] {$\mathit{c}$} ();
+%        edge [in=220, out=250, loop] node[below] {$\mathit{b}$} ()
+        edge [in=40, out=70, loop] node[above] {$\mathit{c}$} ()
+        edge [in=300, out=330, loop] node[below] {$\mathit{s}$} ();        
       %
@@
       \node at (0.6,1.0) [node, label=right:$12$] (12) {}
-        edge [in=220, out=250, loop] node[below] {$\mathit{b}$} ()
-        edge [in=40, out=70, loop] node[above] {$\mathit{r}$} ();        
+%        edge [in=220, out=250, loop] node[below] {$\mathit{b}$} ()
+        edge [in=40, out=70, loop] node[above] {$\mathit{r}$} ()
+        edge [in=300, out=330, loop] node[below] {$\mathit{s}$} ();        
         % 

### 2024-07-08 arxiv_concur/main.tex
arxiv

\documentclass[a4paper,UKenglish,cleveref,pdftex,thm-restate,numberwithinsect]{lipics-v2021}
\newif\ifreport
\reporttrue 
%\reportfalse

% full includes some additional material
\newif\iffull
%\fulltrue
\fullfalse

% additional text
\iffull
\newcommand{\full}[1]{{color{blue}#1}}
%\newcommand{\short}[1]{}
\else 
\newcommand{\full}[1]{}
%\newcommand{\short}[1]{#1}  xfl
\fi

\nolinenumbers %uncomment to disable line numbering

\ifreport
\nolinenumbers %uncomment to disable line numbering
\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
\else
\relatedversion{An extended version is available at \url{https://arxiv.org/abs/2007.04213}.} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
%\relatedversion{A full version of the paper is available at \url{...}.}
\fi

\bibliographystyle{abbrv}% the mandatory bibstyle

\usepackage{hyperref}
\usepackage[disable,%
textsize=tiny]{todonotes}
%\usepackage{etex}
\usepackage[all]{xy}
\SelectTips{cm}{}
% derivations and labels
\usepackage{proof}
\newcommand{\lab}[1]{\ensuremath{\mathsf{{#1}}}}
\newcommand{\slab}[1]{\ensuremath{\scriptstyle{\mathsf{{#1}}}}}
\usepackage{wrapfig}

%frecce
\newcommand{\mor}{\mathsf{Mor}}
\newcommand{\mon}{\mathsf{Mono}}
\newcommand{\reg}{\mathsf{Reg}}

% ``boxed'' \infer command
\newcommand{\binfer}[3][]{
  \mbox{\infer[#1]{#2}{#3}}}

% Command for labels on the left side of the rule
%       \inferL{<name>}{<post>}{<pre>}
% generates:
%             <pre>
%      <name> ------
%             <post>
%
\newlength{\myheight}
\newcommand{\inferL}[3]
  {\settoheight{\myheight}{\mbox{${#2}$}}
   \raisebox{\myheight}{{#1}}
   \makebox[1mm]{}
   \mbox{\infer{#2}{#3}}
}

\usepackage{amssymb,graphicx,epsfig,color}
%\usepackage[scriptsize]{subfigure}
\usepackage{subcaption}
\usepackage{wrapfig}

% re-stating 
%\usepackage{thm-restate}

% showing labels
%\usepackage[inline]{showlabels}

\usepackage{pgf}
\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri,fit,positioning,calc}
\tikzstyle{node}=[circle, draw=black, minimum size=1mm, inner sep=1.5pt, font=\tiny]

\tikzstyle{trans}=[font=\scriptsize]
\tikzstyle{lab}=[font=\small]
\tikzset{
  coloredge/.style={
        ->,
        color=red
        %densely dotted
    }
}

\tikzset{
  colorloop/.style={
        loop,
        color=red
        %densely dotted
    }
}

\tikzcdset{
  perm/.style={
    shorten >=-1mm, shorten <=-1mm,
    -,
    % dotted
  }
}

\newcommand{\pgfBox}{
  \begin{pgfonlayer}{background} 
    \fill[blue!2,thick,draw=black!50,rounded corners,inner sep=3mm] ([xshift=-1.5pt,yshift=-1.5pt]current bounding box.south west) rectangle ([xshift=1.5pt,yshift=1.5pt]current bounding box.north east);
  \end{pgfonlayer}
}
\usepackage{scalerel}
\newcommand{\smallmin}{\scaleobj{0.6}{-}}
\newcommand{\Deltamin}{\Delta^{\hspace{-1pt}\downarrow\hspace{-1pt}}}
\newcommand{\Rrel}[1]   {\stackrel{{#1}}{\Longrightarrow}}
\newcommand{\oa}{\overline a}
\newcommand{\ob}{\overline b}
\newcommand{\oc}{\overline c}
\newcommand{\od}{\overline d}
\newcommand{\rec}{\emph{rec}}
\newcommand{\fn}[1]{{\mathtt{fn}}(#1)}
%\usepackage{latexsym}
\usepackage{stmaryrd}
\def\encodep#1{\llfloor#1\rrfloor}

\newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}

\newcommand{\dpo}{\textsc{dpo}}

% base classes of categories for adhesive and quasi adhesive case
\newcommand{\bAdh}{\ensuremath{\mathbb{B}}}
\newcommand{\bQAdh}{\ensuremath{\mathbb{QB}}}

%from pawel
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{xspace}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage{float}
\usepackage{fancybox}
\usepackage{proof-at-the-end}
\usepackage{cleveref}

%\spnewtheorem*{notation}{Notation}{\bfseries}{\rmfamily}

%%%%%%%% MATHEMATICAL NOTATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%symbol for natural numbers
\newcommand{\nat}{\ensuremath{\mathbb{N}}}

% finite subset
\newcommand{\sfin}{\ensuremath{\subseteq_{\mathit{fin}}}}

% flattening of a multiset
\newcommand{\flt}[1]{\ensuremath{[\![{#1}]\!]}}

% compact elements
\newcommand{\compact}[1]{\ensuremath{\mathop{\mathsf{K}({#1})}}}

% principal ideal
\newcommand{\principal}[1]{\ensuremath{\mathop{\downarrow\!{#1}}}}

% ideal completion
\newcommand{\ideal}[1]{\ensuremath{\mathsf{Idl}({#1})}}

% complete prime elements
\newcommand{\pr}[1]{\ensuremath{\mathop{\mathit{pr}({#1})}}}
\newcommand{\wpr}[1]{\ensuremath{\mathop{\mathit{wpr}({#1})}}}

% irreducible elements
\newcommand{\ir}[1]{\ensuremath{\mathop{\mathit{ir}({#1})}}}

% difference of irreducible elements
\newcommand{\diff}[2]{\ensuremath{\delta({#1},{#2})}}

% immediate precedence

% abbreviation for event structure
% \newcommand{\esabbr}{event structure}
\newcommand{\esabbr}{\textsc{es}}
\newcommand{\esnabbr}{\textsc{esnb}}
\newcommand{\esnmabbr}{\textsc{esn}}
\newcommand{\eseqabbr}{\textsc{epes}}

% predecessor of an irreducible
\newcommand{\pred}[1]{\ensuremath{\mathit{p}({#1})}}

% irreducible elements in es domains
\newcommand{\esir}[2]{\ensuremath{\langle{#1}, {#2}\rangle}}

% equivalence classes [of irreducibles]
\newcommand{\eqclass}[2][]{\ensuremath{[{#2}]_{\scriptscriptstyle {#1}}}}
% union of the equivalence classes of the elements in a set
\newcommand{\eqclasscup}[2]{\ensuremath{{#2}_{\scriptscriptstyle {#1}}}}

\newcommand{\eqclassir}[1]{\ensuremath{\eqclass[\leftrightarrow^*]{#1}}}

% quotient of set wrt a relation
\newcommand{\quotient}[2]{\ensuremath{{#1}_{\scriptscriptstyle {#2}}}}

% category of event structures 
\newcommand{\es}{\ensuremath{\mathsf{ES}}}
% category of stable event structures 
\newcommand{\ses}{\ensuremath{\mathsf{sES}}}
% category of prime event structures 
\newcommand{\pes}{\ensuremath{\mathsf{pES}}}
% category of prime event structures with equivalence
\newcommand{\epes}{\ensuremath{\mathsf{epES}}}

% category of connected event structures 
\newcommand{\ces}{\ensuremath{\mathsf{cES}}}

% category of weak prime algebraic domains domains 
\newcommand{\WDom}{\ensuremath{\mathsf{wDom}}}
% category of domains
\newcommand{\Dom}{\ensuremath{\mathsf{Dom}}}
% category of prime algebraic domains
\newcommand{\PDom}{\ensuremath{\mathsf{pDom}}}

%%%%% NON BINARY CONFLICT

% category of event structures 
\newcommand{\esn}{\ensuremath{\mathsf{ES_{nb}}}}
% category of stable event structures 
\newcommand{\sesn}{\ensuremath{\mathsf{sES_n}}}

% category of connected event structures 
\newcommand{\cesn}{\ensuremath{\mathsf{cES_{nb}}}}

% category of prime event structures 
\newcommand{\pesn}{\ensuremath{\mathsf{pES_n}}}

% category of fusion domains 
\newcommand{\WDomb}{\ensuremath{\mathsf{wDom_b}}}
% category of domains
\newcommand{\Domb}{\ensuremath{\mathsf{Dom_b}}}
% category of prime algebraic domains
\newcommand{\PDomb}{\ensuremath{\mathsf{pDom_b}}}

%%%%% END NON BINARY CONFLICT

% slice category
\newcommand{\slice}[2]{\ensuremath{({#1} \downarrow {#2})}}

% event structure for a domain
\newcommand{\zev}[0]{\ensuremath{\mathcal{E}}}
\newcommand{\ev}[1]{\ensuremath{\zev({#1})}}

% from general to connected event structures
\newcommand{\zconnes}[0]{\ensuremath{\mathcal{C}}}
\newcommand{\connes}[1]{\ensuremath{\zconnes({#1})}}
% and inclusion
\newcommand{\zinces}[0]{\ensuremath{\mathcal{I}}}
\newcommand{\inces}[1]{\ensuremath{\zinces({#1})}}

% stable version
\newcommand{\zsev}[0]{\ensuremath{\mathcal{E}_S}}
\newcommand{\sev}[1]{\ensuremath{\zsev({#1})}}

% with equivalence
\newcommand{\zeveq}[0]{\ensuremath{\mathcal{E}_{eq}}}
\newcommand{\eveq}[1]{\ensuremath{\zeveq({#1})}}

% es with equivalence to es and vice
\newcommand{\zfuse}[0]{\ensuremath{\mathcal{M}}}
\newcommand{\fuse}[1]{\ensuremath{\zfuse({#1})}}
\newcommand{\zunf}[0]{\ensuremath{\zunf}}
\newcommand{\unf}[1]{\ensuremath{\mathcal{U}({#1})}}

% Winskel/Droste version
\newcommand{\zevwd}[0]{\ensuremath{\mathcal{E}_{wd}}}
\newcommand{\evwd}[1]{\ensuremath{\zevwd({#1})}}

% configurations of an event structure
\newcommand{\conf}[1]{\ensuremath{\mathit{Conf}({#1})}}
% finite configurations
\newcommand{\conff}[1]{\ensuremath{\mathit{Conf_F}({#1})}}

% product of the sets of minimal enablinsg
\newcommand{\pmin}[1]{\ensuremath{U_{#1}}}

% connectectedness of minimal enablinsg
\newcommand{\conn}[1]{\ensuremath{\stackrel{#1}{\frown}}}

% domain for an event structure or graph grammar
\newcommand{\zdom}[0]{\ensuremath{\mathcal{D}}}
\newcommand{\dom}[1]{\ensuremath{\zdom({#1})}}

\newcommand{\zdomeq}[0]{\ensuremath{\mathcal{D}_{eq}}}
\newcommand{\domeq}[1]{\ensuremath{\zdomeq({#1})}}

% partial order for a graph grammar
\newcommand{\poset}[1]{\ensuremath{\mathcal{P}({#1})}}

% stable version
\newcommand{\pdom}[1]{\ensuremath{\mathcal{D}_S({#1})}}
\newcommand{\ppdom}[0]{\ensuremath{\mathcal{D}_S}}

% powerset
\newcommand{\Pow}[1]{\ensuremath{\mathbf{2}^{#1}}}

% powerset of finite subsets
\newcommand{\Powfin}[1]{\ensuremath{\mathbf{2}_\mathit{fin}^{#1}}}

% powerset of subsets of cardinality <= 1
\newcommand{\Powone}[1]{\ensuremath{\mathbf{2}_1^{#1}}}

% integer interval
\newcommand{\interval}[2][1]{\ensuremath{[{#1},{#2}]}}

% domain interval
\newcommand{\dint}[2]{\ensuremath{[{#1},{#2}]}}

% set of intervals
\newcommand{\IntSet}[1]{\ensuremath{\mathop{\mathit{Int}({#1})}}}

% intervals to irreducibles and vice
\newcommand{\inir}{\ensuremath{\mathop{\mathit{\zeta}}}}
\newcommand{\irin}{\ensuremath{\mathop{\mathit{\iota}}}}

% permutations
\newcommand{\perm}{\sigma}

% causes
\newcommand{\causes}[1]{\ensuremath{\lfloor {#1})}}

%%% GRAPH GRAMMARS

\newcommand{\Abs}[1]{\ensuremath{\mathsf{Abs}({#1})}}
\newcommand{\tr}[1]{\ensuremath{\mathsf{Tr}({#1})}}
% fusion safe traces
\newcommand{\trs}[1]{\ensuremath{\mathsf{Tr}_s({#1})}}
%\newcommand{\graph}{\ensuremath{\mathsf{Graph}}}
\newcommand{\tgraph}[1]{\ensuremath{\mathsf{Graph}_{#1}}}
\newcommand{\can}[1]{\ensuremath{\mathsf{C}({#1})}}
% source and target of a derivation
\newcommand{\source}[1]{\ensuremath{\mathsf{s}({#1})}}
\newcommand{\target}[1]{\ensuremath{\mathsf{t}({#1})}}
\newcommand{\col}[1]{\ensuremath{\mathsf{col}({#1})}}

% left decorated trace
\newcommand{\ltrace}[1]{\ensuremath{\langle {#1}\rangle_c}}

\newcommand{\bx}[1]{\phantom{\big(}#1{\phantom{\big)}}}
\newcommand{\bxx}[1]{\,#1\,}
\newcommand{\cycl}[1]{\ensuremath{\mbox{\textcircled{\scriptsize{$#1$}}}}}
\renewcommand{\iff}{\ensuremath{\Leftrightarrow}}

%%%%GENERAL CATEGORICAL NOTATION

\newcommand{\gph}[1]{\textbf{\textup{{#1}-Graph}}}

\newcommand{\dph}{\mathsf{dph}}
%identità
\newcommand{\id}[1]{\mathsf{id}_{#1}}
%codominio
\newcommand{\cod}[1]{\mathsf{cod}({#1})}
	%Variabili categorie
\def\A{\textbf {\textup{A}}}
%mono
\newcommand{\mto}[0]{\scalebox{1}{$\rightarrowtail$}}

\newcommand{\sk}{\mathsf{sk}_{\X}}

\def\R{\mathsf{R}}
\def\B{\textbf {\textup{B}}}
\def\C{\textbf {\textup{C}}}
\def\D{\textbf {\textup{D}}}
\def\X{\textbf {\textup{X}}}
\def\Y{\textbf {\textup{Y}}}
\def\G{\textbf {\textup{G}}}

\newcommand{\ske}{\mathsf{sk}(\X)}
\renewcommand{\P}{\textbf {\textup{P}}}

%\derivazioni

\newcommand{\dder}[1]{\mathscr{#1}}
\newcommand{\sder}[2]{S_{i_1,i_2}(\mathscr{#1}, \mathscr{#2})}
\newcommand{\der}[1]{\underline{\dder{#1}}}
\def\dpo{\mathsf{C}^{\X}_R}
\def\gpo{\mathsf{G}^{\X}_R}
\def\dpi{[\mathsf{C}]^{\X}_R}
\def\gpi{[\mathsf{G}]^{\X}_R}

\newcommand{\ider}[1]{\mathscr{I}_{#1}}

%categorie
\def\Set{\textbf {\textup{Set}}}

%comma
\newcommand{\comma}[2]{#1\hspace{1pt} {\downarrow}\hspace{1pt} #2}
\newcommand{\cma}[2]{\mathcal{#1}\hspace{1pt} {\downarrow}\hspace{1pt} \mathcal{#2}}

%derivazioni
\newcommand{\lpro}{\langle \hspace{-1.85pt}[}
\newcommand{\rpro}{]\hspace{-1.85pt}\rangle}
\newcommand{\tpro}[1]{\lpro \der{#1}\rpro}
\newcommand{\tproi}[2]{\lpro \der{#1}_{#2}\rpro}
\newcommand{\lgh}[0]{\mathsf{lg}}

%%% NEW

\usepackage{xparse}

% inversions
\newcommand{\inv}[1]{\mathsf{inv}({#1})}
\newcommand{\tnv}[1]{\mathsf{tnv}({#1})}

%% sequential independence
%\newcommand{\seqind}{\ensuremath{\updownarrow}}

% direct shift
\newcommand{\shift}[1]{\ensuremath{\mathrel{{\leftrightsquigarrow}_{#1}}}}

% shift equivalence
\newcommand{\shifteq}[1][]{\ensuremath{\mathrel{{\equiv}^\mathit{sh}_{#1}}}}

% transp{source}[target]: if target not specified source+1
\NewDocumentCommand{\transp}{m o}{%
  \ensuremath{({#1},%
  \IfNoValueTF{#2}%
    {{#1}+1}%
    {#2}%
    )}
}

\NewDocumentCommand{\mycommand}{o}{%
  % <code>
  \IfNoValueTF{#1}
    {code when no optional argument is passed}
    {code when the optional argument #1 is present}%
  % <code>
}
% interchange
\newcommand{\IC}[1]{\ensuremath{\mathit{IC}({#1})}}

%%%%% Ambienti matematici  %%%%%%
%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{corollary}[theorem]{Corollary}

%\theoremstyle{definition}
%\newtheorem{definition}[theorem]{Definition}
\newtheorem*{notation}{Notation}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{example}[theorem]{Example}

% commands for restructuring
\newcommand{\rem}[2]{{\color{blue}#1}{\color{red}#2}}
\renewcommand{\rem}[2]{}

% fake author for anonymous submission
%\author{Alan Turing} 
%{Department of Mathematics, Somewhere}
%{alan@turing.com}{}{}

\author{Paolo Baldan} 
{Department of Mathematics, University of Padua, Italy}
{baldan@math.unipd.it}
{https://orcid.org/0000-0001-9357-5599}{}

\author{Davide Castelnovo}
{Department of Mathematics, University of Padua, Italy}
{davide.castelnovo@math.unipd.it}
{https://orcid.org/0000-0002-5926-5615}{}

\author{Andrea Corradini}
{Department of Computer Science, University of Pisa, Italy}
{andrea.corradini@unipi.it}
{https://orcid.org/0000-0001-6123-4175}{}

\author{Fabio Gadducci}
{Department of Computer Science, University of Pisa, Italy}
{fabio.gadducci@unipi.it}
{https://orcid.org/0000-0003-0690-3051}{}

\authorrunning{P.~Baldan, D.~Castelnovo, A.~Corradini, F.~Gadducci}
%
\Copyright{Paolo Baldan, Davide Castelnovo, Andrea Corradini, and Fabio Gadducci}
%
\ccsdesc[500]{Theory of Computation~Models of computation}
\ccsdesc[500]{Theory of Computation~Semantics and reasoning}
%
\keywords{
Adhesive categories, double-pushout rewriting, left-linear rules, switch equivalence, local Church-Rosser property.
}

\funding{The research has been partially supported by the EuropeanUnion - NextGenerationEU under the National Recovery and Resilience Plan (NRRP) - Call PRIN 2022 PNRR - Project P2022HXNSC ``Resource Awareness in Programming: Algebra, Rewriting, and Analysis'', by the Italian MUR - Call PRIN 2022 - Project 20228KXFN2 
``Spatio-Temporal Enhancement of Neural nets for Deeply
Hierarchical Automatised Logic'' and by the University of Pisa - Call PRA 2022 - Project 2022\_99 ``Formal Methods for the Healthcare Domain based on Spatial Information''.}

\EventEditors{Rupak Majumdar and Alexandra Silva}
\EventNoEds{2}
\EventLongTitle{35th International Conference on Concurrency Theory (CONCUR 2024)}
\EventShortTitle{CONCUR 2024}
\EventAcronym{CONCUR}
\EventYear{2024}
\EventDate{Septembre 9--13, 2024}
\EventLocation{Calgary, Canada}
\EventLogo{}
\SeriesVolume{311}
\ArticleNo{6}

\title{Left-Linear Rewriting in Adhesive Categories}

\begin{document}
\maketitle

\begin{abstract}
  When can two sequential steps performed by a computing device be
  considered (causally) independent?  This is a relevant question for
  concurrent and distributed systems, since independence means that
  they could be executed in any order, and potentially in
  parallel. Equivalences identifying rewriting sequences which differ
  only for independent steps are at the core of the theory of
  concurrency of many formalisms. We investigate the issue in the context of the double pushout
  approach to rewriting in the general setting of adhesive categories.
  While a consolidated theory exists for linear rules, which
  can consume, preserve and generate entities, this paper focuses on
  left-linear rules which may also ``merge'' parts of the state.  This is an apparently minimal, yet technically hard enhancement, since  a standard characterisation of independence that -- in the
  linear case -- allows one to derive a number of properties,
  essential in the development of a theory of concurrency, no longer
  holds.  The paper performs an in-depth study of the notion of independence
  for left-linear rules: it introduces a novel characterisation of
  independence, identifies well-behaved classes of left-linear
  rewriting systems, and provides some fundamental results including a
  Church-Rosser property and the existence of canonical equivalence
  proofs for concurrent computations. These results properly extends
  the class of formalisms that can be modelled in the adhesive
  framework.
\end{abstract}

\section{Introduction}

One of the key pay-off of concurrency theory is the idea that the behaviour of 
a computational device can be modelled by abstracting its sequences of steps
via a suitable equivalence. Intuitively, the equivalence 
captures when steps are causally unrelated and thus could be executed in any 
order, and possibly in parallel. Two seminal contributions to this line of research have been
Mazurkiewicz's traces~\cite{Mazurkiewicz86} and Winskel's event structures~\cite{NPW:PNES}.
Concerning formalisms based on the rewriting paradigm, concurrency often boils down to having a notion of independence between two consecutive steps. 
Noteworthy examples are the
interchange law~\cite{Mes92} in term rewriting and permutation 
equivalence~\cite{JJL80} in $\lambda$-calculi.

Among rewriting-based formalisms, those manipulating graph-like
structures proved useful in many settings for representing the
dynamics of distributed systems: the graph is used to represent the
entities and their relations within states, while rewriting steps,
modifying the graph, model computation steps that result in changes to
the system state. The DPO (double-pushout) approach~\cite{EhrigPS73}
is nowadays considered a standard one for these structures, thanks to
its locality (rule application has a local effect on a state,
differently from more recent approaches like
SqPO~\cite{CorradiniHHK06} or PBPO$^+$~\cite{OverbeekER23}) and to its
flexibility: the rules allow to specify that, in a rewriting step,
some entities in the current state are removed, some others are needed
for the rewriting step to occur but remain unaltered, and some new
entities can be generated. Concerning concurrency, the chosen notion
is switch (also referred to as shift) equivalence, and independence is formally captured by what is
called the Church-Rosser theorem of DPO
rewriting~\cite[Chapter 3, Section~3.4]{CorradiniMREHL97}.

A noteworthy advantage of DPO rewriting is that it can be formulated over
adhesive categories and their variants~\cite{lack2005adhesive,ehrig2006weak}, which include, among others, toposes~\cite{johnstone2007quasitoposes} and string diagrams~\cite{bonchi2022string}. Operating within the framework of adhesive categories allows one to devise the foundations of a rewriting theory that can be then instantiated to the context of interest, thus avoiding the need of
repeatedly proving similar ad-hoc results for each specific setting.

So far, most of the theoretical results focused on \emph{linear rules}: intuitively, a step is required only to consume, preserve and generate entities.  However, in some situations it is also necessary to ``merge'' parts of the state.  This happens in the context of string diagrams mentioned above, but also in graphical implementations of nominal calculi where, as a result of name passing, the received name is identified with a local one at the receiver~\cite{CVY:ESSPE,Gad07}, or in the visual modelling of bonding in biological/chemical processes~\cite{PUY:MBPE}. A similar mechanism is at the core of e-graphs (equality graphs), used for rewrite-driven compiler optimisations~\cite{WNW:egg}: rather thanmerging nodes corresponding to equal expressions, the idea -- conceptually and, as we will see, also mathematically similar -- is to maintain an
equivalence over the nodes.

Technically, to acquire the expressiveness needed for capturing fusions, i.e.~the merge of some elements in the state, requires to move from linear to left-linear rewriting rules. While left-linear rules have been considered in various instances (mainly in categories of graphs) and some results concerning the corresponding rewriting theory have been put forward~\cite{Ehrig1976,EHP:BRfTToHLRS,baldan2011adhesivity}, the phenomena arising when devising a theory of independence and concurrency for rewriting with left-linear rules in the general
setting of adhesive and quasi-adhesive categories have not been systematically explored, even if an investigation in the setting of quasi-topoi, considering non-linear rules yet restricting their applicability, has been presented in~\cite{behr2021concurrency,BehrHK23}.

\begin{figure}
  \input{Figure/coffee-rules.tex}

  \caption{Rewriting rules for the coffee example.}
  \label{fi:coffee-rules}
\end{figure}

\begin{figure}
  \input{Figure/coffee-rewriting.tex}
  \caption{A sequence of rewriting steps.}
  \label{fi:coffee-rewriting}
\end{figure}

Just to get some basic intuition about left-linear rewriting systems, their capabilities and the problems that can arise, assume we want to model a situation in which a coffee comes with a bag of white sugar and a bag of brown sugar. The situation is represented by the graph $G_0$ in Fig.~\ref{fi:coffee-rewriting}: the loop $\mathit{c}$ is the coffee, the two loops $b$ and $w$  represent the white and brown sugar. The corresponding nodes are connected to the coffee node by an $s$-labelled edge to indicate that they can be possibly added to the coffee. The available rules are in Fig.~\ref{fi:coffee-rules}. Rules $\rho_w$ and $\rho_b$ model the addition of white and brown sugar, respectively, to the coffee. Note that adding one kind of sugar, say $x$, to the coffee is realised by deleting loop $x$ and merging the corresponding node with the coffee node so that a self-loop $s$ is created.

Once some sugar has been added, the coffee is ready for drinking. This is represented by rule $\rho_r$, which checks for the presence of sugar, represented by the loop $s$, in the coffee, and brings it to the $r$ state, ready for drinking.

A rewriting sequence is depicted in Fig.~\ref{fi:coffee-rewriting}, applying $\rho_w$, $\rho_b$, and $\rho_r$ in sequence, thus producing a coffee with both white and brown sugar, ready for drinking. A first interesting observation is that after applying rule $\rho_w$ to $G_0$, thus producing graph $G_1$, we can still apply rule $\rho_b$, with a non-injective match. Intuitively, once the coffee is ready for drinking because some sugar has been added, adding more sugar will not change its state. Indeed, the rules could also be applied in reverse order. Should they be considered independent? Moreover, since rule $\rho_r$ just requires the presence of sugar, it could be applied immediately after $\rho_w$. This might lead to think that $\rho_b$ and $\rho_r$ are independent. However, this is not completely clear, since in absence of $\rho_w$, the application of $\rho_b$ would be essential to enable $\rho_r$.

In this paper we perform a systematic exploration of these phenomena at the level of $\mathcal{M}$-adhesive categories, which encompass a large family of DPO-based formalisms.

As an initial step, we observe that for left-linear rules some fundamental properties that play a role
in the concurrency theory of linear rewriting need to be deeply revised, or plainly do not hold. Firstly, the notion of sequential independence and the Church-Rosser theorem, ensuring that sequential independent steps can be performed in reverse order, does not hold out of the box. Even worse, given two independent steps it might be possible to switch them in several
different ways. As we will observe, this prevents the development of a sensible theory
of concurrency, since switches are used as a basis for equating
sequences of rewriting steps that differ only in the order of
independent steps.

We single out a class of left-linear rewriting systems, referred to as \emph{well-switching rewriting systems}, where sequential independence ensures existence and uniqueness of the switch, and argue that this is the right setting for dealing with left-linear rewriting systems.

On the one hand, they capture most categories of interest for rewriting. Indeed, we identify general classes of left-linear rewriting systems on graph-like structures that are well-switching. As a sanity check, we prove that linear rewriting systems are well-switching.

On the other hand, we argue that a concurrency theory of rewriting can be developed for well-switching rewriting systems, recovering, sometimes in weakened form, most of the results that hold in the linear case. The development faces a main technical obstacle. In the literature on linear rewriting systems, a central result is the characterisation of switch equivalence of sequences of steps based on
what are called processes or consistent permutations~\cite{CMR:GP,Handbook,BaldanCHKS06,heindel2009category}. In turn this is the key to derive some fundamental properties for linear rewriting, namely
\begin{enumerate}
\item \emph{globality of independence}: if two independent steps are
  moved forward or backward due to the application of switchings to a
  sequence, they remain independent;
\item \emph{consistency of switching}: when transforming
  sequences of rewriting steps into equivalent ones by switching independent steps, the
  result does not depend on the order in which switchings are applied, but
  only on the associated permutation.
\end{enumerate}
Properties (1) and (2) allow one to deduce a canonical form for equivalence proofs 
between sequences of rewriting steps seen as concurrent computations.

The fact that for left-linear rewriting systems the characterisation of switch equivalence via consistent permutations fails, and thus cannot be used for proving (1) and (2), leads to asking if these
properties hold.  We show that much of the theory can be retained: globality of independence holds in a weaker form, conceptually linked to the fact that fusions introduce a form of disjunctive causality, while consistency of switching holds unchanged. Finally, we prove that a canonical form for switching
sequences can also be recovered. These results represent a solid basis for developing a satisfactory theory of concurrency for left-linear rules.

\emph{Synopsis.} 
In \S\ref{sec:ade} we recall the basic definitions of DPO rewriting for $\mathcal{M}$-adhesive categories. 
In \S\ref{sec:equi} we present the key novelties of our proposal, introducing the standard notion of independence and a novel axiomatic notion of switchability, showing that the former fails to imply the latter for left-linear rewriting systems. We then define a subclass of left-linear rewriting systems
that we call well-switching rewriting systems, and we prove that the classical results for linear rewriting systems are recovered for such a class. Finally, in \S\ref{conclusions} we outline directions for future work. The appendices recall basic results on adhesive categories (Appendix~\ref{app:ade}), present \emph{strong enforcing} rewriting systems, a class of systems where the local Church-Rosser Theorem holds (Appendix~\ref{app:fill}), and give proofs of the results (Appendix~\ref{omitted}).

\section{$\mathcal{M}$-adhesive categories and rewriting systems}\label{sec:ade}

This  section recalls the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}. Given a category $\X$ we will not distinguish notationally between $\X$ and its class of objects, so
``$X\in \X$'' means that $X$ is an object of $\X$. We let $\mor(\X)$, $\mon(\X)$ and $\reg(\X)$ denote the class of all arrows, monos and regular monos of $\X$, respectively.  Given an integer $n\in \mathbb{Z}$, $[0,n]$ denotes the set of natural numbers less than or equal to $n$; in particular, $[0,n]=\emptyset$ if $n<0$.

\subsection{$\mathcal{M}$-adhesivity}\label{subsec:ade}
The key property of $\mathcal{M}$-adhesive categories is the \emph{Van Kampen condition}~\cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive}. In order to define it we need to introduce some terminology.  Let  $\X$ be a category. A subclass $\mathcal{A}$ of
  $\mor(\X)$ is called
  \begin{itemize}
    \parbox{11cm}{\item
      \emph{stable under pushouts (pullbacks)} if for every pushout (pullback) square as the one on the right, 	if $m \in \mathcal{A}$ ($n\in \mathcal{A}$) then $n \in \mathcal{A}$ ($m \in \mathcal{A}$);
    \item \emph{closed under composition} if $h, k\in \mathcal{A}$ implies $h\circ k\in \mathcal{A}$ whenever $h$ and $k$ are composable.{\tiny }}\hfill
    \parbox{2cm}{$\xymatrix{A\ar[r]^f  \ar[d]_{m}& B \ar[d]^n \\ C \ar[r]_g & D}$}
    \parbox{11cm}{}\hfill
  \end{itemize}

  \begin{definition}[Van Kampen property]
    Let $\X$ be a category and consider the diagram\\
    \parbox{10cm}{
      aside.
    Given  a class of arrows $\mathcal{A}\subseteq \mor(\X)$, we say that the bottom square
    is an \emph{$\mathcal{A}$-Van Kampen square} if
      \begin{enumerate}
      \item it is a pushout square;
    \item 	whenever the cube above has pullbacks as back and left faces and the vertical arrows belong to $\mathcal{A}$, then its top face is a pushout 
      if and only if the front and right faces are pullbacks.
      \end{enumerate}}
    \parbox{2cm}{$\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D }$ }\\
    Pushout squares that enjoy only the ``if'' half of item (2) above are called \emph{$\mathcal{A}$-stable}.

    A $\mor(\X)$-Van Kampen square is called  \emph{Van
      Kampen} and a $\mor(\X)$-stable square  \emph{stable}.
  \end{definition}

We can now define $\mathcal{M}$-adhesive categories.

\begin{definition}[$\mathcal{M}$-adhesive category]
  Let $\X$ be a category and $\mathcal{M}$ a subclass of
  $\mon(\X)$  including  all isomorphisms, closed under composition,  and stable under pullbacks and pushouts.  The category  $\X$ is said to be \emph{$\mathcal{M}$-adhesive} if
  \begin{enumerate}
  \item it has \emph{$\mathcal{M}$-pullbacks}, i.e.~pullbacks along arrows of $\mathcal{M}$;
  \item it has \emph{$\mathcal{M}$-pushouts}, i.e.~pushouts along arrows of $\mathcal{M}$;
  \item  $\mathcal{M}$-pushouts are $\mathcal{M}$-Van Kampen squares.
  \end{enumerate}

  A category $\X$ is said to be \emph{strictly $\mathcal{M}$-adhesive}
  if $\mathcal{M}$-pushouts are Van Kampen squares.
\end{definition}

We write $m\colon X\mto Y$ to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$.

\begin{remark}
  \label{rem:salva}
  \emph{Adhesivity} and \emph{quasiadhesivity} 
  \cite{lack2005adhesive,garner2012axioms} coincide with strict
  $\mon(\X) $-adhesivity and strict $\reg(\X)$-adhesivity,
  respectively.
\end{remark}

\begin{example}
  \label{rem:iso}
  Every category $\X$ is $\mathsf{I(\X)}$-adhesive, where $\mathsf{I(\X)}$ is the class of 
  isomorphisms.
\end{example}

$\mathcal{M}$-adhesivity is well-behaved with respect to  the construction of slice and functor categories \cite{mac2013categories}, as shown by the following theorems~\cite{ehrig2006fundamentals,lack2005adhesive}.

\begin{theorem}
  \label{thm:slice-functors}
  Let $\X$ be an $\mathcal{M}$-adhesive category. Given an object $X$
  the category $\X/X$ is $\mathcal{M}/X$-adhesive with
  $\mathcal{M}/X:=\{m\in \mor(\X/X) \mid m\in
  \mathcal{M}\}$. Similarly, $X/\X$ is $X/\mathcal{M}$-adhesive with
  $X/\mathcal{M}:=\{m\in \mor(X/\X) \mid m\in \mathcal{M}\}$.

  Moreover for every small category $\Y$, the category $\X^\Y$ of
  functors $\Y\to \X$ is $\mathcal{M}^{\Y}$-adhesive, where
  $\mathcal{M}^{\Y}:=\{\eta \in \mor(\X^\Y) \mid \eta_Y \in
    \mathcal{M} \text{ for every } Y\in \Y\}$.
\end{theorem}

We can list various examples of $\mathcal{M}$-adhesive categories (see
\cite{castelnovo2023thesis,CastelnovoGM22,lack2006toposes}).

\begin{example}
  \label{ex:adhesive}
  $\cat{Set}$ is adhesive, and, more generally, every topos is
  adhesive~\cite{lack2006toposes}. By the closure properties above, every presheaf $[\cat{X},\cat{Set}]$ is adhesive, thus the category
  $\cat{Graph} = [ E \rightrightarrows V, \cat{Set}]$ is adhesive
  where $E \rightrightarrows {V}$ is the two objects category with two
  morphisms $s,t \colon{E} \to {V}$. Similarly, various
  categories of hypergraphs can be shown to be adhesive, such as term
  graphs and hierarchical graphs~\cite{CastelnovoGM24}. Note that the category $\cat{sGraphs}$ of simple graphs, 
  i.e.~graphs without parallel edges, is
  $\reg{(\cat{sGraphs})}$-adhesive~\cite{BehrHK23} but not
  quasiadhesive.
\end{example}

A number of properties of adhesive categories that play a role in the
theory of rewriting generalise to $\mathcal{M}$-adhesive
categories. These include $\mathcal{M}$-pushout-pullback decomposition
and uniqueness of pushouts complements (details and proofs are in
\Cref{app:ade}).

\subsection{DPO rewriting systems derivations}\label{subsec:DPO}

$\mathcal{M}$-adhesive categories are the right context in which to
perform abstract rewriting using what is called the Double-Pushout
(DPO) approach.

\begin{definition}[\!\!\cite{habel2012mathcal,heindel2009category}]
  Let $\X$ be an $\mathcal{M}$-adhesive category. A \emph{left
    $\mathcal{M}$-linear} rule $\rho$ is a pair  of
  arrows $\rho = (l: K \to L, r: K \to R)$ such that $l$ belongs to
  $\mathcal{M}$.  The rule $\rho$ is \emph{$\mathcal{M}$-linear} if
  $r\in \mathcal{M}$ too.
  \full{A rule $\rho$ is said to be
    \emph{consuming} if $l$ is not an isomorphism.}
  The object $L$ is
  the \emph{left-hand side}, $R$ the \emph{right-hand side}, and
  $K$ the \emph{interface}.

  A \emph{left-linear rewriting system} is a pair $(\X, \R)$ where
  $\X$ is an $\mathcal{M}$-adhesive category and $\R$ a set of left
  $\mathcal{M}$-linear rules. It  is  called $\mathcal{M}$-\emph{linear} if every rule in $\R$ is  $\mathcal{M}$-linear.

  \vspace{.1cm}
  \noindent
  \parbox{10cm}{\hspace{15pt}Given two objects $G$ and $H$ and a rule
    $\rho=(l,r)$ in $\R$, a \emph{direct derivation $\mathscr{D}$ from
      $G$ to $H$ applying rule $\rho$} is a diagram as the one
    aside, in which both squares are pushouts. The arrow $m$ is called
    the \emph{match} of the derivation, while $h$ is its
    \emph{co-match}.  We denote a direct derivation $\dder{D}$
    from $G$ to $H$ as $\dder{D}\colon G\Mapsto H$. }
  \parbox{3cm}{$\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l}
      \ar[r]^{r} & R \ar[d]^{h}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}&
      H}$}
\end{definition}

A derivation can now be defined simply as a sequence of direct derivations.

\begin{definition}[Derivation]
  Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a
  left-linear rewriting system.  Given $G, H \in \X$, a
  \emph{derivation} $\der{D}$ with source $G$ and target $H$, written
  $\der{D}: G \Mapsto H$, is defined as a sequence
  $\{\dder{D}_i\}_{i=0}^n$ of direct derivations such that
  $\dder{D}_i : G_i \Mapsto G_{i+1}$ is a direct derivation for every
  index $i$ and $G_0=G$, $G_{n+1}=H$. Moreover, we have an \emph{empty derivation} $G : G \Mapsto G$ for each $G \in \X$.  We denote by $\lgh(\der{D})$ the \emph{length} of a derivation $\der{D}$.

  Given a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^n$, we define $r(\der{D})  = \{\rho_i\}_{i=0}^n$ as the sequence of 
 rules such that every $\dder{D}_i$ applies rule $\rho_i\in \R$.  
\end{definition}

Derivations naturally compose: given $\der{D}: G \Mapsto H$ and $\der{E}: H \Mapsto F$, we can consider their composition $\der{D} \cdot \der{E}: G \to F$, defined in the obvious way.

Often, we are interested in derivations only up to some notion of coherent isomorphism between them. This leads us to the following definition.

\noindent
\parbox{8cm}{
  \begin{definition}[Abstraction equivalence]
    Let  $\X$ be an $\mathcal{M}$-adhesive category and 
    $(\X, \R)$ a left-linear rewriting system. 
    An \emph{abstraction equivalence} between derivations $\der{D}$
    and $\der{D'}$ with the same length and
    $r(\der{D})=r(\der{D}')$ is a family of isomorphisms
    $\{\phi_X\}_{X\in \{G_i,D_i\}}$ such that the diagram on the right commutes
    for $i\in [0, \min(0, \lgh(\der{D})-1 )]$. We say that $\der{D}$ are $\der{D}'$ are \emph{abstraction
      equivalent}, written $\der{D}\equiv_a \der{D}'$, if there exists an abstraction equivalence between
    them.
  \end{definition}
}
\parbox{4cm}{\vspace{-1.35em}$\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i}
    \ar@{>->}[l]_{f'_i}&G'_{i+1}\\ L_i \ar[u]^{m'_i} \ar[d]_{m_i}& K_i
    \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i}
    &R_i \ar[u]^{h'_i} \ar[d]_{h_i}\\G_i
    \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar@{>->}[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole
    \ar[r]_{g_i}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{G_{i+1}}}}$}

$\mathcal{M}$-adhesivity of $\X$ ensures the
uniqueness of the result of applying a rule to an object: two
direct derivations using the same match are abstraction equivalent
(see Proposition~\ref{prop:unique}).

\section{Independence in rewriting}
\label{sec:equi}

In this section we discuss the notion of independence between two
consecutive rewriting steps, a fundamental ingredient of the rewriting
theory, which comes into play when viewing a sequence of steps as a
concurrent computation. We observe that moving from linear to
left-linear rules leads to the failure of various basic properties of
the classical notion of independence used in the linear setting and we
single out a framework in which these can be re-established, possibly
in a weakened form.

\subsection{Sequentially independent and switchable derivations }\label{subsec:switch}

Sequential independence is the canonical notion of independence in the DPO approach.

\begin{definition}[Sequential independence]
  \label{de:sequential-independence}
  Let $\X$ be an $\mathcal{M}$-adhesive category 
  and $(\X, \R)$ a left-linear rewriting system. 
  Let also
  $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation of length $2$, with
  $\dder{D}_i$ using rule $\rho_i = (l_i,r_i)$.  We say that $\dder{D}_0$ and
  $\dder{D}_1$ are
  \emph{sequentially independent}
  if there is a pair of arrows
  $i_0\colon R_0\to D_1$ and $i_1\colon L_1\to D_0$ such that the
  following diagram commutes. In this case $(i_0,i_1)$ is called an  \emph{independence
    pair}.
  \[\xymatrix@R=16pt@C=15pt{L_0 \ar[d]_{m_0}&& K_0
      \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
      \ar@{.>}@/^.35cm/[drrr]|(.3)\hole_(.4){i_0}
      \ar[dr]|(.3)\hole_{h_0} && L_1 \ar@{.>}@/_.35cm/[dlll]^(.4){i_1}
      \ar[dl]|(.3)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
      \ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
      D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
      \ar[rr]_{g_1}&& G_2}
  \]
\end{definition}

Intuitively, the existence of the independence pair
captures the possibility of switching the application of the two rules:
$f_0 \circ i_1$ is a match for $\rho_1$ in $G_0$ and the
existence of $i_0 : R_0 \to D_1$ means that $\rho_1$ does not delete
items in the image of $K_0$, thus $\rho_0$ can be applied after
$\rho_1$.

\begin{remark}\label{rem:uni}
	It is worth mentioning that if $(\X, \R)$ is a linear rewriting system then two derivations $\dder{D}_0$ and $\dder{D}_1$ can have at most one independence pair. Indeed if $(i_0,i_1)$ and $(i'_0, i'_1)$ are independence pairs, then
	\[g_0\circ i_1 = g_0\circ i'_1 \qquad f_1\circ i_0=f_1\circ i'_0\]
But in linear systems $g_0$ and $f_1$ are both monos, entailing $i_0=i'_0$ and $i_1=i'_1$.
\end{remark}

We next formalise what it means for a derivation being the switch of another.

\begin{definition}[Switch]
  \label{def:switch}
  Let $\X$ be an $\mathcal{M}$-adhesive category 
  and $(\X, \R)$ a left-linear rewriting system. 
  Let also
  $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation made
  of two sequentially independent derivations $\dder{D}_0$,
  $\dder{D}_1$ with independence pair $(i_0, i_1)$, as in the diagram
  on the left below. A \emph{switch} of $\der{D}$ along $(i_0,i_1)$ is
  a derivation $\der{E}=\{\dder{E}_i\}_{i=0}^1$, between the same objects and using the same rules
  in reverse order, as in the diagram on the right below
  \[
    \def\objectstyle{\scriptstyle}\def\labelstyle{\scriptstyle}
    \xymatrix@C=1.1mm@R=8mm{
      {L_0} \ar[d]_{m_0}
      & & {K_0} \ar@{>->}[ll]_{l_0} \ar[rr]^{r_0} \ar[d]_{k_0}
      & & {R_0} \ar[drr]|(.35)\hole_(.6){h_0}  \ar@/^.22cm/[drrrrrr]|(.3)\hole^(.75){i_0}
      & & & & 
      % 
      {L_1}\ar[dll]|(.35)\hole^(.6){m_1} \ar@/_.22cm/_(.75){i_1}[dllllll]
      & & {K_1} \ar@{>->}[ll]_{l_1} \ar[rr]^{r_1} \ar[d]^{k_1}
      & & {R_1} \ar[d]^{h_1} \\
      % 
      % 
      {G_0}
      & & {D_0} \ar@{>->}[ll]^{f_0} \ar[rrrr]_{g_0}
      & & & & {G_1} & &
      & &  {D_1} \ar@{>->}[llll]^{f_1} \ar[rr]_{g_1}
      & & {G_2}
    }
    % 
    \xymatrix@C=1.1mm@R=8mm{
      {L_1} \ar[d]_{m_0'}
      & & {K_1} \ar@{>->}[ll]_{l_1} \ar[rr]^{r_1} \ar[d]_{k_0'}
      & & {R_1} \ar[drr]|(.35)\hole_(.6){h_0'}  \ar@/^.22cm/@{.>}^(.75){i_0'}|(.3)\hole[drrrrrr]
      & & & & 
      % 
      {L_0}\ar[dll]|(.35)\hole^(.6){m_1'} \ar@/_.22cm/@{.>}_(.75){i_1'}[dllllll] 
      & & {K_0} \ar@{>->}[ll]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
      & & {R_0} \ar[d]^{h_1'} \\
      % 
      % 
      {G_0}
      & & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rrrr]_{g_0'}
      & & & & {G'_1} & &
      & &  {D_1'} \ar@{>->}[llll]^{f_1'} \ar[rr]_{g_1'}
      & & {G_2}  }
    %
  \]
  such that there is an independence pair $(i_0', i_1')$ between
  $\dder{E}_0$ and $\dder{E}_1$ and 
  \begin{center}   
    $m_0=f_0' \circ i_1'$
    \qquad $h_1=g_1' \circ i_0'$
    \qquad $m_0'= f_0 \circ i_1$
    \qquad $h_1'= g_{1}\circ i_0$.
  \end{center}

  If a switch of $\dder{D}_0$ and $\dder{D}_1$ exists we say that
  they are \emph{switchable}.
\end{definition}

It can be shown that switches along the same independence pair are unique up to abstraction
equivalence (see Proposition~\ref{thm:switch_uni}).

\begin{example}
  \label{ex:seq-ind}
  Consider a rewriting system in $\cat{Graph}$, the category of
  directed graphs and graph morphisms, which is adhesive. The set of
  rules $\R = \{ \rho_0, \rho_1, \rho_2\}$ is in
  Fig.~\ref{fi:rules}, where numbers are used to represent the
  morphisms from the interface to the left- and right-hand
  sides. Rules $\rho_0$ and $\rho_1$ are linear: $\rho_0$ generates a
  new node and a new edge, while $\rho_1$ creates a self-loop edge. Instead,
  $\rho_2$ is left-linear but not linear, as it ``merges'' two nodes.

  \begin{figure}
    \input{Figure/rules.tex}
    \caption{A rewriting system in $\cat{Graph}$.}
    \label{fi:rules}
  \end{figure}

  A derivation $\der{D}$ consisting of three steps $\dder{D}_0$,
  $\dder{D}_1$, and $\dder{D}_2$, each applying the corresponding rule
  $\rho_i$, is depicted in Fig.~\ref{fi:derD}. Note that the numbers in $\rho_1$
  were changed consistently to represent the vertical morphisms.
  Steps $\dder{D}_1$ and $\dder{D}_2$ are clearly sequential
  independent via the independence pair $(R_1 \to D_2, L_2 \to D_1)$,
  mapping nodes according to their numbering.
  %
  A switch of $\der{D}$ along such independence pair is the derivation
  $\der{E}$ in Fig.~\ref{fi:derE}. Instead, in $\der{D}$ the first two
  steps applying $\rho_0$ and $\rho_1$ are not sequential independent,
  intuitively because $\rho_1$ uses the node produced by $\rho_0$ for
  attaching a self-loop.

  \begin{figure}[t]
    \input{Figure/derD.tex}
    \caption{The derivation $\der{D}$.}
    \label{fi:derD}
  \end{figure}
  \begin{figure}[b]
    \input{Figure/derE.tex}
    \caption{The derivation $\der{E}$.}
    \label{fi:derE}
  \end{figure}
\end{example}

As we mentioned, for linear rewriting systems
it is canonical to identify
derivations that are equal ``up to switching'', i.e.~that differ
only in the order of independent steps. The same notion can be given
for left-linear rewriting systems by relying on the notion of switch.

We  recall some notations on permutations.  A \emph{permutation} on
$\interval[0]{n}$ is a bijection
$\sigma : \interval[0]{n} \to \interval[0]{n}$. It is a
\emph{transposition} $\nu$ if there are $i, j \in \interval{n}$,
$i \neq j$ such that $\sigma(i)=j$, $\sigma(j) = i$, and
$\sigma(k) = k$ otherwise; it is denoted as $\transp{i}[j]$. Given a permutation $\perm$, 
an \emph{inversion} for $\sigma$ is a pair $(i,j)$ such that $i<j$ and
$\sigma(j)< \sigma(i)$; $\inv{\sigma}$ denotes the set of
inversions of $\perm$.

Switch equivalence is now defined as the equivalence relating derivations that 
can be obtained one from another by a sequence of switches. Moreover, intermediate graphs can be taken up to isomorphism according to abstraction equivalence.

\begin{definition}[Switch equivalence]
  \label{de:switch-equivalence}
  Let $(\X, \R)$ be a left-linear rewriting system.  Let also
  $\der{D}, \der{E} : G \Mapsto H$ be derivations with the same
  length, $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and
  $\der{E}=\{\dder{E}_{i}\}_{i=0}^n$. If
  $\dder{D}_i \cdot \dder{D}_{i+1}$ is a switch of
  $\dder{E}_i \cdot \dder{E}_{i+1}$ for some $i \in [0,n-1]$ and  $\dder{D}_j = \dder{E}_j$ for each $j \not \in \{i,i+1\}$ then we write
  $\der{D} \shift{\transp{i}} \der{E}$. 
 A \emph{switching sequence} is a sequence $\{\der{D}_{k}\}_{k=0}^m$
  of derivations such that
    $\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
    \shift{\nu_m} \der{D}_m$  with $\nu_{k} = \transp{i_k}$.

    Let us denote by $\nu_{k,h}$ the composition
  $\nu_h \circ \nu_{h-1} \circ \ldots \nu_k$. We say that the
  switching sequence \emph{consists of inversions} if for all
  $k \in \interval[0]{m}$ the transposition $\nu_k$ is an inversion
  for $\nu_{1,m}$.

  Two derivations $\der{D}, \der{E}:G\Mapsto H$ are \emph{switch
    equivalent}, written $\der{D}\equiv^{sh} \der{E}$, if there is a
  switching sequence $\{\der{D}_{k}\}_{k=0}^m$ such that
  $\der{D}\equiv_a \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2}
  \ldots \shift{\nu_m} \der{D}_m \equiv _a \der{E}$.   
  To point out a chosen permutation of rewriting steps, we will also write $\der{D}\equiv^{sh}_{\sigma} \der{E}$, 
  where $\sigma$ is the composition of the transposition appearing in a chosen switching sequence. 
\end{definition}

\begin{remark}\label{rem:abst}
	The possibility of an empty switching sequence assures that two abstraction equivalent derivations are switch equivalent.
\end{remark}

\subsection{Church-Rosser: Sequential independence and switchability}\label{subsec:CR}

The fact that sequential independence implies switchability always
holds for linear rules (see \Cref{prop:equi}). The result is so
indispensable that typically, in the literature, it is not even
stated, in the sense that switchability is not introduced
axiomatically as in Definition~\ref{def:switch}, but it is based on
the explicit construction of a switch.

For left-linear rewriting systems
sequential independence does not imply switchability (while the
converse implication clearly holds), as shown by the next example.

\begin{figure}
  \begin{subfigure}{0.2\textwidth}
    {\small
      \xymatrix@C=16pt@R=1pt{
        & 0 \ar@{-}[dd] \ar@{-}[ddddddl] \ar@{-}[ddddddr] &  \\
        &  & \\
        & 1 \ar@{-}[dd] \ar@{-}[ddddl]  \ar@{-}[ddddr]   &  \\
        &  & \\
        & 2 \ar@{.}[d] \ar@{-}[ddl]   \ar@{-}[ddr]     &  \\
        &  \ar@{.}[dl]   \ar@{.}[dr] & \\
        b \ar@{-}[dr] & & c \ar@{-}[dl]\\
        & a 
      }
    }
    \caption{Poset $(P, \sqsubseteq)$}
    \label{fig:diff1:P}
  \end{subfigure}
  \begin{subfigure}{0.58\textwidth}
    \xymatrix@C=20pt{
      a \ar[d]_{\sqsubseteq} & a \ar[d]_{\sqsubseteq} \ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} & 
      0 \ar@{>->}@/^.35cm/[drrr]|(.3)\hole^(.75){\id{0}}
      \ar@{>->}[dr]|(.3)\hole_{\id{0}} &  &
      a \ar@/_.35cm/[dlll]_(.75){\sqsubseteq}
      \ar[dl]|(.3)\hole^{\sqsubseteq} & 
      a \ar[d]^{\sqsubseteq}\ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} &
      b \ar[d]_{\sqsubseteq}\\
      c &
      \ar@{>->}[l]^{\id{c}} c \ar[rr]_{\sqsubseteq}& &  0 &&
      \ar@{>->}[ll]^{\id{0}} 0 \ar@{>->}[r]_{\id{0}}& 0
    }
    \caption{Two rewriting steps}
    \label{fig:diff1:rew}
  \end{subfigure}
  \begin{subfigure}{0.20\textwidth}
    \xymatrix@C=20pt{a \ar[d]^{\sqsubseteq}& a
      \ar[d]^{\sqsubseteq}\ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} & b \\c & c
      \ar@{>->}[l]^{\id{c}}
    }
    \caption{No rewriting step}
    \label{ex:diff1:no-step}
  \end{subfigure}
  \caption{Sequential independence does not imply switchability}
  \label{fig:diff1} 
\end{figure}

\begin{example}
  \label{ex:diff1}
  Consider the poset $(P, \sqsubseteq)$ in Fig.~\ref{fig:diff1:P} where
  $P = \mathbb{N} \cup \{a,b,c\}$ and $\sqsubseteq$ is defined by
  $m \sqsubseteq n$ if $m \geq n$, $a \sqsubseteq x$ for all $x \in P$
  and $b, c \sqsubseteq n$ for all $n \in \mathbb{N}$.
  %
  Let $\X$ be the  
  category associated with this order, which by \Cref{rem:iso} is
  $\mathsf{I(\X)}$-adhesive. 
  %
  Consider a rewriting
  system whose set of rules contains the following 
  \[\xymatrix{a & a \ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & 0 & a & a
      \ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & b }\]
  We can then consider the  derivation
  $\der{D}=\{\dder{D}_i\}_{i=0}^1$ in Fig.~\ref{fig:diff1:rew}.
  % \[
  %   \xymatrix@C=30pt{a \ar[d]_{m_0}&& a \ar[d]_{k_0}\ar[ll]_{\id{a}}
  %     \ar[r]^{(a,0)} & 0 \ar@/^.35cm/[drrr]|(.315)\hole_(.45){\id{0}}
  %     \ar[dr]|(.3)\hole_{\id{0}} && a \ar@/_.35cm/[dlll]^(.45){(a,c)}
  %     \ar[dl]|(.3)\hole^{(a,0)}& a \ar[d]^{(a,0)}\ar@{>->}[l]_{\id{a}}
  %     \ar[rr]^{(a,b)} && b \ar[d]^{(b,0)}\\c &&
  %     \ar@{>->}[ll]^{\id{c}} c \ar[rr]_{(c,0)}&& 0 &&
  %     \ar@{>->}[ll]^{\id{0}} 0 \ar[rr]_{\id{0}}&& 0}\]
  %
  Note that the two direct derivations are sequential
  independent. However there is no switch since the rule applied by
  $\dder{D}_1$ cannot be applied to $c$. In fact, there is a unique morphism
  $a\to c$, yielding the diagram in Fig.~\ref{ex:diff1:no-step}. But $b$ and $c$
  do not have a supremum in the poset underlying $\X$, thus the arrows
  $a\to b$ and $a\to c$ do not have a
  pushout. Hence we do not get a direct derivation from $c$.
\end{example}

The conditions guaranteeing switchability are inspired
by the notion of \emph{canonical filler}
\cite{heindel2009category}.

\begin{definition}[Strong independence pair]
  \label{def:filler}
  Let $\X$ be an $\mathcal{M}$-adhesive category 
  and $(\X, \R)$ a left-linear rewriting system. 
  Let also $(i_0, i_1)$ be an independence pair between two direct
  derivations $\dder{D}_0$, $\dder{D}_1$
  as in the solid part of the diagram below
  \[
    \xymatrix@C=18pt@R=17pt{L_0 \ar[d]_{m_0}&& K_0
      \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} \ar@{.>}@/^.20cm/[ddrr]|(.32)\hole|(.57)\hole_(.7){u_0} & R_0
      \ar@/^.35cm/[drrr]|(.3)\hole^(.2){i_0} \ar[dr]|(.3)\hole_{h_0}
      && L_1 \ar@/_.35cm/[dlll]_(.2){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
      \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} \ar@{.>}@/_.20cm/[ddll]|(.32)\hole|(.57)\hole^(.7){u_1} && R_1 \ar[d]^{h_1} \\
      %
      G_0 &&
      \ar@{>->}[ll]^{f_0} D_0 \ar[rr]_(.3){g_0}&& G_1 &&
      \ar@{>->}[ll]^(.3){f_1} D_1 \ar[rr]_{g_1}&& G_2\\
      %
      & & & & P \ar@/^.3cm/@{>.>}[ull]^{p_0} \ar@/_.3cm/@{.>}[urr]_{p_1}
    }
  \]

  Consider the pullback of $g_0$ and $f_1$, which yields $p_i : P \to D_i$
  for $i \in \{0,1\}$ and the mediating arrows $u_i\colon K_i\to P$ 
  for $i \in \{0,1\}$ 
  into the pullback object (see \Cref{prop:tec} for details). 
  We say that $(i_0, i_1)$ is a \emph{strong independence pair} if
  the first two squares depicted  
  below are pushouts and if the pushout of $r_1 : K_1 \to R_1$ and $u_1 : K_1 \to P$ exists
  \[
    \xymatrix@R=16pt{
      K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
      \ar@{>->}[r]^{l_1} \ar[d]_{u_1}& L_1 \ar[d]^{i_1}
       &K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1\ar@{.>}[d]^{j_0}
      \\
      P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0
       & P \ar@{.>}[r]_{q_1} & Q_1
    }
  \]
\end{definition}

We can now prove a Local Church-Rosser Theorem for strong independence pairs.

\begin{restatable}[Local Church-Rosser Theorem]{proposition}{prChurch}
  \label{pr:church}
  Let $(i_0, i_1)$ be a strong independence pair
  between $\dder{D}_0$ and $\dder{D}_1$. Then $\dder{D}_0$ and
  $\dder{D}_1$ are switchable.
\end{restatable}

The correspondence between sequential independence and switchability
is fundamental. We name the class of rewriting systems where this property holds.

\begin{definition}[Strong enforcing rewriting systems]
  A left-linear rewriting system is \emph{strong enforcing} if
  every independence pair between two direct derivations is strong.
\end{definition}

We can identify a large class of adhesive categories such that all
left-linear rewriting systems over such categories are strong
enforcing. This class includes $\cat{Set}$ and it is closed
under comma and functor category constructions.  As such, it includes
essentially all categories (e.g., presheaves over set) that are
typically considered for modelling purposes. Notably, it contains the
category $\cat{Graph}$ of directed graphs.
This is a natural generalisation from adhesive to $\mathcal{M}$-adhesive categories of a class studied in \cite{baldan2011adhesivity} (see \Cref{app:fill} for details).

Still, there are $\mathcal{M}$-adhesive rewriting systems that are not strong enforcing.

\begin{example}[Non-strong enforcing left-linear rewriting system]
  \label{ex:diff2}
  In light of \Cref{pr:church}, \Cref{ex:diff1} provides an example of
  an independence pair that is not strong. This gives an example of a
  left-linear rewriting system in a $\mathcal{M}$-adhesive category that is quite
  pathological since $\mathcal{M}=\mathsf{I(\X)}$. However, this is expected, 
  since all natural examples seem to belong to the well-behaved class mentioned above. 
\end{example}

\begin{remark}
  By \Cref{pr:church} the existence of a strong independence pair
  entails switchability, which in turn entails sequential
  independence by construction. Strong enforcing rewriting systems are exactly
  those rewriting systems in which these three notions coincide.
\end{remark}

Consistency with the theory of linear rewriting systems is ensured by the fact that all linear rewriting systems are strong enforcing (see \cref{prop:equi}).

\subsection{Well-switching rewriting systems}
\label{subsec:verytame}

Even if we work in strong enforcing rewriting systems where sequential
independence ensures switchability, when dealing with left-linear
rules there is a further, possibly more serious issue, 
namely that there can be more than one independence pair between
the same derivations (cfr. \Cref{rem:uni}). This hinders the very idea of using
sequential independence as a basis of a theory of concurrency for
rewriting systems, since exchanges performed using different
independence pairs may lead to derivations that are not abstraction
equivalent, thus equating computations that should
definitively be taken apart, as shown in the example below.

\begin{example}
  Consider the derivation $\der{E}$ from Example~\ref{ex:seq-ind} (see Fig.~\ref{fi:derE}).
   The last two steps are sequential independent, but one easily sees
  that there are two distinct independence pairs, as the left-hand side
  of $\rho_1$ can be mapped either to node $1$ or to node
  $2$ in $D_1'$. Correspondingly, there
  are two switches of $\der{E}$: one is the derivation $\der{D}$ in
  Fig.~\ref{fi:derD} we started from, the other is the derivation
  $\der{D}'$ in Fig.~\ref{fi:derD1}.

  \begin{figure}
    \input{Figure/derD1.tex}
    \caption{The derivation $\der{D}'$.}
    \label{fi:derD1}
  \end{figure}

  As a consequence, $\der{D}$ and $\der{D}'$ would be switch
  equivalent, but this is not acceptable when viewing equivalence
  classes of derivations as concurrent computations: in $\der{D}$ the
  first two steps are not sequential independent, while in $\der{D}'$
  they are, intuitively because in $\der{D}$ rule $\rho_1$ uses the
  node generated by $\rho_0$ (adding a self-loop to it), while in
  $\der{D}'$ rule $\rho_1$ uses the node that was in the initial
  graph. Also observe that the graphs $G_2$ and $G_2'$ produced after
  two steps in $\der{D}$ and $\der{D'}$ are not isomorphic. From the
  technical point of view, the property of being switch equivalent is
  not closed by prefix, and this prevents deriving a sensible
  concurrent semantics: In fact
  $\der{D} = \dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ and
  $\der{D}' = \dder{D}_0'\cdot \dder{D}_1' \cdot \dder{D}_2'$ are
  switch equivalent, while if we consider the first two steps,
  derivations $\dder{D}_0 \cdot \dder{D}_1$ and
  $\dder{D}_0' \cdot \dder{D}_1'$ are not switch equivalent.
\end{example}

\full{Moreover, limiting sequential independence to the case in which the independence
pair is unique (as suggested in~\cite{baldan2017domains}) brings to the same problems.}

For these reasons we believe a theory of rewriting for
left-linear rules in adhesive categories should be developed for
systems where the uniqueness of the independence pair is ensured.

\begin{definition}[Well-switching rewriting systems]
A left-linear rewriting system $(\X, \R)$ is \emph{well-switching} if it is strong enforcing and, for every derivation $\der{D}:=\{\dder{D}_{i}\}_{i=0}^1$, there is at most one independence pair between $\dder{D}_0$ and $\dder{D}_1$.
\end{definition}

Clearly, linear rewriting systems are well-switching (see Proposition~\ref{pr:weak}).
Moreover, we next observe that various classes of rewriting systems,
comprising all the ones used in modelling the applications to the
encoding of process calculi or of bio and chemical systems mentioned
in the introduction, are actually well-switching.

A first class consists of those rewriting systems over
possibly hierarchical graphical structures obtained as algebras of
suitable signatures where rules are constrained not to merge elements
of top level sorts in the hierarchy (for graphs, nodes can be
merged while edges cannot). The idea here is to consider graph
structures as presheaves on categories in which there are objects that play 
the role of \emph{roots}, i.e.~objects that are not the codomain of 
any arrow besides the identity.

\begin{definition}[Root-preserving graphical rewriting systems]
	Let $\X$ be a category, an object $X\in \X$ is a \emph{root} if the only arrow with codomain $X$ is $\id{X}$.
	The category $\gph{X}$ of \emph{$\X$-graphs} is the category
	$\Set^{\X}$. A
	\emph{root-preserving graphical rewriting system} is a left-linear
	rewriting system $(\gph{X}, \R)$ such that for each rule
	$(l\colon K\to L, r\colon K\to R)$ in $\R$ it holds
	\begin{enumerate}
		\item for every $X\in \X$ and $x\in L(X)$, there exists a root $Y$
		 and an arrow $f\colon Y\to X$ such that $x$ belongs to the image of
		$L(f)\colon L(Y)\to L(X)$;
		\item $r\colon K\to R$ is mono on the roots, i.e.~for every root $X\in \X$ the component $r_X:K(X)\to R(X)$ is injective.
	\end{enumerate}
\end{definition}

For instance, the category $\cat{Graph}$ can be obtained
by taking as $\X$ the category generated by $E \rightrightarrows V$. In this case $E$ is the only root, hence, condition $1$ asks that in the left-hand side of each rule
there are no isolated nodes, while condition $2$ asks that the
morphism $r: K \to R$ is injective on edges, i.e.~it can only merge nodes.

\begin{restatable}{lemma}{lemVTame}
\label{bono}
  All root-preserving graphical rewriting systems are well-switching.
\end{restatable}

Another interesting class of well-switching rewriting systems is given by e-graphs.

\begin{example}[E-graphs]
  Consider the category $\cat{EGraphs}$, where objects are (directed)
  graphs endowed with an equivalence over nodes, and arrows are graph
  morphisms that preserve the equivalence, as considered
  in~\cite{BaldanGM06}, closely related to e-graphs~\cite{WNW:egg}. 
  Formally, $\cat{EGraphs}$ can be seen as the
  subcategory of the presheaf
  $[E \rightrightarrows V \to Q, \cat{Set}]$ where objects are
  constrained to have the component $V \to Q$ surjective.

  Explicitly, an
  e-graph $G$ is a triple $\langle s_G, t_G, q_G \rangle$ where
  $s_G, t_G: E_G \rightrightarrows V_G$ provides the graphical
  structure, while the surjective function $q_G : V_G \to Q_G$ maps
  each node to the corresponding equivalence class. 
  Notice that the inclusion functor into  $[E \rightrightarrows V \to Q, \cat{Set}]$ 
  creates pullbacks and pushouts \cite{mac2013categories}, so that they are computed component-wise.

  A morphism in $\cat{EGraph}$ is mono if the components over $E$
  and $V$ are mono, i.e.~if it is mono as a morphism in
  $\cat{Graph}$. It is regular mono if also the component on
  $Q$ is mono, i.e.~if it reflects equivalence classes besides
  preserving them. This characterisation of regular monos and the fact that pullbacks and pushouts are computed component-wise allows us to prove quasi-adhesivity of $\cat{EGraphs}$ at once. Moreover, one can deduce that every rewriting system $(\X, \R)$ that is left-linear with respect to $\reg(\cat{EGraphs})$ is strong enforcing: this is done exploiting again the inclusion functor into $[E \rightrightarrows V \to Q, \cat{Set}]$.

Left-linear rewriting systems with respect to $\reg(\cat{EGraphs})$ are well-switching. They have been used in~\cite{BaldanGM06} for the graphical implementation of nominal calculi, where,
differently from~\cite{Gad07}, as a result of name passing the received name is not merged with a local one, but put in the same equivalence class, better tracing the causal dependencies among reductions.
\end{example}

\subsection{A canonical form for  switch equivalences}
\label{subsec:canonical}

As discussed in the introduction, in the linear case a number of
basic properties of switch equivalence, i.e.~the globality of
independence, the consistency of switching, and the existence of a
canonical form for equivalence proofs, can be derived from a
characterisation of switch equivalence in terms of consistent
permutations or processes.

When dealing with left-linear rules, such a characterisation
fails. Leaving aside the formal details (the interested reader can
refer to \Cref{def:permcon}), the intuition is quite simple. In the
linear case one proves that two derivations using the same rules in
different orders are switch equivalent when the colimits of the two
derivations, seen as diagrams, are isomorphic and the isomorphism
properly commutes with the embeddings of the rules. When considering
left-linear derivations, this is no longer true. Intuitively this is
due to the fact that a rewriting step can merge parts of an
object thus making the colimit little informative.
This effect can be seen for derivations $\der{D}$ in
Fig.~\ref{fi:derD} and $\der{D}'$ in Fig.~\ref{fi:derD1}. They are not
abstraction equivalent but the colimit of both derivations is a single node with two self-loops, in a way that  all commutativity requirements are
trivially satisfied.

In this section we show that, despite the failure of such
characterisation, actually much of the theory can be retained, taking
a different and sensibly more complex route for the proofs: globality
of independence holds in a weak form, conceptually linked to the fact
that fusions introduce a form of disjunctive causality, while
consistency of switching holds unchanged. Finally, a canonical form
for switching sequences can also be recovered.

We start by proving two lemmas dealing with derivations of length
$3$. Despite being technical, these lemmas are fundamental building blocks for obtaining our results.

\smallskip

\noindent
\begin{minipage}{.8\textwidth}
  \setlength\parindent{1.5em}
  The first lemma is at the core of globality for independence. It shows that if we have a derivation consisting of three rewriting steps, say $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ where $\dder{D}_0$ and $\dder{D}_1$ are independent, then if we switch $\dder{D}_2$ to the first position, 
obtaining a derivation $\dder{D}_2'' \cdot  \dder{D}_0'\cdot\dder{D}_1'$, as in the diagram on the right where vertical lines represent permutations, the steps $\dder{D}_0'$ and $\dder{D}_1'$ are still independent.
\end{minipage}
\begin{minipage}{.18\textwidth}
\ \hspace{-14mm}
\begin{tikzpicture}[node/.style={draw, minimum size=8mm}]
  \begin{tikzcd}[row sep=2mm, column sep=1mm]
    \dder{D}_0 \arrow[perm,d]  & \dder{D}_1 \arrow[perm,dr] & \dder{D}_2 \arrow[perm,dl]\\
    \dder{D}_0 \arrow[perm,dr]  & \dder{D}_2' \arrow[perm,dl] & \dder{D}_1' \arrow[perm,d]\\
    \dder{D}_2''   & \dder{D}_0' & \dder{D}_1'
  \end{tikzcd}
\end{tikzpicture}
\end{minipage}

\smallskip

\noindent
\begin{minipage}{.8\textwidth}
  If instead $\dder{D}_1$ and $\dder{D}_2$ are
independent in $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ and we switch $\dder{D}_0$ to the last position, obtaining a
derivation $\dder{D}_1'\cdot \dder{D}_2'\cdot  \dder{D}_0''$, as in the diagram on the right, the steps $\dder{D}_1'$ and $\dder{D}_2'$ could be no
longer independent. %unless an additional condition is satisfied. 
Intuitively, this is due to the fact that dealing with
left-linear rewriting systems introduces disjunctive forms of
causality. Hence, if in $\dder{D}_0\cdot \dder{D}_1\cdot \dder{D}_2$ we have that $\dder{D}_0$ and $\dder{D}_1$ are
disjunctive causes of $\dder{D}_2$, at least one of the two is needed to
enable the application of $\dder{D}_2$ and this explain why in
$\dder{D}_1'\cdot \dder{D}_2'\cdot \dder{D}_0''$ we have that $\dder{D}_1'$ and $\dder{D}_2'$ are no longer
independent. This is exemplified below.
\end{minipage}
\begin{minipage}{.18\textwidth}
\ \hspace{-14mm}
\begin{tikzpicture}[node/.style={draw, minimum size=8mm}]
     \begin{tikzcd}[row sep=2mm, column sep=1mm]
      \dder{D}_0 \arrow[perm,dr]  & \dder{D}_1 \arrow[perm,dl] & \dder{D}_2 \arrow[perm,d]\\
      \dder{D}_1' \arrow[perm,d]  & \dder{D}_0' \arrow[perm,dr] & \dder{D}_2 \arrow[perm,dl]\\
      \dder{D}_1'   & \dder{D}_2' & \dder{D}_0''
    \end{tikzcd}
  \end{tikzpicture} 
\end{minipage}

\begin{example}
  \label{ex:non-global}
  Consider the rewriting system in $\cat{Graph}$ consisting of the
  rules $\lambda_0$, $\lambda_1$, and $\lambda_2$ in
  Fig.~\ref{fi:rules-cas}. Consider the derivation $\der{F}$ in Fig.~\ref{fi:derF}. Note that rule
  $\lambda_2$ needs the black self-loop on node $12$ to be applied. This can be
  generated either by $\lambda_0$ or by $\lambda_1$ merging nodes $1$ and
  $2$, hence at least one of them must precede the application of
  $\lambda_2$. Indeed, in $\der{F}$ it is easily seen that the second
  and the third step applying $\lambda_1$ and $\lambda_2$ are
  independent. However, we could switch twice the application of
  $\lambda_0$, bringing it in the last position, obtaining a derivation
  $\der{F}'$ as depicted in Fig.~\ref{fi:derF1}, where the
  applications of $\lambda_1$ and $\lambda_2$ are no longer independent.
   %
  \begin{figure}[t]
    \input{Figure/rules-cas.tex}    
    \caption{A new rewriting system in $\cat{Graph}$.}
    \label{fi:rules-cas}
  \end{figure}
%
  \begin{figure}[t]
    \input{Figure/derF.tex}    
    \caption{The derivation $\der{F}$.} 
    \label{fi:derF}
  \end{figure}
%
  \begin{figure}[t]
    \input{Figure/derF1.tex}    
    \caption{The derivation $\der{F}'$.} 
    \label{fi:derF1}
  \end{figure}
\end{example}
%
\begin{restatable}[Globality of independence]{lemma}{lemIndepGlobalLeft}
  \label{lem:indep-global-left}
  Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X,\R)$ a
  well-switching rewriting system.  Let
  $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ be a three-steps
  derivation.
  \begin{enumerate}
  \item
    \label{lem:indep-global-left:1}
    If $\dder{D}_0$ and $\dder{D}_1$ are switchable and there is a
    switching sequence
    $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(1,2)}
    \dder{D}_0 \cdot \dder{D}_2' \cdot \dder{D}_1' \shift{(0,1)}
    \dder{D}_2'' \cdot \dder{D}_0' \cdot \dder{D}_1'$ then
    in the last derivation $\dder{D}_0'$ and $\dder{D}_1'$ are switchable;

  \item
    \label{lem:indep-global-left:2}
    Suppose that $\dder{D}_1$ and $\dder{D}_2$ are switchable, hence $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(1,2)}
    \dder{D}_0 \cdot \dder{D}_2' \cdot \dder{D}_1'$ and $\dder{D}_0$ and $\dder{D}_2'$ are switchable.  If there
    is a switching sequence
    $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(0,1)}
    \dder{D}_1' \cdot \dder{D}_0' \cdot \dder{D}_2 \shift{(1,2)}
    \dder{D}_1' \cdot \dder{D}_2' \cdot \dder{D}_0''$ then in the last derivation $\dder{D}_1'$ and $\dder{D}_2'$ are switchable.
  \end{enumerate}
\end{restatable}

The second lemma captures the essence of the consistency of
switchings. If in a derivation of three
rewriting steps, say $\dder{D}_0\cdot \dder{D}_1\cdot  \dder{D}_2$, we invert them leading to a
sequence reordered as $\dder{D}_2\cdot  \dder{D}_1\cdot  \dder{D}_0$, we obtain the same derivation,
independently from the order of switchings.

\begin{restatable}[Consistency of switchings]{lemma}{lemSwitchConfluence}
	\label{lem:switch-confluence}
	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X,\R)$ a well-switching rewriting system.
	% 
	Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$ and suppose that we have the following two switching sequences
	\[\der{D} \shift{(0,1)} \der{D}' \shift{(1,2)} \der{D}'' \shift{(0,1)}\der{D}'''\\
          \qquad \der{D}\shift{(1,2)}\der{E}'\shift{(0,1)} \der{E}'' \shift{(1,2)}\der{E}''' \]
Then $\der{D}'''$ and $\der{E}'''$ are abstraction equivalent. 
\end{restatable}

The lemmas above open the way to the key result of this section, which establishes a canonical form for
switching derivations.

The first result shows that when equating two derivation sequences by performing a series of switchings, we can limit ourselves to switchings that invert the order of steps that in the target derivation has to be reversed, i.e.~we can limit ourselves to applying inversions.

\begin{restatable}[No need of useless switches]{theorem}{thNoNeed}
  \label{th:no-need}
  Let $\der{D}$ and $\der{D}'$ be derivation sequences. If $\der{D} \shifteq \der{D}'$ then there is a switching sequence 
  %\begin{center}
    $\der{D} \equiv_a \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
    \shift{\nu_n} \der{D}_n \equiv_a \der{D}'$
  %\end{center}
  consisting only of inversions.
\end{restatable}

\full{[Proof~\ref{thNoNeed-proof}]}

While inversions can be
performed in any order in the case of linear rewriting systems, this is no longer true for left-linear
rewriting systems due to the fact that, as already observed, globality of independence holds in a weak form. 
For instance, if we get back to Example~\ref{ex:non-global} and consider derivation $\der{F}$ in Fig.~\ref{fi:derF}, 
the last two steps applying rules $\lambda_1$ and $\lambda_2$ can be switched, thus leading to a derivation, 
call it $\der{F}''$,  applying $\lambda_0, \lambda_2, \lambda_1$. This $\der{F}''$ is switch equivalent to $\der{F}'$ in Fig.~\ref{fi:derF1}, 
hence starting from $\der{F}''$ we can obtain $\der{F}'$ via a switching sequence, but we cannot start 
by switching $\lambda_0$ and $\lambda_2$, even if this is an inversion.

\newpage
Still, we can identify a
canonical form for switching derivations: at each step one can apply a switch to the inversion with largest index.

\begin{restatable}[Canonical form]{corollary}{coCanonical}
  \label{co:canonical}
  Let $\der{D}$ and $\der{D}'$ be derivation sequences. If
  $\der{D} \shifteq[\sigma]\der{D}'$ then there is a switching sequence
  \begin{center}
    $\der{D} \equiv_a \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
    \shift{\nu_n} \der{D}_n \equiv_a\der{D}'$
  \end{center}
  where for $i \in \interval{n}$ we have $\nu_i  = \transp{k}$ with 
  $k = \max \{ j \mid \transp{j} \in \inv{\nu_{i,n}}\}$.
\end{restatable}

\section{Conclusions and further work}
\label{conclusions}

We performed an in-depth investigation of the notion of independence between
rewriting steps in the setting of left-linear rewriting systems
over $\mathcal{M}$-adhesive categories, which encompasses most of the
structures commonly used in analysing and modelling applications.

We showed that the canonical notion of independence adopted for linear
systems does not enjoy some properties that are essential for
developing a sensible theory of concurrency, notably a Church-Rosser
theorem, and we identified a subclass of left-linear rewriting systems,
which we call well-switching, as an appropriate setting where 
many key results can be re-established. Specifically, a Church-Rosser 
theorem, i.e.~the possibility of performing independent steps in any order, is
fully recovered. Moreover, the switch construction and correspondingly
the switch equivalence, at the core of a theory of concurrency for
rewriting systems, enjoy a number of fundamental properties: a weak form of globality of independence, 
consistency of switching and
the existence of a canonical form for switch equivalence proofs.

The class of well-switching $\mathcal{M}$-adhesive rewriting systems is large. Generalising a result in~\cite{baldan2011adhesivity},
we showed that one of its defining properties (the fact that sequential independence implies switchability) holds 
for a general class of $\mathcal{M}$-adhesive categories that include all presheaves over $\cat{Set}$. Moreover, the second property, uniqueness 
of switching, is ensured when rewriting possibly hierarchical graphical structures, as long as elements belonging to the sorts 
of the roots  are not merged (e.g., one can consider rewriting systems over directed graphs where only nodes are merged, as it 
happens in most of the approaches to the modelling of calculi and biological systems that we cited in the introduction, 
as well as in string diagrams).

In the DPO approach to rewriting, the notion of sequential
independence, identifying consecutive rewriting steps that %are independent and thus
can be performed in reverse order is typically
closely linked to that of \emph{parallel
	independence}~\cite{ehrig2014adhesive}. Parallel independence
relates two rewriting steps starting from
the same object, which can be applied in
any order producing, up to isomorphism, the same resulting
object. Parallel independent steps, when applied in sequence, lead to
sequential independent steps and, conversely, from two sequential
independent steps, as a byproduct of the switch construction, one can
get two parallel independent steps.

Under mild additional conditions, one can have a notion of \emph{parallel rule} in a way that two
parallel independent steps can be also combined in a single rewriting step.
Even if this is not discussed explicitly in the paper, our theory can be easily accommodated to encompass a notion of parallel independence and parallel rule application, enjoying the properties outlined above. To ensure this, however, one must require that the underlying category $\X$ has binary coproducts and that the class $\mathcal{M}$ is closed under them.

The results in this paper open the way to the development of a
concurrent semantics for left-linear rewriting systems over $\mathcal{M}$-adhesive
categories. In~\cite{baldan2017domains} the authors argue that for
computational systems that allow one to express merging or fusions,
the right semantical models are weak prime domains, a generalisation
of prime domains, a staple in concurrency theory, and connected event
structures, their event-based counterpart. The mentioned paper
discusses only the case of graph rewriting and does not focus into the
problems induced by the occurring of ``merges'' to the theory of rewriting (the systems
considered there are implicitly assumed to be well-switching). 
We plan to consolidate the statement that weak prime domains are 
``the'' model for systems with fusions by showing that they allow to provide a semantics
for left-linear rewriting systems in $\mathcal{M}$-adhesive categories.

On the practical side, the present paper just surveyed the possibility
of modelling e-graphs. This appears to be quite interesting as
concurrent rewriting on such structures is an active area of
research~\cite{abs-2208-06295}.
We plan to make the correspondence precise
and investigate how the analysis techniques enabled by a concurrent
semantics of rewriting can impact on e-graphs.

\bibstyle{plainurl}
\bibliography{bibliog.bib}

\appendix
\section{Properties of $\mathcal{M}$-adhesive categories}\label{app:ade}

This first appendix is devoted to the proofs of a few well-known results about $\mathcal{M}$-adhesive categories.
%
Observe that our notion of $\mathcal{M}$-adhesivity follows
\cite{ehrig2012,ehrig2014adhesive} and is different from the one of
\cite{azzi2019essence}. What is called $\mathcal{M}$-adhesivity in
the latter paper corresponds to our strict
$\mathcal{M}$-adhesivity. Moreover, in \cite{azzi2019essence} the
class $\mathcal{M}$ is assumed to be only stable under
pullbacks. However, if $\mathcal{M}$ contains all split monos, then
stability under pushouts can be deduced from the other
axioms~\cite[Prop.~$5.1.21$]{castelnovo2023thesis}.

\subsection{Some results on $\mathcal{A}$-stable and $\mathcal{A}$-Van Kampen squares}
We start proving some general results regarding $\mathcal{A}$-Van Kampen and $\mathcal{A}$-stable squares. Let us begin recalling some classical results about  about pullbacks and pushouts\cite{mac2013categories}.

\noindent 
\parbox{10.5cm}{\begin{lemma}\label{lem:popb1} \label{lem:pb1} \label{lem:po1}
Let $\X$ be a category, and consider the diagram  on the right, then the following hold
	\begin{enumerate}
		\item if the right square is a pullback, then the whole rectangle is a pullback if and only if the left square is one;
		\item if the left square is a pushout, 	then the whole rectangle is a pushout if and only if the right square is one.
	\end{enumerate}
\end{lemma}}
\parbox{4cm}{$\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}$}\\

The following proposition establishes a key property of $\mathcal{A}$-Van Kampen squares with a mono as a side: they are not only pushouts, but also pullbacks \cite{ehrig2004adhesive,BehrHK23,lack2005adhesive}.

\noindent 
\parbox{11.5cm}{\begin{proposition}\label{prop:pbpo} Let $\mathcal{A}$ be a class of arrows stable under pushouts and containing all the isomorphisms.  If the square to the right is $\mathcal{A}$-Van Kampen and $m\colon A\to C$ is mono and belongs to $\mathcal{A}$, then the square is a pullback and $n$ is a monomorphism.
\end{proposition}}
\parbox{2cm}{\vspace{1.5ex}$\xymatrix{A\ar[r]^{g} \ar[d]_{m} & B \ar[d]^{n} \\ C \ar[r]_{f}  & D}$}

The previous proposition allows us to establish the following result.

\noindent \parbox{7.4cm}{
\begin{lemma}\label{lem:varie}Let $\mathcal{A}$ be a class of arrows stable under pullbacks, pushouts and containing all isomorphisms.  Suppose that the left square aside is $\mathcal{A}$-Van Kampen, while the vertical faces in the right cube are pullbacks. 	Suppose moreover that $m\colon A\to C$ and $d\colon D'\to D$ are mono and that $d$ belongs to $\mathcal{A}$. Then $d\leq n$ if and only if $c \leq m$.
\end{lemma}}
	\parbox{6cm}{$\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{g'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{g}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){f'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){g} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{f} &&D&&C \ar[rr]_{f} & & D}$}

\noindent 
\parbox{11cm}{\begin{remark}
	Recall that, given two monos $m:M\to X$ and $n:N\to X$ with the same codomain, $m\leq n$ means that there exists a, necessarily unique and necessarily mono, $k:M\to N$ fitting in the triangle aside.

	\hspace{15pt}Notice, moreover, that  if $m\leq n$ and $n\leq m$, then the arrow $k:M\to N$ is an isomorphism.
\end{remark}}
\parbox{4cm}{$\xymatrix@C=15pt{M\ar@{.>}[rr]^{k}  \ar[dr]_{m}&& N \ar[dl]^{n}\\ & X}$}\\

Finally, we show that $\mathcal{A}$-stable pushouts enjoy a \emph{pullback-pushout decomposition} property.

\noindent 
\parbox{10cm}{
\begin{proposition}\label{prop:stab}Let $\X$ be a category and $\mathcal{A}$ a class of arrows stable under pullbacks. Suppose that, in the diagram aside, the whole rectangle is an $\mathcal{A}$-stable pushout and the right square a pullback. If the arrow $k$ is in $\mathcal{A}$ and it is a monomorphism,  then both squares are pushouts.
\end{proposition}}
\parbox{4cm}{\vspace{-.3cm}
	$\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}$}

\subsection{Useful properties of $\mathcal{M}$-adhesive categories}

We are now going to apply the results of the previous section to $\mathcal{M}$-adhesive categories in order to establish some \emph{high-level replacement properties} \cite{ehrig2004adhesive,ehrig2014adhesive,ehrig2006fundamentals}.  
A first important  result that can be immediately established, with the aid of \Cref{prop:pbpo}, is the following one.

\begin{proposition}
	\label{prop:pbpoad}
	Let $\X$ be an $\mathcal{M}$-adhesive category. Then
	$\mathcal{M}$-pushouts are pullbacks.
\end{proposition}

From \Cref{prop:pbpoad}, in turn, we can derive the following corollaries.
\begin{corollary}\label{cor:rego}
	In a $\mathcal{M}$-adhesive category $\X$, every $m\in\mathcal{M}$ is a regular mono.
\end{corollary}

The following result now follows at once noticing that a regular monomorphism which is also epic is automatically an isomorphism.

\begin{corollary}\label{prop:bal}
	If $\X$ is an $\mathcal{M}$-adhesive categories, then every epimorphism in $\mathcal{M}$ is an isomorphism. In particular, every adhesive category $\X$ is \emph{balanced}: if a morphism is monic and epic, then it is an isomorphism.
\end{corollary}

\noindent 
\parbox{10cm}{\begin{lemma}[$\mathcal{M}$-pushout-pullback decomposition]\label{lem:popb} Let $\X$ be an $\mathcal{M}$-adhesive category  and suppose that, in the diagram aside, the whole rectangle is a pushout and the right square a pullback. Then the following statements hold
\parbox{13cm}	{\begin{enumerate}
		\item if $a$ belongs to $\mathcal{M}$ and $k$ is a mono,  then both squares are pushouts and pullbacks;
		\item if $f$ and $k $ are in  $\mathcal{M}$, then both squares are pushouts and pullbacks.
	\end{enumerate}}
\end{lemma}}
\parbox{4cm}{\vspace{-1cm}
	$\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}$}\\

Let us turn our attention to pushout complements.

\noindent
\parbox{11cm}{
	\begin{definition}[Pushout complement]
		Let $f\colon X\to Y$ and $g\colon Y\to Z$ be two composable arrows in a category $\X$. A \emph{pushout complement} for the pair $(f,g)$ is a pair $(h,k)$ with $h\colon X\to W$ and $k\colon W\to Z$ such that the square aside is a pushout.
	\end{definition}} \quad
\parbox{4cm}{\vspace{.1cm}
	$\xymatrix{X \ar[r]^{f} \ar[d]_{h}& Y \ar[d]^{g} \\ W \ar[r]_{k}& Z}$}\\

Working in an $\mathcal{M}$-adhesive category we can guarantee that pushout complements are unique.

\noindent
\parbox{8.5cm}{
	\begin{lemma}\label{lem:radj}
		Let $f\colon X \to Y$ be an arrow in an $\mathcal{M}$-adhesive category $\X$ and suppose that the left square aside is a pushout while the  right one is a pullback, with $ m\colon M \rightarrowtail X$ and $n\colon N \rightarrowtail Y$ in $\mathcal{M}$.
		Then $n\leq k$ if and only if $p_2\leq m$.
	\end{lemma}}
\parbox{3cm}{\vspace{-2ex}
	$\xymatrix{M \ar@{>->}[d]_{m}\ar[r]^{h}& Q \ar@{>->}[d]^{k} & P \ar[r]^{p_1} \ar@{>->}[d]_{p_2}& N \ar@{>->}[d]^{n}\\X\ar[r]_{f}&Y &X \ar[r]_f&Y}$}

\noindent
\parbox{10cm}{
	\begin{corollary}[Uniqueness of pushout complements]\label{lem:pocomp}
		Let $\X$ be a $\mathcal{M}$-adhesive category. Given $m\colon X\mto Y$ in $\mathcal{M}$ and $f\colon Y\to Z$, let $(h_1, k_1)$ and $(h_2, k_2)$ be pushout complements of $m$  and $f$ depicted aside. Then there exists a unique isomorphism $\phi\colon W_1\to W_2$ making the diagram on the right commutative.
	\end{corollary}}
\parbox{3cm}{\vspace{1em}$\xymatrix{&X \ar@{>->}[r]^{m} \ar[d]_{h_1} \ar@/_.3cm/[dl]_{h_2}& Y \ar[d]^{f} \\ W_2 \ar@{>->}@/_.4cm/[rr]_{k_2} &W_1 \ar@{.>}[l]_{\phi} \ar@{>->}[r]^{k_1} & Z }$}

\section{$\mathcal{M}$-adhesivity is not enough}\label{app:fill}
In \Cref{sec:equi} we introduced the notion of strong enforcing left-linear rewriting system, a class that contains all the linear rewriting systems. This result can be further refined: in \cite{baldan2011adhesivity} a class  $\mathbb{B}$ of (quasi-)adhesive category is defined for which the local Church-Rosser Theorem holds for left-linear rewriting system. In our language, this means that every left-linear rewriting system based on a category in $\mathbb{B}$ is strong enforcing. This section is devoted to repropose, and slightly generalise, the results of \cite{baldan2011adhesivity} to our context.

\noindent
\parbox{10.4cm}{
	\begin{definition}Let $\mathcal{M}$ be a class of monos in a category $\X$, closed under composition, containing all isomorphisms and stable under pullbacks and pushouts. Suppose that the  diagram aside is given and the whole rectangle is a pushout. We say that $\X$ satisfies
		\parbox{14cm}{\begin{itemize}
				\item the \emph{$\mathcal{M}$-mixed decomposition} property if, whenever $k$ belongs to $\mathcal{M}$ and the right half of the previous diagram is a pullback, then the left one is a pushout;
				\item the \emph{$\mathcal{M}$-pushout decomposition} property if whenever $a, b$ and $c$ belongs to $\mathcal{M}$ and the right half of the diagram above is a pushout, then its left half is a pushout too.
			\end{itemize}}
	\end{definition}} \parbox{3cm}{\vspace{-2cm}$\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}$}\\

The class of categories of type $\mathbb{B}$ is closed under the same constructions of \Cref{thm:slice-functors}. This can be deduced at once from the fact that in such categories pullbacks and pushouts are computed component-wise.

\begin{lemma}\label{lem:closed} Let $\X$ be a category satisfying the $\mathcal{M}$-mixed and $\mathcal{M}$-pushout decomposition properties, then the following hold
	\begin{enumerate}
		\item  for every object $X$, $\X/X$ satisfies  the $\mathcal{M}/X$-mixed and the $\mathcal{M}/X$-pushout decomposition properties, while $X/\mathcal{M}$-adhesive satisfies their $X/\mathcal{M}$ variants, where
		\[\mathcal{M}/X:=\{m\in \mathcal{A}(\X/X) \mid m\in \mathcal{M} \}
		\qquad X/\mathcal{M}:=\{m\in \mathcal{A}(X/\X) \mid m\in
		\mathcal{M} \}
		\]
		\item  for every small
		category $\Y$, the category $\X^\Y$ satisfies the 
		$\mathcal{M}^{\Y}$-mixed and the $\mathcal{M}^{\Y}$-pushout decomposition properties, where
		\[\mathcal{M}^{\Y}:=\{\eta \in \mathcal{A}(\X^\Y) \mid \eta_Y \in
		\mathcal{M} \text{ for every } Y\in \Y\}\]
	\end{enumerate}
\end{lemma}

The following result shows that the mixed and pushout decomposition properties guarantee that every independence pair is strong.

\begin{theorem}\label{thm:good1}Let $\X$ be an $\mathcal{M}$-adhesive category with all pushouts and satisfying the $\mathcal{M}$-mixed and the $\mathcal{M}$-pushout decomposition properties. Then every left-linear rewriting system on $\X$ is strong enforcing.
\end{theorem}
\begin{proof}
	Consider the derivation $\der{D}=\{\dder{D}_i\}_{i=0}^1$, made by two sequentially independent derivations, depicted below
	\[\xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0} && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{h_1} \\G_0 && \ar@{>->}[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar@{>->}[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2 }\]

	We have to show that $(i_0, i_1)$ is a strong independence pair. Now, by hypothesis $\X$ has all pushouts, thus the only thing to show is that the squares below are pushouts (the third one is the usual pullback of $f_1\colon D_1\mto G_0$ along $g_0\colon D_0\to G_1$)
	\[\xymatrix{K_0 \ar[r]^{r_0}  \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1 \ar@{>->}[r]^{l_1}  \ar[d]_{u_1}& L_1 \ar[d]^{i_1}&P \ar@{>->}[r]^{p_0} \ar[d]_{p_1}& D_0\ar[d]^{g_0} \\ P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0}  & D_0&D_1 \ar@{>->}[r]_{f_1} & G_1}\]

	To see this, consider the following two diagrams
	\[\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0} \ar[d]_{r_0} \ar[r]_{u_0}& \ar@{>->}[r]_{p_0} P \ar[d]_{p_1}& D_0 \ar[d]^{g_0}&K_1 \ar@/^.4cm/[rr]^{k_1} \ar@{>->}[d]_{l_1} \ar[r]_{u_1}& \ar[r]_{p_1} P \ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\ R_0 \ar@/_.4cm/[rr]_{h_0}  \ar[r]^{i_0}& D_1 \ar@{>->}[r]^{f_1}& G_1 &L_1 \ar@/_.4cm/[rr]_{m_1}  \ar[r]^{i_1}& D_0 \ar[r]^{g_0}& G_1}\]

	The thesis now follows from the $\mathcal{M}$-mixed and the $\mathcal{M}$-pushout decomposition property.
\end{proof}

Our next step is to identify sufficient conditions for a category $\X$ to satisfy the mixed and $\mathcal{M}$-pushout decomposition properties.

\begin{definition} 
	Let $\X$ be an  $\mathcal{M}$-adhesive category, the pair $(\X, \mathcal{M})$ is of \emph{type $\mathbb{B}$} if
	\begin{enumerate}
		\item every arrow in $\mathcal{M}$ is a coproduct coprojection;
		\item $\X$ has all pushouts;
		\item $\X$ has strict initial objects and, for every object $X$, the unique arrow $?_X\colon 0\to X $ belongs to $\mathcal{M}$;
		\item all pushouts are $\mathcal{M}$-stable.
	\end{enumerate}
\end{definition}

\begin{remark}
	It is worth to examine more closely conditions $1$ and $3$ of the above definition.
	\smallskip 
	\begin{itemize}
	\parbox{10.3cm}{\item Let $m_0\colon X_0 \rightarrowtail Y$ be an arrow in $\mathcal{M}$, the first condition means that there exists $m_1\colon X_1\to Y$ such that $(Y, \{m_i\}_{i=0}^1)$ is a coproduct. This, together with property $3$, entails that every coprojection in a coproduct is in $\mathcal{M}$. This follows since any coproduct $(X_1+X_2, \{\iota_{X_i}\}_{i=0}^1)$ fits in a pushout diagram as the one aside.}
	  \parbox{3cm}{\vspace{-0em}$\xymatrix@C=25pt{0  \ar@{>->}[r]^-{?_{X_1}} \ar@{>->}[d]^{?_{X_2}}& X_1 \ar@{>->}[d]^{\iota_{X_1}}\\ X_2 \ar@{>->}[r]_-{\iota_{X_2}} & X_1+X_2}$}

	\smallskip 	\noindent 
	\parbox{13.5cm}{\item $\X$ has strict initial objects if it has initial objects and every arrow $f:X\to 0$ is an isomorphism. Notice that if initial objects are strict, then $?_X\colon 0\to X$ is mono for every $X$: indeed for every pair $f,g\colon Y\rightrightarrows 0$ then, by strictness, $Y$ is initial and so $f=g$.}
	\end{itemize} 
\end{remark}

\begin{example}
The category $\Set$ of sets and functions, with its class of monos, is of type $\mathbb{B}$. Similarly, the category $\textbf{Inj}$ of sets and injective functions is quasiadhesive and, with its class of regular monos, of type $\mathbb{B}$. 
\end{example}

Categories of type $\mathbb{B}$ satisfy a property resembling \emph{extensivity} \cite{carboni1993introduction}.

\noindent
\parbox{10cm}{\begin{proposition}\label{prop:ext}
Let $(\X, \mathcal{M})$ be a pair of type $\mathbb{B}$. Then for every diagram as the one aside, in which the bottom row is a coproduct cocone and the vertical arrows are in $\mathcal{M}$, the top row is a coproduct if and only if the two squares are pullbacks.
\end{proposition}}
\parbox{2cm}{\vspace{-.4em}$\xymatrix{A\ar[r]^-{f} \ar@{>->}[d]_{r}& C  \ar@{>->}[d]_{s}& B \ar@{>->}[d]^{t}\ar[l]_-{g}\\X  \ar[r]_-{\iota_X}& X+Y & Y \ar[l]^-{\iota_Y}}$}

\noindent 
\parbox{4cm}{$\xymatrix@C=10pt@R=10pt{&I\ar@{>->}[dd]|\hole_(.65){a}\ar[rr]^{k} \ar[dl]_{h} && B \ar@{>->}[dd]^{t} \ar[dl]_{g} \\ A  \ar@{>->}[dd]_{r}\ar[rr]^(.7){f} & & C \ar@{>->}[dd]_(.3){s}\\&0\ar@{>->}[rr]|\hole^(.65){?_Y} \ar@{>->}[dl]^{?_X} && Y \ar@{>->}[dl]^{\iota_Y} \\X \ar@{>->}[rr]_{\iota_X} & & X+Y}$}
 \parbox{10cm}{\begin{proof}
Consider the cube aside, in which the back faces are pullbacks. The bottom faces is an $\mathcal{M}$-Van Kampen pushout, thus the top face is a pushout if and only if the front faces are pullbacks. By strictness of $0$, $a\colon I\to 0$ is an isomorphism, so that $I$ is initial, therefore the $\mathcal{M}$-Van Kampen condition reduces to the request that $(C, \{f,g\})$ is a coproduct cocone if and only if the front faces are pullbacks, as claimed.
\end{proof}}

The previous result entails the following one, needed to show that  in any pair $(\X, \mathcal{M})$ of type $\mathbb{B}$, the category $\X$ satisfies the $\mathcal{M}$-mixed and $\mathcal{M}$-pushout decomposition properties.

\noindent
\parbox{10.7cm}{\begin{proposition}\label{prop:po2}
		Let $(\X, \mathcal{M})$ be a pair of type $\mathbb{B}$, and suppose that the square aside is an $\mathcal{M}$-pullback. Then there exists $E\in \X$, $e\colon E\mto C$ in $\mathcal{M}$, $\phi:E\to B_1$ such that $(C, \{m, e\})$ is a coproduct and $g=f+\phi$. Moreover, such a square is a pushout if and only if $\phi$ is an isomorphism.
\end{proposition}} \parbox{3cm}{\vspace{-.2cm}$\xymatrix{A  \ar[r]^{f} \ar@{>->}[d]_{m}& B_0 \ar@{>->}[d]^{\iota_{B_{0}}}\\ C\ar[r]_-{g} & B_0+B_1}$}

\begin{lemma}\label{lem:prop} Let $(\X, \mathcal{M})$ be a pair of type $\mathbb{B}$, then $\X$ satisfies the $\mathcal{M}$-mixed and $\mathcal{M}$-pushout decomposition properties.
\end{lemma}
\begin{proof}$\mathcal{M}$-mixed decomposition property. This follows at once from \Cref{prop:stab}.

	\medskip \noindent
	\parbox{3cm}{$\xymatrix{X \ar[r]^f \ar@{>->}[d]_{\iota_X}& Y\ar[r]^g \ar@{>->}[d]^{\iota_Y} & Z\ar@{>->}[d]^{\iota_Z}\\X+A  \ar@/_.4cm/[rr]_{(g\circ f) + (\varphi \circ \phi)}\ar[r]^{f+\phi}& Y+B \ar[r]^{g+\varphi}& Z+C}$} \qquad \qquad  \qquad   \qquad \parbox{8cm}{ $\mathcal{M}$-pushout-decomposition property. Using \Cref{prop:ext,prop:po2} and the fact that arrows in $\mathcal{M}$ are coproduct coprojections, we can reduce to prove the property for diagrams as the one on the left. By hypothesis and \Cref{prop:po2}, $\varphi$ and $\varphi\circ \phi$ are both isomorphisms, therefore $\phi$ is an isomorphism too and we can conclude again using \Cref{prop:po2}.\qedhere 
}	
\end{proof}

\begin{definition} Let $\X$ be an $\mathcal{M}$-adhesive category, we say that the pair $(\X, \mathcal{M})$ is of \emph{type $\mathbb{B}^+$} if (at least) one of the following holds
	\begin{enumerate}
		\item $(\X, \mathcal{M})$ is of type $\mathbb{B}$;
	\item $\X$ is $\Y/Y$ and $\mathcal{M}=\mathcal{N}/Y$for some $(\Y, \mathcal{N})$ of type $\mathbb{B}^+$ and $Y\in \Y$;
 	\item $\X$ is $Y/\Y$ and $\mathcal{M}=Y/\mathcal{N}$for some $(\Y, \mathcal{N})$ of type $\mathbb{B}^+$ and $Y\in \Y$:
 	\item $\X$ is $\Y^{\A}$ and $\mathcal{M}=\mathcal{N}^{\A}$ for some category category $\A$ and $(\Y, \mathcal{N})$ of type $\mathbb{B}^+$.
	\end{enumerate}
\end{definition}
\begin{example}
  \label{ex:graph-type-bb}
	The pair $(\mathbf{Graph}, \mon(\mathbf{Graph}))$ made by the topos of graphs and its class of monos is of type $\mathbb{B}^+$  but not of type $\mathbb{B}$. Indeed, not every monomorphism of graphs is a coproduct coprojection.
\end{example}

From \Cref{lem:closed,lem:prop} we can now deduce at once the following.
\begin{corollary}
	For every $(\X, \mathcal{M})$ of type $\mathbb{B}^+$, the category $\X$ has the $\mathcal{M}$-mixed and $\mathcal{M}$-pushout decomposition properties.
\end{corollary}

Using \Cref{thm:good1} we finally get the main result of our appendix.
\begin{corollary}
  \label{cor:llr-is-strEnf}
Let $(\X, \mathcal{M})$ be a pair of type $\mathbb{B}^+$, then every left-linear rewriting system is strong enforcing.
\end{corollary}

\section{Omitted proofs}\label{omitted}
In this appendix we provide the proofs of the main results of this paper.

\subsection{Proofs for \Cref{sec:ade}}

\begin{proposition}
  \label{prop:unique}
  Let $\X$ be an $\mathcal{M}$-adhesive category. Suppose that the two
  direct derivations $\dder{D}$ and $\dder{D}'$ below, with the same
  match and applying the same left-linear rule $\rho$, are given
  \[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} &
      R \ar[d]^{h} & L \ar[d]_{m}& K \ar[d]^{k'}\ar@{>->}[l]_{l}
      \ar[r]^{r} & R \ar[d]^{h'}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}& H
      & G & \ar@{>->}[l]^{f'} D' \ar[r]_{g'}& H'}\]
  Then there is an abstraction equivalence between $\dder{D}$ and
  $\dder{D}'$, whose first component is $\id{G}$.
\end{proposition}
\begin{proof}
  Both pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$
  and $n$, thus, \Cref{lem:pocomp} yields an isomorphism
  $\phi_D\colon D\to D'$. An easy computation shows that $g'\circ \phi_D \circ k=h'\circ r$.
  \noindent
  \parbox{3cm}{
    $\xymatrix{K \ar@/^.4cm/[rr]^{k'}\ar[d]_{r} \ar[r]_{k}&
      \ar[r]_{\phi_D} D \ar[d]^{g}& D' \ar[d]^{g'}\\ R
      \ar@/_.4cm/[rr]_{h'} \ar[r]^{h}& H \ar[r]^{\phi_H}& H'}$}
  \hfill
  \parbox{10cm}{ \hspace{15pt}Hence, we have
    $\phi_H\colon H\to H'$. To see that $\phi_H$ is an isomorphism,
    consider the diagram aside. By hypothesis the whole rectangle and
    its left half are pushouts, therefore, by \Cref{lem:po1} its right
    square is a pushout too. The claim now follows from the fact that
    the pushout of an isomorphism is an isomorphism. \qedhere }
\end{proof}

\subsection{Proofs for \Cref{sec:equi}}
This section provides further details and proofs for the concepts introduced in \Cref{sec:equi}.

\subsubsection{Proofs for \Cref{subsec:switch}}
Consider a switch $\der{E}=\{\dder{E}_i\}_{i=0}^1$ for $\dder{D}_0$
and $\dder{D}_1$, then by definition $\dder{E}_0$ and $\dder{E}_1$ are
sequentially independent. We can then wonder if they are switchable.

\begin{proposition}
  \label{prop:switch}
  Let $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation and suppose
  that $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a switch for it. Then
  $\der{D}$ is a switch for $\dder{E}_0$ and $\dder{E}_1$ along
  $(i'_0, i'_1)$.
\end{proposition}

\begin{proof}
 Clearly $\der{D}$ uses the same rule of $\der{E}$ in reverse order. Moreover, since $\der{E}$ is a switch for $\der{D}$, we already know that
   \begin{center}   
 	$m_0=f_0' \circ i_1'$
 	\qquad $h_1=g_1' \circ i_0'$
 	\qquad $m_0'= f_0 \circ i_1$
 	\qquad $h_1'= g_{1}\circ i_0$.
 \end{center}
Since  these equations are those that must hold for $\der{D}$ to be a switch for $\der{E}$ along $(i_0', i_1')$ we can conclude.
\end{proof}

\begin{lemma}[Uniqueness of switches]
  \label{thm:switch_uni}
  Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation and suppose
  that both $\der{E}=\{\dder{E}_i\}_{i=0}^1$ and
  $\der{F}=\{\dder{F}_i\}_{i=0}^1$ are switches of $\dder{D}_0$ and
  $\dder{D}_1$. Then $\der{E}$ and $\der{F}$ are abstraction
  equivalent.
\end{lemma}

\begin{proof}
    By definition of switch $\der{E}_0$ and $\der{F}_0$ have the same match $f_0\circ i_1$ and that $\der{E}_1$ and $\der{F}_1$ have the same comatch $g_1\circ i_0$. Thus we get the solid part of the diagram below
    \[\xymatrix@C=22pt{G_{0} && \ar@{>->}[ll]_{f_{\der{F},0}} D_{\der{F},0} \ar[rr]^{g_{\der{F},0}}&& G_{\der{F},1} && \ar@{>->}[ll]_{f_{\der{F},1}} D_{\der{F},1} \ar[rr]^{g_{\der{F},1}}&& G_{2}\\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}&& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_{1} \ar@/^.35cm/[drrr]|(.3)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{h_{\der{E},0}} \ar@/_.35cm/[urrr]|(.3)\hole^(.4){a_0} \ar[ur]|(.3)\hole^{h_{\der{F},0}}& &L_{0} \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{m_{\der{E},1}} \ar@/^.35cm/[ulll]_(.4){a_1} \ar[ul]|(.3)\hole_{m_{\der{F},1}}& K_{0} \ar[d]_{k_{\der{E},1}} \ar[u]^{k_{\der{F},1}}\ar@{>->}[l]_{l_{0}} \ar[rr]^{r_0} && R_{0} \ar[d]_{g_1\circ i_0} \ar[u]^{g_1\circ i_0}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} && \ar[ll]^{f_{\der{E},0}} D_{\der{E},0} \ar@{.>}@/^.5cm/[uu]^(.33){\phi_{0}}|\hole \ar[rr]_{g_{\der{E},0}}&& G_{\der{E},1} \ar@{.>}[uu]^(.76){\psi_1}|(.45)\hole |(.55)\hole&& \ar@{>->}[ll]^{f_{\der{E},1}} D_{\der{E},1} \ar@{.>}@/_.5cm/[uu]_(.33){\phi_{1}}|\hole\ar[rr]_{g_{\der{E},1}}&& G_{2}\ar@{.>}@/_.5cm/[uu]_{\psi_2}}\]

    \parbox{7cm}{\hspace{15pt}Now, by \Cref{prop:unique} we get $\phi_0\colon D_{\der{E},0}\to D_{\der{F},0}$ and $\psi_1 \colon G_{\der{E},1}\to G_{\der{F},1}$ such that the diagram aside commutes. But then we have
    	\[
    	f_{\der{F},0}\circ \phi_0\circ j_1=f_{\der{E},0} \circ j_1=m_0=f_{\der{F},0}\circ a_1\]
    	which entails $a_1= \phi_0\circ j_1$.}
\parbox{4cm} {$\xymatrix{G_{0} & \ar@{>->}[l]_{f_{\der{F},0}} D_{\der{F},0} \ar[r]^{g_{\der{F},0}}& G_{\der{F},1} \\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar[l]_{l_1} \ar[r]^{r_1} & R_{1}  \ar[d]_{h_{\der{E},0}}  \ar[u]^{h_{\der{F},0}}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} & \ar@{>->}[l]^{f_{\der{E},0}} D_{\der{E},0} \ar@/^.5cm/[uu]^(.33){\phi_{0}}|\hole \ar[r]_{g_{\der{E},0}}& G_{\der{E},1} \ar@/_.5cm/[uu]_{\psi_1}}$}

     This, in turn, gives us that
    \[\psi\circ m_{\der{E},1}=\psi \circ g_{\der{E},0}\circ j_1=g_{\der{F},0}\circ \phi_0\circ j_1=g_{\der{F},0}\circ a_1=m_{\der{F},1}\]

    Now, the square on the left in the diagram below is a pushout and $\psi_1\circ m_{\der{E},1}=m_{\der{F},1}$. Thus, by \Cref{prop:unique} there are the dotted $\phi_1\colon D_{\der{E},1}\to D_{\der{F},1}$ and $\psi_2\colon G_2\to G_2$ in the diagram on the right
    \[\xymatrix{&&G_{\der{F},1} & \ar@{>->}[l]_{f_{\der{F},1}} D_{\der{F},1} \ar[r]^{g_{\der{F},1}}& G_2 \\K_0 \ar[d]_{k_{\der{E,1}}} \ar@{>->}[r]^{l_0}& L_0 \ar[d]^{\psi_1\circ m_{\der{E},1}}&L_0 \ar[d]^{m_{\der{E},1}} \ar[u]_{m_{\der{F},1}}& K_{1} \ar[d]^{m_{\der{E},1}} \ar[u]_{m_{\der{F},1}}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_{1}  \ar[d]_{g_1\circ i_0}  \ar[u]^{g_1\circ i_0}\\D_{\der{E},1} \ar@{>->}[r]_{\psi_1\circ f_{\der{E},1}}& G_{\der{F}, 1}& \ar@/^.5cm/[uu]^{\psi_1} G_{\der{E},1} & \ar@{>->}[l]^{f_{\der{E},1}} D_{\der{E},1} \ar@{.>}@/^.5cm/[uu]^(.33){\phi_{1}}|\hole \ar[r]_{g_{\der{E},1}}& G_2 \ar@{.>}@/_.5cm/[uu]_{\psi_2}}\]

    To conclude, it is now enough to notice that
    \[f_{\der{F},1} \circ \phi_1\circ j_0=\psi_1\circ f_{\der{E},1}\circ j_0=\psi_1\circ h_{\der{E,0}}=h_{\der{F},0}=f_{\der{F},1}\circ a_0\]
    allowing us to deduce $ \phi_1\circ j_0=a_0$.
    \qedhere
\end{proof}

\begin{proposition}
	\label{prop:tec}
	Let $(\X,\R)$ be a left-linear rewriting system and
	$(i_0, i_1)$ an independence pair between two direct
	derivations $\dder{D}_0$ and $\dder{D}_1$. Consider the pullback of
	$f_1\colon D_1\mto G_1$ along $g_0\colon D_0\to G_1$ (first
	square below), then there exist the arrows
	$u_1\colon K_1\to P$ and $u_0\colon K_0\to P$ fitting in the
	central and right square. Moreover, the right one is always
	a pullback.
	\[\xymatrix@R=15pt{P \ar@{>->}[r]^{p_0} \ar[d]_{p_1} & D_0
		\ar[d]^{g_0}& K_0 \ar[r]^{r_0} \ar@{.>}[d]_{u_0}& R_0
		\ar[d]^{i_0} & K_1 \ar@{>->}[r]^{l_1} \ar@{.>}[d]_{u_1}&
		L_1 \ar[d]^{i_1}\\ D_1 \ar@{>->}[r]_{f_1} &G_1 &P
		\ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0}
	\]
\end{proposition}

\begin{proof}
	We start noticing that
	\[
	f_1\circ i_0\circ r_0=h_0\circ r_0=g_0\circ k_0 \qquad
	g_0\circ i_1\circ l_1=m_1\circ l_1= f_1 \circ k_1
	\]
	Thus there exists the dotted $u_0\colon K_0\to P$,
	$u_1\colon K_1\to P$ in the diagram
	\[\xymatrix@R=15pt{K_0 \ar[d]_{r_0}
		\ar@{.>}[r]_{u_0}\ar@/^.4cm/[rr]^{k_0} &P
		\ar@{>->}[r]_{p_0} \ar[d]_{p_1}& D_0 \ar[d]^{g_0}&K_1
		\ar@{>->}[d]_{l_1}
		\ar@{.>}[r]_{u_1}\ar@/^.4cm/[rr]^{k_1} &P \ar[r]_{p_1}
		\ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\R_0
		\ar@/_.4cm/[rr]_{h_0}\ar[r]^{i_0}& D_1
		\ar@{>->}[r]^{f_1}& G_1&L_1
		\ar@/_.4cm/[rr]_{m_1}\ar[r]^{i_1}& D_0 \ar[r]^{g_0}&
		G_1}\]
	By \Cref{prop:pbpoad,lem:pb1} we get that the left half of
	the second rectangle is a pullback.
	\qedhere
\end{proof}

There is another
useful property of  sequentially independent direct
derivations that is worth mentioning.

\noindent
\parbox{9.5cm}
{\begin{proposition}\label{lem:cose}Let
    $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation and suppose
    that $(i_0, i_1)$ is an independence pair between $\dder{D}_0$
    and $\der{D}_1$.  If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a
    switch of $\der{D}$ along $(i_0, i_1)$, then there exists
    $q_0\colon P\to D_{\der{E},0}$ in the diagram
    aside. \end{proposition}}
\parbox{4cm}{$\xymatrix{D_{\der{E},0} \ar@{>->}[d]_{f_{\der{E},0}}&P
    \ar@{.>}[l]_{q_0} \ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1
    \ar@{>->}[d]^{f_1}\\ G_{0}&D_0 \ar@{>->}[l]^{f_0}\ar[r]_{g_0}&
    G_1}$}

\begin{proof}
  Consider the arrow $u_1\colon K_1\to P$ obtained using
  \Cref{prop:tec}. It fits in the big square on the left
\[		\xymatrix@R=15pt{K_1 \ar[r]^{u_1} \ar@{>->}[d]_{l_1}&P
	\ar[r]^{\id{P}}\ar@{>->}[d]_{p_0}& P\ar@{>->}[d]^{p_0}\\L_1
	\ar[d]_{\id{L_1}}\ar[r]^{i_1}&D_0 \ar[r]^{\id{D_0}}
	\ar[d]_{\id{D_0}}& D_{0} \ar@{>->}[d]^{f_0}&K_1 \ar@{>->}[d]_{l_1}\ar[r]^{k_{\der{E},0}}&
	D_{\der{E},0} \ar@{>->}[d]^{f_{\der{E},0}} & K_1 \ar[r]^{u}
	\ar@{>->}[d]_{l_1}& P \ar@{>->}[d]^{f_0\circ
		p_0}\\
	L_1\ar[r]^{i_1} \ar@/_.4cm/[rr]_{m_{\der{E},0}}&D_0
	\ar@{>->}[r]^{f_0}&G_0 & L_1\ar[r]_{m_{\der{E},0}}&G_0 &L_1
	\ar[r]_{m_{\der{E},0}}&G_0}\]

  	Since $f_0$ is a monomorphism, every square in the diagram on the left above
  	is a pullback. Thus the whole big square is a pullback too.
  	Applying \Cref{lem:radj} to the pair of squares on the right now gives
  	us the wanted $q_0\colon P\to D_{\der{E},0}$.
\end{proof}

\subsubsection{Proofs for \Cref{subsec:CR}}

To prove the Local Church-Rosser Theorem, let us begin by deducing some properties from the existence of a strong independence pair.

\begin{remark}\label{rem:deco} 
	Let $(i_0, i_1)$ be a strong
	independence pair between the direct derivations $\dder{D}_0$ and
	$\dder{D}_1$. We can then build the solid part of the diagram
	below
	\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
		\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
		\ar@/_.6cm/[ddrr]^(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
		\ar@/^.6cm/[ddll]_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
		\ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0}
		\ar@{.>}@/_.6cm/[ddrr]_{j_1}&& D_0
		\ar@{>->}[dl]|(.42)\hole_(.64){f_0}\ar[ur]|(.48)\hole^(.7){g_1}&&D_1
		\ar[dr]|(.42)\hole^(.65){g_1}
		\ar@{>->}[ul]|(.48)\hole_(.7){f_1}&&R_1\ar@/^.6cm/[ddll]^{j_0}\ar[dl]^{h_1}\\&G_0
		&&P\ar[dr]^{q_1}
		\ar@{>.>}[dl]_{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\&&Q_0
		\ar@{>->}@{>.>}[ul]_{a_0} &&Q_1\ar@{.>}[ur]^{b_1}}
	\]

	Let us complete this diagram defining the dotted arrows. To get
	$j_1\colon L_0\to Q_0$ and $q_0\colon P\to Q_0$ it is enough to
	take a pushout of $l_0$ along $u_0$, which exists since
	$l_0\in \mathcal{M}$. Moreover, the existence of the wanted
	$a_0\colon Q_0\to G_0$ and $b_1\colon Q_1\to G_2$ follows from
	\[
	f_0\circ p_0 \circ u_0 = f_0\circ k_0 = m_0\circ l_0 \qquad
	g_1\circ p_1\circ u_1 = g_1\circ k_1=h_1\circ r_1
	\]

	\noindent
	\parbox{5.5cm}{\hspace{15pt}We can prove some other properties of
		the arrows appearing in the diagram above. The four rectangles
		aside are pushouts and their left halves are pushouts
		too. Therefore, by \Cref{lem:po1} also their right halves are
		pushouts.  Moreover, $q_0$ and $a_0$ are pushouts of
		respectively $l_0$ and $p_0$, thus they are elements of
		$\mathcal{M}$. By \Cref{prop:pbpoad} the left halves of the
		first and third rectangles are pullbacks too.}  \parbox{3.5cm}{
		$\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar[d]_{r_0}\ar[r]_{u_0}
			&P\ar[d]^{p_1} \ar@{>->}[r]_{p_0} & D_0 \ar[d]^{g_0}&K_1
			\ar@/^.4cm/[rr]^{k_1}\ar@{>->}[d]_{l_1}\ar[r]_{u_1}
			&P\ar@{>->}[d]^{p_0} \ar[r]_{p_1} & D_1 \ar@{>->}[d]^{f_1}\\
			R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i_0}&D_1 \ar@{>->}[r]^{f_1}
			& G_1&L_1 \ar@/_.4cm/[rr]_{m_1} \ar[r]^{i_1}&D_0\ar[r]^{g_0} &
			G_1}$
		$\xymatrix{K_0
			\ar@/^.4cm/[rr]^{k_0}\ar@{>->}[d]_{l_0}\ar[r]_{u_0}
			&P\ar@{>->}[d]^{q_0} \ar@{>->}[r]_{p_0} & D_0
			\ar@{>->}[d]^{f_0}&K_1
			\ar@/^.4cm/[rr]^{k_1}\ar[d]_{r_1}\ar[r]_{u_1}
			&P\ar[d]^{q_1} \ar[r]_{p_1} & D_1 \ar[d]^{g_1}\\
			L_0 \ar@/_.4cm/[rr]_{m_0} \ar[r]^{j_1}&Q_0 \ar@{>->}[r]^{a_0}
			& G_0&R_1 \ar@/_.4cm/[rr]_{h_1} \ar[r]^{j_0}&Q_1 \ar[r]^{b_1}
			& G_2}$}
\end{remark}

\prChurch*
\label{prChurch-proof}

\begin{proof}

  Let us begin considering the diagram
  built in \Cref{rem:deco}
  \[\xymatrix@C=15pt@R=15pt{&&R_0
      \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole \ar[dr]^{h_0}&&
      L_1\ar@/^.8cm/[ddll]^(.2){i_1}
      \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
      \ar@/_.6cm/[ddrr]^(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
      \ar@/^.6cm/[ddll]_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
      \ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0} \ar@{>}@/_.6cm/[ddrr]_{j_1}&& D_0
      \ar@{>->}[dl]|(.42)\hole_(.64){f_0}\ar[ur]|(.48)\hole^(.7){g_1}&&D_1
      \ar[dr]|(.42)\hole^(.65){g_1}
      \ar@{>->}[ul]|(.48)\hole_(.7){f_1}&&R_1\ar@/^.6cm/[ddll]^{j_0}\ar[dl]^{h_1}\\&G_0
      &&P\ar[dr]^{q_1}
      \ar@{>->}[dl]_{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\&&Q_0
      \ar@{>->}@{>->}[ul]_{a_0} \ar@{.>}[dr]_{b_0} &&Q_1\ar[ur]^{b_1}
      \ar@{>.>}[dl]^{a_1} \\ &&&H_1 }\] Since $q_0\colon P\to Q_0$ is in
  $\mathcal{M}$, we can take its pushout along $q_1$ to get the dotted
  arrows $a_1\colon Q_1\to H_1$ and $q_0\colon Q_0\to H_1$. But then,
  since the composite of two pushout squares is a pushout, the diagram
  below is a derivation
  \[\xymatrix@C=15pt{L_1 \ar[d]_{f_0 \circ i_1}&& K_1
      \ar[d]_{q_0\circ u_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1
      \ar@/^.35cm/[drrr]|(.3)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{a_1\circ
        j_0} && L_0 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{b_0\circ
        j_1}& K_1 \ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
      \ar[d]^{g_1\circ i_0} \\G_0 && \ar@{>->}[ll]^{a_0} D_0 \ar[rr]_{b_0}&&
      G_1 && \ar@{>->}[ll]^{a_1} D_1 \ar[rr]_{b_1}&& G_2}\] It is immediate
  now to see that it is a switch of $\dder{D}_0$ and $\dder{D}_1$ along
  $(i_0, i_1)$.
\end{proof}

\begin{remark}
	\label{rem:church}
	It is worth to point out that, by
	\Cref{prop:switch,thm:switch_uni}, the derivation we obtain from
	\Cref{pr:church} %\todo{missing} 
	is made by two switchable derivations that will
	give back the starting derivation (up to abstraction equivalence),
	if switched again.

	Moreover, by \Cref{prop:pbpoad}, the first square below is a
	pullback, therefore, by \cref{rem:deco} the last three squares
	witness that $(j_0, j_1)$ is a strong independence pair too.
	\[
	\xymatrix@R=15pt{P\ar[r]^{q_1} \ar@{>->}[d]_{q_0}&Q_1
		\ar@{>->}[d]^{a_1}&K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1
		\ar[d]^{j_0} & K_0 \ar@{>->}[r]^{l_0} \ar[d]_{u_0}& L_0
		\ar[d]^{j_1}&K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0\ar[d]^{i_0} \\
		Q_ 0\ar[r]_{b_0}&H_1&P \ar[r]_{q_1} & Q_1 &P \ar[r]_{q_0} &
		Q_0&P \ar[r]_{p_1} & D_1}
	\]
\end{remark}

\begin{proposition}
  \label{prop:equi}
  Every linear rewriting system $(\X, \R)$ is strong enforcing.
\end{proposition}

\begin{proof}
  Suppose that $\X$ is $\mathcal{M}$-adhesive and let $(i_0, i_1)$ be
  an independence pair as below
  \[
    \xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0
      \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar@{>->}[r]^{r_0} & R_0
      \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0}
      && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
      \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar@{>->}[rr]^{r_1} && R_1
      \ar[d]^{h_1} \\G_0 && \ar@{>->}[ll]^{f_0} D_0
      \ar@{>->}[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
      \ar@{>->}[rr]_{g_1}&& G_2}\]

  Since $(\X, \R)$ is linear, then $r_1\colon K_1\to R_1$ belongs to
  $\mathcal{M}$, thus it admits a pushout along $u_1\colon K_1\to P$,
  as desired. Moreover, let us consider the two rectangles below
  \[
    \xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar@{>->}[d]_{r_0}\ar[r]_{u_0}
      &P\ar@{>->}[d]^{p_1} \ar@{>->}[r]_{p_0} & D_0
      \ar@{>->}[d]^{f_0}& K_1
      \ar@/^.4cm/[rr]^{k_1}\ar@{>->}[d]_{l_1}\ar[r]_{u_1}
      &P\ar@{>->}[d]^{p_0} \ar@{>->}[r]_{p_1} & D_1
      \ar@{>->}[d]^{f_1}\\ R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i_0}&D_1
      \ar@{>->}[r]^{f_1} & G_1& L_1 \ar@/_.4cm/[rr]_{m_1}
      \ar[r]^{i_1}&D_0 \ar@{>->}[r]^{g_0} & G_1} \] By hypothesis
  $r_0$ and $l_1$ are in $\mathcal{M}$, thus $f_1$ and $g_0$ belong to
  it too. The first point of \Cref{lem:popb} yields the thesis.
\end{proof}

\begin{remark}\label{rem:fill} Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ be a derivation and $(i_0, i_1)$ a strong independence pair between $\dder{D}_0$ and $\dder{D}_1$. Let also $\{\der{E}_{i}\}_{i=0}^1$ be a switch for them along $(i_0, i_1)$. Since, by \Cref{thm:switch_uni}, all switches are abstraction equivalent, we get the diagram below
	\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
		\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
		\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){u_0}\ar[ur]^{r_0}&& G_1 &&
		K_1
		\ar@/^.6cm/[ddll]|(.36)\hole_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
		\ar[dr]^{r_1}\\L_0
		\ar@/_.6cm/[ddrr]_(.2){i'_0}|(.31)\hole|(.81)\hole
		\ar[dr]^(.4){m_0}|(.61)\hole && D_0
		\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1
		\ar[dr]|(.4)\hole^(.65){g_1}
		\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
		&&P_1\ar[dr]_{q_1}	\ar@{>->}[dl]^{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole^(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole_(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_1}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_0} |(.69)\hole }\]

\end{remark}

\subsubsection{Proofs for \Cref{subsec:verytame}}

\begin{proposition}\label{pr:weak} Every linear rewriting system is well-switching.
\end{proposition}
\begin{proof}

	Let $(i_0, i_1)$ and $(i'_0, i'_1)$ be independence pairs for the
	direct derivations $\dder{D}$ and $\dder{D}'$. Notice that, by
	definition, we have
	\[
	f_1\circ i_0=h_0=f_1\circ i'_0 \qquad g_0\circ i_1=m_1= g_0\circ i'_1
	\]

	The arrow $f_1\colon D\to G_1$ is the pushout of
	$l_1\colon K_1\mto L_1$, thus it is in $\mathcal{M}$ implying
	$i_0=i'_0$. If, moreover, we suppose that the rule $\rho$ applied in
	$\dder{D}$ is linear, then $g_0\colon D_0\to G_1$ is in
	$\mathcal{M}$ too, entailing $i_1=i'_1$.
\end{proof}

\begin{remark}\label{rem:po}
	Notice that $\gph{X}$ is adhesive and that pushouts are computed component-wise, thus if $g\colon F\to G$ is the pushout of $r\colon K\to R$, then $g_X\colon F(X)\to G(X)$ is mono for every root $X$.
\end{remark}

\lemVTame*
\label{lemVTame}

\begin{proof}
	Every root-preserving graphical rewriting system is strong enforcing because $\gph{G}$ is in the class $\mathbb{B}^+$ defined in \Cref{app:fill}.  Consider the following diagram 
	\[\xymatrix@R=25pt@C=30pt{L_0 \ar[d]_{m_0}&& K_0
		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
		\ar@<-.5ex>@/^.35cm/[drrr]|(.23)\hole|(.34)\hole_(.4){i_0} 	\ar@<.5ex>@/^.35cm/[drrr]^(.2){j_0}|(.31)\hole |(.4)\hole
		\ar[dr]|(.3)\hole_{h_0} && L_1 \ar@<.5ex>@/_.35cm/[dlll]^(.4){i_1} \ar@<-.5ex>@/_.35cm/[dlll]_(.2){j_1}
		\ar[dl]|(.3)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
		\ar[rr]_{g_1}&& G_2}\]

	Since $f_1$ is mono then $i_0=j_0$. For every  root $X$ we have
	\[g_{0,X}\circ i_{1,X}=m_{1,X}=g_{0,X}\circ j_{1,X}\]
	which entails $i_{1,X}=j_{1,X}$. Let now $Y$ be another object, and take $y\in L_1(Y)$. By definition, we have a root $X$ and an arrow $f:X\to Y$ and $x\in L_{1}(X)$ such that $L(f)(y)=x$. By naturality we have
	\[i_{1,Y}(y)=i_{1,Y}(L(f)(x))=L(f)(i_{1, X}(x))=L(f)(j_{1, X}(x))=j_{1,X}(L(f)(x))=j_{1,Y}(y)\]
Thus $i_{1,Y}=j_{1,Y}$, as wanted.
\end{proof}

\subsubsection{Proofs for \cref{subsec:canonical}}

The section opens recalling the definition of \emph{consistent permutation} for the interested reader.

\begin{definition}[Consistent permutation]
	\label{def:permcon}
	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ 
	a left-linear rewriting system.  Take two derivations $\der{D}:=\{\dder{D}_i\}_{i=0}^n$ and
	$\der{D}':=\{\dder{D}'_i\}_{i=0}^n$ with the same length and with isomorphic sources and targets.
	Let also $r(\der{D})=\{\rho_i\}_{i=0}^n$ and
	$r(\der{D}')=\{\rho'_i\}_{i=0}^n$ be the  associated sequence of rules. 
	A \emph{consistent permutation}
	between $\der{D}$ and
	$\der{D}'$ is a permutation
	$\sigma\colon [0,n]\to [0,n]$ such that, for every $i\in [0,n]$,
	$\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a
	\emph{mediating isomorphism}
	$\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the
	following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, the matches and co-matches of $\dder{D}_i$ and
	$\dder{D}'_i$.
	\[
	\xymatrix@C=30pt{L_i
		\ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}}
		&\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i}
		\ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}}
		&\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)}
		\ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro&
		G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro
		\der{D}' \rpro}
	\]
\end{definition}

We can now turn to the proofs of the results of \Cref{subsec:canonical}.

\begin{notation}
  Recall that by \cref{thm:switch_uni} switches are uniquely
  determined, up to abstraction equivalence.
  %
  In the sequel we denote any switch of two switchable direct
  derivations $\dder{D}_0$ and $\dder{D}_1$ along an independence pair
  $(i_0, i_1)$ by $S_{i_0, i_1}(\dder{D}_0, \dder{D}_1)$. Moreover, we
  use $S_{i_0,i_1}(\dder{D}_1)$ and $S_{i_0,i_1}(\dder{D}_0)$ to
  denote its components, in such a way that
  $S_{i_0, i_1}(\dder{D}_0, \dder{D}_1)=S_{i_0,i_1}(\dder{D}_1)\cdot
  S_{i_0,i_1}(\dder{D}_0)$.
\end{notation}

\lemIndepGlobalLeft*
\label{lemIndepGlobalLeft-proof}

\begin{proof}   
	Since $(\X, \R)$ is well-switching, there exists unique independence pairs 
$(i_0,i_1)$ between $\dder{D}_0$ and $\dder{D}_1$,	$(a_0,a_1)$ between $\dder{D}_1$ and $\dder{D}_2$ and	$(e_0, e_1)$ between $\dder{D}_0$ and
	$S_{a_0,a_1}(\dder{D}_2)$. 	Using \Cref{rem:fill} we can build the diagrams in \Cref{fi:first,fi:second,fi:third}.  The first depicts the  switching $\dder{D}_0$ and $\dder{D}_1$ along  $(i_0, i_1)$, the second that of $\dder{D}_1$ and $\dder{D}_2$ along $(a_0, a_1)$, while the third refers to $\dder{D}_0$ and
	$S_{a_0,a_1}(\dder{D}_2)$.

	\begin{figure}[h]
		\centering
		$\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
			\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
			\ar[dl]_{m_1}\\&K_0\ar@{>->}[dr]^{k_0}\ar[dl]_{l_0}
			\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){v_0}\ar[ur]^{r_0}&& G_1 &&
			K_1
			\ar@/^.6cm/[ddll]|(.36)\hole_(.65){v_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
			\ar[dr]^{r_1}\\L_0
			\ar@/_.6cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole
			\ar[dr]^(.4){m_0}|(.61)\hole && D_0
			\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1
			\ar[dr]|(.4)\hole^(.65){g_1}
			\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_(.4){h_1}|(.6)\hole\\&G_0
			&&P_1\ar[dr]_{q_1}
			\ar@{>->}[dl]^{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1
			\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ
				i_1}|(.61)\hole&&Q_0
			\ar@{>->}[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0}
			&&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar@{>->}[dl]|(.5)\hole_(.65){s_1}
			&& R_0 \ar[ul]^(.35){g_1\circ
				i_0}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\&K_1
			\ar[ur]_{q_0\circ v_1} \ar[dr]_{r_1}
			\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){v_1}&&H'_1&& K_0
			\ar[ur]_{r_0} \ar[ul]^{q_1\circ v_0} \ar@{>->}[dl]^{l_0}
			\ar@/_.6cm/[uull]^(.65){v_0}\\&& R_1
			\ar[ur]_{\hspace{-6pt}s_1\circ
				j_1}\ar@/^.8cm/[uurr]^(.2){j_1}&& L_0 \ar[ul]^{t_0\circ
				j_0\hspace{-6pt}} \ar@/_.8cm/[uull]_(.2){j_0} |(.69)\hole
		}	$
		\caption{Picture for the proof of \Cref{lem:indep-global-left}: switch of $\dder{D}_0$ and $\dder{D}_1$.}
		\label{fi:first}
	\end{figure}

	\begin{figure}[t]
		\centering 
		$\xymatrix@C=15pt@R=15pt{&&R_1 \ar@/_.8cm/[ddrr]_(.2){a_0}|(.7)\hole
			\ar[dr]^{h_1}&& L_2\ar@/^.8cm/[ddll]^(.2){a_1}
			\ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar@{>->}[dl]_{l_1}
			\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){u_1}\ar[ur]^{r_1}&& G_2 &&
			K_2
			\ar@/^.6cm/[ddll]|(.36)\hole_(.65){u_2}\ar[dl]_{k_2}\ar@{>->}[lu]_{l_2}
			\ar[dr]^{r_2}\\L_1
			\ar@/_.6cm/[ddrr]_(.2){b_0}|(.31)\hole|(.81)\hole
			\ar[dr]^(.4){m_1}|(.61)\hole && D_1
			\ar@{>->}[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2
			\ar[dr]|(.4)\hole^(.65){g_2}
			\ar@{>->}[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.6cm/[ddll]^(.2){b_1}|(.31)\hole|(.81)\hole\ar[dl]_(.4){h_2}|(.61)\hole\\&G_1
			&&P_2\ar[dr]_{d_1}
			\ar@{>->}[dl]^{d_0}\ar[ur]^(.4){c_1}\ar@{>->}[ul]_(.4){c_0}&&G_3\\L_2
			\ar@/^.6cm/[uurr]^(.2){a_1} \ar[ur]_(.35){f_1\circ
				a_1}|(.61)\hole&&Q_2
			\ar@{>->}[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1}
			&&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar@{>->}[dl]|(.5)\hole_(.65){x_2}
			&& R_1 \ar[ul]^(.3){g_2\circ
				a_0}|(.61)\hole\ar@/_.6cm/[uull]_(.2){a_0}\\&K_2
			\ar[ur]_{d_0\circ u_2} \ar[dr]_{r_2}
			\ar@{>->}[ul]^{l_2}\ar@/^.6cm/[uurr]_(.65){u_2}&&G'_2&& K_1
			\ar[ur]_{r_1} \ar[ul]^{d_1\circ u_1} \ar@{>->}[dl]^{l_1}
			\ar@/_.6cm/[uull]^(.65){u_1}\\&& R_2
			\ar[ur]_{\hspace{-6pt}x_2\circ
				b_1}\ar@/^.8cm/[uurr]^(.2){b_1}&& L_1 \ar[ul]^{y_1\circ
				b_0\hspace{-7pt}} \ar@/_.8cm/[uull]_(.2){b_0} |(.69)\hole
		}	$		
		\caption{Picture for the proof of \Cref{lem:indep-global-left}: switch of $\dder{D}_1$ and $\dder{D}_2$.}
		\label{fi:second}
	\end{figure}

	\begin{figure}
		\centering
		$\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){e_0}|(.7)\hole
			\ar[dr]^{\hspace{-5pt}h_0}&& L_2\ar@/^.8cm/[ddll]^(.2){e_1}
			\ar[dl]_{f_1\circ a_1\hspace{-5pt}}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
			\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){w_0}\ar[ur]^{r_0}&& G_1 &&
			K_2 \ar@/^.6cm/[ddll]|(.36)\hole_(.65){w_2}\ar[dl]_{d_0\circ
				u_2\hspace{-5pt}}\ar@{>->}[lu]_{l_2} \ar[dr]^{r_2}\\L_0
			\ar@/_.6cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole
			\ar[dr]^(.4){m_0}|(.61)\hole && D_0
			\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2
			\ar[dr]|(.4)\hole^(.65){y_1}
			\ar@{>->}[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.6cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.3){x_2\circ
				b_1}|(.58)\hole \\&G_0 &&P_3\ar[dr]_{n_1}
			\ar@{>->}[dl]^{n_0}\ar[ur]^(.4){\theta_1}\ar@{>->}[ul]_(.4){\theta_0}&&G'_2\\L_2
			\ar@/^.6cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ
				e_1}|(.61)\hole&&Q_4
			\ar@{>->}[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0}
			&&Q_5\ar[ur]|(.4)\hole^(.65){z'_1}
			\ar@{>->}[dl]|(.5)\hole_(.65){z_1} && R_0 \ar[ul]^(.3){y_1\circ
				e_0}|(.6)\hole\ar@/_.6cm/[uull]_(.2){e_0}\\&K_2
			\ar[ur]_{\hspace{-2pt}n_0\circ w_2} \ar[dr]_{r_2}
			\ar@{>->}[ul]^{l_2}\ar@/^.6cm/[uurr]_(.65){w_2}&&G'_1&& K_0
			\ar[ur]_{r_0} \ar[ul]^{n_1\circ w_0} \ar[dl]^{l_0}
			\ar@/_.6cm/[uull]^(.65){w_0}\\&& R_2
			\ar[ur]_{\hspace{-4pt}z_1\circ
				o_1}\ar@/^.8cm/[uurr]^(.2){o_1}&& L_0 \ar[ul]^{z'_0\circ
				o_0\hspace{-7pt}} \ar@/_.8cm/[uull]_(.2){o_0} |(.69)\hole
		}	$
		\caption{Picture for the proof of \Cref{lem:indep-global-left}: switch of $\dder{D}_0$ and $S_{a_0,a_1}(\dder{D}_2)$.}
		\label{fi:third}
	\end{figure}

	\begin{enumerate}
		\item We have to construct the two dotted arrows in the diagram
		below
		\[\xymatrix@C=15pt{L_0 \ar[d]_{z'_0\circ o_0}&& K_0
			\ar[d]_{n_1\circ w_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
			\ar@{.>}@/^.35cm/[drrr]_(.4){\beta_0}|(.29)\hole
			\ar[dr]|(.28)\hole_{y_1\circ e_0} && L_1
			\ar@{.>}@/_.35cm/[dlll]^(.4){\beta_1}
			\ar[dl]|(.28)\hole^{y_1\circ b_0}& K_1 \ar[d]^{d_1\circ
				u_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ
				a_1}\\G'_1 && \ar@{>->}[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2 &&
			\ar@{>->}[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_3}\]

		The arrows $i_0\colon R_0\to D_1$,
		$e_0\colon R_0\to Q_2$, $i_1\colon L_1\to D_0$ and $b_0\colon L_1 \to Q_2$ satisfy
		\[
		f_1\circ i_0  = h_0 =x_1\circ e_0 \qquad 
		g_0\circ i_1 = m_1 = x_1 \circ b_0 \]

		These identities entail the existence of the dotted
		$\beta'_0\colon R_0\to P_2$ and $\beta'_1\colon L_1\to P_3$ below
		\[\xymatrix{R_0 \ar@{.>}[dr]^{\beta'_0} \ar@/^.3cm/[drr]^{i_0}
			\ar@/_.3cm/[ddr]_{e_0} &&& L_1 \ar@{.>}[dr]^{\beta'_1} \ar@/^.3cm/[drr]^{i_1}
			\ar@/_.3cm/[ddr]_{b_0}\\ &P_2 \ar@{>->}[r]^{c_0} \ar@{>->}[d]_{d_0}& D_1
			\ar@{>->}[d]^{f_1} & &P_3 \ar@{>->}[r]^{\theta_0} \ar[d]_{\theta_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar@{>->}[r]_{x_1} & G_1 & &Q_2\ar@{>->}[r]_{x_1} & G_1}\]

                    We can now define $\beta_0\colon R_0\to Q_3$ as $d_1\circ \beta'_1$ and $\beta_1\colon L_1\to Q_5$ be $n_1\circ \beta'_1$, so that
		\begin{align*}
			x_2\circ \beta_0 & =x_2\circ d_2\circ \beta'_0 = y_1\circ d_0\circ \beta'_0=y_1\circ e_0\\
			z'_1 \circ \beta_1 & = z'_1 \circ n_1\circ \beta'_1 =y_1\circ \theta_1\circ \beta'_1=y_1\circ b_0
		\end{align*}

		Therefore, $(\beta_0, \beta_1)$ is the wanted independence pair.

              \item Here we assume that
                $\dder{D}_1$ and $\dder{D}_2$ are switchable  with an
    independence pair $(\alpha_0, \alpha_1)$ and that
    $\dder{D}_0$ and $S_{\alpha_0, \alpha_1}(\dder{D}_2)$ are switchable.
    % 
                Hence, in addition to the three diagrams above, we have a fourth one, depicted in \Cref{fi:fourth}.
		\begin{figure}[h]
			\centering
			$\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){\alpha_0}|(.7)\hole \ar[dr]^{\hspace{-1pt}g_1\circ i_0}&& L_2\ar@/^.8cm/[ddll]^(.2){\alpha_1}  \ar[dl]_{m_2\hspace{-2pt}}\\
				&K_0\ar[dr]^{\hspace{-4pt}q_1\circ v_0}\ar@{>->}[dl]_{l_0} \ar@/_.6cm/[ddrr]|(.36)\hole^(.65){\phi_0}\ar[ur]^{r_0}&& G_2 && K_2 \ar@/^.6cm/[ddll]|(.36)\hole_(.65){\phi_2}\ar[dl]_{k_2}\ar@{>->}[lu]_{l_2} \ar[dr]^{r_2}\\
				L_0 \ar@/_.6cm/[ddrr]_(.2){\gamma_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){\hspace{-4pt}t_0\circ j_0}|(.6)\hole && Q_1 \ar@{>->}[dl]|(.4)\hole_(.65){s_1}\ar[ur]|(.5)\hole^(.7){t_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar@{>->}[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.6cm/[ddll]^(.2){\gamma_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){h_2}|(.6)\hole\\&H'_1 &&P_4\ar[dr]_{\lambda_1} \ar@{>->}[dl]^{\lambda_0}\ar[ur]^(.4){\zeta_1}\ar@{>->}[ul]_(.4){\zeta_0}&&G_3\\
				L_2 \ar@/^.6cm/[uurr]^(.2){\alpha_1} \ar[ur]_(.35){\hspace{-2pt}s_1\circ
					\alpha_1}|(.61)\hole&&Q_6
				\ar@{>->}[ul]|(.4)\hole_(.6){\xi_0}\ar[dr]|(.5)\hole^(.65){\xi'_0}
				&&Q_7\ar[ur]|(.4)\hole^(.6){\xi'_1}
				\ar@{>->}[dl]|(.5)\hole_(.65){\xi_1} && R_0 \ar[ul]^(.35){g_2\circ
					\alpha_0}|(.61)\hole\ar@/_.6cm/[uull]_(.2){\alpha_0}\\&K_2
				\ar[ur]_{\lambda_0\circ \phi_2} \ar[dr]_{r_2}
				\ar@{>->}[ul]^{l_2}\ar@/^.6cm/[uurr]_(.65){\phi_2}&&H'_2&& K_0
				\ar[ur]_{r_0} \ar[ul]^{\lambda_1\circ \phi_0} \ar@{>->}[dl]^{l_0}
				\ar@/_.6cm/[uull]^(.65){\phi_0}\\&& R_2
				\ar[ur]_{\hspace{-5pt}\xi_1\circ
					\gamma_1}\ar@/^.8cm/[uurr]^(.2){\gamma_1}&& L_0
				\ar[ul]^{\xi'_0\circ \gamma_0\hspace{-7pt}}
				\ar@/_.8cm/[uull]_(.2){\gamma_0} |(.69)\hole 
			}	$
			\caption{Picture for the proof of \Cref{lem:indep-global-left}: switch of $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$.}
			\label{fi:fourth}
		\end{figure}

		Our aim is to construct the dotted arrows in the following diagram
		\[\xymatrix@C=15pt{L_1 \ar[d]_{f_0\circ i_0}&& K_1
			\ar[d]_{q_0\circ v_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1
			\ar@{.>}@/^.35cm/[drrr]_(.4){\epsilon_0}|(.29)\hole
			\ar[dr]|(.28)\hole_{s_1\circ j_1} && L_2
			\ar@{.>}@/_.35cm/[dlll]^(.4){\epsilon_1}
			\ar[dl]|(.28)\hole^{s_1\circ \alpha_1}& K_2
			\ar[d]^{\lambda_0\circ \phi_2}\ar@{>->}[l]_{l_2} \ar[rr]^{r_2} &&
			R_2 \ar[d]^{\xi_1\circ \gamma_1}\\G_0 && \ar@{>->}[ll]^{s_0} Q_0
			\ar[rr]_{t_0}&& H'_1 && \ar@{>->}[ll]^{\xi_0} Q_6
			\ar[rr]_{\xi'_0}&& H'_2}\]

		We can take the arrows $j_1\colon R_1\to Q_1$, 
		$a_0\colon R_1\to D_2$, $e_1\colon L_2 \to D_0$ and $a_1\colon L_2\to D_1$ and notice that
		\[	f_2\circ a_0 =h_1 =t_1\circ j_1 \qquad   g_0\circ e_1=f_1\circ a_1\]
		and thus we get the dotted arrows $\epsilon'_0\colon R_1\to P_4$, $\epsilon'_1\colon L_2\to P:1$ 
		\[\xymatrix{R_1 \ar@{.>}[dr]^{\epsilon'_0} 
			\ar@/^.3cm/[drr]^{j_1} \ar@/_.3cm/[ddr]_{a_0}&&& L_2 \ar@{.>}[dr]^{\epsilon'_1}
			\ar@/^.3cm/[drr]^{a_1} \ar@/_.3cm/[ddr]_{e_0}\\ &P_4
			\ar@{>->}[r]^{\zeta_0} \ar[d]_{\zeta_1}& Q_1 \ar[d]^{t_1} &&P_1
			\ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\
			&D_2\ar@{>->}[r]_{f_2} & G_2& 	&D_0\ar[r]_{g_0} & G_1} \]

		Now, notice that
		\[
		t_1\circ q_1\circ \epsilon'_1  =g_1\circ p_1\circ \epsilon'_1  =g_1\circ a_1 =m_2
		\]
		Hence $(\alpha_0, q_1\circ \epsilon'_1)$ is an independence pair
		for $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$. By hypothesis $(\X, \R)$ is well-switching and therefore
		$q_1\circ \epsilon'_1$ must coincide with $\alpha_1$.

		We can then define $\epsilon_0\colon R_1\to Q_6$ and $\epsilon_1\colon L_2\to Q_0$ to be, respectively, 
		$\lambda_0\circ \epsilon'_0$ and $q_0\circ
		\epsilon'_1$. Then for these  arrows we have  identities
		\begin{align*}
			\xi_0\circ \epsilon_0 & =\xi_0\circ \lambda_0\circ \epsilon'_0 =s_1\circ \zeta_0 \circ \epsilon'_0=s_1\circ j_1\\	t_0\circ \epsilon_1 & = t_0\circ q_0\circ \epsilon'_1 =s_1\circ q_1\circ \epsilon'_1=s_1\circ \alpha_1
		\end{align*}
		Allowing us to conclude that
		$S_{i_0,i_1}(\dder{D}_1)$ and $S_{\alpha_0,
			\alpha_1}(\dder{D}_2)$ are switchable.  \qedhere
	\end{enumerate}
\end{proof}

\lemSwitchConfluence*
\label{lemSwitchConfluence-proof}

\begin{proof}
	To fix the notation, let us depict the derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$
	\[\xymatrix@C=15pt{L_0\ar[d]^{m_0}&& K_0 \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]_(.4){i_0}|(.29)\hole \ar[dr]|(.28)\hole_{h_0} && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.28)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_1 \ar[dr]|(.28)\hole_{h_1} \ar@/^.35cm/[drrr]_(.4){j_0}|(.29)\hole  && L_2 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.28)\hole^{m_2}& K_2 \ar[d]^{k_2}\ar@{>->}[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]_{h_2} \\G_0 && \ar@{>->}[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar@{>->}[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2 && \ar@{>->}[ll]^{f_2} D_2 \ar[rr]_{g_2}&& G_3 }\]

	We are going to do the two sequences of switches and compare the results.

	\smallskip \noindent First sequence of switches.

	We begin switching $\dder{D}_0$ and $\dder{D}_1$ to get the following diagram
	\[\xymatrix@C=15pt{L_1\ar[d]^{f_0\circ i_1}&& K_1 \ar[d]_{k'_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){a_0}|(.29)\hole \ar[dr]|(.28)\hole_{h'_1} && L_0 \ar@/_.35cm/[dlll]^(.4){a_1} \ar[dl]|(.28)\hole^{m'_0}& K_0 \ar[d]^{k'_0}\ar@{>->}[l]_{l_0} \ar[r]^{r_0} & R_0 \ar[dr]|(.28)\hole_{g_1\circ i_0} \ar@/^.35cm/[drrr]_(.4){b_0}|(.29)\hole  && L_2 \ar@/_.35cm/[dlll]^(.4){b_1} \ar[dl]|(.28)\hole^{m_2}& K_2 \ar[d]^{k_2}\ar@{>->}[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]_{h_2} \\G_0 && \ar@{>->}[ll]^{f'_0} D'_0 \ar[rr]_{g'_0}&& G'_1  && \ar@{>->}[ll]^{f'_1} D'_1 \ar[rr]_{g'_1}&& G_2 && \ar@{>->}[ll]^{f_2} D_2 \ar[rr]_{g_2}&& G_3 }\]

	By \Cref{def:switch} we also know that $m_0=f'_0\circ a_1$ and $h_1=g'_1\circ a_0$. Now, let us switch $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$. In this case we obtain
	\[\xymatrix@C=15pt{L_1\ar[d]^{f_0\circ i_1}&& K_1 \ar[d]_{k'_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){c_0}|(.29)\hole \ar[dr]|(.28)\hole_{h'_1} && L_2 \ar@/_.35cm/[dlll]^(.4){c_1} \ar[dl]|(.28)\hole^{f'_1\circ b_1}& K_2 \ar[d]^{k'_2}\ar@{>->}[l]_{l_2} \ar[r]^{r_2} & R_2 \ar[dr]|(.28)\hole_{h'_2} \ar@/^.35cm/[drrr]_(.4){d_0}|(.29)\hole  && L_0 \ar@/_.35cm/[dlll]^(.4){d_1} \ar[dl]|(.28)\hole^{\hat{m}_0}& K_0 \ar[d]^{\hat{k}_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]_{g_2\circ b_0} \\G_0 && \ar@{>->}[ll]^{f'_0} D'_0 \ar[rr]_{g'_0}&& G'_1  && \ar@{>->}[ll]^{\hat{f}_1} \hat{D}_1 \ar[rr]_{\hat{g}_1}&& G'_2 && \ar@{>->}[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 }\]
	Using again the definition of switch, we know that $m'_0=\hat{f}_1\circ d_1$ and $h_2=g'_2\circ d_0$. Moreover, by hypothesis $(\X, \R)$ is well-switching and the hypothesis of the second point of \Cref{lem:indep-global-left} are satisfied by $\der{D}$. Thus we can characterise $c_0\colon R_1\to \hat{D}_1$ and $c_1\colon L_2\to D'_0$ as the unique arrows fitting in the diagrams below, where the bottom squares are pullbacks
	\[\xymatrix@R=15pt@C=15pt{&&R_1 \ar@/_1.2cm/[dddl]_(.4){a_0}|(.63)\hole\ar[dl]^{j_0}\ar[dd]^{c'_0} \ar@{>}[dr]^{c_0}&&&&&L_2 \ar[dl]^{j_1} \ar@/_1.2cm/[dddl]_(.4){z_1}|(.63)\hole\ar[dd]^{c'_1} \ar@{>}[dr]^{c_1}\\&D_2 \ar@{>->}[dl]^(.4){f_2}&&\hat{D}_1 \ar[dr]^{\hat{g}_1}  &&&D_1 \ar@{>->}[dl]^(.4){f_1}&&D'_0 \ar[dr]^{g'_0}\\G_2 && P\ar[dr]_{p_4} \ar@{>->}[ur]_{p_3}\ar@{>->}[dl]^{p_1} \ar[ul]^{p_2}&&G'_2&G_1 && Q\ar[dr]_{q_4} \ar@{>->}[ur]_{q_3}\ar@{>->}[dl]^{q_1} \ar[ul]^{q_2}&&G'_1\\& D'_1 \ar[ul]^{g'_1}&&D'_2 \ar@{>->}[ur]_{f'_2}&&& D_0 \ar[ul]^{g_0}&&D'_1 \ar@{>->}[ur]_{f'_1}}\]

Finally, we switch the first two direct derivations
	\[\xymatrix@C=15pt{L_2\ar[d]^{f'_0\circ c_1}&& K_2 \ar[d]_{\hat{k}_2}\ar@{>->}[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){e_0}|(.29)\hole \ar[dr]|(.28)\hole_{\hat{h}_2} && L_1 \ar@/_.35cm/[dlll]^(.4){e_1} \ar[dl]|(.28)\hole^{\hat{m}_1}& K_1 \ar[d]^{\hat{k}_1}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){t_0}|(.29)\hole \ar[dr]|(.28)\hole_{\hat{g}_1\circ c_0}   && L_0  \ar[dl]|(.28)\hole^{\hat{m}_0} \ar@/_.35cm/[dlll]^(.4){t_1}& K_0 \ar[d]^{\hat{k}_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]_{g_2\circ b_0} \\G_0 && \ar@{>->}[ll]^{\hat{f}_0} \hat{D}_0 \ar[rr]_{\hat{g}_0}&& \hat{G}_1  && \ar@{>->}[ll]^{\tilde{f}_1} \tilde{D}_1 \ar[rr]_{\tilde{g}_1}&& G'_2 && \ar@{>->}[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 }\]
	As before, we have identities $f_0\circ i_1=\hat{f}_0\circ e_1$ and $h'_2=\tilde{g}_1\circ e_0$. Now, the derivation $S_{i_0, i_1}(\dder{D}_1)\cdot S_{i_0, i_1}(\dder{D}_0)\cdot \dder{D}_2$ satisfies the hypothesis of the first point of \Cref{lem:indep-global-left}. Thus, since there is at most one independence pair between two direct derivations, we know that  $t_0\colon R_1\to \tilde{D}_1$ and $t_1\colon L_0\to D'_2$  fit in
	\[\xymatrix{&R_1 \ar[dl]_{a_0} \ar@{>}[dr]^{t_0} \ar@/^.4cm/[dd]|\hole^(.6){c_0}\ar[d]_{t'_0}&&L_ 0\ar[d]_{d_1} \ar@/_.4cm/[ddrr]|(.41)\hole_(.7){a_1}\ar[drr]^{t'_1} \ar@{>}[rr]^{t_1}&&\tilde{D}_1 \ar@{>->}[r]^{\tilde{f}_1}&\hat{G}_1\\ D'_1 \ar@{>->}[d]_{f'_1}&P\ar@{>->}[d]_{p_3} \ar[r]^{p_4} \ar@{>->}[l]_{p_1}&D'_2\ar@{>->}[d]^{f'_2}&\hat{D}_1 \ar@{>->}[d]_{\hat{f}_1}&&S\ar@{>->}[r]_{s_4} \ar[u]_{s_3}\ar@{>->}[d]^{s_1} \ar[ll]_{s_2} &\hat{D}_0 \ar[u]_{\hat{g}_0} \ar@{>->}[d]^{\hat{f}_0}\\G'_1&\hat{D}_1 \ar@{>->}[l]^{\hat{f}_1}\ar[r]_{\hat{g}_1}& G'_2&G'_1 && D'_0 \ar[ll]^{g'_0}  \ar@{>->}[r]_{f'_0}& G_0 }\]

	\smallskip \noindent Second sequence of switches.

	This time we start switching $\dder{D}_1$ and $\dder{D}_2$.
	\[\xymatrix@C=15pt{L_0\ar[d]^{m_0}&& K_0 \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]_(.4){z_0}|(.29)\hole \ar[dr]|(.28)\hole_{h_0} && L_2 \ar@/_.35cm/[dlll]^(.4){z_1} \ar[dl]|(.28)\hole^{f_1\circ j_1}& K_2 \ar[d]^{\check{k}_2}\ar@{>->}[l]_{l_2} \ar[r]^{r_2} & R_2 \ar[dr]|(.28)\hole_{\check{h}_2} \ar@/^.35cm/[drrr]_(.4){w_0}|(.29)\hole  && L_1 \ar@/_.35cm/[dlll]^(.4){w_1} \ar[dl]|(.28)\hole^{\check{m}_1}& K_1 \ar[d]^{\check{k}_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} && R_1\ar[d]_{g_2\circ j_0} \\G_0 && \ar@{>->}[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar@{>->}[ll]^{\check{f}_1} \check{D}_1 \ar[rr]_{\check{g}_1}&& \check{G}_2 && \ar@{>->}[ll]^{\check{f}_2} \check{D}_2 \ar[rr]_{\check{g}_2}&& G_3 }\]
	As in the previous case, we already know that $m_1=\check{f}_1\circ w_1$ and $h_2=\check{g}_2\circ w_0$.

	Next, we switch $\dder{D}_0$ and $S_{j_0, j_1}(\dder{D}_2)$ getting
	\[\xymatrix@C=15pt{L_2\ar[d]^{f_0\circ z_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar@{>->}[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){y_0}|(.29)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_0 \ar@/_.35cm/[dlll]^(.4){y_1} \ar[dl]|(.28)\hole^{\check{m}_0}& K_0 \ar[d]^{\check{k}_0}\ar@{>->}[l]_{l_0} \ar[r]^{r_0} & R_0 \ar[dr]|(.28)\hole_{\check{g}_1\circ z_0} \ar@/^.35cm/[drrr]_(.4){x_0}|(.29)\hole  && L_1 \ar@/_.35cm/[dlll]^(.4){x_1} \ar[dl]|(.28)\hole^{\check{m}_1}& K_1 \ar[d]^{\check{k}_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} && R_1\ar[d]_{g_2\circ j_0} \\G_0 && \ar@{>->}[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar@{>->}[ll]^{\mathring{f}_1} \mathring{D}_1 \ar[rr]_{\mathring{g}_1}&& \check{G}_2 && \ar@{>->}[ll]^{\check{f}_2} \check{D}_2 \ar[rr]_{\check{g}_2}&& G_3 }\]
	The usual identities $m_0=\check{f}_0\circ y_1$, $\check{h}_2=\mathring{g}_1\circ y_0$ hold. But the really important thing to notice is that the first match of these derivation coincide with $f'_0\circ c_1$
	\[	f_0'\circ c_1  =f'_0\circ q_3\circ c'_1 =f_0\circ q_1\circ c'_1=f_0\circ z_1\]

	Moreover, we can characterise the pair $(x_0, x_1)$. If we apply the first point of \Cref{lem:indep-global-left} to $\dder{D}$ we get an independence pair between the last two steps of the derivation above, which, since $(\X, \R)$ is well-switching, must coincide with $(x_0, x_1)$. Thus we have two diagrams

	\[\xymatrix{&R_0 \ar[dl]_{i_0} \ar@{>}[dr]^{x_0} \ar@/^.4cm/[dd]|\hole^(.6){z_0}\ar[d]_{x'_0}&&L_ 1\ar[d]_{w_1} \ar@/_.4cm/[ddrr]|(.41)\hole_(.7){i_1}\ar[drr]^{x'_1} \ar@{>}[rr]^{x_1}&&\mathring{D}_1 \ar@{>->}[r]^{\mathring{f}_1}&\check{G}_1\\ D_1 \ar@{>->}[d]_{f_1}&P'\ar@{>->}[d]_{p'_3} \ar[r]^{p'_4} \ar@{>->}[l]_{p'_1}&\check{D}_2\ar@{>->}[d]^{\check{f}_2}&\check{D}_1 \ar@{>->}[d]_{\check{f}_1}&&S'\ar@{>->}[r]_{s'_4} \ar[u]_{s'_3}\ar@{>->}[d]^{s'_1} \ar[ll]_{s'_2} &\check{D}_0 \ar[u]_{\check{g}_0} \ar@{>->}[d]^{\check{f}_0}\\G_1&\check{D}_1 \ar@{>->}[l]^{\check{f}_1}\ar[r]_{\check{g}_1}& \check{G}_2&G_1 && D_0 \ar[ll]^{g_0}  \ar@{>->}[r]_{f_0}& G_0 }\]
	From this diagram we can recover another identity. Notice that, if $p'_2\colon P'\to D_2$ is the last projection from $P'$, then
	\[f_2\circ p'_2\circ x'_0=g_1\circ p'_1\circ x'_0=g_1\circ i_0=f_2\circ b_0\]
	Implying, since $f_2$ is mono, that $p'_2\circ x'_0=b_0$. From this, we can also deduce that 
	\[\check{g}_2\circ x_0=\check{g}_2\circ p'_4\circ x'_0=g_2\circ p'_2\circ x'_0=g_2\circ b_0 \]

	Finally, switching the second and the third step we get
	\[\xymatrix@C=15pt{L_2\ar[d]^{f_0\circ z_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar@{>->}[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){v_0}|(.29)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_1 \ar@/_.35cm/[dlll]^(.4){v_1} \ar[dl]|(.28)\hole^{\mathring{f}_1 \circ x_1}& K_1 \ar[d]^{\mathring{k}_1}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){u_0}|(.29)\hole\ar[dr]_{\check{h}_1}|(.28)\hole   && L_0 \ar@/_.35cm/[dlll]^(.4){u_1} \ar[dl]^{\mathring{m}_0}|(.28)\hole& K_0 \ar[d]^{\mathring{k}_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0\ar[d]_{\check{g}_2\circ x_0} \\G_0 && \ar[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar@{>->}[ll]^{\bar{f}_1} \bar{D}_1 \ar[rr]_{\bar{g}_1}&& \bar{G}_2 && \ar@{>->}[ll]^{\bar{f}_2} \bar{D}_2 \ar[rr]_{\bar{g}_2}&& G_3 }\]
	As usual, this last switch brings identities $\check{m}_0=\bar{f}_1\circ u_1$ and $g_2\circ j_0=\bar{g}_2\circ u_0$. Applying the second point of \Cref{lem:indep-global-left} to $\dder{D}_0\cdot S_{j_0, j_1}(\dder{D}_2)\cdot S_{j_0, j_1}(\dder{D}_1)$ and the fact that $(\X, \R)$ is well-switching we get the following diagrams
	\[\xymatrix@R=15pt@C=15pt{&&R_2 \ar@/_1.2cm/[dddl]_(.4){y_0}|(.63)\hole\ar[dl]^{w_0}\ar[dd]^{v'_0} \ar@{>}[dr]^{v_0}&&&&&L_1 \ar[dl]^{w_1} \ar@/_1.2cm/[dddl]_(.4){i_1}|(.63)\hole\ar[dd]^{v'_1} \ar@{>}[dr]^{v_1}\\&\check{D}_2 \ar@{>->}[dl]^(.4){\check{f}_2}&&\bar{D}_1 \ar[dr]^{\bar{g}_1}  &&&\check{D}_1 \ar@{>->}[dl]^(.4){\check{f}_1}&&\check{D}_0 \ar[dr]^{\check{g}_0}\\\check{G}_2 && \bar{P}\ar[dr]_{\bar{p}_4} \ar@{>->}[ur]_{\bar{p}_3}\ar@{>->}[dl]^{\bar{p}_1} \ar[ul]^{\bar{p}_2}&&\bar{G}_2&G_1 && \bar{Q}\ar[dr]_{\bar{q}_4} \ar@{>->}[ur]_{\bar{q}_3}\ar@{>->}[dl]^{\bar{q}_1} \ar[ul]^{\bar{q}_2}&&\check{G}_1\\& \mathring{D}_1 \ar[ul]^{\mathring{g}_1}&&\bar{D}_2 \ar@{>->}[ur]_{\bar{f}_2}&&& D_0 \ar[ul]^{g_0}&&\mathring{D}_1 \ar@{>->}[ur]_{\mathring{f}_1}}\]

We have to build the dotted arrows in the diagram below
	\[\xymatrix@C=15pt@R=30pt{G_0 && \ar@{>->}[ll]_{\hat{f}_0} \hat{D}_0 \ar[rr]^{\hat{g}_0}&& \hat{G}_1  && \ar@{>->}[ll]_{\tilde{f}_1} \tilde{D}_1 \ar[rr]^{\tilde{g}_1}&& G'_2 && \ar@{>->}[ll]_{f'_2} D'_2 \ar[rr]^{g'_2}&& G_3 \\
		L_2\ar[d]^{f_0\circ z_1} \ar[u]_{f'_0\circ c_1}&& K_2 \ar[u]^{\hat{k}_2}\ar[d]_{\mathring{k}_2}\ar@{>->}[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/_.35cm/[urrr]^(.4){e_0}|(.29)\hole \ar[ur]|(.28)\hole^{\hat{h}_2} \ar@/^.35cm/[drrr]_(.4){v_0}|(.29)\hole \ar@/_.2cm/[dr]|(.28)\hole_{\mathring{h}_2} && L_1 \ar@/^.35cm/[ulll]_(.4){e_1} \ar[ul]|(.28)\hole_{\hat{m}_1} \ar@/_.35cm/[dlll]^(.4){v_1} \ar[dl]|(.28)\hole^{\mathring{f}_1 \circ x_1}& K_1  \ar[u]_{\hat{k}_1}\ar[d]^{\mathring{k}_1}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){u_0}|(.29)\hole\ar@/_.2cm/[dr]_{\check{h}_1}|(.28)\hole \ar@/_.35cm/[urrr]^(.4){t_0}|(.29)\hole \ar[ur]|(.28)\hole^{\hat{g}_1\circ c_0}  && L_0\ar[ul]|(.28)\hole_{\hat{m}_0} \ar@/^.35cm/[ulll]_(.4){t_1} \ar@/_.35cm/[dlll]^(.4){u_1} \ar[dl]^{\mathring{m}_0}& K_0 \ar[d]_{\mathring{k}_0}\ar[u]^{\hat{k}_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[u]^{g_2\circ b_0}\ar[d]_{\check{g}_2\circ x_0} \\G_0 \ar@/^.3cm/[uu]^{\id{G_0}}&& \ar@{>->}[ll]^{\check{f}_0} \check{D}_0 \ar@{.>}@/_.3cm/[uu]_(.3){\phi_{0}}|\hole  \ar[rr]_{\check{g}_0}&& \check{G}_1  \ar@{.>}@/_.0cm/[uu]^(.2){\psi_{1}}|(.43)\hole |(.57)\hole  && \ar@{>->}[ll]^{\bar{f}_1} \bar{D}_1 \ar@{.>}@/^.3cm/[uu]^(.3){\phi_{1}}|\hole \ar[rr]_{\bar{g}_1}&& \bar{G}_2 \ar@{.>}@/_.0cm/[uu]^(.2){\psi_{2}}|(.43)\hole |(.57)\hole && \ar@{>->}[ll]^{\bar{f}_2} \ar@{.>}@/_.4cm/[uu]_(.3){\phi_{2}}|\hole \bar{D}_2 \ar[rr]_{\bar{g}_2}&& G_3 \ar@{.>}@/_.3cm/[uu]_{\psi_{3}} }\]

	Now, we have already proved that $f_0\circ z_1=f'_0\circ c_1$, thus by \Cref{prop:unique} we have isomorphisms $\phi_{0}\colon \check{D}_0\to \hat{D}_0$ and $\psi_{1}\colon \check{G}_1\to \hat{G}_1$.
	Notice that
	\[
	\hat{f}_0\circ \phi_{0}\circ v_1  = \check{f}_0\circ v_1 =\check{f}_0\circ \check{q}_3\circ v'_1=f_0\circ \check{q}_1\circ v'_1=f_0\circ i_1=\hat{f}_0\circ e_1\]
Thus, using the fact that $\hat{f}_0$ is mono, we can conclude that $\phi_0\circ v_1=e_1$. Thus we have
\[\psi_1\circ \mathring{f}\circ x_1=\psi_1\circ \check{g}_0\circ v_1= \hat{g}_0\circ \phi_0\circ v_1=\hat{g}_0\circ e_1=\hat{m}_1 \]
	 \Cref{prop:unique} now yields the $\phi_1\colon \bar{D}_1\to\tilde{D}_1$ and $\psi_2\colon \bar{G}_2\to G'_2$.  We can compute to get
	 \[
	 \tilde{f}_1\circ \phi_1\circ v_0=\psi_1\circ \bar{f}_1\circ v_0=\psi_1\circ \mathring{h}_2=\hat{h}_2=\tilde{f}_1\circ e_0\]
	 Hence $\phi_1\circ v_0=e_0$. On the other hand, notice that
	 \[\hat{f}_0\circ s_4\circ t'_1=f'_0\circ s_1\circ t'_1=f'_0\circ a_1=m_0=\check{f}\circ y_1=\hat{f}_0\circ \phi_0\circ y_1\]
	 Yielding $s_4\circ t'_1=\phi_0\circ y_1$. But then
	 \begin{align*}
&\tilde{f}_1\circ \phi_1\circ u_1=\psi_1\circ \bar{f}_1\circ u_1=\psi_1\circ \check{m}_0= \psi_1\circ \check{g}_0\circ y_1\\=&\hat{g}_0\circ \phi_0\circ y_1=\hat{g}_0\circ s_4\circ t'_1=\tilde{f}_1\circ s_3\circ t'_1=\tilde{f}_1\circ t_1 
	 \end{align*}

	 In turn, the previous identity entails that
	\[\psi_2\circ \mathring{m}_0=\psi_2\circ \bar{g}_1\circ u_1 = \tilde{g}_1\circ \phi_1\circ u_1 = \tilde{g}_1\circ t_1=\hat{m}_0\]

	We can use \Cref{prop:unique} a third time to get $\phi_2\colon \bar{D}_2\to D'_2$ and $\psi_3\colon G_3\to G_3$.  Now, as a last computation, we have
	\[f'_2\circ t_0= \hat{g}_2\circ c_0=\psi_2\circ h_1=\psi_2\circ \bar{f}_2\circ u_0=f'_2\circ \phi_2\circ u_0\]
	Therefore $\phi_2\circ u_0=t_0$ and this concludes the proof.
\end{proof}

We next prove some technical lemma that will be useful to show the
possibility of transforming a derivation into a switch equivalent one
by switching steps only along inversions.

\begin{lemma}
  \label{le:switchA}
  Let $\der{D}_i$ for $i \in \interval[0]{n}$ be derivation sequences
  and consider a switching sequence consisting only of inversions
  \begin{center}
    $\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
    \shift{\nu_n} \der{D}_n$
  \end{center}
  Let $i \in \interval{n}$ be such that
  $\transp{i} \in \inv{\nu_{1,n}}$ and for all $k > i+1$ it holds
  $\nu_{1,n}(k) > \nu_{1,n}(i+1)$.  Then there is a switching sequence
  consisting only of inversions that starts with $\transp{i}$, i.e.
  \begin{center}
    $\der{D}_0 \shift{\transp{i}} \der{D}_1' \shift{\nu_2'} \ldots
    \shift{\nu_n'} \der{D}_n$
  \end{center}
\end{lemma}

\begin{proof}
  We proceed by induction on $n$. If $n=1$, necessarily
  $\nu_1 =  \transp{i}$ and we are done.

  If $n>1$, let $\nu_1 = \transp{j}$.  We need three cases,
  depending on how $\nu_1$ relates to $\transp{i}$.

  \bigskip
  \noindent
  (1) $j=i$\\
  %
  In this case there is nothing to prove: $\nu_1 = \transp{i}$, hence
  the original switching sequence is already of the desired shape.

  \bigskip
  \noindent
  (2) $j<i-1$ or $j>i-1$\\
  %
  In this case $\nu_1$ does not ``interfere'' with $\transp{i}$, i.e.~$i$ still satisfies the hypotheses of the lemma with respect to the
  switching sequence
  $\der{D}_1 \shift{\nu_2} \ldots \shift{\nu_n} \der{D}_n$.

  Hence we apply the inductive hypothesis and derive the existence
  of a switching sequence
  \begin{center}
    $\der{D}_1 \shift{\transp{i}} \der{D}_2' \shift{\nu_3'} \ldots \shift{\nu_n'} \der{D}_n$
  \end{center}

  Recall that $\der{D}_0 \shift{\nu_1} \der{D}_1$ and, given the
  working assumption (ii), the switches $\nu_1$ and $\transp{i}$ can
  be done in reverse order, thus getting, as desired
  \begin{center}
    $\der{D}_0 \shift{\transp{i}} \der{D}_1' \shift{\nu_1} \ldots
    \shift{\nu_n'} \der{D}_n$
  \end{center}

  \bigskip
  \noindent
  (3) $j=i-1$, i.e., $\nu_1 = \transp{i-1}[i]$\\
  %
  In this case $\der{D}_1$ is obtained from $\der{D}_0$ by switching
  steps $i-1$ and $i$, as pictorially reported in the first two
  columns of Fig.~\ref{fi:switchA}. Since we are dealing with
  switching sequence consisting only of inversions and by hypothesis
  $\nu_{1,n}(i) > \nu_{1,n}(i+1)$, whence
  $\nu_{2,n}(i-1) > \nu_{2,n}(i+1)$, we deduce that necessarily
  $\nu_{2,n}(i) > \nu_{2,n}(i+1)$ and $\nu_{2,n}(k) > \nu_{2,n}(i+1)$
  for all $k > i+1$. Hence we can use the inductive hypothesis to
  deduce that the switching sequence from $\der{D}_1$ can start by
  switching $\transp{i}$, i.e.~we obtain (see the third column in
  Fig.~\ref{fi:switchA})
  \begin{center}
    $\der{D}_1 \shift{\transp{i}} \der{D}_2' \shift{\nu_3'} \ldots
    \shift{\nu_n'} \der{D}_n$
  \end{center}

  Now, if we focus on $\der{D}_2'$ we observe that
  $\nu_{3,n}'(i-1) > \nu_{3,n}'(i)$ and
  $\nu_{3,n}'(k) > \nu_{3,n}'(i)$ for all $k > i$. Hence we can apply
  again the inductive hypothesis and get a switching sequence
    \begin{center}
    $\der{D}_2' \shift{\transp{i-1}[i]} \der{D}_3'' \shift{\nu_3''} \ldots
    \shift{\nu_n''} \der{D}_n$
  \end{center}
  as depicted in Fig.~~\ref{fi:switchA}, starting from the fourth column.

  By Lemma~\ref{lem:indep-global-left}(\ref{lem:indep-global-left:1})
  we can reorganise the first three switchings as

  \begin{center}
    $\der{D}_0 \shift{\transp{i}} \der{D}_1'''
    \shift{\transp{i-1}[i]} \der{D}_2'''
    \shift{\transp{i}} \der{D}_3''$
  \end{center}

  The fact that the three switchings above lead to $\der{D}_3''$ is a
  consequence of Lemma~\ref{lem:switch-confluence}.

  \bigskip

  Note that it cannot be $j=i+1$, otherwise we would have
  $\nu_{1,n}(j+1) < \nu_{1,n}(i)$, contradicting the hypotheses. Thus
  this case can be ignored and the proof is completed.  
\end{proof}

\begin{figure}
  \centering
  \begin{tikzpicture}[font=\small]
    % Define arrow colors
    \def\colorA{green!60!black}
    \def\colorB{blue}
    \def\colorC{red!100}

    % Define the length of each line
    \def\vlen{5mm}
    \def\hlen{18mm}
    \def\gap{1mm}

    % First line D0 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Draw label on top of the line
    \node[above] at (0*\hlen,0) {$\der{D}_0$};
    \node[above] at (0.5*\hlen,0) {$\shift{\nu_1}$};

    % Draw the black part of the line
    \draw (0*\hlen,0) -- (0*\hlen,-2*\vlen+\gap);

    % Draw the first colored labeled arrow
    \draw[->, \colorA] (0*\hlen,-2*\vlen) -- (0*\hlen,-3*\vlen+\gap) node[midway, left] {$i-1$};
    % Draw the second colored labeled arrow
    \draw[->, \colorB] (0*\hlen,-3*\vlen) -- (0*\hlen,-4*\vlen+\gap) node[midway, left] {$i$};
    % Draw the third colored labeled arrow
    \draw[->, \colorC] (0*\hlen,-4*\vlen) -- (0*\hlen,-5*\vlen+\gap) node[midway, left] {$i+1$};
    % Draw the last black part of the line
    \draw (0*\hlen,-5*\vlen) -- (0*\hlen,-7*\vlen);

    % Second line D1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Draw label on top of the line
    \node[above] at (1*\hlen,0) {$\der{D}_1$};
    \node[above] at (1.5*\hlen,0) {$\shift{\transp{i}}$};

    % Draw the black part of the line
    \draw (1*\hlen,0) -- (1*\hlen,-2*\vlen+\gap);

    % Draw the first colored labeled arrow
    \draw[->, \colorB] (1*\hlen,-2*\vlen) -- (1*\hlen,-3*\vlen+\gap) node[midway, left] {};
    % Draw the second colored labeled arrow
    \draw[->, \colorA] (1*\hlen,-3*\vlen) -- (1*\hlen,-4*\vlen+\gap) node[midway, left] {};
    % Draw the third colored labeled arrow
    \draw[->, \colorC] (1*\hlen,-4*\vlen) -- (1*\hlen,-5*\vlen+\gap) node[midway, left] {};
    % Draw the last black part of the line
    \draw (1*\hlen,-5*\vlen) -- (1*\hlen,-7*\vlen);

    % Repeat similar patterns for the third and fourth lines

    % Third line: d2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \node[above] at (2*\hlen,0) {$\der{D}_2'$};
    \node[above] at (2.5*\hlen,0) {$\shift{\transp{i-1}[i]}$};

    \draw (2*\hlen,0) -- (2*\hlen,-2*\vlen+\gap);

    \draw[->, \colorB] (2*\hlen,-2*\vlen) -- (2*\hlen,-3*\vlen+\gap) node[midway, left] {};
    \draw[->, \colorC] (2*\hlen,-3*\vlen) -- (2*\hlen,-4*\vlen+\gap) node[midway, left] {};
    \draw[->, \colorA] (2*\hlen,-4*\vlen) -- (2*\hlen,-5*\vlen+\gap) node[midway, left] {};
    \draw (2*\hlen,-5*\vlen) -- (2*\hlen,-7*\vlen);

    % Fourth line %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \node[above] at (3*\hlen,0) {$\der{D}_3''$};
    \node[above] at (3.5*\hlen,0) {$\shift{\nu_3''}$};

    \draw (3*\hlen,0) -- (3*\hlen,-2*\vlen+\gap);
    \draw[->, \colorC] (3*\hlen,-2*\vlen) -- (3*\hlen,-3*\vlen+\gap) node[midway, left] {};
    \draw[->, \colorB] (3*\hlen,-3*\vlen) -- (3*\hlen,-4*\vlen+\gap) node[midway, left] {};
    \draw[->, \colorA] (3*\hlen,-4*\vlen) -- (3*\hlen,-5*\vlen+\gap) node[midway, left] {};
    \draw (3*\hlen,-5*\vlen) -- (3*\hlen,-7*\vlen);

    % Dots after the last line
    \draw (4*\hlen,0*\vlen) node[above] {$\dots$};

    % Last line %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \node[above] at (5*\hlen,0) {$\der{D}_n$};
    \node[above] at (4.5*\hlen,0) {$\shift{\nu_{n-1}}$};

  \end{tikzpicture}
  \caption{Picture for the proof of Lemma~\ref{le:switchA}}
  \label{fi:switchA}
\end{figure}

\begin{remark}
  \label{rem:switchA}
  Observe that given a switching sequence as in the lemma above
  $\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
  \shift{\nu_n} \der{D}_n$, if we consider the inversion with largest index
  \begin{center}
    $k = \max \{j \mid \transp{j} \in \inv{\nu_{1,n}}\}$
  \end{center}
  then it satisfies the hypotheses of the lemma.
\end{remark}

\begin{lemma}
  \label{le:switchB}
  Let $\der{D}_i$ for $i \in \interval[0]{n}$ be derivation sequences
  and consider a switching sequence consisting only of inversions
  \begin{center}
    $\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
    \shift{\nu_n} \der{D}_n$
  \end{center}
  Let $i \in \interval{n}$ be such that
  $\transp{i} \in \inv{\nu_{1,n}}$ and assume that steps $i$ and $i+1$ in $\der{D}_0$ are sequentially independent. Then there is a switching sequence
  consisting only of inversions that starts with $\transp{i}$, i.e.,
  \begin{center}
    $\der{D}_0 \shift{\transp{i}} \der{D}_1' \shift{\nu_2'} \ldots
    \shift{\nu_n'} \der{D}_n$
  \end{center}
\end{lemma}

\begin{proof}
  We proceed by induction on $n$. If $n=1$, necessarily
  $\nu_1 =  \transp{i}$ and we are done.

  If $n>1$, take $k = \max \{j \mid \transp{j} \in \inv{\nu_{1,n}}\}$, which,
  as observed in Remark~\ref{rem:switchA}, satisfies the hypotheses of
  Lemma~\ref{le:switchA}. Hence, by the mentioned lemma, we can start
  the switching sequence with the transposition $\transp{k}$, thus
  obtaining
  \begin{center}
    $\der{D}_0 \shift{\transp{k}} \der{D}_1' \shift{\nu_2'} \ldots
    \shift{\nu_n'} \der{D}_n$
  \end{center}

  Moreover, since $\transp{i}$ is an inversion, we have that
  $\i \leq k$.  We distinguish various case depending on how $k$
  relates to $i$.

  \bigskip
  \noindent
  (i) $j=i$\\
  %
  In this case we are done: $\nu_1' = \transp{i}$, hence we obtained a
  switching sequence of the desired shape.

  \bigskip
  \noindent
  (ii) $k > i+1$\\
  %
  In this case the switching $\transp{k}$ does not ``interfere'' with
  $\transp{i}$, as depicted in Fig.~\ref{fi:switchB1} (first two
  columns).

  Hence if we focus on
  \begin{center}
    $\der{D}_1' \shift{\nu_2'} \ldots
    \shift{\nu_n'} \der{D}_n$
  \end{center}
  we can observe that
  $\nu_{2,n}'(i)=\nu_{1,n}(i) > \nu_{1,n}(i+1)=\nu_{2,n}'(i+1)$.
  %
  Thus we can use the inductive hypothesis and obtain (see
  Fig.~\ref{fi:switchB1}, third column)
  \begin{center}
    $\der{D}_1' \shift{\transp{i}} \der{D}_2'' \shift{\nu_3''} \ldots
    \shift{\nu_n''} \der{D}_n$
  \end{center}

\begin{figure}
  \centering
  \begin{tikzpicture}[font=\small]
    % Define arrow colors
    \def\colorA{red!100}
    \def\colorB{blue}
    \def\colorC{green!60!black}
    \def\colorD{orange!60!black}

    % Define the length of each line
    \def\vlen{5mm}
    \def\hlen{20mm}
    \def\gap{1mm}

    % First line D0 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Draw label on top of the line
    \node[above] at (0*\hlen,0) {$\der{D}_0$};
    \node[above] at (0.5*\hlen,0) {$\shift{\transp{k}}$};

    % Draw the black part of the line
    \draw (0*\hlen,0) -- (0*\hlen,-1*\vlen+\gap);

    % Draw the first colored labeled arrow
    \draw[->, \colorA] (0*\hlen,-1*\vlen) -- (0*\hlen,-2*\vlen+\gap) node[midway, left] {$i$};
    % Draw the second colored labeled arrow
    \draw[->, \colorB] (0*\hlen,-2*\vlen) -- (0*\hlen,-3*\vlen+\gap) node[midway, left] {$i+1$};
    % Draw the second black part of the line
    \draw (0*\hlen,-3*\vlen) -- (0*\hlen,-4*\vlen+\gap);

    % Draw the third colored labeled arrow
    \draw[->, \colorC] (0*\hlen,-4*\vlen) -- (0*\hlen,-5*\vlen+\gap) node[midway, left] {$k$};
    % Draw the fourth colored labeled arrow
    \draw[->, \colorD] (0*\hlen,-5*\vlen) -- (0*\hlen,-6*\vlen+\gap) node[midway, left] {$k+1$};
    % Draw the last black part of the line
    \draw (0*\hlen,-6*\vlen) -- (0*\hlen,-7*\vlen);

    % Second line D1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Draw label on top of the line
    \node[above] at (1*\hlen,0) {$\der{D}_1'$};
    \node[above] at (1.5*\hlen,0) {$\shift{\nu_2'}$};

    % Draw the black part of the line
    \draw (1*\hlen,0) -- (1*\hlen,-1*\vlen+\gap);

    % Draw the first colored labeled arrow
    \draw[->, \colorA] (1*\hlen,-1*\vlen) -- (1*\hlen,-2*\vlen+\gap) node[midway, left] {};
    % Draw the second colored labeled arrow
    \draw[->, \colorB] (1*\hlen,-2*\vlen) -- (1*\hlen,-3*\vlen+\gap) node[midway, left] {};
    % Draw the second black part of the line
    \draw (1*\hlen,-3*\vlen) -- (1*\hlen,-4*\vlen+\gap);

    % Draw the third colored labeled arrow
    \draw[->, \colorD] (1*\hlen,-4*\vlen) -- (1*\hlen,-5*\vlen+\gap) node[midway, left] {};
    % Draw the fourth colored labeled arrow
    \draw[->, \colorC] (1*\hlen,-5*\vlen) -- (1*\hlen,-6*\vlen+\gap) node[midway, left] {};
    % Draw the last black part of the line
    \draw (1*\hlen,-6*\vlen) -- (1*\hlen,-7*\vlen);

    % Third line D2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Draw label on top of the line
    \node[above] at (2*\hlen,0) {$\der{D}_2''$};
    \node[above] at (2.5*\hlen,0) {$\shift{\nu_3''}$};

    % Draw the black part of the line
    \draw (2*\hlen,0) -- (2*\hlen,-1*\vlen+\gap);

    % Draw the first colored labeled arrow
    \draw[->, \colorB] (2*\hlen,-1*\vlen) -- (2*\hlen,-2*\vlen+\gap) node[midway, left] {};
    % Draw the second colored labeled arrow
    \draw[->, \colorA] (2*\hlen,-2*\vlen) -- (2*\hlen,-3*\vlen+\gap) node[midway, left] {};
    % Draw the second black part of the line
    \draw (2*\hlen,-3*\vlen) -- (2*\hlen,-4*\vlen+\gap);

    % Draw the third colored labeled arrow
    \draw[->, \colorC] (2*\hlen,-4*\vlen) -- (2*\hlen,-5*\vlen+\gap) node[midway, left] {};
    % Draw the fourth colored labeled arrow
    \draw[->, \colorD] (2*\hlen,-5*\vlen) -- (2*\hlen,-6*\vlen+\gap) node[midway, left] {};
    % Draw the last black part of the line
    \draw (2*\hlen,-6*\vlen) -- (2*\hlen,-7*\vlen);

    % Dots after the last line
    \draw (3*\hlen,0*\vlen) node[above] {$\dots$};

    % Last line %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \node[above] at (4*\hlen,0) {$\der{D}_n$};
    \node[above] at (3.5*\hlen,0) {$\shift{\nu_{n-1}''}$};

  \end{tikzpicture}
  \caption{Picture for the proof of Lemma~\ref{le:switchB}, item (ii)}
  \label{fi:switchB1}
\end{figure}

  Now, since $k>i+1$, the switchings $\transp{i}$ and $\transp{k}$ can
  be performed in reverse order and thus we obtain
  \begin{center}
    $\der{D}_0 \shift{\transp{i}} \der{D}_1'' \shift{\transp{k}}
    \der{D}_2'' \shift{\nu_3''} \ldots \shift{\nu_n''} \der{D}_n$
  \end{center}
  as desired.

  \bigskip
  \noindent
  (iii) $k = i+1$\\
  %
  The situation is depicted in Fig.~\ref{fi:switchB2}. In
  $\der{D}_1'$, by the choice of $k$ and the fact that all $\nu_i$ are
  inversions, one can deduce that $i$ satisfies the hypotheses of
  Lemma~\ref{le:switchA}. Hence we obtain (see Fig.~\ref{fi:switchB2}, first two columns)
  \begin{center}
    $\der{D}_1' \shift{\transp{i}} \der{D}_2'' \shift{\nu_2''}
    \der{D}_3'' \shift{\nu_4''} \ldots \shift{\nu_n''} \der{D}_n$
  \end{center}

  Since in $\der{D}_0$ steps in positions $i$ and $i+1$ are sequentially
  independent, we can use
  Lemma~\ref{lem:indep-global-left}(\ref{lem:indep-global-left:1}) and
  we have that the corresponding steps in positions $i+1$ and $i+2$ in
  $\der{D}_2''$ are still sequentially independent. Hence, we can use
  the inductive hypothesis on $\der{D}_2''$ and deduce the existence
  of a switching sequence where $\transp{i+1}[i+2]$ can be switched
  first, i.e.~we obtain (see Fig.~\ref{fi:switchB2}, third column)
  \begin{center}
    $\der{D}_2'' \shift{\transp{i+1}[i+2]}
    \der{D}_3''' \shift{\nu_4'''} \ldots \shift{\nu_n'''} \der{D}_n$
  \end{center}

  Putting things together, we obtain
  \begin{center}
    $\der{D}_0 \shift{\transp{i+1}[i+2]} \der{D}_1' \shift{\transp{i}}
    \der{D}_2'' \shift{\transp{i+1}[i+2]} \der{D}_3''' \shift{\nu_4'''}\ldots \shift{\nu_n'''} \der{D}_n$
  \end{center}
  Since we additionally know that in $\der{D}_0$ the steps $i$ and
  $i+1$ are sequentially independent, we can use
  Lemma~\ref{lem:indep-global-left}(\ref{lem:indep-global-left:2}) to
  reorder the first three switchings, obtaining
  \begin{center}
    $\der{D}_0 \shift{\transp{i}} \der{D}_1' \shift{\transp{i+1}[i+2]}
    \der{D}_2'' \shift{\transp{i}} \der{D}_3''' \shift{\nu_4'''}\ldots \shift{\nu_n'''} \der{D}_n$
  \end{center}
  as desired.  The fact that the three switchings above lead to
  $\der{D}_3'''$ is a consequence of Lemma~\ref{lem:switch-confluence}.
\end{proof}

\begin{figure}
  \centering
  \begin{tikzpicture}[font=\small]
    % Define arrow colors
    \def\colorA{red!100}
    \def\colorB{blue}
    \def\colorC{green!60!black}

    % Define the length of each line
    \def\vlen{5mm}
    \def\hlen{22mm}
    \def\gap{1mm}

    % First line D0 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Draw label on top of the line
    \node[above] at (0*\hlen,0) {$\der{D}_0$};
    \node[above] at (0.5*\hlen,0) {$\shift{\transp{i+1}[i+2]}$};

    % Draw the black part of the line
    \draw (0*\hlen,0) -- (0*\hlen,-2*\vlen+\gap);

    % Draw the first colored labeled arrow
    \draw[->, \colorA] (0*\hlen,-2*\vlen) -- (0*\hlen,-3*\vlen+\gap) node[midway, left] {$i$};
    % Draw the second colored labeled arrow
    \draw[->, \colorB] (0*\hlen,-3*\vlen) -- (0*\hlen,-4*\vlen+\gap) node[midway, left] {$k=i+1$};
    % Draw the third colored labeled arrow
    \draw[->, \colorC] (0*\hlen,-4*\vlen) -- (0*\hlen,-5*\vlen+\gap) node[midway, left] {$i+2$};
    % Draw the last black part of the line
    \draw (0*\hlen,-5*\vlen) -- (0*\hlen,-7*\vlen);

    % Second line D1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    % Draw label on top of the line
    \node[above] at (1*\hlen,0) {$\der{D}_1'$};
    \node[above] at (1.5*\hlen,0) {$\shift{\transp{i}}$};

    % Draw the black part of the line
    \draw (1*\hlen,0) -- (1*\hlen,-2*\vlen+\gap);

    % Draw the first colored labeled arrow
    \draw[->, \colorA] (1*\hlen,-2*\vlen) -- (1*\hlen,-3*\vlen+\gap) node[midway, left] {};
    % Draw the second colored labeled arrow
    \draw[->, \colorC] (1*\hlen,-3*\vlen) -- (1*\hlen,-4*\vlen+\gap) node[midway, left] {};
    % Draw the third colored labeled arrow
    \draw[->, \colorB] (1*\hlen,-4*\vlen) -- (1*\hlen,-5*\vlen+\gap) node[midway, left] {};
    % Draw the last black part of the line
    \draw (1*\hlen,-5*\vlen) -- (1*\hlen,-7*\vlen);

    % Repeat similar patterns for the third and fourth lines

    % Third line: d2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \node[above] at (2*\hlen,0) {$\der{D}_2''$};
    \node[above] at (2.5*\hlen,0) {$\shift{\transp{i+1}[i+2]}$};

    \draw (2*\hlen,0) -- (2*\hlen,-2*\vlen+\gap);

    \draw[->, \colorC] (2*\hlen,-2*\vlen) -- (2*\hlen,-3*\vlen+\gap) node[midway, left] {};
    \draw[->, \colorA] (2*\hlen,-3*\vlen) -- (2*\hlen,-4*\vlen+\gap) node[midway, left] {};
    \draw[->, \colorB] (2*\hlen,-4*\vlen) -- (2*\hlen,-5*\vlen+\gap) node[midway, left] {};
    \draw (2*\hlen,-5*\vlen) -- (2*\hlen,-7*\vlen);

    % Fourth line %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \node[above] at (3*\hlen,0) {$\der{D}_3'''$};
    \node[above] at (3.5*\hlen,0) {$\shift{\nu_3'''}$};

    \draw (3*\hlen,0) -- (3*\hlen,-2*\vlen+\gap);
    \draw[->, \colorC] (3*\hlen,-2*\vlen) -- (3*\hlen,-3*\vlen+\gap) node[midway, left] {};
    \draw[->, \colorB] (3*\hlen,-3*\vlen) -- (3*\hlen,-4*\vlen+\gap) node[midway, left] {};
    \draw[->, \colorA] (3*\hlen,-4*\vlen) -- (3*\hlen,-5*\vlen+\gap) node[midway, left] {};
    \draw (3*\hlen,-5*\vlen) -- (3*\hlen,-7*\vlen);

    % Dots after the last line
    \draw (4*\hlen,0*\vlen) node[above] {$\dots$};

    % Last line %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \node[above] at (5*\hlen,0) {$\der{D}_n$};
    \node[above] at (4.5*\hlen,0) {$\shift{\nu_{n-1}'''}$};

  \end{tikzpicture}
  \caption{Picture for the proof of Lemma~\ref{le:switchB} (item (iii))}
  \label{fi:switchB2}
\end{figure}

The next lemma intuitively states that if we have a switching sequence
where the first switch is applied to $\transp{i}$ and the last one
reverses the same switch, then, assuming that in the middle there are
only inversions, we can strip the first and last switches.

\begin{lemma}
  \label{le:switchC}
  Let $\der{D}_i$ for $i \in \interval[0]{n+1}$ be derivation sequences
  and consider a switching sequence
  \begin{center}
    $\der{D}_0 \shift{\nu_0} \der{D}_1 \shift{\nu_1} \ldots
     \der{D}_n \shift{\nu_n} \der{D}_{n+1}$
  \end{center}
  If the subsequence starting from $\der{D}_1$ consists of
  inversions and $\nu_0=\transp{i}$ while
  $\nu_n = \transp{\nu_{1,n}(i)}$, then there is shorter switching sequence
  consisting only of inversions
  \begin{center}
    $\der{D}_0 \equiv_a \der{D}_0' \shift{\nu_2'} \der{D}_3' \shift{\nu_3'} \ldots
    \shift{\nu_{n-1}'} \der{D}_n'$
  \end{center}
\end{lemma}

\begin{proof}
  Just observe that in $\der{D}_1$ the steps of position $i$ and $i+1$
  are sequentially independent and $\nu_{1,n}(i) >
  \nu_{1,n}(i+1)$. Hence we can use Lemma~\ref{le:switchB} and obtain
  a switching sequence from $\der{D}_1$ where $\transp{i}$ is
  performed first, hence we obtain
  \begin{center}
    $\der{D}_0 \shift{\transp{i}}
    \der{D}_1 \shift{\transp{i}}
    \der{D}_2' \shift{\nu_2'} \ldots
    \shift{\nu_n'} \der{D}_{n+1}$
  \end{center}

  Now, switching $\transp{i}$ twice one obtains a derivation
  which is abstraction equivalent to the starting one.  Hence we have
  \begin{center}
    $\der{D}_0 \equiv_a
    \der{D}_2' \shift{\nu_2'} \ldots
    \shift{\nu_n'} \der{D}_{n+1}$
  \end{center}
  as desired.
\end{proof}

\begin{lemma}
  \label{le:switchD}
  Let $\der{D}_i$ for $i \in \interval[0]{n+1}$ be derivation sequences
  and consider a switching sequence
  \begin{center}
    $\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
    \shift{\nu_n}\der{D}_n$
  \end{center}
  If the switching sequence does not consists only of inversions,
  there is a shorter switching sequence relating
  $\der{D}_0' \equiv_a \der{D}_0$ and $\der{D}_n$.
\end{lemma}

\begin{proof}
  Take a maximal subsequence
  $\der{D}_i \shift{\nu_{i+1}} \der{D}_{i+1} \shift{\nu_{i+2}} \ldots
  \shift{\nu_j}\der{D}_j$ consisting only of inversions.
  %
  If $i=0$ and $j=n$, there is nothing to show. Hence assume that
  $i>0$ and consider the sequence
  \begin{center}
    $\der{D}_{i-1} \shift{\nu_{i}} \der{D}_{i} \shift{\nu_{i+1}} \ldots
    \shift{\nu_j}\der{D}_j$
  \end{center}
  Then, by maximality, if $\nu_{i-1}=\transp{k}$ it must hold that
  $\nu_{j}=\transp{\nu_{i,j}(i)}$. Then, by Lemma~\ref{le:switchC},
  the switching sequence from $\der{D}_{i-1}$ to $\der{D}_{j}$ can be
  shortened by $2$, i.e.
  \begin{center}
    $\der{D}_{i-1} \equiv_a \der{D}_{i+1}' \shift{\nu_{i+1}'} \ldots
    \shift{\nu_j'}\der{D}_j$
  \end{center}
  and thus the same applies to the original switching sequence.
\end{proof}

\thNoNeed*
\label{thNoNeed-proof}

\begin{proof}
  Let $\der{D} \shifteq \der{D}'$. Then there is a switching
  sequence
  \begin{center}
    $\der{D} \equiv_a \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
    \shift{\nu_n} \der{D}_n \equiv_a \der{D}'$
  \end{center}
  If it does not consist only of inversions, by Lemma~\ref{le:switchD}
  we can reduce its length by $2$. An inductive reasoning allows us to
  conclude.
\end{proof}

\coCanonical*
\label{coCanonical-proof}

\begin{proof}
  Immediate consequence of Theorem~\ref{th:no-need} and Lemma~\ref{le:switchA}.
\end{proof}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2024-08-15 quozienti.tex
inserite unioni e parte sui sistemi di fattorizzazioni

\documentclass[a4paper]{article}
\usepackage{hyperref}
\usepackage[textsize=tiny]{todonotes}
%\usepackage{etex}
\usepackage[all]{xy}
\SelectTips{cm}{}
% derivations and labels
\usepackage{proof}
\newcommand{\lab}[1]{\ensuremath{\mathsf{{#1}}}}
\newcommand{\slab}[1]{\ensuremath{\scriptstyle{\mathsf{{#1}}}}}

\newcommand{\sub}[3]{{\mathcal{#1}}\textrm{-}\mathsf{Sub}_{\textbf {\textup{#2}}}(#3)}

\newcommand{\msub}[2]{\mathsf{Sub}_{\textbf {\textup{#1}}}(#2)}

%frecce
\newcommand{\mor}{\mathsf{Mor}}
\newcommand{\mon}{\mathsf{Mono}}
\newcommand{\reg}{\mathsf{Reg}}

% ``boxed'' \infer command
\newcommand{\binfer}[3][]{
  \mbox{\infer[#1]{#2}{#3}}}

% Command for labels on the left side of the rule
%       \inferL{<name>}{<post>}{<pre>}
% generates:
%             <pre>
%      <name> ------
%             <post>
%
\newlength{\myheight}
\newcommand{\inferL}[3]
  {\settoheight{\myheight}{\mbox{${#2}$}}
   \raisebox{\myheight}{{#1}}
   \makebox[1mm]{}
   \mbox{\infer{#2}{#3}}
}

\usepackage{amssymb,graphicx,epsfig,color}
%\usepackage[scriptsize]{subfigure}
\usepackage{subcaption}
\usepackage{wrapfig}

% re-stating 
%\usepackage{thm-restate}

% showing labels
%\usepackage[inline]{showlabels}

\usepackage{pgf}
\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri,fit,positioning}
\tikzstyle{node}=[circle, draw=black, minimum size=1mm]
\tikzstyle{trans}=[font=\scriptsize]
\tikzstyle{lab}=[font=\small]

\newcommand{\pgfBox}{
  \begin{pgfonlayer}{background} 
    \fill[blue!2,thick,draw=black!50,rounded corners,inner sep=3mm] ([xshift=-1.5pt,yshift=-1.5pt]current bounding box.south west) rectangle ([xshift=1.5pt,yshift=1.5pt]current bounding box.north east);
  \end{pgfonlayer}
}
\usepackage{scalerel}
\newcommand{\smallmin}{\scaleobj{0.6}{-}}
\newcommand{\Deltamin}{\Delta^{\hspace{-1pt}\downarrow\hspace{-1pt}}}
\newcommand{\Rrel}[1]   {\stackrel{{#1}}{\Longrightarrow}}
\newcommand{\oa}{\overline a}
\newcommand{\ob}{\overline b}
\newcommand{\oc}{\overline c}
\newcommand{\od}{\overline d}
\newcommand{\rec}{\emph{rec}}
\newcommand{\fn}[1]{{\mathtt{fn}}(#1)}
%\usepackage{latexsym}
\usepackage{stmaryrd}
\def\encodep#1{\llfloor#1\rrfloor}

\newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}

\newcommand{\dpo}{\textsc{dpo}}

\newcommand{\cmd}{\mathbf{IC}}

\newcommand{\cori}{\mathbf{CR}}

% base classes of categories for adhesive and quasi adhesive case
\newcommand{\bAdh}{\ensuremath{\mathbb{B}}}
\newcommand{\bQAdh}{\ensuremath{\mathbb{QB}}}

%from pawel
\usepackage[latin1]{inputenc}
\usepackage{amsmath}

\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{xspace}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage{float}
\usepackage{fancybox}

\usepackage{cleveref}

%\spnewtheorem*{notation}{Notation}{\bfseries}{\rmfamily}

%%%%%%%% MATHEMATICAL NOTATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%symbol for natural numbers
\newcommand{\nat}{\ensuremath{\mathbb{N}}}

% finite subset
\newcommand{\sfin}{\ensuremath{\subseteq_{\mathit{fin}}}}

% flattening of a multiset
\newcommand{\flt}[1]{\ensuremath{[\![{#1}]\!]}}

% compact elements
\newcommand{\compact}[1]{\ensuremath{\mathop{\mathsf{K}({#1})}}}

% principal ideal
\newcommand{\principal}[1]{\ensuremath{\mathop{\downarrow\!{#1}}}}

% ideal completion
\newcommand{\ideal}[1]{\ensuremath{\mathsf{Idl}({#1})}}

% complete prime elements
\newcommand{\pr}[1]{\ensuremath{\mathop{\mathit{pr}({#1})}}}
\newcommand{\wpr}[1]{\ensuremath{\mathop{\mathit{wpr}({#1})}}}

% irreducible elements
\newcommand{\ir}[1]{\ensuremath{\mathop{\mathit{ir}({#1})}}}

% difference of irreducible elements
\newcommand{\diff}[2]{\ensuremath{\delta({#1},{#2})}}

% immediate precedence

% abbreviation for event structure
% \newcommand{\esabbr}{event structure}
\newcommand{\esabbr}{\textsc{es}}
\newcommand{\esnabbr}{\textsc{esnb}}
\newcommand{\esnmabbr}{\textsc{esn}}
\newcommand{\eseqabbr}{\textsc{epes}}

% predecessor of an irreducible
\newcommand{\pred}[1]{\ensuremath{\mathit{p}({#1})}}

% irreducible elements in es domains
\newcommand{\esir}[2]{\ensuremath{\langle{#1}, {#2}\rangle}}

% equivalence classes [of irreducibles]
\newcommand{\eqclass}[2][]{\ensuremath{[{#2}]_{\scriptscriptstyle {#1}}}}
% union of the equivalence classes of the elements in a set
\newcommand{\eqclasscup}[2]{\ensuremath{{#2}_{\scriptscriptstyle {#1}}}}

\newcommand{\eqclassir}[1]{\ensuremath{\eqclass[\leftrightarrow^*]{#1}}}

% quotient of set wrt a relation
\newcommand{\quotient}[2]{\ensuremath{{#1}_{\scriptscriptstyle {#2}}}}

% category of event structures 
\newcommand{\es}{\ensuremath{\mathsf{ES}}}
% category of stable event structures 
\newcommand{\ses}{\ensuremath{\mathsf{sES}}}
% category of prime event structures 
\newcommand{\pes}{\ensuremath{\mathsf{pES}}}
% category of prime event structures with equivalence
\newcommand{\epes}{\ensuremath{\mathsf{epES}}}

% category of connected event structures 
\newcommand{\ces}{\ensuremath{\mathsf{cES}}}

% category of weak prime algebraic domains domains 
\newcommand{\WDom}{\ensuremath{\mathsf{wDom}}}
% category of domains
\newcommand{\Dom}{\ensuremath{\mathsf{Dom}}}
% category of prime algebraic domains
\newcommand{\PDom}{\ensuremath{\mathsf{pDom}}}

%%%%% NON BINARY CONFLICT

% category of event structures 
\newcommand{\esn}{\ensuremath{\mathsf{ES_{nb}}}}
% category of stable event structures 
\newcommand{\sesn}{\ensuremath{\mathsf{sES_n}}}

% category of connected event structures 
\newcommand{\cesn}{\ensuremath{\mathsf{cES_{nb}}}}

% category of prime event structures 
\newcommand{\pesn}{\ensuremath{\mathsf{pES_n}}}

% category of fusion domains 
\newcommand{\WDomb}{\ensuremath{\mathsf{wDom_b}}}
% category of domains
\newcommand{\Domb}{\ensuremath{\mathsf{Dom_b}}}
% category of prime algebraic domains
\newcommand{\PDomb}{\ensuremath{\mathsf{pDom_b}}}

%%%%% END NON BINARY CONFLICT

% slice category
\newcommand{\slice}[2]{\ensuremath{({#1} \downarrow {#2})}}

% event structure for a domain
\newcommand{\zev}[0]{\ensuremath{\mathcal{E}}}
\newcommand{\ev}[1]{\ensuremath{\zev({#1})}}

% from general to connected event structures
\newcommand{\zconnes}[0]{\ensuremath{\mathcal{C}}}
\newcommand{\connes}[1]{\ensuremath{\zconnes({#1})}}
% and inclusion
\newcommand{\zinces}[0]{\ensuremath{\mathcal{I}}}
\newcommand{\inces}[1]{\ensuremath{\zinces({#1})}}

% stable version
\newcommand{\zsev}[0]{\ensuremath{\mathcal{E}_S}}
\newcommand{\sev}[1]{\ensuremath{\zsev({#1})}}

% with equivalence
\newcommand{\zeveq}[0]{\ensuremath{\mathcal{E}_{eq}}}
\newcommand{\eveq}[1]{\ensuremath{\zeveq({#1})}}

% es with equivalence to es and vice
\newcommand{\zfuse}[0]{\ensuremath{\mathcal{M}}}
\newcommand{\fuse}[1]{\ensuremath{\zfuse({#1})}}
\newcommand{\zunf}[0]{\ensuremath{\zunf}}
\newcommand{\unf}[1]{\ensuremath{\mathcal{U}({#1})}}

% Winskel/Droste version
\newcommand{\zevwd}[0]{\ensuremath{\mathcal{E}_{wd}}}
\newcommand{\evwd}[1]{\ensuremath{\zevwd({#1})}}

% configurations of an event structure
\newcommand{\conf}[1]{\ensuremath{\mathit{Conf}({#1})}}
% finite configurations
\newcommand{\conff}[1]{\ensuremath{\mathit{Conf_F}({#1})}}

% product of the sets of minimal enablinsg
\newcommand{\pmin}[1]{\ensuremath{U_{#1}}}

% connectectedness of minimal enablinsg
\newcommand{\conn}[1]{\ensuremath{\stackrel{#1}{\frown}}}

% domain for an event structure or graph grammar
\newcommand{\zdom}[0]{\ensuremath{\mathcal{D}}}
\newcommand{\dom}[1]{\ensuremath{\zdom({#1})}}

\newcommand{\zdomeq}[0]{\ensuremath{\mathcal{D}_{eq}}}
\newcommand{\domeq}[1]{\ensuremath{\zdomeq({#1})}}

% partial order for a graph grammar
\newcommand{\poset}[1]{\ensuremath{\mathcal{P}({#1})}}

% stable version
\newcommand{\pdom}[1]{\ensuremath{\mathcal{D}_S({#1})}}
\newcommand{\ppdom}[0]{\ensuremath{\mathcal{D}_S}}

% powerset
\newcommand{\Pow}[1]{\ensuremath{\mathbf{2}^{#1}}}

% powerset of finite subsets
\newcommand{\Powfin}[1]{\ensuremath{\mathbf{2}_\mathit{fin}^{#1}}}

% powerset of subsets of cardinality <= 1
\newcommand{\Powone}[1]{\ensuremath{\mathbf{2}_1^{#1}}}

% integer interval
\newcommand{\interval}[2][1]{\ensuremath{[{#1},{#2}]}}

% domain interval
\newcommand{\dint}[2]{\ensuremath{[{#1},{#2}]}}

% set of intervals
\newcommand{\IntSet}[1]{\ensuremath{\mathop{\mathit{Int}({#1})}}}

% intervals to irreducibles and vice
\newcommand{\inir}{\ensuremath{\mathop{\mathit{\zeta}}}}
\newcommand{\irin}{\ensuremath{\mathop{\mathit{\iota}}}}

% permutations
\newcommand{\perm}{\sigma}

% causes
\newcommand{\causes}[1]{\ensuremath{\lfloor {#1})}}

%%% GRAPH GRAMMARS

\newcommand{\Abs}[1]{\ensuremath{\mathsf{Abs}({#1})}}
\newcommand{\tr}[1]{\ensuremath{\mathsf{Tr}({#1})}}
% fusion safe traces
\newcommand{\trs}[1]{\ensuremath{\mathsf{Tr}_s({#1})}}
%\newcommand{\graph}{\ensuremath{\mathsf{Graph}}}
\newcommand{\tgraph}[1]{\ensuremath{\mathsf{Graph}_{#1}}}
\newcommand{\can}[1]{\ensuremath{\mathsf{C}({#1})}}
% source and target of a derivation
\newcommand{\source}[1]{\ensuremath{\mathsf{s}({#1})}}
\newcommand{\target}[1]{\ensuremath{\mathsf{t}({#1})}}
\newcommand{\col}[1]{\ensuremath{\mathsf{col}({#1})}}

% left decorated trace
\newcommand{\ltrace}[1]{\ensuremath{\langle {#1}\rangle_c}}

\newcommand{\bx}[1]{\phantom{\big(}#1{\phantom{\big)}}}
\newcommand{\bxx}[1]{\,#1\,}
\newcommand{\cycl}[1]{\ensuremath{\mbox{\textcircled{\scriptsize{$#1$}}}}}
\renewcommand{\iff}{\ensuremath{\Leftrightarrow}}

%%%%GENERAL CATEGORICAL NOTATION

%identità
\newcommand{\id}[1]{\mathsf{id}_{#1}}
%codominio
\newcommand{\cod}[1]{\mathsf{cod}({#1})}
	%Variabili categorie
\def\A{\textbf {\textup{A}}}
%arrows
\newcommand{\rightarrowdbl}{\rightarrow\mathrel{\mkern-14mu}\rightarrow}

\newcommand{\xrightarrowdbl}[2][]{%
	\xrightarrow[#1]{#2}\mathrel{\mkern-14mu}\rightarrow
}

\newcommand{\mini}[0]{\scalebox{.4}{$\bullet$}}
\newcommand{\mto}[0]{\rightarrowtail}
\newcommand{\rto}[0]{\xrightarrow{\mini}}
\newcommand{\fto}[0]{\xrightarrowdbl{\mini}}
\newcommand{\eto}[0]{\twoheadrightarrow}

\newcommand{\sk}{\mathsf{sk}_{\X}}

\def\R{\mathsf{R}}
\def\B{\textbf {\textup{B}}}
\def\C{\textbf {\textup{C}}}
\def\D{\textbf {\textup{D}}}
\def\X{\textbf {\textup{X}}}
\def\Y{\textbf {\textup{Y}}}
\def\Z{\textbf {\textup{Z}}}
\def\E{\textbf {\textup{E}}}
\newcommand{\m}[1]{\mathbb{#1}}

\newcommand{\ske}{\mathsf{sk}(\X)}
\renewcommand{\P}{\textbf {\textup{P}}}

%\derivazioni

\newcommand{\dder}[1]{\mathscr{#1}}
\newcommand{\sder}[2]{S_{i_1,i_2}(\mathscr{#1}, \mathscr{#2})}
\newcommand{\der}[1]{\underline{\dder{#1}}}
\def\dpo{\mathsf{C}^{\X}_R}
\def\gpo{\mathsf{G}^{\X}_R}
\def\dpi{[\mathsf{C}]^{\X}_R}
\def\gpi{[\mathsf{G}]^{\X}_R}

\newcommand{\ider}[1]{\mathscr{I}_{#1}}

%categorie
\def\Set{\textbf {\textup{Set}}}

%comma
\newcommand{\comma}[2]{#1\hspace{1pt} {\downarrow}\hspace{1pt} #2}
\newcommand{\cma}[2]{\mathcal{#1}\hspace{1pt} {\downarrow}\hspace{1pt} \mathcal{#2}}

%derivazioni
\newcommand{\lpro}{\langle \hspace{-1.85pt}[}
\newcommand{\rpro}{]\hspace{-1.85pt}\rangle}
\newcommand{\tpro}[1]{\lpro \der{#1}\rpro}
\newcommand{\tproi}[2]{\lpro \der{#1}_{#2}\rpro}
\newcommand{\lgh}[0]{\mathsf{lg}}

%%% NEW

\usepackage{xparse}

% inversions
\newcommand{\inv}[1]{\ensuremath{inv}({#1})}

% direct shift
\newcommand{\shiftdir}[1][]{\ensuremath{\mathrel{{\rightsquigarrow}^{\mathit{sh}}_{#1}}}}

% shift preorder
\newcommand{\shiftpre}[1][]{\ensuremath{\mathrel{{\sqsubseteq}^{\mathit{sh}}_{#1}}}}

% shift equivalence
\newcommand{\shifteq}[1][]{\ensuremath{\mathrel{{\equiv}^\mathit{sh}_{#1}}}}

% transp{source}[target]: if target not specified source+1
\NewDocumentCommand{\transp}{m o}{%
  \ensuremath{({#1},%
  \IfNoValueTF{#2}%
    {{#1}+1}%
    {#2}%
    )}
}

\NewDocumentCommand{\mycommand}{o}{%
  % <code>
  \IfNoValueTF{#1}
    {code when no optional argument is passed}
    {code when the optional argument #1 is present}%
  % <code>
}
% interchange
\newcommand{\IC}[1]{\ensuremath{\mathit{IC}({#1})}}

%%%%% Ambienti matematici  %%%%%%
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{notation}{Notation}
\newtheorem*{setting}{Setting}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}

\title{Switch equivalence and weak prime domains for fusions - quotients}
\author{Paolo Baldan\and Davide Castelnovo\and  Andrea Corradini\and Fabio Gadducci}

\begin{document}
\maketitle

\section{Preliminaries on subobjects, images, pullbacks and factorization systems}\label{app:fact}

This first section is devoted to recall some classic notions related to subobjects, pullbacks and ways to factorize an arrow. The main source for the presentation is \cite[Ch.~1]{dikranjan2013categorical}.
\subsection{The pullback functor and right $\mathcal{M}$-images}

Let us start defining the \emph{pullback functor} and show how the existence of a left adjoint to it yields a notion of image of an arrow.

\begin{definition}
	Let $\mathcal{M}$ be a class of arrows in a category $\X$ with $\mathcal{M}$-pullbacks. Suppose that $\mathcal{M}$ is stable under pullbacks, then given an arrow $f\colon X\to Y$, we define the \emph{pullback functor} $f^*\colon \mathcal{M}/Y\to \mathcal{M}/X$ sending an arrow $m:M\to Y$ in $\mathcal{M}$ to a chosen pullback of it along $f$. Given a morphism $g:m\to n$ in $\mathcal{M}/Y$, the arrow $f^*(g)$ is the unique one fitting in the diagram below.
	\[\xymatrix{f^*(M)  \ar[dd]_{f^*(m)} \ar@{.>}[dr]_{f^*(g)}\ar[rr]^{p_m}&& M \ar[dr]^{g}\ar[dd]^(.3){m} \\&f^*(N)  \ar[rr]^(.35){p_n}|(.55)\hole \ar[dl]_{f^*(n)}&& N \ar[dl]^{n}\\ X \ar[rr]_{f}&& Y }\]
\end{definition}

\begin{notation}
If $m\colon M\to X$ is an arrow in $\mathcal{M}$ and $f\colon X\to Y$ is another morphism, we will denote the chosen domain of $f^*(m)$ by $f^*(M)$.
\end{notation}

\begin{proposition} Let $f\colon X\to Y$ be an arrow in a category $\X$ and $\mathcal{M}$ a class of arrows stable under pullbacks and such that $f$ has a pullback along any arrow in $\mathcal{M}$. Let also $F\colon\D\to \mathcal{M}/Y$ be a diagram with a limiting cone $(l, \{l_D\}_{D\in \D})$ and suppose that  $L$ is the domain of $l$. Denoting $F(D)$ by  $m_D\colon M_D\to Y$, if  $(L, \{l_D\}_{D\in \D}+\{l\})$ is limiting for the diagram in $\X$ determined by the family of arrows $\{m_D\}_{D\in \D}$, then for every $f\colon X\to Y$, $f^*$ preserves the limit of $F$.
\end{proposition}
\begin{proof}
Let $(a, \{a_D\}_{D\in \D})$ be a cocone in $\{\mathcal{M}/X\}$ over $f^*\circ F$. Then we have the solid part of the diagram below.
\[\xymatrix{A \ar@/_.8cm/[dd]_{a}\ar[d]^{a_D}  \ar@{.>}[r]_-{b} \ar@/^.5cm/@{.>}[rrr]^{c}&f^*(L)  \ar@/^.7cm/[ddl]|(.37)\hole^(.6){f^*(l)} \ar[rr]_{q} \ar[dl]^{f^*(l_D)}&&L \ar@/^.3cm/[ddl]^{l} \ar[dl]_{l_D}\\f^*(M_D)  \ar[d]^{f^*(m_D)} \ar[rr]^(.7){p_{F(D)}}&& M_D \ar[d]_{m_D} \\ X \ar[rr]_{f}&& Y }\]

Now, notice that, for every $D\in \D$ we have
\begin{align*}
	m_D\circ p_{F(D)} \circ a_D&=f\circ f^*(m_D)\circ a_D \\&=f\circ a
\end{align*}
Moreover, given an arrow $g\colon D\to D'$ in $\D$ then we have
\begin{align*}
F(g)\circ p_{F(D)}\circ a_D&=p_{F(D')}\circ f^*(F(g))\circ a_D\\&=p_{F(D')}\circ a_{D'}
\end{align*}

Thus $(A, \{p_{F(D)}\circ a_D\}_{D\in \D}+ \{f\circ a\})$ is a cone over the diagram in $\X$ determined by $\{m_D\}_{D\in \D}$, so that we get the dotted arrow $b\colon A\to L$ in the diagram above. This arrow,  in turn, yields also $a\colon A\to f^*(L)$. Moreover, we also have that
\[
\begin{split}
	p_{F(D)}\circ f^*(l_D)\circ b&= l_D\circ q \circ b\\&=l_D\circ c\\&=p_{F(D)}\circ a_D
\end{split}\qquad 
\begin{split}
f^*(m_D) \circ f^*(l_D)\circ b&= f^*(l)\circ b\\&=a\\&=f^*(m_D)\circ a_D
\end{split}
\]
So that $b$ defines an arrow $a\to f^*(l)$ in $\mathcal{M}/X$ auch that $f^*(l_D)\circ b =a_D$

To see that $b$ is unique, let $b'\colon a\to f^*(l)$ be another arrow such that $f^*(l_D)\circ b' =a_D$, then
\[\begin{split}
l\circ q \circ b'&=f\circ f^*(l)\circ b'\\&=f\circ a\\&=l\circ c
\end{split} \qquad \begin{split}
l_D\circ q \circ b'&=p_{F(D)}\circ f^*(l_D)\circ b'\\&=p_{F(D)}\circ a_D\\&=l_D\circ c
3\end{split}\]
Thus $q\circ b'=c$, implying that $b'=b$.
\end{proof}

The previous theorem gives us at once the following result.

\begin{corollary} \label{cor:finlim}
 Let $f\colon X\to Y$ be an arrow in a category $\X$ and $\mathcal{M}$ a class of arrows stable under pullbacks and such that $f$ has a pullback along any arrow in $\mathcal{M}$. Then $f^*$ preserves binary products. If, moreover, $\id{Y}$ belongs to $\mathcal{M}$ then $f^*$ preserves finite products.
\end{corollary}

Having examined the continuity properties of the pullback functor we can now turn to the notion of \emph{right $\mathcal{M}$-images}.

\begin{definition}
Let $\mathcal{M}$ be a class of arrows in a category $\X$. A \emph{right $\mathcal{M}$-factorization
} of a morphism $f\colon X\to Y$ is a pair of arrows $m\colon M\to Y$ and $e\colon X\to M$ such that:
\begin{enumerate}
	\item $m$ belongs to $\mathcal{M}$ and $f=m\circ e$;
	\item given an arrow $n\colon N\to Z$ in $\mathcal{M}$ and two morphisms $g\colon Y\to Z$, $h\colon X\to N$ makint the solid part of the diagram below commutative, then there exists a unique dotted $v\colon M\to N$ fitting in it.
	\[\xymatrix{X \ar[r]_-{e} \ar@/^.4cm/[rr]^{f} \ar[d]_{h}& M \ar[r]_-{m} \ar@{.>}[dl]^{v} & Y \ar[d]^{g}\\N \ar[rr]_{n} && Z}\] 
\end{enumerate}

The arrow $m$ will be called the \emph{right $\mathcal{M}$-image} of $f$.
\end{definition}

\begin{remark}\label{rem:uniq}
	Right $\mathcal{M}$-factorization are essentially unique. To see this, let $e\colon X\to M$ and $m\colon M\to Y$ be a right $\mathcal{M}$-factorization of an arrow $f\colon X\to Y$ and suppose that  $e'\colon X\to M'$ and $m'\colon M'\to Y$ is another, then we  get the existence of the dotted arrows in the following two diagrams
	\[\xymatrix{X \ar[r]^-{e}  \ar[d]_-{e'}& M \ar[r]^-{m} \ar@{.>}[dl]^{v} & Y \ar[d]^{\id{Y}} & X \ar[r]^-{e'}  \ar[d]_{e}& M' \ar[r]_-{m'} \ar@{.>}[dl]^{w} & Y \ar[d]^{\id{Y}}\\M' \ar[rr]_{m'} && Y & M \ar[rr]_{m} && Y}\] 
	On the other hand, from the commutativity of the diagram below we get at once that $v\circ w=\id{M'}$ and $w\circ v=\id{M}$.
	\[\xymatrix{X \ar[rr]^-{e}  \ar[dr]_-{e'} \ar[dd]_{e}&& M \ar[r]^-{m} \ar[dl]^{v} & Y \ar[dd]^{\id{Y}} & X \ar[dr]^{e} \ar[rr]^-{e'}  \ar[dd]_{e'}&& M' \ar[r]_-{m'} \ar[dl]^{w} &Y \ar[dd]^{\id{Y}}\\ & M' \ar[dl]^{w}  \ar[drr]^{m'} &&&&M\ar[dl]^{v} \ar[drr]^{m}\\M \ar[rrr]_{m} &&& Y & M' \ar[rrr]_{m'} &&& Y}\] 
\end{remark}

\begin{proposition}\label{prop:im}
Let $\mathcal{M}$ be a class of arrows in a category $\X$ and suppose that every morphism in $\X$ has a right $\mathcal{M}$-factorization. Then for every arrow $f\colon X\to Y$, there is a functor $f_*\colon \mathcal{M}/X\to \mathcal{M}/Y$ sending $m\colon M\to X$ to a chosen right $\mathcal{M}$-image of $f\circ m$.
\end{proposition}
\begin{notation}
	As in the case of the pullback functor, if $m$ is an arrow $M\to X$, then we will denote the chosen domain of $f_*(m)$ by $f_*(M)$.
\end{notation}
\begin{proof}
We only have to define $f_*$ on arrows. Let thus $g$ be a morphism in $\mathcal{M}/X$ between $m\colon M\to X$ and $n\colon N\to X$. Now, since \[f\circ m = f\circ n\circ g\] the solid part of the diagram below commutes, allowing us to define $f_*(g)$ as the dotted arrow.
\[\xymatrix@C=30pt{M \ar[dr]_(.35){m}|(.55)\hole\ar[r]^-{e_m} \ar[d]_{g}& f_*(M)  \ar@/_.3cm/@{.>}[ddl]^(.7){f_*(g)}\ar[r]^-{f_*(m)}& Y \ar[dd]^{\id{Y}}\\N \ar[d]_{e_n} \ar[r]|(.32)\hole^(.6){n} & X  \ar[dr]^{f}\\f_*(N) \ar[rr]_{f_*(n)}&& Y}\]

 It is clear that, with the above definition, $f_*(\id{m})=\id{f_*(m)}$. Let $h\colon n\to o$ be another morphism in $\mathcal{M}/X$, then we can build the following diagram.
\[\xymatrix@C=30pt{M \ar[r]^-{e_m} \ar[d]_{g}& f_*(M)  \ar[d]_{f_*(g)}\ar[r]^-{f_*(m)}& Y \ar[dd]^{\id{Y}}\\N \ar[r]^-{e_n} \ar[d]_{h} & f_*(N) \ar[d]_{f_*(h)} \ar[dr]^{f_*(n)}\\O\ar[r]_-{e_o}& f_*(O) \ar[r]_{f_*(o)}& Y}\]
From this it follows at once that $f_*(h)\circ f_*(g)=f_*(g\circ h)$.
\end{proof}
\begin{remark} If $\id{X}$ belongs to $\mathcal{M}$, then $f_*(\id{X})$ is a right $\mathcal{M}$-image of $f$.
\end{remark}

The relationship of right $\mathcal{M}$-images to the pullback functors is explained by the following two results.

\begin{proposition}\label{prop:part}
	Let $\mathcal{M}$ be a class of arrows  in a category $\X$, containing  all identities and stable under pullbacks. Suppose, moreover, that every morphism has a right $\mathcal{M}$-factorization. Then $f_*\dashv f^*$ for every arrow $f\colon X\to Y$.  
\end{proposition}
\begin{proof}
	First of all we can notice that for every $m\colon M\to X$ in $\mathcal{M}/X$ the commutativity of the solid part of the following diagram yields the dotted morphism $\eta_n\colon m\to f^*(f_*(m))$.
	\[\xymatrix@C=30pt{M \ar@{.>}[dr]^{\eta_m} \ar@/^.4cm/[drr]^{e_m} \ar@/_.4cm/[ddr]_{m}\\ & f^*(f_*(M)) \ar[d]^{f^*(f_*(m))}\ar[r]^-{p_{f_*(m)}}& f_*(M) \ar[d]^{f_*(m)}\\ & X\ar[r]_f & Y}\]

	To see that $\eta_n$ is the component of a unit $\eta\colon \id{\mathcal{M}/X}\to f^*\circ f_*$, let $g$ be a morphism $m\to f^*(n)$ for some $n\colon N\to Y$ in $\mathcal{M}/Y$. If $p_n:f^*(N)\to N$ is the canonical projection, then 
	\begin{align*}
		n\circ p_n\circ g&=f\circ f^*(n)\circ g\\&=f\circ m
	\end{align*}
	Therefore we can consider the diagram below to get $h\colon f_*(m)\to n$ in $\mathcal{M}/Y$. 
	\[\xymatrix@C=30pt{M \ar[r]^-{e_m} \ar[d]_{g}& f_*(M) \ar[r]^-{f_*(m)}\ar@{.>}@/^.3cm/[ddl]^{h} & Y \ar[dd]^{\id{Y}}\\f^*(N) \ar[d]_{p_n}\\N \ar[rr]_{n}&& Y}\]

	Finally, the equations
	\[\begin{split}
		f^*(n)\circ f^*(h)\circ \eta_m&=f^*(f_*(m))\circ \eta_m\\&=m\\&=f^*(n)\circ g
	\end{split} \qquad \begin{split}
		p_n\circ f^*(h)\circ \eta_m&=h\circ p_m\circ \eta_m\\&=h\circ e_m\\&=p_n\circ g
	\end{split}\]
	entail that $f^*(h)\circ \eta_m=g$ as wanted.

	Let now $h'\colon f_*(m)\to n$ be an arrow such that $f*(h')\circ \eta_m=g$, then
	\begin{align*}
		h'\circ e_m&=h'\circ p_{f_*(m)}\circ \eta_m\\&=p_n\circ f^*(h')\circ \eta_m\\&=p_n\circ g
	\end{align*}
	Thus $h'$ fits in the diagram
	\[\xymatrix@C=30pt{M \ar[r]^-{e_m} \ar[d]_{g}& f_*(M) \ar[r]^-{f_*(m)}\ar@/^.3cm/[ddl]^{h'} & Y \ar[dd]^{\id{Y}}\\f^*(N) \ar[d]_{p_n}\\N \ar[rr]_{n}&& Y}\]
	showing that $h=h'$.	
\end{proof}

\begin{lemma}\label{lem:rfact}
	Let $\mathcal{M}$ be a class of arrows  in a category $\X$, containing all identities then the following are equivalent:
	\begin{enumerate}
		\item $\mathcal{M}$ is stable under pullbacks, $\X$ has all $\mathcal{M}$-pullbacks and every morphism has a right $\mathcal{M}$-factorization;
		\item $\mathcal{M}$ is stable under pullbacks, $\X$ has all $\mathcal{M}$-pullbacks and for every morphism $f\colon X\to Y$, $f^*$ has a left adjoint;
		\item every morphism has a right $\mathcal{M}$-factorization and for every arrow $f\colon X\to Y$, $f_*$ has a right adjoint.
	\end{enumerate}
\end{lemma}
\begin{proof}
	$(1\Rightarrow 2)$ This follows at once from \Cref{prop:part}.

	\smallskip \noindent $(2\Rightarrow 1)$ Let $L_f\colon \mathcal{M}/X\to \mathcal{M}/Y$ be the left adjoint to $f^*$. Since $\id{X}$ belongs to $\mathcal{M}$ we can define $m\colon M\to Y$ in $\mathcal{M}$ as  $L_f(\id{X})$. Moreover, let $\eta_{\id{X}}$ be the component at $\id{X}$ of the unit of the adjunction $L_f \dashv f^*$, if $p_m$ is the projection $f^*(M)\to M$, we can also define $e$ as $p_m\circ \eta_{\id{X}}$. Notice that, by construction, $m\circ e=f$.
	\[\xymatrix@C=30pt{X \ar@/^.4cm/[rr]^e \ar@/_.4cm/[dr]_{\id{X}} \ar[r]_-{\eta_{\id{X}}} & f^*(M) \ar[r]_-{p_m} \ar[d]^{f^*(m)}& M \ar[d]^{m}\\ & X \ar[r]_f& Y}\]

	We have to show that $e$ and $m$ so defined really give us a right $\mathcal{M}$-factorization of $f$. We thus start with the solid part of the diagram below, with $n\in \mathcal{M}$.
		\[\xymatrix@C=35pt{f^*(M)\ar[dr]^-{p_m}\\X \ar[r]^-{e} \ar[u]^{\eta_{\id{X}}} \ar|(.36)\hole@/_.5cm/[rr]_{f} \ar[d]_{h}&   M \ar[r]^-{m} \ar@{.>}[dl]^(.6){v} & Y \ar[d]^{g}\\N \ar[rr]_{n} && Z}\]

	We can apply the pullback property of the inner rectangle below to get the dotted arrow $w\colon M\to f^*(g^*(N))$, which, by construction, defines an arrow $m\to f^*(g^*(n))$.
	\[\xymatrix@C=30pt{X \ar@/^.5cm/[drrr]^{h} \ar@/_1cm/[ddr]_{\id{X}} \ar@{.>}[dr]^{w}\\ &f^*(g^*(N)) \ar[d]_{f^*(g^*(n))}\ar[r]^-{p_{g^*(n)}}& g^*(N) \ar[d]_{g^*(n)} \ar[r]^{p_n} & N \ar[d]^{n} \\ &X \ar[r]_{f}& Y \ar[r]_g & Z}\]

	By construction $w$ defines a morphism $\id{X}\to f^*(g^*(n))$, thus by adjointness, this implies the existence of a unique $\hat{w}\colon m\to g^*(n)$ such that $f^*(\hat{w})\circ \eta_{\id{X}} =w$. Let $v$ be $p_n\circ \hat{w}$, then
	\[\begin{split}
		v\circ e &= p_n\circ \hat{w} \circ p_m\circ \eta_{\id{X}} \\&=p_n\circ p_{g^*(n)}\circ f^*(\hat{w})\circ \eta_{\id{X}}\\&=p_n\circ p_{g^*(n)}\circ w \\&=h
	\end{split}\qquad  \begin{split}
n\circ v &=n\circ p_n\circ \hat{w}\\&=g\circ g^*(n)\circ \hat{w}\\&=g\circ m\\&
	\end{split}\]

	To see that such $v$ is unique, let $v'$ be another arrow $M\to N$ such that
	\[v'\circ e=h \qquad n\circ v'=g\circ m\]
The second of these equations entail the existence of the dotted $q\colon M\to g^*(N)$.
\[\xymatrix{M \ar@{.>}[dr]^{q}\ar@/^.3cm/[drr]^{v'} \ar@/_.3cm/[ddr]_{m}\\ &g^*(N) \ar[d]^{g^*(n)}\ar[r]^{p_n}& N\ar[d]^{n}\\ &Y\ar[r]_{g} & Z}\]
Notice that, in particular, $q$ is a morphism $m\to g^*(n)$ in $\mathcal{M}/Y$. Now, we can also consider the following diagram, which entails that $f^*(q)\circ \eta_{\id{X}}=w$.
	\[\xymatrix@C=30pt{f^*(M) \ar@/_1.2cm/[ddd]_{f^*(m)}\ar[dd]_{f^*(q)}\ar[rr]^{p_m}&&M \ar[dd]_{q}\ar@/^.9cm/[ddd]_(.4){m}|(.67)\hole \ar@/^.6cm/[ddr]^{v'}\\&X\ar@/^.8cm/[ddl]|(.33)\hole_(.2){\id{X}} \ar[drr]_(.3){h}|\hole|(.74)\hole\ar[ul]^{\eta_{\id{X}}} \ar[ur]_{e}\\ f^*(g^*(N)) \ar[d]^{f^*(g^*(n))}\ar[rr]_(.67){p_{g^*(n)}}&& g^*(N) \ar[d]_{g^*(n)} \ar[r]_(.65){p_n} & N \ar[d]^{n} \\ X \ar[rr]_{f}&& Y \ar[r]_g & Z}\]
Thus $q$ must coincide with $\hat{w}$ and therefore $v'=v$.

\smallskip \noindent $(1\Rightarrow 3)$ This also follows from \Cref{prop:part}.

	\smallskip \noindent $(3\Rightarrow 1)$ Let $R_f\colon \mathcal{M}/Y\to \mathcal{M}/Y$ be the right adjoint to $f_*$. Given $n\colon N\to Y$ in $\mathcal{M}$, we can build the rectangle below, where $f(R_f(n))$ and $e$ is a (chosen) right $\mathcal{M}$-factorization of $f\circ R_f(n)$ and $\epsilon\colon f_*\circ R_f\to \id{\mathcal{M}/Y}$ is the counit of the adjunction $f_* \dashv f^*$. 
	\[\xymatrix{R_f(N) \ar[d]_{R_f(n)} \ar[r]^-{e}& f_*(R_f(N))  \ar[r]^-{\epsilon_n} \ar[dr]_{f_*(R_f(n)) \hspace{3pt}}& N \ar[d]^{n}\\
	X \ar[rr]_{f}&& Y}\]

	We have to show that such a rectangle is a pullback. To do so, let $h\colon Z\to N$ and $g\colon Z\to X$ be arrows such that $n\circ h=f\circ g$ and consider the right $\mathcal{M}$-factorization of $g$ given by arrows $i\colon Z\to K$ and $k\colon K\to X$, with $k\in \mathcal{M}$. Thus there exists the dotted $w\colon K\to N$ in the diagram below.
	\[\xymatrix{Z \ar[r]_{i}\ar@/^.4cm/[rr]^{g}\ar[d]_{h}& K \ar@{.>}[dl]^{w} \ar[r]_k & X \ar[d]^{f}\\
	N \ar[rr]_{n}&& Y}\]

	In turn, we can factor $f\circ k$ to get the following rectangle and, henceforth, the existence of the dotted $u\colon f_*(K)\to N$.
	\[\xymatrix{K \ar[r]_-{j}\ar@/^.4cm/[rr]^-{f\circ k}\ar[d]_{w}& f_*(K) \ar@{.>}[dl]^{u} \ar[r]_{f_*(k)} & Y \ar[d]^{\id{Y}}\\
	N \ar[rr]_{n}&& Y}\]

	By construction $u$ is a morphism $f_*(k)\to n$, we can thus consider the unique morphism $\hat{u}\colon k\to R_f(n)$ such that
	\[\epsilon_n\circ f_*(\hat{u})=u\]

	Summing up we have constructed the diagram that follows.
	\[\xymatrix{Z \ar@/^.4cm/[drrrr]^{h}\ar[dr]^{i} \ar@/_1cm/[ddrr]_{g}\\& K \ar[r]^-{\hat{u}} \ar@/_.2cm/[dr]_{k}& R_f(N) \ar[d]_{R_f(n)} \ar[r]^-{e}& f_*(R_f(N))  \ar[r]_-{\epsilon_n} \ar[dr]_{f_*(R_f(n)) \hspace{3pt}}& N \ar[d]^{n}\\ && 
	X \ar[rr]_{f}&& Y}\]

	To conclude it is now enough to show that $\hat{u}\circ i$ is the unique morphism $Z\to R_f(N)$ such that 
	\[\epsilon_n\circ e \circ \hat{u}\circ i=h\qquad R_f(n)\circ \hat{u}\circ i=g\]

	Let, therefore, $t$ be an arrow $Z\to R_f(N)$ such that
	\[\epsilon_n\circ e \circ t=h\qquad R_f(n)\circ t=g\]
	The second equation provides us with the commutative rectangle below, guaranteeing the existence of the dotted $s\colon k\to R_f(n)$.
	\[\xymatrix{Z \ar[r]_-{i}\ar@/^.4cm/[rr]^-{g}\ar[d]_{t}& K \ar@{.>}[dl]^{s} \ar[r]_{k} & X \ar[d]^{\id{X}}\\
		R_f(N) \ar[rr]_{R_f(n)}&& X}\]

	If we compute we get:
	\[\begin{split}
		n\circ \epsilon_n\circ e\circ s&=f_*(R_f(n))\circ e\circ s\\&=f\circ R_f(n)\circ s\\&=f\circ k
	\end{split} \qquad \begin{split}
	\epsilon_n\circ e\circ s\circ i&=\epsilon_n\circ e\circ t\\&=h\\&
	\end{split} \]

On the other hand, the definition of $f_*$ gives us the inner rectangle of the diagram below.
\[\xymatrix@C=30pt{K \ar@/_1.2cm/[ddd]_{w}\ar[dr]_(.35){k}|(.55)\hole\ar[r]^-{j} \ar[d]_{s}& f_*(K)  \ar@/_.3cm/[ddl]^(.75){f_*(s)}\ar[r]^-{f_*(k)}& Y \ar[dd]^{\id{Y}}\\R_f(N) \ar[d]_{e} \ar[r]|(.34)\hole_(.6){R_f(n)} & X  \ar[dr]^{f}\\f_*(R_f(N)) \ar[d]_{\epsilon_n} \ar[rr]_{f_*(R_f(n))}&& Y\\N\ar@/_.8cm/[urr]_{n}}\]

From the commutativity of the whole diagram it follows that $\epsilon_n\circ f_*(s)=u$ and thus $s=\hat{u}$, entailing the thesis.
\end{proof}

\subsection{Factorization systems}

We move now to the notion of \emph{factorization system} \cite{adamek2009abstract,bousfield1977constructions,kelly1991note,rosicky2007factorization,tholen1983factorizations}. Let us start by recalling its definition.

\begin{definition}\label{def:fs}
	Let $\X$ be a category and $\mathcal{E}$, $\mathcal{M}$ two classes of arrows, we will say that $(\mathcal{E},\mathcal{M})$ is a \emph{factorization system} if:
	\begin{enumerate}
		\item $\mathcal{E}$ and $\mathcal{M}$ are closed under composition with isomorphisms: if $f\colon X\to Y$ belongs to $\mathcal{E}$ (to $\mathcal{M}$) and $h\colon Y\to Z$ is an isomorphism then $h\circ f$ belongs to $\mathcal{E}$ (to $\mathcal{M}$);
		\item  every arrow $f\colon X\to Y$ of $\X$ admits a \emph{$(\mathcal{E}, \mathcal{M})$-factorization}, i.e.~there are arrows $e\in \mathcal{E}$ and $m\in \mathcal{M}$ with the property that $f=m\circ e$;
		\item every $e\in \mathcal{E}$ has the \emph{left lifting property} with respect to every $m\in \mathcal{M}$: for every commutative square as the one below, with $e\in \mathcal{E}$ and $m\in \mathcal{M}$ there exists a unique dotted $k\colon Y\rightarrow Z$ which fits in it.
		\[\xymatrix{X \ar[r]^g \ar[d]_{e}& Z \ar[d]^{m}\\ Y \ar[r]_{f} \ar@{.>}[ur]^{k}& V}\] 
	\end{enumerate}

	A factorization system is \emph{proper} if every $e\in \mathcal{E}$ is epi and every $m\in \mathcal{M}$ is mono; it is \emph{stable} if $\mathcal{E}$ is stable under pullbacks.
\end{definition}

\begin{remark}\label{rem:dual}It is immediate to notice that, given a factorization system $(\mathcal{E}, \mathcal{M})$ on $\X$, then $(\mathcal{M}, \mathcal{E})$ is a factorization system on $\X^{op}$. Such factorization system on $\X^{op}$ is proper if and only if $(\mathcal{E}, \mathcal{M})$ is so, it is stable if and only if $\mathcal{M}$ is stable under pushouts in $\X$.  
\end{remark}

We can now begin to prove some properties of factorization systems.

\begin{proposition}\label{prop:el}
Let $(\mathcal{E}, \mathcal{M})$ be a factorization system on a category $\X$, then the following hold true:
\begin{enumerate}
	\item $\mathcal{E}$ is the class of all arrows with the left lifting properties with respect to every $m\in \mathcal{M}$;
	\item every isomorphism belongs to $\mathcal{E}$;
	\item $\mathcal{E}$ is closed under composition.
\end{enumerate}
\end{proposition}
\begin{proof}
	\begin{enumerate}
		\item By definition, every arrow in $\mathcal{E}$ has the left lifting property with respect to every arrow in $\mathcal{M}$. To prove the converse, let $f\colon X\to Y$ be an arrow with such a property with respect to every element of $\mathcal{M}$.  We can factorize it as $m\circ e$ with $m\colon M\to Y$ in $\mathcal{M}$ and $e\colon X\to M$ in $\mathcal{E}$. Thus, in the diagram below, the outer square commutes and so we get the dotted $k\colon Y\to M$.
		\[\xymatrix{X\ar[d]_f\ar[r]^e & M\ar[d]^{m}\\Y\ar[r]_{\id{Y}} \ar@{.>}[ur]^{k} & Y}\]

		On the other hand, $k\circ m$ fits in the diagram below, showing that $k$ and $m$ are mutually inverses. Thus $f=m\circ e$ belongs to $\mathcal{E}$.
		\[\xymatrix{X\ar[rr]^{e} \ar[dd]_{e} \ar[dr]^{f}&& M\ar[dd]^{m} \ar@{<-}[dl]^{m}\\& Y\ar@{<-}[dl]^{k}\\M \ar[rr]_{m}&&Y}\]
		\item By the previous point, it is enough to show that every isomorphism has the left lifting property. But this follows at once: indeed given a square
				\[\xymatrix{X\ar[d]_e\ar[r]^f & M\ar[d]^{m}\\E\ar[r]_{g} \ar@{.>}[ur]^{k} & Y}\]
	the unique $k\colon E\to M$ filling the diagonal in the diagram above is $f\circ e^{-1}$.

		\item Let $e\colon X\to Y$ and $e'\colon Y\to Z$ be two arrows in $\mathcal{E}$. Suppose that the outer rectangle below is given, with $m\in \mathcal{M}$.
		\[\xymatrix{X  \ar[r]^f \ar[d]_{e}& M \ar[dd]^{m}\\Y \ar@{.>}[ur]^{k} \ar[d]_{e'}\\Z \ar@{.>}[uur]_{h}\ar[r]_{g}& W}\]

		Then the first dotted arrow $k\colon Y\to M$ exists since $e$ has the left lifting property with respecto to $m$. Its existence, in turn yields the existence of the other dotted arrow $h\colon Z\to M$.

		 Let $h'\colon Z\to M$ be another arrow such that 
		 \[m\circ h'=g \qquad h'\circ e'\circ e=f\]
		 Then $h'\circ e'$ must coincide with $k$ by the uniqueness clause of the left lifting property and thus, by the same clause, $h'$ must be equal to $h$. By the first point $e'\circ e$ belongs to $\mathcal{E}$. \qedhere 
	\end{enumerate}
\end{proof}

Taking into account \Cref{rem:dual}, the previous proposition gives us the following results.

\begin{corollary}\label{cor:m}Let $(\mathcal{E}, \mathcal{M})$ be a factorization system on a category $\X$, then the following hold true:
	\begin{enumerate}
		\item every isomorphism belongs to $\mathcal{M}$;
		\item $\mathcal{M}$ is closed under composition.
	\end{enumerate}
\end{corollary}

In the presence of a factorization system, we also have right $\mathcal{M}$-factorizations.

\begin{proposition}\label{prop:rfact}
	Let $(\mathcal{E}, \mathcal{M})$ be a factorization system on a category $\X$. Let $f\colon X\to Y$ be a morphism with $e\colon X\to M$ and $m\colon M\to Y$ as an $(\mathcal{E}, \mathcal{M})$-factorization of $f$, then the pair $(e, m)$ is also a right $\mathcal{M}$-factorization of $f$.
\end{proposition}
\begin{proof}
	Suppose that the solid part of the rectangle below is given, with $n\colon N\to Z$ in $\mathcal{M}$. 
	\[\xymatrix{X \ar[d]_{h} \ar@/^.4cm/[rr]^{f} \ar[r]_{e}& M \ar@{.>}[dl]^{k} \ar[r]_{m} & Y \ar[d]^{g}\\N \ar[rr]_{n}&& Z}\]
	Bu the existence of the dotted $k\colon M\to N$ is guaranteed by the left lifting property of $e$ with respect to $n$.
\end{proof}

The previous proposition, together with \Cref{rem:uniq} gives us the following.

\begin{corollary}\label{prop:iso}
	Let $(\mathcal{E}, \mathcal{M})$ be a factorization system on a category $\X$. If $e\colon Y\to E$, $e'\colon Y\to E'$ and $m\colon Y\to X$, $m'\colon Y'\to X $ are arrows, respectively, in $\mathcal{E}$ and $\mathcal{M}$ such that
	$e'\circ m'=e\circ m$,  then  there exist a unique isomorphism $\phi\colon E \rightarrow E'$ such that the diagram below commutes.
	\[\xymatrix@C=40pt{Y \ar[r]^{e'} \ar[d]_{e}& E' \ar[d]^{m'}\\ E \ar[r]_{m} \ar@{.>}[ur]^{\phi}& X}\]
\end{corollary}

The previous corollary, in turn, allows us to deduce other useful properties of factorization systems.

\begin{proposition}\label{cor:iso} Given a factorization system $(\mathcal{E}, \mathcal{M})$ on a category $\X$, the following hold:
	\begin{enumerate}
		\item an arrow $f\colon X\to Y$ with $(\mathcal{E}, \mathcal{M})$-decomposition given by $e$ in $\mathcal{E}$ and $m\in \mathcal{M}$ is in $\mathcal{M}$ if and only if $e$ is an isomorphism;
		\item $f\in \mathcal{E}$ and $f\in \mathcal{M}$ if and only if $f$ is an isomorphism;
		\item $\mathcal{M}$ is stable under pullback.
		\item  if $(\mathcal{E}, \mathcal{M})$ is proper, then $g\circ f$ is in $\mathcal{M}$ implies $f\in \mathcal{M}$.
	\end{enumerate}
\end{proposition}
\begin{proof}
	\begin{enumerate}
		\item  ($\Rightarrow$) By hypothesis $f=f\circ \id{X}$ is a factorization with $\id{X}\in \mathcal{E}$ and $f\in \mathcal{M}$, thus the thesis follows from \Cref{prop:iso}.

		\smallskip \noindent
		($\Leftarrow$) Let $f=m\circ e$ be an $(\mathcal{E}, \mathcal{M})$-factorization. The thesis  follows from \Cref{cor:m} since, if $e$ is an isomorphism, then $f$ is the composition of two arrows in $\mathcal{M}$.

		\item This follows from the previous point, \Cref{cor:m} and \Cref{prop:el}.

		\item 	Suppose that the square below is a pullback, with $m\in \mathcal{M}$
		\[\xymatrix{X\ar[r]^{g} \ar[d]_{n} & M \ar[d]^{m} \\ Y \ar[r]_{f}  & Z}\] 
		We can factor  $n$ as $t\circ e$ for $e\colon X\to M$ in  $\mathcal{E}$ and $t\colon T\to Y$ in $ \mathcal{M}$.  By the left lifting property we get the dotted $l\colon T\to M$ in the diagram below.
		\[\xymatrix{X \ar[d]_{e}\ar[rr]^{g} & &V\ar[d]^{m}\\  T  \ar@{.>}[urr]^{l} \ar[r]_{t}&Y\ar[r]_{f} & Z}\]
		Therefore we get another diagram
		\[\xymatrix{ T \ar@/^.5cm/[drr]^{l}\ar@{.>}[dr]^{k} \ar@/_.5cm/[ddr]_{t}\\ & X \ar[d]_{n}\ar[r]^{g}& M  \ar[d]^{m} \\ &Y \ar[r]_{f} & Z }\]
		and thus we can deduce the existence of the dotted $k\colon E\to V$. On the one hand, computing we get
		\[\begin{split}
			n\circ 	k\circ e&=t  \circ  e\\ &=n
		\end{split}\qquad \begin{split}
			g\circ k\circ e &=l\circ e\\ &=g \end{split}\]
		and so $k\circ e= \id{X}$.  On the other hand 
		\[\begin{split}
			t\circ k \circ t &= \id{Y} \circ t \\&= t
		\end{split} \qquad 
		\begin{split}
			k \circ t \circ e &= k\circ n \\&= e
		\end{split}
		\]	
		so the following diagram commutes.
		\[
		\xymatrix@C=50pt{X \ar[d]_{e}\ar[r]^{e}& T \ar[d]^{t} \\
			T\ar[ur]^{e\circ k}\ar[r]_{t} & Y}\]
		Hence, by the uniqueness clause of the left lifting property, $e\circ k=\id{E}$. Therefore $e$ is an isomorphism and the thesis follows from  point $1$.

			\item 
		Factor $f$ and $g$ as $m_f\circ e_f$ and $m_g\circ e_g$, respectively. Let also $h$ be $e_g\circ m_f$ and factor it as $m_h\circ e_h$ so that we get 
		\[\xymatrix@C=45pt{& C \ar[dr]^{m_h}&\\
			A\ar[ur]^{e_h} \ar[rr]^{h}  \ar[dr]^{m_f}& &B \ar[d]^{m_g}\\
			X \ar[u]^{e_f} \ar[r]_f& Y \ar[r]_g \ar[ur]^{e_g} & Z}\]
	B \Cref{prop:el,cor:m}, $\mathcal{E}$ and $\mathcal{M}$ are closed under composition, therefore $e_h\circ e_f\in \mathcal{E}$ and $m_g \circ m_h\in \mathcal{M}$. Thus these two arrows gives a $(\mathcal{E}, \mathcal{M})$-factorization of $g\circ f$. On the other hand $g\circ f\in \mathcal{M}$, thus point $1$ above  implies that  $e_h\circ e_f$ is an isomorphism, so $e_f$ is a epic split mono which is also an epimorphism. \qedhere
	\end{enumerate}
\end{proof}

With the help of \Cref{rem:dual} we can easy dualize the previous proposition.
\begin{corollary}\label{cor:iso2}
	Given a factorization system $(\mathcal{E}, \mathcal{M})$ on a category $\X$, the following hold:
	\begin{enumerate}
		\item an arrow $f\colon X\to Y$ is in $\mathcal{E}$ if and only if $m_f$ is an isomorphism;
		\item $\mathcal{E}$ is stable under pushouts;
		\item  if $(\mathcal{E}, \mathcal{M})$ is proper, then $g\circ f$ is in $\mathcal{E}$ implies $g\in \mathcal{E}$.
	\end{enumerate}
\end{corollary}

We conclude this section with a result linking closely factorization systems with the existence of right $\mathcal{M}$-factorizations.

\begin{lemma}\label{lem:fact}Let $\mathcal{M}$ be a class of arrows in a category $\X$ closed under composition with isomorphisms, then the following are equivalent:
	\begin{enumerate}
		\item every arrow $f\colon X\to Y$ has a right $\mathcal{M}$-factorization and $\mathcal{M}$ is closed under composition;
		\item there exists a class $\mathcal{E}$ such that $(\mathcal{E}, \mathcal{M})$ is a factorization system on $\X$.
	\end{enumerate}
\end{lemma}
\begin{proof} $(1\Rightarrow 2)$ Let $\mathcal{E}$ be the class of arrows which have the left lifting property with respect to every element of $\mathcal{M}$. Let us show that the three properties of \Cref{def:fs} hold.

	\begin{enumerate}
		\item $\mathcal{M}$ is closed under composition with isomorphisms by hypothesis. On the other hand, if $e\colon X\to Y$ is in $\mathcal{E}$ and $h\colon Y \to Z$ is an isomorphism, then $h\circ e$ still belongs to $\mathcal{E}$. To see this, consider the square below, with $m\in \mathcal{M}$.
		\[\xymatrix{X\ar[r]^{f} \ar[d]_{e}& M\ar[dd]^{m}  \\Y \ar@{.>}[ur]_{k}\ar[d]_h \\Z \ar[r]_{g}& V}\]

		The dotted $k\colon Y\to M$ exists, and it is unique, because $e\in \mathcal{E}$. The thesis now follows taking $k\circ h^{-1}$ as the lifting of $g$.

		\item Given $f\colon X\to Y$, let $e\colon X\to M$ and $m\colon M\to Y$ be a right $\mathcal{M}$-factorization of it. We have to show that $e$ belongs to $\mathcal{E}$. We can further factor $e$ as $n\circ d$, with $n\in \mathcal{M}$. Then we can build the rectangle below.
		\[\xymatrix{X  \ar[dr]_(.3){e}\ar[d]_{d} \ar@/^.4cm/[rr]^{f}\ar[r]_{e} & M \ar@{.>}[dl]^(.3){k} \ar[r]_{m} & Y \ar[d]^{\id{Y}}\\
		D \ar[r]_{n} & M \ar[r]_{m}& Y}\]

		By hypothesis $m\circ n$ is in $\mathcal{M}$, so we can deduce the existence of the dotted $k\colon M\to D$.   Now, from the diagram below, we can deduce that $n\circ k=\id{M}$.
		\[\xymatrix{X \ar[rr]^{e} \ar[dr]^{d}\ar[dd]_{e}& &M \ar[r]^{m}\ar[dl]^{k}& Y \ar[dd]^{\id{Y}}\\ & D\ar[dl]^{n}\\M\ar[rrr]_{m}&&&Y}\]

		On the other hand, the previous result yields also the commutativity of the following diagram, entailing $k\circ n=\id{D}$.
		\[\xymatrix{X \ar[rr]^{d} \ar[dr]^{e}\ar[dd]_{d}& &D \ar[r]^{n}\ar[dl]^{n}& M \ar[dd]^{\id{M}}\\ & M\ar[dl]^{k} \ar[drr]^{\id{M}}\\D\ar[rrr]_{n}&&&M}\]

		Now, suppose that the outer square in the diagram below is given, with $v\in \mathcal{M}$.
		\[\xymatrix{X \ar[dd]_{e} \ar[dr]_{d}\ar[rr]^{t}&& V \ar[dd]^{v}\\ & D \ar[dl]^{n} \ar@{.>}[ur]_{h}\\M \ar[rr]_{s}&& Z}\]

		Then the dotted $h\colon N\to V$ exists and it is unique since $n$ is a right $\mathcal{M}$-image of  $e$. Thus $h\circ k$ is the unique lifting for $s$ along $v$, proving that $e\in \mathcal{E}$.
		\item This holds by construction.
	\end{enumerate}

	\smallskip \noindent $(2\Rightarrow 1)$  This follows from the second point of \Cref{cor:m} and from \Cref{prop:rfact}. \qedhere  
\end{proof}

Putting together \Cref{lem:fact,lem:rfact} we get the following result.

\begin{corollary}\label{cor:fact}
	Let $\mathcal{M}$ be a class of arrows in a category $\X$ closed under composition stable under pullbacks and containing the identities. If $\X$ has $\mathcal{M}$-pullbacks and for every arrow $f\colon X\to Y$ the pullback functor $f^*$ has a left adjoint, then there exists a, unique, class $\mathcal{E}$ such that $(\mathcal{E}, \mathcal{M})$ is a factorization system on $\X$.
\end{corollary}

\subsection{$\mathcal{M}$-subobjects and factorization systems}

In this section we focus on studying the category $\mathcal{M}/X$ when $\mathcal{M}$ is a class of monomorphism.

\begin{remark}
	If  $\mathcal{M}$ is a class of monos in a category $\X$, then $\mathcal{M}/X(f,g)$ has cardinality at most one for every two arrows $f$ and $g$ with codomain $X$. Thus it is a preordered class, in which $f\leq g$ if and only if  $\mathcal{M}/X(f,g)$ is non-empty. Now, it is immediate to notice that $f\leq g$ and $g\leq f$, then there exists a (unique) isomorphism fitting in the triangle below.
	\[\xymatrix{A\ar@{.>}[rr]^{\phi} \ar[dr]_{f} && B \ar[dl]^{g}\\ & X}\]
	In such a case we will write $f\equiv g$. It is immediate to see that in this way we get an equivalence relation on the class of objects of $\mathcal{M}/X$.
\end{remark}

Given the previous remark, we are led to the following definition.

\begin{definition} Let $\mathcal{M}$ be a class of monos in a category $\X$. For every object $X$ a \emph{$\mathcal{M}$-subobject} is an equivalence class $[f]$ of an object $f$ in $\mathcal{M}/X$ with respect to $\equiv$. Given two \emph{$\mathcal{M}$-subobjects} $[f]$ and $[g]$, represented by $f$ and $g$, respectively, we will define $[f]\leq [g]$ if and only if $f\leq g$. It is immediate to see that this defines a partially ordered class $(\sub{M}{X}{X}, \leq)$.

	When $\mathcal{M}$ coincides with the class of all monos we will suppress the prefix, so that a \emph{subobject} is just an equivalence class of a mono and $(\msub{X}{X}, \leq)$ will denote the ordered class of such subobjects of $X$.
\end{definition}

\begin{remark}\label{rem:pbo} Let $f\colon X\to Y$ be an arrows admitting a pullback along arrows in $\mathcal{M}/Y$ and suppose that $\mathcal{M}$ is stable under pullbacks. The categories associated to $(\sub{M}{X}{X}, \leq)$ and $(\sub{M}{Y}{Y}, \leq)$ are equivalent to $\mathcal{M}/X$ and $\mathcal{M}/Y$, respectively, thus we get a monotone function $f^{-1}\colon \sub{M}{X}{Y}\to \sub{M}{X}{X}$ sending $[m]$ to $[f^*(m)]$.

	Similarly, if $f\circ m$ has a right $\mathcal{M}$-factorization for every $m\in \mathcal{M}$, then the functor $f_*$ induces a monotone function $\exists_f\colon \sub{M}{X}{X}\to \sub{M}{X}{Y}$.

	Notice that, whenever $\mathcal{M}$ is stable unr pullbacks, $\X$ has $\mathcal{M}$-pullbacks and  right $\mathcal{M}$-factorizations, then $\exists_f \dashv f^{-1}$ by \Cref{lem:rfact}.
\end{remark}

\Cref{cor:finlim} gives us immediately the following.

\begin{proposition}\label{prop:finlim}
Let $f\colon X\to Y$ be an arrow in a category $\X$ and $\mathcal{M}$ a class of arrows stable under pullbacks and such that $f$ has a pullback along any arrow in $\mathcal{M}$. Then $f^{-1}$ preserves binary infima. If, moreover, $\id{Y}$ belongs to $\mathcal{M}$ then $f^{-1}$ preserves finite infima.
\end{proposition}

Now, let us recall the following lemma, which is the application of the Adjoint Functor Theorem to the partial ordered case.

\begin{lemma}\label{lem:adj}
	Let $f\colon (P,\leq)\to (Q, \leq)$ be a monotone function. If $f$ preserves all infima then it has a left adjoint.
\end{lemma}
\begin{proof}
	For every $q\in Q$ define
	\[P_q:=\{p\in P \mid q \leq f(p)\}\]
Clearly if $q'\leq q$ then $P_{q}\subseteq P_{q'}$. Let us define $g(q)$ as the infimum of $P_q$, the previous observation entails that in this way we get a monotone function $g\colon (Q, \leq)\to (P, \leq)$.
 We can also notice that, since $f$ preserves infima:
\begin{align*}
	f(g(q))&=f(\inf(P_q))\\&=\inf(f(P_q))
\end{align*}
Now, by definition, $q$ is less or equal than every element in $f(P_q)$, thus $q\leq f(g(q))$, so that $g(q)$ is actually the infimum of $P_q$.

 So equpped, we can now prove that $g$ is the right adjoint to $f$.
\begin{itemize}
	\item Suppose that $g(q)\leq p$.  Then $f(g(q))\leq p$, but we already know that $q\leq f(g(q))$, therefore we can conclude that $q\leq f(p)$.
	\item  Suppose that $q\leq f(p)$. Thus $p$ belongs to $P_q$ and so $g(q)\leq p$. \qedhere 
\end{itemize}
\end{proof}

The previous result, together with \Cref{cor:fact} and \Cref{prop:finlim}, allows us to deduce the following result, which has been used in \cite{baldan2011lattice,braatz2010finitary} to show that certain $\mathcal{M}$-adhesive categories have a factorization system.

\begin{corollary}\label{cor:fin}
	Let $\mathcal{M}$ be a class of monomorphism in a category $\X$ stable under pullbacks, containing all identities and closed under composition. If $\sub{M}{X}{X}$ is finite for every object $X$ of $\X$, then there exists a factorization system $(\mathcal{E},\mathcal{M})$ on $\X$
\end{corollary}

\section{Idempotent comonads}

\begin{definition}
	A \emph{comonad} $\m{C}$ on a category $\X$ is a triple $(C, \delta, \epsilon)$ given by a functor $C\colon \X\to \X$ and two natural transformations $\delta\colon C\to C\circ C $, $\epsilon\colon C\to \id{\X}$, called, respectively \emph{comultiplication} and \emph{counit} such that the following diagram commute
	\[\xymatrix@C=30pt{C \ar[d]_{\delta}\ar[r]^-{\delta}& C\circ C  \ar[d]^{\delta*C}&  C \ar[d]_{\delta}\ar[r]^{\delta} \ar[dr]^-{\id{C}} & C\circ C \ar[d]^{\epsilon *C}\\ C\circ C \ar[r]_-{C*\delta}& C\circ C\circ C & C\circ C \ar[r]_-{C*\epsilon} & C}\]

	A comonad $\m{C}$ is \emph{idempotent} if $\delta$ is an isomorphism.  A \emph{morphism} between two comonad $\m{C}=(C, \delta, \epsilon)$ and $\m{D}=(D, \mu, \eta)$ is a natural transformation $\chi\colon C\to D$ such that the following diagrams commute
	\[\xymatrix@C=30pt{ C \ar[r]^-{\delta} \ar[d]_{\chi} & C\circ C \ar[d]^{\chi*\chi}& C \ar[r]^{\epsilon} \ar[d]_{\chi}& 
\id{\X}  \\ D \ar[r]_-{\mu} & D\circ D
	& D \ar[ur]_{\eta} }\]

	We will denote by $\cmd(\X)$ the (possibly not locally small) category whose objects are idempotent comonads and whose arrows are morphisms of monads.
\end{definition}

\begin{remark} Let us recall that, given two functors $F, G\colon \X\rightrightarrows \Y$ and a natural transformation $\chi$ between them, then for every $X\in \X$ we have a naturality square
		\[\xymatrix@C=40pt{F(F(X)) \ar[r]^{F(\chi_X)} \ar[d]_{\chi_{F(X)}}& F(G(X)) \ar[d]^{\chi_{G(X)}}\\G(F(X)) \ar[r]_{G(\chi_X)} & G(G(X))}\]

	This entails that $(\chi * G)\circ (F*\chi)$ and $(G*\chi) \circ (\chi* F)$ are the same natural transformation, which we denote by $\chi*\chi$.
\end{remark}

\begin{example}\label{ex:1}
	\todo{connessi}
\end{example}

\begin{example}\label{ex:2}
	\todo{grafi con equivalenza}
\end{example}
\begin{example}
	\todo{Ce ne sono altri? sarebbe bello usare i calcoli ma credo rientrino nel primo}
\end{example}

We recall the following lemma relating idempotent comonads and coreflective subcategories.

\begin{lemma}\label{lem:comsub}
	Let $L\colon \Y\to \X$ and $R\colon \X \to \Y$ be two functors such that $L\dashv R$
\end{lemma}

Associated to any idempotent comonad we have a class of arrows.

\begin{definition}
	Let $\m{T}$ be an idempotent comonad on a category $\X$. We say that an arrow $f:X\to Y$ i
\end{definition}
\begin{remark}
	contenuto...
\end{remark}

\subsection{A left adjoint to $\mathcal{R}_{(-)}$}

\begin{setting}Let $\X$ be a category with a proper factorization system $(\mathcal{E}, \mathcal{M})$. Our abstract setting to deal with fusions begins with a coreflective subcategory $I\colon \Y\to \X$ with coreflector $F\colon \X\to \Y$ with the following properties:
	\begin{enumerate}
		\item the counit $\epsilon \colon I\circ F\to \id{\X}$ has all components in $\mathcal{M}$; 
		\item given a pushout as the one below, if $F(f)$ is mono then $F(h)$ is mono too.
		\[\xymatrix{X \ar[r]^{g} \ar[d]_{f}& Z \ar[d]^{h}\\ Y\ar[r]_{k} & W}\]
	\end{enumerate}

We denote by $\mathcal{R}$ the class of all arrows of $\X$ whose image in $\Y$ is mono.  A \emph{fusion} is an arrow belonging to both $\mathcal{R}$ and $\mathcal{E}$.
 \end{setting}
 \begin{notation}
 	Given an arrow $f\colon X\to Y$ of $\X$, we will use the following notational conventions:
 	\begin{itemize}
 		\item $f\colon X\mto Y$ if $f$ belongs to $\mathcal{M}$;
 		\item $f\colon X\eto Y$ if $f$ belongs to $\mathcal{E}$;
 		\item $f\colon X \rto Y$ if $f$ belongs to $\mathcal{R}$;
 		\item $f\colon X \fto Y$ if $f$ is a fusion.
 	\end{itemize}
 \end{notation}

 \begin{remark}The following facts hold true:
 	\begin{itemize}
 		\item since $F$ us a right adjoint, it sends monos to monos, thus all monos, in particular those in $\mathcal{M}$, are in $\mathcal{R}$;
 		\item $\mathcal{R}$ is closed under composition and pullbacks;
 		\item if $g\circ f$ is in $\mathcal{R}$, then $f$ is in $\mathcal{R}$ too.
 	\end{itemize}
 \end{remark}

The main property in which we are interested in is given by the following proposition.

\begin{proposition}\label{prop:main}
	Let $h\colon X \rto Y$ be an arrow in $\mathcal{R}$. Given an object $L$ of $\Y$ and $f,g\colon L\rightrightarrows X$, if $h\circ g=h\circ f$ then $g=f$.
\end{proposition}
\begin{proof}
	Since $h\circ g=h\circ f$ and $h$ is in $\mathcal{R}$ we have that $F(g)=F(h)$. Thus we have:
	\begin{align*}
		f\circ \epsilon_{L}&=\epsilon_X\circ I(F(f))\\&=\epsilon_X\circ I(F(g))\\&=g\circ \epsilon_L
	\end{align*}
	By hypothesis $L$ is in $\Y$, thus $\epsilon_L$ is an isomorphism and we can conclude.
\end{proof}

We can wonder if, given a class of arrows in a sufficiently nice category $\X$, we can recover all the properties of our setting. This is the content of the lemma below. We need a technical definition first.

\begin{definition}
	Let $\mathcal{M}$ be a class of monos in $\X$. We say that $\mathcal{M}$ has \emph{$\mathcal{M}$-unions} if, for every object $X$,  $\sub{M}{\X}{X}$ has all suprema and these are computed by multiple pushouts. 
\end{definition}

\begin{remark}
	Being computed by multiple pushout means that the supremum of a family $\{[m_j]\}_{j\in J}$ in $\sub{M}{\X}{X}$ is represented by an arrow $m\colon M\to X$ with the following universal property: given the solid part of the diagram below, there exists a unique dotted arrow $t\colon M\to Z$ making it commutative.
	\[\xymatrix{& M_j \ar[d]_{k_j} \ar@{>->}[dr]^{m_j} \\Z  \ar@{<-}[ur]^{h_j} \ar@{>->}@/_.4cm/[rr]_{z} \ar@{<.}[r]^t & M \ar@{>->}[r]^m & X }\]

	In particular, if $J$ is empty, we get an arrow $o_X\colon O_X\to X$ which is initial in $\mathcal{M}/X$. Notice that, in particular, $o_X$ is the unique element of $\X(O_X, X)$. Indeed, if $f$ is another arrow $O_X\to X$ then we can factor it as $m\circ e$ with $m$ in $\mathcal{M}$. Thus there 
\end{remark}

\begin{lemma}	
Let $\X$ be an $\mathcal{M}$-adhesive category $\X$  with a proper and stable factorization system $(\mathcal{E}, \mathcal{M})$. Suppose that $\mathcal{M}$ has $\mathcal{M}$-unions. Then there exists a corefelctive subcategory $I\colon \Y\to \X$ satisfying the assumptions of our setting.
\end{lemma}
\begin{proof}
	contenuto...
\end{proof}

\section{Rewriting with fusions}

 \begin{setting}
 	contenuto...
 \end{setting}

\begin{definition}

\end{definition}

\bibliographystyle{plain}
\bibliography{bibliog.bib}
\end{document}

### 2024-08-27 quozienti.tex
iniziale

@@
 
-\section{Idempotent comonads}
+\section{Coreflective subcategories}
+
+In order to identify a class of well-behaved DPO-rewriting system we need to recall some other general notion of category theory.
 
 \begin{definition}
-	A \emph{comonad} $\m{C}$ on a category $\X$ is a triple $(C, \delta, \epsilon)$ given by a functor $C\colon \X\to \X$ and two natural transformations $\delta\colon C\to C\circ C $, $\epsilon\colon C\to \id{\X}$, called, respectively \emph{comultiplication} and \emph{counit} such that the following diagram commute
-	\[\xymatrix@C=30pt{C \ar[d]_{\delta}\ar[r]^-{\delta}& C\circ C  \ar[d]^{\delta*C}&  C \ar[d]_{\delta}\ar[r]^{\delta} \ar[dr]^-{\id{C}} & C\circ C \ar[d]^{\epsilon *C}\\ C\circ C \ar[r]_-{C*\delta}& C\circ C\circ C & C\circ C \ar[r]_-{C*\epsilon} & C}\]
-
-	A comonad $\m{C}$ is \emph{idempotent} if $\delta$ is an isomorphism.
-A \emph{morphism} between two comonad $\m{C}=(C, \delta, \epsilon)$ and $\m{D}=(D, \mu, \eta)$ is a natural transformation $\chi\colon C\to D$ such that the following diagrams commute
-	\[\xymatrix@C=30pt{ C \ar[r]^-{\delta} \ar[d]_{\chi} & C\circ C \ar[d]^{\chi*\chi}& C \ar[r]^{\epsilon} \ar[d]_{\chi}& 
-\id{\X}  \\ D \ar[r]_-{\mu} & D\circ D
-	& D \ar[ur]_{\eta} }\]
-
-	We will denote by $\cmd(\X)$ the (possibly not locally small) category whose objects are idempotent comonads and whose arrows are morphisms of monads.
-\end{definition}
-
-\begin{remark} Let us recall that, given two functors $F, G\colon \X\rightrightarrows \Y$ and a natural transformation $\chi$ between them, then for every $X\in \X$ we have a naturality square
-		\[\xymatrix@C=40pt{F(F(X)) \ar[r]^{F(\chi_X)} \ar[d]_{\chi_{F(X)}}& F(G(X)) \ar[d]^{\chi_{G(X)}}\\G(F(X)) \ar[r]_{G(\chi_X)} & G(G(X))}\]
-
-	This entails that $(\chi * G)\circ (F*\chi)$ and $(G*\chi) \circ (\chi* F)$ are the same natural transformation, which we denote by $\chi*\chi$.
-\end{remark}
+	Let $\X$ be a category, a subcategory $\Y$ of $\X$ is \emph{coreflective} if the inclusion functor $I_\Y\colon \Y\to \X$ has a right adjoint $R_\Y$.
+A \emph{coreflective pair} $(\Y, R_\Y)$ is a pair made by a coreflective subcategory $\Y$ of $\X$ and a chosen right adjoint to $I_\Y$.
+A morphism between two coreflective pairs $(\Y, R_\Y)$ and $(\Z, R_\Z)$ is a functor $F\colon \Y \to \Z$ making the following diagrams commutative.
+	\[\xymatrix{\Y  \ar[dr]_{I_\Y}  \ar[rr]^{F} &&\Z  \ar[dl]^{I_\Z}&&\X \ar[dr]^{R_\Z} \ar[dl]_{R_\Y} \\ & \X && \Y \ar[rr]_{F} && \Z }\]
+
+	We will denote by $\cori(\X)$ the category obtained in this way.
+\end{definition}
 
@@
 
+Let us recall the following well known fact.
+
+\begin{proposition}\label{prop:counit}
+Let $L\colon \X\to \Y$ and $R\colon \Y \to \X$ be a pair of functors such that $L\dashv R$. Then the following are equivalent:
+\begin{enumerate}
+	\item $L$ is full and faithful;
+	\item the unit $\eta \colon \id{\X}\to R\circ L$ is an isomorphism.
+\end{enumerate} 
+\end{proposition}
+\begin{proof}
+	We can start noticing that, for every pair of objects $X$ and $Y$ in $\X$, we have two functions:
+	\[F_{X, Y}\colon \X(X, Y)\to \Y(L(X), L(Y)) \quad 	 \Phi_{X, Y}\colon \Y(L(X), L(Y))\to \X(X, R(L(Y)))\]
+	where $F_L$ sends $f\colon X\to Y$ to $L(f)$ and $\Phi_{X, Y}$ is the bijection $\Y(L(X), L(Y))\to \X(X, R(L(Y)))$ given by $L\dashv R$.
+Now, notice that, for every $f\colon X\to Y$ the diagram below commutes.
+	\[\xymatrix@C=35pt{X \ar[r]^{f} \ar[d]_{\eta_X}& Y \ar[d]^{\eta_Y}\\R(L(X)) \ar[r]_-{R(L(f))} &R(L(Y)) }\]
+
+This, in turn, entail that the composit $\Psi_{X,Y} \circ F_{X, Y}$ coincides with $\eta_Y\circ (-)$.
+
+	\smallskip \noindent 
+	$(1\Rightarrow 2)$ Let $X$ and $Y$ be two objects of $\X$, by hypothesis $\eta_Y$ is an isomorphism and so $\eta_Y\circ (-)$ is a bijection.
+But then $F_{X, Y}$ must be a bijection too by what we have observed above.
+
+	\smallskip \noindent 
+	$(2\Rightarrow 1)$ Let $X$ be an object of $\X$, if $L$ is full and faithful then $\eta_Y\circ (-)$ is the composition of the two bijections $\Psi_{Y,Y}\circ F_{Y,Y}$.
+By the Yoneda Lemma this entails that $\eta_Y$ is an isomorphism.
+\end{proof}
+
+\begin{corollary}\label{cor:counit}
+Let $\Y$ be a coreflective subcategory of $\X$ and let $\epsilon \colon I_\Y\circ R_\Y \to  \id{\X}$ be the counit of $I_\Y\dashv R_\Y$. Given an object $X\in \X$, the following are equivalent:
+\begin{enumerate}
+	\item $X$ is in the essential image of the inclusion $I_\Y$;
+	\item $\epsilon_X$ is an isomorphism.
+\end{enumerate} 
+\end{corollary}
+\begin{proof}
+	$(1\Rightarrow 2)$ By hypothesis there is an object $Y$ of $\Y$ and an isomorphism $\phi\colon I_\Y(Y)\to X$. This, in turn, yields the commutative square below.
+	\[\xymatrix@C=40pt{I_\Y(Y) \ar[r]^-{\phi} \ar[d]_{I_\Y(\eta_Y)}&  X\\ I_\Y(R_\Y(I_\Y(Y)))  \ar[r]_-{I_\Y(R_\Y(\phi))}& I_\Y(R_\Y(X)) \ar[u]_{\epsilon_X}}\]
+
+	By hypotesis $\phi$ is an isomorphism and $\eta_Y$ is so by \Cref{prop:counit}, thus $I_\Y(\eta_Y)$ and 
+$I_\Y(R_\Y(\phi))$ are isomorphisms too and the thesis follows.
+
+	\smallskip \noindent
+	$(2\Rightarrow 1)$ This is a tautology.
+\end{proof}
+
+Associated to a coreflective subcategory $\Y$ of $\X$ we have a class of arrows which enjoys some desiderable properties.
+
+ \begin{definition}
+ 	contenuto...
+ \end{definition}
+
+ \begin{proposition}
+ 	contenuto...
+ \end{proposition}
+  \begin{proof}
+  	contenuto...
+  \end{proof}
+
+In general, the class $\mathcal{R}_{(\Y, R_\Y)}$ is not closed under pushout.
+Nonetheless such property is desirable and often enjoyed in the setting of DPO-rewriting.
+We are thus lead to the following definition.
+
+ \begin{definition}
+ 	contenuto...
+ \end{definition}
+
+ \begin{proposition}
+ 	contenuto...
+ \end{proposition}
+ \begin{proof}
+ 	contenuto...
+ \end{proof}
+
+ \begin{definition}
+ 	contenuto...
+ \end{definition}
+
+ \begin{proposition}\label{prop:funct}
+ 	contenuto...
+ \end{proposition}
+ \begin{proof}
+ 	contenuto...
+ \end{proof}
+
+ \iffalse 
+\begin{definition}
+	A \emph{comonad} $\m{C}$ on a category $\X$ is a triple $(C, \delta, \epsilon)$ given by a functor $C\colon \X\to \X$ and two natural transformations $\delta\colon C\to C\circ C $, $\epsilon\colon C\to \id{\X}$, called, respectively \emph{comultiplication} and \emph{counit} such that the following diagram commute
+	\[\xymatrix@C=30pt{C \ar[d]_{\delta}\ar[r]^-{\delta}& C\circ C  \ar[d]^{\delta*C}&  C \ar[d]_{\delta}\ar[r]^{\delta} \ar[dr]^-{\id{C}} & C\circ C \ar[d]^{\epsilon *C}\\ C\circ C \ar[r]_-{C*\delta}& C\circ C\circ C & C\circ C \ar[r]_-{C*\epsilon} & C}\]
+
+	A comonad $\m{C}$ is \emph{idempotent} if $\delta$ is an isomorphism.
+A \emph{morphism} between two comonad $\m{C}=(C, \delta, \epsilon)$ and $\m{D}=(D, \mu, \eta)$ is a natural transformation $\chi\colon C\to D$ such that the following diagrams commute
+	\[\xymatrix@C=30pt{ C \ar[r]^-{\delta} \ar[d]_{\chi} & C\circ C \ar[d]^{\chi*\chi}& C \ar[r]^{\epsilon} \ar[d]_{\chi}& 
+\id{\X}  \\ D \ar[r]_-{\mu} & D\circ D
+	& D \ar[ur]_{\eta} }\]
+
+	We will denote by $\cmd(\X)$ the (possibly not locally small) category whose objects are idempotent comonads and whose arrows are morphisms of monads.
+\end{definition}
+
+\begin{remark} Let us recall that, given two functors $F, G\colon \X\rightrightarrows \Y$ and a natural transformation $\chi$ between them, then for every $X\in \X$ we have a naturality square
+		\[\xymatrix@C=40pt{F(F(X)) \ar[r]^{F(\chi_X)} \ar[d]_{\chi_{F(X)}}& F(G(X)) \ar[d]^{\chi_{G(X)}}\\G(F(X)) \ar[r]_{G(\chi_X)} & G(G(X))}\]
+
+	This entails that $(\chi * G)\circ (F*\chi)$ and $(G*\chi) \circ (\chi* F)$ are the same natural transformation, which we denote by $\chi*\chi$.
+\end{remark}
+
+\begin{proposition}
+Let $L\colon \X \to \Y$ and $R\colon \Y \to \X$ be two functors such that $L\dashv R$.
+If $\eta \colon \id{\X}\to R\circ L$ and $\epsilon\colon L\circ R \to \id{Y}$ are the unit and the counit of this adjunction, then $(L\circ R, L*\eta *R ,\epsilon)$ is a comonad on $\Y$.
+\end{proposition}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+The next definition shows that every comonad come from an adjunction.
+
+\begin{definition}
+	contenuto...
+\end{definition}
+
+\begin{proposition}
+	contenuto...
+\end{proposition}
+\begin{proof}
+	contenuto...
+\end{proof}
+
 We recall the following lemma relating idempotent comonads and coreflective subcategories.
@@
 \end{lemma}
+\begin{proof}
+	contenuto...
+\end{proof}
 
@@
 \end{remark}
+\fi
 

### 2024-09-01 quozienti.tex
minori

@@
 
-\newcommand{\cmd}{\mathbf{IC}}
-
-\newcommand{\cori}{\mathbf{CR}}
+\newcommand{\cori}{\mathbf{CS}}
+\newcommand{\cla}{\mathbf{CL}}
+\newcommand{\pos}{\mathbf{PO}}
+\newcommand{\gori}{\mathbf{GS}}
 
@@
 \newcommand{\dom}[1]{\ensuremath{\zdom({#1})}}
+
+\newcommand{\dm}[1]{\mathsf{dom}({#1})}
 
@@
 \begin{definition}
-	Let $\X$ be a category, a subcategory $\Y$ of $\X$ is \emph{coreflective} if the inclusion functor $I_\Y\colon \Y\to \X$ has a right adjoint $R_\Y$.
-A \emph{coreflective pair} $(\Y, R_\Y)$ is a pair made by a coreflective subcategory $\Y$ of $\X$ and a chosen right adjoint to $I_\Y$.
-A morphism between two coreflective pairs $(\Y, R_\Y)$ and $(\Z, R_\Z)$ is a functor $F\colon \Y \to \Z$ making the following diagrams commutative.
-	\[\xymatrix{\Y  \ar[dr]_{I_\Y}  \ar[rr]^{F} &&\Z  \ar[dl]^{I_\Z}&&\X \ar[dr]^{R_\Z} \ar[dl]_{R_\Y} \\ & \X && \Y \ar[rr]_{F} && \Z }\]
+	Let $\X$ be a category, a full subcategory $\Y$ of $\X$ is \emph{coreflective} if the inclusion functor $I_\Y\colon \Y\to \X$ has a right adjoint $R_\Y$, called \emph{coreflector}.
+A morphism between two coreflective subcategories $\Y$ and $\Z$ is a functor $F\colon \Y \to \Z$ such that $I_\Z \circ F=I_\Y$ and $F\circ R_\Y$ is isomorphic to $R_\Z$.
 
@@
 \end{definition}
+
+\begin{remark}
+	Notice that, since adjoints are unique up to isomorphism, being a morphism $\Y\to \Z$ of $\cori(\X)$ does not depends on the choice of coreflectors for $\Y$ and $\Z$.
+\end{remark}
+
+\begin{remark}\label{rem:ff}
+	Let $F\colon \Y \to \Z$ be a morphism in $\cori(\X)$.
+Since $I_\Z\circ F=I_\Y$, then $\Y$ must be a full subcategory of $\Z$ and $F$ must coincide with its inclusion.
+In particular, $F$ is full and faithful and $\cori(\X)$ is a ordered class.
+\end{remark}
 
@@
 
-Associated to a coreflective subcategory $\Y$ of $\X$ we have a class of arrows which enjoys some desiderable properties.
+Associated to a coreflective subcategory $\Y$ of $\X$ we have a class of arrows which enjoys some useful properties.
 
  \begin{definition}
- 	contenuto...
+ 	Let $\Y$ be a coreflective subcategory of $\X$ with coreflector $R_\Y$, we define the class $\mathcal{R}_\Y$ as the class of all arrows in $\X$ whose image through $R_\Y$ is a mono in $\Y$.
  \end{definition}
 
+ \begin{remark}
+ 	Let $I_\Y\colon \Y \to \X$ be the inclusion functor of a coreflective subcategory $\Y$.
+If $R_\Y$ and $R'_\Y$ are coreflectors, then we have a natural isomorphism $\phi\colon R_\Y\to R'_\Y$ and so, for every $f\colon X\to Y$ there is a square
+ 	\[\xymatrix{ \ar[d]_{\phi_X} R_\Y(X) \ar[r]^{R_\Y(f)}& R_\Y(Y) \ar[d]^{\phi_Y}\\R'_\Y(X) \ar[r]_{R_\Y(f)} & R'_\Y(Y)}\]
+
+ In particular, $R_\Y(f)$ is mono if and only if $R'_\Y(f)$ is so, thus the definition of $\mathcal{R}_\Y$ is independent from the choice of coreflector.
+ \end{remark}
+
  \begin{proposition}
- 	contenuto...
- \end{proposition}
-  \begin{proof}
-  	contenuto...
-  \end{proof}
-
-In general, the class $\mathcal{R}_{(\Y, R_\Y)}$ is not closed under pushout.
-Nonetheless such property is desirable and often enjoyed in the setting of DPO-rewriting.
-We are thus lead to the following definition.
+Let $\Y$ be a coreflective subcategory of $\X$. Then the following hold true:
+\begin{enumerate}
+	\item $\mathcal{R}_\Y$ contains all monos;
+	\item $\mathcal{R}_\Y$ is stable under pullbacks;
+	\item given $f\colon X\to Y$ and $g\colon Y\to Z$, if $g\circ f$ is in $\mathcal{R}_\Y$ then $f$ is in $\mathcal{R}_\Y$ too;
+	\item given $f\colon X\to Y$ in $\mathcal{R}_\Y$ and $g,h\colon I_\Y(Z)\rightrightarrows X$, if $f\circ g = f\circ h$, then $g=h$.
+\end{enumerate}
+ \end{proposition}
+  \begin{proof}\begin{enumerate}
+  		\item This follows at once from the fact that $R_\Y$, being a right adjoint, preserves monos.
+  		\item Consider the following two diagrams, with $f\in \mathcal{R}_\Y$, in which the left one is a pullback. $R_\Y$ preserves limits, thus the right square is a pullback too.
+  		\[\xymatrix@C=30pt{P \ar[r]^{p_1} \ar[d]_{p_2}& X \ar[d]^{f} & R_\Y(P) \ar[r]^{R_\Y(p_1)} \ar[d]_{R_\Y(p_2)} & R_\Y(X) \ar[d]^{R_\Y(f)}\\Z \ar[r]_{g}& Y & R_\Y(Z) \ar[r]_{R_\Y(g)} & R_\Y(Y)}\]
+  		By definition, $R_\Y(f)$ is a mono in $\Y$, but this implies that $R_\Y(g)$ is a mono too, proving $g\in \mathcal{R}_\Y$.
+  		\item We know that $R_\Y(g\circ f)$ is mono, thus $R_\Y(f)$ is mono too.
+  		\item 	Since $f\circ g=f\circ h$ and $f$ is in $\mathcal{R}_\Y$ we can conclude that $R_\Y(g)=R_\Y(h)$. Thus we have:
+  		\begin{align*}
+  			g\circ \epsilon_{I_\Y(Z)}&=\epsilon_X\circ I_\Y(R_\Y(g))\\&=\epsilon_X\circ I_\Y(R_\Y(h))\\&=h\circ \epsilon_{I_\Y(Z)}
+  		\end{align*}
+  		By \Cref{cor:counit},  $\epsilon_{I_\Y(Z)}$ is an isomorphism and so $g=h$. \qedhere
+  	\end{enumerate}
+  \end{proof}
+
+In general, the class $\mathcal{R}_{\Y}$ is not stable under pushout. Nonetheless such property is desirable. We are thus lead to the following definition.
 
  \begin{definition}
- 	contenuto...
+A coreflective subcategory is \emph{good} if  $\mathcal{R}_\Y$ is stable under pushout. $\gori(\X)$ will denote the subcategory of $\cori(\X)$ given by good coreflective subcategories. 
  \end{definition}
 
- \begin{proposition}
- 	contenuto...
- \end{proposition}
- \begin{proof}
- 	contenuto...
- \end{proof}
-
- \begin{definition}
- 	contenuto...
- \end{definition}
+\iffalse 
+ \begin{remark}\label{rem:good}
+Let $\Y$ be a full subcategory of $\X$ with coreflector $R_\Y$.
+Let also $f\colon X\to Y$ be in $\mathcal{R}_\Y$ and consider the following two diagrams, where the left one is a pushout.
+Then $\Y$ is a good subcategory if and only if $R_{\Y}()$
+ \end{remark}
+ \fi
+
+ We end this section extending the construction of $\mathcal{R}_\Y$ to a functor on $\cori(\X)$.
 
  \begin{proposition}\label{prop:funct}
- 	contenuto...
- \end{proposition}
- \begin{proof}
- 	contenuto...
- \end{proof}
+ Let $F\colon \Y \to \Z$ be a morphism of $\cori(\X)$, then $\mathcal{R}_\Z \subseteq \mathcal{R}_{\Y}$.
+ \end{proposition}
+ \begin{proof}
+ Let $f$ be an arrow in $\mathcal{R}_\Z$.
+Since $F$ is an arrow in $\cori(\X)$ we know that there exists a natural isomorphism $\phi\colon F\circ R_\Y\to R_\Z$, therefore $F(R_\Y(f))$ is a monomorphism.
+By \Cref{rem:ff} we know that $F$ is full and faithful and so reflects mono, implying that $f$ belongs to $\mathcal{R}_\Y$ too.
+ \end{proof}
+
+ \begin{corollary}\label{cor:funct}
+ Let $\cla(\X)$ be the category associated to the collection of all classes of a category $\X$, ordered by the inclusion.
+Then there exists a functor $\mathcal{R}_{(-)}\colon \cori(\X)^{op}\to \cla(\X) $.
+
+ Let, moreover, $\pos(\X),$ be the subcategory of $\cla(\X)$  given by classes of arrows stable under pushouts, Then  $\mathcal{R}^G_{(-)}\colon \gori(\X)^{op}\to \pos(\X) $ fitting in the rectangle below, where the vertical arrows are inclusions.
+ \[\xymatrix{\cori(\X)^{op} \ar[r]^{\mathcal{R}_{(-)}}& \cla(\X)\\ \gori(\X)^{op} \ar[u]^{J} \ar[r]_{\mathcal{R}^{G}_{(-)}}& \pos(\X) \ar[u]_{I}}\]
+ \end{corollary}
 
@@
 
-\subsection{A left adjoint to $\mathcal{R}_{(-)}$}
-
+\subsection{Left adjoints to $\mathcal{R}_{(-)}$ and $\mathcal{R}^G_{(-)}$}
+
+In this section we will show that, under suitable hypotheses, the functors $\mathcal{R}_{(-)}$ and $\mathcal{R}^G_{(-)}$ built in the previous sections, both have left adjoints.
+To do so, we need some preliminary work to be done.
+
+\begin{definition}
+	Let $\mathcal{M}$ be a class of arrows in a category $\X$ and let $\{m_i\}_{i\in I}$ be a family of objects in $\mathcal{M}/X$.
+We say that $\{m_i\}_{i\in I}$ has the \emph{epic $\mathcal{M}$-sum property} if:
+	\begin{enumerate}
+		\item it has a  coproduct $m\colon M\to X$;
+		\item the family  of coprojection $\{k_i\}_{i\in I}$ is jointly epic in $\X$.
+	\end{enumerate}
+
+	We say that $\X$ has \emph{epic $\mathcal{M}$-sums} if every family in $\sub{M}{X}{X}$ has the epic $\mathcal{M}$-sum property.
+\end{definition}
+
+\begin{remark}
+	contenuto...
+\end{remark}
+\begin{example}\todo{controesempio spazi topologici}
+\end{example}
+\begin{example}
+\todo{insiemi}
+\end{example}
+
+\begin{example}
+	\todo{adesive finitare}
+\end{example}
+\begin{example}
+	\todo{simple graph}
+\end{example}
+
+We are now ready to construct a left adjoint to $\mathcal{R}_{(-)}$.
+
+\begin{definition} 
+	Let $\X$ be a category and $\mathcal{A}$ a class of arrows of it.
+We define the category $\C(\mathcal{A})$ as the full subcategory of $\X$ given by the objects $Z\in \X$ such that, for every  pair of arrows $g,h\colon Z\rightrightarrows X$, if $f\circ g=f\circ h$ for some $f\colon X\to Y$ belonging to $\mathcal{A}$, then $g=h$.
+\end{definition}
+
+A first thing that we can notice about $\C(\mathcal{A})$ is that, in the presence of a factorization system, is its closure under epimorphisms, as shown by the following proposition.
+
+\begin{proposition}\label{prop:ima}
+ $\mathcal{A}$ be a class of arrows in a category $\X$ If $e\colon X\to Y$ is an epimorphism with domain in $\C(\mathcal{A})$, then $Y$ belongs to $\C(\mathcal{A})$ too.
+\end{proposition}
+\begin{proof}
+	Let $f\colon Z\to V$ be an arrow of $\mathcal{A}$ and take two other arrows $g,h\colon Y\to Z$ such that $f\circ g=f\circ h$. Then we also know that
+	\[f\circ g\circ e= f\circ h\circ e\]
+	By hypothesis $X$ is in $\C(\mathcal{A})$, so that $g\circ e=f\circ e$. The thesis now follows since $e$ is an epimorphism.
+\end{proof}
+\begin{example}
+	\todo{spazi topologici puntati - controesempio}
+\end{example}
+
+\begin{lemma}
+Let $\X$ be a category with a proper factorization system $(\mathcal{E}, \mathcal{M})$.
+Suppose, moreover, that $\X$ has the epic $\mathcal{M}$-sum property.
+Then for every $\mathcal{A}\in \cla(\X)$, $\C(\mathcal{A})$ is a coreflective subcategory of $\X$.
+\end{lemma}
+
+\begin{proof}
+For every object $X$ of $\X$, let us define
+\[\mathcal{F}_X:=\{m\in \mathcal{M}/X \mid \dm{m} \text{ belongs to } \C(\mathcal{A})\}\] 
+We can then define $R(X)$ as the domain of the sum over $\mathcal{F}_X$ in $\mathcal{M}/X$. In particular, we have an arrow $\epsilon_X\colon R(X)\to X$, belonging to $\mathcal{M}$.
+
+First of all, we have to prove that $R(X)$ so defined is an object of $\C(\mathcal{A})$.
+Let thus $f\colon A\to Y$ be an arrow in $\mathcal{A}$ and suppose that there are $g,h\colon R(X)\to A$ such that  $f\circ h= f \circ g$.
+Now, for every $m\colon M\to X$ in $\mathcal{F}_X$ we have a coprojection $k_m\colon m\to \epsilon_X$.
+Precomposing with it we get
+\[f\circ h \circ k_m=f\circ g\circ k_m\]
+By definition $M$ is in $\C(\mathcal{A})$, so we can conclude that $h\circ k_m=g\circ k_m$.
+Since  this holds for every $m\in \mathcal{F}_Z$, the epic $\mathcal{M}$-sum property of $\X$ entails $f=g$ as wanted.
+
+To conclude, is it now enough to show that $\epsilon_X$ has the universal property of a counit.
+Let $Y$ be an object of $\C(\mathcal{A})$ with an arrow $f\colon Y\to X$.
+We can factor $f$ it as $m\circ e$ with $e\colon Y\to E$ and $m\colon E\to X$ in $\mathcal{M}$.
+By \Cref{prop:ima} we know that $E$ is in $\C(\mathcal{A})$, thus there exists a coprojection $k_m\colon m\to \epsilon_X$.
+\end{proof}
+
+\begin{example}
+	\todo{spazi topologici puntati - controesempio 2}
+\end{example}
+
+\begin{proposition}
+	contenuto...
+\end{proposition}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{corollary}
+	contenuto...
+\end{corollary}
+\iffalse 
 \begin{setting}Let $\X$ be a category with a proper factorization system $(\mathcal{E}, \mathcal{M})$.
@@
 \end{proof}
+\fi
 

### 2024-09-04 domains/domains.tex
section domains

--- 2024-07-08 arxiv_concur/main.tex
@@
 \newif\ifreport
-\reporttrue 
-%\reportfalse
+%\reporttrue 
+\reportfalse
 
@@
 \else
-\relatedversion{An extended version is available at \url{https://arxiv.org/abs/2007.04213}.} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
+\relatedversion{An extended version is available at \url{https://arxiv.org/abs/2407.06181}.} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
 %\relatedversion{A full version of the paper is available at \url{...}.}
@@
 
-\title{Left-Linear Rewriting in Adhesive Categories}
+\title{Concurrent semantics for left-linear rewriting [in adhesive categories]}
 
@@
 \begin{abstract}
-  When can two sequential steps performed by a computing device be
-  considered (causally) independent?  This is a relevant question for
-  concurrent and distributed systems, since independence means that
-  they could be executed in any order, and potentially in
-  parallel. Equivalences identifying rewriting sequences which differ
-  only for independent steps are at the core of the theory of
-  concurrency of many formalisms. We investigate the issue in the context of the double pushout
-  approach to rewriting in the general setting of adhesive categories.
-  While a consolidated theory exists for linear rules, which
-  can consume, preserve and generate entities, this paper focuses on
-  left-linear rules which may also ``merge'' parts of the state.  This is an apparently minimal, yet technically hard enhancement, since  a standard characterisation of independence that -- in the
-  linear case -- allows one to derive a number of properties,
-  essential in the development of a theory of concurrency, no longer
-  holds.  The paper performs an in-depth study of the notion of independence
-  for left-linear rules: it introduces a novel characterisation of
-  independence, identifies well-behaved classes of left-linear
-  rewriting systems, and provides some fundamental results including a
-  Church-Rosser property and the existence of canonical equivalence
-  proofs for concurrent computations. These results properly extends
-  the class of formalisms that can be modelled in the adhesive
-  framework.
+  When moving from linear to left-linear rewriting, many properties
+  cease to hold (see concur), and some require to overcome new
+  obstacles to be proven. Here, we identify a very general class of
+  left-linear rewriting systems on adhesive categories where a
+  semantics based on event structures/domains with good properties can
+  be defined. Two semantic structures introduced previously, namely
+  connected event structures and weakly prime domains, introduced in
+  the context of graph rewriting, emerge as canonical structures for
+  rewriting with fusion in the context of adhesive categories.
 \end{abstract}
 
+%\tableofcontents
+
+\section*{Summary}
+
+\subsection*{1. Background}
+
+CONCUR ruslts: strong enforcing + well-switching => nice behaviour of independence.
+
+\subsection*{2. A class of well behaved rewriting systems}
+   [note pag. 11-19]
+
+   Adhesive categories, with all POs, ...,
+   coreflection with a subcat from which we take lhs and monos as right legs
+
+   implies
+
+   - strong enforcing + well-switching
+
+   - well-behaved with respect to quotients, e.g.,
+   \begin{enumerate}
+   \item  if we can rewrite G with L <- K -> R and we take a quotient
+     of G which factories through the colimit, then we can still rewrite
+
+   \item if we can rewrite G with L <- K -> R and we take a G' which
+     has G as a quotient and we can find a match in G' (which factorises
+     through the quotient) then we can still rewrite
+
+   \item existence of the "largest" quotient to which a rule applies
+
+   \item independence "in the colimit" [notes pag. 20-22 for ordinary
+     derivations, then adapt to derivations up to fusion, which are ordinary
+     derivations in the quotient]
+   \end{enumerate}
+
+\subsection*{3. Domain and event structure semantics}
+
+\subsubsection*{3.1 Domain of traces}
+finitary, coherent, irreducible algebraic
+    characterise irreducibles [traces with last step not switchable]
+    [notes page 1-9, holds in general in the setting of concur]
+
+    \subsubsection*{3.2 Weak prime domain and connected event structures}
+
+    - Interchargeability relation and its characterisation via the notion
+    of derivation up to fusion
+
+    - derivations up to fusion and properties [notes pag. 24-27]
+
+    - characterising the interchangeability relation using
+    derivations up to fusion [some idea at pag. 29, notes]
+
+    - proving the interchangeability axioms to conclude that we
+    obtain a weak prime domain [pag. 30-32, notes]
+
 \section{Introduction}
 
-One of the key pay-off of concurrency theory is the idea that the behaviour of 
-a computational device can be modelled by abstracting its sequences of steps
-via a suitable equivalence. Intuitively, the equivalence 
-captures when steps are causally unrelated and thus could be executed in any 
-order, and possibly in parallel. Two seminal contributions to this line of research have been
-Mazurkiewicz's traces~\cite{Mazurkiewicz86} and Winskel's event structures~\cite{NPW:PNES}.
-Concerning formalisms based on the rewriting paradigm, concurrency often boils down to having a notion of independence between two consecutive steps. 
-Noteworthy examples are the
-interchange law~\cite{Mes92} in term rewriting and permutation 
-equivalence~\cite{JJL80} in $\lambda$-calculi.
-
-Among rewriting-based formalisms, those manipulating graph-like
-structures proved useful in many settings for representing the
-dynamics of distributed systems: the graph is used to represent the
-entities and their relations within states, while rewriting steps,
-modifying the graph, model computation steps that result in changes to
-the system state. The DPO (double-pushout) approach~\cite{EhrigPS73}
-is nowadays considered a standard one for these structures, thanks to
-its locality (rule application has a local effect on a state,
-differently from more recent approaches like
-SqPO~\cite{CorradiniHHK06} or PBPO$^+$~\cite{OverbeekER23}) and to its
-flexibility: the rules allow to specify that, in a rewriting step,
-some entities in the current state are removed, some others are needed
-for the rewriting step to occur but remain unaltered, and some new
-entities can be generated. Concerning concurrency, the chosen notion
-is switch (also referred to as shift) equivalence, and independence is formally captured by what is
-called the Church-Rosser theorem of DPO
-rewriting~\cite[Chapter 3, Section~3.4]{CorradiniMREHL97}.
-
-A noteworthy advantage of DPO rewriting is that it can be formulated over
-adhesive categories and their variants~\cite{lack2005adhesive,ehrig2006weak}, which include, among others, toposes~\cite{johnstone2007quasitoposes} and string diagrams~\cite{bonchi2022string}.
-Operating within the framework of adhesive categories allows one to devise the foundations of a rewriting theory that can be then instantiated to the context of interest, thus avoiding the need of
-repeatedly proving similar ad-hoc results for each specific setting.
-
-So far, most of the theoretical results focused on \emph{linear rules}: intuitively, a step is required only to consume, preserve and generate entities.
-However, in some situations it is also necessary to ``merge'' parts of the state.
-This happens in the context of string diagrams mentioned above, but also in graphical implementations of nominal calculi where, as a result of name passing, the received name is identified with a local one at the receiver~\cite{CVY:ESSPE,Gad07}, or in the visual modelling of bonding in biological/chemical processes~\cite{PUY:MBPE}.
-A similar mechanism is at the core of e-graphs (equality graphs), used for rewrite-driven compiler optimisations~\cite{WNW:egg}: rather thanmerging nodes corresponding to equal expressions, the idea -- conceptually and, as we will see, also mathematically similar -- is to maintain an
-equivalence over the nodes.
-
-Technically, to acquire the expressiveness needed for capturing fusions, i.e.~the merge of some elements in the state, requires to move from linear to left-linear rewriting rules.
-While left-linear rules have been considered in various instances (mainly in categories of graphs) and some results concerning the corresponding rewriting theory have been put forward~\cite{Ehrig1976,EHP:BRfTToHLRS,baldan2011adhesivity}, the phenomena arising when devising a theory of independence and concurrency for rewriting with left-linear rules in the general
-setting of adhesive and quasi-adhesive categories have not been systematically explored, even if an investigation in the setting of quasi-topoi, considering non-linear rules yet restricting their applicability, has been presented in~\cite{behr2021concurrency,BehrHK23}.
-
-\begin{figure}
-  \input{Figure/coffee-rules.tex}
-
-  \caption{Rewriting rules for the coffee example.}
-  \label{fi:coffee-rules}
-\end{figure}
-
-\begin{figure}
-  \input{Figure/coffee-rewriting.tex}
-  \caption{A sequence of rewriting steps.}
-  \label{fi:coffee-rewriting}
-\end{figure}
-
-Just to get some basic intuition about left-linear rewriting systems, their capabilities and the problems that can arise, assume we want to model a situation in which a coffee comes with a bag of white sugar and a bag of brown sugar.
-The situation is represented by the graph $G_0$ in Fig.~\ref{fi:coffee-rewriting}: the loop $\mathit{c}$ is the coffee, the two loops $b$ and $w$  represent the white and brown sugar.
-The corresponding nodes are connected to the coffee node by an $s$-labelled edge to indicate that they can be possibly added to the coffee.
-The available rules are in Fig.~\ref{fi:coffee-rules}.
-Rules $\rho_w$ and $\rho_b$ model the addition of white and brown sugar, respectively, to the coffee.
-Note that adding one kind of sugar, say $x$, to the coffee is realised by deleting loop $x$ and merging the corresponding node with the coffee node so that a self-loop $s$ is created.
-
-Once some sugar has been added, the coffee is ready for drinking.
-This is represented by rule $\rho_r$, which checks for the presence of sugar, represented by the loop $s$, in the coffee, and brings it to the $r$ state, ready for drinking.
-
-A rewriting sequence is depicted in Fig.~\ref{fi:coffee-rewriting}, applying $\rho_w$, $\rho_b$, and $\rho_r$ in sequence, thus producing a coffee with both white and brown sugar, ready for drinking.
-A first interesting observation is that after applying rule $\rho_w$ to $G_0$, thus producing graph $G_1$, we can still apply rule $\rho_b$, with a non-injective match.
-Intuitively, once the coffee is ready for drinking because some sugar has been added, adding more sugar will not change its state.
-Indeed, the rules could also be applied in reverse order.
-Should they be considered independent?
-Moreover, since rule $\rho_r$ just requires the presence of sugar, it could be applied immediately after $\rho_w$.
-This might lead to think that $\rho_b$ and $\rho_r$ are independent.
-However, this is not completely clear, since in absence of $\rho_w$, the application of $\rho_b$ would be essential to enable $\rho_r$.
-
-In this paper we perform a systematic exploration of these phenomena at the level of $\mathcal{M}$-adhesive categories, which encompass a large family of DPO-based formalisms.
-
-As an initial step, we observe that for left-linear rules some fundamental properties that play a role
-in the concurrency theory of linear rewriting need to be deeply revised, or plainly do not hold.
-Firstly, the notion of sequential independence and the Church-Rosser theorem, ensuring that sequential independent steps can be performed in reverse order, does not hold out of the box.
-Even worse, given two independent steps it might be possible to switch them in several
-different ways. As we will observe, this prevents the development of a sensible theory
-of concurrency, since switches are used as a basis for equating
-sequences of rewriting steps that differ only in the order of
-independent steps.
-
-We single out a class of left-linear rewriting systems, referred to as \emph{well-switching rewriting systems}, where sequential independence ensures existence and uniqueness of the switch, and argue that this is the right setting for dealing with left-linear rewriting systems.
-
-On the one hand, they capture most categories of interest for rewriting.
-Indeed, we identify general classes of left-linear rewriting systems on graph-like structures that are well-switching.
-As a sanity check, we prove that linear rewriting systems are well-switching.
-
-On the other hand, we argue that a concurrency theory of rewriting can be developed for well-switching rewriting systems, recovering, sometimes in weakened form, most of the results that hold in the linear case.
-The development faces a main technical obstacle.
-In the literature on linear rewriting systems, a central result is the characterisation of switch equivalence of sequences of steps based on
-what are called processes or consistent permutations~\cite{CMR:GP,Handbook,BaldanCHKS06,heindel2009category}. In turn this is the key to derive some fundamental properties for linear rewriting, namely
-\begin{enumerate}
-\item \emph{globality of independence}: if two independent steps are
-  moved forward or backward due to the application of switchings to a
-  sequence, they remain independent;
-\item \emph{consistency of switching}: when transforming
-  sequences of rewriting steps into equivalent ones by switching independent steps, the
-  result does not depend on the order in which switchings are applied, but
-  only on the associated permutation.
-\end{enumerate}
-Properties (1) and (2) allow one to deduce a canonical form for equivalence proofs 
-between sequences of rewriting steps seen as concurrent computations.
-
-The fact that for left-linear rewriting systems the characterisation of switch equivalence via consistent permutations fails, and thus cannot be used for proving (1) and (2), leads to asking if these
-properties hold.
-We show that much of the theory can be retained: globality of independence holds in a weaker form, conceptually linked to the fact that fusions introduce a form of disjunctive causality, while consistency of switching holds unchanged.
-Finally, we prove that a canonical form for switching
-sequences can also be recovered. These results represent a solid basis for developing a satisfactory theory of concurrency for left-linear rules.
-
-\emph{Synopsis.} 
-In \S\ref{sec:ade} we recall the basic definitions of DPO rewriting for $\mathcal{M}$-adhesive categories. 
-In \S\ref{sec:equi} we present the key novelties of our proposal, introducing the standard notion of independence and a novel axiomatic notion of switchability, showing that the former fails to imply the latter for left-linear rewriting systems.
-We then define a subclass of left-linear rewriting systems
-that we call well-switching rewriting systems, and we prove that the classical results for linear rewriting systems are recovered for such a class.
-Finally, in \S\ref{conclusions} we outline directions for future work.
-The appendices recall basic results on adhesive categories (Appendix~\ref{app:ade}), present \emph{strong enforcing} rewriting systems, a class of systems where the local Church-Rosser Theorem holds (Appendix~\ref{app:fill}), and give proofs of the results (Appendix~\ref{omitted}).
-
-\section{$\mathcal{M}$-adhesive categories and rewriting systems}\label{sec:ade}
-
-This  section recalls the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive,heindel2009category}.
-Given a category $\X$ we will not distinguish notationally between $\X$ and its class of objects, so
-``$X\in \X$'' means that $X$ is an object of $\X$.
-We let $\mor(\X)$, $\mon(\X)$ and $\reg(\X)$ denote the class of all arrows, monos and regular monos of $\X$, respectively.
-Given an integer $n\in \mathbb{Z}$, $[0,n]$ denotes the set of natural numbers less than or equal to $n$; in particular, $[0,n]=\emptyset$ if $n<0$.
-
-\subsection{$\mathcal{M}$-adhesivity}\label{subsec:ade}
-The key property of $\mathcal{M}$-adhesive categories is the \emph{Van Kampen condition}~\cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive}.
-In order to define it we need to introduce some terminology.
-Let  $\X$ be a category.
-A subclass $\mathcal{A}$ of
-  $\mor(\X)$ is called
-  \begin{itemize}
-    \parbox{11cm}{\item
-      \emph{stable under pushouts (pullbacks)} if for every pushout (pullback) square as the one on the right, 	if $m \in \mathcal{A}$ ($n\in \mathcal{A}$) then $n \in \mathcal{A}$ ($m \in \mathcal{A}$);
-    \item \emph{closed under composition} if $h, k\in \mathcal{A}$ implies $h\circ k\in \mathcal{A}$ whenever $h$ and $k$ are composable.{\tiny }}\hfill
-    \parbox{2cm}{$\xymatrix{A\ar[r]^f  \ar[d]_{m}& B \ar[d]^n \\ C \ar[r]_g & D}$}
-    \parbox{11cm}{}\hfill
-  \end{itemize}
-
-  \begin{definition}[Van Kampen property]
-    Let $\X$ be a category and consider the diagram\\
-    \parbox{10cm}{
-      aside.
-    Given  a class of arrows $\mathcal{A}\subseteq \mor(\X)$, we say that the bottom square
-    is an \emph{$\mathcal{A}$-Van Kampen square} if
-      \begin{enumerate}
-      \item it is a pushout square;
-    \item 	whenever the cube above has pullbacks as back and left faces and the vertical arrows belong to $\mathcal{A}$, then its top face is a pushout 
-      if and only if the front and right faces are pullbacks.
-      \end{enumerate}}
-    \parbox{2cm}{$\xymatrix@C=10pt@R=6pt{&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{g} & & D }$ }\\
-    Pushout squares that enjoy only the ``if'' half of item (2) above are called \emph{$\mathcal{A}$-stable}.
-
-    A $\mor(\X)$-Van Kampen square is called  \emph{Van
-      Kampen} and a $\mor(\X)$-stable square  \emph{stable}.
-  \end{definition}
-
-We can now define $\mathcal{M}$-adhesive categories.
-
-\begin{definition}[$\mathcal{M}$-adhesive category]
-  Let $\X$ be a category and $\mathcal{M}$ a subclass of
-  $\mon(\X)$  including  all isomorphisms, closed under composition,  and stable under pullbacks and pushouts.  The category  $\X$ is said to be \emph{$\mathcal{M}$-adhesive} if
-  \begin{enumerate}
-  \item it has \emph{$\mathcal{M}$-pullbacks}, i.e.~pullbacks along arrows of $\mathcal{M}$;
-  \item it has \emph{$\mathcal{M}$-pushouts}, i.e.~pushouts along arrows of $\mathcal{M}$;
-  \item  $\mathcal{M}$-pushouts are $\mathcal{M}$-Van Kampen squares.
-  \end{enumerate}
-
-  A category $\X$ is said to be \emph{strictly $\mathcal{M}$-adhesive}
-  if $\mathcal{M}$-pushouts are Van Kampen squares.
-\end{definition}
-
-We write $m\colon X\mto Y$ to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$.
-
-\begin{remark}
-  \label{rem:salva}
-  \emph{Adhesivity} and \emph{quasiadhesivity} 
-  \cite{lack2005adhesive,garner2012axioms} coincide with strict
-  $\mon(\X) $-adhesivity and strict $\reg(\X)$-adhesivity,
-  respectively.
-\end{remark}
-
-\begin{example}
-  \label{rem:iso}
-  Every category $\X$ is $\mathsf{I(\X)}$-adhesive, where $\mathsf{I(\X)}$ is the class of 
-  isomorphisms.
-\end{example}
-
-$\mathcal{M}$-adhesivity is well-behaved with respect to  the construction of slice and functor categories \cite{mac2013categories}, as shown by the following theorems~\cite{ehrig2006fundamentals,lack2005adhesive}.
-
-\begin{theorem}
-  \label{thm:slice-functors}
-  Let $\X$ be an $\mathcal{M}$-adhesive category. Given an object $X$
-  the category $\X/X$ is $\mathcal{M}/X$-adhesive with
-  $\mathcal{M}/X:=\{m\in \mor(\X/X) \mid m\in
-  \mathcal{M}\}$. Similarly, $X/\X$ is $X/\mathcal{M}$-adhesive with
-  $X/\mathcal{M}:=\{m\in \mor(X/\X) \mid m\in \mathcal{M}\}$.
-
-  Moreover for every small category $\Y$, the category $\X^\Y$ of
-  functors $\Y\to \X$ is $\mathcal{M}^{\Y}$-adhesive, where
-  $\mathcal{M}^{\Y}:=\{\eta \in \mor(\X^\Y) \mid \eta_Y \in
-    \mathcal{M} \text{ for every } Y\in \Y\}$.
-\end{theorem}
-
-We can list various examples of $\mathcal{M}$-adhesive categories (see
-\cite{castelnovo2023thesis,CastelnovoGM22,lack2006toposes}).
-
-\begin{example}
-  \label{ex:adhesive}
-  $\cat{Set}$ is adhesive, and, more generally, every topos is
-  adhesive~\cite{lack2006toposes}. By the closure properties above, every presheaf $[\cat{X},\cat{Set}]$ is adhesive, thus the category
-  $\cat{Graph} = [ E \rightrightarrows V, \cat{Set}]$ is adhesive
-  where $E \rightrightarrows {V}$ is the two objects category with two
-  morphisms $s,t \colon{E} \to {V}$. Similarly, various
-  categories of hypergraphs can be shown to be adhesive, such as term
-  graphs and hierarchical graphs~\cite{CastelnovoGM24}. Note that the category $\cat{sGraphs}$ of simple graphs, 
-  i.e.~graphs without parallel edges, is
-  $\reg{(\cat{sGraphs})}$-adhesive~\cite{BehrHK23} but not
-  quasiadhesive.
-\end{example}
-
-A number of properties of adhesive categories that play a role in the
-theory of rewriting generalise to $\mathcal{M}$-adhesive
-categories. These include $\mathcal{M}$-pushout-pullback decomposition
-and uniqueness of pushouts complements (details and proofs are in
-\Cref{app:ade}).
-
-\subsection{DPO rewriting systems derivations}\label{subsec:DPO}
-
-$\mathcal{M}$-adhesive categories are the right context in which to
-perform abstract rewriting using what is called the Double-Pushout
-(DPO) approach.
-
-\begin{definition}[\!\!\cite{habel2012mathcal,heindel2009category}]
-  Let $\X$ be an $\mathcal{M}$-adhesive category. A \emph{left
-    $\mathcal{M}$-linear} rule $\rho$ is a pair  of
-  arrows $\rho = (l: K \to L, r: K \to R)$ such that $l$ belongs to
-  $\mathcal{M}$.  The rule $\rho$ is \emph{$\mathcal{M}$-linear} if
-  $r\in \mathcal{M}$ too.
-  \full{A rule $\rho$ is said to be
-    \emph{consuming} if $l$ is not an isomorphism.}
-  The object $L$ is
-  the \emph{left-hand side}, $R$ the \emph{right-hand side}, and
-  $K$ the \emph{interface}.
-
-  A \emph{left-linear rewriting system} is a pair $(\X, \R)$ where
-  $\X$ is an $\mathcal{M}$-adhesive category and $\R$ a set of left
-  $\mathcal{M}$-linear rules. It  is  called $\mathcal{M}$-\emph{linear} if every rule in $\R$ is  $\mathcal{M}$-linear.
-
-  \vspace{.1cm}
-  \noindent
-  \parbox{10cm}{\hspace{15pt}Given two objects $G$ and $H$ and a rule
-    $\rho=(l,r)$ in $\R$, a \emph{direct derivation $\mathscr{D}$ from
-      $G$ to $H$ applying rule $\rho$} is a diagram as the one
-    aside, in which both squares are pushouts. The arrow $m$ is called
-    the \emph{match} of the derivation, while $h$ is its
-    \emph{co-match}.  We denote a direct derivation $\dder{D}$
-    from $G$ to $H$ as $\dder{D}\colon G\Mapsto H$. }
-  \parbox{3cm}{$\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l}
-      \ar[r]^{r} & R \ar[d]^{h}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}&
-      H}$}
-\end{definition}
-
-A derivation can now be defined simply as a sequence of direct derivations.
-
-\begin{definition}[Derivation]
-  Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a
-  left-linear rewriting system.  Given $G, H \in \X$, a
-  \emph{derivation} $\der{D}$ with source $G$ and target $H$, written
-  $\der{D}: G \Mapsto H$, is defined as a sequence
-  $\{\dder{D}_i\}_{i=0}^n$ of direct derivations such that
-  $\dder{D}_i : G_i \Mapsto G_{i+1}$ is a direct derivation for every
-  index $i$ and $G_0=G$, $G_{n+1}=H$. Moreover, we have an \emph{empty derivation} $G : G \Mapsto G$ for each $G \in \X$.  We denote by $\lgh(\der{D})$ the \emph{length} of a derivation $\der{D}$.
-
-  Given a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^n$, we define $r(\der{D})  = \{\rho_i\}_{i=0}^n$ as the sequence of 
- rules such that every $\dder{D}_i$ applies rule $\rho_i\in \R$.  
-\end{definition}
-
-Derivations naturally compose: given $\der{D}: G \Mapsto H$ and $\der{E}: H \Mapsto F$, we can consider their composition $\der{D} \cdot \der{E}: G \to F$, defined in the obvious way.
-
-Often, we are interested in derivations only up to some notion of coherent isomorphism between them. This leads us to the following definition.
-
-\noindent
-\parbox{8cm}{
-  \begin{definition}[Abstraction equivalence]
-    Let  $\X$ be an $\mathcal{M}$-adhesive category and 
-    $(\X, \R)$ a left-linear rewriting system. 
-    An \emph{abstraction equivalence} between derivations $\der{D}$
-    and $\der{D'}$ with the same length and
-    $r(\der{D})=r(\der{D}')$ is a family of isomorphisms
-    $\{\phi_X\}_{X\in \{G_i,D_i\}}$ such that the diagram on the right commutes
-    for $i\in [0, \min(0, \lgh(\der{D})-1 )]$. We say that $\der{D}$ are $\der{D}'$ are \emph{abstraction
-      equivalent}, written $\der{D}\equiv_a \der{D}'$, if there exists an abstraction equivalence between
-    them.
-  \end{definition}
-}
-\parbox{4cm}{\vspace{-1.35em}$\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i}
-    \ar@{>->}[l]_{f'_i}&G'_{i+1}\\ L_i \ar[u]^{m'_i} \ar[d]_{m_i}& K_i
-    \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i}
-    &R_i \ar[u]^{h'_i} \ar[d]_{h_i}\\G_i
-    \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar@{>->}[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole
-    \ar[r]_{g_i}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{G_{i+1}}}}$}
-
-$\mathcal{M}$-adhesivity of $\X$ ensures the
-uniqueness of the result of applying a rule to an object: two
-direct derivations using the same match are abstraction equivalent
-(see Proposition~\ref{prop:unique}).
-
-\section{Independence in rewriting}
-\label{sec:equi}
-
-In this section we discuss the notion of independence between two
-consecutive rewriting steps, a fundamental ingredient of the rewriting
-theory, which comes into play when viewing a sequence of steps as a
-concurrent computation. We observe that moving from linear to
-left-linear rules leads to the failure of various basic properties of
-the classical notion of independence used in the linear setting and we
-single out a framework in which these can be re-established, possibly
-in a weakened form.
-
-\subsection{Sequentially independent and switchable derivations }\label{subsec:switch}
-
-Sequential independence is the canonical notion of independence in the DPO approach.
-
-\begin{definition}[Sequential independence]
-  \label{de:sequential-independence}
-  Let $\X$ be an $\mathcal{M}$-adhesive category 
-  and $(\X, \R)$ a left-linear rewriting system. 
-  Let also
-  $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation of length $2$, with
-  $\dder{D}_i$ using rule $\rho_i = (l_i,r_i)$.  We say that $\dder{D}_0$ and
-  $\dder{D}_1$ are
-  \emph{sequentially independent}
-  if there is a pair of arrows
-  $i_0\colon R_0\to D_1$ and $i_1\colon L_1\to D_0$ such that the
-  following diagram commutes. In this case $(i_0,i_1)$ is called an  \emph{independence
-    pair}.
-  \[\xymatrix@R=16pt@C=15pt{L_0 \ar[d]_{m_0}&& K_0
-      \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
-      \ar@{.>}@/^.35cm/[drrr]|(.3)\hole_(.4){i_0}
-      \ar[dr]|(.3)\hole_{h_0} && L_1 \ar@{.>}@/_.35cm/[dlll]^(.4){i_1}
-      \ar[dl]|(.3)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
-      \ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
-      D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
-      \ar[rr]_{g_1}&& G_2}
-  \]
-\end{definition}
-
-Intuitively, the existence of the independence pair
-captures the possibility of switching the application of the two rules:
-$f_0 \circ i_1$ is a match for $\rho_1$ in $G_0$ and the
-existence of $i_0 : R_0 \to D_1$ means that $\rho_1$ does not delete
-items in the image of $K_0$, thus $\rho_0$ can be applied after
-$\rho_1$.
-
-\begin{remark}\label{rem:uni}
-	It is worth mentioning that if $(\X, \R)$ is a linear rewriting system then two derivations $\dder{D}_0$ and $\dder{D}_1$ can have at most one independence pair.
-Indeed if $(i_0,i_1)$ and $(i'_0, i'_1)$ are independence pairs, then
-	\[g_0\circ i_1 = g_0\circ i'_1 \qquad f_1\circ i_0=f_1\circ i'_0\]
-But in linear systems $g_0$ and $f_1$ are both monos, entailing $i_0=i'_0$ and $i_1=i'_1$.
-\end{remark}
-
-We next formalise what it means for a derivation being the switch of another.
-
-\begin{definition}[Switch]
-  \label{def:switch}
-  Let $\X$ be an $\mathcal{M}$-adhesive category 
-  and $(\X, \R)$ a left-linear rewriting system. 
-  Let also
-  $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation made
-  of two sequentially independent derivations $\dder{D}_0$,
-  $\dder{D}_1$ with independence pair $(i_0, i_1)$, as in the diagram
-  on the left below. A \emph{switch} of $\der{D}$ along $(i_0,i_1)$ is
-  a derivation $\der{E}=\{\dder{E}_i\}_{i=0}^1$, between the same objects and using the same rules
-  in reverse order, as in the diagram on the right below
-  \[
-    \def\objectstyle{\scriptstyle}\def\labelstyle{\scriptstyle}
-    \xymatrix@C=1.1mm@R=8mm{
-      {L_0} \ar[d]_{m_0}
-      & & {K_0} \ar@{>->}[ll]_{l_0} \ar[rr]^{r_0} \ar[d]_{k_0}
-      & & {R_0} \ar[drr]|(.35)\hole_(.6){h_0}  \ar@/^.22cm/[drrrrrr]|(.3)\hole^(.75){i_0}
-      & & & & 
-      % 
-      {L_1}\ar[dll]|(.35)\hole^(.6){m_1} \ar@/_.22cm/_(.75){i_1}[dllllll]
-      & & {K_1} \ar@{>->}[ll]_{l_1} \ar[rr]^{r_1} \ar[d]^{k_1}
-      & & {R_1} \ar[d]^{h_1} \\
-      % 
-      % 
-      {G_0}
-      & & {D_0} \ar@{>->}[ll]^{f_0} \ar[rrrr]_{g_0}
-      & & & & {G_1} & &
-      & &  {D_1} \ar@{>->}[llll]^{f_1} \ar[rr]_{g_1}
-      & & {G_2}
-    }
-    % 
-    \xymatrix@C=1.1mm@R=8mm{
-      {L_1} \ar[d]_{m_0'}
-      & & {K_1} \ar@{>->}[ll]_{l_1} \ar[rr]^{r_1} \ar[d]_{k_0'}
-      & & {R_1} \ar[drr]|(.35)\hole_(.6){h_0'}  \ar@/^.22cm/@{.>}^(.75){i_0'}|(.3)\hole[drrrrrr]
-      & & & & 
-      % 
-      {L_0}\ar[dll]|(.35)\hole^(.6){m_1'} \ar@/_.22cm/@{.>}_(.75){i_1'}[dllllll] 
-      & & {K_0} \ar@{>->}[ll]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
-      & & {R_0} \ar[d]^{h_1'} \\
-      % 
-      % 
-      {G_0}
-      & & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rrrr]_{g_0'}
-      & & & & {G'_1} & &
-      & &  {D_1'} \ar@{>->}[llll]^{f_1'} \ar[rr]_{g_1'}
-      & & {G_2}  }
-    %
-  \]
-  such that there is an independence pair $(i_0', i_1')$ between
-  $\dder{E}_0$ and $\dder{E}_1$ and 
-  \begin{center}   
-    $m_0=f_0' \circ i_1'$
-    \qquad $h_1=g_1' \circ i_0'$
-    \qquad $m_0'= f_0 \circ i_1$
-    \qquad $h_1'= g_{1}\circ i_0$.
-  \end{center}
-
-  If a switch of $\dder{D}_0$ and $\dder{D}_1$ exists we say that
-  they are \emph{switchable}.
-\end{definition}
-
-It can be shown that switches along the same independence pair are unique up to abstraction
-equivalence (see Proposition~\ref{thm:switch_uni}).
-
-\begin{example}
-  \label{ex:seq-ind}
-  Consider a rewriting system in $\cat{Graph}$, the category of
-  directed graphs and graph morphisms, which is adhesive. The set of
-  rules $\R = \{ \rho_0, \rho_1, \rho_2\}$ is in
-  Fig.~\ref{fi:rules}, where numbers are used to represent the
-  morphisms from the interface to the left- and right-hand
-  sides. Rules $\rho_0$ and $\rho_1$ are linear: $\rho_0$ generates a
-  new node and a new edge, while $\rho_1$ creates a self-loop edge. Instead,
-  $\rho_2$ is left-linear but not linear, as it ``merges'' two nodes.
-
-  \begin{figure}
-    \input{Figure/rules.tex}
-    \caption{A rewriting system in $\cat{Graph}$.}
-    \label{fi:rules}
-  \end{figure}
-
-  A derivation $\der{D}$ consisting of three steps $\dder{D}_0$,
-  $\dder{D}_1$, and $\dder{D}_2$, each applying the corresponding rule
-  $\rho_i$, is depicted in Fig.~\ref{fi:derD}. Note that the numbers in $\rho_1$
-  were changed consistently to represent the vertical morphisms.
-  Steps $\dder{D}_1$ and $\dder{D}_2$ are clearly sequential
-  independent via the independence pair $(R_1 \to D_2, L_2 \to D_1)$,
-  mapping nodes according to their numbering.
-  %
-  A switch of $\der{D}$ along such independence pair is the derivation
-  $\der{E}$ in Fig.~\ref{fi:derE}. Instead, in $\der{D}$ the first two
-  steps applying $\rho_0$ and $\rho_1$ are not sequential independent,
-  intuitively because $\rho_1$ uses the node produced by $\rho_0$ for
-  attaching a self-loop.
-
-  \begin{figure}[t]
-    \input{Figure/derD.tex}
-    \caption{The derivation $\der{D}$.}
-    \label{fi:derD}
-  \end{figure}
-  \begin{figure}[b]
-    \input{Figure/derE.tex}
-    \caption{The derivation $\der{E}$.}
-    \label{fi:derE}
-  \end{figure}
-\end{example}
-
-As we mentioned, for linear rewriting systems
-it is canonical to identify
-derivations that are equal ``up to switching'', i.e.~that differ
-only in the order of independent steps. The same notion can be given
-for left-linear rewriting systems by relying on the notion of switch.
-
-We  recall some notations on permutations.  A \emph{permutation} on
-$\interval[0]{n}$ is a bijection
-$\sigma : \interval[0]{n} \to \interval[0]{n}$. It is a
-\emph{transposition} $\nu$ if there are $i, j \in \interval{n}$,
-$i \neq j$ such that $\sigma(i)=j$, $\sigma(j) = i$, and
-$\sigma(k) = k$ otherwise; it is denoted as $\transp{i}[j]$. Given a permutation $\perm$, 
-an \emph{inversion} for $\sigma$ is a pair $(i,j)$ such that $i<j$ and
-$\sigma(j)< \sigma(i)$; $\inv{\sigma}$ denotes the set of
-inversions of $\perm$.
-
-Switch equivalence is now defined as the equivalence relating derivations that 
-can be obtained one from another by a sequence of switches. Moreover, intermediate graphs can be taken up to isomorphism according to abstraction equivalence.
-
-\begin{definition}[Switch equivalence]
-  \label{de:switch-equivalence}
-  Let $(\X, \R)$ be a left-linear rewriting system.  Let also
-  $\der{D}, \der{E} : G \Mapsto H$ be derivations with the same
-  length, $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and
-  $\der{E}=\{\dder{E}_{i}\}_{i=0}^n$. If
-  $\dder{D}_i \cdot \dder{D}_{i+1}$ is a switch of
-  $\dder{E}_i \cdot \dder{E}_{i+1}$ for some $i \in [0,n-1]$ and  $\dder{D}_j = \dder{E}_j$ for each $j \not \in \{i,i+1\}$ then we write
-  $\der{D} \shift{\transp{i}} \der{E}$. 
- A \emph{switching sequence} is a sequence $\{\der{D}_{k}\}_{k=0}^m$
-  of derivations such that
-    $\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
-    \shift{\nu_m} \der{D}_m$  with $\nu_{k} = \transp{i_k}$.
-
-    Let us denote by $\nu_{k,h}$ the composition
-  $\nu_h \circ \nu_{h-1} \circ \ldots \nu_k$. We say that the
-  switching sequence \emph{consists of inversions} if for all
-  $k \in \interval[0]{m}$ the transposition $\nu_k$ is an inversion
-  for $\nu_{1,m}$.
-
-  Two derivations $\der{D}, \der{E}:G\Mapsto H$ are \emph{switch
-    equivalent}, written $\der{D}\equiv^{sh} \der{E}$, if there is a
-  switching sequence $\{\der{D}_{k}\}_{k=0}^m$ such that
-  $\der{D}\equiv_a \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2}
-  \ldots \shift{\nu_m} \der{D}_m \equiv _a \der{E}$.   
-  To point out a chosen permutation of rewriting steps, we will also write $\der{D}\equiv^{sh}_{\sigma} \der{E}$, 
-  where $\sigma$ is the composition of the transposition appearing in a chosen switching sequence. 
-\end{definition}
-
-\begin{remark}\label{rem:abst}
-	The possibility of an empty switching sequence assures that two abstraction equivalent derivations are switch equivalent.
-\end{remark}
-
-\subsection{Church-Rosser: Sequential independence and switchability}\label{subsec:CR}
-
-The fact that sequential independence implies switchability always
-holds for linear rules (see \Cref{prop:equi}). The result is so
-indispensable that typically, in the literature, it is not even
-stated, in the sense that switchability is not introduced
-axiomatically as in Definition~\ref{def:switch}, but it is based on
-the explicit construction of a switch.
-
-For left-linear rewriting systems
-sequential independence does not imply switchability (while the
-converse implication clearly holds), as shown by the next example.
-
-\begin{figure}
-  \begin{subfigure}{0.2\textwidth}
-    {\small
-      \xymatrix@C=16pt@R=1pt{
-        & 0 \ar@{-}[dd] \ar@{-}[ddddddl] \ar@{-}[ddddddr] &  \\
-        &  & \\
-        & 1 \ar@{-}[dd] \ar@{-}[ddddl]  \ar@{-}[ddddr]   &  \\
-        &  & \\
-        & 2 \ar@{.}[d] \ar@{-}[ddl]   \ar@{-}[ddr]     &  \\
-        &  \ar@{.}[dl]   \ar@{.}[dr] & \\
-        b \ar@{-}[dr] & & c \ar@{-}[dl]\\
-        & a 
-      }
-    }
-    \caption{Poset $(P, \sqsubseteq)$}
-    \label{fig:diff1:P}
-  \end{subfigure}
-  \begin{subfigure}{0.58\textwidth}
-    \xymatrix@C=20pt{
-      a \ar[d]_{\sqsubseteq} & a \ar[d]_{\sqsubseteq} \ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} & 
-      0 \ar@{>->}@/^.35cm/[drrr]|(.3)\hole^(.75){\id{0}}
-      \ar@{>->}[dr]|(.3)\hole_{\id{0}} &  &
-      a \ar@/_.35cm/[dlll]_(.75){\sqsubseteq}
-      \ar[dl]|(.3)\hole^{\sqsubseteq} & 
-      a \ar[d]^{\sqsubseteq}\ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} &
-      b \ar[d]_{\sqsubseteq}\\
-      c &
-      \ar@{>->}[l]^{\id{c}} c \ar[rr]_{\sqsubseteq}& &  0 &&
-      \ar@{>->}[ll]^{\id{0}} 0 \ar@{>->}[r]_{\id{0}}& 0
-    }
-    \caption{Two rewriting steps}
-    \label{fig:diff1:rew}
-  \end{subfigure}
-  \begin{subfigure}{0.20\textwidth}
-    \xymatrix@C=20pt{a \ar[d]^{\sqsubseteq}& a
-      \ar[d]^{\sqsubseteq}\ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} & b \\c & c
-      \ar@{>->}[l]^{\id{c}}
-    }
-    \caption{No rewriting step}
-    \label{ex:diff1:no-step}
-  \end{subfigure}
-  \caption{Sequential independence does not imply switchability}
-  \label{fig:diff1} 
-\end{figure}
-
-\begin{example}
-  \label{ex:diff1}
-  Consider the poset $(P, \sqsubseteq)$ in Fig.~\ref{fig:diff1:P} where
-  $P = \mathbb{N} \cup \{a,b,c\}$ and $\sqsubseteq$ is defined by
-  $m \sqsubseteq n$ if $m \geq n$, $a \sqsubseteq x$ for all $x \in P$
-  and $b, c \sqsubseteq n$ for all $n \in \mathbb{N}$.
-  %
-  Let $\X$ be the  
-  category associated with this order, which by \Cref{rem:iso} is
-  $\mathsf{I(\X)}$-adhesive. 
-  %
-  Consider a rewriting
-  system whose set of rules contains the following 
-  \[\xymatrix{a & a \ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & 0 & a & a
-      \ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & b }\]
-  We can then consider the  derivation
-  $\der{D}=\{\dder{D}_i\}_{i=0}^1$ in Fig.~\ref{fig:diff1:rew}.
-  % \[
-  %   \xymatrix@C=30pt{a \ar[d]_{m_0}&& a \ar[d]_{k_0}\ar[ll]_{\id{a}}
-  %     \ar[r]^{(a,0)} & 0 \ar@/^.35cm/[drrr]|(.315)\hole_(.45){\id{0}}
-  %     \ar[dr]|(.3)\hole_{\id{0}} && a \ar@/_.35cm/[dlll]^(.45){(a,c)}
-  %     \ar[dl]|(.3)\hole^{(a,0)}& a \ar[d]^{(a,0)}\ar@{>->}[l]_{\id{a}}
-  %     \ar[rr]^{(a,b)} && b \ar[d]^{(b,0)}\\c &&
-  %     \ar@{>->}[ll]^{\id{c}} c \ar[rr]_{(c,0)}&& 0 &&
-  %     \ar@{>->}[ll]^{\id{0}} 0 \ar[rr]_{\id{0}}&& 0}\]
-  %
-  Note that the two direct derivations are sequential
-  independent. However there is no switch since the rule applied by
-  $\dder{D}_1$ cannot be applied to $c$. In fact, there is a unique morphism
-  $a\to c$, yielding the diagram in Fig.~\ref{ex:diff1:no-step}. But $b$ and $c$
-  do not have a supremum in the poset underlying $\X$, thus the arrows
-  $a\to b$ and $a\to c$ do not have a
-  pushout. Hence we do not get a direct derivation from $c$.
-\end{example}
-
-The conditions guaranteeing switchability are inspired
-by the notion of \emph{canonical filler}
-\cite{heindel2009category}.
-
-\begin{definition}[Strong independence pair]
-  \label{def:filler}
-  Let $\X$ be an $\mathcal{M}$-adhesive category 
-  and $(\X, \R)$ a left-linear rewriting system. 
-  Let also $(i_0, i_1)$ be an independence pair between two direct
-  derivations $\dder{D}_0$, $\dder{D}_1$
-  as in the solid part of the diagram below
-  \[
-    \xymatrix@C=18pt@R=17pt{L_0 \ar[d]_{m_0}&& K_0
-      \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} \ar@{.>}@/^.20cm/[ddrr]|(.32)\hole|(.57)\hole_(.7){u_0} & R_0
-      \ar@/^.35cm/[drrr]|(.3)\hole^(.2){i_0} \ar[dr]|(.3)\hole_{h_0}
-      && L_1 \ar@/_.35cm/[dlll]_(.2){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
-      \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} \ar@{.>}@/_.20cm/[ddll]|(.32)\hole|(.57)\hole^(.7){u_1} && R_1 \ar[d]^{h_1} \\
-      %
-      G_0 &&
-      \ar@{>->}[ll]^{f_0} D_0 \ar[rr]_(.3){g_0}&& G_1 &&
-      \ar@{>->}[ll]^(.3){f_1} D_1 \ar[rr]_{g_1}&& G_2\\
-      %
-      & & & & P \ar@/^.3cm/@{>.>}[ull]^{p_0} \ar@/_.3cm/@{.>}[urr]_{p_1}
-    }
-  \]
-
-  Consider the pullback of $g_0$ and $f_1$, which yields $p_i : P \to D_i$
-  for $i \in \{0,1\}$ and the mediating arrows $u_i\colon K_i\to P$ 
-  for $i \in \{0,1\}$ 
-  into the pullback object (see \Cref{prop:tec} for details). 
-  We say that $(i_0, i_1)$ is a \emph{strong independence pair} if
-  the first two squares depicted  
-  below are pushouts and if the pushout of $r_1 : K_1 \to R_1$ and $u_1 : K_1 \to P$ exists
-  \[
-    \xymatrix@R=16pt{
-      K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
-      \ar@{>->}[r]^{l_1} \ar[d]_{u_1}& L_1 \ar[d]^{i_1}
-       &K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1\ar@{.>}[d]^{j_0}
-      \\
-      P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0
-       & P \ar@{.>}[r]_{q_1} & Q_1
-    }
-  \]
-\end{definition}
-
-We can now prove a Local Church-Rosser Theorem for strong independence pairs.
-
-\begin{restatable}[Local Church-Rosser Theorem]{proposition}{prChurch}
-  \label{pr:church}
-  Let $(i_0, i_1)$ be a strong independence pair
-  between $\dder{D}_0$ and $\dder{D}_1$. Then $\dder{D}_0$ and
-  $\dder{D}_1$ are switchable.
-\end{restatable}
-
-The correspondence between sequential independence and switchability
-is fundamental. We name the class of rewriting systems where this property holds.
-
-\begin{definition}[Strong enforcing rewriting systems]
-  A left-linear rewriting system is \emph{strong enforcing} if
-  every independence pair between two direct derivations is strong.
-\end{definition}
-
-We can identify a large class of adhesive categories such that all
-left-linear rewriting systems over such categories are strong
-enforcing. This class includes $\cat{Set}$ and it is closed
-under comma and functor category constructions.  As such, it includes
-essentially all categories (e.g., presheaves over set) that are
-typically considered for modelling purposes. Notably, it contains the
-category $\cat{Graph}$ of directed graphs.
-This is a natural generalisation from adhesive to $\mathcal{M}$-adhesive categories of a class studied in \cite{baldan2011adhesivity} (see \Cref{app:fill} for details).
-
-Still, there are $\mathcal{M}$-adhesive rewriting systems that are not strong enforcing.
-
-\begin{example}[Non-strong enforcing left-linear rewriting system]
-  \label{ex:diff2}
-  In light of \Cref{pr:church}, \Cref{ex:diff1} provides an example of
-  an independence pair that is not strong. This gives an example of a
-  left-linear rewriting system in a $\mathcal{M}$-adhesive category that is quite
-  pathological since $\mathcal{M}=\mathsf{I(\X)}$. However, this is expected, 
-  since all natural examples seem to belong to the well-behaved class mentioned above. 
-\end{example}
-
-\begin{remark}
-  By \Cref{pr:church} the existence of a strong independence pair
-  entails switchability, which in turn entails sequential
-  independence by construction. Strong enforcing rewriting systems are exactly
-  those rewriting systems in which these three notions coincide.
-\end{remark}
-
-Consistency with the theory of linear rewriting systems is ensured by the fact that all linear rewriting systems are strong enforcing (see \cref{prop:equi}).
-
-\subsection{Well-switching rewriting systems}
-\label{subsec:verytame}
-
-Even if we work in strong enforcing rewriting systems where sequential
-independence ensures switchability, when dealing with left-linear
-rules there is a further, possibly more serious issue, 
-namely that there can be more than one independence pair between
-the same derivations (cfr. \Cref{rem:uni}). This hinders the very idea of using
-sequential independence as a basis of a theory of concurrency for
-rewriting systems, since exchanges performed using different
-independence pairs may lead to derivations that are not abstraction
-equivalent, thus equating computations that should
-definitively be taken apart, as shown in the example below.
-
-\begin{example}
-  Consider the derivation $\der{E}$ from Example~\ref{ex:seq-ind} (see Fig.~\ref{fi:derE}).
-   The last two steps are sequential independent, but one easily sees
-  that there are two distinct independence pairs, as the left-hand side
-  of $\rho_1$ can be mapped either to node $1$ or to node
-  $2$ in $D_1'$. Correspondingly, there
-  are two switches of $\der{E}$: one is the derivation $\der{D}$ in
-  Fig.~\ref{fi:derD} we started from, the other is the derivation
-  $\der{D}'$ in Fig.~\ref{fi:derD1}.
-
-  \begin{figure}
-    \input{Figure/derD1.tex}
-    \caption{The derivation $\der{D}'$.}
-    \label{fi:derD1}
-  \end{figure}
-
-  As a consequence, $\der{D}$ and $\der{D}'$ would be switch
-  equivalent, but this is not acceptable when viewing equivalence
-  classes of derivations as concurrent computations: in $\der{D}$ the
-  first two steps are not sequential independent, while in $\der{D}'$
-  they are, intuitively because in $\der{D}$ rule $\rho_1$ uses the
-  node generated by $\rho_0$ (adding a self-loop to it), while in
-  $\der{D}'$ rule $\rho_1$ uses the node that was in the initial
-  graph. Also observe that the graphs $G_2$ and $G_2'$ produced after
-  two steps in $\der{D}$ and $\der{D'}$ are not isomorphic. From the
-  technical point of view, the property of being switch equivalent is
-  not closed by prefix, and this prevents deriving a sensible
-  concurrent semantics: In fact
-  $\der{D} = \dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ and
-  $\der{D}' = \dder{D}_0'\cdot \dder{D}_1' \cdot \dder{D}_2'$ are
-  switch equivalent, while if we consider the first two steps,
-  derivations $\dder{D}_0 \cdot \dder{D}_1$ and
-  $\dder{D}_0' \cdot \dder{D}_1'$ are not switch equivalent.
-\end{example}
-
-\full{Moreover, limiting sequential independence to the case in which the independence
-pair is unique (as suggested in~\cite{baldan2017domains}) brings to the same problems.}
-
-For these reasons we believe a theory of rewriting for
-left-linear rules in adhesive categories should be developed for
-systems where the uniqueness of the independence pair is ensured.
-
-\begin{definition}[Well-switching rewriting systems]
-A left-linear rewriting system $(\X, \R)$ is \emph{well-switching} if it is strong enforcing and, for every derivation $\der{D}:=\{\dder{D}_{i}\}_{i=0}^1$, there is at most one independence pair between $\dder{D}_0$ and $\dder{D}_1$.
-\end{definition}
-
-Clearly, linear rewriting systems are well-switching (see Proposition~\ref{pr:weak}).
-Moreover, we next observe that various classes of rewriting systems,
-comprising all the ones used in modelling the applications to the
-encoding of process calculi or of bio and chemical systems mentioned
-in the introduction, are actually well-switching.
-
-A first class consists of those rewriting systems over
-possibly hierarchical graphical structures obtained as algebras of
-suitable signatures where rules are constrained not to merge elements
-of top level sorts in the hierarchy (for graphs, nodes can be
-merged while edges cannot). The idea here is to consider graph
-structures as presheaves on categories in which there are objects that play 
-the role of \emph{roots}, i.e.~objects that are not the codomain of 
-any arrow besides the identity.
-
-\begin{definition}[Root-preserving graphical rewriting systems]
-	Let $\X$ be a category, an object $X\in \X$ is a \emph{root} if the only arrow with codomain $X$ is $\id{X}$.
-	The category $\gph{X}$ of \emph{$\X$-graphs} is the category
-	$\Set^{\X}$. A
-	\emph{root-preserving graphical rewriting system} is a left-linear
-	rewriting system $(\gph{X}, \R)$ such that for each rule
-	$(l\colon K\to L, r\colon K\to R)$ in $\R$ it holds
-	\begin{enumerate}
-		\item for every $X\in \X$ and $x\in L(X)$, there exists a root $Y$
-		 and an arrow $f\colon Y\to X$ such that $x$ belongs to the image of
-		$L(f)\colon L(Y)\to L(X)$;
-		\item $r\colon K\to R$ is mono on the roots, i.e.~for every root $X\in \X$ the component $r_X:K(X)\to R(X)$ is injective.
-	\end{enumerate}
-\end{definition}
-
-For instance, the category $\cat{Graph}$ can be obtained
-by taking as $\X$ the category generated by $E \rightrightarrows V$. In this case $E$ is the only root, hence, condition $1$ asks that in the left-hand side of each rule
-there are no isolated nodes, while condition $2$ asks that the
-morphism $r: K \to R$ is injective on edges, i.e.~it can only merge nodes.
-
-\begin{restatable}{lemma}{lemVTame}
-\label{bono}
-  All root-preserving graphical rewriting systems are well-switching.
-\end{restatable}
-
-Another interesting class of well-switching rewriting systems is given by e-graphs.
-
-\begin{example}[E-graphs]
-  Consider the category $\cat{EGraphs}$, where objects are (directed)
-  graphs endowed with an equivalence over nodes, and arrows are graph
-  morphisms that preserve the equivalence, as considered
-  in~\cite{BaldanGM06}, closely related to e-graphs~\cite{WNW:egg}. 
-  Formally, $\cat{EGraphs}$ can be seen as the
-  subcategory of the presheaf
-  $[E \rightrightarrows V \to Q, \cat{Set}]$ where objects are
-  constrained to have the component $V \to Q$ surjective.
-
-  Explicitly, an
-  e-graph $G$ is a triple $\langle s_G, t_G, q_G \rangle$ where
-  $s_G, t_G: E_G \rightrightarrows V_G$ provides the graphical
-  structure, while the surjective function $q_G : V_G \to Q_G$ maps
-  each node to the corresponding equivalence class. 
-  Notice that the inclusion functor into  $[E \rightrightarrows V \to Q, \cat{Set}]$ 
-  creates pullbacks and pushouts \cite{mac2013categories}, so that they are computed component-wise.
-
-  A morphism in $\cat{EGraph}$ is mono if the components over $E$
-  and $V$ are mono, i.e.~if it is mono as a morphism in
-  $\cat{Graph}$. It is regular mono if also the component on
-  $Q$ is mono, i.e.~if it reflects equivalence classes besides
-  preserving them.
-This characterisation of regular monos and the fact that pullbacks and pushouts are computed component-wise allows us to prove quasi-adhesivity of $\cat{EGraphs}$ at once.
-Moreover, one can deduce that every rewriting system $(\X, \R)$ that is left-linear with respect to $\reg(\cat{EGraphs})$ is strong enforcing: this is done exploiting again the inclusion functor into $[E \rightrightarrows V \to Q, \cat{Set}]$.
-
-Left-linear rewriting systems with respect to $\reg(\cat{EGraphs})$ are well-switching. They have been used in~\cite{BaldanGM06} for the graphical implementation of nominal calculi, where,
-differently from~\cite{Gad07}, as a result of name passing the received name is not merged with a local one, but put in the same equivalence class, better tracing the causal dependencies among reductions.
-\end{example}
-
-\subsection{A canonical form for  switch equivalences}
-\label{subsec:canonical}
-
-As discussed in the introduction, in the linear case a number of
-basic properties of switch equivalence, i.e.~the globality of
-independence, the consistency of switching, and the existence of a
-canonical form for equivalence proofs, can be derived from a
-characterisation of switch equivalence in terms of consistent
-permutations or processes.
-
-When dealing with left-linear rules, such a characterisation
-fails. Leaving aside the formal details (the interested reader can
-refer to \Cref{def:permcon}), the intuition is quite simple. In the
-linear case one proves that two derivations using the same rules in
-different orders are switch equivalent when the colimits of the two
-derivations, seen as diagrams, are isomorphic and the isomorphism
-properly commutes with the embeddings of the rules. When considering
-left-linear derivations, this is no longer true. Intuitively this is
-due to the fact that a rewriting step can merge parts of an
-object thus making the colimit little informative.
-This effect can be seen for derivations $\der{D}$ in
-Fig.~\ref{fi:derD} and $\der{D}'$ in Fig.~\ref{fi:derD1}. They are not
-abstraction equivalent but the colimit of both derivations is a single node with two self-loops, in a way that  all commutativity requirements are
-trivially satisfied.
-
-In this section we show that, despite the failure of such
-characterisation, actually much of the theory can be retained, taking
-a different and sensibly more complex route for the proofs: globality
-of independence holds in a weak form, conceptually linked to the fact
-that fusions introduce a form of disjunctive causality, while
-consistency of switching holds unchanged. Finally, a canonical form
-for switching sequences can also be recovered.
-
-We start by proving two lemmas dealing with derivations of length
-$3$. Despite being technical, these lemmas are fundamental building blocks for obtaining our results.
-
-\smallskip
-
-\noindent
-\begin{minipage}{.8\textwidth}
-  \setlength\parindent{1.5em}
-  The first lemma is at the core of globality for independence.
-It shows that if we have a derivation consisting of three rewriting steps, say $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ where $\dder{D}_0$ and $\dder{D}_1$ are independent, then if we switch $\dder{D}_2$ to the first position,
-obtaining a derivation $\dder{D}_2'' \cdot  \dder{D}_0'\cdot\dder{D}_1'$, as in the diagram on the right where vertical lines represent permutations, the steps $\dder{D}_0'$ and $\dder{D}_1'$ are still independent.
-\end{minipage}
-\begin{minipage}{.18\textwidth}
-\ \hspace{-14mm}
-\begin{tikzpicture}[node/.style={draw, minimum size=8mm}]
-  \begin{tikzcd}[row sep=2mm, column sep=1mm]
-    \dder{D}_0 \arrow[perm,d]  & \dder{D}_1 \arrow[perm,dr] & \dder{D}_2 \arrow[perm,dl]\\
-    \dder{D}_0 \arrow[perm,dr]  & \dder{D}_2' \arrow[perm,dl] & \dder{D}_1' \arrow[perm,d]\\
-    \dder{D}_2''   & \dder{D}_0' & \dder{D}_1'
-  \end{tikzcd}
-\end{tikzpicture}
-\end{minipage}
-
-\smallskip
-
-\noindent
-\begin{minipage}{.8\textwidth}
-  If instead $\dder{D}_1$ and $\dder{D}_2$ are
-independent in $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ and we switch $\dder{D}_0$ to the last position, obtaining a
-derivation $\dder{D}_1'\cdot \dder{D}_2'\cdot  \dder{D}_0''$, as in the diagram on the right, the steps $\dder{D}_1'$ and $\dder{D}_2'$ could be no
-longer independent. %unless an additional condition is satisfied. 
-Intuitively, this is due to the fact that dealing with
-left-linear rewriting systems introduces disjunctive forms of
-causality. Hence, if in $\dder{D}_0\cdot \dder{D}_1\cdot \dder{D}_2$ we have that $\dder{D}_0$ and $\dder{D}_1$ are
-disjunctive causes of $\dder{D}_2$, at least one of the two is needed to
-enable the application of $\dder{D}_2$ and this explain why in
-$\dder{D}_1'\cdot \dder{D}_2'\cdot \dder{D}_0''$ we have that $\dder{D}_1'$ and $\dder{D}_2'$ are no longer
-independent. This is exemplified below.
-\end{minipage}
-\begin{minipage}{.18\textwidth}
-\ \hspace{-14mm}
-\begin{tikzpicture}[node/.style={draw, minimum size=8mm}]
-     \begin{tikzcd}[row sep=2mm, column sep=1mm]
-      \dder{D}_0 \arrow[perm,dr]  & \dder{D}_1 \arrow[perm,dl] & \dder{D}_2 \arrow[perm,d]\\
-      \dder{D}_1' \arrow[perm,d]  & \dder{D}_0' \arrow[perm,dr] & \dder{D}_2 \arrow[perm,dl]\\
-      \dder{D}_1'   & \dder{D}_2' & \dder{D}_0''
-    \end{tikzcd}
-  \end{tikzpicture} 
-\end{minipage}
-
-\begin{example}
-  \label{ex:non-global}
-  Consider the rewriting system in $\cat{Graph}$ consisting of the
-  rules $\lambda_0$, $\lambda_1$, and $\lambda_2$ in
-  Fig.~\ref{fi:rules-cas}. Consider the derivation $\der{F}$ in Fig.~\ref{fi:derF}. Note that rule
-  $\lambda_2$ needs the black self-loop on node $12$ to be applied. This can be
-  generated either by $\lambda_0$ or by $\lambda_1$ merging nodes $1$ and
-  $2$, hence at least one of them must precede the application of
-  $\lambda_2$. Indeed, in $\der{F}$ it is easily seen that the second
-  and the third step applying $\lambda_1$ and $\lambda_2$ are
-  independent. However, we could switch twice the application of
-  $\lambda_0$, bringing it in the last position, obtaining a derivation
-  $\der{F}'$ as depicted in Fig.~\ref{fi:derF1}, where the
-  applications of $\lambda_1$ and $\lambda_2$ are no longer independent.
-   %
-  \begin{figure}[t]
-    \input{Figure/rules-cas.tex}    
-    \caption{A new rewriting system in $\cat{Graph}$.}
-    \label{fi:rules-cas}
-  \end{figure}
-%
-  \begin{figure}[t]
-    \input{Figure/derF.tex}    
-    \caption{The derivation $\der{F}$.} 
-    \label{fi:derF}
-  \end{figure}
-%
-  \begin{figure}[t]
-    \input{Figure/derF1.tex}    
-    \caption{The derivation $\der{F}'$.} 
-    \label{fi:derF1}
-  \end{figure}
-\end{example}
-%
-\begin{restatable}[Globality of independence]{lemma}{lemIndepGlobalLeft}
-  \label{lem:indep-global-left}
-  Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X,\R)$ a
-  well-switching rewriting system.  Let
-  $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ be a three-steps
-  derivation.
-  \begin{enumerate}
-  \item
-    \label{lem:indep-global-left:1}
-    If $\dder{D}_0$ and $\dder{D}_1$ are switchable and there is a
-    switching sequence
-    $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(1,2)}
-    \dder{D}_0 \cdot \dder{D}_2' \cdot \dder{D}_1' \shift{(0,1)}
-    \dder{D}_2'' \cdot \dder{D}_0' \cdot \dder{D}_1'$ then
-    in the last derivation $\dder{D}_0'$ and $\dder{D}_1'$ are switchable;
-
-  \item
-    \label{lem:indep-global-left:2}
-    Suppose that $\dder{D}_1$ and $\dder{D}_2$ are switchable, hence $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(1,2)}
-    \dder{D}_0 \cdot \dder{D}_2' \cdot \dder{D}_1'$ and $\dder{D}_0$ and $\dder{D}_2'$ are switchable.  If there
-    is a switching sequence
-    $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(0,1)}
-    \dder{D}_1' \cdot \dder{D}_0' \cdot \dder{D}_2 \shift{(1,2)}
-    \dder{D}_1' \cdot \dder{D}_2' \cdot \dder{D}_0''$ then in the last derivation $\dder{D}_1'$ and $\dder{D}_2'$ are switchable.
-  \end{enumerate}
-\end{restatable}
-
-The second lemma captures the essence of the consistency of
-switchings. If in a derivation of three
-rewriting steps, say $\dder{D}_0\cdot \dder{D}_1\cdot  \dder{D}_2$, we invert them leading to a
-sequence reordered as $\dder{D}_2\cdot  \dder{D}_1\cdot  \dder{D}_0$, we obtain the same derivation,
-independently from the order of switchings.
-
-\begin{restatable}[Consistency of switchings]{lemma}{lemSwitchConfluence}
-	\label{lem:switch-confluence}
-	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X,\R)$ a well-switching rewriting system.
-	% 
-	Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$ and suppose that we have the following two switching sequences
-	\[\der{D} \shift{(0,1)} \der{D}' \shift{(1,2)} \der{D}'' \shift{(0,1)}\der{D}'''\\
-          \qquad \der{D}\shift{(1,2)}\der{E}'\shift{(0,1)} \der{E}'' \shift{(1,2)}\der{E}''' \]
-Then $\der{D}'''$ and $\der{E}'''$ are abstraction equivalent. 
-\end{restatable}
-
-The lemmas above open the way to the key result of this section, which establishes a canonical form for
-switching derivations.
-
-The first result shows that when equating two derivation sequences by performing a series of switchings, we can limit ourselves to switchings that invert the order of steps that in the target derivation has to be reversed, i.e.~we can limit ourselves to applying inversions.
-
-\begin{restatable}[No need of useless switches]{theorem}{thNoNeed}
-  \label{th:no-need}
-  Let $\der{D}$ and $\der{D}'$ be derivation sequences. If $\der{D} \shifteq \der{D}'$ then there is a switching sequence 
-  %\begin{center}
-    $\der{D} \equiv_a \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
-    \shift{\nu_n} \der{D}_n \equiv_a \der{D}'$
-  %\end{center}
-  consisting only of inversions.
-\end{restatable}
-
-\full{[Proof~\ref{thNoNeed-proof}]}
-
-While inversions can be
-performed in any order in the case of linear rewriting systems, this is no longer true for left-linear
-rewriting systems due to the fact that, as already observed, globality of independence holds in a weak form. 
-For instance, if we get back to Example~\ref{ex:non-global} and consider derivation $\der{F}$ in Fig.~\ref{fi:derF}, 
-the last two steps applying rules $\lambda_1$ and $\lambda_2$ can be switched, thus leading to a derivation, 
-call it $\der{F}''$,  applying $\lambda_0, \lambda_2, \lambda_1$. This $\der{F}''$ is switch equivalent to $\der{F}'$ in Fig.~\ref{fi:derF1}, 
-hence starting from $\der{F}''$ we can obtain $\der{F}'$ via a switching sequence, but we cannot start 
-by switching $\lambda_0$ and $\lambda_2$, even if this is an inversion.
-
-\newpage
-Still, we can identify a
-canonical form for switching derivations: at each step one can apply a switch to the inversion with largest index.
-
-\begin{restatable}[Canonical form]{corollary}{coCanonical}
-  \label{co:canonical}
-  Let $\der{D}$ and $\der{D}'$ be derivation sequences. If
-  $\der{D} \shifteq[\sigma]\der{D}'$ then there is a switching sequence
-  \begin{center}
-    $\der{D} \equiv_a \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
-    \shift{\nu_n} \der{D}_n \equiv_a\der{D}'$
-  \end{center}
-  where for $i \in \interval{n}$ we have $\nu_i  = \transp{k}$ with 
-  $k = \max \{ j \mid \transp{j} \in \inv{\nu_{i,n}}\}$.
-\end{restatable}
-
-\section{Conclusions and further work}
-\label{conclusions}
-
-We performed an in-depth investigation of the notion of independence between
-rewriting steps in the setting of left-linear rewriting systems
-over $\mathcal{M}$-adhesive categories, which encompasses most of the
-structures commonly used in analysing and modelling applications.
-
-We showed that the canonical notion of independence adopted for linear
-systems does not enjoy some properties that are essential for
-developing a sensible theory of concurrency, notably a Church-Rosser
-theorem, and we identified a subclass of left-linear rewriting systems,
-which we call well-switching, as an appropriate setting where 
-many key results can be re-established. Specifically, a Church-Rosser 
-theorem, i.e.~the possibility of performing independent steps in any order, is
-fully recovered. Moreover, the switch construction and correspondingly
-the switch equivalence, at the core of a theory of concurrency for
-rewriting systems, enjoy a number of fundamental properties: a weak form of globality of independence, 
-consistency of switching and
-the existence of a canonical form for switch equivalence proofs.
-
-The class of well-switching $\mathcal{M}$-adhesive rewriting systems is large. Generalising a result in~\cite{baldan2011adhesivity},
-we showed that one of its defining properties (the fact that sequential independence implies switchability) holds 
-for a general class of $\mathcal{M}$-adhesive categories that include all presheaves over $\cat{Set}$. Moreover, the second property, uniqueness 
-of switching, is ensured when rewriting possibly hierarchical graphical structures, as long as elements belonging to the sorts 
-of the roots  are not merged (e.g., one can consider rewriting systems over directed graphs where only nodes are merged, as it 
-happens in most of the approaches to the modelling of calculi and biological systems that we cited in the introduction, 
-as well as in string diagrams).
-
-In the DPO approach to rewriting, the notion of sequential
-independence, identifying consecutive rewriting steps that %are independent and thus
-can be performed in reverse order is typically
-closely linked to that of \emph{parallel
-	independence}~\cite{ehrig2014adhesive}. Parallel independence
-relates two rewriting steps starting from
-the same object, which can be applied in
-any order producing, up to isomorphism, the same resulting
-object. Parallel independent steps, when applied in sequence, lead to
-sequential independent steps and, conversely, from two sequential
-independent steps, as a byproduct of the switch construction, one can
-get two parallel independent steps.
-
-Under mild additional conditions, one can have a notion of \emph{parallel rule} in a way that two
-parallel independent steps can be also combined in a single rewriting step.
-Even if this is not discussed explicitly in the paper, our theory can be easily accommodated to encompass a notion of parallel independence and parallel rule application, enjoying the properties outlined above.
-To ensure this, however, one must require that the underlying category $\X$ has binary coproducts and that the class $\mathcal{M}$ is closed under them.
-
-The results in this paper open the way to the development of a
-concurrent semantics for left-linear rewriting systems over $\mathcal{M}$-adhesive
-categories. In~\cite{baldan2017domains} the authors argue that for
-computational systems that allow one to express merging or fusions,
-the right semantical models are weak prime domains, a generalisation
-of prime domains, a staple in concurrency theory, and connected event
-structures, their event-based counterpart. The mentioned paper
-discusses only the case of graph rewriting and does not focus into the
-problems induced by the occurring of ``merges'' to the theory of rewriting (the systems
-considered there are implicitly assumed to be well-switching). 
-We plan to consolidate the statement that weak prime domains are 
-``the'' model for systems with fusions by showing that they allow to provide a semantics
-for left-linear rewriting systems in $\mathcal{M}$-adhesive categories.
-
-On the practical side, the present paper just surveyed the possibility
-of modelling e-graphs. This appears to be quite interesting as
-concurrent rewriting on such structures is an active area of
-research~\cite{abs-2208-06295}.
-We plan to make the correspondence precise
-and investigate how the analysis techniques enabled by a concurrent
-semantics of rewriting can impact on e-graphs.
-
-\bibstyle{plainurl}
-\bibliography{bibliog.bib}
-
-\appendix
-\section{Properties of $\mathcal{M}$-adhesive categories}\label{app:ade}
-
-This first appendix is devoted to the proofs of a few well-known results about $\mathcal{M}$-adhesive categories.
-%
-Observe that our notion of $\mathcal{M}$-adhesivity follows
-\cite{ehrig2012,ehrig2014adhesive} and is different from the one of
-\cite{azzi2019essence}. What is called $\mathcal{M}$-adhesivity in
-the latter paper corresponds to our strict
-$\mathcal{M}$-adhesivity. Moreover, in \cite{azzi2019essence} the
-class $\mathcal{M}$ is assumed to be only stable under
-pullbacks. However, if $\mathcal{M}$ contains all split monos, then
-stability under pushouts can be deduced from the other
-axioms~\cite[Prop.~$5.1.21$]{castelnovo2023thesis}.
-
-\subsection{Some results on $\mathcal{A}$-stable and $\mathcal{A}$-Van Kampen squares}
-We start proving some general results regarding $\mathcal{A}$-Van Kampen and $\mathcal{A}$-stable squares.
-Let us begin recalling some classical results about  about pullbacks and pushouts\cite{mac2013categories}.
-
-\noindent 
-\parbox{10.5cm}{\begin{lemma}\label{lem:popb1} \label{lem:pb1} \label{lem:po1}
-Let $\X$ be a category, and consider the diagram  on the right, then the following hold
-	\begin{enumerate}
-		\item if the right square is a pullback, then the whole rectangle is a pullback if and only if the left square is one;
-		\item if the left square is a pushout, 	then the whole rectangle is a pushout if and only if the right square is one.
-	\end{enumerate}
-\end{lemma}}
-\parbox{4cm}{$\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}$}\\
-
-The following proposition establishes a key property of $\mathcal{A}$-Van Kampen squares with a mono as a side: they are not only pushouts, but also pullbacks \cite{ehrig2004adhesive,BehrHK23,lack2005adhesive}.
-
-\noindent 
-\parbox{11.5cm}{\begin{proposition}\label{prop:pbpo} Let $\mathcal{A}$ be a class of arrows stable under pushouts and containing all the isomorphisms.
-If the square to the right is $\mathcal{A}$-Van Kampen and $m\colon A\to C$ is mono and belongs to $\mathcal{A}$, then the square is a pullback and $n$ is a monomorphism.
-\end{proposition}}
-\parbox{2cm}{\vspace{1.5ex}$\xymatrix{A\ar[r]^{g} \ar[d]_{m} & B \ar[d]^{n} \\ C \ar[r]_{f}  & D}$}
-
-The previous proposition allows us to establish the following result.
-
-\noindent \parbox{7.4cm}{
-\begin{lemma}\label{lem:varie}Let $\mathcal{A}$ be a class of arrows stable under pullbacks, pushouts and containing all isomorphisms.
-Suppose that the left square aside is $\mathcal{A}$-Van Kampen, while the vertical faces in the right cube are pullbacks.
-	Suppose moreover that $m\colon A\to C$ and $d\colon D'\to D$ are mono and that $d$ belongs to $\mathcal{A}$.
-Then $d\leq n$ if and only if $c \leq m$.
-\end{lemma}}
-	\parbox{6cm}{$\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{g'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{g}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){f'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){g} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{f} &&D&&C \ar[rr]_{f} & & D}$}
-
-\noindent 
-\parbox{11cm}{\begin{remark}
-	Recall that, given two monos $m:M\to X$ and $n:N\to X$ with the same codomain, $m\leq n$ means that there exists a, necessarily unique and necessarily mono, $k:M\to N$ fitting in the triangle aside.
-
-	\hspace{15pt}Notice, moreover, that  if $m\leq n$ and $n\leq m$, then the arrow $k:M\to N$ is an isomorphism.
-\end{remark}}
-\parbox{4cm}{$\xymatrix@C=15pt{M\ar@{.>}[rr]^{k}  \ar[dr]_{m}&& N \ar[dl]^{n}\\ & X}$}\\
-
-Finally, we show that $\mathcal{A}$-stable pushouts enjoy a \emph{pullback-pushout decomposition} property.
-
-\noindent 
-\parbox{10cm}{
-\begin{proposition}\label{prop:stab}Let $\X$ be a category and $\mathcal{A}$ a class of arrows stable under pullbacks.
-Suppose that, in the diagram aside, the whole rectangle is an $\mathcal{A}$-stable pushout and the right square a pullback.
-If the arrow $k$ is in $\mathcal{A}$ and it is a monomorphism,  then both squares are pushouts.
-\end{proposition}}
-\parbox{4cm}{\vspace{-.3cm}
-	$\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}$}
-
-\subsection{Useful properties of $\mathcal{M}$-adhesive categories}
-
-We are now going to apply the results of the previous section to $\mathcal{M}$-adhesive categories in order to establish some \emph{high-level replacement properties} \cite{ehrig2004adhesive,ehrig2014adhesive,ehrig2006fundamentals}.
-A first important  result that can be immediately established, with the aid of \Cref{prop:pbpo}, is the following one.
-
-\begin{proposition}
-	\label{prop:pbpoad}
-	Let $\X$ be an $\mathcal{M}$-adhesive category. Then
-	$\mathcal{M}$-pushouts are pullbacks.
-\end{proposition}
-
-From \Cref{prop:pbpoad}, in turn, we can derive the following corollaries.
-\begin{corollary}\label{cor:rego}
-	In a $\mathcal{M}$-adhesive category $\X$, every $m\in\mathcal{M}$ is a regular mono.
-\end{corollary}
-
-The following result now follows at once noticing that a regular monomorphism which is also epic is automatically an isomorphism.
-
-\begin{corollary}\label{prop:bal}
-	If $\X$ is an $\mathcal{M}$-adhesive categories, then every epimorphism in $\mathcal{M}$ is an isomorphism.
-In particular, every adhesive category $\X$ is \emph{balanced}: if a morphism is monic and epic, then it is an isomorphism.
-\end{corollary}
-
-\noindent 
-\parbox{10cm}{\begin{lemma}[$\mathcal{M}$-pushout-pullback decomposition]\label{lem:popb} Let $\X$ be an $\mathcal{M}$-adhesive category  and suppose that, in the diagram aside, the whole rectangle is a pushout and the right square a pullback.
-Then the following statements hold
-\parbox{13cm}	{\begin{enumerate}
-		\item if $a$ belongs to $\mathcal{M}$ and $k$ is a mono,  then both squares are pushouts and pullbacks;
-		\item if $f$ and $k $ are in  $\mathcal{M}$, then both squares are pushouts and pullbacks.
-	\end{enumerate}}
-\end{lemma}}
-\parbox{4cm}{\vspace{-1cm}
-	$\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}$}\\
-
-Let us turn our attention to pushout complements.
-
-\noindent
-\parbox{11cm}{
-	\begin{definition}[Pushout complement]
-		Let $f\colon X\to Y$ and $g\colon Y\to Z$ be two composable arrows in a category $\X$.
-A \emph{pushout complement} for the pair $(f,g)$ is a pair $(h,k)$ with $h\colon X\to W$ and $k\colon W\to Z$ such that the square aside is a pushout.
-	\end{definition}} \quad
-\parbox{4cm}{\vspace{.1cm}
-	$\xymatrix{X \ar[r]^{f} \ar[d]_{h}& Y \ar[d]^{g} \\ W \ar[r]_{k}& Z}$}\\
-
-Working in an $\mathcal{M}$-adhesive category we can guarantee that pushout complements are unique.
-
-\noindent
-\parbox{8.5cm}{
-	\begin{lemma}\label{lem:radj}
-		Let $f\colon X \to Y$ be an arrow in an $\mathcal{M}$-adhesive category $\X$ and suppose that the left square aside is a pushout while the  right one is a pullback, with $ m\colon M \rightarrowtail X$ and $n\colon N \rightarrowtail Y$ in $\mathcal{M}$.
-		Then $n\leq k$ if and only if $p_2\leq m$.
-	\end{lemma}}
-\parbox{3cm}{\vspace{-2ex}
-	$\xymatrix{M \ar@{>->}[d]_{m}\ar[r]^{h}& Q \ar@{>->}[d]^{k} & P \ar[r]^{p_1} \ar@{>->}[d]_{p_2}& N \ar@{>->}[d]^{n}\\X\ar[r]_{f}&Y &X \ar[r]_f&Y}$}
-
-\noindent
-\parbox{10cm}{
-	\begin{corollary}[Uniqueness of pushout complements]\label{lem:pocomp}
-		Let $\X$ be a $\mathcal{M}$-adhesive category.
-Given $m\colon X\mto Y$ in $\mathcal{M}$ and $f\colon Y\to Z$, let $(h_1, k_1)$ and $(h_2, k_2)$ be pushout complements of $m$  and $f$ depicted aside.
-Then there exists a unique isomorphism $\phi\colon W_1\to W_2$ making the diagram on the right commutative.
-	\end{corollary}}
-\parbox{3cm}{\vspace{1em}$\xymatrix{&X \ar@{>->}[r]^{m} \ar[d]_{h_1} \ar@/_.3cm/[dl]_{h_2}& Y \ar[d]^{f} \\ W_2 \ar@{>->}@/_.4cm/[rr]_{k_2} &W_1 \ar@{.>}[l]_{\phi} \ar@{>->}[r]^{k_1} & Z }$}
-
-\section{$\mathcal{M}$-adhesivity is not enough}\label{app:fill}
-In \Cref{sec:equi} we introduced the notion of strong enforcing left-linear rewriting system, a class that contains all the linear rewriting systems.
-This result can be further refined: in \cite{baldan2011adhesivity} a class  $\mathbb{B}$ of (quasi-)adhesive category is defined for which the local Church-Rosser Theorem holds for left-linear rewriting system.
-In our language, this means that every left-linear rewriting system based on a category in $\mathbb{B}$ is strong enforcing.
-This section is devoted to repropose, and slightly generalise, the results of \cite{baldan2011adhesivity} to our context.
-
-\noindent
-\parbox{10.4cm}{
-	\begin{definition}Let $\mathcal{M}$ be a class of monos in a category $\X$, closed under composition, containing all isomorphisms and stable under pullbacks and pushouts.
-Suppose that the  diagram aside is given and the whole rectangle is a pushout.
-We say that $\X$ satisfies
-		\parbox{14cm}{\begin{itemize}
-				\item the \emph{$\mathcal{M}$-mixed decomposition} property if, whenever $k$ belongs to $\mathcal{M}$ and the right half of the previous diagram is a pullback, then the left one is a pushout;
-				\item the \emph{$\mathcal{M}$-pushout decomposition} property if whenever $a, b$ and $c$ belongs to $\mathcal{M}$ and the right half of the diagram above is a pushout, then its left half is a pushout too.
-			\end{itemize}}
-	\end{definition}} \parbox{3cm}{\vspace{-2cm}$\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}$}\\
-
-The class of categories of type $\mathbb{B}$ is closed under the same constructions of \Cref{thm:slice-functors}.
-This can be deduced at once from the fact that in such categories pullbacks and pushouts are computed component-wise.
-
-\begin{lemma}\label{lem:closed} Let $\X$ be a category satisfying the $\mathcal{M}$-mixed and $\mathcal{M}$-pushout decomposition properties, then the following hold
-	\begin{enumerate}
-		\item  for every object $X$, $\X/X$ satisfies  the $\mathcal{M}/X$-mixed and the $\mathcal{M}/X$-pushout decomposition properties, while $X/\mathcal{M}$-adhesive satisfies their $X/\mathcal{M}$ variants, where
-		\[\mathcal{M}/X:=\{m\in \mathcal{A}(\X/X) \mid m\in \mathcal{M} \}
-		\qquad X/\mathcal{M}:=\{m\in \mathcal{A}(X/\X) \mid m\in
-		\mathcal{M} \}
-		\]
-		\item  for every small
-		category $\Y$, the category $\X^\Y$ satisfies the 
-		$\mathcal{M}^{\Y}$-mixed and the $\mathcal{M}^{\Y}$-pushout decomposition properties, where
-		\[\mathcal{M}^{\Y}:=\{\eta \in \mathcal{A}(\X^\Y) \mid \eta_Y \in
-		\mathcal{M} \text{ for every } Y\in \Y\}\]
-	\end{enumerate}
-\end{lemma}
-
-The following result shows that the mixed and pushout decomposition properties guarantee that every independence pair is strong.
-
-\begin{theorem}\label{thm:good1}Let $\X$ be an $\mathcal{M}$-adhesive category with all pushouts and satisfying the $\mathcal{M}$-mixed and the $\mathcal{M}$-pushout decomposition properties.
-Then every left-linear rewriting system on $\X$ is strong enforcing.
-\end{theorem}
-\begin{proof}
-	Consider the derivation $\der{D}=\{\dder{D}_i\}_{i=0}^1$, made by two sequentially independent derivations, depicted below
-	\[\xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0} && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{h_1} \\G_0 && \ar@{>->}[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar@{>->}[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2 }\]
-
-	We have to show that $(i_0, i_1)$ is a strong independence pair.
-Now, by hypothesis $\X$ has all pushouts, thus the only thing to show is that the squares below are pushouts (the third one is the usual pullback of $f_1\colon D_1\mto G_0$ along $g_0\colon D_0\to G_1$)
-	\[\xymatrix{K_0 \ar[r]^{r_0}  \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1 \ar@{>->}[r]^{l_1}  \ar[d]_{u_1}& L_1 \ar[d]^{i_1}&P \ar@{>->}[r]^{p_0} \ar[d]_{p_1}& D_0\ar[d]^{g_0} \\ P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0}  & D_0&D_1 \ar@{>->}[r]_{f_1} & G_1}\]
-
-	To see this, consider the following two diagrams
-	\[\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0} \ar[d]_{r_0} \ar[r]_{u_0}& \ar@{>->}[r]_{p_0} P \ar[d]_{p_1}& D_0 \ar[d]^{g_0}&K_1 \ar@/^.4cm/[rr]^{k_1} \ar@{>->}[d]_{l_1} \ar[r]_{u_1}& \ar[r]_{p_1} P \ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\ R_0 \ar@/_.4cm/[rr]_{h_0}  \ar[r]^{i_0}& D_1 \ar@{>->}[r]^{f_1}& G_1 &L_1 \ar@/_.4cm/[rr]_{m_1}  \ar[r]^{i_1}& D_0 \ar[r]^{g_0}& G_1}\]
-
-	The thesis now follows from the $\mathcal{M}$-mixed and the $\mathcal{M}$-pushout decomposition property.
-\end{proof}
-
-Our next step is to identify sufficient conditions for a category $\X$ to satisfy the mixed and $\mathcal{M}$-pushout decomposition properties.
-
-\begin{definition} 
-	Let $\X$ be an  $\mathcal{M}$-adhesive category, the pair $(\X, \mathcal{M})$ is of \emph{type $\mathbb{B}$} if
-	\begin{enumerate}
-		\item every arrow in $\mathcal{M}$ is a coproduct coprojection;
-		\item $\X$ has all pushouts;
-		\item $\X$ has strict initial objects and, for every object $X$, the unique arrow $?_X\colon 0\to X $ belongs to $\mathcal{M}$;
-		\item all pushouts are $\mathcal{M}$-stable.
-	\end{enumerate}
-\end{definition}
-
-\begin{remark}
-	It is worth to examine more closely conditions $1$ and $3$ of the above definition.
-	\smallskip 
-	\begin{itemize}
-	\parbox{10.3cm}{\item Let $m_0\colon X_0 \rightarrowtail Y$ be an arrow in $\mathcal{M}$, the first condition means that there exists $m_1\colon X_1\to Y$ such that $(Y, \{m_i\}_{i=0}^1)$ is a coproduct.
-This, together with property $3$, entails that every coprojection in a coproduct is in $\mathcal{M}$.
-This follows since any coproduct $(X_1+X_2, \{\iota_{X_i}\}_{i=0}^1)$ fits in a pushout diagram as the one aside.}
-	  \parbox{3cm}{\vspace{-0em}$\xymatrix@C=25pt{0  \ar@{>->}[r]^-{?_{X_1}} \ar@{>->}[d]^{?_{X_2}}& X_1 \ar@{>->}[d]^{\iota_{X_1}}\\ X_2 \ar@{>->}[r]_-{\iota_{X_2}} & X_1+X_2}$}
-
-	\smallskip 	\noindent 
-	\parbox{13.5cm}{\item $\X$ has strict initial objects if it has initial objects and every arrow $f:X\to 0$ is an isomorphism.
-Notice that if initial objects are strict, then $?_X\colon 0\to X$ is mono for every $X$: indeed for every pair $f,g\colon Y\rightrightarrows 0$ then, by strictness, $Y$ is initial and so $f=g$.}
-	\end{itemize} 
-\end{remark}
-
-\begin{example}
-The category $\Set$ of sets and functions, with its class of monos, is of type $\mathbb{B}$.
-Similarly, the category $\textbf{Inj}$ of sets and injective functions is quasiadhesive and, with its class of regular monos, of type $\mathbb{B}$.
-\end{example}
-
-Categories of type $\mathbb{B}$ satisfy a property resembling \emph{extensivity} \cite{carboni1993introduction}.
-
-\noindent
-\parbox{10cm}{\begin{proposition}\label{prop:ext}
-Let $(\X, \mathcal{M})$ be a pair of type $\mathbb{B}$.
-Then for every diagram as the one aside, in which the bottom row is a coproduct cocone and the vertical arrows are in $\mathcal{M}$, the top row is a coproduct if and only if the two squares are pullbacks.
-\end{proposition}}
-\parbox{2cm}{\vspace{-.4em}$\xymatrix{A\ar[r]^-{f} \ar@{>->}[d]_{r}& C  \ar@{>->}[d]_{s}& B \ar@{>->}[d]^{t}\ar[l]_-{g}\\X  \ar[r]_-{\iota_X}& X+Y & Y \ar[l]^-{\iota_Y}}$}
-
-\noindent 
-\parbox{4cm}{$\xymatrix@C=10pt@R=10pt{&I\ar@{>->}[dd]|\hole_(.65){a}\ar[rr]^{k} \ar[dl]_{h} && B \ar@{>->}[dd]^{t} \ar[dl]_{g} \\ A  \ar@{>->}[dd]_{r}\ar[rr]^(.7){f} & & C \ar@{>->}[dd]_(.3){s}\\&0\ar@{>->}[rr]|\hole^(.65){?_Y} \ar@{>->}[dl]^{?_X} && Y \ar@{>->}[dl]^{\iota_Y} \\X \ar@{>->}[rr]_{\iota_X} & & X+Y}$}
- \parbox{10cm}{\begin{proof}
-Consider the cube aside, in which the back faces are pullbacks.
-The bottom faces is an $\mathcal{M}$-Van Kampen pushout, thus the top face is a pushout if and only if the front faces are pullbacks.
-By strictness of $0$, $a\colon I\to 0$ is an isomorphism, so that $I$ is initial, therefore the $\mathcal{M}$-Van Kampen condition reduces to the request that $(C, \{f,g\})$ is a coproduct cocone if and only if the front faces are pullbacks, as claimed.
-\end{proof}}
-
-The previous result entails the following one, needed to show that  in any pair $(\X, \mathcal{M})$ of type $\mathbb{B}$, the category $\X$ satisfies the $\mathcal{M}$-mixed and $\mathcal{M}$-pushout decomposition properties.
-
-\noindent
-\parbox{10.7cm}{\begin{proposition}\label{prop:po2}
-		Let $(\X, \mathcal{M})$ be a pair of type $\mathbb{B}$, and suppose that the square aside is an $\mathcal{M}$-pullback.
-Then there exists $E\in \X$, $e\colon E\mto C$ in $\mathcal{M}$, $\phi:E\to B_1$ such that $(C, \{m, e\})$ is a coproduct and $g=f+\phi$.
-Moreover, such a square is a pushout if and only if $\phi$ is an isomorphism.
-\end{proposition}} \parbox{3cm}{\vspace{-.2cm}$\xymatrix{A  \ar[r]^{f} \ar@{>->}[d]_{m}& B_0 \ar@{>->}[d]^{\iota_{B_{0}}}\\ C\ar[r]_-{g} & B_0+B_1}$}
-
-\begin{lemma}\label{lem:prop} Let $(\X, \mathcal{M})$ be a pair of type $\mathbb{B}$, then $\X$ satisfies the $\mathcal{M}$-mixed and $\mathcal{M}$-pushout decomposition properties.
-\end{lemma}
-\begin{proof}$\mathcal{M}$-mixed decomposition property. This follows at once from \Cref{prop:stab}.
-
-	\medskip \noindent
-	\parbox{3cm}{$\xymatrix{X \ar[r]^f \ar@{>->}[d]_{\iota_X}& Y\ar[r]^g \ar@{>->}[d]^{\iota_Y} & Z\ar@{>->}[d]^{\iota_Z}\\X+A  \ar@/_.4cm/[rr]_{(g\circ f) + (\varphi \circ \phi)}\ar[r]^{f+\phi}& Y+B \ar[r]^{g+\varphi}& Z+C}$} \qquad \qquad  \qquad   \qquad \parbox{8cm}{ $\mathcal{M}$-pushout-decomposition property.
-Using \Cref{prop:ext,prop:po2} and the fact that arrows in $\mathcal{M}$ are coproduct coprojections, we can reduce to prove the property for diagrams as the one on the left.
-By hypothesis and \Cref{prop:po2}, $\varphi$ and $\varphi\circ \phi$ are both isomorphisms, therefore $\phi$ is an isomorphism too and we can conclude again using \Cref{prop:po2}.\qedhere
-}	
-\end{proof}
-
-\begin{definition} Let $\X$ be an $\mathcal{M}$-adhesive category, we say that the pair $(\X, \mathcal{M})$ is of \emph{type $\mathbb{B}^+$} if (at least) one of the following holds
-	\begin{enumerate}
-		\item $(\X, \mathcal{M})$ is of type $\mathbb{B}$;
-	\item $\X$ is $\Y/Y$ and $\mathcal{M}=\mathcal{N}/Y$for some $(\Y, \mathcal{N})$ of type $\mathbb{B}^+$ and $Y\in \Y$;
- 	\item $\X$ is $Y/\Y$ and $\mathcal{M}=Y/\mathcal{N}$for some $(\Y, \mathcal{N})$ of type $\mathbb{B}^+$ and $Y\in \Y$:
- 	\item $\X$ is $\Y^{\A}$ and $\mathcal{M}=\mathcal{N}^{\A}$ for some category category $\A$ and $(\Y, \mathcal{N})$ of type $\mathbb{B}^+$.
-	\end{enumerate}
-\end{definition}
-\begin{example}
-  \label{ex:graph-type-bb}
-	The pair $(\mathbf{Graph}, \mon(\mathbf{Graph}))$ made by the topos of graphs and its class of monos is of type $\mathbb{B}^+$  but not of type $\mathbb{B}$.
-Indeed, not every monomorphism of graphs is a coproduct coprojection.
-\end{example}
-
-From \Cref{lem:closed,lem:prop} we can now deduce at once the following.
-\begin{corollary}
-	For every $(\X, \mathcal{M})$ of type $\mathbb{B}^+$, the category $\X$ has the $\mathcal{M}$-mixed and $\mathcal{M}$-pushout decomposition properties.
-\end{corollary}
-
-Using \Cref{thm:good1} we finally get the main result of our appendix.
-\begin{corollary}
-  \label{cor:llr-is-strEnf}
-Let $(\X, \mathcal{M})$ be a pair of type $\mathbb{B}^+$, then every left-linear rewriting system is strong enforcing.
-\end{corollary}
-
-\section{Omitted proofs}\label{omitted}
-In this appendix we provide the proofs of the main results of this paper.
-
-\subsection{Proofs for \Cref{sec:ade}}
-
-\begin{proposition}
-  \label{prop:unique}
-  Let $\X$ be an $\mathcal{M}$-adhesive category. Suppose that the two
-  direct derivations $\dder{D}$ and $\dder{D}'$ below, with the same
-  match and applying the same left-linear rule $\rho$, are given
-  \[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} &
-      R \ar[d]^{h} & L \ar[d]_{m}& K \ar[d]^{k'}\ar@{>->}[l]_{l}
-      \ar[r]^{r} & R \ar[d]^{h'}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}& H
-      & G & \ar@{>->}[l]^{f'} D' \ar[r]_{g'}& H'}\]
-  Then there is an abstraction equivalence between $\dder{D}$ and
-  $\dder{D}'$, whose first component is $\id{G}$.
-\end{proposition}
-\begin{proof}
-  Both pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$
-  and $n$, thus, \Cref{lem:pocomp} yields an isomorphism
-  $\phi_D\colon D\to D'$. An easy computation shows that $g'\circ \phi_D \circ k=h'\circ r$.
-  \noindent
-  \parbox{3cm}{
-    $\xymatrix{K \ar@/^.4cm/[rr]^{k'}\ar[d]_{r} \ar[r]_{k}&
-      \ar[r]_{\phi_D} D \ar[d]^{g}& D' \ar[d]^{g'}\\ R
-      \ar@/_.4cm/[rr]_{h'} \ar[r]^{h}& H \ar[r]^{\phi_H}& H'}$}
-  \hfill
-  \parbox{10cm}{ \hspace{15pt}Hence, we have
-    $\phi_H\colon H\to H'$. To see that $\phi_H$ is an isomorphism,
-    consider the diagram aside. By hypothesis the whole rectangle and
-    its left half are pushouts, therefore, by \Cref{lem:po1} its right
-    square is a pushout too. The claim now follows from the fact that
-    the pushout of an isomorphism is an isomorphism. \qedhere }
-\end{proof}
-
-\subsection{Proofs for \Cref{sec:equi}}
-This section provides further details and proofs for the concepts introduced in \Cref{sec:equi}.
-
-\subsubsection{Proofs for \Cref{subsec:switch}}
-Consider a switch $\der{E}=\{\dder{E}_i\}_{i=0}^1$ for $\dder{D}_0$
-and $\dder{D}_1$, then by definition $\dder{E}_0$ and $\dder{E}_1$ are
-sequentially independent. We can then wonder if they are switchable.
-
-\begin{proposition}
-  \label{prop:switch}
-  Let $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation and suppose
-  that $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a switch for it. Then
-  $\der{D}$ is a switch for $\dder{E}_0$ and $\dder{E}_1$ along
-  $(i'_0, i'_1)$.
-\end{proposition}
-
-\begin{proof}
- Clearly $\der{D}$ uses the same rule of $\der{E}$ in reverse order. Moreover, since $\der{E}$ is a switch for $\der{D}$, we already know that
-   \begin{center}   
- 	$m_0=f_0' \circ i_1'$
- 	\qquad $h_1=g_1' \circ i_0'$
- 	\qquad $m_0'= f_0 \circ i_1$
- 	\qquad $h_1'= g_{1}\circ i_0$.
- \end{center}
-Since  these equations are those that must hold for $\der{D}$ to be a switch for $\der{E}$ along $(i_0', i_1')$ we can conclude.
-\end{proof}
-
-\begin{lemma}[Uniqueness of switches]
-  \label{thm:switch_uni}
-  Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation and suppose
-  that both $\der{E}=\{\dder{E}_i\}_{i=0}^1$ and
-  $\der{F}=\{\dder{F}_i\}_{i=0}^1$ are switches of $\dder{D}_0$ and
-  $\dder{D}_1$. Then $\der{E}$ and $\der{F}$ are abstraction
-  equivalent.
-\end{lemma}
-
-\begin{proof}
-    By definition of switch $\der{E}_0$ and $\der{F}_0$ have the same match $f_0\circ i_1$ and that $\der{E}_1$ and $\der{F}_1$ have the same comatch $g_1\circ i_0$.
-Thus we get the solid part of the diagram below
-    \[\xymatrix@C=22pt{G_{0} && \ar@{>->}[ll]_{f_{\der{F},0}} D_{\der{F},0} \ar[rr]^{g_{\der{F},0}}&& G_{\der{F},1} && \ar@{>->}[ll]_{f_{\der{F},1}} D_{\der{F},1} \ar[rr]^{g_{\der{F},1}}&& G_{2}\\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}&& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_{1} \ar@/^.35cm/[drrr]|(.3)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{h_{\der{E},0}} \ar@/_.35cm/[urrr]|(.3)\hole^(.4){a_0} \ar[ur]|(.3)\hole^{h_{\der{F},0}}& &L_{0} \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{m_{\der{E},1}} \ar@/^.35cm/[ulll]_(.4){a_1} \ar[ul]|(.3)\hole_{m_{\der{F},1}}& K_{0} \ar[d]_{k_{\der{E},1}} \ar[u]^{k_{\der{F},1}}\ar@{>->}[l]_{l_{0}} \ar[rr]^{r_0} && R_{0} \ar[d]_{g_1\circ i_0} \ar[u]^{g_1\circ i_0}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} && \ar[ll]^{f_{\der{E},0}} D_{\der{E},0} \ar@{.>}@/^.5cm/[uu]^(.33){\phi_{0}}|\hole \ar[rr]_{g_{\der{E},0}}&& G_{\der{E},1} \ar@{.>}[uu]^(.76){\psi_1}|(.45)\hole |(.55)\hole&& \ar@{>->}[ll]^{f_{\der{E},1}} D_{\der{E},1} \ar@{.>}@/_.5cm/[uu]_(.33){\phi_{1}}|\hole\ar[rr]_{g_{\der{E},1}}&& G_{2}\ar@{.>}@/_.5cm/[uu]_{\psi_2}}\]
-
-    \parbox{7cm}{\hspace{15pt}Now, by \Cref{prop:unique} we get $\phi_0\colon D_{\der{E},0}\to D_{\der{F},0}$ and $\psi_1 \colon G_{\der{E},1}\to G_{\der{F},1}$ such that the diagram aside commutes.
-But then we have
-    	\[
-    	f_{\der{F},0}\circ \phi_0\circ j_1=f_{\der{E},0} \circ j_1=m_0=f_{\der{F},0}\circ a_1\]
-    	which entails $a_1= \phi_0\circ j_1$.}
-\parbox{4cm} {$\xymatrix{G_{0} & \ar@{>->}[l]_{f_{\der{F},0}} D_{\der{F},0} \ar[r]^{g_{\der{F},0}}& G_{\der{F},1} \\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar[l]_{l_1} \ar[r]^{r_1} & R_{1}  \ar[d]_{h_{\der{E},0}}  \ar[u]^{h_{\der{F},0}}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} & \ar@{>->}[l]^{f_{\der{E},0}} D_{\der{E},0} \ar@/^.5cm/[uu]^(.33){\phi_{0}}|\hole \ar[r]_{g_{\der{E},0}}& G_{\der{E},1} \ar@/_.5cm/[uu]_{\psi_1}}$}
-
-     This, in turn, gives us that
-    \[\psi\circ m_{\der{E},1}=\psi \circ g_{\der{E},0}\circ j_1=g_{\der{F},0}\circ \phi_0\circ j_1=g_{\der{F},0}\circ a_1=m_{\der{F},1}\]
-
-    Now, the square on the left in the diagram below is a pushout and $\psi_1\circ m_{\der{E},1}=m_{\der{F},1}$.
-Thus, by \Cref{prop:unique} there are the dotted $\phi_1\colon D_{\der{E},1}\to D_{\der{F},1}$ and $\psi_2\colon G_2\to G_2$ in the diagram on the right
-    \[\xymatrix{&&G_{\der{F},1} & \ar@{>->}[l]_{f_{\der{F},1}} D_{\der{F},1} \ar[r]^{g_{\der{F},1}}& G_2 \\K_0 \ar[d]_{k_{\der{E,1}}} \ar@{>->}[r]^{l_0}& L_0 \ar[d]^{\psi_1\circ m_{\der{E},1}}&L_0 \ar[d]^{m_{\der{E},1}} \ar[u]_{m_{\der{F},1}}& K_{1} \ar[d]^{m_{\der{E},1}} \ar[u]_{m_{\der{F},1}}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_{1}  \ar[d]_{g_1\circ i_0}  \ar[u]^{g_1\circ i_0}\\D_{\der{E},1} \ar@{>->}[r]_{\psi_1\circ f_{\der{E},1}}& G_{\der{F}, 1}& \ar@/^.5cm/[uu]^{\psi_1} G_{\der{E},1} & \ar@{>->}[l]^{f_{\der{E},1}} D_{\der{E},1} \ar@{.>}@/^.5cm/[uu]^(.33){\phi_{1}}|\hole \ar[r]_{g_{\der{E},1}}& G_2 \ar@{.>}@/_.5cm/[uu]_{\psi_2}}\]
-
-    To conclude, it is now enough to notice that
-    \[f_{\der{F},1} \circ \phi_1\circ j_0=\psi_1\circ f_{\der{E},1}\circ j_0=\psi_1\circ h_{\der{E,0}}=h_{\der{F},0}=f_{\der{F},1}\circ a_0\]
-    allowing us to deduce $ \phi_1\circ j_0=a_0$.
-    \qedhere
-\end{proof}
-
-\begin{proposition}
-	\label{prop:tec}
-	Let $(\X,\R)$ be a left-linear rewriting system and
-	$(i_0, i_1)$ an independence pair between two direct
-	derivations $\dder{D}_0$ and $\dder{D}_1$. Consider the pullback of
-	$f_1\colon D_1\mto G_1$ along $g_0\colon D_0\to G_1$ (first
-	square below), then there exist the arrows
-	$u_1\colon K_1\to P$ and $u_0\colon K_0\to P$ fitting in the
-	central and right square. Moreover, the right one is always
-	a pullback.
-	\[\xymatrix@R=15pt{P \ar@{>->}[r]^{p_0} \ar[d]_{p_1} & D_0
-		\ar[d]^{g_0}& K_0 \ar[r]^{r_0} \ar@{.>}[d]_{u_0}& R_0
-		\ar[d]^{i_0} & K_1 \ar@{>->}[r]^{l_1} \ar@{.>}[d]_{u_1}&
-		L_1 \ar[d]^{i_1}\\ D_1 \ar@{>->}[r]_{f_1} &G_1 &P
-		\ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0}
-	\]
-\end{proposition}
-
-\begin{proof}
-	We start noticing that
-	\[
-	f_1\circ i_0\circ r_0=h_0\circ r_0=g_0\circ k_0 \qquad
-	g_0\circ i_1\circ l_1=m_1\circ l_1= f_1 \circ k_1
-	\]
-	Thus there exists the dotted $u_0\colon K_0\to P$,
-	$u_1\colon K_1\to P$ in the diagram
-	\[\xymatrix@R=15pt{K_0 \ar[d]_{r_0}
-		\ar@{.>}[r]_{u_0}\ar@/^.4cm/[rr]^{k_0} &P
-		\ar@{>->}[r]_{p_0} \ar[d]_{p_1}& D_0 \ar[d]^{g_0}&K_1
-		\ar@{>->}[d]_{l_1}
-		\ar@{.>}[r]_{u_1}\ar@/^.4cm/[rr]^{k_1} &P \ar[r]_{p_1}
-		\ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\R_0
-		\ar@/_.4cm/[rr]_{h_0}\ar[r]^{i_0}& D_1
-		\ar@{>->}[r]^{f_1}& G_1&L_1
-		\ar@/_.4cm/[rr]_{m_1}\ar[r]^{i_1}& D_0 \ar[r]^{g_0}&
-		G_1}\]
-	By \Cref{prop:pbpoad,lem:pb1} we get that the left half of
-	the second rectangle is a pullback.
-	\qedhere
-\end{proof}
-
-There is another
-useful property of  sequentially independent direct
-derivations that is worth mentioning.
-
-\noindent
-\parbox{9.5cm}
-{\begin{proposition}\label{lem:cose}Let
-    $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation and suppose
-    that $(i_0, i_1)$ is an independence pair between $\dder{D}_0$
-    and $\der{D}_1$.  If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a
-    switch of $\der{D}$ along $(i_0, i_1)$, then there exists
-    $q_0\colon P\to D_{\der{E},0}$ in the diagram
-    aside. \end{proposition}}
-\parbox{4cm}{$\xymatrix{D_{\der{E},0} \ar@{>->}[d]_{f_{\der{E},0}}&P
-    \ar@{.>}[l]_{q_0} \ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1
-    \ar@{>->}[d]^{f_1}\\ G_{0}&D_0 \ar@{>->}[l]^{f_0}\ar[r]_{g_0}&
-    G_1}$}
-
-\begin{proof}
-  Consider the arrow $u_1\colon K_1\to P$ obtained using
-  \Cref{prop:tec}. It fits in the big square on the left
-\[		\xymatrix@R=15pt{K_1 \ar[r]^{u_1} \ar@{>->}[d]_{l_1}&P
-	\ar[r]^{\id{P}}\ar@{>->}[d]_{p_0}& P\ar@{>->}[d]^{p_0}\\L_1
-	\ar[d]_{\id{L_1}}\ar[r]^{i_1}&D_0 \ar[r]^{\id{D_0}}
-	\ar[d]_{\id{D_0}}& D_{0} \ar@{>->}[d]^{f_0}&K_1 \ar@{>->}[d]_{l_1}\ar[r]^{k_{\der{E},0}}&
-	D_{\der{E},0} \ar@{>->}[d]^{f_{\der{E},0}} & K_1 \ar[r]^{u}
-	\ar@{>->}[d]_{l_1}& P \ar@{>->}[d]^{f_0\circ
-		p_0}\\
-	L_1\ar[r]^{i_1} \ar@/_.4cm/[rr]_{m_{\der{E},0}}&D_0
-	\ar@{>->}[r]^{f_0}&G_0 & L_1\ar[r]_{m_{\der{E},0}}&G_0 &L_1
-	\ar[r]_{m_{\der{E},0}}&G_0}\]
-
-  	Since $f_0$ is a monomorphism, every square in the diagram on the left above
-  	is a pullback. Thus the whole big square is a pullback too.
-  	Applying \Cref{lem:radj} to the pair of squares on the right now gives
-  	us the wanted $q_0\colon P\to D_{\der{E},0}$.
-\end{proof}
-
-\subsubsection{Proofs for \Cref{subsec:CR}}
-
-To prove the Local Church-Rosser Theorem, let us begin by deducing some properties from the existence of a strong independence pair.
-
-\begin{remark}\label{rem:deco} 
-	Let $(i_0, i_1)$ be a strong
-	independence pair between the direct derivations $\dder{D}_0$ and
-	$\dder{D}_1$. We can then build the solid part of the diagram
-	below
-	\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
-		\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
-		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
-		\ar@/_.6cm/[ddrr]^(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
-		\ar@/^.6cm/[ddll]_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
-		\ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0}
-		\ar@{.>}@/_.6cm/[ddrr]_{j_1}&& D_0
-		\ar@{>->}[dl]|(.42)\hole_(.64){f_0}\ar[ur]|(.48)\hole^(.7){g_1}&&D_1
-		\ar[dr]|(.42)\hole^(.65){g_1}
-		\ar@{>->}[ul]|(.48)\hole_(.7){f_1}&&R_1\ar@/^.6cm/[ddll]^{j_0}\ar[dl]^{h_1}\\&G_0
-		&&P\ar[dr]^{q_1}
-		\ar@{>.>}[dl]_{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\&&Q_0
-		\ar@{>->}@{>.>}[ul]_{a_0} &&Q_1\ar@{.>}[ur]^{b_1}}
-	\]
-
-	Let us complete this diagram defining the dotted arrows. To get
-	$j_1\colon L_0\to Q_0$ and $q_0\colon P\to Q_0$ it is enough to
-	take a pushout of $l_0$ along $u_0$, which exists since
-	$l_0\in \mathcal{M}$. Moreover, the existence of the wanted
-	$a_0\colon Q_0\to G_0$ and $b_1\colon Q_1\to G_2$ follows from
-	\[
-	f_0\circ p_0 \circ u_0 = f_0\circ k_0 = m_0\circ l_0 \qquad
-	g_1\circ p_1\circ u_1 = g_1\circ k_1=h_1\circ r_1
-	\]
-
-	\noindent
-	\parbox{5.5cm}{\hspace{15pt}We can prove some other properties of
-		the arrows appearing in the diagram above. The four rectangles
-		aside are pushouts and their left halves are pushouts
-		too. Therefore, by \Cref{lem:po1} also their right halves are
-		pushouts.  Moreover, $q_0$ and $a_0$ are pushouts of
-		respectively $l_0$ and $p_0$, thus they are elements of
-		$\mathcal{M}$. By \Cref{prop:pbpoad} the left halves of the
-		first and third rectangles are pullbacks too.}  \parbox{3.5cm}{
-		$\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar[d]_{r_0}\ar[r]_{u_0}
-			&P\ar[d]^{p_1} \ar@{>->}[r]_{p_0} & D_0 \ar[d]^{g_0}&K_1
-			\ar@/^.4cm/[rr]^{k_1}\ar@{>->}[d]_{l_1}\ar[r]_{u_1}
-			&P\ar@{>->}[d]^{p_0} \ar[r]_{p_1} & D_1 \ar@{>->}[d]^{f_1}\\
-			R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i_0}&D_1 \ar@{>->}[r]^{f_1}
-			& G_1&L_1 \ar@/_.4cm/[rr]_{m_1} \ar[r]^{i_1}&D_0\ar[r]^{g_0} &
-			G_1}$
-		$\xymatrix{K_0
-			\ar@/^.4cm/[rr]^{k_0}\ar@{>->}[d]_{l_0}\ar[r]_{u_0}
-			&P\ar@{>->}[d]^{q_0} \ar@{>->}[r]_{p_0} & D_0
-			\ar@{>->}[d]^{f_0}&K_1
-			\ar@/^.4cm/[rr]^{k_1}\ar[d]_{r_1}\ar[r]_{u_1}
-			&P\ar[d]^{q_1} \ar[r]_{p_1} & D_1 \ar[d]^{g_1}\\
-			L_0 \ar@/_.4cm/[rr]_{m_0} \ar[r]^{j_1}&Q_0 \ar@{>->}[r]^{a_0}
-			& G_0&R_1 \ar@/_.4cm/[rr]_{h_1} \ar[r]^{j_0}&Q_1 \ar[r]^{b_1}
-			& G_2}$}
-\end{remark}
-
-\prChurch*
-\label{prChurch-proof}
-
-\begin{proof}
-
-  Let us begin considering the diagram
-  built in \Cref{rem:deco}
-  \[\xymatrix@C=15pt@R=15pt{&&R_0
-      \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole \ar[dr]^{h_0}&&
-      L_1\ar@/^.8cm/[ddll]^(.2){i_1}
-      \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
-      \ar@/_.6cm/[ddrr]^(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
-      \ar@/^.6cm/[ddll]_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
-      \ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0} \ar@{>}@/_.6cm/[ddrr]_{j_1}&& D_0
-      \ar@{>->}[dl]|(.42)\hole_(.64){f_0}\ar[ur]|(.48)\hole^(.7){g_1}&&D_1
-      \ar[dr]|(.42)\hole^(.65){g_1}
-      \ar@{>->}[ul]|(.48)\hole_(.7){f_1}&&R_1\ar@/^.6cm/[ddll]^{j_0}\ar[dl]^{h_1}\\&G_0
-      &&P\ar[dr]^{q_1}
-      \ar@{>->}[dl]_{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\&&Q_0
-      \ar@{>->}@{>->}[ul]_{a_0} \ar@{.>}[dr]_{b_0} &&Q_1\ar[ur]^{b_1}
-      \ar@{>.>}[dl]^{a_1} \\ &&&H_1 }\] Since $q_0\colon P\to Q_0$ is in
-  $\mathcal{M}$, we can take its pushout along $q_1$ to get the dotted
-  arrows $a_1\colon Q_1\to H_1$ and $q_0\colon Q_0\to H_1$. But then,
-  since the composite of two pushout squares is a pushout, the diagram
-  below is a derivation
-  \[\xymatrix@C=15pt{L_1 \ar[d]_{f_0 \circ i_1}&& K_1
-      \ar[d]_{q_0\circ u_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1
-      \ar@/^.35cm/[drrr]|(.3)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{a_1\circ
-        j_0} && L_0 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{b_0\circ
-        j_1}& K_1 \ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
-      \ar[d]^{g_1\circ i_0} \\G_0 && \ar@{>->}[ll]^{a_0} D_0 \ar[rr]_{b_0}&&
-      G_1 && \ar@{>->}[ll]^{a_1} D_1 \ar[rr]_{b_1}&& G_2}\] It is immediate
-  now to see that it is a switch of $\dder{D}_0$ and $\dder{D}_1$ along
-  $(i_0, i_1)$.
-\end{proof}
-
-\begin{remark}
-	\label{rem:church}
-	It is worth to point out that, by
-	\Cref{prop:switch,thm:switch_uni}, the derivation we obtain from
-	\Cref{pr:church} %\todo{missing} 
-	is made by two switchable derivations that will
-	give back the starting derivation (up to abstraction equivalence),
-	if switched again.
-
-	Moreover, by \Cref{prop:pbpoad}, the first square below is a
-	pullback, therefore, by \cref{rem:deco} the last three squares
-	witness that $(j_0, j_1)$ is a strong independence pair too.
-	\[
-	\xymatrix@R=15pt{P\ar[r]^{q_1} \ar@{>->}[d]_{q_0}&Q_1
-		\ar@{>->}[d]^{a_1}&K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1
-		\ar[d]^{j_0} & K_0 \ar@{>->}[r]^{l_0} \ar[d]_{u_0}& L_0
-		\ar[d]^{j_1}&K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0\ar[d]^{i_0} \\
-		Q_ 0\ar[r]_{b_0}&H_1&P \ar[r]_{q_1} & Q_1 &P \ar[r]_{q_0} &
-		Q_0&P \ar[r]_{p_1} & D_1}
-	\]
-\end{remark}
-
-\begin{proposition}
-  \label{prop:equi}
-  Every linear rewriting system $(\X, \R)$ is strong enforcing.
-\end{proposition}
-
-\begin{proof}
-  Suppose that $\X$ is $\mathcal{M}$-adhesive and let $(i_0, i_1)$ be
-  an independence pair as below
-  \[
-    \xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0
-      \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar@{>->}[r]^{r_0} & R_0
-      \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0}
-      && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
-      \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar@{>->}[rr]^{r_1} && R_1
-      \ar[d]^{h_1} \\G_0 && \ar@{>->}[ll]^{f_0} D_0
-      \ar@{>->}[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
-      \ar@{>->}[rr]_{g_1}&& G_2}\]
-
-  Since $(\X, \R)$ is linear, then $r_1\colon K_1\to R_1$ belongs to
-  $\mathcal{M}$, thus it admits a pushout along $u_1\colon K_1\to P$,
-  as desired. Moreover, let us consider the two rectangles below
-  \[
-    \xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar@{>->}[d]_{r_0}\ar[r]_{u_0}
-      &P\ar@{>->}[d]^{p_1} \ar@{>->}[r]_{p_0} & D_0
-      \ar@{>->}[d]^{f_0}& K_1
-      \ar@/^.4cm/[rr]^{k_1}\ar@{>->}[d]_{l_1}\ar[r]_{u_1}
-      &P\ar@{>->}[d]^{p_0} \ar@{>->}[r]_{p_1} & D_1
-      \ar@{>->}[d]^{f_1}\\ R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i_0}&D_1
-      \ar@{>->}[r]^{f_1} & G_1& L_1 \ar@/_.4cm/[rr]_{m_1}
-      \ar[r]^{i_1}&D_0 \ar@{>->}[r]^{g_0} & G_1} \] By hypothesis
-  $r_0$ and $l_1$ are in $\mathcal{M}$, thus $f_1$ and $g_0$ belong to
-  it too. The first point of \Cref{lem:popb} yields the thesis.
-\end{proof}
-
-\begin{remark}\label{rem:fill} Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ be a derivation and $(i_0, i_1)$ a strong independence pair between $\dder{D}_0$ and $\dder{D}_1$.
-Let also $\{\der{E}_{i}\}_{i=0}^1$ be a switch for them along $(i_0, i_1)$.
-Since, by \Cref{thm:switch_uni}, all switches are abstraction equivalent, we get the diagram below
-	\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
-		\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
-		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
-		\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){u_0}\ar[ur]^{r_0}&& G_1 &&
-		K_1
-		\ar@/^.6cm/[ddll]|(.36)\hole_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
-		\ar[dr]^{r_1}\\L_0
-		\ar@/_.6cm/[ddrr]_(.2){i'_0}|(.31)\hole|(.81)\hole
-		\ar[dr]^(.4){m_0}|(.61)\hole && D_0
-		\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1
-		\ar[dr]|(.4)\hole^(.65){g_1}
-		\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
-		&&P_1\ar[dr]_{q_1}	\ar@{>->}[dl]^{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole^(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole_(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_1}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_0} |(.69)\hole }\]
-
-\end{remark}
-
-\subsubsection{Proofs for \Cref{subsec:verytame}}
-
-\begin{proposition}\label{pr:weak} Every linear rewriting system is well-switching.
-\end{proposition}
-\begin{proof}
-
-	Let $(i_0, i_1)$ and $(i'_0, i'_1)$ be independence pairs for the
-	direct derivations $\dder{D}$ and $\dder{D}'$. Notice that, by
-	definition, we have
-	\[
-	f_1\circ i_0=h_0=f_1\circ i'_0 \qquad g_0\circ i_1=m_1= g_0\circ i'_1
-	\]
-
-	The arrow $f_1\colon D\to G_1$ is the pushout of
-	$l_1\colon K_1\mto L_1$, thus it is in $\mathcal{M}$ implying
-	$i_0=i'_0$. If, moreover, we suppose that the rule $\rho$ applied in
-	$\dder{D}$ is linear, then $g_0\colon D_0\to G_1$ is in
-	$\mathcal{M}$ too, entailing $i_1=i'_1$.
-\end{proof}
-
-\begin{remark}\label{rem:po}
-	Notice that $\gph{X}$ is adhesive and that pushouts are computed component-wise, thus if $g\colon F\to G$ is the pushout of $r\colon K\to R$, then $g_X\colon F(X)\to G(X)$ is mono for every root $X$.
-\end{remark}
-
-\lemVTame*
-\label{lemVTame}
-
-\begin{proof}
-	Every root-preserving graphical rewriting system is strong enforcing because $\gph{G}$ is in the class $\mathbb{B}^+$ defined in \Cref{app:fill}.  Consider the following diagram 
-	\[\xymatrix@R=25pt@C=30pt{L_0 \ar[d]_{m_0}&& K_0
-		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
-		\ar@<-.5ex>@/^.35cm/[drrr]|(.23)\hole|(.34)\hole_(.4){i_0} 	\ar@<.5ex>@/^.35cm/[drrr]^(.2){j_0}|(.31)\hole |(.4)\hole
-		\ar[dr]|(.3)\hole_{h_0} && L_1 \ar@<.5ex>@/_.35cm/[dlll]^(.4){i_1} \ar@<-.5ex>@/_.35cm/[dlll]_(.2){j_1}
-		\ar[dl]|(.3)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
-		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
-		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
-		\ar[rr]_{g_1}&& G_2}\]
-
-	Since $f_1$ is mono then $i_0=j_0$. For every  root $X$ we have
-	\[g_{0,X}\circ i_{1,X}=m_{1,X}=g_{0,X}\circ j_{1,X}\]
-	which entails $i_{1,X}=j_{1,X}$.
-Let now $Y$ be another object, and take $y\in L_1(Y)$.
-By definition, we have a root $X$ and an arrow $f:X\to Y$ and $x\in L_{1}(X)$ such that $L(f)(y)=x$.
-By naturality we have
-	\[i_{1,Y}(y)=i_{1,Y}(L(f)(x))=L(f)(i_{1, X}(x))=L(f)(j_{1, X}(x))=j_{1,X}(L(f)(x))=j_{1,Y}(y)\]
-Thus $i_{1,Y}=j_{1,Y}$, as wanted.
-\end{proof}
-
-\subsubsection{Proofs for \cref{subsec:canonical}}
-
-The section opens recalling the definition of \emph{consistent permutation} for the interested reader.
-
-\begin{definition}[Consistent permutation]
-	\label{def:permcon}
-	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ 
-	a left-linear rewriting system.  Take two derivations $\der{D}:=\{\dder{D}_i\}_{i=0}^n$ and
-	$\der{D}':=\{\dder{D}'_i\}_{i=0}^n$ with the same length and with isomorphic sources and targets.
-	Let also $r(\der{D})=\{\rho_i\}_{i=0}^n$ and
-	$r(\der{D}')=\{\rho'_i\}_{i=0}^n$ be the  associated sequence of rules. 
-	A \emph{consistent permutation}
-	between $\der{D}$ and
-	$\der{D}'$ is a permutation
-	$\sigma\colon [0,n]\to [0,n]$ such that, for every $i\in [0,n]$,
-	$\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a
-	\emph{mediating isomorphism}
-	$\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the
-	following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, the matches and co-matches of $\dder{D}_i$ and
-	$\dder{D}'_i$.
-	\[
-	\xymatrix@C=30pt{L_i
-		\ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}}
-		&\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i}
-		\ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}}
-		&\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)}
-		\ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro&
-		G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro
-		\der{D}' \rpro}
-	\]
-\end{definition}
-
-We can now turn to the proofs of the results of \Cref{subsec:canonical}.
-
-\begin{notation}
-  Recall that by \cref{thm:switch_uni} switches are uniquely
-  determined, up to abstraction equivalence.
-  %
-  In the sequel we denote any switch of two switchable direct
-  derivations $\dder{D}_0$ and $\dder{D}_1$ along an independence pair
-  $(i_0, i_1)$ by $S_{i_0, i_1}(\dder{D}_0, \dder{D}_1)$. Moreover, we
-  use $S_{i_0,i_1}(\dder{D}_1)$ and $S_{i_0,i_1}(\dder{D}_0)$ to
-  denote its components, in such a way that
-  $S_{i_0, i_1}(\dder{D}_0, \dder{D}_1)=S_{i_0,i_1}(\dder{D}_1)\cdot
-  S_{i_0,i_1}(\dder{D}_0)$.
-\end{notation}
-
-\lemIndepGlobalLeft*
-\label{lemIndepGlobalLeft-proof}
-
-\begin{proof}   
-	Since $(\X, \R)$ is well-switching, there exists unique independence pairs 
-$(i_0,i_1)$ between $\dder{D}_0$ and $\dder{D}_1$,	$(a_0,a_1)$ between $\dder{D}_1$ and $\dder{D}_2$ and	$(e_0, e_1)$ between $\dder{D}_0$ and
-	$S_{a_0,a_1}(\dder{D}_2)$.
-	Using \Cref{rem:fill} we can build the diagrams in \Cref{fi:first,fi:second,fi:third}.
-The first depicts the  switching $\dder{D}_0$ and $\dder{D}_1$ along  $(i_0, i_1)$, the second that of $\dder{D}_1$ and $\dder{D}_2$ along $(a_0, a_1)$, while the third refers to $\dder{D}_0$ and
-	$S_{a_0,a_1}(\dder{D}_2)$.
-
-	\begin{figure}[h]
-		\centering
-		$\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
-			\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
-			\ar[dl]_{m_1}\\&K_0\ar@{>->}[dr]^{k_0}\ar[dl]_{l_0}
-			\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){v_0}\ar[ur]^{r_0}&& G_1 &&
-			K_1
-			\ar@/^.6cm/[ddll]|(.36)\hole_(.65){v_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
-			\ar[dr]^{r_1}\\L_0
-			\ar@/_.6cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole
-			\ar[dr]^(.4){m_0}|(.61)\hole && D_0
-			\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1
-			\ar[dr]|(.4)\hole^(.65){g_1}
-			\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_(.4){h_1}|(.6)\hole\\&G_0
-			&&P_1\ar[dr]_{q_1}
-			\ar@{>->}[dl]^{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1
-			\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ
-				i_1}|(.61)\hole&&Q_0
-			\ar@{>->}[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0}
-			&&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar@{>->}[dl]|(.5)\hole_(.65){s_1}
-			&& R_0 \ar[ul]^(.35){g_1\circ
-				i_0}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\&K_1
-			\ar[ur]_{q_0\circ v_1} \ar[dr]_{r_1}
-			\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){v_1}&&H'_1&& K_0
-			\ar[ur]_{r_0} \ar[ul]^{q_1\circ v_0} \ar@{>->}[dl]^{l_0}
-			\ar@/_.6cm/[uull]^(.65){v_0}\\&& R_1
-			\ar[ur]_{\hspace{-6pt}s_1\circ
-				j_1}\ar@/^.8cm/[uurr]^(.2){j_1}&& L_0 \ar[ul]^{t_0\circ
-				j_0\hspace{-6pt}} \ar@/_.8cm/[uull]_(.2){j_0} |(.69)\hole
-		}	$
-		\caption{Picture for the proof of \Cref{lem:indep-global-left}: switch of $\dder{D}_0$ and $\dder{D}_1$.}
-		\label{fi:first}
-	\end{figure}
-
-	\begin{figure}[t]
-		\centering 
-		$\xymatrix@C=15pt@R=15pt{&&R_1 \ar@/_.8cm/[ddrr]_(.2){a_0}|(.7)\hole
-			\ar[dr]^{h_1}&& L_2\ar@/^.8cm/[ddll]^(.2){a_1}
-			\ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar@{>->}[dl]_{l_1}
-			\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){u_1}\ar[ur]^{r_1}&& G_2 &&
-			K_2
-			\ar@/^.6cm/[ddll]|(.36)\hole_(.65){u_2}\ar[dl]_{k_2}\ar@{>->}[lu]_{l_2}
-			\ar[dr]^{r_2}\\L_1
-			\ar@/_.6cm/[ddrr]_(.2){b_0}|(.31)\hole|(.81)\hole
-			\ar[dr]^(.4){m_1}|(.61)\hole && D_1
-			\ar@{>->}[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2
-			\ar[dr]|(.4)\hole^(.65){g_2}
-			\ar@{>->}[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.6cm/[ddll]^(.2){b_1}|(.31)\hole|(.81)\hole\ar[dl]_(.4){h_2}|(.61)\hole\\&G_1
-			&&P_2\ar[dr]_{d_1}
-			\ar@{>->}[dl]^{d_0}\ar[ur]^(.4){c_1}\ar@{>->}[ul]_(.4){c_0}&&G_3\\L_2
-			\ar@/^.6cm/[uurr]^(.2){a_1} \ar[ur]_(.35){f_1\circ
-				a_1}|(.61)\hole&&Q_2
-			\ar@{>->}[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1}
-			&&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar@{>->}[dl]|(.5)\hole_(.65){x_2}
-			&& R_1 \ar[ul]^(.3){g_2\circ
-				a_0}|(.61)\hole\ar@/_.6cm/[uull]_(.2){a_0}\\&K_2
-			\ar[ur]_{d_0\circ u_2} \ar[dr]_{r_2}
-			\ar@{>->}[ul]^{l_2}\ar@/^.6cm/[uurr]_(.65){u_2}&&G'_2&& K_1
-			\ar[ur]_{r_1} \ar[ul]^{d_1\circ u_1} \ar@{>->}[dl]^{l_1}
-			\ar@/_.6cm/[uull]^(.65){u_1}\\&& R_2
-			\ar[ur]_{\hspace{-6pt}x_2\circ
-				b_1}\ar@/^.8cm/[uurr]^(.2){b_1}&& L_1 \ar[ul]^{y_1\circ
-				b_0\hspace{-7pt}} \ar@/_.8cm/[uull]_(.2){b_0} |(.69)\hole
-		}	$		
-		\caption{Picture for the proof of \Cref{lem:indep-global-left}: switch of $\dder{D}_1$ and $\dder{D}_2$.}
-		\label{fi:second}
-	\end{figure}
-
-	\begin{figure}
-		\centering
-		$\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){e_0}|(.7)\hole
-			\ar[dr]^{\hspace{-5pt}h_0}&& L_2\ar@/^.8cm/[ddll]^(.2){e_1}
-			\ar[dl]_{f_1\circ a_1\hspace{-5pt}}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
-			\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){w_0}\ar[ur]^{r_0}&& G_1 &&
-			K_2 \ar@/^.6cm/[ddll]|(.36)\hole_(.65){w_2}\ar[dl]_{d_0\circ
-				u_2\hspace{-5pt}}\ar@{>->}[lu]_{l_2} \ar[dr]^{r_2}\\L_0
-			\ar@/_.6cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole
-			\ar[dr]^(.4){m_0}|(.61)\hole && D_0
-			\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2
-			\ar[dr]|(.4)\hole^(.65){y_1}
-			\ar@{>->}[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.6cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.3){x_2\circ
-				b_1}|(.58)\hole \\&G_0 &&P_3\ar[dr]_{n_1}
-			\ar@{>->}[dl]^{n_0}\ar[ur]^(.4){\theta_1}\ar@{>->}[ul]_(.4){\theta_0}&&G'_2\\L_2
-			\ar@/^.6cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ
-				e_1}|(.61)\hole&&Q_4
-			\ar@{>->}[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0}
-			&&Q_5\ar[ur]|(.4)\hole^(.65){z'_1}
-			\ar@{>->}[dl]|(.5)\hole_(.65){z_1} && R_0 \ar[ul]^(.3){y_1\circ
-				e_0}|(.6)\hole\ar@/_.6cm/[uull]_(.2){e_0}\\&K_2
-			\ar[ur]_{\hspace{-2pt}n_0\circ w_2} \ar[dr]_{r_2}
-			\ar@{>->}[ul]^{l_2}\ar@/^.6cm/[uurr]_(.65){w_2}&&G'_1&& K_0
-			\ar[ur]_{r_0} \ar[ul]^{n_1\circ w_0} \ar[dl]^{l_0}
-			\ar@/_.6cm/[uull]^(.65){w_0}\\&& R_2
-			\ar[ur]_{\hspace{-4pt}z_1\circ
-				o_1}\ar@/^.8cm/[uurr]^(.2){o_1}&& L_0 \ar[ul]^{z'_0\circ
-				o_0\hspace{-7pt}} \ar@/_.8cm/[uull]_(.2){o_0} |(.69)\hole
-		}	$
-		\caption{Picture for the proof of \Cref{lem:indep-global-left}: switch of $\dder{D}_0$ and $S_{a_0,a_1}(\dder{D}_2)$.}
-		\label{fi:third}
-	\end{figure}
-
-	\begin{enumerate}
-		\item We have to construct the two dotted arrows in the diagram
-		below
-		\[\xymatrix@C=15pt{L_0 \ar[d]_{z'_0\circ o_0}&& K_0
-			\ar[d]_{n_1\circ w_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
-			\ar@{.>}@/^.35cm/[drrr]_(.4){\beta_0}|(.29)\hole
-			\ar[dr]|(.28)\hole_{y_1\circ e_0} && L_1
-			\ar@{.>}@/_.35cm/[dlll]^(.4){\beta_1}
-			\ar[dl]|(.28)\hole^{y_1\circ b_0}& K_1 \ar[d]^{d_1\circ
-				u_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ
-				a_1}\\G'_1 && \ar@{>->}[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2 &&
-			\ar@{>->}[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_3}\]
-
-		The arrows $i_0\colon R_0\to D_1$,
-		$e_0\colon R_0\to Q_2$, $i_1\colon L_1\to D_0$ and $b_0\colon L_1 \to Q_2$ satisfy
-		\[
-		f_1\circ i_0  = h_0 =x_1\circ e_0 \qquad 
-		g_0\circ i_1 = m_1 = x_1 \circ b_0 \]
-
-		These identities entail the existence of the dotted
-		$\beta'_0\colon R_0\to P_2$ and $\beta'_1\colon L_1\to P_3$ below
-		\[\xymatrix{R_0 \ar@{.>}[dr]^{\beta'_0} \ar@/^.3cm/[drr]^{i_0}
-			\ar@/_.3cm/[ddr]_{e_0} &&& L_1 \ar@{.>}[dr]^{\beta'_1} \ar@/^.3cm/[drr]^{i_1}
-			\ar@/_.3cm/[ddr]_{b_0}\\ &P_2 \ar@{>->}[r]^{c_0} \ar@{>->}[d]_{d_0}& D_1
-			\ar@{>->}[d]^{f_1} & &P_3 \ar@{>->}[r]^{\theta_0} \ar[d]_{\theta_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar@{>->}[r]_{x_1} & G_1 & &Q_2\ar@{>->}[r]_{x_1} & G_1}\]
-
-                    We can now define $\beta_0\colon R_0\to Q_3$ as $d_1\circ \beta'_1$ and $\beta_1\colon L_1\to Q_5$ be $n_1\circ \beta'_1$, so that
-		\begin{align*}
-			x_2\circ \beta_0 & =x_2\circ d_2\circ \beta'_0 = y_1\circ d_0\circ \beta'_0=y_1\circ e_0\\
-			z'_1 \circ \beta_1 & = z'_1 \circ n_1\circ \beta'_1 =y_1\circ \theta_1\circ \beta'_1=y_1\circ b_0
-		\end{align*}
-
-		Therefore, $(\beta_0, \beta_1)$ is the wanted independence pair.
-
-              \item Here we assume that
-                $\dder{D}_1$ and $\dder{D}_2$ are switchable  with an
-    independence pair $(\alpha_0, \alpha_1)$ and that
-    $\dder{D}_0$ and $S_{\alpha_0, \alpha_1}(\dder{D}_2)$ are switchable.
-    % 
-                Hence, in addition to the three diagrams above, we have a fourth one, depicted in \Cref{fi:fourth}.
-		\begin{figure}[h]
-			\centering
-			$\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){\alpha_0}|(.7)\hole \ar[dr]^{\hspace{-1pt}g_1\circ i_0}&& L_2\ar@/^.8cm/[ddll]^(.2){\alpha_1}  \ar[dl]_{m_2\hspace{-2pt}}\\
-				&K_0\ar[dr]^{\hspace{-4pt}q_1\circ v_0}\ar@{>->}[dl]_{l_0} \ar@/_.6cm/[ddrr]|(.36)\hole^(.65){\phi_0}\ar[ur]^{r_0}&& G_2 && K_2 \ar@/^.6cm/[ddll]|(.36)\hole_(.65){\phi_2}\ar[dl]_{k_2}\ar@{>->}[lu]_{l_2} \ar[dr]^{r_2}\\
-				L_0 \ar@/_.6cm/[ddrr]_(.2){\gamma_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){\hspace{-4pt}t_0\circ j_0}|(.6)\hole && Q_1 \ar@{>->}[dl]|(.4)\hole_(.65){s_1}\ar[ur]|(.5)\hole^(.7){t_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar@{>->}[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.6cm/[ddll]^(.2){\gamma_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){h_2}|(.6)\hole\\&H'_1 &&P_4\ar[dr]_{\lambda_1} \ar@{>->}[dl]^{\lambda_0}\ar[ur]^(.4){\zeta_1}\ar@{>->}[ul]_(.4){\zeta_0}&&G_3\\
-				L_2 \ar@/^.6cm/[uurr]^(.2){\alpha_1} \ar[ur]_(.35){\hspace{-2pt}s_1\circ
-					\alpha_1}|(.61)\hole&&Q_6
-				\ar@{>->}[ul]|(.4)\hole_(.6){\xi_0}\ar[dr]|(.5)\hole^(.65){\xi'_0}
-				&&Q_7\ar[ur]|(.4)\hole^(.6){\xi'_1}
-				\ar@{>->}[dl]|(.5)\hole_(.65){\xi_1} && R_0 \ar[ul]^(.35){g_2\circ
-					\alpha_0}|(.61)\hole\ar@/_.6cm/[uull]_(.2){\alpha_0}\\&K_2
-				\ar[ur]_{\lambda_0\circ \phi_2} \ar[dr]_{r_2}
-				\ar@{>->}[ul]^{l_2}\ar@/^.6cm/[uurr]_(.65){\phi_2}&&H'_2&& K_0
-				\ar[ur]_{r_0} \ar[ul]^{\lambda_1\circ \phi_0} \ar@{>->}[dl]^{l_0}
-				\ar@/_.6cm/[uull]^(.65){\phi_0}\\&& R_2
-				\ar[ur]_{\hspace{-5pt}\xi_1\circ
-					\gamma_1}\ar@/^.8cm/[uurr]^(.2){\gamma_1}&& L_0
-				\ar[ul]^{\xi'_0\circ \gamma_0\hspace{-7pt}}
-				\ar@/_.8cm/[uull]_(.2){\gamma_0} |(.69)\hole 
-			}	$
-			\caption{Picture for the proof of \Cref{lem:indep-global-left}: switch of $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$.}
-			\label{fi:fourth}
-		\end{figure}
-
-		Our aim is to construct the dotted arrows in the following diagram
-		\[\xymatrix@C=15pt{L_1 \ar[d]_{f_0\circ i_0}&& K_1
-			\ar[d]_{q_0\circ v_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1
-			\ar@{.>}@/^.35cm/[drrr]_(.4){\epsilon_0}|(.29)\hole
-			\ar[dr]|(.28)\hole_{s_1\circ j_1} && L_2
-			\ar@{.>}@/_.35cm/[dlll]^(.4){\epsilon_1}
-			\ar[dl]|(.28)\hole^{s_1\circ \alpha_1}& K_2
-			\ar[d]^{\lambda_0\circ \phi_2}\ar@{>->}[l]_{l_2} \ar[rr]^{r_2} &&
-			R_2 \ar[d]^{\xi_1\circ \gamma_1}\\G_0 && \ar@{>->}[ll]^{s_0} Q_0
-			\ar[rr]_{t_0}&& H'_1 && \ar@{>->}[ll]^{\xi_0} Q_6
-			\ar[rr]_{\xi'_0}&& H'_2}\]
-
-		We can take the arrows $j_1\colon R_1\to Q_1$, 
-		$a_0\colon R_1\to D_2$, $e_1\colon L_2 \to D_0$ and $a_1\colon L_2\to D_1$ and notice that
-		\[	f_2\circ a_0 =h_1 =t_1\circ j_1 \qquad   g_0\circ e_1=f_1\circ a_1\]
-		and thus we get the dotted arrows $\epsilon'_0\colon R_1\to P_4$, $\epsilon'_1\colon L_2\to P:1$ 
-		\[\xymatrix{R_1 \ar@{.>}[dr]^{\epsilon'_0} 
-			\ar@/^.3cm/[drr]^{j_1} \ar@/_.3cm/[ddr]_{a_0}&&& L_2 \ar@{.>}[dr]^{\epsilon'_1}
-			\ar@/^.3cm/[drr]^{a_1} \ar@/_.3cm/[ddr]_{e_0}\\ &P_4
-			\ar@{>->}[r]^{\zeta_0} \ar[d]_{\zeta_1}& Q_1 \ar[d]^{t_1} &&P_1
-			\ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\
-			&D_2\ar@{>->}[r]_{f_2} & G_2& 	&D_0\ar[r]_{g_0} & G_1} \]
-
-		Now, notice that
-		\[
-		t_1\circ q_1\circ \epsilon'_1  =g_1\circ p_1\circ \epsilon'_1  =g_1\circ a_1 =m_2
-		\]
-		Hence $(\alpha_0, q_1\circ \epsilon'_1)$ is an independence pair
-		for $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$. By hypothesis $(\X, \R)$ is well-switching and therefore
-		$q_1\circ \epsilon'_1$ must coincide with $\alpha_1$.
-
-		We can then define $\epsilon_0\colon R_1\to Q_6$ and $\epsilon_1\colon L_2\to Q_0$ to be, respectively, 
-		$\lambda_0\circ \epsilon'_0$ and $q_0\circ
-		\epsilon'_1$. Then for these  arrows we have  identities
-		\begin{align*}
-			\xi_0\circ \epsilon_0 & =\xi_0\circ \lambda_0\circ \epsilon'_0 =s_1\circ \zeta_0 \circ \epsilon'_0=s_1\circ j_1\\	t_0\circ \epsilon_1 & = t_0\circ q_0\circ \epsilon'_1 =s_1\circ q_1\circ \epsilon'_1=s_1\circ \alpha_1
-		\end{align*}
-		Allowing us to conclude that
-		$S_{i_0,i_1}(\dder{D}_1)$ and $S_{\alpha_0,
-			\alpha_1}(\dder{D}_2)$ are switchable.  \qedhere
-	\end{enumerate}
-\end{proof}
-
-\lemSwitchConfluence*
-\label{lemSwitchConfluence-proof}
-
-\begin{proof}
-	To fix the notation, let us depict the derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$
-	\[\xymatrix@C=15pt{L_0\ar[d]^{m_0}&& K_0 \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]_(.4){i_0}|(.29)\hole \ar[dr]|(.28)\hole_{h_0} && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.28)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_1 \ar[dr]|(.28)\hole_{h_1} \ar@/^.35cm/[drrr]_(.4){j_0}|(.29)\hole  && L_2 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.28)\hole^{m_2}& K_2 \ar[d]^{k_2}\ar@{>->}[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]_{h_2} \\G_0 && \ar@{>->}[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar@{>->}[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2 && \ar@{>->}[ll]^{f_2} D_2 \ar[rr]_{g_2}&& G_3 }\]
-
-	We are going to do the two sequences of switches and compare the results.
-
-	\smallskip \noindent First sequence of switches.
-
-	We begin switching $\dder{D}_0$ and $\dder{D}_1$ to get the following diagram
-	\[\xymatrix@C=15pt{L_1\ar[d]^{f_0\circ i_1}&& K_1 \ar[d]_{k'_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){a_0}|(.29)\hole \ar[dr]|(.28)\hole_{h'_1} && L_0 \ar@/_.35cm/[dlll]^(.4){a_1} \ar[dl]|(.28)\hole^{m'_0}& K_0 \ar[d]^{k'_0}\ar@{>->}[l]_{l_0} \ar[r]^{r_0} & R_0 \ar[dr]|(.28)\hole_{g_1\circ i_0} \ar@/^.35cm/[drrr]_(.4){b_0}|(.29)\hole  && L_2 \ar@/_.35cm/[dlll]^(.4){b_1} \ar[dl]|(.28)\hole^{m_2}& K_2 \ar[d]^{k_2}\ar@{>->}[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]_{h_2} \\G_0 && \ar@{>->}[ll]^{f'_0} D'_0 \ar[rr]_{g'_0}&& G'_1  && \ar@{>->}[ll]^{f'_1} D'_1 \ar[rr]_{g'_1}&& G_2 && \ar@{>->}[ll]^{f_2} D_2 \ar[rr]_{g_2}&& G_3 }\]
-
-	By \Cref{def:switch} we also know that $m_0=f'_0\circ a_1$ and $h_1=g'_1\circ a_0$. Now, let us switch $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$. In this case we obtain
-	\[\xymatrix@C=15pt{L_1\ar[d]^{f_0\circ i_1}&& K_1 \ar[d]_{k'_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){c_0}|(.29)\hole \ar[dr]|(.28)\hole_{h'_1} && L_2 \ar@/_.35cm/[dlll]^(.4){c_1} \ar[dl]|(.28)\hole^{f'_1\circ b_1}& K_2 \ar[d]^{k'_2}\ar@{>->}[l]_{l_2} \ar[r]^{r_2} & R_2 \ar[dr]|(.28)\hole_{h'_2} \ar@/^.35cm/[drrr]_(.4){d_0}|(.29)\hole  && L_0 \ar@/_.35cm/[dlll]^(.4){d_1} \ar[dl]|(.28)\hole^{\hat{m}_0}& K_0 \ar[d]^{\hat{k}_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]_{g_2\circ b_0} \\G_0 && \ar@{>->}[ll]^{f'_0} D'_0 \ar[rr]_{g'_0}&& G'_1  && \ar@{>->}[ll]^{\hat{f}_1} \hat{D}_1 \ar[rr]_{\hat{g}_1}&& G'_2 && \ar@{>->}[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 }\]
-	Using again the definition of switch, we know that $m'_0=\hat{f}_1\circ d_1$ and $h_2=g'_2\circ d_0$.
-Moreover, by hypothesis $(\X, \R)$ is well-switching and the hypothesis of the second point of \Cref{lem:indep-global-left} are satisfied by $\der{D}$.
-Thus we can characterise $c_0\colon R_1\to \hat{D}_1$ and $c_1\colon L_2\to D'_0$ as the unique arrows fitting in the diagrams below, where the bottom squares are pullbacks
-	\[\xymatrix@R=15pt@C=15pt{&&R_1 \ar@/_1.2cm/[dddl]_(.4){a_0}|(.63)\hole\ar[dl]^{j_0}\ar[dd]^{c'_0} \ar@{>}[dr]^{c_0}&&&&&L_2 \ar[dl]^{j_1} \ar@/_1.2cm/[dddl]_(.4){z_1}|(.63)\hole\ar[dd]^{c'_1} \ar@{>}[dr]^{c_1}\\&D_2 \ar@{>->}[dl]^(.4){f_2}&&\hat{D}_1 \ar[dr]^{\hat{g}_1}  &&&D_1 \ar@{>->}[dl]^(.4){f_1}&&D'_0 \ar[dr]^{g'_0}\\G_2 && P\ar[dr]_{p_4} \ar@{>->}[ur]_{p_3}\ar@{>->}[dl]^{p_1} \ar[ul]^{p_2}&&G'_2&G_1 && Q\ar[dr]_{q_4} \ar@{>->}[ur]_{q_3}\ar@{>->}[dl]^{q_1} \ar[ul]^{q_2}&&G'_1\\& D'_1 \ar[ul]^{g'_1}&&D'_2 \ar@{>->}[ur]_{f'_2}&&& D_0 \ar[ul]^{g_0}&&D'_1 \ar@{>->}[ur]_{f'_1}}\]
-
-Finally, we switch the first two direct derivations
-	\[\xymatrix@C=15pt{L_2\ar[d]^{f'_0\circ c_1}&& K_2 \ar[d]_{\hat{k}_2}\ar@{>->}[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){e_0}|(.29)\hole \ar[dr]|(.28)\hole_{\hat{h}_2} && L_1 \ar@/_.35cm/[dlll]^(.4){e_1} \ar[dl]|(.28)\hole^{\hat{m}_1}& K_1 \ar[d]^{\hat{k}_1}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){t_0}|(.29)\hole \ar[dr]|(.28)\hole_{\hat{g}_1\circ c_0}   && L_0  \ar[dl]|(.28)\hole^{\hat{m}_0} \ar@/_.35cm/[dlll]^(.4){t_1}& K_0 \ar[d]^{\hat{k}_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]_{g_2\circ b_0} \\G_0 && \ar@{>->}[ll]^{\hat{f}_0} \hat{D}_0 \ar[rr]_{\hat{g}_0}&& \hat{G}_1  && \ar@{>->}[ll]^{\tilde{f}_1} \tilde{D}_1 \ar[rr]_{\tilde{g}_1}&& G'_2 && \ar@{>->}[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 }\]
-	As before, we have identities $f_0\circ i_1=\hat{f}_0\circ e_1$ and $h'_2=\tilde{g}_1\circ e_0$.
-Now, the derivation $S_{i_0, i_1}(\dder{D}_1)\cdot S_{i_0, i_1}(\dder{D}_0)\cdot \dder{D}_2$ satisfies the hypothesis of the first point of \Cref{lem:indep-global-left}.
-Thus, since there is at most one independence pair between two direct derivations, we know that  $t_0\colon R_1\to \tilde{D}_1$ and $t_1\colon L_0\to D'_2$  fit in
-	\[\xymatrix{&R_1 \ar[dl]_{a_0} \ar@{>}[dr]^{t_0} \ar@/^.4cm/[dd]|\hole^(.6){c_0}\ar[d]_{t'_0}&&L_ 0\ar[d]_{d_1} \ar@/_.4cm/[ddrr]|(.41)\hole_(.7){a_1}\ar[drr]^{t'_1} \ar@{>}[rr]^{t_1}&&\tilde{D}_1 \ar@{>->}[r]^{\tilde{f}_1}&\hat{G}_1\\ D'_1 \ar@{>->}[d]_{f'_1}&P\ar@{>->}[d]_{p_3} \ar[r]^{p_4} \ar@{>->}[l]_{p_1}&D'_2\ar@{>->}[d]^{f'_2}&\hat{D}_1 \ar@{>->}[d]_{\hat{f}_1}&&S\ar@{>->}[r]_{s_4} \ar[u]_{s_3}\ar@{>->}[d]^{s_1} \ar[ll]_{s_2} &\hat{D}_0 \ar[u]_{\hat{g}_0} \ar@{>->}[d]^{\hat{f}_0}\\G'_1&\hat{D}_1 \ar@{>->}[l]^{\hat{f}_1}\ar[r]_{\hat{g}_1}& G'_2&G'_1 && D'_0 \ar[ll]^{g'_0}  \ar@{>->}[r]_{f'_0}& G_0 }\]
-
-	\smallskip \noindent Second sequence of switches.
-
-	This time we start switching $\dder{D}_1$ and $\dder{D}_2$.
-	\[\xymatrix@C=15pt{L_0\ar[d]^{m_0}&& K_0 \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]_(.4){z_0}|(.29)\hole \ar[dr]|(.28)\hole_{h_0} && L_2 \ar@/_.35cm/[dlll]^(.4){z_1} \ar[dl]|(.28)\hole^{f_1\circ j_1}& K_2 \ar[d]^{\check{k}_2}\ar@{>->}[l]_{l_2} \ar[r]^{r_2} & R_2 \ar[dr]|(.28)\hole_{\check{h}_2} \ar@/^.35cm/[drrr]_(.4){w_0}|(.29)\hole  && L_1 \ar@/_.35cm/[dlll]^(.4){w_1} \ar[dl]|(.28)\hole^{\check{m}_1}& K_1 \ar[d]^{\check{k}_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} && R_1\ar[d]_{g_2\circ j_0} \\G_0 && \ar@{>->}[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar@{>->}[ll]^{\check{f}_1} \check{D}_1 \ar[rr]_{\check{g}_1}&& \check{G}_2 && \ar@{>->}[ll]^{\check{f}_2} \check{D}_2 \ar[rr]_{\check{g}_2}&& G_3 }\]
-	As in the previous case, we already know that $m_1=\check{f}_1\circ w_1$ and $h_2=\check{g}_2\circ w_0$.
-
-	Next, we switch $\dder{D}_0$ and $S_{j_0, j_1}(\dder{D}_2)$ getting
-	\[\xymatrix@C=15pt{L_2\ar[d]^{f_0\circ z_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar@{>->}[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){y_0}|(.29)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_0 \ar@/_.35cm/[dlll]^(.4){y_1} \ar[dl]|(.28)\hole^{\check{m}_0}& K_0 \ar[d]^{\check{k}_0}\ar@{>->}[l]_{l_0} \ar[r]^{r_0} & R_0 \ar[dr]|(.28)\hole_{\check{g}_1\circ z_0} \ar@/^.35cm/[drrr]_(.4){x_0}|(.29)\hole  && L_1 \ar@/_.35cm/[dlll]^(.4){x_1} \ar[dl]|(.28)\hole^{\check{m}_1}& K_1 \ar[d]^{\check{k}_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} && R_1\ar[d]_{g_2\circ j_0} \\G_0 && \ar@{>->}[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar@{>->}[ll]^{\mathring{f}_1} \mathring{D}_1 \ar[rr]_{\mathring{g}_1}&& \check{G}_2 && \ar@{>->}[ll]^{\check{f}_2} \check{D}_2 \ar[rr]_{\check{g}_2}&& G_3 }\]
-	The usual identities $m_0=\check{f}_0\circ y_1$, $\check{h}_2=\mathring{g}_1\circ y_0$ hold.
-But the really important thing to notice is that the first match of these derivation coincide with $f'_0\circ c_1$
-	\[	f_0'\circ c_1  =f'_0\circ q_3\circ c'_1 =f_0\circ q_1\circ c'_1=f_0\circ z_1\]
-
-	Moreover, we can characterise the pair $(x_0, x_1)$.
-If we apply the first point of \Cref{lem:indep-global-left} to $\dder{D}$ we get an independence pair between the last two steps of the derivation above, which, since $(\X, \R)$ is well-switching, must coincide with $(x_0, x_1)$.
-Thus we have two diagrams
-
-	\[\xymatrix{&R_0 \ar[dl]_{i_0} \ar@{>}[dr]^{x_0} \ar@/^.4cm/[dd]|\hole^(.6){z_0}\ar[d]_{x'_0}&&L_ 1\ar[d]_{w_1} \ar@/_.4cm/[ddrr]|(.41)\hole_(.7){i_1}\ar[drr]^{x'_1} \ar@{>}[rr]^{x_1}&&\mathring{D}_1 \ar@{>->}[r]^{\mathring{f}_1}&\check{G}_1\\ D_1 \ar@{>->}[d]_{f_1}&P'\ar@{>->}[d]_{p'_3} \ar[r]^{p'_4} \ar@{>->}[l]_{p'_1}&\check{D}_2\ar@{>->}[d]^{\check{f}_2}&\check{D}_1 \ar@{>->}[d]_{\check{f}_1}&&S'\ar@{>->}[r]_{s'_4} \ar[u]_{s'_3}\ar@{>->}[d]^{s'_1} \ar[ll]_{s'_2} &\check{D}_0 \ar[u]_{\check{g}_0} \ar@{>->}[d]^{\check{f}_0}\\G_1&\check{D}_1 \ar@{>->}[l]^{\check{f}_1}\ar[r]_{\check{g}_1}& \check{G}_2&G_1 && D_0 \ar[ll]^{g_0}  \ar@{>->}[r]_{f_0}& G_0 }\]
-	From this diagram we can recover another identity. Notice that, if $p'_2\colon P'\to D_2$ is the last projection from $P'$, then
-	\[f_2\circ p'_2\circ x'_0=g_1\circ p'_1\circ x'_0=g_1\circ i_0=f_2\circ b_0\]
-	Implying, since $f_2$ is mono, that $p'_2\circ x'_0=b_0$. From this, we can also deduce that 
-	\[\check{g}_2\circ x_0=\check{g}_2\circ p'_4\circ x'_0=g_2\circ p'_2\circ x'_0=g_2\circ b_0 \]
-
-	Finally, switching the second and the third step we get
-	\[\xymatrix@C=15pt{L_2\ar[d]^{f_0\circ z_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar@{>->}[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){v_0}|(.29)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_1 \ar@/_.35cm/[dlll]^(.4){v_1} \ar[dl]|(.28)\hole^{\mathring{f}_1 \circ x_1}& K_1 \ar[d]^{\mathring{k}_1}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){u_0}|(.29)\hole\ar[dr]_{\check{h}_1}|(.28)\hole   && L_0 \ar@/_.35cm/[dlll]^(.4){u_1} \ar[dl]^{\mathring{m}_0}|(.28)\hole& K_0 \ar[d]^{\mathring{k}_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0\ar[d]_{\check{g}_2\circ x_0} \\G_0 && \ar[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar@{>->}[ll]^{\bar{f}_1} \bar{D}_1 \ar[rr]_{\bar{g}_1}&& \bar{G}_2 && \ar@{>->}[ll]^{\bar{f}_2} \bar{D}_2 \ar[rr]_{\bar{g}_2}&& G_3 }\]
-	As usual, this last switch brings identities $\check{m}_0=\bar{f}_1\circ u_1$ and $g_2\circ j_0=\bar{g}_2\circ u_0$.
-Applying the second point of \Cref{lem:indep-global-left} to $\dder{D}_0\cdot S_{j_0, j_1}(\dder{D}_2)\cdot S_{j_0, j_1}(\dder{D}_1)$ and the fact that $(\X, \R)$ is well-switching we get the following diagrams
-	\[\xymatrix@R=15pt@C=15pt{&&R_2 \ar@/_1.2cm/[dddl]_(.4){y_0}|(.63)\hole\ar[dl]^{w_0}\ar[dd]^{v'_0} \ar@{>}[dr]^{v_0}&&&&&L_1 \ar[dl]^{w_1} \ar@/_1.2cm/[dddl]_(.4){i_1}|(.63)\hole\ar[dd]^{v'_1} \ar@{>}[dr]^{v_1}\\&\check{D}_2 \ar@{>->}[dl]^(.4){\check{f}_2}&&\bar{D}_1 \ar[dr]^{\bar{g}_1}  &&&\check{D}_1 \ar@{>->}[dl]^(.4){\check{f}_1}&&\check{D}_0 \ar[dr]^{\check{g}_0}\\\check{G}_2 && \bar{P}\ar[dr]_{\bar{p}_4} \ar@{>->}[ur]_{\bar{p}_3}\ar@{>->}[dl]^{\bar{p}_1} \ar[ul]^{\bar{p}_2}&&\bar{G}_2&G_1 && \bar{Q}\ar[dr]_{\bar{q}_4} \ar@{>->}[ur]_{\bar{q}_3}\ar@{>->}[dl]^{\bar{q}_1} \ar[ul]^{\bar{q}_2}&&\check{G}_1\\& \mathring{D}_1 \ar[ul]^{\mathring{g}_1}&&\bar{D}_2 \ar@{>->}[ur]_{\bar{f}_2}&&& D_0 \ar[ul]^{g_0}&&\mathring{D}_1 \ar@{>->}[ur]_{\mathring{f}_1}}\]
-
-We have to build the dotted arrows in the diagram below
-	\[\xymatrix@C=15pt@R=30pt{G_0 && \ar@{>->}[ll]_{\hat{f}_0} \hat{D}_0 \ar[rr]^{\hat{g}_0}&& \hat{G}_1  && \ar@{>->}[ll]_{\tilde{f}_1} \tilde{D}_1 \ar[rr]^{\tilde{g}_1}&& G'_2 && \ar@{>->}[ll]_{f'_2} D'_2 \ar[rr]^{g'_2}&& G_3 \\
-		L_2\ar[d]^{f_0\circ z_1} \ar[u]_{f'_0\circ c_1}&& K_2 \ar[u]^{\hat{k}_2}\ar[d]_{\mathring{k}_2}\ar@{>->}[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/_.35cm/[urrr]^(.4){e_0}|(.29)\hole \ar[ur]|(.28)\hole^{\hat{h}_2} \ar@/^.35cm/[drrr]_(.4){v_0}|(.29)\hole \ar@/_.2cm/[dr]|(.28)\hole_{\mathring{h}_2} && L_1 \ar@/^.35cm/[ulll]_(.4){e_1} \ar[ul]|(.28)\hole_{\hat{m}_1} \ar@/_.35cm/[dlll]^(.4){v_1} \ar[dl]|(.28)\hole^{\mathring{f}_1 \circ x_1}& K_1  \ar[u]_{\hat{k}_1}\ar[d]^{\mathring{k}_1}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){u_0}|(.29)\hole\ar@/_.2cm/[dr]_{\check{h}_1}|(.28)\hole \ar@/_.35cm/[urrr]^(.4){t_0}|(.29)\hole \ar[ur]|(.28)\hole^{\hat{g}_1\circ c_0}  && L_0\ar[ul]|(.28)\hole_{\hat{m}_0} \ar@/^.35cm/[ulll]_(.4){t_1} \ar@/_.35cm/[dlll]^(.4){u_1} \ar[dl]^{\mathring{m}_0}& K_0 \ar[d]_{\mathring{k}_0}\ar[u]^{\hat{k}_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[u]^{g_2\circ b_0}\ar[d]_{\check{g}_2\circ x_0} \\G_0 \ar@/^.3cm/[uu]^{\id{G_0}}&& \ar@{>->}[ll]^{\check{f}_0} \check{D}_0 \ar@{.>}@/_.3cm/[uu]_(.3){\phi_{0}}|\hole  \ar[rr]_{\check{g}_0}&& \check{G}_1  \ar@{.>}@/_.0cm/[uu]^(.2){\psi_{1}}|(.43)\hole |(.57)\hole  && \ar@{>->}[ll]^{\bar{f}_1} \bar{D}_1 \ar@{.>}@/^.3cm/[uu]^(.3){\phi_{1}}|\hole \ar[rr]_{\bar{g}_1}&& \bar{G}_2 \ar@{.>}@/_.0cm/[uu]^(.2){\psi_{2}}|(.43)\hole |(.57)\hole && \ar@{>->}[ll]^{\bar{f}_2} \ar@{.>}@/_.4cm/[uu]_(.3){\phi_{2}}|\hole \bar{D}_2 \ar[rr]_{\bar{g}_2}&& G_3 \ar@{.>}@/_.3cm/[uu]_{\psi_{3}} }\]
-
-	Now, we have already proved that $f_0\circ z_1=f'_0\circ c_1$, thus by \Cref{prop:unique} we have isomorphisms $\phi_{0}\colon \check{D}_0\to \hat{D}_0$ and $\psi_{1}\colon \check{G}_1\to \hat{G}_1$.
-	Notice that
-	\[
-	\hat{f}_0\circ \phi_{0}\circ v_1  = \check{f}_0\circ v_1 =\check{f}_0\circ \check{q}_3\circ v'_1=f_0\circ \check{q}_1\circ v'_1=f_0\circ i_1=\hat{f}_0\circ e_1\]
-Thus, using the fact that $\hat{f}_0$ is mono, we can conclude that $\phi_0\circ v_1=e_1$. Thus we have
-\[\psi_1\circ \mathring{f}\circ x_1=\psi_1\circ \check{g}_0\circ v_1= \hat{g}_0\circ \phi_0\circ v_1=\hat{g}_0\circ e_1=\hat{m}_1 \]
-	 \Cref{prop:unique} now yields the $\phi_1\colon \bar{D}_1\to\tilde{D}_1$ and $\psi_2\colon \bar{G}_2\to G'_2$.  We can compute to get
-	 \[
-	 \tilde{f}_1\circ \phi_1\circ v_0=\psi_1\circ \bar{f}_1\circ v_0=\psi_1\circ \mathring{h}_2=\hat{h}_2=\tilde{f}_1\circ e_0\]
-	 Hence $\phi_1\circ v_0=e_0$. On the other hand, notice that
-	 \[\hat{f}_0\circ s_4\circ t'_1=f'_0\circ s_1\circ t'_1=f'_0\circ a_1=m_0=\check{f}\circ y_1=\hat{f}_0\circ \phi_0\circ y_1\]
-	 Yielding $s_4\circ t'_1=\phi_0\circ y_1$. But then
-	 \begin{align*}
-&\tilde{f}_1\circ \phi_1\circ u_1=\psi_1\circ \bar{f}_1\circ u_1=\psi_1\circ \check{m}_0= \psi_1\circ \check{g}_0\circ y_1\\=&\hat{g}_0\circ \phi_0\circ y_1=\hat{g}_0\circ s_4\circ t'_1=\tilde{f}_1\circ s_3\circ t'_1=\tilde{f}_1\circ t_1
-	 \end{align*}
-
-	 In turn, the previous identity entails that
-	\[\psi_2\circ \mathring{m}_0=\psi_2\circ \bar{g}_1\circ u_1 = \tilde{g}_1\circ \phi_1\circ u_1 = \tilde{g}_1\circ t_1=\hat{m}_0\]
-
-	We can use \Cref{prop:unique} a third time to get $\phi_2\colon \bar{D}_2\to D'_2$ and $\psi_3\colon G_3\to G_3$.  Now, as a last computation, we have
-	\[f'_2\circ t_0= \hat{g}_2\circ c_0=\psi_2\circ h_1=\psi_2\circ \bar{f}_2\circ u_0=f'_2\circ \phi_2\circ u_0\]
-	Therefore $\phi_2\circ u_0=t_0$ and this concludes the proof.
-\end{proof}
-
-We next prove some technical lemma that will be useful to show the
-possibility of transforming a derivation into a switch equivalent one
-by switching steps only along inversions.
-
-\begin{lemma}
-  \label{le:switchA}
-  Let $\der{D}_i$ for $i \in \interval[0]{n}$ be derivation sequences
-  and consider a switching sequence consisting only of inversions
-  \begin{center}
-    $\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
-    \shift{\nu_n} \der{D}_n$
-  \end{center}
-  Let $i \in \interval{n}$ be such that
-  $\transp{i} \in \inv{\nu_{1,n}}$ and for all $k > i+1$ it holds
-  $\nu_{1,n}(k) > \nu_{1,n}(i+1)$.  Then there is a switching sequence
-  consisting only of inversions that starts with $\transp{i}$, i.e.
-  \begin{center}
-    $\der{D}_0 \shift{\transp{i}} \der{D}_1' \shift{\nu_2'} \ldots
-    \shift{\nu_n'} \der{D}_n$
-  \end{center}
-\end{lemma}
-
-\begin{proof}
-  We proceed by induction on $n$. If $n=1$, necessarily
-  $\nu_1 =  \transp{i}$ and we are done.
-
-  If $n>1$, let $\nu_1 = \transp{j}$.  We need three cases,
-  depending on how $\nu_1$ relates to $\transp{i}$.
-
-  \bigskip
-  \noindent
-  (1) $j=i$\\
-  %
-  In this case there is nothing to prove: $\nu_1 = \transp{i}$, hence
-  the original switching sequence is already of the desired shape.
-
-  \bigskip
-  \noindent
-  (2) $j<i-1$ or $j>i-1$\\
-  %
-  In this case $\nu_1$ does not ``interfere'' with $\transp{i}$, i.e.~$i$ still satisfies the hypotheses of the lemma with respect to the
-  switching sequence
-  $\der{D}_1 \shift{\nu_2} \ldots \shift{\nu_n} \der{D}_n$.
-
-  Hence we apply the inductive hypothesis and derive the existence
-  of a switching sequence
-  \begin{center}
-    $\der{D}_1 \shift{\transp{i}} \der{D}_2' \shift{\nu_3'} \ldots \shift{\nu_n'} \der{D}_n$
-  \end{center}
-
-  Recall that $\der{D}_0 \shift{\nu_1} \der{D}_1$ and, given the
-  working assumption (ii), the switches $\nu_1$ and $\transp{i}$ can
-  be done in reverse order, thus getting, as desired
-  \begin{center}
-    $\der{D}_0 \shift{\transp{i}} \der{D}_1' \shift{\nu_1} \ldots
-    \shift{\nu_n'} \der{D}_n$
-  \end{center}
-
-  \bigskip
-  \noindent
-  (3) $j=i-1$, i.e., $\nu_1 = \transp{i-1}[i]$\\
-  %
-  In this case $\der{D}_1$ is obtained from $\der{D}_0$ by switching
-  steps $i-1$ and $i$, as pictorially reported in the first two
-  columns of Fig.~\ref{fi:switchA}. Since we are dealing with
-  switching sequence consisting only of inversions and by hypothesis
-  $\nu_{1,n}(i) > \nu_{1,n}(i+1)$, whence
-  $\nu_{2,n}(i-1) > \nu_{2,n}(i+1)$, we deduce that necessarily
-  $\nu_{2,n}(i) > \nu_{2,n}(i+1)$ and $\nu_{2,n}(k) > \nu_{2,n}(i+1)$
-  for all $k > i+1$. Hence we can use the inductive hypothesis to
-  deduce that the switching sequence from $\der{D}_1$ can start by
-  switching $\transp{i}$, i.e.~we obtain (see the third column in
-  Fig.~\ref{fi:switchA})
-  \begin{center}
-    $\der{D}_1 \shift{\transp{i}} \der{D}_2' \shift{\nu_3'} \ldots
-    \shift{\nu_n'} \der{D}_n$
-  \end{center}
-
-  Now, if we focus on $\der{D}_2'$ we observe that
-  $\nu_{3,n}'(i-1) > \nu_{3,n}'(i)$ and
-  $\nu_{3,n}'(k) > \nu_{3,n}'(i)$ for all $k > i$. Hence we can apply
-  again the inductive hypothesis and get a switching sequence
-    \begin{center}
-    $\der{D}_2' \shift{\transp{i-1}[i]} \der{D}_3'' \shift{\nu_3''} \ldots
-    \shift{\nu_n''} \der{D}_n$
-  \end{center}
-  as depicted in Fig.~~\ref{fi:switchA}, starting from the fourth column.
-
-  By Lemma~\ref{lem:indep-global-left}(\ref{lem:indep-global-left:1})
-  we can reorganise the first three switchings as
-
-  \begin{center}
-    $\der{D}_0 \shift{\transp{i}} \der{D}_1'''
-    \shift{\transp{i-1}[i]} \der{D}_2'''
-    \shift{\transp{i}} \der{D}_3''$
-  \end{center}
-
-  The fact that the three switchings above lead to $\der{D}_3''$ is a
-  consequence of Lemma~\ref{lem:switch-confluence}.
-
-  \bigskip
-
-  Note that it cannot be $j=i+1$, otherwise we would have
-  $\nu_{1,n}(j+1) < \nu_{1,n}(i)$, contradicting the hypotheses. Thus
-  this case can be ignored and the proof is completed.  
-\end{proof}
-
-\begin{figure}
-  \centering
-  \begin{tikzpicture}[font=\small]
-    % Define arrow colors
-    \def\colorA{green!60!black}
-    \def\colorB{blue}
-    \def\colorC{red!100}
-
-    % Define the length of each line
-    \def\vlen{5mm}
-    \def\hlen{18mm}
-    \def\gap{1mm}
-
-    % First line D0 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    % Draw label on top of the line
-    \node[above] at (0*\hlen,0) {$\der{D}_0$};
-    \node[above] at (0.5*\hlen,0) {$\shift{\nu_1}$};
-
-    % Draw the black part of the line
-    \draw (0*\hlen,0) -- (0*\hlen,-2*\vlen+\gap);
-
-    % Draw the first colored labeled arrow
-    \draw[->, \colorA] (0*\hlen,-2*\vlen) -- (0*\hlen,-3*\vlen+\gap) node[midway, left] {$i-1$};
-    % Draw the second colored labeled arrow
-    \draw[->, \colorB] (0*\hlen,-3*\vlen) -- (0*\hlen,-4*\vlen+\gap) node[midway, left] {$i$};
-    % Draw the third colored labeled arrow
-    \draw[->, \colorC] (0*\hlen,-4*\vlen) -- (0*\hlen,-5*\vlen+\gap) node[midway, left] {$i+1$};
-    % Draw the last black part of the line
-    \draw (0*\hlen,-5*\vlen) -- (0*\hlen,-7*\vlen);
-
-    % Second line D1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    % Draw label on top of the line
-    \node[above] at (1*\hlen,0) {$\der{D}_1$};
-    \node[above] at (1.5*\hlen,0) {$\shift{\transp{i}}$};
-
-    % Draw the black part of the line
-    \draw (1*\hlen,0) -- (1*\hlen,-2*\vlen+\gap);
-
-    % Draw the first colored labeled arrow
-    \draw[->, \colorB] (1*\hlen,-2*\vlen) -- (1*\hlen,-3*\vlen+\gap) node[midway, left] {};
-    % Draw the second colored labeled arrow
-    \draw[->, \colorA] (1*\hlen,-3*\vlen) -- (1*\hlen,-4*\vlen+\gap) node[midway, left] {};
-    % Draw the third colored labeled arrow
-    \draw[->, \colorC] (1*\hlen,-4*\vlen) -- (1*\hlen,-5*\vlen+\gap) node[midway, left] {};
-    % Draw the last black part of the line
-    \draw (1*\hlen,-5*\vlen) -- (1*\hlen,-7*\vlen);
-
-    % Repeat similar patterns for the third and fourth lines
-
-    % Third line: d2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \node[above] at (2*\hlen,0) {$\der{D}_2'$};
-    \node[above] at (2.5*\hlen,0) {$\shift{\transp{i-1}[i]}$};
-
-    \draw (2*\hlen,0) -- (2*\hlen,-2*\vlen+\gap);
-
-    \draw[->, \colorB] (2*\hlen,-2*\vlen) -- (2*\hlen,-3*\vlen+\gap) node[midway, left] {};
-    \draw[->, \colorC] (2*\hlen,-3*\vlen) -- (2*\hlen,-4*\vlen+\gap) node[midway, left] {};
-    \draw[->, \colorA] (2*\hlen,-4*\vlen) -- (2*\hlen,-5*\vlen+\gap) node[midway, left] {};
-    \draw (2*\hlen,-5*\vlen) -- (2*\hlen,-7*\vlen);
-
-    % Fourth line %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \node[above] at (3*\hlen,0) {$\der{D}_3''$};
-    \node[above] at (3.5*\hlen,0) {$\shift{\nu_3''}$};
-
-    \draw (3*\hlen,0) -- (3*\hlen,-2*\vlen+\gap);
-    \draw[->, \colorC] (3*\hlen,-2*\vlen) -- (3*\hlen,-3*\vlen+\gap) node[midway, left] {};
-    \draw[->, \colorB] (3*\hlen,-3*\vlen) -- (3*\hlen,-4*\vlen+\gap) node[midway, left] {};
-    \draw[->, \colorA] (3*\hlen,-4*\vlen) -- (3*\hlen,-5*\vlen+\gap) node[midway, left] {};
-    \draw (3*\hlen,-5*\vlen) -- (3*\hlen,-7*\vlen);
-
-    % Dots after the last line
-    \draw (4*\hlen,0*\vlen) node[above] {$\dots$};
-
-    % Last line %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \node[above] at (5*\hlen,0) {$\der{D}_n$};
-    \node[above] at (4.5*\hlen,0) {$\shift{\nu_{n-1}}$};
-
-  \end{tikzpicture}
-  \caption{Picture for the proof of Lemma~\ref{le:switchA}}
-  \label{fi:switchA}
-\end{figure}
-
-\begin{remark}
-  \label{rem:switchA}
-  Observe that given a switching sequence as in the lemma above
-  $\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
-  \shift{\nu_n} \der{D}_n$, if we consider the inversion with largest index
-  \begin{center}
-    $k = \max \{j \mid \transp{j} \in \inv{\nu_{1,n}}\}$
-  \end{center}
-  then it satisfies the hypotheses of the lemma.
-\end{remark}
-
-\begin{lemma}
-  \label{le:switchB}
-  Let $\der{D}_i$ for $i \in \interval[0]{n}$ be derivation sequences
-  and consider a switching sequence consisting only of inversions
-  \begin{center}
-    $\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
-    \shift{\nu_n} \der{D}_n$
-  \end{center}
-  Let $i \in \interval{n}$ be such that
-  $\transp{i} \in \inv{\nu_{1,n}}$ and assume that steps $i$ and $i+1$ in $\der{D}_0$ are sequentially independent. Then there is a switching sequence
-  consisting only of inversions that starts with $\transp{i}$, i.e.,
-  \begin{center}
-    $\der{D}_0 \shift{\transp{i}} \der{D}_1' \shift{\nu_2'} \ldots
-    \shift{\nu_n'} \der{D}_n$
-  \end{center}
-\end{lemma}
-
-\begin{proof}
-  We proceed by induction on $n$. If $n=1$, necessarily
-  $\nu_1 =  \transp{i}$ and we are done.
-
-  If $n>1$, take $k = \max \{j \mid \transp{j} \in \inv{\nu_{1,n}}\}$, which,
-  as observed in Remark~\ref{rem:switchA}, satisfies the hypotheses of
-  Lemma~\ref{le:switchA}. Hence, by the mentioned lemma, we can start
-  the switching sequence with the transposition $\transp{k}$, thus
-  obtaining
-  \begin{center}
-    $\der{D}_0 \shift{\transp{k}} \der{D}_1' \shift{\nu_2'} \ldots
-    \shift{\nu_n'} \der{D}_n$
-  \end{center}
-
-  Moreover, since $\transp{i}$ is an inversion, we have that
-  $\i \leq k$.  We distinguish various case depending on how $k$
-  relates to $i$.
-
-  \bigskip
-  \noindent
-  (i) $j=i$\\
-  %
-  In this case we are done: $\nu_1' = \transp{i}$, hence we obtained a
-  switching sequence of the desired shape.
-
-  \bigskip
-  \noindent
-  (ii) $k > i+1$\\
-  %
-  In this case the switching $\transp{k}$ does not ``interfere'' with
-  $\transp{i}$, as depicted in Fig.~\ref{fi:switchB1} (first two
-  columns).
-
-  Hence if we focus on
-  \begin{center}
-    $\der{D}_1' \shift{\nu_2'} \ldots
-    \shift{\nu_n'} \der{D}_n$
-  \end{center}
-  we can observe that
-  $\nu_{2,n}'(i)=\nu_{1,n}(i) > \nu_{1,n}(i+1)=\nu_{2,n}'(i+1)$.
-  %
-  Thus we can use the inductive hypothesis and obtain (see
-  Fig.~\ref{fi:switchB1}, third column)
-  \begin{center}
-    $\der{D}_1' \shift{\transp{i}} \der{D}_2'' \shift{\nu_3''} \ldots
-    \shift{\nu_n''} \der{D}_n$
-  \end{center}
-
-\begin{figure}
-  \centering
-  \begin{tikzpicture}[font=\small]
-    % Define arrow colors
-    \def\colorA{red!100}
-    \def\colorB{blue}
-    \def\colorC{green!60!black}
-    \def\colorD{orange!60!black}
-
-    % Define the length of each line
-    \def\vlen{5mm}
-    \def\hlen{20mm}
-    \def\gap{1mm}
-
-    % First line D0 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    % Draw label on top of the line
-    \node[above] at (0*\hlen,0) {$\der{D}_0$};
-    \node[above] at (0.5*\hlen,0) {$\shift{\transp{k}}$};
-
-    % Draw the black part of the line
-    \draw (0*\hlen,0) -- (0*\hlen,-1*\vlen+\gap);
-
-    % Draw the first colored labeled arrow
-    \draw[->, \colorA] (0*\hlen,-1*\vlen) -- (0*\hlen,-2*\vlen+\gap) node[midway, left] {$i$};
-    % Draw the second colored labeled arrow
-    \draw[->, \colorB] (0*\hlen,-2*\vlen) -- (0*\hlen,-3*\vlen+\gap) node[midway, left] {$i+1$};
-    % Draw the second black part of the line
-    \draw (0*\hlen,-3*\vlen) -- (0*\hlen,-4*\vlen+\gap);
-
-    % Draw the third colored labeled arrow
-    \draw[->, \colorC] (0*\hlen,-4*\vlen) -- (0*\hlen,-5*\vlen+\gap) node[midway, left] {$k$};
-    % Draw the fourth colored labeled arrow
-    \draw[->, \colorD] (0*\hlen,-5*\vlen) -- (0*\hlen,-6*\vlen+\gap) node[midway, left] {$k+1$};
-    % Draw the last black part of the line
-    \draw (0*\hlen,-6*\vlen) -- (0*\hlen,-7*\vlen);
-
-    % Second line D1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    % Draw label on top of the line
-    \node[above] at (1*\hlen,0) {$\der{D}_1'$};
-    \node[above] at (1.5*\hlen,0) {$\shift{\nu_2'}$};
-
-    % Draw the black part of the line
-    \draw (1*\hlen,0) -- (1*\hlen,-1*\vlen+\gap);
-
-    % Draw the first colored labeled arrow
-    \draw[->, \colorA] (1*\hlen,-1*\vlen) -- (1*\hlen,-2*\vlen+\gap) node[midway, left] {};
-    % Draw the second colored labeled arrow
-    \draw[->, \colorB] (1*\hlen,-2*\vlen) -- (1*\hlen,-3*\vlen+\gap) node[midway, left] {};
-    % Draw the second black part of the line
-    \draw (1*\hlen,-3*\vlen) -- (1*\hlen,-4*\vlen+\gap);
-
-    % Draw the third colored labeled arrow
-    \draw[->, \colorD] (1*\hlen,-4*\vlen) -- (1*\hlen,-5*\vlen+\gap) node[midway, left] {};
-    % Draw the fourth colored labeled arrow
-    \draw[->, \colorC] (1*\hlen,-5*\vlen) -- (1*\hlen,-6*\vlen+\gap) node[midway, left] {};
-    % Draw the last black part of the line
-    \draw (1*\hlen,-6*\vlen) -- (1*\hlen,-7*\vlen);
-
-    % Third line D2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    % Draw label on top of the line
-    \node[above] at (2*\hlen,0) {$\der{D}_2''$};
-    \node[above] at (2.5*\hlen,0) {$\shift{\nu_3''}$};
-
-    % Draw the black part of the line
-    \draw (2*\hlen,0) -- (2*\hlen,-1*\vlen+\gap);
-
-    % Draw the first colored labeled arrow
-    \draw[->, \colorB] (2*\hlen,-1*\vlen) -- (2*\hlen,-2*\vlen+\gap) node[midway, left] {};
-    % Draw the second colored labeled arrow
-    \draw[->, \colorA] (2*\hlen,-2*\vlen) -- (2*\hlen,-3*\vlen+\gap) node[midway, left] {};
-    % Draw the second black part of the line
-    \draw (2*\hlen,-3*\vlen) -- (2*\hlen,-4*\vlen+\gap);
-
-    % Draw the third colored labeled arrow
-    \draw[->, \colorC] (2*\hlen,-4*\vlen) -- (2*\hlen,-5*\vlen+\gap) node[midway, left] {};
-    % Draw the fourth colored labeled arrow
-    \draw[->, \colorD] (2*\hlen,-5*\vlen) -- (2*\hlen,-6*\vlen+\gap) node[midway, left] {};
-    % Draw the last black part of the line
-    \draw (2*\hlen,-6*\vlen) -- (2*\hlen,-7*\vlen);
-
-    % Dots after the last line
-    \draw (3*\hlen,0*\vlen) node[above] {$\dots$};
-
-    % Last line %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \node[above] at (4*\hlen,0) {$\der{D}_n$};
-    \node[above] at (3.5*\hlen,0) {$\shift{\nu_{n-1}''}$};
-
-  \end{tikzpicture}
-  \caption{Picture for the proof of Lemma~\ref{le:switchB}, item (ii)}
-  \label{fi:switchB1}
-\end{figure}
-
-  Now, since $k>i+1$, the switchings $\transp{i}$ and $\transp{k}$ can
-  be performed in reverse order and thus we obtain
-  \begin{center}
-    $\der{D}_0 \shift{\transp{i}} \der{D}_1'' \shift{\transp{k}}
-    \der{D}_2'' \shift{\nu_3''} \ldots \shift{\nu_n''} \der{D}_n$
-  \end{center}
-  as desired.
-
-  \bigskip
-  \noindent
-  (iii) $k = i+1$\\
-  %
-  The situation is depicted in Fig.~\ref{fi:switchB2}. In
-  $\der{D}_1'$, by the choice of $k$ and the fact that all $\nu_i$ are
-  inversions, one can deduce that $i$ satisfies the hypotheses of
-  Lemma~\ref{le:switchA}. Hence we obtain (see Fig.~\ref{fi:switchB2}, first two columns)
-  \begin{center}
-    $\der{D}_1' \shift{\transp{i}} \der{D}_2'' \shift{\nu_2''}
-    \der{D}_3'' \shift{\nu_4''} \ldots \shift{\nu_n''} \der{D}_n$
-  \end{center}
-
-  Since in $\der{D}_0$ steps in positions $i$ and $i+1$ are sequentially
-  independent, we can use
-  Lemma~\ref{lem:indep-global-left}(\ref{lem:indep-global-left:1}) and
-  we have that the corresponding steps in positions $i+1$ and $i+2$ in
-  $\der{D}_2''$ are still sequentially independent. Hence, we can use
-  the inductive hypothesis on $\der{D}_2''$ and deduce the existence
-  of a switching sequence where $\transp{i+1}[i+2]$ can be switched
-  first, i.e.~we obtain (see Fig.~\ref{fi:switchB2}, third column)
-  \begin{center}
-    $\der{D}_2'' \shift{\transp{i+1}[i+2]}
-    \der{D}_3''' \shift{\nu_4'''} \ldots \shift{\nu_n'''} \der{D}_n$
-  \end{center}
-
-  Putting things together, we obtain
-  \begin{center}
-    $\der{D}_0 \shift{\transp{i+1}[i+2]} \der{D}_1' \shift{\transp{i}}
-    \der{D}_2'' \shift{\transp{i+1}[i+2]} \der{D}_3''' \shift{\nu_4'''}\ldots \shift{\nu_n'''} \der{D}_n$
-  \end{center}
-  Since we additionally know that in $\der{D}_0$ the steps $i$ and
-  $i+1$ are sequentially independent, we can use
-  Lemma~\ref{lem:indep-global-left}(\ref{lem:indep-global-left:2}) to
-  reorder the first three switchings, obtaining
-  \begin{center}
-    $\der{D}_0 \shift{\transp{i}} \der{D}_1' \shift{\transp{i+1}[i+2]}
-    \der{D}_2'' \shift{\transp{i}} \der{D}_3''' \shift{\nu_4'''}\ldots \shift{\nu_n'''} \der{D}_n$
-  \end{center}
-  as desired.  The fact that the three switchings above lead to
-  $\der{D}_3'''$ is a consequence of Lemma~\ref{lem:switch-confluence}.
-\end{proof}
-
-\begin{figure}
-  \centering
-  \begin{tikzpicture}[font=\small]
-    % Define arrow colors
-    \def\colorA{red!100}
-    \def\colorB{blue}
-    \def\colorC{green!60!black}
-
-    % Define the length of each line
-    \def\vlen{5mm}
-    \def\hlen{22mm}
-    \def\gap{1mm}
-
-    % First line D0 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    % Draw label on top of the line
-    \node[above] at (0*\hlen,0) {$\der{D}_0$};
-    \node[above] at (0.5*\hlen,0) {$\shift{\transp{i+1}[i+2]}$};
-
-    % Draw the black part of the line
-    \draw (0*\hlen,0) -- (0*\hlen,-2*\vlen+\gap);
-
-    % Draw the first colored labeled arrow
-    \draw[->, \colorA] (0*\hlen,-2*\vlen) -- (0*\hlen,-3*\vlen+\gap) node[midway, left] {$i$};
-    % Draw the second colored labeled arrow
-    \draw[->, \colorB] (0*\hlen,-3*\vlen) -- (0*\hlen,-4*\vlen+\gap) node[midway, left] {$k=i+1$};
-    % Draw the third colored labeled arrow
-    \draw[->, \colorC] (0*\hlen,-4*\vlen) -- (0*\hlen,-5*\vlen+\gap) node[midway, left] {$i+2$};
-    % Draw the last black part of the line
-    \draw (0*\hlen,-5*\vlen) -- (0*\hlen,-7*\vlen);
-
-    % Second line D1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    % Draw label on top of the line
-    \node[above] at (1*\hlen,0) {$\der{D}_1'$};
-    \node[above] at (1.5*\hlen,0) {$\shift{\transp{i}}$};
-
-    % Draw the black part of the line
-    \draw (1*\hlen,0) -- (1*\hlen,-2*\vlen+\gap);
-
-    % Draw the first colored labeled arrow
-    \draw[->, \colorA] (1*\hlen,-2*\vlen) -- (1*\hlen,-3*\vlen+\gap) node[midway, left] {};
-    % Draw the second colored labeled arrow
-    \draw[->, \colorC] (1*\hlen,-3*\vlen) -- (1*\hlen,-4*\vlen+\gap) node[midway, left] {};
-    % Draw the third colored labeled arrow
-    \draw[->, \colorB] (1*\hlen,-4*\vlen) -- (1*\hlen,-5*\vlen+\gap) node[midway, left] {};
-    % Draw the last black part of the line
-    \draw (1*\hlen,-5*\vlen) -- (1*\hlen,-7*\vlen);
-
-    % Repeat similar patterns for the third and fourth lines
-
-    % Third line: d2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \node[above] at (2*\hlen,0) {$\der{D}_2''$};
-    \node[above] at (2.5*\hlen,0) {$\shift{\transp{i+1}[i+2]}$};
-
-    \draw (2*\hlen,0) -- (2*\hlen,-2*\vlen+\gap);
-
-    \draw[->, \colorC] (2*\hlen,-2*\vlen) -- (2*\hlen,-3*\vlen+\gap) node[midway, left] {};
-    \draw[->, \colorA] (2*\hlen,-3*\vlen) -- (2*\hlen,-4*\vlen+\gap) node[midway, left] {};
-    \draw[->, \colorB] (2*\hlen,-4*\vlen) -- (2*\hlen,-5*\vlen+\gap) node[midway, left] {};
-    \draw (2*\hlen,-5*\vlen) -- (2*\hlen,-7*\vlen);
-
-    % Fourth line %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \node[above] at (3*\hlen,0) {$\der{D}_3'''$};
-    \node[above] at (3.5*\hlen,0) {$\shift{\nu_3'''}$};
-
-    \draw (3*\hlen,0) -- (3*\hlen,-2*\vlen+\gap);
-    \draw[->, \colorC] (3*\hlen,-2*\vlen) -- (3*\hlen,-3*\vlen+\gap) node[midway, left] {};
-    \draw[->, \colorB] (3*\hlen,-3*\vlen) -- (3*\hlen,-4*\vlen+\gap) node[midway, left] {};
-    \draw[->, \colorA] (3*\hlen,-4*\vlen) -- (3*\hlen,-5*\vlen+\gap) node[midway, left] {};
-    \draw (3*\hlen,-5*\vlen) -- (3*\hlen,-7*\vlen);
-
-    % Dots after the last line
-    \draw (4*\hlen,0*\vlen) node[above] {$\dots$};
-
-    % Last line %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \node[above] at (5*\hlen,0) {$\der{D}_n$};
-    \node[above] at (4.5*\hlen,0) {$\shift{\nu_{n-1}'''}$};
-
-  \end{tikzpicture}
-  \caption{Picture for the proof of Lemma~\ref{le:switchB} (item (iii))}
-  \label{fi:switchB2}
-\end{figure}
-
-The next lemma intuitively states that if we have a switching sequence
-where the first switch is applied to $\transp{i}$ and the last one
-reverses the same switch, then, assuming that in the middle there are
-only inversions, we can strip the first and last switches.
-
-\begin{lemma}
-  \label{le:switchC}
-  Let $\der{D}_i$ for $i \in \interval[0]{n+1}$ be derivation sequences
-  and consider a switching sequence
-  \begin{center}
-    $\der{D}_0 \shift{\nu_0} \der{D}_1 \shift{\nu_1} \ldots
-     \der{D}_n \shift{\nu_n} \der{D}_{n+1}$
-  \end{center}
-  If the subsequence starting from $\der{D}_1$ consists of
-  inversions and $\nu_0=\transp{i}$ while
-  $\nu_n = \transp{\nu_{1,n}(i)}$, then there is shorter switching sequence
-  consisting only of inversions
-  \begin{center}
-    $\der{D}_0 \equiv_a \der{D}_0' \shift{\nu_2'} \der{D}_3' \shift{\nu_3'} \ldots
-    \shift{\nu_{n-1}'} \der{D}_n'$
-  \end{center}
-\end{lemma}
-
-\begin{proof}
-  Just observe that in $\der{D}_1$ the steps of position $i$ and $i+1$
-  are sequentially independent and $\nu_{1,n}(i) >
-  \nu_{1,n}(i+1)$. Hence we can use Lemma~\ref{le:switchB} and obtain
-  a switching sequence from $\der{D}_1$ where $\transp{i}$ is
-  performed first, hence we obtain
-  \begin{center}
-    $\der{D}_0 \shift{\transp{i}}
-    \der{D}_1 \shift{\transp{i}}
-    \der{D}_2' \shift{\nu_2'} \ldots
-    \shift{\nu_n'} \der{D}_{n+1}$
-  \end{center}
-
-  Now, switching $\transp{i}$ twice one obtains a derivation
-  which is abstraction equivalent to the starting one.  Hence we have
-  \begin{center}
-    $\der{D}_0 \equiv_a
-    \der{D}_2' \shift{\nu_2'} \ldots
-    \shift{\nu_n'} \der{D}_{n+1}$
-  \end{center}
-  as desired.
-\end{proof}
-
-\begin{lemma}
-  \label{le:switchD}
-  Let $\der{D}_i$ for $i \in \interval[0]{n+1}$ be derivation sequences
-  and consider a switching sequence
-  \begin{center}
-    $\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
-    \shift{\nu_n}\der{D}_n$
-  \end{center}
-  If the switching sequence does not consists only of inversions,
-  there is a shorter switching sequence relating
-  $\der{D}_0' \equiv_a \der{D}_0$ and $\der{D}_n$.
-\end{lemma}
-
-\begin{proof}
-  Take a maximal subsequence
-  $\der{D}_i \shift{\nu_{i+1}} \der{D}_{i+1} \shift{\nu_{i+2}} \ldots
-  \shift{\nu_j}\der{D}_j$ consisting only of inversions.
-  %
-  If $i=0$ and $j=n$, there is nothing to show. Hence assume that
-  $i>0$ and consider the sequence
-  \begin{center}
-    $\der{D}_{i-1} \shift{\nu_{i}} \der{D}_{i} \shift{\nu_{i+1}} \ldots
-    \shift{\nu_j}\der{D}_j$
-  \end{center}
-  Then, by maximality, if $\nu_{i-1}=\transp{k}$ it must hold that
-  $\nu_{j}=\transp{\nu_{i,j}(i)}$. Then, by Lemma~\ref{le:switchC},
-  the switching sequence from $\der{D}_{i-1}$ to $\der{D}_{j}$ can be
-  shortened by $2$, i.e.
-  \begin{center}
-    $\der{D}_{i-1} \equiv_a \der{D}_{i+1}' \shift{\nu_{i+1}'} \ldots
-    \shift{\nu_j'}\der{D}_j$
-  \end{center}
-  and thus the same applies to the original switching sequence.
-\end{proof}
-
-\thNoNeed*
-\label{thNoNeed-proof}
-
-\begin{proof}
-  Let $\der{D} \shifteq \der{D}'$. Then there is a switching
-  sequence
-  \begin{center}
-    $\der{D} \equiv_a \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
-    \shift{\nu_n} \der{D}_n \equiv_a \der{D}'$
-  \end{center}
-  If it does not consist only of inversions, by Lemma~\ref{le:switchD}
-  we can reduce its length by $2$. An inductive reasoning allows us to
-  conclude.
-\end{proof}
-
-\coCanonical*
-\label{coCanonical-proof}
-
-\begin{proof}
-  Immediate consequence of Theorem~\ref{th:no-need} and Lemma~\ref{le:switchA}.
-\end{proof}
+\section{Background}
+\label{sec:back}
+
+\section{A class of well behaved rewriting systems}
+\label{sec:rewr}
+
+\section{Domain and event structure semantics}
+\subsection{Domain of traces}
+\subsection{Weak prime domain and connected event structures}
 

### 2024-09-05 concur/presentazione/pres_lunga.tex
fatto

\documentclass[usenames,dvipsnames]{beamer}
\usepackage[utf8]{inputenc}
\usepackage{stmaryrd}
\usepackage{verbatim}

\usetheme{Padova}

\usepackage[utf8]{inputenc}
\usepackage{graphics}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{mathpartir}
\usepackage{mathrsfs}
\usepackage[all]{xy}
\usepackage{amsfonts}

\usepackage[mathscr]{eucal}
\usepackage{ragged2e}
\addtobeamertemplate{theorem begin}{}{\justifying}
\addtobeamertemplate{block begin}{}{\justifying}
\addtobeamertemplate{exampleblock begin}{}{\justifying}
\addtobeamertemplate{alertblock begin}{}{\justifying}
%%% Bibliography
\usepackage[style=authoryear,backend=bibtex]{biblatex}
\addbibresource{bibliog.bib}

\newcommand{\terms}[1]{\mathcal{{#1}}\text{-}\mathsf{Terms}}
\makeatletter
\renewcommand{\itemize}[1][]{%
	\beamer@ifempty{#1}{}{\def\beamer@defaultospec{#1}}%
	\ifnum \@itemdepth >2\relax\@toodeep\else
	\advance\@itemdepth\@ne
	\beamer@computepref\@itemdepth% sets \beameritemnestingprefix
	\usebeamerfont{itemize/enumerate \beameritemnestingprefix body}%
	\usebeamercolor[fg]{itemize/enumerate \beameritemnestingprefix body}%
	\usebeamertemplate{itemize/enumerate \beameritemnestingprefix body begin}%
	\list
	{\usebeamertemplate{itemize \beameritemnestingprefix item}}
	{\def\makelabel##1{%
			{%
				\hss\llap{{%
						\usebeamerfont*{itemize \beameritemnestingprefix item}%
						\usebeamercolor[fg]{itemize \beameritemnestingprefix item}##1}}%
			}%
		}%
	}
	\fi%
	\beamer@cramped%
	\justifying% NEW
	%\raggedright% ORIGINAL
	\beamer@firstlineitemizeunskip%
}
\makeatother

% Author names in publication list are consistent 
% i.e. name1 surname1, name2 surname2
% See https://tex.stackexchange.com/questions/106914/biblatex-does-not-reverse-the-first-and-last-names-of-the-second-author
%\DeclareNameAlias{author}{first-last}

%%% Suppress biblatex annoying warning
\usepackage{silence}
\WarningFilter{biblatex}{Patching footnotes failed}
\usepackage{physics}
%%% Some useful commands
% pdf-friendly newline in links
\newcommand{\pdfnewline}{\texorpdfstring{\newline}{ }} 
% Fill the vertical space in a slide (to put text at the bottom)

% direct shift
\newcommand{\shift}[1]{\ensuremath{\mathrel{{\leftrightsquigarrow}_{#1}}}}

% shift equivalence
\newcommand{\shifteq}[1][]{\ensuremath{\mathrel{{\equiv}^\mathit{sh}_{#1}}}}

\newcommand{\dder}[1]{\mathscr{#1}}
\usepackage{ragged2e}
\addtobeamertemplate{theorem begin}{}{\justifying}
\addtobeamertemplate{block begin}{}{\justifying}
\addtobeamertemplate{exampleblock begin}{}{\justifying}
\addtobeamertemplate{alertblock begin}{}{\justifying}
\addtobeamertemplate{block alerted begin}{}{\justifying}

\usepackage{etoolbox}
\apptocmd{\thebibliography}{\justifying}{}{}

\usepackage{mathpartir}
\usepackage[usestackEOL]{stackengine}
\usepackage{mathtools,amssymb}
%\newcommand{\ar}[0]{\mathsf{ar}}
\newcommand{\comma}[2]{#1\hspace{1pt} {\downarrow}\hspace{1pt} #2}
\newcommand{\ex}[2]{\mathsf{m}\qty(#1, #2)}
\newcommand{\ext}[2]{\mathsf{m}\qty(#1, #2)}
\newcommand{\cri}[1]{\mathsf{cri}\hspace{-.4pt}\left({#1}\right)}
\newcommand\functorop[1][l]{\csname#1functor\endcsname}
\newcommand\lfunctorop[3]{%
	\setbox0=\hbox{$#2$}%
	\kern\wd0%
	\ensurestackMath{\Centerstack[c]{#1\\ \mathllap{#2\;\,}\mathclap{\DownArrow}\\#3}}%
}
\newcommand\rfunctorop[3]{%
	\setbox0=\hbox{$#2$}%
	\ensurestackMath{\Centerstack[c]{#1\\\mathclap{\UpArrow}\mathrlap{\,\;#2}\\#3}}%
	\kern\wd0%
}
\newcommand\functoropmapsto{\mathrel{\ensurestackMath{\Centerstack[c]{\longmapsto\\ \\\longmapsto}}}}
\setstackgap{L}{1.3\normalbaselineskip}
\newcommand\UpArrow{\rotatebox[origin=c]{90}{$\longrightarrow$\,}}
\newcommand\DownArrow{\rotatebox[origin=c]{-90}{$\longrightarrow$\,}}

\newcommand{\arro}[0]{\mathrel{\rotatebox[origin=c]{270}{$\twoheadrightarrow$}}}

\newcommand{\arr}[2]{{#1}{\arro}{\catname{#2}}}
\newcommand\functor[1][l]{\csname#1functor\endcsname}

\newcommand{\tg}[0]{\catname{TG}_{\Sigma}}
\newcommand{\ari}[0]{\mathsf{ar}}
\newcommand{\lgt}[0]{\mathsf{length}}

\newcommand{\cma}[2]{\mathcal{#1}\hspace{1pt} {\downarrow}\hspace{1pt} \mathcal{#2}}
\newcommand\lfunctor[3]{%
	\setbox0=\hbox{$#2$}%
	\kern\wd0%
	\ensurestackMath{\Centerstack[c]{#1\\ \mathllap{#2\;\,}\mathclap{\DownArrow}\\#3}}%
}
\newcommand\rfunctor[3]{%
	\setbox0=\hbox{$#2$}%
	\ensurestackMath{\Centerstack[c]{#1\\\mathclap{\DownArrow}\mathrlap{\,\;#2}\\#3}}%
	\kern\wd0%
}
\newcommand\functormapsto{\mathrel{\ensurestackMath{\Centerstack[c]{\longmapsto\\ \\\longmapsto}}}}
\setstackgap{L}{1.3\normalbaselineskip}
%\newcommand\DownArrow{\rotatebox[origin=c]{-90}{$\longrightarrow$\,}}

\newcommand{\framefill}{\vskip0pt plus 1filll}
\newcommand{\vin}{\rotatebox[origin=c]{-90}{$\dashv$}}
\newcommand{\catname}[1]{{\normalfont\textbf{#1}}}
\newcommand{\homodd}[0]{\catname{HoMod}}
\newcommand{\jp}[0]{\mathfrak{j}_{\mathcal{M}, \mathcal{N}}}
\newcommand{\slice}[2]{(\catname{#1}\downarrow{#2})}
\newcommand{\supp}[1]{\mathsf{supp}({#1},\mu_{#1})}
%\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
%\newcommand{\abs}[1]{\left\lvert#1\right\rvert}
\newcommand{\nat}{\mathsf{nat}}
\newcommand{\y}{\mathsf{y}}
\newcommand{\im}[1]{\mathrm{Im}(#1)}
\newcommand{\chain}[1]{\catname{Ch}(\catname{#1})}
\newcommand{\homo}[1]{\mathcal{K}(\catname{#1})}
\newcommand{\colim}[0]{\mathrm{colim}}
\newcommand{\rela}[2]{\mathscr{Rel}_\mathcal{#2}(\catname{#1})}
\newcommand{\sub}{\mathsf{Sub}}
\newcommand{\dom}{\mathrm{dom}}
\newcommand{\cod}{\mathrm{cod}}
\newcommand{\co}[1]{\{\abs{#1}\}}
\newcommand{\eq}[3]{[#1 = #2]_{#3}}
\newcommand{\equ}[2]{[#1 \equiv #2]}
\newcommand{\rel}[3]{\frak{R}_{\mathcal{#3}}(#1, #2)}
\newcommand{\sat}[0]{\mathsf{cl}}
\newcommand{\cov}{\vartriangleleft}
\newcommand{\pos}[1]{\mathsf{Pos}_{\mathfrak{#1}}}
\newcommand{\rk}[2]{\mathrm{rk}_{#1}({#2})}
\newcommand{\lind}[1]{\mathcal{L}({#1})}
\newcommand{\class}[1]{\catname{Cl}({#1})}
\newcommand{\hoclass}[1]{\catname{HoCl}({#1})}
\newcommand{\propo}[0]{\mathsf{Prop}}
\newcommand{\term}[2]{\mathbf{Term}({#1}, {#2})}
\newcommand{\formu}[1]{\mathbf{Form}_{#1}}
%\newcommand{\ex}[1]{\mathscr{ex(#1)}}
\newcommand{\inte}[1]{\llbracket{#1}\rrbracket}
\newcommand{\typ}[1]{\mathsf{Type}({#1})}
\newcommand{\Set}{\textbf{\textup{Set}}}
\newcommand{\m}[1]{\textbf{\textup{#1}}}
\newcommand{\sh}{\textbf{\textup{Sh}}}
\NewDocumentCommand{\transp}{m o}{%
	\ensuremath{({#1},%
		\IfNoValueTF{#2}%
		{{#1}+1}%
		{#2}%
		)}
}

\newcommand{\inv}[1]{\mathsf{inv}({#1})}

\newcommand{\modd}[0]{\catname{Mod}}
\newcommand{\des}[1]{Des({#1})}
\newcommand{\prof}[2]{\mathsf{Proof}({#1},{#2})}
\newcommand{\ab}[0]{=-Adj}
\newcommand{\ba}[0]{=-E}
\newcommand{\su}[2]{\mathfrak{s}_{#1}^{#2}}
\newcommand{\ipos}[1]{\catname{Pos}(\catname{#1})}
\newcommand{\Su}[2]{\mathfrak{S}_{#1}^{#2}}
\newcommand{\Pro}[2]{\mathfrak{P}_{#1}^{#2}}
\newcommand{\surr}[0]{\mathsf{surr}}
\newcommand{\propag}[0]{\mathsf{propag}}
\newcommand{\mdl}[1]{\catname{Mod}(#1)}
\newcommand{\alg}[1]{\catname{FAlg}(#1)}
\newcommand{\eim}[1]{\catname{EM}(\m{#1})}
\def\H{\textbf {\textup{H}}}
\def\X{\textbf {\textup{X}}}
\def\Y{\textbf {\textup{Y}}}
\newcommand{\fuz}[1]{\textbf{\textup{Fuz}}({\textbf {\textup{#1}}})}
%\newcommand{\yo}{\mathcal{Y}}
\renewcommand*{\bibfont}{\footnotesize}

\newcommand{\der}[1]{\underline{\dder{#1}}}

\DeclareFontFamily{U}{dmjhira}{}
\DeclareFontShape{U}{dmjhira}{m}{n}{
	<-> s*[0.95] dmjhira
}{}
\DeclareFontSubstitution{U}{dmjhira}{m}{n}

\newcommand{\yo}{%
	\raisebox{0.2\depth}[\fontcharht\font`A][0.1\depth]{%
		\usefont{U}{dmjhira}{m}{n}\symbol{"48}%
	}%
}

\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri,fit,positioning,calc}
\tikzstyle{node}=[circle, draw=black, minimum size=1mm, inner sep=1.5pt, font=\tiny]

\tikzstyle{trans}=[font=\scriptsize]
\tikzstyle{lab}=[font=\small]
\tikzset{
	coloredge/.style={
		->,
		color=red
		%densely dotted
	}
}

\tikzset{
	colorloop/.style={
		loop,
		color=red
		%densely dotted
	}
}

\tikzcdset{
	perm/.style={
		shorten >=-1mm, shorten <=-1mm,
		-,
		% dotted
	}
}

\newcommand{\pgfBox}{
	\begin{pgfonlayer}{background} 
		\fill[blue!2,thick,draw=black!50,rounded corners,inner sep=3mm] ([xshift=-1.5pt,yshift=-1.5pt]current bounding box.south west) rectangle ([xshift=1.5pt,yshift=1.5pt]current bounding box.north east);
	\end{pgfonlayer}
}

\newcommand{\id}[1]{\mathsf{id}_{#1}}

\title{Left-Linear Rewriting in Adhesive Categories}

\date[May 1977]{Calgary, September 11, 2024}
\begin{document}
	\maketitle

\begin{frame}{Concurrency}\justifying

	Key  idea of concurrency theory:  the behaviour of a computational
	device can be modelled by abstracting its sequences of steps via a suitable equivalence.

	\pause 
	\medskip 
	The equivalence captures when steps are causally unrelated and thus could be
	executed in any order, and possibly in parallel.

	\pause 
	\medskip 
	Defining this equivalence often boils down to having a notion
	of independence between two consecutive steps.

\end{frame}

\begin{frame}{DPO rewriting sytems}\justifying

		We will focus on the \emph{double pushout} (DPO) approach  to  graph rewriting (cfr. \cite{ehrig2006fundamentals}).

	\smallskip 
	\begin{overprint}
		\onslide<1|handout:1>
		A \emph{rewriting rule} is a pair  of arrows $l:K\to L$ and $r:K\to R$ with the same domain. To rewrite an object $G$ according to a rule we proceed in three steps.

		\onslide<2| handout:0>

		A \emph{rewriting rule} is a pair  of arrows $l:K\to L$ and $r:K\to R$ with the same domain. To rewrite an object $G$ according to a rule we proceed in three steps.

		First: find a \emph{match} $m:L\to G$.
		\begin{center}
			\begin{tikzpicture}
				\node(L)at(0,0){$L$};
				\node(K)at(2,0){$K$};
				\node(R)at(4,0){$R$};
				\node(G)at(0,-2){$G$};
				\draw[->](K)--(L)node[pos=0.5, above]{$l$};
				\draw[->](K)--(R)node[pos=0.5, above]{$r$};
				\draw[->, dotted](L)--(G)node[pos=0.5, left]{$m$};
			\end{tikzpicture}
		\end{center}

		\onslide<3| handout:0>

A \emph{rewriting rule} is a pair  of arrows $l:K\to L$ and $r:K\to R$ with the same domain. To rewrite an object $G$ according to a rule we proceed in three steps.

		Second: remove the image of $m$  building a pushout square. \vspace{-0.075cm}
		\begin{center}
			\begin{tikzpicture}
				\node(L)at(0,0){$L$};
				\node(K)at(2,0){$K$};
				\node(R)at(4,0){$R$};
				\node(G)at(0,-2){$G$};
				\node(C)at(2,-2){$C$};
				\draw[->](K)--(L)node[pos=0.5, above]{$l$};
				\draw[->](K)--(R)node[pos=0.5, above]{$r$};
				\draw[->](L)--(G)node[pos=0.5, left]{$m$};
				\draw[->, dotted](K)--(C)node[pos=0.5, right]{$p$};
				\draw[->, dotted](C)--(G)node[pos=0.5, below]{$l'$};
			\end{tikzpicture}
		\end{center}		
		\onslide<4| handout:0>

		A \emph{rewriting rule} in a category $\X$ is a pair  of arrows $l:K\to L$ and $r:K\to R$ with the same domain. To rewrite an object $G$ according to a rule we proceed in three steps.

		Third: fill the hole so obtained, with $R$ taking a pushout.\vspace{-0.075cm}
		\begin{center}\hspace{0.045cm}
			\begin{tikzpicture}
				\node(L)at(0,0){$L$};
				\node(K)at(2,0){$K$};
				\node(R)at(4,0){$R$};
				\node(G)at(0,-2){$G$};
				\node(C)at(2,-2){$C$};
				\node(H)at(4,-2){$H$};
				\draw[->](K)--(L)node[pos=0.5, above]{$l$};
				\draw[->](K)--(R)node[pos=0.5, above]{$r$};
				\draw[->](L)--(G)node[pos=0.5, left]{$m$};
				\draw[->](K)--(C)node[pos=0.5, right]{$p$};
				\draw[->](C)--(G)node[pos=0.5, below]{$l'$};
				\draw[->, dotted ](C)--(H)node[pos=0.5, below]{$r'$};
				\draw[->, dotted ](R)--(H)node[pos=0.5, right]{$q$};
			\end{tikzpicture}
		\end{center}		
	\end{overprint}  	
\end{frame}

\begin{frame}{DPO rewriting system}\justifying
The categorical framework is given by \emph{$\mathcal{M}$-adhesive categories}. \pause 
\begin{definition}[\cite{lack2005adhesive,azzi2019essence,ehrig2014adhesive}]
	Let $\mathcal{M}$ be a class of monos in a category $\X$, containing all isomorphisms, stable under pullbacks and composition. $\X$ is \emph{$\mathcal{M}$-adhesive} if, given a cube below with the hooked arrows in $\mathcal{M}$, the bottom face a pushout and the back faces pullbacks, we have:

	\parbox{5cm}{\centering \begin{tikzpicture}
		\node(C)at(-1,0.4){$C$};
		\node(A)at(1,0.8){$A$};
		\node(B)at(2,0.4){$B$};
		\node(D)at(0,0){$D$};
		\node(A')at(1,2){$A'$};
		\node(B')at(2,1.6){$B'$};
		\node(C')at(-1,1.6){$C'$};
		\node(D')at(0,1.2){$D'$};
		\draw[<-](B')--(A');
		\draw[>->](B')--(B);
		\draw[>->](C')--(C); 
		\draw[>->](D')--(D);
		\draw[->](A')--(C'); 
		\draw[->](B')--(D');
		\draw[->](C')--(D');
		\draw[->](A)--(B);
		\draw[->](C)--(D);
		\draw[->](B)--(D);
		\draw[>-](A')--(1,1.45);
		\draw[->](1,1.35)--(A);
		\draw[>-](A)--(0.05, 0.61);
		\draw[<-](C)--(-0.05,0.59);
\end{tikzpicture}} \quad 	\parbox{4cm}{\centering
	Top face is a pushout \\ $\iff$ \\ Front faces are pullbacks}

\end{definition}
\end{frame}

\begin{frame}{DPO rewriting systems}\justifying
		\begin{definition}
		A \emph{DPO-rewriting system} is a pair $(\X, R)$ where $\X$ is an $\mathcal{M}$-adhesive category and $R$ is a set of rewriting rules.
		\pause

		A system is \emph{linear} if every rule is made by arrows in $\mathcal{M}$, \emph{left linear} if the left hand side of every rule is in $\mathcal{M}$.
	\end{definition}

\pause

In left linear rewriting systems a rule can ``merge'' parts of the state.

\pause 
\begin{alertblock}{Motivation}
	Our long term aim is to provide a concurrent semantics for left linear DPO-rewriting systems (see \cite{baldan2017domains}). 
\end{alertblock}

\end{frame}

\begin{frame}{An example}\justifying

	We want to model a situation in which a coffee comes
	with a bag of sugar, a portion of milk and bag of cocoa.

	\pause 
\begin{figure}
	\input{Figure/coffee-rules2.tex}

\end{figure}
\end{frame}

\begin{frame}{An example}
	If we want a (very sweet) coffee we can add first the milk and sugar, then cocoa. Finally we can stir it.
	\pause 
\begin{figure}
	\input{Figure/coffee-rewriting2.tex}
\end{figure}\pause

$\rho_s$ only needs sugar, so it can be anticipated before $\rho_c$, but in order to do so the presence of $\rho_m$ at the beginning is essential.
\end{frame}

\begin{frame}{Sequential Independence}\justifying

	\begin{definition}  Two consecutive steps are \emph{sequentially independent} it the dotted arrows in the diagram below exist (\emph{independence pair}).
		\begin{center}
			\begin{tikzpicture}
				\node (A)at(0,1){$L_1$};
				\node (B)at(1,1){$K_1$};
				\node (C)at(2,1){$R_1$};
				\node (D)at(4,1){$L_2$};
				\node (E)at(5,1){$K_2$};
				\node(F) at(6,1){$R_2$};
				\node (G)at(0,0){$G_1$};
				\node (H)at(1,0){$H_1$};
				\node (I)at(3,0){$G_2$};
				\node (L)at(5,0){$H_2$};
				\node (M)at(6,0){$G_3$};

				\draw[>->](B)--(A);
				\draw[->](B)--(C);
				\draw[>->](E)--(D);
				\draw[->](E)--(F);
				\draw[>->](H)--(G);
				\draw[->](H)--(I);
				\draw[>->](L)--(I);
				\draw[->](L)--(M);
				\draw[->](A)--(G);
				\draw[->](B)--(H);
				\draw[->](C)--(I);
				\draw[->](D)--(I);
				\draw[->](E)--(L);
				\draw[->](F)--(M);
				\draw[dotted, ->](C) to [out=0, in=150](L);
				\draw[dotted, ->](D)to [out=180, in=30](H);
			\end{tikzpicture}
		\end{center}
		\end{definition}

\pause 
If a system is linear:
\begin{enumerate}
	\item uniqueness of independence pair; \pause 
	\item Local Church-Rosser Theorem: sequentially independent steps can be switched.
\end{enumerate}

\end{frame}

\begin{frame}{Church-Rosser can fail}\justifying

\begin{columns} 
	\begin{column}{.30\textwidth}\centering 	
\xymatrix@C=16pt@R=1pt{
	& 0 \ar@{-}[dd] \ar@{-}[ddddddl] \ar@{-}[ddddddr] &  \\
	&  & \\
	& 1 \ar@{-}[dd] \ar@{-}[ddddl]  \ar@{-}[ddddr]   &  \\
	&  & \\
	& 2 \ar@{.}[d] \ar@{-}[ddl]   \ar@{-}[ddr]     &  \\
	&  \ar@{.}[dl]   \ar@{.}[dr] & \\
	b \ar@{-}[dr] & & c \ar@{-}[dl]\\
	& a } \\
	$\mathcal{M}$ is the class of the identities.	
\end{column}

	\begin{column}{.70\textwidth} \centering
\begin{tikzpicture}
		\node (A)at(0,1){$a$};
		\node (B)at(1,1){$a$};
		\node (C)at(2,1){$0$};
		\node (D)at(4,1){$a$};
		\node (E)at(5,1){$a$};
		\node(F) at(6,1){$b$};
		\node (G)at(0,0){$c$};
		\node (H)at(1,0){$c$};
		\node (I)at(3,0){$0$};
		\node (L)at(5,0){$0$};
		\node (M)at(6,0){$0$};

		\draw[>->](B)--(A);
	\draw[->](B)--(C);
	\draw[>->](E)--(D);
	\draw[->](E)--(F);
	\draw[>->](H)--(G);
	\draw[->](H)--(I);
	\draw[>->](L)--(I);
	\draw[>->](L)--(M);
	\draw[->](A)--(G);
	\draw[->](B)--(H);
	\draw[>->](C)--(I);
	\draw[->](D)--(I);
	\draw[->](E)--(L);
	\draw[->](F)--(M);
	\draw[>->](C) to [out=0, in=150](L);
	\draw[->](D)to [out=180, in=30](H);
	\end{tikzpicture}
\\	
Two rewriting steps.
	\end{column}
\end{columns}

 \centering
 \begin{tikzpicture}
 		\node (A)at(0,1){$a$};
 		\node (B)at(1,1){$a$};
 		\node (C)at(2,1){$b$};

 		\node (G)at(0,0){$c$};
 		\node (H)at(1,0){$c$};

 		\draw[>->](B)--(A);
 		\draw[->](B)--(C);

 		\draw[>->](H)--(G);

 		\draw[->](A)--(G);
 		\draw[->](B)--(H);

 	\end{tikzpicture}
\\
No rewriting step.

\end{frame}

\begin{frame}{Well switching rewriting systems}\justifying

\begin{definition}
A rewriting system $(\X, R)$ is \emph{well switching} of independence pairs are unique and the Local Church-Rosser Theorem holds (sequentially independent derivation can be switched).
\end{definition}
\pause 
\begin{block}{Remark}
	It is possible to identify a larce class of categories on which every left-linear rewriting system enjoys the Local-Church Rosser Theorem holds (\cite{baldan2011adhesivity}).
\end{block}
\pause 
\begin{block}{Example}In the category $\catname{Graph}$, if the rules of a left-linear rewriting system only merge nodes and their left-hand sides contain no isolated nodes, then the system is well-switching.
\end{block}

\end{frame}

\begin{frame}{Results: the Three Steps Lemma}\justifying

\begin{lemma}  Let
	$\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ be a three-steps
	derivation in a well-switching rewriting system. 
	\begin{enumerate}\justifying
		\item
		If $\dder{D}_0$ and $\dder{D}_1$ are independent and there is a
		 sequence of switches
		$\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(1,2)}
		\dder{D}_0 \cdot \dder{D}_2' \cdot \dder{D}_1' \shift{(0,1)}
		\dder{D}_2'' \cdot \dder{D}_0' \cdot \dder{D}_1'$ then
		in the last derivation $\dder{D}_0'$ and $\dder{D}_1'$ are independent;

		\item
		\label{lem:indep-global-left:2}
		Suppose that $\dder{D}_1$ and $\dder{D}_2$ are independent, and that, in $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(1,2)}
		\dder{D}_0 \cdot \dder{D}_2' \cdot \dder{D}_1'$, $\dder{D}_0$ and $\dder{D}_2'$ are independent.  If there
		is a switching sequence
		$\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(0,1)}
		\dder{D}_1' \cdot \dder{D}_0' \cdot \dder{D}_2 \shift{(1,2)}
		\dder{D}_1' \cdot \dder{D}_2' \cdot \dder{D}_0''$ then in the last derivation $\dder{D}_1'$ and $\dder{D}_2'$ are independent.
	\end{enumerate}
\end{lemma}
\end{frame}

\begin{frame}{Results: the Three Steps Lemma}\justifying

	\begin{lemma}  Let
		$\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ be a three-steps
		derivation in a well-switching rewriting system. \pause 
		\begin{enumerate}\justifying
			\item
			If $\dder{D}_0$ and $\dder{D}_1$ are independent and there is a
			sequence of switches
			$\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(1,2)}
			\dder{D}_0 \cdot \dder{D}_2' \cdot \dder{D}_1' \shift{(0,1)}
			\dder{D}_2'' \cdot \dder{D}_0' \cdot \dder{D}_1'$ then
			in the last derivation $\dder{D}_0'$ and $\dder{D}_1'$ are independent; \pause

			\item 
			Suppose that $\dder{D}_1$ and $\dder{D}_2$ are independent, and that, in $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(1,2)}
			\dder{D}_0 \cdot \dder{D}_2' \cdot \dder{D}_1'$, $\dder{D}_0$ and $\dder{D}_2'$ are independent.  If there
			is a switching sequence
			$\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(0,1)}
			\dder{D}_1' \cdot \dder{D}_0' \cdot \dder{D}_2 \shift{(1,2)}
			\dder{D}_1' \cdot \dder{D}_2' \cdot \dder{D}_0''$ then in the last derivation $\dder{D}_1'$ and $\dder{D}_2'$ are independent.
		\end{enumerate}
	\end{lemma}
\end{frame}

\begin{frame}{Results: the Three Steps Lemma}\justifying
Meaning of the previous the previous Lemma: \pause 
\begin{enumerate}
	\item if two derivation steps are independent and we are able to \emph{anticipate} something, then the steps remains independent; \pause 
	\item the independence of two derivation steps can depend on the steps before them, in particular \emph{posticipating} something does not preserves independence.
\end{enumerate}
\pause

\begin{block}{Remark}
The possibility of losing independence posticipating a derivation is due to left-linearity: it can be proved that in linear systems \emph{independence is global}, i.e. that given two independent contiguous steps, if  at the end of a sequence of switchings they are again contiguous, then they are also still independent (\cite{heindel2009category}).
\end{block}

\end{frame}

\begin{frame}{Risultati: Canonical Form}\justifying

	\begin{theorem}[No need of useless switches]
		Let $\der{D}$ and $\der{D}'$ be derivations If $\der{D} \shifteq[\sigma] \der{D}'$ then there is a switching sequence 
		%\begin{center}
		$\der{D} \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
		\shift{\nu_n} \der{D}'$
		%\end{center}
		consisting only of inversions for $\sigma$ (i.e. permutations $(i, i+1)$ such that $\sigma(i)>\sigma(i+1)$).
	\end{theorem}

\begin{theorem}[Canonical form]
	Let $\der{D}$ and $\der{D}'$ be derivations. If
	$\der{D} \shifteq[\sigma]\der{D}'$ then there is a switching sequence
	\begin{center}
		$\der{D} \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
		\shift{\nu_n} \der{D}'$
	\end{center}
	where for $i \in [1,n]$ we have $\nu_i  = \transp{k}$ with 
	$k = \max \{ j \mid \transp{j} \in \inv{\nu_{i,n}}\}$.
\end{theorem}
\end{frame}

\begin{frame}{Future works}\justifying 
	This work is only the first step in an attempt to construct a concurrent semantics for left-linear DPO rewriting systems.

	In \cite{baldan2017domains} a category of domains, called \emph{weak prime domains} has been proposed as a possible concurrent semantic for systems allowing fusions. We plan to build on the results proved in this paper to show that to every left-linear DPO rewriting system it is possible to associate one of these domains, representing ``derivation up to switches''.
\end{frame}

\begin{frame}{\hspace{1pt}}
	\LARGE
	\begin{center}
		Thank you for your attention!
	\end{center}

\end{frame}

\section{Bibliography}
\begin{frame}[allowframebreaks]{Bibliography}\justifying 
\printbibliography
\end{frame}

\end{document}

### 2024-09-09 domains/domains.tex
section domains

@@
 
-CONCUR ruslts: strong enforcing + well-switching => nice behaviour of independence.
+CONCUR results: strong enforcing + well-switching => nice behaviour of independence.
 
@@
 
-   implies
+$\Rightarrow$
 
@@
 - well-behaved with respect to quotients, e.g.,
-   \begin{enumerate}
-   \item  if we can rewrite G with L <- K -> R and we take a quotient
-     of G which factories through the colimit, then we can still rewrite
 
-   \item if we can rewrite G with L <- K -> R and we take a G' which
-     has G as a quotient and we can find a match in G' (which factorises
+\begin{enumerate}[a.]
+\item  if we can rewrite $G$ with $L \leftarrow K \to R$ and we take a quotient
+  of $G$ which factorises through the colimit, then we can still rewrite
+
+\item if we can rewrite $G$ with $L \leftarrow K \to R$ and we take a $G'$ which
+  has $G$ as a quotient and we can find a match in $G'$ (which factorises
   through the quotient) then we can still rewrite
 
-   \item existence of the "largest" quotient to which a rule applies
+\item existence of the ``largest'' quotient to which a rule applies
 
-   \item independence "in the colimit" [notes pag. 20-22 for ordinary
-     derivations, then adapt to derivations up to fusion, which are ordinary
+\item independence ``in the colimit'' [notes pag. 20-22 for ordinary
+  derivations, later adapt to derivations up to fusion, which are ordinary
   derivations in the quotient]
@@
 \subsubsection*{3.1 Domain of traces}
-finitary, coherent, irreducible algebraic
-    characterise irreducibles [traces with last step not switchable]
-    [notes page 1-9, holds in general in the setting of concur]
+
+\begin{enumerate}[a.]
+
+\item  finitary, coherent, irreducible algebraic
+
+\item need of characterising the  irreducibles: traces with last step not switchable
+\end{enumerate}
+
+[notes page 1-9, this holds in general in the setting of concur]
 
@@
 
-    - Interchargeability relation and its characterisation via the notion
+\begin{enumerate}[a.]
+
+\item Interchargeability relation and its characterisation via the notion
   of derivation up to fusion
 
-    - derivations up to fusion and properties [notes pag. 24-27]
+\item derivations up to fusion and properties [notes pag. 24-27]
 
-    - characterising the interchangeability relation using
+\item characterising the interchangeability relation using
 derivations up to fusion [some idea at pag. 29, notes]
 
-    - proving the interchangeability axioms to conclude that we
+\item  proving the interchangeability axioms to conclude that we
 obtain a weak prime domain [pag. 30-32, notes]
+\end{enumerate}
 

### 2024-09-09 concur/presentazione/Figure/coffee-rewriting2.tex

--- 2024-07-02 concur/Figure/coffee-rewriting.tex
@@
   % 
-  \begin{tikzpicture}[node distance=4mm, font=\small]
+  \begin{tikzpicture}[node distance=8mm, font=\small]
     % graph G0
     \node (G0) {
-      \begin{tikzpicture}[node distance=2mm, font=\scriptsize]
+      \begin{tikzpicture}[node distance=2mm, label distance=1mm, font=\scriptsize]
         % 
         \node at (0,1.0) [node, label=left:$1$] (1) {}
-        edge [in=110, out=140, loop] node[above] {$\mathit{w}$} ()
-        edge [in=220, out=250, loop] node[below] {$\mathit{b}$} ();
+        edge [in=110, out=140, loop] node[above] {$\mathit{m}$} ()
+        edge [in=220, out=250, loop] node[below] {$\mathit{c}$} ();
 
         \node at (0.7,1.0) [node, label=right:$2$] (2) {}
-        edge [in=40, out=70, loop] node[above] {$\mathit{c}$} ();
+        edge [in=40, out=70, loop] node[above] {$\mathit{u}$} ();
 
@@
     \node [right=of G0] (G1) {
-      \begin{tikzpicture}[node distance=2mm, font=\scriptsize]
+      \begin{tikzpicture}[node distance=2mm, label distance=1mm,, font=\scriptsize]
       % 
       \node at (0.6,1.0) [node, label=right:$12$] (12) {}
-        edge [in=220, out=250, loop] node[below] {$\mathit{b}$} ()
-        edge [in=40, out=70, loop] node[above] {$\mathit{c}$} ()
+        edge [in=220, out=250, loop] node[below] {$\mathit{c}$} ()
+        edge [in=40, out=70, loop] node[above] {$\mathit{u}$} ()
         edge [in=300, out=330, loop] node[below] {$\mathit{s}$} ();        
@@
     \node [right=of G1] (G2) {        
-      \begin{tikzpicture}[node distance=2mm, font=\scriptsize]
+      \begin{tikzpicture}[node distance=2mm, label distance=1mm, font=\scriptsize]
         %
+        \node at (0.4,0.5) {};
       \node at (0.6,1.0) [node, label=right:$12$] (12) {}
 %        edge [in=220, out=250, loop] node[below] {$\mathit{b}$} ()
-        edge [in=40, out=70, loop] node[above] {$\mathit{c}$} ()
+        edge [in=40, out=70, loop] node[above] {$\mathit{u}$} ()
         edge [in=300, out=330, loop] node[below] {$\mathit{s}$} ();        
@@
     \node [right=of G2] (G3) {      
-      \begin{tikzpicture}[node distance=2mm, font=\scriptsize]
+      \begin{tikzpicture}[node distance=2mm, label distance=1mm, font=\scriptsize]
         %
+        \node at (0.4,0.5) {};
       \node at (0.6,1.0) [node, label=right:$12$] (12) {}
@@
 
-    \path (G0) edge[->] node[trans, above] {$\rho_w$} (G1);
-    \path (G1) edge[->] node[trans, above] {$\rho_b$} (G2);
-    \path (G2) edge[->] node[trans, above] {$\rho_r$} (G3);    
+    \path (G0) edge[->] node[trans, above] {$\rho_m$} (G1);
+    \path (G1) edge[->] node[trans, above] {$\rho_c$} (G2);
+    \path (G2) edge[->] node[trans, above] {$\rho_s$} (G3);    
   \end{tikzpicture}

### 2024-09-09 concur/presentazione/Figure/coffee-rules2.tex

\begin{center}

  %%% RULES 
  % 
  % RULE add white sugar
  % 
  \begin{tikzpicture}[node distance=3mm, font=\small]
    %, baseline=(current bounding box.center), font=\small]
      \node (l) {
      \begin{tikzpicture}[node distance=2mm, label distance=1mm, font=\scriptsize]
      % 
      \node at (0,1.0) [node, label=left:$1$] (1) {}
        edge [in=110, out=140, loop] node[above] {$\mathit{m}$} ();

        \node at (0,0.6) {};

        \node at (0.7,1.0) [node, label=right:$2$] (2) {};

        \draw[->] (1) to node[above, pos=0.4]{$\mathit{s}$} (2);        
      %
      \pgfBox
      \end{tikzpicture} 
    };
    \node [right=of l] (r) {
      \begin{tikzpicture}[node distance=2mm, label distance=1mm, font=\scriptsize]
        %
        \node at (0,1.45) {};
        \node at (0,0.5) {};
        \node at (0.6,1.0) [node, label=right:$12$] (12) {}
          edge [in=300, out=330, loop] node[below] {$\mathit{s}$} (); 
      %
      \pgfBox
      \end{tikzpicture}
    };
    %\node[below] at (l.south east) {$\rho_w$};
    \path (l) edge[->] (r);
    \node at ($(l)!0.54!(r)$) [below=7.5mm] {$\rho_m$: add milk and sugar}; 
    \end{tikzpicture}
    % 
    %
    \hspace{5mm}
    % \hfill
    % 
    % RULE cocoa
    %
    \begin{tikzpicture}[node distance=3mm, font=\small]
    %, baseline=(current bounding box.center), font=\small]
      \node (l) {
      \begin{tikzpicture}[node distance=2mm, label distance=1mm, font=\scriptsize]
      % 
       \node at (0,1.0) [node, label=left:$1$] (1) {}
        edge [in=220, out=250, loop] node[below] {$\mathit{c}$} ();

        \node at (0,0.6) {};

        \node at (0.7,1.0) [node, label=right:$2$] (2) {};

        \draw[->] (1) to node[above, pos=0.4]{$\mathit{s}$} (2);

      %
      \pgfBox
      \end{tikzpicture} 
    };
    \node [right=of l] (r) {
      \begin{tikzpicture}[node distance=2mm, label distance=1mm, font=\scriptsize]
      %
      \node at (0,1.45) {};  
      \node at (0,0.5) {};
      \node at (0.6,1.0) [node, label=right:$12$] (12) {}
          edge [in=300, out=330, loop] node[below] {$\mathit{s}$} ();        
      %
      \pgfBox
      \end{tikzpicture}
    };
    \path (l) edge[->]  (r);
    \node at ($(l)!0.54!(r)$) [below=7.5mm] {$\rho_c$: add cocoa and sugar};         
    \end{tikzpicture}
    %
    \hspace{5mm}
    % RULE ready
    % 
    \begin{tikzpicture}[node distance=3mm, font=\small]
    %, baseline=(current bounding box.center), font=\small]
      \node (l) {
      \begin{tikzpicture}[node distance=2mm, label distance=1mm, font=\scriptsize]
      % 
      \node at (0.4,0.5) {};
      \node at (0.6,1.0) [node, label=right:$1$] (1) {}
        edge [in=40, out=70, loop] node[above] {$\mathit{u}$} ()
        edge [in=300, out=330, loop] node[below] {$\mathit{s}$} ();
      %
      \pgfBox
      \end{tikzpicture} 
    };
    \node [right=of l] (r) {
      \begin{tikzpicture}[node distance=2mm, label distance=1mm, font=\scriptsize]
      % 
      \node at (0.4,0.5) {};
      \node at (0.6,1.0) [node, label=right:$1$] (1) {}
        edge [in=40, out=70, loop] node[above] {$\mathit{r}$} ()
        edge [in=300, out=330, loop] node[below] {$\mathit{s}$} ();
      %
      \pgfBox
      \end{tikzpicture}
    };
    \path (l) edge[->] (r);    
    \node at ($(l)!0.54!(r)$) [below=7.5mm] {$\rho_s$: stir and drink!}; 
    \end{tikzpicture}
  %
\end{center}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../final"
%%% End:

### 2024-09-09 concur/presentazione/pres_lunga.tex

@@
 	The equivalence captures when steps are causally unrelated and thus could be
-	executed in any order, and possibly in parallel.
+	executed in \emph{any} order, and possibly in \emph{parallel}.
 
@@
 	Defining this equivalence often boils down to having a notion
-	of independence between two consecutive steps.
+	of \emph{independence} between two consecutive steps.
 
@@
 
-		A system is \emph{linear} if every rule is made by arrows in $\mathcal{M}$, \emph{left linear} if the left hand side of every rule is in $\mathcal{M}$.
+		A system is \emph{linear} if every rule is made by arrows in $\mathcal{M}$, \emph{left-linear} if the left hand side of every rule is in $\mathcal{M}$.
 	\end{definition}
@@
 
-In left linear rewriting systems a rule can ``merge'' parts of the state.
+In left-linear rewriting systems a rule can ``merge'' parts of the state.
 
@@
 \begin{alertblock}{Motivation}
-	Our long term aim is to provide a concurrent semantics for left linear DPO-rewriting systems (see \cite{baldan2017domains}). 
+	Our long term aim is to provide a concurrent semantics for left-linear DPO-rewriting systems (see \cite{baldan2017domains}). 
 \end{alertblock}
@@
 	We want to model a situation in which a coffee comes
-	with a bag of sugar, a portion of milk and bag of cocoa.
+	with a bag of white sugar and a bag of brown sugar.
 
@@
 \begin{frame}{An example}
-	If we want a (very sweet) coffee we can add first the milk and sugar, then cocoa. Finally we can stir it.
+	If we want a (very sweet) coffee we can add first the white sugar and then the brown one. Finally we can stir it.
 	\pause 
@@
 
-$\rho_s$ only needs sugar, so it can be anticipated before $\rho_c$, but in order to do so the presence of $\rho_m$ at the beginning is essential.
+$\rho_r$ only needs that some sugar is added, so it can be anticipated before $\rho_b$, but in order to do so the presence of $\rho_w$ at the beginning is essential.
 \end{frame}
@@
 \begin{definition}
-A rewriting system $(\X, R)$ is \emph{well switching} of independence pairs are unique and the Local Church-Rosser Theorem holds (sequentially independent derivation can be switched).
+A rewriting system $(\X, R)$ is \emph{well switching} if independence pairs are unique and the Local Church-Rosser Theorem holds (sequentially independent derivation can be switched).
 \end{definition}
@@
 \begin{block}{Remark}
-	It is possible to identify a larce class of categories on which every left-linear rewriting system enjoys the Local-Church Rosser Theorem holds (\cite{baldan2011adhesivity}).
+	It is possible to identify a large class of categories on which every left-linear rewriting system enjoys the Local-Church Rosser Theorem holds (\cite{baldan2011adhesivity}).
 \end{block}
@@
 			\item 
-			Suppose that $\dder{D}_1$ and $\dder{D}_2$ are independent, and that, in $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(1,2)}
+			suppose that $\dder{D}_1$ and $\dder{D}_2$ are independent, and that, in $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(1,2)}
 			\dder{D}_0 \cdot \dder{D}_2' \cdot \dder{D}_1'$, $\dder{D}_0$ and $\dder{D}_2'$ are independent.  If there
@@
 
-\begin{frame}{Risultati: Canonical Form}\justifying
+\begin{frame}{Results: Canonical Form}\justifying
 
@@
 	\end{theorem}
-
+\pause 	
 \begin{theorem}[Canonical form]
@@
 
+	\smallskip \pause
+
 	In \cite{baldan2017domains} a category of domains, called \emph{weak prime domains} has been proposed as a possible concurrent semantic for systems allowing fusions.
-We plan to build on the results proved in this paper to show that to every left-linear DPO rewriting system it is possible to associate one of these domains, representing ``derivation up to switches''.
+
+	\smallskip \pause We plan to build on the results proved in this paper to show that to every left-linear DPO rewriting system it is possible to associate one of these domains, representing ``derivation up to switches''.
 \end{frame}

### 2024-10-11 domains/domains.tex
minori

@@
 
+\newcommand{\cori}{\mathbf{CS}}
+\newcommand{\cla}{\mathbf{CL}}
+\newcommand{\pos}{\mathbf{PO}}
+\newcommand{\gori}{\mathbf{GS}}
+
 %symbol for natural numbers
@@
 \newcommand{\diff}[2]{\ensuremath{\delta({#1},{#2})}}
+
+%arrows
+\newcommand{\rightarrowdbl}{\rightarrow\mathrel{\mkern-14mu}\rightarrow}
+
+\newcommand{\xrightarrowdbl}[2][]{%
+	\xrightarrow[#1]{#2}\mathrel{\mkern-14mu}\rightarrow
+}
+
+\newcommand{\mini}[0]{\scalebox{.4}{$\bullet$}}
+\newcommand{\rto}[0]{\xrightarrow{\mini}}
+\newcommand{\fto}[0]{\xrightarrowdbl{\mini}}
+\newcommand{\eto}[0]{\twoheadrightarrow}
 
@@
 
+\newcommand{\mf}[1]{{#1}^\mathsf{m}}
 \newcommand{\dph}{\mathsf{dph}}
@@
 %mono
-\newcommand{\mto}[0]{\scalebox{1}{$\rightarrowtail$}}
+\newcommand{\mto}[0]{\rightarrowtail}
 
@@
 \def\G{\textbf {\textup{G}}}
+\def\Z{\textbf {\textup{Z}}}
+
+\newcommand{\dm}[1]{\mathsf{dom}({#1})}
+
+\newcommand{\sub}[3]{{\mathcal{#1}}\textrm{-}\mathsf{Sub}_{\textbf {\textup{#2}}}(#3)}
+
+\newcommand{\msub}[2]{\mathsf{Sub}_{\textbf {\textup{#1}}}(#2)}
 
@@
 
+\newtheorem*{setting}{Setting}
 %\theoremstyle{definition}
@@
 
-\section{A class of well behaved rewriting systems}
+\subsection{Consistent permutations}
+
+\section{A class of well-behaved rewriting systems}
 \label{sec:rewr}
+
+This section is devoted to the introduction and study of a, quite general, setting in which the study of the concurrency properties of left-linear DPO-rewriting systems can be carried on.
+
+\begin{setting}Let $(\X, \R)$ be a left-linear DPO-rewriting system on an $\mathcal{M}$-adhesive category $\X$. For the remaining of this section we assume the following properties:
+	\begin{enumerate}
+		\item $\X$ has all pushouts and pullbacks;
+		\item there is a proper and stable factorization system $(\mathcal{E}, \mathcal{M})$ on $\X$;
+		\item $(\X, \R)$ is strong-enforcing;
+		\item there is a good coreflective subcategory $\Y$ of $\X$ containing that the left- hand side of every rule in $\R$;
+		\item $ I_{\Y}\circ R_{\Y}$ sends arrows who are in  $\mathcal{R}_\Y\cap \mathcal{E}$ to arrows in $\mathcal{E}$;
+		\item $\mathcal{R}_\Y $ contains the right leg of every rule in $\R$.
+	\end{enumerate}
+
+	Given an arrow $f\colon X\to Y$ of $\X$,  we will use the following notational conventions:
+	\begin{itemize}
+		\item $f\colon X\mto Y$ if $f$ belongs to $\mathcal{M}$;
+		\item $f\colon X\eto Y$ if $f$ belongs to $\mathcal{E}$;
+		\item $f\colon X \rto Y$ if $f$ belongs to $\mathcal{R}_\Y$ ;
+		\item $f\colon X \fto Y$ if $f$ is a \emph{fusion}, i.e.~belongs to both $\mathcal{R}_\Y$ and $\mathcal{E}$. 
+		\end{itemize}
+
+		Given an object $X$, we can consider the poset $\fuse{X}$
+\end{setting}
+
+\begin{proposition}\label{prop:fusion}
+	The class of fusions is stable under pullbacks, pushouts and closed under composition. Moreover, the image of a fusion through $I_\Y\circ R_{\Y}$ is again a fusion.
+\end{proposition}
+\begin{proof}
+	By \Cref{prop:varie} we know that $\mathcal{R}_\Y$ is closed under composition and stable under pullbacks, while it is stable under pushout by definition.
+On yhe other hand, $\mathcal{E}$ is stable under pushout and closed under composition by \Cref{cor:iso2}.
+By hypothesis $(\mathcal{E}, \mathcal{M})$ is stable and so $\mathcal{E}$ is stable under pullbacks.
+Let now $e\colon X\fto Y$ be a fusion we have a diagram:
+	\[\xymatrix@C=35pt{R_\Y(I_\Y(R_{\Y}(X))) \ar[r]^-{R_\Y(\epsilon_X)} \ar[d]_{R_\Y(I_\Y(R_\Y(e)))}&R_{\Y}(X) \ar[d]^{R_\Y(e)}\\R_\Y(I_\Y(R_{\Y}(Y))) \ar[r]_-{R_\Y(\epsilon_Y)}&R_\Y(Y)}\]
+
+	By \Cref{cor:cou} the horizontal arrows are isomorphisms and $R_\Y(e)$ is mono because $e$ is a fusion, thus $I_\Y(R_\Y(e))$ is in $\mathcal{R}_\Y$.
+By hypothesis $I_\Y(R_\Y(e))$ is in $\mathcal{E}$ and we can conclude.
+\end{proof}
+
+\begin{example}
+\todo{grafi}
+\end{example}
+
+\begin{remark}\label{rem:ws}
+Under the conditions of our setting, the system $(\X, \R)$ is well switching.
+Indeed, suppose that the diagram below is given.
+Since $f_1$ is in $\mathcal{M}$ we have that $j_0=i_0$, on the other hand, $L_1$ belongs to $\Y$ and $g_0$ belongs to $\mathcal{R}_\Y$, and so $j_1$ is equal to $i_1$ by the fourth point of \Cref{prop:varie}.
+	\[\xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]_{r_0}^{\mini} & R_0 \ar@/^.3cm/@<-.5ex>[drrr]|(.22)\hole|(.32)\hole_(.4){i_0} \ar@<.5ex>@/^.3cm/[drrr]|(.3)\hole|(.39)\hole^(.7){j_0} \ar[dr]|(.29)\hole|(.35)\hole_{h_0} && L_1 \ar@<.5ex>@/_.3cm/[dlll]^(.4){i_1} \ar@<-.5ex>@/_.3cm/[dlll]_(.7){j_1} \ar[dl]|(.29)\hole|(.35)\hole^(.6){m_1}& K_1\ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[rr]_{r_1}^{\mini} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0} D \ar[rr]_{g_0}^{\mini}&& G_1  && \ar@{>->}[ll]^{f_1} D_1 \ar[rr]_{g_1}^{\mini}&& G_2}\]
+\end{remark}
+
+\begin{lemma}Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^{n}$ be a derivation, then the following hold true:
+	\begin{enumerate}
+		\item $\iota_{\der{D}, G_0}\colon G_0\to \tpro{D}$ belongs to $\mathcal{R}$ and $\iota_{\der{D}, G_{n+1}}\colon G_{n+1}\to \tpro{D}$ belongs to $\mathcal{M}$;
+		\item for every $i\in [0, n+1]$, there are  arrows $m_i$ in $\mathcal{M}$ and $r_i$ in $\mathcal{R}$ such that the coprojection $\iota_{\der{D}, G_i}\colon G_i\to \tpro{D}$ is equal to $r_i\circ m_i$.
+	\end{enumerate}
+\end{lemma}
+\begin{proof}
+	\begin{enumerate}		
+		\item We proceed by induction on the length of $\der{D}$.
+
+		\smallskip \noindent $\lgh(\dder{D})=0$. then $\tpro{\dder{D}}$ is simply $(G_0, \{\id{G_0}\})$ and $\id{G_0}$ belongs to $\mathcal{M}$ and $\mathcal{R}$.
+
+		\smallskip \noindent$\lgh(\dder{D})=1$. Suppose that $\dder{D}$ has as its single component the derivation
+		\[\xymatrix{L_0 \ar[d]_{m_0}& K_0 \ar[d]^{k_0}\ar@{>->}[l]_{l_0} \ar[r]_{r_0}^{\mini} & R_0 \ar[d]^{h_0} \\G_0& \ar@{>->}[l]^{f_0} D_0 \ar[r]_{g_0}^{\mini}& G_1  \\}\]
+	Then the thesis follows since we have the following pushout square.
+		\[\xymatrix{D_0 \ar@{>->}[d]_{f_0} \ar[r]_{g_0}^{\mini} & G_1 \ar@{>->}[d]^{\iota_{\der{D}, G_1}} \\G_0 \ar[r]_-{\iota_{\der{D}, G_0}}^{\mini}& \tpro{D} }\]
+
+		\smallskip \noindent$\lgh(\dder{D})\geq 2$.
+Let $\der{D}$ be $\{\dder{D}_i\}_{i=0}^n$ with $n\geq 1$.
+Let also $\der{D}'$ be $\{\dder{D}_i\}^{n-1}_{i=0}$ and $\rho_n=(l_n, r_n)$ be the rule applied in $\dder{D}_n$.
+The thesis follows from the inductive hypothesis and the diagram below.
+		\[\xymatrix@C=30pt{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar@{>->}[l]_{l_{n}} \ar[r]_{r_{n}}^{\mini} & R_{n} \ar[d]^{h_n} \\ G_{n} \ar@{>->}[d]_{\iota_{\der{D}' , G_{n}}}& \ar@{>->}[l]^{f_n} D_n \ar[r]^{\mini}_{g_n}& G_{n+1}  \ar@{>->}[d]^{\iota_{\der{D}, G_{n+1}}}\\  \lpro \der{D}' \ar[rr]_{p}^{\mini} \rpro && \tpro{D}\\ G_0 \ar[u]^-{\iota_{\der{D}', G_{0}}}_{\mini} \ar@/_.5cm/[urr]_{\iota_{\der{D}, G_0}}^\mini}\]
+
+		\item We proceed again by induction the length of $\der{D}$.
+
+		\smallskip \noindent$\lgh(\dder{D})=0$. This follows at once from the previous point.
+
+		\smallskip \noindent$\lgh(\dder{D})=1$. Again, this follows from the previous point.
+
+		\smallskip \noindent$\lgh(\dder{D})\geq 2$.
+As above, if $\der{D}$ is $\{\dder{D}_i\}_{i=0}^n$ with $n\geq 1$, we can consider the derivation $\der{D}':=\{\dder{D}_i\}^{n-1}_{i=0}$ and consider the rule $\rho_n$ be the rule applied in $\dder{D}_n$.
+By the inductive hypothesis, for every $i\in [0,n]$ we have the diagram below.
+		\[\xymatrix@C=30pt{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar@{>->}[l]_{l_{n}} \ar[r]_{r_{n}}^{\mini} & R_{n} \ar[d]^{h_n} \\ G_{n} \ar@{>->}[d]_{\iota_{\der{D}' , G_{n}}}& \ar@{>->}[l]^{f_n} D_n \ar[r]^{\mini}_{g_n}& G_{n+1}  \ar@{>->}[d]^{\iota_{\der{D}, G_{n+1}}}\\  \lpro \der{D}' \ar[rr]_{p}^{\mini} \rpro && \tpro{D}\\X \ar[u]^{r_i}_{\mini} &&  G_i \ar[ull]^-{\iota_{\der{D}', G_{i}}} \ar[u]_{\iota_{\der{D}, G_i}} \ar@{>->}[ll]^{m_i}}\]
+
+		The thesis now follows since $\mathcal{R}$ is closed under composition. To conclude, it is enough to notice that  the thesis for $i=n+1$ follows immediately from point $1$. 
+		\qedhere 
+	\end{enumerate}
+\end{proof}
+\begin{corollary}
+	\todo{match}
+\end{corollary}
+
+Our next step is to show that, in our setting, there is a kind of ``minimum'' fusion of an object $X$ to which a rewriting rule can be applied.
+
+\begin{definition} Let $\rho$ be a rule $(l, r)$ in $\R$ with left-hand side $L$.
+Let $e\colon X\fto Y$ and $e'\colon X\fto Y'$ be two fusions with the same domain and $m\colon L\to Y$ and $m'\colon L\to Y'$ be two arrows, we say that the pairs $(e,m)$ and $(e', m')$ are \emph{compatible with respect to $\rho$} if the following diagram is commutative, where the outer square is a pushout.
+
+\[\xymatrix{X\ar@{>>}[rr]^\mini_{e} \ar@{>>}[dd]_{e'}^\mini & & Y \ar@{>>}[dd]_{q}^\mini\\ &L  \ar[ur]_{m} \ar[dl]^{m'}\\Y' \ar@{>>}[rr]_{q'}^{\mini} && Q}\]
+
+Given a fusion $e\colon X\fto Y$ and an arrow $m\colon L\to Y$, we will denote by $\mathcal{F}_\rho(e, m)$ the class of pairs compatible with $(e, m)$ with respect to a given rule $\rho$.  
+\end{definition}
+
+\begin{example}
+	tutti i sotto quozienti
+\end{example}
+
+\begin{lemma}
+	Let $e\colon X\fto Y$, $\rho\in \R$ with left-hand side $L$ and $m\colon L\to Y$ be such that $\mathcal{F}_\rho(e, m)$.
+Then there exists a fusion $(\mf{e},\mf{m})\colon L\to \mf{Y}$  in $\mathcal{F}_\rho(e, m)$ and for every other $(e', m')$ in it there exists $f\colon \mf{Y}\to Y'$, where $Y'$ is the codomain of $e'$, such that:
+\[f\circ e =e' \qquad f\circ m=m'\]
+\end{lemma}
+
+\begin{proof}By hypothesis $I$ is non-empty, thus we can consider $k$ in it and $e_k\colon X\to Y_k$.
+Consider the two diagrams below, where the upper square  in the inner rectangle one is the image through $I_\Y\circ R_\Y$ of a pullback square, while the outer rectangle is a pushout.
+Notice that, by hypothesis and \Cref{prop:fusion}, all the horizontal arrows and the coprojection $e\colon X\to Y$ are fusions and, moreover, there exists the dotted arrow $f_k\colon Y\to Y_k$.
+	\[\xymatrix@C=55pt{I_\Y(R_\Y(P)) \ar[d]_{I_\Y(R_\Y(p_2)) } \ar@{>>}[r]_-{I_\Y(R_\Y(p_1))}^{\mini} & I_\Y(R_\Y(L)) \ar@/^.4cm/[dddr]^{q} \ar[d]_{I_\Y(R_\Y(m_k)) } \\ I_\Y(R_\Y(X)) \ar[d]_{\epsilon_X} \ar@{>>}[r]_-{I_\Y(R_\Y(e_k))}^{\mini}& I_\Y(R_\Y(Y_k)) \ar[d]_{\epsilon_X}  \\ X\ar@{>>}@/_.5cm/[drr]^{\mini}_{e} \ar@{>>}[r]_{e_k}^{\mini}& Y_k \\ &&Y\ar@{.>}[ul]_{f_k}}\]
+
+	Let now $i$ be any other element of $i$.
+
+\end{proof}
+
+ \begin{corollary}
+\todo{quoziente minimo}
+ \end{corollary}
+
+Finally....
+
+\todo{indipendenza}
+
+\subsection{Derivations with fusions}
 
@@
 \subsection{Weak prime domain and connected event structures}
+
+\bibliographystyle{plain}
+\bibliography{bibliog.bib}
+
+\appendix
+
+\section{Preliminaries on subobjects, images, pullbacks and factorization systems}\label{app:fact}
+
+This first section is devoted to recall some classic notions related to subobjects, pullbacks and ways to factorize an arrow.
+The main source for the presentation is \cite[Ch.~1]{dikranjan2013categorical}.
+\subsection{The pullback functor and right $\mathcal{M}$-images}
+
+Let us start defining the \emph{pullback functor} and show how the existence of a left adjoint to it yields a notion of image of an arrow.
+
+\begin{definition}
+	Let $\mathcal{M}$ be a class of arrows in a category $\X$ with $\mathcal{M}$-pullbacks.
+Suppose that $\mathcal{M}$ is stable under pullbacks, then given an arrow $f\colon X\to Y$, we define the \emph{pullback functor} $f^*\colon \mathcal{M}/Y\to \mathcal{M}/X$ sending an arrow $m:M\to Y$ in $\mathcal{M}$ to a chosen pullback of it along $f$.
+Given a morphism $g:m\to n$ in $\mathcal{M}/Y$, the arrow $f^*(g)$ is the unique one fitting in the diagram below.
+	\[\xymatrix{f^*(M)  \ar[dd]_{f^*(m)} \ar@{.>}[dr]_{f^*(g)}\ar[rr]^{p_m}&& M \ar[dr]^{g}\ar[dd]^(.3){m} \\&f^*(N)  \ar[rr]^(.35){p_n}|(.55)\hole \ar[dl]_{f^*(n)}&& N \ar[dl]^{n}\\ X \ar[rr]_{f}&& Y }\]
+\end{definition}
+
+\begin{notation}
+	If $m\colon M\to X$ is an arrow in $\mathcal{M}$ and $f\colon X\to Y$ is another morphism, we will denote the chosen domain of $f^*(m)$ by $f^*(M)$.
+\end{notation}
+
+\begin{proposition} Let $f\colon X\to Y$ be an arrow in a category $\X$ and $\mathcal{M}$ a class of arrows stable under pullbacks and such that $f$ has a pullback along any arrow in $\mathcal{M}$.
+Let also $F\colon\D\to \mathcal{M}/Y$ be a diagram with a limiting cone $(l, \{l_D\}_{D\in \D})$ and suppose that  $L$ is the domain of $l$.
+Denoting $F(D)$ by  $m_D\colon M_D\to Y$, if  $(L, \{l_D\}_{D\in \D}+\{l\})$ is limiting for the diagram in $\X$ determined by the family of arrows $\{m_D\}_{D\in \D}$, then for every $f\colon X\to Y$, $f^*$ preserves the limit of $F$.
+\end{proposition}
+\begin{proof}
+	Let $(a, \{a_D\}_{D\in \D})$ be a cocone in $\{\mathcal{M}/X\}$ over $f^*\circ F$. Then we have the solid part of the diagram below.
+	\[\xymatrix{A \ar@/_.8cm/[dd]_{a}\ar[d]^{a_D}  \ar@{.>}[r]_-{b} \ar@/^.5cm/@{.>}[rrr]^{c}&f^*(L)  \ar@/^.7cm/[ddl]|(.37)\hole^(.6){f^*(l)} \ar[rr]_{q} \ar[dl]^{f^*(l_D)}&&L \ar@/^.3cm/[ddl]^{l} \ar[dl]_{l_D}\\f^*(M_D)  \ar[d]^{f^*(m_D)} \ar[rr]^(.7){p_{F(D)}}&& M_D \ar[d]_{m_D} \\ X \ar[rr]_{f}&& Y }\]
+
+	Now, notice that, for every $D\in \D$ we have
+	\begin{align*}
+		m_D\circ p_{F(D)} \circ a_D&=f\circ f^*(m_D)\circ a_D \\&=f\circ a
+	\end{align*}
+	Moreover, given an arrow $g\colon D\to D'$ in $\D$ then we have
+	\begin{align*}
+		F(g)\circ p_{F(D)}\circ a_D&=p_{F(D')}\circ f^*(F(g))\circ a_D\\&=p_{F(D')}\circ a_{D'}
+	\end{align*}
+
+	Thus $(A, \{p_{F(D)}\circ a_D\}_{D\in \D}+ \{f\circ a\})$ is a cone over the diagram in $\X$ determined by $\{m_D\}_{D\in \D}$, so that we get the dotted arrow $b\colon A\to L$ in the diagram above.
+This arrow,  in turn, yields also $a\colon A\to f^*(L)$.
+Moreover, we also have that
+	\[
+	\begin{split}
+		p_{F(D)}\circ f^*(l_D)\circ b&= l_D\circ q \circ b\\&=l_D\circ c\\&=p_{F(D)}\circ a_D
+	\end{split}\qquad 
+	\begin{split}
+		f^*(m_D) \circ f^*(l_D)\circ b&= f^*(l)\circ b\\&=a\\&=f^*(m_D)\circ a_D
+	\end{split}
+	\]
+	So that $b$ defines an arrow $a\to f^*(l)$ in $\mathcal{M}/X$ auch that $f^*(l_D)\circ b =a_D$
+
+	To see that $b$ is unique, let $b'\colon a\to f^*(l)$ be another arrow such that $f^*(l_D)\circ b' =a_D$, then
+	\[\begin{split}
+		l\circ q \circ b'&=f\circ f^*(l)\circ b'\\&=f\circ a\\&=l\circ c
+	\end{split} \qquad \begin{split}
+		l_D\circ q \circ b'&=p_{F(D)}\circ f^*(l_D)\circ b'\\&=p_{F(D)}\circ a_D\\&=l_D\circ c
+		3\end{split}\]
+	Thus $q\circ b'=c$, implying that $b'=b$.
+\end{proof}
+
+The previous theorem gives us at once the following result.
+
+\begin{corollary} \label{cor:finlim}
+	Let $f\colon X\to Y$ be an arrow in a category $\X$ and $\mathcal{M}$ a class of arrows stable under pullbacks and such that $f$ has a pullback along any arrow in $\mathcal{M}$.
+Then $f^*$ preserves binary products.
+If, moreover, $\id{Y}$ belongs to $\mathcal{M}$ then $f^*$ preserves finite products.
+\end{corollary}
+
+Having examined the continuity properties of the pullback functor we can now turn to the notion of \emph{right $\mathcal{M}$-images}.
+
+\begin{definition}
+	Let $\mathcal{M}$ be a class of arrows in a category $\X$. A \emph{right $\mathcal{M}$-factorization
+	} of a morphism $f\colon X\to Y$ is a pair of arrows $m\colon M\to Y$ and $e\colon X\to M$ such that:
+	\begin{enumerate}
+		\item $m$ belongs to $\mathcal{M}$ and $f=m\circ e$;
+		\item given an arrow $n\colon N\to Z$ in $\mathcal{M}$ and two morphisms $g\colon Y\to Z$, $h\colon X\to N$ makint the solid part of the diagram below commutative, then there exists a unique dotted $v\colon M\to N$ fitting in it.
+		\[\xymatrix{X \ar[r]_-{e} \ar@/^.4cm/[rr]^{f} \ar[d]_{h}& M \ar[r]_-{m} \ar@{.>}[dl]^{v} & Y \ar[d]^{g}\\N \ar[rr]_{n} && Z}\] 
+	\end{enumerate}
+
+	The arrow $m$ will be called the \emph{right $\mathcal{M}$-image} of $f$.
+\end{definition}
+
+\begin{remark}\label{rem:uniq}
+	Right $\mathcal{M}$-factorization are essentially unique.
+To see this, let $e\colon X\to M$ and $m\colon M\to Y$ be a right $\mathcal{M}$-factorization of an arrow $f\colon X\to Y$ and suppose that  $e'\colon X\to M'$ and $m'\colon M'\to Y$ is another, then we  get the existence of the dotted arrows in the following two diagrams
+	\[\xymatrix{X \ar[r]^-{e}  \ar[d]_-{e'}& M \ar[r]^-{m} \ar@{.>}[dl]^{v} & Y \ar[d]^{\id{Y}} & X \ar[r]^-{e'}  \ar[d]_{e}& M' \ar[r]_-{m'} \ar@{.>}[dl]^{w} & Y \ar[d]^{\id{Y}}\\M' \ar[rr]_{m'} && Y & M \ar[rr]_{m} && Y}\]
+	On the other hand, from the commutativity of the diagram below we get at once that $v\circ w=\id{M'}$ and $w\circ v=\id{M}$.
+	\[\xymatrix{X \ar[rr]^-{e}  \ar[dr]_-{e'} \ar[dd]_{e}&& M \ar[r]^-{m} \ar[dl]^{v} & Y \ar[dd]^{\id{Y}} & X \ar[dr]^{e} \ar[rr]^-{e'}  \ar[dd]_{e'}&& M' \ar[r]_-{m'} \ar[dl]^{w} &Y \ar[dd]^{\id{Y}}\\ & M' \ar[dl]^{w}  \ar[drr]^{m'} &&&&M\ar[dl]^{v} \ar[drr]^{m}\\M \ar[rrr]_{m} &&& Y & M' \ar[rrr]_{m'} &&& Y}\]
+\end{remark}
+
+\begin{proposition}\label{prop:im}
+	Let $\mathcal{M}$ be a class of arrows in a category $\X$ and suppose that every morphism in $\X$ has a right $\mathcal{M}$-factorization.
+Then for every arrow $f\colon X\to Y$, there is a functor $f_*\colon \mathcal{M}/X\to \mathcal{M}/Y$ sending $m\colon M\to X$ to a chosen right $\mathcal{M}$-image of $f\circ m$.
+\end{proposition}
+\begin{notation}
+	As in the case of the pullback functor, if $m$ is an arrow $M\to X$, then we will denote the chosen domain of $f_*(m)$ by $f_*(M)$.
+\end{notation}
+\begin{proof}
+	We only have to define $f_*$ on arrows.
+Let thus $g$ be a morphism in $\mathcal{M}/X$ between $m\colon M\to X$ and $n\colon N\to X$.
+Now, since \[f\circ m = f\circ n\circ g\] the solid part of the diagram below commutes, allowing us to define $f_*(g)$ as the dotted arrow.
+	\[\xymatrix@C=30pt{M \ar[dr]_(.35){m}|(.55)\hole\ar[r]^-{e_m} \ar[d]_{g}& f_*(M)  \ar@/_.3cm/@{.>}[ddl]^(.7){f_*(g)}\ar[r]^-{f_*(m)}& Y \ar[dd]^{\id{Y}}\\N \ar[d]_{e_n} \ar[r]|(.32)\hole^(.6){n} & X  \ar[dr]^{f}\\f_*(N) \ar[rr]_{f_*(n)}&& Y}\]
+
+	It is clear that, with the above definition, $f_*(\id{m})=\id{f_*(m)}$. Let $h\colon n\to o$ be another morphism in $\mathcal{M}/X$, then we can build the following diagram.
+	\[\xymatrix@C=30pt{M \ar[r]^-{e_m} \ar[d]_{g}& f_*(M)  \ar[d]_{f_*(g)}\ar[r]^-{f_*(m)}& Y \ar[dd]^{\id{Y}}\\N \ar[r]^-{e_n} \ar[d]_{h} & f_*(N) \ar[d]_{f_*(h)} \ar[dr]^{f_*(n)}\\O\ar[r]_-{e_o}& f_*(O) \ar[r]_{f_*(o)}& Y}\]
+	From this it follows at once that $f_*(h)\circ f_*(g)=f_*(g\circ h)$.
+\end{proof}
+\begin{remark} If $\id{X}$ belongs to $\mathcal{M}$, then $f_*(\id{X})$ is a right $\mathcal{M}$-image of $f$.
+\end{remark}
+
+The relationship of right $\mathcal{M}$-images to the pullback functors is explained by the following two results.
+
+\begin{proposition}\label{prop:part}
+	Let $\mathcal{M}$ be a class of arrows  in a category $\X$, containing  all identities and stable under pullbacks.
+Suppose, moreover, that every morphism has a right $\mathcal{M}$-factorization.
+Then $f_*\dashv f^*$ for every arrow $f\colon X\to Y$.
+\end{proposition}
+\begin{proof}
+	First of all we can notice that for every $m\colon M\to X$ in $\mathcal{M}/X$ the commutativity of the solid part of the following diagram yields the dotted morphism $\eta_n\colon m\to f^*(f_*(m))$.
+	\[\xymatrix@C=30pt{M \ar@{.>}[dr]^{\eta_m} \ar@/^.4cm/[drr]^{e_m} \ar@/_.4cm/[ddr]_{m}\\ & f^*(f_*(M)) \ar[d]^{f^*(f_*(m))}\ar[r]^-{p_{f_*(m)}}& f_*(M) \ar[d]^{f_*(m)}\\ & X\ar[r]_f & Y}\]
+
+	To see that $\eta_n$ is the component of a unit $\eta\colon \id{\mathcal{M}/X}\to f^*\circ f_*$, let $g$ be a morphism $m\to f^*(n)$ for some $n\colon N\to Y$ in $\mathcal{M}/Y$.
+If $p_n:f^*(N)\to N$ is the canonical projection, then
+	\begin{align*}
+		n\circ p_n\circ g&=f\circ f^*(n)\circ g\\&=f\circ m
+	\end{align*}
+	Therefore we can consider the diagram below to get $h\colon f_*(m)\to n$ in $\mathcal{M}/Y$. 
+	\[\xymatrix@C=30pt{M \ar[r]^-{e_m} \ar[d]_{g}& f_*(M) \ar[r]^-{f_*(m)}\ar@{.>}@/^.3cm/[ddl]^{h} & Y \ar[dd]^{\id{Y}}\\f^*(N) \ar[d]_{p_n}\\N \ar[rr]_{n}&& Y}\]
+
+	Finally, the equations
+	\[\begin{split}
+		f^*(n)\circ f^*(h)\circ \eta_m&=f^*(f_*(m))\circ \eta_m\\&=m\\&=f^*(n)\circ g
+	\end{split} \qquad \begin{split}
+		p_n\circ f^*(h)\circ \eta_m&=h\circ p_m\circ \eta_m\\&=h\circ e_m\\&=p_n\circ g
+	\end{split}\]
+	entail that $f^*(h)\circ \eta_m=g$ as wanted.
+
+	Let now $h'\colon f_*(m)\to n$ be an arrow such that $f*(h')\circ \eta_m=g$, then
+	\begin{align*}
+		h'\circ e_m&=h'\circ p_{f_*(m)}\circ \eta_m\\&=p_n\circ f^*(h')\circ \eta_m\\&=p_n\circ g
+	\end{align*}
+	Thus $h'$ fits in the diagram
+	\[\xymatrix@C=30pt{M \ar[r]^-{e_m} \ar[d]_{g}& f_*(M) \ar[r]^-{f_*(m)}\ar@/^.3cm/[ddl]^{h'} & Y \ar[dd]^{\id{Y}}\\f^*(N) \ar[d]_{p_n}\\N \ar[rr]_{n}&& Y}\]
+	showing that $h=h'$.	
+\end{proof}
+
+\begin{lemma}\label{lem:rfact}
+	Let $\mathcal{M}$ be a class of arrows  in a category $\X$, containing all identities then the following are equivalent:
+	\begin{enumerate}
+		\item $\mathcal{M}$ is stable under pullbacks, $\X$ has all $\mathcal{M}$-pullbacks and every morphism has a right $\mathcal{M}$-factorization;
+		\item $\mathcal{M}$ is stable under pullbacks, $\X$ has all $\mathcal{M}$-pullbacks and for every morphism $f\colon X\to Y$, $f^*$ has a left adjoint;
+		\item every morphism has a right $\mathcal{M}$-factorization and for every arrow $f\colon X\to Y$, $f_*$ has a right adjoint.
+	\end{enumerate}
+\end{lemma}
+\begin{proof}
+	$(1\Rightarrow 2)$ This follows at once from \Cref{prop:part}.
+
+	\smallskip \noindent $(2\Rightarrow 1)$ Let $L_f\colon \mathcal{M}/X\to \mathcal{M}/Y$ be the left adjoint to $f^*$.
+Since $\id{X}$ belongs to $\mathcal{M}$ we can define $m\colon M\to Y$ in $\mathcal{M}$ as  $L_f(\id{X})$.
+Moreover, let $\eta_{\id{X}}$ be the component at $\id{X}$ of the unit of the adjunction $L_f \dashv f^*$, if $p_m$ is the projection $f^*(M)\to M$, we can also define $e$ as $p_m\circ \eta_{\id{X}}$.
+Notice that, by construction, $m\circ e=f$.
+	\[\xymatrix@C=30pt{X \ar@/^.4cm/[rr]^e \ar@/_.4cm/[dr]_{\id{X}} \ar[r]_-{\eta_{\id{X}}} & f^*(M) \ar[r]_-{p_m} \ar[d]^{f^*(m)}& M \ar[d]^{m}\\ & X \ar[r]_f& Y}\]
+
+	We have to show that $e$ and $m$ so defined really give us a right $\mathcal{M}$-factorization of $f$. We thus start with the solid part of the diagram below, with $n\in \mathcal{M}$.
+	\[\xymatrix@C=35pt{f^*(M)\ar[dr]^-{p_m}\\X \ar[r]^-{e} \ar[u]^{\eta_{\id{X}}} \ar|(.36)\hole@/_.5cm/[rr]_{f} \ar[d]_{h}&   M \ar[r]^-{m} \ar@{.>}[dl]^(.6){v} & Y \ar[d]^{g}\\N \ar[rr]_{n} && Z}\]
+
+	We can apply the pullback property of the inner rectangle below to get the dotted arrow $w\colon M\to f^*(g^*(N))$, which, by construction, defines an arrow $m\to f^*(g^*(n))$.
+	\[\xymatrix@C=30pt{X \ar@/^.5cm/[drrr]^{h} \ar@/_1cm/[ddr]_{\id{X}} \ar@{.>}[dr]^{w}\\ &f^*(g^*(N)) \ar[d]_{f^*(g^*(n))}\ar[r]^-{p_{g^*(n)}}& g^*(N) \ar[d]_{g^*(n)} \ar[r]^{p_n} & N \ar[d]^{n} \\ &X \ar[r]_{f}& Y \ar[r]_g & Z}\]
+
+	By construction $w$ defines a morphism $\id{X}\to f^*(g^*(n))$, thus by adjointness, this implies the existence of a unique $\hat{w}\colon m\to g^*(n)$ such that $f^*(\hat{w})\circ \eta_{\id{X}} =w$.
+Let $v$ be $p_n\circ \hat{w}$, then
+	\[\begin{split}
+		v\circ e &= p_n\circ \hat{w} \circ p_m\circ \eta_{\id{X}} \\&=p_n\circ p_{g^*(n)}\circ f^*(\hat{w})\circ \eta_{\id{X}}\\&=p_n\circ p_{g^*(n)}\circ w \\&=h
+	\end{split}\qquad  \begin{split}
+		n\circ v &=n\circ p_n\circ \hat{w}\\&=g\circ g^*(n)\circ \hat{w}\\&=g\circ m\\&
+	\end{split}\]
+
+	To see that such $v$ is unique, let $v'$ be another arrow $M\to N$ such that
+	\[v'\circ e=h \qquad n\circ v'=g\circ m\]
+	The second of these equations entail the existence of the dotted $q\colon M\to g^*(N)$.
+	\[\xymatrix{M \ar@{.>}[dr]^{q}\ar@/^.3cm/[drr]^{v'} \ar@/_.3cm/[ddr]_{m}\\ &g^*(N) \ar[d]^{g^*(n)}\ar[r]^{p_n}& N\ar[d]^{n}\\ &Y\ar[r]_{g} & Z}\]
+	Notice that, in particular, $q$ is a morphism $m\to g^*(n)$ in $\mathcal{M}/Y$. Now, we can also consider the following diagram, which entails that $f^*(q)\circ \eta_{\id{X}}=w$.
+	\[\xymatrix@C=30pt{f^*(M) \ar@/_1.2cm/[ddd]_{f^*(m)}\ar[dd]_{f^*(q)}\ar[rr]^{p_m}&&M \ar[dd]_{q}\ar@/^.9cm/[ddd]_(.4){m}|(.67)\hole \ar@/^.6cm/[ddr]^{v'}\\&X\ar@/^.8cm/[ddl]|(.33)\hole_(.2){\id{X}} \ar[drr]_(.3){h}|\hole|(.74)\hole\ar[ul]^{\eta_{\id{X}}} \ar[ur]_{e}\\ f^*(g^*(N)) \ar[d]^{f^*(g^*(n))}\ar[rr]_(.67){p_{g^*(n)}}&& g^*(N) \ar[d]_{g^*(n)} \ar[r]_(.65){p_n} & N \ar[d]^{n} \\ X \ar[rr]_{f}&& Y \ar[r]_g & Z}\]
+	Thus $q$ must coincide with $\hat{w}$ and therefore $v'=v$.
+
+	\smallskip \noindent $(1\Rightarrow 3)$ This also follows from \Cref{prop:part}.
+
+	\smallskip \noindent $(3\Rightarrow 1)$ Let $R_f\colon \mathcal{M}/Y\to \mathcal{M}/Y$ be the right adjoint to $f_*$.
+Given $n\colon N\to Y$ in $\mathcal{M}$, we can build the rectangle below, where $f(R_f(n))$ and $e$ is a (chosen) right $\mathcal{M}$-factorization of $f\circ R_f(n)$ and $\epsilon\colon f_*\circ R_f\to \id{\mathcal{M}/Y}$ is the counit of the adjunction $f_* \dashv f^*$.
+	\[\xymatrix{R_f(N) \ar[d]_{R_f(n)} \ar[r]^-{e}& f_*(R_f(N))  \ar[r]^-{\epsilon_n} \ar[dr]_{f_*(R_f(n)) \hspace{3pt}}& N \ar[d]^{n}\\
+		X \ar[rr]_{f}&& Y}\]
+
+	We have to show that such a rectangle is a pullback.
+To do so, let $h\colon Z\to N$ and $g\colon Z\to X$ be arrows such that $n\circ h=f\circ g$ and consider the right $\mathcal{M}$-factorization of $g$ given by arrows $i\colon Z\to K$ and $k\colon K\to X$, with $k\in \mathcal{M}$.
+Thus there exists the dotted $w\colon K\to N$ in the diagram below.
+	\[\xymatrix{Z \ar[r]_{i}\ar@/^.4cm/[rr]^{g}\ar[d]_{h}& K \ar@{.>}[dl]^{w} \ar[r]_k & X \ar[d]^{f}\\
+		N \ar[rr]_{n}&& Y}\]
+
+	In turn, we can factor $f\circ k$ to get the following rectangle and, henceforth, the existence of the dotted $u\colon f_*(K)\to N$.
+	\[\xymatrix{K \ar[r]_-{j}\ar@/^.4cm/[rr]^-{f\circ k}\ar[d]_{w}& f_*(K) \ar@{.>}[dl]^{u} \ar[r]_{f_*(k)} & Y \ar[d]^{\id{Y}}\\
+		N \ar[rr]_{n}&& Y}\]
+
+	By construction $u$ is a morphism $f_*(k)\to n$, we can thus consider the unique morphism $\hat{u}\colon k\to R_f(n)$ such that
+	\[\epsilon_n\circ f_*(\hat{u})=u\]
+
+	Summing up we have constructed the diagram that follows.
+	\[\xymatrix{Z \ar@/^.4cm/[drrrr]^{h}\ar[dr]^{i} \ar@/_1cm/[ddrr]_{g}\\& K \ar[r]^-{\hat{u}} \ar@/_.2cm/[dr]_{k}& R_f(N) \ar[d]_{R_f(n)} \ar[r]^-{e}& f_*(R_f(N))  \ar[r]_-{\epsilon_n} \ar[dr]_{f_*(R_f(n)) \hspace{3pt}}& N \ar[d]^{n}\\ &&
+		X \ar[rr]_{f}&& Y}\]
+
+	To conclude it is now enough to show that $\hat{u}\circ i$ is the unique morphism $Z\to R_f(N)$ such that 
+	\[\epsilon_n\circ e \circ \hat{u}\circ i=h\qquad R_f(n)\circ \hat{u}\circ i=g\]
+
+	Let, therefore, $t$ be an arrow $Z\to R_f(N)$ such that
+	\[\epsilon_n\circ e \circ t=h\qquad R_f(n)\circ t=g\]
+	The second equation provides us with the commutative rectangle below, guaranteeing the existence of the dotted $s\colon k\to R_f(n)$.
+	\[\xymatrix{Z \ar[r]_-{i}\ar@/^.4cm/[rr]^-{g}\ar[d]_{t}& K \ar@{.>}[dl]^{s} \ar[r]_{k} & X \ar[d]^{\id{X}}\\
+		R_f(N) \ar[rr]_{R_f(n)}&& X}\]
+
+	If we compute we get:
+	\[\begin{split}
+		n\circ \epsilon_n\circ e\circ s&=f_*(R_f(n))\circ e\circ s\\&=f\circ R_f(n)\circ s\\&=f\circ k
+	\end{split} \qquad \begin{split}
+		\epsilon_n\circ e\circ s\circ i&=\epsilon_n\circ e\circ t\\&=h\\&
+	\end{split} \]
+
+	On the other hand, the definition of $f_*$ gives us the inner rectangle of the diagram below.
+	\[\xymatrix@C=30pt{K \ar@/_1.2cm/[ddd]_{w}\ar[dr]_(.35){k}|(.55)\hole\ar[r]^-{j} \ar[d]_{s}& f_*(K)  \ar@/_.3cm/[ddl]^(.75){f_*(s)}\ar[r]^-{f_*(k)}& Y \ar[dd]^{\id{Y}}\\R_f(N) \ar[d]_{e} \ar[r]|(.34)\hole_(.6){R_f(n)} & X  \ar[dr]^{f}\\f_*(R_f(N)) \ar[d]_{\epsilon_n} \ar[rr]_{f_*(R_f(n))}&& Y\\N\ar@/_.8cm/[urr]_{n}}\]
+
+	From the commutativity of the whole diagram it follows that $\epsilon_n\circ f_*(s)=u$ and thus $s=\hat{u}$, entailing the thesis.
+\end{proof}
+
+\subsection{Factorization systems}
+
+We move now to the notion of \emph{factorization system} \cite{adamek2009abstract,bousfield1977constructions,kelly1991note,rosicky2007factorization,tholen1983factorizations}.
+Let us start by recalling its definition.
+
+\begin{definition}\label{def:fs}
+	Let $\X$ be a category and $\mathcal{E}$, $\mathcal{M}$ two classes of arrows, we will say that $(\mathcal{E},\mathcal{M})$ is a \emph{factorization system} if:
+	\begin{enumerate}
+		\item $\mathcal{E}$ and $\mathcal{M}$ are closed under composition with isomorphisms: if $f\colon X\to Y$ belongs to $\mathcal{E}$ (to $\mathcal{M}$) and $h\colon Y\to Z$ is an isomorphism then $h\circ f$ belongs to $\mathcal{E}$ (to $\mathcal{M}$);
+		\item  every arrow $f\colon X\to Y$ of $\X$ admits a \emph{$(\mathcal{E}, \mathcal{M})$-factorization}, i.e.~there are arrows $e\in \mathcal{E}$ and $m\in \mathcal{M}$ with the property that $f=m\circ e$;
+		\item every $e\in \mathcal{E}$ has the \emph{left lifting property} with respect to every $m\in \mathcal{M}$: for every commutative square as the one below, with $e\in \mathcal{E}$ and $m\in \mathcal{M}$ there exists a unique dotted $k\colon Y\rightarrow Z$ which fits in it.
+		\[\xymatrix{X \ar[r]^g \ar[d]_{e}& Z \ar[d]^{m}\\ Y \ar[r]_{f} \ar@{.>}[ur]^{k}& V}\] 
+	\end{enumerate}
+
+	A factorization system is \emph{proper} if every $e\in \mathcal{E}$ is epi and every $m\in \mathcal{M}$ is mono; it is \emph{stable} if $\mathcal{E}$ is stable under pullbacks.
+\end{definition}
+
+\begin{remark}\label{rem:dual}It is immediate to notice that, given a factorization system $(\mathcal{E}, \mathcal{M})$ on $\X$, then $(\mathcal{M}, \mathcal{E})$ is a factorization system on $\X^{op}$.
+Such factorization system on $\X^{op}$ is proper if and only if $(\mathcal{E}, \mathcal{M})$ is so, it is stable if and only if $\mathcal{M}$ is stable under pushouts in $\X$.
+\end{remark}
+
+We can now begin to prove some properties of factorization systems.
+
+\begin{proposition}\label{prop:el}
+	Let $(\mathcal{E}, \mathcal{M})$ be a factorization system on a category $\X$, then the following hold true:
+	\begin{enumerate}
+		\item $\mathcal{E}$ is the class of all arrows with the left lifting properties with respect to every $m\in \mathcal{M}$;
+		\item every isomorphism belongs to $\mathcal{E}$;
+		\item $\mathcal{E}$ is closed under composition.
+	\end{enumerate}
+\end{proposition}
+\begin{proof}
+	\begin{enumerate}
+		\item By definition, every arrow in $\mathcal{E}$ has the left lifting property with respect to every arrow in $\mathcal{M}$.
+To prove the converse, let $f\colon X\to Y$ be an arrow with such a property with respect to every element of $\mathcal{M}$.
+We can factorize it as $m\circ e$ with $m\colon M\to Y$ in $\mathcal{M}$ and $e\colon X\to M$ in $\mathcal{E}$.
+Thus, in the diagram below, the outer square commutes and so we get the dotted $k\colon Y\to M$.
+		\[\xymatrix{X\ar[d]_f\ar[r]^e & M\ar[d]^{m}\\Y\ar[r]_{\id{Y}} \ar@{.>}[ur]^{k} & Y}\]
+
+		On the other hand, $k\circ m$ fits in the diagram below, showing that $k$ and $m$ are mutually inverses. Thus $f=m\circ e$ belongs to $\mathcal{E}$.
+		\[\xymatrix{X\ar[rr]^{e} \ar[dd]_{e} \ar[dr]^{f}&& M\ar[dd]^{m} \ar@{<-}[dl]^{m}\\& Y\ar@{<-}[dl]^{k}\\M \ar[rr]_{m}&&Y}\]
+		\item By the previous point, it is enough to show that every isomorphism has the left lifting property. But this follows at once: indeed given a square
+		\[\xymatrix{X\ar[d]_e\ar[r]^f & M\ar[d]^{m}\\E\ar[r]_{g} \ar@{.>}[ur]^{k} & Y}\]
+		the unique $k\colon E\to M$ filling the diagonal in the diagram above is $f\circ e^{-1}$.
+
+		\item Let $e\colon X\to Y$ and $e'\colon Y\to Z$ be two arrows in $\mathcal{E}$. Suppose that the outer rectangle below is given, with $m\in \mathcal{M}$.
+		\[\xymatrix{X  \ar[r]^f \ar[d]_{e}& M \ar[dd]^{m}\\Y \ar@{.>}[ur]^{k} \ar[d]_{e'}\\Z \ar@{.>}[uur]_{h}\ar[r]_{g}& W}\]
+
+		Then the first dotted arrow $k\colon Y\to M$ exists since $e$ has the left lifting property with respecto to $m$.
+Its existence, in turn yields the existence of the other dotted arrow $h\colon Z\to M$.
+
+		Let $h'\colon Z\to M$ be another arrow such that 
+		\[m\circ h'=g \qquad h'\circ e'\circ e=f\]
+		Then $h'\circ e'$ must coincide with $k$ by the uniqueness clause of the left lifting property and thus, by the same clause, $h'$ must be equal to $h$.
+By the first point $e'\circ e$ belongs to $\mathcal{E}$.
+\qedhere
+	\end{enumerate}
+\end{proof}
+
+Taking into account \Cref{rem:dual}, the previous proposition gives us the following results.
+
+\begin{corollary}\label{cor:m}Let $(\mathcal{E}, \mathcal{M})$ be a factorization system on a category $\X$, then the following hold true:
+	\begin{enumerate}
+		\item every isomorphism belongs to $\mathcal{M}$;
+		\item $\mathcal{M}$ is closed under composition.
+	\end{enumerate}
+\end{corollary}
+
+In the presence of a factorization system, we also have right $\mathcal{M}$-factorizations.
+
+\begin{proposition}\label{prop:rfact}
+	Let $(\mathcal{E}, \mathcal{M})$ be a factorization system on a category $\X$.
+Let $f\colon X\to Y$ be a morphism with $e\colon X\to M$ and $m\colon M\to Y$ as an $(\mathcal{E}, \mathcal{M})$-factorization of $f$, then the pair $(e, m)$ is also a right $\mathcal{M}$-factorization of $f$.
+\end{proposition}
+\begin{proof}
+	Suppose that the solid part of the rectangle below is given, with $n\colon N\to Z$ in $\mathcal{M}$. 
+	\[\xymatrix{X \ar[d]_{h} \ar@/^.4cm/[rr]^{f} \ar[r]_{e}& M \ar@{.>}[dl]^{k} \ar[r]_{m} & Y \ar[d]^{g}\\N \ar[rr]_{n}&& Z}\]
+	Bu the existence of the dotted $k\colon M\to N$ is guaranteed by the left lifting property of $e$ with respect to $n$.
+\end{proof}
+
+The previous proposition, together with \Cref{rem:uniq} gives us the following.
+
+\begin{corollary}\label{prop:iso}
+	Let $(\mathcal{E}, \mathcal{M})$ be a factorization system on a category $\X$.
+If $e\colon Y\to E$, $e'\colon Y\to E'$ and $m\colon Y\to X$, $m'\colon Y'\to X $ are arrows, respectively, in $\mathcal{E}$ and $\mathcal{M}$ such that
+	$e'\circ m'=e\circ m$,  then  there exist a unique isomorphism $\phi\colon E \rightarrow E'$ such that the diagram below commutes.
+	\[\xymatrix@C=40pt{Y \ar[r]^{e'} \ar[d]_{e}& E' \ar[d]^{m'}\\ E \ar[r]_{m} \ar@{.>}[ur]^{\phi}& X}\]
+\end{corollary}
+
+The previous corollary, in turn, allows us to deduce other useful properties of factorization systems.
+
+\begin{proposition}\label{cor:iso} Given a factorization system $(\mathcal{E}, \mathcal{M})$ on a category $\X$, the following hold:
+	\begin{enumerate}
+		\item an arrow $f\colon X\to Y$ with $(\mathcal{E}, \mathcal{M})$-decomposition given by $e$ in $\mathcal{E}$ and $m\in \mathcal{M}$ is in $\mathcal{M}$ if and only if $e$ is an isomorphism;
+		\item $f\in \mathcal{E}$ and $f\in \mathcal{M}$ if and only if $f$ is an isomorphism;
+		\item $\mathcal{M}$ is stable under pullback.
+		\item  if $(\mathcal{E}, \mathcal{M})$ is proper, then $g\circ f$ is in $\mathcal{M}$ implies $f\in \mathcal{M}$.
+	\end{enumerate}
+\end{proposition}
+\begin{proof}
+	\begin{enumerate}
+		\item  ($\Rightarrow$) By hypothesis $f=f\circ \id{X}$ is a factorization with $\id{X}\in \mathcal{E}$ and $f\in \mathcal{M}$, thus the thesis follows from \Cref{prop:iso}.
+
+		\smallskip \noindent
+		($\Leftarrow$) Let $f=m\circ e$ be an $(\mathcal{E}, \mathcal{M})$-factorization.
+The thesis  follows from \Cref{cor:m} since, if $e$ is an isomorphism, then $f$ is the composition of two arrows in $\mathcal{M}$.
+
+		\item This follows from the previous point, \Cref{cor:m} and \Cref{prop:el}.
+
+		\item 	Suppose that the square below is a pullback, with $m\in \mathcal{M}$
+		\[\xymatrix{X\ar[r]^{g} \ar[d]_{n} & M \ar[d]^{m} \\ Y \ar[r]_{f}  & Z}\] 
+		We can factor  $n$ as $t\circ e$ for $e\colon X\to M$ in  $\mathcal{E}$ and $t\colon T\to Y$ in $ \mathcal{M}$.  By the left lifting property we get the dotted $l\colon T\to M$ in the diagram below.
+		\[\xymatrix{X \ar[d]_{e}\ar[rr]^{g} & &V\ar[d]^{m}\\  T  \ar@{.>}[urr]^{l} \ar[r]_{t}&Y\ar[r]_{f} & Z}\]
+		Therefore we get another diagram
+		\[\xymatrix{ T \ar@/^.5cm/[drr]^{l}\ar@{.>}[dr]^{k} \ar@/_.5cm/[ddr]_{t}\\ & X \ar[d]_{n}\ar[r]^{g}& M  \ar[d]^{m} \\ &Y \ar[r]_{f} & Z }\]
+		and thus we can deduce the existence of the dotted $k\colon E\to V$. On the one hand, computing we get
+		\[\begin{split}
+			n\circ 	k\circ e&=t  \circ  e\\ &=n
+		\end{split}\qquad \begin{split}
+			g\circ k\circ e &=l\circ e\\ &=g \end{split}\]
+		and so $k\circ e= \id{X}$.  On the other hand 
+		\[\begin{split}
+			t\circ k \circ t &= \id{Y} \circ t \\&= t
+		\end{split} \qquad 
+		\begin{split}
+			k \circ t \circ e &= k\circ n \\&= e
+		\end{split}
+		\]	
+		so the following diagram commutes.
+		\[
+		\xymatrix@C=50pt{X \ar[d]_{e}\ar[r]^{e}& T \ar[d]^{t} \\
+			T\ar[ur]^{e\circ k}\ar[r]_{t} & Y}\]
+		Hence, by the uniqueness clause of the left lifting property, $e\circ k=\id{E}$. Therefore $e$ is an isomorphism and the thesis follows from  point $1$.
+
+		\item 
+		Factor $f$ and $g$ as $m_f\circ e_f$ and $m_g\circ e_g$, respectively. Let also $h$ be $e_g\circ m_f$ and factor it as $m_h\circ e_h$ so that we get 
+		\[\xymatrix@C=45pt{& C \ar[dr]^{m_h}&\\
+			A\ar[ur]^{e_h} \ar[rr]^{h}  \ar[dr]^{m_f}& &B \ar[d]^{m_g}\\
+			X \ar[u]^{e_f} \ar[r]_f& Y \ar[r]_g \ar[ur]^{e_g} & Z}\]
+		B \Cref{prop:el,cor:m}, $\mathcal{E}$ and $\mathcal{M}$ are closed under composition, therefore $e_h\circ e_f\in \mathcal{E}$ and $m_g \circ m_h\in \mathcal{M}$.
+Thus these two arrows gives a $(\mathcal{E}, \mathcal{M})$-factorization of $g\circ f$.
+On the other hand $g\circ f\in \mathcal{M}$, thus point $1$ above  implies that  $e_h\circ e_f$ is an isomorphism, so $e_f$ is a epic split mono which is also an epimorphism.
+\qedhere
+	\end{enumerate}
+\end{proof}
+
+With the help of \Cref{rem:dual} we can easy dualize the previous proposition.
+\begin{corollary}\label{cor:iso2}
+	Given a factorization system $(\mathcal{E}, \mathcal{M})$ on a category $\X$, the following hold:
+	\begin{enumerate}
+		\item an arrow $f\colon X\to Y$ is in $\mathcal{E}$ if and only if $m_f$ is an isomorphism;
+		\item $\mathcal{E}$ is stable under pushouts;
+		\item  if $(\mathcal{E}, \mathcal{M})$ is proper, then $g\circ f$ is in $\mathcal{E}$ implies $g\in \mathcal{E}$.
+	\end{enumerate}
+\end{corollary}
+
+We conclude this section with a result linking closely factorization systems with the existence of right $\mathcal{M}$-factorizations.
+
+\begin{lemma}\label{lem:fact}Let $\mathcal{M}$ be a class of arrows in a category $\X$ closed under composition with isomorphisms, then the following are equivalent:
+	\begin{enumerate}
+		\item every arrow $f\colon X\to Y$ has a right $\mathcal{M}$-factorization and $\mathcal{M}$ is closed under composition;
+		\item there exists a class $\mathcal{E}$ such that $(\mathcal{E}, \mathcal{M})$ is a factorization system on $\X$.
+	\end{enumerate}
+\end{lemma}
+\begin{proof} $(1\Rightarrow 2)$ Let $\mathcal{E}$ be the class of arrows which have the left lifting property with respect to every element of $\mathcal{M}$.
+Let us show that the three properties of \Cref{def:fs} hold.
+
+	\begin{enumerate}
+		\item $\mathcal{M}$ is closed under composition with isomorphisms by hypothesis.
+On the other hand, if $e\colon X\to Y$ is in $\mathcal{E}$ and $h\colon Y \to Z$ is an isomorphism, then $h\circ e$ still belongs to $\mathcal{E}$.
+To see this, consider the square below, with $m\in \mathcal{M}$.
+		\[\xymatrix{X\ar[r]^{f} \ar[d]_{e}& M\ar[dd]^{m}  \\Y \ar@{.>}[ur]_{k}\ar[d]_h \\Z \ar[r]_{g}& V}\]
+
+		The dotted $k\colon Y\to M$ exists, and it is unique, because $e\in \mathcal{E}$. The thesis now follows taking $k\circ h^{-1}$ as the lifting of $g$.
+
+		\item Given $f\colon X\to Y$, let $e\colon X\to M$ and $m\colon M\to Y$ be a right $\mathcal{M}$-factorization of it.
+We have to show that $e$ belongs to $\mathcal{E}$.
+We can further factor $e$ as $n\circ d$, with $n\in \mathcal{M}$.
+Then we can build the rectangle below.
+		\[\xymatrix{X  \ar[dr]_(.3){e}\ar[d]_{d} \ar@/^.4cm/[rr]^{f}\ar[r]_{e} & M \ar@{.>}[dl]^(.3){k} \ar[r]_{m} & Y \ar[d]^{\id{Y}}\\
+			D \ar[r]_{n} & M \ar[r]_{m}& Y}\]
+
+		By hypothesis $m\circ n$ is in $\mathcal{M}$, so we can deduce the existence of the dotted $k\colon M\to D$.   Now, from the diagram below, we can deduce that $n\circ k=\id{M}$.
+		\[\xymatrix{X \ar[rr]^{e} \ar[dr]^{d}\ar[dd]_{e}& &M \ar[r]^{m}\ar[dl]^{k}& Y \ar[dd]^{\id{Y}}\\ & D\ar[dl]^{n}\\M\ar[rrr]_{m}&&&Y}\]
+
+		On the other hand, the previous result yields also the commutativity of the following diagram, entailing $k\circ n=\id{D}$.
+		\[\xymatrix{X \ar[rr]^{d} \ar[dr]^{e}\ar[dd]_{d}& &D \ar[r]^{n}\ar[dl]^{n}& M \ar[dd]^{\id{M}}\\ & M\ar[dl]^{k} \ar[drr]^{\id{M}}\\D\ar[rrr]_{n}&&&M}\]
+
+		Now, suppose that the outer square in the diagram below is given, with $v\in \mathcal{M}$.
+		\[\xymatrix{X \ar[dd]_{e} \ar[dr]_{d}\ar[rr]^{t}&& V \ar[dd]^{v}\\ & D \ar[dl]^{n} \ar@{.>}[ur]_{h}\\M \ar[rr]_{s}&& Z}\]
+
+		Then the dotted $h\colon N\to V$ exists and it is unique since $n$ is a right $\mathcal{M}$-image of  $e$. Thus $h\circ k$ is the unique lifting for $s$ along $v$, proving that $e\in \mathcal{E}$.
+		\item This holds by construction.
+	\end{enumerate}
+
+	\smallskip \noindent $(2\Rightarrow 1)$  This follows from the second point of \Cref{cor:m} and from \Cref{prop:rfact}. \qedhere  
+\end{proof}
+
+Putting together \Cref{lem:fact,lem:rfact} we get the following result.
+
+\begin{corollary}\label{cor:fact}
+	Let $\mathcal{M}$ be a class of arrows in a category $\X$ closed under composition stable under pullbacks and containing the identities.
+If $\X$ has $\mathcal{M}$-pullbacks and for every arrow $f\colon X\to Y$ the pullback functor $f^*$ has a left adjoint, then there exists a, unique, class $\mathcal{E}$ such that $(\mathcal{E}, \mathcal{M})$ is a factorization system on $\X$.
+\end{corollary}
+
+\subsection{$\mathcal{M}$-subobjects and factorization systems}
+
+In this section we focus on studying the category $\mathcal{M}/X$ when $\mathcal{M}$ is a class of monomorphism.
+
+\begin{remark}
+	If  $\mathcal{M}$ is a class of monos in a category $\X$, then $\mathcal{M}/X(f,g)$ has cardinality at most one for every two arrows $f$ and $g$ with codomain $X$.
+Thus it is a preordered class, in which $f\leq g$ if and only if  $\mathcal{M}/X(f,g)$ is non-empty.
+Now, it is immediate to notice that $f\leq g$ and $g\leq f$, then there exists a (unique) isomorphism fitting in the triangle below.
+	\[\xymatrix{A\ar@{.>}[rr]^{\phi} \ar[dr]_{f} && B \ar[dl]^{g}\\ & X}\]
+	In such a case we will write $f\equiv g$. It is immediate to see that in this way we get an equivalence relation on the class of objects of $\mathcal{M}/X$.
+\end{remark}
+
+Given the previous remark, we are led to the following definition.
+
+\begin{definition} Let $\mathcal{M}$ be a class of monos in a category $\X$.
+For every object $X$ a \emph{$\mathcal{M}$-subobject} is an equivalence class $[f]$ of an object $f$ in $\mathcal{M}/X$ with respect to $\equiv$.
+Given two \emph{$\mathcal{M}$-subobjects} $[f]$ and $[g]$, represented by $f$ and $g$, respectively, we will define $[f]\leq [g]$ if and only if $f\leq g$.
+It is immediate to see that this defines a partially ordered class $(\sub{M}{X}{X}, \leq)$.
+
+	When $\mathcal{M}$ coincides with the class of all monos we will suppress the prefix, so that a \emph{subobject} is just an equivalence class of a mono and $(\msub{X}{X}, \leq)$ will denote the ordered class of such subobjects of $X$.
+\end{definition}
+
+\begin{remark}\label{rem:pbo} Let $f\colon X\to Y$ be an arrows admitting a pullback along arrows in $\mathcal{M}/Y$ and suppose that $\mathcal{M}$ is stable under pullbacks.
+The categories associated to $(\sub{M}{X}{X}, \leq)$ and $(\sub{M}{Y}{Y}, \leq)$ are equivalent to $\mathcal{M}/X$ and $\mathcal{M}/Y$, respectively, thus we get a monotone function $f^{-1}\colon \sub{M}{X}{Y}\to \sub{M}{X}{X}$ sending $[m]$ to $[f^*(m)]$.
+
+	Similarly, if $f\circ m$ has a right $\mathcal{M}$-factorization for every $m\in \mathcal{M}$, then the functor $f_*$ induces a monotone function $\exists_f\colon \sub{M}{X}{X}\to \sub{M}{X}{Y}$.
+
+	Notice that, whenever $\mathcal{M}$ is stable unr pullbacks, $\X$ has $\mathcal{M}$-pullbacks and  right $\mathcal{M}$-factorizations, then $\exists_f \dashv f^{-1}$ by \Cref{lem:rfact}.
+\end{remark}
+
+\Cref{cor:finlim} gives us immediately the following.
+
+\begin{proposition}\label{prop:finlim}
+	Let $f\colon X\to Y$ be an arrow in a category $\X$ and $\mathcal{M}$ a class of arrows stable under pullbacks and such that $f$ has a pullback along any arrow in $\mathcal{M}$.
+Then $f^{-1}$ preserves binary infima.
+If, moreover, $\id{Y}$ belongs to $\mathcal{M}$ then $f^{-1}$ preserves finite infima.
+\end{proposition}
+
+Now, let us recall the following lemma, which is the application of the Adjoint Functor Theorem to the partial ordered case.
+
+\begin{lemma}\label{lem:adj}
+	Let $f\colon (P,\leq)\to (Q, \leq)$ be a monotone function. If $f$ preserves all infima then it has a left adjoint.
+\end{lemma}
+\begin{proof}
+	For every $q\in Q$ define
+	\[P_q:=\{p\in P \mid q \leq f(p)\}\]
+	Clearly if $q'\leq q$ then $P_{q}\subseteq P_{q'}$.
+Let us define $g(q)$ as the infimum of $P_q$, the previous observation entails that in this way we get a monotone function $g\colon (Q, \leq)\to (P, \leq)$.
+	We can also notice that, since $f$ preserves infima:
+	\begin{align*}
+		f(g(q))&=f(\inf(P_q))\\&=\inf(f(P_q))
+	\end{align*}
+	Now, by definition, $q$ is less or equal than every element in $f(P_q)$, thus $q\leq f(g(q))$, so that $g(q)$ is actually the infimum of $P_q$.
+
+	So equpped, we can now prove that $g$ is the right adjoint to $f$.
+	\begin{itemize}
+		\item Suppose that $g(q)\leq p$.  Then $f(g(q))\leq p$, but we already know that $q\leq f(g(q))$, therefore we can conclude that $q\leq f(p)$.
+		\item  Suppose that $q\leq f(p)$. Thus $p$ belongs to $P_q$ and so $g(q)\leq p$. \qedhere 
+	\end{itemize}
+\end{proof}
+
+The previous result, together with \Cref{cor:fact} and \Cref{prop:finlim}, allows us to deduce the following result, which has been used in \cite{baldan2011lattice,braatz2010finitary} to show that certain $\mathcal{M}$-adhesive categories have a factorization system.
+
+\begin{corollary}\label{cor:fin}
+	Let $\mathcal{M}$ be a class of monomorphism in a category $\X$ stable under pullbacks, containing all identities and closed under composition.
+If $\sub{M}{X}{X}$ is finite for every object $X$ of $\X$, then there exists a factorization system $(\mathcal{E},\mathcal{M})$ on $\X$
+\end{corollary}
+
+\section{Coreflective subcategories}
+
+In order to identify a class of well-behaved DPO-rewriting system we need to recall some other general notion of category theory.
+
+\begin{definition}
+	Let $\X$ be a category, a full subcategory $\Y$ of $\X$ is \emph{coreflective} if the inclusion functor $I_\Y\colon \Y\to \X$ has a right adjoint $R_\Y$, called \emph{coreflector}.
+A morphism between two coreflective subcategories $\Y$ and $\Z$ is a functor $F\colon \Y \to \Z$ such that $I_\Z \circ F=I_\Y$ and $F\circ R_\Y$ is isomorphic to $R_\Z$.
+
+	We will denote by $\cori(\X)$ the category obtained in this way.
+\end{definition}
+
+\begin{remark}
+	Notice that, since adjoints are unique up to isomorphism, being a morphism $\Y\to \Z$ of $\cori(\X)$ does not depends on the choice of coreflectors for $\Y$ and $\Z$.
+\end{remark}
+
+\begin{remark}\label{rem:ff}
+	Let $F\colon \Y \to \Z$ be a morphism in $\cori(\X)$.
+Since $I_\Z\circ F=I_\Y$, then $\Y$ must be a full subcategory of $\Z$ and $F$ must coincide with its inclusion.
+In particular, $F$ is full and faithful and $\cori(\X)$ is a ordered class.
+\end{remark}
+
+\begin{example}\label{ex:1}
+	\todo{connessi}
+\end{example}
+
+\begin{example}\label{ex:2}
+	\todo{grafi con equivalenza}
+\end{example}
+\begin{example}
+	\todo{Ce ne sono altri? sarebbe bello usare i calcoli ma credo rientrino nel primo}
+\end{example}
+
+Let us recall the following well known fact.
+
+\begin{proposition}\label{prop:counit}
+	Let $L\colon \X\to \Y$ and $R\colon \Y \to \X$ be a pair of functors such that $L\dashv R$. Then the following are equivalent:
+	\begin{enumerate}
+		\item $L$ is full and faithful;
+		\item the unit $\eta \colon \id{\X}\to R\circ L$ is an isomorphism.
+	\end{enumerate} 
+\end{proposition}
+\begin{proof}
+	We can start noticing that, for every pair of objects $X$ and $Y$ in $\X$, we have two functions:
+	\[F_{X, Y}\colon \X(X, Y)\to \Y(L(X), L(Y)) \quad 	 \Phi_{X, Y}\colon \Y(L(X), L(Y))\to \X(X, R(L(Y)))\]
+	where $F_L$ sends $f\colon X\to Y$ to $L(f)$ and $\Phi_{X, Y}$ is the bijection $\Y(L(X), L(Y))\to \X(X, R(L(Y)))$ given by $L\dashv R$.
+Now, notice that, for every $f\colon X\to Y$ the diagram below commutes.
+	\[\xymatrix@C=35pt{X \ar[r]^{f} \ar[d]_{\eta_X}& Y \ar[d]^{\eta_Y}\\R(L(X)) \ar[r]_-{R(L(f))} &R(L(Y)) }\]
+
+	This, in turn, entail that the composit $\Psi_{X,Y} \circ F_{X, Y}$ coincides with $\eta_Y\circ (-)$.
+
+	\smallskip \noindent 
+	$(1\Rightarrow 2)$ Let $X$ and $Y$ be two objects of $\X$, by hypothesis $\eta_Y$ is an isomorphism and so $\eta_Y\circ (-)$ is a bijection.
+But then $F_{X, Y}$ must be a bijection too by what we have observed above.
+
+	\smallskip \noindent 
+	$(2\Rightarrow 1)$ Let $X$ be an object of $\X$, if $L$ is full and faithful then $\eta_Y\circ (-)$ is the composition of the two bijections $\Psi_{Y,Y}\circ F_{Y,Y}$.
+By the Yoneda Lemma this entails that $\eta_Y$ is an isomorphism.
+\end{proof}
+
+\begin{corollary}\label{cor:cou}
+Let $L\colon \X\to \Y$ and $R\colon \Y \to \X$ be a pair of functors such that $L\dashv R$ and suppose that $L$ is full and faithful.
+Let $\epsilon\colon L\circ R\to \id{\Y}$ be the unit of the adjunction, then the following are true for every object $X$:
+\begin{enumerate}
+	\item the arrow $R(\epsilon_X)$ is an isomorphism;
+	\item $L(R(\epsilon_X))$ is equal to $\epsilon_{L(R(X))}$.
+\end{enumerate}
+\end{corollary}
+\begin{proof}
+	\begin{enumerate}
+		\item Let $\eta\colon \id{X}\circ R\circ L$ be the unit of the adjunction.
+By the triangular identity we know that $R(\epsilon_X)\circ \eta_{R(X)}=\id{R(X)}$.
+The thesis now follows from \Cref{prop:counit}.
+		\item Using again the triangular identities and the previous point we have
+		\begin{align*}
+			\id{L(R(X))}&=\epsilon_{L(R(X))}\circ L(\eta_{R(X)})\\&= \epsilon_{L(R(X))}\circ L(R(\epsilon_X))^{-1}
+		\end{align*}
+		Which yields the theis. \qedhere 
+	\end{enumerate}
+\end{proof}
+
+\begin{corollary}\label{cor:counit}
+	Let $\Y$ be a coreflective subcategory of $\X$ and let $\epsilon \colon I_\Y\circ R_\Y \to  \id{\X}$ be the counit of $I_\Y\dashv R_\Y$. Given an object $X\in \X$, the following are equivalent:
+	\begin{enumerate}
+		\item $X$ is in the essential image of the inclusion $I_\Y$;
+		\item $\epsilon_X$ is an isomorphism.
+	\end{enumerate} 
+\end{corollary}
+\begin{proof}
+	$(1\Rightarrow 2)$ By hypothesis there is an object $Y$ of $\Y$ and an isomorphism $\phi\colon I_\Y(Y)\to X$. This, in turn, yields the commutative square below.
+	\[\xymatrix@C=40pt{I_\Y(Y) \ar[r]^-{\phi} \ar[d]_{I_\Y(\eta_Y)}&  X\\ I_\Y(R_\Y(I_\Y(Y)))  \ar[r]_-{I_\Y(R_\Y(\phi))}& I_\Y(R_\Y(X)) \ar[u]_{\epsilon_X}}\]
+
+	By hypotesis $\phi$ is an isomorphism and $\eta_Y$ is so by \Cref{prop:counit}, thus $I_\Y(\eta_Y)$ and 
+	$I_\Y(R_\Y(\phi))$ are isomorphisms too and the thesis follows.
+
+	\smallskip \noindent
+	$(2\Rightarrow 1)$ This is a tautology.
+\end{proof}
+
+Associated to a coreflective subcategory $\Y$ of $\X$ we have a class of arrows which enjoys some useful properties.
+
+\begin{definition}
+	Let $\Y$ be a coreflective subcategory of $\X$ with coreflector $R_\Y$, we define the class $\mathcal{R}_\Y$ as the class of all arrows in $\X$ whose image through $R_\Y$ is a mono in $\Y$.
+\end{definition}
+
+\begin{remark}
+	Let $I_\Y\colon \Y \to \X$ be the inclusion functor of a coreflective subcategory $\Y$.
+If $R_\Y$ and $R'_\Y$ are coreflectors, then we have a natural isomorphism $\phi\colon R_\Y\to R'_\Y$ and so, for every $f\colon X\to Y$ there is a square
+	\[\xymatrix{ \ar[d]_{\phi_X} R_\Y(X) \ar[r]^{R_\Y(f)}& R_\Y(Y) \ar[d]^{\phi_Y}\\R'_\Y(X) \ar[r]_{R_\Y(f)} & R'_\Y(Y)}\]
+
+	In particular, $R_\Y(f)$ is mono if and only if $R'_\Y(f)$ is so, thus the definition of $\mathcal{R}_\Y$ is independent from the choice of coreflector.
+\end{remark}
+
+\begin{proposition}\label{prop:varie}
+	Let $\Y$ be a coreflective subcategory of $\X$. Then the following hold true:
+	\begin{enumerate}
+		\item $\mathcal{R}_\Y$ contains all monos;
+		\item $\mathcal{R}_\Y$ is stable under pullbacks;
+		\item given $f\colon X\to Y$ and $g\colon Y\to Z$, if $g\circ f$ is in $\mathcal{R}_\Y$ then $f$ is in $\mathcal{R}_\Y$ too;
+		\item given $f\colon X\to Y$ in $\mathcal{R}_\Y$ and $g,h\colon I_\Y(Z)\rightrightarrows X$, if $f\circ g = f\circ h$, then $g=h$.
+	\end{enumerate}
+\end{proposition}
+\begin{proof}\begin{enumerate}
+		\item This follows at once from the fact that $R_\Y$, being a right adjoint, preserves monos.
+		\item Consider the following two diagrams, with $f\in \mathcal{R}_\Y$, in which the left one is a pullback. $R_\Y$ preserves limits, thus the right square is a pullback too.
+		\[\xymatrix@C=30pt{P \ar[r]^{p_1} \ar[d]_{p_2}& X \ar[d]^{f} & R_\Y(P) \ar[r]^{R_\Y(p_1)} \ar[d]_{R_\Y(p_2)} & R_\Y(X) \ar[d]^{R_\Y(f)}\\Z \ar[r]_{g}& Y & R_\Y(Z) \ar[r]_{R_\Y(g)} & R_\Y(Y)}\]
+		By definition, $R_\Y(f)$ is a mono in $\Y$, but this implies that $R_\Y(g)$ is a mono too, proving $g\in \mathcal{R}_\Y$.
+		\item We know that $R_\Y(g\circ f)$ is mono, thus $R_\Y(f)$ is mono too.
+		\item 	Since $f\circ g=f\circ h$ and $f$ is in $\mathcal{R}_\Y$ we can conclude that $R_\Y(g)=R_\Y(h)$. Thus we have:
+		\begin{align*}
+			g\circ \epsilon_{I_\Y(Z)}&=\epsilon_X\circ I_\Y(R_\Y(g))\\&=\epsilon_X\circ I_\Y(R_\Y(h))\\&=h\circ \epsilon_{I_\Y(Z)}
+		\end{align*}
+		By \Cref{cor:counit},  $\epsilon_{I_\Y(Z)}$ is an isomorphism and so $g=h$. \qedhere
+	\end{enumerate}
+\end{proof}
+
+In general, the class $\mathcal{R}_{\Y}$ is not stable under pushout. Nonetheless such property is desirable. We are thus lead to the following definition.
+
+\begin{definition}
+	A coreflective subcategory is \emph{good} if  $\mathcal{R}_\Y$ is stable under pushout. $\gori(\X)$ will denote the subcategory of $\cori(\X)$ given by good coreflective subcategories. 
+\end{definition}
+
+\iffalse 
+\begin{remark}\label{rem:good}
+	Let $\Y$ be a full subcategory of $\X$ with coreflector $R_\Y$.
+Let also $f\colon X\to Y$ be in $\mathcal{R}_\Y$ and consider the following two diagrams, where the left one is a pushout.
+Then $\Y$ is a good subcategory if and only if $R_{\Y}()$
+\end{remark}
+\fi
+
+We end this section extending the construction of $\mathcal{R}_\Y$ to a functor on $\cori(\X)$.
+
+\begin{proposition}\label{prop:funct}
+	Let $F\colon \Y \to \Z$ be a morphism of $\cori(\X)$, then $\mathcal{R}_\Z \subseteq \mathcal{R}_{\Y}$.
+\end{proposition}
+\begin{proof}
+	Let $f$ be an arrow in $\mathcal{R}_\Z$.
+Since $F$ is an arrow in $\cori(\X)$ we know that there exists a natural isomorphism $\phi\colon F\circ R_\Y\to R_\Z$, therefore $F(R_\Y(f))$ is a monomorphism.
+By \Cref{rem:ff} we know that $F$ is full and faithful and so reflects mono, implying that $f$ belongs to $\mathcal{R}_\Y$ too.
+\end{proof}
+
+\begin{corollary}\label{cor:funct}
+	Let $\cla(\X)$ be the category associated to the collection of all classes of a category $\X$, ordered by the inclusion.
+Then there exists a functor $\mathcal{R}_{(-)}\colon \cori(\X)^{op}\to \cla(\X) $.
+
+	Let, moreover, $\pos(\X),$ be the subcategory of $\cla(\X)$  given by classes of arrows stable under pushouts, Then  $\mathcal{R}^G_{(-)}\colon \gori(\X)^{op}\to \pos(\X) $ fitting in the rectangle below, where the vertical arrows are inclusions.
+	\[\xymatrix{\cori(\X)^{op} \ar[r]^{\mathcal{R}_{(-)}}& \cla(\X)\\ \gori(\X)^{op} \ar[u]^{J} \ar[r]_{\mathcal{R}^{G}_{(-)}}& \pos(\X) \ar[u]_{I}}\]
+\end{corollary}
+
+\iffalse 
+\begin{definition}
+	A \emph{comonad} $\m{C}$ on a category $\X$ is a triple $(C, \delta, \epsilon)$ given by a functor $C\colon \X\to \X$ and two natural transformations $\delta\colon C\to C\circ C $, $\epsilon\colon C\to \id{\X}$, called, respectively \emph{comultiplication} and \emph{counit} such that the following diagram commute
+	\[\xymatrix@C=30pt{C \ar[d]_{\delta}\ar[r]^-{\delta}& C\circ C  \ar[d]^{\delta*C}&  C \ar[d]_{\delta}\ar[r]^{\delta} \ar[dr]^-{\id{C}} & C\circ C \ar[d]^{\epsilon *C}\\ C\circ C \ar[r]_-{C*\delta}& C\circ C\circ C & C\circ C \ar[r]_-{C*\epsilon} & C}\]
+
+	A comonad $\m{C}$ is \emph{idempotent} if $\delta$ is an isomorphism.
+A \emph{morphism} between two comonad $\m{C}=(C, \delta, \epsilon)$ and $\m{D}=(D, \mu, \eta)$ is a natural transformation $\chi\colon C\to D$ such that the following diagrams commute
+	\[\xymatrix@C=30pt{ C \ar[r]^-{\delta} \ar[d]_{\chi} & C\circ C \ar[d]^{\chi*\chi}& C \ar[r]^{\epsilon} \ar[d]_{\chi}& 
+		\id{\X}  \\ D \ar[r]_-{\mu} & D\circ D
+		& D \ar[ur]_{\eta} }\]
+
+	We will denote by $\cmd(\X)$ the (possibly not locally small) category whose objects are idempotent comonads and whose arrows are morphisms of monads.
+\end{definition}
+
+\begin{remark} Let us recall that, given two functors $F, G\colon \X\rightrightarrows \Y$ and a natural transformation $\chi$ between them, then for every $X\in \X$ we have a naturality square
+	\[\xymatrix@C=40pt{F(F(X)) \ar[r]^{F(\chi_X)} \ar[d]_{\chi_{F(X)}}& F(G(X)) \ar[d]^{\chi_{G(X)}}\\G(F(X)) \ar[r]_{G(\chi_X)} & G(G(X))}\]
+
+	This entails that $(\chi * G)\circ (F*\chi)$ and $(G*\chi) \circ (\chi* F)$ are the same natural transformation, which we denote by $\chi*\chi$.
+\end{remark}
+
+\begin{proposition}
+	Let $L\colon \X \to \Y$ and $R\colon \Y \to \X$ be two functors such that $L\dashv R$.
+If $\eta \colon \id{\X}\to R\circ L$ and $\epsilon\colon L\circ R \to \id{Y}$ are the unit and the counit of this adjunction, then $(L\circ R, L*\eta *R ,\epsilon)$ is a comonad on $\Y$.
+\end{proposition}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+The next definition shows that every comonad come from an adjunction.
+
+\begin{definition}
+	contenuto...
+\end{definition}
+
+\begin{proposition}
+	contenuto...
+\end{proposition}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+We recall the following lemma relating idempotent comonads and coreflective subcategories.
+
+\begin{lemma}\label{lem:comsub}
+	Let $L\colon \Y\to \X$ and $R\colon \X \to \Y$ be two functors such that $L\dashv R$
+\end{lemma}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+Associated to any idempotent comonad we have a class of arrows.
+
+\begin{definition}
+	Let $\m{T}$ be an idempotent comonad on a category $\X$. We say that an arrow $f:X\to Y$ i
+\end{definition}
+\begin{remark}
+	contenuto...
+\end{remark}
+\fi
+
+\subsection{A left adjoint to $\mathcal{R}_{(-)}$}
+
+In this section we will show that, under suitable hypotheses, the functors $\mathcal{R}_{(-)}$ and $\mathcal{R}^G_{(-)}$ built in the previous sections, both have left adjoints.
+To do so, we need some preliminary work to be done.
+
+\begin{definition}
+	Let $\mathcal{M}$ be a class of arrows in a category $\X$ and let $\{m_i\}_{i\in I}$ be a family of objects in $\mathcal{M}/X$.
+We say that $\{m_i\}_{i\in I}$ has the \emph{epic $\mathcal{M}$-sum property} if:
+	\begin{enumerate}
+		\item it has a  coproduct $m\colon M\to X$;
+		\item the family  of coprojection $\{k_i\}_{i\in I}$ is jointly epic in $\X$.
+	\end{enumerate}
+
+	We say that $\X$ has \emph{epic $\mathcal{M}$-sums} if every family in $\sub{M}{X}{X}$ has the epic $\mathcal{M}$-sum property.
+\end{definition}
+
+Clearly the family $\{k_i\}_{i\in I}$ is always epic in $\mathcal{M}/X$, but from this it does not follow that it is so in $\X$, as shown from the following example.
+
+\begin{example}Let $\cat{Top}$ be the category of topological spaces and $\mathcal{C}$ the category of closed embeddings, and  consider the family $\{c_i\}_{i\in \mathbb{N}}$, where $c_i$ is the inclusion of $[\frac{1}{i+1}, +\infty)$ into $\mathbb{R}_{\geq 0}$.
+In $\mathcal{C}/\mathbb{R}_{\geq 0}$ their coproduct is the  identity $\id{\mathbb{R}_{\geq 0}}$.
+To see that the family of coprojections $\{k_i\}_{i\in \mathbb{N}}$ is not jointly epic in $\cat{Top}$, we can consider the space $X$ given by the quotient of $\mathbb{R}_{\geq 0}+\mathbb{R}_{\geq 0}$ by the equivalence relation generated from
+	\[R:=\{(x, y)\in X\times X \mid x=\iota_1(r), y=\iota_2(r) \text{ for some } r \in \mathbb{R}_{\geq 0}\smallsetminus\{0\}\}\]
+	Now, let $\pi$ be the quotient map and define $f_1, f_2\colon \mathbb{R}_{\geq 0}\rightrightarrows X$ as $\pi\circ \iota_1$ and $\pi \circ \iota_2$, respectively.
+Then, for every $i\in \mathbb{N}$ we have that $f_1\circ c_i=f_2\circ c_i$ because, given $r\in [\frac{1}{i+1}, +\infty)$ we have
+	\begin{align*}
+		f_1(c_i(r))&=\pi(\iota_1(c_i(r)))\\&=\pi(\iota_1(r))\\&=\pi(\iota_2(r))\\&=\pi(\iota_1(c_i(r)))\\&=f_1(c_i(r))
+	\end{align*}
+
+On the other hand, $f_1(0)\neq f_2(0)$, thus $\cat{Top}$ does not have epic $\mathcal{C}$-sums.
+\end{example}
+\begin{example}
+	\todo{insiemi}
+\end{example}
+
+\begin{example}
+	\todo{adesive finitare}
+\end{example}
+\begin{example}
+	\todo{simple graph}
+\end{example}
+
+We are now ready to construct a left adjoint to $\mathcal{R}_{(-)}$.
+
+\begin{definition} 
+	Let $\X$ be a category and $\mathcal{A}$ a class of arrows of it.
+We define the category $\C(\mathcal{A})$ as the full subcategory of $\X$ given by the objects $Z\in \X$ such that, for every  pair of arrows $g,h\colon Z\rightrightarrows X$, if $f\circ g=f\circ h$ for some $f\colon X\to Y$ belonging to $\mathcal{A}$, then $g=h$.
+\end{definition}
+
+A first thing that we can notice about $\C(\mathcal{A})$ is that, in the presence of a factorization system, is its closure under epimorphisms, as shown by the following proposition.
+
+\begin{proposition}\label{prop:ima}
+	$\mathcal{A}$ be a class of arrows in a category $\X$ If $e\colon X\to Y$ is an epimorphism with domain in $\C(\mathcal{A})$, then $Y$ belongs to $\C(\mathcal{A})$ too.
+\end{proposition}
+\begin{proof}
+	Let $f\colon Z\to V$ be an arrow of $\mathcal{A}$ and take two other arrows $g,h\colon Y\to Z$ such that $f\circ g=f\circ h$. Then we also know that
+	\[f\circ g\circ e= f\circ h\circ e\]
+	By hypothesis $X$ is in $\C(\mathcal{A})$, so that $g\circ e=f\circ e$. The thesis now follows since $e$ is an epimorphism.
+\end{proof}
+\begin{example}
+	\todo{spazi topologici puntati - controesempio}
+\end{example}
+
+\begin{lemma}\label{lem:cor}
+	Let $\X$ be a category with a proper factorization system $(\mathcal{E}, \mathcal{M})$.
+Suppose, moreover, that $\X$ has the epic $\mathcal{M}$-sum property.
+Then for every $\mathcal{A}\in \cla(\X)$, $\C(\mathcal{A})$ is a coreflective subcategory of $\X$.
+\end{lemma}
+
+\begin{proof}
+	For every object $X$ of $\X$, let us define
+	\[\mathcal{F}_X:=\{m\in \mathcal{M}/X \mid \dm{m} \text{ belongs to } \C(\mathcal{A})\}\] 
+	We can then define $R(X)$ as the domain of the sum over $\mathcal{F}_X$ in $\mathcal{M}/X$. In particular, we have an arrow $\epsilon_X\colon R(X)\to X$, belonging to $\mathcal{M}$.
+
+	First of all, we have to prove that $R(X)$ so defined is an object of $\C(\mathcal{A})$.
+Let thus $f\colon A\to Y$ be an arrow in $\mathcal{A}$ and suppose that there are $g,h\colon R(X)\to A$ such that  $f\circ h= f \circ g$.
+Now, for every $m\colon M\to X$ in $\mathcal{F}_X$ we have a coprojection $k_m\colon m\to \epsilon_X$.
+Precomposing with it we get
+	\[f\circ h \circ k_m=f\circ g\circ k_m\]
+	By definition $M$ is in $\C(\mathcal{A})$, so we can conclude that $h\circ k_m=g\circ k_m$.
+Since  this holds for every $m\in \mathcal{F}_Z$, the epic $\mathcal{M}$-sum property of $\X$ entails $f=g$ as wanted.
+
+	To conclude, is it now enough to show that $\epsilon_X$ has the universal property of a counit.
+Let $Y$ be an object of $\C(\mathcal{A})$ with an arrow $f\colon Y\to X$.
+We can factor $f$ it as $m\circ e$ with $e\colon Y\to E$ and $m\colon E\to X$ in $\mathcal{M}$.
+By \Cref{prop:ima} we know that $E$ is in $\C(\mathcal{A})$, thus there exists a coprojection $k_m\colon m\to \epsilon_X$.
+In particular we have
+	\begin{align*}
+		\epsilon_X\circ k_m\circ e&=m\circ e = f
+	\end{align*}
+
+On the other hand, if $g\colon Y\to R(X)$ is such that $\epsilon_X\circ g=f$, then $g$ must coincide with $k_m\circ e$ because $\epsilon_X$, being in $\mathcal{M}$ is monic.
+\end{proof}
+
+\begin{example}
+	\todo{spazi topologici puntati - controesempio 2}
+\end{example}
+
+\begin{proposition}Let $(\mathcal{E}, \mathcal{M})$ be a proper factorization system on a acategory $\X$ with $\mathcal{M}$-sums. Then the following hold true:
+	\begin{enumerate}
+		\item for every class $\mathcal{A}$ in $\cla(\X)$, $\mathcal{A}\subseteq \mathcal{R}_{\C(\mathcal{A})}$;
+		\item the functor $\mathcal{R}_{(-)}\colon \cori(\X )^{op}\to \cla(\X)$ has a left adjoint.
+	\end{enumerate} 
+\end{proposition}
+\begin{proof}\begin{enumerate}
+		\item Let $f\colon X\to Y$ be an arrow in $\mathcal{A}$ and suppose that $g,h\colon Z\to R(X)$ are arrows in $\C(\A)$ such that $R(f)\circ g=R(f)\circ h$. Then
+		\begin{align*}
+			f\circ \epsilon_X\circ I(g)&=\epsilon_Y\circ I(R(f))\circ I(g)\\&=
+			\epsilon_Y\circ I(R(f))\circ I(h)\\&=f\circ \epsilon_X\circ I(h)
+		\end{align*}
+		Since $f$ is in $\mathcal{A}$, we can deduce that $\epsilon_X\circ I(g)=\epsilon_X\circ I(h)$. The thesis now follows from the fact that $\epsilon_X$ is mono.
+
+		\item Let $\Y$ be a coreflective subcategory of $\X$ such that $\mathcal{A}\subseteq \mathcal{R}_\Y$.
+We have to show that $\Y\subseteq \C(\mathcal{A})$.
+Let then $Y$ be an object of $Y$, $f\colon X\to Z$ and arrow in $\mathcal{A}$ and $g, h\colon I_\Y(Y)\rightrightarrows X$ two arrows in $\X$ such that $f\circ g=f\circ h$.
+Applying $R_\Y$ and since, by hypothesis, $R_\Y(f)$ is mono, we get that $R_\Y(g)=R_\Y(h)$.
+Now, by naturality of the counit we have
+	\begin{align*}g\circ \epsilon_{I_\Y(Z)}&=\epsilon_X\circ R_\Y(g)\\&=\epsilon_X\circ R_\Y(h)\\&=h\circ \epsilon_{I_\Y(Z)}
+	\end{align*}
+	By \Cref{cor:counit}  we know that $\epsilon_{I_\Y(Z)}$ is an isomorphism and we can conclude. \qedhere 
+	\end{enumerate}
+\end{proof}
 

### 2024-10-16 concur/presentazione/pres_lunga.tex
finale

@@
 %\newcommand{\yo}{\mathcal{Y}}
-\renewcommand*{\bibfont}{\footnotesize}
+%\renewcommand*{\bibfont}{\footnotesize}
 
@@
 \begin{frame}{DPO rewriting sytems}\justifying
+	\begin{overprint}
+		\onslide<1|handout:1>
 
 		We will focus on the \emph{double pushout} (DPO) approach  to  graph rewriting (cfr. \cite{ehrig2006fundamentals}). 
+		\smallskip
 
+		\onslide<2|handout:0>
+
+		We will focus on the \emph{double pushout} (DPO) approach  to  graph rewriting (cfr. \cite{ehrig2006fundamentals}). 
 		\smallskip
-	\begin{overprint}
-		\onslide<1|handout:1>
+
 		A \emph{rewriting rule} is a pair  of arrows $l:K\to L$ and $r:K\to R$ with the same domain. To rewrite an object $G$ according to a rule we proceed in three steps.
 
-		\onslide<2| handout:0>
+		\onslide<3| handout:0>
+
+		We will focus on the \emph{double pushout} (DPO) approach  to  graph rewriting (cfr. \cite{ehrig2006fundamentals}). 
+		\smallskip
 
@@
 
-		\onslide<3| handout:0>
+		\onslide<4| handout:0>
+
+We will focus on the \emph{double pushout} (DPO) approach  to  graph rewriting (cfr. \cite{ehrig2006fundamentals}). 
+\smallskip
 
@@
 
-		Second: remove the image of $m$  building a pushout square. \vspace{-0.075cm}
+		Second: ``remove'' the image of $m$  building a pushout square. \vspace{-0.075cm}
 		\begin{center}
@@
 		\end{center}		
-		\onslide<4| handout:0>
+		\onslide<5| handout:0>
 
-		A \emph{rewriting rule} in a category $\X$ is a pair  of arrows $l:K\to L$ and $r:K\to R$ with the same domain. To rewrite an object $G$ according to a rule we proceed in three steps.
+We will focus on the \emph{double pushout} (DPO) approach  to  graph rewriting (cfr. \cite{ehrig2006fundamentals}). 
+\smallskip
 
-		Third: fill the hole so obtained, with $R$ taking a pushout.\vspace{-0.075cm}
-		\begin{center}\hspace{0.045cm}
+		A \emph{rewriting rule} is a pair  of arrows $l:K\to L$ and $r:K\to R$ with the same domain. To rewrite an object $G$ according to a rule we proceed in three steps.
+
+		Third: glue $R$ into the ``hole'',  taking a pushout.\vspace{-0.075cm}
+		\begin{center}\hspace{0.08cm}
 			\begin{tikzpicture}
@@
 
-\begin{frame}{DPO rewriting system}\justifying
+\begin{frame}{DPO rewriting systems}\justifying
 The categorical framework is given by \emph{$\mathcal{M}$-adhesive categories}. \pause 
@@
 
-		A system is \emph{linear} if every rule is made by arrows in $\mathcal{M}$, \emph{left-linear} if the left hand side of every rule is in $\mathcal{M}$.
+		A system is \emph{linear} if every rule is made by arrows in $\mathcal{M}$, \emph{left-linear} if the left leg of every rule is in $\mathcal{M}$.
 	\end{definition}
@@
 \begin{alertblock}{Motivation}
-	Our long term aim is to provide a concurrent semantics for left-linear DPO-rewriting systems (see \cite{baldan2017domains}). 
+	Our long term aim is to provide a concurrent semantics for left-linear DPO-rewriting systems (see \cite{baldan2021concurrent}). 
 \end{alertblock}
@@
 
-\begin{frame}{An example}
+\begin{frame}{An example}\justifying
 	If we want a (very sweet) coffee we can add first the white sugar and then the brown one. Finally we can stir it.
@@
 \end{frame}
-
+\iffalse 
 \begin{frame}{Results: the Three Steps Lemma}\justifying
@@
 \end{frame}
+\fi
 
@@
 
-	\smallskip \pause
+	\medskip \pause
 
-	In \cite{baldan2017domains} a category of domains, called \emph{weak prime domains} has been proposed as a possible concurrent semantic for systems allowing fusions.
+	In \cite{baldan2021concurrent} a category of domains, called \emph{weak prime domains} has been proposed as a possible concurrent semantic for systems allowing fusions.
 
-	\smallskip \pause We plan to build on the results proved in this paper to show that to every left-linear DPO rewriting system it is possible to associate one of these domains, representing ``derivation up to switches''.
+	\medskip \pause We plan to build on the results proved in this paper to show that to every left-linear DPO rewriting system it is possible to associate one of these domains, representing ``derivation up to switches''.
 \end{frame}

### 2024-10-29 domains/domains.tex
minimo

@@
 		\end{itemize}
-
-		Given an object $X$, we can consider the poset $\fuse{X}$
 \end{setting}
+
+\begin{remark}\label{rem:cont}
+	Notice that, by \Cref{prop:varie}, $\mathcal{R}_\Y$ contains all monos, therefore, in particular, it contains all arrows in $\mathcal{M}$.
+\end{remark}
 
@@
 
-\begin{lemma}Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^{n}$ be a derivation, then the following hold true:
-	\begin{enumerate}
-		\item $\iota_{\der{D}, G_0}\colon G_0\to \tpro{D}$ belongs to $\mathcal{R}$ and $\iota_{\der{D}, G_{n+1}}\colon G_{n+1}\to \tpro{D}$ belongs to $\mathcal{M}$;
-		\item for every $i\in [0, n+1]$, there are  arrows $m_i$ in $\mathcal{M}$ and $r_i$ in $\mathcal{R}$ such that the coprojection $\iota_{\der{D}, G_i}\colon G_i\to \tpro{D}$ is equal to $r_i\circ m_i$.
-	\end{enumerate}
+\begin{lemma}Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^{n}$ be a derivation, then $\iota_{\der{D}, G_{n+1}}\colon G_{n+1}\to \tpro{D}$ belongs to $\mathcal{M}$ and,  for every $i\in [0, n]$,  $\iota_{\der{D}, G_i}\colon G_i\to \tpro{D}$ is in $\mathcal{R}_\Y$.
 \end{lemma}
-\begin{proof}
-	\begin{enumerate}		
-		\item We proceed by induction on the length of $\der{D}$.
-
-		\smallskip \noindent $\lgh(\dder{D})=0$. then $\tpro{\dder{D}}$ is simply $(G_0, \{\id{G_0}\})$ and $\id{G_0}$ belongs to $\mathcal{M}$ and $\mathcal{R}$.
+\begin{remark}\label{rem:cont2}
+	By \Cref{rem:cont}, $\mathcal{M}$ is a subclass of $\mathcal{R}_\Y$, so that the previous lemma entails that all the coprojections belong to $\mathcal{R}_\Y$.
+\end{remark}
+\begin{proof} 
+We proceed by induction on the length of $\der{D}$.
+
+		\smallskip \noindent $\lgh(\dder{D})=0$. then $\tpro{\dder{D}}$ is simply $(G_0, \{\id{G_0}\})$ and $\id{G_0}$ belongs to $\mathcal{M}$.
 
@@
 Let also $\der{D}'$ be $\{\dder{D}_i\}^{n-1}_{i=0}$ and $\rho_n=(l_n, r_n)$ be the rule applied in $\dder{D}_n$.
-The thesis follows from the inductive hypothesis and the diagram below.
-		\[\xymatrix@C=30pt{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar@{>->}[l]_{l_{n}} \ar[r]_{r_{n}}^{\mini} & R_{n} \ar[d]^{h_n} \\ G_{n} \ar@{>->}[d]_{\iota_{\der{D}' , G_{n}}}& \ar@{>->}[l]^{f_n} D_n \ar[r]^{\mini}_{g_n}& G_{n+1}  \ar@{>->}[d]^{\iota_{\der{D}, G_{n+1}}}\\  \lpro \der{D}' \ar[rr]_{p}^{\mini} \rpro && \tpro{D}\\ G_0 \ar[u]^-{\iota_{\der{D}', G_{0}}}_{\mini} \ar@/_.5cm/[urr]_{\iota_{\der{D}, G_0}}^\mini}\]
-
-		\item We proceed again by induction the length of $\der{D}$.
-
-		\smallskip \noindent$\lgh(\dder{D})=0$. This follows at once from the previous point.
-
-		\smallskip \noindent$\lgh(\dder{D})=1$. Again, this follows from the previous point.
-
-		\smallskip \noindent$\lgh(\dder{D})\geq 2$.
-As above, if $\der{D}$ is $\{\dder{D}_i\}_{i=0}^n$ with $n\geq 1$, we can consider the derivation $\der{D}':=\{\dder{D}_i\}^{n-1}_{i=0}$ and consider the rule $\rho_n$ be the rule applied in $\dder{D}_n$.
-By the inductive hypothesis, for every $i\in [0,n]$ we have the diagram below.
-		\[\xymatrix@C=30pt{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar@{>->}[l]_{l_{n}} \ar[r]_{r_{n}}^{\mini} & R_{n} \ar[d]^{h_n} \\ G_{n} \ar@{>->}[d]_{\iota_{\der{D}' , G_{n}}}& \ar@{>->}[l]^{f_n} D_n \ar[r]^{\mini}_{g_n}& G_{n+1}  \ar@{>->}[d]^{\iota_{\der{D}, G_{n+1}}}\\  \lpro \der{D}' \ar[rr]_{p}^{\mini} \rpro && \tpro{D}\\X \ar[u]^{r_i}_{\mini} &&  G_i \ar[ull]^-{\iota_{\der{D}', G_{i}}} \ar[u]_{\iota_{\der{D}, G_i}} \ar@{>->}[ll]^{m_i}}\]
-
-		The thesis now follows since $\mathcal{R}$ is closed under composition. To conclude, it is enough to notice that  the thesis for $i=n+1$ follows immediately from point $1$. 
-		\qedhere 
-	\end{enumerate}
+We can then build the diagram below, in which the bootm half is a pushout.
+		\[\xymatrix@C=30pt{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar@{>->}[l]_{l_{n}} \ar[r]_{r_{n}}^{\mini} & R_{n} \ar[d]^{h_n} \\ G_{n} \ar@{>->}[d]_{\iota_{\der{D}' , G_{n}}}& \ar@{>->}[l]^{f_n} D_n \ar[r]^{\mini}_{g_n}& G_{n+1}  \ar@{>->}[d]^{\iota_{\der{D}, G_{n+1}}}\\  \lpro \der{D}' \ar[rr]_{p}^{\mini} \rpro && \tpro{D}\\ G_i \ar[u]^-{\iota_{\der{D}', G_{i}}}_{\mini} \ar@/_.5cm/[urr]_{\iota_{\der{D}, G_i}}}\]
+
+		The thesis follows from the inductive hypothesis and the fact that, by \Cref{prop:varie}, $\mathcal{R}_\Y$ is closed under composition.
 \end{proof}
@@
 \begin{definition} Let $\rho$ be a rule $(l, r)$ in $\R$ with left-hand side $L$.
-Let $e\colon X\fto Y$ and $e'\colon X\fto Y'$ be two fusions with the same domain and $m\colon L\to Y$ and $m'\colon L\to Y'$ be two arrows, we say that the pairs $(e,m)$ and $(e', m')$ are \emph{compatible with respect to $\rho$} if the following diagram is commutative, where the outer square is a pushout.
-
-\[\xymatrix{X\ar@{>>}[rr]^\mini_{e} \ar@{>>}[dd]_{e'}^\mini & & Y \ar@{>>}[dd]_{q}^\mini\\ &L  \ar[ur]_{m} \ar[dl]^{m'}\\Y' \ar@{>>}[rr]_{q'}^{\mini} && Q}\]
+Let $e\colon X\fto Y$ and $e'\colon X\fto Y'$ be two fusions with the same domain and $m\colon L\to Y$ and $m'\colon L\to Y'$ be two arrows, we say that the pairs $(e,m)$ and $(e', m')$ are \emph{compatible with respect to $\rho$} if there exists $q\colon Y\fto Q$ and $q'\colon Y'\fto Q'$ making the following diagram commutative.
+
+\[\xymatrix{X\ar@{>>}[rr]^\mini_{e} \ar@{>>}[dd]_{e'}^\mini & & Y \ar@{.>>}[dd]_{q}^\mini\\ &L  \ar[ur]_{m} \ar[dl]^{m'}\\Y' \ar@{.>>}[rr]_{q'}^{\mini} && Q}\]
 
@@
 
+\begin{proposition}
+Let $\rho$ be a rule with left-hand side $L$ and $(e,m)$ a pair made by a fusion $e\colon X\fto Y$ and an arrow $m\colon L\to Y$.
+Then for every $(e', m')$ in $\mathcal{F}_\rho(e,m)$ \[\mathcal{F}_\rho(e,m)=\mathcal{F}_\rho(e',m')\]
+\end{proposition}
+\begin{proof} Let $e'$ be an arrow $X\fto Y'$, by definition of compatibility, we know that there exist $q\colon Y'\to Q$ and $Q\colon Y\to Q$ fitting in the diagram below. 
+\[\xymatrix{X\ar@{>>}[rr]^\mini_{e} \ar@{>>}[dd]_{e'}^\mini & & Y \ar@{.>>}[dd]_{q}^\mini\\ &L  \ar[ur]_{m} \ar[dl]^{m'}\\Y' \ar@{.>>}[rr]_{q'}^{\mini} && Q}\]
+
+We are now going to show the two inclusions.
+
+	\smallskip \noindent $(\subseteq)$. Let $(e'', m'')$ be another element of $\mathcal{F}_\rho(e,m)$, so that we have a square as the one below
+
+	\[\xymatrix{X\ar@{>>}[rr]^\mini_{e} \ar@{>>}[dd]_{e''}^\mini & & Y \ar@{>>}[dd]_{\hat{q}}^\mini\\ &L  \ar[ur]_{m} \ar[dl]^{m''}\\Y'' \ar@{>>}[rr]_{q''}^{\mini} && \hat{Q}}\]
+
+	Since $\X$ has all pushouts, and using \Cref{prop:fusion}, we can build the following diagram, where the bottom square is a pushout.
+	\[\xymatrix{&& X \ar@{>>}[d]_{e}^{\mini} \ar@/^.3cm/@{>>}[drr]_{e'}^{\mini} \ar@/_.3cm/@{>>}[dll]^{e'''}_{\mini}\\Y'' \ar@{>>}[dr]_{q''}^{\mini} && Y \ar@{>>}[dr]_{q}^{\mini} \ar@{>>}[dl]^{\hat{q}}_{\mini}  && Y'\ar@{>>}[dl]^{q'}_{\mini}  \\ & \hat{Q} \ar@{>>}[dr]_{p_1}^{\mini} && Q\ar@{>>}[dl]^{p_2}_{\mini}\\ &&Q'}\]
+
+	To get the thesis, it is now enough to compute:
+	\begin{align*}
+		p_1\circ q''\circ m''&=p_1\circ \hat{q}\circ m\\&=p_2\circ q\circ m\\&=p_2\circ q'\circ m
+	\end{align*}
+
+	\smallskip \noindent $(\supseteq)$ This follows immediately from the previous point since $(e,m)\in \mathcal{F}_\rho(e,m)$.
+\end{proof}
+
 \begin{lemma}
-	Let $e\colon X\fto Y$, $\rho\in \R$ with left-hand side $L$ and $m\colon L\to Y$ be such that $\mathcal{F}_\rho(e, m)$.
-Then there exists a fusion $(\mf{e},\mf{m})\colon L\to \mf{Y}$  in $\mathcal{F}_\rho(e, m)$ and for every other $(e', m')$ in it there exists $f\colon \mf{Y}\to Y'$, where $Y'$ is the codomain of $e'$, such that:
-\[f\circ e =e' \qquad f\circ m=m'\]
+	Let $e\colon X\fto Y$ be a fusion, $\rho$ a rule with left-hand side $L$ and $m\colon L\to Y$ an arrow.
+Then there exists $(\mf{e},\mf{m})$, with $\mf{e}\colon X\fto \mf{Y}$,  in $\mathcal{F}_\rho(e, m)$ with the property that for every other $(e', m')$ in $\mathcal{F}_\rho(e, m)$, there exists an arrow $f_{(e', m')}\colon \mf{Y}\to Y'$, where $Y'$ is the codomain of $e'$, such that:
+\[f_{(e', m')}\circ \mf{e} =e' \qquad f_{(e', m')}\circ \mf{m}=m'\]
 \end{lemma}
 
-\begin{proof}By hypothesis $I$ is non-empty, thus we can consider $k$ in it and $e_k\colon X\to Y_k$.
-Consider the two diagrams below, where the upper square  in the inner rectangle one is the image through $I_\Y\circ R_\Y$ of a pullback square, while the outer rectangle is a pushout.
-Notice that, by hypothesis and \Cref{prop:fusion}, all the horizontal arrows and the coprojection $e\colon X\to Y$ are fusions and, moreover, there exists the dotted arrow $f_k\colon Y\to Y_k$.
-	\[\xymatrix@C=55pt{I_\Y(R_\Y(P)) \ar[d]_{I_\Y(R_\Y(p_2)) } \ar@{>>}[r]_-{I_\Y(R_\Y(p_1))}^{\mini} & I_\Y(R_\Y(L)) \ar@/^.4cm/[dddr]^{q} \ar[d]_{I_\Y(R_\Y(m_k)) } \\ I_\Y(R_\Y(X)) \ar[d]_{\epsilon_X} \ar@{>>}[r]_-{I_\Y(R_\Y(e_k))}^{\mini}& I_\Y(R_\Y(Y_k)) \ar[d]_{\epsilon_X}  \\ X\ar@{>>}@/_.5cm/[drr]^{\mini}_{e} \ar@{>>}[r]_{e_k}^{\mini}& Y_k \\ &&Y\ar@{.>}[ul]_{f_k}}\]
-
-	Let now $i$ be any other element of $i$.
-
-\end{proof}
-
- \begin{corollary}
-\todo{quoziente minimo}
- \end{corollary}
+\begin{proof} We start by taking the following pullback square. Since $e\colon X\fto Y$ is a fusion, by \Cref{prop:fusion} we know that $p_1\colon P\to L$ is a fusion too.
+	\[\xymatrix{P \ar@{>>}[r]_{p_1}^{\mini} \ar[d]_{p_2}& L \ar[d]^{m} \\ X \ar@{>>}[r]_{e}^{\mini} & Y}\]
+
+Now, applying $I_\Y\circ R_\Y$ we get the two squares in the diagram below, while the outer boundary of it is a pushout.
+Notice that, by hypothesis and \Cref{prop:fusion}, all the horizontal arrows and the coprojection $\mf{e}\colon X\to \mf{Y}$ are fusions.
+Moreover the universal property of pushouts yields the dotted $f_{(e,m)}\colon \mf{Y}\to Y$
+	\[\xymatrix@C=55pt{I_\Y(R_\Y(P)) \ar[d]_{I_\Y(R_\Y(p_2)) } \ar@{>>}[r]_-{I_\Y(R_\Y(p_1))}^{\mini} & I_\Y(R_\Y(L)) \ar@/^.4cm/[dddr]^{n} \ar[d]_{I_\Y(R_\Y(m)) } \\ I_\Y(R_\Y(X)) \ar[d]_{\epsilon_X} \ar@{>>}[r]_-{I_\Y(R_\Y(e))}^{\mini}& I_\Y(R_\Y(Y)) \ar[d]_{\epsilon_X}  \\ X\ar@{>>}@/_.5cm/[drr]^{\mini}_{\mf{e}} \ar@{>>}[r]_{e}^{\mini}& Y \\ &&\mf{Y}\ar@{.>}[ul]_{f_{(e,m)}}}\]
+
+Now, by hypothesis $L$ is in $\Y$, thus by \Cref{cor:counit} $\epsilon_L$ is an isomorphism and we can define $\mf{m}\colon L\to \mf{Y}$ as $n\circ \epsilon^{-1}_L$, so that 
+\begin{align*}
+f_{(e,m)}\circ \mf{m}&=f_{(e,m)}\circ n\circ \epsilon^{-1}_L\\&= \epsilon_X\circ I_\Y(R_\Y(m))\\&=m\circ \epsilon_L\circ \epsilon^{-1}_L\\&=m
+\end{align*}
+
+We have now to show that $(\mf{e}, \mf{m})$ belongs to $\mathcal{F}_\rho(e,m)$. But to do so it is enough to consider the pushout square below:
+\[\xymatrix{X \ar@{>>}[r]^{\mf{e}}^\mini \ar@{>>}[d]_{e}^\mini& \mf{Y} \ar[d]_{\mf{q}}^\mini\\ Y \ar@{>>}[r]_{q}^\mini & Q}\]
+
+Indeed, on one hand we have
+\begin{align*}
+	q\circ f_{(e,m)}\circ \mf{e}&=q\circ e\\&=\mf{q}\circ \mf{e}
+\end{align*}
+So that, since $\mf{e}$ is an epimorphism, we know that  $q\circ f_{(e,m)}=\mf{q}$. But then
+\begin{align*}
+	q\circ m&=q\circ f_{(e,m)}\circ \mf{m}\\&=
+	\mf{q}\circ \mf{m}
+\end{align*}
+
+	Let now $(e', m')$ be another element of $\mathcal{F}_\rho(e,m)$, thus we have a square as the one below.
+\[\xymatrix{X\ar@{>>}[rr]^\mini_{e} \ar@{>>}[dd]_{e'}^\mini & & Y \ar@{>>}[dd]_{q}^\mini\\ &L  \ar[ur]_{m} \ar[dl]^{m'}\\Y' \ar@{>>}[rr]_{q'}^{\mini} && Q}\]
+
+ Now, computing we have:
+ \begin{align*}
+ q'\circ	m'\circ \epsilon_L\circ I_\Y(R_\Y(p_1))&=q\circ m\circ \epsilon_L\circ I_\Y(R_\Y(p_1))\\&=q\circ m\circ p_1\circ \epsilon_P\\&=q\circ e \circ p_2\circ \epsilon_P\\&=q'\circ e' \circ \epsilon_X\circ I_\Y(R_\Y(p_2))
+ \end{align*}
+
+Since $q'$ is a fusion, by the fourth point of \Cref{prop:varie} the outer square in the diagram below commutes.
+
+	\[\xymatrix@C=55pt{I_\Y(R_\Y(P)) \ar[d]_{I_\Y(R_\Y(p_2)) } \ar@{>>}[r]_-{I_\Y(R_\Y(p_1))}^{\mini} & I_\Y(R_\Y(L))  \ar[dd]_{n} \ar[dr]^-{\epsilon_L}\\ I_\Y(R_\Y(X)) \ar[d]_{\epsilon_X} && L \ar[dd]^{m'} \ar[dl]_{\mf{m}}   \\ X\ar@{>>}@/_.5cm/[drr]^{\mini}_{e'} \ar@{>>}[r]_{\mf{e}}^{\mini}& \mf{Y} \ar@{.>}[dr]^{f_{(e',m')}}\\ &&Y'}\]
+
+Thus  we obtain the arrow $f_{(e', m')}\colon \mf{Y}\to Y'$ by the universal property of pushouts.	
+\end{proof}
+
+ \begin{definition}\todo{quoziente minimo}
+ \end{definition}
 
@@
 Let $L\colon \X\to \Y$ and $R\colon \Y \to \X$ be a pair of functors such that $L\dashv R$ and suppose that $L$ is full and faithful.
-Let $\epsilon\colon L\circ R\to \id{\Y}$ be the unit of the adjunction, then the following are true for every object $X$:
+Let $\epsilon\colon L\circ R\to \id{\Y}$ be the counit of the adjunction, then the following are true for every object $X$:
 \begin{enumerate}

### 2024-11-14 domains/domains.tex
small
minori

@@
 
+\newpage
+\begin{definition}Let $\X$ be an $\mathcal{M}$-adhesive category and consider a left-linear DPO-rewriting system $(\X, \R)$ on it.
+Take two non-empty decorated derivations $(\der{D}, \alpha, \omega)$ and  $(\der{D}', \alpha', \omega')$ with the same length and with isomorphic sources and targets.
+
+	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with assciated sequence of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{semi-consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma\colon [0,n]\to [0,n]$  such that, for every $i\in [0,n]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
+	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_\sigma}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro\\L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
+\end{definition}
+
+\begin{remark}\label{rem:coproj}
+	Notice that, in particular, the previous diagram entails
+	\[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
+\end{remark}
+
+\begin{proposition}\label{prop:isouno} For every semi-consistent permutation $\sigma$ between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, the mediating isomorphism $\xi_\sigma\colon \tpro{D}\to \lpro \der{D}'\rpro$ is unique.
+\end{proposition}
+\begin{proof} Let $\xi'_\sigma$ be another mediating isomorphism, then by \Cref{rem:coproj} we have
+	\[\begin{split}
+		\xi_\sigma \circ \iota_{L_i}&=\iota'_{L_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{L_i}
+	\end{split} \qquad \begin{split}
+		\xi_\sigma \circ \iota_{K_i}&=\iota'_{K_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{K_i}
+	\end{split} \qquad \begin{split}
+		\xi_\sigma \circ \iota_{R_i}&=\iota'_{R_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{R_i}
+	\end{split}\]
+
+	Now, notice that 
+	\begin{align*}
+		\xi_\sigma \circ \iota_{G_0}&=\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}\\&=\xi'_\sigma \circ \iota_{G_0}
+	\end{align*}
+
+	If $\lgh(\der{D})=0$ this is enough to conclude, otherwise we are going to prove by induction that, for every $i\in [0, \lgh(\der{D})-1]$
+	\[
+	\xi_\sigma \circ \iota_{G_i}=\xi'_\sigma\circ \iota_{G_i}
+	\]
+
+	\smallskip \noindent $i=0$. This is simply the result obtained before.
+
+	\smallskip \noindent $i >0$. If $i>0$, we know that there is a pushout square
+	\[\xymatrix{K_{i-1}\ar[r]^{r_{i-1}} \ar[d]_{k_{i-1}}& R_{i-1} \ar[d]^{h_{i-1}}\\ D_{i-1} \ar[r]_{g_{i-1}}& G_i}\] 
+	By \Cref{rem:coproj} and the induction hypothesis we know that
+	\[\begin{split}
+		\xi_\sigma \circ \iota_{G_i}\circ h_{i-1}&=  \xi_\sigma\circ \iota_{R_{i-1}}\\&=\iota'_{R_{\sigma(i-1)}}\\&=\xi'_{\sigma}\circ \iota_{R_{i-1}}\\&=\xi'_{\sigma} \circ \iota_{G_i}\circ h_{i-1}\\&
+	\end{split} \qquad
+	\begin{split}
+		\xi_\sigma \circ \iota_{G_i}\circ g_{i-1}&=\xi_{\sigma}\circ \iota_{D_{i-1}}\\&=\xi_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi'_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi'_{\sigma}\circ \iota_{D_{i-1}} \\&=\xi'_{\sigma}\circ \iota_{G_{i}} \circ g_{i-1}
+	\end{split}
+	\]
+
+	Since $\xi_\sigma \circ \iota_{D_i}$ must be $\xi_\sigma \circ \iota_{G_i}\circ f_i$, we also have
+	\[\xi_\sigma \circ \iota_{D_i}=\xi'_\sigma \circ \iota_{D_i}\] 
+	and the thesis follows.
+\end{proof}
+
+\begin{proposition}\label{prop:abstoswitch}
+	Let $(\der{D, \alpha, \omega})$ and $(\der{D}', \alpha, \omega')$ be two derivation with an abstract equivalence among them with the identity as first component.
+Then $\id{n}$ is a semi-consistent permutation among them.
+\end{proposition}
+\begin{proof}
+Let $\xi\colon \tpro{D}\to \lpro \der{D}'\rpro$ be the arrow induced by 
+\[\xi \circ \iota_{G_i}:=\iota'_{G'_i}\circ \phi_{G_i}\] 
+Then we have
+	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha} & G_0 \ar[dl]^{\id{G_0}} \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi}\\ G_0 \ar[rr]_{\iota'_{G_0}} & &\lpro \der{D}' \rpro\\L_i \ar[r]^{m_i} \ar[d]_{m'_{i}}& G_i \ar[dl]^{\phi_i} \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi} & R_i \ar[r]^{h_i} \ar[d]_{h'_{i}}& G_{i+1} \ar[dl]_{\phi_{i+1}} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{i}}}&& \lpro \der{D}' \rpro& G'_{i+1} \ar[rr]_{\iota'_{G'_{i+1}}}&& \lpro \der{D}' \rpro}\]
+\end{proof}
+
+\begin{lemma}Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X,\R)$ a well-switching rewriting system.
+	Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$ and suppose that we have the following two switching sequences
+	\[\der{D} \shift{(0,1)} \der{D}' \shift{(1,2)} \der{D}'' \shift{(0,1)}\der{D}'''\\
+	\qquad \der{D}\shift{(1,2)}\der{E}'\shift{(0,1)} \der{E}'' \shift{(1,2)}\der{E}''' \]
+	Then $\der{D}'''$ and $\der{E}'''$ are abstraction equivalent. The abstraction equivalence has the identity has a first and last isomorphism.
+\end{lemma}
+\begin{proof}
+	To fix the notation, let us depict the derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$
+	\[\xymatrix@C=15pt{L_0\ar[d]^{m_0}&& K_0 \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]_(.4){i_0}|(.29)\hole \ar[dr]|(.28)\hole_{h_0} && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.28)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_1 \ar[dr]|(.28)\hole_{h_1} \ar@/^.35cm/[drrr]_(.4){j_0}|(.29)\hole  && L_2 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.28)\hole^{m_2}& K_2 \ar[d]^{k_2}\ar@{>->}[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]_{h_2} \\G_0 && \ar@{>->}[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar@{>->}[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2 && \ar@{>->}[ll]^{f_2} D_2 \ar[rr]_{g_2}&& G_3 }\]
+
+	We are going to do the two sequences of switches and compare the results.
+
+	\smallskip \noindent First sequence of switches.
+
+	We begin switching $\dder{D}_0$ and $\dder{D}_1$ to get the following diagram
+	\[\xymatrix@C=15pt{L_1\ar[d]^{f_0\circ i_1}&& K_1 \ar[d]_{k'_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){a_0}|(.29)\hole \ar[dr]|(.28)\hole_{h'_1} && L_0 \ar@/_.35cm/[dlll]^(.4){a_1} \ar[dl]|(.28)\hole^{m'_0}& K_0 \ar[d]^{k'_0}\ar@{>->}[l]_{l_0} \ar[r]^{r_0} & R_0 \ar[dr]|(.28)\hole_{g_1\circ i_0} \ar@/^.35cm/[drrr]_(.4){b_0}|(.29)\hole  && L_2 \ar@/_.35cm/[dlll]^(.4){b_1} \ar[dl]|(.28)\hole^{m_2}& K_2 \ar[d]^{k_2}\ar@{>->}[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]_{h_2} \\G_0 && \ar@{>->}[ll]^{f'_0} D'_0 \ar[rr]_{g'_0}&& G'_1  && \ar@{>->}[ll]^{f'_1} D'_1 \ar[rr]_{g'_1}&& G_2 && \ar@{>->}[ll]^{f_2} D_2 \ar[rr]_{g_2}&& G_3 }\]
+
+	By \Cref{def:switch} we also know that $m_0=f'_0\circ a_1$ and $h_1=g'_1\circ a_0$. Now, let us switch $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$. In this case we obtain
+	\[\xymatrix@C=15pt{L_1\ar[d]^{f_0\circ i_1}&& K_1 \ar[d]_{k'_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){c_0}|(.29)\hole \ar[dr]|(.28)\hole_{h'_1} && L_2 \ar@/_.35cm/[dlll]^(.4){c_1} \ar[dl]|(.28)\hole^{f'_1\circ b_1}& K_2 \ar[d]^{k'_2}\ar@{>->}[l]_{l_2} \ar[r]^{r_2} & R_2 \ar[dr]|(.28)\hole_{h'_2} \ar@/^.35cm/[drrr]_(.4){d_0}|(.29)\hole  && L_0 \ar@/_.35cm/[dlll]^(.4){d_1} \ar[dl]|(.28)\hole^{\hat{m}_0}& K_0 \ar[d]^{\hat{k}_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]_{g_2\circ b_0} \\G_0 && \ar@{>->}[ll]^{f'_0} D'_0 \ar[rr]_{g'_0}&& G'_1  && \ar@{>->}[ll]^{\hat{f}_1} \hat{D}_1 \ar[rr]_{\hat{g}_1}&& G'_2 && \ar@{>->}[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 }\]
+	Using again the definition of switch, we know that $m'_0=\hat{f}_1\circ d_1$ and $h_2=g'_2\circ d_0$.
+Moreover, by hypothesis $(\X, \R)$ is well-switching and the hypothesis of the second point of \Cref{lem:indep-global-left} are satisfied by $\der{D}$.
+Thus we can characterise $c_0\colon R_1\to \hat{D}_1$ and $c_1\colon L_2\to D'_0$ as the unique arrows fitting in the diagrams below, where the bottom squares are pullbacks
+	\[\xymatrix@R=15pt@C=15pt{&&R_1 \ar@/_1.2cm/[dddl]_(.4){a_0}|(.63)\hole\ar[dl]^{j_0}\ar[dd]^{c'_0} \ar@{>}[dr]^{c_0}&&&&&L_2 \ar[dl]^{j_1} \ar@/_1.2cm/[dddl]_(.4){z_1}|(.63)\hole\ar[dd]^{c'_1} \ar@{>}[dr]^{c_1}\\&D_2 \ar@{>->}[dl]^(.4){f_2}&&\hat{D}_1 \ar[dr]^{\hat{g}_1}  &&&D_1 \ar@{>->}[dl]^(.4){f_1}&&D'_0 \ar[dr]^{g'_0}\\G_2 && P\ar[dr]_{p_4} \ar@{>->}[ur]_{p_3}\ar@{>->}[dl]^{p_1} \ar[ul]^{p_2}&&G'_2&G_1 && Q\ar[dr]_{q_4} \ar@{>->}[ur]_{q_3}\ar@{>->}[dl]^{q_1} \ar[ul]^{q_2}&&G'_1\\& D'_1 \ar[ul]^{g'_1}&&D'_2 \ar@{>->}[ur]_{f'_2}&&& D_0 \ar[ul]^{g_0}&&D'_1 \ar@{>->}[ur]_{f'_1}}\]
+
+	Finally, we switch the first two direct derivations
+	\[\xymatrix@C=15pt{L_2\ar[d]^{f'_0\circ c_1}&& K_2 \ar[d]_{\hat{k}_2}\ar@{>->}[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){e_0}|(.29)\hole \ar[dr]|(.28)\hole_{\hat{h}_2} && L_1 \ar@/_.35cm/[dlll]^(.4){e_1} \ar[dl]|(.28)\hole^{\hat{m}_1}& K_1 \ar[d]^{\hat{k}_1}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){t_0}|(.29)\hole \ar[dr]|(.28)\hole_{\hat{g}_1\circ c_0}   && L_0  \ar[dl]|(.28)\hole^{\hat{m}_0} \ar@/_.35cm/[dlll]^(.4){t_1}& K_0 \ar[d]^{\hat{k}_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]_{g_2\circ b_0} \\G_0 && \ar@{>->}[ll]^{\hat{f}_0} \hat{D}_0 \ar[rr]_{\hat{g}_0}&& \hat{G}_1  && \ar@{>->}[ll]^{\tilde{f}_1} \tilde{D}_1 \ar[rr]_{\tilde{g}_1}&& G'_2 && \ar@{>->}[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 }\]
+	As before, we have identities $f_0\circ i_1=\hat{f}_0\circ e_1$ and $h'_2=\tilde{g}_1\circ e_0$.
+Now, the derivation $S_{i_0, i_1}(\dder{D}_1)\cdot S_{i_0, i_1}(\dder{D}_0)\cdot \dder{D}_2$ satisfies the hypothesis of the first point of \Cref{lem:indep-global-left}.
+Thus, since there is at most one independence pair between two direct derivations, we know that  $t_0\colon R_1\to \tilde{D}_1$ and $t_1\colon L_0\to D'_2$  fit in
+	\[\xymatrix{&R_1 \ar[dl]_{a_0} \ar@{>}[dr]^{t_0} \ar@/^.4cm/[dd]|\hole^(.6){c_0}\ar[d]_{t'_0}&&L_ 0\ar[d]_{d_1} \ar@/_.4cm/[ddrr]|(.41)\hole_(.7){a_1}\ar[drr]^{t'_1} \ar@{>}[rr]^{t_1}&&\tilde{D}_1 \ar@{>->}[r]^{\tilde{f}_1}&\hat{G}_1\\ D'_1 \ar@{>->}[d]_{f'_1}&P\ar@{>->}[d]_{p_3} \ar[r]^{p_4} \ar@{>->}[l]_{p_1}&D'_2\ar@{>->}[d]^{f'_2}&\hat{D}_1 \ar@{>->}[d]_{\hat{f}_1}&&S\ar@{>->}[r]_{s_4} \ar[u]_{s_3}\ar@{>->}[d]^{s_1} \ar[ll]_{s_2} &\hat{D}_0 \ar[u]_{\hat{g}_0} \ar@{>->}[d]^{\hat{f}_0}\\G'_1&\hat{D}_1 \ar@{>->}[l]^{\hat{f}_1}\ar[r]_{\hat{g}_1}& G'_2&G'_1 && D'_0 \ar[ll]^{g'_0}  \ar@{>->}[r]_{f'_0}& G_0 }\]
+
+	\smallskip \noindent Second sequence of switches.
+
+	This time we start switching $\dder{D}_1$ and $\dder{D}_2$.
+	\[\xymatrix@C=15pt{L_0\ar[d]^{m_0}&& K_0 \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]_(.4){z_0}|(.29)\hole \ar[dr]|(.28)\hole_{h_0} && L_2 \ar@/_.35cm/[dlll]^(.4){z_1} \ar[dl]|(.28)\hole^{f_1\circ j_1}& K_2 \ar[d]^{\check{k}_2}\ar@{>->}[l]_{l_2} \ar[r]^{r_2} & R_2 \ar[dr]|(.28)\hole_{\check{h}_2} \ar@/^.35cm/[drrr]_(.4){w_0}|(.29)\hole  && L_1 \ar@/_.35cm/[dlll]^(.4){w_1} \ar[dl]|(.28)\hole^{\check{m}_1}& K_1 \ar[d]^{\check{k}_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} && R_1\ar[d]_{g_2\circ j_0} \\G_0 && \ar@{>->}[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar@{>->}[ll]^{\check{f}_1} \check{D}_1 \ar[rr]_{\check{g}_1}&& \check{G}_2 && \ar@{>->}[ll]^{\check{f}_2} \check{D}_2 \ar[rr]_{\check{g}_2}&& G_3 }\]
+	As in the previous case, we already know that $m_1=\check{f}_1\circ w_1$ and $h_2=\check{g}_2\circ w_0$.
+
+	Next, we switch $\dder{D}_0$ and $S_{j_0, j_1}(\dder{D}_2)$ getting
+	\[\xymatrix@C=15pt{L_2\ar[d]^{f_0\circ z_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar@{>->}[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){y_0}|(.29)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_0 \ar@/_.35cm/[dlll]^(.4){y_1} \ar[dl]|(.28)\hole^{\check{m}_0}& K_0 \ar[d]^{\check{k}_0}\ar@{>->}[l]_{l_0} \ar[r]^{r_0} & R_0 \ar[dr]|(.28)\hole_{\check{g}_1\circ z_0} \ar@/^.35cm/[drrr]_(.4){x_0}|(.29)\hole  && L_1 \ar@/_.35cm/[dlll]^(.4){x_1} \ar[dl]|(.28)\hole^{\check{m}_1}& K_1 \ar[d]^{\check{k}_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} && R_1\ar[d]_{g_2\circ j_0} \\G_0 && \ar@{>->}[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar@{>->}[ll]^{\mathring{f}_1} \mathring{D}_1 \ar[rr]_{\mathring{g}_1}&& \check{G}_2 && \ar@{>->}[ll]^{\check{f}_2} \check{D}_2 \ar[rr]_{\check{g}_2}&& G_3 }\]
+	The usual identities $m_0=\check{f}_0\circ y_1$, $\check{h}_2=\mathring{g}_1\circ y_0$ hold.
+But the really important thing to notice is that the first match of these derivation coincide with $f'_0\circ c_1$
+	\[	f_0'\circ c_1  =f'_0\circ q_3\circ c'_1 =f_0\circ q_1\circ c'_1=f_0\circ z_1\]
+
+	Moreover, we can characterise the pair $(x_0, x_1)$.
+If we apply the first point of \Cref{lem:indep-global-left} to $\dder{D}$ we get an independence pair between the last two steps of the derivation above, which, since $(\X, \R)$ is well-switching, must coincide with $(x_0, x_1)$.
+Thus we have two diagrams
+
+	\[\xymatrix{&R_0 \ar[dl]_{i_0} \ar@{>}[dr]^{x_0} \ar@/^.4cm/[dd]|\hole^(.6){z_0}\ar[d]_{x'_0}&&L_ 1\ar[d]_{w_1} \ar@/_.4cm/[ddrr]|(.41)\hole_(.7){i_1}\ar[drr]^{x'_1} \ar@{>}[rr]^{x_1}&&\mathring{D}_1 \ar@{>->}[r]^{\mathring{f}_1}&\check{G}_1\\ D_1 \ar@{>->}[d]_{f_1}&P'\ar@{>->}[d]_{p'_3} \ar[r]^{p'_4} \ar@{>->}[l]_{p'_1}&\check{D}_2\ar@{>->}[d]^{\check{f}_2}&\check{D}_1 \ar@{>->}[d]_{\check{f}_1}&&S'\ar@{>->}[r]_{s'_4} \ar[u]_{s'_3}\ar@{>->}[d]^{s'_1} \ar[ll]_{s'_2} &\check{D}_0 \ar[u]_{\check{g}_0} \ar@{>->}[d]^{\check{f}_0}\\G_1&\check{D}_1 \ar@{>->}[l]^{\check{f}_1}\ar[r]_{\check{g}_1}& \check{G}_2&G_1 && D_0 \ar[ll]^{g_0}  \ar@{>->}[r]_{f_0}& G_0 }\]
+	From this diagram we can recover another identity. Notice that, if $p'_2\colon P'\to D_2$ is the last projection from $P'$, then
+	\[f_2\circ p'_2\circ x'_0=g_1\circ p'_1\circ x'_0=g_1\circ i_0=f_2\circ b_0\]
+	Implying, since $f_2$ is mono, that $p'_2\circ x'_0=b_0$. From this, we can also deduce that 
+	\[\check{g}_2\circ x_0=\check{g}_2\circ p'_4\circ x'_0=g_2\circ p'_2\circ x'_0=g_2\circ b_0 \]
+
+	Finally, switching the second and the third step we get
+	\[\xymatrix@C=15pt{L_2\ar[d]^{f_0\circ z_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar@{>->}[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){v_0}|(.29)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_1 \ar@/_.35cm/[dlll]^(.4){v_1} \ar[dl]|(.28)\hole^{\mathring{f}_1 \circ x_1}& K_1 \ar[d]^{\mathring{k}_1}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){u_0}|(.29)\hole\ar[dr]_{\check{h}_1}|(.28)\hole   && L_0 \ar@/_.35cm/[dlll]^(.4){u_1} \ar[dl]^{\mathring{m}_0}|(.28)\hole& K_0 \ar[d]^{\mathring{k}_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0\ar[d]_{\check{g}_2\circ x_0} \\G_0 && \ar[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar@{>->}[ll]^{\bar{f}_1} \bar{D}_1 \ar[rr]_{\bar{g}_1}&& \bar{G}_2 && \ar@{>->}[ll]^{\bar{f}_2} \bar{D}_2 \ar[rr]_{\bar{g}_2}&& G_3 }\]
+	As usual, this last switch brings identities $\check{m}_0=\bar{f}_1\circ u_1$ and $g_2\circ j_0=\bar{g}_2\circ u_0$.
+Applying the second point of \Cref{lem:indep-global-left} to $\dder{D}_0\cdot S_{j_0, j_1}(\dder{D}_2)\cdot S_{j_0, j_1}(\dder{D}_1)$ and the fact that $(\X, \R)$ is well-switching we get the following diagrams
+	\[\xymatrix@R=15pt@C=15pt{&&R_2 \ar@/_1.2cm/[dddl]_(.4){y_0}|(.63)\hole\ar[dl]^{w_0}\ar[dd]^{v'_0} \ar@{>}[dr]^{v_0}&&&&&L_1 \ar[dl]^{w_1} \ar@/_1.2cm/[dddl]_(.4){i_1}|(.63)\hole\ar[dd]^{v'_1} \ar@{>}[dr]^{v_1}\\&\check{D}_2 \ar@{>->}[dl]^(.4){\check{f}_2}&&\bar{D}_1 \ar[dr]^{\bar{g}_1}  &&&\check{D}_1 \ar@{>->}[dl]^(.4){\check{f}_1}&&\check{D}_0 \ar[dr]^{\check{g}_0}\\\check{G}_2 && \bar{P}\ar[dr]_{\bar{p}_4} \ar@{>->}[ur]_{\bar{p}_3}\ar@{>->}[dl]^{\bar{p}_1} \ar[ul]^{\bar{p}_2}&&\bar{G}_2&G_1 && \bar{Q}\ar[dr]_{\bar{q}_4} \ar@{>->}[ur]_{\bar{q}_3}\ar@{>->}[dl]^{\bar{q}_1} \ar[ul]^{\bar{q}_2}&&\check{G}_1\\& \mathring{D}_1 \ar[ul]^{\mathring{g}_1}&&\bar{D}_2 \ar@{>->}[ur]_{\bar{f}_2}&&& D_0 \ar[ul]^{g_0}&&\mathring{D}_1 \ar@{>->}[ur]_{\mathring{f}_1}}\]
+
+	We have to build the dotted arrows in the diagram below
+	\[\xymatrix@C=15pt@R=30pt{G_0 && \ar@{>->}[ll]_{\hat{f}_0} \hat{D}_0 \ar[rr]^{\hat{g}_0}&& \hat{G}_1  && \ar@{>->}[ll]_{\tilde{f}_1} \tilde{D}_1 \ar[rr]^{\tilde{g}_1}&& G'_2 && \ar@{>->}[ll]_{f'_2} D'_2 \ar[rr]^{g'_2}&& G_3 \\
+		L_2\ar[d]^{f_0\circ z_1} \ar[u]_{f'_0\circ c_1}&& K_2 \ar[u]^{\hat{k}_2}\ar[d]_{\mathring{k}_2}\ar@{>->}[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/_.35cm/[urrr]^(.4){e_0}|(.29)\hole \ar[ur]|(.28)\hole^{\hat{h}_2} \ar@/^.35cm/[drrr]_(.4){v_0}|(.29)\hole \ar@/_.2cm/[dr]|(.28)\hole_{\mathring{h}_2} && L_1 \ar@/^.35cm/[ulll]_(.4){e_1} \ar[ul]|(.28)\hole_{\hat{m}_1} \ar@/_.35cm/[dlll]^(.4){v_1} \ar[dl]|(.28)\hole^{\mathring{f}_1 \circ x_1}& K_1  \ar[u]_{\hat{k}_1}\ar[d]^{\mathring{k}_1}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){u_0}|(.29)\hole\ar@/_.2cm/[dr]_{\check{h}_1}|(.28)\hole \ar@/_.35cm/[urrr]^(.4){t_0}|(.29)\hole \ar[ur]|(.28)\hole^{\hat{g}_1\circ c_0}  && L_0\ar[ul]|(.28)\hole_{\hat{m}_0} \ar@/^.35cm/[ulll]_(.4){t_1} \ar@/_.35cm/[dlll]^(.4){u_1} \ar[dl]^{\mathring{m}_0}& K_0 \ar[d]_{\mathring{k}_0}\ar[u]^{\hat{k}_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[u]^{g_2\circ b_0}\ar[d]_{\check{g}_2\circ x_0} \\G_0 \ar@/^.3cm/[uu]^{\id{G_0}}&& \ar@{>->}[ll]^{\check{f}_0} \check{D}_0 \ar@{.>}@/_.3cm/[uu]_(.3){\phi_{0}}|\hole  \ar[rr]_{\check{g}_0}&& \check{G}_1  \ar@{.>}@/_.0cm/[uu]^(.2){\psi_{1}}|(.43)\hole |(.57)\hole  && \ar@{>->}[ll]^{\bar{f}_1} \bar{D}_1 \ar@{.>}@/^.3cm/[uu]^(.3){\phi_{1}}|\hole \ar[rr]_{\bar{g}_1}&& \bar{G}_2 \ar@{.>}@/_.0cm/[uu]^(.2){\psi_{2}}|(.43)\hole |(.57)\hole && \ar@{>->}[ll]^{\bar{f}_2} \ar@{.>}@/_.4cm/[uu]_(.3){\phi_{2}}|\hole \bar{D}_2 \ar[rr]_{\bar{g}_2}&& G_3 \ar@{.>}@/_.3cm/[uu]_{\psi_{3}} }\]
+
+	Now, we have already proved that $f_0\circ z_1=f'_0\circ c_1$, thus by \Cref{prop:unique} we have isomorphisms $\phi_{0}\colon \check{D}_0\to \hat{D}_0$ and $\psi_{1}\colon \check{G}_1\to \hat{G}_1$.
+	Notice that
+	\[
+	\hat{f}_0\circ \phi_{0}\circ v_1  = \check{f}_0\circ v_1 =\check{f}_0\circ \check{q}_3\circ v'_1=f_0\circ \check{q}_1\circ v'_1=f_0\circ i_1=\hat{f}_0\circ e_1\]
+	Thus, using the fact that $\hat{f}_0$ is mono, we can conclude that $\phi_0\circ v_1=e_1$. Thus we have
+	\[\psi_1\circ \mathring{f}\circ x_1=\psi_1\circ \check{g}_0\circ v_1= \hat{g}_0\circ \phi_0\circ v_1=\hat{g}_0\circ e_1=\hat{m}_1 \]
+	\Cref{prop:unique} now yields the $\phi_1\colon \bar{D}_1\to\tilde{D}_1$ and $\psi_2\colon \bar{G}_2\to G'_2$.  We can compute to get
+	\[
+	\tilde{f}_1\circ \phi_1\circ v_0=\psi_1\circ \bar{f}_1\circ v_0=\psi_1\circ \mathring{h}_2=\hat{h}_2=\tilde{f}_1\circ e_0\]
+	Hence $\phi_1\circ v_0=e_0$. On the other hand, notice that
+	\[\hat{f}_0\circ s_4\circ t'_1=f'_0\circ s_1\circ t'_1=f'_0\circ a_1=m_0=\check{f}\circ y_1=\hat{f}_0\circ \phi_0\circ y_1\]
+	Yielding $s_4\circ t'_1=\phi_0\circ y_1$. But then
+	\begin{align*}
+		&\tilde{f}_1\circ \phi_1\circ u_1=\psi_1\circ \bar{f}_1\circ u_1=\psi_1\circ \check{m}_0= \psi_1\circ \check{g}_0\circ y_1\\=&\hat{g}_0\circ \phi_0\circ y_1=\hat{g}_0\circ s_4\circ t'_1=\tilde{f}_1\circ s_3\circ t'_1=\tilde{f}_1\circ t_1
+	\end{align*}
+
+	In turn, the previous identity entails that
+	\[\psi_2\circ \mathring{m}_0=\psi_2\circ \bar{g}_1\circ u_1 = \tilde{g}_1\circ \phi_1\circ u_1 = \tilde{g}_1\circ t_1=\hat{m}_0\]
+
+	We can use \Cref{prop:unique} a third time to get $\phi_2\colon \bar{D}_2\to D'_2$ and $\psi_3\colon G_3\to G_3$.  Now, as a last computation, we have
+	\[f'_2\circ t_0= \hat{g}_2\circ c_0=\psi_2\circ h_1=\psi_2\circ \bar{f}_2\circ u_0=f'_2\circ \phi_2\circ u_0\]
+	Therefore $\phi_2\circ u_0=t_0$ and this concludes the proof.
+
+	Since
+
+\end{proof}
+
 \end{document}

### 2024-11-14 arxiv_concur/main.tex

@@
   \noindent
-  (2) $j<i-1$ or $j>i-1$\\
+  (2) $j<i-1$ or $j>i+1$\\
   %
@@
   Recall that $\der{D}_0 \shift{\nu_1} \der{D}_1$ and, given the
-  working assumption (ii), the switches $\nu_1$ and $\transp{i}$ can
+  working assumption (2), the switches $\nu_1$ and $\transp{i}$ can
   be done in reverse order, thus getting, as desired
@@
 
-  By Lemma~\ref{lem:indep-global-left}(\ref{lem:indep-global-left:1})
+  By Lemma~\ref{lem:indep-global-left}(\ref{lem:indep-global-left:1}) and (\ref{lem:indep-global-left:2})
   we can reorganise the first three switchings as

### 2024-11-14 full_version/adhesivity.tex
full version che compila in un tempo normale

\chapter{$\mathcal{M}$-adhesive categories}

This first section is devoted to recall the definition and the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive}.

\begin{notation} 
We stipulate here some notational conventions which will be used throughout this paper. 
\begin{itemize}\item 
	Given a category $\X$ we will not distinguish notationally between $\X$ and its class of objects: so that ``$X\in \X$'' means that $X$ belongs to the class of objects of $\X$.  
	\item 
	If $1$ is a terminal object in a category $\X$,  the unique arrow $X\to 1$ from another object $X$ will be denoted by $!_X$. Similarly, if $0$ is initial in $\X$ then $?_X$ will denote the unique arrow $0\to X$. %When $\X$ is $\Set$ and $1$ is a singleton, $\delta_x$ will denote the arrow $1\to X$ with value $x\in X$.
	\item  $\mor(\X)$, $\mon(\X)$ and $\reg(\X)$ will denote the class of all arrows, monos and regular monos of $\X$, respectively.

	\item Given an integer $n\in \mathbb{Z}$, $[0,n]$ will denote the set
	\[[0,n]:=\{x\in \mathbb{N}\mid x\leq n\}\] 
	Indeed, if $n<0$, then $[0,n]=\emptyset$.
\end{itemize}
\end{notation}

\section{The Van Kampen property}
The key property that $\mathcal{M}$-adhesive categories enjoy is given by  the so-called \emph{Van Kampen condition} \cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive}. We will recall it and examine some of its consequences. First of all we need to recall some terminology and facts regarding subclasses of $\mor(\X)$.

\begin{definition}
	Let $\X$ be a category and $\mathcal{A}$ a  subclass of $\mor(\X)$. We say that  $\mathcal{A}$ is
	\begin{itemize}
		\item 
		\emph{stable under pushouts (pullbacks)} if for every pushout (pullbacks) square 
		\[\xymatrix{A\ar[r]^f  \ar[d]_{m}& B \ar[d]^n \\ C \ar[r]_g & D}\]
		if $m \in \mathcal{A}$ ($n\in \mathcal{A}$) then $n \in \mathcal{A}$ ($m \in \mathcal{A}$);
		\item \emph{closed under composition} if $g, f\in \mathcal{A}$ implies $g\circ f\in \mathcal{A}$ whenever $g$ and $f$ are composable;
		\item \emph{closed under decomposition} if $g\circ f, g\in \mathcal{A}$ implies $f\in \mathcal{A}$.
	\end{itemize}
\end{definition}

\begin{remark}In the previous definition, ``decomposition'' corresponds to ``left cancellation'', but we prefer to stick to the name commonly used in literature (see e.g.~\cite{habel2012mathcal}).
\end{remark}

So equipped, we can introduce the notion of \emph{$\mathcal{A}$-Van Kampen square}.
\begin{definition}[Van Kampen property] Let $\X$ be a category  and consider the two diagrams below
	\[\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{f}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{g} &&D&&C \ar[rr]_{g} & & D}\]

	Given  a class of arrows $\mathcal{A}\subseteq \mor(\X)$, we say that the left square \emph{has the Van Kampen property relatively to $\mathcal{A}$}, or that it  is a \emph{$\mathcal{A}$-Van Kampen square} if:
	\begin{enumerate}
		\item is a pushout square;
		\item 	whenever the right cube has pullbacks as back and left faces and the vertical arrows belong to $\mathcal{A}$, then its top face is a pushout if and only if the front and right faces are pullbacks.
	\end{enumerate}
	Pushout squares which enjoy the ``if'' half of the second point of the condition above are called \emph{$\mathcal{A}$-stable}.

We will call a $\mor(\X)$-Van Kampen ($\mor(\X)$-stable) square simply a \emph{Van Kampen} (\emph{stable}) square.
\end{definition}

Before proceeding further, we recall this classical result about pullbacks.

\begin{lemma}\label{lem:pb1}
	Let $\X$ be a category, and consider the following diagram 	in which the right square is a pullback.
	\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
	Then the whole rectangle is a pullback if and only if the left square is one.
\end{lemma}

The previous result can be dualised to get an analogous lemma for pushouts.

\begin{lemma}\label{lem:po1}
	Let $\X$ be a category, and consider the following diagram 	in which the left square is a pushout.
	\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
	Then the whole rectangle is a pushout if and only if the right square is one.
\end{lemma}

The following proposition establishes a key property of $\mathcal{A}$-Van Kampen squares with a mono as a side: they are not only pushouts, but also pullbacks.
\begin{proposition}\label{prop:pbpo} Let $\mathcal{A}$ be a class of arrows stable under pushouts and containing all the isomorphisms.  If $m\colon A\to C$ is mono and belongs to $\mathcal{A}$, then every $\mathcal{A}$-Van Kampen square
	\[\xymatrix{A\ar[r]^{g} \ar[d]_{m} & B \ar[d]^{n} \\ C \ar[r]_{f}  & D}\]
	is also a pullback square and $n$ is a monomorphism.
\end{proposition}
\begin{proof} We can start considering the cube below and noticing that $n$, being the pushout of $m\in \mathcal{M}$, belongs to $\mathcal{A}$ too.
	\[\xymatrix@C=13pt@R=13pt{&A\ar[dd]|\hole_(.65){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_{\id{B}} \\ A  \ar[dd]_{m}\ar[rr]^(.65){g} & & B \ar[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{f} & & D}\]
	By construction the top face of the cube is a pushout and the back one a pullback. The left face is a pullback because $m$ is mono. Thus the $\mathcal{A}$-Van Kampen property yields that the front and the right faces are pullbacks. 
\end{proof}

The previous proposition, in turn, allows us to establish the following results.
\begin{lemma}\label{lem:varie}Let $\mathcal{A}$ be a class of arrows stable under pullbacks, pushouts and containing all isomorphisms.  Suppose that, the left square below is $\mathcal{A}$-Van Kampen, while the vertical faces in the right cube are pullbacks.
		\[\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{g'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{g}&&B\ar[dd]^{n}&&C'  \ar@{.>}[dr]_{h} _{}\ar[dd]_{c}\ar[rr]^(.7){f'} & & D' \ar@{.>}[dr]^{k}\ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){g} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{f} &&D&&C \ar[rr]_{f} & & D}\]
Supppose, moreover that $m\colon A\to C$ and $d\colon D'\to D$ are mono and that $d$ belongs to $\mathcal{A}$. Then the dotted arrow  $k\colon D'\to B$ exists if and only if the other dotted arrow  $h\colon C'\to A$ exists too.
\end{lemma}

\begin{remark}
	Notice that, since $d$ is a mono and the vertical faces are pullbacks, then $a, b$ and $c$ are monomorphisms too. Moreover, $n$ is mono by \Cref{prop:pbpo}, so that even $m'$ and $n'$ are monos.
\end{remark}

\begin{proof}
	$(\Rightarrow)$ By hypothesis there exists $k:D'\to B$ such that $n\circ k = d$. By \Cref{prop:pbpo}, the bottom face of the cube is a pullback. Thus there exists a unique $h:C'\to A$ as in the diagram below, implying the thesis.
		\[\xymatrix@C=40pt{C'  \ar@{.>}[d]^{h}\ar[r]^{f'} \ar@/_.5cm/[dd]_{c}& D' \ar@/^.5cm/[dd]^{d}\ar[d]_{k}\\ A \ar[d]^{m} \ar[r]^{g} & B \ar[d]_{n} \\  C \ar[r]_f & D}\]

	\smallskip \noindent 
	$(\Leftarrow)$ Let $h:C\to A$ be such that $c=m\circ h$. By the $\mathcal{A}$-Van Kampen property the top face of the given cube is a pushout. Thus we get  the dotted $k:D'\to B$ in the following diagram exists.
		\[\xymatrix@C=40pt{A' \ar@/_.5cm/[dd]_{a} \ar[d]^{m'} \ar[r]^{g'} & B' \ar[d]_{n'} \ar@/^.5cm/[dd]^{b} \\  C' \ar[d]^{h} \ar[r]_{f'} & D' \ar@{.>}[d]_{k}\\ A \ar[r]_g& B }\]
Moreover, by construction we have
\[\begin{split}
n\circ k \circ n' &= n\circ b\\&=d\circ n'\\&\\&
\end{split} \qquad \begin{split}
n\circ k \circ f' &= n\circ g\circ h\\&=f\circ m\circ h\\&=f\circ c\\&= d\circ f' \end{split}\]
We can therefore conclude that $n\circ k =d$. \qedhere 
\end{proof}

Finally, we can show that $\mathcal{A}$-stable pushouts enjoy a kind of \emph{pullback-pushout decomposition} property.

\begin{proposition}\label{prop:stab}Let $\X$ be a category and $\mathcal{A}$ a class of arrows stable under pullbacks. Suppose that, in the diagram below, the whole rectangle is an $\mathcal{A}$-stable pushout and the right square a pullback.
	\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
	If the arrow $k$ is in $\mathcal{A}$ and it is a monomorphism,  then both squares are pushouts.
\end{proposition}

\begin{proof} We can begin noticing that $g$, being the pullback of $k$, is mono and in $\mathcal{A}$ too. Thus we can build the cube below, in which all the vertical faces are pullbacks, entailing that all the vertical arrows are in $\mathcal{A}$.
	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y  \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
	By hypothesis the face is an $\mathcal{A}$-stable pushout and so its top one is a pushout. Using \Cref{lem:po1} we can conclude that the right half of the rectangle with which we have started is a pushout too. \qedhere 
\end{proof}

\section{$\mathcal{M}$-adhesivity}

In this section we will define the notion of $\mathcal{M}$-adhesivity \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,heindel2009category,lack2005adhesive} and explore some of the consequence of such a property.

\begin{definition}[$\mathcal{M}$-adhesive category]
	Let $\X$ be a category and consider a subclass $\mathcal{M}$ of the class $\mon(\X)$ of monomorphisms such that:
	\begin{enumerate}
		\item $\mathcal{M}$ contains all isomorphisms and is closed under composition;
		\item $\mathcal{M}$ is stable under pullbacks and pushouts.
	\end{enumerate} 
	We will use $m\colon X\mto Y$ to denote that an arrow $m\colon X\to Y$ belongs to $\mathcal{M}$. $\X$ is said to be \emph{$\mathcal{M}$-adhesive} if
	\begin{enumerate}
		\item for every $m\colon X\mto Y$ in $\mathcal{M}$ and $g\colon Z\to Y$, a pullback square
		\[\xymatrix{P\ar[r]^p \ar@{>->}[d]_{n}& X \ar@{>->}[d]^{m}\\ Z \ar[r]_g& Y}\]
		exists, such pullbacks will be called \emph{$\mathcal{M}$-pullbacks};
		\item for every $m\colon X\mto Y$ in $\mathcal{M}$ and $f\colon X\to Z$, a pushout square
		\[\xymatrix{X \ar[r]^f \ar@{>->}[d]_{m}& Z \ar[d]^{q}\\ Y\ar[r]_p &Q}\]
		exists, such pushouts  will be called \emph{$\mathcal{M}$-pushouts}; 
		\item  $\mathcal{M}$-pushouts are $\mathcal{M}$-Van Kampen squares.
	\end{enumerate}

A category $\X$ is said to be \emph{strictly $\mathcal{M}$-adhesive} if $\mathcal{M}$-pushouts are Van Kampen squares.	
\end{definition}

\begin{remark}\label{rem:diff}Our notion of $\mathcal{M}$-adhesivity follows \cite{ehrig2012,ehrig2014adhesive} and is different from the one of \cite{azzi2019essence}. What is called $\mathcal{M}$-adhesivity in that paper corresponds to our strict $\mathcal{M}$-adhesivity. Moreover, in \cite{azzi2019essence} the class $\mathcal{M}$ is assumed to be only stable under pullbacks. However, if $\mathcal{M}$ contains all split monos, then stability under pushouts can be deduced from the other axioms \cite[Prop.~$5.1.21$]{castelnovo2023thesis}.
\end{remark}

\begin{remark}\label{rem:salva} 
	\emph{Adhesivity} and \emph{quasiadhesivity} as defined in \cite{lack2005adhesive,garner2012axioms}  coincide with  strict $\mon(\X) $-adhesivity and strict $\reg(\X)$-adhesivity, respectively. 
\end{remark}

\begin{remark}\label{rem:pb}
	Let $X$ be an object of $\X$, with $\X$ an $\mathcal{M}$-adhesive. category We can consider  the full subcategory $\mathcal{M}/X$ of $\X/X$ made by arrows in $\mathcal{M}$. Since $\X$ has all $\mathcal{M}$-pullbacks, for every arrow $f\colon X\to Y$ we have a functor $f^*\colon \mathcal{M}/Y\to \mathcal{M}/X $ sending $m\colon M \mto X$ to a chosen pullback of it along $f$.
	\end{remark}

A first result we can prove regards closure under decomposition of $\mathcal{M}$.

\begin{proposition}\label{prop:deco}Let  $\mathcal{A}$ be a class of arrows stable under pullbacks. For every arrow $f\colon X\to Y$ and monomorphism $m\colon Y\to Z$, if $m\circ f \in\mathcal{A}$ then $f\in \mathcal{A}$.
\end{proposition}
\begin{proof}Take the diagram
	\[\xymatrix{X \ar[d]_{\id{X}}\ar[r]^{f}& Y \ar[r]^{\id{Y}}  \ar[d]_{\id{Y}}& Y \ar[d]^{m}\\
		X \ar[r]_{f}& Y \ar[r]_{m} & Z}\]
	Since $m$ is mono the right square is a pullback, while the left square is a pullback by construction. By \Cref{lem:pb1} the whole rectangle is a pullback and the thesis follows.
\end{proof}
\begin{corollary}\label{cor:deco}
	In every $\mathcal{M}$-adhesive category $\X$, the class $\mathcal{M}$ is closed under decomposition.
\end{corollary}

Another result which can be immediately established, with the aid of \Cref{prop:pbpo}, is the following one.
\begin{proposition}\label{prop:pbpoad}
	Let $\X$ be an $\mathcal{M}$-adhesive category. Then $\mathcal{M}$-pushouts are also pullback squares.
\end{proposition}

From \Cref{prop:pbpoad}, in turn, we can derive the following corollaries.
\begin{corollary}\label{cor:rego}
	In a $\mathcal{M}$-adhesive category $\X$, every $m\in\mathcal{M}$ is a regular mono.
\end{corollary}
\begin{proof}
Let $m$ be an element of $\mathcal{M}$ and consider its pushout along itself.
\[\xymatrix{X\ar@{>->}[r]^m \ar@{>->}[d]_m& Y\ar@{>->}[d]^{f}\\Y \ar@{>->}[r]_g & Z}\]
By \Cref{prop:pbpoad} this square is a pullback, proving that $m$ is the equalizer of the arrows $f,g\colon Y\rightrightarrows Z$. \qedhere 
\end{proof}

The following result now follows at once noticing that a regular monomorphism which is also epic is automatically an isomorphism.

\begin{corollary}\label{prop:bal}
If $\X$ is an $\mathcal{M}$-adhesive categories, then every epimorphisms in $\mathcal{M}$ is an isomorphisms. In particular, every adhesive category $\X$ is \emph{balanced}: if a morphism is monic and epic, then it is an isomorphism.
\end{corollary}

$\mathcal{M}$-adhesivity is well-behaved with respect to  the comma construction \cite{mac2013categories}, as shown by the following theorem.
\begin{theorem}[\cite{ehrig2006fundamentals,lack2005adhesive}]\label{lem:comma}
	Let $\A$ and $\B$ be respectively an $\mathcal{M}$-adhesive and an $\mathcal{M}'$-adhesive category. Let also $L:\A\rightarrow \C$ be a functor that preserves $\mathcal{M}$-pushouts, and  $R:\B\rightarrow \C$ be a functor which preserves pullbacks.Then $\comma{L}{R}$ is $\cma{M}{M'}$-adhesive, where 
	\[
	\cma{M}{M}':=\{(h,k)\in \mathcal{A}(\comma{L}{R}) \mid h\in \mathcal{M}, k\in \mathcal{M}'\}\]
\end{theorem}

In particular, we can apply this result to slices over and under a given object.

\begin{corollary}\label{cor:slice}
	Let  $X$ be an object of an $\mathcal{M}$-adhesive category $\X$. Then  $\X/X$ and $X/\X$ are, respectively, $\mathcal{M}_X$- and $\mathcal{M}^X$-adhesive, where
	\[\mathcal{M}_X:=\{m\in  \mathcal{A}(\X/X) \mid m\in \mathcal{M} \} \qquad \mathcal{M}^X:=\{m\in  \mathcal{A}(X/\X) \mid m\in \mathcal{M} \}\]
\end{corollary}

Another categorical construction which preserves $\mathcal{M}$-adhesivity property is the formation of the category of functors.

\begin{theorem}[\cite{ehrig2006fundamentals,lack2005adhesive}]\label{thm:functors}
If $\X$ is an $\mathcal{M}$-adhesive category, then for every small category $\Y$, the category $\X^\Y$  of functors $\Y\to \X$ is $\mathcal{M}^{\Y}$-adhesive, where
\[\mathcal{M}^{\Y}:=\{\eta \in \mathcal{A}(\X^\Y) \mid \eta_Y \in \mathcal{M} \text{ for every } Y\in \Y\}\]
\end{theorem}

We can list various examples of $\mathcal{M}$-adhesive categories (see \cite{castelnovo2023thesis,CastelnovoGM22,lack2006toposes}).

\begin{example}\todo{Topos, ipergrafi e grafi}
\end{example}

\begin{example}
	\todo{grafi semplici}
\end{example}

\begin{example}\todo{GRAFI GERARCHICI}
\end{example}

\begin{example}\todo{term graph}
\end{example}

We end this section proving a useful property of $\mathcal{M}$-adhesive categories:  $\mathcal{M}$-pushout-pullback decomposition.

\begin{lemma}[$\mathcal{M}$-pushout-pullback decomposition]\label{lem:popb} Let $\X$ be an $\mathcal{M}$-adhesive category  and suppose that, in the diagram below, the whole rectangle is a pushout and the right square a pullback.
\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
	Then the following statements hold true:
	\begin{enumerate}
\item if $a$ belongs to $\mathcal{M}$ and $k$ is a monomorphism,  then both squares are pushouts and pullbacks;
\item if $f$ and $k $ are in  $\mathcal{M}$, then both squares are pushouts and pullbacks.
	\end{enumerate}
\end{lemma}
\begin{proof}
\begin{enumerate}
	\item By \Cref{prop:stab}, it follows that both squares are pushouts, thus the thesis follows from \Cref{prop:pbpoad}.
	\item By hypothesis, $g$ is the pullback of an arrow in $\mathcal{M}$, thus it belongs to it. But then $g\circ f\in \mathcal{M}$ too  and the whole rectangle is a $\mathcal{M}$-pushout. Therefore, by \Cref{prop:pbpoad} a pullback, so that its left half is a pullback too, by \Cref{prop:pbpo}. Moreover $k\circ h$ is in $\mathcal{M}$ as the pushout of $g\circ f$ and, by \Cref{cor:deco}, we also know that $h\in \mathcal{M}$.

	Using \Cref{lem:po1}, it is enough to show that the left half of the original rectangle is a pushout. We can build the following cube:
	\[\xymatrix@C=20pt@R=10pt{ & &X\ar@{>->}[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar@{>->}[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar@{>->}[ddd]_{g} \ar[rrr]^{b}&&& B\ar@{>->}[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar@{>->}[dl]_{f}&&& A \ar@{>->}[dl]^{h}\\ & Y \ar[rrr]|(.67)\hole^{b} \ar@{>->}[dl]_{g}&&& B \ar@{>->}[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
	Its vertical faces are all pullbacks and all the vertical arrows are in $\mathcal{M}$, hence the top face is a pushout and we can conclude. \qedhere 
\end{enumerate}
\end{proof}

\subsubsection{Pushout complements}

We turn now to the exam of the notion of \emph{pushout complement}. We will prove that, in an $\mathcal{M}$-adhesive category $\X$ certain pushout complements are unique and are \emph{final pullbacks complements} in the sense of \cite{dyckhoff1987exponentiable,corradini2006sesqui}.

\begin{definition}[Pushout complement]
Let $f\colon X\to Y$ and $g\colon Y\to Z$ be two composable arrows in a category $\X$. A \emph{pushout complement} for the composable pair $(f,g)$ is a pair $(h,k)$ with $h\colon X\to W$ and $k\colon W\to Z$ such that the square below commutes and it is a pushout.
\[\xymatrix{X \ar[r]^{f} \ar[d]_{h}& Y \ar[d]^{g} \\ W \ar[r]_{k}& Z}\]
\end{definition}

\begin{example}
	In a generic category $\X$, pushout complements may not exist: in $\Set$ the arrows $?_{2}\colon \emptyset \to 2$ and $!_2\colon 2\to 1$ do not have a pushout complement.

	Moreover, composable arrows $f\colon X\to Y$ and $g\colon Y\to Z$ may have  pushout complements which are non-isomorphic: for instance, in $\Set$ the two squares below are both pushouts.

	\[\xymatrix{2 \ar[r]^{!_2} \ar[d]_{\id{2}}& 1 \ar[d]^{\id{1}} & 2 \ar[r]^{!_2} \ar[d]_{!_2}& 1 \ar[d]^{\id{1}}\\ 2 \ar[r]_{!_2}& 1 & 1 \ar[r]_{\id{1}}& 1}\]
\end{example}

In an $\mathcal{M}$-adhesive category we can approach pushout complements in a more abstract way, using the pullback functor of \Cref{rem:pb}.

\begin{definition}
Let $F\colon \X \to \Y$ be a functor and $Y$ an object of $\Y$. We say that $F$ has a \emph{partial right adjoint at $Y$} if there exists an object $G(Y)$ in $\X$ and an arrow $\epsilon_Y\colon F(G(Y))\to Y$ such that, for every  $f\colon F(X)\to Y$ there exists a unique $g\colon X\to G(Y)$ making the diagram below commutative.
\[\xymatrix@C=15pt{F(X) \ar[rr]^{F(g)} \ar[dr]_{f}&&F(G(Y)) \ar[dl]^{\epsilon_Y}\\ & Y}\]
\end{definition}

\begin{remark}
	It is immediate to see that $F$ is a left adjoint if and only if it has a partial right adjoint at every $Y\in \Y$.
\end{remark}

We can prove two  useful properties of partial right adjoints.

\begin{proposition}\label{prop:uni}
	Let $F\colon \X\to \Y$ be a functor and suppose that it has a partial right adjoint $(G(Y), \epsilon_Y)$ at $Y$. Then the following hold true:
	\begin{enumerate}
\item there is a natural isomorphism $\psi\colon \X(-, G(Y))\to \Y(F(-), Y)$;
\item if $(G'(Y), \epsilon'_Y)$ is another partial right adjoint to $F$ at $Y$, then there exists a unique isomorphism $\phi_Y\colon G(Y)\to G'(Y)$ such that the diagram below commutes.
\[\xymatrix@C=15pt{F(G(Y)) \ar[rr]^{F(\phi_Y)} \ar[dr]_{\epsilon_Y} & &F(G'(Y)) \ar[dl]^{\epsilon'_Y}\\ & Y}\]
	\end{enumerate}
\end{proposition}
\begin{proof}
	\begin{enumerate}
		\item Given an object $X$ of $\X$ we can define $\phi_X$ putting
		\begin{align*}
			\phi_X \colon \X(X, G(Y))&\to \Y(F(X), Y)\\
			g&\mapsto \epsilon_Y\circ F(g)
		\end{align*}
		By definition of partial right adjoint $\phi_X$ is a bijection. Consider now an arrow $f\colon X_1\to X_2$, then, for every $g\colon X_2\to G(Y)$ we have:
		\begin{align*}
			\phi_X(g)\circ F(f)&=\epsilon_Y\circ F(g)\circ F(f)\\&= \epsilon_Y\circ F(g\circ f)\\&=\phi_X(g\circ f)
		\end{align*}
		Naturality now follows at once.

		\item Let $\phi_Y\colon G(Y)\to G'(Y)$ and $\phi'_Y\colon G(Y)\to G'(Y)$ be the unique arrows making the diagram below commutative.
\[\xymatrix@C=15pt{F(G(Y)) \ar[rr]^{F(\phi_Y)} \ar[dr]_{\epsilon_Y} & &F(G'(Y)) \ar[dl]^{\epsilon'_Y} && F(G'(Y)) \ar[rr]^{F(\phi_Y)} \ar[dr]_{\epsilon'_Y} & &F(G(Y)) \ar[dl]^{\epsilon_Y}\\ & Y &&&&Y}\]
		Now, we can notice that the diagram belows commute.

	\[\xymatrix{F(G(Y)) \ar[r]^{F(\phi_Y)} \ar[dr]_{\epsilon_Y} &F(G'(Y)) \ar[r]^{F(\phi_Y)} \ar[d]_{\epsilon'_Y} & F(G(Y)) \ar[dl]^{\epsilon_Y} \\ & Y \\ F(G'(Y)) \ar[r]_{F(\phi'_Y)} \ar[ur]^{\epsilon'_Y} &F(G(Y)) \ar[r]_{F(\phi'_Y)} \ar[u]_{\epsilon_Y} & F(G'(Y)) \ar[ul]_{\epsilon'_Y}}\]	
This implies at once that $\phi_Y$ and $\phi'_Y$ are mutally inverse. \qedhere 
	\end{enumerate}

\end{proof}

\begin{lemma}\label{lem:part}
	Let $\X$ be an  an $\mathcal{M}$-adhesive category  and cosinder a pair $(m,f)$ with $m\colon M\mto X $ in $\mathcal{M}$ and $f:X\to Y$. If $(h, k)$ is a pushout complement for the pair $(m,f)$, then there exists an isomorphism $\epsilon_k:f^*(k)\to m$ in $\mathcal{M}/X$ such that $(k, \epsilon_k)$ is  a partial right adjoint at $m$ to the pullback functor $f^*\colon \mathcal{M}/Y\to \mathcal{M}/X$.
\end{lemma}
\begin{proof}
	By \Cref{prop:pbpoad}, in the diagram below the inner square is both  a pushout and a pullback, yielding the dotted isomorphism $\epsilon_k\colon f^*(Q)\to M$.
\[\xymatrix{f^*(Q) \ar@{.>}[dr]^{\epsilon_k} \ar@{>->}@/^.3cm/[drr]^{f^*(k)} \ar@/_.3cm/[ddr]_{p}\\& M \ar@{>->}[r]^{m}\ar[d]_{h}& X \ar[d]^f \\&Q\ar@{>->}[r]_{k}&Y}\]

To see that in this way we get a partial right adjoint, let $g\colon f^*(n)\to m $ be a morphism in $\mathcal{M}/X$, then we have the solid diagram below
\[\xymatrix{f^*(N) \ar[dr]^{g} \ar@{>->}@/^.3cm/[drr]^{f^*(n)} \ar[ddd]_{q}\\& M \ar@{>->}[r]^{m}\ar[d]_{h}& X \ar[d]^f \\&Q\ar@{>->}[r]_{k}&Y\\N \ar@{>->}@/_.3cm/[urr]_{n} \ar@{.>}[ur]^{t}}\]
Now, since $n$ and $f^*(n)$ are in $\mathcal{M}$ we can form two other pullback squares:
\[\xymatrix{A \ar@{>->}[d]_{a}\ar@{>->}[r]^-{r}& f^*(N) \ar@{>->}[d]^{f^*(n)} & B \ar@{>->}[r]^{s} \ar@{>->}[d]_{b}& N \ar@{>->}[d]^{n}\\M \ar@{>->}[r]_{m}&X &Q \ar@{>->}[r]_k&Y\\}\]
Notice that 
\begin{align*}
	k\circ h\circ a&=f\circ m\circ a\\&=f\circ f^*(n)\circ r\\&=n\circ q \circ r
\end{align*}
Thus there exists a unique $c\colon A\to B$ as in the diagram
\[\xymatrix{A \ar@{>->}[d]_{a} \ar@{.>}[dr]^{c}\ar@{>->}[r]^-{r} &f^*(N) \ar@/^.2cm/[dr]^{q} \\ M \ar@/_.2cm/[dr]_{h}&B\ar@{>->}[r]^{s}  \ar@{>->}[d]_{b}& N \ar@{>->}[d]^{n}\\ &Q \ar@{>->}[r]_{k} & Y}\]
We can then consider the two diagrams below, noticing that the left one is $\mathcal{M}$-Van Kampen and in the cube on the right the front, right and left faces are pullbacks.
		\[\xymatrix@C=10pt@R=10pt{&&&&&A\ar@{>->}[dd]|\hole_(.65){a}\ar[rr]^{c} \ar@{>->}[dl]_{r} && B \ar@{>->}[dd]^{b} \ar@{>->}[dl]_{s} \\ M \ar@{>->}[dd]_{m}\ar[rr]^{h}&&Q\ar@{>->}[dd]^{k}&&f^*(N)  \ar@{>->}[dd]_{f^*(n)}\ar[rr]^(.7){q} & & N \ar@{>->}[dd]_(.3){n}\\&&&&&M\ar[rr]|\hole^(.65){h} \ar@{>->}[dl]^{m} && Q \ar@{>->}[dl]^{k} \\X\ar[rr]_{f} &&Y&&X \ar[rr]_{f} & & Y}\]
Now, we can also notice that the back square is a pullback too. To see this it is enough to apply \Cref{lem:pb1} to the diagram
\[\xymatrix{A  \ar@/^.4cm/[rr]^{a\circ r}\ar@{>->}[d]_{a} \ar[r]_{c}& \ar@{>->}[r]_{s}B \ar@{>->}[d]^{b}& N \ar[d]^{n}\\ M \ar@/_.4cm/[rr]_{f\circ m}\ar[r]^{h}& Q \ar@{>->}[r]^{k}& Y}\]

By hypothesis we have $g\colon f^*(n)\to m$ in $\mathcal{M}/X$, thus \Cref{lem:varie} yields a unique morphism $\bar{g}\colon n\to k$ in $\mathcal{M}/Y$. fitting in the diagram below.
 \[\xymatrix{f^*(N) \ar@/_.3cm/[ddr]_{q} \ar[r]^{f^*(\bar{g})}& f^*(Q) \ar[dr]^{\epsilon_k} \ar@{>->}@/^.3cm/[drr]^{f^*(k)} \ar@/_.3cm/[ddr]_{p}\\&& M \ar@{>->}[r]^{m}\ar[d]_{h}& X \ar[d]^f \\&N \ar@{>->}[r]^{\bar{g}} \ar@{>->}@/_.4cm/[rr]_{n} &Q\ar@{>->}[r]^{k}&Y}\]
In particular we have
\begin{align*}k\circ h\circ \epsilon_k\circ f^*(\bar{g})&=k\circ p\circ f^*(\bar{g})\\&=k\circ \bar{g}\circ q\\&=n\circ q\\&=k\circ h\circ g
\end{align*}
Therefore $ h\circ \epsilon_k\circ f^*(\bar{g})=h\circ g$. On the other hand we already know that $m\circ g=m\circ \epsilon_k\circ f^*(\bar{g})$, so that we can deduce $\epsilon_k \circ f^*(\bar{g})=g$ as wanted.
\end{proof}

We can deduce some properties of pushout complements from \Cref{lem:part}.

\begin{corollary}\label{lem:radj} Let $\X$ be an $\mathcal{M}$-adhesive category and consider two composable arrows $m\colon M \mto X$  and $f\colon X\to Y$, with $m\in \mathcal{M}$. Suppose moreover that the following square is a pushout, so that $(h,k)$ is a pushout complement og $(m,f)$:
	\[\xymatrix{M \ar@{>->}[r]^{m}\ar[d]_{h}& X \ar[d]^{f} \\Q\ar@{>->}[r]_{k}&Y}\]

Then the following properties hold true.
\begin{enumerate}
	\item  Given another arrow $n\colon N\to Y$ in $\mathcal{M}$ and the pullback square below,
	\[\xymatrix{P \ar[r]^{p_1} \ar@{>->}[d]_{p_2}& N \ar@{>->}[d]^{n}\\X \ar[r]_f&Y}\]
	$\mathcal{M}/Y(n, k)$ is non-empty  if and only $\mathcal{M}/X(p_2, m)$ is so.
	\item (Uniqueness of pushout complements) If $h'\colon M\to Q' $ and $k'\colon Q'\mto Y$ is a pushout complement for $(m,f)$, then there exists a unique isomorphism $\phi\colon Q\to Q'$ making the following diagram commutative.
	\[\xymatrix{&M \ar@{>->}[r]^{m} \ar[d]_{h} \ar@/_.3cm/[ddl]_{h'}& X \ar[d]^{f} \\ &Q \ar@{.>}[dl]^{\phi} \ar@{>->}[r]_{k} & Y \\ Q' \ar@{>->}@/_.3cm/[urr]_{k'}}\]
	\item The pair $(h,k)$ is a \emph{final $\mathcal{M}$-pullback complement} of $(m,f)$, i.e. the pushout square of $m$ along $h$ is also a pullback square for $f$ along $k$ and, moreover, given the solid part of the diagram
	\[\xymatrix{M' \ar[r]^{g}\ar[d]_{h'} & M \ar@{>->}[r]^{m}\ar[d]_{h}& X \ar[d]^{f}  \\  Q' \ar@{.>}[r]^{t} \ar@/_.4cm/@{>->}[rr]_{k'}&Q\ar@{>->}[r]^{k}&Y}\]
	in which the external rectangle is a pullback, then there exists a unique $t\colon Q'\to Q$ making the whole diagrams commutative.
\end{enumerate}
\end{corollary}
\begin{proof}
	\begin{enumerate}
		\item  This follows from point $1$ of \Cref{prop:uni} and \Cref{lem:part}.
		\item  By the second point  of \Cref{prop:uni} and \Cref{lem:part} we get an isomorphism $\phi:k\to k'$ in $\mathcal{M}/Y$. On the other hand we have
		\begin{align*}
			k'\circ \phi \circ  h_1&=k\circ h\\&=f\circ m\\&= k'\circ h'
		\end{align*}
		Since $k'$ is a monomorphism we conclude that $h'=\phi\circ h$.
		\item  This follows from the first point since $g$ belongs to $\mathcal{M}/X(m\circ g, m)$. \qedhere 
	\end{enumerate}
\end{proof}

\subsection{$\mathcal{M}$-adhesivity is not enough}\label{app:fill}
In \Cref{prop:equi} we proved that, in the linear case, the existence of an indpendence pair between two derivation is equivalent to that of a filler between them. This result can be further refined: in a\cite{baldan2011adhesivity} a class  $\mathbb{B}$ of (quasi)adhesive category is defined for which the local Church-Rosser Theorem holds even for left-linear DPO-rewriting system. In our language, and given \Cref{prop:fil} and \Cref{rem:locCR}, this amount to prove that, for elements of $\mathbb{B}$, every independence pair induces a filler.

\begin{definition}Let $\X$ be a category, we say that $\X$ satisfies
	\begin{itemize}
		\item the \emph{mixed decomposition} property if for every diagram
		\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
		whose outer boundary is a pushout and in which $k$ is a monomorphisms, 
		\item the \emph{pushout decomposition} property
	\end{itemize}
\end{definition}

\begin{lemma}
	contenuto...
\end{lemma}
\begin{proof}
	contenuto...\qedhere 
\end{proof}

\begin{corollary}
	contenuto...
\end{corollary}

The following result shows that the mixed and pushout decomposition properties guarantee that every independence pair gives rise to a filler.

\begin{theorem}
	\todo{filler e classe B+}
\end{theorem}
\begin{proof}\qedhere 
\end{proof}

Our next step is to identify sufficient conditions for a category $\X$ to satisfy the mixed and pushout decomposition properties.

\begin{definition}
	\todo{classe B e class B+}
\end{definition}

\begin{example}
	\todo{esempi}
\end{example}

\begin{example}
	\todo{esempi}
\end{example}

\begin{proposition}
	\todo{da B a B+}
\end{proposition}
\begin{proof}
	contenuto... \qedhere 
\end{proof}
\begin{lemma}\todo{due proprietà classe B}
\end{lemma}
\begin{proof}
	\qedhere 
\end{proof}

\begin{corollary}
	\todo{due proprietà classe B+}
\end{corollary}

\begin{corollary}
	\todo{filler e classe B+}
\end{corollary}

\section{Strict $\mathcal{M}$-adhesivity and $\mathcal{M}$-unions}

 In this section we will prove that in a strict $\mathcal{M}$-adhesive category $\X$, the poset of $\mathcal{M}$-subobjects (see  \Cref{app:sub}) is a distributive lattice.

 We start by  proving the following a rather technical lemma \cite{garner2012axioms}, which will be needed afterward.

\begin{lemma}\label{lem:pb2}
	Let $\X$ be a category with pullbacks and $\mathcal{A}$  a class of arrows in it  stable under pullbacks. Suppose that  the following diagrams are given, with $r\colon W\to R$ and $q\colon Q'\to Q$ in $\mathcal{A}$.
	\[
	\xymatrix{Y\ar[r]^{f_2} \ar[d]_{f_1} & X_2 \ar[d]^{r_2} & Z_1 \ar[d]_{x_1}\ar[r]^{z_1} & W \ar[r]^{w} \ar[d]_{r} & Q'\ar[d]^{q} & Z_2 \ar[d]_{x_2} \ar[r]^{z_2}  & W  \ar[r]^{w} \ar[d]_{r}  & Q' \ar[d]^{q}\\ X_1 \ar[r]_{r_1} &R  & X_1 \ar[r]_{r_1} & R \ar[r]_{s}  & Q& X_2 \ar[r]_{r_2} & R \ar[r]_{s} & Q}\]

	If the first square is an $\mathcal{A}$-stable pushout and the whole rectangles and their left halves are pullbacks, then their common right half is a pullback too.
\end{lemma}
\begin{proof}Pulling back  $q$ along $s$ we get a square 
	\[\xymatrix{U \ar[r]^{u} \ar[d]_{h}& Q' \ar[d]^{q}\\ R \ar[r]_s & S}\]
	Notice that
	\[
	q\circ w\circ z_1=s\circ r_1\circ x_1 \qquad 
	q\circ w\circ z_2=s\circ r_2\circ x_2 \]
	Thus we get the dotted $u_1\colon Z_1\to U$ and $u_2\colon Z_2\to U$ fitting in the diagram
	\[\xymatrix{  Z_1  \ar@/^.4cm/[rr]^{w\circ z_1}\ar@{.>}[r]_{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]_{u} & Q'  \ar[d]^{q}&  Z_2 \ar@/^.4cm/[rr]^{w\circ z_2} \ar@{.>}[r]_{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]_{u}& Q' \ar[d]^{q} \\  X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
	which, by hypothesis and  \Cref{lem:pb1} have left halves which are pullbacks. Now,
	\[s\circ r_1\circ f_1 =s\circ r_2\circ f_2\]
	Pulling back $q$ along this arrow we get another square
	\[\xymatrix@C=40pt{Z'_0 \ar[r]^{t} \ar[d]_{y}& Q' \ar[d]^{q}\\ R \ar[r]_{s\circ r_1\circ f_1} & S}\]
	In particular, we obtain the dotted $b_1\colon Z'_0\to Z_1$ and $b_2\colon Z'_0\to Z_2$ in
	\[\xymatrix@C=30pt{ Z'_0 \ar@/^.4cm/[rrr]^{t}\ar[d]_{y} \ar@{.>}[r]_{b_1} & Z_1  \ar[r]_{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]_{u} & Q'  \ar[d]^{q} &Z'_0 \ar@/^.4cm/[rrr]^{t} \ar[d]_{y}\ar@{.>}[r]_{b_2}  & Z_2  \ar[r]_{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]_{u}& Q' \ar[d]^{q} \\ Y \ar[r]_{f_1}& X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & Y \ar[r]_{f_2} & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
	Notice that, again  by\Cref{lem:pb1}, all of the squares on the bottom rows of the two diagrams are pullbacks.

	We are going to construct another row above the previous ones. By hypothesis we have that
	\[q\circ w = s\circ r\]
	Thus there exists a unique $g\colon W\to U$ such that
	\[r=h\circ g \qquad w=u\circ g\]
	Moreover, we also have that
	\[\begin{split}h\circ g \circ z_1&=r \circ z_1\\&= r_1\circ x_1 \\&=h\circ u_1
	\end{split}\qquad\begin{split}h\circ g \circ z_2&=r \circ z_2\\&= r_2\circ x_2 \\&=h\circ u_2
	\end{split}\]
	and 
	\[\begin{split}u\circ g \circ z_1&=w \circ z_1\\&= u\circ u_1 
	\end{split} \qquad \begin{split}u\circ g \circ z_1&=w \circ z_2\\&= u\circ u_2
	\end{split}\]
	which together show that
	\[g\circ z_1=u_1 \qquad g\circ z_2=u_2\]

	Summing up, we can depict all the arrows we have constucted so far in the following diagrams
	\[\xymatrix{Z'_0 \ar[r]^{b_1} \ar[d]_{\id{Z'}}& Z_1 \ar[r]^{z_1} \ar[d]_{\id{Z_1}} &  W \ar[d]_g \ar[r]^{w} & Q' \ar[d]^{\id{Q'}}&& Z'_0 \ar[r]^{b_2}  \ar[d]_{\id{Z'}}& Z_2 \ar[d]_{\id{Z_2}} \ar[r]^{z_2}&  W \ar[d]_g\ar[r]^{w}& Q' \ar[d]^{\id{Q'}}\\ Z'_0 \ar[d]_{y} \ar[r]^{b_1} & Z_1  \ar[r]^{u_1}\ar[d]_{x_1}&  U \ar[d]_h \ar[r]^{u} & Q'  \ar[d]^{q}& &Z'_0  \ar[d]_{y}\ar[r]^{b_2}  & Z_2  \ar[r]^{u_2}\ar[d]_{x_2} &  U \ar[d]_h \ar[r]^{u}& Q' \ar[d]^{q} \\ Y \ar[r]_{f_1}& X_1 \ar[r]_{r_1} & R \ar[r]_s& Q & &Y \ar[r]_{f_2} & X_2 \ar[r]_{r_2}& R \ar[r]_s & Q}\]
	If we show that $g$ is an isomorphism we are done. Consider the cubes
	\[\xymatrix@C=13pt@R=13pt{&Z_0'\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{x_2} \ar[dl]_{z_2}  &&Z'_0\ar[dd]|\hole_(.7){y}\ar[rr]^{b_2} \ar[dl]_{b_1} && Z_2 \ar[dd]^{x_2} \ar[dl]_{u_2}\\Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){z_1} & & W \ar[dd]_(.3){r}&& Z_1  \ar[dd]_{x_1}\ar[rr]^(.65){u_1} & &U \ar[dd]_(.3){h}\\&Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2} && Y\ar[rr]|\hole^(.65){f_2} \ar[dl]_{f_1} && X_2 \ar[dl]^{r_2}\\X_1 \ar[rr]_{r_1} & & R && X_1 \ar[rr]_{r_1} & & R}\]
	in which the vertical faces are pullbacks. The bottom face is an $\mathcal{A}$-stable pushout and all the vertical arrows are in $\mathcal{A}$, therefore the top faces are pushouts too. Now,  the arrow $g$ fits in the following  diagram
	\[\xymatrix{Z'_0\ar[r]^{b_2} \ar[d] _{b_1}& Z_2 \ar@/^.3cm/[ddr]^{u_2}\ar[d]^{z_2} \\ Z_1 \ar[r]_{z_1}  \ar@/_.3cm/[drr]_{u_1}& W \ar[dr]^{g} \\ &&U}\]
	and thus it is an isomorphism.
\end{proof}

Given a strict $\mathcal{M}$-adhesive category with pullbacks, the previous result allows us to compute binary suprema of elements of the lattice of subobjects $\msub{X}{X}$ if, at least, one of the subobjects involved is in $\sub{M}{X}{X}$ .

\begin{proposition}\label{prop:uni2} Let $\X$ be a strict $\mathcal{M}$-adhesive category with pullbacks. Given  $m\colon M\mto X$ in $\mathcal{M}$  and another mono $n\colon N\to X$, consider the diagram 
	\[\xymatrix{P \ar[r]^{p_1} \ar@{>->}[d]_{p_2} & M\ar@{>->}[d]^{u_2} \ar@{>->}@/^.3cm/[ddr]^{m} \\ N \ar@/_.3cm/[drr]_{n}\ar[r]_{u_1} & U \ar@{.>}[dr]^{u} \\ && X}\]
	in which the outer boundary form a pullback and the inner square a pushout. Then the dotted arrow $u\colon U\to X$ is a monomorphism and, in $(\msub{X}{X}, \leq)$, $[u]$ is the supremum of $[m]$ and $[n]$.  
\end{proposition}
\begin{remark}
	Notice that the  $p_2$ and $p_1$ are both monos, moreover, $p_2$, as the pullback of $m$, is in $\mathcal{M}$. This, moreover, guarantees the existence of the inner pushout and thus of the dotted arrow $u$.  Finally, notice that also $u_2$, being the pushout of $p_2$ is in $\mathcal{M}$.
\end{remark}
\begin{proof}
	Consider the following two pullback squares
	\[\xymatrix{Q \ar[r]^{q_1} \ar[d]_{q_2} & N\ar[d]^{n} & W \ar[r]^{w_1} \ar@{>->}[d]_{w_2}& M\ar@{>->}[d]^{m}\\
		U \ar[r]_{u}& X & U \ar[r]_{u}& X}\]
	By construction we have the following equalities 
	\[\begin{split}
		n&=u\circ u_1  \qquad \\
		u\circ u_2 \circ p_1&=m\circ p_1\\&=n\circ p_2
	\end{split}\qquad \begin{split}
		m&=u\circ u_2\\ u\circ u_1\circ p_1&=n\circ p_2\\&=m\circ p_1
	\end{split}\]
	which give us the arrows $f_1\colon N\to Q$, $f_2\colon P\to Q$, $g_1\colon M\to W$, $g_2\colon P\to W$ making the following diagrams commute
	\[\xymatrix@C=20pt{N\ar@/^.4cm/[rr]^{\id{N}}\ar@{.>}[r]_{f_1}  \ar[d]_{\id{N}} &Q\ar[r]_{q_1} \ar[d]_{q_2} & N \ar[d]^{n}  &P\ar@{>->}@/^.4cm/[rr]^{p_2}\ar@{.>}[r]_{f_2}  \ar[d]_{p_1} &Q\ar[r]_{q_1} \ar[d]_{q_2} & N \ar[d]^{n}
		\\ N \ar@/_.4cm/[rr]_{n}\ar[r]^{u_1} & U \ar[r]^{u}  & X  & M\ar@{>->}@/_.4cm/[rr]_{m}\ar@{>->}[r]^{u_2}   &U\ar[r]^{u}  & X }\]
	\[\xymatrix@C=20pt{M\ar@/^.4cm/[rr]^{\id{M}}\ar@{.>}[r]_{g_1}  \ar[d]_{\id{M}} &W\ar[r]_{w_1} \ar@{>->}[d]_{w_2} & M \ar@{>->}[d]^{m} & P\ar@/^.4cm/[rr]^{p_1}\ar@{.>}[r]_{g_2}  \ar@{>->}[d]_{p_2} &W\ar[r]_{w_1} \ar@{>->}[d]_{w_2} & M \ar@{>->}[d]^{m}
		\\ M \ar@{>->}@/_.4cm/[rr]_{m}\ar@{>->}[r]^{u_2} & U \ar[r]^{u}  & X & N\ar@/_.4cm/[rr]_{n}\ar[r]^{u_1}  &U\ar[r]^{u} & X }\]

	Their outer edges are pullbacks, thus in the following cubes, the vertical faces are pullbacks
	\[\xymatrix@C=13pt@R=13pt{&P\ar[dd]|\hole_(.65){\id{P}}\ar[rr]^{\id{P}} \ar@{>->}[dl]_{p_2} && P \ar[dd]^{p_1} \ar[dl]_{f_2} & & P\ar[dd]|\hole_(.65){\id{P}}\ar[rr]^{p_1} \ar[dl]_{\id{P}} && M \ar[dd]^{\id{M}} \ar[dl]_{g_1}\\ N  \ar[dd]_{\id{N}}\ar[rr]^(.65){f_1} & & Q \ar[dd]_(.3){q_2}&& P  \ar@{>->}[dd]_{p_2}\ar[rr]^(.65){g_2} & & W \ar@{>->}[dd]_(.3){w_2}\\&P\ar[rr]|\hole^(.65){p_1} \ar@{>->}[dl]^{p_2} && M \ar@{>->}[dl]^{u_2} && P\ar[rr]|\hole^(.65){p_1} \ar@{>->}[dl]^{p_2} && M \ar@{>->}[dl]^{u_2}\\N \ar[rr]_{u_1} & & U && N \ar[rr]_{u_1} & & U}\]

	We know that $p_2$ is an element of $\mathcal{M}$, thus  the top faces are pushouts and therefore $f_1$ and $g_1$ are isomorphisms with inverses given by $q_1$ and $w_1$.  But then, since
	\[u_1=q_2\circ f_1 \qquad u_2=w_2\circ g_1\]
	we can further deduce that the squares below  are both pullbacks.
	\[\xymatrix{N \ar[r]^{\id{N}} \ar[d]_{u_1} & N\ar[d]^{n} & M \ar[r]^{\id{M}} \ar@{>->}[d]_{u_2}& M\ar@{>->}[d]^{m}\\
		U \ar[r]_{u}& X & U \ar[r]_{u}& X}\]

	We have three diagrams 
	\[\xymatrix{P\ar@{>->}[d]_{p_2} \ar[r]^{p_1} & M \ar@{>->}[d]^{m}  & N \ar[d]_{\id{N}} \ar[r]^{u_1}& U\ar[d]_{\id{U}} \ar[r]^{\id{U}}  & U \ar[d]^{u} &  M \ar[d]_{\id{M}} \ar[r]^{u_2}& U \ar[r]^{\id{U}} \ar[d]_{\id{U}}  & U \ar[d]^{u}\\N \ar[r]_{n} & X & N \ar@/_.3cm/[rr]_{n}\ar[r]^{u_1} & U  \ar[r]^u  &X & M\ar@{>->}@/_.3cm/[rr]_{m}\ar@{>->}[r]^{u_2} & U  \ar[r]^u  &X }\]
	and we have just proved that the rectangles are pullbacks. Thus we can apply \Cref{lem:pb2} to deduce that 
	\[\xymatrix{ U \ar[r]^{\id{U}} \ar[d]_{\id{U}}  & U \ar[d]^{u}\\ U  \ar[r]_u  &X }\]
	is a pullback, but this means exactly that $u$ is a mono.

	For the second half: suppose that $k\colon K\to X$ is an upper bound for $m$ and $n$, thus there exists $k_1\colon M\to K$ and $k_2\colon N\to K$ such that
	\[m=k\circ k_1 \qquad n=k\circ k_2\] 
	But then
	\begin{align*}
		k\circ k_1 \circ p_1 &= m\circ p_1\\&= n\circ p_2\\&= k\circ k_2\circ p_2
	\end{align*}
	Since $k$ is mono, this implies that there exists a unique $h\colon U\to K$ such that 
	\[k_2=h\circ u_1 \qquad k_1=h\circ u_1\]
	and we have
	\[\begin{split}
		k\circ h \circ u_1&=k\circ k_2\\&=n \\&=u \circ u_1 
	\end{split}\qquad 
	\begin{split}
		k\circ h \circ u_2&=k\circ k_1\\&=m \\&=u \circ u_2 
	\end{split} \]
	showing that $u=k\circ h$, i.e.~that $[u]\leq [k]$.
\end{proof}

Our next step is to prove that, if $m\colon M\to X$ and $n\colon N\to X$ are in $\mathcal{M}$, then their supremum $u$ in $\msub{X}{X}$ belongs to $\mathcal{M}$ too. To do this we need another technical tool.

\begin{definition}\index{codiagonal} \index{codiagonal!$\mathcal{N}$-}
	Let $f\colon X\to Y$ be an arrow in a category $\X$ such that the pushout square below  exists.
	\[\xymatrix{ X \ar[r]^f \ar[d]_f& Y \ar[d]^{y_1}\\ Y \ar[r]_{y_2} & Q_f}\]
	The \emph{codiagonal} $\upsilon_f\colon Q_f\to Y$ is the unique arrow  fitting in the following diagram.
	\[\xymatrix{ X \ar[r]^f \ar[d]_f& Y \ar@/^.3cm/[ddr]^{\id{Y}} \ar[d]^{y_1}\\ Y \ar@/_.3cm/[drr]_{\id{Y}}\ar[r]_{y_2} & Q_f \ar@{.>}[dr]^{\upsilon_f}\\ && Y}\]
\end{definition}

\begin{remark}\label{rem:cod}
	Notice that, in a  $\mathcal{M}$-adhesive category,  for every $m\in \mathcal{M}$ there exists a pushout square of $m$ along itself and so also its codiagonal $\upsilon_m$.
\end{remark}

Let us list some useful properties of codiagonals.

\begin{lemma}\label{rem:coeq}
	Let $f\colon X\to Y$ be a morphism in a category $\X$ and suppose that $f$ admits a codiagonal $\upsilon_f\colon Q_f\to Y$, then the following hold true:
	\begin{enumerate}
		\item $\upsilon_f$ is the coequalizer of the pair of coprojections $y_1, y_2\colon Y\rightrightarrows Q_f$;
		\item suppose that the square below is a pullback $y_1$ along $y_2$
		\[\xymatrix{P \ar[r]^{p_1} \ar[d]_{p_2} & Y \ar[d]^{y_1}\\  Y\ar[r]_{y_2} &  Q_f}\]
		Then $p_1=p_2$ and the pair $y_1, y_2\colon Y\rightrightarrows Q_f$ has an equalizer $p_1\colon P\to Y$.
	\end{enumerate}
\end{lemma}
\begin{proof}\begin{enumerate}
		\item  Let $z\colon Q_f\to Z$ be such that
		\[z\circ y_1=z\circ y_2\]
		Then we also have the identities
		\[\begin{split}
			z\circ y_1 \circ \upsilon_f  \circ y_1 &=z\circ y_1 \circ \id{Y}\\&= z\circ y_1\\&
		\end{split}\qquad \begin{split}z\circ y_1\circ \upsilon \circ  y_2&= z\circ y_1 \circ \id{Y}\\&=z\circ y_1\\&=z\circ y_2
		\end{split}\]
		Therefore, \[z\circ y_1 \circ \nu_f=z\]

		Uniqueness follows from the fact that $\upsilon_f$ is a split epi.
		\item  First of all we can notice that in every square, not necessarily a pullback one, as the one in the diagram below, the existence of the codiagonal implies $q_1=q_2$.
		\[\xymatrix{Q \ar[r]^{q_1} \ar[d]_{q_2} & Y \ar[d]^{y_1} \ar@/^.3cm/[ddr]^{\id{Y}}\\  Y\ar[r]_{y_2}  \ar@/_.3cm/[drr]_{\id{Y}}&  Q_f\ar[dr]^{\upsilon_f}\\ && Y}\]

		To see that $p_1\colon P \to Y$ is an equalizer for $y_1$ and $y_2$, consider an arrow $z\colon Z\to X$ such that
		\[y_1\circ z=y_2\circ z\]

		Then the universal property of the pullback of $y_1$ along $y_2$ yields a unique $g\colon Z\to P$ such that $z=p_1\circ g$.
		\qedhere
	\end{enumerate}
\end{proof}

\begin{lemma}\label{lem:fact2}
	Let $\X$ be a strict $\mathcal{M}$-adhesive category with pullbacks. Let $m\colon M\mto X$ and $n\colon N\mto X$ be two arrows in $\mathcal{M}$ and suppose that $u\colon U\to X$ is a representative for $[m]\vee[n]$ in $\msub{X}{X}$. Then:
	\begin{enumerate}
		\item $u$ admits pushouts  along itself (i.e.~it has a \emph{cokernel pair}); 
		\item if $\mathcal{M}$ the class of split monos, then there exists an epi $e_u\colon M\to E_u$ and an element $m_u\colon  E_u\to X$ of $\mathcal{M}$ such that   $u=m_u\circ e_u$.
	\end{enumerate}
\end{lemma}

\begin{proof}
	\begin{enumerate}
		\item 
		By \Cref{prop:uni2}, we can consider the following diagram	in which the outer edges form a pullback and the inner square is a pushout.
		\[\xymatrix{P \ar@{>->}[r]^{p_1} \ar@{>->}[d]_{p_2} & M\ar@{>->}[d]^{u_2} \ar@{>->}@/^.3cm/[ddr]^{m} \\ N \ar@{>->}@/_.3cm/[drr]_{n}\ar@{>->}[r]_{u_1} & U \ar[dr]^{u} \\ && X}\]

		By \Cref{rem:cod} we know that the codiagonal $\nu_n$ exists. We can then pull back $m$ along $\upsilon_n$, we obtaining the square below.
		\[\xymatrix{T\ar[r]^{t_1}  \ar@{>->}[d]_{t_2}& M\ar@{>->}[d]^{m}\\ Q_{n} \ar[r]_{\upsilon_n} & X}\]

		Now, we have identities
		\[\begin{split}
			m \circ \id{M}&=m \\&=\id{X} \circ  m \\&=\upsilon_n\circ n_1 \circ m
		\end{split} \qquad \begin{split}
			m \circ \id{M}&=m \\&=\id{X} \circ  m \\&=\upsilon_n\circ n_2\circ m
		\end{split}\]
		Thus, denoting by $n_1$ and $n_2$ the coprojections $X\rightrightarrows Q_n$, which are both in $\mathcal{M}$, there exist $l_1, l_2\colon M\rightrightarrows T$ as in the following diagram

			\[\xymatrix{ M\ar@{.>}[r]_{l_1} \ar@/^.4cm/[rr]^{\id{M}} \ar@{>->}[d]_{m}&T\ar[r]_{t_1}  \ar@{>->}[d]_{t_2}& M\ar@{>->}[d]^{m} & M\ar@{.>}[r]_{l_2} \ar@/^.4cm/[rr]^{\id{M}} \ar@{>->}[d]_{m}&T\ar[r]_{t_1}  \ar@{>->}[d]_{t_2}& M\ar@{>->}[d]^{m}\\ X  \ar@/_.4cm/[rr]_{\id{X}} \ar@{>->}[r]^{n_1}&Q_{n} \ar[r]^{\upsilon_n} & X & X \ar@/_.4cm/[rr]_{\id{X}} \ar@{>->}[r]^{n_2} &Q_{n} \ar[r]^{\upsilon_n} & X}\]

		In particular, by \Cref{lem:pb1}, the left halves of the above rectangles are pullbacks and both $l_1$ and $l_2$ belongs to $\mathcal{M}$. Now, notice that, by construction $t_1\circ l_1=t_1\circ l_2$, so that
		\[	t_1\circ l_1\circ p_1=	t_1\circ l_2\circ p_1\]

		Moreover, we can also compute to get
		\begin{align*}
		t_2\circ l_1\circ p_1&=n_1\circ m \circ p_1\\&=n_1\circ n\circ p_2\\&=n_2\circ n\circ p_2\\&=n_2\circ m\circ p_1\\&= t_2\circ l_2\circ p_1
		\end{align*}

		Summing up, the cube below commutes and,  by the Van Kampen property, its top face is a pushout, proving that $t_1$ is a codiagonal of $p_1$.
		\[\xymatrix@C=13pt@R=13pt{&P\ar@{>->}[dd]|\hole_(.65){p_2}\ar@{>->}[rr]^{p_1} \ar@{>->}[dl]_{p_1} && M \ar@{>->}[dd]^{m} \ar@{>->}[dl]_{l_1}\\ M  \ar@{>->}[dd]_{m}\ar@{>->}[rr]^(.65){l_2} & & T\ar@{>->}[dd]_(.3){t_2}\\&N\ar@{>->}[rr]|\hole^(.65){n} \ar@{>->}[dl]_{n} && X \ar@{>->}[dl]^{n_1} \\X \ar@{>->}[rr]_{n_2} & & Q_n}\]

		As a next step, we can take the pushout of $t_2\colon T\mto Q_n$ alon $t_1$, obtaining the square below.
		\[\xymatrix{T \ar[r]^{t_1} \ar@{>->}[d]_{t_2}& M \ar@{>->}[d]^{q_1}\\ Q_n \ar[r]_{q_2} & Q }\]

		Now, if we compute on the one hand we have:
		\begin{align*}
			q_2\circ n_1\circ u \circ \circ u_1&=q_2\circ n_1\circ n\\&=q_2\circ n_2\circ n\\&=q_2\circ n_2 \circ u\circ u_1
		\end{align*}
		On the other hand a further computation yields
		\begin{align*}
		q_2\circ n_1\circ u \circ \circ u_2&=q_2\circ n_1\circ m\\&=q_2\circ t_2\circ l_1\\&=q_1\circ t_1 \circ l_1\\&=q_1\circ t_1\circ l_2\\&=q_2\circ t_2\circ l_2\\&=q_2\circ n_2\circ m\\&=q_2\circ n_2\circ u \circ \circ u_2
		\end{align*}

		Thus $q_2\circ n_1\circ u = q_2\circ n_2\circ u$ and the square below commutes. To conclude the proof, we have to show that it is a pushout.
		\[\xymatrix{U \ar[r]^u \ar[d]_u & X \ar[d]^{q_2\circ n_1}\\  X\ar[r]_{q_2\circ n_2} &  Q }\]

		Let now $z_1, z_2\colon X\rightrightarrows Z$ be two arrows such that 
		\[z_1\circ u=z_2\circ u\]

		If we precompose both sides of the previous equation  with $u_1$ and $u_2$ we get the following identities.
		\[\begin{split}
			z_1\circ m &= z_1\circ u\circ u_2\\&=z_2\circ u \circ u_2\\&=z_2\circ m
		\end{split} \qquad \begin{split}
			z_1\circ n &= z_1\circ u\circ u_1\\&=z_2\circ u \circ u_1\\&=z_2\circ n
		\end{split}\]

		The second chain of the equalities above allows us to deduce the existence of the dotted $w\colon Q_n\to Z$.
		\[\xymatrix{N \ar@{>->}[r]^{n} \ar@{>->}[d]_{n} & X\ar@{>->}[d]^{n_1} \ar@/^.3cm/[ddr]^{z_1} \\ X \ar@/_.3cm/[drr]_{z_2}\ar@{>->}[r]_{n_2} & Q_n \ar@{.>}[dr]^{w} \\ && Z}\]

		We compute to obtain
		\begin{align*}w\circ t_2\circ l_2&=w\circ n_2\circ m\\&=z_2\circ m\\&=z_1\circ m\\&=w\circ n_1\circ m\\&=w\circ t_2\circ l_1
		\end{align*}

	Now, we have already noted that $t_1$ is a codiagonal for $p_1$. Thus the first point of  \Cref{rem:coeq} entails the existence of a unique $k\colon M\to Z$ such that 
	\[k\circ t_1=w\circ t_2\]

	Thus the solid part in the diagram below commutes, yielding the existence of the dotted $z\colon Q\to Z$.
		\[\xymatrix{T \ar[r]^{t_1} \ar@{>->}[d]_{t_2}& M \ar@/^.3cm/[ddr]^{k}\ar@{>->}[d]^{q_1}\\ Q_n \ar@/_.3cm/[drr]_{w}\ar[r]_{q_2} & Q \ar@{.>}[dr]^{z}\\ && Z }\]

Computing further we have
		\[\begin{split}
		z\circ q_2\circ n_1&=z_1\\&=w\circ n_1
		\end{split}\qquad 
		\begin{split}
			z\circ q_2\circ n_2&=z_2\\&=w\circ n_2
		\end{split}\]

		Moreover, if $z'\colon Q\to Z$ is such that
		\[z_1=z'\circ q_2\circ n_1 \qquad z_2=z'\circ q_2\circ n_2\]
		then we also have 
		\[\begin{split}
			z'\circ q_2\circ n_1&=z_1\\
			&=w\circ n_1 
		\end{split}\qquad \begin{split}
			z'\circ q_2\circ n_2&=z_2\\
			&=w\circ n_2
		\end{split}\]
		which shows that $w=z'\circ q_2$. On the other hand
		\[\begin{split}
			z'\circ q_1\circ t_1 & = z'\circ q_2\circ t_2\\&=w\circ t_2
		\end{split}\]
		and so we also have that $z'\circ q_1=k$, allowing us to conclude that $z=z'$.

		\item By the previous point, there exists a pushout square		
		\[\xymatrix{U \ar[r]^{u} \ar[d]_{u}& X \ar[d]^{a_1} \\ X \ar[r]_{a_2}  & A}\]

		Thus $u$ also has a codiagonal $\upsilon_{u}\colon A\to U$. In particular, the two coprojections $a_1$ and $a_2$  are split monos and thus are in $\mathcal{M}$. By the second point of \Cref{rem:coeq}, they have an equalizer $m_u\colon E_u\to X$ which, since $\mathcal{M}$ are stable under pullback, is also an element of $\mathcal{M}$. Since $a_1\circ u= a_2\circ u$, there exists also an arrow $e_u\colon U\to E_u$ such that $u=m_u\circ e_u$.

		To show that this arrow is epi, we can start with the equalities
		\[\begin{split}
			m&=u\circ u_2\\&=m_u\circ e_u\circ u_2
		\end{split} \qquad \begin{split}
			n&=u\circ u_2\\&=m_u\circ e_u\circ u_1
		\end{split}  \]
		By \Cref{cor:deco}  $e_u\circ u_1$ and $e_u\circ u_2$ belong to $\mathcal{M}$. In particular they are monomorphisms and
		\[[e_u\circ u_1] \leq [e_u] \qquad [e_u\circ u_2] \leq [e_u]\]

		Now, we can also prove that,, in $(\msub{X}{E_u}, \leq)$ 
		\[[e_u]=[e_u\circ u_1]\vee [e_u\circ u_2]\]

		To see this, let  $b\colon B\to E_u$ be another mono such that 
		\[b\circ b_1 =e_u\circ u_1 \qquad b\circ b_2 =e_u\circ u_2\] 
		for some $b_1\colon N\to B$ and $b_2\colon M\to B$. Then 
		\begin{align*}
			b \circ b_1 \circ p_2 & = e_u \circ u_1\circ p_2\\&= e_u \circ  u_2\circ p_1\\&=b\circ b_2\circ p_1
		\end{align*}
		which, since $b$ is a mono, entails
		\[b_1\circ  p_2 =  b_2\circ p_1\]
		Thus there exists $\hat{b}\colon U\to B$ such that
		\[b_1 =\hat{b} \circ u_1 \qquad b_2=\hat{b}\circ u_2\]
		By computing further we get
		\[\begin{split}
			b\circ \hat{b} \circ u_1 &=b\circ b_1 \\&=e_u\circ u_1 
		\end{split}\qquad \begin{split}
			b\circ \hat{b} \circ u_2 &=b\circ b_2 \\&=e_u\circ u_2 
		\end{split}\]
	so that $e_u=b\circ \hat{b}$ and $[e_u] \leq [b]$.

	By the previous point and point $2$ of \Cref{rem:coeq}, there exist a diagram in which the outer edges form a pushout, the inner square is a pullback  and $c$ is the equalizer of $c_1$ and $c_2$.
		\[\xymatrix{U  \ar@/^.5cm/[rr]^{e_u} \ar@/_.4cm/[dr]_{e_u}  \ar@{.>}[r]_{e}& C \ar[d]_{c} \ar[r]_{c} & E_u \ar[d]^{c_2} \\  & E_u \ar[r]_{c_1} & \hat{Q}}\]
		The existence of $e\colon U\to C$ can then be inferred from the universal property of pullbacks.

		Now, if we show that $c$ is invertible, then we are done: in such a case $c_1$ and $c_2$ must be equals , proving that $e_u$ is an epimorphism.

		Being the coprojections of the pushout of $c$ along itself,  $c_1$ and $c_2$ are split monos and thus are in $\mathcal{M}$. Thus $c\in \mathcal{M}$ too.

		Take two arrows $z_1, z_2\colon X\rightrightarrows Z $ such that
		\[z_1\circ m_u\circ c=z_2\circ m_u \circ c\]
			Then we have
		\begin{align*}
			z_1\circ u &= z_1\circ m_u\circ e_u \\&= z_1\circ m_u\circ c \circ e \\&= z_2\circ m_u\circ c \circ e \\&= z_2\circ m_u \circ e_u\\&= z_2\circ u 
		\end{align*}
		and thus there exists $z\colon A\to Z$ such that 
		\[z_1= z\circ a_1\qquad z_2=z\circ a_2\]

		Uniqueness of such a $z$ follows at once since $a_1$ and $a_2$ are the coprojections of the pushout of $u$ along itself.  We can then conclude that the square below is a pushout.
		\[\xymatrix@C=40pt{U \ar[r]^{m_u\circ c} \ar[d]_{m_u\circ c} & X \ar[d]^{a_1}\\  X\ar[r]_{a_2} &  Q }\]
		Now, $\mathcal{M}$ and $\mathcal{N}$ are closed under composition. Thus $m_u\circ c$ is in $\mathcal{M}$ and so, by \Cref{cor:rego} that $m_u\circ c$ is a regular mono. But regular monos are always equalizers of the coprojections into their cokernel pair. Since we already know that $m_u$ is the equalizer of $a_1, a_2\colon X \rightrightarrows A$, we conclude that $c$ is an isomorphism. 	\qedhere 
	\end{enumerate}
\end{proof}

With these tools available, we are ready to provide a way to construct binary suprema in $\sub{M}{\X}{X}$.

 \begin{theorem}[\cite{garner2012axioms,castelnovo2023thesis,johnstone2007quasitoposes}]\label{thm:un}Let $\X$ be a strict $\mathcal{M}$-adhesive category with pullbacks and suppose that $\mathcal{M}$ contains all split monomorphisms. Then for every object $X$, $(\sub{M}{X}{X}, \leq)$ has binary suprema, which are preserved by the inclusion $(\sub{M}{X}{X}, \leq)\to (\msub{X}{X}, \leq)$.
 \end{theorem}
\begin{proof}	Let $m\colon M\to X$  and $n\colon N\to X$ be elements of in $\mathcal{M}$. By \Cref{prop:uni2} we know that $[m]$ and $[n]$  have a supremum in $(\msub{X}{X}, \leq)$ given by $[u]$, where $u\colon U\to X$ fits in the  diagram
	\[\xymatrix{P \ar@{>->}[r]^{p_1} \ar@{>->}[d]_{p_2} & M\ar@{>->}[d]^{u_2} \ar@{>->}@/^.3cm/[ddr]^{m} \\ N \ar@{>->}@/_.3cm/[drr]_{n}\ar@{>->}[r]_{u_1} & U \ar[dr]^{u} \\ && X}\]
	in which the outer edges form a pullback and the inner square is a pushout.

	 By the second point of \Cref{lem:fact2}, we also know that $u=m_u\circ e_u$ for some epi $e_u\colon Y\to E_u$ and $m_u\colon E_u\to X$ in $\mathcal{M}$. Our strategy to prove the theorem consists in showing that $e_u$ is an isomorphism.

	First of all notice that $e_u$ is a mono because $u=m_u\circ e_u$ and \Cref{prop:uni2}. Thus in the following diagram every square is a pullback and, applying \Cref{lem:pb1}, we can deduce that the composite square is a pullback too.
	\[\xymatrix{P \ar@{>->}[r]^{p_1} \ar@{>->}[d]_{p_2}& M \ar[r]^{\id{M}} \ar@{>->}[d]_{u_2} & M \ar[d]^{u_2} \\ N \ar@{>->}[r]_{u_1}  \ar[d]_{\id{U}}& U \ar[r]_{\id{U}} \ar[d]_{\id{U}} & U \ar[d]^{e_u} \\ N  \ar[r]_{u_1}& U \ar[r]_{e_u} & E_u}\].

	 As we have noticed before, \Cref{cor:deco} entails that both $e_u\circ u_1$ and $e_u\circ u_2$ belongs to $\mathcal{M}$. We can then build the following two pushout squares, which, by \Cref{prop:pbpoad}, are also pullbacks.
	\[\xymatrix@C=40pt{N \ar@{>->}[r]^-{e_u\circ u_1} \ar@{>->}[d]_{e_u\circ u_1} & E_u \ar@{>->}[d]^{e_1} & N \ar@{>->}[r]^-{e_u\circ u_1} \ar@{>->}[d]_{ u_1} & E_u \ar@{>->}[d]^{a_1} \\ E_u   \ar@{>->}[r]_-{e_2} & Q_{e_u\circ u_1} & U \ar@{>->}[r]_{a_2}& A}\]

	By construction the upper rectangle in the following diagram is commutative. Thus the dotted arrow $a$ exists and, by \Cref{lem:po1}, the bottom rectangle is a pushout.
	\[\xymatrix{N \ar@{>->}[r]^{u_1} \ar@{>->}[d]_{u_1} & U \ar[r]^{e_u} & E_u \ar@{>->}[d]_{a_1} \ar@{>->}@/^.5cm/[dd]^{e_1} \\
		U \ar[d]_{e_u} \ar@{>->}[rr]^{a_2}&& A \ar@{.>}[d]_{a} \\ E_u \ar@{>->}[rr]_{e_2}&&Q_{e_u\circ u_1}}\]

	The arrow $e_2$ is the pushout of $e_u\circ u_1$ along itself, thus it is in $\mathcal{M}$, and so it is a mono. Together with \Cref{lem:pb1}, this entails that the following rectangle is a pullback.
	\[\xymatrix{U \ar[r]^{e_u}  \ar[d]_{\id{U}}& E_u \ar[r]^-{\id{E_u}} \ar[d]_{\id{E_u}} & E_u \ar@{>->}[d]^{e_2}\\ U \ar[r]_{e_u} & E_u \ar@{>->}[r]_-{e_2} & Q_{e_u\circ u_1}}\]

	Similarly, the arrow $a_2$ is in $\mathcal{M}$ as it is the pushout of $e_u\circ u_1$ along $u_1$. Thus we can apply \Cref{lem:pb2} to the diagrams
	\[\xymatrix{ N \ar@{>->}[rr]^-{e_u\circ u_1} \ar@{>->}[d]_{ u_1} && E_u \ar@{>->}[d]^{a_1} & N \ar@{>->}[d]_{e_u\circ u_1} \ar@{>->}[r]^{u_1} & U \ar@{>->}[d]_{a_2}\ar[r]^-{e_u} & E_u  \ar@{>->}[d]^{e_2}\\ U \ar@{>->}[rr]_{a_2}&& A & E_u \ar@{>->}@/_.4cm/[rr]_{e_1} \ar@{>->}[r]^{a_1} &  A \ar[r]^-{a} & Q_{e_u\circ u_1} }\]
	\[\xymatrix{U  \ar[r]^{\id{U}} \ar[d]_{\id{U}}& U \ar@{>->}[d]_{a_2} \ar[r]^-{e_u} & E_u \ar@{>->}[d]^{e_2} \\U \ar@{>->}[r]^{a_2} \ar@{>->}@/_.4cm/[rr]_{e_2\circ e_u} & A \ar[r]^-{a} & Q_{e_u\circ u_1}}\]
	to get that also the following square is a pullback.
	\[\xymatrix{
		U \ar[d]_{e_u} \ar@{>->}[r]^-{a_2}& A \ar[d]^{a} \\ E_u \ar@{>->}[r]_-{e_2}&Q_{e_u\circ u_1}}\]

	On the other hand,  $p_1$ is in $\mathcal{M}$, thus we can push it out along itself.
	\[\xymatrix{P \ar@{>->}[r]^{p_1} \ar@{>->}[d]_{p_1}& M \ar@{>->}[d]^{m_1} \\ M \ar@{>->}[r]_{m_2} & Q_{p_1}}\]
	We can then construct the solid part of the rightmost rectangle in the diagram below, inducing the dotted $b\colon Q_{p_1}\to A$. Notice that the first rectangle is a pushout by \Cref{lem:po1} so that  the right half of the second diagram also is a pushout, again because of \Cref{lem:po1}, proving that $b$ belongs to $\mathcal{M}$ too.
	\[\xymatrix{P \ar@{>->}[r]^{p_2} \ar@{>->}[d]_{p_1}& N \ar@{>->}[d]_{u_1} \ar@{>->}[r]^{u_1}& U \ar[r]^{e_u} & E_u \ar@{>->}[d]^{a_1} & P \ar@{>->}@/^.4cm/[rrr]^{e_u\circ u_1\circ p_2}\ar@{>->}[r]_{p_1} \ar@{>->}[d]_{p_1}& M \ar@{>->}[d]_{m_1} \ar@{>->}[r]_{u_2}& U \ar[r]_{e_u}& E_u \ar@{>->}[d]^{a_1}\\ M \ar@{>->}[r]_{u_2}& U \ar@{>->}[rr]_{a_2}&& A& M \ar@{>->}@/_.4cm/[rrr]_{a_2\circ u_2}\ar@{>->}[r]^{m_2} & Q_{p_1} \ar@{>.>}[rr]^{b} && A}\]

	We can compose with the codiagonal $\upsilon_{p_1}\colon Q_{p_1}\to M$ to obtain the solid part of the diagram below.
	\[\xymatrix{M \ar@/_.4cm/[dd]_{\id{M}}\ar@{>->}[r]^{u_2} \ar@{>->}[d]^{m_1} & U \ar[r]^-{e_u} & E_u \ar@{>->}[d]_{a_1} \ar@/^.4cm/[dd]^{\id{E_u}} \\
		Q_{p_1} \ar[d]^{\upsilon_{p_1}} \ar@{>->}[rr]^{b}&& A \ar@{.>}[d]_{r} \\ M\ar@{>->}[r]_{u_2} & U\ar[r]_-{e_u}&E_u}\]	
	Since the upper half of the square above is a pushout, the dotted $r\colon A\to Q_{e_u\circ u_1}$ exists. Moreover, since the outer boundary is a pushout square, the lower half is a pushout too, by \Cref{lem:po1}. By \Cref{prop:pbpoad} the bottom rectangle of the previous diagram is also a pullback.

	As a next step, since $e_1\circ u_1$ is in $\mathcal{M}$, then we can form the following pushout. 
	\[\xymatrix@C=40pt{N \ar@{>->}[r]^{e_u\circ u_1} \ar@{>->}[d]_{e_u\circ u_1}& E_u\ar@{>->}[d]^{e_1}\\
		E_u \ar@{>->}[r]_{e_2}& Q_{e_u\circ u_1} }\]

		Moreover, we can notice that
		\[\begin{split}
		a\circ b \circ m_1&=a\circ a_1\circ e_u\circ u_2\\&=e_1\circ e_u\circ u_2
		\end{split}\qquad \begin{split}
		a\circ b \circ m_2&=a\circ a_2\circ u_2\\&=e_2\circ e_u\circ u_2
		\end{split}\]

	Thus the following cube commutes, has an $\mathcal{M}$-pushout as a bottom and top face and the back and left faces are pullbacks. Hence the front and right faces are pullbacks too.

	\[\xymatrix@C=15pt@R=15pt{&P\ar@{>->}[dd]|\hole_(.65){p_2}\ar@{>->}[rr]^{p_1} \ar@{>->}[dl]_{p_1} && M \ar@{>->}[dd]^{e_u\circ u_2} \ar@{>->}[dl]_{m_2}\\ M  \ar@{>->}[dd]_{e_u\circ u_2}\ar@{>->}[rr]^(.65){m_1} & & Q_{p_1}\ar[dd]_(.3){a\circ b}\\&N\ar@{>->}[rr]|\hole^(.7){e_u\circ u_1} \ar@{>->}[dl]^{e_u\circ u_1} && X \ar@{>->}[dl]^{e_2} \\X \ar@{>->}[rr]_{e_1} & & Q_{e_u\circ u_1}}\]

	Now, we can notice that for every $z_1\colon  Z\to M$ and $z_2\colon Z\to E_u$ such that 
	\[m\circ z_1=m_u\circ z_2\]
	we have the following chain of equalities
	\begin{align*}
		m_u\circ e_u\circ u_2\circ z_1&=u\circ u_2\circ z_1\\&=m\circ z_1\\&=m_u\circ z_2 
	\end{align*}
	which, since $m_u$ is mono, entails
	\[z_2=e_u\circ u_2\circ z_1\]
	But this means that the square below is a pullback. 
	\[\xymatrix{M \ar[r]^{\id{M}} \ar@{>->}[d]_{e_u\circ u_2}& M \ar@{>->}[d]^{m}\\ E_u \ar@{>->}[r]_{m_u} & X}\]

	We can therefore apply \Cref{lem:pb2} to the pushout of $e_u\circ u_1$ along itself and to the following two diagrams, where $\upsilon_{e_u\circ u_1}$ is the codiagonal of $e_u\circ u_1$.
	\[
	\xymatrix@C=30pt@R=30pt{ M \ar@/^.4cm/[rrr]^{\id{M}} \ar@{>->}[d]_{e_u\circ u_2}\ar@{>->}[r]_{m_2} & Q_{p_1} \ar[rr]_{\upsilon_{p_1}} \ar[d]_{a\circ b} && M\ar@{>->}[d]^{m} \\ E_u \ar@{>->}@/_.4cm/[rrr]_{m_u}\ar@{>->}[r]^-{e_2} & Q_{e_u\circ u_1} \ar[r]^-{\upsilon_{e_u\circ u_1}} &E_u \ar@{>->}[r]^{m_u} &X\\ 
	M\ar@/^.4cm/[rrr]^{\id{M}} \ar@{>->}[d]_{e_u\circ u_2} \ar@{>->}[r]_{m_1}  & Q_{p_1} \ar[rr]_{\upsilon_{p_1}} \ar[d]_{a\circ b}  && M \ar@{>->}[d]^{m}\\ E_u \ar@{>->}@/_.4cm/[rrr]_{m_u}\ar@{>->}[r]^-{e_1}& Q_{e_u\circ u_1} \ar[r]^-{\upsilon_{e_u\circ u_1}} & E_u \ar@{>->}[r]^{m_u} &X }\]

	Hence the outer rectangle in the diagram below is a pullback, so that, in particular, $a\circ b\in \mathcal{M}$. We can also apply \Cref{lem:pb1} to deduce that the left half of the rectangle  is a pullback, too. 
	\[\xymatrix@C=40pt{Q_{p_1} \ar[r]^{\upsilon_{p_1}} \ar@{>->}[d]_{a\circ b} &M \ar[r]^{\id{M}} \ar@{>->}[d]_{e_u\circ u_2}& M \ar@{>->}[d]^{m}\\ Q_{e_u\circ u_1} \ar[r]_-{\upsilon_{e_u\circ u_1}} & E_u \ar@{>->}[r]_{m_u}& X}\]

	We can compute to obtain two other identities:
	\[\begin{split}
		\upsilon_{e_u\circ u_1}\circ a\circ b & = e_u\circ u_2\circ \upsilon_{p_1}\\&= r\circ b\\&
	\end{split}\qquad \begin{split}
		\upsilon_{e_u\circ u_1}\circ a\circ a_1 &= \upsilon_{e_u\circ u_1}\circ e_1\\&= \id{E_u}\\&=r\circ a_1
	\end{split}\]

	Therefore $r= \upsilon_{e_u\circ u_1}\circ a$. Applying again \Cref{lem:pb1} to the following rectangle, we get that its left half is a pullback.
	\[ \xymatrix@C=30pt{Q_{p_1} \ar@{>->}[d]_b \ar[r]^{\id{Q_{p_1}}} & Q_{p_1}  \ar@{>->}[d]_{a\circ b}\ar[r]^{\upsilon_{p_1}}& M \ar@{>->}[d]^{e_u\circ u_2}\\ A \ar@/_.4cm/[rr]_{r}\ar[r]^-a&Q_{e_u\circ u_1} \ar[r]^-{\upsilon_{e_u\circ u_1}}& E_u }\]

	We want now to show that the inner rectangle of the diagram below is a pushout.  Let thus $z_1\colon Q_{e_u\circ u_1}\to Z$ and $z_2\colon M\ to Z$ be arrows such that $z_1\circ a\circ b=z_2\circ \upsilon_{p_1}$. Since $\upsilon_{e_u\circ u_1}$ is an epimorphism it is enougH to construct the dotted $z\colon E_u \to Z$. 
	\[\xymatrix{Q_{p_1} \ar@{>->}[r]^{b} \ar[d]_{\upsilon_{p_1}}& A \ar[r]^-{a}& Q_{e_u\circ u_1} \ar[d]_{\upsilon_{e_u\circ u_1}} \ar@/^.3cm/[ddr]^{z_1} \\M \ar@/_.3cm/[drrr]_{z_2}\ar@{>->}[r]^-{u_2}&U \ar[r]_{e_u}& E_u \ar@{.>}[dr]^{z}\\ & & & Z}\]

	First of all we can notice that
	\[z_1\circ e_1\circ e_u\circ u_1 = z_1\circ e_2\circ e_u\circ u_1\]
	while we also have
	\begin{align*}
		z_1\circ e_1\circ e_u\circ u_2 &= z_1\circ a\circ a_1\circ e_u\circ u_2\\&=z_1\circ a \circ b\circ m_1\\&=z_2\circ \upsilon_{p_1} \circ m_1
		\\&=z_2\circ \upsilon_{p_1} \circ m_2
		\\&=z_1\circ a \circ b\circ m_2 
		\\&=z_1\circ a\circ a_2\circ u_2
		\\&=z_1\circ e_2\circ e_u \circ u_2
	\end{align*}
	which implies that
	\[z_1\circ e_1\circ e_u  = z_1\circ e_2\circ e_u\]
	which, since $e_u$ is an epimorphism, allows us to conclude that $z_1\circ e_1$ and $z_1\circ e_2$ are eual. So equipped, we can now compute:
	\[\begin{split}
		z_1\circ e_1\circ \upsilon_{e_u\circ u_1}\circ e_1&=z_1\circ e_1\circ \id{E_u}\\&=z_1\circ e_1\\&
	\end{split} \qquad \begin{split}
		z_1\circ e_1\circ \upsilon_{e_u\circ u_1}\circ e_2&=z_1\circ e_1\circ \id{E_u}\\&=z_1\circ e_1\\&=z_1\circ e_2
	\end{split}\]
	showing 
	\[z_1=z_1\circ e_1 \circ  \upsilon_{e_u\circ u_1}\]

	Moreover, computing again we obtain
	\begin{align*}
		z_2\circ \upsilon_{p_1}&=z_1\circ a \circ b \\&=z_1\circ \id{E_u} \circ a \circ b\\&=z_1\circ e_1 \circ \upsilon_{e_u\circ u_1} \circ a\circ b\\&=z_1\circ e_1\circ e_u\circ u_2 \circ \upsilon_{p_1} 
	\end{align*}
	and $\upsilon_{p_1}$ is an epimorphism, thus
	\[z_2=z_1\circ e_1\circ e_u \circ u_2\]
	Summing up, $z_1\circ e_1$ fills our original diagram, thus its inner rectangle is indeed a pushout.

	We are now ready to collect all our arrows in the following cube
	\[\xymatrix@C=20pt@R=10pt{ & &Q_{p_1}\ar@{>->}[ddll]_{b} \ar[ddd]^(.4){\id{Q_{p_1}}}|(.666666)\hole\ar[rrr]^{\upsilon_{p_1}} &&&M \ar[ddd]^{\id{M}} \ar@{>->}[dl]^{u_2}\\&  &&&U \ar[ddd]^{\id{U}} \ar[dl]^{e_u} \\A \ar[ddd]_{a} \ar[rrr]^{r}&&& E_u\ar[ddd]^{\id{E_u}}\\&&Q_{p_1} \ar[rrr]|(.34)\hole^{\upsilon_{p_1}}|(.67)\hole \ar@{>->}[dl]_{b}&&& M \ar@{>->}[dl]^{u_2}\\ & A  \ar[dl]_(.4){a}&&& U \ar[dl]^{e_u} \\ Q_{e_u\circ u_1}\ar[rrr]_{\upsilon_{e_u\circ u_1}} &&& E_u}\]

	The top and bottom faces of this cube are $\mathcal{M}$-pushouts and all faces beside the frontal one are pullbacks, hence, by strict $\mathcal{M}$-adhesivity it follows that also this last face is a pullback. By \Cref{lem:pb1} the rectangle
	\[\xymatrix@C=40pt{U\ar[r]^{a_2} \ar[d]_{e_u} & A \ar[r]^{r} \ar[d]_{a}& E_u \ar[d]^{\id{E_u}}\\
		E_u \ar[r]_{e_2}& Q_{e_u\circ u_1} \ar[r]_{\upsilon_{e_u\circ u_1}} & E_u}\]
	is a pullback. Thus $e_u$ is an isomorphism as it is the pullback of $\id{E_u}$.
\end{proof}

\begin{example}\label{ex:sem}In \cite{johnstone2007quasitoposes} it is shown that the category $\cat{SGraph}$ of simple graphs is not quasiadhesive. Too see this, first of all recall that a morphism in $\cat{SGraph}$ is a regular monos if and only if it is injective on vertex and reflects edges. Now, take 
	\[\mathcal{G}:=(1, \{0,1\}, \delta_0, \delta_1) \qquad \mathcal{H}:=( \emptyset, 1, ?_1, ?_1) \quad \]
	Then we have two regular monomorphisms $ (?_1, \delta_0), (?_1, \delta_1)\colon \mathcal{H}\rightrightarrows \mathcal{G} $. Their supremum in $\msub{SGraph}{\mathcal{G}}$ is represented by inclusion of $(\emptyset, \{0,1\}, ?_0, ?_1)$ into $\mathcal{G}$ which is not a regular monomorphism, thus, by \Cref{thm:un}, $\cat{SGraph}$ is not quasiadhesive. 
\end{example}

 \begin{proposition}\label{prop:distlat}Let $\X$ be a strict $\mathcal{M}$-adhesive with pullbacks. If $\mathcal{M}$ contains all split monos then for every object $X$, $(\sub{M}{X}{X})$ is a distributive lattice. 
 \end{proposition}
\begin{proof}
	Since $\X$ has pullbacks then $(\sub{M}{X}{X})$  has binary infima. The existence of binary suprema is guaranteed by \Cref{thm:un}. We only have to show that, given $m\colon M\mto X$, $n\colon N\mto X$ and $v\colon V\mto X$ we have
	\[[n]\wedge ([m]\vee[v])=([n]\wedge [m]) \vee ([n]\wedge [v])\]

	Let $u\colon \mto X$ be a representative of $[m]\vee [v]$, thus by \Cref{prop:uni2} and \Cref{thm:un} we know that it fits in the diagram below, whose outer boundary is a pullback and in which the inner square is a pushout.
		\[\xymatrix{P \ar@{>->}[r]^{p_1} \ar@{>->}[d]_{p_2} & M\ar@{>->}[d]^{u_2} \ar@{>->}@/^.3cm/[ddr]^{m} \\ V \ar@{>->}@/_.3cm/[drr]_{v}\ar@{>->}[r]_{u_1} & U \ar@{>->}[dr]^{u} \\ && X}\]

	Let also $r\colon R\mto X$,  $s\colon S\mto X$, $t\colon T\mto X$ and $q\colon Q\mto X$ be  representative for, respectively $[n]\wedge [u]$, $[n]  \wedge [m]$, $[n]\wedge [v]$ and $[s]\wedge [t]$,  then we have the four pullback squares below.
	\[\xymatrix{R \ar@{>->}[r]^{r_1} \ar@{>->}[d]_{r_2}\ar@{>->}[dr]^{r}& N \ar@{>->}[d]^{n} & S \ar@{>->}[r]^{s_1} \ar@{>->}[d]_{s_2}\ar@{>->}[dr]^{s}& N \ar@{>->}[d]^{n}&T \ar@{>->}[r]^{t_1} \ar@{>->}[d]_{t_2}\ar@{>->}[dr]^{t}& N \ar@{>->}[d]^{n}& Q \ar@{>->}[r]^{q_1} \ar@{>->}[d]_{q_2}\ar@{>->}[dr]^{q}& T \ar@{>->}[d]^{t}\\U \ar@{>->}[r]_{u} & X&M \ar@{>->}[r]_{m} & X&V \ar@{>->}[r]_{v} & X&S \ar@{>->}[r]_{s} & X}\]

Using the universal property of the first square, we can construct the two dotted arrows $m_1\colon T\to R$ and $m_2\colon S\to R$ fitting in the following diagrams. Notice that the left halves of these rectangles are pullbacks by \Cref{lem:pb1}.

\[\xymatrix{T \ar[d]_{t_2} \ar@/^.4cm/[rr]^{t_1} \ar@{.>}[r]_{m_1}& R \ar@{>->}[r]_{r_1} \ar@{>->}[d]_{r_2}& N \ar@{>->}[d]^{n} & S \ar[d]_{s_2} \ar@/^.4cm/[rr]^{s_1} \ar@{.>}[r]_{m_2}& R \ar@{>->}[r]_{r_1} \ar@{>->}[d]_{r_2}& N \ar@{>->}[d]^{n}\\ V \ar@/_.4cm/[rr]_{v} \ar@{>->}[r]^{u_1}&U \ar@{>->}[r]^{u} & X &  M \ar@/_.4cm/[rr]_{m} \ar@{>->}[r]^{u_2}&U \ar@{>->}[r]^{u} & X}\]

On the other hand, we can also build the dotted $j\colon Q\to P$ as follows.

		\[\xymatrix{Q \ar[r]^{q_2} \ar[d]_{q_1} \ar@{.>}[dr]^{j}& S \ar@{>->}@/^.2cm/[dr]^{s_2}\\ T \ar@{>->}@/_.2cm/[dr]_{t_2}&P \ar@{>->}[r]^{p_1} \ar@{>->}[d]_{p_2} & M\ar@{>->}[d]^{u_2}  \\ &V \ar@{>->}[r]_{u_1} & U }\]

	Thus we have the commutative cube below, whose front and right faces are pullbacks and whose bottom face is an $\mathcal{M}$-pushout.
		\[\xymatrix@C=15pt@R=15pt{&Q\ar[dd]|\hole_(.65){j}\ar@{>->}[rr]^{q_2} \ar@{>->}[dl]_{q_1} && S \ar@{>->}[dd]^{s_2} \ar@{>->}[dl]_{m_2}\\ T \ar@{>->}[dd]_{t_2}\ar@{>->}[rr]^(.65){m_1} & & R \ar@{>->}[dd]_(.3){r_2}\\&P\ar@{>->}[rr]|\hole^(.7){p_1} \ar@{>->}[dl]_{p_2} && M \ar@{>->}[dl]^{u_2} \\V \ar@{>->}[rr]_{u_1} & & U}\]

		To show that the top face is a pushout it is enough to show that the left and back faces are pullbacks. Suppose thus that the solid part of the following two diagrams are given.
		\[\xymatrix{Z \ar@{.>}[dr]^{z} \ar@/^.3cm/[drr]^{z_1} \ar@/_.3cm/[ddr]_{z_2}&& &Y \ar@{.>}[dr]^{y} \ar@/^.3cm/[drr]^{y_1} \ar@/_.3cm/[ddr]_{y_2}\\&Q \ar@{>->}[r]^{q_2} \ar[d]_j & S \ar@{>->}[d]^{s_2}& &Q \ar@{>->}[r]^{q_1} \ar[d]_{j} & T \ar@{>->}[d]^{t_2}\\& P \ar@{>->}[r]_{p_1} & M && P \ar@{>->}[r]_{p_2}& V}\]

		By the universal property of pullbacks, we get the dotted arrows $z'\colon Z\to T$ and $y'\colon Y\to S$ fitting in the diagrams below.
		\[\xymatrix{Z \ar@{.>}[dr]^{z'} \ar[r]^{z_1} \ar[d]_{z_2}& S \ar@{>->}@/^.2cm/[dr]^{s_1}& &Y \ar@{.>}[dr]^{y'} \ar[r]^{y_1} \ar[d]_{y_2} & T  \ar@{>->}@/^.2cm/[dr]^{t_1}\\P \ar@{>->}@/_.2cm/[dr]_{p_2}&T \ar@{>->}[r]^{t_1} \ar@{>->}[d]_{t_2} & N \ar@{>->}[d]^{s_2}& P\ar@{>->}@/_.2cm/[dr]_{p_1}&S \ar@{>->}[r]^{s_1} \ar@{>->}[d]_{s_2} & N \ar@{>->}[d]^{n}\\& V \ar@{>->}[r]_{v} & X && M \ar@{>->}[r]_{m}& X}\]

		In turn, these two arrows yields $\hat{z}\colon Z \to Q$ and $\hat{y}\colon Y \to Q$ as below.
				\[\xymatrix{Z \ar@{.>}[dr]^{\hat{z}} \ar@/^.3cm/[drr]^{z_1} \ar@/_.3cm/[ddr]_{z'}&& &Y \ar@{.>}[dr]^{y} \ar@/^.3cm/[drr]^{y_1} \ar@/_.3cm/[ddr]_{y'}\\&Q \ar@{>->}[r]^{q_2} \ar@{>->}[d]_{q_1} & S \ar@{>->}[d]^{s}& &Q \ar@{>->}[r]^{q_1} \ar@{>->}[d]_{q_2} & T \ar@{>->}[d]^{t}\\& T \ar@{>->}[r]_{t} & X && S \ar@{>->}[r]_{s}& X}\]

	If we compute we get:
	\[\begin{split}
		p_2\circ j\circ \hat{z}&= t_2\circ q_1\circ \hat{z}\\&=t_2\circ z'\\&= p_2\circ z_2
	\end{split}\qquad \begin{split}
	p_1\circ j \circ \hat{y}&=s_2\circ q_2\circ \hat{y}\\&=s_2\circ y'\\&=p_1\circ y_2
	\end{split}\]

	Since $p_1$ and $p_2$ are mono it follows that 
	\[j\circ \hat{z}=z_2 \qquad j\circ \hat{y}=y_2\]

	Moreover, $q_2$ and $q_1$  are monos too, thus $\hat{z}$ and $\hat{y}$ are the unique arrows fitting in the two diagram with which we have begun, proving that the back and right faces of our original cubes are pullbacks.

	To end the proof it is now enough to see that 
	\[\begin{split}
	r\circ m_1&=u\circ r_2\circ m_1\\&=u\circ u_1\circ t_2\\&=v\circ t_2\\&=t
	\end{split}\qquad \begin{split}
	r\circ m_2&=u\circ r_2\circ m_2\\&=u\circ u_2\circ s_2\\&=m\circ s_2\\&=s
	\end{split}\]

Thus by \Cref{prop:uni2,thm:un} $[r]$ is the supremum of $[s]$ and $[t]$, which is exactly the thesis.	
\end{proof}

### 2024-11-14 full_version/factorization.tex
full version che compila in un tempo normale

--- 2024-10-11 domains/domains.tex
@@
-\documentclass[a4paper,UKenglish,cleveref,pdftex,thm-restate,numberwithinsect]{lipics-v2021}
-\newif\ifreport
-%\reporttrue 
-\reportfalse
-
-% full includes some additional material
-\newif\iffull
-%\fulltrue
-\fullfalse
-
-% additional text
-\iffull
-\newcommand{\full}[1]{{color{blue}#1}}
-%\newcommand{\short}[1]{}
-\else 
-\newcommand{\full}[1]{}
-%\newcommand{\short}[1]{#1}  xfl
-\fi
-
-\nolinenumbers %uncomment to disable line numbering
-
-\ifreport
-\nolinenumbers %uncomment to disable line numbering
-\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository
-\else
-\relatedversion{An extended version is available at \url{https://arxiv.org/abs/2407.06181}.} %optional, e.g. full version hosted on arXiv, HAL, or other respository/website
-%\relatedversion{A full version of the paper is available at \url{...}.}
-\fi
-
-\bibliographystyle{abbrv}% the mandatory bibstyle
-
-\usepackage{hyperref}
-\usepackage[disable,%
-textsize=tiny]{todonotes}
-%\usepackage{etex}
-\usepackage[all]{xy}
-\SelectTips{cm}{}
-% derivations and labels
-\usepackage{proof}
-\newcommand{\lab}[1]{\ensuremath{\mathsf{{#1}}}}
-\newcommand{\slab}[1]{\ensuremath{\scriptstyle{\mathsf{{#1}}}}}
-\usepackage{wrapfig}
-
-%frecce
-\newcommand{\mor}{\mathsf{Mor}}
-\newcommand{\mon}{\mathsf{Mono}}
-\newcommand{\reg}{\mathsf{Reg}}
-
-% ``boxed'' \infer command
-\newcommand{\binfer}[3][]{
-  \mbox{\infer[#1]{#2}{#3}}}
-
-% Command for labels on the left side of the rule
-%       \inferL{<name>}{<post>}{<pre>}
-% generates:
-%             <pre>
-%      <name> ------
-%             <post>
-%
-\newlength{\myheight}
-\newcommand{\inferL}[3]
-  {\settoheight{\myheight}{\mbox{${#2}$}}
-   \raisebox{\myheight}{{#1}}
-   \makebox[1mm]{}
-   \mbox{\infer{#2}{#3}}
-}
-
-\usepackage{amssymb,graphicx,epsfig,color}
-%\usepackage[scriptsize]{subfigure}
-\usepackage{subcaption}
-\usepackage{wrapfig}
-
-% re-stating 
-%\usepackage{thm-restate}
-
-% showing labels
-%\usepackage[inline]{showlabels}
-
-\usepackage{pgf}
-\usepackage{tikz}
-\usepackage{tikz-cd}
-\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri,fit,positioning,calc}
-\tikzstyle{node}=[circle, draw=black, minimum size=1mm, inner sep=1.5pt, font=\tiny]
-
-\tikzstyle{trans}=[font=\scriptsize]
-\tikzstyle{lab}=[font=\small]
-\tikzset{
-  coloredge/.style={
-        ->,
-        color=red
-        %densely dotted
-    }
-}
-
-\tikzset{
-  colorloop/.style={
-        loop,
-        color=red
-        %densely dotted
-    }
-}
-
-\tikzcdset{
-  perm/.style={
-    shorten >=-1mm, shorten <=-1mm,
-    -,
-    % dotted
-  }
-}
-
-\newcommand{\pgfBox}{
-  \begin{pgfonlayer}{background} 
-    \fill[blue!2,thick,draw=black!50,rounded corners,inner sep=3mm] ([xshift=-1.5pt,yshift=-1.5pt]current bounding box.south west) rectangle ([xshift=1.5pt,yshift=1.5pt]current bounding box.north east);
-  \end{pgfonlayer}
-}
-\usepackage{scalerel}
-\newcommand{\smallmin}{\scaleobj{0.6}{-}}
-\newcommand{\Deltamin}{\Delta^{\hspace{-1pt}\downarrow\hspace{-1pt}}}
-\newcommand{\Rrel}[1]   {\stackrel{{#1}}{\Longrightarrow}}
-\newcommand{\oa}{\overline a}
-\newcommand{\ob}{\overline b}
-\newcommand{\oc}{\overline c}
-\newcommand{\od}{\overline d}
-\newcommand{\rec}{\emph{rec}}
-\newcommand{\fn}[1]{{\mathtt{fn}}(#1)}
-%\usepackage{latexsym}
-\usepackage{stmaryrd}
-\def\encodep#1{\llfloor#1\rrfloor}
-
-\newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}
-
-\newcommand{\dpo}{\textsc{dpo}}
-
-% base classes of categories for adhesive and quasi adhesive case
-\newcommand{\bAdh}{\ensuremath{\mathbb{B}}}
-\newcommand{\bQAdh}{\ensuremath{\mathbb{QB}}}
-
-%from pawel
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{enumerate}
-\usepackage{xspace}
-\usepackage{amsfonts}
-\usepackage{mathrsfs}
-\usepackage{cite}
-\usepackage{float}
-\usepackage{fancybox}
-\usepackage{proof-at-the-end}
-\usepackage{cleveref}
-
-%\spnewtheorem*{notation}{Notation}{\bfseries}{\rmfamily}
-
-%%%%%%%% MATHEMATICAL NOTATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newcommand{\cori}{\mathbf{CS}}
-\newcommand{\cla}{\mathbf{CL}}
-\newcommand{\pos}{\mathbf{PO}}
-\newcommand{\gori}{\mathbf{GS}}
-
-%symbol for natural numbers
-\newcommand{\nat}{\ensuremath{\mathbb{N}}}
-
-% finite subset
-\newcommand{\sfin}{\ensuremath{\subseteq_{\mathit{fin}}}}
-
-% flattening of a multiset
-\newcommand{\flt}[1]{\ensuremath{[\![{#1}]\!]}}
-
-% compact elements
-\newcommand{\compact}[1]{\ensuremath{\mathop{\mathsf{K}({#1})}}}
-
-% principal ideal
-\newcommand{\principal}[1]{\ensuremath{\mathop{\downarrow\!{#1}}}}
-
-% ideal completion
-\newcommand{\ideal}[1]{\ensuremath{\mathsf{Idl}({#1})}}
-
-% complete prime elements
-\newcommand{\pr}[1]{\ensuremath{\mathop{\mathit{pr}({#1})}}}
-\newcommand{\wpr}[1]{\ensuremath{\mathop{\mathit{wpr}({#1})}}}
-
-% irreducible elements
-\newcommand{\ir}[1]{\ensuremath{\mathop{\mathit{ir}({#1})}}}
-
-% difference of irreducible elements
-\newcommand{\diff}[2]{\ensuremath{\delta({#1},{#2})}}
-
-%arrows
-\newcommand{\rightarrowdbl}{\rightarrow\mathrel{\mkern-14mu}\rightarrow}
-
-\newcommand{\xrightarrowdbl}[2][]{%
-	\xrightarrow[#1]{#2}\mathrel{\mkern-14mu}\rightarrow
-}
-
-\newcommand{\mini}[0]{\scalebox{.4}{$\bullet$}}
-\newcommand{\rto}[0]{\xrightarrow{\mini}}
-\newcommand{\fto}[0]{\xrightarrowdbl{\mini}}
-\newcommand{\eto}[0]{\twoheadrightarrow}
-
-% immediate precedence
-
-% abbreviation for event structure
-% \newcommand{\esabbr}{event structure}
-\newcommand{\esabbr}{\textsc{es}}
-\newcommand{\esnabbr}{\textsc{esnb}}
-\newcommand{\esnmabbr}{\textsc{esn}}
-\newcommand{\eseqabbr}{\textsc{epes}}
-
-% predecessor of an irreducible
-\newcommand{\pred}[1]{\ensuremath{\mathit{p}({#1})}}
-
-% irreducible elements in es domains
-\newcommand{\esir}[2]{\ensuremath{\langle{#1}, {#2}\rangle}}
-
-% equivalence classes [of irreducibles]
-\newcommand{\eqclass}[2][]{\ensuremath{[{#2}]_{\scriptscriptstyle {#1}}}}
-% union of the equivalence classes of the elements in a set
-\newcommand{\eqclasscup}[2]{\ensuremath{{#2}_{\scriptscriptstyle {#1}}}}
-
-\newcommand{\eqclassir}[1]{\ensuremath{\eqclass[\leftrightarrow^*]{#1}}}
-
-% quotient of set wrt a relation
-\newcommand{\quotient}[2]{\ensuremath{{#1}_{\scriptscriptstyle {#2}}}}
-
-% category of event structures 
-\newcommand{\es}{\ensuremath{\mathsf{ES}}}
-% category of stable event structures 
-\newcommand{\ses}{\ensuremath{\mathsf{sES}}}
-% category of prime event structures 
-\newcommand{\pes}{\ensuremath{\mathsf{pES}}}
-% category of prime event structures with equivalence
-\newcommand{\epes}{\ensuremath{\mathsf{epES}}}
-
-% category of connected event structures 
-\newcommand{\ces}{\ensuremath{\mathsf{cES}}}
-
-% category of weak prime algebraic domains domains 
-\newcommand{\WDom}{\ensuremath{\mathsf{wDom}}}
-% category of domains
-\newcommand{\Dom}{\ensuremath{\mathsf{Dom}}}
-% category of prime algebraic domains
-\newcommand{\PDom}{\ensuremath{\mathsf{pDom}}}
-
-%%%%% NON BINARY CONFLICT
-
-% category of event structures 
-\newcommand{\esn}{\ensuremath{\mathsf{ES_{nb}}}}
-% category of stable event structures 
-\newcommand{\sesn}{\ensuremath{\mathsf{sES_n}}}
-
-% category of connected event structures 
-\newcommand{\cesn}{\ensuremath{\mathsf{cES_{nb}}}}
-
-% category of prime event structures 
-\newcommand{\pesn}{\ensuremath{\mathsf{pES_n}}}
-
-% category of fusion domains 
-\newcommand{\WDomb}{\ensuremath{\mathsf{wDom_b}}}
-% category of domains
-\newcommand{\Domb}{\ensuremath{\mathsf{Dom_b}}}
-% category of prime algebraic domains
-\newcommand{\PDomb}{\ensuremath{\mathsf{pDom_b}}}
-
-%%%%% END NON BINARY CONFLICT
-
-% slice category
-\newcommand{\slice}[2]{\ensuremath{({#1} \downarrow {#2})}}
-
-% event structure for a domain
-\newcommand{\zev}[0]{\ensuremath{\mathcal{E}}}
-\newcommand{\ev}[1]{\ensuremath{\zev({#1})}}
-
-% from general to connected event structures
-\newcommand{\zconnes}[0]{\ensuremath{\mathcal{C}}}
-\newcommand{\connes}[1]{\ensuremath{\zconnes({#1})}}
-% and inclusion
-\newcommand{\zinces}[0]{\ensuremath{\mathcal{I}}}
-\newcommand{\inces}[1]{\ensuremath{\zinces({#1})}}
-
-% stable version
-\newcommand{\zsev}[0]{\ensuremath{\mathcal{E}_S}}
-\newcommand{\sev}[1]{\ensuremath{\zsev({#1})}}
-
-% with equivalence
-\newcommand{\zeveq}[0]{\ensuremath{\mathcal{E}_{eq}}}
-\newcommand{\eveq}[1]{\ensuremath{\zeveq({#1})}}
-
-% es with equivalence to es and vice
-\newcommand{\zfuse}[0]{\ensuremath{\mathcal{M}}}
-\newcommand{\fuse}[1]{\ensuremath{\zfuse({#1})}}
-\newcommand{\zunf}[0]{\ensuremath{\zunf}}
-\newcommand{\unf}[1]{\ensuremath{\mathcal{U}({#1})}}
-
-% Winskel/Droste version
-\newcommand{\zevwd}[0]{\ensuremath{\mathcal{E}_{wd}}}
-\newcommand{\evwd}[1]{\ensuremath{\zevwd({#1})}}
-
-% configurations of an event structure
-\newcommand{\conf}[1]{\ensuremath{\mathit{Conf}({#1})}}
-% finite configurations
-\newcommand{\conff}[1]{\ensuremath{\mathit{Conf_F}({#1})}}
-
-% product of the sets of minimal enablinsg
-\newcommand{\pmin}[1]{\ensuremath{U_{#1}}}
-
-% connectectedness of minimal enablinsg
-\newcommand{\conn}[1]{\ensuremath{\stackrel{#1}{\frown}}}
-
-% domain for an event structure or graph grammar
-\newcommand{\zdom}[0]{\ensuremath{\mathcal{D}}}
-\newcommand{\dom}[1]{\ensuremath{\zdom({#1})}}
-
-\newcommand{\zdomeq}[0]{\ensuremath{\mathcal{D}_{eq}}}
-\newcommand{\domeq}[1]{\ensuremath{\zdomeq({#1})}}
-
-% partial order for a graph grammar
-\newcommand{\poset}[1]{\ensuremath{\mathcal{P}({#1})}}
-
-% stable version
-\newcommand{\pdom}[1]{\ensuremath{\mathcal{D}_S({#1})}}
-\newcommand{\ppdom}[0]{\ensuremath{\mathcal{D}_S}}
-
-% powerset
-\newcommand{\Pow}[1]{\ensuremath{\mathbf{2}^{#1}}}
-
-% powerset of finite subsets
-\newcommand{\Powfin}[1]{\ensuremath{\mathbf{2}_\mathit{fin}^{#1}}}
-
-% powerset of subsets of cardinality <= 1
-\newcommand{\Powone}[1]{\ensuremath{\mathbf{2}_1^{#1}}}
-
-% integer interval
-\newcommand{\interval}[2][1]{\ensuremath{[{#1},{#2}]}}
-
-% domain interval
-\newcommand{\dint}[2]{\ensuremath{[{#1},{#2}]}}
-
-% set of intervals
-\newcommand{\IntSet}[1]{\ensuremath{\mathop{\mathit{Int}({#1})}}}
-
-% intervals to irreducibles and vice
-\newcommand{\inir}{\ensuremath{\mathop{\mathit{\zeta}}}}
-\newcommand{\irin}{\ensuremath{\mathop{\mathit{\iota}}}}
-
-% permutations
-\newcommand{\perm}{\sigma}
-
-% causes
-\newcommand{\causes}[1]{\ensuremath{\lfloor {#1})}}
-
-%%% GRAPH GRAMMARS
-
-\newcommand{\Abs}[1]{\ensuremath{\mathsf{Abs}({#1})}}
-\newcommand{\tr}[1]{\ensuremath{\mathsf{Tr}({#1})}}
-% fusion safe traces
-\newcommand{\trs}[1]{\ensuremath{\mathsf{Tr}_s({#1})}}
-%\newcommand{\graph}{\ensuremath{\mathsf{Graph}}}
-\newcommand{\tgraph}[1]{\ensuremath{\mathsf{Graph}_{#1}}}
-\newcommand{\can}[1]{\ensuremath{\mathsf{C}({#1})}}
-% source and target of a derivation
-\newcommand{\source}[1]{\ensuremath{\mathsf{s}({#1})}}
-\newcommand{\target}[1]{\ensuremath{\mathsf{t}({#1})}}
-\newcommand{\col}[1]{\ensuremath{\mathsf{col}({#1})}}
-
-% left decorated trace
-\newcommand{\ltrace}[1]{\ensuremath{\langle {#1}\rangle_c}}
-
-\newcommand{\bx}[1]{\phantom{\big(}#1{\phantom{\big)}}}
-\newcommand{\bxx}[1]{\,#1\,}
-\newcommand{\cycl}[1]{\ensuremath{\mbox{\textcircled{\scriptsize{$#1$}}}}}
-\renewcommand{\iff}{\ensuremath{\Leftrightarrow}}
-
-%%%%GENERAL CATEGORICAL NOTATION
-
-\newcommand{\gph}[1]{\textbf{\textup{{#1}-Graph}}}
-
-\newcommand{\mf}[1]{{#1}^\mathsf{m}}
-\newcommand{\dph}{\mathsf{dph}}
-%identità
-\newcommand{\id}[1]{\mathsf{id}_{#1}}
-%codominio
-\newcommand{\cod}[1]{\mathsf{cod}({#1})}
-	%Variabili categorie
-\def\A{\textbf {\textup{A}}}
-%mono
-\newcommand{\mto}[0]{\rightarrowtail}
-
-\newcommand{\sk}{\mathsf{sk}_{\X}}
-
-\def\R{\mathsf{R}}
-\def\B{\textbf {\textup{B}}}
-\def\C{\textbf {\textup{C}}}
-\def\D{\textbf {\textup{D}}}
-\def\X{\textbf {\textup{X}}}
-\def\Y{\textbf {\textup{Y}}}
-\def\G{\textbf {\textup{G}}}
-\def\Z{\textbf {\textup{Z}}}
-
-\newcommand{\dm}[1]{\mathsf{dom}({#1})}
-
-\newcommand{\sub}[3]{{\mathcal{#1}}\textrm{-}\mathsf{Sub}_{\textbf {\textup{#2}}}(#3)}
-
-\newcommand{\msub}[2]{\mathsf{Sub}_{\textbf {\textup{#1}}}(#2)}
-
-\newcommand{\ske}{\mathsf{sk}(\X)}
-\renewcommand{\P}{\textbf {\textup{P}}}
-
-%\derivazioni
-
-\newcommand{\dder}[1]{\mathscr{#1}}
-\newcommand{\sder}[2]{S_{i_1,i_2}(\mathscr{#1}, \mathscr{#2})}
-\newcommand{\der}[1]{\underline{\dder{#1}}}
-\def\dpo{\mathsf{C}^{\X}_R}
-\def\gpo{\mathsf{G}^{\X}_R}
-\def\dpi{[\mathsf{C}]^{\X}_R}
-\def\gpi{[\mathsf{G}]^{\X}_R}
-
-\newcommand{\ider}[1]{\mathscr{I}_{#1}}
-
-%categorie
-\def\Set{\textbf {\textup{Set}}}
-
-%comma
-\newcommand{\comma}[2]{#1\hspace{1pt} {\downarrow}\hspace{1pt} #2}
-\newcommand{\cma}[2]{\mathcal{#1}\hspace{1pt} {\downarrow}\hspace{1pt} \mathcal{#2}}
-
-%derivazioni
-\newcommand{\lpro}{\langle \hspace{-1.85pt}[}
-\newcommand{\rpro}{]\hspace{-1.85pt}\rangle}
-\newcommand{\tpro}[1]{\lpro \der{#1}\rpro}
-\newcommand{\tproi}[2]{\lpro \der{#1}_{#2}\rpro}
-\newcommand{\lgh}[0]{\mathsf{lg}}
-
-%%% NEW
-
-\usepackage{xparse}
-
-% inversions
-\newcommand{\inv}[1]{\mathsf{inv}({#1})}
-\newcommand{\tnv}[1]{\mathsf{tnv}({#1})}
-
-%% sequential independence
-%\newcommand{\seqind}{\ensuremath{\updownarrow}}
-
-% direct shift
-\newcommand{\shift}[1]{\ensuremath{\mathrel{{\leftrightsquigarrow}_{#1}}}}
-
-% shift equivalence
-\newcommand{\shifteq}[1][]{\ensuremath{\mathrel{{\equiv}^\mathit{sh}_{#1}}}}
-
-% transp{source}[target]: if target not specified source+1
-\NewDocumentCommand{\transp}{m o}{%
-  \ensuremath{({#1},%
-  \IfNoValueTF{#2}%
-    {{#1}+1}%
-    {#2}%
-    )}
-}
-
-\NewDocumentCommand{\mycommand}{o}{%
-  % <code>
-  \IfNoValueTF{#1}
-    {code when no optional argument is passed}
-    {code when the optional argument #1 is present}%
-  % <code>
-}
-% interchange
-\newcommand{\IC}[1]{\ensuremath{\mathit{IC}({#1})}}
-
-%%%%% Ambienti matematici  %%%%%%
-%\newtheorem{theorem}{Theorem}[section]
-%\newtheorem{proposition}[theorem]{Proposition}
-%\newtheorem{lemma}[theorem]{Lemma}
-%\newtheorem{corollary}[theorem]{Corollary}
-
-\newtheorem*{setting}{Setting}
-%\theoremstyle{definition}
-%\newtheorem{definition}[theorem]{Definition}
-\newtheorem*{notation}{Notation}
-%\newtheorem{remark}[theorem]{Remark}
-%\newtheorem{example}[theorem]{Example}
-
-% commands for restructuring
-\newcommand{\rem}[2]{{\color{blue}#1}{\color{red}#2}}
-\renewcommand{\rem}[2]{}
-
-% fake author for anonymous submission
-%\author{Alan Turing} 
-%{Department of Mathematics, Somewhere}
-%{alan@turing.com}{}{}
-
-\author{Paolo Baldan} 
-{Department of Mathematics, University of Padua, Italy}
-{baldan@math.unipd.it}
-{https://orcid.org/0000-0001-9357-5599}{}
-
-\author{Davide Castelnovo}
-{Department of Mathematics, University of Padua, Italy}
-{davide.castelnovo@math.unipd.it}
-{https://orcid.org/0000-0002-5926-5615}{}
-
-\author{Andrea Corradini}
-{Department of Computer Science, University of Pisa, Italy}
-{andrea.corradini@unipi.it}
-{https://orcid.org/0000-0001-6123-4175}{}
-
-\author{Fabio Gadducci}
-{Department of Computer Science, University of Pisa, Italy}
-{fabio.gadducci@unipi.it}
-{https://orcid.org/0000-0003-0690-3051}{}
-
-\authorrunning{P.~Baldan, D.~Castelnovo, A.~Corradini, F.~Gadducci}
-%
-\Copyright{Paolo Baldan, Davide Castelnovo, Andrea Corradini, and Fabio Gadducci}
-%
-\ccsdesc[500]{Theory of Computation~Models of computation}
-\ccsdesc[500]{Theory of Computation~Semantics and reasoning}
-%
-\keywords{
-Adhesive categories, double-pushout rewriting, left-linear rules, switch equivalence, local Church-Rosser property.
-}
-
-\funding{The research has been partially supported by the EuropeanUnion - NextGenerationEU under the National Recovery and Resilience Plan (NRRP) - Call PRIN 2022 PNRR - Project P2022HXNSC ``Resource Awareness in Programming: Algebra, Rewriting, and Analysis'', by the Italian MUR - Call PRIN 2022 - Project 20228KXFN2
-``Spatio-Temporal Enhancement of Neural nets for Deeply
-Hierarchical Automatised Logic'' and by the University of Pisa - Call PRA 2022 - Project 2022\_99 ``Formal Methods for the Healthcare Domain based on Spatial Information''.}
-
-\EventEditors{Rupak Majumdar and Alexandra Silva}
-\EventNoEds{2}
-\EventLongTitle{35th International Conference on Concurrency Theory (CONCUR 2024)}
-\EventShortTitle{CONCUR 2024}
-\EventAcronym{CONCUR}
-\EventYear{2024}
-\EventDate{Septembre 9--13, 2024}
-\EventLocation{Calgary, Canada}
-\EventLogo{}
-\SeriesVolume{311}
-\ArticleNo{6}
-
-\title{Concurrent semantics for left-linear rewriting [in adhesive categories]}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-  When moving from linear to left-linear rewriting, many properties
-  cease to hold (see concur), and some require to overcome new
-  obstacles to be proven. Here, we identify a very general class of
-  left-linear rewriting systems on adhesive categories where a
-  semantics based on event structures/domains with good properties can
-  be defined. Two semantic structures introduced previously, namely
-  connected event structures and weakly prime domains, introduced in
-  the context of graph rewriting, emerge as canonical structures for
-  rewriting with fusion in the context of adhesive categories.
-\end{abstract}
-
-%\tableofcontents
-
-\section*{Summary}
-
-\subsection*{1. Background}
-
-CONCUR results: strong enforcing + well-switching => nice behaviour of independence.
-
-\subsection*{2. A class of well behaved rewriting systems}
-[note pag. 11-19]
-
-Adhesive categories, with all POs, ...,
-coreflection with a subcat from which we take lhs and monos as right legs
-
-$\Rightarrow$
-
-- strong enforcing + well-switching
-
-- well-behaved with respect to quotients, e.g.,
-
-\begin{enumerate}[a.]
-\item  if we can rewrite $G$ with $L \leftarrow K \to R$ and we take a quotient
-  of $G$ which factorises through the colimit, then we can still rewrite
-
-\item if we can rewrite $G$ with $L \leftarrow K \to R$ and we take a $G'$ which
-  has $G$ as a quotient and we can find a match in $G'$ (which factorises
-  through the quotient) then we can still rewrite
-
-\item existence of the ``largest'' quotient to which a rule applies
-
-\item independence ``in the colimit'' [notes pag. 20-22 for ordinary
-  derivations, later adapt to derivations up to fusion, which are ordinary
-  derivations in the quotient]
-\end{enumerate}
-
-\subsection*{3. Domain and event structure semantics}
-
-\subsubsection*{3.1 Domain of traces}
-
-\begin{enumerate}[a.]
-
-\item  finitary, coherent, irreducible algebraic
-
-\item need of characterising the  irreducibles: traces with last step not switchable
-\end{enumerate}
-
-[notes page 1-9, this holds in general in the setting of concur]
-
-\subsubsection*{3.2 Weak prime domain and connected event structures}
-
-\begin{enumerate}[a.]
-
-\item Interchargeability relation and its characterisation via the notion
-  of derivation up to fusion
-
-\item derivations up to fusion and properties [notes pag. 24-27]
-
-\item characterising the interchangeability relation using
-derivations up to fusion [some idea at pag. 29, notes]
-
-\item  proving the interchangeability axioms to conclude that we
-obtain a weak prime domain [pag. 30-32, notes]
-\end{enumerate}
-
-\section{Introduction}
-
-\section{Background}
-\label{sec:back}
-
-\subsection{Consistent permutations}
-
-\section{A class of well-behaved rewriting systems}
-\label{sec:rewr}
-
-This section is devoted to the introduction and study of a, quite general, setting in which the study of the concurrency properties of left-linear DPO-rewriting systems can be carried on.
-
-\begin{setting}Let $(\X, \R)$ be a left-linear DPO-rewriting system on an $\mathcal{M}$-adhesive category $\X$. For the remaining of this section we assume the following properties:
-	\begin{enumerate}
-		\item $\X$ has all pushouts and pullbacks;
-		\item there is a proper and stable factorization system $(\mathcal{E}, \mathcal{M})$ on $\X$;
-		\item $(\X, \R)$ is strong-enforcing;
-		\item there is a good coreflective subcategory $\Y$ of $\X$ containing that the left- hand side of every rule in $\R$;
-		\item $ I_{\Y}\circ R_{\Y}$ sends arrows who are in  $\mathcal{R}_\Y\cap \mathcal{E}$ to arrows in $\mathcal{E}$;
-		\item $\mathcal{R}_\Y $ contains the right leg of every rule in $\R$.
-	\end{enumerate}
-
-	Given an arrow $f\colon X\to Y$ of $\X$,  we will use the following notational conventions:
-	\begin{itemize}
-		\item $f\colon X\mto Y$ if $f$ belongs to $\mathcal{M}$;
-		\item $f\colon X\eto Y$ if $f$ belongs to $\mathcal{E}$;
-		\item $f\colon X \rto Y$ if $f$ belongs to $\mathcal{R}_\Y$ ;
-		\item $f\colon X \fto Y$ if $f$ is a \emph{fusion}, i.e.~belongs to both $\mathcal{R}_\Y$ and $\mathcal{E}$. 
-		\end{itemize}
-
-		Given an object $X$, we can consider the poset $\fuse{X}$
-\end{setting}
-
-\begin{proposition}\label{prop:fusion}
-	The class of fusions is stable under pullbacks, pushouts and closed under composition. Moreover, the image of a fusion through $I_\Y\circ R_{\Y}$ is again a fusion.
-\end{proposition}
-\begin{proof}
-	By \Cref{prop:varie} we know that $\mathcal{R}_\Y$ is closed under composition and stable under pullbacks, while it is stable under pushout by definition.
-On yhe other hand, $\mathcal{E}$ is stable under pushout and closed under composition by \Cref{cor:iso2}.
-By hypothesis $(\mathcal{E}, \mathcal{M})$ is stable and so $\mathcal{E}$ is stable under pullbacks.
-Let now $e\colon X\fto Y$ be a fusion we have a diagram:
-	\[\xymatrix@C=35pt{R_\Y(I_\Y(R_{\Y}(X))) \ar[r]^-{R_\Y(\epsilon_X)} \ar[d]_{R_\Y(I_\Y(R_\Y(e)))}&R_{\Y}(X) \ar[d]^{R_\Y(e)}\\R_\Y(I_\Y(R_{\Y}(Y))) \ar[r]_-{R_\Y(\epsilon_Y)}&R_\Y(Y)}\]
-
-	By \Cref{cor:cou} the horizontal arrows are isomorphisms and $R_\Y(e)$ is mono because $e$ is a fusion, thus $I_\Y(R_\Y(e))$ is in $\mathcal{R}_\Y$.
-By hypothesis $I_\Y(R_\Y(e))$ is in $\mathcal{E}$ and we can conclude.
-\end{proof}
-
-\begin{example}
-\todo{grafi}
-\end{example}
-
-\begin{remark}\label{rem:ws}
-Under the conditions of our setting, the system $(\X, \R)$ is well switching.
-Indeed, suppose that the diagram below is given.
-Since $f_1$ is in $\mathcal{M}$ we have that $j_0=i_0$, on the other hand, $L_1$ belongs to $\Y$ and $g_0$ belongs to $\mathcal{R}_\Y$, and so $j_1$ is equal to $i_1$ by the fourth point of \Cref{prop:varie}.
-	\[\xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]_{r_0}^{\mini} & R_0 \ar@/^.3cm/@<-.5ex>[drrr]|(.22)\hole|(.32)\hole_(.4){i_0} \ar@<.5ex>@/^.3cm/[drrr]|(.3)\hole|(.39)\hole^(.7){j_0} \ar[dr]|(.29)\hole|(.35)\hole_{h_0} && L_1 \ar@<.5ex>@/_.3cm/[dlll]^(.4){i_1} \ar@<-.5ex>@/_.3cm/[dlll]_(.7){j_1} \ar[dl]|(.29)\hole|(.35)\hole^(.6){m_1}& K_1\ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[rr]_{r_1}^{\mini} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0} D \ar[rr]_{g_0}^{\mini}&& G_1  && \ar@{>->}[ll]^{f_1} D_1 \ar[rr]_{g_1}^{\mini}&& G_2}\]
-\end{remark}
-
-\begin{lemma}Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^{n}$ be a derivation, then the following hold true:
-	\begin{enumerate}
-		\item $\iota_{\der{D}, G_0}\colon G_0\to \tpro{D}$ belongs to $\mathcal{R}$ and $\iota_{\der{D}, G_{n+1}}\colon G_{n+1}\to \tpro{D}$ belongs to $\mathcal{M}$;
-		\item for every $i\in [0, n+1]$, there are  arrows $m_i$ in $\mathcal{M}$ and $r_i$ in $\mathcal{R}$ such that the coprojection $\iota_{\der{D}, G_i}\colon G_i\to \tpro{D}$ is equal to $r_i\circ m_i$.
-	\end{enumerate}
-\end{lemma}
-\begin{proof}
-	\begin{enumerate}		
-		\item We proceed by induction on the length of $\der{D}$.
-
-		\smallskip \noindent $\lgh(\dder{D})=0$. then $\tpro{\dder{D}}$ is simply $(G_0, \{\id{G_0}\})$ and $\id{G_0}$ belongs to $\mathcal{M}$ and $\mathcal{R}$.
-
-		\smallskip \noindent$\lgh(\dder{D})=1$. Suppose that $\dder{D}$ has as its single component the derivation
-		\[\xymatrix{L_0 \ar[d]_{m_0}& K_0 \ar[d]^{k_0}\ar@{>->}[l]_{l_0} \ar[r]_{r_0}^{\mini} & R_0 \ar[d]^{h_0} \\G_0& \ar@{>->}[l]^{f_0} D_0 \ar[r]_{g_0}^{\mini}& G_1  \\}\]
-	Then the thesis follows since we have the following pushout square.
-		\[\xymatrix{D_0 \ar@{>->}[d]_{f_0} \ar[r]_{g_0}^{\mini} & G_1 \ar@{>->}[d]^{\iota_{\der{D}, G_1}} \\G_0 \ar[r]_-{\iota_{\der{D}, G_0}}^{\mini}& \tpro{D} }\]
-
-		\smallskip \noindent$\lgh(\dder{D})\geq 2$.
-Let $\der{D}$ be $\{\dder{D}_i\}_{i=0}^n$ with $n\geq 1$.
-Let also $\der{D}'$ be $\{\dder{D}_i\}^{n-1}_{i=0}$ and $\rho_n=(l_n, r_n)$ be the rule applied in $\dder{D}_n$.
-The thesis follows from the inductive hypothesis and the diagram below.
-		\[\xymatrix@C=30pt{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar@{>->}[l]_{l_{n}} \ar[r]_{r_{n}}^{\mini} & R_{n} \ar[d]^{h_n} \\ G_{n} \ar@{>->}[d]_{\iota_{\der{D}' , G_{n}}}& \ar@{>->}[l]^{f_n} D_n \ar[r]^{\mini}_{g_n}& G_{n+1}  \ar@{>->}[d]^{\iota_{\der{D}, G_{n+1}}}\\  \lpro \der{D}' \ar[rr]_{p}^{\mini} \rpro && \tpro{D}\\ G_0 \ar[u]^-{\iota_{\der{D}', G_{0}}}_{\mini} \ar@/_.5cm/[urr]_{\iota_{\der{D}, G_0}}^\mini}\]
-
-		\item We proceed again by induction the length of $\der{D}$.
-
-		\smallskip \noindent$\lgh(\dder{D})=0$. This follows at once from the previous point.
-
-		\smallskip \noindent$\lgh(\dder{D})=1$. Again, this follows from the previous point.
-
-		\smallskip \noindent$\lgh(\dder{D})\geq 2$.
-As above, if $\der{D}$ is $\{\dder{D}_i\}_{i=0}^n$ with $n\geq 1$, we can consider the derivation $\der{D}':=\{\dder{D}_i\}^{n-1}_{i=0}$ and consider the rule $\rho_n$ be the rule applied in $\dder{D}_n$.
-By the inductive hypothesis, for every $i\in [0,n]$ we have the diagram below.
-		\[\xymatrix@C=30pt{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar@{>->}[l]_{l_{n}} \ar[r]_{r_{n}}^{\mini} & R_{n} \ar[d]^{h_n} \\ G_{n} \ar@{>->}[d]_{\iota_{\der{D}' , G_{n}}}& \ar@{>->}[l]^{f_n} D_n \ar[r]^{\mini}_{g_n}& G_{n+1}  \ar@{>->}[d]^{\iota_{\der{D}, G_{n+1}}}\\  \lpro \der{D}' \ar[rr]_{p}^{\mini} \rpro && \tpro{D}\\X \ar[u]^{r_i}_{\mini} &&  G_i \ar[ull]^-{\iota_{\der{D}', G_{i}}} \ar[u]_{\iota_{\der{D}, G_i}} \ar@{>->}[ll]^{m_i}}\]
-
-		The thesis now follows since $\mathcal{R}$ is closed under composition. To conclude, it is enough to notice that  the thesis for $i=n+1$ follows immediately from point $1$. 
-		\qedhere 
-	\end{enumerate}
-\end{proof}
-\begin{corollary}
-	\todo{match}
-\end{corollary}
-
-Our next step is to show that, in our setting, there is a kind of ``minimum'' fusion of an object $X$ to which a rewriting rule can be applied.
-
-\begin{definition} Let $\rho$ be a rule $(l, r)$ in $\R$ with left-hand side $L$.
-Let $e\colon X\fto Y$ and $e'\colon X\fto Y'$ be two fusions with the same domain and $m\colon L\to Y$ and $m'\colon L\to Y'$ be two arrows, we say that the pairs $(e,m)$ and $(e', m')$ are \emph{compatible with respect to $\rho$} if the following diagram is commutative, where the outer square is a pushout.
-
-\[\xymatrix{X\ar@{>>}[rr]^\mini_{e} \ar@{>>}[dd]_{e'}^\mini & & Y \ar@{>>}[dd]_{q}^\mini\\ &L  \ar[ur]_{m} \ar[dl]^{m'}\\Y' \ar@{>>}[rr]_{q'}^{\mini} && Q}\]
-
-Given a fusion $e\colon X\fto Y$ and an arrow $m\colon L\to Y$, we will denote by $\mathcal{F}_\rho(e, m)$ the class of pairs compatible with $(e, m)$ with respect to a given rule $\rho$.  
-\end{definition}
-
-\begin{example}
-	tutti i sotto quozienti
-\end{example}
-
-\begin{lemma}
-	Let $e\colon X\fto Y$, $\rho\in \R$ with left-hand side $L$ and $m\colon L\to Y$ be such that $\mathcal{F}_\rho(e, m)$.
-Then there exists a fusion $(\mf{e},\mf{m})\colon L\to \mf{Y}$  in $\mathcal{F}_\rho(e, m)$ and for every other $(e', m')$ in it there exists $f\colon \mf{Y}\to Y'$, where $Y'$ is the codomain of $e'$, such that:
-\[f\circ e =e' \qquad f\circ m=m'\]
-\end{lemma}
-
-\begin{proof}By hypothesis $I$ is non-empty, thus we can consider $k$ in it and $e_k\colon X\to Y_k$.
-Consider the two diagrams below, where the upper square  in the inner rectangle one is the image through $I_\Y\circ R_\Y$ of a pullback square, while the outer rectangle is a pushout.
-Notice that, by hypothesis and \Cref{prop:fusion}, all the horizontal arrows and the coprojection $e\colon X\to Y$ are fusions and, moreover, there exists the dotted arrow $f_k\colon Y\to Y_k$.
-	\[\xymatrix@C=55pt{I_\Y(R_\Y(P)) \ar[d]_{I_\Y(R_\Y(p_2)) } \ar@{>>}[r]_-{I_\Y(R_\Y(p_1))}^{\mini} & I_\Y(R_\Y(L)) \ar@/^.4cm/[dddr]^{q} \ar[d]_{I_\Y(R_\Y(m_k)) } \\ I_\Y(R_\Y(X)) \ar[d]_{\epsilon_X} \ar@{>>}[r]_-{I_\Y(R_\Y(e_k))}^{\mini}& I_\Y(R_\Y(Y_k)) \ar[d]_{\epsilon_X}  \\ X\ar@{>>}@/_.5cm/[drr]^{\mini}_{e} \ar@{>>}[r]_{e_k}^{\mini}& Y_k \\ &&Y\ar@{.>}[ul]_{f_k}}\]
-
-	Let now $i$ be any other element of $i$.
-
-\end{proof}
-
- \begin{corollary}
-\todo{quoziente minimo}
- \end{corollary}
-
-Finally....
-
-\todo{indipendenza}
-
-\subsection{Derivations with fusions}
-
-\section{Domain and event structure semantics}
-\subsection{Domain of traces}
-\subsection{Weak prime domain and connected event structures}
-
-\bibliographystyle{plain}
-\bibliography{bibliog.bib}
-
-\appendix
-
-\section{Preliminaries on subobjects, images, pullbacks and factorization systems}\label{app:fact}
-
+\chapter{Preliminaries on subobjects, images, pullbacks and factorization systems}\label{app:fact}
 This first section is devoted to recall some classic notions related to subobjects, pullbacks and ways to factorize an arrow.
 The main source for the presentation is \cite[Ch.~1]{dikranjan2013categorical}.
-\subsection{The pullback functor and right $\mathcal{M}$-images}
 
+\section{The pullback functor and right $\mathcal{M}$-images}
 Let us start defining the \emph{pullback functor} and show how the existence of a left adjoint to it yields a notion of image of an arrow.
@@
 
-\subsection{Factorization systems}
+\section{Factorization systems}
 
@@
 
-\subsection{$\mathcal{M}$-subobjects and factorization systems}
+\subsection{$\mathcal{M}$-subobjects and factorization systems}\label{app:sub}
 
@@
 
-Now, let us recall the following lemma, which is the application of the Adjoint Functor Theorem to the partial ordered case.
+Now, let us recall the following lemma, which is the application of the Adjoint Functor Theorem \cite{freyd1964abelian,freyd1990categories} to the partial ordered case.
 
@@
 
-The previous result, together with \Cref{cor:fact} and \Cref{prop:finlim}, allows us to deduce the following result, which has been used in \cite{baldan2011lattice,braatz2010finitary} to show that certain $\mathcal{M}$-adhesive categories have a factorization system.
+The previous Lemma, together with \Cref{cor:fact} and \Cref{prop:finlim}, allows us to deduce the following result.
 
@@
 \end{corollary}
-
-\section{Coreflective subcategories}
-
-In order to identify a class of well-behaved DPO-rewriting system we need to recall some other general notion of category theory.
-
-\begin{definition}
-	Let $\X$ be a category, a full subcategory $\Y$ of $\X$ is \emph{coreflective} if the inclusion functor $I_\Y\colon \Y\to \X$ has a right adjoint $R_\Y$, called \emph{coreflector}.
-A morphism between two coreflective subcategories $\Y$ and $\Z$ is a functor $F\colon \Y \to \Z$ such that $I_\Z \circ F=I_\Y$ and $F\circ R_\Y$ is isomorphic to $R_\Z$.
-
-	We will denote by $\cori(\X)$ the category obtained in this way.
-\end{definition}
-
-\begin{remark}
-	Notice that, since adjoints are unique up to isomorphism, being a morphism $\Y\to \Z$ of $\cori(\X)$ does not depends on the choice of coreflectors for $\Y$ and $\Z$.
-\end{remark}
-
-\begin{remark}\label{rem:ff}
-	Let $F\colon \Y \to \Z$ be a morphism in $\cori(\X)$.
-Since $I_\Z\circ F=I_\Y$, then $\Y$ must be a full subcategory of $\Z$ and $F$ must coincide with its inclusion.
-In particular, $F$ is full and faithful and $\cori(\X)$ is a ordered class.
-\end{remark}
-
-\begin{example}\label{ex:1}
-	\todo{connessi}
-\end{example}
-
-\begin{example}\label{ex:2}
-	\todo{grafi con equivalenza}
-\end{example}
-\begin{example}
-	\todo{Ce ne sono altri? sarebbe bello usare i calcoli ma credo rientrino nel primo}
-\end{example}
-
-Let us recall the following well known fact.
-
-\begin{proposition}\label{prop:counit}
-	Let $L\colon \X\to \Y$ and $R\colon \Y \to \X$ be a pair of functors such that $L\dashv R$. Then the following are equivalent:
-	\begin{enumerate}
-		\item $L$ is full and faithful;
-		\item the unit $\eta \colon \id{\X}\to R\circ L$ is an isomorphism.
-	\end{enumerate} 
-\end{proposition}
-\begin{proof}
-	We can start noticing that, for every pair of objects $X$ and $Y$ in $\X$, we have two functions:
-	\[F_{X, Y}\colon \X(X, Y)\to \Y(L(X), L(Y)) \quad 	 \Phi_{X, Y}\colon \Y(L(X), L(Y))\to \X(X, R(L(Y)))\]
-	where $F_L$ sends $f\colon X\to Y$ to $L(f)$ and $\Phi_{X, Y}$ is the bijection $\Y(L(X), L(Y))\to \X(X, R(L(Y)))$ given by $L\dashv R$.
-Now, notice that, for every $f\colon X\to Y$ the diagram below commutes.
-	\[\xymatrix@C=35pt{X \ar[r]^{f} \ar[d]_{\eta_X}& Y \ar[d]^{\eta_Y}\\R(L(X)) \ar[r]_-{R(L(f))} &R(L(Y)) }\]
-
-	This, in turn, entail that the composit $\Psi_{X,Y} \circ F_{X, Y}$ coincides with $\eta_Y\circ (-)$.
-
-	\smallskip \noindent 
-	$(1\Rightarrow 2)$ Let $X$ and $Y$ be two objects of $\X$, by hypothesis $\eta_Y$ is an isomorphism and so $\eta_Y\circ (-)$ is a bijection.
-But then $F_{X, Y}$ must be a bijection too by what we have observed above.
-
-	\smallskip \noindent 
-	$(2\Rightarrow 1)$ Let $X$ be an object of $\X$, if $L$ is full and faithful then $\eta_Y\circ (-)$ is the composition of the two bijections $\Psi_{Y,Y}\circ F_{Y,Y}$.
-By the Yoneda Lemma this entails that $\eta_Y$ is an isomorphism.
-\end{proof}
-
-\begin{corollary}\label{cor:cou}
-Let $L\colon \X\to \Y$ and $R\colon \Y \to \X$ be a pair of functors such that $L\dashv R$ and suppose that $L$ is full and faithful.
-Let $\epsilon\colon L\circ R\to \id{\Y}$ be the unit of the adjunction, then the following are true for every object $X$:
-\begin{enumerate}
-	\item the arrow $R(\epsilon_X)$ is an isomorphism;
-	\item $L(R(\epsilon_X))$ is equal to $\epsilon_{L(R(X))}$.
-\end{enumerate}
-\end{corollary}
-\begin{proof}
-	\begin{enumerate}
-		\item Let $\eta\colon \id{X}\circ R\circ L$ be the unit of the adjunction.
-By the triangular identity we know that $R(\epsilon_X)\circ \eta_{R(X)}=\id{R(X)}$.
-The thesis now follows from \Cref{prop:counit}.
-		\item Using again the triangular identities and the previous point we have
-		\begin{align*}
-			\id{L(R(X))}&=\epsilon_{L(R(X))}\circ L(\eta_{R(X)})\\&= \epsilon_{L(R(X))}\circ L(R(\epsilon_X))^{-1}
-		\end{align*}
-		Which yields the theis. \qedhere 
-	\end{enumerate}
-\end{proof}
-
-\begin{corollary}\label{cor:counit}
-	Let $\Y$ be a coreflective subcategory of $\X$ and let $\epsilon \colon I_\Y\circ R_\Y \to  \id{\X}$ be the counit of $I_\Y\dashv R_\Y$. Given an object $X\in \X$, the following are equivalent:
-	\begin{enumerate}
-		\item $X$ is in the essential image of the inclusion $I_\Y$;
-		\item $\epsilon_X$ is an isomorphism.
-	\end{enumerate} 
-\end{corollary}
-\begin{proof}
-	$(1\Rightarrow 2)$ By hypothesis there is an object $Y$ of $\Y$ and an isomorphism $\phi\colon I_\Y(Y)\to X$. This, in turn, yields the commutative square below.
-	\[\xymatrix@C=40pt{I_\Y(Y) \ar[r]^-{\phi} \ar[d]_{I_\Y(\eta_Y)}&  X\\ I_\Y(R_\Y(I_\Y(Y)))  \ar[r]_-{I_\Y(R_\Y(\phi))}& I_\Y(R_\Y(X)) \ar[u]_{\epsilon_X}}\]
-
-	By hypotesis $\phi$ is an isomorphism and $\eta_Y$ is so by \Cref{prop:counit}, thus $I_\Y(\eta_Y)$ and 
-	$I_\Y(R_\Y(\phi))$ are isomorphisms too and the thesis follows.
-
-	\smallskip \noindent
-	$(2\Rightarrow 1)$ This is a tautology.
-\end{proof}
-
-Associated to a coreflective subcategory $\Y$ of $\X$ we have a class of arrows which enjoys some useful properties.
-
-\begin{definition}
-	Let $\Y$ be a coreflective subcategory of $\X$ with coreflector $R_\Y$, we define the class $\mathcal{R}_\Y$ as the class of all arrows in $\X$ whose image through $R_\Y$ is a mono in $\Y$.
-\end{definition}
-
-\begin{remark}
-	Let $I_\Y\colon \Y \to \X$ be the inclusion functor of a coreflective subcategory $\Y$.
-If $R_\Y$ and $R'_\Y$ are coreflectors, then we have a natural isomorphism $\phi\colon R_\Y\to R'_\Y$ and so, for every $f\colon X\to Y$ there is a square
-	\[\xymatrix{ \ar[d]_{\phi_X} R_\Y(X) \ar[r]^{R_\Y(f)}& R_\Y(Y) \ar[d]^{\phi_Y}\\R'_\Y(X) \ar[r]_{R_\Y(f)} & R'_\Y(Y)}\]
-
-	In particular, $R_\Y(f)$ is mono if and only if $R'_\Y(f)$ is so, thus the definition of $\mathcal{R}_\Y$ is independent from the choice of coreflector.
-\end{remark}
-
-\begin{proposition}\label{prop:varie}
-	Let $\Y$ be a coreflective subcategory of $\X$. Then the following hold true:
-	\begin{enumerate}
-		\item $\mathcal{R}_\Y$ contains all monos;
-		\item $\mathcal{R}_\Y$ is stable under pullbacks;
-		\item given $f\colon X\to Y$ and $g\colon Y\to Z$, if $g\circ f$ is in $\mathcal{R}_\Y$ then $f$ is in $\mathcal{R}_\Y$ too;
-		\item given $f\colon X\to Y$ in $\mathcal{R}_\Y$ and $g,h\colon I_\Y(Z)\rightrightarrows X$, if $f\circ g = f\circ h$, then $g=h$.
-	\end{enumerate}
-\end{proposition}
-\begin{proof}\begin{enumerate}
-		\item This follows at once from the fact that $R_\Y$, being a right adjoint, preserves monos.
-		\item Consider the following two diagrams, with $f\in \mathcal{R}_\Y$, in which the left one is a pullback. $R_\Y$ preserves limits, thus the right square is a pullback too.
-		\[\xymatrix@C=30pt{P \ar[r]^{p_1} \ar[d]_{p_2}& X \ar[d]^{f} & R_\Y(P) \ar[r]^{R_\Y(p_1)} \ar[d]_{R_\Y(p_2)} & R_\Y(X) \ar[d]^{R_\Y(f)}\\Z \ar[r]_{g}& Y & R_\Y(Z) \ar[r]_{R_\Y(g)} & R_\Y(Y)}\]
-		By definition, $R_\Y(f)$ is a mono in $\Y$, but this implies that $R_\Y(g)$ is a mono too, proving $g\in \mathcal{R}_\Y$.
-		\item We know that $R_\Y(g\circ f)$ is mono, thus $R_\Y(f)$ is mono too.
-		\item 	Since $f\circ g=f\circ h$ and $f$ is in $\mathcal{R}_\Y$ we can conclude that $R_\Y(g)=R_\Y(h)$. Thus we have:
-		\begin{align*}
-			g\circ \epsilon_{I_\Y(Z)}&=\epsilon_X\circ I_\Y(R_\Y(g))\\&=\epsilon_X\circ I_\Y(R_\Y(h))\\&=h\circ \epsilon_{I_\Y(Z)}
-		\end{align*}
-		By \Cref{cor:counit},  $\epsilon_{I_\Y(Z)}$ is an isomorphism and so $g=h$. \qedhere
-	\end{enumerate}
-\end{proof}
-
-In general, the class $\mathcal{R}_{\Y}$ is not stable under pushout. Nonetheless such property is desirable. We are thus lead to the following definition.
-
-\begin{definition}
-	A coreflective subcategory is \emph{good} if  $\mathcal{R}_\Y$ is stable under pushout. $\gori(\X)$ will denote the subcategory of $\cori(\X)$ given by good coreflective subcategories. 
-\end{definition}
-
-\iffalse 
-\begin{remark}\label{rem:good}
-	Let $\Y$ be a full subcategory of $\X$ with coreflector $R_\Y$.
-Let also $f\colon X\to Y$ be in $\mathcal{R}_\Y$ and consider the following two diagrams, where the left one is a pushout.
-Then $\Y$ is a good subcategory if and only if $R_{\Y}()$
-\end{remark}
-\fi
-
-We end this section extending the construction of $\mathcal{R}_\Y$ to a functor on $\cori(\X)$.
-
-\begin{proposition}\label{prop:funct}
-	Let $F\colon \Y \to \Z$ be a morphism of $\cori(\X)$, then $\mathcal{R}_\Z \subseteq \mathcal{R}_{\Y}$.
-\end{proposition}
-\begin{proof}
-	Let $f$ be an arrow in $\mathcal{R}_\Z$.
-Since $F$ is an arrow in $\cori(\X)$ we know that there exists a natural isomorphism $\phi\colon F\circ R_\Y\to R_\Z$, therefore $F(R_\Y(f))$ is a monomorphism.
-By \Cref{rem:ff} we know that $F$ is full and faithful and so reflects mono, implying that $f$ belongs to $\mathcal{R}_\Y$ too.
-\end{proof}
-
-\begin{corollary}\label{cor:funct}
-	Let $\cla(\X)$ be the category associated to the collection of all classes of a category $\X$, ordered by the inclusion.
-Then there exists a functor $\mathcal{R}_{(-)}\colon \cori(\X)^{op}\to \cla(\X) $.
-
-	Let, moreover, $\pos(\X),$ be the subcategory of $\cla(\X)$  given by classes of arrows stable under pushouts, Then  $\mathcal{R}^G_{(-)}\colon \gori(\X)^{op}\to \pos(\X) $ fitting in the rectangle below, where the vertical arrows are inclusions.
-	\[\xymatrix{\cori(\X)^{op} \ar[r]^{\mathcal{R}_{(-)}}& \cla(\X)\\ \gori(\X)^{op} \ar[u]^{J} \ar[r]_{\mathcal{R}^{G}_{(-)}}& \pos(\X) \ar[u]_{I}}\]
-\end{corollary}
-
-\iffalse 
-\begin{definition}
-	A \emph{comonad} $\m{C}$ on a category $\X$ is a triple $(C, \delta, \epsilon)$ given by a functor $C\colon \X\to \X$ and two natural transformations $\delta\colon C\to C\circ C $, $\epsilon\colon C\to \id{\X}$, called, respectively \emph{comultiplication} and \emph{counit} such that the following diagram commute
-	\[\xymatrix@C=30pt{C \ar[d]_{\delta}\ar[r]^-{\delta}& C\circ C  \ar[d]^{\delta*C}&  C \ar[d]_{\delta}\ar[r]^{\delta} \ar[dr]^-{\id{C}} & C\circ C \ar[d]^{\epsilon *C}\\ C\circ C \ar[r]_-{C*\delta}& C\circ C\circ C & C\circ C \ar[r]_-{C*\epsilon} & C}\]
-
-	A comonad $\m{C}$ is \emph{idempotent} if $\delta$ is an isomorphism.
-A \emph{morphism} between two comonad $\m{C}=(C, \delta, \epsilon)$ and $\m{D}=(D, \mu, \eta)$ is a natural transformation $\chi\colon C\to D$ such that the following diagrams commute
-	\[\xymatrix@C=30pt{ C \ar[r]^-{\delta} \ar[d]_{\chi} & C\circ C \ar[d]^{\chi*\chi}& C \ar[r]^{\epsilon} \ar[d]_{\chi}& 
-		\id{\X}  \\ D \ar[r]_-{\mu} & D\circ D
-		& D \ar[ur]_{\eta} }\]
-
-	We will denote by $\cmd(\X)$ the (possibly not locally small) category whose objects are idempotent comonads and whose arrows are morphisms of monads.
-\end{definition}
-
-\begin{remark} Let us recall that, given two functors $F, G\colon \X\rightrightarrows \Y$ and a natural transformation $\chi$ between them, then for every $X\in \X$ we have a naturality square
-	\[\xymatrix@C=40pt{F(F(X)) \ar[r]^{F(\chi_X)} \ar[d]_{\chi_{F(X)}}& F(G(X)) \ar[d]^{\chi_{G(X)}}\\G(F(X)) \ar[r]_{G(\chi_X)} & G(G(X))}\]
-
-	This entails that $(\chi * G)\circ (F*\chi)$ and $(G*\chi) \circ (\chi* F)$ are the same natural transformation, which we denote by $\chi*\chi$.
-\end{remark}
-
-\begin{proposition}
-	Let $L\colon \X \to \Y$ and $R\colon \Y \to \X$ be two functors such that $L\dashv R$.
-If $\eta \colon \id{\X}\to R\circ L$ and $\epsilon\colon L\circ R \to \id{Y}$ are the unit and the counit of this adjunction, then $(L\circ R, L*\eta *R ,\epsilon)$ is a comonad on $\Y$.
-\end{proposition}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-The next definition shows that every comonad come from an adjunction.
-
-\begin{definition}
-	contenuto...
-\end{definition}
-
-\begin{proposition}
-	contenuto...
-\end{proposition}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-We recall the following lemma relating idempotent comonads and coreflective subcategories.
-
-\begin{lemma}\label{lem:comsub}
-	Let $L\colon \Y\to \X$ and $R\colon \X \to \Y$ be two functors such that $L\dashv R$
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-Associated to any idempotent comonad we have a class of arrows.
-
-\begin{definition}
-	Let $\m{T}$ be an idempotent comonad on a category $\X$. We say that an arrow $f:X\to Y$ i
-\end{definition}
-\begin{remark}
-	contenuto...
-\end{remark}
-\fi
-
-\subsection{A left adjoint to $\mathcal{R}_{(-)}$}
-
-In this section we will show that, under suitable hypotheses, the functors $\mathcal{R}_{(-)}$ and $\mathcal{R}^G_{(-)}$ built in the previous sections, both have left adjoints.
-To do so, we need some preliminary work to be done.
-
-\begin{definition}
-	Let $\mathcal{M}$ be a class of arrows in a category $\X$ and let $\{m_i\}_{i\in I}$ be a family of objects in $\mathcal{M}/X$.
-We say that $\{m_i\}_{i\in I}$ has the \emph{epic $\mathcal{M}$-sum property} if:
-	\begin{enumerate}
-		\item it has a  coproduct $m\colon M\to X$;
-		\item the family  of coprojection $\{k_i\}_{i\in I}$ is jointly epic in $\X$.
-	\end{enumerate}
-
-	We say that $\X$ has \emph{epic $\mathcal{M}$-sums} if every family in $\sub{M}{X}{X}$ has the epic $\mathcal{M}$-sum property.
-\end{definition}
-
-Clearly the family $\{k_i\}_{i\in I}$ is always epic in $\mathcal{M}/X$, but from this it does not follow that it is so in $\X$, as shown from the following example.
-
-\begin{example}Let $\cat{Top}$ be the category of topological spaces and $\mathcal{C}$ the category of closed embeddings, and  consider the family $\{c_i\}_{i\in \mathbb{N}}$, where $c_i$ is the inclusion of $[\frac{1}{i+1}, +\infty)$ into $\mathbb{R}_{\geq 0}$.
-In $\mathcal{C}/\mathbb{R}_{\geq 0}$ their coproduct is the  identity $\id{\mathbb{R}_{\geq 0}}$.
-To see that the family of coprojections $\{k_i\}_{i\in \mathbb{N}}$ is not jointly epic in $\cat{Top}$, we can consider the space $X$ given by the quotient of $\mathbb{R}_{\geq 0}+\mathbb{R}_{\geq 0}$ by the equivalence relation generated from
-	\[R:=\{(x, y)\in X\times X \mid x=\iota_1(r), y=\iota_2(r) \text{ for some } r \in \mathbb{R}_{\geq 0}\smallsetminus\{0\}\}\]
-	Now, let $\pi$ be the quotient map and define $f_1, f_2\colon \mathbb{R}_{\geq 0}\rightrightarrows X$ as $\pi\circ \iota_1$ and $\pi \circ \iota_2$, respectively.
-Then, for every $i\in \mathbb{N}$ we have that $f_1\circ c_i=f_2\circ c_i$ because, given $r\in [\frac{1}{i+1}, +\infty)$ we have
-	\begin{align*}
-		f_1(c_i(r))&=\pi(\iota_1(c_i(r)))\\&=\pi(\iota_1(r))\\&=\pi(\iota_2(r))\\&=\pi(\iota_1(c_i(r)))\\&=f_1(c_i(r))
-	\end{align*}
-
-On the other hand, $f_1(0)\neq f_2(0)$, thus $\cat{Top}$ does not have epic $\mathcal{C}$-sums.
-\end{example}
-\begin{example}
-	\todo{insiemi}
-\end{example}
-
-\begin{example}
-	\todo{adesive finitare}
-\end{example}
-\begin{example}
-	\todo{simple graph}
-\end{example}
-
-We are now ready to construct a left adjoint to $\mathcal{R}_{(-)}$.
-
-\begin{definition} 
-	Let $\X$ be a category and $\mathcal{A}$ a class of arrows of it.
-We define the category $\C(\mathcal{A})$ as the full subcategory of $\X$ given by the objects $Z\in \X$ such that, for every  pair of arrows $g,h\colon Z\rightrightarrows X$, if $f\circ g=f\circ h$ for some $f\colon X\to Y$ belonging to $\mathcal{A}$, then $g=h$.
-\end{definition}
-
-A first thing that we can notice about $\C(\mathcal{A})$ is that, in the presence of a factorization system, is its closure under epimorphisms, as shown by the following proposition.
-
-\begin{proposition}\label{prop:ima}
-	$\mathcal{A}$ be a class of arrows in a category $\X$ If $e\colon X\to Y$ is an epimorphism with domain in $\C(\mathcal{A})$, then $Y$ belongs to $\C(\mathcal{A})$ too.
-\end{proposition}
-\begin{proof}
-	Let $f\colon Z\to V$ be an arrow of $\mathcal{A}$ and take two other arrows $g,h\colon Y\to Z$ such that $f\circ g=f\circ h$. Then we also know that
-	\[f\circ g\circ e= f\circ h\circ e\]
-	By hypothesis $X$ is in $\C(\mathcal{A})$, so that $g\circ e=f\circ e$. The thesis now follows since $e$ is an epimorphism.
-\end{proof}
-\begin{example}
-	\todo{spazi topologici puntati - controesempio}
-\end{example}
-
-\begin{lemma}\label{lem:cor}
-	Let $\X$ be a category with a proper factorization system $(\mathcal{E}, \mathcal{M})$.
-Suppose, moreover, that $\X$ has the epic $\mathcal{M}$-sum property.
-Then for every $\mathcal{A}\in \cla(\X)$, $\C(\mathcal{A})$ is a coreflective subcategory of $\X$.
-\end{lemma}
-
-\begin{proof}
-	For every object $X$ of $\X$, let us define
-	\[\mathcal{F}_X:=\{m\in \mathcal{M}/X \mid \dm{m} \text{ belongs to } \C(\mathcal{A})\}\] 
-	We can then define $R(X)$ as the domain of the sum over $\mathcal{F}_X$ in $\mathcal{M}/X$. In particular, we have an arrow $\epsilon_X\colon R(X)\to X$, belonging to $\mathcal{M}$.
-
-	First of all, we have to prove that $R(X)$ so defined is an object of $\C(\mathcal{A})$.
-Let thus $f\colon A\to Y$ be an arrow in $\mathcal{A}$ and suppose that there are $g,h\colon R(X)\to A$ such that  $f\circ h= f \circ g$.
-Now, for every $m\colon M\to X$ in $\mathcal{F}_X$ we have a coprojection $k_m\colon m\to \epsilon_X$.
-Precomposing with it we get
-	\[f\circ h \circ k_m=f\circ g\circ k_m\]
-	By definition $M$ is in $\C(\mathcal{A})$, so we can conclude that $h\circ k_m=g\circ k_m$.
-Since  this holds for every $m\in \mathcal{F}_Z$, the epic $\mathcal{M}$-sum property of $\X$ entails $f=g$ as wanted.
-
-	To conclude, is it now enough to show that $\epsilon_X$ has the universal property of a counit.
-Let $Y$ be an object of $\C(\mathcal{A})$ with an arrow $f\colon Y\to X$.
-We can factor $f$ it as $m\circ e$ with $e\colon Y\to E$ and $m\colon E\to X$ in $\mathcal{M}$.
-By \Cref{prop:ima} we know that $E$ is in $\C(\mathcal{A})$, thus there exists a coprojection $k_m\colon m\to \epsilon_X$.
-In particular we have
-	\begin{align*}
-		\epsilon_X\circ k_m\circ e&=m\circ e = f
-	\end{align*}
-
-On the other hand, if $g\colon Y\to R(X)$ is such that $\epsilon_X\circ g=f$, then $g$ must coincide with $k_m\circ e$ because $\epsilon_X$, being in $\mathcal{M}$ is monic.
-\end{proof}
-
-\begin{example}
-	\todo{spazi topologici puntati - controesempio 2}
-\end{example}
-
-\begin{proposition}Let $(\mathcal{E}, \mathcal{M})$ be a proper factorization system on a acategory $\X$ with $\mathcal{M}$-sums. Then the following hold true:
-	\begin{enumerate}
-		\item for every class $\mathcal{A}$ in $\cla(\X)$, $\mathcal{A}\subseteq \mathcal{R}_{\C(\mathcal{A})}$;
-		\item the functor $\mathcal{R}_{(-)}\colon \cori(\X )^{op}\to \cla(\X)$ has a left adjoint.
-	\end{enumerate} 
-\end{proposition}
-\begin{proof}\begin{enumerate}
-		\item Let $f\colon X\to Y$ be an arrow in $\mathcal{A}$ and suppose that $g,h\colon Z\to R(X)$ are arrows in $\C(\A)$ such that $R(f)\circ g=R(f)\circ h$. Then
-		\begin{align*}
-			f\circ \epsilon_X\circ I(g)&=\epsilon_Y\circ I(R(f))\circ I(g)\\&=
-			\epsilon_Y\circ I(R(f))\circ I(h)\\&=f\circ \epsilon_X\circ I(h)
-		\end{align*}
-		Since $f$ is in $\mathcal{A}$, we can deduce that $\epsilon_X\circ I(g)=\epsilon_X\circ I(h)$. The thesis now follows from the fact that $\epsilon_X$ is mono.
-
-		\item Let $\Y$ be a coreflective subcategory of $\X$ such that $\mathcal{A}\subseteq \mathcal{R}_\Y$.
-We have to show that $\Y\subseteq \C(\mathcal{A})$.
-Let then $Y$ be an object of $Y$, $f\colon X\to Z$ and arrow in $\mathcal{A}$ and $g, h\colon I_\Y(Y)\rightrightarrows X$ two arrows in $\X$ such that $f\circ g=f\circ h$.
-Applying $R_\Y$ and since, by hypothesis, $R_\Y(f)$ is mono, we get that $R_\Y(g)=R_\Y(h)$.
-Now, by naturality of the counit we have
-	\begin{align*}g\circ \epsilon_{I_\Y(Z)}&=\epsilon_X\circ R_\Y(g)\\&=\epsilon_X\circ R_\Y(h)\\&=h\circ \epsilon_{I_\Y(Z)}
-	\end{align*}
-	By \Cref{cor:counit}  we know that $\epsilon_{I_\Y(Z)}$ is an isomorphism and we can conclude. \qedhere 
-	\end{enumerate}
-\end{proof}
-
-\end{document}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2024-11-14 full_version/fusione.tex
full version che compila in un tempo normale

--- 2023-12-19 fusione.tex
@@
-\documentclass[a4paper]{article}
+\documentclass[a4paper]{report}
 \usepackage{hyperref}
@@
 \newcommand{\slab}[1]{\ensuremath{\scriptstyle{\mathsf{{#1}}}}}
+
+\newcommand{\sub}[3]{{\mathcal{#1}}\textrm{-}\mathsf{Sub}_{\textbf {\textup{#2}}}(#3)}
+
+\newcommand{\msub}[2]{\mathsf{Sub}_{\textbf {\textup{#1}}}(#2)}
 
@@
 \def\Y{\textbf {\textup{Y}}}
+\def\E{\textbf {\textup{E}}}
 
@@
 \tableofcontents
+
+\section*{Summary (with dependencies)}
+
+\subsection*{REWRITING}
+\begin{itemize}
+\item DPO Rewriting in $\mathcal{M}$-adhesive categories, with left-$\mathcal{M}$-linear rules (from now on shortened in ``linear'')\\
+  Observe that rewriting is deterministic (by uniqueness of
+  PO-complement Corollary~\ref{lem:radj})
+
+\item Category of abstract derivation for DPO-rewriting system $(\X, \R)$
+  \begin{itemize}
+  \item \emph{DPO-derivation category} $\dpo$: objects are graphs, arrows between possibly empty, derivations.
+  \item \emph{DPO-abstract decorated derivation category} $\dpi$
+  \end{itemize}
+
+\item \emph{Consistent permutations} (Definition~\ref{def:permcon}):
+  permutation on the steps of two abstract decorated derivations and isomorphism between the colimits such
+  that arrows into the colimits ``commutes''.
+  \begin{enumerate}
+  \item It is unique for consuming rewriting systems
+    (Corollary~\ref{cor:unique})
+  \item They can be composed (Lemma~\ref{lem:sum})
+  \end{enumerate}
+\item
+
+\item Notions of independence\\
+  We have several possibile notions of independence for two direct
+  derivations $\dder{D} ; \dder{D'}$
+  \begin{enumerate}
+
+  \item \emph{Existence of a filler}
+    There is a filler for $\dder{D} ; \dder{D'}$
+    (Definition~\ref{def:filler})
+
+  \item \emph{Switchable}
+    There is $\dder{D}_1' ; \dder{D}_1$ which is a \emph{switch}
+    of $\dder{D} ; \dder{D'}$ (Definition~\ref{de:switch}, being a
+    switch is defined axiomatically) [actually, Definition~\ref{de:good-switchable} provides a definition of switchable which looks different to me, I would avoid this, to be checked]
+
+  \item \emph{(Weakly) Sequential independent} There is an
+    \emph{independence pair}
+    (Definition~\ref{de:sequential-independence}) They are called
+    \emph{strongly sequential independent} if the independence pair is
+    unique.
+  \end{enumerate}
+
+  We have that $(1) \Rightarrow (2)$ (Theorem~\ref{prop:fil}) and $(2) \Rightarrow (3)$ while
+  we expect that in general $(3) \not\Rightarrow (1)$ (but no
+  counterexample). This is instead known to hold for linear rules.
+
+  Some terminology (Definition~\ref{de:good-switchable})
+  \begin{itemize}
+
+  \item \emph{Tame rewriting systems}\\
+    An independence pairs induced by a filler is called \emph{good}
+    A rewriting system where all indepedence pairs are good is called
+    \emph{tame}
+
+    NOTE: the categories in which condition $B$
+    from~\cite{baldan2011adhesivity} identifies a large class of
+    (quasi)adhesive categories where left-linear systems are all
+    tame. Adapted here to M-adhesivity.
+
+  \item \emph{Very Tame rewriting systems}\\
+    Tame and existing indepence pairs are unique (hence switching is unique)
+    (see later for examples)
+  \end{itemize}
+
+\item \emph{Switch equivalent derivations} (concrete)\\
+  Definition~\ref{de:switchable}
+
+  THEOREM: Two switch equivalent derivations admit a consistent
+  permutation (Lemma~\ref{lem:consperm} ??).
+
+  A consequence of this used for proving that the slice of traces is a pre-order.
+
+  The converse holds only when rules are linear [proof clear, but not written]
+
+\end{itemize}
+
+\subsection*{CONCURRENCY}
+
+This part is dealt with for very tame rewriting systems and depends on this assumption. Note that
+\begin{itemize}
+\item Linear rewriting systems on adhesive categories are very tame
+\item Left-linear rewritint systems on graph-like categories with generalisation of (i) no isolated nodes in $L$ and (ii) right leg injective on nodes is very tame
+\item Graphs with equivalences (Egg) with left-leg regular mono, right leg mono is very tame
+\end{itemize}
+
+We show
+\begin{itemize}
+
+\item Three-steps lemma (Lemma~\ref{lem:iig1}), which is a weakened version of ``indepedence is global''.
+  \begin{itemize}
+
+  \item If in $abc$ I have that $ab$ are independent and $c$ is anticipated, they remain independent.
+  \item  If in $abc$ I have that $bc$ are independent and $a$ is moved to the end, they remain independent only if there is an additional condition (essentially requiring that $a$ was not a cause of $c$)
+  \end{itemize}
+
+\item No need of useless switchs (if two derivations are switch equivalent I can obtain one from another applying only inversions)
+
+\item weak prime domain e connected es semantics
+\end{itemize}
+
 \section{Introduction}
@@
 
-Graph-like structures are used in uncountably many setting for representing the dynamic of software systems: the graph represents the entities in the states and their relations, while rewriting steps, modifying the graph, are used to model events which produce state changes.
+Graph-like structures are used in uncountably many setting for representing the dynamics of software systems: the graph represents the entities in the states and their relations, while rewriting steps, modifying the graph, model computational steps which produce state changes.
 
 Rewriting over graph-like structures is elegantly captured by
-DPO-rewriting over adhesive categories and variants.  This has been
-largely studied for so-called linear rewriting rules. Roughly
-speaking, with linear rules a rewriting step can express the fact that
-some entities in the current state are removed, some other are needed
-for the rewriting step to occur but preserved and some new entities
-are generated.
+DPO-rewriting over adhesive categories and their
+variants~\cite{lack2005adhesive,ehrig2006weak}.  This has been largely
+studied for so-called linear rewriting rules. Roughly speaking, with
+linear rules a rewriting step can express the fact that some entities
+in the current state are removed, some other are needed for the
+rewriting step to occur but preserved and some new entities are
+generated.
 
@@
 concurrently. This phenomenon is formally captured by the so-called
-Church-Rosser theorem of DPO rewriting. This represent the basis for
+Church-Rosser theorem of DPO rewriting and shift equivalence over derivations~\cite{CMREHL:AAGT}. This represent the basis for
 viewing sequences of rewriting in the DPO approach as concurrent
@@
 the dependencies this setting can be captured by a classical structure
-in concurrency theory, the so-called prime event structures where
-dependencies are reduced to causality and conflict.
-
-It can be the case that linear rules are not sufficiently expressive for capturing the dynamic of a system.
+in concurrency theory, the so-called prime event structures~\cite{NPW:PNES} where
+dependencies are reduced to causality and conflict~\cite{Handbook,Bal:PhD,Sch:RRSG}.
+
+In some situations linear rules are not sufficiently expressive for capturing the dynamic of a system.
 This is the case when  a computational step is required not only to consume, preserve and generated, but also ``merge'' parts of the state.
-This happens, e.g., in nominal calculi where, as a result of name passing, the received name is identified with a local one at the receiver, in the modelling of bonding in biological/chemical processes, add EGGS, something about string diagrams?
-
-Technically, describing fusions requires to move from linear to left-linear rewriting rules.
+This happens, e.g.,
+in nominal calculi where, as a result of name passing,
+the received name is identified with a local one at the
+receiver~\cite{CVY:ESSPE,Gad07} or in the modelling of bonding in biological/chemical processes~\cite{PUY:MBPE}.
+ add EGGS, something about string diagrams?
+
+Technically, describing fusions, in the DPO jargon, requires to move from linear to left-linear rewriting rules.
 While left-linear rules have been considered in various instances (mainly for graph rewriting( and some results concerning the corresponding rewriting theory have been put forward, to the best of our knowledge the phenomena arising when rewriting with left-linear rules in the general setting of adhesive categories (which capture most ``applications'') have not been systematically explored.
@@
 
-Firstly, Church-Rosser theorem does not work out of the box: the independence condition for adhesive categories does not extend smoothly to left-linear rules, i.e., existence of an independence pair does not ensure the possibility of switching two derivation and a refined notion, involving the concept of a so-called filler has to be introduced.
-The problem was identified already in ...
-where a suitable subclass of adhesive categories is identified where independence as induced by a filler coincide with independence as induced by an independence pair.
+Firstly, Church-Rosser theorem does not work out of the box: the
+independence condition for adhesive categories does not extend
+smoothly to left-linear rules, i.e., existence of an independence pair
+does not ensure the possibility of switching two derivation and a
+refined notion, involving the concept of a so-called filler has to be
+introduced. The problem was identified already
+in~\cite{baldan2011adhesivity} where a suitable subclass of adhesive
+categories is identified where independence as induced by a filler
+coincide with independence as induced by an independence pair.
 
 Having a notion of independence between computation steps sits at the core of the possibility of viewing an execution trace as a concurrent computation.
-This is obtained by considering traces up to an equivalence that identifies traces differing only for the order of independent steps (e.g., interchange law [?] in term rewriting, shift equivalence [?] in graph rewriting or permutation equivalence [?] in lambda-calculus).
+This is obtained by considering traces up to an equivalence that identifies traces differing only for the order of independent steps (e.g., interchange law~\cite{Mes92} in term rewriting, shift
+equivalence~\cite{CMREHL:AAGT} in graph rewriting or permutation
+equivalence~\cite{JJL80} in $\lambda$-calculus).
 While for linear rewriting systems this works smoothly, for left-linear ones one has to face the problem that if two rewriting steps $r_a r_b$ are independent, if we switch $r_a$ after $r_a$ and then switch it back we can obtain a computation which is not the original one, making the theory of derivation traces inconsistent.
@@
 We also identify a large class of adhesive categories, arising as presheaves, where the condition is automatically satisfied.
-[this solves also the previous problem, right;
+[this solves also the previous problem, right?]
 
 Additionally, a central property for linear rewriting systems is the fact that independence of two rewriting steps is a global notion, independently of the context in which the rewritings take place.
-This is at the basis of the possibility of capturing the dependencies between rewriting steps in terms of two basic relations, causality and conflict, investigated in ...
-
-This fails for left-linear rules where, as observed in ...
-for graph rewriting, the possibility of merging parts of the state leads to a sort of disjunctive causality, i.e., a rewriting step, say $r_c$ can be enabled by two different rewriting steps $r_a$ and $r_b$, in a way that in a derivation $r_a r_b r_c$ steps $r_b$ and $r_c$ are independent since the presence of $r_a$ in the past is sufficient for enabling $r_a$, while in $r_b r_c r_a$ , the steps $r_b$ and $r_c$ are not independent.
-The paper shows that for left-linear rewriting systems a special form of globality of independence can be recovered.
-
-The concurrent semantics of linear graph rewriting systems over adhesive categories can be captured by prime event structures and prime algebraic domains [extend] [...].
-This is extended to adhesive categories in   [IS THIS IN TOBIAS?]
-
-In [...] it is observed for graph rewriting systems that the presence of fusions, the same event can be enabled by different minimal sets of events, thus preventing the identification of a proper notion of causality and making prime event structures and prime domain inadequate.
+This is at the basis of the possibility of capturing the dependencies between rewriting steps in terms of two basic relations, causality and conflict, investigated in~~\cite{Handbook,Bal:PhD,Sch:RRSG}.
+
+This fails for left-linear rules where, as observed
+in~\cite{baldan2017domains}, for graph rewriting, the possibility of
+merging parts of the state leads to a sort of disjunctive causality,
+i.e., a rewriting step, say $r_c$ can be enabled by two different
+rewriting steps $r_a$ and $r_b$, in a way that in a derivation
+$r_a r_b r_c$ steps $r_b$ and $r_c$ are independent since the presence
+of $r_a$ in the past is sufficient for enabling $r_a$, while in
+$r_b r_c r_a$ , the steps $r_b$ and $r_c$ are not independent. The
+paper shows that for left-linear rewriting systems a special form of
+globality of independence can be recovered.
+
+The concurrent semantics of linear graph rewriting systems over
+adhesive categories can be captured by prime event structures and
+prime algebraic domains. The idea consists in considering a partially
+ordered domain, where elements are concurrent computations
+(derivations up to shift equivalence), and the order relates two
+computations when the latter is an extension of the former.
+%
+Events are then identified with computations consisting of a rewriting
+step with all its causes. This is generalised to adhesive categories
+in~\cite{heindel2009category}. [IS THIS IN TOBIAS?]
+
+In~\cite{baldan2017domains} it is observed for graph rewriting systems that the presence of fusions, the same event can be enabled by different minimal sets of events, i.e., a central property of the domain of configuration, namely stability, fails.
+This prevents the identification of a proper notion of causality and makes prime event structures and prime domains inadequate to represent computations with fusions.
 It is argued that the right class of structures capturing the concurrent behaviour in the presence of fusion are connected event structures and weak prime algebraic domains.
-This is worked out for DPO rewriting systems over graphs.
-However the proof relies on a characterisation of independence which fails for non linear rules.
-Here we correct that result and extend it to DPO rewriting over a large class of adhesive categories.
-
-\section{$\mathcal{M}$-adhesive categories}
-
-This first section is devoted to recall the definition and the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive}.
-
-\begin{notation} 
-We stipulate here some notational conventions which will be used throughout this paper. 
-\begin{itemize}\item 
-	Given a category $\X$ we will not distinguish notationally between $\X$ and its class of objects: so that ``$X\in \X$'' means that $X$ belongs to the class of objects of $\X$.  
-	\item 
-	If $1$ is a terminal object in a category $\X$,  the unique arrow $X\to 1$ from another object $X$ will be denoted by $!_X$.
-Similarly, if $0$ is initial in $\X$ then $?_X$ will denote the unique arrow $0\to X$.
-%When $\X$ is $\Set$ and $1$ is a singleton, $\delta_x$ will denote the arrow $1\to X$ with value $x\in X$.
-	\item  $\mor(\X)$, $\mon(\X)$ and $\reg(\X)$ will denote the class of all arrows, monos and regular monos of $\X$, respectively.
-
-	\item Given an integer $n\in \mathbb{Z}$, $[0,n]$ will denote the set
-	\[[0,n]:=\{x\in \mathbb{N}\mid x\leq n\}\]
-	Indeed, if $n<0$, then $[0,n]=\emptyset$.
-\end{itemize}
-\end{notation}
-
-\subsection{The Van Kampen property}
-The key property that $\mathcal{M}$-adhesive categories enjoy is given by  the so-called \emph{Van Kampen condition} \cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive}.
-We will recall it and examine some of its consequences.
-First of all we need to recall some terminology and facts regarding subclasses of $\mor(\X)$.
-
-\begin{definition}
-	Let $\X$ be a category and $\mathcal{A}$ a  subclass of $\mor(\X)$. We say that  $\mathcal{A}$ is
-	\begin{itemize}
-		\item 
-		\emph{stable under pushouts (pullbacks)} if for every pushout (pullbacks) square 
-		\[\xymatrix{A\ar[r]^f  \ar[d]_{m}& B \ar[d]^n \\ C \ar[r]_g & D}\]
-		if $m \in \mathcal{A}$ ($n\in \mathcal{A}$) then $n \in \mathcal{A}$ ($m \in \mathcal{A}$);
-		\item \emph{closed under composition} if $g, f\in \mathcal{A}$ implies $g\circ f\in \mathcal{A}$ whenever $g$ and $f$ are composable;
-		\item \emph{closed under decomposition} if $g\circ f, g\in \mathcal{A}$ implies $f\in \mathcal{A}$.
-	\end{itemize}
-\end{definition}
-
-\begin{remark}In the previous definition, ``decomposition'' corresponds to ``left cancellation'', but we prefer to stick to the name commonly used in literature (see e.g.~\cite{habel2012mathcal}).
-\end{remark}
-
-So equipped, we can introduce the notion of \emph{$\mathcal{A}$-Van Kampen square}.
-\begin{definition}[Van Kampen property] Let $\X$ be a category  and consider the two diagrams below
-	\[\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{f}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{g} &&D&&C \ar[rr]_{g} & & D}\]
-
-	Given  a class of arrows $\mathcal{A}\subseteq \mor(\X)$, we say that the left square \emph{has the Van Kampen property relatively to $\mathcal{A}$}, or that it  is a \emph{$\mathcal{A}$-Van Kampen square} if:
-	\begin{enumerate}
-		\item is a pushout square;
-		\item 	whenever the right cube has pullbacks as back and left faces and the vertical arrows belong to $\mathcal{A}$, then its top face is a pushout if and only if the front and right faces are pullbacks.
-	\end{enumerate}
-	Pushout squares which enjoy the ``if'' half of the second point of the condition above are called \emph{$\mathcal{A}$-stable}.
-
-We will call a $\mor(\X)$-Van Kampen ($\mor(\X)$-stable) square simply a \emph{Van Kampen} (\emph{stable}) square.
-\end{definition}
-
-Before proceeding further, we recall this classical result about pullbacks.
-
-\begin{lemma}\label{lem:pb1}
-	Let $\X$ be a category, and consider the following diagram 	in which the right square is a pullback.
-	\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
-	Then the whole rectangle is a pullback if and only if the left square is one.
-\end{lemma}
-
-The previous result can be dualised to get an analogous lemma for pushouts.
-
-\begin{lemma}\label{lem:po1}
-	Let $\X$ be a category, and consider the following diagram 	in which the left square is a pushout.
-	\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
-	Then the whole rectangle is a pushout if and only if the right square is one.
-\end{lemma}
-
-The following proposition establishes a key property of $\mathcal{A}$-Van Kampen squares with a mono as a side: they are not only pushouts, but also pullbacks.
-\begin{proposition}\label{prop:pbpo} Let $\mathcal{A}$ be a class of arrows stable under pushouts and containing all the isomorphisms.
-If $m\colon A\to C$ is mono and belongs to $\mathcal{A}$, then every $\mathcal{A}$-Van Kampen square
-	\[\xymatrix{A\ar[r]^{g} \ar[d]_{m} & B \ar[d]^{n} \\ C \ar[r]_{f}  & D}\]
-	is also a pullback square and $n$ is a monomorphism.
-\end{proposition}
-\begin{proof} We can start considering the cube below and noticing that $n$, being the pushout of $m\in \mathcal{M}$, belongs to $\mathcal{A}$ too.
-	\[\xymatrix@C=13pt@R=13pt{&A\ar[dd]|\hole_(.65){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_{\id{B}} \\ A  \ar[dd]_{m}\ar[rr]^(.65){g} & & B \ar[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{f} & & D}\]
-	By construction the top face of the cube is a pushout and the back one a pullback.
-The left face is a pullback because $m$ is mono.
-Thus the $\mathcal{A}$-Van Kampen property yields that the front and the right faces are pullbacks.
-\end{proof}
-
-The previous proposition, in turn, allows us to establish the following results.
-\begin{lemma}\label{lem:varie}Let $\mathcal{A}$ be a class of arrows stable under pullbacks, pushouts and containing all isomorphisms.
-Suppose that, the left square below is $\mathcal{A}$-Van Kampen, while the vertical faces in the right cube are pullbacks.
-		\[\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{g'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{g}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){f'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){g} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{f} &&D&&C \ar[rr]_{f} & & D}\]
-Supppose, moreover that $m:A\to C$ and $d:D'\to D$ are mono and that $d$ belongs to $\mathcal{A}$. Then $d\leq n$ if and only if $c \leq m$.
-\end{lemma}
-
-\begin{remark}
-	Recall that, given two monos $m:M\to X$ and $n:N\to X$ with the same codomain, $m\leq n$ means that there exists a, necessarily unique and necessarily mono, $k:M\to N$ fitting in the triangle below:
-	\[\xymatrix{M\ar[rr]^{k}  \ar[dr]_{m}&& N \ar[dl]^{n}\\ & X}\]
-	Notice that, if $m\leq n$ and $n\leq m$, then the arrow $k:M\to N$ is an isomorphism.  
-\end{remark}
-\begin{remark}
-	Notice that, since $d$ is a mono and the vertical faces are pullbacks, then $a, b$ and $c$ are monomorphisms too. Moreover, $n$ is mono by \Cref{prop:pbpo}, so that even $m'$ and $n'$ are monos.
-\end{remark}
-
-\begin{proof}
-	$(\Rightarrow)$ By hypothesis there exists $k:D'\to B$ such that $n\circ k = d$.
-By \Cref{prop:pbpo}, the bottom face of the cube is a pullback.
-Thus there exists a unique $h:C'\to A$ as in the diagram below, implying the thesis.
-		\[\xymatrix@C=40pt{C'  \ar[d]^{h}\ar[r]^{f'} \ar@/_.5cm/[dd]_{c}& D' \ar@/^.5cm/[dd]^{d}\ar[d]_{k}\\ A \ar[d]^{m} \ar[r]^{g} & B \ar[d]_{n} \\  C \ar[r]_f & D}\]
-
-	\smallskip \noindent 
-	$(\Leftarrow)$ Let $h:C\to A$ be such that $c=m\circ h$.
-By the $\mathcal{A}$-Van Kampen property the top face of the given cube is a pushout.
-Thus the dotted $k:D'\to B$ in the following diagram exists.
-		\[\xymatrix@C=40pt{A' \ar@/_.5cm/[dd]_{a} \ar[d]^{m'} \ar[r]^{g'} & B' \ar[d]_{n'} \ar@/^.5cm/[dd]^{b} \\  C' \ar[d]^{h} \ar[r]_{f'} & D' \ar@{.>}[d]_{k}\\ A \ar[r]_g& B }\]
-Moreover, by construction we have
-\[\begin{split}
-n\circ k \circ n' &= n\circ b\\&=d\circ n'\\&\\&
-\end{split} \qquad \begin{split}
-n\circ k \circ f' &= n\circ g\circ h\\&=f\circ m\circ h\\&=f\circ c\\&= d\circ f' \end{split}\]
-We can therefore conclude that $n\circ k =d$. \qedhere 
-\end{proof}
-
-Finally, we can show that $\mathcal{A}$-stable pushouts enjoy a kind of \emph{pullback-pushout decomposition} property.
-
-\begin{proposition}\label{prop:stab}Let $\X$ be a category and $\mathcal{A}$ a class of arrows stable under pullbacks.
-Suppose that, in the diagram below, the whole rectangle is an $\mathcal{A}$-stable pushout and the right square a pullback.
-	\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
-	If the arrow $k$ is in $\mathcal{A}$ and it is a monomorphism,  then both squares are pushouts.
-\end{proposition}
-
-\begin{proof} We can begin noticing that $g$, being the pullback of $k$, is mono and in $\mathcal{A}$ too.
-Thus we can build the cube below, in which all the vertical faces are pullbacks, entailing that all the vertical arrows are in $\mathcal{A}$.
-	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y  \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
-	By hypothesis the face is an $\mathcal{A}$-stable pushout and so its top one is a pushout.
-Using \Cref{lem:po1} we can conclude that the right half of the rectangle with which we have started is a pushout too.
-\qedhere
-\end{proof}
-
-\subsection{$\mathcal{M}$-adhesivity}
-
-In this section we will define the notion of $\mathcal{M}$-adhesivity \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,heindel2009category,lack2005adhesive} and explore some of the consequence of such a property.
-
-\begin{definition}[$\mathcal{M}$-adhesive category]
-	Let $\X$ be a category and consider a subclass $\mathcal{M}$ of the class $\mon(\X)$ of monomorphisms such that:
-	\begin{enumerate}
-		\item $\mathcal{M}$ contains all isomorphisms and is closed under composition;
-		\item $\mathcal{M}$ is stable under pullbacks and pushouts.
-	\end{enumerate} 
-	We will use $m\colon X\mto Y$ to denote that an arrow $m:X\to Y$ belongs to $\mathcal{M}$. $\X$ is said to be \emph{$\mathcal{M}$-adhesive} if
-	\begin{enumerate}
-		\item for every $m\colon X\mto Y$ in $\mathcal{M}$ and $g\colon Z\to Y$, a pullback square
-		\[\xymatrix{P\ar[r]^p \ar@{>->}[d]_{n}& X \ar@{>->}[d]^{m}\\ Z \ar[r]_g& Y}\]
-		exists, such pullbacks will be called \emph{$\mathcal{M}$-pullbacks};
-		\item for every $m\colon X\mto Y$ in $\mathcal{M}$ and $f\colon X\to Z$, a pushout square
-		\[\xymatrix{X \ar[r]^f \ar@{>->}[d]_{m}& Z \ar[d]^{q}\\ Y\ar[r]_p &Q}\]
-		exists, such pushouts  will be called \emph{$\mathcal{M}$-pushouts}; 
-		\item  $\mathcal{M}$-pushouts are $\mathcal{M}$-Van Kampen squares.
-	\end{enumerate}
-
-A category $\X$ is said to be \emph{strictly $\mathcal{M}$-adhesive} if $\mathcal{M}$-pushouts are Van Kampen squares.	
-\end{definition}
-
-\begin{remark}\label{rem:diff}Our notion of $\mathcal{M}$-adhesivity follows \cite{ehrig2012,ehrig2014adhesive} and is different from the one of \cite{azzi2019essence}.
-What is called $\mathcal{M}$-adhesivity in that paper corresponds to our strict $\mathcal{M}$-adhesivity.
-Moreover, in \cite{azzi2019essence} the class $\mathcal{M}$ is assumed to be only stable under pullbacks.
-However, if $\mathcal{M}$ contains all split monos, then stability under pushouts can be deduced from the other axioms \cite[Prop.~$5.1.21$]{castelnovo2023thesis}.
-\end{remark}
-
-\begin{remark}\label{rem:salva} 
-	\emph{Adhesivity} and \emph{quasiadhesivity} as defined in \cite{lack2005adhesive,garner2012axioms}  coincide with  strict $\mon(\X) $-adhesivity and strict $\reg(\X)$-adhesivity, respectively. 
-\end{remark}
-
-A first result we can prove regards closure under decomposition of $\mathcal{M}$.
-
-\begin{proposition}\label{prop:deco}Let  $\mathcal{A}$ be a class of arrows stable under pullbacks.
-For every arrow $f\colon X\to Y$ and monomorphism $m\colon Y\to Z$, if $m\circ f \in\mathcal{A}$ then $f\in \mathcal{A}$.
-\end{proposition}
-\begin{proof}Take the diagram
-	\[\xymatrix{X \ar[d]_{\id{X}}\ar[r]^{f}& Y \ar[r]^{\id{Y}}  \ar[d]_{\id{Y}}& Y \ar[d]^{m}\\
-		X \ar[r]_{f}& Y \ar[r]_{m} & Z}\]
-	Since $m$ is mono the right square is a pullback, while the left square is a pullback by construction. By \Cref{lem:pb1} the whole rectangle is a pullback and the thesis follows.
-\end{proof}
-\begin{corollary}\label{cor:deco}
-	In every $\mathcal{M}$-adhesive category $\X$, the class $\mathcal{M}$ is closed under decomposition.
-\end{corollary}
-
-Another result which can be immediately established, with the aid of \Cref{prop:pbpo}, is the following one.
-\begin{proposition}\label{prop:pbpoad}
-	Let $\X$ be an $\mathcal{M}$-adhesive category. Then $\mathcal{M}$-pushouts are also pullback squares.
-\end{proposition}
-
-From \Cref{prop:pbpoad}, in turn, we can derive the following corollaries.
-\begin{corollary}\label{cor:rego}
-	In a $\mathcal{M}$-adhesive category $\X$, every $m\in\mathcal{M}$ is a regular mono.
-\end{corollary}
-\begin{proof}
-Let $m$ be an element of $\mathcal{M}$ and consider its pushout along itself.
-\[\xymatrix{X\ar@{>->}[r]^m \ar@{>->}[d]_m& Y\ar@{>->}[d]^{f}\\Y \ar@{>->}[r]_g & Z}\]
-By \Cref{prop:pbpoad} this square is a pullback, proving that $m$ is the equalizer of the arrows $f,g\colon Y\rightrightarrows Z$. \qedhere 
-\end{proof}
-
-The following result now follows at once noticing that a regular monomorphism which is also epic is automatically an isomorphism.
-
-\begin{corollary}\label{prop:bal}
-If $\X$ is an $\mathcal{M}$-adhesive categories, then every epimorphisms in $\mathcal{M}$ is an isomorphisms.
-In particular, every adhesive category $\X$ is \emph{balanced}: if a morphism is monic and epic, then it is an isomorphism.
-\end{corollary}
-
-$\mathcal{M}$-adhesivity is well-behaved with respect to  the comma construction \cite{mac2013categories}, as shown by the following theorem.
-\begin{theorem}[\cite{ehrig2006fundamentals,lack2005adhesive}]\label{lem:comma}
-	Let $\A$ and $\B$ be respectively an $\mathcal{M}$-adhesive and an $\mathcal{M}'$-adhesive category.
-Let also $L:\A\rightarrow \C$ be a functor that preserves $\mathcal{M}$-pushouts, and  $R:\B\rightarrow \C$ be a functor which preserves pullbacks.Then $\comma{L}{R}$ is $\cma{M}{M'}$-adhesive, where
-	\[
-	\cma{M}{M}':=\{(h,k)\in \mathcal{A}(\comma{L}{R}) \mid h\in \mathcal{M}, k\in \mathcal{M}'\}\]
-\end{theorem}
-
-In particular, we can apply this result to slices over and under a given object.
-
-\begin{corollary}\label{cor:slice}
-	Let  $X$ be an object of an $\mathcal{M}$-adhesive category $\X$. Then  $\X/X$ and $X/\X$ are, respectively, is $\mathcal{M}/X$- and $X/\mathcal{M}$-adhesive, where
-	\[\mathcal{M}/X:=\{m\in  \mathcal{A}(\X/X) \mid m\in \mathcal{M} \} \qquad X/\mathcal{M}:=\{m\in  \mathcal{A}(X/\X) \mid m\in \mathcal{M} \}\]
-\end{corollary}
-
-Another categorical construction which preserves $\mathcal{M}$-adhesivity property is the formation of the category of functors.
-
-\begin{theorem}[\cite{ehrig2006fundamentals,lack2005adhesive}]\label{thm:functors}
-If $\X$ is an $\mathcal{M}$-adhesive category, then for every small category $\Y$, the category $\X^\Y$  of functors $\Y\to \X$ is $\mathcal{M}^{\Y}$-adhesive, where
-\[\mathcal{M}^{\Y}:=\{\eta \in \mathcal{A}(\X^\Y) \mid \eta_Y \in \mathcal{M} \text{ for every } Y\in \Y\}\]
-\end{theorem}
-
-We can list various examples of $\mathcal{M}$-adhesive categories (see \cite{castelnovo2023thesis,CastelnovoGM22,lack2006toposes}).
-
-\begin{example}\todo{Topos, ipergrafi e grafi}
-\end{example}
-
-\begin{example}
-	\todo{grafi semplici}
-\end{example}
-
-\begin{example}\todo{GRAFI GERARCHICI}
-\end{example}
-
-\begin{example}\todo{term graph}
-\end{example}
-
-We end this section proving two properties of $\mathcal{M}$-adhesive categories:  $\mathcal{M}$-pushout-pullback decomposition and uniqueness of pushouts complements.
-
-\begin{lemma}[$\mathcal{M}$-pushout-pullback decomposition]\label{lem:popb} Let $\X$ be an $\mathcal{M}$-adhesive category  and suppose that, in the diagram below, the whole rectangle is a pushout and the right square a pullback.
-\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
-	Then the following statements hold true:
-	\begin{enumerate}
-\item if $a$ belongs to $\mathcal{M}$ and $k$ is a monomorphism,  then both squares are pushouts and pullbacks;
-\item if $f$ and $k $ are in  $\mathcal{M}$, then both squares are pushouts and pullbacks.
-	\end{enumerate}
-\end{lemma}
-\begin{proof}
-\begin{enumerate}
-	\item By \Cref{prop:stab}, it follows that both squares are pushouts, thus the thesis follows from \Cref{prop:pbpoad}.
-	\item By hypothesis, $g$ is the pullback of an arrow in $\mathcal{M}$, thus it belongs to it.
-But then $g\circ f\in \mathcal{M}$ too  and the whole rectangle is a $\mathcal{M}$-pushout.
-Therefore, by \Cref{prop:pbpoad} a pullback, so that its left half is a pullback too, by \Cref{prop:pbpo}.
-Moreover $k\circ h$ is in $\mathcal{M}$ as the pushout of $g\circ f$ and, by \Cref{cor:deco}, we also know that $h\in \mathcal{M}$.
-
-	Using \Cref{lem:po1}, it is enough to show that the left half of the original rectangle is a pushout. We can build the following cube:
-	\[\xymatrix@C=20pt@R=10pt{ & &X\ar@{>->}[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar@{>->}[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar@{>->}[ddd]_{g} \ar[rrr]^{b}&&& B\ar@{>->}[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar@{>->}[dl]_{f}&&& A \ar@{>->}[dl]^{h}\\ & Y \ar[rrr]|(.67)\hole^{b} \ar@{>->}[dl]_{g}&&& B \ar@{>->}[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
-	Its vertical faces are all pullbacks and all the vertical arrows are in $\mathcal{M}$, hence the top face is a pushout and we can conclude. \qedhere 
-\end{enumerate}
-\end{proof}
-
-Let us turn our attention to pushout complements.
-
-\begin{definition}[Pushout complement]
-Let $f\colon X\to Y$ and $g\colon Y\to Z$ ba two composable arrows in a category $\X$.
-A \emph{pushout complement} for the pair $(f,g)$ is a pair $(h,k)$ with $h\colon X\to W$ and $k\colon W\to Z$ such that the square below commutes and it is a pushout.
-\[\xymatrix{X \ar[r]^{f} \ar[d]_{h}& Y \ar[d]^{g} \\ W \ar[r]_{k}& Z}\]
-\end{definition}
-
-\begin{example}
-	In a generic category $\X$, pushout complements may not exist: in $\Set$ the arrows $?_{2}\colon \emptyset \to 2$ and $!_2\colon 2\to 1$ do not have a pushout complement.
-
-	Moreover, composable arrows $f\colon X\to Y$ and $g\colon Y\to Z$ may have  pushout complements which are non-isomorphic: for instance, in $\Set$ the two squares below are both pushouts.
-
-	\[\xymatrix{2 \ar[r]^{!_2} \ar[d]_{\id{2}}& 1 \ar[d]^{\id{1}} & 2 \ar[r]^{!_2} \ar[d]_{!_2}& 1 \ar[d]^{\id{1}}\\ 2 \ar[r]_{!_2}& 1 & 1 \ar[r]_{\id{1}}& 1}\]
-\end{example}
-
-Working in an $\mathcal{M}$-adhesive category we can amend the second defect.
-
-\begin{lemma}[Uniqueness of pushouts complements]\label{lem:pocomp} 
-Let $\X$ be a $\mathcal{M}$-adhesive category.
-Given $m\colon X\mto Y$ in $\mathcal{M}$ and $n\colon Y\to Z$, let $(h_1, k_1)$ and $(h_2, k_2)$ be pushout complements of $m$  and $n$ and $W_1=\cod{h_1}$, $W_2=\cod{h_2}$.
-Then there exists a unique isomorphism $f\colon W_1\to W_2$ making the following diagram commutative.
-\[\xymatrix{&X \ar@{>->}[r]^{m} \ar[d]_{h_1} \ar@/_.3cm/[ddl]_{h_2}& Y \ar[d]^{n} \\ &W_1 \ar@{.>}[dl]^{f} \ar@{>->}[r]_{k_1} & Z \\ W_2 \ar@{>->}@/_.3cm/[urr]_{k_2}}\]
-
-\end{lemma}
-\begin{proof} By hypothesis
-	$k_1$ and $k_2$, being the pushout of $m$, are elements of $\mathcal{M}$ and therefore are monomorphisms.
-In particular, $k_2$ is a monomorphism and this  entails at once the uniqueness of $f$.
-Moreover, notice that the squares
-	\[\xymatrix{X \ar@{>->}[r]^{m} \ar[d]_{h_1}& Y \ar[d]^{n}& X \ar[d]_{h_2}\ar@{>->}[r]^{m} & Y \ar[d]^{n}\\ W_1 \ar@{>->}[r]_{k_1} & Z & W_2 \ar@{>->}[r]_{k_2}& Z}\]
-	are $\mathcal{M}$-pushouts and thus $\mathcal{M}$-Van Kampen.
-
-Now, take the $\mathcal{M}$-pullback square
-	\[\xymatrix{P\ar[r]^{p_1}  \ar[d]_{p_2}& W_1 \ar@{>->}[d]^{k_1}\\ W_2 \ar@{>->}[r]_{k_2} & Z}\]
-	Since $k_1\circ h_1=k_2\circ h_2$, there exists a unique $g\colon X\to P$ fitting in
-	\[\xymatrix{X \ar@/^.3cm/[drr]^{h_1} \ar@{.>}[dr]^{g} \ar@/_.3cm/[ddr]_{h_2}\\ &P\ar[r]^{p_1}  \ar[d]_{p_2}& W_1 \ar@{>->}[d]^{k_1}\\ &W_2 \ar@{>->}[r]_{k_2} & Z}\]
-	We can then build the cubes
-	\[\xymatrix@C=13pt@R=13pt{&X\ar[dd]|\hole_(.65){\id{X}}\ar[rr]^{g} \ar[dl]_{\id{X}} && P \ar[dd]^{p_1} \ar[dl]_{p_2} & &X\ar[dd]|\hole_(.65){\id{X}}\ar[rr]^{g} \ar[dl]_{\id{X}} && P \ar[dd]^{p_2} \ar[dl]_{p_1}\\ X  \ar@{>->}[dd]_{m}\ar[rr]^(.65){h_2} & & W_2 \ar@{>->}[dd]_(.3){k_2}& &  X  \ar@{>->}[dd]_{m}\ar[rr]^(.65){h_1} & & W_1 \ar@{>->}[dd]_(.3){k_1}\\&X\ar[rr]|\hole^(.65){h_1} \ar@{>->}[dl]^{m} && W_1 \ar@{>->}[dl]^{k_1} & &X\ar[rr]|\hole^(.65){h_2} \ar@{>->}[dl]^{m} && W_2 \ar@{>->}[dl]^{k_2}\\Y \ar[rr]_{n} & & Z & &Y \ar[rr]_{n} & & Z}\]
-
-	Now, in both cubes the front and left faces are pullbacks, thus, by \Cref{lem:pb1}, their back face is a pullback too.
-Since $m\leq m$, \Cref{lem:varie} now entails that $k_1\leq k_2$ and $k_2\leq k_1$.
-Thus there exists an isomorphism $f\colon W_1\to W_2$ such that $k_1=k_2\circ f$.
-To see that $h_2=f\circ h_1$, we can compute:
-	\begin{align*}
-		k_2\circ f \circ h_1 & = k_1\circ h_1\\&= n\circ m\\&= k_2\circ h_2
-	\end{align*}
-	The claim now follows since $k_2$ is a monomorphism. \qedhere 
-\end{proof}
-
-\section{DPO rewriting and derivations}
-
-$\mathcal{M}$-adhesive categories are the right context in which to perform abstract rewriting using the so-called ``douple pushout approach'' (DPO).
-We will recall the basic definitions and properties of this approach to abstract rewriting.
-
-\subsection{Left-linear DPO-rewriting systems}
-We are now going to study rewriting systems in $\mathcal{M}, \mathcal{N}$-adhesive categories.
-
-\begin{definition}[\cite{habel2012mathcal,heindel2009category}]
-	Let $\X$ be a $\mathcal{M}$-adhesive category, a  \emph{left $\mathcal{M}$-linear} rule $\rho$ is a pair $(l,r)$ of arrows with the same domain, such that $l$ belongs to $\mathcal{M}$.
-The rule $\rho$ is said to be \emph{$\mathcal{M}$-linear} if $r\in \mathcal{M}$ too.
-A rule $\rho$ is said to be \emph{consuming} if $l$ is not an isomorphism.
-We will represent a rule $\rho$ as a span
-	\[\xymatrix{L & K\ar[l]_{l} \ar[r]^{r} & R}\]
-$L$ is the \emph{left-hand side}, $R$ is the \emph{right-hand side} and $K$ the \emph{glueing object}.
-
-A \emph{left-linear DPO-rewriting system} is a pair $(\X, \R)$ where $\X$ is a $\mathcal{M}$-adhesive category and $R$ is a set of left $\mathcal{M}$-linear rules.
-$(\X, \R)$ will be called \emph{linear} if every rule in $R$ is $\mathcal{M}$-linear.
-
-Given  two objects $G$ and $H$ and a rule $\rho=(l,r)$ in $\R$, a \emph{direct derivation $\mathscr{D}$ from $G$ to $H$ applying the rule $\rho$}, is a diagram as the one below, in which both squares are pushouts.
-	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
-	The arrow $n$ is called the \emph{match} of the derivation, while $h$ is its \emph{back-match}.
-	We will denote a direct derivation $\dder{D}$ between $G$ and $H$ as $\dder{D}\colon G\Mapsto H$. 
-\end{definition}
-
-\begin{example}\todo{
-esempi di	derivazione}
-\end{example}
-
-\begin{remark}\label{exa:conc} Let  $\dder{D}\colon G\Mapsto H$ be the direct derivation 
-		\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
-	If $\phi\colon G'\to G$ and $\psi\colon H\to H'$ are two isomorphisms, 	we can consider the direct derivation	$\phi * \dder{D}*\psi \colon G'\Mapsto H'$ given by the following diagram.
-	\[\xymatrix{L \ar[d]_{\phi^{-1} \circ n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{\psi \circ h}\\G' & \ar[l]^{\phi^{-1} \circ f} D \ar[r]_{\psi \circ g}& H'}\]
-
-	In particular, we will use $\phi*\dder{D}$ and $\dder{D}*\psi$  to denote $\phi*\dder{D}*\id{H}$ and $\id{G}*\dder{D}*\psi$.
-\end{remark}
-
-$\mathcal{M}$-adhesivity of $\X$ guarantes the essential uniqueness of the result obtained rewriting an object, as shown by the next proposition.
-
-\begin{proposition}\label{prop:unique} Let $\X$  be a $\mathcal{M}$-adhesive category.
-Suppose that the two direct derivations $\mathscr{D}$ and $\mathscr{D'}$ below, with the same match and applying the same left $\mathcal{M}$-linear rule $\rho$ are given.
-	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L \ar[d]_{m}& K \ar[d]^{k'}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h'}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}& H & G & \ar@{>->}[l]^{f'} D' \ar[r]_{g'}& H'}\]
-Then there exist isomorphisms $t\colon D\to D'$ and $s\colon H\to H'$ as in the following diagram.
-\[\xymatrix@C=40pt{&&D' \ar[r]^{g'} \ar@{>->}@/_.45cm/[dll]_{f'}&H'\\G & L \ar[l]_{m} & K \ar[u]_{k'} \ar[d]^{k}\ar[r]^{r} \ar@{>->}[l]_{l} &R\ar[u]^{h'} \ar[d]_{h}\\&&D\ar@{>->}@/^.45cm/[ull]^{f}\ar@/^.4cm/@{.>}[uu]^(.4){t}|\hole \ar[r]_{g}&H\ar@/_.4cm/@{.>}[uu]_{s}}\]
-\end{proposition}
-\begin{proof}
-	By construction, the pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$ and $n$.
-Thus, the existence of the isomorphism $t\colon D\to D'$ follows from \Cref{lem:pocomp}.
-Now, computing we have
-	\begin{align*}
-		g'\circ t \circ k &= g' \circ k'\\&=h'\circ r
-	\end{align*}
-	Hence, we have the wanted $s\colon H\to H'$. To see that $s$ is an isomorphism, consider the diagram 
-	\[\xymatrix{K  \ar@/^.4cm/[rr]^{k'}\ar[d]_{r} \ar[r]_{k}& \ar[r]_{t} D \ar[d]^{g}& D' \ar[d]^{g'}\\ R \ar@/_.4cm/[rr]_{h'} \ar[r]^{h}& H \ar[r]^{s}& H'}\]
-	By hypothesis the whole rectangle and its left half are pushouts, therefore, by \Cref{lem:po1} its right square is a pushout too.
-The claim now follows from the fact that the pushout of an isomorphism is an isomorphism.
-\end{proof}
-
-If we look to direct derivations as transitions, it is natural to consider them as edges in a direct graph.
-Taking objects as vertices objects led us to the following definition \cite{heindel2009category}.
-
-\begin{definition}
-	Let $(\X, \R)$ be a DPO-rewrityng system, with $\X$ $\mathcal{M}$-adhesive.
-The \emph{DPO-derivation graph} of $(\X, \R)$ is the (large)  directed graph $\gpo$ having as vertices the objects of $\X$ and in which an edge between $G$ and $H$ is a direct derivation $\dder{D}\colon G\Mapsto H$.	A \emph{derivation} $\der{D}$ between two objects $G$ and $H$ is a path between them in $\gpo$.
-The \emph{source} and \emph{target} of $\der{D}$ are, respectively, $G$ and $H$.
-\end{definition}
-
-\begin{remark}
-We can spell out more explicitly what  a derivation $\dder{D}$ is.
-An \emph{empty derivation} starting and ending in $G$ is just $G$ itself.
-A \emph{non-empty derivation} $\dder{D}$ is a sequence $\{\dder{D}_i\}_{i=0}^n$ of direct derivations such that:
-\begin{enumerate}
-	\item for every index $i$, $\dder{D}_i$ is a direct derivation $G_i \Mapsto G_{i+1}$;
-	\item $G_0=G$ and $G_{n+1}=H$.
-\end{enumerate}
-
-We will call the number $n+1$ the \emph{length} of the derivation, denoted by $\lgh(\der{D})$. We will also say that an empty derivation has length $0$.
-
-Moreover,  if every $\dder{D}_i$ applies the rule $\rho_i\in R$, then we can define an associated sequence of rules as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.
-\end{remark}
-
-\begin{remark}\label{rem:func}
-	Consider a derivation $\der{D}$ in a DPO-rewriting system $(\X, \R)$.
-We can take the subcategory $\Delta(\der{D})$ of $\X$ given by the arrows appearing in $\der{D}$.
-This subcategory comes equipped with an inclusion functor $I(\der{D})\colon \Delta(\der{D})\to \X$.
-Moreover, we can further define $\Deltamin(\der{D})$ as the subcategory of $\Delta(\der{D})$ containing only the bottom row of the derivation.
-\end{remark}
-
-\begin{notation}Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ be a derivation. We will depict the $i^\text{th}$ element $\dder{D}_i$ of $\der{D}$ as in the following diagram.  
-	\[\xymatrix{L_i \ar[d]_{m_i}& K_i \ar[d]^{k_i}\ar[l]_{l_i} \ar[r]^{r_i} & R_i \ar[d]^{h_i} \\G_{i} & \ar[l]^{f_{i}} D_{i} \ar[r]_{g_{i}}& G_{i+1} }\]
-	Notice that, in particular, if $\der{D}\colon G\to H$, then $G_0=G$ and $G_{n+1}=H$.
-When $\der{D}$ has length $1$ we will suppress the indexes.
-In such case, we will also identify $\der{D}$ with its only element.
-\end{notation}
-
-\begin{example}\todo{esempi di derivazione}
-\end{example}
-
-\begin{definition}
-	The \emph{DPO-derivation category} $\dpo$ of a DPO-rewriting system $(\X, \R)$ is the category in which arrows between $G$ and $H$ are given by, possibly empty, derivations.
-Composition is concatenation of paths in $\gpo$ and identities are given by empty derivations.
-\end{definition} 	
-\begin{remark}
-	More explicitly, given $\der{D}=\{\dder{D}\}_{i=0}^n$ between $G$ and $H$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^m$, their concatenation $\der{D}\cdot\der{D}'$ is the derivation $\{\dder{E}_i\}_{i=0}^{m+n+1}$ in which
-	\[\dder{E}_i:=\begin{cases}
-		\dder{D}_i & i \leq n\\
-		\dder{D}'_{i-(n+1)} & n< i 
-	\end{cases}\]
-
-Notice, moreover that, $\der{D}\cdot \der{D'}$ is equal to $\der{D}'$ if $\der{D}$ is empty, while it coincides with $\der{D}$ if $\der{D}'$ has length zero.
-\end{remark}
-
- \Cref{exa:conc} allows us to compose derivations with isomorphisms.
-
-\begin{definition} Let $(\X, \R)$ be a a left-linear DPO-rewriting system.
-Given a derivation $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ between $G$ and $H$ and isomorphisms $\phi\colon G\to G'$, $\psi\colon H\to H'$, the derivations  $\phi*\der{D}$ and $\der{D}*\psi$ are defined as
-	\[\phi *\der{D} := \begin{cases}
-		G' & \lgh(\der{D})=0\\ 
-		\{\phi* \dder{D}_0\}\cdot \{\dder{D}_i\}_{i=1}^{n}  & \lgh(\der{D})\neq 0
-	\end{cases}\] 
-	\[\der{D}*\psi := \begin{cases}
-		H' & \lgh(\der{D})=0\\ 
-		 \{\dder{D}_i\}_{i=0}^{n-1} \cdot \{\dder{D}_n*\psi\} & \lgh(\der{D})\neq 0
-	\end{cases}\]
-
-	Moreover, if $\lgh(\der{D})>0$,  we define the derivation $\phi *\der{D} * \psi$ as
-	\[\phi *\der{D} * \psi = \{\phi* \dder{D}_0\}\cdot \{\dder{D}_i\}_{i=1}^{n-1} \cdot \{\dder{D}_n*\psi\}\] 
-\end{definition}
-
-\begin{remark}
-When $\der{D}$ consists only in the direct derivation $\dder{D}$, then $\phi*\der{D}*\psi$ is the derivation of length one whose unique element is $\phi*\dder{D}*\psi$.
-\end{remark}
-
-We are often interested in an object of $\X$ only up to isomorphism.
-It is therefore useful to consider a version of $\gpo$ in which vertices are classes of isomorphism of object of $\X$.
-In order to do so, some preliminary work is needed.
-
-\begin{definition}\cite{mac2013categories}
-Let $\X$ be a category, we say that  $\X$ is \emph{skeletal} if, for every two objects $X$ and $Y$, the existence of an isomorphism $\phi\colon X\to Y$ entails $X=Y$.
-A \emph{skeleton} for a category $\X$ is a full subcategory $\ske$ which is skeletal and such that the inclusion functor $\ske\to \X$ is an equivalence.
-\end{definition}
-
-\begin{remark}
-By definition the inclusion $\ske \to \X$ is an equivalence.
-In particular, this mean that, for every objects $X$ of $\X$ there exists $\pi(X)$ in $\ske$ and an isomorphism $\phi_X\colon \pi(X) \to X$.
-\end{remark}
-
-\begin{proposition}\label{prop:ske}
-	Every category $\X$ has a skeleton. 
-\end{proposition}
-\begin{proof}
-	For every object $X\in \X$, pick a single representative $\pi(X)$ of its isomorphism class.
-Let $\ske$ be the full subcategory given by these objects.
-By definition $\ske$ is skeletal and the inclusion functor is full, faithful and essentially surjective.\qedhere
-\end{proof}
-\begin{remark}
-	The proof of \Cref{prop:ske} relies on the axiom of choice for classes.
-	\end{remark}
-\begin{remark}
-	It is possible to proof that every two skeleta of a given category $\X$ are isomorphic (not only equivalent).
-For the remaining of this paper we assume that a skeleton $\ske$ of $\X$ and a functor $\pi\colon \X\to \ske$ are chosen once and for all.
-\end{remark}
-
-\begin{definition}
-	Let $(\X, \R)$ be a DPO-rewriting system, a \emph{decorated derivation} between two objects $G$ and $H$ is a triple $(\der{D}, \alpha, \omega)$, where $\der{D}$ is a derivation between $G$ and $H$, and $\alpha\colon \pi(G)\to G$ and $\omega\colon \pi(H)\to H$ are isomorphisms.
-\end{definition}
-
-\begin{notation}
-	We will extend the use of the words length, source and target to decorated derivations in the obvious way, forgetting the decorations $\alpha$ and $\omega$.
-\end{notation}
-
-\begin{example}A decorated derivation $(\der{D}, \alpha, \omega)$ with $\der{D}$ empty is just a span
-	\[\xymatrix{G & \pi(G) \ar[r]^-{\omega} \ar[l]_-{\alpha} & G}\]
-	in which both $\omega$ and $\alpha$ are isomorphisms.
-\end{example}
-
-As we are interested in objects only up to isomorphism, so we are interested in (decorated) derivations only up to some notion of coherent isomorphism between them.
-This is done with the help of \Cref{rem:func}.
-
-\begin{definition}Let $(\X, \R)$ be a DPO-rewriting system,  an \emph{abstraction equivalence} between two derivations $\der{D}$ and $\der{D'}$ with the same length and such that $r(\der{D})=r(\der{D}')$, is a family of isomorphisms $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ such that, for every $i\in [0, \lgh(\der{D})]$ the following diagram commutes
-	\[\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i} \ar[l]_{f'_i}&G'_{i+1}\\  L_i \ar[u]^{n'_i} \ar[d]_{n_i}& K_i \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar[l]_{l_i} &R\ar[u]^{h'_i} \ar[d]_{h_i}\\G_i \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole \ar[r]_{g_i}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{H_i}}}\]
-
-Given two decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, we say that they are \emph{abstraction equivalent}, if $\lgh(\der{D})=\lgh(\der{D}')$, $r(\der{D})=r(\der{D'})$, and there exists an of abstraction equivalence between $\der{D}$ and  $\der{D}$ such that the triangles below commute.
-\[\xymatrix@C=15pt{&\pi(G_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G_{n+1}) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G_0 \ar[rr]_{\phi_{G_0}} && G'_0 &G_{n+1} \ar[rr]_{\phi_{G_{n+1}}} && G'_{n+1} } \]
-We will use $\equiv^a$ to denote the resulting relation.
-\end{definition}
-
-\begin{remark}\label{rem:equi}
-	It is immediate to see that $\equiv^a$ is an equivalence relation.
-Indeed $(\der{D}, \alpha, \omega)$ is abstract equivalent to itself via the abstract equivalence with the identities as components.
-Furthermore, if  $\{\phi_X\}_{X\in \Deltamin(\der{D})}$  witnesses $(\der{D}, \alpha, \omega)\equiv_a (\der{D}', \alpha', \omega')$, then considering $\{\phi^{-1}_X\}_{X\in \Deltamin(\der{D})}$ shows $(\der{D}', \alpha', \omega)\equiv_a (\der{D}, \alpha, \omega)$.
-Finally, transitivity is assured composing abstract equivalences.
-
-	We will denote by $[\der{D}, \alpha, \omega]_a$ is just the equivalence class of  $(\der{D}, \alpha, \omega)$.
-	 Such equivalence classes will be called  \emph{abstract decorated derivation}.  
-\end{remark}
-
-\begin{remark}\label{rem:empty}
-Let $(\der{D},\alpha, \omega)$ be an empty derivation from an object $G$ and  $(\der{D}',\alpha', \omega')$ a another empty one from $G'$.
-If $(\der{D},\alpha, \omega)\equiv_a(\der{D}',\alpha', \omega')$ then an abstraction equivalence between $\der(D)$ and $\der{D}'$ is just an isomorphism $\phi\colon G\to G'$, so that $\pi(G)=\pi(G')$.
-Moreover, such isomorphism must fit in the diagrams below.
-\[\xymatrix@C=15pt{&\pi(G) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G\ar[rr]_{\phi} && G' &G \ar[rr]_{\phi} && G' } \]
-In particular, these two triangles imply that
-\begin{align*}
-	\alpha'\circ \alpha^{-1}&=\phi \\&=\omega'\circ \omega^{-1}
-\end{align*}
-\end{remark}
-
-\begin{remark}\label{rem:res} \Cref{prop:unique} can be restated as saying that, given two direct derivations $\dder{D}$ and $\dder{D'}$ with the same match, there exists an abstract equivalence between them whose first component is an identity.
-\end{remark}
-
-\begin{example}\label{rem:absequi}
-	Let $\der{D}$ be a derivation with source $G$ and target $H$. Let also $\phi:G'\to G$ and $\psi:H\to H'$ be two isomorphisms. Then for every $X\in \Deltamin(\der{D})$ we can define 
-	\[\varphi_X:=\begin{cases}
-		\phi^{-1} & X=G\\
-		\psi & X=H\\
-		\id{X} & \text{otherwise}
-	\end{cases}\]
-
-It is immediate to see that the family $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ is an abstraction equivalence between $\der{D}$ and $\phi *\der{D}*\psi$.	
-\end{example}
-
-\begin{definition}\label{def:conc}
-Let $(\der{D}, \alpha, \omega)$ be a decorated derivation between $G$ and $H$ and $(\der{D}', \alpha', \omega')$ one between $H'$ and $K$.
-If $H$ and $H'$ are isomorphic, so that $\pi(H)=\pi(H')$, we define the  \emph{composite decorated derivation} putting
-\[(\der{D}, \alpha, \omega)\cdot (\der{D}', \alpha', \omega'):=\begin{cases}
-(\der{D}', \alpha'\circ \omega^{-1}\circ \alpha, \omega')	&\lgh(\der{D})=0 \\
-	(\der{D}, \alpha, \omega \circ (\alpha')^{-1}\circ \omega')&\lgh(\der{D}')=0 \text{ and } \lgh(\der{D})\neq 0\\
-(\der{D}*\omega^{-1}\cdot \alpha'*\der{D'}, \alpha, \omega')	&\text{otherwise}
-\end{cases}\]
-\end{definition}
-
-\begin{remark}\label{rem:lgt}
-	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ two composable decorated derivations   such that $\lgh(\der{D})=n$ and $\lgh(\der{D}')=m$.	 Then $(\der{D}*\omega^{-1}\cdot \alpha'*\der{D'}, \alpha, \omega')$ has length $n+m$.
-\end{remark}
-
-The next proposition justifies the use of decorations, guaranteeing that concatenation of abstract decorated derivations is well-defined.
-\begin{lemma}\label{lem:conc}
-	Given a decorated derivation $(\der{D}, \alpha, \omega)$  between $G$ and $H$ and  another one $(\der{E}, \beta, \xi)$ between $E$ and $K$ with $\pi(H)=\pi(E)$.
-If  $(\der{D}', \alpha', \omega')$ and $(\der{E}', \beta', \xi')$ are two other decorated derivations such that
-	\[[\der{D}, \alpha, \omega]_a = [\der{D}', \alpha', \omega']_a \qquad [\der{D}, \beta, \xi]_a=[\der{E}', \beta', \xi']_a\]
-	Then
-	\[[(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)]_a=[(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')]_a\]
-\end{lemma}
-
-\begin{proof} Take two abstraction equivalences $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ and $\{\varphi_X\}_{X\in \Deltamin(\der{D})}$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ and between $(\der{E}, \beta, \xi)$ and $(\der{E}', \beta', \xi')$, respectively.
-To fix the notation, suppose that goes from $G'$ to $H'$ and $(\der{E}', \beta', \xi')$ from $E'$ to $K'$.
-We have three cases.
-
-\begin{itemize}
-	\item $\lgh(\der{D})=0$. Then, $\lgh(\der{D}')$ is $0$ too. By \Cref{def:conc} we have
-	\begin{align*}
-	(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)&=(\der{E}, \beta\circ \omega^{-1}\circ \alpha, \xi)\\
-		(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')&=(\der{E}', \beta'\circ (\omega')^{-1}\circ \alpha', \xi')
-	\end{align*}
- Now, notice that $G$ and $H$ must coincide.
-Moreover, by \Cref{rem:empty} we also know that $\pi(G)=\pi(G')$ too.
-The same \Cref{rem:empty} entails that the inner squares of the following diagram are commutative, so that the whole rectangle commutes too.
- \[\xymatrix@C=35pt{\pi(G) \ar[r]^{\alpha} \ar[d]_{\id{\pi(G)}}& G  \ar[d]_{\phi_G}\ar[r]^-{\omega^{-1}} & \pi(G) \ar[d]_{\id{\pi(G)}} \ar[r]^{\beta}& E \ar[d]^{\varphi_E}\\\pi(G') \ar[r]_{\alpha'}& G' \ar[r]_-{(\omega')^{-1}} & \pi(G') \ar[r]_{\beta'} & E'}\]
-
- We can  then conclude that $\{\varphi_X\}_{X\in \Deltamin(\der{D})}$ witnesses the fact that $(\der{E}, \beta\circ \omega^{-1}\circ \alpha, \xi)$ is abstraction equivalent to $(\der{E}', \beta'\circ (\omega')^{-1}\circ \alpha', \xi')$.
-
-\item $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})= 0$. As in the point above, we get that also $\der{E}'$  is an empty derivation, thus we have
-\begin{align*}
-	(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)&=(\der{D},  \alpha, \omega \circ \beta^{-1}\circ \xi)\\
-	(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')&=(\der{D}',  \alpha', \omega' \circ (\beta')^{-1}\circ \xi')
-\end{align*}
-In this case we have that $E=K$ and that $\pi(E)=\pi(E')$. From \Cref{rem:empty} we deduce that the diagram below commutes.
-\[\xymatrix@C=35pt{\pi(E) \ar[r]^{\xi} \ar[d]_{\id{\pi(E)}}& E  \ar[d]_{\varphi_E}\ar[r]^-{\beta^{-1}} & \pi(E) \ar[d]_{\id{\pi(E)}} \ar[r]^{\omega}& H \ar[d]^{\phi_H}\\\pi(E') \ar[r]_{\xi'}& E' \ar[r]_-{(\beta')^{-1}} & \pi(E') \ar[r]_{\omega'} & H'}\]
-The thesis now follows at once.
-	\item $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})\neq 0$. In this case we have
-	\begin{align*}
-		(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)&=(\der{D}*\omega^{-1}\cdot \beta*\der{E}, \alpha, \xi)\\
-		(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')&=(\der{D}'*(\omega')^{-1}\cdot \beta'*\der{E'}, \alpha', \xi')
-	\end{align*}
- To fix the notation, suppose that $\der{D}$, $\der{D}'$, $\der{E}$ and $\der{E}'$ are given by
-	\[\der{D}=\{\dder{D}_i\}_{i=0}^n \quad \der{D}'=\{\dder{D}'_i\}_{i=0}^n \quad \der{E}=\{\dder{E}_i\}_{i=0}^t \quad \der{E}'=\{\dder{E}'_i\}_{i=0}^t\]
-	Moreover, noticing that the rule applied by $\dder{D}_i$ and the one applied in $\mathcal{E}_i$  must coincide with, respectively, the one applied in $\dder{D}'_i$ and the one applied $\dder{E}'_i$.
-We will also assume that $\dder{D}_i$, $\dder{D}'_i$, $\dder{E}_i$ and $\dder{E}'_i$ are given, respectively, by the following four diagrams.
-	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}, i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}, i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}, i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}, i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}, i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}, i}} \\G_i & D_i \ar[r]_{g_{\der{D},i}} \ar[l]^{f_{\der{D},i}} & G_{i+1} & E_i & F_i\ar[r]_{g_{\der{E},i}} \ar[l]^{f_{\der{E},i}}  & E_{i+1}}\]
-	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}', i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}', i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}', i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}', i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}', i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}', i}} \\G'_i & D'_i \ar[r]_{g_{\der{D}',i}} \ar[l]^{f_{\der{D}',i}} & G'_{i+1} & E'_i & F'_i\ar[r]_{g_{\der{E}',i}} \ar[l]^{f_{\der{E}',i}}  & E'_{i+1}}\]
-
-Now, for every $X\in \Deltamin(\der{D}*\omega^{-1}\cdot \beta*\der{E})$ we can define
-\[\psi_X:=\begin{cases}
-	\phi_X & X\in  \Deltamin(\der{D})\text{ and } X\neq H\\\varphi_X & X\in  \Deltamin(\der{E}) \text{ and } X\neq E\\\id{\pi(H)}& X=\pi(H)\end{cases}\]
-Notice that, since $\psi_G=\phi_G$ and $\psi_K=\varphi_K$ we have at once  the commutativity of the triangles
-\[\xymatrix@C=15pt{&\pi(G) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(K) \ar[dr]^{\xi'} \ar[dl]_{\xi}\\ G\ar[rr]_{\psi_G} && G' &K \ar[rr]_{\psi_K} && K' } \]
-
-To show that $\{\psi_X\}_{\Deltamin(\der{D}*\omega^{-1}\cdot \beta*\der{E})}$ is an abstraction equivalence, it is now enough to prove the commutativity of the diagrams
-	\[\xymatrix@C=45pt@R=15pt{G'_n&D'_n \ar[r]^-{(\omega')^{-1}\circ g_{\der{D}',n}} \ar@/_.2cm/[dr]_(.6){g_{\der{D}',n}} \ar[l]_{f_{\der{D}',n}}&\pi(H') \\&&H' \ar[u]^{(\omega')^{-1}}\\  L_{\der{D}, n} \ar[uu]^{m_{\der{D}',n}} \ar[dd]_{m_{\der{D},n}}& K_{\der{D}, n} \ar[uu]^{k_{\der{D}',n}} \ar[dd]_{k_{\der{D},n}} \ar[r]^{r_{\der{D},n}} \ar[l]_{l_{\der{D},n}} &R_{\der{D}, n}\ar[u]^{h_{\der{D}',n}} \ar[d]_{h_{\der{D},n}}\\&&H \ar[d]_{\omega^{-1}}\\G_n \ar@/_.7cm/[uuuu]_(.35){\phi_{G_n}}|\hole&D_n\ar[l]^{f_{\der{D},n}}\ar@/_.7cm/[uuuu]_(.35){\phi_{D_n}}|\hole \ar@/^.2cm/[ur]^(.6){g_{\der{D},n}}\ar[r]_{\omega^{-1}\circ g_{\der{D},n}}&\pi(H)\ar@/_.7cm/[uuuu]_{\id{\pi(H)}}\\ \pi(E')&F'_0 \ar[l]_-{(\beta')^{-1}\circ f_{\der{E}',0}} \ar@/^.2cm/[dl]^(.6){f_{\der{E}',0}} \ar[r]^{g_{\der{E}',0}}&E'_1 \\E' \ar[u]_{(\beta')^{-1}}&& \\  L_{\der{E}, 0} \ar[u]_{m_{\der{E}', 0}} \ar[d]^{m_{\der{E}, 0}}& K_{\der{E}, 0} \ar[uu]_{k_{\der{E}', 0}} \ar[dd]^{k_{\der{E}, i}} \ar[r]^{r_{\der{E},0}} \ar[l]_{l_{\der{E},0}} &R_{\der{E}, 0}\ar[uu]_{h_{\der{E}',0}} \ar[dd]^{h_{\der{E},0}}\\E \ar[d]^{\beta^{-1}}&& \\\pi(E) \ar@/^.7cm/[uuuu]^{\id{\pi(E)}}&F_0\ar[l]^{\beta^{-1}\circ f_{\der{E},0}}\ar@/^.7cm/[uuuu]^(.35){\varphi_{F_0}}|\hole \ar@/_.2cm/[ul]_(.6){f_{\der{E},0}}\ar[r]_{g_{\der{E},0}}&E_1\ar@/^.7cm/[uuuu]^(.35){\varphi_{E_1}}|\hole}\]
-
-To see this, in turn, it is enough to show that	the squares
-\[\xymatrix{&R_{\der{D}, n} \ar[d]_{h_{\der{D}, n}}\ar[r]^{h_{\der{D}', n}} & H' \ar[d]^{(\omega')^{-1}} &L_{\der{E}, 0} \ar[d]_{m_{\der{E}, 0}}\ar[r]^{m_{\der{E}', 0}}& E' \ar[d]^{(\beta')^{-1}}\\&H\ar[r]_{\omega^{-1}} &\pi(H)&E \ar[r]_{\beta^{-1}} & \pi(E)\\D_n \ar[rr]^{\phi_{D_n}} \ar[d]_{g_{\der{D}, n}}&&D'_n \ar[d]^{g_{\der{D}', n}}&F_0 \ar[d]_{f_{\der{E}, 0}} \ar[rr]^{\varphi_{F_0}} && F_0' \ar[d]^{f_{\der{E}', 0}}\\H \ar[r]_-{\omega^{-1}} &\pi(H)&H' \ar[l]^-{(\omega')^{-1}}  &E \ar[r]_-{\beta^{-1}} & \pi(E) & E' \ar[l]^-{(\beta')^{-1}}}\]
-are commutative. For the first ones, we have
-	\begin{align*} 
-	\omega^{-1} \circ h_{\der{D}, n}&=\id{\pi(H)}\circ \omega^{-1} \circ h_{\der{D}, n} \\&=(\omega')^{-1}\circ \phi_H \circ \omega \circ \omega^{-1} \circ h_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H  \circ h_{\der{D}, n}\\&=(\omega')^{-1}  \circ h_{\der{D}', n}
-\end{align*} 
-and
-\begin{align*} 
-	\beta^{-1} \circ m_{\der{E}, 0}&=\id{\pi(E)}\circ \beta^{-1} \circ m_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_{E} \circ \beta \circ \beta^{-1} \circ m_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_{E}  \circ m_{\der{E}, 0}\\&=(\beta')^{-1}  \circ m_{\der{E}', 0}
-\end{align*}
-
-The commutativity of the second row of diagrams follows from
-\begin{align*}
- \omega^{-1} \circ g_{\der{D}, n}&=\id{\pi(H)}\circ \omega^{-1} \circ g_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H \circ \omega\circ \omega^{-1} \circ g_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H  \circ g_{\der{D}, n}\\&= (\omega')^{-1} \circ g_{\der{D}', n}\circ \phi_{D_n}
-r\end{align*}
-and
-\begin{align*}
-	\beta^{-1} \circ f_{\der{E}, 0}&=\id{\pi(E)}\circ \beta^{-1} \circ f_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_E \circ \beta\circ \beta^{-1} \circ f_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_E  \circ f_{\der{E}, 0}\\&= (\beta')^{-1} \circ f_{\der{E}', n}\circ \varphi_{F_0}
-\end{align*}
- The thesis now follows.	\qedhere 
-\end{itemize}	
-\end{proof}
-
-\begin{definition}
-	Let $(\X, \R)$ be a DPO-rewrityng system, with $\X$ an $\mathcal{M}$-adhesive category. The  category $\dpi$ is defined as follows:
-	\begin{itemize}
-		\item objects are isomorphism classes of objects of $\X$;
-		\item an arrow $[G]\to [H]$ is an equivalence class $[\der{D}, \alpha, \omega]_a$ of a decorated derivation between $G'$ and $H'$ for some $G'$ and $H'$ such that $\pi(G')=G$ and $\pi(H')=H$;
-		\item composition is concatenation of abstract decorated derivations;
-		\item the identity on $[G]$ is $[G, \alpha, \alpha]_a$, where $\alpha$ is any isomorphism $\pi(G)\to G$.	\end{itemize}
-\end{definition}
-
-\subsection{Consistent permutations}
-
-Given DPO-rewriting system $(\X, \R)$,  we have already noted in \Cref{rem:func} that a derivation $\der{D}$  determines a diagram $\Delta(\der{D})$ in $\X$.
-We can then wonder if such a diagram has a colimit.
-Clearly if $\der{D}$ is the empty derivation $G$ then a colimit for $\Delta(\der{D})$ is simply the object $G$.
-More generally, we have the following result.
-
-\begin{lemma}\label{lem:colim}
-	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO-rewriting system over it. The following properties hold true.
-	\begin{enumerate}
-		\item  If $\der{D}$ is a derivation from $G$ to $H$, then the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belongs to $\mathcal{M}$.
-		\item Let $\der{D}$ be the concatenation $\der{D}_1\cdot \der{D}_2$ of two derivations $\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^{n_1}$ between $G$ and $H$ and $\der{D}_2=\{\dder{D}_{2,j}\}_{j=0}^{n_2}$ between $H$ and $T$,  then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists too and there is a pushout square
-		\[\xymatrix{H\ar[r]^-{\iota_{2, H}} \ar@{>->}[d]_-{\iota_{1, H}} & \tproi{D}{2} \ar[d]^{p_2}\\  \tproi{D}{1} \ar[r]_{p_1}& \tpro{D}}\]
-		where $(\tproi{D}{1}, \{\iota_{1, X}\}_{X\in \Delta(\der{D}_1)})$ and $(\tproi{D}{2}, \{\iota_{2, X}\}_{X\in \Delta(\der{D}_2)})$ are the colimiting cocone for $\Delta(\der{D}_1)$ and $\Delta(\der{D}_2)$, respectively.
-	\end{enumerate}
-\end{lemma}
-\begin{remark}\label{rem:cof}
-Let $I:\Deltamin(\dder{D})\to \Delta(\dder{D})$ be the inclusion functor.
-It is immediate to see that such functor is \emph{final} \cite{mac2013categories}.
-This means that for every functor $F\colon \Delta(\dder{D})\to \Y$ we have:
-\begin{enumerate}
-	\item if  $(C, \{c_X\}_{X\in \Deltamin(\dder{D})})$ is colimiting for $F\circ I$, then there exists a colimiting cocone $(D, \{d_X\}_{X\in \Delta(\dder{D})})$ for $F$;
-	\item $(C, \{c_X\}_{X\in \Deltamin(\dder{D})})$ and $(D, \{d_X\}_{X\in \Delta(\dder{D})})$ are colimiting for, repsectively, $F\circ I$ and $F$, then the canonical arrow $\phi\colon C\to D$ induced by $(D, \{d_X\}_{X\in \Deltamin(\dder{D})})$ is an isomorphism.
-\end{enumerate}
-\end{remark}
-
-\begin{proof}\begin{enumerate}
-		\item Let us proceed by induction on the length of $\der{D}$.
-		\begin{itemize}
-			\item  $\lgh(\dder{D})=0$. then the $\tpro{\dder{D}}$ is simply $(G, \{\id{G}\})$ and $\id{G}\in \mathcal{M}$.¸
-			\item $\lgh(\dder{D})=0$. Suppose that $\dder{D}$ has as its single component the derivation
-			\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G& \ar@{>->}[l]^{f} D \ar[r]_{g}& H  \\}\]
-			The arrow $f$ is  the pushout of $l$ and so it is in in $\mathcal{M}$. We can thus consider the $\mathcal{M}$-pushout square
-			\[\xymatrix{D \ar@{>->}[d]_{f} \ar[r]^{g} & H \ar@{>->}[d]^{p} \\G \ar[r]_{q}& P }\]
-			Since $p\in \mathcal{M}$, the thesis follows immediately from \Cref{rem:cof}. 
-			\item $\lgh(\dder{D})\geq 2$.
-Let $\der{D}$ be $\{\dder{D}_i\}_{i=0}^n$ with $n\geq 1$.
-Let also $\der{D}'$ be $\{\dder{D}_i\}^{n-1}_{i=0}$ and $\rho_n=(l_n, r_n)$ be the rule applied in $\dder{D}_n$.
-The pushout of $l_n$ is the arrow $f_n\colon D_n\to G_n$ is in $\mathcal{M}$ and, by inductive hypothesis, $\iota_{G_{n}}\colon G_{n}\to \lpro \der{D}'\rpro$ is in $\mathcal{M}$ too.
-Thus, we can consider the diagram below, having a pushout as its lower half.
-			\[\xymatrix{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar@{>->}[l]_{l_{n}} \ar[r]^{r_{n}} & R_{n} \ar[d]^{h_n} \\G_{n} \ar@{>->}[d]_{\iota'_{G_{n}}}& \ar@{>->}[l]^{f_n} D_n \ar[r]_{g_n}& H  \ar@{>->}[d]^{q}\\ \lpro \der{D}' \ar[rr]_{p}\rpro && P}\]
-			Notice that, as in the point above, the arrow $q\colon H\to P$ is the pushout of an element in $\mathcal{M}$, therefore it is enough to show that the diagram so constructed provides a colimiting cocone for $\Delta(\der{D})$.
-
-			Let $(C, \{c_X\}_{X\in \Delta(\der{D})})$ be a cocone, since $\Delta(\der{D}')$ is a subdiagram of $\Delta(\der{D})$, we get another cocone $(c, \{c_X\}_{X\in \Delta(\der{D}')})$ which induces an arrow $c'\colon \lpro \der{D}' \rpro \to C$ such that
-			\begin{align*}
-				c'\circ \iota_{G_n} \circ f_n &=c_{G_n} \circ f_n\\&= c_{D_n}\\&= c_{H}\circ g_n
-			\end{align*}
-			Therefore the arrows $c'$ and $c_H$ induce a morphism $c\colon P\to C$ and the thesis now follows at once.
-		\end{itemize}
-
-		\item  As a first step, notice that $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D}_1)})$ and $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D}_2)})$ are cocone on, respectively, $\Delta(\der{D}_1)$ and $\Delta(\der{D}_2)$.
-Hence, there exist two arrows $p_1\colon \tproi{D}{1}\to \tpro{D}$, $p_2\colon \tproi{D}{2}\to \tpro{D}$ such that, for every $X\in  \Delta(\der{D}_1)$ and $Y\in  \Delta(\der{D}_2)$
-		\[p_1\circ \iota_{1, X} = \iota_X \qquad p_2\circ \iota_{2, Y}=\iota_{2,Y}\]
-		In particular, this entails the commutativity of the square
-				\[\xymatrix{H \ar[dr]^{\iota_H} \ar[r]^-{\iota_{2, H}} \ar@{>->}[d]_-{\iota_{1, H}} & \tproi{D}{2} \ar[d]^{p_2}\\  \tproi{D}{1} \ar[r]_{p_1}& \tpro{D}}\]
-
-	Let us now show that the square above is a pushout. Take two arrows $a\colon \tproi{D}{1}\to C$, $b\colon \tproi{D}{2}\to C$ such that
-	\[a\circ \iota_{1, H}=b\circ \iota_{2, H}\]
-	We can use the previous equality to define a cocone $(C, \{c_X\}_{X\in \Delta(\der{D})})$ putting:
-	\[c_X:=\begin{cases}
-		a\circ \iota_{1, X} & X\in \Delta(\der{D}_1)\\
-		b\circ \iota_{2, X} & X\in \Delta(\der{D}_2)
-	\end{cases}\]
-From this, we can deduce at once the existence of a unique $c\colon \tpro{D}\to C$ such that 
-\[c\circ \iota_X = c_X\]
-By construction, for every $X\in  \Delta(\der{D}_1)$ and $Y\in  \Delta(\der{D}_2)$ we have
-\[\begin{split}
-	c\circ p_1 \circ \iota_{1,X}&=c\circ \iota_{X}\\&=c_X \\&=a\circ \iota_{1,X}\\&=a\circ p_1\circ \iota_{1,X}
-\end{split}\qquad \begin{split}
-	c\circ p_2 \circ \iota_{2,Y}&=c\circ \iota_{Y}\\&=c_Y \\&=b\circ \iota_{2,Y}\\&=b\circ p_2\circ \iota_{2,Y}
-\end{split}\]
-Therefore
-\[c\circ p_1=a \qquad c\circ p_2 = b\]
-
-	For uniqueness, suppose that $c'\colon \tpro{D}\to C$ is such that
-	\[c'\circ p_1=a \qquad c'\circ p_2 = b\]
-Then, for every $X\in \Delta(\der{D})$ we have
-\begin{align*}
-	c'\circ \iota_X &= \begin{cases}
-	c'\circ p_1\circ \iota_{1, X} & X\in \Delta(\der{D}_1)\\
-	c'\circ p_2\circ \iota_{2, X} & X\in \Delta(\der{D}_2)
-	\end{cases}\\&=\begin{cases}
-a\circ \iota_{1, X} & X\in \Delta(\der{D}_1)\\
-b\circ \iota_{2, X} & X\in \Delta(\der{D}_2)
-	\end{cases}\\&=c_X\\&=c\circ \iota_X
-\end{align*}
-showing that $c'=c$ as wanted.	 \qedhere 
-	\end{enumerate}
-\end{proof}
-
-\begin{corollary}\label{cor:colim}
-Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ a derivation of length $n+1$ and fix an index $j\in[0,n]$. Define
-\[\der{D}^j_1:=\{\dder{D}_i\}_{i=0}^{j-1} \qquad  \der{D}^j_2=\{\dder{D}_j\} \qquad \der{D}^j_3:=\{\dder{D}_i\}_{i=j+1}^n\]
-with the convention that $\der{D}^0_1$ and $\der{D}^n_3$ are the empty derivation on, respectively, $G_0$ and $G_n$. Then the square below is a pushout and a pullback
-\[\xymatrix@C=30pt{D_{j} \ar[ddrr]^{\iota_{D_j}} \ar[r]^{g_j}\ar@{>->}[d]_{f_j}& G_{j+1} \ar[ddr]^{\iota_{G_{j+1}}} \ar[r]^-{\iota_{3, G_{j+1}}} & \lpro \der{D}^j_3\rpro \ar[dd]^{p_2} \\ G_j\ar[drr]_{\iota_{G_{j}}} \ar@{>->}[d]_{\iota_{1,G_j}}\\ \lpro \der{D}^j_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
-Where the two arrows $p_1\colon \lpro\der{D}^j_1 \rpro\to \tpro{D}$, $p_2\colon \lpro \der{D}^j_3\rpro \to \tpro{D}$ are induced by the cocones $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}^j_1)})$ and $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}^j_3)})$, respectively.
-\end{corollary}
-\begin{remark}
-If $\der{D}$ is empty then $\der{D}^j_1, \der{D}^j_2$ and $\der{D}^j_3$ are empty too.
-\end{remark}
-\begin{proof}
-We can notice that $\der{D}=\der{D}^j_1\cdot \der{D}^j_2 \cdot \der{D}^j_3$.
-By the first and the second point of \Cref{lem:colim} then we get the following diagram, in which all squares are $\mathcal{M}$-pushouts.
-
-\[\xymatrix@C=30pt{D_{j}  \ar[r]^{g_j}\ar@{>->}[d]_{f_j}& G_{j+1}  \ar[r]^-{\iota_{3,G_{j+1}}} \ar[d]_{\iota_{2, G_{j+1}}}  \ar@/^.5cm/[dd]^{\iota_{1,2, G_{j+1}}}& \lpro \der{D}^j_3\rpro \ar[dd]^{p_2} \\ G_j \ar[r]^{\iota_{2, G_j}}\ar@{>->}[d]_{\iota_{1,G_j}} & \lpro \der{D}^j_2\rpro \ar[d]_a\\ \lpro \der{D}^j_1 \rpro \ar@/_.4cm/[rr]_{p_1} \ar[r]^b &\lpro \der{D}^j_1\cdot \der{D}^j_2 \rpro \ar[r]^c&\tpro{D} }\]
-Applying \Cref{lem:po1} twice we get that the whole square is an $\mathcal{M}$-pushout. Then the thesis follows from \Cref{prop:pbpoad}.
-\end{proof}
-
-\begin{remark}\label{rem:zero1} In particular, considering $j=0$ or $j=n$, we get that the following two squares are $\mathcal{M}$-pushouts and, thus, pullbacks.
-	\[\xymatrix{D_0 \ar[r]^-{\iota_{3, D_0}} \ar@{>->}[d]_{f_0}& \lpro \der{D}^0_3 \rpro \ar@{>->}[d]^{p_2} &D_n \ar@{>->}[d]_{\iota_{1, D_n}}\ar[r]^{g_n}& G_n \ar@{>->}[d]^{\iota_{G_n}}\\ G \ar[r]_{\iota_G}& \tpro{D} & \lpro \der{D}^n_1 \rpro \ar[r]_{p_1}  & \tpro{D}}\]
-\end{remark}
-
-\begin{corollary}\label{cor:ele}
-	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ be a derivation between $G$ and $H$.
-Let $j$ and $k$ be two indexes less or equal than $n+1$ and suppose that $j< k$.
-Consider two arrows $a\colon T\to G_j$, $b\colon T\to G_k$.
-If $\iota_{G_j}\circ a = \iota_{G_k}\circ b$,
-	then  there exist a unique arrow $c\colon T\to D_j $  such that \[f_j\circ c = a\qquad \iota_{D_j}\circ c =\iota_{G_k}\circ b\]
-	\end{corollary}
-\begin{proof} Consider the diagram
-			\[\xymatrix@C=34pt{T  \ar@/_.6cm/[dd]_{a}\ar@{.>}[d]^{c}\ar[rr]^{b}&& G_k \ar[d]_{\iota_{3, G_k}} \ar@/^.6cm/[ddd]^{\iota_{G_k}}\\D_{j} \ar[r]^{g_j} \ar[ddrr]^{\iota_{D_j}}\ar@{>->}[d]^{f_j}& G_{j+1} \ar[r]^-{\iota_{3,G_{j+1}}} \ar[ddr]^{\iota_{G_{j+1}}} & \lpro \der{D}^j_3\rpro \ar[dd]_(.6){p_2} \\ G_j \ar@{>->}[d]_{\iota_{1,G_j}} \ar[drr]_{\iota_{G_j}}\\ \lpro \der{D}^j_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
-			Thanks to \Cref{cor:colim} we know that the bottom right rectangle in the diagram above is a pullback and the thesis follows at once.
-\end{proof}
-
-So equipped, we can introduce the notion of \emph{consistent permutation}.
-
-\begin{definition}[Consistent permutation]\label{def:permcon}
-	Let $\X$ be an $\mathcal{M}$-adhesive category and consider a left-linear DPO-rewriting system $(\X, \R)$ on it.
-Take two non-empty decorated derivations $(\der{D}, \alpha, \omega)$ and  $(\der{D}', \alpha', \omega')$ with the same length and with isomorphic sources and targets.
-
-	 	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with assciated sequence of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma\colon [0,n]\to [0,n]$  such that, for every $i\in [0,n]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
-	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_\sigma}&   \pi(G_{n+1}) \ar[r]^{\omega} \ar[d]_{\omega'} & G_{n+1} \ar@{>->}[r]^{\iota_{G_{n+1}}} &\tpro{D} \ar[d]^{\xi_\sigma}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro& G'_{n+1} \ar@{>->}[rr]_{\iota'_{G'_{n+1}}} & &\lpro \der{D}' \rpro\\L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
-\end{definition}
-
-\begin{remark}
-The commutativity of the last two rectangles in \Cref{def:permcon}, is equivalent to the commutativity of the following bigger diagram.		
-\[\xymatrix@C=40pt{G_i\ar@/^1cm/[rrr]^{\iota_{G_{i}}}&D_i\ar@/^.4cm/[rr]^(.35){\iota_{D_i}} \ar[r]_{g_i} \ar@{>->}[l]^{f_i}&G_{i+1} \ar[r]_{\iota_{G_{i+1}}}&\tpro{D} \ar[dd]^{\xi_\sigma}\\  L_i \ar[u]^{n_i} \ar[d]_{n'_{\sigma(i)}}& K_i \ar[d]^{k'_{\sigma(i)}} \ar[u]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i} &R\ar[u]^{h_i} \ar[d]_{h'_{\sigma(i)}}\\G'_{\sigma(i)}\ar@/_1cm/[rrr]_{\iota'_{G'_{\sigma(i)}}} &D'_{\sigma(i)}\ar@{>->}[l]_{f'_{\sigma(i)}} \ar[r]^{g'_i} \ar@/_.4cm/[rr]_(.35){\iota'_{D'_{\sigma(i)}}}&G'_{\sigma(i)+1} \ar[r]^{\iota'_{G'_{\sigma{i}+1}}}& \lpro\der{D}' \rpro }\]
-This follows at once from the following chain of identities::
-\begin{align*}
-	\xi_\sigma \circ \iota_{D_i}\circ k_i&=\xi_\sigma \circ \iota_{G_{i}} \circ f_i\\&= \xi_\sigma \circ \iota_{G_{i}}\circ m_i \circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ m'_i\circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ f'_{\sigma(i)}\circ k'_i\\&=\iota_{D'_\sigma(i)}\circ k_i'
-\end{align*}
-\end{remark}
-
-\begin{remark}\label{rem:coproj}
-Notice that, in particular, the previous diagram entails
-		\[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
-\end{remark}
-
-\begin{remark}\label{rem:inversa}
-Let $\sigma\colon [0,n]\to [0,n]$ be a consistent permutation between $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, then its inverse $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$.
-Indeed, it is enough to consider, as mediating isomorphism, the inverse $\xi^{-1}_\sigma$ of $\xi_\sigma$.
-\end{remark}
-
-\begin{remark}\label{rem:comp} Consistent permutations can be composed.
-Indeed, given decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$ all of length $n$, if $\sigma$ is a consistent permutation between the first two and $\sigma'$ one between the second and the third, then  we have diagrams
-	\[\xymatrix@C=18pt{ & G_0 \ar[rr]^{\iota_{G_0}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_{n} \ar@{>->}[rr]^{\iota_{ G_{n}}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G_0) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G'_0 \ar[rr]^{\iota'_{G'_0}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&\pi({ G_{n}})\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & { G'_{n}} \ar@{>->}[rr]^{\iota'_{{ G'_{n}}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_0  \ar[rr]_{\hat{\iota}_{\hat{G}_0}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_n \ar@{>->}[rr]_{\hat{\iota}_{\hat{G}_n}}&& \lpro \hat{\der{D}} \rpro \\& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_{\sigma'(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\sigma'(\sigma(i))} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}} \rpro	}\]
-	We deduce at once that $\sigma'\circ \sigma$ is a consistent permutation with mediating isomorphism given by $\xi_{\sigma'} \circ \xi_\sigma$.
-\end{remark}
-
-\begin{example} RISCRIVERE Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstraction equivalent non-empty decorated derivations of length $n+1$.
-Then the identity permutation $\id{[0,n]}$ is a consistent permutation between them.
-In such a case $\xi_{\id{[0,n]}}$ is simply the isomorphism induced by any abstraction equivalence $\{\phi_X\}_{X\in \Delta(X)}$.
-
-	If $\der{D}$ and $\der{D}'$ are empty, then the converse also holds: indeed in such a case a mediating isomorphism provides the wanted abstraction equivalence.
-\end{example}
-
-\begin{example}\todo{identità consistente non implica astrazione}
-\end{example}
-
-\begin{proposition}\label{prop:uniqu}
-	Let $\sigma,\sigma'\colon [0,n]\rightrightarrows [0,n]$ be two consistent permutations between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.  Then the following hold true:
-	\begin{enumerate}
-	\item $\xi_\sigma \circ \iota_{G_0} = \xi_{\sigma'} \circ \iota_{G_0}$;
-	\item  $\xi_\sigma \circ \iota_{G_i}=\xi_{\sigma'} \circ \iota_{G_i}$ for every index $i\in [0,n]$ such that $\sigma_{|[0,i]}=\sigma'_{|[0,i]}$.
-	\end{enumerate}
-\end{proposition}
-\begin{proof}\begin{enumerate}
-		\item This follows at once noticing that both $\xi_\sigma \circ \iota_{G_0}$ and $\xi_{\sigma'} \circ \iota_{G_0}$ are equal to $\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}$.
-		\item  If $\sigma(0)\neq \sigma'(0)$ there is nothing to show. Otherwise, let $j$ be the maximum of the set
-		\[\{i\in [0,n]\mid \sigma_{|[0,i]}=\sigma'_{|[0,i]}\}\]
-		We proceed by induction on $i\in [0,j]$. 
-		\begin{itemize}
-			\item If $i=0$ the thesis follows from point $1$.
-			\item If $i>0$, we know that there is a pushout square
-			\[\xymatrix{K_{i-1}\ar[r]^{r_{i-1}} \ar[d]_{k_{i-1}}& R_{i-1} \ar[d]^{h_{i-1}}\\ D_{i-1} \ar[r]_{g_{i-1}}& G_i}\] 
-			By \Cref{rem:coproj} we know that
-			\begin{align*}
-				\xi_\sigma \circ \iota_{G_i}\circ h_{i-1}&=  \xi_\sigma\circ \iota_{R_{i-1}}\\&=\iota'_{R_{\sigma(i-1)}}\\&=\iota'_{R_{\sigma'(i-1)}}\\&=\xi_{\sigma'}\circ \iota_{R_{i-1}}\\&=\xi_{\sigma'} \circ \iota_{G_i}\circ h_{i-1}
-			\end{align*}
-			But, by the induction hypothesis we also have
-			\begin{align*}
-				\xi_\sigma \circ \iota_{G_i}\circ g_{i-1}&=\xi_{\sigma}\circ \iota_{D_{i-1}}\\&=\xi_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi_{\sigma'}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi_{\sigma'}\circ \iota_{D_{i-1}} \\&=\xi_{\sigma'}\circ \iota_{G_{i}} \circ g_{i-1}
-			\end{align*}
-			The thesis now follows.			\qedhere
-		\end{itemize}
-	\end{enumerate}
-\end{proof}
-
-Now, notice that, given a consistent permutation $\sigma\colon [0,n]\to[0,n]$, we already know, by \Cref{rem:coproj} that
-\[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
-	Moreover, $\xi_\sigma \circ \iota_{D_i}$ must be $\xi_\sigma \circ \iota_{G_i}\circ f_i$.
-Thus $\xi_\sigma$ is uniquely determined by $\xi_{\sigma} \circ \iota_{G_i}$ for every $i\in [0, n]$.
-In particular,  \Cref{prop:uniqu} entails the following.
-\begin{corollary} For every consistent permutation $\sigma$ between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, the mediating isomorphism $\xi_\sigma\colon \tpro{D}\to \lpro \der{D}'\rpro$ is unique.
-\end{corollary}
-
-We are now ready to prove the central result of this section.
-
-\begin{lemma} Let $(\X,R)$ be a left-linear DPO-rewriting system.
-Consider two consistent permutation $\sigma,\sigma'\colon [0,n]\rightrightarrows [0,n]$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
-Suppose that $\sigma\neq \sigma'$ and let $j$ be the minimum index such that $\sigma(j)\neq \sigma'(j)$.
-Let also $r(\der{D})$ be $\{\rho_i\}_{i=0}^n$.
+%
+An event is still a computation that cannot be decomposed
+as the join of other computations, hence, in order theoretical terms,
+it is an irreducible.
+%
+However, due to unstability, irreducibles are not necessarily primes:
+two different irreducibles can represent the same computation step
+with different minimal enablings.  In~\cite{baldan2017domains} this
+is worked out for DPO rewriting systems over graphs. However the proof
+relies on a wrong characterisation of independence which fails for non
+linear rules. Here we rework in depth the result and extend it to DPO
+rewriting over a large class of adhesive categories.
+
+\include{permutations.tex}
+
+\include{domains.tex}
+
+\todo{integrare sopra}
+\newpage
+QUOZIENTI VARI
+
+The setting from now on is: $\X$ $\mathcal{M}$-adhesive, $(\mathcal{E}, \mathcal{M})$ a proper (maybe also stable) factorization system. $\X$ has all pushouts.
+
+\begin{lemma}\label{lem:pushandpullpb}
+	Let $\X$ be a category and suppose that the diagram below is given.
+	\[\xymatrix{ P \ar[r]^{p_0} \ar[d]_{p_1}& A  \ar@/^.2cm/[ddr]^{k_0}\ar[d]^{f}\\  B  \ar@/_.2cm/[drr]_{k_1} \ar[r]_g & C \ar[dr]^{h}\\&& D }\]
 	Then the following hold true:
 	\begin{enumerate}
-		\item if $j=0$, then the rule $\rho_0$ is not consuming;
-		\item if $j\neq 0$ then the rule $\rho_{j-1}$ is not consuming.
+		\item if the outer boundary is a pullback, then the inner square is a pullback too;
+		\item if the inner square is a pullback and $h$ is mono then also the outer square is a pullback.
 	\end{enumerate}
@@
 \begin{proof}\begin{enumerate}
-		\item Let $k$ be $\sigma^{-1}(\sigma'(0))$ and notice that, since $\sigma(0)\neq \sigma'(0)$, then $0< k$.  By  the first point of  \Cref{prop:uniqu} we can consider the diagram
-		\[\xymatrix@C=40pt{& L_0 \ar[d]_{m'_{\sigma'(0)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{0}} \\G_{0} \ar@/_.2cm/[drr]_(.3){\iota_{G_0}}|(.515)\hole \ar[d]_{\iota_{G_0}}& G'_{\sigma'(0)} \ar[d]^{\iota_{G'_{\sigma'(0)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\sigma'}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
-	From \Cref{cor:ele}, we can conclude that there exists $c\colon L_0\to D_0$ such that $f_0\circ c=m_0$. We thus have the solid part of the commutative diagram below.
-		\[\xymatrix{L_0 \ar@/^.3cm/[drr]^{\id{L_0}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_0 \ar[d]_{k_0}\ar@{>->}[r]^{l_0}& L_0 \ar[d]^{m_0} \\& D_0 \ar@{>->}[r]_{f_0} & G_0} \]
-		The internal square is an $\mathcal{M}$-pushout and thus a pullback, by \Cref{prop:pbpoad}, so that we have the existence of the dotted $t\colon L_0\to K_0$.
-Therefore $\id{L_0}=l_0\circ t$, proving that $l_0$ is an epimorphism.
-The thesis now follows from \Cref{cor:rego}.
-		\item  Let $k$ be $\sigma^{-1}(\sigma'(j-1))$ and notice that $\rho_{j-1}=\rho_k$.
-By definition of $j$, $\sigma_{|[0,j-1]}=\sigma'_{|[0,j-1]}$, thus the second point of \Cref{prop:unique} yields the diagram
-			\[\xymatrix@C=40pt{& L_{j-1} \ar[d]_{m'_{\sigma'(j-1)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{j-1}} \\G_{j-1} \ar@/_.2cm/[drr]_(.3){\iota_{G_{j-1}}}|(.515)\hole \ar[d]_{\iota_{G_{j-1}}}& G'_{\sigma'(j-1)} \ar[d]^{\iota_{G'_{\sigma'(j-1)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\sigma'}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
-			Let $a$ be $\min(j-1, k)$, by \Cref{cor:ele},  there exists $c\colon L_{j-1}\to D_a$ such that $f_a\circ c=m_a$. As before this yields the solid part of the following diagram
-			\[\xymatrix{L_{j-1} \ar@/^.3cm/[drr]^{\id{L_{j-1}}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_{j-1} \ar[d]_{k_a}\ar@{>->}[r]^{l_{j-1}}& L_{j-1} \ar[d]^{m_a} \\& D_a \ar@{>->}[r]_{f_a} & G_a} \]
-			The existence of the dotted $t\colon L_{j-1}\to K_{j-1}$ follows from  \Cref{prop:pbpoad} and we can conclude. \qedhere
+		\item Let $e_0\colon E\to A$ and $e_1\colon E\to B$ be a pair of arrows such that 
+		\[f\circ e_0=g\circ e_1\]
+		Then we also have 
+		\begin{align*}
+		k_0\circ e_0 &= h\circ f\circ e_0\\&=h\circ g \circ e_1\\&=k_1\circ e_1
+		\end{align*}
+		Thus there exists a unique arrow $e\colon E\to P$ such that
+		\[p_0\circ e= e_0 \qquad p_1\circ e=e_1\]
+		which entails our claim.
+		\item We proceed as before considering two arrows $e_0\colon E\to A$ and $e_1\colon E\to B$, but in this case we suppose that 
+		\[k_0\circ e_0=k_1\circ e_1\]
+		In particular, we have
+		\begin{align*}
+			h\circ f \circ e_0 &= k_0\circ e_0\\&=k_1\circ e_1\\&=h\circ g\circ e_1
+		\end{align*}
+		Thus, since $h$ is mono, we can deduce that $f\circ e_0$ and $g\circ e_1$ are equal and the thesis now follows immediately.
+		\qedhere 
 	\end{enumerate}
@@
 
-\begin{corollary}[Uniqueness of consistent permutation]\label{cor:unique}
-Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that every rule in $R$ is consuming.
-For every two non-empty decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, there exists at most one consistent permutation between them.
-\end{corollary}
-
-We end this section proving two rather technical result about consistent permutations between composite decorated derivations.
-
-\begin{proposition}\label{prop:sum} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstract decorated derivations such that
-	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)\]
-	If $\sigma\colon [0, \lgh(\der{D}_1)-1]\to [0, \lgh(\der{D}_1)-1]$ is a consistent permutation between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$ and $\tau:[0, \lgh(\der{D}_2)-1]\to [0, \lgh(\der{D}_2)-1]$ one between $(\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$, then
-	\[\sigma+\tau\colon[0, \lgh(\der{D})-1]\to[0, \lgh(\der{D})-1] \qquad n \mapsto \begin{cases}
-		\sigma(n) & n < \lgh(\der{D}_1)\\
-		\tau(n-\lgh(\der{D}_1)) &   \lgh(\der{D}_1) \leq n
-	\end{cases}\]
-	is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
-\end{proposition}
+	\begin{lemma}\label{lem:cond} Let $f\colon A\to C$, $g\colon B\to C$ and $h\colon C\to D$ be arrows in a category $\X$, let also $l_0\colon A'\to A$, $l_1\colon B'\to B$ be two monomorphisms.
+Suppose moreover, that the following squares are pullbacks:
+		\[\xymatrix@C=35pt{Q \ar[r]^{q_0} \ar[d]_{q_1} & A' \ar[d]^{h\circ f\circ l_0} & P \ar[r]^{p_0} \ar[d]_{p_1} & A \ar[d]^{f} & Q  \ar[r]^{l_0\circ q_0} \ar[d]_{l_1\circ q_1}& A \ar[d]^{h\circ f}\\ B \ar[r]_{h\circ g\circ l_1} &D& B \ar[r]_{g}& C &  B \ar[r]_{h\circ g} & D}\]
+		Then there exists an arrow $\phi\colon P\to Q$ such that $(P, \{q_i\circ \phi\}_{i=0}^1)$ is a pullback for $f\circ l_0$ along $g\circ l_1$.
+	\end{lemma} 
 	\begin{proof}
-	Let us start fixing some notation.
-Given $X_1\in \Delta(\der{D}_1)$, $X_2\in \Delta(\der{D}_2)$, $X'_1\in \Delta(\der{D}'_1)$, $X'_2\in \Delta(\der{D}'_2)$, we will denote their coprojections into, respectively, $\lpro \der{D}_1\rpro$, $\lpro \der{D}'_2\rpro$, $\lpro \der{D}'_1\rpro$, $\lpro \der{D}'_2\rpro$ by
-	$\iota_{1, X_1}\colon X_1\to \lpro\der{D}_1\rpro$, $\iota_{1, X_2}\colon X_2\to \lpro\der{D}_1\rpro$, $\iota'_{1, X'_1}\colon X'_1\to \lpro\der{D}'_1\rpro$ and $\iota'_{2, X'_2}\colon X'_2\to \lpro\der{D}_1\rpro$.
-
-	Now that these preliminaries matters have been addressed, we will proceed with the rest of the proof.. We split the proof in three cases.
-	\begin{itemize}
-		\item $\lgh(\der{D}_1)=0$. Thus $\lgh(\der{D}'_1)=0$ too  and we have
+To prove the existence of $\phi\colon P\to Q$ it's enough to consider the solid part of the diagram below.
+\[\xymatrix@C=30pt{P \ar@{.>}[dr]^{\phi} \ar@/^.2cm/[drr]^{p_0} \ar@/_.2cm/[ddr]_{p_1}\\ & Q  \ar[r]^(.4){l_0\circ q_0} \ar[d]^{l_1\circ q_1}& A \ar[d]^{h\circ f} \\ &B \ar[r]_{h\circ g} & D}\]
+Notice that $\phi$ is a monomorphism. If $\phi\circ a=\phi \circ b$ for some $a,b\colon T\rightrightarrows P$ then
+\[\begin{split}
+	p_0\circ a&=l_0\circ q_0\circ \phi \circ a\\&=l_0\circ q_0\circ \phi \circ b\\&=p_0\circ b
+\end{split} \qquad \begin{split}
+p_1\circ a&=l_1\circ q_1\circ \phi \circ a\\&=l_1\circ q_1\circ \phi \circ b\\&=p_1\circ b
+\end{split} \]
+
+Moreover, we also have the following chain of equalities, showing that  $(P, \{q_i\circ \phi\}_{i=0}^1)$  is a candidate to be a pullback of $f\circ l_0$ along $g\circ l_1$.
 \begin{align*}
-			(\der{D}, \alpha, \omega)&=(\der{D}_2, \alpha_2\circ \omega_1^{-1}\circ \alpha_1, \omega_2) \\ (\der{D}', \alpha', \omega')&=(\der{D}'_2, \alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1, \omega'_2)
+f\circ l_0\circ q_0\circ \phi &=f\circ p_0\\&=g\circ p_1\\&=g\circ l_1\circ q_1\circ \phi 
 \end{align*}
-		Moreover, in this case $\sigma$ must be $\id{\emptyset}$ and $\sigma+\tau$ must be equal to $\tau$. The thesis now follows from the commutativity of the following diagram.
-		\[\xymatrix@C=35pt{& G_{1,0}\ar[dd]^{\xi_{\id{\emptyset}}} \ar[dr]^{\omega^{-1}_1}&&G_{2,0}\ar[r]^-{\iota_{2, G_{2,0}}} & \lpro \der{D}_2\rpro \ar[dd]^{\xi_{\tau}}\\\pi(G_{1,0})  \ar[ur]^{\alpha_1} \ar[dr]_{\alpha'_1}&& \pi(G_{2,0}) \ar[ur]^{\alpha_2} \ar[dr]_{\alpha'_2}\\& G'_{1,0} \ar[ur]_{(\omega'_1)^{-1}}&&G'_{2,0} \ar[r]_-{\iota'_{2, G_{2,0}}}& \lpro \der{D}'_2\rpro}\]
-
-		\item $\lgh(\der{D}_2)=0$.  As before this implies that also $\lgh(\der{D}'_2)$ is $0$.  Applying \Cref{def:conc} we get 
-		\begin{align*}
-			(\der{D}, \alpha, \omega)&=(\der{D}_1, \alpha_1, \omega_1 \circ (\alpha_2)^{-1}\circ \omega_2) \\ (\der{D}', \alpha', \omega')&=(\der{D}'_1, \alpha'_1, \omega'_1 \circ (\alpha'_2)^{-1}\circ \omega'_2)
-		\end{align*}
-		Since $\der{D}_2$ is empty, then $\tau=\id{\emptyset}$ and $\sigma+\tau=\sigma$. Let $n$ be $\lg(\der{D}_1)$, as before the thesis follows from the diagram below.
-		\[\xymatrix@C=35pt{& G_{2,0}\ar[dd]^{\xi_{\id{\emptyset}}} \ar[dr]^{\alpha^{-1}_2}&&G_{1,n}\ar@{>->}[r]^-{\iota_{1, G_{1,n}}} & \lpro \der{D}_2\rpro \ar[dd]^{\xi_{\sigma_1}}\\\pi(G_{2,0})  \ar[ur]^{\omega_2} \ar[dr]_{\omega'_2}&& \pi(G_{1,n}) \ar[ur]^{\omega_1} \ar[dr]_{\omega'_1}\\& G'_{2,0} \ar[ur]_{(\alpha'_1)^{-1}}&&G'_{1,n} \ar@{>->}[r]_-{\iota'_{1, G_{1,n}}}& \lpro \der{D}'_2\rpro}\]
-		\item   $\lgh(\der{D}_1)\neq0$ and $\lgh(\der{D}_2)\neq 0$. Thus $\der{D}'_1$ and $\der{D}'_2$ are non-empty too. In this case we have:
-		\begin{align*}
-			(\der{D}, \alpha, \omega)&=(\der{D}_1*\omega_1^{-1}\cdot \alpha_2*\der{D}_2, \alpha_1, \omega_2)\\
-			(\der{D}', \alpha', \omega')&=(\der{D}'_1*(\omega'_1)^{-1}\cdot \alpha'_2*\der{D}'_2, \alpha'_1, \omega'_2)
-		\end{align*}
-
-		Let us assume that $\der{D}_1$, $\der{D}'_1$, $\der{D}_2$ and $\der{D}'_2$ are given by
-		\[\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^n \quad \der{D}'_1=\{\dder{D}'_{1,i}\}_{i=0}^n \quad \der{D}_2=\{\dder{D}_{2,i}\}_{i=0}^t \quad \der{D}_2'=\{\dder{D}'_{2,i}\}_{i=0}^t\]
-		By definition of consistent permutation, the rule applied by $\dder{D}_{1,i}$ and the one applied in $\dder{D}_{2,i}$  must coincide with, respectively, the one applied in $\dder{D}'_{1,i}$ and the one applied $\dder{D}'_{2,1}$.
-Let $\dder{D}_{1,i}$, $\dder{D}'_{1,i}$, $\dder{D}_{2,i}$ and $\dder{D}'_{2,i}$ be given, by the following four diagrams.
-		\[\xymatrix{L_{1,i} \ar[d]_{m_{1, i}}& K_{1,i} \ar[d]_{k_{1, i}} \ar[r]^{r_{1,i}} \ar@{>->}[l]_{l_{1,i}} & R_{1,i}\ar[d]^{h_{1, i}} &L_{1,i} \ar[d]_{m'_{1, i}}& K_{1,i} \ar[d]_{k'_{1, i}} \ar[r]^{r_{1,i}} \ar@{>->}[l]_{l_{1,i}} & R_{1,i}\ar[d]^{h'_{1, i}} \\G_{1,i} & D_{1,i} \ar[r]_{g_{1,i}} \ar@{>->}[l]^{f_{1,i}} & G_{1,i+1} & G'_{1,i} & D'_{1,i}\ar[r]_{g'_{1,i}} \ar@{>->}[l]^{f'_{1,i}}  & G'_{1,i+1}}\]
-		\[\xymatrix{L_{2,i} \ar[d]_{m_{2, i}}& K_{2,i} \ar[d]_{k_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h_{2, i}} &L_{2,i} \ar[d]_{m'_{2, i}}& K_{2,i} \ar[d]_{k'_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h'_{2, i}} \\G_{2,i} & D_{2,i} \ar[r]_{g_{2,i}} \ar@{>->}[l]^{f_{2,i}} & G_{2,i+1} & G'_{2,i} & D'_{2,i}\ar[r]_{g'_{2,i}} \ar@{>->}[l]^{f'_{2,i}}  & G'_{2,i+1}}\]
-	\end{itemize}
-	Let $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$, $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$, $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$ and $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$ be colimiting cocones.
-Define two other cocones and  $\der{D}'_1*(\omega'_1)^{-1}\cdot \alpha'_2*\der{D}'_2$
-	Using point $2$ of \Cref{lem:colim} we get two pushout squares
-	\[\xymatrix{\pi(H) & }\]
-	Now, notice that $()$ and $bb$ are cocones on ... so that there exists... such that. 
+Let now $e_0\colon E\to A'$ and $e_1\colon E\to B'$ be arrows such that 
+\[f\circ l_0\circ e_0=g\circ l_1\circ e_1\]
+By hypothesis $(P, \{p_i\}_{i=0}^1)$ is a pullback of $f$ along $g$, therefore we there is a unique  arrow $e\colon E\to P$ such that
+\[p_0\circ e = l_0\circ e_0 \qquad p_1\circ e=l_1\circ e_1\]
+But then the two identities
+\[\begin{split}
+	l_0\circ q_0\circ \phi\circ e&=p_0\circ e\\& =l_0\circ e_0 \end{split} \qquad \begin{split}l_1\circ q_1\circ \phi\circ e&=p_1\circ e\\& =l_1\circ e_1
+\end{split}\]
+allow us to conclude that 
+\[q_0\circ \phi\circ e=l_0\circ e_0 \qquad q_1\circ \phi\circ e=l_1\circ e_1\]
+
+Finally, if $e'\colon E \to P$ is another arrow such that 		
+\[q_0\circ \phi\circ e'=l_0\circ e_0 \qquad q_1\circ \phi\circ e'=l_1\circ e_1\]
+then we have 
+\[q_0\circ \phi\circ e'=q_0\circ \phi\circ e \qquad q_1\circ \phi\circ e'=q_1\circ \phi\circ e\]
+Therefore $\phi\circ e'=\phi \circ e$ and we can conclude since $\phi$ is mono.
 	\end{proof}
 
-\begin{corollary}\label{cor:presuffix}
-	\todo{prefisso e suffisso}
-\end{corollary}
+\begin{lemma}
+	Da ind pair a pb
+\end{lemma}
+
 \begin{proof}
@@
 
-\section{Shift equivalence and traces}
-\todo{A VERY NICE INTRO}
-
-\subsection{Sequentially independent and switchable derivations}
-\todo{A VERY NICE INTRO}
-
-\begin{definition}  Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Let also $\dder{D}\colon G\Mapsto H$ and $\dder{D'}\colon H\Mapsto T$ be the two direct derivations depicted below.
-
-\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
-
-An \emph{independence pair} between $\dder{D}$ and $\dder{D'}$, is a pair of  arrows $i_1\colon R\to D'$ and $i_2\colon L'\to D$ such that the following diagram commutes.
-
-\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
-We will say that $\dder{D}$ and $\dder{D'}$ are \emph{weakly sequentially independent} if an independence pair exists.
-If such independence pair is unique we will say that $\dder{D}$ and $\dder{D'}$ are \emph{sequentially independent}.
-\end{definition}
-
-\begin{example}
-	\todo{sequential independence}
-\end{example}
-\begin{example}
-	\todo{sequential independence che serva anche per es successivo}
-\end{example}
-
-\begin{remark}\label{rem:weak} Let $(i_1, i_2)$ and $(j_1, j_2)$ be independence pairs for the direct derivations $\dder{D}$ and $\dder{D'}$. Notice that, by definition, we have
-	\begin{align*}f'\circ i_1&=h\\&=f'\circ j_1
-	\end{align*}
-	On the other hand, 
-	 $f'\colon D'\to H$ is  the pushout of $l'\colon K'\to L'$ and so it is in $\mathcal{M}$, implying $j_1=i_1$.
-If, moreover, we suppose that the rule $\rho$ applied in $\dder{D}$ is linear, then $g\colon D\to H$ is in $\mathcal{M}$ too, hence, from the equation
-	 \begin{align*}
-	 g\circ i_2&=h \\&= g\circ j_2
-	 \end{align*}
-we can deduce that $i_2=j_2$, too.
-
-Summing up, if $(\X, \R)$ is a linear DPO-rewriting system, then sequential independence and weak sequential independence coincide. 
-\end{remark}
-
-When working with linear rewriting systems, (weakly) sequential independent direct derivations can be switched, producing two new (weakly) sequential independent direct derivations between the same objects \cite[Thm.~$7.7$]{lack2005adhesive} .
-This is no more the case if the rules are only left-linear, as shown by the next example.
-
-\begin{example}\label{ex:difficile}
-	\todo{pensare ad un esempio in cui l'indipendenza non basta }
-\end{example}
-
-To fix this problem, we adapt the notion of \emph{canonical filler} from \cite{heindel2009category}.
-
-\begin{definition}\label{def:filler}
-Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ $\mathcal{M}$-adhesive. Let also $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$ be the two derivations depicted below.
-\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
-Since $f'$ is in $\mathcal{M}$, we can moreover consider a pullback square
-\[\xymatrix{P \ar[r]^{p} \ar[d]_{p'}& D\ar[d]^{g} \\ D' \ar[r]_{f'} & H}\]
-
-A \emph{filler} between $\dder{D}$ and $\dder{D}'$ is  given by a pair of arrows $u\colon K\to P$ and $u'\colon K'\to P$ satisfying the following conditions
-\begin{enumerate}
-	\item $p\circ u = k$, $p'\circ u' = k'$ and there exists a pushout square
-\[\xymatrix{K' \ar[r]^{r'} \ar[d]_{u'}& R'\ar@{.>}[d]^{j'} \\ P \ar@{.>}[r]_{q'} & Q'}\]
-	\item  there exist arrows $i_1\colon R\to D'$, $i_2\colon L'\to D$ satisfying $f'\circ i_1=h$, $g\circ i_2=n'$ and such that the following squares are pushouts
-\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar@{.>}[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar@{.>}[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
-\end{enumerate}
-\end{definition}
-
-\begin{remark}\label{rem:deco} Let $\dder{D}$ and $\dder{D'}$ be two switchable direct derivations. Then the existence of a filler allows us to build the solid part of the diagram below.
-	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole  \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@{.>}@/_.8cm/[ddrr]_{j}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j'}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar@{.>}[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar@{.>}[ul]_{s} &&Q'\ar@{.>}[ur]^{t}}\]
-
-	Let us complete this diagram defining the dotted arrows. We can start noticing that, since $l\in \mathcal{M}$, there exists a pushout square 
-	\[\xymatrix{K \ar[r]^{l} \ar[d]_{u}& L\ar[d]^{j} \\ P \ar[r]_{q} & Q}\]
-	Moreover, the existence of the wanted $s\colon Q\to G$ and $t\colon Q'\to T$ follows from the following equalities
-	\[\begin{split}
-		f\circ p \circ u &= f\circ k \\&= n\circ l
-	\end{split} \qquad \begin{split}
-		g'\circ p'\circ u' &= g'\circ k'\\&=h'\circ r'
-	\end{split}\]
-
-	We can prove some other properties of the arrows appearing in the diagram above.
-The three rectangles below are pushouts and their left halves are pushouts too.
-Therefore, by \Cref{lem:po1}, also their right halves are pushouts.
-	\[\xymatrix{K \ar@/^.4cm/[rr]^{u}\ar[d]_{r}\ar[r]_{u} &P\ar[d]^{p'} \ar[r]_{p} & D \ar[d]^{g}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{l'}\ar[r]_{u'} &P\ar[d]^{p} \ar[r]_{p'} & D' \ar[d]^{f'}\\  R \ar@/_.4cm/[rr]_{h} \ar[r]^{i_1}&D' \ar[r]^{f'} & H&L' \ar@/_.4cm/[rr]_{n'} \ar[r]^{i_2}&D \ar[r]^{g} & H}\]
-	\[ \xymatrix{K \ar@/^.4cm/[rr]^{k}\ar[d]_{l}\ar[r]_{u} &P\ar[d]^{q} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{r'}\ar[r]_{u'} &P\ar[d]^{q'} \ar[r]_{p'} & D' \ar[d]^{g'}\\ L \ar@/_.4cm/[rr]_{n} \ar[r]^{j}&Q \ar[r]^{s} & G&R' \ar@/_.4cm/[rr]_{h'} \ar[r]^{j'}&Q' \ar[r]^{t} & T}\]
-
-	Notice, moreover, that $p, q$ are the pushouts of $l'$ and $l$, respectively, thus they  are elements of $\mathcal{M}$. By \Cref{prop:pbpoad} the squares
-	\[\xymatrix{P\ar[r]^{p} \ar[d]_{p'} & D \ar[d]^{g}& P \ar[r]^{p} \ar[d]_{q} &D\ar[d]^{f}\\ D' \ar[r]_{f'} & H & Q \ar[r]_{s}& G}\]
-	are pullbacks too.
-\end{remark}
-
-Notice that if there is a filler between  $\dder{D}$ and $\dder{D}'$ are switchable, then they are weakly sequentially independent: indeed, if a filler between them exists, then $(i_1, i_2)$ is an independence pair.
-On the other hand, \Cref{ex:difficile} shows that not every independence pair arises in this way.
-
-\begin{definition} Let  $\dder{D}\colon H\Mapsto H$, $\dder{D}'\colon H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system  $(\X, \R)$.
-An independence pair $(i_1, i_2)$ between $\dder{D}$ and $\dder{D}'$ is \emph{good} if there exists a filler $(u,u')$ between them such that  the squares below are pushouts.\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
-
-We will say that $\dder{D}$ and $\dder{D}'$ are \emph{switchable} if a good independence pair between them exists.
-If such a pair is unique, we will say that $\dder{D}$ and $\dder{D}'$ are \emph{uniquely switchable}.
-We will use the notation $\dder{D}\updownarrow \dder{D'}$ to mean that $\dder{D}$ and $\dder{D}'$ are switchable, while $\dder{D}\updownarrow_!
-\dder{D'}$ will denote that they are uniquely so.
-
-If every independence pair is good we will say that $(\X, \R)$ is \emph{tame}.
-\end{definition}
-
-\begin{remark}\label{rem:unic} Given a good independence pair $(i_1, i_2)$ between $\dder{D}$ and $\dder{D}'$, there is a unique filler  such that $(u,u')$ such that 
-	\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
-	are pushouts. Indeed, for every other filler $(v,v')$, it must be that
-	\[\begin{split}
-		p\circ u &=k \\&= p\circ v
-	\end{split}\qquad \begin{split}
-	p\circ u' &= i_2\circ l' \\&= p\circ v'
-	\end{split}\]
-	Since the arrow $p\colon P\to D$, which is the pullback of $f'$, is in $\mathcal{M}$ we conclude that $(u,u')=(v,v')$.
-\end{remark}
-
-\begin{remark}
-  Clearly in a tame left-linear DPO-rewriting system two direct derivations are sequentially independent if and only if they are unquely switchable.
-\end{remark}
-
-A source of tame left-linear DPO-rewriting systems is given by the linear ones, as shown by the following proposition.
-
-\begin{proposition}\label{prop:equi}Every linear DPO-rewriting system $(\X, \R)$ is tame.
- \end{proposition}
-\begin{proof} Suppose that $\X$ is $\mathcal{M}$-adhesive and let $(i_1, i_2)$ be an independence pair between $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$. We have a diagram
-	\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
-Pulling back $g$ along $f'$, we get another diagram 
-	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@{.>}@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@{.>}@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} && D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar[dl]^{h'}\\&G &&P\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T}\]
-Now, if we compute we get
-\[\begin{split}
-	f'\circ i_1\circ r &= h\circ r \\&= g\circ k
-\end{split}\qquad \begin{split}
-g\circ i_2\circ l' &= n'\circ l'\\&=f'\circ k'
-\end{split}\]
-Therefore the two dotted arrows $u\colon K\to P$ and $u'\colon K'\to P$ exist. We have to show that they satisfy the two conditions in the definition of a filler. 
-\begin{enumerate}
-	\item  By construction $p\circ u = k$ and $p'\circ u'=k'$. Since $(\X, \R)$ is linear, then $r'\colon K'\to R'$ belongs to $\mathcal{M}$, thus it admits a pushout along $u'\colon K'\to P$, as wanted.
-	\item Take the following two rectangles
-\[\xymatrix{K \ar@/^.4cm/[rr]^{u}\ar[d]_{r}\ar[r]_{u} &P\ar[d]^{p'} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{l'}\ar[r]_{u'} &P\ar[d]^{p} \ar[r]_{p'} & D' \ar[d]^{f'}\\  R \ar@/_.4cm/[rr]_{h} \ar[r]^{i_1}&D' \ar[r]^{f'} & H&L' \ar@/_.4cm/[rr]_{n'} \ar[r]^{i_2}&D \ar[r]^{g} & H}\]
-	By hypothesis $r$ and $l'$ are in $\mathcal{M}$, thus $f'$ and $g$ belong to it too. The first point of \Cref{lem:popb}  yields the thesis. \qedhere 
-\end{enumerate}
-\end{proof}
-
-\begin{remark} \cite{baldan2011adhesivity} identifies a large class of (quasi)adhesive categories with the property that every left linear DPO-rewriting system on them is tame.
-We adapt these results to our context in \Cref{app:fill}.
-\end{remark}
-\begin{definition}[Very tameneness]
-	\todo{very tame}
-\end{definition}
-
-\begin{remark}
-	\todo{tutto coincide con tutto}
-\end{remark}
-
-We are now going to justify the choice of the name for the relation $\updownarrow$, showing that two switchable direct derivations $\dder{D}$ and $\dder{D'}$ can be actually switched.
-
-Let $(i_1, i_2)$ be a good independence pair and consider the following diagram: the solid part exists by the definition of a filler, while the two new dotted arrows $v\colon Q\to J$ and $v'\colon Q'\to J$ are obtained  as the pushout of $q\colon P\to Q$, which is in $\mathcal{M}$ by \Cref{rem:deco}, along $q'\colon P\to Q'$.
-	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@/_.8cm/[ddrr]_{j}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j'}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar[ul]_{s}\ar@{.>}[dr]_{v} &&Q'\ar[ur]^{t} \ar@{.>}[dl]^{v'}\\&&&J}\]
-
-	Since, by \Cref{rem:deco}, all the curved rectangles are pushouts, as well as the bottom square, we can state the following definition.
-\begin{definition}\label{def:switch}
-	Let $(\X,R)$ be a left-linear DPO-rewriting system and suppose that $\X$ is $\mathcal{M}$-adhesive.
-Given a good independence pair $(i_1, i_2)$ between $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$, if $(u,u')$ is the associate filler, we define other two direct derivations $S_{i_1,i_2}(\dder{D}')\colon G\Mapsto J$ and $S_{i_1,i_2}(\dder{D})\colon J\Mapsto T$ as follows:
-		\[\xymatrix{L' \ar[d]_{f\circ i_2}& \ar[l]_{l'}K'\ar[d]_{q\circ u'} \ar[r]^{r'} & R' \ar[d]_{v'\circ j'} & L \ar[d]_{v\circ j} & \ar[l]_{l}K \ar[d]^{q'\circ u}\ar[r]^{r}& R \ar[d]^{g'\circ i_1}\\
-		G &\ar[l]^{s} Q \ar[r]_{v}& J&J & \ar[l]^{v'}Q' \ar[r]_{t} & T}\]
-	The \emph{switching} $\sder{D}{D'}$ of $\dder{D}$ and $\dder{D'}$ is the derivation $S_{i_1,i_2}(\dder{D}')\cdot S_{i_1,i_2}(\dder{D})$.
-\end{definition}
-
-\begin{remark}\label{rem:indip}Notice that $(j', j)$ is an independence pair for $S_{i_1,i_2}(\dder{D}')$ and $S_{i_1,i_2}(\dder{D})$.
-This is witnessed by the following diagram, commutative by construction.
-	\[\xymatrix@C=15pt{L' \ar[d]_{f\circ i_2}&& K' \ar[d]_{q\circ u'}\ar[ll]_{l'} \ar[r]^{r'} & R' \ar@/^.35cm/[drrr]_(.4){j'}|(.285)\hole \ar[dr]|(.28)\hole_{v'\circ j'} && L \ar@/_.35cm/[dlll]^(.4){j} \ar[dl]|(.28)\hole^{v\circ j}& K \ar[d]^{q'\circ u}\ar[l]_{l} \ar[rr]^{r} && R \ar[d]^{g'\circ i_1}\\G && \ar[ll]^{s} Q \ar[rr]_{v}&& J  && \ar[ll]^{v'} Q' \ar[rr]_{t}&& T}\]
-\end{remark}
-
-\begin{theorem}[Local Church-Rosser Theorem]\label{prop:fil}Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Then every filler between two direct derivations $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$ is a filler also for $S_{u,u'}(\dder{D'})\colon G\Mapsto J$ and $S_{u,u'}(\dder{D})\colon J\Mapsto H$.
-In particular, if $\dder{D}\updownarrow \dder{D}'$, then $S_{u,u'}(\dder{D}')\updownarrow S_{u,u'}(\dder{D})$.
-\end{theorem}
-\begin{proof}By definition of filler, we have two pushout square
-		\[\xymatrix{K \ar[r]^{l} \ar[d]_{u}& L \ar[d]^{j} & K' \ar[r]^{r'} \ar[d]_{u'} & R' \ar[d]^{j'}\\ P \ar[r]_q & Q & P \ar[r]_{q'} & Q'}\]
-		In particular, $q$ is an arrow of $\mathcal{M}$, therefore, by \Cref{prop:pbpoad}, the square below is a pullback.
-		\[\xymatrix{P \ar[r]^{q} \ar[d]_{q'}& Q\ar[d]^{v}\\ Q' \ar[r]_{v'} & J}\]
-		To prove our claim, it is now enough to show that $(u',u)$ is a filler between $S_{u,u'}(\dder{D}')$ and $S_{u, u'}(\dder{D})$.
-		\begin{enumerate}
-			\item As for the first  point of \Cref{def:filler}, the only non obvious part is the existence of a pushout of $u$ along $r$.
-But, since $(u,u')$ is a filler between $\dder{D}$ and $\dder{D'}$, we know that such a pushout exists: it is enough to take the square
-			\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} \\P \ar[r]_{p'}& D'}\]
-			\item For the second point, notice that the arrows $j$ and $j'$ fit in the squares
-	\[\xymatrix{K' \ar[r]^{r'} \ar[d]_{u'}& R' \ar[d]^{j'} &K \ar[r]^{l} \ar[d]_{u}& L\ar[d]^{j} \\P \ar[r]_{q}& Q& P \ar[r]_{q'} & Q'}\] 
-		\end{enumerate}
-
-By \Cref{rem:indip} we know that $(j,j')$ is an independence pair. The results above now implies that $(j,j')$ is good.
-\end{proof}
-
-The previous remark allow us to further switch the direct derivation $S_{i_1,i_2}(\dder{D})$ and $S_{i_2,i_2}(\dder{D}')$.
-The following lemma guarantees us that, in this way, we get back a derivation which is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
-
-\todo{introdurre decorazione}
-
-\begin{lemma}\label{lem:rev}
-	Let $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system $(\X, \R)$ and let $(i_1,i_2)$ be a good independence pair between them.
-Then $S_{j',j}(S_{i_1,i_2}(\dder{D}, \dder{D'}))$ is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
-\end{lemma}
-\begin{proof}Let $(u,u')$ be the filler associated to $(i_1, i_2)$.
-By \Cref{prop:fil}, $(u', u)$ is a filler between $S_{i_1,i_2}(\dder{D}')$ and $S_{i_1,i_2}(\dder{D})$.
-Thus we have a diagram as the one below.
-		\[\xymatrix{&&R' \ar@/_1cm/[ddrr]_(.35){j'}|(.7)\hole \ar[dr]^{v'\circ j'}&& L \ar@/^1cm/[ddll]^(.35){j}  \ar[dl]_{v\circ j}\\&K'\ar[dr]^{q\circ u'}\ar[dl]_{l'} \ar@/_.8cm/[ddrr]^(.65){u'}\ar[ur]^{r'}&& J && K \ar@/^.8cm/[ddll]_(.65){u}\ar[dl]_{q'\circ u}\ar[lu]_{l} \ar[dr]^{r}\\L' \ar[dr]^{f\circ i_2} \ar@/_.8cm/[ddrr]_{c_2}&& Q \ar[dl]|(.42)\hole_(.64){s}\ar[ur]|(.48)\hole^(.7){v}&&Q' \ar[dr]|(.42)\hole_(.65){t} \ar[ul]|(.48)\hole_(.7){v'}&&R\ar@/^.8cm/[ddll]^{c_1}\ar[dl]_{g'\circ i_1}\\&G &&P\ar[dr]^{e} \ar[dl]_{e'}\ar[ur]^(.4){q'}\ar[ul]_(.4){q}&&T\\&&E' \ar[ul]_{a}\ar[dr]_{w'} &&E\ar[ur]^{b} \ar[dl]^{w}\\&&&F}\]
-
-	Now, to ease the notation, let $S_{j',j}(S_{i_1,i_2}(\dder{D}, \dder{D'}))$ be $\dder{E}_0\cdot \dder{E}_1$, then $\dder{E}_0$ and $\dder{E}_1$ are the direct derivations given by the diagrams
-	\[\xymatrix{L \ar[d]_{s\circ j}& K\ar[l]_{l} \ar[r]^{r} \ar[d]_{e'\circ u} & R \ar[d]_{w\circ c_1} & L' \ar[d]^{w'\circ c_2}& K' \ar[d]^{e\circ u'} \ar[r]^{r'} \ar[l]_{l'}& R' \ar[d]^{t\circ j'}\\G & E' \ar[l]^{a}  \ar[r]_{w'}& F & F & E \ar[l]^{w} \ar[r]_{b} & R}\]
-
-	Notice, moreover, that, since the squares
-	\[\xymatrix{K' \ar[d]_{u'} \ar[r]^{l'}& L' \ar[d]^{c_2} & K \ar[r]^{r}\ar[d]_{u} & R \ar[d]^{c_1}\\ P \ar[r]_{e'} & E' & P\ar[r]_e & E}\]
-	are pushouts, we have isomorphisms  $\phi'\colon D\to E'$, $\phi\colon D'\to E$ making the following diagrams commutative.
-	\[\xymatrix{K' \ar[d]_{u'} \ar[r]^{l'}& L'\ar[d]^{i_2}  \ar@/^.2cm/[dr]^{c_2} & &K \ar[r]^{r}\ar[d]_{u} & R \ar[d]^{i_1} \ar@/^.2cm/[dr]^{c_1}\\ P \ar@/_.4cm/[rr]_{e'}\ar[r]^{p} & D\ar@{.>}[r]^{\phi'} &E'& P\ar@/_.4cm/[rr]_{e}\ar[r]^{p'} & D'\ar@{.>}[r]^{\phi}& E}\]
-	In particular, we have
-	\[\begin{split}
-		a\circ \phi' \circ i_2&=a \circ c_2\\&=f\circ i_2\\&
-	\end{split}\quad \begin{split}
-	a\circ \phi' \circ p'&=a \circ e'\\&=s\circ q\\&=f\circ p
-	\end{split}\quad \begin{split}
-	b\circ \phi \circ i_1&=b \circ c_1\\&=g'\circ i_1\\&
-	\end{split}\quad \begin{split}
-	b\circ \phi \circ p&=b \circ e\\&=t\circ q'\\&=g'\circ p'
-	\end{split} \]
-	and this shows that 
-	\[a\circ \phi'=f \qquad b\circ \phi = g'\]
-	Now, since $\phi'$ is an isomorphism and by \Cref{prop:pbpoad}, the two halves of the rectangle
-	\[\xymatrix{K\ar[r]^{\id{K}} \ar[d]_{(\phi')^{-1} \circ e' \circ u}&K\ar[d]_{e'\circ u} \ar[r]^{l} & L \ar[d]^{s\circ j} \\D\ar[r]_{\phi'} & E' \ar[r]_{a}&G}\]
-	are pullbacks.
-Thus the whole diagram is a pullback.
-But, by construction $s\circ j =n$ and we have already proved that $a\circ \phi'=f$.
-We then conclude that ther exists an isomorphism $\zeta\colon K\to K$ which makes the diagram below commutative
-	\[\xymatrix{K \ar@{.>}[r]_{\zeta}\ar@/^.4cm/[rr]^{l}  \ar@/_.5cm/[dr]_{(\phi')^{-1} \circ e' \circ u}& K \ar[r]_{l} \ar[d]_{n} & L \ar[d]^{n} \\ & D \ar[r]_{f} & G}\]
-	The commutativity of the upper triangle entails $l\circ \zeta=l$. Since $l$ is an element of $\mathcal{M}$  we can deduce that. $\zeta=\id{K}$. From this, we conclude that
-	\[e'\circ u = \phi' \circ k\]
-
-	As a next step, notice the existence of $\phi$ and $\phi'$, together with \Cref{rem:deco}, entails  the existence of a third isomorphism $\psi\colon H\to F$ fitting in the diagram below.
-	\[\xymatrix{P  \ar[d]^{p'}\ar@/_.4cm/[dd]_{e}\ar@/^.4cm/[rr]^{e'} \ar[r]_{p} & D \ar[d]^{g} \ar[r]_{\phi'} & E'\ar[d]^{w'}\\D' \ar[d]^{\phi} \ar[r]_{f'} & H\ar@{.>}[r]^{\psi} & F \\E \ar@/_.4cm/[urr]_{w}}\]
-Now, if we compute, we get
-\begin{align*}
-	\psi^{-1}\circ w\circ c_1&=f'\circ \phi^{-1}\circ c_1\\&=f'\circ i_1\\&=h
-\end{align*}
-	Summing up, we have just build the diagram below.	
-	\[\xymatrix@C=40pt@R=10pt{ &&&R\ar[dddr]^{w\circ c_1} \ar[dddl]_{h}|(.67)\hole\\&&K \ar[dl]_{l} \ar[ur]^{r}\ar[dddr]^{e'\circ u} \ar[dddl]_{k}|(.67)\hole\\&L\ar[dddr]^(.4){s\circ j} \ar[dddl]_(.4){n}\\&&H \ar[rr]^{\psi} && F\\ & D \ar[ur]_(.7){g} \ar[rr]^{\phi'} \ar[dl]_{f}&& E' \ar[ur]_{w'}\ar[dl]^{a}\\ G \ar[rr]_{\id{G}} && G}\]
-
-Next, we already know that
-\[t\circ j'= h' \quad w\circ \phi = \psi \circ f' \quad b\circ \phi = g'\]
-If we compute further, we also get
-\[\begin{split}
-	\psi^{-1}\circ w'\circ c_2 &= g\circ (\phi')^{-1}\circ c_2\\&=g\circ i_2\\&=n'
-\end{split}\qquad \begin{split}
-\phi^{-1}\circ e \circ u'&=p'\circ u'\\&= k'\\&
-\end{split}\]
-These equations allow us to conclude that the following diagram commutes.
-	\[\xymatrix@C=40pt@R=10pt{ &&&R'\ar[dddr]^{t\circ j'} \ar[dddl]_{h'}|(.67)\hole\\&&K' \ar[dl]_{l'} \ar[ur]^{r}\ar[dddr]^{e\circ u'} \ar[dddl]_{k}|(.67)\hole\\&L'\ar[dddr]^(.4){w'\circ c_2} \ar[dddl]_(.4){n'}\\&&T \ar[rr]^{\id{T}} && T\\ & D' \ar[ur]_(.7){g'} \ar[rr]^{\phi} \ar[dl]_{f'}&& E \ar[ur]_{b}\ar[dl]^{w}\\ H \ar[rr]_{\psi} && F}\]
-
-Putting together the two diagrams above we get the thesis. \qedhere 
-\end{proof}
-
-Our next step is to relate derivations which are equal ``up to switching''.
-
-\begin{definition} Let $(\X, \R)$ be a left-linear DPO-rewriting system.
-Given two direct derivations $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$, we say that  $\dder{D}$ and $\dder{D}'$ are \emph{properly switchable} if $\dder{D}\updownarrow_!
-\dder{D'}$ and $S_{i_1,i_2}(\dder{D}')\updownarrow_!S_{i_1,i_2}(\dder{D})$, where $(i_2,i_2)$ is a good independence pair betwwen $\dder{D}$ and $\dder{D}'$.
-In such a case, we will write $\dder{D}\Updownarrow\dder{D}'$.
-
-Take two derivations $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_{i}\}_{i=0}^n$ with the same length and between the same $G_0$ and $G_n$.
-We say that $\der{D}'$ is \emph{obtained by a proper switch from $\der{D}$} if there exists an index $j < n$ such that
-	\begin{enumerate}
-\item for every $i\notin \{j, j+1\} $, $\dder{D}_i=\dder{D}'_i$;
-\item $\dder{D}_j \Updownarrow \dder{D}_{j+1}$;		
-\item $\dder{D}'_j\cdot \dder{D}'_{j+1} = S_{i_1,i_2}(\dder{D}, \dder{D}')$.
-	\end{enumerate}
-	In such a case, we will write $\der{D}\rightsquigarrow_j \der{D}'$ to denote that $\der{D}'$ is obtained by a proper switch between $\dder{D}_j$ and $\dder{D}_{j+1}$.
-
-	We will say that $\der{D}$ is \emph{switch equivalent} to $\der{D}'$, if there exists a sequence, $\{\der{D}_i\}_{i=0}^n$ of derivations such that
-	\begin{enumerate}
-		\item $\der{D}_0=\der{D}$ and $\der{D}_n=\der{D}'$;
-		\item for every $i< n$, $\der{D}_{i+1}$ is obtained by a proper switch from $\der{D}_i$.
-	\end{enumerate}
-
-	We will write $\der{D} \equiv^s \der{D}'$ to denote that $\der{D}$ is switch equivalent to $\der{D}'$.
-\end{definition}
-
-\begin{example}
-	\todo{il punto due sopra è necessario}
-\end{example}
-
-We can now prove some properties of switch equivalence.
-\begin{lemma}\todo{Def. 3 della bozza di Andrea }Let $(\X, \R)$ be a left-linear DPO-rewriting system. Then the following hold true: 
-	\begin{enumerate}
-		\item 
-		\item 
-		\item 
-		\item 
-	\end{enumerate}
-\end{lemma}
-\begin{proof}\begin{enumerate}
-		\item 
-		\item 
-		\item 
-		\item \qedhere 
-	\end{enumerate}
-\end{proof}
-
-\begin{example}\todo{esempio sul perché weakly independence non è invertibile}
-\end{example}
-
-\begin{lemma}\label{lem:consperm} Let $(\X, \R)$ be a left-linear DPO-rewriting system $(\X, \R)$. Then the following hold true
-	\begin{enumerate}
-		\item If $\dder{D}$ and $\dder{D'}$ are two direct derivations such that $\dder{D}\updownarrow \dder{D'}$, then for every filler $(u,u')$ between them, the function
-		\[\tau\colon 2\to2 \qquad x \mapsto \begin{cases}
-			1 & x=0\\
-			0 & x=1
-		\end{cases}\]
-		defines a consistent permutation between $\dder{D}\cdot \dder{D}'$ and $\sder{D}{D'}$;
-		\item if $\der{D}$ and $\der{D}'$ are two switch equivalent derivation, then there exists a consistent permutation between them.
-	\end{enumerate}
-\end{lemma}
-\begin{proof}
-	\begin{enumerate}
-		\item 
-		\item \qedhere 
-	\end{enumerate}
-\end{proof}
- This, together with ???
-\begin{corollary}
-	\todo{unicità}
-\end{corollary}
-
-\begin{example}\label{ex:contro}\todo{permutazione consistente non implica scambiabilità}
-\end{example}
-
-\subsubsection{Graphical rewriting systems}\label{subsubsec:graphical}
-
-\todo{ci sono un sacco di sistemi very tame}
-\subsection{On the globality of $\Updownarrow$}
-\todo{intro}
-
-\begin{lemma}[Three steps Lemma]\label{lem:iig1}Let $(\X,\R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$ and suppose that $(i_0,i_1)$ is a good independence pair between $\dder{D}_0$ and $\dder{D}_1$, $(a_0,a_1)$ one between $\dder{D}_1$ and $\dder{D}_2$ and $(e_0, e_1)$ one between $\dder{D}_0$ and $S_{a_0,a_1}(\dder{D}_2)$.
-Then the following properties hold true.
-	\begin{enumerate}
-		\item $S_{e_0,e_1}(\dder{D}_0)$ and $S_{a_0,a_1}(\dder{D}_1)$ are weakly sequentially independent.
-		\item If $S_{i_0, i_1}(\dder{D}_0)\updownarrow_!
-\dder{D}_2$ with a good independence pair $(\alpha_0, \alpha_1)$, then  $S_{i_0,i_1}(\dder{D}_1)$ and $S_{\alpha_0, \alpha_1}(\dder{D}_2)$ are weakly sequentially independent.
-	\end{enumerate}
-
-\end{lemma}
-\begin{proof}  As a preliminary step, we are going to use \Cref{def:filler,def:switch} to get some diagrams.
-First of all, let $(v,v')$ be the filler between $\dder{D}_0$ and $\dder{D}_1$ associated to $(i_0, i_1)$, then we have
-	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&H'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
-
-	Secondly, the filler $(u,u')$ induced by $(a_0, a_1)$ between $\dder{D}_1$ and $\dder{D}_2$ yields:
-	\[
-	\xymatrix{&&R_1 \ar@/_1cm/[ddrr]_(.35){a_0}|(.7)\hole \ar[dr]^{h_1}&& L_2\ar@/^1cm/[ddll]^(.35){a_1}  \ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar[dl]_{l_1} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){u}\ar[ur]^{r_1}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){u'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_1 \ar@/_.8cm/[ddrr]_(.2){b_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_1}|(.61)\hole && D_1 \ar[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){b_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_2}\\&G_1 &&P_2\ar[dr]_{d_1} \ar[dl]^{d_0}\ar[ur]^(.4){c_1}\ar[ul]_(.4){c_0}&&G_3\\L_2 \ar@/^.8cm/[uurr]^(.2){a_1} \ar[ur]_(.35){f_1\circ a_1}|(.61)\hole&&Q_2 \ar[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1} &&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar[dl]|(.5)\hole_(.65){x_2} && R_1  \ar[ul]^(.35){g_2\circ a_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){a_0}\\&K_2 \ar[ur]_{d_0\circ u'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){u'}&&G'_2&& K_1 \ar[ur]_{r_1} \ar[ul]^{d_1\circ u} \ar[dl]^{l_1} \ar@/_.8cm/[uull]^(.65){u}\\&& R_2 \ar[ur]_{\hspace{-5pt}x_2\circ b_1}\ar@/^1cm/[uurr]^(.25){b_1}&& L_1 \ar[ul]^{y_1\circ b_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){b_0} |(.69)\hole }\]
-
-	Finally, the filler $(w,w')$  between $\dder{D}_0$ and $S_{a_0,a_1}(\dder{D}_2)$ given by $(e_0, e_1)$ provides us with:
-\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){e_0}|(.7)\hole \ar[dr]^{h_0}&& L_2\ar@/^1cm/[ddll]^(.35){e_1}  \ar[dl]_{f_1\circ a_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){w}\ar[ur]^{r_0}&& G_1 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){w'}\ar[dl]_{d_0\circ u'\hspace{-5pt}}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_0 \ar@/_.8cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2 \ar[dr]|(.4)\hole^(.65){y_1} \ar[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.8cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){x_2\circ b_1}\\&G_0 &&P_3\ar[dr]_{n_1} \ar[dl]^{n_0}\ar[ur]^(.4){u_1}\ar[ul]_(.4){u_0}&&G'_2\\L_2 \ar@/^.8cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ e_1}|(.61)\hole&&Q_4 \ar[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0} &&Q_5\ar[ur]|(.4)\hole^(.65){z'_1} \ar[dl]|(.5)\hole_(.65){z_1} && R_0  \ar[ul]^(.35){y_1\circ e_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){e_0}\\&K_2 \ar[ur]_{n_0\circ w'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){w'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{n_1\circ w} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){w}\\&& R_2 \ar[ur]_{\hspace{-4pt}z_1\circ o_1}\ar@/^1cm/[uurr]^(.25){o_1}&& L_0 \ar[ul]^{z'_0\circ o_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){o_0} |(.69)\hole }\]
-So equipped we can turn to the prove of our claims.	
-	\begin{enumerate}
-		\item We have to construct the two dotted arrows in the diagram below.
-			\[\xymatrix@C=15pt{L_0 \ar[d]_{z'_0\circ o_0}&& K_0 \ar[d]_{n_1\circ w}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@{.>}@/^.35cm/[drrr]_(.4){\beta_0}|(.285)\hole \ar[dr]|(.28)\hole_{y_1\circ e_0} && L_1 \ar@{.>}@/_.35cm/[dlll]^(.4){\beta_1} \ar[dl]|(.28)\hole^{y_1\circ b_0}& K_1 \ar[d]^{d_1\circ u}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ a_1}\\G'_1 && \ar[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2  && \ar[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_3}\]
-
-		Consider the arrows $i_0\colon R_0\to D_1$ and $e_0\colon R_0\to Q_2$. An easy computation shows that
-			\begin{align*}
-				f_1\circ i_0&= h_0\\&=x_1\circ e_0
-			\end{align*}
-			entailing the existence of  the dotted $\beta'_0\colon R_0\to P_2$ in the diagram
-			\[\xymatrix{R_0 \ar@{.>}[dr]^{\beta'_0} \ar@/^.3cm/[drr]^{i_0} \ar@/_.3cm/[ddr]_{e_0}\\ &P_2 \ar[r]^{c_1} \ar[d]_{d_0}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
-			If we define $\beta_0\colon R_0\to Q_3$ as $d_1\circ \beta'_1$, then we easily get that 
-		\begin{align*}
-			x_2\circ \beta_0&=x_2\circ d_2\circ \beta'_0\\&= y_1\circ d_0\circ \beta'_0\\&=y_1\circ e_0
-		\end{align*}
-
-		To define $\beta_1$, we proceed similarly. First consider  $i_1\colon L_1\to D_0$ and $b_0\colon L_1 \to Q_2$ and notice that
-		\begin{align*}
-			g_0\circ i_1&= m_1 \\&= x_1 \circ b_0
-		\end{align*}
-			implying the existence of $\beta'_1\colon L_1\to P_3$ fitting in the diagram below.
-			\[\xymatrix{L_1 \ar@{.>}[dr]^{\beta'_1} \ar@/^.3cm/[drr]^{i_1} \ar@/_.3cm/[ddr]_{b_0}\\ &P_3 \ar[r]^{u_0} \ar[d]_{u_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar[r]_{x_1} & G_1}\] 
-			Let $\beta_1\colon L_1\to Q_5$ be $n_1\circ \beta'_1$, then
-			\begin{align*}
-				z'_1 \circ \beta_1 & = z'_1 \circ n_1\circ \beta'_1\\&=y_1\circ u_1\circ \beta'_1\\&=y_1\circ b_0
-			\end{align*}
-		Therefore, $(\beta_0, \beta_1)$ is the wanted independence pair.
-
-\item  In addition to the three diagram above, we have a fourth one given by the filler $(\varphi_0, \varphi_1)$ associated to $(\alpha_0, \alpha_1)$. 
-\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){\alpha_0}|(.7)\hole \ar[dr]^{g_1\circ i_0}&& L_2\ar@/^1cm/[ddll]^(.35){\alpha_1}  \ar[dl]_{m_2}\\
-&K_0\ar[dr]^{\hspace{-4pt}q_1\circ v}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){\varphi}\ar[ur]^{r_0}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){\varphi'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\
-L_0 \ar@/_.8cm/[ddrr]_(.2){\gamma_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){\hspace{-4pt}t_0\circ j_0}|(.61)\hole && Q_1 \ar[dl]|(.4)\hole_(.65){s_1}\ar[ur]|(.5)\hole^(.7){t_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){\gamma_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){h_2}\\&H'_1 &&P_4\ar[dr]_{\lambda_1} \ar[dl]^{\lambda_0}\ar[ur]^(.4){\zeta_1}\ar[ul]_(.4){\zeta_0}&&G_3\\
-L_2 \ar@/^.8cm/[uurr]^(.2){\alpha_1} \ar[ur]_(.35){s_1\circ \alpha_1}|(.61)\hole&&Q_6 \ar[ul]|(.4)\hole_(.65){\xi_0}\ar[dr]|(.5)\hole^(.65){\xi'_0} &&Q_7\ar[ur]|(.4)\hole^(.65){\xi'_1} \ar[dl]|(.5)\hole_(.65){\xi_1} && R_0  \ar[ul]^(.35){g_2\circ \alpha_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){\alpha_0}\\&K_2 \ar[ur]_{\lambda_0\circ \phi'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){\phi'}&&H'_2&& K_0 \ar[ur]_{r_0} \ar[ul]^{\lambda_1\circ \phi} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){\phi}\\&& R_2 \ar[ur]_{\hspace{-4pt}\xi_1\circ \gamma_1}\ar@/^1cm/[uurr]^(.25){\gamma_1}&& L_0 \ar[ul]^{\xi'_0\circ \gamma_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){\gamma_0} |(.69)\hole }\]
-
-Our aim is to construct the dotted arrow in the following diagram.
-		\[\xymatrix@C=15pt{L_1 \ar[d]_{f_0\circ i_0}&& K_1 \ar[d]_{q_0\circ v'}\ar[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@{.>}@/^.35cm/[drrr]_(.4){\epsilon_0}|(.285)\hole \ar[dr]|(.28)\hole_{s_1\circ j_1} && L_2 \ar@{.>}@/_.35cm/[dlll]^(.4){\epsilon_1} \ar[dl]|(.28)\hole^{s_1\circ \alpha_1}& K_2 \ar[d]^{\lambda_0\circ \phi'}\ar[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]^{\xi_1\circ \gamma_1}\\G_0 && \ar[ll]^{s_0} Q_0 \ar[rr]_{t_0}&& H'_1  && \ar[ll]^{\xi_0} Q_6 \ar[rr]_{\xi'_0}&& H'_2}\]
-
-Let us start considering $j_1\colon R_1\to Q_1$ and $a_0\colon R_1\to D_2$. We have
-\begin{align*}
-	f_2\circ a_0&=h_1\\&=t_1\circ j_1
-\end{align*}
-and thus we get an arrow $\epsilon'_0\colon R_1\to P_4$ which makes the diagram below commutative.
-			\[\xymatrix{R_1 \ar@{.>}[dr]^{\epsilon'_0} \ar@/^.3cm/[drr]^{j_1} \ar@/_.3cm/[ddr]_{a_0}\\ &P_4 \ar[r]^{\zeta_0} \ar[d]_{\zeta_1}& Q_1 \ar[d]^{t_1}\\ &D_2\ar[r]_{f_2} & G_2}\] 
-We can then define $\epsilon_0\colon R_1\to Q_6$ to be $\lambda_0\circ \epsilon'_0$. For such an arrow we have a chain of identities:
-\begin{align*}
-	\xi_0\circ \epsilon_0&=\xi_0\circ \lambda_0\circ \epsilon'_0\\&=s_1\circ \zeta_0 \circ \epsilon'_0\\&=s_1\circ j_1
-\end{align*}
-
-Next, to define $\epsilon_1\colon L_2\to Q_0$ we take $e_1\colon L_2 \to D_0$ and $a_1\colon L_2\to D_1$. By definition we have $	g_0\circ e_1=f_1\circ a_1$, giving us the dotted arrow below
-	\[\xymatrix{L_2 \ar@{.>}[dr]^{\epsilon'_1} \ar@/^.3cm/[drr]^{a_1} \ar@/_.3cm/[ddr]_{e_0}\\ &P_1 \ar[r]^{p_1} \ar[d]_{p_0}& D_1 \ar[d]^{f_1}\\ &D_0\ar[r]_{g_0} & G_1}\] 
-Now, notice that 
-\begin{align*}
-	t_1\circ q_1\circ \epsilon'_1&=g_1\circ p_1\circ \epsilon'_1&=g_1\circ a_1\\&=m_2
-\end{align*}
-Hence $(\alpha_0, q_1\circ \epsilon'_1)$ is an independence pair for $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$.
-By hypothesis $S_{i_0, i_1}(\dder{D}_0)\updownarrow_!
-\dder{D}_2$ and thus $q_1\circ \epsilon'_1$ must coincide with $\alpha_1$.
-Now, let $\epsilon_1\colon L_2\to Q_0$ be $q_0\circ \epsilon'_1$.
-Computing we get
-\begin{align*}
-t_0\circ \epsilon_1&= t_0\circ q_0\circ \epsilon'_1\\&=s_1\circ q_1\circ \epsilon'_1\\&=s_1\circ \alpha_1
-\end{align*}
-Allowing us to conclude that  $S_{i_0,i_1}(\dder{D}_1)\updownarrow S_{\alpha_0, \alpha_1}(\dder{D}_2)$.
-\qedhere 
-			\end{enumerate}
-\end{proof}
-\iffalse 
-\begin{corollary} Given a tame  left-linear DPO-rewriting system  $(\X,\R)$ with $\X$ an $\mathcal{M}$-adhesive category and a decorated derivation $(\der{D}, \alpha, \omega)$ with $\der{D}=\{\dder{D}_i\}_{i=0}^2$.
-Then the following are true:
-	\begin{enumerate}
-		\item suppose that $(a_1,a_2)$ and $(e_0,e_1)$ are independence pairs witnessing  $\dder{D}_1\updownarrow_!
-\dder{D}_2$ and $\dder{D}_0\updownarrow_!
-S_{a_1,a_2}(\dder{D}_2)$ respectively, if $\dder{D}_0\updownarrow_!\dder{D}_1$, then $S_{e_0,e_1}(\dder{D}_0)\updownarrow_!S_{a_2,a_2}(\dder{D}_1)$;
-		\item 
-	\end{enumerate}
-\end{corollary}
-
-\todo{ripulire le ipotesi: serve scambiabilità propria tra 1 e 2}
-\todo{sistemare il fatto che qua utilizziamo derivazioni di 3 passi}
-\begin{proof}
-	\begin{enumerate}
-		\item Let $(i_1,i_2)$ be the unique independence pair between $\dder{D}_0$ and $\dder{D}_1$.
-By tameness and \Cref{lem:iig1} we know that $S_{e_0,e_1}(\dder{D}_0)\updownarrow S_{a_1,a_2}(\dder{D}_1)$.
-Let $(\alpha_1, \alpha_2)$ be the independence pair constructed in the proof of \Cref{lem:iig1}.
-Take another independence pair $(\beta_1, \beta_2)$,  by \Cref{rem:weak} we already know that $\beta_1=\alpha_1$.
-Let also $\der{E}$ be the derivation $S_{e_0, e_1}(S_{a_1, a_2}(\der{D}_2))\cdot S_{e_0, e_1}(\dder{D}_0) \cdot S_{a_1, a_2}(\der{D}_1)$.
-Let $\sigma\colon [0,2]\to [0,2]$ be the cycle $(0,1,2)$.
-By \Cref{lem:consperm} we know that $\sigma$ is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{E}, \alpha, \omega)$.
-In particular, we have
-		\begin{align*}
-			\iota_{\der{E}, G_0}\circ f_0\circ  i_1 &=\xi_\sigma \circ 	\iota_{\der{D}, G_0}\circ f_0\circ  i_1 \\&= \xi_\sigma \circ 	\iota_{\der{D}, D_0}\circ  i_1\\ &= \xi_\sigma \circ \iota_{\der{D}, G_1} \circ g_0\circ  i_1 \\&=\xi_\sigma \circ \iota_{\der{D}, G_1}\circ m_1\\ &=  \iota_{\der{E}, G'_2}\circ y_1\circ b_1\\&= \iota_{\der{E}, G'_2}\circ z'_1\circ \beta_2\\&= \iota_{\der{E}, Q_5}\circ \beta_2
-		\end{align*}
-		Using	\Cref{rem:pbsalva} we can deduce the existence of a unique arrow $\beta'_2\colon L_1\to P_3$ fitting in the diagram below
-		\[\xymatrix@C=30pt{L_1  \ar@/^.3cm/[drr]^{\beta_2} \ar@/_.3cm/[ddr]_{i_1}\ar@{.>}[dr]^{\beta'_2}\\& P_3 \ar[r]^{n_1}  \ar[d]_{u_0}& Q_5 \ar[d]^{\iota_{\dder{E}, Q_5}}\\
-		&D_0 \ar[r]_{\iota_{\dder{E}, G_0}}& \tpro{E}}\]
-		If we further compute, we get
-		\begin{align*}
-			y_1\circ u_1\circ \beta'_2&=z'_1\circ n_1\circ \beta'_2=\\&= z'_1\circ \beta_2 \\&=y_1\circ b_1
-		\end{align*}
-		Thus $(u_1\circ \beta'_2, b_2)$ is an independence pair between $S_{a_1, a_2}(\der{D}_2)$ and $S_{a_1, a_2}(\der{D}_1)$ therefore, by hypothesis $u_1\circ \beta'_2=b_1$.
-But this implies that $\beta'_2$ and $\alpha'_2$ are equal, giving us the thesis.
-
-\todo{ripulire le ipotesi: serve scambiabilità propria tra 1 e 2}
-\todo{sistemare il fatto che qua utilizziamo derivazioni di 3 passi}
-
-		\item \qedhere 
-	\end{enumerate}
-\end{proof}
-
- \todo{mettere esempio del perché fallisce nell'altra direziome}
- \todo{anche una breve intro}
-
-\begin{lemma}\label{lem:iig2}Let $(\X,\R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-For every derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$, if $(i_0,i_1)$ is a good independence pair between $\dder{D}_0$ and $\dder{D}_1$, $(a_1,a_2)$ one between $\dder{D}_1$ and $\dder{D}_2$ and $\dder{D}_0\updownarrow S_{a_1,a_2}(\dder{D}_2)$ with good independence pair $(e_0,e_1)$, then $S_{e_0,e_1}(\dder{D}_0)$ and $S_{a_1,a_2}(\dder{D}_1)$ are weakly sequentially independent.
-\end{lemma}
-\begin{proof} As in the proof of \Cref{lem:iig1}, \Cref{def:filler,def:switch} yield to us some diagrams.
-First of all, let $(v,v')$ be the filler between $\dder{D}_0$ and $\dder{D}_1$ associated to $(i_1, i_2)$, then we have
-	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
-
-	Secondly, the filler $(u,u')$ induced by $(a_1, a_2)$ between $\dder{D}_1$ and $\dder{D}_2$ yields:
-	\[
-	\xymatrix{&&R_1 \ar@/_1cm/[ddrr]_(.35){a_1}|(.7)\hole \ar[dr]^{h_1}&& L_2\ar@/^1cm/[ddll]^(.35){a_2}  \ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar[dl]_{l_1} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){u}\ar[ur]^{r_1}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){u'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_1 \ar@/_.8cm/[ddrr]_(.2){b_1}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_1}|(.61)\hole && D_1 \ar[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){b_2}|(.31)\hole|(.81)\hole\ar[dl]_{h_2}\\&G_1 &&P_2\ar[dr]_{d_2} \ar[dl]^{d_1}\ar[ur]^(.4){c_2}\ar[ul]_(.4){c_1}&&G_2\\L_2 \ar@/^.8cm/[uurr]^(.2){a_2} \ar[ur]_(.35){f_1\circ a_2}|(.61)\hole&&Q_2 \ar[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1} &&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar[dl]|(.5)\hole_(.65){x_2} && R_1  \ar[ul]^(.35){g_2\circ a_1}|(.61)\hole\ar@/_.8cm/[uull]_(.2){a_1}\\&K_2 \ar[ur]_{d_1\circ u'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){u'}&&G'_2&& K_1 \ar[ur]_{r_1} \ar[ul]^{d_2\circ u} \ar[dl]^{l_1} \ar@/_.8cm/[uull]^(.65){u}\\&& R_2 \ar[ur]_{\hspace{-5pt}x_2\circ b_2}\ar@/^1cm/[uurr]^(.25){b_2}&& L_1 \ar[ul]^{y_1\circ b_1\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){b_1} |(.69)\hole }\]
-
-	Finally, the filler $(w,w')$  between $\dder{D}_0$ and $S_{u,u'}(\dder{D}_2)$ given by $(e_0, e_1)$ provides us with:
-	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){e_0}|(.7)\hole \ar[dr]^{h_0}&& L_2\ar@/^1cm/[ddll]^(.35){e_1}  \ar[dl]_{f_1\circ a_2}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){w}\ar[ur]^{r_0}&& G_1 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){w'}\ar[dl]_{d_1\circ u'\hspace{-5pt}}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_0 \ar@/_.8cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2 \ar[dr]|(.4)\hole^(.65){y_1} \ar[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.8cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){x_2\circ b_2}\\&G_0 &&P_3\ar[dr]_{n_1} \ar[dl]^{n_0}\ar[ur]^(.4){u_1}\ar[ul]_(.4){u_0}&&G'_2\\L_2 \ar@/^.8cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ e_1}|(.61)\hole&&Q_4 \ar[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0} &&Q_5\ar[ur]|(.4)\hole^(.65){z'_1} \ar[dl]|(.5)\hole_(.65){z_1} && R_0  \ar[ul]^(.35){y_1\circ e_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){e_0}\\&K_2 \ar[ur]_{n_0\circ w'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){w'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{n_1\circ w} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){w}\\&& R_2 \ar[ur]_{\hspace{-4pt}z_1\circ o_1}\ar@/^1cm/[uurr]^(.25){o_1}&& L_0 \ar[ul]^{z'_0\circ o_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){o_0} |(.69)\hole }\]
-
-	We have to construct the two dotted arrows in the diagram below.
-	\[\xymatrix@C=15pt{L_0 \ar[d]_{z'_0\circ o_0}&& K_0 \ar[d]_{n_1\circ w}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@{.>}@/^.35cm/[drrr]_(.4){\alpha_1}|(.285)\hole \ar[dr]|(.28)\hole_{y_1\circ e_0} && L_1 \ar@{.>}@/_.35cm/[dlll]^(.4){\alpha_2} \ar[dl]|(.28)\hole^{y_1\circ b_1}& K_1 \ar[d]^{d_2\circ u}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ a_1}\\G'_1 && \ar[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2  && \ar[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_2}\]
-
-	Consider the arrows $i_0\colon R_0\to D_1$ and $e_0\colon R_0\to Q_2$. An easy computation shows that
-	\begin{align*}
-		f_1\circ i_0&= h_0\\&=x_1\circ e_0
-	\end{align*}
-	entailing the existence of  the dotted $\alpha'_1\colon R_0\to P_2$ in the diagram
-	\[\xymatrix{R_0 \ar@{.>}[dr]^{\alpha'_1} \ar@/^.3cm/[drr]^{i_0} \ar@/_.3cm/[ddr]_{e_0}\\ &P_2 \ar[r]^{c_2} \ar[d]_{d_1}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
-	If we define $\alpha_1\colon R_0\to Q_3$ as $d_2\circ \alpha'_1$, then we easily get that 
-	\begin{align*}
-		x_2\circ \alpha_1&=x_2\circ d_2\circ \alpha'_1\\&= y_1\circ d_1\circ \alpha'_1\\&=y_1\circ e_0
-	\end{align*}
-
-	For $\alpha_2$, we proceed similarly. First consider  $i_1\colon L_1\to D_0$ and $b_1\colon L_1 \to Q_2$ and notice that
-	\begin{align*}
-		g_0\circ i_1&= m_1 \\&= x_1 \circ b_1
-	\end{align*}
-	implying the existence of $\alpha'_2\colon L_1\to P_3$ fitting in the diagram below.
-	\[\xymatrix{L_1 \ar@{.>}[dr]^{\alpha'_2} \ar@/^.3cm/[drr]^{i_1} \ar@/_.3cm/[ddr]_{b_1}\\ &P_3 \ar[r]^{u_0} \ar[d]_{u_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar[r]_{x_1} & G_1}\] 
-	Let $\alpha_2\colon L_1\to Q_5$ be $n_1\circ \alpha'_2$, then
-	\begin{align*}
-		z'_1 \circ \alpha_2 & = z'_1 \circ n_1\circ \alpha'_2\\&=y_1\circ u_1\circ \alpha'_2\\&=y_1\circ b_1
-	\end{align*}
-	The thesis now follows.  
-\end{proof}
-\fi
-
-\subsection{Concatenable traces}
 \begin{lemma}
-	\todo{abstract equivalence and switch }
+	da pb a ind pair
 \end{lemma}
@@
 \end{proof}
-\begin{definition}
-	\todo{tracce}
-\end{definition}
-
-Before moving forward, we will prove some other useful properties of the switch equivalence relation.
-
-\begin{lemma}
-	\todo{lemma 19}
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{theorem}
-	\todo{preordine}
-\end{theorem}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\section{ Domains for DPO-rewriting}
-
-\subsection{weak domains}
-
-\subsection{From adhesive grammars to weak domains}
+
+\begin{corollary}
+	caratterizzazione
+\end{corollary}
 
@@
 
-\section{A note on fillers and sequential independence}\label{app:fill}
- In \Cref{prop:equi} we proved that, in the linear case, the existence of an indpendence pair between two derivation is equivalent to that of a filler between them.
-This result can be further refined: in a\cite{baldan2011adhesivity} a class  $\mathbb{B}$ of (quasi)adhesive category is defined for which the local Church-Rosser Theorem holds even for left-linear DPO-rewriting system.
-In our language, and given \Cref{prop:fil} and \Cref{rem:locCR}, this amount to prove that, for elements of $\mathbb{B}$, every independence pair induces a filler.
-
-\begin{definition}Let $\X$ be a category, we say that $\X$ satisfies
-	\begin{itemize}
-		\item the \emph{mixed decomposition} property if for every diagram
-		\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
-		whose outer boundary is a pushout and in which $k$ is a monomorphisms, 
-		\item the \emph{pushout decomposition} property
-	\end{itemize}
-\end{definition}
-
-\begin{lemma}
-	contenuto...
-\end{lemma}
-\begin{proof}
-	contenuto...\qedhere 
-\end{proof}
-
-\begin{corollary}
-	contenuto...
-\end{corollary}
-
-The following result shows that the mixed and pushout decomposition properties guarantee that every independence pair gives rise to a filler.
-
-\begin{theorem}
-	\todo{filler e classe B+}
-\end{theorem}
-\begin{proof}\qedhere 
-\end{proof}
-
-Our next step is to identify sufficient conditions for a category $\X$ to satisfy the mixed and pushout decomposition properties.
-
-\begin{definition}
-	\todo{classe B e class B+}
-\end{definition}
-
-\begin{example}
-\todo{esempi}
-\end{example}
-
-\begin{example}
-	\todo{esempi}
-\end{example}
-
-\begin{proposition}
-	\todo{da B a B+}
-\end{proposition}
-\begin{proof}
-	contenuto... \qedhere 
-\end{proof}
-\begin{lemma}\todo{due proprietà classe B}
-\end{lemma}
-\begin{proof}
-	\qedhere 
-\end{proof}
-
-\begin{corollary}
-	\todo{due proprietà classe B+}
-\end{corollary}
-
-\begin{corollary}
-	\todo{filler e classe B+}
-\end{corollary}
+\include{factorization.tex}
+
+\include{adhesivity.tex}
 
@@
 \todo{inserire risutati sulle permutazione che abbiamo usato}
+
+\begin{definition}
+	\todo{inversioni}
+\end{definition}
 

### 2024-11-14 full_version/introduzione.tex
nuovo

--- 2024-11-14 full_version/fusione.tex
@@
-\documentclass[a4paper]{report}
-\usepackage{hyperref}
-\usepackage[textsize=tiny]{todonotes}
-%\usepackage{etex}
-\usepackage[all]{xy}
-\SelectTips{cm}{}
-% derivations and labels
-\usepackage{proof}
-\newcommand{\lab}[1]{\ensuremath{\mathsf{{#1}}}}
-\newcommand{\slab}[1]{\ensuremath{\scriptstyle{\mathsf{{#1}}}}}
-
-\newcommand{\sub}[3]{{\mathcal{#1}}\textrm{-}\mathsf{Sub}_{\textbf {\textup{#2}}}(#3)}
-
-\newcommand{\msub}[2]{\mathsf{Sub}_{\textbf {\textup{#1}}}(#2)}
-
-%frecce
-\newcommand{\mor}{\mathsf{Mor}}
-\newcommand{\mon}{\mathsf{Mono}}
-\newcommand{\reg}{\mathsf{Reg}}
-
-% ``boxed'' \infer command
-\newcommand{\binfer}[3][]{
-  \mbox{\infer[#1]{#2}{#3}}}
-
-% Command for labels on the left side of the rule
-%       \inferL{<name>}{<post>}{<pre>}
-% generates:
-%             <pre>
-%      <name> ------
-%             <post>
-%
-\newlength{\myheight}
-\newcommand{\inferL}[3]
-  {\settoheight{\myheight}{\mbox{${#2}$}}
-   \raisebox{\myheight}{{#1}}
-   \makebox[1mm]{}
-   \mbox{\infer{#2}{#3}}
-}
-
-\usepackage{amssymb,graphicx,epsfig,color}
-%\usepackage[scriptsize]{subfigure}
-\usepackage{subcaption}
-\usepackage{wrapfig}
-
-% re-stating 
-%\usepackage{thm-restate}
-
-% showing labels
-%\usepackage[inline]{showlabels}
-
-\usepackage{pgf}
-\usepackage{tikz}
-\usepackage{tikz-cd}
-\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri,fit,positioning}
-\tikzstyle{node}=[circle, draw=black, minimum size=1mm]
-\tikzstyle{trans}=[font=\scriptsize]
-\tikzstyle{lab}=[font=\small]
-
-\newcommand{\pgfBox}{
-  \begin{pgfonlayer}{background} 
-    \fill[blue!2,thick,draw=black!50,rounded corners,inner sep=3mm] ([xshift=-1.5pt,yshift=-1.5pt]current bounding box.south west) rectangle ([xshift=1.5pt,yshift=1.5pt]current bounding box.north east);
-  \end{pgfonlayer}
-}
-\usepackage{scalerel}
-\newcommand{\smallmin}{\scaleobj{0.6}{-}}
-\newcommand{\Deltamin}{\Delta^{\hspace{-1pt}\downarrow\hspace{-1pt}}}
-\newcommand{\Rrel}[1]   {\stackrel{{#1}}{\Longrightarrow}}
-\newcommand{\oa}{\overline a}
-\newcommand{\ob}{\overline b}
-\newcommand{\oc}{\overline c}
-\newcommand{\od}{\overline d}
-\newcommand{\rec}{\emph{rec}}
-\newcommand{\fn}[1]{{\mathtt{fn}}(#1)}
-%\usepackage{latexsym}
-\usepackage{stmaryrd}
-\def\encodep#1{\llfloor#1\rrfloor}
-
-\newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}
-
-\newcommand{\dpo}{\textsc{dpo}}
-
-% base classes of categories for adhesive and quasi adhesive case
-\newcommand{\bAdh}{\ensuremath{\mathbb{B}}}
-\newcommand{\bQAdh}{\ensuremath{\mathbb{QB}}}
-
-%from pawel
-\usepackage[latin1]{inputenc}
-\usepackage{amsmath}
-
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{enumerate}
-\usepackage{xspace}
-\usepackage{amsfonts}
-\usepackage{mathrsfs}
-\usepackage{cite}
-\usepackage{float}
-\usepackage{fancybox}
-
-\usepackage{cleveref}
-
-%\spnewtheorem*{notation}{Notation}{\bfseries}{\rmfamily}
-
-%%%%%%%% MATHEMATICAL NOTATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%symbol for natural numbers
-\newcommand{\nat}{\ensuremath{\mathbb{N}}}
-
-% finite subset
-\newcommand{\sfin}{\ensuremath{\subseteq_{\mathit{fin}}}}
-
-% flattening of a multiset
-\newcommand{\flt}[1]{\ensuremath{[\![{#1}]\!]}}
-
-% compact elements
-\newcommand{\compact}[1]{\ensuremath{\mathop{\mathsf{K}({#1})}}}
-
-% principal ideal
-\newcommand{\principal}[1]{\ensuremath{\mathop{\downarrow\!{#1}}}}
-
-% ideal completion
-\newcommand{\ideal}[1]{\ensuremath{\mathsf{Idl}({#1})}}
-
-% complete prime elements
-\newcommand{\pr}[1]{\ensuremath{\mathop{\mathit{pr}({#1})}}}
-\newcommand{\wpr}[1]{\ensuremath{\mathop{\mathit{wpr}({#1})}}}
-
-% irreducible elements
-\newcommand{\ir}[1]{\ensuremath{\mathop{\mathit{ir}({#1})}}}
-
-% difference of irreducible elements
-\newcommand{\diff}[2]{\ensuremath{\delta({#1},{#2})}}
-
-% immediate precedence
-
-% abbreviation for event structure
-% \newcommand{\esabbr}{event structure}
-\newcommand{\esabbr}{\textsc{es}}
-\newcommand{\esnabbr}{\textsc{esnb}}
-\newcommand{\esnmabbr}{\textsc{esn}}
-\newcommand{\eseqabbr}{\textsc{epes}}
-
-% predecessor of an irreducible
-\newcommand{\pred}[1]{\ensuremath{\mathit{p}({#1})}}
-
-% irreducible elements in es domains
-\newcommand{\esir}[2]{\ensuremath{\langle{#1}, {#2}\rangle}}
-
-% equivalence classes [of irreducibles]
-\newcommand{\eqclass}[2][]{\ensuremath{[{#2}]_{\scriptscriptstyle {#1}}}}
-% union of the equivalence classes of the elements in a set
-\newcommand{\eqclasscup}[2]{\ensuremath{{#2}_{\scriptscriptstyle {#1}}}}
-
-\newcommand{\eqclassir}[1]{\ensuremath{\eqclass[\leftrightarrow^*]{#1}}}
-
-% quotient of set wrt a relation
-\newcommand{\quotient}[2]{\ensuremath{{#1}_{\scriptscriptstyle {#2}}}}
-
-% category of event structures 
-\newcommand{\es}{\ensuremath{\mathsf{ES}}}
-% category of stable event structures 
-\newcommand{\ses}{\ensuremath{\mathsf{sES}}}
-% category of prime event structures 
-\newcommand{\pes}{\ensuremath{\mathsf{pES}}}
-% category of prime event structures with equivalence
-\newcommand{\epes}{\ensuremath{\mathsf{epES}}}
-
-% category of connected event structures 
-\newcommand{\ces}{\ensuremath{\mathsf{cES}}}
-
-% category of weak prime algebraic domains domains 
-\newcommand{\WDom}{\ensuremath{\mathsf{wDom}}}
-% category of domains
-\newcommand{\Dom}{\ensuremath{\mathsf{Dom}}}
-% category of prime algebraic domains
-\newcommand{\PDom}{\ensuremath{\mathsf{pDom}}}
-
-%%%%% NON BINARY CONFLICT
-
-% category of event structures 
-\newcommand{\esn}{\ensuremath{\mathsf{ES_{nb}}}}
-% category of stable event structures 
-\newcommand{\sesn}{\ensuremath{\mathsf{sES_n}}}
-
-% category of connected event structures 
-\newcommand{\cesn}{\ensuremath{\mathsf{cES_{nb}}}}
-
-% category of prime event structures 
-\newcommand{\pesn}{\ensuremath{\mathsf{pES_n}}}
-
-% category of fusion domains 
-\newcommand{\WDomb}{\ensuremath{\mathsf{wDom_b}}}
-% category of domains
-\newcommand{\Domb}{\ensuremath{\mathsf{Dom_b}}}
-% category of prime algebraic domains
-\newcommand{\PDomb}{\ensuremath{\mathsf{pDom_b}}}
-
-%%%%% END NON BINARY CONFLICT
-
-% slice category
-\newcommand{\slice}[2]{\ensuremath{({#1} \downarrow {#2})}}
-
-% event structure for a domain
-\newcommand{\zev}[0]{\ensuremath{\mathcal{E}}}
-\newcommand{\ev}[1]{\ensuremath{\zev({#1})}}
-
-% from general to connected event structures
-\newcommand{\zconnes}[0]{\ensuremath{\mathcal{C}}}
-\newcommand{\connes}[1]{\ensuremath{\zconnes({#1})}}
-% and inclusion
-\newcommand{\zinces}[0]{\ensuremath{\mathcal{I}}}
-\newcommand{\inces}[1]{\ensuremath{\zinces({#1})}}
-
-% stable version
-\newcommand{\zsev}[0]{\ensuremath{\mathcal{E}_S}}
-\newcommand{\sev}[1]{\ensuremath{\zsev({#1})}}
-
-% with equivalence
-\newcommand{\zeveq}[0]{\ensuremath{\mathcal{E}_{eq}}}
-\newcommand{\eveq}[1]{\ensuremath{\zeveq({#1})}}
-
-% es with equivalence to es and vice
-\newcommand{\zfuse}[0]{\ensuremath{\mathcal{M}}}
-\newcommand{\fuse}[1]{\ensuremath{\zfuse({#1})}}
-\newcommand{\zunf}[0]{\ensuremath{\zunf}}
-\newcommand{\unf}[1]{\ensuremath{\mathcal{U}({#1})}}
-
-% Winskel/Droste version
-\newcommand{\zevwd}[0]{\ensuremath{\mathcal{E}_{wd}}}
-\newcommand{\evwd}[1]{\ensuremath{\zevwd({#1})}}
-
-% configurations of an event structure
-\newcommand{\conf}[1]{\ensuremath{\mathit{Conf}({#1})}}
-% finite configurations
-\newcommand{\conff}[1]{\ensuremath{\mathit{Conf_F}({#1})}}
-
-% product of the sets of minimal enablinsg
-\newcommand{\pmin}[1]{\ensuremath{U_{#1}}}
-
-% connectectedness of minimal enablinsg
-\newcommand{\conn}[1]{\ensuremath{\stackrel{#1}{\frown}}}
-
-% domain for an event structure or graph grammar
-\newcommand{\zdom}[0]{\ensuremath{\mathcal{D}}}
-\newcommand{\dom}[1]{\ensuremath{\zdom({#1})}}
-
-\newcommand{\zdomeq}[0]{\ensuremath{\mathcal{D}_{eq}}}
-\newcommand{\domeq}[1]{\ensuremath{\zdomeq({#1})}}
-
-% partial order for a graph grammar
-\newcommand{\poset}[1]{\ensuremath{\mathcal{P}({#1})}}
-
-% stable version
-\newcommand{\pdom}[1]{\ensuremath{\mathcal{D}_S({#1})}}
-\newcommand{\ppdom}[0]{\ensuremath{\mathcal{D}_S}}
-
-% powerset
-\newcommand{\Pow}[1]{\ensuremath{\mathbf{2}^{#1}}}
-
-% powerset of finite subsets
-\newcommand{\Powfin}[1]{\ensuremath{\mathbf{2}_\mathit{fin}^{#1}}}
-
-% powerset of subsets of cardinality <= 1
-\newcommand{\Powone}[1]{\ensuremath{\mathbf{2}_1^{#1}}}
-
-% integer interval
-\newcommand{\interval}[2][1]{\ensuremath{[{#1},{#2}]}}
-
-% domain interval
-\newcommand{\dint}[2]{\ensuremath{[{#1},{#2}]}}
-
-% set of intervals
-\newcommand{\IntSet}[1]{\ensuremath{\mathop{\mathit{Int}({#1})}}}
-
-% intervals to irreducibles and vice
-\newcommand{\inir}{\ensuremath{\mathop{\mathit{\zeta}}}}
-\newcommand{\irin}{\ensuremath{\mathop{\mathit{\iota}}}}
-
-% permutations
-\newcommand{\perm}{\sigma}
-
-% causes
-\newcommand{\causes}[1]{\ensuremath{\lfloor {#1})}}
-
-%%% GRAPH GRAMMARS
-
-\newcommand{\Abs}[1]{\ensuremath{\mathsf{Abs}({#1})}}
-\newcommand{\tr}[1]{\ensuremath{\mathsf{Tr}({#1})}}
-% fusion safe traces
-\newcommand{\trs}[1]{\ensuremath{\mathsf{Tr}_s({#1})}}
-%\newcommand{\graph}{\ensuremath{\mathsf{Graph}}}
-\newcommand{\tgraph}[1]{\ensuremath{\mathsf{Graph}_{#1}}}
-\newcommand{\can}[1]{\ensuremath{\mathsf{C}({#1})}}
-% source and target of a derivation
-\newcommand{\source}[1]{\ensuremath{\mathsf{s}({#1})}}
-\newcommand{\target}[1]{\ensuremath{\mathsf{t}({#1})}}
-\newcommand{\col}[1]{\ensuremath{\mathsf{col}({#1})}}
-
-% left decorated trace
-\newcommand{\ltrace}[1]{\ensuremath{\langle {#1}\rangle_c}}
-
-\newcommand{\bx}[1]{\phantom{\big(}#1{\phantom{\big)}}}
-\newcommand{\bxx}[1]{\,#1\,}
-\newcommand{\cycl}[1]{\ensuremath{\mbox{\textcircled{\scriptsize{$#1$}}}}}
-\renewcommand{\iff}{\ensuremath{\Leftrightarrow}}
-
-%%%%GENERAL CATEGORICAL NOTATION
-
-%identità
-\newcommand{\id}[1]{\mathsf{id}_{#1}}
-%codominio
-\newcommand{\cod}[1]{\mathsf{cod}({#1})}
-	%Variabili categorie
-\def\A{\textbf {\textup{A}}}
-%mono
-\newcommand{\mto}[0]{\scalebox{1}{$\rightarrowtail$}}
-
-\newcommand{\sk}{\mathsf{sk}_{\X}}
-
-\def\R{\mathsf{R}}
-\def\B{\textbf {\textup{B}}}
-\def\C{\textbf {\textup{C}}}
-\def\D{\textbf {\textup{D}}}
-\def\X{\textbf {\textup{X}}}
-\def\Y{\textbf {\textup{Y}}}
-\def\E{\textbf {\textup{E}}}
-
-\newcommand{\ske}{\mathsf{sk}(\X)}
-\renewcommand{\P}{\textbf {\textup{P}}}
-
-%\derivazioni
-
-\newcommand{\dder}[1]{\mathscr{#1}}
-\newcommand{\sder}[2]{S_{i_1,i_2}(\mathscr{#1}, \mathscr{#2})}
-\newcommand{\der}[1]{\underline{\dder{#1}}}
-\def\dpo{\mathsf{C}^{\X}_R}
-\def\gpo{\mathsf{G}^{\X}_R}
-\def\dpi{[\mathsf{C}]^{\X}_R}
-\def\gpi{[\mathsf{G}]^{\X}_R}
-
-\newcommand{\ider}[1]{\mathscr{I}_{#1}}
-
-%categorie
-\def\Set{\textbf {\textup{Set}}}
-
-%comma
-\newcommand{\comma}[2]{#1\hspace{1pt} {\downarrow}\hspace{1pt} #2}
-\newcommand{\cma}[2]{\mathcal{#1}\hspace{1pt} {\downarrow}\hspace{1pt} \mathcal{#2}}
-
-%derivazioni
-\newcommand{\lpro}{\langle \hspace{-1.85pt}[}
-\newcommand{\rpro}{]\hspace{-1.85pt}\rangle}
-\newcommand{\tpro}[1]{\lpro \der{#1}\rpro}
-\newcommand{\tproi}[2]{\lpro \der{#1}_{#2}\rpro}
-\newcommand{\lgh}[0]{\mathsf{lg}}
-
-%%% NEW
-
-\usepackage{xparse}
-
-% inversions
-\newcommand{\inv}[1]{\ensuremath{inv}({#1})}
-
-% direct shift
-\newcommand{\shiftdir}[1][]{\ensuremath{\mathrel{{\rightsquigarrow}^{\mathit{sh}}_{#1}}}}
-
-% shift preorder
-\newcommand{\shiftpre}[1][]{\ensuremath{\mathrel{{\sqsubseteq}^{\mathit{sh}}_{#1}}}}
-
-% shift equivalence
-\newcommand{\shifteq}[1][]{\ensuremath{\mathrel{{\equiv}^\mathit{sh}_{#1}}}}
-
-% transp{source}[target]: if target not specified source+1
-\NewDocumentCommand{\transp}{m o}{%
-  \ensuremath{({#1},%
-  \IfNoValueTF{#2}%
-    {{#1}+1}%
-    {#2}%
-    )}
-}
-
-\NewDocumentCommand{\mycommand}{o}{%
-  % <code>
-  \IfNoValueTF{#1}
-    {code when no optional argument is passed}
-    {code when the optional argument #1 is present}%
-  % <code>
-}
-% interchange
-\newcommand{\IC}[1]{\ensuremath{\mathit{IC}({#1})}}
-
-%%%%% Ambienti matematici  %%%%%%
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem*{notation}{Notation}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{example}[theorem]{Example}
-
-\title{Switch equivalence and weak prime domains for fusions}
-\author{Paolo Baldan\and Davide Castelnovo\and  Andrea Corradini\and Fabio Gadducci}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-\todo{	A VERY NICE ABSTRACT}
-\end{abstract}
-
-\tableofcontents
+\chapter{Introduction}
 
@@
 \end{itemize}
-
-\section{Introduction}
 
@@
 rewriting over a large class of adhesive categories.
-
-\include{permutations.tex}
-
-\include{domains.tex}
-
-\todo{integrare sopra}
-\newpage
-QUOZIENTI VARI
-
-The setting from now on is: $\X$ $\mathcal{M}$-adhesive, $(\mathcal{E}, \mathcal{M})$ a proper (maybe also stable) factorization system. $\X$ has all pushouts.
-
-\begin{lemma}\label{lem:pushandpullpb}
-	Let $\X$ be a category and suppose that the diagram below is given.
-	\[\xymatrix{ P \ar[r]^{p_0} \ar[d]_{p_1}& A  \ar@/^.2cm/[ddr]^{k_0}\ar[d]^{f}\\  B  \ar@/_.2cm/[drr]_{k_1} \ar[r]_g & C \ar[dr]^{h}\\&& D }\]
-	Then the following hold true:
-	\begin{enumerate}
-		\item if the outer boundary is a pullback, then the inner square is a pullback too;
-		\item if the inner square is a pullback and $h$ is mono then also the outer square is a pullback.
-	\end{enumerate}
-\end{lemma}
-\begin{proof}\begin{enumerate}
-		\item Let $e_0\colon E\to A$ and $e_1\colon E\to B$ be a pair of arrows such that 
-		\[f\circ e_0=g\circ e_1\]
-		Then we also have 
-		\begin{align*}
-		k_0\circ e_0 &= h\circ f\circ e_0\\&=h\circ g \circ e_1\\&=k_1\circ e_1
-		\end{align*}
-		Thus there exists a unique arrow $e\colon E\to P$ such that
-		\[p_0\circ e= e_0 \qquad p_1\circ e=e_1\]
-		which entails our claim.
-		\item We proceed as before considering two arrows $e_0\colon E\to A$ and $e_1\colon E\to B$, but in this case we suppose that 
-		\[k_0\circ e_0=k_1\circ e_1\]
-		In particular, we have
-		\begin{align*}
-			h\circ f \circ e_0 &= k_0\circ e_0\\&=k_1\circ e_1\\&=h\circ g\circ e_1
-		\end{align*}
-		Thus, since $h$ is mono, we can deduce that $f\circ e_0$ and $g\circ e_1$ are equal and the thesis now follows immediately.
-		\qedhere 
-	\end{enumerate}
-	\end{proof}
-
-	\begin{lemma}\label{lem:cond} Let $f\colon A\to C$, $g\colon B\to C$ and $h\colon C\to D$ be arrows in a category $\X$, let also $l_0\colon A'\to A$, $l_1\colon B'\to B$ be two monomorphisms.
-Suppose moreover, that the following squares are pullbacks:
-		\[\xymatrix@C=35pt{Q \ar[r]^{q_0} \ar[d]_{q_1} & A' \ar[d]^{h\circ f\circ l_0} & P \ar[r]^{p_0} \ar[d]_{p_1} & A \ar[d]^{f} & Q  \ar[r]^{l_0\circ q_0} \ar[d]_{l_1\circ q_1}& A \ar[d]^{h\circ f}\\ B \ar[r]_{h\circ g\circ l_1} &D& B \ar[r]_{g}& C &  B \ar[r]_{h\circ g} & D}\]
-		Then there exists an arrow $\phi\colon P\to Q$ such that $(P, \{q_i\circ \phi\}_{i=0}^1)$ is a pullback for $f\circ l_0$ along $g\circ l_1$.
-	\end{lemma} 
-	\begin{proof}
-To prove the existence of $\phi\colon P\to Q$ it's enough to consider the solid part of the diagram below.
-\[\xymatrix@C=30pt{P \ar@{.>}[dr]^{\phi} \ar@/^.2cm/[drr]^{p_0} \ar@/_.2cm/[ddr]_{p_1}\\ & Q  \ar[r]^(.4){l_0\circ q_0} \ar[d]^{l_1\circ q_1}& A \ar[d]^{h\circ f} \\ &B \ar[r]_{h\circ g} & D}\]
-Notice that $\phi$ is a monomorphism. If $\phi\circ a=\phi \circ b$ for some $a,b\colon T\rightrightarrows P$ then
-\[\begin{split}
-	p_0\circ a&=l_0\circ q_0\circ \phi \circ a\\&=l_0\circ q_0\circ \phi \circ b\\&=p_0\circ b
-\end{split} \qquad \begin{split}
-p_1\circ a&=l_1\circ q_1\circ \phi \circ a\\&=l_1\circ q_1\circ \phi \circ b\\&=p_1\circ b
-\end{split} \]
-
-Moreover, we also have the following chain of equalities, showing that  $(P, \{q_i\circ \phi\}_{i=0}^1)$  is a candidate to be a pullback of $f\circ l_0$ along $g\circ l_1$.
-\begin{align*}
-f\circ l_0\circ q_0\circ \phi &=f\circ p_0\\&=g\circ p_1\\&=g\circ l_1\circ q_1\circ \phi 
-\end{align*}
-Let now $e_0\colon E\to A'$ and $e_1\colon E\to B'$ be arrows such that 
-\[f\circ l_0\circ e_0=g\circ l_1\circ e_1\]
-By hypothesis $(P, \{p_i\}_{i=0}^1)$ is a pullback of $f$ along $g$, therefore we there is a unique  arrow $e\colon E\to P$ such that
-\[p_0\circ e = l_0\circ e_0 \qquad p_1\circ e=l_1\circ e_1\]
-But then the two identities
-\[\begin{split}
-	l_0\circ q_0\circ \phi\circ e&=p_0\circ e\\& =l_0\circ e_0 \end{split} \qquad \begin{split}l_1\circ q_1\circ \phi\circ e&=p_1\circ e\\& =l_1\circ e_1
-\end{split}\]
-allow us to conclude that 
-\[q_0\circ \phi\circ e=l_0\circ e_0 \qquad q_1\circ \phi\circ e=l_1\circ e_1\]
-
-Finally, if $e'\colon E \to P$ is another arrow such that 		
-\[q_0\circ \phi\circ e'=l_0\circ e_0 \qquad q_1\circ \phi\circ e'=l_1\circ e_1\]
-then we have 
-\[q_0\circ \phi\circ e'=q_0\circ \phi\circ e \qquad q_1\circ \phi\circ e'=q_1\circ \phi\circ e\]
-Therefore $\phi\circ e'=\phi \circ e$ and we can conclude since $\phi$ is mono.
-	\end{proof}
-
-\begin{lemma}
-	Da ind pair a pb
-\end{lemma}
-
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{lemma}
-	da pb a ind pair
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{corollary}
-	caratterizzazione
-\end{corollary}
-
-\section{Conclusions and further work}
-\todo{VERY NICE CONCLUSIONS}
-
-\bibliographystyle{plain}
-\bibliography{bibliog.bib}
-
-\appendix
-
-\include{factorization.tex}
-
-\include{adhesivity.tex}
-
-\section{Rewriting systems on $\Set$.}\label{app:set}
-
-\section{On permutations}\label{app:perm}
-\todo{inserire risutati sulle permutazione che abbiamo usato}
-
-\begin{definition}
-	\todo{inversioni}
-\end{definition}
-
-\end{document}
-
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:

### 2024-11-14 full_version/permutations.tex
lavorato sulle permutazioni consistenti :^)))))))

--- 2023-12-15 fusione.tex
@@
-\documentclass[a4paper]{article}
-\usepackage{hyperref}
-\usepackage[textsize=tiny]{todonotes}
-%\usepackage{etex}
-
-\usepackage[all]{xy}
-\newdir^{ (}{{}*!/-5pt/@^{(}}
-\SelectTips{cm}{}
-% derivations and labels
-\usepackage{proof}
-\newcommand{\lab}[1]{\ensuremath{\mathsf{{#1}}}}
-\newcommand{\slab}[1]{\ensuremath{\scriptstyle{\mathsf{{#1}}}}}
-
-%frecce
-\newcommand{\mor}{\mathsf{Mor}}
-\newcommand{\mon}{\mathsf{Mono}}
-\newcommand{\reg}{\mathsf{Reg}}
-
-% ``boxed'' \infer command
-\newcommand{\binfer}[3][]{
-  \mbox{\infer[#1]{#2}{#3}}}
-
-% Command for labels on the left side of the rule
-%       \inferL{<name>}{<post>}{<pre>}
-% generates:
-%             <pre>
-%      <name> ------
-%             <post>
-%
-\newlength{\myheight}
-\newcommand{\inferL}[3]
-  {\settoheight{\myheight}{\mbox{${#2}$}}
-   \raisebox{\myheight}{{#1}}
-   \makebox[1mm]{}
-   \mbox{\infer{#2}{#3}}
-}
-
-\usepackage{amssymb,graphicx,epsfig,color}
-%\usepackage[scriptsize]{subfigure}
-\usepackage{subcaption}
-\usepackage{wrapfig}
-
-% re-stating 
-%\usepackage{thm-restate}
-
-% showing labels
-%\usepackage[inline]{showlabels}
-
-\usepackage{pgf}
-\usepackage{tikz}
-\usepackage{tikz-cd}
-\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri,fit,positioning}
-\tikzstyle{node}=[circle, draw=black, minimum size=1mm]
-\tikzstyle{trans}=[font=\scriptsize]
-\tikzstyle{lab}=[font=\small]
-
-\newcommand{\pgfBox}{
-  \begin{pgfonlayer}{background} 
-    \fill[blue!2,thick,draw=black!50,rounded corners,inner sep=3mm] ([xshift=-1.5pt,yshift=-1.5pt]current bounding box.south west) rectangle ([xshift=1.5pt,yshift=1.5pt]current bounding box.north east);
-  \end{pgfonlayer}
-}
-\usepackage{scalerel}
-\newcommand{\smallmin}{\scaleobj{0.6}{-}}
-\newcommand{\Deltamin}{\Delta^{\hspace{-1pt}\downarrow\hspace{-1pt}}}
-\newcommand{\Rrel}[1]   {\stackrel{{#1}}{\Longrightarrow}}
-\newcommand{\oa}{\overline a}
-\newcommand{\ob}{\overline b}
-\newcommand{\oc}{\overline c}
-\newcommand{\od}{\overline d}
-\newcommand{\rec}{\emph{rec}}
-\newcommand{\fn}[1]{{\mathtt{fn}}(#1)}
-%\usepackage{latexsym}
-\usepackage{stmaryrd}
-\def\encodep#1{\llfloor#1\rrfloor}
-
-\newcommand{\cat}[1]{\ensuremath{\mathbf{#1}}}
-
-\newcommand{\dpo}{\textsc{dpo}}
-
-% base classes of categories for adhesive and quasi adhesive case
-\newcommand{\bAdh}{\ensuremath{\mathbb{B}}}
-\newcommand{\bQAdh}{\ensuremath{\mathbb{QB}}}
-
-%from pawel
-\usepackage[latin1]{inputenc}
-\usepackage{amsmath}
-
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{enumerate}
-\usepackage{xspace}
-\usepackage{amsfonts}
-\usepackage{mathrsfs}
-\usepackage{cite}
-\usepackage{float}
-\usepackage{fancybox}
-
-\usepackage{cleveref}
-
-%\spnewtheorem*{notation}{Notation}{\bfseries}{\rmfamily}
-
-%%%%%%%% MATHEMATICAL NOTATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%symbol for natural numbers
-\newcommand{\nat}{\ensuremath{\mathbb{N}}}
-
-% finite subset
-\newcommand{\sfin}{\ensuremath{\subseteq_{\mathit{fin}}}}
-
-% flattening of a multiset
-\newcommand{\flt}[1]{\ensuremath{[\![{#1}]\!]}}
-
-% compact elements
-\newcommand{\compact}[1]{\ensuremath{\mathop{\mathsf{K}({#1})}}}
-
-% principal ideal
-\newcommand{\principal}[1]{\ensuremath{\mathop{\downarrow\!{#1}}}}
-
-% ideal completion
-\newcommand{\ideal}[1]{\ensuremath{\mathsf{Idl}({#1})}}
-
-% complete prime elements
-\newcommand{\pr}[1]{\ensuremath{\mathop{\mathit{pr}({#1})}}}
-\newcommand{\wpr}[1]{\ensuremath{\mathop{\mathit{wpr}({#1})}}}
-
-% irreducible elements
-\newcommand{\ir}[1]{\ensuremath{\mathop{\mathit{ir}({#1})}}}
-
-% difference of irreducible elements
-\newcommand{\diff}[2]{\ensuremath{\delta({#1},{#2})}}
-
-% immediate precedence
-
-% abbreviation for event structure
-% \newcommand{\esabbr}{event structure}
-\newcommand{\esabbr}{\textsc{es}}
-\newcommand{\esnabbr}{\textsc{esnb}}
-\newcommand{\esnmabbr}{\textsc{esn}}
-\newcommand{\eseqabbr}{\textsc{epes}}
-
-% predecessor of an irreducible
-\newcommand{\pred}[1]{\ensuremath{\mathit{p}({#1})}}
-
-% irreducible elements in es domains
-\newcommand{\esir}[2]{\ensuremath{\langle{#1}, {#2}\rangle}}
-
-% equivalence classes [of irreducibles]
-\newcommand{\eqclass}[2][]{\ensuremath{[{#2}]_{\scriptscriptstyle {#1}}}}
-% union of the equivalence classes of the elements in a set
-\newcommand{\eqclasscup}[2]{\ensuremath{{#2}_{\scriptscriptstyle {#1}}}}
-
-\newcommand{\eqclassir}[1]{\ensuremath{\eqclass[\leftrightarrow^*]{#1}}}
-
-% quotient of set wrt a relation
-\newcommand{\quotient}[2]{\ensuremath{{#1}_{\scriptscriptstyle {#2}}}}
-
-% category of event structures 
-\newcommand{\es}{\ensuremath{\mathsf{ES}}}
-% category of stable event structures 
-\newcommand{\ses}{\ensuremath{\mathsf{sES}}}
-% category of prime event structures 
-\newcommand{\pes}{\ensuremath{\mathsf{pES}}}
-% category of prime event structures with equivalence
-\newcommand{\epes}{\ensuremath{\mathsf{epES}}}
-
-% category of connected event structures 
-\newcommand{\ces}{\ensuremath{\mathsf{cES}}}
-
-% category of weak prime algebraic domains domains 
-\newcommand{\WDom}{\ensuremath{\mathsf{wDom}}}
-% category of domains
-\newcommand{\Dom}{\ensuremath{\mathsf{Dom}}}
-% category of prime algebraic domains
-\newcommand{\PDom}{\ensuremath{\mathsf{pDom}}}
-
-%%%%% NON BINARY CONFLICT
-
-% category of event structures 
-\newcommand{\esn}{\ensuremath{\mathsf{ES_{nb}}}}
-% category of stable event structures 
-\newcommand{\sesn}{\ensuremath{\mathsf{sES_n}}}
-
-% category of connected event structures 
-\newcommand{\cesn}{\ensuremath{\mathsf{cES_{nb}}}}
-
-% category of prime event structures 
-\newcommand{\pesn}{\ensuremath{\mathsf{pES_n}}}
-
-% category of fusion domains 
-\newcommand{\WDomb}{\ensuremath{\mathsf{wDom_b}}}
-% category of domains
-\newcommand{\Domb}{\ensuremath{\mathsf{Dom_b}}}
-% category of prime algebraic domains
-\newcommand{\PDomb}{\ensuremath{\mathsf{pDom_b}}}
-
-%%%%% END NON BINARY CONFLICT
-
-% slice category
-\newcommand{\slice}[2]{\ensuremath{({#1} \downarrow {#2})}}
-
-% event structure for a domain
-\newcommand{\zev}[0]{\ensuremath{\mathcal{E}}}
-\newcommand{\ev}[1]{\ensuremath{\zev({#1})}}
-
-% from general to connected event structures
-\newcommand{\zconnes}[0]{\ensuremath{\mathcal{C}}}
-\newcommand{\connes}[1]{\ensuremath{\zconnes({#1})}}
-% and inclusion
-\newcommand{\zinces}[0]{\ensuremath{\mathcal{I}}}
-\newcommand{\inces}[1]{\ensuremath{\zinces({#1})}}
-
-% stable version
-\newcommand{\zsev}[0]{\ensuremath{\mathcal{E}_S}}
-\newcommand{\sev}[1]{\ensuremath{\zsev({#1})}}
-
-% with equivalence
-\newcommand{\zeveq}[0]{\ensuremath{\mathcal{E}_{eq}}}
-\newcommand{\eveq}[1]{\ensuremath{\zeveq({#1})}}
-
-% es with equivalence to es and vice
-\newcommand{\zfuse}[0]{\ensuremath{\mathcal{M}}}
-\newcommand{\fuse}[1]{\ensuremath{\zfuse({#1})}}
-\newcommand{\zunf}[0]{\ensuremath{\zunf}}
-\newcommand{\unf}[1]{\ensuremath{\mathcal{U}({#1})}}
-
-% Winskel/Droste version
-\newcommand{\zevwd}[0]{\ensuremath{\mathcal{E}_{wd}}}
-\newcommand{\evwd}[1]{\ensuremath{\zevwd({#1})}}
-
-% configurations of an event structure
-\newcommand{\conf}[1]{\ensuremath{\mathit{Conf}({#1})}}
-% finite configurations
-\newcommand{\conff}[1]{\ensuremath{\mathit{Conf_F}({#1})}}
-
-% product of the sets of minimal enablinsg
-\newcommand{\pmin}[1]{\ensuremath{U_{#1}}}
-
-% connectectedness of minimal enablinsg
-\newcommand{\conn}[1]{\ensuremath{\stackrel{#1}{\frown}}}
-
-% domain for an event structure or graph grammar
-\newcommand{\zdom}[0]{\ensuremath{\mathcal{D}}}
-\newcommand{\dom}[1]{\ensuremath{\zdom({#1})}}
-
-\newcommand{\zdomeq}[0]{\ensuremath{\mathcal{D}_{eq}}}
-\newcommand{\domeq}[1]{\ensuremath{\zdomeq({#1})}}
-
-% partial order for a graph grammar
-\newcommand{\poset}[1]{\ensuremath{\mathcal{P}({#1})}}
-
-% stable version
-\newcommand{\pdom}[1]{\ensuremath{\mathcal{D}_S({#1})}}
-\newcommand{\ppdom}[0]{\ensuremath{\mathcal{D}_S}}
-
-% powerset
-\newcommand{\Pow}[1]{\ensuremath{\mathbf{2}^{#1}}}
-
-% powerset of finite subsets
-\newcommand{\Powfin}[1]{\ensuremath{\mathbf{2}_\mathit{fin}^{#1}}}
-
-% powerset of subsets of cardinality <= 1
-\newcommand{\Powone}[1]{\ensuremath{\mathbf{2}_1^{#1}}}
-
-% integer interval
-\newcommand{\interval}[2][1]{\ensuremath{[{#1},{#2}]}}
-
-% domain interval
-\newcommand{\dint}[2]{\ensuremath{[{#1},{#2}]}}
-
-% set of intervals
-\newcommand{\IntSet}[1]{\ensuremath{\mathop{\mathit{Int}({#1})}}}
-
-% intervals to irreducibles and vice
-\newcommand{\inir}{\ensuremath{\mathop{\mathit{\zeta}}}}
-\newcommand{\irin}{\ensuremath{\mathop{\mathit{\iota}}}}
-
-% permutations
-\newcommand{\perm}{\sigma}
-
-% causes
-\newcommand{\causes}[1]{\ensuremath{\lfloor {#1})}}
-
-%%% GRAPH GRAMMARS
-
-\newcommand{\Abs}[1]{\ensuremath{\mathsf{Abs}({#1})}}
-\newcommand{\tr}[1]{\ensuremath{\mathsf{Tr}({#1})}}
-% fusion safe traces
-\newcommand{\trs}[1]{\ensuremath{\mathsf{Tr}_s({#1})}}
-%\newcommand{\graph}{\ensuremath{\mathsf{Graph}}}
-\newcommand{\tgraph}[1]{\ensuremath{\mathsf{Graph}_{#1}}}
-\newcommand{\can}[1]{\ensuremath{\mathsf{C}({#1})}}
-% source and target of a derivation
-\newcommand{\source}[1]{\ensuremath{\mathsf{s}({#1})}}
-\newcommand{\target}[1]{\ensuremath{\mathsf{t}({#1})}}
-\newcommand{\col}[1]{\ensuremath{\mathsf{col}({#1})}}
-
-% left decorated trace
-\newcommand{\ltrace}[1]{\ensuremath{\langle {#1}\rangle_c}}
-
-\newcommand{\bx}[1]{\phantom{\big(}#1{\phantom{\big)}}}
-\newcommand{\bxx}[1]{\,#1\,}
-\newcommand{\cycl}[1]{\ensuremath{\mbox{\textcircled{\scriptsize{$#1$}}}}}
-\renewcommand{\iff}{\ensuremath{\Leftrightarrow}}
-
-%%%%GENERAL CATEGORICAL NOTATION
-
-%identità
-\newcommand{\id}[1]{\mathsf{id}_{#1}}
-%codominio
-\newcommand{\cod}[1]{\mathsf{cod}({#1})}
-	%Variabili categorie
-\def\A{\textbf {\textup{A}}}
-%mono
-\newcommand{\mto}[0]{\scalebox{1}{$\rightarrowtail$}}
-
-\newcommand{\sk}{\mathsf{sk}_{\X}}
-
-\def\R{\mathsf{R}}
-\def\B{\textbf {\textup{B}}}
-\def\C{\textbf {\textup{C}}}
-\def\D{\textbf {\textup{D}}}
-\def\X{\textbf {\textup{X}}}
-\def\Y{\textbf {\textup{Y}}}
-
-\newcommand{\ske}{\mathsf{sk}(\X)}
-\renewcommand{\P}{\textbf {\textup{P}}}
-
-%\derivazioni
-
-\newcommand{\dder}[1]{\mathscr{#1}}
-\newcommand{\sder}[2]{S_{i_1,i_2}(\mathscr{#1}, \mathscr{#2})}
-\newcommand{\der}[1]{\underline{\dder{#1}}}
-\def\dpo{\mathsf{C}^{\X}_R}
-\def\gpo{\mathsf{G}^{\X}_R}
-\def\dpi{[\mathsf{C}]^{\X}_R}
-\def\gpi{[\mathsf{G}]^{\X}_R}
-
-\newcommand{\ider}[1]{\mathscr{I}_{#1}}
-
-%categorie
-\def\Set{\textbf {\textup{Set}}}
-
-%comma
-\newcommand{\comma}[2]{#1\hspace{1pt} {\downarrow}\hspace{1pt} #2}
-\newcommand{\cma}[2]{\mathcal{#1}\hspace{1pt} {\downarrow}\hspace{1pt} \mathcal{#2}}
-
-%derivazioni
-\newcommand{\lpro}{\langle \hspace{-1.85pt}[}
-\newcommand{\rpro}{]\hspace{-1.85pt}\rangle}
-\newcommand{\tpro}[1]{\lpro \der{#1}\rpro}
-\newcommand{\tproi}[2]{\lpro \der{#1}_{#2}\rpro}
-\newcommand{\lgh}[0]{\mathsf{lg}}
-
-%%% NEW
-
-\usepackage{xparse}
-
-% inversions
-\newcommand{\inv}[1]{\ensuremath{inv}({#1})}
-
-% direct shift
-\newcommand{\shiftdir}[1][]{\ensuremath{\mathrel{{\rightsquigarrow}^{\mathit{sh}}_{#1}}}}
-
-% shift preorder
-\newcommand{\shiftpre}[1][]{\ensuremath{\mathrel{{\sqsubseteq}^{\mathit{sh}}_{#1}}}}
-
-% shift equivalence
-\newcommand{\shifteq}[1][]{\ensuremath{\mathrel{{\equiv}^\mathit{sh}_{#1}}}}
-
-% transp{source}[target]: if target not specified source+1
-\NewDocumentCommand{\transp}{m o}{%
-  \ensuremath{({#1},%
-  \IfNoValueTF{#2}%
-    {{#1}+1}%
-    {#2}%
-    )}
-}
-
-\NewDocumentCommand{\mycommand}{o}{%
-  % <code>
-  \IfNoValueTF{#1}
-    {code when no optional argument is passed}
-    {code when the optional argument #1 is present}%
-  % <code>
-}
-% interchange
-\newcommand{\IC}[1]{\ensuremath{\mathit{IC}({#1})}}
-
-%%%%% Ambienti matematici  %%%%%%
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{proposition}[theorem]{Proposition}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{corollary}[theorem]{Corollary}
-
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem*{notation}{Notation}
-\newtheorem{remark}[theorem]{Remark}
-\newtheorem{example}[theorem]{Example}
-
-\title{Switch equivalence and weak prime domains for fusions}
-\author{Paolo Baldan\and Davide Castelnovo\and  Andrea Corradini\and Fabio Gadducci}
-
-\begin{document}
-\maketitle
-
-\begin{abstract}
-\todo{	A VERY NICE ABSTRACT}
-\end{abstract}
-
-\tableofcontents
-\section{Introduction}
-
-\todo{A VERY NICE INTRODUCTION}
-
-\section{$\mathcal{M}$-adhesive categories}
-
-This first section is devoted to recall the definition and the basic theory of \emph{$\mathcal{M}$-adhesive categories} \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,lack2005adhesive}.
-
-\begin{notation} 
-We stipulate here some notational conventions which will be used throughout this paper. 
-\begin{itemize}\item 
-	Given a category $\X$ we will not distinguish notationally between $\X$ and its class of objects: so that ``$X\in \X$'' means that $X$ belongs to the class of objects of $\X$.  
-	\item 
-	If $1$ is a terminal object in a category $\X$,  the unique arrow $X\to 1$ from another object $X$ will be denoted by $!_X$.
-Similarly, if $0$ is initial in $\X$ then $?_X$ will denote the unique arrow $0\to X$.
-%When $\X$ is $\Set$ and $1$ is a singleton, $\delta_x$ will denote the arrow $1\to X$ with value $x\in X$.
-	\item  $\mor(\X)$, $\mon(\X)$ and $\reg(\X)$ will denote the class of all arrows, monos and regular monos of $\X$, respectively.
-
-	\item Given an integer $n\in \mathbb{Z}$, $[0,n]$ will denote the set
-	\[[0,n]:=\{x\in \mathbb{N}\mid x\leq n\}\]
-	Indeed, if $n<0$, then $[0,n]=\emptyset$.
-\end{itemize}
-\end{notation}
-
-\subsection{The Van Kampen property}
-The key property that $\mathcal{M}$-adhesive categories enjoy is given by  the so-called \emph{Van Kampen condition} \cite{brown1997van,johnstone2007quasitoposes,lack2005adhesive}.
-We will recall it and examine some of its consequences.
-First of all we need to recall some terminology and facts regarding subclasses of $\mor(\X)$.
-
-\begin{definition}
-	Let $\X$ be a category and $\mathcal{A}$ a  subclass of $\mor(\X)$. We say that  $\mathcal{A}$ is
-	\begin{itemize}
-		\item 
-		\emph{stable under pushouts (pullbacks)} if for every pushout (pullbacks) square 
-		\[\xymatrix{A\ar[r]^f  \ar[d]_{m}& B \ar[d]^n \\ C \ar[r]_g & D}\]
-		if $m \in \mathcal{A}$ ($n\in \mathcal{A}$) then $n \in \mathcal{A}$ ($m \in \mathcal{A}$);
-		\item \emph{closed under composition} if $g, f\in \mathcal{A}$ implies $g\circ f\in \mathcal{A}$ whenever $g$ and $f$ are composable;
-		\item \emph{closed under decomposition} if $g\circ f, g\in \mathcal{A}$ implies $f\in \mathcal{A}$.
-	\end{itemize}
-\end{definition}
-
-\begin{remark}In the previous definition, ``decomposition'' corresponds to ``left cancellation'', but we prefer to stick to the name commonly used in literature (see e.g.~\cite{habel2012mathcal}).
-\end{remark}
-
-So equipped, we can introduce the notion of \emph{$\mathcal{A}$-Van Kampen square}.
-\begin{definition}[Van Kampen property] Let $\X$ be a category  and consider the two diagrams below
-	\[\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{f'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{f}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){g'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){f} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{g} &&D&&C \ar[rr]_{g} & & D}\]
-
-	Given  a class of arrows $\mathcal{A}\subseteq \mor(\X)$, we say that the left square \emph{has the Van Kampen property relatively to $\mathcal{A}$}, or that it  is a \emph{$\mathcal{A}$-Van Kampen square} if:
-	\begin{enumerate}
-		\item is a pushout square;
-		\item 	whenever the right cube has pullbacks as back and left faces and the vertical arrows belong to $\mathcal{A}$, then its top face is a pushout if and only if the front and right faces are pullbacks.
-	\end{enumerate}
-	Pushout squares which enjoy the ``if'' half of the second point of the condition above are called \emph{$\mathcal{A}$-stable}.
-
-We will call a $\mor(\X)$-Van Kampen ($\mor(\X)$-stable) square simply a \emph{Van Kampen} (\emph{stable}) square.
-\end{definition}
-
-Before proceeding further, we recall this classical result about pullbacks.
-
-\begin{lemma}\label{lem:pb1}
-	Let $\X$ be a category, and consider the following diagram 	in which the right square is a pullback.
-	\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
-	Then the whole rectangle is a pullback if and only if the left square is one.
-\end{lemma}
-
-The previous result can be dualised to get an analogous lemma for pushouts.
-
-\begin{lemma}\label{lem:po1}
-	Let $\X$ be a category, and consider the following diagram 	in which the left square is a pushout.
-	\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
-	Then the whole rectangle is a pushout if and only if the right square is one.
-\end{lemma}
-
-The following proposition establishes a key property of $\mathcal{A}$-Van Kampen squares with a mono as a side: they are not only pushouts, but also pullbacks.
-\begin{proposition}\label{prop:pbpo} Let $\mathcal{A}$ be a class of arrows stable under pushouts and containing all the isomorphisms.
-If $m\colon A\to C$ is mono and belongs to $\mathcal{A}$, then every $\mathcal{A}$-Van Kampen square
-	\[\xymatrix{A\ar[r]^{g} \ar[d]_{m} & B \ar[d]^{n} \\ C \ar[r]_{f}  & D}\]
-	is also a pullback square and $n$ is a monomorphism.
-\end{proposition}
-\begin{proof} We can start considering the cube below and noticing that $n$, being the pushout of $m\in \mathcal{M}$, belongs to $\mathcal{A}$ too.
-	\[\xymatrix@C=13pt@R=13pt{&A\ar[dd]|\hole_(.65){\id{A}}\ar[rr]^{g} \ar[dl]_{\id{A}} && B \ar[dd]^{\id{B}} \ar[dl]_{\id{B}} \\ A  \ar[dd]_{m}\ar[rr]^(.65){g} & & B \ar[dd]_(.3){n}\\&A\ar[rr]|\hole^(.65){g} \ar[dl]^{m} && B \ar[dl]^{n} \\C \ar[rr]_{f} & & D}\]
-	By construction the top face of the cube is a pushout and the back one a pullback.
-The left face is a pullback because $m$ is mono.
-Thus the $\mathcal{A}$-Van Kampen property yields that the front and the right faces are pullbacks.
-\end{proof}
-
-The previous proposition, in turn, allows us to establish the following results.
-\begin{lemma}\label{lem:varie}Let $\mathcal{A}$ be a class of arrows stable under pullbacks, pushouts and containing all isomorphisms.
-Suppose that, the left square below is $\mathcal{A}$-Van Kampen, while the vertical faces in the right cube are pullbacks.
-		\[\xymatrix@C=10pt@R=10pt{&&&&&A'\ar[dd]|\hole_(.65){a}\ar[rr]^{g'} \ar[dl]_{m'} && B' \ar[dd]^{b} \ar[dl]_{n'} \\ A \ar[dd]_{m}\ar[rr]^{g}&&B\ar[dd]^{n}&&C'  \ar[dd]_{c}\ar[rr]^(.7){f'} & & D' \ar[dd]_(.3){d}\\&&&&&A\ar[rr]|\hole^(.65){g} \ar[dl]^{m} && B \ar[dl]^{n} \\C\ar[rr]_{f} &&D&&C \ar[rr]_{f} & & D}\]
-Supppose, moreover that $m:A\to C$ and $d:D'\to D$ are mono and that $d$ belongs to $\mathcal{A}$. Then $d\leq n$ if and only if $c \leq m$.
-\end{lemma}
-
-\begin{remark}
-	Recall that, given two monos $m:M\to X$ and $n:N\to X$ with the same codomain, $m\leq n$ means that there exists a, necessarily unique and necessarily mono, $k:M\to N$ fitting in the triangle below:
-	\[\xymatrix{M\ar[rr]^{k}  \ar[dr]_{m}&& N \ar[dl]^{n}\\ & X}\]
-	Notice that, if $m\leq n$ and $n\leq m$, then the arrow $k:M\to N$ is an isomorphism.  
-\end{remark}
-\begin{remark}
-	Notice that, since $d$ is a mono and the vertical faces are pullbacks, then $a, b$ and $c$ are monomorphisms too. Moreover, $n$ is mono by \Cref{prop:pbpo}, so that even $m'$ and $n'$ are monos.
-\end{remark}
-
-\begin{proof}
-	$(\Rightarrow)$ By hypothesis there exists $k:D'\to B$ such that $n\circ k = d$.
-By \Cref{prop:pbpo}, the bottom face of the cube is a pullback.
-Thus there exists a unique $h:C'\to A$ as in the diagram below, implying the thesis.
-		\[\xymatrix@C=40pt{C'  \ar[d]^{h}\ar[r]^{f'} \ar@/_.5cm/[dd]_{c}& D' \ar@/^.5cm/[dd]^{d}\ar[d]_{k}\\ A \ar[d]^{m} \ar[r]^{g} & B \ar[d]_{n} \\  C \ar[r]_f & D}\]
-
-	\smallskip \noindent 
-	$(\Leftarrow)$ Let $h:C\to A$ be such that $c=m\circ h$.
-By the $\mathcal{A}$-Van Kampen property the top face of the given cube is a pushout.
-Thus the dotted $k:D'\to B$ in the following diagram exists.
-		\[\xymatrix@C=40pt{A' \ar@/_.5cm/[dd]_{a} \ar[d]^{m'} \ar[r]^{g'} & B' \ar[d]_{n'} \ar@/^.5cm/[dd]^{b} \\  C' \ar[d]^{h} \ar[r]_{f'} & D' \ar@{.>}[d]_{k}\\ A \ar[r]_g& B }\]
-Moreover, by construction we have
-\[\begin{split}
-n\circ k \circ n' &= n\circ b\\&=d\circ n'\\&\\&
-\end{split} \qquad \begin{split}
-n\circ k \circ f' &= n\circ g\circ h\\&=f\circ m\circ h\\&=f\circ c\\&= d\circ f' \end{split}\]
-We can therefore conclude that $n\circ k =d$. \qedhere 
-\end{proof}
-
-Finally, we can show that $\mathcal{A}$-stable pushouts enjoy a kind of \emph{pullback-pushout decomposition} property.
-
-\begin{proposition}\label{prop:stab}Let $\X$ be a category and $\mathcal{A}$ a class of arrows stable under pullbacks.
-Suppose that, in the diagram below, the whole rectangle is an $\mathcal{A}$-stable pushout and the right square a pullback.
-	\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
-	If the arrow $k$ is in $\mathcal{A}$ and it is a monomorphism,  then both squares are pushouts.
-\end{proposition}
-
-\begin{proof} We can begin noticing that $g$, being the pullback of $k$, is mono and in $\mathcal{A}$ too.
-Thus we can build the cube below, in which all the vertical faces are pullbacks, entailing that all the vertical arrows are in $\mathcal{A}$.
-	\[\xymatrix@C=20pt@R=10pt{ & &X\ar[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar[ddd]_{g} \ar[rrr]^{b}&&& B\ar[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar[dl]_{f}&&& A \ar[dl]^{h}\\ & Y  \ar[dl]_{g}&&& B \ar[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
-	By hypothesis the face is an $\mathcal{A}$-stable pushout and so its top one is a pushout.
-Using \Cref{lem:po1} we can conclude that the right half of the rectangle with which we have started is a pushout too.
-\qedhere
-\end{proof}
-
-\subsection{$\mathcal{M}$-adhesivity}
-
-In this section we will define the notion of $\mathcal{M}$-adhesivity \cite{azzi2019essence,ehrig2012,ehrig2014adhesive,heindel2009category,lack2005adhesive} and explore some of the consequence of such a property.
-
-\begin{definition}[$\mathcal{M}$-adhesive category]
-	Let $\X$ be a category and consider a subclass $\mathcal{M}$ of the class $\mon(\X)$ of monomorphisms such that:
-	\begin{enumerate}
-		\item $\mathcal{M}$ contains all isomorphisms and is closed under composition;
-		\item $\mathcal{M}$ is stable under pullbacks and pushouts.
-	\end{enumerate} 
-	We will use $m\colon X\mto Y$ to denote that an arrow $m:X\to Y$ belongs to $\mathcal{M}$. $\X$ is said to be \emph{$\mathcal{M}$-adhesive} if
-	\begin{enumerate}
-		\item for every $m\colon X\mto Y$ in $\mathcal{M}$ and $g\colon Z\to Y$, a pullback square
-		\[\xymatrix{P\ar[r]^p \ar@{>->}[d]_{n}& X \ar@{>->}[d]^{m}\\ Z \ar[r]_g& Y}\]
-		exists, such pullbacks will be called \emph{$\mathcal{M}$-pullbacks};
-		\item for every $m\colon X\mto Y$ in $\mathcal{M}$ and $f\colon X\to Z$, a pushout square
-		\[\xymatrix{X \ar[r]^f \ar@{>->}[d]_{m}& Z \ar[d]^{q}\\ Y\ar[r]_p &Q}\]
-		exists, such pushouts  will be called \emph{$\mathcal{M}$-pushouts}; 
-		\item  $\mathcal{M}$-pushouts are $\mathcal{M}$-Van Kampen squares.
-	\end{enumerate}
-
-A category $\X$ is said to be \emph{strictly $\mathcal{M}$-adhesive} if $\mathcal{M}$-pushouts are Van Kampen squares.	
-\end{definition}
-
-\begin{remark}\label{rem:diff}Our notion of $\mathcal{M}$-adhesivity follows \cite{ehrig2012,ehrig2014adhesive} and is different from the one of \cite{azzi2019essence}.
-What is called $\mathcal{M}$-adhesivity in that paper corresponds to our strict $\mathcal{M}$-adhesivity.
-Moreover, in \cite{azzi2019essence} the class $\mathcal{M}$ is assumed to be only stable under pullbacks.
-However, if $\mathcal{M}$ contains all split monos, then stability under pushouts can be deduced from the other axioms \cite[Prop.~$5.1.21$]{castelnovo2023thesis}.
-\end{remark}
-
-\begin{remark}\label{rem:salva} 
-	\emph{Adhesivity} and \emph{quasiadhesivity} as defined in \cite{lack2005adhesive,garner2012axioms}  coincide with  strict $\mon(\X) $-adhesivity and strict $\reg(\X)$-adhesivity, respectively. 
-\end{remark}
-
-A first result we can prove regards closure under decomposition of $\mathcal{M}$.
-
-\begin{proposition}\label{prop:deco}Let  $\mathcal{A}$ be a class of arrows stable under pullbacks.
-For every arrow $f\colon X\to Y$ and monomorphism $m\colon Y\to Z$, if $m\circ f \in\mathcal{A}$ then $f\in \mathcal{A}$.
-\end{proposition}
-\begin{proof}Take the diagram
-	\[\xymatrix{X \ar[d]_{\id{X}}\ar[r]^{f}& Y \ar[r]^{\id{Y}}  \ar[d]_{\id{Y}}& Y \ar[d]^{m}\\
-		X \ar[r]_{f}& Y \ar[r]_{m} & Z}\]
-	Since $m$ is mono the right square is a pullback, while the left square is a pullback by construction. By \Cref{lem:pb1} the whole rectangle is a pullback and the thesis follows.
-\end{proof}
-\begin{corollary}\label{cor:deco}
-	In every $\mathcal{M}$-adhesive category $\X$, the class $\mathcal{M}$ is closed under decomposition.
-\end{corollary}
-
-Another result which can be immediately established, with the aid of \Cref{prop:pbpo}, is the following one.
-\begin{proposition}\label{prop:pbpoad}
-	Let $\X$ be an $\mathcal{M}$-adhesive category. Then $\mathcal{M}$-pushouts are also pullback squares.
-\end{proposition}
-
-From \Cref{prop:pbpoad}, in turn, we can derive the following corollaries.
-\begin{corollary}\label{cor:rego}
-	In a $\mathcal{M}$-adhesive category $\X$, every $m\in\mathcal{M}$ is a regular mono.
-\end{corollary}
-\begin{proof}
-Let $m$ be an element of $\mathcal{M}$ and consider its pushout along itself.
-\[\xymatrix{X\ar@{>->}[r]^m \ar@{>->}[d]_m& Y\ar@{>->}[d]^{f}\\Y \ar@{>->}[r]_g & Z}\]
-By \Cref{prop:pbpoad} this square is a pullback, proving that $m$ is the equalizer of the arrows $f,g\colon Y\rightrightarrows Z$. \qedhere 
-\end{proof}
-
-The following result now follows at once noticing that a regular monomorphism which is also epic is automatically an isomorphism.
-
-\begin{corollary}\label{prop:bal}
-If $\X$ is an $\mathcal{M}$-adhesive categories, then every epimorphisms in $\mathcal{M}$ is an isomorphisms.
-In particular, every adhesive category $\X$ is \emph{balanced}: if a morphism is monic and epic, then it is an isomorphism.
-\end{corollary}
-
-$\mathcal{M}$-adhesivity is well-behaved with respect to  the comma construction \cite{mac2013categories}, as shown by the following theorem.
-\begin{theorem}[\cite{ehrig2006fundamentals,lack2005adhesive}]\label{lem:comma}
-	Let $\A$ and $\B$ be respectively an $\mathcal{M}$-adhesive and an $\mathcal{M}'$-adhesive category.
-Let also $L:\A\rightarrow \C$ be a functor that preserves $\mathcal{M}$-pushouts, and  $R:\B\rightarrow \C$ be a functor which preserves pullbacks.Then $\comma{L}{R}$ is $\cma{M}{M'}$-adhesive, where
-	\[
-	\cma{M}{M}':=\{(h,k)\in \mathcal{A}(\comma{L}{R}) \mid h\in \mathcal{M}, k\in \mathcal{M}'\}\]
-\end{theorem}
-
-In particular, we can apply this result to slices over and under a given object.
-
-\begin{corollary}\label{cor:slice}
-	Let  $X$ be an object of an $\mathcal{M}$-adhesive category $\X$. Then  $\X/X$ and $X/\X$ are, respectively, is $\mathcal{M}/X$- and $X/\mathcal{M}$-adhesive, where
-	\[\mathcal{M}/X:=\{m\in  \mathcal{A}(\X/X) \mid m\in \mathcal{M} \} \qquad X/\mathcal{M}:=\{m\in  \mathcal{A}(X/\X) \mid m\in \mathcal{M} \}\]
-\end{corollary}
-
-Another categorical construction which preserves $\mathcal{M}$-adhesivity property is the formation of the category of functors.
-
-\begin{theorem}[\cite{ehrig2006fundamentals,lack2005adhesive}]\label{thm:functors}
-If $\X$ is an $\mathcal{M}$-adhesive category, then for every small category $\Y$, the category $\X^\Y$  of functors $\Y\to \X$ is $\mathcal{M}^{\Y}$-adhesive, where
-\[\mathcal{M}^{\Y}:=\{\eta \in \mathcal{A}(\X^\Y) \mid \eta_Y \in \mathcal{M} \text{ for every } Y\in \Y\}\]
-\end{theorem}
-
-We can list various examples of $\mathcal{M}$-adhesive categories (see \cite{castelnovo2023thesis,CastelnovoGM22,lack2006toposes}).
-
-\begin{example}\todo{Topos, ipergrafi e grafi}
-\end{example}
-
-\begin{example}
-	\todo{grafi semplici}
-\end{example}
-
-\begin{example}\todo{GRAFI GERARCHICI}
-\end{example}
-
-\begin{example}\todo{term graph}
-\end{example}
-
-We end this section proving two properties of $\mathcal{M}$-adhesive categories:  $\mathcal{M}$-pushout-pullback decomposition and uniqueness of pushouts complements.
-
-\begin{lemma}[$\mathcal{M}$-pushout-pullback decomposition]\label{lem:popb} Let $\X$ be an $\mathcal{M}$-adhesive category  and suppose that, in the diagram below, the whole rectangle is a pushout and the right square a pullback.
-\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
-	Then the following statements hold true:
-	\begin{enumerate}
-\item if $a$ belongs to $\mathcal{M}$ and $k$ is a monomorphism,  then both squares are pushouts and pullbacks;
-\item if $f$ and $k $ are in  $\mathcal{M}$, then both squares are pushouts and pullbacks.
-	\end{enumerate}
-\end{lemma}
-\begin{proof}
-\begin{enumerate}
-	\item By \Cref{prop:stab}, it follows that both squares are pushouts, thus the thesis follows from \Cref{prop:pbpoad}.
-	\item By hypothesis, $g$ is the pullback of an arrow in $\mathcal{M}$, thus it belongs to it.
-But then $g\circ f\in \mathcal{M}$ too  and the whole rectangle is a $\mathcal{M}$-pushout.
-Therefore, by \Cref{prop:pbpoad} a pullback, so that its left half is a pullback too, by \Cref{prop:pbpo}.
-Moreover $k\circ h$ is in $\mathcal{M}$ as the pushout of $g\circ f$ and, by \Cref{cor:deco}, we also know that $h\in \mathcal{M}$.
-
-	Using \Cref{lem:po1}, it is enough to show that the left half of the original rectangle is a pushout. We can build the following cube:
-	\[\xymatrix@C=20pt@R=10pt{ & &X\ar@{>->}[dl]_{f} \ar[ddd]^(.333333){\id{X}}|(.666666)\hole\ar[rrr]^{a} &&&A \ar[ddd]^{\id{A}} \ar@{>->}[dl]^{h}\\& Y\ar[dl]_{\id{Y}} \ar[ddd]|(.333333)\hole_{\id{Y}} &&&B \ar[ddd]^{\id{B}} \ar[dl]_{\id{B}} \\Y \ar@{>->}[ddd]_{g} \ar[rrr]^{b}&&& B\ar@{>->}[ddd]^{k}\\&&X \ar[rrr]|(.34)\hole^{a}|(.67)\hole \ar@{>->}[dl]_{f}&&& A \ar@{>->}[dl]^{h}\\ & Y \ar[rrr]|(.67)\hole^{b} \ar@{>->}[dl]_{g}&&& B \ar@{>->}[dl]^{k}\\ Z\ar[rrr]_{c} &&& C}\]
-	Its vertical faces are all pullbacks and all the vertical arrows are in $\mathcal{M}$, hence the top face is a pushout and we can conclude. \qedhere 
-\end{enumerate}
-\end{proof}
-
-Let us turn our attention to pushout complements.
-
-\begin{definition}[Pushout complement]
-Let $f\colon X\to Y$ and $g\colon Y\to Z$ ba two composable arrows in a category $\X$.
-A \emph{pushout complement} for the pair $(f,g)$ is a pair $(h,k)$ with $h\colon X\to W$ and $k\colon W\to Z$ such that the square below commutes and it is a pushout.
-\[\xymatrix{X \ar[r]^{f} \ar[d]_{h}& Y \ar[d]^{g} \\ W \ar[r]_{k}& Z}\]
-\end{definition}
-
-\begin{example}
-	In a generic category $\X$, pushout complements may not exist: in $\Set$ the arrows $?_{2}\colon \emptyset \to 2$ and $!_2\colon 2\to 1$ do not have a pushout complement.
-
-	Moreover, composable arrows $f\colon X\to Y$ and $g\colon Y\to Z$ may have  pushout complements which are non-isomorphic: for instance, in $\Set$ the two squares below are both pushouts.
-
-	\[\xymatrix{2 \ar[r]^{!_2} \ar[d]_{\id{2}}& 1 \ar[d]^{\id{1}} & 2 \ar[r]^{!_2} \ar[d]_{!_2}& 1 \ar[d]^{\id{1}}\\ 2 \ar[r]_{!_2}& 1 & 1 \ar[r]_{\id{1}}& 1}\]
-\end{example}
-
-Working in an $\mathcal{M}$-adhesive category we can amend the second defect.
-
-\begin{lemma}[Uniqueness of pushouts complements]\label{lem:pocomp} 
-Let $\X$ be a $\mathcal{M}$-adhesive category.
-Given $m\colon X\mto Y$ in $\mathcal{M}$ and $n\colon Y\to Z$, let $(h_1, k_1)$ and $(h_2, k_2)$ be pushout complements of $m$  and $n$ and $W_1=\cod{h_1}$, $W_2=\cod{h_2}$.
-Then there exists a unique isomorphism $f\colon W_1\to W_2$ making the following diagram commutative.
-\[\xymatrix{&X \ar@{>->}[r]^{m} \ar[d]_{h_1} \ar@/_.3cm/[ddl]_{h_2}& Y \ar[d]^{n} \\ &W_1 \ar@{.>}[dl]^{f} \ar@{>->}[r]_{k_1} & Z \\ W_2 \ar@{>->}@/_.3cm/[urr]_{k_2}}\]
-
-\end{lemma}
-\begin{proof} By hypothesis
-	$k_1$ and $k_2$, being the pushout of $m$, are elements of $\mathcal{M}$ and therefore are monomorphisms.
-In particular, $k_2$ is a monomorphism and this  entails at once the uniqueness of $f$.
-Moreover, notice that the squares
-	\[\xymatrix{X \ar@{>->}[r]^{m} \ar[d]_{h_1}& Y \ar[d]^{n}& X \ar[d]_{h_2}\ar@{>->}[r]^{m} & Y \ar[d]^{n}\\ W_1 \ar@{>->}[r]_{k_1} & Z & W_2 \ar@{>->}[r]_{k_2}& Z}\]
-	are $\mathcal{M}$-pushouts and thus $\mathcal{M}$-Van Kampen.
-
-Now, take the $\mathcal{M}$-pullback square
-	\[\xymatrix{P\ar[r]^{p_1}  \ar[d]_{p_2}& W_1 \ar@{>->}[d]^{k_1}\\ W_2 \ar@{>->}[r]_{k_2} & Z}\]
-	Since $k_1\circ h_1=k_2\circ h_2$, there exists a unique $g\colon X\to P$ fitting in
-	\[\xymatrix{X \ar@/^.3cm/[drr]^{h_1} \ar@{.>}[dr]^{g} \ar@/_.3cm/[ddr]_{h_2}\\ &P\ar[r]^{p_1}  \ar[d]_{p_2}& W_1 \ar@{>->}[d]^{k_1}\\ &W_2 \ar@{>->}[r]_{k_2} & Z}\]
-	We can then build the cubes
-	\[\xymatrix@C=13pt@R=13pt{&X\ar[dd]|\hole_(.65){\id{X}}\ar[rr]^{g} \ar[dl]_{\id{X}} && P \ar[dd]^{p_1} \ar[dl]_{p_2} & &X\ar[dd]|\hole_(.65){\id{X}}\ar[rr]^{g} \ar[dl]_{\id{X}} && P \ar[dd]^{p_2} \ar[dl]_{p_1}\\ X  \ar@{>->}[dd]_{m}\ar[rr]^(.65){h_2} & & W_2 \ar@{>->}[dd]_(.3){k_2}& &  X  \ar@{>->}[dd]_{m}\ar[rr]^(.65){h_1} & & W_1 \ar@{>->}[dd]_(.3){k_1}\\&X\ar[rr]|\hole^(.65){h_1} \ar@{>->}[dl]^{m} && W_1 \ar@{>->}[dl]^{k_1} & &X\ar[rr]|\hole^(.65){h_2} \ar@{>->}[dl]^{m} && W_2 \ar@{>->}[dl]^{k_2}\\Y \ar[rr]_{n} & & Z & &Y \ar[rr]_{n} & & Z}\]
-
-	Now, in both cubes the front and left faces are pullbacks, thus, by \Cref{lem:pb1}, their back face is a pullback too.
-Since $m\leq m$, \Cref{lem:varie} now entails that $k_1\leq k_2$ and $k_2\leq k_1$.
-Thus there exists an isomorphism $f\colon W_1\to W_2$ such that $k_1=k_2\circ f$.
-To see that $h_2=f\circ h_1$, we can compute:
-	\begin{align*}
-		k_2\circ f \circ h_1 & = k_1\circ h_1\\&= n\circ m\\&= k_2\circ h_2
-	\end{align*}
-	The claim now follows since $k_2$ is a monomorphism. \qedhere 
-\end{proof}
-
-\section{DPO rewriting and derivations}
+\chapter{DPO-rewriting and derivations}
 
@@
 
-\subsection{Left-linear DPO-rewriting systems}
-We are now going to study rewriting systems in $\mathcal{M}, \mathcal{N}$-adhesive categories.
+\section{Left-linear DPO-rewriting systems}
+We are now going to study rewriting systems in $\mathcal{M}$-adhesive categories.
 
 \begin{definition}[\cite{habel2012mathcal,heindel2009category}]
-	Let $\X$ be a $\mathcal{M}$-adhesive category, a  \emph{left $\mathcal{M}$-linear} rule $\rho$ is a pair $(l,r)$ of arrows with the same domain, such that $l$ belongs to $\mathcal{M}$.
+	Let $\X$ be an $\mathcal{M}$-adhesive category, a  \emph{left $\mathcal{M}$-linear} rule $\rho$ is a pair $(l,r)$ of arrows with the same domain, such that $l$ belongs to $\mathcal{M}$.
 The rule $\rho$ is said to be \emph{$\mathcal{M}$-linear} if $r\in \mathcal{M}$ too.
@@
 $(\X, \R)$ will be called \emph{linear} if every rule in $R$ is $\mathcal{M}$-linear.
+Similarly, a \emph{consuming} left-linear DPO-rewriting system is one in which every rule is consuming.
 
@@
 \begin{definition}
-	Let $(\X, \R)$ be a DPO-rewrityng system, with $\X$ $\mathcal{M}$-adhesive.
+	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ $\mathcal{M}$-adhesive.
 The \emph{DPO-derivation graph} of $(\X, \R)$ is the (large)  directed graph $\gpo$ having as vertices the objects of $\X$ and in which an edge between $G$ and $H$ is a direct derivation $\dder{D}\colon G\Mapsto H$.	A \emph{derivation} $\der{D}$ between two objects $G$ and $H$ is a path between them in $\gpo$.
@@
 \begin{remark}\label{rem:func}
-	Consider a derivation $\der{D}$ in a DPO-rewriting system $(\X, \R)$.
+	Consider a derivation $\der{D}$ in a left-linear DPO-rewriting system $(\X, \R)$.
 We can take the subcategory $\Delta(\der{D})$ of $\X$ given by the arrows appearing in $\der{D}$.
@@
 \begin{definition}
-	The \emph{DPO-derivation category} $\dpo$ of a DPO-rewriting system $(\X, \R)$ is the category in which arrows between $G$ and $H$ are given by, possibly empty, derivations.
+	The \emph{DPO-derivation category} $\dpo$ of a left-linear DPO-rewriting system $(\X, \R)$ is the category in which arrows between $G$ and $H$ are given by, possibly empty, derivations.
 Composition is concatenation of paths in $\gpo$ and identities are given by empty derivations.
@@
 		\{\phi* \dder{D}_0\}\cdot \{\dder{D}_i\}_{i=1}^{n}  & \lgh(\der{D})\neq 0
-	\end{cases}\] 
-	\[\der{D}*\psi := \begin{cases}
+	\end{cases} \qquad \der{D}*\psi := \begin{cases}
 	H' & \lgh(\der{D})=0\\ 
@@
 
+\subsection{Decorations and abstraction equivalence}
 We are often interested in an object of $\X$ only up to isomorphism.
@@
 \begin{definition}
-	Let $(\X, \R)$ be a DPO-rewriting system, a \emph{decorated derivation} between two objects $G$ and $H$ is a triple $(\der{D}, \alpha, \omega)$, where $\der{D}$ is a derivation between $G$ and $H$, and $\alpha\colon \pi(G)\to G$ and $\omega\colon \pi(H)\to H$ are isomorphisms.
+	Let $(\X, \R)$ be a left-linear DPO-rewriting system, a \emph{decorated derivation} between two objects $G$ and $H$ is a triple $(\der{D}, \alpha, \omega)$, where $\der{D}$ is a derivation between $G$ and $H$, and $\alpha\colon \pi(G)\to G$ and $\omega\colon \pi(H)\to H$ are isomorphisms.
 \end{definition}
@@
 
-\begin{definition}Let $(\X, \R)$ be a DPO-rewriting system,  an \emph{abstraction equivalence} between two derivations $\der{D}$ and $\der{D'}$ with the same length and such that $r(\der{D})=r(\der{D}')$, is a family of isomorphisms $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ such that, for every $i\in [0, \lgh(\der{D})]$ the following diagram commutes
+\begin{definition}Let $(\X, \R)$ be a left-linear DPO-rewriting system,  an \emph{abstraction equivalence} between two derivations $\der{D}$ and $\der{D'}$ with the same length and such that $r(\der{D})=r(\der{D}')$, is a family of isomorphisms $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ such that, for every $i\in [0, \lgh(\der{D})]$ the following diagram commutes
 	\[\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i} \ar[l]_{f'_i}&G'_{i+1}\\  L_i \ar[u]^{n'_i} \ar[d]_{n_i}& K_i \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar[l]_{l_i} &R\ar[u]^{h'_i} \ar[d]_{h_i}\\G_i \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole \ar[r]_{g_i}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{H_i}}}\]
@@
 
-\begin{remark}\label{rem:empty}
+\begin{example}\label{rem:empty}
 Let $(\der{D},\alpha, \omega)$ be an empty derivation from an object $G$ and  $(\der{D}',\alpha', \omega')$ a another empty one from $G'$.
-If $(\der{D},\alpha, \omega)\equiv_a(\der{D}',\alpha', \omega')$ then an abstraction equivalence between $\der(D)$ and $\der{D}'$ is just an isomorphism $\phi\colon G\to G'$, so that $\pi(G)=\pi(G')$.
+If $(\der{D},\alpha, \omega)\equiv_a(\der{D}',\alpha', \omega')$ then an abstraction equivalence between $\der{D}$ and $\der{D}'$ is just an isomorphism $\phi\colon G\to G'$, so that $\pi(G)=\pi(G')$.
 Moreover, such isomorphism must fit in the diagrams below.
@@
 \end{align*}
-\end{remark}
+\end{example}
 
@@
 To see this, in turn, it is enough to show that	the squares
-\[\xymatrix{&R_{\der{D}, n} \ar[d]_{h_{\der{D}, n}}\ar[r]^{h_{\der{D}', n}} & H' \ar[d]^{(\omega')^{-1}} &L_{\der{E}, 0} \ar[d]_{m_{\der{E}, 0}}\ar[r]^{m_{\der{E}', 0}}& E' \ar[d]^{(\beta')^{-1}}\\&H\ar[r]_{\omega^{-1}} &\pi(H)&E \ar[r]_{\beta^{-1}} & \pi(E)\\D_n \ar[rr]^{\phi_{D_n}} \ar[d]_{g_{\der{D}, n}}&&D'_n \ar[d]^{g_{\der{D}', n}}&F_0 \ar[d]_{f_{\der{E}, 0}} \ar[rr]^{\varphi_{F_0}} && F_0' \ar[d]^{f_{\der{E}', 0}}\\H \ar[r]_-{\omega^{-1}} &\pi(H)&H' \ar[l]^-{(\omega')^{-1}}  &E \ar[r]_-{\beta^{-1}} & \pi(E) & E' \ar[l]^-{(\beta')^{-1}}}\]
+\[\xymatrix{R_{\der{D}, n} \ar[d]_{h_{\der{D}, n}}\ar[r]^{h_{\der{D}', n}} & H' \ar[d]_{(\omega')^{-1}} &L_{\der{E}, 0} \ar[d]^{m_{\der{E}, 0}}\ar[r]^{m_{\der{E}', 0}}& E' \ar[d]^{(\beta')^{-1}}\\H\ar[r]_{\omega^{-1}} &\pi(H)&E \ar[r]_{\beta^{-1}} & \pi(E)}\]
+\[\xymatrix{D_n \ar[rr]^{\phi_{D_n}} \ar[d]_{g_{\der{D}, n}}&&D'_n \ar[d]_{g_{\der{D}', n}}&F_0 \ar[d]^{f_{\der{E}, 0}} \ar[rr]^{\varphi_{F_0}} && F_0' \ar[d]^{f_{\der{E}', 0}}\\H \ar[r]_-{\omega^{-1}} &\pi(H)&H' \ar[l]^-{(\omega')^{-1}}  &E \ar[r]_-{\beta^{-1}} & \pi(E) & E' \ar[l]^-{(\beta')^{-1}}}\]
 are commutative. For the first ones, we have
-	\begin{align*} 
+\[
+\begin{split} 
 	\omega^{-1} \circ h_{\der{D}, n}&=\id{\pi(H)}\circ \omega^{-1} \circ h_{\der{D}, n} \\&=(\omega')^{-1}\circ \phi_H \circ \omega \circ \omega^{-1} \circ h_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H  \circ h_{\der{D}, n}\\&=(\omega')^{-1}  \circ h_{\der{D}', n}
-\end{align*} 
-and
-\begin{align*} 
+\end{split} \qquad  	\begin{split} 
 \beta^{-1} \circ m_{\der{E}, 0}&=\id{\pi(E)}\circ \beta^{-1} \circ m_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_{E} \circ \beta \circ \beta^{-1} \circ m_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_{E}  \circ m_{\der{E}, 0}\\&=(\beta')^{-1}  \circ m_{\der{E}', 0}
-\end{align*}
-
-The commutativity of the second row of diagrams follows from
-\begin{align*}
+\end{split}  \]
+
+Similarly, the commutativity of the second row of diagrams can be deduced from
+\[\begin{split}
 \omega^{-1} \circ g_{\der{D}, n}&=\id{\pi(H)}\circ \omega^{-1} \circ g_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H \circ \omega\circ \omega^{-1} \circ g_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H  \circ g_{\der{D}, n}\\&= (\omega')^{-1} \circ g_{\der{D}', n}\circ \phi_{D_n}
-r\end{align*}
-and
-\begin{align*}
-	\beta^{-1} \circ f_{\der{E}, 0}&=\id{\pi(E)}\circ \beta^{-1} \circ f_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_E \circ \beta\circ \beta^{-1} \circ f_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_E  \circ f_{\der{E}, 0}\\&= (\beta')^{-1} \circ f_{\der{E}', n}\circ \varphi_{F_0}
-\end{align*}
+\end{split}\qquad \begin{split}\beta^{-1} \circ f_{\der{E}, 0}&=\id{\pi(E)}\circ \beta^{-1} \circ f_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_E \circ \beta\circ \beta^{-1} \circ f_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_E  \circ f_{\der{E}, 0}\\&= (\beta')^{-1} \circ f_{\der{E}', n}\circ \varphi_{F_0}
+\end{split}\]
+
  The thesis now follows.	\qedhere 
@@
 \begin{definition}
-	Let $(\X, \R)$ be a DPO-rewrityng system, with $\X$ an $\mathcal{M}$-adhesive category. The  category $\dpi$ is defined as follows:
+	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ an $\mathcal{M}$-adhesive category. The  category $\dpi$ is defined as follows:
 	\begin{itemize}
@@
 
-\subsection{Consistent permutations}
-
-Given DPO-rewriting system $(\X, \R)$,  we have already noted in \Cref{rem:func} that a derivation $\der{D}$  determines a diagram $\Delta(\der{D})$ in $\X$.
+\section{A theory of processes for left-linear DPO-rewriting systems}
+
+Given a DPO-rewriting system $(\X, \R)$,  we have already noted in \Cref{rem:func} that a derivation $\der{D}$  determines a diagram $\Delta(\der{D})$ in $\X$.
 We can then wonder if such a diagram has a colimit.
@@
 \begin{lemma}\label{lem:colim}
-	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO-rewriting system over it. The following properties hold true.
-	\begin{enumerate}
-		\item  If $\der{D}$ is a derivation from $G$ to $H$, then the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belongs to $\mathcal{M}$.
+	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO-rewriting system over it. The following properties hold true:
+	\begin{enumerate}
+		\item  for eevery derivation $\der{D}$ is a derivation from $G$ to $H$, then the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belongs to $\mathcal{M}$.
 		\item Let $\der{D}$ be the concatenation $\der{D}_1\cdot \der{D}_2$ of two derivations $\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^{n_1}$ between $G$ and $H$ and $\der{D}_2=\{\dder{D}_{2,j}\}_{j=0}^{n_2}$ between $H$ and $T$,  then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists too and there is a pushout square
@@
 		\item Let us proceed by induction on the length of $\der{D}$.
-		\begin{itemize}
-			\item  $\lgh(\dder{D})=0$. then the $\tpro{\dder{D}}$ is simply $(G, \{\id{G}\})$ and $\id{G}\in \mathcal{M}$.¸
-			\item $\lgh(\dder{D})=0$. Suppose that $\dder{D}$ has as its single component the derivation
+
+	\smallskip \noindent $\lgh(\dder{D})=0$. then the $\tpro{\dder{D}}$ is simply $(G, \{\id{G}\})$ and $\id{G}\in \mathcal{M}$.
+
+	\smallskip \noindent$\lgh(\dder{D})=1$. Suppose that $\dder{D}$ has as its single component the derivation
 			\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G& \ar@{>->}[l]^{f} D \ar[r]_{g}& H  \\}\]
@@
 			Since $p\in \mathcal{M}$, the thesis follows immediately from \Cref{rem:cof}.
-			\item $\lgh(\dder{D})\geq 2$.
+
+	\smallskip \noindent$\lgh(\dder{D})\geq 2$.
 Let $\der{D}$ be $\{\dder{D}_i\}_{i=0}^n$ with $n\geq 1$.
 Let also $\der{D}'$ be $\{\dder{D}_i\}^{n-1}_{i=0}$ and $\rho_n=(l_n, r_n)$ be the rule applied in $\dder{D}_n$.
-The pushout of $l_n$ is the arrow $f_n\colon D_n\to G_n$ is in $\mathcal{M}$ and, by inductive hypothesis, $\iota_{G_{n}}\colon G_{n}\to \lpro \der{D}'\rpro$ is in $\mathcal{M}$ too.
-Thus, we can consider the diagram below, having a pushout as its lower half.
+The arrow $f_n\colon D_n\to G_n$, being a pushout of $l_n$ is an element $\mathcal{M}$.
+By inductive hypothesis, $\iota_{G_{n}}\colon G_{n}\to \lpro \der{D}'\rpro$ is in $\mathcal{M}$ too, thus, we can consider the diagram below, having a pushout as its lower half.
 			\[\xymatrix{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar@{>->}[l]_{l_{n}} \ar[r]^{r_{n}} & R_{n} \ar[d]^{h_n} \\G_{n} \ar@{>->}[d]_{\iota'_{G_{n}}}& \ar@{>->}[l]^{f_n} D_n \ar[r]_{g_n}& H  \ar@{>->}[d]^{q}\\ \lpro \der{D}' \ar[rr]_{p}\rpro && P}\]
@@
 
-			Let $(C, \{c_X\}_{X\in \Delta(\der{D})})$ be a cocone, since $\Delta(\der{D}')$ is a subdiagram of $\Delta(\der{D})$, we get another cocone $(c, \{c_X\}_{X\in \Delta(\der{D}')})$ which induces an arrow $c'\colon \lpro \der{D}' \rpro \to C$ such that
+			Let $(C, \{c_X\}_{X\in \Delta(\der{D})})$ be a cocone, since $\Delta(\der{D}')$ is a subdiagram of $\Delta(\der{D})$, we get another cocone $(C, \{c_X\}_{X\in \Delta(\der{D}')})$ which induces an arrow $c'\colon \lpro \der{D}' \rpro \to C$ such that
 			\begin{align*}
@@
 
-	Let us now show that the square above is a pushout. Take two arrows $a\colon \tproi{D}{1}\to C$, $b\colon \tproi{D}{2}\to C$ such that
-	\[a\circ \iota_{1, H}=b\circ \iota_{2, H}\]
+	Let us now show that the square above is a pushout.
+Take two arrows $a\colon \tproi{D}{1}\to C$, $b\colon \tproi{D}{2}\to C$ such that $a\circ \iota_{1, H}=b\circ \iota_{2, H}$.
 We can use the previous equality to define a cocone $(C, \{c_X\}_{X\in \Delta(\der{D})})$ putting:
@@
 	\end{cases}\]
-From this, we can deduce at once the existence of a unique $c\colon \tpro{D}\to C$ such that 
-\[c\circ \iota_X = c_X\]
+From this, we can deduce at once the existence of a unique $c\colon \tpro{D}\to C$ such that $c\circ \iota_X = c_X$.
 By construction, for every $X\in  \Delta(\der{D}_1)$ and $Y\in  \Delta(\der{D}_2)$ we have
@@
 \end{split}\]
-Therefore
-\[c\circ p_1=a \qquad c\circ p_2 = b\]
-
-	For uniqueness, suppose that $c'\colon \tpro{D}\to C$ is such that
-	\[c'\circ p_1=a \qquad c'\circ p_2 = b\]
-Then, for every $X\in \Delta(\der{D})$ we have
+Therefore we get that $c\circ p_1=a$ and $c\circ p_2 = b$.
+
+	For uniqueness, suppose that $c'\colon \tpro{D}\to C$ is such that $c'\circ p_1=a$ and  $c'\circ p_2 = b$. Then, for every $X\in \Delta(\der{D})$ we have
 \begin{align*}
@@
 
-So equipped, we can introduce the notion of \emph{consistent permutation}.
-
-\begin{definition}[Consistent permutation]\label{def:permcon}
+\subsection{Semi-consistent and consistent permutations}
+
+Equipped with the theory developed so far, we can introduce the notions of \emph{semi-consistent} and \emph{consistent} permutation.
+
+\begin{definition}[(Semi)-consistent permutation]\label{def:permcon}
 	Let $\X$ be an $\mathcal{M}$-adhesive category and consider a left-linear DPO-rewriting system $(\X, \R)$ on it.
-Take two non-empty decorated derivations $(\der{D}, \alpha, \omega)$ and  $(\der{D}', \alpha', \omega')$ with the same length and with isomorphic sources and targets.
-
-	 	If $\der{D}=\{\dder{D}_i\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^n$ with assciated sequence of rules $r(\der{D})=\{\rho_i\}_{i=0}^n$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^n$, a \emph{consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma\colon [0,n]\to [0,n]$  such that, for every $i\in [0,n]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
-	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_\sigma}&   \pi(G_{n+1}) \ar[r]^{\omega} \ar[d]_{\omega'} & G_{n+1} \ar@{>->}[r]^{\iota_{G_{n+1}}} &\tpro{D} \ar[d]^{\xi_\sigma}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro& G'_{n+1} \ar@{>->}[rr]_{\iota'_{G'_{n+1}}} & &\lpro \der{D}' \rpro\\L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
-\end{definition}
-
-\begin{remark}
-The commutativity of the last two rectangles in \Cref{def:permcon}, is equivalent to the commutativity of the following bigger diagram.		
-\[\xymatrix@C=40pt{G_i\ar@/^1cm/[rrr]^{\iota_{G_{i}}}&D_i\ar@/^.4cm/[rr]^(.35){\iota_{D_i}} \ar[r]_{g_i} \ar@{>->}[l]^{f_i}&G_{i+1} \ar[r]_{\iota_{G_{i+1}}}&\tpro{D} \ar[dd]^{\xi_\sigma}\\  L_i \ar[u]^{n_i} \ar[d]_{n'_{\sigma(i)}}& K_i \ar[d]^{k'_{\sigma(i)}} \ar[u]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i} &R\ar[u]^{h_i} \ar[d]_{h'_{\sigma(i)}}\\G'_{\sigma(i)}\ar@/_1cm/[rrr]_{\iota'_{G'_{\sigma(i)}}} &D'_{\sigma(i)}\ar@{>->}[l]_{f'_{\sigma(i)}} \ar[r]^{g'_i} \ar@/_.4cm/[rr]_(.35){\iota'_{D'_{\sigma(i)}}}&G'_{\sigma(i)+1} \ar[r]^{\iota'_{G'_{\sigma{i}+1}}}& \lpro\der{D}' \rpro }\]
-This follows at once from the following chain of identities::
+Consider two decorated derivations $(\der{D}, \alpha, \omega)$ and  $(\der{D}', \alpha', \omega')$ with the same length $l$ and with isomorphic sources and targets.
+Let also $r(\der{D})=\{\rho_i\}_{i=0}^{l-1}$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^{l-1}$	be sequences of rules associated to the two derivations.
+
+	A \emph{semi-consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma\colon [0,l-1]\to [0,l-1]$  such that, for every $i\in [0,l-1]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
+	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_\sigma}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro}\]
+	\[\xymatrix@C=30pt{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
+
+	A semi-consistent permutation is \emph{consistent} if the following square commutes too.
+	\[\xymatrix@C=30pt{ \pi(G_{l}) \ar[r]^{\omega} \ar[d]_{\omega'} & G_{l} \ar@{>->}[r]^{\iota_{G_{l}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\  G'_{l} \ar@{>->}[rr]_{\iota'_{G'_{l}}} & &\lpro \der{D}' \rpro}\]
+\end{definition}
+
+\begin{remark}\label{rem:inversa}
+	Let $\sigma\colon [0,n]\to [0,n]$ be a consistent permutation between $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, then its inverse $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$.
+Indeed, it is enough to consider, as mediating isomorphism, the inverse $\xi^{-1}_\sigma$ of $\xi_\sigma$.
+\end{remark}
+
+\begin{example}\label{rem:empty2}
+	Let $(\{G\}, \alpha, \omega)$ and $(\{G'\}, \alpha', \omega')$ be two derivations of length $0$.
+Then $\id{\emptyset}$ is a consistent permutations between them if and only if there exists an isomorphism $\phi\colon G_0\to G'_0$ fitting in the diagrams below
+	\[\xymatrix@C=15pt{&\pi(G) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G\ar[rr]_{\phi} && G' &G \ar[rr]_{\phi} && G' } \]
+	That is, by \Cref{rem:empty} if and only if they are abstract equivalent decorated derivations.
+\end{example}
+
+\begin{remark} Notice that if $\sigma$ is a semi-consistent permutation between two derivations  $\der{D}$ and $\der{D}'$ of length $l$, then for every  $i\in [0,l-1]$ the diagram below commutes.
+	\[\xymatrix@C=40pt{G_i\ar@/^1cm/[rrr]^{\iota_{G_{i}}}&D_i\ar@/^.4cm/[rr]^(.35){\iota_{D_i}} \ar[r]_{g_i} \ar@{>->}[l]^{f_i}&G_{i+1} \ar[r]_{\iota_{G_{i+1}}}&\tpro{D} \ar[dd]^{\xi_\sigma}\\  L_i \ar[u]^{n_i} \ar[d]_{n'_{\sigma(i)}}& K_i \ar[d]^{k'_{\sigma(i)}} \ar[u]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i} &R\ar[u]^{h_i} \ar[d]_{h'_{\sigma(i)}}\\G'_{\sigma(i)}\ar@/_1cm/[rrr]_{\iota'_{G'_{\sigma(i)}}} &D'_{\sigma(i)}\ar@{>->}[l]_{f'_{\sigma(i)}} \ar[r]^{g'_i} \ar@/_.4cm/[rr]_(.35){\iota'_{D'_{\sigma(i)}}}&G'_{\sigma(i)+1} \ar[r]^{\iota'_{G'_{\sigma(i)+1}}}& \lpro\der{D}' \rpro }\]
+
+	This follows at once from the following chain of identities:
 	\begin{align*}
@@
 
-\begin{remark}\label{rem:inversa}
-Let $\sigma\colon [0,n]\to [0,n]$ be a consistent permutation between $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, then its inverse $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$.
-Indeed, it is enough to consider, as mediating isomorphism, the inverse $\xi^{-1}_\sigma$ of $\xi_\sigma$.
-\end{remark}
-
-\begin{remark}\label{rem:comp} Consistent permutations can be composed.
-Indeed, given decorated derivations $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$ all of length $n$, if $\sigma$ is a consistent permutation between the first two and $\sigma'$ one between the second and the third, then  we have diagrams
-	\[\xymatrix@C=18pt{ & G_0 \ar[rr]^{\iota_{G_0}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_{n} \ar@{>->}[rr]^{\iota_{ G_{n}}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G_0) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G'_0 \ar[rr]^{\iota'_{G'_0}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&\pi({ G_{n}})\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & { G'_{n}} \ar@{>->}[rr]^{\iota'_{{ G'_{n}}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_0  \ar[rr]_{\hat{\iota}_{\hat{G}_0}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_n \ar@{>->}[rr]_{\hat{\iota}_{\hat{G}_n}}&& \lpro \hat{\der{D}} \rpro \\& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\sigma'}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\sigma'(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\sigma'}}\\ &\hat{G}_{\sigma'(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\sigma'(\sigma(i))} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\sigma'(\sigma(i))}}}&& \lpro \hat{\der{D}} \rpro	}\]
-	We deduce at once that $\sigma'\circ \sigma$ is a consistent permutation with mediating isomorphism given by $\xi_{\sigma'} \circ \xi_\sigma$.
-\end{remark}
-
-\begin{example} RISCRIVERE Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstraction equivalent non-empty decorated derivations of length $n+1$.
-Then the identity permutation $\id{[0,n]}$ is a consistent permutation between them.
-In such a case $\xi_{\id{[0,n]}}$ is simply the isomorphism induced by any abstraction equivalence $\{\phi_X\}_{X\in \Delta(X)}$.
-
-	If $\der{D}$ and $\der{D}'$ are empty, then the converse also holds: indeed in such a case a mediating isomorphism provides the wanted abstraction equivalence.
+The previous remark allows us to prove the following.
+
+\begin{lemma}\label{prop:isouno} For every semi-consistent permutation $\sigma$ between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, the mediating isomorphism $\xi_\sigma\colon \tpro{D}\to \lpro \der{D}'\rpro$ is unique.
+\end{lemma}
+\begin{proof} Let $\xi'_\sigma$ be another mediating isomorphism, then by \Cref{rem:coproj} we have
+	\[\begin{split}
+		\xi_\sigma \circ \iota_{L_i}&=\iota'_{L_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{L_i}
+	\end{split} \qquad \begin{split}
+		\xi_\sigma \circ \iota_{K_i}&=\iota'_{K_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{K_i}
+	\end{split} \qquad \begin{split}
+		\xi_\sigma \circ \iota_{R_i}&=\iota'_{R_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{R_i}
+	\end{split}\]
+
+	Now, notice that 
+	\begin{align*}
+		\xi_\sigma \circ \iota_{G_0}&=\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}\\&=\xi'_\sigma \circ \iota_{G_0}
+	\end{align*}
+
+	If $\lgh(\der{D})=0$ this is enough to conclude, otherwise we are going to prove by induction that, for every $i\in [0, \lgh(\der{D})-1]$, $\xi_\sigma \circ \iota_{G_i}=\xi'_\sigma\circ \iota_{G_i}$.
+
+	\smallskip \noindent $i=0$. This is simply the result obtained before.
+
+	\smallskip \noindent $i >0$. If $i>0$, we know that there is a pushout square
+	\[\xymatrix{K_{i-1}\ar[r]^{r_{i-1}} \ar[d]_{k_{i-1}}& R_{i-1} \ar[d]^{h_{i-1}}\\ D_{i-1} \ar[r]_{g_{i-1}}& G_i}\] 
+	By \Cref{rem:coproj} and the induction hypothesis we know that
+	\[\begin{split}
+		\xi_\sigma \circ \iota_{G_i}\circ h_{i-1}&=  \xi_\sigma\circ \iota_{R_{i-1}}\\&=\iota'_{R_{\sigma(i-1)}}\\&=\xi'_{\sigma}\circ \iota_{R_{i-1}}\\&=\xi'_{\sigma} \circ \iota_{G_i}\circ h_{i-1}\\&
+	\end{split} \qquad
+	\begin{split}
+		\xi_\sigma \circ \iota_{G_i}\circ g_{i-1}&=\xi_{\sigma}\circ \iota_{D_{i-1}}\\&=\xi_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi'_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi'_{\sigma}\circ \iota_{D_{i-1}} \\&=\xi'_{\sigma}\circ \iota_{G_{i}} \circ g_{i-1}
+	\end{split}
+	\]
+
+	Since $\xi_\sigma \circ \iota_{D_i}$ must be $\xi_\sigma \circ \iota_{G_i}\circ f_i$, we also have
+	$\xi_\sigma \circ \iota_{D_i}=\xi'_\sigma \circ \iota_{D_i}$
+	and the thesis follows.
+\end{proof}
+
+As a next step, we will show that the existence of abstraction equivalences satisfying certain coherence conditions is enough to guarantee the (semi-)consistency of the identical permutation.
+
+\begin{proposition}\label{rem:abscons}
+	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations in an left-linear rewriting system $(\X, \R)$ of length $l$.
+Let also $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ be an abstraction equivalence between $\der{D}$ and $\der{D}'$.
+If $\alpha'\circ \phi_{G_0}=\alpha$ then the the identity $\id{[0,l-1]}$ is a semi-consistent permutation.
+If, moreover, $\omega'\circ \phi_{G_{l}}=\omega$, then $\id{[0,l-1]}$ is a consistent one.
+\end{proposition}
+\begin{proof}
+	For every $X\in \Deltamin(\der{D}) $, let $X'$ the codomain of $\phi_X$.
+Then we can define $\xi_{\id{[0,l-1]}}\colon \tpro{D}\to \lpro \der{D}'\rpro$ as the unique morphism such that, for every $X\in \Deltamin(\der{D})$,
+	\[\xi_{\id{[0,l-1]}} \circ \iota_{X}= \iota'_{X'}\circ \phi_X\]
+
+As a first step we can notice that $\xi_{\id{[0,l-1]}}$ is an isomorphism: indeed we can define $\Theta\colon \lpro\der{D}'\rpro \to \tpro{D}$ as the unique arrow satisfying, for every $X'\in \Deltamin(\der{D}')$
+\[\Theta \circ \iota'_{X'}= \iota_{X}\circ \phi^{-1}_X\]
+
+From the following two computations we can derive that $\Theta$ is the inverse of $\xi_{\id{[0,l-1]}}$.
+\[\begin{split}
+	\Theta \circ \xi_{\id{[0,l-1]}}\circ \iota_{X}&=\Theta \circ\iota'_{X'}\circ \phi_X\\&=\iota_{X}\circ \phi^{-1}_X\circ \phi_X\\&=\iota_X 
+\end{split}\qquad \begin{split}
+\xi_{\id{[0,l-1]}}\circ \Theta \circ \iota'_{X'}&=\xi_{\id{[0,l-1]}}\circ \iota_X\circ \phi^{-1}_{X}\\&=\iota'_{X'}\circ \phi_X\circ \phi^{-1}_{X}\\&=\iota'_{X'}
+\end{split}\]
+
+To conclude, let us observe that all the internal subdiagrams of the following diagrams commutes, guaranteeing the commutativity of the full ones.
+\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[dl]^{\phi_{G_0}} \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro}\]
+\[\xymatrix@C=30pt{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[dl]^{\phi_{G_i}} \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}} & R_i \ar[r]^{h_i} \ar[d]_{h'_{i}}& G_{i+1} \ar[dl]^{\phi_{G_{i+1}}}\ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}} \\G'_{i} \ar[rr]_{\iota'_{G'_{i}}}&& \lpro \der{D}' \rpro& G'_{i+1} \ar[rr]_{\iota'_{G'_{i+1}}}&& \lpro \der{D}' \rpro}\]
+
+For the last half of the thesis, we can reason similarly. Indeed, the diagram below commutes.
+\[\xymatrix@C=30pt{\pi(G_l)\ar[r]^{\omega} \ar[d]_{\omega'} & G_l \ar[dl]^{\phi_{G_l}} \ar[r]^{\iota_{G_l}} &\tpro{D} \ar[d]^{\xi_{\id{[l, l-1]}}}\\ G'_l \ar[rr]_{\iota'_{G'_l}} & &\lpro \der{D}' \rpro}\]
+This clearly entails the thesis.
+\end{proof}
+
+The previous proposition, in turn, gives us a technical but quite useful result.
+
+\begin{corollary}\label{cor:fromsemitocons}
+			Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations in an left-linear rewriting system $(\X, \R)$ of length $l$.
+Let also $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ be an abstraction equivalence between $\der{D}$ and $\der{D}'$ such that  $\alpha'\circ \phi_{G_0}=\alpha$.
+If  the identity $\id{[0,l-1]}$ is a consistent permutation, then $\omega'\circ \phi_{G_l}=\omega$, so that $(\der{D}, \alpha, \omega) \equiv_a (\der{D}', \alpha', \omega')$.
+\end{corollary}
+\begin{proof}
+	Let $\xi_{\id{[0, l-1]}}$ be the isomorphism $\tpro{D}\to \lpro\der{D}'\rpro$ witnessing the consistency of $\id{[0, l-1]}$.
+By \Cref{prop:isouno} and \Cref{rem:abscons}, we know that $\xi_{\id{[0,l-1]}} \circ \iota_{X}= \iota'_{X'}\circ \phi_X$ for every object $X\in \Deltamin(\der{D})$.
+Then we have
+	\begin{align*}
+		\iota'_{ G'_{l}}\circ \phi_{G_l}\circ \omega&=\xi_{\id{[0, l-1]}}\circ \iota_{G_l}\circ \omega\\&=\iota'_{G'_l}\circ \omega'
+	\end{align*}
+
+	By the first point of \Cref{lem:colim}, $\iota'_{ G'_{l}}$ is mono and we can conclude.
+\end{proof}
+
+\begin{remark}\label{rem:abscons2}
+	In particular, given a decorated derivation $(\der{D}, \alpha, \omega)$ with source $G$ and target $H$ and two isomorphisms, $\phi\colon G'\to G$ $\psi\colon H\to H'$ be two isomorphisms, we know, by \Cref{rem:absequi}, that \[(\der{D}, \alpha, \omega)\equiv_a (\phi*\der{D}, \phi^{-1}\circ \alpha, \omega ) \qquad (\der{D}, \alpha, \omega)\equiv_a (\der{D}*\psi, \alpha, \psi \circ \omega )\]
+	In these cases, if the cocones $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$, $(\lpro \phi *\der{D} \rpro, \{\iota'_X\}_{X\in \Delta(\phi *\der{D})})$ and $(\lpro \der{D}*\psi \rpro, \{\iota'_X\}_{X\in \Delta(\der{D}*\psi)})$ are colimiting, we can take as mediating isomorphisms, respectively, the unique arrows $\Gamma^{\phi} \colon \tpro{D}\to \lpro \phi*\der{D} \rpro$ and $\Gamma_\psi\colon \tpro{D}\to \lpro \der{D}*\psi \rpro$  such that, for every $X\in \Deltamin(\der{D})$:
+	\[\Gamma^\phi \circ \iota_X:=\begin{cases}
+		\iota'_{G'}\circ \phi^{-1}  & X=G\\
+		\iota'_X & \text{otherwise}
+	\end{cases} \qquad \Gamma_\psi \circ \iota_X:=\begin{cases}
+		\hat{\iota}_{H'}\circ \psi  & X=H\\
+		\hat{\iota}_X & \text{otherwise}
+	\end{cases}\]
+\end{remark}
+
+\begin{example}\todo{identita consistente non implica astrazione}Notice that, in general, there cannot, in general, be generalized to non-empty derivations. A counterexample is the following one.
 \end{example}
 
-\begin{example}\todo{identità consistente non implica astrazione}
-\end{example}
-
-\begin{proposition}\label{prop:uniqu}
-	Let $\sigma,\sigma'\colon [0,n]\rightrightarrows [0,n]$ be two consistent permutations between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.  Then the following hold true:
-	\begin{enumerate}
-	\item $\xi_\sigma \circ \iota_{G_0} = \xi_{\sigma'} \circ \iota_{G_0}$;
-	\item  $\xi_\sigma \circ \iota_{G_i}=\xi_{\sigma'} \circ \iota_{G_i}$ for every index $i\in [0,n]$ such that $\sigma_{|[0,i]}=\sigma'_{|[0,i]}$.
-	\end{enumerate}
+We can also observe that (semi-)consistent permutations can be composed, as shown by the next proposition.
+
+\begin{proposition}\label{rem:comp}  Let $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$ be three decorated derivations of length $l$.
+Let $\sigma$ be a consistent permutation between the first two and $\tau$ one between the second and the third, then $\tau \circ \sigma$ is a semi-consistent permutations between the first and the third.
+If, moreover, $\sigma$ and $\tau$ are consistent, then $\tau \circ \sigma$ is consistent too.
 \end{proposition}
+
+\begin{proof} Let $l$ be the length of the three given derivations.
+By hypothesis each subdiagram of the following ones commutes, thus the whole diagrams commute too, proving that $\tau\circ \sigma$ is a semi-consistent permutation with mediating isomorphism given by $\xi_{\tau} \circ \xi_\sigma$.
+		\[\xymatrix@C=18pt{ & G_0 \ar[rr]^{\iota_{G_0}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G_0) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G'_0 \ar[rr]^{\iota'_{G'_0}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\tau}}\\ &\hat{G}_0  \ar[rr]_{\hat{\iota}_{\hat{G}_0}}&& \lpro \hat{\der{D}}\rpro }\]
+		\[\xymatrix@C=18pt{& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_{i+1} \ar[rr]^{\iota_{G_{i+1}}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\tau(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\tau}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\tau(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)+1} \ar[rr]^{\iota'_{G'_{\sigma(i)+1}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\tau}}\\ &\hat{G}_{\tau(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\tau(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\tau(\sigma(i))+1} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\tau(\sigma(i))+1}}}&& \lpro \hat{\der{D}} \rpro	}\]
+
+	If, in addition, $\sigma$ and $\tau$ are consistent then we also have the commutativity of the following additional diagram.
+	\[\xymatrix@C=18pt{&   G_{l} \ar@{>->}[rr]^{\iota_{ G_{l}}} &&\tpro{D} \ar[d]^{\xi_\sigma}\\ \pi({ G_{l}})\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & { G'_{l}} \ar@{>->}[rr]^{\iota'_{{ G'_{l}}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\tau}}\\& \hat{G}_l \ar@{>->}[rr]_{\hat{\iota}_{\hat{G}_l}}&& \lpro \hat{\der{D}} \rpro}\]
+
+	Again this proves that $\xi_\tau \circ \xi_\sigma$ witnesses the constistency of $\tau\circ \sigma$.
+\end{proof}
+
+\subsubsection{Restricting  consistent permutations}
+Now that we have established some initial facts about consistent permutations, we are going to embark in a, quite long, voyage to explore how to restrict them to suitable subderivations.
+
+\begin{lemma}\label{rem:dett}
+	Let $(\der{D}, \alpha, \omega)$ be the composite $(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)$ of two derivation of length $l_1$ and $l_2$. Suppose that:
+\[r(\der{D}_1)=\{\rho_{1,i}\}_{i=0}^{l_1-1} \quad r(\der{D}_2)=\{\rho_{2,i}\}_{i=0}^{l_2-1} \quad  r(\der{D})=\{\rho_{i}\}_{i=0}^{l_1+l_2-1}\]
+and let  $G_{1,0}, G_{2,0}$ and $G_{0}$ be the sources of $\der{D}_1$, $\der{D}_2$,  and $\der{D}$.
+Similary, denote, by $G_{1,i+1}, G_{2,i+1}$ and $G_{i+1}$ the results of the application of, respectively, $\rho_{1,i}, \rho_{2,i}, \rho_i$ to $G_{1,i}, G_{2,i}$ and $G_{i}$  in the corresponding derivation.
+Then there are arrows $q_1\colon \lpro \der{D}_1\rpro \to \tpro{D}$, $q_2\colon \lpro \der{D}_2\rpro \to \tpro{D}$ such that
+\[q_1\circ \iota_{G_{1,0}}\circ \alpha_1 = \iota_{G_{0}}\circ \alpha \qquad q_2\circ \iota_{G_{2,l_2}}\circ \omega_2 = \iota_{G_{l_1+l_2}}\circ \omega \]
+and, for every $i\in [0, l_1-1]$, $j\in [l_1+1, l_1+l_2]$
+	\[q_1\circ \iota_{1, G_{1,i}}=\iota_{G_{i}}\qquad q_2\circ \iota_{2, G_{2,j}}=\iota_{G_{j+l_1}} \]
+\end{lemma}
+\begin{proof}According to \Cref{def:conc}, we have three cases.
+\begin{itemize}
+	\item $\lgh(\der{D}_1)=0$.
+Then  $(\der{D}, \alpha, \omega)$ is $(\der{D}_2, \alpha_2\circ \omega_1^{-1}\circ \alpha_1, \omega_2)$ thus we can take as $q_2$ the identity on $\lpro \der{D}_2\rpro$.
+Moreover, in this case $\iota_{1,G_{1,0}}$ is an isomorphism, so that we can take as $q_1$ the composition $\iota_{G_0}\circ \alpha_2\circ \omega^{-1}_1 \circ \iota^{-1}_{1,G_{1,0}}$.
+	\item $\lgh(\der{D}_1)\neq 0$ and $\lgh(\der{D}_2)=0$ .
+Hence  $(\der{D}, \alpha, \omega)$ is $(\der{D}_1, \alpha_1, \omega_1 \circ \alpha^{-1}_2\circ \omega_2)$.
+We can then define $q_1$ as $\id{\lpro \der{D}_1\rpro}$.
+Since $\iota_{2,G_{2,0}}$ is an isomorphism, $q_2$ can be taken as  $\iota_{G_{l_1+l_2}}\circ  \omega_1  \circ \alpha^{-1}_2 \circ \iota^{-1}_{2,G_{2,0}}$.
+	\item  $\lgh(\der{D}_1)\neq 0$ and $\lgh(\der{D}_2)\neq 0$.
+In this case we have that $(\der{D}, \alpha, \omega)$  is $(\der{D}_1*\omega_1^{-1}\cdot \alpha_2*\der{D}_2, \alpha_1, \omega_2)$.
+By second point of \Cref{lem:colim} and by \Cref{rem:abscons2} we can build the following diagram.
+	\[\xymatrix@C=40pt{&&G_{2,0}  \ar@/_.3cm/[dl]_{\alpha^{-1}_2} \ar@/^.3cm/[dr]^{\iota_{2, G_{2,0}}}\\&\pi(G_{2,0}) \ar[dr]^{\iota_{G_{l_1}}}\ar[r]^-{\iota'_{2, \pi(G_{2,0})}} \ar@{>->}[d]_-{\iota'_{1, \pi(G_{1,l_1})}} & \lpro \alpha_2*\der{D}_2 \rpro \ar@{>->}[d]^{p_2} &\tproi{D}{2} \ar[l]_-{\Gamma^{\alpha_2}} \ar@{>.>}@/^.2cm/[dl]^{q_2}\\ G_{1,l_1}  \ar@/^.3cm/[ur]^{\omega^{-1}_1}  \ar@{>->}@/_.3cm/[dr]_{\iota_{1, G_{1, l_1}}}& \lpro \der{D}_1*\omega_1^{-1} \rpro  \ar[r]_{p_1}& \tpro{D} \\ &\tproi{D}{1} \ar[u]^{\Gamma_{\omega^{-1}_1}}  \ar@{.>}@/_.2cm/[ur]_{q_1}}\]
+
+	Let us define $q_1$ as $p_1\circ \Gamma_{\omega^{-1}_1}$ and $q_2$ as $p_2\circ \Gamma^{\alpha_2}$. Then, for every $i\in [0,l_1-1]$ and $j\in [l_1+1, l_1+l_2]$
+	\[\begin{split}
+		q_1\circ \iota_{1, G_{1,i}}&=p_1\circ \Gamma_{\omega^{-1}_1}\circ \iota_{1, G_{1,i}}\\&=p_1\circ \iota'_{1, G_{1,i}} \\&=\iota_{G_{i}}
+	\end{split} \qquad \begin{split}
+		q_2\circ \iota_{2, G_{2,j}}&=p_2\circ \Gamma^{\alpha_2}\circ \iota_{2, G_{2,j}}\\&=p_2\circ \iota'_{2, G_{2,j}} \\&=\iota_{G_{j+l_1}}
+	\end{split}\]
+	Moreover, we also have:
+	\[
+	\begin{split}
+		q_1\circ \iota_{G_{1,0}}\circ \alpha_1&= p_1\circ \Gamma_{\omega^{-1}_1}\circ \iota_{G_{1,0}}\circ \alpha_1 \\&=p_1\circ \iota'_{1, G_{1,0}} \circ \alpha_1 \\&= \iota_{G_{0}}\circ \alpha
+	\end{split}\qquad 
+	\begin{split}
+	q_2\circ \iota_{G_{2,l_2}}\circ \omega_2&= p_2\circ \Gamma^{\alpha_2}\circ \iota_{G_{2,l_2}}\circ \omega_2 \\&=p_2\circ \iota'_{1, G_{2,l_2}} \circ \omega_2 \\&= \iota_{G_{l_1+l_2}}\circ \omega
+	\end{split} \]
+
+	This concludes the proof. \qedhere
+\end{itemize}	
+\end{proof}
+
+\begin{remark}\label{rem:dett2}
+It is worth noticing that, for every $i\in [0,l_1-1]$ and $j\in [l_1+1, l_1+l_2]$ the previous equalities also entail that,
+\[\begin{split}q_1\circ \iota_{1, D_{1,i}}&=\iota_{D_{i}}\\q_2\circ \iota_{2, D_{2,j}}&=\iota_{D_{j+l_1}} 	\\q_1\circ \iota_{1, R_{1,i-1}}&=\iota_{R_{i-1}} \\
+	q_2\circ \iota_{2, R_{2,j-1}}&=\iota_{R_{j+l_1-1}}
+\end{split} \qquad 
+\begin{split}    	q_1\circ \iota_{1, L_{1,i}}&=\iota_{L_{i}} \\q_2\circ \iota_{2, L_{2,j}}&=\iota_{L_{j+l_1}}\\ q_1\circ \iota_{1, K_{1,i}}&=\iota_{K_{i}}\\q_2\circ \iota_{2, K_{2,j}}&=\iota_{K_{j+l_1}}\end{split}\]
+\end{remark}
+
+We can now turn our attention to the case in which a consistent permutation between two composite derivations is given.
+
+\begin{lemma}[Restriction Lemma]\label{prop:uniqu}
+	Let $\sigma\colon [0,n]\to [0,n]$ be a consistent permutations between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ and suppose that 
+	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1) \cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1) \cdot (\der{D}'_2, \alpha'_2, \omega'_2) \]
+
+	 Let $l_1$ be the length of $\der{D}_1$, and suppose that there exists a consistent permutation $\tau:[0,l_1-1]\to [0, l_1-1]$.
+If $q_1\colon \lpro \der{D}_1\rpro \to \lpro \der{D}\rpro$  and $q'_1\colon \lpro \der{D}'_1\rpro \to \lpro \der{D}'\rpro$ are the canonical arrows defined in \Cref{rem:dett}, then the following hold true:
+	\begin{enumerate}
+	\item  if $l_1=0$, then the following diagram commutes:
+		\[\xymatrix{\lpro \der{D}_1\rpro \ar[r]^{\xi_\tau} \ar[d]_{q_1}& \lpro \der{D}'_1 \ar[d]^{q'_1}\rpro\\ \lpro \der{D}\rpro \ar[r]_{\xi_\sigma} & \lpro \der{D}'\rpro } \]
+	%\[\xi_\sigma \circ q_1 \circ \iota_{1, G_{1,0}} = q'_1\circ \xi_{\tau} \circ  \iota_{1, G_{1,0}}\]
+	\item if $l_1\neq 0$, so that $G_{1,0}=G_0$, then $\xi_\sigma \circ \iota_{G_0} = q'_1\circ \xi_{\tau} \circ  \iota_{1, G_{1,0}}$.
+	\end{enumerate}
+
+	Moreover, define the set $E_{\sigma, \tau}$ as
+	\[E_{\sigma, \tau}:=\{i\in  [0, l_1-1] \mid \sigma(j)=\tau(j) \text{ for every } j \leq i \}\]
+	then also the following hold true:
+	\begin{enumerate}
+		\setcounter{enumi}{2}
+	\item  if $E_{\sigma, \tau}\neq \emptyset$,  for every index $i\in [0, \max(E_{\sigma, \tau})]$ we have 
+	$\xi_\sigma \circ \iota_{G_i}=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_i}$;
+	\item if $l_1-1\in E_{\sigma, \tau}$ and $l_2=0$ so that  $G_{l_1}=G_{1, l_1}$, then 
+	$\xi_\sigma \circ \iota_{G_{l_1}}=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}$;
+	\item if $l_1-1\in E_{\sigma, \tau}$ and $l_2\neq 0$, so that $G_{l_1}=\pi(G_{2,0})$, then 
+	$\xi_\sigma \circ \iota_{G_{l_1}}=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ \omega_1$;
+	\item if $l_1-1\in E_{\sigma, \tau}$, then the following diagram commutes:
+	\[\xymatrix{\lpro \der{D}_1\rpro \ar[r]^{\xi_\tau} \ar[d]_{q_1}& \lpro \der{D}'_1 \ar[d]^{q'_1}\rpro\\ \lpro \der{D}\rpro \ar[r]_{\xi_\sigma} & \lpro \der{D}'\rpro } \]
+	\end{enumerate}
+\end{lemma}
 \begin{proof}\begin{enumerate}
-		\item This follows at once noticing that both $\xi_\sigma \circ \iota_{G_0}$ and $\xi_{\sigma'} \circ \iota_{G_0}$ are equal to $\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}$.
-		\item  If $\sigma(0)\neq \sigma'(0)$ there is nothing to show. Otherwise, let $j$ be the maximum of the set
-		\[\{i\in [0,n]\mid \sigma_{|[0,i]}=\sigma'_{|[0,i]}\}\]
-		We proceed by induction on $i\in [0,j]$. 
-		\begin{itemize}
-			\item If $i=0$ the thesis follows from point $1$.
-			\item If $i>0$, we know that there is a pushout square
+		\item Recall that, in this case \[q_1=\iota_{G_0}\circ \alpha_2\circ \omega^{-1}_1 \circ \iota^{-1}_{1,G_{1,0}} \qquad q'_1=\iota'_{G'_0}\circ \alpha'_2\circ (\omega'_1)^{-1} \circ (\iota'_{1,G'_{1,0}})^{-1}\]
+
+		If we compute we have
+		\begin{align*}
+	\xi_\sigma \circ q_1 &=\xi_\sigma \circ \iota_{G_0}\circ \alpha_2\circ \omega^{-1}_1 \circ \iota^{-1}_{1,G_{1,0}} \\&=\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}\circ \alpha_2\circ \omega^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}
+		\end{align*}
+		Now, since $l_1=0$ we also have that 
+		\[\alpha=\alpha_2\circ \omega_1^{-1}\circ \alpha_1 \qquad \alpha'=\alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1\]
+
+		Therefore, using \Cref{rem:empty}, we get:
+		\begin{align*}
+	\alpha'\circ \alpha^{-1}&=\alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1\circ \alpha^{-1}_1\circ \omega_1\circ \alpha^{-1}_2\\&=\alpha'_2\circ (\omega'_1)^{-1}\circ \omega'_1\circ \omega^{-1}_1\circ \omega_1\circ \alpha^{-1}_2\\&=\alpha'_2\circ \alpha^{-1}_2
+		\end{align*}
+	Hence, again by \Cref{rem:empty} we obtain:
+				\begin{align*}
+			\xi_\sigma \circ q_1 &=\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}\circ \alpha_2\circ \omega^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=\iota'_{G'_0}\circ \alpha'_2\circ \alpha^{-1}_2\circ \alpha_2\circ \omega^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=\iota'_{G'_0}\circ \alpha'_2\circ \omega^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=\iota'_{G'_0}\circ \alpha'_2\circ (\omega'_1)^{-1} \circ  \omega'_1\circ \omega^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=\iota'_{G_0}\circ \alpha'_2\circ (\omega'_1)^{-1} \circ \alpha'_1\circ \alpha^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=\iota'_{G'_0}\circ \alpha'_2\circ (\omega'_1)^{-1} \circ (\iota'_{1,G_{1,0}})^{-1}\circ \iota'_{1,G'_{1,0}}\circ \alpha'_1\circ \alpha^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=q'_1\circ \iota'_{1,G'_{1,0}}\circ \alpha'_1\circ \alpha^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=q'_1\circ \xi_{\tau}
+		\end{align*}
+
+		\item We can start noticing that
+		\[\xi_\sigma \circ \iota_{G_0}=\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1} \qquad \xi_{\tau} \circ \iota_{1,G_{1,0}}= \iota'_{1, G'_{1,0}} \circ \alpha'_1\circ \alpha^{-1}_1\] 
+		Therefore:
+		\begin{align*}
+		q'_1\circ \xi_{\tau} \circ \iota_{1, G_{1,0}}&=q'_1 \circ \iota'_{1, G'_{1,0}} \circ \alpha'_1\circ \alpha^{-1}_1\\ &= \iota'_{G'_{0}}\circ \alpha' \circ \alpha^{-1}_1
+		\end{align*}
+		By hypothesis $\lgh(\der{D}_1) \neq 0$, thus $\alpha_1=\alpha$ and we can conclude.
+
+		\item  From $E_{\sigma, \tau}\neq \emptyset$ we deduce that $l_1\neq 0$ and that $0\in E_{\sigma, \tau}$.   We proceed by induction on $i\in [0,\max(E_{\sigma, \tau})]$.
+
+\smallskip \noindent  If $i=0$ the thesis follows from point $1$.
+
+\smallskip \noindent If $i>0$, we proceed as in the proof of \Cref{prop:isouno} considering the pushout square
 			\[\xymatrix{K_{i-1}\ar[r]^{r_{i-1}} \ar[d]_{k_{i-1}}& R_{i-1} \ar[d]^{h_{i-1}}\\ D_{i-1} \ar[r]_{g_{i-1}}& G_i}\] 
-			By \Cref{rem:coproj} we know that
-			\begin{align*}
-				\xi_\sigma \circ \iota_{G_i}\circ h_{i-1}&=  \xi_\sigma\circ \iota_{R_{i-1}}\\&=\iota'_{R_{\sigma(i-1)}}\\&=\iota'_{R_{\sigma'(i-1)}}\\&=\xi_{\sigma'}\circ \iota_{R_{i-1}}\\&=\xi_{\sigma'} \circ \iota_{G_i}\circ h_{i-1}
-			\end{align*}
-			But, by the induction hypothesis we also have
-			\begin{align*}
-				\xi_\sigma \circ \iota_{G_i}\circ g_{i-1}&=\xi_{\sigma}\circ \iota_{D_{i-1}}\\&=\xi_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi_{\sigma'}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi_{\sigma'}\circ \iota_{D_{i-1}} \\&=\xi_{\sigma'}\circ \iota_{G_{i}} \circ g_{i-1}
-			\end{align*}
-			The thesis now follows.			\qedhere
-		\end{itemize}
-	\end{enumerate}
-\end{proof}
-
-Now, notice that, given a consistent permutation $\sigma\colon [0,n]\to[0,n]$, we already know, by \Cref{rem:coproj} that
-\[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
-	Moreover, $\xi_\sigma \circ \iota_{D_i}$ must be $\xi_\sigma \circ \iota_{G_i}\circ f_i$.
-Thus $\xi_\sigma$ is uniquely determined by $\xi_{\sigma} \circ \iota_{G_i}$ for every $i\in [0, n]$.
-In particular,  \Cref{prop:uniqu} entails the following.
-\begin{corollary} For every consistent permutation $\sigma$ between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, the mediating isomorphism $\xi_\sigma\colon \tpro{D}\to \lpro \der{D}'\rpro$ is unique.
-\end{corollary}
-
-We are now ready to prove the central result of this section.
-
-\begin{lemma} Let $(\X,R)$ be a left-linear DPO-rewriting system.
-Consider two consistent permutation $\sigma,\sigma'\colon [0,n]\rightrightarrows [0,n]$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
-Suppose that $\sigma\neq \sigma'$ and let $j$ be the minimum index such that $\sigma(j)\neq \sigma'(j)$.
-Let also $r(\der{D})$ be $\{\rho_i\}_{i=0}^n$.
-Then the following hold true:
+		Since $i$ belongs to $E_{\sigma, \tau}$, then $i-1\in E_{\sigma, \tau}$ too. By definition, $i\leq l_1-1$, so that, using \Cref{rem:coproj}, \Cref{rem:dett} and the induction hypothesis we have
+			\[\begin{split}
+				\xi_\sigma \circ \iota_{G_i}\circ h_{i-1}&=  \xi_\sigma\circ \iota_{R_{i-1}}\\&=\iota'_{R'_{\sigma(i-1)}}\\&=\iota'_{R'_{\tau(i-1)}}\\&=q'_1\circ \iota'_{1, R'_{1,\tau(i-1)}}\\&=q'_1\circ \xi_{\tau}\circ \iota_{1, R_{i-1}}\\&=q'_1\circ \xi_{\tau} \circ \iota_{1, G_{1,i}}\circ h_{1, i-1}\\&=q'_1\circ \xi_\tau \circ \iota_{1, G_i} \circ h_{i-1}
+			\end{split} \qquad  \begin{split}
+			\xi_\sigma \circ \iota_{G_i}\circ g_{i-1}&=\xi_{\sigma}\circ \iota_{D_{i-1}}\\&=\xi_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{i-1}} \circ f_{i-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{i-1}} \circ f_{1, i-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, D_{i-1}}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_i}\circ g_{1, i-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_i}\circ g_{i-1}
+			\end{split}\]
+
+	From which the thesis follows.
+
+			\item Since $l_1-1\in E_{\sigma, \tau}$ we have $l_1\neq 0$ and $E_{\sigma, \tau}=[0,l_1-1]$.  We can start with the pushout
+			\[\xymatrix{K_{l_1-1}\ar[r]^{r_{l_1-1}} \ar[d]_{k_{l_1-1}}& R_{i-1} \ar[d]^{h_{l_1-1}}\\ D_{l_1-1} \ar[r]_{g_{l_1-1}}& G_{l_1}}\] 
+			By \Cref{def:conc}, we have $h_{l_1-1}=h_{1, l_1}$ and $g_{l_1-1}=g_{1,l_1}$.
+Since $q'_1=\id{\lpro \der{D}'_1\rpro}$ these two equalities imply that $	\iota'_{R_{\tau(l_1-1)}}=q'_1\circ \iota'_{1, R'_{1,\tau(l_1-1)}}$.
+
+			Moreover, by hypothesis $l_1-1\in E_{\sigma, \tau}$, so that point $3$ of this lemma entails that
+			\[\xi_\sigma \circ \iota_{G_{l_1-1}}=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1-1}}\]
+
+			We can thus repeat the same argument of the previous point:
+			\[\begin{split}
+				\xi_\sigma \circ \iota_{G_{l_1}}\circ h_{l_1-1}&=  \xi_\sigma\circ \iota_{R_{l_1-1}}\\&=\iota'_{R'_{\sigma(l_1-1)}}\\&=\iota'_{R'_{\tau(l_1-1)}}\\&=q'_1\circ \iota'_{1, R'_{1,\tau(l_1-1)}}\\&=q'_1\circ \xi_{\tau}\circ \iota_{1, R_{l_1-1}}\\&=q'_1\circ \xi_{\tau} \circ \iota_{1, G_{1,l_1}}\circ h_{1, l_1-1}\\&=q'_1\circ \xi_\tau \circ \iota_{1, G_{l_1}} \circ h_{l_1-1}			\end{split}
+			\qquad  \begin{split}
+				\xi_\sigma \circ \iota_{G_{l_1}}\circ g_{l_1-1}&=\xi_{\sigma}\circ \iota_{D_{l_1-1}}\\&=\xi_{\sigma}\circ \iota_{G_{l_1-1}} \circ f_{l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1-1}} \circ f_{l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}-1} \circ f_{1, l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, D_{l_1-1}}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ g_{1, l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ g_{l_1-1}
+			\end{split}\]
+
+		And again this implies the thesis.
+
+			\item In this case, we can consider the following diagram, in which the inner rectangle and the outer border are pushouts
+		\[\xymatrix@C=35pt{K_{1,l_1-1}\ar[r]^{r_{1,l_1-1}} \ar[d]_{k_{1,l_1-1}}& R_{i-1} \ar[d]_{h_{1,l_1-1}} \ar@/^.3cm/[ddr]^{h_{l_1-1}}\\ D_{1,l_1-1} \ar[r]_{g_{1,l_1-1}} \ar@/_.3cm/[drr]_{g_{l_1-1}}& G_{1,l_1} \ar[dr]^{\omega_1^{-1}}\\ &&\pi(G_{2,0})}\]
+
+		\iffalse 
+	\[	\xi_\sigma \circ \iota_{G_{l_1}}=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ \omega_1\]
+	\fi 
+		We can start noticing that, by the proof of  the third point of \Cref{rem:dett}, we know that  $q'_1\circ \iota'_{1, G'_{1,l_1}}=\iota'_{G'_{l_1}} \circ \omega_1^{-1}$. Therefore
+		\begin{align*}q'_1\circ \iota'_{1, R'_{1,l_1}}&=q'_1\circ \iota'_{1, G'_{1,l_1}}\circ  h'_{1, l_1}\\&=q'_1\circ \iota'_{1, G'_{1,l_1}}\circ \omega_1 \circ  h'_{ l_1}\\&= \iota'_{G'_{l_1}}\circ h'_{l_1}\\&=\iota'_{R'_{l_1-1}}
+		\end{align*}
+
+		The argument now proceeds almost verbatim like the one of the previous two point. Indeed, using the third point of this lemma we get:
+		\[\begin{split}
+			\xi_\sigma \circ \iota_{G_{l_1}}\circ h_{l_1-1}&=  \xi_\sigma\circ \iota_{R_{l_1-1}}\\&=\iota'_{R'_{\sigma(l_1-1)}}\\&=\iota'_{R'_{\tau(l_1-1)}}\\&=q'_1\circ \iota'_{1, R'_{1,\tau(l_1-1)}}\\&=q'_1\circ \xi_{\tau}\circ \iota_{1, R_{l_1-1}}\\&=q'_1\circ \xi_{\tau} \circ \iota_{1, G_{1,l_1}}\circ h_{1, l_1-1}\\&=q'_1\circ \xi_\tau \circ \iota_{1, G_{1, l_1}} \circ \omega_1 \circ  h_{l_1-1}			\end{split}  \qquad  		\begin{split}
+			\xi_\sigma \circ \iota_{G_{l_1}}\circ g_{l_1-1}&=\xi_{\sigma}\circ \iota_{D_{l_1-1}}\\&=\xi_{\sigma}\circ \iota_{G_{l_1-1}} \circ f_{l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}} \circ f_{l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}} \circ f_{1, {l_1}-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, D_{{l_1}-1}}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ g_{1, l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ \omega_1\circ g_{l_1-1}
+			\end{split}\]
+
+			\item  The thesis follows from points $3$ and $4$ if $l_2=0$, from $3$ and $5$ if $l_2\neq 0$.	\qedhere
+	\end{enumerate}
+\end{proof}
+
+We are now ready to prove the central result of this section: the uniqueness of a consistency permutation between two decorated derivations in a consuming rewriting system.
+
+\begin{lemma}\label{lem:impo}
+	Let $(\X,R)$ be a left-linear DPO-rewriting system and let also $(\der{D}_1, \alpha_1, \omega_1)$, $(\der{D}_2, \alpha_2, \omega_2)$ be two composable decorated derivations of length, respectively, $l_1$ and $l_2$.
+Suppose that $\sigma:[0, l_1+l_2-1]\to [0, l_1+l_2-1]$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)$ for some other two composable decorated derivations $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}_2, \alpha_2, \omega_2)$.
+If $\tau:[0,l_1-1]\to [0, l_1-1]$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$.
+Suppose that  the set
+	\[D_{\sigma, \tau}:=\{i\in [0, l_1-1]\mid \sigma(i)\neq \tau(i)\}\]
+	is non-empty and let $j$ be its minimum. Let also $r(\der{D}_1)$ be $\{\rho_i\}_{i=0}^{l_1-1}$. Then the following hold true:
 	\begin{enumerate}
@@
 \end{lemma}
-\begin{proof}\begin{enumerate}
-		\item Let $k$ be $\sigma^{-1}(\sigma'(0))$ and notice that, since $\sigma(0)\neq \sigma'(0)$, then $0< k$.  By  the first point of  \Cref{prop:uniqu} we can consider the diagram
-		\[\xymatrix@C=40pt{& L_0 \ar[d]_{m'_{\sigma'(0)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{0}} \\G_{0} \ar@/_.2cm/[drr]_(.3){\iota_{G_0}}|(.515)\hole \ar[d]_{\iota_{G_0}}& G'_{\sigma'(0)} \ar[d]^{\iota_{G'_{\sigma'(0)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\sigma'}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
+\begin{remark}\label{rem:minmax}It is worth to notice that the hypothesis $D_{\sigma, \tau} \neq \emptyset$ entails $l_1\neq 0$.
+Moreover, if $j\neq 0$, then $j-1$ is the maximum of $E_{\sigma, \tau}$.
+\end{remark}
+\begin{proof}
+	\begin{enumerate}
+		\item Let $k$ be $\sigma^{-1}(\tau(0))$ and notice that, since $\sigma(0)\neq \tau(0)$, then $0< k$.  By  the second point of  \Cref{prop:uniqu} we can consider the diagram
+		\[\xymatrix@C=40pt{G_{0} \ar[drrr]_(.4){\iota_{G_0}}|(.675)\hole \ar[d]_{\iota_{1,G_{1,0}}}& L_0 \ar[r]_{m'_{\tau(0)}} \ar@/^.4cm/[rr]^{m_{k}} \ar[l]_{m_{0}} &G'_{\tau(0)} \ar[d]^(.45){\iota'_{G'_{\tau(0)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \lpro\der{D}_1 \rpro \ar[r]_{\xi_{\tau}} &\lpro \der{D}'_1\rpro \ar[r]_{q'_1} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
 		From \Cref{cor:ele}, we can conclude that there exists $c\colon L_0\to D_0$ such that $f_0\circ c=m_0$. We thus have the solid part of the commutative diagram below.
@@
 The thesis now follows from \Cref{cor:rego}.
-		\item  Let $k$ be $\sigma^{-1}(\sigma'(j-1))$ and notice that $\rho_{j-1}=\rho_k$.
-By definition of $j$, $\sigma_{|[0,j-1]}=\sigma'_{|[0,j-1]}$, thus the second point of \Cref{prop:unique} yields the diagram
-			\[\xymatrix@C=40pt{& L_{j-1} \ar[d]_{m'_{\sigma'(j-1)}} \ar@/^.2cm/[dr]^{m_{k}} \ar@/_.2cm/[dl]_{m_{j-1}} \\G_{j-1} \ar@/_.2cm/[drr]_(.3){\iota_{G_{j-1}}}|(.515)\hole \ar[d]_{\iota_{G_{j-1}}}& G'_{\sigma'(j-1)} \ar[d]^{\iota_{G'_{\sigma'(j-1)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \tpro{D} \ar[r]_{\xi_{\sigma'}} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
-			Let $a$ be $\min(j-1, k)$, by \Cref{cor:ele},  there exists $c\colon L_{j-1}\to D_a$ such that $f_a\circ c=m_a$. As before this yields the solid part of the following diagram
+		\item  Let $k$ be $\sigma^{-1}(\tau(j-1))$ and notice that $\rho_{j-1}=\rho_k$.
+We have already noticed in \Cref{rem:minmax} that $j-1$ is the maximum of $E_{\sigma, \tau}$.
+Hence, by the third point of \Cref{prop:uniqu} we have
+		\[\xymatrix@C=40pt{G_{1,{j-1}} \ar[drrr]_(.4){\iota_{G_{j-1}}}|(.675)\hole \ar[d]_{\iota_{1,G_{1,j-1}}}& L_{j-1} \ar[r]_{m'_{\tau({j-1})}} \ar@/^.4cm/[rr]^{m_{k}} \ar[l]_{m_{{j-1}}} &G'_{\tau({j-1})} \ar[d]^{\iota'_{G'_{\tau({j-1})}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \lpro\der{D}_1 \rpro \ar[r]_{\xi_{\tau}} &\lpro \der{D}'_1\rpro \ar[r]_{q'_1} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
+		Let $a$ be $\min(j-1, k)$, by \Cref{cor:ele},  there exists $c\colon L_{j-1}\to D_a$ such that $f_a\circ c=m_a$.
+As before this yields the solid part of the following diagram, in which the square is an $\mathcal{M}$-pushout.
 		\[\xymatrix{L_{j-1} \ar@/^.3cm/[drr]^{\id{L_{j-1}}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_{j-1} \ar[d]_{k_a}\ar@{>->}[r]^{l_{j-1}}& L_{j-1} \ar[d]^{m_a} \\& D_a \ar@{>->}[r]_{f_a} & G_a} \]
@@
 \begin{corollary}[Uniqueness of consistent permutation]\label{cor:unique}
-Let $(\X,R)$ ba left-linear DPO-rewriting system and suppose that every rule in $R$ is consuming.
-For every two non-empty decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, there exists at most one consistent permutation between them.
+Let $(\X,\R)$ be a consuming left-linear DPO-rewriting system.
+Then, for every two decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, there exists at most one consistent permutation between them.
 \end{corollary}
-
-We end this section proving two rather technical result about consistent permutations between composite decorated derivations.
-
-\begin{proposition}\label{prop:sum} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstract decorated derivations such that
+\begin{proof}
+Let $\sigma, \tau: [0, \lgh(\der{D})-1]\rightrightarrows [0, \lgh(\der{D})-1]$ be two consistent permutations.
+Let $H$  and $H'$ be, respectively, the target of $\der{D}$ and $\der{D}'$.
+Take two isomorphisms $\gamma:\pi(H)\to \gamma$, $\gamma':\pi(H')\to H'$, then, according to \Cref{def:conc}:
+\begin{align*}(\der{D}, \alpha, \omega)&=(\der{D}, \alpha, \omega)\cdot (\der{D}_2, \gamma, \gamma) \\(\der{D}', \alpha', \omega')&=(\der{D}', \alpha', \omega')\cdot (\der{D}'_2, \gamma', \gamma') 
+\end{align*} 
+where $\der{D}_2$ and $\der{D}'_2$ are the empty derivation on $H$ and $H'$. Since $(\X, \R)$ is consuming, then \Cref{lem:impo} entails $D_{\sigma, \tau}=\emptyset$, from which the thesis follows.
+\end{proof}
+
+\begin{lemma}[Corestriction Lemma]\label{lem:presuffix} Let $(\X, \R)$ be a consuming left-linear DPO-rewriting system.
+Let also $(\der{D}_1, \alpha_1, \omega_1)$, $(\der{D}_2, \alpha_2, \omega_2)$ be two composable decorated derivations of length, respectively, $l_1$ and $l_2$.
+Suppose that $\sigma\colon [0, l_1+l_2-1]\to [0, l_1+l_2-1]$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)$ for some other two composable decorated derivations $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}_2, \alpha_2, \omega_2)$.
+If $\tau\colon [0,l_1-1]\to [0, l_1-1]$ is a consistent permutation between $(\der{D_1}, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$.
+Then the following hold true:
+	\begin{enumerate}
+		\item suppose that $l_1$ and $l_2$ are different from $0$ and consider the following two pushout squares given by \Cref{rem:dett}:
+		\[\xymatrix@C=45pt@R=30pt{\pi(G_{2,0}) \ar@{>->}[d]_{\iota_{1, G_{1,n+1}} \circ \omega_1}\ar[r]^{\iota_{2, G_{2,0}} \circ \alpha_2}& \lpro \der{D}_2 \rpro \ar@{>->}[d]^{q_2} &  \pi(G'_{2,0}) \ar@{>->}[d]_{\iota'_{1, G'_{1,n+1}} \circ \omega'_1} \ar[r]^{\iota'_{2, G'_{2,0}} \circ \alpha'_2}& \lpro \der{D}'_2 \rpro \ar@{>->}[d]^{q'_2} \\ \lpro \der{D}_1 \rpro  \ar[r]_{q_1} & \tpro{D} & \lpro \der{D}'_1\rpro \ar[r]_{q'_1} & \lpro \der{D}'\rpro  }\]
+		then, for every $i\in [0, l_2]$ there exists a unique $\zeta_i\colon G_{2,i}\to \lpro \der{D}_2\rpro $ fitting in the diagram below
+		\[\xymatrix@R=35pt{G_{2,i} \ar[r]^{\iota_{2,G_{2,i}}} \ar@{.>}[d]_{\zeta_i}&\lpro \der{D}_2 \rpro \ar@{>->}[r]^{q_2}& \tpro{D} \ar[d]^{\xi_{\sigma}} \\
+			\lpro \der{D}'_2 \rpro \ar@{>->}[rr]_{q'_2}&& \lpro \der{D}'\rpro }\]
+		\item the permutation
+		\[\varrho\colon [0,l_2-1]\to [0, l_2-1] \qquad i \mapsto \sigma(i+l_1)-l_1\]
+		is a consistent one.
+	\end{enumerate}
+\end{lemma}
+\begin{proof}\begin{enumerate}
+		\item We can start noticing that  by \Cref{lem:impo}, $\sigma(i)=\tau(i)$ for every $i\in  [0, l_1-1]$. By the second point of \Cref{prop:uniqu} we can deduce that
+		\[\xi_\sigma \circ \iota_{G_{i}}=\]Let us prove the existence of $\zeta_i$ by induction on $i\in [0, l_2]$.
+
+		\smallskip \noindent $i=0$. We already know that $G_{l_1}$ and $G'_{l_1}$ are both equal to $\pi(G_{2,0})$.  Moreover, we also know that
+		\begin{align*}
+		q_2\circ \iota_{2, G_{2,0}}=\iota_{G_{l_1}} \circ \alpha^{-1}_2 \qquad
+		\end{align*}
+
+		Thus we have a diagram
+		\[\xymatrix{&G_{2,0} \\
+		G_{l_1} \\
+		G'_{2,0}&}\]
+
+	Moreover, $\pi(mj$
+		\begin{align*}
+			\xi_\sigma \circ p_2\circ \iota_{2, G_{2,0}}&=\xi_\sigma \circ \iota_{G_{n+1}}\circ \alpha^{-1}_2\\&g
+		\end{align*}
+
+		\smallskip \noindent $i>0$.
+
+		The uniqueness half of the thesis follows at once since $p'_2$ is in $\mathcal{M}$.
+
+		\item Let us split the cases.
+
+		\smallskip \noindent $l_1=0$. then $\varrho=\sigma$ and there is nothing to proof.
+
+		\smallskip \noindent $l_2=0$ and $l_1\neq0$. Then $\varrho=\id{\emptyset}$ and
+
+		\smallskip \noindent $l_1\neq0$ and $l_2\neq 0$. 
+		\[\xymatrix{xy code}\]
+
+		Consistency now follows at once. \qedhere 
+	\end{enumerate}
+\end{proof}
+
+Finally, we  end this section showing that consistent permutations between composable abstract derivations yield a consistent permutation between the composites.
+
+\begin{lemma}\label{lem:sum} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstract decorated derivations such that
 	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)\]
-	If $\sigma\colon [0, \lgh(\der{D}_1)-1]\to [0, \lgh(\der{D}_1)-1]$ is a consistent permutation between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$ and $\tau:[0, \lgh(\der{D}_2)-1]\to [0, \lgh(\der{D}_2)-1]$ one between $(\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$, then
-	\[\sigma+\tau\colon[0, \lgh(\der{D})-1]\to[0, \lgh(\der{D})-1] \qquad n \mapsto \begin{cases}
-		\sigma(n) & n < \lgh(\der{D}_1)\\
-		\tau(n-\lgh(\der{D}_1)) &   \lgh(\der{D}_1) \leq n
+	Given a consistent permutation $\sigma\colon [0, \lgh(\der{D}_1)-1]\to [0, \lgh(\der{D}_1)-1]$ between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$ and another $\tau\colon [0, \lgh(\der{D}_2)-1]\to [0, \lgh(\der{D}_2)-1]$ between $(\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$, then
+	\[\sigma+\tau\colon[0, \lgh(\der{D})-1]\to[0, \lgh(\der{D})-1] \quad i \mapsto \begin{cases}
+		\sigma(i) & i < \lgh(\der{D}_1)\\
+		\lgh(\der{D}_1)+\tau(i-\lgh(\der{D}_1)) &   i\geq \lgh(\der{D}_1) 
 	\end{cases}\]
 	is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
-\end{proposition}
-\begin{proof}
-	Let us start fixing some notation.
+\end{lemma}
+
+\begin{notation}
 Given $X_1\in \Delta(\der{D}_1)$, $X_2\in \Delta(\der{D}_2)$, $X'_1\in \Delta(\der{D}'_1)$, $X'_2\in \Delta(\der{D}'_2)$, we will denote their coprojections into, respectively, $\lpro \der{D}_1\rpro$, $\lpro \der{D}'_2\rpro$, $\lpro \der{D}'_1\rpro$, $\lpro \der{D}'_2\rpro$ by
 $\iota_{1, X_1}\colon X_1\to \lpro\der{D}_1\rpro$, $\iota_{1, X_2}\colon X_2\to \lpro\der{D}_1\rpro$, $\iota'_{1, X'_1}\colon X'_1\to \lpro\der{D}'_1\rpro$ and $\iota'_{2, X'_2}\colon X'_2\to \lpro\der{D}_1\rpro$.
-
-	Now that these preliminaries matters have been addressed, we will proceed with the rest of the proof.. We split the proof in three cases.
+Similarly, given $X\in \Delta(\der{D})$ and $X'\in \Delta(\der{D}')$ we will use $\iota_X\colon X\to \tpro{D}$ and $\iota'_{X'}\colon X'\to \lpro \der{D}' \rpro$ for the coprojections.
+\end{notation}
+
+\begin{proof}
+We split the proof in three cases, according to \Cref{def:conc}.
 	\begin{itemize}
 	\item $\lgh(\der{D}_1)=0$. Thus $\lgh(\der{D}'_1)=0$ too  and we have
-		\begin{align*}
-			(\der{D}, \alpha, \omega)&=(\der{D}_2, \alpha_2\circ \omega_1^{-1}\circ \alpha_1, \omega_2) \\ (\der{D}', \alpha', \omega')&=(\der{D}'_2, \alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1, \omega'_2)
-		\end{align*}
+	\[
+	(\der{D}, \alpha, \omega)=(\der{D}_2, \alpha_2\circ \omega_1^{-1}\circ \alpha_1, \omega_2) \qquad  (\der{D}', \alpha', \omega')=(\der{D}'_2, \alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1, \omega'_2)\]
+
 	Moreover, in this case $\sigma$ must be $\id{\emptyset}$ and $\sigma+\tau$ must be equal to $\tau$. The thesis now follows from the commutativity of the following diagram.
@@
 \item $\lgh(\der{D}_2)=0$.  As before this implies that also $\lgh(\der{D}'_2)$ is $0$.  Applying \Cref{def:conc} we get 
-		\begin{align*}
-			(\der{D}, \alpha, \omega)&=(\der{D}_1, \alpha_1, \omega_1 \circ (\alpha_2)^{-1}\circ \omega_2) \\ (\der{D}', \alpha', \omega')&=(\der{D}'_1, \alpha'_1, \omega'_1 \circ (\alpha'_2)^{-1}\circ \omega'_2)
-		\end{align*}
-		Since $\der{D}_2$ is empty, then $\tau=\id{\emptyset}$ and $\sigma+\tau=\sigma$. Let $n$ be $\lg(\der{D}_1)$, as before the thesis follows from the diagram below.
-		\[\xymatrix@C=35pt{& G_{2,0}\ar[dd]^{\xi_{\id{\emptyset}}} \ar[dr]^{\alpha^{-1}_2}&&G_{1,n}\ar@{>->}[r]^-{\iota_{1, G_{1,n}}} & \lpro \der{D}_2\rpro \ar[dd]^{\xi_{\sigma_1}}\\\pi(G_{2,0})  \ar[ur]^{\omega_2} \ar[dr]_{\omega'_2}&& \pi(G_{1,n}) \ar[ur]^{\omega_1} \ar[dr]_{\omega'_1}\\& G'_{2,0} \ar[ur]_{(\alpha'_1)^{-1}}&&G'_{1,n} \ar@{>->}[r]_-{\iota'_{1, G_{1,n}}}& \lpro \der{D}'_2\rpro}\]
-		\item   $\lgh(\der{D}_1)\neq0$ and $\lgh(\der{D}_2)\neq 0$. Thus $\der{D}'_1$ and $\der{D}'_2$ are non-empty too. In this case we have:
-		\begin{align*}
-			(\der{D}, \alpha, \omega)&=(\der{D}_1*\omega_1^{-1}\cdot \alpha_2*\der{D}_2, \alpha_1, \omega_2)\\
-			(\der{D}', \alpha', \omega')&=(\der{D}'_1*(\omega'_1)^{-1}\cdot \alpha'_2*\der{D}'_2, \alpha'_1, \omega'_2)
-		\end{align*}
+\[
+(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1 \circ (\alpha_2)^{-1}\circ \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1 \circ (\alpha'_2)^{-1}\circ \omega'_2)\]
+
+	Since $\der{D}_2$ is empty, then $\tau=\id{\emptyset}$ and $\sigma+\tau=\sigma$. Let $n$ be $\lgh(\der{D}_1)$, as before the thesis follows from the diagram below.
+	\[\xymatrix@C=35pt{& G_{2,0}\ar[dd]^{\xi_{\id{\emptyset}}} \ar[dr]^{\alpha^{-1}_2}&&G_{1,n}\ar@{>->}[r]^-{\iota_{1, G_{1,n}}} & \lpro \der{D}_2\rpro \ar[dd]^{\xi_{\sigma}}\\\pi(G_{2,0})  \ar[ur]^{\omega_2} \ar[dr]_{\omega'_2}&& \pi(G_{1,n}) \ar[ur]^{\omega_1} \ar[dr]_{\omega'_1}\\& G'_{2,0} \ar[ur]_{(\alpha'_1)^{-1}}&&G'_{1,n} \ar@{>->}[r]_-{\iota'_{1, G_{1,n}}}& \lpro \der{D}'_2\rpro}\]
+
+\item  $\lgh(\der{D}_1)\neq0$ and $\lgh(\der{D}_2)\neq 0$. Thus $\der{D}'_1$ and $\der{D}'_2$ are non-empty too. In this case we have
+\[	(\der{D}, \alpha, \omega)=(\der{D}_1*\omega_1^{-1}\cdot \alpha_2*\der{D}_2, \alpha_1, \omega_2)\qquad
+(\der{D}', \alpha', \omega')=(\der{D}'_1*(\omega'_1)^{-1}\cdot \alpha'_2*\der{D}'_2, \alpha'_1, \omega'_2)\]
 
@@
 \[\xymatrix{L_{2,i} \ar[d]_{m_{2, i}}& K_{2,i} \ar[d]_{k_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h_{2, i}} &L_{2,i} \ar[d]_{m'_{2, i}}& K_{2,i} \ar[d]_{k'_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h'_{2, i}} \\G_{2,i} & D_{2,i} \ar[r]_{g_{2,i}} \ar@{>->}[l]^{f_{2,i}} & G_{2,i+1} & G'_{2,i} & D'_{2,i}\ar[r]_{g'_{2,i}} \ar@{>->}[l]^{f'_{2,i}}  & G'_{2,i+1}}\]
+
+%Let $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$, $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$, $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$ and $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$ be colimiting cocones.
+By \Cref{rem:dett} we get the following diagram, in which the two solid squares are pushouts:
+\[\xymatrix@C=45pt@R=30pt{\pi(G_{2,0}) \ar@/^.4cm/[rrr]^{\id{\pi(G_{2,0})}}\ar@{>->}[d]_{\iota_{1, G_{1,n+1}} \circ \omega_1}\ar[r]_{\iota_{2, G_{2,0}} \circ \alpha_2}& \lpro \der{D}_2 \rpro \ar@{>->}[d]^{q_2}\ar[r]_{\xi_\tau} & \lpro \der{D}'_2 \rpro \ar@{>->}[d]_{q'_2} &\pi(G'_{2,0}) \ar@{>->}[d]^{\iota'_{1, G'_{1,n+1}} \circ \omega'_1} \ar[l]^{\iota'_{2, G'_{2,0}} \circ \alpha'_2}\\ \lpro \der{D}_1 \rpro \ar@/_.4cm/[rrr]_{\xi_\sigma} \ar[r]^{q_1} & \tpro{D} \ar@{.>}[r]^{\xi_{\sigma+\tau}} & \lpro \der{D}'\rpro & \lpro \der{D}'_1\rpro  \ar[l]_{q'_1}}\]
+
+Moreover, we can point out that, for every index $i\in [0,n+t+2]$ we have
+
+\[\iota_{G_i}=\begin{cases}q_1\circ \iota_{1, G_{1,i}} & i \leq n\\
+	q_1\circ \iota_{1, G_{1, i}}\circ \omega_1& i=n+1\\
+	q_2\circ \iota_{2, G_{2,i-(n+1)}} & i > n+1 
+\end{cases} \qquad \iota'_{G'_i}=\begin{cases}q'_1\circ \iota'_{1, G'_{1,i}} & i \leq n\\
+	q'_1\circ \iota'_{1, G'_{1, i}}\circ \omega'_1& i=n+1\\
+	q'_2\circ \iota'_{2, G'_{2,i-(n+1)}} & i > n+1 
+\end{cases}\]
+
+Now, on the one hand, the existence of the dotted arrow $\xi_{\sigma+\tau}\colon \tpro{D}\to \lpro \der{D}'\rpro$ in the diagram above follows from the following computation:
+\begin{align*}
+	q'_1\circ \xi_\sigma \circ \iota_{1, G_{1,n+1}} \circ \omega_1&=q'_1\circ \iota'_{1,G'_{1, n+1}} \circ \omega'_1\\&= q'_2 \circ \iota'_{2, G'_{2,0}} \circ \alpha'_2\\&=q'_2\circ \xi_\tau \circ \iota_{2, G_{2,0}} \circ \alpha_2
+\end{align*} 
+On the other hand, we can repeat the same computation for $\xi^{-1}_\sigma$ and $\xi^{-1}_\tau$ to get
+\begin{align*}
+	q_1\circ \xi^{-1}_\sigma \circ \iota'_{1, G'_{1,n+1}} \circ \omega'_1&=q_1\circ \iota_{1,G_{1, n+1}} \circ \omega_1\\&= q_2 \circ \iota_{2, G_{2,0}} \circ \alpha_2\\&=q_2\circ \xi^{-1}_\tau \circ \iota'_{2, G'_{2,0}} \circ \alpha'_2
+\end{align*} 
+Hence there exists a $\psi\colon \lpro \der{D}'\rpro \to \tpro{D}$ such that:
+\[\psi \circ q'_1=q_1\circ \xi^{-1}_\sigma \qquad \psi \circ q'_2=q_2\circ \xi^{-1}_\tau\]
+
+Furthermore, the computations below show that $\psi$ is the inverse of $\xi_{\sigma+\tau}$.
+\[\begin{split}
+	\psi \circ \xi_{\sigma+\tau}\circ  q_1&=\psi \circ q'_1\circ \xi_\sigma \\&=q_1\circ \xi^{-1}_{\sigma}\circ \xi_\sigma\\&=q_1\\\\
+	\xi_{\sigma+\tau}\circ \psi \circ q'_1&=\xi_{\sigma+\tau}\circ q_1\circ \xi^{-1}_\sigma \\&=q'_1\circ \xi_{\sigma}\circ \xi^{-1}_\sigma\\&=q'_1
+\end{split}\qquad \begin{split}
+	\psi \circ \xi_{\sigma+\tau}\circ  q_2&=\psi \circ q'_2\circ \xi_\tau \\&=q_2\circ \xi^{-1}_{\tau}\circ \xi_\tau\\&=q_2\\ \\ 	\xi_{\sigma+\tau}\circ \psi \circ q'_2&=\xi_{\sigma+\tau}\circ q_2\circ \xi^{-1}_\tau \\&=q'_2\circ \xi_{\tau}\circ \xi^{-1}_\tau\\&=q'_2
+\end{split}\]
+To conclude we have to show that $\xi_{\sigma+\tau}$ fits in the diagrams of \Cref{def:permcon}.  For the ones involving the decorations we have:
+\[\begin{split}
+	\xi_{\sigma+\tau} \circ \iota_{G_{0}}\circ \alpha&=\xi_{\sigma+\tau} \circ q_1 \circ \iota_{1,G_{1,0}}\circ \alpha_1\\&=q_1'\circ \xi_\sigma \circ  \iota_{1,G_{1,0}} \alpha_1\\&=q'_1\circ \iota'_{1, G'_{1,0}}\circ \alpha'_1\\&=\iota'_{G'_0}\circ \alpha'
+\end{split}  \qquad 
+\begin{split}
+\xi_{\sigma+\tau} \circ \iota_{G_{n+t+2}}\circ \omega&=\xi_{\sigma+\tau} \circ q_2 \circ \iota_{2,G_{2,t+1}}\circ \omega_2\\&=q'_2\circ \xi_\tau \circ  \iota_{2,G_{2,t+1}} \omega_2\\&=q'_2\circ \iota'_{2, G'_{2,t+1}}\circ \omega'_2\\&=\iota'_{G'_{n+t+2}}\circ \omega'
+\end{split}  \]
+
+Let now $i$ be an index in $[0, n+t+1]$, we proceed splitting the cases.
+\begin{itemize}
+	\item $i$ is in $[0,n]$. Then we have
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_i} \circ m_i &= \xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,i}}\circ m_{1,i}\\&=q'_1 \circ \xi_\sigma \circ \iota_{1, G_{1,i}}\circ m_{1,i}\\&= q'_1\circ \iota'_{1, G'_{1,\sigma(i)}}\circ m'_{1,\sigma(i)}\\&=\iota'_{G'_{\sigma(i)}}\circ m'_{\sigma(i)}
+	\end{align*}
+	Now, suppose that $i\neq n$, then 
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i &= \xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,{i+1}}}\circ h_{1,i}\\&=q'_1\circ \xi_\sigma \circ \iota_{1, G_{1,{i+1}}}\circ h_{1,i}\\&= q'_1\circ \iota'_{1, G'_{1,\sigma(i)+1}}\circ h'_{1,\sigma(i)}
+	\end{align*}
+	and we have two subcases. If $\sigma(i)\neq n$, then \[h'_{1, \sigma(i)}=h'_{\sigma(i)} \qquad q'_1\circ \iota'_{1, G'_{1,\sigma(i)+1}}=
+	\iota'_{G'_{\sigma(i)+1}}\] 
+	and we can conclude. Otherwise, we have
+	\begin{align*}q'_1\circ \iota'_{1, G'_{1,n+1}}\circ h'_{1,n}&=q'_1 \circ \iota'_{1,G'_{1,n+1}} \circ \omega'_1\circ (\omega')^{-1}_1 \circ h'_{1,n}\\&=\iota'_{G'_{n+1}}\circ h'_n
+	\end{align*}
+	yielding again the wanted equality
+	\[\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i=\iota'_{G'_{\sigma(i)+1}}\circ h'_{\sigma(i)}\]
+	Finally, if $i=n$ we get
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ h_n &= \xi_{\sigma+\tau} \circ \iota_{\pi(G_{1,n+1})} \circ \omega^{-1}_1\circ h_{1,n}\\&= \xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,n+1}} \circ \omega_1 \circ \omega^{-1}_1 \circ h_{1,n}\\&=q'_1 \circ \xi_\sigma \circ \iota_{1, G_{1,n+1}} \circ h_{1,n}\\&=q'_1\circ \iota'_{1, G_{1,\sigma(n)+1}} \circ h'_{1,\sigma(n)}
+	\end{align*}
+	We have again two cases. If $\sigma(n)\neq n$ then we can conclude at once since 
+	\[h'_{1, \sigma(n)}=h'_{\sigma(n)} \qquad q'_1\circ \iota'_{1, G'_{1,\sigma(n)+1}}=
+	\iota'_{G'_{\sigma(n)+1}}\] 
+	While, if $\sigma(n)=n$, then we can use the identities
+	\[(\omega'_1)^{-1}\circ h'_{1, n}=h'_{n} \qquad q'_1\circ \iota'_{1, G'_{1, n+1}}=
+	\iota'_{G'_{n+1}}\circ (\omega'_1)^{-1}\] 
+	to get
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ h_n &= q'_1\circ \iota'_{1, G_{1,n+1}} \circ h'_{1,n}\\&=\iota'_{G'_{n+1}}\circ (\omega'_1)^{-1}\circ h'_{1,n}\\&=\iota'_{G'_{n+1}} h'_{n}
+	\end{align*}
+	\item $i$ is in $[n+1, n+t+1]$- We proceed  similarly to the point above. First of all we have
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i &= \xi_{\sigma+\tau} \circ q_2\circ \iota_{1, G_{2,i-n}}\circ h_{2,i-(n+1)}\\&=q'_2 \circ \xi_\tau \circ \iota_{2, G_{2,i-n}}\circ h_{2,i-(n+1)}\\&= q'_2\circ \iota'_{2, G'_{2,\tau(i-n)}}\circ h'_{2,\tau(i-(n+1))}\\&=\iota'_{G'_{\tau(i-n)}}\circ h'_{n+1+\tau(i-(n+1))}
+	\end{align*}
+	Next, supposing that $i\neq n+1$:	
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{i}} \circ m_i &= \xi_{\sigma+\tau} \circ q_2\circ \iota_{2, G_{2,i-(n+1)}}\circ m_{2,i-(n+1)}\\&=q'_2\circ \xi_\tau \circ \iota_{2, G_{2,{i-(n+1)}}}\circ m_{2,i-(n+1)}\\&= q'_2\circ \iota'_{2, G'_{2,\tau(i-(n+1))}}\circ m'_{2,\tau(i-(n+1))}
+	\end{align*}
+	and we have again two possibilities.
+If $\tau(i-(n+1))\neq 0$, then the thesis follows from the equalities \[m'_{2, \tau(i-(n+1))}=m'_{(\sigma+\tau)(i)} \qquad q'_2\circ \iota'_{2, G'_{2,\tau(i-(n+1))}}=
+	\iota'_{G'_{(\sigma+\tau)(i)}}\] 
+	Suppose, instead, that $\tau(i-(n+1))= 0$, then we have
+	\begin{align*} q'_2\circ \iota'_{2, G'_{2,0}}\circ m'_{2,0}&=q'_2 \circ \iota'_{2,G'_{2,0}} \circ \alpha'_2 \circ \alpha'^{-1}_2 \circ m'_{2,0}\\&=q'_1\circ \iota'_{1, G'_{1, n+1}}\circ \omega'_1\circ \alpha'^{-1}_2 \circ m'_{2,0}\\&=\iota'_{G'_{n+1}}\circ m'_{n+1}
+	\end{align*}
+	allowing us to conclude again.
+
+	We are left with the case $i=n+1$. Let us compute
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= \xi_{\sigma+\tau} \circ \iota_{\pi(G_{2,0})} \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,n+1}} \circ \omega_1 \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ q'_2 \circ \iota'_{2,G'_{2,0}} \circ \alpha'_2 \circ (\alpha'_2)^{-1}\circ m_{2,0} \\&=q'_2 \circ \xi_\tau \circ \iota_{2, G_{2,0}} \circ m_{2,0}\\&=q'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}
+	\end{align*}
+	We have again two cases. If $\tau(0)\neq 0$ then $(\sigma+\tau)(i)\neq n+1$ and we can conclude at once since 
+	\[m'_{2, \tau(0)}=m'_{(\sigma+\tau)(n+1)} \qquad q'_2\circ \iota'_{2, G'_{2,\tau(0)}}=
+	\iota'_{G'_{(\sigma+\tau)(0)}}\] 
+	If $\tau(0)=0$, so that  $(\sigma+\tau)(0)= n+1$ we appeal to the equalities
+	\[(\alpha')^{-1}_2\circ m'_{2, 0}=m'_{n+1} \qquad q'_2\circ \iota'_{2, G'_{2, 0}}=
+	\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\] 
+	to get
+	\begin{align*}
+		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= q'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}\\&=	\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\circ m'_{2,0}\\&=\iota'_{G'_{n+1}}\circ  m'_{n+1}
+	\end{align*}
 \end{itemize}
-	Let $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$, $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$, $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$ and $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$ be colimiting cocones.
-Define two other cocones and  $\der{D}'_1*(\omega'_1)^{-1}\cdot \alpha'_2*\der{D}'_2$
-	Using point $2$ of \Cref{lem:colim} we get two pushout squares
-	\[\xymatrix{\pi(H) & }\]
-	Now, notice that $()$ and $bb$ are cocones on ... so that there exists... such that. 
-\end{proof}
-
-\begin{corollary}\label{cor:presuffix}
-	\todo{prefisso e suffisso}
-\end{corollary}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\section{Shift equivalence and traces}
+The thesis now follows at once.	 \qedhere 
+\end{itemize} \end{proof}
+
+\section{Independence in rewriting}
 \todo{A VERY NICE INTRO}
 
-\subsection{Sequentially independent and switchable derivations}
+\subsection{Sequentially independent and switchable derivations }
+\todo{this is an attempt to rewrite in a better way the following section. Hopefully this will spare us the use of fillers}
 \todo{A VERY NICE INTRO}
 
-\begin{definition}  Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
+\begin{definition}[Sequential independence]
+  \label{de:sequential-independence}
+  Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
 Let also $\dder{D}\colon G\Mapsto H$ and $\dder{D'}\colon H\Mapsto T$ be the two direct derivations depicted below.
 
-\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
+	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{m'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
 
@@
 
-\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
+	\[\xymatrix@C=15pt{L \ar[d]_{m}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
 	We will say that $\dder{D}$ and $\dder{D'}$ are \emph{weakly sequentially independent} if an independence pair exists.
@@
 
+ Let $(i_0, i_1)$ and $(i'_0, i'_1)$ be independence pairs for the direct derivations $\dder{D}$ and $\dder{D'}$. Notice that, by definition, we have
+	\begin{align*}f'\circ i_0&=h\\&=f'\circ i'_0
+	\end{align*}
+	On the other hand, 
+	$f'\colon D'\to H$ is  the pushout of $l'\colon K'\to L'$ and so it is in $\mathcal{M}$, implying $i_0=i'_0$.
+If, moreover, we suppose that the rule $\rho$ applied in $\dder{D}$ is linear, then $g\colon D\to H$ is in $\mathcal{M}$ too, hence, from the equation
+	\begin{align*}
+		g\circ i_1&=h \\&= g\circ i'_1
+	\end{align*}
+	we can deduce that $i'_0=i'_1$, too. Summing up, we have just proved the following.
+
+	\begin{proposition}\label{rem:weak}
+	Let $(\X, \R)$ be a linear DPO-rewriting system, then two direct derivations $\dder{D}$ and $\dder{D}'$ are weakly sequential independet if and only if they are sequential independent. 
+\end{proposition}
+
+We want to be able to exchange to switch the application of two rules used by two consecutive weakly independent direct derivations. This leads us to the following definition.
+
+\begin{definition}[Switch]
+  \label{de:switch}
+ Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category and suppose that $\der{D}=\{\dder{D}_i\}_{i=0}^1$  is a derivation of length $2$ made by the following two weakly sequentially independent derivations $\dder{D}_0$, $\der{D}_1$, with independence pair $(i_0, i_1)$:
+ 	\[\xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0} && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2}\]
+
+ 	Take another derivation $\der{E}=\{\dder{E}_i\}_{i=0}^1$ with source $G_0$ and target $G_2$ and in which $\der{E}_0$, $\der{E}_1$ are
+\[\xymatrix{L_{\der{E},0} \ar[d]_{m_{\der{E},0}}& K_{\der{E},0} \ar[d]^{k_{\der{E},0}}\ar[l]_{l_{\der{E},0}} \ar[r]^{r_{\der{E},0}} & R_{\der{E},0} \ar[d]^{h_{\der{E},0}} & L_{\der{E},1} \ar[d]_{m_{\der{E},1}}& K_{\der{E},1} \ar[d]^{k_{\der{E},1}}\ar[l]_{l_{\der{E},1}} \ar[r]^{r_{\der{E},1}} & R_{\der{E},1} \ar[d]^{h_{\der{E},1}}\\G_{0} & \ar[l]^{f_{\der{E},0}} D_{\der{E},0} \ar[r]_{g_{\der{E},0}}& G_{\der{E},1} & G_{\der{E},1} & \ar[l]^{f_{\der{E},1}} D_{\der{E},1} \ar[r]_{g_{\der{E},1}}& G_{2}}\]
+ 	We say that $\der{E}$ is a
+ 	 	 \emph{switch} of $\der{D}$ along $(i_1, i_2)$ if
+ 	\begin{enumerate}
+ 		\item $\dder{E}_0$ applies the rule used by $\dder{D}_1$ and $\dder{E}_1$ the one used by $\dder{D}_0$, so that
+ 		\[(l_{\der{E},0}, r_{\der{E},0})=(l_1,r_1)  \qquad (l_{\der{E},1}, r_{\der{E},1})=(l_0,r_0)\]
+ 		\item there exists an independence pair $(j_0, j_1)$ between $\dder{E}_0$ and $\dder{E}_1$ such that
+ 		\[ m_0=f_{\der{E},0} \circ j_1 \qquad h_1=g_{\der{E},1} \circ j_0\]
+ 		\item $m_{\der{E},0}= f_0\circ i_1$ and $h_{\der{E},1}= g_{1}\circ i_0$.
+ 	\end{enumerate}
+\end{definition}
+
+\begin{remark}\label{rem:fact}
+	Notice that, since $f_{\der{E}, 0}$ is in $\mathcal{M}$, there is at most one $j_1\colon L_0\to D_{\der{E},0}$ such that $m_0=f_{\der{E}, 0} \circ j_1$.
+Moreover, we already know that there is at most one $j_0\colon R_1\to D_{\der{E},1}$ such that $m_{\der{E},1}=f_{\der{E},1}\circ j_0$, therefore, the independence pair $(j_0,j_1)$ between the component of a switch is uniquely determined.
+\end{remark}
+
+Our first result about switches is their uniqueness up to abstraction equivalence.
+
+\begin{theorem}[Uniqueness of switches]\label{thm:switch_uni} Let $\der{D}=\{\dder{D}_i\}_{i=0}^1$
+
+\end{theorem}
+
+\begin{lemma}\label{lem:cose} Let $(\der{D}, \alpha, \omega)$ be a decorated derivation with $\der{D}=\{\dder{D}_i\}_{i=0}^1$,  and suppose that $(i_0, i_1)$ is an independence pair between $\dder{D}_0$  and $\der{D}_1$.
+If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a switch of $\der{D}$ along $(i_0, i_1)$, then the following hold true:
+	\begin{enumerate}
+			\item the pullback square below is an $\mathcal{M}$-pushout;
+			\[\xymatrix{P \ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\ D_0 \ar[r]_{g_1}& G_1}\]
+			\item there exist $q_0\colon P\to D_{\der{E},0}$, $q_1\colon P\to D_{\der{E},1}$ making the squares 
+			\[\xymatrix{}\]
+			commutative, moreover, they are all pushouts;
+			\[\xymatrix{}\]
+ 		\item there exists an arrow $j_0\colon R_1\to D_{\der{E},1}$ such that 
+ 		\[h_{\der{E},0}=f_{\der{E},1}\circ j_0 \qquad h_1=g_{\der{E},1} \circ j_0\]
+	\end{enumerate}
+\end{lemma}
+\begin{proof}
+	Before starting with the proof of our claims, it is worth noticing that the definition of switchin gives us the following diagram:
+			\[\xymatrix@R=28pt{&&R_0 \ar@/_1.15cm/[ddrr]_(.8){i_0}|(.68)\hole \ar[dr]^{h_0}&& L_1\ar@/^1.15cm/[ddll]^(.8){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar[ur]^{r_0}&& G_1 && K_1 \ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.94cm/[ddrr]_(.8){j_1}|(.31)\hole \ar[dr]^(.35){m_0}|(.6)\hole && D_0 \ar[dl]^{f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]_{g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar[dl]^(.35){h_1}|(.6)\hole\\&G_0 &&&&G_2\\L_1 \ar@/^.94cm/[uurr]^(.8){i_1} \ar[ur]_(.35){m_{\der{E},0}}|(.61)\hole&&D_{\der{E},0} \ar[ul]_{f_{\der{E},0}}\ar[dr]^{g_{\der{E},0}} &&D_{\der{E},1}\ar[ur]^{g_{\der{E},1}} \ar[dl]|(.5)\hole^(.7){f_{\der{E},1}} && R_0  \ar@/_.94cm/[uull]_(.8){j_1} \ar[ul]^{h_{\der{E},1}}\\&K_1 \ar[ur]_{k_{\der{E},0}} \ar[dr]_{r_1} \ar[ul]^{l_1}&&G_{\der{E},1}&& K_0 \ar[ur]_{r_0} \ar[ul]^{k_{\der{E},1}} \ar[dl]^{l_0} \\&& R_1 \ar[ur]_{h_{\der{E},0}}&& L_0 \ar[ul]^{m_{\der{E},1}} \ar@/_1.15cm/[uull]_(.6){j_1} }\]
+
+			Let us turn to our statements.
+	\begin{enumerate}
+		\item We start noticing that 
+		\begin{align*}
+			g_0\circ i_1\circ l_1&=m_1\circ l_1\\&=k_1\circ f_1
+		\end{align*}
+		Thus there exists the dotted $u\colon K_1\to P$ in the diagram
+		\[\]
+		The thesis now follows applyin \Cref{lem:popb} to
+
+		\item 
+		\item  We already have an arrow $j_1\colon L_0\to D_{\der{E},0}$ such that
+		\[m_{\der{E},1}=g_{\der{E},0}\circ j_1\]
+		Therefore the thesis follows at once from the previous point.
+
+	\item
+
+		\item \qedhere 
+	\end{enumerate}
+\end{proof}
+
+\todo{ $\dder{E}_0$ and $\dder{E}_1$ are weak sequentially independent;
+
+if $\der{E}'=\{\dder{E}'_i\}_{i=0}^1$ is another switching of $\der{D}$ along $(i_0, i_1)$, then there exist arrows.... such that the following diagram commutes:
+}
+In particular [...]
+\begin{definition}\todo{switch}
+	contenuto...
+\end{definition}
+\begin{remark}
+Canonico
+\end{remark}
+\begin{corollary}\todo{inversione}
+\end{corollary}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{lemma}
+	\todo{permutazione}
+\end{lemma}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{lemma}\label{lem:swfill}
+\todo{equi}
+\end{lemma}
+\begin{remark}
+	\todo{tobias}
+\end{remark}
+\begin{remark}
+	contenuto...
+\end{remark}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+When working with linear rewriting systems, (weakly) sequential independent direct derivations can be switched, producing two new (weakly) sequential independent direct derivations between the same objects \cite[Thm.~$7.7$]{lack2005adhesive} .
+This is no more the case if the rules are only left-linear, as shown by the next example.
+
+\begin{example}\label{ex:difficile}
+	\todo{pensare ad un esempio in cui l'indipendenza non basta }
+\end{example}
+
+\subsection{Sequentially independent and switchable derivations}
+\todo{A VERY NICE INTRO}
+
+\begin{definition}  Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
+Let also $\dder{D}\colon G\Mapsto H$ and $\dder{D'}\colon H\Mapsto T$ be the two direct derivations depicted below.
+
+	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
+
+	An \emph{independence pair} between $\dder{D}$ and $\dder{D'}$, is a pair of  arrows $i_1\colon R\to D'$ and $i_2\colon L'\to D$ such that the following diagram commutes.
+
+	\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
+	We will say that $\dder{D}$ and $\dder{D'}$ are \emph{weakly sequentially independent} if an independence pair exists.
+If such independence pair is unique we will say that $\dder{D}$ and $\dder{D'}$ are \emph{sequentially independent}.
+\end{definition}
+
+\begin{example}
+	\todo{sequential independence}
+\end{example}
+\begin{example}
+	\todo{sequential independence che serva anche per es successivo}
+\end{example}
+
 \begin{remark}\label{rem:weak} Let $(i_1, i_2)$ and $(j_1, j_2)$ be independence pairs for the direct derivations $\dder{D}$ and $\dder{D'}$. Notice that, by definition, we have
@@
 \end{remark}
+
+We want to be able to exchange to switch the application of two rules used by two consecutive weakly independent direct derivations
+\begin{definition}
+	contenuto...
+\end{definition}
+
+\begin{proposition}
+	\todo{equi}
+\end{proposition}
+\begin{remark}
+	contenuto...
+\end{remark}
+\begin{proof}
+	contenuto...
+\end{proof}
 
@@
 
-\begin{definition} Let  $\dder{D}\colon H\Mapsto H$, $\dder{D}'\colon H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system  $(\X, \R)$.
-An independence pair $(i_1, i_2)$ between $\dder{D}$ and $\dder{D}'$ is \emph{good} if there exists a filler $(u,u')$ between them such that  the squares below are pushouts.\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
+\begin{definition}
+  \label{de:good-switchable}
+  Let $\dder{D}\colon H\Mapsto H$, $\dder{D}'\colon H\Mapsto T$ be two
+  direct derivations in a left-linear DPO-rewriting system $(\X,
+  \R)$. An independence pair $(i_1, i_2)$ between $\dder{D}$ and
+  $\dder{D}'$ is \emph{good} if there exists a filler $(u,u')$ between
+  them such that the squares below are
+  pushouts.\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K'
+      \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P
+      \ar[r]_{p} & D}\]
 
@@
 
-\begin{definition} Let $(\X, \R)$ be a left-linear DPO-rewriting system.
-Given two direct derivations $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$, we say that  $\dder{D}$ and $\dder{D}'$ are \emph{properly switchable} if $\dder{D}\updownarrow_!
-\dder{D'}$ and $S_{i_1,i_2}(\dder{D}')\updownarrow_!S_{i_1,i_2}(\dder{D})$, where $(i_2,i_2)$ is a good independence pair betwwen $\dder{D}$ and $\dder{D}'$.
-In such a case, we will write $\dder{D}\Updownarrow\dder{D}'$.
+\begin{definition}
+  \label{de:switchable}
+  Let $(\X, \R)$ be a left-linear DPO-rewriting system. Given two
+  direct derivations $\dder{D}\colon G\Mapsto H$ and
+  $\dder{D}'\colon H\Mapsto T$, we say that $\dder{D}$ and $\dder{D}'$
+  are \emph{properly switchable} if $\dder{D}\updownarrow_! \dder{D'}$
+  and $S_{i_1,i_2}(\dder{D}')\updownarrow_!S_{i_1,i_2}(\dder{D})$,
+  where $(i_2,i_2)$ is a good independence pair betwwen $\dder{D}$ and
+  $\dder{D}'$. In such a case, we will write
+  $\dder{D}\Updownarrow\dder{D}'$.
 
@@
 \todo{ci sono un sacco di sistemi very tame}
-\subsection{On the globality of $\Updownarrow$}
+\subsection{Switch equivalence}
 \todo{intro}
 
+\subsubsection{The $3$-steps lemmas}
+
+As a beginning step in our analysis of switch equivalence, we will establish three lemmas  dealing with derivations of length $3$.
+
+\begin{lemma}[First $3$-steps Lemma]\label{lem:primo}
+Let $(\X,\R)$ be a left-linear DPO-rewriting system.
+Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$ and suppose that $(i_0,i_1)$ is a good independence pair between $\dder{D}_0$ and $\dder{D}_1$, $(a_0,a_1)$ one between $\dder{D}_1$ and $\dder{D}_2$ and $(e_0, e_1)$ one between $\dder{D}_0$ and $S_{a_0,a_1}(\dder{D}_2)$.
+\end{lemma}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{lemma}[Second $3$-steps Lemma]\label{lem:secondo}
+	contenuto...
+\end{lemma}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{lemma}[Third $3$-steps Lemma]\label{lem:terzo}
+	contenuto...
+\end{lemma}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\todo{dividere in due il lemma dopo. devono venire tre lemmi}
 \begin{lemma}[Three steps Lemma]\label{lem:iig1}Let $(\X,\R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
@@
 First of all, let $(v,v')$ be the filler between $\dder{D}_0$ and $\dder{D}_1$ associated to $(i_0, i_1)$, then we have
-	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&H'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
+	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&H'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
 
@@
 \end{proof}
-\iffalse 
-\begin{corollary} Given a tame  left-linear DPO-rewriting system  $(\X,\R)$ with $\X$ an $\mathcal{M}$-adhesive category and a decorated derivation $(\der{D}, \alpha, \omega)$ with $\der{D}=\{\dder{D}_i\}_{i=0}^2$.
-Then the following are true:
-	\begin{enumerate}
-		\item suppose that $(a_1,a_2)$ and $(e_0,e_1)$ are independence pairs witnessing  $\dder{D}_1\updownarrow_!
-\dder{D}_2$ and $\dder{D}_0\updownarrow_!
-S_{a_1,a_2}(\dder{D}_2)$ respectively, if $\dder{D}_0\updownarrow_!\dder{D}_1$, then $S_{e_0,e_1}(\dder{D}_0)\updownarrow_!S_{a_2,a_2}(\dder{D}_1)$;
-		\item 
-	\end{enumerate}
+
+\subsubsection{Inversions and switch equivalence}
+\todo{richiamare cosa sono le inversioni}
+
+\begin{lemma}[Fundamental Lemma] Let $(\der{D}, \alpha, \omega)$ and $(\der{D'}, \alpha, \omega)$ be two decorated derivations and suppose that there exists a non-empty sequence $\{\der{D}_i\}_{i=0}^n$ a of derivations witnessing $\der{D}\equiv^s \der{D}'$.
+For every $i\in [0,n-1]$, let $\nu_i\colon [0, \lgh(\der{D})-1]\to [0, \lgh(\der{D})-1]$ be the $2$-cycle associated to the switch between $\der{D}_i$ and $\der{D}_{i+1}$, let also $\sigma$ be the associated consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
+Define $k$ as the maximum of the set
+\[M_\sigma:=\{j\in [0, \lgh(\der{D}-1] \mid \sigma(j+1) < \sigma(j) \}\]
+If every $\nu_i$ is an inversion for $\sigma$, then there exists a family $\{\nu'_i\}_{i=0}^n$ of inversions for $\sigma$ such that jj\todo{capire come scriverlo meglio, l} $\nu'_0=(k, k+1)$.
+\end{lemma}
+\begin{remark}
+	Since $\{\der{D}_i\}_{i=0}^n$ is non-empty, then $\sigma$ must be different from $\id{[0, \lgh(\der{D}-1)]}$ and $M_{\sigma}\neq \emptyset$.
+\end{remark}
+\begin{proof}
+	We proceed by induction on $n$.
+
+	\smallskip\noindent $n=1$. In this case there is nothing to prove.
+
+	\smallskip \noindent $n>1$. Then...
+\end{proof}
+
+\begin{corollary}
+	contenuto...
 \end{corollary}
-
-\todo{ripulire le ipotesi: serve scambiabilità propria tra 1 e 2}
-\todo{sistemare il fatto che qua utilizziamo derivazioni di 3 passi}
-\begin{proof}
-	\begin{enumerate}
-		\item Let $(i_1,i_2)$ be the unique independence pair between $\dder{D}_0$ and $\dder{D}_1$.
-By tameness and \Cref{lem:iig1} we know that $S_{e_0,e_1}(\dder{D}_0)\updownarrow S_{a_1,a_2}(\dder{D}_1)$.
-Let $(\alpha_1, \alpha_2)$ be the independence pair constructed in the proof of \Cref{lem:iig1}.
-Take another independence pair $(\beta_1, \beta_2)$,  by \Cref{rem:weak} we already know that $\beta_1=\alpha_1$.
-Let also $\der{E}$ be the derivation $S_{e_0, e_1}(S_{a_1, a_2}(\der{D}_2))\cdot S_{e_0, e_1}(\dder{D}_0) \cdot S_{a_1, a_2}(\der{D}_1)$.
-Let $\sigma\colon [0,2]\to [0,2]$ be the cycle $(0,1,2)$.
-By \Cref{lem:consperm} we know that $\sigma$ is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{E}, \alpha, \omega)$.
-In particular, we have
-		\begin{align*}
-			\iota_{\der{E}, G_0}\circ f_0\circ  i_1 &=\xi_\sigma \circ 	\iota_{\der{D}, G_0}\circ f_0\circ  i_1 \\&= \xi_\sigma \circ 	\iota_{\der{D}, D_0}\circ  i_1\\ &= \xi_\sigma \circ \iota_{\der{D}, G_1} \circ g_0\circ  i_1 \\&=\xi_\sigma \circ \iota_{\der{D}, G_1}\circ m_1\\ &=  \iota_{\der{E}, G'_2}\circ y_1\circ b_1\\&= \iota_{\der{E}, G'_2}\circ z'_1\circ \beta_2\\&= \iota_{\der{E}, Q_5}\circ \beta_2
-		\end{align*}
-		Using	\Cref{rem:pbsalva} we can deduce the existence of a unique arrow $\beta'_2\colon L_1\to P_3$ fitting in the diagram below
-		\[\xymatrix@C=30pt{L_1  \ar@/^.3cm/[drr]^{\beta_2} \ar@/_.3cm/[ddr]_{i_1}\ar@{.>}[dr]^{\beta'_2}\\& P_3 \ar[r]^{n_1}  \ar[d]_{u_0}& Q_5 \ar[d]^{\iota_{\dder{E}, Q_5}}\\
-		&D_0 \ar[r]_{\iota_{\dder{E}, G_0}}& \tpro{E}}\]
-		If we further compute, we get
-		\begin{align*}
-			y_1\circ u_1\circ \beta'_2&=z'_1\circ n_1\circ \beta'_2=\\&= z'_1\circ \beta_2 \\&=y_1\circ b_1
-		\end{align*}
-		Thus $(u_1\circ \beta'_2, b_2)$ is an independence pair between $S_{a_1, a_2}(\der{D}_2)$ and $S_{a_1, a_2}(\der{D}_1)$ therefore, by hypothesis $u_1\circ \beta'_2=b_1$.
-But this implies that $\beta'_2$ and $\alpha'_2$ are equal, giving us the thesis.
-
-\todo{ripulire le ipotesi: serve scambiabilità propria tra 1 e 2}
-\todo{sistemare il fatto che qua utilizziamo derivazioni di 3 passi}
-
-		\item \qedhere 
-	\end{enumerate}
-\end{proof}
-
- \todo{mettere esempio del perché fallisce nell'altra direziome}
- \todo{anche una breve intro}
-
-\begin{lemma}\label{lem:iig2}Let $(\X,\R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-For every derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$, if $(i_0,i_1)$ is a good independence pair between $\dder{D}_0$ and $\dder{D}_1$, $(a_1,a_2)$ one between $\dder{D}_1$ and $\dder{D}_2$ and $\dder{D}_0\updownarrow S_{a_1,a_2}(\dder{D}_2)$ with good independence pair $(e_0,e_1)$, then $S_{e_0,e_1}(\dder{D}_0)$ and $S_{a_1,a_2}(\dder{D}_1)$ are weakly sequentially independent.
-\end{lemma}
-\begin{proof} As in the proof of \Cref{lem:iig1}, \Cref{def:filler,def:switch} yield to us some diagrams.
-First of all, let $(v,v')$ be the filler between $\dder{D}_0$ and $\dder{D}_1$ associated to $(i_1, i_2)$, then we have
-	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
-
-	Secondly, the filler $(u,u')$ induced by $(a_1, a_2)$ between $\dder{D}_1$ and $\dder{D}_2$ yields:
-	\[
-	\xymatrix{&&R_1 \ar@/_1cm/[ddrr]_(.35){a_1}|(.7)\hole \ar[dr]^{h_1}&& L_2\ar@/^1cm/[ddll]^(.35){a_2}  \ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar[dl]_{l_1} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){u}\ar[ur]^{r_1}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){u'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_1 \ar@/_.8cm/[ddrr]_(.2){b_1}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_1}|(.61)\hole && D_1 \ar[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){b_2}|(.31)\hole|(.81)\hole\ar[dl]_{h_2}\\&G_1 &&P_2\ar[dr]_{d_2} \ar[dl]^{d_1}\ar[ur]^(.4){c_2}\ar[ul]_(.4){c_1}&&G_2\\L_2 \ar@/^.8cm/[uurr]^(.2){a_2} \ar[ur]_(.35){f_1\circ a_2}|(.61)\hole&&Q_2 \ar[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1} &&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar[dl]|(.5)\hole_(.65){x_2} && R_1  \ar[ul]^(.35){g_2\circ a_1}|(.61)\hole\ar@/_.8cm/[uull]_(.2){a_1}\\&K_2 \ar[ur]_{d_1\circ u'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){u'}&&G'_2&& K_1 \ar[ur]_{r_1} \ar[ul]^{d_2\circ u} \ar[dl]^{l_1} \ar@/_.8cm/[uull]^(.65){u}\\&& R_2 \ar[ur]_{\hspace{-5pt}x_2\circ b_2}\ar@/^1cm/[uurr]^(.25){b_2}&& L_1 \ar[ul]^{y_1\circ b_1\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){b_1} |(.69)\hole }\]
-
-	Finally, the filler $(w,w')$  between $\dder{D}_0$ and $S_{u,u'}(\dder{D}_2)$ given by $(e_0, e_1)$ provides us with:
-	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){e_0}|(.7)\hole \ar[dr]^{h_0}&& L_2\ar@/^1cm/[ddll]^(.35){e_1}  \ar[dl]_{f_1\circ a_2}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){w}\ar[ur]^{r_0}&& G_1 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){w'}\ar[dl]_{d_1\circ u'\hspace{-5pt}}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_0 \ar@/_.8cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2 \ar[dr]|(.4)\hole^(.65){y_1} \ar[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.8cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){x_2\circ b_2}\\&G_0 &&P_3\ar[dr]_{n_1} \ar[dl]^{n_0}\ar[ur]^(.4){u_1}\ar[ul]_(.4){u_0}&&G'_2\\L_2 \ar@/^.8cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ e_1}|(.61)\hole&&Q_4 \ar[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0} &&Q_5\ar[ur]|(.4)\hole^(.65){z'_1} \ar[dl]|(.5)\hole_(.65){z_1} && R_0  \ar[ul]^(.35){y_1\circ e_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){e_0}\\&K_2 \ar[ur]_{n_0\circ w'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){w'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{n_1\circ w} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){w}\\&& R_2 \ar[ur]_{\hspace{-4pt}z_1\circ o_1}\ar@/^1cm/[uurr]^(.25){o_1}&& L_0 \ar[ul]^{z'_0\circ o_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){o_0} |(.69)\hole }\]
-
-	We have to construct the two dotted arrows in the diagram below.
-	\[\xymatrix@C=15pt{L_0 \ar[d]_{z'_0\circ o_0}&& K_0 \ar[d]_{n_1\circ w}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@{.>}@/^.35cm/[drrr]_(.4){\alpha_1}|(.285)\hole \ar[dr]|(.28)\hole_{y_1\circ e_0} && L_1 \ar@{.>}@/_.35cm/[dlll]^(.4){\alpha_2} \ar[dl]|(.28)\hole^{y_1\circ b_1}& K_1 \ar[d]^{d_2\circ u}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ a_1}\\G'_1 && \ar[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2  && \ar[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_2}\]
-
-	Consider the arrows $i_0\colon R_0\to D_1$ and $e_0\colon R_0\to Q_2$. An easy computation shows that
-	\begin{align*}
-		f_1\circ i_0&= h_0\\&=x_1\circ e_0
-	\end{align*}
-	entailing the existence of  the dotted $\alpha'_1\colon R_0\to P_2$ in the diagram
-	\[\xymatrix{R_0 \ar@{.>}[dr]^{\alpha'_1} \ar@/^.3cm/[drr]^{i_0} \ar@/_.3cm/[ddr]_{e_0}\\ &P_2 \ar[r]^{c_2} \ar[d]_{d_1}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
-	If we define $\alpha_1\colon R_0\to Q_3$ as $d_2\circ \alpha'_1$, then we easily get that 
-	\begin{align*}
-		x_2\circ \alpha_1&=x_2\circ d_2\circ \alpha'_1\\&= y_1\circ d_1\circ \alpha'_1\\&=y_1\circ e_0
-	\end{align*}
-
-	For $\alpha_2$, we proceed similarly. First consider  $i_1\colon L_1\to D_0$ and $b_1\colon L_1 \to Q_2$ and notice that
-	\begin{align*}
-		g_0\circ i_1&= m_1 \\&= x_1 \circ b_1
-	\end{align*}
-	implying the existence of $\alpha'_2\colon L_1\to P_3$ fitting in the diagram below.
-	\[\xymatrix{L_1 \ar@{.>}[dr]^{\alpha'_2} \ar@/^.3cm/[drr]^{i_1} \ar@/_.3cm/[ddr]_{b_1}\\ &P_3 \ar[r]^{u_0} \ar[d]_{u_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar[r]_{x_1} & G_1}\] 
-	Let $\alpha_2\colon L_1\to Q_5$ be $n_1\circ \alpha'_2$, then
-	\begin{align*}
-		z'_1 \circ \alpha_2 & = z'_1 \circ n_1\circ \alpha'_2\\&=y_1\circ u_1\circ \alpha'_2\\&=y_1\circ b_1
-	\end{align*}
-	The thesis now follows.  
-\end{proof}
-\fi
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{corollary}
+	contenuto...
+\end{corollary}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{corollary}
+	contenuto...
+\end{corollary}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{corollary}[No need for useless shifts]
+	contenuto...
+\end{corollary}
+\begin{proof}
+	contenuto...
+\end{proof}
+\newpage
+
+NOTES ON THE FUNDAMENTAL LEMMA WE NEED\todo{da integrare sopra}
+
+Everything is very tame, so that sequential independence coincides with switchability and we do not have ambiguity in the choice of an independence pair
+
+We start with the following situation.
+	\[\xymatrix@C=15pt{L_0\ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]_(.4){i_0}|(.285)\hole \ar[dr]|(.28)\hole_{h_0} && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.28)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar[dr]|(.28)\hole_{h_1} \ar@/^.35cm/[drrr]_(.4){j_0}|(.285)\hole  && L_2 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.28)\hole^{m_2}& K_2 \ar[d]^{k_2}\ar[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]^{h_2} \\G_0 && \ar[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2 && \ar[ll]^{f_2} D_2 \ar[rr]_{g_2}&& G_3 }\]
+
+	We can do two things:
+
+	FIRST SEQUENCE OF SWITCHINGS:
+
+	Switch the first two
+
+	\[\xymatrix@C=15pt{L_1\ar[d]_{f_0\circ i_1}&& K_1 \ar[d]_{k'_1}\ar[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){a_0}|(.285)\hole \ar[dr]|(.28)\hole_{h'_1} && L_0 \ar@/_.35cm/[dlll]^(.4){a_1} \ar[dl]|(.28)\hole^{m'_0}& K_0 \ar[d]^{k'_0}\ar[l]_{l_0} \ar[r]^{r_0} & R_0 \ar[dr]|(.28)\hole_{g_1\circ j_0} \ar@/^.35cm/[drrr]_(.4){b_0}|(.285)\hole  && L_2 \ar@/_.35cm/[dlll]^(.4){b_1} \ar[dl]|(.28)\hole^{m_2}& K_2 \ar[d]^{k_2}\ar[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]^{h_2} \\G_0 && \ar[ll]^{f'_0} D'_0 \ar[rr]_{g'_0}&& G'_1  && \ar[ll]^{f'_1} D'_1 \ar[rr]_{g'_1}&& G_2 && \ar[ll]^{f_2} D_2 \ar[rr]_{g_2}&& G_3 }\]
+
+	Moreover, we know that
+	\[m_0=f'_0\circ a_1 \qquad h_1=g'_1\circ a_0\]
+
+	Switch second and third 
+	\[\xymatrix@C=15pt{L_1\ar[d]_{f_0\circ i_1}&& K_1 \ar[d]_{k'_1}\ar[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){c_0}|(.285)\hole \ar[dr]|(.28)\hole_{h'_1} && L_2 \ar@/_.35cm/[dlll]^(.4){c_1} \ar[dl]|(.28)\hole^{f'_1\circ b_1}& K_2 \ar[d]^{k'_2}\ar[l]_{l_2} \ar[r]^{r_2} & R_2 \ar[dr]|(.28)\hole_{h'_2} \ar@/^.35cm/[drrr]_(.4){d_0}|(.285)\hole  && L_0 \ar@/_.35cm/[dlll]^(.4){d_1} \ar[dl]|(.28)\hole^{\hat{m}_0}& K_0 \ar[d]^{\hat{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]^{g_2\circ b_0} \\G_0 && \ar[ll]^{f'_0} D'_0 \ar[rr]_{g'_0}&& G'_1  && \ar[ll]^{\hat{f}_1} \hat{D}_1 \ar[rr]_{\hat{g}_1}&& G'_2 && \ar[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 }\]
+	And we know that
+	\[m'_0=\hat{f}_1\circ d_1 \qquad h_2=g'_2\circ d_0\]
+	\todo{qua abbiamo usato il secondo lemma dei tre passi (quello condizionale)}Since the rewriting system is very tame and using the three steps lemmas we can characterize $c_0\colon R_1\to \hat{D}_1$ and $c_1\colon L_2\to D'_0$ as the unique arrows fitting in the diagrams
+\[\xymatrix@R=15pt@C=15pt{&&R_1 \ar@/_1.2cm/[dddl]_(.4){a_0}|(.63)\hole\ar[dl]^{j_0}\ar[dd]^{c'_0} \ar@{.>}[dr]^{c_0}\\&D_2 \ar[dl]^(.4){f_2}&&\hat{D}_1 \ar[dr]^{\hat{g}_1}\\G_2 && P\ar[dr]_{p_4} \ar[ur]_{p_3}\ar[dl]^{p_1} \ar[ul]^{p_2}&&G'_2\\& D'_1 \ar[ul]^{g'_1}&&D'_2 \ar[ur]_{f'_2}}\]
+
+\[\xymatrix@R=15pt@C=15pt{&&L_2 \ar[dl]^{j_1} \ar@/_1.2cm/[dddl]_(.4){z_1}|(.63)\hole\ar[dd]^{c'_1} \ar@{.>}[dr]^{c_1}\\&D_1 \ar[dl]^(.4){f_1}&&D'_0 \ar[dr]^{g'_0}\\G_1 && Q\ar[dr]_{q_4} \ar[ur]_{q_3}\ar[dl]^{q_1} \ar[ul]_{q_2}&&G'_1\\& D_0 \ar[ul]^{g_0}&&D'_1 \ar[ur]_{f'_1}}\]
+
+	Switch first and second 
+	\[\xymatrix@C=15pt{L_2\ar[d]_{f'_0\circ c_1}&& K_2 \ar[d]_{\hat{k}_2}\ar[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){e_0}|(.285)\hole \ar[dr]|(.28)\hole_{\hat{h}_2} && L_1 \ar@/_.35cm/[dlll]^(.4){e_1} \ar[dl]|(.28)\hole^{\hat{m}_1}& K_1 \ar[d]^{\hat{k}_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){t_0} \ar[dr]|(.28)\hole_{\hat{g}_1\circ c_0}   && L_0  \ar[dl]|(.28)\hole^{\hat{m}_0} \ar@/_.35cm/[dlll]^(.4){t_1}& K_0 \ar[d]^{\hat{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]^{g_2\circ b_0} \\G_0 && \ar[ll]^{\hat{f}_0} \hat{D}_0 \ar[rr]_{\hat{g}_0}&& \hat{G}_1  && \ar[ll]^{\tilde{f}_1} \tilde{D}_1 \ar[rr]_{\tilde{g}_1}&& G'_2 && \ar[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 }\]
+	Moreover
+	\[f_0\circ i_1=\hat{f}_0\circ e_1 \qquad h'_2=\tilde{g}_1\circ e_0\]
+	and $(t_0, t_1)$ is characterized using again very tameness and the first $3$-steps Lemma as the unique arrows fitting in:
+	\[\xymatrix{&R_1 \ar[dl]_{a_0} \ar@{.>}[dr]^{t_0} \ar@/^.4cm/[dd]|\hole^(.6){c_0}\ar[d]_{t'_0}\\ D'_1 \ar[d]_{g'_1}&P\ar[d]_{p_3} \ar[r]^{p_4} \ar[l]_{p_1}&D'_2\ar[d]^{f'_2}\\G'_1&\hat{D}_1 \ar[l]^{\hat{f}_1}\ar[r]_{\hat{g}_1}& G'_2}\]
+
+	\[\xymatrix@R=15pt@C=15pt{&&L_ 0\ar[dl]^{a_1} \ar@/_1.2cm/[dddl]_(.4){d_1}|(.63)\hole\ar[dd]^{t'_1} \ar@{.>}[dr]^{t_1}\\&D'_0 \ar[dl]^(.4){g'_0}&&\tilde{D}_1 \ar[dr]^{\tilde{f}_1}\\G'_1 && S\ar[dr]_{s_4} \ar[ur]_{s_3}\ar[dl]^{s_1} \ar[ul]_{s_2}&&\hat{G}_1\\& \hat{D}_1 \ar[ul]^{\hat{f}_1}&&\hat{D}_0 \ar[ur]_{\hat{g}_0}}\]
+
+	SECOND SEQUENCE OF SWITCHINGS:
+
+	Switch third and second
+
+	\[\xymatrix@C=15pt{L_0\ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]_(.4){z_0}|(.285)\hole \ar[dr]|(.28)\hole_{h_0} && L_2 \ar@/_.35cm/[dlll]^(.4){z_1} \ar[dl]|(.28)\hole^{f_1\circ j_1}& K_2 \ar[d]^{\check{k}_2}\ar[l]_{l_2} \ar[r]^{r_2} & R_2 \ar[dr]|(.28)\hole_{\check{h}_2} \ar@/^.35cm/[drrr]_(.4){w_0}|(.285)\hole  && L_1 \ar@/_.35cm/[dlll]^(.4){w_1} \ar[dl]|(.28)\hole^{\check{m}_1}& K_1 \ar[d]^{\check{k}_1}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1\ar[d]^{g_2\circ j_0} \\G_0 && \ar[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar[ll]^{\check{f}_1} \check{D}_1 \ar[rr]_{\check{g}_1}&& \check{G}_2 && \ar[ll]^{\check{f}_2} \check{D}_2 \ar[rr]_{\check{g}_2}&& G_3 }\]
+	Moreover
+	\[m_1=\check{f}_1\circ w_1 \qquad h_2=\check{g}_2\circ w_0\]
+
+	Switch second and first
+		\[\xymatrix@C=15pt{L_2\ar[d]_{f_0\circ z_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){y_0}|(.285)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_0 \ar@/_.35cm/[dlll]^(.4){y_1} \ar[dl]|(.28)\hole^{\check{m}_0}& K_0 \ar[d]^{\check{k}_0}\ar[l]_{l_0} \ar[r]^{r_0} & R_0 \ar[dr]|(.28)\hole_{\check{g}_1\circ z_0} \ar@/^.35cm/[drrr]_(.4){x_0}|(.285)\hole  && L_1 \ar@/_.35cm/[dlll]^(.4){x_1} \ar[dl]|(.28)\hole^{\check{m}_1}& K_1 \ar[d]^{\check{k}_1}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1\ar[d]^{g_2\circ j_0} \\G_0 && \ar[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar[ll]^{\mathring{f}_1} \mathring{D}_1 \ar[rr]_{\mathring{g}_1}&& \check{G}_2 && \ar[ll]^{\check{f}_2} \check{D}_2 \ar[rr]_{\check{g}_2}&& G_3 }\]
+	As before we have
+	\[m_0=\check{f}_0\circ y_1 \qquad \check{h}_2=\mathring{g}_1\circ y_0\]
+	The really important thing to notice is that, by very tameness we have
+	\begin{align*}
+		f_0'\circ c_1&=f'_0\circ q_3\circ c'_1\\&=f_0\circ q_1\circ c'_1\\&=f_0\circ z_1
+	\end{align*}
+
+	\todo{GOOD! i primi match sono uguali, ora giochiamoci il primo lemma dei tre passi}
+
+	Switch second and third
+\[\xymatrix@C=15pt{L_2\ar[d]_{f_0\circ z_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){v_0}|(.285)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_1 \ar@/_.35cm/[dlll]^(.4){v_1} \ar[dl]|(.28)\hole^{\mathring{f}_1 \circ x_1}& K_1 \ar[d]^{\mathring{k}_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){u_0}|(.285)\hole\ar[dr]_{\check{h}_1}   && L_0 \ar@/_.35cm/[dlll]^(.4){u_1} \ar[dl]^{\mathring{m}_0}& K_0 \ar[d]^{\mathring{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0\ar[d]^{\check{g}_2\circ x_0} \\G_0 && \ar[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar[ll]^{\bar{f}_1} \bar{D}_1 \ar[rr]_{\bar{g}_1}&& \bar{G}_2 && \ar[ll]^{\bar{f}_2} \bar{D}_2 \ar[rr]_{\bar{g}_2}&& G_3 }\]
+
+\[\xymatrix@R=15pt@C=15pt{&&R_1 \ar@/_1.2cm/[dddl]_(.4){a_0}|(.63)\hole\ar[dl]^{j_0}\ar[dd]^{c'_0} \ar@{.>}[dr]^{c_0}\\&D_2 \ar[dl]^(.4){f_2}&&\hat{D}_1 \ar[dr]^{\hat{g}_1}\\G_2 && P\ar[dr]_{p_4} \ar[ur]_{p_3}\ar[dl]^{p_1} \ar[ul]^{p_2}&&G'_2\\& D'_1 \ar[ul]^{g'_1}&&D'_2 \ar[ur]_{f'_2}}\]
+
+\[\xymatrix@R=15pt@C=15pt{&&L_1 \ar[dl]^{w_1} \ar@/_1.2cm/[dddl]_(.4){i_1}|(.63)\hole\ar[dd]^{v'_1} \ar@{.>}[dr]^{v_1}\\&\check{D}_1 \ar[dl]^(.4){\check{f}_1}&&\check{D}_0 \ar[dr]^{g'_0}\\G_1 && \check{Q}\ar[dr]_{\check{q}_4} \ar[ur]_{\check{q}_3}\ar[dl]^{\check{q}_1} \ar[ul]_{\check{q}_2}&&\check{G}_1\\& D_0 \ar[ul]^{g_0}&&\mathring{D}_1 \ar[ur]_{\check{f}_1}}\]
+
+HUGE DIAGRAM
+
+\[\xymatrix@C=15pt{
+  & K_1 \ar[d]^{\hat{k}_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){t_0} \ar[dr]|(.28)\hole_{\hat{g}_1\circ c_0}   && L_0  \ar[dl]|(.28)\hole^{\hat{m}_0} \ar@/_.35cm/[dlll]^(.4){t_1}& K_0 \ar[d]^{\hat{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]^{g_2\circ b_0} \\G_0 && \ar[ll]^{\hat{f}_0} \hat{D}_0 \ar[rr]_{\hat{g}_0}&& \hat{G}_1  && \ar[ll]^{\tilde{f}_1} \tilde{D}_1 \ar[rr]_{\tilde{g}_1}&& G'_2 && \ar[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 \\
+	L_2\ar[d]_{f_0\circ z_1} \ar[u]^{f'_0\circ c_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/_.35cm/[urrr]^(.4){e_0}|(.285)\hole \ar[ur]|(.28)\hole^{\hat{h}_2} \ar@/^.35cm/[drrr]_(.4){v_0}|(.285)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_1 \ar@/^.35cm/[ulll]_(.4){e_1} \ar[ul]|(.28)\hole_{\hat{m}_1} \ar@/_.35cm/[dlll]^(.4){v_1} \ar[dl]|(.28)\hole^{\mathring{f}_1 \circ x_1}& K_1 \ar[d]^{\mathring{k}_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){u_0}|(.285)\hole\ar[dr]_{\check{h}_1}   && L_0 \ar@/_.35cm/[dlll]^(.4){u_1} \ar[dl]^{\mathring{m}_0}& K_0 \ar[d]^{\mathring{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0\ar[d]^{\check{g}_2\circ x_0} \\G_0 && \ar[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar[ll]^{\bar{f}_1} \bar{D}_1 \ar[rr]_{\bar{g}_1}&& \bar{G}_2 && \ar[ll]^{\bar{f}_2} \bar{D}_2 \ar[rr]_{\bar{g}_2}&& G_3 }\]
+
+Now, by determinism we have isomorphisms $\phi_{\check{D}_0}\colon \check{D}_0\to \hat{D}_0$ $\phi_{\check{G}_1}\colon \check{G}_1\to \hat{G}_1$
+Notice that
+\begin{align*}
+	\hat{f}_0\circ \phi_{\check{D}_0}\circ v_1&= \check{f}_0\circ v_1\\&=\check{f}_0\circ \check{q}_3\circ v'_1\\&=f_0\circ \check{q}_1\circ v'_1\\&=f_0\circ i_1\\&=\hat{f}_0\circ e_1
+\end{align*}
+
+GOOD: $\phi_{\check{D}_0}$ sends $v_1$ to $e_1$, thus it respects the match of $L_1$. Automatically it sends $v_0$ to $e_0$.
+
+CHECK THAT $\check{g}_2\circ x_0=g_2\circ j_0$
+
+USO IL PRIMO LEMMA DEI TRE PASSI:
+
+	\[\xymatrix{&R_0 \ar[dl]_{i_0} \ar@{.>}[dr]^{x_0} \ar@/^.4cm/[dd]|\hole^(.6){j_0}\ar[d]_{x'_0}\\ D_1 \ar[d]_{g_1}&P'\ar[d]_{p'_3} \ar[r]^{p'_4} \ar[l]_{p'_1}&\check{D}_2\ar[d]^{\check{g}_2}\\G_2&D_2 \ar[l]^{f_2}\ar[r]_{g_2}& G_3}\]
+
+\[\xymatrix@R=15pt@C=15pt{&&L_ 0\ar[dl]^{I_1} \ar@/_1.2cm/[dddl]_(.4){d_1}|(.63)\hole\ar[dd]^{t'_1} \ar@{.>}[dr]^{t_1}\\&D'_0 \ar[dl]^(.4){g'_0}&&\tilde{D}_1 \ar[dr]^{\tilde{f}_1}\\G'_1 && S\ar[dr]_{s_4} \ar[ur]_{s_3}\ar[dl]^{s_1} \ar[ul]_{s_2}&&\hat{G}_1\\& \hat{D}_1 \ar[ul]^{\hat{f}_1}&&\hat{D}_0 \ar[ur]_{\hat{g}_0}}\]
 
@@
 
-\section{ Domains for DPO-rewriting}
-
-\subsection{weak domains}
-
-\subsection{From adhesive grammars to weak domains}
-
-\section{Conclusions and further work}
-\todo{VERY NICE CONCLUSIONS}
-
-\bibliographystyle{plain}
-\bibliography{bibliog.bib}
-
-\appendix
-
-\section{A note on fillers and sequential independence}\label{app:fill}
- In \Cref{prop:equi} we proved that, in the linear case, the existence of an indpendence pair between two derivation is equivalent to that of a filler between them.
-This result can be further refined: in a\cite{baldan2011adhesivity} a class  $\mathbb{B}$ of (quasi)adhesive category is defined for which the local Church-Rosser Theorem holds even for left-linear DPO-rewriting system.
-In our language, and given \Cref{prop:fil} and \Cref{rem:locCR}, this amount to prove that, for elements of $\mathbb{B}$, every independence pair induces a filler.
-
-\begin{definition}Let $\X$ be a category, we say that $\X$ satisfies
-	\begin{itemize}
-		\item the \emph{mixed decomposition} property if for every diagram
-		\[\xymatrix{X \ar[d]_{a} \ar[r]^{f}& \ar[r]^{g} Y \ar[d]^{b}& Z \ar[d]^{c}\\ A \ar[r]_{h}& B \ar[r]_{k}& C}\]
-		whose outer boundary is a pushout and in which $k$ is a monomorphisms, 
-		\item the \emph{pushout decomposition} property
-	\end{itemize}
-\end{definition}
-
-\begin{lemma}
-	contenuto...
-\end{lemma}
-\begin{proof}
-	contenuto...\qedhere 
-\end{proof}
-
-\begin{corollary}
-	contenuto...
-\end{corollary}
-
-The following result shows that the mixed and pushout decomposition properties guarantee that every independence pair gives rise to a filler.
-
-\begin{theorem}
-	\todo{filler e classe B+}
-\end{theorem}
-\begin{proof}\qedhere 
-\end{proof}
-
-Our next step is to identify sufficient conditions for a category $\X$ to satisfy the mixed and pushout decomposition properties.
-
-\begin{definition}
-	\todo{classe B e class B+}
-\end{definition}
-
-\begin{example}
-\todo{esempi}
-\end{example}
-
-\begin{example}
-	\todo{esempi}
-\end{example}
-
-\begin{proposition}
-	\todo{da B a B+}
-\end{proposition}
-\begin{proof}
-	contenuto... \qedhere 
-\end{proof}
-\begin{lemma}\todo{due proprietà classe B}
-\end{lemma}
-\begin{proof}
-	\qedhere 
-\end{proof}
-
-\begin{corollary}
-	\todo{due proprietà classe B+}
-\end{corollary}
-
-\begin{corollary}
-	\todo{filler e classe B+}
-\end{corollary}
-
-\section{Rewriting systems on $\Set$.}\label{app:set}
-
-\section{On permutations}\label{app:perm}
-\todo{inserire risutati sulle permutazione che abbiamo usato}
-
-\end{document}
+\section{A class of well-behaved left-linear DPO-rewriting systems}

### 2024-11-20 full_version/fusione.tex
segmentazione

@@
-\documentclass[a4paper]{report}
+\documentclass[a4paper,twoside]{report}
+\usepackage{geometry}
 \usepackage{hyperref}
@@
 
+\includeonly{leftlinear.tex,permutations.tex}
+
 \begin{document}
@@
 
-\begin{abstract}
-\todo{	A VERY NICE ABSTRACT}
-\end{abstract}
-
 \tableofcontents
 
-\section*{Summary (with dependencies)}
+\include{introduzione.tex}
 
-\subsection*{REWRITING}
-\begin{itemize}
-\item DPO Rewriting in $\mathcal{M}$-adhesive categories, with left-$\mathcal{M}$-linear rules (from now on shortened in ``linear'')\\
-  Observe that rewriting is deterministic (by uniqueness of
-  PO-complement Corollary~\ref{lem:radj})
+\part{DPO rewriting and derivations}
 
-\item Category of abstract derivation for DPO-rewriting system $(\X, \R)$
-  \begin{itemize}
-  \item \emph{DPO-derivation category} $\dpo$: objects are graphs, arrows between possibly empty, derivations.
-  \item \emph{DPO-abstract decorated derivation category} $\dpi$
-  \end{itemize}
+ \include{leftlinear.tex}
+\include{permutations.tex}
 
-\item \emph{Consistent permutations} (Definition~\ref{def:permcon}):
-  permutation on the steps of two abstract decorated derivations and isomorphism between the colimits such
-  that arrows into the colimits ``commutes''.
-  \begin{enumerate}
-  \item It is unique for consuming rewriting systems
-    (Corollary~\ref{cor:unique})
-  \item They can be composed (Lemma~\ref{lem:sum})
-  \end{enumerate}
-\item
-
-\item Notions of independence\\
-  We have several possibile notions of independence for two direct
-  derivations $\dder{D} ; \dder{D'}$
-  \begin{enumerate}
-
-  \item \emph{Existence of a filler}
-    There is a filler for $\dder{D} ; \dder{D'}$
-    (Definition~\ref{def:filler})
-
-  \item \emph{Switchable}
-    There is $\dder{D}_1' ; \dder{D}_1$ which is a \emph{switch}
-    of $\dder{D} ; \dder{D'}$ (Definition~\ref{de:switch}, being a
-    switch is defined axiomatically) [actually, Definition~\ref{de:good-switchable} provides a definition of switchable which looks different to me, I would avoid this, to be checked]
-
-  \item \emph{(Weakly) Sequential independent} There is an
-    \emph{independence pair}
-    (Definition~\ref{de:sequential-independence}) They are called
-    \emph{strongly sequential independent} if the independence pair is
-    unique.
-  \end{enumerate}
-
-  We have that $(1) \Rightarrow (2)$ (Theorem~\ref{prop:fil}) and $(2) \Rightarrow (3)$ while
-  we expect that in general $(3) \not\Rightarrow (1)$ (but no
-  counterexample). This is instead known to hold for linear rules.
-
-  Some terminology (Definition~\ref{de:good-switchable})
-  \begin{itemize}
-
-  \item \emph{Tame rewriting systems}\\
-    An independence pairs induced by a filler is called \emph{good}
-    A rewriting system where all indepedence pairs are good is called
-    \emph{tame}
-
-    NOTE: the categories in which condition $B$
-    from~\cite{baldan2011adhesivity} identifies a large class of
-    (quasi)adhesive categories where left-linear systems are all
-    tame. Adapted here to M-adhesivity.
-
-  \item \emph{Very Tame rewriting systems}\\
-    Tame and existing indepence pairs are unique (hence switching is unique)
-    (see later for examples)
-  \end{itemize}
-
-\item \emph{Switch equivalent derivations} (concrete)\\
-  Definition~\ref{de:switchable}
-
-  THEOREM: Two switch equivalent derivations admit a consistent
-  permutation (Lemma~\ref{lem:consperm} ??).
-
-  A consequence of this used for proving that the slice of traces is a pre-order.
-
-  The converse holds only when rules are linear [proof clear, but not written]
-
-\end{itemize}
-
-\subsection*{CONCURRENCY}
-
-This part is dealt with for very tame rewriting systems and depends on this assumption. Note that
-\begin{itemize}
-\item Linear rewriting systems on adhesive categories are very tame
-\item Left-linear rewritint systems on graph-like categories with generalisation of (i) no isolated nodes in $L$ and (ii) right leg injective on nodes is very tame
-\item Graphs with equivalences (Egg) with left-leg regular mono, right leg mono is very tame
-\end{itemize}
-
-We show
-\begin{itemize}
-
-\item Three-steps lemma (Lemma~\ref{lem:iig1}), which is a weakened version of ``indepedence is global''.
-  \begin{itemize}
-
-  \item If in $abc$ I have that $ab$ are independent and $c$ is anticipated, they remain independent.
-  \item  If in $abc$ I have that $bc$ are independent and $a$ is moved to the end, they remain independent only if there is an additional condition (essentially requiring that $a$ was not a cause of $c$)
-  \end{itemize}
-
-\item No need of useless switchs (if two derivations are switch equivalent I can obtain one from another applying only inversions)
-
-\item weak prime domain e connected es semantics
-\end{itemize}
-
-\section{Introduction}
-
-\todo{A VERY NICE INTRODUCTION}
-
-SOME IDEAS (BADLY WRITTEN, JUST TO START TO PUT IDEAS IN ORDER)
-
-Graph-like structures are used in uncountably many setting for representing the dynamics of software systems: the graph represents the entities in the states and their relations, while rewriting steps, modifying the graph, model computational steps which produce state changes.
-
-Rewriting over graph-like structures is elegantly captured by
-DPO-rewriting over adhesive categories and their
-variants~\cite{lack2005adhesive,ehrig2006weak}.  This has been largely
-studied for so-called linear rewriting rules. Roughly speaking, with
-linear rules a rewriting step can express the fact that some entities
-in the current state are removed, some other are needed for the
-rewriting step to occur but preserved and some new entities are
-generated.
-
-The computation described by a rewriting system can be naturally
-interpreted as a distributed computation and a notion of independence
-between rewriting steps naturally emerges. When different rules are
-applied at ``distinct'' parts of the state, possibly overlapping on
-preserved items, the rewriting steps can be naturally deemed as
-independent and their application can occur in any order and possibly
-concurrently. This phenomenon is formally captured by the so-called
-Church-Rosser theorem of DPO rewriting and shift equivalence over derivations~\cite{CMREHL:AAGT}. This represent the basis for
-viewing sequences of rewriting in the DPO approach as concurrent
-computations and derive corresponding concurrent semantics. Derivation
-traces can be quotiented by an equivalence relation which identifies
-sequences of rewritings which differs only for the order of
-independent steps, leading to so-called derivation traces. In turn,
-the dependencies this setting can be captured by a classical structure
-in concurrency theory, the so-called prime event structures~\cite{NPW:PNES} where
-dependencies are reduced to causality and conflict~\cite{Handbook,Bal:PhD,Sch:RRSG}.
-
-In some situations linear rules are not sufficiently expressive for capturing the dynamic of a system.
-This is the case when  a computational step is required not only to consume, preserve and generated, but also ``merge'' parts of the state.
-This happens, e.g.,
-in nominal calculi where, as a result of name passing,
-the received name is identified with a local one at the
-receiver~\cite{CVY:ESSPE,Gad07} or in the modelling of bonding in biological/chemical processes~\cite{PUY:MBPE}.
- add EGGS, something about string diagrams?
-
-Technically, describing fusions, in the DPO jargon, requires to move from linear to left-linear rewriting rules.
-While left-linear rules have been considered in various instances (mainly for graph rewriting( and some results concerning the corresponding rewriting theory have been put forward, to the best of our knowledge the phenomena arising when rewriting with left-linear rules in the general setting of adhesive categories (which capture most ``applications'') have not been systematically explored.
-
-Here we perform this exploration by observing that a number of basic
-properties of rewriting which play a role in the corresponding
-rewriting and concurrency theory need a deep rethinking for
-left-linear rules and we propose solutions for the problems which
-arise.
-
-Firstly, Church-Rosser theorem does not work out of the box: the
-independence condition for adhesive categories does not extend
-smoothly to left-linear rules, i.e., existence of an independence pair
-does not ensure the possibility of switching two derivation and a
-refined notion, involving the concept of a so-called filler has to be
-introduced. The problem was identified already
-in~\cite{baldan2011adhesivity} where a suitable subclass of adhesive
-categories is identified where independence as induced by a filler
-coincide with independence as induced by an independence pair.
-
-Having a notion of independence between computation steps sits at the core of the possibility of viewing an execution trace as a concurrent computation.
-This is obtained by considering traces up to an equivalence that identifies traces differing only for the order of independent steps (e.g., interchange law~\cite{Mes92} in term rewriting, shift
-equivalence~\cite{CMREHL:AAGT} in graph rewriting or permutation
-equivalence~\cite{JJL80} in $\lambda$-calculus).
-While for linear rewriting systems this works smoothly, for left-linear ones one has to face the problem that if two rewriting steps $r_a r_b$ are independent, if we switch $r_a$ after $r_a$ and then switch it back we can obtain a computation which is not the original one, making the theory of derivation traces inconsistent.
-In order to solve this problem, we work in a subclass of adhesive categories where derivation steps can be switched in an ``essentially unique way''.
-We also identify a large class of adhesive categories, arising as presheaves, where the condition is automatically satisfied.
-[this solves also the previous problem, right?]
-
-Additionally, a central property for linear rewriting systems is the fact that independence of two rewriting steps is a global notion, independently of the context in which the rewritings take place.
-This is at the basis of the possibility of capturing the dependencies between rewriting steps in terms of two basic relations, causality and conflict, investigated in~~\cite{Handbook,Bal:PhD,Sch:RRSG}.
-
-This fails for left-linear rules where, as observed
-in~\cite{baldan2017domains}, for graph rewriting, the possibility of
-merging parts of the state leads to a sort of disjunctive causality,
-i.e., a rewriting step, say $r_c$ can be enabled by two different
-rewriting steps $r_a$ and $r_b$, in a way that in a derivation
-$r_a r_b r_c$ steps $r_b$ and $r_c$ are independent since the presence
-of $r_a$ in the past is sufficient for enabling $r_a$, while in
-$r_b r_c r_a$ , the steps $r_b$ and $r_c$ are not independent. The
-paper shows that for left-linear rewriting systems a special form of
-globality of independence can be recovered.
-
-The concurrent semantics of linear graph rewriting systems over
-adhesive categories can be captured by prime event structures and
-prime algebraic domains. The idea consists in considering a partially
-ordered domain, where elements are concurrent computations
-(derivations up to shift equivalence), and the order relates two
-computations when the latter is an extension of the former.
-%
-Events are then identified with computations consisting of a rewriting
-step with all its causes. This is generalised to adhesive categories
-in~\cite{heindel2009category}. [IS THIS IN TOBIAS?]
-
-In~\cite{baldan2017domains} it is observed for graph rewriting systems that the presence of fusions, the same event can be enabled by different minimal sets of events, i.e., a central property of the domain of configuration, namely stability, fails.
-This prevents the identification of a proper notion of causality and makes prime event structures and prime domains inadequate to represent computations with fusions.
-It is argued that the right class of structures capturing the concurrent behaviour in the presence of fusion are connected event structures and weak prime algebraic domains.
-%
-An event is still a computation that cannot be decomposed
-as the join of other computations, hence, in order theoretical terms,
-it is an irreducible.
-%
-However, due to unstability, irreducibles are not necessarily primes:
-two different irreducibles can represent the same computation step
-with different minimal enablings.  In~\cite{baldan2017domains} this
-is worked out for DPO rewriting systems over graphs. However the proof
-relies on a wrong characterisation of independence which fails for non
-linear rules. Here we rework in depth the result and extend it to DPO
-rewriting over a large class of adhesive categories.
-
-\include{permutations.tex}
+\part{Domains for DPO rewriting}
 
@@
 
-\todo{integrare sopra}
+\include{conclusion.tex}
+
+\iffalse 
 \newpage
@@
 \end{corollary}
-
-\section{Conclusions and further work}
-\todo{VERY NICE CONCLUSIONS}
+\fi
 
@@
 
+\iffalse
+
 \section{Rewriting systems on $\Set$.}\label{app:set}
@@
 \todo{inserire risutati sulle permutazione che abbiamo usato}
+\fi
 

### 2024-11-20 full_version/leftlinear.tex
segmentazione

--- 2024-11-14 full_version/permutations.tex
@@
-\chapter{DPO-rewriting and derivations}
+% !TeX root = ./fusione.tex
+
+\chapter{Left-linear DPO-rewriting systems}
 
@@
 We will recall the basic definitions and properties of this approach to abstract rewriting.
-
-\section{Left-linear DPO-rewriting systems}
+\section{First definitions and properties}
 We are now going to study rewriting systems in $\mathcal{M}$-adhesive categories.
@@
 \end{definition}
-
-\section{A theory of processes for left-linear DPO-rewriting systems}
-
-Given a DPO-rewriting system $(\X, \R)$,  we have already noted in \Cref{rem:func} that a derivation $\der{D}$  determines a diagram $\Delta(\der{D})$ in $\X$.
-We can then wonder if such a diagram has a colimit.
-Clearly if $\der{D}$ is the empty derivation $G$ then a colimit for $\Delta(\der{D})$ is simply the object $G$.
-More generally, we have the following result.
-
-\begin{lemma}\label{lem:colim}
-	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO-rewriting system over it. The following properties hold true:
-	\begin{enumerate}
-		\item  for eevery derivation $\der{D}$ is a derivation from $G$ to $H$, then the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belongs to $\mathcal{M}$.
-		\item Let $\der{D}$ be the concatenation $\der{D}_1\cdot \der{D}_2$ of two derivations $\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^{n_1}$ between $G$ and $H$ and $\der{D}_2=\{\dder{D}_{2,j}\}_{j=0}^{n_2}$ between $H$ and $T$,  then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists too and there is a pushout square
-		\[\xymatrix{H\ar[r]^-{\iota_{2, H}} \ar@{>->}[d]_-{\iota_{1, H}} & \tproi{D}{2} \ar[d]^{p_2}\\  \tproi{D}{1} \ar[r]_{p_1}& \tpro{D}}\]
-		where $(\tproi{D}{1}, \{\iota_{1, X}\}_{X\in \Delta(\der{D}_1)})$ and $(\tproi{D}{2}, \{\iota_{2, X}\}_{X\in \Delta(\der{D}_2)})$ are the colimiting cocone for $\Delta(\der{D}_1)$ and $\Delta(\der{D}_2)$, respectively.
-	\end{enumerate}
-\end{lemma}
-\begin{remark}\label{rem:cof}
-Let $I:\Deltamin(\dder{D})\to \Delta(\dder{D})$ be the inclusion functor.
-It is immediate to see that such functor is \emph{final} \cite{mac2013categories}.
-This means that for every functor $F\colon \Delta(\dder{D})\to \Y$ we have:
-\begin{enumerate}
-	\item if  $(C, \{c_X\}_{X\in \Deltamin(\dder{D})})$ is colimiting for $F\circ I$, then there exists a colimiting cocone $(D, \{d_X\}_{X\in \Delta(\dder{D})})$ for $F$;
-	\item $(C, \{c_X\}_{X\in \Deltamin(\dder{D})})$ and $(D, \{d_X\}_{X\in \Delta(\dder{D})})$ are colimiting for, repsectively, $F\circ I$ and $F$, then the canonical arrow $\phi\colon C\to D$ induced by $(D, \{d_X\}_{X\in \Deltamin(\dder{D})})$ is an isomorphism.
-\end{enumerate}
-\end{remark}
-
-\begin{proof}\begin{enumerate}
-		\item Let us proceed by induction on the length of $\der{D}$.
-
-	\smallskip \noindent $\lgh(\dder{D})=0$. then the $\tpro{\dder{D}}$ is simply $(G, \{\id{G}\})$ and $\id{G}\in \mathcal{M}$.
-
-	\smallskip \noindent$\lgh(\dder{D})=1$. Suppose that $\dder{D}$ has as its single component the derivation
-			\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G& \ar@{>->}[l]^{f} D \ar[r]_{g}& H  \\}\]
-			The arrow $f$ is  the pushout of $l$ and so it is in in $\mathcal{M}$. We can thus consider the $\mathcal{M}$-pushout square
-			\[\xymatrix{D \ar@{>->}[d]_{f} \ar[r]^{g} & H \ar@{>->}[d]^{p} \\G \ar[r]_{q}& P }\]
-			Since $p\in \mathcal{M}$, the thesis follows immediately from \Cref{rem:cof}.
-
-	\smallskip \noindent$\lgh(\dder{D})\geq 2$.
-Let $\der{D}$ be $\{\dder{D}_i\}_{i=0}^n$ with $n\geq 1$.
-Let also $\der{D}'$ be $\{\dder{D}_i\}^{n-1}_{i=0}$ and $\rho_n=(l_n, r_n)$ be the rule applied in $\dder{D}_n$.
-The arrow $f_n\colon D_n\to G_n$, being a pushout of $l_n$ is an element $\mathcal{M}$.
-By inductive hypothesis, $\iota_{G_{n}}\colon G_{n}\to \lpro \der{D}'\rpro$ is in $\mathcal{M}$ too, thus, we can consider the diagram below, having a pushout as its lower half.
-			\[\xymatrix{L_n \ar[d]_{m_{n}}& K_{n} \ar[d]^{k_{n}}\ar@{>->}[l]_{l_{n}} \ar[r]^{r_{n}} & R_{n} \ar[d]^{h_n} \\G_{n} \ar@{>->}[d]_{\iota'_{G_{n}}}& \ar@{>->}[l]^{f_n} D_n \ar[r]_{g_n}& H  \ar@{>->}[d]^{q}\\ \lpro \der{D}' \ar[rr]_{p}\rpro && P}\]
-			Notice that, as in the point above, the arrow $q\colon H\to P$ is the pushout of an element in $\mathcal{M}$, therefore it is enough to show that the diagram so constructed provides a colimiting cocone for $\Delta(\der{D})$.
-
-			Let $(C, \{c_X\}_{X\in \Delta(\der{D})})$ be a cocone, since $\Delta(\der{D}')$ is a subdiagram of $\Delta(\der{D})$, we get another cocone $(C, \{c_X\}_{X\in \Delta(\der{D}')})$ which induces an arrow $c'\colon \lpro \der{D}' \rpro \to C$ such that
-			\begin{align*}
-				c'\circ \iota_{G_n} \circ f_n &=c_{G_n} \circ f_n\\&= c_{D_n}\\&= c_{H}\circ g_n
-			\end{align*}
-			Therefore the arrows $c'$ and $c_H$ induce a morphism $c\colon P\to C$ and the thesis now follows at once.
-
-		\item  As a first step, notice that $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D}_1)})$ and $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D}_2)})$ are cocone on, respectively, $\Delta(\der{D}_1)$ and $\Delta(\der{D}_2)$.
-Hence, there exist two arrows $p_1\colon \tproi{D}{1}\to \tpro{D}$, $p_2\colon \tproi{D}{2}\to \tpro{D}$ such that, for every $X\in  \Delta(\der{D}_1)$ and $Y\in  \Delta(\der{D}_2)$
-		\[p_1\circ \iota_{1, X} = \iota_X \qquad p_2\circ \iota_{2, Y}=\iota_{2,Y}\]
-		In particular, this entails the commutativity of the square
-				\[\xymatrix{H \ar[dr]^{\iota_H} \ar[r]^-{\iota_{2, H}} \ar@{>->}[d]_-{\iota_{1, H}} & \tproi{D}{2} \ar[d]^{p_2}\\  \tproi{D}{1} \ar[r]_{p_1}& \tpro{D}}\]
-
-	Let us now show that the square above is a pushout.
-Take two arrows $a\colon \tproi{D}{1}\to C$, $b\colon \tproi{D}{2}\to C$ such that $a\circ \iota_{1, H}=b\circ \iota_{2, H}$.
-We can use the previous equality to define a cocone $(C, \{c_X\}_{X\in \Delta(\der{D})})$ putting:
-	\[c_X:=\begin{cases}
-		a\circ \iota_{1, X} & X\in \Delta(\der{D}_1)\\
-		b\circ \iota_{2, X} & X\in \Delta(\der{D}_2)
-	\end{cases}\]
-From this, we can deduce at once the existence of a unique $c\colon \tpro{D}\to C$ such that $c\circ \iota_X = c_X$.
-By construction, for every $X\in  \Delta(\der{D}_1)$ and $Y\in  \Delta(\der{D}_2)$ we have
-\[\begin{split}
-	c\circ p_1 \circ \iota_{1,X}&=c\circ \iota_{X}\\&=c_X \\&=a\circ \iota_{1,X}\\&=a\circ p_1\circ \iota_{1,X}
-\end{split}\qquad \begin{split}
-	c\circ p_2 \circ \iota_{2,Y}&=c\circ \iota_{Y}\\&=c_Y \\&=b\circ \iota_{2,Y}\\&=b\circ p_2\circ \iota_{2,Y}
-\end{split}\]
-Therefore we get that $c\circ p_1=a$ and $c\circ p_2 = b$.
-
-	For uniqueness, suppose that $c'\colon \tpro{D}\to C$ is such that $c'\circ p_1=a$ and  $c'\circ p_2 = b$. Then, for every $X\in \Delta(\der{D})$ we have
-\begin{align*}
-	c'\circ \iota_X &= \begin{cases}
-	c'\circ p_1\circ \iota_{1, X} & X\in \Delta(\der{D}_1)\\
-	c'\circ p_2\circ \iota_{2, X} & X\in \Delta(\der{D}_2)
-	\end{cases}\\&=\begin{cases}
-a\circ \iota_{1, X} & X\in \Delta(\der{D}_1)\\
-b\circ \iota_{2, X} & X\in \Delta(\der{D}_2)
-	\end{cases}\\&=c_X\\&=c\circ \iota_X
-\end{align*}
-showing that $c'=c$ as wanted.	 \qedhere 
-	\end{enumerate}
-\end{proof}
-
-\begin{corollary}\label{cor:colim}
-Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ a derivation of length $n+1$ and fix an index $j\in[0,n]$. Define
-\[\der{D}^j_1:=\{\dder{D}_i\}_{i=0}^{j-1} \qquad  \der{D}^j_2=\{\dder{D}_j\} \qquad \der{D}^j_3:=\{\dder{D}_i\}_{i=j+1}^n\]
-with the convention that $\der{D}^0_1$ and $\der{D}^n_3$ are the empty derivation on, respectively, $G_0$ and $G_n$. Then the square below is a pushout and a pullback
-\[\xymatrix@C=30pt{D_{j} \ar[ddrr]^{\iota_{D_j}} \ar[r]^{g_j}\ar@{>->}[d]_{f_j}& G_{j+1} \ar[ddr]^{\iota_{G_{j+1}}} \ar[r]^-{\iota_{3, G_{j+1}}} & \lpro \der{D}^j_3\rpro \ar[dd]^{p_2} \\ G_j\ar[drr]_{\iota_{G_{j}}} \ar@{>->}[d]_{\iota_{1,G_j}}\\ \lpro \der{D}^j_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
-Where the two arrows $p_1\colon \lpro\der{D}^j_1 \rpro\to \tpro{D}$, $p_2\colon \lpro \der{D}^j_3\rpro \to \tpro{D}$ are induced by the cocones $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}^j_1)})$ and $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}^j_3)})$, respectively.
-\end{corollary}
-\begin{remark}
-If $\der{D}$ is empty then $\der{D}^j_1, \der{D}^j_2$ and $\der{D}^j_3$ are empty too.
-\end{remark}
-\begin{proof}
-We can notice that $\der{D}=\der{D}^j_1\cdot \der{D}^j_2 \cdot \der{D}^j_3$.
-By the first and the second point of \Cref{lem:colim} then we get the following diagram, in which all squares are $\mathcal{M}$-pushouts.
-
-\[\xymatrix@C=30pt{D_{j}  \ar[r]^{g_j}\ar@{>->}[d]_{f_j}& G_{j+1}  \ar[r]^-{\iota_{3,G_{j+1}}} \ar[d]_{\iota_{2, G_{j+1}}}  \ar@/^.5cm/[dd]^{\iota_{1,2, G_{j+1}}}& \lpro \der{D}^j_3\rpro \ar[dd]^{p_2} \\ G_j \ar[r]^{\iota_{2, G_j}}\ar@{>->}[d]_{\iota_{1,G_j}} & \lpro \der{D}^j_2\rpro \ar[d]_a\\ \lpro \der{D}^j_1 \rpro \ar@/_.4cm/[rr]_{p_1} \ar[r]^b &\lpro \der{D}^j_1\cdot \der{D}^j_2 \rpro \ar[r]^c&\tpro{D} }\]
-Applying \Cref{lem:po1} twice we get that the whole square is an $\mathcal{M}$-pushout. Then the thesis follows from \Cref{prop:pbpoad}.
-\end{proof}
-
-\begin{remark}\label{rem:zero1} In particular, considering $j=0$ or $j=n$, we get that the following two squares are $\mathcal{M}$-pushouts and, thus, pullbacks.
-	\[\xymatrix{D_0 \ar[r]^-{\iota_{3, D_0}} \ar@{>->}[d]_{f_0}& \lpro \der{D}^0_3 \rpro \ar@{>->}[d]^{p_2} &D_n \ar@{>->}[d]_{\iota_{1, D_n}}\ar[r]^{g_n}& G_n \ar@{>->}[d]^{\iota_{G_n}}\\ G \ar[r]_{\iota_G}& \tpro{D} & \lpro \der{D}^n_1 \rpro \ar[r]_{p_1}  & \tpro{D}}\]
-\end{remark}
-
-\begin{corollary}\label{cor:ele}
-	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ be a derivation between $G$ and $H$.
-Let $j$ and $k$ be two indexes less or equal than $n+1$ and suppose that $j< k$.
-Consider two arrows $a\colon T\to G_j$, $b\colon T\to G_k$.
-If $\iota_{G_j}\circ a = \iota_{G_k}\circ b$,
-	then  there exist a unique arrow $c\colon T\to D_j $  such that \[f_j\circ c = a\qquad \iota_{D_j}\circ c =\iota_{G_k}\circ b\]
-	\end{corollary}
-\begin{proof} Consider the diagram
-			\[\xymatrix@C=34pt{T  \ar@/_.6cm/[dd]_{a}\ar@{.>}[d]^{c}\ar[rr]^{b}&& G_k \ar[d]_{\iota_{3, G_k}} \ar@/^.6cm/[ddd]^{\iota_{G_k}}\\D_{j} \ar[r]^{g_j} \ar[ddrr]^{\iota_{D_j}}\ar@{>->}[d]^{f_j}& G_{j+1} \ar[r]^-{\iota_{3,G_{j+1}}} \ar[ddr]^{\iota_{G_{j+1}}} & \lpro \der{D}^j_3\rpro \ar[dd]_(.6){p_2} \\ G_j \ar@{>->}[d]_{\iota_{1,G_j}} \ar[drr]_{\iota_{G_j}}\\ \lpro \der{D}^j_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
-			Thanks to \Cref{cor:colim} we know that the bottom right rectangle in the diagram above is a pullback and the thesis follows at once.
-\end{proof}
-
-\subsection{Semi-consistent and consistent permutations}
-
-Equipped with the theory developed so far, we can introduce the notions of \emph{semi-consistent} and \emph{consistent} permutation.
-
-\begin{definition}[(Semi)-consistent permutation]\label{def:permcon}
-	Let $\X$ be an $\mathcal{M}$-adhesive category and consider a left-linear DPO-rewriting system $(\X, \R)$ on it.
-Consider two decorated derivations $(\der{D}, \alpha, \omega)$ and  $(\der{D}', \alpha', \omega')$ with the same length $l$ and with isomorphic sources and targets.
-Let also $r(\der{D})=\{\rho_i\}_{i=0}^{l-1}$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^{l-1}$	be sequences of rules associated to the two derivations.
-
-	A \emph{semi-consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma\colon [0,l-1]\to [0,l-1]$  such that, for every $i\in [0,l-1]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
-	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_\sigma}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro}\]
-	\[\xymatrix@C=30pt{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
-
-	A semi-consistent permutation is \emph{consistent} if the following square commutes too.
-	\[\xymatrix@C=30pt{ \pi(G_{l}) \ar[r]^{\omega} \ar[d]_{\omega'} & G_{l} \ar@{>->}[r]^{\iota_{G_{l}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\  G'_{l} \ar@{>->}[rr]_{\iota'_{G'_{l}}} & &\lpro \der{D}' \rpro}\]
-\end{definition}
-
-\begin{remark}\label{rem:inversa}
-	Let $\sigma\colon [0,n]\to [0,n]$ be a consistent permutation between $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, then its inverse $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$.
-Indeed, it is enough to consider, as mediating isomorphism, the inverse $\xi^{-1}_\sigma$ of $\xi_\sigma$.
-\end{remark}
-
-\begin{example}\label{rem:empty2}
-	Let $(\{G\}, \alpha, \omega)$ and $(\{G'\}, \alpha', \omega')$ be two derivations of length $0$.
-Then $\id{\emptyset}$ is a consistent permutations between them if and only if there exists an isomorphism $\phi\colon G_0\to G'_0$ fitting in the diagrams below
-	\[\xymatrix@C=15pt{&\pi(G) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G\ar[rr]_{\phi} && G' &G \ar[rr]_{\phi} && G' } \]
-	That is, by \Cref{rem:empty} if and only if they are abstract equivalent decorated derivations.
-\end{example}
-
-\begin{remark} Notice that if $\sigma$ is a semi-consistent permutation between two derivations  $\der{D}$ and $\der{D}'$ of length $l$, then for every  $i\in [0,l-1]$ the diagram below commutes.
-	\[\xymatrix@C=40pt{G_i\ar@/^1cm/[rrr]^{\iota_{G_{i}}}&D_i\ar@/^.4cm/[rr]^(.35){\iota_{D_i}} \ar[r]_{g_i} \ar@{>->}[l]^{f_i}&G_{i+1} \ar[r]_{\iota_{G_{i+1}}}&\tpro{D} \ar[dd]^{\xi_\sigma}\\  L_i \ar[u]^{n_i} \ar[d]_{n'_{\sigma(i)}}& K_i \ar[d]^{k'_{\sigma(i)}} \ar[u]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i} &R\ar[u]^{h_i} \ar[d]_{h'_{\sigma(i)}}\\G'_{\sigma(i)}\ar@/_1cm/[rrr]_{\iota'_{G'_{\sigma(i)}}} &D'_{\sigma(i)}\ar@{>->}[l]_{f'_{\sigma(i)}} \ar[r]^{g'_i} \ar@/_.4cm/[rr]_(.35){\iota'_{D'_{\sigma(i)}}}&G'_{\sigma(i)+1} \ar[r]^{\iota'_{G'_{\sigma(i)+1}}}& \lpro\der{D}' \rpro }\]
-
-	This follows at once from the following chain of identities:
-	\begin{align*}
-		\xi_\sigma \circ \iota_{D_i}\circ k_i&=\xi_\sigma \circ \iota_{G_{i}} \circ f_i\\&= \xi_\sigma \circ \iota_{G_{i}}\circ m_i \circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ m'_i\circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ f'_{\sigma(i)}\circ k'_i\\&=\iota_{D'_\sigma(i)}\circ k_i'
-	\end{align*}
-\end{remark}
-
-\begin{remark}\label{rem:coproj}
-	Notice that, in particular, the previous diagram entails
-	\[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
-\end{remark}
-
-The previous remark allows us to prove the following.
-
-\begin{lemma}\label{prop:isouno} For every semi-consistent permutation $\sigma$ between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, the mediating isomorphism $\xi_\sigma\colon \tpro{D}\to \lpro \der{D}'\rpro$ is unique.
-\end{lemma}
-\begin{proof} Let $\xi'_\sigma$ be another mediating isomorphism, then by \Cref{rem:coproj} we have
-	\[\begin{split}
-		\xi_\sigma \circ \iota_{L_i}&=\iota'_{L_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{L_i}
-	\end{split} \qquad \begin{split}
-		\xi_\sigma \circ \iota_{K_i}&=\iota'_{K_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{K_i}
-	\end{split} \qquad \begin{split}
-		\xi_\sigma \circ \iota_{R_i}&=\iota'_{R_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{R_i}
-	\end{split}\]
-
-	Now, notice that 
-	\begin{align*}
-		\xi_\sigma \circ \iota_{G_0}&=\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}\\&=\xi'_\sigma \circ \iota_{G_0}
-	\end{align*}
-
-	If $\lgh(\der{D})=0$ this is enough to conclude, otherwise we are going to prove by induction that, for every $i\in [0, \lgh(\der{D})-1]$, $\xi_\sigma \circ \iota_{G_i}=\xi'_\sigma\circ \iota_{G_i}$.
-
-	\smallskip \noindent $i=0$. This is simply the result obtained before.
-
-	\smallskip \noindent $i >0$. If $i>0$, we know that there is a pushout square
-	\[\xymatrix{K_{i-1}\ar[r]^{r_{i-1}} \ar[d]_{k_{i-1}}& R_{i-1} \ar[d]^{h_{i-1}}\\ D_{i-1} \ar[r]_{g_{i-1}}& G_i}\] 
-	By \Cref{rem:coproj} and the induction hypothesis we know that
-	\[\begin{split}
-		\xi_\sigma \circ \iota_{G_i}\circ h_{i-1}&=  \xi_\sigma\circ \iota_{R_{i-1}}\\&=\iota'_{R_{\sigma(i-1)}}\\&=\xi'_{\sigma}\circ \iota_{R_{i-1}}\\&=\xi'_{\sigma} \circ \iota_{G_i}\circ h_{i-1}\\&
-	\end{split} \qquad
-	\begin{split}
-		\xi_\sigma \circ \iota_{G_i}\circ g_{i-1}&=\xi_{\sigma}\circ \iota_{D_{i-1}}\\&=\xi_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi'_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi'_{\sigma}\circ \iota_{D_{i-1}} \\&=\xi'_{\sigma}\circ \iota_{G_{i}} \circ g_{i-1}
-	\end{split}
-	\]
-
-	Since $\xi_\sigma \circ \iota_{D_i}$ must be $\xi_\sigma \circ \iota_{G_i}\circ f_i$, we also have
-	$\xi_\sigma \circ \iota_{D_i}=\xi'_\sigma \circ \iota_{D_i}$
-	and the thesis follows.
-\end{proof}
-
-As a next step, we will show that the existence of abstraction equivalences satisfying certain coherence conditions is enough to guarantee the (semi-)consistency of the identical permutation.
-
-\begin{proposition}\label{rem:abscons}
-	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations in an left-linear rewriting system $(\X, \R)$ of length $l$.
-Let also $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ be an abstraction equivalence between $\der{D}$ and $\der{D}'$.
-If $\alpha'\circ \phi_{G_0}=\alpha$ then the the identity $\id{[0,l-1]}$ is a semi-consistent permutation.
-If, moreover, $\omega'\circ \phi_{G_{l}}=\omega$, then $\id{[0,l-1]}$ is a consistent one.
-\end{proposition}
-\begin{proof}
-	For every $X\in \Deltamin(\der{D}) $, let $X'$ the codomain of $\phi_X$.
-Then we can define $\xi_{\id{[0,l-1]}}\colon \tpro{D}\to \lpro \der{D}'\rpro$ as the unique morphism such that, for every $X\in \Deltamin(\der{D})$,
-	\[\xi_{\id{[0,l-1]}} \circ \iota_{X}= \iota'_{X'}\circ \phi_X\]
-
-As a first step we can notice that $\xi_{\id{[0,l-1]}}$ is an isomorphism: indeed we can define $\Theta\colon \lpro\der{D}'\rpro \to \tpro{D}$ as the unique arrow satisfying, for every $X'\in \Deltamin(\der{D}')$
-\[\Theta \circ \iota'_{X'}= \iota_{X}\circ \phi^{-1}_X\]
-
-From the following two computations we can derive that $\Theta$ is the inverse of $\xi_{\id{[0,l-1]}}$.
-\[\begin{split}
-	\Theta \circ \xi_{\id{[0,l-1]}}\circ \iota_{X}&=\Theta \circ\iota'_{X'}\circ \phi_X\\&=\iota_{X}\circ \phi^{-1}_X\circ \phi_X\\&=\iota_X 
-\end{split}\qquad \begin{split}
-\xi_{\id{[0,l-1]}}\circ \Theta \circ \iota'_{X'}&=\xi_{\id{[0,l-1]}}\circ \iota_X\circ \phi^{-1}_{X}\\&=\iota'_{X'}\circ \phi_X\circ \phi^{-1}_{X}\\&=\iota'_{X'}
-\end{split}\]
-
-To conclude, let us observe that all the internal subdiagrams of the following diagrams commutes, guaranteeing the commutativity of the full ones.
-\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[dl]^{\phi_{G_0}} \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro}\]
-\[\xymatrix@C=30pt{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[dl]^{\phi_{G_i}} \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}} & R_i \ar[r]^{h_i} \ar[d]_{h'_{i}}& G_{i+1} \ar[dl]^{\phi_{G_{i+1}}}\ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}} \\G'_{i} \ar[rr]_{\iota'_{G'_{i}}}&& \lpro \der{D}' \rpro& G'_{i+1} \ar[rr]_{\iota'_{G'_{i+1}}}&& \lpro \der{D}' \rpro}\]
-
-For the last half of the thesis, we can reason similarly. Indeed, the diagram below commutes.
-\[\xymatrix@C=30pt{\pi(G_l)\ar[r]^{\omega} \ar[d]_{\omega'} & G_l \ar[dl]^{\phi_{G_l}} \ar[r]^{\iota_{G_l}} &\tpro{D} \ar[d]^{\xi_{\id{[l, l-1]}}}\\ G'_l \ar[rr]_{\iota'_{G'_l}} & &\lpro \der{D}' \rpro}\]
-This clearly entails the thesis.
-\end{proof}
-
-The previous proposition, in turn, gives us a technical but quite useful result.
-
-\begin{corollary}\label{cor:fromsemitocons}
-			Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations in an left-linear rewriting system $(\X, \R)$ of length $l$.
-Let also $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ be an abstraction equivalence between $\der{D}$ and $\der{D}'$ such that  $\alpha'\circ \phi_{G_0}=\alpha$.
-If  the identity $\id{[0,l-1]}$ is a consistent permutation, then $\omega'\circ \phi_{G_l}=\omega$, so that $(\der{D}, \alpha, \omega) \equiv_a (\der{D}', \alpha', \omega')$.
-\end{corollary}
-\begin{proof}
-	Let $\xi_{\id{[0, l-1]}}$ be the isomorphism $\tpro{D}\to \lpro\der{D}'\rpro$ witnessing the consistency of $\id{[0, l-1]}$.
-By \Cref{prop:isouno} and \Cref{rem:abscons}, we know that $\xi_{\id{[0,l-1]}} \circ \iota_{X}= \iota'_{X'}\circ \phi_X$ for every object $X\in \Deltamin(\der{D})$.
-Then we have
-	\begin{align*}
-		\iota'_{ G'_{l}}\circ \phi_{G_l}\circ \omega&=\xi_{\id{[0, l-1]}}\circ \iota_{G_l}\circ \omega\\&=\iota'_{G'_l}\circ \omega'
-	\end{align*}
-
-	By the first point of \Cref{lem:colim}, $\iota'_{ G'_{l}}$ is mono and we can conclude.
-\end{proof}
-
-\begin{remark}\label{rem:abscons2}
-	In particular, given a decorated derivation $(\der{D}, \alpha, \omega)$ with source $G$ and target $H$ and two isomorphisms, $\phi\colon G'\to G$ $\psi\colon H\to H'$ be two isomorphisms, we know, by \Cref{rem:absequi}, that \[(\der{D}, \alpha, \omega)\equiv_a (\phi*\der{D}, \phi^{-1}\circ \alpha, \omega ) \qquad (\der{D}, \alpha, \omega)\equiv_a (\der{D}*\psi, \alpha, \psi \circ \omega )\]
-	In these cases, if the cocones $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$, $(\lpro \phi *\der{D} \rpro, \{\iota'_X\}_{X\in \Delta(\phi *\der{D})})$ and $(\lpro \der{D}*\psi \rpro, \{\iota'_X\}_{X\in \Delta(\der{D}*\psi)})$ are colimiting, we can take as mediating isomorphisms, respectively, the unique arrows $\Gamma^{\phi} \colon \tpro{D}\to \lpro \phi*\der{D} \rpro$ and $\Gamma_\psi\colon \tpro{D}\to \lpro \der{D}*\psi \rpro$  such that, for every $X\in \Deltamin(\der{D})$:
-	\[\Gamma^\phi \circ \iota_X:=\begin{cases}
-		\iota'_{G'}\circ \phi^{-1}  & X=G\\
-		\iota'_X & \text{otherwise}
-	\end{cases} \qquad \Gamma_\psi \circ \iota_X:=\begin{cases}
-		\hat{\iota}_{H'}\circ \psi  & X=H\\
-		\hat{\iota}_X & \text{otherwise}
-	\end{cases}\]
-\end{remark}
-
-\begin{example}\todo{identita consistente non implica astrazione}Notice that, in general, there cannot, in general, be generalized to non-empty derivations. A counterexample is the following one.
-\end{example}
-
-We can also observe that (semi-)consistent permutations can be composed, as shown by the next proposition.
-
-\begin{proposition}\label{rem:comp}  Let $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$ be three decorated derivations of length $l$.
-Let $\sigma$ be a consistent permutation between the first two and $\tau$ one between the second and the third, then $\tau \circ \sigma$ is a semi-consistent permutations between the first and the third.
-If, moreover, $\sigma$ and $\tau$ are consistent, then $\tau \circ \sigma$ is consistent too.
-\end{proposition}
-
-\begin{proof} Let $l$ be the length of the three given derivations.
-By hypothesis each subdiagram of the following ones commutes, thus the whole diagrams commute too, proving that $\tau\circ \sigma$ is a semi-consistent permutation with mediating isomorphism given by $\xi_{\tau} \circ \xi_\sigma$.
-		\[\xymatrix@C=18pt{ & G_0 \ar[rr]^{\iota_{G_0}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G_0) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G'_0 \ar[rr]^{\iota'_{G'_0}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\tau}}\\ &\hat{G}_0  \ar[rr]_{\hat{\iota}_{\hat{G}_0}}&& \lpro \hat{\der{D}}\rpro }\]
-		\[\xymatrix@C=18pt{& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_{i+1} \ar[rr]^{\iota_{G_{i+1}}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\tau(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\tau}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\tau(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)+1} \ar[rr]^{\iota'_{G'_{\sigma(i)+1}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\tau}}\\ &\hat{G}_{\tau(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\tau(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\tau(\sigma(i))+1} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\tau(\sigma(i))+1}}}&& \lpro \hat{\der{D}} \rpro	}\]
-
-	If, in addition, $\sigma$ and $\tau$ are consistent then we also have the commutativity of the following additional diagram.
-	\[\xymatrix@C=18pt{&   G_{l} \ar@{>->}[rr]^{\iota_{ G_{l}}} &&\tpro{D} \ar[d]^{\xi_\sigma}\\ \pi({ G_{l}})\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & { G'_{l}} \ar@{>->}[rr]^{\iota'_{{ G'_{l}}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\tau}}\\& \hat{G}_l \ar@{>->}[rr]_{\hat{\iota}_{\hat{G}_l}}&& \lpro \hat{\der{D}} \rpro}\]
-
-	Again this proves that $\xi_\tau \circ \xi_\sigma$ witnesses the constistency of $\tau\circ \sigma$.
-\end{proof}
-
-\subsubsection{Restricting  consistent permutations}
-Now that we have established some initial facts about consistent permutations, we are going to embark in a, quite long, voyage to explore how to restrict them to suitable subderivations.
-
-\begin{lemma}\label{rem:dett}
-	Let $(\der{D}, \alpha, \omega)$ be the composite $(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)$ of two derivation of length $l_1$ and $l_2$. Suppose that:
-\[r(\der{D}_1)=\{\rho_{1,i}\}_{i=0}^{l_1-1} \quad r(\der{D}_2)=\{\rho_{2,i}\}_{i=0}^{l_2-1} \quad  r(\der{D})=\{\rho_{i}\}_{i=0}^{l_1+l_2-1}\]
-and let  $G_{1,0}, G_{2,0}$ and $G_{0}$ be the sources of $\der{D}_1$, $\der{D}_2$,  and $\der{D}$.
-Similary, denote, by $G_{1,i+1}, G_{2,i+1}$ and $G_{i+1}$ the results of the application of, respectively, $\rho_{1,i}, \rho_{2,i}, \rho_i$ to $G_{1,i}, G_{2,i}$ and $G_{i}$  in the corresponding derivation.
-Then there are arrows $q_1\colon \lpro \der{D}_1\rpro \to \tpro{D}$, $q_2\colon \lpro \der{D}_2\rpro \to \tpro{D}$ such that
-\[q_1\circ \iota_{G_{1,0}}\circ \alpha_1 = \iota_{G_{0}}\circ \alpha \qquad q_2\circ \iota_{G_{2,l_2}}\circ \omega_2 = \iota_{G_{l_1+l_2}}\circ \omega \]
-and, for every $i\in [0, l_1-1]$, $j\in [l_1+1, l_1+l_2]$
-	\[q_1\circ \iota_{1, G_{1,i}}=\iota_{G_{i}}\qquad q_2\circ \iota_{2, G_{2,j}}=\iota_{G_{j+l_1}} \]
-\end{lemma}
-\begin{proof}According to \Cref{def:conc}, we have three cases.
-\begin{itemize}
-	\item $\lgh(\der{D}_1)=0$.
-Then  $(\der{D}, \alpha, \omega)$ is $(\der{D}_2, \alpha_2\circ \omega_1^{-1}\circ \alpha_1, \omega_2)$ thus we can take as $q_2$ the identity on $\lpro \der{D}_2\rpro$.
-Moreover, in this case $\iota_{1,G_{1,0}}$ is an isomorphism, so that we can take as $q_1$ the composition $\iota_{G_0}\circ \alpha_2\circ \omega^{-1}_1 \circ \iota^{-1}_{1,G_{1,0}}$.
-	\item $\lgh(\der{D}_1)\neq 0$ and $\lgh(\der{D}_2)=0$ .
-Hence  $(\der{D}, \alpha, \omega)$ is $(\der{D}_1, \alpha_1, \omega_1 \circ \alpha^{-1}_2\circ \omega_2)$.
-We can then define $q_1$ as $\id{\lpro \der{D}_1\rpro}$.
-Since $\iota_{2,G_{2,0}}$ is an isomorphism, $q_2$ can be taken as  $\iota_{G_{l_1+l_2}}\circ  \omega_1  \circ \alpha^{-1}_2 \circ \iota^{-1}_{2,G_{2,0}}$.
-	\item  $\lgh(\der{D}_1)\neq 0$ and $\lgh(\der{D}_2)\neq 0$.
-In this case we have that $(\der{D}, \alpha, \omega)$  is $(\der{D}_1*\omega_1^{-1}\cdot \alpha_2*\der{D}_2, \alpha_1, \omega_2)$.
-By second point of \Cref{lem:colim} and by \Cref{rem:abscons2} we can build the following diagram.
-	\[\xymatrix@C=40pt{&&G_{2,0}  \ar@/_.3cm/[dl]_{\alpha^{-1}_2} \ar@/^.3cm/[dr]^{\iota_{2, G_{2,0}}}\\&\pi(G_{2,0}) \ar[dr]^{\iota_{G_{l_1}}}\ar[r]^-{\iota'_{2, \pi(G_{2,0})}} \ar@{>->}[d]_-{\iota'_{1, \pi(G_{1,l_1})}} & \lpro \alpha_2*\der{D}_2 \rpro \ar@{>->}[d]^{p_2} &\tproi{D}{2} \ar[l]_-{\Gamma^{\alpha_2}} \ar@{>.>}@/^.2cm/[dl]^{q_2}\\ G_{1,l_1}  \ar@/^.3cm/[ur]^{\omega^{-1}_1}  \ar@{>->}@/_.3cm/[dr]_{\iota_{1, G_{1, l_1}}}& \lpro \der{D}_1*\omega_1^{-1} \rpro  \ar[r]_{p_1}& \tpro{D} \\ &\tproi{D}{1} \ar[u]^{\Gamma_{\omega^{-1}_1}}  \ar@{.>}@/_.2cm/[ur]_{q_1}}\]
-
-	Let us define $q_1$ as $p_1\circ \Gamma_{\omega^{-1}_1}$ and $q_2$ as $p_2\circ \Gamma^{\alpha_2}$. Then, for every $i\in [0,l_1-1]$ and $j\in [l_1+1, l_1+l_2]$
-	\[\begin{split}
-		q_1\circ \iota_{1, G_{1,i}}&=p_1\circ \Gamma_{\omega^{-1}_1}\circ \iota_{1, G_{1,i}}\\&=p_1\circ \iota'_{1, G_{1,i}} \\&=\iota_{G_{i}}
-	\end{split} \qquad \begin{split}
-		q_2\circ \iota_{2, G_{2,j}}&=p_2\circ \Gamma^{\alpha_2}\circ \iota_{2, G_{2,j}}\\&=p_2\circ \iota'_{2, G_{2,j}} \\&=\iota_{G_{j+l_1}}
-	\end{split}\]
-	Moreover, we also have:
-	\[
-	\begin{split}
-		q_1\circ \iota_{G_{1,0}}\circ \alpha_1&= p_1\circ \Gamma_{\omega^{-1}_1}\circ \iota_{G_{1,0}}\circ \alpha_1 \\&=p_1\circ \iota'_{1, G_{1,0}} \circ \alpha_1 \\&= \iota_{G_{0}}\circ \alpha
-	\end{split}\qquad 
-	\begin{split}
-	q_2\circ \iota_{G_{2,l_2}}\circ \omega_2&= p_2\circ \Gamma^{\alpha_2}\circ \iota_{G_{2,l_2}}\circ \omega_2 \\&=p_2\circ \iota'_{1, G_{2,l_2}} \circ \omega_2 \\&= \iota_{G_{l_1+l_2}}\circ \omega
-	\end{split} \]
-
-	This concludes the proof. \qedhere
-\end{itemize}	
-\end{proof}
-
-\begin{remark}\label{rem:dett2}
-It is worth noticing that, for every $i\in [0,l_1-1]$ and $j\in [l_1+1, l_1+l_2]$ the previous equalities also entail that,
-\[\begin{split}q_1\circ \iota_{1, D_{1,i}}&=\iota_{D_{i}}\\q_2\circ \iota_{2, D_{2,j}}&=\iota_{D_{j+l_1}} 	\\q_1\circ \iota_{1, R_{1,i-1}}&=\iota_{R_{i-1}} \\
-	q_2\circ \iota_{2, R_{2,j-1}}&=\iota_{R_{j+l_1-1}}
-\end{split} \qquad 
-\begin{split}    	q_1\circ \iota_{1, L_{1,i}}&=\iota_{L_{i}} \\q_2\circ \iota_{2, L_{2,j}}&=\iota_{L_{j+l_1}}\\ q_1\circ \iota_{1, K_{1,i}}&=\iota_{K_{i}}\\q_2\circ \iota_{2, K_{2,j}}&=\iota_{K_{j+l_1}}\end{split}\]
-\end{remark}
-
-We can now turn our attention to the case in which a consistent permutation between two composite derivations is given.
-
-\begin{lemma}[Restriction Lemma]\label{prop:uniqu}
-	Let $\sigma\colon [0,n]\to [0,n]$ be a consistent permutations between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ and suppose that 
-	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1) \cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1) \cdot (\der{D}'_2, \alpha'_2, \omega'_2) \]
-
-	 Let $l_1$ be the length of $\der{D}_1$, and suppose that there exists a consistent permutation $\tau:[0,l_1-1]\to [0, l_1-1]$.
-If $q_1\colon \lpro \der{D}_1\rpro \to \lpro \der{D}\rpro$  and $q'_1\colon \lpro \der{D}'_1\rpro \to \lpro \der{D}'\rpro$ are the canonical arrows defined in \Cref{rem:dett}, then the following hold true:
-	\begin{enumerate}
-	\item  if $l_1=0$, then the following diagram commutes:
-		\[\xymatrix{\lpro \der{D}_1\rpro \ar[r]^{\xi_\tau} \ar[d]_{q_1}& \lpro \der{D}'_1 \ar[d]^{q'_1}\rpro\\ \lpro \der{D}\rpro \ar[r]_{\xi_\sigma} & \lpro \der{D}'\rpro } \]
-	%\[\xi_\sigma \circ q_1 \circ \iota_{1, G_{1,0}} = q'_1\circ \xi_{\tau} \circ  \iota_{1, G_{1,0}}\]
-	\item if $l_1\neq 0$, so that $G_{1,0}=G_0$, then $\xi_\sigma \circ \iota_{G_0} = q'_1\circ \xi_{\tau} \circ  \iota_{1, G_{1,0}}$.
-	\end{enumerate}
-
-	Moreover, define the set $E_{\sigma, \tau}$ as
-	\[E_{\sigma, \tau}:=\{i\in  [0, l_1-1] \mid \sigma(j)=\tau(j) \text{ for every } j \leq i \}\]
-	then also the following hold true:
-	\begin{enumerate}
-		\setcounter{enumi}{2}
-	\item  if $E_{\sigma, \tau}\neq \emptyset$,  for every index $i\in [0, \max(E_{\sigma, \tau})]$ we have 
-	$\xi_\sigma \circ \iota_{G_i}=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_i}$;
-	\item if $l_1-1\in E_{\sigma, \tau}$ and $l_2=0$ so that  $G_{l_1}=G_{1, l_1}$, then 
-	$\xi_\sigma \circ \iota_{G_{l_1}}=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}$;
-	\item if $l_1-1\in E_{\sigma, \tau}$ and $l_2\neq 0$, so that $G_{l_1}=\pi(G_{2,0})$, then 
-	$\xi_\sigma \circ \iota_{G_{l_1}}=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ \omega_1$;
-	\item if $l_1-1\in E_{\sigma, \tau}$, then the following diagram commutes:
-	\[\xymatrix{\lpro \der{D}_1\rpro \ar[r]^{\xi_\tau} \ar[d]_{q_1}& \lpro \der{D}'_1 \ar[d]^{q'_1}\rpro\\ \lpro \der{D}\rpro \ar[r]_{\xi_\sigma} & \lpro \der{D}'\rpro } \]
-	\end{enumerate}
-\end{lemma}
-\begin{proof}\begin{enumerate}
-		\item Recall that, in this case \[q_1=\iota_{G_0}\circ \alpha_2\circ \omega^{-1}_1 \circ \iota^{-1}_{1,G_{1,0}} \qquad q'_1=\iota'_{G'_0}\circ \alpha'_2\circ (\omega'_1)^{-1} \circ (\iota'_{1,G'_{1,0}})^{-1}\]
-
-		If we compute we have
-		\begin{align*}
-	\xi_\sigma \circ q_1 &=\xi_\sigma \circ \iota_{G_0}\circ \alpha_2\circ \omega^{-1}_1 \circ \iota^{-1}_{1,G_{1,0}} \\&=\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}\circ \alpha_2\circ \omega^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}
-		\end{align*}
-		Now, since $l_1=0$ we also have that 
-		\[\alpha=\alpha_2\circ \omega_1^{-1}\circ \alpha_1 \qquad \alpha'=\alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1\]
-
-		Therefore, using \Cref{rem:empty}, we get:
-		\begin{align*}
-	\alpha'\circ \alpha^{-1}&=\alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1\circ \alpha^{-1}_1\circ \omega_1\circ \alpha^{-1}_2\\&=\alpha'_2\circ (\omega'_1)^{-1}\circ \omega'_1\circ \omega^{-1}_1\circ \omega_1\circ \alpha^{-1}_2\\&=\alpha'_2\circ \alpha^{-1}_2
-		\end{align*}
-	Hence, again by \Cref{rem:empty} we obtain:
-				\begin{align*}
-			\xi_\sigma \circ q_1 &=\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}\circ \alpha_2\circ \omega^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=\iota'_{G'_0}\circ \alpha'_2\circ \alpha^{-1}_2\circ \alpha_2\circ \omega^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=\iota'_{G'_0}\circ \alpha'_2\circ \omega^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=\iota'_{G'_0}\circ \alpha'_2\circ (\omega'_1)^{-1} \circ  \omega'_1\circ \omega^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=\iota'_{G_0}\circ \alpha'_2\circ (\omega'_1)^{-1} \circ \alpha'_1\circ \alpha^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=\iota'_{G'_0}\circ \alpha'_2\circ (\omega'_1)^{-1} \circ (\iota'_{1,G_{1,0}})^{-1}\circ \iota'_{1,G'_{1,0}}\circ \alpha'_1\circ \alpha^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=q'_1\circ \iota'_{1,G'_{1,0}}\circ \alpha'_1\circ \alpha^{-1}_1\circ \iota^{-1}_{1,G_{1,0}}\\&=q'_1\circ \xi_{\tau}
-		\end{align*}
-
-		\item We can start noticing that
-		\[\xi_\sigma \circ \iota_{G_0}=\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1} \qquad \xi_{\tau} \circ \iota_{1,G_{1,0}}= \iota'_{1, G'_{1,0}} \circ \alpha'_1\circ \alpha^{-1}_1\] 
-		Therefore:
-		\begin{align*}
-		q'_1\circ \xi_{\tau} \circ \iota_{1, G_{1,0}}&=q'_1 \circ \iota'_{1, G'_{1,0}} \circ \alpha'_1\circ \alpha^{-1}_1\\ &= \iota'_{G'_{0}}\circ \alpha' \circ \alpha^{-1}_1
-		\end{align*}
-		By hypothesis $\lgh(\der{D}_1) \neq 0$, thus $\alpha_1=\alpha$ and we can conclude.
-
-		\item  From $E_{\sigma, \tau}\neq \emptyset$ we deduce that $l_1\neq 0$ and that $0\in E_{\sigma, \tau}$.   We proceed by induction on $i\in [0,\max(E_{\sigma, \tau})]$.
-
-\smallskip \noindent  If $i=0$ the thesis follows from point $1$.
-
-\smallskip \noindent If $i>0$, we proceed as in the proof of \Cref{prop:isouno} considering the pushout square
-			\[\xymatrix{K_{i-1}\ar[r]^{r_{i-1}} \ar[d]_{k_{i-1}}& R_{i-1} \ar[d]^{h_{i-1}}\\ D_{i-1} \ar[r]_{g_{i-1}}& G_i}\] 
-		Since $i$ belongs to $E_{\sigma, \tau}$, then $i-1\in E_{\sigma, \tau}$ too. By definition, $i\leq l_1-1$, so that, using \Cref{rem:coproj}, \Cref{rem:dett} and the induction hypothesis we have
-			\[\begin{split}
-				\xi_\sigma \circ \iota_{G_i}\circ h_{i-1}&=  \xi_\sigma\circ \iota_{R_{i-1}}\\&=\iota'_{R'_{\sigma(i-1)}}\\&=\iota'_{R'_{\tau(i-1)}}\\&=q'_1\circ \iota'_{1, R'_{1,\tau(i-1)}}\\&=q'_1\circ \xi_{\tau}\circ \iota_{1, R_{i-1}}\\&=q'_1\circ \xi_{\tau} \circ \iota_{1, G_{1,i}}\circ h_{1, i-1}\\&=q'_1\circ \xi_\tau \circ \iota_{1, G_i} \circ h_{i-1}
-			\end{split} \qquad  \begin{split}
-			\xi_\sigma \circ \iota_{G_i}\circ g_{i-1}&=\xi_{\sigma}\circ \iota_{D_{i-1}}\\&=\xi_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{i-1}} \circ f_{i-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{i-1}} \circ f_{1, i-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, D_{i-1}}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_i}\circ g_{1, i-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_i}\circ g_{i-1}
-			\end{split}\]
-
-	From which the thesis follows.
-
-			\item Since $l_1-1\in E_{\sigma, \tau}$ we have $l_1\neq 0$ and $E_{\sigma, \tau}=[0,l_1-1]$.  We can start with the pushout
-			\[\xymatrix{K_{l_1-1}\ar[r]^{r_{l_1-1}} \ar[d]_{k_{l_1-1}}& R_{i-1} \ar[d]^{h_{l_1-1}}\\ D_{l_1-1} \ar[r]_{g_{l_1-1}}& G_{l_1}}\] 
-			By \Cref{def:conc}, we have $h_{l_1-1}=h_{1, l_1}$ and $g_{l_1-1}=g_{1,l_1}$.
-Since $q'_1=\id{\lpro \der{D}'_1\rpro}$ these two equalities imply that $	\iota'_{R_{\tau(l_1-1)}}=q'_1\circ \iota'_{1, R'_{1,\tau(l_1-1)}}$.
-
-			Moreover, by hypothesis $l_1-1\in E_{\sigma, \tau}$, so that point $3$ of this lemma entails that
-			\[\xi_\sigma \circ \iota_{G_{l_1-1}}=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1-1}}\]
-
-			We can thus repeat the same argument of the previous point:
-			\[\begin{split}
-				\xi_\sigma \circ \iota_{G_{l_1}}\circ h_{l_1-1}&=  \xi_\sigma\circ \iota_{R_{l_1-1}}\\&=\iota'_{R'_{\sigma(l_1-1)}}\\&=\iota'_{R'_{\tau(l_1-1)}}\\&=q'_1\circ \iota'_{1, R'_{1,\tau(l_1-1)}}\\&=q'_1\circ \xi_{\tau}\circ \iota_{1, R_{l_1-1}}\\&=q'_1\circ \xi_{\tau} \circ \iota_{1, G_{1,l_1}}\circ h_{1, l_1-1}\\&=q'_1\circ \xi_\tau \circ \iota_{1, G_{l_1}} \circ h_{l_1-1}			\end{split}
-			\qquad  \begin{split}
-				\xi_\sigma \circ \iota_{G_{l_1}}\circ g_{l_1-1}&=\xi_{\sigma}\circ \iota_{D_{l_1-1}}\\&=\xi_{\sigma}\circ \iota_{G_{l_1-1}} \circ f_{l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1-1}} \circ f_{l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}-1} \circ f_{1, l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, D_{l_1-1}}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ g_{1, l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ g_{l_1-1}
-			\end{split}\]
-
-		And again this implies the thesis.
-
-			\item In this case, we can consider the following diagram, in which the inner rectangle and the outer border are pushouts
-		\[\xymatrix@C=35pt{K_{1,l_1-1}\ar[r]^{r_{1,l_1-1}} \ar[d]_{k_{1,l_1-1}}& R_{i-1} \ar[d]_{h_{1,l_1-1}} \ar@/^.3cm/[ddr]^{h_{l_1-1}}\\ D_{1,l_1-1} \ar[r]_{g_{1,l_1-1}} \ar@/_.3cm/[drr]_{g_{l_1-1}}& G_{1,l_1} \ar[dr]^{\omega_1^{-1}}\\ &&\pi(G_{2,0})}\]
-
-		\iffalse 
-	\[	\xi_\sigma \circ \iota_{G_{l_1}}=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ \omega_1\]
-	\fi 
-		We can start noticing that, by the proof of  the third point of \Cref{rem:dett}, we know that  $q'_1\circ \iota'_{1, G'_{1,l_1}}=\iota'_{G'_{l_1}} \circ \omega_1^{-1}$. Therefore
-		\begin{align*}q'_1\circ \iota'_{1, R'_{1,l_1}}&=q'_1\circ \iota'_{1, G'_{1,l_1}}\circ  h'_{1, l_1}\\&=q'_1\circ \iota'_{1, G'_{1,l_1}}\circ \omega_1 \circ  h'_{ l_1}\\&= \iota'_{G'_{l_1}}\circ h'_{l_1}\\&=\iota'_{R'_{l_1-1}}
-		\end{align*}
-
-		The argument now proceeds almost verbatim like the one of the previous two point. Indeed, using the third point of this lemma we get:
-		\[\begin{split}
-			\xi_\sigma \circ \iota_{G_{l_1}}\circ h_{l_1-1}&=  \xi_\sigma\circ \iota_{R_{l_1-1}}\\&=\iota'_{R'_{\sigma(l_1-1)}}\\&=\iota'_{R'_{\tau(l_1-1)}}\\&=q'_1\circ \iota'_{1, R'_{1,\tau(l_1-1)}}\\&=q'_1\circ \xi_{\tau}\circ \iota_{1, R_{l_1-1}}\\&=q'_1\circ \xi_{\tau} \circ \iota_{1, G_{1,l_1}}\circ h_{1, l_1-1}\\&=q'_1\circ \xi_\tau \circ \iota_{1, G_{1, l_1}} \circ \omega_1 \circ  h_{l_1-1}			\end{split}  \qquad  		\begin{split}
-			\xi_\sigma \circ \iota_{G_{l_1}}\circ g_{l_1-1}&=\xi_{\sigma}\circ \iota_{D_{l_1-1}}\\&=\xi_{\sigma}\circ \iota_{G_{l_1-1}} \circ f_{l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}} \circ f_{l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}} \circ f_{1, {l_1}-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, D_{{l_1}-1}}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ g_{1, l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ \omega_1\circ g_{l_1-1}
-			\end{split}\]
-
-			\item  The thesis follows from points $3$ and $4$ if $l_2=0$, from $3$ and $5$ if $l_2\neq 0$.	\qedhere
-	\end{enumerate}
-\end{proof}
-
-We are now ready to prove the central result of this section: the uniqueness of a consistency permutation between two decorated derivations in a consuming rewriting system.
-
-\begin{lemma}\label{lem:impo}
-	Let $(\X,R)$ be a left-linear DPO-rewriting system and let also $(\der{D}_1, \alpha_1, \omega_1)$, $(\der{D}_2, \alpha_2, \omega_2)$ be two composable decorated derivations of length, respectively, $l_1$ and $l_2$.
-Suppose that $\sigma:[0, l_1+l_2-1]\to [0, l_1+l_2-1]$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)$ for some other two composable decorated derivations $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}_2, \alpha_2, \omega_2)$.
-If $\tau:[0,l_1-1]\to [0, l_1-1]$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$.
-Suppose that  the set
-	\[D_{\sigma, \tau}:=\{i\in [0, l_1-1]\mid \sigma(i)\neq \tau(i)\}\]
-	is non-empty and let $j$ be its minimum. Let also $r(\der{D}_1)$ be $\{\rho_i\}_{i=0}^{l_1-1}$. Then the following hold true:
-	\begin{enumerate}
-		\item if $j=0$, then the rule $\rho_0$ is not consuming;
-		\item if $j\neq 0$ then the rule $\rho_{j-1}$ is not consuming.
-	\end{enumerate}
-\end{lemma}
-\begin{remark}\label{rem:minmax}It is worth to notice that the hypothesis $D_{\sigma, \tau} \neq \emptyset$ entails $l_1\neq 0$.
-Moreover, if $j\neq 0$, then $j-1$ is the maximum of $E_{\sigma, \tau}$.
-\end{remark}
-\begin{proof}
-	\begin{enumerate}
-		\item Let $k$ be $\sigma^{-1}(\tau(0))$ and notice that, since $\sigma(0)\neq \tau(0)$, then $0< k$.  By  the second point of  \Cref{prop:uniqu} we can consider the diagram
-		\[\xymatrix@C=40pt{G_{0} \ar[drrr]_(.4){\iota_{G_0}}|(.675)\hole \ar[d]_{\iota_{1,G_{1,0}}}& L_0 \ar[r]_{m'_{\tau(0)}} \ar@/^.4cm/[rr]^{m_{k}} \ar[l]_{m_{0}} &G'_{\tau(0)} \ar[d]^(.45){\iota'_{G'_{\tau(0)}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \lpro\der{D}_1 \rpro \ar[r]_{\xi_{\tau}} &\lpro \der{D}'_1\rpro \ar[r]_{q'_1} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
-		From \Cref{cor:ele}, we can conclude that there exists $c\colon L_0\to D_0$ such that $f_0\circ c=m_0$. We thus have the solid part of the commutative diagram below.
-		\[\xymatrix{L_0 \ar@/^.3cm/[drr]^{\id{L_0}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_0 \ar[d]_{k_0}\ar@{>->}[r]^{l_0}& L_0 \ar[d]^{m_0} \\& D_0 \ar@{>->}[r]_{f_0} & G_0} \]
-		The internal square is an $\mathcal{M}$-pushout and thus a pullback, by \Cref{prop:pbpoad}, so that we have the existence of the dotted $t\colon L_0\to K_0$.
-Therefore $\id{L_0}=l_0\circ t$, proving that $l_0$ is an epimorphism.
-The thesis now follows from \Cref{cor:rego}.
-		\item  Let $k$ be $\sigma^{-1}(\tau(j-1))$ and notice that $\rho_{j-1}=\rho_k$.
-We have already noticed in \Cref{rem:minmax} that $j-1$ is the maximum of $E_{\sigma, \tau}$.
-Hence, by the third point of \Cref{prop:uniqu} we have
-		\[\xymatrix@C=40pt{G_{1,{j-1}} \ar[drrr]_(.4){\iota_{G_{j-1}}}|(.675)\hole \ar[d]_{\iota_{1,G_{1,j-1}}}& L_{j-1} \ar[r]_{m'_{\tau({j-1})}} \ar@/^.4cm/[rr]^{m_{k}} \ar[l]_{m_{{j-1}}} &G'_{\tau({j-1})} \ar[d]^{\iota'_{G'_{\tau({j-1})}}} & G_{k} \ar[d]^{\iota_{G_k}}\\ \lpro\der{D}_1 \rpro \ar[r]_{\xi_{\tau}} &\lpro \der{D}'_1\rpro \ar[r]_{q'_1} & \lpro \der{D'}\rpro & \tpro{D} \ar[l]^{\xi_{\sigma}}}\]
-		Let $a$ be $\min(j-1, k)$, by \Cref{cor:ele},  there exists $c\colon L_{j-1}\to D_a$ such that $f_a\circ c=m_a$.
-As before this yields the solid part of the following diagram, in which the square is an $\mathcal{M}$-pushout.
-		\[\xymatrix{L_{j-1} \ar@/^.3cm/[drr]^{\id{L_{j-1}}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_{j-1} \ar[d]_{k_a}\ar@{>->}[r]^{l_{j-1}}& L_{j-1} \ar[d]^{m_a} \\& D_a \ar@{>->}[r]_{f_a} & G_a} \]
-		The existence of the dotted $t\colon L_{j-1}\to K_{j-1}$ follows from  \Cref{prop:pbpoad} and we can conclude. \qedhere
-	\end{enumerate}
-\end{proof}
-
-\begin{corollary}[Uniqueness of consistent permutation]\label{cor:unique}
-Let $(\X,\R)$ be a consuming left-linear DPO-rewriting system.
-Then, for every two decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, there exists at most one consistent permutation between them.
-\end{corollary}
-\begin{proof}
-Let $\sigma, \tau: [0, \lgh(\der{D})-1]\rightrightarrows [0, \lgh(\der{D})-1]$ be two consistent permutations.
-Let $H$  and $H'$ be, respectively, the target of $\der{D}$ and $\der{D}'$.
-Take two isomorphisms $\gamma:\pi(H)\to \gamma$, $\gamma':\pi(H')\to H'$, then, according to \Cref{def:conc}:
-\begin{align*}(\der{D}, \alpha, \omega)&=(\der{D}, \alpha, \omega)\cdot (\der{D}_2, \gamma, \gamma) \\(\der{D}', \alpha', \omega')&=(\der{D}', \alpha', \omega')\cdot (\der{D}'_2, \gamma', \gamma') 
-\end{align*} 
-where $\der{D}_2$ and $\der{D}'_2$ are the empty derivation on $H$ and $H'$. Since $(\X, \R)$ is consuming, then \Cref{lem:impo} entails $D_{\sigma, \tau}=\emptyset$, from which the thesis follows.
-\end{proof}
-
-\begin{lemma}[Corestriction Lemma]\label{lem:presuffix} Let $(\X, \R)$ be a consuming left-linear DPO-rewriting system.
-Let also $(\der{D}_1, \alpha_1, \omega_1)$, $(\der{D}_2, \alpha_2, \omega_2)$ be two composable decorated derivations of length, respectively, $l_1$ and $l_2$.
-Suppose that $\sigma\colon [0, l_1+l_2-1]\to [0, l_1+l_2-1]$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)$ for some other two composable decorated derivations $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}_2, \alpha_2, \omega_2)$.
-If $\tau\colon [0,l_1-1]\to [0, l_1-1]$ is a consistent permutation between $(\der{D_1}, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$.
-Then the following hold true:
-	\begin{enumerate}
-		\item suppose that $l_1$ and $l_2$ are different from $0$ and consider the following two pushout squares given by \Cref{rem:dett}:
-		\[\xymatrix@C=45pt@R=30pt{\pi(G_{2,0}) \ar@{>->}[d]_{\iota_{1, G_{1,n+1}} \circ \omega_1}\ar[r]^{\iota_{2, G_{2,0}} \circ \alpha_2}& \lpro \der{D}_2 \rpro \ar@{>->}[d]^{q_2} &  \pi(G'_{2,0}) \ar@{>->}[d]_{\iota'_{1, G'_{1,n+1}} \circ \omega'_1} \ar[r]^{\iota'_{2, G'_{2,0}} \circ \alpha'_2}& \lpro \der{D}'_2 \rpro \ar@{>->}[d]^{q'_2} \\ \lpro \der{D}_1 \rpro  \ar[r]_{q_1} & \tpro{D} & \lpro \der{D}'_1\rpro \ar[r]_{q'_1} & \lpro \der{D}'\rpro  }\]
-		then, for every $i\in [0, l_2]$ there exists a unique $\zeta_i\colon G_{2,i}\to \lpro \der{D}_2\rpro $ fitting in the diagram below
-		\[\xymatrix@R=35pt{G_{2,i} \ar[r]^{\iota_{2,G_{2,i}}} \ar@{.>}[d]_{\zeta_i}&\lpro \der{D}_2 \rpro \ar@{>->}[r]^{q_2}& \tpro{D} \ar[d]^{\xi_{\sigma}} \\
-			\lpro \der{D}'_2 \rpro \ar@{>->}[rr]_{q'_2}&& \lpro \der{D}'\rpro }\]
-		\item the permutation
-		\[\varrho\colon [0,l_2-1]\to [0, l_2-1] \qquad i \mapsto \sigma(i+l_1)-l_1\]
-		is a consistent one.
-	\end{enumerate}
-\end{lemma}
-\begin{proof}\begin{enumerate}
-		\item We can start noticing that  by \Cref{lem:impo}, $\sigma(i)=\tau(i)$ for every $i\in  [0, l_1-1]$. By the second point of \Cref{prop:uniqu} we can deduce that
-		\[\xi_\sigma \circ \iota_{G_{i}}=\]Let us prove the existence of $\zeta_i$ by induction on $i\in [0, l_2]$.
-
-		\smallskip \noindent $i=0$. We already know that $G_{l_1}$ and $G'_{l_1}$ are both equal to $\pi(G_{2,0})$.  Moreover, we also know that
-		\begin{align*}
-		q_2\circ \iota_{2, G_{2,0}}=\iota_{G_{l_1}} \circ \alpha^{-1}_2 \qquad
-		\end{align*}
-
-		Thus we have a diagram
-		\[\xymatrix{&G_{2,0} \\
-		G_{l_1} \\
-		G'_{2,0}&}\]
-
-	Moreover, $\pi(mj$
-		\begin{align*}
-			\xi_\sigma \circ p_2\circ \iota_{2, G_{2,0}}&=\xi_\sigma \circ \iota_{G_{n+1}}\circ \alpha^{-1}_2\\&g
-		\end{align*}
-
-		\smallskip \noindent $i>0$.
-
-		The uniqueness half of the thesis follows at once since $p'_2$ is in $\mathcal{M}$.
-
-		\item Let us split the cases.
-
-		\smallskip \noindent $l_1=0$. then $\varrho=\sigma$ and there is nothing to proof.
-
-		\smallskip \noindent $l_2=0$ and $l_1\neq0$. Then $\varrho=\id{\emptyset}$ and
-
-		\smallskip \noindent $l_1\neq0$ and $l_2\neq 0$. 
-		\[\xymatrix{xy code}\]
-
-		Consistency now follows at once. \qedhere 
-	\end{enumerate}
-\end{proof}
-
-Finally, we  end this section showing that consistent permutations between composable abstract derivations yield a consistent permutation between the composites.
-
-\begin{lemma}\label{lem:sum} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstract decorated derivations such that
-	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)\]
-	Given a consistent permutation $\sigma\colon [0, \lgh(\der{D}_1)-1]\to [0, \lgh(\der{D}_1)-1]$ between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$ and another $\tau\colon [0, \lgh(\der{D}_2)-1]\to [0, \lgh(\der{D}_2)-1]$ between $(\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$, then
-	\[\sigma+\tau\colon[0, \lgh(\der{D})-1]\to[0, \lgh(\der{D})-1] \quad i \mapsto \begin{cases}
-		\sigma(i) & i < \lgh(\der{D}_1)\\
-		\lgh(\der{D}_1)+\tau(i-\lgh(\der{D}_1)) &   i\geq \lgh(\der{D}_1) 
-	\end{cases}\]
-	is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
-\end{lemma}
-
-\begin{notation}
-Given $X_1\in \Delta(\der{D}_1)$, $X_2\in \Delta(\der{D}_2)$, $X'_1\in \Delta(\der{D}'_1)$, $X'_2\in \Delta(\der{D}'_2)$, we will denote their coprojections into, respectively, $\lpro \der{D}_1\rpro$, $\lpro \der{D}'_2\rpro$, $\lpro \der{D}'_1\rpro$, $\lpro \der{D}'_2\rpro$ by
-$\iota_{1, X_1}\colon X_1\to \lpro\der{D}_1\rpro$, $\iota_{1, X_2}\colon X_2\to \lpro\der{D}_1\rpro$, $\iota'_{1, X'_1}\colon X'_1\to \lpro\der{D}'_1\rpro$ and $\iota'_{2, X'_2}\colon X'_2\to \lpro\der{D}_1\rpro$.
-Similarly, given $X\in \Delta(\der{D})$ and $X'\in \Delta(\der{D}')$ we will use $\iota_X\colon X\to \tpro{D}$ and $\iota'_{X'}\colon X'\to \lpro \der{D}' \rpro$ for the coprojections.
-\end{notation}
-
-\begin{proof}
-We split the proof in three cases, according to \Cref{def:conc}.
-	\begin{itemize}
-	\item $\lgh(\der{D}_1)=0$. Thus $\lgh(\der{D}'_1)=0$ too  and we have
-	\[
-	(\der{D}, \alpha, \omega)=(\der{D}_2, \alpha_2\circ \omega_1^{-1}\circ \alpha_1, \omega_2) \qquad  (\der{D}', \alpha', \omega')=(\der{D}'_2, \alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1, \omega'_2)\]
-
-	Moreover, in this case $\sigma$ must be $\id{\emptyset}$ and $\sigma+\tau$ must be equal to $\tau$. The thesis now follows from the commutativity of the following diagram.
-	\[\xymatrix@C=35pt{& G_{1,0}\ar[dd]^{\xi_{\id{\emptyset}}} \ar[dr]^{\omega^{-1}_1}&&G_{2,0}\ar[r]^-{\iota_{2, G_{2,0}}} & \lpro \der{D}_2\rpro \ar[dd]^{\xi_{\tau}}\\\pi(G_{1,0})  \ar[ur]^{\alpha_1} \ar[dr]_{\alpha'_1}&& \pi(G_{2,0}) \ar[ur]^{\alpha_2} \ar[dr]_{\alpha'_2}\\& G'_{1,0} \ar[ur]_{(\omega'_1)^{-1}}&&G'_{2,0} \ar[r]_-{\iota'_{2, G_{2,0}}}& \lpro \der{D}'_2\rpro}\]
-
-\item $\lgh(\der{D}_2)=0$.  As before this implies that also $\lgh(\der{D}'_2)$ is $0$.  Applying \Cref{def:conc} we get 
-\[
-(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1 \circ (\alpha_2)^{-1}\circ \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1 \circ (\alpha'_2)^{-1}\circ \omega'_2)\]
-
-	Since $\der{D}_2$ is empty, then $\tau=\id{\emptyset}$ and $\sigma+\tau=\sigma$. Let $n$ be $\lgh(\der{D}_1)$, as before the thesis follows from the diagram below.
-	\[\xymatrix@C=35pt{& G_{2,0}\ar[dd]^{\xi_{\id{\emptyset}}} \ar[dr]^{\alpha^{-1}_2}&&G_{1,n}\ar@{>->}[r]^-{\iota_{1, G_{1,n}}} & \lpro \der{D}_2\rpro \ar[dd]^{\xi_{\sigma}}\\\pi(G_{2,0})  \ar[ur]^{\omega_2} \ar[dr]_{\omega'_2}&& \pi(G_{1,n}) \ar[ur]^{\omega_1} \ar[dr]_{\omega'_1}\\& G'_{2,0} \ar[ur]_{(\alpha'_1)^{-1}}&&G'_{1,n} \ar@{>->}[r]_-{\iota'_{1, G_{1,n}}}& \lpro \der{D}'_2\rpro}\]
-
-\item  $\lgh(\der{D}_1)\neq0$ and $\lgh(\der{D}_2)\neq 0$. Thus $\der{D}'_1$ and $\der{D}'_2$ are non-empty too. In this case we have
-\[	(\der{D}, \alpha, \omega)=(\der{D}_1*\omega_1^{-1}\cdot \alpha_2*\der{D}_2, \alpha_1, \omega_2)\qquad
-(\der{D}', \alpha', \omega')=(\der{D}'_1*(\omega'_1)^{-1}\cdot \alpha'_2*\der{D}'_2, \alpha'_1, \omega'_2)\]
-
-Let us assume that $\der{D}_1$, $\der{D}'_1$, $\der{D}_2$ and $\der{D}'_2$ are given by
-\[\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^n \quad \der{D}'_1=\{\dder{D}'_{1,i}\}_{i=0}^n \quad \der{D}_2=\{\dder{D}_{2,i}\}_{i=0}^t \quad \der{D}_2'=\{\dder{D}'_{2,i}\}_{i=0}^t\]
-By definition of consistent permutation, the rule applied by $\dder{D}_{1,i}$ and the one applied in $\dder{D}_{2,i}$  must coincide with, respectively, the one applied in $\dder{D}'_{1,i}$ and the one applied $\dder{D}'_{2,1}$.
-Let $\dder{D}_{1,i}$, $\dder{D}'_{1,i}$, $\dder{D}_{2,i}$ and $\dder{D}'_{2,i}$ be given, by the following four diagrams.
-\[\xymatrix{L_{1,i} \ar[d]_{m_{1, i}}& K_{1,i} \ar[d]_{k_{1, i}} \ar[r]^{r_{1,i}} \ar@{>->}[l]_{l_{1,i}} & R_{1,i}\ar[d]^{h_{1, i}} &L_{1,i} \ar[d]_{m'_{1, i}}& K_{1,i} \ar[d]_{k'_{1, i}} \ar[r]^{r_{1,i}} \ar@{>->}[l]_{l_{1,i}} & R_{1,i}\ar[d]^{h'_{1, i}} \\G_{1,i} & D_{1,i} \ar[r]_{g_{1,i}} \ar@{>->}[l]^{f_{1,i}} & G_{1,i+1} & G'_{1,i} & D'_{1,i}\ar[r]_{g'_{1,i}} \ar@{>->}[l]^{f'_{1,i}}  & G'_{1,i+1}}\]
-\[\xymatrix{L_{2,i} \ar[d]_{m_{2, i}}& K_{2,i} \ar[d]_{k_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h_{2, i}} &L_{2,i} \ar[d]_{m'_{2, i}}& K_{2,i} \ar[d]_{k'_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h'_{2, i}} \\G_{2,i} & D_{2,i} \ar[r]_{g_{2,i}} \ar@{>->}[l]^{f_{2,i}} & G_{2,i+1} & G'_{2,i} & D'_{2,i}\ar[r]_{g'_{2,i}} \ar@{>->}[l]^{f'_{2,i}}  & G'_{2,i+1}}\]
-
-%Let $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$, $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$, $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$ and $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$ be colimiting cocones.
-By \Cref{rem:dett} we get the following diagram, in which the two solid squares are pushouts:
-\[\xymatrix@C=45pt@R=30pt{\pi(G_{2,0}) \ar@/^.4cm/[rrr]^{\id{\pi(G_{2,0})}}\ar@{>->}[d]_{\iota_{1, G_{1,n+1}} \circ \omega_1}\ar[r]_{\iota_{2, G_{2,0}} \circ \alpha_2}& \lpro \der{D}_2 \rpro \ar@{>->}[d]^{q_2}\ar[r]_{\xi_\tau} & \lpro \der{D}'_2 \rpro \ar@{>->}[d]_{q'_2} &\pi(G'_{2,0}) \ar@{>->}[d]^{\iota'_{1, G'_{1,n+1}} \circ \omega'_1} \ar[l]^{\iota'_{2, G'_{2,0}} \circ \alpha'_2}\\ \lpro \der{D}_1 \rpro \ar@/_.4cm/[rrr]_{\xi_\sigma} \ar[r]^{q_1} & \tpro{D} \ar@{.>}[r]^{\xi_{\sigma+\tau}} & \lpro \der{D}'\rpro & \lpro \der{D}'_1\rpro  \ar[l]_{q'_1}}\]
-
-Moreover, we can point out that, for every index $i\in [0,n+t+2]$ we have
-
-\[\iota_{G_i}=\begin{cases}q_1\circ \iota_{1, G_{1,i}} & i \leq n\\
-	q_1\circ \iota_{1, G_{1, i}}\circ \omega_1& i=n+1\\
-	q_2\circ \iota_{2, G_{2,i-(n+1)}} & i > n+1 
-\end{cases} \qquad \iota'_{G'_i}=\begin{cases}q'_1\circ \iota'_{1, G'_{1,i}} & i \leq n\\
-	q'_1\circ \iota'_{1, G'_{1, i}}\circ \omega'_1& i=n+1\\
-	q'_2\circ \iota'_{2, G'_{2,i-(n+1)}} & i > n+1 
-\end{cases}\]
-
-Now, on the one hand, the existence of the dotted arrow $\xi_{\sigma+\tau}\colon \tpro{D}\to \lpro \der{D}'\rpro$ in the diagram above follows from the following computation:
-\begin{align*}
-	q'_1\circ \xi_\sigma \circ \iota_{1, G_{1,n+1}} \circ \omega_1&=q'_1\circ \iota'_{1,G'_{1, n+1}} \circ \omega'_1\\&= q'_2 \circ \iota'_{2, G'_{2,0}} \circ \alpha'_2\\&=q'_2\circ \xi_\tau \circ \iota_{2, G_{2,0}} \circ \alpha_2
-\end{align*} 
-On the other hand, we can repeat the same computation for $\xi^{-1}_\sigma$ and $\xi^{-1}_\tau$ to get
-\begin{align*}
-	q_1\circ \xi^{-1}_\sigma \circ \iota'_{1, G'_{1,n+1}} \circ \omega'_1&=q_1\circ \iota_{1,G_{1, n+1}} \circ \omega_1\\&= q_2 \circ \iota_{2, G_{2,0}} \circ \alpha_2\\&=q_2\circ \xi^{-1}_\tau \circ \iota'_{2, G'_{2,0}} \circ \alpha'_2
-\end{align*} 
-Hence there exists a $\psi\colon \lpro \der{D}'\rpro \to \tpro{D}$ such that:
-\[\psi \circ q'_1=q_1\circ \xi^{-1}_\sigma \qquad \psi \circ q'_2=q_2\circ \xi^{-1}_\tau\]
-
-Furthermore, the computations below show that $\psi$ is the inverse of $\xi_{\sigma+\tau}$.
-\[\begin{split}
-	\psi \circ \xi_{\sigma+\tau}\circ  q_1&=\psi \circ q'_1\circ \xi_\sigma \\&=q_1\circ \xi^{-1}_{\sigma}\circ \xi_\sigma\\&=q_1\\\\
-	\xi_{\sigma+\tau}\circ \psi \circ q'_1&=\xi_{\sigma+\tau}\circ q_1\circ \xi^{-1}_\sigma \\&=q'_1\circ \xi_{\sigma}\circ \xi^{-1}_\sigma\\&=q'_1
-\end{split}\qquad \begin{split}
-	\psi \circ \xi_{\sigma+\tau}\circ  q_2&=\psi \circ q'_2\circ \xi_\tau \\&=q_2\circ \xi^{-1}_{\tau}\circ \xi_\tau\\&=q_2\\ \\ 	\xi_{\sigma+\tau}\circ \psi \circ q'_2&=\xi_{\sigma+\tau}\circ q_2\circ \xi^{-1}_\tau \\&=q'_2\circ \xi_{\tau}\circ \xi^{-1}_\tau\\&=q'_2
-\end{split}\]
-To conclude we have to show that $\xi_{\sigma+\tau}$ fits in the diagrams of \Cref{def:permcon}.  For the ones involving the decorations we have:
-\[\begin{split}
-	\xi_{\sigma+\tau} \circ \iota_{G_{0}}\circ \alpha&=\xi_{\sigma+\tau} \circ q_1 \circ \iota_{1,G_{1,0}}\circ \alpha_1\\&=q_1'\circ \xi_\sigma \circ  \iota_{1,G_{1,0}} \alpha_1\\&=q'_1\circ \iota'_{1, G'_{1,0}}\circ \alpha'_1\\&=\iota'_{G'_0}\circ \alpha'
-\end{split}  \qquad 
-\begin{split}
-\xi_{\sigma+\tau} \circ \iota_{G_{n+t+2}}\circ \omega&=\xi_{\sigma+\tau} \circ q_2 \circ \iota_{2,G_{2,t+1}}\circ \omega_2\\&=q'_2\circ \xi_\tau \circ  \iota_{2,G_{2,t+1}} \omega_2\\&=q'_2\circ \iota'_{2, G'_{2,t+1}}\circ \omega'_2\\&=\iota'_{G'_{n+t+2}}\circ \omega'
-\end{split}  \]
-
-Let now $i$ be an index in $[0, n+t+1]$, we proceed splitting the cases.
-\begin{itemize}
-	\item $i$ is in $[0,n]$. Then we have
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_i} \circ m_i &= \xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,i}}\circ m_{1,i}\\&=q'_1 \circ \xi_\sigma \circ \iota_{1, G_{1,i}}\circ m_{1,i}\\&= q'_1\circ \iota'_{1, G'_{1,\sigma(i)}}\circ m'_{1,\sigma(i)}\\&=\iota'_{G'_{\sigma(i)}}\circ m'_{\sigma(i)}
-	\end{align*}
-	Now, suppose that $i\neq n$, then 
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i &= \xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,{i+1}}}\circ h_{1,i}\\&=q'_1\circ \xi_\sigma \circ \iota_{1, G_{1,{i+1}}}\circ h_{1,i}\\&= q'_1\circ \iota'_{1, G'_{1,\sigma(i)+1}}\circ h'_{1,\sigma(i)}
-	\end{align*}
-	and we have two subcases. If $\sigma(i)\neq n$, then \[h'_{1, \sigma(i)}=h'_{\sigma(i)} \qquad q'_1\circ \iota'_{1, G'_{1,\sigma(i)+1}}=
-	\iota'_{G'_{\sigma(i)+1}}\] 
-	and we can conclude. Otherwise, we have
-	\begin{align*}q'_1\circ \iota'_{1, G'_{1,n+1}}\circ h'_{1,n}&=q'_1 \circ \iota'_{1,G'_{1,n+1}} \circ \omega'_1\circ (\omega')^{-1}_1 \circ h'_{1,n}\\&=\iota'_{G'_{n+1}}\circ h'_n
-	\end{align*}
-	yielding again the wanted equality
-	\[\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i=\iota'_{G'_{\sigma(i)+1}}\circ h'_{\sigma(i)}\]
-	Finally, if $i=n$ we get
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ h_n &= \xi_{\sigma+\tau} \circ \iota_{\pi(G_{1,n+1})} \circ \omega^{-1}_1\circ h_{1,n}\\&= \xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,n+1}} \circ \omega_1 \circ \omega^{-1}_1 \circ h_{1,n}\\&=q'_1 \circ \xi_\sigma \circ \iota_{1, G_{1,n+1}} \circ h_{1,n}\\&=q'_1\circ \iota'_{1, G_{1,\sigma(n)+1}} \circ h'_{1,\sigma(n)}
-	\end{align*}
-	We have again two cases. If $\sigma(n)\neq n$ then we can conclude at once since 
-	\[h'_{1, \sigma(n)}=h'_{\sigma(n)} \qquad q'_1\circ \iota'_{1, G'_{1,\sigma(n)+1}}=
-	\iota'_{G'_{\sigma(n)+1}}\] 
-	While, if $\sigma(n)=n$, then we can use the identities
-	\[(\omega'_1)^{-1}\circ h'_{1, n}=h'_{n} \qquad q'_1\circ \iota'_{1, G'_{1, n+1}}=
-	\iota'_{G'_{n+1}}\circ (\omega'_1)^{-1}\] 
-	to get
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ h_n &= q'_1\circ \iota'_{1, G_{1,n+1}} \circ h'_{1,n}\\&=\iota'_{G'_{n+1}}\circ (\omega'_1)^{-1}\circ h'_{1,n}\\&=\iota'_{G'_{n+1}} h'_{n}
-	\end{align*}
-	\item $i$ is in $[n+1, n+t+1]$- We proceed  similarly to the point above. First of all we have
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i &= \xi_{\sigma+\tau} \circ q_2\circ \iota_{1, G_{2,i-n}}\circ h_{2,i-(n+1)}\\&=q'_2 \circ \xi_\tau \circ \iota_{2, G_{2,i-n}}\circ h_{2,i-(n+1)}\\&= q'_2\circ \iota'_{2, G'_{2,\tau(i-n)}}\circ h'_{2,\tau(i-(n+1))}\\&=\iota'_{G'_{\tau(i-n)}}\circ h'_{n+1+\tau(i-(n+1))}
-	\end{align*}
-	Next, supposing that $i\neq n+1$:	
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{i}} \circ m_i &= \xi_{\sigma+\tau} \circ q_2\circ \iota_{2, G_{2,i-(n+1)}}\circ m_{2,i-(n+1)}\\&=q'_2\circ \xi_\tau \circ \iota_{2, G_{2,{i-(n+1)}}}\circ m_{2,i-(n+1)}\\&= q'_2\circ \iota'_{2, G'_{2,\tau(i-(n+1))}}\circ m'_{2,\tau(i-(n+1))}
-	\end{align*}
-	and we have again two possibilities.
-If $\tau(i-(n+1))\neq 0$, then the thesis follows from the equalities \[m'_{2, \tau(i-(n+1))}=m'_{(\sigma+\tau)(i)} \qquad q'_2\circ \iota'_{2, G'_{2,\tau(i-(n+1))}}=
-	\iota'_{G'_{(\sigma+\tau)(i)}}\] 
-	Suppose, instead, that $\tau(i-(n+1))= 0$, then we have
-	\begin{align*} q'_2\circ \iota'_{2, G'_{2,0}}\circ m'_{2,0}&=q'_2 \circ \iota'_{2,G'_{2,0}} \circ \alpha'_2 \circ \alpha'^{-1}_2 \circ m'_{2,0}\\&=q'_1\circ \iota'_{1, G'_{1, n+1}}\circ \omega'_1\circ \alpha'^{-1}_2 \circ m'_{2,0}\\&=\iota'_{G'_{n+1}}\circ m'_{n+1}
-	\end{align*}
-	allowing us to conclude again.
-
-	We are left with the case $i=n+1$. Let us compute
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= \xi_{\sigma+\tau} \circ \iota_{\pi(G_{2,0})} \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,n+1}} \circ \omega_1 \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ q'_2 \circ \iota'_{2,G'_{2,0}} \circ \alpha'_2 \circ (\alpha'_2)^{-1}\circ m_{2,0} \\&=q'_2 \circ \xi_\tau \circ \iota_{2, G_{2,0}} \circ m_{2,0}\\&=q'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}
-	\end{align*}
-	We have again two cases. If $\tau(0)\neq 0$ then $(\sigma+\tau)(i)\neq n+1$ and we can conclude at once since 
-	\[m'_{2, \tau(0)}=m'_{(\sigma+\tau)(n+1)} \qquad q'_2\circ \iota'_{2, G'_{2,\tau(0)}}=
-	\iota'_{G'_{(\sigma+\tau)(0)}}\] 
-	If $\tau(0)=0$, so that  $(\sigma+\tau)(0)= n+1$ we appeal to the equalities
-	\[(\alpha')^{-1}_2\circ m'_{2, 0}=m'_{n+1} \qquad q'_2\circ \iota'_{2, G'_{2, 0}}=
-	\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\] 
-	to get
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= q'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}\\&=	\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\circ m'_{2,0}\\&=\iota'_{G'_{n+1}}\circ  m'_{n+1}
-	\end{align*}
-\end{itemize}
-The thesis now follows at once.	 \qedhere 
-\end{itemize} \end{proof}
 

### 2024-11-22 full_version/leftlinear.tex
minori

@@
 
-\chapter{Left-linear DPO-rewriting systems}
-
-$\mathcal{M}$-adhesive categories are the right context in which to perform abstract rewriting using the so-called ``douple pushout approach'' (DPO).
-We will recall the basic definitions and properties of this approach to abstract rewriting.
-\section{First definitions and properties}
-We are now going to study rewriting systems in $\mathcal{M}$-adhesive categories.
-
-\begin{definition}[\cite{habel2012mathcal,heindel2009category}]
-	Let $\X$ be an $\mathcal{M}$-adhesive category, a  \emph{left $\mathcal{M}$-linear} rule $\rho$ is a pair $(l,r)$ of arrows with the same domain, such that $l$ belongs to $\mathcal{M}$.
-The rule $\rho$ is said to be \emph{$\mathcal{M}$-linear} if $r\in \mathcal{M}$ too.
-A rule $\rho$ is said to be \emph{consuming} if $l$ is not an isomorphism.
-We will represent a rule $\rho$ as a span
-	\[\xymatrix{L & K\ar[l]_{l} \ar[r]^{r} & R}\]
-$L$ is the \emph{left-hand side}, $R$ is the \emph{right-hand side} and $K$ the \emph{glueing object}.
-
-A \emph{left-linear DPO-rewriting system} is a pair $(\X, \R)$ where $\X$ is a $\mathcal{M}$-adhesive category and $R$ is a set of left $\mathcal{M}$-linear rules.
-$(\X, \R)$ will be called \emph{linear} if every rule in $R$ is $\mathcal{M}$-linear.
-Similarly, a \emph{consuming} left-linear DPO-rewriting system is one in which every rule is consuming.
-
-Given  two objects $G$ and $H$ and a rule $\rho=(l,r)$ in $\R$, a \emph{direct derivation $\mathscr{D}$ from $G$ to $H$ applying the rule $\rho$}, is a diagram as the one below, in which both squares are pushouts.
-	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
-	The arrow $n$ is called the \emph{match} of the derivation, while $h$ is its \emph{back-match}.
-	We will denote a direct derivation $\dder{D}$ between $G$ and $H$ as $\dder{D}\colon G\Mapsto H$. 
-\end{definition}
-
-\begin{example}\todo{
-esempi di	derivazione}
-\end{example}
-
-\begin{remark}\label{exa:conc} Let  $\dder{D}\colon G\Mapsto H$ be the direct derivation 
-		\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
-	If $\phi\colon G'\to G$ and $\psi\colon H\to H'$ are two isomorphisms, 	we can consider the direct derivation	$\phi * \dder{D}*\psi \colon G'\Mapsto H'$ given by the following diagram.
-	\[\xymatrix{L \ar[d]_{\phi^{-1} \circ n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{\psi \circ h}\\G' & \ar[l]^{\phi^{-1} \circ f} D \ar[r]_{\psi \circ g}& H'}\]
-
-	In particular, we will use $\phi*\dder{D}$ and $\dder{D}*\psi$  to denote $\phi*\dder{D}*\id{H}$ and $\id{G}*\dder{D}*\psi$.
-\end{remark}
-
-$\mathcal{M}$-adhesivity of $\X$ guarantes the essential uniqueness of the result obtained rewriting an object, as shown by the next proposition.
-
-\begin{proposition}\label{prop:unique} Let $\X$  be a $\mathcal{M}$-adhesive category.
-Suppose that the two direct derivations $\mathscr{D}$ and $\mathscr{D'}$ below, with the same match and applying the same left $\mathcal{M}$-linear rule $\rho$ are given.
-	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L \ar[d]_{m}& K \ar[d]^{k'}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h'}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}& H & G & \ar@{>->}[l]^{f'} D' \ar[r]_{g'}& H'}\]
-Then there exist isomorphisms $t\colon D\to D'$ and $s\colon H\to H'$ as in the following diagram.
-\[\xymatrix@C=40pt{&&D' \ar[r]^{g'} \ar@{>->}@/_.45cm/[dll]_{f'}&H'\\G & L \ar[l]_{m} & K \ar[u]_{k'} \ar[d]^{k}\ar[r]^{r} \ar@{>->}[l]_{l} &R\ar[u]^{h'} \ar[d]_{h}\\&&D\ar@{>->}@/^.45cm/[ull]^{f}\ar@/^.4cm/@{.>}[uu]^(.4){t}|\hole \ar[r]_{g}&H\ar@/_.4cm/@{.>}[uu]_{s}}\]
-\end{proposition}
-\begin{proof}
-	By construction, the pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$ and $n$.
-Thus, the existence of the isomorphism $t\colon D\to D'$ follows from \Cref{lem:pocomp}.
-Now, computing we have
-	\begin{align*}
-		g'\circ t \circ k &= g' \circ k'\\&=h'\circ r
-	\end{align*}
-	Hence, we have the wanted $s\colon H\to H'$. To see that $s$ is an isomorphism, consider the diagram 
-	\[\xymatrix{K  \ar@/^.4cm/[rr]^{k'}\ar[d]_{r} \ar[r]_{k}& \ar[r]_{t} D \ar[d]^{g}& D' \ar[d]^{g'}\\ R \ar@/_.4cm/[rr]_{h'} \ar[r]^{h}& H \ar[r]^{s}& H'}\]
-	By hypothesis the whole rectangle and its left half are pushouts, therefore, by \Cref{lem:po1} its right square is a pushout too.
-The claim now follows from the fact that the pushout of an isomorphism is an isomorphism.
-\end{proof}
-
-If we look to direct derivations as transitions, it is natural to consider them as edges in a direct graph.
-Taking objects as vertices objects led us to the following definition \cite{heindel2009category}.
-
-\begin{definition}
-	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ $\mathcal{M}$-adhesive.
-The \emph{DPO-derivation graph} of $(\X, \R)$ is the (large)  directed graph $\gpo$ having as vertices the objects of $\X$ and in which an edge between $G$ and $H$ is a direct derivation $\dder{D}\colon G\Mapsto H$.	A \emph{derivation} $\der{D}$ between two objects $G$ and $H$ is a path between them in $\gpo$.
-The \emph{source} and \emph{target} of $\der{D}$ are, respectively, $G$ and $H$.
-\end{definition}
-
-\begin{remark}
-We can spell out more explicitly what  a derivation $\dder{D}$ is.
-An \emph{empty derivation} starting and ending in $G$ is just $G$ itself.
-A \emph{non-empty derivation} $\dder{D}$ is a sequence $\{\dder{D}_i\}_{i=0}^n$ of direct derivations such that:
-\begin{enumerate}
-	\item for every index $i$, $\dder{D}_i$ is a direct derivation $G_i \Mapsto G_{i+1}$;
-	\item $G_0=G$ and $G_{n+1}=H$.
-\end{enumerate}
-
-We will call the number $n+1$ the \emph{length} of the derivation, denoted by $\lgh(\der{D})$. We will also say that an empty derivation has length $0$.
-
-Moreover,  if every $\dder{D}_i$ applies the rule $\rho_i\in R$, then we can define an associated sequence of rules as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.
-\end{remark}
-
-\begin{remark}\label{rem:func}
-	Consider a derivation $\der{D}$ in a left-linear DPO-rewriting system $(\X, \R)$.
-We can take the subcategory $\Delta(\der{D})$ of $\X$ given by the arrows appearing in $\der{D}$.
-This subcategory comes equipped with an inclusion functor $I(\der{D})\colon \Delta(\der{D})\to \X$.
-Moreover, we can further define $\Deltamin(\der{D})$ as the subcategory of $\Delta(\der{D})$ containing only the bottom row of the derivation.
-\end{remark}
-
-\begin{notation}Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ be a derivation. We will depict the $i^\text{th}$ element $\dder{D}_i$ of $\der{D}$ as in the following diagram.  
-	\[\xymatrix{L_i \ar[d]_{m_i}& K_i \ar[d]^{k_i}\ar[l]_{l_i} \ar[r]^{r_i} & R_i \ar[d]^{h_i} \\G_{i} & \ar[l]^{f_{i}} D_{i} \ar[r]_{g_{i}}& G_{i+1} }\]
-	Notice that, in particular, if $\der{D}\colon G\to H$, then $G_0=G$ and $G_{n+1}=H$.
-When $\der{D}$ has length $1$ we will suppress the indexes.
-In such case, we will also identify $\der{D}$ with its only element.
-\end{notation}
-
-\begin{example}\todo{esempi di derivazione}
-\end{example}
-
-\begin{definition}
-	The \emph{DPO-derivation category} $\dpo$ of a left-linear DPO-rewriting system $(\X, \R)$ is the category in which arrows between $G$ and $H$ are given by, possibly empty, derivations.
-Composition is concatenation of paths in $\gpo$ and identities are given by empty derivations.
-\end{definition} 	
-\begin{remark}
-	More explicitly, given $\der{D}=\{\dder{D}\}_{i=0}^n$ between $G$ and $H$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^m$, their concatenation $\der{D}\cdot\der{D}'$ is the derivation $\{\dder{E}_i\}_{i=0}^{m+n+1}$ in which
-	\[\dder{E}_i:=\begin{cases}
-		\dder{D}_i & i \leq n\\
-		\dder{D}'_{i-(n+1)} & n< i 
-	\end{cases}\]
-
-Notice, moreover that, $\der{D}\cdot \der{D'}$ is equal to $\der{D}'$ if $\der{D}$ is empty, while it coincides with $\der{D}$ if $\der{D}'$ has length zero.
-\end{remark}
-
- \Cref{exa:conc} allows us to compose derivations with isomorphisms.
-
-\begin{definition} Let $(\X, \R)$ be a a left-linear DPO-rewriting system.
-Given a derivation $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ between $G$ and $H$ and isomorphisms $\phi\colon G\to G'$, $\psi\colon H\to H'$, the derivations  $\phi*\der{D}$ and $\der{D}*\psi$ are defined as
-	\[\phi *\der{D} := \begin{cases}
-		G' & \lgh(\der{D})=0\\ 
-		\{\phi* \dder{D}_0\}\cdot \{\dder{D}_i\}_{i=1}^{n}  & \lgh(\der{D})\neq 0
-	\end{cases} \qquad \der{D}*\psi := \begin{cases}
-	H' & \lgh(\der{D})=0\\ 
-	\{\dder{D}_i\}_{i=0}^{n-1} \cdot \{\dder{D}_n*\psi\} & \lgh(\der{D})\neq 0
-	\end{cases}\]
-
-	Moreover, if $\lgh(\der{D})>0$,  we define the derivation $\phi *\der{D} * \psi$ as
-	\[\phi *\der{D} * \psi = \{\phi* \dder{D}_0\}\cdot \{\dder{D}_i\}_{i=1}^{n-1} \cdot \{\dder{D}_n*\psi\}\] 
-\end{definition}
-
-\begin{remark}
-When $\der{D}$ consists only in the direct derivation $\dder{D}$, then $\phi*\der{D}*\psi$ is the derivation of length one whose unique element is $\phi*\dder{D}*\psi$.
-\end{remark}
-
-\subsection{Decorations and abstraction equivalence}
-We are often interested in an object of $\X$ only up to isomorphism.
-It is therefore useful to consider a version of $\gpo$ in which vertices are classes of isomorphism of object of $\X$.
-In order to do so, some preliminary work is needed.
-
-\begin{definition}\cite{mac2013categories}
-Let $\X$ be a category, we say that  $\X$ is \emph{skeletal} if, for every two objects $X$ and $Y$, the existence of an isomorphism $\phi\colon X\to Y$ entails $X=Y$.
-A \emph{skeleton} for a category $\X$ is a full subcategory $\ske$ which is skeletal and such that the inclusion functor $\ske\to \X$ is an equivalence.
-\end{definition}
-
-\begin{remark}
-By definition the inclusion $\ske \to \X$ is an equivalence.
-In particular, this mean that, for every objects $X$ of $\X$ there exists $\pi(X)$ in $\ske$ and an isomorphism $\phi_X\colon \pi(X) \to X$.
-\end{remark}
-
-\begin{proposition}\label{prop:ske}
-	Every category $\X$ has a skeleton. 
-\end{proposition}
-\begin{proof}
-	For every object $X\in \X$, pick a single representative $\pi(X)$ of its isomorphism class.
-Let $\ske$ be the full subcategory given by these objects.
-By definition $\ske$ is skeletal and the inclusion functor is full, faithful and essentially surjective.\qedhere
-\end{proof}
-\begin{remark}
-	The proof of \Cref{prop:ske} relies on the axiom of choice for classes.
-	\end{remark}
-\begin{remark}
-	It is possible to proof that every two skeleta of a given category $\X$ are isomorphic (not only equivalent).
-For the remaining of this paper we assume that a skeleton $\ske$ of $\X$ and a functor $\pi\colon \X\to \ske$ are chosen once and for all.
-\end{remark}
-
-\begin{definition}
-	Let $(\X, \R)$ be a left-linear DPO-rewriting system, a \emph{decorated derivation} between two objects $G$ and $H$ is a triple $(\der{D}, \alpha, \omega)$, where $\der{D}$ is a derivation between $G$ and $H$, and $\alpha\colon \pi(G)\to G$ and $\omega\colon \pi(H)\to H$ are isomorphisms.
-\end{definition}
-
-\begin{notation}
-	We will extend the use of the words length, source and target to decorated derivations in the obvious way, forgetting the decorations $\alpha$ and $\omega$.
-\end{notation}
-
-\begin{example}A decorated derivation $(\der{D}, \alpha, \omega)$ with $\der{D}$ empty is just a span
-	\[\xymatrix{G & \pi(G) \ar[r]^-{\omega} \ar[l]_-{\alpha} & G}\]
-	in which both $\omega$ and $\alpha$ are isomorphisms.
-\end{example}
-
-As we are interested in objects only up to isomorphism, so we are interested in (decorated) derivations only up to some notion of coherent isomorphism between them.
-This is done with the help of \Cref{rem:func}.
-
-\begin{definition}Let $(\X, \R)$ be a left-linear DPO-rewriting system,  an \emph{abstraction equivalence} between two derivations $\der{D}$ and $\der{D'}$ with the same length and such that $r(\der{D})=r(\der{D}')$, is a family of isomorphisms $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ such that, for every $i\in [0, \lgh(\der{D})]$ the following diagram commutes
-	\[\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i} \ar[l]_{f'_i}&G'_{i+1}\\  L_i \ar[u]^{n'_i} \ar[d]_{n_i}& K_i \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar[l]_{l_i} &R\ar[u]^{h'_i} \ar[d]_{h_i}\\G_i \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole \ar[r]_{g_i}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{H_i}}}\]
-
-Given two decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, we say that they are \emph{abstraction equivalent}, if $\lgh(\der{D})=\lgh(\der{D}')$, $r(\der{D})=r(\der{D'})$, and there exists an of abstraction equivalence between $\der{D}$ and  $\der{D}$ such that the triangles below commute.
-\[\xymatrix@C=15pt{&\pi(G_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G_{n+1}) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G_0 \ar[rr]_{\phi_{G_0}} && G'_0 &G_{n+1} \ar[rr]_{\phi_{G_{n+1}}} && G'_{n+1} } \]
-We will use $\equiv^a$ to denote the resulting relation.
-\end{definition}
-
-\begin{remark}\label{rem:equi}
-	It is immediate to see that $\equiv^a$ is an equivalence relation.
-Indeed $(\der{D}, \alpha, \omega)$ is abstract equivalent to itself via the abstract equivalence with the identities as components.
-Furthermore, if  $\{\phi_X\}_{X\in \Deltamin(\der{D})}$  witnesses $(\der{D}, \alpha, \omega)\equiv_a (\der{D}', \alpha', \omega')$, then considering $\{\phi^{-1}_X\}_{X\in \Deltamin(\der{D})}$ shows $(\der{D}', \alpha', \omega)\equiv_a (\der{D}, \alpha, \omega)$.
-Finally, transitivity is assured composing abstract equivalences.
-
-	We will denote by $[\der{D}, \alpha, \omega]_a$ is just the equivalence class of  $(\der{D}, \alpha, \omega)$.
-	 Such equivalence classes will be called  \emph{abstract decorated derivation}.  
-\end{remark}
-
-\begin{example}\label{rem:empty}
-Let $(\der{D},\alpha, \omega)$ be an empty derivation from an object $G$ and  $(\der{D}',\alpha', \omega')$ a another empty one from $G'$.
-If $(\der{D},\alpha, \omega)\equiv_a(\der{D}',\alpha', \omega')$ then an abstraction equivalence between $\der{D}$ and $\der{D}'$ is just an isomorphism $\phi\colon G\to G'$, so that $\pi(G)=\pi(G')$.
-Moreover, such isomorphism must fit in the diagrams below.
-\[\xymatrix@C=15pt{&\pi(G) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G\ar[rr]_{\phi} && G' &G \ar[rr]_{\phi} && G' } \]
-In particular, these two triangles imply that
-\begin{align*}
-	\alpha'\circ \alpha^{-1}&=\phi \\&=\omega'\circ \omega^{-1}
-\end{align*}
-\end{example}
-
-\begin{remark}\label{rem:res} \Cref{prop:unique} can be restated as saying that, given two direct derivations $\dder{D}$ and $\dder{D'}$ with the same match, there exists an abstract equivalence between them whose first component is an identity.
-\end{remark}
-
-\begin{remark}\label{rem:absequi}
-	Let $\der{D}$ be a derivation with source $G$ and target $H$. Let also $\phi\colon G'\to G$ and $\psi\colon H\to H'$ be two isomorphisms. Then for every $X\in \Deltamin(\der{D})$ we can define 
-	\[\varphi_X:=\begin{cases}
-		\phi^{-1} & X=G\\
-		\id{X} & \text{otherwise}
-	\end{cases} \qquad \varphi'_X:=\begin{cases}
-	\psi & X=H\\
-	\id{X} & \text{otherwise}
-	\end{cases}\]
-It is immediate to see that the family $\{\varphi_X\}_{X\in \Deltamin(\der{D})}$ is an abstraction equivalence between $\der{D}$ and $\phi *\der{D}$, while $\{\varphi'_X\}_{X\in \Deltamin(\der{D})}$ is one between $\der{D}$ and $\der{D}*\psi$.
-\end{remark}
-
-\begin{definition}\label{def:conc}
-Let $(\der{D}, \alpha, \omega)$ be a decorated derivation between $G$ and $H$ and $(\der{D}', \alpha', \omega')$ one between $H'$ and $K$.
-If $H$ and $H'$ are isomorphic, so that $\pi(H)=\pi(H')$, we define the  \emph{composite decorated derivation} putting
-\[(\der{D}, \alpha, \omega)\cdot (\der{D}', \alpha', \omega'):=\begin{cases}
-(\der{D}', \alpha'\circ \omega^{-1}\circ \alpha, \omega')	&\lgh(\der{D})=0 \\
-	(\der{D}, \alpha, \omega \circ (\alpha')^{-1}\circ \omega')&\lgh(\der{D}')=0 \text{ and } \lgh(\der{D})\neq 0\\
-(\der{D}*\omega^{-1}\cdot \alpha'*\der{D'}, \alpha, \omega')	&\text{otherwise}
-\end{cases}\]
-\end{definition}
-
-\begin{remark}\label{rem:lgt}
-	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ two composable decorated derivations   such that $\lgh(\der{D})=n$ and $\lgh(\der{D}')=m$.	 Then $(\der{D}*\omega^{-1}\cdot \alpha'*\der{D'}, \alpha, \omega')$ has length $n+m$.
-\end{remark}
-
-The next proposition justifies the use of decorations, guaranteeing that concatenation of abstract decorated derivations is well-defined.
-\begin{lemma}\label{lem:conc}
-	Given a decorated derivation $(\der{D}, \alpha, \omega)$  between $G$ and $H$ and  another one $(\der{E}, \beta, \xi)$ between $E$ and $K$ with $\pi(H)=\pi(E)$.
-If  $(\der{D}', \alpha', \omega')$ and $(\der{E}', \beta', \xi')$ are two other decorated derivations such that
-	\[[\der{D}, \alpha, \omega]_a = [\der{D}', \alpha', \omega']_a \qquad [\der{D}, \beta, \xi]_a=[\der{E}', \beta', \xi']_a\]
-	Then
-	\[[(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)]_a=[(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')]_a\]
-\end{lemma}
-
-\begin{proof} Take two abstraction equivalences $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ and $\{\varphi_X\}_{X\in \Deltamin(\der{D})}$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ and between $(\der{E}, \beta, \xi)$ and $(\der{E}', \beta', \xi')$, respectively.
-To fix the notation, suppose that goes from $G'$ to $H'$ and $(\der{E}', \beta', \xi')$ from $E'$ to $K'$.
-We have three cases.
-
-\begin{itemize}
-	\item $\lgh(\der{D})=0$. Then, $\lgh(\der{D}')$ is $0$ too. By \Cref{def:conc} we have
-	\begin{align*}
-	(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)&=(\der{E}, \beta\circ \omega^{-1}\circ \alpha, \xi)\\
-		(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')&=(\der{E}', \beta'\circ (\omega')^{-1}\circ \alpha', \xi')
-	\end{align*}
- Now, notice that $G$ and $H$ must coincide.
-Moreover, by \Cref{rem:empty} we also know that $\pi(G)=\pi(G')$ too.
-The same \Cref{rem:empty} entails that the inner squares of the following diagram are commutative, so that the whole rectangle commutes too.
- \[\xymatrix@C=35pt{\pi(G) \ar[r]^{\alpha} \ar[d]_{\id{\pi(G)}}& G  \ar[d]_{\phi_G}\ar[r]^-{\omega^{-1}} & \pi(G) \ar[d]_{\id{\pi(G)}} \ar[r]^{\beta}& E \ar[d]^{\varphi_E}\\\pi(G') \ar[r]_{\alpha'}& G' \ar[r]_-{(\omega')^{-1}} & \pi(G') \ar[r]_{\beta'} & E'}\]
-
- We can  then conclude that $\{\varphi_X\}_{X\in \Deltamin(\der{D})}$ witnesses the fact that $(\der{E}, \beta\circ \omega^{-1}\circ \alpha, \xi)$ is abstraction equivalent to $(\der{E}', \beta'\circ (\omega')^{-1}\circ \alpha', \xi')$.
-
-\item $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})= 0$. As in the point above, we get that also $\der{E}'$  is an empty derivation, thus we have
-\begin{align*}
-	(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)&=(\der{D},  \alpha, \omega \circ \beta^{-1}\circ \xi)\\
-	(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')&=(\der{D}',  \alpha', \omega' \circ (\beta')^{-1}\circ \xi')
-\end{align*}
-In this case we have that $E=K$ and that $\pi(E)=\pi(E')$. From \Cref{rem:empty} we deduce that the diagram below commutes.
-\[\xymatrix@C=35pt{\pi(E) \ar[r]^{\xi} \ar[d]_{\id{\pi(E)}}& E  \ar[d]_{\varphi_E}\ar[r]^-{\beta^{-1}} & \pi(E) \ar[d]_{\id{\pi(E)}} \ar[r]^{\omega}& H \ar[d]^{\phi_H}\\\pi(E') \ar[r]_{\xi'}& E' \ar[r]_-{(\beta')^{-1}} & \pi(E') \ar[r]_{\omega'} & H'}\]
-The thesis now follows at once.
-	\item $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})\neq 0$. In this case we have
-	\begin{align*}
-		(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \xi)&=(\der{D}*\omega^{-1}\cdot \beta*\der{E}, \alpha, \xi)\\
-		(\der{D}', \alpha', \omega')\cdot (\der{E}', \beta', \xi')&=(\der{D}'*(\omega')^{-1}\cdot \beta'*\der{E'}, \alpha', \xi')
-	\end{align*}
- To fix the notation, suppose that $\der{D}$, $\der{D}'$, $\der{E}$ and $\der{E}'$ are given by
-	\[\der{D}=\{\dder{D}_i\}_{i=0}^n \quad \der{D}'=\{\dder{D}'_i\}_{i=0}^n \quad \der{E}=\{\dder{E}_i\}_{i=0}^t \quad \der{E}'=\{\dder{E}'_i\}_{i=0}^t\]
-	Moreover, noticing that the rule applied by $\dder{D}_i$ and the one applied in $\mathcal{E}_i$  must coincide with, respectively, the one applied in $\dder{D}'_i$ and the one applied $\dder{E}'_i$.
-We will also assume that $\dder{D}_i$, $\dder{D}'_i$, $\dder{E}_i$ and $\dder{E}'_i$ are given, respectively, by the following four diagrams.
-	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}, i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}, i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}, i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}, i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}, i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}, i}} \\G_i & D_i \ar[r]_{g_{\der{D},i}} \ar[l]^{f_{\der{D},i}} & G_{i+1} & E_i & F_i\ar[r]_{g_{\der{E},i}} \ar[l]^{f_{\der{E},i}}  & E_{i+1}}\]
-	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}', i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}', i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}', i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}', i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}', i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}', i}} \\G'_i & D'_i \ar[r]_{g_{\der{D}',i}} \ar[l]^{f_{\der{D}',i}} & G'_{i+1} & E'_i & F'_i\ar[r]_{g_{\der{E}',i}} \ar[l]^{f_{\der{E}',i}}  & E'_{i+1}}\]
-
-Now, for every $X\in \Deltamin(\der{D}*\omega^{-1}\cdot \beta*\der{E})$ we can define
-\[\psi_X:=\begin{cases}
-	\phi_X & X\in  \Deltamin(\der{D})\text{ and } X\neq H\\\varphi_X & X\in  \Deltamin(\der{E}) \text{ and } X\neq E\\\id{\pi(H)}& X=\pi(H)\end{cases}\]
-Notice that, since $\psi_G=\phi_G$ and $\psi_K=\varphi_K$ we have at once  the commutativity of the triangles
-\[\xymatrix@C=15pt{&\pi(G) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(K) \ar[dr]^{\xi'} \ar[dl]_{\xi}\\ G\ar[rr]_{\psi_G} && G' &K \ar[rr]_{\psi_K} && K' } \]
-
-To show that $\{\psi_X\}_{\Deltamin(\der{D}*\omega^{-1}\cdot \beta*\der{E})}$ is an abstraction equivalence, it is now enough to prove the commutativity of the diagrams
-	\[\xymatrix@C=45pt@R=15pt{G'_n&D'_n \ar[r]^-{(\omega')^{-1}\circ g_{\der{D}',n}} \ar@/_.2cm/[dr]_(.6){g_{\der{D}',n}} \ar[l]_{f_{\der{D}',n}}&\pi(H') \\&&H' \ar[u]^{(\omega')^{-1}}\\  L_{\der{D}, n} \ar[uu]^{m_{\der{D}',n}} \ar[dd]_{m_{\der{D},n}}& K_{\der{D}, n} \ar[uu]^{k_{\der{D}',n}} \ar[dd]_{k_{\der{D},n}} \ar[r]^{r_{\der{D},n}} \ar[l]_{l_{\der{D},n}} &R_{\der{D}, n}\ar[u]^{h_{\der{D}',n}} \ar[d]_{h_{\der{D},n}}\\&&H \ar[d]_{\omega^{-1}}\\G_n \ar@/_.7cm/[uuuu]_(.35){\phi_{G_n}}|\hole&D_n\ar[l]^{f_{\der{D},n}}\ar@/_.7cm/[uuuu]_(.35){\phi_{D_n}}|\hole \ar@/^.2cm/[ur]^(.6){g_{\der{D},n}}\ar[r]_{\omega^{-1}\circ g_{\der{D},n}}&\pi(H)\ar@/_.7cm/[uuuu]_{\id{\pi(H)}}\\ \pi(E')&F'_0 \ar[l]_-{(\beta')^{-1}\circ f_{\der{E}',0}} \ar@/^.2cm/[dl]^(.6){f_{\der{E}',0}} \ar[r]^{g_{\der{E}',0}}&E'_1 \\E' \ar[u]_{(\beta')^{-1}}&& \\  L_{\der{E}, 0} \ar[u]_{m_{\der{E}', 0}} \ar[d]^{m_{\der{E}, 0}}& K_{\der{E}, 0} \ar[uu]_{k_{\der{E}', 0}} \ar[dd]^{k_{\der{E}, i}} \ar[r]^{r_{\der{E},0}} \ar[l]_{l_{\der{E},0}} &R_{\der{E}, 0}\ar[uu]_{h_{\der{E}',0}} \ar[dd]^{h_{\der{E},0}}\\E \ar[d]^{\beta^{-1}}&& \\\pi(E) \ar@/^.7cm/[uuuu]^{\id{\pi(E)}}&F_0\ar[l]^{\beta^{-1}\circ f_{\der{E},0}}\ar@/^.7cm/[uuuu]^(.35){\varphi_{F_0}}|\hole \ar@/_.2cm/[ul]_(.6){f_{\der{E},0}}\ar[r]_{g_{\der{E},0}}&E_1\ar@/^.7cm/[uuuu]^(.35){\varphi_{E_1}}|\hole}\]
-
-To see this, in turn, it is enough to show that	the squares
-\[\xymatrix{R_{\der{D}, n} \ar[d]_{h_{\der{D}, n}}\ar[r]^{h_{\der{D}', n}} & H' \ar[d]_{(\omega')^{-1}} &L_{\der{E}, 0} \ar[d]^{m_{\der{E}, 0}}\ar[r]^{m_{\der{E}', 0}}& E' \ar[d]^{(\beta')^{-1}}\\H\ar[r]_{\omega^{-1}} &\pi(H)&E \ar[r]_{\beta^{-1}} & \pi(E)}\]
-\[\xymatrix{D_n \ar[rr]^{\phi_{D_n}} \ar[d]_{g_{\der{D}, n}}&&D'_n \ar[d]_{g_{\der{D}', n}}&F_0 \ar[d]^{f_{\der{E}, 0}} \ar[rr]^{\varphi_{F_0}} && F_0' \ar[d]^{f_{\der{E}', 0}}\\H \ar[r]_-{\omega^{-1}} &\pi(H)&H' \ar[l]^-{(\omega')^{-1}}  &E \ar[r]_-{\beta^{-1}} & \pi(E) & E' \ar[l]^-{(\beta')^{-1}}}\]
-are commutative. For the first ones, we have
-\[
-\begin{split} 
-	\omega^{-1} \circ h_{\der{D}, n}&=\id{\pi(H)}\circ \omega^{-1} \circ h_{\der{D}, n} \\&=(\omega')^{-1}\circ \phi_H \circ \omega \circ \omega^{-1} \circ h_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H  \circ h_{\der{D}, n}\\&=(\omega')^{-1}  \circ h_{\der{D}', n}
-\end{split} \qquad  	\begin{split} 
-\beta^{-1} \circ m_{\der{E}, 0}&=\id{\pi(E)}\circ \beta^{-1} \circ m_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_{E} \circ \beta \circ \beta^{-1} \circ m_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_{E}  \circ m_{\der{E}, 0}\\&=(\beta')^{-1}  \circ m_{\der{E}', 0}
-\end{split}  \]
-
-Similarly, the commutativity of the second row of diagrams can be deduced from
-\[\begin{split}
-\omega^{-1} \circ g_{\der{D}, n}&=\id{\pi(H)}\circ \omega^{-1} \circ g_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H \circ \omega\circ \omega^{-1} \circ g_{\der{D}, n}\\&=(\omega')^{-1}\circ \phi_H  \circ g_{\der{D}, n}\\&= (\omega')^{-1} \circ g_{\der{D}', n}\circ \phi_{D_n}
-\end{split}\qquad \begin{split}\beta^{-1} \circ f_{\der{E}, 0}&=\id{\pi(E)}\circ \beta^{-1} \circ f_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_E \circ \beta\circ \beta^{-1} \circ f_{\der{E}, 0}\\&=(\beta')^{-1}\circ \varphi_E  \circ f_{\der{E}, 0}\\&= (\beta')^{-1} \circ f_{\der{E}', n}\circ \varphi_{F_0}
-\end{split}\]
-
- The thesis now follows.	\qedhere 
-\end{itemize}	
-\end{proof}
-
-\begin{definition}
-	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ an $\mathcal{M}$-adhesive category. The  category $\dpi$ is defined as follows:
-	\begin{itemize}
-		\item objects are isomorphism classes of objects of $\X$;
-		\item an arrow $[G]\to [H]$ is an equivalence class $[\der{D}, \alpha, \omega]_a$ of a decorated derivation between $G'$ and $H'$ for some $G'$ and $H'$ such that $\pi(G')=G$ and $\pi(H')=H$;
-		\item composition is concatenation of abstract decorated derivations;
-		\item the identity on $[G]$ is $[G, \alpha, \alpha]_a$, where $\alpha$ is any isomorphism $\pi(G)\to G$.	\end{itemize}
-\end{definition}
-
-\section{Independence in rewriting}
-\todo{A VERY NICE INTRO}
-
-\subsection{Sequentially independent and switchable derivations }
-\todo{this is an attempt to rewrite in a better way the following section. Hopefully this will spare us the use of fillers}
-\todo{A VERY NICE INTRO}
+\chapter{Independence in rewriting}
+
+In this chapter we discuss the notion of independence between two
+consecutive rewriting steps, a fundamental ingredient of the rewriting
+theory, which comes into play when viewing a sequence of steps as a
+concurrent computation. We observe that moving from linear to
+left-linear rules leads to the failure of various basic properties of
+the classical notion of independence used in the linear setting and we
+single out a framework in which these can be re-established, possibly
+in a weakened form.
+
+\section{Sequentially independent and switchable derivations }\label{subsec:switch}
+
+Sequential independence is the canonical notion of independence in the DPO approach.
 
@@
 	\label{de:sequential-independence}
-  Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Let also $\dder{D}\colon G\Mapsto H$ and $\dder{D'}\colon H\Mapsto T$ be the two direct derivations depicted below.
-
-	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{m'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
-
-	An \emph{independence pair} between $\dder{D}$ and $\dder{D'}$, is a pair of  arrows $i_1\colon R\to D'$ and $i_2\colon L'\to D$ such that the following diagram commutes.
-
-	\[\xymatrix@C=15pt{L \ar[d]_{m}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
-	We will say that $\dder{D}$ and $\dder{D'}$ are \emph{weakly sequentially independent} if an independence pair exists.
-If such independence pair is unique we will say that $\dder{D}$ and $\dder{D'}$ are \emph{sequentially independent}.
+	Let $\X$ be an $\mathcal{M}$-adhesive category 
+	and $(\X, \R)$ a left-linear rewriting system. 
+	Let also
+	$\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation of length $2$, with
+	$\dder{D}_i$ using rule $\rho_i = (l_i,r_i)$.  We say that $\dder{D}_0$ and
+	$\dder{D}_1$ are
+	\emph{sequentially independent}
+	if there is a pair of arrows
+	$i_0\colon R_0\to D_1$ and $i_1\colon L_1\to D_0$ such that the
+	following diagram commutes. In this case $(i_0,i_1)$ is called an  \emph{independence
+		pair}.
+	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
+		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
+		\ar@{.>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
+		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{.>}@/_.25cm/[dlll]^(.4){i_1}
+		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
+		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
+		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
+		\ar[rr]_{g_1}&& G_2}
+	\]
 \end{definition}
 
+\begin{remark}\label{rem:seqabs}
+Let $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ be an abstraction equivalence between $\der{D}=\{\dder{D}_i\}_{i=0}^1$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^1$.
+If there is an independence pair between $(i_0, i_1)$ between $\dder{D}_0$ and $\dder{D}_1$, then $(\phi_{D_0}\circ i_1, \phi_{D_1}\circ i_0)$ is an independence pair between $\dder{D}'_0$ and $\dder{D}'_1$.
+Indeed we have
+\[\begin{split}
+g'_0\circ \phi_{D_0}\circ i_1&=\phi_{G_1}\circ g_0\circ i_1\\&=\phi_{G_1}\circ m_1\\&= m'_1
+\end{split}\qquad \begin{split}
+f'_1\circ \phi_{D_1}\circ i_0&=\phi_{G_1}\circ f_1\circ i_0\\&=\phi_{G_1}\circ h_0\\&= h'_1
+\end{split}\]
+\end{remark}
+
+\begin{remark}\label{rem:uni}
+	It is worth mentioning that if $(\X, \R)$ is a linear rewriting system then two derivations $\dder{D}_0$ and $\dder{D}_1$ can have at most one independence pair.
+Indeed if $(i_0,i_1)$ and $(i'_0, i'_1)$ are independence pairs, then
+	\[g_0\circ i_1 = g_0\circ i'_1 \qquad f_1\circ i_0=f_1\circ i'_0\]
+	But in linear systems $g_0$ and $f_1$ are both monos, entailing $i_0=i'_0$ and $i_1=i'_1$.
+\end{remark}
+
+Intuitively, the existence of the independence pair
+captures the possibility of switching the application of the two rules:
+$f_0 \circ i_1$ is a match for $\rho_1$ in $G_0$ and the
+existence of $i_0 : R_0 \to D_1$ means that $\rho_1$ does not delete
+items in the image of $K_0$, thus $\rho_0$ can be applied after
+$\rho_1$. The following definition formalise what it means for a derivation to be the switch of another.
+
+\begin{definition}[Switch] \label{def:switch}
+	Let $\X$ be an $\mathcal{M}$-adhesive category 
+	and $(\X, \R)$ a left-linear rewriting system. 
+	Let also
+	$\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation made
+	of two sequentially independent derivations $\dder{D}_0$,
+	$\dder{D}_1$ with independence pair $(i_0, i_1)$, as in the diagram
+	on the left below. A \emph{switch} of $\der{D}$ along $(i_0,i_1)$ is
+	a derivation $\der{E}=\{\dder{E}_i\}_{i=0}^1$, between the same objects and using the same rules
+	in reverse order, as in the diagram on the right below
+	\[
+	\def\objectstyle{\scriptstyle}\def\labelstyle{\scriptstyle}
+	\xymatrix@C=1.1mm@R=8mm{
+		{L_0} \ar[d]_{m_0}
+		& & {K_0} \ar@{>->}[ll]_{l_0} \ar[rr]^{r_0} \ar[d]_{k_0}
+		& & {R_0} \ar[drr]|(.35)\hole_(.6){h_0}  \ar@/^.22cm/[drrrrrr]|(.3)\hole^(.75){i_0}
+		& & & & 
+		% 
+		{L_1}\ar[dll]|(.35)\hole^(.6){m_1} \ar@/_.22cm/_(.75){i_1}[dllllll]
+		& & {K_1} \ar@{>->}[ll]_{l_1} \ar[rr]^{r_1} \ar[d]^{k_1}
+		& & {R_1} \ar[d]^{h_1} \\
+		% 
+		% 
+		{G_0}
+		& & {D_0} \ar@{>->}[ll]^{f_0} \ar[rrrr]_{g_0}
+		& & & & {G_1} & &
+		& &  {D_1} \ar@{>->}[llll]^{f_1} \ar[rr]_{g_1}
+		& & {G_2}
+	}
+	% 
+	\xymatrix@C=1.1mm@R=8mm{
+		{L_1} \ar[d]_{m_0'}
+		& & {K_1} \ar@{>->}[ll]_{l_1} \ar[rr]^{r_1} \ar[d]_{k_0'}
+		& & {R_1} \ar[drr]|(.35)\hole_(.6){h_0'}  \ar@/^.22cm/@{.>}^(.75){i_0'}|(.3)\hole[drrrrrr]
+		& & & & 
+		% 
+		{L_0}\ar[dll]|(.35)\hole^(.6){m_1'} \ar@/_.22cm/@{.>}_(.75){i_1'}[dllllll] 
+		& & {K_0} \ar@{>->}[ll]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
+		& & {R_0} \ar[d]^{h_1'} \\
+		% 
+		% 
+		{G_0}
+		& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rrrr]_{g_0'}
+		& & & & {G'_1} & &
+		& &  {D_1'} \ar@{>->}[llll]^{f_1'} \ar[rr]_{g_1'}
+		& & {G_2}  }
+	%
+	\]
+	such that there is an independence pair $(i_0', i_1')$ between
+	$\dder{E}_0$ and $\dder{E}_1$ and 
+	\begin{center}   
+		$m_0=f_0' \circ i_1'$
+		\qquad $h_1=g_1' \circ i_0'$
+		\qquad $m_0'= f_0 \circ i_1$
+		\qquad $h_1'= g_{1}\circ i_0$.
+	\end{center}
+
+	If a switch of $\dder{D}_0$ and $\dder{D}_1$ exists we say that
+	they are \emph{switchable}.
+\end{definition}
+
+\begin{example}	\label{ex:seq-ind}
+	Consider the rewriting system  $(\cat{Graph}, \R)$ and the derivarion $\der{D}$ introduced in \Cref{ex:1}.	Steps $\dder{D}_1$ and $\dder{D}_2$ are clearly sequential
+	independent via the arrows $R_1 \to D_2$, $L_2 \to D_1$
+	mapping nodes according to their numbering.
+	%
+	A switch of $\der{D}$ along such independence pair is the derivation
+	$\der{E}$ depicted below. Instead,  the first two
+	steps $\dder{D}_0$ and $\dder{D}_1$ are not sequential independent. Intuitively, this happens because $\rho_1$ uses the node generated by $\rho_0$ to produce a self-loop.
+
+\begin{center}
+	\begin{tikzpicture}[node distance=2mm, font=\small,  baseline=(current bounding box.center)]      
+		\node (L1) at (0,2) {
+			\begin{tikzpicture}
+				% 
+				\node at (0,0.53) {};
+				\node at (0,0) [node, label=below:$1$] (1) {} ;
+				% 
+				\pgfBox
+			\end{tikzpicture} 
+		};
+		\node [right=of L1] (K1) {
+			\begin{tikzpicture}
+				% 
+				\node at (0,0.53) {}; 
+				\node at (0,0) [node, label=below:$1$] (1) {};
+				% 
+				\pgfBox
+			\end{tikzpicture} 
+		};
+		%     \node [above=of K1] {$\rho_0$};
+		\node [above] at (K1.north) {$\rho_0$};
+		\node [right=of K1](R1) {
+			\begin{tikzpicture}
+				\node at (0,0.53) {}; 
+				\node at (0,0) [node, label=below:$1$] (1) {};
+				\node at (.5,0) [node, label=below:$2$] (2) {}; 
+				\draw[coloredge] (1) to[out=20, in=160] (2);
+				% 
+				\pgfBox
+			\end{tikzpicture}
+		};
+		\path (K1) edge[->] node[trans, above] {} (L1);
+		\path (K1) edge[->] node[trans, above] {} (R1);
+
+		\node at (4,2) (L3) {
+			\begin{tikzpicture}
+				% 
+				\node at (0,0.53) {}; 
+				\node at (0,0) [node, label=below:$1$] (1) {} ;
+				\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+				% 
+				\pgfBox
+			\end{tikzpicture} 
+		};
+		\node [right=of L3] (K3) {
+			\begin{tikzpicture}
+				% 
+				\node at (0,0.53) {}; 
+				\node at (0,0) [node, label=below:$1$] (1) {} ;
+				\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+				% 
+				\pgfBox
+			\end{tikzpicture} 
+		};
+		%     \node [above=of K3] {$\rho_2$};
+		\node [above] at (K3.north) {$\rho_2$};
+		\node [right=of K3] (R3) {
+			\begin{tikzpicture}
+				\node at (0,0.53) {}; 
+				\node at (0,0) [node, label=below:$12$] (12) {};
+				% 
+				\pgfBox
+			\end{tikzpicture}
+		};
+		\path (K3) edge[->] node[trans, above] {} (L3);
+		\path (K3) edge[->] node[trans, above] {} (R3);
+
+		\node at (8,2) (L2) {
+			\begin{tikzpicture}
+				% 
+				\node at (0,0.53) {}; 
+				\node at (0,0) [node, label=below:$2$] (1) {} ;
+				% 
+				\pgfBox
+			\end{tikzpicture} 
+		};
+		\node [right=of L2] (K2) {
+			\begin{tikzpicture}
+				% 
+				\node at (0,0.53) {}; 
+				\node at (0,0) [node, label=below:$2$] (1) {};
+				% 
+				\pgfBox
+			\end{tikzpicture} 
+		};
+		%     \node [above=of K2] {$\rho_1$};
+		\node [above] at (K2.north) {$\rho_1$};
+
+		\node [right=of K2] (R2) {
+			\begin{tikzpicture}
+				\node at (0,0) [node, label=below:$2$] (1) {}
+				edge [in=55, out=85, loop] ();
+				% 
+				\pgfBox
+			\end{tikzpicture}
+		};
+		\path (K2) edge[->] node[trans, above] {} (L2);
+		\path (K2) edge[->] node[trans, above] {} (R2);
+
+		%%%%%% second row
+		\node at (0,0) (G1) {
+			\begin{tikzpicture}
+				% 
+				\node at (0,0.53) {};
+				\node at (0,0) [node, label=below:$1$] (1) {} ;
+				% 
+				\pgfBox
+			\end{tikzpicture} 
+		};
+		\node [right=of G1] (D1) {
+			\begin{tikzpicture}
+				% 
+				\node at (0,0.53) {}; 
+				\node at (0,0) [node, label=below:$1$] (1) {};
+				% 
+				\pgfBox
+			\end{tikzpicture} 
+		};
+		\node at (3,0) (G2) {
+			\begin{tikzpicture}
+				% 
+				\node at (0,0.53) {}; 
+				\node at (0,0) [node, label=below:$1$] (1) {} ;
+				\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+				\draw[coloredge] (1) to[out=20, in=160] (2);
+				% 
+				\pgfBox
+			\end{tikzpicture} 
+		};
+		\path (D1) edge[->] node[trans, above] {} (G1);
+		\path (D1) edge[->] node[trans, above] {} (G2);
+		\path (L1) edge[->] node[trans, above] {} (G1);
+		\path (K1) edge[->] node[trans, above] {} (D1);
+		\path (R1) edge[->] node[trans, above] {} (G2);
+
+		\node at (5.5,0) (D2) {
+			\begin{tikzpicture}
+				% 
+				\node at (0,0.53) {};
+				\node at (0,0) [node, label=below:$1$] (1) {} ;
+				\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+				\draw[coloredge] (1) to[out=20, in=160] (2);
+				% 
+				\pgfBox
+			\end{tikzpicture} 
+		};
+		\node at (7.4,0) (G3) {
+			\begin{tikzpicture}
+				% 
+				\node at (0,0.53) {}; 
+				\node at (0,0) [node, label=below:$12$] (12) {}
+				edge [in=125, out=155, colorloop] ();
+				% 
+				\pgfBox
+			\end{tikzpicture} 
+		};
+
+		\path (D2) edge[->] node[trans, above] {} (G2);
+		\path (D2) edge[->] node[trans, above] {} (G3);
+		\path (L3) edge[->] node[trans, above] {} (G2);
+		\path (K3) edge[->] node[trans, above] {} (D2);
+		\path (R3) edge[->] node[trans, above] {} (G3);
+
+		\node at (9.1,0) (D3) {
+			\begin{tikzpicture}
+				% 
+				\node at (0,0.53) {}; 
+				\node at (0,0) [node, label=below:$12$] (12) {}
+				edge [in=125, out=155, colorloop] ();
+				% 
+				\pgfBox
+			\end{tikzpicture} 
+		};
+		\node [right=of D3] (G4) {
+			\begin{tikzpicture}
+				% 
+				\node at (0,0) [node, label=below:$12$] (12) {}
+				edge [in=55, out=85, loop] ()
+				edge [in=125, out=155, colorloop] ();
+				% 
+				\pgfBox
+			\end{tikzpicture} 
+		};
+
+		\node[font=\scriptsize, below] at (G1.south) {$G_0$};
+		\node[font=\scriptsize, below] at (D1.south) {$D_0$};      
+		\node[font=\scriptsize, below] at (G2.south) {$G_1$};
+		\node[font=\scriptsize, below] at (D2.south) {$D_1'$};      
+		\node[font=\scriptsize, below] at (G3.south) {$G_2'$};
+		\node[font=\scriptsize, below] at (D3.south) {$D_2'$};      
+		\node[font=\scriptsize, below] at (G4.south) {$G_3$};
+
+		\path (D3) edge[->] node[trans, above] {} (G3);
+		\path (D3) edge[->] node[trans, above] {} (G4);
+		\path (L2) edge[->] node[trans, above] {} (G3);
+		\path (K2) edge[->] node[trans, above] {} (D3);
+		\path (R2) edge[->] node[trans, above] {} (G4);
+	\end{tikzpicture}
+	%
+\end{center}
+
+\end{example}
+
+We can now prove some properties relating switching and abstraction equivalence. As a first step we can show that switches along the same independence paire are unique up to abstraction equivalence.
+
+\begin{lemma}[Uniqueness of switches]
+	\label{thm:switch_uni}
+	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation and suppose
+	that both $\der{E}=\{\dder{E}_i\}_{i=0}^1$ and
+	$\der{F}=\{\dder{F}_i\}_{i=0}^1$ are switches of $\dder{D}_0$ and
+	$\dder{D}_1$. Then there is an abstraction equivalence between $\der{E}$ and $\der{F}$, whose first component is $\id{G_0}$.
+\end{lemma}
+
+\begin{proof}
+	By definition of switch $\der{E}_0$ and $\der{F}_0$ have the same match $f_0\circ i_1$ and that $\der{E}_1$ and $\der{F}_1$ have the same comatch $g_1\circ i_0$.
+Thus we get the solid part of the diagram below
+	\[\xymatrix@C=22pt{G_{0} && \ar@{>->}[ll]_{f_{\der{F},0}} D_{\der{F},0} \ar[rr]^{g_{\der{F},0}}&& G_{\der{F},1} && \ar@{>->}[ll]_{f_{\der{F},1}} D_{\der{F},1} \ar[rr]^{g_{\der{F},1}}&& G_{2}\\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}&& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_{1} \ar@/^.35cm/[drrr]|(.315)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{h_{\der{E},0}} \ar@/_.35cm/[urrr]|(.315)\hole^(.4){a_0} \ar[ur]|(.3)\hole^{h_{\der{F},0}}& &L_{0} \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{m_{\der{E},1}} \ar@/^.35cm/[ulll]_(.4){a_1} \ar[ul]|(.3)\hole_{m_{\der{F},1}}& K_{0} \ar[d]_{k_{\der{E},1}} \ar[u]^{k_{\der{F},1}}\ar@{>->}[l]_{l_{0}} \ar[rr]^{r_0} && R_{0} \ar[d]_{g_1\circ i_0} \ar[u]^{g_1\circ i_0}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} && \ar[ll]^{f_{\der{E},0}} D_{\der{E},0} \ar@{.>}@/^.5cm/[uu]^(.33){\phi_{0}}|\hole \ar[rr]_{g_{\der{E},0}}&& G_{\der{E},1} \ar@{.>}[uu]^(.76){\psi_1}|(.45)\hole |(.55)\hole&& \ar@{>->}[ll]^{f_{\der{E},1}} D_{\der{E},1} \ar@{.>}@/_.5cm/[uu]_(.33){\phi_{1}}|\hole\ar[rr]_{g_{\der{E},1}}&& G_{2}\ar@{.>}@/_.5cm/[uu]_{\psi_2}}\]
+
+Now, by \Cref{prop:unique} we get $\phi_0\colon D_{\der{E},0}\to D_{\der{F},0}$ and $\psi_1 \colon G_{\der{E},1}\to G_{\der{F},1}$ such that the diagram below commutes.
+\[\xymatrix{G_{0} & \ar@{>->}[l]_{f_{\der{F},0}} D_{\der{F},0} \ar[r]^{g_{\der{F},0}}& G_{\der{F},1} \\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar[l]_{l_1} \ar[r]^{r_1} & R_{1}  \ar[d]_{h_{\der{E},0}}  \ar[u]^{h_{\der{F},0}}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} & \ar@{>->}[l]^{f_{\der{E},0}} D_{\der{E},0} \ar@/^.5cm/[uu]^(.33){\phi_{0}}|\hole \ar[r]_{g_{\der{E},0}}& G_{\der{E},1} \ar@/_.5cm/[uu]_{\psi_1}}\]
+
+ But then we have
+ \begin{align*}
+ 	f_{\der{F},0}\circ \phi_0\circ j_1&=f_{\der{E},0} \circ j_1\\&=m_0\\&=f_{\der{F},0}\circ a_1 \end{align*}
+	which, since $f_{\der{D},0}$ is mono, entails $a_1= \phi_0\circ j_1$.	This equality, in turn, gives us that
+	\begin{align*}
+	\psi_1\circ m_{\der{E},1}&=\psi_1 \circ g_{\der{E},0}\circ j_1\\&=g_{\der{F},0}\circ \phi_0\circ j_1\\&=g_{\der{F},0}\circ a_1\\&=m_{\der{F},1}
+	\end{align*}
+
+	Since $\psi_1$ is an isomorphism, the square below is a pushout. 
+		\[\xymatrix{K_0 \ar[d]_{k_{\der{E,1}}} \ar@{>->}[r]^{l_0}& L_0 \ar[d]^{\psi_1\circ m_{\der{E},1}}\\D_{\der{E},1} \ar@{>->}[r]_{\psi_1\circ f_{\der{E},1}}& G_{\der{F}, 1}}\]
+
+	 Moreover, we have already shown that $\psi_1\circ m_{\der{E},1}=m_{\der{F},1}$.
+Thus, by \Cref{prop:unique} there are the dotted $\phi_1\colon D_{\der{E},1}\to D_{\der{F},1}$ and $\psi_2\colon G_2\to G_2$ as below.
+	\[\xymatrix{G_{\der{F},1} & \ar@{>->}[l]_{f_{\der{F},1}} D_{\der{F},1} \ar[r]^{g_{\der{F},1}}& G_2 \\L_0 \ar[d]^{m_{\der{E},1}} \ar[u]_{m_{\der{F},1}}& K_{0} \ar[d]^{k_{\der{E},1}} \ar[u]_{k_{\der{F},1}}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_{0}  \ar[d]_{g_1\circ i_0}  \ar[u]^{g_1\circ i_0}\\ \ar@/^.5cm/[uu]^{\psi_1} G_{\der{E},1} & \ar@{>->}[l]^{f_{\der{E},1}} D_{\der{E},1} \ar@{.>}@/^.5cm/[uu]^(.33){\phi_{1}}|\hole \ar[r]_{g_{\der{E},1}}& G_2 \ar@{.>}@/_.5cm/[uu]_{\psi_2}}\]
+
+	To conclude, it is now enough to notice that
+	\begin{align*}
+f_{\der{F},1} \circ \phi_1\circ j_0&=\psi_1\circ f_{\der{E},1}\circ j_0\\&=\psi_1\circ h_{\der{E,0}}\\&=h_{\der{F},0}\\&=f_{\der{F},1}\circ a_0
+	\end{align*}
+	allowing us to deduce $ \phi_1\circ j_0=a_0$.
+\end{proof}
+
+\begin{corollary}\label{cor:switch}
+	\todo{switches}
+\end{corollary}
+
+\begin{corollary}\label{cor:cons}
+	\todo{consistency of switch}
+\end{corollary}
+
+Another useful property of switches is that they can be performed back and forth, giving back the original derivation. This is the content of the following two results.
+
+\todo{switch di switch}
+
+\begin{proposition}
+	contenuto...
+\end{proposition}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{corollary}
+	contenuto...
+\end{corollary}
+
+As we mentioned, for linear rewriting systems
+it is canonical to identify
+derivations that are equal ``up to switching'', i.e.~that differ
+only in the order of independent steps. The same notion can be given
+for left-linear rewriting systems by relying on the notion of switch.
+
+We  recall some notations on permutations.  A \emph{permutation} on
+$\interval[0]{n}$ is a bijection
+$\sigma : \interval[0]{n} \to \interval[0]{n}$. It is a
+\emph{transposition} $\nu$ if there are $i, j \in \interval{n}$,
+$i \neq j$ such that $\sigma(i)=j$, $\sigma(j) = i$, and
+$\sigma(k) = k$ otherwise; it is denoted as $\transp{i}[j]$. Given a permutation $\perm$, 
+an \emph{inversion} for $\sigma$ is a pair $(i,j)$ such that $i<j$ and
+$\sigma(j)< \sigma(i)$; $\inv{\sigma}$ denotes the set of
+inversions of $\perm$.
+
+Switch equivalence is now defined as the equivalence relating derivations that 
+can be obtained one from another by a sequence of switches. Moreover, intermediate graphs can be taken up to isomorphism according to abstraction equivalence.
+
+\begin{definition}[Switching sequence]
+	\label{de:switch-equivalence}
+	Let $(\X, \R)$ be a left-linear rewriting system.  Let also
+	$\der{D}, \der{E} : G \Mapsto H$ be derivations with the same
+	length, $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and
+	$\der{E}=\{\dder{E}_{i}\}_{i=0}^n$. If
+	$\dder{D}_i \cdot \dder{D}_{i+1}$ is a switch of
+	$\dder{E}_i \cdot \dder{E}_{i+1}$ for some $i \in [0,n-1]$ and  $\dder{D}_j = \dder{E}_j$ for each $j \not \in \{i,i+1\}$ then we write
+	$\der{D} \shift{\transp{i}} \der{E}$. 
+	A \emph{switching sequence} is a sequence $\{\der{D}_{k}\}_{k=0}^m$
+	of derivations such that
+	$\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
+	\shift{\nu_m} \der{D}_m$  with $\nu_{k} = \transp{i_k}$.
+
+	Let us denote by $\nu_{k,h}$ the composition
+	$\nu_h \circ \nu_{h-1} \circ \ldots \nu_k$. We say that the
+	switching sequence \emph{consists of inversions} if for all
+	$k \in \interval[0]{m}$ the transposition $\nu_k$ is an inversion
+	for $\nu_{1,m}$.
+
+	Two derivations $\der{D}, \der{E}:G\Mapsto H$ are \emph{switch
+		equivalent}, written $\der{D}\equiv^{sh} \der{E}$, if there is a
+	switching sequence $\{\der{D}_{k}\}_{k=0}^m$ such that
+	$\der{D}\equiv_a \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2}
+	\ldots \shift{\nu_m} \der{D}_m \equiv _a \der{E}$.   
+	To point out a chosen permutation of rewriting steps, we will also write $\der{D}\equiv^{sh}_{\sigma} \der{E}$, 
+	where $\sigma$ is the composition of the transposition appearing in a chosen switching sequence. 
+\end{definition}
+
+\subsection{The local Church-Rosser Theorem}\label{subsec:CR}
+
+The fact that sequential independence implies switchability always
+holds for linear rules (see \Cref{prop:equi}). The result is so
+indispensable that typically, in the literature, it is not even
+stated, in the sense that switchability is not introduced
+axiomatically as in Definition~\ref{def:switch}, but it is based on
+the explicit construction of a switch.
+
+For left-linear rewriting systems
+sequential independence does not imply switchability (while the
+converse implication clearly holds), as shown by the next example.
+
+\begin{figure}
+	\begin{subfigure}{0.2\textwidth}
+		{\small
+			\xymatrix@C=16pt@R=1pt{
+				& 0 \ar@{-}[dd] \ar@{-}[ddddddl] \ar@{-}[ddddddr] &  \\
+				&  & \\
+				& 1 \ar@{-}[dd] \ar@{-}[ddddl]  \ar@{-}[ddddr]   &  \\
+				&  & \\
+				& 2 \ar@{.}[d] \ar@{-}[ddl]   \ar@{-}[ddr]     &  \\
+				&  \ar@{.}[dl]   \ar@{.}[dr] & \\
+				b \ar@{-}[dr] & & c \ar@{-}[dl]\\
+				& a 
+			}
+		}
+		\caption{Poset $(P, \sqsubseteq)$}
+		\label{fig:diff1:P}
+	\end{subfigure}
+	\begin{subfigure}{0.58\textwidth}
+		\xymatrix@C=20pt{
+			a \ar[d]_{\sqsubseteq} & a \ar[d]_{\sqsubseteq} \ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} & 
+			0 \ar@{>->}@/^.35cm/[drrr]|(.3)\hole^(.75){\id{0}}
+			\ar@{>->}[dr]|(.3)\hole_{\id{0}} &  &
+			a \ar@/_.35cm/[dlll]_(.75){\sqsubseteq}
+			\ar[dl]|(.3)\hole^{\sqsubseteq} & 
+			a \ar[d]^{\sqsubseteq}\ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} &
+			b \ar[d]_{\sqsubseteq}\\
+			c &
+			\ar@{>->}[l]^{\id{c}} c \ar[rr]_{\sqsubseteq}& &  0 &&
+			\ar@{>->}[ll]^{\id{0}} 0 \ar@{>->}[r]_{\id{0}}& 0
+		}
+		\caption{Two rewriting steps}
+		\label{fig:diff1:rew}
+	\end{subfigure}
+	\begin{subfigure}{0.20\textwidth}
+		\xymatrix@C=20pt{a \ar[d]^{\sqsubseteq}& a
+			\ar[d]^{\sqsubseteq}\ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} & b \\c & c
+			\ar@{>->}[l]^{\id{c}}
+		}
+		\caption{No rewriting step}
+		\label{ex:diff1:no-step}
+	\end{subfigure}
+	\caption{Sequential independence does not imply switchability}
+	\label{fig:diff1} 
+\end{figure}
+
 \begin{example}
-	\todo{sequential independence}
+	\label{ex:diff1}
+	Consider the poset $(P, \sqsubseteq)$ in Fig.~\ref{fig:diff1:P} where
+	$P = \mathbb{N} \cup \{a,b,c\}$ and $\sqsubseteq$ is defined by
+	$m \sqsubseteq n$ if $m \geq n$, $a \sqsubseteq x$ for all $x \in P$
+	and $b, c \sqsubseteq n$ for all $n \in \mathbb{N}$.
+	%
+	Let $\X$ be the  
+	category associated with this order, which by \Cref{rem:iso} is
+	$\mathsf{I(\X)}$-adhesive. 
+	%
+	Consider a rewriting
+	system whose set of rules contains the following 
+	\[\xymatrix{a & a \ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & 0 & a & a
+		\ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & b }\]
+	We can then consider the  derivation
+	$\der{D}=\{\dder{D}_i\}_{i=0}^1$ in Fig.~\ref{fig:diff1:rew}.
+	% \[
+	%   \xymatrix@C=30pt{a \ar[d]_{m_0}&& a \ar[d]_{k_0}\ar[ll]_{\id{a}}
+		%     \ar[r]^{(a,0)} & 0 \ar@/^.35cm/[drrr]|(.315)\hole_(.45){\id{0}}
+		%     \ar[dr]|(.3)\hole_{\id{0}} && a \ar@/_.35cm/[dlll]^(.45){(a,c)}
+		%     \ar[dl]|(.3)\hole^{(a,0)}& a \ar[d]^{(a,0)}\ar@{>->}[l]_{\id{a}}
+		%     \ar[rr]^{(a,b)} && b \ar[d]^{(b,0)}\\c &&
+		%     \ar@{>->}[ll]^{\id{c}} c \ar[rr]_{(c,0)}&& 0 &&
+		%     \ar@{>->}[ll]^{\id{0}} 0 \ar[rr]_{\id{0}}&& 0}\]
+	%
+	Note that the two direct derivations are sequential
+	independent. However there is no switch since the rule applied by
+	$\dder{D}_1$ cannot be applied to $c$. In fact, there is a unique morphism
+	$a\to c$, yielding the diagram in Fig.~\ref{ex:diff1:no-step}. But $b$ and $c$
+	do not have a supremum in the poset underlying $\X$, thus the arrows
+	$a\to b$ and $a\to c$ do not have a
+	pushout. Hence we do not get a direct derivation from $c$.
 \end{example}
+
+The conditions guaranteeing switchability are inspired
+by the notion of \emph{canonical filler}
+\cite{heindel2009category}.
+
+\begin{definition}[Strong independence pair]
+	\label{def:filler}
+	Let $\X$ be an $\mathcal{M}$-adhesive category 
+	and $(\X, \R)$ a left-linear rewriting system. 
+	Let also $(i_0, i_1)$ be an independence pair between two direct
+	derivations $\dder{D}_0$, $\dder{D}_1$
+	as in the solid part of the diagram below
+	\[
+	\xymatrix@C=18pt@R=17pt{L_0 \ar[d]_{m_0}&& K_0
+		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} \ar@{.>}@/^.20cm/[ddrr]|(.32)\hole|(.57)\hole_(.7){u_0} & R_0
+		\ar@/^.35cm/[drrr]|(.3)\hole^(.2){i_0} \ar[dr]|(.3)\hole_{h_0}
+		&& L_1 \ar@/_.35cm/[dlll]_(.2){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
+		\ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} \ar@{.>}@/_.20cm/[ddll]|(.32)\hole|(.57)\hole^(.7){u_1} && R_1 \ar[d]^{h_1} \\
+		%
+		G_0 &&
+		\ar@{>->}[ll]^{f_0} D_0 \ar[rr]_(.3){g_0}&& G_1 &&
+		\ar@{>->}[ll]^(.3){f_1} D_1 \ar[rr]_{g_1}&& G_2\\
+		%
+		& & & & P \ar@/^.3cm/@{>.>}[ull]^{p_0} \ar@/_.3cm/@{.>}[urr]_{p_1}
+	}
+	\]
+
+	Consider the pullback of $g_0$ and $f_1$, which yields $p_i : P \to D_i$
+	for $i \in \{0,1\}$ and the mediating arrows $u_i\colon K_i\to P$ 
+	for $i \in \{0,1\}$ 
+	into the pullback object (see \Cref{prop:tec} for details). 
+	We say that $(i_0, i_1)$ is a \emph{strong independence pair} if
+	the first two squares depicted  
+	below are pushouts and if the pushout of $r_1 : K_1 \to R_1$ and $u_1 : K_1 \to P$ exists
+	\[
+	\xymatrix@R=16pt{
+		K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
+		\ar@{>->}[r]^{l_1} \ar[d]_{u_1}& L_1 \ar[d]^{i_1}
+		&K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1\ar@{.>}[d]^{j_0}
+		\\
+		P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0
+		& P \ar@{.>}[r]_{q_1} & Q_1
+	}
+	\]
+\end{definition}
+
+We can now prove a Local Church-Rosser Theorem for strong independence pairs.
+
+\begin{proposition}	\label{pr:church}
+	Let $(i_0, i_1)$ be a strong independence pair
+	between $\dder{D}_0$ and $\dder{D}_1$. Then $\dder{D}_0$ and
+	$\dder{D}_1$ are switchable.
+\end{proposition}
+
+The correspondence between sequential independence and switchability
+is fundamental. We name the class of rewriting systems where this property holds.
+
+\begin{definition}[Strong enforcing rewriting systems]
+	A left-linear rewriting system is \emph{strong enforcing} if
+	every independence pair between two direct derivations is strong.
+\end{definition}
+
+We can identify a large class of adhesive categories such that all
+left-linear rewriting systems over such categories are strong
+enforcing. This class includes $\cat{Set}$ and it is closed
+under comma and functor category constructions.  As such, it includes
+essentially all categories (e.g., presheaves over set) that are
+typically considered for modelling purposes. Notably, it contains the
+category $\cat{Graph}$ of directed graphs.
+This is a natural generalisation from adhesive to $\mathcal{M}$-adhesive categories of a class studied in \cite{baldan2011adhesivity} (see \Cref{app:fill} for details).
+
+Still, there are $\mathcal{M}$-adhesive rewriting systems that are not strong enforcing.
+
+\begin{example}[Non-strong enforcing left-linear rewriting system]
+	\label{ex:diff2}
+	In light of \Cref{pr:church}, \Cref{ex:diff1} provides an example of
+	an independence pair that is not strong. This gives an example of a
+	left-linear rewriting system in a $\mathcal{M}$-adhesive category that is quite
+	pathological since $\mathcal{M}=\mathsf{I(\X)}$. However, this is expected, 
+	since all natural examples seem to belong to the well-behaved class mentioned above. 
+\end{example}
+
+\begin{remark}
+	By \Cref{pr:church} the existence of a strong independence pair
+	entails switchability, which in turn entails sequential
+	independence by construction. Strong enforcing rewriting systems are exactly
+	those rewriting systems in which these three notions coincide.
+\end{remark}
+
+Consistency with the theory of linear rewriting systems is ensured by the fact that all linear rewriting systems are strong enforcing (see \cref{prop:equi}).
+
+\subsection{Well-switching rewriting systems}
+\label{subsec:verytame}
+
+Even if we work in strong enforcing rewriting systems where sequential
+independence ensures switchability, when dealing with left-linear
+rules there is a further, possibly more serious issue, 
+namely that there can be more than one independence pair between
+the same derivations (cfr. \Cref{rem:uni}). This hinders the very idea of using
+sequential independence as a basis of a theory of concurrency for
+rewriting systems, since exchanges performed using different
+independence pairs may lead to derivations that are not abstraction
+equivalent, thus equating computations that should
+definitively be taken apart, as shown in the example below.
+
 \begin{example}
-	\todo{sequential independence che serva anche per es successivo}
+	Consider the derivation $\der{E}$ from Example~\ref{ex:seq-ind} (see Fig.~\ref{fi:derE}).
+	The last two steps are sequential independent, but one easily sees
+	that there are two distinct independence pairs, as the left-hand side
+	of $\rho_1$ can be mapped either to node $1$ or to node
+	$2$ in $D_1'$. Correspondingly, there
+	are two switches of $\der{E}$: one is the derivation $\der{D}$ in
+	Fig.~\ref{fi:derD} we started from, the other is the derivation
+	$\der{D}'$ in Fig.~\ref{fi:derD1}.
+
+	\begin{figure}
+%		\input{Figure/derD1.tex}
+		\caption{The derivation $\der{D}'$.}
+		\label{fi:derD1}
+	\end{figure}
+
+	As a consequence, $\der{D}$ and $\der{D}'$ would be switch
+	equivalent, but this is not acceptable when viewing equivalence
+	classes of derivations as concurrent computations: in $\der{D}$ the
+	first two steps are not sequential independent, while in $\der{D}'$
+	they are, intuitively because in $\der{D}$ rule $\rho_1$ uses the
+	node generated by $\rho_0$ (adding a self-loop to it), while in
+	$\der{D}'$ rule $\rho_1$ uses the node that was in the initial
+	graph. Also observe that the graphs $G_2$ and $G_2'$ produced after
+	two steps in $\der{D}$ and $\der{D'}$ are not isomorphic. From the
+	technical point of view, the property of being switch equivalent is
+	not closed by prefix, and this prevents deriving a sensible
+	concurrent semantics: In fact
+	$\der{D} = \dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ and
+	$\der{D}' = \dder{D}_0'\cdot \dder{D}_1' \cdot \dder{D}_2'$ are
+	switch equivalent, while if we consider the first two steps,
+	derivations $\dder{D}_0 \cdot \dder{D}_1$ and
+	$\dder{D}_0' \cdot \dder{D}_1'$ are not switch equivalent.
 \end{example}
 
- Let $(i_0, i_1)$ and $(i'_0, i'_1)$ be independence pairs for the direct derivations $\dder{D}$ and $\dder{D'}$. Notice that, by definition, we have
-	\begin{align*}f'\circ i_0&=h\\&=f'\circ i'_0
-	\end{align*}
-	On the other hand, 
-	$f'\colon D'\to H$ is  the pushout of $l'\colon K'\to L'$ and so it is in $\mathcal{M}$, implying $i_0=i'_0$.
-If, moreover, we suppose that the rule $\rho$ applied in $\dder{D}$ is linear, then $g\colon D\to H$ is in $\mathcal{M}$ too, hence, from the equation
-	\begin{align*}
-		g\circ i_1&=h \\&= g\circ i'_1
-	\end{align*}
-	we can deduce that $i'_0=i'_1$, too. Summing up, we have just proved the following.
-
-	\begin{proposition}\label{rem:weak}
-	Let $(\X, \R)$ be a linear DPO-rewriting system, then two direct derivations $\dder{D}$ and $\dder{D}'$ are weakly sequential independet if and only if they are sequential independent. 
-\end{proposition}
-
-We want to be able to exchange to switch the application of two rules used by two consecutive weakly independent direct derivations. This leads us to the following definition.
-
-\begin{definition}[Switch]
-  \label{de:switch}
- Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category and suppose that $\der{D}=\{\dder{D}_i\}_{i=0}^1$  is a derivation of length $2$ made by the following two weakly sequentially independent derivations $\dder{D}_0$, $\der{D}_1$, with independence pair $(i_0, i_1)$:
- 	\[\xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0} && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2}\]
-
- 	Take another derivation $\der{E}=\{\dder{E}_i\}_{i=0}^1$ with source $G_0$ and target $G_2$ and in which $\der{E}_0$, $\der{E}_1$ are
-\[\xymatrix{L_{\der{E},0} \ar[d]_{m_{\der{E},0}}& K_{\der{E},0} \ar[d]^{k_{\der{E},0}}\ar[l]_{l_{\der{E},0}} \ar[r]^{r_{\der{E},0}} & R_{\der{E},0} \ar[d]^{h_{\der{E},0}} & L_{\der{E},1} \ar[d]_{m_{\der{E},1}}& K_{\der{E},1} \ar[d]^{k_{\der{E},1}}\ar[l]_{l_{\der{E},1}} \ar[r]^{r_{\der{E},1}} & R_{\der{E},1} \ar[d]^{h_{\der{E},1}}\\G_{0} & \ar[l]^{f_{\der{E},0}} D_{\der{E},0} \ar[r]_{g_{\der{E},0}}& G_{\der{E},1} & G_{\der{E},1} & \ar[l]^{f_{\der{E},1}} D_{\der{E},1} \ar[r]_{g_{\der{E},1}}& G_{2}}\]
- 	We say that $\der{E}$ is a
- 	 	 \emph{switch} of $\der{D}$ along $(i_1, i_2)$ if
+Moreover, limiting sequential independence to the case in which the independence
+	pair is unique (as suggested in~\cite{baldan2017domains}) brings to the same problems.
+
+For these reasons we believe a theory of rewriting for
+left-linear rules in adhesive categories should be developed for
+systems where the uniqueness of the independence pair is ensured.
+
+\begin{definition}[Well-switching rewriting systems]
+	A left-linear rewriting system $(\X, \R)$ is \emph{well-switching} if it is strong enforcing and, for every derivation $\der{D}:=\{\dder{D}_{i}\}_{i=0}^1$, there is at most one independence pair between $\dder{D}_0$ and $\dder{D}_1$.
+\end{definition}
+
+Clearly, linear rewriting systems are well-switching (see Proposition~\ref{pr:weak}).
+Moreover, we next observe that various classes of rewriting systems,
+comprising all the ones used in modelling the applications to the
+encoding of process calculi or of bio and chemical systems mentioned
+in the introduction, are actually well-switching.
+
+\subsubsection{Some examples of well-switching rewriting systems}
+
+A first class consists of those rewriting systems over
+possibly hierarchical graphical structures obtained as algebras of
+suitable signatures where rules are constrained not to merge elements
+of top level sorts in the hierarchy (for graphs, nodes can be
+merged while edges cannot). The idea here is to consider graph
+structures as presheaves on categories in which there are objects that play 
+the role of \emph{roots}, i.e.~objects that are not the codomain of 
+any arrow besides the identity.
+
+\begin{definition}[Root-preserving graphical rewriting systems]
+	Let $\X$ be a category, an object $X\in \X$ is a \emph{root} if the only arrow with codomain $X$ is $\id{X}$.
+	The category $\gph{X}$ of \emph{$\X$-graphs} is the category
+	$\Set^{\X}$. A
+	\emph{root-preserving graphical rewriting system} is a left-linear
+	rewriting system $(\gph{X}, \R)$ such that for each rule
+	$(l\colon K\to L, r\colon K\to R)$ in $\R$ it holds
 	\begin{enumerate}
- 		\item $\dder{E}_0$ applies the rule used by $\dder{D}_1$ and $\dder{E}_1$ the one used by $\dder{D}_0$, so that
- 		\[(l_{\der{E},0}, r_{\der{E},0})=(l_1,r_1)  \qquad (l_{\der{E},1}, r_{\der{E},1})=(l_0,r_0)\]
- 		\item there exists an independence pair $(j_0, j_1)$ between $\dder{E}_0$ and $\dder{E}_1$ such that
- 		\[ m_0=f_{\der{E},0} \circ j_1 \qquad h_1=g_{\der{E},1} \circ j_0\]
- 		\item $m_{\der{E},0}= f_0\circ i_1$ and $h_{\der{E},1}= g_{1}\circ i_0$.
+		\item for every $X\in \X$ and $x\in L(X)$, there exists a root $Y$
+		and an arrow $f\colon Y\to X$ such that $x$ belongs to the image of
+		$L(f)\colon L(Y)\to L(X)$;
+		\item $r\colon K\to R$ is mono on the roots, i.e.~for every root $X\in \X$ the component $r_X:K(X)\to R(X)$ is injective.
 	\end{enumerate}
@@
 
-\begin{remark}\label{rem:fact}
-	Notice that, since $f_{\der{E}, 0}$ is in $\mathcal{M}$, there is at most one $j_1\colon L_0\to D_{\der{E},0}$ such that $m_0=f_{\der{E}, 0} \circ j_1$.
-Moreover, we already know that there is at most one $j_0\colon R_1\to D_{\der{E},1}$ such that $m_{\der{E},1}=f_{\der{E},1}\circ j_0$, therefore, the independence pair $(j_0,j_1)$ between the component of a switch is uniquely determined.
-\end{remark}
-
-Our first result about switches is their uniqueness up to abstraction equivalence.
-
-\begin{theorem}[Uniqueness of switches]\label{thm:switch_uni} Let $\der{D}=\{\dder{D}_i\}_{i=0}^1$
-
-\end{theorem}
-
-\begin{lemma}\label{lem:cose} Let $(\der{D}, \alpha, \omega)$ be a decorated derivation with $\der{D}=\{\dder{D}_i\}_{i=0}^1$,  and suppose that $(i_0, i_1)$ is an independence pair between $\dder{D}_0$  and $\der{D}_1$.
-If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a switch of $\der{D}$ along $(i_0, i_1)$, then the following hold true:
-	\begin{enumerate}
-			\item the pullback square below is an $\mathcal{M}$-pushout;
-			\[\xymatrix{P \ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\ D_0 \ar[r]_{g_1}& G_1}\]
-			\item there exist $q_0\colon P\to D_{\der{E},0}$, $q_1\colon P\to D_{\der{E},1}$ making the squares 
-			\[\xymatrix{}\]
-			commutative, moreover, they are all pushouts;
-			\[\xymatrix{}\]
- 		\item there exists an arrow $j_0\colon R_1\to D_{\der{E},1}$ such that 
- 		\[h_{\der{E},0}=f_{\der{E},1}\circ j_0 \qquad h_1=g_{\der{E},1} \circ j_0\]
-	\end{enumerate}
+For instance, the category $\cat{Graph}$ can be obtained
+by taking as $\X$ the category generated by $E \rightrightarrows V$. In this case $E$ is the only root, hence, condition $1$ asks that in the left-hand side of each rule
+there are no isolated nodes, while condition $2$ asks that the
+morphism $r: K \to R$ is injective on edges, i.e.~it can only merge nodes.
+
+\begin{lemma}{lemma}{lemVTame}
+	\label{bono}
+	All root-preserving graphical rewriting systems are well-switching.
 \end{lemma}
-\begin{proof}
-	Before starting with the proof of our claims, it is worth noticing that the definition of switchin gives us the following diagram:
-			\[\xymatrix@R=28pt{&&R_0 \ar@/_1.15cm/[ddrr]_(.8){i_0}|(.68)\hole \ar[dr]^{h_0}&& L_1\ar@/^1.15cm/[ddll]^(.8){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar[ur]^{r_0}&& G_1 && K_1 \ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.94cm/[ddrr]_(.8){j_1}|(.31)\hole \ar[dr]^(.35){m_0}|(.6)\hole && D_0 \ar[dl]^{f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]_{g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar[dl]^(.35){h_1}|(.6)\hole\\&G_0 &&&&G_2\\L_1 \ar@/^.94cm/[uurr]^(.8){i_1} \ar[ur]_(.35){m_{\der{E},0}}|(.61)\hole&&D_{\der{E},0} \ar[ul]_{f_{\der{E},0}}\ar[dr]^{g_{\der{E},0}} &&D_{\der{E},1}\ar[ur]^{g_{\der{E},1}} \ar[dl]|(.5)\hole^(.7){f_{\der{E},1}} && R_0  \ar@/_.94cm/[uull]_(.8){j_1} \ar[ul]^{h_{\der{E},1}}\\&K_1 \ar[ur]_{k_{\der{E},0}} \ar[dr]_{r_1} \ar[ul]^{l_1}&&G_{\der{E},1}&& K_0 \ar[ur]_{r_0} \ar[ul]^{k_{\der{E},1}} \ar[dl]^{l_0} \\&& R_1 \ar[ur]_{h_{\der{E},0}}&& L_0 \ar[ul]^{m_{\der{E},1}} \ar@/_1.15cm/[uull]_(.6){j_1} }\]
-
-			Let us turn to our statements.
-	\begin{enumerate}
-		\item We start noticing that 
-		\begin{align*}
-			g_0\circ i_1\circ l_1&=m_1\circ l_1\\&=k_1\circ f_1
-		\end{align*}
-		Thus there exists the dotted $u\colon K_1\to P$ in the diagram
-		\[\]
-		The thesis now follows applyin \Cref{lem:popb} to
-
-		\item 
-		\item  We already have an arrow $j_1\colon L_0\to D_{\der{E},0}$ such that
-		\[m_{\der{E},1}=g_{\der{E},0}\circ j_1\]
-		Therefore the thesis follows at once from the previous point.
-
-	\item
-
-		\item \qedhere 
-	\end{enumerate}
-\end{proof}
-
-\todo{ $\dder{E}_0$ and $\dder{E}_1$ are weak sequentially independent;
-
-if $\der{E}'=\{\dder{E}'_i\}_{i=0}^1$ is another switching of $\der{D}$ along $(i_0, i_1)$, then there exist arrows.... such that the following diagram commutes:
-}
-In particular [...]
-\begin{definition}\todo{switch}
-	contenuto...
-\end{definition}
-\begin{remark}
-Canonico
-\end{remark}
-\begin{corollary}\todo{inversione}
-\end{corollary}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{lemma}
-	\todo{permutazione}
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{lemma}\label{lem:swfill}
-\todo{equi}
-\end{lemma}
-\begin{remark}
-	\todo{tobias}
-\end{remark}
-\begin{remark}
-	contenuto...
-\end{remark}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-When working with linear rewriting systems, (weakly) sequential independent direct derivations can be switched, producing two new (weakly) sequential independent direct derivations between the same objects \cite[Thm.~$7.7$]{lack2005adhesive} .
-This is no more the case if the rules are only left-linear, as shown by the next example.
-
-\begin{example}\label{ex:difficile}
-	\todo{pensare ad un esempio in cui l'indipendenza non basta }
+
+Another interesting class of well-switching rewriting systems is given by e-graphs.
+
+\begin{example}[E-graphs]
+	Consider the category $\cat{EGraphs}$, where objects are (directed)
+	graphs endowed with an equivalence over nodes, and arrows are graph
+	morphisms that preserve the equivalence, as considered
+	in~\cite{BaldanGM06}, closely related to e-graphs~\cite{WNW:egg}. 
+	Formally, $\cat{EGraphs}$ can be seen as the
+	subcategory of the presheaf
+	$[E \rightrightarrows V \to Q, \cat{Set}]$ where objects are
+	constrained to have the component $V \to Q$ surjective.
+
+	Explicitly, an
+	e-graph $G$ is a triple $\langle s_G, t_G, q_G \rangle$ where
+	$s_G, t_G: E_G \rightrightarrows V_G$ provides the graphical
+	structure, while the surjective function $q_G : V_G \to Q_G$ maps
+	each node to the corresponding equivalence class. 
+	Notice that the inclusion functor into  $[E \rightrightarrows V \to Q, \cat{Set}]$ 
+	creates pullbacks and pushouts \cite{mac2013categories}, so that they are computed component-wise.
+
+	A morphism in $\cat{EGraph}$ is mono if the components over $E$
+	and $V$ are mono, i.e.~if it is mono as a morphism in
+	$\cat{Graph}$. It is regular mono if also the component on
+	$Q$ is mono, i.e.~if it reflects equivalence classes besides
+	preserving them.
+This characterisation of regular monos and the fact that pullbacks and pushouts are computed component-wise allows us to prove quasi-adhesivity of $\cat{EGraphs}$ at once.
+Moreover, one can deduce that every rewriting system $(\X, \R)$ that is left-linear with respect to $\reg(\cat{EGraphs})$ is strong enforcing: this is done exploiting again the inclusion functor into $[E \rightrightarrows V \to Q, \cat{Set}]$.
+
+	Left-linear rewriting systems with respect to $\reg(\cat{EGraphs})$ are well-switching. They have been used in~\cite{BaldanGM06} for the graphical implementation of nominal calculi, where,
+	differently from~\cite{Gad07}, as a result of name passing the received name is not merged with a local one, but put in the same equivalence class, better tracing the causal dependencies among reductions.
 \end{example}
 
-\subsection{Sequentially independent and switchable derivations}
-\todo{A VERY NICE INTRO}
-
-\begin{definition}  Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Let also $\dder{D}\colon G\Mapsto H$ and $\dder{D'}\colon H\Mapsto T$ be the two direct derivations depicted below.
-
-	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
-
-	An \emph{independence pair} between $\dder{D}$ and $\dder{D'}$, is a pair of  arrows $i_1\colon R\to D'$ and $i_2\colon L'\to D$ such that the following diagram commutes.
-
-	\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
-	We will say that $\dder{D}$ and $\dder{D'}$ are \emph{weakly sequentially independent} if an independence pair exists.
-If such independence pair is unique we will say that $\dder{D}$ and $\dder{D'}$ are \emph{sequentially independent}.
-\end{definition}
-
-\begin{example}
-	\todo{sequential independence}
-\end{example}
-\begin{example}
-	\todo{sequential independence che serva anche per es successivo}
-\end{example}
-
-\begin{remark}\label{rem:weak} Let $(i_1, i_2)$ and $(j_1, j_2)$ be independence pairs for the direct derivations $\dder{D}$ and $\dder{D'}$. Notice that, by definition, we have
-	\begin{align*}f'\circ i_1&=h\\&=f'\circ j_1
-	\end{align*}
-	On the other hand, 
-	$f'\colon D'\to H$ is  the pushout of $l'\colon K'\to L'$ and so it is in $\mathcal{M}$, implying $j_1=i_1$.
-If, moreover, we suppose that the rule $\rho$ applied in $\dder{D}$ is linear, then $g\colon D\to H$ is in $\mathcal{M}$ too, hence, from the equation
-	\begin{align*}
-		g\circ i_2&=h \\&= g\circ j_2
-	\end{align*}
-	we can deduce that $i_2=j_2$, too.
-
-	Summing up, if $(\X, \R)$ is a linear DPO-rewriting system, then sequential independence and weak sequential independence coincide. 
-\end{remark}
-
-We want to be able to exchange to switch the application of two rules used by two consecutive weakly independent direct derivations
-\begin{definition}
-	contenuto...
-\end{definition}
-
-\begin{proposition}
-	\todo{equi}
-\end{proposition}
-\begin{remark}
-	contenuto...
-\end{remark}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-When working with linear rewriting systems, (weakly) sequential independent direct derivations can be switched, producing two new (weakly) sequential independent direct derivations between the same objects \cite[Thm.~$7.7$]{lack2005adhesive} .
-This is no more the case if the rules are only left-linear, as shown by the next example.
-
-\begin{example}\label{ex:difficile}
-	\todo{pensare ad un esempio in cui l'indipendenza non basta }
-\end{example}
-
-To fix this problem, we adapt the notion of \emph{canonical filler} from \cite{heindel2009category}.
-
-\begin{definition}\label{def:filler}
-Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ $\mathcal{M}$-adhesive. Let also $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$ be the two derivations depicted below.
-\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
-Since $f'$ is in $\mathcal{M}$, we can moreover consider a pullback square
-\[\xymatrix{P \ar[r]^{p} \ar[d]_{p'}& D\ar[d]^{g} \\ D' \ar[r]_{f'} & H}\]
-
-A \emph{filler} between $\dder{D}$ and $\dder{D}'$ is  given by a pair of arrows $u\colon K\to P$ and $u'\colon K'\to P$ satisfying the following conditions
-\begin{enumerate}
-	\item $p\circ u = k$, $p'\circ u' = k'$ and there exists a pushout square
-\[\xymatrix{K' \ar[r]^{r'} \ar[d]_{u'}& R'\ar@{.>}[d]^{j'} \\ P \ar@{.>}[r]_{q'} & Q'}\]
-	\item  there exist arrows $i_1\colon R\to D'$, $i_2\colon L'\to D$ satisfying $f'\circ i_1=h$, $g\circ i_2=n'$ and such that the following squares are pushouts
-\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar@{.>}[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar@{.>}[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
-\end{enumerate}
-\end{definition}
-
-\begin{remark}\label{rem:deco} Let $\dder{D}$ and $\dder{D'}$ be two switchable direct derivations. Then the existence of a filler allows us to build the solid part of the diagram below.
-	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole  \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@{.>}@/_.8cm/[ddrr]_{j}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j'}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar@{.>}[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar@{.>}[ul]_{s} &&Q'\ar@{.>}[ur]^{t}}\]
-
-	Let us complete this diagram defining the dotted arrows. We can start noticing that, since $l\in \mathcal{M}$, there exists a pushout square 
-	\[\xymatrix{K \ar[r]^{l} \ar[d]_{u}& L\ar[d]^{j} \\ P \ar[r]_{q} & Q}\]
-	Moreover, the existence of the wanted $s\colon Q\to G$ and $t\colon Q'\to T$ follows from the following equalities
-	\[\begin{split}
-		f\circ p \circ u &= f\circ k \\&= n\circ l
-	\end{split} \qquad \begin{split}
-		g'\circ p'\circ u' &= g'\circ k'\\&=h'\circ r'
-	\end{split}\]
-
-	We can prove some other properties of the arrows appearing in the diagram above.
-The three rectangles below are pushouts and their left halves are pushouts too.
-Therefore, by \Cref{lem:po1}, also their right halves are pushouts.
-	\[\xymatrix{K \ar@/^.4cm/[rr]^{u}\ar[d]_{r}\ar[r]_{u} &P\ar[d]^{p'} \ar[r]_{p} & D \ar[d]^{g}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{l'}\ar[r]_{u'} &P\ar[d]^{p} \ar[r]_{p'} & D' \ar[d]^{f'}\\  R \ar@/_.4cm/[rr]_{h} \ar[r]^{i_1}&D' \ar[r]^{f'} & H&L' \ar@/_.4cm/[rr]_{n'} \ar[r]^{i_2}&D \ar[r]^{g} & H}\]
-	\[ \xymatrix{K \ar@/^.4cm/[rr]^{k}\ar[d]_{l}\ar[r]_{u} &P\ar[d]^{q} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{r'}\ar[r]_{u'} &P\ar[d]^{q'} \ar[r]_{p'} & D' \ar[d]^{g'}\\ L \ar@/_.4cm/[rr]_{n} \ar[r]^{j}&Q \ar[r]^{s} & G&R' \ar@/_.4cm/[rr]_{h'} \ar[r]^{j'}&Q' \ar[r]^{t} & T}\]
-
-	Notice, moreover, that $p, q$ are the pushouts of $l'$ and $l$, respectively, thus they  are elements of $\mathcal{M}$. By \Cref{prop:pbpoad} the squares
-	\[\xymatrix{P\ar[r]^{p} \ar[d]_{p'} & D \ar[d]^{g}& P \ar[r]^{p} \ar[d]_{q} &D\ar[d]^{f}\\ D' \ar[r]_{f'} & H & Q \ar[r]_{s}& G}\]
-	are pullbacks too.
-\end{remark}
-
-Notice that if there is a filler between  $\dder{D}$ and $\dder{D}'$ are switchable, then they are weakly sequentially independent: indeed, if a filler between them exists, then $(i_1, i_2)$ is an independence pair.
-On the other hand, \Cref{ex:difficile} shows that not every independence pair arises in this way.
-
-\begin{definition}
-  \label{de:good-switchable}
-  Let $\dder{D}\colon H\Mapsto H$, $\dder{D}'\colon H\Mapsto T$ be two
-  direct derivations in a left-linear DPO-rewriting system $(\X,
-  \R)$. An independence pair $(i_1, i_2)$ between $\dder{D}$ and
-  $\dder{D}'$ is \emph{good} if there exists a filler $(u,u')$ between
-  them such that the squares below are
-  pushouts.\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K'
-      \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P
-      \ar[r]_{p} & D}\]
-
-We will say that $\dder{D}$ and $\dder{D}'$ are \emph{switchable} if a good independence pair between them exists.
-If such a pair is unique, we will say that $\dder{D}$ and $\dder{D}'$ are \emph{uniquely switchable}.
-We will use the notation $\dder{D}\updownarrow \dder{D'}$ to mean that $\dder{D}$ and $\dder{D}'$ are switchable, while $\dder{D}\updownarrow_!
-\dder{D'}$ will denote that they are uniquely so.
-
-If every independence pair is good we will say that $(\X, \R)$ is \emph{tame}.
-\end{definition}
-
-\begin{remark}\label{rem:unic} Given a good independence pair $(i_1, i_2)$ between $\dder{D}$ and $\dder{D}'$, there is a unique filler  such that $(u,u')$ such that 
-	\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
-	are pushouts. Indeed, for every other filler $(v,v')$, it must be that
-	\[\begin{split}
-		p\circ u &=k \\&= p\circ v
-	\end{split}\qquad \begin{split}
-	p\circ u' &= i_2\circ l' \\&= p\circ v'
-	\end{split}\]
-	Since the arrow $p\colon P\to D$, which is the pullback of $f'$, is in $\mathcal{M}$ we conclude that $(u,u')=(v,v')$.
-\end{remark}
-
-\begin{remark}
-  Clearly in a tame left-linear DPO-rewriting system two direct derivations are sequentially independent if and only if they are unquely switchable.
-\end{remark}
-
-A source of tame left-linear DPO-rewriting systems is given by the linear ones, as shown by the following proposition.
-
-\begin{proposition}\label{prop:equi}Every linear DPO-rewriting system $(\X, \R)$ is tame.
- \end{proposition}
-\begin{proof} Suppose that $\X$ is $\mathcal{M}$-adhesive and let $(i_1, i_2)$ be an independence pair between $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$. We have a diagram
-	\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
-Pulling back $g$ along $f'$, we get another diagram 
-	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@{.>}@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@{.>}@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} && D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar[dl]^{h'}\\&G &&P\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T}\]
-Now, if we compute we get
-\[\begin{split}
-	f'\circ i_1\circ r &= h\circ r \\&= g\circ k
-\end{split}\qquad \begin{split}
-g\circ i_2\circ l' &= n'\circ l'\\&=f'\circ k'
-\end{split}\]
-Therefore the two dotted arrows $u\colon K\to P$ and $u'\colon K'\to P$ exist. We have to show that they satisfy the two conditions in the definition of a filler. 
-\begin{enumerate}
-	\item  By construction $p\circ u = k$ and $p'\circ u'=k'$. Since $(\X, \R)$ is linear, then $r'\colon K'\to R'$ belongs to $\mathcal{M}$, thus it admits a pushout along $u'\colon K'\to P$, as wanted.
-	\item Take the following two rectangles
-\[\xymatrix{K \ar@/^.4cm/[rr]^{u}\ar[d]_{r}\ar[r]_{u} &P\ar[d]^{p'} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{l'}\ar[r]_{u'} &P\ar[d]^{p} \ar[r]_{p'} & D' \ar[d]^{f'}\\  R \ar@/_.4cm/[rr]_{h} \ar[r]^{i_1}&D' \ar[r]^{f'} & H&L' \ar@/_.4cm/[rr]_{n'} \ar[r]^{i_2}&D \ar[r]^{g} & H}\]
-	By hypothesis $r$ and $l'$ are in $\mathcal{M}$, thus $f'$ and $g$ belong to it too. The first point of \Cref{lem:popb}  yields the thesis. \qedhere 
-\end{enumerate}
-\end{proof}
-
-\begin{remark} \cite{baldan2011adhesivity} identifies a large class of (quasi)adhesive categories with the property that every left linear DPO-rewriting system on them is tame.
-We adapt these results to our context in \Cref{app:fill}.
-\end{remark}
-\begin{definition}[Very tameneness]
-	\todo{very tame}
-\end{definition}
-
-\begin{remark}
-	\todo{tutto coincide con tutto}
-\end{remark}
-
-We are now going to justify the choice of the name for the relation $\updownarrow$, showing that two switchable direct derivations $\dder{D}$ and $\dder{D'}$ can be actually switched.
-
-Let $(i_1, i_2)$ be a good independence pair and consider the following diagram: the solid part exists by the definition of a filler, while the two new dotted arrows $v\colon Q\to J$ and $v'\colon Q'\to J$ are obtained  as the pushout of $q\colon P\to Q$, which is in $\mathcal{M}$ by \Cref{rem:deco}, along $q'\colon P\to Q'$.
-	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@/_.8cm/[ddrr]_{j}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j'}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar[ul]_{s}\ar@{.>}[dr]_{v} &&Q'\ar[ur]^{t} \ar@{.>}[dl]^{v'}\\&&&J}\]
-
-	Since, by \Cref{rem:deco}, all the curved rectangles are pushouts, as well as the bottom square, we can state the following definition.
-\begin{definition}\label{def:switch}
-	Let $(\X,R)$ be a left-linear DPO-rewriting system and suppose that $\X$ is $\mathcal{M}$-adhesive.
-Given a good independence pair $(i_1, i_2)$ between $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$, if $(u,u')$ is the associate filler, we define other two direct derivations $S_{i_1,i_2}(\dder{D}')\colon G\Mapsto J$ and $S_{i_1,i_2}(\dder{D})\colon J\Mapsto T$ as follows:
-		\[\xymatrix{L' \ar[d]_{f\circ i_2}& \ar[l]_{l'}K'\ar[d]_{q\circ u'} \ar[r]^{r'} & R' \ar[d]_{v'\circ j'} & L \ar[d]_{v\circ j} & \ar[l]_{l}K \ar[d]^{q'\circ u}\ar[r]^{r}& R \ar[d]^{g'\circ i_1}\\
-		G &\ar[l]^{s} Q \ar[r]_{v}& J&J & \ar[l]^{v'}Q' \ar[r]_{t} & T}\]
-	The \emph{switching} $\sder{D}{D'}$ of $\dder{D}$ and $\dder{D'}$ is the derivation $S_{i_1,i_2}(\dder{D}')\cdot S_{i_1,i_2}(\dder{D})$.
-\end{definition}
-
-\begin{remark}\label{rem:indip}Notice that $(j', j)$ is an independence pair for $S_{i_1,i_2}(\dder{D}')$ and $S_{i_1,i_2}(\dder{D})$.
-This is witnessed by the following diagram, commutative by construction.
-	\[\xymatrix@C=15pt{L' \ar[d]_{f\circ i_2}&& K' \ar[d]_{q\circ u'}\ar[ll]_{l'} \ar[r]^{r'} & R' \ar@/^.35cm/[drrr]_(.4){j'}|(.285)\hole \ar[dr]|(.28)\hole_{v'\circ j'} && L \ar@/_.35cm/[dlll]^(.4){j} \ar[dl]|(.28)\hole^{v\circ j}& K \ar[d]^{q'\circ u}\ar[l]_{l} \ar[rr]^{r} && R \ar[d]^{g'\circ i_1}\\G && \ar[ll]^{s} Q \ar[rr]_{v}&& J  && \ar[ll]^{v'} Q' \ar[rr]_{t}&& T}\]
-\end{remark}
-
-\begin{theorem}[Local Church-Rosser Theorem]\label{prop:fil}Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Then every filler between two direct derivations $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$ is a filler also for $S_{u,u'}(\dder{D'})\colon G\Mapsto J$ and $S_{u,u'}(\dder{D})\colon J\Mapsto H$.
-In particular, if $\dder{D}\updownarrow \dder{D}'$, then $S_{u,u'}(\dder{D}')\updownarrow S_{u,u'}(\dder{D})$.
-\end{theorem}
-\begin{proof}By definition of filler, we have two pushout square
-		\[\xymatrix{K \ar[r]^{l} \ar[d]_{u}& L \ar[d]^{j} & K' \ar[r]^{r'} \ar[d]_{u'} & R' \ar[d]^{j'}\\ P \ar[r]_q & Q & P \ar[r]_{q'} & Q'}\]
-		In particular, $q$ is an arrow of $\mathcal{M}$, therefore, by \Cref{prop:pbpoad}, the square below is a pullback.
-		\[\xymatrix{P \ar[r]^{q} \ar[d]_{q'}& Q\ar[d]^{v}\\ Q' \ar[r]_{v'} & J}\]
-		To prove our claim, it is now enough to show that $(u',u)$ is a filler between $S_{u,u'}(\dder{D}')$ and $S_{u, u'}(\dder{D})$.
-		\begin{enumerate}
-			\item As for the first  point of \Cref{def:filler}, the only non obvious part is the existence of a pushout of $u$ along $r$.
-But, since $(u,u')$ is a filler between $\dder{D}$ and $\dder{D'}$, we know that such a pushout exists: it is enough to take the square
-			\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} \\P \ar[r]_{p'}& D'}\]
-			\item For the second point, notice that the arrows $j$ and $j'$ fit in the squares
-	\[\xymatrix{K' \ar[r]^{r'} \ar[d]_{u'}& R' \ar[d]^{j'} &K \ar[r]^{l} \ar[d]_{u}& L\ar[d]^{j} \\P \ar[r]_{q}& Q& P \ar[r]_{q'} & Q'}\] 
-		\end{enumerate}
-
-By \Cref{rem:indip} we know that $(j,j')$ is an independence pair. The results above now implies that $(j,j')$ is good.
-\end{proof}
-
-The previous remark allow us to further switch the direct derivation $S_{i_1,i_2}(\dder{D})$ and $S_{i_2,i_2}(\dder{D}')$.
-The following lemma guarantees us that, in this way, we get back a derivation which is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
-
-\todo{introdurre decorazione}
-
-\begin{lemma}\label{lem:rev}
-	Let $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system $(\X, \R)$ and let $(i_1,i_2)$ be a good independence pair between them.
-Then $S_{j',j}(S_{i_1,i_2}(\dder{D}, \dder{D'}))$ is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
-\end{lemma}
-\begin{proof}Let $(u,u')$ be the filler associated to $(i_1, i_2)$.
-By \Cref{prop:fil}, $(u', u)$ is a filler between $S_{i_1,i_2}(\dder{D}')$ and $S_{i_1,i_2}(\dder{D})$.
-Thus we have a diagram as the one below.
-		\[\xymatrix{&&R' \ar@/_1cm/[ddrr]_(.35){j'}|(.7)\hole \ar[dr]^{v'\circ j'}&& L \ar@/^1cm/[ddll]^(.35){j}  \ar[dl]_{v\circ j}\\&K'\ar[dr]^{q\circ u'}\ar[dl]_{l'} \ar@/_.8cm/[ddrr]^(.65){u'}\ar[ur]^{r'}&& J && K \ar@/^.8cm/[ddll]_(.65){u}\ar[dl]_{q'\circ u}\ar[lu]_{l} \ar[dr]^{r}\\L' \ar[dr]^{f\circ i_2} \ar@/_.8cm/[ddrr]_{c_2}&& Q \ar[dl]|(.42)\hole_(.64){s}\ar[ur]|(.48)\hole^(.7){v}&&Q' \ar[dr]|(.42)\hole_(.65){t} \ar[ul]|(.48)\hole_(.7){v'}&&R\ar@/^.8cm/[ddll]^{c_1}\ar[dl]_{g'\circ i_1}\\&G &&P\ar[dr]^{e} \ar[dl]_{e'}\ar[ur]^(.4){q'}\ar[ul]_(.4){q}&&T\\&&E' \ar[ul]_{a}\ar[dr]_{w'} &&E\ar[ur]^{b} \ar[dl]^{w}\\&&&F}\]
-
-	Now, to ease the notation, let $S_{j',j}(S_{i_1,i_2}(\dder{D}, \dder{D'}))$ be $\dder{E}_0\cdot \dder{E}_1$, then $\dder{E}_0$ and $\dder{E}_1$ are the direct derivations given by the diagrams
-	\[\xymatrix{L \ar[d]_{s\circ j}& K\ar[l]_{l} \ar[r]^{r} \ar[d]_{e'\circ u} & R \ar[d]_{w\circ c_1} & L' \ar[d]^{w'\circ c_2}& K' \ar[d]^{e\circ u'} \ar[r]^{r'} \ar[l]_{l'}& R' \ar[d]^{t\circ j'}\\G & E' \ar[l]^{a}  \ar[r]_{w'}& F & F & E \ar[l]^{w} \ar[r]_{b} & R}\]
-
-	Notice, moreover, that, since the squares
-	\[\xymatrix{K' \ar[d]_{u'} \ar[r]^{l'}& L' \ar[d]^{c_2} & K \ar[r]^{r}\ar[d]_{u} & R \ar[d]^{c_1}\\ P \ar[r]_{e'} & E' & P\ar[r]_e & E}\]
-	are pushouts, we have isomorphisms  $\phi'\colon D\to E'$, $\phi\colon D'\to E$ making the following diagrams commutative.
-	\[\xymatrix{K' \ar[d]_{u'} \ar[r]^{l'}& L'\ar[d]^{i_2}  \ar@/^.2cm/[dr]^{c_2} & &K \ar[r]^{r}\ar[d]_{u} & R \ar[d]^{i_1} \ar@/^.2cm/[dr]^{c_1}\\ P \ar@/_.4cm/[rr]_{e'}\ar[r]^{p} & D\ar@{.>}[r]^{\phi'} &E'& P\ar@/_.4cm/[rr]_{e}\ar[r]^{p'} & D'\ar@{.>}[r]^{\phi}& E}\]
-	In particular, we have
-	\[\begin{split}
-		a\circ \phi' \circ i_2&=a \circ c_2\\&=f\circ i_2\\&
-	\end{split}\quad \begin{split}
-	a\circ \phi' \circ p'&=a \circ e'\\&=s\circ q\\&=f\circ p
-	\end{split}\quad \begin{split}
-	b\circ \phi \circ i_1&=b \circ c_1\\&=g'\circ i_1\\&
-	\end{split}\quad \begin{split}
-	b\circ \phi \circ p&=b \circ e\\&=t\circ q'\\&=g'\circ p'
-	\end{split} \]
-	and this shows that 
-	\[a\circ \phi'=f \qquad b\circ \phi = g'\]
-	Now, since $\phi'$ is an isomorphism and by \Cref{prop:pbpoad}, the two halves of the rectangle
-	\[\xymatrix{K\ar[r]^{\id{K}} \ar[d]_{(\phi')^{-1} \circ e' \circ u}&K\ar[d]_{e'\circ u} \ar[r]^{l} & L \ar[d]^{s\circ j} \\D\ar[r]_{\phi'} & E' \ar[r]_{a}&G}\]
-	are pullbacks.
-Thus the whole diagram is a pullback.
-But, by construction $s\circ j =n$ and we have already proved that $a\circ \phi'=f$.
-We then conclude that ther exists an isomorphism $\zeta\colon K\to K$ which makes the diagram below commutative
-	\[\xymatrix{K \ar@{.>}[r]_{\zeta}\ar@/^.4cm/[rr]^{l}  \ar@/_.5cm/[dr]_{(\phi')^{-1} \circ e' \circ u}& K \ar[r]_{l} \ar[d]_{n} & L \ar[d]^{n} \\ & D \ar[r]_{f} & G}\]
-	The commutativity of the upper triangle entails $l\circ \zeta=l$. Since $l$ is an element of $\mathcal{M}$  we can deduce that. $\zeta=\id{K}$. From this, we conclude that
-	\[e'\circ u = \phi' \circ k\]
-
-	As a next step, notice the existence of $\phi$ and $\phi'$, together with \Cref{rem:deco}, entails  the existence of a third isomorphism $\psi\colon H\to F$ fitting in the diagram below.
-	\[\xymatrix{P  \ar[d]^{p'}\ar@/_.4cm/[dd]_{e}\ar@/^.4cm/[rr]^{e'} \ar[r]_{p} & D \ar[d]^{g} \ar[r]_{\phi'} & E'\ar[d]^{w'}\\D' \ar[d]^{\phi} \ar[r]_{f'} & H\ar@{.>}[r]^{\psi} & F \\E \ar@/_.4cm/[urr]_{w}}\]
-Now, if we compute, we get
-\begin{align*}
-	\psi^{-1}\circ w\circ c_1&=f'\circ \phi^{-1}\circ c_1\\&=f'\circ i_1\\&=h
-\end{align*}
-	Summing up, we have just build the diagram below.	
-	\[\xymatrix@C=40pt@R=10pt{ &&&R\ar[dddr]^{w\circ c_1} \ar[dddl]_{h}|(.67)\hole\\&&K \ar[dl]_{l} \ar[ur]^{r}\ar[dddr]^{e'\circ u} \ar[dddl]_{k}|(.67)\hole\\&L\ar[dddr]^(.4){s\circ j} \ar[dddl]_(.4){n}\\&&H \ar[rr]^{\psi} && F\\ & D \ar[ur]_(.7){g} \ar[rr]^{\phi'} \ar[dl]_{f}&& E' \ar[ur]_{w'}\ar[dl]^{a}\\ G \ar[rr]_{\id{G}} && G}\]
-
-Next, we already know that
-\[t\circ j'= h' \quad w\circ \phi = \psi \circ f' \quad b\circ \phi = g'\]
-If we compute further, we also get
-\[\begin{split}
-	\psi^{-1}\circ w'\circ c_2 &= g\circ (\phi')^{-1}\circ c_2\\&=g\circ i_2\\&=n'
-\end{split}\qquad \begin{split}
-\phi^{-1}\circ e \circ u'&=p'\circ u'\\&= k'\\&
-\end{split}\]
-These equations allow us to conclude that the following diagram commutes.
-	\[\xymatrix@C=40pt@R=10pt{ &&&R'\ar[dddr]^{t\circ j'} \ar[dddl]_{h'}|(.67)\hole\\&&K' \ar[dl]_{l'} \ar[ur]^{r}\ar[dddr]^{e\circ u'} \ar[dddl]_{k}|(.67)\hole\\&L'\ar[dddr]^(.4){w'\circ c_2} \ar[dddl]_(.4){n'}\\&&T \ar[rr]^{\id{T}} && T\\ & D' \ar[ur]_(.7){g'} \ar[rr]^{\phi} \ar[dl]_{f'}&& E \ar[ur]_{b}\ar[dl]^{w}\\ H \ar[rr]_{\psi} && F}\]
-
-Putting together the two diagrams above we get the thesis. \qedhere 
-\end{proof}
-
-Our next step is to relate derivations which are equal ``up to switching''.
-
-\begin{definition}
-  \label{de:switchable}
-  Let $(\X, \R)$ be a left-linear DPO-rewriting system. Given two
-  direct derivations $\dder{D}\colon G\Mapsto H$ and
-  $\dder{D}'\colon H\Mapsto T$, we say that $\dder{D}$ and $\dder{D}'$
-  are \emph{properly switchable} if $\dder{D}\updownarrow_! \dder{D'}$
-  and $S_{i_1,i_2}(\dder{D}')\updownarrow_!S_{i_1,i_2}(\dder{D})$,
-  where $(i_2,i_2)$ is a good independence pair betwwen $\dder{D}$ and
-  $\dder{D}'$. In such a case, we will write
-  $\dder{D}\Updownarrow\dder{D}'$.
-
-Take two derivations $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_{i}\}_{i=0}^n$ with the same length and between the same $G_0$ and $G_n$.
-We say that $\der{D}'$ is \emph{obtained by a proper switch from $\der{D}$} if there exists an index $j < n$ such that
-	\begin{enumerate}
-\item for every $i\notin \{j, j+1\} $, $\dder{D}_i=\dder{D}'_i$;
-\item $\dder{D}_j \Updownarrow \dder{D}_{j+1}$;		
-\item $\dder{D}'_j\cdot \dder{D}'_{j+1} = S_{i_1,i_2}(\dder{D}, \dder{D}')$.
-	\end{enumerate}
-	In such a case, we will write $\der{D}\rightsquigarrow_j \der{D}'$ to denote that $\der{D}'$ is obtained by a proper switch between $\dder{D}_j$ and $\dder{D}_{j+1}$.
-
-	We will say that $\der{D}$ is \emph{switch equivalent} to $\der{D}'$, if there exists a sequence, $\{\der{D}_i\}_{i=0}^n$ of derivations such that
-	\begin{enumerate}
-		\item $\der{D}_0=\der{D}$ and $\der{D}_n=\der{D}'$;
-		\item for every $i< n$, $\der{D}_{i+1}$ is obtained by a proper switch from $\der{D}_i$.
-	\end{enumerate}
-
-	We will write $\der{D} \equiv^s \der{D}'$ to denote that $\der{D}$ is switch equivalent to $\der{D}'$.
-\end{definition}
-
-\begin{example}
-	\todo{il punto due sopra è necessario}
-\end{example}
-
-We can now prove some properties of switch equivalence.
-\begin{lemma}\todo{Def. 3 della bozza di Andrea }Let $(\X, \R)$ be a left-linear DPO-rewriting system. Then the following hold true: 
-	\begin{enumerate}
-		\item 
-		\item 
-		\item 
-		\item 
-	\end{enumerate}
-\end{lemma}
-\begin{proof}\begin{enumerate}
-		\item 
-		\item 
-		\item 
-		\item \qedhere 
-	\end{enumerate}
-\end{proof}
-
-\begin{example}\todo{esempio sul perché weakly independence non è invertibile}
-\end{example}
-
-\begin{lemma}\label{lem:consperm} Let $(\X, \R)$ be a left-linear DPO-rewriting system $(\X, \R)$. Then the following hold true
-	\begin{enumerate}
-		\item If $\dder{D}$ and $\dder{D'}$ are two direct derivations such that $\dder{D}\updownarrow \dder{D'}$, then for every filler $(u,u')$ between them, the function
-		\[\tau\colon 2\to2 \qquad x \mapsto \begin{cases}
-			1 & x=0\\
-			0 & x=1
-		\end{cases}\]
-		defines a consistent permutation between $\dder{D}\cdot \dder{D}'$ and $\sder{D}{D'}$;
-		\item if $\der{D}$ and $\der{D}'$ are two switch equivalent derivation, then there exists a consistent permutation between them.
-	\end{enumerate}
-\end{lemma}
-\begin{proof}
-	\begin{enumerate}
-		\item 
-		\item \qedhere 
-	\end{enumerate}
-\end{proof}
- This, together with ???
-\begin{corollary}
-	\todo{unicità}
-\end{corollary}
-
-\begin{example}\label{ex:contro}\todo{permutazione consistente non implica scambiabilità}
-\end{example}
-
 \subsubsection{Graphical rewriting systems}\label{subsubsec:graphical}
@@
 \todo{ci sono un sacco di sistemi very tame}
-\subsection{Switch equivalence}
+\subsection{Canonical switching sequences}
 \todo{intro}
@@
 
-\subsection{Concatenable traces}
+\subsection{Switch equivalence and consistent permutations}
+
+\section{Concatenable traces}
+
 \begin{lemma}

### 2024-11-22 full_version/permutations.tex
minori

@@
-\chapter{DPO-rewriting and derivations}
+\chapter{Left-linear DPO-rewriting systems}
 
@@
 We will represent a rule $\rho$ as a span
-	\[\xymatrix{L & K\ar[l]_{l} \ar[r]^{r} & R}\]
+	\[\xymatrix{L & K\ar@{>->}[l]_{l} \ar[r]^{r} & R}\]
 	$L$ is the \emph{left-hand side}, $R$ is the \emph{right-hand side} and $K$ the \emph{glueing object}.
@@
 	Given  two objects $G$ and $H$ and a rule $\rho=(l,r)$ in $\R$, a \emph{direct derivation $\mathscr{D}$ from $G$ to $H$ applying the rule $\rho$}, is a diagram as the one below, in which both squares are pushouts.
-	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
+	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}& H}\]
 	The arrow $n$ is called the \emph{match} of the derivation, while $h$ is its \emph{back-match}.
@@
 
-\begin{example}\todo{
-esempi di	derivazione}
+\begin{remark}\label{exa:conc} Let  $\dder{D}\colon G\Mapsto H$ be the direct derivation 
+	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}& H}\]
+	If $\phi\colon G'\to G$ and $\psi\colon H\to H'$ are two isomorphisms, 	we can consider the direct derivation	$\phi * \dder{D}*\psi \colon G'\Mapsto H'$ given by the following diagram.
+	\[\xymatrix{L \ar[d]_{\phi^{-1} \circ n}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{\psi \circ h}\\G' & \ar@{>->}[l]^{\phi^{-1} \circ f} D \ar[r]_{\psi \circ g}& H'}\]
+
+	In particular, we will use $\phi*\dder{D}$ and $\dder{D}*\psi$  to denote $\phi*\dder{D}*\id{H}$ and $\id{G}*\dder{D}*\psi$.
+\end{remark}
+
+\begin{example}\label{ex:1}
+	Let us consider the category of $\cat{Graph}$ of all graphs and graph morphisms, which is adhesive (see, for instance \cite{lack2005adhesive,lack2006toposes}).
+We can endow $\cat{Graph}$ with a set of left-linear rules, for instance taking the following ones.
+Here numbers are used to represent the
+	morphisms from the interface to the left- and right-hand
+	sides. Rules $\rho_0$ and $\rho_1$ are linear: $\rho_0$ generates a
+	new node and a new edge, while $\rho_1$ creates a self-loop edge. Instead,
+	$\rho_2$ is left-linear but not linear, as it ``merges'' two nodes.
+	\begin{center}
+		\begin{tikzpicture}[node distance=2mm, font=\small]
+			%, baseline=(current bounding box.center), font=\small]
+			\node (l) {
+				\begin{tikzpicture}
+					%
+					\node at (0,0.53) {};
+					\node at (0,0) [node, label=below:$1$] (1) {} ;        
+					%
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node[font=\scriptsize, above] at (l.north) {$L_0$};
+			\node [right=of l] (k) {
+				\begin{tikzpicture}
+					%
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {};
+					%
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node[font=\scriptsize, above] at (k.north) {$K_0$};
+			\node[below] at (k.south) {$\rho_0$};
+			\node  [right=of k] (r) {
+				\begin{tikzpicture}
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {};
+					\node at (.5,0) [node, label=below:$2$] (2) {};
+					\draw[->] (1) to[out=20, in=160] (2);
+					%
+					\pgfBox
+				\end{tikzpicture}
+			};
+			\node[font=\scriptsize, above] at (r.north) {$R_0$};
+			\path (k) edge[->] node[trans, above] {} (l);
+			\path (k) edge[->] node[trans, above] {} (r);    
+		\end{tikzpicture}
+		%  }
+	%
+	\hspace{1cm}
+	%  \hfill
+	%
+	%  \subcaptionbox*{}{
+		% RULE P1
+		%
+		\begin{tikzpicture}[node distance=2mm, font=\small]
+			\node (l) {
+				\begin{tikzpicture}
+					%
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node[font=\scriptsize, above] at (l.north) {$L_1$};
+			\node [right=of l] (k) {
+				\begin{tikzpicture}
+					%
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {};
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node[font=\scriptsize, above] at (k.north) {$K_1$};
+			\node[below] at (k.south) {$\rho_1$};
+			\node  [right=of k] (r) {
+				\begin{tikzpicture}
+					\node at (0,0) [node, label=below:$1$] (1) {}
+					edge [in=55, out=85, loop] ();
+					%
+					\pgfBox
+				\end{tikzpicture}
+			};
+			\node[font=\scriptsize, above] at (r.north) {$R_1$};
+			\path (k) edge[->] node[trans, above] {} (l);
+			\path (k) edge[->] node[trans, above] {} (r);
+		\end{tikzpicture}
+		%  }
+	% 
+	\hspace{1cm}
+	%\hfill
+	%
+	%    \subcaptionbox*{}{
+		% RULE P2
+		%
+		\begin{tikzpicture}[node distance=2mm, font=\small]
+			\node (l) {
+				\begin{tikzpicture}
+					%
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+					%
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node[font=\scriptsize, above] at (l.north) {$L_2$};
+			\node [right=of l] (k) {
+				\begin{tikzpicture}
+					%
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+					%
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node[font=\scriptsize, above] at (k.north) {$K_2$};
+			\node[below] at (k.south) {$\rho_2$};
+			\node  [right=of k] (r) {
+				\begin{tikzpicture}
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$12$] (12) {};
+					%
+					\pgfBox
+				\end{tikzpicture}
+			};
+			\node[font=\scriptsize, above] at (r.north) {$R_2$};
+			\path (k) edge[->] node[trans, above] {} (l);
+			\path (k) edge[->] node[trans, above] {} (r);
+		\end{tikzpicture}
+	\end{center}
+
+	We can also give an example of derivation as follows, where the colors are used to avoid ambiguity in the edges.
+Note that the numbers in $\rho_1$ were changed consistently to represent the vertical morphisms.
+
+	\begin{center}
+		\begin{tikzpicture}[node distance=2mm, font=\small, baseline=(current bounding box.center)]      
+			\node (L0) at (0,2) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {};
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node [right=of L0] (K0) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {};
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node [above] at (K0.north) {$\rho_0$};
+			%     \node [above=of K1] {$\rho_0$};
+			\node [right=of K0](R0) {
+				\begin{tikzpicture}
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {};
+					\node at (.5,0) [node, label=below:$2$] (2) {};
+					\draw[coloredge] (1) to[out=20, in=160] (2);
+					% 
+					\pgfBox
+				\end{tikzpicture}
+			};
+			\path (K0) edge[->] node[trans, above] {} (L0);
+			\path (K0) edge[->] node[trans, above] {} (R0);
+
+			\node at (4,2) (L1) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$2$] (2) {} ;
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node [right=of L1] (K1) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$2$] (2) {};
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			%     \node [above=of K1] {$\rho_1$};
+			\node [above] at (K1.north) {$\rho_1$};
+			\node [right=of K1] (R1) {
+				\begin{tikzpicture}
+					\node at (0,0) [node, label=below:$2$] (2) {}
+					edge [in=55, out=85, loop] ();        
+					% 
+					\pgfBox
+				\end{tikzpicture}
+			};
+			\path (K1) edge[->] node[trans, above] {} (L1);
+			\path (K1) edge[->] node[trans, above] {} (R1);
+
+			\node at (8,2) (L2) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node [right=of L2] (K2) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			%      \node [above=of K2] {$\rho_2$};
+			\node [above] at (K2.north) {$\rho_2$};
+			\node [right=of K2] (R2) {
+				\begin{tikzpicture}
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$12$] (12) {};
+					% 
+					\pgfBox
+				\end{tikzpicture}
+			};
+			\path (K2) edge[->] node[trans, above] {} (L2);
+			\path (K2) edge[->] node[trans, above] {} (R2);
+
+			%%%%%% second row
+			\node at (0,0) (G0) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {};
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node [right=of G0] (D0) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {};
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node at (3,0) (G1) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+					\draw[coloredge] (1) to[out=20, in=160] (2);
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\path (D0) edge[->] node[trans, above] {} (G0);
+			\path (D0) edge[->] node[trans, above] {} (G1);
+			\path (L0) edge[->] node[trans, above] {} (G0);
+			\path (K0) edge[->] node[trans, above] {} (D0);
+			\path (R0) edge[->] node[trans, above] {} (G1);
+
+			\node at (5,0) (D1) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {};
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+					\draw[coloredge] (1) to[out=20, in=160] (2);
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node at (7,0) (G2) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {};
+					\node at (0.5,0) [node, label=below:$2$] (2) {}
+					edge [in=55, out=85, loop] (); 
+					\draw[coloredge] (1) to[out=20, in=160] (2);
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+
+			\path (D1) edge[->] node[trans, above] {} (G1);
+			\path (D1) edge[->] node[trans, above] {} (G2);
+			\path (L1) edge[->] node[trans, above] {} (G1);
+			\path (K1) edge[->] node[trans, above] {} (D1);
+			\path (R1) edge[->] node[trans, above] {} (G2);
+
+			\node at (9.46,0) (D2) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0) [node, label=below:$1$] (1) {};
+					\node at (0.5,0) [node, label=below:$2$] (2) {}
+					edge [in=55, out=85, loop] ();
+					\draw[coloredge] (1) to[out=20, in=160] (2);
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node [right=of D2] (G3) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0) [node, label=below:$12$] (12) {}
+					edge [in=55, out=85, loop] ()
+					edge [in=125, out=155, colorloop] ();
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node[font=\scriptsize, below] at (G0.south) {$G_0$};
+			\node[font=\scriptsize, below] at (D0.south) {$D_0$};      
+			\node[font=\scriptsize, below] at (G1.south) {$G_1$};
+			\node[font=\scriptsize, below] at (D1.south) {$D_1$};      
+			\node[font=\scriptsize, below] at (G2.south) {$G_2$};
+			\node[font=\scriptsize, below] at (D2.south) {$D_2$};      
+			\node[font=\scriptsize, below] at (G3.south) {$G_3$};      
+			\path (D2) edge[->] node[trans, above] {} (G2);
+			\path (D2) edge[->] node[trans, above] {} (G3);
+			\path (L2) edge[->] node[trans, above] {} (G2);
+			\path (K2) edge[->] node[trans, above] {} (D2);
+			\path (R2) edge[->] node[trans, above] {} (G3);
+		\end{tikzpicture}
+		%
+	\end{center}
+
 \end{example}
-
-\begin{remark}\label{exa:conc} Let  $\dder{D}\colon G\Mapsto H$ be the direct derivation 
-		\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar[l]^{f} D \ar[r]_{g}& H}\]
-	If $\phi\colon G'\to G$ and $\psi\colon H\to H'$ are two isomorphisms, 	we can consider the direct derivation	$\phi * \dder{D}*\psi \colon G'\Mapsto H'$ given by the following diagram.
-	\[\xymatrix{L \ar[d]_{\phi^{-1} \circ n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{\psi \circ h}\\G' & \ar[l]^{\phi^{-1} \circ f} D \ar[r]_{\psi \circ g}& H'}\]
-
-	In particular, we will use $\phi*\dder{D}$ and $\dder{D}*\psi$  to denote $\phi*\dder{D}*\id{H}$ and $\id{G}*\dder{D}*\psi$.
-\end{remark}
 
@@
 	By construction, the pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$ and $n$.
-Thus, the existence of the isomorphism $t\colon D\to D'$ follows from \Cref{lem:pocomp}.
+Thus, the existence of the isomorphism $t\colon D\to D'$ follows from the second point of \Cref{lem:radj}.
 Now, computing we have
@@
 \begin{notation}Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ be a derivation. We will depict the $i^\text{th}$ element $\dder{D}_i$ of $\der{D}$ as in the following diagram.  
-	\[\xymatrix{L_i \ar[d]_{m_i}& K_i \ar[d]^{k_i}\ar[l]_{l_i} \ar[r]^{r_i} & R_i \ar[d]^{h_i} \\G_{i} & \ar[l]^{f_{i}} D_{i} \ar[r]_{g_{i}}& G_{i+1} }\]
+	\[\xymatrix{L_i \ar[d]_{m_i}& K_i \ar[d]^{k_i}\ar@{>->}[l]_{l_i} \ar[r]^{r_i} & R_i \ar[d]^{h_i} \\G_{i} & \ar@{>->}[l]^{f_{i}} D_{i} \ar[r]_{g_{i}}& G_{i+1} }\]
 	Notice that, in particular, if $\der{D}\colon G\to H$, then $G_0=G$ and $G_{n+1}=H$.
@@
 \begin{definition} Let $(\X, \R)$ be a a left-linear DPO-rewriting system.
-Given a derivation $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ between $G$ and $H$ and isomorphisms $\phi\colon G\to G'$, $\psi\colon H\to H'$, the derivations  $\phi*\der{D}$ and $\der{D}*\psi$ are defined as
+Given a derivation $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ between $G$ and $H$ and isomorphisms $\phi\colon G'\to G$, $\psi\colon H\to H'$, the derivations  $\phi*\der{D}$ and $\der{D}*\psi$ are defined as
 	\[\phi *\der{D} := \begin{cases}
@@
 \begin{definition}Let $(\X, \R)$ be a left-linear DPO-rewriting system,  an \emph{abstraction equivalence} between two derivations $\der{D}$ and $\der{D'}$ with the same length and such that $r(\der{D})=r(\der{D}')$, is a family of isomorphisms $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ such that, for every $i\in [0, \lgh(\der{D})]$ the following diagram commutes
-	\[\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i} \ar[l]_{f'_i}&G'_{i+1}\\  L_i \ar[u]^{n'_i} \ar[d]_{n_i}& K_i \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar[l]_{l_i} &R\ar[u]^{h'_i} \ar[d]_{h_i}\\G_i \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole \ar[r]_{g_i}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{H_i}}}\]
+	\[\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i} \ar@{>->}[l]_{f'_i}&G'_{i+1}\\  L_i \ar[u]^{n'_i} \ar[d]_{n_i}& K_i \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i} &R\ar[u]^{h'_i} \ar[d]_{h_i}\\G_i \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar@{>->}[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole \ar[r]_{g_i}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{H_i}}}\]
 
@@
 Indeed $(\der{D}, \alpha, \omega)$ is abstract equivalent to itself via the abstract equivalence with the identities as components.
-Furthermore, if  $\{\phi_X\}_{X\in \Deltamin(\der{D})}$  witnesses $(\der{D}, \alpha, \omega)\equiv_a (\der{D}', \alpha', \omega')$, then considering $\{\phi^{-1}_X\}_{X\in \Deltamin(\der{D})}$ shows $(\der{D}', \alpha', \omega)\equiv_a (\der{D}, \alpha, \omega)$.
+Furthermore, if  $\{\phi_X\}_{X\in \Deltamin(\der{D})}$  witnesses $(\der{D}, \alpha, \omega)\equiv^a (\der{D}', \alpha', \omega')$, then considering $\{\phi^{-1}_X\}_{X\in \Deltamin(\der{D})}$ shows $(\der{D}', \alpha', \omega)\equiv^a (\der{D}, \alpha, \omega)$.
 Finally, transitivity is assured composing abstract equivalences.
@@
 	Let $(\der{D},\alpha, \omega)$ be an empty derivation from an object $G$ and  $(\der{D}',\alpha', \omega')$ a another empty one from $G'$.
-If $(\der{D},\alpha, \omega)\equiv_a(\der{D}',\alpha', \omega')$ then an abstraction equivalence between $\der{D}$ and $\der{D}'$ is just an isomorphism $\phi\colon G\to G'$, so that $\pi(G)=\pi(G')$.
+If $(\der{D},\alpha, \omega)\equiv^a(\der{D}',\alpha', \omega')$ then an abstraction equivalence between $\der{D}$ and $\der{D}'$ is just an isomorphism $\phi\colon G\to G'$, so that $\pi(G)=\pi(G')$.
 Moreover, such isomorphism must fit in the diagrams below.
@@
 	It is immediate to see that the family $\{\varphi_X\}_{X\in \Deltamin(\der{D})}$ is an abstraction equivalence between $\der{D}$ and $\phi *\der{D}$, while $\{\varphi'_X\}_{X\in \Deltamin(\der{D})}$ is one between $\der{D}$ and $\der{D}*\psi$.
+
+	Taking in account the decorations, we also have that $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ and  $\{\phi'_X\}_{X\in \Deltamin(\der{D})}$ witness, respectively, that 
+	\[(\der{D}, \alpha, \omega) \equiv^a (\phi * \der{D}, \phi^{-1}\circ \alpha,   \varphi^{-1}_{H} \circ \omega) \qquad (\der{D}, \alpha, \omega) \equiv^a ( \der{D}*\psi, \varphi'_{G} \circ \alpha, \psi \circ \omega )\]
+
+Notice, moreover, that if $\der{D}$ is not empty, then the previous equations become
+\[(\der{D}, \alpha, \omega) \equiv^a (\phi * \der{D}, \phi^{-1}\circ \alpha,   \omega) \qquad (\der{D}, \alpha, \omega) \equiv^a ( \der{D}*\psi, \alpha, \psi \circ \omega )\]
 \end{remark}
@@
 We will also assume that $\dder{D}_i$, $\dder{D}'_i$, $\dder{E}_i$ and $\dder{E}'_i$ are given, respectively, by the following four diagrams.
-	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}, i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}, i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}, i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}, i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}, i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}, i}} \\G_i & D_i \ar[r]_{g_{\der{D},i}} \ar[l]^{f_{\der{D},i}} & G_{i+1} & E_i & F_i\ar[r]_{g_{\der{E},i}} \ar[l]^{f_{\der{E},i}}  & E_{i+1}}\]
-	\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}', i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}', i}} \ar[r]^{r_{\der{D},i}} \ar[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}', i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}', i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}', i}} \ar[r]^{r_{\der{E},i}} \ar[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}', i}} \\G'_i & D'_i \ar[r]_{g_{\der{D}',i}} \ar[l]^{f_{\der{D}',i}} & G'_{i+1} & E'_i & F'_i\ar[r]_{g_{\der{E}',i}} \ar[l]^{f_{\der{E}',i}}  & E'_{i+1}}\]
+		\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}, i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}, i}} \ar[r]^{r_{\der{D},i}} \ar@{>->}[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}, i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}, i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}, i}} \ar[r]^{r_{\der{E},i}} \ar@{>->}[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}, i}} \\G_i & D_i \ar[r]_{g_{\der{D},i}} \ar@{>->}[l]^{f_{\der{D},i}} & G_{i+1} & E_i & F_i\ar[r]_{g_{\der{E},i}} \ar@{>->}[l]^{f_{\der{E},i}}  & E_{i+1}}\]
+		\[\xymatrix{L_{\der{D},i} \ar[d]_{m_{\der{D}', i}}& K_{\der{D},i} \ar[d]_{k_{\der{D}', i}} \ar[r]^{r_{\der{D},i}} \ar@{>->}[l]_{l_{\der{D},i}} & R_{\der{D},i}\ar[d]^{h_{\der{D}', i}} &L_{\der{E},i} \ar[d]_{m_{\der{E}', i}}& K_{\der{E},i} \ar[d]_{k_{\der{E}', i}} \ar[r]^{r_{\der{E},i}} \ar@{>->}[l]_{l_{\der{E},i}} & R_{\der{E},i}\ar[d]^{h_{\der{E}', i}} \\G'_i & D'_i \ar[r]_{g_{\der{D}',i}} \ar@{>->}[l]^{f_{\der{D}',i}} & G'_{i+1} & E'_i & F'_i\ar[r]_{g_{\der{E}',i}} \ar@{>->}[l]^{f_{\der{E}',i}}  & E'_{i+1}}\]
 
@@
 
-To show that $\{\psi_X\}_{\Deltamin(\der{D}*\omega^{-1}\cdot \beta*\der{E})}$ is an abstraction equivalence, it is now enough to prove the commutativity of the diagrams
-	\[\xymatrix@C=45pt@R=15pt{G'_n&D'_n \ar[r]^-{(\omega')^{-1}\circ g_{\der{D}',n}} \ar@/_.2cm/[dr]_(.6){g_{\der{D}',n}} \ar[l]_{f_{\der{D}',n}}&\pi(H') \\&&H' \ar[u]^{(\omega')^{-1}}\\  L_{\der{D}, n} \ar[uu]^{m_{\der{D}',n}} \ar[dd]_{m_{\der{D},n}}& K_{\der{D}, n} \ar[uu]^{k_{\der{D}',n}} \ar[dd]_{k_{\der{D},n}} \ar[r]^{r_{\der{D},n}} \ar[l]_{l_{\der{D},n}} &R_{\der{D}, n}\ar[u]^{h_{\der{D}',n}} \ar[d]_{h_{\der{D},n}}\\&&H \ar[d]_{\omega^{-1}}\\G_n \ar@/_.7cm/[uuuu]_(.35){\phi_{G_n}}|\hole&D_n\ar[l]^{f_{\der{D},n}}\ar@/_.7cm/[uuuu]_(.35){\phi_{D_n}}|\hole \ar@/^.2cm/[ur]^(.6){g_{\der{D},n}}\ar[r]_{\omega^{-1}\circ g_{\der{D},n}}&\pi(H)\ar@/_.7cm/[uuuu]_{\id{\pi(H)}}\\ \pi(E')&F'_0 \ar[l]_-{(\beta')^{-1}\circ f_{\der{E}',0}} \ar@/^.2cm/[dl]^(.6){f_{\der{E}',0}} \ar[r]^{g_{\der{E}',0}}&E'_1 \\E' \ar[u]_{(\beta')^{-1}}&& \\  L_{\der{E}, 0} \ar[u]_{m_{\der{E}', 0}} \ar[d]^{m_{\der{E}, 0}}& K_{\der{E}, 0} \ar[uu]_{k_{\der{E}', 0}} \ar[dd]^{k_{\der{E}, i}} \ar[r]^{r_{\der{E},0}} \ar[l]_{l_{\der{E},0}} &R_{\der{E}, 0}\ar[uu]_{h_{\der{E}',0}} \ar[dd]^{h_{\der{E},0}}\\E \ar[d]^{\beta^{-1}}&& \\\pi(E) \ar@/^.7cm/[uuuu]^{\id{\pi(E)}}&F_0\ar[l]^{\beta^{-1}\circ f_{\der{E},0}}\ar@/^.7cm/[uuuu]^(.35){\varphi_{F_0}}|\hole \ar@/_.2cm/[ul]_(.6){f_{\der{E},0}}\ar[r]_{g_{\der{E},0}}&E_1\ar@/^.7cm/[uuuu]^(.35){\varphi_{E_1}}|\hole}\]
-
-To see this, in turn, it is enough to show that	the squares
+		To show that $\{\psi_X\}_{\Deltamin(\der{D}*\omega^{-1}\cdot \beta*\der{E})}$ is an abstraction equivalence, it is now enough to prove the commutativity of the diagrams below.
+		\[\xymatrix@R=15pt@C=22pt{\pi(E')&&F'_0 \ar@{>->}[ll]_-{(\beta')^{-1}\circ f_{\der{E}',0}} \ar@{>->}@/^.2cm/[dll]^(.6){f_{\der{E}',0}} \ar[r]^{g_{\der{E}',0}}&E'_1 &G'_n&D'_n \ar[rr]^-{(\omega')^{-1}\circ g_{\der{D}',n}} \ar@/_.2cm/[drr]_(.6){g_{\der{D}',n}} \ar@{>->}[l]_{f_{\der{D}',n}}&&\pi(H')
+			\\E' \ar[u]_{(\beta')^{-1}} &&&&&&&H' \ar[u]^{(\omega')^{-1}}
+			\\  L_{\der{E}, 0} \ar[u]_{m_{\der{E}', 0}} \ar[d]^{m_{\der{E}, 0}}&& K_{\der{E}, 0} \ar[uu]_{k_{\der{E}', 0}} \ar[dd]^{k_{\der{E}, i}} \ar[r]^(.4){r_{\der{E},0}} \ar@{>->}[ll]_{l_{\der{E},0}} &R_{\der{E}, 0}\ar[uu]_{h_{\der{E}',0}} \ar[dd]^{h_{\der{E},0}} & L_{\der{D}, n} \ar[uu]^{m_{\der{D}',n}} \ar[dd]_{m_{\der{D},n}}& K_{\der{D}, n} \ar[uu]^{k_{\der{D}',n}} \ar[dd]_{k_{\der{D},n}} \ar[rr]^{r_{\der{D},n}} \ar@{>->}[l]_(.4){l_{\der{D},n}} &&R_{\der{D}, n}\ar[u]^{h_{\der{D}',n}} \ar[d]_{h_{\der{D},n}}
+			\\E \ar[d]^{\beta^{-1}}&&&&&&&H \ar[d]_{\omega^{-1}}
+			\\\pi(E) \ar@/^.7cm/[uuuu]^(.2){\id{\pi(E)}}&&F_0\ar@{>->}[ll]^{\beta^{-1}\circ f_{\der{E},0}}\ar@/^.7cm/[uuuu]^(.35){\varphi_{F_0}}|\hole \ar@{>->}@/_.2cm/[ull]_(.6){f_{\der{E},0}}\ar[r]_{g_{\der{E},0}}&E_1\ar@/^.7cm/[uuuu]^(.35){\varphi_{E_1}}|\hole&G_n \ar@/_.7cm/[uuuu]_(.35){\phi_{G_n}}|\hole&D_n\ar@{>->}[l]^{f_{\der{D},n}}\ar@/_.7cm/[uuuu]_(.35){\phi_{D_n}}|\hole \ar@/^.2cm/[urr]^(.6){g_{\der{D},n}}\ar[rr]_{\omega^{-1}\circ g_{\der{D},n}}&&\pi(H)\ar@/_.7cm/[uuuu]_(.2){\id{\pi(H)}}} \]
+
+		To see this, in turn, it is enough to show that	the following squares are commutative.
 		\[\xymatrix{R_{\der{D}, n} \ar[d]_{h_{\der{D}, n}}\ar[r]^{h_{\der{D}', n}} & H' \ar[d]_{(\omega')^{-1}} &L_{\der{E}, 0} \ar[d]^{m_{\der{E}, 0}}\ar[r]^{m_{\der{E}', 0}}& E' \ar[d]^{(\beta')^{-1}}\\H\ar[r]_{\omega^{-1}} &\pi(H)&E \ar[r]_{\beta^{-1}} & \pi(E)}\]
-\[\xymatrix{D_n \ar[rr]^{\phi_{D_n}} \ar[d]_{g_{\der{D}, n}}&&D'_n \ar[d]_{g_{\der{D}', n}}&F_0 \ar[d]^{f_{\der{E}, 0}} \ar[rr]^{\varphi_{F_0}} && F_0' \ar[d]^{f_{\der{E}', 0}}\\H \ar[r]_-{\omega^{-1}} &\pi(H)&H' \ar[l]^-{(\omega')^{-1}}  &E \ar[r]_-{\beta^{-1}} & \pi(E) & E' \ar[l]^-{(\beta')^{-1}}}\]
-are commutative. For the first ones, we have
+		\[\xymatrix{D_n \ar[rr]^{\phi_{D_n}} \ar[d]_{g_{\der{D}, n}}&&D'_n \ar[d]_{g_{\der{D}', n}}&F_0 \ar@{>->}[d]^{f_{\der{E}, 0}} \ar[rr]^{\varphi_{F_0}} && F_0' \ar@{>->}[d]^{f_{\der{E}', 0}}\\H \ar[r]_-{\omega^{-1}} &\pi(H)&H' \ar[l]^-{(\omega')^{-1}}  &E \ar[r]_-{\beta^{-1}} & \pi(E) & E' \ar[l]^-{(\beta')^{-1}}}\]
+
+		For the first ones, we have
 		\[
@@
 
-\section{A theory of processes for left-linear DPO-rewriting systems}
-
+\subsection{Colimits of derivations}
 Given a DPO-rewriting system $(\X, \R)$,  we have already noted in \Cref{rem:func} that a derivation $\der{D}$  determines a diagram $\Delta(\der{D})$ in $\X$.
@@
 			\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} \\G& \ar@{>->}[l]^{f} D \ar[r]_{g}& H  \\}\]
-			The arrow $f$ is  the pushout of $l$ and so it is in in $\mathcal{M}$. We can thus consider the $\mathcal{M}$-pushout square
+			The arrow $f$ is  the pushout of $l$ and so it is in in $\mathcal{M}$. We can thus consider the following $\mathcal{M}$-pushout square.
 			\[\xymatrix{D \ar@{>->}[d]_{f} \ar[r]^{g} & H \ar@{>->}[d]^{p} \\G \ar[r]_{q}& P }\]
@@
 
-\subsection{Semi-consistent and consistent permutations}
+\section{Semi-consistent and consistent permutations}
 
@@
 \begin{remark}\label{rem:inversa}
-	Let $\sigma\colon [0,n]\to [0,n]$ be a consistent permutation between $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, then its inverse $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$.
+	Let  $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations and $\sigma\colon [0,n]\to [0,n]$ be a consistent permutation between them.
+Then its inverse $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$.
 Indeed, it is enough to consider, as mediating isomorphism, the inverse $\xi^{-1}_\sigma$ of $\xi_\sigma$.
@@
 
-\begin{remark} Notice that if $\sigma$ is a semi-consistent permutation between two derivations  $\der{D}$ and $\der{D}'$ of length $l$, then for every  $i\in [0,l-1]$ the diagram below commutes.
+\begin{remark} \label{rem:coproj} Notice that if $\sigma$ is a semi-consistent permutation between two derivations  $\der{D}$ and $\der{D}'$ of length $l$, then for every  $i\in [0,l-1]$ the diagram below commutes.
 	\[\xymatrix@C=40pt{G_i\ar@/^1cm/[rrr]^{\iota_{G_{i}}}&D_i\ar@/^.4cm/[rr]^(.35){\iota_{D_i}} \ar[r]_{g_i} \ar@{>->}[l]^{f_i}&G_{i+1} \ar[r]_{\iota_{G_{i+1}}}&\tpro{D} \ar[dd]^{\xi_\sigma}\\  L_i \ar[u]^{n_i} \ar[d]_{n'_{\sigma(i)}}& K_i \ar[d]^{k'_{\sigma(i)}} \ar[u]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i} &R\ar[u]^{h_i} \ar[d]_{h'_{\sigma(i)}}\\G'_{\sigma(i)}\ar@/_1cm/[rrr]_{\iota'_{G'_{\sigma(i)}}} &D'_{\sigma(i)}\ar@{>->}[l]_{f'_{\sigma(i)}} \ar[r]^{g'_i} \ar@/_.4cm/[rr]_(.35){\iota'_{D'_{\sigma(i)}}}&G'_{\sigma(i)+1} \ar[r]^{\iota'_{G'_{\sigma(i)+1}}}& \lpro\der{D}' \rpro }\]
@@
 	\end{align*}
-\end{remark}
-
-\begin{remark}\label{rem:coproj}
-	Notice that, in particular, the previous diagram entails
+
+	In particular, the previous diagram entails the following identities.
 	\[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
@@
 For the last half of the thesis, we can reason similarly. Indeed, the diagram below commutes.
-\[\xymatrix@C=30pt{\pi(G_l)\ar[r]^{\omega} \ar[d]_{\omega'} & G_l \ar[dl]^{\phi_{G_l}} \ar[r]^{\iota_{G_l}} &\tpro{D} \ar[d]^{\xi_{\id{[l, l-1]}}}\\ G'_l \ar[rr]_{\iota'_{G'_l}} & &\lpro \der{D}' \rpro}\]
+\[\xymatrix@C=30pt{\pi(G_l)\ar[r]^{\omega} \ar[d]_{\omega'} & G_l \ar[dl]^{\phi_{G_l}} \ar@{>->}[r]^{\iota_{G_l}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}}\\ G'_l \ar@{>->}[rr]_{\iota'_{G'_l}} & &\lpro \der{D}' \rpro}\]
 This clearly entails the thesis.
@@
 Let also $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ be an abstraction equivalence between $\der{D}$ and $\der{D}'$ such that  $\alpha'\circ \phi_{G_0}=\alpha$.
-If  the identity $\id{[0,l-1]}$ is a consistent permutation, then $\omega'\circ \phi_{G_l}=\omega$, so that $(\der{D}, \alpha, \omega) \equiv_a (\der{D}', \alpha', \omega')$.
+If  the identity $\id{[0,l-1]}$ is a consistent permutation, then $\omega'\circ \phi_{G_l}=\omega$, so that $(\der{D}, \alpha, \omega) \equiv^a (\der{D}', \alpha', \omega')$.
 \end{corollary}
@@
 \begin{remark}\label{rem:abscons2}
-	In particular, given a decorated derivation $(\der{D}, \alpha, \omega)$ with source $G$ and target $H$ and two isomorphisms, $\phi\colon G'\to G$ $\psi\colon H\to H'$ be two isomorphisms, we know, by \Cref{rem:absequi}, that \[(\der{D}, \alpha, \omega)\equiv_a (\phi*\der{D}, \phi^{-1}\circ \alpha, \omega ) \qquad (\der{D}, \alpha, \omega)\equiv_a (\der{D}*\psi, \alpha, \psi \circ \omega )\]
-	In these cases, if the cocones $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$, $(\lpro \phi *\der{D} \rpro, \{\iota'_X\}_{X\in \Delta(\phi *\der{D})})$ and $(\lpro \der{D}*\psi \rpro, \{\iota'_X\}_{X\in \Delta(\der{D}*\psi)})$ are colimiting, we can take as mediating isomorphisms, respectively, the unique arrows $\Gamma^{\phi} \colon \tpro{D}\to \lpro \phi*\der{D} \rpro$ and $\Gamma_\psi\colon \tpro{D}\to \lpro \der{D}*\psi \rpro$  such that, for every $X\in \Deltamin(\der{D})$:
+	In particular, given a decorated derivation $(\der{D}, \alpha, \omega)$ with source $G$ and target $H$ and two isomorphisms $\phi\colon G'\to G$, $\psi\colon H\to H'$, we know, by \Cref{rem:absequi}, that
+	\[(\der{D}, \alpha, \omega) \equiv^a (\phi * \der{D}, \phi^{-1}\circ \alpha,   \varphi^{-1}_{H} \circ \omega) \qquad (\der{D}, \alpha, \omega) \equiv^a ( \der{D}*\psi, \varphi'_{G} \circ \alpha, \psi \circ \omega )\]
+
+	Now, denoting by $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$, $(\lpro \phi *\der{D} \rpro, \{\iota'_X\}_{X\in \Delta(\phi *\der{D})})$ and $(\lpro \der{D}*\psi \rpro, \{\hat{\iota}_X\}_{X\in \Delta(\der{D}*\psi)})$ the colimiting cocones, in this case we have that the, unique, mediating isomorphisms witnessing the consistency of $\id{[0, \lgh(\der{D})-1]}$ are given by the arrows $\Gamma^{\phi} \colon \tpro{D}\to \lpro \phi*\der{D} \rpro$ and $\Gamma_\psi\colon \tpro{D}\to \lpro \der{D}*\psi \rpro$  such that, for every $X\in \Deltamin(\der{D})$:
 	\[\Gamma^\phi \circ \iota_X:=\begin{cases}
@@
 
-\subsubsection{Restricting  consistent permutations}
+\section{Composing and decomposing consistent permutations}
 Now that we have established some initial facts about consistent permutations, we are going to embark in a, quite long, voyage to explore how to restrict them to suitable subderivations.
@@
 
-We can now turn our attention to the case in which a consistent permutation between two composite derivations is given.
-
-\begin{lemma}[Restriction Lemma]\label{prop:uniqu}
+We can now turn our attention to the case in which a consistent permutation between two composite derivations is given. As a first step we need to prove some technicalities.
+
+\begin{lemma}\label{prop:uniqu}
 	Let $\sigma\colon [0,n]\to [0,n]$ be a consistent permutations between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ and suppose that 
@@
 Suppose that $\sigma:[0, l_1+l_2-1]\to [0, l_1+l_2-1]$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)$ for some other two composable decorated derivations $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}_2, \alpha_2, \omega_2)$.
-If $\tau:[0,l_1-1]\to [0, l_1-1]$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$.
-Suppose that  the set
+Let, moreover, $\tau:[0,l_1-1]\to [0, l_1-1]$ be a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$.
+Suppose, finally, that  the set
 	\[D_{\sigma, \tau}:=\{i\in [0, l_1-1]\mid \sigma(i)\neq \tau(i)\}\]
-	is non-empty and let $j$ be its minimum. Let also $r(\der{D}_1)$ be $\{\rho_i\}_{i=0}^{l_1-1}$. Then the following hold true:
+	is non-empty and let $j$ be its minimum. If $r(\der{D}_1)$ is $\{\rho_i\}_{i=0}^{l_1-1}$ then the following hold true:
 	\begin{enumerate}
@@
 
-\begin{lemma}[Corestriction Lemma]\label{lem:presuffix} Let $(\X, \R)$ be a consuming left-linear DPO-rewriting system.
+\begin{lemma}[Restriction Lemma]\label{lem:presuffix} Let $(\X, \R)$ be a consuming left-linear DPO-rewriting system.
 Let also $(\der{D}_1, \alpha_1, \omega_1)$, $(\der{D}_2, \alpha_2, \omega_2)$ be two composable decorated derivations of length, respectively, $l_1$ and $l_2$.
@@
 
-\begin{lemma}\label{lem:sum} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstract decorated derivations such that
+\begin{lemma}[Composition lemma]\label{lem:sum} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstract decorated derivations such that:
 	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)\]
-	Given a consistent permutation $\sigma\colon [0, \lgh(\der{D}_1)-1]\to [0, \lgh(\der{D}_1)-1]$ between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$ and another $\tau\colon [0, \lgh(\der{D}_2)-1]\to [0, \lgh(\der{D}_2)-1]$ between $(\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$, then
+
+	Given a consistent permutation $\sigma\colon [0, \lgh(\der{D}_1)-1]\to [0, \lgh(\der{D}_1)-1]$ between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$ and another $\tau\colon [0, \lgh(\der{D}_2)-1]\to [0, \lgh(\der{D}_2)-1]$ between $(\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$, then:
 	\[\sigma+\tau\colon[0, \lgh(\der{D})-1]\to[0, \lgh(\der{D})-1] \quad i \mapsto \begin{cases}
@@
 \end{itemize} \end{proof}
-
-\section{Independence in rewriting}
-\todo{A VERY NICE INTRO}
-
-\subsection{Sequentially independent and switchable derivations }
-\todo{this is an attempt to rewrite in a better way the following section. Hopefully this will spare us the use of fillers}
-\todo{A VERY NICE INTRO}
-
-\begin{definition}[Sequential independence]
-  \label{de:sequential-independence}
-  Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Let also $\dder{D}\colon G\Mapsto H$ and $\dder{D'}\colon H\Mapsto T$ be the two direct derivations depicted below.
-
-	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{m'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
-
-	An \emph{independence pair} between $\dder{D}$ and $\dder{D'}$, is a pair of  arrows $i_1\colon R\to D'$ and $i_2\colon L'\to D$ such that the following diagram commutes.
-
-	\[\xymatrix@C=15pt{L \ar[d]_{m}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
-	We will say that $\dder{D}$ and $\dder{D'}$ are \emph{weakly sequentially independent} if an independence pair exists.
-If such independence pair is unique we will say that $\dder{D}$ and $\dder{D'}$ are \emph{sequentially independent}.
-\end{definition}
-
-\begin{example}
-	\todo{sequential independence}
-\end{example}
-\begin{example}
-	\todo{sequential independence che serva anche per es successivo}
-\end{example}
-
- Let $(i_0, i_1)$ and $(i'_0, i'_1)$ be independence pairs for the direct derivations $\dder{D}$ and $\dder{D'}$. Notice that, by definition, we have
-	\begin{align*}f'\circ i_0&=h\\&=f'\circ i'_0
-	\end{align*}
-	On the other hand, 
-	$f'\colon D'\to H$ is  the pushout of $l'\colon K'\to L'$ and so it is in $\mathcal{M}$, implying $i_0=i'_0$.
-If, moreover, we suppose that the rule $\rho$ applied in $\dder{D}$ is linear, then $g\colon D\to H$ is in $\mathcal{M}$ too, hence, from the equation
-	\begin{align*}
-		g\circ i_1&=h \\&= g\circ i'_1
-	\end{align*}
-	we can deduce that $i'_0=i'_1$, too. Summing up, we have just proved the following.
-
-	\begin{proposition}\label{rem:weak}
-	Let $(\X, \R)$ be a linear DPO-rewriting system, then two direct derivations $\dder{D}$ and $\dder{D}'$ are weakly sequential independet if and only if they are sequential independent. 
-\end{proposition}
-
-We want to be able to exchange to switch the application of two rules used by two consecutive weakly independent direct derivations. This leads us to the following definition.
-
-\begin{definition}[Switch]
-  \label{de:switch}
- Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category and suppose that $\der{D}=\{\dder{D}_i\}_{i=0}^1$  is a derivation of length $2$ made by the following two weakly sequentially independent derivations $\dder{D}_0$, $\der{D}_1$, with independence pair $(i_0, i_1)$:
- 	\[\xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0} && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2}\]
-
- 	Take another derivation $\der{E}=\{\dder{E}_i\}_{i=0}^1$ with source $G_0$ and target $G_2$ and in which $\der{E}_0$, $\der{E}_1$ are
-\[\xymatrix{L_{\der{E},0} \ar[d]_{m_{\der{E},0}}& K_{\der{E},0} \ar[d]^{k_{\der{E},0}}\ar[l]_{l_{\der{E},0}} \ar[r]^{r_{\der{E},0}} & R_{\der{E},0} \ar[d]^{h_{\der{E},0}} & L_{\der{E},1} \ar[d]_{m_{\der{E},1}}& K_{\der{E},1} \ar[d]^{k_{\der{E},1}}\ar[l]_{l_{\der{E},1}} \ar[r]^{r_{\der{E},1}} & R_{\der{E},1} \ar[d]^{h_{\der{E},1}}\\G_{0} & \ar[l]^{f_{\der{E},0}} D_{\der{E},0} \ar[r]_{g_{\der{E},0}}& G_{\der{E},1} & G_{\der{E},1} & \ar[l]^{f_{\der{E},1}} D_{\der{E},1} \ar[r]_{g_{\der{E},1}}& G_{2}}\]
- 	We say that $\der{E}$ is a
- 	 	 \emph{switch} of $\der{D}$ along $(i_1, i_2)$ if
- 	\begin{enumerate}
- 		\item $\dder{E}_0$ applies the rule used by $\dder{D}_1$ and $\dder{E}_1$ the one used by $\dder{D}_0$, so that
- 		\[(l_{\der{E},0}, r_{\der{E},0})=(l_1,r_1)  \qquad (l_{\der{E},1}, r_{\der{E},1})=(l_0,r_0)\]
- 		\item there exists an independence pair $(j_0, j_1)$ between $\dder{E}_0$ and $\dder{E}_1$ such that
- 		\[ m_0=f_{\der{E},0} \circ j_1 \qquad h_1=g_{\der{E},1} \circ j_0\]
- 		\item $m_{\der{E},0}= f_0\circ i_1$ and $h_{\der{E},1}= g_{1}\circ i_0$.
- 	\end{enumerate}
-\end{definition}
-
-\begin{remark}\label{rem:fact}
-	Notice that, since $f_{\der{E}, 0}$ is in $\mathcal{M}$, there is at most one $j_1\colon L_0\to D_{\der{E},0}$ such that $m_0=f_{\der{E}, 0} \circ j_1$.
-Moreover, we already know that there is at most one $j_0\colon R_1\to D_{\der{E},1}$ such that $m_{\der{E},1}=f_{\der{E},1}\circ j_0$, therefore, the independence pair $(j_0,j_1)$ between the component of a switch is uniquely determined.
-\end{remark}
-
-Our first result about switches is their uniqueness up to abstraction equivalence.
-
-\begin{theorem}[Uniqueness of switches]\label{thm:switch_uni} Let $\der{D}=\{\dder{D}_i\}_{i=0}^1$
-
-\end{theorem}
-
-\begin{lemma}\label{lem:cose} Let $(\der{D}, \alpha, \omega)$ be a decorated derivation with $\der{D}=\{\dder{D}_i\}_{i=0}^1$,  and suppose that $(i_0, i_1)$ is an independence pair between $\dder{D}_0$  and $\der{D}_1$.
-If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a switch of $\der{D}$ along $(i_0, i_1)$, then the following hold true:
-	\begin{enumerate}
-			\item the pullback square below is an $\mathcal{M}$-pushout;
-			\[\xymatrix{P \ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\ D_0 \ar[r]_{g_1}& G_1}\]
-			\item there exist $q_0\colon P\to D_{\der{E},0}$, $q_1\colon P\to D_{\der{E},1}$ making the squares 
-			\[\xymatrix{}\]
-			commutative, moreover, they are all pushouts;
-			\[\xymatrix{}\]
- 		\item there exists an arrow $j_0\colon R_1\to D_{\der{E},1}$ such that 
- 		\[h_{\der{E},0}=f_{\der{E},1}\circ j_0 \qquad h_1=g_{\der{E},1} \circ j_0\]
-	\end{enumerate}
-\end{lemma}
-\begin{proof}
-	Before starting with the proof of our claims, it is worth noticing that the definition of switchin gives us the following diagram:
-			\[\xymatrix@R=28pt{&&R_0 \ar@/_1.15cm/[ddrr]_(.8){i_0}|(.68)\hole \ar[dr]^{h_0}&& L_1\ar@/^1.15cm/[ddll]^(.8){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar[ur]^{r_0}&& G_1 && K_1 \ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.94cm/[ddrr]_(.8){j_1}|(.31)\hole \ar[dr]^(.35){m_0}|(.6)\hole && D_0 \ar[dl]^{f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]_{g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar[dl]^(.35){h_1}|(.6)\hole\\&G_0 &&&&G_2\\L_1 \ar@/^.94cm/[uurr]^(.8){i_1} \ar[ur]_(.35){m_{\der{E},0}}|(.61)\hole&&D_{\der{E},0} \ar[ul]_{f_{\der{E},0}}\ar[dr]^{g_{\der{E},0}} &&D_{\der{E},1}\ar[ur]^{g_{\der{E},1}} \ar[dl]|(.5)\hole^(.7){f_{\der{E},1}} && R_0  \ar@/_.94cm/[uull]_(.8){j_1} \ar[ul]^{h_{\der{E},1}}\\&K_1 \ar[ur]_{k_{\der{E},0}} \ar[dr]_{r_1} \ar[ul]^{l_1}&&G_{\der{E},1}&& K_0 \ar[ur]_{r_0} \ar[ul]^{k_{\der{E},1}} \ar[dl]^{l_0} \\&& R_1 \ar[ur]_{h_{\der{E},0}}&& L_0 \ar[ul]^{m_{\der{E},1}} \ar@/_1.15cm/[uull]_(.6){j_1} }\]
-
-			Let us turn to our statements.
-	\begin{enumerate}
-		\item We start noticing that 
-		\begin{align*}
-			g_0\circ i_1\circ l_1&=m_1\circ l_1\\&=k_1\circ f_1
-		\end{align*}
-		Thus there exists the dotted $u\colon K_1\to P$ in the diagram
-		\[\]
-		The thesis now follows applyin \Cref{lem:popb} to
-
-		\item 
-		\item  We already have an arrow $j_1\colon L_0\to D_{\der{E},0}$ such that
-		\[m_{\der{E},1}=g_{\der{E},0}\circ j_1\]
-		Therefore the thesis follows at once from the previous point.
-
-	\item
-
-		\item \qedhere 
-	\end{enumerate}
-\end{proof}
-
-\todo{ $\dder{E}_0$ and $\dder{E}_1$ are weak sequentially independent;
-
-if $\der{E}'=\{\dder{E}'_i\}_{i=0}^1$ is another switching of $\der{D}$ along $(i_0, i_1)$, then there exist arrows.... such that the following diagram commutes:
-}
-In particular [...]
-\begin{definition}\todo{switch}
-	contenuto...
-\end{definition}
-\begin{remark}
-Canonico
-\end{remark}
-\begin{corollary}\todo{inversione}
-\end{corollary}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{lemma}
-	\todo{permutazione}
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{lemma}\label{lem:swfill}
-\todo{equi}
-\end{lemma}
-\begin{remark}
-	\todo{tobias}
-\end{remark}
-\begin{remark}
-	contenuto...
-\end{remark}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-When working with linear rewriting systems, (weakly) sequential independent direct derivations can be switched, producing two new (weakly) sequential independent direct derivations between the same objects \cite[Thm.~$7.7$]{lack2005adhesive} .
-This is no more the case if the rules are only left-linear, as shown by the next example.
-
-\begin{example}\label{ex:difficile}
-	\todo{pensare ad un esempio in cui l'indipendenza non basta }
-\end{example}
-
-\subsection{Sequentially independent and switchable derivations}
-\todo{A VERY NICE INTRO}
-
-\begin{definition}  Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Let also $\dder{D}\colon G\Mapsto H$ and $\dder{D'}\colon H\Mapsto T$ be the two direct derivations depicted below.
-
-	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
-
-	An \emph{independence pair} between $\dder{D}$ and $\dder{D'}$, is a pair of  arrows $i_1\colon R\to D'$ and $i_2\colon L'\to D$ such that the following diagram commutes.
-
-	\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/@{.>}[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/@{.>}[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
-	We will say that $\dder{D}$ and $\dder{D'}$ are \emph{weakly sequentially independent} if an independence pair exists.
-If such independence pair is unique we will say that $\dder{D}$ and $\dder{D'}$ are \emph{sequentially independent}.
-\end{definition}
-
-\begin{example}
-	\todo{sequential independence}
-\end{example}
-\begin{example}
-	\todo{sequential independence che serva anche per es successivo}
-\end{example}
-
-\begin{remark}\label{rem:weak} Let $(i_1, i_2)$ and $(j_1, j_2)$ be independence pairs for the direct derivations $\dder{D}$ and $\dder{D'}$. Notice that, by definition, we have
-	\begin{align*}f'\circ i_1&=h\\&=f'\circ j_1
-	\end{align*}
-	On the other hand, 
-	$f'\colon D'\to H$ is  the pushout of $l'\colon K'\to L'$ and so it is in $\mathcal{M}$, implying $j_1=i_1$.
-If, moreover, we suppose that the rule $\rho$ applied in $\dder{D}$ is linear, then $g\colon D\to H$ is in $\mathcal{M}$ too, hence, from the equation
-	\begin{align*}
-		g\circ i_2&=h \\&= g\circ j_2
-	\end{align*}
-	we can deduce that $i_2=j_2$, too.
-
-	Summing up, if $(\X, \R)$ is a linear DPO-rewriting system, then sequential independence and weak sequential independence coincide. 
-\end{remark}
-
-We want to be able to exchange to switch the application of two rules used by two consecutive weakly independent direct derivations
-\begin{definition}
-	contenuto...
-\end{definition}
-
-\begin{proposition}
-	\todo{equi}
-\end{proposition}
-\begin{remark}
-	contenuto...
-\end{remark}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-When working with linear rewriting systems, (weakly) sequential independent direct derivations can be switched, producing two new (weakly) sequential independent direct derivations between the same objects \cite[Thm.~$7.7$]{lack2005adhesive} .
-This is no more the case if the rules are only left-linear, as shown by the next example.
-
-\begin{example}\label{ex:difficile}
-	\todo{pensare ad un esempio in cui l'indipendenza non basta }
-\end{example}
-
-To fix this problem, we adapt the notion of \emph{canonical filler} from \cite{heindel2009category}.
-
-\begin{definition}\label{def:filler}
-Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ $\mathcal{M}$-adhesive. Let also $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$ be the two derivations depicted below.
-\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L' \ar[d]_{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[r]^{r'} & R' \ar[d]^{h'}\\G & \ar[l]^{f} D \ar[r]_{g}& H & H & \ar[l]^{f'} D' \ar[r]_{g'}& T}\]
-Since $f'$ is in $\mathcal{M}$, we can moreover consider a pullback square
-\[\xymatrix{P \ar[r]^{p} \ar[d]_{p'}& D\ar[d]^{g} \\ D' \ar[r]_{f'} & H}\]
-
-A \emph{filler} between $\dder{D}$ and $\dder{D}'$ is  given by a pair of arrows $u\colon K\to P$ and $u'\colon K'\to P$ satisfying the following conditions
-\begin{enumerate}
-	\item $p\circ u = k$, $p'\circ u' = k'$ and there exists a pushout square
-\[\xymatrix{K' \ar[r]^{r'} \ar[d]_{u'}& R'\ar@{.>}[d]^{j'} \\ P \ar@{.>}[r]_{q'} & Q'}\]
-	\item  there exist arrows $i_1\colon R\to D'$, $i_2\colon L'\to D$ satisfying $f'\circ i_1=h$, $g\circ i_2=n'$ and such that the following squares are pushouts
-\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar@{.>}[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar@{.>}[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
-\end{enumerate}
-\end{definition}
-
-\begin{remark}\label{rem:deco} Let $\dder{D}$ and $\dder{D'}$ be two switchable direct derivations. Then the existence of a filler allows us to build the solid part of the diagram below.
-	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole  \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@{.>}@/_.8cm/[ddrr]_{j}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j'}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar@{.>}[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar@{.>}[ul]_{s} &&Q'\ar@{.>}[ur]^{t}}\]
-
-	Let us complete this diagram defining the dotted arrows. We can start noticing that, since $l\in \mathcal{M}$, there exists a pushout square 
-	\[\xymatrix{K \ar[r]^{l} \ar[d]_{u}& L\ar[d]^{j} \\ P \ar[r]_{q} & Q}\]
-	Moreover, the existence of the wanted $s\colon Q\to G$ and $t\colon Q'\to T$ follows from the following equalities
-	\[\begin{split}
-		f\circ p \circ u &= f\circ k \\&= n\circ l
-	\end{split} \qquad \begin{split}
-		g'\circ p'\circ u' &= g'\circ k'\\&=h'\circ r'
-	\end{split}\]
-
-	We can prove some other properties of the arrows appearing in the diagram above.
-The three rectangles below are pushouts and their left halves are pushouts too.
-Therefore, by \Cref{lem:po1}, also their right halves are pushouts.
-	\[\xymatrix{K \ar@/^.4cm/[rr]^{u}\ar[d]_{r}\ar[r]_{u} &P\ar[d]^{p'} \ar[r]_{p} & D \ar[d]^{g}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{l'}\ar[r]_{u'} &P\ar[d]^{p} \ar[r]_{p'} & D' \ar[d]^{f'}\\  R \ar@/_.4cm/[rr]_{h} \ar[r]^{i_1}&D' \ar[r]^{f'} & H&L' \ar@/_.4cm/[rr]_{n'} \ar[r]^{i_2}&D \ar[r]^{g} & H}\]
-	\[ \xymatrix{K \ar@/^.4cm/[rr]^{k}\ar[d]_{l}\ar[r]_{u} &P\ar[d]^{q} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{r'}\ar[r]_{u'} &P\ar[d]^{q'} \ar[r]_{p'} & D' \ar[d]^{g'}\\ L \ar@/_.4cm/[rr]_{n} \ar[r]^{j}&Q \ar[r]^{s} & G&R' \ar@/_.4cm/[rr]_{h'} \ar[r]^{j'}&Q' \ar[r]^{t} & T}\]
-
-	Notice, moreover, that $p, q$ are the pushouts of $l'$ and $l$, respectively, thus they  are elements of $\mathcal{M}$. By \Cref{prop:pbpoad} the squares
-	\[\xymatrix{P\ar[r]^{p} \ar[d]_{p'} & D \ar[d]^{g}& P \ar[r]^{p} \ar[d]_{q} &D\ar[d]^{f}\\ D' \ar[r]_{f'} & H & Q \ar[r]_{s}& G}\]
-	are pullbacks too.
-\end{remark}
-
-Notice that if there is a filler between  $\dder{D}$ and $\dder{D}'$ are switchable, then they are weakly sequentially independent: indeed, if a filler between them exists, then $(i_1, i_2)$ is an independence pair.
-On the other hand, \Cref{ex:difficile} shows that not every independence pair arises in this way.
-
-\begin{definition}
-  \label{de:good-switchable}
-  Let $\dder{D}\colon H\Mapsto H$, $\dder{D}'\colon H\Mapsto T$ be two
-  direct derivations in a left-linear DPO-rewriting system $(\X,
-  \R)$. An independence pair $(i_1, i_2)$ between $\dder{D}$ and
-  $\dder{D}'$ is \emph{good} if there exists a filler $(u,u')$ between
-  them such that the squares below are
-  pushouts.\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K'
-      \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P
-      \ar[r]_{p} & D}\]
-
-We will say that $\dder{D}$ and $\dder{D}'$ are \emph{switchable} if a good independence pair between them exists.
-If such a pair is unique, we will say that $\dder{D}$ and $\dder{D}'$ are \emph{uniquely switchable}.
-We will use the notation $\dder{D}\updownarrow \dder{D'}$ to mean that $\dder{D}$ and $\dder{D}'$ are switchable, while $\dder{D}\updownarrow_!
-\dder{D'}$ will denote that they are uniquely so.
-
-If every independence pair is good we will say that $(\X, \R)$ is \emph{tame}.
-\end{definition}
-
-\begin{remark}\label{rem:unic} Given a good independence pair $(i_1, i_2)$ between $\dder{D}$ and $\dder{D}'$, there is a unique filler  such that $(u,u')$ such that 
-	\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} &K' \ar[r]^{l'} \ar[d]_{u'}& L'\ar[d]^{i_2} \\P \ar[r]_{p'}& D' & P \ar[r]_{p} & D}\]
-	are pushouts. Indeed, for every other filler $(v,v')$, it must be that
-	\[\begin{split}
-		p\circ u &=k \\&= p\circ v
-	\end{split}\qquad \begin{split}
-	p\circ u' &= i_2\circ l' \\&= p\circ v'
-	\end{split}\]
-	Since the arrow $p\colon P\to D$, which is the pullback of $f'$, is in $\mathcal{M}$ we conclude that $(u,u')=(v,v')$.
-\end{remark}
-
-\begin{remark}
-  Clearly in a tame left-linear DPO-rewriting system two direct derivations are sequentially independent if and only if they are unquely switchable.
-\end{remark}
-
-A source of tame left-linear DPO-rewriting systems is given by the linear ones, as shown by the following proposition.
-
-\begin{proposition}\label{prop:equi}Every linear DPO-rewriting system $(\X, \R)$ is tame.
- \end{proposition}
-\begin{proof} Suppose that $\X$ is $\mathcal{M}$-adhesive and let $(i_1, i_2)$ be an independence pair between $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$. We have a diagram
-	\[\xymatrix@C=15pt{L \ar[d]_{n}&& K \ar[d]_{k}\ar[ll]_{l} \ar[r]^{r} & R \ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_1} \ar[dr]|(.3)\hole_{h} && L' \ar@/_.35cm/[dlll]^(.4){i_2} \ar[dl]|(.3)\hole^{n'}& K' \ar[d]^{k'}\ar[l]_{l'} \ar[rr]^{r'} && R' \ar[d]^{h'}\\G && \ar[ll]^{f} D \ar[rr]_{g}&& H  && \ar[ll]^{f'} D' \ar[rr]_{g'}&& T}\]
-Pulling back $g$ along $f'$, we get another diagram 
-	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@{.>}@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@{.>}@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} && D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar[dl]^{h'}\\&G &&P\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T}\]
-Now, if we compute we get
-\[\begin{split}
-	f'\circ i_1\circ r &= h\circ r \\&= g\circ k
-\end{split}\qquad \begin{split}
-g\circ i_2\circ l' &= n'\circ l'\\&=f'\circ k'
-\end{split}\]
-Therefore the two dotted arrows $u\colon K\to P$ and $u'\colon K'\to P$ exist. We have to show that they satisfy the two conditions in the definition of a filler. 
-\begin{enumerate}
-	\item  By construction $p\circ u = k$ and $p'\circ u'=k'$. Since $(\X, \R)$ is linear, then $r'\colon K'\to R'$ belongs to $\mathcal{M}$, thus it admits a pushout along $u'\colon K'\to P$, as wanted.
-	\item Take the following two rectangles
-\[\xymatrix{K \ar@/^.4cm/[rr]^{u}\ar[d]_{r}\ar[r]_{u} &P\ar[d]^{p'} \ar[r]_{p} & D \ar[d]^{f}&K' \ar@/^.4cm/[rr]^{k'}\ar[d]_{l'}\ar[r]_{u'} &P\ar[d]^{p} \ar[r]_{p'} & D' \ar[d]^{f'}\\  R \ar@/_.4cm/[rr]_{h} \ar[r]^{i_1}&D' \ar[r]^{f'} & H&L' \ar@/_.4cm/[rr]_{n'} \ar[r]^{i_2}&D \ar[r]^{g} & H}\]
-	By hypothesis $r$ and $l'$ are in $\mathcal{M}$, thus $f'$ and $g$ belong to it too. The first point of \Cref{lem:popb}  yields the thesis. \qedhere 
-\end{enumerate}
-\end{proof}
-
-\begin{remark} \cite{baldan2011adhesivity} identifies a large class of (quasi)adhesive categories with the property that every left linear DPO-rewriting system on them is tame.
-We adapt these results to our context in \Cref{app:fill}.
-\end{remark}
-\begin{definition}[Very tameneness]
-	\todo{very tame}
-\end{definition}
-
-\begin{remark}
-	\todo{tutto coincide con tutto}
-\end{remark}
-
-We are now going to justify the choice of the name for the relation $\updownarrow$, showing that two switchable direct derivations $\dder{D}$ and $\dder{D'}$ can be actually switched.
-
-Let $(i_1, i_2)$ be a good independence pair and consider the following diagram: the solid part exists by the definition of a filler, while the two new dotted arrows $v\colon Q\to J$ and $v'\colon Q'\to J$ are obtained  as the pushout of $q\colon P\to Q$, which is in $\mathcal{M}$ by \Cref{rem:deco}, along $q'\colon P\to Q'$.
-	\[\xymatrix{&&R \ar@/_1cm/[ddrr]_(.35){i_1}|(.7)\hole \ar[dr]^{h}&& L'\ar@/^1cm/[ddll]^(.35){i_2}  \ar[dl]_{n'}\\&K\ar[dr]^{k}\ar[dl]_{l} \ar@/_.8cm/[ddrr]^(.65){u}\ar[ur]^{r}&& H && K' \ar@/^.8cm/[ddll]_(.65){u'}\ar[dl]_{k'}\ar[lu]_{l'} \ar[dr]^{r'}\\L \ar[dr]_{n} \ar@/_.8cm/[ddrr]_{j}&& D \ar[dl]|(.42)\hole_(.64){f}\ar[ur]|(.48)\hole^(.7){g}&&D' \ar[dr]|(.42)\hole^(.65){g'} \ar[ul]|(.48)\hole_(.7){f'}&&R'\ar@/^.8cm/[ddll]^{j'}\ar[dl]^{h'}\\&G &&P\ar[dr]^{q'} \ar[dl]_{q}\ar[ur]^(.4){p'}\ar[ul]_(.4){p}&&T\\&&Q \ar[ul]_{s}\ar@{.>}[dr]_{v} &&Q'\ar[ur]^{t} \ar@{.>}[dl]^{v'}\\&&&J}\]
-
-	Since, by \Cref{rem:deco}, all the curved rectangles are pushouts, as well as the bottom square, we can state the following definition.
-\begin{definition}\label{def:switch}
-	Let $(\X,R)$ be a left-linear DPO-rewriting system and suppose that $\X$ is $\mathcal{M}$-adhesive.
-Given a good independence pair $(i_1, i_2)$ between $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$, if $(u,u')$ is the associate filler, we define other two direct derivations $S_{i_1,i_2}(\dder{D}')\colon G\Mapsto J$ and $S_{i_1,i_2}(\dder{D})\colon J\Mapsto T$ as follows:
-		\[\xymatrix{L' \ar[d]_{f\circ i_2}& \ar[l]_{l'}K'\ar[d]_{q\circ u'} \ar[r]^{r'} & R' \ar[d]_{v'\circ j'} & L \ar[d]_{v\circ j} & \ar[l]_{l}K \ar[d]^{q'\circ u}\ar[r]^{r}& R \ar[d]^{g'\circ i_1}\\
-		G &\ar[l]^{s} Q \ar[r]_{v}& J&J & \ar[l]^{v'}Q' \ar[r]_{t} & T}\]
-	The \emph{switching} $\sder{D}{D'}$ of $\dder{D}$ and $\dder{D'}$ is the derivation $S_{i_1,i_2}(\dder{D}')\cdot S_{i_1,i_2}(\dder{D})$.
-\end{definition}
-
-\begin{remark}\label{rem:indip}Notice that $(j', j)$ is an independence pair for $S_{i_1,i_2}(\dder{D}')$ and $S_{i_1,i_2}(\dder{D})$.
-This is witnessed by the following diagram, commutative by construction.
-	\[\xymatrix@C=15pt{L' \ar[d]_{f\circ i_2}&& K' \ar[d]_{q\circ u'}\ar[ll]_{l'} \ar[r]^{r'} & R' \ar@/^.35cm/[drrr]_(.4){j'}|(.285)\hole \ar[dr]|(.28)\hole_{v'\circ j'} && L \ar@/_.35cm/[dlll]^(.4){j} \ar[dl]|(.28)\hole^{v\circ j}& K \ar[d]^{q'\circ u}\ar[l]_{l} \ar[rr]^{r} && R \ar[d]^{g'\circ i_1}\\G && \ar[ll]^{s} Q \ar[rr]_{v}&& J  && \ar[ll]^{v'} Q' \ar[rr]_{t}&& T}\]
-\end{remark}
-
-\begin{theorem}[Local Church-Rosser Theorem]\label{prop:fil}Let $(\X, \R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Then every filler between two direct derivations $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$ is a filler also for $S_{u,u'}(\dder{D'})\colon G\Mapsto J$ and $S_{u,u'}(\dder{D})\colon J\Mapsto H$.
-In particular, if $\dder{D}\updownarrow \dder{D}'$, then $S_{u,u'}(\dder{D}')\updownarrow S_{u,u'}(\dder{D})$.
-\end{theorem}
-\begin{proof}By definition of filler, we have two pushout square
-		\[\xymatrix{K \ar[r]^{l} \ar[d]_{u}& L \ar[d]^{j} & K' \ar[r]^{r'} \ar[d]_{u'} & R' \ar[d]^{j'}\\ P \ar[r]_q & Q & P \ar[r]_{q'} & Q'}\]
-		In particular, $q$ is an arrow of $\mathcal{M}$, therefore, by \Cref{prop:pbpoad}, the square below is a pullback.
-		\[\xymatrix{P \ar[r]^{q} \ar[d]_{q'}& Q\ar[d]^{v}\\ Q' \ar[r]_{v'} & J}\]
-		To prove our claim, it is now enough to show that $(u',u)$ is a filler between $S_{u,u'}(\dder{D}')$ and $S_{u, u'}(\dder{D})$.
-		\begin{enumerate}
-			\item As for the first  point of \Cref{def:filler}, the only non obvious part is the existence of a pushout of $u$ along $r$.
-But, since $(u,u')$ is a filler between $\dder{D}$ and $\dder{D'}$, we know that such a pushout exists: it is enough to take the square
-			\[\xymatrix{K \ar[r]^{r} \ar[d]_{u}& R \ar[d]^{i_1} \\P \ar[r]_{p'}& D'}\]
-			\item For the second point, notice that the arrows $j$ and $j'$ fit in the squares
-	\[\xymatrix{K' \ar[r]^{r'} \ar[d]_{u'}& R' \ar[d]^{j'} &K \ar[r]^{l} \ar[d]_{u}& L\ar[d]^{j} \\P \ar[r]_{q}& Q& P \ar[r]_{q'} & Q'}\] 
-		\end{enumerate}
-
-By \Cref{rem:indip} we know that $(j,j')$ is an independence pair. The results above now implies that $(j,j')$ is good.
-\end{proof}
-
-The previous remark allow us to further switch the direct derivation $S_{i_1,i_2}(\dder{D})$ and $S_{i_2,i_2}(\dder{D}')$.
-The following lemma guarantees us that, in this way, we get back a derivation which is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
-
-\todo{introdurre decorazione}
-
-\begin{lemma}\label{lem:rev}
-	Let $\dder{D}\colon G\Mapsto H$ and $\dder{D}'\colon H\Mapsto T$ be two direct derivations in a left-linear DPO-rewriting system $(\X, \R)$ and let $(i_1,i_2)$ be a good independence pair between them.
-Then $S_{j',j}(S_{i_1,i_2}(\dder{D}, \dder{D'}))$ is abstraction equivalent to $\dder{D}\cdot \dder{D}'$.
-\end{lemma}
-\begin{proof}Let $(u,u')$ be the filler associated to $(i_1, i_2)$.
-By \Cref{prop:fil}, $(u', u)$ is a filler between $S_{i_1,i_2}(\dder{D}')$ and $S_{i_1,i_2}(\dder{D})$.
-Thus we have a diagram as the one below.
-		\[\xymatrix{&&R' \ar@/_1cm/[ddrr]_(.35){j'}|(.7)\hole \ar[dr]^{v'\circ j'}&& L \ar@/^1cm/[ddll]^(.35){j}  \ar[dl]_{v\circ j}\\&K'\ar[dr]^{q\circ u'}\ar[dl]_{l'} \ar@/_.8cm/[ddrr]^(.65){u'}\ar[ur]^{r'}&& J && K \ar@/^.8cm/[ddll]_(.65){u}\ar[dl]_{q'\circ u}\ar[lu]_{l} \ar[dr]^{r}\\L' \ar[dr]^{f\circ i_2} \ar@/_.8cm/[ddrr]_{c_2}&& Q \ar[dl]|(.42)\hole_(.64){s}\ar[ur]|(.48)\hole^(.7){v}&&Q' \ar[dr]|(.42)\hole_(.65){t} \ar[ul]|(.48)\hole_(.7){v'}&&R\ar@/^.8cm/[ddll]^{c_1}\ar[dl]_{g'\circ i_1}\\&G &&P\ar[dr]^{e} \ar[dl]_{e'}\ar[ur]^(.4){q'}\ar[ul]_(.4){q}&&T\\&&E' \ar[ul]_{a}\ar[dr]_{w'} &&E\ar[ur]^{b} \ar[dl]^{w}\\&&&F}\]
-
-	Now, to ease the notation, let $S_{j',j}(S_{i_1,i_2}(\dder{D}, \dder{D'}))$ be $\dder{E}_0\cdot \dder{E}_1$, then $\dder{E}_0$ and $\dder{E}_1$ are the direct derivations given by the diagrams
-	\[\xymatrix{L \ar[d]_{s\circ j}& K\ar[l]_{l} \ar[r]^{r} \ar[d]_{e'\circ u} & R \ar[d]_{w\circ c_1} & L' \ar[d]^{w'\circ c_2}& K' \ar[d]^{e\circ u'} \ar[r]^{r'} \ar[l]_{l'}& R' \ar[d]^{t\circ j'}\\G & E' \ar[l]^{a}  \ar[r]_{w'}& F & F & E \ar[l]^{w} \ar[r]_{b} & R}\]
-
-	Notice, moreover, that, since the squares
-	\[\xymatrix{K' \ar[d]_{u'} \ar[r]^{l'}& L' \ar[d]^{c_2} & K \ar[r]^{r}\ar[d]_{u} & R \ar[d]^{c_1}\\ P \ar[r]_{e'} & E' & P\ar[r]_e & E}\]
-	are pushouts, we have isomorphisms  $\phi'\colon D\to E'$, $\phi\colon D'\to E$ making the following diagrams commutative.
-	\[\xymatrix{K' \ar[d]_{u'} \ar[r]^{l'}& L'\ar[d]^{i_2}  \ar@/^.2cm/[dr]^{c_2} & &K \ar[r]^{r}\ar[d]_{u} & R \ar[d]^{i_1} \ar@/^.2cm/[dr]^{c_1}\\ P \ar@/_.4cm/[rr]_{e'}\ar[r]^{p} & D\ar@{.>}[r]^{\phi'} &E'& P\ar@/_.4cm/[rr]_{e}\ar[r]^{p'} & D'\ar@{.>}[r]^{\phi}& E}\]
-	In particular, we have
-	\[\begin{split}
-		a\circ \phi' \circ i_2&=a \circ c_2\\&=f\circ i_2\\&
-	\end{split}\quad \begin{split}
-	a\circ \phi' \circ p'&=a \circ e'\\&=s\circ q\\&=f\circ p
-	\end{split}\quad \begin{split}
-	b\circ \phi \circ i_1&=b \circ c_1\\&=g'\circ i_1\\&
-	\end{split}\quad \begin{split}
-	b\circ \phi \circ p&=b \circ e\\&=t\circ q'\\&=g'\circ p'
-	\end{split} \]
-	and this shows that 
-	\[a\circ \phi'=f \qquad b\circ \phi = g'\]
-	Now, since $\phi'$ is an isomorphism and by \Cref{prop:pbpoad}, the two halves of the rectangle
-	\[\xymatrix{K\ar[r]^{\id{K}} \ar[d]_{(\phi')^{-1} \circ e' \circ u}&K\ar[d]_{e'\circ u} \ar[r]^{l} & L \ar[d]^{s\circ j} \\D\ar[r]_{\phi'} & E' \ar[r]_{a}&G}\]
-	are pullbacks.
-Thus the whole diagram is a pullback.
-But, by construction $s\circ j =n$ and we have already proved that $a\circ \phi'=f$.
-We then conclude that ther exists an isomorphism $\zeta\colon K\to K$ which makes the diagram below commutative
-	\[\xymatrix{K \ar@{.>}[r]_{\zeta}\ar@/^.4cm/[rr]^{l}  \ar@/_.5cm/[dr]_{(\phi')^{-1} \circ e' \circ u}& K \ar[r]_{l} \ar[d]_{n} & L \ar[d]^{n} \\ & D \ar[r]_{f} & G}\]
-	The commutativity of the upper triangle entails $l\circ \zeta=l$. Since $l$ is an element of $\mathcal{M}$  we can deduce that. $\zeta=\id{K}$. From this, we conclude that
-	\[e'\circ u = \phi' \circ k\]
-
-	As a next step, notice the existence of $\phi$ and $\phi'$, together with \Cref{rem:deco}, entails  the existence of a third isomorphism $\psi\colon H\to F$ fitting in the diagram below.
-	\[\xymatrix{P  \ar[d]^{p'}\ar@/_.4cm/[dd]_{e}\ar@/^.4cm/[rr]^{e'} \ar[r]_{p} & D \ar[d]^{g} \ar[r]_{\phi'} & E'\ar[d]^{w'}\\D' \ar[d]^{\phi} \ar[r]_{f'} & H\ar@{.>}[r]^{\psi} & F \\E \ar@/_.4cm/[urr]_{w}}\]
-Now, if we compute, we get
-\begin{align*}
-	\psi^{-1}\circ w\circ c_1&=f'\circ \phi^{-1}\circ c_1\\&=f'\circ i_1\\&=h
-\end{align*}
-	Summing up, we have just build the diagram below.	
-	\[\xymatrix@C=40pt@R=10pt{ &&&R\ar[dddr]^{w\circ c_1} \ar[dddl]_{h}|(.67)\hole\\&&K \ar[dl]_{l} \ar[ur]^{r}\ar[dddr]^{e'\circ u} \ar[dddl]_{k}|(.67)\hole\\&L\ar[dddr]^(.4){s\circ j} \ar[dddl]_(.4){n}\\&&H \ar[rr]^{\psi} && F\\ & D \ar[ur]_(.7){g} \ar[rr]^{\phi'} \ar[dl]_{f}&& E' \ar[ur]_{w'}\ar[dl]^{a}\\ G \ar[rr]_{\id{G}} && G}\]
-
-Next, we already know that
-\[t\circ j'= h' \quad w\circ \phi = \psi \circ f' \quad b\circ \phi = g'\]
-If we compute further, we also get
-\[\begin{split}
-	\psi^{-1}\circ w'\circ c_2 &= g\circ (\phi')^{-1}\circ c_2\\&=g\circ i_2\\&=n'
-\end{split}\qquad \begin{split}
-\phi^{-1}\circ e \circ u'&=p'\circ u'\\&= k'\\&
-\end{split}\]
-These equations allow us to conclude that the following diagram commutes.
-	\[\xymatrix@C=40pt@R=10pt{ &&&R'\ar[dddr]^{t\circ j'} \ar[dddl]_{h'}|(.67)\hole\\&&K' \ar[dl]_{l'} \ar[ur]^{r}\ar[dddr]^{e\circ u'} \ar[dddl]_{k}|(.67)\hole\\&L'\ar[dddr]^(.4){w'\circ c_2} \ar[dddl]_(.4){n'}\\&&T \ar[rr]^{\id{T}} && T\\ & D' \ar[ur]_(.7){g'} \ar[rr]^{\phi} \ar[dl]_{f'}&& E \ar[ur]_{b}\ar[dl]^{w}\\ H \ar[rr]_{\psi} && F}\]
-
-Putting together the two diagrams above we get the thesis. \qedhere 
-\end{proof}
-
-Our next step is to relate derivations which are equal ``up to switching''.
-
-\begin{definition}
-  \label{de:switchable}
-  Let $(\X, \R)$ be a left-linear DPO-rewriting system. Given two
-  direct derivations $\dder{D}\colon G\Mapsto H$ and
-  $\dder{D}'\colon H\Mapsto T$, we say that $\dder{D}$ and $\dder{D}'$
-  are \emph{properly switchable} if $\dder{D}\updownarrow_! \dder{D'}$
-  and $S_{i_1,i_2}(\dder{D}')\updownarrow_!S_{i_1,i_2}(\dder{D})$,
-  where $(i_2,i_2)$ is a good independence pair betwwen $\dder{D}$ and
-  $\dder{D}'$. In such a case, we will write
-  $\dder{D}\Updownarrow\dder{D}'$.
-
-Take two derivations $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and $\der{D}'=\{\dder{D}'_{i}\}_{i=0}^n$ with the same length and between the same $G_0$ and $G_n$.
-We say that $\der{D}'$ is \emph{obtained by a proper switch from $\der{D}$} if there exists an index $j < n$ such that
-	\begin{enumerate}
-\item for every $i\notin \{j, j+1\} $, $\dder{D}_i=\dder{D}'_i$;
-\item $\dder{D}_j \Updownarrow \dder{D}_{j+1}$;		
-\item $\dder{D}'_j\cdot \dder{D}'_{j+1} = S_{i_1,i_2}(\dder{D}, \dder{D}')$.
-	\end{enumerate}
-	In such a case, we will write $\der{D}\rightsquigarrow_j \der{D}'$ to denote that $\der{D}'$ is obtained by a proper switch between $\dder{D}_j$ and $\dder{D}_{j+1}$.
-
-	We will say that $\der{D}$ is \emph{switch equivalent} to $\der{D}'$, if there exists a sequence, $\{\der{D}_i\}_{i=0}^n$ of derivations such that
-	\begin{enumerate}
-		\item $\der{D}_0=\der{D}$ and $\der{D}_n=\der{D}'$;
-		\item for every $i< n$, $\der{D}_{i+1}$ is obtained by a proper switch from $\der{D}_i$.
-	\end{enumerate}
-
-	We will write $\der{D} \equiv^s \der{D}'$ to denote that $\der{D}$ is switch equivalent to $\der{D}'$.
-\end{definition}
-
-\begin{example}
-	\todo{il punto due sopra è necessario}
-\end{example}
-
-We can now prove some properties of switch equivalence.
-\begin{lemma}\todo{Def. 3 della bozza di Andrea }Let $(\X, \R)$ be a left-linear DPO-rewriting system. Then the following hold true: 
-	\begin{enumerate}
-		\item 
-		\item 
-		\item 
-		\item 
-	\end{enumerate}
-\end{lemma}
-\begin{proof}\begin{enumerate}
-		\item 
-		\item 
-		\item 
-		\item \qedhere 
-	\end{enumerate}
-\end{proof}
-
-\begin{example}\todo{esempio sul perché weakly independence non è invertibile}
-\end{example}
-
-\begin{lemma}\label{lem:consperm} Let $(\X, \R)$ be a left-linear DPO-rewriting system $(\X, \R)$. Then the following hold true
-	\begin{enumerate}
-		\item If $\dder{D}$ and $\dder{D'}$ are two direct derivations such that $\dder{D}\updownarrow \dder{D'}$, then for every filler $(u,u')$ between them, the function
-		\[\tau\colon 2\to2 \qquad x \mapsto \begin{cases}
-			1 & x=0\\
-			0 & x=1
-		\end{cases}\]
-		defines a consistent permutation between $\dder{D}\cdot \dder{D}'$ and $\sder{D}{D'}$;
-		\item if $\der{D}$ and $\der{D}'$ are two switch equivalent derivation, then there exists a consistent permutation between them.
-	\end{enumerate}
-\end{lemma}
-\begin{proof}
-	\begin{enumerate}
-		\item 
-		\item \qedhere 
-	\end{enumerate}
-\end{proof}
- This, together with ???
-\begin{corollary}
-	\todo{unicità}
-\end{corollary}
-
-\begin{example}\label{ex:contro}\todo{permutazione consistente non implica scambiabilità}
-\end{example}
-
-\subsubsection{Graphical rewriting systems}\label{subsubsec:graphical}
-
-\todo{ci sono un sacco di sistemi very tame}
-\subsection{Switch equivalence}
-\todo{intro}
-
-\subsubsection{The $3$-steps lemmas}
-
-As a beginning step in our analysis of switch equivalence, we will establish three lemmas  dealing with derivations of length $3$.
-
-\begin{lemma}[First $3$-steps Lemma]\label{lem:primo}
-Let $(\X,\R)$ be a left-linear DPO-rewriting system.
-Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$ and suppose that $(i_0,i_1)$ is a good independence pair between $\dder{D}_0$ and $\dder{D}_1$, $(a_0,a_1)$ one between $\dder{D}_1$ and $\dder{D}_2$ and $(e_0, e_1)$ one between $\dder{D}_0$ and $S_{a_0,a_1}(\dder{D}_2)$.
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{lemma}[Second $3$-steps Lemma]\label{lem:secondo}
-	contenuto...
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{lemma}[Third $3$-steps Lemma]\label{lem:terzo}
-	contenuto...
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\todo{dividere in due il lemma dopo. devono venire tre lemmi}
-\begin{lemma}[Three steps Lemma]\label{lem:iig1}Let $(\X,\R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$ and suppose that $(i_0,i_1)$ is a good independence pair between $\dder{D}_0$ and $\dder{D}_1$, $(a_0,a_1)$ one between $\dder{D}_1$ and $\dder{D}_2$ and $(e_0, e_1)$ one between $\dder{D}_0$ and $S_{a_0,a_1}(\dder{D}_2)$.
-Then the following properties hold true.
-	\begin{enumerate}
-		\item $S_{e_0,e_1}(\dder{D}_0)$ and $S_{a_0,a_1}(\dder{D}_1)$ are weakly sequentially independent.
-		\item If $S_{i_0, i_1}(\dder{D}_0)\updownarrow_!
-\dder{D}_2$ with a good independence pair $(\alpha_0, \alpha_1)$, then  $S_{i_0,i_1}(\dder{D}_1)$ and $S_{\alpha_0, \alpha_1}(\dder{D}_2)$ are weakly sequentially independent.
-	\end{enumerate}
-
-\end{lemma}
-\begin{proof}  As a preliminary step, we are going to use \Cref{def:filler,def:switch} to get some diagrams.
-First of all, let $(v,v')$ be the filler between $\dder{D}_0$ and $\dder{D}_1$ associated to $(i_0, i_1)$, then we have
-	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&H'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
-
-	Secondly, the filler $(u,u')$ induced by $(a_0, a_1)$ between $\dder{D}_1$ and $\dder{D}_2$ yields:
-	\[
-	\xymatrix{&&R_1 \ar@/_1cm/[ddrr]_(.35){a_0}|(.7)\hole \ar[dr]^{h_1}&& L_2\ar@/^1cm/[ddll]^(.35){a_1}  \ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar[dl]_{l_1} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){u}\ar[ur]^{r_1}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){u'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_1 \ar@/_.8cm/[ddrr]_(.2){b_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_1}|(.61)\hole && D_1 \ar[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){b_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_2}\\&G_1 &&P_2\ar[dr]_{d_1} \ar[dl]^{d_0}\ar[ur]^(.4){c_1}\ar[ul]_(.4){c_0}&&G_3\\L_2 \ar@/^.8cm/[uurr]^(.2){a_1} \ar[ur]_(.35){f_1\circ a_1}|(.61)\hole&&Q_2 \ar[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1} &&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar[dl]|(.5)\hole_(.65){x_2} && R_1  \ar[ul]^(.35){g_2\circ a_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){a_0}\\&K_2 \ar[ur]_{d_0\circ u'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){u'}&&G'_2&& K_1 \ar[ur]_{r_1} \ar[ul]^{d_1\circ u} \ar[dl]^{l_1} \ar@/_.8cm/[uull]^(.65){u}\\&& R_2 \ar[ur]_{\hspace{-5pt}x_2\circ b_1}\ar@/^1cm/[uurr]^(.25){b_1}&& L_1 \ar[ul]^{y_1\circ b_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){b_0} |(.69)\hole }\]
-
-	Finally, the filler $(w,w')$  between $\dder{D}_0$ and $S_{a_0,a_1}(\dder{D}_2)$ given by $(e_0, e_1)$ provides us with:
-\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){e_0}|(.7)\hole \ar[dr]^{h_0}&& L_2\ar@/^1cm/[ddll]^(.35){e_1}  \ar[dl]_{f_1\circ a_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){w}\ar[ur]^{r_0}&& G_1 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){w'}\ar[dl]_{d_0\circ u'\hspace{-5pt}}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_0 \ar@/_.8cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2 \ar[dr]|(.4)\hole^(.65){y_1} \ar[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.8cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){x_2\circ b_1}\\&G_0 &&P_3\ar[dr]_{n_1} \ar[dl]^{n_0}\ar[ur]^(.4){u_1}\ar[ul]_(.4){u_0}&&G'_2\\L_2 \ar@/^.8cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ e_1}|(.61)\hole&&Q_4 \ar[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0} &&Q_5\ar[ur]|(.4)\hole^(.65){z'_1} \ar[dl]|(.5)\hole_(.65){z_1} && R_0  \ar[ul]^(.35){y_1\circ e_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){e_0}\\&K_2 \ar[ur]_{n_0\circ w'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){w'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{n_1\circ w} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){w}\\&& R_2 \ar[ur]_{\hspace{-4pt}z_1\circ o_1}\ar@/^1cm/[uurr]^(.25){o_1}&& L_0 \ar[ul]^{z'_0\circ o_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){o_0} |(.69)\hole }\]
-So equipped we can turn to the prove of our claims.	
-	\begin{enumerate}
-		\item We have to construct the two dotted arrows in the diagram below.
-			\[\xymatrix@C=15pt{L_0 \ar[d]_{z'_0\circ o_0}&& K_0 \ar[d]_{n_1\circ w}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@{.>}@/^.35cm/[drrr]_(.4){\beta_0}|(.285)\hole \ar[dr]|(.28)\hole_{y_1\circ e_0} && L_1 \ar@{.>}@/_.35cm/[dlll]^(.4){\beta_1} \ar[dl]|(.28)\hole^{y_1\circ b_0}& K_1 \ar[d]^{d_1\circ u}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ a_1}\\G'_1 && \ar[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2  && \ar[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_3}\]
-
-		Consider the arrows $i_0\colon R_0\to D_1$ and $e_0\colon R_0\to Q_2$. An easy computation shows that
-			\begin{align*}
-				f_1\circ i_0&= h_0\\&=x_1\circ e_0
-			\end{align*}
-			entailing the existence of  the dotted $\beta'_0\colon R_0\to P_2$ in the diagram
-			\[\xymatrix{R_0 \ar@{.>}[dr]^{\beta'_0} \ar@/^.3cm/[drr]^{i_0} \ar@/_.3cm/[ddr]_{e_0}\\ &P_2 \ar[r]^{c_1} \ar[d]_{d_0}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
-			If we define $\beta_0\colon R_0\to Q_3$ as $d_1\circ \beta'_1$, then we easily get that 
-		\begin{align*}
-			x_2\circ \beta_0&=x_2\circ d_2\circ \beta'_0\\&= y_1\circ d_0\circ \beta'_0\\&=y_1\circ e_0
-		\end{align*}
-
-		To define $\beta_1$, we proceed similarly. First consider  $i_1\colon L_1\to D_0$ and $b_0\colon L_1 \to Q_2$ and notice that
-		\begin{align*}
-			g_0\circ i_1&= m_1 \\&= x_1 \circ b_0
-		\end{align*}
-			implying the existence of $\beta'_1\colon L_1\to P_3$ fitting in the diagram below.
-			\[\xymatrix{L_1 \ar@{.>}[dr]^{\beta'_1} \ar@/^.3cm/[drr]^{i_1} \ar@/_.3cm/[ddr]_{b_0}\\ &P_3 \ar[r]^{u_0} \ar[d]_{u_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar[r]_{x_1} & G_1}\] 
-			Let $\beta_1\colon L_1\to Q_5$ be $n_1\circ \beta'_1$, then
-			\begin{align*}
-				z'_1 \circ \beta_1 & = z'_1 \circ n_1\circ \beta'_1\\&=y_1\circ u_1\circ \beta'_1\\&=y_1\circ b_0
-			\end{align*}
-		Therefore, $(\beta_0, \beta_1)$ is the wanted independence pair.
-
-\item  In addition to the three diagram above, we have a fourth one given by the filler $(\varphi_0, \varphi_1)$ associated to $(\alpha_0, \alpha_1)$. 
-\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){\alpha_0}|(.7)\hole \ar[dr]^{g_1\circ i_0}&& L_2\ar@/^1cm/[ddll]^(.35){\alpha_1}  \ar[dl]_{m_2}\\
-&K_0\ar[dr]^{\hspace{-4pt}q_1\circ v}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){\varphi}\ar[ur]^{r_0}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){\varphi'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\
-L_0 \ar@/_.8cm/[ddrr]_(.2){\gamma_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){\hspace{-4pt}t_0\circ j_0}|(.61)\hole && Q_1 \ar[dl]|(.4)\hole_(.65){s_1}\ar[ur]|(.5)\hole^(.7){t_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){\gamma_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){h_2}\\&H'_1 &&P_4\ar[dr]_{\lambda_1} \ar[dl]^{\lambda_0}\ar[ur]^(.4){\zeta_1}\ar[ul]_(.4){\zeta_0}&&G_3\\
-L_2 \ar@/^.8cm/[uurr]^(.2){\alpha_1} \ar[ur]_(.35){s_1\circ \alpha_1}|(.61)\hole&&Q_6 \ar[ul]|(.4)\hole_(.65){\xi_0}\ar[dr]|(.5)\hole^(.65){\xi'_0} &&Q_7\ar[ur]|(.4)\hole^(.65){\xi'_1} \ar[dl]|(.5)\hole_(.65){\xi_1} && R_0  \ar[ul]^(.35){g_2\circ \alpha_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){\alpha_0}\\&K_2 \ar[ur]_{\lambda_0\circ \phi'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){\phi'}&&H'_2&& K_0 \ar[ur]_{r_0} \ar[ul]^{\lambda_1\circ \phi} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){\phi}\\&& R_2 \ar[ur]_{\hspace{-4pt}\xi_1\circ \gamma_1}\ar@/^1cm/[uurr]^(.25){\gamma_1}&& L_0 \ar[ul]^{\xi'_0\circ \gamma_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){\gamma_0} |(.69)\hole }\]
-
-Our aim is to construct the dotted arrow in the following diagram.
-		\[\xymatrix@C=15pt{L_1 \ar[d]_{f_0\circ i_0}&& K_1 \ar[d]_{q_0\circ v'}\ar[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@{.>}@/^.35cm/[drrr]_(.4){\epsilon_0}|(.285)\hole \ar[dr]|(.28)\hole_{s_1\circ j_1} && L_2 \ar@{.>}@/_.35cm/[dlll]^(.4){\epsilon_1} \ar[dl]|(.28)\hole^{s_1\circ \alpha_1}& K_2 \ar[d]^{\lambda_0\circ \phi'}\ar[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]^{\xi_1\circ \gamma_1}\\G_0 && \ar[ll]^{s_0} Q_0 \ar[rr]_{t_0}&& H'_1  && \ar[ll]^{\xi_0} Q_6 \ar[rr]_{\xi'_0}&& H'_2}\]
-
-Let us start considering $j_1\colon R_1\to Q_1$ and $a_0\colon R_1\to D_2$. We have
-\begin{align*}
-	f_2\circ a_0&=h_1\\&=t_1\circ j_1
-\end{align*}
-and thus we get an arrow $\epsilon'_0\colon R_1\to P_4$ which makes the diagram below commutative.
-			\[\xymatrix{R_1 \ar@{.>}[dr]^{\epsilon'_0} \ar@/^.3cm/[drr]^{j_1} \ar@/_.3cm/[ddr]_{a_0}\\ &P_4 \ar[r]^{\zeta_0} \ar[d]_{\zeta_1}& Q_1 \ar[d]^{t_1}\\ &D_2\ar[r]_{f_2} & G_2}\] 
-We can then define $\epsilon_0\colon R_1\to Q_6$ to be $\lambda_0\circ \epsilon'_0$. For such an arrow we have a chain of identities:
-\begin{align*}
-	\xi_0\circ \epsilon_0&=\xi_0\circ \lambda_0\circ \epsilon'_0\\&=s_1\circ \zeta_0 \circ \epsilon'_0\\&=s_1\circ j_1
-\end{align*}
-
-Next, to define $\epsilon_1\colon L_2\to Q_0$ we take $e_1\colon L_2 \to D_0$ and $a_1\colon L_2\to D_1$. By definition we have $	g_0\circ e_1=f_1\circ a_1$, giving us the dotted arrow below
-	\[\xymatrix{L_2 \ar@{.>}[dr]^{\epsilon'_1} \ar@/^.3cm/[drr]^{a_1} \ar@/_.3cm/[ddr]_{e_0}\\ &P_1 \ar[r]^{p_1} \ar[d]_{p_0}& D_1 \ar[d]^{f_1}\\ &D_0\ar[r]_{g_0} & G_1}\] 
-Now, notice that 
-\begin{align*}
-	t_1\circ q_1\circ \epsilon'_1&=g_1\circ p_1\circ \epsilon'_1&=g_1\circ a_1\\&=m_2
-\end{align*}
-Hence $(\alpha_0, q_1\circ \epsilon'_1)$ is an independence pair for $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$.
-By hypothesis $S_{i_0, i_1}(\dder{D}_0)\updownarrow_!
-\dder{D}_2$ and thus $q_1\circ \epsilon'_1$ must coincide with $\alpha_1$.
-Now, let $\epsilon_1\colon L_2\to Q_0$ be $q_0\circ \epsilon'_1$.
-Computing we get
-\begin{align*}
-t_0\circ \epsilon_1&= t_0\circ q_0\circ \epsilon'_1\\&=s_1\circ q_1\circ \epsilon'_1\\&=s_1\circ \alpha_1
-\end{align*}
-Allowing us to conclude that  $S_{i_0,i_1}(\dder{D}_1)\updownarrow S_{\alpha_0, \alpha_1}(\dder{D}_2)$.
-\qedhere 
-			\end{enumerate}
-\end{proof}
-
-\subsubsection{Inversions and switch equivalence}
-\todo{richiamare cosa sono le inversioni}
-
-\begin{lemma}[Fundamental Lemma] Let $(\der{D}, \alpha, \omega)$ and $(\der{D'}, \alpha, \omega)$ be two decorated derivations and suppose that there exists a non-empty sequence $\{\der{D}_i\}_{i=0}^n$ a of derivations witnessing $\der{D}\equiv^s \der{D}'$.
-For every $i\in [0,n-1]$, let $\nu_i\colon [0, \lgh(\der{D})-1]\to [0, \lgh(\der{D})-1]$ be the $2$-cycle associated to the switch between $\der{D}_i$ and $\der{D}_{i+1}$, let also $\sigma$ be the associated consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
-Define $k$ as the maximum of the set
-\[M_\sigma:=\{j\in [0, \lgh(\der{D}-1] \mid \sigma(j+1) < \sigma(j) \}\]
-If every $\nu_i$ is an inversion for $\sigma$, then there exists a family $\{\nu'_i\}_{i=0}^n$ of inversions for $\sigma$ such that jj\todo{capire come scriverlo meglio, l} $\nu'_0=(k, k+1)$.
-\end{lemma}
-\begin{remark}
-	Since $\{\der{D}_i\}_{i=0}^n$ is non-empty, then $\sigma$ must be different from $\id{[0, \lgh(\der{D}-1)]}$ and $M_{\sigma}\neq \emptyset$.
-\end{remark}
-\begin{proof}
-	We proceed by induction on $n$.
-
-	\smallskip\noindent $n=1$. In this case there is nothing to prove.
-
-	\smallskip \noindent $n>1$. Then...
-\end{proof}
-
-\begin{corollary}
-	contenuto...
-\end{corollary}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{corollary}
-	contenuto...
-\end{corollary}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{corollary}
-	contenuto...
-\end{corollary}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{corollary}[No need for useless shifts]
-	contenuto...
-\end{corollary}
-\begin{proof}
-	contenuto...
-\end{proof}
-\newpage
-
-NOTES ON THE FUNDAMENTAL LEMMA WE NEED\todo{da integrare sopra}
-
-Everything is very tame, so that sequential independence coincides with switchability and we do not have ambiguity in the choice of an independence pair
-
-We start with the following situation.
-	\[\xymatrix@C=15pt{L_0\ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]_(.4){i_0}|(.285)\hole \ar[dr]|(.28)\hole_{h_0} && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.28)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar[dr]|(.28)\hole_{h_1} \ar@/^.35cm/[drrr]_(.4){j_0}|(.285)\hole  && L_2 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.28)\hole^{m_2}& K_2 \ar[d]^{k_2}\ar[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]^{h_2} \\G_0 && \ar[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2 && \ar[ll]^{f_2} D_2 \ar[rr]_{g_2}&& G_3 }\]
-
-	We can do two things:
-
-	FIRST SEQUENCE OF SWITCHINGS:
-
-	Switch the first two
-
-	\[\xymatrix@C=15pt{L_1\ar[d]_{f_0\circ i_1}&& K_1 \ar[d]_{k'_1}\ar[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){a_0}|(.285)\hole \ar[dr]|(.28)\hole_{h'_1} && L_0 \ar@/_.35cm/[dlll]^(.4){a_1} \ar[dl]|(.28)\hole^{m'_0}& K_0 \ar[d]^{k'_0}\ar[l]_{l_0} \ar[r]^{r_0} & R_0 \ar[dr]|(.28)\hole_{g_1\circ j_0} \ar@/^.35cm/[drrr]_(.4){b_0}|(.285)\hole  && L_2 \ar@/_.35cm/[dlll]^(.4){b_1} \ar[dl]|(.28)\hole^{m_2}& K_2 \ar[d]^{k_2}\ar[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]^{h_2} \\G_0 && \ar[ll]^{f'_0} D'_0 \ar[rr]_{g'_0}&& G'_1  && \ar[ll]^{f'_1} D'_1 \ar[rr]_{g'_1}&& G_2 && \ar[ll]^{f_2} D_2 \ar[rr]_{g_2}&& G_3 }\]
-
-	Moreover, we know that
-	\[m_0=f'_0\circ a_1 \qquad h_1=g'_1\circ a_0\]
-
-	Switch second and third 
-	\[\xymatrix@C=15pt{L_1\ar[d]_{f_0\circ i_1}&& K_1 \ar[d]_{k'_1}\ar[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){c_0}|(.285)\hole \ar[dr]|(.28)\hole_{h'_1} && L_2 \ar@/_.35cm/[dlll]^(.4){c_1} \ar[dl]|(.28)\hole^{f'_1\circ b_1}& K_2 \ar[d]^{k'_2}\ar[l]_{l_2} \ar[r]^{r_2} & R_2 \ar[dr]|(.28)\hole_{h'_2} \ar@/^.35cm/[drrr]_(.4){d_0}|(.285)\hole  && L_0 \ar@/_.35cm/[dlll]^(.4){d_1} \ar[dl]|(.28)\hole^{\hat{m}_0}& K_0 \ar[d]^{\hat{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]^{g_2\circ b_0} \\G_0 && \ar[ll]^{f'_0} D'_0 \ar[rr]_{g'_0}&& G'_1  && \ar[ll]^{\hat{f}_1} \hat{D}_1 \ar[rr]_{\hat{g}_1}&& G'_2 && \ar[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 }\]
-	And we know that
-	\[m'_0=\hat{f}_1\circ d_1 \qquad h_2=g'_2\circ d_0\]
-	\todo{qua abbiamo usato il secondo lemma dei tre passi (quello condizionale)}Since the rewriting system is very tame and using the three steps lemmas we can characterize $c_0\colon R_1\to \hat{D}_1$ and $c_1\colon L_2\to D'_0$ as the unique arrows fitting in the diagrams
-\[\xymatrix@R=15pt@C=15pt{&&R_1 \ar@/_1.2cm/[dddl]_(.4){a_0}|(.63)\hole\ar[dl]^{j_0}\ar[dd]^{c'_0} \ar@{.>}[dr]^{c_0}\\&D_2 \ar[dl]^(.4){f_2}&&\hat{D}_1 \ar[dr]^{\hat{g}_1}\\G_2 && P\ar[dr]_{p_4} \ar[ur]_{p_3}\ar[dl]^{p_1} \ar[ul]^{p_2}&&G'_2\\& D'_1 \ar[ul]^{g'_1}&&D'_2 \ar[ur]_{f'_2}}\]
-
-\[\xymatrix@R=15pt@C=15pt{&&L_2 \ar[dl]^{j_1} \ar@/_1.2cm/[dddl]_(.4){z_1}|(.63)\hole\ar[dd]^{c'_1} \ar@{.>}[dr]^{c_1}\\&D_1 \ar[dl]^(.4){f_1}&&D'_0 \ar[dr]^{g'_0}\\G_1 && Q\ar[dr]_{q_4} \ar[ur]_{q_3}\ar[dl]^{q_1} \ar[ul]_{q_2}&&G'_1\\& D_0 \ar[ul]^{g_0}&&D'_1 \ar[ur]_{f'_1}}\]
-
-	Switch first and second 
-	\[\xymatrix@C=15pt{L_2\ar[d]_{f'_0\circ c_1}&& K_2 \ar[d]_{\hat{k}_2}\ar[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){e_0}|(.285)\hole \ar[dr]|(.28)\hole_{\hat{h}_2} && L_1 \ar@/_.35cm/[dlll]^(.4){e_1} \ar[dl]|(.28)\hole^{\hat{m}_1}& K_1 \ar[d]^{\hat{k}_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){t_0} \ar[dr]|(.28)\hole_{\hat{g}_1\circ c_0}   && L_0  \ar[dl]|(.28)\hole^{\hat{m}_0} \ar@/_.35cm/[dlll]^(.4){t_1}& K_0 \ar[d]^{\hat{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]^{g_2\circ b_0} \\G_0 && \ar[ll]^{\hat{f}_0} \hat{D}_0 \ar[rr]_{\hat{g}_0}&& \hat{G}_1  && \ar[ll]^{\tilde{f}_1} \tilde{D}_1 \ar[rr]_{\tilde{g}_1}&& G'_2 && \ar[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 }\]
-	Moreover
-	\[f_0\circ i_1=\hat{f}_0\circ e_1 \qquad h'_2=\tilde{g}_1\circ e_0\]
-	and $(t_0, t_1)$ is characterized using again very tameness and the first $3$-steps Lemma as the unique arrows fitting in:
-	\[\xymatrix{&R_1 \ar[dl]_{a_0} \ar@{.>}[dr]^{t_0} \ar@/^.4cm/[dd]|\hole^(.6){c_0}\ar[d]_{t'_0}\\ D'_1 \ar[d]_{g'_1}&P\ar[d]_{p_3} \ar[r]^{p_4} \ar[l]_{p_1}&D'_2\ar[d]^{f'_2}\\G'_1&\hat{D}_1 \ar[l]^{\hat{f}_1}\ar[r]_{\hat{g}_1}& G'_2}\]
-
-	\[\xymatrix@R=15pt@C=15pt{&&L_ 0\ar[dl]^{a_1} \ar@/_1.2cm/[dddl]_(.4){d_1}|(.63)\hole\ar[dd]^{t'_1} \ar@{.>}[dr]^{t_1}\\&D'_0 \ar[dl]^(.4){g'_0}&&\tilde{D}_1 \ar[dr]^{\tilde{f}_1}\\G'_1 && S\ar[dr]_{s_4} \ar[ur]_{s_3}\ar[dl]^{s_1} \ar[ul]_{s_2}&&\hat{G}_1\\& \hat{D}_1 \ar[ul]^{\hat{f}_1}&&\hat{D}_0 \ar[ur]_{\hat{g}_0}}\]
-
-	SECOND SEQUENCE OF SWITCHINGS:
-
-	Switch third and second
-
-	\[\xymatrix@C=15pt{L_0\ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]_(.4){z_0}|(.285)\hole \ar[dr]|(.28)\hole_{h_0} && L_2 \ar@/_.35cm/[dlll]^(.4){z_1} \ar[dl]|(.28)\hole^{f_1\circ j_1}& K_2 \ar[d]^{\check{k}_2}\ar[l]_{l_2} \ar[r]^{r_2} & R_2 \ar[dr]|(.28)\hole_{\check{h}_2} \ar@/^.35cm/[drrr]_(.4){w_0}|(.285)\hole  && L_1 \ar@/_.35cm/[dlll]^(.4){w_1} \ar[dl]|(.28)\hole^{\check{m}_1}& K_1 \ar[d]^{\check{k}_1}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1\ar[d]^{g_2\circ j_0} \\G_0 && \ar[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar[ll]^{\check{f}_1} \check{D}_1 \ar[rr]_{\check{g}_1}&& \check{G}_2 && \ar[ll]^{\check{f}_2} \check{D}_2 \ar[rr]_{\check{g}_2}&& G_3 }\]
-	Moreover
-	\[m_1=\check{f}_1\circ w_1 \qquad h_2=\check{g}_2\circ w_0\]
-
-	Switch second and first
-		\[\xymatrix@C=15pt{L_2\ar[d]_{f_0\circ z_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){y_0}|(.285)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_0 \ar@/_.35cm/[dlll]^(.4){y_1} \ar[dl]|(.28)\hole^{\check{m}_0}& K_0 \ar[d]^{\check{k}_0}\ar[l]_{l_0} \ar[r]^{r_0} & R_0 \ar[dr]|(.28)\hole_{\check{g}_1\circ z_0} \ar@/^.35cm/[drrr]_(.4){x_0}|(.285)\hole  && L_1 \ar@/_.35cm/[dlll]^(.4){x_1} \ar[dl]|(.28)\hole^{\check{m}_1}& K_1 \ar[d]^{\check{k}_1}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1\ar[d]^{g_2\circ j_0} \\G_0 && \ar[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar[ll]^{\mathring{f}_1} \mathring{D}_1 \ar[rr]_{\mathring{g}_1}&& \check{G}_2 && \ar[ll]^{\check{f}_2} \check{D}_2 \ar[rr]_{\check{g}_2}&& G_3 }\]
-	As before we have
-	\[m_0=\check{f}_0\circ y_1 \qquad \check{h}_2=\mathring{g}_1\circ y_0\]
-	The really important thing to notice is that, by very tameness we have
-	\begin{align*}
-		f_0'\circ c_1&=f'_0\circ q_3\circ c'_1\\&=f_0\circ q_1\circ c'_1\\&=f_0\circ z_1
-	\end{align*}
-
-	\todo{GOOD! i primi match sono uguali, ora giochiamoci il primo lemma dei tre passi}
-
-	Switch second and third
-\[\xymatrix@C=15pt{L_2\ar[d]_{f_0\circ z_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){v_0}|(.285)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_1 \ar@/_.35cm/[dlll]^(.4){v_1} \ar[dl]|(.28)\hole^{\mathring{f}_1 \circ x_1}& K_1 \ar[d]^{\mathring{k}_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){u_0}|(.285)\hole\ar[dr]_{\check{h}_1}   && L_0 \ar@/_.35cm/[dlll]^(.4){u_1} \ar[dl]^{\mathring{m}_0}& K_0 \ar[d]^{\mathring{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0\ar[d]^{\check{g}_2\circ x_0} \\G_0 && \ar[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar[ll]^{\bar{f}_1} \bar{D}_1 \ar[rr]_{\bar{g}_1}&& \bar{G}_2 && \ar[ll]^{\bar{f}_2} \bar{D}_2 \ar[rr]_{\bar{g}_2}&& G_3 }\]
-
-\[\xymatrix@R=15pt@C=15pt{&&R_1 \ar@/_1.2cm/[dddl]_(.4){a_0}|(.63)\hole\ar[dl]^{j_0}\ar[dd]^{c'_0} \ar@{.>}[dr]^{c_0}\\&D_2 \ar[dl]^(.4){f_2}&&\hat{D}_1 \ar[dr]^{\hat{g}_1}\\G_2 && P\ar[dr]_{p_4} \ar[ur]_{p_3}\ar[dl]^{p_1} \ar[ul]^{p_2}&&G'_2\\& D'_1 \ar[ul]^{g'_1}&&D'_2 \ar[ur]_{f'_2}}\]
-
-\[\xymatrix@R=15pt@C=15pt{&&L_1 \ar[dl]^{w_1} \ar@/_1.2cm/[dddl]_(.4){i_1}|(.63)\hole\ar[dd]^{v'_1} \ar@{.>}[dr]^{v_1}\\&\check{D}_1 \ar[dl]^(.4){\check{f}_1}&&\check{D}_0 \ar[dr]^{g'_0}\\G_1 && \check{Q}\ar[dr]_{\check{q}_4} \ar[ur]_{\check{q}_3}\ar[dl]^{\check{q}_1} \ar[ul]_{\check{q}_2}&&\check{G}_1\\& D_0 \ar[ul]^{g_0}&&\mathring{D}_1 \ar[ur]_{\check{f}_1}}\]
-
-HUGE DIAGRAM
-
-\[\xymatrix@C=15pt{
-  & K_1 \ar[d]^{\hat{k}_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){t_0} \ar[dr]|(.28)\hole_{\hat{g}_1\circ c_0}   && L_0  \ar[dl]|(.28)\hole^{\hat{m}_0} \ar@/_.35cm/[dlll]^(.4){t_1}& K_0 \ar[d]^{\hat{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]^{g_2\circ b_0} \\G_0 && \ar[ll]^{\hat{f}_0} \hat{D}_0 \ar[rr]_{\hat{g}_0}&& \hat{G}_1  && \ar[ll]^{\tilde{f}_1} \tilde{D}_1 \ar[rr]_{\tilde{g}_1}&& G'_2 && \ar[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 \\
-	L_2\ar[d]_{f_0\circ z_1} \ar[u]^{f'_0\circ c_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/_.35cm/[urrr]^(.4){e_0}|(.285)\hole \ar[ur]|(.28)\hole^{\hat{h}_2} \ar@/^.35cm/[drrr]_(.4){v_0}|(.285)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_1 \ar@/^.35cm/[ulll]_(.4){e_1} \ar[ul]|(.28)\hole_{\hat{m}_1} \ar@/_.35cm/[dlll]^(.4){v_1} \ar[dl]|(.28)\hole^{\mathring{f}_1 \circ x_1}& K_1 \ar[d]^{\mathring{k}_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){u_0}|(.285)\hole\ar[dr]_{\check{h}_1}   && L_0 \ar@/_.35cm/[dlll]^(.4){u_1} \ar[dl]^{\mathring{m}_0}& K_0 \ar[d]^{\mathring{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0\ar[d]^{\check{g}_2\circ x_0} \\G_0 && \ar[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar[ll]^{\bar{f}_1} \bar{D}_1 \ar[rr]_{\bar{g}_1}&& \bar{G}_2 && \ar[ll]^{\bar{f}_2} \bar{D}_2 \ar[rr]_{\bar{g}_2}&& G_3 }\]
-
-Now, by determinism we have isomorphisms $\phi_{\check{D}_0}\colon \check{D}_0\to \hat{D}_0$ $\phi_{\check{G}_1}\colon \check{G}_1\to \hat{G}_1$
-Notice that
-\begin{align*}
-	\hat{f}_0\circ \phi_{\check{D}_0}\circ v_1&= \check{f}_0\circ v_1\\&=\check{f}_0\circ \check{q}_3\circ v'_1\\&=f_0\circ \check{q}_1\circ v'_1\\&=f_0\circ i_1\\&=\hat{f}_0\circ e_1
-\end{align*}
-
-GOOD: $\phi_{\check{D}_0}$ sends $v_1$ to $e_1$, thus it respects the match of $L_1$. Automatically it sends $v_0$ to $e_0$.
-
-CHECK THAT $\check{g}_2\circ x_0=g_2\circ j_0$
-
-USO IL PRIMO LEMMA DEI TRE PASSI:
-
-	\[\xymatrix{&R_0 \ar[dl]_{i_0} \ar@{.>}[dr]^{x_0} \ar@/^.4cm/[dd]|\hole^(.6){j_0}\ar[d]_{x'_0}\\ D_1 \ar[d]_{g_1}&P'\ar[d]_{p'_3} \ar[r]^{p'_4} \ar[l]_{p'_1}&\check{D}_2\ar[d]^{\check{g}_2}\\G_2&D_2 \ar[l]^{f_2}\ar[r]_{g_2}& G_3}\]
-
-\[\xymatrix@R=15pt@C=15pt{&&L_ 0\ar[dl]^{I_1} \ar@/_1.2cm/[dddl]_(.4){d_1}|(.63)\hole\ar[dd]^{t'_1} \ar@{.>}[dr]^{t_1}\\&D'_0 \ar[dl]^(.4){g'_0}&&\tilde{D}_1 \ar[dr]^{\tilde{f}_1}\\G'_1 && S\ar[dr]_{s_4} \ar[ur]_{s_3}\ar[dl]^{s_1} \ar[ul]_{s_2}&&\hat{G}_1\\& \hat{D}_1 \ar[ul]^{\hat{f}_1}&&\hat{D}_0 \ar[ur]_{\hat{g}_0}}\]
-
-\subsection{Concatenable traces}
-\begin{lemma}
-	\todo{abstract equivalence and switch }
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-\begin{definition}
-	\todo{tracce}
-\end{definition}
-
-Before moving forward, we will prove some other useful properties of the switch equivalence relation.
-
-\begin{lemma}
-	\todo{lemma 19}
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{theorem}
-	\todo{preordine}
-\end{theorem}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\section{A class of well-behaved left-linear DPO-rewriting systems}

### 2024-11-22 full_version/fusione.tex
minori

@@
 \usepackage{tikz-cd}
-\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri,fit,positioning}
-\tikzstyle{node}=[circle, draw=black, minimum size=1mm]
+\usetikzlibrary{arrows,shapes,snakes,automata,backgrounds,petri,fit,positioning,calc}
+\tikzstyle{node}=[circle, draw=black, minimum size=1mm, inner sep=1.5pt, font=\tiny]
+
 \tikzstyle{trans}=[font=\scriptsize]
 \tikzstyle{lab}=[font=\small]
+\tikzset{
+	coloredge/.style={
+		->,
+		color=red
+		%densely dotted
+	}
+}
+
+\tikzset{
+	colorloop/.style={
+		loop,
+		color=red
+		%densely dotted
+	}
+}
+
+\tikzcdset{
+	perm/.style={
+		shorten >=-1mm, shorten <=-1mm,
+		-,
+		% dotted
+	}
+}
 
@@
 \newcommand{\unf}[1]{\ensuremath{\mathcal{U}({#1})}}
+
+\newcommand{\gph}[1]{\textbf{\textup{{#1}-Graph}}}
 
@@
 
-\title{Switch equivalence and weak prime domains for fusions}
+% direct shift
+\newcommand{\shift}[1]{\ensuremath{\mathrel{{\leftrightsquigarrow}_{#1}}}}
+
+\title{Switch equivalence and weak prime domains for left-linear DPO rewriting systems}
 \author{Paolo Baldan\and Davide Castelnovo\and  Andrea Corradini\and Fabio Gadducci}
@@
 \maketitle
-
 \tableofcontents
@@
 
+\include{permutations.tex}
  \include{leftlinear.tex}
-\include{permutations.tex}
 

### 2024-11-28 full_version/permutations.tex
permutazioni again

@@
 \[\xymatrix@C=30pt{D_{j} \ar[ddrr]^{\iota_{D_j}} \ar[r]^{g_j}\ar@{>->}[d]_{f_j}& G_{j+1} \ar[ddr]^{\iota_{G_{j+1}}} \ar[r]^-{\iota_{3, G_{j+1}}} & \lpro \der{D}^j_3\rpro \ar[dd]^{p_2} \\ G_j\ar[drr]_{\iota_{G_{j}}} \ar@{>->}[d]_{\iota_{1,G_j}}\\ \lpro \der{D}^j_1 \rpro \ar[rr]_{p_1}  &&\tpro{D} }\]
-Where the two arrows $p_1\colon \lpro\der{D}^j_1 \rpro\to \tpro{D}$, $p_2\colon \lpro \der{D}^j_3\rpro \to \tpro{D}$ are induced by the cocones $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}^j_1)})$ and $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}^j_3)})$, respectively.
+Where the two arrows $p_1\colon \lpro\der{D}^j_1 \rpro\to \tpro{D}$, $p_2\colon \lpro \der{D}^j_3\rpro \to \tpro{D}$ are induced, respectively, by the cocones $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}^j_1)})$ and $(\tpro{D}, \{\iota_{X}\}_{X\in \Delta(\der{D}^j_3)})$.
 \end{corollary}
@@
 
-	If $\lgh(\der{D})=0$ this is enough to conclude, otherwise we are going to prove by induction that, for every $i\in [0, \lgh(\der{D})-1]$, $\xi_\sigma \circ \iota_{G_i}=\xi'_\sigma\circ \iota_{G_i}$.
+	If $\lgh(\der{D})=0$ this is enough to conclude, otherwise we are going to prove by induction that, $\xi_\sigma \circ \iota_{G_i}=\xi'_\sigma\circ \iota_{G_i}$ for every $i\in [0, \lgh(\der{D})-1]$.
 
@@
 
-\section{Composing and decomposing consistent permutations}
+\subsection{Permutation equivalence}
+
+\begin{definition}
+	contenuto...
+\end{definition}
+
+\begin{theorem}[Characterization of $\equiv_p$]
+	contenuto...
+\end{theorem}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\section{Composing and restricting consistent permutations}
 Now that we have established some initial facts about consistent permutations, we are going to embark in a, quite long, voyage to explore how to restrict them to suitable subderivations.
@@
 Then there are arrows $q_1\colon \lpro \der{D}_1\rpro \to \tpro{D}$, $q_2\colon \lpro \der{D}_2\rpro \to \tpro{D}$ such that
-\[q_1\circ \iota_{G_{1,0}}\circ \alpha_1 = \iota_{G_{0}}\circ \alpha \qquad q_2\circ \iota_{G_{2,l_2}}\circ \omega_2 = \iota_{G_{l_1+l_2}}\circ \omega \]
+\[ q_1\circ \iota_{G_{1,0}}\circ \alpha_1 = \iota_{G_{0}}\circ \alpha \quad  q_2\circ \iota_{G_{2,l_2}}\circ \omega_2 = \iota_{G_{l_1+l_2}}\circ \omega \quad 	q_2\circ \iota_{2, G_{2,0}} \circ \alpha_2=q_1\circ \iota_{1, G_{1, l_1}}\circ \omega_1\]
 and, for every $i\in [0, l_1-1]$, $j\in [l_1+1, l_1+l_2]$
@@
 We can then define $q_1$ as $\id{\lpro \der{D}_1\rpro}$.
-Since $\iota_{2,G_{2,0}}$ is an isomorphism, $q_2$ can be taken as  $\iota_{G_{l_1+l_2}}\circ  \omega_1  \circ \alpha^{-1}_2 \circ \iota^{-1}_{2,G_{2,0}}$.
+Since $\iota_{2,G_{2,0}}$ is an isomorphism, $q_2$ can be taken as  $\iota_{G_{l_1}}\circ  \omega_1  \circ \alpha^{-1}_2 \circ \iota^{-1}_{2,G_{2,0}}$.
 	\item  $\lgh(\der{D}_1)\neq 0$ and $\lgh(\der{D}_2)\neq 0$.
@@
 It is worth noticing that, for every $i\in [0,l_1-1]$ and $j\in [l_1+1, l_1+l_2]$ the previous equalities also entail that,
-\[\begin{split}q_1\circ \iota_{1, D_{1,i}}&=\iota_{D_{i}}\\q_2\circ \iota_{2, D_{2,j}}&=\iota_{D_{j+l_1}} 	\\q_1\circ \iota_{1, R_{1,i-1}}&=\iota_{R_{i-1}} \\
-	q_2\circ \iota_{2, R_{2,j-1}}&=\iota_{R_{j+l_1-1}}
-\end{split} \qquad 
-\begin{split}    	q_1\circ \iota_{1, L_{1,i}}&=\iota_{L_{i}} \\q_2\circ \iota_{2, L_{2,j}}&=\iota_{L_{j+l_1}}\\ q_1\circ \iota_{1, K_{1,i}}&=\iota_{K_{i}}\\q_2\circ \iota_{2, K_{2,j}}&=\iota_{K_{j+l_1}}\end{split}\]
+\[\begin{split}q_1\circ \iota_{1, L_{1,i}}&=\iota_{L_{i}}\\q_2\circ \iota_{2, L_{2,j}}&=\iota_{L_{j+l_1}} 	
+\end{split} \quad 
+\begin{split}    	q_1\circ \iota_{1, K_{1,i}}&=\iota_{K_{i}} \\q_2\circ \iota_{2, K_{2,j}}&=\iota_{K_{j+l_1}}\\ \end{split}\quad 
+\begin{split}    	q_1\circ \iota_{1, R_{1,i-1}}&=\iota_{R_{i-1}} \\q_2\circ \iota_{2, R_{2,j-1}}&=\iota_{R_{j+l_1-1}}\end{split}\quad 
+\begin{split}    	q_1\circ \iota_{1, D_{1,i}}&=\iota_{D_{i}} \\q_2\circ \iota_{2, D_{2,j}}&=\iota_{D_{j+l_1}}\end{split}\]
+
+Moreover, if $l_2\neq 0$, we also have that
+\begin{align*} 
+q_2\circ \iota_{2, D_{2, 0}}&=q_2\circ \iota_{2, G_{2, 1}}\circ g_{2, 0}\\&=\iota_{G_{l_1+1}}\circ g_{2,0}\\&=\iota_{G_{l_1+1}}\circ g_{l_1}\\&=\iota_{D_{l_1}}
+\end{align*}
+which, in turn, also entails that
+\begin{align*}
+	q_2\circ \iota_{2, K_{2, 0}}&=q_2\circ \iota_{D_{2, 0}}\circ k_{2, 0}\\&=\iota_{D_{l_1}}\circ k_{l_1}\\&=\iota_{K_{l_1}}
+\end{align*}
+
+Finally, whenever $l_1$ and $l_2$ are different from $0$ we have other two equalities.
+\[q_1\circ \iota_{1, G_{1, l_1}}=\iota_{ G_{l_1}}\circ \omega^{-1}_1 \qquad q_2\circ \iota_{2, G_{2, 0}}=\iota_{ G_{l_1}}\circ \alpha^{-1}_2\]
+
 \end{remark}
@@
 
-\smallskip \noindent  If $i=0$ the thesis follows from point $1$.
+\smallskip \noindent  If $i=0$ the thesis follows from the previous point.
 
@@
 				\xi_\sigma \circ \iota_{G_{l_1}}\circ h_{l_1-1}&=  \xi_\sigma\circ \iota_{R_{l_1-1}}\\&=\iota'_{R'_{\sigma(l_1-1)}}\\&=\iota'_{R'_{\tau(l_1-1)}}\\&=q'_1\circ \iota'_{1, R'_{1,\tau(l_1-1)}}\\&=q'_1\circ \xi_{\tau}\circ \iota_{1, R_{l_1-1}}\\&=q'_1\circ \xi_{\tau} \circ \iota_{1, G_{1,l_1}}\circ h_{1, l_1-1}\\&=q'_1\circ \xi_\tau \circ \iota_{1, G_{l_1}} \circ h_{l_1-1}			\end{split}
-			\qquad  \begin{split}
+			\quad  \begin{split}
 				\xi_\sigma \circ \iota_{G_{l_1}}\circ g_{l_1-1}&=\xi_{\sigma}\circ \iota_{D_{l_1-1}}\\&=\xi_{\sigma}\circ \iota_{G_{l_1-1}} \circ f_{l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1-1}} \circ f_{l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}-1} \circ f_{1, l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, D_{l_1-1}}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ g_{1, l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ g_{l_1-1}
@@
 			\item In this case, we can consider the following diagram, in which the inner rectangle and the outer border are pushouts
-		\[\xymatrix@C=35pt{K_{1,l_1-1}\ar[r]^{r_{1,l_1-1}} \ar[d]_{k_{1,l_1-1}}& R_{i-1} \ar[d]_{h_{1,l_1-1}} \ar@/^.3cm/[ddr]^{h_{l_1-1}}\\ D_{1,l_1-1} \ar[r]_{g_{1,l_1-1}} \ar@/_.3cm/[drr]_{g_{l_1-1}}& G_{1,l_1} \ar[dr]^{\omega_1^{-1}}\\ &&\pi(G_{2,0})}\]
+		\[\xymatrix@C=35pt{K_{1,l_1-1}\ar[r]^{r_{1,l_1-1}} \ar[d]_{k_{1,l_1-1}}& R_{i-1} \ar[d]_{h_{1,l_1-1}} \ar@/^.4cm/[ddr]^{h_{l_1-1}}\\ D_{1,l_1-1} \ar[r]_{g_{1,l_1-1}} \ar@/_.4cm/[drr]_{g_{l_1-1}}& G_{1,l_1} \ar[dr]^{\omega_1^{-1}}\\ &&\pi(G_{2,0})}\]
 
@@
 		\[\begin{split}
-			\xi_\sigma \circ \iota_{G_{l_1}}\circ h_{l_1-1}&=  \xi_\sigma\circ \iota_{R_{l_1-1}}\\&=\iota'_{R'_{\sigma(l_1-1)}}\\&=\iota'_{R'_{\tau(l_1-1)}}\\&=q'_1\circ \iota'_{1, R'_{1,\tau(l_1-1)}}\\&=q'_1\circ \xi_{\tau}\circ \iota_{1, R_{l_1-1}}\\&=q'_1\circ \xi_{\tau} \circ \iota_{1, G_{1,l_1}}\circ h_{1, l_1-1}\\&=q'_1\circ \xi_\tau \circ \iota_{1, G_{1, l_1}} \circ \omega_1 \circ  h_{l_1-1}			\end{split}  \qquad  		\begin{split}
+			\xi_\sigma \circ \iota_{G_{l_1}}\circ h_{l_1-1}&=  \xi_\sigma\circ \iota_{R_{l_1-1}}\\&=\iota'_{R'_{\sigma(l_1-1)}}\\&=\iota'_{R'_{\tau(l_1-1)}}\\&=q'_1\circ \iota'_{1, R'_{1,\tau(l_1-1)}}\\&=q'_1\circ \xi_{\tau}\circ \iota_{1, R_{l_1-1}}\\&=q'_1\circ \xi_{\tau} \circ \iota_{1, G_{1,l_1}}\circ h_{1, l_1-1}\\&=q'_1\circ \xi_\tau \circ \iota_{1, G_{1, l_1}} \circ \omega_1 \circ  h_{l_1-1}			\end{split}   	\hspace{-5pt}	\begin{split}
 			\xi_\sigma \circ \iota_{G_{l_1}}\circ g_{l_1-1}&=\xi_{\sigma}\circ \iota_{D_{l_1-1}}\\&=\xi_{\sigma}\circ \iota_{G_{l_1-1}} \circ f_{l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}} \circ f_{l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}} \circ f_{1, {l_1}-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, D_{{l_1}-1}}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ g_{1, l_1-1}\\&=q'_1 \circ \xi_{\tau} \circ \iota_{1, G_{l_1}}\circ \omega_1\circ g_{l_1-1}
@@
 		\[\xymatrix{L_{j-1} \ar@/^.3cm/[drr]^{\id{L_{j-1}}} \ar@{.>}[dr]_{t} \ar@/_.3cm/[ddr]_{c}\\ & K_{j-1} \ar[d]_{k_a}\ar@{>->}[r]^{l_{j-1}}& L_{j-1} \ar[d]^{m_a} \\& D_a \ar@{>->}[r]_{f_a} & G_a} \]
-		The existence of the dotted $t\colon L_{j-1}\to K_{j-1}$ follows from  \Cref{prop:pbpoad} and we can conclude. \qedhere
+
+	\Cref{prop:pbpoad} we can now deduce the existence of the dotted $t\colon L_{j-1}\to K_{j-1}$, from which the thesis  follows. \qedhere
 	\end{enumerate}
@@
 Take two isomorphisms $\gamma:\pi(H)\to \gamma$, $\gamma':\pi(H')\to H'$, then, according to \Cref{def:conc}:
-\begin{align*}(\der{D}, \alpha, \omega)&=(\der{D}, \alpha, \omega)\cdot (\der{D}_2, \gamma, \gamma) \\(\der{D}', \alpha', \omega')&=(\der{D}', \alpha', \omega')\cdot (\der{D}'_2, \gamma', \gamma') 
-\end{align*} 
+\[(\der{D}, \alpha, \omega)=(\der{D}, \alpha, \omega)\cdot (\der{D}_2, \gamma, \gamma) \qquad (\der{D}', \alpha', \omega')=(\der{D}', \alpha', \omega')\cdot (\der{D}'_2, \gamma', \gamma') \]
 where $\der{D}_2$ and $\der{D}'_2$ are the empty derivation on $H$ and $H'$. Since $(\X, \R)$ is consuming, then \Cref{lem:impo} entails $D_{\sigma, \tau}=\emptyset$, from which the thesis follows.
@@
 	\begin{enumerate}
-		\item suppose that $l_1$ and $l_2$ are different from $0$ and consider the following two pushout squares given by \Cref{rem:dett}:
-		\[\xymatrix@C=45pt@R=30pt{\pi(G_{2,0}) \ar@{>->}[d]_{\iota_{1, G_{1,n+1}} \circ \omega_1}\ar[r]^{\iota_{2, G_{2,0}} \circ \alpha_2}& \lpro \der{D}_2 \rpro \ar@{>->}[d]^{q_2} &  \pi(G'_{2,0}) \ar@{>->}[d]_{\iota'_{1, G'_{1,n+1}} \circ \omega'_1} \ar[r]^{\iota'_{2, G'_{2,0}} \circ \alpha'_2}& \lpro \der{D}'_2 \rpro \ar@{>->}[d]^{q'_2} \\ \lpro \der{D}_1 \rpro  \ar[r]_{q_1} & \tpro{D} & \lpro \der{D}'_1\rpro \ar[r]_{q'_1} & \lpro \der{D}'\rpro  }\]
-		then, for every $i\in [0, l_2]$ there exists a unique $\zeta_i\colon G_{2,i}\to \lpro \der{D}_2\rpro $ fitting in the diagram below
-		\[\xymatrix@R=35pt{G_{2,i} \ar[r]^{\iota_{2,G_{2,i}}} \ar@{.>}[d]_{\zeta_i}&\lpro \der{D}_2 \rpro \ar@{>->}[r]^{q_2}& \tpro{D} \ar[d]^{\xi_{\sigma}} \\
-			\lpro \der{D}'_2 \rpro \ar@{>->}[rr]_{q'_2}&& \lpro \der{D}'\rpro }\]
+		\item for every $i\in [0, l_2]$ there exist a unique $\zeta_i\colon G_{2,i}\to \lpro \der{D}'_2\rpro $ and a unique $\varsigma_{i}\colon G'_{2,i}\to \lpro \der{D}_2\rpro$ fitting in the diagrams below;
+		\[\xymatrix@C=30pt{G_{2,i} \ar[r]^-{\iota_{2,G_{2,i}}} \ar@{.>}[d]_{\zeta_i}&\lpro \der{D}_2 \rpro \ar@{>->}[r]^{q_2}& \tpro{D} \ar[d]^{\xi_{\sigma}} &G'_{2,i} \ar[r]^-{\iota'_{2,G'_{2,i}}} \ar@{.>}[d]_{\varsigma_i}&\lpro \der{D}'_2 \rpro \ar@{>->}[r]^{q'_2}& \lpro D'\rpro \ar[d]^{\xi^{-1}_{\sigma}}\\
+			\lpro \der{D}'_2 \rpro \ar@{>->}[rr]_{q'_2}&& \lpro \der{D}'\rpro & 			\lpro \der{D}_2 \rpro \ar@{>->}[rr]_{q_2}&& \lpro \der{D}\rpro }\]
+
+		\item there exists an isomorphism $\psi\colon \lpro \der{D}_2\rpro \to \lpro \der{D}'_2\rpro$ fitting in the diagrams below; 
+		\[\xymatrix@C=30pt{G_{2,i} \ar[r]^-{\iota_{2,G_{2,i}}} \ar@/_.3cm/[dr]_{\zeta_i}&\lpro \der{D}_2 \rpro \ar@{>->}[r]^{q_2} \ar@{.>}[d]_{\psi}& \tpro{D} \ar[d]^{\xi_{\sigma}} &G'_{2,i} \ar[r]^-{\iota'_{2,G'_{2,i}}} \ar@/_.3cm/[dr]_{\varsigma_i}&\lpro \der{D}'_2 \rpro\ar@{<.}[d]_{\psi}  \ar@{>->}[r]^{q'_2}& \lpro \der{D}'\rpro \ar[d]^{\xi^{-1}_{\sigma}}\\&
+			\lpro \der{D}'_2 \rpro \ar@{>->}[r]_{q'_2}& \lpro \der{D}'\rpro & 		&	\lpro \der{D}_2 \rpro \ar@{>->}[r]_{q_2}& \lpro \der{D}\rpro }\]
 		\item the permutation
@@
 \end{lemma}
-\begin{proof}\begin{enumerate}
-		\item We can start noticing that  by \Cref{lem:impo}, $\sigma(i)=\tau(i)$ for every $i\in  [0, l_1-1]$. By the second point of \Cref{prop:uniqu} we can deduce that
-		\[\xi_\sigma \circ \iota_{G_{i}}=\]Let us prove the existence of $\zeta_i$ by induction on $i\in [0, l_2]$.
-
-		\smallskip \noindent $i=0$. We already know that $G_{l_1}$ and $G'_{l_1}$ are both equal to $\pi(G_{2,0})$.  Moreover, we also know that
-		\begin{align*}
-		q_2\circ \iota_{2, G_{2,0}}=\iota_{G_{l_1}} \circ \alpha^{-1}_2 \qquad
-		\end{align*}
-
-		Thus we have a diagram
-		\[\xymatrix{&G_{2,0} \\
-		G_{l_1} \\
-		G'_{2,0}&}\]
-
-	Moreover, $\pi(mj$
-		\begin{align*}
-			\xi_\sigma \circ p_2\circ \iota_{2, G_{2,0}}&=\xi_\sigma \circ \iota_{G_{n+1}}\circ \alpha^{-1}_2\\&g
-		\end{align*}
+\begin{proof}
+	To fix the notation, we will use $\der{D}=\{\dder{D}_i\}_{i=0}^{l_1+l_2-1}$ and $\der{D}'=\{\dder{D}_i\}_{i=0}^{l_1+l_2-1}$ to denote the composite derivations.
+The direct derivations $\dder{D}_i$ and $\dder{D}_i$ are given by the two diagrams below.
+	\[\xymatrix{L_i \ar[d]_{m_i}& K_i \ar[r]^{r_i} \ar@{>->}[l]_{l_i} \ar[d]_{k_i}& R_i \ar[d]^{h_i}& L'_i \ar[d]_{m'_i} & K'_i \ar[d]_{k'_i} \ar[r]^{r'_i} \ar@{>->}[l]_{l'_i} & R'_i \ar[d]^{h'_i}\\ G_i & D_i \ar[r]_{g_i} \ar@{>->}[l]^{f_i} & G_{i+1} & G'_i & D'_i \ar[r]_{g'_i} \ar@{>->}[l]^{f'_i} & G'_{i+1}}\]
+
+	We can also notice that,  by \Cref{lem:impo}, $\sigma(i)=\tau(i)$ for every $i\in  [0, l_1-1]$.
+In particular, this implies that the image  $[l_1, l_1+l_2-1]$ through $\sigma$ is again the interval $[l_1, l_1+l_2-1]$ and that $\varrho$ is well-defined.
+Moreover, if $l_1\neq 0$, then $l_1-1$ is the maximum of $E_{\sigma,\tau}$.
+
+	\begin{enumerate}
+		\item 		To prove the existence of $\zeta_i$ we proceed by induction on $i\in [0, l_2]$.
+
+		\smallskip \noindent $i=0$.
+We know that $G_{2,0}$ and $G'_{2,0}$ are isomorphic to, respectively, $G_{1, l_1}$ and $G'_{1, l_1}$.
+By hypothesis $\tau$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$, so that $G_{1,l_1}$ and $G'_{1, l_1}$ are isomorphic too.
+We can therefore consider as $\zeta_0$ the arrow $\iota'_{2, G'_{2,0}}\circ (\alpha'_2)\circ \alpha^{-1}_2$.
+Now, by \Cref{rem:dett,prop:uniqu}, all subdiagrams of the following diagram commute, so that the whole diagram is commutative and the thesis follows.
+		\[\xymatrix@R=10pt@C=35pt{G_{2,0}\ar[r]^{\iota_{2, G_{2,0}}} \ar[dd]_{\alpha^{-1}_2}&\lpro \der{D}_2\rpro \ar[rr]^{q_2}&&\tpro{D}\ar[dddd]^{\xi_{\sigma}}\\& G_{1,l_1} \ar[r]^{\iota_{1, G_{1, l_1}}}& \lpro \der{D}_1\ar[dd]^{\xi_\tau} \ar[ur]_{q_1} \rpro \\\pi(G_{2,0}) \ar[ur]^{\omega_1}\ar[dr]_{\omega'_1} \\ & G'_{1,l_1} \ar[r]_{\iota'_{1, G'_{1, l_1}}}& \lpro \der{D}'_1 \rpro \ar[dr]^{q_1}\\G'_{2,0} \ar@{<-}[uu]^{\alpha'_2}\ar[r]_{\iota'_{2, G'_{2,0}}}&\lpro \der{D}'_2\rpro \ar[rr]_{q'_2}&& \lpro \der{D}'\rpro }\]
 
 		\smallskip \noindent $i>0$.
-
-		The uniqueness half of the thesis follows at once since $p'_2$ is in $\mathcal{M}$.
-
-		\item Let us split the cases.
-
-		\smallskip \noindent $l_1=0$. then $\varrho=\sigma$ and there is nothing to proof.
-
-		\smallskip \noindent $l_2=0$ and $l_1\neq0$. Then $\varrho=\id{\emptyset}$ and
-
-		\smallskip \noindent $l_1\neq0$ and $l_2\neq 0$. 
-		\[\xymatrix{xy code}\]
+Let $j$ be $\sigma(i-1+l_1)-l_1$.
+We have already observed that $\sigma(i-1+l_1)$ belongs to $[l_1, l_1+l_2-1]$, so that $j$ is an element of $[0, l_2-1]$.
+By consistency of $\sigma$ we get that, if $\der{D}_1=\{\dder{D}_{2,s}\}_{s=0}^{l_2-1}$ and $\der{D}'_2=\{\dder{D}'_{1,s}\}_{s=0}^{l_2-1}$, then $\dder{D}_{2, i-1}$ and $\dder{D}'_{2, j}$ are given by the following two direct derivations.
+		\[\xymatrix@C=30pt{L_{2,i-1} \ar[d]_{m_{2,i-1}} & K_{2,i-1} \ar[d]_{k_{2, i-1}} \ar[r]^{r_{2,i-1}} \ar@{>->}[l]_{l_{2,i-1}} & R_{2,i-1} \ar[d]^{h_{2,{i-1}}} & L_{2,i-1} \ar[d]_{m'_{2,j}} & K_{2,i-1}\ar[d]_{k'_{2, j}} \ar[r]^{r_{2,i-1}} \ar@{>->}[l]_{l_{2,i-1}}& R_{2,i-1} \ar[d]^{h'_{2, j}}\\ G_{2,i-1} & D_{2,i-1} \ar@{>->}[l]^{f_{2, i-1}} \ar[r]_{g_{2, i-1}} & G_{2,i} & G'_{2,j} & D'_{2,j}\ar@{>->}[l]^{f'_{2, j}} \ar[r]_{g'_{2, j}} & G'_{2,j+1} }\]
+
+		Notice, moreover, that these two derivations coincide with $\dder{D}_{i-1+l_1}$ and  $\dder{D}'_{\sigma(i-1+l_1)}$.	Now, if we compute, from \Cref{rem:coproj,rem:dett2} we get:
+		\begin{align*}
+			q'_2\circ \iota'_{2, R'_{2, j}}\circ r_{2, j}&=q'_2\circ \iota'_{2, K'_{2,j}}\\&=q'_2\circ \iota'_{2,D'_{2,j}}\circ k'_{2,j}\\&= \iota'_{D'_{\sigma(i-1+l_1)}}\circ k'_{\sigma(i-1+l_1)}\\&=\xi_\sigma \circ \iota_{D_{i-1+l_1}} \circ k_{i-1+l_1}\\&=\xi_\sigma \circ q_2 \circ \iota_{2, D_{2,i-1}}\circ k_{2, i-1}\\&=\xi_\sigma \circ q_2 \circ \iota_{2, G_{2,i-1}}\circ f_{2,i-1}\circ k_{2,i-1}\\&=q'_2\circ \zeta_{i-1}\circ f_{2, i-1}\circ k_{2, i-1}
+		\end{align*}
+
+		Since $q'_2$ is in $\mathcal{M}$, then 
+		\[\zeta_i\circ f_{2, i-1}\circ k_{2, i-1}=\iota'_{2, R'_{2, j}}\circ r_{2, j}\]
+		Therefore there is a unique arrow $\zeta_i\colon G_{2, i}\to \lpro \der{D}'_2\rpro$ making the diagram below commutative.
+		\[\xymatrix{K_{2, i-1} \ar[d]_{k_{2, i-1}} \ar[r]^{r_{2, i-1}} & R_{2,i-1} \ar[d]_{h_{2, i-1}} \ar@/^.3cm/[ddr]^{\iota'_{2, R'_{2,j}}}\\
+		D_{2, i-1} \ar[r]_{g_{2, i-1}} \ar@/_.2cm/@{>->}[dr]_{f_{2, i-1}}& G_{2, i} \ar@{.>}[dr]^{\zeta_i} \\ &G_{2, i-1}\ar[r]_{\zeta_{i-1}}& \lpro \der{D}'_2\rpro}\]
+
+		Finally, we have to check that this $\zeta_i$ fits in the wanted rectangle.
+To see this, since $G_{2,i}$ is obtained as a pushout, it is enough to perform the following computations, again with the aid of \Cref{rem:coproj,rem:dett2}:
+		\[\begin{split}
+		q'_2\circ \zeta_i\circ h_{2, i-1}&=q'_2\circ \iota'_{2, R'_{2,j}}\\&=\iota'_{R'_{\sigma(i-1+l_1)}} \\&=\xi_\sigma \circ \iota'_{R_{i-1+l_1}}\\&=\xi_\sigma \circ q_2\circ \iota_{2, R_{2,i-1}}\\&=\xi_\sigma \circ q_2\circ \iota_{2, G_{2,i}}\circ h_{2,i-1}
+		\end{split}\qquad \begin{split}
+		q'_2\circ \zeta_i\circ g_{2, i-1}&=q'_2\circ \zeta_{i-1}\circ f_{2, i-1}\\&=\xi_\sigma\circ q_2\circ \iota_{2, G_{2,i-1}}\circ f_{2, i-1} \\&=\xi_\sigma \circ q_2\circ \iota_{2, D_{2, i-1}}\\&=\xi_\sigma \circ q_2\circ \iota_{2, G_{2, i-1}}\circ g_{2,i-1}\\&
+		\end{split}\]
+
+		The uniqueness half of the thesis follows at once since $q'_2$ is in $\mathcal{M}$.
+
+		To prove the existence of $\varsigma_{i}$, it is enough to apply the previous point to $\sigma^{-1}$ and $\tau^{-1}$, noticing that, by \Cref{rem:inversa} and \Cref{prop:isouno}, $\xi^{-1}_\sigma$ must coincide with $\xi_{\sigma^{-1}}$.
+
+		\item We can use the arrows $\zeta_i$  and $\varsigma_{i}$ constructed in point $1$ to define a cocone $(\lpro \der{D}'_2\rpro, \{c_X\}_{X\in \Deltamin(\der{D}_2)})$ on $\Deltamin(\der{D}_2)$ and another one $(\lpro \der{D}_2\rpro, \{d_Y\}_{Y\in \Deltamin(\der{D}'_2)})$ on $\Deltamin(\der{D}'_2)$  putting, for every $i\in [0, l_2]$
+		\[c_X:=\begin{cases}
+			\zeta_i & X=G_{2,i}\\
+			\zeta_{i} \circ f_{2,i} & X=D_{2,i}
+		\end{cases} \qquad d_Y:=\begin{cases}
+		\varsigma_i & Y=G'_{2,i}\\
+		\varsigma_{i} \circ f'_{2,i} & Y=D'_{2,i}
+		\end{cases} \]
+
+		Notice that, by the construction provided in the previous point, for every $i\in [1, l_2]$ we have
+		\[\zeta_i\circ g_{2, i-1}=\zeta_{i-1}\circ f_{2,i-1} \qquad \varsigma_i\circ g'_{2, i-1}=\varsigma_{i-1}\circ f'_{2,i-1} \]
+		so that $(\lpro \der{D}'_2\rpro, \{c_X\}_{X\in \Deltamin(\der{D}_2)})$ and $(\lpro \der{D}_2\rpro, \{c_Y\}_{Y\in \Deltamin(\der{D}'_2)})$ are really cocones.
+
+		Thus we can consider the induced arrows $\psi\colon \lpro \der{D}_2\rpro \to \lpro \der{D}'_2\rpro$ and $\phi\colon \lpro \der{D}'_2\rpro \to \lpro \der{D}_2\rpro$.
+Now, on the one hand given $X\in \Deltamin(\der{D}_2)$ we have:
+		\begin{align*}
+			q'_2\circ \psi \circ \iota_{2,X}&=q'_2\circ c_X\\&=\begin{cases}
+				q'_2\circ  \zeta_i & X =G_{2,i}\\
+				q'_2 \circ  \zeta_{i}\circ f_{2,i} & X={D_{2,i}}
+			\end{cases}\\&=\begin{cases}
+			\xi_\sigma \circ q_2\circ \iota_{2, G_{2,i}} & X =G_{2,i}\\
+			\xi_\sigma \circ q_2\circ \iota_{2, G_{2,i}} \circ f_{2,i} & X={D_{2,i}}
+			\end{cases}\\&=\begin{cases}
+			\xi_\sigma \circ q_2\circ \iota_{2, G_{2,i}} & X =G_{2,i}\\
+			\xi_\sigma \circ q_2\circ \iota_{2, D_{2,i}} & X={D_{2,i}}
+			\end{cases}\\&= \xi_\sigma \circ q_2\circ \iota_{2, X}
+		\end{align*}
+		so that $q'_2\circ \psi = \xi_{\sigma} \circ q_2$. On the other hand, for every $Y\in \Deltamin(\der{D}'_2)$:
+		\begin{align*}
+	q_2\circ \phi \circ \iota'_{2,Y}&=q_2\circ d_Y\\&=\begin{cases}
+		q_2\circ  \varsigma_i & Y =G'_{2,i}\\
+		q_2 \circ \varsigma_{i}\circ f'_{2,i} & Y={D'_{2,i}}
+	\end{cases}\\&=\begin{cases}
+		\xi^{-1}_\sigma \circ q'_2\circ \iota'_{2, G'_{2,i}} & Y =G'_{2,i}\\
+		\xi^{-1}_\sigma \circ q'_2\circ \iota'_{2, G'_{2,i}} \circ f'_{2,i} & Y={D'_{2,i}}
+	\end{cases}\\&=\begin{cases}
+		\xi^{-1}_\sigma \circ q'_2\circ \iota'_{2, G'_{2,i}} & Y =G'_{2,i}\\
+		\xi^{-1}_\sigma \circ q'_2\circ \iota'_{2, D'_{2,i}} & Y={D'_{2,i}}
+	\end{cases}\\&= \xi^{-1}_\sigma \circ q'_2\circ \iota_{2, Y}
+		\end{align*}
+	therefore we also have $q_2\circ \phi =\xi^{-1}_{\sigma}\circ q'_2$.  If we compute further, given $X\in \Deltamin(\der{D}_2)$ we get:
+		\begin{align*}
+			q_2\circ \phi \circ \psi \circ \iota_{2, X}&=q'_2\circ \phi \circ c_X\\&=\begin{cases}
+				q_2\circ \phi \circ \zeta_i & X=G_{2,i}\\
+				q_2\circ \phi \circ \zeta_{i} \circ f_{2,i} & X=D_{2,i}
+			\end{cases}\\&=\begin{cases}
+				\xi^{-1}_{\sigma}\circ q'_2 \circ \zeta_i & X=G_{2,i}\\
+				\xi^{-1}_{\sigma}\circ q'_2 \circ \zeta_{i} \circ f_{2,i} & X=D_{2,i}
+			\end{cases}\\&=\begin{cases}
+				\xi^{-1}_{\sigma} \circ \xi_\sigma \circ q_2\circ \iota_{2, G_{2,i}} & X=G_{2,i}\\
+				\xi^{-1}_{\sigma}\circ \xi_\sigma \circ q_2\circ \iota_{2, G_{2,i}}  \circ f_{2,i} & X=D_{2,i}
+			\end{cases}\\&=\begin{cases}
+				q_2\circ \iota_{2, G_{2,i}} & X=G_{2,i}\\
+				q_2\circ \iota_{2, D_{2,i}} & X=D_{2,i}
+			\end{cases}\\&=q_2\circ \iota_{2,X}
+		\end{align*}
+		Hence $q_2\circ \phi \circ \psi = q_2$ and, since $q_2$ is mono this entails $\phi \circ \psi =\id{\lpro \der{D}_2 \rpro}$.
+
+		Similarly, if  $Y$ is an object of $\Deltamin(\der{D}_2)$ then:
+				\begin{align*}
+			q'_2\circ \psi \circ \phi \circ \iota'_{2, Y}&=q_2\circ \psi \circ d_Y\\&=\begin{cases}
+				q'_2\circ \psi \circ \varsigma_i & Y=G'_{2,i}\\
+				q'_2\circ \psi \circ \varsigma_{i} \circ f'_{2,i} & Y=D'_{2,i}
+			\end{cases}\\&=\begin{cases}
+				\xi_{\sigma} \circ q_2\circ \varsigma_i & Y=G'_{2,i}\\
+				\xi_{\sigma} \circ q_2 \circ \varsigma_{i} \circ f'_{2,i} & Y=D'_{2,i}
+			\end{cases}\\&=\begin{cases}
+				\xi_{\sigma} \circ \xi^{-1}_\sigma \circ q'_2\circ \iota'_{2, G'_{2,i}} & Y=G'_{2,i}\\
+				\xi_{\sigma}\circ \xi^{-1}_\sigma \circ  q'_2\circ \iota'_{2, G'_{2,i}}  \circ f'_{2,i} & Y=D'_{2,i}
+			\end{cases}\\&=\begin{cases}
+				q'_2\circ \iota'_{2, G'_{2,i}} & X=G'_{2,i}\\
+				q'_2\circ \iota'_{2, D'_{2,i}} & X=D'_{2,i}
+			\end{cases}\\&=q'_2\circ \iota'_{2,X}
+		\end{align*}
+		As before, this implies $q'_2\circ \psi \circ \phi= q'_2$, showing that $\phi$ is the inverse of $\psi$.
+
+		\item Let us consider the isomorphism $\psi \colon \lpro \der{D}_2\rpro \to \lpro \der{D}'_2\rpro$ constructed in the previous point.
+To see that it witnesses the consistency we need to split the cases.
+
+		\smallskip \noindent $l_1=0$. In this case we have that $\varrho=\sigma$, $\tau=\id{\emptyset}$ and 
+		\begin{align*}(\{G_{1,0}\}, \alpha_1, \omega_1) \cdot (\der{D}_2, \alpha_2, \omega_2)&= (\der{D}_2, \alpha_2\circ \omega^{-1}_1\circ \alpha_1, \omega_2)\\(\{G'_{1,0}\}, \alpha'_1, \omega'_1) \cdot (\der{D}'_2, \alpha'_2, \omega'_2)&= (\der{D}'_2, \alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1, \omega'_2)
+		\end{align*}
+		In particular, by \Cref{rem:dett} $q_2$  and $q'_2$ are identities, so that $\psi =\xi_\sigma$. To conclude it is thus enough to show that 
+			\[\psi \circ \iota_{2, G_{2,0}} \circ \alpha_2=\iota'_{2, G'_{2,0}}\circ  \alpha'_2\]
+
+		Now, since $\psi$ is equal to $\xi_\sigma$ then 
+		\[\psi \circ \iota_{2, G_{2,0}} \circ \alpha_2\circ \omega^{-1}_1\circ \alpha_1=\iota'_{2, G'_{2,0}}\circ  \alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1 \]
+
+		Since by \Cref{rem:empty,rem:empty2}, we know that $ \omega^{-1}_1\circ \alpha_1= (\omega'_1)^{-1}\circ \alpha'_1$, the thesis now follows.
+
+		\smallskip \noindent $l_2=0$ and $l_1\neq0$. Then $\varrho=\id{\emptyset}$, $\tau = \sigma$ and 
+		\begin{align*}(\der{D}_1, \alpha_1, \omega_1) \cdot (\{G_{2,0}\}, \alpha_2, \omega_2)
+			&=(\der{D}_1, \alpha_1, \omega_1 \circ \alpha_2^{-1}\circ \omega_2)\\(\der{D}'_1, \alpha'_1, \omega'_1) \cdot (\{G'_{2,0}\}, \alpha'_2, \omega'_2)&=(\der{D}'_1, \alpha'_1, \omega'_1 \circ (\alpha'_2)^{-1}\circ \omega'_2)
+		\end{align*}
+
+	Now, by the construction in point $1$, we can start computing to get:
+	\begin{align*}
+		 \psi \circ \iota_{2, G_{2,0}}\circ \alpha_2&=\zeta_0\circ \alpha_2\\&=  \alpha'_2\circ \alpha^{-1}_2\circ \alpha_2 \\&=\alpha'_2
+	\end{align*}
+
+		Now, \Cref{rem:dett} we have the following equalities:
+		\[q_2=\iota_{G_{l_1}}\circ  \omega_1  \circ \alpha^{-1}_2 \circ \iota^{-1}_{2,G_{2,0}} \qquad q'_2=\iota'_{G_{l_1}}\circ  \omega'_1  \circ (\alpha'_2)^{-1} \circ (\iota'_{2,G_{2,0}})^{-1}\]
+
+	Moreover, by hypothesis $\sigma$ is a consistent permutation, so that:
+		\[\xi_\sigma\circ \iota_{G_{l_1}}\circ \omega_1 \circ \alpha_2^{-1}\circ \omega_2=\iota'_{G'_{l_1}}\circ \omega'_1 \circ (\alpha'_2)^{-1}\circ \omega'_2\]
+
+		If we compute, now we get:
+		\begin{align*}
+			q'_2\circ \psi \circ \iota_{2, G_{2,0}}\circ \omega_2 & = \xi_\sigma \circ q_2\circ \iota_{2, G_{2,0}}\circ \omega_2 \\&=\xi_\sigma \circ \iota_{G_{l_1}}\circ  \omega_1  \circ \alpha^{-1}_2 \circ \iota^{-1}_{2,G_{2,0}}\circ \iota_{2, G_{2,0}}\circ \omega_2\\&=\xi_\sigma \circ \iota_{G_{l_1}}\circ  \omega_1  \circ \alpha^{-1}_2 \circ \omega_2\\&=\iota'_{G'_{l_1}}\circ \omega'_1 \circ (\alpha'_2)^{-1}\circ \omega'_2\\&=q'_2\circ \iota'_{2, G_{2,0}}\circ \omega_2
+		\end{align*}
+		The thesis follows since $q_2$ is mono.
+
+		\smallskip \noindent $l_1\neq0$ and $l_2\neq 0$.  We can start noticing that, for every $i\in [0, l_2-1]$ we have
+		\[\begin{split}G_{l_1+i}&=\begin{cases}
+		\pi(G_{2, 0}) & i=0\\
+		G_{2,i} &i\neq 0
+		\end{cases} \\G'_{l_1+i}&=\begin{cases}
+			\pi(G'_{2, 0}) & i=0\\
+			G'_{2,i} &i\neq 0
+			\end{cases} \end{split}\qquad 
+	\begin{split} m_{l_1+i}&=\begin{cases}
+		\alpha^{-1}_{2}\circ m_{2,0} & i=0\\
+		m_{2,i} & i\neq 0
+		\end{cases} \\m'_{l_1+i}&=\begin{cases}
+		(\alpha'_2)^{-1}\circ m'_{2,0} & i=0\\
+		m'_{2,i} & i\neq 0
+		\end{cases}
+	\end{split} \qquad 
+	\begin{split}
+h_{l_1+i}&=h_{2,i}\\h'_{l_1+i}&=h'_{2,i}
+\end{split}\]
+
+We are now going to use the properties of $q_1$ and $q_2$ proven in the previous points, in \Cref{rem:dett} and \Cref{rem:dett2}.
+Let us start showing the consistency of $\varrho$ with respect to the decorations.
+
+On the one hand, computing we get:
+		\begin{align*}
+	q'_2\circ \psi \circ \iota_{2, G_{2,0}}\circ \alpha_2&=q \alpha_2\\&=\xi_\sigma \circ \iota_{G_{l_1+l_1}} \circ \omega_2\\&=\iota'_{G'_{l_1+l_2}}\circ \omega'_2\\&=q_2\circ \iota'_{2, G'_{2, l_2}}\circ \omega'_{2}
+\end{align*}
+
+		\begin{align*}
+			q_2\circ \psi \circ \iota_{2, G_{2,l_2}}\circ \omega_2&=\xi_\sigma\circ q_2\circ \iota_{2, G_{2,l_2}}\circ \omega_2\\&=\xi_\sigma \circ \iota_{G_{l_1+l_1}} \circ \omega_2\\&=\iota'_{G'_{l_1+l_2}}\circ \omega'_2\\&=q_2\circ \iota'_{2, G'_{2, l_2}}\circ \omega'_{2}
+		\end{align*}
+	But $q_2$ is mono and then  $\psi \circ \iota_{2, G_{2,l_2}}\circ \omega_2=\iota'_{2, G'_{\varrho(i)}}\circ \omega'_{2}$ as wanted.
+
+	On the other hand, by we have
+
+	We proceed similarly for the back-matches:
+	\begin{align*}
+		q_2\circ \psi \circ \iota_{2, G_{2,i+1}}\circ h_{2,i}&=\xi_\sigma\circ q_2\circ \iota_{2, G_{2,i+1}}\circ h_{2,i}\\&=\xi_\sigma \circ \iota_{G_{i+l_1+1}} \circ h_{i+l_1}\\&=\iota'_{G'_{\sigma(i+l_1)+1}}\circ h'_{\sigma(i+l_1)}\\&=q_2\circ \iota'_{2, G'_{\varrho(i)+1}}\circ h'_{2, \varrho(i)}
+	\end{align*}
+
+	For every
+
+		Let now $i$ be an index different from $0$ and $\sigma^{-1}(l_1+1)$, then, using \Cref{rem:dett} and the previous point of this lemma we have:
+		\begin{align*}	q_2\circ \psi \circ \iota_{2, G_{2,i}}\circ m_{2,i}&=\xi_\sigma\circ q_2\circ \iota_{2, G_{2,i}}\circ m_{2,i}\\&=\xi_\sigma \circ \iota_{G_{i+l_1}} \circ m_{i+l_1}\\&=\iota'_{G'_{\sigma(i+l_1)}}\circ m'_{\sigma(i+l_1)}\\&=q_2\circ \iota'_{2, G'_{\varrho(i)}}\circ m'_{2, \varrho(i)}
+		\end{align*}
+
+	Using the fact that $q_2$ belongs to $\mathcal{M}$ we conclude that 
+	\[\psi \circ \iota_{2, G_{2,i+1}}\circ h_{2,i}=\iota'_{2, G'_{\varrho(i)+1}}\circ h'_{2, \varrho(i)}\]
+
+		We are left with two cases. First of all, we can notice thatIn this case we have:
+		\[G_{i}=\pi(G_{2,0}) \quad G'_{i}=\pi(G'_{2,0}) \quad m_{l_1}= \alpha^{-1}_2 \circ m_{2,0} \quad m'_{l_1}= (\alpha^{-1}_2)^{-1} \circ m'_{2,0} \]
+
+		Let's compute:
+		\[q_2\circ \psi \circ \iota_{2}\]
 
@@
 
-\begin{notation}
+\begin{proof}
+
 Given $X_1\in \Delta(\der{D}_1)$, $X_2\in \Delta(\der{D}_2)$, $X'_1\in \Delta(\der{D}'_1)$, $X'_2\in \Delta(\der{D}'_2)$, we will denote their coprojections into, respectively, $\lpro \der{D}_1\rpro$, $\lpro \der{D}'_2\rpro$, $\lpro \der{D}'_1\rpro$, $\lpro \der{D}'_2\rpro$ by
@@
 Similarly, given $X\in \Delta(\der{D})$ and $X'\in \Delta(\der{D}')$ we will use $\iota_X\colon X\to \tpro{D}$ and $\iota'_{X'}\colon X'\to \lpro \der{D}' \rpro$ for the coprojections.
-\end{notation}
-
-\begin{proof}
+
 We split the proof in three cases, according to \Cref{def:conc}.
@@
 By \Cref{rem:dett} we get the following diagram, in which the two solid squares are pushouts:
-\[\xymatrix@C=45pt@R=30pt{\pi(G_{2,0}) \ar@/^.4cm/[rrr]^{\id{\pi(G_{2,0})}}\ar@{>->}[d]_{\iota_{1, G_{1,n+1}} \circ \omega_1}\ar[r]_{\iota_{2, G_{2,0}} \circ \alpha_2}& \lpro \der{D}_2 \rpro \ar@{>->}[d]^{q_2}\ar[r]_{\xi_\tau} & \lpro \der{D}'_2 \rpro \ar@{>->}[d]_{q'_2} &\pi(G'_{2,0}) \ar@{>->}[d]^{\iota'_{1, G'_{1,n+1}} \circ \omega'_1} \ar[l]^{\iota'_{2, G'_{2,0}} \circ \alpha'_2}\\ \lpro \der{D}_1 \rpro \ar@/_.4cm/[rrr]_{\xi_\sigma} \ar[r]^{q_1} & \tpro{D} \ar@{.>}[r]^{\xi_{\sigma+\tau}} & \lpro \der{D}'\rpro & \lpro \der{D}'_1\rpro  \ar[l]_{q'_1}}\]
+\[\xymatrix@C=45pt{\pi(G_{2,0}) \ar@/^.4cm/[rrr]^{\id{\pi(G_{2,0})}}\ar@{>->}[d]_{\iota_{1, G_{1,n+1}} \circ \omega_1}\ar[r]_{\iota_{2, G_{2,0}} \circ \alpha_2}& \lpro \der{D}_2 \rpro \ar@{>->}[d]^{q_2}\ar[r]_{\xi_\tau} & \lpro \der{D}'_2 \rpro \ar@{>->}[d]_{q'_2} &\pi(G'_{2,0}) \ar@{>->}[d]^{\iota'_{1, G'_{1,n+1}} \circ \omega'_1} \ar[l]^{\iota'_{2, G'_{2,0}} \circ \alpha'_2}\\ \lpro \der{D}_1 \rpro \ar@/_.4cm/[rrr]_{\xi_\sigma} \ar[r]^{q_1} & \tpro{D} \ar@{.>}[r]^{\xi_{\sigma+\tau}} & \lpro \der{D}'\rpro & \lpro \der{D}'_1\rpro  \ar[l]_{q'_1}}\]
 
@@
 \end{itemize} \end{proof}
+
+We can sum up the results of this section recasting them in the language of permutation equivalence.
+
+\begin{lemma}
+	contenuto...
+\end{lemma} 
+\begin{proof}
+	contenuto...
+\end{proof}

### 2024-12-02 full_version/permutations.tex
minori

@@
 \end{remark}
+
+$\mathcal{M}$-adhesivity of $\X$ guarantes the essential uniqueness of the result obtained rewriting an object, as shown by the next proposition.
+
+\begin{proposition}\label{prop:unique} Let $\X$  be a $\mathcal{M}$-adhesive category.
+Suppose that the two direct derivations $\mathscr{D}$ and $\mathscr{D'}$ below, with the same match and applying the same left $\mathcal{M}$-linear rule $\rho$ are given.
+	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L \ar[d]_{m}& K \ar[d]^{k'}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h'}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}& H & G & \ar@{>->}[l]^{f'} D' \ar[r]_{g'}& H'}\]
+	Then there exist isomorphisms $t\colon D\to D'$ and $s\colon H\to H'$ as in the following diagram.
+	\[\xymatrix@C=40pt{&&D' \ar[r]^{g'} \ar@{>->}@/_.45cm/[dll]_{f'}&H'\\G & L \ar[l]_{m} & K \ar[u]_{k'} \ar[d]^{k}\ar[r]^{r} \ar@{>->}[l]_{l} &R\ar[u]^{h'} \ar[d]_{h}\\&&D\ar@{>->}@/^.45cm/[ull]^{f}\ar@/^.4cm/@{.>}[uu]^(.4){t}|\hole \ar[r]_{g}&H\ar@/_.4cm/@{.>}[uu]_{s}}\]
+\end{proposition}
+\begin{proof}
+	By construction, the pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$ and $n$.
+Thus, the existence of the isomorphism $t\colon D\to D'$ follows from the second point of \Cref{lem:radj}.
+Now, computing we have
+	\begin{align*}
+		g'\circ t \circ k &= g' \circ k'\\&=h'\circ r
+	\end{align*}
+	Hence, we have the wanted $s\colon H\to H'$. To see that $s$ is an isomorphism, consider the diagram 
+	\[\xymatrix{K  \ar@/^.4cm/[rr]^{k'}\ar[d]_{r} \ar[r]_{k}& \ar[r]_{t} D \ar[d]^{g}& D' \ar[d]^{g'}\\ R \ar@/_.4cm/[rr]_{h'} \ar[r]^{h}& H \ar[r]^{s}& H'}\]
+	By hypothesis the whole rectangle and its left half are pushouts, therefore, by \Cref{lem:po1} its right square is a pushout too.
+The claim now follows from the fact that the pushout of an isomorphism is an isomorphism.
+\end{proof}
+
+If we look to direct derivations as transitions, it is natural to consider them as edges in a direct graph.
+Taking objects as vertices objects led us to the following definition \cite{heindel2009category}.
+
+\begin{definition}
+	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ $\mathcal{M}$-adhesive.
+The \emph{DPO-derivation graph} of $(\X, \R)$ is the (large)  directed graph $\gpo$ having as vertices the objects of $\X$ and in which an edge between $G$ and $H$ is a direct derivation $\dder{D}\colon G\Mapsto H$.	A \emph{derivation} $\der{D}$ between two objects $G$ and $H$ is a path between them in $\gpo$.
+The \emph{source} and \emph{target} of $\der{D}$ are, respectively, $G$ and $H$.
+\end{definition}
+
+\begin{remark}
+	We can spell out more explicitly what  a derivation $\dder{D}$ is.
+An \emph{empty derivation} starting and ending in $G$ is just $G$ itself.
+A \emph{non-empty derivation} $\dder{D}$ is a sequence $\{\dder{D}_i\}_{i=0}^n$ of direct derivations such that:
+	\begin{enumerate}
+		\item for every index $i$, $\dder{D}_i$ is a direct derivation $G_i \Mapsto G_{i+1}$;
+		\item $G_0=G$ and $G_{n+1}=H$.
+	\end{enumerate}
+
+	We will call the number $n+1$ the \emph{length} of the derivation, denoted by $\lgh(\der{D})$. We will also say that an empty derivation has length $0$.
+
+	Moreover,  if every $\dder{D}_i$ applies the rule $\rho_i\in R$, then we can define an associated sequence of rules as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.
+\end{remark}
+
+\begin{remark}\label{rem:func}
+	Consider a derivation $\der{D}$ in a left-linear DPO-rewriting system $(\X, \R)$.
+We can take the subcategory $\Delta(\der{D})$ of $\X$ given by the arrows appearing in $\der{D}$.
+This subcategory comes equipped with an inclusion functor $I(\der{D})\colon \Delta(\der{D})\to \X$.
+Moreover, we can further define $\Deltamin(\der{D})$ as the subcategory of $\Delta(\der{D})$ containing only the bottom row of the derivation.
+\end{remark}
+
+\begin{notation}Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ be a derivation. We will depict the $i^\text{th}$ element $\dder{D}_i$ of $\der{D}$ as in the following diagram.  
+	\[\xymatrix{L_i \ar[d]_{m_i}& K_i \ar[d]^{k_i}\ar@{>->}[l]_{l_i} \ar[r]^{r_i} & R_i \ar[d]^{h_i} \\G_{i} & \ar@{>->}[l]^{f_{i}} D_{i} \ar[r]_{g_{i}}& G_{i+1} }\]
+	Notice that, in particular, if $\der{D}\colon G\to H$, then $G_0=G$ and $G_{n+1}=H$.
+When $\der{D}$ has length $1$ we will suppress the indexes.
+In such case, we will also identify $\der{D}$ with its only element.
+\end{notation}
 
@@
 
-$\mathcal{M}$-adhesivity of $\X$ guarantes the essential uniqueness of the result obtained rewriting an object, as shown by the next proposition.
-
-\begin{proposition}\label{prop:unique} Let $\X$  be a $\mathcal{M}$-adhesive category.
-Suppose that the two direct derivations $\mathscr{D}$ and $\mathscr{D'}$ below, with the same match and applying the same left $\mathcal{M}$-linear rule $\rho$ are given.
-	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L \ar[d]_{m}& K \ar[d]^{k'}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h'}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}& H & G & \ar@{>->}[l]^{f'} D' \ar[r]_{g'}& H'}\]
-	Then there exist isomorphisms $t\colon D\to D'$ and $s\colon H\to H'$ as in the following diagram.
-	\[\xymatrix@C=40pt{&&D' \ar[r]^{g'} \ar@{>->}@/_.45cm/[dll]_{f'}&H'\\G & L \ar[l]_{m} & K \ar[u]_{k'} \ar[d]^{k}\ar[r]^{r} \ar@{>->}[l]_{l} &R\ar[u]^{h'} \ar[d]_{h}\\&&D\ar@{>->}@/^.45cm/[ull]^{f}\ar@/^.4cm/@{.>}[uu]^(.4){t}|\hole \ar[r]_{g}&H\ar@/_.4cm/@{.>}[uu]_{s}}\]
-\end{proposition}
-\begin{proof}
-	By construction, the pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$ and $n$.
-Thus, the existence of the isomorphism $t\colon D\to D'$ follows from the second point of \Cref{lem:radj}.
-Now, computing we have
-	\begin{align*}
-		g'\circ t \circ k &= g' \circ k'\\&=h'\circ r
-	\end{align*}
-	Hence, we have the wanted $s\colon H\to H'$. To see that $s$ is an isomorphism, consider the diagram 
-	\[\xymatrix{K  \ar@/^.4cm/[rr]^{k'}\ar[d]_{r} \ar[r]_{k}& \ar[r]_{t} D \ar[d]^{g}& D' \ar[d]^{g'}\\ R \ar@/_.4cm/[rr]_{h'} \ar[r]^{h}& H \ar[r]^{s}& H'}\]
-	By hypothesis the whole rectangle and its left half are pushouts, therefore, by \Cref{lem:po1} its right square is a pushout too.
-The claim now follows from the fact that the pushout of an isomorphism is an isomorphism.
-\end{proof}
-
-If we look to direct derivations as transitions, it is natural to consider them as edges in a direct graph.
-Taking objects as vertices objects led us to the following definition \cite{heindel2009category}.
-
-\begin{definition}
-	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ $\mathcal{M}$-adhesive.
-The \emph{DPO-derivation graph} of $(\X, \R)$ is the (large)  directed graph $\gpo$ having as vertices the objects of $\X$ and in which an edge between $G$ and $H$ is a direct derivation $\dder{D}\colon G\Mapsto H$.	A \emph{derivation} $\der{D}$ between two objects $G$ and $H$ is a path between them in $\gpo$.
-The \emph{source} and \emph{target} of $\der{D}$ are, respectively, $G$ and $H$.
-\end{definition}
-
-\begin{remark}
-	We can spell out more explicitly what  a derivation $\dder{D}$ is.
-An \emph{empty derivation} starting and ending in $G$ is just $G$ itself.
-A \emph{non-empty derivation} $\dder{D}$ is a sequence $\{\dder{D}_i\}_{i=0}^n$ of direct derivations such that:
-	\begin{enumerate}
-		\item for every index $i$, $\dder{D}_i$ is a direct derivation $G_i \Mapsto G_{i+1}$;
-		\item $G_0=G$ and $G_{n+1}=H$.
-	\end{enumerate}
-
-	We will call the number $n+1$ the \emph{length} of the derivation, denoted by $\lgh(\der{D})$. We will also say that an empty derivation has length $0$.
-
-	Moreover,  if every $\dder{D}_i$ applies the rule $\rho_i\in R$, then we can define an associated sequence of rules as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.
-\end{remark}
-
-\begin{remark}\label{rem:func}
-	Consider a derivation $\der{D}$ in a left-linear DPO-rewriting system $(\X, \R)$.
-We can take the subcategory $\Delta(\der{D})$ of $\X$ given by the arrows appearing in $\der{D}$.
-This subcategory comes equipped with an inclusion functor $I(\der{D})\colon \Delta(\der{D})\to \X$.
-Moreover, we can further define $\Deltamin(\der{D})$ as the subcategory of $\Delta(\der{D})$ containing only the bottom row of the derivation.
-\end{remark}
-
-\begin{notation}Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ be a derivation. We will depict the $i^\text{th}$ element $\dder{D}_i$ of $\der{D}$ as in the following diagram.  
-	\[\xymatrix{L_i \ar[d]_{m_i}& K_i \ar[d]^{k_i}\ar@{>->}[l]_{l_i} \ar[r]^{r_i} & R_i \ar[d]^{h_i} \\G_{i} & \ar@{>->}[l]^{f_{i}} D_{i} \ar[r]_{g_{i}}& G_{i+1} }\]
-	Notice that, in particular, if $\der{D}\colon G\to H$, then $G_0=G$ and $G_{n+1}=H$.
-When $\der{D}$ has length $1$ we will suppress the indexes.
-In such case, we will also identify $\der{D}$ with its only element.
-\end{notation}
-
-\begin{example}\todo{esempi di derivazione}
-\end{example}
-
 \begin{definition}
@@
 
-\subsection{Colimits of derivations}
+\subsection{Colimits of derivations}\label{subsec:col}
 Given a DPO-rewriting system $(\X, \R)$,  we have already noted in \Cref{rem:func} that a derivation $\der{D}$  determines a diagram $\Delta(\der{D})$ in $\X$.
@@
 
-\section{Semi-consistent and consistent permutations}
-
-Equipped with the theory developed so far, we can introduce the notions of \emph{semi-consistent} and \emph{consistent} permutation.
-
-\begin{definition}[(Semi)-consistent permutation]\label{def:permcon}
-	Let $\X$ be an $\mathcal{M}$-adhesive category and consider a left-linear DPO-rewriting system $(\X, \R)$ on it.
-Consider two decorated derivations $(\der{D}, \alpha, \omega)$ and  $(\der{D}', \alpha', \omega')$ with the same length $l$ and with isomorphic sources and targets.
-Let also $r(\der{D})=\{\rho_i\}_{i=0}^{l-1}$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^{l-1}$	be sequences of rules associated to the two derivations.
-
-	A \emph{semi-consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma\colon [0,l-1]\to [0,l-1]$  such that, for every $i\in [0,l-1]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
-	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_\sigma}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro}\]
-	\[\xymatrix@C=30pt{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
-
-	A semi-consistent permutation is \emph{consistent} if the following square commutes too.
-	\[\xymatrix@C=30pt{ \pi(G_{l}) \ar[r]^{\omega} \ar[d]_{\omega'} & G_{l} \ar@{>->}[r]^{\iota_{G_{l}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\  G'_{l} \ar@{>->}[rr]_{\iota'_{G'_{l}}} & &\lpro \der{D}' \rpro}\]
-\end{definition}
-
-\begin{remark}\label{rem:inversa}
-	Let  $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations and $\sigma\colon [0,n]\to [0,n]$ be a consistent permutation between them.
-Then its inverse $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$.
-Indeed, it is enough to consider, as mediating isomorphism, the inverse $\xi^{-1}_\sigma$ of $\xi_\sigma$.
-\end{remark}
-
-\begin{example}\label{rem:empty2}
-	Let $(\{G\}, \alpha, \omega)$ and $(\{G'\}, \alpha', \omega')$ be two derivations of length $0$.
-Then $\id{\emptyset}$ is a consistent permutations between them if and only if there exists an isomorphism $\phi\colon G_0\to G'_0$ fitting in the diagrams below
-	\[\xymatrix@C=15pt{&\pi(G) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G\ar[rr]_{\phi} && G' &G \ar[rr]_{\phi} && G' } \]
-	That is, by \Cref{rem:empty} if and only if they are abstract equivalent decorated derivations.
-\end{example}
-
-\begin{remark} \label{rem:coproj} Notice that if $\sigma$ is a semi-consistent permutation between two derivations  $\der{D}$ and $\der{D}'$ of length $l$, then for every  $i\in [0,l-1]$ the diagram below commutes.
-	\[\xymatrix@C=40pt{G_i\ar@/^1cm/[rrr]^{\iota_{G_{i}}}&D_i\ar@/^.4cm/[rr]^(.35){\iota_{D_i}} \ar[r]_{g_i} \ar@{>->}[l]^{f_i}&G_{i+1} \ar[r]_{\iota_{G_{i+1}}}&\tpro{D} \ar[dd]^{\xi_\sigma}\\  L_i \ar[u]^{n_i} \ar[d]_{n'_{\sigma(i)}}& K_i \ar[d]^{k'_{\sigma(i)}} \ar[u]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i} &R\ar[u]^{h_i} \ar[d]_{h'_{\sigma(i)}}\\G'_{\sigma(i)}\ar@/_1cm/[rrr]_{\iota'_{G'_{\sigma(i)}}} &D'_{\sigma(i)}\ar@{>->}[l]_{f'_{\sigma(i)}} \ar[r]^{g'_i} \ar@/_.4cm/[rr]_(.35){\iota'_{D'_{\sigma(i)}}}&G'_{\sigma(i)+1} \ar[r]^{\iota'_{G'_{\sigma(i)+1}}}& \lpro\der{D}' \rpro }\]
-
-	This follows at once from the following chain of identities:
-	\begin{align*}
-		\xi_\sigma \circ \iota_{D_i}\circ k_i&=\xi_\sigma \circ \iota_{G_{i}} \circ f_i\\&= \xi_\sigma \circ \iota_{G_{i}}\circ m_i \circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ m'_i\circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ f'_{\sigma(i)}\circ k'_i\\&=\iota_{D'_\sigma(i)}\circ k_i'
-	\end{align*}
-
-	In particular, the previous diagram entails the following identities.
-	\[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
-\end{remark}
-
-The previous remark allows us to prove the following.
-
-\begin{lemma}\label{prop:isouno} For every semi-consistent permutation $\sigma$ between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, the mediating isomorphism $\xi_\sigma\colon \tpro{D}\to \lpro \der{D}'\rpro$ is unique.
-\end{lemma}
-\begin{proof} Let $\xi'_\sigma$ be another mediating isomorphism, then by \Cref{rem:coproj} we have
-	\[\begin{split}
-		\xi_\sigma \circ \iota_{L_i}&=\iota'_{L_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{L_i}
-	\end{split} \qquad \begin{split}
-		\xi_\sigma \circ \iota_{K_i}&=\iota'_{K_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{K_i}
-	\end{split} \qquad \begin{split}
-		\xi_\sigma \circ \iota_{R_i}&=\iota'_{R_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{R_i}
-	\end{split}\]
-
-	Now, notice that 
-	\begin{align*}
-		\xi_\sigma \circ \iota_{G_0}&=\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}\\&=\xi'_\sigma \circ \iota_{G_0}
-	\end{align*}
-
-	If $\lgh(\der{D})=0$ this is enough to conclude, otherwise we are going to prove by induction that, $\xi_\sigma \circ \iota_{G_i}=\xi'_\sigma\circ \iota_{G_i}$ for every $i\in [0, \lgh(\der{D})-1]$.
-
-	\smallskip \noindent $i=0$. This is simply the result obtained before.
-
-	\smallskip \noindent $i >0$. If $i>0$, we know that there is a pushout square
-	\[\xymatrix{K_{i-1}\ar[r]^{r_{i-1}} \ar[d]_{k_{i-1}}& R_{i-1} \ar[d]^{h_{i-1}}\\ D_{i-1} \ar[r]_{g_{i-1}}& G_i}\] 
-	By \Cref{rem:coproj} and the induction hypothesis we know that
-	\[\begin{split}
-		\xi_\sigma \circ \iota_{G_i}\circ h_{i-1}&=  \xi_\sigma\circ \iota_{R_{i-1}}\\&=\iota'_{R_{\sigma(i-1)}}\\&=\xi'_{\sigma}\circ \iota_{R_{i-1}}\\&=\xi'_{\sigma} \circ \iota_{G_i}\circ h_{i-1}\\&
-	\end{split} \qquad
-	\begin{split}
-		\xi_\sigma \circ \iota_{G_i}\circ g_{i-1}&=\xi_{\sigma}\circ \iota_{D_{i-1}}\\&=\xi_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi'_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi'_{\sigma}\circ \iota_{D_{i-1}} \\&=\xi'_{\sigma}\circ \iota_{G_{i}} \circ g_{i-1}
-	\end{split}
-	\]
-
-	Since $\xi_\sigma \circ \iota_{D_i}$ must be $\xi_\sigma \circ \iota_{G_i}\circ f_i$, we also have
-	$\xi_\sigma \circ \iota_{D_i}=\xi'_\sigma \circ \iota_{D_i}$
-	and the thesis follows.
-\end{proof}
-
-As a next step, we will show that the existence of abstraction equivalences satisfying certain coherence conditions is enough to guarantee the (semi-)consistency of the identical permutation.
-
-\begin{proposition}\label{rem:abscons}
-	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations in an left-linear rewriting system $(\X, \R)$ of length $l$.
-Let also $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ be an abstraction equivalence between $\der{D}$ and $\der{D}'$.
-If $\alpha'\circ \phi_{G_0}=\alpha$ then the the identity $\id{[0,l-1]}$ is a semi-consistent permutation.
-If, moreover, $\omega'\circ \phi_{G_{l}}=\omega$, then $\id{[0,l-1]}$ is a consistent one.
-\end{proposition}
-\begin{proof}
-	For every $X\in \Deltamin(\der{D}) $, let $X'$ the codomain of $\phi_X$.
-Then we can define $\xi_{\id{[0,l-1]}}\colon \tpro{D}\to \lpro \der{D}'\rpro$ as the unique morphism such that, for every $X\in \Deltamin(\der{D})$,
-	\[\xi_{\id{[0,l-1]}} \circ \iota_{X}= \iota'_{X'}\circ \phi_X\]
-
-As a first step we can notice that $\xi_{\id{[0,l-1]}}$ is an isomorphism: indeed we can define $\Theta\colon \lpro\der{D}'\rpro \to \tpro{D}$ as the unique arrow satisfying, for every $X'\in \Deltamin(\der{D}')$
-\[\Theta \circ \iota'_{X'}= \iota_{X}\circ \phi^{-1}_X\]
-
-From the following two computations we can derive that $\Theta$ is the inverse of $\xi_{\id{[0,l-1]}}$.
-\[\begin{split}
-	\Theta \circ \xi_{\id{[0,l-1]}}\circ \iota_{X}&=\Theta \circ\iota'_{X'}\circ \phi_X\\&=\iota_{X}\circ \phi^{-1}_X\circ \phi_X\\&=\iota_X 
-\end{split}\qquad \begin{split}
-\xi_{\id{[0,l-1]}}\circ \Theta \circ \iota'_{X'}&=\xi_{\id{[0,l-1]}}\circ \iota_X\circ \phi^{-1}_{X}\\&=\iota'_{X'}\circ \phi_X\circ \phi^{-1}_{X}\\&=\iota'_{X'}
-\end{split}\]
-
-To conclude, let us observe that all the internal subdiagrams of the following diagrams commutes, guaranteeing the commutativity of the full ones.
-\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[dl]^{\phi_{G_0}} \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro}\]
-\[\xymatrix@C=30pt{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[dl]^{\phi_{G_i}} \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}} & R_i \ar[r]^{h_i} \ar[d]_{h'_{i}}& G_{i+1} \ar[dl]^{\phi_{G_{i+1}}}\ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}} \\G'_{i} \ar[rr]_{\iota'_{G'_{i}}}&& \lpro \der{D}' \rpro& G'_{i+1} \ar[rr]_{\iota'_{G'_{i+1}}}&& \lpro \der{D}' \rpro}\]
-
-For the last half of the thesis, we can reason similarly. Indeed, the diagram below commutes.
-\[\xymatrix@C=30pt{\pi(G_l)\ar[r]^{\omega} \ar[d]_{\omega'} & G_l \ar[dl]^{\phi_{G_l}} \ar@{>->}[r]^{\iota_{G_l}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}}\\ G'_l \ar@{>->}[rr]_{\iota'_{G'_l}} & &\lpro \der{D}' \rpro}\]
-This clearly entails the thesis.
-\end{proof}
-
-The previous proposition, in turn, gives us a technical but quite useful result.
-
-\begin{corollary}\label{cor:fromsemitocons}
-			Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations in an left-linear rewriting system $(\X, \R)$ of length $l$.
-Let also $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ be an abstraction equivalence between $\der{D}$ and $\der{D}'$ such that  $\alpha'\circ \phi_{G_0}=\alpha$.
-If  the identity $\id{[0,l-1]}$ is a consistent permutation, then $\omega'\circ \phi_{G_l}=\omega$, so that $(\der{D}, \alpha, \omega) \equiv^a (\der{D}', \alpha', \omega')$.
-\end{corollary}
-\begin{proof}
-	Let $\xi_{\id{[0, l-1]}}$ be the isomorphism $\tpro{D}\to \lpro\der{D}'\rpro$ witnessing the consistency of $\id{[0, l-1]}$.
-By \Cref{prop:isouno} and \Cref{rem:abscons}, we know that $\xi_{\id{[0,l-1]}} \circ \iota_{X}= \iota'_{X'}\circ \phi_X$ for every object $X\in \Deltamin(\der{D})$.
-Then we have
-	\begin{align*}
-		\iota'_{ G'_{l}}\circ \phi_{G_l}\circ \omega&=\xi_{\id{[0, l-1]}}\circ \iota_{G_l}\circ \omega\\&=\iota'_{G'_l}\circ \omega'
-	\end{align*}
-
-	By the first point of \Cref{lem:colim}, $\iota'_{ G'_{l}}$ is mono and we can conclude.
-\end{proof}
-
-\begin{remark}\label{rem:abscons2}
-	In particular, given a decorated derivation $(\der{D}, \alpha, \omega)$ with source $G$ and target $H$ and two isomorphisms $\phi\colon G'\to G$, $\psi\colon H\to H'$, we know, by \Cref{rem:absequi}, that
-	\[(\der{D}, \alpha, \omega) \equiv^a (\phi * \der{D}, \phi^{-1}\circ \alpha,   \varphi^{-1}_{H} \circ \omega) \qquad (\der{D}, \alpha, \omega) \equiv^a ( \der{D}*\psi, \varphi'_{G} \circ \alpha, \psi \circ \omega )\]
-
-	Now, denoting by $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$, $(\lpro \phi *\der{D} \rpro, \{\iota'_X\}_{X\in \Delta(\phi *\der{D})})$ and $(\lpro \der{D}*\psi \rpro, \{\hat{\iota}_X\}_{X\in \Delta(\der{D}*\psi)})$ the colimiting cocones, in this case we have that the, unique, mediating isomorphisms witnessing the consistency of $\id{[0, \lgh(\der{D})-1]}$ are given by the arrows $\Gamma^{\phi} \colon \tpro{D}\to \lpro \phi*\der{D} \rpro$ and $\Gamma_\psi\colon \tpro{D}\to \lpro \der{D}*\psi \rpro$  such that, for every $X\in \Deltamin(\der{D})$:
-	\[\Gamma^\phi \circ \iota_X:=\begin{cases}
-		\iota'_{G'}\circ \phi^{-1}  & X=G\\
-		\iota'_X & \text{otherwise}
-	\end{cases} \qquad \Gamma_\psi \circ \iota_X:=\begin{cases}
-		\hat{\iota}_{H'}\circ \psi  & X=H\\
-		\hat{\iota}_X & \text{otherwise}
-	\end{cases}\]
-\end{remark}
-
-\begin{example}\todo{identita consistente non implica astrazione}Notice that, in general, there cannot, in general, be generalized to non-empty derivations. A counterexample is the following one.
-\end{example}
-
-We can also observe that (semi-)consistent permutations can be composed, as shown by the next proposition.
-
-\begin{proposition}\label{rem:comp}  Let $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$ be three decorated derivations of length $l$.
-Let $\sigma$ be a consistent permutation between the first two and $\tau$ one between the second and the third, then $\tau \circ \sigma$ is a semi-consistent permutations between the first and the third.
-If, moreover, $\sigma$ and $\tau$ are consistent, then $\tau \circ \sigma$ is consistent too.
-\end{proposition}
-
-\begin{proof} Let $l$ be the length of the three given derivations.
-By hypothesis each subdiagram of the following ones commutes, thus the whole diagrams commute too, proving that $\tau\circ \sigma$ is a semi-consistent permutation with mediating isomorphism given by $\xi_{\tau} \circ \xi_\sigma$.
-		\[\xymatrix@C=18pt{ & G_0 \ar[rr]^{\iota_{G_0}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G_0) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G'_0 \ar[rr]^{\iota'_{G'_0}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\tau}}\\ &\hat{G}_0  \ar[rr]_{\hat{\iota}_{\hat{G}_0}}&& \lpro \hat{\der{D}}\rpro }\]
-		\[\xymatrix@C=18pt{& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_{i+1} \ar[rr]^{\iota_{G_{i+1}}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\tau(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\tau}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\tau(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)+1} \ar[rr]^{\iota'_{G'_{\sigma(i)+1}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\tau}}\\ &\hat{G}_{\tau(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\tau(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\tau(\sigma(i))+1} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\tau(\sigma(i))+1}}}&& \lpro \hat{\der{D}} \rpro	}\]
-
-	If, in addition, $\sigma$ and $\tau$ are consistent then we also have the commutativity of the following additional diagram.
-	\[\xymatrix@C=18pt{&   G_{l} \ar@{>->}[rr]^{\iota_{ G_{l}}} &&\tpro{D} \ar[d]^{\xi_\sigma}\\ \pi({ G_{l}})\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & { G'_{l}} \ar@{>->}[rr]^{\iota'_{{ G'_{l}}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\tau}}\\& \hat{G}_l \ar@{>->}[rr]_{\hat{\iota}_{\hat{G}_l}}&& \lpro \hat{\der{D}} \rpro}\]
-
-	Again this proves that $\xi_\tau \circ \xi_\sigma$ witnesses the constistency of $\tau\circ \sigma$.
-\end{proof}
-
-\subsection{Permutation equivalence}
-
-\begin{definition}
-	contenuto...
-\end{definition}
-
-\begin{theorem}[Characterization of $\equiv_p$]
-	contenuto...
-\end{theorem}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\section{Composing and restricting consistent permutations}
-Now that we have established some initial facts about consistent permutations, we are going to embark in a, quite long, voyage to explore how to restrict them to suitable subderivations.
+We want now to relate the colimit of a composite decorated derivation with the colimits of its components. The following two lemmas will be pivotal to develop the subsequent sections.
 
@@
 
-We can now turn our attention to the case in which a consistent permutation between two composite derivations is given. As a first step we need to prove some technicalities.
+\section{Semi-consistent and consistent permutations}
+
+Equipped with the theory developed so far, we can introduce the notions of \emph{semi-consistent} and \emph{consistent} permutation.
+
+\begin{definition}[(Semi)-consistent permutation]\label{def:permcon}
+	Let $\X$ be an $\mathcal{M}$-adhesive category and consider a left-linear DPO-rewriting system $(\X, \R)$ on it.
+Consider two decorated derivations $(\der{D}, \alpha, \omega)$ and  $(\der{D}', \alpha', \omega')$ with the same length $l$ and with isomorphic sources and targets.
+Let also $r(\der{D})=\{\rho_i\}_{i=0}^{l-1}$ and $r(\der{D}')=\{\rho'_i\}_{i=0}^{l-1}$	be sequences of rules associated to the two derivations.
+
+	A \emph{semi-consistent permutation} between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ is a permutation $\sigma\colon [0,l-1]\to [0,l-1]$  such that, for every $i\in [0,l-1]$, $\rho_i=\rho'_{\sigma(i)}$ and, moreover, there exists a \emph{mediating isomorphism} $\xi_\sigma\colon \tpro{D} \to \lpro \der{D}' \rpro$ fitting in the following diagrams, where $m_i, m'_i, h_i$ and $h'_i$ are, respectively, the matches and back-matches of $\dder{D}_i$ and $\dder{D}'_i$.
+	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_\sigma}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro}\]
+	\[\xymatrix@C=30pt{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_\sigma} & R_i \ar[r]^{h_i} \ar[d]_{h'_{\sigma(i)}}& G_{i+1} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{\sigma(i)}}}&& \lpro \der{D}' \rpro& G'_{\sigma(i)+1} \ar[rr]_{\iota'_{G'_{\sigma(i)+1}}}&& \lpro \der{D}' \rpro}\]
+
+	A semi-consistent permutation is \emph{consistent} if the following square commutes too.
+	\[\xymatrix@C=30pt{ \pi(G_{l}) \ar[r]^{\omega} \ar[d]_{\omega'} & G_{l} \ar@{>->}[r]^{\iota_{G_{l}}} &\tpro{D} \ar[d]^{\xi_\sigma} \\  G'_{l} \ar@{>->}[rr]_{\iota'_{G'_{l}}} & &\lpro \der{D}' \rpro}\]
+\end{definition}
+
+\begin{remark}\label{rem:inversa}
+	Let  $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations and $\sigma\colon [0,n]\to [0,n]$ be a consistent permutation between them.
+Then its inverse $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$.
+Indeed, it is enough to consider, as mediating isomorphism, the inverse $\xi^{-1}_\sigma$ of $\xi_\sigma$.
+\end{remark}
+
+\begin{example}\label{rem:empty2}
+	Let $(\{G\}, \alpha, \omega)$ and $(\{G'\}, \alpha', \omega')$ be two derivations of length $0$.
+Then $\id{\emptyset}$ is a consistent permutations between them if and only if there exists an isomorphism $\phi\colon G_0\to G'_0$ fitting in the diagrams below
+	\[\xymatrix@C=15pt{&\pi(G) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G\ar[rr]_{\phi} && G' &G \ar[rr]_{\phi} && G' } \]
+	That is, by \Cref{rem:empty} if and only if they are abstract equivalent decorated derivations.
+\end{example}
+
+\begin{remark} \label{rem:coproj} Notice that if $\sigma$ is a semi-consistent permutation between two derivations  $\der{D}$ and $\der{D}'$ of length $l$, then for every  $i\in [0,l-1]$ the diagram below commutes.
+	\[\xymatrix@C=40pt{G_i\ar@/^1cm/[rrr]^{\iota_{G_{i}}}&D_i\ar@/^.4cm/[rr]^(.35){\iota_{D_i}} \ar[r]_{g_i} \ar@{>->}[l]^{f_i}&G_{i+1} \ar[r]_{\iota_{G_{i+1}}}&\tpro{D} \ar[dd]^{\xi_\sigma}\\  L_i \ar[u]^{n_i} \ar[d]_{n'_{\sigma(i)}}& K_i \ar[d]^{k'_{\sigma(i)}} \ar[u]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i} &R\ar[u]^{h_i} \ar[d]_{h'_{\sigma(i)}}\\G'_{\sigma(i)}\ar@/_1cm/[rrr]_{\iota'_{G'_{\sigma(i)}}} &D'_{\sigma(i)}\ar@{>->}[l]_{f'_{\sigma(i)}} \ar[r]^{g'_i} \ar@/_.4cm/[rr]_(.35){\iota'_{D'_{\sigma(i)}}}&G'_{\sigma(i)+1} \ar[r]^{\iota'_{G'_{\sigma(i)+1}}}& \lpro\der{D}' \rpro }\]
+
+	This follows at once from the following chain of identities:
+	\begin{align*}
+		\xi_\sigma \circ \iota_{D_i}\circ k_i&=\xi_\sigma \circ \iota_{G_{i}} \circ f_i\\&= \xi_\sigma \circ \iota_{G_{i}}\circ m_i \circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ m'_i\circ l_i\\&=\iota_{G'_{\sigma(i)}}\circ f'_{\sigma(i)}\circ k'_i\\&=\iota_{D'_\sigma(i)}\circ k_i'
+	\end{align*}
+
+	In particular, the previous diagram entails the following identities.
+	\[\xi_\sigma \circ \iota_{L_i}=\iota'_{L_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{K_i}=\iota'_{K_{\sigma(i)}} \quad \xi_\sigma \circ \iota_{R_i}=\iota'_{R_{\sigma(i)}} \]
+\end{remark}
+
+The previous remark allows us to prove the following.
+
+\begin{lemma}\label{prop:isouno} For every semi-consistent permutation $\sigma$ between  $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, the mediating isomorphism $\xi_\sigma\colon \tpro{D}\to \lpro \der{D}'\rpro$ is unique.
+\end{lemma}
+\begin{proof} Let $\xi'_\sigma$ be another mediating isomorphism, then by \Cref{rem:coproj} we have
+	\[\begin{split}
+		\xi_\sigma \circ \iota_{L_i}&=\iota'_{L_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{L_i}
+	\end{split} \qquad \begin{split}
+		\xi_\sigma \circ \iota_{K_i}&=\iota'_{K_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{K_i}
+	\end{split} \qquad \begin{split}
+		\xi_\sigma \circ \iota_{R_i}&=\iota'_{R_{\sigma(i)}}\\&=\xi'_\sigma\circ \iota_{R_i}
+	\end{split}\]
+
+	Now, notice that 
+	\begin{align*}
+		\xi_\sigma \circ \iota_{G_0}&=\iota'_{G'_0}\circ \alpha'\circ \alpha^{-1}\\&=\xi'_\sigma \circ \iota_{G_0}
+	\end{align*}
+
+	If $\lgh(\der{D})=0$ this is enough to conclude, otherwise we are going to prove by induction that, $\xi_\sigma \circ \iota_{G_i}=\xi'_\sigma\circ \iota_{G_i}$ for every $i\in [0, \lgh(\der{D})-1]$.
+
+	\smallskip \noindent $i=0$. This is simply the result obtained before.
+
+	\smallskip \noindent $i >0$. If $i>0$, we know that there is a pushout square
+	\[\xymatrix{K_{i-1}\ar[r]^{r_{i-1}} \ar[d]_{k_{i-1}}& R_{i-1} \ar[d]^{h_{i-1}}\\ D_{i-1} \ar[r]_{g_{i-1}}& G_i}\] 
+	By \Cref{rem:coproj} and the induction hypothesis we know that
+	\[\begin{split}
+		\xi_\sigma \circ \iota_{G_i}\circ h_{i-1}&=  \xi_\sigma\circ \iota_{R_{i-1}}\\&=\iota'_{R_{\sigma(i-1)}}\\&=\xi'_{\sigma}\circ \iota_{R_{i-1}}\\&=\xi'_{\sigma} \circ \iota_{G_i}\circ h_{i-1}\\&
+	\end{split} \qquad
+	\begin{split}
+		\xi_\sigma \circ \iota_{G_i}\circ g_{i-1}&=\xi_{\sigma}\circ \iota_{D_{i-1}}\\&=\xi_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi'_{\sigma}\circ \iota_{G_{i-1}} \circ f_{i-1}\\&=\xi'_{\sigma}\circ \iota_{D_{i-1}} \\&=\xi'_{\sigma}\circ \iota_{G_{i}} \circ g_{i-1}
+	\end{split}
+	\]
+
+	Since $\xi_\sigma \circ \iota_{D_i}$ must be $\xi_\sigma \circ \iota_{G_i}\circ f_i$, we also have
+	$\xi_\sigma \circ \iota_{D_i}=\xi'_\sigma \circ \iota_{D_i}$
+	and the thesis follows.
+\end{proof}
+
+As a next step, we will show that the existence of abstraction equivalences satisfying certain coherence conditions is enough to guarantee the (semi-)consistency of the identical permutation.
+
+\begin{proposition}\label{rem:abscons}
+	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations in an left-linear rewriting system $(\X, \R)$ of length $l$.
+Let also $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ be an abstraction equivalence between $\der{D}$ and $\der{D}'$.
+If $\alpha'\circ \phi_{G_0}=\alpha$ then the the identity $\id{[0,l-1]}$ is a semi-consistent permutation.
+If, moreover, $\omega'\circ \phi_{G_{l}}=\omega$, then $\id{[0,l-1]}$ is a consistent one.
+\end{proposition}
+\begin{proof}
+	For every $X\in \Deltamin(\der{D}) $, let $X'$ the codomain of $\phi_X$.
+Then we can define $\xi_{\id{[0,l-1]}}\colon \tpro{D}\to \lpro \der{D}'\rpro$ as the unique morphism such that, for every $X\in \Deltamin(\der{D})$,
+	\[\xi_{\id{[0,l-1]}} \circ \iota_{X}= \iota'_{X'}\circ \phi_X\]
+
+As a first step we can notice that $\xi_{\id{[0,l-1]}}$ is an isomorphism: indeed we can define $\Theta\colon \lpro\der{D}'\rpro \to \tpro{D}$ as the unique arrow satisfying, for every $X'\in \Deltamin(\der{D}')$
+\[\Theta \circ \iota'_{X'}= \iota_{X}\circ \phi^{-1}_X\]
+
+From the following two computations we can derive that $\Theta$ is the inverse of $\xi_{\id{[0,l-1]}}$.
+\[\begin{split}
+	\Theta \circ \xi_{\id{[0,l-1]}}\circ \iota_{X}&=\Theta \circ\iota'_{X'}\circ \phi_X\\&=\iota_{X}\circ \phi^{-1}_X\circ \phi_X\\&=\iota_X 
+\end{split}\qquad \begin{split}
+\xi_{\id{[0,l-1]}}\circ \Theta \circ \iota'_{X'}&=\xi_{\id{[0,l-1]}}\circ \iota_X\circ \phi^{-1}_{X}\\&=\iota'_{X'}\circ \phi_X\circ \phi^{-1}_{X}\\&=\iota'_{X'}
+\end{split}\]
+
+To conclude, let us observe that all the internal subdiagrams of the following diagrams commutes, guaranteeing the commutativity of the full ones.
+\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[dl]^{\phi_{G_0}} \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro}\]
+\[\xymatrix@C=30pt{L_i \ar[r]^{m_i} \ar[d]_{m'_{\sigma(i)}}& G_i \ar[dl]^{\phi_{G_i}} \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}} & R_i \ar[r]^{h_i} \ar[d]_{h'_{i}}& G_{i+1} \ar[dl]^{\phi_{G_{i+1}}}\ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}} \\G'_{i} \ar[rr]_{\iota'_{G'_{i}}}&& \lpro \der{D}' \rpro& G'_{i+1} \ar[rr]_{\iota'_{G'_{i+1}}}&& \lpro \der{D}' \rpro}\]
+
+For the last half of the thesis, we can reason similarly. Indeed, the diagram below commutes.
+\[\xymatrix@C=30pt{\pi(G_l)\ar[r]^{\omega} \ar[d]_{\omega'} & G_l \ar[dl]^{\phi_{G_l}} \ar@{>->}[r]^{\iota_{G_l}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}}\\ G'_l \ar@{>->}[rr]_{\iota'_{G'_l}} & &\lpro \der{D}' \rpro}\]
+This clearly entails the thesis.
+\end{proof}
+
+The previous proposition, in turn, gives us a technical but quite useful result.
+
+\begin{corollary}\label{cor:fromsemitocons}
+			Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations in an left-linear rewriting system $(\X, \R)$ of length $l$.
+Let also $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ be an abstraction equivalence between $\der{D}$ and $\der{D}'$ such that  $\alpha'\circ \phi_{G_0}=\alpha$.
+If  the identity $\id{[0,l-1]}$ is a consistent permutation, then $\omega'\circ \phi_{G_l}=\omega$, so that $(\der{D}, \alpha, \omega) \equiv^a (\der{D}', \alpha', \omega')$.
+\end{corollary}
+\begin{proof}
+	Let $\xi_{\id{[0, l-1]}}$ be the isomorphism $\tpro{D}\to \lpro\der{D}'\rpro$ witnessing the consistency of $\id{[0, l-1]}$.
+By \Cref{prop:isouno} and \Cref{rem:abscons}, we know that $\xi_{\id{[0,l-1]}} \circ \iota_{X}= \iota'_{X'}\circ \phi_X$ for every object $X\in \Deltamin(\der{D})$.
+Then we have
+	\begin{align*}
+		\iota'_{ G'_{l}}\circ \phi_{G_l}\circ \omega&=\xi_{\id{[0, l-1]}}\circ \iota_{G_l}\circ \omega\\&=\iota'_{G'_l}\circ \omega'
+	\end{align*}
+
+	By the first point of \Cref{lem:colim}, $\iota'_{ G'_{l}}$ is mono and we can conclude.
+\end{proof}
+
+\begin{remark}\label{rem:abscons2}
+	In particular, given a decorated derivation $(\der{D}, \alpha, \omega)$ with source $G$ and target $H$ and two isomorphisms $\phi\colon G'\to G$, $\psi\colon H\to H'$, we know, by \Cref{rem:absequi}, that
+	\[(\der{D}, \alpha, \omega) \equiv^a (\phi * \der{D}, \phi^{-1}\circ \alpha,   \varphi^{-1}_{H} \circ \omega) \qquad (\der{D}, \alpha, \omega) \equiv^a ( \der{D}*\psi, \varphi'_{G} \circ \alpha, \psi \circ \omega )\]
+
+	Now, denoting by $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$, $(\lpro \phi *\der{D} \rpro, \{\iota'_X\}_{X\in \Delta(\phi *\der{D})})$ and $(\lpro \der{D}*\psi \rpro, \{\hat{\iota}_X\}_{X\in \Delta(\der{D}*\psi)})$ the colimiting cocones, in this case we have that the, unique, mediating isomorphisms witnessing the consistency of $\id{[0, \lgh(\der{D})-1]}$ are given by the arrows $\Gamma^{\phi} \colon \tpro{D}\to \lpro \phi*\der{D} \rpro$ and $\Gamma_\psi\colon \tpro{D}\to \lpro \der{D}*\psi \rpro$  such that, for every $X\in \Deltamin(\der{D})$:
+	\[\Gamma^\phi \circ \iota_X:=\begin{cases}
+		\iota'_{G'}\circ \phi^{-1}  & X=G\\
+		\iota'_X & \text{otherwise}
+	\end{cases} \qquad \Gamma_\psi \circ \iota_X:=\begin{cases}
+		\hat{\iota}_{H'}\circ \psi  & X=H\\
+		\hat{\iota}_X & \text{otherwise}
+	\end{cases}\]
+\end{remark}
+
+\begin{example}\todo{identita consistente non implica astrazione}Notice that, in general, there cannot, in general, be generalized to non-empty derivations. A counterexample is the following one.
+\end{example}
+
+We can also observe that (semi-)consistent permutations can be composed, as shown by the next proposition.
+
+\begin{proposition}\label{rem:comp}  Let $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$ be three decorated derivations of length $l$.
+Let $\sigma$ be a consistent permutation between the first two and $\tau$ one between the second and the third, then $\tau \circ \sigma$ is a semi-consistent permutations between the first and the third.
+If, moreover, $\sigma$ and $\tau$ are consistent, then $\tau \circ \sigma$ is consistent too.
+\end{proposition}
+
+\begin{proof} Let $l$ be the length of the three given derivations.
+By hypothesis each subdiagram of the following ones commutes, thus the whole diagrams commute too, proving that $\tau\circ \sigma$ is a semi-consistent permutation with mediating isomorphism given by $\xi_{\tau} \circ \xi_\sigma$.
+		\[\xymatrix@C=18pt{ & G_0 \ar[rr]^{\iota_{G_0}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ \pi(G_0) \ar@/_.2cm/[dr]_{\hat{\alpha}}\ar@/^.2cm/[ur]^{\alpha} \ar[r]^{\alpha'} &G'_0 \ar[rr]^{\iota'_{G'_0}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\tau}}\\ &\hat{G}_0  \ar[rr]_{\hat{\iota}_{\hat{G}_0}}&& \lpro \hat{\der{D}}\rpro }\]
+		\[\xymatrix@C=18pt{& G_i \ar[rr]^{\iota_{G_i}} &&\tpro{D} \ar[d]^{\xi_\sigma}&  &  G_{i+1} \ar[rr]^{\iota_{G_{i+1}}} &&\tpro{D} \ar[d]^{\xi_\sigma} \\ L_i \ar@/_.2cm/[dr]_{\hat{m}_{\tau(\sigma(i))}}\ar@/^.2cm/[ur]^{m_i} \ar[r]^{m'_{\sigma(i)}} &G'_{\sigma(i)} \ar[rr]^{\iota'_{G'_{\sigma(i)}}}  &&\lpro \der{D}'  \rpro \ar[d]^{\xi_{\tau}}&R_i \ar@/_.2cm/[dr]_{\hat{h}_{\tau(\sigma(i))}}\ar@/^.2cm/[ur]^{h_i} \ar[r]^{h'_{\sigma(i)}} & G'_{\sigma(i)+1} \ar[rr]^{\iota'_{G'_{\sigma(i)+1}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\tau}}\\ &\hat{G}_{\tau(\sigma(i))}  \ar[rr]_-{\hat{\iota}_{\hat{G}_{\tau(\sigma(i))}}}&& \lpro \hat{\der{D}}\rpro  && \hat{G}_{\tau(\sigma(i))+1} \ar[rr]_-{\hat{\iota}_{\hat{G}_{\tau(\sigma(i))+1}}}&& \lpro \hat{\der{D}} \rpro	}\]
+
+	If, in addition, $\sigma$ and $\tau$ are consistent then we also have the commutativity of the following additional diagram.
+	\[\xymatrix@C=18pt{&   G_{l} \ar@{>->}[rr]^{\iota_{ G_{l}}} &&\tpro{D} \ar[d]^{\xi_\sigma}\\ \pi({ G_{l}})\ar@/_.2cm/[dr]_{\hat{\omega}}\ar@/^.2cm/[ur]^{\omega} \ar[r]^{\omega'} & { G'_{l}} \ar@{>->}[rr]^{\iota'_{{ G'_{l}}}} && \lpro \der{D}' \rpro \ar[d]^{\xi_{\tau}}\\& \hat{G}_l \ar@{>->}[rr]_{\hat{\iota}_{\hat{G}_l}}&& \lpro \hat{\der{D}} \rpro}\]
+
+	Again this proves that $\xi_\tau \circ \xi_\sigma$ witnesses the constistency of $\tau\circ \sigma$.
+\end{proof}
+
+We have already proved in \Cref{rem:abscons} that the identity defines a consistent permutation between any two representatives of an equivalence class $[\der{D}, \alpha, \omega]_a$.
+This, together with \Cref{rem:comp}, allow us to immediately derive the following fact.
+
+\begin{corollary}\label{prop:abs}
+Let $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}_2, \alpha_2, \omega_2)$ be two decorated derivations and suppose that $\sigma$ is a consistent permutation between them.
+If  $(\der{D}'_1, \alpha'_1, \omega'_1)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$ are such that
+\[ (\der{D}_1, \alpha_1, \omega_1)\equiv^a (\der{D}'_1, \alpha'_1, \omega'_1) \qquad (\der{D}_2, \alpha_2, \omega_2)\equiv^a (\der{D}'_2, \alpha'_2, \omega'_2) \] 
+then $\sigma$ is a consistent permutation between $(\der{D}'_1, \alpha'_1, \omega'_1)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$ too.
+\end{corollary}
+
+\begin{proof} Let $l_1$ and $l_2$ be the lengths of $\der{D}_1$ and $\der{D}_2$.
+By \Cref{rem:abscons} we know that  $\id{[0, l_1-1]}$ is a consistent permutation between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$  and $\id{[0, l_2-1]}$ one between   $(\der{D}_2, \alpha_2, \omega_2)$  and $(\der{D}'_2, \alpha'_2, \omega'_2)$.
+Using \Cref{rem:comp} we get the thesis at once.
+\end{proof}
+
+The previous result suggests that the existence of a consistent permutations induces an equivalence relation on the arrows of $\dpi$. This is formalized by the next definition.
+
+\begin{definition}Let $(\X, \R)$ be a left-linear DPO rewriting system. We say that two arrows
+	$[\der{D}, \alpha, \omega]_a, [\der{D}', \alpha', \omega']_a\colon [G]\rightrightarrows [H]$ in $\dpi$ are \emph{permutation equivalent} if there exists a consistent permutation between $(\der{D}, \alpha, \omega)$  and $(\der{D}', \alpha', \omega')$.
+
+	We will use the notation $[\der{D}, \alpha, \omega]_a, \equiv^p [\der{D}', \alpha', \omega']_a$  to denote permutation equivalence, while we will use $[\der{D}, \alpha, \omega]_a, \equiv_\sigma^p [\der{D}', \alpha', \omega']_a$ to point out a witness $\sigma$ to this relation.
+\end{definition}
+
+\begin{remark}
+	The relation $\equiv^p$ is an equivalence: \Cref{prop:abs} guarantees that it is well-defined, \Cref{rem:abscons} guarantees reflexivity, while symmetry and transitivity follow from, respectively \Cref{rem:inversa} and \Cref{rem:comp}.
+\end{remark}
+
+\begin{notation}
+	We will denote by $[\der{D}, \alpha, \omega]_p$ the equivalence class of $[\der{D}, \alpha, \omega]_a$ with respect to the permutation equivalence.
+\end{notation}
+
+\section{Composing and restricting consistent permutations}
+
+We want now to exploit the results proved at the end of \Cref{subsec:col} to study the behaviour of permutation equivalence with respect to composition of decorated derivations.
+As a first step we need to establish some technical points.
 
 \begin{lemma}\label{prop:uniqu}
-	Let $\sigma\colon [0,n]\to [0,n]$ be a consistent permutations between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ and suppose that 
+	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations such that $[\der{D}, \alpha, \omega]_a\equiv^p_\sigma [\der{D}', \alpha', \omega']_a $. Suppose that 
 	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1) \cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1) \cdot (\der{D}'_2, \alpha'_2, \omega'_2) \]
 
-	 Let $l_1$ be the length of $\der{D}_1$, and suppose that there exists a consistent permutation $\tau:[0,l_1-1]\to [0, l_1-1]$.
+	 Let $l_1$ and $l_2$ be the lengths of, respectively, $\der{D}_1$ and $\der{D}_2$ and suppose that  $[\der{D}_1, \alpha_1, \omega_1]_a\equiv^p_\tau [\der{D}'_1, \alpha'_1, \omega'_1]_a$ for some consistent permutation $\tau\colon [0, l_1-1]\to [0,l_1-1]$.
 If $q_1\colon \lpro \der{D}_1\rpro \to \lpro \der{D}\rpro$  and $q'_1\colon \lpro \der{D}'_1\rpro \to \lpro \der{D}'\rpro$ are the canonical arrows defined in \Cref{rem:dett}, then the following hold true:
@@
 
-We are now ready to prove the central result of this section: the uniqueness of a consistency permutation between two decorated derivations in a consuming rewriting system.
+We want now to show that permutation equivalence is a congruence with respect to composition in $\dpi$.
+This, in turn, will allow us to build  a category in which arrows are are exactly the equivalence classes of permutation equivalent abstract decorated decorations.
+
+\begin{remark}\label{rem:sum}
+	Let $n$ and $m$ be two natural numbers and $\sigma\colon [0, n-1]\to [0,n-1]$ and $\tau\colon [0, m-1]\to [0,m-1]$ be two permutations.
+Then they induce a permutation $[0, n+m-1]\to [0, n+m-1]$.
+To see this, it is enough to define
+		\[\sigma+\tau\colon[0, n+m-1]\to[0, n+m-1] \quad i \mapsto \begin{cases}
+		\sigma(i) & i < n\\
+		\tau(i-n) + n &  n\leq i 
+	\end{cases}\]
+\end{remark}
+
+\begin{lemma}[Composition lemma]\label{lem:sum} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstract decorated derivations such that:
+	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)\]
+
+Suppose that $[\der{D}_1, \alpha_1, \omega_1]_a \equiv^p_\sigma [\der{D}'_1, \alpha'_1, \omega'_1]_a$ and $[\der{D}_2, \alpha_2, \omega_2]_a \equiv^p_\tau [\der{D}'_2, \alpha'_2, \omega'_2]_a$, then:
+\[[\der{D}, \alpha, \omega]_a\equiv^p_{\sigma+\tau} [\der{D}', \alpha', \omega']_a\]
+\end{lemma}
+\begin{proof}
+By \Cref{prop:abs}	it is enough to show that $\sigma+\tau$	is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
+
+We need to fix some notation.	Given $X_1\in \Delta(\der{D}_1)$, $X_2\in \Delta(\der{D}_2)$, $X'_1\in \Delta(\der{D}'_1)$, $X'_2\in \Delta(\der{D}'_2)$, we will denote their coprojections into, respectively, $\lpro \der{D}_1\rpro$, $\lpro \der{D}'_2\rpro$, $\lpro \der{D}'_1\rpro$, $\lpro \der{D}'_2\rpro$ by
+	$\iota_{1, X_1}\colon X_1\to \lpro\der{D}_1\rpro$, $\iota_{1, X_2}\colon X_2\to \lpro\der{D}_1\rpro$, $\iota'_{1, X'_1}\colon X'_1\to \lpro\der{D}'_1\rpro$ and $\iota'_{2, X'_2}\colon X'_2\to \lpro\der{D}_1\rpro$.
+Similarly, given $X\in \Delta(\der{D})$ and $X'\in \Delta(\der{D}')$ we will use $\iota_X\colon X\to \tpro{D}$ and $\iota'_{X'}\colon X'\to \lpro \der{D}' \rpro$ for the coprojections.
+
+	We split the proof in three cases, according to \Cref{def:conc}.
+	\begin{itemize}
+		\item $\lgh(\der{D}_1)=0$. Thus $\lgh(\der{D}'_1)=0$ too  and we have
+		\[
+		(\der{D}, \alpha, \omega)=(\der{D}_2, \alpha_2\circ \omega_1^{-1}\circ \alpha_1, \omega_2) \qquad  (\der{D}', \alpha', \omega')=(\der{D}'_2, \alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1, \omega'_2)\]
+
+		Moreover, in this case $\sigma$ must be $\id{\emptyset}$ and $\sigma+\tau$ must be equal to $\tau$. The thesis now follows from the commutativity of the following diagram.
+		\[\xymatrix@C=35pt{& G_{1,0}\ar[dd]^{\xi_{\id{\emptyset}}} \ar[dr]^{\omega^{-1}_1}&&G_{2,0}\ar[r]^-{\iota_{2, G_{2,0}}} & \lpro \der{D}_2\rpro \ar[dd]^{\xi_{\tau}}\\\pi(G_{1,0})  \ar[ur]^{\alpha_1} \ar[dr]_{\alpha'_1}&& \pi(G_{2,0}) \ar[ur]^{\alpha_2} \ar[dr]_{\alpha'_2}\\& G'_{1,0} \ar[ur]_{(\omega'_1)^{-1}}&&G'_{2,0} \ar[r]_-{\iota'_{2, G_{2,0}}}& \lpro \der{D}'_2\rpro}\]
+
+		\item $\lgh(\der{D}_2)=0$.  As before this implies that also $\lgh(\der{D}'_2)$ is $0$.  Applying \Cref{def:conc} we get 
+		\[
+		(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1 \circ (\alpha_2)^{-1}\circ \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1 \circ (\alpha'_2)^{-1}\circ \omega'_2)\]
+
+		Since $\der{D}_2$ is empty, then $\tau=\id{\emptyset}$ and $\sigma+\tau=\sigma$. Let $n$ be $\lgh(\der{D}_1)$, as before the thesis follows from the diagram below.
+		\[\xymatrix@C=35pt{& G_{2,0}\ar[dd]^{\xi_{\id{\emptyset}}} \ar[dr]^{\alpha^{-1}_2}&&G_{1,n}\ar@{>->}[r]^-{\iota_{1, G_{1,n}}} & \lpro \der{D}_2\rpro \ar[dd]^{\xi_{\sigma}}\\\pi(G_{2,0})  \ar[ur]^{\omega_2} \ar[dr]_{\omega'_2}&& \pi(G_{1,n}) \ar[ur]^{\omega_1} \ar[dr]_{\omega'_1}\\& G'_{2,0} \ar[ur]_{(\alpha'_1)^{-1}}&&G'_{1,n} \ar@{>->}[r]_-{\iota'_{1, G_{1,n}}}& \lpro \der{D}'_2\rpro}\]
+
+		\item  $\lgh(\der{D}_1)\neq0$ and $\lgh(\der{D}_2)\neq 0$. Thus $\der{D}'_1$ and $\der{D}'_2$ are non-empty too. In this case we have
+		\[	(\der{D}, \alpha, \omega)=(\der{D}_1*\omega_1^{-1}\cdot \alpha_2*\der{D}_2, \alpha_1, \omega_2)\qquad
+		(\der{D}', \alpha', \omega')=(\der{D}'_1*(\omega'_1)^{-1}\cdot \alpha'_2*\der{D}'_2, \alpha'_1, \omega'_2)\]
+
+		Let us assume that $\der{D}_1$, $\der{D}'_1$, $\der{D}_2$ and $\der{D}'_2$ are given by
+		\[\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^n \quad \der{D}'_1=\{\dder{D}'_{1,i}\}_{i=0}^n \quad \der{D}_2=\{\dder{D}_{2,i}\}_{i=0}^t \quad \der{D}_2'=\{\dder{D}'_{2,i}\}_{i=0}^t\]
+		By definition of consistent permutation, the rule applied by $\dder{D}_{1,i}$ and the one applied in $\dder{D}_{2,i}$  must coincide with, respectively, the one applied in $\dder{D}'_{1,i}$ and the one applied $\dder{D}'_{2,1}$.
+Let $\dder{D}_{1,i}$, $\dder{D}'_{1,i}$, $\dder{D}_{2,i}$ and $\dder{D}'_{2,i}$ be given, by the following four diagrams.
+		\[\xymatrix{L_{1,i} \ar[d]_{m_{1, i}}& K_{1,i} \ar[d]_{k_{1, i}} \ar[r]^{r_{1,i}} \ar@{>->}[l]_{l_{1,i}} & R_{1,i}\ar[d]^{h_{1, i}} &L_{1,i} \ar[d]_{m'_{1, i}}& K_{1,i} \ar[d]_{k'_{1, i}} \ar[r]^{r_{1,i}} \ar@{>->}[l]_{l_{1,i}} & R_{1,i}\ar[d]^{h'_{1, i}} \\G_{1,i} & D_{1,i} \ar[r]_{g_{1,i}} \ar@{>->}[l]^{f_{1,i}} & G_{1,i+1} & G'_{1,i} & D'_{1,i}\ar[r]_{g'_{1,i}} \ar@{>->}[l]^{f'_{1,i}}  & G'_{1,i+1}}\]
+		\[\xymatrix{L_{2,i} \ar[d]_{m_{2, i}}& K_{2,i} \ar[d]_{k_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h_{2, i}} &L_{2,i} \ar[d]_{m'_{2, i}}& K_{2,i} \ar[d]_{k'_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h'_{2, i}} \\G_{2,i} & D_{2,i} \ar[r]_{g_{2,i}} \ar@{>->}[l]^{f_{2,i}} & G_{2,i+1} & G'_{2,i} & D'_{2,i}\ar[r]_{g'_{2,i}} \ar@{>->}[l]^{f'_{2,i}}  & G'_{2,i+1}}\]
+
+		%Let $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$, $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$, $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$ and $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$ be colimiting cocones.
+		By \Cref{rem:dett} we get the following diagram, in which the two solid squares are pushouts:
+		\[\xymatrix@C=45pt{\pi(G_{2,0}) \ar@/^.4cm/[rrr]^{\id{\pi(G_{2,0})}}\ar@{>->}[d]_{\iota_{1, G_{1,n+1}} \circ \omega_1}\ar[r]_{\iota_{2, G_{2,0}} \circ \alpha_2}& \lpro \der{D}_2 \rpro \ar@{>->}[d]^{q_2}\ar[r]_{\xi_\tau} & \lpro \der{D}'_2 \rpro \ar@{>->}[d]_{q'_2} &\pi(G'_{2,0}) \ar@{>->}[d]^{\iota'_{1, G'_{1,n+1}} \circ \omega'_1} \ar[l]^{\iota'_{2, G'_{2,0}} \circ \alpha'_2}\\ \lpro \der{D}_1 \rpro \ar@/_.4cm/[rrr]_{\xi_\sigma} \ar[r]^{q_1} & \tpro{D} \ar@{.>}[r]^{\xi_{\sigma+\tau}} & \lpro \der{D}'\rpro & \lpro \der{D}'_1\rpro  \ar[l]_{q'_1}}\]
+
+		Moreover, we can point out that, for every index $i\in [0,n+t+2]$ we have
+
+		\[\iota_{G_i}=\begin{cases}q_1\circ \iota_{1, G_{1,i}} & i \leq n\\
+			q_1\circ \iota_{1, G_{1, i}}\circ \omega_1& i=n+1\\
+			q_2\circ \iota_{2, G_{2,i-(n+1)}} & i > n+1 
+		\end{cases} \qquad \iota'_{G'_i}=\begin{cases}q'_1\circ \iota'_{1, G'_{1,i}} & i \leq n\\
+			q'_1\circ \iota'_{1, G'_{1, i}}\circ \omega'_1& i=n+1\\
+			q'_2\circ \iota'_{2, G'_{2,i-(n+1)}} & i > n+1 
+		\end{cases}\]
+
+		Now, on the one hand, the existence of the dotted arrow $\xi_{\sigma+\tau}\colon \tpro{D}\to \lpro \der{D}'\rpro$ in the diagram above follows from the following computation:
+		\begin{align*}
+			q'_1\circ \xi_\sigma \circ \iota_{1, G_{1,n+1}} \circ \omega_1&=q'_1\circ \iota'_{1,G'_{1, n+1}} \circ \omega'_1\\&= q'_2 \circ \iota'_{2, G'_{2,0}} \circ \alpha'_2\\&=q'_2\circ \xi_\tau \circ \iota_{2, G_{2,0}} \circ \alpha_2
+		\end{align*} 
+		On the other hand, we can repeat the same computation for $\xi^{-1}_\sigma$ and $\xi^{-1}_\tau$ to get
+		\begin{align*}
+			q_1\circ \xi^{-1}_\sigma \circ \iota'_{1, G'_{1,n+1}} \circ \omega'_1&=q_1\circ \iota_{1,G_{1, n+1}} \circ \omega_1\\&= q_2 \circ \iota_{2, G_{2,0}} \circ \alpha_2\\&=q_2\circ \xi^{-1}_\tau \circ \iota'_{2, G'_{2,0}} \circ \alpha'_2
+		\end{align*} 
+		Hence there exists a $\psi\colon \lpro \der{D}'\rpro \to \tpro{D}$ such that:
+		\[\psi \circ q'_1=q_1\circ \xi^{-1}_\sigma \qquad \psi \circ q'_2=q_2\circ \xi^{-1}_\tau\]
+
+		Furthermore, the computations below show that $\psi$ is the inverse of $\xi_{\sigma+\tau}$.
+		\[\begin{split}
+			\psi \circ \xi_{\sigma+\tau}\circ  q_1&=\psi \circ q'_1\circ \xi_\sigma \\&=q_1\circ \xi^{-1}_{\sigma}\circ \xi_\sigma\\&=q_1\\\\
+			\xi_{\sigma+\tau}\circ \psi \circ q'_1&=\xi_{\sigma+\tau}\circ q_1\circ \xi^{-1}_\sigma \\&=q'_1\circ \xi_{\sigma}\circ \xi^{-1}_\sigma\\&=q'_1
+		\end{split}\qquad \begin{split}
+			\psi \circ \xi_{\sigma+\tau}\circ  q_2&=\psi \circ q'_2\circ \xi_\tau \\&=q_2\circ \xi^{-1}_{\tau}\circ \xi_\tau\\&=q_2\\ \\ 	\xi_{\sigma+\tau}\circ \psi \circ q'_2&=\xi_{\sigma+\tau}\circ q_2\circ \xi^{-1}_\tau \\&=q'_2\circ \xi_{\tau}\circ \xi^{-1}_\tau\\&=q'_2
+		\end{split}\]
+		To conclude we have to show that $\xi_{\sigma+\tau}$ fits in the diagrams of \Cref{def:permcon}.  For the ones involving the decorations we have:
+		\[\begin{split}
+			\xi_{\sigma+\tau} \circ \iota_{G_{0}}\circ \alpha&=\xi_{\sigma+\tau} \circ q_1 \circ \iota_{1,G_{1,0}}\circ \alpha_1\\&=q_1'\circ \xi_\sigma \circ  \iota_{1,G_{1,0}} \alpha_1\\&=q'_1\circ \iota'_{1, G'_{1,0}}\circ \alpha'_1\\&=\iota'_{G'_0}\circ \alpha'
+		\end{split}  \qquad 
+		\begin{split}
+			\xi_{\sigma+\tau} \circ \iota_{G_{n+t+2}}\circ \omega&=\xi_{\sigma+\tau} \circ q_2 \circ \iota_{2,G_{2,t+1}}\circ \omega_2\\&=q'_2\circ \xi_\tau \circ  \iota_{2,G_{2,t+1}} \omega_2\\&=q'_2\circ \iota'_{2, G'_{2,t+1}}\circ \omega'_2\\&=\iota'_{G'_{n+t+2}}\circ \omega'
+		\end{split}  \]
+
+		Let now $i$ be an index in $[0, n+t+1]$, we proceed splitting the cases.
+		\begin{itemize}
+			\item $i$ is in $[0,n]$. Then we have
+			\begin{align*}
+				\xi_{\sigma+\tau}\circ \iota_{G_i} \circ m_i &= \xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,i}}\circ m_{1,i}\\&=q'_1 \circ \xi_\sigma \circ \iota_{1, G_{1,i}}\circ m_{1,i}\\&= q'_1\circ \iota'_{1, G'_{1,\sigma(i)}}\circ m'_{1,\sigma(i)}\\&=\iota'_{G'_{\sigma(i)}}\circ m'_{\sigma(i)}
+			\end{align*}
+			Now, suppose that $i\neq n$, then 
+			\begin{align*}
+				\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i &= \xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,{i+1}}}\circ h_{1,i}\\&=q'_1\circ \xi_\sigma \circ \iota_{1, G_{1,{i+1}}}\circ h_{1,i}\\&= q'_1\circ \iota'_{1, G'_{1,\sigma(i)+1}}\circ h'_{1,\sigma(i)}
+			\end{align*}
+			and we have two subcases. If $\sigma(i)\neq n$, then \[h'_{1, \sigma(i)}=h'_{\sigma(i)} \qquad q'_1\circ \iota'_{1, G'_{1,\sigma(i)+1}}=
+			\iota'_{G'_{\sigma(i)+1}}\] 
+			and we can conclude. Otherwise, we have
+			\begin{align*}q'_1\circ \iota'_{1, G'_{1,n+1}}\circ h'_{1,n}&=q'_1 \circ \iota'_{1,G'_{1,n+1}} \circ \omega'_1\circ (\omega')^{-1}_1 \circ h'_{1,n}\\&=\iota'_{G'_{n+1}}\circ h'_n
+			\end{align*}
+			yielding again the wanted equality
+			\[\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i=\iota'_{G'_{\sigma(i)+1}}\circ h'_{\sigma(i)}\]
+			Finally, if $i=n$ we get
+			\begin{align*}
+				\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ h_n &= \xi_{\sigma+\tau} \circ \iota_{\pi(G_{1,n+1})} \circ \omega^{-1}_1\circ h_{1,n}\\&= \xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,n+1}} \circ \omega_1 \circ \omega^{-1}_1 \circ h_{1,n}\\&=q'_1 \circ \xi_\sigma \circ \iota_{1, G_{1,n+1}} \circ h_{1,n}\\&=q'_1\circ \iota'_{1, G_{1,\sigma(n)+1}} \circ h'_{1,\sigma(n)}
+			\end{align*}
+			We have again two cases. If $\sigma(n)\neq n$ then we can conclude at once since 
+			\[h'_{1, \sigma(n)}=h'_{\sigma(n)} \qquad q'_1\circ \iota'_{1, G'_{1,\sigma(n)+1}}=
+			\iota'_{G'_{\sigma(n)+1}}\] 
+			While, if $\sigma(n)=n$, then we can use the identities
+			\[(\omega'_1)^{-1}\circ h'_{1, n}=h'_{n} \qquad q'_1\circ \iota'_{1, G'_{1, n+1}}=
+			\iota'_{G'_{n+1}}\circ (\omega'_1)^{-1}\] 
+			to get
+			\begin{align*}
+				\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ h_n &= q'_1\circ \iota'_{1, G_{1,n+1}} \circ h'_{1,n}\\&=\iota'_{G'_{n+1}}\circ (\omega'_1)^{-1}\circ h'_{1,n}\\&=\iota'_{G'_{n+1}} h'_{n}
+			\end{align*}
+			\item $i$ is in $[n+1, n+t+1]$- We proceed  similarly to the point above. First of all we have
+			\begin{align*}
+				\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i &= \xi_{\sigma+\tau} \circ q_2\circ \iota_{1, G_{2,i-n}}\circ h_{2,i-(n+1)}\\&=q'_2 \circ \xi_\tau \circ \iota_{2, G_{2,i-n}}\circ h_{2,i-(n+1)}\\&= q'_2\circ \iota'_{2, G'_{2,\tau(i-n)}}\circ h'_{2,\tau(i-(n+1))}\\&=\iota'_{G'_{\tau(i-n)}}\circ h'_{n+1+\tau(i-(n+1))}
+			\end{align*}
+			Next, supposing that $i\neq n+1$:	
+			\begin{align*}
+				\xi_{\sigma+\tau}\circ \iota_{G_{i}} \circ m_i &= \xi_{\sigma+\tau} \circ q_2\circ \iota_{2, G_{2,i-(n+1)}}\circ m_{2,i-(n+1)}\\&=q'_2\circ \xi_\tau \circ \iota_{2, G_{2,{i-(n+1)}}}\circ m_{2,i-(n+1)}\\&= q'_2\circ \iota'_{2, G'_{2,\tau(i-(n+1))}}\circ m'_{2,\tau(i-(n+1))}
+			\end{align*}
+			and we have again two possibilities.
+If $\tau(i-(n+1))\neq 0$, then the thesis follows from the equalities \[m'_{2, \tau(i-(n+1))}=m'_{(\sigma+\tau)(i)} \qquad q'_2\circ \iota'_{2, G'_{2,\tau(i-(n+1))}}=
+			\iota'_{G'_{(\sigma+\tau)(i)}}\] 
+			Suppose, instead, that $\tau(i-(n+1))= 0$, then we have
+			\begin{align*} q'_2\circ \iota'_{2, G'_{2,0}}\circ m'_{2,0}&=q'_2 \circ \iota'_{2,G'_{2,0}} \circ \alpha'_2 \circ \alpha'^{-1}_2 \circ m'_{2,0}\\&=q'_1\circ \iota'_{1, G'_{1, n+1}}\circ \omega'_1\circ \alpha'^{-1}_2 \circ m'_{2,0}\\&=\iota'_{G'_{n+1}}\circ m'_{n+1}
+			\end{align*}
+			allowing us to conclude again.
+
+			We are left with the case $i=n+1$. Let us compute
+			\begin{align*}
+				\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= \xi_{\sigma+\tau} \circ \iota_{\pi(G_{2,0})} \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,n+1}} \circ \omega_1 \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ q'_2 \circ \iota'_{2,G'_{2,0}} \circ \alpha'_2 \circ (\alpha'_2)^{-1}\circ m_{2,0} \\&=q'_2 \circ \xi_\tau \circ \iota_{2, G_{2,0}} \circ m_{2,0}\\&=q'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}
+			\end{align*}
+			We have again two cases. If $\tau(0)\neq 0$ then $(\sigma+\tau)(i)\neq n+1$ and we can conclude at once since 
+			\[m'_{2, \tau(0)}=m'_{(\sigma+\tau)(n+1)} \qquad q'_2\circ \iota'_{2, G'_{2,\tau(0)}}=
+			\iota'_{G'_{(\sigma+\tau)(0)}}\] 
+			If $\tau(0)=0$, so that  $(\sigma+\tau)(0)= n+1$ we appeal to the equalities
+			\[(\alpha')^{-1}_2\circ m'_{2, 0}=m'_{n+1} \qquad q'_2\circ \iota'_{2, G'_{2, 0}}=
+			\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\] 
+			to get
+			\begin{align*}
+				\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= q'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}\\&=	\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\circ m'_{2,0}\\&=\iota'_{G'_{n+1}}\circ  m'_{n+1}
+			\end{align*}
+		\end{itemize}
+		The thesis now follows at once.	 \qedhere 
+\end{itemize} \end{proof}
+
+\begin{definition}
+Let $(\X, \R)$ be a left-linear DPO rewriting system. The category $\ppi$ is defined as follows: 
+	\begin{itemize}
+	\item objects are isomorphism classes of objects of $\X$;
+	\item an arrow $[G]\to [H]$ is an equivalence class $[\der{D}, \alpha, \omega]_p$ of abstract decorated derivations between $[G]$ and $[H]$;
+	\item given their composition is defined as
+	\[[\der{D}_2, \alpha_2, \omega_2]_p \circ [\der{D}_1, \alpha_1, \omega_1]_p:=[(\der{D}_1, \alpha_1, \omega_1) \cdot (\der{D}_2, \alpha_2, \omega_2)]_p\] 
+	\item the identity on $[G]$ is $[G, \alpha, \alpha]_p$, where $\alpha$ is any isomorphism $\pi(G)\to G$.	\end{itemize}
+\end{definition}
+\begin{remark}By \Cref{rem:empty2}
+\end{remark}
+
+We are now going to proceed towards the central result of this section: the uniqueness of a consistency permutation between two decorated derivations in a consuming rewriting system.
 
 \begin{lemma}\label{lem:impo}
-	Let $(\X,R)$ be a left-linear DPO-rewriting system and let also $(\der{D}_1, \alpha_1, \omega_1)$, $(\der{D}_2, \alpha_2, \omega_2)$ be two composable decorated derivations of length, respectively, $l_1$ and $l_2$.
-Suppose that $\sigma:[0, l_1+l_2-1]\to [0, l_1+l_2-1]$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)$ for some other two composable decorated derivations $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}_2, \alpha_2, \omega_2)$.
-Let, moreover, $\tau:[0,l_1-1]\to [0, l_1-1]$ be a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$.
-Suppose, finally, that  the set
+Let  $(\der{D}_1, \alpha_1, \omega_1)$, $(\der{D}_2, \alpha_2, \omega_2)$ be two composable decorated derivations of length, respectively, $l_1$ and $l_2$  in a left-linear DPO-rewriting system $(\X,R)$.
+Let also  $(\der{D}'_1, \alpha'_1, \omega'_1)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$ be other two composable decorated derivations such that:
+	\begin{align*}(\der{D}_1, \alpha_1, \omega_1)&\equiv^p_\tau(\der{D}'_1, \alpha'_1, \omega'_1)\\
+	(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)&\equiv^p_\sigma (\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)
+	\end{align*}
+
+Suppose, moreover, that the set
 	\[D_{\sigma, \tau}:=\{i\in [0, l_1-1]\mid \sigma(i)\neq \tau(i)\}\]
@@
 		\begin{align*}
-	q'_2\circ \psi \circ \iota_{2, G_{2,0}}\circ \alpha_2&=q \alpha_2\\&=\xi_\sigma \circ \iota_{G_{l_1+l_1}} \circ \omega_2\\&=\iota'_{G'_{l_1+l_2}}\circ \omega'_2\\&=q_2\circ \iota'_{2, G'_{2, l_2}}\circ \omega'_{2}
-\end{align*}
-
-		\begin{align*}
-			q_2\circ \psi \circ \iota_{2, G_{2,l_2}}\circ \omega_2&=\xi_\sigma\circ q_2\circ \iota_{2, G_{2,l_2}}\circ \omega_2\\&=\xi_\sigma \circ \iota_{G_{l_1+l_1}} \circ \omega_2\\&=\iota'_{G'_{l_1+l_2}}\circ \omega'_2\\&=q_2\circ \iota'_{2, G'_{2, l_2}}\circ \omega'_{2}
-		\end{align*}
-	But $q_2$ is mono and then  $\psi \circ \iota_{2, G_{2,l_2}}\circ \omega_2=\iota'_{2, G'_{\varrho(i)}}\circ \omega'_{2}$ as wanted.
-
+\psi \circ \iota_{2, G_{2,0}}\circ \alpha_2&=  \zeta_0\circ \alpha_2\\&=  \iota'_{2, G'_{2,0}}\circ \alpha'_2\circ \alpha^{-1}_2\circ \alpha_2\\&=\iota'_{2, G'_{2,0}}\circ \alpha'_2
+\end{align*}
 	On the other hand, by we have
+		\begin{align*}
+			q'_2\circ \psi \circ \iota_{2, G_{2,l_2}}\circ \omega_2&=\xi_\sigma\circ q_2\circ \iota_{2, G_{2,l_2}}\circ \omega_2\\&=\xi_\sigma \circ \iota_{G_{l_1+l_1}} \circ \omega_2\\&=\iota'_{G'_{l_1+l_2}}\circ \omega'_2\\&=q'_2\circ \iota'_{2, G'_{2, l_2}}\circ \omega'_{2}
+		\end{align*}
+	But $q'_2$ is mono and then  $\psi \circ \iota_{2, G_{2,l_2}}\circ \omega_2=\iota'_{2, G'_{l_2}}\circ \omega'_{2}$ as wanted.
 
@@
 	\begin{align*}
-		q_2\circ \psi \circ \iota_{2, G_{2,i+1}}\circ h_{2,i}&=\xi_\sigma\circ q_2\circ \iota_{2, G_{2,i+1}}\circ h_{2,i}\\&=\xi_\sigma \circ \iota_{G_{i+l_1+1}} \circ h_{i+l_1}\\&=\iota'_{G'_{\sigma(i+l_1)+1}}\circ h'_{\sigma(i+l_1)}\\&=q_2\circ \iota'_{2, G'_{\varrho(i)+1}}\circ h'_{2, \varrho(i)}
-	\end{align*}
-
-	For every
-
-		Let now $i$ be an index different from $0$ and $\sigma^{-1}(l_1+1)$, then, using \Cref{rem:dett} and the previous point of this lemma we have:
-		\begin{align*}	q_2\circ \psi \circ \iota_{2, G_{2,i}}\circ m_{2,i}&=\xi_\sigma\circ q_2\circ \iota_{2, G_{2,i}}\circ m_{2,i}\\&=\xi_\sigma \circ \iota_{G_{i+l_1}} \circ m_{i+l_1}\\&=\iota'_{G'_{\sigma(i+l_1)}}\circ m'_{\sigma(i+l_1)}\\&=q_2\circ \iota'_{2, G'_{\varrho(i)}}\circ m'_{2, \varrho(i)}
-		\end{align*}
-
-	Using the fact that $q_2$ belongs to $\mathcal{M}$ we conclude that 
-	\[\psi \circ \iota_{2, G_{2,i+1}}\circ h_{2,i}=\iota'_{2, G'_{\varrho(i)+1}}\circ h'_{2, \varrho(i)}\]
-
-		We are left with two cases. First of all, we can notice thatIn this case we have:
-		\[G_{i}=\pi(G_{2,0}) \quad G'_{i}=\pi(G'_{2,0}) \quad m_{l_1}= \alpha^{-1}_2 \circ m_{2,0} \quad m'_{l_1}= (\alpha^{-1}_2)^{-1} \circ m'_{2,0} \]
-
-		Let's compute:
-		\[q_2\circ \psi \circ \iota_{2}\]
-
-		Consistency now follows at once. \qedhere 
+		q'_2\circ \psi \circ \iota_{2, G_{2,i+1}}\circ h_{2,i}&=\xi_\sigma\circ q_2\circ \iota_{2, G_{2,i+1}}\circ h_{2,i}\\&=\xi_\sigma \circ \iota_{G_{i+l_1+1}} \circ h_{i+l_1}\\&=\iota'_{G'_{\sigma(i+l_1)+1}}\circ h'_{\sigma(i+l_1)}\\&=q'_2\circ \iota'_{2, G'_{\varrho(i)+1}}\circ h'_{2, \varrho(i)}
+	\end{align*}
+	Again we conclude since $q'_2$ is a monomorphism.
+
+	We turn now to consistency of $\varrho$ with respect to the matches. If $i$ is an index different from $0$ then we have:
+		\begin{align*}	q_2\circ \psi \circ \iota_{2, G_{2,i}}\circ m_{2,i}&=\xi_\sigma\circ q_2\circ \iota_{2, G_{2,i}}\circ m_{2,i}\\&=\xi_\sigma \circ \iota_{G_{i+l_1}} \circ m_{i+l_1}\\&=\iota'_{G'_{\sigma(i+l_1)}}\circ m'_{\sigma(i+l_1)} \\&=
+			\begin{cases}
+			\iota'_{G'_{l_1}}\circ (\alpha'_2)^{-1} \circ m'_{2, 0}  &\sigma(i+l_1) = l_1\\
+				\iota'_{G'_{\sigma(i+l_1)}}\circ m'_{2,\varrho(i)} & \sigma(i+l_1)\neq l_1
+			\end{cases}
+			\\&=\begin{cases}
+			q'_2\circ \iota_{2, G'_{2,0}} \circ \alpha'_2\circ  (\alpha'_1)^{-1} \circ m'_{2, 0}& \varrho(i)=0\\
+			q'_2\circ \iota'_{G'_{2, \varrho(i)}} \circ m'_{2,\varrho(i)} & \varrho(i)\neq 0
+			\end{cases}\\&=q_2\circ \iota'_{2, G'_{\varrho(i)}}\circ m'_{2, \varrho(i)}
+		\end{align*}
+		and the thesis follows since $q'_2$ belongs to $\mathcal{M}$.
+
+	 We are thus left with the case $i=0$. The argument is more or less the same as before:
+	 \begin{align*}
+	 	q_2\circ \psi \circ \iota_{2, G_{2,0}}\circ m_{2,0}&=\xi_\sigma \circ q_2\circ \iota_{2, G_{2,0}}\circ m_{2,0}\\&=\xi_\sigma \circ \iota_{G_{l_1}}\circ \alpha^{-1}_2\circ m_{2,0}\\&=\xi_\sigma \circ \iota_{ G_{l_1}}\circ m_{l_1}\\&=\iota'_{G_{\sigma(l_1)}}\circ m'_{\sigma(l_1)}\\&=\begin{cases}
+	 		\iota'_{G'_{l_1}}\circ (\alpha'_2)^{-1} \circ m'_{2, 0}  &\sigma(l_1) = l_1\\
+	 		\iota'_{G'_{\sigma(l_1)}}\circ m'_{2,\varrho(0)} & \sigma(l_1)\neq l_1
+	 	\end{cases}
+	 	\\&=\begin{cases}
+	 		q'_2\circ \iota_{2, G'_{2,0}} \circ \alpha'_2\circ  (\alpha'_1)^{-1} \circ m'_{2, 0}& \varrho(i)=0\\
+	 		q'_2\circ \iota'_{G'_{2, \varrho(i)}} \circ m'_{2,\varrho(i)} & \varrho(i)\neq 0
+	 	\end{cases}\\&=q_2\circ \iota'_{2, G'_{\varrho(i)}}\circ m'_{2, \varrho(i)}
+	 \end{align*}
+	 But $q_2$ is a mono and so we can conclude.	  \qedhere 
 	\end{enumerate}
@@
 
-Finally, we  end this section showing that consistent permutations between composable abstract derivations yield a consistent permutation between the composites.
-
-\begin{lemma}[Composition lemma]\label{lem:sum} Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two abstract decorated derivations such that:
-	\[(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)\]
-
-	Given a consistent permutation $\sigma\colon [0, \lgh(\der{D}_1)-1]\to [0, \lgh(\der{D}_1)-1]$ between  $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$ and another $\tau\colon [0, \lgh(\der{D}_2)-1]\to [0, \lgh(\der{D}_2)-1]$ between $(\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$, then:
-	\[\sigma+\tau\colon[0, \lgh(\der{D})-1]\to[0, \lgh(\der{D})-1] \quad i \mapsto \begin{cases}
-		\sigma(i) & i < \lgh(\der{D}_1)\\
-		\lgh(\der{D}_1)+\tau(i-\lgh(\der{D}_1)) &   i\geq \lgh(\der{D}_1) 
-	\end{cases}\]
-	is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
-\end{lemma}
-
-\begin{proof}
-
-Given $X_1\in \Delta(\der{D}_1)$, $X_2\in \Delta(\der{D}_2)$, $X'_1\in \Delta(\der{D}'_1)$, $X'_2\in \Delta(\der{D}'_2)$, we will denote their coprojections into, respectively, $\lpro \der{D}_1\rpro$, $\lpro \der{D}'_2\rpro$, $\lpro \der{D}'_1\rpro$, $\lpro \der{D}'_2\rpro$ by
-$\iota_{1, X_1}\colon X_1\to \lpro\der{D}_1\rpro$, $\iota_{1, X_2}\colon X_2\to \lpro\der{D}_1\rpro$, $\iota'_{1, X'_1}\colon X'_1\to \lpro\der{D}'_1\rpro$ and $\iota'_{2, X'_2}\colon X'_2\to \lpro\der{D}_1\rpro$.
-Similarly, given $X\in \Delta(\der{D})$ and $X'\in \Delta(\der{D}')$ we will use $\iota_X\colon X\to \tpro{D}$ and $\iota'_{X'}\colon X'\to \lpro \der{D}' \rpro$ for the coprojections.
-
-We split the proof in three cases, according to \Cref{def:conc}.
-	\begin{itemize}
-	\item $\lgh(\der{D}_1)=0$. Thus $\lgh(\der{D}'_1)=0$ too  and we have
-	\[
-	(\der{D}, \alpha, \omega)=(\der{D}_2, \alpha_2\circ \omega_1^{-1}\circ \alpha_1, \omega_2) \qquad  (\der{D}', \alpha', \omega')=(\der{D}'_2, \alpha'_2\circ (\omega'_1)^{-1}\circ \alpha'_1, \omega'_2)\]
-
-	Moreover, in this case $\sigma$ must be $\id{\emptyset}$ and $\sigma+\tau$ must be equal to $\tau$. The thesis now follows from the commutativity of the following diagram.
-	\[\xymatrix@C=35pt{& G_{1,0}\ar[dd]^{\xi_{\id{\emptyset}}} \ar[dr]^{\omega^{-1}_1}&&G_{2,0}\ar[r]^-{\iota_{2, G_{2,0}}} & \lpro \der{D}_2\rpro \ar[dd]^{\xi_{\tau}}\\\pi(G_{1,0})  \ar[ur]^{\alpha_1} \ar[dr]_{\alpha'_1}&& \pi(G_{2,0}) \ar[ur]^{\alpha_2} \ar[dr]_{\alpha'_2}\\& G'_{1,0} \ar[ur]_{(\omega'_1)^{-1}}&&G'_{2,0} \ar[r]_-{\iota'_{2, G_{2,0}}}& \lpro \der{D}'_2\rpro}\]
-
-\item $\lgh(\der{D}_2)=0$.  As before this implies that also $\lgh(\der{D}'_2)$ is $0$.  Applying \Cref{def:conc} we get 
-\[
-(\der{D}, \alpha, \omega)=(\der{D}_1, \alpha_1, \omega_1 \circ (\alpha_2)^{-1}\circ \omega_2) \qquad (\der{D}', \alpha', \omega')=(\der{D}'_1, \alpha'_1, \omega'_1 \circ (\alpha'_2)^{-1}\circ \omega'_2)\]
-
-	Since $\der{D}_2$ is empty, then $\tau=\id{\emptyset}$ and $\sigma+\tau=\sigma$. Let $n$ be $\lgh(\der{D}_1)$, as before the thesis follows from the diagram below.
-	\[\xymatrix@C=35pt{& G_{2,0}\ar[dd]^{\xi_{\id{\emptyset}}} \ar[dr]^{\alpha^{-1}_2}&&G_{1,n}\ar@{>->}[r]^-{\iota_{1, G_{1,n}}} & \lpro \der{D}_2\rpro \ar[dd]^{\xi_{\sigma}}\\\pi(G_{2,0})  \ar[ur]^{\omega_2} \ar[dr]_{\omega'_2}&& \pi(G_{1,n}) \ar[ur]^{\omega_1} \ar[dr]_{\omega'_1}\\& G'_{2,0} \ar[ur]_{(\alpha'_1)^{-1}}&&G'_{1,n} \ar@{>->}[r]_-{\iota'_{1, G_{1,n}}}& \lpro \der{D}'_2\rpro}\]
-
-\item  $\lgh(\der{D}_1)\neq0$ and $\lgh(\der{D}_2)\neq 0$. Thus $\der{D}'_1$ and $\der{D}'_2$ are non-empty too. In this case we have
-\[	(\der{D}, \alpha, \omega)=(\der{D}_1*\omega_1^{-1}\cdot \alpha_2*\der{D}_2, \alpha_1, \omega_2)\qquad
-(\der{D}', \alpha', \omega')=(\der{D}'_1*(\omega'_1)^{-1}\cdot \alpha'_2*\der{D}'_2, \alpha'_1, \omega'_2)\]
-
-Let us assume that $\der{D}_1$, $\der{D}'_1$, $\der{D}_2$ and $\der{D}'_2$ are given by
-\[\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^n \quad \der{D}'_1=\{\dder{D}'_{1,i}\}_{i=0}^n \quad \der{D}_2=\{\dder{D}_{2,i}\}_{i=0}^t \quad \der{D}_2'=\{\dder{D}'_{2,i}\}_{i=0}^t\]
-By definition of consistent permutation, the rule applied by $\dder{D}_{1,i}$ and the one applied in $\dder{D}_{2,i}$  must coincide with, respectively, the one applied in $\dder{D}'_{1,i}$ and the one applied $\dder{D}'_{2,1}$.
-Let $\dder{D}_{1,i}$, $\dder{D}'_{1,i}$, $\dder{D}_{2,i}$ and $\dder{D}'_{2,i}$ be given, by the following four diagrams.
-\[\xymatrix{L_{1,i} \ar[d]_{m_{1, i}}& K_{1,i} \ar[d]_{k_{1, i}} \ar[r]^{r_{1,i}} \ar@{>->}[l]_{l_{1,i}} & R_{1,i}\ar[d]^{h_{1, i}} &L_{1,i} \ar[d]_{m'_{1, i}}& K_{1,i} \ar[d]_{k'_{1, i}} \ar[r]^{r_{1,i}} \ar@{>->}[l]_{l_{1,i}} & R_{1,i}\ar[d]^{h'_{1, i}} \\G_{1,i} & D_{1,i} \ar[r]_{g_{1,i}} \ar@{>->}[l]^{f_{1,i}} & G_{1,i+1} & G'_{1,i} & D'_{1,i}\ar[r]_{g'_{1,i}} \ar@{>->}[l]^{f'_{1,i}}  & G'_{1,i+1}}\]
-\[\xymatrix{L_{2,i} \ar[d]_{m_{2, i}}& K_{2,i} \ar[d]_{k_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h_{2, i}} &L_{2,i} \ar[d]_{m'_{2, i}}& K_{2,i} \ar[d]_{k'_{2, i}} \ar[r]^{r_{2,i}} \ar@{>->}[l]_{l_{2,i}} & R_{2,i}\ar[d]^{h'_{2, i}} \\G_{2,i} & D_{2,i} \ar[r]_{g_{2,i}} \ar@{>->}[l]^{f_{2,i}} & G_{2,i+1} & G'_{2,i} & D'_{2,i}\ar[r]_{g'_{2,i}} \ar@{>->}[l]^{f'_{2,i}}  & G'_{2,i+1}}\]
-
-%Let $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$, $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$, $(\lpro \der{D}_1*(\omega_1)^{-1}\rpro, \{j_X\}_{X\in \Delta( \der{D}_1*(\omega_1)^{-1})})$ and $(\lpro \der{D}'_1*(\omega'_1)^{-1}\rpro, \{j'_X\}_{X\in \Delta( \der{D}'_1*(\omega'_1)^{-1})})$ be colimiting cocones.
-By \Cref{rem:dett} we get the following diagram, in which the two solid squares are pushouts:
-\[\xymatrix@C=45pt{\pi(G_{2,0}) \ar@/^.4cm/[rrr]^{\id{\pi(G_{2,0})}}\ar@{>->}[d]_{\iota_{1, G_{1,n+1}} \circ \omega_1}\ar[r]_{\iota_{2, G_{2,0}} \circ \alpha_2}& \lpro \der{D}_2 \rpro \ar@{>->}[d]^{q_2}\ar[r]_{\xi_\tau} & \lpro \der{D}'_2 \rpro \ar@{>->}[d]_{q'_2} &\pi(G'_{2,0}) \ar@{>->}[d]^{\iota'_{1, G'_{1,n+1}} \circ \omega'_1} \ar[l]^{\iota'_{2, G'_{2,0}} \circ \alpha'_2}\\ \lpro \der{D}_1 \rpro \ar@/_.4cm/[rrr]_{\xi_\sigma} \ar[r]^{q_1} & \tpro{D} \ar@{.>}[r]^{\xi_{\sigma+\tau}} & \lpro \der{D}'\rpro & \lpro \der{D}'_1\rpro  \ar[l]_{q'_1}}\]
-
-Moreover, we can point out that, for every index $i\in [0,n+t+2]$ we have
-
-\[\iota_{G_i}=\begin{cases}q_1\circ \iota_{1, G_{1,i}} & i \leq n\\
-	q_1\circ \iota_{1, G_{1, i}}\circ \omega_1& i=n+1\\
-	q_2\circ \iota_{2, G_{2,i-(n+1)}} & i > n+1 
-\end{cases} \qquad \iota'_{G'_i}=\begin{cases}q'_1\circ \iota'_{1, G'_{1,i}} & i \leq n\\
-	q'_1\circ \iota'_{1, G'_{1, i}}\circ \omega'_1& i=n+1\\
-	q'_2\circ \iota'_{2, G'_{2,i-(n+1)}} & i > n+1 
-\end{cases}\]
-
-Now, on the one hand, the existence of the dotted arrow $\xi_{\sigma+\tau}\colon \tpro{D}\to \lpro \der{D}'\rpro$ in the diagram above follows from the following computation:
-\begin{align*}
-	q'_1\circ \xi_\sigma \circ \iota_{1, G_{1,n+1}} \circ \omega_1&=q'_1\circ \iota'_{1,G'_{1, n+1}} \circ \omega'_1\\&= q'_2 \circ \iota'_{2, G'_{2,0}} \circ \alpha'_2\\&=q'_2\circ \xi_\tau \circ \iota_{2, G_{2,0}} \circ \alpha_2
-\end{align*} 
-On the other hand, we can repeat the same computation for $\xi^{-1}_\sigma$ and $\xi^{-1}_\tau$ to get
-\begin{align*}
-	q_1\circ \xi^{-1}_\sigma \circ \iota'_{1, G'_{1,n+1}} \circ \omega'_1&=q_1\circ \iota_{1,G_{1, n+1}} \circ \omega_1\\&= q_2 \circ \iota_{2, G_{2,0}} \circ \alpha_2\\&=q_2\circ \xi^{-1}_\tau \circ \iota'_{2, G'_{2,0}} \circ \alpha'_2
-\end{align*} 
-Hence there exists a $\psi\colon \lpro \der{D}'\rpro \to \tpro{D}$ such that:
-\[\psi \circ q'_1=q_1\circ \xi^{-1}_\sigma \qquad \psi \circ q'_2=q_2\circ \xi^{-1}_\tau\]
-
-Furthermore, the computations below show that $\psi$ is the inverse of $\xi_{\sigma+\tau}$.
-\[\begin{split}
-	\psi \circ \xi_{\sigma+\tau}\circ  q_1&=\psi \circ q'_1\circ \xi_\sigma \\&=q_1\circ \xi^{-1}_{\sigma}\circ \xi_\sigma\\&=q_1\\\\
-	\xi_{\sigma+\tau}\circ \psi \circ q'_1&=\xi_{\sigma+\tau}\circ q_1\circ \xi^{-1}_\sigma \\&=q'_1\circ \xi_{\sigma}\circ \xi^{-1}_\sigma\\&=q'_1
-\end{split}\qquad \begin{split}
-	\psi \circ \xi_{\sigma+\tau}\circ  q_2&=\psi \circ q'_2\circ \xi_\tau \\&=q_2\circ \xi^{-1}_{\tau}\circ \xi_\tau\\&=q_2\\ \\ 	\xi_{\sigma+\tau}\circ \psi \circ q'_2&=\xi_{\sigma+\tau}\circ q_2\circ \xi^{-1}_\tau \\&=q'_2\circ \xi_{\tau}\circ \xi^{-1}_\tau\\&=q'_2
-\end{split}\]
-To conclude we have to show that $\xi_{\sigma+\tau}$ fits in the diagrams of \Cref{def:permcon}.  For the ones involving the decorations we have:
-\[\begin{split}
-	\xi_{\sigma+\tau} \circ \iota_{G_{0}}\circ \alpha&=\xi_{\sigma+\tau} \circ q_1 \circ \iota_{1,G_{1,0}}\circ \alpha_1\\&=q_1'\circ \xi_\sigma \circ  \iota_{1,G_{1,0}} \alpha_1\\&=q'_1\circ \iota'_{1, G'_{1,0}}\circ \alpha'_1\\&=\iota'_{G'_0}\circ \alpha'
-\end{split}  \qquad 
-\begin{split}
-\xi_{\sigma+\tau} \circ \iota_{G_{n+t+2}}\circ \omega&=\xi_{\sigma+\tau} \circ q_2 \circ \iota_{2,G_{2,t+1}}\circ \omega_2\\&=q'_2\circ \xi_\tau \circ  \iota_{2,G_{2,t+1}} \omega_2\\&=q'_2\circ \iota'_{2, G'_{2,t+1}}\circ \omega'_2\\&=\iota'_{G'_{n+t+2}}\circ \omega'
-\end{split}  \]
-
-Let now $i$ be an index in $[0, n+t+1]$, we proceed splitting the cases.
-\begin{itemize}
-	\item $i$ is in $[0,n]$. Then we have
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_i} \circ m_i &= \xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,i}}\circ m_{1,i}\\&=q'_1 \circ \xi_\sigma \circ \iota_{1, G_{1,i}}\circ m_{1,i}\\&= q'_1\circ \iota'_{1, G'_{1,\sigma(i)}}\circ m'_{1,\sigma(i)}\\&=\iota'_{G'_{\sigma(i)}}\circ m'_{\sigma(i)}
-	\end{align*}
-	Now, suppose that $i\neq n$, then 
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i &= \xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,{i+1}}}\circ h_{1,i}\\&=q'_1\circ \xi_\sigma \circ \iota_{1, G_{1,{i+1}}}\circ h_{1,i}\\&= q'_1\circ \iota'_{1, G'_{1,\sigma(i)+1}}\circ h'_{1,\sigma(i)}
-	\end{align*}
-	and we have two subcases. If $\sigma(i)\neq n$, then \[h'_{1, \sigma(i)}=h'_{\sigma(i)} \qquad q'_1\circ \iota'_{1, G'_{1,\sigma(i)+1}}=
-	\iota'_{G'_{\sigma(i)+1}}\] 
-	and we can conclude. Otherwise, we have
-	\begin{align*}q'_1\circ \iota'_{1, G'_{1,n+1}}\circ h'_{1,n}&=q'_1 \circ \iota'_{1,G'_{1,n+1}} \circ \omega'_1\circ (\omega')^{-1}_1 \circ h'_{1,n}\\&=\iota'_{G'_{n+1}}\circ h'_n
-	\end{align*}
-	yielding again the wanted equality
-	\[\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i=\iota'_{G'_{\sigma(i)+1}}\circ h'_{\sigma(i)}\]
-	Finally, if $i=n$ we get
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ h_n &= \xi_{\sigma+\tau} \circ \iota_{\pi(G_{1,n+1})} \circ \omega^{-1}_1\circ h_{1,n}\\&= \xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,n+1}} \circ \omega_1 \circ \omega^{-1}_1 \circ h_{1,n}\\&=q'_1 \circ \xi_\sigma \circ \iota_{1, G_{1,n+1}} \circ h_{1,n}\\&=q'_1\circ \iota'_{1, G_{1,\sigma(n)+1}} \circ h'_{1,\sigma(n)}
-	\end{align*}
-	We have again two cases. If $\sigma(n)\neq n$ then we can conclude at once since 
-	\[h'_{1, \sigma(n)}=h'_{\sigma(n)} \qquad q'_1\circ \iota'_{1, G'_{1,\sigma(n)+1}}=
-	\iota'_{G'_{\sigma(n)+1}}\] 
-	While, if $\sigma(n)=n$, then we can use the identities
-	\[(\omega'_1)^{-1}\circ h'_{1, n}=h'_{n} \qquad q'_1\circ \iota'_{1, G'_{1, n+1}}=
-	\iota'_{G'_{n+1}}\circ (\omega'_1)^{-1}\] 
-	to get
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ h_n &= q'_1\circ \iota'_{1, G_{1,n+1}} \circ h'_{1,n}\\&=\iota'_{G'_{n+1}}\circ (\omega'_1)^{-1}\circ h'_{1,n}\\&=\iota'_{G'_{n+1}} h'_{n}
-	\end{align*}
-	\item $i$ is in $[n+1, n+t+1]$- We proceed  similarly to the point above. First of all we have
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{i+1}} \circ h_i &= \xi_{\sigma+\tau} \circ q_2\circ \iota_{1, G_{2,i-n}}\circ h_{2,i-(n+1)}\\&=q'_2 \circ \xi_\tau \circ \iota_{2, G_{2,i-n}}\circ h_{2,i-(n+1)}\\&= q'_2\circ \iota'_{2, G'_{2,\tau(i-n)}}\circ h'_{2,\tau(i-(n+1))}\\&=\iota'_{G'_{\tau(i-n)}}\circ h'_{n+1+\tau(i-(n+1))}
-	\end{align*}
-	Next, supposing that $i\neq n+1$:	
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{i}} \circ m_i &= \xi_{\sigma+\tau} \circ q_2\circ \iota_{2, G_{2,i-(n+1)}}\circ m_{2,i-(n+1)}\\&=q'_2\circ \xi_\tau \circ \iota_{2, G_{2,{i-(n+1)}}}\circ m_{2,i-(n+1)}\\&= q'_2\circ \iota'_{2, G'_{2,\tau(i-(n+1))}}\circ m'_{2,\tau(i-(n+1))}
-	\end{align*}
-	and we have again two possibilities.
-If $\tau(i-(n+1))\neq 0$, then the thesis follows from the equalities \[m'_{2, \tau(i-(n+1))}=m'_{(\sigma+\tau)(i)} \qquad q'_2\circ \iota'_{2, G'_{2,\tau(i-(n+1))}}=
-	\iota'_{G'_{(\sigma+\tau)(i)}}\] 
-	Suppose, instead, that $\tau(i-(n+1))= 0$, then we have
-	\begin{align*} q'_2\circ \iota'_{2, G'_{2,0}}\circ m'_{2,0}&=q'_2 \circ \iota'_{2,G'_{2,0}} \circ \alpha'_2 \circ \alpha'^{-1}_2 \circ m'_{2,0}\\&=q'_1\circ \iota'_{1, G'_{1, n+1}}\circ \omega'_1\circ \alpha'^{-1}_2 \circ m'_{2,0}\\&=\iota'_{G'_{n+1}}\circ m'_{n+1}
-	\end{align*}
-	allowing us to conclude again.
-
-	We are left with the case $i=n+1$. Let us compute
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= \xi_{\sigma+\tau} \circ \iota_{\pi(G_{2,0})} \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ q_1\circ \iota_{1, G_{1,n+1}} \circ \omega_1 \circ (\alpha'_2)^{-1}\circ m_{2,0}\\&=\xi_{\sigma+\tau} \circ q'_2 \circ \iota'_{2,G'_{2,0}} \circ \alpha'_2 \circ (\alpha'_2)^{-1}\circ m_{2,0} \\&=q'_2 \circ \xi_\tau \circ \iota_{2, G_{2,0}} \circ m_{2,0}\\&=q'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}
-	\end{align*}
-	We have again two cases. If $\tau(0)\neq 0$ then $(\sigma+\tau)(i)\neq n+1$ and we can conclude at once since 
-	\[m'_{2, \tau(0)}=m'_{(\sigma+\tau)(n+1)} \qquad q'_2\circ \iota'_{2, G'_{2,\tau(0)}}=
-	\iota'_{G'_{(\sigma+\tau)(0)}}\] 
-	If $\tau(0)=0$, so that  $(\sigma+\tau)(0)= n+1$ we appeal to the equalities
-	\[(\alpha')^{-1}_2\circ m'_{2, 0}=m'_{n+1} \qquad q'_2\circ \iota'_{2, G'_{2, 0}}=
-	\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\] 
-	to get
-	\begin{align*}
-		\xi_{\sigma+\tau}\circ \iota_{G_{n+1}} \circ m_{n+1} &= q'_2\circ \iota'_{2, G_{2,\tau(0)}} \circ m'_{2,\tau(0)}\\&=	\iota'_{G'_{n+1}}\circ (\alpha'_2)^{-1}\circ m'_{2,0}\\&=\iota'_{G'_{n+1}}\circ  m'_{n+1}
-	\end{align*}
-\end{itemize}
-The thesis now follows at once.	 \qedhere 
-\end{itemize} \end{proof}
-
-We can sum up the results of this section recasting them in the language of permutation equivalence.
-
-\begin{lemma}
+\begin{corollary}\label{cor:epi}
 	contenuto...
-\end{lemma} 
-\begin{proof}
-	contenuto...
-\end{proof}
+\end{corollary}

### 2024-12-03 full_version/permutations.tex
fine permutazioni

@@
 
+\begin{remark}\label{rem:ugu}
+	It is worth noticing that, by \Cref{rem:empty2}, the permutation equivalence relation reduces to abstract equivalence in the case of empty derivations.
+This means that, given an object $G$, we have ~$[\{G\}, \alpha, \omega]_a=[\{G\}, \alpha, \omega]_p$.
+\end{remark}
+
 \section{Composing and restricting consistent permutations}
@@
 	\item an arrow $[G]\to [H]$ is an equivalence class $[\der{D}, \alpha, \omega]_p$ of abstract decorated derivations between $[G]$ and $[H]$;
-	\item given their composition is defined as
+	\item given two arrows $[\der{D}_1, \alpha_1, \omega_1] _p\colon [G]\to [H]$ and $[\der{D}_2, \alpha_2, \omega_2] _p\colon [H]\to [K]$, their composition is defined as
 	\[[\der{D}_2, \alpha_2, \omega_2]_p \circ [\der{D}_1, \alpha_1, \omega_1]_p:=[(\der{D}_1, \alpha_1, \omega_1) \cdot (\der{D}_2, \alpha_2, \omega_2)]_p\] 
-	\item the identity on $[G]$ is $[G, \alpha, \alpha]_p$, where $\alpha$ is any isomorphism $\pi(G)\to G$.	\end{itemize}
+	\item the identity on $[G]$ is $[\{G\}, \alpha, \alpha]_p$, where $\alpha$ is any isomorphism $\pi(G)\to G$.	\end{itemize}
 \end{definition}
-\begin{remark}By \Cref{rem:empty2}
-\end{remark}
-
-We are now going to proceed towards the central result of this section: the uniqueness of a consistency permutation between two decorated derivations in a consuming rewriting system.
+\begin{remark} We can point out two facts;
+	\begin{itemize}
+		\item the composition 	$[\der{D}_2, \alpha_2, \omega_2]_p \circ [\der{D}_1, \alpha_1, \omega_1]_p$ coincides with the permuation equivalence class of $	[\der{D}_2, \alpha_2, \omega_2]_a \circ [\der{D}_1, \alpha_1, \omega_1]_a$;
+		\item by \Cref{rem:ugu}, $[\{G, \alpha, \alpha\}]_p=[\{G, \alpha, \alpha\}]_a$, guaranteeing that it is the neutral element with respect of the composition we have defined above.
+	\end{itemize}
+
+	In particular, there is a quotient functor $\Pi\colon \dpi\to \ppi$ which is the identity on objects and sends an abstraction equivalence class to its permutation equivalence one.
+\end{remark}
+
+\subsection{Uniqueness of consistent permutations}
+
+We are now going to proceed towards the central result of this section: the uniqueness of a consistent permutation between two decorated derivations in a consuming DPO rewriting system.
 
@@
 
+The previous results, in turn, allows us to deduce a property which is in some sense the converse of the Composition \Cref{lem:sum}.
+
 \begin{lemma}[Restriction Lemma]\label{lem:presuffix} Let $(\X, \R)$ be a consuming left-linear DPO-rewriting system.
-Let also $(\der{D}_1, \alpha_1, \omega_1)$, $(\der{D}_2, \alpha_2, \omega_2)$ be two composable decorated derivations of length, respectively, $l_1$ and $l_2$.
-Suppose that $\sigma\colon [0, l_1+l_2-1]\to [0, l_1+l_2-1]$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)$ for some other two composable decorated derivations $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}_2, \alpha_2, \omega_2)$.
-If $\tau\colon [0,l_1-1]\to [0, l_1-1]$ is a consistent permutation between $(\der{D_1}, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$.
-Then the following hold true:
+Let also $(\der{D}_1, \alpha_1, \omega_1)$, $(\der{D}_2, \alpha_2, \omega_2)$ be two composable decorated derivations of length, respectively, $l_1$ and $l_2$ such that there are  other two composable decorated derivations $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}_2, \alpha_2, \omega_2)$ with the property that
+	\[[(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)]_a\equiv^p_\sigma[(\der{D}'_1, \alpha'_1, \omega'_1)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)]_a\]
+
+Suppose, finally, that $[\der{D_1}, \alpha_1, \omega_1]_a \equiv^p_\tau [\der{D}'_1, \alpha'_1, \omega'_1]_a$ for some $\tau$. Then the following hold true:
 	\begin{enumerate}
@@
 \end{lemma}
+
 \begin{proof}
@@
 	We can also notice that,  by \Cref{lem:impo}, $\sigma(i)=\tau(i)$ for every $i\in  [0, l_1-1]$.
-In particular, this implies that the image  $[l_1, l_1+l_2-1]$ through $\sigma$ is again the interval $[l_1, l_1+l_2-1]$ and that $\varrho$ is well-defined.
+In particular, this implies that the image  $[l_1, l_1+l_2-1]$ through $\sigma$ is again the interval $[l_1, l_1+l_2-1]$, that $\varrho$ is well-defined and $\sigma=\tau +\varrho$.
 Moreover, if $l_1\neq 0$, then $l_1-1$ is the maximum of $E_{\sigma,\tau}$.
@@
 We know that $G_{2,0}$ and $G'_{2,0}$ are isomorphic to, respectively, $G_{1, l_1}$ and $G'_{1, l_1}$.
-By hypothesis $\tau$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$, so that $G_{1,l_1}$ and $G'_{1, l_1}$ are isomorphic too.
+By \Cref{prop:abs}, $\tau$ is a consistent permutation between $(\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}'_1, \alpha'_1, \omega'_1)$, so that $G_{1,l_1}$ and $G'_{1, l_1}$ are isomorphic too.
 We can therefore consider as $\zeta_0$ the arrow $\iota'_{2, G'_{2,0}}\circ (\alpha'_2)\circ \alpha^{-1}_2$.
@@
 \begin{corollary}\label{cor:epi}
-	contenuto...
+	Let $(\X, \R)$ be a consuming left-linear DPO rewriting, then in $\ppi$ every arrow is epi.
 \end{corollary}
+\begin{proof}
+Let $[\der{D}, \alpha, \omega]_p$ be an arrow in $\ppi$ between $[G]\to [H]$ and suppose that two arrows $[\der{D}_1, \alpha_1, \omega_1]_p, [\der{D}_2, \alpha_2, \omega_2]_p\colon [H]\to [K]$  are given such that
+\[[\der{D}_1, \alpha_1, \omega_1]_p\circ [\der{D}, \alpha, \omega]_p=[\der{D}_2, \alpha_2, \omega_2]_p\circ [\der{D}, \alpha, \omega]_p\]
+
+By construction and \Cref{prop:abs}, the previous equation entails the existence of a consistent permutation $\sigma$ between $(\der{D}, \alpha, \omega)\cdot (\der{D}_1, \alpha_1, \omega_1)$ and $(\der{D}, \alpha, \omega)\cdot (\der{D}_2, \alpha_2, \omega_2)$.
+Since the identity is a consistent permutation between $(\der{D}, \alpha, \omega)$ and itself, the thesis follows immediately from \Cref{lem:presuffix}.
+\end{proof}

### 2024-12-05 full_version/leftlinear.tex
permutazioni again
minori

@@
 
-\begin{definition}[Switch] \label{def:switch}
+\begin{definition}[Concrete  and decorated switch] \label{def:switch}
 	Let $\X$ be an $\mathcal{M}$-adhesive category 
@@
 	of two sequentially independent derivations $\dder{D}_0$,
-	$\dder{D}_1$ with independence pair $(i_0, i_1)$, as in the diagram
-	on the left below. A \emph{switch} of $\der{D}$ along $(i_0,i_1)$ is
+	$\dder{D}_1$ with independence pair $(i_0, i_1)$, as in the following diagram. 
+		\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
+		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
+		\ar@{.>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
+		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{.>}@/_.25cm/[dlll]^(.4){i_1}
+		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
+		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
+		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
+		\ar[rr]_{g_1}&& G_2}
+	\]
+
+	A \emph{concrete switch} of $\der{D}$ along $(i_0,i_1)$ is
 	a derivation $\der{E}=\{\dder{E}_i\}_{i=0}^1$, between the same objects and using the same rules
@@
 	\[
-	\def\objectstyle{\scriptstyle}\def\labelstyle{\scriptstyle}
-	\xymatrix@C=1.1mm@R=8mm{
-		{L_0} \ar[d]_{m_0}
-		& & {K_0} \ar@{>->}[ll]_{l_0} \ar[rr]^{r_0} \ar[d]_{k_0}
-		& & {R_0} \ar[drr]|(.35)\hole_(.6){h_0}  \ar@/^.22cm/[drrrrrr]|(.3)\hole^(.75){i_0}
-		& & & & 
-		% 
-		{L_1}\ar[dll]|(.35)\hole^(.6){m_1} \ar@/_.22cm/_(.75){i_1}[dllllll]
-		& & {K_1} \ar@{>->}[ll]_{l_1} \ar[rr]^{r_1} \ar[d]^{k_1}
-		& & {R_1} \ar[d]^{h_1} \\
-		% 
-		% 
+	\xymatrix@R=20pt@C=20pt{
+		{L_1} \ar[d]_{m_0'}
+		&&  {K_1} \ar@{>->}[ll]_{l_1} \ar[r]^{r_1} \ar[d]_{k_0'}
+		&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{.>}_(.4){i_0'}|(.32)\hole[drrr]
+		& & 
+		{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{.>}^(.4){i_1'}[dlll] 
+		&  {K_0} \ar@{>->}[l]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
+		& & {R_0} \ar[d]^{h_1'} \\		
 		{G_0}
-		& & {D_0} \ar@{>->}[ll]^{f_0} \ar[rrrr]_{g_0}
-		& & & & {G_1} & &
-		& &  {D_1} \ar@{>->}[llll]^{f_1} \ar[rr]_{g_1}
-		& & {G_2}
-	}
-	% 
-	\xymatrix@C=1.1mm@R=8mm{
-		{L_1} \ar[d]_{m_0'}
-		& & {K_1} \ar@{>->}[ll]_{l_1} \ar[rr]^{r_1} \ar[d]_{k_0'}
-		& & {R_1} \ar[drr]|(.35)\hole_(.6){h_0'}  \ar@/^.22cm/@{.>}^(.75){i_0'}|(.3)\hole[drrrrrr]
-		& & & & 
-		% 
-		{L_0}\ar[dll]|(.35)\hole^(.6){m_1'} \ar@/_.22cm/@{.>}_(.75){i_1'}[dllllll] 
-		& & {K_0} \ar@{>->}[ll]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
-		& & {R_0} \ar[d]^{h_1'} \\
-		% 
-		% 
-		{G_0}
-		& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rrrr]_{g_0'}
-		& & & & {G'_1} & &
-		& &  {D_1'} \ar@{>->}[llll]^{f_1'} \ar[rr]_{g_1'}
+		& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rr]_{g_0'}
+		& &  {G'_1} 
+		& &  {D_1'} \ar@{>->}[ll]^{f_1'} \ar[rr]_{g_1'}
 		& & {G_2}  }
-	%
 	\]
@@
 
-	If a switch of $\dder{D}_0$ and $\dder{D}_1$ exists we say that
-	they are \emph{switchable}.
+	If a concrete switch of $\dder{D}_0$ and $\dder{D}_1$ exists we say that they are \emph{switchable}.
+
+	Let $(\der{D}, \alpha, \omega)$ be a decorated derivation of length $2$, and $(i_0, i_1)$ an independence pair between $\dder{D}_0$ and $\dder{D}_1$.
+A \emph{decorated switch} of $(\der{D}, \alpha, \omega)$ along $(i_0, i_1)$ is $(\der{E}, \alpha, \omega)$, where $\der{E}$ is a switch for $\der{D}$ along $(i_0, i_1)$.
 \end{definition}
@@
 \end{center}
-
 	\end{example}
 
+\begin{remark}\label{rem:switch}
+
+Let $\der{E}=\{\dder{E}_i\}_{i=0}^1$ be a concrete switch for $\dder{D}_0$
+and $\dder{D}_1$ along an independence pair $(i_0, i_1)$, then by definition we have an independence pair $(i'_0, i'_1)$ between $\dder{E}_0$ and $\dder{E}_1$ such that
+\[
+m_0=f_0' \circ i_1'
+\quad h_1=g_1' \circ i_0'
+\quad m_0'= f_0 \circ i_1
+\quad h_1'= g_{1}\circ i_0\]
+
+Moreover, $\der{D}$ uses the same rule of $\der{E}$ in reverse order, thus it is a concrete switch for $\der{E}$ along $(i_0', i_1')$.
+
+Similarly, if $(\der{E}, \alpha, \omega)$ is a decorated switch for $(\der{D}, \alpha, \omega)$ along $(i_0, i_1)$, then the latter is a decorated switch for the former along $(i'_0, i'_1)$.
+\end{remark}
+
+We can now turn to prove the fundamental property that we need to rely upon:  any decorated switch induces a consistent permutation.
+
+\begin{lemma}\label{lem:switchtoperm}
+	Let $(\der{D}, \alpha, \omega)$ be a decorated derivations of length $2$ and suppose that $(\der{E}, \alpha, \omega)$ is a decorated switch for it along the independence pair $(i_0, i_1)$.
+Then the following are true:
+	\begin{enumerate}
+		\item there exists an arrow $\kappa\colon G_1\to \tpro{E}$ such that 
+		\[\kappa \circ g_0 = \iota_{\der{E}, G_0}\circ f_0 \qquad \kappa\circ h_0= \iota_{\der{E}, R_0}\]
+\item there exists an isomorphism $\phi\colon \tpro{D}\to \tpro{E}$ such that
+\[\phi \circ \iota_{\der{D}, G_0}=\iota_{\der{E}, G_0} \qquad \phi \circ \iota_{\der{D}, G_1}=\kappa \qquad \phi \circ \iota_{\der{D}, G_2}=\iota_{\der{E}, G_2}\]
+		\item $2$-cycle $\tau_{0,1}$ is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}, \alpha, \omega)$.
+	\end{enumerate}
+\end{lemma}
+\begin{proof}\begin{enumerate}
+		\item 
+		\item \qedhere 
+	\end{enumerate}
+\end{proof}
+
+\subsection{Strong-enforcing and well-switching rewriting systems}
+
+\subsection{Abstract switches}
 We can now prove some properties relating switching and abstraction equivalence. As a first step we can show that switches along the same independence paire are unique up to abstraction equivalence.
 
-\begin{lemma}[Uniqueness of switches]
+\begin{lemma}[Uniqueness of concrete switches]
 	\label{thm:switch_uni}
@@
 
-\begin{corollary}\label{cor:switch}
+\begin{definition}
+	contenuto...
+\end{definition}
+
+\begin{corollary}[Uniqueness of switches]\label{cor:switch}
 	\todo{switches}
@@
 
-\begin{corollary}\label{cor:cons}
-	\todo{consistency of switch}
+Another useful property of switches is that they can be performed back and forth, giving back the original derivation. This is the content of the following two results.
+
+\todo{switch di switch}
+
+\begin{proposition}
+	contenuto...
+\end{proposition}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{corollary}
+	contenuto...
 \end{corollary}
-
-Another useful property of switches is that they can be performed back and forth, giving back the original derivation. This is the content of the following two results.
-
-\todo{switch di switch}
-
-\begin{proposition}
-	contenuto...
-\end{proposition}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{corollary}
-	contenuto...
-\end{corollary}
-
-As we mentioned, for linear rewriting systems
-it is canonical to identify
-derivations that are equal ``up to switching'', i.e.~that differ
-only in the order of independent steps. The same notion can be given
-for left-linear rewriting systems by relying on the notion of switch.
-
-We  recall some notations on permutations.  A \emph{permutation} on
-$\interval[0]{n}$ is a bijection
-$\sigma : \interval[0]{n} \to \interval[0]{n}$. It is a
-\emph{transposition} $\nu$ if there are $i, j \in \interval{n}$,
-$i \neq j$ such that $\sigma(i)=j$, $\sigma(j) = i$, and
-$\sigma(k) = k$ otherwise; it is denoted as $\transp{i}[j]$. Given a permutation $\perm$, 
-an \emph{inversion} for $\sigma$ is a pair $(i,j)$ such that $i<j$ and
-$\sigma(j)< \sigma(i)$; $\inv{\sigma}$ denotes the set of
-inversions of $\perm$.
-
-Switch equivalence is now defined as the equivalence relating derivations that 
-can be obtained one from another by a sequence of switches. Moreover, intermediate graphs can be taken up to isomorphism according to abstraction equivalence.
-
-\begin{definition}[Switching sequence]
-	\label{de:switch-equivalence}
-	Let $(\X, \R)$ be a left-linear rewriting system.  Let also
-	$\der{D}, \der{E} : G \Mapsto H$ be derivations with the same
-	length, $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and
-	$\der{E}=\{\dder{E}_{i}\}_{i=0}^n$. If
-	$\dder{D}_i \cdot \dder{D}_{i+1}$ is a switch of
-	$\dder{E}_i \cdot \dder{E}_{i+1}$ for some $i \in [0,n-1]$ and  $\dder{D}_j = \dder{E}_j$ for each $j \not \in \{i,i+1\}$ then we write
-	$\der{D} \shift{\transp{i}} \der{E}$. 
-	A \emph{switching sequence} is a sequence $\{\der{D}_{k}\}_{k=0}^m$
-	of derivations such that
-	$\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
-	\shift{\nu_m} \der{D}_m$  with $\nu_{k} = \transp{i_k}$.
-
-	Let us denote by $\nu_{k,h}$ the composition
-	$\nu_h \circ \nu_{h-1} \circ \ldots \nu_k$. We say that the
-	switching sequence \emph{consists of inversions} if for all
-	$k \in \interval[0]{m}$ the transposition $\nu_k$ is an inversion
-	for $\nu_{1,m}$.
-
-	Two derivations $\der{D}, \der{E}:G\Mapsto H$ are \emph{switch
-		equivalent}, written $\der{D}\equiv^{sh} \der{E}$, if there is a
-	switching sequence $\{\der{D}_{k}\}_{k=0}^m$ such that
-	$\der{D}\equiv_a \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2}
-	\ldots \shift{\nu_m} \der{D}_m \equiv _a \der{E}$.   
-	To point out a chosen permutation of rewriting steps, we will also write $\der{D}\equiv^{sh}_{\sigma} \der{E}$, 
-	where $\sigma$ is the composition of the transposition appearing in a chosen switching sequence. 
-\end{definition}
-
-\subsection{The local Church-Rosser Theorem}\label{subsec:CR}
 
@@
 
-\subsection{Well-switching rewriting systems}
-\label{subsec:verytame}
-
 Even if we work in strong enforcing rewriting systems where sequential
@@
 
-\subsubsection{Graphical rewriting systems}\label{subsubsec:graphical}
-
-\todo{ci sono un sacco di sistemi very tame}
-\subsection{Canonical switching sequences}
+\section{Switch equivalence and concatenable traces}
 \todo{intro}
 
-\subsubsection{The $3$-steps lemmas}
+As we mentioned, for linear rewriting systems
+it is canonical to identify
+derivations that are equal ``up to switching'', i.e.~that differ
+only in the order of independent steps. The same notion can be given
+for left-linear rewriting systems by relying on the notion of switch.
+
+We  recall some notations on permutations.  A \emph{permutation} on
+$\interval[0]{n}$ is a bijection
+$\sigma : \interval[0]{n} \to \interval[0]{n}$. It is a
+\emph{transposition} $\nu$ if there are $i, j \in \interval{n}$,
+$i \neq j$ such that $\sigma(i)=j$, $\sigma(j) = i$, and
+$\sigma(k) = k$ otherwise; it is denoted as $\transp{i}[j]$. Given a permutation $\perm$, 
+an \emph{inversion} for $\sigma$ is a pair $(i,j)$ such that $i<j$ and
+$\sigma(j)< \sigma(i)$; $\inv{\sigma}$ denotes the set of
+inversions of $\perm$.
+
+Switch equivalence is now defined as the equivalence relating derivations that 
+can be obtained one from another by a sequence of switches. Moreover, intermediate graphs can be taken up to isomorphism according to abstraction equivalence.
+
+\begin{definition}[Switching sequence]
+	\label{de:switch-equivalence}
+	Let $(\X, \R)$ be a left-linear rewriting system.  Let also
+	$\der{D}, \der{E} : G \Mapsto H$ be derivations with the same
+	length, $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and
+	$\der{E}=\{\dder{E}_{i}\}_{i=0}^n$. If
+	$\dder{D}_i \cdot \dder{D}_{i+1}$ is a switch of
+	$\dder{E}_i \cdot \dder{E}_{i+1}$ for some $i \in [0,n-1]$ and  $\dder{D}_j = \dder{E}_j$ for each $j \not \in \{i,i+1\}$ then we write
+	$\der{D} \shift{\transp{i}} \der{E}$. 
+	A \emph{switching sequence} is a sequence $\{\der{D}_{k}\}_{k=0}^m$
+	of derivations such that
+	$\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
+	\shift{\nu_m} \der{D}_m$  with $\nu_{k} = \transp{i_k}$.
+
+	Let us denote by $\nu_{k,h}$ the composition
+	$\nu_h \circ \nu_{h-1} \circ \ldots \nu_k$. We say that the
+	switching sequence \emph{consists of inversions} if for all
+	$k \in \interval[0]{m}$ the transposition $\nu_k$ is an inversion
+	for $\nu_{1,m}$.
+
+	Two derivations $\der{D}, \der{E}:G\Mapsto H$ are \emph{switch
+		equivalent}, written $\der{D}\equiv^{sh} \der{E}$, if there is a
+	switching sequence $\{\der{D}_{k}\}_{k=0}^m$ such that
+	$\der{D}\equiv_a \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2}
+	\ldots \shift{\nu_m} \der{D}_m \equiv _a \der{E}$.   
+	To point out a chosen permutation of rewriting steps, we will also write $\der{D}\equiv^{sh}_{\sigma} \der{E}$, 
+	where $\sigma$ is the composition of the transposition appearing in a chosen switching sequence. 
+\end{definition}
+
+\todo{Consistent permutations from switchings}
+
+\subsection{A canonical form for switching sequences}
 
@@
 
-\begin{lemma}[First $3$-steps Lemma]\label{lem:primo}
+\begin{lemma}[Forward $3$-steps Lemma]\label{lem:primo}
 Let $(\X,\R)$ be a left-linear DPO-rewriting system.
@@
 
-\begin{lemma}[Second $3$-steps Lemma]\label{lem:secondo}
+\begin{lemma}[Backward $3$-steps Lemma]\label{lem:secondo}
 	contenuto...
@@
 
-HUGE DIAGRAM
+HUGE DIAGRAMF
 
@@
 
-\subsection{Switch equivalence and consistent permutations}
-
-\section{Concatenable traces}
+\section{Switch equivalence and concatenable traces}
 

### 2025-01-11 full_version/permutations.tex
fine permutations

@@
 
-\begin{definition}Let $(\X, \R)$ be a left-linear DPO-rewriting system,  an \emph{abstraction equivalence} between two derivations $\der{D}$ and $\der{D'}$ with the same length and such that $r(\der{D})=r(\der{D}')$, is a family of isomorphisms $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ such that, for every $i\in [0, \lgh(\der{D})]$ the following diagram commutes
-	\[\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i} \ar@{>->}[l]_{f'_i}&G'_{i+1}\\  L_i \ar[u]^{n'_i} \ar[d]_{n_i}& K_i \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i} &R\ar[u]^{h'_i} \ar[d]_{h_i}\\G_i \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar@{>->}[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole \ar[r]_{g_i}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{H_i}}}\]
-
-	Given two decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, we say that they are \emph{abstraction equivalent}, if $\lgh(\der{D})=\lgh(\der{D}')$, $r(\der{D})=r(\der{D'})$, and there exists an of abstraction equivalence between $\der{D}$ and  $\der{D}$ such that the triangles below commute.
-	\[\xymatrix@C=15pt{&\pi(G_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G_{n+1}) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G_0 \ar[rr]_{\phi_{G_0}} && G'_0 &G_{n+1} \ar[rr]_{\phi_{G_{n+1}}} && G'_{n+1} } \]
-	We will use $\equiv^a$ to denote the resulting relation.
+\begin{definition}Let $(\X, \R)$ be a left-linear DPO-rewriting system,  an \emph{abstraction equivalence} between two derivations $\der{D}$ and $\der{D'}$ with the same length and such that $r(\der{D})=r(\der{D}')$, is a family of isomorphisms $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ such that, for every $i\in [0, \lgh(\der{D})-1]$ the following diagram commutes
+	\[\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i} \ar@{>->}[l]_{f'_i}&G'_{i+1}\\  L_i \ar[u]^{m'_i} \ar[d]_{m_i}& K_i \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i} &R_i\ar[u]^{h'_i} \ar[d]_{h_i}\\G_i \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar@{>->}[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole \ar[r]_{g_i}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{H_i}}}\]
+
+	If such an abstraction equivalence exists we will say that $\der{D}$ and $\der{D}'$ are \emph{abstraction equivalent} and we will use $\equiv^{abs}$ to denote the resulting relation-
+
+Given two decorated derivations $(\der{D}, \alpha, \omega)$  and $(\der{D}', \alpha', \omega')$, with the same length $n$ and using the same rules, an abstraction equivalence $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ is \emph{left consistent} if the left diagram below commutes, while it is \emph{right consistent} if the right one does so.
+A \emph{consistent} abstraction equivalence  is one which is both left and right consistent.
+\[\xymatrix@C=15pt{&\pi(G_0) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G_{n}) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G_0 \ar[rr]_{\phi_{G_0}} && G'_0 &G_{n} \ar[rr]_{\phi_{G_{n}}} && G'_{n} } \]
+
+We will say that $(\der{D}, \alpha, \omega)$  and $(\der{D}', \alpha', \omega')$ are \emph{left consistently}, respectively \emph{right consistently} or \emph{consistently}, abstraction equivalent, if there is a left consistent, respectively a right consistent or a consistent, abstraction equivalence between them.
+We will use $\equiv^{l}$, $\equiv^{r}$ and $\equiv^{a}$ to denote the resulting relations.
 \end{definition}
 
-\begin{remark}\label{rem:equi}
-	It is immediate to see that $\equiv^a$ is an equivalence relation.
-Indeed $(\der{D}, \alpha, \omega)$ is abstract equivalent to itself via the abstract equivalence with the identities as components.
-Furthermore, if  $\{\phi_X\}_{X\in \Deltamin(\der{D})}$  witnesses $(\der{D}, \alpha, \omega)\equiv^a (\der{D}', \alpha', \omega')$, then considering $\{\phi^{-1}_X\}_{X\in \Deltamin(\der{D})}$ shows $(\der{D}', \alpha', \omega)\equiv^a (\der{D}, \alpha, \omega)$.
-Finally, transitivity is assured composing abstract equivalences.
-
-	We will denote by $[\der{D}, \alpha, \omega]_a$ is just the equivalence class of  $(\der{D}, \alpha, \omega)$.
-	Such equivalence classes will be called  \emph{abstract decorated derivation}.  
-\end{remark}
+\begin{proposition}\label{prop:equi}
+The relations $\equiv^{abs}, \equiv^l, \equiv^r$ and $\equiv^a$ are equivalences.
+\end{proposition}
+\begin{proof}
+
+	 Let $\der{D}$ be a derivation, then $\{\id{X}\}_{X\in \Deltamin(\der{D})}$ is an abstraction equivalence between $\der{D}$ and itself.
+Moreover, starting with a decorated derivation $(\der{D}, \alpha, \omega)$, the same $\{\id{X}\}_{X\in \Deltamin(\der{D})}$  is also consistent, so that all the four relations are reflexive.
+
+	 For simmetry, let us suppose that $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ is an abstraction equivalence between $\der{D}$ and $\der{D}'$, then $\{\phi^{-1}_X\}$ defines an abstraction equivalence  between $\der{D}'$ and $\der{D}$.
+Indeed, for every $i\in [0, \lgh(\der{D})-1]$ we have
+	 \[\begin{split}
+	 	m_i&=\id{G_i}\circ m_i\\&=\phi^{-1}_{G_i}\circ \phi_{G_i}\circ m_i\\&=\phi^{-1}_{G_i}\circ m'_i
+	 \end{split} \qquad \begin{split}
+ 	k_i&=\id{D_i}\circ k_i\\&=\phi^{-1}_{D_i}\circ \phi_{D_i}\circ k_i\\&=\phi^{-1}_{D_i}\circ k'_i
+	 \end{split}\qquad \begin{split}
+ 	h_i&=\id{G_{i+1}}\circ h_i\\&=\phi^{-1}_{G_{i+1}}\circ \phi_{G_{i+1}}\circ h_i\\&=\phi^{-1}_{G_{i+1}}\circ h'_i
+	 \end{split} \]
+
+	Starting with two decorated derivations $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$, if $\{\phi_X\}_{X\in \Deltamin(\der{D})}$  is left, respectively right, consistent  then, putting $n$ as the length of $\der{D}$, we have:
+	\[\begin{split}
+		\alpha&=\id{G_0}\circ \alpha\\&=\phi^{-1}_{G_0}\circ \phi_{G_0}\circ \alpha\\&=\phi^{-1}_{G_0}\circ \alpha'
+	\end{split}\qquad \begin{split}
+		\omega&=\id{G_n}\circ \omega\\&=\phi^{-1}_{G_n}\circ \phi_{G_n}\circ \omega\\&=\phi^{-1}_{G_n}\circ \omega'
+	\end{split}\]
+
+	Finally, let $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ and $\{\psi_X\}_{X\in \Deltamin(\der{D}')}$ be abstraction equivalence witnessing $\der{D} \equiv^{abs}\der{D}'$ and $\der{D}'\equiv^{abs}\der{D}''$.
+Then we can consider the family $\{\psi_X\circ \phi_X\}_{X\in \Deltamin(\der{D})}$  and check that, for every $i\in [0,\lgh(\der{D})]$ we have
+	 \[\begin{split}
+	\psi_{G_i}\circ \phi_{G_i}\circ m_i&= \psi_{G_i}\circ m'_i\\&=m''_i 
+\end{split} \qquad \begin{split}
+	\psi_{D_i}\circ \phi_{D_i}\circ k_i&= \psi_{D_i}\circ k'_i\\&=k''_i
+\end{split}\qquad \begin{split}
+\psi_{G_{i+1}}\circ \phi_{G_{i+1}}\circ h_i&= \psi_{G_{i+1}}\circ h'_i\\&=h''_i
+\end{split} \]
+
+	For decorations, if $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ and $\{\psi_X\}_{X\in \Deltamin(\der{D}')}$ are left or right consistent we have
+	 \[\begin{split}
+		\psi_{G_0}\circ \phi_{G_0}\circ \alpha&= \psi_{G_0}\circ \alpha'\\&=\alpha'' 
+	\end{split} \qquad \begin{split}
+		\psi_{G_{\lgh(\der{D})}}\circ \phi_{G_{\lgh(\der{D})}}\circ \omega&= \psi_{G_{\lgh(\der{D})}}\circ \omega'\\&=\omega''
+	\end{split}\]
+	And we can conclude.
+\end{proof}
+
+\begin{notation}
+	Since we are mainly interested into consistent abstraction equivalence, we will use  $[\der{D}, \alpha, \omega]_a$ to denote the equivalence class of  $(\der{D}, \alpha, \omega)$ with respect to $\equiv^a$.
+	Such equivalence classes will be called  \emph{abstract decorated derivations}.  
+\end{notation}
 
 \begin{example}\label{rem:empty}
-	Let $(\der{D},\alpha, \omega)$ be an empty derivation from an object $G$ and  $(\der{D}',\alpha', \omega')$ a another empty one from $G'$.
-If $(\der{D},\alpha, \omega)\equiv^a(\der{D}',\alpha', \omega')$ then an abstraction equivalence between $\der{D}$ and $\der{D}'$ is just an isomorphism $\phi\colon G\to G'$, so that $\pi(G)=\pi(G')$.
-Moreover, such isomorphism must fit in the diagrams below.
+	Let $\{G\}$ and  $\{G'\}'$ be two empty derivations  An abstraction equivalence between $\{G\}$ and $\{G\}'$ is just an isomorphism $\phi\colon G\to G'$, so that $\pi(G)=\pi(G')$.
+If we are dealing with decorated derivations $(\{G\}, \alpha, \omega)$ and $(\{G'\}, \alpha, \omega)$,  left and right consistency of $\phi $ correspond to the commutativity of the diagrams below.
 	\[\xymatrix@C=15pt{&\pi(G) \ar[dr]^{\alpha'} \ar[dl]_{\alpha}&&& \pi(G) \ar[dr]^{\omega'} \ar[dl]_{\omega}\\ G\ar[rr]_{\phi} && G' &G \ar[rr]_{\phi} && G' } \]
-	In particular, these two triangles imply that
-	\begin{align*}
-		\alpha'\circ \alpha^{-1}&=\phi \\&=\omega'\circ \omega^{-1}
-	\end{align*}
+
+	In particular, this prove that two empty decorated derivations $(\{G\},\alpha, \omega) $ and $(\{G'\}',\alpha', \omega')$ are consistently abstraction equivalent if and only if
+	\[	\alpha'\circ \alpha^{-1}=\omega'\circ \omega^{-1}\]
 \end{example}
 
-\begin{remark}\label{rem:res} \Cref{prop:unique} can be restated as saying that, given two direct derivations $\dder{D}$ and $\dder{D'}$ with the same match, there exists an abstract equivalence between them whose first component is an identity.
+\begin{remark}\label{rem:res} \Cref{prop:unique} can be restated as saying that, given two direct derivations $\dder{D}$ and $\dder{D'}$ with the same match, there exists an abstract equivalence between them whose first component is the identity.
 \end{remark}
@@
 
-Notice, moreover, that if $\der{D}$ is not empty, then the previous equations become
+if $\der{D}$ is not empty, then the previous equations become
 \[(\der{D}, \alpha, \omega) \equiv^a (\phi * \der{D}, \phi^{-1}\circ \alpha,   \omega) \qquad (\der{D}, \alpha, \omega) \equiv^a ( \der{D}*\psi, \alpha, \psi \circ \omega )\]
+
+In particular, given an empty decorated derivation $(\{G\}, \alpha, \omega)$, we can apply what we have noticed to $\alpha \colon \pi(G)\to G$ and to $\omega^{-1}\colon G\to \pi(G) $ to get that 
+\[(\{G\}, \alpha, \omega)\equiv^a (\{\pi(G)\}, \id{\pi(G)}, \alpha^{-1}\circ \omega) \qquad (\{G\}, \alpha, \omega)\equiv^a (\{\pi(G)\}, 	\omega^{-1}\circ \alpha, \id{\pi(G)})\]
 \end{remark}
@@
 \begin{remark}\label{rem:lgt}
-	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ two composable decorated derivations   such that $\lgh(\der{D})=n$ and $\lgh(\der{D}')=m$.	 Then $(\der{D}*\omega^{-1}\cdot \alpha'*\der{D'}, \alpha, \omega')$ has length $n+m$.
-\end{remark}
+	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ two composable decorated derivations   such that $\lgh(\der{D})=n$ and $\lgh(\der{D}')=m$.	 Then $(\der{D}, \alpha, \omega)\cdot (\der{D}', \alpha', \omega')$ has length $n+m$.
+\end{remark}
+
+\begin{remark}\label{rem:id}
+	Let us consider  $(\{G\}, \alpha, \alpha)$ be a decoration of length $0$ with the same isomorphism as initial and final decoration.
+Then for every other derivations $(\der{D}, \beta, \omega)$ with source isomorphic to $G$, we have
+	\[(\{G\}, \alpha, \alpha)\cdot (\der{D}, \beta, \omega) = (\der{D}, \beta, \omega)\]
+
+	On the other hand, if  $(\der{E}, \gamma, \zeta)$  has a target isomorphic to $G$, we have
+	\[(\der{E}, \gamma, \zeta)\cdot (\{G\}, \alpha, \alpha) = \begin{cases}
+		(\{G\}, \alpha \circ \zeta^{-1}\circ \gamma, \alpha)	&\lgh(\der{E})=0 \\
+		(\der{E}, \gamma, \zeta )& \lgh(\der{E})= 0
+	\end{cases}\]
+
+Now,  in the first case, we have that
+\[\alpha \circ \zeta^{-1} \circ \gamma \circ \gamma ^{-1} = \alpha \circ \zeta^{-1}\]
+therefore, by \Cref{rem:empty}, $(\der{E}, \gamma, \zeta)\cdot (\{G\}, \alpha, \alpha)\equiv^a  (\der{E}, \gamma, \zeta)$.
+\end{remark}
+
+\begin{remark}\label{ex:zero}
+Let $(\{G\}, \alpha, \omega)$ and $(\{G'\}, \alpha', \omega')$ be two decorated derivations of length zero with $G$ and $G'$ isomorphic.
+Then we can always compose with another empty decorated derivations to get one from the other.
+In particular, using \Cref{rem:absequi} we have:
+\begin{align*}
+(\{G\}, \alpha, \omega)&\equiv^{a} (\pi(G), \id{\pi(G)}, \alpha^{-1}\circ \omega)\\&=(\{\pi(G)\}, (\alpha')^{-1}\circ \omega'\circ \omega'^{-1} \circ \alpha', \alpha^{-1}\circ \omega)\\&=(\{G'\}, \alpha', \omega')\cdot (\{\pi(G)\}, (\alpha')^{-1}\circ \omega', \alpha^{-1}\circ \omega)
+\\(\{G\}, \alpha, \omega)&\equiv^{a} (\{\pi(G)\}, 	\omega^{-1}\circ \alpha, \id{\pi(G)})\\&=(\{\pi(G)\}, \omega^{-1}\circ \alpha, (\omega')^{-1}\circ\alpha'\circ (\alpha')^{-1} \circ \omega')\\&= (\{\pi(G)\}, \omega^{-1}\circ \alpha, (\omega')^{-1}\circ\alpha') \cdot (\{G'\}, \alpha', \omega')
+\end{align*}
+\end{remark}
+
+We can generalize the previous remark to the following elementary, but useful, result about abstraction equivalence of composite decorated derivations. 
+\begin{lemma}\label{rem:obv}
+	Let  $(\der{D}_1, \alpha_1, \omega_1)$, $(\der{D}_2, \alpha_2, \omega_2)$, $(\der{D}'_1, \alpha'_1, \omega'_1)$ and $(\der{D}'_2, \alpha'_2, \omega'_2)$ be two pairs of composable derivations and define $(\der{E}, \xi, \theta)$ and $(\der{E}', \xi', \theta')$ as
+	\[(\der{E}, \xi, \theta):=(\der{D}_1, \alpha_1, \omega_1) \cdot (\der{D}_2, \alpha_2, \omega_2) \qquad (\der{E}', \xi', \theta'):=(\der{D}'_1, \alpha'_1, \omega'_1) \cdot (\der{D}'_2, \alpha'_2, \omega'_2)\]
+	 If $\lgh(\der{D}_1)=\lgh(\der{D}'_1)$, $\lgh(\der{D}_2)=\lgh(\der{D}'_2)$ and $\der{E}\equiv^a \der{E}'$  then there exist empty derivations $(\{A\}, \gamma_1, \delta_1)$ and $(\{B\}, \gamma_2, \delta_2)$ such that
+	 \[(\der{D}_1, \alpha_1, \omega_1) \equiv^a (\der{D}'_1, \alpha'_1, \omega'_1) \cdot  (\{A\}, \gamma_1, \delta_1) \qquad (\der{D}_2, \alpha_2, \omega_2) \equiv^a (\{B\}, \gamma_2, \delta_2)\cdot (\der{D}'_2, \alpha'_2, \omega'_2)  \]
+\end{lemma}
+\begin{proof} Let $\{\phi_X\}_{X\in \Deltamin(\der{E})}$ be an abstraction equivalent witnessing that $(\der{E}, \zeta, \theta)\equiv^{a}(\der{E}', \zeta', \theta')$.	We split the cases following \Cref{def:conc}.
+
+	\smallskip \noindent $\lgh(\der{D}_1)=0$. In this case we have that
+	\[(\der{E}, \zeta, \theta)=(\der{D}_2, \alpha_2\circ \omega^{-1}_1 \circ \alpha_1, \omega_2) \qquad (\der{E}', \zeta', \theta')=(\der{D}'_2, \alpha'_2\circ (\omega'_1)^{-1} \circ \alpha'_1, \omega'_2)\]
+	By hypothesis $\der{D}_1$ and $\der{D}'_1$ are given by $\{G_{1,0}\}$ and $\{G'_{1,0}\}$.
+Moreover we know that $G_{1,0}$ is isomorphic to $G_{2,0}$ and  $G'_{1,0}$ to $G'_{2,0}$.
+Since $\phi_{G_{2,0}}$ is an isomorphism we conclude that $G_{1,0}$ and $G_{2,0}$ are isomorphic and we deduce the first half of the thesis from \Cref{ex:zero}.
+
+	For the second half, let us consider define $B$ as $\pi(G_{2,0})$ and
+	\[\gamma_2:=\alpha^{-1}_1\circ \omega_1\qquad  \delta_2:=(\alpha'_1)^{-1}\circ \omega'_1  \]
+
+	Hence we have
+\[
+(\{\pi(G_{2,0})\}, \alpha^{-1}_1\circ \omega_1,  (\alpha'_1)^{-1}\circ \omega'_1 )\cdot(\der{D}'_2, \alpha'_2, \omega'_2)  =(\der{D}_2, \alpha'_2\circ (\omega'_1)^{-1} \circ \alpha'_1\circ \alpha_1^{-1}\circ \omega_1, \omega'_2)\]
+Now, by consistency of $\{\phi_{X}\}_{X\in \Deltamin(\der{D}_2)}$ we know that
+\[\phi_{G_{2,0}}\circ \alpha_2\circ \omega^{-1}_1\circ \alpha_1=\alpha'_2\circ (\omega'_1)^{-1} \circ \alpha'_1\]
+	therefore we also have the equality
+	\[\phi_{G_{2,0}}\circ \alpha_2=\alpha'_2\circ (\omega'_1)^{-1} \circ \alpha'_1 \circ \alpha^{-1}_1\circ \omega_1 \]
+	We conclude that $\{\phi_X\}_{X\in \der{D}_2}$ wintesses the thesis.
+
+	\smallskip \noindent $\lgh(\der{D}_2)=0$ and $\lgh(\der{D}_1)\neq 0$. By definition we know that
+	\[(\der{E}, \zeta, \theta)=(\der{D}_1, \alpha_1, \omega_1\circ \alpha_2^{-1}\circ \omega_2) \qquad (\der{E}', \zeta', \theta')=(\der{D}'_1, \alpha'_1, \omega'_1\circ (\alpha'_2)^{-1}\circ \omega'_2)\]
+
+	Let $l$ be the length of $\der{D}_1$, and consider $(\{\pi(G'_{1, l})\}, (\omega'_2)^{-1}\circ \alpha'_2, \omega^{-1}_2\circ \alpha_2)$, so that
+	\[ (\der{D}'_1, \alpha'_1, \omega'_1) \cdot  (\{\pi(G_{1, l})\}, (\omega'_2)^{-1}\circ \alpha'_2, \omega^{-1}_2\circ \alpha_2)= (\der{D}'_1, \alpha'_1, \omega'_1\circ (\alpha'_2)^{-1}\circ \omega'_2 \circ \omega^{-1}_2\circ \alpha_2)\]
+	Now, let us consider the abstraction equivalence between  the decorated derivations $(\der{D}_1, \alpha_1, \omega_1)$ and  $(\der{D}'_1, \alpha'_1, \omega'_1) \cdot  (\{\pi(G_{1, l})\}, (\omega'_2)^{-1}\circ \alpha'_2, \omega^{-1}_2\circ \alpha_2)$ given by $\{\phi_X\}_{X\in \Deltamin(\der{D}_1)}$.
+On the one hand it is, by construction, left consistent.
+On the other hand we know that
+
+	\[\phi_{G_{1,l}}\circ \omega_1\circ \alpha_2^{-1}\circ \omega_2=\omega'_1\circ (\alpha'_2)^{-1}\circ \omega'_2 \]
+
+	 Composing on both sides with $\omega^{-1}_1\circ \alpha_2$ yields now the thesis.
+
+The second half of the thesis follows immediately from \Cref{ex:zero}.
+
+	\smallskip \noindent  $\lgh(\der{D}_1)$ and $\lgh(\der{D}_2)$ are both different from $0$. By \Cref{def:conc} in this case we have
+	\[(\der{E}, \zeta, \theta)=(\der{D}_1*\omega^{-1}_1 \cdot \alpha_2*\der{D}_2, \alpha_1,\omega_2 ) \qquad (\der{E}', \zeta', \theta')=(\der{D}'_1*(\omega'_1)^{-1} \cdot \alpha'_2*\der{D}'_2, \alpha'_1,\omega'_2 )\]
+
+\end{proof}
 
@@
 
-	\begin{itemize}
-		\item $\lgh(\der{D})=0$. Then, $\lgh(\der{D}')$ is $0$ too. By \Cref{def:conc} we have
+	\smallskip \noindent  $\lgh(\der{D})=0$. Then, $\lgh(\der{D}')$ is $0$ too. By \Cref{def:conc} we have
 		\begin{align*}
@@
 
-		\item $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})= 0$. As in the point above, we get that also $\der{E}'$  is an empty derivation, thus we have
+\smallskip \noindent  $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})= 0$. As in the point above, we get that also $\der{E}'$  is an empty derivation, thus we have
 		\begin{align*}
@@
 		The thesis now follows at once.
-		\item $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})\neq 0$. In this case we have
+
+		\smallskip \noindent $\lgh(\der{D})\neq 0$ and $\lgh(\der{E})\neq 0$. In this case we have
 		\begin{align*}
@@
 
-		The thesis now follows.	\qedhere 
-	\end{itemize}	
-\end{proof}
+		The thesis now follows.	
+\end{proof}
+
+We are now ready to prove that the operatione defined by \Cref{def:conc} is associative up to decorated abstraction equivalence.
+
+\begin{lemma}[Associativity Lemma]\label{lem:ass}  
+Let $(\der{D}_1, \alpha_1, \omega_1)$ be a decorated derivation between $G$ and $H$, $(\der{D}_2, \alpha_2, \omega_2)$, one between $H$ and $K$ and $(\der{D}_3, \alpha_3, \omega_3)$ one between $K$ and $T$ in a left-linear DPO rewriting system.
+Then
+\[((\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)) \cdot (\der{D}_3, \alpha_3, \omega_3) \equiv^a (\der{D}_1, \alpha_1, \omega_1)\cdot ( (\der{D}_2, \alpha_2, \omega_2)\cdot (\der{D}_3, \alpha_3, \omega_3))\]
+\end{lemma}
+\begin{proof} We have seven cases.
+
+\smallskip \noindent  $\der{D}_1$, $\der{D}_2$ are both empty.
+In this case computing we get:
+\begin{align*}
+	((\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)) \cdot (\der{D}_3, \alpha_3, \omega_3)&=(\der{D}_2, \alpha_2\circ \omega^{-1}_1 \circ \alpha_1, \omega_2)\cdot (\der{D}_3, \alpha_3,\omega_3)\\&=(\der{D}_3,\alpha_3\circ\omega^{-1}_2\circ \alpha_2\circ \omega^{-1}_1\circ \alpha_1 ,\omega_3)\\&=(\der{D}_1, \alpha_1, \omega_1) \cdot (\der{D}_3, \alpha_3\circ \omega^{-1}_2 \circ \alpha_2,\omega_3)\\&=(\der{D}_1, \alpha_1, \omega_1) \cdot ((\der{D}_2, \alpha_2, \omega_2)\cdot (\der{D}_3, \alpha_3, \omega_3))
+\end{align*}
+
+\smallskip \noindent $\der{D}_1$ and $\der{D}_3$ are empty while $\der{D}_2$ is not. Apply \Cref{def:conc} we get
+\begin{align*}
+((\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)) \cdot (\der{D}_3, \alpha_3, \omega_3)&=(\der{D}_2, \alpha_2\circ \omega^{-1}_1 \circ \alpha_1, \omega_2)\cdot (\der{D}_3, \alpha_3,\omega_3)\\&=(\der{D}_2, \alpha_2\circ \omega^{-1}_1 \circ \alpha_1, \omega_2\circ \alpha^{-1}_3 \circ \omega_3)\\&=(\der{D}_1, \alpha_1, \omega_1 )\cdot  (\der{D}_2, \alpha_2,\omega_2\circ \alpha^{-1}_3 \circ  \omega_3)\\&= (\der{D}_1, \alpha_1, \omega_1 )\cdot((\der{D}_2, \alpha_2, \omega_2)\cdot (\der{D}_3, \alpha_3, \omega_3) )
+\end{align*}
+
+\smallskip \noindent  $\der{D}_1$ is empty, $\der{D}_2$ and $\der{D}_3$ are not. As above we can compute to get
+\begin{align*}
+((\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)) \cdot (\der{D}_3, \alpha_3, \omega_3)&=(\der{D}_2, \alpha_2\circ \omega^{-1}_1 \circ \alpha_1, \omega_2)\cdot (\der{D}_3, \alpha_3, \omega_3)\\&=(\der{D}_2*\omega^{-1}_2\cdot \alpha_3*\der{D}_3, \alpha_2\circ \omega^{-1}_1 \circ \alpha_1, \omega_3 )\\&=(\der{D}_1, \alpha_1, \omega_1) \cdot (\der{D}_2*\omega^{-1}_2\cdot \alpha_3*\der{D}_3, \alpha_2, \omega_3 )\\&=(\der{D}_1, \alpha_1, \omega_1) \cdot ((\der{D}_2, \alpha_2, \omega_2) \cdot (\der{D}_3, \alpha_3, \omega_3)  )
+\end{align*}
+
+\smallskip \noindent $\der{D}_1$ is non-empty while $\der{D}_2$ and $\der{D}_3$ have length $0$. Therefore:
+\begin{align*}
+	((\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)) \cdot (\der{D}_3, \alpha_3, \omega_3)&=(\der{D}_1, \alpha_1, \omega_1\circ \alpha^{-1}_2\circ \omega_2)\cdot (\der{D}_3, \alpha_3, \omega_3)\\&=(\der{D}_1, \alpha_1, \omega_1\circ \alpha^{-1}_2\circ \omega_2\circ \alpha^{-1}_3 \circ \omega_3 )\\&=(\der{D}_1, \alpha_1, \omega_1) \cdot (\der{D}_3, \alpha_3\circ \omega^{-1}_2\circ \alpha_2, \omega_3)\\&=(\der{D}_1, \alpha_1, \omega_1) \cdot ((\der{D}_2, \alpha_2, \omega_2) \cdot (\der{D}_3, \alpha_3, \omega_3)  )
+\end{align*}
+
+\smallskip \noindent $\der{D}_1$ and $\der{D}_3$ are non-empty while $\der{D}_2$ is. As above we have
+
+\begin{align*}
+	((\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)) \cdot (\der{D}_3, \alpha_3, \omega_3)&=(\der{D}_1, \alpha_1, \omega_1\circ \alpha^{-1}_2\circ \omega_2)\cdot (\der{D}_3, \alpha_3, \omega_3)\\&=(\der{D}_1*(\omega^{-1}_2\circ \alpha_2\circ \omega^{-1}_1)\cdot \alpha_3*\der{D}_3, \alpha_1, \omega_3 )\\(\der{D}_1, \alpha_1, \omega_1) \cdot ((\der{D}_2, \alpha_2, \omega_2) \cdot (\der{D}_3, \alpha_3, \omega_3)  )&=(\der{D}_1, \alpha_1, \omega_1) \cdot (\der{D}_3, \alpha_3\circ \omega^{-1}_2\circ \alpha_2, \omega_3)\\&=(\der{D}_1*\omega^{-1}_1\cdot (\alpha_3\circ \omega^{-1}_2 \circ \alpha_2)*\der{D}_3, \alpha_1, \omega_3)
+\end{align*}
+
+Let $n$ be the length of $\der{D}_1$, so that $\pi(G_{1,n})=\pi(G_{3,0})$. We can notice that the following two diagrams commute.
+	\[\xymatrix@C=55pt{G_{1, n-1}&D_{1,n-1} \ar[r]^{g_{1,n}} \ar@{>->}[l]_{f_{1,n}}&G_{1,n}  \ar[r]^{\omega^{-1}_1}& \pi(G_{1,n})\\  L_{1,n-1} \ar[u]_{m_{1,n-1}} \ar[d]^{m_{1, n-1}}& K_{1, n-1} \ar[u]^{k_{1,n-1}} \ar[d]_{k_{1,n-1}} \ar[rr]^{r_{1, n-1}} \ar@{>->}[l]_{l_{1,n-1}} &&R_{1, n-1}\ar[u]^{\omega^{-1}_1\circ h_{1,n-1}} \ar[d]_{\omega^{-1}_2\circ \alpha_2\circ \omega^{-1}_1\circ h_{1, n-1}}\\G_{1, n-1} \ar@/^.80cm/[uu]^{\id{G_{1, n-1}}}&D_{1, n-1}\ar@{>->}[l]^{f_{1, n-1}}\ar@/_.80cm/[uu]_(.35){\id{D_{1, n-1}}}|\hole \ar[r]_{g_{1, n-1}}&G_{1, n}\ar[r]_-{\omega^{-1}_2\circ \alpha_2\circ \omega^{-1}_1}& \pi(G_{1, n})\ar@/_.80cm/[uu]_{\alpha^{-1}_2\circ \omega_2}}\]
+		\[\xymatrix@C=55pt{\pi(G_{3, 0}) & G_{3,0}  \ar[l]_-{\alpha_3\circ \omega^{-1}_2\circ \alpha_2}&D_{3,0} \ar[r]^{g_{3,0}} \ar@{>->}[l]_{f_{3,0}}&G_{3,1}  \\  L_{3,0} \ar[u]_{\alpha_3\circ \omega^{-1}_2\circ \alpha_2\circ m_{3,0}} \ar[d]^{\alpha_3\circ  m_{3, 0}}& & K_{3, 0} \ar[u]^{k_{3,0}} \ar[d]_{k_{3,0}} \ar[r]^{r_{3, 0}} \ar@{>->}[ll]_{l_{3,0}} &R_{3, 0}\ar[u]^{ h_{3,0}} \ar[d]_{ h_{3, 0}}\\\pi(G_{3, 0})  \ar@/^.80cm/[uu]^{\alpha^{-1}_2\circ \omega_2}&G_{3,0} \ar[l]^{\alpha_3}&D_{3, 0}\ar@{>->}[l]^{f_{3, 0}}\ar@/_.80cm/[uu]_(.35){\id{D_{3, 0}}}|\hole \ar[r]_{g_{3, 0}}&G_{3, 1}\ar@/_.80cm/[uu]_{\id{G_{3,1}}}}\]
+
+Thus the family $\{\phi_{X}\}_{X\in \Deltamin(\der{D}_1*(\omega^{-1}_2\circ \alpha_2\circ \omega^{-1}_1)\cdot \alpha_3*\der{D}_3)}$ defined as
+\[\phi_X:=\begin{cases}
+	\id{X} & X\neq \pi(G_{1,n})\\
+	\alpha^{-1}_2 \circ \omega_2 & X= \pi(G_{1,n})
+\end{cases}\]
+is a consistent abstraction equivalence witnessing our thesis.
+
+\smallskip \noindent  $\der{D}_1$, $\der{D}_2$ and $\der{D}_3$ are all non-empty.
+For this case we rely to the fact that concatenation of derivations, being simply concatenation of paths in a graph, is associative.
+Indeed we have
+\begin{align*}
+	((\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)) \cdot (\der{D}_3, \alpha_3, \omega_3)&=(\der{D}_1*\omega^{-1}_1\cdot \alpha_2*\der{D}_2, \alpha_1, \omega_2)\cdot (\der{D}_3, \alpha_3, \omega_3)\\&=((\der{D}_1*\omega^{-1}_1\cdot \alpha_2*\der{D}_2)*\omega^{-1}_2\cdot \alpha_3*\der{D}_3, \alpha_1, \omega_3 )\\&=(\der{D}_1*\omega^{-1}_1\cdot (\alpha_2*\der{D}_2*\omega^{-1}_2)\cdot \alpha_3*\der{D}_3, \alpha_1, \omega_3 )\\&=(\der{D}_1*\omega^{-1}_1\cdot \alpha_2*(\der{D}_2*\omega^{-1}_2 \cdot \alpha_3*\der{D}_3), \alpha_1, \omega_3)\\&=(\der{D}_1, \alpha_1, \omega_1) \cdot (\der{D}_2*\omega^{-1}_2 \cdot \alpha_3*\der{D}_3, \alpha_2, \omega_3)\\&=
+	(\der{D}_1, \alpha_1, \omega_1) \cdot ((\der{D}_2, \alpha_2, \omega_2) \cdot (\der{D}_3, \alpha_3, \omega_3))
+\end{align*}
+And the thesis now follows.
+\end{proof}
+
+Given \Cref{rem:id}  and \Cref{lem:ass}, we are now ready to give the following definition.
 
@@
 		\item composition is concatenation of abstract decorated derivations;
-		\item the identity on $[G]$ is $[G, \alpha, \alpha]_a$, where $\alpha$ is any isomorphism $\pi(G)\to G$.	\end{itemize}
+		\item the identity on $[G]$ is $[\{G\}, \alpha, \alpha]_a$, where $\alpha$ is any isomorphism $\pi(G)\to G$.	\end{itemize}
 \end{definition}
+
+In the next proposition we fully characterize the isomorphism in $\dpi$.
+
+\begin{proposition} Let $(\X, \R)$ be a left-linear DPO rewriting system, then the isomorphisms in $\dpi$ are exactly the classes of empty decorated derivations.
+\end{proposition}
+\begin{proof}
+	Let $[\der{D}, \alpha, \omega]_a$ be an isomorphism, thus there exists $(\der{E}, \beta, \gamma)$ such that $(\der{D}, \alpha, \omega)\cdot (\der{E}, \beta, \gamma)\equiv^a(\{G_{\der{D}, 0}\}, \alpha, \alpha)$.
+Since the latter has length $0$, \Cref{rem:lgt} entails that $\der{D}$ is empty too.
+
+	Vice versa, if $(\{G\}, \alpha, \omega)$ be a derivation of length $0$, then 
+	\begin{align*}
+	(\{G\}, \alpha, \omega) \cdot (\{G\}, \omega, \alpha)&=(\{G\}, \omega\circ \omega^{-1} \circ \alpha, \alpha )\\&=(\{G\}, \alpha, \alpha)\\
+	(\{G\}, \omega, \alpha) \cdot (\{G\}, \alpha, \omega)&=(\{G\}, \alpha\circ \alpha^{-1} \circ \omega, \omega )\\&=(\{G\}, \omega, \omega)
+	\end{align*}
+	showing that  $[\{G\}, \alpha, \omega]_a$ is an isomorphism.
+\end{proof}
 

### 2025-01-20 full_version/leftlinear.tex
minori

@@
 
-\begin{definition}[Concrete  and decorated switch] \label{def:switch}
+\begin{definition}[Switch] \label{def:switch}
 	Let $\X$ be an $\mathcal{M}$-adhesive category 
@@
 
-	A \emph{concrete switch} of $\der{D}$ along $(i_0,i_1)$ is
+	A \emph{switch} of $\der{D}$ along $(i_0,i_1)$ is
 	a derivation $\der{E}=\{\dder{E}_i\}_{i=0}^1$, between the same objects and using the same rules
@@
 
-	If a concrete switch of $\dder{D}_0$ and $\dder{D}_1$ exists we say that they are \emph{switchable}.
+	If a switch of $\dder{D}_0$ and $\dder{D}_1$ exists we say that they are \emph{switchable}.
 
@@
 	mapping nodes according to their numbering.
-	%
+
 	A switch of $\der{D}$ along such independence pair is the derivation
@@
 	steps $\dder{D}_0$ and $\dder{D}_1$ are not sequential independent. Intuitively, this happens because $\rho_1$ uses the node generated by $\rho_0$ to produce a self-loop.
-
 \begin{center}
@@
 
-Let $\der{E}=\{\dder{E}_i\}_{i=0}^1$ be a concrete switch for $\dder{D}_0$
+Let $\der{E}=\{\dder{E}_i\}_{i=0}^1$ be a switch for $\dder{D}_0$
 and $\dder{D}_1$ along an independence pair $(i_0, i_1)$, then by definition we have an independence pair $(i'_0, i'_1)$ between $\dder{E}_0$ and $\dder{E}_1$ such that
@@
 
-Moreover, $\der{D}$ uses the same rule of $\der{E}$ in reverse order, thus it is a concrete switch for $\der{E}$ along $(i_0', i_1')$.
-
-Similarly, if $(\der{E}, \alpha, \omega)$ is a decorated switch for $(\der{D}, \alpha, \omega)$ along $(i_0, i_1)$, then the latter is a decorated switch for the former along $(i'_0, i'_1)$.
+ The derivation $\der{D}$ uses the same rule of $\der{E}$ in reverse order, thus it is a switch for $\der{E}$ along $(i_0', i_1')$.
+Moreover, the same argument shows that if $(\der{E}, \alpha, \omega)$ is a decorated switch for $(\der{D}, \alpha, \omega)$ along $(i_0, i_1)$, then the latter is a decorated switch for the former along $(i'_0, i'_1)$.
 \end{remark}
 
-We can now turn to prove the fundamental property that we need to rely upon:  any decorated switch induces a consistent permutation.
-
-\begin{lemma}\label{lem:switchtoperm}
-	Let $(\der{D}, \alpha, \omega)$ be a decorated derivations of length $2$ and suppose that $(\der{E}, \alpha, \omega)$ is a decorated switch for it along the independence pair $(i_0, i_1)$.
-Then the following are true:
-	\begin{enumerate}
-		\item there exists an arrow $\kappa\colon G_1\to \tpro{E}$ such that 
-		\[\kappa \circ g_0 = \iota_{\der{E}, G_0}\circ f_0 \qquad \kappa\circ h_0= \iota_{\der{E}, R_0}\]
-\item there exists an isomorphism $\phi\colon \tpro{D}\to \tpro{E}$ such that
-\[\phi \circ \iota_{\der{D}, G_0}=\iota_{\der{E}, G_0} \qquad \phi \circ \iota_{\der{D}, G_1}=\kappa \qquad \phi \circ \iota_{\der{D}, G_2}=\iota_{\der{E}, G_2}\]
-		\item $2$-cycle $\tau_{0,1}$ is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}, \alpha, \omega)$.
-	\end{enumerate}
-\end{lemma}
-\begin{proof}\begin{enumerate}
-		\item 
-		\item \qedhere 
-	\end{enumerate}
-\end{proof}
-
-\subsection{Strong-enforcing and well-switching rewriting systems}
-
-\subsection{Abstract switches}
-We can now prove some properties relating switching and abstraction equivalence. As a first step we can show that switches along the same independence paire are unique up to abstraction equivalence.
-
-\begin{lemma}[Uniqueness of concrete switches]
+A first property of switches is that they are unique up to abstraction equivalence.
+
+\begin{lemma}[Uniqueness of switches]
 	\label{thm:switch_uni}
@@
 
-\begin{definition}
-	contenuto...
-\end{definition}
-
-\begin{corollary}[Uniqueness of switches]\label{cor:switch}
-	\todo{switches}
-\end{corollary}
-
-Another useful property of switches is that they can be performed back and forth, giving back the original derivation. This is the content of the following two results.
-
-\todo{switch di switch}
-
-\begin{proposition}
-	contenuto...
-\end{proposition}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{corollary}
-	contenuto...
-\end{corollary}
-
-The fact that sequential independence implies switchability always
-holds for linear rules (see \Cref{prop:equi}). The result is so
-indispensable that typically, in the literature, it is not even
-stated, in the sense that switchability is not introduced
-axiomatically as in Definition~\ref{def:switch}, but it is based on
-the explicit construction of a switch.
-
-For left-linear rewriting systems
-sequential independence does not imply switchability (while the
-converse implication clearly holds), as shown by the next example.
-
-\begin{figure}
-	\begin{subfigure}{0.2\textwidth}
-		{\small
-			\xymatrix@C=16pt@R=1pt{
+Given two sequentially independent direct derivations, it is not necessarily true that a switch for them exists, as shown by the following example.
+
+\begin{example}\label{ex:diff1}
+	Consider the poset $(P, \sqsubseteq)$ depicted below, where
+	$P = \mathbb{N} \cup \{a,b,c\}$ and $\sqsubseteq$ is defined by
+	$m \sqsubseteq n$ if $m \geq n$, $a \sqsubseteq x$ for all $x \in P$
+	and $b, c \sqsubseteq n$ for all $n \in \mathbb{N}$.
+	\[\xymatrix@C=16pt@R=1pt{
 		& 0 \ar@{-}[dd] \ar@{-}[ddddddl] \ar@{-}[ddddddr] &  \\
@@
 		b \ar@{-}[dr] & & c \ar@{-}[dl]\\
-				& a 
+		& a} \]
+
+	Let $\X$ be the  
+	category associated with this order, which by \Cref{rem:iso} is
+	$\mathsf{I(\X)}$-adhesive. Consider a rewriting
+	system whose set of rules contains the following 
+	\[\xymatrix{a & a \ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & 0 & a & a
+		\ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & b }\]
+	We can then consider the  following derivation
+	$\der{D}=\{\dder{D}_i\}_{i=0}^1$.
+	 \[
+   \xymatrix@C=25pt{a \ar[d]_{(a,c)}&& \ar@{>->}[d]_{k_0}\ar[ll]_{\id{a}}
+		    \ar[r]^{(a,0)} & 0 \ar@/^.35cm/[drrr]|(.315)\hole_(.45){\id{0}}
+		    \ar[dr]|(.3)\hole_{\id{0}} && a \ar@/_.35cm/[dlll]^(.45){\hspace{5pt}(a,c)}
+		     \ar[dl]|(.3)\hole^{(a,0)}& a \ar[d]^{(a,0)}\ar@{>->}[l]_{\id{a}}
+		     \ar[rr]^{(a,b)} && b \ar[d]^{(b,0)}\\c &&
+		     \ar@{>->}[ll]^{\id{c}} c \ar[rr]_{(c,0)}&& 0 &&
+		     \ar@{>->}[ll]^{\id{0}} 0 \ar[rr]_{\id{0}}&& 0}\]
+
+	Note that the two direct derivations are sequential
+	independent. However there is no switch since the rule applied by
+	$\dder{D}_1$ cannot be applied to $c$. In fact, there is a unique morphism
+	$a\to c$, yielding the diagram
+	\[	\xymatrix{a \ar[d]_{(a,c)}& a
+		\ar[d]^{(a,c)}\ar@{>->}[l]_{\id{a}} \ar[r]^{(a,b)}& b \\c & c
+		\ar@{>->}[l]^{\id{c}}
+	}\]
+
+	Since $b$ and $c$ do not have a supremum in the poset underlying $\X$, the arrows
+	$a\to b$ and $a\to c$ do not have a pushout. Hence we do not get a direct derivation from $c$.
+\end{example}
+
+\subsection{Strong-enforcing and well-switching rewriting systems}
+
+\Cref{ex:diff1} show that sequential independence it does not suffice, in general, to guarantee the existence of a switch.  Inspired by the notion of of \emph{canonical filler}
+\cite{heindel2009category}, we are now going to give some conditions guaranteeing the existence of a switch. We start proving some technical properties of independence pairs.
+
+\begin{proposition}
+	\label{prop:tec}
+	Let $(\X,\R)$ be a left-linear rewriting system and
+	$(i_0, i_1)$ an independence pair between two direct
+	derivations $\dder{D}_0$ and $\dder{D}_1$. Consider the pullback of
+	$f_1\colon D_1\mto G_1$ along $g_0\colon D_0\to G_1$ (first
+	square below), then there exist the arrows
+	$u_1\colon K_1\to P$ and $u_0\colon K_0\to P$ fitting in the
+	central and right square. Moreover, the right one is always
+	a pullback.
+	\[\xymatrix@R=15pt{P \ar@{>->}[r]^{p_0} \ar[d]_{p_1} & D_0
+		\ar[d]^{g_0}& K_0 \ar[r]^{r_0} \ar@{.>}[d]_{u_0}& R_0
+		\ar[d]^{i_0} & K_1 \ar@{>->}[r]^{l_1} \ar@{.>}[d]_{u_1}&
+		L_1 \ar[d]^{i_1}\\ D_1 \ar@{>->}[r]_{f_1} &G_1 &P
+		\ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0}
+	\]
+\end{proposition}
+
+\begin{proof}
+	We start noticing that
+	\[\begin{split}
+	f_1\circ i_0\circ r_0&=h_0\circ r_0\\&=g_0\circ k_0	\end{split}
+	 \qquad\begin{split}
+	 	g_0\circ i_1\circ l_1&=m_1\circ l_1\\&= f_1 \circ k_1
+	 \end{split}
+	\]
+	Thus there exists the dotted $u_0\colon K_0\to P$,
+	$u_1\colon K_1\to P$ in the diagram
+	\[\xymatrix@R=15pt{K_0 \ar[d]_{r_0}
+		\ar@{.>}[r]_{u_0}\ar@/^.4cm/[rr]^{k_0} &P
+		\ar@{>->}[r]_{p_0} \ar[d]_{p_1}& D_0 \ar[d]^{g_0}&K_1
+		\ar@{>->}[d]_{l_1}
+		\ar@{.>}[r]_{u_1}\ar@/^.4cm/[rr]^{k_1} &P \ar[r]_{p_1}
+		\ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\R_0
+		\ar@/_.4cm/[rr]_{h_0}\ar[r]^{i_0}& D_1
+		\ar@{>->}[r]^{f_1}& G_1&L_1
+		\ar@/_.4cm/[rr]_{m_1}\ar[r]^{i_1}& D_0 \ar[r]^{g_0}&
+		G_1}\]
+	By \Cref{prop:pbpoad,lem:pb1} we get that the left half of
+	the second rectangle is a pullback.
+	\qedhere
+\end{proof}
+
+\begin{corollary}\label{lem:cose}Let
+		$\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation and suppose
+		that $(i_0, i_1)$ is an independence pair between $\dder{D}_0$
+		and $\der{D}_1$.  If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a
+		switch of $\der{D}$ along $(i_0, i_1)$, then there exists
+		$q_0\colon P\to D_{\der{E},0}$ in the diagram below. 
+		\[\xymatrix{D_{\der{E},0} \ar@{>->}[d]_{f_{\der{E},0}}&P
+			\ar@{.>}[l]_{q_0} \ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1
+			\ar@{>->}[d]^{f_1}\\ G_{0}&D_0 \ar@{>->}[l]^{f_0}\ar[r]_{g_0}&
+			G_1}\]
+		\end{corollary}
+\begin{proof}
+	Consider the arrow $u_1\colon K_1\to P$ obtained using
+	\Cref{prop:tec}. It fits in the big square on the left
+	\[		\xymatrix@R=15pt{K_1 \ar[r]^{u_1} \ar@{>->}[d]_{l_1}&P
+		\ar[r]^{\id{P}}\ar@{>->}[d]_{p_0}& P\ar@{>->}[d]^{p_0}\\L_1
+		\ar[d]_{\id{L_1}}\ar[r]^{i_1}&D_0 \ar[r]^{\id{D_0}}
+		\ar[d]_{\id{D_0}}& D_{0} \ar@{>->}[d]^{f_0}&K_1 \ar@{>->}[d]_{l_1}\ar[r]^{k_{\der{E},0}}&
+		D_{\der{E},0} \ar@{>->}[d]^{f_{\der{E},0}} & K_1 \ar[r]^{u_1}
+		\ar@{>->}[d]_{l_1}& P \ar@{>->}[d]^{f_0\circ
+			p_0}\\
+		L_1\ar[r]^{i_1} \ar@/_.4cm/[rr]_{m_{\der{E},0}}&D_0
+		\ar@{>->}[r]^{f_0}&G_0 & L_1\ar[r]_{m_{\der{E},0}}&G_0 &L_1
+		\ar[r]_{m_{\der{E},0}}&G_0}\]
+
+	Since $f_0$ is a monomorphism, every square in the diagram on the left above
+	is a pullback. Thus the whole big square is a pullback too.
+	Applying \Cref{lem:radj} to the pair of squares on the right now gives
+	us the wanted $q_0\colon P\to D_{\der{E},0}$.
+\end{proof}
+
+We are now ready to introduce the fundamental concept of this section.
+
+\begin{definition}[Strong independence pair]
+	\label{def:strong}
+	Let $\X$ be an $\mathcal{M}$-adhesive category 
+	and $(\X, \R)$ a left-linear rewriting system. 
+	Let also $(i_0, i_1)$ be an independence pair between two direct
+	derivations $\dder{D}_0$, $\dder{D}_1$
+	as in the solid part of the diagram below
+	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
+	\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
+	\ar@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
+	\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@/_.25cm/[dlll]^(.4){i_1}
+	\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
+	\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
+	D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
+	\ar[rr]_{g_1}&& G_2}
+\]
+
+	We say that $(i_0, i_1)$ is a \emph{strong independence pair} if
+	the first two squares depicted  
+	below are pushouts and if the pushout of $r_1 : K_1 \to R_1$ along $u_1 : K_1 \to P$ exists.
+	\[
+	\xymatrix@R=16pt{
+		K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
+		\ar@{>->}[r]^{l_1} \ar[d]_{u_1}& L_1 \ar[d]^{i_1}
+		&K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1\ar@{.>}[d]^{j_0}
+		\\
+		%
+		P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0
+		& P \ar@{.>}[r]_{q_1} & Q_1
 	}
-		}
-		\caption{Poset $(P, \sqsubseteq)$}
-		\label{fig:diff1:P}
-	\end{subfigure}
+	\]
+\end{definition}
+
+\begin{remark}\label{rem:deco} 
+	Let $(i_0, i_1)$ be a strong
+	independence pair between the direct derivations $\dder{D}_0$ and
+	$\dder{D}_1$. We can then build the solid part of the diagram
+	below
+	\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
+		\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
+		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
+		\ar@/_.6cm/[ddrr]^(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
+		\ar@/^.6cm/[ddll]_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
+		\ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0}
+		\ar@{.>}@/_.6cm/[ddrr]_{j_1}&& D_0
+		\ar@{>->}[dl]|(.42)\hole_(.64){f_0}\ar[ur]|(.48)\hole^(.7){g_1}&&D_1
+		\ar[dr]|(.42)\hole^(.65){g_1}
+		\ar@{>->}[ul]|(.48)\hole_(.7){f_1}&&R_1\ar@/^.6cm/[ddll]^{j_0}\ar[dl]^{h_1}\\&G_0
+		&&P\ar[dr]^{q_1}
+		\ar@{>.>}[dl]_{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\&&Q_0
+		\ar@{>->}@{>.>}[ul]_{a_0} &&Q_1\ar@{.>}[ur]^{b_1}}
+	\]
+
+	Let us complete this diagram defining the dotted arrows. To get
+	$j_1\colon L_0\to Q_0$ and $q_0\colon P\to Q_0$ it is enough to
+	take a pushout of $l_0$ along $u_0$, which exists since
+	$l_0\in \mathcal{M}$. Moreover, the existence of the wanted
+	$a_0\colon Q_0\to G_0$ and $b_1\colon Q_1\to G_2$ follows from
+	\[\begin{split}
+	f_0\circ p_0 \circ u_0 &= f_0\circ k_0 \\&= m_0\circ l_0
+	\end{split}
+	 \qquad\begin{split}
+	 	g_1\circ p_1\circ u_1 &= g_1\circ k_1\\&=h_1\circ r_1
+	 \end{split}
+	\]
+	We can prove some other properties of
+		the arrows appearing in the diagram above. The four rectangles
+		below are pushouts and their left halves are pushouts
+		too. Therefore, by \Cref{lem:po1} also their right halves are
+		pushouts.  Moreover, $q_0$ and $a_0$ are pushouts of
+		respectively $l_0$ and $p_0$, thus they are elements of
+		$\mathcal{M}$. By \Cref{prop:pbpoad} the left halves of the
+		first and third rectangles are pullbacks too.
+
+		\[\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar[d]_{r_0}\ar[r]_{u_0}
+			&P\ar[d]^{p_1} \ar@{>->}[r]_{p_0} & D_0 \ar[d]^{g_0}&K_1
+			\ar@/^.4cm/[rr]^{k_1}\ar@{>->}[d]_{l_1}\ar[r]_{u_1}
+			&P\ar@{>->}[d]^{p_0} \ar[r]_{p_1} & D_1 \ar@{>->}[d]^{f_1}\\
+			R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i_0}&D_1 \ar@{>->}[r]^{f_1}
+			& G_1&L_1 \ar@/_.4cm/[rr]_{m_1} \ar[r]^{i_1}&D_0\ar[r]^{g_0} &
+			G_1}\]
+			\[\xymatrix{K_0
+			\ar@/^.4cm/[rr]^{k_0}\ar@{>->}[d]_{l_0}\ar[r]_{u_0}
+			&P\ar@{>->}[d]^{q_0} \ar@{>->}[r]_{p_0} & D_0
+			\ar@{>->}[d]^{f_0}&K_1
+			\ar@/^.4cm/[rr]^{k_1}\ar[d]_{r_1}\ar[r]_{u_1}
+			&P\ar[d]^{q_1} \ar[r]_{p_1} & D_1 \ar[d]^{g_1}\\
+			L_0 \ar@/_.4cm/[rr]_{m_0} \ar[r]^{j_1}&Q_0 \ar@{>->}[r]^{a_0}
+			& G_0&R_1 \ar@/_.4cm/[rr]_{h_1} \ar[r]^{j_0}&Q_1 \ar[r]^{b_1}
+			& G_2}\]
+\end{remark}
+
+So equipped we can now prove a version of the Local Church-Rosser Theorem for strong independence pairs in ledt-linear DPO rewriting systems.
+
+\begin{theorem}[Local Church-Rosser Theorem]\label{prChurch} Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO rewriting system on it.
+If $(i_0, i_1)$ is a strong independence pair
+	between $\dder{D}_0$ and $\dder{D}_1$, then there exists a switch of $\dder{D}_0$ and $\dder{D}_1$ along it.
+\end{theorem}
+\begin{proof}
+	Let us begin considering the diagram
+	built in \Cref{rem:deco}
+	\[\xymatrix@C=15pt@R=15pt{&&R_0
+		\ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole \ar[dr]^{h_0}&&
+		L_1\ar@/^.8cm/[ddll]^(.2){i_1}
+		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
+		\ar@/_.6cm/[ddrr]^(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
+		\ar@/^.6cm/[ddll]_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
+		\ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0} \ar@{>}@/_.6cm/[ddrr]_{j_1}&& D_0
+		\ar@{>->}[dl]|(.42)\hole_(.64){f_0}\ar[ur]|(.48)\hole^(.7){g_1}&&D_1
+		\ar[dr]|(.42)\hole^(.65){g_1}
+		\ar@{>->}[ul]|(.48)\hole_(.7){f_1}&&R_1\ar@/^.6cm/[ddll]^{j_0}\ar[dl]_{h_1}\\&G_0
+		&&P\ar[dr]^{q_1}
+		\ar@{>->}[dl]_{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\&&Q_0
+		\ar@{>->}@{>->}[ul]_{a_0} \ar@{.>}[dr]_{b_0} &&Q_1\ar[ur]^{b_1}
+		\ar@{>.>}[dl]^{a_1} \\ &&&H_1 }\] Since $q_0\colon P\to Q_0$ is in
+	$\mathcal{M}$, we can take its pushout along $q_1$ to get the dotted
+	arrows $a_1\colon Q_1\mto H_1$ and $q_0\colon Q_0\to H_1$. But then,
+	since the composite of two pushout squares is a pushout, the diagram
+	below is a derivation
+	\[\xymatrix{L_1 \ar[d]_{f_0 \circ i_1}&& K_1
+		\ar[d]_{q_0\circ u_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1
+		\ar@/^.35cm/[drrr]|(.31)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{a_1\circ
+			j_0} && L_0 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{b_0\circ
+			j_1}& K_1 \ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
+		\ar[d]^{g_1\circ i_0} \\G_0 && \ar@{>->}[ll]^{a_0} Q_0 \ar[rr]_{b_0}&&
+		H_1 && \ar@{>->}[ll]^{a_1} Q_1 \ar[rr]_{b_1}&& G_2}\] It is immediate
+	now to see that it is a switch of $\dder{D}_0$ and $\dder{D}_1$ along
+	$(i_0, i_1)$.
+\end{proof}
+
+The previous theorem not only assures about the existence of a switch along a strong independence pair, but it provides us with an explicit description of it.
+In turn this, using \Cref{thm:switch_uni}, allows us to deduce some property common to all switches along strong independence pairs.
+
+\begin{corollary}\label{cor:strongip}
+	Let $(\X, \R)$ be a left-linear DPO rewriting system and consider the following derivation $\der{D}={\dder{D}_{i}}_{i=0}^i$ and suppose that $(i_0, i_1)$ is a strong independence pair.
+	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
+		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
+		\ar@{.>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
+		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{.>}@/_.25cm/[dlll]^(.4){i_1}
+		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
+		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
+		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
+		\ar[rr]_{g_1}&& G_2}
+	\]
+
+	Suppose, moreover, that the following diagram defines a switch for $\dder{D}_0$ and $\dder{D}_1$ along $(i_0, i_1)$. 	
+	\[
+	\xymatrix@R=20pt@C=20pt{
+		{L_1} \ar[d]_{m_0'}
+		&&  {K_1} \ar@{>->}[ll]_{l_1} \ar[r]^{r_1} \ar[d]_{k_0'}
+		&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{.>}_(.4){i_0'}|(.32)\hole[drrr]
+		& & 
+		{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{.>}^(.4){i_1'}[dlll] 
+		&  {K_0} \ar@{>->}[l]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
+		& & {R_0} \ar[d]^{h_1'} \\		
+		{G_0}
+		& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rr]_{g_0'}
+		& &  {G'_1} 
+		& &  {D_1'} \ar@{>->}[ll]^{f_1'} \ar[rr]_{g_1'}
+		& & {G_2}  }
+	\]
+
+	Then the following hold true:
+	\begin{enumerate}
+		\item consider the diagram below, in which the inner square is a pullback and the dotted arrows are constructed as in \Cref{rem:deco}:
+		\[\xymatrix{K_1 \ar[r]^{r_1} \ar@/_.3cm/[ddr]_{k'_0} \ar@{.>}[dr]^{e_0}& R_1  \ar[dr]^{i'_0}  && K_0 \ar@{>->}[r]^{l_0} \ar@/_.3cm/[ddr]_{k'_1} \ar@{.>}[dr]^{e_1}& L_1  \ar[dr]^{i'_1} \\& T\ar@{>->}[d]_{t_0} \ar[r]^{t_1}& D'_1  \ar@{>->}[d]^{f'_1} && T \ar@{>->}[r]^{t_0} \ar[d]_{t_1}& D'_0 \ar[d]^{g'_0}\\&D'_0 \ar[r]_{g'_0} & G'_1 && D'_1\ar@{>->}[r]_{f'_1} & G'_1}\]
+		then the squares below are pushouts.
+		\[\xymatrix{K_1 \ar[d]_{e_0} \ar[r]^{{r_1}}& R_1 \ar[d]^{i'_0} & K_1 \ar@{>->}[r]^{l_1} \ar[d]_{e_1}& L_1 \ar[d]^{i'_1} \\
+			T\ar[r]_{t_1} & D'_1 &T \ar@{>->}[r]_{t_0}&D'_0}\]
+
+		\item $(i'_0, i'_1)$ is a strong independence pair.
+	\end{enumerate}
+\end{corollary}
+\begin{proof}
+	\begin{enumerate}
+		\item Let us consider the derivation below, constructed in the proof of \Cref{prChurch}. 
+		\[\xymatrix{L_1 \ar[d]_{f_0 \circ i_1}&& K_1
+			\ar[d]_{q_0\circ u_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1
+			\ar@/^.35cm/[drrr]|(.31)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{a_1\circ
+				j_0} && L_0 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{b_0\circ
+				j_1}& K_1 \ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
+			\ar[d]^{g_1\circ i_0} \\G_0 && \ar@{>->}[ll]^{a_0} Q_0 \ar[rr]_{b_0}&&
+			H_1 && \ar@{>->}[ll]^{a_1} Q_1 \ar[rr]_{b_1}&& G_2}\]
+
+		By \Cref{thm:switch_uni} we know that there exists three isomorphisms $\phi_{Q_0}\colon Q_0\to D'_0$, $\phi_{Q_1}\colon Q_1\to D'_1$ and $\phi_{H_1}\colon H_1\to G'_1$ fitting in the diagrams below.
+		\[\xymatrix{ P \ar@{.>}[dr]^{v} \ar[rrr]^{q_1} \ar@{>->}[ddd]_{q_0}&&& Q_1 \ar@{>->}[ddd]^{a_1} \ar[dl]_{\phi_{Q_1}}& T\ar@{.>}[dr]^{w}  \ar[rrr]^{t_1} \ar@{>->}[ddd]_{t_0}&&& D'_1 \ar[dl]_{\phi^{-1}_{Q_1}} \ar@{>->}[ddd]^{f'_1}\\&T \ar@{>->}[d]_{t_0}\ar[r]^{t_1}& D'_1 \ar@{>->}[d]^{f'_1} &&& P \ar@{>->}[d]_{q_0}\ar[r]^{q_1}& Q_1\ar@{>->}[d]^{a_1}\\ & D'_0\ar[r]_{g'_0} & G'_1 &&& Q_0 \ar[r]_{b_0}& H_1 \\Q_0 \ar[rrr]_{b_0} \ar[ur]_{\phi_{Q_0}}&&& H_1 \ar[ul]^{\phi_{H_1}} & D'_0 \ar[rrr]_{g'_0} \ar[ur]_{\phi^{-1}_{Q_0}}&&&G'_1 \ar[ul]^{\phi^{-1}_{H_1}}}\]
+
+		In particular, we have
+		\[\begin{split}
+		g'_0\circ \phi_{Q_0}\circ q_0&=\phi_{H_1}\circ b_0\circ q_0\\&=\phi_{H_1}\circ a_1\circ q_1\\&= f'_1\circ \phi_{Q_1}\circ q_1
+		\end{split} \qquad  \begin{split}b_0\circ \phi^{-1}_{Q_0} \circ t_0&=\phi^{-1}_{H_1} \circ g'_0\circ t_0\\&=\phi^{-1}_{H_1} \circ f'_1\circ t_1\\&= a_1\circ \phi^{-1}_{Q_1}\circ t_1
+		\end{split}\]
+		therefore, by the universal property of pullbacks we get the dotted arrows $v\colon P\to T$ and $w\colon T\to P$. To see that they are one the inverse of the other it is then enough to compute.
+		\[\begin{split}
+		t_0\circ v\circ w &=\phi_{Q_0}\circ q_0\circ w\\&=\phi_{Q_0}\circ \phi^{-1}_{Q_0} \circ t_0\\&=t_0\\q_0\circ w\circ v&=\phi^{-1}_{Q_0}	\circ t_0\circ v\\&=\phi^{-1}_{Q_0} \circ \phi_{Q_0}\circ q_0\\&=q_0 	\end{split}\qquad \begin{split}
+		t_1\circ v\circ w &=\phi_{Q_1}\circ q_1\circ w\\&=\phi_{Q_1}\circ \phi^{-1}_{Q_1} \circ t_1\\&=t_1\\q_1\circ w\circ v&=\phi^{-1}_{Q_1}	\circ t_1\circ v\\&=\phi^{-1}_{Q_1} \circ \phi_{Q_1}\circ q_1\\&=q_1
+		\end{split}\]
+
+		Moreover, notice that
+		\begin{align*}
+	f'_1\circ \circ  \phi_{Q_1}\circ j_0&=\phi_{H_1}\circ a_1\circ j_0\\&= h'_0\\&=f'_1\circ i'_0
+		\end{align*}
+		thus, since $f'_1$ is mono, we have $\phi_{Q_1}\circ j_0=i'_0$.  The thesis now follows immediately from the diagram below, since the left square is a pushout by construction.		
+		\[\xymatrix{K_1  \ar@/^.4cm/[rr]^{e_0}\ar[r]_{u_1} \ar[d]_{r_1}& P \ar[r]_{v} \ar[d]_{q_1} & T \ar[d]^{t} \\ R_1 \ar@/_.4cm/[rr]_{i'_0} \ar[r]^{j_0}& Q_1 \ar[r]^{\phi_{Q_1}} & D'_1}\]
+
+		\item aaa
+	\end{enumerate}
+\end{proof}
+
+\begin{remark}
+	\label{rem:church}
+	It is worth to point out that, by
+	\Cref{prop:switch,thm:switch_uni}, the derivation we obtain from
+	\Cref{pr:church} %\todo{missing} 
+	is made by two switchable derivations that will
+	give back the starting derivation (up to abstraction equivalence),
+	if switched again.
+
+	Moreover, by \Cref{prop:pbpoad}, the first square below is a
+	pullback, therefore, by \cref{rem:deco} the last three squares
+	witness that $(j_0, j_1)$ is a strong independence pair too.
+	\[
+	\xymatrix@R=15pt{P\ar[r]^{q_1} \ar@{>->}[d]_{q_0}&Q_1
+		\ar@{>->}[d]^{a_1}&K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1
+		\ar[d]^{j_0} & K_0 \ar@{>->}[r]^{l_0} \ar[d]_{u_0}& L_0
+		\ar[d]^{j_1}&K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0\ar[d]^{i_0} \\
+		Q_ 0\ar[r]_{b_0}&H_1&P \ar[r]_{q_1} & Q_1 &P \ar[r]_{q_0} &
+		Q_0&P \ar[r]_{p_1} & D_1}
+	\]
+\end{remark}
+
+\begin{definition}
+	contenuto...
+\end{definition}
+
+\begin{proposition}
+	\label{prop:equi}
+	Every linear rewriting system $(\X, \R)$ is strong enforcing.
+\end{proposition}
+
+\begin{proof}
+	Suppose that $\X$ is $\mathcal{M}$-adhesive and let $(i_0, i_1)$ be
+	an independence pair as below
+	\[
+	\xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0
+		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar@{>->}[r]^{r_0} & R_0
+		\ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0}
+		&& L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
+		\ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar@{>->}[rr]^{r_1} && R_1
+		\ar[d]^{h_1} \\G_0 && \ar@{>->}[ll]^{f_0} D_0
+		\ar@{>->}[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
+		\ar@{>->}[rr]_{g_1}&& G_2}\]
+
+	Since $(\X, \R)$ is linear, then $r_1\colon K_1\to R_1$ belongs to
+	$\mathcal{M}$, thus it admits a pushout along $u_1\colon K_1\to P$,
+	as desired. Moreover, let us consider the two rectangles below
+	\[
+	\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar@{>->}[d]_{r_0}\ar[r]_{u_0}
+		&P\ar@{>->}[d]^{p_1} \ar@{>->}[r]_{p_0} & D_0
+		\ar@{>->}[d]^{f_0}& K_1
+		\ar@/^.4cm/[rr]^{k_1}\ar@{>->}[d]_{l_1}\ar[r]_{u_1}
+		&P\ar@{>->}[d]^{p_0} \ar@{>->}[r]_{p_1} & D_1
+		\ar@{>->}[d]^{f_1}\\ R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i_0}&D_1
+		\ar@{>->}[r]^{f_1} & G_1& L_1 \ar@/_.4cm/[rr]_{m_1}
+		\ar[r]^{i_1}&D_0 \ar@{>->}[r]^{g_0} & G_1} \] By hypothesis
+	$r_0$ and $l_1$ are in $\mathcal{M}$, thus $f_1$ and $g_0$ belong to
+	it too. The first point of \Cref{lem:popb} yields the thesis.
+\end{proof}
+
+\begin{remark}\label{rem:fill} Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ be a derivation and $(i_0, i_1)$ a strong independence pair between $\dder{D}_0$ and $\dder{D}_1$.
+Let also $\{\der{E}_{i}\}_{i=0}^1$ be a switch for them along $(i_0, i_1)$.
+Since, by \Cref{thm:switch_uni}, all switches are abstraction equivalent, we get the diagram below
+	\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
+		\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
+		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
+		\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){u_0}\ar[ur]^{r_0}&& G_1 &&
+		K_1
+		\ar@/^.6cm/[ddll]|(.36)\hole_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
+		\ar[dr]^{r_1}\\L_0
+		\ar@/_.6cm/[ddrr]_(.2){i'_0}|(.31)\hole|(.81)\hole
+		\ar[dr]^(.4){m_0}|(.61)\hole && D_0
+		\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1
+		\ar[dr]|(.4)\hole^(.65){g_1}
+		\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
+		&&P_1\ar[dr]_{q_1}	\ar@{>->}[dl]^{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole^(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole_(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_1}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_0} |(.69)\hole }\]
+
+\end{remark}
+
+We can now turn to prove the fundamental property that we need to rely upon:  any decorated switch induces a consistent permutation.
+
+\begin{lemma}\label{lem:switchtoperm}
+	Let $(\der{D}, \alpha, \omega)$ be a decorated derivations of length $2$ and suppose that $(\der{E}, \alpha, \omega)$ is a decorated switch for it along the independence pair $(i_0, i_1)$.
+Then the following are true:
+	\begin{enumerate}
+		\item there exists an arrow $\kappa\colon G_1\to \tpro{E}$ such that 
+		\[\kappa \circ g_{0} = \iota_{\der{E}, G_0}\circ f_{0} \qquad \kappa\circ h_{0}= \iota_{\der{E}, R_0}\]
+\item there exists an arrow $\phi\colon \tpro{D}\to \tpro{E}$ such that
+\[\phi \circ \iota_{\der{D}, G_0}=\iota_{\der{E}, G_0} \qquad \phi \circ \iota_{\der{D}, G_1}=\kappa \qquad \phi \circ \iota_{\der{D}, G_2}=\iota_{\der{E}, G_2}\]
+		\item the $2$-cycle $\tau_{0,1}\colon [0,1]\to [0,1]$ is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{E}, \alpha, \omega)$.
+	\end{enumerate}
+\end{lemma}
+\begin{proof}
+	To fix the notation let $\der{D}$ be given by the first diagram below and $\der{E}$ by the second one.
+	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
+		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
+		\ar@{>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
+		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{>}@/_.25cm/[dlll]^(.4){i_1}
+		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
+		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
+		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
+		\ar[rr]_{g_1}&& G_2}
+	\]
+	\[
+	\xymatrix@R=20pt@C=20pt{
+		{L_1} \ar[d]_{m_0'}
+		&&  {K_1} \ar@{>->}[ll]_{l_1} \ar[r]^{r_1} \ar[d]_{k_0'}
+		&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{>}_(.4){i_0'}|(.32)\hole[drrr]
+		& & 
+		{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{>}^(.4){i_1'}[dlll] 
+		&  {K_0} \ar@{>->}[l]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
+		& & {R_0} \ar[d]^{h_1'} \\		
+		{G_0}
+		& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rr]_{g_0'}
+		& &  {G'_1} 
+		& &  {D_1'} \ar@{>->}[ll]^{f_1'} \ar[rr]_{g_1'}
+		& & {G_2}  }
+	\]
+
+	\begin{enumerate}
+		\item  We can start computing to get:
+		\begin{align*}
+			\iota_{\der{E}, G_0}\circ f_{0}\circ  k_{0}&= \iota_{\der{E}, G_0}\circ m_{0} \circ l_{ 0}\\&=\iota_{\der{E}, G_0}\circ  f'_{0} \circ i'_1 \circ l_0\\&=\iota_{\der{E}, D'_0}\circ i'_1 \circ l_0\\&=\iota_{\der{E}, G'_1} \circ g'_0\circ m'_1 \circ l_0\\&=\iota_{\der{E}, G'_1}\circ m'_1\circ l_0	\\&=\iota_{\der{E}, G'_1} \circ f'_1\circ k'_1\\&=\iota_{\der{E}, D'_1}\circ k'_1\\&=\iota_{\der{E}, K'_0}\\&= \iota_{\der{E}, R_0} \circ r_0
+		\end{align*}
+		Thus we get the wanted arrow $\kappa\colon G_1\to \tpro{E}$.
+
+		\item 
+		\item 
+		\qedhere 
+	\end{enumerate}
+\end{proof}
+
+\subsection{Well-switching rewriting systems}
+
+\subsection{Abstract switches}
+We can now prove some properties relating switching and abstraction equivalence. As a first step we can show that switches along the same independence paire are unique up to abstraction equivalence.
+
+\todo{Unicità}
+
+\todo{switchabilità}
+
+\begin{definition}
+	contenuto...
+\end{definition}
+
+\begin{corollary}[Uniqueness of switches]\label{cor:switch}
+	\todo{switches}
+\end{corollary}
+
+Another useful property of switches is that they can be performed back and forth, giving back the original derivation. This is the content of the following two results.
+
+\todo{switch di switch}
+
+\begin{proposition}
+	contenuto...
+\end{proposition}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\begin{corollary}
+	contenuto...
+\end{corollary}
+
+The fact that sequential independence implies switchability always
+holds for linear rules (see \Cref{prop:equi}). The result is so
+indispensable that typically, in the literature, it is not even
+stated, in the sense that switchability is not introduced
+axiomatically as in Definition~\ref{def:switch}, but it is based on
+the explicit construction of a switch.
+
+For left-linear rewriting systems
+sequential independence does not imply switchability (while the
+converse implication clearly holds), as shown by the next example.
+
+\begin{figure}
+
 	\begin{subfigure}{0.58\textwidth}
@@
 	\begin{subfigure}{0.20\textwidth}
-		\xymatrix@C=20pt{a \ar[d]^{\sqsubseteq}& a
-			\ar[d]^{\sqsubseteq}\ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} & b \\c & c
-			\ar@{>->}[l]^{\id{c}}
-		}
+
 		\caption{No rewriting step}
@@
 \end{figure}
-
-\begin{example}
-	\label{ex:diff1}
-	Consider the poset $(P, \sqsubseteq)$ in Fig.~\ref{fig:diff1:P} where
-	$P = \mathbb{N} \cup \{a,b,c\}$ and $\sqsubseteq$ is defined by
-	$m \sqsubseteq n$ if $m \geq n$, $a \sqsubseteq x$ for all $x \in P$
-	and $b, c \sqsubseteq n$ for all $n \in \mathbb{N}$.
-	%
-	Let $\X$ be the  
-	category associated with this order, which by \Cref{rem:iso} is
-	$\mathsf{I(\X)}$-adhesive. 
-	%
-	Consider a rewriting
-	system whose set of rules contains the following 
-	\[\xymatrix{a & a \ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & 0 & a & a
-		\ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & b }\]
-	We can then consider the  derivation
-	$\der{D}=\{\dder{D}_i\}_{i=0}^1$ in Fig.~\ref{fig:diff1:rew}.
-	% \[
-	%   \xymatrix@C=30pt{a \ar[d]_{m_0}&& a \ar[d]_{k_0}\ar[ll]_{\id{a}}
-		%     \ar[r]^{(a,0)} & 0 \ar@/^.35cm/[drrr]|(.315)\hole_(.45){\id{0}}
-		%     \ar[dr]|(.3)\hole_{\id{0}} && a \ar@/_.35cm/[dlll]^(.45){(a,c)}
-		%     \ar[dl]|(.3)\hole^{(a,0)}& a \ar[d]^{(a,0)}\ar@{>->}[l]_{\id{a}}
-		%     \ar[rr]^{(a,b)} && b \ar[d]^{(b,0)}\\c &&
-		%     \ar@{>->}[ll]^{\id{c}} c \ar[rr]_{(c,0)}&& 0 &&
-		%     \ar@{>->}[ll]^{\id{0}} 0 \ar[rr]_{\id{0}}&& 0}\]
-	%
-	Note that the two direct derivations are sequential
-	independent. However there is no switch since the rule applied by
-	$\dder{D}_1$ cannot be applied to $c$. In fact, there is a unique morphism
-	$a\to c$, yielding the diagram in Fig.~\ref{ex:diff1:no-step}. But $b$ and $c$
-	do not have a supremum in the poset underlying $\X$, thus the arrows
-	$a\to b$ and $a\to c$ do not have a
-	pushout. Hence we do not get a direct derivation from $c$.
-\end{example}
 
@@
 
-\section{A class of well-behaved left-linear DPO-rewriting systems}
+\section{A class of well-behaved left-linear DPO rewriting systems}

### 2025-02-20 domains/domains.tex
minori

@@
 \begin{proof}
-Let $\xi\colon \tpro{D}\to \lpro \der{D}'\rpro$ be the arrow induced by 
+Let $\xi\colon \tpro{D}\to \lpro \der{D}'\rpro$ be the unique arrow $\tpro{D}\to \lpro \der{D}'\rpro$ satisfying 
 \[\xi \circ \iota_{G_i}:=\iota'_{G'_i}\circ \phi_{G_i}\]
-Then we have
+
+Then the square below commute.
 	\[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha} & G_0 \ar[dl]^{\id{G_0}} \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi}\\ G_0 \ar[rr]_{\iota'_{G_0}} & &\lpro \der{D}' \rpro\\L_i \ar[r]^{m_i} \ar[d]_{m'_{i}}& G_i \ar[dl]^{\phi_i} \ar[r]^{\iota_{G_i}} &\tpro{D} \ar[d]^{\xi} & R_i \ar[r]^{h_i} \ar[d]_{h'_{i}}& G_{i+1} \ar[dl]_{\phi_{i+1}} \ar[r]^{\iota_{G_{i+1}}} &\tpro{D} \ar[d]^{\xi} \\G'_{\sigma(i)} \ar[rr]_{\iota'_{G'_{i}}}&& \lpro \der{D}' \rpro& G'_{i+1} \ar[rr]_{\iota'_{G'_{i+1}}}&& \lpro \der{D}' \rpro}\]
+	But this is exactly the thesis.
 \end{proof}
@@
 
-	Since
+Now, the sequence of switches between $\lpro \der{D}''\rpro$ and  $\lpro \der{E}'' \rpro$  witnesses that $\id{2}$ is a consistent permutation and so there is a mediating isomorphism $\xi_{\id{2}}$.
+On the other hand, by
 

### 2025-02-20 full_version/adhesivity.tex
lavorato sulle permutazioni consistenti :^)))))))
minori

@@
 
+\begin{remark}
+	\label{rem:iso}
+	Every category $\X$ is $\mathsf{I(\X)}$-adhesive, where $\mathsf{I(\X)}$ is the class of 
+	isomorphisms.
+\end{remark}
+
 \begin{remark}\label{rem:pb}
@@
 
-\subsubsection{Pushout complements}
+\subsection{Pushout complements}
 
@@
 \begin{corollary}\label{lem:radj} Let $\X$ be an $\mathcal{M}$-adhesive category and consider two composable arrows $m\colon M \mto X$  and $f\colon X\to Y$, with $m\in \mathcal{M}$.
-Suppose moreover that the following square is a pushout, so that $(h,k)$ is a pushout complement og $(m,f)$:
+Suppose moreover that the following square is a pushout, so that $(h,k)$ is a pushout complement of $(m,f)$:
 	\[\xymatrix{M \ar@{>->}[r]^{m}\ar[d]_{h}& X \ar[d]^{f} \\Q\ar@{>->}[r]_{k}&Y}\]

### 2025-02-20 full_version/leftlinear.tex
minori

@@
 	$\der{F}=\{\dder{F}_i\}_{i=0}^1$ are switches of $\dder{D}_0$ and
-	$\dder{D}_1$. Then there is an abstraction equivalence between $\der{E}$ and $\der{F}$, whose first component is $\id{G_0}$.
+	$\dder{D}_1$. Then there is an abstraction equivalence $\{\phi_X\}_{X\in \Deltamin(\der{E})}$ between $\der{E}$ and $\der{F}$, whose first component is $\id{G_0}$. Moreover, 
+	\[\phi_{D_{\der{E}, 0}}\circ j_1=a_1 \qquad \phi_{\der{E}, 1}\circ j_0=a_0\]
 \end{lemma}
@@
 	By definition of switch $\der{E}_0$ and $\der{F}_0$ have the same match $f_0\circ i_1$ and that $\der{E}_1$ and $\der{F}_1$ have the same comatch $g_1\circ i_0$.
-Thus we get the solid part of the diagram below
+Thus we get the solid part of the diagram below.
+If we are able to construct the dotted arrow and prove that they are isomorphism we are done.
 	\[\xymatrix@C=22pt{G_{0} && \ar@{>->}[ll]_{f_{\der{F},0}} D_{\der{F},0} \ar[rr]^{g_{\der{F},0}}&& G_{\der{F},1} && \ar@{>->}[ll]_{f_{\der{F},1}} D_{\der{F},1} \ar[rr]^{g_{\der{F},1}}&& G_{2}\\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}&& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_{1} \ar@/^.35cm/[drrr]|(.315)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{h_{\der{E},0}} \ar@/_.35cm/[urrr]|(.315)\hole^(.4){a_0} \ar[ur]|(.3)\hole^{h_{\der{F},0}}& &L_{0} \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{m_{\der{E},1}} \ar@/^.35cm/[ulll]_(.4){a_1} \ar[ul]|(.3)\hole_{m_{\der{F},1}}& K_{0} \ar[d]_{k_{\der{E},1}} \ar[u]^{k_{\der{F},1}}\ar@{>->}[l]_{l_{0}} \ar[rr]^{r_0} && R_{0} \ar[d]_{g_1\circ i_0} \ar[u]^{g_1\circ i_0}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} && \ar[ll]^{f_{\der{E},0}} D_{\der{E},0} \ar@{.>}@/^.5cm/[uu]^(.33){\phi_{0}}|\hole \ar[rr]_{g_{\der{E},0}}&& G_{\der{E},1} \ar@{.>}[uu]^(.76){\psi_1}|(.45)\hole |(.55)\hole&& \ar@{>->}[ll]^{f_{\der{E},1}} D_{\der{E},1} \ar@{.>}@/_.5cm/[uu]_(.33){\phi_{1}}|\hole\ar[rr]_{g_{\der{E},1}}&& G_{2}\ar@{.>}@/_.5cm/[uu]_{\psi_2}}\]
@@
 	Since $\psi_1$ is an isomorphism, the square below is a pushout. 
-	\[\xymatrix{K_0 \ar[d]_{k_{\der{E,1}}} \ar@{>->}[r]^{l_0}& L_0 \ar[d]^{\psi_1\circ m_{\der{E},1}}\\D_{\der{E},1} \ar@{>->}[r]_{\psi_1\circ f_{\der{E},1}}& G_{\der{F}, 1}}\]
+	\[\xymatrix@C=35pt{K_0 \ar[d]_{k_{\der{E},1}} \ar@{>->}[r]^{l_0}& L_0 \ar[d]^{\psi_1\circ m_{\der{E},1}}\\D_{\der{E},1} \ar@{>->}[r]_{\psi_1\circ f_{\der{E},1}}& G_{\der{F}, 1}}\]
 
@@
 	a pullback.
-	\[\xymatrix@R=15pt{P \ar@{>->}[r]^{p_0} \ar[d]_{p_1} & D_0
+	\[\xymatrix{P \ar@{>->}[r]^{p_0} \ar[d]_{p_1} & D_0
 		\ar[d]^{g_0}& K_0 \ar[r]^{r_0} \ar@{.>}[d]_{u_0}& R_0
@@
 	$u_1\colon K_1\to P$ in the diagram
-	\[\xymatrix@R=15pt{K_0 \ar[d]_{r_0}
+	\[\xymatrix{K_0 \ar[d]_{r_0}
 		\ar@{.>}[r]_{u_0}\ar@/^.4cm/[rr]^{k_0} &P
@@
 	\Cref{prop:tec}. It fits in the big square on the left
-	\[		\xymatrix@R=15pt{K_1 \ar[r]^{u_1} \ar@{>->}[d]_{l_1}&P
+	\[		\xymatrix{K_1 \ar[r]^{u_1} \ar@{>->}[d]_{l_1}&P
 		\ar[r]^{\id{P}}\ar@{>->}[d]_{p_0}& P\ar@{>->}[d]^{p_0}\\L_1
@@
 	\[
-	\xymatrix@R=16pt{
+	\xymatrix{
 		K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
@@
 		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
-		\ar@/_.6cm/[ddrr]^(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
-		\ar@/^.6cm/[ddll]_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
+		\ar@/_.6cm/[ddrr]_(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
+		\ar@/^.6cm/[ddll]^(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
 		\ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0}
@@
 		$\mathcal{M}$. By \Cref{prop:pbpoad} the left halves of the
-		first and third rectangles are pullbacks too.
+		second and third rectangles are pullbacks too.
 
@@
 		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
-		\ar@/_.6cm/[ddrr]^(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
-		\ar@/^.6cm/[ddll]_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
+		\ar@/_.6cm/[ddrr]_(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
+		\ar@/^.6cm/[ddll]^(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
 		\ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0} \ar@{>}@/_.6cm/[ddrr]_{j_1}&& D_0
@@
 		\ar@{>->}@{>->}[ul]_{a_0} \ar@{.>}[dr]_{b_0} &&Q_1\ar[ur]^{b_1}
-		\ar@{>.>}[dl]^{a_1} \\ &&&H_1 }\] Since $q_0\colon P\to Q_0$ is in
+		\ar@{>.>}[dl]^{a_1} \\ &&&H_1 }\]
+
+		Since $q_0\colon P\to Q_0$ is in
 	$\mathcal{M}$, we can take its pushout along $q_1$ to get the dotted
@@
 			j_0} && L_0 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{b_0\circ
-			j_1}& K_1 \ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
+			j_1}& K_0 \ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
 		\ar[d]^{g_1\circ i_0} \\G_0 && \ar@{>->}[ll]^{a_0} Q_0 \ar[rr]_{b_0}&&
-		H_1 && \ar@{>->}[ll]^{a_1} Q_1 \ar[rr]_{b_1}&& G_2}\] It is immediate
-	now to see that it is a switch of $\dder{D}_0$ and $\dder{D}_1$ along
-	$(i_0, i_1)$.
+		H_1 && \ar@{>->}[ll]^{a_1} Q_1 \ar[rr]_{b_1}&& G_2}\]
+
+		The thesis now follows at once since, by construction, the derivation above is a switch of $\dder{D}_0$ and $\dder{D}_1$ along	$(i_0, i_1)$.
 \end{proof}
@@
 
-\begin{corollary}\label{cor:strongip}
+\begin{lemma}\label{cor:strongip}
 	Let $(\X, \R)$ be a left-linear DPO rewriting system and consider the following derivation $\der{D}={\dder{D}_{i}}_{i=0}^i$ and suppose that $(i_0, i_1)$ is a strong independence pair.
@@
 	\]
-
-	Then the following hold true:
-	\begin{enumerate}
-		\item consider the diagram below, in which the inner square is a pullback and the dotted arrows are constructed as in \Cref{rem:deco}:
-		\[\xymatrix{K_1 \ar[r]^{r_1} \ar@/_.3cm/[ddr]_{k'_0} \ar@{.>}[dr]^{e_0}& R_1  \ar[dr]^{i'_0}  && K_0 \ar@{>->}[r]^{l_0} \ar@/_.3cm/[ddr]_{k'_1} \ar@{.>}[dr]^{e_1}& L_1  \ar[dr]^{i'_1} \\& T\ar@{>->}[d]_{t_0} \ar[r]^{t_1}& D'_1  \ar@{>->}[d]^{f'_1} && T \ar@{>->}[r]^{t_0} \ar[d]_{t_1}& D'_0 \ar[d]^{g'_0}\\&D'_0 \ar[r]_{g'_0} & G'_1 && D'_1\ar@{>->}[r]_{f'_1} & G'_1}\]
-		then the squares below are pushouts.
-		\[\xymatrix{K_1 \ar[d]_{e_0} \ar[r]^{{r_1}}& R_1 \ar[d]^{i'_0} & K_1 \ar@{>->}[r]^{l_1} \ar[d]_{e_1}& L_1 \ar[d]^{i'_1} \\
-			T\ar[r]_{t_1} & D'_1 &T \ar@{>->}[r]_{t_0}&D'_0}\]
-
-		\item $(i'_0, i'_1)$ is a strong independence pair.
-	\end{enumerate}
-\end{corollary}
-\begin{proof}
-	\begin{enumerate}
-		\item Let us consider the derivation below, constructed in the proof of \Cref{prChurch}. 
+and define $T$, with the arrows $t_0\colon T\mto D'_0$ and $t_1\colon T\to D'_1$ as the pullback of $f'_1$ along $g'_0$.
+
+Finally, consider the derivation $\der{F}$ below, constructed in the proof of \Cref{prChurch}. 
 \[\xymatrix{L_1 \ar[d]_{f_0 \circ i_1}&& K_1
@@
 		j_0} && L_0 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{b_0\circ
-				j_1}& K_1 \ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
+		j_1}& K_0\ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
 	\ar[d]^{g_1\circ i_0} \\G_0 && \ar@{>->}[ll]^{a_0} Q_0 \ar[rr]_{b_0}&&
 	H_1 && \ar@{>->}[ll]^{a_1} Q_1 \ar[rr]_{b_1}&& G_2}\]
-
-		By \Cref{thm:switch_uni} we know that there exists three isomorphisms $\phi_{Q_0}\colon Q_0\to D'_0$, $\phi_{Q_1}\colon Q_1\to D'_1$ and $\phi_{H_1}\colon H_1\to G'_1$ fitting in the diagrams below.
-		\[\xymatrix{ P \ar@{.>}[dr]^{v} \ar[rrr]^{q_1} \ar@{>->}[ddd]_{q_0}&&& Q_1 \ar@{>->}[ddd]^{a_1} \ar[dl]_{\phi_{Q_1}}& T\ar@{.>}[dr]^{w}  \ar[rrr]^{t_1} \ar@{>->}[ddd]_{t_0}&&& D'_1 \ar[dl]_{\phi^{-1}_{Q_1}} \ar@{>->}[ddd]^{f'_1}\\&T \ar@{>->}[d]_{t_0}\ar[r]^{t_1}& D'_1 \ar@{>->}[d]^{f'_1} &&& P \ar@{>->}[d]_{q_0}\ar[r]^{q_1}& Q_1\ar@{>->}[d]^{a_1}\\ & D'_0\ar[r]_{g'_0} & G'_1 &&& Q_0 \ar[r]_{b_0}& H_1 \\Q_0 \ar[rrr]_{b_0} \ar[ur]_{\phi_{Q_0}}&&& H_1 \ar[ul]^{\phi_{H_1}} & D'_0 \ar[rrr]_{g'_0} \ar[ur]_{\phi^{-1}_{Q_0}}&&&G'_1 \ar[ul]^{\phi^{-1}_{H_1}}}\]
-
-		In particular, we have
-		\[\begin{split}
-		g'_0\circ \phi_{Q_0}\circ q_0&=\phi_{H_1}\circ b_0\circ q_0\\&=\phi_{H_1}\circ a_1\circ q_1\\&= f'_1\circ \phi_{Q_1}\circ q_1
-		\end{split} \qquad  \begin{split}b_0\circ \phi^{-1}_{Q_0} \circ t_0&=\phi^{-1}_{H_1} \circ g'_0\circ t_0\\&=\phi^{-1}_{H_1} \circ f'_1\circ t_1\\&= a_1\circ \phi^{-1}_{Q_1}\circ t_1
-		\end{split}\]
-		therefore, by the universal property of pullbacks we get the dotted arrows $v\colon P\to T$ and $w\colon T\to P$. To see that they are one the inverse of the other it is then enough to compute.
-		\[\begin{split}
-		t_0\circ v\circ w &=\phi_{Q_0}\circ q_0\circ w\\&=\phi_{Q_0}\circ \phi^{-1}_{Q_0} \circ t_0\\&=t_0\\q_0\circ w\circ v&=\phi^{-1}_{Q_0}	\circ t_0\circ v\\&=\phi^{-1}_{Q_0} \circ \phi_{Q_0}\circ q_0\\&=q_0 	\end{split}\qquad \begin{split}
-		t_1\circ v\circ w &=\phi_{Q_1}\circ q_1\circ w\\&=\phi_{Q_1}\circ \phi^{-1}_{Q_1} \circ t_1\\&=t_1\\q_1\circ w\circ v&=\phi^{-1}_{Q_1}	\circ t_1\circ v\\&=\phi^{-1}_{Q_1} \circ \phi_{Q_1}\circ q_1\\&=q_1
-		\end{split}\]
-
-		Moreover, notice that
-		\begin{align*}
-	f'_1\circ \circ  \phi_{Q_1}\circ j_0&=\phi_{H_1}\circ a_1\circ j_0\\&= h'_0\\&=f'_1\circ i'_0
-		\end{align*}
-		thus, since $f'_1$ is mono, we have $\phi_{Q_1}\circ j_0=i'_0$.  The thesis now follows immediately from the diagram below, since the left square is a pushout by construction.		
-		\[\xymatrix{K_1  \ar@/^.4cm/[rr]^{e_0}\ar[r]_{u_1} \ar[d]_{r_1}& P \ar[r]_{v} \ar[d]_{q_1} & T \ar[d]^{t} \\ R_1 \ar@/_.4cm/[rr]_{i'_0} \ar[r]^{j_0}& Q_1 \ar[r]^{\phi_{Q_1}} & D'_1}\]
-
-		\item aaa
-	\end{enumerate}
-\end{proof}
-
-\begin{remark}
-	\label{rem:church}
-	It is worth to point out that, by
-	\Cref{prop:switch,thm:switch_uni}, the derivation we obtain from
-	\Cref{pr:church} %\todo{missing} 
-	is made by two switchable derivations that will
-	give back the starting derivation (up to abstraction equivalence),
-	if switched again.
-
-	Moreover, by \Cref{prop:pbpoad}, the first square below is a
-	pullback, therefore, by \cref{rem:deco} the last three squares
-	witness that $(j_0, j_1)$ is a strong independence pair too.
-	\[
-	\xymatrix@R=15pt{P\ar[r]^{q_1} \ar@{>->}[d]_{q_0}&Q_1
-		\ar@{>->}[d]^{a_1}&K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1
-		\ar[d]^{j_0} & K_0 \ar@{>->}[r]^{l_0} \ar[d]_{u_0}& L_0
-		\ar[d]^{j_1}&K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0\ar[d]^{i_0} \\
-		Q_ 0\ar[r]_{b_0}&H_1&P \ar[r]_{q_1} & Q_1 &P \ar[r]_{q_0} &
-		Q_0&P \ar[r]_{p_1} & D_1}
-	\]
-\end{remark}
-
-\begin{definition}
-	contenuto...
-\end{definition}
-
-\begin{proposition}
-	\label{prop:equi}
-	Every linear rewriting system $(\X, \R)$ is strong enforcing.
-\end{proposition}
-
-\begin{proof}
-	Suppose that $\X$ is $\mathcal{M}$-adhesive and let $(i_0, i_1)$ be
-	an independence pair as below
-	\[
-	\xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0
-		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar@{>->}[r]^{r_0} & R_0
-		\ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0}
-		&& L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
-		\ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar@{>->}[rr]^{r_1} && R_1
-		\ar[d]^{h_1} \\G_0 && \ar@{>->}[ll]^{f_0} D_0
-		\ar@{>->}[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
-		\ar@{>->}[rr]_{g_1}&& G_2}\]
-
-	Since $(\X, \R)$ is linear, then $r_1\colon K_1\to R_1$ belongs to
-	$\mathcal{M}$, thus it admits a pushout along $u_1\colon K_1\to P$,
-	as desired. Moreover, let us consider the two rectangles below
-	\[
-	\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar@{>->}[d]_{r_0}\ar[r]_{u_0}
-		&P\ar@{>->}[d]^{p_1} \ar@{>->}[r]_{p_0} & D_0
-		\ar@{>->}[d]^{f_0}& K_1
-		\ar@/^.4cm/[rr]^{k_1}\ar@{>->}[d]_{l_1}\ar[r]_{u_1}
-		&P\ar@{>->}[d]^{p_0} \ar@{>->}[r]_{p_1} & D_1
-		\ar@{>->}[d]^{f_1}\\ R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i_0}&D_1
-		\ar@{>->}[r]^{f_1} & G_1& L_1 \ar@/_.4cm/[rr]_{m_1}
-		\ar[r]^{i_1}&D_0 \ar@{>->}[r]^{g_0} & G_1} \] By hypothesis
-	$r_0$ and $l_1$ are in $\mathcal{M}$, thus $f_1$ and $g_0$ belong to
-	it too. The first point of \Cref{lem:popb} yields the thesis.
-\end{proof}
-
-\begin{remark}\label{rem:fill} Let $\der{D}=\{\dder{D}_i\}_{i=0}^n$ be a derivation and $(i_0, i_1)$ a strong independence pair between $\dder{D}_0$ and $\dder{D}_1$.
-Let also $\{\der{E}_{i}\}_{i=0}^1$ be a switch for them along $(i_0, i_1)$.
-Since, by \Cref{thm:switch_uni}, all switches are abstraction equivalent, we get the diagram below
+and let $\{\phi_{X}\}_{X\in \Deltamin(\der{F})}$ be the abstraction equivalence built in \Cref{thm:switch_uni}.
+
+	Then the following hold true:
+	\begin{enumerate}
+		\item consider the following two squares, the first of which is a pullback and the second an $\mathcal{M}$-pushout,
+		\[\xymatrix{P \ar[r]^{p_1} \ar@{>->}[d]_{p_0} & D_1 \ar@{>->}[d]^{f_1}& P \ar[r]^{q_1} \ar@{>->}[d]_{q_0} & Q_1 \ar@{>->}[d]^{a_1}\\ D_0 \ar[r]_{g_0} & G_1&Q_0 \ar[r]_{b_0} & H_1}\]
+		then there exists an isomorphism $v\colon P\to T$ fitting in the diagram below:
+		\[\xymatrix{ P \ar@{.>}[dr]^{v} \ar[rrr]^{q_1} \ar@{>->}[ddd]_{q_0}&&& Q_1 \ar@{>->}[ddd]^{a_1} \ar[dl]_{\phi_{Q_1}}\\&T \ar@{>->}[d]_{t_0}\ar[r]^{t_1}& D'_1 \ar@{>->}[d]^{f'_1} \\ & D'_0\ar[r]_{g'_0} & G'_1\\Q_0 \ar[rrr]_{b_0} \ar[ur]_{\phi_{Q_0}}&&& H_1 \ar[ul]^{\phi_{H_1}}}\]
+
+		\item consider the diagram below, in which the inner square is a pullback and the dotted arrows are constructed as in \Cref{rem:deco}:
+		\[\xymatrix{K_1 \ar[r]^{r_1} \ar@/_.3cm/[ddr]_{k'_0} \ar@{.>}[dr]^{e_0}& R_1  \ar[dr]^{i'_0}  && K_0 \ar@{>->}[r]^{l_0} \ar@/_.3cm/[ddr]_{k'_1} \ar@{.>}[dr]^{e_1}& L_1  \ar[dr]^{i'_1} \\& T\ar@{>->}[d]_{t_0} \ar[r]^{t_1}& D'_1  \ar@{>->}[d]^{f'_1} && T \ar@{>->}[r]^{t_0} \ar[d]_{t_1}& D'_0 \ar[d]^{g'_0}\\&D'_0 \ar[r]_{g'_0} & G'_1 && D'_1\ar@{>->}[r]_{f'_1} & G'_1}\]
+		then $v\circ u_1=e_0$, $v\circ u_0=e_1$ and the two squares below are pushouts;
+		\[\xymatrix{K_1  \ar[d]_{e_0} \ar[r]^{r_1} & R_1 \ar[d]^{i'_0} & K_0 \ar@{>->}[r]^{l_0} \ar[d]_{e_1}& L_0 \ar[d]^{i'_1}\\ T \ar[r]_{t_1}  & D'_1 & T \ar@{>->}[r]_{t_0} & D'_0 }\]
+
+	\item $(i'_0, i'_1)$ is a strong independence pair;
+
+	\item there exists a commutative diagram the one below.
+
 	\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
@@
 		\ar[dr]^{r_1}\\L_0
-		\ar@/_.6cm/[ddrr]_(.2){i'_0}|(.31)\hole|(.81)\hole
+		\ar@/_.6cm/[ddrr]_(.2){i'_1}|(.31)\hole|(.81)\hole
 		\ar[dr]^(.4){m_0}|(.61)\hole && D_0
@@
 		\ar[dr]|(.4)\hole^(.65){g_1}
-		\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
-		&&P_1\ar[dr]_{q_1}	\ar@{>->}[dl]^{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole^(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole_(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_1}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_0} |(.69)\hole }\]
-
-\end{remark}
-
-We can now turn to prove the fundamental property that we need to rely upon:  any decorated switch induces a consistent permutation.
+		\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_0}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
+		&&P\ar@{.>}[dr]_{z_1}	\ar@{>.>}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
+	in which the following four squares are all pushouts, while the first three are also pullbacks.
+	\[\xymatrix{P \ar@{>->}[r]^{p_0} \ar@{>->}[d]_{p_1}& D_0 \ar@{>->}[d]^{g_0}  & P \ar@{>->}[r]^{z_0} \ar@{>->}[d]_{p_0}& D'_0 \ar@{>->}[d]^{f'_0} &  P \ar@{>->}[d]_{z_0} \ar[r]^{z_1} & D'_1 \ar@{>->}[d]^{f'_1} & P\ar[r]^{z_1} \ar[d]_{p_1}&D'_1 \ar[d]^{g'_1}\\ D_1 \ar@{>->}[r]_{f_1} & G_1  & D_0 \ar@{>->}[r]_{f_0} & G_0 & D'_0 \ar[r]_{g'_0}& G'_1 & D_1 \ar[r]_{g_1}& G_2}\]
+	\end{enumerate}
+\end{lemma}
+\begin{proof}
+	\begin{enumerate}
+		\item  By \Cref{prop:pbpoad}, the square below is also a pullback.
+			\[\xymatrix{P \ar[r]^{q_1} \ar@{>->}[d]_{q_0} & Q_1 \ar@{>->}[d]^{a_1}\\ Q_0 \ar[r]_{b_0} & H_1}\]
+			Thus by the universal property of pullbacks  we get the dotted arrows $v\colon P\to T$ and $w\colon T\to P$ in the following diagrams.
+		\[\xymatrix{ P \ar@{.>}[dr]^{v} \ar[rrr]^{q_1} \ar@{>->}[ddd]_{q_0}&&& Q_1 \ar@{>->}[ddd]^{a_1} \ar[dl]_{\phi_{Q_1}}& T\ar@{.>}[dr]^{w}  \ar[rrr]^{t_1} \ar@{>->}[ddd]_{t_0}&&& D'_1 \ar[dl]_{\phi^{-1}_{Q_1}} \ar@{>->}[ddd]^{f'_1}\\&T \ar@{>->}[d]_{t_0}\ar[r]^{t_1}& D'_1 \ar@{>->}[d]^{f'_1} &&& P \ar@{>->}[d]_{q_0}\ar[r]^{q_1}& Q_1\ar@{>->}[d]^{a_1}\\ & D'_0\ar[r]_{g'_0} & G'_1 &&& Q_0 \ar[r]_{b_0}& H_1 \\Q_0 \ar[rrr]_{b_0} \ar[ur]_{\phi_{Q_0}}&&& H_1 \ar[ul]^{\phi_{H_1}} & D'_0 \ar[rrr]_{g'_0} \ar[ur]_{\phi^{-1}_{Q_0}}&&&G'_1 \ar[ul]^{\phi^{-1}_{H_1}}}\]
+
+To see that they are one the inverse of the other it is then enough to compute.
+		\[\begin{split}
+		t_0\circ v\circ w &=\phi_{Q_0}\circ q_0\circ w\\&=\phi_{Q_0}\circ \phi^{-1}_{Q_0} \circ t_0\\&=t_0\\q_0\circ w\circ v&=\phi^{-1}_{Q_0}	\circ t_0\circ v\\&=\phi^{-1}_{Q_0} \circ \phi_{Q_0}\circ q_0\\&=q_0 	\end{split}\qquad \begin{split}
+		t_1\circ v\circ w &=\phi_{Q_1}\circ q_1\circ w\\&=\phi_{Q_1}\circ \phi^{-1}_{Q_1} \circ t_1\\&=t_1\\q_1\circ w\circ v&=\phi^{-1}_{Q_1}	\circ t_1\circ v\\&=\phi^{-1}_{Q_1} \circ \phi_{Q_1}\circ q_1\\&=q_1
+		\end{split}\]
+
+	\item By \Cref{thm:switch_uni}, we know that $\phi_{G_0}=\id{G_0}$, so that $a_0=f'_0\circ \phi_{Q_0}$, moreover, by the same theorem we have 
+	\[\phi_{Q_1}\circ j_0=i'_0 \qquad  \phi_{Q_0}\circ j_1=i'_1\]
+
+		We can now use the previous equalities to get
+		\[\begin{split}
+			t_0\circ v\circ u_0&=\phi_{Q_0} \circ q_0\circ u_0\\&=\phi_{Q_0}\circ j_1\circ l_0\\&=i'_1\circ l_0\\&=t_0\circ e_1\\	t_0\circ v\circ u_1&=\phi_{Q_0} \circ q_0\circ u_1\\&=k'_0\\&= t_0\circ e_0
+		\end{split} \qquad \begin{split}
+			t_1\circ v\circ u_1&=\phi_{Q_1} \circ q_1\circ u_1\\&=\phi_{Q_1}\circ j_0\circ r_1\\&=i'_0\circ r_1\\&= t_1\circ e_0 \\ t_1\circ v\circ u_0&=\phi_{Q_1} \circ q_1\circ u_0\\&=k'_1\\&=t_1\circ e_1
+		\end{split}\]
+
+	So that $v\circ u_1=e_0$ and $v\circ u_0=e_1$. The thesis now follows from the two diagrams below, since their left halves are pushouts by construction.		
+		\[\xymatrix{K_1  \ar@/^.4cm/[rr]^{e_0}\ar[r]_{u_1} \ar[d]_{r_1}& P \ar[r]_{v} \ar[d]_{q_1} & T \ar[d]^{t_1} & K_0 \ar@/^.4cm/[rr]^{e_1} \ar@{>->}[d]_{l_0}\ar[r]_{u_0} & P \ar[r]_{v}  \ar@{>->}[d]_{q_0}& T \ar@{>->}[d]^{t_0}\\ R_1 \ar@/_.4cm/[rr]_{i'_0} \ar[r]^{j_0}& Q_1 \ar[r]^{\phi_{Q_1}} & D'_1 & L_0 \ar@/_.4cm/[rr]_{i'_1} \ar[r]^{j_0} & Q_0 \ar[r]^{\phi_{Q_0}} & D'_0 }\]
+
+		\item Given the results of the previous point, it is now enough to show that the pushout of $r_0\colon K_0\to R_0$ along $e_1\colon K_0\to T$ exists. We can consider the diagram below
+		\[\xymatrix{K_0 \ar@/^.4cm/[rr]^{u_0} \ar[d]_{r_0} \ar[r]_{e_1}& T  \ar[d]_{p_1\circ w}\ar[r]_{w} & P \ar[d]^{p_1}\\ R_0 \ar[r]_{i_0}& D_1 \ar[r]_{\id{D_1}}& D_1}\]
+		But the outer diagram is a pushout since $(i_0, i_1)$ is strong and we can conclude.
+
+		\item Let $z_0\colon P\mto D'_0$ and $z_1\colon P\to D_1$ be, respectively, $t_0\circ v$ and $t_1\circ v$. Then we have
+
+		\[\begin{split}
+		g'_0\circ z_0&=g'_0\circ t_0\circ v\\&=f'_1\circ t_1\circ v\\&=f'_1\circ z_1
+		\end{split}\quad \begin{split}
+		z_0\circ u_1&=t_0\circ v\circ u_1\\&=\phi_{Q_0}\circ q_0\circ u_1\\&=k'_0
+		\end{split} \quad \begin{split}
+		z_1\circ u_0&=t_1\circ v\circ u_0\\&=\phi_{Q_1}\circ q_1\circ u_0\\&=k'_1
+		\end{split}\]
+
+		Moreover
+		\[\begin{split}
+			f'_0\circ z_0&=f'_0\circ t_0\circ v\\&=f'_0\circ \phi_{Q_0}\circ q_0\\&=a_0\circ q_0\\&=f_0\circ p_0
+		\end{split} \qquad \begin{split}
+		g'_1\circ z_1=g'_1\circ t_1\circ v\\&=g'_1\circ \phi_{Q_1}\circ q_1\\&=\phi_{G_2}\circ b_1 \circ q_1\\&=\phi_{G_2}\circ g_1\circ p_1\\&=f_0\circ p_0
+		\end{split} \]
+
+		Therefore the $z_0$ and $z_1$ fit in the diagram above.
+
+		To conclude, notice that the the four rectangles below and their halves, by construction and by point $3$, are pushouts, thus by \Cref{lem:po1} also their right halves are
+		pushouts.
+
+		\[\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar[d]_{r_0}\ar[r]_{u_0}
+			&P\ar[d]^{p_1} \ar@{>->}[r]_{p_0} & D_0 \ar[d]^{g_0}&K_0
+			\ar@/^.4cm/[rr]^{k'_1}\ar@{>->}[d]_{l_0}\ar[r]_{u_0}
+			&P\ar@{>->}[d]^{z_0} \ar[r]_{z_1} & D'_1 \ar@{>->}[d]^{f'_1}\\
+			R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i'_1}&D_1 \ar@{>->}[r]^{f_1}
+			& G_1&L_1 \ar@/_.4cm/[rr]_{m'_1} \ar[r]^{i_1}&D'_0\ar[r]^{g'_0} &
+			G'_1}\]
+		\[\xymatrix{K_0
+			\ar@/^.4cm/[rr]^{k_0}\ar@{>->}[d]_{l_0}\ar[r]_{u_0}
+			&P\ar@{>->}[d]^{z_0} \ar@{>->}[r]_{p_0} & D_0
+			\ar@{>->}[d]^{f_0}&K_1
+			\ar@/^.4cm/[rr]^{k_1}\ar[d]_{r_1}\ar[r]_{u_1}
+			&P\ar[d]^{z_1} \ar[r]_{p_1} & D_1 \ar[d]^{g_1}\\
+			L_0 \ar@/_.4cm/[rr]_{m_0} \ar[r]^{i'_1}&D'_0 \ar@{>->}[r]^{f'_0}
+			& G_0&R_1 \ar@/_.4cm/[rr]_{h_1} \ar[r]^{i'_0}&D'_1 \ar[r]^{b_1}
+			& G_2}\]
+
+			We conclude by \Cref{prop:pbpoad}. \qedhere 
+	\end{enumerate}
+\end{proof}
+
+We can now turn to prove the fundamental property that we need to rely upon:  any decorated switch along a strong independence pair induces a consistent permutation.
 
@@
 	Let $(\der{D}, \alpha, \omega)$ be a decorated derivations of length $2$ and suppose that $(\der{E}, \alpha, \omega)$ is a decorated switch for it along the independence pair $(i_0, i_1)$.
-Then the following are true:
+Then there exists an arrow $\kappa\colon G_1\to \tpro{E}$ such that
+		\[\kappa \circ g_{0} = \iota_{\der{E}, G_0}\circ f_{0} \qquad \kappa\circ h_{0}= \iota_{\der{E}, R_0}\]
+
+		Moreover, if $(i_0, i_1)$ is strong, also the following facts are true:
 		\begin{enumerate}
-		\item there exists an arrow $\kappa\colon G_1\to \tpro{E}$ such that 
-		\[\kappa \circ g_{0} = \iota_{\der{E}, G_0}\circ f_{0} \qquad \kappa\circ h_{0}= \iota_{\der{E}, R_0}\]
 		\item there exists an arrow $\phi\colon \tpro{D}\to \tpro{E}$ such that
@@
 
-	\begin{enumerate}
-		\item  We can start computing to get:
+ $G_1$ is obtained as the pushout of $k_0$ along $r_0$m thus get the wanted arrow $\kappa\colon G_1\to \tpro{E}$ it is now enough to compute:
 	\begin{align*}
@@
 	\end{align*}
-		Thus we get the wanted arrow $\kappa\colon G_1\to \tpro{E}$.
-
-		\item 
+
+	Let us now suppose that $(i_0,i_1)$ is a strong independence pair. We can then consider the following two squares, the first of which is a pullback and the second one, by strongness, a  pushout.
+
+			\[\xymatrix{P \ar[r]^{p_1}  \ar@{>->}[d]_{p_0} & D_1 \ar@{>->}[d]^{f_1} & K_0 \ar[r]^{r_0}  \ar[d]_{u_0} & R_0 \ar[d]^{i_0}\\ D_0\ar[r]_{g_0} & G_1 & P\ar[r]_{p_1} & D_1}\]
+
+	\begin{enumerate}
+		\item   Consider the arrow $\kappa\colon G_1\to \tpro{E}$ built in the previous point, then we have
+		\begin{align*}
+			\kappa \circ f_1\circ i_0&=\kappa\circ h_0\\&=\iota_{\der{E},R_0}\\&=\iota_{\der{E}{G_2}}\circ h'_1\\&=\iota_{\der{E}{G_2}}\circ g_1\circ i_0
+		\end{align*}
+
+		\begin{align*}
+			\kappa\circ f_1\circ p_1&=\kappa \circ g_0\circ p_0\\&=\iota_{\der{E},G_0}\circ f_0\circ p_0
+		\end{align*}
 		\item 
@@
 	\end{enumerate}
+\end{proof}
+
+\Cref{prChurch} and \Cref{lem:switchtoperm} guarantees some basic but fundamental properties of switches whithout which developing a theory of concurrency seems hopeless, we are thus lead to the following definition.
+
+\begin{definition}
+A left-linear DPO rewriting system $(\X, \R)$ is \emph{strong enforcing} if every independence pair is strong.
+\end{definition}
+
+The notion of strong enforcing DPO rewriting system encompasses that of linear one.
+
+\begin{proposition}\label{prop:linstrong}
+	Every linear rewriting system $(\X, \R)$ is strong enforcing.
+\end{proposition}
+\begin{proof}
+	Suppose that $\X$ is $\mathcal{M}$-adhesive and let $(i_0, i_1)$ be
+	an independence pair as below
+	\[
+	\xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0
+		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar@{>->}[r]^{r_0} & R_0
+		\ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0}
+		&& L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
+		\ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar@{>->}[rr]^{r_1} && R_1
+		\ar[d]^{h_1} \\G_0 && \ar@{>->}[ll]^{f_0} D_0
+		\ar@{>->}[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
+		\ar@{>->}[rr]_{g_1}&& G_2}\]
+
+	Since $(\X, \R)$ is linear, then $r_1\colon K_1\to R_1$ belongs to
+	$\mathcal{M}$, thus it admits a pushout along $u_1\colon K_1\to P$,
+	as desired. Moreover, let us consider the two rectangles below
+	\[
+	\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar@{>->}[d]_{r_0}\ar[r]_{u_0}
+		&P\ar@{>->}[d]^{p_1} \ar@{>->}[r]_{p_0} & D_0
+		\ar@{>->}[d]^{f_0}& K_1
+		\ar@/^.4cm/[rr]^{k_1}\ar@{>->}[d]_{l_1}\ar[r]_{u_1}
+		&P\ar@{>->}[d]^{p_0} \ar@{>->}[r]_{p_1} & D_1
+		\ar@{>->}[d]^{f_1}\\ R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i_0}&D_1
+		\ar@{>->}[r]^{f_1} & G_1& L_1 \ar@/_.4cm/[rr]_{m_1}
+		\ar[r]^{i_1}&D_0 \ar@{>->}[r]^{g_0} & G_1} \] By hypothesis
+	$r_0$ and $l_1$ are in $\mathcal{M}$, thus $f_1$ and $g_0$ belong to
+	it too. The first point of \Cref{lem:popb} yields the thesis.
+\end{proof}
+
+We can easily
+
+\begin{lemma}
+Let $(P, \{p_0, p_1\})$ be the pullback of $f_1$ along $g_1$, then there exists $z_0\colon P\mto D'_0$ and $z_1\colon P\to D'_1$ making the following diagram commutative
+\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
+	\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
+	\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
+	\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){u_0}\ar[ur]^{r_0}&& G_1 &&
+	K_1
+	\ar@/^.6cm/[ddll]|(.36)\hole_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
+	\ar[dr]^{r_1}\\L_0
+	\ar@/_.6cm/[ddrr]_(.2){i'_1}|(.31)\hole|(.81)\hole
+	\ar[dr]^(.4){m_0}|(.61)\hole && D_0
+	\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1
+	\ar[dr]|(.4)\hole^(.65){g_1}
+	\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_0}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
+	&&P\ar@{.>}[dr]_{z_1}	\ar@{>.>}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
+moreover, the following squares are all pushouts, moreover the first two are also pullbacks.
+\[\xymatrix{P \ar@{>->}[r]^{z_0} \ar@{>->}[d]_{p_0}& D'_0 \ar@{>->}[d]^{f'_0} &  P \ar@{>->}[d]_{z_0} \ar[r]^{z_1} & D'_1 \ar@{>->}[d]^{f'_1} & P\ar[r]^{z_1} \ar[d]_{p_1}&D'_1 \ar[d]^{g'_1}\\ D_0 \ar@{>->}[r]_{f_0} & G_0 & D'_0 \ar[r]_{g'_0}& G'_1 & D_1 \ar[r]_{g_1}& G_2}\]
+\end{lemma}
+\begin{proof}
+	Define $z_0$ and $z_1$ to be, respectively, $t_0\circ v$ and $t_1\circ v$. To prove the commutativity of the diagram in the thesis, first of all we can notice that
+	\begin{align*}
+		g'_0\circ z_0\\&= g'_0\circ t_0\circ v\\&=f'_1\circ t_1\circ v\\&=f'_1\circ z_1
+	\end{align*}
+	To prove the other identities, it is enough to compute and use the identities obtained in the previous point. On the one hand we have
+	\[	\begin{split}f'_0\circ z_0&=f'_0\circ t_0\circ v\\&=f'_0\circ \phi_{Q_0}\circ q_0\\&=a_0\circ q_0\\&=f_0\circ p_0 
+	\end{split} \qquad \begin{split}
+		g'_1\circ z_1&=g'_1\circ t_1\circ v\\&=g'_1\circ \phi_{Q_1}\circ q_1\\&=\phi_{G_2}\circ b_1\circ q_1\\\phi_{G_2}\circ g_1\circ p_1\\&=
+	\end{split}\]
+
+	\[\begin{split}
+		z_0\circ u_0&= t_0\circ v \circ u_0\\&=t_0\circ e_1\\&=i'_1\circ l_0\\ 	f'_0\circ z_0&=f'_0\circ t_0\circ v\\&=f'_0\circ \phi_{Q_0}\circ q_0\\&=a_0\circ q_0\\&=f_0\circ p_0
+	\end{split}\quad \begin{split}
+		z_1\circ u_1&=t_1\circ v\circ u_1\\&=t_1\circ e_1\\&=i'_0\circ r_1
+	\end{split} \quad \begin{split}
+	aaa	
+	\end{split}\]
+
 \end{proof}
@@
 
+\todo{Questa sezione è da riscrivere bene}
+
 A first class consists of those rewriting systems over

### 2025-02-28 2025-notes.tex
notes

\documentclass{article}
\usepackage{pdfpages}
\usepackage{hyperref}
\usepackage{forloop}
\usepackage{tikz}

\newcounter{pdfpage}
\begin{document}

\hypertarget{start}{}

\section*{Some ideas for the second part of the paper}

\begin{itemize}

  \thispagestyle{empty}

\item Irreducibles and axioms:
  \begin{itemize}
  \item Characterisation of the irreducibles \hyperlink{pdfpage.1}{page 1}
  \item Interchangebility axioms in this context \hyperlink{pdfpage.3}{page 3}
  \end{itemize}

\item \textbf{Idea}: work with rewriting systems with stronger
  properties ensuring both interchangeability and good properties
  w.r.t. fusions (\hyperlink{pdfpage.4}{page 4}, done also in the paper)

  \emph{Paradigmantic example}: left-linear rules on graphs where lhs
  has no isolated nodes and right-leg is inective on edges.

  The context ensures that 
  \begin{itemize}
  \item the rewriting system is well swiitching

  \item morphisms into the colimit are in the class of morphisms used for lhs

  \item existence of a minimal quotient to which a rule applies
  \end{itemize}

  Additionally, in this setting:
  \begin{itemize}
  \item a rewriting step can be lifted up and down along quotients (see property 1 page \hyperlink{pdfpage.9}{page 9}, property 2 page \hyperlink{pdfpage.10}{page 10})

  \item independence (up to fusion) can be checked in the colimit
    [\hyperlink{pdfpage.13}{page 13}, some considerations here might be uselessly
    complex as they might be done before taking the assumptions on
    rules]

  \item 
   we can work with derivations up to fusion: each step can be preceded by a quotient which is (the minimal one - unclear whether it is convenient to require minimality) sufficient to allow the application of the rule [some reflections starting from page \hyperlink{pdfpage.17}{page 17}, including a notion of switch and further considerations on independence in the colimit)

 \item characterise transitively interchangeable irreducibles via
   derivations up to fusions [\hyperlink{pdfpage.23}{page 23}]

 \item prove the interchangeability axioms [page
   \hyperlink{pdfpage.24}{page 24}]

 \end{itemize}
\end{itemize}

\setcounter{page}{0}

\forloop{pdfpage}{1}{\value{pdfpage} < 27}{
  \includepdf[pages=\thepdfpage,pagecommand={
    \vspace*{-9cm}
    \hypertarget{pdfpage.\thepdfpage}{}
        \begin{tikzpicture}[remember picture, overlay]
            % Position text at the top-right corner
            \node[anchor=north east, xshift=-10pt, yshift=-10pt] at (current page.north east) {
                \textbf{\large \hyperlink{start}{Start}}
            };
        \end{tikzpicture}
        }]{2025-notes-file.pdf}
}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2025-03-07 full_version/leftlinear.tex
minima

@@
 \begin{example}	\label{ex:seq-ind}
-	Consider the rewriting system  $(\cat{Graph}, \R)$ and the derivarion $\der{D}$ introduced in \Cref{ex:1}.	Steps $\dder{D}_1$ and $\dder{D}_2$ are clearly sequential
+	Consider the rewriting system  $(\cat{Graph}, \R)$ and the derivation $\der{D}$ introduced in \Cref{ex:1}.	Steps $\dder{D}_1$ and $\dder{D}_2$ are clearly sequential
 	independent via the arrows $R_1 \to D_2$, $L_2 \to D_1$
@@
 
-\Cref{ex:diff1} show that sequential independence it does not suffice, in general, to guarantee the existence of a switch.  Inspired by the notion of of \emph{canonical filler}
+\Cref{ex:diff1} show that sequential independence does not suffice, in general, to guarantee the existence of a switch.  Inspired by the notion of of \emph{canonical filler}
 \cite{heindel2009category}, we are now going to give some conditions guaranteeing the existence of a switch. We start proving some technical properties of independence pairs.
@@
 
-To see that they are one the inverse of the other it is then enough to compute.
+To see that they are one the inverse of the other is then enough to compute.
 		\[\begin{split}
@@
 
- $G_1$ is obtained as the pushout of $k_0$ along $r_0$m thus get the wanted arrow $\kappa\colon G_1\to \tpro{E}$ it is now enough to compute:
+ $G_1$ is obtained as the pushout of $k_0$ along $r_0$, thus to get the wanted arrow $\kappa\colon G_1\to \tpro{E}$ is now enough to compute:
 	\begin{align*}
@@
 	&&P\ar@{.>}[dr]_{z_1}	\ar@{>.>}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
-moreover, the following squares are all pushouts, moreover the first two are also pullbacks.
+moreover, the following squares are all pushouts, and the first two are also pullbacks.
 \[\xymatrix{P \ar@{>->}[r]^{z_0} \ar@{>->}[d]_{p_0}& D'_0 \ar@{>->}[d]^{f'_0} &  P \ar@{>->}[d]_{z_0} \ar[r]^{z_1} & D'_1 \ar@{>->}[d]^{f'_1} & P\ar[r]^{z_1} \ar[d]_{p_1}&D'_1 \ar[d]^{g'_1}\\ D_0 \ar@{>->}[r]_{f_0} & G_0 & D'_0 \ar[r]_{g'_0}& G'_1 & D_1 \ar[r]_{g_1}& G_2}\]
@@
 
-\begin{lemma}{lemma}{lemVTame}
+\begin{lemma}%{lemma}{lemVTame}
 	\label{bono}

### 2025-03-07 full_version/leftlinear.tex
switch

--- 2025-02-20 full_version/leftlinear.tex
@@
 
-\begin{definition}[Switch] \label{def:switch}
+\begin{definition}[Pre-switch] \label{def:switch}
 	Let $\X$ be an $\mathcal{M}$-adhesive category 
@@
 		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
-		\ar@{.>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
-		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{.>}@/_.25cm/[dlll]^(.4){i_1}
+		\ar@{>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
+		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{>}@/_.25cm/[dlll]^(.4){i_1}
 		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
@@
 
-	A \emph{switch} of $\der{D}$ along $(i_0,i_1)$ is
+	A \emph{pre-switch} of $\der{D}$ along $(i_0,i_1)$ is
 	a derivation $\der{E}=\{\dder{E}_i\}_{i=0}^1$, between the same objects and using the same rules
@@
 
-	If a switch of $\dder{D}_0$ and $\dder{D}_1$ exists we say that they are \emph{switchable}.
-
-	Let $(\der{D}, \alpha, \omega)$ be a decorated derivation of length $2$, and $(i_0, i_1)$ an independence pair between $\dder{D}_0$ and $\dder{D}_1$.
-A \emph{decorated switch} of $(\der{D}, \alpha, \omega)$ along $(i_0, i_1)$ is $(\der{E}, \alpha, \omega)$, where $\der{E}$ is a switch for $\der{D}$ along $(i_0, i_1)$.
 \end{definition}
@@
 
-	A switch of $\der{D}$ along such independence pair is the derivation
+	A pre-switch of $\der{D}$ along such independence pair is the derivation
 	$\der{E}$ depicted below. Instead,  the first two
@@
 
-Let $\der{E}=\{\dder{E}_i\}_{i=0}^1$ be a switch for $\dder{D}_0$
+Let $\der{E}=\{\dder{E}_i\}_{i=0}^1$ be a pre-switch for $\dder{D}_0$
 and $\dder{D}_1$ along an independence pair $(i_0, i_1)$, then by definition we have an independence pair $(i'_0, i'_1)$ between $\dder{E}_0$ and $\dder{E}_1$ such that
@@
 
-A first property of switches is that they are unique up to abstraction equivalence.
-
-\begin{lemma}[Uniqueness of switches]
+A first property of pre-switches is that they are unique up to abstraction equivalence.
+
+\begin{lemma}[Uniqueness of pre-switches]
 	\label{thm:switch_uni}
@@
 	that both $\der{E}=\{\dder{E}_i\}_{i=0}^1$ and
-	$\der{F}=\{\dder{F}_i\}_{i=0}^1$ are switches of $\dder{D}_0$ and
-	$\dder{D}_1$. Then there is an abstraction equivalence $\{\phi_X\}_{X\in \Deltamin(\der{E})}$ between $\der{E}$ and $\der{F}$, whose first component is $\id{G_0}$. Moreover, 
-	\[\phi_{D_{\der{E}, 0}}\circ j_1=a_1 \qquad \phi_{\der{E}, 1}\circ j_0=a_0\]
+	$\der{F}=\{\dder{F}_i\}_{i=0}^1$ are pre-switches of $\dder{D}_0$ and
+	$\dder{D}_1$. Then there is a unique abstraction equivalence $\{\phi_X\}_{X\in \Deltamin(\der{E})}$ between $\der{E}$ and $\der{F}$, whose first component is $\id{G_0}$. Moreover, 
+	\[\phi_{D_{\der{E}, 0}}\circ j_1=a_1 \qquad \phi_{D_{\der{E}, 1}}\circ j_0=a_0\]
 \end{lemma}
@@
 \begin{proof}
-	By definition of switch $\der{E}_0$ and $\der{F}_0$ have the same match $f_0\circ i_1$ and that $\der{E}_1$ and $\der{F}_1$ have the same comatch $g_1\circ i_0$.
+	By definition of pre-switch $\der{E}_0$ and $\der{F}_0$ have the same match $f_0\circ i_1$ and that $\der{E}_1$ and $\der{F}_1$ have the same comatch $g_1\circ i_0$.
 Thus we get the solid part of the diagram below.
@@
 
-	Now, by \Cref{prop:unique} we get $\phi_0\colon D_{\der{E},0}\to D_{\der{F},0}$ and $\psi_1 \colon G_{\der{E},1}\to G_{\der{F},1}$ such that the diagram below commutes.
+	Now, by \Cref{prop:unique} we get isomorphisms $\phi_0\colon D_{\der{E},0}\to D_{\der{F},0}$ and $\psi_1 \colon G_{\der{E},1}\to G_{\der{F},1}$ such that the diagram below commutes.
 	\[\xymatrix{G_{0} & \ar@{>->}[l]_{f_{\der{F},0}} D_{\der{F},0} \ar[r]^{g_{\der{F},0}}& G_{\der{F},1} \\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar[l]_{l_1} \ar[r]^{r_1} & R_{1}  \ar[d]_{h_{\der{E},0}}  \ar[u]^{h_{\der{F},0}}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} & \ar@{>->}[l]^{f_{\der{E},0}} D_{\der{E},0} \ar@/^.5cm/[uu]^(.33){\phi_{0}}|\hole \ar[r]_{g_{\der{E},0}}& G_{\der{E},1} \ar@/_.5cm/[uu]_{\psi_1}}\]
@@
 	Moreover, we have already shown that $\psi_1\circ m_{\der{E},1}=m_{\der{F},1}$.
-Thus, by \Cref{prop:unique} there are the dotted $\phi_1\colon D_{\der{E},1}\to D_{\der{F},1}$ and $\psi_2\colon G_2\to G_2$ as below.
+Thus, by \Cref{prop:unique} there are the dotted isomorphisms $\phi_1\colon D_{\der{E},1}\to D_{\der{F},1}$ and $\psi_2\colon G_2\to G_2$ in the diagram below.
 	\[\xymatrix{G_{\der{F},1} & \ar@{>->}[l]_{f_{\der{F},1}} D_{\der{F},1} \ar[r]^{g_{\der{F},1}}& G_2 \\L_0 \ar[d]^{m_{\der{E},1}} \ar[u]_{m_{\der{F},1}}& K_{0} \ar[d]^{k_{\der{E},1}} \ar[u]_{k_{\der{F},1}}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_{0}  \ar[d]_{g_1\circ i_0}  \ar[u]^{g_1\circ i_0}\\ \ar@/^.5cm/[uu]^{\psi_1} G_{\der{E},1} & \ar@{>->}[l]^{f_{\der{E},1}} D_{\der{E},1} \ar@{.>}@/^.5cm/[uu]^(.33){\phi_{1}}|\hole \ar[r]_{g_{\der{E},1}}& G_2 \ar@{.>}@/_.5cm/[uu]_{\psi_2}}\]
@@
 
-Given two sequentially independent direct derivations, it is not necessarily true that a switch for them exists, as shown by the following example.
+\begin{example}\label{ex:abs}
+	Let $\X$ be the category of $\Set$ and, besides the terminal obect $1$, take the sets
+	\[2=\{0,1\} \qquad 3=\{0,1,2\} \qquad 4=\{0,1,2,3\}\]
+
+Let us consider the DPO-rewriting system given by the (linear) rules below.
+		\[\xymatrix{1 & 1\ar@{>->}[l]_{\id{1}} \ar@{>->}[r]^{\id{1}} & 1 & 1 & 1\ar@{>->}[r]^{\delta^2_0} \ar@{>->}[l]_{\id{1}} & 2}\]
+
+We then have the derivation $\der{D}$ below, composed by two sequentially independent steps.
+		\[\xymatrix@R=20pt@C=20pt{1 \ar@{>->}[d]_{\delta^3_0}&& 1
+	\ar@{>->}[d]_{\delta^3_0}\ar@{>->}[ll]_{\id{1}} \ar@{>->}[r]^{\id{1}} & 1
+	\ar@{>->}@/^.25cm/[drrr]|(.32)\hole_(.4){\delta^3_0}
+	\ar[dr]|(.33)\hole_{\delta^3_0} && 1 \ar@{>->}@/_.25cm/[dlll]^(.4){\delta^3_0}
+	\ar@{>->}[dl]|(.33)\hole^{\delta^3_0}& 1 \ar@{>->}[d]^{\delta^3_0}\ar@{>->}[l]_{\id{1}}
+	\ar@{>->}[rr]^{\delta^2_0} && 2 \ar@{>->}[d]^{i_2}\\3 && \ar@{>->}[ll]^{\id{3}}
+	3 \ar@{>->}[rr]_{\id{3}}&& 3 && \ar@{>->}[ll]^{\id{3}} 3
+	\ar@{>->}[rr]_{i_3}&& 4}
+\]
+where $i_3\colon 3\mto 4$ is the obvious inclusion, while $i_2\colon 2\mto 4$ sends $0$ to $0$ and $1$ to $3$.	 Now, we can construct two pre-switches for $\dder{D}_0$ and $\dder{D}_1$ along $(\delta_0, \delta_0)$.
+Indeed, on the one hand we can consider  $\der{E}:=\{\dder{E}_i\}_{i=0}^1$ as
+		\[\xymatrix@R=20pt@C=20pt{1 \ar@{>->}[d]_{\delta^3_0}&& 1
+	\ar@{>->}[d]_{\delta^3_0}\ar@{>->}[ll]_{\id{1}} \ar@{>->}[r]^{\delta^2_0} & 2
+	\ar@{>->}@/^.25cm/[drrr]|(.32)\hole_(.4){i_2}
+	\ar[dr]|(.33)\hole_{i_2} && 1 \ar@{>->}@/_.25cm/[dlll]^(.4){\delta^3_0}
+	\ar@{>->}[dl]|(.33)\hole^{\delta^4_0}& 1 \ar@{>->}[d]^{\delta^4_0}\ar@{>->}[l]_{\id{1}}
+	\ar@{>->}[rr]^{\id{1}} && 1 \ar@{>->}[d]^{\delta^4_0}\\3 && \ar@{>->}[ll]^{\id{3}}
+	3 \ar@{>->}[rr]_{i_{3}}&& 4 && \ar@{>->}[ll]^{\id{4}} 4
+	\ar@{>->}[rr]_{\id{4}}&& 4}
+\]
+and we have
+\[
+\delta^3_0=\id{3} \circ \delta^3_0
+\qquad i_2=\id{4} \circ i_2
+\qquad \delta^3_0= \id{3} \circ \delta^3_0
+\qquad \delta^4_0= i_3\circ \delta^3_0\]
+
+On the other hand, there is an isomorphism $t\colon 4\mto 4$ be the isomorphism which swap $1$ with $2$ and fix the other elements of $4$.
+Then we can also construct $\der{F}:=\{\dder{F}_i\}_{i=0}^1$ as below:
+		\[\xymatrix@R=20pt@C=20pt{1 \ar@{>->}[d]_{\delta^3_0}&& 1
+		\ar@{>->}[d]_{\delta^3_0}\ar@{>->}[ll]_{\id{1}} \ar@{>->}[r]^{\delta^2_0} & 2
+		\ar@{>->}@/^.25cm/[drrr]|(.32)\hole_(.4){i_2}
+		\ar[dr]|(.33)\hole_{i_2} && 1 \ar@{>->}@/_.25cm/[dlll]^(.4){\delta^3_0}
+		\ar@{>->}[dl]|(.33)\hole^{\delta^4_0}& 1 \ar@{>->}[d]^{\delta^4_0}\ar@{>->}[l]_{\id{1}}
+		\ar@{>->}[rr]^{\id{1}} && 1 \ar@{>->}[d]^{\delta^4_0}\\3 && \ar@{>->}[ll]^{\id{3}}
+		3 \ar@{>->}[rr]_{i_{3}}&& 4 && \ar@{>->}[ll]^{\id{4}} 4
+		\ar@{>->}[rr]_{t}&& 4}
+	\]
+	and also in this case we get a pre-switch since
+	\[
+	\delta^3_0=\id{3} \circ \delta^3_0
+	\qquad i_2=t\circ i_2
+	\qquad \delta^3_0= \id{3} \circ \delta^3_0
+	\qquad \delta^4_0= i_3\circ \delta^3_0\]
+
+	Now, by \Cref{thm:switch_uni} we get an abstraction equivalence fitting in the diagram below.
+	\[\xymatrix@C=30pt@R=25pt{3 && \ar@{>->}[ll]_{\id{3}} 3 \ar@{>->}[rr]^{i_3}&& 4 && \ar@{>->}[ll]_{\id{4}} 4 \ar@{>->}[rr]^{\id{4}}&& 4\\1 \ar@{>->}[d]^{\delta^3_0} \ar@{>->}[u]_{\delta^3_0}&& 1 \ar@{>->}[d]^{\delta^3_0} \ar@{>->}[u]_{\delta^3_0}\ar@{>->}[ll]_{\id{1}} \ar@{>->}[r]^{\delta^2_0} & 2 \ar@{>->}@/^.35cm/[drrr]|(.315)\hole_(.4){i_2} \ar@{>->}[dr]|(.3)\hole_{i_2} \ar@{>->}@/_.35cm/[urrr]|(.315)\hole^(.4){i_2} \ar@{>->}[ur]|(.3)\hole^{i_2}& &1 \ar@{>->}@/_.35cm/[dlll]^(.4){\delta^3_0} \ar@{>->}[dl]|(.3)\hole^{\delta^4_0} \ar@{>->}@/^.35cm/[ulll]_(.4){\delta^3_0} \ar@{>->}[ul]|(.3)\hole_{\delta^4_0}& 1 \ar@{>->}[d]_{\delta^4_0} \ar@{>->}[u]^{\delta^4_0}\ar@{>->}[l]_{\id{1}} \ar@{>->}[rr]^{\id{1}} && 1 \ar@{>->}[d]_{\delta^4_0} \ar@{>->}[u]^{\delta^4_0}\\ \ar@/^.5cm/[uu]^{\id{3}} 3 && \ar[ll]^{\id{3}} 3 \ar@{>}@/^.5cm/[uu]^(.33){\phi_0}|\hole \ar[rr]_{i_3}&& 4 \ar@{>}[uu]_(.76){\psi_1}|(.45)\hole |(.55)\hole&& \ar@{>->}[ll]^{\id{4}} 4 \ar@{>}@/_.5cm/[uu]_(.33){\phi_1}|\hole\ar[rr]_{t}&& 4\ar@{>}@/_.5cm/[uu]_{\psi_2}}\]
+	But then there is only one component of this abstraction equivalence different from the identity, namely the last one, which must coincide with $t$.
+\end{example}
+
+Given two sequentially independent direct derivations, it is not necessarily true that a pre-switch for them exists, as shown by the following example.
 
@@
 	Note that the two direct derivations are sequential
-	independent. However there is no switch since the rule applied by
+	independent. However there is no pre-switch since the rule applied by
 	$\dder{D}_1$ cannot be applied to $c$. In fact, there is a unique morphism
@@
 
-\subsection{Strong-enforcing and well-switching rewriting systems}
-
-\Cref{ex:diff1} show that sequential independence it does not suffice, in general, to guarantee the existence of a switch.  Inspired by the notion of of \emph{canonical filler}
-\cite{heindel2009category}, we are now going to give some conditions guaranteeing the existence of a switch. We start proving some technical properties of independence pairs.
+Before proceeding further we need to prove some other properties of independence pairs.
 
@@
 	$u_1\colon K_1\to P$ and $u_0\colon K_0\to P$ fitting in the
-	central and right square. Moreover, the right one is always
-	a pullback.
+	central and right square. Moreover, the right square is a pullback.
 	\[\xymatrix{P \ar@{>->}[r]^{p_0} \ar[d]_{p_1} & D_0
@@
 		G_1}\]
-	By \Cref{prop:pbpoad,lem:pb1} we get that the left half of
-	the second rectangle is a pullback.
-	\qedhere
+
+The outer diagram given by the second rectangle is an $\mathcal{M}$-pushout, thus we can deduce from \Cref{prop:pbpoad} and \Cref{lem:pb1} that its left half is a pullback.
 \end{proof}
@@
 	and $\der{D}_1$.  If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a
-		switch of $\der{D}$ along $(i_0, i_1)$, then there exists
-		$q_0\colon P\to D_{\der{E},0}$ in the diagram below. 
-		\[\xymatrix{D_{\der{E},0} \ar@{>->}[d]_{f_{\der{E},0}}&P
-			\ar@{.>}[l]_{q_0} \ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1
-			\ar@{>->}[d]^{f_1}\\ G_{0}&D_0 \ar@{>->}[l]^{f_0}\ar[r]_{g_0}&
-			G_1}\]
+	pre-switch of $\der{D}$ along $(i_0, i_1)$, then there is an arrow
+	$z_0\colon P\to D_{\der{E},0}$ in $\mathcal{M}$ fitting in the square below.
+	\[\xymatrix{P \ar@{.>}[r]^-{z_0}  \ar@{>->}[d]_{p_0}& D_{\der{E}, 0} \ar@{>->}[d]^{f_{\der{E},0}} \\ D_0 \ar@{>->}[r]_{f_0} & G_0 }\]
 \end{corollary}
@@
 
-	Since $f_0$ is a monomorphism, every square in the diagram on the left above
-	is a pullback. Thus the whole big square is a pullback too.
-	Applying \Cref{lem:radj} to the pair of squares on the right now gives
-	us the wanted $q_0\colon P\to D_{\der{E},0}$.
-\end{proof}
+	Since $f_0$ is a monomorphism, all the inner squares of the left diagram are pullbacks, thus the whole big square is a pullback too.
+	Now the thesis follows applying \Cref{lem:radj} to the pair of squares on the right.
+	\end{proof}
+
+\begin{example}\label{ex:abs2}
+Let $\der{D}$ be the derivation of \Cref{ex:abs} and consider the pre-switch $\der{F}$. Then we have the following diagram
+
+	\[\xymatrix@C=22pt@R=22pt{&&1 \ar@{>->}@/_.9cm/[ddrr]_(.2){\delta^3_0}|(.72)\hole
+	\ar@{>->}[dr]^{\delta^3_0}&& 1\ar@{>->}@/^.9cm/[ddll]^(.2){\delta^3_0}
+	\ar@{>->}[dl]_{\delta^3_0}\\
+	&1\ar@{>->}[dr]^{\delta^3_0}\ar@{>->}[dl]_{\id{1}}
+	\ar@{>->}@/_.7cm/[ddrr]|(.38)\hole^(.7){\delta^3_0}\ar@{>->}[ur]^{\id{1}}&& 3 &&
+	1
+	\ar@{>->}@/^.7cm/[ddll]|(.38)\hole_(.7){\delta^3_0}\ar@{>->}[dl]_{\delta^3_0}\ar@{>->}[lu]_{\delta^3_0}
+	\ar@{>->}[dr]^{\delta^2_0}\\
+	1 \ar@/_.7cm/[ddrr]_(.2){\delta^3_0}|(.325)\hole|(.81)\hole
+	\ar@{>->}[dr]^(.35){\delta^3_0}|(.6)\hole && 3
+	\ar@{>->}[dl]|(.4)\hole^(.65){\id{3}}\ar@{>->}[ur]|(.5)\hole^(.7){\id{3} }&&3
+	\ar@{>->}[dr]|(.4)\hole_(.65){i_3}
+	\ar@{>->}[ul]|(.475)\hole_(.7){\id{3}}&&2\ar@{>->}@/^.7cm/[ddll]^(.2){i_2}|(.325)\hole|(.81)\hole\ar@{>->}[dl]_(.35){i_2}|(.6)\hole\\
+	&3 &&3	\ar@{>->}[dl]^{\id{3}}\ar@{>->}[ur]^{\id{3}}\ar@{>->}[ul]_{\id{3}}&&4\\
+	1	\ar@{>->}@/^.7cm/[uurr]^(.2){\delta^3_0} \ar@{>->}[ur]_(.35){\delta^3_0}|(.61)\hole && 3	\ar@{>->}[ul]|(.4)\hole_(.65){\id{3}}\ar@{>->}[dr]|(.5)\hole_(.65){i_3}	&&4\ar@{>->}[ur]|(.4)\hole^(.65){t} \ar@{>->}[dl]|(.5)\hole^(.65){\id{4}}	&& 1\ar[ul]^(.35){\delta^4_0}|(.61)\hole\ar@/_.7cm/[uull]_(.2){\delta^3_0}\\
+	&1	\ar@{>->}[ur]_{\delta^3_0} \ar@{>->}[dr]_{i_2}	\ar@{>->}[ul]^{\id{1}}\ar@/^.7cm/[uurr]_(.65){\delta^3_0}&&4&& 1\ar@{>->}[ur]_{\id{1}} \ar@{>->}[ul]^{\delta^4_0} \ar@{>->}[dl]^{\id{1}} \ar@{>->}@/_.7cm/[uull]^(.65){\delta^3_0}\\&& 2	\ar@{>->}[ur]_{i_2}\ar@{>->}@/^.9cm/[uurr]^(.2){i_2}&& 1 \ar@{>->}[ul]^{\delta^4_0} \ar@{>->}@/_.9cm/[uull]_(.2){\delta^3_0} |(.72)\hole }\]
+
+Notice that there is no arrow $f\colon 3\to 4$ such that 
+\[t\circ f=i_3\circ \id{3} \qquad \id{4}\circ f=i_3\circ \id{3}\]
+
+Indeed, if $f$ satisfies the first equation then $f=t\circ i_3$, while the second one entails $f=i_3$, but $t\circ i_3$ and $i_3$ are different.
+\end{example}
+
+The definition of pre-switch raises some issues.
+First of all we do not have sufficient conditions guaranteeing the existence of a pre-switch, moreover the fact that, as shown by \Cref{ex:abs}, the abstraction equivalence between two pre-switches does not necessarily have the identity as last component is somewhat unfortunate.
+Finally, \Cref{ex:abs2}, shows that this notion  is somewhat asymmetric in nature.
+We will now tackle this last defect, while a solution to the first two is deferred to the next section.
+
+\begin{definition}(Switch) 	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear rewriting system. 
+	Let also $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation made
+	of two sequentially independent derivations $\dder{D}_0$,
+	$\dder{D}_1$ with independence pair $(i_0, i_1)$, as in the diagram below, where the cone with vertex $P$ is a pullback and $u_0\colon K_0\to P$ and $u_1\colon K_1\to P$ are the arrows built in \Cref{prop:tec}.
+	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0 \ar @/^.35cm/[ddrr]^(.3){u_0}
+		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
+		\ar@{>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}|(.68)\hole
+		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{>}@/_.25cm/[dlll]^(.4){i_1}|(.68)\hole 
+		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar @/_.35cm/[ddll]_(.3){u_1}
+		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
+		D_0 \ar[rr]_{g_0}|(.7)\hole&& G_1 && \ar@{>->}[ll]^{f_1}|(.7)\hole D_1
+		\ar[rr]_{g_1}&& G_2 \\ & & & & P \ar[urr]_{p_1} \ar@{>->}[ull]^{p_0}}
+	\]
+
+	Let $\der{E}=\{\dder{E}_i\}_{i=0}^1$, depicted below, be a pre-switch for $\der{D}$ along $(i_0,i_1)$.
+	\[
+	\xymatrix@R=20pt@C=20pt{
+		{L_1} \ar[d]_{m_0'}
+		&&  {K_1} \ar@{>->}[ll]_{l_1} \ar[r]^{r_1} \ar[d]_{k_0'}
+		&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{>}_(.4){i_0'}|(.32)\hole[drrr]
+		& & 
+		{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{>}^(.4){i_1'}[dlll] 
+		&  {K_0} \ar@{>->}[l]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
+		& & {R_0} \ar[d]^{h_1'} \\		
+		{G_0}
+		& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rr]_{g_0'}
+		& &  {G'_1} 
+		& &  {D_1'} \ar@{>->}[ll]^{f_1'} \ar[rr]_{g_1'}
+		& & {G_2}  }
+	\]
+
+	We say that $\der{E}$ is a \emph{switch} for $\der{D}$ along $(i_0, i_1)$ if there is an arrow $z_1\colon P\to D'_1$ fitting in the diagram below, where $z_0\colon P\to D'_0$ is the arrow constructed in \Cref{lem:cose}.
+	\[\xymatrix{D'_0  \ar[d]_{g'_0}& P \ar[r]^{p_1} \ar[l]_{z_0} \ar@{.>}[d]^{z_1} & D_1 \ar[d]^{g_1}\\ G'_1 & D'_1 \ar[r]_{g'_1} \ar@{>->}[l]_{f'_1} & G_2}\]
+
+	If a switch of $\dder{D}_0$ and $\dder{D}_1$ exists we say that they are \emph{switchable}.
+If $(\der{D}, \alpha, \omega)$ is a decorated derivation of length $2$, and $(i_0, i_1)$ an independence pair between $\dder{D}_0$ and $\dder{D}_1$.
+A \emph{decorated switch} of $(\der{D}, \alpha, \omega)$ along $(i_0, i_1)$ is $(\der{E}, \alpha, \omega)$, where $\der{E}$ is a switch for $\der{D}$ along $(i_0, i_1)$.
+\end{definition}
+
+\begin{remark} 
+vari quadrati
+\end{remark}
+
+\begin{lemma}
+	equivalenze
+
+	\begin{enumerate}
+		\item 
+		\item 
+	\end{enumerate}
+\end{lemma}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+We end this section showing that, if a switch exists, then any pre-switch can be turned into one.
+
+\begin{proposition}
+	contenuto...
+\end{proposition}
+\begin{proof}
+	contenuto...
+\end{proof}
+
+\subsection{Strong-enforcing and well-switching rewriting systems}
+
+\Cref{ex:diff1} show that sequential independence it does not suffice, in general, to guarantee the existence of a switch.  Inspired by the notion of of \emph{canonical filler}
+\cite{heindel2009category}, we build on the last results of the previous section to give some conditions guaranteeing the existence of a switch.
 

### 2025-03-07 full_version/leftlinear.tex

@@
 \begin{lemma}
-	equivalenze
-
+
+Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation of length $2$ and $(i_0, i_1)$ an independence pair between $\dder{D}_0$ and $\dder{D}_1$.
+Given a pre-switch $\der{E}$ for $\der{D}$ along $(i_0, i_1)$, the following are equivalent:
 	\begin{enumerate}
-		\item 
-		\item 
+		\item $\der{E}$ is a switch;
+		\item if $(P, \{p_i\}_{i=0}^1)$ is a pullback for $f_{\der{D},1}$ along $g_{\der{D},0}$, then $\iota_{\der{E}}$
 	\end{enumerate}

### 2025-03-07 full_version/permutations.tex
minori

@@
 	A \emph{left-linear DPO-rewriting system} is a pair $(\X, \R)$ where $\X$ is a $\mathcal{M}$-adhesive category and $R$ is a set of left $\mathcal{M}$-linear rules.
-$(\X, \R)$ will be called \emph{linear} if every rule in $R$ is $\mathcal{M}$-linear.
+$(\X, \R)$ is called \emph{linear} if every rule in $R$ is $\mathcal{M}$-linear.
 Similarly, a \emph{consuming} left-linear DPO-rewriting system is one in which every rule is consuming.
 
-	Given  two objects $G$ and $H$ and a rule $\rho=(l,r)$ in $\R$, a \emph{direct derivation $\mathscr{D}$ from $G$ to $H$ applying the rule $\rho$}, is a diagram as the one below, in which both squares are pushouts.
+	Given  two objects $G$ and $H$ and a rule $\rho=(l,r)$ in $\R$, a \emph{direct derivation $\mathscr{D}$ from $G$ to $H$ applying the rule $\rho$} is a diagram as the one below, in which both squares are pushouts
+	(adhesivity ensures that $f$ belongs to $\mathcal{M}$)
+
 	\[\xymatrix{L \ar[d]_{n}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}& H}\]
@@
 \begin{definition}
-	Let $(\X, \R)$ be a left-linear DPO-rewrityng system, with $\X$ $\mathcal{M}$-adhesive.
+	Let $(\X, \R)$ be a left-linear DPO-rewriting system, with $\X$ $\mathcal{M}$-adhesive.
 The \emph{DPO-derivation graph} of $(\X, \R)$ is the (large)  directed graph $\gpo$ having as vertices the objects of $\X$ and in which an edge between $G$ and $H$ is a direct derivation $\dder{D}\colon G\Mapsto H$.	A \emph{derivation} $\der{D}$ between two objects $G$ and $H$ is a path between them in $\gpo$.
@@
 
-	Moreover,  if every $\dder{D}_i$ applies the rule $\rho_i\in R$, then we can define an associated sequence of rules as $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.
+	Moreover,  if every $\dder{D}_i$ applies the rule $\rho_i\in R$, then we can define an associated sequence of rules $r(\der{D})$ as $\{\rho_i\}_{i=0}^n$.
 \end{remark}
@@
 \begin{example}\label{ex:1}
-	Let us consider the category of $\cat{Graph}$ of all graphs and graph morphisms, which is adhesive (see, for instance \cite{lack2005adhesive,lack2006toposes}).
+	Let us consider the category of $\cat{Graph}$ of graphs and graph morphisms, which is adhesive (see, for instance \cite{lack2005adhesive,lack2006toposes}).
 We can endow $\cat{Graph}$ with a set of left-linear rules, for instance taking the following ones.
@@
 \begin{remark}
-	By definition the inclusion $\ske \to \X$ is an equivalence.
-In particular, this mean that, for every objects $X$ of $\X$ there exists $\pi(X)$ in $\ske$ and an isomorphism $\phi_X\colon \pi(X) \to X$.
+	By definition the inclusion $\ske \to \X$ is an equivalence. In particular, for every objects $X$ of $\X$ there exists $\pi(X)$ in $\ske$ and an isomorphism $\phi_X\colon \pi(X) \to X$.
 \end{remark}
@@
 \begin{remark}
-	It is possible to proof that every two skeleta of a given category $\X$ are isomorphic (not only equivalent).
+	It is possible to prove that every two skeleta of a given category $\X$ are isomorphic (not only equivalent).
 For the remaining of this paper we assume that a skeleton $\ske$ of $\X$ and a functor $\pi\colon \X\to \ske$ are chosen once and for all.
@@
 
-\begin{definition}Let $(\X, \R)$ be a left-linear DPO-rewriting system,  an \emph{abstraction equivalence} between two derivations $\der{D}$ and $\der{D'}$ with the same length and such that $r(\der{D})=r(\der{D}')$, is a family of isomorphisms $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ such that, for every $i\in [0, \lgh(\der{D})-1]$ the following diagram commutes
+\begin{definition}Let $(\X, \R)$ be a left-linear DPO-rewriting system.
+An \emph{abstraction equivalence} between two derivations $\der{D}$ and $\der{D'}$ with the same length and such that $r(\der{D})=r(\der{D}')$ is a family of isomorphisms $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ such that, for every $i\in [0, \lgh(\der{D})-1]$ the following diagram commutes
 	\[\xymatrix@C=40pt{G'_i&D'_i \ar[r]^{g'_i} \ar@{>->}[l]_{f'_i}&G'_{i+1}\\  L_i \ar[u]^{m'_i} \ar[d]_{m_i}& K_i \ar[u]^{k'_i} \ar[d]_{k_i} \ar[r]^{r_i} \ar@{>->}[l]_{l_i} &R_i\ar[u]^{h'_i} \ar[d]_{h_i}\\G_i \ar@/_.45cm/[uu]_(.35){\phi_{G_i}}|\hole&D_i\ar@{>->}[l]^{f_i}\ar@/_.45cm/[uu]_(.35){\phi_{D_i}}|\hole \ar[r]_{g_i}&G_{i+1}\ar@/_.45cm/[uu]_{\phi_{H_i}}}\]
@@
 \begin{remark}\label{rem:id}
-	Let us consider  $(\{G\}, \alpha, \alpha)$ be a decoration of length $0$ with the same isomorphism as initial and final decoration.
+	Let  $(\{G\}, \alpha, \alpha)$ be a decoration of length $0$ with the same isomorphism as initial and final decoration.
 Then for every other derivations $(\der{D}, \beta, \omega)$ with source isomorphic to $G$, we have
@@
 	\[\phi_{G_{2,0}}\circ \alpha_2=\alpha'_2\circ (\omega'_1)^{-1} \circ \alpha'_1 \circ \alpha^{-1}_1\circ \omega_1 \]
-	We conclude that $\{\phi_X\}_{X\in \der{D}_2}$ wintesses the thesis.
+	We conclude that $\{\phi_X\}_{X\in \der{D}_2}$ witnesses the thesis.
 
@@
 \begin{proof} Take two abstraction equivalences $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ and $\{\varphi_X\}_{X\in \Deltamin(\der{D})}$ between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ and between $(\der{E}, \beta, \xi)$ and $(\der{E}', \beta', \xi')$, respectively.
-To fix the notation, suppose that goes from $G'$ to $H'$ and $(\der{E}', \beta', \xi')$ from $E'$ to $K'$.
+To fix the notation, suppose that $(\der{D}', \alpha', \omega')$ goes from $G'$ to $H'$ and $(\der{E}', \beta', \xi')$ from $E'$ to $K'$.
 We have three cases.
@@
 
-	Vice versa, if $(\{G\}, \alpha, \omega)$ be a derivation of length $0$, then 
+	Vice versa, if $(\{G\}, \alpha, \omega)$ is a derivation of length $0$, then 
 	\begin{align*}
@@
 	\begin{enumerate}
-		\item  for eevery derivation $\der{D}$ is a derivation from $G$ to $H$, then the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belongs to $\mathcal{M}$.
-		\item Let $\der{D}$ be the concatenation $\der{D}_1\cdot \der{D}_2$ of two derivations $\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^{n_1}$ between $G$ and $H$ and $\der{D}_2=\{\dder{D}_{2,j}\}_{j=0}^{n_2}$ between $H$ and $T$,  then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists too and there is a pushout square
+		\item  if $\der{D}$ is a derivation from $G$ to $H$, then the diagram $\Delta(\der{D})$ has a colimit $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ such that $\iota_H$ belongs to $\mathcal{M}$.
+		\item if $\der{D}$ is the concatenation $\der{D}_1\cdot \der{D}_2$ of two derivations $\der{D}_1=\{\dder{D}_{1,i}\}_{i=0}^{n_1}$ between $G$ and $H$ and $\der{D}_2=\{\dder{D}_{2,j}\}_{j=0}^{n_2}$ between $H$ and $T$,  then the colimiting cocone $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$ exists too and there is a pushout square
 		\[\xymatrix{H\ar[r]^-{\iota_{2, H}} \ar@{>->}[d]_-{\iota_{1, H}} & \tproi{D}{2} \ar[d]^{p_2}\\  \tproi{D}{1} \ar[r]_{p_1}& \tpro{D}}\]
@@
 	\item if  $(C, \{c_X\}_{X\in \Deltamin(\dder{D})})$ is colimiting for $F\circ I$, then there exists a colimiting cocone $(D, \{d_X\}_{X\in \Delta(\dder{D})})$ for $F$;
-	\item $(C, \{c_X\}_{X\in \Deltamin(\dder{D})})$ and $(D, \{d_X\}_{X\in \Delta(\dder{D})})$ are colimiting for, repsectively, $F\circ I$ and $F$, then the canonical arrow $\phi\colon C\to D$ induced by $(D, \{d_X\}_{X\in \Deltamin(\dder{D})})$ is an isomorphism.
+	\item $(C, \{c_X\}_{X\in \Deltamin(\dder{D})})$ and $(D, \{d_X\}_{X\in \Delta(\dder{D})})$ are colimiting for, respectively, $F\circ I$ and $F$, then the canonical arrow $\phi\colon C\to D$ induced by $(D, \{d_X\}_{X\in \Deltamin(\dder{D})})$ is an isomorphism.
 \end{enumerate}
@@
 
-			Let $(C, \{c_X\}_{X\in \Delta(\der{D})})$ be a cocone, since $\Delta(\der{D}')$ is a subdiagram of $\Delta(\der{D})$, we get another cocone $(C, \{c_X\}_{X\in \Delta(\der{D}')})$ which induces an arrow $c'\colon \lpro \der{D}' \rpro \to C$ such that
+			Let $(C, \{c_X\}_{X\in \Delta(\der{D})})$ be a cocone.
+Since $\Delta(\der{D}')$ is a subdiagram of $\Delta(\der{D})$, we get another cocone $(C, \{c_X\}_{X\in \Delta(\der{D}')})$ which induces an arrow $c'\colon \lpro \der{D}' \rpro \to C$ such that
 			\begin{align*}
@@
 \begin{lemma}\label{rem:dett}
-	Let $(\der{D}, \alpha, \omega)$ be the composite $(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)$ of two derivation of length $l_1$ and $l_2$. Suppose that:
+	Let $(\der{D}, \alpha, \omega)$ be the composite $(\der{D}_1, \alpha_1, \omega_1)\cdot (\der{D}_2, \alpha_2, \omega_2)$ of two derivations of length $l_1$ and $l_2$. Suppose that:
 	\[r(\der{D}_1)=\{\rho_{1,i}\}_{i=0}^{l_1-1} \quad r(\der{D}_2)=\{\rho_{2,i}\}_{i=0}^{l_2-1} \quad  r(\der{D})=\{\rho_{i}\}_{i=0}^{l_1+l_2-1}\]
@@
 \begin{remark}\label{rem:inversa}
-	Let  $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations and $\sigma\colon [0,n]\to [0,n]$ be a consistent permutation between them.
+	Let  $(\der{D},\alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations and $\sigma\colon [0,n]\to [0,n]$ a consistent permutation between them.
 Then its inverse $\sigma^{-1}$ is a consistent permutation between $(\der{D}', \alpha', \omega')$ and $(\der{D},\alpha, \omega)$.
@@
 \begin{proposition}\label{rem:abscons}
-	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations in an left-linear rewriting system $(\X, \R)$ of length $l$.
+	Let $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$ be two decorated derivations in a left-linear rewriting system $(\X, \R)$ of length $l$.
 Let also $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ be an abstraction equivalence between $\der{D}$ and $\der{D}'$.
@@
 
-	Now, denoting by $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$, $(\lpro \phi *\der{D} \rpro, \{\iota'_X\}_{X\in \Delta(\phi *\der{D})})$ and $(\lpro \der{D}*\psi \rpro, \{\hat{\iota}_X\}_{X\in \Delta(\der{D}*\psi)})$ the colimiting cocones, in this case we have that the, unique, mediating isomorphisms witnessing the consistency of $\id{[0, \lgh(\der{D})-1]}$ are given by the arrows $\Gamma^{\phi} \colon \tpro{D}\to \lpro \phi*\der{D} \rpro$ and $\Gamma_\psi\colon \tpro{D}\to \lpro \der{D}*\psi \rpro$  such that, for every $X\in \Deltamin(\der{D})$:
+	Now, denoting by $(\tpro{D}, \{\iota_X\}_{X\in \Delta(\der{D})})$, $(\lpro \phi *\der{D} \rpro, \{\iota'_X\}_{X\in \Delta(\phi *\der{D})})$ and $(\lpro \der{D}*\psi \rpro, \{\hat{\iota}_X\}_{X\in \Delta(\der{D}*\psi)})$ the colimiting cocones, in this case we have that the (unique) mediating isomorphisms witnessing the consistency of $\id{[0, \lgh(\der{D})-1]}$ are given by the arrows $\Gamma^{\phi} \colon \tpro{D}\to \lpro \phi*\der{D} \rpro$ and $\Gamma_\psi\colon \tpro{D}\to \lpro \der{D}*\psi \rpro$  such that, for every $X\in \Deltamin(\der{D})$:
 	\[\Gamma^\phi \circ \iota_X:=\begin{cases}
@@
 \begin{proposition}\label{rem:comp}  Let $(\der{D}, \alpha, \omega)$, $(\der{D}', \alpha', \omega')$ and $(\der{\hat{D}}, \hat{\alpha}, \hat{\omega})$ be three decorated derivations of length $l$.
-Let $\sigma$ be a consistent permutation between the first two and $\tau$ one between the second and the third, then $\tau \circ \sigma$ is a semi-consistent permutations between the first and the third.
+If $\sigma$ is a semi-consistent permutation between the first two and $\tau$ one between the second and the third, then $\tau \circ \sigma$ is a semi-consistent permutation between the first and the third.
 If, moreover, $\sigma$ and $\tau$ are consistent, then $\tau \circ \sigma$ is consistent too.
@@
 \begin{remark}
-	The relation $\equiv^p$ is an equivalence: \Cref{prop:abs} guarantees that it is well-defined, \Cref{rem:abscons} guarantees reflexivity, while symmetry and transitivity follow from, respectively \Cref{rem:inversa} and \Cref{rem:comp}.
+	The relation $\equiv^p$ is an equivalence: \Cref{prop:abs} guarantees that it is well-defined, \Cref{rem:abscons} guarantees reflexivity, while symmetry and transitivity follow from, respectively, 
+	\Cref{rem:inversa} and \Cref{rem:comp}.
 \end{remark}
@@
 We want now to show that permutation equivalence is a congruence with respect to composition in $\dpi$.
-This, in turn, will allow us to build  a category in which arrows are are exactly the equivalence classes of permutation equivalent abstract decorated decorations.
+This, in turn, will allow us to build  a category in which arrows are exactly the equivalence classes of permutation equivalent abstract decorated decorations.
 
@@
 	\begin{itemize}
-		\item the composition 	$[\der{D}_2, \alpha_2, \omega_2]_p \circ [\der{D}_1, \alpha_1, \omega_1]_p$ coincides with the permuation equivalence class of $	[\der{D}_2, \alpha_2, \omega_2]_a \circ [\der{D}_1, \alpha_1, \omega_1]_a$;
+		\item the composition 	$[\der{D}_2, \alpha_2, \omega_2]_p \circ [\der{D}_1, \alpha_1, \omega_1]_p$ coincides with the permutation equivalence class of $	[\der{D}_2, \alpha_2, \omega_2]_a \circ [\der{D}_1, \alpha_1, \omega_1]_a$;
 		\item by \Cref{rem:ugu}, $[\{G, \alpha, \alpha\}]_p=[\{G, \alpha, \alpha\}]_a$, guaranteeing that it is the neutral element with respect of the composition we have defined above.
@@
 
-	\Cref{prop:pbpoad} we can now deduce the existence of the dotted $t\colon L_{j-1}\to K_{j-1}$, from which the thesis  follows. \qedhere
+	From \Cref{prop:pbpoad} we can now deduce the existence of the dotted $t\colon L_{j-1}\to K_{j-1}$, from which the thesis  follows. \qedhere
 	\end{enumerate}

### 2025-03-21 full_version/leftlinear.tex
minori

--- 2025-03-07 full_version/leftlinear.tex
@@
 	$\der{F}=\{\dder{F}_i\}_{i=0}^1$ are pre-switches of $\dder{D}_0$ and
-	$\dder{D}_1$. Then there is a unique abstraction equivalence $\{\phi_X\}_{X\in \Deltamin(\der{E})}$ between $\der{E}$ and $\der{F}$, whose first component is $\id{G_0}$. Moreover, 
+	$\dder{D}_1$ along the same independence pair $(i_0, i_1)$.
+Then there is a unique abstraction equivalence $\{\phi_X\}_{X\in \Deltamin(\der{E})}$ between $\der{E}$ and $\der{F}$, whose first component is $\id{G_0}$.
+Moreover,
 	\[\phi_{D_{\der{E}, 0}}\circ j_1=a_1 \qquad \phi_{D_{\der{E}, 1}}\circ j_0=a_0\]
@@
 
-	Now, by \Cref{prop:unique} we get isomorphisms $\phi_0\colon D_{\der{E},0}\to D_{\der{F},0}$ and $\psi_1 \colon G_{\der{E},1}\to G_{\der{F},1}$ such that the diagram below commutes.
+	Now, by \Cref{prop:unique} we know that there are two unique isomorphisms $\phi_0\colon D_{\der{E},0}\to D_{\der{F},0}$ and $\psi_1 \colon G_{\der{E},1}\to G_{\der{F},1}$ such that the diagram below commutes.
 	\[\xymatrix{G_{0} & \ar@{>->}[l]_{f_{\der{F},0}} D_{\der{F},0} \ar[r]^{g_{\der{F},0}}& G_{\der{F},1} \\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar[l]_{l_1} \ar[r]^{r_1} & R_{1}  \ar[d]_{h_{\der{E},0}}  \ar[u]^{h_{\der{F},0}}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} & \ar@{>->}[l]^{f_{\der{E},0}} D_{\der{E},0} \ar@/^.5cm/[uu]^(.33){\phi_{0}}|\hole \ar[r]_{g_{\der{E},0}}& G_{\der{E},1} \ar@/_.5cm/[uu]_{\psi_1}}\]
@@
 	Moreover, we have already shown that $\psi_1\circ m_{\der{E},1}=m_{\der{F},1}$.
-Thus, by \Cref{prop:unique} there are the dotted isomorphisms $\phi_1\colon D_{\der{E},1}\to D_{\der{F},1}$ and $\psi_2\colon G_2\to G_2$ in the diagram below.
+Thus, again by \Cref{prop:unique} there are the dotted isomorphisms $\phi_1\colon D_{\der{E},1}\to D_{\der{F},1}$ and $\psi_2\colon G_2\to G_2$ in the diagram below and such arrows are unique.
 	\[\xymatrix{G_{\der{F},1} & \ar@{>->}[l]_{f_{\der{F},1}} D_{\der{F},1} \ar[r]^{g_{\der{F},1}}& G_2 \\L_0 \ar[d]^{m_{\der{E},1}} \ar[u]_{m_{\der{F},1}}& K_{0} \ar[d]^{k_{\der{E},1}} \ar[u]_{k_{\der{F},1}}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_{0}  \ar[d]_{g_1\circ i_0}  \ar[u]^{g_1\circ i_0}\\ \ar@/^.5cm/[uu]^{\psi_1} G_{\der{E},1} & \ar@{>->}[l]^{f_{\der{E},1}} D_{\der{E},1} \ar@{.>}@/^.5cm/[uu]^(.33){\phi_{1}}|\hole \ar[r]_{g_{\der{E},1}}& G_2 \ar@{.>}@/_.5cm/[uu]_{\psi_2}}\]
@@
 \begin{example}\label{ex:abs2}
-Let $\der{D}$ be the derivation of \Cref{ex:abs} and consider the pre-switch $\der{F}$. Then we have the following diagram
-
-	\[\xymatrix@C=22pt@R=22pt{&&1 \ar@{>->}@/_.9cm/[ddrr]_(.2){\delta^3_0}|(.72)\hole
+Let $\der{D}$ be the derivation of \Cref{ex:abs} and consider the pre-switch $\der{F}$. Then we can build the diagram belo
+	\[\xymatrix@C=20pt@R=20pt{&&1 \ar@{>->}@/_.9cm/[ddrr]_(.2){\delta^3_0}|(.72)\hole
 	\ar@{>->}[dr]^{\delta^3_0}&& 1\ar@{>->}@/^.9cm/[ddll]^(.2){\delta^3_0}
@@
 
-\begin{definition}(Switch) 	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear rewriting system. 
+\begin{definition}[Switch] 	Let $(\X, \R)$ be a left-linear rewriting system, with $\X$ an $\mathcal{M}$-adhesive category.
 	Let also $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation made
@@
 	$\dder{D}_1$ with independence pair $(i_0, i_1)$, as in the diagram below, where the cone with vertex $P$ is a pullback and $u_0\colon K_0\to P$ and $u_1\colon K_1\to P$ are the arrows built in \Cref{prop:tec}.
-	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0 \ar @/^.35cm/[ddrr]^(.3){u_0}
+	\[\xymatrix@R=15pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0 \ar @/^.35cm/[ddrr]_(.2){u_0}
 		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
@@
 		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{>}@/_.25cm/[dlll]^(.4){i_1}|(.68)\hole 
-		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar @/_.35cm/[ddll]_(.3){u_1}
+		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar @/_.35cm/[ddll]^(.2){u_1}
 		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
@@
 	\[
-	\xymatrix@R=20pt@C=20pt{
+	\xymatrix@R=18pt@C=20pt{
 		{L_1} \ar[d]_{m_0'}
@@
 	We say that $\der{E}$ is a \emph{switch} for $\der{D}$ along $(i_0, i_1)$ if there is an arrow $z_1\colon P\to D'_1$ fitting in the diagram below, where $z_0\colon P\to D'_0$ is the arrow constructed in \Cref{lem:cose}.
-	\[\xymatrix{D'_0  \ar[d]_{g'_0}& P \ar[r]^{p_1} \ar[l]_{z_0} \ar@{.>}[d]^{z_1} & D_1 \ar[d]^{g_1}\\ G'_1 & D'_1 \ar[r]_{g'_1} \ar@{>->}[l]_{f'_1} & G_2}\]
+	\[\xymatrix@R=18pt{D'_0  \ar[d]_{g'_0}& P \ar[r]^{p_1} \ar[l]_{z_0} \ar@{.>}[d]^{z_1} & D_1 \ar[d]^{g_1}\\ G'_1 & D'_1 \ar[r]_{g'_1} \ar@{>->}[l]^{f'_1} & G_2}\]
 
 	If a switch of $\dder{D}_0$ and $\dder{D}_1$ exists we say that they are \emph{switchable}.
-If $(\der{D}, \alpha, \omega)$ is a decorated derivation of length $2$, and $(i_0, i_1)$ an independence pair between $\dder{D}_0$ and $\dder{D}_1$.
-A \emph{decorated switch} of $(\der{D}, \alpha, \omega)$ along $(i_0, i_1)$ is $(\der{E}, \alpha, \omega)$, where $\der{E}$ is a switch for $\der{D}$ along $(i_0, i_1)$.
+If $(\der{D}, \alpha, \omega)$ is a decorated derivation of length $2$, and $(i_0, i_1)$ an independence pair between $\dder{D}_0$ and $\dder{D}_1$, a \emph{decorated switch} of $(\der{D}, \alpha, \omega)$ along $(i_0, i_1)$ is $(\der{E}, \alpha, \omega)$, where $\der{E}$ is a switch for $\der{D}$ along $(i_0, i_1)$.
 \end{definition}
 
-\begin{remark} 
-vari quadrati
+\begin{remark}\label{rem:quadrati}
+Let $\der{D}$ be a derivation made by two sequentially independence direct derivations with independence pair $(i_0, i_1)$.
+Suppose that $\der{E}$ is a pre-switch for $\der{D}$ along $(i_0, i_1)$.
+Then we have the solid part of the diagram below.
+If, moreover $\der{E}$ is a switch, then we can complete it with the dotted arrow $z_1\colon P\to D'_1$.
+		\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
+		\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
+		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
+		\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){u_0}\ar[ur]^{r_0}&& G_1 &&
+		K_1
+		\ar@/^.6cm/[ddll]|(.36)\hole_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
+		\ar[dr]^{r_1}\\L_0
+		\ar@/_.6cm/[ddrr]_(.2){i'_1}|(.31)\hole|(.81)\hole
+		\ar[dr]^(.4){m_0}|(.61)\hole && D_0
+		\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1
+		\ar[dr]|(.4)\hole^(.65){g_1}
+		\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_0}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
+		&&P\ar@{.>}[dr]_{z_1}	\ar@{>}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
 \end{remark}
@@
 \begin{lemma}
-	equivalenze
-
+Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation of length $2$ and $(i_0, i_1)$ an independence pair between $\dder{D}_0$ and $\dder{D}_1$.
+Given a pre-switch $\der{E}=\{\dder{E}_{i}\}_{i=0}^1$ for $\der{D}$ along $(i_0, i_1)$, the following are equivalent:
 	\begin{enumerate}
-		\item 
-		\item 
+		\item $\der{E}$ is a switch;
+		\item if $(P, \{p_i\}_{i=0}^1)$ is a pullback for $f_{\der{D},1}$ along $g_{\der{D},0}$, then $\iota_{\der{E}, G_2} \circ g_1\circ p_1=\iota_{\der{E}, G'_1}\circ g'_0\circ z_0$.
 	\end{enumerate}
 \end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-We end this section showing that, if a switch exists, then any pre-switch can be turned into one.
-
-\begin{proposition}
-	contenuto...
+\begin{proof}$(1 \Rightarrow 2)$. If $\der{E}$ is a switch then we have
+	\begin{align*}
+		\iota_{\der{E}, G_2} \circ g_1\circ p_1&=\iota_{\der{E}, G_2} \circ g'_1\circ z_1\\&=\iota_{\der{E}, D'_1}\circ z_1\\&=\iota_{\der{E}, G'_1}\circ f'_1\circ z_1\\&=\iota_{\der{E}, G'_1}\circ g'_0\circ z_0
+	\end{align*}
+
+	\smallskip \noindent $(2\Rightarrow 1)$. By hypothesis the solid part of the diagram below commutes.
+	\[\xymatrix@C=30pt{P \ar[r]^{z_0} \ar@{.>}[dr]^{z_1}\ar[d]_{p_1} & D'_0 \ar[r]^{g'_0} & G'_1 \ar@{>->}[dr]^{\iota'_{1, G'_1}}\\ D_1 \ar[dr]_{g'_1}& D'_1 \ar[d]^{g'_1}\ar@{>->}[r]^{f'_1} &G'_1 \ar@{>->}[r]^{\iota'_{1, G'_1}} &\lpro \dder{E}_0 \rpro 	\ar@{>->}[d]^{p_1} \\ & G'_1 	\ar[rr]_{\iota_{\der{E}, G_2}}&& \tpro{E} }\]
+
+	By \Cref{rem:zero1} the inner square is a pullback, proving that the dotted arrow $z_1\colon P\to D'_1$ exists.
+Since, by \Cref{lem:colim} $\iota'_{1, G'_1}$ is in $\mathcal{M}$, we conclude that $f'\circ z_1=g'\circ z_0$ as wanted.
+\end{proof}
+
+We end this section showing that, if a switch exists, then any pre-switch can be turned into one composing it with an isomorphism.
+
+\begin{proposition}\label{prop:pretosw} 	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation and suppose
+	that both $\der{E}=\{\dder{E}_i\}_{i=0}^1$ and
+	$\der{F}=\{\dder{F}_i\}_{i=0}^1$ are pre-switches of $\dder{D}_0$ and
+	$\dder{D}_1$ along the same independence pair $(i_0, i_1)$.
+Let $\{\phi_X\}_{X\in \Deltamin(\der{E})}$ be the abstraction equivalence built in \Cref{thm:switch_uni}.
+If $\der{F}$ is a switch then also $\der{E}*\phi_{G_2}$ is one.
 \end{proposition}

### 2025-03-21 full_version/permutations.tex
minori

@@
 	\[\xymatrix{L \ar[d]_{m}& K \ar[d]^{k}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h} & L \ar[d]_{m}& K \ar[d]^{k'}\ar@{>->}[l]_{l} \ar[r]^{r} & R \ar[d]^{h'}\\G & \ar@{>->}[l]^{f} D \ar[r]_{g}& H & G & \ar@{>->}[l]^{f'} D' \ar[r]_{g'}& H'}\]
-	Then there exist isomorphisms $t\colon D\to D'$ and $s\colon H\to H'$ as in the following diagram.
+	Then there exist two unique isomorphisms $t\colon D\to D'$, $s\colon H\to H'$ as in the diagram below.
 	\[\xymatrix@C=40pt{&&D' \ar[r]^{g'} \ar@{>->}@/_.45cm/[dll]_{f'}&H'\\G & L \ar[l]_{m} & K \ar[u]_{k'} \ar[d]^{k}\ar[r]^{r} \ar@{>->}[l]_{l} &R\ar[u]^{h'} \ar[d]_{h}\\&&D\ar@{>->}@/^.45cm/[ull]^{f}\ar@/^.4cm/@{.>}[uu]^(.4){t}|\hole \ar[r]_{g}&H\ar@/_.4cm/@{.>}[uu]_{s}}\]
@@
 	By construction, the pairs $(k, f)$ and $(k', f')$ are pushout complements of $l$ and $n$.
-Thus, the existence of the isomorphism $t\colon D\to D'$ follows from the second point of \Cref{lem:radj}.
+Thus, existence and uniqueness of the isomorphism $t\colon D\to D'$ follows from the second point of \Cref{lem:radj}.
 Now, computing we have
@@
 	\end{align*}
-	Hence, we have the wanted $s\colon H\to H'$. To see that $s$ is an isomorphism, consider the diagram 
+	Hence, we have a unique arrow $s\colon H\to H'$. To see that $s$ is an isomorphism, consider the diagram 
 	\[\xymatrix{K  \ar@/^.4cm/[rr]^{k'}\ar[d]_{r} \ar[r]_{k}& \ar[r]_{t} D \ar[d]^{g}& D' \ar[d]^{g'}\\ R \ar@/_.4cm/[rr]_{h'} \ar[r]^{h}& H \ar[r]^{s}& H'}\]

### 2025-04-02 full_version/leftlinear.tex
cose

@@
 Let $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ be an abstraction equivalence between $\der{D}=\{\dder{D}_i\}_{i=0}^1$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^1$.
-If there is an independence pair between $(i_0, i_1)$ between $\dder{D}_0$ and $\dder{D}_1$, then $(\phi_{D_0}\circ i_1, \phi_{D_1}\circ i_0)$ is an independence pair between $\dder{D}'_0$ and $\dder{D}'_1$.
+If there is an independence pair between $(i_0, i_1)$ between $\dder{D}_0$ and $\dder{D}_1$, then $(\phi_{D_1}\circ i_0, \phi_{D_0}\circ i_1)$ is an independence pair between $\dder{D}'_0$ and $\dder{D}'_1$.
 Indeed we have
@@
 	$\dder{E}_0$ and $\dder{E}_1$ and 
-	\begin{center}   
-		$m_0=f_0' \circ i_1'$
-		\qquad $h_1=g_1' \circ i_0'$
-		\qquad $m_0'= f_0 \circ i_1$
-		\qquad $h_1'= g_{1}\circ i_0$.
-	\end{center}
+\[
+	m_0=f_0' \circ i_1' \qquad 
+	h_1=g_1' \circ i_0' 
+		\qquad m_0'= f_0 \circ i_1
+		\qquad h_1'= g_{1}\circ i_0\]
 
@@
 
-A first property of pre-switches is that they are unique up to abstraction equivalence.
+We start by examining how pre-switches interact with abstraction equivalence. A first property that we can establish in that direction is uniqueness of pre-switches up to abstraction equivalence.
 
@@
 \end{example}
+
+Another useful facts that we can establish is that being a pre-switch is invariant under abstraction equivalence, as made precise by the following lemma.
+
+\begin{lemma}\label{lem:abs}
+	Let $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be the following derivation:
+
+	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
+		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
+		\ar@{>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
+		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{>}@/_.25cm/[dlll]^(.4){i_1}
+		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
+		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
+		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
+		\ar[rr]_{g_1}&& G_2}
+	\]
+	and suppose that the derivation $\der{E}$ below is a pre-switch for $\der{D}$ along $(i_0,i_1)$.
+	\[
+	\xymatrix@R=20pt@C=20pt{
+		{L_1} \ar[d]_{m_0'}
+		&&  {K_1} \ar@{>->}[ll]_{l_1} \ar[r]^{r_1} \ar[d]_{k_0'}
+		&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{>}_(.4){i_0'}|(.32)\hole[drrr]
+		& & 
+		{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{>}^(.4){i_1'}[dlll] 
+		&  {K_0} \ar@{>->}[l]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
+		& & {R_0} \ar[d]^{h_1'} \\		
+		{G_0}
+		& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rr]_{g_0'}
+		& &  {G'_1} 
+		& &  {D_1'} \ar@{>->}[ll]^{f_1'} \ar[rr]_{g_1'}
+		& & {G_2}  }
+	\]
+
+	Then the following hold true:
+	\begin{enumerate}
+		\item if $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ is an abstraction equivalence between $\der{D}$ and another derivation $\der{F}=\{\dder{F}_i\}_{i=0}^1$, then $\phi^{-1}_{G_0}*\der{E}*\phi_{G_2}$ is a pre-switch for $\der{F}$ along $(\phi_{D_1}\circ i_0, \phi_{D_0}\circ i_1 )$;
+		\item if $\{\psi_X\}_{X\in \Deltamin(\der{E})}$ is an abstraction equivalence between $\der{E}$ and $\der{G}=\{\dder{G}_{i}\}_{i=0}^1$, then $\psi_{G_0}*\der{G}*\psi^{-1}_{G_2}$ is a pre-switch for $\der{D}$ along $(i_0, i_1)$.
+	\end{enumerate}
+	\begin{remark}Recall that, by \Cref{rem:seqabs}, $(\phi_{D_1}\circ i_0, \phi_{D_0}\circ i_1 )$ is an independence pair between $\dder{F}_0$ and $\dder{F}_1$.
+	\end{remark}
+\end{lemma}
+\begin{proof}\begin{enumerate}
+		\item To prove this, it is enough to compute:
+		\[\begin{split}
+			m_{\der{F},0}=&\phi_{G_0}\circ m_0\\=&\phi_{G_0}\circ f'_0\circ i'_1\\\phi_{G_0}\circ	m'_0=&\phi_{G_0}\circ f_0\circ i_1\\=&f_{\der{F},0}\circ \phi_{D_{0}}\circ i_1
+		\end{split} \quad \begin{split}
+	h_{\der{F},1}=&\phi_{G_2}\circ h_1\\=&\phi_{G_2}\circ g_1' \circ i_0' \\	\phi_{G_2}\circ h'_1=&\phi_{G_2}\circ g_1\circ i_0\\=&g_{\der{F}, 1}\circ \phi_{D_1}\circ i_0\end{split} 
+	\]
+
+		\item
+
+		And we can conclude. \qedhere 
+	\end{enumerate}
+\end{proof}
 
@@
 	$\dder{D}_1$ with independence pair $(i_0, i_1)$, as in the diagram below, where the cone with vertex $P$ is a pullback and $u_0\colon K_0\to P$ and $u_1\colon K_1\to P$ are the arrows built in \Cref{prop:tec}.
-	\[\xymatrix@R=15pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0 \ar @/^.35cm/[ddrr]_(.2){u_0}
+	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0 \ar @/^.35cm/[ddrr]_(.2){u_0}
 		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
@@
 	\[
-	\xymatrix@R=18pt@C=20pt{
+	\xymatrix@R=20pt@C=20pt{
 		{L_1} \ar[d]_{m_0'}
@@
 \begin{proof}
-	contenuto...
+Suppose that $\der{D}$ is given by the following derivation.
+
+	By \Cref{thm:switch_uni} we have a diagram as the one below.
+	\[\xymatrix@C=22pt{G_{0} && \ar@{>->}[ll]_{f_{\der{F},0}} D_{\der{F},0} \ar[rr]^{g_{\der{F},0}}&& G_{\der{F},1} && \ar@{>->}[ll]_{f_{\der{F},1}} D_{\der{F},1} \ar[rr]^{g_{\der{F},1}}&& G_{2}\\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}&& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_{1} \ar@/^.35cm/[drrr]|(.315)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{h_{\der{E},0}} \ar@/_.35cm/[urrr]|(.315)\hole^(.4){a_0} \ar[ur]|(.3)\hole^{h_{\der{F},0}}& &L_{0} \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{m_{\der{E},1}} \ar@/^.35cm/[ulll]_(.4){a_1} \ar@/_.3cm/[ul]|(.252)\hole_(.4){m_{\der{F},1}}& K_{0} \ar[d]_{k_{\der{E},1}} \ar[u]^{k_{\der{F},1}}\ar@{>->}[l]_{l_{0}} \ar[rr]^{r_0} && R_{0} \ar[d]_{g_1\circ i_0} \ar[u]^{g_1\circ i_0}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} && \ar[ll]^{f_{\der{E},0}} D_{\der{E},0} \ar@{>}@/^.5cm/[uu]^(.33){\phi_{D_{\der{E},0}}}|\hole \ar[rr]_{g_{\der{E},0}}&& G_{\der{E},1} \ar@{>}[uu]_(.76){\phi_{G_{\der{E}, 1}}}|(.45)\hole |(.55)\hole&& \ar@{>->}[ll]^{f_{\der{E},1}} D_{\der{E},1} \ar@{>}@/_.5cm/[uu]_(.33){\phi_{D_{\der{E},1}}}|\hole\ar[rr]_{g_{\der{E},1}}&& G_{2}\ar@{>}@/_.5cm/[uu]_{\phi_{G_2}}}\]
+
+	Moreover, by definition $\der{E}*\phi_{G_2}$
+
 	\end{proof}
@@
 		\end{split} \qquad \begin{split}
-		g'_1\circ z_1=g'_1\circ t_1\circ v\\&=g'_1\circ \phi_{Q_1}\circ q_1\\&=\phi_{G_2}\circ b_1 \circ q_1\\&=\phi_{G_2}\circ g_1\circ p_1\\&=f_0\circ p_0
+		g'_1\circ z_1&=g'_1\circ t_1\circ v\\&=g'_1\circ \phi_{Q_1}\circ q_1\\&=\phi_{G_2}\circ b_1 \circ q_1\\&=\phi_{G_2}\circ g_1\circ p_1\\&=f_0\circ p_0
 		\end{split} \]

### 2025-04-17 full_version/leftlinear.tex
switch

@@
 		\node[font=\scriptsize, below] at (D3.south) {$D_2'$};      
-		\node[font=\scriptsize, below] at (G4.south) {$G_3$};
+		\node[font=\scriptsize, below] at (G4.south) {$G_2$};
 
@@
 	Let $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be the following derivation:
-
 	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
@@
 		\[\begin{split}
-			m_{\der{F},0}=&\phi_{G_0}\circ m_0\\=&\phi_{G_0}\circ f'_0\circ i'_1\\\phi_{G_0}\circ	m'_0=&\phi_{G_0}\circ f_0\circ i_1\\=&f_{\der{F},0}\circ \phi_{D_{0}}\circ i_1
-		\end{split} \quad \begin{split}
-	h_{\der{F},1}=&\phi_{G_2}\circ h_1\\=&\phi_{G_2}\circ g_1' \circ i_0' \\	\phi_{G_2}\circ h'_1=&\phi_{G_2}\circ g_1\circ i_0\\=&g_{\der{F}, 1}\circ \phi_{D_1}\circ i_0\end{split} 
-	\]
-
-		\item
-
-		And we can conclude. \qedhere 
+			m_{\der{F},0}=&\phi_{G_0}\circ m_0\\=&\phi_{G_0}\circ f'_0\circ i'_1
+		\end{split} \quad \begin{split}\phi_{G_0}\circ	m'_0=&\phi_{G_0}\circ f_0\circ i_1\\=&f_{\der{F},0}\circ \phi_{D_{0}}\circ i_1
+	 \end{split} 
+	\]
+	\[\begin{split}
+	h_{\der{F},1}=&\phi_{G_2}\circ h_1\\=&\phi_{G_2}\circ g_1' \circ i_0'
+	\end{split} \qquad \begin{split}
+		\phi_{G_2}\circ h'_1=&\phi_{G_2}\circ g_1\circ i_0\\=&g_{\der{F}, 1}\circ \phi_{D_1}\circ i_0
+	\end{split}\]
+
+		\item By \Cref{rem:seqabs} we know that $(\psi_{D'_1}\circ i'_0,\psi_{D'_0}\circ i'_1)$ is an independence pair between $\dder{G}_0$ and $\dder{G}_1$.
+By \Cref{rem:absequi} and again by \Cref{rem:seqabs} we conclude that  $(\psi_{D'_1}\circ i'_0,\psi_{D'_0}\circ i'_1)$ witnesses the sequential independence of the two steps making $\psi_{G_0}*\der{G}*\psi^{-1}_{G_2}$.
+Moreover:
+
+		\[\begin{split}
+			m_{0}=&f'_0\circ i'_1\\=&\psi^{-1}_{G_0}\circ f_{\der{G},0}\circ \psi_{D'_0}\circ i'_1
+		\end{split} \qquad \begin{split}\psi^{-1}_{G_0}\circ	m_{\der{G},0}=&m'_0\\=&f_0\circ i_1 \end{split} \]
+		\[\begin{split}h_1=&g'_1\circ i'_0\\=&\psi^{-1}_{G_2}\circ g_{\der{G},1} \circ\psi_{D'_0}\circ  i_0'
+		\end{split} \qquad \begin{split}
+			\psi^{-1}_{G_2}\circ h_{\der{G},1}=&h'_1\\=&g_1\circ i_0\end{split} \]
+		yielding the thesis. \qedhere 
 	\end{enumerate}
@@
 	system whose set of rules contains the following 
-	\[\xymatrix{a & a \ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & 0 & a & a
-		\ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & b }\]
+	\[\xymatrix{a & a \ar[r]^{(a,0)} \ar@{>->}[l]_{\id{a}} & 0 & a & a
+		\ar[r]^{(a,b)} \ar@{>->}[l]_{\id{a}} & b }\]
 	We can then consider the  following derivation
@@
 	$\dder{D}_1$ with independence pair $(i_0, i_1)$, as in the diagram below, where the cone with vertex $P$ is a pullback and $u_0\colon K_0\to P$ and $u_1\colon K_1\to P$ are the arrows built in \Cref{prop:tec}.
-	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0 \ar @/^.35cm/[ddrr]_(.2){u_0}
+	\[\xymatrix@R=15pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0 \ar @/^.35cm/[ddrr]_(.2){u_0}
 		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
@@
 	\[
-	\xymatrix@R=20pt@C=20pt{
+	\xymatrix@R=15pt@C=20pt{
 		{L_1} \ar[d]_{m_0'}
@@
 
-\begin{lemma}
+\begin{remark}\label{rem:un}
+	Notice that, since $f'_1$ belongs to $\mathcal{M}$, there is at most one arrow $z_1\colon P\to D'_1$ such that $f'{1}\circ z_1=g'_0\circ z_0$.
+\end{remark}
+
+We are now going to characterize switches along a given independence pair by means of a property of its colimit.
+
+\begin{lemma}\label{lem:equi}
 Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation of length $2$ and $(i_0, i_1)$ an independence pair between $\dder{D}_0$ and $\dder{D}_1$.
@@
 		\item $\der{E}$ is a switch;
-		\item if $(P, \{p_i\}_{i=0}^1)$ is a pullback for $f_{\der{D},1}$ along $g_{\der{D},0}$, then $\iota_{\der{E}, G_2} \circ g_1\circ p_1=\iota_{\der{E}, G'_1}\circ g'_0\circ z_0$.
+		\item if $(P, \{p_i\}_{i=0}^1)$ is a pullback for $f_{\der{D},1}$ along $g_{\der{D},0}$, then \[\iota_{\der{E}, G_2} \circ g_1\circ p_1=\iota_{\der{E}, G'_1}\circ g'_0\circ z_0\]
 	\end{enumerate}
@@
 \end{proof}
+\iffalse 
+We turn now to simmetry of the switchability relation. Surely one desires an analog of \Cref{rem:switch} even for switches: this is assured by the following proposition.
+
+\begin{proposition}\label{prop:pb}
+	Let $\der{D}:=\{\dder{D}_{i}\}_{i=0}^1$ be the derivation below, with $(i_0, i_1)$ an independence pair between $\dder{D}_0$  and $\dder{D}_1$.
+	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
+		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
+		\ar@{>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
+		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{>}@/_.25cm/[dlll]^(.4){i_1}
+		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
+		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
+		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
+		\ar[rr]_{g_1}&& G_2}
+	\]
+
+	If $\der{E}:=\{\dder{E}_{i}\}_{i=0}^1$ is a switch for $\dder{D}$ along $(i_0, i_1)$, then the square below is a pullback.
+	\[\xymatrix{P  \ar[r]^-{z_1} \ar[d]_{z_0}& D_{\der{E}, 1} \ar@{>->}[d]^{f_{\der{E},1}} \\ D_{\der{E},0} \ar[r]_{g_{\der{E},0}}& G_{\der{E},1}}\]
+
+	In particular, the arrow $z_0\colon P\to D_{\der{E},0}$ belongs to $\mathcal{M}$.
+\end{proposition}
+\begin{proof}
+	Take two arrows $t_0\colon T\to D_{\der{E}_1}$ and $t_1\colon T\to D_{\der{E},0}$ such that \[f_{\der{E},1}\circ t_1=g_{\der{E},0}\circ t_0\]
+
+	Thus we have
+	\begin{align*}
+		\iota_{\der{E}, G_0}\circ f_{\der{E},0}\circ t_0=&\iota_{\der{E}, D_{\der{E},0}}\circ t_0\\=&\iota_{\der{E}, G_1}\circ g_{\der{E},0}\circ t_0\\=&\iota_{\der{E}, G_1}\circ f_{\der{E},1}\circ t_1\\&= \iota_{\der{E}, D_{\der{E},1}}\circ t_1\\&=\iota_{\der{E}, G_2}\circ g_{\der{E},1} \circ t_1
+	\end{align*}
+
+	By \Cref{cor:ele} we know that there exists a unique $t\colon T\to D_{}$
+\end{proof}
+
+\begin{corollary}
+	contenuto...
+\end{corollary}
+
+\fi
 
@@
 \begin{proof}
-Suppose that $\der{D}$ is given by the following derivation.
-
-	By \Cref{thm:switch_uni} we have a diagram as the one below.
-	\[\xymatrix@C=22pt{G_{0} && \ar@{>->}[ll]_{f_{\der{F},0}} D_{\der{F},0} \ar[rr]^{g_{\der{F},0}}&& G_{\der{F},1} && \ar@{>->}[ll]_{f_{\der{F},1}} D_{\der{F},1} \ar[rr]^{g_{\der{F},1}}&& G_{2}\\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}&& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_{1} \ar@/^.35cm/[drrr]|(.315)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{h_{\der{E},0}} \ar@/_.35cm/[urrr]|(.315)\hole^(.4){a_0} \ar[ur]|(.3)\hole^{h_{\der{F},0}}& &L_{0} \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{m_{\der{E},1}} \ar@/^.35cm/[ulll]_(.4){a_1} \ar@/_.3cm/[ul]|(.252)\hole_(.4){m_{\der{F},1}}& K_{0} \ar[d]_{k_{\der{E},1}} \ar[u]^{k_{\der{F},1}}\ar@{>->}[l]_{l_{0}} \ar[rr]^{r_0} && R_{0} \ar[d]_{g_1\circ i_0} \ar[u]^{g_1\circ i_0}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} && \ar[ll]^{f_{\der{E},0}} D_{\der{E},0} \ar@{>}@/^.5cm/[uu]^(.33){\phi_{D_{\der{E},0}}}|\hole \ar[rr]_{g_{\der{E},0}}&& G_{\der{E},1} \ar@{>}[uu]_(.76){\phi_{G_{\der{E}, 1}}}|(.45)\hole |(.55)\hole&& \ar@{>->}[ll]^{f_{\der{E},1}} D_{\der{E},1} \ar@{>}@/_.5cm/[uu]_(.33){\phi_{D_{\der{E},1}}}|\hole\ar[rr]_{g_{\der{E},1}}&& G_{2}\ar@{>}@/_.5cm/[uu]_{\phi_{G_2}}}\]
-
-	Moreover, by definition $\der{E}*\phi_{G_2}$
-
+	By \Cref{rem:absequi} and \Cref{lem:abs} we know that $\der{E}*\phi_{G_2}$ is a pre-switch for $\der{D}$ along $(i_0, i_1)$.
+Let $(\tpro{E}, \{\iota_{\der{E}, X}\}_{X\in \Deltamin(\der{E})})$, $(\tpro{F}, \{\iota_{\der{F}, X}\}_{X\in \Deltamin(\der{F})})$ and $(\lpro \der{E}*\phi_{G_2}\rpro , \{\iota'_{X}\}_{X\in \Deltamin(\der{E}*\phi_{G_2})})$ be colimiting cocones.
+By \Cref{rem:absequi,rem:abscol} we have isomorphisms $\Psi \colon \tpro{E}\to \lpro \der{E}*\phi_{G_2}\rpro $ and $\Phi\colon \tpro{E}\to \tpro{F}$ such that
+	\[\begin{split}
+		\Psi\circ \iota_{\der{E}, G_0}&=\iota'_{G_0}\\\Phi\circ \iota_{\der{E}, G_0}&=\iota_{\der{F}, G_0}
+	\end{split} \quad \begin{split}
+	\Psi \circ \iota_{\der{E}, G_{\der{E}, 1}}&=\iota'_{G_1}\\
+	\Phi \circ \iota_{\der{E}, G_{\der{E}, 1}}&=\iota_{\der{F}, G_{\der{F}, 1}}\circ \phi_{G_{\der{E}, 1}}
+	\end{split} \quad \begin{split}
+	\Psi \circ \iota_{\der{E}, G_2}&=\iota'_{G_2}\circ \phi_{G_2}\\
+	\Phi \circ \iota_{\der{E}, G_2}&=\iota_{\der{F}, G_2}\circ \phi_{G_2}
+	\end{split}\]
+
+ 	Let $(P, \{p_0, p_1\})$ be the pullback of $g_{0}$ along $f_1$, so that by \Cref{lem:cose} 	and the definition of switch we have the diagrams below.
+
+ 		\[\xymatrix{P\ar[r]^{z_0} \ar@{>->}[d]_{p_0}& D'_{0} \ar@{>->}[d]^{f'_{0}} & P \ar@{>->}[d]_{p_0}\ar[r]^-{z_{\der{F},0}} & D_{\der{F}, 0}\ar@{>->}[d]^{f_{\der{F},0}} & D_{\der{F},0}  \ar[d]_{g_{\der{F},0}}& P \ar[r]^{p_1} \ar[l]_-{z_{\der{F},0}} \ar[d]^{z_{\der{F},1}} & D_1 \ar[d]^{g_1}\\ D_0\ar@{>->}[r]_{f_0} & G_0 & D_0\ar@{>->}[r]_{f_0} & G_0 & G_{\der{F},2} & D_{\der{F},1} \ar[r]_-{g_{\der{F},1}} \ar@{>->}[l]^-{f_{\der{F},1}} & G_2}\]
+
+ 	Now, by \Cref{thm:switch_uni} we know that $f'_{0}=f_{\der{F},0}\circ \phi_{D_{\der{E},0}}$, so that 
+ 	\begin{align*}
+ 		f_{\der{F},0}\circ \phi_{D_{\der{E},0}}\circ z_0&=f'_{0}\circ z_0\\&=f_0\circ p_0=f_{\der{F},0}\circ z_{\der{F},0}
+ 	\end{align*}
+ 	and thus $z_{\der{F},0}=\phi_{D_{\der{E},0}}\circ z_0$. Since $\der{F}$ is a switch we can use \Cref{lem:equi} to get:
+	\begin{align*}
+		\iota'_{G_2}\circ g_1\circ p_1=&\Psi\circ \iota_{\der{E}, G_2}\circ \phi^{-1}_{G_2}\circ g_1\circ p_1\\=&\Psi\circ \Phi^{-1}\circ \iota_{\der{F}, G_2}\circ g_1\circ p_1\\=&\Psi \circ \Phi^{-1}\circ \iota_{\der{F}, G_{\der{F}, 1}}\circ g_{\der{F}, 0}\circ z_{\der{F},0}\\=&\Psi \circ \iota_{\der{E}, G_{\der{E}, 1}}\circ \phi^{-1}_{G_{\der{E}, 1}}\circ g_{\der{F}, 0}\circ z_{\der{F},0}\\=&\Psi \circ \iota_{\der{E}, G_{\der{E}, 1}}\circ g_{\der{E},0}\circ \phi^{-1}_{D_{\der{E}, 0}}\circ  z_{\der{F},0}\\=&\iota'_{G_1}\circ g'_{0} \circ \phi^{-1}_{D_{\der{E}, 0}} \circ z_{\der{F},0}\\=&	\iota'_{G_1}\circ g'_{0} \circ z_{0}\end{align*}
+
+	The thesis now follows using again from \Cref{lem:equi}.
 	\end{proof}
@@
 \cite{heindel2009category}, we build on the last results of the previous section to give some conditions guaranteeing the existence of a switch.
-
-We are now ready to introduce the fundamental concept of this section.
 
@@
 	the first two squares depicted  
-	below are pushouts and if the pushout of $r_1 : K_1 \to R_1$ along $u_1 : K_1 \to P$ exists.
+	below are pushouts and if $r_1 : K_1 \to R_1$  has a pushout along $u_1 : K_1 \to P$.
 	\[
@@
 	Let us complete this diagram defining the dotted arrows. To get
-	$j_1\colon L_0\to Q_0$ and $q_0\colon P\to Q_0$ it is enough to
+	$j_1\colon L_0\to Q_0$ and $q_0\colon P\mto Q_0$ it is enough to
 	take a pushout of $l_0$ along $u_0$, which exists since
 	$l_0\in \mathcal{M}$. Moreover, the existence of the wanted
-	$a_0\colon Q_0\to G_0$ and $b_1\colon Q_1\to G_2$ follows from
+	$a_0\colon Q_0\to G_0$ and $b_1\colon Q_1\to G_2$ follows from the following equalities.
 	\[\begin{split}
@@
 	\]
+
 	We can prove some other properties of
-		the arrows appearing in the diagram above. The four rectangles
+		the arrows appearing in the diagram above. Indeed $q_0$ and $a_0$, being pushouts of
+		respectively $l_0$ and $p_0$ belongs to
+		$\mathcal{M}$. Moreover, the four rectangles
 		below are pushouts and their left halves are pushouts
 		too. Therefore, by \Cref{lem:po1} also their right halves are
-		pushouts.  Moreover, $q_0$ and $a_0$ are pushouts of
-		respectively $l_0$ and $p_0$, thus they are elements of
-		$\mathcal{M}$. By \Cref{prop:pbpoad} the left halves of the
+		pushouts. By \Cref{prop:pbpoad} the left halves of the
 		second and third rectangles are pullbacks too. 
-
 		\[\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar[d]_{r_0}\ar[r]_{u_0}
@@
 
-So equipped we can now prove a version of the Local Church-Rosser Theorem for strong independence pairs in ledt-linear DPO rewriting systems.
+So equipped we can now prove a version of the Local Church-Rosser Theorem for strong independence pairs in left-linear DPO rewriting systems.
 
@@
 
-		Since $q_0\colon P\to Q_0$ is in
+		Since $q_0\colon P\mto Q_0$ is in
 	$\mathcal{M}$, we can take its pushout along $q_1$ to get the dotted
-	arrows $a_1\colon Q_1\mto H_1$ and $q_0\colon Q_0\to H_1$. But then,
-	since the composite of two pushout squares is a pushout, the diagram
-	below is a derivation
+	arrows $a_1\colon Q_1\mto H_1$ and $q_0\colon Q_0\to H_1$. But then by \Cref{lem:po1}, the diagram
+	below is a derivation.
 	\[\xymatrix{L_1 \ar[d]_{f_0 \circ i_1}&& K_1
@@
 
-		The thesis now follows at once since, by construction, the derivation above is a switch of $\dder{D}_0$ and $\dder{D}_1$ along	$(i_0, i_1)$.
+		By construction, the above derivation is a pre-switch for $\der{D}$ along $(i_0, i_1)$ which, by the existence of $q_1$, is a switch.
 \end{proof}
@@
 \begin{lemma}\label{cor:strongip}
-	Let $(\X, \R)$ be a left-linear DPO rewriting system and consider the following derivation $\der{D}={\dder{D}_{i}}_{i=0}^i$ and suppose that $(i_0, i_1)$ is a strong independence pair.
+	Let $(\X, \R)$ be a left-linear DPO rewriting system. Let us consider the following derivation $\der{D}={\dder{D}_{i}}_{i=0}^i$ and suppose that $(i_0, i_1)$ is a strong independence pair.
 	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
 		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
-		\ar@{.>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
-		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{.>}@/_.25cm/[dlll]^(.4){i_1}
+		\ar@{>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
+		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{>}@/_.25cm/[dlll]^(.4){i_1}
 		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
@@
 
-	Suppose, moreover, that the following diagram defines a switch for $\dder{D}_0$ and $\dder{D}_1$ along $(i_0, i_1)$. 	
+	Suppose, moreover, that the following diagram defines a switch $\der{E}$ for $\dder{D}_0$ and $\dder{D}_1$ along $(i_0, i_1)$. 	
 	\[
@@
 		&&  {K_1} \ar@{>->}[ll]_{l_1} \ar[r]^{r_1} \ar[d]_{k_0'}
-		&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{.>}_(.4){i_0'}|(.32)\hole[drrr]
+		&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{>}_(.4){i_0'}|(.32)\hole[drrr]
 		& & 
-		{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{.>}^(.4){i_1'}[dlll] 
+		{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{>}^(.4){i_1'}[dlll] 
 		&  {K_0} \ar@{>->}[l]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
@@
 	\]
-and define $T$, with the arrows $t_0\colon T\mto D'_0$ and $t_1\colon T\to D'_1$ as the pullback of $f'_1$ along $g'_0$.
-
-Finally, consider the derivation $\der{F}$ below, constructed in the proof of \Cref{prChurch}. 
-\[\xymatrix{L_1 \ar[d]_{f_0 \circ i_1}&& K_1
-	\ar[d]_{q_0\circ u_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1
-	\ar@/^.35cm/[drrr]|(.31)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{a_1\circ
-		j_0} && L_0 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{b_0\circ
-		j_1}& K_0\ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
-	\ar[d]^{g_1\circ i_0} \\G_0 && \ar@{>->}[ll]^{a_0} Q_0 \ar[rr]_{b_0}&&
-	H_1 && \ar@{>->}[ll]^{a_1} Q_1 \ar[rr]_{b_1}&& G_2}\]
-and let $\{\phi_{X}\}_{X\in \Deltamin(\der{F})}$ be the abstraction equivalence built in \Cref{thm:switch_uni}.
 
@@
 	\begin{enumerate}
-		\item consider the following two squares, the first of which is a pullback and the second an $\mathcal{M}$-pushout,
-		\[\xymatrix{P \ar[r]^{p_1} \ar@{>->}[d]_{p_0} & D_1 \ar@{>->}[d]^{f_1}& P \ar[r]^{q_1} \ar@{>->}[d]_{q_0} & Q_1 \ar@{>->}[d]^{a_1}\\ D_0 \ar[r]_{g_0} & G_1&Q_0 \ar[r]_{b_0} & H_1}\]
-		then there exists an isomorphism $v\colon P\to T$ fitting in the diagram below:
-		\[\xymatrix{ P \ar@{.>}[dr]^{v} \ar[rrr]^{q_1} \ar@{>->}[ddd]_{q_0}&&& Q_1 \ar@{>->}[ddd]^{a_1} \ar[dl]_{\phi_{Q_1}}\\&T \ar@{>->}[d]_{t_0}\ar[r]^{t_1}& D'_1 \ar@{>->}[d]^{f'_1} \\ & D'_0\ar[r]_{g'_0} & G'_1\\Q_0 \ar[rrr]_{b_0} \ar[ur]_{\phi_{Q_0}}&&& H_1 \ar[ul]^{\phi_{H_1}}}\]
-
-		\item consider the diagram below, in which the inner square is a pullback and the dotted arrows are constructed as in \Cref{rem:deco}:
-		\[\xymatrix{K_1 \ar[r]^{r_1} \ar@/_.3cm/[ddr]_{k'_0} \ar@{.>}[dr]^{e_0}& R_1  \ar[dr]^{i'_0}  && K_0 \ar@{>->}[r]^{l_0} \ar@/_.3cm/[ddr]_{k'_1} \ar@{.>}[dr]^{e_1}& L_1  \ar[dr]^{i'_1} \\& T\ar@{>->}[d]_{t_0} \ar[r]^{t_1}& D'_1  \ar@{>->}[d]^{f'_1} && T \ar@{>->}[r]^{t_0} \ar[d]_{t_1}& D'_0 \ar[d]^{g'_0}\\&D'_0 \ar[r]_{g'_0} & G'_1 && D'_1\ar@{>->}[r]_{f'_1} & G'_1}\]
-		then $v\circ u_1=e_0$, $v\circ u_0=e_1$ and the two squares below are pushouts;
-		\[\xymatrix{K_1  \ar[d]_{e_0} \ar[r]^{r_1} & R_1 \ar[d]^{i'_0} & K_0 \ar@{>->}[r]^{l_0} \ar[d]_{e_1}& L_0 \ar[d]^{i'_1}\\ T \ar[r]_{t_1}  & D'_1 & T \ar@{>->}[r]_{t_0} & D'_0 }\]
-
 		\item $(i'_0, i'_1)$ is a strong independence pair;
 
-	\item there exists a commutative diagram the one below.
+		\item consider the diagram below, built as in \Cref{rem:quadrati}:
 
@@
 			\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_0}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
-		&&P\ar@{.>}[dr]_{z_1}	\ar@{>.>}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
-	in which the following four squares are all pushouts, while the first three are also pullbacks.
-	\[\xymatrix{P \ar@{>->}[r]^{p_0} \ar@{>->}[d]_{p_1}& D_0 \ar@{>->}[d]^{g_0}  & P \ar@{>->}[r]^{z_0} \ar@{>->}[d]_{p_0}& D'_0 \ar@{>->}[d]^{f'_0} &  P \ar@{>->}[d]_{z_0} \ar[r]^{z_1} & D'_1 \ar@{>->}[d]^{f'_1} & P\ar[r]^{z_1} \ar[d]_{p_1}&D'_1 \ar[d]^{g'_1}\\ D_1 \ar@{>->}[r]_{f_1} & G_1  & D_0 \ar@{>->}[r]_{f_0} & G_0 & D'_0 \ar[r]_{g'_0}& G'_1 & D_1 \ar[r]_{g_1}& G_2}\]
+			&&P\ar@{>}[dr]_{z_1}	\ar@{>}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
+
+		The following four squares are all pushouts, while the first three are also pullbacks. 
+		\[\xymatrix{P \ar@{>->}[r]^{p_0} \ar@{>->}[d]_{p_1}& D_0 \ar@{>->}[d]^{g_0}  & P \ar@{>}[r]^{z_0} \ar@{>->}[d]_{p_0}& D'_0 \ar@{>->}[d]^{f'_0} &  P \ar@{->}[d]_{z_0} \ar[r]^{z_1} & D'_1 \ar@{>->}[d]^{f'_1} & P\ar[r]^{z_1} \ar[d]_{p_1}&D'_1 \ar[d]^{g'_1}\\ D_1 \ar@{>->}[r]_{f_1} & G_1  & D_0 \ar@{>->}[r]_{f_0} & G_0 & D'_0 \ar[r]_{g'_0}& G'_1 & D_1 \ar[r]_{g_1}& G_2}\]
+		In particular, the arrow $z_0\colon P\to D'_0$ belongs to $\mathcal{M}$.
 	\end{enumerate}
@@
 \begin{proof}
+	Consider the derivation $\der{F}$ below, constructed in the proof of \Cref{prChurch}. 
+	\[\xymatrix{L_1 \ar[d]_{f_0 \circ i_1}&& K_1
+		\ar[d]_{q_0\circ u_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1
+		\ar@/^.35cm/[drrr]|(.31)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{a_1\circ
+			j_0} && L_0 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{b_0\circ
+			j_1}& K_0\ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
+		\ar[d]^{g_1\circ i_0} \\G_0 && \ar@{>->}[ll]^{a_0} Q_0 \ar[rr]_{b_0}&&
+		H_1 && \ar@{>->}[ll]^{a_1} Q_1 \ar[rr]_{b_1}&& G_2}\]
+	and let $\{\phi_{X}\}_{X\in \Deltamin(\der{F})}$ be the abstraction equivalence between $\der{F}$ and $\der{E}$ built in \Cref{thm:switch_uni}.
+
+	We can also take the following three squares, the first two of which are pullbacks and the third one is an $\mathcal{M}$-pushout and so, by \Cref{prop:pbpoad} is a pullback too.
+	\[\xymatrix{T \ar[r]^{t_1} \ar@{>->}[d]_{t_0} & D'_1 \ar@{>->}[d]^{f'_1} & P \ar[r]^{p_1} \ar@{>->}[d]_{p_0} & D_1 \ar@{>->}[d]^{f_1} &P \ar[r]^{q_1} \ar@{>->}[d]_{q_0} & Q_1 \ar@{>->}[d]^{a_1}\\ D'_0 \ar[r]_{g'_0}& G'_1 &D_0 \ar[r]_{g_0} & G_1&Q_0 \ar[r]_{b_0} & H_1}\]
+
+	 By the universal property of pullbacks  we get the dotted arrows $v\colon P\to T$ and $w\colon T\to P$ in the following two diagrams.
+	\[\xymatrix@R=15pt{ P \ar@{.>}[dr]^{v} \ar[rrr]^{q_1} \ar@{>->}[ddd]_{q_0}&&& Q_1 \ar@{>->}[ddd]^{a_1} \ar[dl]_{\phi_{Q_1}}& T\ar@{.>}[dr]^{w}  \ar[rrr]^{t_1} \ar@{>->}[ddd]_{t_0}&&& D'_1 \ar[dl]_{\phi^{-1}_{Q_1}} \ar@{>->}[ddd]^{f'_1}\\&T \ar@{>->}[d]_{t_0}\ar[r]^{t_1}& D'_1 \ar@{>->}[d]^{f'_1} &&& P \ar@{>->}[d]_{q_0}\ar[r]^{q_1}& Q_1\ar@{>->}[d]^{a_1}\\ & D'_0\ar[r]_{g'_0} & G'_1 &&& Q_0 \ar[r]_{b_0}& H_1 \\Q_0 \ar[rrr]_{b_0} \ar[ur]_{\phi_{Q_0}}&&& H_1 \ar[ul]^{\phi_{H_1}} & D'_0 \ar[rrr]_{g'_0} \ar[ur]_{\phi^{-1}_{Q_0}}&&&G'_1 \ar[ul]^{\phi^{-1}_{H_1}}}\]
+
+	The following equalities now show that $v$ and $w$ are one the inverse of the other.
+	\[\begin{split}
+		t_0\circ v\circ w &=\phi_{Q_0}\circ q_0\circ w\\&=\phi_{Q_0}\circ \phi^{-1}_{Q_0} \circ t_0\\&=t_0 	\end{split}\qquad \begin{split}
+		t_1\circ v\circ w &=\phi_{Q_1}\circ q_1\circ w\\&=\phi_{Q_1}\circ \phi^{-1}_{Q_1} \circ t_1\\&=t_1
+	\end{split}\]
+	\[\begin{split}q_0\circ w\circ v&=\phi^{-1}_{Q_0}	\circ t_0\circ v\\&=\phi^{-1}_{Q_0} \circ \phi_{Q_0}\circ q_0\\&=q_0 
+	\end{split}\qquad \begin{split}
+	q_1\circ w\circ v&=\phi^{-1}_{Q_1}	\circ t_1\circ v\\&=\phi^{-1}_{Q_1} \circ \phi_{Q_1}\circ q_1\\&=q_1
+	\end{split}\]
+
+	Notice that by \Cref{rem:deco} there exist the two dotted arrows in the diagrams below.
+	\[\xymatrix{K_1 \ar[r]^{r_1} \ar@/_.3cm/[ddr]_{k'_0} \ar@{.>}[dr]^{e_0}& R_1  \ar[dr]^{i'_0}  && K_0 \ar@{>->}[r]^{l_0} \ar@/_.3cm/[ddr]_{k'_1} \ar@{.>}[dr]^{e_1}& L_1  \ar[dr]^{i'_1} \\& T\ar@{>->}[d]_{t_0} \ar[r]^{t_1}& D'_1  \ar@{>->}[d]^{f'_1} && T \ar@{>->}[r]^{t_0} \ar[d]_{t_1}& D'_0 \ar[d]^{g'_0}\\&D'_0 \ar[r]_{g'_0} & G'_1 && D'_1\ar@{>->}[r]_{f'_1} & G'_1}\]
+
+	By \Cref{thm:switch_uni}, we know that $\phi_{G_0}=\id{G_0}$ and so $a_0=f'_0\circ \phi_{Q_0}$. By the same theorem we also have 
+	$\phi_{Q_1}\circ j_0=i'_0$ and $\phi_{Q_0}\circ j_1=i'_1$. We can now use these equalities to get:
+	\[\begin{split}
+		t_0\circ v\circ u_0&=\phi_{Q_0} \circ q_0\circ u_0\\&=\phi_{Q_0}\circ j_1\circ l_0\\&=i'_1\circ l_0\\&=t_0\circ e_1
+	\end{split} \qquad \begin{split}
+		t_1\circ v\circ u_1&=\phi_{Q_1} \circ q_1\circ u_1\\&=\phi_{Q_1}\circ j_0\circ r_1\\&=i'_0\circ r_1\\&= t_1\circ e_0 
+	\end{split}\]
+	\[\begin{split}t_0\circ v\circ u_1&=\phi_{Q_0} \circ q_0\circ u_1\\&=k'_0\\&= t_0\circ e_0
+	\end{split}\qquad \begin{split}
+	t_1\circ v\circ u_0&=\phi_{Q_1} \circ q_1\circ u_0\\&=k'_1\\&=t_1\circ e_1
+	\end{split}\]
+	So that $v\circ u_1=e_0$ and $v\circ u_0=e_1$.
+
 	\begin{enumerate}
-		\item  By \Cref{prop:pbpoad}, the square below is also a pullback.
-			\[\xymatrix{P \ar[r]^{q_1} \ar@{>->}[d]_{q_0} & Q_1 \ar@{>->}[d]^{a_1}\\ Q_0 \ar[r]_{b_0} & H_1}\]
-			Thus by the universal property of pullbacks  we get the dotted arrows $v\colon P\to T$ and $w\colon T\to P$ in the following diagrams.
-		\[\xymatrix{ P \ar@{.>}[dr]^{v} \ar[rrr]^{q_1} \ar@{>->}[ddd]_{q_0}&&& Q_1 \ar@{>->}[ddd]^{a_1} \ar[dl]_{\phi_{Q_1}}& T\ar@{.>}[dr]^{w}  \ar[rrr]^{t_1} \ar@{>->}[ddd]_{t_0}&&& D'_1 \ar[dl]_{\phi^{-1}_{Q_1}} \ar@{>->}[ddd]^{f'_1}\\&T \ar@{>->}[d]_{t_0}\ar[r]^{t_1}& D'_1 \ar@{>->}[d]^{f'_1} &&& P \ar@{>->}[d]_{q_0}\ar[r]^{q_1}& Q_1\ar@{>->}[d]^{a_1}\\ & D'_0\ar[r]_{g'_0} & G'_1 &&& Q_0 \ar[r]_{b_0}& H_1 \\Q_0 \ar[rrr]_{b_0} \ar[ur]_{\phi_{Q_0}}&&& H_1 \ar[ul]^{\phi_{H_1}} & D'_0 \ar[rrr]_{g'_0} \ar[ur]_{\phi^{-1}_{Q_0}}&&&G'_1 \ar[ul]^{\phi^{-1}_{H_1}}}\]
-
-To see that they are one the inverse of the other it is then enough to compute.
-		\[\begin{split}
-		t_0\circ v\circ w &=\phi_{Q_0}\circ q_0\circ w\\&=\phi_{Q_0}\circ \phi^{-1}_{Q_0} \circ t_0\\&=t_0\\q_0\circ w\circ v&=\phi^{-1}_{Q_0}	\circ t_0\circ v\\&=\phi^{-1}_{Q_0} \circ \phi_{Q_0}\circ q_0\\&=q_0 	\end{split}\qquad \begin{split}
-		t_1\circ v\circ w &=\phi_{Q_1}\circ q_1\circ w\\&=\phi_{Q_1}\circ \phi^{-1}_{Q_1} \circ t_1\\&=t_1\\q_1\circ w\circ v&=\phi^{-1}_{Q_1}	\circ t_1\circ v\\&=\phi^{-1}_{Q_1} \circ \phi_{Q_1}\circ q_1\\&=q_1
-		\end{split}\]
-
-	\item By \Cref{thm:switch_uni}, we know that $\phi_{G_0}=\id{G_0}$, so that $a_0=f'_0\circ \phi_{Q_0}$, moreover, by the same theorem we have 
-	\[\phi_{Q_1}\circ j_0=i'_0 \qquad  \phi_{Q_0}\circ j_1=i'_1\]
-
-		We can now use the previous equalities to get
-		\[\begin{split}
-			t_0\circ v\circ u_0&=\phi_{Q_0} \circ q_0\circ u_0\\&=\phi_{Q_0}\circ j_1\circ l_0\\&=i'_1\circ l_0\\&=t_0\circ e_1\\	t_0\circ v\circ u_1&=\phi_{Q_0} \circ q_0\circ u_1\\&=k'_0\\&= t_0\circ e_0
-		\end{split} \qquad \begin{split}
-			t_1\circ v\circ u_1&=\phi_{Q_1} \circ q_1\circ u_1\\&=\phi_{Q_1}\circ j_0\circ r_1\\&=i'_0\circ r_1\\&= t_1\circ e_0 \\ t_1\circ v\circ u_0&=\phi_{Q_1} \circ q_1\circ u_0\\&=k'_1\\&=t_1\circ e_1
-		\end{split}\]
-
-	So that $v\circ u_1=e_0$ and $v\circ u_0=e_1$. The thesis now follows from the two diagrams below, since their left halves are pushouts by construction.		
-		\[\xymatrix{K_1  \ar@/^.4cm/[rr]^{e_0}\ar[r]_{u_1} \ar[d]_{r_1}& P \ar[r]_{v} \ar[d]_{q_1} & T \ar[d]^{t_1} & K_0 \ar@/^.4cm/[rr]^{e_1} \ar@{>->}[d]_{l_0}\ar[r]_{u_0} & P \ar[r]_{v}  \ar@{>->}[d]_{q_0}& T \ar@{>->}[d]^{t_0}\\ R_1 \ar@/_.4cm/[rr]_{i'_0} \ar[r]^{j_0}& Q_1 \ar[r]^{\phi_{Q_1}} & D'_1 & L_0 \ar@/_.4cm/[rr]_{i'_1} \ar[r]^{j_0} & Q_0 \ar[r]^{\phi_{Q_0}} & D'_0 }\]
-
-		\item Given the results of the previous point, it is now enough to show that the pushout of $r_0\colon K_0\to R_0$ along $e_1\colon K_0\to T$ exists. We can consider the diagram below
-		\[\xymatrix{K_0 \ar@/^.4cm/[rr]^{u_0} \ar[d]_{r_0} \ar[r]_{e_1}& T  \ar[d]_{p_1\circ w}\ar[r]_{w} & P \ar[d]^{p_1}\\ R_0 \ar[r]_{i_0}& D_1 \ar[r]_{\id{D_1}}& D_1}\]
-		But the outer diagram is a pushout since $(i_0, i_1)$ is strong and we can conclude.
-
-		\item Let $z_0\colon P\mto D'_0$ and $z_1\colon P\to D_1$ be, respectively, $t_0\circ v$ and $t_1\circ v$. Then we have
-
-		\[\begin{split}
-		g'_0\circ z_0&=g'_0\circ t_0\circ v\\&=f'_1\circ t_1\circ v\\&=f'_1\circ z_1
-		\end{split}\quad \begin{split}
-		z_0\circ u_1&=t_0\circ v\circ u_1\\&=\phi_{Q_0}\circ q_0\circ u_1\\&=k'_0
-		\end{split} \quad \begin{split}
-		z_1\circ u_0&=t_1\circ v\circ u_0\\&=\phi_{Q_1}\circ q_1\circ u_0\\&=k'_1
-		\end{split}\]
-
-		Moreover
-		\[\begin{split}
-			f'_0\circ z_0&=f'_0\circ t_0\circ v\\&=f'_0\circ \phi_{Q_0}\circ q_0\\&=a_0\circ q_0\\&=f_0\circ p_0
-		\end{split} \qquad \begin{split}
-		g'_1\circ z_1&=g'_1\circ t_1\circ v\\&=g'_1\circ \phi_{Q_1}\circ q_1\\&=\phi_{G_2}\circ b_1 \circ q_1\\&=\phi_{G_2}\circ g_1\circ p_1\\&=f_0\circ p_0
-		\end{split} \]
-
-		Therefore the $z_0$ and $z_1$ fit in the diagram above.
-
-		To conclude, notice that the the four rectangles below and their halves, by construction and by point $3$, are pushouts, thus by \Cref{lem:po1} also their right halves are
-		pushouts.
-
+	\item To verify the conditions of \Cref{def:strong}, it is enough to show that the three squares below are pushouts.
+	\[\xymatrix{K_1  \ar[d]_{e_0} \ar[r]^{r_1} & R_1 \ar[d]^{i'_0} & K_0 \ar@{>->}[r]^{l_0} \ar[d]_{e_1}& L_0 \ar[d]^{i'_1}& K_0  \ar[r]_{r_0} \ar[d]_{e_1}& R_0  \ar[d]^{i_0}\\ T \ar[r]_{t_1}  & D'_1 & T \ar@{>->}[r]_{t_0} & D'_0 &T \ar[r]_-{p_1\circ w}& D_1}\]
+
+	 The thesis now follows from the three diagrams below.
+The left halves of the first two are pushouts by construction while $\phi_{Q_1}$ and $\phi_{Q_0}$ are isomorphism, so the whole rectangles are pushouts.
+The outer boundary of the third diagram is a pushout since $(i_0, i_1)$ is strong and $w$ is an isomorphism, therefore its left half is a pushout as wanted.
+	\[\xymatrix{K_1  \ar@/^.4cm/[rr]^{e_0}\ar[r]_{u_1} \ar[d]_{r_1}& P \ar[r]_{v} \ar[d]_{q_1} & T \ar[d]^{t_1} & K_0 \ar@/^.4cm/[rr]^{e_1} \ar@{>->}[d]_{l_0}\ar[r]_{u_0} & P \ar[r]_{v}  \ar@{>->}[d]_{q_0}& T \ar@{>->}[d]^{t_0}& K_0 \ar@/^.4cm/[rr]^{u_0} \ar[d]_{r_0} \ar[r]_{e_1}& T  \ar[d]_{p_1\circ w}\ar[r]_{w} & P \ar[d]^{p_1}\\ R_1 \ar@/_.4cm/[rr]_{i'_0} \ar[r]^{j_0}& Q_1 \ar[r]^{\phi_{Q_1}} & D'_1 & L_0 \ar@/_.4cm/[rr]_{i'_1} \ar[r]^{j_0} & Q_0 \ar[r]^{\phi_{Q_0}} & D'_0 &R_0 \ar[r]_{i_0}& D_1 \ar[r]_{\id{D_1}}& D_1}\]
+
+	\item We already know that $e_0=v\circ u_1$ and $e_1=v\circ u_0$, but we can prove other two equalities. On the one hand computing we get:
+	\begin{align*}
+		f'_0\circ t_0\circ v&=f'_0\circ \phi_{Q_0}\circ q_0\\&=a_0\circ q_0\\&=f_0\circ p_0\\&=f'_0\circ z_0
+	\end{align*}
+	Since $f'_0$ is mono then we can deduce that $z_0=t_0\circ v$. On the other hand, this equation allows as to deduce that
+	\begin{align*}
+	f'_1\circ t_1\circ v&=f'_1\circ \phi_{Q_1}\circ q_1\\&=\phi_{H_1}\circ a_1\circ q_1\\&=\phi_{H_1}\circ b_0\circ q_0\\&=g'_0\circ \phi_{Q_0}\circ q_0\\&=g'_0\circ t_0\circ v\\&=g'_0\circ z_0\\&=f'_1\circ z_1
+	\end{align*}
+	and so we can deduce that $z_1=t_1\circ v$. Therefore the diagrams below commute and by the previous point they have pushouts as inner squares. Hence their outer boundaries are pushouts too.
+
+	\[\xymatrix{&K_1  \ar@/_.3cm/[dl]_{u_1}\ar[d]^{e_0} \ar[r]^{r_1} & R_1 \ar[d]^{i'_0} && K_0 \ar@/_.3cm/[dl]_{u_0}\ar@{>->}[r]^{l_0} \ar[d]^{e_1}& L_0 \ar[d]^{i'_1}&& K_0 \ar@/_.3cm/[dl]_{u_0} \ar[r]_{r_0} \ar[d]^{e_1}& R_0  \ar[d]^{i_0}\\ P\ar@/_.4cm/[rr]_{z_1}\ar[r]^{v} &T \ar[r]^{t_1} &  D'_1 &P \ar@/_.4cm/[rr]_{z_0}\ar[r]^{d}& T \ar@{>->}[r]^{t_0}  &D'_0 &P\ar@/_.4cm/[rr]_{p_1}\ar[r]^{v}&T \ar[r]^-{p_1\circ w}& D_1}\]
+
+	But then the four rectangles below and their left halves are pushouts. Thus by \Cref{lem:po1} also their right halves are pushouts. 
 	\[\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar[d]_{r_0}\ar[r]_{u_0}
@@
 		\ar@/^.4cm/[rr]^{k'_1}\ar@{>->}[d]_{l_0}\ar[r]_{u_0}
-			&P\ar@{>->}[d]^{z_0} \ar[r]_{z_1} & D'_1 \ar@{>->}[d]^{f'_1}\\
-			R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i'_1}&D_1 \ar@{>->}[r]^{f_1}
-			& G_1&L_1 \ar@/_.4cm/[rr]_{m'_1} \ar[r]^{i_1}&D'_0\ar[r]^{g'_0} &
+		&P\ar@{>}[d]^{z_0} \ar[r]_{z_1} & D'_1 \ar@{>->}[d]^{f'_1}\\
+		R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i_0}&D_1 \ar@{>->}[r]^{f_1}
+		& G_1&L_0 \ar@/_.4cm/[rr]_{m'_1} \ar[r]^{i'_1}&D'_0\ar[r]^{g'_0} &
 		G'_1}\]
@@
 		\ar@/^.4cm/[rr]^{k_0}\ar@{>->}[d]_{l_0}\ar[r]_{u_0}
-			&P\ar@{>->}[d]^{z_0} \ar@{>->}[r]_{p_0} & D_0
+		&P\ar@{>}[d]^{z_0} \ar@{>->}[r]_{p_0} & D_0
 		\ar@{>->}[d]^{f_0}&K_1
@@
 	\end{enumerate}
+\end{proof}
+
+\begin{corollary}\label{cor:refl}
+	Let $\der{D}:=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation and let $(i_0, i_1)$ be a strong independence pair between $\dder{D}_0$ and $\dder{D}_1$.
+Suppose that the derivation $\der{E}$ below is a switch for $\der{D}$ along $(i_0, i_1)$.
+	\[
+	\xymatrix@R=20pt@C=20pt{
+		{L_1} \ar[d]_{m_0'}
+		&&  {K_1} \ar@{>->}[ll]_{l_1} \ar[r]^{r_1} \ar[d]_{k_0'}
+		&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{>}_(.4){i_0'}|(.32)\hole[drrr]
+		& & 
+		{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{>}^(.4){i_1'}[dlll] 
+		&  {K_0} \ar@{>->}[l]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
+		& & {R_0} \ar[d]^{h_1'} \\		
+		{G_0}
+		& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rr]_{g_0'}
+		& &  {G'_1} 
+		& &  {D_1'} \ar@{>->}[ll]^{f_1'} \ar[rr]_{g_1'}
+		& & {G_2}  }
+	\]
+
+	Then $\der{D}$ is a switch for $\der{E}$ along $(i'_0, i'_1)$.
+\end{corollary}
+\begin{proof}
+	By \Cref{rem:switch} we know that $\der{D}$ is a pre-switch.
+By the last point of \Cref{cor:strongip} $(P, \{z_i\}_{i=0}^1)$ is a pullback for $f'_1$ along $g'_0$ and so the existence of $p_1$ witnesses that $\der{D}$ is a switch.
 \end{proof}
@@
 
- $G_1$ is obtained as the pushout of $k_0$ along $r_0$m thus get the wanted arrow $\kappa\colon G_1\to \tpro{E}$ it is now enough to compute:
+	If we compute we get
 	\begin{align*}
@@
 
-	Let us now suppose that $(i_0,i_1)$ is a strong independence pair. We can then consider the following two squares, the first of which is a pullback and the second one, by strongness, a  pushout.
-
+Since $G_1$ is obtained as the pushout of $k_0$ along $r_0$ we obtain the wanted arrow $\kappa\colon G_1\to \tpro{E}$.
+
+	\begin{enumerate}
+		\item  Suppose now that $(i_0,i_1)$ is a strong independence pair.
+Thus we can then consider the following two squares, the first of which is a pullback and the second one, by strongness, a  pushout.
 			\[\xymatrix{P \ar[r]^{p_1}  \ar@{>->}[d]_{p_0} & D_1 \ar@{>->}[d]^{f_1} & K_0 \ar[r]^{r_0}  \ar[d]_{u_0} & R_0 \ar[d]^{i_0}\\ D_0\ar[r]_{g_0} & G_1 & P\ar[r]_{p_1} & D_1}\]
 
-	\begin{enumerate}
-		\item   Consider the arrow $\kappa\colon G_1\to \tpro{E}$ built in the previous point, then we have
-		\begin{align*}
-			\kappa \circ f_1\circ i_0&=\kappa\circ h_0\\&=\iota_{\der{E},R_0}\\&=\iota_{\der{E}{G_2}}\circ h'_1\\&=\iota_{\der{E}{G_2}}\circ g_1\circ i_0
-		\end{align*}
-
-		\begin{align*}
-			\kappa\circ f_1\circ p_1&=\kappa \circ g_0\circ p_0\\&=\iota_{\der{E},G_0}\circ f_0\circ p_0
-		\end{align*}
-		\item 
-		\qedhere 
+Let us consider the arrow $\kappa\colon G_1\to \tpro{E}$ built before. We have:
+\[	\begin{split}
+	\kappa \circ f_1\circ i_0&=\kappa\circ h_0\\&=\iota_{\der{E},R_0}\\&=\iota_{\der{E}{G_2}}\circ h'_1\\&=\iota_{\der{E}{G_2}}\circ g_1\circ i_0\\ & \\&
+\end{split}\qquad 
+\begin{split}
+\kappa\circ f_1\circ p_1&=\kappa \circ g_0\circ p_0\\&=\iota_{\der{E},G_0}\circ f_0\circ p_0\\&=\iota_{\der{E},G_0}\circ f'_0\circ z_0\\&=\iota_{\der{E}, D'_1} \circ z_0\\&=\iota_{\der{E}, G'_1}\circ g'_0 \circ z_0\\&=\iota_{\der{E}, G_2}\circ g_1\circ p_1
+\end{split}
+\]
+Thus $\kappa\circ f_1=\iota_{\der{E}, G_2}\circ g_1$. But this entails that we have a cocone $\{\theta_X\}_{X\in \Deltamin(\der{D})}$ on $\Deltamin(\der{D})$ given by:
+\[\theta_X:=\begin{cases}
+\iota_{\der{E}, G_0} & X=G_0\\
+	\iota_{\der{E}, G_0}\circ f_0 & X=D_0\\
+	\kappa & X=G_1\\
+	\kappa \circ f_1 & X=D_1\\
+	\iota_{\der{E}, G_2} & X=G_2
+\end{cases}\]
+To conclude it is now enougb to take as $\phi$ the arrow induced by this cocone.
+
+		\item By \Cref{cor:refl} and the first half of this lemma we know that ther is an arrow $\kappa'\colon G'_1\to \tpro{D}$ such that:
+				\[\kappa' \circ g'_{0} = \iota_{\der{D}, G_0}\circ f'_{0} \qquad \kappa'\circ h'_{0}= \iota_{\der{D}, R_1}\]
+
+		By the first point of \Cref{cor:strongip}, $(i'_0,i'_1)$ is a strong independence pair.
+Thus by the previous point we get arrows $\phi\colon \tpro{D}\to \tpro{E}$ and $\phi'\colon \tpro{E}\to \tpro{E}$ such that
+			\[\begin{split}\phi \circ \iota_{\der{D}, G_0}&=\iota_{\der{E}, G_0} \\  \phi' \circ \iota_{\der{E}, G_0}&=\iota_{\der{D}, G_0} \end{split} \qquad \begin{split}\phi \circ \iota_{\der{D}, G_1}&=\kappa \\\phi' \circ \iota_{\der{E}, G'_1}&=\kappa'  \end{split} \qquad \begin{split} \phi\circ \iota_{\der{D}, G_2}&=\iota_{\der{E}, G_2}\\  \phi'\circ \iota_{\der{E}, G_2}&=\iota_{\der{D}, G_2}\end{split}   \]
+
+	We want to show that $\phi$ and $\phi'$ are one the inverse on the other. To do so we can start noticing that:
+	\[\begin{split}
+		\phi'\circ\phi \circ  \iota_{\der{D}, G_1}\circ  h_0&=\phi'\circ \kappa\circ h_0\\&=\phi'\circ \iota_{\der{E}, R_0}\\&=\phi'\circ \iota_{\der{E}, G_2}\circ h'_1\\&=\iota_{\der{D}, G_2}\circ h'_1\\&=\iota_{\der{D}, G_2}\circ g_1\circ i_0\\&=\iota_{\der{D}, D_1}\circ i_0\\&=\iota_{\der{D}, G_1}\circ f_1\circ i_0\\&=\iota_{\der{D}, G_1}\circ h_0
+	\end{split}\qquad \begin{split}
+	\phi\circ\phi' \circ  \iota_{\der{E}, G'_1}\circ  h'_0&=\phi\circ \kappa'\circ h'_0\\&=\phi\circ \iota_{\der{E}, R_1}\\&=\phi\circ \iota_{\der{D}, G_2}\circ h_1\\&=\iota_{\der{E}, G_2}\circ h_1\\&=\iota_{\der{E}, G_2}\circ g'_1\circ i'_0\\&=\iota_{\der{E}, D'_1}\circ i'_0\\&=\iota_{\der{E}, G'_1}\circ f'_1\circ i'_0\\&=\iota_{\der{E}, G'_1}\circ h'_0
+	\end{split}\]
+		\[\begin{split}
+		\phi'\circ\phi \circ  \iota_{\der{D}, G_1}\circ  g_0&=\phi'\circ \kappa\circ g_0\\&=\phi'\circ \iota_{\der{E}, G_0}\circ f_0\\&=\iota_{\der{D}, G_0}\circ f_0\\&=\iota_{\der{D}, D_1}\\&=\iota_{\der{D}, G_1}\circ g_0
+	\end{split}\qquad \begin{split}	\phi\circ\phi' \circ  \iota_{\der{E}, G'_1}\circ  g'_0&=\phi\circ \kappa'\circ g'_0\\&=\phi\circ \iota_{\der{D}, G_0}\circ f'_0\\&=\iota_{\der{E}, G_0}\circ f'_0\\&=\iota_{\der{E}, D'_1}\\&=\iota_{\der{E}, G'_1}\circ g'_0
+	\end{split}\]
+	Thus $\phi'\circ \phi\circ  \iota_{\der{D}, G_1}=\iota_{\der{D}, G_1}$ and $\phi\circ \phi'\circ \iota_{\der{E}, G_1}=\iota_{\der{E}, G_1}$. Moreover we have:
+
+\[\begin{split}\phi'\circ \phi \circ \iota_{\der{D}, G_0}&=\phi'\circ \iota_{\der{E}, G_0} \\&=\iota_{\der{D}, G_0} \end{split} \qquad \begin{split}\phi'\circ \phi\circ \iota_{\der{D}, G_2}&=\phi'\circ \iota_{\der{E}, G_2}\\&=\iota_{\der{D}, G_2} \end{split}   \]
+\[\begin{split}\phi\circ \phi' \circ \iota_{\der{E}, G_0}&=\phi\circ \iota_{\der{D}, G_0} \\&=\iota_{\der{E}, G_0} \end{split} \qquad \begin{split}\phi\circ \phi'\circ \iota_{\der{E}, G_2}&=\phi \circ \iota_{\der{D}, G_2}\\&=\iota_{\der{E}, G_2} \end{split}   \]
+
+But then we also have
+\[
+\begin{split} \phi'\circ \phi\circ \iota_{\der{D}, D_0}&=\phi'\circ \phi \circ \iota_{\der{D}, G_0}\circ f_0\\&=\iota_{\der{D}, G_0}\circ f_0\\&=\iota_{\der{D}, D_0}\end{split} \qquad 
+\begin{split} \phi'\circ \phi\circ \iota_{\der{D}, D_1}&=\phi'\circ \phi \circ \iota_{\der{D}, G_2}\circ g_1\\&=\iota_{\der{D}, G_2}\circ g_1\\&=\iota_{\der{D}, D_1}\end{split} \]
+\[
+\begin{split} \phi\circ \phi'\circ \iota_{\der{E}, D'_0}&=\phi\circ \phi' \circ \iota_{\der{E}, G_0}\circ f'_0\\&=\iota_{\der{E}, G_0}\circ f'_0\\&=\iota_{\der{E}, D'_0}\end{split} \qquad 
+\begin{split} \phi\circ \phi'\circ \iota_{\der{E}, D'_1}&=\phi\circ \phi' \circ \iota_{\der{E}, G_2}\circ g'_1\\&=\iota_{\der{E}, G_2}\circ g'_1\\&=\iota_{\der{E}, D'_1}\end{split} \]
+
+		Therefore $\phi$ is an isomorphism with inverse $\phi'$.
+
+Finally, on the one hand we have
+\[\phi \circ \iota_{\der{D}, G_0}\circ \alpha=\iota_{\der{E}, G_0}\circ \alpha \qquad \phi \circ \iota_{\der{D}, G_2}\circ \omega=\iota_{\der{E}, G_2}\circ \omega\]
+while, on the other hand:
+\[\begin{split}
+	\phi\circ \iota_{\der{D}, G_0}\circ m_0&=\iota_{\der{E}, G_0}\circ m_0\\&=\iota_{\der{E}, G_0}\circ f'_0\circ i'_1\\&=\iota_{\der{E}, D'_0}\circ i'_1\\&=\iota_{\der{E}, G'_1}\circ g'_0\circ i'_1\\&=\iota_{\der{E}, G'_1}\circ m'_1
+\end{split} \qquad \begin{split}
+\phi \circ \iota_{\der{D}, G_2}\circ h_1&=\iota_{\der{E}, G_2}\circ h_1\\&=\iota_{\der{E}, G_2}\circ g'_1\circ i'_0\\&=\iota_{\der{E}, D'_1}\circ i'_0\\&=\iota_{\der{E}, G'_1}\circ f'_1 \circ i'_0\\&=\iota_{\der{E}, G'_1}\circ h'_0
+\end{split} \]
+\[	\begin{split}
+	\phi\circ \iota_{\der{D}, G_1}\circ h_0&=\kappa \circ h_0\\&=\iota_{\der{E}, R_0}\\&=\iota_{\der{E}, G_2}\circ h'_1\\&
+\end{split} \qquad \begin{split}
+\phi\circ \iota_{\der{D}, G_1}\circ m_1&=\kappa\circ m_1\\&=\kappa\circ g_0\circ i_1\\&= \iota_{\der{E}, G_0} \circ f_0 \circ i_1\\&=\iota_{\der{E}, G_0}\circ m_0
+\end{split}\]
+	And so $\phi$ witnesses the consistency of $\tau$. \qedhere 
 	\end{enumerate}
+\end{proof}
+
+\begin{corollary}[Uniqueness of switches]\label{cor:absequi}
+	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation and suppose
+that both $\der{E}=\{\dder{E}_i\}_{i=0}^1$ and
+$\der{F}=\{\dder{F}_i\}_{i=0}^1$ are switches of $\dder{D}_0$ and
+$\dder{D}_1$ along the same strong independence pair $(i_0, i_1)$.
+Then there is a unique abstraction equivalence $\{\phi_X\}_{X\in \Deltamin(\der{E})}$ between $\der{E}$ and $\der{F}$ such that $\phi_{G_0}=\id{G_0}$ and $\phi_{G_2}=\id{G_2}$.
+\end{corollary}
+\begin{proof} We can take two isomorphisms $\alpha\colon \pi(G_0)\to G_0$ and $\omega\colon \pi(G_2)\to G_2$ so that $(\der{D}, \alpha, \omega)$ is a decorated derivation and both $(\der{E}, \alpha, \omega)$ and $(\der{F},\alpha, \omega)$ are decorated switches.
+
+Let $\{\phi_X\}_{X\in \Deltamin\der{E}}$ be the abstraction equivalence built in \Cref{thm:switch_uni}.
+By \Cref{rem:abscons} we know that $\id{[0,1]}$ is a semi-consistent permutation between $(\der{E}, \alpha, \omega)$ and $(\der{F}, \alpha, \omega)$.
+Now, using the third point of \Cref{lem:switchtoperm} and \Cref{rem:inversa} we know that $\tau_{0,1}$ is a both a consistent permutation between $(\der{E}, \alpha, \omega)$ and $(\der{D}, \alpha, \omega)$ and between $(\der{D}, \alpha, \omega)$ and $(\der{F}, \alpha, \omega)$.
+Thus by \Cref{rem:comp} $\id{[0,1]}$ is a consistent permutation between $(\der{E}, \alpha, \omega)$  and $(\der{F}, \alpha, \omega)$.
+By \Cref{cor:fromsemitocons} we deduce that $\omega\circ \phi_{G_2}=\omega$ and so $\phi_{G_2}$ must be $\id{G_2}$.
 \end{proof}
@@
 \end{definition}
+
+\begin{remark}
+We can identify a large class of adhesive categories such that all
+left-linear rewriting systems over such categories are strong
+enforcing. This class includes $\cat{Set}$ and it is closed
+under comma and functor category constructions.  As such, it includes
+essentially all categories (e.g., presheaves over set) that are
+typically considered for modelling purposes. Notably, it contains the
+category $\cat{Graph}$ of directed graphs.
+This is a natural generalisation from adhesive to $\mathcal{M}$-adhesive categories of a class studied in \cite{baldan2011adhesivity} (see \Cref{app:fill} for details).
+\end{remark}
+
+\begin{remark}
+	By \Cref{prChurch} the existence of a strong independence pair
+	entails switchability, which in turn entails sequential
+	independence by construction. Strong enforcing rewriting systems are exactly
+	those rewriting systems in which these three notions coincide.
+\end{remark}
+
+Despite the previous remark, there are $\mathcal{M}$-adhesive rewriting systems in which not every independence pair is strong.
+
+\begin{example}
+	\label{ex:diff2}
+	In light of \Cref{prChurch}, \Cref{ex:diff1} provides an example of
+	an independence pair that is not strong. This gives an example of a
+	left-linear rewriting system in a $\mathcal{M}$-adhesive category that is quite
+	pathological since $\mathcal{M}=\mathsf{I(\X)}$. However, this is expected, 
+	since all natural examples seem to belong to the well-behaved class studied in \Cref{app:fill}.
+\end{example}
 
@@
 	an independence pair as below
-	\[
-	\xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0
-		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar@{>->}[r]^{r_0} & R_0
-		\ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0}
-		&& L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
-		\ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar@{>->}[rr]^{r_1} && R_1
-		\ar[d]^{h_1} \\G_0 && \ar@{>->}[ll]^{f_0} D_0
-		\ar@{>->}[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
-		\ar@{>->}[rr]_{g_1}&& G_2}\]
-
-	Since $(\X, \R)$ is linear, then $r_1\colon K_1\to R_1$ belongs to
+\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
+	\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
+	\ar@{>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
+	\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{>}@/_.25cm/[dlll]^(.4){i_1}
+	\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
+	\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
+	D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
+	\ar[rr]_{g_1}&& G_2}
+\]
+
+	Since $(\X, \R)$ is linear, then $r_1\colon K_1\mto R_1$ belongs to
 	$\mathcal{M}$, thus it admits a pushout along $u_1\colon K_1\to P$,
@@
 
-We can easily
-
-\begin{lemma}
-Let $(P, \{p_0, p_1\})$ be the pullback of $f_1$ along $g_1$, then there exists $z_0\colon P\mto D'_0$ and $z_1\colon P\to D'_1$ making the following diagram commutative
-\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
-	\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
-	\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
-	\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){u_0}\ar[ur]^{r_0}&& G_1 &&
-	K_1
-	\ar@/^.6cm/[ddll]|(.36)\hole_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
-	\ar[dr]^{r_1}\\L_0
-	\ar@/_.6cm/[ddrr]_(.2){i'_1}|(.31)\hole|(.81)\hole
-	\ar[dr]^(.4){m_0}|(.61)\hole && D_0
-	\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1
-	\ar[dr]|(.4)\hole^(.65){g_1}
-	\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_0}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
-	&&P\ar@{.>}[dr]_{z_1}	\ar@{>.>}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
-moreover, the following squares are all pushouts, moreover the first two are also pullbacks.
-\[\xymatrix{P \ar@{>->}[r]^{z_0} \ar@{>->}[d]_{p_0}& D'_0 \ar@{>->}[d]^{f'_0} &  P \ar@{>->}[d]_{z_0} \ar[r]^{z_1} & D'_1 \ar@{>->}[d]^{f'_1} & P\ar[r]^{z_1} \ar[d]_{p_1}&D'_1 \ar[d]^{g'_1}\\ D_0 \ar@{>->}[r]_{f_0} & G_0 & D'_0 \ar[r]_{g'_0}& G'_1 & D_1 \ar[r]_{g_1}& G_2}\]
-\end{lemma}
-\begin{proof}
-	Define $z_0$ and $z_1$ to be, respectively, $t_0\circ v$ and $t_1\circ v$. To prove the commutativity of the diagram in the thesis, first of all we can notice that
-	\begin{align*}
-		g'_0\circ z_0\\&= g'_0\circ t_0\circ v\\&=f'_1\circ t_1\circ v\\&=f'_1\circ z_1
-	\end{align*}
-	To prove the other identities, it is enough to compute and use the identities obtained in the previous point. On the one hand we have
-	\[	\begin{split}f'_0\circ z_0&=f'_0\circ t_0\circ v\\&=f'_0\circ \phi_{Q_0}\circ q_0\\&=a_0\circ q_0\\&=f_0\circ p_0 
-	\end{split} \qquad \begin{split}
-		g'_1\circ z_1&=g'_1\circ t_1\circ v\\&=g'_1\circ \phi_{Q_1}\circ q_1\\&=\phi_{G_2}\circ b_1\circ q_1\\\phi_{G_2}\circ g_1\circ p_1\\&=
-	\end{split}\]
-
-	\[\begin{split}
-		z_0\circ u_0&= t_0\circ v \circ u_0\\&=t_0\circ e_1\\&=i'_1\circ l_0\\ 	f'_0\circ z_0&=f'_0\circ t_0\circ v\\&=f'_0\circ \phi_{Q_0}\circ q_0\\&=a_0\circ q_0\\&=f_0\circ p_0
-	\end{split}\quad \begin{split}
-		z_1\circ u_1&=t_1\circ v\circ u_1\\&=t_1\circ e_1\\&=i'_0\circ r_1
-	\end{split} \quad \begin{split}
-	aaa	
-	\end{split}\]
-
-\end{proof}
-
-\subsection{Well-switching rewriting systems}
-
-\subsection{Abstract switches}
-We can now prove some properties relating switching and abstraction equivalence. As a first step we can show that switches along the same independence paire are unique up to abstraction equivalence.
-
-\todo{Unicità}
-
-\todo{switchabilità}
-
-\begin{definition}
-	contenuto...
-\end{definition}
-
-\begin{corollary}[Uniqueness of switches]\label{cor:switch}
-	\todo{switches}
-\end{corollary}
-
-Another useful property of switches is that they can be performed back and forth, giving back the original derivation. This is the content of the following two results.
-
-\todo{switch di switch}
-
-\begin{proposition}
-	contenuto...
-\end{proposition}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{corollary}
-	contenuto...
-\end{corollary}
-
-The fact that sequential independence implies switchability always
-holds for linear rules (see \Cref{prop:equi}). The result is so
-indispensable that typically, in the literature, it is not even
-stated, in the sense that switchability is not introduced
-axiomatically as in Definition~\ref{def:switch}, but it is based on
-the explicit construction of a switch.
-
-For left-linear rewriting systems
-sequential independence does not imply switchability (while the
-converse implication clearly holds), as shown by the next example.
-
-\begin{figure}
-
-	\begin{subfigure}{0.58\textwidth}
-		\xymatrix@C=20pt{
-			a \ar[d]_{\sqsubseteq} & a \ar[d]_{\sqsubseteq} \ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} & 
-			0 \ar@{>->}@/^.35cm/[drrr]|(.3)\hole^(.75){\id{0}}
-			\ar@{>->}[dr]|(.3)\hole_{\id{0}} &  &
-			a \ar@/_.35cm/[dlll]_(.75){\sqsubseteq}
-			\ar[dl]|(.3)\hole^{\sqsubseteq} & 
-			a \ar[d]^{\sqsubseteq}\ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} &
-			b \ar[d]_{\sqsubseteq}\\
-			c &
-			\ar@{>->}[l]^{\id{c}} c \ar[rr]_{\sqsubseteq}& &  0 &&
-			\ar@{>->}[ll]^{\id{0}} 0 \ar@{>->}[r]_{\id{0}}& 0
-		}
-		\caption{Two rewriting steps}
-		\label{fig:diff1:rew}
-	\end{subfigure}
-	\begin{subfigure}{0.20\textwidth}
-
-		\caption{No rewriting step}
-		\label{ex:diff1:no-step}
-	\end{subfigure}
-	\caption{Sequential independence does not imply switchability}
-	\label{fig:diff1} 
-\end{figure}
-
-The conditions guaranteeing switchability are inspired
-by the notion of \emph{canonical filler}
-\cite{heindel2009category}.
-
-\begin{definition}[Strong independence pair]
-	\label{def:filler}
-	Let $\X$ be an $\mathcal{M}$-adhesive category 
-	and $(\X, \R)$ a left-linear rewriting system. 
-	Let also $(i_0, i_1)$ be an independence pair between two direct
-	derivations $\dder{D}_0$, $\dder{D}_1$
-	as in the solid part of the diagram below
-	\[
-	\xymatrix@C=18pt@R=17pt{L_0 \ar[d]_{m_0}&& K_0
-		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} \ar@{.>}@/^.20cm/[ddrr]|(.32)\hole|(.57)\hole_(.7){u_0} & R_0
-		\ar@/^.35cm/[drrr]|(.3)\hole^(.2){i_0} \ar[dr]|(.3)\hole_{h_0}
-		&& L_1 \ar@/_.35cm/[dlll]_(.2){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
-		\ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} \ar@{.>}@/_.20cm/[ddll]|(.32)\hole|(.57)\hole^(.7){u_1} && R_1 \ar[d]^{h_1} \\
-		%
-		G_0 &&
-		\ar@{>->}[ll]^{f_0} D_0 \ar[rr]_(.3){g_0}&& G_1 &&
-		\ar@{>->}[ll]^(.3){f_1} D_1 \ar[rr]_{g_1}&& G_2\\
-		%
-		& & & & P \ar@/^.3cm/@{>.>}[ull]^{p_0} \ar@/_.3cm/@{.>}[urr]_{p_1}
-	}
-	\]
-
-	Consider the pullback of $g_0$ and $f_1$, which yields $p_i : P \to D_i$
-	for $i \in \{0,1\}$ and the mediating arrows $u_i\colon K_i\to P$ 
-	for $i \in \{0,1\}$ 
-	into the pullback object (see \Cref{prop:tec} for details). 
-	We say that $(i_0, i_1)$ is a \emph{strong independence pair} if
-	the first two squares depicted  
-	below are pushouts and if the pushout of $r_1 : K_1 \to R_1$ and $u_1 : K_1 \to P$ exists
-	\[
-	\xymatrix@R=16pt{
-		K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
-		\ar@{>->}[r]^{l_1} \ar[d]_{u_1}& L_1 \ar[d]^{i_1}
-		&K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1\ar@{.>}[d]^{j_0}
-		\\
-		P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0
-		& P \ar@{.>}[r]_{q_1} & Q_1
-	}
-	\]
-\end{definition}
-
-We can now prove a Local Church-Rosser Theorem for strong independence pairs.
-
-\begin{proposition}	\label{pr:church}
-	Let $(i_0, i_1)$ be a strong independence pair
-	between $\dder{D}_0$ and $\dder{D}_1$. Then $\dder{D}_0$ and
-	$\dder{D}_1$ are switchable.
-\end{proposition}
-
-The correspondence between sequential independence and switchability
-is fundamental. We name the class of rewriting systems where this property holds.
-
-\begin{definition}[Strong enforcing rewriting systems]
-	A left-linear rewriting system is \emph{strong enforcing} if
-	every independence pair between two direct derivations is strong.
-\end{definition}
-
-We can identify a large class of adhesive categories such that all
-left-linear rewriting systems over such categories are strong
-enforcing. This class includes $\cat{Set}$ and it is closed
-under comma and functor category constructions.  As such, it includes
-essentially all categories (e.g., presheaves over set) that are
-typically considered for modelling purposes. Notably, it contains the
-category $\cat{Graph}$ of directed graphs.
-This is a natural generalisation from adhesive to $\mathcal{M}$-adhesive categories of a class studied in \cite{baldan2011adhesivity} (see \Cref{app:fill} for details).
-
-Still, there are $\mathcal{M}$-adhesive rewriting systems that are not strong enforcing.
-
-\begin{example}[Non-strong enforcing left-linear rewriting system]
-	\label{ex:diff2}
-	In light of \Cref{pr:church}, \Cref{ex:diff1} provides an example of
-	an independence pair that is not strong. This gives an example of a
-	left-linear rewriting system in a $\mathcal{M}$-adhesive category that is quite
-	pathological since $\mathcal{M}=\mathsf{I(\X)}$. However, this is expected, 
-	since all natural examples seem to belong to the well-behaved class mentioned above. 
-\end{example}
-
-\begin{remark}
-	By \Cref{pr:church} the existence of a strong independence pair
-	entails switchability, which in turn entails sequential
-	independence by construction. Strong enforcing rewriting systems are exactly
-	those rewriting systems in which these three notions coincide.
-\end{remark}
-
-Consistency with the theory of linear rewriting systems is ensured by the fact that all linear rewriting systems are strong enforcing (see \cref{prop:equi}).
-
 Even if we work in strong enforcing rewriting systems where sequential
@@
 namely that there can be more than one independence pair between
-the same derivations (cfr. \Cref{rem:uni}). This hinders the very idea of using
-sequential independence as a basis of a theory of concurrency for
+the same derivations.
+
+This hinders the very idea of using sequential independence as a basis of a theory of concurrency for
 rewriting systems, since exchanges performed using different
@@
 \begin{example} 
-	Consider the derivation $\der{E}$ from Example~\ref{ex:seq-ind} (see Fig.~\ref{fi:derE}).
-	The last two steps are sequential independent, but one easily sees
+	Consider the rewriting system $(\cat{Graph}, \R)$ of \Cref{ex:1}, which,by the results of \Cref{app:fill} is strong enforcing.
+The last two steps of the derivation $\der{E}$ of  \Cref{ex:seq-ind} are sequentially independent, but one easily sees
 	that there are two distinct independence pairs, as the left-hand side
@@
 	$2$ in $D_1'$. Correspondingly, there
-	are two switches of $\der{E}$: one is the derivation $\der{D}$ in
-	Fig.~\ref{fi:derD} we started from, the other is the derivation
-	$\der{D}'$ in Fig.~\ref{fi:derD1}.
-
-	\begin{figure}
-%		\input{Figure/derD1.tex}
-		\caption{The derivation $\der{D}'$.}
-		\label{fi:derD1}
-	\end{figure}
-
-	As a consequence, $\der{D}$ and $\der{D}'$ would be switch
+	are two switches of $\der{E}$: one, by \Cref{cor:refl} is the derivation $\der{D}$ in \Cref{ex:1}
+	 we started from, the other is the derivation
+	$\der{D}'$ below.
+
+	  \begin{center}
+		\begin{tikzpicture}[node distance=2mm, font=\small, baseline=(current bounding box.center)]      
+			\node (L1) at (0,2) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {};
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node [right=of L1] (K1) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {};
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			%      \node [above=of K1] {$\rho_0$};
+			\node [above] at (K1.north) {$\rho_0$};
+			\node [right=of K1](R1) {
+				\begin{tikzpicture}
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {};
+					\node at (.5,0) [node, label=below:$2$] (2) {};
+					\draw[coloredge] (1) to[out=20, in=160] (2);
+					% 
+					\pgfBox
+				\end{tikzpicture}
+			};
+			\path (K1) edge[->] node[trans, above] {} (L1);
+			\path (K1) edge[->] node[trans, above] {} (R1);
+
+			\node at (4,2) (L2) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node [right=of L2] (K2) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {};
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			%      \node [above=of K2] {$\rho_1$};
+			\node [above] at (K2.north) {$\rho_1$};
+			\node [right=of K2] (R2) {
+				\begin{tikzpicture}
+					\node at (0,0) [node, label=below:$1$] (1) {}
+					edge [in=55, out=85, loop] ();        
+					% 
+					\pgfBox
+				\end{tikzpicture}
+			};
+			\path (K2) edge[->] node[trans, above] {} (L2);
+			\path (K2) edge[->] node[trans, above] {} (R2);
+
+			\node at (8,2) (L3) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node [right=of L3] (K3) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			%     \node [above=of K3] {$\rho_2$};
+			\node [above] at (K3.north) {$\rho_2$};
+			\node [right=of K3] (R3) {
+				\begin{tikzpicture}
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$12$] (12) {};
+					% 
+					\pgfBox
+				\end{tikzpicture}
+			};
+			\path (K3) edge[->] node[trans, above] {} (L3);
+			\path (K3) edge[->] node[trans, above] {} (R3);
+
+			%%%%%% second row
+			\node at (0,0) (G1) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {};
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node [right=of G1] (D1) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {};
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node at (3,0) (G2) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+					\draw[coloredge] (1) to[out=20, in=160] (2);
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\path (D1) edge[->] node[trans, above] {} (G1);
+			\path (D1) edge[->] node[trans, above] {} (G2);
+			\path (L1) edge[->] node[trans, above] {} (G1);
+			\path (K1) edge[->] node[trans, above] {} (D1);
+			\path (R1) edge[->] node[trans, above] {} (G2);
+
+			\node at (5,0) (D2) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {};
+					\node at (0,0) [node, label=below:$1$] (1) {} ;
+					\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+					\draw[coloredge] (1) to[out=20, in=160] (2);
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node at (7,0) (G3) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0.53) {}; 
+					\node at (0,0) [node, label=below:$1$] (1) {}
+					edge [in=55, out=85, loop] ();
+					\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+					\draw[coloredge] (1) to[out=20, in=160] (2);
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+
+			\path (D2) edge[->] node[trans, above] {} (G2);
+			\path (D2) edge[->] node[trans, above] {} (G3);
+			\path (L2) edge[->] node[trans, above] {} (G2);
+			\path (K2) edge[->] node[trans, above] {} (D2);
+			\path (R2) edge[->] node[trans, above] {} (G3);
+
+			\node at (9.46,0) (D3) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0) [node, label=below:$1$] (1) {}
+					edge [in=55, out=85, loop] ();
+					\node at (0.5,0) [node, label=below:$2$] (2) {} ;
+					\draw[coloredge] (1) to[out=20, in=160] (2);
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node [right=of D3] (G4) {
+				\begin{tikzpicture}
+					% 
+					\node at (0,0) [node, label=below:$12$] (12) {}
+					edge [in=55, out=85, loop] ()
+					edge [in=125, out=155, colorloop] ();
+					% 
+					\pgfBox
+				\end{tikzpicture} 
+			};
+			\node[font=\scriptsize, below] at (G1.south) {$G_0$};
+			\node[font=\scriptsize, below] at (D1.south) {$D_0$};      
+			\node[font=\scriptsize, below] at (G2.south) {$G_1$};
+			\node[font=\scriptsize, below] at (D2.south) {$D_1''$};      
+			\node[font=\scriptsize, below] at (G3.south) {$G_2''$};
+			\node[font=\scriptsize, below] at (D3.south) {$D_2''$};      
+			\node[font=\scriptsize, below] at (G4.south) {$G_3$};
+
+			\path (D3) edge[->] node[trans, above] {} (G3);
+			\path (D3) edge[->] node[trans, above] {} (G4);
+			\path (L3) edge[->] node[trans, above] {} (G3);
+			\path (K3) edge[->] node[trans, above] {} (D3);
+			\path (R3) edge[->] node[trans, above] {} (G4);
+		\end{tikzpicture}
+		%
+	\end{center}
+
+	As a consequence, $\der{D}$ and $\der{D}'$ would be
 	equivalent, but this is not acceptable when viewing equivalence
@@
 	first two steps are not sequential independent, while in $\der{D}'$
-	they are, intuitively because in $\der{D}$ rule $\rho_1$ uses the
+	they are. This happens because in $\der{D}$ rule $\rho_1$ uses the
 	node generated by $\rho_0$ (adding a self-loop to it), while in
 	$\der{D}'$ rule $\rho_1$ uses the node that was in the initial
-	graph. Also observe that the graphs $G_2$ and $G_2'$ produced after
-	two steps in $\der{D}$ and $\der{D'}$ are not isomorphic. From the
-	technical point of view, the property of being switch equivalent is
+	graph. We can also observe that the final graphs $G_2$ and $G_2'$ are not isomorphic.
+
+	From the technical point of view, the property of being switch equivalent is
 	not closed by prefix, and this prevents deriving a sensible
-	concurrent semantics: In fact
+	concurrent semantics: in fact
 	$\der{D} = \dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ and
@@
 
-Moreover, limiting sequential independence to the case in which the independence
-	pair is unique (as suggested in~\cite{baldan2017domains}) brings to the same problems.
+Moreover, limiting sequential independence to the case in which the independence pair is unique (as suggested in~\cite{baldan2017domains}) brings to the same problems.
 
@@
 
-Clearly, linear rewriting systems are well-switching (see Proposition~\ref{pr:weak}).
+\begin{remark}
+	From \Cref{rem:uni} and \Cref{prop:linstrong} it follows that linear rewriting systems are well-switching.
+\end{remark}
+
+\subsubsection{Equipping hypergraphs with equivalences}
+
 Moreover, we next observe that various classes of rewriting systems,
@@
 
+\todo{da fare}
 \subsubsection{Some examples of well-switching rewriting systems}
 
-\todo{Questa sezione è da riscrivere bene}
+\todo{Questa sezione è da riscrivere bene ma penso vada incorporata nella sez sui well.behaved}
 
@@
 
-As we mentioned, for linear rewriting systems
-it is canonical to identify
-derivations that are equal ``up to switching'', i.e.~that differ
-only in the order of independent steps. The same notion can be given
-for left-linear rewriting systems by relying on the notion of switch.
+Switch equivalence is now defined as the equivalence relating derivations that 
+can be obtained one from another by a sequence of switches. Moreover, intermediate graphs can be taken up to isomorphism according to abstraction equivalence.
+
+\todo{la definizione sotto è da sistemare}
+\begin{definition}[Concrete switching sequence]
+	\label{de:switch-equivalence}
+	Let $(\X, \R)$ be a left-linear rewriting system.  Let also
+	$\der{D}, \der{E} : G \Mapsto H$ be derivations with the same
+	length, $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and
+	$\der{E}=\{\dder{E}_{i}\}_{i=0}^n$. If
+	$\dder{D}_i \cdot \dder{D}_{i+1}$ is a switch of
+	$\dder{E}_i \cdot \dder{E}_{i+1}$ for some $i \in [0,n-1]$ and  $\dder{D}_j = \dder{E}_j$ for each $j \not \in \{i,i+1\}$ then we write
+	$\der{D} \shift{\transp{i}} \der{E}$. 
+	A \emph{concrere switching sequence} is a sequence $\{\der{D}_{k}\}_{k=0}^m$
+	of derivations such that
+	$\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
+	\shift{\nu_m} \der{D}_m$, where $\nu_{k}$ is the transposition $\transp{i_k}$.
+
+	Two derivations $\der{D}, \der{E}:G\Mapsto H$ are \emph{switch
+		equivalent}, written $\der{D}\equiv^{sh} \der{E}$, if there is a
+	switching sequence $\{\der{D}_{k}\}_{k=0}^m$ such that
+	\begin{itemize}
+		\item $\der{D}_0$ is $\der{D}$ and $\der{D}_m$ is $\der{E}$;
+		\item for every $i\in [0,m-1]$, $\der{D}_i \shift{\transp{h}}\der{D}_{i+1}$ for some $h\in [0, n-1]$.
+	\end{itemize}
+
+	To point out a chosen permutation of rewriting steps, we will also write $\der{D}\equiv^{sh}_{\sigma} \der{E}$, 
+	where $\sigma$ is the composition of the transposition appearing in a chosen switching sequence. 
+\end{definition}
+
+\begin{proposition}
+\todo{Se uso le stesse trasposizioni ho la stessa cosa}
+\end{proposition}
+\begin{proof}
+
+\end{proof}
+
+We can now  start by proving two globality results regarding the possibility of moving back and forth a direct derivation.
+
+\begin{lemma}[Globality of independence]
+	\label{lem:indep-global-left}
+	Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X,\R)$ a
+	well-switching rewriting system.  Let $\der{D}:=\{\dder{D}_i\}_{i=0}^2$  be a derivation of length $3$.
+	\begin{enumerate}
+		\item
+		\label{lem:indep-global-left:1} \emph{(Forward globality of independence)}.
+		If the first two direct derivations $\dder{D}_0$ and $\dder{D}_1$ are switchable and there is a
+		switching sequence
+		\[\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(1,2)}
+		\dder{D}_0 \cdot \dder{D}_2' \cdot \dder{D}_1' \shift{(0,1)}
+		\dder{D}_2'' \cdot \dder{D}_0' \cdot \dder{D}_1'\]
+		then
+		in the last derivation $\dder{D}_0'$ and $\dder{D}_1'$ are switchable;
+
+		\item
+		\label{lem:indep-global-left:2} \emph{(Backward globality of independence)}.
+		Suppose  that $\dder{D}_1$ and $\dder{D}_2$ are switchable and consider the switching sequence  $\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(1,2)}
+		\dder{D}_0 \cdot \dder{D}_2' \cdot \dder{D}_1'$ and suppose that $\dder{D}_0$ and $\dder{D}_2'$ are switchable.  If there
+		is a switching sequence
+		\[\dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2 \shift{(0,1)}
+		\dder{D}_1' \cdot \dder{D}_0' \cdot \dder{D}_2 \shift{(1,2)}
+		\dder{D}_1' \cdot \dder{D}_2' \cdot \dder{D}_0''\] 
+		then in the last derivation $\dder{D}_1'$ and $\dder{D}_2'$ are switchable.
+	\end{enumerate}
+\end{lemma}
+\begin{proof}
+
+			Since $(\X, \R)$ is well-switching, there exists unique independence pairs 
+		$(i_0,i_1)$ between $\dder{D}_0$ and $\dder{D}_1$,	$(a_0,a_1)$ between $\dder{D}_1$ and $\dder{D}_2$ and	$(e_0, e_1)$ between $\dder{D}_0$ and
+		$\dder{D}'_2$. 	By \Cref{rem:quadrati} we can build the diagram below, depicting the switch  along  $(i_0, i_1)$.
+		\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
+			\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
+			\ar[dl]_{m_1}\\&K_0\ar@{>->}[dr]^{k_0}\ar[dl]_{l_0}
+			\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){v_0}\ar[ur]^{r_0}&& G_1 &&
+			K_1
+			\ar@/^.6cm/[ddll]|(.36)\hole_(.65){v_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
+			\ar[dr]^{r_1}\\L_0
+			\ar@/_.6cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole
+			\ar[dr]^(.4){m_0}|(.61)\hole && D_0
+			\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1
+			\ar[dr]|(.4)\hole^(.65){g_1}
+			\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_(.4){h_1}|(.6)\hole\\&G_0
+			&&P_1\ar[dr]_{q_1}
+			\ar@{>->}[dl]^{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1
+			\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ
+				i_1}|(.61)\hole&&Q_0
+			\ar@{>->}[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0}
+			&&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar@{>->}[dl]|(.5)\hole_(.65){s_1}
+			&& R_0 \ar[ul]^(.35){g_1\circ
+				i_0}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\&K_1
+			\ar[ur]_{q_0\circ v_1} \ar[dr]_{r_1}
+			\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){v_1}&&H'_1&& K_0
+			\ar[ur]_{r_0} \ar[ul]^{q_1\circ v_0} \ar@{>->}[dl]^{l_0}
+			\ar@/_.6cm/[uull]^(.65){v_0}\\&& R_1
+			\ar[ur]_{\hspace{-6pt}s_1\circ
+				j_1}\ar@/^.8cm/[uurr]^(.2){j_1}&& L_0 \ar[ul]^{t_0\circ
+				j_0\hspace{-6pt}} \ar@/_.8cm/[uull]_(.2){j_0} |(.69)\hole
+		}	\]
+
+		Simlarly we have we have a diagram for the switch of $\dder{D}_1$ along $(a_0, a_1)$.
+		\[\xymatrix@C=15pt@R=15pt{&&R_1 \ar@/_.8cm/[ddrr]_(.2){a_0}|(.7)\hole
+			\ar[dr]^{h_1}&& L_2\ar@/^.8cm/[ddll]^(.2){a_1}
+			\ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar@{>->}[dl]_{l_1}
+			\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){u_1}\ar[ur]^{r_1}&& G_2 &&
+			K_2
+			\ar@/^.6cm/[ddll]|(.36)\hole_(.65){u_2}\ar[dl]_{k_2}\ar@{>->}[lu]_{l_2}
+			\ar[dr]^{r_2}\\L_1
+			\ar@/_.6cm/[ddrr]_(.2){b_0}|(.31)\hole|(.81)\hole
+			\ar[dr]^(.4){m_1}|(.61)\hole && D_1
+			\ar@{>->}[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2
+			\ar[dr]|(.4)\hole^(.65){g_2}
+			\ar@{>->}[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.6cm/[ddll]^(.2){b_1}|(.31)\hole|(.81)\hole\ar[dl]_(.4){h_2}|(.61)\hole\\&G_1
+			&&P_2\ar[dr]_{d_1}
+			\ar@{>->}[dl]^{d_0}\ar[ur]^(.4){c_1}\ar@{>->}[ul]_(.4){c_0}&&G_3\\L_2
+			\ar@/^.6cm/[uurr]^(.2){a_1} \ar[ur]_(.35){f_1\circ
+				a_1}|(.61)\hole&&Q_2
+			\ar@{>->}[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1}
+			&&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar@{>->}[dl]|(.5)\hole_(.65){x_2}
+			&& R_1 \ar[ul]^(.3){g_2\circ
+				a_0}|(.61)\hole\ar@/_.6cm/[uull]_(.2){a_0}\\&K_2
+			\ar[ur]_{d_0\circ u_2} \ar[dr]_{r_2}
+			\ar@{>->}[ul]^{l_2}\ar@/^.6cm/[uurr]_(.65){u_2}&&G'_2&& K_1
+			\ar[ur]_{r_1} \ar[ul]^{d_1\circ u_1} \ar@{>->}[dl]^{l_1}
+			\ar@/_.6cm/[uull]^(.65){u_1}\\&& R_2
+			\ar[ur]_{\hspace{-6pt}x_2\circ
+				b_1}\ar@/^.8cm/[uurr]^(.2){b_1}&& L_1 \ar[ul]^{y_1\circ
+				b_0\hspace{-7pt}} \ar@/_.8cm/[uull]_(.2){b_0} |(.69)\hole
+		}	\]
+
+		Finally, we have a third diagram built from the independence pair between $\dder{D}_0$ and $\dder{D}'_2$.
+\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){e_0}|(.7)\hole
+				\ar[dr]^{\hspace{-5pt}h_0}&& L_2\ar@/^.8cm/[ddll]^(.2){e_1}
+				\ar[dl]_{f_1\circ a_1\hspace{-5pt}}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
+				\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){w_0}\ar[ur]^{r_0}&& G_1 &&
+				K_2 \ar@/^.6cm/[ddll]|(.36)\hole_(.65){w_2}\ar[dl]_{d_0\circ
+					u_2\hspace{-5pt}}\ar@{>->}[lu]_{l_2} \ar[dr]^{r_2}\\L_0
+				\ar@/_.6cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole
+				\ar[dr]^(.4){m_0}|(.61)\hole && D_0
+				\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2
+				\ar[dr]|(.4)\hole^(.65){y_1}
+				\ar@{>->}[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.6cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.3){x_2\circ
+					b_1}|(.58)\hole \\&G_0 &&P_3\ar[dr]_{n_1}
+				\ar@{>->}[dl]^{n_0}\ar[ur]^(.4){\theta_1}\ar@{>->}[ul]_(.4){\theta_0}&&G'_2\\L_2
+				\ar@/^.6cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ
+					e_1}|(.61)\hole&&Q_4
+				\ar@{>->}[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0}
+				&&Q_5\ar[ur]|(.4)\hole^(.65){z'_1}
+				\ar@{>->}[dl]|(.5)\hole_(.65){z_1} && R_0 \ar[ul]^(.3){y_1\circ
+					e_0}|(.6)\hole\ar@/_.6cm/[uull]_(.2){e_0}\\&K_2
+				\ar[ur]_{\hspace{-2pt}n_0\circ w_2} \ar[dr]_{r_2}
+				\ar@{>->}[ul]^{l_2}\ar@/^.6cm/[uurr]_(.65){w_2}&&G'_1&& K_0
+				\ar[ur]_{r_0} \ar[ul]^{n_1\circ w_0} \ar[dl]^{l_0}
+				\ar@/_.6cm/[uull]^(.65){w_0}\\&& R_2
+				\ar[ur]_{\hspace{-4pt}z_1\circ
+					o_1}\ar@/^.8cm/[uurr]^(.2){o_1}&& L_0 \ar[ul]^{z'_0\circ
+					o_0\hspace{-7pt}} \ar@/_.8cm/[uull]_(.2){o_0} |(.69)\hole
+			}\]
+	\begin{enumerate}		
+		\item We have to construct the two dotted arrows in the diagram
+		below
+		\[\xymatrix@C=20pt@R=20pt{L_0 \ar[d]_{z'_0\circ o_0}&& K_0
+			\ar[d]_{n_1\circ w_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
+			\ar@{.>}@/^.25cm/[drrr]_(.4){\beta_0}|(.32)\hole
+			\ar[dr]|(.33)\hole_{y_1\circ e_0} && L_1
+			\ar@{.>}@/_.25cm/[dlll]^(.4){\beta_1}
+			\ar[dl]|(.33)\hole^{y_1\circ b_0}& K_1 \ar[d]^{d_1\circ
+				u_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ
+				a_1}\\G'_1 && \ar@{>->}[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2 &&
+			\ar@{>->}[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_3}\]
+
+		The arrows $i_0\colon R_0\to D_1$,
+		$e_0\colon R_0\to Q_2$, $i_1\colon L_1\to D_0$ and $b_0\colon L_1 \to Q_2$ satisfy
+		\[\begin{split}
+		f_1\circ i_0  &= h_0 \\&=x_1\circ e_0 
+		\end{split}
+		\qquad \begin{split}
+		g_0\circ i_1 &= m_1 \\&= x_1 \circ b_0 
+		\end{split}
+		\]
+
+		These identities entail the existence of the dotted
+		$\beta'_0\colon R_0\to P_2$ and $\beta'_1\colon L_1\to P_3$ below
+		\[\xymatrix{R_0 \ar@{.>}[dr]^{\beta'_0} \ar@/^.3cm/[drr]^{i_0}
+			\ar@/_.3cm/[ddr]_{e_0} &&& L_1 \ar@{.>}[dr]^{\beta'_1} \ar@/^.3cm/[drr]^{i_1}
+			\ar@/_.3cm/[ddr]_{b_0}\\ &P_2 \ar@{>->}[r]^{c_0} \ar@{>->}[d]_{d_0}& D_1
+			\ar@{>->}[d]^{f_1} & &P_3 \ar@{>->}[r]^{\theta_0} \ar[d]_{\theta_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar@{>->}[r]_{x_1} & G_1 & &Q_2\ar@{>->}[r]_{x_1} & G_1}\]
+
+		We can now define $\beta_0\colon R_0\to Q_3$ as $d_1\circ \beta'_1$ and $\beta_1\colon L_1\to Q_5$ as $n_1\circ \beta'_1$, so that
+		\[\begin{split}
+				x_2\circ \beta_0 & =x_2\circ d_2\circ \beta'_0 \\&= y_1\circ d_0\circ \beta'_0\\&=y_1\circ e_0
+		\end{split} \qquad \begin{split}
+z'_1 \circ \beta_1 & = z'_1 \circ n_1\circ \beta'_1\\& =y_1\circ \theta_1\circ \beta'_1\\&=y_1\circ b_0
+		\end{split}\]
+		Therefore, $(\beta_0, \beta_1)$ is the wanted independence pair.
+		\item Here we assume that
+		$\dder{D}_1$ and $\dder{D}_2$ are switchable  with an
+		independence pair $(\alpha_0, \alpha_1)$ and that
+		$\dder{D}_0$ and $S_{\alpha_0, \alpha_1}(\dder{D}_2)$ are switchable.
+		% 
+		Hence, in addition to the three diagrams above, we have a fourth one, depicted in \Cref{fi:fourth}.
+		\begin{figure}[h]
+			\centering
+			$\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){\alpha_0}|(.7)\hole \ar[dr]^{\hspace{-1pt}g_1\circ i_0}&& L_2\ar@/^.8cm/[ddll]^(.2){\alpha_1}  \ar[dl]_{m_2\hspace{-2pt}}\\
+				&K_0\ar[dr]^{\hspace{-4pt}q_1\circ v_0}\ar@{>->}[dl]_{l_0} \ar@/_.6cm/[ddrr]|(.36)\hole^(.65){\phi_0}\ar[ur]^{r_0}&& G_2 && K_2 \ar@/^.6cm/[ddll]|(.36)\hole_(.65){\phi_2}\ar[dl]_{k_2}\ar@{>->}[lu]_{l_2} \ar[dr]^{r_2}\\
+				L_0 \ar@/_.6cm/[ddrr]_(.2){\gamma_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){\hspace{-4pt}t_0\circ j_0}|(.6)\hole && Q_1 \ar@{>->}[dl]|(.4)\hole_(.65){s_1}\ar[ur]|(.5)\hole^(.7){t_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar@{>->}[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.6cm/[ddll]^(.2){\gamma_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){h_2}|(.6)\hole\\&H'_1 &&P_4\ar[dr]_{\lambda_1} \ar@{>->}[dl]^{\lambda_0}\ar[ur]^(.4){\zeta_1}\ar@{>->}[ul]_(.4){\zeta_0}&&G_3\\
+				L_2 \ar@/^.6cm/[uurr]^(.2){\alpha_1} \ar[ur]_(.35){\hspace{-2pt}s_1\circ
+					\alpha_1}|(.61)\hole&&Q_6
+				\ar@{>->}[ul]|(.4)\hole_(.6){\xi_0}\ar[dr]|(.5)\hole^(.65){\xi'_0}
+				&&Q_7\ar[ur]|(.4)\hole^(.6){\xi'_1}
+				\ar@{>->}[dl]|(.5)\hole_(.65){\xi_1} && R_0 \ar[ul]^(.35){g_2\circ
+					\alpha_0}|(.61)\hole\ar@/_.6cm/[uull]_(.2){\alpha_0}\\&K_2
+				\ar[ur]_{\lambda_0\circ \phi_2} \ar[dr]_{r_2}
+				\ar@{>->}[ul]^{l_2}\ar@/^.6cm/[uurr]_(.65){\phi_2}&&H'_2&& K_0
+				\ar[ur]_{r_0} \ar[ul]^{\lambda_1\circ \phi_0} \ar@{>->}[dl]^{l_0}
+				\ar@/_.6cm/[uull]^(.65){\phi_0}\\&& R_2
+				\ar[ur]_{\hspace{-5pt}\xi_1\circ
+					\gamma_1}\ar@/^.8cm/[uurr]^(.2){\gamma_1}&& L_0
+				\ar[ul]^{\xi'_0\circ \gamma_0\hspace{-7pt}}
+				\ar@/_.8cm/[uull]_(.2){\gamma_0} |(.69)\hole 
+			}	$
+			\caption{Picture for the proof of \Cref{lem:indep-global-left}: switch of $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$.}
+			\label{fi:fourth}
+		\end{figure}
+
+		Our aim is to construct the dotted arrows in the following diagram
+		\[\xymatrix@C=20pt@R=20pt{L_1 \ar[d]_{f_0\circ i_0}&& K_1
+			\ar[d]_{q_0\circ v_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1
+			\ar@{.>}@/^.35cm/[drrr]_(.4){\epsilon_0}|(.32)\hole
+			\ar[dr]|(.33)\hole_{s_1\circ j_1} && L_2
+			\ar@{.>}@/_.35cm/[dlll]^(.4){\epsilon_1}
+			\ar[dl]|(.33)\hole^{s_1\circ \alpha_1}& K_2
+			\ar[d]^{\lambda_0\circ \phi_2}\ar@{>->}[l]_{l_2} \ar[rr]^{r_2} &&
+			R_2 \ar[d]^{\xi_1\circ \gamma_1}\\G_0 && \ar@{>->}[ll]^{s_0} Q_0
+			\ar[rr]_{t_0}&& H'_1 && \ar@{>->}[ll]^{\xi_0} Q_6
+			\ar[rr]_{\xi'_0}&& H'_2}\]
+
+		We can take the arrows $j_1\colon R_1\to Q_1$, 
+		$a_0\colon R_1\to D_2$, $e_1\colon L_2 \to D_0$ and $a_1\colon L_2\to D_1$ and notice that
+		\[	f_2\circ a_0 =h_1 =t_1\circ j_1 \qquad   g_0\circ e_1=f_1\circ a_1\]
+		and thus we get the dotted arrows $\epsilon'_0\colon R_1\to P_4$, $\epsilon'_1\colon L_2\to P:1$ 
+		\[\xymatrix{R_1 \ar@{.>}[dr]^{\epsilon'_0} 
+			\ar@/^.3cm/[drr]^{j_1} \ar@/_.3cm/[ddr]_{a_0}&&& L_2 \ar@{.>}[dr]^{\epsilon'_1}
+			\ar@/^.3cm/[drr]^{a_1} \ar@/_.3cm/[ddr]_{e_0}\\ &P_4
+			\ar@{>->}[r]^{\zeta_0} \ar[d]_{\zeta_1}& Q_1 \ar[d]^{t_1} &&P_1
+			\ar[r]^{p_1} \ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\
+			&D_2\ar@{>->}[r]_{f_2} & G_2& 	&D_0\ar[r]_{g_0} & G_1} \]
+
+		Now, notice that
+		\[
+		t_1\circ q_1\circ \epsilon'_1  =g_1\circ p_1\circ \epsilon'_1  =g_1\circ a_1 =m_2
+		\]
+		Hence $(\alpha_0, q_1\circ \epsilon'_1)$ is an independence pair
+		for $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$. By hypothesis $(\X, \R)$ is well-switching and therefore
+		$q_1\circ \epsilon'_1$ must coincide with $\alpha_1$.
+
+		We can then define $\epsilon_0\colon R_1\to Q_6$ and $\epsilon_1\colon L_2\to Q_0$ to be, respectively, 
+		$\lambda_0\circ \epsilon'_0$ and $q_0\circ
+		\epsilon'_1$. Then for these  arrows we have  identities
+		\begin{align*}
+			\xi_0\circ \epsilon_0 & =\xi_0\circ \lambda_0\circ \epsilon'_0 =s_1\circ \zeta_0 \circ \epsilon'_0=s_1\circ j_1\\	t_0\circ \epsilon_1 & = t_0\circ q_0\circ \epsilon'_1 =s_1\circ q_1\circ \epsilon'_1=s_1\circ \alpha_1
+		\end{align*}
+		Allowing us to conclude that
+		$S_{i_0,i_1}(\dder{D}_1)$ and $S_{\alpha_0,
+			\alpha_1}(\dder{D}_2)$ are switchable.  \qedhere 
+	\end{enumerate}
+\end{proof}
+
+\todo{Consistent permutations from switchings}
+
+\todo{Lemma dei tre passi}
+
+\subsubsection{Abstract switches}
+
+\subsection{A canonical form for switching sequences}
 
@@
 
-Switch equivalence is now defined as the equivalence relating derivations that 
-can be obtained one from another by a sequence of switches. Moreover, intermediate graphs can be taken up to isomorphism according to abstraction equivalence.
-
-\begin{definition}[Switching sequence]
-	\label{de:switch-equivalence}
-	Let $(\X, \R)$ be a left-linear rewriting system.  Let also
-	$\der{D}, \der{E} : G \Mapsto H$ be derivations with the same
-	length, $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and
-	$\der{E}=\{\dder{E}_{i}\}_{i=0}^n$. If
-	$\dder{D}_i \cdot \dder{D}_{i+1}$ is a switch of
-	$\dder{E}_i \cdot \dder{E}_{i+1}$ for some $i \in [0,n-1]$ and  $\dder{D}_j = \dder{E}_j$ for each $j \not \in \{i,i+1\}$ then we write
-	$\der{D} \shift{\transp{i}} \der{E}$. 
-	A \emph{switching sequence} is a sequence $\{\der{D}_{k}\}_{k=0}^m$
-	of derivations such that
-	$\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
-	\shift{\nu_m} \der{D}_m$  with $\nu_{k} = \transp{i_k}$.
-
 Let us denote by $\nu_{k,h}$ the composition
@@
 for $\nu_{1,m}$.
-
-	Two derivations $\der{D}, \der{E}:G\Mapsto H$ are \emph{switch
-		equivalent}, written $\der{D}\equiv^{sh} \der{E}$, if there is a
-	switching sequence $\{\der{D}_{k}\}_{k=0}^m$ such that
-	$\der{D}\equiv_a \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2}
-	\ldots \shift{\nu_m} \der{D}_m \equiv _a \der{E}$.   
-	To point out a chosen permutation of rewriting steps, we will also write $\der{D}\equiv^{sh}_{\sigma} \der{E}$, 
-	where $\sigma$ is the composition of the transposition appearing in a chosen switching sequence. 
-\end{definition}
-
-\todo{Consistent permutations from switchings}
-
-\subsection{A canonical form for switching sequences}
 

### 2025-04-17 full_version/permutations.tex
switch

@@
 
+	Thus we conclude.
 \end{proof}
@@
 \begin{enumerate}
-	\item if  $(C, \{c_X\}_{X\in \Deltamin(\dder{D})})$ is colimiting for $F\circ I$, then there exists a colimiting cocone $(D, \{d_X\}_{X\in \Delta(\dder{D})})$ for $F$;
+	\item if  $(C, \{c_X\}_{X\in \Deltamin(\dder{D})})$ is a colimiting cocone for $F\circ I$, then there also exists a colimiting cocone $(D, \{d_X\}_{X\in \Delta(\dder{D})})$ for $F$;
 	\item $(C, \{c_X\}_{X\in \Deltamin(\dder{D})})$ and $(D, \{d_X\}_{X\in \Delta(\dder{D})})$ are colimiting for, respectively, $F\circ I$ and $F$, then the canonical arrow $\phi\colon C\to D$ induced by $(D, \{d_X\}_{X\in \Deltamin(\dder{D})})$ is an isomorphism.
@@
 \end{proof}
+
+\begin{remark}\label{rem:abscol}
+Another useful property is that the abstractly equivalent derivations yield isomorphic colimits.
+Indeed, let $\{\phi_X\}$ be an abstraction equivalence between $\der{D}$ and $\der{E}$ and for every $X\in \Deltamin(\der{D})$ denote by $X'$ the codomain of $\phi_X$.
+We can define $\Phi \colon \tpro{D}\to \lpro \der{E}\rpro$ and $\Theta \colon \lpro\der{E}\rpro \to \tpro{D}$ as the unique morphisms such that, for every $X\in \Deltamin(\der{D})$:
+\[\Phi \circ \iota_{\der{D},X}= \iota_{\der{E}, X'}\circ \phi_X \qquad \Theta \circ \iota_{\der{E}, X'}= \iota_{\der{D}, X}\circ \phi^{-1}_X \]
+
+If we compute we get:.
+\[\begin{split}
+	\Theta \circ \Phi \circ \iota_{\der{D}, X}&=\Theta \circ\iota_{\der{E}, X'}\circ \phi_X\\&=\iota_{\der{D}, X}\circ \phi^{-1}_X\circ \phi_X\\&=\iota_{\der{D}, X} 
+\end{split}\qquad \begin{split}
+	\Phi \circ \Theta \circ \iota_{\der{E}, X'}&=\Phi \circ \iota_{\der{D}, X}\circ \phi^{-1}_{X}\\&=\iota_{, \der{E}, X'}\circ \phi_X\circ \phi^{-1}_{X}\\&=\iota_{\der{E},X'}
+\end{split}\]
+
+Therefore, $\Phi$ is an isomorphism with inverse $\Theta$.
+\end{remark}
 
@@
 \begin{proof}
-	For every $X\in \Deltamin(\der{D}) $, let $X'$ the codomain of $\phi_X$.
-Then we can define $\xi_{\id{[0,l-1]}}\colon \tpro{D}\to \lpro \der{D}'\rpro$ as the unique morphism such that, for every $X\in \Deltamin(\der{D})$,
-	\[\xi_{\id{[0,l-1]}} \circ \iota_{X}= \iota'_{X'}\circ \phi_X\]
-
-As a first step we can notice that $\xi_{\id{[0,l-1]}}$ is an isomorphism: indeed we can define $\Theta\colon \lpro\der{D}'\rpro \to \tpro{D}$ as the unique arrow satisfying, for every $X'\in \Deltamin(\der{D}')$
-\[\Theta \circ \iota'_{X'}= \iota_{X}\circ \phi^{-1}_X\]
-
-From the following two computations we can derive that $\Theta$ is the inverse of $\xi_{\id{[0,l-1]}}$.
-\[\begin{split}
-	\Theta \circ \xi_{\id{[0,l-1]}}\circ \iota_{X}&=\Theta \circ\iota'_{X'}\circ \phi_X\\&=\iota_{X}\circ \phi^{-1}_X\circ \phi_X\\&=\iota_X 
-\end{split}\qquad \begin{split}
-\xi_{\id{[0,l-1]}}\circ \Theta \circ \iota'_{X'}&=\xi_{\id{[0,l-1]}}\circ \iota_X\circ \phi^{-1}_{X}\\&=\iota'_{X'}\circ \phi_X\circ \phi^{-1}_{X}\\&=\iota'_{X'}
-\end{split}\]
-
-To conclude, let us observe that all the internal subdiagrams of the following diagrams commutes, guaranteeing the commutativity of the full ones.
+By \Cref{rem:abscol} we know that there is an isomorphism  $\xi_{\id{[0, l-1]}}\colon \tpro{D}\to \lpro \der{D}'\rpro$.
+We can notice that all the internal subdiagrams of the following diagrams commutes, guaranteeing the commutativity of the full ones.
 \[\xymatrix@C=30pt{\pi(G_0)\ar[r]^{\alpha} \ar[d]_{\alpha'} & G_0 \ar[dl]^{\phi_{G_0}} \ar[r]^{\iota_{G_0}} &\tpro{D} \ar[d]^{\xi_{\id{[0, l-1]}}}\\ G'_0 \ar[rr]_{\iota'_{G'_0}} & &\lpro \der{D}' \rpro}\]

### 2025-04-17 full_version/esempi.tex
aggiunto capitolo

--- 2025-03-21 full_version/leftlinear.tex
@@
-% !TeX root = ./fusione.tex
+\chapter{Some examples of well-switching rewriting systems}
 
-\chapter{Independence in rewriting}
+\subsubsection{Some examples of well-switching rewriting systems}
 
-In this chapter we discuss the notion of independence between two
-consecutive rewriting steps, a fundamental ingredient of the rewriting
-theory, which comes into play when viewing a sequence of steps as a
-concurrent computation. We observe that moving from linear to
-left-linear rules leads to the failure of various basic properties of
-the classical notion of independence used in the linear setting and we
-single out a framework in which these can be re-established, possibly
-in a weakened form.
+\subsubsection{Equipping hypergraphs with equivalences}
 
-\section{Sequentially independent and switchable derivations }\label{subsec:switch}
-
-Sequential independence is the canonical notion of independence in the DPO approach.
-
-\begin{definition}[Sequential independence]
-	\label{de:sequential-independence}
-	Let $\X$ be an $\mathcal{M}$-adhesive category 
-	and $(\X, \R)$ a left-linear rewriting system. 
-	Let also
-	$\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation of length $2$, with
-	$\dder{D}_i$ using rule $\rho_i = (l_i,r_i)$.  We say that $\dder{D}_0$ and
-	$\dder{D}_1$ are
-	\emph{sequentially independent}
-	if there is a pair of arrows
-	$i_0\colon R_0\to D_1$ and $i_1\colon L_1\to D_0$ such that the
-	following diagram commutes. In this case $(i_0,i_1)$ is called an  \emph{independence
-		pair}.
-	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
-		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
-		\ar@{.>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
-		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{.>}@/_.25cm/[dlll]^(.4){i_1}
-		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
-		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
-		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
-		\ar[rr]_{g_1}&& G_2}
-	\]
-\end{definition}
-
-\begin{remark}\label{rem:seqabs}
-Let $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ be an abstraction equivalence between $\der{D}=\{\dder{D}_i\}_{i=0}^1$ and $\der{D}'=\{\dder{D}'_i\}_{i=0}^1$.
-If there is an independence pair between $(i_0, i_1)$ between $\dder{D}_0$ and $\dder{D}_1$, then $(\phi_{D_0}\circ i_1, \phi_{D_1}\circ i_0)$ is an independence pair between $\dder{D}'_0$ and $\dder{D}'_1$.
-Indeed we have
-\[\begin{split}
-g'_0\circ \phi_{D_0}\circ i_1&=\phi_{G_1}\circ g_0\circ i_1\\&=\phi_{G_1}\circ m_1\\&= m'_1
-\end{split}\qquad \begin{split}
-f'_1\circ \phi_{D_1}\circ i_0&=\phi_{G_1}\circ f_1\circ i_0\\&=\phi_{G_1}\circ h_0\\&= h'_1
-\end{split}\]
-\end{remark}
-
-\begin{remark}\label{rem:uni}
-	It is worth mentioning that if $(\X, \R)$ is a linear rewriting system then two derivations $\dder{D}_0$ and $\dder{D}_1$ can have at most one independence pair.
-Indeed if $(i_0,i_1)$ and $(i'_0, i'_1)$ are independence pairs, then
-	\[g_0\circ i_1 = g_0\circ i'_1 \qquad f_1\circ i_0=f_1\circ i'_0\]
-	But in linear systems $g_0$ and $f_1$ are both monos, entailing $i_0=i'_0$ and $i_1=i'_1$.
-\end{remark}
-
-Intuitively, the existence of the independence pair
-captures the possibility of switching the application of the two rules:
-$f_0 \circ i_1$ is a match for $\rho_1$ in $G_0$ and the
-existence of $i_0 : R_0 \to D_1$ means that $\rho_1$ does not delete
-items in the image of $K_0$, thus $\rho_0$ can be applied after
-$\rho_1$. The following definition formalise what it means for a derivation to be the switch of another.
-
-\begin{definition}[Pre-switch] \label{def:switch}
-	Let $\X$ be an $\mathcal{M}$-adhesive category 
-	and $(\X, \R)$ a left-linear rewriting system. 
-	Let also
-	$\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation made
-	of two sequentially independent derivations $\dder{D}_0$,
-	$\dder{D}_1$ with independence pair $(i_0, i_1)$, as in the following diagram. 
-		\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
-		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
-		\ar@{>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
-		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{>}@/_.25cm/[dlll]^(.4){i_1}
-		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
-		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
-		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
-		\ar[rr]_{g_1}&& G_2}
-	\]
-
-	A \emph{pre-switch} of $\der{D}$ along $(i_0,i_1)$ is
-	a derivation $\der{E}=\{\dder{E}_i\}_{i=0}^1$, between the same objects and using the same rules
-	in reverse order, as in the diagram on the right below
-	\[
-	\xymatrix@R=20pt@C=20pt{
-		{L_1} \ar[d]_{m_0'}
-		&&  {K_1} \ar@{>->}[ll]_{l_1} \ar[r]^{r_1} \ar[d]_{k_0'}
-		&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{.>}_(.4){i_0'}|(.32)\hole[drrr]
-		& & 
-		{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{.>}^(.4){i_1'}[dlll] 
-		&  {K_0} \ar@{>->}[l]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
-		& & {R_0} \ar[d]^{h_1'} \\		
-		{G_0}
-		& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rr]_{g_0'}
-		& &  {G'_1} 
-		& &  {D_1'} \ar@{>->}[ll]^{f_1'} \ar[rr]_{g_1'}
-		& & {G_2}  }
-	\]
-	such that there is an independence pair $(i_0', i_1')$ between
-	$\dder{E}_0$ and $\dder{E}_1$ and 
-	\begin{center}   
-		$m_0=f_0' \circ i_1'$
-		\qquad $h_1=g_1' \circ i_0'$
-		\qquad $m_0'= f_0 \circ i_1$
-		\qquad $h_1'= g_{1}\circ i_0$.
-	\end{center}
-
-\end{definition}
-
-\begin{example}	\label{ex:seq-ind}
-	Consider the rewriting system  $(\cat{Graph}, \R)$ and the derivation $\der{D}$ introduced in \Cref{ex:1}.	Steps $\dder{D}_1$ and $\dder{D}_2$ are clearly sequential
-	independent via the arrows $R_1 \to D_2$, $L_2 \to D_1$
-	mapping nodes according to their numbering.
-
-	A pre-switch of $\der{D}$ along such independence pair is the derivation
-	$\der{E}$ depicted below. Instead,  the first two
-	steps $\dder{D}_0$ and $\dder{D}_1$ are not sequential independent. Intuitively, this happens because $\rho_1$ uses the node generated by $\rho_0$ to produce a self-loop.
-\begin{center}
-	\begin{tikzpicture}[node distance=2mm, font=\small,  baseline=(current bounding box.center)]      
-		\node (L1) at (0,2) {
-			\begin{tikzpicture}
-				% 
-				\node at (0,0.53) {};
-				\node at (0,0) [node, label=below:$1$] (1) {} ;
-				% 
-				\pgfBox
-			\end{tikzpicture} 
-		};
-		\node [right=of L1] (K1) {
-			\begin{tikzpicture}
-				% 
-				\node at (0,0.53) {}; 
-				\node at (0,0) [node, label=below:$1$] (1) {};
-				% 
-				\pgfBox
-			\end{tikzpicture} 
-		};
-		%     \node [above=of K1] {$\rho_0$};
-		\node [above] at (K1.north) {$\rho_0$};
-		\node [right=of K1](R1) {
-			\begin{tikzpicture}
-				\node at (0,0.53) {}; 
-				\node at (0,0) [node, label=below:$1$] (1) {};
-				\node at (.5,0) [node, label=below:$2$] (2) {}; 
-				\draw[coloredge] (1) to[out=20, in=160] (2);
-				% 
-				\pgfBox
-			\end{tikzpicture}
-		};
-		\path (K1) edge[->] node[trans, above] {} (L1);
-		\path (K1) edge[->] node[trans, above] {} (R1);
-
-		\node at (4,2) (L3) {
-			\begin{tikzpicture}
-				% 
-				\node at (0,0.53) {}; 
-				\node at (0,0) [node, label=below:$1$] (1) {} ;
-				\node at (0.5,0) [node, label=below:$2$] (2) {} ;
-				% 
-				\pgfBox
-			\end{tikzpicture} 
-		};
-		\node [right=of L3] (K3) {
-			\begin{tikzpicture}
-				% 
-				\node at (0,0.53) {}; 
-				\node at (0,0) [node, label=below:$1$] (1) {} ;
-				\node at (0.5,0) [node, label=below:$2$] (2) {} ;
-				% 
-				\pgfBox
-			\end{tikzpicture} 
-		};
-		%     \node [above=of K3] {$\rho_2$};
-		\node [above] at (K3.north) {$\rho_2$};
-		\node [right=of K3] (R3) {
-			\begin{tikzpicture}
-				\node at (0,0.53) {}; 
-				\node at (0,0) [node, label=below:$12$] (12) {};
-				% 
-				\pgfBox
-			\end{tikzpicture}
-		};
-		\path (K3) edge[->] node[trans, above] {} (L3);
-		\path (K3) edge[->] node[trans, above] {} (R3);
-
-		\node at (8,2) (L2) {
-			\begin{tikzpicture}
-				% 
-				\node at (0,0.53) {}; 
-				\node at (0,0) [node, label=below:$2$] (1) {} ;
-				% 
-				\pgfBox
-			\end{tikzpicture} 
-		};
-		\node [right=of L2] (K2) {
-			\begin{tikzpicture}
-				% 
-				\node at (0,0.53) {}; 
-				\node at (0,0) [node, label=below:$2$] (1) {};
-				% 
-				\pgfBox
-			\end{tikzpicture} 
-		};
-		%     \node [above=of K2] {$\rho_1$};
-		\node [above] at (K2.north) {$\rho_1$};
-
-		\node [right=of K2] (R2) {
-			\begin{tikzpicture}
-				\node at (0,0) [node, label=below:$2$] (1) {}
-				edge [in=55, out=85, loop] ();
-				% 
-				\pgfBox
-			\end{tikzpicture}
-		};
-		\path (K2) edge[->] node[trans, above] {} (L2);
-		\path (K2) edge[->] node[trans, above] {} (R2);
-
-		%%%%%% second row
-		\node at (0,0) (G1) {
-			\begin{tikzpicture}
-				% 
-				\node at (0,0.53) {};
-				\node at (0,0) [node, label=below:$1$] (1) {} ;
-				% 
-				\pgfBox
-			\end{tikzpicture} 
-		};
-		\node [right=of G1] (D1) {
-			\begin{tikzpicture}
-				% 
-				\node at (0,0.53) {}; 
-				\node at (0,0) [node, label=below:$1$] (1) {};
-				% 
-				\pgfBox
-			\end{tikzpicture} 
-		};
-		\node at (3,0) (G2) {
-			\begin{tikzpicture}
-				% 
-				\node at (0,0.53) {}; 
-				\node at (0,0) [node, label=below:$1$] (1) {} ;
-				\node at (0.5,0) [node, label=below:$2$] (2) {} ;
-				\draw[coloredge] (1) to[out=20, in=160] (2);
-				% 
-				\pgfBox
-			\end{tikzpicture} 
-		};
-		\path (D1) edge[->] node[trans, above] {} (G1);
-		\path (D1) edge[->] node[trans, above] {} (G2);
-		\path (L1) edge[->] node[trans, above] {} (G1);
-		\path (K1) edge[->] node[trans, above] {} (D1);
-		\path (R1) edge[->] node[trans, above] {} (G2);
-
-		\node at (5.5,0) (D2) {
-			\begin{tikzpicture}
-				% 
-				\node at (0,0.53) {};
-				\node at (0,0) [node, label=below:$1$] (1) {} ;
-				\node at (0.5,0) [node, label=below:$2$] (2) {} ;
-				\draw[coloredge] (1) to[out=20, in=160] (2);
-				% 
-				\pgfBox
-			\end{tikzpicture} 
-		};
-		\node at (7.4,0) (G3) {
-			\begin{tikzpicture}
-				% 
-				\node at (0,0.53) {}; 
-				\node at (0,0) [node, label=below:$12$] (12) {}
-				edge [in=125, out=155, colorloop] ();
-				% 
-				\pgfBox
-			\end{tikzpicture} 
-		};
-
-		\path (D2) edge[->] node[trans, above] {} (G2);
-		\path (D2) edge[->] node[trans, above] {} (G3);
-		\path (L3) edge[->] node[trans, above] {} (G2);
-		\path (K3) edge[->] node[trans, above] {} (D2);
-		\path (R3) edge[->] node[trans, above] {} (G3);
-
-		\node at (9.1,0) (D3) {
-			\begin{tikzpicture}
-				% 
-				\node at (0,0.53) {}; 
-				\node at (0,0) [node, label=below:$12$] (12) {}
-				edge [in=125, out=155, colorloop] ();
-				% 
-				\pgfBox
-			\end{tikzpicture} 
-		};
-		\node [right=of D3] (G4) {
-			\begin{tikzpicture}
-				% 
-				\node at (0,0) [node, label=below:$12$] (12) {}
-				edge [in=55, out=85, loop] ()
-				edge [in=125, out=155, colorloop] ();
-				% 
-				\pgfBox
-			\end{tikzpicture} 
-		};
-
-		\node[font=\scriptsize, below] at (G1.south) {$G_0$};
-		\node[font=\scriptsize, below] at (D1.south) {$D_0$};      
-		\node[font=\scriptsize, below] at (G2.south) {$G_1$};
-		\node[font=\scriptsize, below] at (D2.south) {$D_1'$};      
-		\node[font=\scriptsize, below] at (G3.south) {$G_2'$};
-		\node[font=\scriptsize, below] at (D3.south) {$D_2'$};      
-		\node[font=\scriptsize, below] at (G4.south) {$G_3$};
-
-		\path (D3) edge[->] node[trans, above] {} (G3);
-		\path (D3) edge[->] node[trans, above] {} (G4);
-		\path (L2) edge[->] node[trans, above] {} (G3);
-		\path (K2) edge[->] node[trans, above] {} (D3);
-		\path (R2) edge[->] node[trans, above] {} (G4);
-	\end{tikzpicture}
-	%
-\end{center}
-	\end{example}
-
-\begin{remark}\label{rem:switch}
-
-Let $\der{E}=\{\dder{E}_i\}_{i=0}^1$ be a pre-switch for $\dder{D}_0$
-and $\dder{D}_1$ along an independence pair $(i_0, i_1)$, then by definition we have an independence pair $(i'_0, i'_1)$ between $\dder{E}_0$ and $\dder{E}_1$ such that
-\[
-m_0=f_0' \circ i_1'
-\quad h_1=g_1' \circ i_0'
-\quad m_0'= f_0 \circ i_1
-\quad h_1'= g_{1}\circ i_0\]
-
- The derivation $\der{D}$ uses the same rule of $\der{E}$ in reverse order, thus it is a switch for $\der{E}$ along $(i_0', i_1')$.
-Moreover, the same argument shows that if $(\der{E}, \alpha, \omega)$ is a decorated switch for $(\der{D}, \alpha, \omega)$ along $(i_0, i_1)$, then the latter is a decorated switch for the former along $(i'_0, i'_1)$.
-\end{remark}
-
-A first property of pre-switches is that they are unique up to abstraction equivalence.
-
-\begin{lemma}[Uniqueness of pre-switches]
-	\label{thm:switch_uni}
-	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation and suppose
-	that both $\der{E}=\{\dder{E}_i\}_{i=0}^1$ and
-	$\der{F}=\{\dder{F}_i\}_{i=0}^1$ are pre-switches of $\dder{D}_0$ and
-	$\dder{D}_1$ along the same independence pair $(i_0, i_1)$.
-Then there is a unique abstraction equivalence $\{\phi_X\}_{X\in \Deltamin(\der{E})}$ between $\der{E}$ and $\der{F}$, whose first component is $\id{G_0}$.
-Moreover,
-	\[\phi_{D_{\der{E}, 0}}\circ j_1=a_1 \qquad \phi_{D_{\der{E}, 1}}\circ j_0=a_0\]
-\end{lemma}
-
-\begin{proof}
-	By definition of pre-switch $\der{E}_0$ and $\der{F}_0$ have the same match $f_0\circ i_1$ and that $\der{E}_1$ and $\der{F}_1$ have the same comatch $g_1\circ i_0$.
-Thus we get the solid part of the diagram below.
-If we are able to construct the dotted arrow and prove that they are isomorphism we are done.
-	\[\xymatrix@C=22pt{G_{0} && \ar@{>->}[ll]_{f_{\der{F},0}} D_{\der{F},0} \ar[rr]^{g_{\der{F},0}}&& G_{\der{F},1} && \ar@{>->}[ll]_{f_{\der{F},1}} D_{\der{F},1} \ar[rr]^{g_{\der{F},1}}&& G_{2}\\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}&& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_{1} \ar@/^.35cm/[drrr]|(.315)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{h_{\der{E},0}} \ar@/_.35cm/[urrr]|(.315)\hole^(.4){a_0} \ar[ur]|(.3)\hole^{h_{\der{F},0}}& &L_{0} \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{m_{\der{E},1}} \ar@/^.35cm/[ulll]_(.4){a_1} \ar[ul]|(.3)\hole_{m_{\der{F},1}}& K_{0} \ar[d]_{k_{\der{E},1}} \ar[u]^{k_{\der{F},1}}\ar@{>->}[l]_{l_{0}} \ar[rr]^{r_0} && R_{0} \ar[d]_{g_1\circ i_0} \ar[u]^{g_1\circ i_0}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} && \ar[ll]^{f_{\der{E},0}} D_{\der{E},0} \ar@{.>}@/^.5cm/[uu]^(.33){\phi_{0}}|\hole \ar[rr]_{g_{\der{E},0}}&& G_{\der{E},1} \ar@{.>}[uu]^(.76){\psi_1}|(.45)\hole |(.55)\hole&& \ar@{>->}[ll]^{f_{\der{E},1}} D_{\der{E},1} \ar@{.>}@/_.5cm/[uu]_(.33){\phi_{1}}|\hole\ar[rr]_{g_{\der{E},1}}&& G_{2}\ar@{.>}@/_.5cm/[uu]_{\psi_2}}\]
-
-	Now, by \Cref{prop:unique} we know that there are two unique isomorphisms $\phi_0\colon D_{\der{E},0}\to D_{\der{F},0}$ and $\psi_1 \colon G_{\der{E},1}\to G_{\der{F},1}$ such that the diagram below commutes.
-	\[\xymatrix{G_{0} & \ar@{>->}[l]_{f_{\der{F},0}} D_{\der{F},0} \ar[r]^{g_{\der{F},0}}& G_{\der{F},1} \\L_1 \ar[d]^{f_0\circ i_1} \ar[u]_{f_0\circ i_1}& K_{1} \ar[d]^{k_{\der{E},0}} \ar[u]_{k_{\der{F},0}}\ar[l]_{l_1} \ar[r]^{r_1} & R_{1}  \ar[d]_{h_{\der{E},0}}  \ar[u]^{h_{\der{F},0}}\\ \ar@/^.5cm/[uu]^{\id{G_0}} G_{0} & \ar@{>->}[l]^{f_{\der{E},0}} D_{\der{E},0} \ar@/^.5cm/[uu]^(.33){\phi_{0}}|\hole \ar[r]_{g_{\der{E},0}}& G_{\der{E},1} \ar@/_.5cm/[uu]_{\psi_1}}\]
-
-	But then we have
-	\begin{align*}
-		f_{\der{F},0}\circ \phi_0\circ j_1&=f_{\der{E},0} \circ j_1\\&=m_0\\&=f_{\der{F},0}\circ a_1 \end{align*}
-	which, since $f_{\der{D},0}$ is mono, entails $a_1= \phi_0\circ j_1$.	This equality, in turn, gives us that
-	\begin{align*}
-		\psi_1\circ m_{\der{E},1}&=\psi_1 \circ g_{\der{E},0}\circ j_1\\&=g_{\der{F},0}\circ \phi_0\circ j_1\\&=g_{\der{F},0}\circ a_1\\&=m_{\der{F},1}
-	\end{align*}
-
-	Since $\psi_1$ is an isomorphism, the square below is a pushout. 
-	\[\xymatrix@C=35pt{K_0 \ar[d]_{k_{\der{E},1}} \ar@{>->}[r]^{l_0}& L_0 \ar[d]^{\psi_1\circ m_{\der{E},1}}\\D_{\der{E},1} \ar@{>->}[r]_{\psi_1\circ f_{\der{E},1}}& G_{\der{F}, 1}}\]
-
-	Moreover, we have already shown that $\psi_1\circ m_{\der{E},1}=m_{\der{F},1}$.
-Thus, again by \Cref{prop:unique} there are the dotted isomorphisms $\phi_1\colon D_{\der{E},1}\to D_{\der{F},1}$ and $\psi_2\colon G_2\to G_2$ in the diagram below and such arrows are unique.
-	\[\xymatrix{G_{\der{F},1} & \ar@{>->}[l]_{f_{\der{F},1}} D_{\der{F},1} \ar[r]^{g_{\der{F},1}}& G_2 \\L_0 \ar[d]^{m_{\der{E},1}} \ar[u]_{m_{\der{F},1}}& K_{0} \ar[d]^{k_{\der{E},1}} \ar[u]_{k_{\der{F},1}}\ar@{>->}[l]_{l_1} \ar[r]^{r_1} & R_{0}  \ar[d]_{g_1\circ i_0}  \ar[u]^{g_1\circ i_0}\\ \ar@/^.5cm/[uu]^{\psi_1} G_{\der{E},1} & \ar@{>->}[l]^{f_{\der{E},1}} D_{\der{E},1} \ar@{.>}@/^.5cm/[uu]^(.33){\phi_{1}}|\hole \ar[r]_{g_{\der{E},1}}& G_2 \ar@{.>}@/_.5cm/[uu]_{\psi_2}}\]
-
-	To conclude, it is now enough to notice that
-	\begin{align*}
-		f_{\der{F},1} \circ \phi_1\circ j_0&=\psi_1\circ f_{\der{E},1}\circ j_0\\&=\psi_1\circ h_{\der{E,0}}\\&=h_{\der{F},0}\\&=f_{\der{F},1}\circ a_0
-	\end{align*}
-	allowing us to deduce $ \phi_1\circ j_0=a_0$.
-\end{proof}
-
-\begin{example}\label{ex:abs}
-	Let $\X$ be the category of $\Set$ and, besides the terminal obect $1$, take the sets
-	\[2=\{0,1\} \qquad 3=\{0,1,2\} \qquad 4=\{0,1,2,3\}\]
-
-Let us consider the DPO-rewriting system given by the (linear) rules below.
-		\[\xymatrix{1 & 1\ar@{>->}[l]_{\id{1}} \ar@{>->}[r]^{\id{1}} & 1 & 1 & 1\ar@{>->}[r]^{\delta^2_0} \ar@{>->}[l]_{\id{1}} & 2}\]
-
-We then have the derivation $\der{D}$ below, composed by two sequentially independent steps.
-		\[\xymatrix@R=20pt@C=20pt{1 \ar@{>->}[d]_{\delta^3_0}&& 1
-	\ar@{>->}[d]_{\delta^3_0}\ar@{>->}[ll]_{\id{1}} \ar@{>->}[r]^{\id{1}} & 1
-	\ar@{>->}@/^.25cm/[drrr]|(.32)\hole_(.4){\delta^3_0}
-	\ar[dr]|(.33)\hole_{\delta^3_0} && 1 \ar@{>->}@/_.25cm/[dlll]^(.4){\delta^3_0}
-	\ar@{>->}[dl]|(.33)\hole^{\delta^3_0}& 1 \ar@{>->}[d]^{\delta^3_0}\ar@{>->}[l]_{\id{1}}
-	\ar@{>->}[rr]^{\delta^2_0} && 2 \ar@{>->}[d]^{i_2}\\3 && \ar@{>->}[ll]^{\id{3}}
-	3 \ar@{>->}[rr]_{\id{3}}&& 3 && \ar@{>->}[ll]^{\id{3}} 3
-	\ar@{>->}[rr]_{i_3}&& 4}
-\]
-where $i_3\colon 3\mto 4$ is the obvious inclusion, while $i_2\colon 2\mto 4$ sends $0$ to $0$ and $1$ to $3$.	 Now, we can construct two pre-switches for $\dder{D}_0$ and $\dder{D}_1$ along $(\delta_0, \delta_0)$.
-Indeed, on the one hand we can consider  $\der{E}:=\{\dder{E}_i\}_{i=0}^1$ as
-		\[\xymatrix@R=20pt@C=20pt{1 \ar@{>->}[d]_{\delta^3_0}&& 1
-	\ar@{>->}[d]_{\delta^3_0}\ar@{>->}[ll]_{\id{1}} \ar@{>->}[r]^{\delta^2_0} & 2
-	\ar@{>->}@/^.25cm/[drrr]|(.32)\hole_(.4){i_2}
-	\ar[dr]|(.33)\hole_{i_2} && 1 \ar@{>->}@/_.25cm/[dlll]^(.4){\delta^3_0}
-	\ar@{>->}[dl]|(.33)\hole^{\delta^4_0}& 1 \ar@{>->}[d]^{\delta^4_0}\ar@{>->}[l]_{\id{1}}
-	\ar@{>->}[rr]^{\id{1}} && 1 \ar@{>->}[d]^{\delta^4_0}\\3 && \ar@{>->}[ll]^{\id{3}}
-	3 \ar@{>->}[rr]_{i_{3}}&& 4 && \ar@{>->}[ll]^{\id{4}} 4
-	\ar@{>->}[rr]_{\id{4}}&& 4}
-\]
-and we have
-\[
-\delta^3_0=\id{3} \circ \delta^3_0
-\qquad i_2=\id{4} \circ i_2
-\qquad \delta^3_0= \id{3} \circ \delta^3_0
-\qquad \delta^4_0= i_3\circ \delta^3_0\]
-
-On the other hand, there is an isomorphism $t\colon 4\mto 4$ be the isomorphism which swap $1$ with $2$ and fix the other elements of $4$.
-Then we can also construct $\der{F}:=\{\dder{F}_i\}_{i=0}^1$ as below:
-		\[\xymatrix@R=20pt@C=20pt{1 \ar@{>->}[d]_{\delta^3_0}&& 1
-		\ar@{>->}[d]_{\delta^3_0}\ar@{>->}[ll]_{\id{1}} \ar@{>->}[r]^{\delta^2_0} & 2
-		\ar@{>->}@/^.25cm/[drrr]|(.32)\hole_(.4){i_2}
-		\ar[dr]|(.33)\hole_{i_2} && 1 \ar@{>->}@/_.25cm/[dlll]^(.4){\delta^3_0}
-		\ar@{>->}[dl]|(.33)\hole^{\delta^4_0}& 1 \ar@{>->}[d]^{\delta^4_0}\ar@{>->}[l]_{\id{1}}
-		\ar@{>->}[rr]^{\id{1}} && 1 \ar@{>->}[d]^{\delta^4_0}\\3 && \ar@{>->}[ll]^{\id{3}}
-		3 \ar@{>->}[rr]_{i_{3}}&& 4 && \ar@{>->}[ll]^{\id{4}} 4
-		\ar@{>->}[rr]_{t}&& 4}
-	\]
-	and also in this case we get a pre-switch since
-	\[
-	\delta^3_0=\id{3} \circ \delta^3_0
-	\qquad i_2=t\circ i_2
-	\qquad \delta^3_0= \id{3} \circ \delta^3_0
-	\qquad \delta^4_0= i_3\circ \delta^3_0\]
-
-	Now, by \Cref{thm:switch_uni} we get an abstraction equivalence fitting in the diagram below.
-	\[\xymatrix@C=30pt@R=25pt{3 && \ar@{>->}[ll]_{\id{3}} 3 \ar@{>->}[rr]^{i_3}&& 4 && \ar@{>->}[ll]_{\id{4}} 4 \ar@{>->}[rr]^{\id{4}}&& 4\\1 \ar@{>->}[d]^{\delta^3_0} \ar@{>->}[u]_{\delta^3_0}&& 1 \ar@{>->}[d]^{\delta^3_0} \ar@{>->}[u]_{\delta^3_0}\ar@{>->}[ll]_{\id{1}} \ar@{>->}[r]^{\delta^2_0} & 2 \ar@{>->}@/^.35cm/[drrr]|(.315)\hole_(.4){i_2} \ar@{>->}[dr]|(.3)\hole_{i_2} \ar@{>->}@/_.35cm/[urrr]|(.315)\hole^(.4){i_2} \ar@{>->}[ur]|(.3)\hole^{i_2}& &1 \ar@{>->}@/_.35cm/[dlll]^(.4){\delta^3_0} \ar@{>->}[dl]|(.3)\hole^{\delta^4_0} \ar@{>->}@/^.35cm/[ulll]_(.4){\delta^3_0} \ar@{>->}[ul]|(.3)\hole_{\delta^4_0}& 1 \ar@{>->}[d]_{\delta^4_0} \ar@{>->}[u]^{\delta^4_0}\ar@{>->}[l]_{\id{1}} \ar@{>->}[rr]^{\id{1}} && 1 \ar@{>->}[d]_{\delta^4_0} \ar@{>->}[u]^{\delta^4_0}\\ \ar@/^.5cm/[uu]^{\id{3}} 3 && \ar[ll]^{\id{3}} 3 \ar@{>}@/^.5cm/[uu]^(.33){\phi_0}|\hole \ar[rr]_{i_3}&& 4 \ar@{>}[uu]_(.76){\psi_1}|(.45)\hole |(.55)\hole&& \ar@{>->}[ll]^{\id{4}} 4 \ar@{>}@/_.5cm/[uu]_(.33){\phi_1}|\hole\ar[rr]_{t}&& 4\ar@{>}@/_.5cm/[uu]_{\psi_2}}\]
-	But then there is only one component of this abstraction equivalence different from the identity, namely the last one, which must coincide with $t$.
-\end{example}
-
-Given two sequentially independent direct derivations, it is not necessarily true that a pre-switch for them exists, as shown by the following example.
-
-\begin{example}\label{ex:diff1}
-	Consider the poset $(P, \sqsubseteq)$ depicted below, where
-	$P = \mathbb{N} \cup \{a,b,c\}$ and $\sqsubseteq$ is defined by
-	$m \sqsubseteq n$ if $m \geq n$, $a \sqsubseteq x$ for all $x \in P$
-	and $b, c \sqsubseteq n$ for all $n \in \mathbb{N}$.
-	\[\xymatrix@C=16pt@R=1pt{
-		& 0 \ar@{-}[dd] \ar@{-}[ddddddl] \ar@{-}[ddddddr] &  \\
-		&  & \\
-		& 1 \ar@{-}[dd] \ar@{-}[ddddl]  \ar@{-}[ddddr]   &  \\
-		&  & \\
-		& 2 \ar@{.}[d] \ar@{-}[ddl]   \ar@{-}[ddr]     &  \\
-		&  \ar@{.}[dl]   \ar@{.}[dr] & \\
-		b \ar@{-}[dr] & & c \ar@{-}[dl]\\
-		& a} \]
-
-	Let $\X$ be the  
-	category associated with this order, which by \Cref{rem:iso} is
-	$\mathsf{I(\X)}$-adhesive. Consider a rewriting
-	system whose set of rules contains the following 
-	\[\xymatrix{a & a \ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & 0 & a & a
-		\ar[r]^{\sqsubseteq} \ar@{>->}[l]_{\id{a}} & b }\]
-	We can then consider the  following derivation
-	$\der{D}=\{\dder{D}_i\}_{i=0}^1$.
-	 \[
-   \xymatrix@C=25pt{a \ar[d]_{(a,c)}&& \ar@{>->}[d]_{k_0}\ar[ll]_{\id{a}}
-		    \ar[r]^{(a,0)} & 0 \ar@/^.35cm/[drrr]|(.315)\hole_(.45){\id{0}}
-		    \ar[dr]|(.3)\hole_{\id{0}} && a \ar@/_.35cm/[dlll]^(.45){\hspace{5pt}(a,c)}
-		     \ar[dl]|(.3)\hole^{(a,0)}& a \ar[d]^{(a,0)}\ar@{>->}[l]_{\id{a}}
-		     \ar[rr]^{(a,b)} && b \ar[d]^{(b,0)}\\c &&
-		     \ar@{>->}[ll]^{\id{c}} c \ar[rr]_{(c,0)}&& 0 &&
-		     \ar@{>->}[ll]^{\id{0}} 0 \ar[rr]_{\id{0}}&& 0}\]
-
-	Note that the two direct derivations are sequential
-	independent. However there is no pre-switch since the rule applied by
-	$\dder{D}_1$ cannot be applied to $c$. In fact, there is a unique morphism
-	$a\to c$, yielding the diagram
-	\[	\xymatrix{a \ar[d]_{(a,c)}& a
-		\ar[d]^{(a,c)}\ar@{>->}[l]_{\id{a}} \ar[r]^{(a,b)}& b \\c & c
-		\ar@{>->}[l]^{\id{c}}
-	}\]
-
-	Since $b$ and $c$ do not have a supremum in the poset underlying $\X$, the arrows
-	$a\to b$ and $a\to c$ do not have a pushout. Hence we do not get a direct derivation from $c$.
-\end{example}
-
-Before proceeding further we need to prove some other properties of independence pairs.
-
-\begin{proposition}
-	\label{prop:tec}
-	Let $(\X,\R)$ be a left-linear rewriting system and
-	$(i_0, i_1)$ an independence pair between two direct
-	derivations $\dder{D}_0$ and $\dder{D}_1$. Consider the pullback of
-	$f_1\colon D_1\mto G_1$ along $g_0\colon D_0\to G_1$ (first
-	square below), then there exist the arrows
-	$u_1\colon K_1\to P$ and $u_0\colon K_0\to P$ fitting in the
-	central and right square. Moreover, the right square is a pullback.
-	\[\xymatrix{P \ar@{>->}[r]^{p_0} \ar[d]_{p_1} & D_0
-		\ar[d]^{g_0}& K_0 \ar[r]^{r_0} \ar@{.>}[d]_{u_0}& R_0
-		\ar[d]^{i_0} & K_1 \ar@{>->}[r]^{l_1} \ar@{.>}[d]_{u_1}&
-		L_1 \ar[d]^{i_1}\\ D_1 \ar@{>->}[r]_{f_1} &G_1 &P
-		\ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0}
-	\]
-\end{proposition}
-
-\begin{proof}
-	We start noticing that
-	\[\begin{split}
-		f_1\circ i_0\circ r_0&=h_0\circ r_0\\&=g_0\circ k_0	\end{split}
-	\qquad\begin{split}
-		g_0\circ i_1\circ l_1&=m_1\circ l_1\\&= f_1 \circ k_1
-	\end{split}
-	\]
-	Thus there exists the dotted $u_0\colon K_0\to P$,
-	$u_1\colon K_1\to P$ in the diagram
-	\[\xymatrix{K_0 \ar[d]_{r_0}
-		\ar@{.>}[r]_{u_0}\ar@/^.4cm/[rr]^{k_0} &P
-		\ar@{>->}[r]_{p_0} \ar[d]_{p_1}& D_0 \ar[d]^{g_0}&K_1
-		\ar@{>->}[d]_{l_1}
-		\ar@{.>}[r]_{u_1}\ar@/^.4cm/[rr]^{k_1} &P \ar[r]_{p_1}
-		\ar@{>->}[d]_{p_0}& D_1 \ar@{>->}[d]^{f_1}\\R_0
-		\ar@/_.4cm/[rr]_{h_0}\ar[r]^{i_0}& D_1
-		\ar@{>->}[r]^{f_1}& G_1&L_1
-		\ar@/_.4cm/[rr]_{m_1}\ar[r]^{i_1}& D_0 \ar[r]^{g_0}&
-		G_1}\]
-
-The outer diagram given by the second rectangle is an $\mathcal{M}$-pushout, thus we can deduce from \Cref{prop:pbpoad} and \Cref{lem:pb1} that its left half is a pullback.
-\end{proof}
-
-\begin{corollary}\label{lem:cose}Let
-	$\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation and suppose
-	that $(i_0, i_1)$ is an independence pair between $\dder{D}_0$
-	and $\der{D}_1$.  If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a
-	pre-switch of $\der{D}$ along $(i_0, i_1)$, then there is an arrow
-	$z_0\colon P\to D_{\der{E},0}$ in $\mathcal{M}$ fitting in the square below.
-	\[\xymatrix{P \ar@{.>}[r]^-{z_0}  \ar@{>->}[d]_{p_0}& D_{\der{E}, 0} \ar@{>->}[d]^{f_{\der{E},0}} \\ D_0 \ar@{>->}[r]_{f_0} & G_0 }\]
-\end{corollary}
-\begin{proof}
-	Consider the arrow $u_1\colon K_1\to P$ obtained using
-	\Cref{prop:tec}. It fits in the big square on the left
-	\[		\xymatrix{K_1 \ar[r]^{u_1} \ar@{>->}[d]_{l_1}&P
-		\ar[r]^{\id{P}}\ar@{>->}[d]_{p_0}& P\ar@{>->}[d]^{p_0}\\L_1
-		\ar[d]_{\id{L_1}}\ar[r]^{i_1}&D_0 \ar[r]^{\id{D_0}}
-		\ar[d]_{\id{D_0}}& D_{0} \ar@{>->}[d]^{f_0}&K_1 \ar@{>->}[d]_{l_1}\ar[r]^{k_{\der{E},0}}&
-		D_{\der{E},0} \ar@{>->}[d]^{f_{\der{E},0}} & K_1 \ar[r]^{u_1}
-		\ar@{>->}[d]_{l_1}& P \ar@{>->}[d]^{f_0\circ
-			p_0}\\
-		L_1\ar[r]^{i_1} \ar@/_.4cm/[rr]_{m_{\der{E},0}}&D_0
-		\ar@{>->}[r]^{f_0}&G_0 & L_1\ar[r]_{m_{\der{E},0}}&G_0 &L_1
-		\ar[r]_{m_{\der{E},0}}&G_0}\]
-
-	Since $f_0$ is a monomorphism, all the inner squares of the left diagram are pullbacks, thus the whole big square is a pullback too.
-	Now the thesis follows applying \Cref{lem:radj} to the pair of squares on the right.
-	\end{proof}
-
-\begin{example}\label{ex:abs2}
-Let $\der{D}$ be the derivation of \Cref{ex:abs} and consider the pre-switch $\der{F}$. Then we can build the diagram belo
-	\[\xymatrix@C=20pt@R=20pt{&&1 \ar@{>->}@/_.9cm/[ddrr]_(.2){\delta^3_0}|(.72)\hole
-	\ar@{>->}[dr]^{\delta^3_0}&& 1\ar@{>->}@/^.9cm/[ddll]^(.2){\delta^3_0}
-	\ar@{>->}[dl]_{\delta^3_0}\\
-	&1\ar@{>->}[dr]^{\delta^3_0}\ar@{>->}[dl]_{\id{1}}
-	\ar@{>->}@/_.7cm/[ddrr]|(.38)\hole^(.7){\delta^3_0}\ar@{>->}[ur]^{\id{1}}&& 3 &&
-	1
-	\ar@{>->}@/^.7cm/[ddll]|(.38)\hole_(.7){\delta^3_0}\ar@{>->}[dl]_{\delta^3_0}\ar@{>->}[lu]_{\delta^3_0}
-	\ar@{>->}[dr]^{\delta^2_0}\\
-	1 \ar@/_.7cm/[ddrr]_(.2){\delta^3_0}|(.325)\hole|(.81)\hole
-	\ar@{>->}[dr]^(.35){\delta^3_0}|(.6)\hole && 3
-	\ar@{>->}[dl]|(.4)\hole^(.65){\id{3}}\ar@{>->}[ur]|(.5)\hole^(.7){\id{3} }&&3
-	\ar@{>->}[dr]|(.4)\hole_(.65){i_3}
-	\ar@{>->}[ul]|(.475)\hole_(.7){\id{3}}&&2\ar@{>->}@/^.7cm/[ddll]^(.2){i_2}|(.325)\hole|(.81)\hole\ar@{>->}[dl]_(.35){i_2}|(.6)\hole\\
-	&3 &&3	\ar@{>->}[dl]^{\id{3}}\ar@{>->}[ur]^{\id{3}}\ar@{>->}[ul]_{\id{3}}&&4\\
-	1	\ar@{>->}@/^.7cm/[uurr]^(.2){\delta^3_0} \ar@{>->}[ur]_(.35){\delta^3_0}|(.61)\hole && 3	\ar@{>->}[ul]|(.4)\hole_(.65){\id{3}}\ar@{>->}[dr]|(.5)\hole_(.65){i_3}	&&4\ar@{>->}[ur]|(.4)\hole^(.65){t} \ar@{>->}[dl]|(.5)\hole^(.65){\id{4}}	&& 1\ar[ul]^(.35){\delta^4_0}|(.61)\hole\ar@/_.7cm/[uull]_(.2){\delta^3_0}\\
-	&1	\ar@{>->}[ur]_{\delta^3_0} \ar@{>->}[dr]_{i_2}	\ar@{>->}[ul]^{\id{1}}\ar@/^.7cm/[uurr]_(.65){\delta^3_0}&&4&& 1\ar@{>->}[ur]_{\id{1}} \ar@{>->}[ul]^{\delta^4_0} \ar@{>->}[dl]^{\id{1}} \ar@{>->}@/_.7cm/[uull]^(.65){\delta^3_0}\\&& 2	\ar@{>->}[ur]_{i_2}\ar@{>->}@/^.9cm/[uurr]^(.2){i_2}&& 1 \ar@{>->}[ul]^{\delta^4_0} \ar@{>->}@/_.9cm/[uull]_(.2){\delta^3_0} |(.72)\hole }\]
-
-Notice that there is no arrow $f\colon 3\to 4$ such that 
-\[t\circ f=i_3\circ \id{3} \qquad \id{4}\circ f=i_3\circ \id{3}\]
-
-Indeed, if $f$ satisfies the first equation then $f=t\circ i_3$, while the second one entails $f=i_3$, but $t\circ i_3$ and $i_3$ are different.
-\end{example}
-
-The definition of pre-switch raises some issues.
-First of all we do not have sufficient conditions guaranteeing the existence of a pre-switch, moreover the fact that, as shown by \Cref{ex:abs}, the abstraction equivalence between two pre-switches does not necessarily have the identity as last component is somewhat unfortunate.
-Finally, \Cref{ex:abs2}, shows that this notion  is somewhat asymmetric in nature.
-We will now tackle this last defect, while a solution to the first two is deferred to the next section.
-
-\begin{definition}[Switch] 	Let $(\X, \R)$ be a left-linear rewriting system, with $\X$ an $\mathcal{M}$-adhesive category.
-	Let also $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be a derivation made
-	of two sequentially independent derivations $\dder{D}_0$,
-	$\dder{D}_1$ with independence pair $(i_0, i_1)$, as in the diagram below, where the cone with vertex $P$ is a pullback and $u_0\colon K_0\to P$ and $u_1\colon K_1\to P$ are the arrows built in \Cref{prop:tec}.
-	\[\xymatrix@R=15pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0 \ar @/^.35cm/[ddrr]_(.2){u_0}
-		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
-		\ar@{>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}|(.68)\hole
-		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{>}@/_.25cm/[dlll]^(.4){i_1}|(.68)\hole 
-		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar @/_.35cm/[ddll]^(.2){u_1}
-		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
-		D_0 \ar[rr]_{g_0}|(.7)\hole&& G_1 && \ar@{>->}[ll]^{f_1}|(.7)\hole D_1
-		\ar[rr]_{g_1}&& G_2 \\ & & & & P \ar[urr]_{p_1} \ar@{>->}[ull]^{p_0}}
-	\]
-
-	Let $\der{E}=\{\dder{E}_i\}_{i=0}^1$, depicted below, be a pre-switch for $\der{D}$ along $(i_0,i_1)$.
-	\[
-	\xymatrix@R=18pt@C=20pt{
-		{L_1} \ar[d]_{m_0'}
-		&&  {K_1} \ar@{>->}[ll]_{l_1} \ar[r]^{r_1} \ar[d]_{k_0'}
-		&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{>}_(.4){i_0'}|(.32)\hole[drrr]
-		& & 
-		{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{>}^(.4){i_1'}[dlll] 
-		&  {K_0} \ar@{>->}[l]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
-		& & {R_0} \ar[d]^{h_1'} \\		
-		{G_0}
-		& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rr]_{g_0'}
-		& &  {G'_1} 
-		& &  {D_1'} \ar@{>->}[ll]^{f_1'} \ar[rr]_{g_1'}
-		& & {G_2}  }
-	\]
-
-	We say that $\der{E}$ is a \emph{switch} for $\der{D}$ along $(i_0, i_1)$ if there is an arrow $z_1\colon P\to D'_1$ fitting in the diagram below, where $z_0\colon P\to D'_0$ is the arrow constructed in \Cref{lem:cose}.
-	\[\xymatrix@R=18pt{D'_0  \ar[d]_{g'_0}& P \ar[r]^{p_1} \ar[l]_{z_0} \ar@{.>}[d]^{z_1} & D_1 \ar[d]^{g_1}\\ G'_1 & D'_1 \ar[r]_{g'_1} \ar@{>->}[l]^{f'_1} & G_2}\]
-
-	If a switch of $\dder{D}_0$ and $\dder{D}_1$ exists we say that they are \emph{switchable}.
-If $(\der{D}, \alpha, \omega)$ is a decorated derivation of length $2$, and $(i_0, i_1)$ an independence pair between $\dder{D}_0$ and $\dder{D}_1$, a \emph{decorated switch} of $(\der{D}, \alpha, \omega)$ along $(i_0, i_1)$ is $(\der{E}, \alpha, \omega)$, where $\der{E}$ is a switch for $\der{D}$ along $(i_0, i_1)$.
-\end{definition}
-
-\begin{remark}\label{rem:quadrati}
-Let $\der{D}$ be a derivation made by two sequentially independence direct derivations with independence pair $(i_0, i_1)$.
-Suppose that $\der{E}$ is a pre-switch for $\der{D}$ along $(i_0, i_1)$.
-Then we have the solid part of the diagram below.
-If, moreover $\der{E}$ is a switch, then we can complete it with the dotted arrow $z_1\colon P\to D'_1$.
-		\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
-		\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
-		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
-		\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){u_0}\ar[ur]^{r_0}&& G_1 &&
-		K_1
-		\ar@/^.6cm/[ddll]|(.36)\hole_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
-		\ar[dr]^{r_1}\\L_0
-		\ar@/_.6cm/[ddrr]_(.2){i'_1}|(.31)\hole|(.81)\hole
-		\ar[dr]^(.4){m_0}|(.61)\hole && D_0
-		\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1
-		\ar[dr]|(.4)\hole^(.65){g_1}
-		\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_0}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
-		&&P\ar@{.>}[dr]_{z_1}	\ar@{>}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
-\end{remark}
-
-\begin{lemma}
-Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation of length $2$ and $(i_0, i_1)$ an independence pair between $\dder{D}_0$ and $\dder{D}_1$.
-Given a pre-switch $\der{E}=\{\dder{E}_{i}\}_{i=0}^1$ for $\der{D}$ along $(i_0, i_1)$, the following are equivalent:
-	\begin{enumerate}
-		\item $\der{E}$ is a switch;
-		\item if $(P, \{p_i\}_{i=0}^1)$ is a pullback for $f_{\der{D},1}$ along $g_{\der{D},0}$, then $\iota_{\der{E}, G_2} \circ g_1\circ p_1=\iota_{\der{E}, G'_1}\circ g'_0\circ z_0$.
-	\end{enumerate}
-\end{lemma}
-\begin{proof}$(1 \Rightarrow 2)$. If $\der{E}$ is a switch then we have
-	\begin{align*}
-		\iota_{\der{E}, G_2} \circ g_1\circ p_1&=\iota_{\der{E}, G_2} \circ g'_1\circ z_1\\&=\iota_{\der{E}, D'_1}\circ z_1\\&=\iota_{\der{E}, G'_1}\circ f'_1\circ z_1\\&=\iota_{\der{E}, G'_1}\circ g'_0\circ z_0
-	\end{align*}
-
-	\smallskip \noindent $(2\Rightarrow 1)$. By hypothesis the solid part of the diagram below commutes.
-	\[\xymatrix@C=30pt{P \ar[r]^{z_0} \ar@{.>}[dr]^{z_1}\ar[d]_{p_1} & D'_0 \ar[r]^{g'_0} & G'_1 \ar@{>->}[dr]^{\iota'_{1, G'_1}}\\ D_1 \ar[dr]_{g'_1}& D'_1 \ar[d]^{g'_1}\ar@{>->}[r]^{f'_1} &G'_1 \ar@{>->}[r]^{\iota'_{1, G'_1}} &\lpro \dder{E}_0 \rpro 	\ar@{>->}[d]^{p_1} \\ & G'_1 	\ar[rr]_{\iota_{\der{E}, G_2}}&& \tpro{E} }\]
-
-	By \Cref{rem:zero1} the inner square is a pullback, proving that the dotted arrow $z_1\colon P\to D'_1$ exists.
-Since, by \Cref{lem:colim} $\iota'_{1, G'_1}$ is in $\mathcal{M}$, we conclude that $f'\circ z_1=g'\circ z_0$ as wanted.
-\end{proof}
-
-We end this section showing that, if a switch exists, then any pre-switch can be turned into one composing it with an isomorphism.
-
-\begin{proposition}\label{prop:pretosw} 	Let $\der{D}=\{\dder{D}_{i}\}_{i=0}^1$ be a derivation and suppose
-	that both $\der{E}=\{\dder{E}_i\}_{i=0}^1$ and
-	$\der{F}=\{\dder{F}_i\}_{i=0}^1$ are pre-switches of $\dder{D}_0$ and
-	$\dder{D}_1$ along the same independence pair $(i_0, i_1)$.
-Let $\{\phi_X\}_{X\in \Deltamin(\der{E})}$ be the abstraction equivalence built in \Cref{thm:switch_uni}.
-If $\der{F}$ is a switch then also $\der{E}*\phi_{G_2}$ is one.
-\end{proposition}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\subsection{Strong-enforcing and well-switching rewriting systems}
-
-\Cref{ex:diff1} show that sequential independence it does not suffice, in general, to guarantee the existence of a switch.  Inspired by the notion of of \emph{canonical filler}
-\cite{heindel2009category}, we build on the last results of the previous section to give some conditions guaranteeing the existence of a switch.
-
-We are now ready to introduce the fundamental concept of this section.
-
-\begin{definition}[Strong independence pair]
-	\label{def:strong}
-	Let $\X$ be an $\mathcal{M}$-adhesive category 
-	and $(\X, \R)$ a left-linear rewriting system. 
-	Let also $(i_0, i_1)$ be an independence pair between two direct
-	derivations $\dder{D}_0$, $\dder{D}_1$
-	as in the solid part of the diagram below
-	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
-	\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
-	\ar@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
-	\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@/_.25cm/[dlll]^(.4){i_1}
-	\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
-	\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
-	D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
-	\ar[rr]_{g_1}&& G_2}
-\]
-
-	We say that $(i_0, i_1)$ is a \emph{strong independence pair} if
-	the first two squares depicted  
-	below are pushouts and if the pushout of $r_1 : K_1 \to R_1$ along $u_1 : K_1 \to P$ exists.
-	\[
-	\xymatrix{
-		K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
-		\ar@{>->}[r]^{l_1} \ar[d]_{u_1}& L_1 \ar[d]^{i_1}
-		&K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1\ar@{.>}[d]^{j_0}
-		\\
-		%
-		P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0
-		& P \ar@{.>}[r]_{q_1} & Q_1
-	}
-	\]
-\end{definition}
-
-\begin{remark}\label{rem:deco} 
-	Let $(i_0, i_1)$ be a strong
-	independence pair between the direct derivations $\dder{D}_0$ and
-	$\dder{D}_1$. We can then build the solid part of the diagram
-	below
-	\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
-		\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
-		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
-		\ar@/_.6cm/[ddrr]_(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
-		\ar@/^.6cm/[ddll]^(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
-		\ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0}
-		\ar@{.>}@/_.6cm/[ddrr]_{j_1}&& D_0
-		\ar@{>->}[dl]|(.42)\hole_(.64){f_0}\ar[ur]|(.48)\hole^(.7){g_1}&&D_1
-		\ar[dr]|(.42)\hole^(.65){g_1}
-		\ar@{>->}[ul]|(.48)\hole_(.7){f_1}&&R_1\ar@/^.6cm/[ddll]^{j_0}\ar[dl]^{h_1}\\&G_0
-		&&P\ar[dr]^{q_1}
-		\ar@{>.>}[dl]_{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\&&Q_0
-		\ar@{>->}@{>.>}[ul]_{a_0} &&Q_1\ar@{.>}[ur]^{b_1}}
-	\]
-
-	Let us complete this diagram defining the dotted arrows. To get
-	$j_1\colon L_0\to Q_0$ and $q_0\colon P\to Q_0$ it is enough to
-	take a pushout of $l_0$ along $u_0$, which exists since
-	$l_0\in \mathcal{M}$. Moreover, the existence of the wanted
-	$a_0\colon Q_0\to G_0$ and $b_1\colon Q_1\to G_2$ follows from
-	\[\begin{split}
-	f_0\circ p_0 \circ u_0 &= f_0\circ k_0 \\&= m_0\circ l_0
-	\end{split}
-	 \qquad\begin{split}
-	 	g_1\circ p_1\circ u_1 &= g_1\circ k_1\\&=h_1\circ r_1
-	 \end{split}
-	\]
-	We can prove some other properties of
-		the arrows appearing in the diagram above. The four rectangles
-		below are pushouts and their left halves are pushouts
-		too. Therefore, by \Cref{lem:po1} also their right halves are
-		pushouts.  Moreover, $q_0$ and $a_0$ are pushouts of
-		respectively $l_0$ and $p_0$, thus they are elements of
-		$\mathcal{M}$. By \Cref{prop:pbpoad} the left halves of the
-		second and third rectangles are pullbacks too.
-
-		\[\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar[d]_{r_0}\ar[r]_{u_0}
-			&P\ar[d]^{p_1} \ar@{>->}[r]_{p_0} & D_0 \ar[d]^{g_0}&K_1
-			\ar@/^.4cm/[rr]^{k_1}\ar@{>->}[d]_{l_1}\ar[r]_{u_1}
-			&P\ar@{>->}[d]^{p_0} \ar[r]_{p_1} & D_1 \ar@{>->}[d]^{f_1}\\
-			R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i_0}&D_1 \ar@{>->}[r]^{f_1}
-			& G_1&L_1 \ar@/_.4cm/[rr]_{m_1} \ar[r]^{i_1}&D_0\ar[r]^{g_0} &
-			G_1}\]
-			\[\xymatrix{K_0
-			\ar@/^.4cm/[rr]^{k_0}\ar@{>->}[d]_{l_0}\ar[r]_{u_0}
-			&P\ar@{>->}[d]^{q_0} \ar@{>->}[r]_{p_0} & D_0
-			\ar@{>->}[d]^{f_0}&K_1
-			\ar@/^.4cm/[rr]^{k_1}\ar[d]_{r_1}\ar[r]_{u_1}
-			&P\ar[d]^{q_1} \ar[r]_{p_1} & D_1 \ar[d]^{g_1}\\
-			L_0 \ar@/_.4cm/[rr]_{m_0} \ar[r]^{j_1}&Q_0 \ar@{>->}[r]^{a_0}
-			& G_0&R_1 \ar@/_.4cm/[rr]_{h_1} \ar[r]^{j_0}&Q_1 \ar[r]^{b_1}
-			& G_2}\]
-\end{remark}
-
-So equipped we can now prove a version of the Local Church-Rosser Theorem for strong independence pairs in ledt-linear DPO rewriting systems.
-
-\begin{theorem}[Local Church-Rosser Theorem]\label{prChurch} Let $\X$ be an $\mathcal{M}$-adhesive category and $(\X, \R)$ a left-linear DPO rewriting system on it.
-If $(i_0, i_1)$ is a strong independence pair
-	between $\dder{D}_0$ and $\dder{D}_1$, then there exists a switch of $\dder{D}_0$ and $\dder{D}_1$ along it.
-\end{theorem}
-\begin{proof}
-	Let us begin considering the diagram
-	built in \Cref{rem:deco}
-	\[\xymatrix@C=15pt@R=15pt{&&R_0
-		\ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole \ar[dr]^{h_0}&&
-		L_1\ar@/^.8cm/[ddll]^(.2){i_1}
-		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
-		\ar@/_.6cm/[ddrr]_(.65){u_0}\ar[ur]^{r_0}&& G_1 && K_1
-		\ar@/^.6cm/[ddll]^(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
-		\ar[dr]^{r_1}\\L_0 \ar[dr]^{m_0} \ar@{>}@/_.6cm/[ddrr]_{j_1}&& D_0
-		\ar@{>->}[dl]|(.42)\hole_(.64){f_0}\ar[ur]|(.48)\hole^(.7){g_1}&&D_1
-		\ar[dr]|(.42)\hole^(.65){g_1}
-		\ar@{>->}[ul]|(.48)\hole_(.7){f_1}&&R_1\ar@/^.6cm/[ddll]^{j_0}\ar[dl]_{h_1}\\&G_0
-		&&P\ar[dr]^{q_1}
-		\ar@{>->}[dl]_{q_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\&&Q_0
-		\ar@{>->}@{>->}[ul]_{a_0} \ar@{.>}[dr]_{b_0} &&Q_1\ar[ur]^{b_1}
-		\ar@{>.>}[dl]^{a_1} \\ &&&H_1 }\]
-
-		Since $q_0\colon P\to Q_0$ is in
-	$\mathcal{M}$, we can take its pushout along $q_1$ to get the dotted
-	arrows $a_1\colon Q_1\mto H_1$ and $q_0\colon Q_0\to H_1$. But then,
-	since the composite of two pushout squares is a pushout, the diagram
-	below is a derivation
-	\[\xymatrix{L_1 \ar[d]_{f_0 \circ i_1}&& K_1
-		\ar[d]_{q_0\circ u_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1
-		\ar@/^.35cm/[drrr]|(.31)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{a_1\circ
-			j_0} && L_0 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{b_0\circ
-			j_1}& K_0 \ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
-		\ar[d]^{g_1\circ i_0} \\G_0 && \ar@{>->}[ll]^{a_0} Q_0 \ar[rr]_{b_0}&&
-		H_1 && \ar@{>->}[ll]^{a_1} Q_1 \ar[rr]_{b_1}&& G_2}\]
-
-		The thesis now follows at once since, by construction, the derivation above is a switch of $\dder{D}_0$ and $\dder{D}_1$ along	$(i_0, i_1)$.
-\end{proof}
-
-The previous theorem not only assures about the existence of a switch along a strong independence pair, but it provides us with an explicit description of it.
-In turn this, using \Cref{thm:switch_uni}, allows us to deduce some property common to all switches along strong independence pairs.
-
-\begin{lemma}\label{cor:strongip}
-	Let $(\X, \R)$ be a left-linear DPO rewriting system and consider the following derivation $\der{D}={\dder{D}_{i}}_{i=0}^i$ and suppose that $(i_0, i_1)$ is a strong independence pair.
-	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
-		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
-		\ar@{.>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
-		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{.>}@/_.25cm/[dlll]^(.4){i_1}
-		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
-		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
-		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
-		\ar[rr]_{g_1}&& G_2}
-	\]
-
-	Suppose, moreover, that the following diagram defines a switch for $\dder{D}_0$ and $\dder{D}_1$ along $(i_0, i_1)$. 	
-	\[
-	\xymatrix@R=20pt@C=20pt{
-		{L_1} \ar[d]_{m_0'}
-		&&  {K_1} \ar@{>->}[ll]_{l_1} \ar[r]^{r_1} \ar[d]_{k_0'}
-		&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{.>}_(.4){i_0'}|(.32)\hole[drrr]
-		& & 
-		{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{.>}^(.4){i_1'}[dlll] 
-		&  {K_0} \ar@{>->}[l]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
-		& & {R_0} \ar[d]^{h_1'} \\		
-		{G_0}
-		& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rr]_{g_0'}
-		& &  {G'_1} 
-		& &  {D_1'} \ar@{>->}[ll]^{f_1'} \ar[rr]_{g_1'}
-		& & {G_2}  }
-	\]
-and define $T$, with the arrows $t_0\colon T\mto D'_0$ and $t_1\colon T\to D'_1$ as the pullback of $f'_1$ along $g'_0$.
-
-Finally, consider the derivation $\der{F}$ below, constructed in the proof of \Cref{prChurch}. 
-\[\xymatrix{L_1 \ar[d]_{f_0 \circ i_1}&& K_1
-	\ar[d]_{q_0\circ u_1}\ar@{>->}[ll]_{l_1} \ar[r]^{r_1} & R_1
-	\ar@/^.35cm/[drrr]|(.31)\hole_(.4){j_0} \ar[dr]|(.3)\hole_{a_1\circ
-		j_0} && L_0 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.3)\hole^{b_0\circ
-		j_1}& K_0\ar[d]^{q_1\circ u_0}\ar@{>->}[l]_{l_0} \ar[rr]^{r_0} && R_0
-	\ar[d]^{g_1\circ i_0} \\G_0 && \ar@{>->}[ll]^{a_0} Q_0 \ar[rr]_{b_0}&&
-	H_1 && \ar@{>->}[ll]^{a_1} Q_1 \ar[rr]_{b_1}&& G_2}\]
-and let $\{\phi_{X}\}_{X\in \Deltamin(\der{F})}$ be the abstraction equivalence built in \Cref{thm:switch_uni}.
-
-	Then the following hold true:
-	\begin{enumerate}
-		\item consider the following two squares, the first of which is a pullback and the second an $\mathcal{M}$-pushout,
-		\[\xymatrix{P \ar[r]^{p_1} \ar@{>->}[d]_{p_0} & D_1 \ar@{>->}[d]^{f_1}& P \ar[r]^{q_1} \ar@{>->}[d]_{q_0} & Q_1 \ar@{>->}[d]^{a_1}\\ D_0 \ar[r]_{g_0} & G_1&Q_0 \ar[r]_{b_0} & H_1}\]
-		then there exists an isomorphism $v\colon P\to T$ fitting in the diagram below:
-		\[\xymatrix{ P \ar@{.>}[dr]^{v} \ar[rrr]^{q_1} \ar@{>->}[ddd]_{q_0}&&& Q_1 \ar@{>->}[ddd]^{a_1} \ar[dl]_{\phi_{Q_1}}\\&T \ar@{>->}[d]_{t_0}\ar[r]^{t_1}& D'_1 \ar@{>->}[d]^{f'_1} \\ & D'_0\ar[r]_{g'_0} & G'_1\\Q_0 \ar[rrr]_{b_0} \ar[ur]_{\phi_{Q_0}}&&& H_1 \ar[ul]^{\phi_{H_1}}}\]
-
-		\item consider the diagram below, in which the inner square is a pullback and the dotted arrows are constructed as in \Cref{rem:deco}:
-		\[\xymatrix{K_1 \ar[r]^{r_1} \ar@/_.3cm/[ddr]_{k'_0} \ar@{.>}[dr]^{e_0}& R_1  \ar[dr]^{i'_0}  && K_0 \ar@{>->}[r]^{l_0} \ar@/_.3cm/[ddr]_{k'_1} \ar@{.>}[dr]^{e_1}& L_1  \ar[dr]^{i'_1} \\& T\ar@{>->}[d]_{t_0} \ar[r]^{t_1}& D'_1  \ar@{>->}[d]^{f'_1} && T \ar@{>->}[r]^{t_0} \ar[d]_{t_1}& D'_0 \ar[d]^{g'_0}\\&D'_0 \ar[r]_{g'_0} & G'_1 && D'_1\ar@{>->}[r]_{f'_1} & G'_1}\]
-		then $v\circ u_1=e_0$, $v\circ u_0=e_1$ and the two squares below are pushouts;
-		\[\xymatrix{K_1  \ar[d]_{e_0} \ar[r]^{r_1} & R_1 \ar[d]^{i'_0} & K_0 \ar@{>->}[r]^{l_0} \ar[d]_{e_1}& L_0 \ar[d]^{i'_1}\\ T \ar[r]_{t_1}  & D'_1 & T \ar@{>->}[r]_{t_0} & D'_0 }\]
-
-	\item $(i'_0, i'_1)$ is a strong independence pair;
-
-	\item there exists a commutative diagram the one below.
-
-	\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
-		\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
-		\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
-		\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){u_0}\ar[ur]^{r_0}&& G_1 &&
-		K_1
-		\ar@/^.6cm/[ddll]|(.36)\hole_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
-		\ar[dr]^{r_1}\\L_0
-		\ar@/_.6cm/[ddrr]_(.2){i'_1}|(.31)\hole|(.81)\hole
-		\ar[dr]^(.4){m_0}|(.61)\hole && D_0
-		\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1
-		\ar[dr]|(.4)\hole^(.65){g_1}
-		\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_0}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
-		&&P\ar@{.>}[dr]_{z_1}	\ar@{>.>}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
-	in which the following four squares are all pushouts, while the first three are also pullbacks.
-	\[\xymatrix{P \ar@{>->}[r]^{p_0} \ar@{>->}[d]_{p_1}& D_0 \ar@{>->}[d]^{g_0}  & P \ar@{>->}[r]^{z_0} \ar@{>->}[d]_{p_0}& D'_0 \ar@{>->}[d]^{f'_0} &  P \ar@{>->}[d]_{z_0} \ar[r]^{z_1} & D'_1 \ar@{>->}[d]^{f'_1} & P\ar[r]^{z_1} \ar[d]_{p_1}&D'_1 \ar[d]^{g'_1}\\ D_1 \ar@{>->}[r]_{f_1} & G_1  & D_0 \ar@{>->}[r]_{f_0} & G_0 & D'_0 \ar[r]_{g'_0}& G'_1 & D_1 \ar[r]_{g_1}& G_2}\]
-	\end{enumerate}
-\end{lemma}
-\begin{proof}
-	\begin{enumerate}
-		\item  By \Cref{prop:pbpoad}, the square below is also a pullback.
-			\[\xymatrix{P \ar[r]^{q_1} \ar@{>->}[d]_{q_0} & Q_1 \ar@{>->}[d]^{a_1}\\ Q_0 \ar[r]_{b_0} & H_1}\]
-			Thus by the universal property of pullbacks  we get the dotted arrows $v\colon P\to T$ and $w\colon T\to P$ in the following diagrams.
-		\[\xymatrix{ P \ar@{.>}[dr]^{v} \ar[rrr]^{q_1} \ar@{>->}[ddd]_{q_0}&&& Q_1 \ar@{>->}[ddd]^{a_1} \ar[dl]_{\phi_{Q_1}}& T\ar@{.>}[dr]^{w}  \ar[rrr]^{t_1} \ar@{>->}[ddd]_{t_0}&&& D'_1 \ar[dl]_{\phi^{-1}_{Q_1}} \ar@{>->}[ddd]^{f'_1}\\&T \ar@{>->}[d]_{t_0}\ar[r]^{t_1}& D'_1 \ar@{>->}[d]^{f'_1} &&& P \ar@{>->}[d]_{q_0}\ar[r]^{q_1}& Q_1\ar@{>->}[d]^{a_1}\\ & D'_0\ar[r]_{g'_0} & G'_1 &&& Q_0 \ar[r]_{b_0}& H_1 \\Q_0 \ar[rrr]_{b_0} \ar[ur]_{\phi_{Q_0}}&&& H_1 \ar[ul]^{\phi_{H_1}} & D'_0 \ar[rrr]_{g'_0} \ar[ur]_{\phi^{-1}_{Q_0}}&&&G'_1 \ar[ul]^{\phi^{-1}_{H_1}}}\]
-
-To see that they are one the inverse of the other it is then enough to compute.
-		\[\begin{split}
-		t_0\circ v\circ w &=\phi_{Q_0}\circ q_0\circ w\\&=\phi_{Q_0}\circ \phi^{-1}_{Q_0} \circ t_0\\&=t_0\\q_0\circ w\circ v&=\phi^{-1}_{Q_0}	\circ t_0\circ v\\&=\phi^{-1}_{Q_0} \circ \phi_{Q_0}\circ q_0\\&=q_0 	\end{split}\qquad \begin{split}
-		t_1\circ v\circ w &=\phi_{Q_1}\circ q_1\circ w\\&=\phi_{Q_1}\circ \phi^{-1}_{Q_1} \circ t_1\\&=t_1\\q_1\circ w\circ v&=\phi^{-1}_{Q_1}	\circ t_1\circ v\\&=\phi^{-1}_{Q_1} \circ \phi_{Q_1}\circ q_1\\&=q_1
-		\end{split}\]
-
-	\item By \Cref{thm:switch_uni}, we know that $\phi_{G_0}=\id{G_0}$, so that $a_0=f'_0\circ \phi_{Q_0}$, moreover, by the same theorem we have 
-	\[\phi_{Q_1}\circ j_0=i'_0 \qquad  \phi_{Q_0}\circ j_1=i'_1\]
-
-		We can now use the previous equalities to get
-		\[\begin{split}
-			t_0\circ v\circ u_0&=\phi_{Q_0} \circ q_0\circ u_0\\&=\phi_{Q_0}\circ j_1\circ l_0\\&=i'_1\circ l_0\\&=t_0\circ e_1\\	t_0\circ v\circ u_1&=\phi_{Q_0} \circ q_0\circ u_1\\&=k'_0\\&= t_0\circ e_0
-		\end{split} \qquad \begin{split}
-			t_1\circ v\circ u_1&=\phi_{Q_1} \circ q_1\circ u_1\\&=\phi_{Q_1}\circ j_0\circ r_1\\&=i'_0\circ r_1\\&= t_1\circ e_0 \\ t_1\circ v\circ u_0&=\phi_{Q_1} \circ q_1\circ u_0\\&=k'_1\\&=t_1\circ e_1
-		\end{split}\]
-
-	So that $v\circ u_1=e_0$ and $v\circ u_0=e_1$. The thesis now follows from the two diagrams below, since their left halves are pushouts by construction.		
-		\[\xymatrix{K_1  \ar@/^.4cm/[rr]^{e_0}\ar[r]_{u_1} \ar[d]_{r_1}& P \ar[r]_{v} \ar[d]_{q_1} & T \ar[d]^{t_1} & K_0 \ar@/^.4cm/[rr]^{e_1} \ar@{>->}[d]_{l_0}\ar[r]_{u_0} & P \ar[r]_{v}  \ar@{>->}[d]_{q_0}& T \ar@{>->}[d]^{t_0}\\ R_1 \ar@/_.4cm/[rr]_{i'_0} \ar[r]^{j_0}& Q_1 \ar[r]^{\phi_{Q_1}} & D'_1 & L_0 \ar@/_.4cm/[rr]_{i'_1} \ar[r]^{j_0} & Q_0 \ar[r]^{\phi_{Q_0}} & D'_0 }\]
-
-		\item Given the results of the previous point, it is now enough to show that the pushout of $r_0\colon K_0\to R_0$ along $e_1\colon K_0\to T$ exists. We can consider the diagram below
-		\[\xymatrix{K_0 \ar@/^.4cm/[rr]^{u_0} \ar[d]_{r_0} \ar[r]_{e_1}& T  \ar[d]_{p_1\circ w}\ar[r]_{w} & P \ar[d]^{p_1}\\ R_0 \ar[r]_{i_0}& D_1 \ar[r]_{\id{D_1}}& D_1}\]
-		But the outer diagram is a pushout since $(i_0, i_1)$ is strong and we can conclude.
-
-		\item Let $z_0\colon P\mto D'_0$ and $z_1\colon P\to D_1$ be, respectively, $t_0\circ v$ and $t_1\circ v$. Then we have
-
-		\[\begin{split}
-		g'_0\circ z_0&=g'_0\circ t_0\circ v\\&=f'_1\circ t_1\circ v\\&=f'_1\circ z_1
-		\end{split}\quad \begin{split}
-		z_0\circ u_1&=t_0\circ v\circ u_1\\&=\phi_{Q_0}\circ q_0\circ u_1\\&=k'_0
-		\end{split} \quad \begin{split}
-		z_1\circ u_0&=t_1\circ v\circ u_0\\&=\phi_{Q_1}\circ q_1\circ u_0\\&=k'_1
-		\end{split}\]
-
-		Moreover
-		\[\begin{split}
-			f'_0\circ z_0&=f'_0\circ t_0\circ v\\&=f'_0\circ \phi_{Q_0}\circ q_0\\&=a_0\circ q_0\\&=f_0\circ p_0
-		\end{split} \qquad \begin{split}
-		g'_1\circ z_1=g'_1\circ t_1\circ v\\&=g'_1\circ \phi_{Q_1}\circ q_1\\&=\phi_{G_2}\circ b_1 \circ q_1\\&=\phi_{G_2}\circ g_1\circ p_1\\&=f_0\circ p_0
-		\end{split} \]
-
-		Therefore the $z_0$ and $z_1$ fit in the diagram above.
-
-		To conclude, notice that the the four rectangles below and their halves, by construction and by point $3$, are pushouts, thus by \Cref{lem:po1} also their right halves are
-		pushouts.
-
-		\[\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar[d]_{r_0}\ar[r]_{u_0}
-			&P\ar[d]^{p_1} \ar@{>->}[r]_{p_0} & D_0 \ar[d]^{g_0}&K_0
-			\ar@/^.4cm/[rr]^{k'_1}\ar@{>->}[d]_{l_0}\ar[r]_{u_0}
-			&P\ar@{>->}[d]^{z_0} \ar[r]_{z_1} & D'_1 \ar@{>->}[d]^{f'_1}\\
-			R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i'_1}&D_1 \ar@{>->}[r]^{f_1}
-			& G_1&L_1 \ar@/_.4cm/[rr]_{m'_1} \ar[r]^{i_1}&D'_0\ar[r]^{g'_0} &
-			G'_1}\]
-		\[\xymatrix{K_0
-			\ar@/^.4cm/[rr]^{k_0}\ar@{>->}[d]_{l_0}\ar[r]_{u_0}
-			&P\ar@{>->}[d]^{z_0} \ar@{>->}[r]_{p_0} & D_0
-			\ar@{>->}[d]^{f_0}&K_1
-			\ar@/^.4cm/[rr]^{k_1}\ar[d]_{r_1}\ar[r]_{u_1}
-			&P\ar[d]^{z_1} \ar[r]_{p_1} & D_1 \ar[d]^{g_1}\\
-			L_0 \ar@/_.4cm/[rr]_{m_0} \ar[r]^{i'_1}&D'_0 \ar@{>->}[r]^{f'_0}
-			& G_0&R_1 \ar@/_.4cm/[rr]_{h_1} \ar[r]^{i'_0}&D'_1 \ar[r]^{b_1}
-			& G_2}\]
-
-			We conclude by \Cref{prop:pbpoad}. \qedhere 
-	\end{enumerate}
-\end{proof}
-
-We can now turn to prove the fundamental property that we need to rely upon:  any decorated switch along a strong independence pair induces a consistent permutation.
-
-\begin{lemma}\label{lem:switchtoperm}
-	Let $(\der{D}, \alpha, \omega)$ be a decorated derivations of length $2$ and suppose that $(\der{E}, \alpha, \omega)$ is a decorated switch for it along the independence pair $(i_0, i_1)$.
-Then there exists an arrow $\kappa\colon G_1\to \tpro{E}$ such that
-		\[\kappa \circ g_{0} = \iota_{\der{E}, G_0}\circ f_{0} \qquad \kappa\circ h_{0}= \iota_{\der{E}, R_0}\]
-
-		Moreover, if $(i_0, i_1)$ is strong, also the following facts are true:
-		\begin{enumerate}
-		\item there exists an arrow $\phi\colon \tpro{D}\to \tpro{E}$ such that
-		\[\phi \circ \iota_{\der{D}, G_0}=\iota_{\der{E}, G_0} \qquad \phi \circ \iota_{\der{D}, G_1}=\kappa \qquad \phi \circ \iota_{\der{D}, G_2}=\iota_{\der{E}, G_2}\]
-		\item the $2$-cycle $\tau_{0,1}\colon [0,1]\to [0,1]$ is a consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{E}, \alpha, \omega)$.
-	\end{enumerate}
-\end{lemma}
-\begin{proof}
-	To fix the notation let $\der{D}$ be given by the first diagram below and $\der{E}$ by the second one.
-	\[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
-		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} & R_0
-		\ar@{>}@/^.25cm/[drrr]|(.32)\hole_(.4){i_0}
-		\ar[dr]|(.33)\hole_{h_0} && L_1 \ar@{>}@/_.25cm/[dlll]^(.4){i_1}
-		\ar[dl]|(.33)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar@{>->}[l]_{l_1}
-		\ar[rr]^{r_1} && R_1 \ar[d]^{h_1}\\G_0 && \ar@{>->}[ll]^{f_0}
-		D_0 \ar[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
-		\ar[rr]_{g_1}&& G_2}
-	\]
-	\[
-	\xymatrix@R=20pt@C=20pt{
-		{L_1} \ar[d]_{m_0'}
-		&&  {K_1} \ar@{>->}[ll]_{l_1} \ar[r]^{r_1} \ar[d]_{k_0'}
-		&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{>}_(.4){i_0'}|(.32)\hole[drrr]
-		& & 
-		{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{>}^(.4){i_1'}[dlll] 
-		&  {K_0} \ar@{>->}[l]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
-		& & {R_0} \ar[d]^{h_1'} \\		
-		{G_0}
-		& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rr]_{g_0'}
-		& &  {G'_1} 
-		& &  {D_1'} \ar@{>->}[ll]^{f_1'} \ar[rr]_{g_1'}
-		& & {G_2}  }
-	\]
-
- $G_1$ is obtained as the pushout of $k_0$ along $r_0$m thus get the wanted arrow $\kappa\colon G_1\to \tpro{E}$ it is now enough to compute:
-	\begin{align*}
-		\iota_{\der{E}, G_0}\circ f_{0}\circ  k_{0}&= \iota_{\der{E}, G_0}\circ m_{0} \circ l_{ 0}\\&=\iota_{\der{E}, G_0}\circ  f'_{0} \circ i'_1 \circ l_0\\&=\iota_{\der{E}, D'_0}\circ i'_1 \circ l_0\\&=\iota_{\der{E}, G'_1} \circ g'_0\circ m'_1 \circ l_0\\&=\iota_{\der{E}, G'_1}\circ m'_1\circ l_0	\\&=\iota_{\der{E}, G'_1} \circ f'_1\circ k'_1\\&=\iota_{\der{E}, D'_1}\circ k'_1\\&=\iota_{\der{E}, K'_0}\\&= \iota_{\der{E}, R_0} \circ r_0
-	\end{align*}
-
-	Let us now suppose that $(i_0,i_1)$ is a strong independence pair. We can then consider the following two squares, the first of which is a pullback and the second one, by strongness, a  pushout.
-
-			\[\xymatrix{P \ar[r]^{p_1}  \ar@{>->}[d]_{p_0} & D_1 \ar@{>->}[d]^{f_1} & K_0 \ar[r]^{r_0}  \ar[d]_{u_0} & R_0 \ar[d]^{i_0}\\ D_0\ar[r]_{g_0} & G_1 & P\ar[r]_{p_1} & D_1}\]
-
-	\begin{enumerate}
-		\item   Consider the arrow $\kappa\colon G_1\to \tpro{E}$ built in the previous point, then we have
-		\begin{align*}
-			\kappa \circ f_1\circ i_0&=\kappa\circ h_0\\&=\iota_{\der{E},R_0}\\&=\iota_{\der{E}{G_2}}\circ h'_1\\&=\iota_{\der{E}{G_2}}\circ g_1\circ i_0
-		\end{align*}
-
-		\begin{align*}
-			\kappa\circ f_1\circ p_1&=\kappa \circ g_0\circ p_0\\&=\iota_{\der{E},G_0}\circ f_0\circ p_0
-		\end{align*}
-		\item 
-		\qedhere 
-	\end{enumerate}
-\end{proof}
-
-\Cref{prChurch} and \Cref{lem:switchtoperm} guarantees some basic but fundamental properties of switches whithout which developing a theory of concurrency seems hopeless, we are thus lead to the following definition.
-
-\begin{definition}
-A left-linear DPO rewriting system $(\X, \R)$ is \emph{strong enforcing} if every independence pair is strong.
-\end{definition}
-
-The notion of strong enforcing DPO rewriting system encompasses that of linear one.
-
-\begin{proposition}\label{prop:linstrong}
-	Every linear rewriting system $(\X, \R)$ is strong enforcing.
-\end{proposition}
-\begin{proof}
-	Suppose that $\X$ is $\mathcal{M}$-adhesive and let $(i_0, i_1)$ be
-	an independence pair as below
-	\[
-	\xymatrix@C=15pt{L_0 \ar[d]_{m_0}&& K_0
-		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar@{>->}[r]^{r_0} & R_0
-		\ar@/^.35cm/[drrr]|(.3)\hole_(.4){i_0} \ar[dr]|(.3)\hole_{h_0}
-		&& L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
-		\ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar@{>->}[rr]^{r_1} && R_1
-		\ar[d]^{h_1} \\G_0 && \ar@{>->}[ll]^{f_0} D_0
-		\ar@{>->}[rr]_{g_0}&& G_1 && \ar@{>->}[ll]^{f_1} D_1
-		\ar@{>->}[rr]_{g_1}&& G_2}\]
-
-	Since $(\X, \R)$ is linear, then $r_1\colon K_1\to R_1$ belongs to
-	$\mathcal{M}$, thus it admits a pushout along $u_1\colon K_1\to P$,
-	as desired. Moreover, let us consider the two rectangles below
-	\[
-	\xymatrix{K_0 \ar@/^.4cm/[rr]^{k_0}\ar@{>->}[d]_{r_0}\ar[r]_{u_0}
-		&P\ar@{>->}[d]^{p_1} \ar@{>->}[r]_{p_0} & D_0
-		\ar@{>->}[d]^{f_0}& K_1
-		\ar@/^.4cm/[rr]^{k_1}\ar@{>->}[d]_{l_1}\ar[r]_{u_1}
-		&P\ar@{>->}[d]^{p_0} \ar@{>->}[r]_{p_1} & D_1
-		\ar@{>->}[d]^{f_1}\\ R_0 \ar@/_.4cm/[rr]_{h_0} \ar[r]^{i_0}&D_1
-		\ar@{>->}[r]^{f_1} & G_1& L_1 \ar@/_.4cm/[rr]_{m_1}
-		\ar[r]^{i_1}&D_0 \ar@{>->}[r]^{g_0} & G_1} \] By hypothesis
-	$r_0$ and $l_1$ are in $\mathcal{M}$, thus $f_1$ and $g_0$ belong to
-	it too. The first point of \Cref{lem:popb} yields the thesis.
-\end{proof}
-
-We can easily
-
-\begin{lemma}
-Let $(P, \{p_0, p_1\})$ be the pullback of $f_1$ along $g_1$, then there exists $z_0\colon P\mto D'_0$ and $z_1\colon P\to D'_1$ making the following diagram commutative
-\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){i_0}|(.7)\hole
-	\ar[dr]^{h_0}&& L_1\ar@/^.8cm/[ddll]^(.2){i_1}
-	\ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar@{>->}[dl]_{l_0}
-	\ar@/_.6cm/[ddrr]|(.36)\hole^(.65){u_0}\ar[ur]^{r_0}&& G_1 &&
-	K_1
-	\ar@/^.6cm/[ddll]|(.36)\hole_(.65){u_1}\ar[dl]_{k_1}\ar@{>->}[lu]_{l_1}
-	\ar[dr]^{r_1}\\L_0
-	\ar@/_.6cm/[ddrr]_(.2){i'_1}|(.31)\hole|(.81)\hole
-	\ar[dr]^(.4){m_0}|(.61)\hole && D_0
-	\ar@{>->}[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1
-	\ar[dr]|(.4)\hole^(.65){g_1}
-	\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_0}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
-	&&P\ar@{.>}[dr]_{z_1}	\ar@{>.>}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
-moreover, the following squares are all pushouts, moreover the first two are also pullbacks.
-\[\xymatrix{P \ar@{>->}[r]^{z_0} \ar@{>->}[d]_{p_0}& D'_0 \ar@{>->}[d]^{f'_0} &  P \ar@{>->}[d]_{z_0} \ar[r]^{z_1} & D'_1 \ar@{>->}[d]^{f'_1} & P\ar[r]^{z_1} \ar[d]_{p_1}&D'_1 \ar[d]^{g'_1}\\ D_0 \ar@{>->}[r]_{f_0} & G_0 & D'_0 \ar[r]_{g'_0}& G'_1 & D_1 \ar[r]_{g_1}& G_2}\]
-\end{lemma}
-\begin{proof}
-	Define $z_0$ and $z_1$ to be, respectively, $t_0\circ v$ and $t_1\circ v$. To prove the commutativity of the diagram in the thesis, first of all we can notice that
-	\begin{align*}
-		g'_0\circ z_0\\&= g'_0\circ t_0\circ v\\&=f'_1\circ t_1\circ v\\&=f'_1\circ z_1
-	\end{align*}
-	To prove the other identities, it is enough to compute and use the identities obtained in the previous point. On the one hand we have
-	\[	\begin{split}f'_0\circ z_0&=f'_0\circ t_0\circ v\\&=f'_0\circ \phi_{Q_0}\circ q_0\\&=a_0\circ q_0\\&=f_0\circ p_0 
-	\end{split} \qquad \begin{split}
-		g'_1\circ z_1&=g'_1\circ t_1\circ v\\&=g'_1\circ \phi_{Q_1}\circ q_1\\&=\phi_{G_2}\circ b_1\circ q_1\\\phi_{G_2}\circ g_1\circ p_1\\&=
-	\end{split}\]
-
-	\[\begin{split}
-		z_0\circ u_0&= t_0\circ v \circ u_0\\&=t_0\circ e_1\\&=i'_1\circ l_0\\ 	f'_0\circ z_0&=f'_0\circ t_0\circ v\\&=f'_0\circ \phi_{Q_0}\circ q_0\\&=a_0\circ q_0\\&=f_0\circ p_0
-	\end{split}\quad \begin{split}
-		z_1\circ u_1&=t_1\circ v\circ u_1\\&=t_1\circ e_1\\&=i'_0\circ r_1
-	\end{split} \quad \begin{split}
-	aaa	
-	\end{split}\]
-
-\end{proof}
-
-\subsection{Well-switching rewriting systems}
-
-\subsection{Abstract switches}
-We can now prove some properties relating switching and abstraction equivalence. As a first step we can show that switches along the same independence paire are unique up to abstraction equivalence.
-
-\todo{Unicità}
-
-\todo{switchabilità}
-
-\begin{definition}
-	contenuto...
-\end{definition}
-
-\begin{corollary}[Uniqueness of switches]\label{cor:switch}
-	\todo{switches}
-\end{corollary}
-
-Another useful property of switches is that they can be performed back and forth, giving back the original derivation. This is the content of the following two results.
-
-\todo{switch di switch}
-
-\begin{proposition}
-	contenuto...
-\end{proposition}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{corollary}
-	contenuto...
-\end{corollary}
-
-The fact that sequential independence implies switchability always
-holds for linear rules (see \Cref{prop:equi}). The result is so
-indispensable that typically, in the literature, it is not even
-stated, in the sense that switchability is not introduced
-axiomatically as in Definition~\ref{def:switch}, but it is based on
-the explicit construction of a switch.
-
-For left-linear rewriting systems
-sequential independence does not imply switchability (while the
-converse implication clearly holds), as shown by the next example.
-
-\begin{figure}
-
-	\begin{subfigure}{0.58\textwidth}
-		\xymatrix@C=20pt{
-			a \ar[d]_{\sqsubseteq} & a \ar[d]_{\sqsubseteq} \ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} & 
-			0 \ar@{>->}@/^.35cm/[drrr]|(.3)\hole^(.75){\id{0}}
-			\ar@{>->}[dr]|(.3)\hole_{\id{0}} &  &
-			a \ar@/_.35cm/[dlll]_(.75){\sqsubseteq}
-			\ar[dl]|(.3)\hole^{\sqsubseteq} & 
-			a \ar[d]^{\sqsubseteq}\ar@{>->}[l]_{\id{a}} \ar[r]^{\sqsubseteq} &
-			b \ar[d]_{\sqsubseteq}\\
-			c &
-			\ar@{>->}[l]^{\id{c}} c \ar[rr]_{\sqsubseteq}& &  0 &&
-			\ar@{>->}[ll]^{\id{0}} 0 \ar@{>->}[r]_{\id{0}}& 0
-		}
-		\caption{Two rewriting steps}
-		\label{fig:diff1:rew}
-	\end{subfigure}
-	\begin{subfigure}{0.20\textwidth}
-
-		\caption{No rewriting step}
-		\label{ex:diff1:no-step}
-	\end{subfigure}
-	\caption{Sequential independence does not imply switchability}
-	\label{fig:diff1} 
-\end{figure}
-
-The conditions guaranteeing switchability are inspired
-by the notion of \emph{canonical filler}
-\cite{heindel2009category}.
-
-\begin{definition}[Strong independence pair]
-	\label{def:filler}
-	Let $\X$ be an $\mathcal{M}$-adhesive category 
-	and $(\X, \R)$ a left-linear rewriting system. 
-	Let also $(i_0, i_1)$ be an independence pair between two direct
-	derivations $\dder{D}_0$, $\dder{D}_1$
-	as in the solid part of the diagram below
-	\[
-	\xymatrix@C=18pt@R=17pt{L_0 \ar[d]_{m_0}&& K_0
-		\ar[d]_{k_0}\ar@{>->}[ll]_{l_0} \ar[r]^{r_0} \ar@{.>}@/^.20cm/[ddrr]|(.32)\hole|(.57)\hole_(.7){u_0} & R_0
-		\ar@/^.35cm/[drrr]|(.3)\hole^(.2){i_0} \ar[dr]|(.3)\hole_{h_0}
-		&& L_1 \ar@/_.35cm/[dlll]_(.2){i_1} \ar[dl]|(.3)\hole^{m_1}& K_1
-		\ar[d]^{k_1}\ar@{>->}[l]_{l_1} \ar[rr]^{r_1} \ar@{.>}@/_.20cm/[ddll]|(.32)\hole|(.57)\hole^(.7){u_1} && R_1 \ar[d]^{h_1} \\
-		%
-		G_0 &&
-		\ar@{>->}[ll]^{f_0} D_0 \ar[rr]_(.3){g_0}&& G_1 &&
-		\ar@{>->}[ll]^(.3){f_1} D_1 \ar[rr]_{g_1}&& G_2\\
-		%
-		& & & & P \ar@/^.3cm/@{>.>}[ull]^{p_0} \ar@/_.3cm/@{.>}[urr]_{p_1}
-	}
-	\]
-
-	Consider the pullback of $g_0$ and $f_1$, which yields $p_i : P \to D_i$
-	for $i \in \{0,1\}$ and the mediating arrows $u_i\colon K_i\to P$ 
-	for $i \in \{0,1\}$ 
-	into the pullback object (see \Cref{prop:tec} for details). 
-	We say that $(i_0, i_1)$ is a \emph{strong independence pair} if
-	the first two squares depicted  
-	below are pushouts and if the pushout of $r_1 : K_1 \to R_1$ and $u_1 : K_1 \to P$ exists
-	\[
-	\xymatrix@R=16pt{
-		K_0 \ar[r]^{r_0} \ar[d]_{u_0}& R_0 \ar[d]^{i_0} & K_1
-		\ar@{>->}[r]^{l_1} \ar[d]_{u_1}& L_1 \ar[d]^{i_1}
-		&K_1 \ar[r]^{r_1} \ar[d]_{u_1}& R_1\ar@{.>}[d]^{j_0}
-		\\
-		P \ar[r]_{p_1} & D_1 &P \ar[r]_{p_0} & D_0
-		& P \ar@{.>}[r]_{q_1} & Q_1
-	}
-	\]
-\end{definition}
-
-We can now prove a Local Church-Rosser Theorem for strong independence pairs.
-
-\begin{proposition}	\label{pr:church}
-	Let $(i_0, i_1)$ be a strong independence pair
-	between $\dder{D}_0$ and $\dder{D}_1$. Then $\dder{D}_0$ and
-	$\dder{D}_1$ are switchable.
-\end{proposition}
-
-The correspondence between sequential independence and switchability
-is fundamental. We name the class of rewriting systems where this property holds.
-
-\begin{definition}[Strong enforcing rewriting systems]
-	A left-linear rewriting system is \emph{strong enforcing} if
-	every independence pair between two direct derivations is strong.
-\end{definition}
-
-We can identify a large class of adhesive categories such that all
-left-linear rewriting systems over such categories are strong
-enforcing. This class includes $\cat{Set}$ and it is closed
-under comma and functor category constructions.  As such, it includes
-essentially all categories (e.g., presheaves over set) that are
-typically considered for modelling purposes. Notably, it contains the
-category $\cat{Graph}$ of directed graphs.
-This is a natural generalisation from adhesive to $\mathcal{M}$-adhesive categories of a class studied in \cite{baldan2011adhesivity} (see \Cref{app:fill} for details).
-
-Still, there are $\mathcal{M}$-adhesive rewriting systems that are not strong enforcing.
-
-\begin{example}[Non-strong enforcing left-linear rewriting system]
-	\label{ex:diff2}
-	In light of \Cref{pr:church}, \Cref{ex:diff1} provides an example of
-	an independence pair that is not strong. This gives an example of a
-	left-linear rewriting system in a $\mathcal{M}$-adhesive category that is quite
-	pathological since $\mathcal{M}=\mathsf{I(\X)}$. However, this is expected, 
-	since all natural examples seem to belong to the well-behaved class mentioned above. 
-\end{example}
-
-\begin{remark}
-	By \Cref{pr:church} the existence of a strong independence pair
-	entails switchability, which in turn entails sequential
-	independence by construction. Strong enforcing rewriting systems are exactly
-	those rewriting systems in which these three notions coincide.
-\end{remark}
-
-Consistency with the theory of linear rewriting systems is ensured by the fact that all linear rewriting systems are strong enforcing (see \cref{prop:equi}).
-
-Even if we work in strong enforcing rewriting systems where sequential
-independence ensures switchability, when dealing with left-linear
-rules there is a further, possibly more serious issue, 
-namely that there can be more than one independence pair between
-the same derivations (cfr. \Cref{rem:uni}). This hinders the very idea of using
-sequential independence as a basis of a theory of concurrency for
-rewriting systems, since exchanges performed using different
-independence pairs may lead to derivations that are not abstraction
-equivalent, thus equating computations that should
-definitively be taken apart, as shown in the example below.
-
-\begin{example}
-	Consider the derivation $\der{E}$ from Example~\ref{ex:seq-ind} (see Fig.~\ref{fi:derE}).
-	The last two steps are sequential independent, but one easily sees
-	that there are two distinct independence pairs, as the left-hand side
-	of $\rho_1$ can be mapped either to node $1$ or to node
-	$2$ in $D_1'$. Correspondingly, there
-	are two switches of $\der{E}$: one is the derivation $\der{D}$ in
-	Fig.~\ref{fi:derD} we started from, the other is the derivation
-	$\der{D}'$ in Fig.~\ref{fi:derD1}.
-
-	\begin{figure}
-%		\input{Figure/derD1.tex}
-		\caption{The derivation $\der{D}'$.}
-		\label{fi:derD1}
-	\end{figure}
-
-	As a consequence, $\der{D}$ and $\der{D}'$ would be switch
-	equivalent, but this is not acceptable when viewing equivalence
-	classes of derivations as concurrent computations: in $\der{D}$ the
-	first two steps are not sequential independent, while in $\der{D}'$
-	they are, intuitively because in $\der{D}$ rule $\rho_1$ uses the
-	node generated by $\rho_0$ (adding a self-loop to it), while in
-	$\der{D}'$ rule $\rho_1$ uses the node that was in the initial
-	graph. Also observe that the graphs $G_2$ and $G_2'$ produced after
-	two steps in $\der{D}$ and $\der{D'}$ are not isomorphic. From the
-	technical point of view, the property of being switch equivalent is
-	not closed by prefix, and this prevents deriving a sensible
-	concurrent semantics: In fact
-	$\der{D} = \dder{D}_0\cdot \dder{D}_1 \cdot \dder{D}_2$ and
-	$\der{D}' = \dder{D}_0'\cdot \dder{D}_1' \cdot \dder{D}_2'$ are
-	switch equivalent, while if we consider the first two steps,
-	derivations $\dder{D}_0 \cdot \dder{D}_1$ and
-	$\dder{D}_0' \cdot \dder{D}_1'$ are not switch equivalent.
-\end{example}
-
-Moreover, limiting sequential independence to the case in which the independence
-	pair is unique (as suggested in~\cite{baldan2017domains}) brings to the same problems.
-
-For these reasons we believe a theory of rewriting for
-left-linear rules in adhesive categories should be developed for
-systems where the uniqueness of the independence pair is ensured.
-
-\begin{definition}[Well-switching rewriting systems]
-	A left-linear rewriting system $(\X, \R)$ is \emph{well-switching} if it is strong enforcing and, for every derivation $\der{D}:=\{\dder{D}_{i}\}_{i=0}^1$, there is at most one independence pair between $\dder{D}_0$ and $\dder{D}_1$.
-\end{definition}
-
-Clearly, linear rewriting systems are well-switching (see Proposition~\ref{pr:weak}).
 Moreover, we next observe that various classes of rewriting systems,
@@
 
-\subsubsection{Some examples of well-switching rewriting systems}
+\todo{da fare}
 
-\todo{Questa sezione è da riscrivere bene}
+\todo{Questa sezione è da riscrivere bene ma penso vada incorporata nella sez sui well.behaved}
 
@@
 
-\section{Switch equivalence and concatenable traces}
-\todo{intro}
-
-As we mentioned, for linear rewriting systems
-it is canonical to identify
-derivations that are equal ``up to switching'', i.e.~that differ
-only in the order of independent steps. The same notion can be given
-for left-linear rewriting systems by relying on the notion of switch.
-
-We  recall some notations on permutations.  A \emph{permutation} on
-$\interval[0]{n}$ is a bijection
-$\sigma : \interval[0]{n} \to \interval[0]{n}$. It is a
-\emph{transposition} $\nu$ if there are $i, j \in \interval{n}$,
-$i \neq j$ such that $\sigma(i)=j$, $\sigma(j) = i$, and
-$\sigma(k) = k$ otherwise; it is denoted as $\transp{i}[j]$. Given a permutation $\perm$, 
-an \emph{inversion} for $\sigma$ is a pair $(i,j)$ such that $i<j$ and
-$\sigma(j)< \sigma(i)$; $\inv{\sigma}$ denotes the set of
-inversions of $\perm$.
-
-Switch equivalence is now defined as the equivalence relating derivations that 
-can be obtained one from another by a sequence of switches. Moreover, intermediate graphs can be taken up to isomorphism according to abstraction equivalence.
-
-\begin{definition}[Switching sequence]
-	\label{de:switch-equivalence}
-	Let $(\X, \R)$ be a left-linear rewriting system.  Let also
-	$\der{D}, \der{E} : G \Mapsto H$ be derivations with the same
-	length, $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and
-	$\der{E}=\{\dder{E}_{i}\}_{i=0}^n$. If
-	$\dder{D}_i \cdot \dder{D}_{i+1}$ is a switch of
-	$\dder{E}_i \cdot \dder{E}_{i+1}$ for some $i \in [0,n-1]$ and  $\dder{D}_j = \dder{E}_j$ for each $j \not \in \{i,i+1\}$ then we write
-	$\der{D} \shift{\transp{i}} \der{E}$. 
-	A \emph{switching sequence} is a sequence $\{\der{D}_{k}\}_{k=0}^m$
-	of derivations such that
-	$\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
-	\shift{\nu_m} \der{D}_m$  with $\nu_{k} = \transp{i_k}$.
-
-	Let us denote by $\nu_{k,h}$ the composition
-	$\nu_h \circ \nu_{h-1} \circ \ldots \nu_k$. We say that the
-	switching sequence \emph{consists of inversions} if for all
-	$k \in \interval[0]{m}$ the transposition $\nu_k$ is an inversion
-	for $\nu_{1,m}$.
-
-	Two derivations $\der{D}, \der{E}:G\Mapsto H$ are \emph{switch
-		equivalent}, written $\der{D}\equiv^{sh} \der{E}$, if there is a
-	switching sequence $\{\der{D}_{k}\}_{k=0}^m$ such that
-	$\der{D}\equiv_a \der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2}
-	\ldots \shift{\nu_m} \der{D}_m \equiv _a \der{E}$.   
-	To point out a chosen permutation of rewriting steps, we will also write $\der{D}\equiv^{sh}_{\sigma} \der{E}$, 
-	where $\sigma$ is the composition of the transposition appearing in a chosen switching sequence. 
-\end{definition}
-
-\todo{Consistent permutations from switchings}
-
-\subsection{A canonical form for switching sequences}
-
-As a beginning step in our analysis of switch equivalence, we will establish three lemmas  dealing with derivations of length $3$.
-
-\begin{lemma}[Forward $3$-steps Lemma]\label{lem:primo}
-Let $(\X,\R)$ be a left-linear DPO-rewriting system.
-Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$ and suppose that $(i_0,i_1)$ is a good independence pair between $\dder{D}_0$ and $\dder{D}_1$, $(a_0,a_1)$ one between $\dder{D}_1$ and $\dder{D}_2$ and $(e_0, e_1)$ one between $\dder{D}_0$ and $S_{a_0,a_1}(\dder{D}_2)$.
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{lemma}[Backward $3$-steps Lemma]\label{lem:secondo}
-	contenuto...
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{lemma}[Third $3$-steps Lemma]\label{lem:terzo}
-	contenuto...
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\todo{dividere in due il lemma dopo. devono venire tre lemmi}
-\begin{lemma}[Three steps Lemma]\label{lem:iig1}Let $(\X,\R)$ be a left-linear DPO-rewriting system with $\X$ an $\mathcal{M}$-adhesive category.
-Consider a derivation $\der{D}=\{\dder{D}_i\}_{i=0}^2$ and suppose that $(i_0,i_1)$ is a good independence pair between $\dder{D}_0$ and $\dder{D}_1$, $(a_0,a_1)$ one between $\dder{D}_1$ and $\dder{D}_2$ and $(e_0, e_1)$ one between $\dder{D}_0$ and $S_{a_0,a_1}(\dder{D}_2)$.
-Then the following properties hold true.
-	\begin{enumerate}
-		\item $S_{e_0,e_1}(\dder{D}_0)$ and $S_{a_0,a_1}(\dder{D}_1)$ are weakly sequentially independent.
-		\item If $S_{i_0, i_1}(\dder{D}_0)\updownarrow_!
-\dder{D}_2$ with a good independence pair $(\alpha_0, \alpha_1)$, then  $S_{i_0,i_1}(\dder{D}_1)$ and $S_{\alpha_0, \alpha_1}(\dder{D}_2)$ are weakly sequentially independent.
-	\end{enumerate}
-
-\end{lemma}
-\begin{proof}  As a preliminary step, we are going to use \Cref{def:filler,def:switch} to get some diagrams.
-First of all, let $(v,v')$ be the filler between $\dder{D}_0$ and $\dder{D}_1$ associated to $(i_0, i_1)$, then we have
-	\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){i_0}|(.7)\hole \ar[dr]^{h_0}&& L_1\ar@/^1cm/[ddll]^(.35){i_1}  \ar[dl]_{m_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){v}\ar[ur]^{r_0}&& G_1 && K_1 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){v'}\ar[dl]_{k_1}\ar[lu]_{l_1} \ar[dr]^{r_1}\\L_0 \ar@/_.8cm/[ddrr]_(.2){j_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&D_1 \ar[dr]|(.4)\hole^(.65){g_1} \ar[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.8cm/[ddll]^(.2){j_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0 &&P_1\ar[dr]_{q_1} \ar[dl]^{q_0}\ar[ur]^(.4){p_1}\ar[ul]_(.4){p_0}&&G_2\\L_1 \ar@/^.8cm/[uurr]^(.2){i_1} \ar[ur]_(.35){f_0\circ i_1}|(.61)\hole&&Q_0 \ar[ul]|(.4)\hole_(.65){s_0}\ar[dr]|(.5)\hole^(.65){t_0} &&Q_1\ar[ur]|(.4)\hole^(.65){t_1} \ar[dl]|(.5)\hole_(.65){s_1} && R_0  \ar[ul]^(.35){g_1\circ i_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){i_0}\\&K_1 \ar[ur]_{q_0\circ v'} \ar[dr]_{r_1} \ar[ul]^{l_1}\ar@/^.8cm/[uurr]_(.65){v'}&&H'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{q_1\circ v} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){v}\\&& R_1 \ar[ur]_{\hspace{-5pt}s_1\circ j_1}\ar@/^1cm/[uurr]^(.25){j_1}&& L_0 \ar[ul]^{t_0\circ j_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){j_0} |(.69)\hole }\]
-
-	Secondly, the filler $(u,u')$ induced by $(a_0, a_1)$ between $\dder{D}_1$ and $\dder{D}_2$ yields:
-	\[
-	\xymatrix{&&R_1 \ar@/_1cm/[ddrr]_(.35){a_0}|(.7)\hole \ar[dr]^{h_1}&& L_2\ar@/^1cm/[ddll]^(.35){a_1}  \ar[dl]_{m_2}\\&K_1\ar[dr]^{k_1}\ar[dl]_{l_1} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){u}\ar[ur]^{r_1}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){u'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_1 \ar@/_.8cm/[ddrr]_(.2){b_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_1}|(.61)\hole && D_1 \ar[dl]|(.4)\hole_(.65){f_1}\ar[ur]|(.5)\hole^(.7){g_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){b_1}|(.31)\hole|(.81)\hole\ar[dl]_{h_2}\\&G_1 &&P_2\ar[dr]_{d_1} \ar[dl]^{d_0}\ar[ur]^(.4){c_1}\ar[ul]_(.4){c_0}&&G_3\\L_2 \ar@/^.8cm/[uurr]^(.2){a_1} \ar[ur]_(.35){f_1\circ a_1}|(.61)\hole&&Q_2 \ar[ul]|(.4)\hole_(.65){x_1}\ar[dr]|(.5)\hole^(.65){y_1} &&Q_3\ar[ur]|(.4)\hole^(.65){y_2} \ar[dl]|(.5)\hole_(.65){x_2} && R_1  \ar[ul]^(.35){g_2\circ a_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){a_0}\\&K_2 \ar[ur]_{d_0\circ u'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){u'}&&G'_2&& K_1 \ar[ur]_{r_1} \ar[ul]^{d_1\circ u} \ar[dl]^{l_1} \ar@/_.8cm/[uull]^(.65){u}\\&& R_2 \ar[ur]_{\hspace{-5pt}x_2\circ b_1}\ar@/^1cm/[uurr]^(.25){b_1}&& L_1 \ar[ul]^{y_1\circ b_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){b_0} |(.69)\hole }\]
-
-	Finally, the filler $(w,w')$  between $\dder{D}_0$ and $S_{a_0,a_1}(\dder{D}_2)$ given by $(e_0, e_1)$ provides us with:
-\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){e_0}|(.7)\hole \ar[dr]^{h_0}&& L_2\ar@/^1cm/[ddll]^(.35){e_1}  \ar[dl]_{f_1\circ a_1}\\&K_0\ar[dr]^{k_0}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){w}\ar[ur]^{r_0}&& G_1 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){w'}\ar[dl]_{d_0\circ u'\hspace{-5pt}}\ar[lu]_{l_2} \ar[dr]^{r_2}\\L_0 \ar@/_.8cm/[ddrr]_(.2){o_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){m_0}|(.61)\hole && D_0 \ar[dl]|(.4)\hole_(.65){f_0}\ar[ur]|(.5)\hole^(.7){g_0}&&Q_2 \ar[dr]|(.4)\hole^(.65){y_1} \ar[ul]|(.5)\hole_(.65){x_1}&&R_2\ar@/^.8cm/[ddll]^(.2){o_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){x_2\circ b_1}\\&G_0 &&P_3\ar[dr]_{n_1} \ar[dl]^{n_0}\ar[ur]^(.4){u_1}\ar[ul]_(.4){u_0}&&G'_2\\L_2 \ar@/^.8cm/[uurr]^(.2){e_1} \ar[ur]_(.35){f_0\circ e_1}|(.61)\hole&&Q_4 \ar[ul]|(.4)\hole_(.65){z_0}\ar[dr]|(.5)\hole^(.65){z'_0} &&Q_5\ar[ur]|(.4)\hole^(.65){z'_1} \ar[dl]|(.5)\hole_(.65){z_1} && R_0  \ar[ul]^(.35){y_1\circ e_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){e_0}\\&K_2 \ar[ur]_{n_0\circ w'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){w'}&&G'_1&& K_0 \ar[ur]_{r_0} \ar[ul]^{n_1\circ w} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){w}\\&& R_2 \ar[ur]_{\hspace{-4pt}z_1\circ o_1}\ar@/^1cm/[uurr]^(.25){o_1}&& L_0 \ar[ul]^{z'_0\circ o_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){o_0} |(.69)\hole }\]
-So equipped we can turn to the prove of our claims.	
-	\begin{enumerate}
-		\item We have to construct the two dotted arrows in the diagram below.
-			\[\xymatrix@C=15pt{L_0 \ar[d]_{z'_0\circ o_0}&& K_0 \ar[d]_{n_1\circ w}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@{.>}@/^.35cm/[drrr]_(.4){\beta_0}|(.285)\hole \ar[dr]|(.28)\hole_{y_1\circ e_0} && L_1 \ar@{.>}@/_.35cm/[dlll]^(.4){\beta_1} \ar[dl]|(.28)\hole^{y_1\circ b_0}& K_1 \ar[d]^{d_1\circ u}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1 \ar[d]^{g_2\circ a_1}\\G'_1 && \ar[ll]^{z_1} Q_5 \ar[rr]_{z'_1}&& G'_2  && \ar[ll]^{x_2} Q_3 \ar[rr]_{y_2}&& G_3}\]
-
-		Consider the arrows $i_0\colon R_0\to D_1$ and $e_0\colon R_0\to Q_2$. An easy computation shows that
-			\begin{align*}
-				f_1\circ i_0&= h_0\\&=x_1\circ e_0
-			\end{align*}
-			entailing the existence of  the dotted $\beta'_0\colon R_0\to P_2$ in the diagram
-			\[\xymatrix{R_0 \ar@{.>}[dr]^{\beta'_0} \ar@/^.3cm/[drr]^{i_0} \ar@/_.3cm/[ddr]_{e_0}\\ &P_2 \ar[r]^{c_1} \ar[d]_{d_0}& D_1 \ar[d]^{f_1}\\ &Q_2\ar[r]_{x_1} & G_1}\]
-			If we define $\beta_0\colon R_0\to Q_3$ as $d_1\circ \beta'_1$, then we easily get that 
-		\begin{align*}
-			x_2\circ \beta_0&=x_2\circ d_2\circ \beta'_0\\&= y_1\circ d_0\circ \beta'_0\\&=y_1\circ e_0
-		\end{align*}
-
-		To define $\beta_1$, we proceed similarly. First consider  $i_1\colon L_1\to D_0$ and $b_0\colon L_1 \to Q_2$ and notice that
-		\begin{align*}
-			g_0\circ i_1&= m_1 \\&= x_1 \circ b_0
-		\end{align*}
-			implying the existence of $\beta'_1\colon L_1\to P_3$ fitting in the diagram below.
-			\[\xymatrix{L_1 \ar@{.>}[dr]^{\beta'_1} \ar@/^.3cm/[drr]^{i_1} \ar@/_.3cm/[ddr]_{b_0}\\ &P_3 \ar[r]^{u_0} \ar[d]_{u_1}& D_0 \ar[d]^{g_0}\\ &Q_2\ar[r]_{x_1} & G_1}\] 
-			Let $\beta_1\colon L_1\to Q_5$ be $n_1\circ \beta'_1$, then
-			\begin{align*}
-				z'_1 \circ \beta_1 & = z'_1 \circ n_1\circ \beta'_1\\&=y_1\circ u_1\circ \beta'_1\\&=y_1\circ b_0
-			\end{align*}
-		Therefore, $(\beta_0, \beta_1)$ is the wanted independence pair.
-
-\item  In addition to the three diagram above, we have a fourth one given by the filler $(\varphi_0, \varphi_1)$ associated to $(\alpha_0, \alpha_1)$. 
-\[\xymatrix{&&R_0 \ar@/_1cm/[ddrr]_(.35){\alpha_0}|(.7)\hole \ar[dr]^{g_1\circ i_0}&& L_2\ar@/^1cm/[ddll]^(.35){\alpha_1}  \ar[dl]_{m_2}\\
-&K_0\ar[dr]^{\hspace{-4pt}q_1\circ v}\ar[dl]_{l_0} \ar@/_.8cm/[ddrr]|(.36)\hole^(.65){\varphi}\ar[ur]^{r_0}&& G_2 && K_2 \ar@/^.8cm/[ddll]|(.36)\hole_(.65){\varphi'}\ar[dl]_{k_2}\ar[lu]_{l_2} \ar[dr]^{r_2}\\
-L_0 \ar@/_.8cm/[ddrr]_(.2){\gamma_0}|(.31)\hole|(.81)\hole \ar[dr]^(.4){\hspace{-4pt}t_0\circ j_0}|(.61)\hole && Q_1 \ar[dl]|(.4)\hole_(.65){s_1}\ar[ur]|(.5)\hole^(.7){t_1}&&D_2 \ar[dr]|(.4)\hole^(.65){g_2} \ar[ul]|(.5)\hole_(.65){f_2}&&R_2\ar@/^.8cm/[ddll]^(.2){\gamma_1}|(.31)\hole|(.81)\hole\ar[dl]_(.35){h_2}\\&H'_1 &&P_4\ar[dr]_{\lambda_1} \ar[dl]^{\lambda_0}\ar[ur]^(.4){\zeta_1}\ar[ul]_(.4){\zeta_0}&&G_3\\
-L_2 \ar@/^.8cm/[uurr]^(.2){\alpha_1} \ar[ur]_(.35){s_1\circ \alpha_1}|(.61)\hole&&Q_6 \ar[ul]|(.4)\hole_(.65){\xi_0}\ar[dr]|(.5)\hole^(.65){\xi'_0} &&Q_7\ar[ur]|(.4)\hole^(.65){\xi'_1} \ar[dl]|(.5)\hole_(.65){\xi_1} && R_0  \ar[ul]^(.35){g_2\circ \alpha_0}|(.61)\hole\ar@/_.8cm/[uull]_(.2){\alpha_0}\\&K_2 \ar[ur]_{\lambda_0\circ \phi'} \ar[dr]_{r_2} \ar[ul]^{l_2}\ar@/^.8cm/[uurr]_(.65){\phi'}&&H'_2&& K_0 \ar[ur]_{r_0} \ar[ul]^{\lambda_1\circ \phi} \ar[dl]^{l_0} \ar@/_.8cm/[uull]^(.65){\phi}\\&& R_2 \ar[ur]_{\hspace{-4pt}\xi_1\circ \gamma_1}\ar@/^1cm/[uurr]^(.25){\gamma_1}&& L_0 \ar[ul]^{\xi'_0\circ \gamma_0\hspace{-5pt}} \ar@/_1cm/[uull]_(.25){\gamma_0} |(.69)\hole }\]
-
-Our aim is to construct the dotted arrow in the following diagram.
-		\[\xymatrix@C=15pt{L_1 \ar[d]_{f_0\circ i_0}&& K_1 \ar[d]_{q_0\circ v'}\ar[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@{.>}@/^.35cm/[drrr]_(.4){\epsilon_0}|(.285)\hole \ar[dr]|(.28)\hole_{s_1\circ j_1} && L_2 \ar@{.>}@/_.35cm/[dlll]^(.4){\epsilon_1} \ar[dl]|(.28)\hole^{s_1\circ \alpha_1}& K_2 \ar[d]^{\lambda_0\circ \phi'}\ar[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]^{\xi_1\circ \gamma_1}\\G_0 && \ar[ll]^{s_0} Q_0 \ar[rr]_{t_0}&& H'_1  && \ar[ll]^{\xi_0} Q_6 \ar[rr]_{\xi'_0}&& H'_2}\]
-
-Let us start considering $j_1\colon R_1\to Q_1$ and $a_0\colon R_1\to D_2$. We have
-\begin{align*}
-	f_2\circ a_0&=h_1\\&=t_1\circ j_1
-\end{align*}
-and thus we get an arrow $\epsilon'_0\colon R_1\to P_4$ which makes the diagram below commutative.
-			\[\xymatrix{R_1 \ar@{.>}[dr]^{\epsilon'_0} \ar@/^.3cm/[drr]^{j_1} \ar@/_.3cm/[ddr]_{a_0}\\ &P_4 \ar[r]^{\zeta_0} \ar[d]_{\zeta_1}& Q_1 \ar[d]^{t_1}\\ &D_2\ar[r]_{f_2} & G_2}\] 
-We can then define $\epsilon_0\colon R_1\to Q_6$ to be $\lambda_0\circ \epsilon'_0$. For such an arrow we have a chain of identities:
-\begin{align*}
-	\xi_0\circ \epsilon_0&=\xi_0\circ \lambda_0\circ \epsilon'_0\\&=s_1\circ \zeta_0 \circ \epsilon'_0\\&=s_1\circ j_1
-\end{align*}
-
-Next, to define $\epsilon_1\colon L_2\to Q_0$ we take $e_1\colon L_2 \to D_0$ and $a_1\colon L_2\to D_1$. By definition we have $	g_0\circ e_1=f_1\circ a_1$, giving us the dotted arrow below
-	\[\xymatrix{L_2 \ar@{.>}[dr]^{\epsilon'_1} \ar@/^.3cm/[drr]^{a_1} \ar@/_.3cm/[ddr]_{e_0}\\ &P_1 \ar[r]^{p_1} \ar[d]_{p_0}& D_1 \ar[d]^{f_1}\\ &D_0\ar[r]_{g_0} & G_1}\] 
-Now, notice that 
-\begin{align*}
-	t_1\circ q_1\circ \epsilon'_1&=g_1\circ p_1\circ \epsilon'_1&=g_1\circ a_1\\&=m_2
-\end{align*}
-Hence $(\alpha_0, q_1\circ \epsilon'_1)$ is an independence pair for $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$.
-By hypothesis $S_{i_0, i_1}(\dder{D}_0)\updownarrow_!
-\dder{D}_2$ and thus $q_1\circ \epsilon'_1$ must coincide with $\alpha_1$.
-Now, let $\epsilon_1\colon L_2\to Q_0$ be $q_0\circ \epsilon'_1$.
-Computing we get
-\begin{align*}
-t_0\circ \epsilon_1&= t_0\circ q_0\circ \epsilon'_1\\&=s_1\circ q_1\circ \epsilon'_1\\&=s_1\circ \alpha_1
-\end{align*}
-Allowing us to conclude that  $S_{i_0,i_1}(\dder{D}_1)\updownarrow S_{\alpha_0, \alpha_1}(\dder{D}_2)$.
-\qedhere 
-			\end{enumerate}
-\end{proof}
-
-\subsubsection{Inversions and switch equivalence}
-\todo{richiamare cosa sono le inversioni}
-
-\begin{lemma}[Fundamental Lemma] Let $(\der{D}, \alpha, \omega)$ and $(\der{D'}, \alpha, \omega)$ be two decorated derivations and suppose that there exists a non-empty sequence $\{\der{D}_i\}_{i=0}^n$ a of derivations witnessing $\der{D}\equiv^s \der{D}'$.
-For every $i\in [0,n-1]$, let $\nu_i\colon [0, \lgh(\der{D})-1]\to [0, \lgh(\der{D})-1]$ be the $2$-cycle associated to the switch between $\der{D}_i$ and $\der{D}_{i+1}$, let also $\sigma$ be the associated consistent permutation between $(\der{D}, \alpha, \omega)$ and $(\der{D}', \alpha', \omega')$.
-Define $k$ as the maximum of the set
-\[M_\sigma:=\{j\in [0, \lgh(\der{D}-1] \mid \sigma(j+1) < \sigma(j) \}\]
-If every $\nu_i$ is an inversion for $\sigma$, then there exists a family $\{\nu'_i\}_{i=0}^n$ of inversions for $\sigma$ such that jj\todo{capire come scriverlo meglio, l} $\nu'_0=(k, k+1)$.
-\end{lemma}
-\begin{remark}
-	Since $\{\der{D}_i\}_{i=0}^n$ is non-empty, then $\sigma$ must be different from $\id{[0, \lgh(\der{D}-1)]}$ and $M_{\sigma}\neq \emptyset$.
-\end{remark}
-\begin{proof}
-	We proceed by induction on $n$.
-
-	\smallskip\noindent $n=1$. In this case there is nothing to prove.
-
-	\smallskip \noindent $n>1$. Then...
-\end{proof}
-
-\begin{corollary}
-	contenuto...
-\end{corollary}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{corollary}
-	contenuto...
-\end{corollary}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{corollary}
-	contenuto...
-\end{corollary}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{corollary}[No need for useless shifts]
-	contenuto...
-\end{corollary}
-\begin{proof}
-	contenuto...
-\end{proof}
-\newpage
-
-NOTES ON THE FUNDAMENTAL LEMMA WE NEED\todo{da integrare sopra}
-
-Everything is very tame, so that sequential independence coincides with switchability and we do not have ambiguity in the choice of an independence pair
-
-We start with the following situation.
-	\[\xymatrix@C=15pt{L_0\ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]_(.4){i_0}|(.285)\hole \ar[dr]|(.28)\hole_{h_0} && L_1 \ar@/_.35cm/[dlll]^(.4){i_1} \ar[dl]|(.28)\hole^{m_1}& K_1 \ar[d]^{k_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar[dr]|(.28)\hole_{h_1} \ar@/^.35cm/[drrr]_(.4){j_0}|(.285)\hole  && L_2 \ar@/_.35cm/[dlll]^(.4){j_1} \ar[dl]|(.28)\hole^{m_2}& K_2 \ar[d]^{k_2}\ar[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]^{h_2} \\G_0 && \ar[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar[ll]^{f_1} D_1 \ar[rr]_{g_1}&& G_2 && \ar[ll]^{f_2} D_2 \ar[rr]_{g_2}&& G_3 }\]
-
-	We can do two things:
-
-	FIRST SEQUENCE OF SWITCHINGS:
-
-	Switch the first two
-
-	\[\xymatrix@C=15pt{L_1\ar[d]_{f_0\circ i_1}&& K_1 \ar[d]_{k'_1}\ar[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){a_0}|(.285)\hole \ar[dr]|(.28)\hole_{h'_1} && L_0 \ar@/_.35cm/[dlll]^(.4){a_1} \ar[dl]|(.28)\hole^{m'_0}& K_0 \ar[d]^{k'_0}\ar[l]_{l_0} \ar[r]^{r_0} & R_0 \ar[dr]|(.28)\hole_{g_1\circ j_0} \ar@/^.35cm/[drrr]_(.4){b_0}|(.285)\hole  && L_2 \ar@/_.35cm/[dlll]^(.4){b_1} \ar[dl]|(.28)\hole^{m_2}& K_2 \ar[d]^{k_2}\ar[l]_{l_2} \ar[rr]^{r_2} && R_2 \ar[d]^{h_2} \\G_0 && \ar[ll]^{f'_0} D'_0 \ar[rr]_{g'_0}&& G'_1  && \ar[ll]^{f'_1} D'_1 \ar[rr]_{g'_1}&& G_2 && \ar[ll]^{f_2} D_2 \ar[rr]_{g_2}&& G_3 }\]
-
-	Moreover, we know that
-	\[m_0=f'_0\circ a_1 \qquad h_1=g'_1\circ a_0\]
-
-	Switch second and third 
-	\[\xymatrix@C=15pt{L_1\ar[d]_{f_0\circ i_1}&& K_1 \ar[d]_{k'_1}\ar[ll]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){c_0}|(.285)\hole \ar[dr]|(.28)\hole_{h'_1} && L_2 \ar@/_.35cm/[dlll]^(.4){c_1} \ar[dl]|(.28)\hole^{f'_1\circ b_1}& K_2 \ar[d]^{k'_2}\ar[l]_{l_2} \ar[r]^{r_2} & R_2 \ar[dr]|(.28)\hole_{h'_2} \ar@/^.35cm/[drrr]_(.4){d_0}|(.285)\hole  && L_0 \ar@/_.35cm/[dlll]^(.4){d_1} \ar[dl]|(.28)\hole^{\hat{m}_0}& K_0 \ar[d]^{\hat{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]^{g_2\circ b_0} \\G_0 && \ar[ll]^{f'_0} D'_0 \ar[rr]_{g'_0}&& G'_1  && \ar[ll]^{\hat{f}_1} \hat{D}_1 \ar[rr]_{\hat{g}_1}&& G'_2 && \ar[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 }\]
-	And we know that
-	\[m'_0=\hat{f}_1\circ d_1 \qquad h_2=g'_2\circ d_0\]
-	\todo{qua abbiamo usato il secondo lemma dei tre passi (quello condizionale)}Since the rewriting system is very tame and using the three steps lemmas we can characterize $c_0\colon R_1\to \hat{D}_1$ and $c_1\colon L_2\to D'_0$ as the unique arrows fitting in the diagrams
-\[\xymatrix@R=15pt@C=15pt{&&R_1 \ar@/_1.2cm/[dddl]_(.4){a_0}|(.63)\hole\ar[dl]^{j_0}\ar[dd]^{c'_0} \ar@{.>}[dr]^{c_0}\\&D_2 \ar[dl]^(.4){f_2}&&\hat{D}_1 \ar[dr]^{\hat{g}_1}\\G_2 && P\ar[dr]_{p_4} \ar[ur]_{p_3}\ar[dl]^{p_1} \ar[ul]^{p_2}&&G'_2\\& D'_1 \ar[ul]^{g'_1}&&D'_2 \ar[ur]_{f'_2}}\]
-
-\[\xymatrix@R=15pt@C=15pt{&&L_2 \ar[dl]^{j_1} \ar@/_1.2cm/[dddl]_(.4){z_1}|(.63)\hole\ar[dd]^{c'_1} \ar@{.>}[dr]^{c_1}\\&D_1 \ar[dl]^(.4){f_1}&&D'_0 \ar[dr]^{g'_0}\\G_1 && Q\ar[dr]_{q_4} \ar[ur]_{q_3}\ar[dl]^{q_1} \ar[ul]_{q_2}&&G'_1\\& D_0 \ar[ul]^{g_0}&&D'_1 \ar[ur]_{f'_1}}\]
-
-	Switch first and second 
-	\[\xymatrix@C=15pt{L_2\ar[d]_{f'_0\circ c_1}&& K_2 \ar[d]_{\hat{k}_2}\ar[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){e_0}|(.285)\hole \ar[dr]|(.28)\hole_{\hat{h}_2} && L_1 \ar@/_.35cm/[dlll]^(.4){e_1} \ar[dl]|(.28)\hole^{\hat{m}_1}& K_1 \ar[d]^{\hat{k}_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){t_0} \ar[dr]|(.28)\hole_{\hat{g}_1\circ c_0}   && L_0  \ar[dl]|(.28)\hole^{\hat{m}_0} \ar@/_.35cm/[dlll]^(.4){t_1}& K_0 \ar[d]^{\hat{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]^{g_2\circ b_0} \\G_0 && \ar[ll]^{\hat{f}_0} \hat{D}_0 \ar[rr]_{\hat{g}_0}&& \hat{G}_1  && \ar[ll]^{\tilde{f}_1} \tilde{D}_1 \ar[rr]_{\tilde{g}_1}&& G'_2 && \ar[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 }\]
-	Moreover
-	\[f_0\circ i_1=\hat{f}_0\circ e_1 \qquad h'_2=\tilde{g}_1\circ e_0\]
-	and $(t_0, t_1)$ is characterized using again very tameness and the first $3$-steps Lemma as the unique arrows fitting in:
-	\[\xymatrix{&R_1 \ar[dl]_{a_0} \ar@{.>}[dr]^{t_0} \ar@/^.4cm/[dd]|\hole^(.6){c_0}\ar[d]_{t'_0}\\ D'_1 \ar[d]_{g'_1}&P\ar[d]_{p_3} \ar[r]^{p_4} \ar[l]_{p_1}&D'_2\ar[d]^{f'_2}\\G'_1&\hat{D}_1 \ar[l]^{\hat{f}_1}\ar[r]_{\hat{g}_1}& G'_2}\]
-
-	\[\xymatrix@R=15pt@C=15pt{&&L_ 0\ar[dl]^{a_1} \ar@/_1.2cm/[dddl]_(.4){d_1}|(.63)\hole\ar[dd]^{t'_1} \ar@{.>}[dr]^{t_1}\\&D'_0 \ar[dl]^(.4){g'_0}&&\tilde{D}_1 \ar[dr]^{\tilde{f}_1}\\G'_1 && S\ar[dr]_{s_4} \ar[ur]_{s_3}\ar[dl]^{s_1} \ar[ul]_{s_2}&&\hat{G}_1\\& \hat{D}_1 \ar[ul]^{\hat{f}_1}&&\hat{D}_0 \ar[ur]_{\hat{g}_0}}\]
-
-	SECOND SEQUENCE OF SWITCHINGS:
-
-	Switch third and second
-
-	\[\xymatrix@C=15pt{L_0\ar[d]_{m_0}&& K_0 \ar[d]_{k_0}\ar[ll]_{l_0} \ar[r]^{r_0} & R_0 \ar@/^.35cm/[drrr]_(.4){z_0}|(.285)\hole \ar[dr]|(.28)\hole_{h_0} && L_2 \ar@/_.35cm/[dlll]^(.4){z_1} \ar[dl]|(.28)\hole^{f_1\circ j_1}& K_2 \ar[d]^{\check{k}_2}\ar[l]_{l_2} \ar[r]^{r_2} & R_2 \ar[dr]|(.28)\hole_{\check{h}_2} \ar@/^.35cm/[drrr]_(.4){w_0}|(.285)\hole  && L_1 \ar@/_.35cm/[dlll]^(.4){w_1} \ar[dl]|(.28)\hole^{\check{m}_1}& K_1 \ar[d]^{\check{k}_1}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1\ar[d]^{g_2\circ j_0} \\G_0 && \ar[ll]^{f_0} D_0 \ar[rr]_{g_0}&& G_1  && \ar[ll]^{\check{f}_1} \check{D}_1 \ar[rr]_{\check{g}_1}&& \check{G}_2 && \ar[ll]^{\check{f}_2} \check{D}_2 \ar[rr]_{\check{g}_2}&& G_3 }\]
-	Moreover
-	\[m_1=\check{f}_1\circ w_1 \qquad h_2=\check{g}_2\circ w_0\]
-
-	Switch second and first
-		\[\xymatrix@C=15pt{L_2\ar[d]_{f_0\circ z_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){y_0}|(.285)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_0 \ar@/_.35cm/[dlll]^(.4){y_1} \ar[dl]|(.28)\hole^{\check{m}_0}& K_0 \ar[d]^{\check{k}_0}\ar[l]_{l_0} \ar[r]^{r_0} & R_0 \ar[dr]|(.28)\hole_{\check{g}_1\circ z_0} \ar@/^.35cm/[drrr]_(.4){x_0}|(.285)\hole  && L_1 \ar@/_.35cm/[dlll]^(.4){x_1} \ar[dl]|(.28)\hole^{\check{m}_1}& K_1 \ar[d]^{\check{k}_1}\ar[l]_{l_1} \ar[rr]^{r_1} && R_1\ar[d]^{g_2\circ j_0} \\G_0 && \ar[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar[ll]^{\mathring{f}_1} \mathring{D}_1 \ar[rr]_{\mathring{g}_1}&& \check{G}_2 && \ar[ll]^{\check{f}_2} \check{D}_2 \ar[rr]_{\check{g}_2}&& G_3 }\]
-	As before we have
-	\[m_0=\check{f}_0\circ y_1 \qquad \check{h}_2=\mathring{g}_1\circ y_0\]
-	The really important thing to notice is that, by very tameness we have
-	\begin{align*}
-		f_0'\circ c_1&=f'_0\circ q_3\circ c'_1\\&=f_0\circ q_1\circ c'_1\\&=f_0\circ z_1
-	\end{align*}
-
-	\todo{GOOD! i primi match sono uguali, ora giochiamoci il primo lemma dei tre passi}
-
-	Switch second and third
-\[\xymatrix@C=15pt{L_2\ar[d]_{f_0\circ z_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/^.35cm/[drrr]_(.4){v_0}|(.285)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_1 \ar@/_.35cm/[dlll]^(.4){v_1} \ar[dl]|(.28)\hole^{\mathring{f}_1 \circ x_1}& K_1 \ar[d]^{\mathring{k}_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){u_0}|(.285)\hole\ar[dr]_{\check{h}_1}   && L_0 \ar@/_.35cm/[dlll]^(.4){u_1} \ar[dl]^{\mathring{m}_0}& K_0 \ar[d]^{\mathring{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0\ar[d]^{\check{g}_2\circ x_0} \\G_0 && \ar[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar[ll]^{\bar{f}_1} \bar{D}_1 \ar[rr]_{\bar{g}_1}&& \bar{G}_2 && \ar[ll]^{\bar{f}_2} \bar{D}_2 \ar[rr]_{\bar{g}_2}&& G_3 }\]
-
-\[\xymatrix@R=15pt@C=15pt{&&R_1 \ar@/_1.2cm/[dddl]_(.4){a_0}|(.63)\hole\ar[dl]^{j_0}\ar[dd]^{c'_0} \ar@{.>}[dr]^{c_0}\\&D_2 \ar[dl]^(.4){f_2}&&\hat{D}_1 \ar[dr]^{\hat{g}_1}\\G_2 && P\ar[dr]_{p_4} \ar[ur]_{p_3}\ar[dl]^{p_1} \ar[ul]^{p_2}&&G'_2\\& D'_1 \ar[ul]^{g'_1}&&D'_2 \ar[ur]_{f'_2}}\]
-
-\[\xymatrix@R=15pt@C=15pt{&&L_1 \ar[dl]^{w_1} \ar@/_1.2cm/[dddl]_(.4){i_1}|(.63)\hole\ar[dd]^{v'_1} \ar@{.>}[dr]^{v_1}\\&\check{D}_1 \ar[dl]^(.4){\check{f}_1}&&\check{D}_0 \ar[dr]^{g'_0}\\G_1 && \check{Q}\ar[dr]_{\check{q}_4} \ar[ur]_{\check{q}_3}\ar[dl]^{\check{q}_1} \ar[ul]_{\check{q}_2}&&\check{G}_1\\& D_0 \ar[ul]^{g_0}&&\mathring{D}_1 \ar[ur]_{\check{f}_1}}\]
-
-HUGE DIAGRAMF
-
-\[\xymatrix@C=15pt{
-  & K_1 \ar[d]^{\hat{k}_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){t_0} \ar[dr]|(.28)\hole_{\hat{g}_1\circ c_0}   && L_0  \ar[dl]|(.28)\hole^{\hat{m}_0} \ar@/_.35cm/[dlll]^(.4){t_1}& K_0 \ar[d]^{\hat{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0 \ar[d]^{g_2\circ b_0} \\G_0 && \ar[ll]^{\hat{f}_0} \hat{D}_0 \ar[rr]_{\hat{g}_0}&& \hat{G}_1  && \ar[ll]^{\tilde{f}_1} \tilde{D}_1 \ar[rr]_{\tilde{g}_1}&& G'_2 && \ar[ll]^{f'_2} D'_2 \ar[rr]_{g'_2}&& G_3 \\
-	L_2\ar[d]_{f_0\circ z_1} \ar[u]^{f'_0\circ c_1}&& K_2 \ar[d]_{\mathring{k}_2}\ar[ll]_{l_2} \ar[r]^{r_2} & R_2 \ar@/_.35cm/[urrr]^(.4){e_0}|(.285)\hole \ar[ur]|(.28)\hole^{\hat{h}_2} \ar@/^.35cm/[drrr]_(.4){v_0}|(.285)\hole \ar[dr]|(.28)\hole_{\mathring{h}_2} && L_1 \ar@/^.35cm/[ulll]_(.4){e_1} \ar[ul]|(.28)\hole_{\hat{m}_1} \ar@/_.35cm/[dlll]^(.4){v_1} \ar[dl]|(.28)\hole^{\mathring{f}_1 \circ x_1}& K_1 \ar[d]^{\mathring{k}_1}\ar[l]_{l_1} \ar[r]^{r_1} & R_1 \ar@/^.35cm/[drrr]_(.4){u_0}|(.285)\hole\ar[dr]_{\check{h}_1}   && L_0 \ar@/_.35cm/[dlll]^(.4){u_1} \ar[dl]^{\mathring{m}_0}& K_0 \ar[d]^{\mathring{k}_0}\ar[l]_{l_0} \ar[rr]^{r_0} && R_0\ar[d]^{\check{g}_2\circ x_0} \\G_0 && \ar[ll]^{\check{f}_0} \check{D}_0 \ar[rr]_{\check{g}_0}&& \check{G}_1  && \ar[ll]^{\bar{f}_1} \bar{D}_1 \ar[rr]_{\bar{g}_1}&& \bar{G}_2 && \ar[ll]^{\bar{f}_2} \bar{D}_2 \ar[rr]_{\bar{g}_2}&& G_3 }\]
-
-Now, by determinism we have isomorphisms $\phi_{\check{D}_0}\colon \check{D}_0\to \hat{D}_0$ $\phi_{\check{G}_1}\colon \check{G}_1\to \hat{G}_1$
-Notice that
-\begin{align*}
-	\hat{f}_0\circ \phi_{\check{D}_0}\circ v_1&= \check{f}_0\circ v_1\\&=\check{f}_0\circ \check{q}_3\circ v'_1\\&=f_0\circ \check{q}_1\circ v'_1\\&=f_0\circ i_1\\&=\hat{f}_0\circ e_1
-\end{align*}
-
-GOOD: $\phi_{\check{D}_0}$ sends $v_1$ to $e_1$, thus it respects the match of $L_1$. Automatically it sends $v_0$ to $e_0$.
-
-CHECK THAT $\check{g}_2\circ x_0=g_2\circ j_0$
-
-USO IL PRIMO LEMMA DEI TRE PASSI:
-
-	\[\xymatrix{&R_0 \ar[dl]_{i_0} \ar@{.>}[dr]^{x_0} \ar@/^.4cm/[dd]|\hole^(.6){j_0}\ar[d]_{x'_0}\\ D_1 \ar[d]_{g_1}&P'\ar[d]_{p'_3} \ar[r]^{p'_4} \ar[l]_{p'_1}&\check{D}_2\ar[d]^{\check{g}_2}\\G_2&D_2 \ar[l]^{f_2}\ar[r]_{g_2}& G_3}\]
-
-\[\xymatrix@R=15pt@C=15pt{&&L_ 0\ar[dl]^{I_1} \ar@/_1.2cm/[dddl]_(.4){d_1}|(.63)\hole\ar[dd]^{t'_1} \ar@{.>}[dr]^{t_1}\\&D'_0 \ar[dl]^(.4){g'_0}&&\tilde{D}_1 \ar[dr]^{\tilde{f}_1}\\G'_1 && S\ar[dr]_{s_4} \ar[ur]_{s_3}\ar[dl]^{s_1} \ar[ul]_{s_2}&&\hat{G}_1\\& \hat{D}_1 \ar[ul]^{\hat{f}_1}&&\hat{D}_0 \ar[ur]_{\hat{g}_0}}\]
-
-\section{Switch equivalence and concatenable traces}
-
-\begin{lemma}
-	\todo{abstract equivalence and switch }
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-\begin{definition}
-	\todo{tracce}
-\end{definition}
-
-Before moving forward, we will prove some other useful properties of the switch equivalence relation.
-
-\begin{lemma}
-	\todo{lemma 19}
-\end{lemma}
-\begin{proof}
-	contenuto...
-\end{proof}
-
-\begin{theorem}
-	\todo{preordine}
-\end{theorem}
-\begin{proof}
-	contenuto...
-\end{proof}
-
 \section{A class of well-behaved left-linear DPO rewriting systems}

### 2025-04-17 full_version/leftlinear.tex
aggiunto capitolo

@@
 \end{remark}
-
-\subsubsection{Equipping hypergraphs with equivalences}
-
-Moreover, we next observe that various classes of rewriting systems,
-comprising all the ones used in modelling the applications to the
-encoding of process calculi or of bio and chemical systems mentioned
-in the introduction, are actually well-switching.
-
-\todo{da fare}
-\subsubsection{Some examples of well-switching rewriting systems}
-
-\todo{Questa sezione è da riscrivere bene ma penso vada incorporata nella sez sui well.behaved}
-
-A first class consists of those rewriting systems over
-possibly hierarchical graphical structures obtained as algebras of
-suitable signatures where rules are constrained not to merge elements
-of top level sorts in the hierarchy (for graphs, nodes can be
-merged while edges cannot). The idea here is to consider graph
-structures as presheaves on categories in which there are objects that play 
-the role of \emph{roots}, i.e.~objects that are not the codomain of 
-any arrow besides the identity.
-
-\begin{definition}[Root-preserving graphical rewriting systems]
-	Let $\X$ be a category, an object $X\in \X$ is a \emph{root} if the only arrow with codomain $X$ is $\id{X}$.
-	The category $\gph{X}$ of \emph{$\X$-graphs} is the category
-	$\Set^{\X}$. A
-	\emph{root-preserving graphical rewriting system} is a left-linear
-	rewriting system $(\gph{X}, \R)$ such that for each rule
-	$(l\colon K\to L, r\colon K\to R)$ in $\R$ it holds
-	\begin{enumerate}
-		\item for every $X\in \X$ and $x\in L(X)$, there exists a root $Y$
-		and an arrow $f\colon Y\to X$ such that $x$ belongs to the image of
-		$L(f)\colon L(Y)\to L(X)$;
-		\item $r\colon K\to R$ is mono on the roots, i.e.~for every root $X\in \X$ the component $r_X:K(X)\to R(X)$ is injective.
-	\end{enumerate}
-\end{definition}
-
-For instance, the category $\cat{Graph}$ can be obtained
-by taking as $\X$ the category generated by $E \rightrightarrows V$. In this case $E$ is the only root, hence, condition $1$ asks that in the left-hand side of each rule
-there are no isolated nodes, while condition $2$ asks that the
-morphism $r: K \to R$ is injective on edges, i.e.~it can only merge nodes.
-
-\begin{lemma}{lemma}{lemVTame}
-	\label{bono}
-	All root-preserving graphical rewriting systems are well-switching.
-\end{lemma}
-
-Another interesting class of well-switching rewriting systems is given by e-graphs.
-
-\begin{example}[E-graphs]
-	Consider the category $\cat{EGraphs}$, where objects are (directed)
-	graphs endowed with an equivalence over nodes, and arrows are graph
-	morphisms that preserve the equivalence, as considered
-	in~\cite{BaldanGM06}, closely related to e-graphs~\cite{WNW:egg}. 
-	Formally, $\cat{EGraphs}$ can be seen as the
-	subcategory of the presheaf
-	$[E \rightrightarrows V \to Q, \cat{Set}]$ where objects are
-	constrained to have the component $V \to Q$ surjective.
-
-	Explicitly, an
-	e-graph $G$ is a triple $\langle s_G, t_G, q_G \rangle$ where
-	$s_G, t_G: E_G \rightrightarrows V_G$ provides the graphical
-	structure, while the surjective function $q_G : V_G \to Q_G$ maps
-	each node to the corresponding equivalence class. 
-	Notice that the inclusion functor into  $[E \rightrightarrows V \to Q, \cat{Set}]$ 
-	creates pullbacks and pushouts \cite{mac2013categories}, so that they are computed component-wise.
-
-	A morphism in $\cat{EGraph}$ is mono if the components over $E$
-	and $V$ are mono, i.e.~if it is mono as a morphism in
-	$\cat{Graph}$. It is regular mono if also the component on
-	$Q$ is mono, i.e.~if it reflects equivalence classes besides
-	preserving them.
-This characterisation of regular monos and the fact that pullbacks and pushouts are computed component-wise allows us to prove quasi-adhesivity of $\cat{EGraphs}$ at once.
-Moreover, one can deduce that every rewriting system $(\X, \R)$ that is left-linear with respect to $\reg(\cat{EGraphs})$ is strong enforcing: this is done exploiting again the inclusion functor into $[E \rightrightarrows V \to Q, \cat{Set}]$.
-
-	Left-linear rewriting systems with respect to $\reg(\cat{EGraphs})$ are well-switching. They have been used in~\cite{BaldanGM06} for the graphical implementation of nominal calculi, where,
-	differently from~\cite{Gad07}, as a result of name passing the received name is not merged with a local one, but put in the same equivalence class, better tracing the causal dependencies among reductions.
-\end{example}
 
@@
 		Therefore, $(\beta_0, \beta_1)$ is the wanted independence pair.
-		\item Here we assume that
-		$\dder{D}_1$ and $\dder{D}_2$ are switchable  with an
-		independence pair $(\alpha_0, \alpha_1)$ and that
-		$\dder{D}_0$ and $S_{\alpha_0, \alpha_1}(\dder{D}_2)$ are switchable.
-		% 
-		Hence, in addition to the three diagrams above, we have a fourth one, depicted in \Cref{fi:fourth}.
-		\begin{figure}[h]
-			\centering
-			$\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){\alpha_0}|(.7)\hole \ar[dr]^{\hspace{-1pt}g_1\circ i_0}&& L_2\ar@/^.8cm/[ddll]^(.2){\alpha_1}  \ar[dl]_{m_2\hspace{-2pt}}\\
+		\item By hypothesis, there is a independence pair $(\alpha_0, \alpha_1)$ between 	$\dder{D}'_0$ and $\dder{D}_2$. Thus by \Cref{rem:quadrati} we have a fourth diagram.
+		\[\xymatrix@C=15pt@R=15pt{&&R_0 \ar@/_.8cm/[ddrr]_(.2){\alpha_0}|(.7)\hole \ar[dr]^{\hspace{-1pt}g_1\circ i_0}&& L_2\ar@/^.8cm/[ddll]^(.2){\alpha_1}  \ar[dl]_{m_2\hspace{-2pt}}\\
 				&K_0\ar[dr]^{\hspace{-4pt}q_1\circ v_0}\ar@{>->}[dl]_{l_0} \ar@/_.6cm/[ddrr]|(.36)\hole^(.65){\phi_0}\ar[ur]^{r_0}&& G_2 && K_2 \ar@/^.6cm/[ddll]|(.36)\hole_(.65){\phi_2}\ar[dl]_{k_2}\ar@{>->}[lu]_{l_2} \ar[dr]^{r_2}\\
@@
 				\ar@/_.8cm/[uull]_(.2){\gamma_0} |(.69)\hole 
-			}	$
-			\caption{Picture for the proof of \Cref{lem:indep-global-left}: switch of $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$.}
-			\label{fi:fourth}
-		\end{figure}
+			}	\]
 
@@
 
-		We can take the arrows $j_1\colon R_1\to Q_1$, 
-		$a_0\colon R_1\to D_2$, $e_1\colon L_2 \to D_0$ and $a_1\colon L_2\to D_1$ and notice that
-		\[	f_2\circ a_0 =h_1 =t_1\circ j_1 \qquad   g_0\circ e_1=f_1\circ a_1\]
-		and thus we get the dotted arrows $\epsilon'_0\colon R_1\to P_4$, $\epsilon'_1\colon L_2\to P:1$ 
+		Let us consider the arrows $j_1\colon R_1\to Q_1$, 
+		$a_0\colon R_1\to D_2$, $e_1\colon L_2 \to D_0$ and $a_1\colon L_2\to D_1$, on the one hand we know that $g_0\circ e_1=f_1\circ a_1$, while, on the other hand we also have:
+		\begin{align*}
+			f_2\circ a_0 &=h_1 \\&=t_1\circ j_1		\end{align*}
+		Thus we get the dotted arrows $\epsilon'_0\colon R_1\to P_4$, $\epsilon'_1\colon L_2\to P:1$ 
 		\[\xymatrix{R_1 \ar@{.>}[dr]^{\epsilon'_0} 
@@
 		Now, notice that
-		\[
-		t_1\circ q_1\circ \epsilon'_1  =g_1\circ p_1\circ \epsilon'_1  =g_1\circ a_1 =m_2
-		\]
+		\begin{align*}
+			m_2&=g_1\circ a_1\\
+			&=g_1\circ p_1\circ \epsilon'_1\\&=
+		t_1\circ q_1\circ \epsilon'_1 
+			\end{align*}
+
 		Hence $(\alpha_0, q_1\circ \epsilon'_1)$ is an independence pair
-		for $S_{i_0, i_1}(\dder{D}_0)$ and $\dder{D}_2$. By hypothesis $(\X, \R)$ is well-switching and therefore
+		for $\dder{D}'_0$ and $\dder{D}_2$. By hypothesis $(\X, \R)$ is well-switching and therefore
 		$q_1\circ \epsilon'_1$ must coincide with $\alpha_1$.
@@
 		\epsilon'_1$. Then for these  arrows we have  identities
-		\begin{align*}
-			\xi_0\circ \epsilon_0 & =\xi_0\circ \lambda_0\circ \epsilon'_0 =s_1\circ \zeta_0 \circ \epsilon'_0=s_1\circ j_1\\	t_0\circ \epsilon_1 & = t_0\circ q_0\circ \epsilon'_1 =s_1\circ q_1\circ \epsilon'_1=s_1\circ \alpha_1
-		\end{align*}
-		Allowing us to conclude that
-		$S_{i_0,i_1}(\dder{D}_1)$ and $S_{\alpha_0,
-			\alpha_1}(\dder{D}_2)$ are switchable.  \qedhere 
+		\[\begin{split}
+			\xi_0\circ \epsilon_0 & =\xi_0\circ \lambda_0\circ \epsilon'_0 \\&=s_1\circ \zeta_0 \circ \epsilon'_0\\&=s_1\circ j_1
+		\end{split} \qquad \begin{split}
+		t_0\circ \epsilon_1 & = t_0\circ q_0\circ \epsilon'_1\\& =s_1\circ q_1\circ \epsilon'_1\\&=s_1\circ \alpha_1
+		\end{split}\]
+
+		And so we can conclude.  \qedhere 
 	\end{enumerate}
@@
 \end{proof}
-
-\section{A class of well-behaved left-linear DPO rewriting systems}

### 2025-04-18 full_version/leftlinear.tex
coerenza

@@
 	\begin{enumerate}
-		\item if $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ is an abstraction equivalence between $\der{D}$ and another derivation $\der{F}=\{\dder{F}_i\}_{i=0}^1$, then $\phi^{-1}_{G_0}*\der{E}*\phi_{G_2}$ is a pre-switch for $\der{F}$ along $(\phi_{D_1}\circ i_0, \phi_{D_0}\circ i_1 )$;
+		\item if $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ is an abstraction equivalence between $\der{D}$ and $\der{F}=\{\dder{F}_i\}_{i=0}^1$, then $\phi^{-1}_{G_0}*\der{E}*\phi_{G_2}$ is a pre-switch for $\der{F}$ along $(\phi_{D_1}\circ i_0, \phi_{D_0}\circ i_1 )$;
 		\item if $\{\psi_X\}_{X\in \Deltamin(\der{E})}$ is an abstraction equivalence between $\der{E}$ and $\der{G}=\{\dder{G}_{i}\}_{i=0}^1$, then $\psi_{G_0}*\der{G}*\psi^{-1}_{G_2}$ is a pre-switch for $\der{D}$ along $(i_0, i_1)$.
@@
 	and $\der{D}_1$.  If $\der{E}=\{\dder{E}_i\}_{i=0}^1$ is a
-	pre-switch of $\der{D}$ along $(i_0, i_1)$, then there is an arrow
-	$z_0\colon P\to D_{\der{E},0}$ in $\mathcal{M}$ fitting in the square below.
-	\[\xymatrix{P \ar@{.>}[r]^-{z_0}  \ar@{>->}[d]_{p_0}& D_{\der{E}, 0} \ar@{>->}[d]^{f_{\der{E},0}} \\ D_0 \ar@{>->}[r]_{f_0} & G_0 }\]
+	pre-switch of $\der{D}$ along $(i_0, i_1)$, then there is a unique arrow
+	$z_0\colon P\to D_{\der{E},0}$ fitting in the square below. Moreover, such arrow is in $\mathcal{M}$.
+	\[\xymatrix{P \ar@{>.>}[r]^-{z_0}  \ar@{>->}[d]_{p_0}& D_{\der{E}, 0} \ar@{>->}[d]^{f_{\der{E},0}} \\ D_0 \ar@{>->}[r]_{f_0} & G_0 }\]
 \end{corollary}
@@
 	Now the thesis follows applying \Cref{lem:radj} to the pair of squares on the right.
+Since $f_0$ and $p_0$ are element of $\mathcal{M}$, then $f_{\der{E},0}\circ z_0$ is in $\mathcal{M}$ too and so $z_0$ is in $\mathcal{M}$ by \Cref{prop:deco}.
 	\end{proof}
@@
 \begin{example}\label{ex:abs2}
-Let $\der{D}$ be the derivation of \Cref{ex:abs} and consider the pre-switch $\der{F}$. Then we can build the diagram belo
+Let $\der{D}$ be the derivation of \Cref{ex:abs} and consider the pre-switch $\der{F}$. Then we can build the diagram below
 	\[\xymatrix@C=20pt@R=20pt{&&1 \ar@{>->}@/_.9cm/[ddrr]_(.2){\delta^3_0}|(.72)\hole
@@
 	\[
-	\xymatrix@R=15pt@C=20pt{
+	\xymatrix@R=20pt@C=20pt{
 		{L_1} \ar[d]_{m_0'}
@@
 	We say that $\der{E}$ is a \emph{switch} for $\der{D}$ along $(i_0, i_1)$ if there is an arrow $z_1\colon P\to D'_1$ fitting in the diagram below, where $z_0\colon P\to D'_0$ is the arrow constructed in \Cref{lem:cose}.
-	\[\xymatrix@R=18pt{D'_0  \ar[d]_{g'_0}& P \ar[r]^{p_1} \ar[l]_{z_0} \ar@{.>}[d]^{z_1} & D_1 \ar[d]^{g_1}\\ G'_1 & D'_1 \ar[r]_{g'_1} \ar@{>->}[l]^{f'_1} & G_2}\]
+	\[\xymatrix@R=18pt{D'_0  \ar[d]_{g'_0}& P \ar[r]^{p_1} \ar@{>->}[l]_{z_0} \ar@{.>}[d]^{z_1} & D_1 \ar[d]^{g_1}\\ G'_1 & D'_1 \ar[r]_{g'_1} \ar@{>->}[l]^{f'_1} & G_2}\]
 
@@
 		\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_0}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
-		&&P\ar@{.>}[dr]_{z_1}	\ar@{>}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
+		&&P\ar@{.>}[dr]_{z_1}	\ar@{>->}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
 \end{remark}
@@
 \begin{remark}\label{rem:un}
-	Notice that, since $f'_1$ belongs to $\mathcal{M}$, there is at most one arrow $z_1\colon P\to D'_1$ such that $f'{1}\circ z_1=g'_0\circ z_0$.
+	Notice that, since $f'_1$ belongs to $\mathcal{M}$, there is at most one arrow $z_1\colon P\to D'_1$ such that $f'_{1}\circ z_1=g'_0\circ z_0$.
 \end{remark}
@@
 	\smallskip \noindent $(2\Rightarrow 1)$. By hypothesis the solid part of the diagram below commutes.
-	\[\xymatrix@C=30pt{P \ar[r]^{z_0} \ar@{.>}[dr]^{z_1}\ar[d]_{p_1} & D'_0 \ar[r]^{g'_0} & G'_1 \ar@{>->}[dr]^{\iota'_{1, G'_1}}\\ D_1 \ar[dr]_{g'_1}& D'_1 \ar[d]^{g'_1}\ar@{>->}[r]^{f'_1} &G'_1 \ar@{>->}[r]^{\iota'_{1, G'_1}} &\lpro \dder{E}_0 \rpro 	\ar@{>->}[d]^{p_1} \\ & G'_1 	\ar[rr]_{\iota_{\der{E}, G_2}}&& \tpro{E} }\]
+	\[\xymatrix@C=30pt{P \ar@{>->}[r]^{z_0} \ar@{.>}[dr]^{z_1}\ar[d]_{p_1} & D'_0 \ar[r]^{g'_0} & G'_1 \ar@{>->}[dr]^{\iota'_{1, G'_1}}\\ D_1 \ar[dr]_{g'_1}& D'_1 \ar[d]^{g'_1}\ar@{>->}[r]^{f'_1} &G'_1 \ar@{>->}[r]^{\iota'_{1, G'_1}} &\lpro \dder{E}_0 \rpro 	\ar@{>->}[d]^{p_1} \\ & G'_1 	\ar[rr]_{\iota_{\der{E}, G_2}}&& \tpro{E} }\]
 
@@
 \end{proof}
-\iffalse 
-We turn now to simmetry of the switchability relation. Surely one desires an analog of \Cref{rem:switch} even for switches: this is assured by the following proposition.
-
-\begin{proposition}\label{prop:pb}
-	Let $\der{D}:=\{\dder{D}_{i}\}_{i=0}^1$ be the derivation below, with $(i_0, i_1)$ an independence pair between $\dder{D}_0$  and $\dder{D}_1$.
+
+By \Cref{thm:switch_uni} and \Cref{ex:abs2} we know that being a switch is not a property invariant under  abstraction equivalence. Nonetheless we  can still prove an analog to \Cref{lem:abs}.
+
+\begin{proposition}\label{prop:switchabs}
+	Let $\der{D}=\{\dder{D}_i\}_{i=0}^1$ be the following derivation:
 \[\xymatrix@R=20pt@C=20pt{L_0 \ar[d]_{m_0}&& K_0
@@
 \]
-
-	If $\der{E}:=\{\dder{E}_{i}\}_{i=0}^1$ is a switch for $\dder{D}$ along $(i_0, i_1)$, then the square below is a pullback.
-	\[\xymatrix{P  \ar[r]^-{z_1} \ar[d]_{z_0}& D_{\der{E}, 1} \ar@{>->}[d]^{f_{\der{E},1}} \\ D_{\der{E},0} \ar[r]_{g_{\der{E},0}}& G_{\der{E},1}}\]
-
-	In particular, the arrow $z_0\colon P\to D_{\der{E},0}$ belongs to $\mathcal{M}$.
+and suppose that the derivation $\der{E}$ below is a switch for $\der{D}$ along $(i_0,i_1)$.
+\[
+\xymatrix@R=20pt@C=20pt{
+	{L_1} \ar[d]_{m_0'}
+	&&  {K_1} \ar@{>->}[ll]_{l_1} \ar[r]^{r_1} \ar[d]_{k_0'}
+	&  {R_1} \ar[dr]|(.33)\hole_{h_0'}  \ar@/^.25cm/@{>}_(.4){i_0'}|(.32)\hole[drrr]
+	& & 
+	{L_0}\ar[dl]|(.33)\hole^{m_1'} \ar@/_.25cm/@{>}^(.4){i_1'}[dlll] 
+	&  {K_0} \ar@{>->}[l]_{l_0} \ar[rr]^{r_0} \ar[d]^{k_1'}
+	& & {R_0} \ar[d]^{h_1'} \\		
+	{G_0}
+	& & {D_0'} \ar@{>->}[ll]^{f_0'} \ar[rr]_{g_0'}
+	& &  {G'_1} 
+	& &  {D_1'} \ar@{>->}[ll]^{f_1'} \ar[rr]_{g_1'}
+	& & {G_2}  }
+\]
+
+Then the following hold true:
+\begin{enumerate}
+	\item if $\{\phi_X\}_{X\in \Deltamin(\der{D})}$ is an abstraction equivalence between $\der{D}$ and $\der{F}=\{\dder{F}_i\}_{i=0}^1$ such that
+	\[\phi_{G_0}=\id{G_0} \qquad \phi_{G_2}=\id{H_2}\] 
+	then $\der{E}$ is a switch for $\der{F}$ along $(\phi_{D_1}\circ i_0, \phi_{D_0}\circ i_1 )$;
+	\item if $\{\psi_X\}_{X\in \Deltamin(\der{E})}$ is an abstraction equivalence between $\der{E}$ and $\der{G}=\{\dder{G}_{i}\}_{i=0}^1$ such that 
+	\[\phi_{G_0}=\id{G_0} \qquad \phi_{G_2}=\id{H_2}\] 
+	 then $\der{G}$ is a switch for $\der{D}$ along $(i_0, i_1)$.
+	\end{enumerate}
 \end{proposition}
 \begin{proof}
-	Take two arrows $t_0\colon T\to D_{\der{E}_1}$ and $t_1\colon T\to D_{\der{E},0}$ such that \[f_{\der{E},1}\circ t_1=g_{\der{E},0}\circ t_0\]
-
-	Thus we have
-	\begin{align*}
-		\iota_{\der{E}, G_0}\circ f_{\der{E},0}\circ t_0=&\iota_{\der{E}, D_{\der{E},0}}\circ t_0\\=&\iota_{\der{E}, G_1}\circ g_{\der{E},0}\circ t_0\\=&\iota_{\der{E}, G_1}\circ f_{\der{E},1}\circ t_1\\&= \iota_{\der{E}, D_{\der{E},1}}\circ t_1\\&=\iota_{\der{E}, G_2}\circ g_{\der{E},1} \circ t_1
+		\begin{enumerate} 
+	\item 		Let $\der{F}$ be the derivation given by the diagram below.
+\[
+\xymatrix@R=20pt@C=20pt{
+	{L_0} \ar[d]_{m_{\der{F}, 0}}
+	&&  {K_0} \ar@{>->}[ll]_{l_0} \ar[r]^{r_0} \ar[d]_{k_{\der{F}, 0}}
+	&  {R_0} \ar[dr]|(.33)\hole_{h_{\der{F}, 0}}  \ar@/^.25cm/@{>}^(.2){\phi_{D_1} \circ i_0}|(.32)\hole[drrr]
+	& & 
+	{L_1}\ar[dl]|(.33)\hole^{m_{\der{F}, 1}} \ar@/_.25cm/[dlll]_(.2){\phi_{D_0} \circ i_1} 
+	&  {K_1} \ar@{>->}[l]_{l_1} \ar[rr]^{r_1} \ar[d]^{k_{\der{F}, 1}}
+	& & {R_0} \ar[d]^{h_{\der{F}, 1}} \\		
+	{G_0}
+	& & {D_{\der{F},0}} \ar@{>->}[ll]^{f_{\der{F}, 0}} \ar[rr]_{g_{\der{F}, 0}}
+	& &  {G_{\der{F}, 1}} 
+	& &  {D_{\der{F}, 1}} \ar@{>->}[ll]^{f_{\der{F}, 1}} \ar[rr]_{g_{\der{F}, 1}}
+	& & {G_2}  }
+\]
+
+By \Cref{lem:abs} and our hypotheses, we know that $\der{E}$ is a pre-switch, thus by \Cref{lem:cose} we can consider the two diagrams below, whose right halves are pullbacks.
+\[\xymatrix{D'_0 \ar@{>->}[d]_{f'_0}& P_{\der{F}} \ar@{>->}[d]^{p_{\der{F},0}} \ar[r]^{p_{\der{F},1}}\ar@{>->}[l]_{z_{\der{F},0}} & D_{\der{F},1} \ar@{>->}[d]^{f_{\der{F},1}}& D'_0 \ar@{>->}[d]_{f'_0} & P \ar[r]^{p_1} \ar@{>->}[d]^{p_0} \ar@{>->}[l]_{z_0}& D_1 \ar@{>->}[d]^{f_1}\\ G_0 & D_{\der{F}, 0} \ar[r]_{g_{\der{F},0}} \ar@{>->}[l]^{f_{\der{F},0}} & G_{\der{F},1} & G_0 & D_0 \ar[r]_{g_{0}} \ar@{>->}[l]^{f_{0}} & D_1}\]
+
+We can build the following other two diagrams.
+
+\[\xymatrix{P \ar[rr]^{p_1} \ar@{>->}[dd]_{p_0} \ar@{.>}[dr]^{\alpha}&& D_1 \ar[d]_{\phi_{D_1}} \ar@/^.8cm/[ddd]^{f_1}& P_{\der{F}} \ar@{.>}[dr]^{\beta}\ar[rr]^{p_{\der{F},1}} \ar@{>->}[dd]_{p_{\der{F},0}} &&D_{\der{F},1} \ar[d]_{\phi^{-1}_{D_1}} \ar@/^.8cm/[ddd]^{f_{\der{F},1}}\\& P_{\der{F}} \ar@{>->}[d]_{p_{\der{F},0}} \ar[r]^{p_{\der{F},1}} & D_{\der{F},1} \ar@{>->}[d]_{f_{\der{F},1}}&  & P \ar[r]^{p_1} \ar@{>->}[d]_{p_0} & D_1 \ar@{>->}[d]_{f_1}\\ D_0  \ar@/_.4cm/[drr]_{g_0}\ar[r]^-{\phi_{D_0}} & D_{\der{F}, 0} \ar[r]_{g_{\der{F},0}}  & G_{\der{F},1} & D_{\der{F},0} \ar@/_.4cm/[drr]_{g_{\der{F},0}} \ar[r]^{\phi^{-1}_{D_0}}& D_0 \ar[r]_{g_{0}}  & D_1 \\ && G_1 \ar[u]^{\phi_{G_1}}&&&G_{\der{F},1} \ar[u]^{\phi^{-1}_{G_1}}}\]
+
+If we compute we get
+\[\begin{split}
+	p_{\der{F},1}\circ \alpha \circ \beta &= \phi_{D_1}\circ p_1\circ \beta \\&=\phi_{D_1}\circ \phi^{-1}_{D_1}\circ p_{\der{F},1}\\&=p_{\der{F},1}
+\end{split} \qquad \begin{split}
+p_{1}\circ \beta \circ \alpha &= \phi^{-1}_{D_1}\circ p_{\der{F},1}\circ \alpha \\&=\phi^{-1}_{D_1}\circ \phi_{D_1}\circ p_{1}\\&=p_{1}
+\end{split}\]
+\[\begin{split}
+	p_{\der{F},0}\circ \alpha \circ \beta &= \phi_{D_0}\circ p_0\circ \beta \\&=\phi_{D_0}\circ \phi^{-1}_{D_0}\circ p_{\der{F},0}\\&=p_{\der{F},0}
+\end{split} \qquad \begin{split}p_{0}\circ \beta \circ \alpha &= \phi^{-1}_{D_0}\circ p_{\der{F},0}\circ \alpha \\&=\phi^{-1}_{D_0}\circ \phi_{D_0}\circ p_{0}\\&=p_{0}
+\end{split}\]
+	and so $\alpha$ and $\beta$ are one the inverse of the other. Moreover, by hypothesis we know that $f_{\der{F},0}\circ \phi_{D_0}=f_{0}$, so that:
+	\begin{align*}
+		f'_0\circ z_{\der{F},0}\circ \alpha &= f_{\der{F},0}\circ p_{\der{F},0}\circ \alpha \\&=f_{\der{F},0}\circ \phi_{D_0}\circ p_0\\&=f_0\circ p_0\\&=f'_{0}\circ z_0
 	\end{align*}
-
-	By \Cref{cor:ele} we know that there exists a unique $t\colon T\to D_{}$
-\end{proof}
-
-\begin{corollary}
+	therefore $z_{\der{F},0}\circ \alpha=z_0$ and $z_0\circ \beta=z_{\der{F},0}$.
+
+	Since $\phi_{G_2}$ is the identity, then $g_{\der{F},1}\circ \phi_{D_1}=g_1$, hence:
+	\begin{align*}
+		\iota_{\der{E}, G_2} \circ g_{\der{F}, 1}\circ p_{\der{F}, 1}&=\iota_{\der{E}, G_2} \circ g_{\der{F}, 1}\circ \phi_{D_1}\circ p_1 \circ \beta\\&=\iota_{\der{E}, G_2} \circ g_{1}\circ p_1\circ \beta\\&=\iota_{\der{E}, G'_1}\circ g'_0\circ z_0 \circ \beta \\&=\iota_{\der{E}, G'_1}\circ g'_0\circ z_{\der{F},0}
+	\end{align*}
+	We can conclude by \Cref{lem:equi}.
+
+	\item By the second point of \Cref{lem:abs} we know that $\der{G}$ is a pre-switch along $(i_0, i_1)$. Suppose that $\der{G}$ is given by the derivation below.
+	\[
+	\xymatrix@R=20pt@C=20pt{
+		{L_0} \ar[d]_{m_{\der{G}, 0}}
+		&&  {K_0} \ar@{>->}[ll]_{l_0} \ar[r]^{r_0} \ar[d]_{k_{\der{G}, 0}}
+		&  {R_0} \ar[dr]|(.33)\hole_{h_{\der{G}, 0}}  \ar@/^.25cm/@{>}^(.2){\phi_{D_1} \circ i_0}|(.32)\hole[drrr]
+		& & 
+		{L_1}\ar[dl]|(.33)\hole^{m_{\der{G}, 1}} \ar@/_.25cm/[dlll]_(.2){\phi_{D_0} \circ i_1} 
+		&  {K_1} \ar@{>->}[l]_{l_1} \ar[rr]^{r_1} \ar[d]^{k_{\der{G}, 1}}
+		& & {R_0} \ar[d]^{h_{\der{G}, 1}} \\		
+		{G_0}
+		& & {D_{\der{G},0}} \ar@{>->}[ll]^{f_{\der{G}, 0}} \ar[rr]_{g_{\der{G}, 0}}
+		& &  {G_{\der{G}, 1}} 
+		& &  {D_{\der{G}, 1}} \ar@{>->}[ll]^{f_{\der{G}, 1}} \ar[rr]_{g_{\der{G}, 1}}
+		& & {G_2}  }
+	\]
+	Again by \Cref{lem:cose} we know that there are diagrams as the following ones, whose common right half is a pullback.
+\[\xymatrix{D_{\der{G},0} \ar@{>->}[d]_{f_{\der{G},0}}& P \ar@{>->}[d]^{p_{0}} \ar[r]^{p_1}\ar@{>->}[l]_-{z_{\der{G},0}} & D_{1} \ar@{>->}[d]^{f_{1}}& D'_0 \ar@{>->}[d]_{f'_0} & P \ar[r]^{p_1} \ar@{>->}[d]^{p_0} \ar@{>->}[l]_{z_0}& D_1 \ar@{>->}[d]^{f_1}\\ G_0 & D_{0} \ar[r]_{g_{0}} \ar@{>->}[l]^{f_{0}} & G_{1} & G_0 & D_0 \ar[r]_{g_{0}} \ar@{>->}[l]^{f_{0}} & D_1}\]
+
+Since $\psi_{G_0}$ is $\id{G_0}$ then $f_{\der{G},0}\circ \psi_{D'_0}=f'_0$. Similarly, since $\psi_{G_2}=\id{G_2}$, then $g_{\der{G},1}\circ \psi_{D'_1}=g'_1$. Now, from the first equality we have
+\begin{align*}
+	f_{\der{G},0} \circ \psi_{D'_0}\circ z_0&=f'_0 \circ z_0\\&= f_0\circ p_0\\&=f_{\der{G},0} \circ z_{\der{G},0}
+\end{align*}
+and so $\psi_{D'_0}\circ z_0=z_{\der{G},0}$.
+
+By \Cref{rem:abscol}, we know that there exists an isomorphism $\Psi\colon \tpro{E}\to \tpro{G}$ such that
+\[\Psi \circ \iota_{\der{E}, G_0}=\iota_{\der{G}, G_0} \quad \Psi \circ \iota_{\der{E}, G_1}=\iota_{\der{G}, G_{\der{G},1}}\circ \psi_{G'_1} \quad \Psi \circ \iota_{\der{E}, G_2}=\iota_{\der{G}, G_2} \]
+
+Thus:
+\begin{align*}
+	\iota_{\der{G},G_2}\circ g_1\circ p_1&= \Psi \circ \iota_{\der{E}, G_2}\circ g_1\circ p_1\\&=\Psi \circ \iota_{\der{E}, G'_1} \circ g'_0\circ z_0\\&=\iota_{\der{G}, G_{\der{G},1}}\circ \psi_{G'_1}\circ g'_0\circ z_0\\&=\iota_{\der{G}, G_{\der{G},1}}\circ g_{\der{G},0}\circ \psi_{D'_0}\circ z_0\\&=\iota_{\der{G}, G_{\der{G},1}}\circ g_{\der{G},0}\circ z_{\der{G},0}
+\end{align*}
+	We conclude again by \Cref{lem:equi}.\qedhere 
+\end{enumerate}
+ \end{proof}
+
+\begin{corollary}\label{cor:swdeco}
 	contenuto...
 \end{corollary}
-
-\fi
 
@@
 
- 		\[\xymatrix{P\ar[r]^{z_0} \ar@{>->}[d]_{p_0}& D'_{0} \ar@{>->}[d]^{f'_{0}} & P \ar@{>->}[d]_{p_0}\ar[r]^-{z_{\der{F},0}} & D_{\der{F}, 0}\ar@{>->}[d]^{f_{\der{F},0}} & D_{\der{F},0}  \ar[d]_{g_{\der{F},0}}& P \ar[r]^{p_1} \ar[l]_-{z_{\der{F},0}} \ar[d]^{z_{\der{F},1}} & D_1 \ar[d]^{g_1}\\ D_0\ar@{>->}[r]_{f_0} & G_0 & D_0\ar@{>->}[r]_{f_0} & G_0 & G_{\der{F},2} & D_{\der{F},1} \ar[r]_-{g_{\der{F},1}} \ar@{>->}[l]^-{f_{\der{F},1}} & G_2}\]
+ 		\[\xymatrix{P\ar@{>->}[r]^{z_0} \ar@{>->}[d]_{p_0}& D'_{0} \ar@{>->}[d]^{f'_{0}} & P \ar@{>->}[d]_{p_0}\ar@{>->}[r]^-{z_{\der{F},0}} & D_{\der{F}, 0}\ar@{>->}[d]^{f_{\der{F},0}} & D_{\der{F},0}  \ar[d]_{g_{\der{F},0}}& P \ar[r]^{p_1} \ar[l]_-{z_{\der{F},0}} \ar[d]^{z_{\der{F},1}} & D_1 \ar[d]^{g_1}\\ D_0\ar@{>->}[r]_{f_0} & G_0 & D_0\ar@{>->}[r]_{f_0} & G_0 & G_{\der{F},2} & D_{\der{F},1} \ar[r]_-{g_{\der{F},1}} \ar@{>->}[l]^-{f_{\der{F},1}} & G_2}\]
 
@@
 			\ar@{>->}[ul]|(.5)\hole_(.65){f_1}&&R_1\ar@/^.6cm/[ddll]^(.2){i'_0}|(.31)\hole|(.81)\hole\ar[dl]_{h_1}|(.6)\hole\\&G_0
-			&&P\ar@{>}[dr]_{z_1}	\ar@{>}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
+			&&P\ar@{>}[dr]_{z_1}	\ar@{>->}[dl]^{z_0}\ar[ur]^(.4){p_1}\ar@{>->}[ul]_(.4){p_0}&&G_2\\L_1	\ar@/^.6cm/[uurr]^(.2){i_1} \ar[ur]_(.35){m'_0}|(.61)\hole && D'_0	\ar@{>->}[ul]|(.4)\hole_(.65){f'_0}\ar[dr]|(.5)\hole_(.65){g'_0}	&&D'_1\ar[ur]|(.4)\hole^(.65){g'_1} \ar@{>->}[dl]|(.5)\hole^(.65){f'_1}	&& R_0 \ar[ul]^(.35){h'_1}|(.61)\hole\ar@/_.6cm/[uull]_(.2){i_0}\\ &K_1	\ar[ur]_{k'_0} \ar[dr]_{r_1}	\ar@{>->}[ul]^{l_1}\ar@/^.6cm/[uurr]_(.65){u_1}&&G'_1&& K_0\ar[ur]_{r_0} \ar[ul]^{k'_1} \ar@{>->}[dl]^{l_0} \ar@/_.6cm/[uull]^(.65){u_0}\\&& R_1	\ar[ur]_{h'_0}\ar@/^.8cm/[uurr]^(.2){i'_0}&& L_0 \ar[ul]^{m'_1} \ar@/_.8cm/[uull]_(.2){i'_1} |(.69)\hole }\]
 
@@
 		\[\xymatrix{P \ar@{>->}[r]^{p_0} \ar@{>->}[d]_{p_1}& D_0 \ar@{>->}[d]^{g_0}  & P \ar@{>}[r]^{z_0} \ar@{>->}[d]_{p_0}& D'_0 \ar@{>->}[d]^{f'_0} &  P \ar@{->}[d]_{z_0} \ar[r]^{z_1} & D'_1 \ar@{>->}[d]^{f'_1} & P\ar[r]^{z_1} \ar[d]_{p_1}&D'_1 \ar[d]^{g'_1}\\ D_1 \ar@{>->}[r]_{f_1} & G_1  & D_0 \ar@{>->}[r]_{f_0} & G_0 & D'_0 \ar[r]_{g'_0}& G'_1 & D_1 \ar[r]_{g_1}& G_2}\]
-		In particular, the arrow $z_0\colon P\to D'_0$ belongs to $\mathcal{M}$.
 	\end{enumerate}
@@
 \section{Switch equivalence and concatenable traces}
-\todo{intro}
-
-Switch equivalence is now defined as the equivalence relating derivations that 
-can be obtained one from another by a sequence of switches. Moreover, intermediate graphs can be taken up to isomorphism according to abstraction equivalence.
-
-\todo{la definizione sotto è da sistemare}
-\begin{definition}[Concrete switching sequence]
+
+We are now ready to define the notion of \emph{concrete switch equivalence}, relating derivations that 
+can be obtained one from another by a sequence of switches.
+
+\begin{definition}[Concrete switching equivalence]
 	\label{de:switch-equivalence}
-	Let $(\X, \R)$ be a left-linear rewriting system.  Let also
-	$\der{D}, \der{E} : G \Mapsto H$ be derivations with the same
-	length, $\der{D}=\{\dder{D}_{i}\}_{i=0}^n$ and
-	$\der{E}=\{\dder{E}_{i}\}_{i=0}^n$. If
-	$\dder{D}_i \cdot \dder{D}_{i+1}$ is a switch of
+	Let $(\X, \R)$ be a left-linear rewriting system.  Let also  $\der{D}:=\{\dder{D}_{i}\}_{i=0}^n$,  	$\der{E}:=\{\dder{E}_{i}\}_{i=0}^n$
+	be two derivations with the same length and the same
+	source $G$ and  target $H$. 	If $\dder{D}_i \cdot \dder{D}_{i+1}$ is a switch of
 	$\dder{E}_i \cdot \dder{E}_{i+1}$ for some $i \in [0,n-1]$ and  $\dder{D}_j = \dder{E}_j$ for each $j \not \in \{i,i+1\}$ then we write
 	$\der{D} \shift{\transp{i}} \der{E}$.
-	A \emph{concrere switching sequence} is a sequence $\{\der{D}_{k}\}_{k=0}^m$
-	of derivations such that
-	$\der{D}_0 \shift{\nu_1} \der{D}_1 \shift{\nu_2} \ldots
-	\shift{\nu_m} \der{D}_m$, where $\nu_{k}$ is the transposition $\transp{i_k}$.
-
-	Two derivations $\der{D}, \der{E}:G\Mapsto H$ are \emph{switch
-		equivalent}, written $\der{D}\equiv^{sh} \der{E}$, if there is a
-	switching sequence $\{\der{D}_{k}\}_{k=0}^m$ such that
-	\begin{itemize}
-		\item $\der{D}_0$ is $\der{D}$ and $\der{D}_m$ is $\der{E}$;
-		\item for every $i\in [0,m-1]$, $\der{D}_i \shift{\transp{h}}\der{D}_{i+1}$ for some $h\in [0, n-1]$.
-	\end{itemize}
-
-	To point out a chosen permutation of rewriting steps, we will also write $\der{D}\equiv^{sh}_{\sigma} \der{E}$, 
-	where $\sigma$ is the composition of the transposition appearing in a chosen switching sequence. 
+
+	A \emph{switching sequence} is a non-empty sequence $\{\der{D}_{k}\}_{k=0}^m$
+	of derivations such that for every $k\in [0,m-1]$, $\der{D}_k \shift{\transp{h}}\der{D}_{k+1}$ for some $h\in [0, n-1]$.
+We will denote by $\nu_{k}$ the permutation $[0,n-1]\to [0,n-1] $ swapping $h$ and $h+1$.
+
+	Two derivations $\der{D}, \der{E}:G\Mapsto H$ are \emph{concretely switch
+		equivalent}, written $\der{D}\equiv^{csh} \der{E}$, if there exists a
+	switching sequence $\{\der{D}_{k}\}_{k=0}^m$ such that $\der{D}_0$ is $\der{D}$ and $\der{D}_m$ is $\der{E}$.
+To point out a chosen permutation of rewriting steps associated to a switching sequence $\{\der{D}_k\}_{k=0}^m$, we will also write $\der{D}\equiv^{sh}_{\sigma} \der{E}$,
+	where $\sigma$ is the composition of the family of permutations $\{\nu_k\}_{k=0}^{m-1}$. 
 \end{definition}
 
+\begin{remark}\label{rem:st}
+	We can notice that all the elements of switching sequence $\{\der{D}_{k}\}_{k=0}^m$ have the same source and the same target.
+\end{remark}
+
+The definining feature of well-switching rewriting systems is that there is at most one independence pair between two adjacent direct derivations.
+Moreover, by \Cref{cor:absequi}, switches are determined up to an abstraction equivalence  with identities as first and last component.
+Thus, we expect that two switching sequences with the same starting point and the same family of transpositions consist of the same direct derivations, up to abstraction equivalence.
+This is exactly the content of the next proposition.
+
 \begin{proposition}
-\todo{Se uso le stesse trasposizioni ho la stessa cosa}
+	Let $\{\der{D}_k\}_{k=0}^m$ and $\{\der{E}_k\}_{k=0}^m$ be two switching sequences.
+Suppose that $\der{D}_0$ and $\der{E}_0$ have the same source and target and that there is an abstraction equivalence $\{\phi_X\}_{\X\in \Deltamin(\der{D}_0)}$ between them such that $\phi_{G}=\id{G}$ and $\phi_{H}=\id{H}$.
+
+	Let $\{\nu_k\}_{k=0}^{m-1}$  and $\{\sigma_k\}_{k=0}^{m-1}$ be the two associated family of permutations and suppose that $\nu_k=\sigma_k$ for every $k\in [0, m-1]$.
+Then for every $k\in [0,m-1]$ there exists an abstraction equivalence $\{\psi_{X}\}_{X\in \Deltamin(\der{D}_k)}$ between $\der{D}_k$ and $\der{E}_k$ with identities as first and last component.
 \end{proposition}
 \begin{proof}
+	We proceed by  induction on $m$.
+
+	\smallskip\noindent $m=0$. In this case there is nothing to proof.
+
+	\smallskip \noindent $m>0$  Let $(i_0, i_1)$ be the independence pair
 
